### 2021-04-01 output/outline/categorical_imperative_1.tex
played around with kroy's CI + doc prep

%
\begin{isabellebody}%
\setisabellecontext{categorical{\isacharunderscore}imperative{\isacharunderscore}{\isadigit{1}}}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
\isacommand{theory}\isamarkupfalse%
\ categorical{\isacharunderscore}imperative{\isacharunderscore}{\isadigit{1}}\ \isakeyword{imports}\ carmojones{\isacharunderscore}DDL{\isacharunderscore}completeness\isanewline
\isanewline
\isakeyword{begin}%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{The Categorical Imperative%
}
\isamarkuptrue%
%
\isamarkupsubsection{Simple Formulation of the Kingdom of Ends%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
This is my first attempt at formalizing the concept of the Kingdom of Ends%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
NOTE: this attempt revealed a bug in my embedding. I've included it as an artifact, but none of these theorems hold anymore (hence the oops).%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ ddlpermissable{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isasymRightarrow}t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}P{\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharparenleft}P\ A{\isacharparenright}\ {\isasymequiv}\ {\isacharparenleft}\isactrlbold {\isasymnot}{\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}A{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{This operator represents permissibility%
}\isanewline
%
\isamarkupcmt{Will be useful when discussing the categorical imperative%
}\isanewline
%
\isamarkupcmt{Something is permissible if it is not prohibited%
}\isanewline
%
\isamarkupcmt{Something is prohibited if its negation is obligatory%
}\isanewline
\isanewline
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ kingdom{\isacharunderscore}of{\isacharunderscore}ends{\isacharunderscore}{\isadigit{1}}{\isacharcolon}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}{\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymbox}\ {\isacharparenleft}P\ A{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isadelimproof
\ \ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{One interpretation of the categorical imperative is that something is obligatory only if it is permissible in every ideal world%
}\isanewline
%
\isamarkupcmt{This formulation mirrors the kingdom of ends.%
}\isanewline
%
\isamarkupcmt{This formulation is already a theorem of carmo and jones' DDL!.%
}\isanewline
%
\isamarkupcmt{It can be shown using the O diamond rule, which just says that obligatory things must be possible.%
}\isanewline
%
\isamarkupcmt{There are two possibilities: either the logic is already quite powerful OR this formulation is ``empty".%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
\isanewline
%
\endisadelimproof
\isanewline
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ kingdom{\isacharunderscore}of{\isacharunderscore}ends{\isacharunderscore}{\isadigit{2}}{\isacharcolon}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}{\isacharparenleft}{\isasymbox}\ {\isacharparenleft}P\ A{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isadelimproof
\ \ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
\isanewline
%
\isamarkupcmt{Notice also that ideally, this relationship does not hold in the reverse direction.%
}\isanewline
%
\isamarkupcmt{Plenty of things are necessarily permissible (drinking water) but not obligatory.%
}\isanewline
%
\isamarkupcmt{Very strange that this is a theorem in this logic.....%
}\isanewline
%
\isamarkupcmt{That being said, Isabelle seems quite upset with this proof and is very slow to resconstruct it%
}\isanewline
%
\isamarkupcmt{I am struggling to recreate this proof on paper%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
\isanewline
%
\endisadelimproof
\isanewline
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ permissible{\isacharunderscore}to{\isacharunderscore}ob{\isacharcolon}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}{\isacharparenleft}P\ A{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isadelimproof
\ \ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{Uh-oh.....this shouldn't be true...%
}\isanewline
%
\isamarkupcmt{Not all permissable things are obligatory.....%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
\isanewline
%
\endisadelimproof
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ weaker{\isacharunderscore}permissible{\isacharunderscore}to{\isacharunderscore}ob{\isacharcolon}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}{\isacharparenleft}{\isasymdiamond}\ {\isacharparenleft}P\ A{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ O\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isadelimproof
\ \ \ \ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{Makes sense that this follows from the reverse kingdom of ends.%
}\isanewline
%
\isamarkupcmt{Obligation and necessity/possibility are separated in this logic%
}\isanewline
%
\isamarkupcmt{Both the dyadic obligation and necessity operator are world agnostic%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
\isanewline
%
\endisadelimproof
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ contradictory{\isacharunderscore}obligations{\isacharcolon}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymTurnstile}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}{\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isadelimproof
\ \ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{What is the cause of the above strangeness?%
}\isanewline
%
\isamarkupcmt{This very intuitive theorem holds in my logic but not in Benzmuller Parent's%
}\isanewline
%
\isamarkupcmt{It's clear that this theorem results in the strange results above.%
}\isanewline
%
\isamarkupcmt{Conclusion: There is a bug in my embedding%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
Sidebar: the above theorem is really intuitive - it seems like we wouldn't want 
contradictory things to be obligatory in any logic. But for some reason, not only is it not
a theorem of Carmo and Jones' logic, it actually implies some strange conclusions, including 
that everything is either permissible or obligatory. It's not clear to me from a semantic 
perspective why this would be the case. In fact this theorem seems like a desirable 
property. Potential avenue for exploration%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
Did some debugging. What was the problem? A misplaced parentheses in the definition 
of ax5b that led to a term being on the wrong side of an implication. Computer Science :(%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
After the debugging, all of this is no longer true! On to the next attempt :)%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
\isacommand{end}\isamarkupfalse%
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/categorical_imperative_1.thy%:%
%:%10=1%:%
%:%11=1%:%
%:%12=2%:%
%:%13=3%:%
%:%27=5%:%
%:%31=7%:%
%:%43=9%:%
%:%47=10%:%
%:%49=12%:%
%:%50=12%:%
%:%51=13%:%
%:%53=14%:%
%:%54=14%:%
%:%56=15%:%
%:%57=15%:%
%:%59=16%:%
%:%60=16%:%
%:%62=17%:%
%:%63=17%:%
%:%64=18%:%
%:%65=19%:%
%:%66=20%:%
%:%67=20%:%
%:%68=21%:%
%:%71=22%:%
%:%75=22%:%
%:%76=22%:%
%:%78=23%:%
%:%79=23%:%
%:%81=24%:%
%:%82=24%:%
%:%84=25%:%
%:%85=25%:%
%:%87=26%:%
%:%88=26%:%
%:%90=27%:%
%:%96=27%:%
%:%99=28%:%
%:%100=29%:%
%:%101=30%:%
%:%102=30%:%
%:%103=31%:%
%:%106=32%:%
%:%110=32%:%
%:%111=32%:%
%:%112=33%:%
%:%114=34%:%
%:%115=34%:%
%:%117=35%:%
%:%118=35%:%
%:%120=36%:%
%:%121=36%:%
%:%123=37%:%
%:%124=37%:%
%:%126=38%:%
%:%132=38%:%
%:%135=39%:%
%:%136=40%:%
%:%137=41%:%
%:%138=41%:%
%:%139=42%:%
%:%142=43%:%
%:%146=43%:%
%:%147=43%:%
%:%149=44%:%
%:%150=44%:%
%:%152=45%:%
%:%158=45%:%
%:%161=46%:%
%:%162=47%:%
%:%163=47%:%
%:%164=48%:%
%:%167=49%:%
%:%171=49%:%
%:%172=49%:%
%:%174=50%:%
%:%175=50%:%
%:%177=51%:%
%:%178=51%:%
%:%180=52%:%
%:%186=52%:%
%:%189=53%:%
%:%190=54%:%
%:%191=54%:%
%:%192=55%:%
%:%195=56%:%
%:%199=56%:%
%:%200=56%:%
%:%202=57%:%
%:%203=57%:%
%:%205=58%:%
%:%206=58%:%
%:%208=59%:%
%:%209=59%:%
%:%211=60%:%
%:%221=63%:%
%:%222=64%:%
%:%223=65%:%
%:%224=66%:%
%:%225=67%:%
%:%226=68%:%
%:%230=70%:%
%:%231=71%:%
%:%235=73%:%
%:%243=75%:%

### 2021-04-02 output/report/paper.tex
rough paper intro + kroy progress

%
\begin{isabellebody}%
\setisabellecontext{paper}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Introduction%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
Leibniz dreamed of modelling all knowledge in the language of formal logic, so that all 
reasoning could be automated. As machines become increasingly capable of mathematical, strategic, 
and scientific reasoning and Leibniz's dream becomes closer to reality, one key gap remains.
Machines lack the ability to perform any meaningful kind of ethical reasoning. Computational 
ethics is a young but attractive field for two primary reasons. First, the proliferation of 
artifically intelligence and autonomous agents is creating and will continue to create a demand for 
ethical autonomous agents. The call for ``ethical AI" can, in one sense, be answered by the creation 
of an automated ethical reasoner. Second, just as automated mathematical reasoning allows mathematicians 
to explore new proofs, automated ethical reasoning is a tool that philosophers can use when reasoning 
about ethics. Many contradictions or paradoxes with an ethical system may not be immediately obvious 
to the human eye, but can be easily tested using an automated theorem prover.

Modelling ethics without sacrificing the intracacies and complexities of an ethical theory is a 
challenging computational and philosophical problem. Many ethical AI systems encode ethics as a series 
of constraints, and they maximize their objective with respect to such constraints. This approach to 
ethics fails to capture much of the complexity of any plausible ethical system. Any faithful model
of an ethical theory will require machinery more complex than a single constraint satisfaction problem.

In addition to the computational machinery, computational ethics also requires a sophisticated 
ethical theory to model. Constraint satisfaction systems often default to some version of utiliarianism, 
the principle of doing the most good for the most people. Alternatively, they model basic moral 
principles such as ``do not kill," without modelling the theory that these principles originated from.
Modelling a more complex ethical theory will not only enable smarter philosophical machines, it will
also empower philosophers to study more complex ethical issues with the computer's help.

The ideal candidate ethical theory will be both philosophically interesting and easy to 
formalize. Kantian ethics, often described as ``formal," is such a candidate. The categorical imperative,
Kant's universal law of morality, is a moral rule that can be used to guide action in all spheres of life.
Kant's original presentation itself is methodical and formal, and the theory lends itself well to 
formalization.

In this paper, I present, implement, and test three formalizations of Kant's categorical imperative 
in the Isabelle/HOL theorem prover. I start with Carmo and Jones' Dyadic Deontic Logic as a base
logic and model each formalization as an extension of DDL. Section 4.3 implements and tests
the naive implementation, a control group that is not much stronger than DDL itself. Section 4.4
examines a more sophisticated implementation inspired by Moshe Kroy's partial formalization of the 
categorical imperative. Section 4.5 explores ????

I contribute implementations of three different interpretations of the categorical imperative, 
examples of how each implementation can be used to model and solve ethical scenarios, and tests that
examine ethical and logical properties of the system, including logical consistency, consistentency
of obligation, and possibility of permissibility. The implementations themselves are usable models 
of ethical principles and the tests represent the kind of philosophical work that formalized ethics 
can contribute.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{System Overview%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
Formalizing an ethical theory requires a choice of formal language to model the theory in, 
the choice of ethical theory itself, and the choice of theorem prover to implement the formal model.
I use as my base the LogiKEY Workbench \cite{BP} project, a framework for modelling ethics using 
deontic logic. Like LogiKEY, I use Carmo and Jones's Dyadic Deontic Logic \cite{CJDDL}. I focus on 
Kant's categorical imperative, using formalizations inspired by all three formulations of the 
categorical imperative. All the programming is done in Isabelle/HOL.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Dyadic Deontic Logic%
}
\isamarkuptrue%
%
\isamarkupsubsection{Kantian Ethics%
}
\isamarkuptrue%
%
\isamarkupsubsection{Isabelle/HOL%
}
\isamarkuptrue%
%
\isamarkupsection{Details%
}
\isamarkuptrue%
%
\isamarkupsubsection{Naive Implementation/Control Group%
}
\isamarkuptrue%
%
\isamarkupsubsection{Kroy's Partial Formalization%
}
\isamarkuptrue%
%
\isamarkupsection{Related Work%
}
\isamarkuptrue%
%
\isamarkupsection{Conclusion%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper.thy%:%
%:%24=6%:%
%:%36=8%:%
%:%37=9%:%
%:%38=10%:%
%:%39=11%:%
%:%40=12%:%
%:%41=13%:%
%:%42=14%:%
%:%43=15%:%
%:%44=16%:%
%:%45=17%:%
%:%46=18%:%
%:%47=19%:%
%:%48=20%:%
%:%49=21%:%
%:%50=22%:%
%:%51=23%:%
%:%52=24%:%
%:%53=25%:%
%:%54=26%:%
%:%55=27%:%
%:%56=28%:%
%:%57=29%:%
%:%58=30%:%
%:%59=31%:%
%:%60=32%:%
%:%61=33%:%
%:%62=34%:%
%:%63=35%:%
%:%64=36%:%
%:%65=37%:%
%:%66=38%:%
%:%67=39%:%
%:%68=40%:%
%:%69=41%:%
%:%70=42%:%
%:%71=43%:%
%:%72=44%:%
%:%73=45%:%
%:%74=46%:%
%:%75=47%:%
%:%76=48%:%
%:%77=49%:%
%:%78=50%:%
%:%79=51%:%
%:%88=53%:%
%:%100=55%:%
%:%101=56%:%
%:%102=57%:%
%:%103=58%:%
%:%104=59%:%
%:%105=60%:%
%:%114=62%:%
%:%118=64%:%
%:%122=66%:%
%:%126=68%:%
%:%130=70%:%
%:%134=72%:%
%:%138=74%:%
%:%142=76%:%

### 2021-04-04 output/report/paper.tex
need to think more about relationship between contradiction and obligation - is it even necessary??

@@
 Leibniz dreamed of modelling all knowledge in the language of formal logic, so that all 
-reasoning could be automated. As machines become increasingly capable of mathematical, strategic, 
-and scientific reasoning and Leibniz's dream becomes closer to reality, one key gap remains.
-Machines lack the ability to perform any meaningful kind of ethical reasoning. Computational 
+reasoning could be automated and all disputes could be solved with calculation. In the 21st 
+century, both the logical and computational machinery exist to make Leibniz's dream a reality. A
+key area of knowlege that can be automated is ethical reasoning. Computational 
 ethics is a young but attractive field for two primary reasons. First, the proliferation of 
-artifically intelligence and autonomous agents is creating and will continue to create a demand for 
-ethical autonomous agents. The call for ``ethical AI" can, in one sense, be answered by the creation 
-of an automated ethical reasoner. Second, just as automated mathematical reasoning allows mathematicians 
-to explore new proofs, automated ethical reasoning is a tool that philosophers can use when reasoning 
-about ethics. Many contradictions or paradoxes with an ethical system may not be immediately obvious 
-to the human eye, but can be easily tested using an automated theorem prover.
+artifically autonomous agents is creating and will continue to create a demand for 
+ethical autonomous agents. One answer to the call for ``ethical AI" is the creation 
+of automated ethical reasoners. Second, just as automated mathematical reasoning gives mathematicians
+new powers and proof-finding ability, automated ethical reasoning is a tool that philosophers can use 
+when reasoning about ethics. Many contradictions or paradoxes with an ethical system may not be 
+immediately obvious to the human eye, but can be easily tested using an automated theorem prover.
 
 Modelling ethics without sacrificing the intracacies and complexities of an ethical theory is a 
-challenging computational and philosophical problem. Many ethical AI systems encode ethics as a series 
-of constraints, and they maximize their objective with respect to such constraints. This approach to 
-ethics fails to capture much of the complexity of any plausible ethical system. Any faithful model
-of an ethical theory will require machinery more complex than a single constraint satisfaction problem.
+challenging computational and philosophical problem. Much prior work encodes ethics as a constraint 
+satisfaction problem, with ethical rules as the constraints. This approach to ethics does not capture 
+all of the complexity of any plausible ethical system. Any faithful model of an ethical theory will 
+require machinery more complex than a single constraint satisfaction problem.
 
-In addition to the computational machinery, computational ethics also requires a sophisticated 
+In addition to computational machinery, computational ethics also requires a sophisticated 
 ethical theory to model. Constraint satisfaction systems often default to some version of utiliarianism, 
@@
 
-In this paper, I present, implement, and test three formalizations of Kant's categorical imperative 
-in the Isabelle/HOL theorem prover. I start with Carmo and Jones' Dyadic Deontic Logic as a base
-logic and model each formalization as an extension of DDL. Section 4.3 implements and tests
-the naive implementation, a control group that is not much stronger than DDL itself. Section 4.4
-examines a more sophisticated implementation inspired by Moshe Kroy's partial formalization of the 
-categorical imperative. Section 4.5 explores ????
+This paper's objective is to automate reasoning about Kantian ethics. I present, implement, and test
+three formalizations of Kant's categorical imperative in the Isabelle/HOL theorem prover. Each 
+formalization is modelled as an extension of Carmo and Jones' Dyadic Deontic Logic (DDL). The corresponding 
+DDL formalization is then embedded in higher-order logic (HOL) and implemented in Isabelle. Section 
+3.1 implements and tests the naive formalization, a control group that is equivalent to DDL 
+itself. Section 3.2 examines a more sophisticated formalization inspired by Moshe Kroy's partial 
+formalization of thecategorical imperative. Section 3.3 explores ????
 
@@
 examples of how each implementation can be used to model and solve ethical scenarios, and tests that
-examine ethical and logical properties of the system, including logical consistency, consistentency
+examine ethical and logical properties of the system, including logical consistency, consistency
 of obligation, and possibility of permissibility. The implementations themselves are usable models 
@@
 \begin{isamarkuptext}%
-Formalizing an ethical theory requires a choice of formal language to model the theory in, 
-the choice of ethical theory itself, and the choice of theorem prover to implement the formal model.
-I use as my base the LogiKEY Workbench \cite{BP} project, a framework for modelling ethics using 
-deontic logic. Like LogiKEY, I use Carmo and Jones's Dyadic Deontic Logic \cite{CJDDL}. I focus on 
-Kant's categorical imperative, using formalizations inspired by all three formulations of the 
-categorical imperative. All the programming is done in Isabelle/HOL.%
+The goal of this project is to automate sophisticated ethical reasoning. This requires three
+key components. First, the choice of an ethical theory that is both intuitively attractive and 
+lends itself to formalization. Second, the choice of formal logic to model the theory in. Third, the 
+choice of automation engine to implement the formal model in. Section 2.1 introduces Kantian
+ethics, Section 2.2 exposits Carmo and Jones's Dyadic Deontic Logic \cite{CJDDL} as a 
+base logic, and Section 3.3 presents the Isabelle/HOL theorem prover used to implement the 
+formalization.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsection{Kantian Ethics%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
+Kantian ethics is an attractive choice of ethical theory to automate for two key reasons. The 
+first is that Kant's writings have been a major inspiration for much of Western analytic philosophy. 
+In addition to the rich neo-Kantian program, almost all major philosophical traditions after Kant have
+engaged with his work, including the logicians of the 20th century. Much of Western libertarian
+political thought is inspired by Kant's deontology, and his ethics have bled into household ethical 
+conversations. Deontology is seen as one of the three major schools of traditional analytic philosophy.
+
+Kantian ethics also lends itself to formalization because of its rule-based structure. Understanding 
+the ethic's potential for formalization requires understanding some of Kant's system. Kant argues 
+that if morality exists, it must take the form of an inviolable rule, which he calls the ``categorical
+imperative." He presents three formulations of the categorical imperative, as well as a robust defense
+of them in his seminal work on ethics. {@cite Groundwork} He argues that all three formulations are 
+equivalent.
+
+The first formulation of the categorical imperative is often called the ``Formula of Universal Law."
+The FUL states ``I ought never to act except in such a way that I could also will that my maxim should 
+become a universal law."{@cite Groundwork} The FUL creates a thought experiment called the universalizability test: to 
+decide if a maxim is permissible, imagine what would happen if everyone willed that maxim. If your 
+imagined world yields a contradiction, the maxim is prohibited. The universalizability test makes the 
+``formal" nature of Kant's ethics immediately clear. Formal logic has the tools to universalize a 
+maxim (apply a universal quantifier) and to test for contradictions (test for inconsistency or 
+validity).
+
+Kant also presents two additional formulations of the categorical imperative. The Formula of Humanity (FUH)
+is to act in such a way "that you use humanity, whether in your own person or in the person
+of any other, always at the same time as an end, never merely as a means." This formulation cements 
+Kant's belief in human dignity. The third formulation of the categorical imperative, often called 
+the Kingdom of Ends, is that "we should so act that we may think of ourselves as legislating universal 
+laws through our maxims." {@cite Korsgaard} These formulations are not as obviously formal as the FUL, 
+but they can still be modelled in logic. Because Kantian ethics presents a series of rules, a logical
+system can encode the theory by modelling each rule as an axiom.
+
+The formal nature of Kant's ethic is not accidental. Kant has been a major influence on the 
+development of modern logic, and the starting point for his ethic is unequivocally reason. The ethic 
+is often criticized for the stringency of its rules, but the unconditional and universal nature of 
+the categorical imperative is precisely what makes it a good candidate for formalization.
+
+The above outline is a brief and incomplete picture of a rich philosophical tradition. Kantian scholars
+debate the meaning of each formulation of the categorical imperative and develop views far more 
+nuanced than those above. For the purposes of this paper, I will adopt Kant's three original 
+formulations presented above. Note additionally that Kantian ethics is widely disputed. Like any 
+ethical theory, Kant's ethic has vocal critics and has inspired philosophical schools in its 
+opposition. I do not present a defense of Kant's ethic in this paper. My approach to formalizing 
+ethics can be applied to other theories as well. I choose Kantian ethics as a case study due to its 
+influence and formality.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \isamarkupsubsection{Dyadic Deontic Logic%
-}
-\isamarkuptrue%
-%
-\isamarkupsubsection{Kantian Ethics%
 }
@@
 %:%79=51%:%
-%:%88=53%:%
-%:%100=55%:%
+%:%80=52%:%
+%:%89=54%:%
 %:%101=56%:%
@@
 %:%105=60%:%
-%:%114=62%:%
-%:%118=64%:%
-%:%122=66%:%
-%:%126=68%:%
-%:%130=70%:%
+%:%106=61%:%
+%:%107=62%:%
+%:%116=64%:%
+%:%128=66%:%
+%:%129=67%:%
+%:%130=68%:%
+%:%131=69%:%
+%:%132=70%:%
+%:%133=71%:%
 %:%134=72%:%
-%:%138=74%:%
-%:%142=76%:%
+%:%135=73%:%
+%:%136=74%:%
+%:%137=75%:%
+%:%138=76%:%
+%:%139=77%:%
+%:%140=78%:%
+%:%141=79%:%
+%:%142=80%:%
+%:%143=81%:%
+%:%144=82%:%
+%:%145=83%:%
+%:%146=84%:%
+%:%147=85%:%
+%:%148=86%:%
+%:%149=87%:%
+%:%150=88%:%
+%:%151=89%:%
+%:%152=90%:%
+%:%153=91%:%
+%:%154=92%:%
+%:%155=93%:%
+%:%156=94%:%
+%:%157=95%:%
+%:%158=96%:%
+%:%159=97%:%
+%:%160=98%:%
+%:%161=99%:%
+%:%162=100%:%
+%:%163=101%:%
+%:%164=102%:%
+%:%165=103%:%
+%:%166=104%:%
+%:%167=105%:%
+%:%168=106%:%
+%:%169=107%:%
+%:%170=108%:%
+%:%171=109%:%
+%:%172=110%:%
+%:%181=112%:%
+%:%185=114%:%
+%:%189=116%:%
+%:%193=118%:%
+%:%197=120%:%
+%:%201=122%:%
+%:%205=124%:%

### 2021-04-05 output/report/categorical_imperative_1.tex
updated bibtex for BFP

--- 2021-04-01 output/outline/categorical_imperative_1.tex
@@
 \ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymTurnstile}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}{\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}\isanewline
 %
@@
 %
-\isamarkupcmt{This very intuitive theorem holds in my logic but not in Benzmuller Parent's%
+\isamarkupcmt{This very intuitive theorem holds in my logic but not in BFP's%
 }\isanewline
@@
 \isamarkupcmt{Conclusion: There is a bug in my embedding%
+}\isanewline
+%
+\isamarkupcmt{Nitpick found a counterexample for card i = 2:
+
+  Free variable:
+    A = ($\lambda x. \_$)($i_1$ := False, $i_2$ := True)%
 }%
@@
 %:%192=55%:%
-%:%195=56%:%
-%:%199=56%:%
-%:%200=56%:%
+%:%193=56%:%
+%:%194=56%:%
+%:%197=57%:%
+%:%201=57%:%
 %:%202=57%:%
-%:%203=57%:%
+%:%204=58%:%
 %:%205=58%:%
-%:%206=58%:%
+%:%207=59%:%
 %:%208=59%:%
-%:%209=59%:%
+%:%210=60%:%
 %:%211=60%:%
-%:%221=63%:%
-%:%222=64%:%
-%:%223=65%:%
-%:%224=66%:%
-%:%225=67%:%
-%:%226=68%:%
-%:%230=70%:%
-%:%231=71%:%
-%:%235=73%:%
-%:%243=75%:%
+%:%213=61%:%
+%:%214=61%:%
+%:%216=62%:%
+%:%217=63%:%
+%:%218=64%:%
+%:%219=65%:%
+%:%229=68%:%
+%:%230=69%:%
+%:%231=70%:%
+%:%232=71%:%
+%:%233=72%:%
+%:%234=73%:%
+%:%238=75%:%
+%:%239=76%:%
+%:%243=78%:%
+%:%251=80%:%

### 2021-04-16 output/document/paper22.tex
file structure and categorical imperative naive

%
\begin{isabellebody}%
\setisabellecontext{paper{\isadigit{2}}{\isadigit{2}}}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Isabelle/HOL Implementation%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
Isabelle/HOL is an interactive proof assistant \cite{isabelle} built on Haskell and Scala. It 
allows the user to define types, functions, definitions, and axiom systems. It has built-in support for both
automatic and interactive/manual theorem proving.

I started my project by reimplementing Benzmueller, Farjami, and Parent's \cite{BFP} \cite{logikey} implementation 
of DDL in Isabelle/HOL. This helped me learn how to use Isabelle/HOL, and the implementation showcased in the 
next few sections demonstrates the power of Isabelle.

BFP use a shallow semantic embedding. This kind of embedding models the semantics of DDL as 
constants in HOL and axioms as constraints on DDL models. This document will contain a subset of my 
implementation that is particularly interesting and relevant to understanding the rest of the project. 
For the complete implementation, see the source code in \isatt{carmojones{\char`\_}DDL.thy}.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{System Definition%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
The first step in embedding a logic in Isabelle is defining the relevant terms and types.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{typedecl}\isamarkupfalse%
\ i\ %
\isamarkupcmt{i is the type for a set of worlds.%
}\isanewline
\isanewline
\isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
\ t\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}i\ {\isasymRightarrow}\ bool{\isacharparenright}{\isachardoublequoteclose}\ %
\isamarkupcmt{t represents a set of DDL formulas.%
}\isanewline
%
\isamarkupcmt{A set of formulae is defined by its truth value at a set of worlds. For example, the set {``True"}
would be true at any set of worlds.%
}\isanewline
%
\begin{isamarkuptext}%
The main accessibility relation that I will use is the $ob$ relation:%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{consts}\isamarkupfalse%
\ ob{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t\ {\isasymRightarrow}\ {\isacharparenleft}t\ {\isasymRightarrow}\ bool{\isacharparenright}{\isachardoublequoteclose}\ \ %
\isamarkupcmt{set of propositions obligatory in this "context"%
}\isanewline
\ %
\isamarkupcmt{ob(context)(term) is True if t is obligatory in this context%
}\isanewline
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Axiomatization%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
For a semantic embedding, axioms are modelled as restrictions on models of the system. In this case,
a model is specificied by the relevant accessibility relations, so it suffices to place conditions on 
the accessibility relations. These axioms can be quite unweildy, so luckily I was able to lift BFP's \cite{BFP}
implementation of Carmo and Jones's original axioms directly. Here's an example of an axiom:%
\end{isamarkuptext}\isamarkuptrue%
\isanewline
\isakeyword{and}\ ax{\isacharunderscore}{\isadigit{5}}d{\isacharcolon}\ {\isachardoublequoteopen}{\isasymforall}X\ Y\ Z{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isasymforall}w{\isachardot}\ Y{\isacharparenleft}w{\isacharparenright}{\isasymlongrightarrow}X{\isacharparenleft}w{\isacharparenright}{\isacharparenright}\ {\isasymand}\ ob{\isacharparenleft}X{\isacharparenright}{\isacharparenleft}Y{\isacharparenright}\ {\isasymand}\ {\isacharparenleft}{\isasymforall}w{\isachardot}\ X{\isacharparenleft}w{\isacharparenright}{\isasymlongrightarrow}Z{\isacharparenleft}w{\isacharparenright}{\isacharparenright}{\isacharparenright}\ \isanewline
\ \ {\isasymlongrightarrow}ob{\isacharparenleft}Z{\isacharparenright}{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isacharparenleft}Z{\isacharparenleft}w{\isacharparenright}\ {\isasymand}\ {\isasymnot}X{\isacharparenleft}w{\isacharparenright}{\isacharparenright}\ {\isasymor}\ Y{\isacharparenleft}w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{If some subset Y of X is obligatory in the context X, then in a larger context Z,
 any obligatory proposition must either be in Y or in Z-X. Intuitively, expanding the context can't 
cause something unobligatory to become obligatory, so the obligation operator is monotonically increasing
 with respect to changing contexts.%
}\isanewline
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Syntax%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
The syntax that I will work with is defined as abbreviations. Each DDL operator is represented 
as a HOL formula. A formula defined with the \isatt{abbreviation} command is unfolded in every 
instance. While the shallow embedding is generally performant (because it uses Isabelle's original 
syntax tree), abbreviations may possibly hurt performance. In some complicated proofs, we want controlled
unfolding. Benzmueller and Parent told me that eventually, the performance cost of abbreviations can 
be mitigated using a definition instead.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
Modal operators will be useful for my purposes, but the implementation is pretty standard.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ ddlbox{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isasymRightarrow}t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymbox}{\isachardoublequoteclose}{\isacharparenright}\ \isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymbox}\ A\ {\isasymequiv}\ {\isasymlambda}w{\isachardot}{\isasymforall}y{\isachardot}\ A{\isacharparenleft}y{\isacharparenright}{\isachardoublequoteclose}\ \isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ ddldiamond{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t\ {\isasymRightarrow}\ t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymdiamond}{\isachardoublequoteclose}{\isacharparenright}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymdiamond}A\ {\isasymequiv}\ \isactrlbold {\isasymnot}{\isacharparenleft}{\isasymbox}{\isacharparenleft}\isactrlbold {\isasymnot}A{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
\begin{isamarkuptext}%
The most important operator for our purposes is the obligation operator.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ ddlob{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isasymRightarrow}t{\isasymRightarrow}t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}O{\isacharbraceleft}{\isacharunderscore}{\isacharbar}{\isacharunderscore}{\isacharbraceright}{\isachardoublequoteclose}{\isacharparenright}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}O{\isacharbraceleft}B{\isacharbar}A{\isacharbraceright}\ {\isasymequiv}\ {\isasymlambda}\ w{\isachardot}\ ob{\isacharparenleft}A{\isacharparenright}{\isacharparenleft}B{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{O$\{B \vert A\}$ can be read as ``B is obligatory in the context A"%
}\isanewline
%
\begin{isamarkuptext}%
While DDL is powerful because of its support for a dyadic obligation operator, in many cases 
we need a monadic obligation operator. Below is some syntactic sugar for a monadic obligation operator.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ ddltrue{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymtop}{\isachardoublequoteclose}{\isacharparenright}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymtop}\ {\isasymequiv}\ {\isasymlambda}w{\isachardot}\ True{\isachardoublequoteclose}\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ ddlob{\isacharunderscore}normal{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isasymRightarrow}t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}O\ {\isacharbraceleft}{\isacharunderscore}{\isacharbraceright}{\isachardoublequoteclose}{\isacharparenright}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}\ {\isasymequiv}\ {\isacharparenleft}O{\isacharbraceleft}A{\isacharbar}\isactrlbold {\isasymtop}{\isacharbraceright}{\isacharparenright}\ {\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{Intuitively, the context \texttt{True} is the widest context possible because \texttt{True} holds at all worlds.%
}%
\begin{isamarkuptext}%
Validity will be useful when discussing metalogical/ethical properties.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ ddlvalid{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isasymRightarrow}bool{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymTurnstile}{\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymTurnstile}A\ {\isasymequiv}\ {\isasymforall}w{\isachardot}\ A\ w{\isachardoublequoteclose}\isanewline
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Syntactic Properties%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
One way to show that a semantic embedding is complete is to show that the syntactic specification
of the theory (axioms) are valid for this semantics - so to show that every axiom holds at every 
world. BFP \cite{BFP} provide a complete treatment of the completeness of their embedding, but I 
will include selected axioms that are particularly interesting here. This section also demonstrates many
of the relevant features of Isabelle/HOL for my project.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
\textbf{Consistency}%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ True\ \isacommand{nitpick}\isamarkupfalse%
\ {\isacharbrackleft}satisfy{\isacharcomma}user{\isacharunderscore}axioms{\isacharcomma}format{\isacharequal}{\isadigit{2}}{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{by}\isamarkupfalse%
\ simp\isanewline
%
\isamarkupcmt{Isabelle has built-in support for Nitpick, a model checker. 
Nitpick successfully found a model satisfying these axioms so the system is consistent.\cite{hintikka}%
}\isanewline
%
\isamarkupcmt{\color{blue} Nitpick found a model for card i = 1:

  Empty assignment \color{black}%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
{\color{red} Nitpick} \cite{nitpick} can generate models or countermodels, so it's useful to falsify potential
theorems, as well as to show consistency. {\color{red} by simp} indicates the proof method. In this 
case, {\color{red} simp} indicates the Simplification proof method, which involves unfolding definitions
and applying theorems directly. HOL has $True$ as a theorem, which is why this theorem was so easy to prove.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper22.thy%:%
%:%24=6%:%
%:%36=8%:%
%:%37=9%:%
%:%38=10%:%
%:%39=11%:%
%:%40=12%:%
%:%41=13%:%
%:%42=14%:%
%:%43=15%:%
%:%44=16%:%
%:%45=17%:%
%:%46=18%:%
%:%47=19%:%
%:%56=22%:%
%:%68=24%:%
%:%70=26%:%
%:%71=26%:%
%:%72=26%:%
%:%73=26%:%
%:%74=27%:%
%:%75=28%:%
%:%76=28%:%
%:%77=28%:%
%:%78=28%:%
%:%80=29%:%
%:%81=30%:%
%:%82=30%:%
%:%85=44%:%
%:%87=46%:%
%:%88=46%:%
%:%89=46%:%
%:%90=46%:%
%:%91=47%:%
%:%92=47%:%
%:%93=47%:%
%:%101=51%:%
%:%113=53%:%
%:%114=54%:%
%:%115=55%:%
%:%116=56%:%
%:%118=80%:%
%:%119=81%:%
%:%120=82%:%
%:%122=83%:%
%:%123=84%:%
%:%124=85%:%
%:%125=86%:%
%:%126=86%:%
%:%134=93%:%
%:%146=95%:%
%:%147=96%:%
%:%148=97%:%
%:%149=98%:%
%:%150=99%:%
%:%151=100%:%
%:%155=116%:%
%:%157=117%:%
%:%158=117%:%
%:%159=118%:%
%:%160=119%:%
%:%161=119%:%
%:%162=120%:%
%:%164=122%:%
%:%166=123%:%
%:%167=123%:%
%:%168=124%:%
%:%170=125%:%
%:%171=125%:%
%:%174=145%:%
%:%175=146%:%
%:%177=147%:%
%:%178=147%:%
%:%179=148%:%
%:%180=149%:%
%:%181=149%:%
%:%182=150%:%
%:%184=151%:%
%:%187=153%:%
%:%189=154%:%
%:%190=154%:%
%:%191=155%:%
%:%199=162%:%
%:%211=164%:%
%:%212=165%:%
%:%213=166%:%
%:%214=167%:%
%:%215=168%:%
%:%219=170%:%
%:%221=171%:%
%:%222=171%:%
%:%223=171%:%
%:%225=171%:%
%:%229=171%:%
%:%230=171%:%
%:%232=172%:%
%:%233=173%:%
%:%234=173%:%
%:%236=174%:%
%:%237=175%:%
%:%238=176%:%
%:%248=178%:%
%:%249=179%:%
%:%250=180%:%
%:%251=181%:%

### 2021-04-16 paper/output/document/paper31.tex
file structure and categorical imperative naive

%
\begin{isabellebody}%
\setisabellecontext{paper{\isadigit{3}}{\isadigit{1}}}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{The Categorical Imperative%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In this section, I will present three formulations of the categorical imperative. In Section 3.1, I will 
consider a simple, naive formulation of the formula of universal law. This formulation is, as I will 
show, clearly not a good ethical rule. The purpose of this section is to explore the kinds of ethical
tests that Isabelle can carry out. In Section 3.2, I will explore Moshe Kroy's \cite{kroy} partial formalization of 
the first two formulations of the categorical imperative. I will also explore drawbacks of this attempt, 
particularly in the lack of the machinery to handle the important Kantian concept of a maxim: an action 
performed for a particular end. In Section 3.3, I will present my own improved
formalization of the categorical imperative.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Naive Formulation of the Formula of Universal Law%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
This section presents a simple and intuitive formalization of the formula of universal law, which 
is to will only those maxims that you would simultaneously will universalized. The universalizability 
test presents negative obligations: if a maxim passes the universalizability test, it is permissible. Else,
it is prohibited. In order to appropriately formalize this, we need some notion of permissibility.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ ddlpermissable{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isasymRightarrow}t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}P{\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharparenleft}P\ A{\isacharparenright}\ {\isasymequiv}\ {\isacharparenleft}\isactrlbold {\isasymnot}{\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}A{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{An act $A$ is permissible if its negation is not obligated. For example, buying a red folder is 
permissible because I am not requires to refrain from buying a red folder.%
}%
\begin{isamarkuptext}%
This naice formalization will require very little additional logical machinery, but more complex
formalizations may require additional logic concepts beyond just that of permissibility.

Let's now consider a naive reading of the Formula of Universal Law (FUL): 'act only in accordance 
with that maxim through which you can at the same time will that it become a universal law' \cite{groundwork}.
An immediate translation to DDL is that if A is not necessary permissible then it is prohibited. In other
words, if we cannot universalize $P A$ (where universalizing is represented by the modal necessity 
operator), then $A$ is prohibited. Let's add this as an axiom to our logic.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{axiomatization}\isamarkupfalse%
\ \isakeyword{where}\isanewline
FUL{\isacharunderscore}{\isadigit{1}}{\isacharcolon}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}{\isacharparenleft}{\isasymbox}\ {\isacharparenleft}P\ A{\isacharparenright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}O\ {\isacharbraceleft}{\isacharparenleft}\isactrlbold {\isasymnot}A{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
\begin{isamarkuptext}%
Why add the categorical imperative as an axiom of this logic? The purpose of this logic is to 
perform ethical reasoning. Kant's ethical theory is rule based, so it involves applying the categorical
imperative to solve ethical dilemmas. In logic, this is equivalent to adopting the categorical imperative as 
an axiom and then reasoning in the newly formed logic to come to ethical conclusions. Adding the categorical
imperative as an axiom makes it impossible to violate it.

Note that in this system, reasoning about violations of obligation is difficult. Any violation of the 
categorical imperative immediately results in a contradiction. Developing a Kantian account of contrary-
to-duty obligations is a much larger philosophical project that is still open \cite{KorsgaardRTL}. This paper will focus 
on the classical Kantian notion of an ideal moral world \cite{idealtheory}.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/paper31.thy%:%
%:%24=7%:%
%:%36=9%:%
%:%37=10%:%
%:%38=11%:%
%:%39=12%:%
%:%40=13%:%
%:%41=14%:%
%:%42=15%:%
%:%43=16%:%
%:%52=18%:%
%:%64=20%:%
%:%65=21%:%
%:%66=22%:%
%:%67=23%:%
%:%69=25%:%
%:%70=25%:%
%:%71=26%:%
%:%73=27%:%
%:%74=28%:%
%:%77=36%:%
%:%78=37%:%
%:%79=38%:%
%:%80=39%:%
%:%81=40%:%
%:%82=41%:%
%:%83=42%:%
%:%84=43%:%
%:%86=45%:%
%:%87=45%:%
%:%88=46%:%
%:%90=48%:%
%:%91=49%:%
%:%92=50%:%
%:%93=51%:%
%:%94=52%:%
%:%95=53%:%
%:%96=54%:%
%:%97=55%:%
%:%98=56%:%
%:%99=57%:%

### 2021-04-16 paper/output/report/paper.tex
file structure and categorical imperative naive

%
\begin{isabellebody}%
\setisabellecontext{paper}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
\ \ \isakeyword{imports}\ Main\isanewline
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Introduction%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
As artifical reasoners become increasingly powerful, computers become increasingly able to 
perform complex ethical reasoning. The field of machine ethics \cite{mesurvey} is attractive for two reasons.
First, the proliferation of artifically autonomous agents is creating and will continue to create a demand for 
ethical autonomous agents. These agents must be able to model and reason about complex ethical theories 
that withstand philosophical scrutiny. Second, just as automated mathematical reasoning gives mathematicians
new powers and proof-finding ability, automated ethical reasoning is a tool that philosophers can use 
when reasoning about ethics. Many contradictions or paradoxes with an ethical system may not be 
immediately obvious to the human eye, but can be easily tested using an automated theorem prover.

Modelling ethics without sacrificing the intracacies and complexities of an ethical theory is a 
challenging computational and philosophical problem. Simple and intuitive computational approaches, 
such as encoding ethical rules as constraints in a constraint satisfaction problem, fail to capture
the complexity of most philosophically plausible systems. On the other hand, it is not immediately clear
how to formalize many complex moral theories, like virtue ethics.

Computational ethics also requires a sophisticated 
ethical theory to model. Constraint satisfaction systems often default to some version of utiliarianism, 
the principle of doing the most good for the most people. Alternatively, they model basic moral 
principles such as ``do not kill," without modelling the theory that these principles originated from.
Modelling a more complex ethical theory will not only enable smarter philosophical machines, it will
also empower philosophers to study more complex ethical issues with the computer's help. The entire
field of philosophy is devoted to developing and testing robust ethical theories. Plausible machine
ethics must draw on plausible moral philosophy.

The ideal candidate ethical theory will be both philosophically interesting and easy to 
formalize. Kantian ethics, often described as ``formal," has been often floated as such a candidate \cite{powers} \cite{BL}. 
The categorical imperative, Kant's universal law of morality, is a moral rule that can be used to 
guide action.

This project's objective is to automate reasoning about Kantian ethics. I present two different
formalizations of Kant's categorical imperative implemented and tested in the Isabelle/HOL \cite{isabelle} theorem prover.
Each formalization is modelled as an extension of Carmo and Jones' Dyadic Deontic Logic (DDL). The corresponding 
DDL formalization is then embedded in higher-order logic (HOL) and implemented in Isabelle. Section 
3.1 implements and tests the naive formalization, a control group that is equivalent to DDL 
itself. Section 3.2 examines a more sophisticated formalization inspired by Moshe Kroy's partial 
formalization of thecategorical imperative.

I contribute implementations of two different interpretations of the categorical imperative, 
examples of how each implementation can be used to model and solve ethical scenarios, and tests that
examine ethical and logical properties of the system, including logical consistency, consistency
of obligation, and possibility of permissibility. The implementations themselves are usable models 
of ethical principles and the tests represent the kind of philosophical work that formalized ethics 
can contribute.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{System Overview \label{sec:overview}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
The goal of this project is to automate sophisticated ethical reasoning. This requires three
components. First, the choice of an ethical theory that is both intuitively attractive and 
lends itself to formalization. Second, the choice of formal logic to model the theory in. Third, the 
choice of automation engine to implement the formal model in. Section 2.1 introduces Kantian
ethics, Section 2.2 explains Carmo and Jones's Dyadic Deontic Logic \cite{CJDDL} as a 
base logic, and Section 2.3 presents the Isabelle/HOL implementation of the logic.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Kantian Ethics \label{sec:kant}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
Kantian ethics is an attractive choice of ethical theory to automate for two reasons. The 
first is that Kant's writings have been a major inspiration for much of Western analytic philosophy. 
In addition to the rich neo-Kantian program, almost all major philosophical traditions after Kant have
engaged with his work. Much of Western libertarian political thought is inspired by Kant's deontology,
and his ethics have bled into household ethical thought. Deontology is seen as one of the three major 
schools of Western normative philosophy.

Understanding the ethic's potential for formalization requires understanding Kant's system. Kant argues 
that if morality exists, it must take the form of an inviolable rule, which he calls the ``categorical
imperative." He presents three formulations of the categorical imperative, as well as a robust defense
of them in his seminal work on ethics \cite{groundwork}. He argues that all three formulations are 
equivalent.

The first formulation of the categorical imperative is the ``Formula of Universal Law."

$\textbf{Definition}$ \emph{(Formula of Universal Law)}

\emph{I ought never to act except in such a way that I could also will that my maxim should become a universal law} \cite{groundwork}

A ``maxim" is roughly a moral rule like ``I can murder someone to take their job". ``Willing" a maxim is 
equivalent to acting on that rule. The FUL creates a thought experiment called the universalizability 
test: to decide if a maxim is permissible, imagine what would happen if everyone willed that maxim. 
If your imagined world yields a contradiction, the maxim is prohibited. Intuitively, the FUL asks 
the question, "What would happen if everyone did that?" \cite{KorsgaardFUL}.

The universalizability test makes the ``formal" nature of Kant's ethics immediately clear. Formal 
logic has the tools to universalize a maxim (apply a universal quantifier) and to test for 
contradictions (test for inconsistency).

Kant also presents two additional formulations of the categorical imperative.

$\textbf{Definition}$ \emph{(Formula of Humanity)}

\emph{The Formula of Humanity (FUH)
is to act in such a way "that you use humanity, whether in your own person or in the person
of any other, always at the same time as an end, never merely as a means."}\cite{groundwork}

\medskip

$\textbf{Definition}$ \emph{(Kingdom of Ends)}

\emph{The third formulation of the categorical imperative states that "we should so act that we may 
think of ourselves as legislating universal laws through our maxims."}\cite{KorsgaardFUL}

The last two formulations are not as obviously formal as the FUL, but they can still be
modelled in logic. Because Kantian ethics presents a series of rules, a logical system can encode 
the theory by modelling each rule as an axiom.

The above outline is a brief and incomplete picture of a rich philosophical tradition. Kantian scholars
debate the meaning of each formulation of the categorical imperative and develop views far more 
nuanced than those above. For the purposes of this paper, I will adopt Kant's three original 
formulations presented above. Note additionally that Kantian ethics is widely disputed. I do not present 
a defense of Kant's ethic in this paper. My approach to formalizing ethics can be applied to other 
theories as well.

This paper aims to formalize Kant's ethic as faithfully as possible. This is an important choice. 
While it is tempting to modify or simplify an ethical theory in seemingly insignificant way, these 
choices often have ramifications. The entire field of neo-Kantian thought 
has been exploring versions of Kant's ethical theory for centuries. I will not attempt to present a 
radically new conception of Kant's ethic, but will instead draw on philosophical expertise regarding
the content and justification of the categorical imperative.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Dyadic Deontic Logic%
}
\isamarkuptrue%
%
\isamarkupsubsubsection{Deontic Logic%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
Traditional modal logics include $\Box$ operators to represent necessity. In simple modal logics like S5 \cite{cresswell} 
using the Kripke semantics, $\Box p$ is true at a world $w$ if $p$ is true at all of $w$'s neighbors. 
These logics also usually contain the $\diamond$ operator, representing possibility, where
 $\diamond p \iff \sim \Box \sim p$. Additionally, modal logics support operators of propositional 
logic like $\sim, \wedge, \vee, \rightarrow$.

A deontic logic is a special kind of modal logic designed to reason about obligation. Standard deontic
logic \cite{cresswell} \cite{sep-logic-deontic} essentially replaces $\Box$ with the obligation operator
$O$, and $\diamond$ with the permissibility operator $P$. Using the Kripke semantics for $O$, $O p$ 
is true at $w$ if $p$ is true at all  ideal deontic alternatives to $w$. The $O$ operator in SDL
takes a single argument (the formula that is obligatory), and is thus called a monadic deontic operator.

 While SDL is appreciable for its simplicity, it suffers a variety of well-documented paradoxes, 
including contrary-to-duty paradoxes \cite{ctd}. In situations where duty is violated, the logic breaks down 
and produces paradoxical results. Thus, I use an improved deontic logic instead of SDL for this work.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Dyadic Deontic Logic%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
I use as my base logic Carmo and Jones's dyadic deontic logic, or DDL, which improves on SDL \cite{CJDDL}. 
It introduces a dyadic obligation operator $O\{A \vert B\}$ 
to represent the sentence ``A is obligated in the context B". This gracefully handles contrary-to-duty
conditionals. The obligation operator uses a neighborhood semantics \cite{neighborhood1}\cite{neighborhood2}, instead of the Kripke semantics. 
Carmo and Jones define a function $ob$ that maps from worlds to sets of sets of worlds. Intuitively, 
each world is mapped to the set of propositions obligated at that world, where a proposition $p$ is defined as 
the worlds at which the $p$ is true.

DDL also includes many other modal operators. In addition to $\Box$ and $\diamond$, DDL also has a notion
of actual obligation and possible obligation, represented by operators $O_a$ and $O_p$ respectively. 
These notions are accompanied by the corresponding modal operators $\Box_a, \diamond_a, \Box_p, \diamond_p$. 
These operators use a Kripke semantics, with the functions $av$ and $pv$ mapping a world $w$ to the set 
of corresponding actual or possible versions of $w$.

For more of fine-grained properties of DDL see \cite{CJDDL} or this project's source code. DDL is quite a heavy logic and contains many modal operators 
that aren't necessary for my analysis. While this expressivity is powerful, it may also cause performance
impacts. In particular, DDL has a large set of axioms involving quantification over complex higher-order
logical expressions. Proofs involving these axioms will be computationally expensive.  Benzmueller 
and Parent warned me that this may become a problem if Isabelle's automated proof tools begin to time out.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/paper.thy%:%
%:%10=2%:%
%:%25=6%:%
%:%37=8%:%
%:%38=9%:%
%:%39=10%:%
%:%40=11%:%
%:%41=12%:%
%:%42=13%:%
%:%43=14%:%
%:%44=15%:%
%:%45=16%:%
%:%46=17%:%
%:%47=18%:%
%:%48=19%:%
%:%49=20%:%
%:%50=21%:%
%:%51=22%:%
%:%52=23%:%
%:%53=24%:%
%:%54=25%:%
%:%55=26%:%
%:%56=27%:%
%:%57=28%:%
%:%58=29%:%
%:%59=30%:%
%:%60=31%:%
%:%61=32%:%
%:%62=33%:%
%:%63=34%:%
%:%64=35%:%
%:%65=36%:%
%:%66=37%:%
%:%67=38%:%
%:%68=39%:%
%:%69=40%:%
%:%70=41%:%
%:%71=42%:%
%:%72=43%:%
%:%73=44%:%
%:%74=45%:%
%:%75=46%:%
%:%76=47%:%
%:%77=48%:%
%:%78=49%:%
%:%79=50%:%
%:%88=52%:%
%:%100=54%:%
%:%101=55%:%
%:%102=56%:%
%:%103=57%:%
%:%104=58%:%
%:%105=59%:%
%:%114=61%:%
%:%126=63%:%
%:%127=64%:%
%:%128=65%:%
%:%129=66%:%
%:%130=67%:%
%:%131=68%:%
%:%132=69%:%
%:%133=70%:%
%:%134=71%:%
%:%135=72%:%
%:%136=73%:%
%:%137=74%:%
%:%138=75%:%
%:%139=76%:%
%:%140=77%:%
%:%141=78%:%
%:%142=79%:%
%:%143=80%:%
%:%144=81%:%
%:%145=82%:%
%:%146=83%:%
%:%147=84%:%
%:%148=85%:%
%:%149=86%:%
%:%150=87%:%
%:%151=88%:%
%:%152=89%:%
%:%153=90%:%
%:%154=91%:%
%:%155=92%:%
%:%156=93%:%
%:%157=94%:%
%:%158=95%:%
%:%159=96%:%
%:%160=97%:%
%:%161=98%:%
%:%162=99%:%
%:%163=100%:%
%:%164=101%:%
%:%165=102%:%
%:%166=103%:%
%:%167=104%:%
%:%168=105%:%
%:%169=106%:%
%:%170=107%:%
%:%171=108%:%
%:%172=109%:%
%:%173=110%:%
%:%174=111%:%
%:%175=112%:%
%:%176=113%:%
%:%177=114%:%
%:%178=115%:%
%:%179=116%:%
%:%180=117%:%
%:%181=118%:%
%:%182=119%:%
%:%183=120%:%
%:%184=121%:%
%:%185=122%:%
%:%186=123%:%
%:%195=127%:%
%:%199=129%:%
%:%211=131%:%
%:%212=132%:%
%:%213=133%:%
%:%214=134%:%
%:%215=135%:%
%:%216=136%:%
%:%217=137%:%
%:%218=138%:%
%:%219=139%:%
%:%220=140%:%
%:%221=141%:%
%:%222=142%:%
%:%223=143%:%
%:%224=144%:%
%:%225=145%:%
%:%234=147%:%
%:%246=149%:%
%:%247=150%:%
%:%248=151%:%
%:%249=152%:%
%:%250=153%:%
%:%251=154%:%
%:%252=155%:%
%:%253=156%:%
%:%254=157%:%
%:%255=158%:%
%:%256=159%:%
%:%257=160%:%
%:%258=161%:%
%:%259=162%:%
%:%260=163%:%
%:%261=164%:%
%:%262=165%:%
%:%263=166%:%
%:%264=167%:%

### 2021-04-18 paper/output/document/paper31.tex
finished the naive formulation, kroy next

@@
 \isamarkupcmt{An act $A$ is permissible if its negation is not obligated. For example, buying a red folder is 
-permissible because I am not requires to refrain from buying a red folder.%
+permissible because I am not required to refrain from buying a red folder.%
 }%
 \begin{isamarkuptext}%
-This naice formalization will require very little additional logical machinery, but more complex
+This naive formalization will require very little additional logical machinery, but more complex
 formalizations may require additional logic concepts beyond just that of permissibility.
@@
 to-duty obligations is a much larger philosophical project that is still open \cite{KorsgaardRTL}. This paper will focus 
-on the classical Kantian notion of an ideal moral world \cite{idealtheory}.%
+on the classical Kantian notion of an ideal moral world \cite{idealtheory}.
+
+The immediate test for any formalization is consistency, which we can check with Nitpick.%
 \end{isamarkuptext}\isamarkuptrue%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\isatagdocument
-%
-\endisatagdocument
-{\isafolddocument}%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
+\isacommand{lemma}\isamarkupfalse%
+\ True\ \isacommand{nitpick}\isamarkupfalse%
+\ {\isacharbrackleft}satisfy{\isacharcomma}user{\isacharunderscore}axioms{\isacharcomma}format{\isacharequal}{\isadigit{2}}{\isacharbrackright}%
 \isadelimproof
-%
+\ %
 \endisadelimproof
@@
 \isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
 %
+\isamarkupcmt{\color{blue} Nitpick found a model for card i = 1:
+
+  Empty assignment \color{black}%
+}\isanewline
+%
+\isamarkupcmt{Nitpick tells us that the FUL is consistent%
+}%
 \endisatagproof
@@
 %
+\isamarkupsubsubsection{Specifying the Model%
+}
+\isamarkuptrue%
+%
 \endisatagdocument
@@
 \endisadelimdocument
+%
+\begin{isamarkuptext}%
+One category of tests is specified models. Specifying the model allows us to encode certain facts 
+into the system and then ask questions about obligations. Without specifying the model, we are limited 
+to showing high-level metaethical facts. Let's start with analyzing an obvious example - that murder is 
+wrong.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{consts}\isamarkupfalse%
+\ M{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isachardoublequoteclose}\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ murder{\isacharunderscore}wrong{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}murder{\isacharunderscore}wrong\ {\isasymequiv}\ {\isasymTurnstile}{\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ M{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
 %
@@
 \isadelimproof
+\isanewline
 %
 \endisadelimproof
+\isacommand{abbreviation}\isamarkupfalse%
+\ poss{\isacharunderscore}murder{\isacharunderscore}wrong{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}poss{\isacharunderscore}murder{\isacharunderscore}wrong\ {\isasymequiv}\ {\isasymTurnstile}{\isacharparenleft}{\isasymdiamond}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ M{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{These are very simple properties. \isa{poss{\isacharunderscore}murder{\isacharunderscore}wrong} is an abbreviation for the axiom
+that there is some world where murder might be prohibited. Even this is quite a strong assumption - 
+ideally we'd want to give the system nonmoral facts about murder (like a definition) and then make 
+moral claims.%
+}\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ wrong{\isacharunderscore}if{\isacharunderscore}posibly{\isacharunderscore}wrong{\isacharcolon}\isanewline
+\ \ \isakeyword{assumes}\ poss{\isacharunderscore}murder{\isacharunderscore}wrong\isanewline
+\ \ \isakeyword{shows}\ murder{\isacharunderscore}wrong\isanewline
 %
 \isadelimproof
-%
+\ \ %
 \endisadelimproof
@@
 \isatagproof
+\isacommand{using}\isamarkupfalse%
+\ assms\ \isacommand{by}\isamarkupfalse%
+\ blast\isanewline
 %
+\isamarkupcmt{This lemma gets to the ``heart" of this naive interpretation. We really want to say that if something
+ isn't necessarily obligated, it's not obligated anywhere. "%
+}%
 \endisatagproof
@@
 %
+\begin{isamarkuptext}%
+The above example does exactly what we expect it to: we show that if something is wrong somewhere 
+it's wrong everywhere. That being said, it seems like quite a weak claim. We assumed a very strong, moral 
+fact about murder (that it is wrong somewhere), so of course we were able to reach our desired conclusion.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+Let's try a weaker assumption: Not everyone can lie.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{typedecl}\isamarkupfalse%
+\ person\isanewline
+\isacommand{consts}\isamarkupfalse%
+\ lie{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}person{\isasymRightarrow}t{\isachardoublequoteclose}\isanewline
+\isacommand{consts}\isamarkupfalse%
+\ me{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}person{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Notice that this machinery is quite empty. We don't give an axioms about what a person can or can't do.%
+}\isanewline
+\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ lying{\isacharunderscore}not{\isacharunderscore}universal{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}lying{\isacharunderscore}not{\isacharunderscore}universal\ {\isasymequiv}\ {\isasymnot}\ {\isacharparenleft}{\isasymforall}x{\isachardot}\ lie{\isacharparenleft}x{\isacharparenright}\ cw{\isacharparenright}\ {\isasymand}\ {\isacharparenleft}lie{\isacharparenleft}me{\isacharparenright}\ cw{\isacharparenright}{\isachardoublequoteclose}%
+\begin{isamarkuptext}%
+This is a rough translation of failure of the universalizability test: we will the maxim universally,
+as represented by the universal quantifier in the first conjunct, and simulataneously \cite{simul}, as represented by 
+the second conjunct. The FUL tells us that if this sentence is true, then lying should be prohibited. 
+Let's test it.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ breaking{\isacharunderscore}promises{\isacharcolon}\isanewline
+\ \ \isakeyword{assumes}\ lying{\isacharunderscore}not{\isacharunderscore}universal\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}lie{\isacharparenleft}me{\isacharparenright}{\isacharparenright}{\isacharbraceright}{\isacharparenright}\ cw{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}\isanewline
+%
 \isadelimproof
-%
+\ \ %
 \endisadelimproof
@@
 \isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
 %
+\isamarkupcmt{\color{blue} Nitpick found a counterexample for card person = 2 and card i = 2:
+
+  Free variable:
+    lie = ($\lambda x. \_$)($p_1$ := ($\lambda x. \_$)($i_1$ := True, $i_2$ := False), $p_2$ := ($\lambda x. \_$)($i_1$ := False, $i_2$ := False)) \color{black}%
+}%
 \endisatagproof
@@
 %
+\begin{isamarkuptext}%
+This formula isn't valid. While the FUL should tell us that lying is prohibited, the fact that it 
+doesn't demonstrates the weakness of this naive formulation of the categorical imperative. Kant's version of
+the FUL universalizes across people, as we did in the definition of \isa{lying{\isacharunderscore}not{\isacharunderscore}universal\ {\isasymequiv}\ {\isasymnot}\ {\isacharparenleft}{\isasymforall}x{\isachardot}\ lie\ x\ cw{\isacharparenright}\ {\isasymand}\ lie\ me\ cw}.
+The
+naive formalization universalizes across worlds using the $\Box$ operator, so it makes sense that it can't
+handle this example appropriately.
+
+The above implies that the FUL should prescribe consistent obligations across people. If our formalization
+doesn't, clearly something has gone wrong somewhere. Let's test that!%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ universalizability{\isacharcolon}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymTurnstile}\ O\ {\isacharbraceleft}{\isacharparenleft}lie{\isacharparenleft}me{\isacharparenright}{\isacharparenright}{\isacharbraceright}{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}x{\isachardot}\ {\isasymTurnstile}\ {\isacharparenleft}O\ {\isacharbraceleft}{\isacharparenleft}lie{\isacharparenleft}x{\isacharparenright}{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
 \isadelimproof
-%
+\ %
 \endisadelimproof
@@
 \isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
 %
+\isamarkupcmt{\color{blue} Nitpick found a counterexample for card person = 2 and card i = 2:
+
+  Free variable:
+    lie = ($\lambda x. \_$)($p_1$ := ($\lambda x. \_$)($i_1$ := False, $i_2$ := True), $p_2$ := ($\lambda x. \_$)($i_1$ := False, $i_2$ := False))
+  Skolem constant:
+    x = $p_2$ \color{black}%
+}%
 \endisatagproof
@@
 %
+\begin{isamarkuptext}%
+This lemma demonstrates the problem with the naive interpretation. The FUL universalizes across people
+but the naive formalization universalizes across worlds. Because this interpretation is so naive, it is 
+limited in its power. However, this serves as an example of the kind of reasoning that 
+Isabelle empowers us to do. Even this simple argument has philosophical consequences. It tells us that
+reading the FUL as a claim about consistency across possible worlds, instead of consistency across 
+agents, leads to counterintuitive conclusions.%
+\end{isamarkuptext}\isamarkuptrue%
+%
 \isadelimdocument
@@
 \isatagdocument
+%
+\isamarkupsubsubsection{Metaethical Properties%
+}
+\isamarkuptrue%
 %
@@
 %
+\begin{isamarkuptext}%
+The above section specified the model to simulate practical ethical reasoning, or the kind of 
+reasoning that is useful when an agent has to decide what to do. Formalizations of the categorical 
+imperative can also be used to do metaethical reasoning, which can evaluate a particular ethical theory
+as good or bad. In this case, we can analyze properties of the system in the form of theorems. For example,
+if we can show that, in this system, nothing is ever obligated, that would indicate that we have a bad 
+ethical system. This is not only philosophical work, but is also a useful way to test different ethical
+reasoning systems.
+
+An initial property that we might be interested in is permissibility itself. More generally, an ethical
+theory that doesn't allow for permissibility would require that every action is either obligatory or 
+prohibited. In fact, if that is the case, many counterintuitive theorems follow, including that all 
+permissible actions are obligatory.\footnote{Proof is in the appendix.}%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ permissible{\isacharcolon}\isanewline
+\ \ \isakeyword{fixes}\ A\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharbrackright}%
 \isadelimproof
-%
+\ %
 \endisadelimproof
@@
 \isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
 %
+\isamarkupcmt{\color{blue}Nitpick found a model for card i = 1:
+
+  Free variable:
+    A = ($\lambda x. \_$)($i_1$ := False)\color{black}%
+}\isanewline
+%
+\isamarkupcmt{This is exactly the desired result above - we have shown that models exist where an action can be 
+neither obligatory nor prohibited.%
+}\isanewline
+%
+\isamarkupcmt{Note that it's not clear \cite{kitcher} if Kant actually thought that permissibility was a coherent 
+concept. Either way, in modern ethics, permissibility is a pretty widely accepted phenomenon.%
+}%
 \endisatagproof
@@
 %
+\begin{isamarkuptext}%
+Another initial test is the possibility of arbitrary obligations. If anything can be shown to be 
+obligatory in this theory, then clearly it doesn't track out intuitions.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ arbitrary{\isacharunderscore}obligations{\isacharcolon}\isanewline
+\ \ \isakeyword{fixes}\ A{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}O\ {\isacharbraceleft}A{\isacharbraceright}\ w{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharequal}true{\isacharbrackright}%
 \isadelimproof
-%
+\ %
 \endisadelimproof
@@
 \isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
 %
+\isamarkupcmt{\color{blue} Nitpick found a counterexample for card i = 1:
+
+  Free variable:
+    A = ($\lambda x. \_$)($i_1$ := False) \color{black}%
+}\isanewline
+%
+\isamarkupcmt{This is good! Shows us that any arbitrary term isn't obligatory.%
+}%
 \endisatagproof
@@
 %
-\isadelimdocument
+\begin{isamarkuptext}%
+$\textbf{Conflicting Obligations}$%
+\end{isamarkuptext}\isamarkuptrue%
 %
-\endisadelimdocument
-%
-\isatagdocument
-%
-\endisatagdocument
-{\isafolddocument}%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
+\begin{isamarkuptext}%
+A more complex metaethical property is the possibility of conflicting obligations. Many deontological
+ethics are criticized for prescribing conflicting obligations, but it is clear that in Kantian ethics, 
+obligations are never conflicting \cite{contradictoryob}. In order for morality to be action-guiding, it needs to be free of 
+conflicting obligations. Let's see if we can have contradictary obligations under the naive formalization.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ conflicting{\isacharunderscore}obligations{\isacharcolon}\isanewline
+\ \ \isakeyword{fixes}\ A\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymand}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharbrackright}%
 \isadelimproof
-%
+\ %
 \endisadelimproof
@@
 \isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
 %
+\isamarkupcmt{\color{blue} Nitpick found a model for card i = 2:
+
+  Free variable:
+    A = ($\lambda x. \_$)($i_1$ := False, $i_2$ := True) \color{black}%
+}\isanewline
+%
+\isamarkupcmt{Oh no! Nitpick found a model with conflicting obligations - that's bad!%
+}%
 \endisatagproof
@@
 %
+\begin{isamarkuptext}%
+This is a property of DDL itself, not necessarily of my formalization specifically. A future, 
+more robust formalization should add an axiom that disallows this. Let's see if that causes any obvious 
+problems.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ removing{\isacharunderscore}conflicting{\isacharunderscore}obligations{\isacharcolon}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}A{\isachardot}\ {\isasymTurnstile}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymand}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ True\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+\ {\isacharbrackleft}satisfy{\isacharcomma}user{\isacharunderscore}axioms{\isacharcomma}format{\isacharequal}{\isadigit{2}}{\isacharbrackright}%
 \isadelimproof
-%
+\ %
 \endisadelimproof
@@
 \isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
 %
+\isamarkupcmt{\color{blue} Nitpick found a model for card i = 1:
+
+  Empty assignment \color{black}%
+}\isanewline
+%
+\isamarkupcmt{We can disallow conflicting obligations and the system is still consistent - that's good.%
+}%
 \endisatagproof
@@
 %
+\begin{isamarkuptext}%
+The above is a rather weak notion of contradictory obligations. Korsgaard \cite{KorsgaardFUL} argues that Kantian 
+ethics also has the stronger property that if two maxims imply a contradiction, they must not be willed.
+Let's see if that fact holds in this formalization.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ implied{\isacharunderscore}contradiction{\isacharcolon}\isanewline
+\ \ \isakeyword{fixes}\ A{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{fixes}\ B{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isachardoublequoteclose}\ \isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymTurnstile}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}A\ \isactrlbold {\isasymand}\ B{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymTurnstile}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymand}\ O\ {\isacharbraceleft}B{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}\isanewline
+%
 \isadelimproof
@@
 \isatagproof
+\isacommand{proof}\isamarkupfalse%
+\ {\isacharminus}\ \isanewline
+\ \ \isacommand{have}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isasymTurnstile}{\isacharparenleft}\isactrlbold {\isasymnot}{\isacharparenleft}{\isasymdiamond}{\isacharparenleft}A\ \isactrlbold {\isasymand}\ B{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \ \ \isacommand{by}\isamarkupfalse%
+\ {\isacharparenleft}simp\ add{\isacharcolon}\ assms{\isacharparenright}\isanewline
+\ \ \isacommand{then}\isamarkupfalse%
+\ \isacommand{have}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isasymTurnstile}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}A\ \isactrlbold {\isasymand}\ B{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\ \isacommand{by}\isamarkupfalse%
+\ {\isacharparenleft}smt\ O{\isacharunderscore}diamond{\isacharparenright}\isanewline
 %
+\isamarkupcmt{Notice that this is $\textbf{almost}$ the property we are interested in. In fact, if $O \{ A \wedge B \}$
+is equivalent to $O\{A\} \wedge O\{B\}$, then the proof is complete.%
+}\isanewline
+\ \ \isacommand{thus}\isamarkupfalse%
+\ {\isacharquery}thesis\ \isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{\color{blue} Nitpick found a counterexample for card i = 2:
+
+  Free variables:
+    A = ($\lambda x. \_$)($i_1$ := True, $i_2$ := False)
+    B = ($\lambda x. \_$)($i_1$ := False, $i_2$ := True) \color{black}%
+}\isanewline
+%
+\isamarkupcmt{Sadly the property we're actually interested in doesn't follow.%
+}%
 \endisatagproof
@@
 %
+\begin{isamarkuptext}%
+The above proof yields an interesting observation.  $O \{ A \wedge B \} $ is not equivalent to 
+$O\{A\} \wedge O\{B\}$. The rough English translation of  $O \{ A \wedge B \} $ is ``you are obligated to 
+do both A and B". The rough English translation of $O\{A\} \wedge O\{B\}$ is ``you are obligated to do A 
+and you are obligated to do B." We think those English sentences mean the same thing, so they should mean 
+the same thing in our logic as well. Let's test that.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ distribute{\isacharunderscore}obligations{\isacharcolon}\isanewline
+\ \ \isakeyword{assumes}\ \ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymand}\ O\ {\isacharbraceleft}B{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymTurnstile}\ O\ {\isacharbraceleft}A\ \isactrlbold {\isasymand}\ B{\isacharbraceright}{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
 \isadelimproof
-%
+\ %
 \endisadelimproof
@@
 \isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
 %
+\isamarkupcmt{\color{blue} Nitpick found a counterexample for card i = 2:
+
+  Free variables:
+    A = ($\lambda x. \_$)($i_1$ := True, $i_2$ := False)
+    B = ($\lambda x. \_$)($i_1$ := False, $i_2$ := True)\color{black}%
+}%
 \endisatagproof
@@
 %
+\begin{isamarkuptext}%
+Note that this is a property of DDL itself, not just my formalization. A future formalization might 
+add this property as an axiom.\footnote{For discussion of why this property doesn't hold in DDL, see the Appendix.}%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+$\textbf{Miscellaneous Properties}$%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+I named this formalization the naive formulation for a reason. Though it seems to be an immediate
+translation of the FUL into DDL, it doesn't fully respect the properties of modal logic itself. In particular, the 
+formalization as given is equivalent to the below theorem.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ FUL{\isacharunderscore}alternate{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}{\isacharparenleft}{\isasymdiamond}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
 \isadelimproof
-%
+\ \ %
 \endisadelimproof
@@
 \isatagproof
+\isacommand{by}\isamarkupfalse%
+\ simp\isanewline
 %
+\isamarkupcmt{This means that if something is possibly prohibited, it is in fact prohibited.%
+}\isanewline
+%
+\isamarkupcmt{This is a direct consequence\footnote{For a manual proof, see the Appendix.} of the naive formalization, but it's not clear to me that this is 
+actually how we think about ethics. For example, we can imagine an alternate universe where smiling at 
+someone is considered an incredibly rude and disrespectful gesture. In this universe, we are probably 
+prohibited from smiling at people, but this doesn't mean that in this current universe, smiling is 
+morally wrong.%
+}%
 \endisatagproof
@@
 %
+\begin{isamarkuptext}%
+The ``ought implies can" principle is attributed to Kant\footnote{The exact philosophical credence of this view is disupted, but the rough idea holds nonetheless. See \cite{kohl} for more.}
+ and is rather intuitive: you can't be obligated to do the impossible. It is worth noting that deontic 
+logics evolved\cite{cresswell} specifically from this principle, so this should hold in both my 
+modified logic and in DDL.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ ought{\isacharunderscore}implies{\isacharunderscore}can{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}A{\isachardot}\ {\isasymTurnstile}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymdiamond}A{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
 \isadelimproof
-%
+\ \ %
 \endisadelimproof
@@
 \isatagproof
+\isacommand{using}\isamarkupfalse%
+\ O{\isacharunderscore}diamond\ \isacommand{by}\isamarkupfalse%
+\ blast\isanewline
+%
+\isamarkupcmt{\isa{{\isasymTurnstile}{\isasymlambda}w{\isachardot}\ ob\ {\isacharquery}B\ {\isacharquery}A\ {\isasymlongrightarrow}\ {\isasymnot}\ {\isasymTurnstile}\isactrlbold {\isasymnot}\ {\isacharquery}B\isactrlbold {\isasymand}{\isacharquery}A} is an axiom of DDL itself, so this theorem holds in DDL.%
+}\isanewline
 %
@@
 %:%99=57%:%
+%:%100=58%:%
+%:%101=59%:%
+%:%103=62%:%
+%:%104=62%:%
+%:%105=62%:%
+%:%107=62%:%
+%:%111=62%:%
+%:%112=62%:%
+%:%114=63%:%
+%:%115=64%:%
+%:%116=65%:%
+%:%117=65%:%
+%:%119=66%:%
+%:%186=113%:%
+%:%198=115%:%
+%:%199=116%:%
+%:%200=117%:%
+%:%201=118%:%
+%:%203=120%:%
+%:%204=120%:%
+%:%205=121%:%
+%:%206=121%:%
+%:%218=129%:%
+%:%221=130%:%
+%:%222=130%:%
+%:%224=131%:%
+%:%225=132%:%
+%:%226=133%:%
+%:%227=134%:%
+%:%228=134%:%
+%:%229=135%:%
+%:%230=136%:%
+%:%231=136%:%
+%:%232=137%:%
+%:%233=138%:%
+%:%236=139%:%
+%:%240=139%:%
+%:%241=139%:%
+%:%242=139%:%
+%:%244=140%:%
+%:%245=141%:%
+%:%255=143%:%
+%:%256=144%:%
+%:%257=145%:%
+%:%261=147%:%
+%:%263=149%:%
+%:%264=149%:%
+%:%265=150%:%
+%:%266=150%:%
+%:%267=151%:%
+%:%268=151%:%
+%:%270=152%:%
+%:%271=152%:%
+%:%272=153%:%
+%:%273=154%:%
+%:%274=154%:%
+%:%276=156%:%
+%:%277=157%:%
+%:%278=158%:%
+%:%279=159%:%
+%:%281=161%:%
+%:%282=161%:%
+%:%283=162%:%
+%:%284=163%:%
+%:%285=164%:%
+%:%286=164%:%
+%:%289=165%:%
+%:%293=165%:%
+%:%294=165%:%
+%:%296=166%:%
+%:%297=167%:%
+%:%298=168%:%
+%:%299=169%:%
+%:%309=171%:%
+%:%310=172%:%
+%:%311=173%:%
+%:%312=174%:%
+%:%313=175%:%
+%:%314=176%:%
+%:%315=177%:%
+%:%316=178%:%
+%:%318=180%:%
+%:%319=180%:%
+%:%320=181%:%
+%:%321=182%:%
+%:%322=183%:%
+%:%323=183%:%
+%:%325=183%:%
+%:%329=183%:%
+%:%330=183%:%
+%:%332=184%:%
+%:%333=185%:%
+%:%334=186%:%
+%:%335=187%:%
+%:%336=188%:%
+%:%337=189%:%
+%:%347=191%:%
+%:%348=192%:%
+%:%349=193%:%
+%:%350=194%:%
+%:%351=195%:%
+%:%352=196%:%
+%:%361=198%:%
+%:%373=200%:%
+%:%374=201%:%
+%:%375=202%:%
+%:%376=203%:%
+%:%377=204%:%
+%:%378=205%:%
+%:%379=206%:%
+%:%380=207%:%
+%:%381=208%:%
+%:%382=209%:%
+%:%383=210%:%
+%:%384=211%:%
+%:%386=213%:%
+%:%387=213%:%
+%:%388=214%:%
+%:%389=215%:%
+%:%390=216%:%
+%:%391=216%:%
+%:%393=216%:%
+%:%397=216%:%
+%:%398=216%:%
+%:%400=217%:%
+%:%401=218%:%
+%:%402=219%:%
+%:%403=220%:%
+%:%404=220%:%
+%:%406=221%:%
+%:%407=222%:%
+%:%408=222%:%
+%:%410=223%:%
+%:%411=224%:%
+%:%421=226%:%
+%:%422=227%:%
+%:%424=229%:%
+%:%425=229%:%
+%:%426=230%:%
+%:%427=231%:%
+%:%428=232%:%
+%:%429=232%:%
+%:%431=232%:%
+%:%435=232%:%
+%:%436=232%:%
+%:%438=233%:%
+%:%439=234%:%
+%:%440=235%:%
+%:%441=236%:%
+%:%442=236%:%
+%:%444=237%:%
+%:%454=239%:%
+%:%458=241%:%
+%:%459=242%:%
+%:%460=243%:%
+%:%461=244%:%
+%:%463=246%:%
+%:%464=246%:%
+%:%465=247%:%
+%:%466=248%:%
+%:%467=249%:%
+%:%468=249%:%
+%:%470=249%:%
+%:%474=249%:%
+%:%475=249%:%
+%:%477=250%:%
+%:%478=251%:%
+%:%479=252%:%
+%:%480=253%:%
+%:%481=253%:%
+%:%483=254%:%
+%:%493=256%:%
+%:%494=257%:%
+%:%495=258%:%
+%:%497=260%:%
+%:%498=260%:%
+%:%499=261%:%
+%:%500=262%:%
+%:%501=263%:%
+%:%502=263%:%
+%:%504=263%:%
+%:%508=263%:%
+%:%509=263%:%
+%:%511=264%:%
+%:%512=265%:%
+%:%513=266%:%
+%:%514=266%:%
+%:%516=267%:%
+%:%526=269%:%
+%:%527=270%:%
+%:%528=271%:%
+%:%530=273%:%
+%:%531=273%:%
+%:%532=274%:%
+%:%533=275%:%
+%:%534=276%:%
+%:%535=277%:%
+%:%536=278%:%
+%:%537=278%:%
+%:%544=279%:%
+%:%545=279%:%
+%:%546=280%:%
+%:%547=280%:%
+%:%548=281%:%
+%:%549=281%:%
+%:%550=282%:%
+%:%551=282%:%
+%:%552=282%:%
+%:%553=282%:%
+%:%555=283%:%
+%:%556=284%:%
+%:%557=284%:%
+%:%558=285%:%
+%:%559=285%:%
+%:%560=285%:%
+%:%562=286%:%
+%:%563=287%:%
+%:%564=288%:%
+%:%565=289%:%
+%:%566=290%:%
+%:%567=290%:%
+%:%569=291%:%
+%:%579=293%:%
+%:%580=294%:%
+%:%581=295%:%
+%:%582=296%:%
+%:%583=297%:%
+%:%585=299%:%
+%:%586=299%:%
+%:%587=300%:%
+%:%588=301%:%
+%:%589=302%:%
+%:%590=302%:%
+%:%592=302%:%
+%:%596=302%:%
+%:%597=302%:%
+%:%599=303%:%
+%:%600=304%:%
+%:%601=305%:%
+%:%602=306%:%
+%:%603=307%:%
+%:%613=309%:%
+%:%614=310%:%
+%:%618=312%:%
+%:%622=314%:%
+%:%623=315%:%
+%:%624=316%:%
+%:%626=318%:%
+%:%627=318%:%
+%:%628=319%:%
+%:%631=320%:%
+%:%635=320%:%
+%:%636=320%:%
+%:%638=321%:%
+%:%639=321%:%
+%:%641=322%:%
+%:%642=323%:%
+%:%643=324%:%
+%:%644=325%:%
+%:%645=326%:%
+%:%655=328%:%
+%:%656=329%:%
+%:%657=330%:%
+%:%658=331%:%
+%:%660=333%:%
+%:%661=333%:%
+%:%662=334%:%
+%:%665=335%:%
+%:%669=335%:%
+%:%670=335%:%
+%:%671=335%:%
+%:%673=336%:%
+%:%674=336%:%

### 2021-04-21 paper/output/document/paper32.tex
updated readme and started kroy

%
\begin{isabellebody}%
\setisabellecontext{paper{\isadigit{3}}{\isadigit{2}}}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Kroy's Formalization of the Categorical Imperative%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
This section contains a formalization of the categorical imperative introduced by Moshe Kroy in 
1976 \cite{kroy}. Kroy used Hinktikka's deontic logic to formalize the Formula of Universal Law and
the Formula of Humanity. I will first import the additional logical tools that Hintikka's logic contains 
that Kroy relies on, then examine the differences between his logic and DDL, and finally implement 
and test both of Kroy's formalizations.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Additional Logical Tools%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
Kroy's logic relies heavily on some notion of identity or agency. We need some notion of ``x does action", 
which we can write as ``x is the subject of the sentence 'does action'". This requires defining a subject.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{typedecl}\isamarkupfalse%
\ s\ %
\isamarkupcmt{s is the type for a ``subject", like the subject of a sentence%
}%
\begin{isamarkuptext}%
Kroy also defines a substitution operator\footnote{see page 196 in \cite{kroy}}. $P (d/e)$ is read in his logic as ``P with e substituted 
for d." DDL has no such notion of substitution, so I will define a more generalized notion of an ``open 
sentence." An open sentence takes as input a subject and returns a complete or ``closed" DDL formula. For example, 
``does action" is an open sentence that can be instantiated with a subject.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
\ os\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}s\ {\isasymRightarrow}\ t{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{``P sub (d/e)" can be written as ``S(e)", where S(d) = P%
}\isanewline
%
\isamarkupcmt{The terms that we substitute into are actually instantiations of an open sentence, and substitution 
just requires re-instantiating the open sentence with a different subject.%
}%
\begin{isamarkuptext}%
\textbf{New Operators}

Because Isabelle is strongly typed, we need to define new operators to handle open sentences. These operators 
are similar to DDL's original operators. We could probably do without these abbreviations, but they will 
simplify the notation and make it look more similar to Kroy's original paper.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ os{\isacharunderscore}neg{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}os\ {\isasymRightarrow}\ os{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlemph {\isasymnot}{\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharparenleft}\isactrlemph {\isasymnot}A{\isacharparenright}\ {\isasymequiv}\ {\isasymlambda}x{\isachardot}\ \isactrlbold {\isasymnot}{\isacharparenleft}A{\isacharparenleft}x{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ os{\isacharunderscore}and{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}os\ {\isasymRightarrow}\ os\ {\isasymRightarrow}\ os{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharunderscore}\isactrlemph {\isasymand}{\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharparenleft}A\ \isactrlemph {\isasymand}\ B{\isacharparenright}\ {\isasymequiv}\ {\isasymlambda}x{\isachardot}\ {\isacharparenleft}{\isacharparenleft}A{\isacharparenleft}x{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}B{\isacharparenleft}x{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ os{\isacharunderscore}or{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}os\ {\isasymRightarrow}\ os\ {\isasymRightarrow}\ os{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharunderscore}\isactrlemph {\isasymor}{\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharparenleft}A\ \isactrlemph {\isasymor}\ B{\isacharparenright}\ {\isasymequiv}\ {\isasymlambda}x{\isachardot}\ {\isacharparenleft}{\isacharparenleft}A{\isacharparenleft}x{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymor}\ {\isacharparenleft}B{\isacharparenleft}x{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ os{\isacharunderscore}ob{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}os\ {\isasymRightarrow}\ os{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlemph O{\isacharbraceleft}{\isacharunderscore}{\isacharbraceright}{\isachardoublequoteclose}{\isacharparenright}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlemph O{\isacharbraceleft}A{\isacharbraceright}\ {\isasymequiv}\ {\isasymlambda}x{\isachardot}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharparenleft}x{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}%
\begin{isamarkuptext}%
Once again, the notion of permissibility will be useful here.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ ddl{\isacharunderscore}permissible{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isasymRightarrow}t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}P\ {\isacharbraceleft}{\isacharunderscore}{\isacharbraceright}{\isachardoublequoteclose}{\isacharparenright}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}P\ {\isacharbraceleft}A{\isacharbraceright}\ {\isasymequiv}\ \isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ os{\isacharunderscore}permissible{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}os{\isasymRightarrow}os{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlemph P\ {\isacharbraceleft}{\isacharunderscore}{\isacharbraceright}{\isachardoublequoteclose}{\isacharparenright}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlemph P\ {\isacharbraceleft}A{\isacharbraceright}\ {\isasymequiv}\ {\isasymlambda}x{\isachardot}\ P\ {\isacharbraceleft}A{\isacharparenleft}x{\isacharparenright}{\isacharbraceright}{\isachardoublequoteclose}%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Differences Between Kroy's Logic (Kr) and DDL%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/paper32.thy%:%
%:%24=8%:%
%:%36=10%:%
%:%37=11%:%
%:%38=12%:%
%:%39=13%:%
%:%40=14%:%
%:%49=16%:%
%:%61=18%:%
%:%62=19%:%
%:%64=21%:%
%:%65=21%:%
%:%66=21%:%
%:%69=23%:%
%:%70=24%:%
%:%71=25%:%
%:%72=26%:%
%:%74=28%:%
%:%75=28%:%
%:%77=29%:%
%:%78=29%:%
%:%80=30%:%
%:%81=31%:%
%:%84=33%:%
%:%85=34%:%
%:%86=35%:%
%:%87=36%:%
%:%88=37%:%
%:%90=39%:%
%:%91=39%:%
%:%92=40%:%
%:%93=41%:%
%:%94=41%:%
%:%95=42%:%
%:%96=43%:%
%:%97=43%:%
%:%98=44%:%
%:%99=45%:%
%:%100=45%:%
%:%101=46%:%
%:%103=48%:%
%:%105=50%:%
%:%106=50%:%
%:%107=51%:%
%:%108=52%:%
%:%109=52%:%
%:%110=53%:%
%:%117=56%:%

### 2021-04-24 paper/output/document/futurework.tex
prof. amin's feedback + future work

%
\begin{isabellebody}%
\setisabellecontext{futurework}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Future Work%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
I intend to continue this research for the next year as part of my senior thesis. To make that process
easier, I will sketch some goals for the rest of the project. In Section 3.2, I present a young and unfinished 
implementation of Kroy's formalization of the categorical imperative. The finished version of my project will 
ideally include an implementation of Kroy's formalization of the second formulation of the categorical imperative as well.
I also hope to write robust tests for both of these implementations to explore their limitations. These tests
will help inform my eventual formalization of the categorical imperative.

The ultimate goal of the project is to present my own formalization of the categorical imperative that escapes
the limitations on the naive formalization and Kroy's formalization revealed by my tests. This formalization
will likely require some additional logical machinery to handle the complete notion of a maxim, including 
an agent, action, and end. My formalization will also patch up some of the holes in DDL itself that have been
problematic for my project so far, such as the existence of contradictory obligations. I intend to formalize
all three formulations of the categorical imperative.

I will then test my formalization of the categorical imperative. I will create two kinds of tests. First,
I will create metaethical tests that show logical properties independent of any model specification as I did
for the first two formalizations. Second, I will create tests that specify models and apply my formalization
to real, concrete ethical dilemmas. This part of the project will seek to demonstrate the power and limitations of
automated ethical reasoning. Questions to be explored here include: How much model specification is necessary to 
achieve ethical results? How should models be represented and specified? Does the automation of ethical reasoning
provide anything, or is all the ethical work hidden in the model specification itself?

This final question is both technical and philosophical, and will be interesting to explore in the written
component of my thesis. This question is related to Kant's distinction between analytic and synthetic reasoning \cite{groundwork}. 
Analytic statements are true simply by virtue of their meaning, such as ``All bachelors are unmarried." Synthetic 
reasoning involves some contribution by the reasoner, in the form of new insight or facts about the world. 
Kant believes that ethics is synthetic a priori reasoning, but it is unclear if automated theorem provers 
like Isabelle are capable of anything more than analytic reasoning. Many of the basic proof solving 
tools like \texttt{simp} or \texttt{blast} simply unfold definitions and apply axioms, and they appear to 
perform analytic reasoning. smt solvers like \texttt{Nitpick} and \texttt{z3} (bundled with Isabelle) are 
candidates for synthetic reasoning.

Lastly, I hope to explore Kant's argument that the three formulations of the categorical imperative are 
equivalent. This hypothesis has been the subject of controversy, but many neo-Kantians believe that his 
claim is plausible, if not true. Armed with formalizations of each formulation, I will have all the tools 
necessary to test this hypothesis. I would like to either prove or disprove this hypothesis
for my formalization, and analyze the philosophical implications of my result.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/futurework.thy%:%
%:%24=7%:%
%:%36=9%:%
%:%37=10%:%
%:%38=11%:%
%:%39=12%:%
%:%40=13%:%
%:%41=14%:%
%:%42=15%:%
%:%43=16%:%
%:%44=17%:%
%:%45=18%:%
%:%46=19%:%
%:%47=20%:%
%:%48=21%:%
%:%49=22%:%
%:%50=23%:%
%:%51=24%:%
%:%52=25%:%
%:%53=26%:%
%:%54=27%:%
%:%55=28%:%
%:%56=29%:%
%:%57=30%:%
%:%58=31%:%
%:%59=32%:%
%:%60=33%:%
%:%61=34%:%
%:%62=35%:%
%:%63=36%:%
%:%64=37%:%
%:%65=38%:%
%:%66=39%:%
%:%67=40%:%
%:%68=41%:%
%:%69=42%:%
%:%70=43%:%
%:%71=44%:%
%:%72=45%:%

### 2021-04-24 paper/output/document/paper.tex
prof. amin's feedback + future work

--- 2021-04-16 paper/output/report/paper.tex
@@
 \isatagtheory
-\ \ \isakeyword{imports}\ Main\isanewline
 %
@@
 The ideal candidate ethical theory will be both philosophically interesting and easy to 
-formalize. Kantian ethics, often described as ``formal," has been often floated as such a candidate \cite{powers} \cite{BL}. 
+formalize. Kantian ethics, often described as ``formal," has been often floated as such a candidate \cite{powers, BL}. 
 The categorical imperative, Kant's universal law of morality, is a moral rule that can be used to 
@@
 test: to decide if a maxim is permissible, imagine what would happen if everyone willed that maxim. 
-If your imagined world yields a contradiction, the maxim is prohibited. Intuitively, the FUL asks 
+If your imagined world yields a contradiction, the maxim is prohibited\footnote{There is another case here.
+What happens if the imagined world does not yield a logical contradiction, but is still undesirable? Kant 
+distinguishes between these cases as contradictions in conception and contradictions in will. Both yield moral
+prohibitions, but contradictions in conception generate stronger contradictions and therefore stronger obligations. 
+This paper will focus entirely on contradictions in conception, for this is the only kind of contradiction 
+for which a strict logical interpretation makes sense. For a complete treatment of the difference, see \cite{groundwork, KorsgaardFUL}}. Intuitively, the FUL asks 
 the question, "What would happen if everyone did that?" \cite{KorsgaardFUL}.
+
+As an example, let's apply the universalizability test to the maxim of murdering others to take their job.
+Universalized, anyone who wants a job can murder the person currently holding that job. It is contradictory
+to simultaneously will that I acquire a job (through murder) and also that someone can take that job from me 
+whenever they want (also by murder). The maxim thwarts its own end, and is thus internally contradictory.
+ Therefore, this maxim is prohibited.
 
@@
 A deontic logic is a special kind of modal logic designed to reason about obligation. Standard deontic
-logic \cite{cresswell} \cite{sep-logic-deontic} essentially replaces $\Box$ with the obligation operator
+logic \cite{cresswell, sep-logic-deontic} essentially replaces $\Box$ with the obligation operator
 $O$, and $\diamond$ with the permissibility operator $P$. Using the Kripke semantics for $O$, $O p$ 
@@
  While SDL is appreciable for its simplicity, it suffers a variety of well-documented paradoxes, 
-including contrary-to-duty paradoxes \cite{ctd}. In situations where duty is violated, the logic breaks down 
+including contrary-to-duty paradoxes \footnote{The paradigm case of a contrary-to-duty paradox is the 
+Chisholm paradox. Consider the following statements: \begin{enumerate}
+\item It ought to be that Tom ought helps his neighbors
+\item It ought to be that if Tom goes to help his neighbors, he tells them he is coming
+\item If Tom does not go to help his neighbors, he ought not tell them that he is coming
+\item Tom does not help his neighbors
+\end{enumerate} 
+These premises contradict themselves, because items (2)-(4) imply that Tom ought not help his neighbors. The 
+contradiction results because the logic cannot handle violations of duty mixed with
+conditionals. \cite{chisholm, ctd}
+}. 
+In situations where duty is violated, the logic breaks down 
 and produces paradoxical results. Thus, I use an improved deontic logic instead of SDL for this work.%
@@
 to represent the sentence ``A is obligated in the context B". This gracefully handles contrary-to-duty
-conditionals. The obligation operator uses a neighborhood semantics \cite{neighborhood1}\cite{neighborhood2}, instead of the Kripke semantics. 
+conditionals. The obligation operator uses a neighborhood semantics \cite{neighborhood1, neighborhood2}, instead of the Kripke semantics. 
 Carmo and Jones define a function $ob$ that maps from worlds to sets of sets of worlds. Intuitively, 
@@
 %:%file=~/Desktop/cs91r/paper/paper.thy%:%
-%:%10=2%:%
-%:%25=6%:%
-%:%37=8%:%
-%:%38=9%:%
-%:%39=10%:%
-%:%40=11%:%
-%:%41=12%:%
-%:%42=13%:%
-%:%43=14%:%
-%:%44=15%:%
-%:%45=16%:%
-%:%46=17%:%
-%:%47=18%:%
-%:%48=19%:%
-%:%49=20%:%
-%:%50=21%:%
-%:%51=22%:%
-%:%52=23%:%
-%:%53=24%:%
-%:%54=25%:%
-%:%55=26%:%
-%:%56=27%:%
-%:%57=28%:%
-%:%58=29%:%
-%:%59=30%:%
-%:%60=31%:%
-%:%61=32%:%
-%:%62=33%:%
-%:%63=34%:%
-%:%64=35%:%
-%:%65=36%:%
-%:%66=37%:%
-%:%67=38%:%
-%:%68=39%:%
-%:%69=40%:%
-%:%70=41%:%
-%:%71=42%:%
-%:%72=43%:%
-%:%73=44%:%
-%:%74=45%:%
-%:%75=46%:%
-%:%76=47%:%
-%:%77=48%:%
-%:%78=49%:%
-%:%79=50%:%
-%:%88=52%:%
-%:%100=54%:%
-%:%101=55%:%
-%:%102=56%:%
-%:%103=57%:%
-%:%104=58%:%
-%:%105=59%:%
-%:%114=61%:%
-%:%126=63%:%
-%:%127=64%:%
-%:%128=65%:%
-%:%129=66%:%
-%:%130=67%:%
-%:%131=68%:%
-%:%132=69%:%
-%:%133=70%:%
-%:%134=71%:%
-%:%135=72%:%
-%:%136=73%:%
-%:%137=74%:%
-%:%138=75%:%
-%:%139=76%:%
-%:%140=77%:%
-%:%141=78%:%
-%:%142=79%:%
-%:%143=80%:%
-%:%144=81%:%
-%:%145=82%:%
-%:%146=83%:%
-%:%147=84%:%
-%:%148=85%:%
-%:%149=86%:%
-%:%150=87%:%
-%:%151=88%:%
-%:%152=89%:%
-%:%153=90%:%
-%:%154=91%:%
-%:%155=92%:%
-%:%156=93%:%
-%:%157=94%:%
-%:%158=95%:%
-%:%159=96%:%
-%:%160=97%:%
-%:%161=98%:%
-%:%162=99%:%
-%:%163=100%:%
-%:%164=101%:%
-%:%165=102%:%
-%:%166=103%:%
-%:%167=104%:%
-%:%168=105%:%
-%:%169=106%:%
-%:%170=107%:%
-%:%171=108%:%
-%:%172=109%:%
-%:%173=110%:%
-%:%174=111%:%
-%:%175=112%:%
-%:%176=113%:%
-%:%177=114%:%
-%:%178=115%:%
-%:%179=116%:%
-%:%180=117%:%
-%:%181=118%:%
-%:%182=119%:%
-%:%183=120%:%
-%:%184=121%:%
-%:%185=122%:%
-%:%186=123%:%
-%:%195=127%:%
-%:%199=129%:%
-%:%211=131%:%
-%:%212=132%:%
-%:%213=133%:%
-%:%214=134%:%
-%:%215=135%:%
-%:%216=136%:%
-%:%217=137%:%
-%:%218=138%:%
-%:%219=139%:%
-%:%220=140%:%
-%:%221=141%:%
-%:%222=142%:%
-%:%223=143%:%
-%:%224=144%:%
-%:%225=145%:%
-%:%234=147%:%
-%:%246=149%:%
-%:%247=150%:%
-%:%248=151%:%
-%:%249=152%:%
-%:%250=153%:%
-%:%251=154%:%
-%:%252=155%:%
-%:%253=156%:%
-%:%254=157%:%
-%:%255=158%:%
-%:%256=159%:%
-%:%257=160%:%
-%:%258=161%:%
-%:%259=162%:%
-%:%260=163%:%
-%:%261=164%:%
-%:%262=165%:%
-%:%263=166%:%
-%:%264=167%:%
+%:%24=6%:%
+%:%36=8%:%
+%:%37=9%:%
+%:%38=10%:%
+%:%39=11%:%
+%:%40=12%:%
+%:%41=13%:%
+%:%42=14%:%
+%:%43=15%:%
+%:%44=16%:%
+%:%45=17%:%
+%:%46=18%:%
+%:%47=19%:%
+%:%48=20%:%
+%:%49=21%:%
+%:%50=22%:%
+%:%51=23%:%
+%:%52=24%:%
+%:%53=25%:%
+%:%54=26%:%
+%:%55=27%:%
+%:%56=28%:%
+%:%57=29%:%
+%:%58=30%:%
+%:%59=31%:%
+%:%60=32%:%
+%:%61=33%:%
+%:%62=34%:%
+%:%63=35%:%
+%:%64=36%:%
+%:%65=37%:%
+%:%66=38%:%
+%:%67=39%:%
+%:%68=40%:%
+%:%69=41%:%
+%:%70=42%:%
+%:%71=43%:%
+%:%72=44%:%
+%:%73=45%:%
+%:%74=46%:%
+%:%75=47%:%
+%:%76=48%:%
+%:%77=49%:%
+%:%78=50%:%
+%:%87=52%:%
+%:%99=54%:%
+%:%100=55%:%
+%:%101=56%:%
+%:%102=57%:%
+%:%103=58%:%
+%:%104=59%:%
+%:%113=61%:%
+%:%125=63%:%
+%:%126=64%:%
+%:%127=65%:%
+%:%128=66%:%
+%:%129=67%:%
+%:%130=68%:%
+%:%131=69%:%
+%:%132=70%:%
+%:%133=71%:%
+%:%134=72%:%
+%:%135=73%:%
+%:%136=74%:%
+%:%137=75%:%
+%:%138=76%:%
+%:%139=77%:%
+%:%140=78%:%
+%:%141=79%:%
+%:%142=80%:%
+%:%143=81%:%
+%:%144=82%:%
+%:%145=83%:%
+%:%146=84%:%
+%:%147=85%:%
+%:%148=86%:%
+%:%149=87%:%
+%:%150=88%:%
+%:%151=89%:%
+%:%152=90%:%
+%:%153=91%:%
+%:%154=92%:%
+%:%155=93%:%
+%:%156=94%:%
+%:%157=95%:%
+%:%158=96%:%
+%:%159=97%:%
+%:%160=98%:%
+%:%161=99%:%
+%:%162=100%:%
+%:%163=101%:%
+%:%164=102%:%
+%:%165=103%:%
+%:%166=104%:%
+%:%167=105%:%
+%:%168=106%:%
+%:%169=107%:%
+%:%170=108%:%
+%:%171=109%:%
+%:%172=110%:%
+%:%173=111%:%
+%:%174=112%:%
+%:%175=113%:%
+%:%176=114%:%
+%:%177=115%:%
+%:%178=116%:%
+%:%179=117%:%
+%:%180=118%:%
+%:%181=119%:%
+%:%182=120%:%
+%:%183=121%:%
+%:%184=122%:%
+%:%185=123%:%
+%:%186=124%:%
+%:%187=125%:%
+%:%188=126%:%
+%:%189=127%:%
+%:%190=128%:%
+%:%191=129%:%
+%:%192=130%:%
+%:%193=131%:%
+%:%194=132%:%
+%:%195=133%:%
+%:%196=134%:%
+%:%205=138%:%
+%:%209=140%:%
+%:%221=142%:%
+%:%222=143%:%
+%:%223=144%:%
+%:%224=145%:%
+%:%225=146%:%
+%:%226=147%:%
+%:%227=148%:%
+%:%228=149%:%
+%:%229=150%:%
+%:%230=151%:%
+%:%231=152%:%
+%:%232=153%:%
+%:%233=154%:%
+%:%234=155%:%
+%:%235=156%:%
+%:%236=157%:%
+%:%237=158%:%
+%:%238=159%:%
+%:%239=160%:%
+%:%240=161%:%
+%:%241=162%:%
+%:%242=163%:%
+%:%243=164%:%
+%:%244=165%:%
+%:%245=166%:%
+%:%246=167%:%
+%:%255=169%:%
+%:%267=171%:%
+%:%268=172%:%
+%:%269=173%:%
+%:%270=174%:%
+%:%271=175%:%
+%:%272=176%:%
+%:%273=177%:%
+%:%274=178%:%
+%:%275=179%:%
+%:%276=180%:%
+%:%277=181%:%
+%:%278=182%:%
+%:%279=183%:%
+%:%280=184%:%
+%:%281=185%:%
+%:%282=186%:%
+%:%283=187%:%
+%:%284=188%:%
+%:%285=189%:%

### 2021-04-24 paper/output/document/paper22.tex
file structure and categorical imperative naive
prof. amin's feedback + future work

--- 2021-04-16 output/document/paper22.tex
@@
 
-I started my project by reimplementing Benzmueller, Farjami, and Parent's \cite{BFP} \cite{logikey} implementation 
+I started my project by reimplementing Benzmueller, Farjami, and Parent's \cite{BFP, logikey} implementation 
 of DDL in Isabelle/HOL. This helped me learn how to use Isabelle/HOL, and the implementation showcased in the 
@@
 implementation that is particularly interesting and relevant to understanding the rest of the project. 
-For the complete implementation, see the source code in \isatt{carmojones{\char`\_}DDL.thy}.%
+For the complete implementation, see the source code in \isatt{paper22.thy}.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \endinput
-%:%file=~/Desktop/cs91r/paper22.thy%:%
+%:%file=~/Desktop/cs91r/paper/paper22.thy%:%
 %:%24=6%:%

### 2021-04-25 paper/output/document/futurework.tex
prof amin's feedback

@@
 reasoning involves some contribution by the reasoner, in the form of new insight or facts about the world.
+Kant presents the statements ``All bachelors are alone" and ``7+5=12" as examples of synthetic propositions. 
+The analytic/synthetic distinction is hotly debated and has been refined significantly since Kant, and this 
+area will require further research.
+
 Kant believes that ethics is synthetic a priori reasoning, but it is unclear if automated theorem provers 
@@
 tools like \texttt{simp} or \texttt{blast} simply unfold definitions and apply axioms, and they appear to 
-perform analytic reasoning. smt solvers like \texttt{Nitpick} and \texttt{z3} (bundled with Isabelle) are 
-candidates for synthetic reasoning.
+perform analytic reasoning. SMT solvers like \texttt{Nitpick} and \texttt{z3} (bundled with Isabelle) are 
+candidates for synthetic reasoning. Model finding seems more sophisticated than the simple unfolding
+of definitions, but this requires further exploration.
 
@@
 %:%72=45%:%
+%:%73=46%:%
+%:%74=47%:%
+%:%75=48%:%
+%:%76=49%:%
+%:%77=50%:%

### 2021-04-25 paper/output/document/paper.tex
prof amin's feedback

@@
 Chisholm paradox. Consider the following statements: \begin{enumerate}
-\item It ought to be that Tom ought helps his neighbors
-\item It ought to be that if Tom goes to help his neighbors, he tells them he is coming
-\item If Tom does not go to help his neighbors, he ought not tell them that he is coming
+\item It ought to be that Tom helps his neighbors
+\item It ought to be that if Tom helps his neighbors, he tells them he is coming
+\item If Tom does not help his neighbors, he ought not tell them that he is coming
 \item Tom does not help his neighbors

### 2021-04-25 paper/output/document/paper31.tex
prof amin's feedback

@@
 
-Let's now consider a naive reading of the Formula of Universal Law (FUL): 'act only in accordance 
+Let's now consider a naive reading of the Formula of Universal Law (FUL): `act only in accordance 
 with that maxim through which you can at the same time will that it become a universal law' \cite{groundwork}.
@@
 \isacommand{lemma}\isamarkupfalse%
-\ wrong{\isacharunderscore}if{\isacharunderscore}posibly{\isacharunderscore}wrong{\isacharcolon}\isanewline
+\ wrong{\isacharunderscore}if{\isacharunderscore}possibly{\isacharunderscore}wrong{\isacharcolon}\isanewline
 \ \ \isakeyword{assumes}\ poss{\isacharunderscore}murder{\isacharunderscore}wrong\isanewline
@@
     lie = ($\lambda x. \_$)($p_1$ := ($\lambda x. \_$)($i_1$ := True, $i_2$ := False), $p_2$ := ($\lambda x. \_$)($i_1$ := False, $i_2$ := False)) \color{black}%
+}\isanewline
+%
+\isamarkupcmt{Quick note on how to read Nitpick results. Nitpick will either say that it found a ``model" or a ``counterexample" in 
+the first line. It will then provide a model by specifying model components. For readability, all except for the 
+free variables are hidden. This model has cardinality 2 for the person and world (i) types. The term \texttt{lie} is 
+defined for people $p_1$ and $p_2$. $p_1$ lies at world $i_1$ and does not lie at world $i_2$. $p_2$ does
+the opposite.%
+}\isanewline
+%
+\isamarkupcmt{These details will be elided for most Nitpick examples, but this provides guidance on how to interpret
+the output.%
 }%
@@
 \begin{isamarkuptext}%
-The ``ought implies can" principle is attributed to Kant\footnote{The exact philosophical credence of this view is disupted, but the rough idea holds nonetheless. See \cite{kohl} for more.}
+The ``ought implies can" principle is attributed to Kant\footnote{The exact philosophical credence of this view is disputed, but the rough idea holds nonetheless. See \cite{kohl} for more.}
  and is rather intuitive: you can't be obligated to do the impossible. It is worth noting that deontic 
-logics evolved\cite{cresswell} specifically from this principle, so this should hold in both my 
+logics evolved \cite{cresswell} specifically from this principle, so this should hold in both my 
 modified logic and in DDL.%
@@
 %:%299=169%:%
-%:%309=171%:%
-%:%310=172%:%
-%:%311=173%:%
-%:%312=174%:%
-%:%313=175%:%
-%:%314=176%:%
-%:%315=177%:%
-%:%316=178%:%
-%:%318=180%:%
-%:%319=180%:%
-%:%320=181%:%
-%:%321=182%:%
-%:%322=183%:%
-%:%323=183%:%
+%:%300=169%:%
+%:%302=170%:%
+%:%303=171%:%
+%:%304=172%:%
+%:%305=173%:%
+%:%306=174%:%
+%:%307=174%:%
+%:%309=175%:%
+%:%310=176%:%
+%:%320=178%:%
+%:%321=179%:%
+%:%322=180%:%
+%:%323=181%:%
+%:%324=182%:%
 %:%325=183%:%
-%:%329=183%:%
-%:%330=183%:%
-%:%332=184%:%
-%:%333=185%:%
-%:%334=186%:%
-%:%335=187%:%
-%:%336=188%:%
-%:%337=189%:%
-%:%347=191%:%
-%:%348=192%:%
-%:%349=193%:%
-%:%350=194%:%
-%:%351=195%:%
-%:%352=196%:%
-%:%361=198%:%
-%:%373=200%:%
-%:%374=201%:%
-%:%375=202%:%
-%:%376=203%:%
-%:%377=204%:%
-%:%378=205%:%
-%:%379=206%:%
-%:%380=207%:%
-%:%381=208%:%
-%:%382=209%:%
-%:%383=210%:%
-%:%384=211%:%
-%:%386=213%:%
-%:%387=213%:%
-%:%388=214%:%
-%:%389=215%:%
-%:%390=216%:%
-%:%391=216%:%
+%:%326=184%:%
+%:%327=185%:%
+%:%329=187%:%
+%:%330=187%:%
+%:%331=188%:%
+%:%332=189%:%
+%:%333=190%:%
+%:%334=190%:%
+%:%336=190%:%
+%:%340=190%:%
+%:%341=190%:%
+%:%343=191%:%
+%:%344=192%:%
+%:%345=193%:%
+%:%346=194%:%
+%:%347=195%:%
+%:%348=196%:%
+%:%358=198%:%
+%:%359=199%:%
+%:%360=200%:%
+%:%361=201%:%
+%:%362=202%:%
+%:%363=203%:%
+%:%372=205%:%
+%:%384=207%:%
+%:%385=208%:%
+%:%386=209%:%
+%:%387=210%:%
+%:%388=211%:%
+%:%389=212%:%
+%:%390=213%:%
+%:%391=214%:%
+%:%392=215%:%
 %:%393=216%:%
-%:%397=216%:%
-%:%398=216%:%
-%:%400=217%:%
-%:%401=218%:%
-%:%402=219%:%
-%:%403=220%:%
-%:%404=220%:%
-%:%406=221%:%
-%:%407=222%:%
-%:%408=222%:%
-%:%410=223%:%
+%:%394=217%:%
+%:%395=218%:%
+%:%397=220%:%
+%:%398=220%:%
+%:%399=221%:%
+%:%400=222%:%
+%:%401=223%:%
+%:%402=223%:%
+%:%404=223%:%
+%:%408=223%:%
+%:%409=223%:%
 %:%411=224%:%
-%:%421=226%:%
-%:%422=227%:%
-%:%424=229%:%
-%:%425=229%:%
-%:%426=230%:%
-%:%427=231%:%
-%:%428=232%:%
-%:%429=232%:%
-%:%431=232%:%
-%:%435=232%:%
-%:%436=232%:%
-%:%438=233%:%
-%:%439=234%:%
-%:%440=235%:%
-%:%441=236%:%
-%:%442=236%:%
-%:%444=237%:%
-%:%454=239%:%
-%:%458=241%:%
-%:%459=242%:%
-%:%460=243%:%
-%:%461=244%:%
-%:%463=246%:%
-%:%464=246%:%
-%:%465=247%:%
-%:%466=248%:%
-%:%467=249%:%
-%:%468=249%:%
+%:%412=225%:%
+%:%413=226%:%
+%:%414=227%:%
+%:%415=227%:%
+%:%417=228%:%
+%:%418=229%:%
+%:%419=229%:%
+%:%421=230%:%
+%:%422=231%:%
+%:%432=233%:%
+%:%433=234%:%
+%:%435=236%:%
+%:%436=236%:%
+%:%437=237%:%
+%:%438=238%:%
+%:%439=239%:%
+%:%440=239%:%
+%:%442=239%:%
+%:%446=239%:%
+%:%447=239%:%
+%:%449=240%:%
+%:%450=241%:%
+%:%451=242%:%
+%:%452=243%:%
+%:%453=243%:%
+%:%455=244%:%
+%:%465=246%:%
+%:%469=248%:%
 %:%470=249%:%
-%:%474=249%:%
-%:%475=249%:%
-%:%477=250%:%
-%:%478=251%:%
-%:%479=252%:%
-%:%480=253%:%
-%:%481=253%:%
-%:%483=254%:%
-%:%493=256%:%
-%:%494=257%:%
-%:%495=258%:%
-%:%497=260%:%
-%:%498=260%:%
-%:%499=261%:%
-%:%500=262%:%
-%:%501=263%:%
-%:%502=263%:%
+%:%471=250%:%
+%:%472=251%:%
+%:%474=253%:%
+%:%475=253%:%
+%:%476=254%:%
+%:%477=255%:%
+%:%478=256%:%
+%:%479=256%:%
+%:%481=256%:%
+%:%485=256%:%
+%:%486=256%:%
+%:%488=257%:%
+%:%489=258%:%
+%:%490=259%:%
+%:%491=260%:%
+%:%492=260%:%
+%:%494=261%:%
 %:%504=263%:%
-%:%508=263%:%
-%:%509=263%:%
-%:%511=264%:%
-%:%512=265%:%
-%:%513=266%:%
-%:%514=266%:%
-%:%516=267%:%
-%:%526=269%:%
-%:%527=270%:%
-%:%528=271%:%
-%:%530=273%:%
-%:%531=273%:%
-%:%532=274%:%
-%:%533=275%:%
-%:%534=276%:%
-%:%535=277%:%
-%:%536=278%:%
-%:%537=278%:%
-%:%544=279%:%
-%:%545=279%:%
-%:%546=280%:%
-%:%547=280%:%
-%:%548=281%:%
-%:%549=281%:%
-%:%550=282%:%
-%:%551=282%:%
-%:%552=282%:%
-%:%553=282%:%
-%:%555=283%:%
-%:%556=284%:%
-%:%557=284%:%
-%:%558=285%:%
-%:%559=285%:%
-%:%560=285%:%
-%:%562=286%:%
-%:%563=287%:%
-%:%564=288%:%
-%:%565=289%:%
+%:%505=264%:%
+%:%506=265%:%
+%:%508=267%:%
+%:%509=267%:%
+%:%510=268%:%
+%:%511=269%:%
+%:%512=270%:%
+%:%513=270%:%
+%:%515=270%:%
+%:%519=270%:%
+%:%520=270%:%
+%:%522=271%:%
+%:%523=272%:%
+%:%524=273%:%
+%:%525=273%:%
+%:%527=274%:%
+%:%537=276%:%
+%:%538=277%:%
+%:%539=278%:%
+%:%541=280%:%
+%:%542=280%:%
+%:%543=281%:%
+%:%544=282%:%
+%:%545=283%:%
+%:%546=284%:%
+%:%547=285%:%
+%:%548=285%:%
+%:%555=286%:%
+%:%556=286%:%
+%:%557=287%:%
+%:%558=287%:%
+%:%559=288%:%
+%:%560=288%:%
+%:%561=289%:%
+%:%562=289%:%
+%:%563=289%:%
+%:%564=289%:%
 %:%566=290%:%
-%:%567=290%:%
-%:%569=291%:%
-%:%579=293%:%
-%:%580=294%:%
-%:%581=295%:%
-%:%582=296%:%
-%:%583=297%:%
-%:%585=299%:%
-%:%586=299%:%
-%:%587=300%:%
-%:%588=301%:%
-%:%589=302%:%
-%:%590=302%:%
+%:%567=291%:%
+%:%568=291%:%
+%:%569=292%:%
+%:%570=292%:%
+%:%571=292%:%
+%:%573=293%:%
+%:%574=294%:%
+%:%575=295%:%
+%:%576=296%:%
+%:%577=297%:%
+%:%578=297%:%
+%:%580=298%:%
+%:%590=300%:%
+%:%591=301%:%
 %:%592=302%:%
-%:%596=302%:%
-%:%597=302%:%
-%:%599=303%:%
-%:%600=304%:%
-%:%601=305%:%
-%:%602=306%:%
-%:%603=307%:%
-%:%613=309%:%
-%:%614=310%:%
-%:%618=312%:%
-%:%622=314%:%
-%:%623=315%:%
+%:%593=303%:%
+%:%594=304%:%
+%:%596=306%:%
+%:%597=306%:%
+%:%598=307%:%
+%:%599=308%:%
+%:%600=309%:%
+%:%601=309%:%
+%:%603=309%:%
+%:%607=309%:%
+%:%608=309%:%
+%:%610=310%:%
+%:%611=311%:%
+%:%612=312%:%
+%:%613=313%:%
+%:%614=314%:%
 %:%624=316%:%
-%:%626=318%:%
-%:%627=318%:%
-%:%628=319%:%
-%:%631=320%:%
-%:%635=320%:%
-%:%636=320%:%
-%:%638=321%:%
-%:%639=321%:%
-%:%641=322%:%
-%:%642=323%:%
-%:%643=324%:%
-%:%644=325%:%
-%:%645=326%:%
-%:%655=328%:%
-%:%656=329%:%
-%:%657=330%:%
-%:%658=331%:%
-%:%660=333%:%
-%:%661=333%:%
-%:%662=334%:%
-%:%665=335%:%
-%:%669=335%:%
-%:%670=335%:%
-%:%671=335%:%
-%:%673=336%:%
-%:%674=336%:%
+%:%625=317%:%
+%:%629=319%:%
+%:%633=321%:%
+%:%634=322%:%
+%:%635=323%:%
+%:%637=325%:%
+%:%638=325%:%
+%:%639=326%:%
+%:%642=327%:%
+%:%646=327%:%
+%:%647=327%:%
+%:%649=328%:%
+%:%650=328%:%
+%:%652=329%:%
+%:%653=330%:%
+%:%654=331%:%
+%:%655=332%:%
+%:%656=333%:%
+%:%666=335%:%
+%:%667=336%:%
+%:%668=337%:%
+%:%669=338%:%
+%:%671=340%:%
+%:%672=340%:%
+%:%673=341%:%
+%:%676=342%:%
+%:%680=342%:%
+%:%681=342%:%
+%:%682=342%:%
+%:%684=343%:%
+%:%685=343%:%

### 2021-04-27 paper/output/document/paper32.tex
prof amin's feedback
added related work and some more kroy

@@
 \begin{isamarkuptext}%
-Kroy also defines a substitution operator\footnote{see page 196 in \cite{kroy}}. $P (d/e)$ is read in his logic as ``P with e substituted 
+Kroy also defines a substitution operator\footnote{See page 196 in Kroy's original paper \cite{kroy}.}. $P (d/e)$ is read in his logic as ``P with e substituted 
 for d." DDL has no such notion of substitution, so I will define a more generalized notion of an ``open 
@@
 %
+\begin{isamarkuptext}%
+One complication that arises here is that Kroy's original paper uses a different logic than DDL. 
+His custom logic is a slight modification of Hintikka's deontic logic \cite{hintikka}. In this section, 
+I will determine if some of the semantic properties that Kroy's logic (which I will now call Kr) requires 
+hold in DDL. These differences may become important later and can explain differences in my results and 
+Kroy's.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+\textbf{Deontic alternatives versus the neighborhood semantics}%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+The most faithful interpretation of Kr is that if $A$ is permissible in a context, then 
+it must be true at some world in that context. Kr operates under the ``deontic alternatives" or Kripke semantics, 
+summarized by Solt \cite{solt} as follows: ``A proposition of the sort $O A$ is true at the actual world $w$ if and
+only if $A$ is true at every deontic alternative world to $w$." Under this view, permissible propositions
+are obligated at some deontic alternatives, or other worlds in the system, but not at all of them. Let's 
+see if this holds in DDL.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ permissible{\isacharunderscore}semantics{\isacharcolon}\isanewline
+\ \ \isakeyword{fixes}\ A\ w\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}P\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}\ w\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymexists}x{\isachardot}\ A{\isacharparenleft}x{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
 \isadelimproof
-%
+\ %
 \endisadelimproof
@@
 \isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
 %
+\isamarkupcmt{\color{blue} Nitpick found a counterexample for card i = 1:
+
+  Free variable:
+    A = ($\lambda x. \_$)($i_1$ := False) \color{black}%
+}%
 \endisatagproof
@@
 %
+\begin{isamarkuptext}%
+Remember that DDL uses neighborhood semantics, not the deontic alternatives view, which is why this
+ proposition fails in DDL. In DDL, the $ob$ function abstracts away the notion of
+ deontic alternatives and completely determines obligations. Even if one belives that permissible 
+statements should be true at some deontic alternative, it's not clear that permissible statements
+ must be realized at some world. In some ways, this also coheres with our understanding of obligation. There 
+are permissible actions like ``Lavanya buys a red folder" that might not happen in any universe.
+
+An even stricter version of the semantics that Kr requires is that if something is permissible at a world, 
+then it is obligatory at some world. This is a straightforward application of the Kripke semantics. Let's
+test this proposition.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ permissible{\isacharunderscore}semantics{\isacharunderscore}{\isadigit{2}}{\isacharcolon}\isanewline
+\ \ \isakeyword{fixes}\ A\ w\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}P\ {\isacharbraceleft}A{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymexists}x{\isachardot}\ O\ {\isacharbraceleft}A{\isacharbraceright}\ x{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
 \isadelimproof
-%
+\ %
 \endisadelimproof
@@
 %
+\begin{isamarkuptext}%
+This also doesn't hold in DDL because DDL uses neighborhood semantics instead of the deontic 
+alternatives or Kripke semantics. This also seems to cohere with our moral intuitions. The statement 
+``Lavanya buys a red folder" is permissible in the current world, but it's hard to see why it would 
+be oblgiatory in any world.
+
+One implication of the Kripke semantics is that Kr disallows ``vacuously permissible statements." In 
+other words, if something is permissible it has to be obligated at some deontically perfect alternative. 
+If we translate this to the language of DDL, we expect that if $A$ is permissible, it is obligated in some 
+context.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ permissible{\isacharunderscore}semantic{\isacharunderscore}vacuous{\isacharcolon}\isanewline
+\ \ \isakeyword{fixes}\ A\ w\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}P\ {\isacharbraceleft}A{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymexists}x{\isachardot}\ ob{\isacharparenleft}x{\isacharparenright}{\isacharparenleft}A{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
 \isadelimproof
-%
+\ %
 \endisadelimproof
@@
 %
+\begin{isamarkuptext}%
+In order to make this true, we'd have to require that everything is either obligatory or
+prohibited somewhere. Sadly, that breaks everything and destroys the 
+notion of permissibility everywhere \footnote{See Appendix for an examination of a buggy version of DDL that led to this insight.}. 
+If something breaks later in this section, it may be because of vacuous permissibility.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+\textbf{Obligatory Statements Should be Permissible}%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+Kr includes the intuitively appealing theorem that if a statement is obligated at a world, then it 
+is permissible at that world\footnote{This follows straightforwardly from the Kripke semantics. If proposition $A$ is 
+obligated at world $w$, this means that at all of $w$'s neighbors, $O A$ holds. Therefore, 
+$\exists w'$ such that $w$ sees $w'$ and $O A$ holds at $w'$ so $A$ is permissible at $w$.}. Let's see 
+if that also holds in DDL.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ permissible{\isacharunderscore}prereq{\isacharunderscore}ob{\isacharcolon}\isanewline
+\ \ \isakeyword{fixes}\ A\ w\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}O\ {\isacharbraceleft}A{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ P\ {\isacharbraceleft}A{\isacharbraceright}\ w{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
 \isadelimproof
-%
+\ %
 \endisadelimproof
@@
 \isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
 %
+\isamarkupcmt{\color{blue} Nitpick found a counterexample for card i = 2:
+
+  Free variable:
+    A = ($\lambda x. \_$)($i_1$ := False, $i_2$ := True)\color{black}%
+}%
 \endisatagproof
@@
 %
-\isadelimproof
-%
-\endisadelimproof
-%
-\isatagproof
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
+\begin{isamarkuptext}%
+This particular difference seems untenable. Most ethical theories require that if something is 
+obligatory, it must also be permissible. This is an important enough property of an ethical theory that I 
+will add it as an axiom.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{axiomatization}\isamarkupfalse%
+\ \isakeyword{where}\ permissible{\isacharunderscore}prepreq{\isacharunderscore}ob{\isacharcolon}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymrightarrow}\ P\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
 %
@@
 %:%117=56%:%
+%:%129=59%:%
+%:%130=60%:%
+%:%131=61%:%
+%:%132=62%:%
+%:%133=63%:%
+%:%137=65%:%
+%:%141=67%:%
+%:%142=68%:%
+%:%143=69%:%
+%:%144=70%:%
+%:%145=71%:%
+%:%146=72%:%
+%:%148=74%:%
+%:%149=74%:%
+%:%150=75%:%
+%:%151=76%:%
+%:%152=77%:%
+%:%153=77%:%
+%:%155=77%:%
+%:%159=77%:%
+%:%160=77%:%
+%:%162=78%:%
+%:%163=79%:%
+%:%164=80%:%
+%:%165=81%:%
+%:%175=83%:%
+%:%176=84%:%
+%:%177=85%:%
+%:%178=86%:%
+%:%179=87%:%
+%:%180=88%:%
+%:%181=89%:%
+%:%182=90%:%
+%:%183=91%:%
+%:%184=92%:%
+%:%186=94%:%
+%:%187=94%:%
+%:%188=95%:%
+%:%189=96%:%
+%:%190=97%:%
+%:%191=97%:%
+%:%193=97%:%
+%:%197=97%:%
+%:%198=97%:%
+%:%200=98%:%
+%:%201=99%:%
+%:%202=100%:%
+%:%203=101%:%
+%:%213=104%:%
+%:%214=105%:%
+%:%215=106%:%
+%:%216=107%:%
+%:%217=108%:%
+%:%218=109%:%
+%:%219=110%:%
+%:%220=111%:%
+%:%221=112%:%
+%:%223=115%:%
+%:%224=115%:%
+%:%225=116%:%
+%:%226=117%:%
+%:%227=118%:%
+%:%228=118%:%
+%:%230=118%:%
+%:%234=118%:%
+%:%235=118%:%
+%:%237=119%:%
+%:%238=120%:%
+%:%239=121%:%
+%:%240=122%:%
+%:%250=124%:%
+%:%251=125%:%
+%:%252=126%:%
+%:%253=127%:%
+%:%257=129%:%
+%:%261=131%:%
+%:%262=132%:%
+%:%263=133%:%
+%:%264=134%:%
+%:%265=135%:%
+%:%267=137%:%
+%:%268=137%:%
+%:%269=138%:%
+%:%270=139%:%
+%:%271=140%:%
+%:%272=140%:%
+%:%274=140%:%
+%:%278=140%:%
+%:%279=140%:%
+%:%281=141%:%
+%:%282=142%:%
+%:%283=143%:%
+%:%284=144%:%
+%:%294=146%:%
+%:%295=147%:%
+%:%296=148%:%
+%:%298=150%:%
+%:%299=150%:%

### 2021-04-27 paper/output/document/relatedwork.tex
added related work and some more kroy

%
\begin{isabellebody}%
\setisabellecontext{relatedwork}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Related Work%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In 1685, Leibniz dreamed of a universal calculator that could be used to resolve philosophical 
and theological disputes. At the time, the logical and computational resources necessary to make his 
dream a reality did not exist. Today, automated ethics is a growing field, spurred in part by the need for
ethically intelligent AI agents.

Tolmeijer et al. \cite{mesurvey} develop a taxonomy of implementation of machine ethics. An implementation is characterized
by (1) the choice of ethical theory, (2) implementation design decisions like testing, and (3) implementation
details like choice of logic.

In this paper, I formalize Kant's ethical theory. There is a long line of work formalizing other 
kinds of ethical theories, like consequentialism \cite{util1, util2} or particularism \cite{particularism1, particularism2}. 
Kantian ethics is a deontological, or rule based ethic, and there is also prior work formalizing deontology \cite{dde, deon1, deon2} more broadly. 
Kantian ethics specifically appears to be an intuitive candidate for formalization. In 2006, 
Powers \cite{powers} argued that a formalization of Kantian ethics presented technical challenges,
 such as automation of a non-monotonic logic, and philosophical challenges, like a definition of the 
categorical imperative. There has also been prior work in formalizing Kantian metaphysics using
 I/O logic \cite{io}. Deontic logic itself is inspired by Kant's ``ought implies can" principle, 
but it does not include a robust formalization of the entire categorical imperative \cite{cresswell}.

Lindner and Bentzen \cite{BL} have presented a formalization of Kant's second formulation of the categorical 
imperative using a custom logic. They present their goal as ``not to get close to a correct interpretation
 of Kant, but to show that our interpretation of Kant’s ideas can contribute to the development of 
machine ethics." My work aims to formalize Kant's ethic as faithfully as possible. I draw on the 
centuries of work in moral philosophy, as opposed to developing my own ethical theory. I also hope to 
formalize the first and third formulation of the categorical imperative as well.

The implementation of this paper builds on Benzmueller, Parent, and Farjami's work 
on the LogiKey framework for machine ethics \cite{BFP, logikey}. The LogiKey project has done a significant 
amount of formalized metaphysics \cite{godel, metaphysics1}. Fuenmayor and Benzmueller \cite{gewirth} have 
formalized Gewirth's principle of generic consistency, which is similar to Kant's formula of universal law.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/relatedwork.thy%:%
%:%24=6%:%
%:%36=8%:%
%:%37=9%:%
%:%38=10%:%
%:%39=11%:%
%:%40=12%:%
%:%41=13%:%
%:%42=14%:%
%:%43=15%:%
%:%44=16%:%
%:%45=17%:%
%:%46=18%:%
%:%47=19%:%
%:%48=20%:%
%:%49=21%:%
%:%50=22%:%
%:%51=23%:%
%:%52=24%:%
%:%53=25%:%
%:%54=26%:%
%:%55=27%:%
%:%56=28%:%
%:%57=29%:%
%:%58=30%:%
%:%59=31%:%
%:%60=32%:%
%:%61=33%:%
%:%62=34%:%
%:%63=35%:%
%:%64=36%:%
%:%65=37%:%

### 2021-04-28 paper/output/document/futurework.tex
added kroy and prettified

@@
 The ultimate goal of the project is to present my own formalization of the categorical imperative that escapes
-the limitations on the naive formalization and Kroy's formalization revealed by my tests. This formalization
+the limitations of the naive formalization and Kroy's formalization. This formalization
 will likely require some additional logical machinery to handle the complete notion of a maxim, including 
 an agent, action, and end. My formalization will also patch up some of the holes in DDL itself that have been
-problematic for my project so far, such as the existence of contradictory obligations. I intend to formalize
+problematic for my project so far, such as the existence of contradictory obligations. I intend to formalize and implement
 all three formulations of the categorical imperative.
@@
 I will then test my formalization of the categorical imperative. I will create two kinds of tests. First,
-I will create metaethical tests that show logical properties independent of any model specification as I did
+I will create metaethical tests that show logical properties independent of any model specification, as I did
 for the first two formalizations. Second, I will create tests that specify models and apply my formalization

### 2021-04-28 paper/output/document/paper.tex
added kroy and prettified

@@
 \begin{isamarkuptext}%
-As artifical reasoners become increasingly powerful, computers become increasingly able to 
-perform complex ethical reasoning. The field of machine ethics \cite{mesurvey} is attractive for two reasons.
+As artifical reasoners become increasingly powerful, computers become capable of
+performing complex ethical reasoning. The field of machine ethics \cite{mesurvey} is interesting for two reasons.
 First, the proliferation of artifically autonomous agents is creating and will continue to create a demand for 
-ethical autonomous agents. These agents must be able to model and reason about complex ethical theories 
+automated ethics. These agents must be able to reason about complex ethical theories 
 that withstand philosophical scrutiny. Second, just as automated mathematical reasoning gives mathematicians
-new powers and proof-finding ability, automated ethical reasoning is a tool that philosophers can use 
+new powers, automated ethical reasoning is a tool that philosophers can use 
 when reasoning about ethics. Many contradictions or paradoxes with an ethical system may not be 
-immediately obvious to the human eye, but can be easily tested using an automated theorem prover.
+ obvious to the human eye, but can be easily tested using an automated theorem prover.
 
-Modelling ethics without sacrificing the intracacies and complexities of an ethical theory is a 
+Modelling ethics without sacrificing the intracacies of an ethical theory is a 
 challenging computational and philosophical problem. Simple and intuitive computational approaches, 
-such as encoding ethical rules as constraints in a constraint satisfaction problem, fail to capture
+such as encoding ethics as a constraint satisfaction problem, fail to capture
 the complexity of most philosophically plausible systems. On the other hand, it is not immediately clear
@@
 The ideal candidate ethical theory will be both philosophically interesting and easy to 
-formalize. Kantian ethics, often described as ``formal," has been often floated as such a candidate \cite{powers, BL}. 
+formalize. Kantian ethics, often described as ``formal," has been often floated as such a candidate \cite{powers, BL, lin}. 
 The categorical imperative, Kant's universal law of morality, is a moral rule that can be used to 
@@
 
-This project's objective is to automate reasoning about Kantian ethics. I present two different
+This project's objective is to automate Kantian ethics. I present two different
 formalizations of Kant's categorical imperative implemented and tested in the Isabelle/HOL \cite{isabelle} theorem prover.
-Each formalization is modelled as an extension of Carmo and Jones' Dyadic Deontic Logic (DDL). The corresponding 
-DDL formalization is then embedded in higher-order logic (HOL) and implemented in Isabelle. Section 
-3.1 implements and tests the naive formalization, a control group that is equivalent to DDL 
-itself. Section 3.2 examines a more sophisticated formalization inspired by Moshe Kroy's partial 
-formalization of thecategorical imperative.
+I model each formalization  as an extension of Carmo and Jones' Dyadic Deontic Logic (DDL) \cite{CJDDL}. I then embed the corresponding 
+DDL formalization in higher-order logic (HOL) and implement it in Isabelle. Section 
+\ref{sec:naive} implements and tests the naive formalization, a ``control group" that is clearly implausible but 
+demonstrates the methods and tools of my approach. Section \ref{sec:kroy} implements a more sophisticated 
+formalization inspired by Moshe Kroy's partial formalization of the categorical imperative.
 
@@
 lends itself to formalization. Second, the choice of formal logic to model the theory in. Third, the 
-choice of automation engine to implement the formal model in. Section 2.1 introduces Kantian
-ethics, Section 2.2 explains Carmo and Jones's Dyadic Deontic Logic \cite{CJDDL} as a 
-base logic, and Section 2.3 presents the Isabelle/HOL implementation of the logic.%
+choice of automation engine to implement the formal model in. Section \ref{sec:kant} introduces Kantian
+ethics, Section \ref{sec:DDL} explains Carmo and Jones's Dyadic Deontic Logic \cite{CJDDL} as a 
+base logic, and Section \ref{sec:isabelle} presents the Isabelle/HOL implementation of the logic.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-Kantian ethics is an attractive choice of ethical theory to automate for two reasons. The 
-first is that Kant's writings have been a major inspiration for much of Western analytic philosophy. 
+Kantian ethics is an attractive choice of ethical theory to automates. Kant's writings inspired much of Western analytic philosophy. 
 In addition to the rich neo-Kantian program, almost all major philosophical traditions after Kant have
@@
 and his ethics have bled into household ethical thought. Deontology is seen as one of the three major 
-schools of Western normative philosophy.
+schools of Western analytic ethics.
 
@@
 
-A ``maxim" is roughly a moral rule like ``I can murder someone to take their job". ``Willing" a maxim is 
+A ``maxim" is a moral rule such as, ``I can murder someone to take their job". ``Willing" a maxim is 
 equivalent to acting on that rule. The FUL creates a thought experiment called the universalizability 
@@
 \emph{The Formula of Humanity (FUH)
-is to act in such a way "that you use humanity, whether in your own person or in the person
+is to act in such a way ``that you use humanity, whether in your own person or in the person
 of any other, always at the same time as an end, never merely as a means."}\cite{groundwork}
@@
 
-\emph{The third formulation of the categorical imperative states that "we should so act that we may 
+\emph{The third formulation of the categorical imperative states that ``we should so act that we may 
 think of ourselves as legislating universal laws through our maxims."}\cite{KorsgaardFUL}
@@
 %
-\isamarkupsubsection{Dyadic Deontic Logic%
+\isamarkupsubsection{Dyadic Deontic Logic \label{sec:DDL}%
 }
@@
 \begin{isamarkuptext}%
-Traditional modal logics include $\Box$ operators to represent necessity. In simple modal logics like S5 \cite{cresswell} 
-using the Kripke semantics, $\Box p$ is true at a world $w$ if $p$ is true at all of $w$'s neighbors. 
+Traditional modal logics include the necessitation operator, denoted as $\Box$. In simple modal logic
+using the Kripke semantics s \cite{cresswell}, $\Box p$ is true at a world $w$ if $p$ is true at all of $w$'s neighbors. 
 These logics also usually contain the $\diamond$ operator, representing possibility, where
- $\diamond p \iff \sim \Box \sim p$. Additionally, modal logics support operators of propositional 
+ $\diamond p \iff \sim \Box \sim p$. Additionally, modal logics include operators of propositional 
 logic like $\sim, \wedge, \vee, \rightarrow$.
@@
 A deontic logic is a special kind of modal logic designed to reason about obligation. Standard deontic
-logic \cite{cresswell, sep-logic-deontic} essentially replaces $\Box$ with the obligation operator
+logic \cite{cresswell, sep-logic-deontic} replaces $\Box$ with the obligation operator
 $O$, and $\diamond$ with the permissibility operator $P$. Using the Kripke semantics for $O$, $O p$ 
@@
 
-DDL also includes many other modal operators. In addition to $\Box$ and $\diamond$, DDL also has a notion
+DDL also includes other modal operators. In addition to $\Box$ and $\diamond$, DDL also has a notion
 of actual obligation and possible obligation, represented by operators $O_a$ and $O_p$ respectively. 
@@
 
-For more of fine-grained properties of DDL see \cite{CJDDL} or this project's source code. DDL is quite a heavy logic and contains many modal operators 
+For more of fine-grained properties of DDL see \cite{CJDDL} or this project's source code. DDL is a heavy logic and contains modal operators 
 that aren't necessary for my analysis. While this expressivity is powerful, it may also cause performance
-impacts. In particular, DDL has a large set of axioms involving quantification over complex higher-order
+impacts. DDL has a large set of axioms involving quantification over complex higher-order
 logical expressions. Proofs involving these axioms will be computationally expensive.  Benzmueller 
@@
 \end{isamarkuptext}\isamarkuptrue%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\isatagdocument
-%
-\endisatagdocument
-{\isafolddocument}%
-%
-\isadelimdocument
-%
-\endisadelimdocument
 %
@@
 %:%195=133%:%
-%:%196=134%:%
-%:%205=138%:%
-%:%209=140%:%
+%:%204=137%:%
+%:%208=139%:%
+%:%220=141%:%
 %:%221=142%:%
@@
 %:%245=166%:%
-%:%246=167%:%
-%:%255=169%:%
+%:%254=168%:%
+%:%266=170%:%
 %:%267=171%:%
@@
 %:%284=188%:%
-%:%285=189%:%

### 2021-04-28 paper/output/document/paper22.tex
prof amin's feedback
added kroy and prettified

@@
 %
-\isamarkupsubsection{Isabelle/HOL Implementation%
+\isamarkupsubsection{Isabelle/HOL Implementation \label{sec:isabelle}%
 }
@@
 \ t\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}i\ {\isasymRightarrow}\ bool{\isacharparenright}{\isachardoublequoteclose}\ %
-\isamarkupcmt{t represents a set of DDL formulas.%
+\isamarkupcmt{t represents a set of DDL formulae.%
 }\isanewline
 %
-\isamarkupcmt{A set of formulae is defined by its truth value at a set of worlds. For example, the set {``True"}
+\isamarkupcmt{A set of formulae is defined by its truth value at a set of worlds. For example, the set \{True\}
 would be true at any set of worlds.%
@@
 \ ob{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t\ {\isasymRightarrow}\ {\isacharparenleft}t\ {\isasymRightarrow}\ bool{\isacharparenright}{\isachardoublequoteclose}\ \ %
-\isamarkupcmt{set of propositions obligatory in this "context"%
+\isamarkupcmt{set of propositions obligatory in this context%
 }\isanewline
 \ %
-\isamarkupcmt{ob(context)(term) is True if t is obligatory in this context%
+\isamarkupcmt{ob(context)(term) is True if the term is obligatory in this context%
 }\isanewline
@@
 The syntax that I will work with is defined as abbreviations. Each DDL operator is represented 
-as a HOL formula. A formula defined with the \isatt{abbreviation} command is unfolded in every 
-instance. While the shallow embedding is generally performant (because it uses Isabelle's original 
-syntax tree), abbreviations may possibly hurt performance. In some complicated proofs, we want controlled
-unfolding. Benzmueller and Parent told me that eventually, the performance cost of abbreviations can 
+as a HOL formula. Isabelle automatically unfolds formulae defined with the \isatt{abbreviation} command 
+whenever they are applied. While the shallow embedding is performant (because it uses Isabelle's original 
+syntax tree), abbreviations may hurt performance. In some complicated proofs, we want to control definition
+unfolding. Benzmueller and Parent told me that the performance cost of abbreviations can 
 be mitigated using a definition instead.%
@@
 \isamarkupcmt{Isabelle has built-in support for Nitpick, a model checker. 
-Nitpick successfully found a model satisfying these axioms so the system is consistent.\cite{hintikka}%
+Nitpick successfully found a model satisfying these axioms so the system is consistent.%
 }\isanewline
@@
 \begin{isamarkuptext}%
-{\color{red} Nitpick} \cite{nitpick} can generate models or countermodels, so it's useful to falsify potential
+Nitpick \cite{nitpick} can generate models or countermodels, so it's useful to falsify potential
 theorems, as well as to show consistency. {\color{red} by simp} indicates the proof method. In this 

### 2021-04-28 paper/output/document/paper31.tex
added kroy and prettified

@@
 \begin{isamarkuptext}%
-In this section, I will present three formulations of the categorical imperative. In Section 3.1, I will 
+In this section, I will present two formulations of the categorical imperative. In Section \ref{sec:naive}, I will 
 consider a simple, naive formulation of the formula of universal law. This formulation is, as I will 
 show, clearly not a good ethical rule. The purpose of this section is to explore the kinds of ethical
-tests that Isabelle can carry out. In Section 3.2, I will explore Moshe Kroy's \cite{kroy} partial formalization of 
-the first two formulations of the categorical imperative. I will also explore drawbacks of this attempt, 
-particularly in the lack of the machinery to handle the important Kantian concept of a maxim: an action 
-performed for a particular end. In Section 3.3, I will present my own improved
-formalization of the categorical imperative.%
+tests that Isabelle can carry out. In Section \ref{sec:kroy}, I will explore Moshe Kroy's \cite{kroy} partial formalization of 
+the first two formulations of the categorical imperative.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupsubsection{Naive Formulation of the Formula of Universal Law%
+\isamarkupsubsection{Naive Formulation of the Formula of Universal Law \label{sec:naive}%
 }
@@
 is to will only those maxims that you would simultaneously will universalized. The universalizability 
-test presents negative obligations: if a maxim passes the universalizability test, it is permissible. Else,
+test creates negative obligations: if a maxim passes the universalizability test, it is permissible. Else,
 it is prohibited. In order to appropriately formalize this, we need some notion of permissibility.%
@@
 This naive formalization will require very little additional logical machinery, but more complex
-formalizations may require additional logic concepts beyond just that of permissibility.
+formalizations may require additional logic concepts.
 
@@
 with that maxim through which you can at the same time will that it become a universal law' \cite{groundwork}.
-An immediate translation to DDL is that if A is not necessary permissible then it is prohibited. In other
+An immediate translation to DDL is that if $A$ is not necessary permissible then it is prohibited. In other
 words, if we cannot universalize $P A$ (where universalizing is represented by the modal necessity 
@@
 \isamarkupcmt{This lemma gets to the ``heart" of this naive interpretation. We really want to say that if something
- isn't necessarily obligated, it's not obligated anywhere. "%
+ isn't necessarily obligated, it's not obligated anywhere.%
 }%
@@
 it's wrong everywhere. That being said, it seems like quite a weak claim. We assumed a very strong, moral 
-fact about murder (that it is wrong somewhere), so of course we were able to reach our desired conclusion.%
+fact about murder (that it is wrong somewhere), so it's not surprise that we were able to reach our desired conclusion.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupcmt{Notice that this machinery is quite empty. We don't give an axioms about what a person can or can't do.%
+\isamarkupcmt{Notice that this machinery is quite empty. We don't give axioms about what a person can or can't do.%
 }\isanewline
@@
 This is a rough translation of failure of the universalizability test: we will the maxim universally,
-as represented by the universal quantifier in the first conjunct, and simulataneously \cite{simul}, as represented by 
+as represented by the universal quantifier in the first conjunct, and simultaneously \cite{simul}, as represented by 
 the second conjunct. The FUL tells us that if this sentence is true, then lying should be prohibited. 
@@
 Another initial test is the possibility of arbitrary obligations. If anything can be shown to be 
-obligatory in this theory, then clearly it doesn't track out intuitions.%
+obligatory in this theory, then clearly it doesn't track our intuitions.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 A more complex metaethical property is the possibility of conflicting obligations. Many deontological
-ethics are criticized for prescribing conflicting obligations, but it is clear that in Kantian ethics, 
-obligations are never conflicting \cite{contradictoryob}. In order for morality to be action-guiding, it needs to be free of 
+ethics are criticized for prescribing conflicting obligations, but in Kantian ethics, 
+obligations never conflict \cite{contradictoryob}. In order for morality to be action-guiding, it needs to be free of 
 conflicting obligations. Let's see if we can have contradictary obligations under the naive formalization.%
@@
 %:%40=13%:%
-%:%41=14%:%
-%:%42=15%:%
-%:%43=16%:%
-%:%52=18%:%
+%:%49=15%:%
+%:%61=17%:%
+%:%62=18%:%
+%:%63=19%:%
 %:%64=20%:%
-%:%65=21%:%
 %:%66=22%:%
-%:%67=23%:%
-%:%69=25%:%
-%:%70=25%:%
-%:%71=26%:%
-%:%73=27%:%
-%:%74=28%:%
+%:%67=22%:%
+%:%68=23%:%
+%:%70=24%:%
+%:%71=25%:%
+%:%74=33%:%
+%:%75=34%:%
+%:%76=35%:%
 %:%77=36%:%
@@
 %:%81=40%:%
-%:%82=41%:%
 %:%83=42%:%
-%:%84=43%:%
-%:%86=45%:%
+%:%84=42%:%
+%:%85=43%:%
 %:%87=45%:%
 %:%88=46%:%
+%:%89=47%:%
 %:%90=48%:%
@@
 %:%98=56%:%
-%:%99=57%:%
-%:%100=58%:%
+%:%100=59%:%
 %:%101=59%:%
-%:%103=62%:%
-%:%104=62%:%
-%:%105=62%:%
-%:%107=62%:%
-%:%111=62%:%
-%:%112=62%:%
-%:%114=63%:%
-%:%115=64%:%
-%:%116=65%:%
-%:%117=65%:%
-%:%119=66%:%
-%:%186=113%:%
+%:%102=59%:%
+%:%104=59%:%
+%:%108=59%:%
+%:%109=59%:%
+%:%111=60%:%
+%:%112=61%:%
+%:%113=62%:%
+%:%114=62%:%
+%:%116=63%:%
+%:%183=110%:%
+%:%195=112%:%
+%:%196=113%:%
+%:%197=114%:%
 %:%198=115%:%
-%:%199=116%:%
 %:%200=117%:%
-%:%201=118%:%
-%:%203=120%:%
-%:%204=120%:%
-%:%205=121%:%
-%:%206=121%:%
-%:%218=129%:%
-%:%221=130%:%
-%:%222=130%:%
+%:%201=117%:%
+%:%202=118%:%
+%:%203=118%:%
+%:%215=126%:%
+%:%218=127%:%
+%:%219=127%:%
+%:%221=128%:%
+%:%222=129%:%
+%:%223=130%:%
 %:%224=131%:%
-%:%225=132%:%
-%:%226=133%:%
-%:%227=134%:%
-%:%228=134%:%
-%:%229=135%:%
-%:%230=136%:%
-%:%231=136%:%
-%:%232=137%:%
-%:%233=138%:%
-%:%236=139%:%
-%:%240=139%:%
-%:%241=139%:%
-%:%242=139%:%
-%:%244=140%:%
-%:%245=141%:%
-%:%255=143%:%
-%:%256=144%:%
-%:%257=145%:%
-%:%261=147%:%
-%:%263=149%:%
-%:%264=149%:%
-%:%265=150%:%
-%:%266=150%:%
-%:%267=151%:%
-%:%268=151%:%
-%:%270=152%:%
-%:%271=152%:%
-%:%272=153%:%
-%:%273=154%:%
+%:%225=131%:%
+%:%226=132%:%
+%:%227=133%:%
+%:%228=133%:%
+%:%229=134%:%
+%:%230=135%:%
+%:%233=136%:%
+%:%237=136%:%
+%:%238=136%:%
+%:%239=136%:%
+%:%241=137%:%
+%:%242=138%:%
+%:%252=140%:%
+%:%253=141%:%
+%:%254=142%:%
+%:%258=144%:%
+%:%260=146%:%
+%:%261=146%:%
+%:%262=147%:%
+%:%263=147%:%
+%:%264=148%:%
+%:%265=148%:%
+%:%267=149%:%
+%:%268=149%:%
+%:%269=150%:%
+%:%270=151%:%
+%:%271=151%:%
+%:%273=153%:%
 %:%274=154%:%
+%:%275=155%:%
 %:%276=156%:%
-%:%277=157%:%
 %:%278=158%:%
-%:%279=159%:%
-%:%281=161%:%
+%:%279=158%:%
+%:%280=159%:%
+%:%281=160%:%
 %:%282=161%:%
-%:%283=162%:%
-%:%284=163%:%
-%:%285=164%:%
-%:%286=164%:%
-%:%289=165%:%
-%:%293=165%:%
-%:%294=165%:%
+%:%283=161%:%
+%:%286=162%:%
+%:%290=162%:%
+%:%291=162%:%
+%:%293=163%:%
+%:%294=164%:%
+%:%295=165%:%
 %:%296=166%:%
-%:%297=167%:%
-%:%298=168%:%
-%:%299=169%:%
-%:%300=169%:%
+%:%297=166%:%
+%:%299=167%:%
+%:%300=168%:%
+%:%301=169%:%
 %:%302=170%:%
 %:%303=171%:%
-%:%304=172%:%
-%:%305=173%:%
-%:%306=174%:%
-%:%307=174%:%
-%:%309=175%:%
-%:%310=176%:%
+%:%304=171%:%
+%:%306=172%:%
+%:%307=173%:%
+%:%317=175%:%
+%:%318=176%:%
+%:%319=177%:%
 %:%320=178%:%
@@
 %:%324=182%:%
-%:%325=183%:%
 %:%326=184%:%
-%:%327=185%:%
-%:%329=187%:%
+%:%327=184%:%
+%:%328=185%:%
+%:%329=186%:%
 %:%330=187%:%
-%:%331=188%:%
-%:%332=189%:%
-%:%333=190%:%
-%:%334=190%:%
-%:%336=190%:%
-%:%340=190%:%
-%:%341=190%:%
+%:%331=187%:%
+%:%333=187%:%
+%:%337=187%:%
+%:%338=187%:%
+%:%340=188%:%
+%:%341=189%:%
+%:%342=190%:%
 %:%343=191%:%
@@
 %:%345=193%:%
-%:%346=194%:%
-%:%347=195%:%
-%:%348=196%:%
+%:%355=195%:%
+%:%356=196%:%
+%:%357=197%:%
 %:%358=198%:%
@@
 %:%360=200%:%
-%:%361=201%:%
-%:%362=202%:%
-%:%363=203%:%
-%:%372=205%:%
+%:%369=202%:%
+%:%381=204%:%
+%:%382=205%:%
+%:%383=206%:%
 %:%384=207%:%
@@
 %:%392=215%:%
-%:%393=216%:%
 %:%394=217%:%
-%:%395=218%:%
-%:%397=220%:%
+%:%395=217%:%
+%:%396=218%:%
+%:%397=219%:%
 %:%398=220%:%
-%:%399=221%:%
-%:%400=222%:%
-%:%401=223%:%
-%:%402=223%:%
-%:%404=223%:%
-%:%408=223%:%
-%:%409=223%:%
+%:%399=220%:%
+%:%401=220%:%
+%:%405=220%:%
+%:%406=220%:%
+%:%408=221%:%
+%:%409=222%:%
+%:%410=223%:%
 %:%411=224%:%
-%:%412=225%:%
-%:%413=226%:%
-%:%414=227%:%
-%:%415=227%:%
-%:%417=228%:%
-%:%418=229%:%
-%:%419=229%:%
-%:%421=230%:%
-%:%422=231%:%
+%:%412=224%:%
+%:%414=225%:%
+%:%415=226%:%
+%:%416=226%:%
+%:%418=227%:%
+%:%419=228%:%
+%:%429=230%:%
+%:%430=231%:%
 %:%432=233%:%
-%:%433=234%:%
-%:%435=236%:%
+%:%433=233%:%
+%:%434=234%:%
+%:%435=235%:%
 %:%436=236%:%
-%:%437=237%:%
-%:%438=238%:%
-%:%439=239%:%
-%:%440=239%:%
-%:%442=239%:%
-%:%446=239%:%
-%:%447=239%:%
+%:%437=236%:%
+%:%439=236%:%
+%:%443=236%:%
+%:%444=236%:%
+%:%446=237%:%
+%:%447=238%:%
+%:%448=239%:%
 %:%449=240%:%
-%:%450=241%:%
-%:%451=242%:%
-%:%452=243%:%
-%:%453=243%:%
-%:%455=244%:%
-%:%465=246%:%
+%:%450=240%:%
+%:%452=241%:%
+%:%462=243%:%
+%:%466=245%:%
+%:%467=246%:%
+%:%468=247%:%
 %:%469=248%:%
-%:%470=249%:%
 %:%471=250%:%
-%:%472=251%:%
-%:%474=253%:%
+%:%472=250%:%
+%:%473=251%:%
+%:%474=252%:%
 %:%475=253%:%
-%:%476=254%:%
-%:%477=255%:%
-%:%478=256%:%
-%:%479=256%:%
-%:%481=256%:%
-%:%485=256%:%
-%:%486=256%:%
+%:%476=253%:%
+%:%478=253%:%
+%:%482=253%:%
+%:%483=253%:%
+%:%485=254%:%
+%:%486=255%:%
+%:%487=256%:%
 %:%488=257%:%
-%:%489=258%:%
-%:%490=259%:%
-%:%491=260%:%
-%:%492=260%:%
-%:%494=261%:%
-%:%504=263%:%
+%:%489=257%:%
+%:%491=258%:%
+%:%501=260%:%
+%:%502=261%:%
+%:%503=262%:%
 %:%505=264%:%
-%:%506=265%:%
-%:%508=267%:%
+%:%506=264%:%
+%:%507=265%:%
+%:%508=266%:%
 %:%509=267%:%
-%:%510=268%:%
-%:%511=269%:%
-%:%512=270%:%
-%:%513=270%:%
-%:%515=270%:%
-%:%519=270%:%
-%:%520=270%:%
-%:%522=271%:%
-%:%523=272%:%
-%:%524=273%:%
-%:%525=273%:%
-%:%527=274%:%
-%:%537=276%:%
+%:%510=267%:%
+%:%512=267%:%
+%:%516=267%:%
+%:%517=267%:%
+%:%519=268%:%
+%:%520=269%:%
+%:%521=270%:%
+%:%522=270%:%
+%:%524=271%:%
+%:%534=273%:%
+%:%535=274%:%
+%:%536=275%:%
 %:%538=277%:%
-%:%539=278%:%
-%:%541=280%:%
+%:%539=277%:%
+%:%540=278%:%
+%:%541=279%:%
 %:%542=280%:%
@@
 %:%544=282%:%
-%:%545=283%:%
-%:%546=284%:%
-%:%547=285%:%
-%:%548=285%:%
-%:%555=286%:%
-%:%556=286%:%
-%:%557=287%:%
-%:%558=287%:%
-%:%559=288%:%
-%:%560=288%:%
-%:%561=289%:%
-%:%562=289%:%
-%:%563=289%:%
-%:%564=289%:%
-%:%566=290%:%
-%:%567=291%:%
-%:%568=291%:%
-%:%569=292%:%
-%:%570=292%:%
-%:%571=292%:%
+%:%545=282%:%
+%:%552=283%:%
+%:%553=283%:%
+%:%554=284%:%
+%:%555=284%:%
+%:%556=285%:%
+%:%557=285%:%
+%:%558=286%:%
+%:%559=286%:%
+%:%560=286%:%
+%:%561=286%:%
+%:%563=287%:%
+%:%564=288%:%
+%:%565=288%:%
+%:%566=289%:%
+%:%567=289%:%
+%:%568=289%:%
+%:%570=290%:%
+%:%571=291%:%
+%:%572=292%:%
 %:%573=293%:%
 %:%574=294%:%
-%:%575=295%:%
-%:%576=296%:%
-%:%577=297%:%
-%:%578=297%:%
-%:%580=298%:%
+%:%575=294%:%
+%:%577=295%:%
+%:%587=297%:%
+%:%588=298%:%
+%:%589=299%:%
 %:%590=300%:%
 %:%591=301%:%
-%:%592=302%:%
 %:%593=303%:%
-%:%594=304%:%
-%:%596=306%:%
+%:%594=303%:%
+%:%595=304%:%
+%:%596=305%:%
 %:%597=306%:%
-%:%598=307%:%
-%:%599=308%:%
-%:%600=309%:%
-%:%601=309%:%
-%:%603=309%:%
-%:%607=309%:%
-%:%608=309%:%
+%:%598=306%:%
+%:%600=306%:%
+%:%604=306%:%
+%:%605=306%:%
+%:%607=307%:%
+%:%608=308%:%
+%:%609=309%:%
 %:%610=310%:%
 %:%611=311%:%
-%:%612=312%:%
-%:%613=313%:%
-%:%614=314%:%
-%:%624=316%:%
-%:%625=317%:%
-%:%629=319%:%
-%:%633=321%:%
+%:%621=313%:%
+%:%622=314%:%
+%:%626=316%:%
+%:%630=318%:%
+%:%631=319%:%
+%:%632=320%:%
 %:%634=322%:%
-%:%635=323%:%
-%:%637=325%:%
-%:%638=325%:%
-%:%639=326%:%
-%:%642=327%:%
-%:%646=327%:%
-%:%647=327%:%
-%:%649=328%:%
-%:%650=328%:%
+%:%635=322%:%
+%:%636=323%:%
+%:%639=324%:%
+%:%643=324%:%
+%:%644=324%:%
+%:%646=325%:%
+%:%647=325%:%
+%:%649=326%:%
+%:%650=327%:%
+%:%651=328%:%
 %:%652=329%:%
 %:%653=330%:%
-%:%654=331%:%
-%:%655=332%:%
-%:%656=333%:%
+%:%663=332%:%
+%:%664=333%:%
+%:%665=334%:%
 %:%666=335%:%
-%:%667=336%:%
 %:%668=337%:%
-%:%669=338%:%
-%:%671=340%:%
-%:%672=340%:%
-%:%673=341%:%
-%:%676=342%:%
-%:%680=342%:%
-%:%681=342%:%
-%:%682=342%:%
-%:%684=343%:%
-%:%685=343%:%
+%:%669=337%:%
+%:%670=338%:%
+%:%673=339%:%
+%:%677=339%:%
+%:%678=339%:%
+%:%679=339%:%
+%:%681=340%:%
+%:%682=340%:%

### 2021-04-28 paper/output/document/paper32.tex
added kroy and prettified

@@
 %
-\isamarkupsubsection{Kroy's Formalization of the Categorical Imperative%
+\isamarkupsubsection{Kroy's Formalization of the Categorical Imperative \label{sec:kroy}%
 }
@@
 Kroy's logic relies heavily on some notion of identity or agency. We need some notion of ``x does action", 
-which we can write as ``x is the subject of the sentence 'does action'". This requires defining a subject.%
+which we can write as ``x is the subject of the sentence `does action'". This requires defining a subject.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-\textbf{Obligatory Statements Should be Permissible}%
+\textbf{Obligatory statements should be permissible}%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \isacommand{axiomatization}\isamarkupfalse%
-\ \isakeyword{where}\ permissible{\isacharunderscore}prepreq{\isacharunderscore}ob{\isacharcolon}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymrightarrow}\ P\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-%
+\ \isakeyword{where}\ permissible{\isacharunderscore}prepreq{\isacharunderscore}ob{\isacharcolon}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymrightarrow}\ P\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}%
 \isadelimdocument
@@
 \isatagdocument
+%
+\isamarkupsubsubsection{The Categorical Imperative%
+}
+\isamarkuptrue%
 %
@@
 %
+\begin{isamarkuptext}%
+I will now implement Kroy's formalization of the Formula of Universal Law. Recall that the FUL says
+``act only in accordance with that maxim which you can at the same time will a universal law" \cite{groundwork}.
+Kroy interprets this to mean that if an action is permissible for a specific agent, then it must be permissible for everyone.
+This formalizes an important moral intuition: the categorical imperative prohibits free-riding. No one is a moral exception.
+Formalizing this interpretation requires using open sentences to handle the notion of substitution.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{abbreviation}\isamarkupfalse%
+\ FUL{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}FUL\ {\isasymequiv}\ {\isasymforall}w\ A{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isasymexists}p{\isachardot}\ {\isacharparenleft}\isactrlemph P\ {\isacharbraceleft}A{\isacharbraceright}p\ {\isacharparenright}w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}x{\isachardot}\ {\isacharparenleft}\isactrlemph P\ {\isacharbraceleft}A{\isacharbraceright}x{\isacharparenright}w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{In English, this statement roughly means that if there exists a person $p$ for whom action $A$ is 
+permissible, then action $A$ must be permissible for all agents $x$. The notion of ``permissible for" 
+is captured by the substitution of $x$ for $p$.%
+}%
+\begin{isamarkuptext}%
+Let's check if this is already an axiom of DDL. If so, then the formalization is trivial.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ FUL{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ FUL\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
 \isadelimproof
-%
+\ %
 \endisadelimproof
@@
 \isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
 %
+\isamarkupcmt{\color{blue} Nitpick found a counterexample for card s = 2 and card i = 2:
+
+  Skolem constants:
+    A = ($\lambda x. \_$)($s_1$ := ($\lambda x. \_$)($i_1$ := True, $i_2$ := True), $s_2$ := ($\lambda x. \_$)($i_1$ := False, $i_2$ := False))
+    p = $s_1$
+    x = $s_2$\color{black}%
+}%
 \endisatagproof
@@
 %
+\begin{isamarkuptext}%
+This formalization doesn't hold in DDL, so adding it as an axiom will change the logic.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{axiomatization}\isamarkupfalse%
+\ \isakeyword{where}\ FUL{\isacharcolon}\ FUL%
+\begin{isamarkuptext}%
+Consistency check: is the logic still consistent with the FUL added as an axiom?%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ True\ \isacommand{nitpick}\isamarkupfalse%
+{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ satisfy{\isacharcomma}\ card{\isacharequal}{\isadigit{1}}{\isacharbrackright}%
 \isadelimproof
-%
+\ %
 \endisadelimproof
@@
 \isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
 %
+\isamarkupcmt{\color{blue} Nitpicking formula... 
+Nitpick found a model for card i = 1:
+
+  Empty assignment\color{black}%
+}%
 \endisatagproof
@@
 %
-\isadelimproof
-%
-\endisadelimproof
-%
-\isatagproof
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\isatagdocument
-%
-\endisatagdocument
-{\isafolddocument}%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isatagproof
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\isatagdocument
-%
-\endisatagdocument
-{\isafolddocument}%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isatagproof
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isatagproof
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\isatagdocument
-%
-\endisatagdocument
-{\isafolddocument}%
-%
-\isadelimdocument
-%
-\endisadelimdocument
+\begin{isamarkuptext}%
+This completes my implementation of Kroy's formalization of the first formulation of the 
+categorical imperative. I defined new logical constructs to handle Kroy's logic, studied the differences
+between DDL and Kr, implemented Kroy's formalization of the Formula of Universal Law, and showed 
+that it is both non-trivial and consistent. Next semester, I will pick up where I left off and start testing!%
+\end{isamarkuptext}\isamarkuptrue%
 %
@@
 %:%299=150%:%
+%:%306=153%:%
+%:%318=155%:%
+%:%319=156%:%
+%:%320=157%:%
+%:%321=158%:%
+%:%322=159%:%
+%:%324=161%:%
+%:%325=161%:%
+%:%327=162%:%
+%:%328=163%:%
+%:%329=164%:%
+%:%332=166%:%
+%:%334=168%:%
+%:%335=168%:%
+%:%336=169%:%
+%:%337=170%:%
+%:%338=170%:%
+%:%340=170%:%
+%:%344=170%:%
+%:%345=170%:%
+%:%347=171%:%
+%:%348=172%:%
+%:%349=173%:%
+%:%350=174%:%
+%:%351=175%:%
+%:%352=176%:%
+%:%362=178%:%
+%:%364=180%:%
+%:%365=180%:%
+%:%367=182%:%
+%:%369=184%:%
+%:%370=184%:%
+%:%371=184%:%
+%:%373=184%:%
+%:%377=184%:%
+%:%378=184%:%
+%:%380=185%:%
+%:%381=186%:%
+%:%382=187%:%
+%:%383=188%:%
+%:%393=190%:%
+%:%394=191%:%
+%:%395=192%:%
+%:%396=193%:%

### 2021-04-28 paper/output/document/relatedwork.tex
added kroy and prettified

@@
 
-Tolmeijer et al. \cite{mesurvey} develop a taxonomy of implementation of machine ethics. An implementation is characterized
-by (1) the choice of ethical theory, (2) implementation design decisions like testing, and (3) implementation
-details like choice of logic.
+Tolmeijer et al. \cite{mesurvey} developed a taxonomy of works in implementing machine ethics. An implementation is characterized
+by (1) the choice of ethical theory, (2) implementation design decisions (e.g. testing), and (3) implementation
+details (e.g. choice of logic).
 
-In this paper, I formalize Kant's ethical theory. There is a long line of work formalizing other 
+In this paper, I formalize Kantian ethics. There is a long line of work implementing other 
 kinds of ethical theories, like consequentialism \cite{util1, util2} or particularism \cite{particularism1, particularism2}. 
-Kantian ethics is a deontological, or rule based ethic, and there is also prior work formalizing deontology \cite{dde, deon1, deon2} more broadly. 
-Kantian ethics specifically appears to be an intuitive candidate for formalization. In 2006, 
-Powers \cite{powers} argued that a formalization of Kantian ethics presented technical challenges,
+Kantian ethics is a deontological, or rule based ethic, and there is also prior work implementing other
+ deontological theories \cite{dde, deon1, deon2}. 
+Kantian ethics specifically appears to be an intuitive candidate for formalization and implementation \cite{powers, lin}. In 2006, 
+Powers \cite{powers} argued that an implementation of of Kantian ethics presented technical challenges,
  such as automation of a non-monotonic logic, and philosophical challenges, like a definition of the 
@@
 
-Lindner and Bentzen \cite{BL} have presented a formalization of Kant's second formulation of the categorical 
+Lindner and Bentzen \cite{BL} have presented a formalization and implementation of Kant's second formulation of the categorical 
 imperative using a custom logic. They present their goal as ``not to get close to a correct interpretation
@@
 centuries of work in moral philosophy, as opposed to developing my own ethical theory. I also hope to 
-formalize the first and third formulation of the categorical imperative as well.
+formalize the first and third formulations of the categorical imperative, in addition to the first.
 
 The implementation of this paper builds on Benzmueller, Parent, and Farjami's work 
-on the LogiKey framework for machine ethics \cite{BFP, logikey}. The LogiKey project has done a significant 
-amount of formalized metaphysics \cite{godel, metaphysics1}. Fuenmayor and Benzmueller \cite{gewirth} have 
-formalized Gewirth's principle of generic consistency, which is similar to Kant's formula of universal law.%
+with the LogiKey framework for machine ethics \cite{BFP, logikey}. The LogiKey project has been used 
+to implement metaphysics \cite{godel, metaphysics1}. Fuenmayor and Benzmueller \cite{gewirth} have 
+implemented Gewirth's principle of generic consistency, which is similar to Kant's formula of universal law.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %:%65=37%:%
+%:%66=38%:%

### 2021-09-09 paper/output/document/paper31.tex
added outline, began Kroy tests

@@
 %
-\isamarkupcmt{Nitpick tells us that the FUL is consistent%
-}%
+\isamarkupcmt{Nitpick tells us that the FUL is consistent\footnote{``oops" at the end of a lemma indicates that the 
+proof is left unfinished. It does not indicate that an error occurred. In this case, we aren't interested
+in proving True (the proof is trivial and automatic), hence the oops.}%
+}\isanewline
+%
 \endisatagproof
@@
 \begin{isamarkuptext}%
-One category of tests is specified models. Specifying the model allows us to encode certain facts 
+One category of tests involves specified models to encode certain facts 
 into the system and then ask questions about obligations. Without specifying the model, we are limited 
@@
 \isacommand{abbreviation}\isamarkupfalse%
-\ lying{\isacharunderscore}not{\isacharunderscore}universal{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}lying{\isacharunderscore}not{\isacharunderscore}universal\ {\isasymequiv}\ {\isasymnot}\ {\isacharparenleft}{\isasymforall}x{\isachardot}\ lie{\isacharparenleft}x{\isacharparenright}\ cw{\isacharparenright}\ {\isasymand}\ {\isacharparenleft}lie{\isacharparenleft}me{\isacharparenright}\ cw{\isacharparenright}{\isachardoublequoteclose}%
-\begin{isamarkuptext}%
-This is a rough translation of failure of the universalizability test: we will the maxim universally,
+\ lying{\isacharunderscore}not{\isacharunderscore}universal{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}lying{\isacharunderscore}not{\isacharunderscore}universal\ {\isasymequiv}\ {\isasymforall}w{\isachardot}\ {\isasymnot}\ {\isacharparenleft}{\isacharparenleft}{\isasymforall}x{\isachardot}\ lie{\isacharparenleft}x{\isacharparenright}\ w{\isacharparenright}\ {\isasymand}\ {\isacharparenleft}lie{\isacharparenleft}me{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
+\begin{isamarkuptext}%
+This is a rough translation of failure of the universalizability test: we will test the maxim universally,
 as represented by the universal quantifier in the first conjunct, and simultaneously \cite{simul}, as represented by 
@@
 doesn't demonstrates the weakness of this naive formulation of the categorical imperative. Kant's version of
-the FUL universalizes across people, as we did in the definition of \isa{lying{\isacharunderscore}not{\isacharunderscore}universal\ {\isasymequiv}\ {\isasymnot}\ {\isacharparenleft}{\isasymforall}x{\isachardot}\ lie\ x\ cw{\isacharparenright}\ {\isasymand}\ lie\ me\ cw}.
+the FUL universalizes across people, as we did in the definition of \isa{lying{\isacharunderscore}not{\isacharunderscore}universal\ {\isasymequiv}\ {\isasymforall}w{\isachardot}\ {\isasymnot}\ {\isacharparenleft}{\isacharparenleft}{\isasymforall}x{\isachardot}\ lie\ x\ w{\isacharparenright}\ {\isasymand}\ lie\ me\ w{\isacharparenright}}.
 The
@@
 %:%71=25%:%
-%:%74=33%:%
-%:%75=34%:%
-%:%76=35%:%
-%:%77=36%:%
-%:%78=37%:%
-%:%79=38%:%
-%:%80=39%:%
-%:%81=40%:%
-%:%83=42%:%
-%:%84=42%:%
-%:%85=43%:%
-%:%87=45%:%
-%:%88=46%:%
-%:%89=47%:%
-%:%90=48%:%
-%:%91=49%:%
-%:%92=50%:%
-%:%93=51%:%
-%:%94=52%:%
-%:%95=53%:%
-%:%96=54%:%
-%:%97=55%:%
-%:%98=56%:%
-%:%100=59%:%
-%:%101=59%:%
-%:%102=59%:%
-%:%104=59%:%
-%:%108=59%:%
-%:%109=59%:%
-%:%111=60%:%
-%:%112=61%:%
-%:%113=62%:%
-%:%114=62%:%
-%:%116=63%:%
-%:%183=110%:%
-%:%195=112%:%
-%:%196=113%:%
-%:%197=114%:%
-%:%198=115%:%
-%:%200=117%:%
-%:%201=117%:%
-%:%202=118%:%
-%:%203=118%:%
-%:%215=126%:%
-%:%218=127%:%
-%:%219=127%:%
-%:%221=128%:%
-%:%222=129%:%
-%:%223=130%:%
-%:%224=131%:%
-%:%225=131%:%
-%:%226=132%:%
-%:%227=133%:%
-%:%228=133%:%
-%:%229=134%:%
-%:%230=135%:%
-%:%233=136%:%
-%:%237=136%:%
-%:%238=136%:%
-%:%239=136%:%
-%:%241=137%:%
-%:%242=138%:%
-%:%252=140%:%
-%:%253=141%:%
-%:%254=142%:%
-%:%258=144%:%
-%:%260=146%:%
-%:%261=146%:%
-%:%262=147%:%
-%:%263=147%:%
-%:%264=148%:%
-%:%265=148%:%
-%:%267=149%:%
-%:%268=149%:%
-%:%269=150%:%
-%:%270=151%:%
-%:%271=151%:%
-%:%273=153%:%
-%:%274=154%:%
-%:%275=155%:%
-%:%276=156%:%
-%:%278=158%:%
-%:%279=158%:%
-%:%280=159%:%
-%:%281=160%:%
-%:%282=161%:%
-%:%283=161%:%
-%:%286=162%:%
-%:%290=162%:%
-%:%291=162%:%
-%:%293=163%:%
-%:%294=164%:%
-%:%295=165%:%
-%:%296=166%:%
-%:%297=166%:%
-%:%299=167%:%
-%:%300=168%:%
-%:%301=169%:%
-%:%302=170%:%
-%:%303=171%:%
-%:%304=171%:%
-%:%306=172%:%
-%:%307=173%:%
-%:%317=175%:%
-%:%318=176%:%
-%:%319=177%:%
-%:%320=178%:%
-%:%321=179%:%
-%:%322=180%:%
-%:%323=181%:%
-%:%324=182%:%
-%:%326=184%:%
-%:%327=184%:%
-%:%328=185%:%
-%:%329=186%:%
-%:%330=187%:%
-%:%331=187%:%
-%:%333=187%:%
-%:%337=187%:%
-%:%338=187%:%
-%:%340=188%:%
-%:%341=189%:%
-%:%342=190%:%
-%:%343=191%:%
-%:%344=192%:%
-%:%345=193%:%
-%:%355=195%:%
-%:%356=196%:%
-%:%357=197%:%
-%:%358=198%:%
-%:%359=199%:%
-%:%360=200%:%
-%:%369=202%:%
-%:%381=204%:%
-%:%382=205%:%
-%:%383=206%:%
-%:%384=207%:%
-%:%385=208%:%
-%:%386=209%:%
-%:%387=210%:%
-%:%388=211%:%
-%:%389=212%:%
-%:%390=213%:%
-%:%391=214%:%
-%:%392=215%:%
-%:%394=217%:%
-%:%395=217%:%
-%:%396=218%:%
-%:%397=219%:%
-%:%398=220%:%
-%:%399=220%:%
-%:%401=220%:%
-%:%405=220%:%
-%:%406=220%:%
-%:%408=221%:%
-%:%409=222%:%
-%:%410=223%:%
-%:%411=224%:%
-%:%412=224%:%
-%:%414=225%:%
-%:%415=226%:%
-%:%416=226%:%
-%:%418=227%:%
-%:%419=228%:%
-%:%429=230%:%
-%:%430=231%:%
-%:%432=233%:%
-%:%433=233%:%
-%:%434=234%:%
-%:%435=235%:%
-%:%436=236%:%
-%:%437=236%:%
-%:%439=236%:%
-%:%443=236%:%
-%:%444=236%:%
-%:%446=237%:%
-%:%447=238%:%
-%:%448=239%:%
-%:%449=240%:%
-%:%450=240%:%
-%:%452=241%:%
-%:%462=243%:%
-%:%466=245%:%
-%:%467=246%:%
-%:%468=247%:%
-%:%469=248%:%
-%:%471=250%:%
-%:%472=250%:%
-%:%473=251%:%
-%:%474=252%:%
-%:%475=253%:%
-%:%476=253%:%
-%:%478=253%:%
-%:%482=253%:%
-%:%483=253%:%
-%:%485=254%:%
-%:%486=255%:%
-%:%487=256%:%
-%:%488=257%:%
-%:%489=257%:%
-%:%491=258%:%
-%:%501=260%:%
-%:%502=261%:%
-%:%503=262%:%
-%:%505=264%:%
-%:%506=264%:%
-%:%507=265%:%
-%:%508=266%:%
-%:%509=267%:%
-%:%510=267%:%
-%:%512=267%:%
-%:%516=267%:%
-%:%517=267%:%
-%:%519=268%:%
-%:%520=269%:%
-%:%521=270%:%
-%:%522=270%:%
-%:%524=271%:%
-%:%534=273%:%
-%:%535=274%:%
-%:%536=275%:%
-%:%538=277%:%
-%:%539=277%:%
-%:%540=278%:%
-%:%541=279%:%
-%:%542=280%:%
-%:%543=281%:%
-%:%544=282%:%
-%:%545=282%:%
-%:%552=283%:%
-%:%553=283%:%
-%:%554=284%:%
-%:%555=284%:%
-%:%556=285%:%
-%:%557=285%:%
-%:%558=286%:%
-%:%559=286%:%
-%:%560=286%:%
-%:%561=286%:%
-%:%563=287%:%
-%:%564=288%:%
-%:%565=288%:%
-%:%566=289%:%
-%:%567=289%:%
-%:%568=289%:%
-%:%570=290%:%
-%:%571=291%:%
-%:%572=292%:%
-%:%573=293%:%
-%:%574=294%:%
-%:%575=294%:%
-%:%577=295%:%
-%:%587=297%:%
-%:%588=298%:%
-%:%589=299%:%
-%:%590=300%:%
-%:%591=301%:%
-%:%593=303%:%
-%:%594=303%:%
-%:%595=304%:%
-%:%596=305%:%
-%:%597=306%:%
-%:%598=306%:%
-%:%600=306%:%
-%:%604=306%:%
-%:%605=306%:%
-%:%607=307%:%
-%:%608=308%:%
-%:%609=309%:%
-%:%610=310%:%
-%:%611=311%:%
-%:%621=313%:%
-%:%622=314%:%
-%:%626=316%:%
-%:%630=318%:%
-%:%631=319%:%
-%:%632=320%:%
-%:%634=322%:%
-%:%635=322%:%
-%:%636=323%:%
-%:%639=324%:%
-%:%643=324%:%
-%:%644=324%:%
-%:%646=325%:%
-%:%647=325%:%
-%:%649=326%:%
-%:%650=327%:%
-%:%651=328%:%
-%:%652=329%:%
-%:%653=330%:%
-%:%663=332%:%
-%:%664=333%:%
-%:%665=334%:%
-%:%666=335%:%
-%:%668=337%:%
-%:%669=337%:%
-%:%670=338%:%
-%:%673=339%:%
-%:%677=339%:%
-%:%678=339%:%
-%:%679=339%:%
-%:%681=340%:%
-%:%682=340%:%
+%:%74=27%:%
+%:%75=28%:%
+%:%76=29%:%
+%:%77=30%:%
+%:%78=31%:%
+%:%79=32%:%
+%:%80=33%:%
+%:%81=34%:%
+%:%83=36%:%
+%:%84=36%:%
+%:%85=37%:%
+%:%87=39%:%
+%:%88=40%:%
+%:%89=41%:%
+%:%90=42%:%
+%:%91=43%:%
+%:%92=44%:%
+%:%93=45%:%
+%:%94=46%:%
+%:%95=47%:%
+%:%96=48%:%
+%:%97=49%:%
+%:%98=50%:%
+%:%100=53%:%
+%:%101=53%:%
+%:%102=53%:%
+%:%104=53%:%
+%:%108=53%:%
+%:%109=53%:%
+%:%111=54%:%
+%:%112=55%:%
+%:%113=56%:%
+%:%114=56%:%
+%:%116=57%:%
+%:%117=58%:%
+%:%118=59%:%
+%:%119=59%:%
+%:%186=105%:%
+%:%198=107%:%
+%:%199=108%:%
+%:%200=109%:%
+%:%201=110%:%
+%:%203=112%:%
+%:%204=112%:%
+%:%205=113%:%
+%:%206=113%:%
+%:%218=121%:%
+%:%221=122%:%
+%:%222=122%:%
+%:%224=123%:%
+%:%225=124%:%
+%:%226=125%:%
+%:%227=126%:%
+%:%228=126%:%
+%:%229=127%:%
+%:%230=128%:%
+%:%231=128%:%
+%:%232=129%:%
+%:%233=130%:%
+%:%236=131%:%
+%:%240=131%:%
+%:%241=131%:%
+%:%242=131%:%
+%:%244=132%:%
+%:%245=133%:%
+%:%255=135%:%
+%:%256=136%:%
+%:%257=137%:%
+%:%261=139%:%
+%:%263=141%:%
+%:%264=141%:%
+%:%265=142%:%
+%:%266=142%:%
+%:%267=143%:%
+%:%268=143%:%
+%:%270=144%:%
+%:%271=144%:%
+%:%272=145%:%
+%:%273=146%:%
+%:%274=146%:%
+%:%276=148%:%
+%:%277=149%:%
+%:%278=150%:%
+%:%279=151%:%
+%:%281=153%:%
+%:%282=153%:%
+%:%283=154%:%
+%:%284=155%:%
+%:%285=156%:%
+%:%286=156%:%
+%:%289=157%:%
+%:%293=157%:%
+%:%294=157%:%
+%:%296=158%:%
+%:%297=159%:%
+%:%298=160%:%
+%:%299=161%:%
+%:%300=161%:%
+%:%302=162%:%
+%:%303=163%:%
+%:%304=164%:%
+%:%305=165%:%
+%:%306=166%:%
+%:%307=166%:%
+%:%309=167%:%
+%:%310=168%:%
+%:%320=170%:%
+%:%321=171%:%
+%:%322=172%:%
+%:%323=173%:%
+%:%324=174%:%
+%:%325=175%:%
+%:%326=176%:%
+%:%327=177%:%
+%:%329=179%:%
+%:%330=179%:%
+%:%331=180%:%
+%:%332=181%:%
+%:%333=182%:%
+%:%334=182%:%
+%:%336=182%:%
+%:%340=182%:%
+%:%341=182%:%
+%:%343=183%:%
+%:%344=184%:%
+%:%345=185%:%
+%:%346=186%:%
+%:%347=187%:%
+%:%348=188%:%
+%:%358=190%:%
+%:%359=191%:%
+%:%360=192%:%
+%:%361=193%:%
+%:%362=194%:%
+%:%363=195%:%
+%:%372=197%:%
+%:%384=199%:%
+%:%385=200%:%
+%:%386=201%:%
+%:%387=202%:%
+%:%388=203%:%
+%:%389=204%:%
+%:%390=205%:%
+%:%391=206%:%
+%:%392=207%:%
+%:%393=208%:%
+%:%394=209%:%
+%:%395=210%:%
+%:%397=212%:%
+%:%398=212%:%
+%:%399=213%:%
+%:%400=214%:%
+%:%401=215%:%
+%:%402=215%:%
+%:%404=215%:%
+%:%408=215%:%
+%:%409=215%:%
+%:%411=216%:%
+%:%412=217%:%
+%:%413=218%:%
+%:%414=219%:%
+%:%415=219%:%
+%:%417=220%:%
+%:%418=221%:%
+%:%419=221%:%
+%:%421=222%:%
+%:%422=223%:%
+%:%432=225%:%
+%:%433=226%:%
+%:%435=228%:%
+%:%436=228%:%
+%:%437=229%:%
+%:%438=230%:%
+%:%439=231%:%
+%:%440=231%:%
+%:%442=231%:%
+%:%446=231%:%
+%:%447=231%:%
+%:%449=232%:%
+%:%450=233%:%
+%:%451=234%:%
+%:%452=235%:%
+%:%453=235%:%
+%:%455=236%:%
+%:%465=238%:%
+%:%469=240%:%
+%:%470=241%:%
+%:%471=242%:%
+%:%472=243%:%
+%:%474=245%:%
+%:%475=245%:%
+%:%476=246%:%
+%:%477=247%:%
+%:%478=248%:%
+%:%479=248%:%
+%:%481=248%:%
+%:%485=248%:%
+%:%486=248%:%
+%:%488=249%:%
+%:%489=250%:%
+%:%490=251%:%
+%:%491=252%:%
+%:%492=252%:%
+%:%494=253%:%
+%:%504=255%:%
+%:%505=256%:%
+%:%506=257%:%
+%:%508=259%:%
+%:%509=259%:%
+%:%510=260%:%
+%:%511=261%:%
+%:%512=262%:%
+%:%513=262%:%
+%:%515=262%:%
+%:%519=262%:%
+%:%520=262%:%
+%:%522=263%:%
+%:%523=264%:%
+%:%524=265%:%
+%:%525=265%:%
+%:%527=266%:%
+%:%537=268%:%
+%:%538=269%:%
+%:%539=270%:%
+%:%541=272%:%
+%:%542=272%:%
+%:%543=273%:%
+%:%544=274%:%
+%:%545=275%:%
+%:%546=276%:%
+%:%547=277%:%
+%:%548=277%:%
+%:%555=278%:%
+%:%556=278%:%
+%:%557=279%:%
+%:%558=279%:%
+%:%559=280%:%
+%:%560=280%:%
+%:%561=281%:%
+%:%562=281%:%
+%:%563=281%:%
+%:%564=281%:%
+%:%566=282%:%
+%:%567=283%:%
+%:%568=283%:%
+%:%569=284%:%
+%:%570=284%:%
+%:%571=284%:%
+%:%573=285%:%
+%:%574=286%:%
+%:%575=287%:%
+%:%576=288%:%
+%:%577=289%:%
+%:%578=289%:%
+%:%580=290%:%
+%:%590=292%:%
+%:%591=293%:%
+%:%592=294%:%
+%:%593=295%:%
+%:%594=296%:%
+%:%596=298%:%
+%:%597=298%:%
+%:%598=299%:%
+%:%599=300%:%
+%:%600=301%:%
+%:%601=301%:%
+%:%603=301%:%
+%:%607=301%:%
+%:%608=301%:%
+%:%610=302%:%
+%:%611=303%:%
+%:%612=304%:%
+%:%613=305%:%
+%:%614=306%:%
+%:%624=308%:%
+%:%625=309%:%
+%:%629=311%:%
+%:%633=313%:%
+%:%634=314%:%
+%:%635=315%:%
+%:%637=317%:%
+%:%638=317%:%
+%:%639=318%:%
+%:%642=319%:%
+%:%646=319%:%
+%:%647=319%:%
+%:%649=320%:%
+%:%650=320%:%
+%:%652=321%:%
+%:%653=322%:%
+%:%654=323%:%
+%:%655=324%:%
+%:%656=325%:%
+%:%666=327%:%
+%:%667=328%:%
+%:%668=329%:%
+%:%669=330%:%
+%:%671=332%:%
+%:%672=332%:%
+%:%673=333%:%
+%:%676=334%:%
+%:%680=334%:%
+%:%681=334%:%
+%:%682=334%:%
+%:%684=335%:%
+%:%685=335%:%

### 2021-09-12 paper/output/document/paper31.tex
updated stuff

@@
 \isacommand{abbreviation}\isamarkupfalse%
-\ poss{\isacharunderscore}murder{\isacharunderscore}wrong{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}poss{\isacharunderscore}murder{\isacharunderscore}wrong\ {\isasymequiv}\ {\isasymTurnstile}{\isacharparenleft}{\isasymdiamond}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ M{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ possibly{\isacharunderscore}murder{\isacharunderscore}wrong{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}possibly{\isacharunderscore}murder{\isacharunderscore}wrong\ {\isasymequiv}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ M{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ cw{\isachardoublequoteclose}\isanewline
 %
@@
 \ wrong{\isacharunderscore}if{\isacharunderscore}possibly{\isacharunderscore}wrong{\isacharcolon}\isanewline
-\ \ \isakeyword{assumes}\ poss{\isacharunderscore}murder{\isacharunderscore}wrong\isanewline
-\ \ \isakeyword{shows}\ murder{\isacharunderscore}wrong\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}possibly{\isacharunderscore}murder{\isacharunderscore}wrong\ {\isasymlongrightarrow}\ murder{\isacharunderscore}wrong{\isachardoublequoteclose}\isanewline
 %
@@
 \isatagproof
-\isacommand{using}\isamarkupfalse%
-\ assms\ \isacommand{by}\isamarkupfalse%
-\ blast\isanewline
+\isacommand{by}\isamarkupfalse%
+\ simp\isanewline
 %
@@
 \end{isamarkuptext}\isamarkuptrue%
+\ \ \isacommand{lemma}\isamarkupfalse%
+\ permissible{\isacharcolon}\isanewline
+\ \ \ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymexists}A{\isachardot}\ {\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
+\ \ \ \ \isacommand{nitpick}\isamarkupfalse%
+\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{\color{blue}Nitpick found a model for card i = 1 and card s = 1:
+
+  Skolem constant:
+    A =($\lambda x. \_$)($i_1$ := False) \color{black}%
+}\isanewline
+%
+\isamarkupcmt{We want to show that there exists a model where there is some formula A that is permissible, or, 
+in English, that permissibility is possible. Nitpick finds a model where the above formula holds, 
+so permissibility is indeed possible.%
+}\isanewline
+%
+\isamarkupcmt{Note that it's not clear \cite{kitcher} if Kant actually thought that permissibility was a coherent 
+concept. Either way, in modern ethics, permissibility is a pretty widely accepted phenomenon.%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
 \isacommand{lemma}\isamarkupfalse%
-\ permissible{\isacharcolon}\isanewline
+\ fixed{\isacharunderscore}formula{\isacharunderscore}is{\isacharunderscore}permissible{\isacharcolon}\isanewline
 \ \ \isakeyword{fixes}\ A\isanewline
@@
 %
-\isamarkupcmt{This is exactly the desired result above - we have shown that models exist where an action can be 
-neither obligatory nor prohibited.%
-}\isanewline
-%
-\isamarkupcmt{Note that it's not clear \cite{kitcher} if Kant actually thought that permissibility was a coherent 
-concept. Either way, in modern ethics, permissibility is a pretty widely accepted phenomenon.%
+\isamarkupcmt{This is a slightly stronger result: for any arbitrary action A, there is a model that makes it 
+permissible. We actually don't want this to hold, because if A is "murder" then the CI requires that 
+it be prohibited in every world.%
 }%
@@
 %:%232=129%:%
-%:%233=130%:%
-%:%236=131%:%
-%:%240=131%:%
-%:%241=131%:%
+%:%235=130%:%
+%:%239=130%:%
+%:%240=130%:%
 %:%242=131%:%
-%:%244=132%:%
-%:%245=133%:%
-%:%255=135%:%
-%:%256=136%:%
-%:%257=137%:%
-%:%261=139%:%
+%:%243=132%:%
+%:%253=134%:%
+%:%254=135%:%
+%:%255=136%:%
+%:%259=138%:%
+%:%261=140%:%
+%:%262=140%:%
 %:%263=141%:%
@@
 %:%266=142%:%
-%:%267=143%:%
 %:%268=143%:%
+%:%269=143%:%
 %:%270=144%:%
-%:%271=144%:%
+%:%271=145%:%
 %:%272=145%:%
-%:%273=146%:%
-%:%274=146%:%
-%:%276=148%:%
-%:%277=149%:%
-%:%278=150%:%
-%:%279=151%:%
+%:%274=147%:%
+%:%275=148%:%
+%:%276=149%:%
+%:%277=150%:%
+%:%279=152%:%
+%:%280=152%:%
 %:%281=153%:%
-%:%282=153%:%
-%:%283=154%:%
+%:%282=154%:%
+%:%283=155%:%
 %:%284=155%:%
-%:%285=156%:%
-%:%286=156%:%
-%:%289=157%:%
-%:%293=157%:%
+%:%287=156%:%
+%:%291=156%:%
+%:%292=156%:%
 %:%294=157%:%
-%:%296=158%:%
-%:%297=159%:%
+%:%295=158%:%
+%:%296=159%:%
+%:%297=160%:%
 %:%298=160%:%
-%:%299=161%:%
 %:%300=161%:%
-%:%302=162%:%
-%:%303=163%:%
-%:%304=164%:%
+%:%301=162%:%
+%:%302=163%:%
+%:%303=164%:%
+%:%304=165%:%
 %:%305=165%:%
-%:%306=166%:%
 %:%307=166%:%
-%:%309=167%:%
-%:%310=168%:%
-%:%320=170%:%
-%:%321=171%:%
-%:%322=172%:%
-%:%323=173%:%
-%:%324=174%:%
-%:%325=175%:%
-%:%326=176%:%
-%:%327=177%:%
+%:%308=167%:%
+%:%318=169%:%
+%:%319=170%:%
+%:%320=171%:%
+%:%321=172%:%
+%:%322=173%:%
+%:%323=174%:%
+%:%324=175%:%
+%:%325=176%:%
+%:%327=178%:%
+%:%328=178%:%
 %:%329=179%:%
-%:%330=179%:%
-%:%331=180%:%
+%:%330=180%:%
+%:%331=181%:%
 %:%332=181%:%
-%:%333=182%:%
-%:%334=182%:%
-%:%336=182%:%
-%:%340=182%:%
+%:%334=181%:%
+%:%338=181%:%
+%:%339=181%:%
 %:%341=182%:%
-%:%343=183%:%
-%:%344=184%:%
-%:%345=185%:%
-%:%346=186%:%
-%:%347=187%:%
-%:%348=188%:%
-%:%358=190%:%
-%:%359=191%:%
-%:%360=192%:%
-%:%361=193%:%
-%:%362=194%:%
-%:%363=195%:%
-%:%372=197%:%
-%:%384=199%:%
-%:%385=200%:%
-%:%386=201%:%
-%:%387=202%:%
-%:%388=203%:%
-%:%389=204%:%
-%:%390=205%:%
-%:%391=206%:%
-%:%392=207%:%
-%:%393=208%:%
-%:%394=209%:%
+%:%342=183%:%
+%:%343=184%:%
+%:%344=185%:%
+%:%345=186%:%
+%:%346=187%:%
+%:%356=189%:%
+%:%357=190%:%
+%:%358=191%:%
+%:%359=192%:%
+%:%360=193%:%
+%:%361=194%:%
+%:%370=196%:%
+%:%382=198%:%
+%:%383=199%:%
+%:%384=200%:%
+%:%385=201%:%
+%:%386=202%:%
+%:%387=203%:%
+%:%388=204%:%
+%:%389=205%:%
+%:%390=206%:%
+%:%391=207%:%
+%:%392=208%:%
+%:%393=209%:%
 %:%395=210%:%
-%:%397=212%:%
+%:%396=210%:%
+%:%397=211%:%
 %:%398=212%:%
-%:%399=213%:%
-%:%400=214%:%
-%:%401=215%:%
-%:%402=215%:%
-%:%404=215%:%
-%:%408=215%:%
-%:%409=215%:%
+%:%399=212%:%
+%:%401=212%:%
+%:%405=212%:%
+%:%406=212%:%
+%:%408=213%:%
+%:%409=214%:%
+%:%410=215%:%
 %:%411=216%:%
-%:%412=217%:%
-%:%413=218%:%
-%:%414=219%:%
-%:%415=219%:%
-%:%417=220%:%
-%:%418=221%:%
-%:%419=221%:%
-%:%421=222%:%
-%:%422=223%:%
-%:%432=225%:%
-%:%433=226%:%
-%:%435=228%:%
-%:%436=228%:%
-%:%437=229%:%
-%:%438=230%:%
-%:%439=231%:%
-%:%440=231%:%
-%:%442=231%:%
-%:%446=231%:%
-%:%447=231%:%
-%:%449=232%:%
-%:%450=233%:%
-%:%451=234%:%
-%:%452=235%:%
-%:%453=235%:%
-%:%455=236%:%
+%:%412=216%:%
+%:%414=217%:%
+%:%415=218%:%
+%:%416=219%:%
+%:%417=219%:%
+%:%419=220%:%
+%:%420=221%:%
+%:%428=221%:%
+%:%429=222%:%
+%:%430=223%:%
+%:%431=223%:%
+%:%432=224%:%
+%:%433=225%:%
+%:%434=226%:%
+%:%435=226%:%
+%:%437=226%:%
+%:%441=226%:%
+%:%442=226%:%
+%:%444=227%:%
+%:%445=228%:%
+%:%446=229%:%
+%:%447=230%:%
+%:%448=230%:%
+%:%450=231%:%
+%:%451=232%:%
+%:%452=233%:%
+%:%462=235%:%
+%:%463=236%:%
 %:%465=238%:%
-%:%469=240%:%
+%:%466=238%:%
+%:%467=239%:%
+%:%468=240%:%
+%:%469=241%:%
 %:%470=241%:%
-%:%471=242%:%
-%:%472=243%:%
-%:%474=245%:%
-%:%475=245%:%
-%:%476=246%:%
-%:%477=247%:%
-%:%478=248%:%
-%:%479=248%:%
-%:%481=248%:%
-%:%485=248%:%
-%:%486=248%:%
-%:%488=249%:%
-%:%489=250%:%
-%:%490=251%:%
-%:%491=252%:%
-%:%492=252%:%
-%:%494=253%:%
+%:%472=241%:%
+%:%476=241%:%
+%:%477=241%:%
+%:%479=242%:%
+%:%480=243%:%
+%:%481=244%:%
+%:%482=245%:%
+%:%483=245%:%
+%:%485=246%:%
+%:%495=248%:%
+%:%499=250%:%
+%:%500=251%:%
+%:%501=252%:%
+%:%502=253%:%
 %:%504=255%:%
-%:%505=256%:%
-%:%506=257%:%
-%:%508=259%:%
-%:%509=259%:%
-%:%510=260%:%
-%:%511=261%:%
-%:%512=262%:%
-%:%513=262%:%
-%:%515=262%:%
-%:%519=262%:%
-%:%520=262%:%
-%:%522=263%:%
-%:%523=264%:%
-%:%524=265%:%
-%:%525=265%:%
-%:%527=266%:%
-%:%537=268%:%
+%:%505=255%:%
+%:%506=256%:%
+%:%507=257%:%
+%:%508=258%:%
+%:%509=258%:%
+%:%511=258%:%
+%:%515=258%:%
+%:%516=258%:%
+%:%518=259%:%
+%:%519=260%:%
+%:%520=261%:%
+%:%521=262%:%
+%:%522=262%:%
+%:%524=263%:%
+%:%534=265%:%
+%:%535=266%:%
+%:%536=267%:%
 %:%538=269%:%
-%:%539=270%:%
-%:%541=272%:%
+%:%539=269%:%
+%:%540=270%:%
+%:%541=271%:%
 %:%542=272%:%
-%:%543=273%:%
-%:%544=274%:%
-%:%545=275%:%
-%:%546=276%:%
-%:%547=277%:%
-%:%548=277%:%
-%:%555=278%:%
-%:%556=278%:%
-%:%557=279%:%
-%:%558=279%:%
-%:%559=280%:%
-%:%560=280%:%
-%:%561=281%:%
-%:%562=281%:%
-%:%563=281%:%
-%:%564=281%:%
-%:%566=282%:%
-%:%567=283%:%
-%:%568=283%:%
-%:%569=284%:%
-%:%570=284%:%
-%:%571=284%:%
-%:%573=285%:%
-%:%574=286%:%
-%:%575=287%:%
-%:%576=288%:%
-%:%577=289%:%
-%:%578=289%:%
-%:%580=290%:%
-%:%590=292%:%
-%:%591=293%:%
-%:%592=294%:%
-%:%593=295%:%
-%:%594=296%:%
-%:%596=298%:%
-%:%597=298%:%
-%:%598=299%:%
-%:%599=300%:%
-%:%600=301%:%
-%:%601=301%:%
-%:%603=301%:%
-%:%607=301%:%
-%:%608=301%:%
-%:%610=302%:%
-%:%611=303%:%
-%:%612=304%:%
-%:%613=305%:%
-%:%614=306%:%
-%:%624=308%:%
-%:%625=309%:%
-%:%629=311%:%
-%:%633=313%:%
-%:%634=314%:%
-%:%635=315%:%
-%:%637=317%:%
-%:%638=317%:%
-%:%639=318%:%
-%:%642=319%:%
-%:%646=319%:%
-%:%647=319%:%
-%:%649=320%:%
-%:%650=320%:%
-%:%652=321%:%
-%:%653=322%:%
-%:%654=323%:%
-%:%655=324%:%
-%:%656=325%:%
-%:%666=327%:%
-%:%667=328%:%
-%:%668=329%:%
-%:%669=330%:%
-%:%671=332%:%
-%:%672=332%:%
-%:%673=333%:%
-%:%676=334%:%
-%:%680=334%:%
-%:%681=334%:%
-%:%682=334%:%
-%:%684=335%:%
-%:%685=335%:%
+%:%543=272%:%
+%:%545=272%:%
+%:%549=272%:%
+%:%550=272%:%
+%:%552=273%:%
+%:%553=274%:%
+%:%554=275%:%
+%:%555=275%:%
+%:%557=276%:%
+%:%567=278%:%
+%:%568=279%:%
+%:%569=280%:%
+%:%571=282%:%
+%:%572=282%:%
+%:%573=283%:%
+%:%574=284%:%
+%:%575=285%:%
+%:%576=286%:%
+%:%577=287%:%
+%:%578=287%:%
+%:%585=288%:%
+%:%586=288%:%
+%:%587=289%:%
+%:%588=289%:%
+%:%589=290%:%
+%:%590=290%:%
+%:%591=291%:%
+%:%592=291%:%
+%:%593=291%:%
+%:%594=291%:%
+%:%596=292%:%
+%:%597=293%:%
+%:%598=293%:%
+%:%599=294%:%
+%:%600=294%:%
+%:%601=294%:%
+%:%603=295%:%
+%:%604=296%:%
+%:%605=297%:%
+%:%606=298%:%
+%:%607=299%:%
+%:%608=299%:%
+%:%610=300%:%
+%:%620=302%:%
+%:%621=303%:%
+%:%622=304%:%
+%:%623=305%:%
+%:%624=306%:%
+%:%626=308%:%
+%:%627=308%:%
+%:%628=309%:%
+%:%629=310%:%
+%:%630=311%:%
+%:%631=311%:%
+%:%633=311%:%
+%:%637=311%:%
+%:%638=311%:%
+%:%640=312%:%
+%:%641=313%:%
+%:%642=314%:%
+%:%643=315%:%
+%:%644=316%:%
+%:%654=318%:%
+%:%655=319%:%
+%:%659=321%:%
+%:%663=323%:%
+%:%664=324%:%
+%:%665=325%:%
+%:%667=327%:%
+%:%668=327%:%
+%:%669=328%:%
+%:%672=329%:%
+%:%676=329%:%
+%:%677=329%:%
+%:%679=330%:%
+%:%680=330%:%
+%:%682=331%:%
+%:%683=332%:%
+%:%684=333%:%
+%:%685=334%:%
+%:%686=335%:%
+%:%696=337%:%
+%:%697=338%:%
+%:%698=339%:%
+%:%699=340%:%
+%:%701=342%:%
+%:%702=342%:%
+%:%703=343%:%
+%:%706=344%:%
+%:%710=344%:%
+%:%711=344%:%
+%:%712=344%:%
+%:%714=345%:%
+%:%715=345%:%

### 2021-09-12 paper/output/document/paper32.tex
updated stuff

@@
 \begin{isamarkuptext}%
-This particular difference seems untenable. Most ethical theories require that if something is 
-obligatory, it must also be permissible. This is an important enough property of an ethical theory that I 
-will add it as an axiom.%
+This particular difference seems untenable. My custom formalization of the categorical imperative 
+must add this as an axiom.%
 \end{isamarkuptext}\isamarkuptrue%
-\isacommand{axiomatization}\isamarkupfalse%
-\ \isakeyword{where}\ permissible{\isacharunderscore}prepreq{\isacharunderscore}ob{\isacharcolon}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymrightarrow}\ P\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}%
+%
 \isadelimdocument
@@
 \isacommand{abbreviation}\isamarkupfalse%
-\ FUL{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}FUL\ {\isasymequiv}\ {\isasymforall}w\ A{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isasymexists}p{\isachardot}\ {\isacharparenleft}\isactrlemph P\ {\isacharbraceleft}A{\isacharbraceright}p\ {\isacharparenright}w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}x{\isachardot}\ {\isacharparenleft}\isactrlemph P\ {\isacharbraceleft}A{\isacharbraceright}x{\isacharparenright}w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ FUL{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}FUL\ {\isasymequiv}\ {\isasymforall}w\ A{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isasymexists}p{\isacharcolon}{\isacharcolon}s{\isachardot}\ {\isacharparenleft}{\isacharparenleft}P\ {\isacharbraceleft}A\ p{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}\ \ {\isasymlongrightarrow}{\isacharparenleft}\ {\isacharparenleft}{\isasymforall}p{\isachardot}{\isacharparenleft}\ P\ {\isacharbraceleft}A\ p{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isacharparenright}\ {\isachardoublequoteclose}%
+\begin{isamarkuptext}%
+P {A p} vs *P{A} p%
+\end{isamarkuptext}\isamarkuptrue%
 %
-\isamarkupcmt{In English, this statement roughly means that if there exists a person $p$ for whom action $A$ is 
-permissible, then action $A$ must be permissible for all agents $x$. The notion of ``permissible for" 
+\isamarkupcmt{In English, this statement roughly means that, for any person $p$ if action $A$ is 
+permissible for $p$, then action $A$ must be permissible for all agents $x$. The notion of ``permissible for" 
 is captured by the substitution of $x$ for $p$.%
@@
 between DDL and Kr, implemented Kroy's formalization of the Formula of Universal Law, and showed 
-that it is both non-trivial and consistent. Next semester, I will pick up where I left off and start testing!%
+that it is both non-trivial and consistent. Now it's time to start testing!%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsubsection{Application Tests%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
+Recall that in Section 3.1.1, we tested the naive interpretation's ability to show that murder 
+is wrong. We started by showing that if murder is possibly wrong, then it is wrong. Let's test that 
+here.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{consts}\isamarkupfalse%
+\ M{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Let the constant $M$ denote murder.%
+}\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ wrong{\isacharunderscore}if{\isacharunderscore}possibly{\isacharunderscore}wrong{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}{\isasymdiamond}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ M{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ cw{\isacharparenright}\ {\isasymlongrightarrow}\ \ {\isacharparenleft}{\isasymforall}w{\isachardot}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ M{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{by}\isamarkupfalse%
+\ simp%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+This is the same result we got in Section 3.1.1—if murder is wrong at some world, it is wrong at
+every world. Kroy's formulation shouldn't actually mean that this property holds. Kroy interprets the 
+FUL as universalizing across $people$, not worlds. In other words, Kroy's formulation implies that if
+murder is wrong for someone, then it is wrong for everyone. This strange result is actually a property 
+of DDL itself, not a property of Kroy's formalization. Indeed, repeating this experiment in DDL, with no
+additional axioms that represent the categorical imperative shows that, in DDL, if something is 
+possible wrong, it is wrong at every world. So this is not a useful example to test any formulation,
+since it holds in the base logic itself.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+Let's try adapting our murder wrong axiom to Kroy's formulation. In particular, let's see if 
+murder being wrong for one person means that it's wrong for everyone.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{consts}\isamarkupfalse%
+\ M{\isadigit{2}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}os{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Let's define murder as an open sentence this time, so that we can substitute in different people.%
+}\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ wrong{\isacharunderscore}if{\isacharunderscore}wrong{\isacharunderscore}for{\isacharunderscore}someone{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymexists}p{\isachardot}\ {\isasymTurnstile}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}{\isacharparenleft}M{\isadigit{2}}\ p{\isacharparenright}{\isacharbraceright}{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ {\isasymTurnstile}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}{\isacharparenleft}M{\isadigit{2}}\ p{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{proof}\isamarkupfalse%
+\ \isanewline
+\ \ \ \ \isacommand{assume}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymexists}p{\isachardot}\ {\isasymTurnstile}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}{\isacharparenleft}M{\isadigit{2}}\ p{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \ \ \isacommand{show}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymforall}p{\isachardot}\ {\isasymTurnstile}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}{\isacharparenleft}M{\isadigit{2}}\ p{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \ \ \ \ \isacommand{using}\isamarkupfalse%
+\ FUL\ {\isacartoucheopen}{\isasymexists}p{\isachardot}\ {\isasymTurnstile}\isactrlemph O{\isacharbraceleft}\isactrlemph {\isasymnot}M{\isadigit{2}}{\isacharbraceright}\ p{\isacartoucheclose}\ \isacommand{by}\isamarkupfalse%
+\ blast\isanewline
+\ \ \isacommand{qed}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{This lemma gets to the heart of Kroy's formulation of the categorical imperative. If murder is prohobited
+for a specific person $p$, then it must be prohobited for all people. This test case also revealed a 
+bug in my original implementation of Kroy's formulation of the FUL, demonstrating the power of such 
+philosophical tests for automated ethics. Just as engineers use TDD to find bugs in their code, philosophers
+and ethicists can use this approach to find bugs in the precise formulations of their theories.%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+For the naive implementation, we also tested the slightly stronger proposition that if not 
+everyone can simultaneously lie, then lying is prohibited. We want to show that if lying 
+fails the universalizability test, then the FUL prohibits it.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{consts}\isamarkupfalse%
+\ lie{\isacharcolon}{\isacharcolon}os\ \isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ lying{\isacharunderscore}not{\isacharunderscore}universal{\isacharcolon}{\isacharcolon}bool\ \isakeyword{where}\ {\isachardoublequoteopen}lying{\isacharunderscore}not{\isacharunderscore}universal\ {\isasymequiv}\ {\isasymforall}w{\isachardot}\ {\isasymnot}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ lie{\isacharparenleft}p{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{The formula above reads, ``At all worlds, it is not the case that everyone lies."%
+}\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ lying{\isacharunderscore}prohibited{\isacharcolon}\isanewline
+\ \ \isakeyword{fixes}\ p\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}\ lying{\isacharunderscore}not{\isacharunderscore}universal\ {\isasymlongrightarrow}\ {\isasymTurnstile}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}lie{\isacharparenleft}p{\isacharparenright}{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{$\color{blue}$Nitpick found a counterexample for card i = 1 and card s = 1:
+
+  Free variable:
+    p = $s_1$
+  Skolem constant:
+    $\lambda$w. p = ($\lambda$x. $\_$)($i_1$ := $s_1$) $\color{black}$%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+Kroy's formulation also fails to show that if not everyone can lie, then lying is prohibited. 
+      There may be an issue here with our representation of lying not being universal. Specifically, 
+      the FUL is violated if it's not $possible$ for everyone to simultaneously lie, but the abbreviation 
+      above merely represents that fact that not everyone does, in fact, simultaneously lie. It's entirely
+      possible that everyone can simultaneously lie, but for some reason, maybe out of some moral sense, 
+      do not. Let's test a more accurate version of the failure of the universalizability test.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+We want to represent the sentence, call it $S$ $\longleftrightarrow$ ``At all worlds, it is not possible that everyone lies simultaneously.
+      Representing this sentence requires that we apply a universal quantifier inside the possible operator,
+      something that DDL does not support as-is. There are two options here. (1) We can pull the universal outside
+      the diamond operator, resulting in the sentence ``At all worlds, for all people, it is not possible that 
+      they lie." This isn't $\textbf{really}$ the same as $S$. (2) We can define universal and existential 
+      operators that quantify over DDL formulae to actually represent $S$ as we want to. I am going to 
+      try to implement (2), borrowing from \cite{gewirth}'s extension of Carmo and Jones' DDL. This 
+      will also be useful when creating my own formalization of the categorical imperative. MOVE THIS TO NAIVE%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+abbreviation lying not possibly universal::bool where "lying not possibly universal longleftrightarrow forall w. not (diamond (forall p. lie(p)))w)"%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isamarkupcmt{The formula above reads, "At all worlds, it is not possible%
+}%
+\begin{isamarkuptext}%
+something more sophisticated? like the nazi example?%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+maybe trolley problem/self driving car thing%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsubsection{Metaethical Tests%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+\ \ \isacommand{lemma}\isamarkupfalse%
+\ permissible{\isacharcolon}\isanewline
+\ \ \ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymexists}A{\isachardot}\ {\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
+\ \ \ \ \isacommand{nitpick}\isamarkupfalse%
+\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{\color{blue}Nitpick found a model for card i = 1 and card s = 1:
+
+  Skolem constant:
+    A =($\lambda x. \_$)($i_1$ := False) \color{black}%
+}\isanewline
+%
+\isamarkupcmt{Just as with the naive interpretation, permissibility is possible.%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ fixed{\isacharunderscore}formula{\isacharunderscore}is{\isacharunderscore}permissible{\isacharcolon}\isanewline
+\ \ \isakeyword{fixes}\ A\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{\color{blue}Nitpick found a model for card i = 1:
+
+  Free variable:
+    A = ($\lambda x. \_$)($i_1$ := False)\color{black}%
+}\isanewline
+%
+\isamarkupcmt{This bad result also holds under Kroy's formulation. Recall that we want this to fail - if A is ``murder" 
+then no model should render it permissible.%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ arbitrary{\isacharunderscore}obligations{\isacharcolon}\isanewline
+\ \ \isakeyword{fixes}\ A{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}O\ {\isacharbraceleft}A{\isacharbraceright}\ w{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharequal}true{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+ought implies can%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+arbitrary obligations%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+conflicting obligations%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+obligation and permissible relationship%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsection{Misc%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
+stuff from Kroy's paper%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %:%295=147%:%
-%:%296=148%:%
-%:%298=150%:%
-%:%299=150%:%
-%:%306=153%:%
-%:%318=155%:%
-%:%319=156%:%
-%:%320=157%:%
-%:%321=158%:%
+%:%304=152%:%
+%:%316=154%:%
+%:%317=155%:%
+%:%318=156%:%
+%:%319=157%:%
+%:%320=158%:%
 %:%322=159%:%
-%:%324=161%:%
-%:%325=161%:%
-%:%327=162%:%
-%:%328=163%:%
-%:%329=164%:%
-%:%332=166%:%
-%:%334=168%:%
+%:%323=159%:%
+%:%325=160%:%
+%:%328=162%:%
+%:%329=163%:%
+%:%330=164%:%
+%:%333=166%:%
 %:%335=168%:%
-%:%336=169%:%
-%:%337=170%:%
+%:%336=168%:%
+%:%337=169%:%
 %:%338=170%:%
-%:%340=170%:%
-%:%344=170%:%
+%:%339=170%:%
+%:%341=170%:%
 %:%345=170%:%
-%:%347=171%:%
-%:%348=172%:%
-%:%349=173%:%
-%:%350=174%:%
-%:%351=175%:%
-%:%352=176%:%
-%:%362=178%:%
-%:%364=180%:%
+%:%346=170%:%
+%:%348=171%:%
+%:%349=172%:%
+%:%350=173%:%
+%:%351=174%:%
+%:%352=175%:%
+%:%353=176%:%
+%:%363=178%:%
 %:%365=180%:%
-%:%367=182%:%
-%:%369=184%:%
+%:%366=180%:%
+%:%368=182%:%
 %:%370=184%:%
 %:%371=184%:%
-%:%373=184%:%
-%:%377=184%:%
+%:%372=184%:%
+%:%374=184%:%
 %:%378=184%:%
-%:%380=185%:%
-%:%381=186%:%
-%:%382=187%:%
-%:%383=188%:%
-%:%393=190%:%
-%:%394=191%:%
-%:%395=192%:%
-%:%396=193%:%
+%:%379=184%:%
+%:%381=185%:%
+%:%382=186%:%
+%:%383=187%:%
+%:%384=188%:%
+%:%394=190%:%
+%:%395=191%:%
+%:%396=192%:%
+%:%397=193%:%
+%:%406=197%:%
+%:%418=199%:%
+%:%419=200%:%
+%:%420=201%:%
+%:%422=203%:%
+%:%423=203%:%
+%:%425=204%:%
+%:%426=204%:%
+%:%427=205%:%
+%:%428=206%:%
+%:%429=206%:%
+%:%430=207%:%
+%:%433=208%:%
+%:%437=208%:%
+%:%438=208%:%
+%:%447=210%:%
+%:%448=211%:%
+%:%449=212%:%
+%:%450=213%:%
+%:%451=214%:%
+%:%452=215%:%
+%:%453=216%:%
+%:%454=217%:%
+%:%458=219%:%
+%:%459=220%:%
+%:%461=222%:%
+%:%462=222%:%
+%:%464=223%:%
+%:%465=223%:%
+%:%466=224%:%
+%:%467=225%:%
+%:%468=225%:%
+%:%469=226%:%
+%:%472=227%:%
+%:%476=227%:%
+%:%477=227%:%
+%:%478=228%:%
+%:%479=228%:%
+%:%480=229%:%
+%:%481=229%:%
+%:%482=230%:%
+%:%483=230%:%
+%:%484=230%:%
+%:%485=231%:%
+%:%486=231%:%
+%:%488=232%:%
+%:%489=233%:%
+%:%490=234%:%
+%:%491=235%:%
+%:%492=236%:%
+%:%502=238%:%
+%:%503=239%:%
+%:%504=240%:%
+%:%506=242%:%
+%:%507=242%:%
+%:%508=243%:%
+%:%509=243%:%
+%:%511=244%:%
+%:%512=244%:%
+%:%513=245%:%
+%:%514=246%:%
+%:%515=246%:%
+%:%516=247%:%
+%:%517=248%:%
+%:%518=249%:%
+%:%519=249%:%
+%:%521=249%:%
+%:%525=249%:%
+%:%526=249%:%
+%:%528=250%:%
+%:%529=251%:%
+%:%530=252%:%
+%:%531=253%:%
+%:%532=254%:%
+%:%533=255%:%
+%:%543=257%:%
+%:%544=258%:%
+%:%545=259%:%
+%:%546=260%:%
+%:%547=261%:%
+%:%548=262%:%
+%:%552=264%:%
+%:%553=265%:%
+%:%554=266%:%
+%:%555=267%:%
+%:%556=268%:%
+%:%557=269%:%
+%:%558=270%:%
+%:%559=271%:%
+%:%563=273%:%
+%:%566=274%:%
+%:%569=278%:%
+%:%573=280%:%
+%:%582=282%:%
+%:%592=284%:%
+%:%593=284%:%
+%:%594=285%:%
+%:%595=286%:%
+%:%596=286%:%
+%:%598=286%:%
+%:%602=286%:%
+%:%603=286%:%
+%:%605=287%:%
+%:%606=288%:%
+%:%607=289%:%
+%:%608=290%:%
+%:%609=290%:%
+%:%611=291%:%
+%:%619=291%:%
+%:%620=292%:%
+%:%621=293%:%
+%:%622=293%:%
+%:%623=294%:%
+%:%624=295%:%
+%:%625=296%:%
+%:%626=296%:%
+%:%628=296%:%
+%:%632=296%:%
+%:%633=296%:%
+%:%635=297%:%
+%:%636=298%:%
+%:%637=299%:%
+%:%638=300%:%
+%:%639=300%:%
+%:%641=301%:%
+%:%642=302%:%
+%:%650=302%:%
+%:%651=303%:%
+%:%652=304%:%
+%:%653=304%:%
+%:%654=305%:%
+%:%655=306%:%
+%:%656=307%:%
+%:%657=307%:%
+%:%659=307%:%
+%:%663=307%:%
+%:%673=309%:%
+%:%677=313%:%
+%:%681=315%:%
+%:%685=317%:%
+%:%694=319%:%
+%:%706=321%:%

### 2021-09-13 paper/output/document/paper32.tex
finished application tests for Kroy - next steps are to port learnings to the naive interpretation, and move on to metaethical tests

@@
 \isamarkupcmt{This lemma gets to the heart of Kroy's formulation of the categorical imperative. If murder is prohobited
-for a specific person $p$, then it must be prohobited for all people. This test case also revealed a 
+for a specific person $p$, then it must be prohibited for all people. This test case also revealed a 
 bug in my original implementation of Kroy's formulation of the FUL, demonstrating the power of such 
@@
 \begin{isamarkuptext}%
-We want to represent the sentence, call it $S$ $\longleftrightarrow$ ``At all worlds, it is not possible that everyone lies simultaneously.
-      Representing this sentence requires that we apply a universal quantifier inside the possible operator,
-      something that DDL does not support as-is. There are two options here. (1) We can pull the universal outside
-      the diamond operator, resulting in the sentence ``At all worlds, for all people, it is not possible that 
-      they lie." This isn't $\textbf{really}$ the same as $S$. (2) We can define universal and existential 
-      operators that quantify over DDL formulae to actually represent $S$ as we want to. I am going to 
-      try to implement (2), borrowing from \cite{gewirth}'s extension of Carmo and Jones' DDL. This 
-      will also be useful when creating my own formalization of the categorical imperative. MOVE THIS TO NAIVE%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-abbreviation lying not possibly universal::bool where "lying not possibly universal longleftrightarrow forall w. not (diamond (forall p. lie(p)))w)"%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\isamarkupcmt{The formula above reads, "At all worlds, it is not possible%
-}%
-\begin{isamarkuptext}%
-something more sophisticated? like the nazi example?%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-maybe trolley problem/self driving car thing%
+We want to represent the sentence, call it $S$ $\longleftrightarrow$ ``At all worlds, it is 
+      not possible that everyone lies simultaneously." Consider the two abbreviations below.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{abbreviation}\isamarkupfalse%
+\ everyone{\isacharunderscore}lies{\isacharcolon}{\isacharcolon}t\ \isakeyword{where}\ {\isachardoublequoteopen}everyone{\isacharunderscore}lies\ {\isasymequiv}\ {\isasymlambda}w{\isachardot}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ {\isacharparenleft}lie{\isacharparenleft}p{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{This represents the term ``all people lie". Naively, we might think to represent this as $\forall p. lie(p)$.
+In HOL, the $\forall$ operator has type $('a\rightarrow bool) \rightarrow bool$, where $'a$ is a polymorphic
+type representing the type of the argument to $\forall$. This is because the universal quantifier binds 
+the argument of the term given to it, such that it turns an open term into a closed term. In the given example, 
+$\forall$ has the type $(s \rightarrow bool) \rightarrow bool$, so it can only be applied to a formula 
+of type $s \rightarrow bool$. In the abbreviation above, we're applying the quantifier to the sentence 
+$lie(p) w$ for any arbitrary $w$, so the types cohere.%
+}\isanewline
+%
+\isamarkupcmt{The term above is true for a set of worlds $i$ (recall that a term is true at a set of worlds) 
+such that, at all the worlds $w$ in $i$, all people at $w$ lie.%
+}\isanewline
+\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ lying{\isacharunderscore}not{\isacharunderscore}possibly{\isacharunderscore}universal{\isacharcolon}{\isacharcolon}bool\ \isakeyword{where}\ {\isachardoublequoteopen}lying{\isacharunderscore}not{\isacharunderscore}possibly{\isacharunderscore}universal\ {\isasymequiv}\ {\isasymforall}w{\isachardot}\ {\isasymnot}{\isacharparenleft}{\isasymdiamond}everyone{\isacharunderscore}lies\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Armed with \isa{everyone{\isacharunderscore}lies\ {\isasymequiv}\ {\isasymlambda}w{\isachardot}\ {\isasymforall}p{\isachardot}\ lie\ p\ w}, it's easy to represent the sentence $S$.
+The abbreviation above
+reads, ``At all worlds, it is not possible that everyone lies."%
+}\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ lying{\isacharunderscore}prohibited{\isacharunderscore}{\isadigit{2}}{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}lying{\isacharunderscore}not{\isacharunderscore}possible{\isacharunderscore}universal\ {\isasymlongrightarrow}\ \ {\isasymTurnstile}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}lie{\isacharparenleft}p{\isacharparenright}{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{$\color{blue}$Nitpick found a counterexample for card i = 1 and card s = 2:
+
+  Free variables:
+    $lying\_not\_possible\_universal$ = True
+    p = $s_1$ $\color{black}$%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+Even with the stronger assumption that it's not possible for everyone to lie 
+simultaneously, Kroy's formulation is still not able to show that lying is prohibited for an arbitrary
+person. That's a problem! WHY IS THIS HAPPENING%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %:%553=265%:%
-%:%554=266%:%
 %:%555=267%:%
-%:%556=268%:%
-%:%557=269%:%
-%:%558=270%:%
-%:%559=271%:%
+%:%556=267%:%
+%:%558=268%:%
+%:%559=269%:%
+%:%560=270%:%
+%:%561=271%:%
+%:%562=272%:%
 %:%563=273%:%
-%:%566=274%:%
-%:%569=278%:%
-%:%573=280%:%
-%:%582=282%:%
-%:%592=284%:%
-%:%593=284%:%
-%:%594=285%:%
-%:%595=286%:%
-%:%596=286%:%
-%:%598=286%:%
-%:%602=286%:%
-%:%603=286%:%
-%:%605=287%:%
-%:%606=288%:%
-%:%607=289%:%
-%:%608=290%:%
-%:%609=290%:%
-%:%611=291%:%
-%:%619=291%:%
-%:%620=292%:%
-%:%621=293%:%
-%:%622=293%:%
-%:%623=294%:%
-%:%624=295%:%
-%:%625=296%:%
-%:%626=296%:%
-%:%628=296%:%
-%:%632=296%:%
-%:%633=296%:%
-%:%635=297%:%
-%:%636=298%:%
+%:%564=274%:%
+%:%565=274%:%
+%:%567=275%:%
+%:%568=276%:%
+%:%569=276%:%
+%:%570=277%:%
+%:%571=278%:%
+%:%572=278%:%
+%:%574=279%:%
+%:%575=280%:%
+%:%576=280%:%
+%:%577=281%:%
+%:%578=282%:%
+%:%579=282%:%
+%:%580=283%:%
+%:%581=284%:%
+%:%582=284%:%
+%:%584=284%:%
+%:%588=284%:%
+%:%589=284%:%
+%:%591=285%:%
+%:%592=286%:%
+%:%593=287%:%
+%:%594=288%:%
+%:%595=289%:%
+%:%605=291%:%
+%:%606=292%:%
+%:%607=293%:%
+%:%616=295%:%
+%:%626=297%:%
+%:%627=297%:%
+%:%628=298%:%
+%:%629=299%:%
+%:%630=299%:%
+%:%632=299%:%
+%:%636=299%:%
 %:%637=299%:%
-%:%638=300%:%
 %:%639=300%:%
-%:%641=301%:%
-%:%642=302%:%
-%:%650=302%:%
-%:%651=303%:%
-%:%652=304%:%
+%:%640=301%:%
+%:%641=302%:%
+%:%642=303%:%
+%:%643=303%:%
+%:%645=304%:%
 %:%653=304%:%
@@
 %:%655=306%:%
-%:%656=307%:%
+%:%656=306%:%
 %:%657=307%:%
-%:%659=307%:%
-%:%663=307%:%
-%:%673=309%:%
-%:%677=313%:%
-%:%681=315%:%
-%:%685=317%:%
-%:%694=319%:%
-%:%706=321%:%
+%:%658=308%:%
+%:%659=309%:%
+%:%660=309%:%
+%:%662=309%:%
+%:%666=309%:%
+%:%667=309%:%
+%:%669=310%:%
+%:%670=311%:%
+%:%671=312%:%
+%:%672=313%:%
+%:%673=313%:%
+%:%675=314%:%
+%:%676=315%:%
+%:%684=315%:%
+%:%685=316%:%
+%:%686=317%:%
+%:%687=317%:%
+%:%688=318%:%
+%:%689=319%:%
+%:%690=320%:%
+%:%691=320%:%
+%:%693=320%:%
+%:%697=320%:%
+%:%707=322%:%
+%:%711=326%:%
+%:%715=328%:%
+%:%719=330%:%
+%:%728=332%:%
+%:%740=334%:%

### 2021-09-14 paper/outline.tex
added outline.tex

\usepackage{outlines}
\renewcommand{\outlineii}{cenumerate}
\begin{outline}

\end{outline}

### 2021-09-15 paper/outline.tex
updated outline for will

@@
+\documentclass[11pt]{article}
 \usepackage{outlines}
-\renewcommand{\outlineii}{cenumerate}
-\begin{outline}
+\usepackage{xcolor}
+\usepackage{times}
+\usepackage[margin=1in]{geometry}
+
+\normalfont
+
+\begin{document}
+\begin{outline}[enumerate]
+\1[Note: ] Sections highlighted in \textcolor{blue}{blue} are areas where I envision philosophical points of contact. 
+\1[Chapter 1:] Introduction
+\2 Motivation
+\3 In order for AI agents to navigate the world successfully, they need sophisticated ethical reasoning capacity. 
+\3 Just as interactive theorem provers enable mathematicians to prove new theorems and find holes in old arguments, automated ethics can help philosophers better study ethics.
+\2 System components/methods \color{blue}
+\3 \textbf{Kantian ethics} \color{black} I choose to automate Kantian ethics, which presents three equivalent ``formulations" (equality-based, dignity-based, respect-based) of the unviolable rule of morality.
+I will offer a brief introduction to Kantian ethics and explain why I choose to formalize Kantian ethics instead of utilitarianism or virtue ethics.
+Readings: \begin{itemize}
+    \item Should I cite introductory texts (the Groundwork, Bentham, Mill, Aristotle) here as a crash course on each theory?
+Prof.
+Amin (CS advisor) recommended putting a literature review at the end of the thesis, so I've included formalization attempts for each theory there.
+\end{itemize} \color{black}
+\3 \textbf{Logical background} I use Carmo and Jones' Dyadic Deontic Logic. I will explain modal logic, deontic logic, and Carmo and Jones' DDL to a logical beginner. 
+\3 \textbf{Isabelle/HOL} I will explain the choice of Isabelle/HOL and demonstrate basic syntax and proof capabilities through my recreation of Benzmüller, Farjami, and Parent's \cite{BFP} implementation of Carmo and Jones's DDL.
+\3 \textbf{Contributions} I contribute (1) an implementation of a naive formalization of the categorical imperative, (2) an implementation of Kroy's formalization of the categorical imperative, (3) an implementation of my own formalization that addresses gaps in (1) and (2), (4) a testing architecture for evaluating an ethical formalization, (5) examples and methods for applying my implementations to real-world ethical dilemmas, (6) implementation and analysis of Kant's argument that the three formulations of the categorical imperative are equal.
+
+\1[Chapter 2:] Testing Previous Theories
+\2 Explaining and justifying my testing approach
+\3 \textcolor{blue}{\textbf{Metaethical/logical tests}} These tests are proofs of theorems or demonstration of a sentence's consistency or inconsistency.
+They test metaethical properties of the formalization, like ``does the formalization allow contradictory obligations?" Readings:
+\begin{enumerate}
+    \item Timmermann's ``Kantian Dilemmas? Moral Conflict in Kant’s Ethical Theory"  \cite{contradictoryob} examines the possibility of contradictory obligations in Kant's theory.
+    \item Kohl's ``Kant and `Ought Implies Can'" \cite{kohl} explores the ought implies can principle.
+    \item Are there other readings that might be interesting here? Specifically, I'm looking for metaethical properties of Kant's theory.
+\end{enumerate}
+\3 \textcolor{blue}{\textbf{Model specification tests}} These tests specify a model to encode specific background facts into the system.
+They demonstrate how the system can be used to reason about real world ethical dilemmas.
+\begin{enumerate}
+    \item This section focuses on easy, simple examples like lying and murder. If there are other examples that get at the heart of the categorical imperative, that would be helpful here.
+\end{enumerate}
+
+\color{black}
+\3 \textbf{Testing the naive formalization} I will apply the testing approach above to a naive formalization of the categorical imperative and document the lessons learned, which will inform my eventual formulation in Chapter 3.
+\3 \textbf{Testing Kroy's Formulation} These sections apply the testing approach above to the two formalizations that Kroy presents \cite{kroy}, of the FUL and the FUH respectively.
+I will also include miscellaneous tests specific to Kroy's logic and arguments.
+I will document lessons learned and use them to inform my eventual formulation in Chapter 3.
+
+\1[Chapter 3:] New Formalization
+\2 \textbf{Goals} I will set explicit goals for my formalization based on the lessons learned above.
+\2 \textcolor{blue}{\textbf{Formalization}} I will present the logical components of my formalization, which may include a representation of agency, maxims, and willing; additional background axioms about the meaning of "obligated" or "prohibited," and axioms representing the categorical imperative itself.
+Readings:
+\begin{enumerate}
+    \item Korsgaard's ``Kant's Formula of Universal Law," \cite{KorsgaardFUL} explores three interpretations of the FUL and argues in favor of one.
+    \item Hill's ``Dignity and Practical Reason in Kant’s Moral Theory" \cite{hill_2019} picks apart the Groundwork and makes the formulations precise.
+    \item Do you have recommendations for readings that make formulations of the categorical imperative precise? Or common debates in the literature?
+\end{enumerate}
+\2 \textbf{Evaluation} I will apply the tests outlined in Chapter 2 to my new formalization, as well as any additional tests that may be formalization specific.
+The actual research process will be very iterative here - I will implement a formalization, apply the tests, and modify my formalization accordingly.
+Middle iterations may not make it into the thesis itself.
+
+\1[Chapter 4:] Equivalence of the Three Formulations
+\2 \textcolor{blue}{\textbf{Kant's argument}} I will briefly present Kant's argument for the equivalence of the three formulations of the categorical imperative.
+It is well known to be difficult and complex, so presenting it concisely to a non-philosophical audience will be a challenge.
+Readings:
+\begin{enumerate}
+    \item Kitcher's ``Kant's Argument for the Categorical Imperative" \cite{kitcher} examines Kant's argument in depth. 
+    \item Allison's \emph{Kant’s Groundwork for the Metaphysics of Morals: A Commentary} \cite{allison} argues that all three formulations result in the same duties.
+    \item O'Neill's \emph{Acting on Principle} \cite{o'neill_2013}, Engstrom's \emph{The Form of Practical Knowledge} \cite{engstrom}, and Sensen's ``Kant’s Constructivism" \cite{sensen} argue that FUH implies FUL.
+    \item Wood's \emph{Kantian Ethics} \cite{wood_2007} and Cureton's ``A Contractualist Reading of Kant’s Proof of the Formula of Humanity" \cite{cureton_2013} disagree with the above.
+    \item Are there common debates within the literature on the content or correctness of Kant's argument?
+\end{enumerate}
+\2 \textbf{Logical argument for equivalence} I will attempt to recreate Kant's proof of the equivalence of the three formulations.
+This attempt may fail!
+There may be room to repeat this analysis with the naive formalization and Kroy's formalization.
+\2 \textcolor{blue}{\textbf{Philosophical analysis of results}} I will analyze my success or failure and whether it demonstrates a problem with my system or a problem with Kant's.
+The readings from (a) will inform this analysis.
+
+\1[Chapter 5:] Applications
+\2 \textbf{Specifying a model} I will briefly explain some challenges in specifying a model that have been presented before such as how much background information to include and how to encode this background information.
+
+\2 \textcolor{blue}{\textbf{Example dilemmas}} I will present examples of ethical dilemmas that the system can handle.
+Readings: Kemp's ``Kant's Examples of the Categorical Imperative" presents some of the canonical applications of the categorical imperative.
+\3 \textcolor{blue}{\textbf{Evaluation}} This section will analyze the philosophical implications of the applications presented above to determine if the system is performing ethical reasoning in any meaningful sense.
+Three facets of this question:
+\4 How much background knowledge does the reasoner need to reach the expected conclusions?
+How much background knowledge is just giving away the answer?
+Readings: O'Neill's \emph{Constructions of Reason} \cite{constofreason}, Silber's ``Procedural Formalism in Kant’s Ethics" \cite{silber}, and Rawls' ``Kantian Constructivism in Moral Theory" \cite{rawlsconstructivism}.
+\4 Even a computer reaches the same conclusions as a person, is it actually acting morally?
+Is it capable of practical reason?
+Is it capable of giving laws to itself?\footnote{My hypothesis is that the answer to this is a quick no, at least for the system I'm building.
+Might not be worth investing a ton of time here, since the result falls out almost immediately.} Readings include: Korsgaard's \emph{Sources of Normativity} \cite{sources} presents her view of practical reason.
+Bok's \emph{Freedom and Responsibility} \cite{bok} examines the notion of a ``pocket oracle" to distinguish between an oracle (or machine) and a human reasoner.
+\4 Can a computer perform synthetic a priori reasoning?
+I would appreciate reading recommendations here.
+Readings: Benardete's ``AI and the Synthetic A Priori" \cite{benardete} and Hintikka's ``Are Mathematical Truths Synthetic a Priori?" \cite{hintikkaapriori}.
+
+\1[Chapter 6] Discussion
+\2 \textcolor{blue}{\textbf{Related Work}} I will present a brief literature review. Readings:
+\begin{enumerate}
+    \item Attempts to formalize consequentialism include: Abel et.
+al's ``Reinforcement Learning as a Framework for Ethical Decision Making" \cite{util1} and Anderson et.
+al's ``Towards Machine Ethics." \cite{util2}.
+     \item Attempts to formalize deontological theories include: Govindarajulu's ``On Automating the Doctrine of Double Effect," \cite{dde}, Anderson et.
+al's ``ETHEL: Toward a Principled Ethical Eldercare Robot," \cite{deon1}, and Anderson et.
+al's ``GenEth: A General Ethical Dilemma Analyzer." \cite{deon2}.
+    \item Attempts to formalize virtue ethics include: Berberich and Diepold's ``The Virtuous Machine - Old Ethics for New Technology?" \cite{virtue2} and Govindarajulu et.
+al's ``Toward the Engineering of Virtuous Machines" \cite{virtue1}.
+\end{enumerate}
+\2 \textcolor{blue}{\textbf{Conclusions}} I will discuss my findings in Ch. 2-5. Questions that might be interesting here:
+\3 How exactly can automated ethics be used in AI systems? Can it be a black box? Is it possible to make an API for ethics?
+\3 How much common sense reasoning do automated ethical reasoners need? 
+\3 What is the power of automated ethics, in a nutshell?
+\2 \textbf{Future Work} I will presents doors that my approach opens, other ethical theories that may be exciting candidates for formalization, what is left to do to make the implementation usable, and alternative logics beyond DDL.
 
 \end{outline}
+\bibliographystyle{plain}
+\bibliography{document/root.bib}
+\end{document}

### 2021-09-16 paper/output/document/paper31.tex
finished kroy FUL tests

@@
 %
-\isamarkupsection{The Categorical Imperative%
+\isamarkupsection{Prior Formalizations of The Categorical Imperative%
 }
@@
 %
-\isamarkupsubsection{Naive Formulation of the Formula of Universal Law \label{sec:naive}%
+\isamarkupsubsection{Naive Formalization of the Formula of Universal Law \label{sec:naive}%
 }
@@
 test creates negative obligations: if a maxim passes the universalizability test, it is permissible. Else,
-it is prohibited. In order to appropriately formalize this, we need some notion of permissibility.%
+it is prohibited.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsubsection{Formalization \label{sec:naive_form}%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
+In order to appropriately formalize the categorical imperative, we to define the notion of permissibility.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %:%64=20%:%
-%:%66=22%:%
-%:%67=22%:%
-%:%68=23%:%
-%:%70=24%:%
-%:%71=25%:%
-%:%74=27%:%
-%:%75=28%:%
-%:%76=29%:%
-%:%77=30%:%
-%:%78=31%:%
-%:%79=32%:%
-%:%80=33%:%
-%:%81=34%:%
-%:%83=36%:%
-%:%84=36%:%
-%:%85=37%:%
-%:%87=39%:%
-%:%88=40%:%
-%:%89=41%:%
-%:%90=42%:%
-%:%91=43%:%
-%:%92=44%:%
-%:%93=45%:%
-%:%94=46%:%
-%:%95=47%:%
-%:%96=48%:%
-%:%97=49%:%
-%:%98=50%:%
-%:%100=53%:%
-%:%101=53%:%
-%:%102=53%:%
-%:%104=53%:%
-%:%108=53%:%
-%:%109=53%:%
-%:%111=54%:%
-%:%112=55%:%
-%:%113=56%:%
-%:%114=56%:%
-%:%116=57%:%
-%:%117=58%:%
-%:%118=59%:%
-%:%119=59%:%
-%:%186=105%:%
-%:%198=107%:%
-%:%199=108%:%
-%:%200=109%:%
-%:%201=110%:%
-%:%203=112%:%
-%:%204=112%:%
-%:%205=113%:%
-%:%206=113%:%
-%:%218=121%:%
-%:%221=122%:%
-%:%222=122%:%
-%:%224=123%:%
-%:%225=124%:%
-%:%226=125%:%
-%:%227=126%:%
-%:%228=126%:%
-%:%229=127%:%
-%:%230=128%:%
-%:%231=128%:%
-%:%232=129%:%
-%:%235=130%:%
-%:%239=130%:%
-%:%240=130%:%
-%:%242=131%:%
-%:%243=132%:%
-%:%253=134%:%
-%:%254=135%:%
-%:%255=136%:%
-%:%259=138%:%
-%:%261=140%:%
-%:%262=140%:%
-%:%263=141%:%
-%:%264=141%:%
-%:%265=142%:%
-%:%266=142%:%
-%:%268=143%:%
-%:%269=143%:%
-%:%270=144%:%
-%:%271=145%:%
-%:%272=145%:%
-%:%274=147%:%
-%:%275=148%:%
-%:%276=149%:%
-%:%277=150%:%
-%:%279=152%:%
-%:%280=152%:%
-%:%281=153%:%
-%:%282=154%:%
-%:%283=155%:%
-%:%284=155%:%
-%:%287=156%:%
-%:%291=156%:%
-%:%292=156%:%
-%:%294=157%:%
-%:%295=158%:%
-%:%296=159%:%
-%:%297=160%:%
-%:%298=160%:%
-%:%300=161%:%
-%:%301=162%:%
-%:%302=163%:%
-%:%303=164%:%
-%:%304=165%:%
-%:%305=165%:%
-%:%307=166%:%
-%:%308=167%:%
-%:%318=169%:%
-%:%319=170%:%
-%:%320=171%:%
-%:%321=172%:%
-%:%322=173%:%
-%:%323=174%:%
-%:%324=175%:%
-%:%325=176%:%
-%:%327=178%:%
-%:%328=178%:%
-%:%329=179%:%
-%:%330=180%:%
-%:%331=181%:%
-%:%332=181%:%
-%:%334=181%:%
-%:%338=181%:%
-%:%339=181%:%
-%:%341=182%:%
-%:%342=183%:%
-%:%343=184%:%
-%:%344=185%:%
-%:%345=186%:%
-%:%346=187%:%
-%:%356=189%:%
-%:%357=190%:%
-%:%358=191%:%
-%:%359=192%:%
-%:%360=193%:%
-%:%361=194%:%
-%:%370=196%:%
+%:%73=22%:%
+%:%85=24%:%
+%:%87=26%:%
+%:%88=26%:%
+%:%89=27%:%
+%:%91=28%:%
+%:%92=29%:%
+%:%95=31%:%
+%:%96=32%:%
+%:%97=33%:%
+%:%98=34%:%
+%:%99=35%:%
+%:%100=36%:%
+%:%101=37%:%
+%:%102=38%:%
+%:%104=40%:%
+%:%105=40%:%
+%:%106=41%:%
+%:%108=43%:%
+%:%109=44%:%
+%:%110=45%:%
+%:%111=46%:%
+%:%112=47%:%
+%:%113=48%:%
+%:%114=49%:%
+%:%115=50%:%
+%:%116=51%:%
+%:%117=52%:%
+%:%118=53%:%
+%:%119=54%:%
+%:%121=57%:%
+%:%122=57%:%
+%:%123=57%:%
+%:%125=57%:%
+%:%129=57%:%
+%:%130=57%:%
+%:%132=58%:%
+%:%133=59%:%
+%:%134=60%:%
+%:%135=60%:%
+%:%137=61%:%
+%:%138=62%:%
+%:%139=63%:%
+%:%140=63%:%
+%:%207=109%:%
+%:%219=111%:%
+%:%220=112%:%
+%:%221=113%:%
+%:%222=114%:%
+%:%224=116%:%
+%:%225=116%:%
+%:%226=117%:%
+%:%227=117%:%
+%:%239=125%:%
+%:%242=126%:%
+%:%243=126%:%
+%:%245=127%:%
+%:%246=128%:%
+%:%247=129%:%
+%:%248=130%:%
+%:%249=130%:%
+%:%250=131%:%
+%:%251=132%:%
+%:%252=132%:%
+%:%253=133%:%
+%:%256=134%:%
+%:%260=134%:%
+%:%261=134%:%
+%:%263=135%:%
+%:%264=136%:%
+%:%274=138%:%
+%:%275=139%:%
+%:%276=140%:%
+%:%280=142%:%
+%:%282=144%:%
+%:%283=144%:%
+%:%284=145%:%
+%:%285=145%:%
+%:%286=146%:%
+%:%287=146%:%
+%:%289=147%:%
+%:%290=147%:%
+%:%291=148%:%
+%:%292=149%:%
+%:%293=149%:%
+%:%295=151%:%
+%:%296=152%:%
+%:%297=153%:%
+%:%298=154%:%
+%:%300=156%:%
+%:%301=156%:%
+%:%302=157%:%
+%:%303=158%:%
+%:%304=159%:%
+%:%305=159%:%
+%:%308=160%:%
+%:%312=160%:%
+%:%313=160%:%
+%:%315=161%:%
+%:%316=162%:%
+%:%317=163%:%
+%:%318=164%:%
+%:%319=164%:%
+%:%321=165%:%
+%:%322=166%:%
+%:%323=167%:%
+%:%324=168%:%
+%:%325=169%:%
+%:%326=169%:%
+%:%328=170%:%
+%:%329=171%:%
+%:%339=173%:%
+%:%340=174%:%
+%:%341=175%:%
+%:%342=176%:%
+%:%343=177%:%
+%:%344=178%:%
+%:%345=179%:%
+%:%346=180%:%
+%:%348=182%:%
+%:%349=182%:%
+%:%350=183%:%
+%:%351=184%:%
+%:%352=185%:%
+%:%353=185%:%
+%:%355=185%:%
+%:%359=185%:%
+%:%360=185%:%
+%:%362=186%:%
+%:%363=187%:%
+%:%364=188%:%
+%:%365=189%:%
+%:%366=190%:%
+%:%367=191%:%
+%:%377=193%:%
+%:%378=194%:%
+%:%379=195%:%
+%:%380=196%:%
+%:%381=197%:%
 %:%382=198%:%
-%:%383=199%:%
-%:%384=200%:%
-%:%385=201%:%
-%:%386=202%:%
-%:%387=203%:%
-%:%388=204%:%
-%:%389=205%:%
-%:%390=206%:%
-%:%391=207%:%
-%:%392=208%:%
-%:%393=209%:%
-%:%395=210%:%
-%:%396=210%:%
-%:%397=211%:%
-%:%398=212%:%
-%:%399=212%:%
-%:%401=212%:%
-%:%405=212%:%
-%:%406=212%:%
-%:%408=213%:%
-%:%409=214%:%
-%:%410=215%:%
-%:%411=216%:%
-%:%412=216%:%
-%:%414=217%:%
-%:%415=218%:%
-%:%416=219%:%
-%:%417=219%:%
-%:%419=220%:%
-%:%420=221%:%
-%:%428=221%:%
-%:%429=222%:%
-%:%430=223%:%
-%:%431=223%:%
-%:%432=224%:%
-%:%433=225%:%
-%:%434=226%:%
-%:%435=226%:%
-%:%437=226%:%
-%:%441=226%:%
-%:%442=226%:%
-%:%444=227%:%
-%:%445=228%:%
-%:%446=229%:%
-%:%447=230%:%
-%:%448=230%:%
-%:%450=231%:%
-%:%451=232%:%
-%:%452=233%:%
-%:%462=235%:%
-%:%463=236%:%
-%:%465=238%:%
-%:%466=238%:%
-%:%467=239%:%
-%:%468=240%:%
-%:%469=241%:%
-%:%470=241%:%
-%:%472=241%:%
-%:%476=241%:%
-%:%477=241%:%
-%:%479=242%:%
-%:%480=243%:%
-%:%481=244%:%
-%:%482=245%:%
-%:%483=245%:%
-%:%485=246%:%
-%:%495=248%:%
-%:%499=250%:%
-%:%500=251%:%
-%:%501=252%:%
-%:%502=253%:%
-%:%504=255%:%
-%:%505=255%:%
-%:%506=256%:%
-%:%507=257%:%
-%:%508=258%:%
-%:%509=258%:%
-%:%511=258%:%
-%:%515=258%:%
-%:%516=258%:%
-%:%518=259%:%
-%:%519=260%:%
-%:%520=261%:%
-%:%521=262%:%
-%:%522=262%:%
-%:%524=263%:%
-%:%534=265%:%
-%:%535=266%:%
-%:%536=267%:%
-%:%538=269%:%
-%:%539=269%:%
-%:%540=270%:%
-%:%541=271%:%
-%:%542=272%:%
-%:%543=272%:%
-%:%545=272%:%
-%:%549=272%:%
-%:%550=272%:%
-%:%552=273%:%
-%:%553=274%:%
-%:%554=275%:%
-%:%555=275%:%
-%:%557=276%:%
-%:%567=278%:%
-%:%568=279%:%
-%:%569=280%:%
-%:%571=282%:%
-%:%572=282%:%
-%:%573=283%:%
-%:%574=284%:%
-%:%575=285%:%
-%:%576=286%:%
-%:%577=287%:%
-%:%578=287%:%
-%:%585=288%:%
-%:%586=288%:%
-%:%587=289%:%
-%:%588=289%:%
-%:%589=290%:%
-%:%590=290%:%
-%:%591=291%:%
-%:%592=291%:%
-%:%593=291%:%
-%:%594=291%:%
-%:%596=292%:%
-%:%597=293%:%
-%:%598=293%:%
-%:%599=294%:%
-%:%600=294%:%
-%:%601=294%:%
-%:%603=295%:%
-%:%604=296%:%
-%:%605=297%:%
-%:%606=298%:%
-%:%607=299%:%
-%:%608=299%:%
-%:%610=300%:%
-%:%620=302%:%
-%:%621=303%:%
-%:%622=304%:%
-%:%623=305%:%
-%:%624=306%:%
-%:%626=308%:%
-%:%627=308%:%
-%:%628=309%:%
-%:%629=310%:%
-%:%630=311%:%
-%:%631=311%:%
-%:%633=311%:%
-%:%637=311%:%
-%:%638=311%:%
-%:%640=312%:%
-%:%641=313%:%
-%:%642=314%:%
-%:%643=315%:%
-%:%644=316%:%
-%:%654=318%:%
-%:%655=319%:%
-%:%659=321%:%
-%:%663=323%:%
-%:%664=324%:%
-%:%665=325%:%
-%:%667=327%:%
-%:%668=327%:%
-%:%669=328%:%
-%:%672=329%:%
-%:%676=329%:%
-%:%677=329%:%
-%:%679=330%:%
-%:%680=330%:%
-%:%682=331%:%
-%:%683=332%:%
-%:%684=333%:%
-%:%685=334%:%
-%:%686=335%:%
-%:%696=337%:%
-%:%697=338%:%
-%:%698=339%:%
-%:%699=340%:%
-%:%701=342%:%
-%:%702=342%:%
-%:%703=343%:%
-%:%706=344%:%
-%:%710=344%:%
-%:%711=344%:%
-%:%712=344%:%
-%:%714=345%:%
-%:%715=345%:%
+%:%391=200%:%
+%:%403=202%:%
+%:%404=203%:%
+%:%405=204%:%
+%:%406=205%:%
+%:%407=206%:%
+%:%408=207%:%
+%:%409=208%:%
+%:%410=209%:%
+%:%411=210%:%
+%:%412=211%:%
+%:%413=212%:%
+%:%414=213%:%
+%:%416=214%:%
+%:%417=214%:%
+%:%418=215%:%
+%:%419=216%:%
+%:%420=216%:%
+%:%422=216%:%
+%:%426=216%:%
+%:%427=216%:%
+%:%429=217%:%
+%:%430=218%:%
+%:%431=219%:%
+%:%432=220%:%
+%:%433=220%:%
+%:%435=221%:%
+%:%436=222%:%
+%:%437=223%:%
+%:%438=223%:%
+%:%440=224%:%
+%:%441=225%:%
+%:%449=225%:%
+%:%450=226%:%
+%:%451=227%:%
+%:%452=227%:%
+%:%453=228%:%
+%:%454=229%:%
+%:%455=230%:%
+%:%456=230%:%
+%:%458=230%:%
+%:%462=230%:%
+%:%463=230%:%
+%:%465=231%:%
+%:%466=232%:%
+%:%467=233%:%
+%:%468=234%:%
+%:%469=234%:%
+%:%471=235%:%
+%:%472=236%:%
+%:%473=237%:%
+%:%483=239%:%
+%:%484=240%:%
+%:%486=242%:%
+%:%487=242%:%
+%:%488=243%:%
+%:%489=244%:%
+%:%490=245%:%
+%:%491=245%:%
+%:%493=245%:%
+%:%497=245%:%
+%:%498=245%:%
+%:%500=246%:%
+%:%501=247%:%
+%:%502=248%:%
+%:%503=249%:%
+%:%504=249%:%
+%:%506=250%:%
+%:%516=252%:%
+%:%520=254%:%
+%:%521=255%:%
+%:%522=256%:%
+%:%523=257%:%
+%:%525=259%:%
+%:%526=259%:%
+%:%527=260%:%
+%:%528=261%:%
+%:%529=262%:%
+%:%530=262%:%
+%:%532=262%:%
+%:%536=262%:%
+%:%537=262%:%
+%:%539=263%:%
+%:%540=264%:%
+%:%541=265%:%
+%:%542=266%:%
+%:%543=266%:%
+%:%545=267%:%
+%:%555=269%:%
+%:%556=270%:%
+%:%557=271%:%
+%:%559=273%:%
+%:%560=273%:%
+%:%561=274%:%
+%:%562=275%:%
+%:%563=276%:%
+%:%564=276%:%
+%:%566=276%:%
+%:%570=276%:%
+%:%571=276%:%
+%:%573=277%:%
+%:%574=278%:%
+%:%575=279%:%
+%:%576=279%:%
+%:%578=280%:%
+%:%588=282%:%
+%:%589=283%:%
+%:%590=284%:%
+%:%592=286%:%
+%:%593=286%:%
+%:%594=287%:%
+%:%595=288%:%
+%:%596=289%:%
+%:%597=290%:%
+%:%598=291%:%
+%:%599=291%:%
+%:%606=292%:%
+%:%607=292%:%
+%:%608=293%:%
+%:%609=293%:%
+%:%610=294%:%
+%:%611=294%:%
+%:%612=295%:%
+%:%613=295%:%
+%:%614=295%:%
+%:%615=295%:%
+%:%617=296%:%
+%:%618=297%:%
+%:%619=297%:%
+%:%620=298%:%
+%:%621=298%:%
+%:%622=298%:%
+%:%624=299%:%
+%:%625=300%:%
+%:%626=301%:%
+%:%627=302%:%
+%:%628=303%:%
+%:%629=303%:%
+%:%631=304%:%
+%:%641=306%:%
+%:%642=307%:%
+%:%643=308%:%
+%:%644=309%:%
+%:%645=310%:%
+%:%647=312%:%
+%:%648=312%:%
+%:%649=313%:%
+%:%650=314%:%
+%:%651=315%:%
+%:%652=315%:%
+%:%654=315%:%
+%:%658=315%:%
+%:%659=315%:%
+%:%661=316%:%
+%:%662=317%:%
+%:%663=318%:%
+%:%664=319%:%
+%:%665=320%:%
+%:%675=322%:%
+%:%676=323%:%
+%:%680=325%:%
+%:%684=327%:%
+%:%685=328%:%
+%:%686=329%:%
+%:%688=331%:%
+%:%689=331%:%
+%:%690=332%:%
+%:%693=333%:%
+%:%697=333%:%
+%:%698=333%:%
+%:%700=334%:%
+%:%701=334%:%
+%:%703=335%:%
+%:%704=336%:%
+%:%705=337%:%
+%:%706=338%:%
+%:%707=339%:%
+%:%717=341%:%
+%:%718=342%:%
+%:%719=343%:%
+%:%720=344%:%
+%:%722=346%:%
+%:%723=346%:%
+%:%724=347%:%
+%:%727=348%:%
+%:%731=348%:%
+%:%732=348%:%
+%:%733=348%:%
+%:%735=349%:%
+%:%736=349%:%

### 2021-09-16 paper/output/document/paper32.tex
finished kroy FUL tests

@@
 \end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ contradictory{\isacharunderscore}obs{\isacharcolon}\isanewline
+\ \ \isakeyword{fixes}\ A\ B\ w\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}A\ \isactrlbold {\isasymand}\ B{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}A\ \isactrlbold {\isasymand}\ B{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{Contradictory things can't be obligated in Kr, since a contradiction can't be true at any deontic alternative.
+This doesn't hold in DDL, and we already saw this cause problems for the naive formalization. We should 
+expect those problems to hold in our implementation of Kr, but this difference suggests that they are 
+a symptom of DDL, not of any inherent problem with Kroy's formalization.%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
 %
@@
 \endisadelimdocument
+%
+\textbf{Murder}
 %
@@
 %
+\textbf{Lying}
+%
 \begin{isamarkuptext}%
@@
 \isacommand{consts}\isamarkupfalse%
-\ lie{\isacharcolon}{\isacharcolon}os\ \isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ lying{\isacharunderscore}not{\isacharunderscore}universal{\isacharcolon}{\isacharcolon}bool\ \isakeyword{where}\ {\isachardoublequoteopen}lying{\isacharunderscore}not{\isacharunderscore}universal\ {\isasymequiv}\ {\isasymforall}w{\isachardot}\ {\isasymnot}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ lie{\isacharparenleft}p{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
-%
-\isamarkupcmt{The formula above reads, ``At all worlds, it is not the case that everyone lies."%
-}\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ lying{\isacharunderscore}prohibited{\isacharcolon}\isanewline
-\ \ \isakeyword{fixes}\ p\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}\ lying{\isacharunderscore}not{\isacharunderscore}universal\ {\isasymlongrightarrow}\ {\isasymTurnstile}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}lie{\isacharparenleft}p{\isacharparenright}{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-\ \ \isacommand{nitpick}\isamarkupfalse%
-{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{oops}\isamarkupfalse%
-\isanewline
-%
-\isamarkupcmt{$\color{blue}$Nitpick found a counterexample for card i = 1 and card s = 1:
-
-  Free variable:
-    p = $s_1$
-  Skolem constant:
-    $\lambda$w. p = ($\lambda$x. $\_$)($i_1$ := $s_1$) $\color{black}$%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-Kroy's formulation also fails to show that if not everyone can lie, then lying is prohibited. 
-      There may be an issue here with our representation of lying not being universal. Specifically, 
-      the FUL is violated if it's not $possible$ for everyone to simultaneously lie, but the abbreviation 
-      above merely represents that fact that not everyone does, in fact, simultaneously lie. It's entirely
-      possible that everyone can simultaneously lie, but for some reason, maybe out of some moral sense, 
-      do not. Let's test a more accurate version of the failure of the universalizability test.%
-\end{isamarkuptext}\isamarkuptrue%
+\ lie{\isacharcolon}{\isacharcolon}os%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
 %
@@
 In HOL, the $\forall$ operator has type $('a\rightarrow bool) \rightarrow bool$, where $'a$ is a polymorphic
-type representing the type of the argument to $\forall$. This is because the universal quantifier binds 
-the argument of the term given to it, such that it turns an open term into a closed term. In the given example, 
+type of the term being bound by $\forall$. In the given example, 
 $\forall$ has the type $(s \rightarrow bool) \rightarrow bool$, so it can only be applied to a formula 
-of type $s \rightarrow bool$. In the abbreviation above, we're applying the quantifier to the sentence 
-$lie(p) w$ for any arbitrary $w$, so the types cohere.%
+of type $s \rightarrow bool$. In the abbreviation above, we're applying the quantifier to a sentence 
+that takes in a given subject $p$ and returns $lie(p) w$ for any arbitrary $w$, so the types cohere.%
 }\isanewline
@@
 \isacommand{abbreviation}\isamarkupfalse%
-\ lying{\isacharunderscore}not{\isacharunderscore}possibly{\isacharunderscore}universal{\isacharcolon}{\isacharcolon}bool\ \isakeyword{where}\ {\isachardoublequoteopen}lying{\isacharunderscore}not{\isacharunderscore}possibly{\isacharunderscore}universal\ {\isasymequiv}\ {\isasymforall}w{\isachardot}\ {\isasymnot}{\isacharparenleft}{\isasymdiamond}everyone{\isacharunderscore}lies\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ lying{\isacharunderscore}not{\isacharunderscore}possibly{\isacharunderscore}universal{\isacharcolon}{\isacharcolon}bool\ \isakeyword{where}\ {\isachardoublequoteopen}lying{\isacharunderscore}not{\isacharunderscore}possibly{\isacharunderscore}universal\ {\isasymequiv}\ {\isasymTurnstile}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}{\isasymdiamond}\ everyone{\isacharunderscore}lies{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
 %
@@
 \isacommand{lemma}\isamarkupfalse%
-\ lying{\isacharunderscore}prohibited{\isacharunderscore}{\isadigit{2}}{\isacharcolon}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}lying{\isacharunderscore}not{\isacharunderscore}possible{\isacharunderscore}universal\ {\isasymlongrightarrow}\ \ {\isasymTurnstile}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}lie{\isacharparenleft}p{\isacharparenright}{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ lying{\isacharunderscore}prohibited{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}lying{\isacharunderscore}not{\isacharunderscore}possibly{\isacharunderscore}universal\ {\isasymlongrightarrow}\ \ {\isacharparenleft}\ {\isasymTurnstile}{\isacharparenleft}\isactrlbold {\isasymnot}\ P\ {\isacharbraceleft}lie{\isacharparenleft}p{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
 \ \ \isacommand{nitpick}\isamarkupfalse%
@@
   Free variables:
-    $lying\_not\_possible\_universal$ = True
+
+    $lying\_not\_possible_universal$ = True
+
     p = $s_1$ $\color{black}$%
@@
     simultaneously, Kroy's formulation is still not able to show that lying is prohibited for an arbitrary
-person. That's a problem! WHY IS THIS HAPPENING%
+    person. That is not good. Let's investigate why this is happening.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+Let's outline the syllogism that we $\emph{expect}$ to prove that lying is prohibited.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{enumerate}
+        \item At all worlds, it's not possible for everyone to lie. (This is the assumed lemma lying\_not\_possible\_universal)
+        \item At all worlds, there is necessarily someone who doesn't lie. (Modal dual of (1))
+        \item If A is permissible for subject p at world w, A is possible for subject p at world w. (Ought Implies Can)
+        \item If A is permissible at world w for any person p, it must be possible for everyone to A at w. (FUL and (3)) 
+        \item Lying is impermissible. (Follows from (4) and (1)) \end{enumerate}
+%
+\begin{isamarkuptext}%
+Armed with this syllogism, we can figure out which step fails.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ step{\isadigit{2}}{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}lying{\isacharunderscore}not{\isacharunderscore}possibly{\isacharunderscore}universal\ {\isasymlongrightarrow}\ {\isasymTurnstile}{\isacharparenleft}\ {\isacharparenleft}{\isasymbox}\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymexists}p{\isachardot}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}lie{\isacharparenleft}p{\isacharparenright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharparenright}\ {\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{by}\isamarkupfalse%
+\ simp\isanewline
+%
+\isamarkupcmt{Step 2 holds!%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+\isanewline
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ step{\isadigit{3}}{\isacharcolon}\ \isanewline
+\ \ \isakeyword{fixes}\ A\ p\ w\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}P\ {\isacharbraceleft}A{\isacharparenleft}p{\isacharparenright}{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharparenleft}A{\isacharparenleft}p{\isacharparenright}{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{$\color{blue}$Nitpick found a counterexample for card `a = 1, card i = 1, and card s = 1:
+
+  Free variables:
+    A = ($\lambda x. \_$)($a_1$ := ($\lambda x. \_$)($i_1$ := False))
+    p = $a_1$ $\color{black}$%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+As we see above, the syllogism fails at Step 3, explaining why the lemma doesn't 
+        hold as expected. Taking a step back, it's not clear that Step 3 should hold. After all,
+        impossible actions can be permissible (look for citation). Imagine I make a trip to Target to 
+        purchase a folder, and they offer blue and black folders. No one could claim that it's impermissible
+        for me to purchase a red folder, or, equivalently, that I am obligated to not purchase a red folder.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+(This is some actual philosophy - maybe worth fleshing this out and giving it a separate subsection?)
+        Another core issue here is Kroy's interpretation of the formula of universal law. In @cite{korsgaardFUL}, 
+        Korsgaard defends a practical contradiction interpretation of the categorical imperative, whereby 
+        a maxim is prohibited if, when universalized, it defeats itself (Korsgaard 3). In other words, if universalizing
+        the maxim renders the maxim ineffective at achieving its stated objective, the maxim fails the
+        universalizability test.
+
+        This example shows that Kroy, on the other hand, is operating under a very different, circular view of 
+        the formula of universal law. He interprets the FUL as prohibiting A if it is not simultaneously 
+        permissible for everyone to A. This is empty—the categorical imperative is supposed to be a complete,
+        self-contained (cite the groundwork), absolute rule of morality, but Kroy's version of the FUL prescribes obligations 
+        in a self-referencing manner. The FUL is supposed to define what is permissible and what isn't, 
+        but Kroy provides a circular definition that defines permissibility in terms of permissibility.
+
+        This is not obvious from Kroy's presentation of his formalization of 
+        the categorical imperative. This example demonstrates the power of formalized ethics. Making
+        an interpretation of the categorical imperative precise demonstrated a philosophical problem 
+        with that interpretation.
+
+        Another key takeaway here is that in order for a formalization to be faithful to what Korsgaard
+        argues is the most generous interpretation of the formula of universal law, we must have some notion
+        of the actions and ends of a maxim. Specifically, we must be able to represent the notion of the 
+        actions of a maxim being ``undermined" or impossible.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \endisadelimdocument
-\ \ \isacommand{lemma}\isamarkupfalse%
+%
+\begin{isamarkuptext}%
+In addition to testing specific applications of the theory, we're also interested in certain 
+        metaethical properties, as in the naive interpretation. First, we want to see if permissiblility
+        is possible under this formalization.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
 \ permissible{\isacharcolon}\isanewline
-\ \ \ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymexists}A{\isachardot}\ {\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
-\ \ \ \ \isacommand{nitpick}\isamarkupfalse%
-\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharbrackright}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{oops}\isamarkupfalse%
-\isanewline
-%
-\isamarkupcmt{\color{blue}Nitpick found a model for card i = 1 and card s = 1:
-
-  Skolem constant:
-    A =($\lambda x. \_$)($i_1$ := False) \color{black}%
-}\isanewline
-%
-\isamarkupcmt{Just as with the naive interpretation, permissibility is possible.%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ fixed{\isacharunderscore}formula{\isacharunderscore}is{\isacharunderscore}permissible{\isacharcolon}\isanewline
-\ \ \isakeyword{fixes}\ A\isanewline
+\ \ \isakeyword{fixes}\ A\ w\isanewline
 \ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
@@
     A = ($\lambda x. \_$)($i_1$ := False)\color{black}%
-}\isanewline
-%
-\isamarkupcmt{This bad result also holds under Kroy's formulation. Recall that we want this to fail - if A is ``murder" 
-then no model should render it permissible.%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isanewline
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+The above result shows that, for some action A and world w, we can find a model where A 
+        is permissible at w. That's exactly the result we want. If we were to further specify properties
+        of A (such as `A is murder' or `A is prohibited') we would want this result to fail.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+Next, we want to see if the formalization allows arbitrary obligations.%
+\end{isamarkuptext}\isamarkuptrue%
 \isacommand{lemma}\isamarkupfalse%
@@
 \ \ \isacommand{nitpick}\isamarkupfalse%
-\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharequal}true{\isacharbrackright}%
+\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharequal}true{\isacharcomma}\ falsify{\isacharbrackright}%
 \isadelimproof
@@
 \isacommand{oops}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-ought implies can%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-arbitrary obligations%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-conflicting obligations%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-obligation and permissible relationship%
+\isanewline
+%
+\isamarkupcmt{Nitpick found a counterexample for card i = 1 and card s = 1:
+
+  Free variable:
+    A = ($\lambda x. \_$)($i_1$ := False)%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+This is exactly the expected result. Any arbitrary action A isn't obligated. A slightly 
+        stronger property is ``modal collapse," or whether or not A happens implies A is obligated.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ modal{\isacharunderscore}collapse{\isacharcolon}\isanewline
+\ \ \isakeyword{fixes}\ A\ w\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}A\ w\ {\isasymlongrightarrow}\ O\ {\isacharbraceleft}A{\isacharbraceright}\ w{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharequal}true{\isacharcomma}\ falsify{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{Nitpick found a counterexample for card i = 1 and card s = 1:
+
+  Free variables:
+    A = ($\lambda x. \_$)($i_1$ := True)
+    w = $i_1$%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+This test also passes. Next, let's try whether or not ought implies can holds. Recall that I 
+        showed in section 3.1.2 that ought implies can is a theorem of DDL itself, so it should still hold.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ ought{\isacharunderscore}implies{\isacharunderscore}can{\isacharcolon}\isanewline
+\ \ \isakeyword{fixes}\ A\ w\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}O\ {\isacharbraceleft}A{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ {\isasymdiamond}\ A\ w{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{using}\isamarkupfalse%
+\ O{\isacharunderscore}diamond\ \isacommand{by}\isamarkupfalse%
+\ blast%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+This theorem holds. Now that we have a substitution operation, we also expect that if an action 
+      is obligated for a person then it is possible for that person. That should also follow by the 
+      axiom of substitution \cite{cresswell}, or if we just replace the `A' in the formula above with 
+      `A(p)'%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ ought{\isacharunderscore}implies{\isacharunderscore}can{\isacharunderscore}person{\isacharcolon}\isanewline
+\ \ \isakeyword{fixes}\ A\ w\ \isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}O\ {\isacharbraceleft}\ A{\isacharparenleft}p{\isacharparenright}{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ {\isasymdiamond}\ {\isacharparenleft}A\ {\isacharparenleft}p{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{using}\isamarkupfalse%
+\ O{\isacharunderscore}diamond\ \isacommand{by}\isamarkupfalse%
+\ blast%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+This test also passes. Next, let's explore whether or not Kroy's formalization still allows 
+      conflicting obligations.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ conflicting{\isacharunderscore}obligations{\isacharcolon}\isanewline
+\ \ \isakeyword{fixes}\ A\ w\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymand}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{$\color{blue}$Nitpick found a model for card i = 2 and card s = 1:
+
+  Free variable:
+    A = ($\lambda x. \_$)($i_1$ := False, $i_2$ := True)$\color{black}$%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+Just as with the naive formalization, Kroy's formalization allows for contradictory obligations. 
+        Recall earlier that we showed this is a property of DDL itself. This is a good goal to have for 
+        my custom formalization. I will also test the stronger property that if two maxims imply a 
+        contradiction, they may not be simultaneously willed.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ implied{\isacharunderscore}contradiction{\isacharcolon}\isanewline
+\ \ \isakeyword{fixes}\ A\ B\ w\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isacharparenleft}A\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ B{\isacharparenright}{\isacharparenright}w{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymand}\ O\ {\isacharbraceleft}B{\isacharbraceright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{$\color{blue}$Nitpick found a counterexample for card i = 2 and card s = 1:
+
+  Free variables:
+    A = ($\lambda x. \_$)($i_1$ := True, $i_2$  := False)
+    B = ($\lambda x. \_$)($i_1$  := True, $i_2$  := False)
+    w = $i_2$ $\color{black}$%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+Just as with the naive formalization, Kroy's formalization allows implied contradictions because 
+        DDL itself allows implied contradictions and, as we explored in Section (applied tests), Kroy's 
+        formalization doesn't do anything to remedy this. IS THIS ACTUALLY HOW WE REPRESENT A CONTRADICTION%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ ob{\isacharunderscore}perm{\isacharcolon}\isanewline
+\ \ \isakeyword{fixes}\ A\ w\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymor}\ {\isacharparenleft}P\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymor}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{by}\isamarkupfalse%
+\ simp\isanewline
+%
+\isamarkupcmt{This is exactly what we expect - an action should be either obligatory, permissible, or prohibited.%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+(This should be more developed and go at the beginning of this section as a thesis). The combination of these tests shows 
+      that while Kroy's formalization is more powerful and more coherent than the naive formalization, it 
+      still fails to capture most of the desired properties of the categorical imperative. Some of these 
+      problems might be remedied by the fact that Kroy's logic doesn't allow contradictory obligations, 
+      and that possibility will be interesting to explore in my own formalization.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
 %
@@
 %:%253=127%:%
-%:%257=129%:%
-%:%261=131%:%
-%:%262=132%:%
+%:%255=129%:%
+%:%256=129%:%
+%:%257=130%:%
+%:%258=131%:%
+%:%259=132%:%
+%:%260=133%:%
+%:%261=133%:%
 %:%263=133%:%
-%:%264=134%:%
-%:%265=135%:%
-%:%267=137%:%
-%:%268=137%:%
-%:%269=138%:%
-%:%270=139%:%
-%:%271=140%:%
-%:%272=140%:%
-%:%274=140%:%
-%:%278=140%:%
-%:%279=140%:%
-%:%281=141%:%
-%:%282=142%:%
-%:%283=143%:%
-%:%284=144%:%
-%:%294=146%:%
-%:%295=147%:%
-%:%304=152%:%
-%:%316=154%:%
-%:%317=155%:%
-%:%318=156%:%
-%:%319=157%:%
-%:%320=158%:%
-%:%322=159%:%
-%:%323=159%:%
-%:%325=160%:%
-%:%328=162%:%
-%:%329=163%:%
-%:%330=164%:%
-%:%333=166%:%
-%:%335=168%:%
-%:%336=168%:%
-%:%337=169%:%
-%:%338=170%:%
-%:%339=170%:%
-%:%341=170%:%
-%:%345=170%:%
-%:%346=170%:%
-%:%348=171%:%
-%:%349=172%:%
-%:%350=173%:%
-%:%351=174%:%
-%:%352=175%:%
-%:%353=176%:%
-%:%363=178%:%
+%:%267=133%:%
+%:%268=133%:%
+%:%270=134%:%
+%:%271=135%:%
+%:%272=136%:%
+%:%273=137%:%
+%:%283=139%:%
+%:%287=141%:%
+%:%288=142%:%
+%:%289=143%:%
+%:%290=144%:%
+%:%291=145%:%
+%:%293=147%:%
+%:%294=147%:%
+%:%295=148%:%
+%:%296=149%:%
+%:%297=150%:%
+%:%298=150%:%
+%:%300=150%:%
+%:%304=150%:%
+%:%305=150%:%
+%:%307=151%:%
+%:%308=152%:%
+%:%309=153%:%
+%:%310=154%:%
+%:%320=156%:%
+%:%321=157%:%
+%:%330=162%:%
+%:%342=164%:%
+%:%343=165%:%
+%:%344=166%:%
+%:%345=167%:%
+%:%346=168%:%
+%:%348=169%:%
+%:%349=169%:%
+%:%351=170%:%
+%:%354=172%:%
+%:%355=173%:%
+%:%356=174%:%
+%:%359=176%:%
+%:%361=178%:%
+%:%362=178%:%
+%:%363=179%:%
+%:%364=180%:%
 %:%365=180%:%
-%:%366=180%:%
-%:%368=182%:%
-%:%370=184%:%
-%:%371=184%:%
-%:%372=184%:%
-%:%374=184%:%
-%:%378=184%:%
-%:%379=184%:%
-%:%381=185%:%
-%:%382=186%:%
-%:%383=187%:%
-%:%384=188%:%
-%:%394=190%:%
-%:%395=191%:%
-%:%396=192%:%
-%:%397=193%:%
-%:%406=197%:%
-%:%418=199%:%
-%:%419=200%:%
-%:%420=201%:%
-%:%422=203%:%
+%:%367=180%:%
+%:%371=180%:%
+%:%372=180%:%
+%:%374=181%:%
+%:%375=182%:%
+%:%376=183%:%
+%:%377=184%:%
+%:%378=185%:%
+%:%379=186%:%
+%:%389=188%:%
+%:%391=190%:%
+%:%392=190%:%
+%:%394=192%:%
+%:%396=194%:%
+%:%397=194%:%
+%:%398=194%:%
+%:%400=194%:%
+%:%404=194%:%
+%:%405=194%:%
+%:%407=195%:%
+%:%408=196%:%
+%:%409=197%:%
+%:%410=198%:%
+%:%420=200%:%
+%:%421=201%:%
+%:%422=202%:%
 %:%423=203%:%
-%:%425=204%:%
-%:%426=204%:%
-%:%427=205%:%
-%:%428=206%:%
-%:%429=206%:%
-%:%430=207%:%
-%:%433=208%:%
-%:%437=208%:%
-%:%438=208%:%
-%:%447=210%:%
-%:%448=211%:%
-%:%449=212%:%
-%:%450=213%:%
-%:%451=214%:%
-%:%452=215%:%
+%:%432=207%:%
+%:%443=209%:%
+%:%446=211%:%
+%:%447=212%:%
+%:%448=213%:%
+%:%450=215%:%
+%:%451=215%:%
 %:%453=216%:%
-%:%454=217%:%
+%:%454=216%:%
+%:%455=217%:%
+%:%456=218%:%
+%:%457=218%:%
 %:%458=219%:%
-%:%459=220%:%
-%:%461=222%:%
-%:%462=222%:%
-%:%464=223%:%
-%:%465=223%:%
-%:%466=224%:%
-%:%467=225%:%
-%:%468=225%:%
-%:%469=226%:%
-%:%472=227%:%
-%:%476=227%:%
-%:%477=227%:%
-%:%478=228%:%
-%:%479=228%:%
-%:%480=229%:%
-%:%481=229%:%
-%:%482=230%:%
-%:%483=230%:%
-%:%484=230%:%
-%:%485=231%:%
+%:%461=220%:%
+%:%465=220%:%
+%:%466=220%:%
+%:%475=222%:%
+%:%476=223%:%
+%:%477=224%:%
+%:%478=225%:%
+%:%479=226%:%
+%:%480=227%:%
+%:%481=228%:%
+%:%482=229%:%
 %:%486=231%:%
-%:%488=232%:%
-%:%489=233%:%
+%:%487=232%:%
+%:%489=234%:%
 %:%490=234%:%
-%:%491=235%:%
-%:%492=236%:%
-%:%502=238%:%
-%:%503=239%:%
-%:%504=240%:%
-%:%506=242%:%
-%:%507=242%:%
-%:%508=243%:%
-%:%509=243%:%
-%:%511=244%:%
-%:%512=244%:%
-%:%513=245%:%
-%:%514=246%:%
-%:%515=246%:%
-%:%516=247%:%
-%:%517=248%:%
-%:%518=249%:%
-%:%519=249%:%
-%:%521=249%:%
-%:%525=249%:%
-%:%526=249%:%
-%:%528=250%:%
-%:%529=251%:%
-%:%530=252%:%
-%:%531=253%:%
-%:%532=254%:%
-%:%533=255%:%
-%:%543=257%:%
-%:%544=258%:%
-%:%545=259%:%
-%:%546=260%:%
-%:%547=261%:%
-%:%548=262%:%
-%:%552=264%:%
-%:%553=265%:%
-%:%555=267%:%
-%:%556=267%:%
-%:%558=268%:%
-%:%559=269%:%
-%:%560=270%:%
-%:%561=271%:%
-%:%562=272%:%
-%:%563=273%:%
-%:%564=274%:%
-%:%565=274%:%
-%:%567=275%:%
-%:%568=276%:%
-%:%569=276%:%
-%:%570=277%:%
-%:%571=278%:%
-%:%572=278%:%
-%:%574=279%:%
-%:%575=280%:%
-%:%576=280%:%
-%:%577=281%:%
-%:%578=282%:%
-%:%579=282%:%
-%:%580=283%:%
-%:%581=284%:%
-%:%582=284%:%
-%:%584=284%:%
-%:%588=284%:%
-%:%589=284%:%
-%:%591=285%:%
-%:%592=286%:%
-%:%593=287%:%
-%:%594=288%:%
-%:%595=289%:%
-%:%605=291%:%
-%:%606=292%:%
-%:%607=293%:%
-%:%616=295%:%
-%:%626=297%:%
-%:%627=297%:%
-%:%628=298%:%
-%:%629=299%:%
-%:%630=299%:%
-%:%632=299%:%
-%:%636=299%:%
-%:%637=299%:%
-%:%639=300%:%
-%:%640=301%:%
-%:%641=302%:%
-%:%642=303%:%
-%:%643=303%:%
-%:%645=304%:%
-%:%653=304%:%
-%:%654=305%:%
-%:%655=306%:%
-%:%656=306%:%
-%:%657=307%:%
-%:%658=308%:%
-%:%659=309%:%
-%:%660=309%:%
-%:%662=309%:%
-%:%666=309%:%
-%:%667=309%:%
-%:%669=310%:%
-%:%670=311%:%
-%:%671=312%:%
-%:%672=313%:%
-%:%673=313%:%
-%:%675=314%:%
-%:%676=315%:%
-%:%684=315%:%
-%:%685=316%:%
-%:%686=317%:%
-%:%687=317%:%
-%:%688=318%:%
-%:%689=319%:%
-%:%690=320%:%
-%:%691=320%:%
-%:%693=320%:%
-%:%697=320%:%
-%:%707=322%:%
-%:%711=326%:%
-%:%715=328%:%
-%:%719=330%:%
-%:%728=332%:%
-%:%740=334%:%
+%:%492=235%:%
+%:%493=235%:%
+%:%494=236%:%
+%:%495=237%:%
+%:%496=237%:%
+%:%497=238%:%
+%:%500=239%:%
+%:%504=239%:%
+%:%505=239%:%
+%:%506=240%:%
+%:%507=240%:%
+%:%508=241%:%
+%:%509=241%:%
+%:%510=242%:%
+%:%511=242%:%
+%:%512=242%:%
+%:%513=243%:%
+%:%514=243%:%
+%:%516=244%:%
+%:%517=245%:%
+%:%518=246%:%
+%:%519=247%:%
+%:%520=248%:%
+%:%529=250%:%
+%:%532=252%:%
+%:%533=253%:%
+%:%534=254%:%
+%:%536=256%:%
+%:%537=256%:%
+%:%552=278%:%
+%:%553=279%:%
+%:%555=281%:%
+%:%556=281%:%
+%:%558=282%:%
+%:%559=283%:%
+%:%560=284%:%
+%:%561=285%:%
+%:%562=286%:%
+%:%563=287%:%
+%:%564=287%:%
+%:%566=288%:%
+%:%567=289%:%
+%:%568=289%:%
+%:%569=290%:%
+%:%570=291%:%
+%:%571=291%:%
+%:%573=292%:%
+%:%574=293%:%
+%:%575=293%:%
+%:%576=294%:%
+%:%577=295%:%
+%:%578=295%:%
+%:%579=296%:%
+%:%580=297%:%
+%:%581=297%:%
+%:%583=297%:%
+%:%587=297%:%
+%:%588=297%:%
+%:%590=298%:%
+%:%591=299%:%
+%:%592=300%:%
+%:%593=301%:%
+%:%594=302%:%
+%:%595=303%:%
+%:%596=304%:%
+%:%606=306%:%
+%:%607=307%:%
+%:%608=308%:%
+%:%612=311%:%
+%:%615=313%:%
+%:%616=314%:%
+%:%617=315%:%
+%:%618=316%:%
+%:%619=317%:%
+%:%620=318%:%
+%:%623=320%:%
+%:%625=322%:%
+%:%626=322%:%
+%:%627=323%:%
+%:%630=324%:%
+%:%634=324%:%
+%:%635=324%:%
+%:%637=325%:%
+%:%643=325%:%
+%:%646=326%:%
+%:%647=327%:%
+%:%648=327%:%
+%:%649=328%:%
+%:%650=329%:%
+%:%651=330%:%
+%:%652=330%:%
+%:%654=330%:%
+%:%658=330%:%
+%:%659=330%:%
+%:%661=331%:%
+%:%662=332%:%
+%:%663=333%:%
+%:%664=334%:%
+%:%665=335%:%
+%:%675=337%:%
+%:%676=338%:%
+%:%677=339%:%
+%:%678=340%:%
+%:%679=341%:%
+%:%683=343%:%
+%:%684=344%:%
+%:%685=345%:%
+%:%686=346%:%
+%:%687=347%:%
+%:%688=348%:%
+%:%689=349%:%
+%:%690=350%:%
+%:%691=351%:%
+%:%692=352%:%
+%:%693=353%:%
+%:%694=354%:%
+%:%695=355%:%
+%:%696=356%:%
+%:%697=357%:%
+%:%698=358%:%
+%:%699=359%:%
+%:%700=360%:%
+%:%701=361%:%
+%:%702=362%:%
+%:%703=363%:%
+%:%704=364%:%
+%:%705=365%:%
+%:%714=367%:%
+%:%726=369%:%
+%:%727=370%:%
+%:%728=371%:%
+%:%730=373%:%
+%:%731=373%:%
+%:%732=374%:%
+%:%733=375%:%
+%:%734=376%:%
+%:%735=376%:%
+%:%737=376%:%
+%:%741=376%:%
+%:%742=376%:%
+%:%744=377%:%
+%:%745=378%:%
+%:%746=379%:%
+%:%747=380%:%
+%:%757=382%:%
+%:%758=383%:%
+%:%759=384%:%
+%:%763=386%:%
+%:%765=388%:%
+%:%766=388%:%
+%:%767=389%:%
+%:%768=390%:%
+%:%769=391%:%
+%:%770=391%:%
+%:%772=391%:%
+%:%776=391%:%
+%:%777=391%:%
+%:%779=392%:%
+%:%780=393%:%
+%:%781=394%:%
+%:%782=395%:%
+%:%792=397%:%
+%:%793=398%:%
+%:%795=400%:%
+%:%796=400%:%
+%:%797=401%:%
+%:%798=402%:%
+%:%799=403%:%
+%:%800=403%:%
+%:%802=403%:%
+%:%806=403%:%
+%:%807=403%:%
+%:%809=404%:%
+%:%810=405%:%
+%:%811=406%:%
+%:%812=407%:%
+%:%813=408%:%
+%:%823=410%:%
+%:%824=411%:%
+%:%826=413%:%
+%:%827=413%:%
+%:%828=414%:%
+%:%829=415%:%
+%:%832=416%:%
+%:%836=416%:%
+%:%837=416%:%
+%:%838=416%:%
+%:%847=418%:%
+%:%848=419%:%
+%:%849=420%:%
+%:%850=421%:%
+%:%852=423%:%
+%:%853=423%:%
+%:%854=424%:%
+%:%855=425%:%
+%:%858=426%:%
+%:%862=426%:%
+%:%863=426%:%
+%:%864=426%:%
+%:%873=428%:%
+%:%874=429%:%
+%:%876=431%:%
+%:%877=431%:%
+%:%878=432%:%
+%:%879=433%:%
+%:%880=434%:%
+%:%881=434%:%
+%:%883=434%:%
+%:%887=434%:%
+%:%888=434%:%
+%:%890=435%:%
+%:%891=436%:%
+%:%892=437%:%
+%:%893=438%:%
+%:%903=440%:%
+%:%904=441%:%
+%:%905=442%:%
+%:%906=443%:%
+%:%908=445%:%
+%:%909=445%:%
+%:%910=446%:%
+%:%911=447%:%
+%:%912=448%:%
+%:%913=449%:%
+%:%914=449%:%
+%:%916=449%:%
+%:%920=449%:%
+%:%921=449%:%
+%:%923=450%:%
+%:%924=451%:%
+%:%925=452%:%
+%:%926=453%:%
+%:%927=454%:%
+%:%928=455%:%
+%:%938=457%:%
+%:%939=458%:%
+%:%940=459%:%
+%:%942=461%:%
+%:%943=461%:%
+%:%944=462%:%
+%:%945=463%:%
+%:%948=464%:%
+%:%952=464%:%
+%:%953=464%:%
+%:%955=465%:%
+%:%965=467%:%
+%:%966=468%:%
+%:%967=469%:%
+%:%968=470%:%
+%:%969=471%:%
+%:%978=473%:%
+%:%990=475%:%

### 2021-09-20 paper/output/document/paper32.tex
finished kroy i guess

@@
 As we see above, the syllogism fails at Step 3, explaining why the lemma doesn't 
-        hold as expected. Taking a step back, it's not clear that Step 3 should hold. After all,
+        hold as expected. Kroy explicitly states (p. 199 footnote 19) that this lemma holds in his logic, which may explain
+        his choice of formalization. Taking a step back, it's not clear that Step 3 should hold. After all,
         impossible actions can be permissible (look for citation). Imagine I make a trip to Target to 
@@
 \begin{isamarkuptext}%
-(This is some actual philosophy - maybe worth fleshing this out and giving it a separate subsection?)
+(This is actual philosophy - maybe worth fleshing this out?)
         Another core issue here is Kroy's interpretation of the formula of universal law. In @cite{korsgaardFUL}, 
@@
 %
-\isamarkupsubsection{Misc%
+\isamarkupsubsection{Miscellaneous Test%
 }
@@
 \endisadelimdocument
+%
+\begin{isamarkuptext}%
+In this section, I explore tests of properties that Kroy presents in his original paper. These 
+tests will not only test the features of the system that Kroy intended to draw out, but they may also 
+inspire additional tests and criteria for my own formalization in Chapter 3.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+Kroy presents a stronger version of the formula of universal law and argues that his formalization
+is implied by the stronger version. Let's test that claim.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{abbreviation}\isamarkupfalse%
+\ FUL{\isacharunderscore}strong{\isacharcolon}{\isacharcolon}bool\ \isakeyword{where}\ {\isachardoublequoteopen}FUL{\isacharunderscore}strong\ {\isasymequiv}\ \ {\isasymforall}w\ A{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isasymexists}p{\isacharcolon}{\isacharcolon}s{\isachardot}\ {\isacharparenleft}{\isacharparenleft}P\ {\isacharbraceleft}A\ p{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}\ \ {\isasymlongrightarrow}{\isacharparenleft}\ {\isacharparenleft}{\isacharparenleft}\ P\ {\isacharbraceleft}\ {\isasymlambda}x{\isachardot}\ {\isasymforall}p{\isachardot}\ A\ p\ x{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ strong{\isacharunderscore}implies{\isacharunderscore}weak{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}FUL{\isacharunderscore}Strong\ {\isasymlongrightarrow}\ FUL{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{using}\isamarkupfalse%
+\ FUL\ \isacommand{by}\isamarkupfalse%
+\ blast%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+Kroy's stated stronger version of the FUL is indeed stronger than his original version.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+The difference between the stronger version and \isa{FUL\ {\isasymequiv}\ {\isasymforall}w\ A{\isachardot}\ {\isacharparenleft}{\isasymexists}p{\isachardot}\ P\ {\isacharbraceleft}A\ p{\isacharbraceright}\ w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ P\ {\isacharbraceleft}A\ p{\isacharbraceright}\ w{\isacharparenright}} is subtle.
+The antecedent of FUL is ``for all people p,
+it is permissible that they p." The antecedent of this stronger statement is ``it is permissible that 
+everyone p's." In particular, this stronger statement requires that it is permissible for everyone to
+ p simultaneously. Kroy immediately rejects this version of the categorical imperative, arguing that 
+it's impossible for everyone to be the US president simultaneously, so this version of the FUL prohibits
+running for president.
+
+Most Kantians would disagree with this interpretation. Consider the classical example of lying, as presented 
+in \cite{kemp} and in \cite{KorsgaardFUL}. Lying fails the universalizability test because in a 
+world where everyone lied simultaneously, the practice of lying would break down. If we adopt Kroy's 
+version, lying is only prohibited if, no matter who lies, lying is impermissible. As argued above, this 
+rule circularly relies on some existing prohibition against lying for a particular person, and thus 
+fails to show the wrongness of lying. It is tempting to claim that this issue explains why the tests 
+above on the wrongness of lying failed. To test this hypothesis, I will check if the stronger version 
+of the FUL implies that lying is impermissible. (TODO make this and the written philosophy above coherent)%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ strongFUL{\isacharunderscore}implies{\isacharunderscore}lying{\isacharunderscore}is{\isacharunderscore}wrong{\isacharcolon}\isanewline
+\ \ \isakeyword{fixes}\ p\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}FUL{\isacharunderscore}strong\ {\isasymlongrightarrow}\ {\isasymTurnstile}{\isacharparenleft}\isactrlbold {\isasymnot}\ P\ {\isacharbraceleft}lie{\isacharparenleft}p{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{$\color{blue}$
+Nitpick found a counterexample for card i = 1 and card s = 1:
+
+  Free variable:
+    p = $s_1$
+$\color{black}$%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+The test above also fails! This means that not even the stronger version of Kroy's formalization
+        of the FUL can show the wrongness of lying. There are two independent errors. The first is the 
+        cirularity of the formalization and the second is the assumption that impossible actions are 
+        impermissible. The stronger FUL addresses the first error, but the second remains.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+Kroy also argues that the FUL gives us recipes for deriving obligations, in addition to deriving
+        permissibile actions. Specifically, he presents two principles parallel to FUL and strong FUL, 
+        which in his logic are equivalent.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{abbreviation}\isamarkupfalse%
+\ obligation{\isacharunderscore}universal{\isacharunderscore}weak{\isacharcolon}{\isacharcolon}bool\ \isakeyword{where}\ {\isachardoublequoteopen}obligation{\isacharunderscore}universal{\isacharunderscore}weak\ {\isasymequiv}\ {\isasymforall}w\ A{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isasymexists}p{\isacharcolon}{\isacharcolon}s{\isachardot}\ {\isacharparenleft}{\isacharparenleft}O\ {\isacharbraceleft}A\ p{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}\ \ {\isasymlongrightarrow}{\isacharparenleft}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ {\isacharparenleft}\ O\ {\isacharbraceleft}A\ p\ {\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ obligation{\isacharunderscore}universal{\isacharunderscore}strong{\isacharcolon}{\isacharcolon}bool\ \isakeyword{where}\ {\isachardoublequoteopen}obligation{\isacharunderscore}universal{\isacharunderscore}strong\ {\isasymequiv}\ {\isasymforall}w\ A{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isasymexists}p{\isacharcolon}{\isacharcolon}s{\isachardot}\ {\isacharparenleft}{\isacharparenleft}O\ {\isacharbraceleft}A\ p{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}\ \ {\isasymlongrightarrow}{\isacharparenleft}\ {\isacharparenleft}{\isacharparenleft}\ O\ {\isacharbraceleft}\ {\isasymlambda}x{\isachardot}\ {\isasymforall}p{\isachardot}\ A\ p\ x{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ weak{\isacharunderscore}equiv{\isacharunderscore}strong{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}obligation{\isacharunderscore}universal{\isacharunderscore}weak\ {\isasymequiv}\ obligation{\isacharunderscore}universal{\isacharunderscore}strong{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{Isabelle is neither able to find a proof nor a countermodel for the statement above, so I can't say 
+  if it holds or not without completing a full, manual proof. This entire aside is not super relevant to 
+  my project, so I will defer such a proof until later.%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+These two statements are not necessarily equivalent in my logic, but are in Kroy's$\footnote{This follows from
+        the fact that the Barcan formula holds in Kroy's logic but not in mine, as verified with Nitpick. See 
+        Appendix for more.}$ This difference in logics may further explain why tests are not behaving as 
+        they should. Nonetheless, Kroy argues that the FUL implies both statements above. Let's test that.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ FUL{\isacharunderscore}implies{\isacharunderscore}ob{\isacharunderscore}weak{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}FUL\ {\isasymlongrightarrow}\ obligation{\isacharunderscore}universal{\isacharunderscore}weak{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{Isabelle is neither able to find a proof nor a countermodel for this statement.%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ FUL{\isacharunderscore}implies{\isacharunderscore}ob{\isacharunderscore}strong{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}FUL\ {\isasymlongrightarrow}\ obligation{\isacharunderscore}universal{\isacharunderscore}strong{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{Isabelle is neither able to find a proof nor a countermodel for this statement.%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+Isabelle timed out when looking for proofs or countermodels to the statements above. This may be 
+        an indication of a problem that Benzmueller warned me about—mixing quantifiers into a shallow
+        embedding of DDL may be too expensive for Isabelle to handle. Not sure what to do about this.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+Kroy argues that the two statements above are equivalent, but this fails in our logic.%
+\end{isamarkuptext}\isamarkuptrue%
 %
@@
 %:%679=341%:%
-%:%683=343%:%
+%:%680=342%:%
 %:%684=344%:%
@@
 %:%705=365%:%
-%:%714=367%:%
-%:%726=369%:%
+%:%706=366%:%
+%:%715=368%:%
 %:%727=370%:%
 %:%728=371%:%
-%:%730=373%:%
-%:%731=373%:%
+%:%729=372%:%
+%:%731=374%:%
 %:%732=374%:%
@@
 %:%734=376%:%
-%:%735=376%:%
-%:%737=376%:%
-%:%741=376%:%
-%:%742=376%:%
-%:%744=377%:%
+%:%735=377%:%
+%:%736=377%:%
+%:%738=377%:%
+%:%742=377%:%
+%:%743=377%:%
 %:%745=378%:%
@@
 %:%747=380%:%
-%:%757=382%:%
+%:%748=381%:%
 %:%758=383%:%
 %:%759=384%:%
-%:%763=386%:%
-%:%765=388%:%
-%:%766=388%:%
+%:%760=385%:%
+%:%764=387%:%
+%:%766=389%:%
 %:%767=389%:%
@@
 %:%769=391%:%
-%:%770=391%:%
-%:%772=391%:%
-%:%776=391%:%
-%:%777=391%:%
-%:%779=392%:%
+%:%770=392%:%
+%:%771=392%:%
+%:%773=392%:%
+%:%777=392%:%
+%:%778=392%:%
 %:%780=393%:%
@@
 %:%782=395%:%
-%:%792=397%:%
+%:%783=396%:%
 %:%793=398%:%
-%:%795=400%:%
-%:%796=400%:%
+%:%794=399%:%
+%:%796=401%:%
 %:%797=401%:%
@@
 %:%799=403%:%
-%:%800=403%:%
-%:%802=403%:%
-%:%806=403%:%
-%:%807=403%:%
-%:%809=404%:%
+%:%800=404%:%
+%:%801=404%:%
+%:%803=404%:%
+%:%807=404%:%
+%:%808=404%:%
 %:%810=405%:%
@@
 %:%813=408%:%
-%:%823=410%:%
+%:%814=409%:%
 %:%824=411%:%
-%:%826=413%:%
-%:%827=413%:%
+%:%825=412%:%
+%:%827=414%:%
 %:%828=414%:%
 %:%829=415%:%
-%:%832=416%:%
-%:%836=416%:%
-%:%837=416%:%
-%:%838=416%:%
-%:%847=418%:%
+%:%830=416%:%
+%:%833=417%:%
+%:%837=417%:%
+%:%838=417%:%
+%:%839=417%:%
 %:%848=419%:%
@@
 %:%850=421%:%
-%:%852=423%:%
-%:%853=423%:%
+%:%851=422%:%
+%:%853=424%:%
 %:%854=424%:%
 %:%855=425%:%
-%:%858=426%:%
-%:%862=426%:%
-%:%863=426%:%
-%:%864=426%:%
-%:%873=428%:%
+%:%856=426%:%
+%:%859=427%:%
+%:%863=427%:%
+%:%864=427%:%
+%:%865=427%:%
 %:%874=429%:%
-%:%876=431%:%
-%:%877=431%:%
+%:%875=430%:%
+%:%877=432%:%
 %:%878=432%:%
@@
 %:%880=434%:%
-%:%881=434%:%
-%:%883=434%:%
-%:%887=434%:%
-%:%888=434%:%
-%:%890=435%:%
+%:%881=435%:%
+%:%882=435%:%
+%:%884=435%:%
+%:%888=435%:%
+%:%889=435%:%
 %:%891=436%:%
@@
 %:%893=438%:%
-%:%903=440%:%
+%:%894=439%:%
 %:%904=441%:%
@@
 %:%906=443%:%
-%:%908=445%:%
-%:%909=445%:%
+%:%907=444%:%
+%:%909=446%:%
 %:%910=446%:%
@@
 %:%913=449%:%
-%:%914=449%:%
-%:%916=449%:%
-%:%920=449%:%
-%:%921=449%:%
-%:%923=450%:%
+%:%914=450%:%
+%:%915=450%:%
+%:%917=450%:%
+%:%921=450%:%
+%:%922=450%:%
 %:%924=451%:%
@@
 %:%928=455%:%
-%:%938=457%:%
+%:%929=456%:%
 %:%939=458%:%
 %:%940=459%:%
-%:%942=461%:%
-%:%943=461%:%
+%:%941=460%:%
+%:%943=462%:%
 %:%944=462%:%
 %:%945=463%:%
-%:%948=464%:%
-%:%952=464%:%
-%:%953=464%:%
-%:%955=465%:%
-%:%965=467%:%
+%:%946=464%:%
+%:%949=465%:%
+%:%953=465%:%
+%:%954=465%:%
+%:%956=466%:%
 %:%966=468%:%
@@
 %:%969=471%:%
-%:%978=473%:%
-%:%990=475%:%
+%:%970=472%:%
+%:%979=474%:%
+%:%991=476%:%
+%:%992=477%:%
+%:%993=478%:%
+%:%997=480%:%
+%:%998=481%:%
+%:%1000=483%:%
+%:%1001=483%:%
+%:%1002=484%:%
+%:%1003=485%:%
+%:%1004=485%:%
+%:%1005=486%:%
+%:%1008=487%:%
+%:%1012=487%:%
+%:%1013=487%:%
+%:%1014=487%:%
+%:%1023=489%:%
+%:%1027=491%:%
+%:%1028=492%:%
+%:%1029=493%:%
+%:%1030=494%:%
+%:%1031=495%:%
+%:%1032=496%:%
+%:%1033=497%:%
+%:%1034=498%:%
+%:%1035=499%:%
+%:%1036=500%:%
+%:%1037=501%:%
+%:%1038=502%:%
+%:%1039=503%:%
+%:%1040=504%:%
+%:%1041=505%:%
+%:%1043=507%:%
+%:%1044=507%:%
+%:%1045=508%:%
+%:%1046=509%:%
+%:%1047=510%:%
+%:%1048=510%:%
+%:%1050=510%:%
+%:%1054=510%:%
+%:%1055=510%:%
+%:%1057=511%:%
+%:%1058=512%:%
+%:%1059=513%:%
+%:%1060=514%:%
+%:%1061=515%:%
+%:%1062=516%:%
+%:%1072=518%:%
+%:%1073=519%:%
+%:%1074=520%:%
+%:%1075=521%:%
+%:%1079=523%:%
+%:%1080=524%:%
+%:%1081=525%:%
+%:%1083=527%:%
+%:%1084=527%:%
+%:%1085=528%:%
+%:%1086=528%:%
+%:%1087=529%:%
+%:%1088=529%:%
+%:%1089=530%:%
+%:%1092=531%:%
+%:%1096=531%:%
+%:%1097=531%:%
+%:%1099=532%:%
+%:%1100=533%:%
+%:%1101=534%:%
+%:%1111=536%:%
+%:%1112=537%:%
+%:%1113=538%:%
+%:%1114=539%:%
+%:%1116=541%:%
+%:%1117=541%:%
+%:%1118=542%:%
+%:%1120=542%:%
+%:%1124=542%:%
+%:%1125=542%:%
+%:%1127=543%:%
+%:%1135=543%:%
+%:%1136=544%:%
+%:%1137=545%:%
+%:%1138=545%:%
+%:%1139=546%:%
+%:%1141=546%:%
+%:%1145=546%:%
+%:%1146=546%:%
+%:%1148=547%:%
+%:%1158=549%:%
+%:%1159=550%:%
+%:%1160=551%:%
+%:%1177=564%:%
+%:%1181=565%:%

### 2021-09-21 paper/output/document/paper32.tex
small style fix
cleaning

@@
 %
-\isamarkupsubsubsection{Additional Logical Tools%
+\isamarkupsubsubsection{Logical Background \label{sec:kroy_logical_background}%
 }
@@
 \begin{isamarkuptext}%
-Kroy's logic relies heavily on some notion of identity or agency. We need some notion of ``x does action", 
-which we can write as ``x is the subject of the sentence `does action'". This requires defining a subject.%
+Kroy's logic relies heavily on some notion of identity or agency. The logic must be capable of 
+expressing statements like ``x does action", which I can write as ``x is the subject of the sentence
+ `does action.'" This requires defining a subject.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \ s\ %
-\isamarkupcmt{s is the type for a ``subject", like the subject of a sentence%
+\isamarkupcmt{s is the type for a ``subject," i.e. the subject of a sentence%
 }%
@@
 for d." DDL has no such notion of substitution, so I will define a more generalized notion of an ``open 
-sentence." An open sentence takes as input a subject and returns a complete or ``closed" DDL formula. For example, 
+sentence." An open sentence takes as input a subject and returns a complete or ``closed" DDL formula by, 
+in effect, binding the free variable in the sentence to the input. For example, 
 ``does action" is an open sentence that can be instantiated with a subject.%
@@
 \ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlemph P\ {\isacharbraceleft}A{\isacharbraceright}\ {\isasymequiv}\ {\isasymlambda}x{\isachardot}\ P\ {\isacharbraceleft}A{\isacharparenleft}x{\isacharparenright}{\isacharbraceright}{\isachardoublequoteclose}%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\isatagdocument
-%
-\isamarkupsubsubsection{Differences Between Kroy's Logic (Kr) and DDL%
-}
-\isamarkuptrue%
-%
-\endisatagdocument
-{\isafolddocument}%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\begin{isamarkuptext}%
-One complication that arises here is that Kroy's original paper uses a different logic than DDL. 
+\textbf{Differences Between Kroy's Logic (Kr) and DDL}
+%
+\begin{isamarkuptext}%
+There is potential for complication because Kroy's original paper uses a different logic than DDL. 
 His custom logic is a slight modification of Hintikka's deontic logic \cite{hintikka}. In this section, 
@@
 %
-\begin{isamarkuptext}%
-\textbf{Deontic alternatives versus the neighborhood semantics}%
-\end{isamarkuptext}\isamarkuptrue%
+\emph{Deontic alternatives versus the neighborhood semantics}
 %
@@
  proposition fails in DDL. In DDL, the $ob$ function abstracts away the notion of
- deontic alternatives and completely determines obligations. Even if one belives that permissible 
+ deontic alternatives. Even if one believes that permissible 
 statements should be true at some deontic alternative, it's not clear that permissible statements
@@
 \isacommand{lemma}\isamarkupfalse%
-\ permissible{\isacharunderscore}semantics{\isacharunderscore}{\isadigit{2}}{\isacharcolon}\isanewline
+\ permissible{\isacharunderscore}semantics{\isacharunderscore}strong{\isacharcolon}\isanewline
 \ \ \isakeyword{fixes}\ A\ w\isanewline
@@
 %
-\isamarkupcmt{Contradictory things can't be obligated in Kr, since a contradiction can't be true at any deontic alternative.
+\isamarkupcmt{$\color{blue} $Nitpick found a counterexample for card i = 1:
+
+  Free variables:
+    A = ($\lambda x. \_$)($i_1$ := True)
+    B = ($\lambda x. \_$)($i_1$ := True) $\color{blue}$%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+Contradictory things can't be obligated in Kr, since a contradiction can't be true at any deontic alternative.
 This doesn't hold in DDL, and we already saw this cause problems for the naive formalization. We should 
@@
 a symptom of DDL, not of any inherent problem with Kroy's formalization.%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-\textbf{Obligatory statements should be permissible}%
-\end{isamarkuptext}\isamarkuptrue%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\emph{Obligatory statements should be permissible}
 %
@@
 \isacommand{lemma}\isamarkupfalse%
-\ permissible{\isacharunderscore}prereq{\isacharunderscore}ob{\isacharcolon}\isanewline
+\ ob{\isacharunderscore}implies{\isacharunderscore}perm{\isacharcolon}\isanewline
 \ \ \isakeyword{fixes}\ A\ w\isanewline
@@
 \begin{isamarkuptext}%
-This particular difference seems untenable. My custom formalization of the categorical imperative 
-must add this as an axiom.%
+Intuitively, it seems untenable for any ethical theory to not include this principle. My 
+formalization should add this as an axiom.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupsubsubsection{The Categorical Imperative%
+\isamarkupsubsubsection{The Categorical Imperative \label{sec: kroy_ful}%
 }
@@
 Kroy interprets this to mean that if an action is permissible for a specific agent, then it must be permissible for everyone.
-This formalizes an important moral intuition: the categorical imperative prohibits free-riding. No one is a moral exception.
+This formalizes the moral intuition prohibiting free-riding. According to the categorical imperative, no one is a moral exception.
 Formalizing this interpretation requires using open sentences to handle the notion of substitution.%
@@
 \isacommand{abbreviation}\isamarkupfalse%
-\ FUL{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}FUL\ {\isasymequiv}\ {\isasymforall}w\ A{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isasymexists}p{\isacharcolon}{\isacharcolon}s{\isachardot}\ {\isacharparenleft}{\isacharparenleft}P\ {\isacharbraceleft}A\ p{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}\ \ {\isasymlongrightarrow}{\isacharparenleft}\ {\isacharparenleft}{\isasymforall}p{\isachardot}{\isacharparenleft}\ P\ {\isacharbraceleft}A\ p{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isacharparenright}\ {\isachardoublequoteclose}%
-\begin{isamarkuptext}%
-P {A p} vs *P{A} p%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\isamarkupcmt{In English, this statement roughly means that, for any person $p$ if action $A$ is 
-permissible for $p$, then action $A$ must be permissible for all agents $x$. The notion of ``permissible for" 
+\ FUL{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}FUL\ {\isasymequiv}\ {\isasymforall}w\ A{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isasymexists}p{\isacharcolon}{\isacharcolon}s{\isachardot}\ {\isacharparenleft}{\isacharparenleft}P\ {\isacharbraceleft}A\ p{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}\ \ {\isasymlongrightarrow}{\isacharparenleft}\ {\isacharparenleft}{\isasymforall}p{\isachardot}{\isacharparenleft}\ P\ {\isacharbraceleft}A\ p{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isacharparenright}\ {\isachardoublequoteclose}\isanewline
+\isanewline
+%
+\isamarkupcmt{In English, this statement roughly means that, if action $A$ is 
+permissible for some person $p$, then, for any person $p$, action $A$ must be permissible. The notion of ``permissible $for$" 
 is captured by the substitution of $x$ for $p$.%
@@
 %
-\isamarkupsubsubsection{Application Tests%
+\isamarkupsubsubsection{Application Tests\label{sec:app_tests_kroy}%
 }
@@
 %
-\textbf{Murder}
-%
-\begin{isamarkuptext}%
-Recall that in Section 3.1.1, we tested the naive interpretation's ability to show that murder 
-is wrong. We started by showing that if murder is possibly wrong, then it is wrong. Let's test that 
-here.%
+\begin{isamarkuptext}%
+In the following sections, I will use the application and metaethical tests presenting in Sections \ref{sec:app_tests_naive} and \ref{sec:meta_tests_naive}
+        to tease out the strengths and weaknesses of Kroy's formalization. While the formalization is considerably
+        stronger than the naive formalization, it still fails many of these tests. Some of these failures 
+        are due to the differences between Kroy's logic and my logic mentioned in Section \ref{sec:kroy_logical_background}, but some 
+        reveal philosophical problems with Kroy's interpretation of what the formula of universal law means. 
+        I will analyze these problems in the context of philosophical scholarship explicating the content 
+        of the formula of universal law. The findings in these sections will inform milestones for my
+        custom formalization of the categorical imperative. They also serve as an example of how formalized
+        and automated ethics can reveal philosophical strengths and weaknesses of an ethical theory.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+\textbf{Murder}%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+In Section \ref{sec:app_tests_naive}, I began by testing the naive interpretation's ability to show that murder 
+is wrong. I started by showing the morally dubious proposition that if murder is possibly wrong, then 
+it is actually wrong.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \isacommand{by}\isamarkupfalse%
-\ simp%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-This is the same result we got in Section 3.1.1—if murder is wrong at some world, it is wrong at
-every world. Kroy's formulation shouldn't actually mean that this property holds. Kroy interprets the 
-FUL as universalizing across $people$, not worlds. In other words, Kroy's formulation implies that if
-murder is wrong for someone, then it is wrong for everyone. This strange result is actually a property 
-of DDL itself, not a property of Kroy's formalization. Indeed, repeating this experiment in DDL, with no
+\ simp\isanewline
+%
+\isamarkupcmt{This sentence reads: ``If it is possible that murder is prohibited at world cw, then murder is prohibited 
+at all worlds.%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+This is the same result we got in Section \ref{sec:app_tests_naive}—if murder is possibly wrong at some world, it is wrong at
+every world. The result is incredible strong—the mere possibility of wrongness at some world is sufficient
+to imply prohibition at $\text{every world}$.
+
+Kroy's formalization shouldn't actually imply this property. Recall that this property held in the 
+naive interpretation because it universalized a proposition across worlds (using the necessity operator).
+Kroy, on the other hand, interprets the FUL as universalizing across $\text{people}$, not worlds. 
+In other words, Kroy's formulation implies that if murder is wrong for someone, then it is wrong for 
+everyone.
+
+The fact that this strange lemma holds is actually a property of DDL itself, not a property
+of Kroy's formalization. Indeed, repeating this experiment in DDL, with no
 additional axioms that represent the categorical imperative shows that, in DDL, if something is 
-possible wrong, it is wrong at every world. So this is not a useful example to test any formulation,
+possibly wrong, it is wrong at every world. This implies that this is not a useful example to test any formulation,
 since it holds in the base logic itself.%
@@
 \begin{isamarkuptext}%
-Let's try adapting our murder wrong axiom to Kroy's formulation. In particular, let's see if 
-murder being wrong for one person means that it's wrong for everyone.%
+To adapt the murder wrong axiom to capture the spirit of Kroy's formulation, I will modify if 
+to state that if murder is wrong for one person, it is wrong for everyone.%
 \end{isamarkuptext}\isamarkuptrue%
 \isacommand{consts}\isamarkupfalse%
-\ M{\isadigit{2}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}os{\isachardoublequoteclose}\isanewline
-%
-\isamarkupcmt{Let's define murder as an open sentence this time, so that we can substitute in different people.%
+\ M{\isacharunderscore}kroy{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}os{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{This time, murder is an open sentence, so that I can substitute in different agents.%
 }\isanewline
@@
 \ wrong{\isacharunderscore}if{\isacharunderscore}wrong{\isacharunderscore}for{\isacharunderscore}someone{\isacharcolon}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymexists}p{\isachardot}\ {\isasymTurnstile}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}{\isacharparenleft}M{\isadigit{2}}\ p{\isacharparenright}{\isacharbraceright}{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ {\isasymTurnstile}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}{\isacharparenleft}M{\isadigit{2}}\ p{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymexists}p{\isachardot}\ {\isasymTurnstile}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}{\isacharparenleft}M{\isacharunderscore}kroy\ p{\isacharparenright}{\isacharbraceright}{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ {\isasymTurnstile}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}{\isacharparenleft}M{\isacharunderscore}kroy\ p{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
 %
@@
 \ \ \ \ \isacommand{assume}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymexists}p{\isachardot}\ {\isasymTurnstile}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}{\isacharparenleft}M{\isadigit{2}}\ p{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymexists}p{\isachardot}\ {\isasymTurnstile}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}{\isacharparenleft}M{\isacharunderscore}kroy\ p{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
 \ \ \ \ \isacommand{show}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymforall}p{\isachardot}\ {\isasymTurnstile}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}{\isacharparenleft}M{\isadigit{2}}\ p{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymforall}p{\isachardot}\ {\isasymTurnstile}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}{\isacharparenleft}M{\isacharunderscore}kroy\ p{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
 \ \ \ \ \ \ \isacommand{using}\isamarkupfalse%
-\ FUL\ {\isacartoucheopen}{\isasymexists}p{\isachardot}\ {\isasymTurnstile}\isactrlemph O{\isacharbraceleft}\isactrlemph {\isasymnot}M{\isadigit{2}}{\isacharbraceright}\ p{\isacartoucheclose}\ \isacommand{by}\isamarkupfalse%
+\ FUL\ {\isacartoucheopen}{\isasymexists}p{\isachardot}\ {\isasymTurnstile}\isactrlemph O{\isacharbraceleft}\isactrlemph {\isasymnot}M{\isacharunderscore}kroy{\isacharbraceright}\ p{\isacartoucheclose}\ \isacommand{by}\isamarkupfalse%
 \ blast\isanewline
 \ \ \isacommand{qed}\isamarkupfalse%
-\isanewline
-%
-\isamarkupcmt{This lemma gets to the heart of Kroy's formulation of the categorical imperative. If murder is prohobited
-for a specific person $p$, then it must be prohibited for all people. This test case also revealed a 
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+This lemma gets to the heart of Kroy's formulation of the categorical imperative. If murder is prohibited
+for a specific person $p$, then it must be prohibited for all people\footnote{This test case also revealed a 
 bug in my original implementation of Kroy's formulation of the FUL, demonstrating the power of such 
-philosophical tests for automated ethics. Just as engineers use TDD to find bugs in their code, philosophers
-and ethicists can use this approach to find bugs in the precise formulations of their theories.%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\textbf{Lying}
-%
-\begin{isamarkuptext}%
-For the naive implementation, we also tested the slightly stronger proposition that if not 
-everyone can simultaneously lie, then lying is prohibited. We want to show that if lying 
-fails the universalizability test, then the FUL prohibits it.%
+automated tests and precise formulations to find bugs in ethical theories.}.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+\textbf{Lying}%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+For the naive implementation, I also tested the stronger proposition that if not 
+everyone can simultaneously lie, then lying is prohibited. This is the equivalent of claiming that 
+if lying fails the universalizability test, it is prohibited.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+I want to represent the sentence``At all worlds, it is 
+      not possible that everyone lies simultaneously." This requires the following two abbreviations.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \endisadelimproof
-%
-\begin{isamarkuptext}%
-We want to represent the sentence, call it $S$ $\longleftrightarrow$ ``At all worlds, it is 
-      not possible that everyone lies simultaneously." Consider the two abbreviations below.%
-\end{isamarkuptext}\isamarkuptrue%
+\isanewline
 \isacommand{abbreviation}\isamarkupfalse%
@@
 %
-\isamarkupcmt{Armed with \isa{everyone{\isacharunderscore}lies\ {\isasymequiv}\ {\isasymlambda}w{\isachardot}\ {\isasymforall}p{\isachardot}\ lie\ p\ w}, it's easy to represent the sentence $S$.
+\isamarkupcmt{Armed with \isa{everyone{\isacharunderscore}lies\ {\isasymequiv}\ {\isasymlambda}w{\isachardot}\ {\isasymforall}p{\isachardot}\ lie\ p\ w}, it's easy to represent the desired sentence.
 The abbreviation above
 reads, ``At all worlds, it is not possible that everyone lies."%
-}\isanewline
-\isanewline
+}%
+\begin{isamarkuptext}%
+Now that I have defined a sentence stating that lying fails the universalizability test, I can 
+      test if this sentence implies that lying is impermissible.%
+\end{isamarkuptext}\isamarkuptrue%
 \isacommand{lemma}\isamarkupfalse%
@@
 %
-\isamarkupcmt{$\color{blue}$Nitpick found a counterexample for card i = 1 and card s = 2:
+\isamarkupcmt{\color{blue} Nitpick found a counterexample for card i = 1 and card s = 2:
 
@@
 
-    $lying\_not\_possible_universal$ = True
-
-    p = $s_1$ $\color{black}$%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-Even with the stronger assumption that it's not possible for everyone to lie 
-    simultaneously, Kroy's formulation is still not able to show that lying is prohibited for an arbitrary
-    person. That is not good. Let's investigate why this is happening.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-Let's outline the syllogism that we $\emph{expect}$ to prove that lying is prohibited.%
+    $\text{lying\_not\_possibly\_universal}$ = True
+
+    $p = s_1$ \color{black}%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+Kroy's formulation fails this test, and is thus not able to show that if lying is not possible 
+      to universalize, it is prohibited for an arbitrary person. To understand why this is happening, I 
+      will outline the syllogism that I $\emph{expect}$ to prove that lying is prohibited.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{enumerate}
-        \item At all worlds, it's not possible for everyone to lie. (This is the assumed lemma lying\_not\_possible\_universal)
+        \item \text{At all worlds, it is not possible for everyone to lie. (This is the assumed lemma lying\_not\_possibly\_universal)}
         \item At all worlds, there is necessarily someone who doesn't lie. (Modal dual of (1))
-        \item If A is permissible for subject p at world w, A is possible for subject p at world w. (Ought Implies Can)
+        \item If A is permissible for subject p at world w, A is possible for subject p at world w. (Modified Ought Implies Can)
         \item If A is permissible at world w for any person p, it must be possible for everyone to A at w. (FUL and (3)) 
@@
 \begin{isamarkuptext}%
-Armed with this syllogism, we can figure out which step fails.%
+Armed with this syllogism, I can figure out why this test failed.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupcmt{Step 2 holds!%
+\isamarkupcmt{Step 2 holds.%
 }%
@@
 %
-\isamarkupcmt{$\color{blue}$Nitpick found a counterexample for card `a = 1, card i = 1, and card s = 1:
+\isamarkupcmt{$\color{blue}$ Nitpick found a counterexample for card `a = 1, card i = 1, and card s = 1:
 
@@
 As we see above, the syllogism fails at Step 3, explaining why the lemma doesn't 
-        hold as expected. Kroy explicitly states (p. 199 footnote 19) that this lemma holds in his logic, which may explain
-        his choice of formalization. Taking a step back, it's not clear that Step 3 should hold. After all,
-        impossible actions can be permissible (look for citation). Imagine I make a trip to Target to 
-        purchase a folder, and they offer blue and black folders. No one could claim that it's impermissible
+        hold as expected. Kroy explicitly states\footnote{See footnote 19 on p. 199} that this lemma holds in his logic.
+
+        The success of this lemma in Kroy's logic and the emptiness of his formalization of the FUL are 
+        two errors that contribute to the failure of this test. First, the statement expressed in Step 3
+        should not actually hold. Impossible actions can be permissible (do I need a citation?). For example, 
+        imagine I make a trip to Target to 
+        purchase a folder, and they offer blue and black folders. No one would claim that it's impermissible
         for me to purchase a red folder, or, equivalently, that I am obligated to not purchase a red folder.%
@@
 \begin{isamarkuptext}%
-(This is actual philosophy - maybe worth fleshing this out?)
-        Another core issue here is Kroy's interpretation of the formula of universal law. In @cite{korsgaardFUL}, 
-        Korsgaard defends a practical contradiction interpretation of the categorical imperative, whereby 
-        a maxim is prohibited if, when universalized, it defeats itself (Korsgaard 3). In other words, if universalizing
-        the maxim renders the maxim ineffective at achieving its stated objective, the maxim fails the
-        universalizability test.
-
-        This example shows that Kroy, on the other hand, is operating under a very different, circular view of 
-        the formula of universal law. He interprets the FUL as prohibiting A if it is not simultaneously 
-        permissible for everyone to A. This is empty—the categorical imperative is supposed to be a complete,
-        self-contained (cite the groundwork), absolute rule of morality, but Kroy's version of the FUL prescribes obligations 
+The second issue is that Kroy's interpretation of the formula of universal law is circular.
+        His formalization interprets the FUL as prohibiting A if there is someone for whom 
+        $A$'ing is not permissible. This requires some preexisting notion of the permissibility of $A$, and 
+        is thus circuar. The categorical imperative is supposed to be the complete,
+        self-contained rule of morality \cite{groundwork}, but Kroy's version of the FUL prescribes obligations 
         in a self-referencing manner. The FUL is supposed to define what is permissible and what isn't, 
-        but Kroy provides a circular definition that defines permissibility in terms of permissibility.
-
-        This is not obvious from Kroy's presentation of his formalization of 
+        but Kroy defines permissibility in terms of itself.
+
+        Neither of these errors are obvious from Kroy's presentation of his formalization of 
         the categorical imperative. This example demonstrates the power of formalized ethics. Making
-        an interpretation of the categorical imperative precise demonstrated a philosophical problem 
-        with that interpretation.
-
-        Another key takeaway here is that in order for a formalization to be faithful to what Korsgaard
-        argues is the most generous interpretation of the formula of universal law, we must have some notion
-        of the actions and ends of a maxim. Specifically, we must be able to represent the notion of the 
-        actions of a maxim being ``undermined" or impossible.%
+        Kroy's interpretation of the categorical imperative precise demonstrated a philosophical problem 
+        with that interpretation.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupsubsubsection{Metaethical Tests%
+\isamarkupsubsubsection{Metaethical Tests \label{sec:meta_tests_kroy}%
 }
@@
 \begin{isamarkuptext}%
-In addition to testing specific applications of the theory, we're also interested in certain 
-        metaethical properties, as in the naive interpretation. First, we want to see if permissiblility
+In addition to testing specific applications of the theory, I am also interested in 
+        metaethical properties, as in the naive interpretation. First, I will test if permissiblility
         is possible under this formalization.%
@@
 \begin{isamarkuptext}%
-The above result shows that, for some action A and world w, we can find a model where A 
-        is permissible at w. That's exactly the result we want. If we were to further specify properties
-        of A (such as `A is murder' or `A is prohibited') we would want this result to fail.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-Next, we want to see if the formalization allows arbitrary obligations.%
+The above result shows that, for some action $A$ and world $w$, Nitpick can find a model where $A$
+        is permissible at $w$. This means that the logic allows for permissible actions. If I further specify 
+        properties of $A$ (such as `$A$ is murder'), I would want this result to fail.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+Next, I will test if the formalization allows arbitrary obligations.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupcmt{Nitpick found a counterexample for card i = 1 and card s = 1:
+\isamarkupcmt{\color{blue} Nitpick found a counterexample for card i = 1 and card s = 1:
 
   Free variable:
-    A = ($\lambda x. \_$)($i_1$ := False)%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-This is exactly the expected result. Any arbitrary action A isn't obligated. A slightly 
-        stronger property is ``modal collapse," or whether or not A happens implies A is obligated.%
+    A = ($\lambda x. \_$)($i_1$ := False) \color{blue}%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+This is exactly the expected result. Any arbitrary action $A$ isn't obligated. A slightly 
+        stronger property is ``modal collapse," or whether or not `$A$ happens' implies `$A$ is obligated'.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupcmt{Nitpick found a counterexample for card i = 1 and card s = 1:
+\isamarkupcmt{\color{blue} Nitpick found a counterexample for card i = 1 and card s = 1:
 
@@
     A = ($\lambda x. \_$)($i_1$ := True)
-    w = $i_1$%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-This test also passes. Next, let's try whether or not ought implies can holds. Recall that I 
-        showed in section 3.1.2 that ought implies can is a theorem of DDL itself, so it should still hold.%
+    w = $i_1$ \color{black}%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+This test also passes. Next, I will test if not ought implies can holds. Recall that I 
+        showed in Section $\ref{sec:meta_tests_naive}$ that ought implies can is a theorem of DDL itself, so it should still hold.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-This theorem holds. Now that we have a substitution operation, we also expect that if an action 
-      is obligated for a person then it is possible for that person. That should also follow by the 
-      axiom of substitution \cite{cresswell}, or if we just replace the `A' in the formula above with 
+This theorem holds. Now that I have a substitution operation, I also expect that if an action 
+      is obligated for a person, then it is possible for that person. That should follow by the 
+      axiom of substitution \cite{cresswell} which lets me replace the `A' in the formula above with 
       `A(p)'%
@@
 \begin{isamarkuptext}%
-This test also passes. Next, let's explore whether or not Kroy's formalization still allows 
+This test also passes. Next, I will explore whether or not Kroy's formalization still allows 
       conflicting obligations.%
@@
 %
-\isamarkupcmt{$\color{blue}$Nitpick found a model for card i = 2 and card s = 1:
+\isamarkupcmt{\color{blue} Nitpick found a model for card i = 2 and card s = 1:
 
   Free variable:
-    A = ($\lambda x. \_$)($i_1$ := False, $i_2$ := True)$\color{black}$%
+    A = ($\lambda x. \_$)($i_1$ := False, $i_2$ := True) \color{black}%
 }%
@@
 Just as with the naive formalization, Kroy's formalization allows for contradictory obligations. 
-        Recall earlier that we showed this is a property of DDL itself. This is a good goal to have for 
-        my custom formalization. I will also test the stronger property that if two maxims imply a 
+        Recall earlier that I showed this is a property of DDL itself. This is a good goal to have in mind when 
+        developing my custom formalization.
+
+        Next, I will test the stronger property that if two maxims imply a
         contradiction, they may not be simultaneously willed.%
@@
 %
-\isamarkupcmt{$\color{blue}$Nitpick found a counterexample for card i = 2 and card s = 1:
+\isamarkupcmt{\color{blue} Nitpick found a counterexample for card i = 2 and card s = 1:
 
@@
     B = ($\lambda x. \_$)($i_1$  := True, $i_2$  := False)
-    w = $i_2$ $\color{black}$%
+    w = $i_2$ \color{black}%
 }%
@@
 Just as with the naive formalization, Kroy's formalization allows implied contradictions because 
-        DDL itself allows implied contradictions and, as we explored in Section (applied tests), Kroy's 
-        formalization doesn't do anything to remedy this. IS THIS ACTUALLY HOW WE REPRESENT A CONTRADICTION%
+        DDL itself allows implied contradictions and, as I explored in Section \ref{sec:naive_tests_kroy}, Kroy's 
+        formalization doesn't do anything to remedy this. IS THIS ACTUALLY HOW WE REPRESENT A CONTRADICTION
+
+      As my final metaethical test, I will test that an action is either obligatory, permissible, or 
+      prohibited.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupcmt{This is exactly what we expect - an action should be either obligatory, permissible, or prohibited.%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-(This should be more developed and go at the beginning of this section as a thesis). The combination of these tests shows 
-      that while Kroy's formalization is more powerful and more coherent than the naive formalization, it 
+\isamarkupcmt{This test passes.%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+These tests show that, while Kroy's formalization is more powerful and more coherent than the naive formalization, it 
       still fails to capture most of the desired properties of the categorical imperative. Some of these 
-      problems might be remedied by the fact that Kroy's logic doesn't allow contradictory obligations, 
+      problems may be remedied by the fact that Kroy's logic doesn't allow contradictory obligations, 
       and that possibility will be interesting to explore in my own formalization.%
@@
 %
-\isamarkupsubsection{Miscellaneous Test%
+\isamarkupsubsubsection{Miscellaneous Tests \label{sec: misc_tests_kroy}%
 }
@@
 In this section, I explore tests of properties that Kroy presents in his original paper. These 
-tests will not only test the features of the system that Kroy intended to draw out, but they may also 
-inspire additional tests and criteria for my own formalization in Chapter 3.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-Kroy presents a stronger version of the formula of universal law and argues that his formalization
+tests not only test the features of the system that Kroy intended to highlight, but they may also 
+inspire additional tests and criteria for my own formalization in Chapter 3. These tests further underscore 
+the circularity of Kroy's formalization and the differences between my logic and his.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+First, Kroy presents a stronger version of the formula of universal law and argues that his formalization
 is implied by the stronger version. Let's test that claim.%
@@
 \ FUL\ \isacommand{by}\isamarkupfalse%
-\ blast%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-Kroy's stated stronger version of the FUL is indeed stronger than his original version.%
-\end{isamarkuptext}\isamarkuptrue%
+\ blast\isanewline
+%
+\isamarkupcmt{This lemma holds, showing that Kroy is correct in stating that this version of the FUL is stronger than his original
+   version.%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
 %
@@
 The difference between the stronger version and \isa{FUL\ {\isasymequiv}\ {\isasymforall}w\ A{\isachardot}\ {\isacharparenleft}{\isasymexists}p{\isachardot}\ P\ {\isacharbraceleft}A\ p{\isacharbraceright}\ w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ P\ {\isacharbraceleft}A\ p{\isacharbraceright}\ w{\isacharparenright}} is subtle.
-The antecedent of FUL is ``for all people p,
-it is permissible that they p." The antecedent of this stronger statement is ``it is permissible that 
-everyone p's." In particular, this stronger statement requires that it is permissible for everyone to
- p simultaneously. Kroy immediately rejects this version of the categorical imperative, arguing that 
+The consequent of FUL is ``for all people $p$,
+it is permissible that they $A$." The consequent of this stronger statement is ``it is permissible that 
+everyone $A$." In particular, this stronger statement requires that it is permissible for everyone to
+ $A$ simultaneously. Kroy immediately rejects this version of the categorical imperative, arguing that 
 it's impossible for everyone to be the US president simultaneously, so this version of the FUL prohibits
@@
 fails to show the wrongness of lying. It is tempting to claim that this issue explains why the tests 
-above on the wrongness of lying failed. To test this hypothesis, I will check if the stronger version 
-of the FUL implies that lying is impermissible. (TODO make this and the written philosophy above coherent)%
+above failed. To test this hypothesis, I will check if the stronger version 
+of the FUL implies that lying is impermissible.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupcmt{$\color{blue}$
+\isamarkupcmt{\color{blue}
 Nitpick found a counterexample for card i = 1 and card s = 1:
@@
     p = $s_1$
-$\color{black}$%
+\color{black}%
 }%
@@
 The test above also fails! This means that not even the stronger version of Kroy's formalization
-        of the FUL can show the wrongness of lying. There are two independent errors. The first is the 
-        cirularity of the formalization and the second is the assumption that impossible actions are 
-        impermissible. The stronger FUL addresses the first error, but the second remains.%
+        of the FUL can show the wrongness of lying. As mentioned earlier, there are two independent errors. The first is the 
+        the assumption that impossible actions are impermissible and the second is the circularity of the 
+        formalization. The stronger FUL addresses the second error, but the first remains.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 Kroy also argues that the FUL gives us recipes for deriving obligations, in addition to deriving
-        permissibile actions. Specifically, he presents two principles parallel to FUL and strong FUL, 
-        which in his logic are equivalent.%
+        permissible actions. Specifically, he presents the following two principles, which are equivalent 
+        in his logic. These sentences parallel FUL and strong FUL.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \ obligation{\isacharunderscore}universal{\isacharunderscore}strong{\isacharcolon}{\isacharcolon}bool\ \isakeyword{where}\ {\isachardoublequoteopen}obligation{\isacharunderscore}universal{\isacharunderscore}strong\ {\isasymequiv}\ {\isasymforall}w\ A{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isasymexists}p{\isacharcolon}{\isacharcolon}s{\isachardot}\ {\isacharparenleft}{\isacharparenleft}O\ {\isacharbraceleft}A\ p{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}\ \ {\isasymlongrightarrow}{\isacharparenleft}\ {\isacharparenleft}{\isacharparenleft}\ O\ {\isacharbraceleft}\ {\isasymlambda}x{\isachardot}\ {\isasymforall}p{\isachardot}\ A\ p\ x{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Just as with FUL and FUL strong, the weaker version of the above statement has the consequent, ``For all people, 
+A is obligated." The stronger consequent is ``A is obligated for all people simultaneously."%
+}\isanewline
+\isanewline
 \isacommand{lemma}\isamarkupfalse%
@@
 \isamarkupcmt{Isabelle is neither able to find a proof nor a countermodel for the statement above, so I can't say 
-  if it holds or not without completing a full, manual proof. This entire aside is not super relevant to 
-  my project, so I will defer such a proof until later.%
+  if it holds or not without completing a full, manual proof. This aside is not very relevant to 
+  my project, so I will defer such a proof.%
 }%
@@
         Appendix for more.}$ This difference in logics may further explain why tests are not behaving as 
-        they should. Nonetheless, Kroy argues that the FUL implies both statements above. Let's test that.%
+        they should. Nonetheless, Kroy argues that the FUL implies both statements above.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \endisadelimproof
-%
-\begin{isamarkuptext}%
-Kroy argues that the two statements above are equivalent, but this fails in our logic.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-stuff from Kroy's paper%
-\end{isamarkuptext}\isamarkuptrue%
 %
@@
 %:%62=19%:%
-%:%64=21%:%
-%:%65=21%:%
-%:%66=21%:%
-%:%69=23%:%
+%:%63=20%:%
+%:%65=22%:%
+%:%66=22%:%
+%:%67=22%:%
 %:%70=24%:%
@@
 %:%72=26%:%
+%:%73=27%:%
 %:%74=28%:%
-%:%75=28%:%
-%:%77=29%:%
-%:%78=29%:%
-%:%80=30%:%
-%:%81=31%:%
-%:%84=33%:%
-%:%85=34%:%
+%:%76=30%:%
+%:%77=30%:%
+%:%79=31%:%
+%:%80=31%:%
+%:%82=32%:%
+%:%83=33%:%
 %:%86=35%:%
@@
 %:%88=37%:%
+%:%89=38%:%
 %:%90=39%:%
-%:%91=39%:%
-%:%92=40%:%
+%:%92=41%:%
 %:%93=41%:%
-%:%94=41%:%
-%:%95=42%:%
+%:%94=42%:%
+%:%95=43%:%
 %:%96=43%:%
-%:%97=43%:%
-%:%98=44%:%
+%:%97=44%:%
+%:%98=45%:%
 %:%99=45%:%
-%:%100=45%:%
-%:%101=46%:%
+%:%100=46%:%
+%:%101=47%:%
+%:%102=47%:%
 %:%103=48%:%
 %:%105=50%:%
-%:%106=50%:%
-%:%107=51%:%
+%:%107=52%:%
 %:%108=52%:%
-%:%109=52%:%
-%:%110=53%:%
-%:%117=56%:%
-%:%129=59%:%
-%:%130=60%:%
-%:%131=61%:%
-%:%132=62%:%
-%:%133=63%:%
-%:%137=65%:%
-%:%141=67%:%
-%:%142=68%:%
-%:%143=69%:%
-%:%144=70%:%
-%:%145=71%:%
-%:%146=72%:%
-%:%148=74%:%
-%:%149=74%:%
-%:%150=75%:%
-%:%151=76%:%
-%:%152=77%:%
-%:%153=77%:%
-%:%155=77%:%
-%:%159=77%:%
-%:%160=77%:%
-%:%162=78%:%
-%:%163=79%:%
-%:%164=80%:%
-%:%165=81%:%
-%:%175=83%:%
-%:%176=84%:%
-%:%177=85%:%
-%:%178=86%:%
-%:%179=87%:%
-%:%180=88%:%
-%:%181=89%:%
-%:%182=90%:%
-%:%183=91%:%
-%:%184=92%:%
-%:%186=94%:%
-%:%187=94%:%
-%:%188=95%:%
-%:%189=96%:%
-%:%190=97%:%
-%:%191=97%:%
-%:%193=97%:%
-%:%197=97%:%
-%:%198=97%:%
-%:%200=98%:%
-%:%201=99%:%
-%:%202=100%:%
-%:%203=101%:%
-%:%213=104%:%
-%:%214=105%:%
-%:%215=106%:%
-%:%216=107%:%
-%:%217=108%:%
-%:%218=109%:%
-%:%219=110%:%
-%:%220=111%:%
-%:%221=112%:%
-%:%223=115%:%
-%:%224=115%:%
-%:%225=116%:%
-%:%226=117%:%
-%:%227=118%:%
-%:%228=118%:%
-%:%230=118%:%
-%:%234=118%:%
-%:%235=118%:%
-%:%237=119%:%
-%:%238=120%:%
-%:%239=121%:%
-%:%240=122%:%
-%:%250=124%:%
-%:%251=125%:%
-%:%252=126%:%
-%:%253=127%:%
-%:%255=129%:%
-%:%256=129%:%
-%:%257=130%:%
-%:%258=131%:%
-%:%259=132%:%
-%:%260=133%:%
-%:%261=133%:%
-%:%263=133%:%
-%:%267=133%:%
-%:%268=133%:%
-%:%270=134%:%
-%:%271=135%:%
-%:%272=136%:%
-%:%273=137%:%
-%:%283=139%:%
-%:%287=141%:%
-%:%288=142%:%
-%:%289=143%:%
-%:%290=144%:%
-%:%291=145%:%
-%:%293=147%:%
-%:%294=147%:%
-%:%295=148%:%
-%:%296=149%:%
-%:%297=150%:%
-%:%298=150%:%
-%:%300=150%:%
-%:%304=150%:%
-%:%305=150%:%
-%:%307=151%:%
-%:%308=152%:%
-%:%309=153%:%
-%:%310=154%:%
-%:%320=156%:%
-%:%321=157%:%
-%:%330=162%:%
-%:%342=164%:%
-%:%343=165%:%
-%:%344=166%:%
-%:%345=167%:%
-%:%346=168%:%
-%:%348=169%:%
-%:%349=169%:%
-%:%351=170%:%
-%:%354=172%:%
-%:%355=173%:%
-%:%356=174%:%
-%:%359=176%:%
-%:%361=178%:%
-%:%362=178%:%
-%:%363=179%:%
-%:%364=180%:%
-%:%365=180%:%
-%:%367=180%:%
-%:%371=180%:%
-%:%372=180%:%
-%:%374=181%:%
-%:%375=182%:%
-%:%376=183%:%
-%:%377=184%:%
-%:%378=185%:%
-%:%379=186%:%
-%:%389=188%:%
-%:%391=190%:%
-%:%392=190%:%
-%:%394=192%:%
-%:%396=194%:%
-%:%397=194%:%
-%:%398=194%:%
-%:%400=194%:%
-%:%404=194%:%
-%:%405=194%:%
-%:%407=195%:%
-%:%408=196%:%
-%:%409=197%:%
-%:%410=198%:%
-%:%420=200%:%
-%:%421=201%:%
-%:%422=202%:%
-%:%423=203%:%
-%:%432=207%:%
-%:%443=209%:%
-%:%446=211%:%
-%:%447=212%:%
-%:%448=213%:%
-%:%450=215%:%
-%:%451=215%:%
-%:%453=216%:%
-%:%454=216%:%
-%:%455=217%:%
-%:%456=218%:%
-%:%457=218%:%
-%:%458=219%:%
-%:%461=220%:%
-%:%465=220%:%
-%:%466=220%:%
-%:%475=222%:%
-%:%476=223%:%
-%:%477=224%:%
-%:%478=225%:%
-%:%479=226%:%
-%:%480=227%:%
-%:%481=228%:%
-%:%482=229%:%
-%:%486=231%:%
-%:%487=232%:%
-%:%489=234%:%
-%:%490=234%:%
-%:%492=235%:%
-%:%493=235%:%
-%:%494=236%:%
-%:%495=237%:%
-%:%496=237%:%
-%:%497=238%:%
-%:%500=239%:%
-%:%504=239%:%
-%:%505=239%:%
-%:%506=240%:%
-%:%507=240%:%
-%:%508=241%:%
-%:%509=241%:%
-%:%510=242%:%
-%:%511=242%:%
-%:%512=242%:%
-%:%513=243%:%
-%:%514=243%:%
-%:%516=244%:%
-%:%517=245%:%
-%:%518=246%:%
-%:%519=247%:%
-%:%520=248%:%
-%:%529=250%:%
-%:%532=252%:%
-%:%533=253%:%
-%:%534=254%:%
-%:%536=256%:%
-%:%537=256%:%
-%:%552=278%:%
-%:%553=279%:%
-%:%555=281%:%
-%:%556=281%:%
-%:%558=282%:%
-%:%559=283%:%
-%:%560=284%:%
-%:%561=285%:%
-%:%562=286%:%
-%:%563=287%:%
-%:%564=287%:%
-%:%566=288%:%
-%:%567=289%:%
-%:%568=289%:%
-%:%569=290%:%
-%:%570=291%:%
-%:%571=291%:%
-%:%573=292%:%
-%:%574=293%:%
-%:%575=293%:%
-%:%576=294%:%
-%:%577=295%:%
-%:%578=295%:%
-%:%579=296%:%
-%:%580=297%:%
-%:%581=297%:%
-%:%583=297%:%
-%:%587=297%:%
-%:%588=297%:%
-%:%590=298%:%
-%:%591=299%:%
-%:%592=300%:%
-%:%593=301%:%
-%:%594=302%:%
-%:%595=303%:%
-%:%596=304%:%
-%:%606=306%:%
-%:%607=307%:%
-%:%608=308%:%
-%:%612=311%:%
-%:%615=313%:%
-%:%616=314%:%
-%:%617=315%:%
-%:%618=316%:%
-%:%619=317%:%
-%:%620=318%:%
-%:%623=320%:%
-%:%625=322%:%
-%:%626=322%:%
-%:%627=323%:%
-%:%630=324%:%
-%:%634=324%:%
-%:%635=324%:%
-%:%637=325%:%
-%:%643=325%:%
-%:%646=326%:%
-%:%647=327%:%
-%:%648=327%:%
-%:%649=328%:%
-%:%650=329%:%
-%:%651=330%:%
-%:%652=330%:%
-%:%654=330%:%
-%:%658=330%:%
-%:%659=330%:%
-%:%661=331%:%
-%:%662=332%:%
-%:%663=333%:%
-%:%664=334%:%
-%:%665=335%:%
-%:%675=337%:%
-%:%676=338%:%
-%:%677=339%:%
-%:%678=340%:%
-%:%679=341%:%
-%:%680=342%:%
-%:%684=344%:%
-%:%685=345%:%
-%:%686=346%:%
-%:%687=347%:%
-%:%688=348%:%
-%:%689=349%:%
-%:%690=350%:%
-%:%691=351%:%
-%:%692=352%:%
-%:%693=353%:%
-%:%694=354%:%
-%:%695=355%:%
-%:%696=356%:%
-%:%697=357%:%
-%:%698=358%:%
-%:%699=359%:%
-%:%700=360%:%
-%:%701=361%:%
-%:%702=362%:%
-%:%703=363%:%
-%:%704=364%:%
-%:%705=365%:%
-%:%706=366%:%
-%:%715=368%:%
-%:%727=370%:%
-%:%728=371%:%
-%:%729=372%:%
-%:%731=374%:%
-%:%732=374%:%
-%:%733=375%:%
-%:%734=376%:%
-%:%735=377%:%
-%:%736=377%:%
-%:%738=377%:%
-%:%742=377%:%
-%:%743=377%:%
-%:%745=378%:%
-%:%746=379%:%
-%:%747=380%:%
-%:%748=381%:%
-%:%758=383%:%
-%:%759=384%:%
-%:%760=385%:%
-%:%764=387%:%
-%:%766=389%:%
-%:%767=389%:%
-%:%768=390%:%
-%:%769=391%:%
-%:%770=392%:%
-%:%771=392%:%
-%:%773=392%:%
-%:%777=392%:%
-%:%778=392%:%
-%:%780=393%:%
-%:%781=394%:%
-%:%782=395%:%
-%:%783=396%:%
-%:%793=398%:%
-%:%794=399%:%
-%:%796=401%:%
-%:%797=401%:%
-%:%798=402%:%
-%:%799=403%:%
-%:%800=404%:%
-%:%801=404%:%
-%:%803=404%:%
-%:%807=404%:%
-%:%808=404%:%
-%:%810=405%:%
-%:%811=406%:%
-%:%812=407%:%
-%:%813=408%:%
-%:%814=409%:%
-%:%824=411%:%
-%:%825=412%:%
-%:%827=414%:%
-%:%828=414%:%
-%:%829=415%:%
-%:%830=416%:%
-%:%833=417%:%
-%:%837=417%:%
-%:%838=417%:%
-%:%839=417%:%
-%:%848=419%:%
-%:%849=420%:%
-%:%850=421%:%
-%:%851=422%:%
-%:%853=424%:%
-%:%854=424%:%
-%:%855=425%:%
-%:%856=426%:%
-%:%859=427%:%
-%:%863=427%:%
-%:%864=427%:%
-%:%865=427%:%
-%:%874=429%:%
-%:%875=430%:%
-%:%877=432%:%
-%:%878=432%:%
-%:%879=433%:%
-%:%880=434%:%
-%:%881=435%:%
-%:%882=435%:%
-%:%884=435%:%
-%:%888=435%:%
-%:%889=435%:%
-%:%891=436%:%
-%:%892=437%:%
-%:%893=438%:%
-%:%894=439%:%
-%:%904=441%:%
-%:%905=442%:%
-%:%906=443%:%
-%:%907=444%:%
-%:%909=446%:%
-%:%910=446%:%
-%:%911=447%:%
-%:%912=448%:%
-%:%913=449%:%
-%:%914=450%:%
-%:%915=450%:%
-%:%917=450%:%
-%:%921=450%:%
-%:%922=450%:%
-%:%924=451%:%
-%:%925=452%:%
-%:%926=453%:%
-%:%927=454%:%
-%:%928=455%:%
-%:%929=456%:%
-%:%939=458%:%
-%:%940=459%:%
-%:%941=460%:%
-%:%943=462%:%
-%:%944=462%:%
-%:%945=463%:%
-%:%946=464%:%
-%:%949=465%:%
-%:%953=465%:%
-%:%954=465%:%
-%:%956=466%:%
-%:%966=468%:%
-%:%967=469%:%
-%:%968=470%:%
-%:%969=471%:%
-%:%970=472%:%
-%:%979=474%:%
-%:%991=476%:%
-%:%992=477%:%
-%:%993=478%:%
-%:%997=480%:%
-%:%998=481%:%
-%:%1000=483%:%
-%:%1001=483%:%
-%:%1002=484%:%
-%:%1003=485%:%
-%:%1004=485%:%
-%:%1005=486%:%
-%:%1008=487%:%
-%:%1012=487%:%
-%:%1013=487%:%
-%:%1014=487%:%
-%:%1023=489%:%
-%:%1027=491%:%
-%:%1028=492%:%
-%:%1029=493%:%
-%:%1030=494%:%
-%:%1031=495%:%
-%:%1032=496%:%
-%:%1033=497%:%
-%:%1034=498%:%
-%:%1035=499%:%
-%:%1036=500%:%
-%:%1037=501%:%
-%:%1038=502%:%
-%:%1039=503%:%
-%:%1040=504%:%
-%:%1041=505%:%
-%:%1043=507%:%
-%:%1044=507%:%
-%:%1045=508%:%
-%:%1046=509%:%
-%:%1047=510%:%
-%:%1048=510%:%
-%:%1050=510%:%
-%:%1054=510%:%
-%:%1055=510%:%
-%:%1057=511%:%
-%:%1058=512%:%
-%:%1059=513%:%
-%:%1060=514%:%
-%:%1061=515%:%
-%:%1062=516%:%
-%:%1072=518%:%
-%:%1073=519%:%
-%:%1074=520%:%
-%:%1075=521%:%
-%:%1079=523%:%
-%:%1080=524%:%
-%:%1081=525%:%
-%:%1083=527%:%
-%:%1084=527%:%
-%:%1085=528%:%
-%:%1086=528%:%
-%:%1087=529%:%
-%:%1088=529%:%
-%:%1089=530%:%
-%:%1092=531%:%
-%:%1096=531%:%
-%:%1097=531%:%
-%:%1099=532%:%
-%:%1100=533%:%
-%:%1101=534%:%
-%:%1111=536%:%
-%:%1112=537%:%
-%:%1113=538%:%
-%:%1114=539%:%
-%:%1116=541%:%
-%:%1117=541%:%
-%:%1118=542%:%
-%:%1120=542%:%
-%:%1124=542%:%
-%:%1125=542%:%
-%:%1127=543%:%
-%:%1135=543%:%
-%:%1136=544%:%
-%:%1137=545%:%
-%:%1138=545%:%
-%:%1139=546%:%
-%:%1141=546%:%
-%:%1145=546%:%
-%:%1146=546%:%
-%:%1148=547%:%
-%:%1158=549%:%
-%:%1159=550%:%
-%:%1160=551%:%
-%:%1177=564%:%
-%:%1181=565%:%
+%:%109=53%:%
+%:%110=54%:%
+%:%111=54%:%
+%:%112=55%:%
+%:%113=58%:%
+%:%116=61%:%
+%:%117=62%:%
+%:%118=63%:%
+%:%119=64%:%
+%:%120=65%:%
+%:%123=67%:%
+%:%126=69%:%
+%:%127=70%:%
+%:%128=71%:%
+%:%129=72%:%
+%:%130=73%:%
+%:%131=74%:%
+%:%133=76%:%
+%:%134=76%:%
+%:%135=77%:%
+%:%136=78%:%
+%:%137=79%:%
+%:%138=79%:%
+%:%140=79%:%
+%:%144=79%:%
+%:%145=79%:%
+%:%147=80%:%
+%:%148=81%:%
+%:%149=82%:%
+%:%150=83%:%
+%:%160=85%:%
+%:%161=86%:%
+%:%162=87%:%
+%:%163=88%:%
+%:%164=89%:%
+%:%165=90%:%
+%:%166=91%:%
+%:%167=92%:%
+%:%168=93%:%
+%:%169=94%:%
+%:%171=96%:%
+%:%172=96%:%
+%:%173=97%:%
+%:%174=98%:%
+%:%175=99%:%
+%:%176=99%:%
+%:%178=99%:%
+%:%182=99%:%
+%:%183=99%:%
+%:%185=100%:%
+%:%186=101%:%
+%:%187=102%:%
+%:%188=103%:%
+%:%198=106%:%
+%:%199=107%:%
+%:%200=108%:%
+%:%201=109%:%
+%:%202=110%:%
+%:%203=111%:%
+%:%204=112%:%
+%:%205=113%:%
+%:%206=114%:%
+%:%208=117%:%
+%:%209=117%:%
+%:%210=118%:%
+%:%211=119%:%
+%:%212=120%:%
+%:%213=120%:%
+%:%215=120%:%
+%:%219=120%:%
+%:%220=120%:%
+%:%222=121%:%
+%:%223=122%:%
+%:%224=123%:%
+%:%225=124%:%
+%:%235=126%:%
+%:%236=127%:%
+%:%237=128%:%
+%:%238=129%:%
+%:%240=131%:%
+%:%241=131%:%
+%:%242=132%:%
+%:%243=133%:%
+%:%244=134%:%
+%:%245=135%:%
+%:%246=135%:%
+%:%248=135%:%
+%:%252=135%:%
+%:%253=135%:%
+%:%255=136%:%
+%:%256=137%:%
+%:%257=138%:%
+%:%258=139%:%
+%:%259=140%:%
+%:%269=142%:%
+%:%270=143%:%
+%:%271=144%:%
+%:%272=145%:%
+%:%275=147%:%
+%:%278=149%:%
+%:%279=150%:%
+%:%280=151%:%
+%:%281=152%:%
+%:%282=153%:%
+%:%284=155%:%
+%:%285=155%:%
+%:%286=156%:%
+%:%287=157%:%
+%:%288=158%:%
+%:%289=158%:%
+%:%291=158%:%
+%:%295=158%:%
+%:%296=158%:%
+%:%298=159%:%
+%:%299=160%:%
+%:%300=161%:%
+%:%301=162%:%
+%:%311=164%:%
+%:%312=165%:%
+%:%321=170%:%
+%:%333=172%:%
+%:%334=173%:%
+%:%335=174%:%
+%:%336=175%:%
+%:%337=176%:%
+%:%339=177%:%
+%:%340=177%:%
+%:%341=178%:%
+%:%343=179%:%
+%:%344=180%:%
+%:%345=181%:%
+%:%348=183%:%
+%:%350=185%:%
+%:%351=185%:%
+%:%352=186%:%
+%:%353=187%:%
+%:%354=187%:%
+%:%356=187%:%
+%:%360=187%:%
+%:%361=187%:%
+%:%363=188%:%
+%:%364=189%:%
+%:%365=190%:%
+%:%366=191%:%
+%:%367=192%:%
+%:%368=193%:%
+%:%378=195%:%
+%:%380=197%:%
+%:%381=197%:%
+%:%383=199%:%
+%:%385=201%:%
+%:%386=201%:%
+%:%387=201%:%
+%:%389=201%:%
+%:%393=201%:%
+%:%394=201%:%
+%:%396=202%:%
+%:%397=203%:%
+%:%398=204%:%
+%:%399=205%:%
+%:%409=207%:%
+%:%410=208%:%
+%:%411=209%:%
+%:%412=210%:%
+%:%421=213%:%
+%:%433=215%:%
+%:%434=216%:%
+%:%435=217%:%
+%:%436=218%:%
+%:%437=219%:%
+%:%438=220%:%
+%:%439=221%:%
+%:%440=222%:%
+%:%441=223%:%
+%:%445=225%:%
+%:%449=227%:%
+%:%450=228%:%
+%:%451=229%:%
+%:%453=231%:%
+%:%454=231%:%
+%:%456=232%:%
+%:%457=232%:%
+%:%458=233%:%
+%:%459=234%:%
+%:%460=234%:%
+%:%461=235%:%
+%:%464=236%:%
+%:%468=236%:%
+%:%469=236%:%
+%:%471=237%:%
+%:%472=238%:%
+%:%482=240%:%
+%:%483=241%:%
+%:%484=242%:%
+%:%485=243%:%
+%:%486=244%:%
+%:%487=245%:%
+%:%488=246%:%
+%:%489=247%:%
+%:%490=248%:%
+%:%491=249%:%
+%:%492=250%:%
+%:%493=251%:%
+%:%494=252%:%
+%:%495=253%:%
+%:%496=254%:%
+%:%500=256%:%
+%:%501=257%:%
+%:%503=259%:%
+%:%504=259%:%
+%:%506=260%:%
+%:%507=260%:%
+%:%508=261%:%
+%:%509=262%:%
+%:%510=262%:%
+%:%511=263%:%
+%:%514=264%:%
+%:%518=264%:%
+%:%519=264%:%
+%:%520=265%:%
+%:%521=265%:%
+%:%522=266%:%
+%:%523=266%:%
+%:%524=267%:%
+%:%525=267%:%
+%:%526=267%:%
+%:%527=268%:%
+%:%537=270%:%
+%:%538=271%:%
+%:%539=272%:%
+%:%540=273%:%
+%:%544=275%:%
+%:%548=277%:%
+%:%549=278%:%
+%:%550=279%:%
+%:%554=281%:%
+%:%555=282%:%
+%:%557=284%:%
+%:%558=284%:%
+%:%571=305%:%
+%:%572=306%:%
+%:%573=306%:%
+%:%575=307%:%
+%:%576=308%:%
+%:%577=309%:%
+%:%578=310%:%
+%:%579=311%:%
+%:%580=312%:%
+%:%581=312%:%
+%:%583=313%:%
+%:%584=314%:%
+%:%585=314%:%
+%:%586=315%:%
+%:%587=316%:%
+%:%588=316%:%
+%:%590=317%:%
+%:%591=318%:%
+%:%594=320%:%
+%:%595=321%:%
+%:%597=323%:%
+%:%598=323%:%
+%:%599=324%:%
+%:%600=325%:%
+%:%601=325%:%
+%:%603=325%:%
+%:%607=325%:%
+%:%608=325%:%
+%:%610=326%:%
+%:%611=327%:%
+%:%612=328%:%
+%:%613=329%:%
+%:%614=330%:%
+%:%615=331%:%
+%:%616=332%:%
+%:%626=334%:%
+%:%627=335%:%
+%:%628=336%:%
+%:%631=338%:%
+%:%632=339%:%
+%:%633=340%:%
+%:%634=341%:%
+%:%635=342%:%
+%:%636=343%:%
+%:%639=345%:%
+%:%641=347%:%
+%:%642=347%:%
+%:%643=348%:%
+%:%646=349%:%
+%:%650=349%:%
+%:%651=349%:%
+%:%653=350%:%
+%:%659=350%:%
+%:%662=351%:%
+%:%663=352%:%
+%:%664=352%:%
+%:%665=353%:%
+%:%666=354%:%
+%:%667=355%:%
+%:%668=355%:%
+%:%670=355%:%
+%:%674=355%:%
+%:%675=355%:%
+%:%677=356%:%
+%:%678=357%:%
+%:%679=358%:%
+%:%680=359%:%
+%:%681=360%:%
+%:%691=362%:%
+%:%692=363%:%
+%:%693=364%:%
+%:%694=365%:%
+%:%695=366%:%
+%:%696=367%:%
+%:%697=368%:%
+%:%698=369%:%
+%:%699=370%:%
+%:%703=373%:%
+%:%704=374%:%
+%:%705=375%:%
+%:%706=376%:%
+%:%707=377%:%
+%:%708=378%:%
+%:%709=379%:%
+%:%710=380%:%
+%:%711=381%:%
+%:%712=382%:%
+%:%713=383%:%
+%:%714=384%:%
+%:%723=386%:%
+%:%735=388%:%
+%:%736=389%:%
+%:%737=390%:%
+%:%739=392%:%
+%:%740=392%:%
+%:%741=393%:%
+%:%742=394%:%
+%:%743=395%:%
+%:%744=395%:%
+%:%746=395%:%
+%:%750=395%:%
+%:%751=395%:%
+%:%753=396%:%
+%:%754=397%:%
+%:%755=398%:%
+%:%756=399%:%
+%:%766=401%:%
+%:%767=402%:%
+%:%768=403%:%
+%:%772=405%:%
+%:%774=407%:%
+%:%775=407%:%
+%:%776=408%:%
+%:%777=409%:%
+%:%778=410%:%
+%:%779=410%:%
+%:%781=410%:%
+%:%785=410%:%
+%:%786=410%:%
+%:%788=411%:%
+%:%789=412%:%
+%:%790=413%:%
+%:%791=414%:%
+%:%801=416%:%
+%:%802=417%:%
+%:%804=419%:%
+%:%805=419%:%
+%:%806=420%:%
+%:%807=421%:%
+%:%808=422%:%
+%:%809=422%:%
+%:%811=422%:%
+%:%815=422%:%
+%:%816=422%:%
+%:%818=423%:%
+%:%819=424%:%
+%:%820=425%:%
+%:%821=426%:%
+%:%822=427%:%
+%:%832=429%:%
+%:%833=430%:%
+%:%835=432%:%
+%:%836=432%:%
+%:%837=433%:%
+%:%838=434%:%
+%:%841=435%:%
+%:%845=435%:%
+%:%846=435%:%
+%:%847=435%:%
+%:%856=437%:%
+%:%857=438%:%
+%:%858=439%:%
+%:%859=440%:%
+%:%861=442%:%
+%:%862=442%:%
+%:%863=443%:%
+%:%864=444%:%
+%:%867=445%:%
+%:%871=445%:%
+%:%872=445%:%
+%:%873=445%:%
+%:%882=447%:%
+%:%883=448%:%
+%:%885=450%:%
+%:%886=450%:%
+%:%887=451%:%
+%:%888=452%:%
+%:%889=453%:%
+%:%890=453%:%
+%:%892=453%:%
+%:%896=453%:%
+%:%897=453%:%
+%:%899=454%:%
+%:%900=455%:%
+%:%901=456%:%
+%:%902=457%:%
+%:%912=459%:%
+%:%913=460%:%
+%:%914=461%:%
+%:%915=462%:%
+%:%916=463%:%
+%:%917=464%:%
+%:%919=466%:%
+%:%920=466%:%
+%:%921=467%:%
+%:%922=468%:%
+%:%923=469%:%
+%:%924=470%:%
+%:%925=470%:%
+%:%927=470%:%
+%:%931=470%:%
+%:%932=470%:%
+%:%934=471%:%
+%:%935=472%:%
+%:%936=473%:%
+%:%937=474%:%
+%:%938=475%:%
+%:%939=476%:%
+%:%949=478%:%
+%:%950=479%:%
+%:%951=480%:%
+%:%952=481%:%
+%:%953=482%:%
+%:%954=483%:%
+%:%956=485%:%
+%:%957=485%:%
+%:%958=486%:%
+%:%959=487%:%
+%:%962=488%:%
+%:%966=488%:%
+%:%967=488%:%
+%:%969=489%:%
+%:%979=491%:%
+%:%980=492%:%
+%:%981=493%:%
+%:%982=494%:%
+%:%991=496%:%
+%:%1003=498%:%
+%:%1004=499%:%
+%:%1005=500%:%
+%:%1006=501%:%
+%:%1010=503%:%
+%:%1011=504%:%
+%:%1013=506%:%
+%:%1014=506%:%
+%:%1015=507%:%
+%:%1016=508%:%
+%:%1017=508%:%
+%:%1018=509%:%
+%:%1021=510%:%
+%:%1025=510%:%
+%:%1026=510%:%
+%:%1027=510%:%
+%:%1029=511%:%
+%:%1030=512%:%
+%:%1040=514%:%
+%:%1041=515%:%
+%:%1042=516%:%
+%:%1043=517%:%
+%:%1044=518%:%
+%:%1045=519%:%
+%:%1046=520%:%
+%:%1047=521%:%
+%:%1048=522%:%
+%:%1049=523%:%
+%:%1050=524%:%
+%:%1051=525%:%
+%:%1052=526%:%
+%:%1053=527%:%
+%:%1054=528%:%
+%:%1056=530%:%
+%:%1057=530%:%
+%:%1058=531%:%
+%:%1059=532%:%
+%:%1060=533%:%
+%:%1061=533%:%
+%:%1063=533%:%
+%:%1067=533%:%
+%:%1068=533%:%
+%:%1070=534%:%
+%:%1071=535%:%
+%:%1072=536%:%
+%:%1073=537%:%
+%:%1074=538%:%
+%:%1075=539%:%
+%:%1085=541%:%
+%:%1086=542%:%
+%:%1087=543%:%
+%:%1088=544%:%
+%:%1092=546%:%
+%:%1093=547%:%
+%:%1094=548%:%
+%:%1096=550%:%
+%:%1097=550%:%
+%:%1098=551%:%
+%:%1099=551%:%
+%:%1101=552%:%
+%:%1102=553%:%
+%:%1103=553%:%
+%:%1104=554%:%
+%:%1105=555%:%
+%:%1106=555%:%
+%:%1107=556%:%
+%:%1110=557%:%
+%:%1114=557%:%
+%:%1115=557%:%
+%:%1117=558%:%
+%:%1118=559%:%
+%:%1119=560%:%
+%:%1129=562%:%
+%:%1130=563%:%
+%:%1131=564%:%
+%:%1132=565%:%
+%:%1134=567%:%
+%:%1135=567%:%
+%:%1136=568%:%
+%:%1138=568%:%
+%:%1142=568%:%
+%:%1143=568%:%
+%:%1145=569%:%
+%:%1153=569%:%
+%:%1154=570%:%
+%:%1155=571%:%
+%:%1156=571%:%
+%:%1157=572%:%
+%:%1159=572%:%
+%:%1163=572%:%
+%:%1164=572%:%
+%:%1166=573%:%
+%:%1176=575%:%
+%:%1177=576%:%
+%:%1178=577%:%

### 2021-09-26 paper/output/document/paper32.tex
added maxim

@@
 \end{isamarkuptext}\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ contradictory{\isacharunderscore}obs{\isacharcolon}\isanewline
-\ \ \isakeyword{fixes}\ A\ B\ w\isanewline
-\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}A\ \isactrlbold {\isasymand}\ B{\isacharparenright}{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}A\ \isactrlbold {\isasymand}\ B{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
-\ \ \isacommand{nitpick}\isamarkupfalse%
-\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharbrackright}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{oops}\isamarkupfalse%
-\isanewline
-%
-\isamarkupcmt{$\color{blue} $Nitpick found a counterexample for card i = 1:
-
-  Free variables:
-    A = ($\lambda x. \_$)($i_1$ := True)
-    B = ($\lambda x. \_$)($i_1$ := True) $\color{blue}$%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-Contradictory things can't be obligated in Kr, since a contradiction can't be true at any deontic alternative.
-This doesn't hold in DDL, and we already saw this cause problems for the naive formalization. We should 
-expect those problems to hold in our implementation of Kr, but this difference suggests that they are 
-a symptom of DDL, not of any inherent problem with Kroy's formalization.%
-\end{isamarkuptext}\isamarkuptrue%
 %
@@
 Just as with the naive formalization, Kroy's formalization allows for contradictory obligations. 
-        Recall earlier that I showed this is a property of DDL itself. This is a good goal to have in mind when 
+        Testing this lemma in DDL without the FUL shows that this is a property of DDL itself. This is a good goal to have in mind when 
         developing my custom formalization.
@@
 \ \ \isakeyword{fixes}\ A\ B\ w\isanewline
-\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isacharparenleft}A\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ B{\isacharparenright}{\isacharparenright}w{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}A\ \isactrlbold {\isasymand}\ B{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbottom}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
 \ \ \isakeyword{shows}\ {\isachardoublequoteopen}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymand}\ O\ {\isacharbraceleft}B{\isacharbraceright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
@@
         DDL itself allows implied contradictions and, as I explored in Section \ref{sec:naive_tests_kroy}, Kroy's 
-        formalization doesn't do anything to remedy this. IS THIS ACTUALLY HOW WE REPRESENT A CONTRADICTION
+        formalization doesn't do anything to remedy this.
 
@@
 %:%238=129%:%
-%:%240=131%:%
 %:%241=131%:%
-%:%242=132%:%
-%:%243=133%:%
-%:%244=134%:%
-%:%245=135%:%
+%:%244=133%:%
+%:%245=134%:%
 %:%246=135%:%
-%:%248=135%:%
-%:%252=135%:%
-%:%253=135%:%
-%:%255=136%:%
-%:%256=137%:%
-%:%257=138%:%
-%:%258=139%:%
-%:%259=140%:%
-%:%269=142%:%
-%:%270=143%:%
-%:%271=144%:%
-%:%272=145%:%
-%:%275=147%:%
+%:%247=136%:%
+%:%248=137%:%
+%:%250=139%:%
+%:%251=139%:%
+%:%252=140%:%
+%:%253=141%:%
+%:%254=142%:%
+%:%255=142%:%
+%:%257=142%:%
+%:%261=142%:%
+%:%262=142%:%
+%:%264=143%:%
+%:%265=144%:%
+%:%266=145%:%
+%:%267=146%:%
+%:%277=148%:%
 %:%278=149%:%
-%:%279=150%:%
-%:%280=151%:%
-%:%281=152%:%
-%:%282=153%:%
-%:%284=155%:%
-%:%285=155%:%
-%:%286=156%:%
-%:%287=157%:%
-%:%288=158%:%
-%:%289=158%:%
-%:%291=158%:%
-%:%295=158%:%
-%:%296=158%:%
-%:%298=159%:%
-%:%299=160%:%
-%:%300=161%:%
-%:%301=162%:%
-%:%311=164%:%
-%:%312=165%:%
-%:%321=170%:%
-%:%333=172%:%
-%:%334=173%:%
-%:%335=174%:%
-%:%336=175%:%
-%:%337=176%:%
-%:%339=177%:%
-%:%340=177%:%
-%:%341=178%:%
-%:%343=179%:%
-%:%344=180%:%
-%:%345=181%:%
-%:%348=183%:%
-%:%350=185%:%
+%:%287=154%:%
+%:%299=156%:%
+%:%300=157%:%
+%:%301=158%:%
+%:%302=159%:%
+%:%303=160%:%
+%:%305=161%:%
+%:%306=161%:%
+%:%307=162%:%
+%:%309=163%:%
+%:%310=164%:%
+%:%311=165%:%
+%:%314=167%:%
+%:%316=169%:%
+%:%317=169%:%
+%:%318=170%:%
+%:%319=171%:%
+%:%320=171%:%
+%:%322=171%:%
+%:%326=171%:%
+%:%327=171%:%
+%:%329=172%:%
+%:%330=173%:%
+%:%331=174%:%
+%:%332=175%:%
+%:%333=176%:%
+%:%334=177%:%
+%:%344=179%:%
+%:%346=181%:%
+%:%347=181%:%
+%:%349=183%:%
 %:%351=185%:%
-%:%352=186%:%
-%:%353=187%:%
-%:%354=187%:%
-%:%356=187%:%
-%:%360=187%:%
-%:%361=187%:%
-%:%363=188%:%
-%:%364=189%:%
-%:%365=190%:%
-%:%366=191%:%
-%:%367=192%:%
-%:%368=193%:%
-%:%378=195%:%
-%:%380=197%:%
-%:%381=197%:%
-%:%383=199%:%
-%:%385=201%:%
-%:%386=201%:%
-%:%387=201%:%
-%:%389=201%:%
-%:%393=201%:%
-%:%394=201%:%
-%:%396=202%:%
-%:%397=203%:%
-%:%398=204%:%
-%:%399=205%:%
-%:%409=207%:%
-%:%410=208%:%
+%:%352=185%:%
+%:%353=185%:%
+%:%355=185%:%
+%:%359=185%:%
+%:%360=185%:%
+%:%362=186%:%
+%:%363=187%:%
+%:%364=188%:%
+%:%365=189%:%
+%:%375=191%:%
+%:%376=192%:%
+%:%377=193%:%
+%:%378=194%:%
+%:%387=197%:%
+%:%399=199%:%
+%:%400=200%:%
+%:%401=201%:%
+%:%402=202%:%
+%:%403=203%:%
+%:%404=204%:%
+%:%405=205%:%
+%:%406=206%:%
+%:%407=207%:%
 %:%411=209%:%
-%:%412=210%:%
-%:%421=213%:%
-%:%433=215%:%
-%:%434=216%:%
-%:%435=217%:%
-%:%436=218%:%
-%:%437=219%:%
-%:%438=220%:%
-%:%439=221%:%
-%:%440=222%:%
-%:%441=223%:%
-%:%445=225%:%
-%:%449=227%:%
-%:%450=228%:%
-%:%451=229%:%
-%:%453=231%:%
-%:%454=231%:%
+%:%415=211%:%
+%:%416=212%:%
+%:%417=213%:%
+%:%419=215%:%
+%:%420=215%:%
+%:%422=216%:%
+%:%423=216%:%
+%:%424=217%:%
+%:%425=218%:%
+%:%426=218%:%
+%:%427=219%:%
+%:%430=220%:%
+%:%434=220%:%
+%:%435=220%:%
+%:%437=221%:%
+%:%438=222%:%
+%:%448=224%:%
+%:%449=225%:%
+%:%450=226%:%
+%:%451=227%:%
+%:%452=228%:%
+%:%453=229%:%
+%:%454=230%:%
+%:%455=231%:%
 %:%456=232%:%
-%:%457=232%:%
-%:%458=233%:%
-%:%459=234%:%
-%:%460=234%:%
-%:%461=235%:%
-%:%464=236%:%
-%:%468=236%:%
-%:%469=236%:%
-%:%471=237%:%
-%:%472=238%:%
-%:%482=240%:%
-%:%483=241%:%
-%:%484=242%:%
-%:%485=243%:%
-%:%486=244%:%
-%:%487=245%:%
-%:%488=246%:%
-%:%489=247%:%
-%:%490=248%:%
-%:%491=249%:%
-%:%492=250%:%
-%:%493=251%:%
-%:%494=252%:%
-%:%495=253%:%
-%:%496=254%:%
-%:%500=256%:%
-%:%501=257%:%
-%:%503=259%:%
-%:%504=259%:%
-%:%506=260%:%
-%:%507=260%:%
-%:%508=261%:%
-%:%509=262%:%
-%:%510=262%:%
-%:%511=263%:%
-%:%514=264%:%
-%:%518=264%:%
-%:%519=264%:%
+%:%457=233%:%
+%:%458=234%:%
+%:%459=235%:%
+%:%460=236%:%
+%:%461=237%:%
+%:%462=238%:%
+%:%466=240%:%
+%:%467=241%:%
+%:%469=243%:%
+%:%470=243%:%
+%:%472=244%:%
+%:%473=244%:%
+%:%474=245%:%
+%:%475=246%:%
+%:%476=246%:%
+%:%477=247%:%
+%:%480=248%:%
+%:%484=248%:%
+%:%485=248%:%
+%:%486=249%:%
+%:%487=249%:%
+%:%488=250%:%
+%:%489=250%:%
+%:%490=251%:%
+%:%491=251%:%
+%:%492=251%:%
+%:%493=252%:%
+%:%503=254%:%
+%:%504=255%:%
+%:%505=256%:%
+%:%506=257%:%
+%:%510=259%:%
+%:%514=261%:%
+%:%515=262%:%
+%:%516=263%:%
 %:%520=265%:%
-%:%521=265%:%
-%:%522=266%:%
-%:%523=266%:%
-%:%524=267%:%
-%:%525=267%:%
-%:%526=267%:%
-%:%527=268%:%
-%:%537=270%:%
-%:%538=271%:%
-%:%539=272%:%
-%:%540=273%:%
-%:%544=275%:%
-%:%548=277%:%
-%:%549=278%:%
-%:%550=279%:%
-%:%554=281%:%
-%:%555=282%:%
-%:%557=284%:%
-%:%558=284%:%
-%:%571=305%:%
-%:%572=306%:%
-%:%573=306%:%
-%:%575=307%:%
-%:%576=308%:%
-%:%577=309%:%
-%:%578=310%:%
-%:%579=311%:%
-%:%580=312%:%
-%:%581=312%:%
-%:%583=313%:%
-%:%584=314%:%
-%:%585=314%:%
-%:%586=315%:%
-%:%587=316%:%
-%:%588=316%:%
-%:%590=317%:%
-%:%591=318%:%
+%:%521=266%:%
+%:%523=268%:%
+%:%524=268%:%
+%:%537=289%:%
+%:%538=290%:%
+%:%539=290%:%
+%:%541=291%:%
+%:%542=292%:%
+%:%543=293%:%
+%:%544=294%:%
+%:%545=295%:%
+%:%546=296%:%
+%:%547=296%:%
+%:%549=297%:%
+%:%550=298%:%
+%:%551=298%:%
+%:%552=299%:%
+%:%553=300%:%
+%:%554=300%:%
+%:%556=301%:%
+%:%557=302%:%
+%:%560=304%:%
+%:%561=305%:%
+%:%563=307%:%
+%:%564=307%:%
+%:%565=308%:%
+%:%566=309%:%
+%:%567=309%:%
+%:%569=309%:%
+%:%573=309%:%
+%:%574=309%:%
+%:%576=310%:%
+%:%577=311%:%
+%:%578=312%:%
+%:%579=313%:%
+%:%580=314%:%
+%:%581=315%:%
+%:%582=316%:%
+%:%592=318%:%
+%:%593=319%:%
 %:%594=320%:%
-%:%595=321%:%
-%:%597=323%:%
+%:%597=322%:%
 %:%598=323%:%
@@
 %:%600=325%:%
-%:%601=325%:%
-%:%603=325%:%
-%:%607=325%:%
-%:%608=325%:%
-%:%610=326%:%
-%:%611=327%:%
-%:%612=328%:%
-%:%613=329%:%
-%:%614=330%:%
-%:%615=331%:%
-%:%616=332%:%
-%:%626=334%:%
-%:%627=335%:%
-%:%628=336%:%
-%:%631=338%:%
-%:%632=339%:%
-%:%633=340%:%
-%:%634=341%:%
-%:%635=342%:%
-%:%636=343%:%
-%:%639=345%:%
-%:%641=347%:%
-%:%642=347%:%
-%:%643=348%:%
-%:%646=349%:%
-%:%650=349%:%
-%:%651=349%:%
-%:%653=350%:%
-%:%659=350%:%
+%:%601=326%:%
+%:%602=327%:%
+%:%605=329%:%
+%:%607=331%:%
+%:%608=331%:%
+%:%609=332%:%
+%:%612=333%:%
+%:%616=333%:%
+%:%617=333%:%
+%:%619=334%:%
+%:%625=334%:%
+%:%628=335%:%
+%:%629=336%:%
+%:%630=336%:%
+%:%631=337%:%
+%:%632=338%:%
+%:%633=339%:%
+%:%634=339%:%
+%:%636=339%:%
+%:%640=339%:%
+%:%641=339%:%
+%:%643=340%:%
+%:%644=341%:%
+%:%645=342%:%
+%:%646=343%:%
+%:%647=344%:%
+%:%657=346%:%
+%:%658=347%:%
+%:%659=348%:%
+%:%660=349%:%
+%:%661=350%:%
 %:%662=351%:%
 %:%663=352%:%
-%:%664=352%:%
-%:%665=353%:%
-%:%666=354%:%
-%:%667=355%:%
-%:%668=355%:%
-%:%670=355%:%
-%:%674=355%:%
-%:%675=355%:%
-%:%677=356%:%
-%:%678=357%:%
-%:%679=358%:%
-%:%680=359%:%
-%:%681=360%:%
-%:%691=362%:%
-%:%692=363%:%
-%:%693=364%:%
-%:%694=365%:%
-%:%695=366%:%
-%:%696=367%:%
-%:%697=368%:%
-%:%698=369%:%
-%:%699=370%:%
-%:%703=373%:%
-%:%704=374%:%
-%:%705=375%:%
+%:%664=353%:%
+%:%665=354%:%
+%:%669=357%:%
+%:%670=358%:%
+%:%671=359%:%
+%:%672=360%:%
+%:%673=361%:%
+%:%674=362%:%
+%:%675=363%:%
+%:%676=364%:%
+%:%677=365%:%
+%:%678=366%:%
+%:%679=367%:%
+%:%680=368%:%
+%:%689=370%:%
+%:%701=372%:%
+%:%702=373%:%
+%:%703=374%:%
+%:%705=376%:%
 %:%706=376%:%
@@
 %:%709=379%:%
-%:%710=380%:%
-%:%711=381%:%
-%:%712=382%:%
-%:%713=383%:%
-%:%714=384%:%
-%:%723=386%:%
-%:%735=388%:%
-%:%736=389%:%
-%:%737=390%:%
-%:%739=392%:%
-%:%740=392%:%
-%:%741=393%:%
-%:%742=394%:%
-%:%743=395%:%
-%:%744=395%:%
-%:%746=395%:%
-%:%750=395%:%
-%:%751=395%:%
-%:%753=396%:%
-%:%754=397%:%
-%:%755=398%:%
-%:%756=399%:%
-%:%766=401%:%
-%:%767=402%:%
-%:%768=403%:%
-%:%772=405%:%
-%:%774=407%:%
-%:%775=407%:%
-%:%776=408%:%
-%:%777=409%:%
-%:%778=410%:%
-%:%779=410%:%
-%:%781=410%:%
-%:%785=410%:%
-%:%786=410%:%
+%:%710=379%:%
+%:%712=379%:%
+%:%716=379%:%
+%:%717=379%:%
+%:%719=380%:%
+%:%720=381%:%
+%:%721=382%:%
+%:%722=383%:%
+%:%732=385%:%
+%:%733=386%:%
+%:%734=387%:%
+%:%738=389%:%
+%:%740=391%:%
+%:%741=391%:%
+%:%742=392%:%
+%:%743=393%:%
+%:%744=394%:%
+%:%745=394%:%
+%:%747=394%:%
+%:%751=394%:%
+%:%752=394%:%
+%:%754=395%:%
+%:%755=396%:%
+%:%756=397%:%
+%:%757=398%:%
+%:%767=400%:%
+%:%768=401%:%
+%:%770=403%:%
+%:%771=403%:%
+%:%772=404%:%
+%:%773=405%:%
+%:%774=406%:%
+%:%775=406%:%
+%:%777=406%:%
+%:%781=406%:%
+%:%782=406%:%
+%:%784=407%:%
+%:%785=408%:%
+%:%786=409%:%
+%:%787=410%:%
 %:%788=411%:%
-%:%789=412%:%
-%:%790=413%:%
-%:%791=414%:%
+%:%798=413%:%
+%:%799=414%:%
 %:%801=416%:%
-%:%802=417%:%
-%:%804=419%:%
-%:%805=419%:%
-%:%806=420%:%
-%:%807=421%:%
-%:%808=422%:%
-%:%809=422%:%
-%:%811=422%:%
-%:%815=422%:%
-%:%816=422%:%
-%:%818=423%:%
-%:%819=424%:%
-%:%820=425%:%
-%:%821=426%:%
-%:%822=427%:%
-%:%832=429%:%
-%:%833=430%:%
-%:%835=432%:%
-%:%836=432%:%
-%:%837=433%:%
-%:%838=434%:%
-%:%841=435%:%
-%:%845=435%:%
-%:%846=435%:%
-%:%847=435%:%
+%:%802=416%:%
+%:%803=417%:%
+%:%804=418%:%
+%:%807=419%:%
+%:%811=419%:%
+%:%812=419%:%
+%:%813=419%:%
+%:%822=421%:%
+%:%823=422%:%
+%:%824=423%:%
+%:%825=424%:%
+%:%827=426%:%
+%:%828=426%:%
+%:%829=427%:%
+%:%830=428%:%
+%:%833=429%:%
+%:%837=429%:%
+%:%838=429%:%
+%:%839=429%:%
+%:%848=431%:%
+%:%849=432%:%
+%:%851=434%:%
+%:%852=434%:%
+%:%853=435%:%
+%:%854=436%:%
+%:%855=437%:%
 %:%856=437%:%
-%:%857=438%:%
-%:%858=439%:%
-%:%859=440%:%
-%:%861=442%:%
-%:%862=442%:%
-%:%863=443%:%
-%:%864=444%:%
-%:%867=445%:%
-%:%871=445%:%
-%:%872=445%:%
-%:%873=445%:%
+%:%858=437%:%
+%:%862=437%:%
+%:%863=437%:%
+%:%865=438%:%
+%:%866=439%:%
+%:%867=440%:%
+%:%868=441%:%
+%:%878=443%:%
+%:%879=444%:%
+%:%880=445%:%
+%:%881=446%:%
 %:%882=447%:%
@@
 %:%889=453%:%
-%:%890=453%:%
-%:%892=453%:%
-%:%896=453%:%
-%:%897=453%:%
-%:%899=454%:%
+%:%890=454%:%
+%:%891=454%:%
+%:%893=454%:%
+%:%897=454%:%
+%:%898=454%:%
 %:%900=455%:%
@@
 %:%902=457%:%
-%:%912=459%:%
-%:%913=460%:%
-%:%914=461%:%
+%:%903=458%:%
+%:%904=459%:%
+%:%905=460%:%
 %:%915=462%:%
@@
 %:%917=464%:%
+%:%918=465%:%
 %:%919=466%:%
-%:%920=466%:%
-%:%921=467%:%
-%:%922=468%:%
+%:%920=467%:%
+%:%922=469%:%
 %:%923=469%:%
 %:%924=470%:%
-%:%925=470%:%
-%:%927=470%:%
-%:%931=470%:%
-%:%932=470%:%
-%:%934=471%:%
-%:%935=472%:%
-%:%936=473%:%
-%:%937=474%:%
-%:%938=475%:%
-%:%939=476%:%
-%:%949=478%:%
-%:%950=479%:%
-%:%951=480%:%
-%:%952=481%:%
-%:%953=482%:%
-%:%954=483%:%
-%:%956=485%:%
-%:%957=485%:%
-%:%958=486%:%
-%:%959=487%:%
-%:%962=488%:%
-%:%966=488%:%
-%:%967=488%:%
-%:%969=489%:%
-%:%979=491%:%
-%:%980=492%:%
-%:%981=493%:%
-%:%982=494%:%
-%:%991=496%:%
-%:%1003=498%:%
-%:%1004=499%:%
-%:%1005=500%:%
-%:%1006=501%:%
-%:%1010=503%:%
-%:%1011=504%:%
-%:%1013=506%:%
+%:%925=471%:%
+%:%928=472%:%
+%:%932=472%:%
+%:%933=472%:%
+%:%935=473%:%
+%:%945=475%:%
+%:%946=476%:%
+%:%947=477%:%
+%:%948=478%:%
+%:%957=480%:%
+%:%969=482%:%
+%:%970=483%:%
+%:%971=484%:%
+%:%972=485%:%
+%:%976=487%:%
+%:%977=488%:%
+%:%979=490%:%
+%:%980=490%:%
+%:%981=491%:%
+%:%982=492%:%
+%:%983=492%:%
+%:%984=493%:%
+%:%987=494%:%
+%:%991=494%:%
+%:%992=494%:%
+%:%993=494%:%
+%:%995=495%:%
+%:%996=496%:%
+%:%1006=498%:%
+%:%1007=499%:%
+%:%1008=500%:%
+%:%1009=501%:%
+%:%1010=502%:%
+%:%1011=503%:%
+%:%1012=504%:%
+%:%1013=505%:%
 %:%1014=506%:%
@@
 %:%1016=508%:%
-%:%1017=508%:%
-%:%1018=509%:%
-%:%1021=510%:%
-%:%1025=510%:%
-%:%1026=510%:%
-%:%1027=510%:%
-%:%1029=511%:%
-%:%1030=512%:%
-%:%1040=514%:%
-%:%1041=515%:%
-%:%1042=516%:%
-%:%1043=517%:%
-%:%1044=518%:%
-%:%1045=519%:%
-%:%1046=520%:%
-%:%1047=521%:%
-%:%1048=522%:%
-%:%1049=523%:%
-%:%1050=524%:%
+%:%1017=509%:%
+%:%1018=510%:%
+%:%1019=511%:%
+%:%1020=512%:%
+%:%1022=514%:%
+%:%1023=514%:%
+%:%1024=515%:%
+%:%1025=516%:%
+%:%1026=517%:%
+%:%1027=517%:%
+%:%1029=517%:%
+%:%1033=517%:%
+%:%1034=517%:%
+%:%1036=518%:%
+%:%1037=519%:%
+%:%1038=520%:%
+%:%1039=521%:%
+%:%1040=522%:%
+%:%1041=523%:%
 %:%1051=525%:%
@@
 %:%1054=528%:%
-%:%1056=530%:%
-%:%1057=530%:%
-%:%1058=531%:%
-%:%1059=532%:%
-%:%1060=533%:%
-%:%1061=533%:%
-%:%1063=533%:%
-%:%1067=533%:%
-%:%1068=533%:%
-%:%1070=534%:%
-%:%1071=535%:%
-%:%1072=536%:%
-%:%1073=537%:%
-%:%1074=538%:%
-%:%1075=539%:%
-%:%1085=541%:%
-%:%1086=542%:%
-%:%1087=543%:%
-%:%1088=544%:%
-%:%1092=546%:%
-%:%1093=547%:%
-%:%1094=548%:%
-%:%1096=550%:%
-%:%1097=550%:%
-%:%1098=551%:%
-%:%1099=551%:%
-%:%1101=552%:%
-%:%1102=553%:%
-%:%1103=553%:%
-%:%1104=554%:%
-%:%1105=555%:%
-%:%1106=555%:%
-%:%1107=556%:%
-%:%1110=557%:%
-%:%1114=557%:%
-%:%1115=557%:%
-%:%1117=558%:%
-%:%1118=559%:%
-%:%1119=560%:%
-%:%1129=562%:%
-%:%1130=563%:%
-%:%1131=564%:%
-%:%1132=565%:%
-%:%1134=567%:%
-%:%1135=567%:%
-%:%1136=568%:%
-%:%1138=568%:%
-%:%1142=568%:%
-%:%1143=568%:%
-%:%1145=569%:%
-%:%1153=569%:%
-%:%1154=570%:%
-%:%1155=571%:%
-%:%1156=571%:%
-%:%1157=572%:%
-%:%1159=572%:%
-%:%1163=572%:%
-%:%1164=572%:%
-%:%1166=573%:%
-%:%1176=575%:%
-%:%1177=576%:%
-%:%1178=577%:%
+%:%1058=530%:%
+%:%1059=531%:%
+%:%1060=532%:%
+%:%1062=534%:%
+%:%1063=534%:%
+%:%1064=535%:%
+%:%1065=535%:%
+%:%1067=536%:%
+%:%1068=537%:%
+%:%1069=537%:%
+%:%1070=538%:%
+%:%1071=539%:%
+%:%1072=539%:%
+%:%1073=540%:%
+%:%1076=541%:%
+%:%1080=541%:%
+%:%1081=541%:%
+%:%1083=542%:%
+%:%1084=543%:%
+%:%1085=544%:%
+%:%1095=546%:%
+%:%1096=547%:%
+%:%1097=548%:%
+%:%1098=549%:%
+%:%1100=551%:%
+%:%1101=551%:%
+%:%1102=552%:%
+%:%1104=552%:%
+%:%1108=552%:%
+%:%1109=552%:%
+%:%1111=553%:%
+%:%1119=553%:%
+%:%1120=554%:%
+%:%1121=555%:%
+%:%1122=555%:%
+%:%1123=556%:%
+%:%1125=556%:%
+%:%1129=556%:%
+%:%1130=556%:%
+%:%1132=557%:%
+%:%1142=559%:%
+%:%1143=560%:%
+%:%1144=561%:%

### 2021-09-26 paper/output/document/paper41.tex
added maxim

--- 2021-04-27 paper/output/document/relatedwork.tex
@@
 \begin{isabellebody}%
-\setisabellecontext{relatedwork}%
+\setisabellecontext{paper{\isadigit{4}}{\isadigit{1}}}%
 %
@@
 %
-\isamarkupsection{Related Work%
-}
-\isamarkuptrue%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
 %
@@
 \endisadelimdocument
-%
-\begin{isamarkuptext}%
-In 1685, Leibniz dreamed of a universal calculator that could be used to resolve philosophical 
-and theological disputes. At the time, the logical and computational resources necessary to make his 
-dream a reality did not exist. Today, automated ethics is a growing field, spurred in part by the need for
-ethically intelligent AI agents.
-
-Tolmeijer et al. \cite{mesurvey} develop a taxonomy of implementation of machine ethics. An implementation is characterized
-by (1) the choice of ethical theory, (2) implementation design decisions like testing, and (3) implementation
-details like choice of logic.
-
-In this paper, I formalize Kant's ethical theory. There is a long line of work formalizing other 
-kinds of ethical theories, like consequentialism \cite{util1, util2} or particularism \cite{particularism1, particularism2}. 
-Kantian ethics is a deontological, or rule based ethic, and there is also prior work formalizing deontology \cite{dde, deon1, deon2} more broadly. 
-Kantian ethics specifically appears to be an intuitive candidate for formalization. In 2006, 
-Powers \cite{powers} argued that a formalization of Kantian ethics presented technical challenges,
- such as automation of a non-monotonic logic, and philosophical challenges, like a definition of the 
-categorical imperative. There has also been prior work in formalizing Kantian metaphysics using
- I/O logic \cite{io}. Deontic logic itself is inspired by Kant's ``ought implies can" principle, 
-but it does not include a robust formalization of the entire categorical imperative \cite{cresswell}.
-
-Lindner and Bentzen \cite{BL} have presented a formalization of Kant's second formulation of the categorical 
-imperative using a custom logic. They present their goal as ``not to get close to a correct interpretation
- of Kant, but to show that our interpretation of Kant’s ideas can contribute to the development of 
-machine ethics." My work aims to formalize Kant's ethic as faithfully as possible. I draw on the 
-centuries of work in moral philosophy, as opposed to developing my own ethical theory. I also hope to 
-formalize the first and third formulation of the categorical imperative as well.
-
-The implementation of this paper builds on Benzmueller, Parent, and Farjami's work 
-on the LogiKey framework for machine ethics \cite{BFP, logikey}. The LogiKey project has done a significant 
-amount of formalized metaphysics \cite{godel, metaphysics1}. Fuenmayor and Benzmueller \cite{gewirth} have 
-formalized Gewirth's principle of generic consistency, which is similar to Kant's formula of universal law.%
-\end{isamarkuptext}\isamarkuptrue%
 %
@@
 \endinput
-%:%file=~/Desktop/cs91r/paper/relatedwork.thy%:%
-%:%24=6%:%
-%:%36=8%:%
-%:%37=9%:%
-%:%38=10%:%
-%:%39=11%:%
-%:%40=12%:%
-%:%41=13%:%
-%:%42=14%:%
-%:%43=15%:%
-%:%44=16%:%
-%:%45=17%:%
-%:%46=18%:%
-%:%47=19%:%
-%:%48=20%:%
-%:%49=21%:%
-%:%50=22%:%
-%:%51=23%:%
-%:%52=24%:%
-%:%53=25%:%
-%:%54=26%:%
-%:%55=27%:%
-%:%56=28%:%
-%:%57=29%:%
-%:%58=30%:%
-%:%59=31%:%
-%:%60=32%:%
-%:%61=33%:%
-%:%62=34%:%
-%:%63=35%:%
-%:%64=36%:%
-%:%65=37%:%
+%:%file=~/Desktop/cs91r/paper/paper41.thy%:%

### 2021-09-27 paper/output/document/paper41.tex
some restructuring, added some morethoughts on maxims

@@
 %
+\isamarkupsection{Novel Formalization of the Categorical Imperative%
+}
+\isamarkuptrue%
+%
 \endisatagdocument
@@
 %
+\begin{isamarkuptext}%
+In this section, I present a custom formalization of the categorical imperative, as inspired by 
+the goals from the previous chapter.%
+\end{isamarkuptext}\isamarkuptrue%
+%
 \isadelimdocument
@@
 \isatagdocument
+%
+\isamarkupsubsection{Logical Background%
+}
+\isamarkuptrue%
 %
@@
 \endisadelimdocument
+%
+\begin{isamarkuptext}%
+The previous attempts to model the categorical imperative in Chapter 2 partially failed due to 
+lack of expressivity about the complexity of a maxim. Specifically, they treated actions as a single, 
+monolithic unit of evaluation, whereas most Kantians consider the unit of evaluation for the FUL to the more
+complex notion of a maxim. In this section, I will present some logical background necessarily to more fully 
+capture the spirit of a maxim. I will begin by borrowing some machinery to handle ``subjects" who perform 
+actions from Chapter 2.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{typedecl}\isamarkupfalse%
+\ s\ %
+\isamarkupcmt{s is the type for a ``subject," i.e. the subject of a sentence%
+}\isanewline
+\isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
+\ os\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}s\ {\isasymRightarrow}\ t{\isacharparenright}{\isachardoublequoteclose}\ %
+\isamarkupcmt{Recall that an open sentence maps a subject to a term to model substitution.%
+}\isanewline
+\isanewline
+\isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
+\ maxim\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}t\ {\isacharasterisk}\ os\ {\isacharasterisk}\ t{\isacharparenright}{\isachardoublequoteclose}\ %
+\isamarkupcmt{Korsgaard interprets Kant's idea of a maxim as being equivalent 
+to Aristotle's notion of logos or principle, which is a circumstance, act, goal pair. Read logos (C, A, G)
+as ``In circumstance C, I will do A in order to G." A circumstance is represented as a set of worlds 
+$t$ where that circumstance holds. A goal is a term because it can be true or false at a world if it 
+is realized. An act is an open sentence because, once we substitute an agent in, an act can be true or 
+false at a world if it is actually performed by that subject.
+
+Korsgaard interprets a maxim as being equivalent to a logos, and thus only being composed of the features
+above. Kitcher argues that a maxim should also include the motivation. This additional component is read 
+as ``In circumstance C, I will do A in order to G because of M." where M may be ``duty" or ``self-love."
+This captures Kant's idea that an action derives its moral worth from being done for the sake of duty itself.
+Given that, under the Kantian constituvist view, the categorical
+imperative completely defines duty, Kitcher argues that the FUL would obligate maxims of the form 
+``In circumstance C, I will do A in order to G because I would will that I and everyone else simultaneously
+will do A in order to G in circumstance C." In other words, the affirmative result of the FUL becomes 
+the motivation for a moral action.
+
+While Kitcher's conception of a maxim captures Kant's idea of acting for duty's own sake, I will not implement it 
+because it is not essential to putting maxims through the FUL. 
+Notice that in order to pass the maxim through the FUL, it suffices to know C, A and G. The FUL
+derives the purpose that Kitcher bundles into the maxim, so automating the FUL does not require 
+including some notion of a purpose. The ``input" to the FUL is the (C, A, G) pair. My project takes 
+this input and returns the motivation that the dutiful, moral agent would adopt. Additionally, doing
+justice to the rich notion of motivation requires modelling the operation of practical reason itself, 
+which it outside the scope of this project. My work focuses on the FUL test itself, but future work that 
+models the process of practical reason may use my implementation of the FUL as a ``library." Combined 
+with a logic of practical reason, an implementation of the FUL can move from evaluating a maxim to 
+evaluating an agent's behavior, since that's where ``acting from duty" starts to matter.%
+}\isanewline
+\isanewline
+\isacommand{fun}\isamarkupfalse%
+\ act{\isacharunderscore}on\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim\ {\isasymRightarrow}\ s{\isasymRightarrow}\ \ t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}A\ {\isacharunderscore}\ {\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}act{\isacharunderscore}on\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ {\isacharequal}\ {\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}a\ s{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ %
+\isamarkupcmt{A maxim is acted on by a subject at a world if, when the circumstances hold at that world, the 
+subject performs the action (denoted by the application of the action to the subject). At worlds 
+where the circumstances do not hold, a maxim is trivially acted on. This coheres with Kitcher's and
+ Korsgaard's understanding of a maxim as a principle or rule to live by. If your rule is ``I will 
+do X in these cirumstances", then you are trivillay obeying it when the circumstances don't hold.
+
+The type of a maxim that is acted on is a term, allowing me
+to use DDL's obligation operator on the notion of acting on a maxim. While DDL offers a dyadic obligation
+operator (taking in a term and context as arguments), I will only use the monadic version (only 
+taking in a term), since the act\_on function already excludes worlds where the circumstances do not hold.
+
+Worlds where the circumstances do not hold are not relevant for determining obligation. Recall that in 
+our definition of the obligation operator, we define O {B|A} to be true at all worlds iff ob(B)(A), or 
+if the obligation function maps A to obligatory in context B (where the context is a set of worlds). This 
+definition implies that worlds outside of B have no bearing on the obligatory-ness of A in context B, which 
+coheres with intuitions about obligation in a context. Thus, the dyadic obligation operator 
+disqualifies worlds where the context does not hold, so the trivial truth of the act\_on statement in 
+these worlds does not matter.
+
+Given that the `acted\_on' function already excludes worlds where the circumstances fail (by rendering 
+the statement trivially true at them), one may conclude that the dyadic obligation operator is now useless. 
+Using the dyadic obligation operator allows me to take advantage of the power of DDL to represent the bearing 
+that circumstances have on obligation. DDL has powerful axioms expressing the relationship between circumstances 
+and obligation, such as the fact that obligations are monotonically increasing with respect to broader 
+circumstances. Using the monadic obligation operator would require me to either operate with an empty 
+notion of context or to redefine these axioms. The dyadic obligation operator lets me take advantage of the full 
+power of DDL in expressing contrary-to-duty obligations. This is particularly important for Kantian ethics 
+and the FUL specifically because many critiques of the FUL rely on attention to circumstances (tailoring 
+objection) or lack thereof (ideal theory). This is also an innovation that my custom formalization presents 
+over the prior work. By formally including the notion of a circumstance or context, I am able to represent 
+these objections that Kantian scholars study. Formalizing Kantian ethics in a dyadic deontic logic 
+instead of a monadic deontic logic is a key contribution of this thesis.%
+}\isanewline
+\isanewline
+\isacommand{fun}\isamarkupfalse%
+\ effective\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}\ t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}E\ {\isacharunderscore}\ {\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}effective\ {\isacharparenleft}c{\isacharcolon}{\isacharcolon}t{\isacharcomma}\ a{\isacharcolon}{\isacharcolon}os{\isacharcomma}\ g{\isacharcolon}{\isacharcolon}t{\isacharparenright}\ s\ {\isacharequal}\ {\isacharparenleft}{\isacharparenleft}act{\isacharunderscore}on\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ g{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{A maxim is effective for a subject when, if the subject acts on it then the goal is achieved. 
+A maxim is trivially effective in worlds where the circumstances do not hold or where it is not 
+acted on by the argument above. 
+Open Q: If a maxim is effective for me, is it effective for you? Do we need the subject here?%
+}\isanewline
+\isanewline
 %
@@
 %:%file=~/Desktop/cs91r/paper/paper41.thy%:%
+%:%24=6%:%
+%:%36=8%:%
+%:%37=9%:%
+%:%46=11%:%
+%:%58=13%:%
+%:%59=14%:%
+%:%60=15%:%
+%:%61=16%:%
+%:%62=17%:%
+%:%63=18%:%
+%:%65=20%:%
+%:%66=20%:%
+%:%67=20%:%
+%:%68=20%:%
+%:%69=21%:%
+%:%70=21%:%
+%:%71=21%:%
+%:%72=21%:%
+%:%73=22%:%
+%:%74=23%:%
+%:%75=23%:%
+%:%76=23%:%
+%:%77=24%:%
+%:%78=25%:%
+%:%79=26%:%
+%:%80=27%:%
+%:%81=28%:%
+%:%82=29%:%
+%:%83=30%:%
+%:%84=31%:%
+%:%85=32%:%
+%:%86=33%:%
+%:%87=34%:%
+%:%88=35%:%
+%:%89=36%:%
+%:%90=37%:%
+%:%91=38%:%
+%:%92=39%:%
+%:%93=40%:%
+%:%94=41%:%
+%:%95=42%:%
+%:%96=43%:%
+%:%97=44%:%
+%:%98=45%:%
+%:%99=46%:%
+%:%100=47%:%
+%:%101=48%:%
+%:%102=49%:%
+%:%103=50%:%
+%:%104=50%:%
+%:%105=51%:%
+%:%106=52%:%
+%:%107=52%:%
+%:%108=53%:%
+%:%109=54%:%
+%:%110=54%:%
+%:%111=55%:%
+%:%112=56%:%
+%:%113=57%:%
+%:%114=58%:%
+%:%115=59%:%
+%:%116=60%:%
+%:%117=61%:%
+%:%118=62%:%
+%:%119=63%:%
+%:%120=64%:%
+%:%121=65%:%
+%:%122=66%:%
+%:%123=67%:%
+%:%124=68%:%
+%:%125=69%:%
+%:%126=70%:%
+%:%127=71%:%
+%:%128=72%:%
+%:%129=73%:%
+%:%130=74%:%
+%:%131=75%:%
+%:%132=76%:%
+%:%133=77%:%
+%:%134=78%:%
+%:%135=79%:%
+%:%136=80%:%
+%:%137=81%:%
+%:%138=82%:%
+%:%139=83%:%
+%:%140=84%:%
+%:%141=85%:%
+%:%142=86%:%
+%:%143=87%:%
+%:%144=88%:%
+%:%145=88%:%
+%:%146=89%:%
+%:%148=90%:%
+%:%149=91%:%
+%:%150=92%:%
+%:%151=93%:%
+%:%152=93%:%
+%:%153=94%:%

### 2021-09-28 paper/output/document/paper41.tex
added cites for KG and kitcheR

@@
 \ maxim\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}t\ {\isacharasterisk}\ os\ {\isacharasterisk}\ t{\isacharparenright}{\isachardoublequoteclose}\ %
-\isamarkupcmt{Korsgaard interprets Kant's idea of a maxim as being equivalent 
-to Aristotle's notion of logos or principle, which is a circumstance, act, goal pair. Read logos (C, A, G)
+\isamarkupcmt{Korsgaard \cite{actingforareason} interprets Kant's idea of a maxim as being equivalent 
+to Aristotle's notion of logos or principle (insert cite), which is a circumstance, act, goal pair. Read logos (C, A, G)
 as ``In circumstance C, I will do A in order to G." A circumstance is represented as a set of worlds 
@@
 Korsgaard interprets a maxim as being equivalent to a logos, and thus only being composed of the features
-above. Kitcher argues that a maxim should also include the motivation. This additional component is read 
+above. Kitcher \cite{whatisamaxim} argues that a maxim should also include the motivation. This additional component is read 
 as ``In circumstance C, I will do A in order to G because of M." where M may be ``duty" or ``self-love."

### 2021-09-29 paper/output/document/paper41.tex
ugh effectiveness

@@
 \ %
-\isamarkupcmt{A maxim is acted on by a subject at a world if, when the circumstances hold at that world, the 
+\isamarkupcmt{This should be willed on. is there literature on this discussion?
+
+A maxim is acted on by a subject at a world if, when the circumstances hold at that world, the
 subject performs the action (denoted by the application of the action to the subject). At worlds 
@@
 acted on by the argument above. 
-Open Q: If a maxim is effective for me, is it effective for you? Do we need the subject here?%
-}\isanewline
-\isanewline
+Open Q: If a maxim is effective for me, is it effective for you? Do we need the subject here?
+
+nonexistent is ineffective, no trivial effectiveness in philosophy
+write up language to signal the choices that im making
+3 choice points - what version -> FUL; definition of maxim; and practical contradiction interpretation
+PC view -> circumstances are that everyone does it!!!%
+}%
+\pagebreak
+%
+\begin{isamarkuptext}%
+$\textbf{``Effectiveness" of a Maxim}$%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+I wish to formalize the notion of an ``effective" maxim. Intuitively, a maxim (a rule to 
+perform an act A for goal G) is effective if the act results in the goal. For example, studying hard 
+to get good grades is (sometimes) an effective maxim because the act of studying (sometimes) results in
+ the end of getting good grades. At first glance, it is tempting to represent effectiveness 
+as follows: an act, goal pair ($A, G$) is effective if $A \longrightarrow G$. If $A$ then $G$ implies that 
+$A$ is an effective mechanism for achieving $G$.
+
+Trivial truth is a problem for this interpretation. If act $A$ never happens or 
+is impossible, then, $\forall G$, it is trivially true that $A \longrightarrow G$ (since $\sim A$). This leads to the 
+disturbing conclusion that impossible actions are effective in achieving any goal. While the messiness 
+is familiar to logicians, it has troubling implications for ethics.
+
+One such issue arises from Korsgaard's \cite{KorsgaardFUL} argument that, if an act no longer exists, then it is no 
+longer an effective mechanism for achieving any ends at all. This is a critical part of her interpretation 
+of the formula of universal law\footnote{Korsgaard compares two interpretations of the formula of universal law. 
+Under the logical contradiction view, a maxim is prohibited if, when everyone adopts it, it is logically
+impossible. Under the practical contradiction (PC) view, a maxim is prohibited if, when everyone adopt it, 
+it is no longer effective (the act isn't a means to the goal or end. For cases where universalization 
+renders the action impossible (like lying, since if everyone lies no one would believe each other), both 
+views should prohibit the maxim. For the PC view to prohibit the maxim, the maxim's impossibility must 
+also imply its ineffectiveness.}. Under Korsgaard's interpretation, if 
+studying hard is no longer an existing or possible action  (maybe because of perpetual construction outside my room), 
+then the maxim ``studying hard to get a good grade" is no longer effective. Trivial truth means that the
+initial definition of effectiveness cannot achieve this result.
+
+I could fix this problem by defining effectiveness as an act being existent and 
+also achieving the goal. I could try to model existent as ``possible at some world," therefore using 
+the power of modal logic to represent ideas like possibility. That way, a maxim is effective if (1) 
+the act is possible at some world and (2) in worlds where the act is in fact realized, the goal is also
+realized.
+
+This solution draws a distinction between the notions of possibility (which is a modal
+sentence) and truth or occurrence. Drawing this distinction 
+allows us to preserve the fact that trivial truth does, in some way, make sense. Specifically, in a world 
+where the act is not performed, we still think that the maxim is effective. Its effectiveness hasn't been 
+disproven. Just as all purple elephants can fly, hunting purple elephants is an effective way to make money\footnote{Someone not steeped in logic might not agree here.}.
+
+This solution has two drawbacks. First, it introduces additional logical complexity into the effectiveness
+predicate. This is fine, but may have performance/developer time drawbacks. Ideally, a sentence in simple propositional
+logic could represent effectiveness. Second, more importantly, it doesn't address the idea of ``causality." 
+It might be the case that $A \longrightarrow G$ but $A$ does not cause $G$. For example, maybe eating 
+banana bread is a way to improve my grades because I eat banana bread but also happen to study hard, which 
+is the real cause of my GPA. How can I represent this idea? $A \wedge G$ fails because an act doesn't have to occur to be an effective means to an end 
+(the same reason that preserving trivial truth is nice). $A \longleftrightarrow G$ fails because we can imagine
+there also being some other cause for $G$. I can get good grades by studying hard or by bribing my professor, but
+both of those remain effective methods to achieve goal $G$.
+
+How do I solve this problem? Should I look into logics of causation (I'm sure such things exist)? 
+Should I represent effectiveness as the implication $A \longrightarrow G$ holding at every world? That 
+idea addresses the second challenge about causation vs correlation, since if  $A \longrightarrow G$ in
+every possible world, then $A$ must cause $G$, since any fact noncontingent on $A$ will be false at some 
+possible world. This idea introduces even more logical complexity!%
+\end{isamarkuptext}\isamarkuptrue%
 %
@@
 %:%144=88%:%
-%:%145=88%:%
-%:%146=89%:%
-%:%148=90%:%
-%:%149=91%:%
+%:%145=89%:%
+%:%146=90%:%
+%:%147=90%:%
+%:%148=91%:%
 %:%150=92%:%
 %:%151=93%:%
-%:%152=93%:%
-%:%153=94%:%
+%:%152=94%:%
+%:%153=95%:%
+%:%154=96%:%
+%:%155=97%:%
+%:%156=98%:%
+%:%157=99%:%
+%:%158=100%:%
+%:%160=102%:%
+%:%163=104%:%
+%:%167=106%:%
+%:%168=107%:%
+%:%169=108%:%
+%:%170=109%:%
+%:%171=110%:%
+%:%172=111%:%
+%:%173=112%:%
+%:%174=113%:%
+%:%175=114%:%
+%:%176=115%:%
+%:%177=116%:%
+%:%178=117%:%
+%:%179=118%:%
+%:%180=119%:%
+%:%181=120%:%
+%:%182=121%:%
+%:%183=122%:%
+%:%184=123%:%
+%:%185=124%:%
+%:%186=125%:%
+%:%187=126%:%
+%:%188=127%:%
+%:%189=128%:%
+%:%190=129%:%
+%:%191=130%:%
+%:%192=131%:%
+%:%193=132%:%
+%:%194=133%:%
+%:%195=134%:%
+%:%196=135%:%
+%:%197=136%:%
+%:%198=137%:%
+%:%199=138%:%
+%:%200=139%:%
+%:%201=140%:%
+%:%202=141%:%
+%:%203=142%:%
+%:%204=143%:%
+%:%205=144%:%
+%:%206=145%:%
+%:%207=146%:%
+%:%208=147%:%
+%:%209=148%:%
+%:%210=149%:%
+%:%211=150%:%
+%:%212=151%:%
+%:%213=152%:%
+%:%214=153%:%
+%:%215=154%:%
+%:%216=155%:%
+%:%217=156%:%
+%:%218=157%:%

### 2021-10-01 paper/output/document/paper41.tex
added the oneill stuff

--- 2021-09-27 paper/output/document/paper41.tex
@@
 \ maxim\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}t\ {\isacharasterisk}\ os\ {\isacharasterisk}\ t{\isacharparenright}{\isachardoublequoteclose}\ %
-\isamarkupcmt{Korsgaard interprets Kant's idea of a maxim as being equivalent 
-to Aristotle's notion of logos or principle, which is a circumstance, act, goal pair. Read logos (C, A, G)
-as ``In circumstance C, I will do A in order to G." A circumstance is represented as a set of worlds 
+\isamarkupcmt{I define a maxim as a circumstance, act, goal pair (C, A, G), read 
+as ``In circumstances C, do act A for goal G."  A circumstance is represented as a set of worlds 
 $t$ where that circumstance holds. A goal is a term because it can be true or false at a world if it 
 is realized. An act is an open sentence because, once we substitute an agent in, an act can be true or 
-false at a world if it is actually performed by that subject.
+false at a world if it is actually performed by that subject.%
+}%
+\begin{isamarkuptext}%
+My definition of a maxim is inspired by Onora O'Neill's work on maxims, and I will defend my representation
+below and consider an additional component that Patricia Kitcher \cite{whatisamaxim} argues for.
 
-Korsgaard interprets a maxim as being equivalent to a logos, and thus only being composed of the features
-above. Kitcher argues that a maxim should also include the motivation. This additional component is read 
+$\textbf{O'Niell's Original Schematic and The Role of Practical Judgement}$
+
+O'Neill$\footnote{p. 37}$ \cite{actingonprinciple} presents what Kitcher calls the widely accepted view that a maxim is a circumstance, 
+act, goal tuple as I represented above. She views a maxim as a particular, subjective instantiation of a 
+practical principle, which people may choose to act on or live by. Like a practical principle, a maxim 
+is a kind of action-guiding rule and thus naturally includes an action and the circumstances under which 
+it should be performed, which are often referred to as ``morally relevant circumstances."
+
+She also includes the notion of a maxim's purpose or end (which I call goal) because Kant includes this in many of his 
+example maxims and because Kant argues that human activity, because it is guided by a rational will, 
+is inherently purposive. People do not act randomly, but instead in the pursuit of ends which they 
+deem valuable \cite{sources}$\footnote{where in sources is this discussed}$. This inclusion is also essential 
+for the version of the universalizability test that I will implement, explained in Section ??, so is 
+ultimately uncontroversial.
+
+O'Niell's inclusion of circumstances, on the other hand, is interesting because it leaves open the question of what qualifies as a 
+relevant circumstance for a particular maxim. This is gives rise to ``the tailoring objection" \cite{whatisamaxim}$\footnote{Kitcher
+on p.217 cites Wood p. 102 \cite{kantsethicalthought} as offering an example of a false positive due to this objection.}$, 
+under which maxims are arbitrarily specified to pass the FUL. For example, the maxim ``When my name is Lavanya Singh,
+I will lie to get some easy money," is universalizable, but is clearly a false positive. One solution to 
+this problem is to argue that the circumstance ``When my name is Lavanya Singh" is not relevant 
+to the rest of the maxim. This solution requires some discussion of what qualifies as a relevant circumstance.
+
+O'Niell seems to adopt some version of this view when she concedes that a maxim cannot include ALL 
+the infinitely many circumstances in which the agent may perform the action$\footnote{p. 37}$. She argues that this is 
+an artifact of the fact that maxims are closely related to practical principles. Like any practical rule, 
+maxims require an exercise of judgement to determine in which circumstances they should be applied. 
+This judgement, applied in both choosing to exercise the maxim and in the formulation of the maxim 
+itself, is what determines what qualifies as a ``morally relevant circumstance."
+
+The implication for my project is that the computer cannot perform all ethical activity alone. 
+Human judgement or the exercise of practical reason is essential to both formulate kinds maxims and 
+determine when the actual conditions of life coincide with the circumstances in which the maxim is relevant. 
+The second concern is less relevant to my project because analyzing a formal representation of the FUL requires 
+making the circumstances in a given scenario precise. The first concern, on the other hand, demonstrates 
+the important fact that ethics as presented here is not a solely computational activity. A
+human being must create a representation for the dilemma they wish to test, effectively translating 
+a complex, real situation into a flat logical structure. Not only will some of the situation's complexity
+inevitably be lost, the outcome of the test will determine greatly on how the human formulates the maxim
+and whether or not this formulation does indeed include morally relevant circumstances. If the human puts 
+garbage into the test, the test will surely return garbage out.
+
+While this may appear to be a weakness of my system, I believe that it actually
+allows my system to retain some of the human complexity that many philosophers agree cannot be automated away.\footnote{Powers \cite{powers} presents 
+the determination of morally relevant circumstances as an obstacle to the automation of Kantian ethics.}
+Ethics is a fundamentally human activity. As Korsgaard argues, the categorical imperative is a statement 
+about the properties of rational wills, i.e. our human wills. If ethics is meant to guide human behavior, 
+the role of the computer becomes clear as not a replacement for our will (which is the entire focal point 
+of Kantian ethics), but instead as a tool to help guide our wills and help us reason more efficiently 
+and more effectively. Just as calculators don't render mathematicians obsolete, computational ethics
+does not render human judgement obsolete. Chapter 4 Section ??  will be devoted to a more complete discussion 
+of this issue.
+
+$\textbf{Motive}$
+
+Kitcher \cite{whatisamaxim} begins with O'Niell's (C, A, G) view and expands it to include the motivation 
+behind performing the maxim. This additional component is read 
 as ``In circumstance C, I will do A in order to G because of M." where M may be ``duty" or ``self-love."
@@
 While Kitcher's conception of a maxim captures Kant's idea of acting for duty's own sake, I will not implement it 
-because it is not essential to putting maxims through the FUL. 
+because it is not necessary for putting maxims through the FUL. Indeed, Kitcher acknowledges that 
+O'Niell's formulation suffices for the universalizability test, but is not the general notion of a maxim.
 Notice that in order to pass the maxim through the FUL, it suffices to know C, A and G. The FUL
@@
 evaluating an agent's behavior, since that's where ``acting from duty" starts to matter.%
-}\isanewline
-\isanewline
+\end{isamarkuptext}\isamarkuptrue%
 \isacommand{fun}\isamarkupfalse%
-\ act{\isacharunderscore}on\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim\ {\isasymRightarrow}\ s{\isasymRightarrow}\ \ t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}A\ {\isacharunderscore}\ {\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}act{\isacharunderscore}on\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ {\isacharequal}\ {\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}a\ s{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-\ %
-\isamarkupcmt{A maxim is acted on by a subject at a world if, when the circumstances hold at that world, the 
-subject performs the action (denoted by the application of the action to the subject). At worlds 
-where the circumstances do not hold, a maxim is trivially acted on. This coheres with Kitcher's and
- Korsgaard's understanding of a maxim as a principle or rule to live by. If your rule is ``I will 
-do X in these cirumstances", then you are trivillay obeying it when the circumstances don't hold.
+\ will\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim\ {\isasymRightarrow}\ s{\isasymRightarrow}\ \ t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}A\ {\isacharunderscore}\ {\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}will\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ {\isacharequal}\ {\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}a\ s{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
+\begin{isamarkuptext}%
+Korsgaard claims that ``To will an end, rather than just
+wishing for it or wanting it, is to set yourself to be its cause" \cite{sources}. To will a maxim, then, 
+is to set yourself to, in the relevant circumstances, be the cause of its goal by taking the means 
+specified in the maxim. This coheres with 
+Kitcher's and Korsgaard's understanding of a maxim as a principle or rule to live by. At worlds 
+where the circumstances do not hold, a maxim is vacuously willed. If you decide to act on the rule ``I will 
+do X in these cirumstances", then you are vacuously obeying it when the circumstances don't hold.
 
-The type of a maxim that is acted on is a term, allowing me
-to use DDL's obligation operator on the notion of acting on a maxim. While DDL offers a dyadic obligation
-operator (taking in a term and context as arguments), I will only use the monadic version (only 
-taking in a term), since the act\_on function already excludes worlds where the circumstances do not hold.
+The above discussion implies that willing a maxim is particular to the agent, justifying my choice to 
+require that a particular subject will a maxim. O'Niell argues for this interpretation when she distinguishes 
+between the evaluation of a principle, which is generic, and a maxim, which she views as ``individuated only 
+by referring to a person"$\footnote{p. 13}$ \cite{actingonprinciple}. I adopt the spirit of this interpretation but modify it slightly 
+by representing the general maxim as a principle that anyone could adopt, and the act of willing the maxim 
+as a person-particular instantiation of the maxim.
+
+I additionally represent a subject as willing a maxim because I use the word `will' as a verb, to mean committing oneself to living by
+the principle of a maxim. This coheres with Kant's Formula of Universal Law, because it tests the willing 
+of a maxim to determine if it could be a universal law that everyone committed to. Formalizing this idea,
+the type of a maxim that is willed is a term, allowing me
+to use DDL's obligation operator on the notion of willing a maxim.
 
 Worlds where the circumstances do not hold are not relevant for determining obligation. Recall that in 
-our definition of the obligation operator, we define O {B|A} to be true at all worlds iff ob(B)(A), or 
+our definition of the obligation operator, we define $O \{B|A\}$ to be true at all worlds iff ob(B)(A), or 
 if the obligation function maps A to obligatory in context B (where the context is a set of worlds). This 
@@
 coheres with intuitions about obligation in a context. Thus, the dyadic obligation operator 
-disqualifies worlds where the context does not hold, so the trivial truth of the act\_on statement in 
+disqualifies worlds where the context does not hold, so the vacuous truth of the will statement in 
 these worlds does not matter.
 
-Given that the `acted\_on' function already excludes worlds where the circumstances fail (by rendering 
-the statement trivially true at them), one may conclude that the dyadic obligation operator is now useless. 
+Given that the will function already excludes worlds where the circumstances fail (by rendering 
+the statement vacuously true at them), one may conclude that the dyadic obligation operator is now useless. 
 Using the dyadic obligation operator allows me to take advantage of the power of DDL to represent the bearing 
@@
 instead of a monadic deontic logic is a key contribution of this thesis.%
-}\isanewline
-\isanewline
+\end{isamarkuptext}\isamarkuptrue%
 \isacommand{fun}\isamarkupfalse%
 \ effective\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}\ t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}E\ {\isacharunderscore}\ {\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}effective\ {\isacharparenleft}c{\isacharcolon}{\isacharcolon}t{\isacharcomma}\ a{\isacharcolon}{\isacharcolon}os{\isacharcomma}\ g{\isacharcolon}{\isacharcolon}t{\isacharparenright}\ s\ {\isacharequal}\ {\isacharparenleft}{\isacharparenleft}act{\isacharunderscore}on\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ g{\isacharparenright}{\isachardoublequoteclose}\isanewline
-%
-\isamarkupcmt{A maxim is effective for a subject when, if the subject acts on it then the goal is achieved. 
-A maxim is trivially effective in worlds where the circumstances do not hold or where it is not 
-acted on by the argument above. 
-Open Q: If a maxim is effective for me, is it effective for you? Do we need the subject here?%
-}\isanewline
-\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}effective\ {\isacharparenleft}c{\isacharcolon}{\isacharcolon}t{\isacharcomma}\ a{\isacharcolon}{\isacharcolon}os{\isacharcomma}\ g{\isacharcolon}{\isacharcolon}t{\isacharparenright}\ s\ {\isacharequal}\ {\isacharparenleft}{\isacharparenleft}will\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ \isactrlbold {\isasymequiv}\ g{\isacharparenright}{\isachardoublequoteclose}%
+\begin{isamarkuptext}%
+A maxim is effective for a subject when, if the subject wills it then the goal is achieved, and
+when the subject does not act on it, the goal is not achieved.$\footnote{Thank you to Jeremy D. Zucker for helping me think through this.}$ \cite{sepcausation} 
+The former direction of the implication 
+is intuitive: if the act results in the goal, it was effective in causing the goal. This represents `necessary'
+causality.
+
+The latter direction represents `sufficient' causality, or the idea that, counterfactually,
+if the maxim were not willed, then the goal is not achieved \cite{lewiscausality}. Note that nothing else changes about this
+counterfactual world—the circumstances are identical and we neither added additional theorems nor 
+specified the model any further. This represents Lewis's idea of "comparative similarity," \cite{lewiscounterfactuals} where 
+a counterfactual is true if it holds at the most similar world. In our case, this is just the world 
+where everything is the same except the maxim is not acted on.
+
+Combining these ideas, this definition of effective states that a maxim is effective if the 
+maxim being acted on by a subject is the necessary and sufficient cause of the goal.\footnote{Should I wave a hand at critiques of counterfactual causality?}
+
+If the circumstances do not hold and the goal is achieved, then the maxim is vacuously effective, since 
+it is vacuously willed (as described above). While this scenario is counterintuitive, it is not very 
+interesting for my purposes because, when the circumstances do not hold, a maxim is not applicable. It 
+doesn't really make sense to evaluate a maxim when it's not supposed to be applied. The maxim ``When on Jupiter,
+read a book to one-up your nemesis" is vacuously effective because it can never be disproven.%
+\end{isamarkuptext}\isamarkuptrue%
 %
@@
 %:%80=27%:%
-%:%81=28%:%
-%:%82=29%:%
-%:%83=30%:%
-%:%84=31%:%
-%:%85=32%:%
-%:%86=33%:%
-%:%87=34%:%
-%:%88=35%:%
-%:%89=36%:%
-%:%90=37%:%
-%:%91=38%:%
-%:%92=39%:%
-%:%93=40%:%
-%:%94=41%:%
-%:%95=42%:%
-%:%96=43%:%
-%:%97=44%:%
-%:%98=45%:%
-%:%99=46%:%
-%:%100=47%:%
-%:%101=48%:%
-%:%102=49%:%
-%:%103=50%:%
+%:%83=29%:%
+%:%84=30%:%
+%:%85=31%:%
+%:%86=32%:%
+%:%87=33%:%
+%:%88=34%:%
+%:%89=35%:%
+%:%90=36%:%
+%:%91=37%:%
+%:%92=38%:%
+%:%93=39%:%
+%:%94=40%:%
+%:%95=41%:%
+%:%96=42%:%
+%:%97=43%:%
+%:%98=44%:%
+%:%99=45%:%
+%:%100=46%:%
+%:%101=47%:%
+%:%102=48%:%
+%:%103=49%:%
 %:%104=50%:%
@@
 %:%106=52%:%
-%:%107=52%:%
-%:%108=53%:%
-%:%109=54%:%
-%:%110=54%:%
-%:%111=55%:%
-%:%112=56%:%
-%:%113=57%:%
-%:%114=58%:%
-%:%115=59%:%
-%:%116=60%:%
-%:%117=61%:%
-%:%118=62%:%
-%:%119=63%:%
-%:%120=64%:%
-%:%121=65%:%
-%:%122=66%:%
-%:%123=67%:%
-%:%124=68%:%
-%:%125=69%:%
-%:%126=70%:%
-%:%127=71%:%
-%:%128=72%:%
-%:%129=73%:%
-%:%130=74%:%
-%:%131=75%:%
-%:%132=76%:%
-%:%133=77%:%
-%:%134=78%:%
-%:%135=79%:%
-%:%136=80%:%
-%:%137=81%:%
-%:%138=82%:%
-%:%139=83%:%
-%:%140=84%:%
-%:%141=85%:%
-%:%142=86%:%
-%:%143=87%:%
-%:%144=88%:%
-%:%145=88%:%
-%:%146=89%:%
-%:%148=90%:%
-%:%149=91%:%
-%:%150=92%:%
-%:%151=93%:%
-%:%152=93%:%
-%:%153=94%:%
+%:%107=53%:%
+%:%108=54%:%
+%:%109=55%:%
+%:%110=56%:%
+%:%111=57%:%
+%:%112=58%:%
+%:%113=59%:%
+%:%114=60%:%
+%:%115=61%:%
+%:%116=62%:%
+%:%117=63%:%
+%:%118=64%:%
+%:%119=65%:%
+%:%120=66%:%
+%:%121=67%:%
+%:%122=68%:%
+%:%123=69%:%
+%:%124=70%:%
+%:%125=71%:%
+%:%126=72%:%
+%:%127=73%:%
+%:%128=74%:%
+%:%129=75%:%
+%:%130=76%:%
+%:%131=77%:%
+%:%132=78%:%
+%:%133=79%:%
+%:%134=80%:%
+%:%135=81%:%
+%:%136=82%:%
+%:%137=83%:%
+%:%138=84%:%
+%:%139=85%:%
+%:%140=86%:%
+%:%141=87%:%
+%:%142=88%:%
+%:%143=89%:%
+%:%144=90%:%
+%:%145=91%:%
+%:%146=92%:%
+%:%147=93%:%
+%:%148=94%:%
+%:%149=95%:%
+%:%150=96%:%
+%:%151=97%:%
+%:%152=98%:%
+%:%153=99%:%
+%:%154=100%:%
+%:%155=101%:%
+%:%156=102%:%
+%:%157=103%:%
+%:%158=104%:%
+%:%159=105%:%
+%:%160=106%:%
+%:%161=107%:%
+%:%162=108%:%
+%:%164=110%:%
+%:%165=110%:%
+%:%166=111%:%
+%:%168=113%:%
+%:%169=114%:%
+%:%170=115%:%
+%:%171=116%:%
+%:%172=117%:%
+%:%173=118%:%
+%:%174=119%:%
+%:%175=120%:%
+%:%176=121%:%
+%:%177=122%:%
+%:%178=123%:%
+%:%179=124%:%
+%:%180=125%:%
+%:%181=126%:%
+%:%182=127%:%
+%:%183=128%:%
+%:%184=129%:%
+%:%185=130%:%
+%:%186=131%:%
+%:%187=132%:%
+%:%188=133%:%
+%:%189=134%:%
+%:%190=135%:%
+%:%191=136%:%
+%:%192=137%:%
+%:%193=138%:%
+%:%194=139%:%
+%:%195=140%:%
+%:%196=141%:%
+%:%197=142%:%
+%:%198=143%:%
+%:%199=144%:%
+%:%200=145%:%
+%:%201=146%:%
+%:%202=147%:%
+%:%203=148%:%
+%:%204=149%:%
+%:%205=150%:%
+%:%206=151%:%
+%:%207=152%:%
+%:%208=153%:%
+%:%209=154%:%
+%:%211=157%:%
+%:%212=157%:%
+%:%213=158%:%
+%:%215=160%:%
+%:%216=161%:%
+%:%217=162%:%
+%:%218=163%:%
+%:%219=164%:%
+%:%220=165%:%
+%:%221=166%:%
+%:%222=167%:%
+%:%223=168%:%
+%:%224=169%:%
+%:%225=170%:%
+%:%226=171%:%
+%:%227=172%:%
+%:%228=173%:%
+%:%229=174%:%
+%:%230=175%:%
+%:%231=176%:%
+%:%232=177%:%
+%:%233=178%:%
+%:%234=179%:%
+%:%235=180%:%

### 2021-10-03 paper/output/document/paper41.tex
writing on three flags

@@
 \ maxim\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}t\ {\isacharasterisk}\ os\ {\isacharasterisk}\ t{\isacharparenright}{\isachardoublequoteclose}\ %
-\isamarkupcmt{I define a maxim as a circumstance, act, goal pair (C, A, G), read 
-as ``In circumstances C, do act A for goal G."  A circumstance is represented as a set of worlds 
-$t$ where that circumstance holds. A goal is a term because it can be true or false at a world if it 
-is realized. An act is an open sentence because, once we substitute an agent in, an act can be true or 
-false at a world if it is actually performed by that subject.%
+\isamarkupcmt{I define a maxim as a circumstance, act, goal tuple (C, A, G), read 
+as ``In circumstances C, act A for goal G." Isabelle's strict typing rules mean that the choice of the 
+type of each member of this tuple is significant. A circumstance is represented as a set of worlds 
+$t$ where that circumstance holds. A goal is also a term because it can be true or false at a world if it 
+is realized or not. An act is an open sentence because an act itself is not the kind of thing that can 
+be true or false (as in, an act is not truth-apt), but the combination of a subject performing an act 
+can be true or false at a world depending on whether or not the act is indeed performed by that subject. 
+For example, ``running" is not truth-apt, but ``Sara runs" is truth-apt.%
 }%
 \begin{isamarkuptext}%
-My definition of a maxim is inspired by Onora O'Neill's work on maxims, and I will defend my representation
-below and consider an additional component that Patricia Kitcher \cite{whatisamaxim} argues for.
+I define a maxim as a circumstance, act, goal tuple (C, A, G), read 
+as ``In circumstances C, act A for goal G." Isabelle's strict typing rules mean that the choice of the 
+type of each member of this tuple is significant. A circumstance is represented as a set of worlds 
+$t$ where that circumstance holds. A goal is also a term because it can be true or false at a world if it 
+is realized or not. An act is an open sentence because an act itself is not the kind of thing that can 
+be true or false (as in, an act is not truth-apt), but the combination of a subject performing an act 
+can be true or false at a world depending on whether or not the act is indeed performed by that subject. 
+For example, ``running" is not truth-apt, but ``Sara runs" is truth-apt.
 
-$\textbf{O'Niell's Original Schematic and The Role of Practical Judgement}$
+My definition of a maxim is inspired by Onora O'Neill's work on maxims. I will defend my representation
+below and consider an additional component that Patricia Kitcher argues for.
 
-O'Neill$\footnote{p. 37}$ \cite{actingonprinciple} presents what Kitcher calls the widely accepted view that a maxim is a circumstance, 
-act, goal tuple as I represented above. She views a maxim as a particular, subjective instantiation of a 
-practical principle, which people may choose to act on or live by. Like a practical principle, a maxim 
-is a kind of action-guiding rule and thus naturally includes an action and the circumstances under which 
+$\emph{O'Niell's Original Schematic and The Role of Practical Judgement}$
+
+O'Neill$\footnote{p. 37}$ \cite{actingonprinciple} presents what Kitcher \cite{whatisamaxim}  calls the widely accepted 
+view that a maxim is a circumstance, act, goal tuple. A maxim 
+is an action-guiding rule and thus naturally includes an act and the circumstances under which 
 it should be performed, which are often referred to as ``morally relevant circumstances."
 
-She also includes the notion of a maxim's purpose or end (which I call goal) because Kant includes this in many of his 
+She also includes a purpose, end, or goal in the maxim because Kant includes this in many of his 
 example maxims and because Kant argues that human activity, because it is guided by a rational will, 
-is inherently purposive. People do not act randomly, but instead in the pursuit of ends which they 
-deem valuable \cite{sources}$\footnote{where in sources is this discussed}$. This inclusion is also essential 
-for the version of the universalizability test that I will implement, explained in Section ??, so is 
-ultimately uncontroversial.
+is inherently purposive\cite{groundwork}\footnote{(G 4:428)}. A rational will does not act randomly (else it would not be rational), 
+but instead in the pursuit of ends which it deems valuable. This inclusion is also essential for the version of the universalizability test 
+that I will implement, explained in Section ??.
 
-O'Niell's inclusion of circumstances, on the other hand, is interesting because it leaves open the question of what qualifies as a 
+O'Neill's inclusion of circumstances is potentially controversial because it leaves open the question of what qualifies as a 
 relevant circumstance for a particular maxim. This is gives rise to ``the tailoring objection" \cite{whatisamaxim}$\footnote{Kitcher
@@
 I will lie to get some easy money," is universalizable, but is clearly a false positive. One solution to 
-this problem is to argue that the circumstance ``When my name is Lavanya Singh" is not relevant 
-to the rest of the maxim. This solution requires some discussion of what qualifies as a relevant circumstance.
+this problem is to argue that the circumstance ``When my name is Lavanya Singh" is not morally relevant 
+to the act and goal. This solution requires some discussion of what qualifies as a relevant circumstance.
 
-O'Niell seems to adopt some version of this view when she concedes that a maxim cannot include ALL 
-the infinitely many circumstances in which the agent may perform the action$\footnote{p. 37}$. She argues that this is 
-an artifact of the fact that maxims are closely related to practical principles. Like any practical rule, 
-maxims require an exercise of judgement to determine in which circumstances they should be applied. 
-This judgement, applied in both choosing to exercise the maxim and in the formulation of the maxim 
-itself, is what determines what qualifies as a ``morally relevant circumstance."
+O'Neill seems to acknowledge the difficult of determining relevant circumstances when she concedes that a maxim cannot include all 
+of the infinitely many circumstances in which the agent may perform the action$\footnote{p. 37}$. She argues that this is 
+an artifact of the fact that maxims are rules of practical reason, the kind of reason that helps us decide what to do 
+and how to do it \cite{bok}. Like any practical rule, 
+maxims require the exercise of practical judgement to determine in which circumstances they should be applied. 
+This judgement, applied in both choosing when to exercise the maxim and in the formulation of the maxim 
+itself, is what determines the ``morally relevant circumstances."
 
-The implication for my project is that the computer cannot perform all ethical activity alone. 
-Human judgement or the exercise of practical reason is essential to both formulate kinds maxims and 
+The upshot for computational ethics is that the computer cannot perform all ethical activity alone. 
+Human judgement and the exercise of practical reason are essential to both formulate maxims and 
 determine when the actual conditions of life coincide with the circumstances in which the maxim is relevant. 
-The second concern is less relevant to my project because analyzing a formal representation of the FUL requires 
-making the circumstances in a given scenario precise. The first concern, on the other hand, demonstrates 
-the important fact that ethics as presented here is not a solely computational activity. A
+Choosing when to exercise a maxim is less relevant to my project because analyzing a formal representation of the FUL requires 
+making the circumstances in a given scenario precise, but will be important for applications of 
+computational ethics to guiding AI agents. The difficulty in formulating a maxim, on the other hand, demonstrates 
+the important fact that ethics, as presented here, is not a solely computational activity. A
 human being must create a representation for the dilemma they wish to test, effectively translating 
-a complex, real situation into a flat logical structure. Not only will some of the situation's complexity
-inevitably be lost, the outcome of the test will determine greatly on how the human formulates the maxim
+a complex, real situation into a flat logical structure. This parallels the challenge that programmers 
+face when translating the complexity of reality to a programming langauge or computational representation. Not only will some of the situation's complexity
+inevitably be lost, the outcome of the universalizability test will depend on how the human formulates the maxim
 and whether or not this formulation does indeed include morally relevant circumstances. If the human puts 
-garbage into the test, the test will surely return garbage out.
+garbage into the test, the test will return garbage out.
 
@@
 the determination of morally relevant circumstances as an obstacle to the automation of Kantian ethics.}
-Ethics is a fundamentally human activity. As Korsgaard argues, the categorical imperative is a statement 
-about the properties of rational wills, i.e. our human wills. If ethics is meant to guide human behavior, 
-the role of the computer becomes clear as not a replacement for our will (which is the entire focal point 
-of Kantian ethics), but instead as a tool to help guide our wills and help us reason more efficiently 
+Ethics is a fundamentally human activity. Kant argues that the categorical imperative is a statement 
+about the properties of rational wills. In fact, Korsgaard argues that morality derives its authority over us, 
+or normativity, only because is it a property of a rational will, and we, as human beings, are rational wills.
+If ethics is meant to guide human behavior, the role of the computer becomes clear as not a replacement for our will,
+but instead as a tool to help guide our wills and reason more efficiently 
 and more effectively. Just as calculators don't render mathematicians obsolete, computational ethics
-does not render human judgement obsolete. Chapter 4 Section ??  will be devoted to a more complete discussion 
+does not render human judgement or philosophy obsolete. Chapter 4 Section ?? will be devoted to a more complete discussion 
 of this issue.
 
-$\textbf{Motive}$
+$\emph{Exclusion of Motive}$
 
-Kitcher \cite{whatisamaxim} begins with O'Niell's (C, A, G) view and expands it to include the motivation 
+Kitcher \cite{whatisamaxim} begins with O'Niell's circumstance, act, goal view and expands it to include the motive 
 behind performing the maxim. This additional component is read 
-as ``In circumstance C, I will do A in order to G because of M." where M may be ``duty" or ``self-love."
-This captures Kant's idea that an action derives its moral worth from being done for the sake of duty itself.
-Given that, under the Kantian constituvist view, the categorical
-imperative completely defines duty, Kitcher argues that the FUL would obligate maxims of the form 
-``In circumstance C, I will do A in order to G because I would will that I and everyone else simultaneously
-will do A in order to G in circumstance C." In other words, the affirmative result of the FUL becomes 
-the motivation for a moral action.
+as ``In circumstance C, I will do A in order to G because of M," where M may be ``duty" or ``self-love."
+Kitcher argues that the inclusion of motive is necessary for the fullest, most general form of a maxim
+in order to capture Kant's idea that an action derives its moral worth from being done for the sake of duty itself.
+Under this view, the FUL would obligate maxims of the form 
+``In circumstance C, I will do A in order to G because I can will that I and everyone else simultaneously
+will do A in order to G in circumstance C." In other words, if Kant is correct in arguing that moral 
+actions must be done from the motive of duty, the affirmative result of the FUL becomes 
+the motive for a moral action.
 
@@
 because it is not necessary for putting maxims through the FUL. Indeed, Kitcher acknowledges that 
-O'Niell's formulation suffices for the universalizability test, but is not the general notion of a maxim.
-Notice that in order to pass the maxim through the FUL, it suffices to know C, A and G. The FUL
-derives the purpose that Kitcher bundles into the maxim, so automating the FUL does not require 
-including some notion of a purpose. The ``input" to the FUL is the (C, A, G) pair. My project takes 
+O'Neill's formulation suffices for the universalizability test, but is not the general notion of a maxim.
+In order to pass the maxim through the FUL, it suffices to know the circumstance, act, and goal. The FUL
+derives the motive that Kitcher bundles into the maxim, so automating the FUL does not require 
+including a motive. The ``input" to the FUL is the circumstance, act, goal pair. My project takes 
 this input and returns the motivation that the dutiful, moral agent would adopt. Additionally, doing
-justice to the rich notion of motivation requires modelling the operation of practical reason itself, 
-which it outside the scope of this project. My work focuses on the FUL test itself, but future work that 
+justice to the rich notion of motive requires modelling the operation of practical reason itself, 
+which is outside the scope of this project. My work focuses on the universalizability test, but future work that 
 models the process of practical reason may use my implementation of the FUL as a ``library." Combined 
 with a logic of practical reason, an implementation of the FUL can move from evaluating a maxim to 
-evaluating an agent's behavior, since that's where ``acting from duty" starts to matter.%
+evaluating an agent's behavior, since that's when ``acting from duty" starts to matter.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-Korsgaard claims that ``To will an end, rather than just
+Korsgaard claims that ``to will an end, rather than just
 wishing for it or wanting it, is to set yourself to be its cause" \cite{sources}. To will a maxim, then, 
@@
 The above discussion implies that willing a maxim is particular to the agent, justifying my choice to 
-require that a particular subject will a maxim. O'Niell argues for this interpretation when she distinguishes 
+require that a particular subject will a maxim. O'Neill argues for this interpretation when she distinguishes 
 between the evaluation of a principle, which is generic, and a maxim, which she views as ``individuated only 
@@
 %:%80=27%:%
-%:%83=29%:%
-%:%84=30%:%
-%:%85=31%:%
+%:%81=28%:%
+%:%82=29%:%
+%:%83=30%:%
 %:%86=32%:%
@@
 %:%162=108%:%
+%:%163=109%:%
 %:%164=110%:%
-%:%165=110%:%
-%:%166=111%:%
-%:%168=113%:%
-%:%169=114%:%
-%:%170=115%:%
-%:%171=116%:%
-%:%172=117%:%
-%:%173=118%:%
-%:%174=119%:%
-%:%175=120%:%
-%:%176=121%:%
-%:%177=122%:%
-%:%178=123%:%
-%:%179=124%:%
+%:%165=111%:%
+%:%166=112%:%
+%:%167=113%:%
+%:%168=114%:%
+%:%169=115%:%
+%:%170=116%:%
+%:%171=117%:%
+%:%172=118%:%
+%:%173=119%:%
+%:%174=120%:%
+%:%175=121%:%
+%:%176=122%:%
+%:%177=123%:%
+%:%179=125%:%
 %:%180=125%:%
 %:%181=126%:%
-%:%182=127%:%
 %:%183=128%:%
@@
 %:%209=154%:%
-%:%211=157%:%
+%:%210=155%:%
+%:%211=156%:%
 %:%212=157%:%
 %:%213=158%:%
+%:%214=159%:%
 %:%215=160%:%
@@
 %:%224=169%:%
-%:%225=170%:%
-%:%226=171%:%
+%:%226=172%:%
 %:%227=172%:%
 %:%228=173%:%
-%:%229=174%:%
 %:%230=175%:%
@@
 %:%235=180%:%
+%:%236=181%:%
+%:%237=182%:%
+%:%238=183%:%
+%:%239=184%:%
+%:%240=185%:%
+%:%241=186%:%
+%:%242=187%:%
+%:%243=188%:%
+%:%244=189%:%
+%:%245=190%:%
+%:%246=191%:%
+%:%247=192%:%
+%:%248=193%:%
+%:%249=194%:%
+%:%250=195%:%

### 2021-10-03 paper/output/document/threeflags.tex
writing on three flags

--- 2021-10-03 paper/output/document/paper41.tex
@@
 \begin{isabellebody}%
-\setisabellecontext{paper{\isadigit{4}}{\isadigit{1}}}%
+\setisabellecontext{threeflags}%
 %
@@
 %
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\isatagdocument
-%
-\isamarkupsection{Novel Formalization of the Categorical Imperative%
-}
-\isamarkuptrue%
-%
-\endisatagdocument
-{\isafolddocument}%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
 \begin{isamarkuptext}%
-In this section, I present a custom formalization of the categorical imperative, as inspired by 
-the goals from the previous chapter.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\isatagdocument
-%
-\isamarkupsubsection{Logical Background%
-}
-\isamarkuptrue%
-%
-\endisatagdocument
-{\isafolddocument}%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\begin{isamarkuptext}%
-The previous attempts to model the categorical imperative in Chapter 2 partially failed due to 
-lack of expressivity about the complexity of a maxim. Specifically, they treated actions as a single, 
-monolithic unit of evaluation, whereas most Kantians consider the unit of evaluation for the FUL to the more
-complex notion of a maxim. In this section, I will present some logical background necessarily to more fully 
-capture the spirit of a maxim. I will begin by borrowing some machinery to handle ``subjects" who perform 
-actions from Chapter 2.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{typedecl}\isamarkupfalse%
-\ s\ %
-\isamarkupcmt{s is the type for a ``subject," i.e. the subject of a sentence%
-}\isanewline
-\isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
-\ os\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}s\ {\isasymRightarrow}\ t{\isacharparenright}{\isachardoublequoteclose}\ %
-\isamarkupcmt{Recall that an open sentence maps a subject to a term to model substitution.%
-}\isanewline
-\isanewline
-\isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
-\ maxim\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}t\ {\isacharasterisk}\ os\ {\isacharasterisk}\ t{\isacharparenright}{\isachardoublequoteclose}\ %
-\isamarkupcmt{I define a maxim as a circumstance, act, goal tuple (C, A, G), read 
-as ``In circumstances C, act A for goal G." Isabelle's strict typing rules mean that the choice of the 
-type of each member of this tuple is significant. A circumstance is represented as a set of worlds 
-$t$ where that circumstance holds. A goal is also a term because it can be true or false at a world if it 
-is realized or not. An act is an open sentence because an act itself is not the kind of thing that can 
-be true or false (as in, an act is not truth-apt), but the combination of a subject performing an act 
-can be true or false at a world depending on whether or not the act is indeed performed by that subject. 
-For example, ``running" is not truth-apt, but ``Sara runs" is truth-apt.%
-}%
-\begin{isamarkuptext}%
+The literature on Kantian ethics is expansive and complicated. To focus my thesis on the contributions 
+of automated ethics to Kantian thought, I make the following choices.
+
+$\textbf{Choice to Formalize the FUL}$
+
+I am only studying formalizations of Kant's first formulation of the categorical imperative,
+the formula of universal law (FUL), because it is the most formal and thus the easiest to formalize and implement. 
+Onora O'Neill \cite{actingonprinciple}\footnote{p. 33} explains that the formalism of the FUL allows 
+for greater precision in philosophical arguments analyzing its implications and power. This precision 
+is particularly useful in a computational context because any formalism necessarily makes its content 
+precise. The FUL's existing precision reduces ambiguity, allowing me to remain faithful to Kant's writing and 
+philosophical interpretations of it. Precision reduces the need to make choices to resolve debates 
+and ambiguities. Some of these choices may be well-studied and grounded in literature, 
+but some may be unique to formalizing the FUL and thus understudied. Minimizing these choices minimizes 
+arbitrariness in my formalization and puts it on solid philosophical footing. Given that this thesis is a proof-of-concept, 
+the formalism of the FUL is attractive because it reduces both the computational and philosophical complexity of my work.
+
+While some criticize the FUL for its formalism and percieved ``sterility" \cite{actingonprinciple}, 
+Kantian constructivists embrace it. My project is not committed to Kantian constructivism; I argue that computational
+ethics is a valuable tool for any ethicist, with a focus on general Kantian ethics. Nonetheless, Kantian constructivists may find the focus on 
+the FUL particularly appealing.
+
+Though Kantians study all formulations of the categorical imperative, Kant argues in Groundwork 
+that the three formulations of the categorical imperative are equivalent \cite{groundwork}. While this 
+argument is disputed \cite{sepkant}, for those who believe it, the
+stakes for my choice of the FUL are greatly reduced. If all formulations are equivalent, then a formalization of the FUL
+lends the exact same power as a formalization of the second or third formulation of the categorical 
+imperative. In fact, future work could formalize the other formulas and try to prove that they 
+are identical. Kant believes that his argument for the equality of the formulas is analytical, and
+if he is correct, it should be possible to recreate the argument in logic.
+
+$\textbf{Definition of a Maxim}$
+
 I define a maxim as a circumstance, act, goal tuple (C, A, G), read 
@@
 with a logic of practical reason, an implementation of the FUL can move from evaluating a maxim to 
-evaluating an agent's behavior, since that's when ``acting from duty" starts to matter.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{fun}\isamarkupfalse%
-\ will\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim\ {\isasymRightarrow}\ s{\isasymRightarrow}\ \ t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}A\ {\isacharunderscore}\ {\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}will\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ {\isacharequal}\ {\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}a\ s{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
-\begin{isamarkuptext}%
-Korsgaard claims that ``to will an end, rather than just
-wishing for it or wanting it, is to set yourself to be its cause" \cite{sources}. To will a maxim, then, 
-is to set yourself to, in the relevant circumstances, be the cause of its goal by taking the means 
-specified in the maxim. This coheres with 
-Kitcher's and Korsgaard's understanding of a maxim as a principle or rule to live by. At worlds 
-where the circumstances do not hold, a maxim is vacuously willed. If you decide to act on the rule ``I will 
-do X in these cirumstances", then you are vacuously obeying it when the circumstances don't hold.
+evaluating an agent's behavior, since that's when ``acting from duty" starts to matter.
 
-The above discussion implies that willing a maxim is particular to the agent, justifying my choice to 
-require that a particular subject will a maxim. O'Neill argues for this interpretation when she distinguishes 
-between the evaluation of a principle, which is generic, and a maxim, which she views as ``individuated only 
-by referring to a person"$\footnote{p. 13}$ \cite{actingonprinciple}. I adopt the spirit of this interpretation but modify it slightly 
-by representing the general maxim as a principle that anyone could adopt, and the act of willing the maxim 
-as a person-particular instantiation of the maxim.
+$\textbf{Practical Contradiction Interpretation}$
 
-I additionally represent a subject as willing a maxim because I use the word `will' as a verb, to mean committing oneself to living by
-the principle of a maxim. This coheres with Kant's Formula of Universal Law, because it tests the willing 
-of a maxim to determine if it could be a universal law that everyone committed to. Formalizing this idea,
-the type of a maxim that is willed is a term, allowing me
-to use DDL's obligation operator on the notion of willing a maxim.
+Kantians debate the correct interpretation of the formula of universal law because Kant, 
+at times, appears to interpret the universalizability test in different ways. My project uses Korsgaard's practical contradiction 
+interpretation, broadly accepted as correct within the philosophical community \cite{ebelsduggan}\footnote{p. 177}.
+Below, I briefly reconstruct Korsgaard's argument for the practical contradiction interpretation. While 
+she believes that the text partially supports this interpretation, her argument is philosophical and 
+derives its strength from the plausibility of the practical contradiction interpretation.
 
-Worlds where the circumstances do not hold are not relevant for determining obligation. Recall that in 
-our definition of the obligation operator, we define $O \{B|A\}$ to be true at all worlds iff ob(B)(A), or 
-if the obligation function maps A to obligatory in context B (where the context is a set of worlds). This 
-definition implies that worlds outside of B have no bearing on the obligatory-ness of A in context B, which 
-coheres with intuitions about obligation in a context. Thus, the dyadic obligation operator 
-disqualifies worlds where the context does not hold, so the vacuous truth of the will statement in 
-these worlds does not matter.
+Recall that the formula of universal law is “act only in accordance with that maxim through which you can at the 
+same time will that it become a universal law” \cite{groundwork}\footnote{(G: 4:421)}. To determine if a maxim can be willed as a 
+universal law, one must use the “universalizability test,” which requires imagining a world in which 
+everyone for all of time has willed the maxim. If willing the maxim in such a world generates a contradiction, 
+then the action is prohibited. There are three interpretations of what sort of contradiction is necessary: 
+(1) the teleological view, prohibiting actions that conflict with some assumed teleological end when 
+universalized, (2) the logical contradiction view, prohibiting maxims that are logically impossible 
+when universalized, and (3) the practical contradiction view, prohibiting maxims that are self-defeating 
+when universalized.
 
-Given that the will function already excludes worlds where the circumstances fail (by rendering 
-the statement vacuously true at them), one may conclude that the dyadic obligation operator is now useless. 
-Using the dyadic obligation operator allows me to take advantage of the power of DDL to represent the bearing 
-that circumstances have on obligation. DDL has powerful axioms expressing the relationship between circumstances 
-and obligation, such as the fact that obligations are monotonically increasing with respect to broader 
-circumstances. Using the monadic obligation operator would require me to either operate with an empty 
-notion of context or to redefine these axioms. The dyadic obligation operator lets me take advantage of the full 
-power of DDL in expressing contrary-to-duty obligations. This is particularly important for Kantian ethics 
-and the FUL specifically because many critiques of the FUL rely on attention to circumstances (tailoring 
-objection) or lack thereof (ideal theory). This is also an innovation that my custom formalization presents 
-over the prior work. By formally including the notion of a circumstance or context, I am able to represent 
-these objections that Kantian scholars study. Formalizing Kantian ethics in a dyadic deontic logic 
-instead of a monadic deontic logic is a key contribution of this thesis.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{fun}\isamarkupfalse%
-\ effective\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}\ t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}E\ {\isacharunderscore}\ {\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}effective\ {\isacharparenleft}c{\isacharcolon}{\isacharcolon}t{\isacharcomma}\ a{\isacharcolon}{\isacharcolon}os{\isacharcomma}\ g{\isacharcolon}{\isacharcolon}t{\isacharparenright}\ s\ {\isacharequal}\ {\isacharparenleft}{\isacharparenleft}will\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ \isactrlbold {\isasymequiv}\ g{\isacharparenright}{\isachardoublequoteclose}%
-\begin{isamarkuptext}%
-A maxim is effective for a subject when, if the subject wills it then the goal is achieved, and
-when the subject does not act on it, the goal is not achieved.$\footnote{Thank you to Jeremy D. Zucker for helping me think through this.}$ \cite{sepcausation} 
-The former direction of the implication 
-is intuitive: if the act results in the goal, it was effective in causing the goal. This represents `necessary'
-causality.
+Under the logical contradiction interpretation, falsely promising to repay a loan to get some quick cash
+fails the universalizability test because, in such a world, the practice of promising would die out so 
+making a false promise would be impossible. Korsgaard appeals to Dietrichson \cite{dietrichson} to construct the example of 
+a mother killing her children that tend to cry more than average so that she can get some 
+sleep at night. Universalizing this maxim does not generate a logical contradiction, but it is clearly 
+morally wrong. The problem here is that killing is a natural action, which Korsgaard distinguishes from 
+a practice, like promising. Natural actions will never be logically impossible, so the logical contradiction 
+view fails to prohibit them.
 
-The latter direction represents `sufficient' causality, or the idea that, counterfactually,
-if the maxim were not willed, then the goal is not achieved \cite{lewiscausality}. Note that nothing else changes about this
-counterfactual world—the circumstances are identical and we neither added additional theorems nor 
-specified the model any further. This represents Lewis's idea of "comparative similarity," \cite{lewiscounterfactuals} where 
-a counterfactual is true if it holds at the most similar world. In our case, this is just the world 
-where everything is the same except the maxim is not acted on.
+Under the teleological contradiction interpretation, a maxim is prohibited if it undercuts some natural 
+or assigned purpose for some practice, act, or object. For example, the purpose of promising is to 
+create a system of mutual trust and false promising undercuts this purpose and is thus prohibited. The problem 
+with this view is that it assumes that the agent is committed, either because of their own goals or 
+because of some property of a rational will, to some teleological system. Acton formulates Hegel's argument that \cite{acton},
+an agent doesn't have to be committed to promising as a system of mutual trust. Korsgaard concludes that 
+assigning teleological purposes to actions is difficult because ``such purposes may have
+nothing to do with what the agent wants or ought rationally to want, or even with what
+any human being wants." If the agent is not committed to the purpose, then will not see a contradiction 
+in willing an act that violates this purpose.
 
-Combining these ideas, this definition of effective states that a maxim is effective if the 
-maxim being acted on by a subject is the necessary and sufficient cause of the goal.\footnote{Should I wave a hand at critiques of counterfactual causality?}
+This difficulty with the teleological contradiction interpretation drives Korsgaard to look for purposes
+that an agent must necessarily be committed to, and she concludes that this must be the purpose of the 
+maxim itself. By willing a maxim, an agent commits themselves to the goal of the maxim, and thus cannot 
+rationally will a system in which this goal is undercut. This system satisfactorily handles natural actions
+like those of the sleep-deprived mother: in willing the end of sleeping through the night, she is 
+implicitly willing that she be alive in order to secure and enjoy her sleep. If any mother is allowed to kill
+any loud child, then she cannot be secure in the possession of her life, because her own mother may have 
+grown frustrated with her crying. Her willing this maxim thwarts the end that she sought to secure.
 
-If the circumstances do not hold and the goal is achieved, then the maxim is vacuously effective, since 
-it is vacuously willed (as described above). While this scenario is counterintuitive, it is not very 
-interesting for my purposes because, when the circumstances do not hold, a maxim is not applicable. It 
-doesn't really make sense to evaluate a maxim when it's not supposed to be applied. The maxim ``When on Jupiter,
-read a book to one-up your nemesis" is vacuously effective because it can never be disproven.%
+The practical contradiction interpretation not only addresses the problems with the first two 
+interpretations, it also offers a much more satisfying explanation of why certain maxims are immoral. 
+The problem is not the existence of a contradiction itself, but instead the fact that these maxims 
+involve parasitic behavior on social conditions that the agent seeks to benefit from. The false promiser 
+simultaneously wants to abuse the system of promising and benefit from it, and is thus making an exception 
+of themselves. It is this kind of free-riding that the universalizability test seeks to draw out. The test
+raises the same kinds of objections that the question ``What if everyone did that?" seeks to draw out.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \endinput
-%:%file=~/Desktop/cs91r/paper/paper41.thy%:%
-%:%24=6%:%
-%:%36=8%:%
-%:%37=9%:%
-%:%46=11%:%
-%:%58=13%:%
-%:%59=14%:%
-%:%60=15%:%
-%:%61=16%:%
-%:%62=17%:%
-%:%63=18%:%
-%:%65=20%:%
-%:%66=20%:%
-%:%67=20%:%
-%:%68=20%:%
-%:%69=21%:%
-%:%70=21%:%
-%:%71=21%:%
-%:%72=21%:%
-%:%73=22%:%
-%:%74=23%:%
-%:%75=23%:%
-%:%76=23%:%
-%:%77=24%:%
-%:%78=25%:%
-%:%79=26%:%
-%:%80=27%:%
-%:%81=28%:%
-%:%82=29%:%
-%:%83=30%:%
-%:%86=32%:%
-%:%87=33%:%
-%:%88=34%:%
-%:%89=35%:%
-%:%90=36%:%
-%:%91=37%:%
-%:%92=38%:%
-%:%93=39%:%
-%:%94=40%:%
-%:%95=41%:%
-%:%96=42%:%
-%:%97=43%:%
-%:%98=44%:%
-%:%99=45%:%
-%:%100=46%:%
-%:%101=47%:%
-%:%102=48%:%
-%:%103=49%:%
-%:%104=50%:%
-%:%105=51%:%
-%:%106=52%:%
-%:%107=53%:%
-%:%108=54%:%
-%:%109=55%:%
-%:%110=56%:%
-%:%111=57%:%
-%:%112=58%:%
-%:%113=59%:%
-%:%114=60%:%
-%:%115=61%:%
-%:%116=62%:%
-%:%117=63%:%
-%:%118=64%:%
-%:%119=65%:%
-%:%120=66%:%
-%:%121=67%:%
-%:%122=68%:%
-%:%123=69%:%
-%:%124=70%:%
-%:%125=71%:%
-%:%126=72%:%
-%:%127=73%:%
-%:%128=74%:%
-%:%129=75%:%
-%:%130=76%:%
-%:%131=77%:%
-%:%132=78%:%
-%:%133=79%:%
-%:%134=80%:%
-%:%135=81%:%
-%:%136=82%:%
-%:%137=83%:%
-%:%138=84%:%
-%:%139=85%:%
-%:%140=86%:%
-%:%141=87%:%
-%:%142=88%:%
-%:%143=89%:%
-%:%144=90%:%
-%:%145=91%:%
-%:%146=92%:%
-%:%147=93%:%
-%:%148=94%:%
-%:%149=95%:%
-%:%150=96%:%
-%:%151=97%:%
-%:%152=98%:%
-%:%153=99%:%
-%:%154=100%:%
-%:%155=101%:%
-%:%156=102%:%
-%:%157=103%:%
-%:%158=104%:%
-%:%159=105%:%
-%:%160=106%:%
-%:%161=107%:%
-%:%162=108%:%
-%:%163=109%:%
-%:%164=110%:%
-%:%165=111%:%
-%:%166=112%:%
-%:%167=113%:%
-%:%168=114%:%
-%:%169=115%:%
-%:%170=116%:%
-%:%171=117%:%
-%:%172=118%:%
-%:%173=119%:%
-%:%174=120%:%
-%:%175=121%:%
-%:%176=122%:%
-%:%177=123%:%
-%:%179=125%:%
-%:%180=125%:%
-%:%181=126%:%
-%:%183=128%:%
-%:%184=129%:%
-%:%185=130%:%
-%:%186=131%:%
-%:%187=132%:%
-%:%188=133%:%
-%:%189=134%:%
-%:%190=135%:%
-%:%191=136%:%
-%:%192=137%:%
-%:%193=138%:%
-%:%194=139%:%
-%:%195=140%:%
-%:%196=141%:%
-%:%197=142%:%
-%:%198=143%:%
-%:%199=144%:%
-%:%200=145%:%
-%:%201=146%:%
-%:%202=147%:%
-%:%203=148%:%
-%:%204=149%:%
-%:%205=150%:%
-%:%206=151%:%
-%:%207=152%:%
-%:%208=153%:%
-%:%209=154%:%
-%:%210=155%:%
-%:%211=156%:%
-%:%212=157%:%
-%:%213=158%:%
-%:%214=159%:%
-%:%215=160%:%
-%:%216=161%:%
-%:%217=162%:%
-%:%218=163%:%
-%:%219=164%:%
-%:%220=165%:%
-%:%221=166%:%
-%:%222=167%:%
-%:%223=168%:%
-%:%224=169%:%
-%:%226=172%:%
-%:%227=172%:%
-%:%228=173%:%
-%:%230=175%:%
-%:%231=176%:%
-%:%232=177%:%
-%:%233=178%:%
-%:%234=179%:%
-%:%235=180%:%
-%:%236=181%:%
-%:%237=182%:%
-%:%238=183%:%
-%:%239=184%:%
-%:%240=185%:%
-%:%241=186%:%
-%:%242=187%:%
-%:%243=188%:%
-%:%244=189%:%
-%:%245=190%:%
-%:%246=191%:%
-%:%247=192%:%
-%:%248=193%:%
-%:%249=194%:%
-%:%250=195%:%
+%:%file=~/Desktop/cs91r/paper/threeflags.thy%:%
+%:%19=7%:%
+%:%20=8%:%
+%:%21=9%:%
+%:%22=10%:%
+%:%23=11%:%
+%:%24=12%:%
+%:%25=13%:%
+%:%26=14%:%
+%:%27=15%:%
+%:%28=16%:%
+%:%29=17%:%
+%:%30=18%:%
+%:%31=19%:%
+%:%32=20%:%
+%:%33=21%:%
+%:%34=22%:%
+%:%35=23%:%
+%:%36=24%:%
+%:%37=25%:%
+%:%38=26%:%
+%:%39=27%:%
+%:%40=28%:%
+%:%41=29%:%
+%:%42=30%:%
+%:%43=31%:%
+%:%44=32%:%
+%:%45=33%:%
+%:%46=34%:%
+%:%47=35%:%
+%:%48=36%:%
+%:%49=37%:%
+%:%50=38%:%
+%:%51=39%:%
+%:%52=40%:%
+%:%53=41%:%
+%:%54=42%:%
+%:%55=43%:%
+%:%56=44%:%
+%:%57=45%:%
+%:%58=46%:%
+%:%59=47%:%
+%:%60=48%:%
+%:%61=49%:%
+%:%62=50%:%
+%:%63=51%:%
+%:%64=52%:%
+%:%65=53%:%
+%:%66=54%:%
+%:%67=55%:%
+%:%68=56%:%
+%:%69=57%:%
+%:%70=58%:%
+%:%71=59%:%
+%:%72=60%:%
+%:%73=61%:%
+%:%74=62%:%
+%:%75=63%:%
+%:%76=64%:%
+%:%77=65%:%
+%:%78=66%:%
+%:%79=67%:%
+%:%80=68%:%
+%:%81=69%:%
+%:%82=70%:%
+%:%83=71%:%
+%:%84=72%:%
+%:%85=73%:%
+%:%86=74%:%
+%:%87=75%:%
+%:%88=76%:%
+%:%89=77%:%
+%:%90=78%:%
+%:%91=79%:%
+%:%92=80%:%
+%:%93=81%:%
+%:%94=82%:%
+%:%95=83%:%
+%:%96=84%:%
+%:%97=85%:%
+%:%98=86%:%
+%:%99=87%:%
+%:%100=88%:%
+%:%101=89%:%
+%:%102=90%:%
+%:%103=91%:%
+%:%104=92%:%
+%:%105=93%:%
+%:%106=94%:%
+%:%107=95%:%
+%:%108=96%:%
+%:%109=97%:%
+%:%110=98%:%
+%:%111=99%:%
+%:%112=100%:%
+%:%113=101%:%
+%:%114=102%:%
+%:%115=103%:%
+%:%116=104%:%
+%:%117=105%:%
+%:%118=106%:%
+%:%119=107%:%
+%:%120=108%:%
+%:%121=109%:%
+%:%122=110%:%
+%:%123=111%:%
+%:%124=112%:%
+%:%125=113%:%
+%:%126=114%:%
+%:%127=115%:%
+%:%128=116%:%
+%:%129=117%:%
+%:%130=118%:%
+%:%131=119%:%
+%:%132=120%:%
+%:%133=121%:%
+%:%134=122%:%
+%:%135=123%:%
+%:%136=124%:%
+%:%137=125%:%
+%:%138=126%:%
+%:%139=127%:%
+%:%140=128%:%
+%:%141=129%:%
+%:%142=130%:%
+%:%143=131%:%
+%:%144=132%:%
+%:%145=133%:%
+%:%146=134%:%
+%:%147=135%:%
+%:%148=136%:%
+%:%149=137%:%
+%:%150=138%:%
+%:%151=139%:%
+%:%152=140%:%
+%:%153=141%:%
+%:%154=142%:%
+%:%155=143%:%
+%:%156=144%:%
+%:%157=145%:%
+%:%158=146%:%
+%:%159=147%:%
+%:%160=148%:%
+%:%161=149%:%
+%:%162=150%:%
+%:%163=151%:%
+%:%164=152%:%
+%:%165=153%:%
+%:%166=154%:%
+%:%167=155%:%
+%:%168=156%:%
+%:%169=157%:%
+%:%170=158%:%
+%:%171=159%:%
+%:%172=160%:%
+%:%173=161%:%
+%:%174=162%:%
+%:%175=163%:%
+%:%176=164%:%
+%:%177=165%:%
+%:%178=166%:%
+%:%179=167%:%
+%:%180=168%:%
+%:%181=169%:%
+%:%182=170%:%
+%:%183=171%:%
+%:%184=172%:%
+%:%185=173%:%
+%:%186=174%:%
+%:%187=175%:%
+%:%188=176%:%
+%:%189=177%:%
+%:%190=178%:%
+%:%191=179%:%
+%:%192=180%:%
+%:%193=181%:%
+%:%194=182%:%
+%:%195=183%:%
+%:%196=184%:%
+%:%197=185%:%
+%:%198=186%:%
+%:%199=187%:%

### 2021-10-07 paper/output/document/paper41.tex
at least it's consistent

@@
 \isacommand{fun}\isamarkupfalse%
-\ will\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim\ {\isasymRightarrow}\ s{\isasymRightarrow}\ \ t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}A\ {\isacharunderscore}\ {\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
+\ will\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim\ {\isasymRightarrow}\ s{\isasymRightarrow}\ \ t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}W\ {\isacharunderscore}\ {\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
 \ \ \isakeyword{where}\ {\isachardoublequoteopen}will\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ {\isacharequal}\ {\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}a\ s{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
@@
 \end{isamarkuptext}\isamarkuptrue%
+\isacommand{fun}\isamarkupfalse%
+\ not{\isacharunderscore}universalizable\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
+{\isachardoublequoteopen}not{\isacharunderscore}universalizable\ M\ s\ {\isacharequal}\ {\isacharparenleft}{\isasymTurnstile}\ {\isacharparenleft}{\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymforall}p{\isachardot}\ W\ M\ p\ w{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}E\ M\ s{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{The maxim willed by subject $s$ is not universalizable if, for all people $p$, if $p$ wills M, then 
+$M$ is no longer effective for $s$.%
+}%
+\begin{isamarkuptext}%
+This formalizes Korgsaard's definition of the practical contradiction
+interpretation:  a maxim is not universalizable 
+if, in the world where the maxim becomes the standard practice (i.e. everyone acts on the maxim), the
+agent's attempt to use the maxim's act to achieve the maxim's goal is frustrated. In other words, if 
+the maxim is universally willed (captured by applying a universal qunatifier and the will function 
+to the maxim on the LHS), then it is no longer effective for the subject $s$ (RHS above).
+
+One worry is the order of the universal quantifier and the $\vDash$ or derivability symbol. In this 
+representation, the universal quantifier is tightly bound to the left hand side of the equation, so it 
+only quantifies into the statement ``All p will maxim M at any world." We can imagine an alternate
+representation that quantifies over the sentence $\vDash W M p \longrightarrow \sim E M s$. This is 
+a sentence of type $s \longrightarrow bool$, since it accepts a subject ($p$) as input and returns 
+a boolean (the result of $p$ substituted into the sentence.) Thus, applying the universal quantifier 
+$\forall p$ to this sentence results in a boolean that tracks the universalizability (or lack thereof) 
+of the maxim. I chose my representation because it tracks the intuitive meaning of the universalizability 
+test better: ``IF (the maxim is universalized) THEN (it is no longer effective)".
+
+It's not clear to me if there's any intuitive difference between these two representations, but the lemmas 
+below (using simplified versions of the representations) show that my representation is weaker than 
+the representation where the quantifier has larger scope. This seems promising—the representation in 
+lemma test\_2 is likely too strong because the quantifier quantifies into $M a$ as well. It really 
+doesn't seem like this should make a difference, since $p$ never appears on the RHS expression. Let's
+see if Prof. Amin has insight.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
 %
@@
 %:%250=195%:%
+%:%252=197%:%
+%:%253=197%:%
+%:%254=198%:%
+%:%256=199%:%
+%:%257=200%:%
+%:%260=202%:%
+%:%261=203%:%
+%:%262=204%:%
+%:%263=205%:%
+%:%264=206%:%
+%:%265=207%:%
+%:%266=208%:%
+%:%267=209%:%
+%:%268=210%:%
+%:%269=211%:%
+%:%270=212%:%
+%:%271=213%:%
+%:%272=214%:%
+%:%273=215%:%
+%:%274=216%:%
+%:%275=217%:%
+%:%276=218%:%
+%:%277=219%:%
+%:%278=220%:%
+%:%279=221%:%
+%:%280=222%:%
+%:%281=223%:%
+%:%282=224%:%

### 2021-10-07 paper/output/document/paper41.tex
the bar is so low

@@
 }\isanewline
+\isanewline
 \isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
@@
 \ will\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim\ {\isasymRightarrow}\ s{\isasymRightarrow}\ \ t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}W\ {\isacharunderscore}\ {\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}will\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ {\isacharequal}\ {\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}a\ s{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}will\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ {\isacharequal}\ {\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}a\ s{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isacommand{print{\isacharunderscore}theorems}\isamarkupfalse%
+%
 \begin{isamarkuptext}%
@@
 \ effective\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}\ t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}E\ {\isacharunderscore}\ {\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}effective\ {\isacharparenleft}c{\isacharcolon}{\isacharcolon}t{\isacharcomma}\ a{\isacharcolon}{\isacharcolon}os{\isacharcomma}\ g{\isacharcolon}{\isacharcolon}t{\isacharparenright}\ s\ {\isacharequal}\ {\isacharparenleft}{\isacharparenleft}will\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ \isactrlbold {\isasymequiv}\ g{\isacharparenright}{\isachardoublequoteclose}%
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}effective\ {\isacharparenleft}c{\isacharcolon}{\isacharcolon}t{\isacharcomma}\ a{\isacharcolon}{\isacharcolon}os{\isacharcomma}\ g{\isacharcolon}{\isacharcolon}t{\isacharparenright}\ s\ {\isacharequal}\ {\isacharparenleft}{\isacharparenleft}will\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ \isactrlbold {\isasymequiv}\ g{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isacommand{print{\isacharunderscore}theorems}\isamarkupfalse%
+%
 \begin{isamarkuptext}%
@@
 \isacommand{fun}\isamarkupfalse%
+\ LHS{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}t{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
+{\isachardoublequoteopen}LHS\ M\ s\ {\isacharequal}\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ W\ M\ p\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{fun}\isamarkupfalse%
 \ not{\isacharunderscore}universalizable\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
-{\isachardoublequoteopen}not{\isacharunderscore}universalizable\ M\ s\ {\isacharequal}\ {\isacharparenleft}{\isasymTurnstile}\ {\isacharparenleft}{\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymforall}p{\isachardot}\ W\ M\ p\ w{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}E\ M\ s{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+{\isachardoublequoteopen}not{\isacharunderscore}universalizable\ M\ s\ {\isacharequal}\ {\isacharparenleft}{\isasymTurnstile}\ {\isacharparenleft}LHS\ M\ s\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}E\ M\ s{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
 %
@@
 $M$ is no longer effective for $s$.%
-}%
+}\isanewline
+\isacommand{print{\isacharunderscore}theorems}\isamarkupfalse%
+%
 \begin{isamarkuptext}%
@@
 \end{isamarkuptext}\isamarkuptrue%
+\isacommand{abbreviation}\isamarkupfalse%
+\ FUL{\isadigit{0}}{\isacharcolon}{\isacharcolon}bool\ \isakeyword{where}\ {\isachardoublequoteopen}FUL{\isadigit{0}}\ {\isasymequiv}\ {\isasymforall}\ c\ a\ g\ s{\isachardot}\ not{\isacharunderscore}universalizable\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ {\isasymlongrightarrow}\ {\isasymTurnstile}{\isacharparenleft}{\isacharparenleft}O{\isacharbraceleft}{\isacharparenleft}\isactrlbold {\isasymnot}\ W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}{\isacharbar}\ c{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{This representation of the Formula of Universal Law reads, ``For all circumstances, goals, acts, 
+and subjects, if the maxim of the subject performing the act for the goal in the circumstances is not 
+universalizable (as defined above), then, at all worlds, in those circumstances, the subject 
+is prohibited (obligated not to) from willing the maxim.
+
+It's also inconsistent!!!! Boooooo%
+}\isanewline
+\isanewline
+\isacommand{fun}\isamarkupfalse%
+\ imagine{\isacharunderscore}a{\isacharunderscore}world{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
+{\isachardoublequoteopen}imagine{\isacharunderscore}a{\isacharunderscore}world\ M\ {\isacharequal}\ {\isacharparenleft}{\isasymexists}w{\isachardot}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ {\isacharparenleft}W\ M\ p{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{The FUL really says, `imagine a world where the maxim were universalized...' I suspect that part of 
+the problem with FUL0 is that it universalizes the maxim at the same world that prohibits it, which 
+is weird because the agent performs the action (since it's universalized) but it's prohibited. Instead, 
+we want to say that in some other world where the maxim is universalized, let's apply the universalizability 
+test. This particular function represents a world where the maxim is universalized.%
+}\isanewline
+\isanewline
+\isacommand{fun}\isamarkupfalse%
+\ not{\isacharunderscore}contradictory{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
+{\isachardoublequoteopen}not{\isacharunderscore}contradictory\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ {\isacharequal}\ {\isacharparenleft}{\isasymforall}p\ w{\isachardot}\ {\isasymnot}\ {\isacharparenleft}{\isacharparenleft}c\ \isactrlbold {\isasymand}\ {\isacharparenleft}a\ p{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbottom}{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{This function represents a maxim that is not contradictory, in that an agent can will it without 
+contradiction. It's more of a sanity check.%
+}\ \isanewline
+\isanewline
+\isacommand{axiomatization}\isamarkupfalse%
+\ \isakeyword{where}\ imagination{\isacharunderscore}works{\isacharcolon}{\isachardoublequoteopen}{\isasymforall}c{\isacharcolon}{\isacharcolon}t{\isachardot}\ {\isasymforall}a{\isacharcolon}{\isacharcolon}os{\isachardot}\ {\isasymforall}g{\isacharcolon}{\isacharcolon}t{\isachardot}\ \ {\isacharparenleft}{\isasymforall}p{\isacharcolon}{\isacharcolon}s{\isachardot}\ {\isasymforall}w{\isacharcolon}{\isacharcolon}i{\isachardot}\ {\isasymnot}\ {\isacharparenleft}{\isacharparenleft}c\ \isactrlbold {\isasymand}\ {\isacharparenleft}a\ p{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbottom}{\isacharparenright}\ w{\isacharparenright}\ {\isasymlongrightarrow}\ \ {\isacharparenleft}{\isasymexists}w{\isachardot}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ {\isacharparenleft}W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ p{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{This axiom says, effectively, that our imagination works. In other words, for every maxim, if it 
+isn't contradictory, there is some (imagined) world where it is universalized. This guarantees that the 
+FUL can't be trivially true, since there is some world where the universalizability test is carried out.%
+}\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ True\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{Consistent so far:
+Nitpick found a model for card i = 1 and card s = 1:
+
+  Empty assignment%
+}%
+\endisatagproof
+{\isafoldproof}%
 %
@@
 \endisadelimproof
+\isanewline
+\isanewline
+\isacommand{consts}\isamarkupfalse%
+\ a{\isacharcolon}{\isacharcolon}os\isanewline
+\isacommand{consts}\isamarkupfalse%
+\ g{\isacharcolon}{\isacharcolon}t\isanewline
+\isacommand{consts}\isamarkupfalse%
+\ c{\isacharcolon}{\isacharcolon}t\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ M\ \isakeyword{where}\ {\isachardoublequoteopen}M\ {\isasymequiv}\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{consts}\isamarkupfalse%
+\ M{\isadigit{2}}{\isacharcolon}{\isacharcolon}maxim\isanewline
+\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ FUL{\isadigit{2}}\ \isakeyword{where}\ {\isachardoublequoteopen}FUL{\isadigit{2}}\ {\isasymequiv}\ {\isasymforall}s{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isacharparenleft}{\isasymforall}w{\isachardot}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ {\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}a\ p{\isacharparenright}{\isacharparenright}\ w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isasymnot}\ {\isacharparenleft}{\isacharparenleft}{\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}a\ s{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ g{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}\ {\isasymlongrightarrow}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}a\ s{\isacharparenright}{\isacharparenright}{\isacharbraceright}\ cw{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}FUL{\isadigit{2}}{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharcomma}\ show{\isacharunderscore}all{\isacharbrackright}\ \isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ verbose{\isacharcomma}\ falsify{\isacharequal}true{\isacharcomma}\ show{\isacharunderscore}all{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
 %
 \isatagproof
+\isacommand{oops}\isamarkupfalse%
 %
@@
 %
-\isadelimproof
-%
-\endisadelimproof
-%
-\isatagproof
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isatagproof
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isatagproof
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
+\begin{isamarkuptext}%
+This is a formulation of the FUL in which, assuming every maxim is universalized at some
+world (this is the axiom imagination works), at that world (or other worlds like it), if the maxim is 
+not effective for the agent, then it is prohibited at the current world cw. Couple of optimizations 
+necessary to get Nitpick able to handle this:
+(1) Couldn't use the effective and will functions becuase they made Nitpick time out. Is there a way 
+to have a purely syntactic version of these functions? They'll make notation prettier? Like an 
+abbreviation with free variables?
+
+(2) If I quantify over the maxim's components, then Nitpick times out. If I specify a 
+single maxim as a constant, then it can handle everything just fine. I could try, every 
+time I'm working with an example, specifying properties of these constants. The downside is that if I want 
+to work with 2 maxims at once, then I have to add more constants and add the FUL as an axiom again for each of these maxims. This might not 
+be too annoying in practice (I don't think I'll need that many maxims), but there's something theoretically
+unsatisfying about it. I guess one theoretical explanation is that the system can only handle small models?
+Which is maybe not a huge problem?%
+\end{isamarkuptext}\isamarkuptrue%
 %
@@
 %:%69=21%:%
-%:%70=21%:%
-%:%71=21%:%
-%:%72=21%:%
+%:%70=22%:%
+%:%71=22%:%
+%:%72=22%:%
 %:%73=22%:%
 %:%74=23%:%
-%:%75=23%:%
-%:%76=23%:%
+%:%75=24%:%
+%:%76=24%:%
 %:%77=24%:%
@@
 %:%83=30%:%
-%:%86=32%:%
+%:%84=31%:%
 %:%87=33%:%
@@
 %:%177=123%:%
-%:%179=125%:%
-%:%180=125%:%
+%:%178=124%:%
+%:%180=126%:%
 %:%181=126%:%
+%:%182=127%:%
 %:%183=128%:%
-%:%184=129%:%
-%:%185=130%:%
-%:%186=131%:%
-%:%187=132%:%
-%:%188=133%:%
-%:%189=134%:%
-%:%190=135%:%
-%:%191=136%:%
-%:%192=137%:%
-%:%193=138%:%
-%:%194=139%:%
-%:%195=140%:%
-%:%196=141%:%
-%:%197=142%:%
-%:%198=143%:%
-%:%199=144%:%
-%:%200=145%:%
-%:%201=146%:%
-%:%202=147%:%
-%:%203=148%:%
-%:%204=149%:%
-%:%205=150%:%
-%:%206=151%:%
-%:%207=152%:%
-%:%208=153%:%
-%:%209=154%:%
-%:%210=155%:%
-%:%211=156%:%
-%:%212=157%:%
-%:%213=158%:%
-%:%214=159%:%
-%:%215=160%:%
-%:%216=161%:%
-%:%217=162%:%
-%:%218=163%:%
-%:%219=164%:%
-%:%220=165%:%
-%:%221=166%:%
-%:%222=167%:%
-%:%223=168%:%
-%:%224=169%:%
-%:%226=172%:%
-%:%227=172%:%
-%:%228=173%:%
-%:%230=175%:%
-%:%231=176%:%
-%:%232=177%:%
-%:%233=178%:%
-%:%234=179%:%
-%:%235=180%:%
-%:%236=181%:%
-%:%237=182%:%
-%:%238=183%:%
-%:%239=184%:%
-%:%240=185%:%
-%:%241=186%:%
-%:%242=187%:%
-%:%243=188%:%
-%:%244=189%:%
-%:%245=190%:%
-%:%246=191%:%
-%:%247=192%:%
-%:%248=193%:%
-%:%249=194%:%
-%:%250=195%:%
-%:%252=197%:%
-%:%253=197%:%
-%:%254=198%:%
-%:%256=199%:%
+%:%186=130%:%
+%:%187=131%:%
+%:%188=132%:%
+%:%189=133%:%
+%:%190=134%:%
+%:%191=135%:%
+%:%192=136%:%
+%:%193=137%:%
+%:%194=138%:%
+%:%195=139%:%
+%:%196=140%:%
+%:%197=141%:%
+%:%198=142%:%
+%:%199=143%:%
+%:%200=144%:%
+%:%201=145%:%
+%:%202=146%:%
+%:%203=147%:%
+%:%204=148%:%
+%:%205=149%:%
+%:%206=150%:%
+%:%207=151%:%
+%:%208=152%:%
+%:%209=153%:%
+%:%210=154%:%
+%:%211=155%:%
+%:%212=156%:%
+%:%213=157%:%
+%:%214=158%:%
+%:%215=159%:%
+%:%216=160%:%
+%:%217=161%:%
+%:%218=162%:%
+%:%219=163%:%
+%:%220=164%:%
+%:%221=165%:%
+%:%222=166%:%
+%:%223=167%:%
+%:%224=168%:%
+%:%225=169%:%
+%:%226=170%:%
+%:%227=171%:%
+%:%229=174%:%
+%:%230=174%:%
+%:%231=175%:%
+%:%232=176%:%
+%:%235=178%:%
+%:%236=179%:%
+%:%237=180%:%
+%:%238=181%:%
+%:%239=182%:%
+%:%240=183%:%
+%:%241=184%:%
+%:%242=185%:%
+%:%243=186%:%
+%:%244=187%:%
+%:%245=188%:%
+%:%246=189%:%
+%:%247=190%:%
+%:%248=191%:%
+%:%249=192%:%
+%:%250=193%:%
+%:%251=194%:%
+%:%252=195%:%
+%:%253=196%:%
+%:%254=197%:%
+%:%255=198%:%
 %:%257=200%:%
+%:%258=200%:%
+%:%259=201%:%
 %:%260=202%:%
 %:%261=203%:%
-%:%262=204%:%
-%:%263=205%:%
-%:%264=206%:%
-%:%265=207%:%
-%:%266=208%:%
-%:%267=209%:%
-%:%268=210%:%
-%:%269=211%:%
-%:%270=212%:%
-%:%271=213%:%
-%:%272=214%:%
-%:%273=215%:%
-%:%274=216%:%
-%:%275=217%:%
-%:%276=218%:%
-%:%277=219%:%
-%:%278=220%:%
-%:%279=221%:%
-%:%280=222%:%
-%:%281=223%:%
-%:%282=224%:%
+%:%262=203%:%
+%:%263=204%:%
+%:%265=205%:%
+%:%266=206%:%
+%:%267=206%:%
+%:%268=207%:%
+%:%271=210%:%
+%:%272=211%:%
+%:%273=212%:%
+%:%274=213%:%
+%:%275=214%:%
+%:%276=215%:%
+%:%277=216%:%
+%:%278=217%:%
+%:%279=218%:%
+%:%280=219%:%
+%:%281=220%:%
+%:%282=221%:%
+%:%283=222%:%
+%:%284=223%:%
+%:%285=224%:%
+%:%286=225%:%
+%:%287=226%:%
+%:%288=227%:%
+%:%289=228%:%
+%:%290=229%:%
+%:%291=230%:%
+%:%292=231%:%
+%:%293=232%:%
+%:%295=235%:%
+%:%296=235%:%
+%:%298=236%:%
+%:%299=237%:%
+%:%300=238%:%
+%:%301=239%:%
+%:%302=240%:%
+%:%303=241%:%
+%:%304=241%:%
+%:%305=242%:%
+%:%306=243%:%
+%:%307=243%:%
+%:%308=244%:%
+%:%310=245%:%
+%:%311=246%:%
+%:%312=247%:%
+%:%313=248%:%
+%:%314=249%:%
+%:%315=249%:%
+%:%316=250%:%
+%:%317=251%:%
+%:%318=251%:%
+%:%319=252%:%
+%:%321=253%:%
+%:%322=254%:%
+%:%323=254%:%
+%:%324=255%:%
+%:%325=256%:%
+%:%326=256%:%
+%:%328=257%:%
+%:%329=258%:%
+%:%330=259%:%
+%:%331=259%:%
+%:%332=260%:%
+%:%333=261%:%
+%:%334=261%:%
+%:%335=262%:%
+%:%336=262%:%
+%:%338=262%:%
+%:%342=262%:%
+%:%343=262%:%
+%:%345=263%:%
+%:%346=264%:%
+%:%347=265%:%
+%:%348=266%:%
+%:%356=266%:%
+%:%357=267%:%
+%:%358=268%:%
+%:%359=268%:%
+%:%360=269%:%
+%:%361=269%:%
+%:%362=270%:%
+%:%363=270%:%
+%:%364=271%:%
+%:%365=271%:%
+%:%366=272%:%
+%:%367=273%:%
+%:%368=273%:%
+%:%369=274%:%
+%:%370=275%:%
+%:%371=275%:%
+%:%372=276%:%
+%:%373=277%:%
+%:%374=277%:%
+%:%375=278%:%
+%:%376=278%:%
+%:%377=279%:%
+%:%378=279%:%
+%:%380=279%:%
+%:%384=279%:%
+%:%394=281%:%
+%:%395=282%:%
+%:%396=283%:%
+%:%397=284%:%
+%:%398=285%:%
+%:%399=286%:%
+%:%400=287%:%
+%:%401=288%:%
+%:%402=289%:%
+%:%403=290%:%
+%:%404=291%:%
+%:%405=292%:%
+%:%406=293%:%
+%:%407=294%:%
+%:%408=295%:%

### 2021-10-08 paper/output/document/paper41.tex
me: i broke it irreparably and have been crying for the last week. nada: have you tried removing the line that says 2+2=5? me: good idea.

--- 2021-10-07 paper/output/document/paper41.tex
@@
 \end{isamarkuptext}\isamarkuptrue%
-\isacommand{fun}\isamarkupfalse%
+\isacommand{abbreviation}\isamarkupfalse%
 \ will\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim\ {\isasymRightarrow}\ s{\isasymRightarrow}\ \ t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}W\ {\isacharunderscore}\ {\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}will\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ {\isacharequal}\ {\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}a\ s{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}will\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isachardot}\ {\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}a\ s{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isacommand{print{\isacharunderscore}theorems}\isamarkupfalse%
+%
 \begin{isamarkuptext}%
@@
 \end{isamarkuptext}\isamarkuptrue%
-\isacommand{fun}\isamarkupfalse%
+\isacommand{abbreviation}\isamarkupfalse%
 \ effective\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}\ t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}E\ {\isacharunderscore}\ {\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}effective\ {\isacharparenleft}c{\isacharcolon}{\isacharcolon}t{\isacharcomma}\ a{\isacharcolon}{\isacharcolon}os{\isacharcomma}\ g{\isacharcolon}{\isacharcolon}t{\isacharparenright}\ s\ {\isacharequal}\ {\isacharparenleft}{\isacharparenleft}will\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ \isactrlbold {\isasymequiv}\ g{\isacharparenright}{\isachardoublequoteclose}%
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}effective\ \ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isachardot}\ {\isacharparenleft}{\isacharparenleft}will\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ \isactrlbold {\isasymequiv}\ g{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isacommand{print{\isacharunderscore}theorems}\isamarkupfalse%
+%
 \begin{isamarkuptext}%
@@
 \end{isamarkuptext}\isamarkuptrue%
-\isacommand{fun}\isamarkupfalse%
+\isacommand{abbreviation}\isamarkupfalse%
+\ LHS{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}t{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
+{\isachardoublequoteopen}LHS\ {\isasymequiv}\ {\isasymlambda}M\ s{\isachardot}\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ W\ M\ p\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
 \ not{\isacharunderscore}universalizable\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
-{\isachardoublequoteopen}not{\isacharunderscore}universalizable\ M\ s\ {\isacharequal}\ {\isacharparenleft}{\isasymTurnstile}\ {\isacharparenleft}{\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymforall}p{\isachardot}\ W\ M\ p\ w{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}E\ M\ s{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+{\isachardoublequoteopen}not{\isacharunderscore}universalizable\ {\isasymequiv}\ {\isasymlambda}M\ s{\isachardot}\ {\isacharparenleft}{\isasymTurnstile}\ {\isacharparenleft}LHS\ M\ s\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}E\ M\ s{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
 %
@@
 \end{isamarkuptext}\isamarkuptrue%
+\isacommand{abbreviation}\isamarkupfalse%
+\ FUL{\isadigit{0}}{\isacharcolon}{\isacharcolon}bool\ \isakeyword{where}\ {\isachardoublequoteopen}FUL{\isadigit{0}}\ {\isasymequiv}\ {\isasymforall}\ c\ a\ g\ s{\isachardot}\ not{\isacharunderscore}universalizable\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ {\isasymlongrightarrow}\ {\isasymTurnstile}{\isacharparenleft}{\isacharparenleft}O{\isacharbraceleft}{\isacharparenleft}\isactrlbold {\isasymnot}\ W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}{\isacharbar}\ c{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{This representation of the Formula of Universal Law reads, ``For all circumstances, goals, acts, 
+and subjects, if the maxim of the subject performing the act for the goal in the circumstances is not 
+universalizable (as defined above), then, at all worlds, in those circumstances, the subject 
+is prohibited (obligated not to) from willing the maxim.
+
+It's also inconsistent!!!! Boooooo%
+}\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}FUL{\isadigit{0}}\ {\isasymlongrightarrow}\ False{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{using}\isamarkupfalse%
+\ O{\isacharunderscore}diamond\ ax{\isacharunderscore}{\isadigit{5}}d\ \isanewline
+\ \ \isacommand{using}\isamarkupfalse%
+\ prod{\isachardot}simps{\isacharparenleft}{\isadigit{2}}{\isacharparenright}\ split{\isacharunderscore}conv\ \isacommand{by}\isamarkupfalse%
+\ fastforce%
+\endisatagproof
+{\isafoldproof}%
 %
@@
 \endisadelimproof
+\isanewline
+\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ imagine{\isacharunderscore}a{\isacharunderscore}world{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
+{\isachardoublequoteopen}imagine{\isacharunderscore}a{\isacharunderscore}world\ {\isasymequiv}\ {\isasymlambda}M{\isachardot}\ {\isacharparenleft}{\isasymexists}w{\isachardot}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ {\isacharparenleft}W\ M\ p{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{The FUL really says, `imagine a world where the maxim were universalized...' I suspect that part of 
+the problem with FUL0 is that it universalizes the maxim at the same world that prohibits it, which 
+is weird because the agent performs the action (since it's universalized) but it's prohibited. Instead, 
+we want to say that in some other world where the maxim is universalized, let's apply the universalizability 
+test. This particular function represents a world where the maxim is universalized.%
+}\isanewline
+\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ not{\isacharunderscore}contradictory{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
+{\isachardoublequoteopen}not{\isacharunderscore}contradictory\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}{\isachardot}\ {\isacharparenleft}{\isasymforall}p\ w{\isachardot}\ {\isasymnot}\ {\isacharparenleft}{\isacharparenleft}c\ \isactrlbold {\isasymand}\ {\isacharparenleft}a\ p{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbottom}{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{This function represents a maxim that is not contradictory, in that an agent can will it without 
+contradiction. It's more of a sanity check.%
+}\ \isanewline
+\isanewline
+\isacommand{axiomatization}\isamarkupfalse%
+\ \isakeyword{where}\ imagination{\isacharunderscore}works{\isacharcolon}{\isachardoublequoteopen}{\isasymforall}M{\isacharcolon}{\isacharcolon}maxim{\isachardot}\ \ {\isacharparenleft}not{\isacharunderscore}contradictory\ M{\isacharparenright}\ {\isasymlongrightarrow}\ \ {\isacharparenleft}{\isasymexists}w{\isachardot}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ {\isacharparenleft}W\ M\ p{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{This axiom says, effectively, that our imagination works. In other words, for every maxim, if it 
+isn't contradictory, there is some (imagined) world where it is universalized. This guarantees that the 
+FUL can't be trivially true, since there is some world where the universalizability test is carried out.%
+}\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ True\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
 %
 \isatagproof
+\isacommand{by}\isamarkupfalse%
+\ simp\ \isanewline
 %
+\isamarkupcmt{Consistent so far:
+Nitpick found a model for card i = 1 and card s = 1:
+
+  Empty assignment%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ not{\isacharunderscore}vacuous{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
+{\isachardoublequoteopen}not{\isacharunderscore}vacuous\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isachardot}\ {\isasymnot}\ {\isacharparenleft}g\ {\isacharequal}\ c{\isacharparenright}\ {\isasymand}\ {\isasymnot}\ {\isacharparenleft}a\ s\ {\isacharequal}\ c{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ FUL\ \isakeyword{where}\ {\isachardoublequoteopen}FUL\ {\isasymequiv}\ {\isasymforall}M{\isacharcolon}{\isacharcolon}maxim{\isachardot}\ {\isasymforall}s{\isacharcolon}{\isacharcolon}s{\isachardot}\ {\isacharparenleft}not{\isacharunderscore}vacuous\ M\ s{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}not{\isacharunderscore}universalizable\ M\ s\ {\isasymlongrightarrow}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}will\ M\ s{\isacharparenright}{\isacharbraceright}\ cw{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}FUL{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}true{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{$\color{blue}$ Nitpick found a counterexample for card s = 1 and card i = 1:
+
+  Skolem constants:
+    a = ($\lambda x. \_$)($s_1$ := ($\lambda x. \_$)($i_1$ := False))
+    c = ($\lambda x. \_$)($i_1$ := True)
+    g = ($\lambda x. \_$)($i_1$ := False)
+    $\lambda w$. p = ($\lambda x. \_$)($i_1$ := $s_1$)
+    s = $s_1$ $\color{black}$%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{axiomatization}\isamarkupfalse%
+\ \isakeyword{where}\ FUL{\isacharcolon}FUL\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ True\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{by}\isamarkupfalse%
+\ simp\isanewline
+%
+\isamarkupcmt{$\color{blue}$ Nitpick found a model for card i = 1 and card s = 1:
+
+  Empty assignment $\color{black}$%
+}%
 \endisatagproof
@@
 %:%177=123%:%
-%:%179=125%:%
-%:%180=125%:%
+%:%178=124%:%
+%:%180=126%:%
 %:%181=126%:%
+%:%182=127%:%
 %:%183=128%:%
-%:%184=129%:%
-%:%185=130%:%
-%:%186=131%:%
-%:%187=132%:%
-%:%188=133%:%
-%:%189=134%:%
-%:%190=135%:%
-%:%191=136%:%
-%:%192=137%:%
-%:%193=138%:%
-%:%194=139%:%
-%:%195=140%:%
-%:%196=141%:%
-%:%197=142%:%
-%:%198=143%:%
-%:%199=144%:%
-%:%200=145%:%
-%:%201=146%:%
-%:%202=147%:%
-%:%203=148%:%
-%:%204=149%:%
-%:%205=150%:%
-%:%206=151%:%
-%:%207=152%:%
-%:%208=153%:%
-%:%209=154%:%
-%:%210=155%:%
-%:%211=156%:%
-%:%212=157%:%
-%:%213=158%:%
-%:%214=159%:%
-%:%215=160%:%
-%:%216=161%:%
-%:%217=162%:%
-%:%218=163%:%
-%:%219=164%:%
-%:%220=165%:%
-%:%221=166%:%
-%:%222=167%:%
-%:%223=168%:%
-%:%224=169%:%
-%:%226=172%:%
-%:%227=172%:%
-%:%228=173%:%
-%:%230=175%:%
-%:%231=176%:%
-%:%232=177%:%
-%:%233=178%:%
-%:%234=179%:%
-%:%235=180%:%
-%:%236=181%:%
-%:%237=182%:%
-%:%238=183%:%
-%:%239=184%:%
-%:%240=185%:%
-%:%241=186%:%
-%:%242=187%:%
-%:%243=188%:%
-%:%244=189%:%
-%:%245=190%:%
-%:%246=191%:%
-%:%247=192%:%
-%:%248=193%:%
-%:%249=194%:%
-%:%250=195%:%
-%:%252=197%:%
-%:%253=197%:%
-%:%254=198%:%
-%:%256=199%:%
+%:%186=130%:%
+%:%187=131%:%
+%:%188=132%:%
+%:%189=133%:%
+%:%190=134%:%
+%:%191=135%:%
+%:%192=136%:%
+%:%193=137%:%
+%:%194=138%:%
+%:%195=139%:%
+%:%196=140%:%
+%:%197=141%:%
+%:%198=142%:%
+%:%199=143%:%
+%:%200=144%:%
+%:%201=145%:%
+%:%202=146%:%
+%:%203=147%:%
+%:%204=148%:%
+%:%205=149%:%
+%:%206=150%:%
+%:%207=151%:%
+%:%208=152%:%
+%:%209=153%:%
+%:%210=154%:%
+%:%211=155%:%
+%:%212=156%:%
+%:%213=157%:%
+%:%214=158%:%
+%:%215=159%:%
+%:%216=160%:%
+%:%217=161%:%
+%:%218=162%:%
+%:%219=163%:%
+%:%220=164%:%
+%:%221=165%:%
+%:%222=166%:%
+%:%223=167%:%
+%:%224=168%:%
+%:%225=169%:%
+%:%226=170%:%
+%:%227=171%:%
+%:%229=174%:%
+%:%230=174%:%
+%:%231=175%:%
+%:%232=176%:%
+%:%235=178%:%
+%:%236=179%:%
+%:%237=180%:%
+%:%238=181%:%
+%:%239=182%:%
+%:%240=183%:%
+%:%241=184%:%
+%:%242=185%:%
+%:%243=186%:%
+%:%244=187%:%
+%:%245=188%:%
+%:%246=189%:%
+%:%247=190%:%
+%:%248=191%:%
+%:%249=192%:%
+%:%250=193%:%
+%:%251=194%:%
+%:%252=195%:%
+%:%253=196%:%
+%:%254=197%:%
+%:%255=198%:%
 %:%257=200%:%
+%:%258=200%:%
+%:%259=201%:%
 %:%260=202%:%
 %:%261=203%:%
-%:%262=204%:%
-%:%263=205%:%
-%:%264=206%:%
-%:%265=207%:%
-%:%266=208%:%
-%:%267=209%:%
-%:%268=210%:%
-%:%269=211%:%
-%:%270=212%:%
-%:%271=213%:%
-%:%272=214%:%
-%:%273=215%:%
-%:%274=216%:%
-%:%275=217%:%
-%:%276=218%:%
-%:%277=219%:%
-%:%278=220%:%
-%:%279=221%:%
-%:%280=222%:%
-%:%281=223%:%
-%:%282=224%:%
+%:%262=203%:%
+%:%263=204%:%
+%:%265=205%:%
+%:%266=206%:%
+%:%267=206%:%
+%:%268=207%:%
+%:%271=209%:%
+%:%272=210%:%
+%:%273=211%:%
+%:%274=212%:%
+%:%275=213%:%
+%:%276=214%:%
+%:%277=215%:%
+%:%278=216%:%
+%:%279=217%:%
+%:%280=218%:%
+%:%281=219%:%
+%:%282=220%:%
+%:%283=221%:%
+%:%284=222%:%
+%:%285=223%:%
+%:%286=224%:%
+%:%287=225%:%
+%:%288=226%:%
+%:%289=227%:%
+%:%290=228%:%
+%:%291=229%:%
+%:%292=230%:%
+%:%293=231%:%
+%:%295=234%:%
+%:%296=234%:%
+%:%298=235%:%
+%:%299=236%:%
+%:%300=237%:%
+%:%301=238%:%
+%:%302=239%:%
+%:%303=240%:%
+%:%304=240%:%
+%:%305=241%:%
+%:%306=242%:%
+%:%307=242%:%
+%:%309=242%:%
+%:%313=242%:%
+%:%314=242%:%
+%:%315=243%:%
+%:%316=243%:%
+%:%317=243%:%
+%:%324=243%:%
+%:%325=244%:%
+%:%326=245%:%
+%:%327=245%:%
+%:%328=246%:%
+%:%330=247%:%
+%:%331=248%:%
+%:%332=249%:%
+%:%333=250%:%
+%:%334=251%:%
+%:%335=251%:%
+%:%336=252%:%
+%:%337=253%:%
+%:%338=253%:%
+%:%339=254%:%
+%:%341=255%:%
+%:%342=256%:%
+%:%343=256%:%
+%:%344=257%:%
+%:%345=258%:%
+%:%346=258%:%
+%:%348=259%:%
+%:%349=260%:%
+%:%350=261%:%
+%:%351=261%:%
+%:%352=262%:%
+%:%353=263%:%
+%:%354=263%:%
+%:%355=264%:%
+%:%356=264%:%
+%:%358=264%:%
+%:%362=264%:%
+%:%363=264%:%
+%:%365=265%:%
+%:%366=266%:%
+%:%367=267%:%
+%:%368=268%:%
+%:%376=268%:%
+%:%377=269%:%
+%:%378=270%:%
+%:%379=270%:%
+%:%380=271%:%
+%:%381=272%:%
+%:%382=273%:%
+%:%383=273%:%
+%:%384=274%:%
+%:%385=275%:%
+%:%386=275%:%
+%:%387=276%:%
+%:%388=276%:%
+%:%390=276%:%
+%:%394=276%:%
+%:%395=276%:%
+%:%397=277%:%
+%:%398=278%:%
+%:%399=279%:%
+%:%400=280%:%
+%:%401=281%:%
+%:%402=282%:%
+%:%403=283%:%
+%:%404=284%:%
+%:%412=284%:%
+%:%413=285%:%
+%:%414=286%:%
+%:%415=286%:%
+%:%416=287%:%
+%:%417=288%:%
+%:%418=288%:%
+%:%419=289%:%
+%:%420=289%:%
+%:%422=289%:%
+%:%426=289%:%
+%:%427=289%:%
+%:%429=290%:%
+%:%430=291%:%
+%:%431=292%:%
+%:%441=294%:%
+%:%442=295%:%
+%:%443=296%:%
+%:%444=297%:%
+%:%445=298%:%
+%:%446=299%:%
+%:%447=300%:%
+%:%448=301%:%
+%:%449=302%:%
+%:%450=303%:%
+%:%451=304%:%
+%:%452=305%:%
+%:%453=306%:%
+%:%454=307%:%
+%:%455=308%:%

### 2021-10-09 paper/output/document/paper41.tex
fixed contradiction

--- 2021-10-07 paper/output/document/paper41.tex
@@
 \end{isamarkuptext}\isamarkuptrue%
-\isacommand{fun}\isamarkupfalse%
+\isacommand{abbreviation}\isamarkupfalse%
+\ universalized{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}t{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
+{\isachardoublequoteopen}universalized\ {\isasymequiv}\ {\isasymlambda}M\ s{\isachardot}\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ W\ M\ p\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
 \ not{\isacharunderscore}universalizable\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
-{\isachardoublequoteopen}not{\isacharunderscore}universalizable\ M\ s\ {\isacharequal}\ {\isacharparenleft}{\isasymTurnstile}\ {\isacharparenleft}{\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymforall}p{\isachardot}\ W\ M\ p\ w{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}E\ M\ s{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+{\isachardoublequoteopen}not{\isacharunderscore}universalizable\ {\isasymequiv}\ {\isasymlambda}M\ s{\isachardot}\ {\isacharparenleft}{\isasymTurnstile}\ {\isacharparenleft}universalized\ M\ s\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}E\ M\ s{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
 %
@@
 \begin{isamarkuptext}%
-This formalizes Korgsaard's definition of the practical contradiction
+Below is my first attempt at formalizing Korgsaard's definition of the practical contradiction
 interpretation:  a maxim is not universalizable 
@@
 the maxim is universally willed (captured by applying a universal qunatifier and the will function 
-to the maxim on the LHS), then it is no longer effective for the subject $s$ (RHS above).
-
-One worry is the order of the universal quantifier and the $\vDash$ or derivability symbol. In this 
-representation, the universal quantifier is tightly bound to the left hand side of the equation, so it 
-only quantifies into the statement ``All p will maxim M at any world." We can imagine an alternate
-representation that quantifies over the sentence $\vDash W M p \longrightarrow \sim E M s$. This is 
-a sentence of type $s \longrightarrow bool$, since it accepts a subject ($p$) as input and returns 
-a boolean (the result of $p$ substituted into the sentence.) Thus, applying the universal quantifier 
-$\forall p$ to this sentence results in a boolean that tracks the universalizability (or lack thereof) 
-of the maxim. I chose my representation because it tracks the intuitive meaning of the universalizability 
-test better: ``IF (the maxim is universalized) THEN (it is no longer effective)".
-
-It's not clear to me if there's any intuitive difference between these two representations, but the lemmas 
-below (using simplified versions of the representations) show that my representation is weaker than 
-the representation where the quantifier has larger scope. This seems promising—the representation in 
-lemma test\_2 is likely too strong because the quantifier quantifies into $M a$ as well. It really 
-doesn't seem like this should make a difference, since $p$ never appears on the RHS expression. Let's
-see if Prof. Amin has insight.%
+to the maxim on the LHS), then it is no longer effective for the subject $s$ (RHS above).%
 \end{isamarkuptext}\isamarkuptrue%
+\isacommand{abbreviation}\isamarkupfalse%
+\ prohibited{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}t{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
+{\isachardoublequoteopen}prohibited\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isachardot}\ O{\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}will\ {\isacharparenleft}c{\isacharcomma}a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ {\isacharbar}\ c{\isacharbraceright}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ FUL{\isadigit{0}}{\isacharcolon}{\isacharcolon}bool\ \isakeyword{where}\ {\isachardoublequoteopen}FUL{\isadigit{0}}\ {\isasymequiv}\ {\isasymforall}\ c\ a\ g\ s{\isachardot}\ not{\isacharunderscore}universalizable\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ {\isasymlongrightarrow}\ {\isasymTurnstile}{\isacharparenleft}{\isacharparenleft}prohibited\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
 %
+\isamarkupcmt{This representation of the Formula of Universal Law reads, ``For all circumstances, goals, acts, 
+and subjects, if the maxim of the subject performing the act for the goal in the circumstances is not 
+universalizable (as defined above), then, at all worlds, in those circumstances, the subject 
+is prohibited (obligated not to) from willing the maxim.%
+}\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}FUL{\isadigit{0}}\ {\isasymlongrightarrow}\ False{\isachardoublequoteclose}%
 \isadelimproof
-%
+\ %
 \endisadelimproof
@@
 \isatagproof
-%
+\isacommand{using}\isamarkupfalse%
+\ O{\isacharunderscore}diamond\ \isanewline
+\ \ \isacommand{using}\isamarkupfalse%
+\ prod{\isachardot}simps{\isacharparenleft}{\isadigit{2}}{\isacharparenright}\ split{\isacharunderscore}conv\ \isacommand{by}\isamarkupfalse%
+\ fastforce%
 \endisatagproof
@@
 %
+\begin{isamarkuptext}%
+FUL0 is not consistent, and sledgehammer is indeed able to show that it implies a contradiction. 
+The axioms that sledgehammer used are O\_diamond, which is \isa{{\isasymTurnstile}{\isasymlambda}w{\isachardot}\ ob\ {\isacharquery}B\ {\isacharquery}A\ {\isasymlongrightarrow}\ {\isasymnot}\ {\isasymTurnstile}\isactrlbold {\isasymnot}\ {\isacharquery}B\isactrlbold {\isasymand}{\isacharquery}A}.
+This axiom captures
+the idea that an obligation can't contradict its context. This is particularly problematic if the goal or 
+action of a maxim are equivalent to its circumstances. In other words, if the maxim has already been 
+acted on or the goal has already been achieved, then prohibiting it is impossible. 
+In any model that has at least one term, it is possible to construct a maxim where the circumstances, goal, 
+and act (once a subject acts on it) are all that same term, resulting in a contradiction.
+
+To get around this, I will exclude what I call ``badly formed maxims," which are those maxims sucht that the goal has already been 
+achieved or the act has already been acted on. Under my formalization, such maxims are 
+not well-formed. To understand why, we can return to Korsgaard's and O'Neill's interpretations of a maxim as a practical
+guide to action. A maxim is a practical principle that guides how we behave in everyday life. A 
+principle of the form ``When you are eating breakfast, eat breakfast in order to eat breakfast," is not 
+practically relevant. No agent would ever need to act on such a principle. It's not necessarily contradictory
+or prohibited, but it is the wrong kind of question to be asking yourself. It is not a 
+well-formed maxim, so the categorical imperative does not apply to it.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{abbreviation}\isamarkupfalse%
+\ well{\isacharunderscore}formed{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}i{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
+{\isachardoublequoteopen}well{\isacharunderscore}formed\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ w{\isachardot}\ {\isacharparenleft}{\isasymnot}\ {\isacharparenleft}\ {\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ g{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}\ {\isasymand}\ {\isacharparenleft}{\isasymnot}\ {\isacharparenleft}\ {\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ a\ s{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{This abbreviation formalizes the well-formedness of a maxim for a subject. The goal cannot be 
+already achieved in the circumstances and the subject cannot have already performed the act.%
+}\isanewline
+\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ FUL\ \isakeyword{where}\ {\isachardoublequoteopen}FUL\ {\isasymequiv}\ {\isasymforall}M{\isacharcolon}{\isacharcolon}maxim{\isachardot}\ {\isasymforall}s{\isacharcolon}{\isacharcolon}s{\isachardot}\ {\isacharparenleft}{\isasymforall}w{\isachardot}\ well{\isacharunderscore}formed\ M\ s\ w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}not{\isacharunderscore}universalizable\ M\ s\ {\isasymlongrightarrow}\ {\isasymTurnstile}\ prohibited\ M\ s\ {\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Let's try the exact same formalization of the FUL as above, except that it only applies to 
+maxims that are well-formed at every world.%
+}\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}FUL{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}true{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{The FUL does not hold in DDL, because nitpick is able to find a model for my system in which it is 
+false. If the FUL were already a theorem of the system, adding it wouldn't make the system any more 
+powerful, so this is the desired result.
+$\color{blue}$ Nitpick found a counterexample for card s = 1 and card i = 1:
+
+  Skolem constants:
+    a = ($\lambda x. \_$)($s_1$ := ($\lambda x. \_$)($i_1$ := False))
+    c = ($\lambda x. \_$)($i_1$ := True)
+    g = ($\lambda x. \_$)($i_1$ := False)
+    $\lambda w$. p = ($\lambda x. \_$)($i_1$ := $s_1$)
+    s = $s_1$ $\color{black}$%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
 \isadelimproof
@@
 \endisadelimproof
+\isanewline
+\isanewline
+\isacommand{axiomatization}\isamarkupfalse%
+\ \isakeyword{where}\ FUL{\isacharcolon}FUL\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ True\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
 %
 \isatagproof
+\isacommand{by}\isamarkupfalse%
+\ simp\isanewline
 %
+\isamarkupcmt{The system is still consistent! Nitpick is able to find a model in which all axioms are satisfied, 
+so this version of the FUL is consistent.
+$\color{blue}$ Nitpick found a model for card i = 1 and card s = 1:
+
+  Empty assignment $\color{black}$%
+}%
 \endisatagproof
@@
 %
-\isadelimproof
+\begin{isamarkuptext}%
+During the process of making FUL0 consistent, I used Isabelle to gain philosophical insights, 
+especially about vacuous maxims. I used Nitpick and Sledgehammer to quickly test if a small tweak 
+to FUL0 fixed the problem or if I was still able to derive a contradiction.  I then realized that if 
+I defined the circumstances, act, and goal as constant, then FUL0 was indeed consistent. After some 
+experiementation, Prof. Amin correctly pointed out that, as constants, these three entities were 
+distinct. When merely quantifying over (c, a, g), all members of a tuple could be equivalent. Within
+a minute, I could formalize this notion, add it to FUL0, and test if it solved the problem. The fact 
+that it did spurred my philosophical insight about vacuous maxims.
+
+The logic confirmed that certain kinds
+of circumstance, act, goal tuples are too badly formed for the categorical imperative to logically 
+apply to them. The realization of this subtle problem would have been incredibly difficult without 
+computational tools. The syntax and typing of Isabelle/HOL forced me to bind the free-variable $M$
+in the FUL in different ways and allowed me to quickly test many bindings. The discovery of this 
+logical inconsistency then enabled a philosophical insight about which kinds of maxims make sense as 
+practical principles. This is one way to do computational ethics: model a system in a logic, use 
+computational tools to refine and debug the logic, and then use insights about the logic to derive 
+insights about the ethical phenonema it is modelling. This procedure parallels the use of proofs in 
+theoretical math to understand the world.%
+\end{isamarkuptext}\isamarkuptrue%
 %
-\endisadelimproof
-%
-\isatagproof
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
+\begin{isamarkuptext}%
+One potential problem with my formalization is that it does not hugly use the modal nature of the system. 
+All of the properties that the FUL investigates hold at all worlds, in effect removing the modal nature 
+of the system. This approach simplifies logical and therefore computational complexity, improving 
+performance. On the other hand, it doesn't use the full expressivity of DDL. If I run into problems 
+later on, one option is to tweak the FUL to use this expressivity.%
+\end{isamarkuptext}\isamarkuptrue%
 %
@@
 %:%177=123%:%
-%:%179=125%:%
-%:%180=125%:%
+%:%178=124%:%
+%:%180=126%:%
 %:%181=126%:%
+%:%182=127%:%
 %:%183=128%:%
-%:%184=129%:%
-%:%185=130%:%
-%:%186=131%:%
-%:%187=132%:%
-%:%188=133%:%
-%:%189=134%:%
-%:%190=135%:%
-%:%191=136%:%
-%:%192=137%:%
-%:%193=138%:%
-%:%194=139%:%
-%:%195=140%:%
-%:%196=141%:%
-%:%197=142%:%
-%:%198=143%:%
-%:%199=144%:%
-%:%200=145%:%
-%:%201=146%:%
-%:%202=147%:%
-%:%203=148%:%
-%:%204=149%:%
-%:%205=150%:%
-%:%206=151%:%
-%:%207=152%:%
-%:%208=153%:%
-%:%209=154%:%
-%:%210=155%:%
-%:%211=156%:%
-%:%212=157%:%
-%:%213=158%:%
-%:%214=159%:%
-%:%215=160%:%
-%:%216=161%:%
-%:%217=162%:%
-%:%218=163%:%
-%:%219=164%:%
-%:%220=165%:%
-%:%221=166%:%
-%:%222=167%:%
-%:%223=168%:%
-%:%224=169%:%
-%:%226=172%:%
-%:%227=172%:%
-%:%228=173%:%
-%:%230=175%:%
-%:%231=176%:%
-%:%232=177%:%
-%:%233=178%:%
-%:%234=179%:%
-%:%235=180%:%
-%:%236=181%:%
-%:%237=182%:%
-%:%238=183%:%
-%:%239=184%:%
-%:%240=185%:%
-%:%241=186%:%
-%:%242=187%:%
-%:%243=188%:%
-%:%244=189%:%
-%:%245=190%:%
-%:%246=191%:%
-%:%247=192%:%
-%:%248=193%:%
-%:%249=194%:%
-%:%250=195%:%
-%:%252=197%:%
-%:%253=197%:%
-%:%254=198%:%
-%:%256=199%:%
+%:%186=130%:%
+%:%187=131%:%
+%:%188=132%:%
+%:%189=133%:%
+%:%190=134%:%
+%:%191=135%:%
+%:%192=136%:%
+%:%193=137%:%
+%:%194=138%:%
+%:%195=139%:%
+%:%196=140%:%
+%:%197=141%:%
+%:%198=142%:%
+%:%199=143%:%
+%:%200=144%:%
+%:%201=145%:%
+%:%202=146%:%
+%:%203=147%:%
+%:%204=148%:%
+%:%205=149%:%
+%:%206=150%:%
+%:%207=151%:%
+%:%208=152%:%
+%:%209=153%:%
+%:%210=154%:%
+%:%211=155%:%
+%:%212=156%:%
+%:%213=157%:%
+%:%214=158%:%
+%:%215=159%:%
+%:%216=160%:%
+%:%217=161%:%
+%:%218=162%:%
+%:%219=163%:%
+%:%220=164%:%
+%:%221=165%:%
+%:%222=166%:%
+%:%223=167%:%
+%:%224=168%:%
+%:%225=169%:%
+%:%226=170%:%
+%:%227=171%:%
+%:%229=174%:%
+%:%230=174%:%
+%:%231=175%:%
+%:%232=176%:%
+%:%235=178%:%
+%:%236=179%:%
+%:%237=180%:%
+%:%238=181%:%
+%:%239=182%:%
+%:%240=183%:%
+%:%241=184%:%
+%:%242=185%:%
+%:%243=186%:%
+%:%244=187%:%
+%:%245=188%:%
+%:%246=189%:%
+%:%247=190%:%
+%:%248=191%:%
+%:%249=192%:%
+%:%250=193%:%
+%:%251=194%:%
+%:%252=195%:%
+%:%253=196%:%
+%:%254=197%:%
+%:%255=198%:%
 %:%257=200%:%
+%:%258=200%:%
+%:%259=201%:%
 %:%260=202%:%
 %:%261=203%:%
-%:%262=204%:%
-%:%263=205%:%
-%:%264=206%:%
-%:%265=207%:%
-%:%266=208%:%
-%:%267=209%:%
-%:%268=210%:%
-%:%269=211%:%
-%:%270=212%:%
-%:%271=213%:%
-%:%272=214%:%
-%:%273=215%:%
-%:%274=216%:%
-%:%275=217%:%
-%:%276=218%:%
-%:%277=219%:%
-%:%278=220%:%
-%:%279=221%:%
-%:%280=222%:%
-%:%281=223%:%
-%:%282=224%:%
+%:%262=203%:%
+%:%263=204%:%
+%:%265=205%:%
+%:%266=206%:%
+%:%269=208%:%
+%:%270=209%:%
+%:%271=210%:%
+%:%272=211%:%
+%:%273=212%:%
+%:%274=213%:%
+%:%276=216%:%
+%:%277=216%:%
+%:%278=217%:%
+%:%279=218%:%
+%:%280=219%:%
+%:%281=219%:%
+%:%283=220%:%
+%:%284=221%:%
+%:%285=222%:%
+%:%286=223%:%
+%:%287=223%:%
+%:%288=224%:%
+%:%289=225%:%
+%:%290=225%:%
+%:%292=225%:%
+%:%296=225%:%
+%:%297=225%:%
+%:%298=226%:%
+%:%299=226%:%
+%:%300=226%:%
+%:%309=228%:%
+%:%310=229%:%
+%:%311=230%:%
+%:%312=231%:%
+%:%313=232%:%
+%:%314=233%:%
+%:%315=234%:%
+%:%316=235%:%
+%:%317=236%:%
+%:%318=237%:%
+%:%319=238%:%
+%:%320=239%:%
+%:%321=240%:%
+%:%322=241%:%
+%:%323=242%:%
+%:%324=243%:%
+%:%326=245%:%
+%:%327=245%:%
+%:%328=246%:%
+%:%330=247%:%
+%:%331=248%:%
+%:%332=248%:%
+%:%333=249%:%
+%:%334=250%:%
+%:%335=250%:%
+%:%337=251%:%
+%:%338=252%:%
+%:%339=252%:%
+%:%340=253%:%
+%:%341=254%:%
+%:%342=254%:%
+%:%343=255%:%
+%:%344=255%:%
+%:%346=255%:%
+%:%350=255%:%
+%:%351=255%:%
+%:%353=256%:%
+%:%354=257%:%
+%:%355=258%:%
+%:%356=259%:%
+%:%357=260%:%
+%:%358=261%:%
+%:%359=262%:%
+%:%360=263%:%
+%:%361=264%:%
+%:%362=265%:%
+%:%363=266%:%
+%:%371=266%:%
+%:%372=267%:%
+%:%373=268%:%
+%:%374=268%:%
+%:%375=269%:%
+%:%376=270%:%
+%:%377=270%:%
+%:%378=271%:%
+%:%379=271%:%
+%:%381=271%:%
+%:%385=271%:%
+%:%386=271%:%
+%:%388=272%:%
+%:%389=273%:%
+%:%390=274%:%
+%:%391=275%:%
+%:%392=276%:%
+%:%402=278%:%
+%:%403=279%:%
+%:%404=280%:%
+%:%405=281%:%
+%:%406=282%:%
+%:%407=283%:%
+%:%408=284%:%
+%:%409=285%:%
+%:%410=286%:%
+%:%411=287%:%
+%:%412=288%:%
+%:%413=289%:%
+%:%414=290%:%
+%:%415=291%:%
+%:%416=292%:%
+%:%417=293%:%
+%:%418=294%:%
+%:%419=295%:%
+%:%420=296%:%
+%:%424=298%:%
+%:%425=299%:%
+%:%426=300%:%
+%:%427=301%:%
+%:%428=302%:%

### 2021-10-11 paper/output/document/paper41.tex
cleaned fixed

@@
 The previous attempts to model the categorical imperative in Chapter 2 partially failed due to 
-lack of expressivity about the complexity of a maxim. Specifically, they treated actions as a single, 
+an inability to fully represent the complexity of a maxim. Specifically, they treated actions as a single, 
 monolithic unit of evaluation, whereas most Kantians consider the unit of evaluation for the FUL to the more
-complex notion of a maxim. In this section, I will present some logical background necessarily to more fully 
+complex notion of a maxim. In this section, I will present some logical background necessarily to fully 
 capture the spirit of a maxim. I will begin by borrowing some machinery to handle ``subjects" who perform 
@@
 \ s\ %
-\isamarkupcmt{s is the type for a ``subject," i.e. the subject of a sentence%
+\isamarkupcmt{s is the type for a ``subject," i.e. the subject of a sentence. In this interpretation, 
+a subject is merely defined as ``that which can act." It does not include any other properties, such as 
+rationality or dignity. As I will show, for the purposes of defining the universalizability test, this 
+``thin" representation of a subject suffices.%
 }\isanewline
@@
 \ os\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}s\ {\isasymRightarrow}\ t{\isacharparenright}{\isachardoublequoteclose}\ %
-\isamarkupcmt{Recall that an open sentence maps a subject to a term to model substitution.%
+\isamarkupcmt{Recall that an open sentence maps a subject to a term to model the 
+substitution operator.%
 }\isanewline
@@
 \isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
-\ maxim\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}t\ {\isacharasterisk}\ os\ {\isacharasterisk}\ t{\isacharparenright}{\isachardoublequoteclose}\ %
-\isamarkupcmt{I define a maxim as a circumstance, act, goal tuple (C, A, G), read 
-as ``In circumstances C, act A for goal G." Isabelle's strict typing rules mean that the choice of the 
-type of each member of this tuple is significant. A circumstance is represented as a set of worlds 
-$t$ where that circumstance holds. A goal is also a term because it can be true or false at a world if it 
-is realized or not. An act is an open sentence because an act itself is not the kind of thing that can 
-be true or false (as in, an act is not truth-apt), but the combination of a subject performing an act 
-can be true or false at a world depending on whether or not the act is indeed performed by that subject. 
-For example, ``running" is not truth-apt, but ``Sara runs" is truth-apt.%
-}%
+\ maxim\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}t\ {\isacharasterisk}\ os\ {\isacharasterisk}\ t{\isacharparenright}{\isachardoublequoteclose}%
 \begin{isamarkuptext}%
+The central unit of evaluation for the universalizability test is a ``maxim," which Kant defines 
+in a footnote in \emph{Groundworkd} as ``the subjective principle of willing," or the principle that 
+the agent acts on $\cite[16]{groundwork}$. Modern Kantians differ in their interpretations of this definition. The naive view 
+is that a maxim is an act, but Korsgaard adopts the more sophisticated view that a maxim is composed
+of an act and the agent's purpose for acting \cite{actingforareason}. She also compares a maxim 
+to Aristotle's logos, which includes these components and information about the circumstances and methods 
+of the act. O'Neill concludes that Kant's examples imply that a maxim must also include circumstances \cite{actingonprinciple}, and 
+Kitcher \cite{whatisamaxim} uses textual evidence from the Groundwork to argue for the inclusion of a maxim's purpose 
+or motivation. In order to formalize the notion of a maxim, I must adopt a specific definition and 
+defend my choice.
+
 I define a maxim as a circumstance, act, goal tuple (C, A, G), read 
@@
 
-My definition of a maxim is inspired by Onora O'Neill's work on maxims. I will defend my representation
-below and consider an additional component that Patricia Kitcher argues for.
+My definition of a maxim is inspired by O'Neill's work on maxims. I will defend my representation
+below and consider an additional component that Kitcher argues for.
 
@@
 
-O'Neill$\footnote{p. 37}$ \cite{actingonprinciple} presents what Kitcher \cite{whatisamaxim}  calls the widely accepted 
+O'Neill $\cite[37]{actingonprinciple}$ presents what Kitcher \cite{whatisamaxim}  calls the widely accepted 
 view that a maxim is a circumstance, act, goal tuple. A maxim 
@@
 example maxims and because Kant argues that human activity, because it is guided by a rational will, 
-is inherently purposive\cite{groundwork}\footnote{(G 4:428)}. A rational will does not act randomly (else it would not be rational), 
+is inherently purposive $\cite[4:428]{groundwork}$. A rational will does not act randomly (else it would not be rational), 
 but instead in the pursuit of ends which it deems valuable. This inclusion is also essential for the version of the universalizability test 
@@
 O'Neill's inclusion of circumstances is potentially controversial because it leaves open the question of what qualifies as a 
-relevant circumstance for a particular maxim. This is gives rise to ``the tailoring objection" \cite{whatisamaxim}$\footnote{Kitcher
-on p.217 cites Wood p. 102 \cite{kantsethicalthought} as offering an example of a false positive due to this objection.}$, 
+relevant circumstance for a particular maxim. This is gives rise to ``the tailoring objection" $\cite[217]{whatisamaxim} \footnote{Kitcher
+cites \cite{kantsethicalthought}  as offering an example of a false positive due to this objection.}$, 
 under which maxims are arbitrarily specified to pass the FUL. For example, the maxim ``When my name is Lavanya Singh,
@@
 
-O'Neill seems to acknowledge the difficult of determining relevant circumstances when she concedes that a maxim cannot include all 
-of the infinitely many circumstances in which the agent may perform the action$\footnote{p. 37}$. She argues that this is 
+O'Neill seems to acknowledge the difficulty of determining relevant circumstances when she concedes that a maxim cannot include all 
+of the infinitely many circumstances in which the agent may perform the action$\cite[4:428]{actingonprinciple}$. She argues that this is 
 an artifact of the fact that maxims are rules of practical reason, the kind of reason that helps us decide what to do 
@@
 While this may appear to be a weakness of my system, I believe that it actually
-allows my system to retain some of the human complexity that many philosophers agree cannot be automated away.\footnote{Powers \cite{powers} presents 
-the determination of morally relevant circumstances as an obstacle to the automation of Kantian ethics.}
+allows my system to retain some of the human complexity that many philosophers agree cannot be automated away.\footnote{Powers presents 
+the determination of morally relevant circumstances as an obstacle to the automation of Kantian ethics \cite{powers}.}
 Ethics is a fundamentally human activity. Kant argues that the categorical imperative is a statement 
@@
 
-Kitcher \cite{whatisamaxim} begins with O'Niell's circumstance, act, goal view and expands it to include the motive 
-behind performing the maxim. This additional component is read 
+Kitcher begins with O'Niell's circumstance, act, goal view and expands it to include the motive 
+behind performing the maxim \cite{whatisamaxim}. This additional component is read 
 as ``In circumstance C, I will do A in order to G because of M," where M may be ``duty" or ``self-love."
@@
 derives the motive that Kitcher bundles into the maxim, so automating the FUL does not require 
-including a motive. The ``input" to the FUL is the circumstance, act, goal pair. My project takes 
+including a motive. The ``input" to the FUL is the circumstance, act, goal tuple. My project takes 
 this input and returns the motivation that the dutiful, moral agent would adopt. Additionally, doing
@@
 Korsgaard claims that ``to will an end, rather than just
-wishing for it or wanting it, is to set yourself to be its cause" \cite{sources}. To will a maxim, then, 
-is to set yourself to, in the relevant circumstances, be the cause of its goal by taking the means 
-specified in the maxim. This coheres with 
-Kitcher's and Korsgaard's understanding of a maxim as a principle or rule to live by. At worlds 
+wishing for it or wanting it, is to set yourself to be its cause" \cite{sources}. To will a maxim
+is to set yourself to be the cause of its goal by taking the means 
+specified in the maxim in the relevant circumstances. This coheres with 
+Kitcher's and Korsgaard's understanding of a maxim as a principle or rule to live by.
+
+At worlds
 where the circumstances do not hold, a maxim is vacuously willed. If you decide to act on the rule ``I will 
@@
 between the evaluation of a principle, which is generic, and a maxim, which she views as ``individuated only 
-by referring to a person"$\footnote{p. 13}$ \cite{actingonprinciple}. I adopt the spirit of this interpretation but modify it slightly 
+by referring to a person"$\cite[13]{actingonprinciple}$. I adopt the spirit of this interpretation but modify it slightly 
 by representing the general maxim as a principle that anyone could adopt, and the act of willing the maxim 
@@
 I additionally represent a subject as willing a maxim because I use the word `will' as a verb, to mean committing oneself to living by
-the principle of a maxim. This coheres with Kant's Formula of Universal Law, because it tests the willing 
-of a maxim to determine if it could be a universal law that everyone committed to. Formalizing this idea,
-the type of a maxim that is willed is a term, allowing me
-to use DDL's obligation operator on the notion of willing a maxim.
+the principle of a maxim. This coheres with the FUL, which tests the act willing 
+of a maxim by determining if the maxim could be a universal law that everyone committed to. Formalizing this idea,
+the type of a willed maxim is a term, allowing me
+to use DDL's obligation operator on the notion of willing a maxim. Concretely, my system will prove 
+or disprove statements of the form ``Lavanya is obligated to will the maxim M."
 
 Worlds where the circumstances do not hold are not relevant for determining obligation. Recall that in 
-our definition of the obligation operator, we define $O \{B|A\}$ to be true at all worlds iff ob(B)(A), or 
+\cite{BFP}'s definition of the obligation operator,  $O \{B|A\}$ is true at all worlds iff ob(B)(A), or 
 if the obligation function maps A to obligatory in context B (where the context is a set of worlds). This 
-definition implies that worlds outside of B have no bearing on the obligatory-ness of A in context B, which 
-coheres with intuitions about obligation in a context. Thus, the dyadic obligation operator 
+definition implies that worlds outside of B have no bearing on the moral status of A in context B, which 
+coheres with intuitions about contextual obligation. Thus, the dyadic obligation operator 
 disqualifies worlds where the context does not hold, so the vacuous truth of the will statement in 
@@
 
-Given that the will function already excludes worlds where the circumstances fail (by rendering 
+Given that the will abbreviation already excludes worlds where the circumstances fail (by rendering 
 the statement vacuously true at them), one may conclude that the dyadic obligation operator is now useless. 
@@
 A maxim is effective for a subject when, if the subject wills it then the goal is achieved, and
-when the subject does not act on it, the goal is not achieved.$\footnote{Thank you to Jeremy D. Zucker for helping me think through this.}$ \cite{sepcausation} 
+when the subject does not act on it, the goal is not achieved$\footnote{Thank you to Jeremy D. Zucker for helping me think through this.}$ \cite{sepcausation}. 
 The former direction of the implication 
@@
 counterfactual world—the circumstances are identical and we neither added additional theorems nor 
-specified the model any further. This represents Lewis's idea of "comparative similarity," \cite{lewiscounterfactuals} where 
-a counterfactual is true if it holds at the most similar world. In our case, this is just the world 
+specified the model any further. This represents Lewis's idea of "comparative similarity,"  where 
+a counterfactual is true if it holds at the most similar world \cite{lewiscounterfactuals}. In our case, this is just the world 
 where everything is the same except the maxim is not acted on.
@@
 \begin{isamarkuptext}%
-FUL0 is not consistent, and sledgehammer is indeed able to show that it implies a contradiction. 
-The axioms that sledgehammer used are O\_diamond, which is \isa{{\isasymTurnstile}{\isasymlambda}w{\isachardot}\ ob\ {\isacharquery}B\ {\isacharquery}A\ {\isasymlongrightarrow}\ {\isasymnot}\ {\isasymTurnstile}\isactrlbold {\isasymnot}\ {\isacharquery}B\isactrlbold {\isasymand}{\isacharquery}A}.
+FUL0 is not consistent, and sledgehammer is able to prove this by showing that it implies a contradiction 
+usig axiom O\_diamond, which is \isa{{\isasymTurnstile}{\isasymlambda}w{\isachardot}\ ob\ {\isacharquery}B\ {\isacharquery}A\ {\isasymlongrightarrow}\ {\isasymnot}\ {\isasymTurnstile}\isactrlbold {\isasymnot}\ {\isacharquery}B\isactrlbold {\isasymand}{\isacharquery}A}.
 This axiom captures
@@
 
-To get around this, I will exclude what I call ``badly formed maxims," which are those maxims sucht that the goal has already been 
+To get around this, I will exclude what I call ``badly formed maxims," which are those maxims such that the goal has already been 
 achieved or the act has already been acted on. Under my formalization, such maxims are 
-not well-formed. To understand why, we can return to Korsgaard's and O'Neill's interpretations of a maxim as a practical
+not well-formed. To understand why, I return to Korsgaard's and O'Neill's interpretations of a maxim as a practical
 guide to action. A maxim is a practical principle that guides how we behave in everyday life. A 
 principle of the form ``When you are eating breakfast, eat breakfast in order to eat breakfast," is not 
-practically relevant. No agent would ever need to act on such a principle. It's not necessarily contradictory
-or prohibited, but it is the wrong kind of question to be asking yourself. It is not a 
+practically relevant. No agent would ever need to act on such a principle. It is not contradictory
+or prohibited, but it is the wrong kind of question to be asking. It is not a 
 well-formed maxim, so the categorical imperative does not apply to it.%
@@
 powerful, so this is the desired result.
+
 $\color{blue}$ Nitpick found a counterexample for card s = 1 and card i = 1:
@@
 %
-\isamarkupcmt{The system is still consistent! Nitpick is able to find a model in which all axioms are satisfied, 
+\isamarkupcmt{Nitpick is able to find a model in which all axioms are satisfied, 
 so this version of the FUL is consistent.
+
 $\color{blue}$ Nitpick found a model for card i = 1 and card s = 1:
@@
 \begin{isamarkuptext}%
-During the process of making FUL0 consistent, I used Isabelle to gain philosophical insights, 
-especially about vacuous maxims. I used Nitpick and Sledgehammer to quickly test if a small tweak 
-to FUL0 fixed the problem or if I was still able to derive a contradiction.  I then realized that if 
-I defined the circumstances, act, and goal as constant, then FUL0 was indeed consistent. After some 
-experiementation, Prof. Amin correctly pointed out that, as constants, these three entities were 
-distinct. When merely quantifying over (c, a, g), all members of a tuple could be equivalent. Within
+During the process of making FUL0 consistent, I used Isabelle to gain philosophical insights 
+about vacuous maxims. This process is an example of the power of computational tools to aid
+philosophical progress. I used Nitpick and Sledgehammer to quickly test if a small tweak 
+to FUL0 fixed the inconsistency or if I was still able to derive a contradiction.  I then realized that if 
+I defined the circumstances, act, and goal as constants, then FUL0 was indeed consistent. After some 
+experimentation, Prof. Amin correctly pointed out that as constants, these three entities were 
+distinct. However, when merely quantifying over (c, a, g), all members of a tuple could be equivalent. Within
 a minute, I could formalize this notion, add it to FUL0, and test if it solved the problem. The fact 
@@
 insights about the ethical phenonema it is modelling. This procedure parallels the use of proofs in 
-theoretical math to understand the world.%
+theoretical math to understand the mathematical objects they model.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-One potential problem with my formalization is that it does not hugly use the modal nature of the system. 
+One potential problem with my formalization is that it does not use the modal nature of the system. 
 All of the properties that the FUL investigates hold at all worlds, in effect removing the modal nature 
@@
 %:%67=20%:%
-%:%68=20%:%
-%:%69=21%:%
-%:%70=22%:%
-%:%71=22%:%
-%:%72=22%:%
-%:%73=22%:%
-%:%74=23%:%
-%:%75=24%:%
-%:%76=24%:%
-%:%77=24%:%
-%:%78=25%:%
-%:%79=26%:%
-%:%80=27%:%
-%:%81=28%:%
-%:%82=29%:%
-%:%83=30%:%
-%:%84=31%:%
-%:%87=33%:%
-%:%88=34%:%
-%:%89=35%:%
-%:%90=36%:%
-%:%91=37%:%
-%:%92=38%:%
-%:%93=39%:%
-%:%94=40%:%
-%:%95=41%:%
-%:%96=42%:%
-%:%97=43%:%
-%:%98=44%:%
-%:%99=45%:%
-%:%100=46%:%
-%:%101=47%:%
-%:%102=48%:%
-%:%103=49%:%
-%:%104=50%:%
-%:%105=51%:%
-%:%106=52%:%
-%:%107=53%:%
-%:%108=54%:%
-%:%109=55%:%
-%:%110=56%:%
-%:%111=57%:%
-%:%112=58%:%
-%:%113=59%:%
-%:%114=60%:%
-%:%115=61%:%
-%:%116=62%:%
-%:%117=63%:%
-%:%118=64%:%
-%:%119=65%:%
-%:%120=66%:%
-%:%121=67%:%
-%:%122=68%:%
-%:%123=69%:%
-%:%124=70%:%
-%:%125=71%:%
-%:%126=72%:%
-%:%127=73%:%
-%:%128=74%:%
-%:%129=75%:%
-%:%130=76%:%
-%:%131=77%:%
-%:%132=78%:%
-%:%133=79%:%
-%:%134=80%:%
-%:%135=81%:%
-%:%136=82%:%
-%:%137=83%:%
-%:%138=84%:%
-%:%139=85%:%
-%:%140=86%:%
-%:%141=87%:%
-%:%142=88%:%
-%:%143=89%:%
-%:%144=90%:%
-%:%145=91%:%
-%:%146=92%:%
-%:%147=93%:%
-%:%148=94%:%
-%:%149=95%:%
-%:%150=96%:%
-%:%151=97%:%
-%:%152=98%:%
-%:%153=99%:%
-%:%154=100%:%
-%:%155=101%:%
-%:%156=102%:%
-%:%157=103%:%
-%:%158=104%:%
-%:%159=105%:%
-%:%160=106%:%
-%:%161=107%:%
-%:%162=108%:%
-%:%163=109%:%
-%:%164=110%:%
-%:%165=111%:%
-%:%166=112%:%
-%:%167=113%:%
-%:%168=114%:%
-%:%169=115%:%
-%:%170=116%:%
-%:%171=117%:%
-%:%172=118%:%
-%:%173=119%:%
-%:%174=120%:%
-%:%175=121%:%
-%:%176=122%:%
-%:%177=123%:%
-%:%178=124%:%
-%:%180=126%:%
-%:%181=126%:%
-%:%182=127%:%
-%:%183=128%:%
-%:%186=130%:%
-%:%187=131%:%
-%:%188=132%:%
-%:%189=133%:%
-%:%190=134%:%
-%:%191=135%:%
-%:%192=136%:%
-%:%193=137%:%
-%:%194=138%:%
-%:%195=139%:%
-%:%196=140%:%
-%:%197=141%:%
-%:%198=142%:%
-%:%199=143%:%
-%:%200=144%:%
-%:%201=145%:%
-%:%202=146%:%
-%:%203=147%:%
-%:%204=148%:%
-%:%205=149%:%
-%:%206=150%:%
-%:%207=151%:%
-%:%208=152%:%
-%:%209=153%:%
-%:%210=154%:%
-%:%211=155%:%
-%:%212=156%:%
-%:%213=157%:%
-%:%214=158%:%
-%:%215=159%:%
-%:%216=160%:%
-%:%217=161%:%
-%:%218=162%:%
-%:%219=163%:%
-%:%220=164%:%
-%:%221=165%:%
-%:%222=166%:%
-%:%223=167%:%
-%:%224=168%:%
-%:%225=169%:%
-%:%226=170%:%
-%:%227=171%:%
-%:%229=174%:%
-%:%230=174%:%
-%:%231=175%:%
-%:%232=176%:%
-%:%235=178%:%
-%:%236=179%:%
-%:%237=180%:%
-%:%238=181%:%
-%:%239=182%:%
-%:%240=183%:%
-%:%241=184%:%
-%:%242=185%:%
-%:%243=186%:%
-%:%244=187%:%
-%:%245=188%:%
-%:%246=189%:%
-%:%247=190%:%
-%:%248=191%:%
-%:%249=192%:%
-%:%250=193%:%
-%:%251=194%:%
-%:%252=195%:%
-%:%253=196%:%
-%:%254=197%:%
-%:%255=198%:%
-%:%257=200%:%
-%:%258=200%:%
-%:%259=201%:%
-%:%260=202%:%
-%:%261=203%:%
-%:%262=203%:%
-%:%263=204%:%
-%:%265=205%:%
-%:%266=206%:%
-%:%269=208%:%
-%:%270=209%:%
-%:%271=210%:%
-%:%272=211%:%
-%:%273=212%:%
-%:%274=213%:%
-%:%276=216%:%
-%:%277=216%:%
-%:%278=217%:%
-%:%279=218%:%
-%:%280=219%:%
-%:%281=219%:%
-%:%283=220%:%
-%:%284=221%:%
-%:%285=222%:%
-%:%286=223%:%
-%:%287=223%:%
-%:%288=224%:%
-%:%289=225%:%
-%:%290=225%:%
-%:%292=225%:%
-%:%296=225%:%
-%:%297=225%:%
-%:%298=226%:%
-%:%299=226%:%
-%:%300=226%:%
-%:%309=228%:%
-%:%310=229%:%
-%:%311=230%:%
-%:%312=231%:%
-%:%313=232%:%
-%:%314=233%:%
-%:%315=234%:%
-%:%316=235%:%
-%:%317=236%:%
-%:%318=237%:%
-%:%319=238%:%
-%:%320=239%:%
-%:%321=240%:%
-%:%322=241%:%
-%:%323=242%:%
-%:%324=243%:%
-%:%326=245%:%
-%:%327=245%:%
-%:%328=246%:%
-%:%330=247%:%
-%:%331=248%:%
-%:%332=248%:%
-%:%333=249%:%
-%:%334=250%:%
-%:%335=250%:%
-%:%337=251%:%
-%:%338=252%:%
-%:%339=252%:%
-%:%340=253%:%
-%:%341=254%:%
-%:%342=254%:%
-%:%343=255%:%
-%:%344=255%:%
-%:%346=255%:%
-%:%350=255%:%
-%:%351=255%:%
-%:%353=256%:%
-%:%354=257%:%
-%:%355=258%:%
-%:%356=259%:%
-%:%357=260%:%
-%:%358=261%:%
-%:%359=262%:%
-%:%360=263%:%
-%:%361=264%:%
-%:%362=265%:%
-%:%363=266%:%
-%:%371=266%:%
-%:%372=267%:%
-%:%373=268%:%
-%:%374=268%:%
-%:%375=269%:%
-%:%376=270%:%
-%:%377=270%:%
-%:%378=271%:%
-%:%379=271%:%
-%:%381=271%:%
-%:%385=271%:%
-%:%386=271%:%
-%:%388=272%:%
-%:%389=273%:%
-%:%390=274%:%
-%:%391=275%:%
-%:%392=276%:%
-%:%402=278%:%
-%:%403=279%:%
-%:%404=280%:%
-%:%405=281%:%
-%:%406=282%:%
-%:%407=283%:%
-%:%408=284%:%
-%:%409=285%:%
-%:%410=286%:%
-%:%411=287%:%
-%:%412=288%:%
-%:%413=289%:%
-%:%414=290%:%
-%:%415=291%:%
-%:%416=292%:%
-%:%417=293%:%
-%:%418=294%:%
-%:%419=295%:%
-%:%420=296%:%
-%:%424=298%:%
-%:%425=299%:%
-%:%426=300%:%
-%:%427=301%:%
-%:%428=302%:%
+%:%68=21%:%
+%:%69=22%:%
+%:%70=23%:%
+%:%71=23%:%
+%:%72=24%:%
+%:%73=25%:%
+%:%74=25%:%
+%:%75=25%:%
+%:%76=26%:%
+%:%77=26%:%
+%:%78=27%:%
+%:%79=28%:%
+%:%80=28%:%
+%:%82=30%:%
+%:%83=31%:%
+%:%84=32%:%
+%:%85=33%:%
+%:%86=34%:%
+%:%87=35%:%
+%:%88=36%:%
+%:%89=37%:%
+%:%90=38%:%
+%:%91=39%:%
+%:%92=40%:%
+%:%93=41%:%
+%:%94=42%:%
+%:%95=43%:%
+%:%96=44%:%
+%:%97=45%:%
+%:%98=46%:%
+%:%99=47%:%
+%:%100=48%:%
+%:%101=49%:%
+%:%102=50%:%
+%:%103=51%:%
+%:%104=52%:%
+%:%105=53%:%
+%:%106=54%:%
+%:%107=55%:%
+%:%108=56%:%
+%:%109=57%:%
+%:%110=58%:%
+%:%111=59%:%
+%:%112=60%:%
+%:%113=61%:%
+%:%114=62%:%
+%:%115=63%:%
+%:%116=64%:%
+%:%117=65%:%
+%:%118=66%:%
+%:%119=67%:%
+%:%120=68%:%
+%:%121=69%:%
+%:%122=70%:%
+%:%123=71%:%
+%:%124=72%:%
+%:%125=73%:%
+%:%126=74%:%
+%:%127=75%:%
+%:%128=76%:%
+%:%129=77%:%
+%:%130=78%:%
+%:%131=79%:%
+%:%132=80%:%
+%:%133=81%:%
+%:%134=82%:%
+%:%135=83%:%
+%:%136=84%:%
+%:%137=85%:%
+%:%138=86%:%
+%:%139=87%:%
+%:%140=88%:%
+%:%141=89%:%
+%:%142=90%:%
+%:%143=91%:%
+%:%144=92%:%
+%:%145=93%:%
+%:%146=94%:%
+%:%147=95%:%
+%:%148=96%:%
+%:%149=97%:%
+%:%150=98%:%
+%:%151=99%:%
+%:%152=100%:%
+%:%153=101%:%
+%:%154=102%:%
+%:%155=103%:%
+%:%156=104%:%
+%:%157=105%:%
+%:%158=106%:%
+%:%159=107%:%
+%:%160=108%:%
+%:%161=109%:%
+%:%162=110%:%
+%:%163=111%:%
+%:%164=112%:%
+%:%165=113%:%
+%:%166=114%:%
+%:%167=115%:%
+%:%168=116%:%
+%:%169=117%:%
+%:%170=118%:%
+%:%171=119%:%
+%:%172=120%:%
+%:%173=121%:%
+%:%174=122%:%
+%:%175=123%:%
+%:%176=124%:%
+%:%177=125%:%
+%:%178=126%:%
+%:%179=127%:%
+%:%180=128%:%
+%:%181=129%:%
+%:%182=130%:%
+%:%183=131%:%
+%:%184=132%:%
+%:%186=134%:%
+%:%187=134%:%
+%:%188=135%:%
+%:%189=136%:%
+%:%192=138%:%
+%:%193=139%:%
+%:%194=140%:%
+%:%195=141%:%
+%:%196=142%:%
+%:%197=143%:%
+%:%198=144%:%
+%:%199=145%:%
+%:%200=146%:%
+%:%201=147%:%
+%:%202=148%:%
+%:%203=149%:%
+%:%204=150%:%
+%:%205=151%:%
+%:%206=152%:%
+%:%207=153%:%
+%:%208=154%:%
+%:%209=155%:%
+%:%210=156%:%
+%:%211=157%:%
+%:%212=158%:%
+%:%213=159%:%
+%:%214=160%:%
+%:%215=161%:%
+%:%216=162%:%
+%:%217=163%:%
+%:%218=164%:%
+%:%219=165%:%
+%:%220=166%:%
+%:%221=167%:%
+%:%222=168%:%
+%:%223=169%:%
+%:%224=170%:%
+%:%225=171%:%
+%:%226=172%:%
+%:%227=173%:%
+%:%228=174%:%
+%:%229=175%:%
+%:%230=176%:%
+%:%231=177%:%
+%:%232=178%:%
+%:%233=179%:%
+%:%234=180%:%
+%:%235=181%:%
+%:%236=182%:%
+%:%238=185%:%
+%:%239=185%:%
+%:%240=186%:%
+%:%241=187%:%
+%:%244=189%:%
+%:%245=190%:%
+%:%246=191%:%
+%:%247=192%:%
+%:%248=193%:%
+%:%249=194%:%
+%:%250=195%:%
+%:%251=196%:%
+%:%252=197%:%
+%:%253=198%:%
+%:%254=199%:%
+%:%255=200%:%
+%:%256=201%:%
+%:%257=202%:%
+%:%258=203%:%
+%:%259=204%:%
+%:%260=205%:%
+%:%261=206%:%
+%:%262=207%:%
+%:%263=208%:%
+%:%264=209%:%
+%:%266=211%:%
+%:%267=211%:%
+%:%268=212%:%
+%:%269=213%:%
+%:%270=214%:%
+%:%271=214%:%
+%:%272=215%:%
+%:%274=216%:%
+%:%275=217%:%
+%:%278=219%:%
+%:%279=220%:%
+%:%280=221%:%
+%:%281=222%:%
+%:%282=223%:%
+%:%283=224%:%
+%:%285=227%:%
+%:%286=227%:%
+%:%287=228%:%
+%:%288=229%:%
+%:%289=230%:%
+%:%290=230%:%
+%:%292=231%:%
+%:%293=232%:%
+%:%294=233%:%
+%:%295=234%:%
+%:%296=234%:%
+%:%297=235%:%
+%:%298=236%:%
+%:%299=236%:%
+%:%301=236%:%
+%:%305=236%:%
+%:%306=236%:%
+%:%307=237%:%
+%:%308=237%:%
+%:%309=237%:%
+%:%318=239%:%
+%:%319=240%:%
+%:%320=241%:%
+%:%321=242%:%
+%:%322=243%:%
+%:%323=244%:%
+%:%324=245%:%
+%:%325=246%:%
+%:%326=247%:%
+%:%327=248%:%
+%:%328=249%:%
+%:%329=250%:%
+%:%330=251%:%
+%:%331=252%:%
+%:%332=253%:%
+%:%333=254%:%
+%:%335=256%:%
+%:%336=256%:%
+%:%337=257%:%
+%:%339=258%:%
+%:%340=259%:%
+%:%341=259%:%
+%:%342=260%:%
+%:%343=261%:%
+%:%344=261%:%
+%:%346=262%:%
+%:%347=263%:%
+%:%348=263%:%
+%:%349=264%:%
+%:%350=265%:%
+%:%351=265%:%
+%:%352=266%:%
+%:%353=266%:%
+%:%355=266%:%
+%:%359=266%:%
+%:%360=266%:%
+%:%362=267%:%
+%:%363=268%:%
+%:%364=269%:%
+%:%365=270%:%
+%:%366=271%:%
+%:%367=272%:%
+%:%368=273%:%
+%:%369=274%:%
+%:%370=275%:%
+%:%371=276%:%
+%:%372=277%:%
+%:%373=278%:%
+%:%381=278%:%
+%:%382=279%:%
+%:%383=280%:%
+%:%384=280%:%
+%:%385=281%:%
+%:%386=282%:%
+%:%387=282%:%
+%:%388=283%:%
+%:%389=283%:%
+%:%391=283%:%
+%:%395=283%:%
+%:%396=283%:%
+%:%398=284%:%
+%:%399=285%:%
+%:%400=286%:%
+%:%401=287%:%
+%:%402=288%:%
+%:%403=289%:%
+%:%413=291%:%
+%:%414=292%:%
+%:%415=293%:%
+%:%416=294%:%
+%:%417=295%:%
+%:%418=296%:%
+%:%419=297%:%
+%:%420=298%:%
+%:%421=299%:%
+%:%422=300%:%
+%:%423=301%:%
+%:%424=302%:%
+%:%425=303%:%
+%:%426=304%:%
+%:%427=305%:%
+%:%428=306%:%
+%:%429=307%:%
+%:%430=308%:%
+%:%431=309%:%
+%:%432=310%:%
+%:%436=312%:%
+%:%437=313%:%
+%:%438=314%:%
+%:%439=315%:%
+%:%440=316%:%

### 2021-10-11 paper/output/document/threeflags.tex
cleaned fixed

@@
 \begin{isamarkuptext}%
-The literature on Kantian ethics is expansive and complicated. To focus my thesis on the contributions 
-of automated ethics to Kantian thought, I make the following choices.
-
 $\textbf{Choice to Formalize the FUL}$
 
-I am only studying formalizations of Kant's first formulation of the categorical imperative,
+In \emph{Groundwork of the Metaphysics of Morals}, Kant presents three formulations, or versions, 
+of what he calls the ``supreme law of morality." I will focus on the first of these three formulations, 
+and below I explain the formulations and defend my choice.
+
+Kant argues that if  morality 
+exists, it must take the form of a categorical imperative or a law that holds unconditionally. Categorical
+imperatives are contrasted with hypothetical imperatives, which take the form of conditionals as in, 
+``If I want to get good grades, I must study hard." Hypothetical imperatives only have force so long
+as the antecedent holds, but the categorical imperative is unconditionally binding $\cite[28]{groundwork}$. In the first 
+half of \emph{Groundwork}, Kant examines what the categorical imperative, if such a thing exists and has force,
+must be. He concludes that there are three ``formulations" of the categorical imperative, or three ways 
+of articulating the supreme law of morality.
+
+The first formulation of the categorical imperative is the
+formula of universal law (FUL), which reads, ``act only according to that maxim through which you can 
+at the same time will that it become a universal law." $\cite[34]{groundwork}$ This formulation
+generates the universalizability test, which ``tests" the moral value of a maxim by 
+imagining a world in which it becomes a universal law and attempting to will the maxim in that world. The 
+second formulation of the categorical imperative is the formula of humanity (FUH): ``So act that you use humanity, 
+in your own person, as well as in the person of any other, always at the same time as an end, never merely 
+as a means." $\cite[41]{groundwork}$. This formulation is often understood as requiring us to 
+acknowledge and respect the dignity of every other person. The third formulation of the categorical 
+imperative is the formula of autonomy (FOA), which Korsgaard summarizes in her introduction to the Groundwork 
+as, ``we should so act that we may think of ourselves as legislating universal laws through our 
+maxims." $\cite[28]{korsgaardintro}$ While closely related to the FUL, the FOA presents morality as the activity of 
+perfectly rational agents in an ideal ``kingdom of ends," guided by what Kant calls the ``laws of freedom."
+
+I choose to focus on formalizations of Kant's first formulation of the categorical imperative,
 the formula of universal law (FUL), because it is the most formal and thus the easiest to formalize and implement. 
-Onora O'Neill \cite{actingonprinciple}\footnote{p. 33} explains that the formalism of the FUL allows 
-for greater precision in philosophical arguments analyzing its implications and power. This precision 
+Onora O'Neill explains that the formalism of the FUL allows 
+for greater precision in philosophical arguments analyzing its implications and power $\cite[33]{actingonprinciple}$. This precision 
 is particularly useful in a computational context because any formalism necessarily makes its content 
@@
 
-While some criticize the FUL for its formalism and percieved ``sterility" \cite{actingonprinciple}, 
-Kantian constructivists embrace it. My project is not committed to Kantian constructivism; I argue that computational
-ethics is a valuable tool for any ethicist, with a focus on general Kantian ethics. Nonetheless, Kantian constructivists may find the focus on 
+While some criticize the FUL for its formalism and percieved ``sterility" $\cite[33]{actingonprinciple}$, 
+Kantian constructivists embrace it $\cite[173]{ebelsduggan}$. My project is not committed to Kantian constructivism. 
+I believe that computational ethics is likely a valuable tool for any ethicist, and I make the case 
+for Kantian ethics specifically. Nonetheless, Kantian constructivists may find the focus on 
 the FUL particularly appealing.
@@
 
+The central unit of evaluation for the universalizability test is a ``maxim," which Kant defines 
+in a footnote in \emph{Groundworkd} as ``the subjective principle of willing," or the principle that 
+the agent acts on $\cite[16]{groundwork}$. Modern Kantians differ in their interpretations of this definition. The naive view 
+is that a maxim is an act, but Korsgaard adopts the more sophisticated view that a maxim is composed
+of an act and the agent's purpose for acting \cite{actingforareason}. She also compares a maxim 
+to Aristotle's logos, which includes these components and information about the circumstances and methods 
+of the act. O'Neill concludes that Kant's examples imply that a maxim must also include circumstances \cite{actingonprinciple}, and 
+Kitcher \cite{whatisamaxim} uses textual evidence from the Groundwork to argue for the inclusion of a maxim's purpose 
+or motivation. In order to formalize the notion of a maxim, I must adopt a specific definition and 
+defend my choice.
+
 I define a maxim as a circumstance, act, goal tuple (C, A, G), read 
@@
 
-Kantians debate the correct interpretation of the formula of universal law because Kant, 
-at times, appears to interpret the universalizability test in different ways. My project uses Korsgaard's practical contradiction 
-interpretation, broadly accepted as correct within the philosophical community \cite{ebelsduggan}\footnote{p. 177}.
+Kantians debate the correct interpretation of the formula of universal law because Kant appears to 
+interpret the universalizability test in different ways. My project uses Korsgaard's practical contradiction 
+interpretation, broadly accepted as correct within the philosophical community $\cite[177]{ebelsduggan}$.
 Below, I briefly reconstruct Korsgaard's argument for the practical contradiction interpretation. While 
@@
 Recall that the formula of universal law is “act only in accordance with that maxim through which you can at the 
-same time will that it become a universal law” \cite{groundwork}\footnote{(G: 4:421)}. To determine if a maxim can be willed as a 
+same time will that it become a universal law” $\cite[4:421]{groundwork}$. To determine if a maxim can be willed as a 
 universal law, one must use the “universalizability test,” which requires imagining a world in which 
@@
 %:%file=~/Desktop/cs91r/paper/threeflags.thy%:%
-%:%19=7%:%
-%:%20=8%:%
-%:%21=9%:%
-%:%22=10%:%
-%:%23=11%:%
-%:%24=12%:%
-%:%25=13%:%
-%:%26=14%:%
-%:%27=15%:%
-%:%28=16%:%
-%:%29=17%:%
-%:%30=18%:%
-%:%31=19%:%
-%:%32=20%:%
-%:%33=21%:%
-%:%34=22%:%
-%:%35=23%:%
-%:%36=24%:%
-%:%37=25%:%
-%:%38=26%:%
-%:%39=27%:%
-%:%40=28%:%
-%:%41=29%:%
-%:%42=30%:%
-%:%43=31%:%
-%:%44=32%:%
-%:%45=33%:%
-%:%46=34%:%
-%:%47=35%:%
-%:%48=36%:%
-%:%49=37%:%
-%:%50=38%:%
-%:%51=39%:%
-%:%52=40%:%
-%:%53=41%:%
-%:%54=42%:%
-%:%55=43%:%
-%:%56=44%:%
-%:%57=45%:%
-%:%58=46%:%
-%:%59=47%:%
-%:%60=48%:%
-%:%61=49%:%
-%:%62=50%:%
-%:%63=51%:%
-%:%64=52%:%
-%:%65=53%:%
-%:%66=54%:%
-%:%67=55%:%
-%:%68=56%:%
-%:%69=57%:%
-%:%70=58%:%
-%:%71=59%:%
-%:%72=60%:%
-%:%73=61%:%
-%:%74=62%:%
-%:%75=63%:%
-%:%76=64%:%
-%:%77=65%:%
-%:%78=66%:%
-%:%79=67%:%
-%:%80=68%:%
-%:%81=69%:%
-%:%82=70%:%
-%:%83=71%:%
-%:%84=72%:%
-%:%85=73%:%
-%:%86=74%:%
-%:%87=75%:%
-%:%88=76%:%
-%:%89=77%:%
-%:%90=78%:%
-%:%91=79%:%
-%:%92=80%:%
-%:%93=81%:%
-%:%94=82%:%
-%:%95=83%:%
-%:%96=84%:%
-%:%97=85%:%
-%:%98=86%:%
-%:%99=87%:%
-%:%100=88%:%
-%:%101=89%:%
-%:%102=90%:%
-%:%103=91%:%
-%:%104=92%:%
-%:%105=93%:%
-%:%106=94%:%
-%:%107=95%:%
-%:%108=96%:%
-%:%109=97%:%
-%:%110=98%:%
-%:%111=99%:%
-%:%112=100%:%
-%:%113=101%:%
-%:%114=102%:%
-%:%115=103%:%
-%:%116=104%:%
-%:%117=105%:%
-%:%118=106%:%
-%:%119=107%:%
-%:%120=108%:%
-%:%121=109%:%
-%:%122=110%:%
-%:%123=111%:%
-%:%124=112%:%
-%:%125=113%:%
-%:%126=114%:%
-%:%127=115%:%
-%:%128=116%:%
-%:%129=117%:%
-%:%130=118%:%
-%:%131=119%:%
-%:%132=120%:%
-%:%133=121%:%
-%:%134=122%:%
-%:%135=123%:%
-%:%136=124%:%
-%:%137=125%:%
-%:%138=126%:%
-%:%139=127%:%
-%:%140=128%:%
-%:%141=129%:%
-%:%142=130%:%
-%:%143=131%:%
-%:%144=132%:%
-%:%145=133%:%
-%:%146=134%:%
-%:%147=135%:%
-%:%148=136%:%
-%:%149=137%:%
-%:%150=138%:%
-%:%151=139%:%
-%:%152=140%:%
-%:%153=141%:%
-%:%154=142%:%
-%:%155=143%:%
-%:%156=144%:%
-%:%157=145%:%
-%:%158=146%:%
-%:%159=147%:%
-%:%160=148%:%
-%:%161=149%:%
-%:%162=150%:%
-%:%163=151%:%
-%:%164=152%:%
-%:%165=153%:%
-%:%166=154%:%
-%:%167=155%:%
-%:%168=156%:%
-%:%169=157%:%
-%:%170=158%:%
-%:%171=159%:%
-%:%172=160%:%
-%:%173=161%:%
-%:%174=162%:%
-%:%175=163%:%
-%:%176=164%:%
-%:%177=165%:%
-%:%178=166%:%
-%:%179=167%:%
-%:%180=168%:%
-%:%181=169%:%
-%:%182=170%:%
-%:%183=171%:%
-%:%184=172%:%
-%:%185=173%:%
-%:%186=174%:%
-%:%187=175%:%
-%:%188=176%:%
-%:%189=177%:%
-%:%190=178%:%
-%:%191=179%:%
-%:%192=180%:%
-%:%193=181%:%
-%:%194=182%:%
-%:%195=183%:%
-%:%196=184%:%
-%:%197=185%:%
-%:%198=186%:%
-%:%199=187%:%
+%:%19=9%:%
+%:%20=10%:%
+%:%21=11%:%
+%:%22=12%:%
+%:%23=13%:%
+%:%24=14%:%
+%:%25=15%:%
+%:%26=16%:%
+%:%27=17%:%
+%:%28=18%:%
+%:%29=19%:%
+%:%30=20%:%
+%:%31=21%:%
+%:%32=22%:%
+%:%33=23%:%
+%:%34=24%:%
+%:%35=25%:%
+%:%36=26%:%
+%:%37=27%:%
+%:%38=28%:%
+%:%39=29%:%
+%:%40=30%:%
+%:%41=31%:%
+%:%42=32%:%
+%:%43=33%:%
+%:%44=34%:%
+%:%45=35%:%
+%:%46=36%:%
+%:%47=37%:%
+%:%48=38%:%
+%:%49=39%:%
+%:%50=40%:%
+%:%51=41%:%
+%:%52=42%:%
+%:%53=43%:%
+%:%54=44%:%
+%:%55=45%:%
+%:%56=46%:%
+%:%57=47%:%
+%:%58=48%:%
+%:%59=49%:%
+%:%60=50%:%
+%:%61=51%:%
+%:%62=52%:%
+%:%63=53%:%
+%:%64=54%:%
+%:%65=55%:%
+%:%66=56%:%
+%:%67=57%:%
+%:%68=58%:%
+%:%69=59%:%
+%:%70=60%:%
+%:%71=61%:%
+%:%72=62%:%
+%:%73=63%:%
+%:%74=64%:%
+%:%75=65%:%
+%:%76=66%:%
+%:%77=67%:%
+%:%78=68%:%
+%:%79=69%:%
+%:%80=70%:%
+%:%81=71%:%
+%:%82=72%:%
+%:%83=73%:%
+%:%84=74%:%
+%:%85=75%:%
+%:%86=76%:%
+%:%87=77%:%
+%:%88=78%:%
+%:%89=79%:%
+%:%90=80%:%
+%:%91=81%:%
+%:%92=82%:%
+%:%93=83%:%
+%:%94=84%:%
+%:%95=85%:%
+%:%96=86%:%
+%:%97=87%:%
+%:%98=88%:%
+%:%99=89%:%
+%:%100=90%:%
+%:%101=91%:%
+%:%102=92%:%
+%:%103=93%:%
+%:%104=94%:%
+%:%105=95%:%
+%:%106=96%:%
+%:%107=97%:%
+%:%108=98%:%
+%:%109=99%:%
+%:%110=100%:%
+%:%111=101%:%
+%:%112=102%:%
+%:%113=103%:%
+%:%114=104%:%
+%:%115=105%:%
+%:%116=106%:%
+%:%117=107%:%
+%:%118=108%:%
+%:%119=109%:%
+%:%120=110%:%
+%:%121=111%:%
+%:%122=112%:%
+%:%123=113%:%
+%:%124=114%:%
+%:%125=115%:%
+%:%126=116%:%
+%:%127=117%:%
+%:%128=118%:%
+%:%129=119%:%
+%:%130=120%:%
+%:%131=121%:%
+%:%132=122%:%
+%:%133=123%:%
+%:%134=124%:%
+%:%135=125%:%
+%:%136=126%:%
+%:%137=127%:%
+%:%138=128%:%
+%:%139=129%:%
+%:%140=130%:%
+%:%141=131%:%
+%:%142=132%:%
+%:%143=133%:%
+%:%144=134%:%
+%:%145=135%:%
+%:%146=136%:%
+%:%147=137%:%
+%:%148=138%:%
+%:%149=139%:%
+%:%150=140%:%
+%:%151=141%:%
+%:%152=142%:%
+%:%153=143%:%
+%:%154=144%:%
+%:%155=145%:%
+%:%156=146%:%
+%:%157=147%:%
+%:%158=148%:%
+%:%159=149%:%
+%:%160=150%:%
+%:%161=151%:%
+%:%162=152%:%
+%:%163=153%:%
+%:%164=154%:%
+%:%165=155%:%
+%:%166=156%:%
+%:%167=157%:%
+%:%168=158%:%
+%:%169=159%:%
+%:%170=160%:%
+%:%171=161%:%
+%:%172=162%:%
+%:%173=163%:%
+%:%174=164%:%
+%:%175=165%:%
+%:%176=166%:%
+%:%177=167%:%
+%:%178=168%:%
+%:%179=169%:%
+%:%180=170%:%
+%:%181=171%:%
+%:%182=172%:%
+%:%183=173%:%
+%:%184=174%:%
+%:%185=175%:%
+%:%186=176%:%
+%:%187=177%:%
+%:%188=178%:%
+%:%189=179%:%
+%:%190=180%:%
+%:%191=181%:%
+%:%192=182%:%
+%:%193=183%:%
+%:%194=184%:%
+%:%195=185%:%
+%:%196=186%:%
+%:%197=187%:%
+%:%198=188%:%
+%:%199=189%:%
+%:%200=190%:%
+%:%201=191%:%
+%:%202=192%:%
+%:%203=193%:%
+%:%204=194%:%
+%:%205=195%:%
+%:%206=196%:%
+%:%207=197%:%
+%:%208=198%:%
+%:%209=199%:%
+%:%210=200%:%
+%:%211=201%:%
+%:%212=202%:%
+%:%213=203%:%
+%:%214=204%:%
+%:%215=205%:%
+%:%216=206%:%
+%:%217=207%:%
+%:%218=208%:%
+%:%219=209%:%
+%:%220=210%:%
+%:%221=211%:%
+%:%222=212%:%
+%:%223=213%:%
+%:%224=214%:%
+%:%225=215%:%
+%:%226=216%:%
+%:%227=217%:%
+%:%228=218%:%
+%:%229=219%:%
+%:%230=220%:%
+%:%231=221%:%
+%:%232=222%:%
+%:%233=223%:%
+%:%234=224%:%
+%:%235=225%:%

### 2021-10-11 paper/output/document/paper32.tex
feedback

@@
 \begin{isamarkuptext}%
-Once again, the notion of permissibility will be useful here.%
+Once again, the notion of permissibility will be useful here. Recall that an action can either be 
+obligated, permissible, or prohibited. A permissible action is acceptable (there is no specific prohibition 
+against it), but not required (there is no specific obligation requiring it).%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupcmt{Let the constant $M$ denote murder.%
+\isamarkupcmt{Let the constant $M$ denote murder. I have defined no features of this constant, except that it is 
+of the type term, which can be true or false at a set of worlds. Indeed, this constant as-is has no 
+semantic meaning and could be replaced with any symbol, like `Q' or `Going to Target.' This constant 
+will begin to take on features of the act of murder when I specify its properties. In the tests below, 
+I specify its properties as the antecedents of lemmas. For example, the test below specifies that 
+it is possible that murder is prohibited at the current world. This pattern will hold for most constants 
+defined in Isabelle—they have no meaning until I program a meaning.%
 }\isanewline
@@
 additional axioms that represent the categorical imperative shows that, in DDL, if something is 
-possibly wrong, it is wrong at every world. This implies that this is not a useful example to test any formulation,
-since it holds in the base logic itself.%
+possibly wrong, it is wrong at every world. This implies that this is not a useful example to test any formulation. 
+If a lemma is true in the base logic, without any custom axioms added, then it will hold for any set of  
+custom axioms. Testing whether or not it holds as we add axioms tells us nothing, since it held in 
+the base logic itself. Interesting cases are ones that fail (or are indeterminate) in the base logic, 
+but become true as we add axioms.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 Just as with the naive formalization, Kroy's formalization allows implied contradictions because 
-        DDL itself allows implied contradictions and, as I explored in Section \ref{sec:naive_tests_kroy}, Kroy's 
+        DDL itself allows implied contradictions and Kroy's 
         formalization doesn't do anything to remedy this.
@@
 %:%105=50%:%
+%:%106=51%:%
 %:%107=52%:%
-%:%108=52%:%
-%:%109=53%:%
+%:%109=54%:%
 %:%110=54%:%
-%:%111=54%:%
-%:%112=55%:%
-%:%113=58%:%
-%:%116=61%:%
-%:%117=62%:%
+%:%111=55%:%
+%:%112=56%:%
+%:%113=56%:%
+%:%114=57%:%
+%:%115=60%:%
 %:%118=63%:%
@@
 %:%120=65%:%
-%:%123=67%:%
-%:%126=69%:%
-%:%127=70%:%
+%:%121=66%:%
+%:%122=67%:%
+%:%125=69%:%
 %:%128=71%:%
@@
 %:%131=74%:%
+%:%132=75%:%
 %:%133=76%:%
-%:%134=76%:%
-%:%135=77%:%
+%:%135=78%:%
 %:%136=78%:%
 %:%137=79%:%
-%:%138=79%:%
-%:%140=79%:%
-%:%144=79%:%
-%:%145=79%:%
-%:%147=80%:%
-%:%148=81%:%
+%:%138=80%:%
+%:%139=81%:%
+%:%140=81%:%
+%:%142=81%:%
+%:%146=81%:%
+%:%147=81%:%
 %:%149=82%:%
 %:%150=83%:%
-%:%160=85%:%
-%:%161=86%:%
+%:%151=84%:%
+%:%152=85%:%
 %:%162=87%:%
@@
 %:%169=94%:%
+%:%170=95%:%
 %:%171=96%:%
-%:%172=96%:%
-%:%173=97%:%
+%:%173=98%:%
 %:%174=98%:%
 %:%175=99%:%
-%:%176=99%:%
-%:%178=99%:%
-%:%182=99%:%
-%:%183=99%:%
-%:%185=100%:%
-%:%186=101%:%
+%:%176=100%:%
+%:%177=101%:%
+%:%178=101%:%
+%:%180=101%:%
+%:%184=101%:%
+%:%185=101%:%
 %:%187=102%:%
 %:%188=103%:%
-%:%198=106%:%
-%:%199=107%:%
+%:%189=104%:%
+%:%190=105%:%
 %:%200=108%:%
@@
 %:%206=114%:%
-%:%208=117%:%
-%:%209=117%:%
-%:%210=118%:%
+%:%207=115%:%
+%:%208=116%:%
+%:%210=119%:%
 %:%211=119%:%
 %:%212=120%:%
-%:%213=120%:%
-%:%215=120%:%
-%:%219=120%:%
-%:%220=120%:%
-%:%222=121%:%
-%:%223=122%:%
+%:%213=121%:%
+%:%214=122%:%
+%:%215=122%:%
+%:%217=122%:%
+%:%221=122%:%
+%:%222=122%:%
 %:%224=123%:%
 %:%225=124%:%
-%:%235=126%:%
-%:%236=127%:%
+%:%226=125%:%
+%:%227=126%:%
 %:%237=128%:%
 %:%238=129%:%
-%:%241=131%:%
-%:%244=133%:%
-%:%245=134%:%
+%:%239=130%:%
+%:%240=131%:%
+%:%243=133%:%
 %:%246=135%:%
@@
 %:%248=137%:%
+%:%249=138%:%
 %:%250=139%:%
-%:%251=139%:%
-%:%252=140%:%
+%:%252=141%:%
 %:%253=141%:%
 %:%254=142%:%
-%:%255=142%:%
-%:%257=142%:%
-%:%261=142%:%
-%:%262=142%:%
-%:%264=143%:%
-%:%265=144%:%
+%:%255=143%:%
+%:%256=144%:%
+%:%257=144%:%
+%:%259=144%:%
+%:%263=144%:%
+%:%264=144%:%
 %:%266=145%:%
 %:%267=146%:%
-%:%277=148%:%
-%:%278=149%:%
-%:%287=154%:%
-%:%299=156%:%
-%:%300=157%:%
+%:%268=147%:%
+%:%269=148%:%
+%:%279=150%:%
+%:%280=151%:%
+%:%289=156%:%
 %:%301=158%:%
@@
 %:%303=160%:%
-%:%305=161%:%
-%:%306=161%:%
-%:%307=162%:%
-%:%309=163%:%
-%:%310=164%:%
+%:%304=161%:%
+%:%305=162%:%
+%:%307=163%:%
+%:%308=163%:%
+%:%309=164%:%
 %:%311=165%:%
-%:%314=167%:%
+%:%312=166%:%
+%:%313=167%:%
 %:%316=169%:%
-%:%317=169%:%
-%:%318=170%:%
+%:%318=171%:%
 %:%319=171%:%
-%:%320=171%:%
-%:%322=171%:%
-%:%326=171%:%
-%:%327=171%:%
-%:%329=172%:%
-%:%330=173%:%
+%:%320=172%:%
+%:%321=173%:%
+%:%322=173%:%
+%:%324=173%:%
+%:%328=173%:%
+%:%329=173%:%
 %:%331=174%:%
@@
 %:%334=177%:%
-%:%344=179%:%
+%:%335=178%:%
+%:%336=179%:%
 %:%346=181%:%
-%:%347=181%:%
+%:%348=183%:%
 %:%349=183%:%
 %:%351=185%:%
-%:%352=185%:%
-%:%353=185%:%
-%:%355=185%:%
-%:%359=185%:%
-%:%360=185%:%
-%:%362=186%:%
-%:%363=187%:%
+%:%353=187%:%
+%:%354=187%:%
+%:%355=187%:%
+%:%357=187%:%
+%:%361=187%:%
+%:%362=187%:%
 %:%364=188%:%
 %:%365=189%:%
-%:%375=191%:%
-%:%376=192%:%
+%:%366=190%:%
+%:%367=191%:%
 %:%377=193%:%
 %:%378=194%:%
-%:%387=197%:%
-%:%399=199%:%
-%:%400=200%:%
+%:%379=195%:%
+%:%380=196%:%
+%:%389=199%:%
 %:%401=201%:%
@@
 %:%407=207%:%
-%:%411=209%:%
-%:%415=211%:%
-%:%416=212%:%
+%:%408=208%:%
+%:%409=209%:%
+%:%413=211%:%
 %:%417=213%:%
+%:%418=214%:%
 %:%419=215%:%
-%:%420=215%:%
-%:%422=216%:%
-%:%423=216%:%
-%:%424=217%:%
-%:%425=218%:%
-%:%426=218%:%
-%:%427=219%:%
-%:%430=220%:%
-%:%434=220%:%
-%:%435=220%:%
-%:%437=221%:%
-%:%438=222%:%
-%:%448=224%:%
-%:%449=225%:%
-%:%450=226%:%
-%:%451=227%:%
-%:%452=228%:%
-%:%453=229%:%
-%:%454=230%:%
-%:%455=231%:%
+%:%421=217%:%
+%:%422=217%:%
+%:%424=218%:%
+%:%425=219%:%
+%:%426=220%:%
+%:%427=221%:%
+%:%428=222%:%
+%:%429=223%:%
+%:%430=224%:%
+%:%431=224%:%
+%:%432=225%:%
+%:%433=226%:%
+%:%434=226%:%
+%:%435=227%:%
+%:%438=228%:%
+%:%442=228%:%
+%:%443=228%:%
+%:%445=229%:%
+%:%446=230%:%
 %:%456=232%:%
@@
 %:%462=238%:%
-%:%466=240%:%
-%:%467=241%:%
-%:%469=243%:%
-%:%470=243%:%
-%:%472=244%:%
-%:%473=244%:%
-%:%474=245%:%
-%:%475=246%:%
-%:%476=246%:%
-%:%477=247%:%
-%:%480=248%:%
-%:%484=248%:%
-%:%485=248%:%
-%:%486=249%:%
-%:%487=249%:%
-%:%488=250%:%
-%:%489=250%:%
-%:%490=251%:%
-%:%491=251%:%
-%:%492=251%:%
-%:%493=252%:%
-%:%503=254%:%
-%:%504=255%:%
-%:%505=256%:%
-%:%506=257%:%
-%:%510=259%:%
-%:%514=261%:%
-%:%515=262%:%
-%:%516=263%:%
-%:%520=265%:%
-%:%521=266%:%
-%:%523=268%:%
-%:%524=268%:%
-%:%537=289%:%
-%:%538=290%:%
-%:%539=290%:%
-%:%541=291%:%
-%:%542=292%:%
-%:%543=293%:%
-%:%544=294%:%
-%:%545=295%:%
-%:%546=296%:%
-%:%547=296%:%
-%:%549=297%:%
-%:%550=298%:%
-%:%551=298%:%
-%:%552=299%:%
-%:%553=300%:%
-%:%554=300%:%
-%:%556=301%:%
-%:%557=302%:%
-%:%560=304%:%
-%:%561=305%:%
-%:%563=307%:%
-%:%564=307%:%
-%:%565=308%:%
-%:%566=309%:%
-%:%567=309%:%
-%:%569=309%:%
-%:%573=309%:%
-%:%574=309%:%
-%:%576=310%:%
-%:%577=311%:%
-%:%578=312%:%
-%:%579=313%:%
-%:%580=314%:%
-%:%581=315%:%
-%:%582=316%:%
-%:%592=318%:%
-%:%593=319%:%
-%:%594=320%:%
-%:%597=322%:%
-%:%598=323%:%
-%:%599=324%:%
-%:%600=325%:%
-%:%601=326%:%
-%:%602=327%:%
-%:%605=329%:%
-%:%607=331%:%
-%:%608=331%:%
-%:%609=332%:%
-%:%612=333%:%
-%:%616=333%:%
-%:%617=333%:%
-%:%619=334%:%
-%:%625=334%:%
-%:%628=335%:%
-%:%629=336%:%
-%:%630=336%:%
-%:%631=337%:%
-%:%632=338%:%
-%:%633=339%:%
-%:%634=339%:%
-%:%636=339%:%
-%:%640=339%:%
-%:%641=339%:%
-%:%643=340%:%
-%:%644=341%:%
-%:%645=342%:%
-%:%646=343%:%
-%:%647=344%:%
-%:%657=346%:%
-%:%658=347%:%
-%:%659=348%:%
-%:%660=349%:%
-%:%661=350%:%
-%:%662=351%:%
-%:%663=352%:%
-%:%664=353%:%
-%:%665=354%:%
-%:%669=357%:%
-%:%670=358%:%
-%:%671=359%:%
-%:%672=360%:%
-%:%673=361%:%
-%:%674=362%:%
-%:%675=363%:%
-%:%676=364%:%
-%:%677=365%:%
-%:%678=366%:%
-%:%679=367%:%
+%:%463=239%:%
+%:%464=240%:%
+%:%465=241%:%
+%:%466=242%:%
+%:%467=243%:%
+%:%468=244%:%
+%:%469=245%:%
+%:%470=246%:%
+%:%471=247%:%
+%:%472=248%:%
+%:%473=249%:%
+%:%477=251%:%
+%:%478=252%:%
+%:%480=254%:%
+%:%481=254%:%
+%:%483=255%:%
+%:%484=255%:%
+%:%485=256%:%
+%:%486=257%:%
+%:%487=257%:%
+%:%488=258%:%
+%:%491=259%:%
+%:%495=259%:%
+%:%496=259%:%
+%:%497=260%:%
+%:%498=260%:%
+%:%499=261%:%
+%:%500=261%:%
+%:%501=262%:%
+%:%502=262%:%
+%:%503=262%:%
+%:%504=263%:%
+%:%514=265%:%
+%:%515=266%:%
+%:%516=267%:%
+%:%517=268%:%
+%:%521=270%:%
+%:%525=272%:%
+%:%526=273%:%
+%:%527=274%:%
+%:%531=276%:%
+%:%532=277%:%
+%:%534=279%:%
+%:%535=279%:%
+%:%548=300%:%
+%:%549=301%:%
+%:%550=301%:%
+%:%552=302%:%
+%:%553=303%:%
+%:%554=304%:%
+%:%555=305%:%
+%:%556=306%:%
+%:%557=307%:%
+%:%558=307%:%
+%:%560=308%:%
+%:%561=309%:%
+%:%562=309%:%
+%:%563=310%:%
+%:%564=311%:%
+%:%565=311%:%
+%:%567=312%:%
+%:%568=313%:%
+%:%571=315%:%
+%:%572=316%:%
+%:%574=318%:%
+%:%575=318%:%
+%:%576=319%:%
+%:%577=320%:%
+%:%578=320%:%
+%:%580=320%:%
+%:%584=320%:%
+%:%585=320%:%
+%:%587=321%:%
+%:%588=322%:%
+%:%589=323%:%
+%:%590=324%:%
+%:%591=325%:%
+%:%592=326%:%
+%:%593=327%:%
+%:%603=329%:%
+%:%604=330%:%
+%:%605=331%:%
+%:%608=333%:%
+%:%609=334%:%
+%:%610=335%:%
+%:%611=336%:%
+%:%612=337%:%
+%:%613=338%:%
+%:%616=340%:%
+%:%618=342%:%
+%:%619=342%:%
+%:%620=343%:%
+%:%623=344%:%
+%:%627=344%:%
+%:%628=344%:%
+%:%630=345%:%
+%:%636=345%:%
+%:%639=346%:%
+%:%640=347%:%
+%:%641=347%:%
+%:%642=348%:%
+%:%643=349%:%
+%:%644=350%:%
+%:%645=350%:%
+%:%647=350%:%
+%:%651=350%:%
+%:%652=350%:%
+%:%654=351%:%
+%:%655=352%:%
+%:%656=353%:%
+%:%657=354%:%
+%:%658=355%:%
+%:%668=357%:%
+%:%669=358%:%
+%:%670=359%:%
+%:%671=360%:%
+%:%672=361%:%
+%:%673=362%:%
+%:%674=363%:%
+%:%675=364%:%
+%:%676=365%:%
 %:%680=368%:%
-%:%689=370%:%
-%:%701=372%:%
-%:%702=373%:%
-%:%703=374%:%
-%:%705=376%:%
-%:%706=376%:%
-%:%707=377%:%
-%:%708=378%:%
-%:%709=379%:%
-%:%710=379%:%
-%:%712=379%:%
-%:%716=379%:%
-%:%717=379%:%
-%:%719=380%:%
-%:%720=381%:%
-%:%721=382%:%
-%:%722=383%:%
-%:%732=385%:%
-%:%733=386%:%
-%:%734=387%:%
-%:%738=389%:%
-%:%740=391%:%
-%:%741=391%:%
-%:%742=392%:%
-%:%743=393%:%
-%:%744=394%:%
-%:%745=394%:%
-%:%747=394%:%
-%:%751=394%:%
-%:%752=394%:%
-%:%754=395%:%
-%:%755=396%:%
-%:%756=397%:%
-%:%757=398%:%
-%:%767=400%:%
-%:%768=401%:%
-%:%770=403%:%
-%:%771=403%:%
-%:%772=404%:%
-%:%773=405%:%
-%:%774=406%:%
-%:%775=406%:%
-%:%777=406%:%
-%:%781=406%:%
-%:%782=406%:%
-%:%784=407%:%
-%:%785=408%:%
-%:%786=409%:%
-%:%787=410%:%
-%:%788=411%:%
-%:%798=413%:%
-%:%799=414%:%
-%:%801=416%:%
-%:%802=416%:%
-%:%803=417%:%
-%:%804=418%:%
-%:%807=419%:%
-%:%811=419%:%
-%:%812=419%:%
-%:%813=419%:%
-%:%822=421%:%
-%:%823=422%:%
-%:%824=423%:%
-%:%825=424%:%
-%:%827=426%:%
-%:%828=426%:%
-%:%829=427%:%
-%:%830=428%:%
-%:%833=429%:%
-%:%837=429%:%
-%:%838=429%:%
-%:%839=429%:%
-%:%848=431%:%
-%:%849=432%:%
-%:%851=434%:%
-%:%852=434%:%
-%:%853=435%:%
-%:%854=436%:%
-%:%855=437%:%
-%:%856=437%:%
-%:%858=437%:%
-%:%862=437%:%
-%:%863=437%:%
-%:%865=438%:%
-%:%866=439%:%
-%:%867=440%:%
-%:%868=441%:%
-%:%878=443%:%
-%:%879=444%:%
-%:%880=445%:%
-%:%881=446%:%
-%:%882=447%:%
-%:%883=448%:%
-%:%885=450%:%
-%:%886=450%:%
-%:%887=451%:%
-%:%888=452%:%
-%:%889=453%:%
-%:%890=454%:%
-%:%891=454%:%
-%:%893=454%:%
-%:%897=454%:%
-%:%898=454%:%
-%:%900=455%:%
-%:%901=456%:%
-%:%902=457%:%
-%:%903=458%:%
-%:%904=459%:%
-%:%905=460%:%
-%:%915=462%:%
-%:%916=463%:%
-%:%917=464%:%
-%:%918=465%:%
-%:%919=466%:%
-%:%920=467%:%
-%:%922=469%:%
-%:%923=469%:%
-%:%924=470%:%
-%:%925=471%:%
-%:%928=472%:%
-%:%932=472%:%
-%:%933=472%:%
-%:%935=473%:%
-%:%945=475%:%
-%:%946=476%:%
-%:%947=477%:%
-%:%948=478%:%
-%:%957=480%:%
-%:%969=482%:%
-%:%970=483%:%
-%:%971=484%:%
-%:%972=485%:%
-%:%976=487%:%
-%:%977=488%:%
-%:%979=490%:%
-%:%980=490%:%
-%:%981=491%:%
-%:%982=492%:%
-%:%983=492%:%
-%:%984=493%:%
-%:%987=494%:%
-%:%991=494%:%
-%:%992=494%:%
-%:%993=494%:%
-%:%995=495%:%
-%:%996=496%:%
-%:%1006=498%:%
-%:%1007=499%:%
-%:%1008=500%:%
-%:%1009=501%:%
-%:%1010=502%:%
-%:%1011=503%:%
-%:%1012=504%:%
-%:%1013=505%:%
-%:%1014=506%:%
-%:%1015=507%:%
-%:%1016=508%:%
+%:%681=369%:%
+%:%682=370%:%
+%:%683=371%:%
+%:%684=372%:%
+%:%685=373%:%
+%:%686=374%:%
+%:%687=375%:%
+%:%688=376%:%
+%:%689=377%:%
+%:%690=378%:%
+%:%691=379%:%
+%:%700=381%:%
+%:%712=383%:%
+%:%713=384%:%
+%:%714=385%:%
+%:%716=387%:%
+%:%717=387%:%
+%:%718=388%:%
+%:%719=389%:%
+%:%720=390%:%
+%:%721=390%:%
+%:%723=390%:%
+%:%727=390%:%
+%:%728=390%:%
+%:%730=391%:%
+%:%731=392%:%
+%:%732=393%:%
+%:%733=394%:%
+%:%743=396%:%
+%:%744=397%:%
+%:%745=398%:%
+%:%749=400%:%
+%:%751=402%:%
+%:%752=402%:%
+%:%753=403%:%
+%:%754=404%:%
+%:%755=405%:%
+%:%756=405%:%
+%:%758=405%:%
+%:%762=405%:%
+%:%763=405%:%
+%:%765=406%:%
+%:%766=407%:%
+%:%767=408%:%
+%:%768=409%:%
+%:%778=411%:%
+%:%779=412%:%
+%:%781=414%:%
+%:%782=414%:%
+%:%783=415%:%
+%:%784=416%:%
+%:%785=417%:%
+%:%786=417%:%
+%:%788=417%:%
+%:%792=417%:%
+%:%793=417%:%
+%:%795=418%:%
+%:%796=419%:%
+%:%797=420%:%
+%:%798=421%:%
+%:%799=422%:%
+%:%809=424%:%
+%:%810=425%:%
+%:%812=427%:%
+%:%813=427%:%
+%:%814=428%:%
+%:%815=429%:%
+%:%818=430%:%
+%:%822=430%:%
+%:%823=430%:%
+%:%824=430%:%
+%:%833=432%:%
+%:%834=433%:%
+%:%835=434%:%
+%:%836=435%:%
+%:%838=437%:%
+%:%839=437%:%
+%:%840=438%:%
+%:%841=439%:%
+%:%844=440%:%
+%:%848=440%:%
+%:%849=440%:%
+%:%850=440%:%
+%:%859=442%:%
+%:%860=443%:%
+%:%862=445%:%
+%:%863=445%:%
+%:%864=446%:%
+%:%865=447%:%
+%:%866=448%:%
+%:%867=448%:%
+%:%869=448%:%
+%:%873=448%:%
+%:%874=448%:%
+%:%876=449%:%
+%:%877=450%:%
+%:%878=451%:%
+%:%879=452%:%
+%:%889=454%:%
+%:%890=455%:%
+%:%891=456%:%
+%:%892=457%:%
+%:%893=458%:%
+%:%894=459%:%
+%:%896=461%:%
+%:%897=461%:%
+%:%898=462%:%
+%:%899=463%:%
+%:%900=464%:%
+%:%901=465%:%
+%:%902=465%:%
+%:%904=465%:%
+%:%908=465%:%
+%:%909=465%:%
+%:%911=466%:%
+%:%912=467%:%
+%:%913=468%:%
+%:%914=469%:%
+%:%915=470%:%
+%:%916=471%:%
+%:%926=473%:%
+%:%927=474%:%
+%:%928=475%:%
+%:%929=476%:%
+%:%930=477%:%
+%:%931=478%:%
+%:%933=480%:%
+%:%934=480%:%
+%:%935=481%:%
+%:%936=482%:%
+%:%939=483%:%
+%:%943=483%:%
+%:%944=483%:%
+%:%946=484%:%
+%:%956=486%:%
+%:%957=487%:%
+%:%958=488%:%
+%:%959=489%:%
+%:%968=491%:%
+%:%980=493%:%
+%:%981=494%:%
+%:%982=495%:%
+%:%983=496%:%
+%:%987=498%:%
+%:%988=499%:%
+%:%990=501%:%
+%:%991=501%:%
+%:%992=502%:%
+%:%993=503%:%
+%:%994=503%:%
+%:%995=504%:%
+%:%998=505%:%
+%:%1002=505%:%
+%:%1003=505%:%
+%:%1004=505%:%
+%:%1006=506%:%
+%:%1007=507%:%
 %:%1017=509%:%
@@
 %:%1020=512%:%
+%:%1021=513%:%
 %:%1022=514%:%
-%:%1023=514%:%
-%:%1024=515%:%
-%:%1025=516%:%
-%:%1026=517%:%
-%:%1027=517%:%
-%:%1029=517%:%
-%:%1033=517%:%
-%:%1034=517%:%
-%:%1036=518%:%
-%:%1037=519%:%
-%:%1038=520%:%
-%:%1039=521%:%
-%:%1040=522%:%
-%:%1041=523%:%
-%:%1051=525%:%
-%:%1052=526%:%
-%:%1053=527%:%
-%:%1054=528%:%
-%:%1058=530%:%
-%:%1059=531%:%
-%:%1060=532%:%
-%:%1062=534%:%
-%:%1063=534%:%
-%:%1064=535%:%
-%:%1065=535%:%
-%:%1067=536%:%
-%:%1068=537%:%
-%:%1069=537%:%
-%:%1070=538%:%
-%:%1071=539%:%
-%:%1072=539%:%
-%:%1073=540%:%
-%:%1076=541%:%
-%:%1080=541%:%
-%:%1081=541%:%
-%:%1083=542%:%
-%:%1084=543%:%
-%:%1085=544%:%
-%:%1095=546%:%
-%:%1096=547%:%
-%:%1097=548%:%
-%:%1098=549%:%
-%:%1100=551%:%
-%:%1101=551%:%
-%:%1102=552%:%
-%:%1104=552%:%
-%:%1108=552%:%
-%:%1109=552%:%
-%:%1111=553%:%
-%:%1119=553%:%
-%:%1120=554%:%
-%:%1121=555%:%
-%:%1122=555%:%
-%:%1123=556%:%
-%:%1125=556%:%
-%:%1129=556%:%
-%:%1130=556%:%
-%:%1132=557%:%
-%:%1142=559%:%
-%:%1143=560%:%
-%:%1144=561%:%
+%:%1023=515%:%
+%:%1024=516%:%
+%:%1025=517%:%
+%:%1026=518%:%
+%:%1027=519%:%
+%:%1028=520%:%
+%:%1029=521%:%
+%:%1030=522%:%
+%:%1031=523%:%
+%:%1033=525%:%
+%:%1034=525%:%
+%:%1035=526%:%
+%:%1036=527%:%
+%:%1037=528%:%
+%:%1038=528%:%
+%:%1040=528%:%
+%:%1044=528%:%
+%:%1045=528%:%
+%:%1047=529%:%
+%:%1048=530%:%
+%:%1049=531%:%
+%:%1050=532%:%
+%:%1051=533%:%
+%:%1052=534%:%
+%:%1062=536%:%
+%:%1063=537%:%
+%:%1064=538%:%
+%:%1065=539%:%
+%:%1069=541%:%
+%:%1070=542%:%
+%:%1071=543%:%
+%:%1073=545%:%
+%:%1074=545%:%
+%:%1075=546%:%
+%:%1076=546%:%
+%:%1078=547%:%
+%:%1079=548%:%
+%:%1080=548%:%
+%:%1081=549%:%
+%:%1082=550%:%
+%:%1083=550%:%
+%:%1084=551%:%
+%:%1087=552%:%
+%:%1091=552%:%
+%:%1092=552%:%
+%:%1094=553%:%
+%:%1095=554%:%
+%:%1096=555%:%
+%:%1106=557%:%
+%:%1107=558%:%
+%:%1108=559%:%
+%:%1109=560%:%
+%:%1111=562%:%
+%:%1112=562%:%
+%:%1113=563%:%
+%:%1115=563%:%
+%:%1119=563%:%
+%:%1120=563%:%
+%:%1122=564%:%
+%:%1130=564%:%
+%:%1131=565%:%
+%:%1132=566%:%
+%:%1133=566%:%
+%:%1134=567%:%
+%:%1136=567%:%
+%:%1140=567%:%
+%:%1141=567%:%
+%:%1143=568%:%
+%:%1153=570%:%
+%:%1154=571%:%
+%:%1155=572%:%

### 2021-10-13 paper/output/document/paper41.tex
added philosophical upshot

@@
 %
-\isamarkupsubsection{Logical Background%
+\isamarkupsubsection{Constructing the Formalization%
 }
@@
 %
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsection{Application Tests%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
+As with the naive formalization and Kroy's formalization, I will apply my testing framework to 
+my custom formalization of the FUL. I will begin with some basic application tests. In these tests, 
+I specify particular maxims as constants with no properties and gradually add properties to understand 
+how the system handles different kinds of maxims. For example, initially I simply define ``murder'' as 
+a constant $M$, and then I specify properties of murder, such as murder is not universalizable or 
+murder is prohibited.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{consts}\isamarkupfalse%
+\ M{\isacharcolon}{\isacharcolon}os\isanewline
+%
+\isamarkupcmt{The constant $M$ will represent the act ``murder."%
+}\isanewline
+%
+\isamarkupcmt{Should I represent this as a set of maxims? should I specify the circumstances and goals?%
+}\isanewline
+%
 \isadelimproof
@@
 %:%440=316%:%
+%:%449=318%:%
+%:%461=320%:%
+%:%462=321%:%
+%:%463=322%:%
+%:%464=323%:%
+%:%465=324%:%
+%:%466=325%:%
+%:%468=327%:%
+%:%469=327%:%
+%:%471=328%:%
+%:%472=328%:%
+%:%474=329%:%
+%:%475=329%:%

### 2021-10-13 paper/output/document/threeflags.tex
added philosophical upshot

@@
 %
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsection{Choice to Formalize the FUL%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
 \begin{isamarkuptext}%
-$\textbf{Choice to Formalize the FUL}$
-
 In \emph{Groundwork of the Metaphysics of Morals}, Kant presents three formulations, or versions, 
@@
 are identical. Kant believes that his argument for the equality of the formulas is analytical, and
-if he is correct, it should be possible to recreate the argument in logic.
-
-$\textbf{Definition of a Maxim}$
-
+if he is correct, it should be possible to recreate the argument in logic.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsection{Definition of a Maxim%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
 The central unit of evaluation for the universalizability test is a ``maxim," which Kant defines 
@@
 My definition of a maxim is inspired by O'Neill's work on maxims. I will defend my representation
-below and consider an additional component that Kitcher argues for.
-
-$\emph{O'Niell's Original Schematic and The Role of Practical Judgement}$
-
+below and consider an additional component that Kitcher argues for.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsection{O'Niell's Original Schematic and The Role of Practical Judgement%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
 O'Neill $\cite[37]{actingonprinciple}$ presents what Kitcher \cite{whatisamaxim}  calls the widely accepted 
@@
 does not render human judgement or philosophy obsolete. Chapter 4 Section ?? will be devoted to a more complete discussion 
-of this issue.
-
-$\emph{Exclusion of Motive}$
-
+of this issue.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsection{Exclusion of Motive%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
 Kitcher begins with O'Niell's circumstance, act, goal view and expands it to include the motive 
@@
 with a logic of practical reason, an implementation of the FUL can move from evaluating a maxim to 
-evaluating an agent's behavior, since that's when ``acting from duty" starts to matter.
-
-$\textbf{Practical Contradiction Interpretation}$
-
+evaluating an agent's behavior, since that's when ``acting from duty" starts to matter.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsection{Practical Contradiction Interpretation%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
 Kantians debate the correct interpretation of the formula of universal law because Kant appears to 
@@
 %:%file=~/Desktop/cs91r/paper/threeflags.thy%:%
-%:%19=9%:%
-%:%20=10%:%
-%:%21=11%:%
-%:%22=12%:%
-%:%23=13%:%
-%:%24=14%:%
-%:%25=15%:%
-%:%26=16%:%
-%:%27=17%:%
-%:%28=18%:%
-%:%29=19%:%
-%:%30=20%:%
-%:%31=21%:%
-%:%32=22%:%
-%:%33=23%:%
-%:%34=24%:%
-%:%35=25%:%
-%:%36=26%:%
-%:%37=27%:%
-%:%38=28%:%
-%:%39=29%:%
-%:%40=30%:%
-%:%41=31%:%
-%:%42=32%:%
-%:%43=33%:%
-%:%44=34%:%
-%:%45=35%:%
-%:%46=36%:%
-%:%47=37%:%
-%:%48=38%:%
-%:%49=39%:%
-%:%50=40%:%
-%:%51=41%:%
-%:%52=42%:%
-%:%53=43%:%
-%:%54=44%:%
-%:%55=45%:%
-%:%56=46%:%
-%:%57=47%:%
-%:%58=48%:%
-%:%59=49%:%
-%:%60=50%:%
-%:%61=51%:%
-%:%62=52%:%
-%:%63=53%:%
-%:%64=54%:%
-%:%65=55%:%
-%:%66=56%:%
-%:%67=57%:%
-%:%68=58%:%
-%:%69=59%:%
-%:%70=60%:%
-%:%71=61%:%
-%:%72=62%:%
-%:%73=63%:%
-%:%74=64%:%
-%:%75=65%:%
-%:%76=66%:%
-%:%77=67%:%
-%:%78=68%:%
-%:%79=69%:%
-%:%80=70%:%
-%:%81=71%:%
-%:%82=72%:%
-%:%83=73%:%
-%:%84=74%:%
-%:%85=75%:%
-%:%86=76%:%
-%:%87=77%:%
-%:%88=78%:%
-%:%89=79%:%
-%:%90=80%:%
-%:%91=81%:%
-%:%92=82%:%
-%:%93=83%:%
-%:%94=84%:%
-%:%95=85%:%
-%:%96=86%:%
-%:%97=87%:%
-%:%98=88%:%
-%:%99=89%:%
-%:%100=90%:%
-%:%101=91%:%
-%:%102=92%:%
-%:%103=93%:%
-%:%104=94%:%
-%:%105=95%:%
-%:%106=96%:%
-%:%107=97%:%
-%:%108=98%:%
-%:%109=99%:%
-%:%110=100%:%
-%:%111=101%:%
-%:%112=102%:%
-%:%113=103%:%
-%:%114=104%:%
-%:%115=105%:%
-%:%116=106%:%
-%:%117=107%:%
-%:%118=108%:%
-%:%119=109%:%
-%:%120=110%:%
-%:%121=111%:%
-%:%122=112%:%
-%:%123=113%:%
-%:%124=114%:%
-%:%125=115%:%
-%:%126=116%:%
-%:%127=117%:%
-%:%128=118%:%
-%:%129=119%:%
-%:%130=120%:%
-%:%131=121%:%
-%:%132=122%:%
-%:%133=123%:%
-%:%134=124%:%
-%:%135=125%:%
-%:%136=126%:%
-%:%137=127%:%
-%:%138=128%:%
-%:%139=129%:%
-%:%140=130%:%
-%:%141=131%:%
-%:%142=132%:%
-%:%143=133%:%
-%:%144=134%:%
-%:%145=135%:%
-%:%146=136%:%
-%:%147=137%:%
-%:%148=138%:%
-%:%149=139%:%
-%:%150=140%:%
-%:%151=141%:%
-%:%152=142%:%
-%:%153=143%:%
-%:%154=144%:%
-%:%155=145%:%
-%:%156=146%:%
-%:%157=147%:%
-%:%158=148%:%
-%:%159=149%:%
-%:%160=150%:%
-%:%161=151%:%
-%:%162=152%:%
-%:%163=153%:%
-%:%164=154%:%
-%:%165=155%:%
-%:%166=156%:%
-%:%167=157%:%
-%:%168=158%:%
-%:%169=159%:%
-%:%170=160%:%
-%:%171=161%:%
-%:%172=162%:%
-%:%173=163%:%
-%:%174=164%:%
-%:%175=165%:%
-%:%176=166%:%
-%:%177=167%:%
-%:%178=168%:%
-%:%179=169%:%
-%:%180=170%:%
-%:%181=171%:%
-%:%182=172%:%
-%:%183=173%:%
-%:%184=174%:%
-%:%185=175%:%
-%:%186=176%:%
-%:%187=177%:%
-%:%188=178%:%
-%:%189=179%:%
-%:%190=180%:%
-%:%191=181%:%
-%:%192=182%:%
-%:%193=183%:%
-%:%194=184%:%
-%:%195=185%:%
-%:%196=186%:%
-%:%197=187%:%
-%:%198=188%:%
-%:%199=189%:%
-%:%200=190%:%
-%:%201=191%:%
-%:%202=192%:%
-%:%203=193%:%
-%:%204=194%:%
-%:%205=195%:%
-%:%206=196%:%
-%:%207=197%:%
-%:%208=198%:%
-%:%209=199%:%
-%:%210=200%:%
-%:%211=201%:%
-%:%212=202%:%
-%:%213=203%:%
-%:%214=204%:%
-%:%215=205%:%
-%:%216=206%:%
-%:%217=207%:%
-%:%218=208%:%
-%:%219=209%:%
-%:%220=210%:%
-%:%221=211%:%
-%:%222=212%:%
-%:%223=213%:%
-%:%224=214%:%
-%:%225=215%:%
-%:%226=216%:%
-%:%227=217%:%
-%:%228=218%:%
-%:%229=219%:%
-%:%230=220%:%
-%:%231=221%:%
-%:%232=222%:%
-%:%233=223%:%
-%:%234=224%:%
-%:%235=225%:%
+%:%24=9%:%
+%:%36=12%:%
+%:%37=13%:%
+%:%38=14%:%
+%:%39=15%:%
+%:%40=16%:%
+%:%41=17%:%
+%:%42=18%:%
+%:%43=19%:%
+%:%44=20%:%
+%:%45=21%:%
+%:%46=22%:%
+%:%47=23%:%
+%:%48=24%:%
+%:%49=25%:%
+%:%50=26%:%
+%:%51=27%:%
+%:%52=28%:%
+%:%53=29%:%
+%:%54=30%:%
+%:%55=31%:%
+%:%56=32%:%
+%:%57=33%:%
+%:%58=34%:%
+%:%59=35%:%
+%:%60=36%:%
+%:%61=37%:%
+%:%62=38%:%
+%:%63=39%:%
+%:%64=40%:%
+%:%65=41%:%
+%:%66=42%:%
+%:%67=43%:%
+%:%68=44%:%
+%:%69=45%:%
+%:%70=46%:%
+%:%71=47%:%
+%:%72=48%:%
+%:%73=49%:%
+%:%74=50%:%
+%:%75=51%:%
+%:%76=52%:%
+%:%77=53%:%
+%:%78=54%:%
+%:%79=55%:%
+%:%80=56%:%
+%:%81=57%:%
+%:%82=58%:%
+%:%83=59%:%
+%:%84=60%:%
+%:%85=61%:%
+%:%86=62%:%
+%:%87=63%:%
+%:%88=64%:%
+%:%97=66%:%
+%:%109=68%:%
+%:%110=69%:%
+%:%111=70%:%
+%:%112=71%:%
+%:%113=72%:%
+%:%114=73%:%
+%:%115=74%:%
+%:%116=75%:%
+%:%117=76%:%
+%:%118=77%:%
+%:%119=78%:%
+%:%120=79%:%
+%:%121=80%:%
+%:%122=81%:%
+%:%123=82%:%
+%:%124=83%:%
+%:%125=84%:%
+%:%126=85%:%
+%:%127=86%:%
+%:%128=87%:%
+%:%129=88%:%
+%:%130=89%:%
+%:%139=91%:%
+%:%151=93%:%
+%:%152=94%:%
+%:%153=95%:%
+%:%154=96%:%
+%:%155=97%:%
+%:%156=98%:%
+%:%157=99%:%
+%:%158=100%:%
+%:%159=101%:%
+%:%160=102%:%
+%:%161=103%:%
+%:%162=104%:%
+%:%163=105%:%
+%:%164=106%:%
+%:%165=107%:%
+%:%166=108%:%
+%:%167=109%:%
+%:%168=110%:%
+%:%169=111%:%
+%:%170=112%:%
+%:%171=113%:%
+%:%172=114%:%
+%:%173=115%:%
+%:%174=116%:%
+%:%175=117%:%
+%:%176=118%:%
+%:%177=119%:%
+%:%178=120%:%
+%:%179=121%:%
+%:%180=122%:%
+%:%181=123%:%
+%:%182=124%:%
+%:%183=125%:%
+%:%184=126%:%
+%:%185=127%:%
+%:%186=128%:%
+%:%187=129%:%
+%:%188=130%:%
+%:%189=131%:%
+%:%190=132%:%
+%:%191=133%:%
+%:%192=134%:%
+%:%193=135%:%
+%:%194=136%:%
+%:%195=137%:%
+%:%196=138%:%
+%:%197=139%:%
+%:%198=140%:%
+%:%199=141%:%
+%:%200=142%:%
+%:%201=143%:%
+%:%202=144%:%
+%:%211=146%:%
+%:%223=148%:%
+%:%224=149%:%
+%:%225=150%:%
+%:%226=151%:%
+%:%227=152%:%
+%:%228=153%:%
+%:%229=154%:%
+%:%230=155%:%
+%:%231=156%:%
+%:%232=157%:%
+%:%233=158%:%
+%:%234=159%:%
+%:%235=160%:%
+%:%236=161%:%
+%:%237=162%:%
+%:%238=163%:%
+%:%239=164%:%
+%:%240=165%:%
+%:%241=166%:%
+%:%242=167%:%
+%:%243=168%:%
+%:%244=169%:%
+%:%245=170%:%
+%:%254=172%:%
+%:%266=174%:%
+%:%267=175%:%
+%:%268=176%:%
+%:%269=177%:%
+%:%270=178%:%
+%:%271=179%:%
+%:%272=180%:%
+%:%273=181%:%
+%:%274=182%:%
+%:%275=183%:%
+%:%276=184%:%
+%:%277=185%:%
+%:%278=186%:%
+%:%279=187%:%
+%:%280=188%:%
+%:%281=189%:%
+%:%282=190%:%
+%:%283=191%:%
+%:%284=192%:%
+%:%285=193%:%
+%:%286=194%:%
+%:%287=195%:%
+%:%288=196%:%
+%:%289=197%:%
+%:%290=198%:%
+%:%291=199%:%
+%:%292=200%:%
+%:%293=201%:%
+%:%294=202%:%
+%:%295=203%:%
+%:%296=204%:%
+%:%297=205%:%
+%:%298=206%:%
+%:%299=207%:%
+%:%300=208%:%
+%:%301=209%:%
+%:%302=210%:%
+%:%303=211%:%
+%:%304=212%:%
+%:%305=213%:%
+%:%306=214%:%
+%:%307=215%:%
+%:%308=216%:%
+%:%309=217%:%
+%:%310=218%:%
+%:%311=219%:%
+%:%312=220%:%
+%:%313=221%:%
+%:%314=222%:%
+%:%315=223%:%
+%:%316=224%:%
+%:%317=225%:%
+%:%318=226%:%

### 2021-10-13 paper/output/document/upshot.tex
added philosophical upshot

%
\begin{isabellebody}%
\setisabellecontext{upshot}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Philosophical Contributions%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
I argue that computational ethics should be useful for and interesting to philosophers for two 
reasons. First, it serves as the basis for AI agents with the capacity for philosophically sophisticated 
ethical reasoning. For example, my project contributes an implementation of the Formula of Universal Law
that an AI agent could use to reason about the world using the categorical imperative. Second, computational 
ethics helps philosophers think about ethics in the same way that calculators or theorem provers help 
mathematicians think about math. I am not arguing that the computer can replace human reasoning or prove things
that humans theoretically couldn't do. Instead, I argue that the computer bolsters human reasoning, firstly by forcing precision due to 
the rigid syntax of a computer program and secondly by making formal proofs less tedious. Below, I explore each of 
these contributions in greater detail.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{AI Agents%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
As artifical intelligence becomes more powerful, science fiction looms closer to reality and the 
danger of ``unethical" AI becomes more urgent. Ethically intelligent artificial agents will need to 
be able to reason about sophisticated ethical theories in order to navigate the world. My project could 
serve as one component of a complete ethical reasoner. Specifically, my project could easily be repurposed 
into a library or ``engine" that takes as input the logical representation of a maxim and determines if it is obligatory, prohibited, 
or permissible.

As it stands, my project can evaluate the moral status of maxims represented in my logic and potentially 
serves as one component of an ``ethics engine," which an AI agent could use to make ethical decisions.
For example, my system could be combined with an input parser to translate moral dilemmas or situations into maxims in my logic and an output 
to translate the moral status output of my system into a prescription for what action should be taken.
The diagram below depicts the workflow of this example of an ethics engine.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{figure}
\centering
\includegraphics[scale=0.4]{AI_engine.png}
\caption{An example of an ethics engine for an artificial agent} \label{fig:1}
\end{figure}
%
\begin{isamarkuptext}%
In this workflow, an AI agent is faced with a moral dilemma in some internal representation and 
passes this representation to a parser, which converts it to the appropriate logical representation 
for my system to evaluate. For example, if an AI agent represents the moral dilemma in natural language, 
the parser would convert the natural language representation to a representation in my logic.

Once the
input is a sentence in my logic, my project can evaluate its moral status using my implementation of 
the FUL. Concretely, my project would return a value indicating if the maxim is obligatory, permissible, 
or prohibited. The maxim would be prohibited if it fails the universalizability test, permissible if it passes, and obligatory 
if its negation fails the universalizability test. All three of these properties amount to testing if a 
certain theorem holds or not in my logic, a calculation that I demonstrate repeatedly in my tests.

This output could then be converted into some actionable, useful response for the AI agent with another 
output parser. For example, if the AI agent is equipped to evaluate natural language prescriptions, the 
status of the maxim could be parsed into a natural language sentence. This output will be passed back 
to the AI agent, which will make a decision using it.

The ethics engine depicted above is merely one way to use my project to guide an artifical agent. The 
upshot is that an automated version of the categorical imperative could function as the ethical engine 
for an AI agent, with some work to parse the input and the output. Effectively, some version of the kind 
of automated ethics I implement could be 
exposed as an ``ethics API" that AI developers could use to easily give AI agent the capacity for 
sophisticated ethical reasoning faithful to philosophical literature. This represents an improvement 
over existing ethics engines, which, as I examine in Section ??, rarely attempt to capture the complexity 
of any ethical theory that philosophers plausibly defend.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Computational Philosophy%
}
\isamarkuptrue%
%
\isamarkupsubsubsection{Example of a  Philosophical Insight%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
As I tested prior formulations of the categorical imperative and implemented my own, the process 
of implementing a formalization and testing it using an interactive theorem prover resulted in philosophical 
insights that were novel to me. The process resulted in surprising logical results that provoked 
interesting philosophical conversations as I tried to understand their implications for the ethical 
theory I am formalizing.

For example, as I was implementing my formalization of the FUL, I realized
that my formalization was inconsistent unless I specified that the FUL only held for ``well-formed maxims,"
such that neither the act nor goal were already achieved in the given circumstances. Below I document how 
I came to this conclusion. First, I used Sledgehammer to show that my formalization of the FUL\footnote{The full logical representation is \isa{FUL{\isadigit{0}}\ {\isasymequiv}\ {\isasymforall}c\ a\ g\ s{\isachardot}\ not{\isacharunderscore}universalizable\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ {\isasymlongrightarrow}\ {\isasymTurnstile}prohibited\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s}.}
resulted in a contradiction. Sledgehammer was able to tell me which axioms it used to complete 
this proof, showing me that my formalization contradicted the axiom O\_diamond, which states that an 
obligated term cannot contradict its context. I hypothesized that there was some tension between 
the antecedent of the FUL, which states that a maxim is acted on by all agents, and the consequent, 
which states that a maxim is prohibited. If the maxim has already been acted on, then not acting on it
becomes impossible so the prohibition is impossible to obey!

To solve this problem, I returned to Korsgaard's practical contradiction interpretation and focused 
on the imaginatory component of the FUL. Specifically, the universalizability test requires that we IMAGINE 
a world where the maxim is universalized, not that the maxim is actually universalized at this world. 
I implemented another version of the FUL under which, if a maxim is universalized at any world and rendered
ineffective at that world, it is prohibited at the current world. I hypothesized that this would remove 
the contradiction found above. However, Nitpick was still timing out when looking for a model that
satisfied this new version of the FUL. Nitpick is a model checker that generates models that satisfy 
some axioms and theorems, and usually it is able to find small satisfying models in a matter of seconds. 
The fact that Nitpick was timing out was a serious indication that my formalization was still not 
consistent.

I suspected that Nitpick could possibly be timing out due to checking large models that exhausted its 
time limit. To avoid this, I decided to help the system out and specify the exact number of maxims 
in the system by passing as an argument to Nitpick the cardinality of my desired model. This did not 
fix the problem. I next defined a particular (circumstance, act, goal) tuple as a constant and, instead of
stating that the FUL held for all maxims, I stated that the FUL held for the specific maxim formed by this tuple.
To my surprise, Nitpick was now able to show that the FUL was consistent!

This initially appeared counterintuitive—after all, what is the difference between a model of cardinality 
1 and a model with one constant object? Professor Amin pointed out that as constants, the circumstances, 
act, and goal for which the FUL held were all distinct, but when quantified over they were not. One line 
of code later, I tested this hypothesis and found that, indeed, specifying that the circumstances could 
not entail the act or goal fixed the inconsistency! This logical inconsistency showed me that the FUL 
could not hold for maxims in which the act or goal have already been achieved in the circumstances.

To understand this property as a philoosphical insight, I returned to Korsgaard and O'Neill's 
interpretations of maxims as practical, action-guiding principles, and concluding that a maxim in 
which the circumstances already entail the act or goal is vacuous and not a useful practical principle 
to evaluate. This is a non-trivial philosophical insight that the computer helped me discover!%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Two Uses of Computational Ethics%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
I do not argue that computational ethics uncovers philosophical insights that humans have not reached 
or are incapable of reaching. After all, my understanding of a well-formed maxim could 
very well exist in the literature and certainly could be reached by a philosopher working without any 
computational tools. Instead, I argue that computational tools prompt philosophers to ask questions that 
lead to insights. The computer offers a different perspective by forcing philosophers to make their 
work precise and allowing them to quickly complete proofs that would otherwise be tedious.

Representing a philosophical idea in logic and implementing it in an interactive theorem prover requires 
making the idea precise to a degree that ordinary discussion does not require. The initial representation 
of an idea in a logic requires extracting the essence of the idea and making its form precise. For example, 
as I formalized the notion of a maxim, I had to understand its components and make its form as a 
circumstance, act, goal tuple precise. Moreover, Isabelle's strict typing system required that I define 
coherent, consistent types for each of these entities and for a maxim as a whole. This requires understanding 
what role each of these components play in the FUL and assigning them each a type. In my example, I 
concluded that circumstances and goals are terms, which can be true or false at a world, and acts are 
open sentences, which are true for a particular subject at a particular world. This precision is possible 
without computational tools, but computational ethics forces a level of precision that ordinary discussion 
does not demand. Type fuzziness and overloaded definitions are all too common in philosophical writing and 
discussion (would be cool to cite some famous debate revolving around this idea), but computers don't 
allow this kind of imprecision.

The second virtue of computational ethics is that it makes formal ethics far less tedious, and therefore 
within reach even for non-logicians. There is plenty of work attempting to develop logical representations 
of philosophical phenomena in order to make these phenomena precise and use the tools of logic to prove 
facts about them. Much of this work, however, requires tedious pencil and paper proofs which may not 
always produce relevant philosophical insights. Interactive theorem provers make such proofs accessible 
even to philosophers who don't specialize in logic. Moreover, these proofs start from first principles 
without requiring that a human being write pages and pages of syllogism as in Principia Mathematica. 
Just as calculators make arithmetic fast and accessible to non-specialists, computational ethics does the same for 
formal philosophy.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Looking Forward%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
My project does not demonstrate that computational ethics can discover new philosophical 
insights that humans are incapable of reaching. After all, my understanding of a well-formed maxim could 
very well exist in the literature and certainly could be reached by a philosopher working without any 
computational tools. Instead, the upshot is that working with a computer, today, is another way for 
philosophers to arrive at philosophical insights. Just as theorem provers do not replace mathematicians 
entirely, computational ethics does not outdo the philosopher but instead helps them do their work faster. 
The computer offers a different perspective and prompts new questions that lead to insights.

Computational ethics is at its infancy. The use of theorem provers in mathematics is just now beginning 
to make headway (cite Kevin Buzzard), even though theorem provers were first invented in the 1960's (cite 
https://www.cl.cam.ac.uk/~jrh13/papers/joerg.pdf). In contrast, the first attempts to use theorem 
provers for ethics occurred in the last decade. The fact that this nascent technology is already 
helping humans reach non-trivial philosophical conclusions is reason to, at the very least, entertain 
the possibility of a future where computational ethics becomes as normal as using a calculator for arithmetic.

To the skeptic, the ethical insights uncovered by the computer are not necessarily trendy or impressive 
philosophy. Indeed, the fact that a theorem prover requires specialized knowledge outside of the field 
of philosopher indicates that the technology is nowhere near ready for universal use in philosophy 
departments. However, history indicates that as computing power increases and computer scientists make 
progress, computational ethics will become more usable. Theorem provers in mathematics began as toys 
incapable of proving that the real number 2 is not equal to the real number 1, but Buzzard showed that 
moving from such a primitive system to a tool for Fields medal winning mathematics is possible in a 
matter of years (cite Buzzard). Countless examples from the history of computer science, from the Turing 
Test to AI game playing to protein folding, demonstrate that progress in computer science can make seemingly 
obscure computer programs useful and usable in ways that exceed our wildest imaginations. Indeed, 
programmable computers themselves initially began as unwieldy punch card readers, but their current ubiquity 
need not be stated. If computer scientists and philosophers invest in computational ethics, it can 
become as much a tool for philosophy as a calculator is for for arithmetic.\footnote{Is this too like, 
lalalala fantasy of computational philosophy?}%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/upshot.thy%:%
%:%24=6%:%
%:%36=8%:%
%:%37=9%:%
%:%38=10%:%
%:%39=11%:%
%:%40=12%:%
%:%41=13%:%
%:%42=14%:%
%:%43=15%:%
%:%44=16%:%
%:%53=18%:%
%:%65=20%:%
%:%66=21%:%
%:%67=22%:%
%:%68=23%:%
%:%69=24%:%
%:%70=25%:%
%:%71=26%:%
%:%72=27%:%
%:%73=28%:%
%:%74=29%:%
%:%75=30%:%
%:%76=31%:%
%:%79=35%:%
%:%80=36%:%
%:%81=37%:%
%:%82=38%:%
%:%83=39%:%
%:%86=41%:%
%:%87=42%:%
%:%88=43%:%
%:%89=44%:%
%:%90=45%:%
%:%91=46%:%
%:%92=47%:%
%:%93=48%:%
%:%94=49%:%
%:%95=50%:%
%:%96=51%:%
%:%97=52%:%
%:%98=53%:%
%:%99=54%:%
%:%100=55%:%
%:%101=56%:%
%:%102=57%:%
%:%103=58%:%
%:%104=59%:%
%:%105=60%:%
%:%106=61%:%
%:%107=62%:%
%:%108=63%:%
%:%109=64%:%
%:%110=65%:%
%:%119=67%:%
%:%123=69%:%
%:%135=71%:%
%:%136=72%:%
%:%137=73%:%
%:%138=74%:%
%:%139=75%:%
%:%140=76%:%
%:%141=77%:%
%:%142=78%:%
%:%143=79%:%
%:%144=80%:%
%:%145=81%:%
%:%146=82%:%
%:%147=83%:%
%:%148=84%:%
%:%149=85%:%
%:%150=86%:%
%:%151=87%:%
%:%152=88%:%
%:%153=89%:%
%:%154=90%:%
%:%155=91%:%
%:%156=92%:%
%:%157=93%:%
%:%158=94%:%
%:%159=95%:%
%:%160=96%:%
%:%161=97%:%
%:%162=98%:%
%:%163=99%:%
%:%164=100%:%
%:%165=101%:%
%:%166=102%:%
%:%167=103%:%
%:%168=104%:%
%:%169=105%:%
%:%170=106%:%
%:%171=107%:%
%:%172=108%:%
%:%173=109%:%
%:%174=110%:%
%:%175=111%:%
%:%176=112%:%
%:%177=113%:%
%:%178=114%:%
%:%179=115%:%
%:%180=116%:%
%:%189=118%:%
%:%201=120%:%
%:%202=121%:%
%:%203=122%:%
%:%204=123%:%
%:%205=124%:%
%:%206=125%:%
%:%207=126%:%
%:%208=127%:%
%:%209=128%:%
%:%210=129%:%
%:%211=130%:%
%:%212=131%:%
%:%213=132%:%
%:%214=133%:%
%:%215=134%:%
%:%216=135%:%
%:%217=136%:%
%:%218=137%:%
%:%219=138%:%
%:%220=139%:%
%:%221=140%:%
%:%222=141%:%
%:%223=142%:%
%:%224=143%:%
%:%225=144%:%
%:%226=145%:%
%:%227=146%:%
%:%228=147%:%
%:%229=148%:%
%:%230=149%:%
%:%239=151%:%
%:%251=153%:%
%:%252=154%:%
%:%253=155%:%
%:%254=156%:%
%:%255=157%:%
%:%256=158%:%
%:%257=159%:%
%:%258=160%:%
%:%259=161%:%
%:%260=162%:%
%:%261=163%:%
%:%262=164%:%
%:%263=165%:%
%:%264=166%:%
%:%265=167%:%
%:%266=168%:%
%:%267=169%:%
%:%268=170%:%
%:%269=171%:%
%:%270=172%:%
%:%271=173%:%
%:%272=174%:%
%:%273=175%:%
%:%274=176%:%
%:%275=177%:%
%:%276=178%:%
%:%277=179%:%
%:%278=180%:%
%:%279=181%:%
%:%280=182%:%

### 2021-10-13 paper/output/document/upshot.tex
added writing

@@
 that humans theoretically couldn't do. Instead, I argue that the computer bolsters human reasoning, firstly by forcing precision due to 
-the rigid syntax of a computer program and secondly by making formal proofs less tedious. Below, I explore each of 
+the rigid syntax of a computer program and secondly by making formal proofs less tedious. Below, I explore 
 these contributions in greater detail.%
@@
 \begin{isamarkuptext}%
-As artifical intelligence becomes more powerful, science fiction looms closer to reality and the 
-danger of ``unethical" AI becomes more urgent. Ethically intelligent artificial agents will need to 
+As artifical intelligence becomes more powerful, the need for ethical AI becomes more urgent.
+ Ethically intelligent artificial agents will need to 
 be able to reason about sophisticated ethical theories in order to navigate the world. My project could 
-serve as one component of a complete ethical reasoner. Specifically, my project could easily be repurposed 
-into a library or ``engine" that takes as input the logical representation of a maxim and determines if it is obligatory, prohibited, 
+serve as one component of a complete ethical reasoner. Specifically, my project could be repurposed 
+into a library that takes as input the logical representation of a maxim and determines if it is obligatory, prohibited, 
 or permissible.
@@
 As it stands, my project can evaluate the moral status of maxims represented in my logic and potentially 
-serves as one component of an ``ethics engine," which an AI agent could use to make ethical decisions.
-For example, my system could be combined with an input parser to translate moral dilemmas or situations into maxims in my logic and an output 
-to translate the moral status output of my system into a prescription for what action should be taken.
-The diagram below depicts the workflow of this example of an ethics engine.%
+serves as one component of an ``ethics engine," that an AI agent could use to make ethical decisions.
+For example, my system could be combined with an input parser to translate moral dilemmas as represented to the AI agent into maxims in my logic and an output 
+parser to translate the output of my system into a prescription for the action the AI agent should take.
+\ref{fig:AIengine} depicts the workflow of this example of an ethics engine.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \includegraphics[scale=0.4]{AI_engine.png}
-\caption{An example of an ethics engine for an artificial agent} \label{fig:1}
+\caption{An example of an ethics engine for an artificial agent} \label{fig:AIengine}
 \end{figure}
@@
 In this workflow, an AI agent is faced with a moral dilemma in some internal representation and 
-passes this representation to a parser, which converts it to the appropriate logical representation 
+passes this representation to an input parser, which converts it to the appropriate logical representation 
 for my system to evaluate. For example, if an AI agent represents the moral dilemma in natural language, 
@@
 if its negation fails the universalizability test. All three of these properties amount to testing if a 
-certain theorem holds or not in my logic, a calculation that I demonstrate repeatedly in my tests.
+certain theorem holds or not in my logic, a calculation that I demonstrate in my tests.
 
-This output could then be converted into some actionable, useful response for the AI agent with another 
-output parser. For example, if the AI agent is equipped to evaluate natural language prescriptions, the 
+This output could then be converted into some actionable, useful response with another output parser, 
+and then passed back to the AI agent. For example, if the AI agent is equipped to evaluate natural language prescriptions, the 
 status of the maxim could be parsed into a natural language sentence. This output will be passed back 
-to the AI agent, which will make a decision using it.
+to the AI agent, which will use it to make a decision. The input parser, categorical imperative library, 
+and output parser together constitute an ``ethics engine" that AI agents could use as a black box 
+implementation of an ethical theory.
 
-The ethics engine depicted above is merely one way to use my project to guide an artifical agent. The 
+The ethics engine depicted above is a high-level example of one way to use my project to guide an artifical agent. The 
 upshot is that an automated version of the categorical imperative could function as the ethical engine 
-for an AI agent, with some work to parse the input and the output. Effectively, some version of the kind 
+for an AI agent, with some work to parse the input and the output. Effectively, the kind 
 of automated ethics I implement could be 
@@
 sophisticated ethical reasoning faithful to philosophical literature. This represents an improvement 
-over existing ethics engines, which, as I examine in Section ??, rarely attempt to capture the complexity 
-of any ethical theory that philosophers plausibly defend.%
+over existing ethics engines, which rarely attempt to capture the complexity 
+of any ethical theory that philosophers plausibly defend. For more on how my project is situated 
+among other work in automated ethics, see Section ??%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
+Above I explain how my system offers a mechanism for humans to build ethical AI agents. I also 
+argue that computational ethics is a mechanism for computers to help humans think differently about 
+philosophy. Just as theorem provers make mathematics more efficient and push mathematicians to think 
+precisely about the phenomena they are modelling, computational ethics can help philosophers think about 
+philosophy. Below I share an example of the kind of philosophical insight that computational ethics 
+can prompt and analyze the value that this tool offers to philosophers.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
 %
@@
 \begin{isamarkuptext}%
-As I tested prior formulations of the categorical imperative and implemented my own, the process 
-of implementing a formalization and testing it using an interactive theorem prover resulted in philosophical 
-insights that were novel to me. The process resulted in surprising logical results that provoked 
+As I tested prior formalizations of the categorical imperative and created my own, the process 
+of implementing and testing a formalization using an interactive theorem prover resulted in philosophical 
+insights that were novel to me. I reached surprising logical results that provoked 
 interesting philosophical conversations as I tried to understand their implications for the ethical 
-theory I am formalizing.
-
-For example, as I was implementing my formalization of the FUL, I realized
+theory I am formalizing. This serves as an example for how computational ethics can prompt philosophical 
+insights. For example, as I was implementing my formalization of the FUL, I realized
 that my formalization was inconsistent unless I specified that the FUL only held for ``well-formed maxims,"
@@
 I came to this conclusion.
+
 First, I used Sledgehammer to show that my formalization of the FUL\footnote{The full logical representation is \isa{FUL{\isadigit{0}}\ {\isasymequiv}\ {\isasymforall}c\ a\ g\ s{\isachardot}\ not{\isacharunderscore}universalizable\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ {\isasymlongrightarrow}\ {\isasymTurnstile}prohibited\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s}.}
@@
 which states that a maxim is prohibited. If the maxim has already been acted on, then not acting on it
-becomes impossible so the prohibition is impossible to obey!
+becomes impossible so the prohibition is impossible to obey.
 
 To solve this problem, I returned to Korsgaard's practical contradiction interpretation and focused 
-on the imaginatory component of the FUL. Specifically, the universalizability test requires that we IMAGINE 
-a world where the maxim is universalized, not that the maxim is actually universalized at this world. 
+on the imaginatory component of the FUL. Specifically, the universalizability test requires that we imagine 
+a world where the maxim is universalized, not that the maxim is actually universalized at the actual world. 
 I implemented another version of the FUL under which, if a maxim is universalized at any world and rendered
 ineffective at that world, it is prohibited at the current world. I hypothesized that this would remove 
-the contradiction found above. However, Nitpick was still timing out when looking for a model that
-satisfied this new version of the FUL. Nitpick is a model checker that generates models that satisfy 
-some axioms and theorems, and usually it is able to find small satisfying models in a matter of seconds. 
-The fact that Nitpick was timing out was a serious indication that my formalization was still not 
-consistent.
+the contradiction found above. To test this new formalization, I used Nitpick, a model checker that 
+quickly generates models that satisfy some axioms and theorems. Usually, Nitpick can find a satisfying 
+model to show that a logic is consistent in a matter of seconds, but Nitpick consistently timed out 
+when looking for a model of my modified FUL.
 
-I suspected that Nitpick could possibly be timing out due to checking large models that exhausted its 
-time limit. To avoid this, I decided to help the system out and specify the exact number of maxims 
+Nitpick generates many models and checks if they satisfy the given maxims. I suspected that Nitpick 
+could potentially be timing out due to checking large models that exhausted its 
+time limit, especially due to the logical complexity of my theory. To avoid this, I decided to specify the exact number of maxims 
 in the system by passing as an argument to Nitpick the cardinality of my desired model. This did not 
@@
 stating that the FUL held for all maxims, I stated that the FUL held for the specific maxim formed by this tuple.
-To my surprise, Nitpick was now able to show that the FUL was consistent!
+To my surprise, Nitpick was now able to show that the FUL was consistent.
 
-This initially appeared counterintuitive—after all, what is the difference between a model of cardinality 
+This appeared counterintuitive—after all, what is the difference between a model of cardinality 
 1 and a model with one constant object? Professor Amin pointed out that as constants, the circumstances, 
-act, and goal for which the FUL held were all distinct, but when quantified over they were not. One line 
-of code later, I tested this hypothesis and found that, indeed, specifying that the circumstances could 
-not entail the act or goal fixed the inconsistency! This logical inconsistency showed me that the FUL 
+act, and goal for which the FUL held were all distinct, but could be the same when quantified over. One line 
+of code later, I tested this hypothesis and found that requiring that the circumstances did 
+not entail the act or goal fixed the inconsistency. This logical inconsistency showed me that the FUL 
 could not hold for maxims in which the act or goal have already been achieved in the circumstances.
 
-To understand this property as a philoosphical insight, I returned to Korsgaard and O'Neill's 
-interpretations of maxims as practical, action-guiding principles, and concluding that a maxim in 
-which the circumstances already entail the act or goal is vacuous and not a useful practical principle 
-to evaluate. This is a non-trivial philosophical insight that the computer helped me discover!%
+To understand the philosophical plausibility of this property, I returned to Korsgaard and O'Neill's 
+interpretations of maxims as practical, action-guiding principles. A maxim in 
+which the circumstances already entail the act or goal is vacuous and therefore not a useful practical principle 
+to evaluate. For example, the maxim, ``When I am eating breakfast, eat breakfast in order to eat breakfast," 
+is not necessarily prohibited, but it is the wrong kind of question to be asking. The Formula of Universal 
+Law is supposed to guide practical reason, the force that we use to navigate the world and decide what 
+to do. Poorly formed maxims are of no use to practical reason and are the wrong kind of input to pass
+to the categorical imperative. This is a non-trivial philosophical insight that the computer helped me discover.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-I do not argue that computational ethics uncovers philosophical insights that humans have not reached 
+I do not argue that computational ethics, as it stands today, uncovers philosophical insights that humans have not reached 
 or are incapable of reaching. After all, my understanding of a well-formed maxim could 
@@
 lead to insights. The computer offers a different perspective by forcing philosophers to make their 
-work precise and allowing them to quickly complete proofs that would otherwise be tedious.
+work precise and allowing them to quickly complete proofs that would otherwise be tedious. Computational 
+ethics can serve as another tool in a philosopher's arsenal, like a thought experiment or counterexample.
 
+The first contribution of computational ethics is precision.
 Representing a philosophical idea in logic and implementing it in an interactive theorem prover requires 
 making the idea precise to a degree that ordinary discussion does not require. The initial representation 
-of an idea in a logic requires extracting the essence of the idea and making its form precise. For example, 
-as I formalized the notion of a maxim, I had to understand its components and make its form as a 
-circumstance, act, goal tuple precise. Moreover, Isabelle's strict typing system required that I define 
+of an idea in a logic requires making its form precise. For example, 
+as I formalized the notion of a maxim, I had to understand its components and define it as a 
+circumstance, act, goal tuple. Moreover, Isabelle's strict typing system required that I define 
 coherent, consistent types for each of these entities and for a maxim as a whole. This requires understanding 
@@
 of philosophical phenomena in order to make these phenomena precise and use the tools of logic to prove 
-facts about them. Much of this work, however, requires tedious pencil and paper proofs which may not 
+facts about them\footnote{Is there? Should cite stuff}. Much of this work, however, requires tedious pencil and paper proofs which may not 
 always produce relevant philosophical insights. Interactive theorem provers make such proofs accessible 
@@
 \begin{isamarkuptext}%
-My project does not demonstrate that computational ethics can discover new philosophical 
-insights that humans are incapable of reaching. After all, my understanding of a well-formed maxim could 
-very well exist in the literature and certainly could be reached by a philosopher working without any 
-computational tools. Instead, the upshot is that working with a computer, today, is another way for 
-philosophers to arrive at philosophical insights. Just as theorem provers do not replace mathematicians 
-entirely, computational ethics does not outdo the philosopher but instead helps them do their work faster. 
-The computer offers a different perspective and prompts new questions that lead to insights.
-
 Computational ethics is at its infancy. The use of theorem provers in mathematics is just now beginning 
-to make headway (cite Kevin Buzzard), even though theorem provers were first invented in the 1960's (cite 
-https://www.cl.cam.ac.uk/~jrh13/papers/joerg.pdf). In contrast, the first attempts to use theorem 
+to make headway \cite{buzzardvideo}, even though theorem provers were first invented in the 1960's \cite{historyofITP}. In contrast, the first attempts to use theorem 
 provers for ethics occurred in the last decade. The fact that this nascent technology is already 
@@
 
-To the skeptic, the ethical insights uncovered by the computer are not necessarily trendy or impressive 
+To the skeptic, the ethical insights uncovered by the computer are not necessarily impressive 
 philosophy. Indeed, the fact that a theorem prover requires specialized knowledge outside of the field 
-of philosopher indicates that the technology is nowhere near ready for universal use in philosophy 
+of philosophy indicates that the technology is nowhere near ready for universal use in philosophy 
 departments. However, history indicates that as computing power increases and computer scientists make 
@@
 moving from such a primitive system to a tool for Fields medal winning mathematics is possible in a 
-matter of years (cite Buzzard). Countless examples from the history of computer science, from the Turing 
+matter of years \cite{buzzardvideo}. Countless examples from the history of computer science, from the Turing 
 Test to AI game playing to protein folding, demonstrate that progress in computer science can make seemingly 
@@
 become as much a tool for philosophy as a calculator is for for arithmetic.\footnote{Is this too like, 
-lalalala fantasy of computational philosophy?}%
+lalalala fantasy of computational philosophy? Would it be less so if I did more work explaining 
+the history of theorem proving for math? Is this even that important for my project?}%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %:%110=65%:%
-%:%119=67%:%
-%:%123=69%:%
-%:%135=71%:%
-%:%136=72%:%
-%:%137=73%:%
-%:%138=74%:%
-%:%139=75%:%
-%:%140=76%:%
-%:%141=77%:%
-%:%142=78%:%
-%:%143=79%:%
-%:%144=80%:%
-%:%145=81%:%
-%:%146=82%:%
-%:%147=83%:%
-%:%148=84%:%
-%:%149=85%:%
-%:%150=86%:%
-%:%151=87%:%
-%:%152=88%:%
-%:%153=89%:%
-%:%154=90%:%
-%:%155=91%:%
-%:%156=92%:%
-%:%157=93%:%
-%:%158=94%:%
-%:%159=95%:%
-%:%160=96%:%
-%:%161=97%:%
-%:%162=98%:%
-%:%163=99%:%
-%:%164=100%:%
-%:%165=101%:%
-%:%166=102%:%
-%:%167=103%:%
-%:%168=104%:%
-%:%169=105%:%
-%:%170=106%:%
-%:%171=107%:%
-%:%172=108%:%
-%:%173=109%:%
-%:%174=110%:%
-%:%175=111%:%
-%:%176=112%:%
-%:%177=113%:%
-%:%178=114%:%
-%:%179=115%:%
-%:%180=116%:%
-%:%189=118%:%
-%:%201=120%:%
-%:%202=121%:%
-%:%203=122%:%
-%:%204=123%:%
-%:%205=124%:%
-%:%206=125%:%
-%:%207=126%:%
-%:%208=127%:%
-%:%209=128%:%
-%:%210=129%:%
-%:%211=130%:%
-%:%212=131%:%
-%:%213=132%:%
-%:%214=133%:%
-%:%215=134%:%
-%:%216=135%:%
-%:%217=136%:%
-%:%218=137%:%
-%:%219=138%:%
-%:%220=139%:%
-%:%221=140%:%
-%:%222=141%:%
-%:%223=142%:%
-%:%224=143%:%
-%:%225=144%:%
-%:%226=145%:%
-%:%227=146%:%
-%:%228=147%:%
-%:%229=148%:%
-%:%230=149%:%
-%:%239=151%:%
-%:%251=153%:%
-%:%252=154%:%
-%:%253=155%:%
-%:%254=156%:%
-%:%255=157%:%
-%:%256=158%:%
-%:%257=159%:%
-%:%258=160%:%
-%:%259=161%:%
-%:%260=162%:%
-%:%261=163%:%
-%:%262=164%:%
-%:%263=165%:%
-%:%264=166%:%
-%:%265=167%:%
-%:%266=168%:%
-%:%267=169%:%
-%:%268=170%:%
-%:%269=171%:%
-%:%270=172%:%
-%:%271=173%:%
-%:%272=174%:%
-%:%273=175%:%
-%:%274=176%:%
-%:%275=177%:%
-%:%276=178%:%
-%:%277=179%:%
-%:%278=180%:%
-%:%279=181%:%
-%:%280=182%:%
+%:%111=66%:%
+%:%112=67%:%
+%:%113=68%:%
+%:%122=70%:%
+%:%134=72%:%
+%:%135=73%:%
+%:%136=74%:%
+%:%137=75%:%
+%:%138=76%:%
+%:%139=77%:%
+%:%148=79%:%
+%:%160=81%:%
+%:%161=82%:%
+%:%162=83%:%
+%:%163=84%:%
+%:%164=85%:%
+%:%165=86%:%
+%:%166=87%:%
+%:%167=88%:%
+%:%168=89%:%
+%:%169=90%:%
+%:%170=91%:%
+%:%171=92%:%
+%:%172=93%:%
+%:%173=94%:%
+%:%174=95%:%
+%:%175=96%:%
+%:%176=97%:%
+%:%177=98%:%
+%:%178=99%:%
+%:%179=100%:%
+%:%180=101%:%
+%:%181=102%:%
+%:%182=103%:%
+%:%183=104%:%
+%:%184=105%:%
+%:%185=106%:%
+%:%186=107%:%
+%:%187=108%:%
+%:%188=109%:%
+%:%189=110%:%
+%:%190=111%:%
+%:%191=112%:%
+%:%192=113%:%
+%:%193=114%:%
+%:%194=115%:%
+%:%195=116%:%
+%:%196=117%:%
+%:%197=118%:%
+%:%198=119%:%
+%:%199=120%:%
+%:%200=121%:%
+%:%201=122%:%
+%:%202=123%:%
+%:%203=124%:%
+%:%204=125%:%
+%:%205=126%:%
+%:%206=127%:%
+%:%207=128%:%
+%:%208=129%:%
+%:%209=130%:%
+%:%210=131%:%
+%:%219=133%:%
+%:%231=135%:%
+%:%232=136%:%
+%:%233=137%:%
+%:%234=138%:%
+%:%235=139%:%
+%:%236=140%:%
+%:%237=141%:%
+%:%238=142%:%
+%:%239=143%:%
+%:%240=144%:%
+%:%241=145%:%
+%:%242=146%:%
+%:%243=147%:%
+%:%244=148%:%
+%:%245=149%:%
+%:%246=150%:%
+%:%247=151%:%
+%:%248=152%:%
+%:%249=153%:%
+%:%250=154%:%
+%:%251=155%:%
+%:%252=156%:%
+%:%253=157%:%
+%:%254=158%:%
+%:%255=159%:%
+%:%256=160%:%
+%:%257=161%:%
+%:%258=162%:%
+%:%259=163%:%
+%:%260=164%:%
+%:%261=165%:%
+%:%262=166%:%
+%:%271=168%:%
+%:%283=171%:%
+%:%284=172%:%
+%:%285=173%:%
+%:%286=174%:%
+%:%287=175%:%
+%:%288=176%:%
+%:%289=177%:%
+%:%290=178%:%
+%:%291=179%:%
+%:%292=180%:%
+%:%293=181%:%
+%:%294=182%:%
+%:%295=183%:%
+%:%296=184%:%
+%:%297=185%:%
+%:%298=186%:%
+%:%299=187%:%
+%:%300=188%:%
+%:%301=189%:%
+%:%302=190%:%
+%:%303=191%:%

### 2021-10-20 paper/output/document/paper32.tex
finished metaethical test

@@
 
-      As my final metaethical test, I will test that an action is either obligatory, permissible, or 
+      Next, I will test that an action is either obligatory, permissible, or 
       prohibited.%
@@
 \isacommand{lemma}\isamarkupfalse%
-\ ob{\isacharunderscore}perm{\isacharcolon}\isanewline
+\ ob{\isacharunderscore}perm{\isacharunderscore}or{\isacharunderscore}prohibited{\isacharcolon}\isanewline
 \ \ \isakeyword{fixes}\ A\ w\isanewline
@@
 }%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+I also expect obligation to be a strictly stronger property than permissibility. Particularly, 
+if A is obligated, then A should also be permissible.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ obligated{\isacharunderscore}then{\isacharunderscore}permissible{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymrightarrow}\ P\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{This test fails in Kroy's interpretation!
+\color{blue}Nitpick found a counterexample for card i = 2 and card s = 1:
+
+  Free variable:
+    A = ($\lambda x. \_$)($i_1$ := False, $i_2$ := True)\color{black}%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
 \endisatagproof
@@
 %:%957=487%:%
-%:%958=488%:%
-%:%959=489%:%
-%:%968=491%:%
-%:%980=493%:%
-%:%981=494%:%
-%:%982=495%:%
-%:%983=496%:%
-%:%987=498%:%
-%:%988=499%:%
-%:%990=501%:%
-%:%991=501%:%
-%:%992=502%:%
-%:%993=503%:%
-%:%994=503%:%
-%:%995=504%:%
-%:%998=505%:%
-%:%1002=505%:%
-%:%1003=505%:%
-%:%1004=505%:%
-%:%1006=506%:%
-%:%1007=507%:%
-%:%1017=509%:%
-%:%1018=510%:%
-%:%1019=511%:%
-%:%1020=512%:%
-%:%1021=513%:%
-%:%1022=514%:%
-%:%1023=515%:%
-%:%1024=516%:%
-%:%1025=517%:%
-%:%1026=518%:%
-%:%1027=519%:%
-%:%1028=520%:%
-%:%1029=521%:%
-%:%1030=522%:%
-%:%1031=523%:%
-%:%1033=525%:%
-%:%1034=525%:%
-%:%1035=526%:%
-%:%1036=527%:%
-%:%1037=528%:%
-%:%1038=528%:%
-%:%1040=528%:%
-%:%1044=528%:%
-%:%1045=528%:%
-%:%1047=529%:%
-%:%1048=530%:%
-%:%1049=531%:%
-%:%1050=532%:%
-%:%1051=533%:%
-%:%1052=534%:%
-%:%1062=536%:%
-%:%1063=537%:%
-%:%1064=538%:%
-%:%1065=539%:%
-%:%1069=541%:%
-%:%1070=542%:%
-%:%1071=543%:%
-%:%1073=545%:%
-%:%1074=545%:%
-%:%1075=546%:%
-%:%1076=546%:%
-%:%1078=547%:%
-%:%1079=548%:%
-%:%1080=548%:%
-%:%1081=549%:%
-%:%1082=550%:%
-%:%1083=550%:%
-%:%1084=551%:%
-%:%1087=552%:%
-%:%1091=552%:%
-%:%1092=552%:%
-%:%1094=553%:%
-%:%1095=554%:%
-%:%1096=555%:%
-%:%1106=557%:%
-%:%1107=558%:%
-%:%1108=559%:%
-%:%1109=560%:%
-%:%1111=562%:%
-%:%1112=562%:%
-%:%1113=563%:%
-%:%1115=563%:%
-%:%1119=563%:%
-%:%1120=563%:%
-%:%1122=564%:%
-%:%1130=564%:%
-%:%1131=565%:%
-%:%1132=566%:%
-%:%1133=566%:%
+%:%959=488%:%
+%:%960=488%:%
+%:%961=489%:%
+%:%962=490%:%
+%:%963=490%:%
+%:%965=490%:%
+%:%969=490%:%
+%:%970=490%:%
+%:%972=491%:%
+%:%973=492%:%
+%:%974=493%:%
+%:%975=494%:%
+%:%976=495%:%
+%:%999=501%:%
+%:%1000=502%:%
+%:%1001=503%:%
+%:%1002=504%:%
+%:%1011=506%:%
+%:%1023=508%:%
+%:%1024=509%:%
+%:%1025=510%:%
+%:%1026=511%:%
+%:%1030=513%:%
+%:%1031=514%:%
+%:%1033=516%:%
+%:%1034=516%:%
+%:%1035=517%:%
+%:%1036=518%:%
+%:%1037=518%:%
+%:%1038=519%:%
+%:%1041=520%:%
+%:%1045=520%:%
+%:%1046=520%:%
+%:%1047=520%:%
+%:%1049=521%:%
+%:%1050=522%:%
+%:%1060=524%:%
+%:%1061=525%:%
+%:%1062=526%:%
+%:%1063=527%:%
+%:%1064=528%:%
+%:%1065=529%:%
+%:%1066=530%:%
+%:%1067=531%:%
+%:%1068=532%:%
+%:%1069=533%:%
+%:%1070=534%:%
+%:%1071=535%:%
+%:%1072=536%:%
+%:%1073=537%:%
+%:%1074=538%:%
+%:%1076=540%:%
+%:%1077=540%:%
+%:%1078=541%:%
+%:%1079=542%:%
+%:%1080=543%:%
+%:%1081=543%:%
+%:%1083=543%:%
+%:%1087=543%:%
+%:%1088=543%:%
+%:%1090=544%:%
+%:%1091=545%:%
+%:%1092=546%:%
+%:%1093=547%:%
+%:%1094=548%:%
+%:%1095=549%:%
+%:%1105=551%:%
+%:%1106=552%:%
+%:%1107=553%:%
+%:%1108=554%:%
+%:%1112=556%:%
+%:%1113=557%:%
+%:%1114=558%:%
+%:%1116=560%:%
+%:%1117=560%:%
+%:%1118=561%:%
+%:%1119=561%:%
+%:%1121=562%:%
+%:%1122=563%:%
+%:%1123=563%:%
+%:%1124=564%:%
+%:%1125=565%:%
+%:%1126=565%:%
+%:%1127=566%:%
+%:%1130=567%:%
 %:%1134=567%:%
-%:%1136=567%:%
-%:%1140=567%:%
-%:%1141=567%:%
-%:%1143=568%:%
-%:%1153=570%:%
-%:%1154=571%:%
-%:%1155=572%:%
+%:%1135=567%:%
+%:%1137=568%:%
+%:%1138=569%:%
+%:%1139=570%:%
+%:%1149=572%:%
+%:%1150=573%:%
+%:%1151=574%:%
+%:%1152=575%:%
+%:%1154=577%:%
+%:%1155=577%:%
+%:%1156=578%:%
+%:%1158=578%:%
+%:%1162=578%:%
+%:%1163=578%:%
+%:%1165=579%:%
+%:%1173=579%:%
+%:%1174=580%:%
+%:%1175=581%:%
+%:%1176=581%:%
+%:%1177=582%:%
+%:%1179=582%:%
+%:%1183=582%:%
+%:%1184=582%:%
+%:%1186=583%:%
+%:%1196=585%:%
+%:%1197=586%:%
+%:%1198=587%:%

### 2021-10-20 paper/output/document/paper41.tex
finished metaethical test

--- 2021-10-11 paper/output/document/paper41.tex
@@
 The central unit of evaluation for the universalizability test is a ``maxim," which Kant defines 
-in a footnote in \emph{Groundworkd} as ``the subjective principle of willing," or the principle that 
+in a footnote in \emph{Groundwork} as ``the subjective principle of willing," or the principle that 
 the agent acts on $\cite[16]{groundwork}$. Modern Kantians differ in their interpretations of this definition. The naive view 
@@
 Korsgaard claims that ``to will an end, rather than just
-wishing for it or wanting it, is to set yourself to be its cause" \cite{sources}. To will a maxim
+wishing for it or wanting it, is to set yourself to be its cause" \cite[38]{sources}. To will a maxim
 is to set yourself to be the cause of its goal by taking the means 
@@
 Worlds where the circumstances do not hold are not relevant for determining obligation. Recall that in 
-\cite{BFP}'s definition of the obligation operator,  $O \{B|A\}$ is true at all worlds iff ob(B)(A), or 
-if the obligation function maps A to obligatory in context B (where the context is a set of worlds). This 
+Benzmueller et. al's definition of the obligation operator,  $O \{B|A\}$ is true at all worlds iff ob(B)(A), or 
+if the obligation function maps A to obligatory in context B (where the context is a set of worlds) \cite{BFP}. This 
 definition implies that worlds outside of B have no bearing on the moral status of A in context B, which 
@@
 \begin{isamarkuptext}%
+As before, the concepts of prohibition and permissibility will be helpful here. The unit of 
+evaluation for my formalization of the FUL is the act of willing a maxim, which entails performing 
+the maxim's act in the relevant circumstances. Therefore, I will say that, just as the act of willing a
+ maxim can be obligatory for a subject, it can be prohibited or permissible for a subject.\footnote{In 
+the rest of this section, for convenience, I will use the phrase ``subject s willing maxim M is obligatory" 
+interchangeably with ``maxim M is obligatory for subject s." I will use ``maxim M is obligatory" to 
+refer to M being obligatory for any arbitrary subject, which I will show to be equivalent to M being 
+obligatory for a specific subject.}%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{abbreviation}\isamarkupfalse%
+\ prohibited{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}t{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
+{\isachardoublequoteopen}prohibited\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isachardot}\ O{\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}will\ {\isacharparenleft}c{\isacharcomma}a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ {\isacharbar}\ c{\isacharbraceright}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ permissible{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}t{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}permissible\ {\isasymequiv}\ {\isasymlambda}M\ s{\isachardot}\ \isactrlbold {\isasymnot}\ {\isacharparenleft}prohibited\ M\ s{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{I will say that a maxim is permissible for a subject if it is not prohibited for that subject to 
+will that maxim.%
+}%
+\begin{isamarkuptext}%
+One problem with prior formalization of the categorical imperative was that they didn't
+prohibit contradictory obligations, partially because DDL itself allows contradictory obligations. 
+Kant subscribes to the general, popular view that morality is supposed to guide action, so ought implies 
+can\footnote{Kohl points out that this principle is referred to as 
+Kant's dictum or Kant's law in the literature. \cite[footnote 1]{kohl}}. Kohl reconstructs his argument for the principle as 
+follows: if the will cannot comply with the moral law, then the moral law has no prescriptive authority 
+for the will \cite[703-4]{kohl}. This defeats the purpose of Kant's theory—to develop an unconditional, categorical imperative 
+for rational agents. Ought implies can requires that obligations never contradict, because an agent 
+can't perform contradictory actions. Therefore, any ethical theory that respects ought implies can, 
+and Kantian ethics in particular, must not result in conflicting obligations.
+
+Kant only briefly discusses contradictory obligations in \emph{Metaphysics of Morals}, where he argues that 
+conflicting moral obligations are impossible under his theory \cite[V224]{metaphysicsintro}. Particularly, the categorical imperative generates 
+``strict negative laws of omission", which cannot conflict by definition \cite[45]{timmerman}.\footnote{The 
+kinds of obligations generated by the FUL are called ``perfect duties" which arise from ``contradictions 
+in conception," or maxims that we cannot even concieve of universalizing. These duties are always negative 
+and thus never conflict. Kant also presents ``imperfect duties," generated from ``contradictions in will,"
+or maxims that we can concieve of universalizing but would never want to. These duties tend to be broader, 
+such as ``improve oneself" or "help others," and are secondary to perfect duties. My project only analyzes 
+perfect duties, as these are stronger than imperfect duties.}
+
+When analyzing the naive formalization and Kroy's formalization, I learned that DDL and the prior 
+formalizations allow contradictory obligations. This is a major weakness of these systems, and my 
+formalization should fix this. To do so, I will add as an axiom the idea that obligations cannot 
+contradict each other or their internal circumstances. Formally, conflicting obligations are defined below.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{abbreviation}\isamarkupfalse%
+\ non{\isacharunderscore}contradictory\ \isakeyword{where}\ \isanewline
+{\isachardoublequoteopen}non{\isacharunderscore}contradictory\ A\ B\ c\ w\ {\isasymequiv}\ {\isacharparenleft}{\isacharparenleft}O{\isacharbraceleft}A{\isacharbar}c{\isacharbraceright}\ \isactrlbold {\isasymand}\ O{\isacharbraceleft}B{\isacharbar}c{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isasymnot}{\isacharparenleft}{\isacharparenleft}A\ \isactrlbold {\isasymand}\ {\isacharparenleft}B\ \isactrlbold {\isasymand}\ c{\isacharparenright}{\isacharparenright}\ w\ {\isasymlongrightarrow}\ False{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Terms A and B are non contradictory in circumstances c if, when A and B are obligated in circumstances 
+c, the conjunction of A, B, and c, does not imply False.%
+}\isanewline
+\isanewline
+\isacommand{axiomatization}\isamarkupfalse%
+\ \isakeyword{where}\ no{\isacharunderscore}contradictions{\isacharcolon}{\isachardoublequoteopen}{\isasymforall}A{\isacharcolon}{\isacharcolon}t{\isachardot}\ {\isasymforall}B{\isacharcolon}{\isacharcolon}t{\isachardot}\ {\isasymforall}c{\isacharcolon}{\isacharcolon}t{\isachardot}\ {\isasymforall}w{\isacharcolon}{\isacharcolon}i{\isachardot}\ non{\isacharunderscore}contradictory\ A\ B\ c\ w{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{This axiom formalizes the idea that, for any terms A, B, and circumstances c, A and B must be 
+non-contradictory in circumstances c at all worlds. Intuitively, this axiom requires that obligations 
+do not conflict.%
+}%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsection{Formalizing the FUL%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
 Below is my first attempt at formalizing Korgsaard's definition of the practical contradiction
@@
 \end{isamarkuptext}\isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ prohibited{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}t{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
-{\isachardoublequoteopen}prohibited\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isachardot}\ O{\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}will\ {\isacharparenleft}c{\isacharcomma}a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ {\isacharbar}\ c{\isacharbraceright}{\isachardoublequoteclose}\isanewline
-\isanewline
 \isacommand{abbreviation}\isamarkupfalse%
@@
 or prohibited, but it is the wrong kind of question to be asking. It is not a 
-well-formed maxim, so the categorical imperative does not apply to it.%
+well-formed maxim, so the categorical imperative does not apply to it. (more explanation in philosophical 
+writing collection)%
 \end{isamarkuptext}\isamarkuptrue%
@@
   Skolem constants:
-    a = ($\lambda x. \_$)($s_1$ := ($\lambda x. \_$)($i_1$ := False))
-    c = ($\lambda x. \_$)($i_1$ := True)
-    g = ($\lambda x. \_$)($i_1$ := False)
-    $\lambda w$. p = ($\lambda x. \_$)($i_1$ := $s_1$)
+    M = (($\lambda x. \_$)($i_1$ := True), ($\lambda x. \_$)($s_1$ := ($\lambda x. \_$)($i_1$ := False)), ($\lambda x. \_$)
+         ($i_1$ := False))
+    $\lambda$ w. p = ($\lambda x. \_$)($i_1$ := $s_1$)
     s = $s_1$ $\color{black}$%
@@
 \end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsection{Application Tests%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
+As with the naive formalization and Kroy's formalization, I will apply my testing framework to 
+my custom formalization of the FUL. I will begin with some basic application tests. In these tests, 
+I specify particular maxims as constants with no properties and gradually add properties to understand 
+how the system handles different kinds of maxims.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsection{Metaethical Tests%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
+Recall that metaethical tests test formal properties of the system that apply to any maxim, not 
+just those specified in the application tests. In this section I adapt the metaethical tests developed 
+in previous sections to my formalization of the categorical imperative. I preserved the philosophical 
+goal of each test but modified them to test the stronger, richer notion of a maxim.
+
+The first set of tests consider how obligation generalizes, first across worlds and then across
+people. As expected, the tests below show that both wrongness (prohibition) and rightness (obligation)
+generalize across both worlds and people. In other words, if something is obligated at some world, it 
+is obligated at every world and if something is obligated for some person, then it is obligated for 
+every person.
+
+Generalization across people coheres with Kantian ethics—maxims are not person-specific.
+Indeed, Velleman argues that, because reason is accessible to everyone identically, obligations apply 
+to all people \cite[25]{velleman}. When Kant describes the categorical imperative as the objective 
+principle of the will, he is referring to the fact that, as opposed to a subjective principle, the categorical
+imperative applies to all rational agents equally $\cite[16]{groundwork}$.
+
+Generalization across worlds is a consequence of the fact that my interpretation does not make use of the 
+modal nature of DDL. In particular, I do not use any property of the world when prescribing obligations 
+at that world.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ wrong{\isacharunderscore}if{\isacharunderscore}wrong{\isacharunderscore}for{\isacharunderscore}someone{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}w{\isachardot}\ {\isasymforall}c{\isacharcolon}{\isacharcolon}t{\isachardot}\ {\isasymforall}g{\isacharcolon}{\isacharcolon}t{\isachardot}\ {\isasymexists}s{\isacharcolon}{\isacharcolon}s{\isachardot}\ O{\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}W\ {\isacharparenleft}c{\isacharcomma}\ M{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ {\isacharbar}\ c{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ \ O{\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}W\ {\isacharparenleft}c{\isacharcomma}\ M{\isacharcomma}\ g{\isacharparenright}\ p{\isacharparenright}\ {\isacharbar}\ c{\isacharbraceright}\ w{\isacharparenright}\ {\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{by}\isamarkupfalse%
+\ blast%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+\isanewline
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ right{\isacharunderscore}if{\isacharunderscore}right{\isacharunderscore}for{\isacharunderscore}someone{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}w{\isachardot}\ {\isasymforall}c{\isacharcolon}{\isacharcolon}t{\isachardot}\ {\isasymforall}g{\isacharcolon}{\isacharcolon}t{\isachardot}\ {\isasymexists}s{\isacharcolon}{\isacharcolon}s{\isachardot}\ O{\isacharbraceleft}W\ {\isacharparenleft}c{\isacharcomma}\ M{\isacharcomma}\ g{\isacharparenright}\ s\ {\isacharbar}\ c{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ \ O{\isacharbraceleft}W\ {\isacharparenleft}c{\isacharcomma}\ M{\isacharcomma}\ g{\isacharparenright}\ p\ {\isacharbar}\ c{\isacharbraceright}\ w{\isacharparenright}\ {\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{by}\isamarkupfalse%
+\ blast%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+\isanewline
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ wrong{\isacharunderscore}if{\isacharunderscore}wrong{\isacharunderscore}somewhere{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}c\ g{\isachardot}\ {\isasymexists}w{\isadigit{1}}{\isachardot}\ O{\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}W\ {\isacharparenleft}c{\isacharcomma}\ M{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ {\isacharbar}\ c{\isacharbraceright}\ w{\isadigit{1}}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}w{\isadigit{2}}{\isachardot}\ \ O{\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}W\ {\isacharparenleft}c{\isacharcomma}\ M{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ {\isacharbar}\ c{\isacharbraceright}\ w{\isadigit{2}}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{by}\isamarkupfalse%
+\ blast%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+\isanewline
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ right{\isacharunderscore}if{\isacharunderscore}right{\isacharunderscore}somewhere{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}c\ g{\isachardot}\ {\isasymexists}w{\isadigit{1}}{\isachardot}\ O{\isacharbraceleft}W\ {\isacharparenleft}c{\isacharcomma}\ M{\isacharcomma}\ g{\isacharparenright}\ s\ {\isacharbar}\ c{\isacharbraceright}\ w{\isadigit{1}}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}w{\isadigit{2}}{\isachardot}\ \ O{\isacharbraceleft}W\ {\isacharparenleft}c{\isacharcomma}\ M{\isacharcomma}\ g{\isacharparenright}\ s\ {\isacharbar}\ c{\isacharbraceright}\ w{\isadigit{2}}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{by}\isamarkupfalse%
+\ blast%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+As expected, obligation generalizes across people and worlds. In the next set of tests, I will 
+analyze basic properties of permissibility, obligation, and prohibition.
+
+First, I verify that the logic allows
+for permissible maxims, as this is a problem that prior iterations ran into. Below, I use Nitpick to 
+find a model in which there is a circumstance, act, goal tuple that is permissible but not 
+obligated at some world.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ permissible{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O{\isacharbraceleft}{\isacharparenleft}W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ {\isacharbar}\ c{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O{\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ {\isacharbar}\ c{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{\color{blue}Nitpick found a model for card i = 1 and card s = 2:
+
+  Free variables:
+    a = ($\lambda x. \_$)($s_1$ := ($\lambda x. \_$)($i_1$ := False), $s_2$ := ($\lambda x. \_$)($i_1$ := False))
+    c = ($\lambda x. \_$)($i_1$ := False)
+    g = ($\lambda x. \_$)($i_1$ := False)
+    s = $s_2$\color{black}
+Recall that Nitpick is a model checker that finds models making certain formulae true or false. In this 
+case, Nitpick finds a model satisfying the given formula (which simply requires that the sentence 
+``s wills (c, a, g)'' is permissible but not obligator). This model consists of the above specifications 
+of a, c, g, and s.%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+I also expect that any arbitrary maxim should be either permissible or prohibited, since all 
+acts are either permissible or prohibited.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ perm{\isacharunderscore}or{\isacharunderscore}prohibited{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}permissible\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ \isactrlbold {\isasymor}\ {\isacharparenleft}prohibited\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{by}\isamarkupfalse%
+\ blast\isanewline
+%
+\isamarkupcmt{This simple test passes immediately by the definitions of  permissible and prohibited.%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+Obligation should be strictly stronger than permissibility. In other words, if a maxim is 
+obligated at a world, it should be permissible at that world. Below I test this property.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ obligated{\isacharunderscore}then{\isacharunderscore}permissible{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}O{\isacharbraceleft}W{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharbar}c{\isacharbraceright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}permissible\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}{\isacharparenright}\ s{\isacharparenright}\ w\ {\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{using}\isamarkupfalse%
+\ no{\isacharunderscore}contradictions\ \isacommand{by}\isamarkupfalse%
+\ auto\isanewline
+%
+\isamarkupcmt{This test passes and Isabelle is able to find a proof for the fact that all obligatory maxims are 
+also permissible.%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+The above test failed under Kroy's formalization of the categorical imperative and is thus evidence 
+that my formalization improves upon Kroy's. Interestingly, this new test passes because of the additional
+added axiom that prohibits contradictory obligations (recall that Kroy's formalization allowed contradictory
+obligations). The proof is clear: if maxims are either permissible or prohibited and obligation contradicts
+prohibition, then obligation must result in permissibility. Moreover, this property REQUIRES that 
+there be no contradictory obligations. Formally, in the base logic DDL, I can show the sentence 
+$(O \{A\} \wedge O \{\neg A\}) \mathbf{\longrightarrow} (\neg (O \{A\} \mathbf{\longrightarrow}  P \{A\})) w$
+\footnote{Sledgehammer can show this sentence to be true in DDL and in Kroy's formalization.}.
+In English, if A and not A are obligated, then A can be obligated but not permissible.
+
+Is there anything philosophically interesting here? Something about the possibility of genuine moral 
+conflict?%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+Next, I will test if the formalization allows for vacuous obligations or modal collapse. These 
+tests are sanity checks confirmed that the obligation operator is doesn't collapse. First, I will check 
+that any arbitrary term isn't obligated.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ arbitrary{\isacharunderscore}obligations{\isacharcolon}\isanewline
+\ \ \isakeyword{fixes}\ c\ A{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}O{\isacharbraceleft}A{\isacharbar}c{\isacharbraceright}\ w{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharequal}true{\isacharcomma}\ falsify{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{This test passes—Nitpick finds a model where A isn't obligated in circumstances c.
+\color{blue} Nitpick found a counterexample for card i = 1 and card s = 2:
+
+  Free variables:
+    A = ($\lambda x. \_$)($i_1$ := True)
+    c = ($\lambda x. \_$)($i_1$ := False) \color{blue}
+Previous iterations of this test used the monadic obligation operator, which tests the term in the 
+context ``True" (equivalently the set of all worlds since True holds everywhere). In this iteration, 
+I test the term in a context c, because my formalization uses the dyadic obligation operator and must 
+thus specify circumstances.%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+This is exactly the expected result. Any arbitrary action $A$ isn't obligated. A slightly 
+        stronger property is ``modal collapse," or whether or not `$A$ happens' implies `$A$ is obligated'. 
+The proposition below should be falsifiable.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ modal{\isacharunderscore}collapse{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ w{\isacharparenright}\ {\isasymlongrightarrow}\ O{\isacharbraceleft}W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharbar}c{\isacharbraceright}\ w{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharequal}true{\isacharcomma}\ falsify{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{Nitpick finds a counterexample, so willing doesn't imply obligation, so this test passes. 
+\color{blue}Nitpick found a counterexample for card i = 1 and card s = 2:
+
+  Free variables:
+    a = ($\lambda x. \_$)($s_1$ := ($\lambda x. \_$)($i_1$ := False), $s_2$ := ($\lambda x. \_$)($i_1$ := False))
+    c = ($\lambda x. \_$)($i_1$ := False)
+    g = ($\lambda x. \_$)($i_1$ := False)
+    s = $s_2$
+    w = $i_1$\color{black}
+Once again, I modify this test to use the dyadic obligation operator instead of the monadic operator.%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+The final set of tests deal with ought implies can and conflicting obligations. Recall that I 
+specifically added an axiom in my formalization to disallow contradictory obligations, so I expect 
+these tests to pass. Kroy's formalization fails these tests, so this is another area of improvement 
+over Kroy's formalization.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ ought{\isacharunderscore}implies{\isacharunderscore}can{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}O{\isacharbraceleft}W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharbar}c{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymdiamond}\ W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{using}\isamarkupfalse%
+\ O{\isacharunderscore}diamond\ \isacommand{by}\isamarkupfalse%
+\ blast\isanewline
+%
+\isamarkupcmt{This test is a lemma of DDL itself, so it's no surprise that this test passes.%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+\isanewline
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ conflicting{\isacharunderscore}obligations{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymnot}\ {\isacharparenleft}O{\isacharbraceleft}W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharbar}c{\isacharbraceright}\ \isactrlbold {\isasymand}\ O{\isacharbraceleft}\isactrlbold {\isasymnot}{\isacharparenleft}W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}{\isacharbar}\ c{\isacharbraceright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{using}\isamarkupfalse%
+\ no{\isacharunderscore}contradictions\ \isacommand{by}\isamarkupfalse%
+\ blast\isanewline
+%
+\isamarkupcmt{This test passes immediately by the new axiom prohibited contradictory obligations.%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+\isanewline
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ implied{\isacharunderscore}contradiction{\isacharcolon}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}{\isacharparenleft}W\ {\isacharparenleft}c{\isadigit{1}}{\isacharcomma}\ a{\isadigit{1}}{\isacharcomma}\ g{\isadigit{1}}{\isacharparenright}\ s{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}W\ {\isacharparenleft}c{\isadigit{2}}{\isacharcomma}\ a{\isadigit{2}}{\isacharcomma}\ g{\isadigit{2}}{\isacharparenright}\ s{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbottom}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}\isactrlbold {\isasymnot}\ {\isacharparenleft}O{\isacharbraceleft}W{\isacharparenleft}c{\isadigit{1}}{\isacharcomma}\ a{\isadigit{1}}{\isacharcomma}\ g{\isadigit{1}}{\isacharparenright}\ s{\isacharbar}c{\isacharbraceright}\ \isactrlbold {\isasymand}\ O{\isacharbraceleft}W{\isacharparenleft}c{\isadigit{2}}{\isacharcomma}\ a{\isadigit{2}}{\isacharcomma}\ g{\isadigit{2}}{\isacharparenright}\ s{\isacharbar}c{\isacharbraceright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{using}\isamarkupfalse%
+\ assms\ no{\isacharunderscore}contradictions\ \isacommand{by}\isamarkupfalse%
+\ blast\isanewline
+%
+\isamarkupcmt{Recall that the we also expect the stronger property that the combination of obligatory maxims can't
+ imply a contradiction. The added axiom also makes this test pass.%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+The metaethical test suite ran on both Kroy's formalization and my formalizaion show two clear 
+improvements. First, my formalization shows that obligatory maxims are permissible, whereas Kroy's 
+paradoxically does not. Second, my formalization doesn't allow contradictory maxims, but Kroy's does. 
+Both of these improvements are derived from the new axiom I added in my formalization that disallows 
+contradictory obligations. Additionally, my formalization also improves on Kroy's by staying faithful to the 
+strongest interpretation of the FUL, Korsgaard's practical contradiction interpretation. (maybe stick 
+philosophical writing here or above?)%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsection{Formalization Specific Tests%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
+In this section, I explore tests specific to my formalization of the categorical imperative. First, 
+in my previous (buggy) implementation of DDL, prohibiting contradictory obligation led to the strange 
+result that all permissible actions are obligatory. I will test if this bug appears in this implementation 
+as well.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ bug{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}permissible\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ w\ {\isasymlongrightarrow}\ O{\isacharbraceleft}W{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ {\isacharbar}\ c{\isacharbraceright}\ w{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{\color{blue}
+Nitpick found a counterexample for card i = 1 and card s = 1:
+
+  Free variables:
+    a = ($\lambda x. \_$)($s_1$ := ($\lambda x. \_$)($i_1$ := False))
+    c = ($\lambda x. \_$)($i_1$ := False)
+    g = ($\lambda x. \_$)($i_1$ := False)
+    s = $s_1$
+    w = undefined
+\color{black}
+This strange result does not hold; good!%
+}\isanewline
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
 %
@@
 %:%283=224%:%
-%:%285=227%:%
-%:%286=227%:%
+%:%284=225%:%
+%:%285=226%:%
 %:%287=228%:%
-%:%288=229%:%
-%:%289=230%:%
+%:%288=228%:%
+%:%289=229%:%
 %:%290=230%:%
+%:%291=231%:%
 %:%292=231%:%
 %:%293=232%:%
-%:%294=233%:%
-%:%295=234%:%
+%:%295=233%:%
 %:%296=234%:%
-%:%297=235%:%
-%:%298=236%:%
 %:%299=236%:%
-%:%301=236%:%
-%:%305=236%:%
-%:%306=236%:%
-%:%307=237%:%
-%:%308=237%:%
-%:%309=237%:%
-%:%318=239%:%
-%:%319=240%:%
-%:%320=241%:%
-%:%321=242%:%
-%:%322=243%:%
-%:%323=244%:%
-%:%324=245%:%
-%:%325=246%:%
-%:%326=247%:%
-%:%327=248%:%
-%:%328=249%:%
-%:%329=250%:%
-%:%330=251%:%
-%:%331=252%:%
-%:%332=253%:%
-%:%333=254%:%
-%:%335=256%:%
-%:%336=256%:%
-%:%337=257%:%
-%:%339=258%:%
-%:%340=259%:%
-%:%341=259%:%
-%:%342=260%:%
-%:%343=261%:%
-%:%344=261%:%
-%:%346=262%:%
-%:%347=263%:%
-%:%348=263%:%
-%:%349=264%:%
-%:%350=265%:%
-%:%351=265%:%
-%:%352=266%:%
-%:%353=266%:%
-%:%355=266%:%
-%:%359=266%:%
-%:%360=266%:%
-%:%362=267%:%
-%:%363=268%:%
-%:%364=269%:%
-%:%365=270%:%
-%:%366=271%:%
-%:%367=272%:%
-%:%368=273%:%
-%:%369=274%:%
-%:%370=275%:%
-%:%371=276%:%
-%:%372=277%:%
-%:%373=278%:%
-%:%381=278%:%
-%:%382=279%:%
-%:%383=280%:%
-%:%384=280%:%
-%:%385=281%:%
-%:%386=282%:%
-%:%387=282%:%
-%:%388=283%:%
-%:%389=283%:%
-%:%391=283%:%
-%:%395=283%:%
-%:%396=283%:%
-%:%398=284%:%
-%:%399=285%:%
-%:%400=286%:%
-%:%401=287%:%
-%:%402=288%:%
-%:%403=289%:%
-%:%413=291%:%
-%:%414=292%:%
-%:%415=293%:%
-%:%416=294%:%
-%:%417=295%:%
-%:%418=296%:%
-%:%419=297%:%
-%:%420=298%:%
-%:%421=299%:%
-%:%422=300%:%
-%:%423=301%:%
-%:%424=302%:%
-%:%425=303%:%
-%:%426=304%:%
-%:%427=305%:%
-%:%428=306%:%
-%:%429=307%:%
-%:%430=308%:%
-%:%431=309%:%
-%:%432=310%:%
-%:%436=312%:%
-%:%437=313%:%
-%:%438=314%:%
-%:%439=315%:%
-%:%440=316%:%
+%:%300=237%:%
+%:%301=238%:%
+%:%302=239%:%
+%:%303=240%:%
+%:%304=241%:%
+%:%305=242%:%
+%:%306=243%:%
+%:%307=244%:%
+%:%308=245%:%
+%:%309=246%:%
+%:%310=247%:%
+%:%311=248%:%
+%:%312=249%:%
+%:%313=250%:%
+%:%314=251%:%
+%:%315=252%:%
+%:%316=253%:%
+%:%317=254%:%
+%:%318=255%:%
+%:%319=256%:%
+%:%320=257%:%
+%:%321=258%:%
+%:%322=259%:%
+%:%323=260%:%
+%:%325=262%:%
+%:%326=262%:%
+%:%327=263%:%
+%:%329=264%:%
+%:%330=265%:%
+%:%331=265%:%
+%:%332=266%:%
+%:%333=267%:%
+%:%334=267%:%
+%:%336=268%:%
+%:%337=269%:%
+%:%338=270%:%
+%:%346=272%:%
+%:%358=274%:%
+%:%359=275%:%
+%:%360=276%:%
+%:%361=277%:%
+%:%362=278%:%
+%:%363=279%:%
+%:%365=282%:%
+%:%366=282%:%
+%:%368=283%:%
+%:%369=284%:%
+%:%370=285%:%
+%:%371=286%:%
+%:%372=286%:%
+%:%373=287%:%
+%:%374=288%:%
+%:%375=288%:%
+%:%377=288%:%
+%:%381=288%:%
+%:%382=288%:%
+%:%383=289%:%
+%:%384=289%:%
+%:%385=289%:%
+%:%394=291%:%
+%:%395=292%:%
+%:%396=293%:%
+%:%397=294%:%
+%:%398=295%:%
+%:%399=296%:%
+%:%400=297%:%
+%:%401=298%:%
+%:%402=299%:%
+%:%403=300%:%
+%:%404=301%:%
+%:%405=302%:%
+%:%406=303%:%
+%:%407=304%:%
+%:%408=305%:%
+%:%409=306%:%
+%:%410=307%:%
+%:%412=309%:%
+%:%413=309%:%
+%:%414=310%:%
+%:%416=311%:%
+%:%417=312%:%
+%:%418=312%:%
+%:%419=313%:%
+%:%420=314%:%
+%:%421=314%:%
+%:%423=315%:%
+%:%424=316%:%
+%:%425=316%:%
+%:%426=317%:%
+%:%427=318%:%
+%:%428=318%:%
+%:%429=319%:%
+%:%430=319%:%
+%:%432=319%:%
+%:%436=319%:%
+%:%437=319%:%
+%:%439=320%:%
+%:%440=321%:%
+%:%441=322%:%
+%:%442=323%:%
+%:%443=324%:%
+%:%444=325%:%
+%:%445=326%:%
+%:%446=327%:%
+%:%447=328%:%
+%:%448=329%:%
+%:%449=330%:%
+%:%457=330%:%
+%:%458=331%:%
+%:%459=332%:%
+%:%460=332%:%
+%:%461=333%:%
+%:%462=334%:%
+%:%463=334%:%
+%:%464=335%:%
+%:%465=335%:%
+%:%467=335%:%
+%:%471=335%:%
+%:%472=335%:%
+%:%474=336%:%
+%:%475=337%:%
+%:%476=338%:%
+%:%477=339%:%
+%:%478=340%:%
+%:%479=341%:%
+%:%489=343%:%
+%:%490=344%:%
+%:%491=345%:%
+%:%492=346%:%
+%:%493=347%:%
+%:%494=348%:%
+%:%495=349%:%
+%:%496=350%:%
+%:%497=351%:%
+%:%498=352%:%
+%:%499=353%:%
+%:%500=354%:%
+%:%501=355%:%
+%:%502=356%:%
+%:%503=357%:%
+%:%504=358%:%
+%:%505=359%:%
+%:%506=360%:%
+%:%507=361%:%
+%:%508=362%:%
+%:%512=364%:%
+%:%513=365%:%
+%:%514=366%:%
+%:%515=367%:%
+%:%516=368%:%
+%:%525=370%:%
+%:%537=372%:%
+%:%538=373%:%
+%:%539=374%:%
+%:%540=375%:%
+%:%549=378%:%
+%:%561=380%:%
+%:%562=381%:%
+%:%563=382%:%
+%:%564=383%:%
+%:%565=384%:%
+%:%566=385%:%
+%:%567=386%:%
+%:%568=387%:%
+%:%569=388%:%
+%:%570=389%:%
+%:%571=390%:%
+%:%572=391%:%
+%:%573=392%:%
+%:%574=393%:%
+%:%575=394%:%
+%:%576=395%:%
+%:%577=396%:%
+%:%578=397%:%
+%:%579=398%:%
+%:%580=399%:%
+%:%582=401%:%
+%:%583=401%:%
+%:%584=402%:%
+%:%587=403%:%
+%:%591=403%:%
+%:%592=403%:%
+%:%597=403%:%
+%:%600=404%:%
+%:%601=405%:%
+%:%602=405%:%
+%:%603=406%:%
+%:%606=407%:%
+%:%610=407%:%
+%:%611=407%:%
+%:%616=407%:%
+%:%619=408%:%
+%:%620=409%:%
+%:%621=409%:%
+%:%622=410%:%
+%:%625=411%:%
+%:%629=411%:%
+%:%630=411%:%
+%:%635=411%:%
+%:%638=412%:%
+%:%639=413%:%
+%:%640=413%:%
+%:%641=414%:%
+%:%644=415%:%
+%:%648=415%:%
+%:%649=415%:%
+%:%658=417%:%
+%:%659=418%:%
+%:%660=419%:%
+%:%661=420%:%
+%:%662=421%:%
+%:%663=422%:%
+%:%664=423%:%
+%:%666=425%:%
+%:%667=425%:%
+%:%668=426%:%
+%:%669=427%:%
+%:%670=427%:%
+%:%672=427%:%
+%:%676=427%:%
+%:%677=427%:%
+%:%679=428%:%
+%:%680=429%:%
+%:%681=430%:%
+%:%682=431%:%
+%:%683=432%:%
+%:%684=433%:%
+%:%685=434%:%
+%:%686=435%:%
+%:%687=436%:%
+%:%688=437%:%
+%:%689=438%:%
+%:%699=440%:%
+%:%700=441%:%
+%:%702=443%:%
+%:%703=443%:%
+%:%704=444%:%
+%:%707=445%:%
+%:%711=445%:%
+%:%712=445%:%
+%:%714=446%:%
+%:%724=448%:%
+%:%725=449%:%
+%:%727=451%:%
+%:%728=451%:%
+%:%729=452%:%
+%:%732=453%:%
+%:%736=453%:%
+%:%737=453%:%
+%:%738=453%:%
+%:%740=454%:%
+%:%741=455%:%
+%:%751=457%:%
+%:%752=458%:%
+%:%753=459%:%
+%:%754=460%:%
+%:%755=461%:%
+%:%756=462%:%
+%:%757=463%:%
+%:%758=464%:%
+%:%759=465%:%
+%:%760=466%:%
+%:%761=467%:%
+%:%762=468%:%
+%:%766=470%:%
+%:%767=471%:%
+%:%768=472%:%
+%:%770=474%:%
+%:%771=474%:%
+%:%772=475%:%
+%:%773=476%:%
+%:%774=477%:%
+%:%775=477%:%
+%:%777=477%:%
+%:%781=477%:%
+%:%782=477%:%
+%:%784=478%:%
+%:%785=479%:%
+%:%786=480%:%
+%:%787=481%:%
+%:%788=482%:%
+%:%789=483%:%
+%:%790=484%:%
+%:%791=485%:%
+%:%792=486%:%
+%:%793=487%:%
+%:%803=489%:%
+%:%804=490%:%
+%:%805=491%:%
+%:%807=493%:%
+%:%808=493%:%
+%:%809=494%:%
+%:%810=495%:%
+%:%811=495%:%
+%:%813=495%:%
+%:%817=495%:%
+%:%818=495%:%
+%:%820=496%:%
+%:%821=497%:%
+%:%822=498%:%
+%:%823=499%:%
+%:%824=500%:%
+%:%825=501%:%
+%:%826=502%:%
+%:%827=503%:%
+%:%828=504%:%
+%:%829=505%:%
+%:%839=507%:%
+%:%840=508%:%
+%:%841=509%:%
+%:%842=510%:%
+%:%844=512%:%
+%:%845=512%:%
+%:%846=513%:%
+%:%849=514%:%
+%:%853=514%:%
+%:%854=514%:%
+%:%855=514%:%
+%:%857=515%:%
+%:%863=515%:%
+%:%866=516%:%
+%:%867=517%:%
+%:%868=517%:%
+%:%869=518%:%
+%:%872=519%:%
+%:%876=519%:%
+%:%877=519%:%
+%:%878=519%:%
+%:%880=520%:%
+%:%886=520%:%
+%:%889=521%:%
+%:%890=522%:%
+%:%891=522%:%
+%:%892=523%:%
+%:%893=524%:%
+%:%896=525%:%
+%:%900=525%:%
+%:%901=525%:%
+%:%902=525%:%
+%:%904=526%:%
+%:%905=527%:%
+%:%915=529%:%
+%:%916=530%:%
+%:%917=531%:%
+%:%918=532%:%
+%:%919=533%:%
+%:%920=534%:%
+%:%921=535%:%
+%:%930=537%:%
+%:%942=539%:%
+%:%943=540%:%
+%:%944=541%:%
+%:%945=542%:%
+%:%947=544%:%
+%:%948=544%:%
+%:%949=545%:%
+%:%950=546%:%
+%:%951=546%:%
+%:%953=546%:%
+%:%957=546%:%
+%:%958=546%:%
+%:%960=547%:%
+%:%961=548%:%
+%:%962=549%:%
+%:%963=550%:%
+%:%964=551%:%
+%:%965=552%:%
+%:%966=553%:%
+%:%967=554%:%
+%:%968=555%:%
+%:%969=556%:%
+%:%970=557%:%
+%:%971=557%:%

### 2021-10-21 paper/output/document/upshot.tex
idk i did something

@@
 I argue that computational ethics should be useful for and interesting to philosophers for two 
-reasons. First, it serves as the basis for AI agents with the capacity for philosophically sophisticated 
+reasons. First, it could serve as the basis for AI agents with the capacity for philosophically sophisticated 
 ethical reasoning. For example, my project contributes an implementation of the Formula of Universal Law
 that an AI agent could use to reason about the world using the categorical imperative. Second, computational 
-ethics helps philosophers think about ethics in the same way that calculators or theorem provers help 
+ethics helps philosophers think about ethics in the same way that theorem provers help 
 mathematicians think about math. I am not arguing that the computer can replace human reasoning or prove things
-that humans theoretically couldn't do. Instead, I argue that the computer bolsters human reasoning, firstly by forcing precision due to 
-the rigid syntax of a computer program and secondly by making formal proofs less tedious. Below, I explore 
+that humans theoretically couldn't do. Instead, I argue that the computer bolsters human reasoning, by forcing precision due to 
+the rigid syntax of a computer program. Below, I explore 
 these contributions in greater detail.%
@@
 \begin{isamarkuptext}%
-As artifical intelligence becomes more powerful, the need for ethical AI becomes more urgent.
- Ethically intelligent artificial agents will need to 
-be able to reason about sophisticated ethical theories in order to navigate the world. My project could 
-serve as one component of a complete ethical reasoner. Specifically, my project could be repurposed 
-into a library that takes as input the logical representation of a maxim and determines if it is obligatory, prohibited, 
-or permissible.
+As artifical intelligence becomes more powerful, science-fiction predictions about ``evil AI"
+and current calls from regulators are intensifying the need for ``ethical AI". There are many 
+approaches to AI ethics and my project contributes an example of a ``top down" approach that starts with 
+an ethical theory (Kantian ethics) and automates it. My work on automating the categorical imperative 
+could serve as one component of a partially or fully artificial ethical reasoner. Specifically, my 
+project could be repurposed into a ``categorical imperative library" that takes as input the logical representation of a maxim 
+and determines its moral status (if it is obligatory, prohibited, or permissible).
 
@@
 serves as one component of an ``ethics engine," that an AI agent could use to make ethical decisions.
-For example, my system could be combined with an input parser to translate moral dilemmas as represented to the AI agent into maxims in my logic and an output 
+For example, my system could be combined with an input parser to translate moral dilemmas as represented 
+to the AI agent into maxims in my logic and an output 
 parser to translate the output of my system into a prescription for the action the AI agent should take.
@@
 \begin{isamarkuptext}%
-In this workflow, an AI agent is faced with a moral dilemma in some internal representation and 
-passes this representation to an input parser, which converts it to the appropriate logical representation 
-for my system to evaluate. For example, if an AI agent represents the moral dilemma in natural language, 
-the parser would convert the natural language representation to a representation in my logic.
+In this workflow, an AI agent is faced with a moral dilemma in some internal representation. This 
+internal representation would need to be translated by an input parser into an appropriate logical representation, i.e. 
+a circumstance, act, goal tuple. This input parser is the most technically and ethically challenging 
+component of the system. It is this input parser that determines which circumstances are ``morally relevant"
+for a maxim, a judgement that requires commonsense reasoning and knowledge about moral relevance. Much 
+of the work that a Kantian human being does when making decisions is to translate everyday situations 
+into appropriate maxims. Huge misunderstandings about Kantian ethics (maybe cite homophobia or right 
+to lie) in the literature often result from incorrectly formulated maxims, and the entire field of 
+applied Kantian ethics is devoted to generating the right kinds of maxims to test.
 
-Once the
-input is a sentence in my logic, my project can evaluate its moral status using my implementation of 
+This representational
+question will be one of the biggest hurdles to actually using my categorical imperative library 
+in an AI ethics engine. Currently, it may be reasonable for a human being to perform the role of the input
+parser. Once an AI agent stumbles onto an ethical dilemma, a human being could take over, formulate 
+the right question, and feed it into the categorical imperative library to see what action the categorical 
+imperative would prescribe. This may actually be a feature, not a bug, of an ethics engine for AI. 
+Proponents of the ``human-in-the-loop" model argue that fully automated decision-making is doomed 
+to ethical failure, and that the inclusion of a human being injects common-sense sanity into otherwise 
+dangerous decisions\footnote{maybe i should like...read a book}.
+
+It is likely that, regardless of the strengths of the human-in-the-loop model, fully automated AI 
+agents will exist. Setting aside the question of whether or not developing this kind of AI is responsible,
+such developments will require ethics engines, or risk no consideration of ethics at all. Even if a 
+world of fully automated AI is scary, such a world with automated ethics is better than a world without. 
+In such a world, the input parser in my ethics engine would have to be automated. This would require 
+that the parser translate the AI agent's internal representation to the appropriate logical representation.
+The input parser would need enough common sense reasoning to determine what circumstances are morally 
+relevant to a maxim. This is a question that, like all of ethics, philosophers debate robustly (cite the lit,
+there's tons of it). It is likely that, just as different implementations of automated ethics choose 
+a particular ethical theory and implement it, different implementations of such an input parser would 
+need to adopt different interpretations of commonsense reasoning and morally relevant circumstances.
+
+Once the input has been parsed, either by a human or a machine, into  a sentence in my logic, my 
+project can evaluate its moral status using my implementation of 
 the FUL. Concretely, my project would return a value indicating if the maxim is obligatory, permissible, 
@@
 upshot is that an automated version of the categorical imperative could function as the ethical engine 
-for an AI agent, with some work to parse the input and the output. Effectively, the kind 
+for an AI agent, with much work to parse the input and the output. Effectively, the kind 
 of automated ethics I implement could be 
-exposed as an ``ethics API" that AI developers could use to easily give AI agent the capacity for 
+an ``ethics library" that AI developers could use to give AI agents the capacity for 
 sophisticated ethical reasoning faithful to philosophical literature. This represents an improvement 
@@
 \begin{isamarkuptext}%
-Above I explain how my system offers a mechanism for humans to build ethical AI agents. I also 
+Above I explained how my system offers a mechanism for humans to build ethical AI agents. I also 
 argue that computational ethics is a mechanism for computers to help humans think differently about 
@@
 \begin{isamarkuptext}%
-As I tested prior formalizations of the categorical imperative and created my own, the process 
-of implementing and testing a formalization using an interactive theorem prover resulted in philosophical 
-insights that were novel to me. I reached surprising logical results that provoked 
-interesting philosophical conversations as I tried to understand their implications for the ethical 
+The process of implementing and testing a formalization using an interactive theorem prover 
+resulted in logical insights that led to a philosophical 
+insight that was novel to me and is potentially novel to the field. This philosophical insight has
+implications for what kinds of principles a practical reasoner should be concerned with. While this 
+insight could have been reached without the help of the computer, my system's logical results provoked
+an interesting philosophical conversation as I tried to understand their implications for the ethical 
 theory I am formalizing. This serves as an example for how computational ethics can prompt philosophical 
-insights. For example, as I was implementing my formalization of the FUL, I realized
+insights.
+
+As I was implementing my formalization of the FUL, I realized
 that my formalization was inconsistent unless I specified that the FUL only held for ``well-formed maxims,"
-such that neither the act nor goal were already achieved in the given circumstances. Below I document how 
-I came to this conclusion.
+such that neither the act nor goal were already achieved in the given circumstances. Precisely, 
+a circumstance, act, goal tuple (c, a, g) is well-formed if $(\neg (c \longrightarrow a) ) \wedge 
+(\neg(c \longrightarrow g))$. This provoked the philosophical insight that maxims of this form, in which 
+the act or the goal has already been accomplished in the given circumstances are ``vacuous" because 
+any prescriptions they generate have already been acted on or violated. Below I document how I came 
+to this conclusion and explain the notion of a vacuous maxim in greater detail.
+
+\emph{Logical Insight}
 
@@
 this proof, showing me that my formalization contradicted the axiom O\_diamond, which states that an 
-obligated term cannot contradict its context. I hypothesized that there was some tension between 
-the antecedent of the FUL, which states that a maxim is acted on by all agents, and the consequent, 
-which states that a maxim is prohibited. If the maxim has already been acted on, then not acting on it
-becomes impossible so the prohibition is impossible to obey.
+obligated term cannot contradict its context\footnote{The full form of the axiom is 
+$ O { A \vert B } \longrightarrow \diamond (B \wedge A)$}. 
+O\_diamond formalizes the principle ``ought implies can" and requires that if A is obligated in context 
+C, that A is possible in context C. I hypothesized that there was some tension between 
+the antecedent of the FUL, which states that all agents act on the maxim, and the consequent, 
+which states that the maxim is prohibited. If the maxim has already been acted on, then not acting on it
+is impossible so the prohibition is impossible to obey so the ought implies can principle is violated, 
+thus contradicting the axiom O\_diamond.
 
@@
 on the imaginatory component of the FUL. Specifically, the universalizability test requires that we imagine 
-a world where the maxim is universalized, not that the maxim is actually universalized at the actual world. 
-I implemented another version of the FUL under which, if a maxim is universalized at any world and rendered
-ineffective at that world, it is prohibited at the current world. I hypothesized that this would remove 
+a world where the maxim is universalized and study that world to determine whether or not the maxim 
+is obligatory in the actual world. For example, lying is not universalized in our current world, but to 
+determine if lying is prohibited, we imagine a different world in which everyone lied. To capture this difference,
+I implemented another version of the FUL under which  a maxim is prohibited at the current world $cw$ if, 
+when universalized at any world $w$ it is rendered ineffective at $w$. I hypothesized that this would remove 
 the contradiction found above. To test this new formalization, I used Nitpick, a model checker that 
-quickly generates models that satisfy some axioms and theorems. Usually, Nitpick can find a satisfying 
+quickly generates models that satisfy the given axioms and theorems. Usually, Nitpick can find a satisfying 
 model to show that a logic is consistent in a matter of seconds, but Nitpick consistently timed out 
@@
 
-Nitpick generates many models and checks if they satisfy the given maxims. I suspected that Nitpick 
-could potentially be timing out due to checking large models that exhausted its 
-time limit, especially due to the logical complexity of my theory. To avoid this, I decided to specify the exact number of maxims 
+Nitpick performs an optimized version of a brute force model search, in which it generates many models 
+and checks if they satisfy the given maxims. I suspected that Nitpick 
+was  timing out due to checking large models that exhausted its 
+time limit, especially due to the logical complexity of my theory\footnote{Benzmueller warned me that as 
+I added quantifiers to the theory, Isabelle's automated proof tools may start to time out.}. 
+To reduce the logical complexity, I decided to specify the exact number of maxims 
 in the system by passing as an argument to Nitpick the cardinality of my desired model. This did not 
-fix the problem. I next defined a particular (circumstance, act, goal) tuple as a constant and, instead of
+fix the problem.
+
+I next defined a particular (circumstance, act, goal) tuple as a constant and, instead of
 stating that the FUL held for all maxims, I stated that the FUL held for the specific maxim formed by this tuple.
-To my surprise, Nitpick was now able to show that the FUL was consistent.
+While before I added the axiom $\forall (c, a, g). FUL holds for maxim = (c, a, g)$, I now added constants $(c, a, g)$ 
+and added the axiom $FUL holds for maxim = (c, a, g)$. By specifying the circumstance, act, and goal 
+as constants, I removed the external universal quantifier, thus removing a layer of logical complexity.
 
-This appeared counterintuitive—after all, what is the difference between a model of cardinality 
-1 and a model with one constant object? Professor Amin pointed out that as constants, the circumstances, 
-act, and goal for which the FUL held were all distinct, but could be the same when quantified over. One line 
-of code later, I tested this hypothesis and found that requiring that the circumstances did 
-not entail the act or goal fixed the inconsistency. This logical inconsistency showed me that the FUL 
-could not hold for maxims in which the act or goal have already been achieved in the circumstances.
+To my surprise, Nitpick was now able to show that the FUL was consistent!
 
-To understand the philosophical plausibility of this property, I returned to Korsgaard and O'Neill's 
-interpretations of maxims as practical, action-guiding principles. A maxim in 
-which the circumstances already entail the act or goal is vacuous and therefore not a useful practical principle 
-to evaluate. For example, the maxim, ``When I am eating breakfast, eat breakfast in order to eat breakfast," 
-is not necessarily prohibited, but it is the wrong kind of question to be asking. The Formula of Universal 
-Law is supposed to guide practical reason, the force that we use to navigate the world and decide what 
-to do. Poorly formed maxims are of no use to practical reason and are the wrong kind of input to pass
-to the categorical imperative. This is a non-trivial philosophical insight that the computer helped me discover.%
+This result was counterintuitive—after all, what is the difference between a model of cardinality 
+1 and a model with one constant object? Why is quantifying over a tiny number of maxims so much 
+more time-cosuming than analyzing a single maxim? Professor Amin pointed out that when I defined the 
+circumstances, act, and goal as constants, then they were all distinct. When they were quantified over, 
+they could be identical.
+To formalize this idea, I defined a maxim as ``well-formed" if \isa{well{\isacharunderscore}formed\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ w{\isachardot}\ {\isasymnot}\ c\isactrlbold {\isasymrightarrow}g\ w\ {\isasymand}\ {\isasymnot}\ c\isactrlbold {\isasymrightarrow}a\ s\ w}.
+In propositional
+logic, a circumstance, act, goal tuple (c, a, g) is well-formed if $(\neg (c \longrightarrow a) ) \wedge 
+(\neg(c \longrightarrow g))$. I tested my hypothesis by modifying my axiom to instead read $\forall maxim
+(maxim is well-formed \longrightarrow FUL holds for maxim)$. This version of the FUL was indeed inconsistent!
+
+To summarize, I realized that my initial attempt at formalizing the FUL was inconsistent because 
+it required that the FUL hold for badly formed maxims, in which the circumstances entail the act or 
+goal. The logical insight was that if FUL holds for maxims in which $(c \longrightarrow a) \vee 
+(c \longrightarrow g)$, then the logic will be inconsistent.
+
+\emph{Philosophical Insight}
+
+Once I realized this logical property, I tried to understand its philosophical plausibility. I define
+a vacuous maxim as one in which the circumstances entail either the act or the goal. An example
+of a vacuous maxim is: ``When eating breakfast, eat breakfast in order to eat breakfast." This 
+maxim isn't clearly obligatory or prohibited, but there is something empty about it. For one 
+thing, acting on this maxim would never result in any actual action. If an agent adopts this maxim, 
+they decide that, in the circumstances ``eating breakfast" they will perform the act ``eating breakfast"
+for the purpose ``eating breakfast." In these circumstances, the act has 
+already been performed! Making this maxim a rule to live by doesn't change how you live your life. 
+When you are eating breakfast, you eat breakfast, but this statement is already 
+tautologically true regardless of whether you adopt the maxim or not.
+
+Not only does a badly formed maxim fail to prescribe action, any obligations or prohibitions it 
+generates have already been fulfilled or violated and are thus foregone conclusions. If a badly formed 
+maxim generates a prohibition, then this prohibition would be impossible to obey. 
+It is impossible to not eat breakfast while eating breakfast, because the circumstances assume that the 
+act has happened. On the other hand, if a badly formed maxim generates an obligation, then the obligation 
+will have already been fulfilled. If you are required to eat breakfast while eating breakfast, then you've 
+already fulfilled your obligation because the circumstances assume that the act has happened. Thus, 
+a badly formed maxim does not actually guide action because it doesn't generate new obligations or 
+prohibitions that could ever be acted on.
+
+The implication is that any obligations or prohibitions generated by a badly formed maxim are foregone 
+conclusions and thus do not tell us how to live, and thus must not be the domain of ethics, because 
+ethics is supposed to tell us how to live. Kant's categorical imperative
+ guides our use of practical reason, which is the kind of reason that tells us what we should do. 
+A practical reasoner asks moral questions not because they're mental puzzles or out of curiosity, but 
+because the reasoner wants to know how to act. Practical reason is action-guiding, but a badly formed
+ maxim can never be action-guiding because it prescribes no new
+actions or obligations. It is not the kind of maxim that a practical reasoner would consider. 
+There is no explicit prohibition against a badly formed maxim like the breakfast example above, but it 
+is the wrong kind of question for a practical reasoner to ask. Moreover, an ordinary person trying 
+to navigate the world would never ask that kind of question. If ethics and practical reason are meant 
+to guide action, then badly formed maxims are not questions for ethics, because they could never guide 
+action.
+
+Above I show that badly formed maxims are not questions for the ethics, but they also represent a 
+stronger problem. Asking if you should be acting while you act is undermining your will. 
+Under the Kantian acount of willing, when you will a maxim, you make it your end and commit yourself 
+to be its cause. You cannot simultaneously will a maxim and ask if you should be willing it. To say that 
+you are willing the maxim is to say that you have decided to will it—so the question, ``should I be 
+willing this?" is nonsensical. Either you haven't actually adopted the maxim, or you aren't
+actually asking the question. In a badly formed maxim, the circumstances already assume that the agent 
+has willed the maxim. If someone asks me``should I eat breakfast while eating breakfast?" I not only 
+wouldn't be able to answer the question, I wouldn't understand what they're asking. I would say, ``what 
+do you mean? You ARE eating breakfast." The agent must either not actually be eating breakfast or 
+they must not be asking a real question.
+
+That being said, we do often ask ``should I be doing this?" as we do something. What do we mean when 
+we ask this question? In what sense are we trying to evalute the moral status of a badly formed maxim?
+Can this kind of question ever be valid? To understand this worry, I consider the maxim, 
+``When dancing, I should just dance for the sake of dancing."\footnote{Maybe cite Korgsaard since the
+dancing thing is her example.} While this maxim appears to be badly formed (the 
+circumstance `dancing' implies the act and goal), it's a question that practical reasoners 
+do ask. I argue that there are multiple ways of understanding this maxim, and none are inconsistent with 
+my complaints about badly formed maxims.
+
+First is what I call the ``different action" interpretation, under which "I should just dance" is 
+actually referring to a different act than the circumstances. The circumstances ``When dancing" refer 
+to rythmically moving your body to music, but ``I should just dance" refers to dancing without anxiety, 
+completely focused on the joy of dancing itself. More precisely, this maxim should actually read ``When 
+dancing, I should abandon my anxiety and focus on dancing for the sake of dancing." This maxim when so 
+modified is not vacuous at all—abandoning anxiety and focusing on dancing is an entirely different act 
+from moving your body rythmically to music. This maxim is thus actually well-formed, and thus doesn't
+pose a problem for my argument. It is entirely plausible to tell yourself ``When I am dancing, I should focus 
+on dancing for the sake of dancing itself." The circumstances do not entail the act or the goal because 
+they refer to different meanings of the word dancing.
+
+Another version of the ``different action" interpretation is as follows. Consider the maxim modified to 
+be ``When dancing and seeing a child drowning, I should dance for the sake of dancing." Clearly this 
+maxim is fit for moral evaluation, and we expect a moral theory to prohibit this maxim. The circumstances 
+``When dancing and seeing a child drowning" appear to entail the act of dancing. In this case, the question 
+that the agent is actually asking themselves is ``should I continue dancing?" That is the actionable 
+maxim that they will adopt or reject. They mean to ask if they should stop dancing and go help the child. 
+Dancing at the current moment and dancing at the next moment are different acts, and the circumstances 
+imply the former but not the latter. A badly formed maxim would have circumstances and act both 
+``dancing at moment t," but this maxim has circumstances ``dancing at moment t" and act ``dancing 
+at moment t+1."
+
+Another interpretation of the dancing example is the ``self doubt" intepretation. The question ``When I am dancing, 
+should I really be dancing for the sake of dancing?" is the agent asking, ``Am I doing the right thing 
+right now?" The agent is not asking about the next moment, but is expressing doubt about the 
+moral validity of their behavior at this current moment. Under this interpretation, the agent 
+wants to know if they made the right decision. But what decision has the agent made? Did the agent
+adopt the maxim ``When dancing, dance for the sake of dancing?" They could not have, because such a 
+maxim could not have altered their behavior at all. This agent actually wants to know if the maxim that 
+resulted in them dancing, the maxim that got them to the current moment on the dance floor, was actually 
+the right thing to do. They are asking if, in the past, when they decided to dance, they made the 
+right decision. But such a maxim is not vacuous, because it resulted in the act of dancing. 
+The maxim that initiated the dancing would be something like ``When at a wedding, dance for the sake 
+of dancing." This is the maxim that they are currently acting on, not the badly formed example maxim.
+Evaluating the moral validity of this maxim is straightforward.
+
+This analysis also demonstrates the correct way to think about moral regret and self-doubt. When we 
+ask ``should I really be doing this?" we are asking if, when we chose to adopt our current maxim, 
+we made the right decision. The question is not, ``When acting should I act?" The question is, ``When 
+I was in the past, should I have chosen to act?" Regret is a counterfactual question about a valid, 
+well-formed maxim that was adopted in the past and led to the present moment. Unlike a badly formed 
+maxim, it doesn't undermine the will because it acknowledges the will's authority and the fact that the 
+will made a decision, but it asks if the will was mistaken.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupsubsubsection{Two Uses of Computational Ethics%
+\isamarkupsubsubsection{The Value of Computational Ethics%
 }
@@
 computational tools. Instead, I argue that computational tools prompt philosophers to ask questions that 
-lead to insights. The computer offers a different perspective by forcing philosophers to make their 
-work precise and allowing them to quickly complete proofs that would otherwise be tedious. Computational 
+lead to insights. Philosophers already value precision, and the computer forces precision and makes formal
+reasoning easier. Computational 
 ethics can serve as another tool in a philosopher's arsenal, like a thought experiment or counterexample.
+While the technology is not yet mature enough and easy enough to use to become widespread in philosophy
+departments, technical progress could turn computational ethics into an easy-to-use tool for philosophers
+that doesn't require any specialized knowledge.
 
-The first contribution of computational ethics is precision.
+The first contribution of computational ethics is precision. Much of analytic philosophy involves 
+making a particular concept precise. Thought experiments, arguments, counterexamples, and examples 
+illustrate features of a concept in the hope of making the concept itself more precise. Computational 
+ethics can help philosophers reach this goal of precision in another, potentially easier, way. 
 Representing a philosophical idea in logic and implementing it in an interactive theorem prover requires 
-making the idea precise to a degree that ordinary discussion does not require. The initial representation 
+making the idea precise to a degree that ordinary discussion can result in, but does not necessarily require. The initial representation 
 of an idea in a logic requires making its form precise. For example, 
@@
 
-The second virtue of computational ethics is that it makes formal ethics far less tedious, and therefore 
-within reach even for non-logicians. There is plenty of work attempting to develop logical representations 
-of philosophical phenomena in order to make these phenomena precise and use the tools of logic to prove 
-facts about them\footnote{Is there? Should cite stuff}. Much of this work, however, requires tedious pencil and paper proofs which may not 
-always produce relevant philosophical insights. Interactive theorem provers make such proofs accessible 
-even to philosophers who don't specialize in logic. Moreover, these proofs start from first principles 
-without requiring that a human being write pages and pages of syllogism as in Principia Mathematica. 
-Just as calculators make arithmetic fast and accessible to non-specialists, computational ethics does the same for 
-formal philosophy.%
+Another, related benefit of computational ethics is that it makes formal ethics far less tedious. 
+Certain subfields, such as philosophy of language, see such benefit in precision that they already heavily 
+use symbolic logic to represent philosophical concepts, just as mathematicians use symbolic logic to 
+represent mathematical concepts. Some of this work requres tedious pencil and paper proofs to prove 
+theorems, even when many of these theorems may not generate relevant philosophical insights. Ineractive 
+theorem provers make proofs more accessible. Isabelle can complete a proof, starting from first principles, 
+in a matter of seconds that would take a logician pages to complete. Just as calculators make arithmetic 
+more accessible, computational ethics does the same for formal philosophy. Not all philosophy can or will 
+be automated—after all, calculators didn't make accountants or mathematicians obsolete. Just as computers 
+reduce the tedium in other aspects of our life, they can reduce the tedium involved in formal logic for 
+both mathematicians and philosophers.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 helping humans reach non-trivial philosophical conclusions is reason to, at the very least, entertain 
-the possibility of a future where computational ethics becomes as normal as using a calculator for arithmetic.
+the possibility of a future where computational ethics becomes as normal for philosophers.
 
@@
 %:%76=31%:%
-%:%79=35%:%
-%:%80=36%:%
+%:%77=32%:%
+%:%78=33%:%
 %:%81=37%:%
@@
 %:%83=39%:%
-%:%86=41%:%
-%:%87=42%:%
+%:%84=40%:%
+%:%85=41%:%
 %:%88=43%:%
@@
 %:%113=68%:%
-%:%122=70%:%
-%:%134=72%:%
-%:%135=73%:%
-%:%136=74%:%
-%:%137=75%:%
-%:%138=76%:%
-%:%139=77%:%
-%:%148=79%:%
-%:%160=81%:%
-%:%161=82%:%
-%:%162=83%:%
-%:%163=84%:%
-%:%164=85%:%
-%:%165=86%:%
-%:%166=87%:%
-%:%167=88%:%
-%:%168=89%:%
-%:%169=90%:%
-%:%170=91%:%
-%:%171=92%:%
-%:%172=93%:%
-%:%173=94%:%
-%:%174=95%:%
-%:%175=96%:%
-%:%176=97%:%
-%:%177=98%:%
-%:%178=99%:%
-%:%179=100%:%
-%:%180=101%:%
-%:%181=102%:%
-%:%182=103%:%
-%:%183=104%:%
-%:%184=105%:%
-%:%185=106%:%
-%:%186=107%:%
-%:%187=108%:%
-%:%188=109%:%
+%:%114=69%:%
+%:%115=70%:%
+%:%116=71%:%
+%:%117=72%:%
+%:%118=73%:%
+%:%119=74%:%
+%:%120=75%:%
+%:%121=76%:%
+%:%122=77%:%
+%:%123=78%:%
+%:%124=79%:%
+%:%125=80%:%
+%:%126=81%:%
+%:%127=82%:%
+%:%128=83%:%
+%:%129=84%:%
+%:%130=85%:%
+%:%131=86%:%
+%:%132=87%:%
+%:%133=88%:%
+%:%134=89%:%
+%:%135=90%:%
+%:%136=91%:%
+%:%137=92%:%
+%:%138=93%:%
+%:%139=94%:%
+%:%140=95%:%
+%:%141=96%:%
+%:%142=97%:%
+%:%151=99%:%
+%:%163=101%:%
+%:%164=102%:%
+%:%165=103%:%
+%:%166=104%:%
+%:%167=105%:%
+%:%168=106%:%
+%:%177=108%:%
 %:%189=110%:%
@@
 %:%210=131%:%
-%:%219=133%:%
-%:%231=135%:%
-%:%232=136%:%
-%:%233=137%:%
-%:%234=138%:%
-%:%235=139%:%
-%:%236=140%:%
-%:%237=141%:%
-%:%238=142%:%
-%:%239=143%:%
-%:%240=144%:%
-%:%241=145%:%
-%:%242=146%:%
-%:%243=147%:%
-%:%244=148%:%
-%:%245=149%:%
-%:%246=150%:%
-%:%247=151%:%
-%:%248=152%:%
-%:%249=153%:%
-%:%250=154%:%
-%:%251=155%:%
-%:%252=156%:%
-%:%253=157%:%
-%:%254=158%:%
-%:%255=159%:%
-%:%256=160%:%
-%:%257=161%:%
-%:%258=162%:%
-%:%259=163%:%
-%:%260=164%:%
-%:%261=165%:%
-%:%262=166%:%
-%:%271=168%:%
-%:%283=171%:%
-%:%284=172%:%
-%:%285=173%:%
-%:%286=174%:%
-%:%287=175%:%
-%:%288=176%:%
-%:%289=177%:%
-%:%290=178%:%
-%:%291=179%:%
-%:%292=180%:%
-%:%293=181%:%
-%:%294=182%:%
-%:%295=183%:%
-%:%296=184%:%
-%:%297=185%:%
-%:%298=186%:%
-%:%299=187%:%
-%:%300=188%:%
-%:%301=189%:%
-%:%302=190%:%
-%:%303=191%:%
+%:%211=132%:%
+%:%212=133%:%
+%:%213=134%:%
+%:%214=135%:%
+%:%215=136%:%
+%:%216=137%:%
+%:%217=138%:%
+%:%218=139%:%
+%:%219=140%:%
+%:%220=141%:%
+%:%221=142%:%
+%:%222=143%:%
+%:%223=144%:%
+%:%224=145%:%
+%:%225=146%:%
+%:%226=147%:%
+%:%227=148%:%
+%:%228=149%:%
+%:%229=150%:%
+%:%230=151%:%
+%:%231=152%:%
+%:%232=153%:%
+%:%233=154%:%
+%:%234=155%:%
+%:%235=156%:%
+%:%236=157%:%
+%:%237=158%:%
+%:%238=159%:%
+%:%239=160%:%
+%:%240=161%:%
+%:%241=162%:%
+%:%242=163%:%
+%:%243=164%:%
+%:%244=165%:%
+%:%245=166%:%
+%:%246=167%:%
+%:%247=168%:%
+%:%248=169%:%
+%:%249=170%:%
+%:%250=171%:%
+%:%251=172%:%
+%:%252=173%:%
+%:%253=174%:%
+%:%254=175%:%
+%:%255=176%:%
+%:%256=177%:%
+%:%257=178%:%
+%:%258=179%:%
+%:%259=180%:%
+%:%260=181%:%
+%:%261=182%:%
+%:%262=183%:%
+%:%263=184%:%
+%:%264=185%:%
+%:%265=186%:%
+%:%266=187%:%
+%:%267=188%:%
+%:%268=189%:%
+%:%269=190%:%
+%:%270=191%:%
+%:%271=192%:%
+%:%272=193%:%
+%:%273=194%:%
+%:%274=195%:%
+%:%275=196%:%
+%:%276=197%:%
+%:%277=198%:%
+%:%278=199%:%
+%:%279=200%:%
+%:%280=201%:%
+%:%281=202%:%
+%:%282=203%:%
+%:%283=204%:%
+%:%284=205%:%
+%:%285=206%:%
+%:%286=207%:%
+%:%287=208%:%
+%:%288=209%:%
+%:%289=210%:%
+%:%290=211%:%
+%:%291=212%:%
+%:%292=213%:%
+%:%293=214%:%
+%:%294=215%:%
+%:%295=216%:%
+%:%296=217%:%
+%:%297=218%:%
+%:%298=219%:%
+%:%299=220%:%
+%:%300=221%:%
+%:%301=222%:%
+%:%302=223%:%
+%:%303=224%:%
+%:%304=225%:%
+%:%305=226%:%
+%:%306=227%:%
+%:%307=228%:%
+%:%308=229%:%
+%:%309=230%:%
+%:%310=231%:%
+%:%311=232%:%
+%:%312=233%:%
+%:%313=234%:%
+%:%314=235%:%
+%:%315=236%:%
+%:%316=237%:%
+%:%317=238%:%
+%:%318=239%:%
+%:%319=240%:%
+%:%320=241%:%
+%:%321=242%:%
+%:%322=243%:%
+%:%323=244%:%
+%:%324=245%:%
+%:%325=246%:%
+%:%326=247%:%
+%:%327=248%:%
+%:%328=249%:%
+%:%329=250%:%
+%:%330=251%:%
+%:%331=252%:%
+%:%332=253%:%
+%:%333=254%:%
+%:%334=255%:%
+%:%335=256%:%
+%:%336=257%:%
+%:%337=258%:%
+%:%338=259%:%
+%:%339=260%:%
+%:%340=261%:%
+%:%341=262%:%
+%:%342=263%:%
+%:%343=264%:%
+%:%344=265%:%
+%:%345=266%:%
+%:%346=267%:%
+%:%347=268%:%
+%:%348=269%:%
+%:%349=270%:%
+%:%350=271%:%
+%:%351=272%:%
+%:%352=273%:%
+%:%353=274%:%
+%:%354=275%:%
+%:%355=276%:%
+%:%356=277%:%
+%:%357=278%:%
+%:%358=279%:%
+%:%359=280%:%
+%:%360=281%:%
+%:%361=282%:%
+%:%362=283%:%
+%:%363=284%:%
+%:%364=285%:%
+%:%373=288%:%
+%:%385=290%:%
+%:%386=291%:%
+%:%387=292%:%
+%:%388=293%:%
+%:%389=294%:%
+%:%390=295%:%
+%:%391=296%:%
+%:%392=297%:%
+%:%393=298%:%
+%:%394=299%:%
+%:%395=300%:%
+%:%396=301%:%
+%:%397=302%:%
+%:%398=303%:%
+%:%399=304%:%
+%:%400=305%:%
+%:%401=306%:%
+%:%402=307%:%
+%:%403=308%:%
+%:%404=309%:%
+%:%405=310%:%
+%:%406=311%:%
+%:%407=312%:%
+%:%408=313%:%
+%:%409=314%:%
+%:%410=315%:%
+%:%411=316%:%
+%:%412=317%:%
+%:%413=318%:%
+%:%414=319%:%
+%:%415=320%:%
+%:%416=321%:%
+%:%417=322%:%
+%:%418=323%:%
+%:%419=324%:%
+%:%420=325%:%
+%:%421=326%:%
+%:%422=327%:%
+%:%423=328%:%
+%:%424=329%:%
+%:%433=332%:%
+%:%445=335%:%
+%:%446=336%:%
+%:%447=337%:%
+%:%448=338%:%
+%:%449=339%:%
+%:%450=340%:%
+%:%451=341%:%
+%:%452=342%:%
+%:%453=343%:%
+%:%454=344%:%
+%:%455=345%:%
+%:%456=346%:%
+%:%457=347%:%
+%:%458=348%:%
+%:%459=349%:%
+%:%460=350%:%
+%:%461=351%:%
+%:%462=352%:%
+%:%463=353%:%
+%:%464=354%:%
+%:%465=355%:%

### 2021-10-22 paper/output/document/upshot.tex
my hands hurts

@@
 mathematicians think about math. I am not arguing that the computer can replace human reasoning or prove things
-that humans theoretically couldn't do. Instead, I argue that the computer bolsters human reasoning, by forcing precision due to 
+that humans theoretically couldn't do. Instead, I argue that the computer bolsters human reasoning by forcing precision due to 
 the rigid syntax of a computer program. Below, I explore 
@@
 As artifical intelligence becomes more powerful, science-fiction predictions about ``evil AI"
-and current calls from regulators are intensifying the need for ``ethical AI". There are many 
-approaches to AI ethics and my project contributes an example of a ``top down" approach that starts with 
-an ethical theory (Kantian ethics) and automates it. My work on automating the categorical imperative 
+and calls from regulators are intensifying the need for ``ethical AI". My project contributes a ``top down" 
+approach automating a particular ethical theory. My work on automating the categorical imperative 
 could serve as one component of a partially or fully artificial ethical reasoner. Specifically, my 
@@
 As it stands, my project can evaluate the moral status of maxims represented in my logic and potentially 
-serves as one component of an ``ethics engine," that an AI agent could use to make ethical decisions.
+serves as one component of an ``ethics engine" that an AI agent could use to make ethical decisions.
 For example, my system could be combined with an input parser to translate moral dilemmas as represented 
-to the AI agent into maxims in my logic and an output 
-parser to translate the output of my system into a prescription for the action the AI agent should take.
-\ref{fig:AIengine} depicts the workflow of this example of an ethics engine.%
+to the AI agent into maxims in my logic. The ouput of my system could be fed into an output 
+parser to translate this output into a prescription for the action the AI agent should take.
+Figure \ref{fig:AIengine} depicts the workflow of this example ethics engine.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \includegraphics[scale=0.4]{AI_engine.png}
-\caption{An example of an ethics engine for an artificial agent} \label{fig:AIengine}
+\caption{An example of an ethics engine for an artificial agent. I contribute the automated 
+categorical imperative component.} \label{fig:AIengine}
 \end{figure}
@@
 component of the system. It is this input parser that determines which circumstances are ``morally relevant"
-for a maxim, a judgement that requires commonsense reasoning and knowledge about moral relevance. Much 
-of the work that a Kantian human being does when making decisions is to translate everyday situations 
-into appropriate maxims. Huge misunderstandings about Kantian ethics (maybe cite homophobia or right 
-to lie) in the literature often result from incorrectly formulated maxims, and the entire field of 
-applied Kantian ethics is devoted to generating the right kinds of maxims to test.
+for a maxim, a judgement that requires commonsense reasoning and knowledge about moral relevance. Translating 
+ everyday situations into appropriate maxims is the bulk of the work that a Kantian human being does when making decisions. 
+Common misconceptions about Kantian ethics\footnote{For example, some wonder why the FUL doesn't prohibit
+gay sex, as the maxim ``marry someone of the same sex" appears to result in human extinction when 
+universalized. The solution to this dilemma is that the maxim a gay person acts on is usually something 
+of the form, ``marry the person you love because you love them," which is perfectly reasonable to 
+universalize.} often result from incorrectly formulated maxims, and the entire field of 
+applied Kantian ethics is devoted to generating the right kinds of maxims to test. For more discussion 
+of challenges involved with defining morally relevant circumstances, see Section UNWRITTEN.
 
@@
 the right question, and feed it into the categorical imperative library to see what action the categorical 
-imperative would prescribe. This may actually be a feature, not a bug, of an ethics engine for AI. 
+imperative would prescribe. This may actually be a feature, not a bug. 
 Proponents of the ``human-in-the-loop" model argue that fully automated decision-making is doomed 
 to ethical failure, and that the inclusion of a human being injects common-sense sanity into otherwise 
-dangerous decisions\footnote{maybe i should like...read a book}.
+dangerous decisions\footnote{For more discussion of different models of AI ethics, see Section UNWRITTEN}.
 
 It is likely that, regardless of the strengths of the human-in-the-loop model, fully automated AI 
-agents will exist. Setting aside the question of whether or not developing this kind of AI is responsible,
-such developments will require ethics engines, or risk no consideration of ethics at all. Even if a 
-world of fully automated AI is scary, such a world with automated ethics is better than a world without. 
+agents will exist. Even if developing this kind of AI is irresponsible,
+such developments are likely and will require ethics engines, or risk no consideration of ethics at all. Even if 
+fully automated AI is scary, such AI with automated ethics is better than such AI without. 
 In such a world, the input parser in my ethics engine would have to be automated. This would require 
@@
 The input parser would need enough common sense reasoning to determine what circumstances are morally 
-relevant to a maxim. This is a question that, like all of ethics, philosophers debate robustly (cite the lit,
-there's tons of it). It is likely that, just as different implementations of automated ethics choose 
+relevant to a maxim. This is a question that, like all of ethics, philosophers debate robustly
+\footnote{Powers \cite{powers} identifies this as a challenge for automating Kantian ethics and briefly sketches 
+solutions from O'Neill \cite{constofreason}, Silber \cite{silber}, and Rawls \cite{rawlsconstructivism}. }. 
+It is likely that, just as different implementations of automated ethics choose 
 a particular ethical theory and implement it, different implementations of such an input parser would 
 need to adopt different interpretations of commonsense reasoning and morally relevant circumstances.
+Automating this level of commonsense reasoning would represent signifiant technical progress in 
+computational ethics.
 
@@
 The ethics engine depicted above is a high-level example of one way to use my project to guide an artifical agent. The 
-upshot is that an automated version of the categorical imperative could function as the ethical engine 
+upshot is that an automated version of the categorical imperative could become part of the ethical engine 
 for an AI agent, with much work to parse the input and the output. Effectively, the kind 
-of automated ethics I implement could be 
-an ``ethics library" that AI developers could use to give AI agents the capacity for 
+of automated ethics I implement could be a library that AI developers use to give AI agents the capacity for 
 sophisticated ethical reasoning faithful to philosophical literature. This represents an improvement 
 over existing ethics engines, which rarely attempt to capture the complexity 
-of any ethical theory that philosophers plausibly defend. For more on how my project is situated 
-among other work in automated ethics, see Section ??%
+of any ethical theory that philosophers plausibly defend. Moreover, a logic programming approach 
+is potentially more explainable than a black-box deep learning approach, as theorem provers like 
+Isabelle can explicitly list the axioms used to generate moral prescriptions. For more on how my project 
+is situated among other work in automated ethics, see Section Related Work.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 philosophy. Just as theorem provers make mathematics more efficient and push mathematicians to think 
-precisely about the phenomena they are modelling, computational ethics can help philosophers think about 
-philosophy. Below I share an example of the kind of philosophical insight that computational ethics 
+precisely about the phenomena they are modelling, computational ethics can help philosophers think more precisely about 
+philosophy. Below I share a personal example of the kind of philosophical insight that computational ethics 
 can prompt and analyze the value that this tool offers to philosophers.%
@@
 \begin{isamarkuptext}%
-The process of implementing and testing a formalization using an interactive theorem prover 
-resulted in logical insights that led to a philosophical 
-insight that was novel to me and is potentially novel to the field. This philosophical insight has
-implications for what kinds of principles a practical reasoner should be concerned with. While this 
+As I implemented a formalization of the categorical imperative using an interactive theorem prover, 
+I discovered logical insights. These logical insights led to a philosophical 
+insight that was novel to me and is potentially novel to the field.  While this 
 insight could have been reached without the help of the computer, my system's logical results provoked
-an interesting philosophical conversation as I tried to understand their implications for the ethical 
-theory I am formalizing. This serves as an example for how computational ethics can prompt philosophical 
-insights.
+an interesting philosophical conversation. Effectively, the system spat out a logical principle, and 
+I examined the philosophical plausibility of this principle for the ethical 
+theory I am formalizing. In this section, I will first present the logical insight, then the 
+philosophical insights, and then its implications for a debate about self-doubt. I will then
+generalize my personal experience and argue that computational ethics is a new, useful methodology 
+for philosophers.
 
-As I was implementing my formalization of the FUL, I realized
+I arrived at the logical insight while testing my formalization of the FUL. I realized
 that my formalization was inconsistent unless I specified that the FUL only held for ``well-formed maxims,"
@@
 the act or the goal has already been accomplished in the given circumstances are ``vacuous" because 
-any prescriptions they generate have already been acted on or violated. Below I document how I came 
-to this conclusion and explain the notion of a vacuous maxim in greater detail.
+any prescriptions they generate have already been acted on or violated. The notion of a vacuous maxim
+has implications for debates about ethical self-doubt and self-confidence or self-respect.
 
@@
 obligated term cannot contradict its context\footnote{The full form of the axiom is 
-$ O { A \vert B } \longrightarrow \diamond (B \wedge A)$}. 
+$ O \{ A \vert B \} \longrightarrow \diamond (B \wedge A)$}. 
 O\_diamond formalizes the principle ``ought implies can" and requires that if A is obligated in context 
@@
 which states that the maxim is prohibited. If the maxim has already been acted on, then not acting on it
-is impossible so the prohibition is impossible to obey so the ought implies can principle is violated, 
-thus contradicting the axiom O\_diamond.
+is impossible. Thus, the generated prohibition is impossible to obey, so the ought implies can principle
+and axiom O\_diamond are violated.
 
-To solve this problem, I returned to Korsgaard's practical contradiction interpretation and focused 
-on the imaginatory component of the FUL. Specifically, the universalizability test requires that we imagine 
-a world where the maxim is universalized and study that world to determine whether or not the maxim 
-is obligatory in the actual world. For example, lying is not universalized in our current world, but to 
-determine if lying is prohibited, we imagine a different world in which everyone lied. To capture this difference,
-I implemented another version of the FUL under which  a maxim is prohibited at the current world $cw$ if, 
-when universalized at any world $w$ it is rendered ineffective at $w$. I hypothesized that this would remove 
-the contradiction found above. To test this new formalization, I used Nitpick, a model checker that 
-quickly generates models that satisfy the given axioms and theorems. Usually, Nitpick can find a satisfying 
-model to show that a logic is consistent in a matter of seconds, but Nitpick consistently timed out 
-when looking for a model of my modified FUL.
+I then experimented with modifications of the FUL, which I eventually abandoned. I tried universalizing the maxim 
+at a world other than the current world and defining non-contradictory maxims, in which the maxim's 
+circumstances do not contradict the maxim's act. I noticed that, no matter what modifications I made, 
+Nitpick was timing out when looking for a model and Sledgehammer wasn't able to find a proof of
+inconsistency. Isabelle's proof tools weren't able to tell me if my modifications were 
+consistent or not. I suspected that something about my implementation was too slow, perhaps due to 
+my liberal use of quantifiers\footnote{Benzmueller warned me that as 
+I added quantifiers to the theory, Isabelle's automated proof tools may start to time out.}.
 
-Nitpick performs an optimized version of a brute force model search, in which it generates many models 
+Isabelle's model checker Nitpick performs an optimized version of a brute force model search, in which it generates many models
 and checks if they satisfy the given maxims. I suspected that Nitpick 
-was  timing out due to checking large models that exhausted its 
-time limit, especially due to the logical complexity of my theory\footnote{Benzmueller warned me that as 
-I added quantifiers to the theory, Isabelle's automated proof tools may start to time out.}. 
+was checking large models that exhausted its 
+time limit, especially due to the logical complexity of my theory. 
 To reduce the logical complexity, I decided to specify the exact number of maxims 
-in the system by passing as an argument to Nitpick the cardinality of my desired model. This did not 
-fix the problem.
+in the system by passing as an argument to Nitpick the cardinality of my desired model. Nitpick no longer
+timed out, but it could not find a satisfying model with cardinality 1, and thus could not demonstrate
+that my modified FUL was consisteny.
+ This puzzled me, as I felt that I could construct a pencil-and-paper 
+model with a single world and term in which my modified formalizations were consistent.
 
-I next defined a particular (circumstance, act, goal) tuple as a constant and, instead of
+Instead of specifying the cardinality of the model, I decided to tell Nitpick exactly how many 
+maxims there were in my system by defining them as constants. I defined a particular 
+(circumstance, act, goal) tuple as a constant. Instead of
 stating that the FUL held for all maxims, I stated that the FUL held for the specific maxim formed by this tuple.
-While before I added the axiom $\forall (c, a, g). FUL holds for maxim = (c, a, g)$, I now added constants $(c, a, g)$ 
-and added the axiom $FUL holds for maxim = (c, a, g)$. By specifying the circumstance, act, and goal 
+While before I added the axiom $\forall (c, a, g) \text{\emph{FUL holds for maxim}} (c, a, g)$, I now added constants $(c, a, g)$ 
+and added the axiom $\text{\emph{FUL holds for maxim}} (c, a, g)$. By specifying the circumstance, act, and goal 
 as constants, I removed the external universal quantifier, thus removing a layer of logical complexity.
 
-To my surprise, Nitpick was now able to show that the FUL was consistent!
+To my surprise, Nitpick not only returned quickly, it was able to show that the FUL was consistent!
 
 This result was counterintuitive—after all, what is the difference between a model of cardinality 
-1 and a model with one constant object? Why is quantifying over a tiny number of maxims so much 
-more time-cosuming than analyzing a single maxim? Professor Amin pointed out that when I defined the 
-circumstances, act, and goal as constants, then they were all distinct. When they were quantified over, 
+1 and a model with one constant object? Why is quantifying over a tiny number of maxims different
+ than analyzing a single maxim? Professor Amin pointed out that, as constants, the 
+circumstances, act, and goal were all distinct. When they were quantified over, 
 they could be identical.
-To formalize this idea, I defined a maxim as ``well-formed" if \isa{well{\isacharunderscore}formed\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ w{\isachardot}\ {\isasymnot}\ c\isactrlbold {\isasymrightarrow}g\ w\ {\isasymand}\ {\isasymnot}\ c\isactrlbold {\isasymrightarrow}a\ s\ w}.
+To formalize this idea, I defined a maxim as \isa{well{\isacharunderscore}formed\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ w{\isachardot}\ {\isasymnot}\ c\isactrlbold {\isasymrightarrow}g\ w\ {\isasymand}\ {\isasymnot}\ c\isactrlbold {\isasymrightarrow}a\ s\ w}.
 In propositional
 logic, a circumstance, act, goal tuple (c, a, g) is well-formed if $(\neg (c \longrightarrow a) ) \wedge 
-(\neg(c \longrightarrow g))$. I tested my hypothesis by modifying my axiom to instead read $\forall maxim
-(maxim is well-formed \longrightarrow FUL holds for maxim)$. This version of the FUL was indeed inconsistent!
+(\neg(c \longrightarrow g))$. I tested my hypothesis by modifying my axiom to instead read $\forall$\emph{maxim
+(maxim is well-formed} $\longrightarrow$ \emph{FUL holds for maxim}). This version of the FUL was indeed consistent!
 
@@
 
-Once I realized this logical property, I tried to understand its philosophical plausibility. I define
-a vacuous maxim as one in which the circumstances entail either the act or the goal. An example
+Once I realized this logical property, I tried to understand its philosophical plausibility. I 
+wanted to philosophically test the hypothesis that maxims in which  $(c \longrightarrow a) \vee 
+(c \longrightarrow g)$ are not valid inputs to the FUL. I concluded that because vacuous maxims neither 
+change an agent's behavior nor generate meaningful obligations, they are not the right kinds of questions 
+for practical reasoners to be asking. They cannot be action-guiding and are thus not the domain of ethics.
+
+I define a vacuous maxim as one in which the circumstances entail either the act or the goal. An example
 of a vacuous maxim is: ``When eating breakfast, eat breakfast in order to eat breakfast." This 
@@
 for the purpose ``eating breakfast." In these circumstances, the act has 
-already been performed! Making this maxim a rule to live by doesn't change how you live your life. 
-When you are eating breakfast, you eat breakfast, but this statement is already 
-tautologically true regardless of whether you adopt the maxim or not.
+already been performed! Making this maxim a rule to live by doesn't change how you live your life. If 
+you adopt this maxim, when you are eating breakfast, you eat breakfast, but this statement is already 
+tautologically true.
 
-Not only does a badly formed maxim fail to prescribe action, any obligations or prohibitions it 
-generates have already been fulfilled or violated and are thus foregone conclusions. If a badly formed 
+Not only does a vacuous maxim fail to prescribe action, any obligations or prohibitions it 
+generates have already been fulfilled or violated and are thus foregone conclusions. If a vacuous 
 maxim generates a prohibition, then this prohibition would be impossible to obey. 
 It is impossible to not eat breakfast while eating breakfast, because the circumstances assume that the 
-act has happened. On the other hand, if a badly formed maxim generates an obligation, then the obligation 
+act has happened. On the other hand, if a vacuous maxim generates an obligation, then the obligation 
 will have already been fulfilled. If you are required to eat breakfast while eating breakfast, then you've 
 already fulfilled your obligation because the circumstances assume that the act has happened. Thus, 
-a badly formed maxim does not actually guide action because it doesn't generate new obligations or 
+a vacuous maxim does not actually guide action because it doesn't generate new obligations or 
 prohibitions that could ever be acted on.
 
-The implication is that any obligations or prohibitions generated by a badly formed maxim are foregone 
-conclusions and thus do not tell us how to live, and thus must not be the domain of ethics, because 
-ethics is supposed to tell us how to live. Kant's categorical imperative
+If any obligations or prohibitions generated by vacuous maxims do not tell us how to live, such 
+maxims must not be the domain of ethics because ethics is 
+supposed to tell us how to live. Kant's categorical imperative
  guides our use of practical reason, which is the kind of reason that tells us what we should do. 
-A practical reasoner asks moral questions not because they're mental puzzles or out of curiosity, but 
-because the reasoner wants to know how to act. Practical reason is action-guiding, but a badly formed
+A practical reasoner asks moral questions not as a mental puzzle or out of curiosity, but 
+because the reasoner wants to know how to act. Practical reason is action-guiding, but a vacuous
  maxim can never be action-guiding because it prescribes no new
 actions or obligations. It is not the kind of maxim that a practical reasoner would consider. 
-There is no explicit prohibition against a badly formed maxim like the breakfast example above, but it 
+There is no explicit prohibition against a vacuous maxim like the breakfast example above, but it 
 is the wrong kind of question for a practical reasoner to ask. Moreover, an ordinary person trying 
@@
 
-Above I show that badly formed maxims are not questions for the ethics, but they also represent a 
-stronger problem. Asking if you should be acting while you act is undermining your will. 
+Not only are vacuous maxims not questions for ethics, but they also represent a 
+stronger problem. Asking if you should act while you act undermines your will and thus contradicts
+the very idea of willing a maxim. 
 Under the Kantian acount of willing, when you will a maxim, you make it your end and commit yourself 
-to be its cause. You cannot simultaneously will a maxim and ask if you should be willing it. To say that 
-you are willing the maxim is to say that you have decided to will it—so the question, ``should I be 
-willing this?" is nonsensical. Either you haven't actually adopted the maxim, or you aren't
-actually asking the question. In a badly formed maxim, the circumstances already assume that the agent 
-has willed the maxim. If someone asks me``should I eat breakfast while eating breakfast?" I not only 
-wouldn't be able to answer the question, I wouldn't understand what they're asking. I would say, ``what 
-do you mean? You ARE eating breakfast." The agent must either not actually be eating breakfast or 
-they must not be asking a real question.
+to be its cause. You cannot simultaneously commit yourself to a maxim and ask if you should be committing to it. To 
+will the maxim is to decide to will it—so the question, ``should I be 
+willing this?" is nonsensical. Either you haven't actually adopted the maxim (and thus haven't yet 
+committed yourself to it), or you aren't
+actually asking the question (because the decision has already been made). In a vacuous maxim, 
+the circumstances already assume that the agent 
+has willed the maxim. If someone asks ``should I eat breakfast while eating breakfast?" we not only 
+wouldn't be able to answer the question, we wouldn't understand it. Our response would be, ``what 
+do you mean? You are already eating breakfast." The agent must either not actually be eating breakfast or 
+they must not be asking a real question. This argument is not specific to the Kantian account of willing. 
+Under any account of practical action, questioning a commitment as you make the commitment it impossible. 
+Either you haven't actually committed or you're not actually asking the question.
 
-That being said, we do often ask ``should I be doing this?" as we do something. What do we mean when 
-we ask this question? In what sense are we trying to evalute the moral status of a badly formed maxim?
+A skeptic may argue that we do often ask ``should I be doing this?" as we do something. What do we mean when 
+we ask this question? In what sense are we trying to evalute the moral status of a vacuous maxim?
 Can this kind of question ever be valid? To understand this worry, I consider the maxim, 
 ``When dancing, I should just dance for the sake of dancing."\footnote{Maybe cite Korgsaard since the
-dancing thing is her example.} While this maxim appears to be badly formed (the 
-circumstance `dancing' implies the act and goal), it's a question that practical reasoners 
-do ask. I argue that there are multiple ways of understanding this maxim, and none are inconsistent with 
-my complaints about badly formed maxims.
+dancing thing is her example.} While this maxim appears to be vacuous (the 
+circumstance `dancing' implies the act and goal of dancing), it's a question that practical reasoners 
+do ask. I argue that there are this maxim is actually misunderstood and, when interpreted correctly,
+it no longer poses as a counterexample to my complaints about vacuous maxims.
 
-First is what I call the ``different action" interpretation, under which "I should just dance" is 
-actually referring to a different act than the circumstances. The circumstances ``When dancing" refer 
+"I should just dance" is actually referring to a different act than the circumstance ``when dancing". 
+The circumstance ``when dancing" refers 
 to rythmically moving your body to music, but ``I should just dance" refers to dancing without anxiety, 
-completely focused on the joy of dancing itself. More precisely, this maxim should actually read ``When 
+completely focused on the joy of dancing itself. More precisely, this maxim should read ``When 
 dancing, I should abandon my anxiety and focus on dancing for the sake of dancing." This maxim when so 
 modified is not vacuous at all—abandoning anxiety and focusing on dancing is an entirely different act 
-from moving your body rythmically to music. This maxim is thus actually well-formed, and thus doesn't
+from moving your body rythmically to music. This maxim is actually well-formed, and thus doesn't
 pose a problem for my argument. It is entirely plausible to tell yourself ``When I am dancing, I should focus 
@@
 
-Another version of the ``different action" interpretation is as follows. Consider the maxim modified to 
-be ``When dancing and seeing a child drowning, I should dance for the sake of dancing." Clearly this 
+Another interpretation of this example is as follows. Consider the maxim modified to 
+read ``When dancing and seeing a child drowning, I should dance for the sake of dancing." Clearly this 
 maxim is fit for moral evaluation, and we expect a moral theory to prohibit this maxim. The circumstances 
-``When dancing and seeing a child drowning" appear to entail the act of dancing. In this case, the question 
-that the agent is actually asking themselves is ``should I continue dancing?" That is the actionable 
+``When dancing and seeing a child drowning" appear to entail the act of dancing, and the maxim thus 
+appears vacuous. Once again, this maxim is formulated incorrectly. In this case, the question 
+that the agent is actually asking themselves is ``should I continue dancing?" That is the 
 maxim that they will adopt or reject. They mean to ask if they should stop dancing and go help the child. 
 Dancing at the current moment and dancing at the next moment are different acts, and the circumstances 
-imply the former but not the latter. A badly formed maxim would have circumstances and act both 
+imply the former but not the latter. A vacuous maxim would have circumstances and act both 
 ``dancing at moment t," but this maxim has circumstances ``dancing at moment t" and act ``dancing 
-at moment t+1."
+at moment t+1." This is a kind of temporal error that has bearings for other debates in ethics as well. 
+Specifically, the confusion between circumstances and acts that occur at different times (as in this example) and circumstances 
+and acts that occur at the exact same time has bearing on self-doubt, as I will argue next.
 
-Another interpretation of the dancing example is the ``self doubt" intepretation. The question ``When I am dancing, 
-should I really be dancing for the sake of dancing?" is the agent asking, ``Am I doing the right thing 
-right now?" The agent is not asking about the next moment, but is expressing doubt about the 
-moral validity of their behavior at this current moment. Under this interpretation, the agent 
-wants to know if they made the right decision. But what decision has the agent made? Did the agent
-adopt the maxim ``When dancing, dance for the sake of dancing?" They could not have, because such a 
-maxim could not have altered their behavior at all. This agent actually wants to know if the maxim that 
-resulted in them dancing, the maxim that got them to the current moment on the dance floor, was actually 
-the right thing to do. They are asking if, in the past, when they decided to dance, they made the 
-right decision. But such a maxim is not vacuous, because it resulted in the act of dancing. 
-The maxim that initiated the dancing would be something like ``When at a wedding, dance for the sake 
-of dancing." This is the maxim that they are currently acting on, not the badly formed example maxim.
-Evaluating the moral validity of this maxim is straightforward.
+\emph{Implications for Self Doubt and Self Respect}
 
-This analysis also demonstrates the correct way to think about moral regret and self-doubt. When we 
-ask ``should I really be doing this?" we are asking if, when we chose to adopt our current maxim, 
-we made the right decision. The question is not, ``When acting should I act?" The question is, ``When 
-I was in the past, should I have chosen to act?" Regret is a counterfactual question about a valid, 
-well-formed maxim that was adopted in the past and led to the present moment. Unlike a badly formed 
-maxim, it doesn't undermine the will because it acknowledges the will's authority and the fact that the 
-will made a decision, but it asks if the will was mistaken.%
+Another interpretation of the dancing example is the ``self doubt" intepretation. Under this 
+interpretation, the question ``When I am dancing, 
+should I be dancing for the sake of dancing?" is the agent asking, ``Am I doing the right thing 
+right now?" Unlike the drowning example, the agent is not asking about the next moment, but is expressing doubt about the 
+moral validity of their behavior at this current moment. I do not want to argue that self-doubt is 
+contradictory because it undermines the will—after all, self-doubt plays an important role in moral 
+reasoning and often is the mark of a thoughtful agent. I argue instead that questions of self-doubt
+do not actually involve vacuous maxims, for these are not the maxims that the agent is doubting. Indeed,
+this example demonstrates that the tension between self-doubt and self-respect arises from a 
+mistaken characterization of questions of self-doubt as questions about vacuous maxims.
+I first explain the tension between self-doubt and self-respect in epistemology, then 
+explain the parallel tension in ethics, and finally present a resolution of this tension.
+
+In epistemology, there is a tension between the rational requirement to believe in yourself and the 
+value of self-doubt, in moderation. Christensen presents the ``principle of self-respect," which requires 
+that any rational agent refrain from believing that they have mistaken beliefs \cite[4]{christensen}. For example, I cannot 
+rationally both believe that the sky is blue and believe that I believe that the sky is green. I cannot 
+disapprove of my own credences. Christensen argues that this principle, which he abbreviates to SR, holds because 
+a perfectly rational agent can make accurate and confident judgements about what they believe. If this 
+is the case, violating SR results in a simple contradiction \cite[8-9]{christensen}.
+
+While most philosophers accept some version of SR\footnote{Van Fraassen, Vickers, Koons \cite[5]{christensen}}, 
+Sherrilyn Roush argues that the principle must be modified in order to account for healthy epistemic 
+self-doubt. She argues that, while pathological second guessing is roundly criticized, we are generally 
+imperfect beings, and some sensitivity to our own limitations is a virtue \cite[2]{roushselfhelp}. Indeed, even Christensen 
+acknowledges that total self-confidence is an epistemic flaw \cite[1]{christensen}. Thus, there is tension between the rational
+requirement to respect our authority as believers and the practical reality that we are often wrong.
+
+This debate between self-respect and self-doubt in epistemology also applies to ethics and practical 
+reason. When we decide to act and commit ourselves to acting, we cannot simultaneously doubt the 
+validity of our action. If human behavior is purposive, then the very act of committing oneself implies 
+that one has sufficient reasons for committing oneself. These reasons may be flawed, but in making the 
+commitment, the reasoner has accepted them. It is incoherent to claim that someone commits and questions 
+simultaneously, because commitment itself implies a resolution to the question. Either the commitment 
+is not real, or the question is not. The principle that 
+one cannot will a maxim and simultaneously question if they should will that maxim, is what I will call 
+``ethical self-respect" or ESR.
+
+At the same time, self-doubt is an important part of ethical reasoning. Just as believers are often 
+mistaken, so are practical reasoners. An agent with perfect confidence, who is always sure that they 
+are doing the right thing, is clearly not thinking deeply enough about their obligations. Some degree
+of ethical self-doubt is normal and likely desirable. Thus, there is a tension between the rational
+requirement of ESR and the intuitive validity of ethical self-doubt (ESD).
+
+To resolve this tension, I return to my earlier example of a dancer. Imagine Sara is dancing at a 
+weddding, when, in a moment of angst, she asks herself, ``Should I really be dancing right now?" 
+What question is she asking here? The immediate answer is that she asking if the maxim, ``When dancing 
+at your friend's wedding, dance for the sake of dancing" is a valid maxim to act on. Under this 
+simple answer, she is asking if that maxim is prohibited. Notice that the maxim in question is a vacuous
+maxim: the circumstance ``when dancing at a friend's wedding" implies the act ``dance." Because it 
+is a vacuous maxim, this cannot be the maxim that she is questioning, for adopting this maxim could 
+not have changed her behavior at all. Sara is asking a question about her actions and their validity, 
+but any conclusions about the validity of a vacuous maxim would not help her, first because the maxim 
+has no effect on her action, and second because any such validity would be a foregone conclusion. As 
+I argued above, no practical reasoner can coherently ask themselves whether a vacuous maxim is 
+valid or not without undermining their decision-making power, which is a contradiction. Thus, under 
+the interpretation of self-doubt as a vacuous maxim, the tension between ESR and ethical self-doubt 
+appears irresolvable. Those committed to this interpretation must abandon one principle or the other.
+
+To resolve
+this issue, I turn to another interpretation of ethical self-doubt. Under this interpretation, when Sara
+asks, ``Should I really be dancing right now?" she wants to know if the maxim that 
+resulted in the current moment when she is on the dance floor was actually 
+the right thing to will. She is asking if she made the right 
+decision in the past, when she decided to dance. The maxim that initiated the dancing would be something like ``When at a wedding, dance for the sake 
+of dancing." This is the maxim that she is currently acting on, not the vacuous maxim ``When dancing, 
+dance for the sake of dancing." Under this interpretation, there is no tension at all between self-doubt 
+and self-respect. It is perfectly valid for a reasoner to doubt their prior moral judgements, just as 
+it is perfectly rational for a believer to doubt their past beliefs \cite[3-4]{christensen}. Such doubt 
+does not undermine the reasoner's decision-making capacity and is thus perfectly consistent with ethical 
+self-respect.
+
+Not only does this second interpretation resolve the tension between ESR and ESD, it also more accurately 
+tracks the operation of practical reason. As argued above, a practical reasoner would never ask themselves 
+whether or not to will a vacuous maxim, because such a maxim would generate no meaningful obligations. 
+Adopting such a maxim would not alter their behavior in any way. Moreover, the fact that a practical 
+reasoner never adopts a vacuous maxim demonstrates the cause of the tension between ESR and ESD.
+The tension itself arises from a misreading of questions of self-doubt as questions about 
+the evaluation of vacuous maxims. A question of self-doubt cannot refer to a vacuous maxim and must 
+instead refer to a well-formed maxim about the agent's past decision-making. As seen before, cases where 
+agents appear to ask themselves about vacuous maxims are mistaken about the maxim in question, because 
+such a question could never yield a useful answer for a practical reasoner.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
+I will now generalize from the personal insight reached above to the methodological value of 
+computational ethics for philosophers.
 I do not argue that computational ethics, as it stands today, uncovers philosophical insights that humans have not reached
 or are incapable of reaching. After all, my understanding of a well-formed maxim could 
-very well exist in the literature and certainly could be reached by a philosopher working without any 
+very well exist in the literature and certainly could be reached by a philosopher without any 
 computational tools. Instead, I argue that computational tools prompt philosophers to ask questions that 
@@
 departments, technical progress could turn computational ethics into an easy-to-use tool for philosophers
-that doesn't require any specialized knowledge.
+that doesn't require any specialized progamming or logical knowledge.
 
@@
 Another, related benefit of computational ethics is that it makes formal ethics far less tedious. 
-Certain subfields, such as philosophy of language, see such benefit in precision that they already heavily 
+Certain subfields, such as philosophy of language, see such benefit in precision that they already 
 use symbolic logic to represent philosophical concepts, just as mathematicians use symbolic logic to 
@@
 theorems, even when many of these theorems may not generate relevant philosophical insights. Ineractive 
-theorem provers make proofs more accessible. Isabelle can complete a proof, starting from first principles, 
-in a matter of seconds that would take a logician pages to complete. Just as calculators make arithmetic 
-more accessible, computational ethics does the same for formal philosophy. Not all philosophy can or will 
-be automated—after all, calculators didn't make accountants or mathematicians obsolete. Just as computers 
-reduce the tedium in other aspects of our life, they can reduce the tedium involved in formal logic for 
-both mathematicians and philosophers.%
+theorem provers make formal logic more accessible. Isabelle can complete a proof, starting from first principles, 
+in a matter of seconds that would take a logician pages to complete. Similarly, Nitpick can generate 
+examples or counterexamples to a proposition in a brute force manner. The computer can generate hypotheses
+that philosophers can then think about, just as it did for me to prompt the insight above.
+
+Just as calculators make arithmetic more accessible, computational ethics does the same for formal philosophy. 
+Not all philosophy can or will 
+be formalized or automated—after all, calculators didn't make accountants or mathematicians obsolete. Just as computers 
+reduce the tedium in other aspects of our life, they can reduce the tedium involved in formal logic to 
+allow mathematicians and philosophers to focus their attention on understanding.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %:%77=32%:%
-%:%78=33%:%
+%:%80=36%:%
 %:%81=37%:%
@@
 %:%142=97%:%
-%:%151=99%:%
-%:%163=101%:%
-%:%164=102%:%
-%:%165=103%:%
-%:%166=104%:%
-%:%167=105%:%
-%:%168=106%:%
-%:%177=108%:%
-%:%189=110%:%
-%:%190=111%:%
-%:%191=112%:%
-%:%192=113%:%
-%:%193=114%:%
-%:%194=115%:%
-%:%195=116%:%
-%:%196=117%:%
-%:%197=118%:%
+%:%143=98%:%
+%:%144=99%:%
+%:%145=100%:%
+%:%146=101%:%
+%:%147=102%:%
+%:%148=103%:%
+%:%149=104%:%
+%:%150=105%:%
+%:%151=106%:%
+%:%160=108%:%
+%:%172=110%:%
+%:%173=111%:%
+%:%174=112%:%
+%:%175=113%:%
+%:%176=114%:%
+%:%177=115%:%
+%:%186=117%:%
 %:%198=119%:%
@@
 %:%364=285%:%
-%:%373=288%:%
-%:%385=290%:%
-%:%386=291%:%
-%:%387=292%:%
-%:%388=293%:%
-%:%389=294%:%
-%:%390=295%:%
-%:%391=296%:%
-%:%392=297%:%
-%:%393=298%:%
-%:%394=299%:%
-%:%395=300%:%
-%:%396=301%:%
-%:%397=302%:%
-%:%398=303%:%
-%:%399=304%:%
-%:%400=305%:%
-%:%401=306%:%
-%:%402=307%:%
-%:%403=308%:%
-%:%404=309%:%
-%:%405=310%:%
-%:%406=311%:%
-%:%407=312%:%
-%:%408=313%:%
-%:%409=314%:%
-%:%410=315%:%
-%:%411=316%:%
-%:%412=317%:%
-%:%413=318%:%
-%:%414=319%:%
-%:%415=320%:%
-%:%416=321%:%
-%:%417=322%:%
-%:%418=323%:%
-%:%419=324%:%
-%:%420=325%:%
-%:%421=326%:%
-%:%422=327%:%
-%:%423=328%:%
-%:%424=329%:%
-%:%433=332%:%
-%:%445=335%:%
-%:%446=336%:%
-%:%447=337%:%
-%:%448=338%:%
-%:%449=339%:%
-%:%450=340%:%
-%:%451=341%:%
-%:%452=342%:%
-%:%453=343%:%
-%:%454=344%:%
-%:%455=345%:%
-%:%456=346%:%
-%:%457=347%:%
-%:%458=348%:%
-%:%459=349%:%
-%:%460=350%:%
-%:%461=351%:%
-%:%462=352%:%
-%:%463=353%:%
-%:%464=354%:%
-%:%465=355%:%
+%:%365=286%:%
+%:%366=287%:%
+%:%367=288%:%
+%:%368=289%:%
+%:%369=290%:%
+%:%370=291%:%
+%:%371=292%:%
+%:%372=293%:%
+%:%373=294%:%
+%:%374=295%:%
+%:%375=296%:%
+%:%376=297%:%
+%:%377=298%:%
+%:%378=299%:%
+%:%379=300%:%
+%:%380=301%:%
+%:%381=302%:%
+%:%382=303%:%
+%:%383=304%:%
+%:%384=305%:%
+%:%385=306%:%
+%:%386=307%:%
+%:%387=308%:%
+%:%388=309%:%
+%:%389=310%:%
+%:%390=311%:%
+%:%391=312%:%
+%:%392=313%:%
+%:%393=314%:%
+%:%394=315%:%
+%:%395=316%:%
+%:%396=317%:%
+%:%397=318%:%
+%:%398=319%:%
+%:%399=320%:%
+%:%400=321%:%
+%:%401=322%:%
+%:%402=323%:%
+%:%403=324%:%
+%:%404=325%:%
+%:%405=326%:%
+%:%406=327%:%
+%:%407=328%:%
+%:%408=329%:%
+%:%409=330%:%
+%:%410=331%:%
+%:%411=332%:%
+%:%412=333%:%
+%:%413=334%:%
+%:%414=335%:%
+%:%415=336%:%
+%:%416=337%:%
+%:%417=338%:%
+%:%418=339%:%
+%:%419=340%:%
+%:%420=341%:%
+%:%421=342%:%
+%:%422=343%:%
+%:%423=344%:%
+%:%424=345%:%
+%:%425=346%:%
+%:%426=347%:%
+%:%427=348%:%
+%:%428=349%:%
+%:%429=350%:%
+%:%430=351%:%
+%:%431=352%:%
+%:%432=353%:%
+%:%433=354%:%
+%:%434=355%:%
+%:%435=356%:%
+%:%436=357%:%
+%:%437=358%:%
+%:%438=359%:%
+%:%439=360%:%
+%:%440=361%:%
+%:%441=362%:%
+%:%442=363%:%
+%:%443=364%:%
+%:%444=365%:%
+%:%445=366%:%
+%:%446=367%:%
+%:%447=368%:%
+%:%448=369%:%
+%:%449=370%:%
+%:%450=371%:%
+%:%451=372%:%
+%:%452=373%:%
+%:%453=374%:%
+%:%462=378%:%
+%:%474=380%:%
+%:%475=381%:%
+%:%476=382%:%
+%:%477=383%:%
+%:%478=384%:%
+%:%479=385%:%
+%:%480=386%:%
+%:%481=387%:%
+%:%482=388%:%
+%:%483=389%:%
+%:%484=390%:%
+%:%485=391%:%
+%:%486=392%:%
+%:%487=393%:%
+%:%488=394%:%
+%:%489=395%:%
+%:%490=396%:%
+%:%491=397%:%
+%:%492=398%:%
+%:%493=399%:%
+%:%494=400%:%
+%:%495=401%:%
+%:%496=402%:%
+%:%497=403%:%
+%:%498=404%:%
+%:%499=405%:%
+%:%500=406%:%
+%:%501=407%:%
+%:%502=408%:%
+%:%503=409%:%
+%:%504=410%:%
+%:%505=411%:%
+%:%506=412%:%
+%:%507=413%:%
+%:%508=414%:%
+%:%509=415%:%
+%:%510=416%:%
+%:%511=417%:%
+%:%512=418%:%
+%:%513=419%:%
+%:%514=420%:%
+%:%515=421%:%
+%:%516=422%:%
+%:%517=423%:%
+%:%518=424%:%
+%:%519=425%:%
+%:%528=428%:%
+%:%540=431%:%
+%:%541=432%:%
+%:%542=433%:%
+%:%543=434%:%
+%:%544=435%:%
+%:%545=436%:%
+%:%546=437%:%
+%:%547=438%:%
+%:%548=439%:%
+%:%549=440%:%
+%:%550=441%:%
+%:%551=442%:%
+%:%552=443%:%
+%:%553=444%:%
+%:%554=445%:%
+%:%555=446%:%
+%:%556=447%:%
+%:%557=448%:%
+%:%558=449%:%
+%:%559=450%:%
+%:%560=451%:%

### 2021-10-25 paper/output/document/paper41.tex
a solution i guess

@@
 \isacommand{abbreviation}\isamarkupfalse%
-\ universalized{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}t{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
-{\isachardoublequoteopen}universalized\ {\isasymequiv}\ {\isasymlambda}M\ s{\isachardot}\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ W\ M\ p\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ universalized{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}t{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
+{\isachardoublequoteopen}universalized\ {\isasymequiv}\ {\isasymlambda}M{\isachardot}\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ W\ M\ p\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ holds{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}t{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
+{\isachardoublequoteopen}holds\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}{\isachardot}\ c{\isachardoublequoteclose}\isanewline
 \isanewline
@@
 \ not{\isacharunderscore}universalizable\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
-{\isachardoublequoteopen}not{\isacharunderscore}universalizable\ {\isasymequiv}\ {\isasymlambda}M\ s{\isachardot}\ {\isacharparenleft}{\isasymTurnstile}\ {\isacharparenleft}universalized\ M\ s\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}E\ M\ s{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-%
-\isamarkupcmt{The maxim willed by subject $s$ is not universalizable if, for all people $p$, if $p$ wills M, then 
-$M$ is no longer effective for $s$.%
-}%
+{\isachardoublequoteopen}not{\isacharunderscore}universalizable\ {\isasymequiv}\ {\isasymlambda}M\ s{\isachardot}\ {\isasymforall}w{\isachardot}\ {\isacharparenleft}{\isasymnot}\ {\isacharparenleft}holds\ M\ w{\isacharparenright}{\isacharparenright}\ {\isasymor}\ {\isacharparenleft}universalized\ M\ \ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}E\ M\ s{\isacharparenright}{\isacharparenright}{\isacharparenright}w{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{The formula above reads ``at world $w$, if M is universalized and M is acted on (i.e. the circumstances 
+of M hold), then M is not effective."
+
+Notice that the antecedent specifies that the circumstances hold at the given world. 
+When evaluating if a maxim is universalizable or not, we want to ignore worlds where the circumstance 
+do not hold. At these worlds, the maxim is trivially effective and thus trivially universalizable. If we didn't exclude such worlds from 
+consideration, a maxim with circumstances that ever fail to hold would be universalizable. Clearly 
+this is not a desirable conclusion, since maxims like ``When you need money, lie to get easy money"
+would be universalizable.%
+}\isanewline
+\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ imagine{\isacharunderscore}a{\isacharunderscore}world{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
+{\isachardoublequoteopen}imagine{\isacharunderscore}a{\isacharunderscore}world\ {\isasymequiv}\ {\isasymlambda}M{\isachardot}\ {\isacharparenleft}{\isasymexists}w{\isachardot}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ {\isacharparenleft}W\ M\ p{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{This abbreviation formalizes the idea that, for any maxim, some world where exist where the maxim 
+is universally willed.%
+}\isanewline
+\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ not{\isacharunderscore}contradictory{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
+{\isachardoublequoteopen}not{\isacharunderscore}contradictory\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}{\isachardot}\ {\isacharparenleft}{\isasymforall}p\ w{\isachardot}\ {\isasymnot}\ {\isacharparenleft}{\isacharparenleft}c\ \isactrlbold {\isasymand}\ {\isacharparenleft}a\ p{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbottom}{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{axiomatization}\isamarkupfalse%
+\ \isakeyword{where}\ test{\isacharcolon}{\isachardoublequoteopen}{\isasymforall}M{\isachardot}\ not{\isacharunderscore}contradictory\ M\ {\isasymlongrightarrow}\ imagine{\isacharunderscore}a{\isacharunderscore}world\ M{\isachardoublequoteclose}%
 \begin{isamarkuptext}%
@@
 \isacommand{using}\isamarkupfalse%
-\ O{\isacharunderscore}diamond\ \isanewline
-\ \ \isacommand{using}\isamarkupfalse%
-\ prod{\isachardot}simps{\isacharparenleft}{\isadigit{2}}{\isacharparenright}\ split{\isacharunderscore}conv\ \isacommand{by}\isamarkupfalse%
-\ fastforce%
+\ O{\isacharunderscore}diamond\isanewline
+\ \ \isacommand{by}\isamarkupfalse%
+\ force%
 \endisatagproof
@@
 how the system handles different kinds of maxims.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{consts}\isamarkupfalse%
+\ when{\isacharunderscore}strapped{\isacharunderscore}for{\isacharunderscore}cash{\isacharcolon}{\isacharcolon}t\isanewline
+\isacommand{consts}\isamarkupfalse%
+\ lie{\isacharcolon}{\isacharcolon}os\isanewline
+\isacommand{consts}\isamarkupfalse%
+\ to{\isacharunderscore}get{\isacharunderscore}easy{\isacharunderscore}cash{\isacharcolon}{\isacharcolon}t\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ lie{\isacharunderscore}maxim{\isacharcolon}{\isacharcolon}maxim\ \isakeyword{where}\ \isanewline
+{\isachardoublequoteopen}lie{\isacharunderscore}maxim\ {\isasymequiv}\ {\isacharparenleft}when{\isacharunderscore}strapped{\isacharunderscore}for{\isacharunderscore}cash{\isacharcomma}\ lie{\isacharcomma}\ to{\isacharunderscore}get{\isacharunderscore}easy{\isacharunderscore}cash{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ everyone{\isacharunderscore}can{\isacharprime}t{\isacharunderscore}lie\ \isakeyword{where}\ \isanewline
+{\isachardoublequoteopen}everyone{\isacharunderscore}can{\isacharprime}t{\isacharunderscore}lie\ {\isasymequiv}\ {\isasymforall}w{\isachardot}\ {\isasymnot}\ {\isacharparenleft}{\isasymforall}s{\isachardot}\ lie{\isacharparenleft}s{\isacharparenright}\ w{\isacharparenright}\ {\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ lying{\isacharunderscore}bad{\isacharcolon}\isanewline
+\ \ \isakeyword{assumes}\ everyone{\isacharunderscore}can{\isacharprime}t{\isacharunderscore}lie\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}when{\isacharunderscore}strapped{\isacharunderscore}for{\isacharunderscore}cash\ cw{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}s{\isachardot}\ not{\isacharunderscore}universalizable\ lie{\isacharunderscore}maxim\ s{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{using}\isamarkupfalse%
+\ assms{\isacharparenleft}{\isadigit{1}}{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
+\ auto%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+\isanewline
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ test{\isadigit{6}}{\isacharcolon}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}s{\isachardot}\ not{\isacharunderscore}universalizable\ lie{\isacharunderscore}maxim\ s{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}s{\isachardot}\ {\isasymTurnstile}\ {\isacharparenleft}well{\isacharunderscore}formed\ lie{\isacharunderscore}maxim\ s{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}s{\isachardot}\ {\isasymTurnstile}\ {\isacharparenleft}prohibited\ lie{\isacharunderscore}maxim\ s{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{using}\isamarkupfalse%
+\ FUL\ assms{\isacharparenleft}{\isadigit{1}}{\isacharparenright}\ assms{\isacharparenleft}{\isadigit{2}}{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
+\ blast%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+Action is impossible%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+Maxim is bad under PC interp%
 \end{isamarkuptext}\isamarkuptrue%
@@
 }\isanewline
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isatagproof
 %
@@
 %:%272=215%:%
-%:%274=216%:%
+%:%273=216%:%
+%:%274=217%:%
 %:%275=217%:%
+%:%276=218%:%
 %:%278=219%:%
@@
 %:%285=226%:%
-%:%287=228%:%
+%:%286=227%:%
+%:%287=227%:%
 %:%288=228%:%
 %:%289=229%:%
-%:%290=230%:%
-%:%291=231%:%
-%:%292=231%:%
-%:%293=232%:%
-%:%295=233%:%
-%:%296=234%:%
-%:%299=236%:%
-%:%300=237%:%
-%:%301=238%:%
-%:%302=239%:%
-%:%303=240%:%
-%:%304=241%:%
-%:%305=242%:%
-%:%306=243%:%
-%:%307=244%:%
-%:%308=245%:%
-%:%309=246%:%
-%:%310=247%:%
-%:%311=248%:%
-%:%312=249%:%
-%:%313=250%:%
-%:%314=251%:%
-%:%315=252%:%
-%:%316=253%:%
-%:%317=254%:%
-%:%318=255%:%
-%:%319=256%:%
-%:%320=257%:%
-%:%321=258%:%
-%:%322=259%:%
-%:%323=260%:%
-%:%325=262%:%
-%:%326=262%:%
-%:%327=263%:%
-%:%329=264%:%
-%:%330=265%:%
-%:%331=265%:%
-%:%332=266%:%
-%:%333=267%:%
-%:%334=267%:%
-%:%336=268%:%
-%:%337=269%:%
-%:%338=270%:%
-%:%346=272%:%
-%:%358=274%:%
-%:%359=275%:%
-%:%360=276%:%
-%:%361=277%:%
-%:%362=278%:%
-%:%363=279%:%
-%:%365=282%:%
-%:%366=282%:%
-%:%368=283%:%
-%:%369=284%:%
-%:%370=285%:%
-%:%371=286%:%
-%:%372=286%:%
-%:%373=287%:%
-%:%374=288%:%
-%:%375=288%:%
-%:%377=288%:%
-%:%381=288%:%
-%:%382=288%:%
-%:%383=289%:%
-%:%384=289%:%
-%:%385=289%:%
-%:%394=291%:%
-%:%395=292%:%
-%:%396=293%:%
-%:%397=294%:%
-%:%398=295%:%
-%:%399=296%:%
-%:%400=297%:%
-%:%401=298%:%
-%:%402=299%:%
-%:%403=300%:%
-%:%404=301%:%
-%:%405=302%:%
-%:%406=303%:%
-%:%407=304%:%
-%:%408=305%:%
-%:%409=306%:%
-%:%410=307%:%
-%:%412=309%:%
-%:%413=309%:%
-%:%414=310%:%
-%:%416=311%:%
-%:%417=312%:%
-%:%418=312%:%
-%:%419=313%:%
-%:%420=314%:%
-%:%421=314%:%
+%:%290=229%:%
+%:%291=230%:%
+%:%293=231%:%
+%:%294=232%:%
+%:%295=232%:%
+%:%296=233%:%
+%:%297=234%:%
+%:%298=234%:%
+%:%299=235%:%
+%:%300=236%:%
+%:%301=237%:%
+%:%302=237%:%
+%:%304=239%:%
+%:%305=240%:%
+%:%306=241%:%
+%:%307=242%:%
+%:%308=243%:%
+%:%309=244%:%
+%:%310=245%:%
+%:%311=246%:%
+%:%313=248%:%
+%:%314=248%:%
+%:%315=249%:%
+%:%316=250%:%
+%:%317=251%:%
+%:%318=251%:%
+%:%319=252%:%
+%:%321=253%:%
+%:%322=254%:%
+%:%325=256%:%
+%:%326=257%:%
+%:%327=258%:%
+%:%328=259%:%
+%:%329=260%:%
+%:%330=261%:%
+%:%331=262%:%
+%:%332=263%:%
+%:%333=264%:%
+%:%334=265%:%
+%:%335=266%:%
+%:%336=267%:%
+%:%337=268%:%
+%:%338=269%:%
+%:%339=270%:%
+%:%340=271%:%
+%:%341=272%:%
+%:%342=273%:%
+%:%343=274%:%
+%:%344=275%:%
+%:%345=276%:%
+%:%346=277%:%
+%:%347=278%:%
+%:%348=279%:%
+%:%349=280%:%
+%:%351=282%:%
+%:%352=282%:%
+%:%353=283%:%
+%:%355=284%:%
+%:%356=285%:%
+%:%357=285%:%
+%:%358=286%:%
+%:%359=287%:%
+%:%360=287%:%
+%:%362=288%:%
+%:%363=289%:%
+%:%364=290%:%
+%:%372=292%:%
+%:%384=294%:%
+%:%385=295%:%
+%:%386=296%:%
+%:%387=297%:%
+%:%388=298%:%
+%:%389=299%:%
+%:%391=302%:%
+%:%392=302%:%
+%:%394=303%:%
+%:%395=304%:%
+%:%396=305%:%
+%:%397=306%:%
+%:%398=306%:%
+%:%399=307%:%
+%:%400=308%:%
+%:%401=308%:%
+%:%403=308%:%
+%:%407=308%:%
+%:%408=308%:%
+%:%409=309%:%
+%:%410=309%:%
+%:%419=311%:%
+%:%420=312%:%
+%:%421=313%:%
+%:%422=314%:%
 %:%423=315%:%
 %:%424=316%:%
-%:%425=316%:%
-%:%426=317%:%
-%:%427=318%:%
-%:%428=318%:%
-%:%429=319%:%
-%:%430=319%:%
-%:%432=319%:%
-%:%436=319%:%
-%:%437=319%:%
-%:%439=320%:%
-%:%440=321%:%
-%:%441=322%:%
-%:%442=323%:%
-%:%443=324%:%
-%:%444=325%:%
-%:%445=326%:%
-%:%446=327%:%
-%:%447=328%:%
-%:%448=329%:%
-%:%449=330%:%
-%:%457=330%:%
-%:%458=331%:%
-%:%459=332%:%
-%:%460=332%:%
-%:%461=333%:%
-%:%462=334%:%
-%:%463=334%:%
-%:%464=335%:%
-%:%465=335%:%
-%:%467=335%:%
-%:%471=335%:%
-%:%472=335%:%
-%:%474=336%:%
-%:%475=337%:%
-%:%476=338%:%
-%:%477=339%:%
-%:%478=340%:%
-%:%479=341%:%
-%:%489=343%:%
-%:%490=344%:%
-%:%491=345%:%
-%:%492=346%:%
-%:%493=347%:%
-%:%494=348%:%
-%:%495=349%:%
-%:%496=350%:%
-%:%497=351%:%
-%:%498=352%:%
-%:%499=353%:%
-%:%500=354%:%
-%:%501=355%:%
-%:%502=356%:%
-%:%503=357%:%
-%:%504=358%:%
-%:%505=359%:%
-%:%506=360%:%
-%:%507=361%:%
-%:%508=362%:%
-%:%512=364%:%
-%:%513=365%:%
-%:%514=366%:%
-%:%515=367%:%
-%:%516=368%:%
-%:%525=370%:%
-%:%537=372%:%
-%:%538=373%:%
-%:%539=374%:%
-%:%540=375%:%
-%:%549=378%:%
-%:%561=380%:%
-%:%562=381%:%
-%:%563=382%:%
-%:%564=383%:%
-%:%565=384%:%
-%:%566=385%:%
-%:%567=386%:%
-%:%568=387%:%
-%:%569=388%:%
-%:%570=389%:%
-%:%571=390%:%
-%:%572=391%:%
-%:%573=392%:%
-%:%574=393%:%
-%:%575=394%:%
-%:%576=395%:%
-%:%577=396%:%
-%:%578=397%:%
-%:%579=398%:%
-%:%580=399%:%
-%:%582=401%:%
-%:%583=401%:%
-%:%584=402%:%
-%:%587=403%:%
-%:%591=403%:%
-%:%592=403%:%
-%:%597=403%:%
-%:%600=404%:%
-%:%601=405%:%
-%:%602=405%:%
-%:%603=406%:%
-%:%606=407%:%
-%:%610=407%:%
-%:%611=407%:%
-%:%616=407%:%
-%:%619=408%:%
-%:%620=409%:%
-%:%621=409%:%
-%:%622=410%:%
-%:%625=411%:%
-%:%629=411%:%
-%:%630=411%:%
-%:%635=411%:%
-%:%638=412%:%
-%:%639=413%:%
-%:%640=413%:%
-%:%641=414%:%
-%:%644=415%:%
-%:%648=415%:%
-%:%649=415%:%
-%:%658=417%:%
-%:%659=418%:%
-%:%660=419%:%
-%:%661=420%:%
-%:%662=421%:%
-%:%663=422%:%
-%:%664=423%:%
-%:%666=425%:%
-%:%667=425%:%
-%:%668=426%:%
-%:%669=427%:%
-%:%670=427%:%
-%:%672=427%:%
-%:%676=427%:%
-%:%677=427%:%
-%:%679=428%:%
-%:%680=429%:%
-%:%681=430%:%
-%:%682=431%:%
-%:%683=432%:%
-%:%684=433%:%
-%:%685=434%:%
-%:%686=435%:%
-%:%687=436%:%
-%:%688=437%:%
-%:%689=438%:%
-%:%699=440%:%
-%:%700=441%:%
-%:%702=443%:%
-%:%703=443%:%
-%:%704=444%:%
-%:%707=445%:%
-%:%711=445%:%
-%:%712=445%:%
-%:%714=446%:%
-%:%724=448%:%
-%:%725=449%:%
-%:%727=451%:%
-%:%728=451%:%
-%:%729=452%:%
-%:%732=453%:%
-%:%736=453%:%
-%:%737=453%:%
-%:%738=453%:%
-%:%740=454%:%
-%:%741=455%:%
-%:%751=457%:%
-%:%752=458%:%
-%:%753=459%:%
-%:%754=460%:%
-%:%755=461%:%
-%:%756=462%:%
-%:%757=463%:%
-%:%758=464%:%
-%:%759=465%:%
-%:%760=466%:%
-%:%761=467%:%
-%:%762=468%:%
-%:%766=470%:%
-%:%767=471%:%
-%:%768=472%:%
-%:%770=474%:%
-%:%771=474%:%
-%:%772=475%:%
-%:%773=476%:%
-%:%774=477%:%
-%:%775=477%:%
-%:%777=477%:%
-%:%781=477%:%
-%:%782=477%:%
-%:%784=478%:%
-%:%785=479%:%
-%:%786=480%:%
-%:%787=481%:%
-%:%788=482%:%
-%:%789=483%:%
-%:%790=484%:%
-%:%791=485%:%
-%:%792=486%:%
-%:%793=487%:%
-%:%803=489%:%
-%:%804=490%:%
-%:%805=491%:%
-%:%807=493%:%
-%:%808=493%:%
-%:%809=494%:%
-%:%810=495%:%
-%:%811=495%:%
-%:%813=495%:%
-%:%817=495%:%
-%:%818=495%:%
-%:%820=496%:%
-%:%821=497%:%
-%:%822=498%:%
-%:%823=499%:%
-%:%824=500%:%
-%:%825=501%:%
-%:%826=502%:%
-%:%827=503%:%
-%:%828=504%:%
-%:%829=505%:%
-%:%839=507%:%
-%:%840=508%:%
-%:%841=509%:%
-%:%842=510%:%
-%:%844=512%:%
-%:%845=512%:%
-%:%846=513%:%
-%:%849=514%:%
-%:%853=514%:%
-%:%854=514%:%
-%:%855=514%:%
-%:%857=515%:%
-%:%863=515%:%
-%:%866=516%:%
-%:%867=517%:%
-%:%868=517%:%
-%:%869=518%:%
-%:%872=519%:%
-%:%876=519%:%
-%:%877=519%:%
-%:%878=519%:%
-%:%880=520%:%
-%:%886=520%:%
-%:%889=521%:%
-%:%890=522%:%
-%:%891=522%:%
-%:%892=523%:%
-%:%893=524%:%
-%:%896=525%:%
-%:%900=525%:%
-%:%901=525%:%
-%:%902=525%:%
-%:%904=526%:%
-%:%905=527%:%
-%:%915=529%:%
-%:%916=530%:%
-%:%917=531%:%
-%:%918=532%:%
-%:%919=533%:%
-%:%920=534%:%
-%:%921=535%:%
-%:%930=537%:%
-%:%942=539%:%
-%:%943=540%:%
-%:%944=541%:%
-%:%945=542%:%
-%:%947=544%:%
-%:%948=544%:%
-%:%949=545%:%
-%:%950=546%:%
-%:%951=546%:%
-%:%953=546%:%
-%:%957=546%:%
-%:%958=546%:%
-%:%960=547%:%
-%:%961=548%:%
-%:%962=549%:%
-%:%963=550%:%
-%:%964=551%:%
-%:%965=552%:%
-%:%966=553%:%
-%:%967=554%:%
-%:%968=555%:%
-%:%969=556%:%
-%:%970=557%:%
-%:%971=557%:%
+%:%425=317%:%
+%:%426=318%:%
+%:%427=319%:%
+%:%428=320%:%
+%:%429=321%:%
+%:%430=322%:%
+%:%431=323%:%
+%:%432=324%:%
+%:%433=325%:%
+%:%434=326%:%
+%:%435=327%:%
+%:%437=329%:%
+%:%438=329%:%
+%:%439=330%:%
+%:%441=331%:%
+%:%442=332%:%
+%:%443=332%:%
+%:%444=333%:%
+%:%445=334%:%
+%:%446=334%:%
+%:%448=335%:%
+%:%449=336%:%
+%:%450=336%:%
+%:%451=337%:%
+%:%452=338%:%
+%:%453=338%:%
+%:%454=339%:%
+%:%455=339%:%
+%:%457=339%:%
+%:%461=339%:%
+%:%462=339%:%
+%:%464=340%:%
+%:%465=341%:%
+%:%466=342%:%
+%:%467=343%:%
+%:%468=344%:%
+%:%469=345%:%
+%:%470=346%:%
+%:%471=347%:%
+%:%472=348%:%
+%:%473=349%:%
+%:%474=350%:%
+%:%482=350%:%
+%:%483=351%:%
+%:%484=352%:%
+%:%485=352%:%
+%:%486=353%:%
+%:%487=354%:%
+%:%488=354%:%
+%:%489=355%:%
+%:%490=355%:%
+%:%492=355%:%
+%:%496=355%:%
+%:%497=355%:%
+%:%499=356%:%
+%:%500=357%:%
+%:%501=358%:%
+%:%502=359%:%
+%:%503=360%:%
+%:%504=361%:%
+%:%514=363%:%
+%:%515=364%:%
+%:%516=365%:%
+%:%517=366%:%
+%:%518=367%:%
+%:%519=368%:%
+%:%520=369%:%
+%:%521=370%:%
+%:%522=371%:%
+%:%523=372%:%
+%:%524=373%:%
+%:%525=374%:%
+%:%526=375%:%
+%:%527=376%:%
+%:%528=377%:%
+%:%529=378%:%
+%:%530=379%:%
+%:%531=380%:%
+%:%532=381%:%
+%:%533=382%:%
+%:%537=384%:%
+%:%538=385%:%
+%:%539=386%:%
+%:%540=387%:%
+%:%541=388%:%
+%:%550=390%:%
+%:%562=392%:%
+%:%563=393%:%
+%:%564=394%:%
+%:%565=395%:%
+%:%567=397%:%
+%:%568=397%:%
+%:%569=398%:%
+%:%570=398%:%
+%:%571=399%:%
+%:%572=399%:%
+%:%573=400%:%
+%:%574=400%:%
+%:%575=401%:%
+%:%576=402%:%
+%:%577=403%:%
+%:%578=403%:%
+%:%579=404%:%
+%:%580=405%:%
+%:%581=406%:%
+%:%582=406%:%
+%:%583=407%:%
+%:%584=408%:%
+%:%585=409%:%
+%:%588=410%:%
+%:%592=410%:%
+%:%593=410%:%
+%:%594=410%:%
+%:%599=410%:%
+%:%602=411%:%
+%:%603=412%:%
+%:%604=412%:%
+%:%605=413%:%
+%:%606=414%:%
+%:%607=415%:%
+%:%610=416%:%
+%:%614=416%:%
+%:%615=416%:%
+%:%616=416%:%
+%:%625=420%:%
+%:%629=422%:%
+%:%638=424%:%
+%:%650=426%:%
+%:%651=427%:%
+%:%652=428%:%
+%:%653=429%:%
+%:%654=430%:%
+%:%655=431%:%
+%:%656=432%:%
+%:%657=433%:%
+%:%658=434%:%
+%:%659=435%:%
+%:%660=436%:%
+%:%661=437%:%
+%:%662=438%:%
+%:%663=439%:%
+%:%664=440%:%
+%:%665=441%:%
+%:%666=442%:%
+%:%667=443%:%
+%:%668=444%:%
+%:%669=445%:%
+%:%671=447%:%
+%:%672=447%:%
+%:%673=448%:%
+%:%676=449%:%
+%:%680=449%:%
+%:%681=449%:%
+%:%686=449%:%
+%:%689=450%:%
+%:%690=451%:%
+%:%691=451%:%
+%:%692=452%:%
+%:%695=453%:%
+%:%699=453%:%
+%:%700=453%:%
+%:%705=453%:%
+%:%708=454%:%
+%:%709=455%:%
+%:%710=455%:%
+%:%711=456%:%
+%:%714=457%:%
+%:%718=457%:%
+%:%719=457%:%
+%:%724=457%:%
+%:%727=458%:%
+%:%728=459%:%
+%:%729=459%:%
+%:%730=460%:%
+%:%733=461%:%
+%:%737=461%:%
+%:%738=461%:%
+%:%747=463%:%
+%:%748=464%:%
+%:%749=465%:%
+%:%750=466%:%
+%:%751=467%:%
+%:%752=468%:%
+%:%753=469%:%
+%:%755=471%:%
+%:%756=471%:%
+%:%757=472%:%
+%:%758=473%:%
+%:%759=473%:%
+%:%761=473%:%
+%:%765=473%:%
+%:%766=473%:%
+%:%768=474%:%
+%:%769=475%:%
+%:%770=476%:%
+%:%771=477%:%
+%:%772=478%:%
+%:%773=479%:%
+%:%774=480%:%
+%:%775=481%:%
+%:%776=482%:%
+%:%777=483%:%
+%:%778=484%:%
+%:%788=486%:%
+%:%789=487%:%
+%:%791=489%:%
+%:%792=489%:%
+%:%793=490%:%
+%:%796=491%:%
+%:%800=491%:%
+%:%801=491%:%
+%:%803=492%:%
+%:%813=494%:%
+%:%814=495%:%
+%:%816=497%:%
+%:%817=497%:%
+%:%818=498%:%
+%:%821=499%:%
+%:%825=499%:%
+%:%826=499%:%
+%:%827=499%:%
+%:%829=500%:%
+%:%830=501%:%
+%:%840=503%:%
+%:%841=504%:%
+%:%842=505%:%
+%:%843=506%:%
+%:%844=507%:%
+%:%845=508%:%
+%:%846=509%:%
+%:%847=510%:%
+%:%848=511%:%
+%:%849=512%:%
+%:%850=513%:%
+%:%851=514%:%
+%:%855=516%:%
+%:%856=517%:%
+%:%857=518%:%
+%:%859=520%:%
+%:%860=520%:%
+%:%861=521%:%
+%:%862=522%:%
+%:%863=523%:%
+%:%864=523%:%
+%:%866=523%:%
+%:%870=523%:%
+%:%871=523%:%
+%:%873=524%:%
+%:%874=525%:%
+%:%875=526%:%
+%:%876=527%:%
+%:%877=528%:%
+%:%878=529%:%
+%:%879=530%:%
+%:%880=531%:%
+%:%881=532%:%
+%:%882=533%:%
+%:%892=535%:%
+%:%893=536%:%
+%:%894=537%:%
+%:%896=539%:%
+%:%897=539%:%
+%:%898=540%:%
+%:%899=541%:%
+%:%900=541%:%
+%:%902=541%:%
+%:%906=541%:%
+%:%907=541%:%
+%:%909=542%:%
+%:%910=543%:%
+%:%911=544%:%
+%:%912=545%:%
+%:%913=546%:%
+%:%914=547%:%
+%:%915=548%:%
+%:%916=549%:%
+%:%917=550%:%
+%:%918=551%:%
+%:%928=553%:%
+%:%929=554%:%
+%:%930=555%:%
+%:%931=556%:%
+%:%933=558%:%
+%:%934=558%:%
+%:%935=559%:%
+%:%938=560%:%
+%:%942=560%:%
+%:%943=560%:%
+%:%944=560%:%
+%:%946=561%:%
+%:%952=561%:%
+%:%955=562%:%
+%:%956=563%:%
+%:%957=563%:%
+%:%958=564%:%
+%:%961=565%:%
+%:%965=565%:%
+%:%966=565%:%
+%:%967=565%:%
+%:%969=566%:%
+%:%975=566%:%
+%:%978=567%:%
+%:%979=568%:%
+%:%980=568%:%
+%:%981=569%:%
+%:%982=570%:%
+%:%985=571%:%
+%:%989=571%:%
+%:%990=571%:%
+%:%991=571%:%
+%:%993=572%:%
+%:%994=573%:%
+%:%1004=575%:%
+%:%1005=576%:%
+%:%1006=577%:%
+%:%1007=578%:%
+%:%1008=579%:%
+%:%1009=580%:%
+%:%1010=581%:%
+%:%1019=583%:%
+%:%1031=585%:%
+%:%1032=586%:%
+%:%1033=587%:%
+%:%1034=588%:%
+%:%1036=590%:%
+%:%1037=590%:%
+%:%1038=591%:%
+%:%1039=592%:%
+%:%1040=592%:%
+%:%1042=592%:%
+%:%1046=592%:%
+%:%1047=592%:%
+%:%1049=593%:%
+%:%1050=594%:%
+%:%1051=595%:%
+%:%1052=596%:%
+%:%1053=597%:%
+%:%1054=598%:%
+%:%1055=599%:%
+%:%1056=600%:%
+%:%1057=601%:%
+%:%1058=602%:%
+%:%1059=603%:%
+%:%1060=603%:%

### 2021-10-25 paper/output/document/upshot.tex
a solution i guess

@@
 for practical reasoners to be asking. They cannot be action-guiding and are thus not the domain of ethics.
-
-I define a vacuous maxim as one in which the circumstances entail either the act or the goal. An example
-of a vacuous maxim is: ``When eating breakfast, eat breakfast in order to eat breakfast." This 
-maxim isn't clearly obligatory or prohibited, but there is something empty about it. For one 
-thing, acting on this maxim would never result in any actual action. If an agent adopts this maxim, 
+Moreover, under the Kantian account of the will, the very act of asking if a vacuous maxim is prohibited 
+generates a contradiction by undermining the will's authority over itself.
+
+I define a vacuous maxim as one in which the circumstances entail either the act or the goal and argue 
+that such maxims can't meaningfully guide action. Consider the example vacuous maxim, ``when eating 
+breakfast, I will eat breakfast in order to eat breakfast." This 
+maxim isn't clearly obligatory or prohibited, but there is something empty about it. Acting on this
+ maxim could never result in any actual action. If an agent adopts this maxim, 
 they decide that, in the circumstances ``eating breakfast" they will perform the act ``eating breakfast"
 for the purpose ``eating breakfast." In these circumstances, the act has 
-already been performed! Making this maxim a rule to live by doesn't change how you live your life. If 
-you adopt this maxim, when you are eating breakfast, you eat breakfast, but this statement is already 
-tautologically true.
+already been performed! Treating this maxim a law for yourself or a principle to live by doesn't change 
+how you live your life. If you adopt this maxim, when you are eating breakfast, you eat breakfast, 
+but this statement is already tautologically true.
 
 Not only does a vacuous maxim fail to prescribe action, any obligations or prohibitions it 
-generates have already been fulfilled or violated and are thus foregone conclusions. If a vacuous 
+generates have already been fulfilled or violated. If a vacuous 
 maxim generates a prohibition, then this prohibition would be impossible to obey. 
@@
 
-If any obligations or prohibitions generated by vacuous maxims do not tell us how to live, such 
-maxims must not be the domain of ethics because ethics is 
-supposed to tell us how to live. Kant's categorical imperative
- guides our use of practical reason, which is the kind of reason that tells us what we should do. 
+Because vacuous maxims can't prescribe or alter action, they are not practically action-guiding and 
+thus are not the right kinds of maxims for practical reasoners to evaluate. Moreover, if ethics 
+is supposed to guide action, then vacuous maxims cannot be the domain of ethics. Practical reason
+is the kind of reason that helps us decide what we should do. 
 A practical reasoner asks moral questions not as a mental puzzle or out of curiosity, but 
-because the reasoner wants to know how to act. Practical reason is action-guiding, but a vacuous
+in order to decide how to act. Practical reason is action-guiding, but a vacuous
  maxim can never be action-guiding because it prescribes no new
@@
 There is no explicit prohibition against a vacuous maxim like the breakfast example above, but it 
-is the wrong kind of question for a practical reasoner to ask. Moreover, an ordinary person trying 
-to navigate the world would never ask that kind of question. If ethics and practical reason are meant 
+is the wrong kind of question for a practical reasoner to ask. On ordinary person trying 
+to navigate the world would never ask that kind of question. If ethics is meant 
 to guide action, then badly formed maxims are not questions for ethics, because they could never guide 
@@
 
-Not only are vacuous maxims not questions for ethics, but they also represent a 
-stronger problem. Asking if you should act while you act undermines your will and thus contradicts
-the very idea of willing a maxim. 
-Under the Kantian acount of willing, when you will a maxim, you make it your end and commit yourself 
-to be its cause. You cannot simultaneously commit yourself to a maxim and ask if you should be committing to it. To 
-will the maxim is to decide to will it—so the question, ``should I be 
-willing this?" is nonsensical. Either you haven't actually adopted the maxim (and thus haven't yet 
-committed yourself to it), or you aren't
-actually asking the question (because the decision has already been made). In a vacuous maxim, 
-the circumstances already assume that the agent 
-has willed the maxim. If someone asks ``should I eat breakfast while eating breakfast?" we not only 
-wouldn't be able to answer the question, we wouldn't understand it. Our response would be, ``what 
-do you mean? You are already eating breakfast." The agent must either not actually be eating breakfast or 
-they must not be asking a real question. This argument is not specific to the Kantian account of willing. 
-Under any account of practical action, questioning a commitment as you make the commitment it impossible. 
-Either you haven't actually committed or you're not actually asking the question.
+Above I argued that vacuous maxims are not the kind of principle that a practical reasoner would ever
+ask, and are thus not the right kind of question for ethics. Kantians can make an even stronger claim
+about vacuous maxims—because maxims are laws that you give to yourself, asking if you should will 
+a maxim as you will it undermines your will's law-giving ability. The circumstances of a vacuous maxim 
+already assume that the agent has willed the maxim. Under the Kantian acount of willing, this act 
+of willing a maxim is equivalent to giving the maxim to yourself as a law. When you will a maxim, you
+adopt a law to make the maxim your end and commit yourself to be its cause. You cannot simultaneously 
+commit yourself to a maxim and ask if you should be committing to it. To 
+will the maxim is to adopt it as law—so the question, ``should I be 
+willing this?" is paradoxical. Either you haven't actually made the maxim your law (and thus haven't yet 
+committed yourself to it), or you aren't actually asking the question (because the decision has already been made).
+Because a maxim is a law that you give to yourself, you cannot question it absent a sufficient reason 
+(such as a change in the circumstances). To question a law arbitrarily is to not regard it as a law at all.
+This kind of questioning amounts to questioning the will's authority over itself, but this is 
+impossible. The will definitionally has authority over itself, for that is what it is to be a 
+will.
 
@@
 
-"I should just dance" is actually referring to a different act than the circumstance ``when dancing". 
+Under one reading of this maxim, "I should just dance" is actually referring to a different act than the circumstance ``when dancing". 
 The circumstance ``when dancing" refers 
@@
 on dancing for the sake of dancing itself." The circumstances do not entail the act or the goal because 
-they refer to different meanings of the word dancing.
-
-Another interpretation of this example is as follows. Consider the maxim modified to 
+they refer to different meanings of the word dancing. Any valid reading of this maxim will have the structure above, 
+in which the act is actually different from the circumstances. A reasoner cannot accept their will 
+as law-giving or commit themselves to an act and simultaneously question the act. Either they must be 
+questioning a different act or they must have recieved new information to prompt the questioning, 
+modifying the circumstances of the original maxim.
+
+Another related worry has to with maxims that we do in fact think are prohibited. Consider the maxim modified to 
 read ``When dancing and seeing a child drowning, I should dance for the sake of dancing." Clearly this 
@@
 
-Another interpretation of the dancing example is the ``self doubt" intepretation. Under this 
-interpretation, the question ``When I am dancing, 
+The dancing maxim can also be understood through the lens of self-doubt. Under this 
+reading, the question ``When I am dancing, 
 should I be dancing for the sake of dancing?" is the agent asking, ``Am I doing the right thing 
 right now?" Unlike the drowning example, the agent is not asking about the next moment, but is expressing doubt about the 
-moral validity of their behavior at this current moment. I do not want to argue that self-doubt is 
-contradictory because it undermines the will—after all, self-doubt plays an important role in moral 
-reasoning and often is the mark of a thoughtful agent. I argue instead that questions of self-doubt
+moral validity of their behavior at this current moment. I do not want to argue that self-doubt always
+ undermines the will—after all, self-doubt plays an important role in moral 
+reasoning and is often the mark of a thoughtful agent. I argue instead that questions of self-doubt
 do not actually involve vacuous maxims, for these are not the maxims that the agent is doubting. Indeed,
@@
 that any rational agent refrain from believing that they have mistaken beliefs \cite[4]{christensen}. For example, I cannot 
-rationally both believe that the sky is blue and believe that I believe that the sky is green. I cannot 
+rationally both believe that the sky is blue and believe that I believe that the sky is green. In other words, I cannot 
 disapprove of my own credences. Christensen argues that this principle, which he abbreviates to SR, holds because 
@@
 While most philosophers accept some version of SR\footnote{Van Fraassen, Vickers, Koons \cite[5]{christensen}}, 
-Sherrilyn Roush argues that the principle must be modified in order to account for healthy epistemic 
-self-doubt. She argues that, while pathological second guessing is roundly criticized, we are generally 
+Roush argues that the principle must be modified in order to account for healthy epistemic 
+self-doubt. She argues that, while pathological second-guessing is roundly criticized, we are generally 
 imperfect beings, and some sensitivity to our own limitations is a virtue \cite[2]{roushselfhelp}. Indeed, even Christensen 
@@
 
-This debate between self-respect and self-doubt in epistemology also applies to ethics and practical 
-reason. When we decide to act and commit ourselves to acting, we cannot simultaneously doubt the 
+This debate between self-respect and self-doubt in epistemology also applies to ethics. When we 
+decide to act and commit ourselves to acting, we cannot simultaneously doubt the 
 validity of our action. If human behavior is purposive, then the very act of committing oneself implies 
 that one has sufficient reasons for committing oneself. These reasons may be flawed, but in making the 
-commitment, the reasoner has accepted them. It is incoherent to claim that someone commits and questions 
+commitment, the reasoner has accepted them. It is contradictory to claim that someone commits and questions 
 simultaneously, because commitment itself implies a resolution to the question. Either the commitment 
-is not real, or the question is not. The principle that 
-one cannot will a maxim and simultaneously question if they should will that maxim, is what I will call 
+is not real, or the question is not. I will call the principle that 
+one cannot will a maxim and simultaneously question if they should will that maxim
 ``ethical self-respect" or ESR.
 
-At the same time, self-doubt is an important part of ethical reasoning. Just as believers are often 
+On the other hand, self-doubt is an important part of ethical reasoning. Just as believers are often 
 mistaken, so are practical reasoners. An agent with perfect confidence, who is always sure that they 
@@
 What question is she asking here? The immediate answer is that she asking if the maxim, ``When dancing 
-at your friend's wedding, dance for the sake of dancing" is a valid maxim to act on. Under this 
-simple answer, she is asking if that maxim is prohibited. Notice that the maxim in question is a vacuous
-maxim: the circumstance ``when dancing at a friend's wedding" implies the act ``dance." Because it 
-is a vacuous maxim, this cannot be the maxim that she is questioning, for adopting this maxim could 
-not have changed her behavior at all. Sara is asking a question about her actions and their validity, 
-but any conclusions about the validity of a vacuous maxim would not help her, first because the maxim 
-has no effect on her action, and second because any such validity would be a foregone conclusion. As 
+at your friend's wedding, dance for the sake of dancing" is a permissible maxim to act on. Notice that t
+he maxim in question is vacuous: the circumstance ``when dancing at a friend's wedding" implies the act 
+``dance." Because this is a vacuous maxim, it cannot be the maxim that she is questioning, for adopting 
+this maxim could not have changed her behavior at all. Sara is asking a question about her actions and 
+their validity. Any conclusions about the validity of a vacuous maxim would not help her, first because 
+the maxim has no effect on her action, and second because any such validity would be a foregone conclusion
+as she has already adopted the maxim. As 
 I argued above, no practical reasoner can coherently ask themselves whether a vacuous maxim is 
-valid or not without undermining their decision-making power, which is a contradiction. Thus, under 
+valid or not without undermining their will, which is a contradiction. Thus, under 
 the interpretation of self-doubt as a vacuous maxim, the tension between ESR and ethical self-doubt 
@@
 
-To resolve
-this issue, I turn to another interpretation of ethical self-doubt. Under this interpretation, when Sara
-asks, ``Should I really be dancing right now?" she wants to know if the maxim that 
+To resolve this issue, I turn to another interpretation of ethical self-doubt. Under this interpretation, 
+when Sara asks, ``Should I really be dancing right now?" she wants to know if the maxim that 
 resulted in the current moment when she is on the dance floor was actually 
 the right thing to will. She is asking if she made the right 
-decision in the past, when she decided to dance. The maxim that initiated the dancing would be something like ``When at a wedding, dance for the sake 
-of dancing." This is the maxim that she is currently acting on, not the vacuous maxim ``When dancing, 
-dance for the sake of dancing." Under this interpretation, there is no tension at all between self-doubt 
-and self-respect. It is perfectly valid for a reasoner to doubt their prior moral judgements, just as 
-it is perfectly rational for a believer to doubt their past beliefs \cite[3-4]{christensen}. Such doubt 
-does not undermine the reasoner's decision-making capacity and is thus perfectly consistent with ethical 
-self-respect.
+decision in the past, when she decided to dance. The maxim that initiated the dancing would be something 
+like ``When at a wedding, dance for the sake of dancing." This is the maxim that she is currently acting 
+on, not the vacuous maxim ``When dancing, dance for the sake of dancing." Under this interpretation, 
+there is no tension at all between self-doubt and self-respect. It is perfectly valid for a reasoner 
+to doubt their prior moral judgements, just as it is perfectly rational for a believer to doubt their 
+past beliefs \cite[3-4]{christensen}. Such doubt does not undermine the reasoner's decision-making 
+capacity and is thus perfectly consistent with ethical self-respect.
 
@@
 %:%453=374%:%
-%:%462=378%:%
-%:%474=380%:%
-%:%475=381%:%
-%:%476=382%:%
-%:%477=383%:%
-%:%478=384%:%
+%:%454=375%:%
+%:%455=376%:%
+%:%456=377%:%
+%:%457=378%:%
+%:%458=379%:%
+%:%467=383%:%
 %:%479=385%:%
@@
 %:%519=425%:%
-%:%528=428%:%
-%:%540=431%:%
-%:%541=432%:%
-%:%542=433%:%
-%:%543=434%:%
-%:%544=435%:%
+%:%520=426%:%
+%:%521=427%:%
+%:%522=428%:%
+%:%523=429%:%
+%:%524=430%:%
+%:%533=433%:%
 %:%545=436%:%
@@
 %:%560=451%:%
+%:%561=452%:%
+%:%562=453%:%
+%:%563=454%:%
+%:%564=455%:%
+%:%565=456%:%

### 2021-10-25 paper/output/document/paper41.tex
finished application tests

--- 2021-10-20 paper/output/document/paper41.tex
@@
 \ will\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim\ {\isasymRightarrow}\ s{\isasymRightarrow}\ \ t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}W\ {\isacharunderscore}\ {\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}will\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isachardot}\ {\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}a\ s{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-\isacommand{print{\isacharunderscore}theorems}\isamarkupfalse%
-%
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}will\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isachardot}\ {\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}a\ s{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
 \begin{isamarkuptext}%
@@
 \isacommand{abbreviation}\isamarkupfalse%
-\ universalized{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}t{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
-{\isachardoublequoteopen}universalized\ {\isasymequiv}\ {\isasymlambda}M\ s{\isachardot}\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ W\ M\ p\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ universalized{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}t{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
+{\isachardoublequoteopen}universalized\ {\isasymequiv}\ {\isasymlambda}M{\isachardot}\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ {\isacharparenleft}W\ M\ p{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ holds{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}t{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
+{\isachardoublequoteopen}holds\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}{\isachardot}\ c{\isachardoublequoteclose}\isanewline
 \isanewline
@@
 \ not{\isacharunderscore}universalizable\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
-{\isachardoublequoteopen}not{\isacharunderscore}universalizable\ {\isasymequiv}\ {\isasymlambda}M\ s{\isachardot}\ {\isacharparenleft}{\isasymTurnstile}\ {\isacharparenleft}universalized\ M\ s\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}E\ M\ s{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-%
-\isamarkupcmt{The maxim willed by subject $s$ is not universalizable if, for all people $p$, if $p$ wills M, then 
-$M$ is no longer effective for $s$.%
+{\isachardoublequoteopen}not{\isacharunderscore}universalizable\ {\isasymequiv}\ {\isasymlambda}M\ s{\isachardot}\ {\isasymforall}w{\isachardot}\ {\isacharparenleft}{\isacharparenleft}universalized\ M{\isacharparenright}\ \ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}E\ M\ s{\isacharparenright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{The formula above reads ``at world $w$, if M is universalized and M is acted on (i.e. the circumstances 
+of M hold), then M is not effective."
+
+Notice that the antecedent specifies that the circumstances hold at the given world. 
+When evaluating if a maxim is universalizable or not, we want to ignore worlds where the circumstance 
+do not hold. At these worlds, the maxim is trivially effective and thus trivially universalizable. If we didn't exclude such worlds from 
+consideration, a maxim with circumstances that ever fail to hold would be universalizable. Clearly 
+this is not a desirable conclusion, since maxims like ``When you need money, lie to get easy money"
+would be universalizable.%
 }%
@@
 \begin{isamarkuptext}%
-One problem with prior formalization of the categorical imperative was that they didn't
+One problem with prior formalizations of the categorical imperative was that they didn't
 prohibit contradictory obligations, partially because DDL itself allows contradictory obligations. 
@@
 \isacommand{using}\isamarkupfalse%
-\ O{\isacharunderscore}diamond\ \isanewline
+\ O{\isacharunderscore}diamond\isanewline
 \ \ \isacommand{using}\isamarkupfalse%
-\ prod{\isachardot}simps{\isacharparenleft}{\isadigit{2}}{\isacharparenright}\ split{\isacharunderscore}conv\ \isacommand{by}\isamarkupfalse%
+\ case{\isacharunderscore}prod{\isacharunderscore}conv\ no{\isacharunderscore}contradictions\ old{\isachardot}prod{\isachardot}case\ old{\isachardot}prod{\isachardot}case\ \isacommand{by}\isamarkupfalse%
 \ fastforce%
@@
 \ well{\isacharunderscore}formed{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}i{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
-{\isachardoublequoteopen}well{\isacharunderscore}formed\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ w{\isachardot}\ {\isacharparenleft}{\isasymnot}\ {\isacharparenleft}\ {\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ g{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}\ {\isasymand}\ {\isacharparenleft}{\isasymnot}\ {\isacharparenleft}\ {\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ a\ s{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+{\isachardoublequoteopen}well{\isacharunderscore}formed\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}{\isachardot}\ {\isasymlambda}s{\isachardot}\ {\isasymlambda}w{\isachardot}\ {\isacharparenleft}{\isasymnot}\ \ {\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ g{\isacharparenright}\ w{\isacharparenright}\ {\isasymand}\ {\isacharparenleft}{\isasymnot}\ \ {\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ a\ s{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
 %
@@
 \isacommand{abbreviation}\isamarkupfalse%
-\ FUL\ \isakeyword{where}\ {\isachardoublequoteopen}FUL\ {\isasymequiv}\ {\isasymforall}M{\isacharcolon}{\isacharcolon}maxim{\isachardot}\ {\isasymforall}s{\isacharcolon}{\isacharcolon}s{\isachardot}\ {\isacharparenleft}{\isasymforall}w{\isachardot}\ well{\isacharunderscore}formed\ M\ s\ w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}not{\isacharunderscore}universalizable\ M\ s\ {\isasymlongrightarrow}\ {\isasymTurnstile}\ prohibited\ M\ s\ {\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ FUL\ \isakeyword{where}\ {\isachardoublequoteopen}FUL\ {\isasymequiv}\ {\isasymforall}M{\isacharcolon}{\isacharcolon}maxim{\isachardot}\ {\isasymforall}s{\isacharcolon}{\isacharcolon}s{\isachardot}\ {\isacharparenleft}{\isasymforall}w{\isachardot}\ well{\isacharunderscore}formed\ M\ s\ w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}not{\isacharunderscore}universalizable\ M\ s\ {\isasymlongrightarrow}\ {\isasymTurnstile}\ {\isacharparenleft}prohibited\ M\ s{\isacharparenright}\ {\isacharparenright}{\isachardoublequoteclose}\isanewline
 %
@@
 %
+\begin{isamarkuptext}%
+I will show that the maxim, ``When strapped for cash, falsely promise to pay your friend back
+to get some easy money." is prohibited. This example is due to Korsgaard and she uses it to highlight 
+the strength of her preferred interpretation of the FUL, the practical contradiction interpretation \cite{KorsgaardFUL}.
+There are two possible readings of this maxim, and I will show that my formalization can handle both. 
+Under the first reading, the act of falsely promising is read as
+as entering a pre-existing, implicit, social system of promising with no intention of upholding your 
+promise. Under the second reading, the act of falsely promising is equivalent to uttering the worlds 
+``I promise X" without intending to do X. The differences between these readings lies in the difference 
+between promising as an act with meaning in a larger social structure and the utterance ``I promise."
+
+Under the first reading, the maxim fails because falsely promising is no longer possible in a world where 
+everyone everyone does so. This is how the logical contradiction interpretation reads this maxim—falsely 
+promising is no longer possible when universalized because the institution of promising breaks down. 
+The practical contradiction view also prohibits this maxim because if falsely promising is not longer 
+possible, then it is no longer an effective way to achieve the end of getting some money. Below I 
+define some logical tools to formalize this reading of this maxim.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{consts}\isamarkupfalse%
+\ when{\isacharunderscore}strapped{\isacharunderscore}for{\isacharunderscore}cash{\isacharcolon}{\isacharcolon}t\isanewline
+%
+\isamarkupcmt{Constant representing the circumstances ``when strapped for cash." Recall that the type of circumstances 
+is a term because circumstances can be true or false at a world.%
+}\isanewline
+\isacommand{consts}\isamarkupfalse%
+\ falsely{\isacharunderscore}promise{\isacharcolon}{\isacharcolon}os\isanewline
+%
+\isamarkupcmt{Constant representing the act ``make a false promise to pay a loan back." Recall that the type of
+an act is an open sentence because the sentence ``subject s performs act a" can be true or false at a world.%
+}\isanewline
+\isacommand{consts}\isamarkupfalse%
+\ to{\isacharunderscore}get{\isacharunderscore}easy{\isacharunderscore}cash{\isacharcolon}{\isacharcolon}t\isanewline
+%
+\isamarkupcmt{Constant representing the goal ``to get some money." Recall that the type of a goal 
+is a term because a goal can be true or false at a world depending on whether it is achieved or not.%
+}\isanewline
+\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ false{\isacharunderscore}promising{\isacharcolon}{\isacharcolon}maxim\ \isakeyword{where}\ \isanewline
+{\isachardoublequoteopen}false{\isacharunderscore}promising\ {\isasymequiv}\ {\isacharparenleft}when{\isacharunderscore}strapped{\isacharunderscore}for{\isacharunderscore}cash{\isacharcomma}\ falsely{\isacharunderscore}promise{\isacharcomma}\ to{\isacharunderscore}get{\isacharunderscore}easy{\isacharunderscore}cash{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Armed with the circumstances, act, and goal above, I can define the example maxim as a tuple.%
+}%
+\begin{isamarkuptext}%
+The logical objects above are ``empty," in the sense that I haven't specified any of their 
+relevant properties. I will define these properties as assumptions and will show that, if the maxim 
+above satisfies the assumed properties, it is prohibited.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{abbreviation}\isamarkupfalse%
+\ everyone{\isacharunderscore}can{\isacharprime}t{\isacharunderscore}lie\ \isakeyword{where}\ \isanewline
+{\isachardoublequoteopen}everyone{\isacharunderscore}can{\isacharprime}t{\isacharunderscore}lie\ {\isasymequiv}\ {\isasymforall}w{\isachardot}\ {\isasymnot}\ {\isacharparenleft}{\isasymforall}s{\isachardot}\ falsely{\isacharunderscore}promise{\isacharparenleft}s{\isacharparenright}\ w{\isacharparenright}\ {\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Under this reading, the problem with this maxim is that everyone can't
+falsely promise simultaneously because the institution of promising will break down. It's probably 
+possible to say something stronger than this (i.e. that if enough but not necessarily all people
+falsely promise promising is no longer possible), but for my purposes this will suffice. The above 
+formula reads, ``At all worlds, it is not the case that everyone falsely promises."%
+}\isanewline
+\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ circumstances{\isacharunderscore}hold\ \isakeyword{where}\ \isanewline
+{\isachardoublequoteopen}circumstances{\isacharunderscore}hold\ {\isasymequiv}\ {\isasymforall}w{\isachardot}\ when{\isacharunderscore}strapped{\isacharunderscore}for{\isacharunderscore}cash\ w{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{This assumption narrows our scope of consideration to worlds where the circumstances of 
+being strapped for cash hold. This is important because, at worlds where the circumstances do not hold, 
+a maxim is trivially effective (since it's never acted on) and thus trivially universalizable. This 
+assumption also makes practical sense; when evaluating a maxim, an agent would care about it specifically
+at worlds where the circumstances hold, since these are the worlds where the maxim actually prescribes action.%
+}\isanewline
+\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ example{\isacharunderscore}is{\isacharunderscore}well{\isacharunderscore}formed\ \isakeyword{where}\ \isanewline
+{\isachardoublequoteopen}example{\isacharunderscore}is{\isacharunderscore}well{\isacharunderscore}formed\ {\isasymequiv}\ {\isasymforall}s{\isachardot}\ {\isasymTurnstile}\ {\isacharparenleft}well{\isacharunderscore}formed\ false{\isacharunderscore}promising\ s{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{This assumption states that the maxim of falsely promising is well-formed. This breaks down into
+two individual assumptions. First, being strapped for cash can't imply falsely promising, which is plausible
+because many people won't falsely promise under conditions of poverty. Second, being strapped for cash
+can't imply getting ready cash, which is also plausible because people often fail to secure cash even 
+when they need it.%
+}%
+\begin{isamarkuptext}%
+Putting it all together, I want to show that if the three assumptions justified above hold, then 
+the constructed maxim is prohibited. Below is the proof%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ lying{\isacharunderscore}bad{\isacharunderscore}{\isadigit{1}}{\isacharcolon}\isanewline
+\ \ \isakeyword{assumes}\ everyone{\isacharunderscore}can{\isacharprime}t{\isacharunderscore}lie\isanewline
+\ \ \isakeyword{assumes}\ circumstances{\isacharunderscore}hold\isanewline
+\ \ \isakeyword{assumes}\ example{\isacharunderscore}is{\isacharunderscore}well{\isacharunderscore}formed\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}s{\isachardot}\ {\isasymTurnstile}\ {\isacharparenleft}prohibited\ false{\isacharunderscore}promising\ s{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+\isacommand{proof}\isamarkupfalse%
+{\isacharminus}\isanewline
+\ \ \isacommand{have}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isasymforall}s{\isachardot}\ not{\isacharunderscore}universalizable\ false{\isacharunderscore}promising\ s{\isachardoublequoteclose}\isanewline
+\ \ \ \ \isacommand{by}\isamarkupfalse%
+\ {\isacharparenleft}simp\ add{\isacharcolon}\ assms{\isacharparenleft}{\isadigit{1}}{\isacharparenright}\ assms{\isacharparenleft}{\isadigit{2}}{\isacharparenright}{\isacharparenright}\isanewline
+%
+\isamarkupcmt{I manually broke the proof into this intermediate lemma and the conclusion, and then Sledgehammer 
+automatically found a proof.%
+}\isanewline
+\ \ \isacommand{thus}\isamarkupfalse%
+\ {\isacharquery}thesis\isanewline
+\ \ \ \ \isacommand{using}\isamarkupfalse%
+\ FUL\ assms{\isacharparenleft}{\isadigit{3}}{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
+\ blast\ \isanewline
+\isacommand{qed}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+Under the second reading of this maxim, the act ``falsely promising" refers to uttering the 
+sentence ``I promise to do X" with no intention of actually doing X\footnote{Note that under this 
+reading, the maxim isn't prohibited under the logical contradiction interpretation because making an 
+utterance is still possible even if eveyrone else makes that utterance. I will discuss this in detail 
+later in this section in the context of the difference between natural and conventional acts.}. 
+Under this reading, the practical contradiction interpretation prohibits this maxim because, in a world 
+where false promising is universalized, no one believes promises anymore, so the utterance is no longer 
+an effective way to get money. Below I formalize this reading of this maixm.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{consts}\isamarkupfalse%
+\ believed{\isacharcolon}{\isacharcolon}os\ \isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ false{\isacharunderscore}promising{\isacharunderscore}not{\isacharunderscore}believed\ \isakeyword{where}\ \isanewline
+{\isachardoublequoteopen}false{\isacharunderscore}promising{\isacharunderscore}not{\isacharunderscore}believed\ {\isasymequiv}\ {\isasymforall}w\ s{\isachardot}\ {\isacharparenleft}falsely{\isacharunderscore}promise{\isacharparenleft}s{\isacharparenright}\ w\ {\isasymlongrightarrow}\ {\isasymnot}\ believed{\isacharparenleft}s{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{This abbreviation formalizes the idea that if everyone falsely promises, then no one is believed
+when promising.%
+}\isanewline
+\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ need{\isacharunderscore}to{\isacharunderscore}be{\isacharunderscore}believed\ \isakeyword{where}\ \isanewline
+{\isachardoublequoteopen}need{\isacharunderscore}to{\isacharunderscore}be{\isacharunderscore}believed\ {\isasymequiv}\ {\isasymforall}w\ s{\isachardot}\ {\isacharparenleft}{\isasymnot}\ believed{\isacharparenleft}s{\isacharparenright}\ w\ {\isasymlongrightarrow}\ \isactrlbold {\isasymnot}{\isacharparenleft}{\isacharparenleft}falsely{\isacharunderscore}promise\ s{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ to{\isacharunderscore}get{\isacharunderscore}easy{\isacharunderscore}cash{\isacharparenright}w{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{This abbreviation formalizes the idea that if a promise is not believed, then it is not an effective
+way of getting easy cash.%
+}\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ falsely{\isacharunderscore}promising{\isacharunderscore}bad{\isacharunderscore}{\isadigit{2}}{\isacharcolon}\isanewline
+\ \ \isakeyword{assumes}\ false{\isacharunderscore}promising{\isacharunderscore}not{\isacharunderscore}believed\isanewline
+\ \ \isakeyword{assumes}\ need{\isacharunderscore}to{\isacharunderscore}be{\isacharunderscore}believed\isanewline
+%
+\isamarkupcmt{The above two assumptions are specific to this reading and justified above.%
+}\isanewline
+\ \ \isakeyword{assumes}\ circumstances{\isacharunderscore}hold\isanewline
+\ \ \isakeyword{assumes}\ example{\isacharunderscore}is{\isacharunderscore}well{\isacharunderscore}formed\isanewline
+%
+\isamarkupcmt{These two assumptions applied to the first reading as well and were justified there.%
+}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}s{\isachardot}\ {\isasymTurnstile}\ {\isacharparenleft}prohibited\ false{\isacharunderscore}promising\ s{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+\isacommand{proof}\isamarkupfalse%
+{\isacharminus}\isanewline
+\ \ \isacommand{have}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isasymforall}s{\isachardot}\ not{\isacharunderscore}universalizable\ false{\isacharunderscore}promising\ s{\isachardoublequoteclose}\isanewline
+\ \ \ \ \isacommand{using}\isamarkupfalse%
+\ assms{\isacharparenleft}{\isadigit{1}}{\isacharparenright}\ assms{\isacharparenleft}{\isadigit{2}}{\isacharparenright}\ assms{\isacharparenleft}{\isadigit{3}}{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
+\ auto\isanewline
+\ \ \isacommand{thus}\isamarkupfalse%
+\ {\isacharquery}thesis\isanewline
+\ \ \ \ \isacommand{using}\isamarkupfalse%
+\ FUL\ assms{\isacharparenleft}{\isadigit{4}}{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
+\ blast\isanewline
+\isacommand{qed}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{With some help, Isabelle is able to show that the maxim is prohibited under this reading as well.%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+This example demonstrates that my formalization is able to correctly prohibit this maxim, regardless
+of its reading. This is additionally important because the two readings of this maxim represent reading 
+the act as either a conventional or natural action, so my intrepretation can correctly handle both kinds
+of actions. Korsgaard draws a distinction between conventional acts and natural acts. Conventional acts 
+exist within a practice, which is "comprised of certain rules, and its existence (where it is not embodied in 
+an institution with sanctions) consists in the general acknowledgement and following of those rules" 
+\cite[10]{KorsgaardFUL}. For example, promising is a conventional act because it only exists as a 
+practice. Murder, on the other hand, is an example of a natural act because its existence only depends
+on the laws of nature\cite[11]{KorsgaardFUL}.
+
+This distinction is important because Korsgaard argues that only the practical contradiction view can 
+satisfactorily explain the wrongness of certain natural acts like murder\footnote{For more discussion 
+of Korsgaard's argument for the practical contradiction view, see Section Philosophical Writing}. 
+The practical contradiction view is thus stronger than the logical contradiction view because it can 
+explain the wrongness of both conventional and natural acts.
+
+The fact that my interpretation can correctly show the wrongness of both conventional and natural acts
+is evidence for its correctness as a formalization of the practical contradiction interpretation. 
+The first reading of the example maxim reads the act 
+``making a false promise" as entering into an agreement within a socially established system of promising. 
+This is clearly a conventional act, and because it is a conventional act, it is not just contradictory
+when universalized but literally impossible because the practice breaks down. I capture this idea in the 
+assumption \isa{everyone{\isacharunderscore}can{\isacharprime}t{\isacharunderscore}lie\ {\isasymequiv}\ {\isasymforall}w{\isachardot}\ {\isasymnot}\ {\isacharparenleft}{\isasymforall}s{\isachardot}\ falsely{\isacharunderscore}promise\ s\ w{\isacharparenright}}, which states that, at all worlds, not everyone can falsely promise since
+otherwise the practice of promising would break down. The second reading, on the other hand, reads the 
+act of making a false promise as uttering the statement ``I promise to pay you back," while never intending 
+to fulfill this promise. This is a natural act because the act of uttering a sentence does not rely 
+on any conventions, merely the laws of nature governing how your mouth and vocal cords behave\footnote{
+Linguistic relativists may take issue with this claim and may argue that if the English language had 
+never developed, then making this utterance would be impossible. Even if this is true, the laws of 
+nature itself would not prohibit making the sounds corresponding to the English pronounciation of 
+this phrase, so the act would still not be impossible in the way that a conventional act can be.}
+
+I show above that my formalization shows the wrongness of this maxim under both readings. Under the 
+first reading, promising becomes impossible, so both the logical and 
+practical contradiction interpretations prohibit the maxim. Under the second reading, promising is still
+possible, but becomes ineffective because people no longer interpret the utterance as creating a commitment.
+Under this view, only the practical contradiction interpretation succeeds in prohibiting the maxim. Thus, 
+not only does my formalization likely capture the practical contradiction interpretation (as opposed to 
+the teleological or logical contradiction interpretations), it also adequately handles both natural 
+and conventional acts.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+I can also use Isabelle to confirm that the two readings are different. If they were the same, 
+we would expect the assumptions corresponing to each to be equivalent. The RHS of the lemma below represents 
+the second reading and the LHS represents the first reading.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ readings{\isacharunderscore}are{\isacharunderscore}equivalent{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}false{\isacharunderscore}promising{\isacharunderscore}not{\isacharunderscore}believed\ {\isasymand}\ need{\isacharunderscore}to{\isacharunderscore}be{\isacharunderscore}believed\ {\isasymequiv}\ everyone{\isacharunderscore}can{\isacharprime}t{\isacharunderscore}lie{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{Nitpick finds a counterexample, showing that the two readings are different.
+\color{blue}
+Nitpick found a counterexample for card i = 1 and card s = 1:
+
+  Empty assignment
+\color{black}%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+This completes the application tests for my formalization. I showed that my formalization correctly 
+handles an example from Korsgaard with two possible interpretations and also sufficiently handles both 
+conventional and natural acts.%
+\end{isamarkuptext}\isamarkuptrue%
+%
 \isadelimdocument
@@
 %
-\isamarkupcmt{\color{blue}Nitpick found a model for card i = 1 and card s = 2:
+\isamarkupcmt{\color{blue}Nitpick found a model for card i = 1 and card s = 1:
 
   Free variables:
-    a = ($\lambda x. \_$)($s_1$ := ($\lambda x. \_$)($i_1$ := False), $s_2$ := ($\lambda x. \_$)($i_1$ := False))
+    a = ($\lambda x. \_$)($s_1$ := ($\lambda x. \_$)($i_1$ := False))
     c = ($\lambda x. \_$)($i_1$ := False)
     g = ($\lambda x. \_$)($i_1$ := False)
-    s = $s_2$\color{black}
+    s = $s_1$\color{black}
 Recall that Nitpick is a model checker that finds models making certain formulae true or false. In this 
@@
 \ obligated{\isacharunderscore}then{\isacharunderscore}permissible{\isacharcolon}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}O{\isacharbraceleft}W{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharbar}c{\isacharbraceright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}permissible\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}{\isacharparenright}\ s{\isacharparenright}\ w\ {\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}O{\isacharbraceleft}W{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharbar}c{\isacharbraceright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isacharparenleft}permissible\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ {\isacharparenright}\ s{\isacharparenright}{\isacharparenright}\ w\ {\isachardoublequoteclose}\isanewline
 %
@@
 \isamarkupcmt{\color{blue}
-Nitpick found a counterexample for card i = 1 and card s = 1:
+Nitpick found a counterexample for card i = 1 and card s = 2:
 
   Free variables:
-    a = ($\lambda x. \_$)($s_1$ := ($\lambda x. \_$)($i_1$ := False))
+    a = ($\lambda x. \_$)($s_1$ := ($\lambda x. \_$)($i_1$ := False), $s_2$ := ($\lambda x. \_$)($i_1$ := False))
     c = ($\lambda x. \_$)($i_1$ := False)
     g = ($\lambda x. \_$)($i_1$ := False)
-    s = $s_1$
+    s = $s_2$
     w = undefined
@@
 %:%188=135%:%
-%:%189=136%:%
-%:%192=138%:%
-%:%193=139%:%
-%:%194=140%:%
-%:%195=141%:%
-%:%196=142%:%
-%:%197=143%:%
-%:%198=144%:%
-%:%199=145%:%
-%:%200=146%:%
-%:%201=147%:%
-%:%202=148%:%
-%:%203=149%:%
-%:%204=150%:%
-%:%205=151%:%
-%:%206=152%:%
-%:%207=153%:%
-%:%208=154%:%
-%:%209=155%:%
-%:%210=156%:%
-%:%211=157%:%
-%:%212=158%:%
-%:%213=159%:%
-%:%214=160%:%
-%:%215=161%:%
-%:%216=162%:%
-%:%217=163%:%
-%:%218=164%:%
-%:%219=165%:%
-%:%220=166%:%
-%:%221=167%:%
-%:%222=168%:%
-%:%223=169%:%
-%:%224=170%:%
-%:%225=171%:%
-%:%226=172%:%
-%:%227=173%:%
-%:%228=174%:%
-%:%229=175%:%
-%:%230=176%:%
-%:%231=177%:%
-%:%232=178%:%
-%:%233=179%:%
-%:%234=180%:%
-%:%235=181%:%
-%:%236=182%:%
+%:%190=137%:%
+%:%191=138%:%
+%:%192=139%:%
+%:%193=140%:%
+%:%194=141%:%
+%:%195=142%:%
+%:%196=143%:%
+%:%197=144%:%
+%:%198=145%:%
+%:%199=146%:%
+%:%200=147%:%
+%:%201=148%:%
+%:%202=149%:%
+%:%203=150%:%
+%:%204=151%:%
+%:%205=152%:%
+%:%206=153%:%
+%:%207=154%:%
+%:%208=155%:%
+%:%209=156%:%
+%:%210=157%:%
+%:%211=158%:%
+%:%212=159%:%
+%:%213=160%:%
+%:%214=161%:%
+%:%215=162%:%
+%:%216=163%:%
+%:%217=164%:%
+%:%218=165%:%
+%:%219=166%:%
+%:%220=167%:%
+%:%221=168%:%
+%:%222=169%:%
+%:%223=170%:%
+%:%224=171%:%
+%:%225=172%:%
+%:%226=173%:%
+%:%227=174%:%
+%:%228=175%:%
+%:%229=176%:%
+%:%230=177%:%
+%:%231=178%:%
+%:%232=179%:%
+%:%233=180%:%
+%:%234=181%:%
+%:%236=184%:%
+%:%237=184%:%
 %:%238=185%:%
-%:%239=185%:%
-%:%240=186%:%
-%:%241=187%:%
-%:%244=189%:%
-%:%245=190%:%
-%:%246=191%:%
-%:%247=192%:%
-%:%248=193%:%
-%:%249=194%:%
-%:%250=195%:%
-%:%251=196%:%
-%:%252=197%:%
-%:%253=198%:%
-%:%254=199%:%
-%:%255=200%:%
-%:%256=201%:%
-%:%257=202%:%
-%:%258=203%:%
-%:%259=204%:%
-%:%260=205%:%
-%:%261=206%:%
-%:%262=207%:%
-%:%263=208%:%
-%:%264=209%:%
+%:%239=186%:%
+%:%242=188%:%
+%:%243=189%:%
+%:%244=190%:%
+%:%245=191%:%
+%:%246=192%:%
+%:%247=193%:%
+%:%248=194%:%
+%:%249=195%:%
+%:%250=196%:%
+%:%251=197%:%
+%:%252=198%:%
+%:%253=199%:%
+%:%254=200%:%
+%:%255=201%:%
+%:%256=202%:%
+%:%257=203%:%
+%:%258=204%:%
+%:%259=205%:%
+%:%260=206%:%
+%:%261=207%:%
+%:%262=208%:%
+%:%264=210%:%
+%:%265=210%:%
 %:%266=211%:%
-%:%267=211%:%
-%:%268=212%:%
+%:%267=212%:%
+%:%268=213%:%
 %:%269=213%:%
 %:%270=214%:%
-%:%271=214%:%
-%:%272=215%:%
-%:%274=216%:%
-%:%275=217%:%
-%:%278=219%:%
-%:%279=220%:%
-%:%280=221%:%
-%:%281=222%:%
-%:%282=223%:%
-%:%283=224%:%
-%:%284=225%:%
-%:%285=226%:%
+%:%271=215%:%
+%:%272=216%:%
+%:%273=216%:%
+%:%274=217%:%
+%:%276=218%:%
+%:%277=219%:%
+%:%278=220%:%
+%:%279=221%:%
+%:%280=222%:%
+%:%281=223%:%
+%:%282=224%:%
+%:%283=225%:%
+%:%284=226%:%
 %:%287=228%:%
-%:%288=228%:%
-%:%289=229%:%
-%:%290=230%:%
-%:%291=231%:%
-%:%292=231%:%
-%:%293=232%:%
-%:%295=233%:%
-%:%296=234%:%
-%:%299=236%:%
-%:%300=237%:%
-%:%301=238%:%
-%:%302=239%:%
-%:%303=240%:%
-%:%304=241%:%
-%:%305=242%:%
-%:%306=243%:%
-%:%307=244%:%
+%:%288=229%:%
+%:%289=230%:%
+%:%290=231%:%
+%:%291=232%:%
+%:%292=233%:%
+%:%293=234%:%
+%:%294=235%:%
+%:%296=237%:%
+%:%297=237%:%
+%:%298=238%:%
+%:%299=239%:%
+%:%300=240%:%
+%:%301=240%:%
+%:%302=241%:%
+%:%304=242%:%
+%:%305=243%:%
 %:%308=245%:%
@@
 %:%323=260%:%
+%:%324=261%:%
 %:%325=262%:%
-%:%326=262%:%
-%:%327=263%:%
-%:%329=264%:%
-%:%330=265%:%
-%:%331=265%:%
-%:%332=266%:%
-%:%333=267%:%
-%:%334=267%:%
-%:%336=268%:%
-%:%337=269%:%
-%:%338=270%:%
-%:%346=272%:%
-%:%358=274%:%
-%:%359=275%:%
-%:%360=276%:%
-%:%361=277%:%
-%:%362=278%:%
-%:%363=279%:%
-%:%365=282%:%
-%:%366=282%:%
-%:%368=283%:%
-%:%369=284%:%
-%:%370=285%:%
-%:%371=286%:%
-%:%372=286%:%
-%:%373=287%:%
-%:%374=288%:%
-%:%375=288%:%
-%:%377=288%:%
-%:%381=288%:%
-%:%382=288%:%
-%:%383=289%:%
-%:%384=289%:%
-%:%385=289%:%
-%:%394=291%:%
-%:%395=292%:%
-%:%396=293%:%
-%:%397=294%:%
-%:%398=295%:%
-%:%399=296%:%
-%:%400=297%:%
-%:%401=298%:%
-%:%402=299%:%
+%:%326=263%:%
+%:%327=264%:%
+%:%328=265%:%
+%:%329=266%:%
+%:%330=267%:%
+%:%331=268%:%
+%:%332=269%:%
+%:%334=271%:%
+%:%335=271%:%
+%:%336=272%:%
+%:%338=273%:%
+%:%339=274%:%
+%:%340=274%:%
+%:%341=275%:%
+%:%342=276%:%
+%:%343=276%:%
+%:%345=277%:%
+%:%346=278%:%
+%:%347=279%:%
+%:%355=281%:%
+%:%367=283%:%
+%:%368=284%:%
+%:%369=285%:%
+%:%370=286%:%
+%:%371=287%:%
+%:%372=288%:%
+%:%374=291%:%
+%:%375=291%:%
+%:%377=292%:%
+%:%378=293%:%
+%:%379=294%:%
+%:%380=295%:%
+%:%381=295%:%
+%:%382=296%:%
+%:%383=297%:%
+%:%384=297%:%
+%:%386=297%:%
+%:%390=297%:%
+%:%391=297%:%
+%:%392=298%:%
+%:%393=298%:%
+%:%394=298%:%
 %:%403=300%:%
@@
 %:%410=307%:%
+%:%411=308%:%
 %:%412=309%:%
-%:%413=309%:%
-%:%414=310%:%
-%:%416=311%:%
-%:%417=312%:%
-%:%418=312%:%
-%:%419=313%:%
-%:%420=314%:%
-%:%421=314%:%
-%:%423=315%:%
-%:%424=316%:%
-%:%425=316%:%
-%:%426=317%:%
-%:%427=318%:%
-%:%428=318%:%
-%:%429=319%:%
-%:%430=319%:%
-%:%432=319%:%
-%:%436=319%:%
-%:%437=319%:%
-%:%439=320%:%
-%:%440=321%:%
-%:%441=322%:%
-%:%442=323%:%
-%:%443=324%:%
-%:%444=325%:%
-%:%445=326%:%
-%:%446=327%:%
-%:%447=328%:%
+%:%413=310%:%
+%:%414=311%:%
+%:%415=312%:%
+%:%416=313%:%
+%:%417=314%:%
+%:%418=315%:%
+%:%419=316%:%
+%:%421=318%:%
+%:%422=318%:%
+%:%423=319%:%
+%:%425=320%:%
+%:%426=321%:%
+%:%427=321%:%
+%:%428=322%:%
+%:%429=323%:%
+%:%430=323%:%
+%:%432=324%:%
+%:%433=325%:%
+%:%434=325%:%
+%:%435=326%:%
+%:%436=327%:%
+%:%437=327%:%
+%:%438=328%:%
+%:%439=328%:%
+%:%441=328%:%
+%:%445=328%:%
+%:%446=328%:%
 %:%448=329%:%
 %:%449=330%:%
-%:%457=330%:%
-%:%458=331%:%
-%:%459=332%:%
-%:%460=332%:%
-%:%461=333%:%
-%:%462=334%:%
-%:%463=334%:%
-%:%464=335%:%
-%:%465=335%:%
-%:%467=335%:%
-%:%471=335%:%
-%:%472=335%:%
-%:%474=336%:%
-%:%475=337%:%
-%:%476=338%:%
-%:%477=339%:%
-%:%478=340%:%
-%:%479=341%:%
-%:%489=343%:%
-%:%490=344%:%
-%:%491=345%:%
-%:%492=346%:%
-%:%493=347%:%
-%:%494=348%:%
-%:%495=349%:%
-%:%496=350%:%
-%:%497=351%:%
+%:%450=331%:%
+%:%451=332%:%
+%:%452=333%:%
+%:%453=334%:%
+%:%454=335%:%
+%:%455=336%:%
+%:%456=337%:%
+%:%457=338%:%
+%:%458=339%:%
+%:%466=339%:%
+%:%467=340%:%
+%:%468=341%:%
+%:%469=341%:%
+%:%470=342%:%
+%:%471=343%:%
+%:%472=343%:%
+%:%473=344%:%
+%:%474=344%:%
+%:%476=344%:%
+%:%480=344%:%
+%:%481=344%:%
+%:%483=345%:%
+%:%484=346%:%
+%:%485=347%:%
+%:%486=348%:%
+%:%487=349%:%
+%:%488=350%:%
 %:%498=352%:%
@@
 %:%508=362%:%
-%:%512=364%:%
-%:%513=365%:%
-%:%514=366%:%
-%:%515=367%:%
-%:%516=368%:%
-%:%525=370%:%
-%:%537=372%:%
-%:%538=373%:%
-%:%539=374%:%
-%:%540=375%:%
-%:%549=378%:%
-%:%561=380%:%
-%:%562=381%:%
-%:%563=382%:%
-%:%564=383%:%
-%:%565=384%:%
-%:%566=385%:%
-%:%567=386%:%
-%:%568=387%:%
-%:%569=388%:%
-%:%570=389%:%
-%:%571=390%:%
-%:%572=391%:%
-%:%573=392%:%
-%:%574=393%:%
-%:%575=394%:%
-%:%576=395%:%
-%:%577=396%:%
-%:%578=397%:%
-%:%579=398%:%
-%:%580=399%:%
-%:%582=401%:%
-%:%583=401%:%
-%:%584=402%:%
-%:%587=403%:%
-%:%591=403%:%
-%:%592=403%:%
-%:%597=403%:%
-%:%600=404%:%
-%:%601=405%:%
-%:%602=405%:%
-%:%603=406%:%
-%:%606=407%:%
-%:%610=407%:%
-%:%611=407%:%
-%:%616=407%:%
-%:%619=408%:%
-%:%620=409%:%
-%:%621=409%:%
-%:%622=410%:%
-%:%625=411%:%
-%:%629=411%:%
-%:%630=411%:%
-%:%635=411%:%
-%:%638=412%:%
-%:%639=413%:%
-%:%640=413%:%
-%:%641=414%:%
-%:%644=415%:%
-%:%648=415%:%
-%:%649=415%:%
-%:%658=417%:%
-%:%659=418%:%
-%:%660=419%:%
-%:%661=420%:%
-%:%662=421%:%
-%:%663=422%:%
-%:%664=423%:%
-%:%666=425%:%
-%:%667=425%:%
-%:%668=426%:%
-%:%669=427%:%
-%:%670=427%:%
-%:%672=427%:%
-%:%676=427%:%
-%:%677=427%:%
-%:%679=428%:%
-%:%680=429%:%
-%:%681=430%:%
-%:%682=431%:%
-%:%683=432%:%
-%:%684=433%:%
-%:%685=434%:%
-%:%686=435%:%
-%:%687=436%:%
-%:%688=437%:%
-%:%689=438%:%
-%:%699=440%:%
-%:%700=441%:%
-%:%702=443%:%
-%:%703=443%:%
-%:%704=444%:%
-%:%707=445%:%
-%:%711=445%:%
-%:%712=445%:%
-%:%714=446%:%
-%:%724=448%:%
-%:%725=449%:%
-%:%727=451%:%
-%:%728=451%:%
-%:%729=452%:%
-%:%732=453%:%
-%:%736=453%:%
-%:%737=453%:%
-%:%738=453%:%
-%:%740=454%:%
-%:%741=455%:%
-%:%751=457%:%
-%:%752=458%:%
-%:%753=459%:%
-%:%754=460%:%
-%:%755=461%:%
-%:%756=462%:%
-%:%757=463%:%
-%:%758=464%:%
-%:%759=465%:%
-%:%760=466%:%
-%:%761=467%:%
-%:%762=468%:%
-%:%766=470%:%
-%:%767=471%:%
-%:%768=472%:%
-%:%770=474%:%
-%:%771=474%:%
-%:%772=475%:%
-%:%773=476%:%
-%:%774=477%:%
-%:%775=477%:%
-%:%777=477%:%
-%:%781=477%:%
-%:%782=477%:%
-%:%784=478%:%
-%:%785=479%:%
-%:%786=480%:%
-%:%787=481%:%
-%:%788=482%:%
-%:%789=483%:%
-%:%790=484%:%
-%:%791=485%:%
-%:%792=486%:%
-%:%793=487%:%
-%:%803=489%:%
-%:%804=490%:%
-%:%805=491%:%
-%:%807=493%:%
-%:%808=493%:%
-%:%809=494%:%
-%:%810=495%:%
-%:%811=495%:%
-%:%813=495%:%
-%:%817=495%:%
-%:%818=495%:%
-%:%820=496%:%
-%:%821=497%:%
-%:%822=498%:%
-%:%823=499%:%
-%:%824=500%:%
-%:%825=501%:%
-%:%826=502%:%
-%:%827=503%:%
-%:%828=504%:%
-%:%829=505%:%
-%:%839=507%:%
-%:%840=508%:%
-%:%841=509%:%
-%:%842=510%:%
-%:%844=512%:%
-%:%845=512%:%
-%:%846=513%:%
-%:%849=514%:%
-%:%853=514%:%
-%:%854=514%:%
-%:%855=514%:%
-%:%857=515%:%
-%:%863=515%:%
-%:%866=516%:%
-%:%867=517%:%
-%:%868=517%:%
-%:%869=518%:%
-%:%872=519%:%
-%:%876=519%:%
-%:%877=519%:%
-%:%878=519%:%
-%:%880=520%:%
-%:%886=520%:%
-%:%889=521%:%
-%:%890=522%:%
-%:%891=522%:%
-%:%892=523%:%
-%:%893=524%:%
-%:%896=525%:%
-%:%900=525%:%
-%:%901=525%:%
-%:%902=525%:%
-%:%904=526%:%
-%:%905=527%:%
-%:%915=529%:%
-%:%916=530%:%
-%:%917=531%:%
-%:%918=532%:%
-%:%919=533%:%
-%:%920=534%:%
-%:%921=535%:%
-%:%930=537%:%
-%:%942=539%:%
-%:%943=540%:%
-%:%944=541%:%
-%:%945=542%:%
-%:%947=544%:%
-%:%948=544%:%
-%:%949=545%:%
-%:%950=546%:%
-%:%951=546%:%
-%:%953=546%:%
-%:%957=546%:%
-%:%958=546%:%
-%:%960=547%:%
-%:%961=548%:%
-%:%962=549%:%
-%:%963=550%:%
-%:%964=551%:%
-%:%965=552%:%
-%:%966=553%:%
-%:%967=554%:%
-%:%968=555%:%
-%:%969=556%:%
-%:%970=557%:%
-%:%971=557%:%
+%:%509=363%:%
+%:%510=364%:%
+%:%511=365%:%
+%:%512=366%:%
+%:%513=367%:%
+%:%514=368%:%
+%:%515=369%:%
+%:%516=370%:%
+%:%517=371%:%
+%:%521=373%:%
+%:%522=374%:%
+%:%523=375%:%
+%:%524=376%:%
+%:%525=377%:%
+%:%534=379%:%
+%:%546=381%:%
+%:%547=382%:%
+%:%548=383%:%
+%:%549=384%:%
+%:%553=386%:%
+%:%554=387%:%
+%:%555=388%:%
+%:%556=389%:%
+%:%557=390%:%
+%:%558=391%:%
+%:%559=392%:%
+%:%560=393%:%
+%:%561=394%:%
+%:%562=395%:%
+%:%563=396%:%
+%:%564=397%:%
+%:%565=398%:%
+%:%566=399%:%
+%:%567=400%:%
+%:%568=401%:%
+%:%570=403%:%
+%:%571=403%:%
+%:%573=404%:%
+%:%574=405%:%
+%:%575=405%:%
+%:%576=406%:%
+%:%577=406%:%
+%:%579=407%:%
+%:%580=408%:%
+%:%581=408%:%
+%:%582=409%:%
+%:%583=409%:%
+%:%585=410%:%
+%:%586=411%:%
+%:%587=411%:%
+%:%588=412%:%
+%:%589=413%:%
+%:%590=413%:%
+%:%591=414%:%
+%:%593=415%:%
+%:%596=417%:%
+%:%597=418%:%
+%:%598=419%:%
+%:%600=421%:%
+%:%601=421%:%
+%:%602=422%:%
+%:%604=423%:%
+%:%605=424%:%
+%:%606=425%:%
+%:%607=426%:%
+%:%608=427%:%
+%:%609=427%:%
+%:%610=428%:%
+%:%611=429%:%
+%:%612=429%:%
+%:%613=430%:%
+%:%615=431%:%
+%:%616=432%:%
+%:%617=433%:%
+%:%618=434%:%
+%:%619=435%:%
+%:%620=435%:%
+%:%621=436%:%
+%:%622=437%:%
+%:%623=437%:%
+%:%624=438%:%
+%:%626=439%:%
+%:%627=440%:%
+%:%628=441%:%
+%:%629=442%:%
+%:%630=443%:%
+%:%633=445%:%
+%:%634=446%:%
+%:%636=448%:%
+%:%637=448%:%
+%:%638=449%:%
+%:%639=450%:%
+%:%640=451%:%
+%:%641=452%:%
+%:%648=453%:%
+%:%649=453%:%
+%:%650=454%:%
+%:%651=454%:%
+%:%652=455%:%
+%:%653=455%:%
+%:%655=456%:%
+%:%656=457%:%
+%:%657=457%:%
+%:%658=458%:%
+%:%659=458%:%
+%:%660=459%:%
+%:%661=459%:%
+%:%662=459%:%
+%:%663=460%:%
+%:%673=462%:%
+%:%674=463%:%
+%:%675=464%:%
+%:%676=465%:%
+%:%677=466%:%
+%:%678=467%:%
+%:%679=468%:%
+%:%680=469%:%
+%:%682=471%:%
+%:%683=471%:%
+%:%684=472%:%
+%:%685=472%:%
+%:%686=473%:%
+%:%688=474%:%
+%:%689=475%:%
+%:%690=475%:%
+%:%691=476%:%
+%:%692=477%:%
+%:%693=477%:%
+%:%694=478%:%
+%:%696=479%:%
+%:%697=480%:%
+%:%698=480%:%
+%:%699=481%:%
+%:%700=482%:%
+%:%701=482%:%
+%:%702=483%:%
+%:%703=484%:%
+%:%705=485%:%
+%:%706=485%:%
+%:%707=486%:%
+%:%708=487%:%
+%:%710=488%:%
+%:%711=488%:%
+%:%712=489%:%
+%:%719=490%:%
+%:%720=490%:%
+%:%721=491%:%
+%:%722=491%:%
+%:%723=492%:%
+%:%724=492%:%
+%:%725=492%:%
+%:%726=493%:%
+%:%727=493%:%
+%:%728=494%:%
+%:%729=494%:%
+%:%730=494%:%
+%:%731=495%:%
+%:%732=495%:%
+%:%734=496%:%
+%:%744=498%:%
+%:%745=499%:%
+%:%746=500%:%
+%:%747=501%:%
+%:%748=502%:%
+%:%749=503%:%
+%:%750=504%:%
+%:%751=505%:%
+%:%752=506%:%
+%:%753=507%:%
+%:%754=508%:%
+%:%755=509%:%
+%:%756=510%:%
+%:%757=511%:%
+%:%758=512%:%
+%:%759=513%:%
+%:%760=514%:%
+%:%761=515%:%
+%:%762=516%:%
+%:%763=517%:%
+%:%764=518%:%
+%:%765=519%:%
+%:%766=520%:%
+%:%767=521%:%
+%:%768=522%:%
+%:%769=523%:%
+%:%770=524%:%
+%:%771=525%:%
+%:%772=526%:%
+%:%773=527%:%
+%:%774=528%:%
+%:%775=529%:%
+%:%776=530%:%
+%:%777=531%:%
+%:%778=532%:%
+%:%779=533%:%
+%:%780=534%:%
+%:%781=535%:%
+%:%782=536%:%
+%:%783=537%:%
+%:%787=539%:%
+%:%788=540%:%
+%:%789=541%:%
+%:%791=543%:%
+%:%792=543%:%
+%:%793=544%:%
+%:%794=545%:%
+%:%795=545%:%
+%:%797=545%:%
+%:%801=545%:%
+%:%802=545%:%
+%:%804=546%:%
+%:%805=547%:%
+%:%806=548%:%
+%:%807=549%:%
+%:%808=550%:%
+%:%809=551%:%
+%:%819=554%:%
+%:%820=555%:%
+%:%821=556%:%
+%:%830=558%:%
+%:%842=560%:%
+%:%843=561%:%
+%:%844=562%:%
+%:%845=563%:%
+%:%846=564%:%
+%:%847=565%:%
+%:%848=566%:%
+%:%849=567%:%
+%:%850=568%:%
+%:%851=569%:%
+%:%852=570%:%
+%:%853=571%:%
+%:%854=572%:%
+%:%855=573%:%
+%:%856=574%:%
+%:%857=575%:%
+%:%858=576%:%
+%:%859=577%:%
+%:%860=578%:%
+%:%861=579%:%
+%:%863=581%:%
+%:%864=581%:%
+%:%865=582%:%
+%:%868=583%:%
+%:%872=583%:%
+%:%873=583%:%
+%:%878=583%:%
+%:%881=584%:%
+%:%882=585%:%
+%:%883=585%:%
+%:%884=586%:%
+%:%887=587%:%
+%:%891=587%:%
+%:%892=587%:%
+%:%897=587%:%
+%:%900=588%:%
+%:%901=589%:%
+%:%902=589%:%
+%:%903=590%:%
+%:%906=591%:%
+%:%910=591%:%
+%:%911=591%:%
+%:%916=591%:%
+%:%919=592%:%
+%:%920=593%:%
+%:%921=593%:%
+%:%922=594%:%
+%:%925=595%:%
+%:%929=595%:%
+%:%930=595%:%
+%:%939=597%:%
+%:%940=598%:%
+%:%941=599%:%
+%:%942=600%:%
+%:%943=601%:%
+%:%944=602%:%
+%:%945=603%:%
+%:%947=605%:%
+%:%948=605%:%
+%:%949=606%:%
+%:%950=607%:%
+%:%951=607%:%
+%:%953=607%:%
+%:%957=607%:%
+%:%958=607%:%
+%:%960=608%:%
+%:%961=609%:%
+%:%962=610%:%
+%:%963=611%:%
+%:%964=612%:%
+%:%965=613%:%
+%:%966=614%:%
+%:%967=615%:%
+%:%968=616%:%
+%:%969=617%:%
+%:%970=618%:%
+%:%980=620%:%
+%:%981=621%:%
+%:%983=623%:%
+%:%984=623%:%
+%:%985=624%:%
+%:%988=625%:%
+%:%992=625%:%
+%:%993=625%:%
+%:%995=626%:%
+%:%1005=628%:%
+%:%1006=629%:%
+%:%1008=631%:%
+%:%1009=631%:%
+%:%1010=632%:%
+%:%1013=633%:%
+%:%1017=633%:%
+%:%1018=633%:%
+%:%1019=633%:%
+%:%1021=634%:%
+%:%1022=635%:%
+%:%1032=637%:%
+%:%1033=638%:%
+%:%1034=639%:%
+%:%1035=640%:%
+%:%1036=641%:%
+%:%1037=642%:%
+%:%1038=643%:%
+%:%1039=644%:%
+%:%1040=645%:%
+%:%1041=646%:%
+%:%1042=647%:%
+%:%1043=648%:%
+%:%1047=650%:%
+%:%1048=651%:%
+%:%1049=652%:%
+%:%1051=654%:%
+%:%1052=654%:%
+%:%1053=655%:%
+%:%1054=656%:%
+%:%1055=657%:%
+%:%1056=657%:%
+%:%1058=657%:%
+%:%1062=657%:%
+%:%1063=657%:%
+%:%1065=658%:%
+%:%1066=659%:%
+%:%1067=660%:%
+%:%1068=661%:%
+%:%1069=662%:%
+%:%1070=663%:%
+%:%1071=664%:%
+%:%1072=665%:%
+%:%1073=666%:%
+%:%1074=667%:%
+%:%1084=669%:%
+%:%1085=670%:%
+%:%1086=671%:%
+%:%1088=673%:%
+%:%1089=673%:%
+%:%1090=674%:%
+%:%1091=675%:%
+%:%1092=675%:%
+%:%1094=675%:%
+%:%1098=675%:%
+%:%1099=675%:%
+%:%1101=676%:%
+%:%1102=677%:%
+%:%1103=678%:%
+%:%1104=679%:%
+%:%1105=680%:%
+%:%1106=681%:%
+%:%1107=682%:%
+%:%1108=683%:%
+%:%1109=684%:%
+%:%1110=685%:%
+%:%1120=687%:%
+%:%1121=688%:%
+%:%1122=689%:%
+%:%1123=690%:%
+%:%1125=692%:%
+%:%1126=692%:%
+%:%1127=693%:%
+%:%1130=694%:%
+%:%1134=694%:%
+%:%1135=694%:%
+%:%1136=694%:%
+%:%1138=695%:%
+%:%1144=695%:%
+%:%1147=696%:%
+%:%1148=697%:%
+%:%1149=697%:%
+%:%1150=698%:%
+%:%1153=699%:%
+%:%1157=699%:%
+%:%1158=699%:%
+%:%1159=699%:%
+%:%1161=700%:%
+%:%1167=700%:%
+%:%1170=701%:%
+%:%1171=702%:%
+%:%1172=702%:%
+%:%1173=703%:%
+%:%1174=704%:%
+%:%1177=705%:%
+%:%1181=705%:%
+%:%1182=705%:%
+%:%1183=705%:%
+%:%1185=706%:%
+%:%1186=707%:%
+%:%1196=709%:%
+%:%1197=710%:%
+%:%1198=711%:%
+%:%1199=712%:%
+%:%1200=713%:%
+%:%1201=714%:%
+%:%1202=715%:%
+%:%1211=717%:%
+%:%1223=719%:%
+%:%1224=720%:%
+%:%1225=721%:%
+%:%1226=722%:%
+%:%1228=724%:%
+%:%1229=724%:%
+%:%1230=725%:%
+%:%1231=726%:%
+%:%1232=726%:%
+%:%1234=726%:%
+%:%1238=726%:%
+%:%1239=726%:%
+%:%1241=727%:%
+%:%1242=728%:%
+%:%1243=729%:%
+%:%1244=730%:%
+%:%1245=731%:%
+%:%1246=732%:%
+%:%1247=733%:%
+%:%1248=734%:%
+%:%1249=735%:%
+%:%1250=736%:%
+%:%1251=737%:%
+%:%1252=737%:%

### 2021-10-28 paper/output/document/whykant.tex
jkldfa

%
\begin{isabellebody}%
\setisabellecontext{whykant}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Why Kantian Ethics%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In this thesis, I formalize Kantian ethics. Deontological theories are attractive candidates for formalization
because, as Powers argues, rules are generally computationally tractable. Intuitively, algorithms are 
rules or procedures for problem solving and Kantian ethics, particularly the Formula of Universal Law
appears to be one such procedure. While computers are generally successful at applying rules, I will 
argue that Kantian ethics is within reach for automation because of its formalism specifically. Due to 
this formalism, reasoning about Kantian ethics requires far less knowledge of the world than alternative
theories. Like all ethical reasoning, reasoning with Kantian ethics requires some judgements about what 
circumstances and facts are morally relevant, but I argue that it requires fewer such judgements than 
consequentialism or virtue ethics. I will present Kantian ethics and describe its formal nature, then briefly
present consequentialism and virtue ethics and compare their automatability.

I do not aim to show that Kantian ethics is the only tractable theory to automate, and I do not claim to present a comprehensive
overview of all consequentialist or virtue ethical theories. Instead, I present a sample of some theories
in each tradition and argue that Kantian ethics is more straightforward to formalize than these samples.
Insofar as my project serves as an early proof-of-concept for computational ethics, I choose to automate
the ethical theory that appears most amenable to automation.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Kantian Ethics%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
First, I present a brief overview of Kantian ethics. Kant's theory is centered on the idea of 
practical reason, which is the kind of reason that we use practically to decide what to do. In \emph{The 
Groundwork of the Metaphysics of Morals}, Kant's most influential text on ethics, he explains that 
rational beings are unique because we can act ``in accordance with the representations of laws" \cite[4:412]{groundwork}.
A ball thrown into the air acts according to the laws of physics and lacks the ability to ask itself, 
``should I fall back to the ground?" It simply falls. A rational being on the other hand, can ask themselves
``Should I act on this reason? Is this a sufficient reason for acting?" As Korsgaard describes it, when 
choosing which desire to act on, ``it is as if there is something over and above all of your desires, 
somethig which is you, and which chooses which desire to act on" \cite[100]{sources}. Rational beings are
set apart by this reflective capacity. In other words, a rational being's behavior is purposive: their 
actions are guided by practical reason. They have reasons for acting, even when these reasons may be 
opaque to them. The operation of this practical reason is called the will.

The will operates by willing maxims, which are its percieved reasons for acting. Kant defines a maxim as 
the ``subjective principle of willing," which is the reason that the will \emph{subjectively} gives 
to itself for acting \cite[16, footnote 1]{groundwork}. There is debate about what exactly must be 
included in a maxim, but most philosophers agree that a maxim consists of some combination of circumstances, 
act, and goal\footnote{For more discussion of the definition of a maxim, see Section What Is a Maxim?}.
One example of a maxim is ``When I am hungry, I will eat a doughnut in order to satisfy my sweet tooth." 
When a moral agent wills this maxim, they decide to act on it. They commit themselves to the end in the maxim, 
satisfying your sweet tooth in this case. They represent their action, to themselves, as following the 
principle given by this maxim. It is maxims that Kant evaluates as obligatory or prohibited. He argues that
certain maxims have a form or logical structure that requires any rational agent to will them.

The form of an obligatory maxim is given by the categorical imperative, Kant's supreme rule of morality. 
An imperative is a command, such as ``Close the door" or "Eat the doughnut in order to satisfy your 
sweet tooth." A categorical imperative holds unconditionally for all rational agents under all 
circumstances. Kant argues that the moral law must be a categorical imperative, for otherwise it would 
not have the force that makes it a moral law \cite[5]{groundwork}. In order for an imperative to be 
categorical, it must be derived from the will's authority over itself. Our wills are free and bound to 
nothing but themselves. The only thing that can have unconditional authority over a rational will is 
the rational will itself. No one can tell me what reasons to act on because I can always ask why I 
should obey their authority. The only authority that I cannot question is the authority of my own 
practica reason. To question this authority is to demand a reason for acting for reasons, which 
concedes the authority of reason itself \cite[23]{velleman}. Therefore, the only possible candidates 
for the categorical imperative are those rules that are required of the will because it is a will. 
The categorical imperative must be a property of practical reason itself.

Armed with this understanding of practical reason, we can now examine what Kant claims is the categorical 
imperative. He presents three ``formulations" or versions of the categorical imperative and goes on to 
argue that all three formulations are equivalent. In this project, I focus on the first formulation,
the Formula of Universal Law, but will briefly present the other two as well.

The first formulation of the categorical imperative is the
formula of universal law (FUL), which reads, ``act only according to that maxim through which you can 
at the same time will that it become a universal law." $\cite[34]{groundwork}$ This formulation
generates the universalizability test, which ``tests" the moral value of a maxim by 
imagining a world in which it becomes a universal law and attempting to will the maxim in that world.
Velleman presents a concise argument for the FUL. He argues that reason is shared among reasoners. For 
example, all reasoners have equal access to the arithmetic logic that shows that ``2+2=4"\cite[29]{velleman}. The chain of 
reasoning that makes this statement true is not specific to any person, but is universal across people. 
Therefore, if I have sufficient reasont to will a maxim, so will every other rational agent. There is 
nothing special about the operation of my practical reason that other reasoners don't have access to. 
Practical reason is by its very nature shared, so in adopting a maxim, I implicitly state that all reasoners
across time also have reason to adopt that maxim. Therefore, because I act on reasons, I must obey the 
FUL. Notice that this fulfilles the above criterion for a categorical imperative: the FUL is derived from 
a property of practical reason itself and thus derives authority from the will's authority over itself, 
as opposed to some external authority.

The second formulation of the categorical imperative is the formula of humanity (FUH): ``So act that you use humanity, 
in your own person, as well as in the person of any other, always at the same time as an end, never merely 
as a means." $\cite[41]{groundwork}$. This formulation is often understood as requiring us to 
acknowledge and respect the dignity of every other person. The third formulation of the categorical 
imperative is the formula of autonomy (FOA), which Korsgaard summarizes in her introduction to the Groundwork 
as, ``we should so act that we may think of ourselves as legislating universal laws through our 
maxims." $\cite[28]{korsgaardintro}$ While closely related to the FUL, the FOA presents morality as the activity of 
perfectly rational agents in an ideal ``kingdom of ends," guided by what Kant calls the ``laws of freedom."

The above is not meant to serve as a full defense of Kant's ethical theory, as that is outside the scope
of this thesis. Instead, I aim to briefly reconstruct an argument for Kant's ethical theory in the hopes 
of offering context for the implementation of the FUL I present later in the thesis. Additionally, understanding 
the structure of Kant's argument also reveals facts about his theory that make it an ideal candidate 
for formalization.

Kant argues that the categorical imperative, and the FUL in particular, is a formal principle of practical
reason. In other words, the FUL is a property of reason related to the form or structure of a maxim.
It has nothing to do with the circumstances of behavior (beyond those included in a maxim), the agent's
mental state, or any other contingent facts. Instead, it is purely a property of a proposed principle for
action. This formalism makes Kantian ethics an attractive candidate for formalization. While other 
ethical theories often rely on many facts about the world or the actor, Kantian ethics simply relies 
on the form of a given maxim. A computer evaluating a maxim doesn't require any knowledge about the 
world beyond what is contained in a maxim. A maxim is essentially a thin representation of all the knowledge
that a computer needs in order to make a moral judgement. Automating Kantian ethics merely requires 
making the notion of a maxim precise and representing it to the computer. This distinguishes Kantian 
ethics from utilitarianism and virtue ethics, which, as I will argue below, require far more knowledge
about the world or the agent to reach a moral decision.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Consequentialism%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
A consequentialist ethical theory is, broadly speaking, any ethical theory that evaluates an action by evaluating 
its consequences\footnote{There is long debate about what exactly makes an ethical theory consequentialist \cite{consequentialismsep}. 
For this paper, I will focus on theories that place the moral worth of an act in its the consequences.}. For example, 
utilitarianism is a form of consequentialism in which the moral action 
is the action that results in the best consequences or produces the most good \cite{utilsep}. Different 
consequentialists take different stances on what exactly constitutes a ``good" consequence and how 
we can aggregate or calculate the goodness of a state of affairs. For example, hedonists define 
a good action as one that produces pleasure, and the most good action as the one that produces that most
pleasure or avoids the most pain. 
Unlike consequentialists, Kantians derive the moral worth of an action
from the maxim that is acted on. This maxim is the actor's subjective reason for acting, determined 
at the time of action, not as a later consequence.

Because consequentialism evaluates the state of affairs following an action, this kind of  ethical 
reasoning requires more knowledge
about the state of the world than Kantian ethics. Under a naive version of consequentialism, evaluating 
an action requires perfect knowledge of all consequences following an action. Not only does this require 
a lot of knowledge that the implementor of an automated ethical system likely does not have, it also 
requires answering difficult questions about which consequences were actually caused by an action\footnote
{maybe cite the debate about difficulties in determining causation?}. Most consequentialists do not actually
think that agents need to calculate all the consequences of their actions; plausible consequentialist strategies include stopping 
calculation early because constant calculation paralyzes action and is clearly not a desirable state of affairs,
only evaluating consequences that the agent could reasonably forsee before acting, or the legal notion 
of ``proximate cause," in which the agent is only responsible for the immediate consequences of their 
acts but not of consequences resulting from others' voluntary acts prompted by the agent's original act \cite{consequentialismsep}.
The details of these views are not important for my project, but it is clear that they require far 
more data than Kantian ethics. Even if we cut off the chain of causal reasoning at some point, evaluating 
the consequences of an action is still data-intensive. Even evaluating the first or immediate cause of an
action requires immense knowledge about the state of the world and how it changes. Kantian ethics, on the 
other hand, requires only knowledge about the maxim, not knowledge about the state of the world when 
the maxim is adopted. Consequentialism requires knowledge about the situation in which the act is 
performed and following the act, whereas Kantian ethics merely requires knowledge about the act itself.

The fact that consequentialism requires more knowledge about the world makes it more difficult to formalize.
Automated consequentialist ethics would need to represent complex states of the world and causal chains
in an efficient manner and reason about them. This presents a difficult technical challenge and
impedes the usability of such a system. Automated consequentialist ethics would need to come equipped with 
a large enough database of knowledge about the world to extrapolate the consequences of an actions and
up-to-date information about the state of the world at the moment of action. Not only does collecting 
and representing this data pose a technical challenge, it also creates a larger ``trusted code base" for 
the automated system. Trusting a Kantian ethical reasoner merely requires trusting the logical implementation
of the categorical imperative, but trusting a consequentialist ethical reasoner requires trusting both the
logical machinery that actually evaluates the consequences of an act and the background/situational
knowledge that serves as an input to this machinery. There is much more room for debate about 
the background knowledge/state of the world than there is about the act that the agent performs.
The Kantian ethical reasoner includes room for 
disagreement about the formulation of the maxim being evaluated\footnote{For more on the parsing 
of ethical dilemmas into maxims, see Section AI Ethics}, but the surface of this debate is much smaller
than the surface of an entire database about actions and their consequences.

Another such debate that an automated consequentialist reasoner would need to take a stance on is 
the question of what qualifies as a ``good consequence." Simple hedonists associate
good with the presence of pleasure and the lack of pain. Preference utiliarians believe that good is 
the satisfaction of desires and is thus related to individuals' preferences, as opposed to some objective
sensation of pleasure or pain. Other consequentialists adopt a pluralistic theory of value, under which 
many different kinds of things are good for different reasons. For example, Moore values beauty and truth 
and other pluralists value justice, love, and freedom (cite). Welfare utilitarians value a person's 
welfare and utilitarians of right value states of affairs in which respect for some set of crucial
rights is maximized \cite{consequentialismsep}.

Most of the above theories of good require that a moral reasoner understand complex features about
individuals' preferences, desires, or sensations in order to evaluate a moral action, making automated
consequentialist ethics difficult. Regardless of the theory of the good, a consequentialist ethical 
reasoner needs to evaluate a state of affairs, which may encompass each involved individual's pleasure, 
preferences, welfare, freedom, rights, or whatever other criteria make a state good. This not only requires
a lot of data as I argued above, it also requires judgements about whether or not a state of affairs 
actually satisifes the relevant criteria for goodness. These judgements are difficult and debateable, 
and any consequentialist decision requires many of these judgements for each individual involved. As 
systems become more complex and involve more people and more acts, making these judgements quickly becomes
difficult, posing a scaling challenge for a consequentialist ethical reasoner. Perfect knowledge of 
tens of thousands of people's pleasure or preferences or welfare or rights is impossible. Either a human being 
assigns values to states of affairs, which quickly becomes difficult to scale, or the machine does, 
which requires massive knowledge and increases room for doubting the system's judgements.

Once an automated consequentialist agent assigns a goodness measurement to each person in a state of affairs, it 
must also calculate an overall goodness measurement for this state of affairs. One approach to assigning
this value is to aggregate each person's individual goodness score into one complete score for a state. 
For example, under a simple welfare model, each person may be assigned a welfare score and the total 
score for a state of affairs may be the sum of the welfare scores for each involved person.
The more complex the theory of the good, the more difficult that aggregation becomes. For example, 
pluralistic theories struggle to explain how different kinds of value can be compared. How do we compare
one unit of beauty to one unit of pleasure? Subjective theories of the good, such as those focused on 
the sensation of pleasure or an individual's preferences, present difficulties in comparing such 
subjective measures. Resolving this debate requires that the automated reasoner make a decision about
one specific aggregation algorithm, but those who disagree with this choice will not trust the reasoner's
moral judgements.

On the other hand, some consequentialists reject aggregation entirely and instead prefer wholistic
evaluations of a state of affairs. While this approach no longer requires that a reasoner define an 
aggregation algorithm, the reasoner still needs to calculate a goodness measurement for a state of 
affairs. Whereas before the reasoner could restrict analysis to a single person, the algorithm must now 
evaluate an entire state at once, wholistically. Evaluating the goodness of an entire state of affairs is more complicated
than evaluating the goodness of a single person. As consequentialists modulate between aggregation 
and wholistic evaluation, they face a tradeoff between the difficulty of aggregation and the complexity 
of goodness measurements for large units like states of affairs. This tradeoff translates to an automated
consequentialist moral agent. Such an agent either needs to define an aggregation function, thus opening 
the door to those who disagree with this definition, or needs to evaluate the goodness of entire states
of affairs, which is a complex and data-intensive philosophical and technical challenge.

None of the challenges described above are intractable or capture the full literature of 
all variations of consequentialism. I do not argue that consequentialism is 
impossible to automate. Instead, each of the challenges above either makes an automated consequentialist
agent more complex or requires that the developer ``plant certain flags" and take a stance on philosophical
debates. Such points of difficulty also appear in Kantian ethics, and I deal with them throughout this
project (see Section What is a Maxim). These difficulties are present in any ethical theory, but consequentialism
has more points of difficulty than Kantian ethics and is thus more difficult to formalize both computationally
and philosophically. Given that this project is a proof-of-concept and an early attempt to formalize
a philosophically rigorous ethical theory, I choose Kantian ethics because it is the easier theory to 
formalize. Future work could indeed address the challenges above and formalize consequentialism. The more
ethical theories that comptuational tools can handle, the more valuable computational philosophy becomes 
for philosophers and AI agents. My project contributes a formalization of one theory that poses fewer
challenges than others.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Virtue Ethics%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
The virtue ethical tradition predates even consequentialism and has countless variations. Below
I explain the centrality of virtue and practical wisdom, two common tenets of most virtue ethical theories.

All virtue ethical theories place virtue, or those traits that constitute a good moral character, 
at the center. Virtue ethicists recommend actions based on the character traits that such actions
would help cultivate. A virtue is commonly accepted as a character trait that "makes its possessor
good" \cite{vesep}. For example, under Aristotlean virtue ethics, the virtues are the traits that 
enable human flourishing, or fulfilling the purpose of a human being. Many modern virtue ethicists abandon
Aristotle's notion of a ``purpose" of human beings, and instead define virtue in terms of the characteristic
activity of human beings (in ethical terms, not telelological terms) (cite from gened paper). Just as 
consequentialists must offer a view of which consequences are good, virtue ethicists must offer some 
theory of the virtues which justifies and presents a list of the virtues. Such theories are varied in
the literature, from the classical virtues of courage and temperance to the Buddhist virtue of 
equanimity to Sen's conception of the virtues as capabilites that serve as ``effective opportunities to 
undertake the actions and activities" an agent wants to engage in. An automated virtue ethical agent 
will need to commit to a particular theory of the virtues, opening itself up to criticism from those
who disagree with this theory of the virtues. Unlike Kantian ethics, who generally agree on the meaning of
the FUL, virtue ethicists robustly debate which character traits qualify as virtues.

Another difficulty with automating virtue ethics is that the unit of evaluation for a virtue ethical
theory is often a person's entire character. While Kantians evaluate the maxim of an act and utilitarians
evaluate the consequences of an act, virtue ethicists evaluate the actor's moral character and their 
disposition towards the act. Virtues are character traits and evaluating an action as virtuous or 
not requires understanding the agent's character and disposition while acting. If states of affairs
require complex representations, an agent's ethical character and disposition is even more difficult
to represent. Consequentialism posed a data-collection problem in evaluating and representing states
of affairs, but virtue ethics poses a conceptual problem about the formal nature of moral character.
Formalizing the concept of character appears to require significant philosophical and computational
progress, whereas Kantian ethics automatically presents a formal rule to implement. Precise representations
of consequences is a central debate in consequentialism, but precise representation of moral character
is not a central debate in virtue ethics.

One potential appeal of virtue ethics is that many virtue ethical theories involve some form of 
moral education. Artistotle, for example, argued that cultivating virtuous action requires making such
action habitual through moral education. Under the simple, popular view of virtue ethics, the virtuous
act is what the virtuous person would do. Both of these theories imply that ethical behavior can be
learned from some dataset of virtuous behavior, either those prescribed by a moral teacher or those that
a virtuous ideal agent would undertake. Indeed, these theories seem to point towards a machine learning
model for computational ethics, in which ethics is learned from a dataset of acts tagged as ethical
or not ethical. Such approaches exist in the literature and there is a solid body of work attempting 
to learn ethics from past judgements. My project present a different, top-down approach starting 
with an ethical theory and representing it in a logic. Both approaches have their merits, but one 
advantage of my logical approach is that it does not suffer many of the explainability problems that machine learning 
approaches may experience. Many machine learning algorithms cannot sufficiently explain their decisions
to a human being, and often find patterns or correlations in datasets that don't actually cohere with 
the trends and causes that a human being would identify. While there is significant activity and progress
in explainable machine learning, interactive theorem provers are designed to be explainable at the outset.
Indeed, Isabelle can even give the axioms and lemmas it used in constructing a proof, allowing a human 
being to reconstruct the proof independently if they wish. This is, again, not an intractable problem 
for machine learning approaches to computational ethics, but is one reason to prefer logical approaches.

Explainability matters more for ethics.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
\isacommand{end}\isamarkupfalse%
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
\isanewline
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/whykant.thy%:%
%:%24=6%:%
%:%36=8%:%
%:%37=9%:%
%:%38=10%:%
%:%39=11%:%
%:%40=12%:%
%:%41=13%:%
%:%42=14%:%
%:%43=15%:%
%:%44=16%:%
%:%45=17%:%
%:%46=18%:%
%:%47=19%:%
%:%48=20%:%
%:%49=21%:%
%:%50=22%:%
%:%51=23%:%
%:%60=26%:%
%:%72=28%:%
%:%73=29%:%
%:%74=30%:%
%:%75=31%:%
%:%76=32%:%
%:%77=33%:%
%:%78=34%:%
%:%79=35%:%
%:%80=36%:%
%:%81=37%:%
%:%82=38%:%
%:%83=39%:%
%:%84=40%:%
%:%85=41%:%
%:%86=42%:%
%:%87=43%:%
%:%88=44%:%
%:%89=45%:%
%:%90=46%:%
%:%91=47%:%
%:%92=48%:%
%:%93=49%:%
%:%94=50%:%
%:%95=51%:%
%:%96=52%:%
%:%97=53%:%
%:%98=54%:%
%:%99=55%:%
%:%100=56%:%
%:%101=57%:%
%:%102=58%:%
%:%103=59%:%
%:%104=60%:%
%:%105=61%:%
%:%106=62%:%
%:%107=63%:%
%:%108=64%:%
%:%109=65%:%
%:%110=66%:%
%:%111=67%:%
%:%112=68%:%
%:%113=69%:%
%:%114=70%:%
%:%115=71%:%
%:%116=72%:%
%:%117=73%:%
%:%118=74%:%
%:%119=75%:%
%:%120=76%:%
%:%121=77%:%
%:%122=78%:%
%:%123=79%:%
%:%124=80%:%
%:%125=81%:%
%:%126=82%:%
%:%127=83%:%
%:%128=84%:%
%:%129=85%:%
%:%130=86%:%
%:%131=87%:%
%:%132=88%:%
%:%133=89%:%
%:%134=90%:%
%:%135=91%:%
%:%136=92%:%
%:%137=93%:%
%:%138=94%:%
%:%139=95%:%
%:%140=96%:%
%:%141=97%:%
%:%142=98%:%
%:%143=99%:%
%:%144=100%:%
%:%145=101%:%
%:%146=102%:%
%:%147=103%:%
%:%148=104%:%
%:%149=105%:%
%:%150=106%:%
%:%151=107%:%
%:%152=108%:%
%:%153=109%:%
%:%154=110%:%
%:%155=111%:%
%:%156=112%:%
%:%157=113%:%
%:%166=116%:%
%:%178=118%:%
%:%179=119%:%
%:%180=120%:%
%:%181=121%:%
%:%182=122%:%
%:%183=123%:%
%:%184=124%:%
%:%185=125%:%
%:%186=126%:%
%:%187=127%:%
%:%188=128%:%
%:%189=129%:%
%:%190=130%:%
%:%191=131%:%
%:%192=132%:%
%:%193=133%:%
%:%194=134%:%
%:%195=135%:%
%:%196=136%:%
%:%197=137%:%
%:%198=138%:%
%:%199=139%:%
%:%200=140%:%
%:%201=141%:%
%:%202=142%:%
%:%203=143%:%
%:%204=144%:%
%:%205=145%:%
%:%206=146%:%
%:%207=147%:%
%:%208=148%:%
%:%209=149%:%
%:%210=150%:%
%:%211=151%:%
%:%212=152%:%
%:%213=153%:%
%:%214=154%:%
%:%215=155%:%
%:%216=156%:%
%:%217=157%:%
%:%218=158%:%
%:%219=159%:%
%:%220=160%:%
%:%221=161%:%
%:%222=162%:%
%:%223=163%:%
%:%224=164%:%
%:%225=165%:%
%:%226=166%:%
%:%227=167%:%
%:%228=168%:%
%:%229=169%:%
%:%230=170%:%
%:%231=171%:%
%:%232=172%:%
%:%233=173%:%
%:%234=174%:%
%:%235=175%:%
%:%236=176%:%
%:%237=177%:%
%:%238=178%:%
%:%239=179%:%
%:%240=180%:%
%:%241=181%:%
%:%242=182%:%
%:%243=183%:%
%:%244=184%:%
%:%245=185%:%
%:%246=186%:%
%:%247=187%:%
%:%248=188%:%
%:%249=189%:%
%:%250=190%:%
%:%251=191%:%
%:%252=192%:%
%:%253=193%:%
%:%254=194%:%
%:%255=195%:%
%:%256=196%:%
%:%257=197%:%
%:%258=198%:%
%:%259=199%:%
%:%260=200%:%
%:%261=201%:%
%:%262=202%:%
%:%263=203%:%
%:%264=204%:%
%:%265=205%:%
%:%266=206%:%
%:%267=207%:%
%:%268=208%:%
%:%269=209%:%
%:%270=210%:%
%:%271=211%:%
%:%272=212%:%
%:%273=213%:%
%:%274=214%:%
%:%275=215%:%
%:%276=216%:%
%:%277=217%:%
%:%278=218%:%
%:%279=219%:%
%:%280=220%:%
%:%281=221%:%
%:%282=222%:%
%:%283=223%:%
%:%284=224%:%
%:%285=225%:%
%:%286=226%:%
%:%287=227%:%
%:%288=228%:%
%:%289=229%:%
%:%298=232%:%
%:%310=234%:%
%:%311=235%:%
%:%312=236%:%
%:%313=237%:%
%:%314=238%:%
%:%315=239%:%
%:%316=240%:%
%:%317=241%:%
%:%318=242%:%
%:%319=243%:%
%:%320=244%:%
%:%321=245%:%
%:%322=246%:%
%:%323=247%:%
%:%324=248%:%
%:%325=249%:%
%:%326=250%:%
%:%327=251%:%
%:%328=252%:%
%:%329=253%:%
%:%330=254%:%
%:%331=255%:%
%:%332=256%:%
%:%333=257%:%
%:%334=258%:%
%:%335=259%:%
%:%336=260%:%
%:%337=261%:%
%:%338=262%:%
%:%339=263%:%
%:%340=264%:%
%:%341=265%:%
%:%342=266%:%
%:%343=267%:%
%:%344=268%:%
%:%345=269%:%
%:%346=270%:%
%:%347=271%:%
%:%348=272%:%
%:%349=273%:%
%:%350=274%:%
%:%351=275%:%
%:%352=276%:%
%:%353=277%:%
%:%354=278%:%
%:%355=279%:%
%:%356=280%:%
%:%357=281%:%
%:%358=282%:%
%:%359=283%:%
%:%360=284%:%
%:%361=285%:%
%:%369=289%:%
%:%377=289%:%

### 2021-10-28 paper/output/document/outline_whykant.tex
outline done

%
\begin{isabellebody}%
\setisabellecontext{outline{\isacharunderscore}whykant}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Introduction%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In this section, I justify my choice to automate Kantian ethics, as opposed to virtue ethics or
consequentialism. Kantian ethics is easy to formalize for three reasons. First, evaluating a maxim requires little 
data about the world. Second, a maxim is relatively easy to represent to a computer. Third, while 
any ethical theory has debates that automated ethics would need to take a stance on, these debates are 
less frequent and less controversial for Kantian ethics.

The argument is not that no form of consequentialism or virtue ethics is tractable to automate, but 
rather that Kantian ethics is easier. I do not present a comprehensive comparision
of ethical theories, but instead sketch the basic principles that most consequentialist and virtue 
ethical theories share.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Kantian Ethics%
}
\isamarkuptrue%
%
\isamarkupsubsection{Kant Crash Course%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
First, I explain the concepts of 
practical reason, the will, and maxims. I then present Kant's argument that because the will is autonomous,
only the will has authority over itself \cite{sources}. Finally, I argue that a will is definitionally only 
bound by those imperatives that are implied by practical reason itself \cite{velleman}. From there, I present 
the three formulations of the categorical imperative, focusing on the Formula of Universal Law (FUL) \cite{groundwork}. 
This is not a full defense of Kantian ethics but is instead a quick sketch of one argument for the FUL.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Kant is Easy to Formalize%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
The FUL is easy to formalize
because it is a purely formal principle that is only evaluates the form of the maxim that an agent 
acts on. No other information is relevant to the test, so moral judgement can proceed with a relatively small
amount of data.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Common Debates%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
I acknowledge the debates\footnote{I have a separate piece of writing that provides a literature 
review of these debates and justifies my stances. Would that fit here or somewhere else?} in Kantian 
ethics that my project takes a stance on: the correct way to interpret the FUL and the definition of a 
maxim. The stances I take are generally accepted by most Kantians, though some still disagree.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Consequentialism%
}
\isamarkuptrue%
%
\isamarkupsubsection{Consequentialism Crash Course%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
I define
a consequentialist theory as one that evaluates the consequences of an action, acknowledging that
this definition itself is controversial \cite{consequentialismsep}. I then present the debates over theories of the good, which 
consequences to evaluate, and the aggregation of consequences.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Consequentialism is Hard to Formalize%
}
\isamarkuptrue%
%
\isamarkupsubsubsection{Requires Lots of Data About States of Affairs%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
Making a consequentialist moral judgement requires data about the entire state of affairs following
an action, posing many challenges. First, collecting this data is difficult. Second, in order to trust 
the system's judgements, we have to trust the ethical theory, its theory of the good, and the many
judgements required to assign each state of affairs a goodness measurement \cite{utilsep}.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Tradeoff Between Aggregation vs Wholistic Evaluation%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
Consequentialism also faces the further problem of aggregating goodness across people. 
Consequentialists who abandon aggregation must instead find some wholistic evaluation function
for a state of affairs. There is a tradeoff between the difficulty of aggregation
and the complexity of making judgements about an entire state of affairs, as opposed to about a single person.
A reasoner will need large, complicated datasets to settle these questions.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Virtue Ethics%
}
\isamarkuptrue%
%
\isamarkupsubsection{Virtue Ethics Crash Course%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
I understand the concept of virtue as those traits that are 
good for the posessor \cite{vesep}. I briefly explain Aristotle's eudaimonistic conception of virtue and present
some examples of virtues (courage, temperance, equanimity).%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Virtue Ethics is Hard to Formalize%
}
\isamarkuptrue%
%
\isamarkupsubsubsection{What is Virtue?%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
Automated virtue ethics will need to plant a flag in the messy, controversial debate over the exact
list of virtues. While most Kantians agree on one interpretation of the FUL, most virtue ethicists 
have their own interpretations of what the virtues are.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Representing Moral Character is Difficult%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
Automated virtue ethics has to evaluate moral character, which is much more challenging than 
evaluating a maxim. Moral character is a complex concept to precisely represent to a computer.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Machine Learning and Virtue Ethics%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
There is a connection between the ideas of cultivating habit and mimicking virtuous action
and machine learning, which mimics patterns in datasets\footnote{Would love feedback on whether this should
go here or in a Related Work section.}. There's been some
work using machine learning to learn moral behavior from a dataset of actions tagged as ethical \cite{delphi}. 
One drawback of this approach is the fact that machine learning algorithms have trouble
explaining why they made the judgements they made and often pick up on patterns that human beings would 
not see as indicative of causation. In contrast,
my system can explain exactly which axioms and principles resulted in a maxim being obligated or prohibited
and can even present human-reconstructable proofs of its results.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/outline_whykant.thy%:%
%:%24=6%:%
%:%36=8%:%
%:%37=9%:%
%:%38=10%:%
%:%39=11%:%
%:%40=12%:%
%:%41=13%:%
%:%42=14%:%
%:%43=15%:%
%:%44=16%:%
%:%45=17%:%
%:%54=19%:%
%:%58=21%:%
%:%70=23%:%
%:%71=24%:%
%:%72=25%:%
%:%73=26%:%
%:%74=27%:%
%:%75=28%:%
%:%84=31%:%
%:%96=33%:%
%:%97=34%:%
%:%98=35%:%
%:%99=36%:%
%:%108=39%:%
%:%120=41%:%
%:%121=42%:%
%:%122=43%:%
%:%123=44%:%
%:%132=46%:%
%:%136=48%:%
%:%148=50%:%
%:%149=51%:%
%:%150=52%:%
%:%151=53%:%
%:%160=55%:%
%:%164=57%:%
%:%176=59%:%
%:%177=60%:%
%:%178=61%:%
%:%179=62%:%
%:%188=64%:%
%:%200=66%:%
%:%201=67%:%
%:%202=68%:%
%:%203=69%:%
%:%204=70%:%
%:%213=72%:%
%:%217=74%:%
%:%229=76%:%
%:%230=77%:%
%:%231=78%:%
%:%240=80%:%
%:%244=82%:%
%:%256=85%:%
%:%257=86%:%
%:%258=87%:%
%:%267=89%:%
%:%279=91%:%
%:%280=92%:%
%:%289=94%:%
%:%301=96%:%
%:%302=97%:%
%:%303=98%:%
%:%304=99%:%
%:%305=100%:%
%:%306=101%:%
%:%307=102%:%
%:%308=103%:%
%:%309=104%:%

### 2021-10-28 paper/output/document/whykant.tex
cleaned why kant writing

@@
 \begin{isamarkuptext}%
-In this thesis, I formalize Kantian ethics. Deontological theories are attractive candidates for formalization
-because, as Powers argues, rules are generally computationally tractable. Intuitively, algorithms are 
-rules or procedures for problem solving and Kantian ethics, particularly the Formula of Universal Law
-appears to be one such procedure. While computers are generally successful at applying rules, I will 
-argue that Kantian ethics is within reach for automation because of its formalism specifically. Due to 
-this formalism, reasoning about Kantian ethics requires far less knowledge of the world than alternative
-theories. Like all ethical reasoning, reasoning with Kantian ethics requires some judgements about what 
-circumstances and facts are morally relevant, but I argue that it requires fewer such judgements than 
-consequentialism or virtue ethics. I will present Kantian ethics and describe its formal nature, then briefly
-present consequentialism and virtue ethics and compare their automatability.
+In this thesis, I automate Kantian ethics. Deontological theories are attractive candidates for automation
+because, as Powers argues, rules are generally computationally tractable \cite[1]{powers}. Intuitively, algorithms are 
+rules or procedures for problem solving and Kantian ethics, specifically the Formula of Universal Law,
+is one such procedure for the problem of making ethical judgements. I will make this intuition precise by
+arguing that Kantian ethics is natural to formalize because evaluating a maxim requires little additional
+data about the world and a maxim is relatively easy to represent to a computer. Moreover, while all 
+ethical theories have debates that an automated ethical system will need to take a stance on, these debates
+are less frequent and controversial in the case of Kantian ethics as compared to consequentialism and 
+virtue ethics.
 
-I do not aim to show that Kantian ethics is the only tractable theory to automate, and I do not claim to present a comprehensive
-overview of all consequentialist or virtue ethical theories. Instead, I present a sample of some theories
-in each tradition and argue that Kantian ethics is more straightforward to formalize than these samples.
-Insofar as my project serves as an early proof-of-concept for computational ethics, I choose to automate
-the ethical theory that appears most amenable to automation.%
+I do not aim to show that Kantian ethics is the only tractable theory to automate or
+to present a comprehensive overview of all consequentialist or virtue ethical theories. Instead, I 
+present a sample of some approaches in each tradition and argue that Kantian ethics is more straightforward 
+to formalize than these approaches. Insofar as my project serves as an early proof-of-concept for 
+computational ethics, I choose to automate the ethical theory most amenable to automation.
+
+Future work could and likele should address the challenges I outline in this section. The more ethical
+theories that computational tools can handle, the more valuable computational philosophy becomes
+both for philosophers and for AI agents. My project merely contributes a formalization of one theory that 
+poses fewer challenges than others.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
+\isamarkupsubsubsection{Crash Course on Kantian Ethics%
+}
+\isamarkuptrue%
+%
 \endisatagdocument
@@
 \begin{isamarkuptext}%
-First, I present a brief overview of Kantian ethics. Kant's theory is centered on the idea of 
-practical reason, which is the kind of reason that we use practically to decide what to do. In \emph{The 
-Groundwork of the Metaphysics of Morals}, Kant's most influential text on ethics, he explains that 
-rational beings are unique because we can act ``in accordance with the representations of laws" \cite[4:412]{groundwork}.
-A ball thrown into the air acts according to the laws of physics and lacks the ability to ask itself, 
-``should I fall back to the ground?" It simply falls. A rational being on the other hand, can ask themselves
-``Should I act on this reason? Is this a sufficient reason for acting?" As Korsgaard describes it, when 
+Kant's theory is based on the idea of practical reason, which is the kind of reason that we 
+use to decide what to do. In \emph{The Groundwork of the Metaphysics of Morals}, Kant's most influential 
+text on ethics, he explains that rational beings are unique because we can act ``in accordance with 
+the representations of laws" \cite[4:412]{groundwork}. A ball thrown into the air acts according to 
+the laws of physics. It cannot ask itself, ``Should I fall back to the ground?" It simply falls. 
+A rational being on the other hand, can ask themselves ``Should I act on this reason?" As Korsgaard describes it, when 
 choosing which desire to act on, ``it is as if there is something over and above all of your desires, 
 somethig which is you, and which chooses which desire to act on" \cite[100]{sources}. Rational beings are
-set apart by this reflective capacity. In other words, a rational being's behavior is purposive: their 
+set apart by this reflective capacity. A rational being's behavior is purposive and their 
 actions are guided by practical reason. They have reasons for acting, even when these reasons may be 
-opaque to them. The operation of this practical reason is called the will.
+opaque to them. Kant calls the operation of practical reason the will.
 
@@
 included in a maxim, but most philosophers agree that a maxim consists of some combination of circumstances, 
-act, and goal\footnote{For more discussion of the definition of a maxim, see Section What Is a Maxim?}.
+act, and goal\footnote{For more discussion of the definition of a maxim, see Section What Is a Maxim}.
 One example of a maxim is ``When I am hungry, I will eat a doughnut in order to satisfy my sweet tooth." 
-When a moral agent wills this maxim, they decide to act on it. They commit themselves to the end in the maxim, 
-satisfying your sweet tooth in this case. They represent their action, to themselves, as following the 
+When a moral agent wills this maxim, they decide to act on it. They commit themselves to the end in the maxim 
+(e.g. satisfying your sweet tooth). They represent their action, to themselves, as following the 
 principle given by this maxim. It is maxims that Kant evaluates as obligatory or prohibited. He argues that
-certain maxims have a form or logical structure that requires any rational agent to will them.
+certain maxims have a form or logical structure that requires any rational agent to will them, and these
+maxims are obligatory.
 
@@
 not have the force that makes it a moral law \cite[5]{groundwork}. In order for an imperative to be 
-categorical, it must be derived from the will's authority over itself. Our wills are free and bound to 
-nothing but themselves. The only thing that can have unconditional authority over a rational will is 
-the rational will itself. No one can tell me what reasons to act on because I can always ask why I 
-should obey their authority. The only authority that I cannot question is the authority of my own 
-practica reason. To question this authority is to demand a reason for acting for reasons, which 
+categorical, it must be derived from the will's authority over itself. Our wills are autonomous, so 
+the only thing that can have unconditional authority over a rational will is 
+the rational will itself. Velleman clarifies this argument by claiming that no one can tell you what 
+reasons to act on because you can always ask why you 
+should obey their authority. The only authority that you cannot question is the authority of your own 
+practical reason. To question this authority is to demand a reason for acting for reasons, which 
 concedes the authority of reason itself \cite[23]{velleman}. Therefore, the only possible candidates 
@@
 
-Armed with this understanding of practical reason, we can now examine what Kant claims is the categorical 
+Armed with this understanding of practical reason, Kant presents the categorical 
 imperative. He presents three ``formulations" or versions of the categorical imperative and goes on to 
 argue that all three formulations are equivalent. In this project, I focus on the first formulation,
-the Formula of Universal Law, but will briefly present the other two as well.
+the Formula of Universal Law, but will briefly present the other two as well\footnote{For more on this 
+choice, see Section Why FUL}.
 
 The first formulation of the categorical imperative is the
-formula of universal law (FUL), which reads, ``act only according to that maxim through which you can 
-at the same time will that it become a universal law." $\cite[34]{groundwork}$ This formulation
-generates the universalizability test, which ``tests" the moral value of a maxim by 
+Formula of Universal Law (FUL), which reads, ``act only according to that maxim through which you can 
+at the same time will that it become a universal law" $\cite[34]{groundwork}$. This formulation
+generates the universalizability test, which tests the moral value of a maxim by 
 imagining a world in which it becomes a universal law and attempting to will the maxim in that world.
-Velleman presents a concise argument for the FUL. He argues that reason is shared among reasoners. For 
-example, all reasoners have equal access to the arithmetic logic that shows that ``2+2=4"\cite[29]{velleman}. The chain of 
+If there is a contradiction in willing the maxim in a world in which everyone universally wills the maxim,
+the maxim is prohibited. 
+Velleman presents a concise argument for the FUL. He argues that reason is universally shared among reasoners. For 
+example, all reasoners have equal access to the arithmetic logic that shows that ``2+2=4" \cite[29]{velleman}. The chain of 
 reasoning that makes this statement true is not specific to any person, but is universal across people. 
-Therefore, if I have sufficient reasont to will a maxim, so will every other rational agent. There is 
+Therefore, if I have sufficient reasont to will a maxim, so does every other rational agent. There is 
 nothing special about the operation of my practical reason that other reasoners don't have access to. 
-Practical reason is by its very nature shared, so in adopting a maxim, I implicitly state that all reasoners
+Practical reason is shared, so in adopting a maxim, I implicitly state that all reasoners
 across time also have reason to adopt that maxim. Therefore, because I act on reasons, I must obey the 
-FUL. Notice that this fulfilles the above criterion for a categorical imperative: the FUL is derived from 
+FUL. Notice that this fulfills the above criterion for a categorical imperative: the FUL is derived from 
 a property of practical reason itself and thus derives authority from the will's authority over itself, 
@@
 as, ``we should so act that we may think of ourselves as legislating universal laws through our 
-maxims." $\cite[28]{korsgaardintro}$ While closely related to the FUL, the FOA presents morality as the activity of 
+maxims" $\cite[28]{korsgaardintro}$. While closely related to the FUL, the FOA presents morality as the activity of 
 perfectly rational agents in an ideal ``kingdom of ends," guided by what Kant calls the ``laws of freedom."
@@
 the structure of Kant's argument also reveals facts about his theory that make it an ideal candidate 
-for formalization.
+for formalization.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsubsection{Ease of Automation%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
+Kantian ethics is natural to formalize because the categorical imperative, and the FUL in particular, 
+is a formal principle of practical reason. In other words, the FUL is a property of reason related 
+to the form or structure of a maxim. It has nothing to do with the circumstances of behavior 
+(beyond those included in a maxim), the agent's mental state, or any other contingent facts. Instead, 
+it is purely a property of a proposed principle for action. This formalism makes Kantian ethics an 
+attractive candidate for formalization. While other ethical theories often rely on many facts about 
+the world or the actor, Kantian ethics simply relies on the form of a given maxim. A computer evaluating 
+a maxim doesn't require any knowledge about the world beyond what is contained in a maxim. A maxim 
+is the only input that the computer needs to make a moral judgement. Automating 
+Kantian ethics merely requires making the notion of a maxim precise and representing it to the computer. 
+This distinguishes Kantian ethics from consequentialism and virtue ethics, which, as I will argue below, 
+require far more knowledge about the world or the agent to reach a moral decision.
 
-Kant argues that the categorical imperative, and the FUL in particular, is a formal principle of practical
-reason. In other words, the FUL is a property of reason related to the form or structure of a maxim.
-It has nothing to do with the circumstances of behavior (beyond those included in a maxim), the agent's
-mental state, or any other contingent facts. Instead, it is purely a property of a proposed principle for
-action. This formalism makes Kantian ethics an attractive candidate for formalization. While other 
-ethical theories often rely on many facts about the world or the actor, Kantian ethics simply relies 
-on the form of a given maxim. A computer evaluating a maxim doesn't require any knowledge about the 
-world beyond what is contained in a maxim. A maxim is essentially a thin representation of all the knowledge
-that a computer needs in order to make a moral judgement. Automating Kantian ethics merely requires 
-making the notion of a maxim precise and representing it to the computer. This distinguishes Kantian 
-ethics from utilitarianism and virtue ethics, which, as I will argue below, require far more knowledge
-about the world or the agent to reach a moral decision.%
+Not only does evaluating Kantian ethics only require evaluating a maxim, a maxim itself is an object
+with a thin representation for a computer, as contrasted to more complex objects like states of 
+affairs or moral character. Later in my project, I argue that a maxim can be represented simply as 
+a tuple of circumstances, act, and goal\footnote{For more, see Section What is a Maxim?}. This representation
+is simple and efficient, especially when compared to the representation of a causal chain or a state of 
+affairs or moral character. A maxim is a principle with a well-defined form, so representing a maxim
+to the computer merely requires capturing this form. This both reduces the computational complexity
+(in terms of time and space) of representing a maxim, it also make the system easier for human reasoners
+to interact with. A person crafting an input to a Kantian automated agent needs to reason about relatively
+simple units of evaluation, as opposed to the more complex features that consequentialism and virtue
+ethics reqire. I will make the comparision to consequentialism and virtue ethics explicit below.
+
+I do not argue that Kantian ethics is the only theory possible to formalize, but instead that Kantian
+ethics is relatively easier to formalize. Indeed, like any ethical theory, Kantian ethics contains 
+several debates that philosophers disagree on. In this project, I assume stances on debates about
+what exactly constitutes the form of a maxim and the correct precise interpretation of the Formula of 
+Universal Law. Those who disagree with my stances will not trust the judgements of my system. Unlike
+consequentialism or virtue ethics, these debates are considered close to settled in the Kantian literature 
+\cite{ebelsduggan}. Because such debates are fewer and less controversial than those in virtue ethics
+or consequentialism, Kantian ethics is relatively easier to formalize.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 utilitarianism is a form of consequentialism in which the moral action 
-is the action that results in the best consequences or produces the most good \cite{utilsep}. Different 
-consequentialists take different stances on what exactly constitutes a ``good" consequence and how 
-we can aggregate or calculate the goodness of a state of affairs. For example, hedonists define 
-a good action as one that produces pleasure, and the most good action as the one that produces that most
-pleasure or avoids the most pain. 
-Unlike consequentialists, Kantians derive the moral worth of an action
-from the maxim that is acted on. This maxim is the actor's subjective reason for acting, determined 
-at the time of action, not as a later consequence.
-
+is the action that results in the best consequences or produces the most good \cite{utilsep}. The focus
+on the consequences of action distinguishes consequentialists from Kantians, who derive the moral worth
+of an action from the maxim that is acted on as determined at the time of action. Some debates
+in the consequentialist tradition include discussions of which consequences of an action matter,
+what exactly constitutes a ``good" consequence, and how we can aggregate the consequences of an action
+for all the individuals involved.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsubsection{Which Consequences Matter%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
 Because consequentialism evaluates the state of affairs following an action, this kind of ethical 
@@
 about the state of the world than Kantian ethics. Under a naive version of consequentialism, evaluating 
-an action requires perfect knowledge of all consequences following an action. Not only does this require 
-a lot of knowledge that the implementor of an automated ethical system likely does not have, it also 
-requires answering difficult questions about which consequences were actually caused by an action\footnote
-{maybe cite the debate about difficulties in determining causation?}. Most consequentialists do not actually
-think that agents need to calculate all the consequences of their actions; plausible consequentialist strategies include stopping 
-calculation early because constant calculation paralyzes action and is clearly not a desirable state of affairs,
-only evaluating consequences that the agent could reasonably forsee before acting, or the legal notion 
-of ``proximate cause," in which the agent is only responsible for the immediate consequences of their 
-acts but not of consequences resulting from others' voluntary acts prompted by the agent's original act \cite{consequentialismsep}.
-The details of these views are not important for my project, but it is clear that they require far 
-more data than Kantian ethics. Even if we cut off the chain of causal reasoning at some point, evaluating 
-the consequences of an action is still data-intensive. Even evaluating the first or immediate cause of an
-action requires immense knowledge about the state of the world and how it changes. Kantian ethics, on the 
-other hand, requires only knowledge about the maxim, not knowledge about the state of the world when 
-the maxim is adopted. Consequentialism requires knowledge about the situation in which the act is 
-performed and following the act, whereas Kantian ethics merely requires knowledge about the act itself.
+an action requires perfect knowledge of all consequences following an action. This requires that an 
+automated ethical system somehow collect all of the infinite consquences following an action, a likely
+impossible task. Moreover, compiling this database of consequences requires 
+answering difficult questions about which consequences were actually caused by an action\footnote
+{maybe cite the debate about difficulties in determining causation?}.
+
+These challenges also apply to human reasoners, so most consequentialists do not actually think that 
+agents need to calculate all the consequences of their actions. Plausible strategies to avoid this problem
+include stopping calculation early because constant calculation paralyzes action or only evaluating 
+consequences that the agent could reasonably forsee before acting. Another solution is to adopt the legal notion 
+of ``proximate cause," which only holds the agent responsible for the immediate consequences of their 
+acts, but not for consequences resulting from others' voluntary responses to the agent's original act \cite{consequentialismsep}.
+
+Even without understanding the details of these views, it is clear that they require 
+more data than Kantian ethics and scale poorly with the complexity of the act being evaluated. Even 
+if we cut off the chain of causal reasoning at some point based on 
+one of the rules above, evaluating the consequences of an action is still data-intensive. Even evaluating
+the first or immediate cause of an action requires knowledge about the state of the world before
+and after an action. Kantian ethics, on the other hand, requires only knowledge about the maxim, not 
+knowledge about the state of the world when the maxim is adopted. Consequentialism requires knowledge about 
+the situation in which the act is performed and following the act, whereas Kantian ethics merely requires 
+knowledge about the act itself. For simple acts, this data does not seem unreasonable, but as acts become
+more complex and affect more people, the computational time and space required to calculate and store
+their consequences increases. Kantian ethics, on the other hand, does not suffer as intense of a scaling
+challenge because maxims that affect 1 person and maxims that affect 1 million people both have the same
+representation.
 
@@
 Automated consequentialist ethics would need to represent complex states of the world and causal chains
-in an efficient manner and reason about them. This presents a difficult technical challenge and
+in an efficient manner and reason about them. This both presents a difficult technical challenge and
 impedes the usability of such a system. Automated consequentialist ethics would need to come equipped with 
@@
 and representing this data pose a technical challenge, it also creates a larger ``trusted code base" for 
-the automated system. Trusting a Kantian ethical reasoner merely requires trusting the logical implementation
+the automated system. Trusting my Kantian ethical reasoner merely requires trusting the logical implementation
 of the categorical imperative, but trusting a consequentialist ethical reasoner requires trusting both the
 logical machinery that actually evaluates the consequences of an act and the background/situational
-knowledge that serves as an input to this machinery. There is much more room for debate about 
-the background knowledge/state of the world than there is about the act that the agent performs.
-The Kantian ethical reasoner includes room for 
-disagreement about the formulation of the maxim being evaluated\footnote{For more on the parsing 
-of ethical dilemmas into maxims, see Section AI Ethics}, but the surface of this debate is much smaller
-than the surface of an entire database about actions and their consequences.
+knowledge that serves as an input to this machinery.
 
-Another such debate that an automated consequentialist reasoner would need to take a stance on is 
-the question of what qualifies as a ``good consequence." Simple hedonists associate
+The challenge of understanding and representing the circumstances of action is not unique to consequentialism,
+but is particularly acute for consequentialism. Kantian ethicists robustly debate which circumstances 
+of an action are ``morally relevant" and should be included in the formulation of the maxim\footnote{Powers 
+\cite{powers} identifies this as a challenge for automating Kantian ethics and briefly sketches 
+solutions from O'Neill \cite{constofreason}, Silber \cite{silber}, and Rawls \cite{rawlsconstructivism}. }. Those 
+using my system will need to either automatically or manually formulate maxims, a process that involves 
+common-sense reasoning to determine which circumstances, act, and goal tuples the agent is adopting
+\footnote{For more on the parsing of ethical dilemmas into maxims, see Section AI Ethics}.
+Because Kantian ethics merely evaluates a single maxim, the surface of this debate is much smaller
+than the debate about circumstances and consequences in a consequentialist system. An automated 
+consequentialist system must make such judgements about the act itself, the circumstances in which 
+it is performed, and the circumstances following the act. All ethical theories relativize
+their judgements to the situation in which an act is performed to some extent, but consequentialism
+requires far more knowledge about the world than Kantian ethics.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsubsection{Theory of the Good%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
+Another debate that an automated consequentialist reasoner would need to take a stance on is
+the question of what qualifies as a ``good consequence," or what the theory of the good is. Hedonists associate
 good with the presence of pleasure and the lack of pain. Preference utiliarians believe that good is 
-the satisfaction of desires and is thus related to individuals' preferences, as opposed to some objective
+the satisfaction of desires and is thus related to individuals' preferences, as opposed to some
 sensation of pleasure or pain. Other consequentialists adopt a pluralistic theory of value, under which 
 many different kinds of things are good for different reasons. For example, Moore values beauty and truth 
-and other pluralists value justice, love, and freedom (cite). Welfare utilitarians value a person's 
+and other pluralists value justice, love, and freedom \cite{moorepe}. Welfare utilitarians value a person's 
 welfare and utilitarians of right value states of affairs in which respect for some set of crucial
@@
 consequentialist ethics difficult. Regardless of the theory of the good, a consequentialist ethical 
-reasoner needs to evaluate a state of affairs, which may encompass each involved individual's pleasure, 
-preferences, welfare, freedom, rights, or whatever other criteria make a state good. This not only requires
-a lot of data as I argued above, it also requires judgements about whether or not a state of affairs 
-actually satisifes the relevant criteria for goodness. These judgements are difficult and debateable, 
-and any consequentialist decision requires many of these judgements for each individual involved. As 
-systems become more complex and involve more people and more acts, making these judgements quickly becomes
-difficult, posing a scaling challenge for a consequentialist ethical reasoner. Perfect knowledge of 
-tens of thousands of people's pleasure or preferences or welfare or rights is impossible. Either a human being 
+reasoner needs to evaluate a state of affairs, which encompass each involved individual's pleasure, 
+preferences, welfare, freedom, rights, or whatever other criteria make a state good. This requires
+judgements about whether or not a state of affairs actually satisifes the relevant criteria for goodness. 
+These judgements are difficult and debateable, and any consequentialist decision requires many of 
+these judgements for each individual involved. As systems become more complex and involve more people and 
+more acts, making these judgements quickly becomes difficult, posing a scaling challenge for a 
+consequentialist ethical reasoner. Perfect knowledge of tens of thousands of people's pleasure or 
+preferences or welfare or rights is impossible. Either a human being 
 assigns values to states of affairs, which quickly becomes difficult to scale, or the machine does, 
-which requires massive knowledge and increases room for doubting the system's judgements.
-
+which requires massive common-sense, increases room for doubting the system's judgements, and simplifies
+the judgements. This is a tractable problem, but is much more difficult than the Kantian task of formulating
+and evaluating a maxim.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsubsection{Aggregation%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
 Once an automated consequentialist agent assigns a goodness measurement to each person in a state of affairs, it 
@@
 this value is to aggregate each person's individual goodness score into one complete score for a state. 
-For example, under a simple welfare model, each person may be assigned a welfare score and the total 
-score for a state of affairs may be the sum of the welfare scores for each involved person.
-The more complex the theory of the good, the more difficult that aggregation becomes. For example, 
-pluralistic theories struggle to explain how different kinds of value can be compared. How do we compare
-one unit of beauty to one unit of pleasure? Subjective theories of the good, such as those focused on 
-the sensation of pleasure or an individual's preferences, present difficulties in comparing such 
-subjective measures. Resolving this debate requires that the automated reasoner make a decision about
-one specific aggregation algorithm, but those who disagree with this choice will not trust the reasoner's
-moral judgements.
+For example, under a simple welfare model, each person is assigned a welfare score and the total 
+score for a state of affairs is the sum of the welfare scores for each involved person.
+The more complex the theory of the good, the more difficult this aggregation becomes. For example, 
+pluralistic theories struggle to explain how different kinds of value can be compared \cite{consequentialismsep}. 
+How do we compare one unit of beauty to one unit of pleasure? Subjective theories of the good, such 
+as those focused on the sensation of pleasure or an individual's preferences, present difficulties in 
+comparing subjective measures across people. Resolving this debate requires that the automated reasoner 
+choose one specific aggregation algorithm, but those who disagree with this choice will not trust 
+the reasoner's moral judgements. Moreover, for complex theories of the good, this aggregation algorithm
+may be complex and may require a lot of data.
 
-On the other hand, some consequentialists reject aggregation entirely and instead prefer wholistic
+To solve this problem, some consequentialists reject aggregation entirely and instead prefer wholistic
 evaluations of a state of affairs. While this approach no longer requires that a reasoner define an 
@@
 affairs. Whereas before the reasoner could restrict analysis to a single person, the algorithm must now 
-evaluate an entire state at once, wholistically. Evaluating the goodness of an entire state of affairs is more complicated
+evaluate an entire state wholistically. Evaluating the goodness of an entire state of affairs is more complicated
 than evaluating the goodness of a single person. As consequentialists modulate between aggregation 
 and wholistic evaluation, they face a tradeoff between the difficulty of aggregation and the complexity 
-of goodness measurements for large units like states of affairs. This tradeoff translates to an automated
+of goodness measurements for large states of affairs. This tradeoff also holds for an automated
 consequentialist moral agent. Such an agent either needs to define an aggregation function, thus opening 
 the door to those who disagree with this definition, or needs to evaluate the goodness of entire states
-of affairs, which is a complex and data-intensive philosophical and technical challenge.
-
+of affairs, which is a complex and data-intensive philosophical and technical challenge.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsubsection{Prior Attempts to Formalize Consequentialism%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
 None of the challenges described above are intractable or capture the full literature of 
 all variations of consequentialism. I do not argue that consequentialism is 
-impossible to automate. Instead, each of the challenges above either makes an automated consequentialist
-agent more complex or requires that the developer ``plant certain flags" and take a stance on philosophical
-debates. Such points of difficulty also appear in Kantian ethics, and I deal with them throughout this
-project (see Section What is a Maxim). These difficulties are present in any ethical theory, but consequentialism
-has more points of difficulty than Kantian ethics and is thus more difficult to formalize both computationally
-and philosophically. Given that this project is a proof-of-concept and an early attempt to formalize
-a philosophically rigorous ethical theory, I choose Kantian ethics because it is the easier theory to 
-formalize. Future work could indeed address the challenges above and formalize consequentialism. The more
-ethical theories that comptuational tools can handle, the more valuable computational philosophy becomes 
-for philosophers and AI agents. My project contributes a formalization of one theory that poses fewer
-challenges than others.%
+impossible to automate. Instead, each of the challenges above requires that the developer 
+``plant certain flags" and take a stance on philosophical debates. These difficulties are present in 
+any ethical theory, but consequentialism has more such points of difficulty than Kantian ethics and 
+is thus more difficult to automate both computationally and philosophically.
+
+Because of its intuitive appeal, automated ethicists have tried to formalize consequentialism in the past.
+These efforts cannot escape the debates outlines above. For example, Abel et. al represent ethics as a
+Markov Decision Process (MDP), with reward functions customized to particular ethical dilemmas 
+\cite[3]{util1}. While this appears to be a convenient representation, it either leaves unanswered or 
+takes implicit stances on the debates above. It assumes that consequences can be aggregated just as 
+reward is accumulated in an MDP. It leaves open the question of what the reward function is and thus 
+leaves the theory of the good, arguably the defining trait of a particular consequentialist view, 
+undefined. Similarly, Anderson and Anderson's proposal of a hedonistic act 
+utilitarian automated reasoner chooses hedonism\footnote{Recall that hedonism views pleasure as good
+and pain as bad} as the theory of the good \cite[2]{util2}. Again, their proposal assumes that pleasure and pain can be 
+given numeric values and that these values can be aggregated with a simple sum, taking an implicit
+stance on the aggregation question. Other attempts to automate consequentialist ethics will suffer 
+similar problems because, at some point, to actually use an automated consequentialist moral agent, 
+the debates above will need to be resolved.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
+\isamarkupsubsubsection{What Is Virtue%
+}
+\isamarkuptrue%
+%
 \endisatagdocument
@@
 \begin{isamarkuptext}%
-The virtue ethical tradition predates even consequentialism and has countless variations. Below
-I explain the centrality of virtue and practical wisdom, two common tenets of most virtue ethical theories.
-
-All virtue ethical theories place virtue, or those traits that constitute a good moral character, 
-at the center. Virtue ethicists recommend actions based on the character traits that such actions
-would help cultivate. A virtue is commonly accepted as a character trait that "makes its possessor
-good" \cite{vesep}. For example, under Aristotlean virtue ethics, the virtues are the traits that 
-enable human flourishing, or fulfilling the purpose of a human being. Many modern virtue ethicists abandon
-Aristotle's notion of a ``purpose" of human beings, and instead define virtue in terms of the characteristic
-activity of human beings (in ethical terms, not telelological terms) (cite from gened paper). Just as 
-consequentialists must offer a view of which consequences are good, virtue ethicists must offer some 
-theory of the virtues which justifies and presents a list of the virtues. Such theories are varied in
-the literature, from the classical virtues of courage and temperance to the Buddhist virtue of 
-equanimity to Sen's conception of the virtues as capabilites that serve as ``effective opportunities to 
-undertake the actions and activities" an agent wants to engage in. An automated virtue ethical agent 
-will need to commit to a particular theory of the virtues, opening itself up to criticism from those
-who disagree with this theory of the virtues. Unlike Kantian ethics, who generally agree on the meaning of
-the FUL, virtue ethicists robustly debate which character traits qualify as virtues.
-
+The virtue ethical tradition generally place the virtues, or those traits that constitute a 
+good moral character, at the center. Virtue ethicists recommend actions based on the character traits 
+that such actions would help cultivate. A virtue is commonly accepted as a character trait that 
+"makes its possessor good" \cite{vesep}. For example, under Aristotlean virtue ethics, the virtues 
+are the traits that enable human flourishing or fulfill the purpose of a human being. Many modern 
+virtue ethicists abandon Aristotle's notion of a ``purpose" of human beings, and instead define virtue 
+in terms of the characteristic activity of human beings (in ethical terms, not telelological terms) \cite{snow}. 
+Just as consequentialists must offer a view of which consequences are good, virtue ethicists must offer some 
+theory of the virtues which presents and justifices a list of the virtues. Such theories vary
+from Aristotle's virtues of courage and temperance to the Buddhist virtue of 
+equanimity to Robeyns' summary of Sen's conception of the virtues as capabilites that create
+``effective opportunities to undertake the actions and activities" an agent wants to engage in \cite{robeyns}. 
+An automated virtue ethical agent will need to commit to a particular theory of the virtues, opening 
+itself up to criticism from those who disagree with this theory of the virtues. Unlike Kantian ethicists, 
+who generally agree on the meaning of the FUL, virtue ethicists robustly debate which character traits qualify as virtues.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsubsection{Evaluating Moral Character%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
 Another difficulty with automating virtue ethics is that the unit of evaluation for a virtue ethical
-theory is often a person's entire character. While Kantians evaluate the maxim of an act and utilitarians
+theory is often a person's entire moral character. While Kantians evaluate the maxim of an act and utilitarians
 evaluate the consequences of an act, virtue ethicists evaluate the actor's moral character and their 
@@
 Formalizing the concept of character appears to require significant philosophical and computational
-progress, whereas Kantian ethics automatically presents a formal rule to implement. Precise representations
-of consequences is a central debate in consequentialism, but precise representation of moral character
-is not a central debate in virtue ethics.
+progress, whereas Kantian ethics automatically presents a formal rule to implement.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsubsection{Machine Learning and Virtue Ethics%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
+One potential appeal of virtue ethics is that many virtue ethical theories involve some form of 
+moral habit, which seems to suggest a machine learning approach. Artistotle, for example, argued 
+that cultivating virtuous action requires making such action habitual through moral education. Under 
+one view of virtue ethics, the virtuous act is what the virtuous person would do. Both of these ideas
+imply that ethical behavior can be learned from some dataset of virtuous acts, either those 
+prescribed by a moral teacher or those that a virtuous ideal agent would undertake. Indeed, these 
+theories seem to point towards a machine learning model for computational ethics, in which ethics is 
+learned from a dataset of acts tagged as ethical or not ethical. Such approaches exist in the literature, 
+as in the Delphi system \cite{delphi}.
 
-One potential appeal of virtue ethics is that many virtue ethical theories involve some form of 
-moral education. Artistotle, for example, argued that cultivating virtuous action requires making such
-action habitual through moral education. Under the simple, popular view of virtue ethics, the virtuous
-act is what the virtuous person would do. Both of these theories imply that ethical behavior can be
-learned from some dataset of virtuous behavior, either those prescribed by a moral teacher or those that
-a virtuous ideal agent would undertake. Indeed, these theories seem to point towards a machine learning
-model for computational ethics, in which ethics is learned from a dataset of acts tagged as ethical
-or not ethical. Such approaches exist in the literature and there is a solid body of work attempting 
-to learn ethics from past judgements. My project present a different, top-down approach starting 
-with an ethical theory and representing it in a logic. Both approaches have their merits, but one 
-advantage of my logical approach is that it does not suffer many of the explainability problems that machine learning 
-approaches may experience. Many machine learning algorithms cannot sufficiently explain their decisions
-to a human being, and often find patterns or correlations in datasets that don't actually cohere with 
-the trends and causes that a human being would identify. While there is significant activity and progress
-in explainable machine learning, interactive theorem provers are designed to be explainable at the outset.
-Indeed, Isabelle can even give the axioms and lemmas it used in constructing a proof, allowing a human 
-being to reconstruct the proof independently if they wish. This is, again, not an intractable problem 
-for machine learning approaches to computational ethics, but is one reason to prefer logical approaches.
+Just as prior work in consequentialism takes implicit or explicit stances on debates in consequentialist
+literature, so does work in virtue ethics. For example, the dataset that Delphi uses to learn ethical
+behavior contains implicit views on what the virtues are and how certain acts impact an agent's
+moral character. Because Delphi lacks a specified, explicit theory of virtue, it is impossible to 
+determine which traits the system implicitly classifies as virtues without manually examining the 
+dataset.
 
-Explainability matters more for ethics.%
+Machine learning approaches also may suffer explanability problems that my logical, theorem-prover
+based approach does not experience. Many machine learning algorithms cannot sufficiently explain their 
+decisions to a human being, and often find patterns or correlations in datasets that don't actually 
+cohere with the trends and causes that a human being would identify. While there is significant activity 
+and progress in explainable machine learning, interactive theorem provers are designed to be explainable 
+at the outset. Indeed, Isabelle can even give the axioms and lemmas it used in constructing a proof, 
+allowing a human being to reconstruct the proof independently if they wish. This is, again, not an 
+intractable problem for machine learning approaches to computational ethics, but is one reason to 
+prefer logical approaches.
+
+Explanability is particularly important in the case of ethics because ethical judgements are often 
+controversial and ethics generally requires reflection. First, the most interesting and important
+ethical judgements are those resulting from ethical dilemmas. These judgements are usually controversial, 
+and the answers are not obvious because people's intuitions differ and different theories generate
+different answers. In these cases, explainability is particularly important to convince human beings 
+of the correctness of an ethical judgement. If a machine tells us to kill one person to save five without
+explaining the justification for this decision, using this judgement becomes difficult. Second, ethics
+is generally seen as a reflective subject. Practical reason is the exercise of using reason and thought
+to decide what to do. Someone who believes an automated reasoner's judgements without examining or 
+understanding the reasons for these judgements doesn't seem to be doing ethics correctly\footnote{I make
+this argument precise in Section Is CE Even Good For Us?}. This does not preclude other uses of automated
+ethics, such as automated moral agents or hypothesis generation for philosophy, but it does make computer-
+assisted ethical judgement difficult.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \isatagtheory
-\isacommand{end}\isamarkupfalse%
 %
@@
 \endisadelimtheory
-\isanewline
 %
@@
 %:%24=6%:%
-%:%36=8%:%
-%:%37=9%:%
-%:%38=10%:%
-%:%39=11%:%
-%:%40=12%:%
-%:%41=13%:%
-%:%42=14%:%
-%:%43=15%:%
-%:%44=16%:%
-%:%45=17%:%
-%:%46=18%:%
-%:%47=19%:%
-%:%48=20%:%
-%:%49=21%:%
-%:%50=22%:%
-%:%51=23%:%
-%:%60=26%:%
-%:%72=28%:%
-%:%73=29%:%
-%:%74=30%:%
-%:%75=31%:%
-%:%76=32%:%
-%:%77=33%:%
-%:%78=34%:%
-%:%79=35%:%
-%:%80=36%:%
-%:%81=37%:%
-%:%82=38%:%
-%:%83=39%:%
-%:%84=40%:%
-%:%85=41%:%
-%:%86=42%:%
-%:%87=43%:%
-%:%88=44%:%
-%:%89=45%:%
-%:%90=46%:%
-%:%91=47%:%
-%:%92=48%:%
-%:%93=49%:%
-%:%94=50%:%
-%:%95=51%:%
-%:%96=52%:%
-%:%97=53%:%
-%:%98=54%:%
-%:%99=55%:%
-%:%100=56%:%
-%:%101=57%:%
-%:%102=58%:%
-%:%103=59%:%
-%:%104=60%:%
-%:%105=61%:%
-%:%106=62%:%
-%:%107=63%:%
-%:%108=64%:%
-%:%109=65%:%
-%:%110=66%:%
-%:%111=67%:%
-%:%112=68%:%
-%:%113=69%:%
-%:%114=70%:%
-%:%115=71%:%
-%:%116=72%:%
-%:%117=73%:%
-%:%118=74%:%
-%:%119=75%:%
-%:%120=76%:%
-%:%121=77%:%
-%:%122=78%:%
-%:%123=79%:%
-%:%124=80%:%
-%:%125=81%:%
-%:%126=82%:%
-%:%127=83%:%
-%:%128=84%:%
-%:%129=85%:%
-%:%130=86%:%
-%:%131=87%:%
-%:%132=88%:%
-%:%133=89%:%
-%:%134=90%:%
-%:%135=91%:%
-%:%136=92%:%
-%:%137=93%:%
-%:%138=94%:%
-%:%139=95%:%
-%:%140=96%:%
-%:%141=97%:%
-%:%142=98%:%
-%:%143=99%:%
-%:%144=100%:%
-%:%145=101%:%
-%:%146=102%:%
-%:%147=103%:%
-%:%148=104%:%
-%:%149=105%:%
-%:%150=106%:%
-%:%151=107%:%
-%:%152=108%:%
-%:%153=109%:%
-%:%154=110%:%
-%:%155=111%:%
-%:%156=112%:%
-%:%157=113%:%
-%:%166=116%:%
-%:%178=118%:%
-%:%179=119%:%
-%:%180=120%:%
-%:%181=121%:%
-%:%182=122%:%
-%:%183=123%:%
-%:%184=124%:%
-%:%185=125%:%
-%:%186=126%:%
-%:%187=127%:%
-%:%188=128%:%
-%:%189=129%:%
-%:%190=130%:%
-%:%191=131%:%
-%:%192=132%:%
-%:%193=133%:%
-%:%194=134%:%
-%:%195=135%:%
-%:%196=136%:%
-%:%197=137%:%
-%:%198=138%:%
-%:%199=139%:%
-%:%200=140%:%
-%:%201=141%:%
-%:%202=142%:%
-%:%203=143%:%
-%:%204=144%:%
-%:%205=145%:%
-%:%206=146%:%
-%:%207=147%:%
-%:%208=148%:%
-%:%209=149%:%
-%:%210=150%:%
-%:%211=151%:%
-%:%212=152%:%
-%:%213=153%:%
-%:%214=154%:%
-%:%215=155%:%
-%:%216=156%:%
-%:%217=157%:%
-%:%218=158%:%
-%:%219=159%:%
-%:%220=160%:%
-%:%221=161%:%
-%:%222=162%:%
-%:%223=163%:%
-%:%224=164%:%
-%:%225=165%:%
-%:%226=166%:%
-%:%227=167%:%
-%:%228=168%:%
-%:%229=169%:%
-%:%230=170%:%
-%:%231=171%:%
-%:%232=172%:%
-%:%233=173%:%
-%:%234=174%:%
-%:%235=175%:%
-%:%236=176%:%
-%:%237=177%:%
-%:%238=178%:%
-%:%239=179%:%
-%:%240=180%:%
-%:%241=181%:%
-%:%242=182%:%
-%:%243=183%:%
-%:%244=184%:%
-%:%245=185%:%
-%:%246=186%:%
-%:%247=187%:%
-%:%248=188%:%
-%:%249=189%:%
-%:%250=190%:%
-%:%251=191%:%
-%:%252=192%:%
-%:%253=193%:%
-%:%254=194%:%
-%:%255=195%:%
-%:%256=196%:%
-%:%257=197%:%
-%:%258=198%:%
-%:%259=199%:%
-%:%260=200%:%
-%:%261=201%:%
-%:%262=202%:%
-%:%263=203%:%
-%:%264=204%:%
-%:%265=205%:%
-%:%266=206%:%
-%:%267=207%:%
-%:%268=208%:%
-%:%269=209%:%
-%:%270=210%:%
-%:%271=211%:%
-%:%272=212%:%
-%:%273=213%:%
-%:%274=214%:%
-%:%275=215%:%
-%:%276=216%:%
-%:%277=217%:%
-%:%278=218%:%
-%:%279=219%:%
-%:%280=220%:%
-%:%281=221%:%
-%:%282=222%:%
-%:%283=223%:%
-%:%284=224%:%
-%:%285=225%:%
-%:%286=226%:%
-%:%287=227%:%
-%:%288=228%:%
-%:%289=229%:%
-%:%298=232%:%
-%:%310=234%:%
-%:%311=235%:%
-%:%312=236%:%
-%:%313=237%:%
-%:%314=238%:%
-%:%315=239%:%
-%:%316=240%:%
-%:%317=241%:%
-%:%318=242%:%
-%:%319=243%:%
-%:%320=244%:%
-%:%321=245%:%
-%:%322=246%:%
-%:%323=247%:%
-%:%324=248%:%
-%:%325=249%:%
-%:%326=250%:%
-%:%327=251%:%
-%:%328=252%:%
-%:%329=253%:%
-%:%330=254%:%
-%:%331=255%:%
-%:%332=256%:%
-%:%333=257%:%
-%:%334=258%:%
-%:%335=259%:%
-%:%336=260%:%
-%:%337=261%:%
-%:%338=262%:%
-%:%339=263%:%
-%:%340=264%:%
-%:%341=265%:%
-%:%342=266%:%
-%:%343=267%:%
-%:%344=268%:%
-%:%345=269%:%
-%:%346=270%:%
-%:%347=271%:%
-%:%348=272%:%
-%:%349=273%:%
-%:%350=274%:%
-%:%351=275%:%
-%:%352=276%:%
-%:%353=277%:%
-%:%354=278%:%
-%:%355=279%:%
-%:%356=280%:%
-%:%357=281%:%
-%:%358=282%:%
-%:%359=283%:%
-%:%360=284%:%
-%:%361=285%:%
-%:%369=289%:%
-%:%377=289%:%
+%:%36=9%:%
+%:%37=10%:%
+%:%38=11%:%
+%:%39=12%:%
+%:%40=13%:%
+%:%41=14%:%
+%:%42=15%:%
+%:%43=16%:%
+%:%44=17%:%
+%:%45=18%:%
+%:%46=19%:%
+%:%47=20%:%
+%:%48=21%:%
+%:%49=22%:%
+%:%50=23%:%
+%:%51=24%:%
+%:%52=25%:%
+%:%53=26%:%
+%:%54=27%:%
+%:%55=28%:%
+%:%64=31%:%
+%:%68=33%:%
+%:%80=35%:%
+%:%81=36%:%
+%:%82=37%:%
+%:%83=38%:%
+%:%84=39%:%
+%:%85=40%:%
+%:%86=41%:%
+%:%87=42%:%
+%:%88=43%:%
+%:%89=44%:%
+%:%90=45%:%
+%:%91=46%:%
+%:%92=47%:%
+%:%93=48%:%
+%:%94=49%:%
+%:%95=50%:%
+%:%96=51%:%
+%:%97=52%:%
+%:%98=53%:%
+%:%99=54%:%
+%:%100=55%:%
+%:%101=56%:%
+%:%102=57%:%
+%:%103=58%:%
+%:%104=59%:%
+%:%105=60%:%
+%:%106=61%:%
+%:%107=62%:%
+%:%108=63%:%
+%:%109=64%:%
+%:%110=65%:%
+%:%111=66%:%
+%:%112=67%:%
+%:%113=68%:%
+%:%114=69%:%
+%:%115=70%:%
+%:%116=71%:%
+%:%117=72%:%
+%:%118=73%:%
+%:%119=74%:%
+%:%120=75%:%
+%:%121=76%:%
+%:%122=77%:%
+%:%123=78%:%
+%:%124=79%:%
+%:%125=80%:%
+%:%126=81%:%
+%:%127=82%:%
+%:%128=83%:%
+%:%129=84%:%
+%:%130=85%:%
+%:%131=86%:%
+%:%132=87%:%
+%:%133=88%:%
+%:%134=89%:%
+%:%135=90%:%
+%:%136=91%:%
+%:%137=92%:%
+%:%138=93%:%
+%:%139=94%:%
+%:%140=95%:%
+%:%141=96%:%
+%:%142=97%:%
+%:%143=98%:%
+%:%144=99%:%
+%:%145=100%:%
+%:%146=101%:%
+%:%147=102%:%
+%:%148=103%:%
+%:%149=104%:%
+%:%150=105%:%
+%:%151=106%:%
+%:%152=107%:%
+%:%153=108%:%
+%:%154=109%:%
+%:%155=110%:%
+%:%156=111%:%
+%:%165=113%:%
+%:%177=115%:%
+%:%178=116%:%
+%:%179=117%:%
+%:%180=118%:%
+%:%181=119%:%
+%:%182=120%:%
+%:%183=121%:%
+%:%184=122%:%
+%:%185=123%:%
+%:%186=124%:%
+%:%187=125%:%
+%:%188=126%:%
+%:%189=127%:%
+%:%190=128%:%
+%:%191=129%:%
+%:%192=130%:%
+%:%193=131%:%
+%:%194=132%:%
+%:%195=133%:%
+%:%196=134%:%
+%:%197=135%:%
+%:%198=136%:%
+%:%199=137%:%
+%:%200=138%:%
+%:%201=139%:%
+%:%202=140%:%
+%:%203=141%:%
+%:%204=142%:%
+%:%205=143%:%
+%:%206=144%:%
+%:%207=145%:%
+%:%208=146%:%
+%:%209=147%:%
+%:%218=150%:%
+%:%230=152%:%
+%:%231=153%:%
+%:%232=154%:%
+%:%233=155%:%
+%:%234=156%:%
+%:%235=157%:%
+%:%236=158%:%
+%:%237=159%:%
+%:%238=160%:%
+%:%239=161%:%
+%:%248=163%:%
+%:%260=165%:%
+%:%261=166%:%
+%:%262=167%:%
+%:%263=168%:%
+%:%264=169%:%
+%:%265=170%:%
+%:%266=171%:%
+%:%267=172%:%
+%:%268=173%:%
+%:%269=174%:%
+%:%270=175%:%
+%:%271=176%:%
+%:%272=177%:%
+%:%273=178%:%
+%:%274=179%:%
+%:%275=180%:%
+%:%276=181%:%
+%:%277=182%:%
+%:%278=183%:%
+%:%279=184%:%
+%:%280=185%:%
+%:%281=186%:%
+%:%282=187%:%
+%:%283=188%:%
+%:%284=189%:%
+%:%285=190%:%
+%:%286=191%:%
+%:%287=192%:%
+%:%288=193%:%
+%:%289=194%:%
+%:%290=195%:%
+%:%291=196%:%
+%:%292=197%:%
+%:%293=198%:%
+%:%294=199%:%
+%:%295=200%:%
+%:%296=201%:%
+%:%297=202%:%
+%:%298=203%:%
+%:%299=204%:%
+%:%300=205%:%
+%:%301=206%:%
+%:%302=207%:%
+%:%303=208%:%
+%:%304=209%:%
+%:%305=210%:%
+%:%306=211%:%
+%:%307=212%:%
+%:%308=213%:%
+%:%309=214%:%
+%:%310=215%:%
+%:%311=216%:%
+%:%312=217%:%
+%:%313=218%:%
+%:%314=219%:%
+%:%315=220%:%
+%:%324=223%:%
+%:%336=225%:%
+%:%337=226%:%
+%:%338=227%:%
+%:%339=228%:%
+%:%340=229%:%
+%:%341=230%:%
+%:%342=231%:%
+%:%343=232%:%
+%:%344=233%:%
+%:%345=234%:%
+%:%346=235%:%
+%:%347=236%:%
+%:%348=237%:%
+%:%349=238%:%
+%:%350=239%:%
+%:%351=240%:%
+%:%352=241%:%
+%:%353=242%:%
+%:%354=243%:%
+%:%355=244%:%
+%:%356=245%:%
+%:%357=246%:%
+%:%358=247%:%
+%:%359=248%:%
+%:%360=249%:%
+%:%369=251%:%
+%:%381=253%:%
+%:%382=254%:%
+%:%383=255%:%
+%:%384=256%:%
+%:%385=257%:%
+%:%386=258%:%
+%:%387=259%:%
+%:%388=260%:%
+%:%389=261%:%
+%:%390=262%:%
+%:%391=263%:%
+%:%392=264%:%
+%:%393=265%:%
+%:%394=266%:%
+%:%395=267%:%
+%:%396=268%:%
+%:%397=269%:%
+%:%398=270%:%
+%:%399=271%:%
+%:%400=272%:%
+%:%401=273%:%
+%:%402=274%:%
+%:%403=275%:%
+%:%404=276%:%
+%:%405=277%:%
+%:%414=280%:%
+%:%426=282%:%
+%:%427=283%:%
+%:%428=284%:%
+%:%429=285%:%
+%:%430=286%:%
+%:%431=287%:%
+%:%432=288%:%
+%:%433=289%:%
+%:%434=290%:%
+%:%435=291%:%
+%:%436=292%:%
+%:%437=293%:%
+%:%438=294%:%
+%:%439=295%:%
+%:%440=296%:%
+%:%441=297%:%
+%:%442=298%:%
+%:%443=299%:%
+%:%444=300%:%
+%:%445=301%:%
+%:%446=302%:%
+%:%455=304%:%
+%:%459=306%:%
+%:%471=308%:%
+%:%472=309%:%
+%:%473=310%:%
+%:%474=311%:%
+%:%475=312%:%
+%:%476=313%:%
+%:%477=314%:%
+%:%478=315%:%
+%:%479=316%:%
+%:%480=317%:%
+%:%481=318%:%
+%:%482=319%:%
+%:%483=320%:%
+%:%484=321%:%
+%:%485=322%:%
+%:%494=324%:%
+%:%506=326%:%
+%:%507=327%:%
+%:%508=328%:%
+%:%509=329%:%
+%:%510=330%:%
+%:%511=331%:%
+%:%512=332%:%
+%:%513=333%:%
+%:%514=334%:%
+%:%515=335%:%
+%:%524=337%:%
+%:%536=339%:%
+%:%537=340%:%
+%:%538=341%:%
+%:%539=342%:%
+%:%540=343%:%
+%:%541=344%:%
+%:%542=345%:%
+%:%543=346%:%
+%:%544=347%:%
+%:%545=348%:%
+%:%546=349%:%
+%:%547=350%:%
+%:%548=351%:%
+%:%549=352%:%
+%:%550=353%:%
+%:%551=354%:%
+%:%552=355%:%
+%:%553=356%:%
+%:%554=357%:%
+%:%555=358%:%
+%:%556=359%:%
+%:%557=360%:%
+%:%558=361%:%
+%:%559=362%:%
+%:%560=363%:%
+%:%561=364%:%
+%:%562=365%:%
+%:%563=366%:%
+%:%564=367%:%
+%:%565=368%:%
+%:%566=369%:%
+%:%567=370%:%
+%:%568=371%:%
+%:%569=372%:%
+%:%570=373%:%
+%:%571=374%:%
+%:%572=375%:%
+%:%573=376%:%
+%:%574=377%:%
+%:%575=378%:%

### 2021-10-29 paper/output/document/paper33.tex
some restructuring, added some morethoughts on maxims
did goals

--- 2021-09-26 paper/output/document/paper41.tex
@@
 \begin{isabellebody}%
-\setisabellecontext{paper{\isadigit{4}}{\isadigit{1}}}%
+\setisabellecontext{paper{\isadigit{3}}{\isadigit{3}}}%
 %
@@
 %
+\isamarkupsubsection{Lessons Learned and Goals for Chapter 3%
+}
+\isamarkuptrue%
+%
 \endisatagdocument
@@
 %
+\begin{isamarkuptext}%
+In this chapter, I tested two prior attempts to formalize the Formula of Universal Law and found 
+that these attempts didn't actually capture the FUL correctly. Specifically, certain properties that 
+we expect to hold of the FUL didn't hold of these implementations. In an attempt to remedy these 
+shortcomings, I will present my own custom implementation of the FUL that satisfies these properties
+and represents a version of the FUL that is more faithful to the literature. Before presenting my 
+implementation, I first define some goals for my custom formalization based on learnings from prior
+attempt and from literature discussing the FUL.
+
+The results presented below are summarized in Figure \ref{fig:goalstable}. For each goal, I indicate which 
+interpretations successfully meet that goal. The fact that my custom formalization meets all the goals
+presented indicates that it improves on prior formalization attempts. Below I will explain and justify
+the goals, and in the next chapter I will present my custom formalization.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{figure}
+\centering
+\includegraphics[scale=0.4]{goalstable.png}
+\caption{Table indicating which goals are met by the naive formalization, Kroy's formalization, and 
+the custom formalization respectively..} \label{fig:goalstable}
+\end{figure}
+%
 \isadelimdocument
@@
 \isatagdocument
+%
+\isamarkupsubsubsection{Goals From Prior Attempts%
+}
+\isamarkuptrue%
 %
@@
 \endisadelimdocument
+%
+\begin{isamarkuptext}%
+\textbf{FUl Stronger than DDL} One simple objective that the naive formalization failed to meet is the fact that the FUL should
+not hold in the base logic, dyadic deontic logic. Recall that the naive formalization of the FUL\footnote{
+This formalization reads $\vDash ((\neg \square P A) \longrightarrow O \{\neg A\})$.} held in the 
+base logic, so adding it as an axiom didn't actually make the logic any stronger. This is troubling 
+because the base logic does not actually come equipped with the categorical imperative built-in. It 
+defines basic properties of obligation, such as ought implies can, but holds no axioms that represent
+the formula of universal law. Therefore, if a formalization of the FUL holds in the 
+base logic, then it is too weak to be correct. The naive interpretation holds in DDL but Kroy's formalization
+does not. Because the naive interpretation is no stronger than DDL, it is essentially a control group
+because goals that hold in it hold in DDL itself.
+
+\medskip
+
+\textbf{Obligation Universalizes Across People} Another property of the Formula of Universal Law that any implementation should satisfy is that obligation
+generalizes across people. In other words, if a maxim is obligated for one person, it is obligated
+for all other people as well because maxims are not person-specific. Velleman argues that, because 
+reason is accessible to everyone identically, obligations apply to all people \cite[25]{velleman}. 
+When Kant describes the categorical imperative as the objective principle of the will, he is referring 
+to the fact that, as opposed to a subjective principle, the categorical imperative applies to all 
+rational agents equally $\cite[16]{groundwork}$. At its core, the FUL best handles, ``the temptation 
+to make oneself an exception: selfishness, meanness, advantagetaking, and disregard for the rights 
+of others" \cite[30]{korsgaardFUL}. Kroy latches onto this property and makes it the content of his
+formalization, which essentially says that if an act is permissible for someone, it is permissible for 
+everyone. While Kroy's interpretation clearly satisfies this property, the naive interpretation does not.
+
+\textbf{Contradictory Obligations} Another problem with prior formalizations of the categorical imperative was that they didn't
+prohibit contradictory obligations, partially because DDL itself allows contradictory obligations. 
+Kant subscribes to the general, popular view that morality is supposed to guide action, so ought implies 
+can\footnote{Kohl points out that this principle is referred to as 
+Kant's dictum or Kant's law in the literature. \cite[footnote 1]{kohl}}. Kohl reconstructs his argument for the principle as 
+follows: if the will cannot comply with the moral law, then the moral law has no prescriptive authority 
+for the will \cite[703-4]{kohl}. This defeats the purpose of Kant's theory—to develop an unconditional, categorical imperative 
+for rational agents. Ought implies can requires that obligations never contradict, because an agent 
+can't perform contradictory actions. Therefore, any ethical theory that respects ought implies can, 
+and Kantian ethics in particular, must not result in conflicting obligations. 
+Kant only briefly discusses contradictory obligations in \emph{Metaphysics of Morals}, where he argues that 
+conflicting moral obligations are impossible under his theory \cite[V224]{metaphysicsintro}. Particularly, the categorical imperative generates 
+``strict negative laws of omission", which cannot conflict by definition\footnote{The 
+kinds of obligations generated by the FUL are called ``perfect duties" which arise from ``contradictions 
+in conception," or maxims that we cannot even concieve of universalizing. These duties are always negative 
+and thus never conflict. Kant also presents ``imperfect duties," generated from ``contradictions in will,"
+or maxims that we can concieve of universalizing but would never want to. These duties tend to be broader, 
+such as ``improve oneself" or "help others," and are secondary to perfect duties. My project only analyzes 
+perfect duties, as these are stronger than imperfect duties.} \cite[45]{timmerman}.
+
+Neither the naive formalization nor Kroy's formalization disallow contradictory obligations. Additionally,
+during testing, I realized that contradictory obligations are closely related to two other properties
+that also fail in both of these systems. First is the idea that obligation implies permissibility, or 
+that obligation is a stronger property than permissibility. If there are no contradictory obligations, 
+then this property holds because actions are either permissible or prohibited and obligation contradicts
+prohibition. Moreover, in a system with contradictory obligations, this property fails because A is
+obligated and prohibited and therefore not permisible. Indeed, formalizing this property below shows 
+that this follows from the definition of implication in propositional logic and Sledgehammer is able
+to show this property easily.
+
+\medskip%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}{\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymand}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymnot}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}A{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{by}\isamarkupfalse%
+\ simp%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+\textbf{Distributive Property} Another property related to contradictory obligations is the distributive property for the obligation
+operator\footnote{Formally, $O\{A\} \wedge O\{B\} \longleftrightarrow O\{A \wedge B\}$.}. This is 
+another property that we expect to hold. The rough English translation of  $O \{ A \wedge B \} $ is ``you are obligated to 
+do both A and B". The rough English translation of $O\{A\} \wedge O\{B\}$ is ``you are obligated to do A 
+and you are obligated to do B." We think those English sentences mean the same thing, so they should mean 
+the same thing in this logic as well. Moreover, if that (rather intuitive) property holds, then contradictory
+obligations are impossible, as shown in the below proof.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ distributive{\isacharunderscore}implies{\isacharunderscore}no{\isacharunderscore}contradictions{\isacharcolon}\ \isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}A\ B{\isachardot}\ {\isasymTurnstile}\ {\isacharparenleft}{\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymand}\ O\ {\isacharbraceleft}B{\isacharbraceright}{\isacharparenright}\ \isactrlbold {\isasymequiv}\ O\ {\isacharbraceleft}A\ \isactrlbold {\isasymand}\ B{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}A{\isachardot}\ {\isasymTurnstile}{\isacharparenleft}\ \isactrlbold {\isasymnot}{\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymand}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ {\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{using}\isamarkupfalse%
+\ O{\isacharunderscore}diamond\ assms\ \isacommand{by}\isamarkupfalse%
+\ blast%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+Thus, while testing contradictory obligations, I also test the distributive property for the 
+obligation operator. Again, this property fails in the naive formalization and for Kroy's formalization.
+This property is a goal for my custom formalization.
+
+\medskip
+
+\textbf{Un-universalizable Actions} The last goal inspired by prior attempts comes from a test performed for Kroy's formalization. Under 
+the naive, ethics 101 reading of the formula of universal law, it prohibits lying because, in a world 
+where everyone simultaneously lies, lying is impossible. In other words, not everyone can simultaneously
+lie because the institution of lying and believing would break down. More precisely, the FUL should 
+show that actions that aren't universalizable are prohibited, because those acts cannot be willed in 
+a world where they are universalized. This property fails to hold in both the naive formalization 
+and Kroy's formalization and is a goal for my custom formalization.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsubsection{Goals From Philosophical Literature%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
+The goals above come from moral intuition, properties of Kantian ethics, and logical requirements. 
+Philosophers have robustly debated the meaning of the Formula of Universal Law, and the results of these 
+debates should be incorporated into a custom formalization of the categorical imperative.
+
+\textbf{Maxims} First, note
+that Kant does not evaluate the correctness of acts, but rather of maxims. Therefore, any faithful formalization
+of the categorical imperative must evaluate maxims, not acts. This requires representing a maxim, which neither
+of the prior attempts do.
+
+\medskip%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+\textbf{Practical Contradiction Interpretation} Second, Kantians debate the correct interpretation of the formula of universal law because Kant appears to 
+interpret the universalizability test in different ways. Korsgaard argues for the practical contradiction 
+interpretation, broadly accepted as correct within the philosophical community $\cite[177]{ebelsduggan}$.
+Because her argument is broadly accepted, I will make it a goal to represent the practical contradiction
+interpretation of the FUL in my custom formalization. The naive formalization and Kroy's formalization
+clearly do not meet this goal.
+
+Below, I briefly reconstruct Korsgaard's argument for the practical contradiction interpretation. While 
+she believes that the text partially supports this interpretation, her argument is philosophical and 
+derives its strength from the plausibility of the practical contradiction interpretation.
+
+Recall that the formula of universal law is “act only in accordance with that maxim through which you can at the 
+same time will that it become a universal law” $\cite[4:421]{groundwork}$. To determine if a maxim can be willed as a 
+universal law, one must use the “universalizability test,” which requires imagining a world in which 
+everyone for all of time has willed the maxim. If willing the maxim in such a world generates a contradiction, 
+then the action is prohibited. There are three interpretations of what sort of contradiction is necessary: 
+(1) the teleological view, prohibiting actions that conflict with some assumed teleological end when 
+universalized, (2) the logical contradiction view, prohibiting maxims that are logically impossible 
+when universalized (such as the lying example discussed earlier), and (3) the practical contradiction view, prohibiting maxims that are self-defeating 
+when universalized.
+
+Under the logical contradiction interpretation, falsely promising to repay a loan to get some quick cash
+fails the universalizability test because, in such a world, the practice of promising would die out so 
+making a false promise would be impossible. Korsgaard appeals to Dietrichson \cite{dietrichson} to construct the example of 
+a mother killing her children that tend to cry more than average so that she can get some 
+sleep at night. Universalizing this maxim does not generate a logical contradiction, but it is clearly 
+morally wrong. The problem here is that killing is a natural action, which Korsgaard distinguishes from 
+a practice, like promising. Natural actions will never be logically impossible, so the logical contradiction 
+view fails to prohibit them.
+
+Under the teleological contradiction interpretation, a maxim is prohibited if it undercuts some natural 
+or assigned purpose for some practice, act, or object. For example, the purpose of promising is to 
+create a system of mutual trust and false promising undercuts this purpose and is thus prohibited. The problem 
+with this view is that it assumes that the agent is committed, either because of their own goals or 
+because of some property of a rational will, to some teleological system. Acton formulates Hegel's argument that \cite{acton},
+an agent doesn't have to be committed to promising as a system of mutual trust. Korsgaard concludes that 
+assigning teleological purposes to actions is difficult because ``such purposes may have
+nothing to do with what the agent wants or ought rationally to want, or even with what
+any human being wants." If the agent is not committed to the purpose, then will not see a contradiction 
+in willing an act that violates this purpose.
+
+This difficulty with the teleological contradiction interpretation drives Korsgaard to look for purposes
+that an agent must necessarily be committed to, and she concludes that this must be the purpose of the 
+maxim itself. By willing a maxim, an agent commits themselves to the goal of the maxim, and thus cannot 
+rationally will a system in which this goal is undercut. This system satisfactorily handles natural actions
+like those of the sleep-deprived mother: in willing the end of sleeping through the night, she is 
+implicitly willing that she be alive in order to secure and enjoy her sleep. If any mother is allowed to kill
+any loud child, then she cannot be secure in the possession of her life, because her own mother may have 
+grown frustrated with her crying. Her willing this maxim thwarts the end that she sought to secure.
+
+The practical contradiction interpretation not only addresses the problems with the first two 
+interpretations, it also offers a much more satisfying explanation of why certain maxims are immoral. 
+The problem is not the existence of a contradiction itself, but instead the fact that these maxims 
+involve parasitic behavior on social conditions that the agent seeks to benefit from. The false promiser 
+simultaneously wants to abuse the system of promising and benefit from it, and is thus making an exception 
+of themselves. It is this kind of free-riding that the universalizability test seeks to draw out. The test
+raises the same kinds of objections that the question ``What if everyone did that?" seeks to draw out.
+
+Note that the practical contradiction interpretation is strictly stronger than the logical contradiction
+interpretation. Actions that are not universalizble, like lying, are also not effective means to any end
+when universalized because they become impossible. Therefore, a formalization of the practical contradiction
+interpretation must still obey the earlier goal that non-universalizable acts be prohibited.%
+\end{isamarkuptext}\isamarkuptrue%
 %
@@
 \endinput
-%:%file=~/Desktop/cs91r/paper/paper41.thy%:%
+%:%file=~/Desktop/cs91r/paper/paper33.thy%:%
+%:%24=6%:%
+%:%36=8%:%
+%:%37=9%:%
+%:%38=10%:%
+%:%39=11%:%
+%:%40=12%:%
+%:%41=13%:%
+%:%42=14%:%
+%:%43=15%:%
+%:%44=16%:%
+%:%45=17%:%
+%:%46=18%:%
+%:%47=19%:%
+%:%50=22%:%
+%:%51=23%:%
+%:%52=24%:%
+%:%53=25%:%
+%:%54=26%:%
+%:%55=27%:%
+%:%63=29%:%
+%:%75=31%:%
+%:%76=32%:%
+%:%77=33%:%
+%:%78=34%:%
+%:%79=35%:%
+%:%80=36%:%
+%:%81=37%:%
+%:%82=38%:%
+%:%83=39%:%
+%:%84=40%:%
+%:%85=41%:%
+%:%86=42%:%
+%:%87=43%:%
+%:%88=44%:%
+%:%89=45%:%
+%:%90=46%:%
+%:%91=47%:%
+%:%92=48%:%
+%:%93=49%:%
+%:%94=50%:%
+%:%95=51%:%
+%:%96=52%:%
+%:%97=53%:%
+%:%98=54%:%
+%:%99=55%:%
+%:%100=56%:%
+%:%101=57%:%
+%:%102=58%:%
+%:%103=59%:%
+%:%104=60%:%
+%:%105=61%:%
+%:%106=62%:%
+%:%107=63%:%
+%:%108=64%:%
+%:%109=65%:%
+%:%110=66%:%
+%:%111=67%:%
+%:%112=68%:%
+%:%113=69%:%
+%:%114=70%:%
+%:%115=71%:%
+%:%116=72%:%
+%:%117=73%:%
+%:%118=74%:%
+%:%119=75%:%
+%:%120=76%:%
+%:%121=77%:%
+%:%122=78%:%
+%:%123=79%:%
+%:%124=80%:%
+%:%125=81%:%
+%:%126=82%:%
+%:%127=83%:%
+%:%128=84%:%
+%:%129=85%:%
+%:%130=86%:%
+%:%132=90%:%
+%:%133=90%:%
+%:%136=91%:%
+%:%140=91%:%
+%:%141=91%:%
+%:%150=93%:%
+%:%151=94%:%
+%:%152=95%:%
+%:%153=96%:%
+%:%154=97%:%
+%:%155=98%:%
+%:%156=99%:%
+%:%158=101%:%
+%:%159=101%:%
+%:%160=102%:%
+%:%161=103%:%
+%:%164=104%:%
+%:%168=104%:%
+%:%169=104%:%
+%:%170=104%:%
+%:%179=106%:%
+%:%180=107%:%
+%:%181=108%:%
+%:%182=109%:%
+%:%183=110%:%
+%:%184=111%:%
+%:%185=112%:%
+%:%186=113%:%
+%:%187=114%:%
+%:%188=115%:%
+%:%189=116%:%
+%:%190=117%:%
+%:%191=118%:%
+%:%200=120%:%
+%:%212=122%:%
+%:%213=123%:%
+%:%214=124%:%
+%:%215=125%:%
+%:%216=126%:%
+%:%217=127%:%
+%:%218=128%:%
+%:%219=129%:%
+%:%220=130%:%
+%:%221=131%:%
+%:%225=135%:%
+%:%226=136%:%
+%:%227=137%:%
+%:%228=138%:%
+%:%229=139%:%
+%:%230=140%:%
+%:%231=141%:%
+%:%232=142%:%
+%:%233=143%:%
+%:%234=144%:%
+%:%235=145%:%
+%:%236=146%:%
+%:%237=147%:%
+%:%238=148%:%
+%:%239=149%:%
+%:%240=150%:%
+%:%241=151%:%
+%:%242=152%:%
+%:%243=153%:%
+%:%244=154%:%
+%:%245=155%:%
+%:%246=156%:%
+%:%247=157%:%
+%:%248=158%:%
+%:%249=159%:%
+%:%250=160%:%
+%:%251=161%:%
+%:%252=162%:%
+%:%253=163%:%
+%:%254=164%:%
+%:%255=165%:%
+%:%256=166%:%
+%:%257=167%:%
+%:%258=168%:%
+%:%259=169%:%
+%:%260=170%:%
+%:%261=171%:%
+%:%262=172%:%
+%:%263=173%:%
+%:%264=174%:%
+%:%265=175%:%
+%:%266=176%:%
+%:%267=177%:%
+%:%268=178%:%
+%:%269=179%:%
+%:%270=180%:%
+%:%271=181%:%
+%:%272=182%:%
+%:%273=183%:%
+%:%274=184%:%
+%:%275=185%:%
+%:%276=186%:%
+%:%277=187%:%
+%:%278=188%:%
+%:%279=189%:%
+%:%280=190%:%
+%:%281=191%:%
+%:%282=192%:%
+%:%283=193%:%
+%:%284=194%:%
+%:%285=195%:%
+%:%286=196%:%

### 2021-10-29 paper/output/document/paper41.tex
did goals

@@
 \begin{isamarkuptext}%
-One problem with prior formalizations of the categorical imperative was that they didn't
-prohibit contradictory obligations, partially because DDL itself allows contradictory obligations. 
-Kant subscribes to the general, popular view that morality is supposed to guide action, so ought implies 
-can\footnote{Kohl points out that this principle is referred to as 
-Kant's dictum or Kant's law in the literature. \cite[footnote 1]{kohl}}. Kohl reconstructs his argument for the principle as 
-follows: if the will cannot comply with the moral law, then the moral law has no prescriptive authority 
-for the will \cite[703-4]{kohl}. This defeats the purpose of Kant's theory—to develop an unconditional, categorical imperative 
-for rational agents. Ought implies can requires that obligations never contradict, because an agent 
-can't perform contradictory actions. Therefore, any ethical theory that respects ought implies can, 
-and Kantian ethics in particular, must not result in conflicting obligations.
-
-Kant only briefly discusses contradictory obligations in \emph{Metaphysics of Morals}, where he argues that 
-conflicting moral obligations are impossible under his theory \cite[V224]{metaphysicsintro}. Particularly, the categorical imperative generates 
-``strict negative laws of omission", which cannot conflict by definition \cite[45]{timmerman}.\footnote{The 
-kinds of obligations generated by the FUL are called ``perfect duties" which arise from ``contradictions 
-in conception," or maxims that we cannot even concieve of universalizing. These duties are always negative 
-and thus never conflict. Kant also presents ``imperfect duties," generated from ``contradictions in will,"
-or maxims that we can concieve of universalizing but would never want to. These duties tend to be broader, 
-such as ``improve oneself" or "help others," and are secondary to perfect duties. My project only analyzes 
-perfect duties, as these are stronger than imperfect duties.}
-
 When analyzing the naive formalization and Kroy's formalization, I learned that DDL and the prior 
@@
 
-Generalization across people coheres with Kantian ethics—maxims are not person-specific.
-Indeed, Velleman argues that, because reason is accessible to everyone identically, obligations apply 
-to all people \cite[25]{velleman}. When Kant describes the categorical imperative as the objective 
-principle of the will, he is referring to the fact that, as opposed to a subjective principle, the categorical
-imperative applies to all rational agents equally $\cite[16]{groundwork}$.
-
 Generalization across worlds is a consequence of the fact that my interpretation does not make use of the 
@@
 added axiom that prohibits contradictory obligations (recall that Kroy's formalization allowed contradictory
-obligations). The proof is clear: if maxims are either permissible or prohibited and obligation contradicts
-prohibition, then obligation must result in permissibility. Moreover, this property REQUIRES that 
-there be no contradictory obligations. Formally, in the base logic DDL, I can show the sentence 
-$(O \{A\} \wedge O \{\neg A\}) \mathbf{\longrightarrow} (\neg (O \{A\} \mathbf{\longrightarrow}  P \{A\})) w$
-\footnote{Sledgehammer can show this sentence to be true in DDL and in Kroy's formalization.}.
-In English, if A and not A are obligated, then A can be obligated but not permissible.
-
-Is there anything philosophically interesting here? Something about the possibility of genuine moral 
-conflict?%
+obligations).%
 \end{isamarkuptext}\isamarkuptrue%
@@
 }%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+\isanewline
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ distribution{\isacharcolon}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymand}\ O\ {\isacharbraceleft}B{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymTurnstile}\ O\ {\isacharbraceleft}A\ \isactrlbold {\isasymand}\ B{\isacharbraceright}{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{using}\isamarkupfalse%
+\ assms\ no{\isacharunderscore}contradictions\ \isacommand{by}\isamarkupfalse%
+\ fastforce%
 \endisatagproof
@@
 %:%305=243%:%
-%:%308=245%:%
-%:%309=246%:%
-%:%310=247%:%
-%:%311=248%:%
-%:%312=249%:%
-%:%313=250%:%
+%:%308=246%:%
+%:%309=247%:%
+%:%310=248%:%
+%:%311=249%:%
+%:%313=251%:%
 %:%314=251%:%
 %:%315=252%:%
-%:%316=253%:%
-%:%317=254%:%
-%:%318=255%:%
-%:%319=256%:%
-%:%320=257%:%
-%:%321=258%:%
-%:%322=259%:%
-%:%323=260%:%
-%:%324=261%:%
-%:%325=262%:%
-%:%326=263%:%
-%:%327=264%:%
-%:%328=265%:%
-%:%329=266%:%
-%:%330=267%:%
-%:%331=268%:%
-%:%332=269%:%
-%:%334=271%:%
-%:%335=271%:%
-%:%336=272%:%
-%:%338=273%:%
-%:%339=274%:%
-%:%340=274%:%
-%:%341=275%:%
-%:%342=276%:%
-%:%343=276%:%
-%:%345=277%:%
-%:%346=278%:%
-%:%347=279%:%
-%:%355=281%:%
-%:%367=283%:%
-%:%368=284%:%
-%:%369=285%:%
-%:%370=286%:%
-%:%371=287%:%
-%:%372=288%:%
-%:%374=291%:%
-%:%375=291%:%
-%:%377=292%:%
-%:%378=293%:%
-%:%379=294%:%
-%:%380=295%:%
-%:%381=295%:%
-%:%382=296%:%
-%:%383=297%:%
-%:%384=297%:%
-%:%386=297%:%
-%:%390=297%:%
-%:%391=297%:%
-%:%392=298%:%
-%:%393=298%:%
-%:%394=298%:%
-%:%403=300%:%
-%:%404=301%:%
-%:%405=302%:%
-%:%406=303%:%
-%:%407=304%:%
-%:%408=305%:%
-%:%409=306%:%
-%:%410=307%:%
-%:%411=308%:%
-%:%412=309%:%
-%:%413=310%:%
-%:%414=311%:%
-%:%415=312%:%
-%:%416=313%:%
-%:%417=314%:%
-%:%418=315%:%
-%:%419=316%:%
-%:%421=318%:%
-%:%422=318%:%
-%:%423=319%:%
-%:%425=320%:%
-%:%426=321%:%
-%:%427=321%:%
-%:%428=322%:%
-%:%429=323%:%
-%:%430=323%:%
-%:%432=324%:%
-%:%433=325%:%
-%:%434=325%:%
-%:%435=326%:%
-%:%436=327%:%
-%:%437=327%:%
-%:%438=328%:%
-%:%439=328%:%
-%:%441=328%:%
-%:%445=328%:%
-%:%446=328%:%
-%:%448=329%:%
-%:%449=330%:%
-%:%450=331%:%
-%:%451=332%:%
-%:%452=333%:%
-%:%453=334%:%
-%:%454=335%:%
-%:%455=336%:%
-%:%456=337%:%
-%:%457=338%:%
-%:%458=339%:%
-%:%466=339%:%
-%:%467=340%:%
-%:%468=341%:%
-%:%469=341%:%
-%:%470=342%:%
-%:%471=343%:%
-%:%472=343%:%
-%:%473=344%:%
-%:%474=344%:%
-%:%476=344%:%
-%:%480=344%:%
-%:%481=344%:%
-%:%483=345%:%
-%:%484=346%:%
-%:%485=347%:%
-%:%486=348%:%
-%:%487=349%:%
-%:%488=350%:%
-%:%498=352%:%
-%:%499=353%:%
-%:%500=354%:%
-%:%501=355%:%
-%:%502=356%:%
-%:%503=357%:%
-%:%504=358%:%
-%:%505=359%:%
-%:%506=360%:%
-%:%507=361%:%
-%:%508=362%:%
-%:%509=363%:%
-%:%510=364%:%
-%:%511=365%:%
-%:%512=366%:%
-%:%513=367%:%
-%:%514=368%:%
-%:%515=369%:%
-%:%516=370%:%
-%:%517=371%:%
-%:%521=373%:%
-%:%522=374%:%
-%:%523=375%:%
-%:%524=376%:%
-%:%525=377%:%
-%:%534=379%:%
-%:%546=381%:%
-%:%547=382%:%
-%:%548=383%:%
-%:%549=384%:%
-%:%553=386%:%
-%:%554=387%:%
-%:%555=388%:%
-%:%556=389%:%
-%:%557=390%:%
-%:%558=391%:%
-%:%559=392%:%
-%:%560=393%:%
-%:%561=394%:%
-%:%562=395%:%
-%:%563=396%:%
-%:%564=397%:%
-%:%565=398%:%
-%:%566=399%:%
-%:%567=400%:%
-%:%568=401%:%
-%:%570=403%:%
-%:%571=403%:%
-%:%573=404%:%
-%:%574=405%:%
-%:%575=405%:%
-%:%576=406%:%
-%:%577=406%:%
-%:%579=407%:%
-%:%580=408%:%
-%:%581=408%:%
-%:%582=409%:%
-%:%583=409%:%
-%:%585=410%:%
-%:%586=411%:%
-%:%587=411%:%
-%:%588=412%:%
-%:%589=413%:%
-%:%590=413%:%
-%:%591=414%:%
-%:%593=415%:%
-%:%596=417%:%
-%:%597=418%:%
-%:%598=419%:%
-%:%600=421%:%
-%:%601=421%:%
-%:%602=422%:%
-%:%604=423%:%
-%:%605=424%:%
-%:%606=425%:%
-%:%607=426%:%
-%:%608=427%:%
-%:%609=427%:%
-%:%610=428%:%
-%:%611=429%:%
-%:%612=429%:%
-%:%613=430%:%
-%:%615=431%:%
-%:%616=432%:%
-%:%617=433%:%
-%:%618=434%:%
-%:%619=435%:%
-%:%620=435%:%
-%:%621=436%:%
-%:%622=437%:%
-%:%623=437%:%
-%:%624=438%:%
-%:%626=439%:%
-%:%627=440%:%
-%:%628=441%:%
-%:%629=442%:%
-%:%630=443%:%
-%:%633=445%:%
-%:%634=446%:%
-%:%636=448%:%
-%:%637=448%:%
-%:%638=449%:%
-%:%639=450%:%
-%:%640=451%:%
-%:%641=452%:%
-%:%648=453%:%
-%:%649=453%:%
-%:%650=454%:%
-%:%651=454%:%
-%:%652=455%:%
-%:%653=455%:%
-%:%655=456%:%
-%:%656=457%:%
-%:%657=457%:%
-%:%658=458%:%
-%:%659=458%:%
-%:%660=459%:%
-%:%661=459%:%
-%:%662=459%:%
-%:%663=460%:%
-%:%673=462%:%
-%:%674=463%:%
-%:%675=464%:%
-%:%676=465%:%
-%:%677=466%:%
-%:%678=467%:%
-%:%679=468%:%
-%:%680=469%:%
-%:%682=471%:%
-%:%683=471%:%
-%:%684=472%:%
-%:%685=472%:%
-%:%686=473%:%
-%:%688=474%:%
-%:%689=475%:%
-%:%690=475%:%
-%:%691=476%:%
-%:%692=477%:%
-%:%693=477%:%
-%:%694=478%:%
-%:%696=479%:%
-%:%697=480%:%
-%:%698=480%:%
-%:%699=481%:%
-%:%700=482%:%
-%:%701=482%:%
-%:%702=483%:%
-%:%703=484%:%
-%:%705=485%:%
-%:%706=485%:%
-%:%707=486%:%
-%:%708=487%:%
-%:%710=488%:%
-%:%711=488%:%
-%:%712=489%:%
-%:%719=490%:%
-%:%720=490%:%
-%:%721=491%:%
-%:%722=491%:%
-%:%723=492%:%
-%:%724=492%:%
-%:%725=492%:%
-%:%726=493%:%
-%:%727=493%:%
-%:%728=494%:%
-%:%729=494%:%
-%:%730=494%:%
-%:%731=495%:%
-%:%732=495%:%
-%:%734=496%:%
-%:%744=498%:%
-%:%745=499%:%
-%:%746=500%:%
-%:%747=501%:%
-%:%748=502%:%
-%:%749=503%:%
-%:%750=504%:%
-%:%751=505%:%
-%:%752=506%:%
-%:%753=507%:%
-%:%754=508%:%
-%:%755=509%:%
-%:%756=510%:%
-%:%757=511%:%
-%:%758=512%:%
-%:%759=513%:%
-%:%760=514%:%
-%:%761=515%:%
-%:%762=516%:%
-%:%763=517%:%
-%:%764=518%:%
-%:%765=519%:%
-%:%766=520%:%
-%:%767=521%:%
-%:%768=522%:%
-%:%769=523%:%
-%:%770=524%:%
-%:%771=525%:%
-%:%772=526%:%
-%:%773=527%:%
-%:%774=528%:%
-%:%775=529%:%
-%:%776=530%:%
-%:%777=531%:%
-%:%778=532%:%
-%:%779=533%:%
-%:%780=534%:%
-%:%781=535%:%
-%:%782=536%:%
-%:%783=537%:%
-%:%787=539%:%
-%:%788=540%:%
-%:%789=541%:%
-%:%791=543%:%
-%:%792=543%:%
-%:%793=544%:%
-%:%794=545%:%
-%:%795=545%:%
-%:%797=545%:%
-%:%801=545%:%
-%:%802=545%:%
-%:%804=546%:%
-%:%805=547%:%
-%:%806=548%:%
-%:%807=549%:%
-%:%808=550%:%
-%:%809=551%:%
-%:%819=554%:%
-%:%820=555%:%
-%:%821=556%:%
-%:%830=558%:%
-%:%842=560%:%
-%:%843=561%:%
-%:%844=562%:%
-%:%845=563%:%
-%:%846=564%:%
-%:%847=565%:%
-%:%848=566%:%
-%:%849=567%:%
-%:%850=568%:%
-%:%851=569%:%
-%:%852=570%:%
-%:%853=571%:%
-%:%854=572%:%
-%:%855=573%:%
-%:%856=574%:%
-%:%857=575%:%
-%:%858=576%:%
-%:%859=577%:%
-%:%860=578%:%
-%:%861=579%:%
-%:%863=581%:%
-%:%864=581%:%
-%:%865=582%:%
-%:%868=583%:%
-%:%872=583%:%
-%:%873=583%:%
-%:%878=583%:%
-%:%881=584%:%
-%:%882=585%:%
-%:%883=585%:%
-%:%884=586%:%
-%:%887=587%:%
-%:%891=587%:%
-%:%892=587%:%
-%:%897=587%:%
-%:%900=588%:%
-%:%901=589%:%
-%:%902=589%:%
-%:%903=590%:%
-%:%906=591%:%
-%:%910=591%:%
-%:%911=591%:%
-%:%916=591%:%
-%:%919=592%:%
-%:%920=593%:%
-%:%921=593%:%
-%:%922=594%:%
-%:%925=595%:%
-%:%929=595%:%
-%:%930=595%:%
-%:%939=597%:%
-%:%940=598%:%
-%:%941=599%:%
-%:%942=600%:%
-%:%943=601%:%
-%:%944=602%:%
-%:%945=603%:%
-%:%947=605%:%
-%:%948=605%:%
-%:%949=606%:%
-%:%950=607%:%
-%:%951=607%:%
-%:%953=607%:%
-%:%957=607%:%
-%:%958=607%:%
-%:%960=608%:%
-%:%961=609%:%
-%:%962=610%:%
-%:%963=611%:%
-%:%964=612%:%
-%:%965=613%:%
-%:%966=614%:%
-%:%967=615%:%
-%:%968=616%:%
-%:%969=617%:%
-%:%970=618%:%
-%:%980=620%:%
-%:%981=621%:%
-%:%983=623%:%
-%:%984=623%:%
-%:%985=624%:%
-%:%988=625%:%
-%:%992=625%:%
-%:%993=625%:%
-%:%995=626%:%
-%:%1005=628%:%
-%:%1006=629%:%
-%:%1008=631%:%
-%:%1009=631%:%
-%:%1010=632%:%
-%:%1013=633%:%
-%:%1017=633%:%
-%:%1018=633%:%
-%:%1019=633%:%
-%:%1021=634%:%
-%:%1022=635%:%
-%:%1032=637%:%
-%:%1033=638%:%
-%:%1034=639%:%
-%:%1035=640%:%
-%:%1036=641%:%
-%:%1037=642%:%
-%:%1038=643%:%
-%:%1039=644%:%
-%:%1040=645%:%
-%:%1041=646%:%
-%:%1042=647%:%
-%:%1043=648%:%
-%:%1047=650%:%
-%:%1048=651%:%
-%:%1049=652%:%
-%:%1051=654%:%
-%:%1052=654%:%
-%:%1053=655%:%
-%:%1054=656%:%
-%:%1055=657%:%
-%:%1056=657%:%
-%:%1058=657%:%
-%:%1062=657%:%
-%:%1063=657%:%
-%:%1065=658%:%
-%:%1066=659%:%
-%:%1067=660%:%
-%:%1068=661%:%
-%:%1069=662%:%
-%:%1070=663%:%
-%:%1071=664%:%
-%:%1072=665%:%
-%:%1073=666%:%
-%:%1074=667%:%
-%:%1084=669%:%
-%:%1085=670%:%
-%:%1086=671%:%
-%:%1088=673%:%
-%:%1089=673%:%
-%:%1090=674%:%
-%:%1091=675%:%
-%:%1092=675%:%
-%:%1094=675%:%
-%:%1098=675%:%
-%:%1099=675%:%
-%:%1101=676%:%
-%:%1102=677%:%
-%:%1103=678%:%
-%:%1104=679%:%
-%:%1105=680%:%
-%:%1106=681%:%
-%:%1107=682%:%
-%:%1108=683%:%
-%:%1109=684%:%
-%:%1110=685%:%
-%:%1120=687%:%
-%:%1121=688%:%
-%:%1122=689%:%
-%:%1123=690%:%
-%:%1125=692%:%
-%:%1126=692%:%
-%:%1127=693%:%
-%:%1130=694%:%
-%:%1134=694%:%
-%:%1135=694%:%
-%:%1136=694%:%
-%:%1138=695%:%
-%:%1144=695%:%
-%:%1147=696%:%
-%:%1148=697%:%
-%:%1149=697%:%
-%:%1150=698%:%
-%:%1153=699%:%
-%:%1157=699%:%
-%:%1158=699%:%
-%:%1159=699%:%
-%:%1161=700%:%
-%:%1167=700%:%
-%:%1170=701%:%
-%:%1171=702%:%
-%:%1172=702%:%
-%:%1173=703%:%
-%:%1174=704%:%
-%:%1177=705%:%
-%:%1181=705%:%
-%:%1182=705%:%
-%:%1183=705%:%
-%:%1185=706%:%
-%:%1186=707%:%
-%:%1196=709%:%
-%:%1197=710%:%
-%:%1198=711%:%
-%:%1199=712%:%
-%:%1200=713%:%
-%:%1201=714%:%
-%:%1202=715%:%
-%:%1211=717%:%
-%:%1223=719%:%
-%:%1224=720%:%
-%:%1225=721%:%
-%:%1226=722%:%
-%:%1228=724%:%
-%:%1229=724%:%
-%:%1230=725%:%
-%:%1231=726%:%
-%:%1232=726%:%
-%:%1234=726%:%
-%:%1238=726%:%
-%:%1239=726%:%
-%:%1241=727%:%
-%:%1242=728%:%
-%:%1243=729%:%
-%:%1244=730%:%
-%:%1245=731%:%
-%:%1246=732%:%
-%:%1247=733%:%
-%:%1248=734%:%
-%:%1249=735%:%
-%:%1250=736%:%
-%:%1251=737%:%
-%:%1252=737%:%
+%:%317=253%:%
+%:%318=254%:%
+%:%319=254%:%
+%:%320=255%:%
+%:%321=256%:%
+%:%322=256%:%
+%:%324=257%:%
+%:%325=258%:%
+%:%326=259%:%
+%:%334=261%:%
+%:%346=263%:%
+%:%347=264%:%
+%:%348=265%:%
+%:%349=266%:%
+%:%350=267%:%
+%:%351=268%:%
+%:%353=271%:%
+%:%354=271%:%
+%:%356=272%:%
+%:%357=273%:%
+%:%358=274%:%
+%:%359=275%:%
+%:%360=275%:%
+%:%361=276%:%
+%:%362=277%:%
+%:%363=277%:%
+%:%365=277%:%
+%:%369=277%:%
+%:%370=277%:%
+%:%371=278%:%
+%:%372=278%:%
+%:%373=278%:%
+%:%382=280%:%
+%:%383=281%:%
+%:%384=282%:%
+%:%385=283%:%
+%:%386=284%:%
+%:%387=285%:%
+%:%388=286%:%
+%:%389=287%:%
+%:%390=288%:%
+%:%391=289%:%
+%:%392=290%:%
+%:%393=291%:%
+%:%394=292%:%
+%:%395=293%:%
+%:%396=294%:%
+%:%397=295%:%
+%:%398=296%:%
+%:%400=298%:%
+%:%401=298%:%
+%:%402=299%:%
+%:%404=300%:%
+%:%405=301%:%
+%:%406=301%:%
+%:%407=302%:%
+%:%408=303%:%
+%:%409=303%:%
+%:%411=304%:%
+%:%412=305%:%
+%:%413=305%:%
+%:%414=306%:%
+%:%415=307%:%
+%:%416=307%:%
+%:%417=308%:%
+%:%418=308%:%
+%:%420=308%:%
+%:%424=308%:%
+%:%425=308%:%
+%:%427=309%:%
+%:%428=310%:%
+%:%429=311%:%
+%:%430=312%:%
+%:%431=313%:%
+%:%432=314%:%
+%:%433=315%:%
+%:%434=316%:%
+%:%435=317%:%
+%:%436=318%:%
+%:%437=319%:%
+%:%445=319%:%
+%:%446=320%:%
+%:%447=321%:%
+%:%448=321%:%
+%:%449=322%:%
+%:%450=323%:%
+%:%451=323%:%
+%:%452=324%:%
+%:%453=324%:%
+%:%455=324%:%
+%:%459=324%:%
+%:%460=324%:%
+%:%462=325%:%
+%:%463=326%:%
+%:%464=327%:%
+%:%465=328%:%
+%:%466=329%:%
+%:%467=330%:%
+%:%477=332%:%
+%:%478=333%:%
+%:%479=334%:%
+%:%480=335%:%
+%:%481=336%:%
+%:%482=337%:%
+%:%483=338%:%
+%:%484=339%:%
+%:%485=340%:%
+%:%486=341%:%
+%:%487=342%:%
+%:%488=343%:%
+%:%489=344%:%
+%:%490=345%:%
+%:%491=346%:%
+%:%492=347%:%
+%:%493=348%:%
+%:%494=349%:%
+%:%495=350%:%
+%:%496=351%:%
+%:%500=353%:%
+%:%501=354%:%
+%:%502=355%:%
+%:%503=356%:%
+%:%504=357%:%
+%:%513=359%:%
+%:%525=361%:%
+%:%526=362%:%
+%:%527=363%:%
+%:%528=364%:%
+%:%532=366%:%
+%:%533=367%:%
+%:%534=368%:%
+%:%535=369%:%
+%:%536=370%:%
+%:%537=371%:%
+%:%538=372%:%
+%:%539=373%:%
+%:%540=374%:%
+%:%541=375%:%
+%:%542=376%:%
+%:%543=377%:%
+%:%544=378%:%
+%:%545=379%:%
+%:%546=380%:%
+%:%547=381%:%
+%:%549=383%:%
+%:%550=383%:%
+%:%552=384%:%
+%:%553=385%:%
+%:%554=385%:%
+%:%555=386%:%
+%:%556=386%:%
+%:%558=387%:%
+%:%559=388%:%
+%:%560=388%:%
+%:%561=389%:%
+%:%562=389%:%
+%:%564=390%:%
+%:%565=391%:%
+%:%566=391%:%
+%:%567=392%:%
+%:%568=393%:%
+%:%569=393%:%
+%:%570=394%:%
+%:%572=395%:%
+%:%575=397%:%
+%:%576=398%:%
+%:%577=399%:%
+%:%579=401%:%
+%:%580=401%:%
+%:%581=402%:%
+%:%583=403%:%
+%:%584=404%:%
+%:%585=405%:%
+%:%586=406%:%
+%:%587=407%:%
+%:%588=407%:%
+%:%589=408%:%
+%:%590=409%:%
+%:%591=409%:%
+%:%592=410%:%
+%:%594=411%:%
+%:%595=412%:%
+%:%596=413%:%
+%:%597=414%:%
+%:%598=415%:%
+%:%599=415%:%
+%:%600=416%:%
+%:%601=417%:%
+%:%602=417%:%
+%:%603=418%:%
+%:%605=419%:%
+%:%606=420%:%
+%:%607=421%:%
+%:%608=422%:%
+%:%609=423%:%
+%:%612=425%:%
+%:%613=426%:%
+%:%615=428%:%
+%:%616=428%:%
+%:%617=429%:%
+%:%618=430%:%
+%:%619=431%:%
+%:%620=432%:%
+%:%627=433%:%
+%:%628=433%:%
+%:%629=434%:%
+%:%630=434%:%
+%:%631=435%:%
+%:%632=435%:%
+%:%634=436%:%
+%:%635=437%:%
+%:%636=437%:%
+%:%637=438%:%
+%:%638=438%:%
+%:%639=439%:%
+%:%640=439%:%
+%:%641=439%:%
+%:%642=440%:%
+%:%652=442%:%
+%:%653=443%:%
+%:%654=444%:%
+%:%655=445%:%
+%:%656=446%:%
+%:%657=447%:%
+%:%658=448%:%
+%:%659=449%:%
+%:%661=451%:%
+%:%662=451%:%
+%:%663=452%:%
+%:%664=452%:%
+%:%665=453%:%
+%:%667=454%:%
+%:%668=455%:%
+%:%669=455%:%
+%:%670=456%:%
+%:%671=457%:%
+%:%672=457%:%
+%:%673=458%:%
+%:%675=459%:%
+%:%676=460%:%
+%:%677=460%:%
+%:%678=461%:%
+%:%679=462%:%
+%:%680=462%:%
+%:%681=463%:%
+%:%682=464%:%
+%:%684=465%:%
+%:%685=465%:%
+%:%686=466%:%
+%:%687=467%:%
+%:%689=468%:%
+%:%690=468%:%
+%:%691=469%:%
+%:%698=470%:%
+%:%699=470%:%
+%:%700=471%:%
+%:%701=471%:%
+%:%702=472%:%
+%:%703=472%:%
+%:%704=472%:%
+%:%705=473%:%
+%:%706=473%:%
+%:%707=474%:%
+%:%708=474%:%
+%:%709=474%:%
+%:%710=475%:%
+%:%711=475%:%
+%:%713=476%:%
+%:%723=478%:%
+%:%724=479%:%
+%:%725=480%:%
+%:%726=481%:%
+%:%727=482%:%
+%:%728=483%:%
+%:%729=484%:%
+%:%730=485%:%
+%:%731=486%:%
+%:%732=487%:%
+%:%733=488%:%
+%:%734=489%:%
+%:%735=490%:%
+%:%736=491%:%
+%:%737=492%:%
+%:%738=493%:%
+%:%739=494%:%
+%:%740=495%:%
+%:%741=496%:%
+%:%742=497%:%
+%:%743=498%:%
+%:%744=499%:%
+%:%745=500%:%
+%:%746=501%:%
+%:%747=502%:%
+%:%748=503%:%
+%:%749=504%:%
+%:%750=505%:%
+%:%751=506%:%
+%:%752=507%:%
+%:%753=508%:%
+%:%754=509%:%
+%:%755=510%:%
+%:%756=511%:%
+%:%757=512%:%
+%:%758=513%:%
+%:%759=514%:%
+%:%760=515%:%
+%:%761=516%:%
+%:%762=517%:%
+%:%766=519%:%
+%:%767=520%:%
+%:%768=521%:%
+%:%770=523%:%
+%:%771=523%:%
+%:%772=524%:%
+%:%773=525%:%
+%:%774=525%:%
+%:%776=525%:%
+%:%780=525%:%
+%:%781=525%:%
+%:%783=526%:%
+%:%784=527%:%
+%:%785=528%:%
+%:%786=529%:%
+%:%787=530%:%
+%:%788=531%:%
+%:%798=534%:%
+%:%799=535%:%
+%:%800=536%:%
+%:%809=538%:%
+%:%821=540%:%
+%:%822=541%:%
+%:%823=542%:%
+%:%824=543%:%
+%:%825=544%:%
+%:%826=545%:%
+%:%827=546%:%
+%:%828=547%:%
+%:%829=548%:%
+%:%830=549%:%
+%:%831=550%:%
+%:%832=551%:%
+%:%833=552%:%
+%:%834=553%:%
+%:%836=555%:%
+%:%837=555%:%
+%:%838=556%:%
+%:%841=557%:%
+%:%845=557%:%
+%:%846=557%:%
+%:%851=557%:%
+%:%854=558%:%
+%:%855=559%:%
+%:%856=559%:%
+%:%857=560%:%
+%:%860=561%:%
+%:%864=561%:%
+%:%865=561%:%
+%:%870=561%:%
+%:%873=562%:%
+%:%874=563%:%
+%:%875=563%:%
+%:%876=564%:%
+%:%879=565%:%
+%:%883=565%:%
+%:%884=565%:%
+%:%889=565%:%
+%:%892=566%:%
+%:%893=567%:%
+%:%894=567%:%
+%:%895=568%:%
+%:%898=569%:%
+%:%902=569%:%
+%:%903=569%:%
+%:%912=571%:%
+%:%913=572%:%
+%:%914=573%:%
+%:%915=574%:%
+%:%916=575%:%
+%:%917=576%:%
+%:%918=577%:%
+%:%920=579%:%
+%:%921=579%:%
+%:%922=580%:%
+%:%923=581%:%
+%:%924=581%:%
+%:%926=581%:%
+%:%930=581%:%
+%:%931=581%:%
+%:%933=582%:%
+%:%934=583%:%
+%:%935=584%:%
+%:%936=585%:%
+%:%937=586%:%
+%:%938=587%:%
+%:%939=588%:%
+%:%940=589%:%
+%:%941=590%:%
+%:%942=591%:%
+%:%943=592%:%
+%:%953=594%:%
+%:%954=595%:%
+%:%956=597%:%
+%:%957=597%:%
+%:%958=598%:%
+%:%961=599%:%
+%:%965=599%:%
+%:%966=599%:%
+%:%968=600%:%
+%:%978=602%:%
+%:%979=603%:%
+%:%981=605%:%
+%:%982=605%:%
+%:%983=606%:%
+%:%986=607%:%
+%:%990=607%:%
+%:%991=607%:%
+%:%992=607%:%
+%:%994=608%:%
+%:%995=609%:%
+%:%1005=611%:%
+%:%1006=612%:%
+%:%1007=613%:%
+%:%1008=614%:%
+%:%1012=616%:%
+%:%1013=617%:%
+%:%1014=618%:%
+%:%1016=620%:%
+%:%1017=620%:%
+%:%1018=621%:%
+%:%1019=622%:%
+%:%1020=623%:%
+%:%1021=623%:%
+%:%1023=623%:%
+%:%1027=623%:%
+%:%1028=623%:%
+%:%1030=624%:%
+%:%1031=625%:%
+%:%1032=626%:%
+%:%1033=627%:%
+%:%1034=628%:%
+%:%1035=629%:%
+%:%1036=630%:%
+%:%1037=631%:%
+%:%1038=632%:%
+%:%1039=633%:%
+%:%1049=635%:%
+%:%1050=636%:%
+%:%1051=637%:%
+%:%1053=639%:%
+%:%1054=639%:%
+%:%1055=640%:%
+%:%1056=641%:%
+%:%1057=641%:%
+%:%1059=641%:%
+%:%1063=641%:%
+%:%1064=641%:%
+%:%1066=642%:%
+%:%1067=643%:%
+%:%1068=644%:%
+%:%1069=645%:%
+%:%1070=646%:%
+%:%1071=647%:%
+%:%1072=648%:%
+%:%1073=649%:%
+%:%1074=650%:%
+%:%1075=651%:%
+%:%1085=653%:%
+%:%1086=654%:%
+%:%1087=655%:%
+%:%1088=656%:%
+%:%1090=658%:%
+%:%1091=658%:%
+%:%1092=659%:%
+%:%1095=660%:%
+%:%1099=660%:%
+%:%1100=660%:%
+%:%1101=660%:%
+%:%1103=661%:%
+%:%1109=661%:%
+%:%1112=662%:%
+%:%1113=663%:%
+%:%1114=663%:%
+%:%1115=664%:%
+%:%1118=665%:%
+%:%1122=665%:%
+%:%1123=665%:%
+%:%1124=665%:%
+%:%1126=666%:%
+%:%1132=666%:%
+%:%1135=667%:%
+%:%1136=668%:%
+%:%1137=668%:%
+%:%1138=669%:%
+%:%1139=670%:%
+%:%1142=671%:%
+%:%1146=671%:%
+%:%1147=671%:%
+%:%1148=671%:%
+%:%1150=672%:%
+%:%1151=673%:%
+%:%1157=673%:%
+%:%1160=674%:%
+%:%1161=675%:%
+%:%1162=675%:%
+%:%1163=676%:%
+%:%1164=677%:%
+%:%1167=678%:%
+%:%1171=678%:%
+%:%1172=678%:%
+%:%1173=678%:%
+%:%1182=680%:%
+%:%1183=681%:%
+%:%1184=682%:%
+%:%1185=683%:%
+%:%1186=684%:%
+%:%1187=685%:%
+%:%1188=686%:%
+%:%1197=688%:%
+%:%1209=690%:%
+%:%1210=691%:%
+%:%1211=692%:%
+%:%1212=693%:%
+%:%1214=695%:%
+%:%1215=695%:%
+%:%1216=696%:%
+%:%1217=697%:%
+%:%1218=697%:%
+%:%1220=697%:%
+%:%1224=697%:%
+%:%1225=697%:%
+%:%1227=698%:%
+%:%1228=699%:%
+%:%1229=700%:%
+%:%1230=701%:%
+%:%1231=702%:%
+%:%1232=703%:%
+%:%1233=704%:%
+%:%1234=705%:%
+%:%1235=706%:%
+%:%1236=707%:%
+%:%1237=708%:%
+%:%1238=708%:%

### 2021-10-30 paper/output/document/whykant.tex
cleaned whykant

@@
 \begin{isamarkuptext}%
-In this thesis, I automate Kantian ethics. Deontological theories are attractive candidates for automation
-because, as Powers argues, rules are generally computationally tractable \cite[1]{powers}. Intuitively, algorithms are 
-rules or procedures for problem solving and Kantian ethics, specifically the Formula of Universal Law,
-is one such procedure for the problem of making ethical judgements. I will make this intuition precise by
+In this thesis, I automate Kantian ethics. In 2006, Powers posited that deontological theories are 
+attractive candidates for automation because rules are generally computationally tractable \cite[1]{powers}. 
+Intuitively, algorithms are rules or procedures for problem solving and Kantian ethics offer one such 
+procedure for the problem of making ethical judgements. I will make this intuition precise by
 arguing that Kantian ethics is natural to formalize because evaluating a maxim requires little additional
-data about the world and a maxim is relatively easy to represent to a computer. Moreover, while all 
-ethical theories have debates that an automated ethical system will need to take a stance on, these debates
-are less frequent and controversial in the case of Kantian ethics as compared to consequentialism and 
+data about the world and a maxim is relatively easy to represent to a computer. All 
+ethical traditions have debates that an automated ethical system will need to take a stance on, but these debates
+are less frequent and less controversial for Kantian ethics than for consequentialism and 
 virtue ethics.
 
-I do not aim to show that Kantian ethics is the only tractable theory to automate or
+I do not aim to show that Kantian ethics is the only tractable theory to automate and
 to present a comprehensive overview of all consequentialist or virtue ethical theories. Instead, I 
 present a sample of some approaches in each tradition and argue that Kantian ethics is more straightforward 
-to formalize than these approaches. Insofar as my project serves as an early proof-of-concept for 
-computational ethics, I choose to automate the ethical theory most amenable to automation.
-
-Future work could and likele should address the challenges I outline in this section. The more ethical
-theories that computational tools can handle, the more valuable computational philosophy becomes
-both for philosophers and for AI agents. My project merely contributes a formalization of one theory that 
+to formalize than these approaches. Future work could and should address the challenges I outline in 
+this section. The more ethical theories that computational tools can handle, the more valuable 
+computational philosophy becomes both for philosophers and for AI agents. Insofar as my project serves 
+as an early proof-of-concept for computational ethics, I choose to automate an ethical theory that 
 poses fewer challenges than others.%
@@
 \begin{isamarkuptext}%
-Kant's theory is based on the idea of practical reason, which is the kind of reason that we 
+Kant's theory is centered on practical reason, which is the kind of reason that we 
 use to decide what to do. In \emph{The Groundwork of the Metaphysics of Morals}, Kant's most influential 
 text on ethics, he explains that rational beings are unique because we can act ``in accordance with 
-the representations of laws" \cite[4:412]{groundwork}. A ball thrown into the air acts according to 
-the laws of physics. It cannot ask itself, ``Should I fall back to the ground?" It simply falls. 
-A rational being on the other hand, can ask themselves ``Should I act on this reason?" As Korsgaard describes it, when 
-choosing which desire to act on, ``it is as if there is something over and above all of your desires, 
-somethig which is you, and which chooses which desire to act on" \cite[100]{sources}. Rational beings are
-set apart by this reflective capacity. A rational being's behavior is purposive and their 
-actions are guided by practical reason. They have reasons for acting, even when these reasons may be 
-opaque to them. Kant calls the operation of practical reason the will.
+the representations of laws" \cite[4:412]{groundwork}. In contrast, a ball thrown into the air acts 
+according to the laws of physics themselves. It cannot ask itself, ``Should I fall back to the ground?" 
+It simply falls. A rational being on the other hand, can ask themselves ``Should I act on this reason?" 
+As Korsgaard describes it, when choosing which desire to act on, ``it is as if there is something over 
+and above all of your desires, something which is you, and which chooses which desire to act on" \cite[100]{sources}. 
+Rational beings are set apart by this reflective capacity. A rational being's behavior is purposive and 
+their actions are guided by practical reason. They have reasons for acting, even when these reasons may be 
+opaque to them. This operation of practical reason is what Kant calls the will.
 
-The will operates by willing maxims, which are its percieved reasons for acting. Kant defines a maxim as 
-the ``subjective principle of willing," which is the reason that the will \emph{subjectively} gives 
-to itself for acting \cite[16, footnote 1]{groundwork}. There is debate about what exactly must be 
+The will operates by adopting, or willing, maxims, which are its percieved reasons for acting. Kant defines a maxim as 
+the ``subjective principle of willing," or the reason that the will \emph{subjectively} gives 
+to itself for acting \cite[16 footnote 1]{groundwork}. There is debate about what exactly must be 
 included in a maxim, but most philosophers agree that a maxim consists of some combination of circumstances, 
-act, and goal\footnote{For more discussion of the definition of a maxim, see Section What Is a Maxim}.
-One example of a maxim is ``When I am hungry, I will eat a doughnut in order to satisfy my sweet tooth." 
-When a moral agent wills this maxim, they decide to act on it. They commit themselves to the end in the maxim 
+act, and goal.\footnote{For more discussion of the definition of a maxim, see Section What Is a Maxim}
+One example of a maxim is ``when I am hungry, I will eat a doughnut in order to satisfy my sweet tooth." 
+When an agent wills this maxim, they decide to act on it. They commit themselves to the end in the maxim 
 (e.g. satisfying your sweet tooth). They represent their action, to themselves, as following the 
-principle given by this maxim. It is maxims that Kant evaluates as obligatory or prohibited. He argues that
-certain maxims have a form or logical structure that requires any rational agent to will them, and these
-maxims are obligatory.
+principle given by this maxim. Because a maxim captures an agent's principle of action, Kant evaluates
+maxims are obligatory or prohibited. He argues that certain maxims have a form or logical structure 
+that requires any rational agent to will them, and these maxims are obligatory.
 
-The form of an obligatory maxim is given by the categorical imperative, Kant's supreme rule of morality. 
+The form of an obligatory maxim is given by the categorical imperative, or the supreme rule of morality. 
 An imperative is a command, such as ``Close the door" or "Eat the doughnut in order to satisfy your 
-sweet tooth." A categorical imperative holds unconditionally for all rational agents under all 
+sweet tooth." An imperative is categorical if it holds unconditionally for all rational agents under all 
 circumstances. Kant argues that the moral law must be a categorical imperative, for otherwise it would 
@@
 the only thing that can have unconditional authority over a rational will is 
-the rational will itself. Velleman clarifies this argument by claiming that no one can tell you what 
-reasons to act on because you can always ask why you 
+the rational will itself. In Velleman's version of this argument, he claims that no one else can tell you what 
+to do because you can always ask why you 
 should obey their authority. The only authority that you cannot question is the authority of your own 
@@
 reasoning that makes this statement true is not specific to any person, but is universal across people. 
-Therefore, if I have sufficient reasont to will a maxim, so does every other rational agent. There is 
+Therefore, if I have sufficient reason to will a maxim, so does every other rational agent. There is 
 nothing special about the operation of my practical reason that other reasoners don't have access to. 
@@
 The above is not meant to serve as a full defense of Kant's ethical theory, as that is outside the scope
-of this thesis. Instead, I aim to briefly reconstruct an argument for Kant's ethical theory in the hopes 
+of this thesis. Instead, I briefly reconstruct an argument for Kant's ethical theory in the hopes 
 of offering context for the implementation of the FUL I present later in the thesis. Additionally, understanding 
@@
 \begin{isamarkuptext}%
-Kantian ethics is natural to formalize because the categorical imperative, and the FUL in particular, 
+Kantian ethics is natural to formalize because the categorical imperative, particularly the FUL, 
 is a formal principle of practical reason. In other words, the FUL is a property of reason related 
@@
 (beyond those included in a maxim), the agent's mental state, or any other contingent facts. Instead, 
-it is purely a property of a proposed principle for action. This formalism makes Kantian ethics an 
+it is purely a property of the proposed principle for action. This formalism makes Kantian ethics an 
 attractive candidate for formalization. While other ethical theories often rely on many facts about 
@@
 affairs or moral character. A maxim is a principle with a well-defined form, so representing a maxim
-to the computer merely requires capturing this form. This both reduces the computational complexity
+to the computer merely requires capturing this form. This property not only reduces the computational complexity
 (in terms of time and space) of representing a maxim, it also make the system easier for human reasoners
@@
 I do not argue that Kantian ethics is the only theory possible to formalize, but instead that Kantian
-ethics is relatively easier to formalize. Indeed, like any ethical theory, Kantian ethics contains 
-several debates that philosophers disagree on. In this project, I assume stances on debates about
-what exactly constitutes the form of a maxim and the correct precise interpretation of the Formula of 
+ethics is relatively easier to formalize. Indeed, like any ethical theory, the Kantian tradition contains 
+debates that philosophers disagree on. In this project, I assume stances on debates about
+what exactly constitutes the form of a maxim and the correct interpretation of the Formula of 
 Universal Law. Those who disagree with my stances will not trust the judgements of my system. Unlike
@@
 A consequentialist ethical theory is, broadly speaking, any ethical theory that evaluates an action by evaluating 
-its consequences\footnote{There is long debate about what exactly makes an ethical theory consequentialist \cite{consequentialismsep}. 
-For this paper, I will focus on theories that place the moral worth of an act in its the consequences.}. For example, 
+its consequences. \footnote{There is long debate about what exactly makes an ethical theory consequentialist \cite{consequentialismsep}. 
+For this paper, I will focus on theories that place the moral worth of an act in its the consequences.} For example, 
 utilitarianism is a form of consequentialism in which the moral action 
@@
 on the consequences of action distinguishes consequentialists from Kantians, who derive the moral worth
-of an action from the maxim that is acted on as determined at the time of action. Some debates
-in the consequentialist tradition include discussions of which consequences of an action matter,
-what exactly constitutes a ``good" consequence, and how we can aggregate the consequences of an action
-for all the individuals involved.%
+of an action from the maxim that is acted on. Some debates in the consequentialist tradition include 
+which consequences of an action matter, what exactly constitutes a ``good" consequence, and how we can 
+aggregate the consequences of an action over all the individuals involved.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 impossible task. Moreover, compiling this database of consequences requires 
-answering difficult questions about which consequences were actually caused by an action\footnote
-{maybe cite the debate about difficulties in determining causation?}.
+answering difficult questions about which consequences were actually caused by an action.\footnote
+{maybe cite the debate about difficulties in determining causation?}
 
-These challenges also apply to human reasoners, so most consequentialists do not actually think that 
-agents need to calculate all the consequences of their actions. Plausible strategies to avoid this problem
-include stopping calculation early because constant calculation paralyzes action or only evaluating 
-consequences that the agent could reasonably forsee before acting. Another solution is to adopt the legal notion 
-of ``proximate cause," which only holds the agent responsible for the immediate consequences of their 
+These challenges also apply to human reasoners, so most consequentialists do not actually adopt the naivie
+view that agents need to calculate all the consequences of their actions. Plausible strategies to avoid 
+this problem include stopping calculation early because constant calculation paralyzes action or only 
+evaluating consequences that the agent could reasonably forsee before acting. Another solution is the 
+``proximate cause" approach, which only holds the agent responsible for the immediate consequences of their 
 acts, but not for consequences resulting from others' voluntary responses to the agent's original act \cite{consequentialismsep}.
@@
 the situation in which the act is performed and following the act, whereas Kantian ethics merely requires 
-knowledge about the act itself. For simple acts, this data does not seem unreasonable, but as acts become
+knowledge about the act itself. For simple acts, collecting this data may not seem unreasonable, but as acts become
 more complex and affect more people, the computational time and space required to calculate and store
-their consequences increases. Kantian ethics, on the other hand, does not suffer as intense of a scaling
-challenge because maxims that affect 1 person and maxims that affect 1 million people both have the same
+their consequences increases. Kantian ethics, on the other hand, does not suffer this scaling
+challenge because maxims that affect 1 person and maxims that affect 1 million people share the same
 representation.
@@
 The fact that consequentialism requires more knowledge about the world makes it more difficult to formalize.
-Automated consequentialist ethics would need to represent complex states of the world and causal chains
+Automated consequentialist ethical systems would need to represent complex states of the world and causal chains
 in an efficient manner and reason about them. This both presents a difficult technical challenge and
-impedes the usability of such a system. Automated consequentialist ethics would need to come equipped with 
+impedes the usability of such a system. Such a system would need to come equipped with 
 a large enough database of knowledge about the world to extrapolate the consequences of an actions and
@@
 the automated system. Trusting my Kantian ethical reasoner merely requires trusting the logical implementation
-of the categorical imperative, but trusting a consequentialist ethical reasoner requires trusting both the
-logical machinery that actually evaluates the consequences of an act and the background/situational
-knowledge that serves as an input to this machinery.
+of the categorical imperative and the formulation of a maxim, but trusting a consequentialist ethical 
+reasoner requires trusting both the logical machinery that actually evaluates the act and the 
+background/situational knowledge that serves as an input to this machinery.
 
@@
 but is particularly acute for consequentialism. Kantian ethicists robustly debate which circumstances 
-of an action are ``morally relevant" and should be included in the formulation of the maxim\footnote{Powers 
+of an action are ``morally relevant" and should be included in the formulation of the maxim.\footnote{Powers 
 \cite{powers} identifies this as a challenge for automating Kantian ethics and briefly sketches 
-solutions from O'Neill \cite{constofreason}, Silber \cite{silber}, and Rawls \cite{rawlsconstructivism}. }. Those 
-using my system will need to either automatically or manually formulate maxims, a process that involves 
-common-sense reasoning to determine which circumstances, act, and goal tuples the agent is adopting
-\footnote{For more on the parsing of ethical dilemmas into maxims, see Section AI Ethics}.
+solutions from O'Neill \cite{constofreason}, Silber \cite{silber}, and Rawls \cite{rawlsconstructivism}. } Those 
+using my system will need to automatically or manually formulate maxims, a process that involves 
+common-sense reasoning to determine which circumstances, act, and goal tuples the agent is adopting.
+\footnote{For more on the challenge of parsing of ethical dilemmas into maxims, see Section AI Ethics}
 Because Kantian ethics merely evaluates a single maxim, the surface of this debate is much smaller
@@
 the question of what qualifies as a ``good consequence," or what the theory of the good is. Hedonists associate
-good with the presence of pleasure and the lack of pain. Preference utiliarians believe that good is 
-the satisfaction of desires and is thus related to individuals' preferences, as opposed to some
+good with the presence of pleasure and the absence of pain. Preference utiliarians believe that good is 
+the satisfaction of desires and is thus derived from individuals' preferences, as opposed to some
 sensation of pleasure or pain. Other consequentialists adopt a pluralistic theory of value, under which 
@@
 and other pluralists value justice, love, and freedom \cite{moorepe}. Welfare utilitarians value a person's 
-welfare and utilitarians of right value states of affairs in which respect for some set of crucial
+welfare and utilitarians of right value states of affairs in which respect for some set of
 rights is maximized \cite{consequentialismsep}.
@@
 Once an automated consequentialist agent assigns a goodness measurement to each person in a state of affairs, it 
-must also calculate an overall goodness measurement for this state of affairs. One approach to assigning
+must also calculate an overall goodness measurement for the state of affairs. One approach to assigning
 this value is to aggregate each person's individual goodness score into one complete score for a state. 
@@
 as those focused on the sensation of pleasure or an individual's preferences, present difficulties in 
-comparing subjective measures across people. Resolving this debate requires that the automated reasoner 
+comparing different people's subjective measures. Resolving this debate requires that the automated reasoner 
 choose one specific aggregation algorithm, but those who disagree with this choice will not trust 
@@
 impossible to automate. Instead, each of the challenges above requires that the developer 
-``plant certain flags" and take a stance on philosophical debates. These difficulties are present in 
+``plant certain flags" and take a stance on certain philosophical debates. Such debates are present in 
 any ethical theory, but consequentialism has more such points of difficulty than Kantian ethics and 
-is thus more difficult to automate both computationally and philosophically.
+is thus more difficult to automate.
 
@@
 Markov Decision Process (MDP), with reward functions customized to particular ethical dilemmas 
-\cite[3]{util1}. While this appears to be a convenient representation, it either leaves unanswered or 
+\cite[3]{util1}. While this is a convenient representation, it either leaves unanswered or 
 takes implicit stances on the debates above. It assumes that consequences can be aggregated just as 
@@
 utilitarian automated reasoner chooses hedonism\footnote{Recall that hedonism views pleasure as good
-and pain as bad} as the theory of the good \cite[2]{util2}. Again, their proposal assumes that pleasure and pain can be 
+and pain as bad.} as the theory of the good \cite[2]{util2}. Again, their proposal assumes that pleasure and pain can be 
 given numeric values and that these values can be aggregated with a simple sum, taking an implicit
 stance on the aggregation question. Other attempts to automate consequentialist ethics will suffer 
-similar problems because, at some point, to actually use an automated consequentialist moral agent, 
-the debates above will need to be resolved.%
+similar problems because, at some point, a useful automated consequentialist moral agent will need 
+to resolve the above debates.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-The virtue ethical tradition generally place the virtues, or those traits that constitute a 
-good moral character, at the center. Virtue ethicists recommend actions based on the character traits 
+The virtue ethical tradition places the virtues, or those traits that constitute a 
+good moral character, at the center. Virtue ethicists evaluate actions based on the character traits 
 that such actions would help cultivate. A virtue is commonly accepted as a character trait that 
-"makes its possessor good" \cite{vesep}. For example, under Aristotlean virtue ethics, the virtues 
+``makes its possessor good" \cite{vesep}. For example, under Aristotlean virtue ethics, virtues 
 are the traits that enable human flourishing or fulfill the purpose of a human being. Many modern 
@@
 from Aristotle's virtues of courage and temperance to the Buddhist virtue of 
-equanimity to Robeyns' summary of Sen's conception of the virtues as capabilites that create
+equanimity \cite{aristotle, mcrae}. Another theory is Sen's conception of the virtues as capabilites that create
 ``effective opportunities to undertake the actions and activities" an agent wants to engage in \cite{robeyns}. 
@@
 Formalizing the concept of character appears to require significant philosophical and computational
-progress, whereas Kantian ethics automatically presents a formal rule to implement.%
+progress, whereas Kantian ethics immediately presents a formal rule to implement.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 moral habit, which seems to suggest a machine learning approach. Artistotle, for example, argued 
-that cultivating virtuous action requires making such action habitual through moral education. Under 
+that cultivating virtuous action requires making such action habitual through moral education \cite{aristotle}. Under 
 one view of virtue ethics, the virtuous act is what the virtuous person would do. Both of these ideas
@@
 prescribed by a moral teacher or those that a virtuous ideal agent would undertake. Indeed, these 
-theories seem to point towards a machine learning model for computational ethics, in which ethics is 
+theories seem to point towards a machine learning approach to computational ethics, in which ethics is 
 learned from a dataset of acts tagged as ethical or not ethical. Such approaches exist in the literature, 
@@
 Just as prior work in consequentialism takes implicit or explicit stances on debates in consequentialist
-literature, so does work in virtue ethics. For example, the dataset that Delphi uses to learn ethical
+literature, so does work in machine learning-based virtue ethics. For example, the dataset that Delphi uses to learn ethical
 behavior contains implicit views on what the virtues are and how certain acts impact an agent's
@@
 decisions to a human being, and often find patterns or correlations in datasets that don't actually 
-cohere with the trends and causes that a human being would identify. While there is significant activity 
+cohere with the trends and causes that a human being would identify \cite{puiutta}. While there is significant activity 
 and progress in explainable machine learning, interactive theorem provers are designed to be explainable 
 at the outset. Indeed, Isabelle can even give the axioms and lemmas it used in constructing a proof, 
-allowing a human being to reconstruct the proof independently if they wish. This is, again, not an 
+allowing a human being to reconstruct the proof independently if they wish. This is not an 
 intractable problem for machine learning approaches to computational ethics, but is one reason to 
@@
 Explanability is particularly important in the case of ethics because ethical judgements are often 
-controversial and ethics generally requires reflection. First, the most interesting and important
-ethical judgements are those resulting from ethical dilemmas. These judgements are usually controversial, 
-and the answers are not obvious because people's intuitions differ and different theories generate
-different answers. In these cases, explainability is particularly important to convince human beings 
-of the correctness of an ethical judgement. If a machine tells us to kill one person to save five without
-explaining the justification for this decision, using this judgement becomes difficult. Second, ethics
-is generally seen as a reflective subject. Practical reason is the exercise of using reason and thought
-to decide what to do. Someone who believes an automated reasoner's judgements without examining or 
-understanding the reasons for these judgements doesn't seem to be doing ethics correctly\footnote{I make
-this argument precise in Section Is CE Even Good For Us?}. This does not preclude other uses of automated
-ethics, such as automated moral agents or hypothesis generation for philosophy, but it does make computer-
-assisted ethical judgement difficult.%
+controversial and ethics generally requires reflection. Often, the most interesting and important
+ethical judgements result from ethical dilemmas. These judgements are usually controversial 
+because people's intuitions differ and different theories generate different answers. In these cases,
+explainability is particularly important to convince human beings of the correctness of an ethical 
+judgement. If a machine tells us to kill one person to save five without justifying this decision, 
+acting on this judgement becomes difficult. Second, ethics is a reflective subject. Practical reason 
+is the exercise of using reason to decide what to do. Someone who believes an automated reasoner's 
+judgements without examining or understanding the reasons for these judgements doesn't seem to be 
+doing ethics correctly.\footnote{I make this argument precise in Section Is CE Even Good For Us?} 
+This does not preclude other uses of automated ethics, such as automated moral agents or hypothesis 
+generation for philosophy, but it does make computer-assisted ethical judgement difficult.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %:%53=26%:%
-%:%54=27%:%
-%:%55=28%:%
-%:%64=31%:%
-%:%68=33%:%
+%:%62=29%:%
+%:%66=31%:%
+%:%78=33%:%
+%:%79=34%:%
 %:%80=35%:%
@@
 %:%154=109%:%
-%:%155=110%:%
-%:%156=111%:%
-%:%165=113%:%
+%:%163=111%:%
+%:%175=113%:%
+%:%176=114%:%
 %:%177=115%:%
@@
 %:%207=145%:%
-%:%208=146%:%
-%:%209=147%:%
-%:%218=150%:%
+%:%216=148%:%
+%:%228=150%:%
+%:%229=151%:%
 %:%230=152%:%
@@
 %:%236=158%:%
-%:%237=159%:%
-%:%238=160%:%
-%:%239=161%:%
-%:%248=163%:%
+%:%245=160%:%
+%:%257=162%:%
+%:%258=163%:%
+%:%259=164%:%
 %:%260=165%:%
@@
 %:%312=217%:%
-%:%313=218%:%
-%:%314=219%:%
-%:%315=220%:%
-%:%324=223%:%
+%:%321=220%:%
+%:%333=222%:%
+%:%334=223%:%
+%:%335=224%:%
 %:%336=225%:%
@@
 %:%357=246%:%
-%:%358=247%:%
-%:%359=248%:%
-%:%360=249%:%
-%:%369=251%:%
+%:%366=248%:%
+%:%378=250%:%
+%:%379=251%:%
+%:%380=252%:%
 %:%381=253%:%
@@
 %:%402=274%:%
-%:%403=275%:%
-%:%404=276%:%
-%:%405=277%:%
-%:%414=280%:%
+%:%411=277%:%
+%:%423=279%:%
+%:%424=280%:%
+%:%425=281%:%
 %:%426=282%:%
@@
 %:%443=299%:%
-%:%444=300%:%
-%:%445=301%:%
-%:%446=302%:%
-%:%455=304%:%
-%:%459=306%:%
-%:%471=308%:%
-%:%472=309%:%
-%:%473=310%:%
-%:%474=311%:%
-%:%475=312%:%
-%:%476=313%:%
-%:%477=314%:%
-%:%478=315%:%
-%:%479=316%:%
-%:%480=317%:%
-%:%481=318%:%
-%:%482=319%:%
-%:%483=320%:%
-%:%484=321%:%
-%:%485=322%:%
-%:%494=324%:%
-%:%506=326%:%
-%:%507=327%:%
-%:%508=328%:%
-%:%509=329%:%
-%:%510=330%:%
-%:%511=331%:%
-%:%512=332%:%
-%:%513=333%:%
-%:%514=334%:%
-%:%515=335%:%
-%:%524=337%:%
-%:%536=339%:%
-%:%537=340%:%
-%:%538=341%:%
-%:%539=342%:%
-%:%540=343%:%
-%:%541=344%:%
-%:%542=345%:%
-%:%543=346%:%
-%:%544=347%:%
-%:%545=348%:%
-%:%546=349%:%
-%:%547=350%:%
-%:%548=351%:%
-%:%549=352%:%
-%:%550=353%:%
-%:%551=354%:%
-%:%552=355%:%
-%:%553=356%:%
-%:%554=357%:%
-%:%555=358%:%
-%:%556=359%:%
-%:%557=360%:%
-%:%558=361%:%
-%:%559=362%:%
-%:%560=363%:%
-%:%561=364%:%
-%:%562=365%:%
-%:%563=366%:%
-%:%564=367%:%
-%:%565=368%:%
-%:%566=369%:%
-%:%567=370%:%
-%:%568=371%:%
-%:%569=372%:%
-%:%570=373%:%
-%:%571=374%:%
-%:%572=375%:%
-%:%573=376%:%
-%:%574=377%:%
-%:%575=378%:%
+%:%452=302%:%
+%:%456=304%:%
+%:%468=306%:%
+%:%469=307%:%
+%:%470=308%:%
+%:%471=309%:%
+%:%472=310%:%
+%:%473=311%:%
+%:%474=312%:%
+%:%475=313%:%
+%:%476=314%:%
+%:%477=315%:%
+%:%478=316%:%
+%:%479=317%:%
+%:%480=318%:%
+%:%481=319%:%
+%:%482=320%:%
+%:%491=322%:%
+%:%503=324%:%
+%:%504=325%:%
+%:%505=326%:%
+%:%506=327%:%
+%:%507=328%:%
+%:%508=329%:%
+%:%509=330%:%
+%:%510=331%:%
+%:%511=332%:%
+%:%512=333%:%
+%:%521=335%:%
+%:%533=337%:%
+%:%534=338%:%
+%:%535=339%:%
+%:%536=340%:%
+%:%537=341%:%
+%:%538=342%:%
+%:%539=343%:%
+%:%540=344%:%
+%:%541=345%:%
+%:%542=346%:%
+%:%543=347%:%
+%:%544=348%:%
+%:%545=349%:%
+%:%546=350%:%
+%:%547=351%:%
+%:%548=352%:%
+%:%549=353%:%
+%:%550=354%:%
+%:%551=355%:%
+%:%552=356%:%
+%:%553=357%:%
+%:%554=358%:%
+%:%555=359%:%
+%:%556=360%:%
+%:%557=361%:%
+%:%558=362%:%
+%:%559=363%:%
+%:%560=364%:%
+%:%561=365%:%
+%:%562=366%:%
+%:%563=367%:%
+%:%564=368%:%
+%:%565=369%:%
+%:%566=370%:%
+%:%567=371%:%
+%:%568=372%:%
+%:%569=373%:%
+%:%570=374%:%
+%:%571=375%:%

### 2021-10-30 paper/output/document/paper33.tex
cleaned goals

@@
 In this chapter, I tested two prior attempts to formalize the Formula of Universal Law and found 
-that these attempts didn't actually capture the FUL correctly. Specifically, certain properties that 
-we expect to hold of the FUL didn't hold of these implementations. In an attempt to remedy these 
-shortcomings, I will present my own custom implementation of the FUL that satisfies these properties
-and represents a version of the FUL that is more faithful to the literature. Before presenting my 
-implementation, I first define some goals for my custom formalization based on learnings from prior
-attempt and from literature discussing the FUL.
+that these attempts didn't faithfully interpret the FUL. Specifically, certain properties that 
+we expect to hold of the FUL didn't hold in these implementations. In an attempt to remedy these 
+shortcomings, in the next chapter, I present my own custom implementation of the FUL that satisfies these properties
+and is thus more faithful to the literature. Before presenting my 
+implementation, I define some goals for my custom formalization based on learnings from prior
+attempts and from philosophical literature on the FUL.
 
@@
 interpretations successfully meet that goal. The fact that my custom formalization meets all the goals
-presented indicates that it improves on prior formalization attempts. Below I will explain and justify
-the goals, and in the next chapter I will present my custom formalization.%
+indicates that it improves on prior formalization attempts. Below I will explain and justify
+the goals.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-\textbf{FUl Stronger than DDL} One simple objective that the naive formalization failed to meet is the fact that the FUL should
-not hold in the base logic, dyadic deontic logic. Recall that the naive formalization of the FUL\footnote{
-This formalization reads $\vDash ((\neg \square P A) \longrightarrow O \{\neg A\})$.} held in the 
-base logic, so adding it as an axiom didn't actually make the logic any stronger. This is troubling 
-because the base logic does not actually come equipped with the categorical imperative built-in. It 
-defines basic properties of obligation, such as ought implies can, but holds no axioms that represent
+\textbf{FUL Stronger than DDL} One simple objective that the naive formalization failed to meet is the fact that the FUL should
+not hold in the base logic (DDL). Recall that the naive formalization of the FUL\footnote{
+This formalization reads $\vDash ((\neg (\square P \{A\})) \longrightarrow O \{\neg A\})$.} held in the 
+base logic, so adding it as an axiom didn't make the logic any stronger. This is troubling 
+because the base logic does not come equipped with the categorical imperative built-in. It 
+defines basic properties of obligation, such as ought implies can, but contains no axioms that represent
 the formula of universal law. Therefore, if a formalization of the FUL holds in the 
-base logic, then it is too weak to be correct. The naive interpretation holds in DDL but Kroy's formalization
-does not. Because the naive interpretation is no stronger than DDL, it is essentially a control group
-because goals that hold in it hold in DDL itself.
+base logic, then it is too weak to actually represent the FUL. The naive interpretation holds in DDL but Kroy's formalization
+does not. Because the naive interpretation is no stronger than DDL, it is acts a control group equivalent
+to DDL itself.
 
@@
 generalizes across people. In other words, if a maxim is obligated for one person, it is obligated
-for all other people as well because maxims are not person-specific. Velleman argues that, because 
-reason is accessible to everyone identically, obligations apply to all people \cite[25]{velleman}. 
+for all other people because maxims are not person-specific. Velleman argues that, because 
+reason is accessible to everyone identically, obligations apply to all people equually \cite[25]{velleman}. 
 When Kant describes the categorical imperative as the objective principle of the will, he is referring 
@@
 to make oneself an exception: selfishness, meanness, advantagetaking, and disregard for the rights 
-of others" \cite[30]{korsgaardFUL}. Kroy latches onto this property and makes it the content of his
+of others" \cite[30]{KorsgaardFUL}. Kroy latches onto this property and makes it the content of his
 formalization, which essentially says that if an act is permissible for someone, it is permissible for 
-everyone. While Kroy's interpretation clearly satisfies this property, the naive interpretation does not.
+everyone.\footnote{Formally, $P\{A(s)\} \longrightarrow \forall p. P\{A(p)\}$} While Kroy's interpretation 
+clearly satisfies this property, the naive interpretation does not.
 
-\textbf{Contradictory Obligations} Another problem with prior formalizations of the categorical imperative was that they didn't
+\medskip
+
+\textbf{Contradictory Obligations} Another problem with prior formalizations was that they didn't
 prohibit contradictory obligations, partially because DDL itself allows contradictory obligations. 
 Kant subscribes to the general, popular view that morality is supposed to guide action, so ought implies 
-can\footnote{Kohl points out that this principle is referred to as 
-Kant's dictum or Kant's law in the literature. \cite[footnote 1]{kohl}}. Kohl reconstructs his argument for the principle as 
+can.\footnote{Kohl points out that this principle is referred to as 
+Kant's dictum or Kant's law in the literature \cite[footnote 1]{kohl}.} Kohl reconstructs his argument for the principle as 
 follows: if the will cannot comply with the moral law, then the moral law has no prescriptive authority 
@@
 conflicting moral obligations are impossible under his theory \cite[V224]{metaphysicsintro}. Particularly, the categorical imperative generates 
-``strict negative laws of omission", which cannot conflict by definition\footnote{The 
+``strict negative laws of omission," which cannot conflict by definition \cite[45]{timmerman}. \footnote{The 
 kinds of obligations generated by the FUL are called ``perfect duties" which arise from ``contradictions 
@@
 such as ``improve oneself" or "help others," and are secondary to perfect duties. My project only analyzes 
-perfect duties, as these are stronger than imperfect duties.} \cite[45]{timmerman}.
+perfect duties, as these are always stronger than imperfect duties.}. Both the naive formalization and 
+Kroy's formalization allow contradictory obligations.
 
-Neither the naive formalization nor Kroy's formalization disallow contradictory obligations. Additionally,
-during testing, I realized that contradictory obligations are closely related to two other properties
+During testing, I also realized that contradictory obligations are closely related to two other properties
 that also fail in both of these systems. First is the idea that obligation implies permissibility, or 
@@
 then this property holds because actions are either permissible or prohibited and obligation contradicts
-prohibition. Moreover, in a system with contradictory obligations, this property fails because A is
-obligated and prohibited and therefore not permisible. Indeed, formalizing this property below shows 
-that this follows from the definition of implication in propositional logic and Sledgehammer is able
-to show this property easily.
+prohibition. Moreover, in a system with contradictory obligations, this property fails because there is some
+A that is obligated but also prohibited and therefore not permisible. Indeed, formalizing this property below shows 
+that this follows from the definition of implication in propositional logic.
 
@@
 \textbf{Distributive Property} Another property related to contradictory obligations is the distributive property for the obligation
-operator\footnote{Formally, $O\{A\} \wedge O\{B\} \longleftrightarrow O\{A \wedge B\}$.}. This is 
+operator.\footnote{Formally, $O\{A\} \wedge O\{B\} \longleftrightarrow O\{A \wedge B\}$.} This is 
 another property that we expect to hold. The rough English translation of  $O \{ A \wedge B \} $ is ``you are obligated to 
@@
 and you are obligated to do B." We think those English sentences mean the same thing, so they should mean 
-the same thing in this logic as well. Moreover, if that (rather intuitive) property holds, then contradictory
+the same thing in logic as well. Moreover, if that (rather intuitive) property holds, then contradictory
 obligations are impossible, as shown in the below proof.%
@@
 obligation operator. Again, this property fails in the naive formalization and for Kroy's formalization.
-This property is a goal for my custom formalization.
 
@@
 
-\textbf{Un-universalizable Actions} The last goal inspired by prior attempts comes from a test performed for Kroy's formalization. Under 
-the naive, ethics 101 reading of the formula of universal law, it prohibits lying because, in a world 
+\textbf{Un-universalizable Actions} This goal is inspired by a test performed for Kroy's formalization. Under 
+a naive reading of the Formula of Universal Law, it prohibits lying because, in a world 
 where everyone simultaneously lies, lying is impossible. In other words, not everyone can simultaneously
 lie because the institution of lying and believing would break down. More precisely, the FUL should 
-show that actions that aren't universalizable are prohibited, because those acts cannot be willed in 
+show that actions that cannot possibly be universalized are prohibited, because those acts cannot be willed in 
 a world where they are universalized. This property fails to hold in both the naive formalization 
@@
 The goals above come from moral intuition, properties of Kantian ethics, and logical requirements. 
-Philosophers have robustly debated the meaning of the Formula of Universal Law, and the results of these 
-debates should be incorporated into a custom formalization of the categorical imperative.
+In order to stay faithful to centuries of philosophical debate about the meaning of the Formula of 
+Universl Law, I also present some goals inpsired by this literature.
 
-\textbf{Maxims} First, note
-that Kant does not evaluate the correctness of acts, but rather of maxims. Therefore, any faithful formalization
-of the categorical imperative must evaluate maxims, not acts. This requires representing a maxim, which neither
-of the prior attempts do.
+\textbf{Maxims} Kant does not evaluate the correctness of acts, but rather of maxims. Therefore, any 
+faithful formalization of the categorical imperative must evaluate maxims, not acts. This requires 
+representing a maxim and making it the input to the obligation operator, which neither of the prior attempts do.
 
@@
 \begin{isamarkuptext}%
-\textbf{Practical Contradiction Interpretation} Second, Kantians debate the correct interpretation of the formula of universal law because Kant appears to 
+\textbf{Practical Contradiction Interpretation} Kantians debate the correct interpretation of the Formula of Universal Law because Kant appears to 
 interpret the universalizability test in different ways. Korsgaard argues for the practical contradiction 
@@
 %:%130=86%:%
-%:%132=90%:%
-%:%133=90%:%
-%:%136=91%:%
-%:%140=91%:%
-%:%141=91%:%
-%:%150=93%:%
-%:%151=94%:%
+%:%131=87%:%
+%:%132=88%:%
+%:%134=92%:%
+%:%135=92%:%
+%:%138=93%:%
+%:%142=93%:%
+%:%143=93%:%
 %:%152=95%:%
@@
 %:%156=99%:%
+%:%157=100%:%
 %:%158=101%:%
-%:%159=101%:%
-%:%160=102%:%
+%:%160=103%:%
 %:%161=103%:%
-%:%164=104%:%
-%:%168=104%:%
-%:%169=104%:%
-%:%170=104%:%
-%:%179=106%:%
-%:%180=107%:%
+%:%162=104%:%
+%:%163=105%:%
+%:%166=106%:%
+%:%170=106%:%
+%:%171=106%:%
+%:%172=106%:%
 %:%181=108%:%
@@
 %:%191=118%:%
-%:%200=120%:%
-%:%212=122%:%
-%:%213=123%:%
+%:%192=119%:%
+%:%193=120%:%
+%:%202=122%:%
 %:%214=124%:%
@@
 %:%221=131%:%
-%:%225=135%:%
+%:%222=132%:%
 %:%226=136%:%
@@
 %:%286=196%:%
+%:%287=197%:%

### 2021-11-07 paper/output/document/outline_whykant.tex
did goals
idk man

@@
 
-The argument is not that no form of consequentialism or virtue ethics is tractable to automate, but 
+I do not argue that consequentialism and virtue ethics are tractable to automate, but 
 rather that Kantian ethics is easier. I do not present a comprehensive comparision
-of ethical theories, but instead sketch the basic principles that most consequentialist and virtue 
-ethical theories share.%
+of ethical theories, but instead sketch basic principles of consequentialist and virtue 
+ethical theories.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 bound by those imperatives that are implied by practical reason itself \cite{velleman}. From there, I present 
-the three formulations of the categorical imperative, focusing on the Formula of Universal Law (FUL) \cite{groundwork}. 
-This is not a full defense of Kantian ethics but is instead a quick sketch of one argument for the FUL.%
+the three formulations of the categorical imperative, focusing on the Formula of Universal Law (FUL) \cite{groundwork}.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-The FUL is easy to formalize
-because it is a purely formal principle that is only evaluates the form of the maxim that an agent 
-acts on. No other information is relevant to the test, so moral judgement can proceed with a relatively small
-amount of data.%
+The FUL is easy to formalize because it only evaluates the 
+form of the maxim that an agent acts on. No other information is relevant to the test, so moral 
+judgement can proceed with a relatively small amount of data.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 ethics that my project takes a stance on: the correct way to interpret the FUL and the definition of a 
-maxim. The stances I take are generally accepted by most Kantians, though some still disagree.%
+maxim. The stances I take are generally accepted by most Kantians \cite{ebelsduggan, KorsgaardFUL}.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-I define
-a consequentialist theory as one that evaluates the consequences of an action, acknowledging that
-this definition itself is controversial \cite{consequentialismsep}. I then present the debates over theories of the good, which 
-consequences to evaluate, and the aggregation of consequences.%
+I define a consequentialist theory as one that evaluates the consequences of an action, acknowledging 
+that this definition itself is controversial \cite{consequentialismsep}. I then present the debates 
+over theories of the good, which consequences to evaluate, and the aggregation of consequences.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 for a state of affairs. There is a tradeoff between the difficulty of aggregation
-and the complexity of making judgements about an entire state of affairs, as opposed to about a single person.
-A reasoner will need large, complicated datasets to settle these questions.%
+and the complexity of making judgements about an entire state of affairs, as opposed to about a single person.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsubsection{Prior Work%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
+I briefly survey some prior work in formalizing consequentialism and argue that this work either
+implicitly or explicitly takes stances on the debates above, resulting in oversimplification or 
+punting the problem \cite{util1, util2}.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-I understand the concept of virtue as those traits that are 
-good for the posessor \cite{vesep}. I briefly explain Aristotle's eudaimonistic conception of virtue and present
-some examples of virtues (courage, temperance, equanimity).%
+I understand the concept of virtue as those traits that are good for the posessor \cite{vesep}. 
+I briefly explain Aristotle's eudaimonistic conception of virtue and present some examples of virtues 
+(courage, temperance, equanimity).%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-Automated virtue ethics will need to plant a flag in the messy, controversial debate over the exact
-list of virtues. While most Kantians agree on one interpretation of the FUL, most virtue ethicists 
+Automated virtue ethics will need to plant a flag in the messy, controversial debate over the 
+exact list of virtues. While most Kantians agree on one interpretation of the FUL, most virtue ethicists 
 have their own interpretations of what the virtues are.%
@@
 %
-\isamarkupsubsubsection{Machine Learning and Virtue Ethics%
+\isamarkupsubsubsection{Prior Work: Machine Learning and Virtue Ethics%
 }
@@
 \begin{isamarkuptext}%
-There is a connection between the ideas of cultivating habit and mimicking virtuous action
-and machine learning, which mimics patterns in datasets\footnote{Would love feedback on whether this should
-go here or in a Related Work section.}. There's been some
-work using machine learning to learn moral behavior from a dataset of actions tagged as ethical \cite{delphi}. 
-One drawback of this approach is the fact that machine learning algorithms have trouble
-explaining why they made the judgements they made and often pick up on patterns that human beings would 
-not see as indicative of causation. In contrast,
-my system can explain exactly which axioms and principles resulted in a maxim being obligated or prohibited
-and can even present human-reconstructable proofs of its results.%
+One argument for formalizing virtue ethics is the connection between cultivating habit
+and machine learning, which learns patterns in datasets. There's been some work using machine learning 
+to learn moral behavior from a dataset of actions tagged as ethical, but this approach takes an
+implicit stance on the debate above \cite{delphi}. Moreover, machine learning algorithms have trouble
+explaining why they made the judgements they made \cite{puiutta}. In contrast, my system can explain 
+exactly which axioms resulted in a maxim being obligated and can even present human-reconstructable proofs.
+I argue that explanability is particularly important for ethical judgements because these judgements 
+are often controversial and high stakes.\footnote{There also seems to be something about Kantian ethics
+that requires the will have a reason for adopting a maxim, for otherwise it would cede its autonomy
+to the computer. I will flesh this out in a separate section that asks whether it's even a good idea 
+to automate ethics.}%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %:%74=27%:%
-%:%75=28%:%
-%:%84=31%:%
+%:%83=30%:%
+%:%95=32%:%
 %:%96=33%:%
 %:%97=34%:%
-%:%98=35%:%
-%:%99=36%:%
-%:%108=39%:%
-%:%120=41%:%
-%:%121=42%:%
-%:%122=43%:%
-%:%123=44%:%
-%:%132=46%:%
-%:%136=48%:%
-%:%148=50%:%
-%:%149=51%:%
-%:%150=52%:%
-%:%151=53%:%
-%:%160=55%:%
-%:%164=57%:%
-%:%176=59%:%
-%:%177=60%:%
-%:%178=61%:%
-%:%179=62%:%
-%:%188=64%:%
-%:%200=66%:%
-%:%201=67%:%
-%:%202=68%:%
-%:%203=69%:%
-%:%204=70%:%
-%:%213=72%:%
-%:%217=74%:%
-%:%229=76%:%
-%:%230=77%:%
-%:%231=78%:%
-%:%240=80%:%
-%:%244=82%:%
-%:%256=85%:%
-%:%257=86%:%
-%:%258=87%:%
-%:%267=89%:%
-%:%279=91%:%
-%:%280=92%:%
-%:%289=94%:%
-%:%301=96%:%
-%:%302=97%:%
-%:%303=98%:%
-%:%304=99%:%
-%:%305=100%:%
-%:%306=101%:%
-%:%307=102%:%
-%:%308=103%:%
-%:%309=104%:%
+%:%106=36%:%
+%:%118=38%:%
+%:%119=39%:%
+%:%120=40%:%
+%:%121=41%:%
+%:%130=43%:%
+%:%134=45%:%
+%:%146=47%:%
+%:%147=48%:%
+%:%148=49%:%
+%:%157=51%:%
+%:%161=53%:%
+%:%173=55%:%
+%:%174=56%:%
+%:%175=57%:%
+%:%176=58%:%
+%:%185=60%:%
+%:%197=62%:%
+%:%198=63%:%
+%:%199=64%:%
+%:%200=65%:%
+%:%209=68%:%
+%:%221=70%:%
+%:%222=71%:%
+%:%223=72%:%
+%:%232=74%:%
+%:%236=76%:%
+%:%248=78%:%
+%:%249=79%:%
+%:%250=80%:%
+%:%259=82%:%
+%:%263=84%:%
+%:%275=86%:%
+%:%276=87%:%
+%:%277=88%:%
+%:%286=90%:%
+%:%298=92%:%
+%:%299=93%:%
+%:%308=95%:%
+%:%320=97%:%
+%:%321=98%:%
+%:%322=99%:%
+%:%323=100%:%
+%:%324=101%:%
+%:%325=102%:%
+%:%326=103%:%
+%:%327=104%:%
+%:%328=105%:%
+%:%329=106%:%
+%:%330=107%:%

### 2021-11-07 paper/output/document/paper.tex
some restructuring, added some morethoughts on maxims
jkldfa
idk man

@@
 As artifical reasoners become increasingly powerful, computers become capable of
-performing complex ethical reasoning. The field of machine ethics \cite{mesurvey} is interesting for two reasons.
-First, the proliferation of artifically autonomous agents is creating and will continue to create a demand for 
+performing complex ethical reasoning. Moreover, as regulators and academics call for ``ethical AI,"
+the field of machine ethics becomes increasingly popular. Much prior work on machine ethics implements
+relatively simple philosophical theories, partially as an artifact of this work emerging out of
+Computer Science or Mathematics departments \cite{mesurvey}. Such work rarely capitalizes on the 
+centuries of philosophical debate discussing the ethical theories in question. In this thesis, I attempt
+to automate Kantian ethics, a sophisticated ethical theory, while staying faithful to philosophical
+literature on the subject.
+
+Automating a sophisticated ethical theory is interesting for two reasons. First, the proliferation of 
+artifically autonomous agents is creating and will continue to create a demand for 
 automated ethics. These agents must be able to reason about complex ethical theories 
-that withstand philosophical scrutiny. Second, just as automated mathematical reasoning gives mathematicians
-new powers, automated ethical reasoning is a tool that philosophers can use 
-when reasoning about ethics. Many contradictions or paradoxes with an ethical system may not be 
- obvious to the human eye, but can be easily tested using an automated theorem prover.
+that withstand philosophical scrutiny. Second, just as automated mathematical reasoning is a tool
+for mathematicians, automated ethical reasoning is a tool that philosophers can use 
+when reasoning about ethics. I argue that computational ethics can serve as another tool in a 
+philosopher's toolbox, like a thought experiment or counterexample.
 
@@
 such as encoding ethics as a constraint satisfaction problem, fail to capture
-the complexity of most philosophically plausible systems. On the other hand, it is not immediately clear
-how to formalize many complex moral theories, like virtue ethics.
-
-Computational ethics also requires a sophisticated 
-ethical theory to model. Constraint satisfaction systems often default to some version of utiliarianism, 
+the complexity of most philosophically plausible systems. Constraint satisfaction systems often default to some version of utiliarianism, 
 the principle of doing the most good for the most people. Alternatively, they model basic moral 
@@
 field of philosophy is devoted to developing and testing robust ethical theories. Plausible machine
-ethics must draw on plausible moral philosophy.
+ethics must draw on plausible moral philosophy. Despite the importance of formalizing complex moral theories,
+it is not immediately clear how to formalize complex theories like virtue ethics.
 
-The ideal candidate ethical theory will be both philosophically interesting and easy to 
-formalize. Kantian ethics, often described as ``formal," has been often floated as such a candidate \cite{powers, BL, lin}. 
-The categorical imperative, Kant's universal law of morality, is a moral rule that can be used to 
-guide action.
+Kantian ethics, often described as ``formal" due to its rigid, rule-based structure, has been often 
+floated as an attractive theory to automate \cite{powers, BL, lin}. This project's objective is to 
+automate Kantian ethics. Roughly, my approach is to represent Kantian
+ethics as an axioms in Carmo and Jones' Dyadic Deontic Logic (DDL), a modal logic designed to reason
+about concepts like obligation \cite{CJDDL}. Such a representation of Kantian ethics in a logic
+is called a ``formalization." I then embed this DDL formalization in higher-order logic 
+(HOL) and implement it in the Isabelle/HOL theorem prover  \cite{isabelle}. I can then use Isabelle 
+to automatically prove or disprove theorems (such as, ``murder is wrong") in my custom formalization, generating results
+derived from the categorical imperative. Essentially, the computer is performing ethical reasoning using
+the framework of Kantian ethics.
 
-This project's objective is to automate Kantian ethics. I present two different
-formalizations of Kant's categorical imperative implemented and tested in the Isabelle/HOL \cite{isabelle} theorem prover.
-I model each formalization  as an extension of Carmo and Jones' Dyadic Deontic Logic (DDL) \cite{CJDDL}. I then embed the corresponding 
-DDL formalization in higher-order logic (HOL) and implement it in Isabelle. Section 
-\ref{sec:naive} implements and tests the naive formalization, a ``control group" that is clearly implausible but 
-demonstrates the methods and tools of my approach. Section \ref{sec:kroy} implements a more sophisticated 
-formalization inspired by Moshe Kroy's partial formalization of the categorical imperative.
+First, I recreate prior work implementing Dyadic Deontic Logic in Isabelle/HOL. Next, I present two 
+prior attempts to formalize Kantian ethics in modal logic. The first is a naive
+interpretation of Kant's categorical imperative that collapses to the base logic itself. The second is 
+Moshe Kroy's partial formalization of the categorical imperative. As part of this presentation, I also
+create a testing framework that can be used to evaluate these formalizations. In effect, my tests formalize
+expected properties of the categorical imperative (such as the fact that it prohibits murder) and test 
+whether or not these properties hold in a given formalization. My testing framework offers a method for
+evaluating different formalizations against moral intuitions and philosophical literature. Second, based on
+lessons learned from these prior formalization attempts, I contribute my own custom formalization of
+the categorical imperative. My testing framework demonstrates how my custom formalization improves upon
+the prior work. Third, I apply my system to an ethical dilemma to demonstrate its potential use. I also
+consider the philosophical implications and value of automated ethics, studying questions about the 
+possibility and responsibility of automated ethics.
 
@@
 examine ethical and logical properties of the system, including logical consistency, consistency
-of obligation, and possibility of permissibility. The implementations themselves are usable models 
+of obligation, and possibility of permissibility. I also contribute a logical formalization of the categorical
+imperative that improves on previous work, an implementation of this formalization, and evidence of 
+its improvement. Lastly, I demonstrate how such a system could be applied. The implementations themselves are usable models 
 of ethical principles and the tests represent the kind of philosophical work that formalized ethics 
-can contribute.%
+can contribute.
+
+The rest of this project is structured as follows. In Chapter 1, I introduce the logical, computational, and 
+philosophical frameworks underlying my project. In Chapter 2, I implement and test prior formalizations of the categorical
+imperative. In Chapter 3, I contribute my own custom formalization and test it. Finally, in Chapter 4, 
+I apply my custom formalization to an example ethical dilemma.%
 \end{isamarkuptext}\isamarkuptrue%
 %
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\isatagdocument
-%
-\isamarkupsection{System Overview \label{sec:overview}%
-}
-\isamarkuptrue%
-%
-\endisatagdocument
-{\isafolddocument}%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
 \begin{isamarkuptext}%
-The goal of this project is to automate sophisticated ethical reasoning. This requires three
+In the rest of this chapter, I present the background necessary to undersand my work. The goal 
+of this project is to automate sophisticated ethical reasoning. This requires three
 components. First, the choice of an ethical theory that is both intuitively attractive and 
@@
 \begin{isamarkuptext}%
-Kantian ethics is an attractive choice of ethical theory to automates. Kant's writings inspired much of Western analytic philosophy. 
+Kantian ethics is an attractive choice of ethical theory to automate. Kant's writings inspired much of Western analytic philosophy. 
 In addition to the rich neo-Kantian program, almost all major philosophical traditions after Kant have
@@
 %:%78=50%:%
-%:%87=52%:%
-%:%99=54%:%
-%:%100=55%:%
-%:%101=56%:%
-%:%102=57%:%
-%:%103=58%:%
-%:%104=59%:%
-%:%113=61%:%
-%:%125=63%:%
-%:%126=64%:%
-%:%127=65%:%
-%:%128=66%:%
-%:%129=67%:%
-%:%130=68%:%
-%:%131=69%:%
-%:%132=70%:%
-%:%133=71%:%
-%:%134=72%:%
-%:%135=73%:%
-%:%136=74%:%
-%:%137=75%:%
-%:%138=76%:%
-%:%139=77%:%
-%:%140=78%:%
-%:%141=79%:%
-%:%142=80%:%
-%:%143=81%:%
-%:%144=82%:%
-%:%145=83%:%
-%:%146=84%:%
-%:%147=85%:%
-%:%148=86%:%
-%:%149=87%:%
-%:%150=88%:%
-%:%151=89%:%
-%:%152=90%:%
-%:%153=91%:%
-%:%154=92%:%
-%:%155=93%:%
-%:%156=94%:%
-%:%157=95%:%
-%:%158=96%:%
-%:%159=97%:%
-%:%160=98%:%
-%:%161=99%:%
-%:%162=100%:%
-%:%163=101%:%
-%:%164=102%:%
-%:%165=103%:%
-%:%166=104%:%
-%:%167=105%:%
-%:%168=106%:%
-%:%169=107%:%
-%:%170=108%:%
-%:%171=109%:%
-%:%172=110%:%
-%:%173=111%:%
-%:%174=112%:%
-%:%175=113%:%
-%:%176=114%:%
-%:%177=115%:%
-%:%178=116%:%
-%:%179=117%:%
-%:%180=118%:%
-%:%181=119%:%
-%:%182=120%:%
-%:%183=121%:%
-%:%184=122%:%
-%:%185=123%:%
-%:%186=124%:%
-%:%187=125%:%
-%:%188=126%:%
-%:%189=127%:%
-%:%190=128%:%
-%:%191=129%:%
-%:%192=130%:%
-%:%193=131%:%
-%:%194=132%:%
-%:%195=133%:%
-%:%204=137%:%
-%:%208=139%:%
-%:%220=141%:%
-%:%221=142%:%
-%:%222=143%:%
-%:%223=144%:%
-%:%224=145%:%
-%:%225=146%:%
-%:%226=147%:%
-%:%227=148%:%
-%:%228=149%:%
-%:%229=150%:%
-%:%230=151%:%
-%:%231=152%:%
-%:%232=153%:%
-%:%233=154%:%
-%:%234=155%:%
-%:%235=156%:%
-%:%236=157%:%
-%:%237=158%:%
-%:%238=159%:%
-%:%239=160%:%
-%:%240=161%:%
-%:%241=162%:%
-%:%242=163%:%
-%:%243=164%:%
-%:%244=165%:%
-%:%245=166%:%
-%:%254=168%:%
-%:%266=170%:%
-%:%267=171%:%
-%:%268=172%:%
-%:%269=173%:%
-%:%270=174%:%
-%:%271=175%:%
-%:%272=176%:%
-%:%273=177%:%
-%:%274=178%:%
-%:%275=179%:%
-%:%276=180%:%
-%:%277=181%:%
-%:%278=182%:%
-%:%279=183%:%
-%:%280=184%:%
-%:%281=185%:%
-%:%282=186%:%
-%:%283=187%:%
-%:%284=188%:%
+%:%79=51%:%
+%:%80=52%:%
+%:%81=53%:%
+%:%82=54%:%
+%:%83=55%:%
+%:%84=56%:%
+%:%85=57%:%
+%:%86=58%:%
+%:%87=59%:%
+%:%88=60%:%
+%:%89=61%:%
+%:%90=62%:%
+%:%91=63%:%
+%:%92=64%:%
+%:%93=65%:%
+%:%94=66%:%
+%:%95=67%:%
+%:%96=68%:%
+%:%97=69%:%
+%:%98=70%:%
+%:%99=71%:%
+%:%100=72%:%
+%:%101=73%:%
+%:%102=74%:%
+%:%106=77%:%
+%:%107=78%:%
+%:%108=79%:%
+%:%109=80%:%
+%:%110=81%:%
+%:%111=82%:%
+%:%112=83%:%
+%:%121=85%:%
+%:%133=87%:%
+%:%134=88%:%
+%:%135=89%:%
+%:%136=90%:%
+%:%137=91%:%
+%:%138=92%:%
+%:%139=93%:%
+%:%140=94%:%
+%:%141=95%:%
+%:%142=96%:%
+%:%143=97%:%
+%:%144=98%:%
+%:%145=99%:%
+%:%146=100%:%
+%:%147=101%:%
+%:%148=102%:%
+%:%149=103%:%
+%:%150=104%:%
+%:%151=105%:%
+%:%152=106%:%
+%:%153=107%:%
+%:%154=108%:%
+%:%155=109%:%
+%:%156=110%:%
+%:%157=111%:%
+%:%158=112%:%
+%:%159=113%:%
+%:%160=114%:%
+%:%161=115%:%
+%:%162=116%:%
+%:%163=117%:%
+%:%164=118%:%
+%:%165=119%:%
+%:%166=120%:%
+%:%167=121%:%
+%:%168=122%:%
+%:%169=123%:%
+%:%170=124%:%
+%:%171=125%:%
+%:%172=126%:%
+%:%173=127%:%
+%:%174=128%:%
+%:%175=129%:%
+%:%176=130%:%
+%:%177=131%:%
+%:%178=132%:%
+%:%179=133%:%
+%:%180=134%:%
+%:%181=135%:%
+%:%182=136%:%
+%:%183=137%:%
+%:%184=138%:%
+%:%185=139%:%
+%:%186=140%:%
+%:%187=141%:%
+%:%188=142%:%
+%:%189=143%:%
+%:%190=144%:%
+%:%191=145%:%
+%:%192=146%:%
+%:%193=147%:%
+%:%194=148%:%
+%:%195=149%:%
+%:%196=150%:%
+%:%197=151%:%
+%:%198=152%:%
+%:%199=153%:%
+%:%200=154%:%
+%:%201=155%:%
+%:%202=156%:%
+%:%203=157%:%
+%:%212=161%:%
+%:%216=163%:%
+%:%228=165%:%
+%:%229=166%:%
+%:%230=167%:%
+%:%231=168%:%
+%:%232=169%:%
+%:%233=170%:%
+%:%234=171%:%
+%:%235=172%:%
+%:%236=173%:%
+%:%237=174%:%
+%:%238=175%:%
+%:%239=176%:%
+%:%240=177%:%
+%:%241=178%:%
+%:%242=179%:%
+%:%243=180%:%
+%:%244=181%:%
+%:%245=182%:%
+%:%246=183%:%
+%:%247=184%:%
+%:%248=185%:%
+%:%249=186%:%
+%:%250=187%:%
+%:%251=188%:%
+%:%252=189%:%
+%:%253=190%:%
+%:%262=192%:%
+%:%274=194%:%
+%:%275=195%:%
+%:%276=196%:%
+%:%277=197%:%
+%:%278=198%:%
+%:%279=199%:%
+%:%280=200%:%
+%:%281=201%:%
+%:%282=202%:%
+%:%283=203%:%
+%:%284=204%:%
+%:%285=205%:%
+%:%286=206%:%
+%:%287=207%:%
+%:%288=208%:%
+%:%289=209%:%
+%:%290=210%:%
+%:%291=211%:%
+%:%292=212%:%

### 2021-11-07 paper/output/document/upshot.tex
idk man

@@
 relevant to a maxim. This is a question that, like all of ethics, philosophers debate robustly
-\footnote{Powers \cite{powers} identifies this as a challenge for automating Kantian ethics and briefly sketches 
-solutions from O'Neill \cite{constofreason}, Silber \cite{silber}, and Rawls \cite{rawlsconstructivism}. }. 
+\footnote{\citet{powers} identifies this as a challenge for automating Kantian ethics and briefly sketches 
+solutions from \citet{constofreason}, \citet{silber}, and \citet{rawlsconstructivism}. }. 
 It is likely that, just as different implementations of automated ethics choose 
@@
 has implications for debates about ethical self-doubt and self-confidence or self-respect.
+
+Below, I document the process used to arrive at the logical insight that the FUL is inconsistent if it
+holds for maxims in which $(c \longrightarrow a) \wedge (c \longrightarrow g)$. For those uninterested
+in the details of this exploration, it suffices to understand that I used Isabelle to show that if the 
+FUL holds for badly formed maxims, then it is inconsistent. After I realized that my formalization was 
+inconsistent, I made many failed attempts to diagnose and fix the problem before reaizing that the problem 
+lay in badly formed maxims.
 
@@
 represent mathematical concepts. Some of this work requres tedious pencil and paper proofs to prove 
-theorems, even when many of these theorems may not generate relevant philosophical insights. Ineractive 
+theorems, even when many of these theorems may not generate relevant philosophical insights. Interactive 
 theorem provers make formal logic more accessible. Isabelle can complete a proof, starting from first principles, 
@@
 %:%458=379%:%
-%:%467=383%:%
-%:%479=385%:%
-%:%480=386%:%
-%:%481=387%:%
-%:%482=388%:%
-%:%483=389%:%
-%:%484=390%:%
-%:%485=391%:%
+%:%459=380%:%
+%:%460=381%:%
+%:%461=382%:%
+%:%462=383%:%
+%:%463=384%:%
+%:%464=385%:%
+%:%465=386%:%
+%:%474=390%:%
 %:%486=392%:%
@@
 %:%524=430%:%
-%:%533=433%:%
-%:%545=436%:%
-%:%546=437%:%
-%:%547=438%:%
-%:%548=439%:%
-%:%549=440%:%
-%:%550=441%:%
-%:%551=442%:%
+%:%525=431%:%
+%:%526=432%:%
+%:%527=433%:%
+%:%528=434%:%
+%:%529=435%:%
+%:%530=436%:%
+%:%531=437%:%
+%:%540=440%:%
 %:%552=443%:%
@@
 %:%565=456%:%
+%:%566=457%:%
+%:%567=458%:%
+%:%568=459%:%
+%:%569=460%:%
+%:%570=461%:%
+%:%571=462%:%
+%:%572=463%:%

### 2021-11-07 paper/output/document/paper.tex
cleaned much of naive

@@
 relatively simple philosophical theories, partially as an artifact of this work emerging out of
-Computer Science or Mathematics departments \cite{mesurvey}. Such work rarely capitalizes on the 
+Computer Science or Mathematics departments \citep{mesurvey}. Such work rarely capitalizes on the 
 centuries of philosophical debate discussing the ethical theories in question. In this thesis, I attempt
@@
 Kantian ethics, often described as ``formal" due to its rigid, rule-based structure, has been often 
-floated as an attractive theory to automate \cite{powers, BL, lin}. This project's objective is to 
+floated as an attractive theory to automate \citep{powers, BL, lin}. This project's objective is to 
 automate Kantian ethics. Roughly, my approach is to represent Kantian
-ethics as an axioms in Carmo and Jones' Dyadic Deontic Logic (DDL), a modal logic designed to reason
-about concepts like obligation \cite{CJDDL}. Such a representation of Kantian ethics in a logic
+ethics as an axiom in Carmo and Jones' Dyadic Deontic Logic (DDL), a modal logic designed to reason
+about concepts like obligation \citep{CJDDL}. Such a representation of Kantian ethics in a logic
 is called a ``formalization." I then embed this DDL formalization in higher-order logic 
-(HOL) and implement it in the Isabelle/HOL theorem prover  \cite{isabelle}. I can then use Isabelle 
+(HOL) and implement it in the Isabelle/HOL theorem prover  \citep{isabelle}. I can then use Isabelle 
 to automatically prove or disprove theorems (such as, ``murder is wrong") in my custom formalization, generating results
@@
 choice of automation engine to implement the formal model in. Section \ref{sec:kant} introduces Kantian
-ethics, Section \ref{sec:DDL} explains Carmo and Jones's Dyadic Deontic Logic \cite{CJDDL} as a 
+ethics, Section \ref{sec:DDL} explains Carmo and Jones's Dyadic Deontic Logic as a 
 base logic, and Section \ref{sec:isabelle} presents the Isabelle/HOL implementation of the logic.%
 \end{isamarkuptext}\isamarkuptrue%
+%
+\input{whykant}
 %
@@
 %
-\isamarkupsubsection{Kantian Ethics \label{sec:kant}%
+\isamarkupsubsection{Dyadic Deontic Logic \label{sec:DDL}%
 }
@@
 \begin{isamarkuptext}%
-Kantian ethics is an attractive choice of ethical theory to automate. Kant's writings inspired much of Western analytic philosophy. 
-In addition to the rich neo-Kantian program, almost all major philosophical traditions after Kant have
-engaged with his work. Much of Western libertarian political thought is inspired by Kant's deontology,
-and his ethics have bled into household ethical thought. Deontology is seen as one of the three major 
-schools of Western analytic ethics.
-
-Understanding the ethic's potential for formalization requires understanding Kant's system. Kant argues 
-that if morality exists, it must take the form of an inviolable rule, which he calls the ``categorical
-imperative." He presents three formulations of the categorical imperative, as well as a robust defense
-of them in his seminal work on ethics \cite{groundwork}. He argues that all three formulations are 
-equivalent.
-
-The first formulation of the categorical imperative is the ``Formula of Universal Law."
-
-$\textbf{Definition}$ \emph{(Formula of Universal Law)}
-
-\emph{I ought never to act except in such a way that I could also will that my maxim should become a universal law} \cite{groundwork}
-
-A ``maxim" is a moral rule such as, ``I can murder someone to take their job". ``Willing" a maxim is 
-equivalent to acting on that rule. The FUL creates a thought experiment called the universalizability 
-test: to decide if a maxim is permissible, imagine what would happen if everyone willed that maxim. 
-If your imagined world yields a contradiction, the maxim is prohibited\footnote{There is another case here.
-What happens if the imagined world does not yield a logical contradiction, but is still undesirable? Kant 
-distinguishes between these cases as contradictions in conception and contradictions in will. Both yield moral
-prohibitions, but contradictions in conception generate stronger contradictions and therefore stronger obligations. 
-This paper will focus entirely on contradictions in conception, for this is the only kind of contradiction 
-for which a strict logical interpretation makes sense. For a complete treatment of the difference, see \cite{groundwork, KorsgaardFUL}}. Intuitively, the FUL asks 
-the question, "What would happen if everyone did that?" \cite{KorsgaardFUL}.
-
-As an example, let's apply the universalizability test to the maxim of murdering others to take their job.
-Universalized, anyone who wants a job can murder the person currently holding that job. It is contradictory
-to simultaneously will that I acquire a job (through murder) and also that someone can take that job from me 
-whenever they want (also by murder). The maxim thwarts its own end, and is thus internally contradictory.
- Therefore, this maxim is prohibited.
-
-The universalizability test makes the ``formal" nature of Kant's ethics immediately clear. Formal 
-logic has the tools to universalize a maxim (apply a universal quantifier) and to test for 
-contradictions (test for inconsistency).
-
-Kant also presents two additional formulations of the categorical imperative.
-
-$\textbf{Definition}$ \emph{(Formula of Humanity)}
-
-\emph{The Formula of Humanity (FUH)
-is to act in such a way ``that you use humanity, whether in your own person or in the person
-of any other, always at the same time as an end, never merely as a means."}\cite{groundwork}
-
-\medskip
-
-$\textbf{Definition}$ \emph{(Kingdom of Ends)}
-
-\emph{The third formulation of the categorical imperative states that ``we should so act that we may 
-think of ourselves as legislating universal laws through our maxims."}\cite{KorsgaardFUL}
-
-The last two formulations are not as obviously formal as the FUL, but they can still be
-modelled in logic. Because Kantian ethics presents a series of rules, a logical system can encode 
-the theory by modelling each rule as an axiom.
-
-The above outline is a brief and incomplete picture of a rich philosophical tradition. Kantian scholars
-debate the meaning of each formulation of the categorical imperative and develop views far more 
-nuanced than those above. For the purposes of this paper, I will adopt Kant's three original 
-formulations presented above. Note additionally that Kantian ethics is widely disputed. I do not present 
-a defense of Kant's ethic in this paper. My approach to formalizing ethics can be applied to other 
-theories as well.
-
-This paper aims to formalize Kant's ethic as faithfully as possible. This is an important choice. 
-While it is tempting to modify or simplify an ethical theory in seemingly insignificant way, these 
-choices often have ramifications. The entire field of neo-Kantian thought 
-has been exploring versions of Kant's ethical theory for centuries. I will not attempt to present a 
-radically new conception of Kant's ethic, but will instead draw on philosophical expertise regarding
-the content and justification of the categorical imperative.%
+I formalize Kantian ethics by representing it as an axiom on top of a base logic. In this section, 
+I present the logical background necessary to understand my work and my choice of base logic.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \isatagdocument
-%
-\isamarkupsubsection{Dyadic Deontic Logic \label{sec:DDL}%
-}
-\isamarkuptrue%
 %
@@
 Traditional modal logics include the necessitation operator, denoted as $\Box$. In simple modal logic
-using the Kripke semantics s \cite{cresswell}, $\Box p$ is true at a world $w$ if $p$ is true at all of $w$'s neighbors. 
-These logics also usually contain the $\diamond$ operator, representing possibility, where
+using the Kripke semantics, $\Box p$ is true at a world $w$ if $p$ is true at all of $w$'s neighbors \cite{cresswell}. 
+These logics usually also contain the possibility operator $\diamond$, where
  $\diamond p \iff \sim \Box \sim p$. Additionally, modal logics include operators of propositional 
@@
 A deontic logic is a special kind of modal logic designed to reason about obligation. Standard deontic
-logic \cite{cresswell, sep-logic-deontic} replaces $\Box$ with the obligation operator
+logic \citep{cresswell, sep-logic-deontic} replaces $\Box$ with the obligation operator
 $O$, and $\diamond$ with the permissibility operator $P$. Using the Kripke semantics for $O$, $O p$ 
@@
 contradiction results because the logic cannot handle violations of duty mixed with
-conditionals. \cite{chisholm, ctd}
+conditionals. \citep{chisholm, ctd}
 }. 
@@
 
-For more of fine-grained properties of DDL see \cite{CJDDL} or this project's source code. DDL is a heavy logic and contains modal operators 
+For more of fine-grained properties of DDL see \citep{CJDDL} or this project's source code. DDL is a heavy logic and contains modal operators 
 that aren't necessary for my analysis. While this expressivity is powerful, it may also cause performance
@@
 %:%112=83%:%
-%:%121=85%:%
-%:%133=87%:%
-%:%134=88%:%
+%:%115=85%:%
+%:%123=87%:%
 %:%135=89%:%
 %:%136=90%:%
-%:%137=91%:%
-%:%138=92%:%
-%:%139=93%:%
-%:%140=94%:%
-%:%141=95%:%
-%:%142=96%:%
-%:%143=97%:%
-%:%144=98%:%
-%:%145=99%:%
-%:%146=100%:%
-%:%147=101%:%
-%:%148=102%:%
-%:%149=103%:%
-%:%150=104%:%
-%:%151=105%:%
-%:%152=106%:%
-%:%153=107%:%
-%:%154=108%:%
-%:%155=109%:%
-%:%156=110%:%
-%:%157=111%:%
-%:%158=112%:%
-%:%159=113%:%
-%:%160=114%:%
-%:%161=115%:%
-%:%162=116%:%
-%:%163=117%:%
-%:%164=118%:%
-%:%165=119%:%
-%:%166=120%:%
-%:%167=121%:%
-%:%168=122%:%
-%:%169=123%:%
-%:%170=124%:%
-%:%171=125%:%
-%:%172=126%:%
-%:%173=127%:%
-%:%174=128%:%
-%:%175=129%:%
-%:%176=130%:%
-%:%177=131%:%
-%:%178=132%:%
-%:%179=133%:%
-%:%180=134%:%
-%:%181=135%:%
-%:%182=136%:%
-%:%183=137%:%
-%:%184=138%:%
-%:%185=139%:%
-%:%186=140%:%
-%:%187=141%:%
-%:%188=142%:%
-%:%189=143%:%
-%:%190=144%:%
-%:%191=145%:%
-%:%192=146%:%
-%:%193=147%:%
-%:%194=148%:%
-%:%195=149%:%
-%:%196=150%:%
-%:%197=151%:%
-%:%198=152%:%
-%:%199=153%:%
-%:%200=154%:%
-%:%201=155%:%
-%:%202=156%:%
-%:%203=157%:%
-%:%212=161%:%
-%:%216=163%:%
-%:%228=165%:%
-%:%229=166%:%
-%:%230=167%:%
-%:%231=168%:%
-%:%232=169%:%
-%:%233=170%:%
-%:%234=171%:%
-%:%235=172%:%
-%:%236=173%:%
-%:%237=174%:%
-%:%238=175%:%
-%:%239=176%:%
-%:%240=177%:%
-%:%241=178%:%
-%:%242=179%:%
-%:%243=180%:%
-%:%244=181%:%
-%:%245=182%:%
-%:%246=183%:%
-%:%247=184%:%
-%:%248=185%:%
-%:%249=186%:%
-%:%250=187%:%
-%:%251=188%:%
-%:%252=189%:%
-%:%253=190%:%
-%:%262=192%:%
-%:%274=194%:%
-%:%275=195%:%
-%:%276=196%:%
-%:%277=197%:%
-%:%278=198%:%
-%:%279=199%:%
-%:%280=200%:%
-%:%281=201%:%
-%:%282=202%:%
-%:%283=203%:%
-%:%284=204%:%
-%:%285=205%:%
-%:%286=206%:%
-%:%287=207%:%
-%:%288=208%:%
-%:%289=209%:%
-%:%290=210%:%
-%:%291=211%:%
-%:%292=212%:%
+%:%145=92%:%
+%:%157=95%:%
+%:%158=96%:%
+%:%159=97%:%
+%:%160=98%:%
+%:%161=99%:%
+%:%162=100%:%
+%:%163=101%:%
+%:%164=102%:%
+%:%165=103%:%
+%:%166=104%:%
+%:%167=105%:%
+%:%168=106%:%
+%:%169=107%:%
+%:%170=108%:%
+%:%171=109%:%
+%:%172=110%:%
+%:%173=111%:%
+%:%174=112%:%
+%:%175=113%:%
+%:%176=114%:%
+%:%177=115%:%
+%:%178=116%:%
+%:%179=117%:%
+%:%180=118%:%
+%:%181=119%:%
+%:%182=120%:%
+%:%191=122%:%
+%:%203=124%:%
+%:%204=125%:%
+%:%205=126%:%
+%:%206=127%:%
+%:%207=128%:%
+%:%208=129%:%
+%:%209=130%:%
+%:%210=131%:%
+%:%211=132%:%
+%:%212=133%:%
+%:%213=134%:%
+%:%214=135%:%
+%:%215=136%:%
+%:%216=137%:%
+%:%217=138%:%
+%:%218=139%:%
+%:%219=140%:%
+%:%220=141%:%
+%:%221=142%:%

### 2021-11-07 paper/output/document/paper22.tex
finished application tests for Kroy - next steps are to port learnings to the naive interpretation, and move on to metaethical tests
added maxim
cleaned much of naive

@@
 \begin{isamarkuptext}%
-Isabelle/HOL is an interactive proof assistant \cite{isabelle} built on Haskell and Scala. It 
+The final component of my project is the automated theorem prover I use to automate my formalization.
+Isabelle/HOL is an interactive proof assistant built on Haskell and Scala \cite{isabelle}. It 
 allows the user to define types, functions, definitions, and axiom systems. It has built-in support for both
@@
 
-I started my project by reimplementing Benzmueller, Farjami, and Parent's \cite{BFP, logikey} implementation 
-of DDL in Isabelle/HOL. This helped me learn how to use Isabelle/HOL, and the implementation showcased in the 
+I started my project by reimplementing Benzmueller, Farjami, and Parent's implementation 
+of DDL in Isabelle/HOL \cite{BFP, logikey}. This helped me learn how to use Isabelle/HOL, and the implementation showcased in the 
 next few sections demonstrates the power of Isabelle.
 
-BFP use a shallow semantic embedding. This kind of embedding models the semantics of DDL as 
+Benzmueller, Farjami, and Parent use a shallow semantic embedding. This kind of embedding models the semantics of DDL as 
 constants in HOL and axioms as constraints on DDL models. This document will contain a subset of my 
@@
 a model is specificied by the relevant accessibility relations, so it suffices to place conditions on 
-the accessibility relations. These axioms can be quite unweildy, so luckily I was able to lift BFP's \cite{BFP}
-implementation of Carmo and Jones's original axioms directly. Here's an example of an axiom:%
+the accessibility relations. These axioms can be quite unweildy, so luckily I was able to lift BFP's 
+implementation of Carmo and Jones's original axioms directly \citep{BFP}. Here's an example of an axiom:%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \isacommand{abbreviation}\isamarkupfalse%
+\ ddlfalse{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymbottom}{\isachardoublequoteclose}{\isacharparenright}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymbottom}\ {\isasymequiv}\ {\isasymlambda}w{\isachardot}\ False{\isachardoublequoteclose}\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
 \ ddlob{\isacharunderscore}normal{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isasymRightarrow}t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}O\ {\isacharbraceleft}{\isacharunderscore}{\isacharbraceright}{\isachardoublequoteclose}{\isacharparenright}\isanewline
@@
 of the theory (axioms) are valid for this semantics - so to show that every axiom holds at every 
-world. BFP \cite{BFP} provide a complete treatment of the completeness of their embedding, but I 
+world. Benzmueller, Farjami, and Parent provide a complete treatment of the completeness of their embedding, but I 
 will include selected axioms that are particularly interesting here. This section also demonstrates many
@@
 %:%47=19%:%
-%:%56=22%:%
-%:%68=24%:%
-%:%70=26%:%
-%:%71=26%:%
-%:%72=26%:%
-%:%73=26%:%
+%:%48=20%:%
+%:%57=23%:%
+%:%69=25%:%
+%:%71=27%:%
+%:%72=27%:%
+%:%73=27%:%
 %:%74=27%:%
 %:%75=28%:%
-%:%76=28%:%
-%:%77=28%:%
-%:%78=28%:%
-%:%80=29%:%
+%:%76=29%:%
+%:%77=29%:%
+%:%78=29%:%
+%:%79=29%:%
 %:%81=30%:%
-%:%82=30%:%
-%:%85=44%:%
-%:%87=46%:%
-%:%88=46%:%
-%:%89=46%:%
-%:%90=46%:%
+%:%82=31%:%
+%:%83=31%:%
+%:%86=45%:%
+%:%88=47%:%
+%:%89=47%:%
+%:%90=47%:%
 %:%91=47%:%
-%:%92=47%:%
-%:%93=47%:%
-%:%101=51%:%
-%:%113=53%:%
+%:%92=48%:%
+%:%93=48%:%
+%:%94=48%:%
+%:%102=52%:%
 %:%114=54%:%
@@
 %:%116=56%:%
-%:%118=80%:%
+%:%117=57%:%
 %:%119=81%:%
 %:%120=82%:%
-%:%122=83%:%
+%:%121=83%:%
 %:%123=84%:%
@@
 %:%125=86%:%
-%:%126=86%:%
-%:%134=93%:%
-%:%146=95%:%
+%:%126=87%:%
+%:%127=87%:%
+%:%135=94%:%
 %:%147=96%:%
@@
 %:%151=100%:%
-%:%155=116%:%
-%:%157=117%:%
-%:%158=117%:%
+%:%152=101%:%
+%:%156=117%:%
+%:%158=118%:%
 %:%159=118%:%
 %:%160=119%:%
-%:%161=119%:%
+%:%161=120%:%
 %:%162=120%:%
-%:%164=122%:%
-%:%166=123%:%
-%:%167=123%:%
+%:%163=121%:%
+%:%165=123%:%
+%:%167=124%:%
 %:%168=124%:%
-%:%170=125%:%
-%:%171=125%:%
-%:%174=145%:%
+%:%169=125%:%
+%:%171=126%:%
+%:%172=126%:%
 %:%175=146%:%
-%:%177=147%:%
-%:%178=147%:%
+%:%176=147%:%
+%:%178=148%:%
 %:%179=148%:%
 %:%180=149%:%
-%:%181=149%:%
+%:%181=150%:%
 %:%182=150%:%
-%:%184=151%:%
-%:%187=153%:%
-%:%189=154%:%
-%:%190=154%:%
-%:%191=155%:%
-%:%199=162%:%
-%:%211=164%:%
-%:%212=165%:%
-%:%213=166%:%
-%:%214=167%:%
-%:%215=168%:%
-%:%219=170%:%
-%:%221=171%:%
-%:%222=171%:%
-%:%223=171%:%
-%:%225=171%:%
-%:%229=171%:%
-%:%230=171%:%
-%:%232=172%:%
-%:%233=173%:%
-%:%234=173%:%
-%:%236=174%:%
-%:%237=175%:%
-%:%238=176%:%
-%:%248=178%:%
-%:%249=179%:%
-%:%250=180%:%
-%:%251=181%:%
+%:%183=151%:%
+%:%184=152%:%
+%:%185=152%:%
+%:%186=153%:%
+%:%188=154%:%
+%:%191=156%:%
+%:%193=157%:%
+%:%194=157%:%
+%:%195=158%:%
+%:%203=167%:%
+%:%215=169%:%
+%:%216=170%:%
+%:%217=171%:%
+%:%218=172%:%
+%:%219=173%:%
+%:%223=175%:%
+%:%225=176%:%
+%:%226=176%:%
+%:%227=176%:%
+%:%229=176%:%
+%:%233=176%:%
+%:%234=176%:%
+%:%236=177%:%
+%:%237=178%:%
+%:%238=178%:%
+%:%240=179%:%
+%:%241=180%:%
+%:%242=181%:%
+%:%252=183%:%
+%:%253=184%:%
+%:%254=185%:%
+%:%255=186%:%

### 2021-11-07 paper/output/document/paper31.tex
cleaning
did goals
cleaned much of naive

@@
 \begin{isamarkuptext}%
-In this section, I will present two formulations of the categorical imperative. In Section \ref{sec:naive}, I will 
-consider a simple, naive formulation of the formula of universal law. This formulation is, as I will 
-show, clearly not a good ethical rule. The purpose of this section is to explore the kinds of ethical
-tests that Isabelle can carry out. In Section \ref{sec:kroy}, I will explore Moshe Kroy's \cite{kroy} partial formalization of 
-the first two formulations of the categorical imperative.%
+In this section, I present two formalizations of the categorical imperative and a testing framework
+to evaluate them. In Section \ref{sec:naive}, I will consider an intuitive but naive formalization of 
+the formula of universal law. This formalization is equivalent to a theorem in my base logic (DDL), so 
+thus does not actually increase the power of my base logic. In effect, this formalization serves as a control
+group that I use to present the testing architecture used to evaluate following formalizations.
+In Section \ref{sec:kroy}, I will explore Moshe Kroy's partial formalization of 
+the categorical imperative.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-This section presents a simple and intuitive formalization of the formula of universal law, which 
-is to will only those maxims that you would simultaneously will universalized. The universalizability 
-test creates negative obligations: if a maxim passes the universalizability test, it is permissible. Else,
-it is prohibited.%
+This section presents a simple and intuitive formalization of the Formula of Universal Law (FUL). 
+This naive formalization will hold in the base logic itself, so this formalization does not actually
+improve upon a plain deontic logic at all. This section serves two purposes. First, the naive formalization
+is a toy example that demonstrates the implementation and testing process that will be used for the more 
+complex formalizations presented later in Chapters 2 and 3. Second, this formalization is effectively
+a control group used to determine which properties of obligaition hold in the base logic. Future formalizations
+will improve on the base logic by passing more tests, or equivalently, proving more properties of 
+obligation than the base logic can.
+
+The FUL roughly states that, if a maxim cannot be willed in a world where it is universalized, it is prohibited. One
+reading of this rule is that a maxim is only permissible if it is necessarily permissible. To formalize
+a reading of the FUL like this naive one, I will first represent the reading as a sentence in my logic
+and then add this sentence as an axiom in my logic.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-In order to appropriately formalize the categorical imperative, we to define the notion of permissibility.%
+Many of the formalizations of the categorical imperative that I present in this thesis require
+some logical background. This naive formalization requires that I define the notion of permissibility,
+where an action is permissible if and only if it is not prohibited.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-This naive formalization will require very little additional logical machinery, but more complex
-formalizations may require additional logic concepts.
-
-Let's now consider a naive reading of the Formula of Universal Law (FUL): `act only in accordance 
-with that maxim through which you can at the same time will that it become a universal law' \cite{groundwork}.
+This naive formalization requires no additional logical machinery, but more complex
+formalizations may require additional logical concepts.
+
+Let's now consider a naive reading of the Formula of Universal Law (FUL): ``act only in accordance 
+with that maxim through which you can at the same time will that it become a universal law" \citep{groundwork}.
 An immediate translation to DDL is that if $A$ is not necessary permissible then it is prohibited. In other
 words, if we cannot universalize $P A$ (where universalizing is represented by the modal necessity 
-operator), then $A$ is prohibited. Let's add this as an axiom to our logic.%
+operator), then $A$ is prohibited. This sentence is formalized in the abbreviation below:%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{abbreviation}\isamarkupfalse%
+\ FUL{\isacharunderscore}naive\ \isakeyword{where}\ {\isachardoublequoteopen}FUL{\isacharunderscore}naive\ {\isasymequiv}\ {\isasymlambda}A{\isachardot}\ {\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}{\isacharparenleft}{\isasymbox}\ {\isacharparenleft}P\ A{\isacharparenright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}O\ {\isacharbraceleft}{\isacharparenleft}\isactrlbold {\isasymnot}A{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{For a given maxim `A', the FUL states that if A is not necessarily permissible, it is prohibited.%
+}%
+\begin{isamarkuptext}%
+This naive formalization holds as a theorem of DDL. I show this using Isabelle below:%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isasymforall}A{\isachardot}\ {\isasymTurnstile}\ {\isacharparenleft}FUL{\isacharunderscore}naive\ A{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{by}\isamarkupfalse%
+\ simp\isanewline
+%
+\isamarkupcmt{In this short and simple proof, the statement ``by simp" demonstrates that the proof is completed
+using the ``simp" tool, which is Isabelle's term rewriting engine. In this case, the result follows from
+the definitions of the modal operators in DDL, so term rewriting suffices to complete the proof.%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+The general process of an implementation of a formalization of the FUL will be to represent the 
+formalization as a sentence in my logic, as above, and then to add the formalization as an axiom to 
+the logic. Kant's ethical theory is rule based, so it involves applying the categorical
+imperative to solve ethical dilemmas. In logic, this is equivalent to adopting the categorical imperative as 
+an axiom and then reasoning in the newly formed logic to come to ethical conclusions. Adding the categorical
+imperative as an axiom makes it impossible to violate it and thus represents the categorical imperative
+as the supreme, unviolable law of morality.
+
+Note that under this approach, reasoning about violations of obligation is difficult. Any violation of the 
+categorical imperative immediately results in a contradiction. Developing a Kantian account of contrary-
+to-duty obligations is a much larger philosophical project that is still open \cite{KorsgaardRTL}. This paper will focus 
+on the classical Kantian notion of an ideal moral world, and thus does not reason about violations 
+of the moral law \cite{idealtheory}.
+
+Because my naive formalization holds in the base logic, adding it as an axiom does not make the logic
+any more powerful. No new theorems can be derived using the naive formalization that could not already
+be derived in the base logic. Thus, this section serves as a``control group." Tests performed in this
+section establish which properties of obligation don't hold in the base logic. The fact that these 
+tests will pass for the later, more sophisticated formalizations will serve as evidence for the superiority
+of these formalizations over the base logic.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-Why add the categorical imperative as an axiom of this logic? The purpose of this logic is to 
-perform ethical reasoning. Kant's ethical theory is rule based, so it involves applying the categorical
-imperative to solve ethical dilemmas. In logic, this is equivalent to adopting the categorical imperative as 
-an axiom and then reasoning in the newly formed logic to come to ethical conclusions. Adding the categorical
-imperative as an axiom makes it impossible to violate it.
-
-Note that in this system, reasoning about violations of obligation is difficult. Any violation of the 
-categorical imperative immediately results in a contradiction. Developing a Kantian account of contrary-
-to-duty obligations is a much larger philosophical project that is still open \cite{KorsgaardRTL}. This paper will focus 
-on the classical Kantian notion of an ideal moral world \cite{idealtheory}.
-
-The immediate test for any formalization is consistency, which we can check with Nitpick.%
+Once I add a formalization of the FUL as an axiom to my system, I will test the formalization.
+Each test will take the form of a lemma which I expect to either hold or be disproven by the categorical
+imperative. For example, one test might be the lemma ``murder is wrong." I will evaluate formalizations
+based on their ability to prove expected properties of the categorical imperative, as determined by 
+philosophical literature. These tests fall into two categories: metaethical tests, which focus on 
+abstract properties of the ethical system, and application tests, which simulate the kind of practical reasoning 
+that an agent would actually perform by specifying a simple model.
+
+One way to understand computational ethics is as translational work that seeks
+to translate an ethical theory presented by a philosopher to something that a computer can reason about.
+My testing architecture evaluates how faithful a particular formalization is to the ethical theory that 
+it translate. This testing approach is not specific to my ethical theory and could be used to evaluate
+other formalizations of other theories as well.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsubsection{Metaethical Tests \label{sec:meta_tests_naive}%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
+First, I present metaethical tests for the naive formalization (or equivalently the base logic). 
+These tests evaluate abstract properies of the system, independent of a particular agent, situation, or 
+act. For example, one metaethical test may be to determine if the system is capable of generating models 
+in which actions are obligated. If the system can never obligate anything, this indicates that it is 
+not a good ethical system.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+$\textbf{Preliminary Tests}$%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+The immediate test for any formalization is consistency, or the property of being free of contradictions. 
+An inconsistent formalization is immediately useless, because all sentences are true in an inconsistent
+logic. Nitpick, Isabelle's model checker, offers a handy way of checking consistency. Specifically, 
+if Nitpick can find a model that satisfies all the axioms of the logic, then the logic is consistent.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 }\isanewline
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isatagproof
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isatagproof
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isatagproof
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isatagproof
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\isatagdocument
-%
-\isamarkupsubsubsection{Specifying the Model%
-}
-\isamarkuptrue%
-%
-\endisatagdocument
-{\isafolddocument}%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\begin{isamarkuptext}%
-One category of tests involves specified models to encode certain facts 
-into the system and then ask questions about obligations. Without specifying the model, we are limited 
-to showing high-level metaethical facts. Let's start with analyzing an obvious example - that murder is 
-wrong.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{consts}\isamarkupfalse%
-\ M{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isachardoublequoteclose}\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ murder{\isacharunderscore}wrong{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}murder{\isacharunderscore}wrong\ {\isasymequiv}\ {\isasymTurnstile}{\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ M{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isatagproof
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-\isanewline
-%
-\endisadelimproof
-\isacommand{abbreviation}\isamarkupfalse%
-\ possibly{\isacharunderscore}murder{\isacharunderscore}wrong{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}possibly{\isacharunderscore}murder{\isacharunderscore}wrong\ {\isasymequiv}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ M{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ cw{\isachardoublequoteclose}\isanewline
-%
-\isamarkupcmt{These are very simple properties. \isa{poss{\isacharunderscore}murder{\isacharunderscore}wrong} is an abbreviation for the axiom
-that there is some world where murder might be prohibited. Even this is quite a strong assumption - 
-ideally we'd want to give the system nonmoral facts about murder (like a definition) and then make 
-moral claims.%
-}\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ wrong{\isacharunderscore}if{\isacharunderscore}possibly{\isacharunderscore}wrong{\isacharcolon}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}possibly{\isacharunderscore}murder{\isacharunderscore}wrong\ {\isasymlongrightarrow}\ murder{\isacharunderscore}wrong{\isachardoublequoteclose}\isanewline
-%
-\isadelimproof
-\ \ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{by}\isamarkupfalse%
-\ simp\isanewline
-%
-\isamarkupcmt{This lemma gets to the ``heart" of this naive interpretation. We really want to say that if something
- isn't necessarily obligated, it's not obligated anywhere.%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-The above example does exactly what we expect it to: we show that if something is wrong somewhere 
-it's wrong everywhere. That being said, it seems like quite a weak claim. We assumed a very strong, moral 
-fact about murder (that it is wrong somewhere), so it's not surprise that we were able to reach our desired conclusion.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-Let's try a weaker assumption: Not everyone can lie.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{typedecl}\isamarkupfalse%
-\ person\isanewline
-\isacommand{consts}\isamarkupfalse%
-\ lie{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}person{\isasymRightarrow}t{\isachardoublequoteclose}\isanewline
-\isacommand{consts}\isamarkupfalse%
-\ me{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}person{\isachardoublequoteclose}\isanewline
-%
-\isamarkupcmt{Notice that this machinery is quite empty. We don't give axioms about what a person can or can't do.%
-}\isanewline
-\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ lying{\isacharunderscore}not{\isacharunderscore}universal{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}lying{\isacharunderscore}not{\isacharunderscore}universal\ {\isasymequiv}\ {\isasymforall}w{\isachardot}\ {\isasymnot}\ {\isacharparenleft}{\isacharparenleft}{\isasymforall}x{\isachardot}\ lie{\isacharparenleft}x{\isacharparenright}\ w{\isacharparenright}\ {\isasymand}\ {\isacharparenleft}lie{\isacharparenleft}me{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
-\begin{isamarkuptext}%
-This is a rough translation of failure of the universalizability test: we will test the maxim universally,
-as represented by the universal quantifier in the first conjunct, and simultaneously \cite{simul}, as represented by 
-the second conjunct. The FUL tells us that if this sentence is true, then lying should be prohibited. 
-Let's test it.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ breaking{\isacharunderscore}promises{\isacharcolon}\isanewline
-\ \ \isakeyword{assumes}\ lying{\isacharunderscore}not{\isacharunderscore}universal\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}lie{\isacharparenleft}me{\isacharparenright}{\isacharparenright}{\isacharbraceright}{\isacharparenright}\ cw{\isachardoublequoteclose}\isanewline
-\ \ \isacommand{nitpick}\isamarkupfalse%
-\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}\isanewline
-%
-\isadelimproof
-\ \ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{oops}\isamarkupfalse%
-\isanewline
-%
-\isamarkupcmt{\color{blue} Nitpick found a counterexample for card person = 2 and card i = 2:
-
-  Free variable:
-    lie = ($\lambda x. \_$)($p_1$ := ($\lambda x. \_$)($i_1$ := True, $i_2$ := False), $p_2$ := ($\lambda x. \_$)($i_1$ := False, $i_2$ := False)) \color{black}%
-}\isanewline
-%
-\isamarkupcmt{Quick note on how to read Nitpick results. Nitpick will either say that it found a ``model" or a ``counterexample" in 
-the first line. It will then provide a model by specifying model components. For readability, all except for the 
-free variables are hidden. This model has cardinality 2 for the person and world (i) types. The term \texttt{lie} is 
-defined for people $p_1$ and $p_2$. $p_1$ lies at world $i_1$ and does not lie at world $i_2$. $p_2$ does
-the opposite.%
-}\isanewline
-%
-\isamarkupcmt{These details will be elided for most Nitpick examples, but this provides guidance on how to interpret
-the output.%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-This formula isn't valid. While the FUL should tell us that lying is prohibited, the fact that it 
-doesn't demonstrates the weakness of this naive formulation of the categorical imperative. Kant's version of
-the FUL universalizes across people, as we did in the definition of \isa{lying{\isacharunderscore}not{\isacharunderscore}universal\ {\isasymequiv}\ {\isasymforall}w{\isachardot}\ {\isasymnot}\ {\isacharparenleft}{\isacharparenleft}{\isasymforall}x{\isachardot}\ lie\ x\ w{\isacharparenright}\ {\isasymand}\ lie\ me\ w{\isacharparenright}}.
-The
-naive formalization universalizes across worlds using the $\Box$ operator, so it makes sense that it can't
-handle this example appropriately.
-
-The above implies that the FUL should prescribe consistent obligations across people. If our formalization
-doesn't, clearly something has gone wrong somewhere. Let's test that!%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ universalizability{\isacharcolon}\isanewline
-\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymTurnstile}\ O\ {\isacharbraceleft}{\isacharparenleft}lie{\isacharparenleft}me{\isacharparenright}{\isacharparenright}{\isacharbraceright}{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}x{\isachardot}\ {\isasymTurnstile}\ {\isacharparenleft}O\ {\isacharbraceleft}{\isacharparenleft}lie{\isacharparenleft}x{\isacharparenright}{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-\ \ \isacommand{nitpick}\isamarkupfalse%
-\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{oops}\isamarkupfalse%
-\isanewline
-%
-\isamarkupcmt{\color{blue} Nitpick found a counterexample for card person = 2 and card i = 2:
-
-  Free variable:
-    lie = ($\lambda x. \_$)($p_1$ := ($\lambda x. \_$)($i_1$ := False, $i_2$ := True), $p_2$ := ($\lambda x. \_$)($i_1$ := False, $i_2$ := False))
-  Skolem constant:
-    x = $p_2$ \color{black}%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-This lemma demonstrates the problem with the naive interpretation. The FUL universalizes across people
-but the naive formalization universalizes across worlds. Because this interpretation is so naive, it is 
-limited in its power. However, this serves as an example of the kind of reasoning that 
-Isabelle empowers us to do. Even this simple argument has philosophical consequences. It tells us that
-reading the FUL as a claim about consistency across possible worlds, instead of consistency across 
-agents, leads to counterintuitive conclusions.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\isatagdocument
-%
-\isamarkupsubsubsection{Metaethical Properties%
-}
-\isamarkuptrue%
-%
-\endisatagdocument
-{\isafolddocument}%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\begin{isamarkuptext}%
-The above section specified the model to simulate practical ethical reasoning, or the kind of 
-reasoning that is useful when an agent has to decide what to do. Formalizations of the categorical 
-imperative can also be used to do metaethical reasoning, which can evaluate a particular ethical theory
-as good or bad. In this case, we can analyze properties of the system in the form of theorems. For example,
-if we can show that, in this system, nothing is ever obligated, that would indicate that we have a bad 
-ethical system. This is not only philosophical work, but is also a useful way to test different ethical
-reasoning systems.
-
-An initial property that we might be interested in is permissibility itself. More generally, an ethical
-theory that doesn't allow for permissibility would require that every action is either obligatory or 
-prohibited. In fact, if that is the case, many counterintuitive theorems follow, including that all 
-permissible actions are obligatory.\footnote{Proof is in the appendix.}%
+\isanewline
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+An initial property that we might be interested in is the possibility of permissibility, or 
+whether or not the system can generate models in which certain acts are permissible. In modern ethics, 
+permissibility is a well-accepted phenomenon.
+An ethical theory that doesn't allow for permissibility would require that every action is either obligatory or 
+prohibited. If that is the case, many counterintuitive theorems follow, including that all 
+permissible actions are obligatory.\footnote{Proof is in the appendix.} Therefore, I will include 
+the possibility of permissibility as one test for my formalizations.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupcmt{We want to show that there exists a model where there is some formula A that is permissible, or, 
+\isamarkupcmt{I want to show that there exists a model where there is some formula A that is permissible, or, 
 in English, that permissibility is possible. Nitpick finds a model where the above formula holds, 
 so permissibility is indeed possible.%
-}\isanewline
-%
-\isamarkupcmt{Note that it's not clear \cite{kitcher} if Kant actually thought that permissibility was a coherent 
-concept. Either way, in modern ethics, permissibility is a pretty widely accepted phenomenon.%
 }%
@@
 \endisadelimproof
-\isanewline
-\isanewline
+%
+\begin{isamarkuptext}%
+Another similar property is that for any arbitrary action A, there is a model that makes 
+it permissible. This property is actually not desirable, because if A is "murder" then the CI should require that 
+it be prohibited in every world. Therefore, in order for this test to pass, Nitpick should \emph{not}
+be able to find a satisfying model for this formula.%
+\end{isamarkuptext}\isamarkuptrue%
 \isacommand{lemma}\isamarkupfalse%
@@
 %
-\isamarkupcmt{This is a slightly stronger result: for any arbitrary action A, there is a model that makes it 
-permissible. We actually don't want this to hold, because if A is "murder" then the CI requires that 
-it be prohibited in every world.%
+\isamarkupcmt{Because Nitpick finds a satisfying model for this formula, this test fails for the naive interpretation.%
 }%
@@
 \begin{isamarkuptext}%
-Another initial test is the possibility of arbitrary obligations. If anything can be shown to be 
-obligatory in this theory, then clearly it doesn't track our intuitions.%
+Another initial property is that arbitary actions should not be obligated. No sensible ethical
+theory would require that any arbitrary action A is obligated, because A may be something obviously wrong,
+like murder. In order for this test to pass, Nitpick must disprove the formula below by finding a counterexample.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupcmt{This is good! Shows us that any arbitrary term isn't obligatory.%
+\isamarkupcmt{Nitpick finds a counterexample disproving the statement that any arbitrary action is obligatory, so
+this test passes.%
 }%
@@
 \begin{isamarkuptext}%
-A more complex metaethical property is the possibility of conflicting obligations. Many deontological
-ethics are criticized for prescribing conflicting obligations, but in Kantian ethics, 
-obligations never conflict \cite{contradictoryob}. In order for morality to be action-guiding, it needs to be free of 
-conflicting obligations. Let's see if we can have contradictary obligations under the naive formalization.%
+The next set of tests will focus on conflicting obligations. There is some debate about Kant's
+personal stance on conflicting obligations, but neo-Kantian agree that the FUL itself cannot obligate
+conflicting actions. For more complete discussion of conflicting obligations in Kantian literature, 
+see \ref{sec:priorgoals}. I will first test whether or not, for some arbitrary action, Nitpick can find
+a model in which that action is both obligated and prohibited.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupcmt{Oh no! Nitpick found a model with conflicting obligations - that's bad!%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-This is a property of DDL itself, not necessarily of my formalization specifically. A future, 
-more robust formalization should add an axiom that disallows this. Let's see if that causes any obvious 
-problems.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ removing{\isacharunderscore}conflicting{\isacharunderscore}obligations{\isacharcolon}\isanewline
-\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}A{\isachardot}\ {\isasymTurnstile}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymand}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{shows}\ True\isanewline
-\ \ \isacommand{nitpick}\isamarkupfalse%
-\ {\isacharbrackleft}satisfy{\isacharcomma}user{\isacharunderscore}axioms{\isacharcomma}format{\isacharequal}{\isadigit{2}}{\isacharbrackright}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{oops}\isamarkupfalse%
-\isanewline
-%
-\isamarkupcmt{\color{blue} Nitpick found a model for card i = 1:
-
-  Empty assignment \color{black}%
-}\isanewline
-%
-\isamarkupcmt{We can disallow conflicting obligations and the system is still consistent - that's good.%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-The above is a rather weak notion of contradictory obligations. Korsgaard \cite{KorsgaardFUL} argues that Kantian 
-ethics also has the stronger property that if two maxims imply a contradiction, they must not be willed.
-Let's see if that fact holds in this formalization.%
+\isamarkupcmt{Nitpick found a model with conflicting obligations, so this tests fails.%
+}\isanewline
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+The above is a rather weak notion of contradictory obligations. Korsgaard additionally argues that Kantian 
+ethics also has the stronger property that if two maxims imply a contradiction, they must not be willed \cite{KorsgaardFUL}.
+I test this property below. Because this property is stronger than the previous test, and the previous 
+test failed, this test will also fail.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupcmt{Sadly the property we're actually interested in doesn't follow.%
+\isamarkupcmt{Sadly the property I'm actually interested in doesn't follow.%
 }%
@@
 and you are obligated to do B." We think those English sentences mean the same thing, so they should mean 
-the same thing in our logic as well. Let's test that.%
+the same thing in our logic as well. This ``distributive" property of obligation is another test.%
 \end{isamarkuptext}\isamarkuptrue%
@@
     A = ($\lambda x. \_$)($i_1$ := True, $i_2$ := False)
-    B = ($\lambda x. \_$)($i_1$ := False, $i_2$ := True)\color{black}%
+    B = ($\lambda x. \_$)($i_1$ := False, $i_2$ := True)\color{black}
+Once again, this tests fails in the control group.%
 }%
@@
 \begin{isamarkuptext}%
-Note that this is a property of DDL itself, not just my formalization. A future formalization might 
-add this property as an axiom.\footnote{For discussion of why this property doesn't hold in DDL, see the Appendix.}%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
 $\textbf{Miscellaneous Properties}$%
@@
 \begin{isamarkuptext}%
-I named this formalization the naive formulation for a reason. Though it seems to be an immediate
-translation of the FUL into DDL, it doesn't fully respect the properties of modal logic itself. In particular, the 
-formalization as given is equivalent to the below theorem.%
+The last set of metaethical tests involve miscellaneous properties of the categorical 
+imperative. First, I show that the naive formalization is equivalent to the below theorem, which clearly
+fails to track intuition about ethics.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \isamarkupcmt{This is a direct consequence\footnote{For a manual proof, see the Appendix.} of the naive formalization, but it's not clear to me that this is 
-actually how we think about ethics. For example, we can imagine an alternate universe where smiling at 
-someone is considered an incredibly rude and disrespectful gesture. In this universe, we are probably 
+actually how we think about ethics. For example, imagine an alternate universe where smiling at 
+someone is considered an incredibly rude and disrespectful gesture. In this universe, I am probably 
 prohibited from smiling at people, but this doesn't mean that in this current universe, smiling is 
@@
 The ``ought implies can" principle is attributed to Kant\footnote{The exact philosophical credence of this view is disputed, but the rough idea holds nonetheless. See \cite{kohl} for more.}
- and is rather intuitive: you can't be obligated to do the impossible. It is worth noting that deontic 
-logics evolved \cite{cresswell} specifically from this principle, so this should hold in both my 
-modified logic and in DDL.%
+ and is rather intuitive: you can't be obligated to do the impossible. Deontic 
+logics evolved specifically from this principle, so this should hold in the base logic \cite{cresswell}.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupcmt{\isa{{\isasymTurnstile}{\isasymlambda}w{\isachardot}\ ob\ {\isacharquery}B\ {\isacharquery}A\ {\isasymlongrightarrow}\ {\isasymnot}\ {\isasymTurnstile}\isactrlbold {\isasymnot}\ {\isacharquery}B\isactrlbold {\isasymand}{\isacharquery}A} is an axiom of DDL itself, so this theorem holds in DDL.%
-}\isanewline
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isatagproof
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isatagproof
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsubsection{Application Tests \label{sec:app_tests_naive}%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
+STARTHERE One category of tests involves specified models to encode certain facts 
+into the system and then ask questions about obligations. Without specifying the model, we are limited 
+to showing high-level metaethical facts. Let's start with analyzing an obvious example - that murder is 
+wrong.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{consts}\isamarkupfalse%
+\ M{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isachardoublequoteclose}\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ murder{\isacharunderscore}wrong{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}murder{\isacharunderscore}wrong\ {\isasymequiv}\ {\isasymTurnstile}{\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ M{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+\isanewline
+%
+\endisadelimproof
+\isacommand{abbreviation}\isamarkupfalse%
+\ possibly{\isacharunderscore}murder{\isacharunderscore}wrong{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}possibly{\isacharunderscore}murder{\isacharunderscore}wrong\ {\isasymequiv}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ M{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ cw{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{These are very simple properties. \isa{poss{\isacharunderscore}murder{\isacharunderscore}wrong} is an abbreviation for the axiom
+that there is some world where murder might be prohibited. Even this is quite a strong assumption - 
+ideally we'd want to give the system nonmoral facts about murder (like a definition) and then make 
+moral claims.%
+}\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ wrong{\isacharunderscore}if{\isacharunderscore}possibly{\isacharunderscore}wrong{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}possibly{\isacharunderscore}murder{\isacharunderscore}wrong\ {\isasymlongrightarrow}\ murder{\isacharunderscore}wrong{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{by}\isamarkupfalse%
+\ simp\isanewline
+%
+\isamarkupcmt{This lemma gets to the ``heart" of this naive interpretation. We really want to say that if something
+ isn't necessarily obligated, it's not obligated anywhere.%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+The above example does exactly what we expect it to: we show that if something is wrong somewhere 
+it's wrong everywhere. That being said, it seems like quite a weak claim. We assumed a very strong, moral 
+fact about murder (that it is wrong somewhere), so it's not surprise that we were able to reach our desired conclusion.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+Let's try a weaker assumption: Not everyone can lie.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{typedecl}\isamarkupfalse%
+\ person\isanewline
+\isacommand{consts}\isamarkupfalse%
+\ lie{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}person{\isasymRightarrow}t{\isachardoublequoteclose}\isanewline
+\isacommand{consts}\isamarkupfalse%
+\ me{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}person{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Notice that this machinery is quite empty. We don't give axioms about what a person can or can't do.%
+}\isanewline
+\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ lying{\isacharunderscore}not{\isacharunderscore}universal{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}lying{\isacharunderscore}not{\isacharunderscore}universal\ {\isasymequiv}\ {\isasymforall}w{\isachardot}\ {\isasymnot}\ {\isacharparenleft}{\isacharparenleft}{\isasymforall}x{\isachardot}\ lie{\isacharparenleft}x{\isacharparenright}\ w{\isacharparenright}\ {\isasymand}\ {\isacharparenleft}lie{\isacharparenleft}me{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
+\begin{isamarkuptext}%
+This is a rough translation of failure of the universalizability test: we will test the maxim universally,
+as represented by the universal quantifier in the first conjunct, and simultaneously \cite{simul}, as represented by 
+the second conjunct. The FUL tells us that if this sentence is true, then lying should be prohibited. 
+Let's test it.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ breaking{\isacharunderscore}promises{\isacharcolon}\isanewline
+\ \ \isakeyword{assumes}\ lying{\isacharunderscore}not{\isacharunderscore}universal\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}lie{\isacharparenleft}me{\isacharparenright}{\isacharparenright}{\isacharbraceright}{\isacharparenright}\ cw{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{\color{blue} Nitpick found a counterexample for card person = 2 and card i = 2:
+
+  Free variable:
+    lie = ($\lambda x. \_$)($p_1$ := ($\lambda x. \_$)($i_1$ := True, $i_2$ := False), $p_2$ := ($\lambda x. \_$)($i_1$ := False, $i_2$ := False)) \color{black}%
+}\isanewline
+%
+\isamarkupcmt{Quick note on how to read Nitpick results. Nitpick will either say that it found a ``model" or a ``counterexample" in 
+the first line. It will then provide a model by specifying model components. For readability, all except for the 
+free variables are hidden. This model has cardinality 2 for the person and world (i) types. The term \texttt{lie} is 
+defined for people $p_1$ and $p_2$. $p_1$ lies at world $i_1$ and does not lie at world $i_2$. $p_2$ does
+the opposite.%
+}\isanewline
+%
+\isamarkupcmt{These details will be elided for most Nitpick examples, but this provides guidance on how to interpret
+the output.%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+This formula isn't valid. While the FUL should tell us that lying is prohibited, the fact that it 
+doesn't demonstrates the weakness of this naive formulation of the categorical imperative. Kant's version of
+the FUL universalizes across people, as we did in the definition of \isa{lying{\isacharunderscore}not{\isacharunderscore}universal\ {\isasymequiv}\ {\isasymforall}w{\isachardot}\ {\isasymnot}\ {\isacharparenleft}{\isacharparenleft}{\isasymforall}x{\isachardot}\ lie\ x\ w{\isacharparenright}\ {\isasymand}\ lie\ me\ w{\isacharparenright}}.
+The
+naive formalization universalizes across worlds using the $\Box$ operator, so it makes sense that it can't
+handle this example appropriately.
+
+The above implies that the FUL should prescribe consistent obligations across people. If our formalization
+doesn't, clearly something has gone wrong somewhere. Let's test that!%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ universalizability{\isacharcolon}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymTurnstile}\ O\ {\isacharbraceleft}{\isacharparenleft}lie{\isacharparenleft}me{\isacharparenright}{\isacharparenright}{\isacharbraceright}{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}x{\isachardot}\ {\isasymTurnstile}\ {\isacharparenleft}O\ {\isacharbraceleft}{\isacharparenleft}lie{\isacharparenleft}x{\isacharparenright}{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{\color{blue} Nitpick found a counterexample for card person = 2 and card i = 2:
+
+  Free variable:
+    lie = ($\lambda x. \_$)($p_1$ := ($\lambda x. \_$)($i_1$ := False, $i_2$ := True), $p_2$ := ($\lambda x. \_$)($i_1$ := False, $i_2$ := False))
+  Skolem constant:
+    x = $p_2$ \color{black}%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+This lemma demonstrates the problem with the naive interpretation. The FUL universalizes across people
+but the naive formalization universalizes across worlds. Because this interpretation is so naive, it is 
+limited in its power. However, this serves as an example of the kind of reasoning that 
+Isabelle empowers us to do. Even this simple argument has philosophical consequences. It tells us that
+reading the FUL as a claim about consistency across possible worlds, instead of consistency across 
+agents, leads to counterintuitive conclusions.%
+\end{isamarkuptext}\isamarkuptrue%
 %
@@
 \isatagtheory
+\isacommand{end}\isamarkupfalse%
 %
@@
 \endisadelimtheory
+\isanewline
 %
@@
 %:%40=13%:%
-%:%49=15%:%
-%:%61=17%:%
-%:%62=18%:%
+%:%41=14%:%
+%:%42=15%:%
+%:%51=17%:%
 %:%63=19%:%
 %:%64=20%:%
-%:%73=22%:%
-%:%85=24%:%
-%:%87=26%:%
-%:%88=26%:%
-%:%89=27%:%
-%:%91=28%:%
-%:%92=29%:%
-%:%95=31%:%
-%:%96=32%:%
-%:%97=33%:%
-%:%98=34%:%
-%:%99=35%:%
-%:%100=36%:%
-%:%101=37%:%
-%:%102=38%:%
-%:%104=40%:%
-%:%105=40%:%
-%:%106=41%:%
-%:%108=43%:%
-%:%109=44%:%
-%:%110=45%:%
-%:%111=46%:%
-%:%112=47%:%
-%:%113=48%:%
-%:%114=49%:%
-%:%115=50%:%
-%:%116=51%:%
-%:%117=52%:%
-%:%118=53%:%
+%:%65=21%:%
+%:%66=22%:%
+%:%67=23%:%
+%:%68=24%:%
+%:%69=25%:%
+%:%70=26%:%
+%:%71=27%:%
+%:%72=28%:%
+%:%73=29%:%
+%:%74=30%:%
+%:%75=31%:%
+%:%76=32%:%
+%:%85=34%:%
+%:%97=36%:%
+%:%98=37%:%
+%:%99=38%:%
+%:%101=40%:%
+%:%102=40%:%
+%:%103=41%:%
+%:%105=42%:%
+%:%106=43%:%
+%:%109=45%:%
+%:%110=46%:%
+%:%111=47%:%
+%:%112=48%:%
+%:%113=49%:%
+%:%114=50%:%
+%:%115=51%:%
+%:%116=52%:%
+%:%118=54%:%
 %:%119=54%:%
-%:%121=57%:%
-%:%122=57%:%
-%:%123=57%:%
-%:%125=57%:%
-%:%129=57%:%
-%:%130=57%:%
-%:%132=58%:%
-%:%133=59%:%
+%:%121=55%:%
+%:%124=57%:%
+%:%126=59%:%
+%:%127=59%:%
+%:%130=60%:%
 %:%134=60%:%
@@
 %:%139=63%:%
-%:%140=63%:%
-%:%207=109%:%
-%:%219=111%:%
-%:%220=112%:%
-%:%221=113%:%
-%:%222=114%:%
-%:%224=116%:%
-%:%225=116%:%
-%:%226=117%:%
-%:%227=117%:%
-%:%239=125%:%
-%:%242=126%:%
-%:%243=126%:%
-%:%245=127%:%
-%:%246=128%:%
-%:%247=129%:%
-%:%248=130%:%
-%:%249=130%:%
-%:%250=131%:%
-%:%251=132%:%
-%:%252=132%:%
-%:%253=133%:%
-%:%256=134%:%
-%:%260=134%:%
-%:%261=134%:%
-%:%263=135%:%
-%:%264=136%:%
-%:%274=138%:%
-%:%275=139%:%
-%:%276=140%:%
-%:%280=142%:%
-%:%282=144%:%
-%:%283=144%:%
-%:%284=145%:%
-%:%285=145%:%
-%:%286=146%:%
-%:%287=146%:%
-%:%289=147%:%
-%:%290=147%:%
-%:%291=148%:%
-%:%292=149%:%
-%:%293=149%:%
-%:%295=151%:%
-%:%296=152%:%
-%:%297=153%:%
-%:%298=154%:%
-%:%300=156%:%
-%:%301=156%:%
-%:%302=157%:%
-%:%303=158%:%
-%:%304=159%:%
-%:%305=159%:%
-%:%308=160%:%
-%:%312=160%:%
-%:%313=160%:%
-%:%315=161%:%
-%:%316=162%:%
-%:%317=163%:%
-%:%318=164%:%
-%:%319=164%:%
-%:%321=165%:%
-%:%322=166%:%
-%:%323=167%:%
-%:%324=168%:%
-%:%325=169%:%
-%:%326=169%:%
-%:%328=170%:%
-%:%329=171%:%
-%:%339=173%:%
-%:%340=174%:%
-%:%341=175%:%
-%:%342=176%:%
-%:%343=177%:%
-%:%344=178%:%
-%:%345=179%:%
-%:%346=180%:%
-%:%348=182%:%
-%:%349=182%:%
-%:%350=183%:%
-%:%351=184%:%
-%:%352=185%:%
-%:%353=185%:%
-%:%355=185%:%
-%:%359=185%:%
-%:%360=185%:%
-%:%362=186%:%
-%:%363=187%:%
-%:%364=188%:%
-%:%365=189%:%
-%:%366=190%:%
-%:%367=191%:%
-%:%377=193%:%
-%:%378=194%:%
-%:%379=195%:%
-%:%380=196%:%
-%:%381=197%:%
-%:%382=198%:%
-%:%391=200%:%
-%:%403=202%:%
-%:%404=203%:%
-%:%405=204%:%
-%:%406=205%:%
-%:%407=206%:%
-%:%408=207%:%
-%:%409=208%:%
-%:%410=209%:%
-%:%411=210%:%
-%:%412=211%:%
-%:%413=212%:%
-%:%414=213%:%
-%:%416=214%:%
-%:%417=214%:%
-%:%418=215%:%
-%:%419=216%:%
-%:%420=216%:%
-%:%422=216%:%
-%:%426=216%:%
-%:%427=216%:%
-%:%429=217%:%
-%:%430=218%:%
-%:%431=219%:%
-%:%432=220%:%
-%:%433=220%:%
-%:%435=221%:%
-%:%436=222%:%
-%:%437=223%:%
-%:%438=223%:%
-%:%440=224%:%
-%:%441=225%:%
-%:%449=225%:%
-%:%450=226%:%
-%:%451=227%:%
-%:%452=227%:%
-%:%453=228%:%
-%:%454=229%:%
-%:%455=230%:%
-%:%456=230%:%
-%:%458=230%:%
-%:%462=230%:%
-%:%463=230%:%
-%:%465=231%:%
-%:%466=232%:%
-%:%467=233%:%
-%:%468=234%:%
-%:%469=234%:%
-%:%471=235%:%
-%:%472=236%:%
-%:%473=237%:%
-%:%483=239%:%
-%:%484=240%:%
-%:%486=242%:%
-%:%487=242%:%
-%:%488=243%:%
-%:%489=244%:%
-%:%490=245%:%
-%:%491=245%:%
-%:%493=245%:%
-%:%497=245%:%
-%:%498=245%:%
-%:%500=246%:%
-%:%501=247%:%
-%:%502=248%:%
-%:%503=249%:%
-%:%504=249%:%
-%:%506=250%:%
-%:%516=252%:%
-%:%520=254%:%
-%:%521=255%:%
-%:%522=256%:%
-%:%523=257%:%
-%:%525=259%:%
-%:%526=259%:%
-%:%527=260%:%
-%:%528=261%:%
-%:%529=262%:%
-%:%530=262%:%
-%:%532=262%:%
-%:%536=262%:%
-%:%537=262%:%
-%:%539=263%:%
-%:%540=264%:%
-%:%541=265%:%
-%:%542=266%:%
-%:%543=266%:%
-%:%545=267%:%
-%:%555=269%:%
-%:%556=270%:%
-%:%557=271%:%
-%:%559=273%:%
-%:%560=273%:%
-%:%561=274%:%
-%:%562=275%:%
-%:%563=276%:%
-%:%564=276%:%
-%:%566=276%:%
-%:%570=276%:%
-%:%571=276%:%
-%:%573=277%:%
-%:%574=278%:%
-%:%575=279%:%
-%:%576=279%:%
-%:%578=280%:%
-%:%588=282%:%
-%:%589=283%:%
-%:%590=284%:%
-%:%592=286%:%
-%:%593=286%:%
-%:%594=287%:%
-%:%595=288%:%
-%:%596=289%:%
-%:%597=290%:%
-%:%598=291%:%
-%:%599=291%:%
-%:%606=292%:%
-%:%607=292%:%
-%:%608=293%:%
-%:%609=293%:%
-%:%610=294%:%
-%:%611=294%:%
-%:%612=295%:%
-%:%613=295%:%
-%:%614=295%:%
-%:%615=295%:%
-%:%617=296%:%
-%:%618=297%:%
-%:%619=297%:%
-%:%620=298%:%
-%:%621=298%:%
-%:%622=298%:%
-%:%624=299%:%
-%:%625=300%:%
-%:%626=301%:%
-%:%627=302%:%
-%:%628=303%:%
-%:%629=303%:%
-%:%631=304%:%
-%:%641=306%:%
-%:%642=307%:%
-%:%643=308%:%
-%:%644=309%:%
-%:%645=310%:%
-%:%647=312%:%
-%:%648=312%:%
-%:%649=313%:%
-%:%650=314%:%
-%:%651=315%:%
-%:%652=315%:%
-%:%654=315%:%
-%:%658=315%:%
-%:%659=315%:%
-%:%661=316%:%
-%:%662=317%:%
-%:%663=318%:%
-%:%664=319%:%
-%:%665=320%:%
-%:%675=322%:%
-%:%676=323%:%
-%:%680=325%:%
-%:%684=327%:%
-%:%685=328%:%
-%:%686=329%:%
-%:%688=331%:%
-%:%689=331%:%
-%:%690=332%:%
-%:%693=333%:%
-%:%697=333%:%
-%:%698=333%:%
-%:%700=334%:%
-%:%701=334%:%
-%:%703=335%:%
-%:%704=336%:%
-%:%705=337%:%
-%:%706=338%:%
-%:%707=339%:%
-%:%717=341%:%
-%:%718=342%:%
-%:%719=343%:%
-%:%720=344%:%
-%:%722=346%:%
-%:%723=346%:%
-%:%724=347%:%
-%:%727=348%:%
-%:%731=348%:%
-%:%732=348%:%
-%:%733=348%:%
-%:%735=349%:%
-%:%736=349%:%
+%:%149=65%:%
+%:%150=66%:%
+%:%151=67%:%
+%:%152=68%:%
+%:%153=69%:%
+%:%154=70%:%
+%:%155=71%:%
+%:%156=72%:%
+%:%157=73%:%
+%:%158=74%:%
+%:%159=75%:%
+%:%160=76%:%
+%:%161=77%:%
+%:%162=78%:%
+%:%163=79%:%
+%:%164=80%:%
+%:%165=81%:%
+%:%166=82%:%
+%:%167=83%:%
+%:%168=84%:%
+%:%170=86%:%
+%:%171=86%:%
+%:%172=87%:%
+%:%174=89%:%
+%:%175=90%:%
+%:%176=91%:%
+%:%177=92%:%
+%:%178=93%:%
+%:%179=94%:%
+%:%180=95%:%
+%:%181=96%:%
+%:%182=97%:%
+%:%183=98%:%
+%:%184=99%:%
+%:%185=100%:%
+%:%186=101%:%
+%:%195=103%:%
+%:%207=105%:%
+%:%208=106%:%
+%:%209=107%:%
+%:%210=108%:%
+%:%211=109%:%
+%:%215=111%:%
+%:%219=113%:%
+%:%220=114%:%
+%:%221=115%:%
+%:%222=116%:%
+%:%224=119%:%
+%:%225=119%:%
+%:%226=119%:%
+%:%228=119%:%
+%:%232=119%:%
+%:%233=119%:%
+%:%235=120%:%
+%:%236=121%:%
+%:%237=122%:%
+%:%238=122%:%
+%:%240=123%:%
+%:%241=124%:%
+%:%242=125%:%
+%:%243=125%:%
+%:%244=126%:%
+%:%306=173%:%
+%:%307=174%:%
+%:%308=175%:%
+%:%309=176%:%
+%:%310=177%:%
+%:%311=178%:%
+%:%312=179%:%
+%:%314=181%:%
+%:%315=181%:%
+%:%316=182%:%
+%:%317=183%:%
+%:%318=183%:%
+%:%320=183%:%
+%:%324=183%:%
+%:%325=183%:%
+%:%327=184%:%
+%:%328=185%:%
+%:%329=186%:%
+%:%330=187%:%
+%:%331=187%:%
+%:%333=188%:%
+%:%334=189%:%
+%:%335=190%:%
+%:%345=192%:%
+%:%346=193%:%
+%:%347=194%:%
+%:%348=195%:%
+%:%350=197%:%
+%:%351=197%:%
+%:%352=198%:%
+%:%353=199%:%
+%:%354=200%:%
+%:%355=200%:%
+%:%357=200%:%
+%:%361=200%:%
+%:%362=200%:%
+%:%364=201%:%
+%:%365=202%:%
+%:%366=203%:%
+%:%367=204%:%
+%:%368=204%:%
+%:%370=205%:%
+%:%380=207%:%
+%:%381=208%:%
+%:%382=209%:%
+%:%384=211%:%
+%:%385=211%:%
+%:%386=212%:%
+%:%387=213%:%
+%:%388=214%:%
+%:%389=214%:%
+%:%391=214%:%
+%:%395=214%:%
+%:%396=214%:%
+%:%398=215%:%
+%:%399=216%:%
+%:%400=217%:%
+%:%401=218%:%
+%:%402=218%:%
+%:%404=219%:%
+%:%405=220%:%
+%:%415=222%:%
+%:%419=224%:%
+%:%420=225%:%
+%:%421=226%:%
+%:%422=227%:%
+%:%423=228%:%
+%:%425=230%:%
+%:%426=230%:%
+%:%427=231%:%
+%:%428=232%:%
+%:%429=233%:%
+%:%430=233%:%
+%:%432=233%:%
+%:%436=233%:%
+%:%437=233%:%
+%:%439=234%:%
+%:%440=235%:%
+%:%441=236%:%
+%:%442=237%:%
+%:%443=237%:%
+%:%445=238%:%
+%:%446=238%:%
+%:%469=253%:%
+%:%470=254%:%
+%:%471=255%:%
+%:%472=256%:%
+%:%474=258%:%
+%:%475=258%:%
+%:%476=259%:%
+%:%477=260%:%
+%:%478=261%:%
+%:%479=262%:%
+%:%480=263%:%
+%:%481=263%:%
+%:%488=264%:%
+%:%489=264%:%
+%:%490=265%:%
+%:%491=265%:%
+%:%492=266%:%
+%:%493=266%:%
+%:%494=267%:%
+%:%495=267%:%
+%:%496=267%:%
+%:%497=267%:%
+%:%499=268%:%
+%:%500=269%:%
+%:%501=269%:%
+%:%502=270%:%
+%:%503=270%:%
+%:%504=270%:%
+%:%506=271%:%
+%:%507=272%:%
+%:%508=273%:%
+%:%509=274%:%
+%:%510=275%:%
+%:%511=275%:%
+%:%513=276%:%
+%:%523=278%:%
+%:%524=279%:%
+%:%525=280%:%
+%:%526=281%:%
+%:%527=282%:%
+%:%529=284%:%
+%:%530=284%:%
+%:%531=285%:%
+%:%532=286%:%
+%:%533=287%:%
+%:%534=287%:%
+%:%536=287%:%
+%:%540=287%:%
+%:%541=287%:%
+%:%543=288%:%
+%:%544=289%:%
+%:%545=290%:%
+%:%546=291%:%
+%:%547=292%:%
+%:%548=293%:%
+%:%558=295%:%
+%:%562=297%:%
+%:%563=298%:%
+%:%564=299%:%
+%:%566=301%:%
+%:%567=301%:%
+%:%568=302%:%
+%:%571=303%:%
+%:%575=303%:%
+%:%576=303%:%
+%:%578=304%:%
+%:%579=304%:%
+%:%581=305%:%
+%:%582=306%:%
+%:%583=307%:%
+%:%584=308%:%
+%:%585=309%:%
+%:%595=311%:%
+%:%596=312%:%
+%:%597=313%:%
+%:%599=315%:%
+%:%600=315%:%
+%:%601=316%:%
+%:%604=317%:%
+%:%608=317%:%
+%:%609=317%:%
+%:%610=317%:%
+%:%651=337%:%
+%:%663=339%:%
+%:%664=340%:%
+%:%665=341%:%
+%:%666=342%:%
+%:%668=344%:%
+%:%669=344%:%
+%:%670=345%:%
+%:%671=345%:%
+%:%683=353%:%
+%:%686=354%:%
+%:%687=354%:%
+%:%689=355%:%
+%:%690=356%:%
+%:%691=357%:%
+%:%692=358%:%
+%:%693=358%:%
+%:%694=359%:%
+%:%695=360%:%
+%:%696=360%:%
+%:%697=361%:%
+%:%700=362%:%
+%:%704=362%:%
+%:%705=362%:%
+%:%707=363%:%
+%:%708=364%:%
+%:%718=366%:%
+%:%719=367%:%
+%:%720=368%:%
+%:%724=370%:%
+%:%726=372%:%
+%:%727=372%:%
+%:%728=373%:%
+%:%729=373%:%
+%:%730=374%:%
+%:%731=374%:%
+%:%733=375%:%
+%:%734=375%:%
+%:%735=376%:%
+%:%736=377%:%
+%:%737=377%:%
+%:%739=379%:%
+%:%740=380%:%
+%:%741=381%:%
+%:%742=382%:%
+%:%744=384%:%
+%:%745=384%:%
+%:%746=385%:%
+%:%747=386%:%
+%:%748=387%:%
+%:%749=387%:%
+%:%752=388%:%
+%:%756=388%:%
+%:%757=388%:%
+%:%759=389%:%
+%:%760=390%:%
+%:%761=391%:%
+%:%762=392%:%
+%:%763=392%:%
+%:%765=393%:%
+%:%766=394%:%
+%:%767=395%:%
+%:%768=396%:%
+%:%769=397%:%
+%:%770=397%:%
+%:%772=398%:%
+%:%773=399%:%
+%:%783=401%:%
+%:%784=402%:%
+%:%785=403%:%
+%:%786=404%:%
+%:%787=405%:%
+%:%788=406%:%
+%:%789=407%:%
+%:%790=408%:%
+%:%792=410%:%
+%:%793=410%:%
+%:%794=411%:%
+%:%795=412%:%
+%:%796=413%:%
+%:%797=413%:%
+%:%799=413%:%
+%:%803=413%:%
+%:%804=413%:%
+%:%806=414%:%
+%:%807=415%:%
+%:%808=416%:%
+%:%809=417%:%
+%:%810=418%:%
+%:%811=419%:%
+%:%821=421%:%
+%:%822=422%:%
+%:%823=423%:%
+%:%824=424%:%
+%:%825=425%:%
+%:%826=426%:%
+%:%834=430%:%
+%:%842=430%:%

### 2021-11-07 paper/output/document/paper33.tex
cleaned much of naive

@@
 %
-\isamarkupsubsubsection{Goals From Prior Attempts%
+\isamarkupsubsubsection{Goals From Prior Attempts \label{sec:priorgoals}%
 }
@@
 to the fact that, as opposed to a subjective principle, the categorical imperative applies to all 
-rational agents equally $\cite[16]{groundwork}$. At its core, the FUL best handles, ``the temptation 
+rational agents equally \cite[16]{groundwork}. At its core, the FUL best handles, ``the temptation 
 to make oneself an exception: selfishness, meanness, advantagetaking, and disregard for the rights 
@@
 interpret the universalizability test in different ways. Korsgaard argues for the practical contradiction 
-interpretation, broadly accepted as correct within the philosophical community $\cite[177]{ebelsduggan}$.
+interpretation, broadly accepted as correct within the philosophical community \cite[177]{ebelsduggan}.
 Because her argument is broadly accepted, I will make it a goal to represent the practical contradiction
@@
 Recall that the formula of universal law is “act only in accordance with that maxim through which you can at the 
-same time will that it become a universal law” $\cite[4:421]{groundwork}$. To determine if a maxim can be willed as a 
+same time will that it become a universal law” \cite[4:421]{groundwork}. To determine if a maxim can be willed as a 
 universal law, one must use the “universalizability test,” which requires imagining a world in which 

### 2021-11-07 paper/output/document/paper41.tex
cleaned much of naive

@@
 in a footnote in \emph{Groundwork} as ``the subjective principle of willing," or the principle that 
-the agent acts on $\cite[16]{groundwork}$. Modern Kantians differ in their interpretations of this definition. The naive view 
+the agent acts on \cite[16]{groundwork}. Modern Kantians differ in their interpretations of this definition. The naive view 
 is that a maxim is an act, but Korsgaard adopts the more sophisticated view that a maxim is composed
@@
 
-O'Neill $\cite[37]{actingonprinciple}$ presents what Kitcher \cite{whatisamaxim}  calls the widely accepted 
+O'Neill \cite[37]{actingonprinciple} presents what Kitcher \cite{whatisamaxim}  calls the widely accepted 
 view that a maxim is a circumstance, act, goal tuple. A maxim 
@@
 example maxims and because Kant argues that human activity, because it is guided by a rational will, 
-is inherently purposive $\cite[4:428]{groundwork}$. A rational will does not act randomly (else it would not be rational), 
+is inherently purposive \cite[4:428]{groundwork}. A rational will does not act randomly (else it would not be rational), 
 but instead in the pursuit of ends which it deems valuable. This inclusion is also essential for the version of the universalizability test 
@@
 O'Neill's inclusion of circumstances is potentially controversial because it leaves open the question of what qualifies as a 
-relevant circumstance for a particular maxim. This is gives rise to ``the tailoring objection" $\cite[217]{whatisamaxim} \footnote{Kitcher
-cites \cite{kantsethicalthought}  as offering an example of a false positive due to this objection.}$, 
+relevant circumstance for a particular maxim. This is gives rise to ``the tailoring objection" \cite[217]{whatisamaxim} \footnote{Kitcher
+cites \cite{kantsethicalthought}  as offering an example of a false positive due to this objection.}, 
 under which maxims are arbitrarily specified to pass the FUL. For example, the maxim ``When my name is Lavanya Singh,
@@
 O'Neill seems to acknowledge the difficulty of determining relevant circumstances when she concedes that a maxim cannot include all 
-of the infinitely many circumstances in which the agent may perform the action$\cite[4:428]{actingonprinciple}$. She argues that this is 
+of the infinitely many circumstances in which the agent may perform the action\cite[4:428]{actingonprinciple}. She argues that this is 
 an artifact of the fact that maxims are rules of practical reason, the kind of reason that helps us decide what to do 
@@
 between the evaluation of a principle, which is generic, and a maxim, which she views as ``individuated only 
-by referring to a person"$\cite[13]{actingonprinciple}$. I adopt the spirit of this interpretation but modify it slightly 
+by referring to a person"\cite[13]{actingonprinciple}. I adopt the spirit of this interpretation but modify it slightly 
 by representing the general maxim as a principle that anyone could adopt, and the act of willing the maxim 

### 2021-11-07 paper/output/document/threeflags.tex
cleaned much of naive

@@
 ``If I want to get good grades, I must study hard." Hypothetical imperatives only have force so long
-as the antecedent holds, but the categorical imperative is unconditionally binding $\cite[28]{groundwork}$. In the first 
+as the antecedent holds, but the categorical imperative is unconditionally binding \cite[28]{groundwork}. In the first 
 half of \emph{Groundwork}, Kant examines what the categorical imperative, if such a thing exists and has force,
@@
 formula of universal law (FUL), which reads, ``act only according to that maxim through which you can 
-at the same time will that it become a universal law." $\cite[34]{groundwork}$ This formulation
+at the same time will that it become a universal law." \cite[34]{groundwork} This formulation
 generates the universalizability test, which ``tests" the moral value of a maxim by 
@@
 in your own person, as well as in the person of any other, always at the same time as an end, never merely 
-as a means." $\cite[41]{groundwork}$. This formulation is often understood as requiring us to 
+as a means." \cite[41]{groundwork}. This formulation is often understood as requiring us to 
 acknowledge and respect the dignity of every other person. The third formulation of the categorical 
@@
 as, ``we should so act that we may think of ourselves as legislating universal laws through our 
-maxims." $\cite[28]{korsgaardintro}$ While closely related to the FUL, the FOA presents morality as the activity of 
+maxims" \cite[28]{korsgaardintro}. While closely related to the FUL, the FOA presents morality as the activity of 
 perfectly rational agents in an ideal ``kingdom of ends," guided by what Kant calls the ``laws of freedom."
@@
 Onora O'Neill explains that the formalism of the FUL allows 
-for greater precision in philosophical arguments analyzing its implications and power $\cite[33]{actingonprinciple}$. This precision 
+for greater precision in philosophical arguments analyzing its implications and power \cite[33]{actingonprinciple}. This precision 
 is particularly useful in a computational context because any formalism necessarily makes its content 
@@
 
-While some criticize the FUL for its formalism and percieved ``sterility" $\cite[33]{actingonprinciple}$, 
-Kantian constructivists embrace it $\cite[173]{ebelsduggan}$. My project is not committed to Kantian constructivism. 
+While some criticize the FUL for its formalism and percieved ``sterility" \cite[33]{actingonprinciple}, 
+Kantian constructivists embrace it \cite[173]{ebelsduggan}. My project is not committed to Kantian constructivism. 
 I believe that computational ethics is likely a valuable tool for any ethicist, and I make the case 
@@
 in a footnote in \emph{Groundworkd} as ``the subjective principle of willing," or the principle that 
-the agent acts on $\cite[16]{groundwork}$. Modern Kantians differ in their interpretations of this definition. The naive view 
+the agent acts on \cite[16]{groundwork}. Modern Kantians differ in their interpretations of this definition. The naive view 
 is that a maxim is an act, but Korsgaard adopts the more sophisticated view that a maxim is composed
@@
 \begin{isamarkuptext}%
-O'Neill $\cite[37]{actingonprinciple}$ presents what Kitcher \cite{whatisamaxim}  calls the widely accepted 
+O'Neill \cite[37]{actingonprinciple} presents what Kitcher \cite{whatisamaxim}  calls the widely accepted 
 view that a maxim is a circumstance, act, goal tuple. A maxim 
@@
 interpret the universalizability test in different ways. My project uses Korsgaard's practical contradiction 
-interpretation, broadly accepted as correct within the philosophical community $\cite[177]{ebelsduggan}$.
+interpretation, broadly accepted as correct within the philosophical community \cite[177]{ebelsduggan}.
 Below, I briefly reconstruct Korsgaard's argument for the practical contradiction interpretation. While 

### 2021-11-07 paper/output/document/upshot.tex
cleaned much of naive

@@
 change an agent's behavior nor generate meaningful obligations, they are not the right kinds of questions 
-for practical reasoners to be asking. They cannot be action-guiding and are thus not the domain of ethics.
-Moreover, under the Kantian account of the will, the very act of asking if a vacuous maxim is prohibited 
-generates a contradiction by undermining the will's authority over itself.
+for practical reasoners to be asking. They cannot be action-guiding and are thus not the kind of problem that 
+ethics should be concerned with. Moreover, under the Kantian account of the will, the very act of asking 
+if a vacuous maxim is prohibited generates a contradiction by undermining the will's authority over itself.
 
@@
 Because vacuous maxims can't prescribe or alter action, they are not practically action-guiding and 
-thus are not the right kinds of maxims for practical reasoners to evaluate. Moreover, if ethics 
-is supposed to guide action, then vacuous maxims cannot be the domain of ethics. Practical reason
+thus are not the right kinds of maxims for practical reasoners to evaluate. Moreover, insofar as ethics 
+is supposed to guide action, vacuous maxims cannot be part of this project. Vacuous maxims
+will have no bearing on what someone should do. Practical reason
 is the kind of reason that helps us decide what we should do. 
@@
  maxim can never be action-guiding because it prescribes no new
-actions or obligations. It is not the kind of maxim that a practical reasoner would consider. 
+actions or obligations. It is not the kind of maxim that a practical reasoner should consider, because it
+will have no bearing on what the agent should do. 
 There is no explicit prohibition against a vacuous maxim like the breakfast example above, but it 
-is the wrong kind of question for a practical reasoner to ask. On ordinary person trying 
-to navigate the world would never ask that kind of question. If ethics is meant 
+is the wrong kind of question for a practical reasoner to ask. An ordinary person trying 
+to navigate the world would never need to ask that kind of question. If ethics is meant 
 to guide action, then badly formed maxims are not questions for ethics, because they could never guide 
@@
 
-Above I argued that vacuous maxims are not the kind of principle that a practical reasoner would ever
-ask, and are thus not the right kind of question for ethics. Kantians can make an even stronger claim
+Above I argued that vacuous maxims are not the kind of principle that a practical reasoner should 
+evaluate, and are thus not the right kind of question for ethics. Kantians can make an even stronger claim
 about vacuous maxims—because maxims are laws that you give to yourself, asking if you should will 
@@
 %:%465=386%:%
-%:%474=390%:%
-%:%486=392%:%
-%:%487=393%:%
+%:%466=387%:%
+%:%467=388%:%
+%:%476=392%:%
 %:%488=394%:%
@@
 %:%531=437%:%
-%:%540=440%:%
-%:%552=443%:%
-%:%553=444%:%
+%:%532=438%:%
+%:%533=439%:%
+%:%542=442%:%
 %:%554=445%:%
@@
 %:%572=463%:%
+%:%573=464%:%
+%:%574=465%:%

### 2021-11-07 paper/output/document/whykant.tex
cleaned much of naive

@@
 %
-\isamarkupsection{Why Kantian Ethics%
+\isamarkupsubsection{Why Kantian Ethics%
 }
@@
 %
-\isamarkupsubsection{Kantian Ethics%
-}
-\isamarkuptrue%
-%
-\isamarkupsubsubsection{Crash Course on Kantian Ethics%
+\isamarkupsubsubsection{Kantian Ethics%
 }
@@
 \endisadelimdocument
+%
+\begin{isamarkuptext}%
+\textbf{Crash Course on Kantian Ethics}%
+\end{isamarkuptext}\isamarkuptrue%
 %
@@
 Formula of Universal Law (FUL), which reads, ``act only according to that maxim through which you can 
-at the same time will that it become a universal law" $\cite[34]{groundwork}$. This formulation
+at the same time will that it become a universal law" \cite[34]{groundwork}. This formulation
 generates the universalizability test, which tests the moral value of a maxim by 
@@
 as, ``we should so act that we may think of ourselves as legislating universal laws through our 
-maxims" $\cite[28]{korsgaardintro}$. While closely related to the FUL, the FOA presents morality as the activity of 
+maxims" \cite[28]{korsgaardintro}. While closely related to the FUL, the FOA presents morality as the activity of 
 perfectly rational agents in an ideal ``kingdom of ends," guided by what Kant calls the ``laws of freedom."
@@
 %
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\isatagdocument
-%
-\isamarkupsubsubsection{Ease of Automation%
-}
-\isamarkuptrue%
-%
-\endisatagdocument
-{\isafolddocument}%
-%
-\isadelimdocument
-%
-\endisadelimdocument
+\begin{isamarkuptext}%
+\textbf{Ease of Automation}%
+\end{isamarkuptext}\isamarkuptrue%
 %
@@
 %
-\isamarkupsubsection{Consequentialism%
+\isamarkupsubsubsection{Consequentialism%
 }
@@
 %
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\isatagdocument
-%
-\isamarkupsubsubsection{Which Consequences Matter%
-}
-\isamarkuptrue%
-%
-\endisatagdocument
-{\isafolddocument}%
-%
-\isadelimdocument
-%
-\endisadelimdocument
+\begin{isamarkuptext}%
+\textbf{Which Consequences Matter}%
+\end{isamarkuptext}\isamarkuptrue%
 %
@@
 \cite{powers} identifies this as a challenge for automating Kantian ethics and briefly sketches 
-solutions from O'Neill \cite{constofreason}, Silber \cite{silber}, and Rawls \cite{rawlsconstructivism}. } Those 
+solutions from O'Neill \citet{constofreason}, Silber \citet{silber}, and Rawls \citet{rawlsconstructivism}. } Those 
 using my system will need to automatically or manually formulate maxims, a process that involves 
@@
 %
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\isatagdocument
-%
-\isamarkupsubsubsection{Theory of the Good%
-}
-\isamarkuptrue%
-%
-\endisatagdocument
-{\isafolddocument}%
-%
-\isadelimdocument
-%
-\endisadelimdocument
+\begin{isamarkuptext}%
+\textbf{Theory of the Good}%
+\end{isamarkuptext}\isamarkuptrue%
 %
@@
 %
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\isatagdocument
-%
-\isamarkupsubsubsection{Aggregation%
-}
-\isamarkuptrue%
-%
-\endisatagdocument
-{\isafolddocument}%
-%
-\isadelimdocument
-%
-\endisadelimdocument
+\begin{isamarkuptext}%
+\textbf{Aggregation}%
+\end{isamarkuptext}\isamarkuptrue%
 %
@@
 %
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\isatagdocument
-%
-\isamarkupsubsubsection{Prior Attempts to Formalize Consequentialism%
-}
-\isamarkuptrue%
-%
-\endisatagdocument
-{\isafolddocument}%
-%
-\isadelimdocument
-%
-\endisadelimdocument
+\begin{isamarkuptext}%
+\textbf{Prior Attempts to Formalize Consequentialism}%
+\end{isamarkuptext}\isamarkuptrue%
 %
@@
 %
-\isamarkupsubsection{Virtue Ethics%
-}
-\isamarkuptrue%
-%
-\isamarkupsubsubsection{What Is Virtue%
+\isamarkupsubsubsection{Virtue Ethics%
 }
@@
 \endisadelimdocument
+%
+\begin{isamarkuptext}%
+\textbf{What Is Virtue}%
+\end{isamarkuptext}\isamarkuptrue%
 %
@@
 %
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\isatagdocument
-%
-\isamarkupsubsubsection{Evaluating Moral Character%
-}
-\isamarkuptrue%
-%
-\endisatagdocument
-{\isafolddocument}%
-%
-\isadelimdocument
-%
-\endisadelimdocument
+\begin{isamarkuptext}%
+\textbf{Evaluating Moral Character}%
+\end{isamarkuptext}\isamarkuptrue%
 %
@@
 %
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\isatagdocument
-%
-\isamarkupsubsubsection{Machine Learning and Virtue Ethics%
-}
-\isamarkuptrue%
-%
-\endisatagdocument
-{\isafolddocument}%
-%
-\isadelimdocument
-%
-\endisadelimdocument
+\begin{isamarkuptext}%
+\textbf{Machine Learning and Virtue Ethics}%
+\end{isamarkuptext}\isamarkuptrue%
 %
@@
 %:%62=29%:%
-%:%66=31%:%
+%:%74=31%:%
 %:%78=33%:%
@@
 %:%154=109%:%
-%:%163=111%:%
-%:%175=113%:%
-%:%176=114%:%
-%:%177=115%:%
-%:%178=116%:%
-%:%179=117%:%
-%:%180=118%:%
-%:%181=119%:%
-%:%182=120%:%
-%:%183=121%:%
-%:%184=122%:%
-%:%185=123%:%
-%:%186=124%:%
-%:%187=125%:%
-%:%188=126%:%
-%:%189=127%:%
-%:%190=128%:%
-%:%191=129%:%
-%:%192=130%:%
-%:%193=131%:%
-%:%194=132%:%
-%:%195=133%:%
-%:%196=134%:%
-%:%197=135%:%
-%:%198=136%:%
-%:%199=137%:%
-%:%200=138%:%
-%:%201=139%:%
-%:%202=140%:%
-%:%203=141%:%
-%:%204=142%:%
-%:%205=143%:%
-%:%206=144%:%
-%:%207=145%:%
-%:%216=148%:%
-%:%228=150%:%
-%:%229=151%:%
-%:%230=152%:%
-%:%231=153%:%
-%:%232=154%:%
-%:%233=155%:%
-%:%234=156%:%
-%:%235=157%:%
-%:%236=158%:%
-%:%245=160%:%
-%:%257=162%:%
-%:%258=163%:%
-%:%259=164%:%
-%:%260=165%:%
-%:%261=166%:%
-%:%262=167%:%
-%:%263=168%:%
-%:%264=169%:%
-%:%265=170%:%
-%:%266=171%:%
-%:%267=172%:%
-%:%268=173%:%
-%:%269=174%:%
-%:%270=175%:%
-%:%271=176%:%
-%:%272=177%:%
-%:%273=178%:%
-%:%274=179%:%
-%:%275=180%:%
-%:%276=181%:%
-%:%277=182%:%
-%:%278=183%:%
-%:%279=184%:%
-%:%280=185%:%
-%:%281=186%:%
-%:%282=187%:%
-%:%283=188%:%
-%:%284=189%:%
-%:%285=190%:%
-%:%286=191%:%
-%:%287=192%:%
-%:%288=193%:%
-%:%289=194%:%
-%:%290=195%:%
-%:%291=196%:%
-%:%292=197%:%
-%:%293=198%:%
-%:%294=199%:%
-%:%295=200%:%
-%:%296=201%:%
-%:%297=202%:%
-%:%298=203%:%
-%:%299=204%:%
-%:%300=205%:%
-%:%301=206%:%
-%:%302=207%:%
-%:%303=208%:%
-%:%304=209%:%
-%:%305=210%:%
-%:%306=211%:%
-%:%307=212%:%
-%:%308=213%:%
-%:%309=214%:%
-%:%310=215%:%
-%:%311=216%:%
-%:%312=217%:%
-%:%321=220%:%
-%:%333=222%:%
-%:%334=223%:%
-%:%335=224%:%
-%:%336=225%:%
-%:%337=226%:%
-%:%338=227%:%
-%:%339=228%:%
-%:%340=229%:%
-%:%341=230%:%
-%:%342=231%:%
-%:%343=232%:%
-%:%344=233%:%
-%:%345=234%:%
-%:%346=235%:%
-%:%347=236%:%
-%:%348=237%:%
-%:%349=238%:%
-%:%350=239%:%
-%:%351=240%:%
-%:%352=241%:%
-%:%353=242%:%
-%:%354=243%:%
-%:%355=244%:%
-%:%356=245%:%
-%:%357=246%:%
-%:%366=248%:%
-%:%378=250%:%
-%:%379=251%:%
-%:%380=252%:%
-%:%381=253%:%
-%:%382=254%:%
-%:%383=255%:%
-%:%384=256%:%
-%:%385=257%:%
-%:%386=258%:%
-%:%387=259%:%
-%:%388=260%:%
-%:%389=261%:%
-%:%390=262%:%
-%:%391=263%:%
-%:%392=264%:%
-%:%393=265%:%
-%:%394=266%:%
-%:%395=267%:%
-%:%396=268%:%
-%:%397=269%:%
-%:%398=270%:%
-%:%399=271%:%
-%:%400=272%:%
-%:%401=273%:%
-%:%402=274%:%
-%:%411=277%:%
-%:%423=279%:%
-%:%424=280%:%
-%:%425=281%:%
-%:%426=282%:%
-%:%427=283%:%
-%:%428=284%:%
-%:%429=285%:%
-%:%430=286%:%
-%:%431=287%:%
-%:%432=288%:%
-%:%433=289%:%
-%:%434=290%:%
-%:%435=291%:%
-%:%436=292%:%
-%:%437=293%:%
-%:%438=294%:%
-%:%439=295%:%
-%:%440=296%:%
-%:%441=297%:%
-%:%442=298%:%
-%:%443=299%:%
-%:%452=302%:%
-%:%456=304%:%
-%:%468=306%:%
-%:%469=307%:%
-%:%470=308%:%
-%:%471=309%:%
-%:%472=310%:%
-%:%473=311%:%
-%:%474=312%:%
-%:%475=313%:%
-%:%476=314%:%
-%:%477=315%:%
-%:%478=316%:%
-%:%479=317%:%
-%:%480=318%:%
-%:%481=319%:%
-%:%482=320%:%
-%:%491=322%:%
-%:%503=324%:%
-%:%504=325%:%
-%:%505=326%:%
-%:%506=327%:%
-%:%507=328%:%
-%:%508=329%:%
-%:%509=330%:%
-%:%510=331%:%
-%:%511=332%:%
-%:%512=333%:%
-%:%521=335%:%
-%:%533=337%:%
-%:%534=338%:%
-%:%535=339%:%
-%:%536=340%:%
-%:%537=341%:%
-%:%538=342%:%
-%:%539=343%:%
-%:%540=344%:%
-%:%541=345%:%
-%:%542=346%:%
-%:%543=347%:%
-%:%544=348%:%
-%:%545=349%:%
-%:%546=350%:%
-%:%547=351%:%
-%:%548=352%:%
-%:%549=353%:%
-%:%550=354%:%
-%:%551=355%:%
-%:%552=356%:%
-%:%553=357%:%
-%:%554=358%:%
-%:%555=359%:%
-%:%556=360%:%
-%:%557=361%:%
-%:%558=362%:%
-%:%559=363%:%
-%:%560=364%:%
-%:%561=365%:%
-%:%562=366%:%
-%:%563=367%:%
-%:%564=368%:%
-%:%565=369%:%
-%:%566=370%:%
-%:%567=371%:%
-%:%568=372%:%
-%:%569=373%:%
-%:%570=374%:%
-%:%571=375%:%
+%:%158=111%:%
+%:%162=113%:%
+%:%163=114%:%
+%:%164=115%:%
+%:%165=116%:%
+%:%166=117%:%
+%:%167=118%:%
+%:%168=119%:%
+%:%169=120%:%
+%:%170=121%:%
+%:%171=122%:%
+%:%172=123%:%
+%:%173=124%:%
+%:%174=125%:%
+%:%175=126%:%
+%:%176=127%:%
+%:%177=128%:%
+%:%178=129%:%
+%:%179=130%:%
+%:%180=131%:%
+%:%181=132%:%
+%:%182=133%:%
+%:%183=134%:%
+%:%184=135%:%
+%:%185=136%:%
+%:%186=137%:%
+%:%187=138%:%
+%:%188=139%:%
+%:%189=140%:%
+%:%190=141%:%
+%:%191=142%:%
+%:%192=143%:%
+%:%193=144%:%
+%:%194=145%:%
+%:%203=148%:%
+%:%215=150%:%
+%:%216=151%:%
+%:%217=152%:%
+%:%218=153%:%
+%:%219=154%:%
+%:%220=155%:%
+%:%221=156%:%
+%:%222=157%:%
+%:%223=158%:%
+%:%227=160%:%
+%:%231=162%:%
+%:%232=163%:%
+%:%233=164%:%
+%:%234=165%:%
+%:%235=166%:%
+%:%236=167%:%
+%:%237=168%:%
+%:%238=169%:%
+%:%239=170%:%
+%:%240=171%:%
+%:%241=172%:%
+%:%242=173%:%
+%:%243=174%:%
+%:%244=175%:%
+%:%245=176%:%
+%:%246=177%:%
+%:%247=178%:%
+%:%248=179%:%
+%:%249=180%:%
+%:%250=181%:%
+%:%251=182%:%
+%:%252=183%:%
+%:%253=184%:%
+%:%254=185%:%
+%:%255=186%:%
+%:%256=187%:%
+%:%257=188%:%
+%:%258=189%:%
+%:%259=190%:%
+%:%260=191%:%
+%:%261=192%:%
+%:%262=193%:%
+%:%263=194%:%
+%:%264=195%:%
+%:%265=196%:%
+%:%266=197%:%
+%:%267=198%:%
+%:%268=199%:%
+%:%269=200%:%
+%:%270=201%:%
+%:%271=202%:%
+%:%272=203%:%
+%:%273=204%:%
+%:%274=205%:%
+%:%275=206%:%
+%:%276=207%:%
+%:%277=208%:%
+%:%278=209%:%
+%:%279=210%:%
+%:%280=211%:%
+%:%281=212%:%
+%:%282=213%:%
+%:%283=214%:%
+%:%284=215%:%
+%:%285=216%:%
+%:%286=217%:%
+%:%290=220%:%
+%:%294=222%:%
+%:%295=223%:%
+%:%296=224%:%
+%:%297=225%:%
+%:%298=226%:%
+%:%299=227%:%
+%:%300=228%:%
+%:%301=229%:%
+%:%302=230%:%
+%:%303=231%:%
+%:%304=232%:%
+%:%305=233%:%
+%:%306=234%:%
+%:%307=235%:%
+%:%308=236%:%
+%:%309=237%:%
+%:%310=238%:%
+%:%311=239%:%
+%:%312=240%:%
+%:%313=241%:%
+%:%314=242%:%
+%:%315=243%:%
+%:%316=244%:%
+%:%317=245%:%
+%:%318=246%:%
+%:%322=248%:%
+%:%326=250%:%
+%:%327=251%:%
+%:%328=252%:%
+%:%329=253%:%
+%:%330=254%:%
+%:%331=255%:%
+%:%332=256%:%
+%:%333=257%:%
+%:%334=258%:%
+%:%335=259%:%
+%:%336=260%:%
+%:%337=261%:%
+%:%338=262%:%
+%:%339=263%:%
+%:%340=264%:%
+%:%341=265%:%
+%:%342=266%:%
+%:%343=267%:%
+%:%344=268%:%
+%:%345=269%:%
+%:%346=270%:%
+%:%347=271%:%
+%:%348=272%:%
+%:%349=273%:%
+%:%350=274%:%
+%:%354=277%:%
+%:%358=279%:%
+%:%359=280%:%
+%:%360=281%:%
+%:%361=282%:%
+%:%362=283%:%
+%:%363=284%:%
+%:%364=285%:%
+%:%365=286%:%
+%:%366=287%:%
+%:%367=288%:%
+%:%368=289%:%
+%:%369=290%:%
+%:%370=291%:%
+%:%371=292%:%
+%:%372=293%:%
+%:%373=294%:%
+%:%374=295%:%
+%:%375=296%:%
+%:%376=297%:%
+%:%377=298%:%
+%:%378=299%:%
+%:%387=302%:%
+%:%399=304%:%
+%:%403=306%:%
+%:%404=307%:%
+%:%405=308%:%
+%:%406=309%:%
+%:%407=310%:%
+%:%408=311%:%
+%:%409=312%:%
+%:%410=313%:%
+%:%411=314%:%
+%:%412=315%:%
+%:%413=316%:%
+%:%414=317%:%
+%:%415=318%:%
+%:%416=319%:%
+%:%417=320%:%
+%:%421=322%:%
+%:%425=324%:%
+%:%426=325%:%
+%:%427=326%:%
+%:%428=327%:%
+%:%429=328%:%
+%:%430=329%:%
+%:%431=330%:%
+%:%432=331%:%
+%:%433=332%:%
+%:%434=333%:%
+%:%438=335%:%
+%:%442=337%:%
+%:%443=338%:%
+%:%444=339%:%
+%:%445=340%:%
+%:%446=341%:%
+%:%447=342%:%
+%:%448=343%:%
+%:%449=344%:%
+%:%450=345%:%
+%:%451=346%:%
+%:%452=347%:%
+%:%453=348%:%
+%:%454=349%:%
+%:%455=350%:%
+%:%456=351%:%
+%:%457=352%:%
+%:%458=353%:%
+%:%459=354%:%
+%:%460=355%:%
+%:%461=356%:%
+%:%462=357%:%
+%:%463=358%:%
+%:%464=359%:%
+%:%465=360%:%
+%:%466=361%:%
+%:%467=362%:%
+%:%468=363%:%
+%:%469=364%:%
+%:%470=365%:%
+%:%471=366%:%
+%:%472=367%:%
+%:%473=368%:%
+%:%474=369%:%
+%:%475=370%:%
+%:%476=371%:%
+%:%477=372%:%
+%:%478=373%:%
+%:%479=374%:%
+%:%480=375%:%

### 2021-11-09 paper/output/document/paper31.tex
bit more cleaning but really moving on to applications

@@
 This naive formalization will hold in the base logic itself, so this formalization does not actually
-improve upon a plain deontic logic at all. This section serves two purposes. First, the naive formalization
+improve upon an ordinary deontic logic at all. This section serves two purposes. First, the naive formalization
 is a toy example that demonstrates the implementation and testing process that will be used for the more 
@@
 \begin{isamarkuptext}%
-The general process of an implementation of a formalization of the FUL will be to represent the 
+The general process of implementing a formalization of the FUL will be to represent the 
 formalization as a sentence in my logic, as above, and then to add the formalization as an axiom to 
@@
 any more powerful. No new theorems can be derived using the naive formalization that could not already
-be derived in the base logic. Thus, this section serves as a``control group." Tests performed in this
+be derived in the base logic. Thus, this section serves as a ``control group." Tests performed in this
 section establish which properties of obligation don't hold in the base logic. The fact that these 
@@
 %
-\isamarkupcmt{\color{blue}Nitpick found a model for card i = 1 and card s = 1:
+\isamarkupcmt{\color{blue}Nitpick found a model for card i = 1:
 
@@
 so permissibility is indeed possible.%
+}\isanewline
+%
+\isamarkupcmt{Quick note on how to read Nitpick results. Nitpick is Isabelle's model checker, and it can either 
+time out, find a model that satisfies the given theorem, or find a counterexample that disproves
+the given theorem. It will then provide the corresponsing model by specifying model components. For readability, 
+all terms except for the free variables are hidden. This model has cardinality 1 for the world (i) type.
+The term `A' is defined as false at world $i_1$.%
+}\isanewline
+%
+\isamarkupcmt{These details will be elided for most Nitpick examples, but this provides guidance on how to interpret
+the output.%
 }%
@@
 The next set of tests will focus on conflicting obligations. There is some debate about Kant's
-personal stance on conflicting obligations, but neo-Kantian agree that the FUL itself cannot obligate
+personal stance on conflicting obligations, but neo-Kantians agree that the FUL itself cannot obligate
 conflicting actions. For more complete discussion of conflicting obligations in Kantian literature, 
-see \ref{sec:priorgoals}. I will first test whether or not, for some arbitrary action, Nitpick can find
+see Section \ref{sec:priorgoals}. I will first test whether or not, for some arbitrary action, Nitpick can find
 a model in which that action is both obligated and prohibited.%
@@
 The above is a rather weak notion of contradictory obligations. Korsgaard additionally argues that Kantian 
-ethics also has the stronger property that if two maxims imply a contradiction, they must not be willed \cite{KorsgaardFUL}.
+ethics also has the stronger property that if two maxims imply a contradiction, they must not be willed \citep{KorsgaardFUL}.
 I test this property below. Because this property is stronger than the previous test, and the previous 
@@
 \isacommand{lemma}\isamarkupfalse%
-\ distribute{\isacharunderscore}obligations{\isacharcolon}\isanewline
-\ \ \isakeyword{assumes}\ \ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymand}\ O\ {\isacharbraceleft}B{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymTurnstile}\ O\ {\isacharbraceleft}A\ \isactrlbold {\isasymand}\ B{\isacharbraceright}{\isachardoublequoteclose}\isanewline
+\ distributive{\isacharunderscore}property{\isacharunderscore}for{\isacharunderscore}obligation{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymand}\ O\ {\isacharbraceleft}B{\isacharbraceright}{\isacharparenright}\ {\isasymequiv}\ {\isasymTurnstile}\ O\ {\isacharbraceleft}A\ \isactrlbold {\isasymand}\ B{\isacharbraceright}{\isachardoublequoteclose}\isanewline
 \ \ \isacommand{nitpick}\isamarkupfalse%
-\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
+{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
 \isadelimproof
@@
   Free variables:
-    A = ($\lambda x. \_$)($i_1$ := True, $i_2$ := False)
-    B = ($\lambda x. \_$)($i_1$ := False, $i_2$ := True)\color{black}
+    A = ($\lambda x. \_$)($i_1$ := False, $i_2$ := True)
+    B = ($\lambda x. \_$)($i_1$ := True, $i_2$ := False)\color{black}
 Once again, this tests fails in the control group.%
@@
 \isamarkupcmt{This means that if something is possibly prohibited, it is in fact prohibited.%
-}\isanewline
-%
-\isamarkupcmt{This is a direct consequence\footnote{For a manual proof, see the Appendix.} of the naive formalization, but it's not clear to me that this is 
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+This is a direct consequence\footnote{For a manual proof, see the Appendix.} of the naive formalization, but it's not clear to me that this is
 actually how we think about ethics. For example, imagine an alternate universe where smiling at 
@@
 morally wrong.%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
+\end{isamarkuptext}\isamarkuptrue%
 %
@@
  and is rather intuitive: you can't be obligated to do the impossible. Deontic 
-logics evolved specifically from this principle, so this should hold in the base logic \cite{cresswell}.%
+logics evolved specifically from this principle, so this should hold in the base logic \citep{cresswell}.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \ O{\isacharunderscore}diamond\ \isacommand{by}\isamarkupfalse%
-\ blast\isanewline
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
+\ blast%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+This test passes in the base logic, and will thus hold in all future formalizations as well. 
+Therefore, it's an interesting property but not actually useful in evaluating different formalizations 
+of the FUL.%
+\end{isamarkuptext}\isamarkuptrue%
 %
@@
 \begin{isamarkuptext}%
-STARTHERE One category of tests involves specified models to encode certain facts 
-into the system and then ask questions about obligations. Without specifying the model, we are limited 
-to showing high-level metaethical facts. Let's start with analyzing an obvious example - that murder is 
-wrong.%
+The second category of tests I will consider is Application tests, which involve specifying models
+to encode certain facts into the system, and then asking questions about obligations. Metaethical tests
+focus on properties that apply to all acts, circumstances, and actors, but application tests focus
+on specific acts. Let's start with analyzing an obvious example - that murder is 
+wrong.
+
+First, I will define murder as a constant below. Notice that right now, this constant is just a term. 
+I haven't specified any properties of murder, so as of now, it's interchangeable with any other term. 
+Application tests generally define an act and then define properties of the act (e.g. if X is murdered,
+X dies). The tests aim to show that acts with certain properties are either obligated or prohibited.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isadelimproof
-%
-\endisadelimproof
-%
-\isatagproof
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-\isanewline
-%
-\endisadelimproof
+\isamarkupcmt{This abbreviation merely represents the statement that murder is prohibited.%
+}%
+\begin{isamarkuptext}%
+I will now define properties of murder and see if they achieve the desired result that murder
+is prohibited. First, I start with the rather basic property that murder is prohibited in some 
+world, or that murder is possibly wrong. This is quite a strong assumption because it gives the system
+a moral fact about a kind of prohibition against murder. Ideally, an ethical theory can take nonmoral
+facts about murder (like murder kills) and use these to generate a moral judgement about the wrongness of 
+murder. This property is much stronger than the assumptions that we make in ordinary moral
+reasoning and thus should be more than enough to show that murder is wrong.%
+\end{isamarkuptext}\isamarkuptrue%
 \isacommand{abbreviation}\isamarkupfalse%
 \ possibly{\isacharunderscore}murder{\isacharunderscore}wrong{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}possibly{\isacharunderscore}murder{\isacharunderscore}wrong\ {\isasymequiv}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ M{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ cw{\isachardoublequoteclose}\isanewline
-%
-\isamarkupcmt{These are very simple properties. \isa{poss{\isacharunderscore}murder{\isacharunderscore}wrong} is an abbreviation for the axiom
-that there is some world where murder might be prohibited. Even this is quite a strong assumption - 
-ideally we'd want to give the system nonmoral facts about murder (like a definition) and then make 
-moral claims.%
-}\isanewline
 \isanewline
@@
 %
-\isamarkupcmt{This lemma gets to the ``heart" of this naive interpretation. We really want to say that if something
+\isamarkupcmt{This lemma gets to the ``heart" of this naive interpretation. If something
  isn't necessarily obligated, it's not obligated anywhere.%
@@
 \begin{isamarkuptext}%
-The above example does exactly what we expect it to: we show that if something is wrong somewhere 
-it's wrong everywhere. That being said, it seems like quite a weak claim. We assumed a very strong, moral 
-fact about murder (that it is wrong somewhere), so it's not surprise that we were able to reach our desired conclusion.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-Let's try a weaker assumption: Not everyone can lie.%
+The above example does exactly what I expect it to: it shows that if something is wrong somewhere 
+it's wrong everywhere. That being said, it seems like quite a weak claim. I assumed a very strong, moral 
+fact about murder (that it is wrong somewhere), so it's not surprise that I was able to show the wrongness 
+of murder.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+Let's try a different example using a much weaker, nonmoral assumption. Kant argues that the FUL
+prohibits lying.\footnote{Specifically, he prohibits making a false promise in order to get some cash \cite[idk page no]{groundwork}.}
+In this example, I will define lying as a term such that not everyone can lie simultaneously. This is 
+one of Kant's canonical examples of the universalizability test. Lying fails the universalizability 
+test because, in a world where everyone lied, no one would believe each other anymore, so the very system 
+or truth-telling would break down, making lying impossible. I can represent this reasoning in my logic 
+as the assumption that not everyone can lie simultaneously.
+
+To fully capture this idea, I need some notion of
+a person, so that I can argue that not all people can lie simultaneously.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \isacommand{consts}\isamarkupfalse%
-\ me{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}person{\isachardoublequoteclose}\isanewline
-%
-\isamarkupcmt{Notice that this machinery is quite empty. We don't give axioms about what a person can or can't do.%
-}\isanewline
-\isanewline
+\ me{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}person{\isachardoublequoteclose}%
+\begin{isamarkuptext}%
+Again, this machinery is quite empty because it doesn't specify any axioms about what a person can 
+or cannot do. In future formalizations, I will define a more robust notion of a person, but the naive 
+formalization has no conception of a person.%
+\end{isamarkuptext}\isamarkuptrue%
 \isacommand{abbreviation}\isamarkupfalse%
@@
 \begin{isamarkuptext}%
-This is a rough translation of failure of the universalizability test: we will test the maxim universally,
-as represented by the universal quantifier in the first conjunct, and simultaneously \cite{simul}, as represented by 
-the second conjunct. The FUL tells us that if this sentence is true, then lying should be prohibited. 
-Let's test it.%
+This is a rough translation of failure of the universalizability test: I  test the maxim universally,
+as represented by the universal quantifier in the first conjunct, and simultaneously, as represented by 
+the second conjunct \citep{simul}. The FUL says that if this sentence is true, then lying should be prohibited. 
+Therefore, the above sentence should imply that lying is prohibited.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupcmt{\color{blue} Nitpick found a counterexample for card person = 2 and card i = 2:
-
-  Free variable:
-    lie = ($\lambda x. \_$)($p_1$ := ($\lambda x. \_$)($i_1$ := True, $i_2$ := False), $p_2$ := ($\lambda x. \_$)($i_1$ := False, $i_2$ := False)) \color{black}%
-}\isanewline
-%
-\isamarkupcmt{Quick note on how to read Nitpick results. Nitpick will either say that it found a ``model" or a ``counterexample" in 
-the first line. It will then provide a model by specifying model components. For readability, all except for the 
-free variables are hidden. This model has cardinality 2 for the person and world (i) types. The term \texttt{lie} is 
-defined for people $p_1$ and $p_2$. $p_1$ lies at world $i_1$ and does not lie at world $i_2$. $p_2$ does
-the opposite.%
-}\isanewline
-%
-\isamarkupcmt{These details will be elided for most Nitpick examples, but this provides guidance on how to interpret
-the output.%
+\isamarkupcmt{\color{blue}Nitpick found a counterexample for card i = 1 and card person = 1:
+
+  Empty assignment \color{black}%
 }%
@@
 \begin{isamarkuptext}%
-This formula isn't valid. While the FUL should tell us that lying is prohibited, the fact that it 
+This test fails. The FUL should say that lying is prohibited and the fact that it
 doesn't demonstrates the weakness of this naive formulation of the categorical imperative. Kant's version of
-the FUL universalizes across people, as we did in the definition of \isa{lying{\isacharunderscore}not{\isacharunderscore}universal\ {\isasymequiv}\ {\isasymforall}w{\isachardot}\ {\isasymnot}\ {\isacharparenleft}{\isacharparenleft}{\isasymforall}x{\isachardot}\ lie\ x\ w{\isacharparenright}\ {\isasymand}\ lie\ me\ w{\isacharparenright}}.
-The
-naive formalization universalizes across worlds using the $\Box$ operator, so it makes sense that it can't
-handle this example appropriately.
-
-The above implies that the FUL should prescribe consistent obligations across people. If our formalization
-doesn't, clearly something has gone wrong somewhere. Let's test that!%
+the FUL universalizes across people, as in the definition of \isa{lying{\isacharunderscore}not{\isacharunderscore}universal\ {\isasymequiv}\ {\isasymforall}w{\isachardot}\ {\isasymnot}\ {\isacharparenleft}{\isacharparenleft}{\isasymforall}x{\isachardot}\ lie\ x\ w{\isacharparenright}\ {\isasymand}\ lie\ me\ w{\isacharparenright}}.
+When universalizing
+an act, Kant imagines a world in which all \emph{people} perform the act. The naive formalization, 
+on the other hand, universalizes an act across \emph{worlds} because it uses the $\Box$ operator
+to represent universalization. This is the philosophical error that makes the naive 
+formalization so naive, and future formalizations will need to remedy this error.
+This serves as an example of the kind of reasoning that 
+Isabelle empowers us to do. Even this simple argument has philosophical consequences. It tells us that
+reading the FUL as a claim about consistency across possible worlds, instead of consistency across 
+agents, leads to counterintuitive conclusions.
+
+Additionally, Kant argued that obligations are not person-specific but instead apply equally to all 
+rational agents.\footnote{For a philosophical analysis of this idea, see Section \ref{sec:priorgoals}}
+Thus, any formalization of the categorical should generate obligations that are consistent across people.
+This next step analyzes this property.%
 \end{isamarkuptext}\isamarkuptrue%
 \isacommand{lemma}\isamarkupfalse%
-\ universalizability{\isacharcolon}\isanewline
+\ equal{\isacharunderscore}obligations{\isacharcolon}\isanewline
 \ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymTurnstile}\ O\ {\isacharbraceleft}{\isacharparenleft}lie{\isacharparenleft}me{\isacharparenright}{\isacharparenright}{\isacharbraceright}{\isachardoublequoteclose}\isanewline
@@
 \begin{isamarkuptext}%
-This lemma demonstrates the problem with the naive interpretation. The FUL universalizes across people
-but the naive formalization universalizes across worlds. Because this interpretation is so naive, it is 
-limited in its power. However, this serves as an example of the kind of reasoning that 
-Isabelle empowers us to do. Even this simple argument has philosophical consequences. It tells us that
-reading the FUL as a claim about consistency across possible worlds, instead of consistency across 
-agents, leads to counterintuitive conclusions.%
+In this section, I presented the framework I will use to implement and test different interpretations
+of the categorical imperative. An implementation consists of some necessary logical background, a 
+representation of the FUL using that logical background, and a logical system that adds that representation
+as an axiom. To test such an implementation, I design a ``test suite" that consists of properties of 
+the categorical imperative verified by philosophical literature. I demonstrated the performance of 
+these tests in my base logic, which serves as a control group.
+
+I will evaluate more sophisticated formalizations of the FUL using this testing framework. The properties
+I test will remain more or less consisten across different formalizations, but the exact logical representation
+of the tests will depend on the specifics of a particular implementation. In the next section, I will 
+implement Moshe Kroy's formalization of the FUL and evaluate it using this testing framework. Finally, 
+I will use the results of these tests to define clear goals for a custom formalization of the categorical 
+imperative. These goals represent areas of improvement over previous formalizations, and I will justify
+them using philosophical literature.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %:%335=190%:%
-%:%345=192%:%
-%:%346=193%:%
-%:%347=194%:%
-%:%348=195%:%
-%:%350=197%:%
-%:%351=197%:%
-%:%352=198%:%
-%:%353=199%:%
-%:%354=200%:%
-%:%355=200%:%
+%:%336=190%:%
+%:%338=191%:%
+%:%339=192%:%
+%:%340=193%:%
+%:%341=194%:%
+%:%342=195%:%
+%:%343=195%:%
+%:%345=196%:%
+%:%346=197%:%
+%:%356=199%:%
 %:%357=200%:%
-%:%361=200%:%
-%:%362=200%:%
-%:%364=201%:%
-%:%365=202%:%
-%:%366=203%:%
-%:%367=204%:%
-%:%368=204%:%
-%:%370=205%:%
-%:%380=207%:%
-%:%381=208%:%
-%:%382=209%:%
-%:%384=211%:%
-%:%385=211%:%
-%:%386=212%:%
-%:%387=213%:%
-%:%388=214%:%
-%:%389=214%:%
+%:%358=201%:%
+%:%359=202%:%
+%:%361=204%:%
+%:%362=204%:%
+%:%363=205%:%
+%:%364=206%:%
+%:%365=207%:%
+%:%366=207%:%
+%:%368=207%:%
+%:%372=207%:%
+%:%373=207%:%
+%:%375=208%:%
+%:%376=209%:%
+%:%377=210%:%
+%:%378=211%:%
+%:%379=211%:%
+%:%381=212%:%
 %:%391=214%:%
-%:%395=214%:%
-%:%396=214%:%
-%:%398=215%:%
-%:%399=216%:%
-%:%400=217%:%
-%:%401=218%:%
-%:%402=218%:%
-%:%404=219%:%
-%:%405=220%:%
-%:%415=222%:%
-%:%419=224%:%
-%:%420=225%:%
-%:%421=226%:%
-%:%422=227%:%
-%:%423=228%:%
-%:%425=230%:%
-%:%426=230%:%
-%:%427=231%:%
-%:%428=232%:%
-%:%429=233%:%
-%:%430=233%:%
+%:%392=215%:%
+%:%393=216%:%
+%:%395=218%:%
+%:%396=218%:%
+%:%397=219%:%
+%:%398=220%:%
+%:%399=221%:%
+%:%400=221%:%
+%:%402=221%:%
+%:%406=221%:%
+%:%407=221%:%
+%:%409=222%:%
+%:%410=223%:%
+%:%411=224%:%
+%:%412=225%:%
+%:%413=225%:%
+%:%415=226%:%
+%:%416=227%:%
+%:%426=229%:%
+%:%430=231%:%
+%:%431=232%:%
 %:%432=233%:%
-%:%436=233%:%
-%:%437=233%:%
-%:%439=234%:%
-%:%440=235%:%
-%:%441=236%:%
-%:%442=237%:%
-%:%443=237%:%
-%:%445=238%:%
-%:%446=238%:%
-%:%469=253%:%
-%:%470=254%:%
-%:%471=255%:%
-%:%472=256%:%
-%:%474=258%:%
-%:%475=258%:%
-%:%476=259%:%
-%:%477=260%:%
-%:%478=261%:%
-%:%479=262%:%
-%:%480=263%:%
-%:%481=263%:%
-%:%488=264%:%
-%:%489=264%:%
-%:%490=265%:%
-%:%491=265%:%
-%:%492=266%:%
-%:%493=266%:%
-%:%494=267%:%
-%:%495=267%:%
-%:%496=267%:%
-%:%497=267%:%
-%:%499=268%:%
-%:%500=269%:%
-%:%501=269%:%
-%:%502=270%:%
-%:%503=270%:%
-%:%504=270%:%
-%:%506=271%:%
-%:%507=272%:%
-%:%508=273%:%
-%:%509=274%:%
+%:%433=234%:%
+%:%434=235%:%
+%:%436=237%:%
+%:%437=237%:%
+%:%438=238%:%
+%:%439=239%:%
+%:%440=240%:%
+%:%441=240%:%
+%:%443=240%:%
+%:%447=240%:%
+%:%448=240%:%
+%:%450=241%:%
+%:%451=242%:%
+%:%452=243%:%
+%:%453=244%:%
+%:%454=244%:%
+%:%456=245%:%
+%:%457=245%:%
+%:%480=260%:%
+%:%481=261%:%
+%:%482=262%:%
+%:%483=263%:%
+%:%485=265%:%
+%:%486=265%:%
+%:%487=266%:%
+%:%488=267%:%
+%:%489=268%:%
+%:%490=269%:%
+%:%491=270%:%
+%:%492=270%:%
+%:%499=271%:%
+%:%500=271%:%
+%:%501=272%:%
+%:%502=272%:%
+%:%503=273%:%
+%:%504=273%:%
+%:%505=274%:%
+%:%506=274%:%
+%:%507=274%:%
+%:%508=274%:%
 %:%510=275%:%
-%:%511=275%:%
-%:%513=276%:%
-%:%523=278%:%
-%:%524=279%:%
-%:%525=280%:%
-%:%526=281%:%
-%:%527=282%:%
-%:%529=284%:%
-%:%530=284%:%
-%:%531=285%:%
-%:%532=286%:%
-%:%533=287%:%
-%:%534=287%:%
+%:%511=276%:%
+%:%512=276%:%
+%:%513=277%:%
+%:%514=277%:%
+%:%515=277%:%
+%:%517=278%:%
+%:%518=279%:%
+%:%519=280%:%
+%:%520=281%:%
+%:%521=282%:%
+%:%522=282%:%
+%:%524=283%:%
+%:%534=285%:%
+%:%535=286%:%
 %:%536=287%:%
-%:%540=287%:%
-%:%541=287%:%
-%:%543=288%:%
-%:%544=289%:%
-%:%545=290%:%
-%:%546=291%:%
-%:%547=292%:%
-%:%548=293%:%
-%:%558=295%:%
-%:%562=297%:%
-%:%563=298%:%
-%:%564=299%:%
-%:%566=301%:%
-%:%567=301%:%
-%:%568=302%:%
-%:%571=303%:%
-%:%575=303%:%
-%:%576=303%:%
-%:%578=304%:%
-%:%579=304%:%
-%:%581=305%:%
-%:%582=306%:%
-%:%583=307%:%
-%:%584=308%:%
+%:%537=288%:%
+%:%538=289%:%
+%:%540=291%:%
+%:%541=291%:%
+%:%542=292%:%
+%:%543=293%:%
+%:%544=293%:%
+%:%546=293%:%
+%:%550=293%:%
+%:%551=293%:%
+%:%553=294%:%
+%:%554=295%:%
+%:%555=296%:%
+%:%556=297%:%
+%:%557=298%:%
+%:%558=299%:%
+%:%568=301%:%
+%:%572=303%:%
+%:%573=304%:%
+%:%574=305%:%
+%:%576=307%:%
+%:%577=307%:%
+%:%578=308%:%
+%:%581=309%:%
 %:%585=309%:%
-%:%595=311%:%
-%:%596=312%:%
-%:%597=313%:%
-%:%599=315%:%
-%:%600=315%:%
-%:%601=316%:%
-%:%604=317%:%
-%:%608=317%:%
-%:%609=317%:%
-%:%610=317%:%
-%:%651=337%:%
-%:%663=339%:%
-%:%664=340%:%
-%:%665=341%:%
-%:%666=342%:%
-%:%668=344%:%
-%:%669=344%:%
-%:%670=345%:%
-%:%671=345%:%
+%:%586=309%:%
+%:%588=310%:%
+%:%598=312%:%
+%:%599=313%:%
+%:%600=314%:%
+%:%601=315%:%
+%:%602=316%:%
+%:%606=318%:%
+%:%607=319%:%
+%:%608=320%:%
+%:%610=322%:%
+%:%611=322%:%
+%:%612=323%:%
+%:%615=324%:%
+%:%619=324%:%
+%:%620=324%:%
+%:%621=324%:%
+%:%630=326%:%
+%:%631=327%:%
+%:%632=328%:%
+%:%667=347%:%
+%:%679=349%:%
+%:%680=350%:%
+%:%681=351%:%
+%:%682=352%:%
 %:%683=353%:%
-%:%686=354%:%
-%:%687=354%:%
-%:%689=355%:%
-%:%690=356%:%
-%:%691=357%:%
-%:%692=358%:%
-%:%693=358%:%
-%:%694=359%:%
-%:%695=360%:%
-%:%696=360%:%
-%:%697=361%:%
-%:%700=362%:%
-%:%704=362%:%
-%:%705=362%:%
-%:%707=363%:%
-%:%708=364%:%
-%:%718=366%:%
-%:%719=367%:%
-%:%720=368%:%
-%:%724=370%:%
-%:%726=372%:%
-%:%727=372%:%
-%:%728=373%:%
-%:%729=373%:%
-%:%730=374%:%
-%:%731=374%:%
-%:%733=375%:%
-%:%734=375%:%
-%:%735=376%:%
-%:%736=377%:%
-%:%737=377%:%
-%:%739=379%:%
-%:%740=380%:%
-%:%741=381%:%
-%:%742=382%:%
-%:%744=384%:%
-%:%745=384%:%
-%:%746=385%:%
-%:%747=386%:%
-%:%748=387%:%
-%:%749=387%:%
-%:%752=388%:%
-%:%756=388%:%
-%:%757=388%:%
-%:%759=389%:%
-%:%760=390%:%
-%:%761=391%:%
-%:%762=392%:%
-%:%763=392%:%
-%:%765=393%:%
-%:%766=394%:%
-%:%767=395%:%
-%:%768=396%:%
-%:%769=397%:%
-%:%770=397%:%
-%:%772=398%:%
-%:%773=399%:%
-%:%783=401%:%
-%:%784=402%:%
-%:%785=403%:%
-%:%786=404%:%
-%:%787=405%:%
-%:%788=406%:%
-%:%789=407%:%
-%:%790=408%:%
-%:%792=410%:%
-%:%793=410%:%
-%:%794=411%:%
-%:%795=412%:%
-%:%796=413%:%
-%:%797=413%:%
-%:%799=413%:%
-%:%803=413%:%
-%:%804=413%:%
-%:%806=414%:%
-%:%807=415%:%
-%:%808=416%:%
-%:%809=417%:%
-%:%810=418%:%
-%:%811=419%:%
-%:%821=421%:%
-%:%822=422%:%
-%:%823=423%:%
-%:%824=424%:%
-%:%825=425%:%
-%:%826=426%:%
-%:%834=430%:%
-%:%842=430%:%
+%:%684=354%:%
+%:%685=355%:%
+%:%686=356%:%
+%:%687=357%:%
+%:%688=358%:%
+%:%690=360%:%
+%:%691=360%:%
+%:%692=361%:%
+%:%693=361%:%
+%:%695=362%:%
+%:%698=364%:%
+%:%699=365%:%
+%:%700=366%:%
+%:%701=367%:%
+%:%702=368%:%
+%:%703=369%:%
+%:%704=370%:%
+%:%706=372%:%
+%:%707=372%:%
+%:%708=373%:%
+%:%709=374%:%
+%:%710=374%:%
+%:%711=375%:%
+%:%714=376%:%
+%:%718=376%:%
+%:%719=376%:%
+%:%721=377%:%
+%:%722=378%:%
+%:%732=380%:%
+%:%733=381%:%
+%:%734=382%:%
+%:%735=383%:%
+%:%739=385%:%
+%:%740=386%:%
+%:%741=387%:%
+%:%742=388%:%
+%:%743=389%:%
+%:%744=390%:%
+%:%745=391%:%
+%:%746=392%:%
+%:%747=393%:%
+%:%748=394%:%
+%:%750=397%:%
+%:%751=397%:%
+%:%752=398%:%
+%:%753=398%:%
+%:%754=399%:%
+%:%755=399%:%
+%:%757=401%:%
+%:%758=402%:%
+%:%759=403%:%
+%:%761=405%:%
+%:%762=405%:%
+%:%764=407%:%
+%:%765=408%:%
+%:%766=409%:%
+%:%767=410%:%
+%:%769=412%:%
+%:%770=412%:%
+%:%771=413%:%
+%:%772=414%:%
+%:%773=415%:%
+%:%774=415%:%
+%:%777=416%:%
+%:%781=416%:%
+%:%782=416%:%
+%:%784=417%:%
+%:%785=418%:%
+%:%786=419%:%
+%:%796=421%:%
+%:%797=422%:%
+%:%798=423%:%
+%:%799=424%:%
+%:%800=425%:%
+%:%801=426%:%
+%:%802=427%:%
+%:%803=428%:%
+%:%804=429%:%
+%:%805=430%:%
+%:%806=431%:%
+%:%807=432%:%
+%:%808=433%:%
+%:%809=434%:%
+%:%810=435%:%
+%:%811=436%:%
+%:%813=438%:%
+%:%814=438%:%
+%:%815=439%:%
+%:%816=440%:%
+%:%817=441%:%
+%:%818=441%:%
+%:%820=441%:%
+%:%824=441%:%
+%:%825=441%:%
+%:%827=442%:%
+%:%828=443%:%
+%:%829=444%:%
+%:%830=445%:%
+%:%831=446%:%
+%:%832=447%:%
+%:%842=449%:%
+%:%843=450%:%
+%:%844=451%:%
+%:%845=452%:%
+%:%846=453%:%
+%:%847=454%:%
+%:%848=455%:%
+%:%849=456%:%
+%:%850=457%:%
+%:%851=458%:%
+%:%852=459%:%
+%:%853=460%:%
+%:%854=461%:%
+%:%855=462%:%

### 2021-11-15 paper/output/document/paper33.tex
bit more cleaning but really moving on to applications
made writing fixes

@@
 %
-\isamarkupsubsubsection{Goals From Philosophical Literature%
+\isamarkupsubsubsection{Goals From Philosophical Literature \label{sec:litgoals}%
 }
@@
 \begin{isamarkuptext}%
-\textbf{Practical Contradiction Interpretation} Kantians debate the correct interpretation of the Formula of Universal Law because Kant appears to 
-interpret the universalizability test in different ways. Korsgaard argues for the practical contradiction 
-interpretation, broadly accepted as correct within the philosophical community \cite[177]{ebelsduggan}.
-Because her argument is broadly accepted, I will make it a goal to represent the practical contradiction
-interpretation of the FUL in my custom formalization. The naive formalization and Kroy's formalization
-clearly do not meet this goal.
+\textbf{Conventional Acts}
+Kantians debate over the most philosophically sound interpretation of the Formula of Universal Law.
+One litmus test that Korsgaard introduces makes a distinction between conventional and natural acts \citep{KorsgaardFUL}. 
+A conventional act is one like promising, which relies on the convention of promising, in which we all
+implicitly understand a promise as a commitment. Conventional acts are generally easier to show the 
+wrongness of because there are worlds in which these acts are impossible; namely, worlds in which the 
+convention does not exist. For example, the common argument against falsely promising is that if 
+everyone were to falsely promise, the convention of promising would fall apart because people wouldn't believe
+each other anymore, so falsely promising is prohibited. Despite the relative ease of this property,
+it fails in both the naive and Kroy's interpretations, demonstrating the weakness of these 
+formalizations. This property will hold for my custom formalization.
 
-Below, I briefly reconstruct Korsgaard's argument for the practical contradiction interpretation. While 
-she believes that the text partially supports this interpretation, her argument is philosophical and 
-derives its strength from the plausibility of the practical contradiction interpretation.
+\medskip
 
-Recall that the formula of universal law is “act only in accordance with that maxim through which you can at the 
-same time will that it become a universal law” \cite[4:421]{groundwork}. To determine if a maxim can be willed as a 
-universal law, one must use the “universalizability test,” which requires imagining a world in which 
-everyone for all of time has willed the maxim. If willing the maxim in such a world generates a contradiction, 
-then the action is prohibited. There are three interpretations of what sort of contradiction is necessary: 
-(1) the teleological view, prohibiting actions that conflict with some assumed teleological end when 
-universalized, (2) the logical contradiction view, prohibiting maxims that are logically impossible 
-when universalized (such as the lying example discussed earlier), and (3) the practical contradiction view, prohibiting maxims that are self-defeating 
-when universalized.
-
-Under the logical contradiction interpretation, falsely promising to repay a loan to get some quick cash
-fails the universalizability test because, in such a world, the practice of promising would die out so 
-making a false promise would be impossible. Korsgaard appeals to Dietrichson \cite{dietrichson} to construct the example of 
-a mother killing her children that tend to cry more than average so that she can get some 
-sleep at night. Universalizing this maxim does not generate a logical contradiction, but it is clearly 
-morally wrong. The problem here is that killing is a natural action, which Korsgaard distinguishes from 
-a practice, like promising. Natural actions will never be logically impossible, so the logical contradiction 
-view fails to prohibit them.
-
-Under the teleological contradiction interpretation, a maxim is prohibited if it undercuts some natural 
-or assigned purpose for some practice, act, or object. For example, the purpose of promising is to 
-create a system of mutual trust and false promising undercuts this purpose and is thus prohibited. The problem 
-with this view is that it assumes that the agent is committed, either because of their own goals or 
-because of some property of a rational will, to some teleological system. Acton formulates Hegel's argument that \cite{acton},
-an agent doesn't have to be committed to promising as a system of mutual trust. Korsgaard concludes that 
-assigning teleological purposes to actions is difficult because ``such purposes may have
-nothing to do with what the agent wants or ought rationally to want, or even with what
-any human being wants." If the agent is not committed to the purpose, then will not see a contradiction 
-in willing an act that violates this purpose.
-
-This difficulty with the teleological contradiction interpretation drives Korsgaard to look for purposes
-that an agent must necessarily be committed to, and she concludes that this must be the purpose of the 
-maxim itself. By willing a maxim, an agent commits themselves to the goal of the maxim, and thus cannot 
-rationally will a system in which this goal is undercut. This system satisfactorily handles natural actions
-like those of the sleep-deprived mother: in willing the end of sleeping through the night, she is 
-implicitly willing that she be alive in order to secure and enjoy her sleep. If any mother is allowed to kill
-any loud child, then she cannot be secure in the possession of her life, because her own mother may have 
-grown frustrated with her crying. Her willing this maxim thwarts the end that she sought to secure.
-
-The practical contradiction interpretation not only addresses the problems with the first two 
-interpretations, it also offers a much more satisfying explanation of why certain maxims are immoral. 
-The problem is not the existence of a contradiction itself, but instead the fact that these maxims 
-involve parasitic behavior on social conditions that the agent seeks to benefit from. The false promiser 
-simultaneously wants to abuse the system of promising and benefit from it, and is thus making an exception 
-of themselves. It is this kind of free-riding that the universalizability test seeks to draw out. The test
-raises the same kinds of objections that the question ``What if everyone did that?" seeks to draw out.
-
-Note that the practical contradiction interpretation is strictly stronger than the logical contradiction
-interpretation. Actions that are not universalizble, like lying, are also not effective means to any end
-when universalized because they become impossible. Therefore, a formalization of the practical contradiction
-interpretation must still obey the earlier goal that non-universalizable acts be prohibited.%
+\textbf{Natural Acts}
+The more difficult kind of act to show the wrongness of is a natural act, like murder or violence. 
+These acts can never be logically impossible; even if everyone murders or acts violently, murder and 
+violence will still be possible. This property of natural acts makes it difficult for interpretations of
+the FUL to show the wrongness of violence. Both the naive and Kroy's interpretations fail to show
+the wrongness of natural acts (in fact, they fail to show the weaker wrongness of conventional acts). 
+This property will hold for the custom formalization. I will show the wrongness of both natural and 
+conventional acts by formalizing Korsgaard's practical contradiction interpretation of the FUL, which 
+is widely accepted as the canonical interpretation of the FUL \citep{KorsgaardFUL}. I will explain this 
+decision in greater detail in the next chapter, where I present my custom formalization.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %:%249=159%:%
-%:%250=160%:%
-%:%251=161%:%
-%:%252=162%:%
-%:%253=163%:%
-%:%254=164%:%
-%:%255=165%:%
-%:%256=166%:%
-%:%257=167%:%
-%:%258=168%:%
-%:%259=169%:%
-%:%260=170%:%
-%:%261=171%:%
-%:%262=172%:%
-%:%263=173%:%
-%:%264=174%:%
-%:%265=175%:%
-%:%266=176%:%
-%:%267=177%:%
-%:%268=178%:%
-%:%269=179%:%
-%:%270=180%:%
-%:%271=181%:%
-%:%272=182%:%
-%:%273=183%:%
-%:%274=184%:%
-%:%275=185%:%
-%:%276=186%:%
-%:%277=187%:%
-%:%278=188%:%
-%:%279=189%:%
-%:%280=190%:%
-%:%281=191%:%
-%:%282=192%:%
-%:%283=193%:%
-%:%284=194%:%
-%:%285=195%:%
-%:%286=196%:%
-%:%287=197%:%

### 2021-11-15 paper/output/document/upshot.tex
made writing fixes

@@
 
-The first contribution of computational ethics is precision. Much of analytic philosophy involves 
+The first contribution of computational ethics is precision \footnote{TODO: this article discusses 
+benefits of precision: $https://www-jstor-org.ezp-prod1.hul.harvard.edu/stable/pdf/2024318.pdf?refreqid=excelsior%3Aee9f16263a31b3e2d4fe548e8c5c823f$}. Much of analytic philosophy involves 
 making a particular concept precise. Thought experiments, arguments, counterexamples, and examples 
@@
 %:%533=439%:%
-%:%542=442%:%
-%:%554=445%:%
+%:%534=440%:%
+%:%543=443%:%
 %:%555=446%:%
@@
 %:%574=465%:%
+%:%575=466%:%

### 2021-11-15 paper/output/document/whykant.tex
made writing fixes

@@
 %
-\isamarkupsubsection{Why Kantian Ethics%
+\isamarkupsubsection{Choice of Ethical Theory%
 }
@@
 attractive candidates for automation because rules are generally computationally tractable \cite[1]{powers}. 
-Intuitively, algorithms are rules or procedures for problem solving and Kantian ethics offer one such 
+Intuitively, algorithms are rules or procedures for problem solving and deontology offers one such 
 procedure for the problem of making ethical judgements. I will make this intuition precise by
-arguing that Kantian ethics is natural to formalize because evaluating a maxim requires little additional
-data about the world and a maxim is relatively easy to represent to a computer. All 
-ethical traditions have debates that an automated ethical system will need to take a stance on, but these debates
-are less frequent and less controversial for Kantian ethics than for consequentialism and 
-virtue ethics.
+arguing that deontological ethics is natural to formalize because rules generally require little additional
+data about the world and are usually easy to represent to a computer. All ethical traditions have debates that an 
+automated ethical system will need to take a stance on, but these debates are less frequent and controversial
+for deontological ethics than for consequentialism and virtue ethics.
 
-I do not aim to show that Kantian ethics is the only tractable theory to automate and
+I do not aim to show that deontology is the only tractable theory to automate or
 to present a comprehensive overview of all consequentialist or virtue ethical theories. Instead, I 
-present a sample of some approaches in each tradition and argue that Kantian ethics is more straightforward 
+present a sample of some approaches in each tradition and argue that deontology is more straightforward 
 to formalize than these approaches. Future work could and should address the challenges I outline in 
@@
 as an early proof-of-concept for computational ethics, I choose to automate an ethical theory that 
-poses fewer challenges than others.%
+poses fewer challenges than others.
+
+I first present deontological ethics, then consequentialism, and finally virtue ethics. For each 
+tradition, I present a crash course for non-philosophers and then explain some obstacles to automation, 
+arguing that these obstacles are weakest in the case of deontology. Finally, I will present the specific 
+deontological theory I am automating (Kantian ethics) and will argue that it is comparatively easier
+to formalize. I will also outline the specific debates in the literature that my formalization takes
+a stance on and potential challenges for formalizing deontology.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupsubsubsection{Kantian Ethics%
+\isamarkupsubsubsection{Deontological Ethics%
 }
@@
 \begin{isamarkuptext}%
-\textbf{Crash Course on Kantian Ethics}%
+\textbf{Crash Course on Deontology}%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-Kant's theory is centered on practical reason, which is the kind of reason that we 
-use to decide what to do. In \emph{The Groundwork of the Metaphysics of Morals}, Kant's most influential 
-text on ethics, he explains that rational beings are unique because we can act ``in accordance with 
-the representations of laws" \cite[4:412]{groundwork}. In contrast, a ball thrown into the air acts 
-according to the laws of physics themselves. It cannot ask itself, ``Should I fall back to the ground?" 
-It simply falls. A rational being on the other hand, can ask themselves ``Should I act on this reason?" 
-As Korsgaard describes it, when choosing which desire to act on, ``it is as if there is something over 
-and above all of your desires, something which is you, and which chooses which desire to act on" \cite[100]{sources}. 
-Rational beings are set apart by this reflective capacity. A rational being's behavior is purposive and 
-their actions are guided by practical reason. They have reasons for acting, even when these reasons may be 
-opaque to them. This operation of practical reason is what Kant calls the will.
-
-The will operates by adopting, or willing, maxims, which are its percieved reasons for acting. Kant defines a maxim as 
-the ``subjective principle of willing," or the reason that the will \emph{subjectively} gives 
-to itself for acting \cite[16 footnote 1]{groundwork}. There is debate about what exactly must be 
-included in a maxim, but most philosophers agree that a maxim consists of some combination of circumstances, 
-act, and goal.\footnote{For more discussion of the definition of a maxim, see Section What Is a Maxim}
-One example of a maxim is ``when I am hungry, I will eat a doughnut in order to satisfy my sweet tooth." 
-When an agent wills this maxim, they decide to act on it. They commit themselves to the end in the maxim 
-(e.g. satisfying your sweet tooth). They represent their action, to themselves, as following the 
-principle given by this maxim. Because a maxim captures an agent's principle of action, Kant evaluates
-maxims are obligatory or prohibited. He argues that certain maxims have a form or logical structure 
-that requires any rational agent to will them, and these maxims are obligatory.
-
-The form of an obligatory maxim is given by the categorical imperative, or the supreme rule of morality. 
-An imperative is a command, such as ``Close the door" or "Eat the doughnut in order to satisfy your 
-sweet tooth." An imperative is categorical if it holds unconditionally for all rational agents under all 
-circumstances. Kant argues that the moral law must be a categorical imperative, for otherwise it would 
-not have the force that makes it a moral law \cite[5]{groundwork}. In order for an imperative to be 
-categorical, it must be derived from the will's authority over itself. Our wills are autonomous, so 
-the only thing that can have unconditional authority over a rational will is 
-the rational will itself. In Velleman's version of this argument, he claims that no one else can tell you what 
-to do because you can always ask why you 
-should obey their authority. The only authority that you cannot question is the authority of your own 
-practical reason. To question this authority is to demand a reason for acting for reasons, which 
-concedes the authority of reason itself \cite[23]{velleman}. Therefore, the only possible candidates 
-for the categorical imperative are those rules that are required of the will because it is a will. 
-The categorical imperative must be a property of practical reason itself.
-
-Armed with this understanding of practical reason, Kant presents the categorical 
-imperative. He presents three ``formulations" or versions of the categorical imperative and goes on to 
-argue that all three formulations are equivalent. In this project, I focus on the first formulation,
-the Formula of Universal Law, but will briefly present the other two as well\footnote{For more on this 
-choice, see Section Why FUL}.
-
-The first formulation of the categorical imperative is the
-Formula of Universal Law (FUL), which reads, ``act only according to that maxim through which you can 
-at the same time will that it become a universal law" \cite[34]{groundwork}. This formulation
-generates the universalizability test, which tests the moral value of a maxim by 
-imagining a world in which it becomes a universal law and attempting to will the maxim in that world.
-If there is a contradiction in willing the maxim in a world in which everyone universally wills the maxim,
-the maxim is prohibited. 
-Velleman presents a concise argument for the FUL. He argues that reason is universally shared among reasoners. For 
-example, all reasoners have equal access to the arithmetic logic that shows that ``2+2=4" \cite[29]{velleman}. The chain of 
-reasoning that makes this statement true is not specific to any person, but is universal across people. 
-Therefore, if I have sufficient reason to will a maxim, so does every other rational agent. There is 
-nothing special about the operation of my practical reason that other reasoners don't have access to. 
-Practical reason is shared, so in adopting a maxim, I implicitly state that all reasoners
-across time also have reason to adopt that maxim. Therefore, because I act on reasons, I must obey the 
-FUL. Notice that this fulfills the above criterion for a categorical imperative: the FUL is derived from 
-a property of practical reason itself and thus derives authority from the will's authority over itself, 
-as opposed to some external authority.
-
-The second formulation of the categorical imperative is the formula of humanity (FUH): ``So act that you use humanity, 
-in your own person, as well as in the person of any other, always at the same time as an end, never merely 
-as a means." \cite[41]{groundwork}. This formulation is often understood as requiring us to 
-acknowledge and respect the dignity of every other person. The third formulation of the categorical 
-imperative is the formula of autonomy (FOA), which Korsgaard summarizes in her introduction to the Groundwork 
-as, ``we should so act that we may think of ourselves as legislating universal laws through our 
-maxims" \cite[28]{korsgaardintro}. While closely related to the FUL, the FOA presents morality as the activity of 
-perfectly rational agents in an ideal ``kingdom of ends," guided by what Kant calls the ``laws of freedom."
-
-The above is not meant to serve as a full defense of Kant's ethical theory, as that is outside the scope
-of this thesis. Instead, I briefly reconstruct an argument for Kant's ethical theory in the hopes 
-of offering context for the implementation of the FUL I present later in the thesis. Additionally, understanding 
-the structure of Kant's argument also reveals facts about his theory that make it an ideal candidate 
-for formalization.%
+Deontological ethical theories evaluate actions as permissible, obligatory, or prohibited. The 
+deontological tradition argues that an action should not be judged on its consequences, 
+but rather on ``its confirmity with a moral norm" \citep{sepdeont}. In other words, deontological theories
+define a set of moral norms or rules and evaluate actions based on their confirmity or lackthereof to
+these rules. Deontologists do not believe that an agent should maximize the number of times that they 
+conform to such rules; rather they argue that an agent should never violate any of the moral laws. A wrong
+choice is wrong, regardless of its consequences.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-\textbf{Ease of Automation}%
+\textbf{Formalizing Deontology}%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-Kantian ethics is natural to formalize because the categorical imperative, particularly the FUL, 
-is a formal principle of practical reason. In other words, the FUL is a property of reason related 
-to the form or structure of a maxim. It has nothing to do with the circumstances of behavior 
-(beyond those included in a maxim), the agent's mental state, or any other contingent facts. Instead, 
-it is purely a property of the proposed principle for action. This formalism makes Kantian ethics an 
-attractive candidate for formalization. While other ethical theories often rely on many facts about 
-the world or the actor, Kantian ethics simply relies on the form of a given maxim. A computer evaluating 
-a maxim doesn't require any knowledge about the world beyond what is contained in a maxim. A maxim 
-is the only input that the computer needs to make a moral judgement. Automating 
-Kantian ethics merely requires making the notion of a maxim precise and representing it to the computer. 
-This distinguishes Kantian ethics from consequentialism and virtue ethics, which, as I will argue below, 
-require far more knowledge about the world or the agent to reach a moral decision.
+Deontology is immediately an attractive candidate for formalization because computers tend to 
+understand rules; programming languages are designed to teach computers algorithms. Deontological
+ethical theories give inviolable rules that an automated agent can apply, without having to adjust
+the rules in changing situations or contexts. Moreover, because deontological theories focus on
+the action itself, they require relatively little data. A deontological moral judgement does not require
+as much information about context, consequences, or moral character as the other theories presented later in this
+section. All that matters is the action and some limited set of circumstances in which it is performed.
+I will later argue that, in the case of the specific deontological ethic that I implement (Kantian ethics), 
+the action has a very ``thin" representation that is space and memory efficient and requires little data
+about the external world.
 
-Not only does evaluating Kantian ethics only require evaluating a maxim, a maxim itself is an object
-with a thin representation for a computer, as contrasted to more complex objects like states of 
-affairs or moral character. Later in my project, I argue that a maxim can be represented simply as 
-a tuple of circumstances, act, and goal\footnote{For more, see Section What is a Maxim?}. This representation
-is simple and efficient, especially when compared to the representation of a causal chain or a state of 
-affairs or moral character. A maxim is a principle with a well-defined form, so representing a maxim
-to the computer merely requires capturing this form. This property not only reduces the computational complexity
-(in terms of time and space) of representing a maxim, it also make the system easier for human reasoners
-to interact with. A person crafting an input to a Kantian automated agent needs to reason about relatively
-simple units of evaluation, as opposed to the more complex features that consequentialism and virtue
-ethics reqire. I will make the comparision to consequentialism and virtue ethics explicit below.
+Like all ethical traditions, deontology has debates that any implementation of automated deontological
+ethics would need to resolve. Deontologists disagree about whether ethics should focus on agents and 
+prescribe them action or should focus on the patients or potential victims of actions and their rights.
+ Different deontological theories have different conceptions of what an action is, 
+from the actual physical act to the agent's mental state at the time of acting to the principle upon
+which the agent acted.
 
-I do not argue that Kantian ethics is the only theory possible to formalize, but instead that Kantian
-ethics is relatively easier to formalize. Indeed, like any ethical theory, the Kantian tradition contains 
-debates that philosophers disagree on. In this project, I assume stances on debates about
-what exactly constitutes the form of a maxim and the correct interpretation of the Formula of 
-Universal Law. Those who disagree with my stances will not trust the judgements of my system. Unlike
-consequentialism or virtue ethics, these debates are considered close to settled in the Kantian literature 
-\cite{ebelsduggan}. Because such debates are fewer and less controversial than those in virtue ethics
-or consequentialism, Kantian ethics is relatively easier to formalize.%
+While these debates are certainly open, ``if any philosopher is regarded as central
+to deontological moral theories, it is surely Immanuel Kant" \citep{sepdeont}. Out of the three ethical
+traditions considered in this section, deontology has the most central representative in the form of 
+Kant. Many modern deontologists claim to interpret Kant in a particular way, and thus agree on 
+his ethic as the foundation of their theory but disagree in how to interpret it. In this paper, I will 
+formalize Kantian ethics. Deontology's comparatively greater focus on Kant means that the choice of 
+Kant as a guiding figure will be less controversial to deontologists than, for example, the choice of Bentham
+as the guiding figure of consequentialism. Moreover, at the end of this section, I also argue that 
+internal debates in the part of Kantian ethics that I focus on tend to be less controversial than those
+in the consequentialist or virtue ethical traditions.
+
+I do not argue that deontology is the only tractable theory to formalize, but instead that it is 
+easier to formalize because it requires less data, is easily representable to a computer, and has fewer
+and less controversial open debates than consequentialism or virtue ethics. That being said, any ethical
+tradition has debates that an automated agent will need to take a stance on and deontological ethics
+is no exception. Those who disagree with my stances (e.g. non-Kantians) will not trust my system's
+judgements. This project is not irrelevant for them because it still serves as a case study in 
+the power of computational ethics, but Kantians will trust my system's moral judgements the most.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 A consequentialist ethical theory is, broadly speaking, any ethical theory that evaluates an action by evaluating 
-its consequences. \footnote{There is long debate about what exactly makes an ethical theory consequentialist \cite{consequentialismsep}. 
+its consequences.\footnote{There is long debate about what exactly makes an ethical theory consequentialist \citep{consequentialismsep}. 
 For this paper, I will focus on theories that place the moral worth of an act in its the consequences.} For example, 
 utilitarianism is a form of consequentialism in which the moral action 
-is the action that results in the best consequences or produces the most good \cite{utilsep}. The focus
-on the consequences of action distinguishes consequentialists from Kantians, who derive the moral worth
-of an action from the maxim that is acted on. Some debates in the consequentialist tradition include 
+is the action that results in the best consequences or produces the most good \citep{utilsep}. The focus
+on the consequences of action distinguishes consequentialists from deontologists, who derive the moral worth
+of an action from the action itself. Some debates in the consequentialist tradition include 
 which consequences of an action matter, what exactly constitutes a ``good" consequence, and how we can 
@@
 reasoning requires more knowledge
-about the state of the world than Kantian ethics. Under a naive version of consequentialism, evaluating 
+about the state of the world than deontology. Under a naive version of consequentialism, evaluating 
 an action requires perfect knowledge of all consequences following an action. This requires that an 
-automated ethical system somehow collect all of the infinite consquences following an action, a likely
-impossible task. Moreover, compiling this database of consequences requires 
+automated ethical system somehow collect all of the infinite consquences following an action, a 
+difficult, if not impossible, task. Moreover, compiling this database of consequences requires 
 answering difficult questions about which consequences were actually caused by an action.\footnote
@@
 
-These challenges also apply to human reasoners, so most consequentialists do not actually adopt the naivie
+These challenges also apply to human reasoners, so most consequentialists do not actually adopt the naive
 view that agents need to calculate all the consequences of their actions. Plausible strategies to avoid 
@@
 ``proximate cause" approach, which only holds the agent responsible for the immediate consequences of their 
-acts, but not for consequences resulting from others' voluntary responses to the agent's original act \cite{consequentialismsep}.
+acts, but not for consequences resulting from others' voluntary responses to the agent's original act \citep{consequentialismsep}.
 
 Even without understanding the details of these views, it is clear that they require 
-more data than Kantian ethics and scale poorly with the complexity of the act being evaluated. Even 
+more data than deontology and scale poorly with the complexity of the act being evaluated. Even 
 if we cut off the chain of causal reasoning at some point based on 
@@
 the first or immediate cause of an action requires knowledge about the state of the world before
-and after an action. Kantian ethics, on the other hand, requires only knowledge about the maxim, not 
-knowledge about the state of the world when the maxim is adopted. Consequentialism requires knowledge about 
-the situation in which the act is performed and following the act, whereas Kantian ethics merely requires 
+and after an action, in addition to knowledge about the action itself. Consequentialism requires 
+knowledge about 
+the situation in which the act is performed and following the act, whereas deontology mostly requires 
 knowledge about the act itself. For simple acts, collecting this data may not seem unreasonable, but as acts become
 more complex and affect more people, the computational time and space required to calculate and store
-their consequences increases. Kantian ethics, on the other hand, does not suffer this scaling
-challenge because maxims that affect 1 person and maxims that affect 1 million people share the same
+their consequences increases. Collecting this data is theoretically possible, but is labor and resource
+intensive. Deontology, on the other hand, does not suffer this scaling
+challenge because acts that affect 1 person and acts that affect 1 million people share the same
 representation.
@@
 and representing this data pose a technical challenge, it also creates a larger ``trusted code base" for 
-the automated system. Trusting my Kantian ethical reasoner merely requires trusting the logical implementation
-of the categorical imperative and the formulation of a maxim, but trusting a consequentialist ethical 
-reasoner requires trusting both the logical machinery that actually evaluates the act and the 
+the automated system. Trusting my deontological ethical reasoner merely requires trusting the logical implementation
+of the categorical imperative and the formulation of a maxim. Trusting a consequentialist ethical 
+reasoner, on the other hand, requires trusting both the logical machinery that actually evaluates the act and the 
 background/situational knowledge that serves as an input to this machinery.
@@
 The challenge of understanding and representing the circumstances of action is not unique to consequentialism,
-but is particularly acute for consequentialism. Kantian ethicists robustly debate which circumstances 
-of an action are ``morally relevant" and should be included in the formulation of the maxim.\footnote{Powers 
+but is particularly acute for consequentialism. Deontologists robustly debate which circumstances 
+of an action are ``morally relevant" and should be included in the formulation of the action.\footnote{ 
 \cite{powers} identifies this as a challenge for automating Kantian ethics and briefly sketches 
-solutions from O'Neill \citet{constofreason}, Silber \citet{silber}, and Rawls \citet{rawlsconstructivism}. } Those 
-using my system will need to automatically or manually formulate maxims, a process that involves 
-common-sense reasoning to determine which circumstances, act, and goal tuples the agent is adopting.
-\footnote{For more on the challenge of parsing of ethical dilemmas into maxims, see Section AI Ethics}
-Because Kantian ethics merely evaluates a single maxim, the surface of this debate is much smaller
+solutions from \citet{constofreason}, \citet{silber}, and \citet{rawlsconstructivism}. }
+Those using my system will need to use common-sense reasoning to determine which aspects of the circumstances
+in which the action is performed are morally relevant and should thus be represented to the computer.\footnote{For more on the challenge of 
+parsing of ethical dilemmas into maxims, see Section AI Ethics.} However, because deontology
+merely evaluates the action itself, the surface of this debate is much smaller
 than the debate about circumstances and consequences in a consequentialist system. An automated 
-consequentialist system must make such judgements about the act itself, the circumstances in which 
-it is performed, and the circumstances following the act. All ethical theories relativize
-their judgements to the situation in which an act is performed to some extent, but consequentialism
-requires far more knowledge about the world than Kantian ethics.%
+consequentialist system must make judgements about the act itself, the circumstances in which 
+it is performed, and the circumstances following the act. The ``trusted code base" is 
+smaller for deontology than for consequentialism. All ethical theories will require some set of 
+circumstances and common-sense knowledge as part of the trusted code base, but this set is larger for 
+consequentialism than for deontology.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 many different kinds of things are good for different reasons. For example, Moore values beauty and truth 
-and other pluralists value justice, love, and freedom \cite{moorepe}. Welfare utilitarians value a person's 
+and other pluralists value justice, love, and freedom \citep{moorepe}. Welfare utilitarians value a person's 
 welfare and utilitarians of right value states of affairs in which respect for some set of
-rights is maximized \cite{consequentialismsep}.
+rights is maximized \citep{consequentialismsep}.
 
@@
 which requires massive common-sense, increases room for doubting the system's judgements, and simplifies
-the judgements. This is a tractable problem, but is much more difficult than the Kantian task of formulating
-and evaluating a maxim.%
+the judgements. This is a tractable problem, but it is much more difficult than the deontological task of formulating
+and evaluating an action.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 The more complex the theory of the good, the more difficult this aggregation becomes. For example, 
-pluralistic theories struggle to explain how different kinds of value can be compared \cite{consequentialismsep}. 
+pluralistic theories struggle to explain how different kinds of value can be compared \citep{consequentialismsep}. 
 How do we compare one unit of beauty to one unit of pleasure? Subjective theories of the good, such 
@@
 consequentialist moral agent. Such an agent either needs to define an aggregation function, thus opening 
-the door to those who disagree with this definition, or needs to evaluate the goodness of entire states
+the door to critique from those who disagree with this definition, or needs to evaluate the goodness of entire states
 of affairs, which is a complex and data-intensive philosophical and technical challenge.%
@@
 None of the challenges described above are intractable or capture the full literature of 
-all variations of consequentialism. I do not argue that consequentialism is 
-impossible to automate. Instead, each of the challenges above requires that the developer 
+all variations of consequentialism. Instead, the challenges above require that the developer 
 ``plant certain flags" and take a stance on certain philosophical debates. Such debates are present in 
-any ethical theory, but consequentialism has more such points of difficulty than Kantian ethics and 
+any ethical theory, but consequentialism has more such points of difficulty than deontology and 
 is thus more difficult to automate.
 
-Because of its intuitive appeal, automated ethicists have tried to formalize consequentialism in the past.
-These efforts cannot escape the debates outlines above. For example, Abel et. al represent ethics as a
+Because of its intuitive appeal, computer scientists have tried to formalize consequentialism in the past.
+These efforts cannot escape the debates outlined above. For example, Abel et al. represent ethics as a
 Markov Decision Process (MDP), with reward functions customized to particular ethical dilemmas 
-\cite[3]{util1}. While this is a convenient representation, it either leaves unanswered or 
+\citep[3]{util1}. While this is a convenient representation, it either leaves unanswered or 
 takes implicit stances on the debates above. It assumes that consequences can be aggregated just as 
-reward is accumulated in an MDP. It leaves open the question of what the reward function is and thus 
+reward is accumulated in an MDP.\footnote{Generally, reward for an MDP is accumulated according to a 
+``discount factor" $\gamma < 1$, such that if $r_i$ is the reward at time $i$, the total reward is $\sum_{i=0}^{\infty}\gamma^i r_i$.} 
+It leaves open the question of what the reward function is and thus 
 leaves the theory of the good, arguably the defining trait of a particular consequentialist view, 
@@
 utilitarian automated reasoner chooses hedonism\footnote{Recall that hedonism views pleasure as good
-and pain as bad.} as the theory of the good \cite[2]{util2}. Again, their proposal assumes that pleasure and pain can be 
+and pain as bad.} as the theory of the good \citep[2]{util2}. Again, their proposal assumes that pleasure and pain can be 
 given numeric values and that these values can be aggregated with a simple sum, taking an implicit
@@
 that such actions would help cultivate. A virtue is commonly accepted as a character trait that 
-``makes its possessor good" \cite{vesep}. For example, under Aristotlean virtue ethics, virtues 
+``makes its possessor good" \citep{vesep}. For example, under Aristotlean virtue ethics, virtues 
 are the traits that enable human flourishing or fulfill the purpose of a human being. Many modern 
 virtue ethicists abandon Aristotle's notion of a ``purpose" of human beings, and instead define virtue 
-in terms of the characteristic activity of human beings (in ethical terms, not telelological terms) \cite{snow}. 
+in terms of the characteristic activity of human beings (in ethical terms, not telelological terms) \citep{snow}. 
 Just as consequentialists must offer a view of which consequences are good, virtue ethicists must offer some 
-theory of the virtues which presents and justifices a list of the virtues. Such theories vary
+theory of the virtues which presents and justifies a list of the virtues. Such theories vary
 from Aristotle's virtues of courage and temperance to the Buddhist virtue of 
-equanimity \cite{aristotle, mcrae}. Another theory is Sen's conception of the virtues as capabilites that create
-``effective opportunities to undertake the actions and activities" an agent wants to engage in \cite{robeyns}. 
+equanimity \citep{aristotle, mcrae}. Another theory is Sen's conception of the virtues as capabilites that create
+``effective opportunities to undertake the actions and activities" an agent wants to engage in \citep{robeyns}. 
 An automated virtue ethical agent will need to commit to a particular theory of the virtues, opening 
-itself up to criticism from those who disagree with this theory of the virtues. Unlike Kantian ethicists, 
-who generally agree on the meaning of the FUL, virtue ethicists robustly debate which character traits qualify as virtues.%
+itself up to criticism from those who disagree with this theory of the virtues. Any automated virtue
+ethical agent will need to justify its choice of virtues.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 Another difficulty with automating virtue ethics is that the unit of evaluation for a virtue ethical
-theory is often a person's entire moral character. While Kantians evaluate the maxim of an act and utilitarians
+theory is often a person's entire moral character. While deontologists evaluate the act itself and utilitarians
 evaluate the consequences of an act, virtue ethicists evaluate the actor's moral character and their 
@@
 not requires understanding the agent's character and disposition while acting. If states of affairs
-require complex representations, an agent's ethical character and disposition is even more difficult
-to represent. Consequentialism posed a data-collection problem in evaluating and representing states
+require complex representations, an agent's ethical character and disposition are even more difficult
+to represent to a computer. Consequentialism posed a data-collection problem in evaluating and representing states
 of affairs, but virtue ethics poses a conceptual problem about the formal nature of moral character.
 Formalizing the concept of character appears to require significant philosophical and computational
-progress, whereas Kantian ethics immediately presents a formal rule to implement.%
+progress, whereas deontology immediately presents a formal rule to implement.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 One potential appeal of virtue ethics is that many virtue ethical theories involve some form of 
-moral habit, which seems to suggest a machine learning approach. Artistotle, for example, argued 
-that cultivating virtuous action requires making such action habitual through moral education \cite{aristotle}. Under 
+moral habit, which seems to be amenable to a machine learning approach. Artistotle, for example, argued 
+that cultivating virtuous action requires making such action habitual through moral education \citep{aristotle}. Under 
 one view of virtue ethics, the virtuous act is what the virtuous person would do. Both of these ideas
@@
 theories seem to point towards a machine learning approach to computational ethics, in which ethics is 
-learned from a dataset of acts tagged as ethical or not ethical. Such approaches exist in the literature, 
-as in the Delphi system \cite{delphi}.
+learned from a dataset of acts tagged as virtuous or not virtuous.
 
 Just as prior work in consequentialism takes implicit or explicit stances on debates in consequentialist
-literature, so does work in machine learning-based virtue ethics. For example, the dataset that Delphi uses to learn ethical
-behavior contains implicit views on what the virtues are and how certain acts impact an agent's
-moral character. Because Delphi lacks a specified, explicit theory of virtue, it is impossible to 
-determine which traits the system implicitly classifies as virtues without manually examining the 
-dataset.
+literature, so does work in machine learning-based virtue ethics. For example, the training 
+dataset with acts labelled as virtuous or not virtuous will contain an implicit view on what the virtues
+are and how certain acts impact an agent's moral character. Because there is no canonical list of virtues
+that virtue ethicists accept, this implicit view will likely be controversial.
 
@@
 decisions to a human being, and often find patterns or correlations in datasets that don't actually 
-cohere with the trends and causes that a human being would identify \cite{puiutta}. While there is significant activity 
+cohere with the trends and causes that a human being would identify \citep{puiutta}. While there is significant activity 
 and progress in explainable machine learning, interactive theorem provers are designed to be explainable 
-at the outset. Indeed, Isabelle can even give the axioms and lemmas it used in constructing a proof, 
+at the outset. Indeed, Isabelle can show the axioms and lemmas it used in constructing a proof, 
 allowing a human being to reconstruct the proof independently if they wish. This is not an 
@@
 This does not preclude other uses of automated ethics, such as automated moral agents or hypothesis 
-generation for philosophy, but it does make computer-assisted ethical judgement difficult.%
+generation for philosophy, but it does make computer-assisted ethical judgement difficult.
+
+My arguments about theories of virtues and explanability are in the context of virtue ethics and 
+machine learning. Such arguments also apply to a broader class of projects in automated ethics 
+that use ``bottom-up" approaches, in which a system learns moral judgements from prior judgements, as 
+opposed to a top-down ethical theory. I will extend this argument to bottom-up approaches more
+generally in Section Related Work.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsubsection{Kantian Ethics%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
+As mentioned above, in this paper I focus on Kantian ethics, a specific branch of deontology. 
+Kant is widely seen as the most popular representative of deontology, so this choice is not surprising. 
+In this section, I will present a crash course on Kant's ethical theory and then explain why his particular
+theory is more amenable to formalization than consequentialist or virtue ethical theories.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+\textbf{Crash Course on Kantian Ethics}%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+Kant's theory is centered on practical reason, which is the kind of reason that we 
+use to decide what to do. In \emph{The Groundwork of the Metaphysics of Morals}, Kant's most influential 
+text on ethics, he explains that rational beings are unique because we can act ``in accordance with 
+the representations of laws" \cite[4:412]{groundwork}. In contrast, a ball thrown into the air acts 
+according to the laws of physics. It cannot ask itself, ``Should I fall back to the ground?" 
+It simply falls. A rational being, on the other hand, can ask, ``Should I act on this reason?" 
+As Korsgaard describes it, when choosing which desire to act on, ``it is as if there is something over 
+and above all of your desires, something which is you, and which chooses which desire to act on" \cite[100]{sources}. 
+Rational beings are set apart by this reflective capacity. A rational being's behavior is purposive and 
+their actions are guided by practical reason. They have reasons for acting, even when these reasons may be 
+opaque to them. This operation of practical reason is what Kant calls the will.
+
+The will operates by adopting, or willing, maxims, which are its perceived reasons for acting. Kant defines a maxim as 
+the ``subjective principle of willing," or the reason that the will \emph{subjectively} gives 
+to itself for acting \cite[16 footnote 1]{groundwork}. There is debate about what exactly must be 
+included in a maxim, but many philosophers agree that a maxim consists of some combination of circumstances, 
+act, and goal.\footnote{For more discussion of the definition of a maxim, see Section What Is a Maxim}
+One example of a maxim is ``when I am hungry, I will eat a doughnut in order to satisfy my sweet tooth." 
+When an agent wills this maxim, they decide to act on it. They commit themselves to the end in the maxim 
+(e.g. satisfying your sweet tooth). They represent their action, to themselves, as following the 
+principle given by this maxim. Because a maxim captures an agent's principle of action, Kant evaluates
+maxims as obligatory, prohibited, or permissible. He argues that certain maxims have a form or logical structure 
+that requires any rational agent to will them, and these maxims are obligatory.
+
+The form of an obligatory maxim is given by the categorical imperative. 
+An imperative is a command, such as ``Close the door" or ``Eat the doughnut in order to satisfy your 
+sweet tooth." An imperative is categorical if it holds unconditionally for all rational agents under all 
+circumstances. Kant argues that the moral law must be a categorical imperative, for otherwise it would 
+not have the force that makes it a moral law \cite[5]{groundwork}. In order for an imperative to be 
+categorical, it must be derived from the will's authority over itself. Our wills are autonomous, so 
+the only thing that can have unconditional authority over a rational will is 
+the rational will itself. In Velleman's version of this argument, he claims that no one else can tell you what 
+to do because you can always ask why you 
+should obey their authority. The only authority that you cannot question is the authority of your own 
+practical reason. To question this authority is to demand a reason for acting for reasons, which 
+concedes the authority of reason itself \cite[23]{velleman}. Therefore, the only possible candidates 
+for the categorical imperative are those rules that are required of the will because it is a will. 
+The categorical imperative must be a property of practical reason itself.
+
+Armed with this understanding of practical reason, Kant presents the categorical 
+imperative. He presents three ``formulations" or versions of the categorical imperative and goes on to 
+argue that all three formulations are equivalent. In this project, I focus on the first formulation,
+the Formula of Universal Law, but will briefly present the other two as well.\footnote{For more on this 
+choice, see Section Why FUL.}
+
+The first formulation of the categorical imperative is the
+Formula of Universal Law (FUL), which reads, ``act only according to that maxim through which you can 
+at the same time will that it become a universal law" \cite[34]{groundwork}. This formulation
+generates the universalizability test, which tests the moral value of a maxim by 
+imagining a world in which it becomes a universal law and attempting to will the maxim in that world.
+If there is a contradiction in willing the maxim in a world in which everyone universally wills the maxim,
+the maxim is prohibited. 
+Velleman presents a concise argument for the FUL. He argues that reason is universally shared among reasoners. For 
+example, all reasoners have equal access to the arithmetic logic that shows that ``2+2=4" \cite[29]{velleman}. The chain of 
+reasoning that makes this statement true is not specific to any person, but is universal across people. 
+Therefore, if I have sufficient reason to will a maxim, so does every other rational agent. There is 
+nothing special about the operation of my practical reason that other reasoners don't have access to. 
+Practical reason is shared, so in adopting a maxim, I implicitly state that all reasoners
+across time also have reason to adopt that maxim. Therefore, because I act on reasons, I must obey the 
+FUL. Notice that this fulfills the above criterion for a categorical imperative: the FUL is derived from 
+a property of practical reason itself and thus derives authority from the will's authority over itself, 
+as opposed to some external authority.
+
+The second formulation of the categorical imperative is the formula of humanity (FUH): ``So act that you use humanity, 
+in your own person, as well as in the person of any other, always at the same time as an end, never merely 
+as a means." \cite[41]{groundwork}. This formulation is often understood as requiring us to 
+acknowledge and respect the dignity of every other person. The third formulation of the categorical 
+imperative is the formula of autonomy (FOA), which Korsgaard summarizes in her introduction to the Groundwork 
+as, ``we should so act that we may think of ourselves as legislating universal laws through our 
+maxims" \cite[28]{korsgaardintro}. While closely related to the FUL, the FOA presents morality as the activity of 
+perfectly rational agents in an ideal ``kingdom of ends," guided by what Kant calls the ``laws of freedom."
+
+The above is not meant to serve as a full defense or articulation of Kant's ethical theory, as that is outside the scope
+of this thesis. Instead, I briefly reconstruct a sketch of Kant's ethical theory in the hopes 
+of offering context for the implementation of the FUL I present later in the thesis. Additionally, understanding 
+the structure of Kant's theory also reveals why it is an ideal candidate 
+for formalization.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+\textbf{Ease of Automation}%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+Kantian ethics is an especially candidate for formalization because the categorical imperative, particularly the FUL, 
+is a property of reason related to the form or structure of a maxim, or a formal principle of practical
+reason. It does not require any situational knowledge or contingent beyond the circumstances included
+in the maxim itself and thus requires far less contingent facts than other ethical theories.
+Instead, 
+it is purely a property of the proposed principle for action. This formalism makes Kantian ethics an 
+attractive candidate for formalization. While other ethical theories often rely on many facts about 
+the world or the actor, Kantian ethics simply relies on the form of a given maxim. A computer evaluating 
+a maxim doesn't require any knowledge about the world beyond what is contained in a maxim. A maxim 
+is the only input that the computer needs to make a moral judgement. Automating 
+Kantian ethics merely requires making the notion of a maxim precise and representing it to the computer. 
+This distinguishes Kantian ethics from consequentialism and virtue ethics, which, as I argued above, 
+require far more knowledge about the world or the agent to reach a moral decision.
+
+Not only does evaluating Kantian ethics focus on a maxim, a maxim itself is an object
+with a thin representation for a computer, as compares to more complex objects like states of 
+affairs or moral character. Later in my project, I argue that a maxim can be represented simply as 
+a tuple of circumstances, act, and goal.\footnote{For more, see Section What is a Maxim?} This representation
+is simple and efficient, especially when compared to the representation of a causal chain or a state of 
+affairs or moral character. A maxim is a principle with a well-defined form, so representing a maxim
+to the computer merely requires capturing this form. This property not only reduces the computational complexity
+(in terms of time and space) of representing a maxim, it also make the system easier for human reasoners
+to interact with. A person crafting an input to a Kantian automated agent needs to reason about relatively
+simple units of evaluation, as opposed to the more complex features that consequentialism and virtue
+ethics require. I will make the comparision to consequentialism and virtue ethics explicit below.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+\textbf{Difficulties in Automation}%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+My choices to interpret maxims and the Formula of Universal Law in a particular way represent debates
+in Kantian ethics over the meanings of these terms that I take a stance on. Another debate in Kantian 
+ethics is the role of ``common-sense" reasoning. Kantian ethics requires common-sense reasoning to 
+determine which circumstances are ``morally relevant" in the formulation of a maxim. Many misunderstandings
+in Kantian ethics are due to badly formulated maxims, so this question is important for an ethical 
+reasoner to answer. My system does not need to answer this question because I assume a well-formed
+maxim as input and apply the categorical imperative to this input, but if my system were ever to be used
+in a faully automated agent, answering this question would require significant computational and philosophical
+work. For more, see Section AI Ethics.
+
+Common-sense reasoning is also relevant in applying the universalizability test itself. Consider an example
+maxim tested using the Formula of Universal Law: ``When broke, I will falsely promise to repay a loan
+to get some quick cash." This maxim fails the universalizability test because in a world where everyone
+falsely promises to repay loans, no one will believe promises anymore, so the maxim will no longer serve
+its intended purpose (getting some quick cash). Making this judgement requires understanding enough about
+the system of promising to realize that it breaks down if everyone abuses it in this manner. This is a
+kind of common sense reasoning that an automated Kantian agent would need. This need is not unique to 
+Kantian ethics; consequentialists agents need this kind of common sense to determine the consequences of 
+an action and virtue ethical agents need this kind of common sense to determine which virtues an action
+reflects. Making any ethical judgement requires relatively robust conceptions of the action or situation
+at hand, falsely promising in this case. The advantage of Kantian ethics is that this is all the common 
+sense that it requires, whereas a consequentialist or virtue ethical agent will require much more. All
+moral theories evaluating falsely promising will a robust definition of the convention of promising, 
+but consequentialism and virtue ethics will also require additional information about consequences or character
+that Kantian ethics will not. Thus, although the need for common sense poses a challenge to automated
+Kantian ethics, this challenge is more acute for consequentialism or virtue ethics so Kantian ethics remains
+ within the closest reach of automation.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %:%53=26%:%
-%:%62=29%:%
-%:%74=31%:%
-%:%78=33%:%
-%:%79=34%:%
-%:%80=35%:%
-%:%81=36%:%
-%:%82=37%:%
-%:%83=38%:%
+%:%54=27%:%
+%:%55=28%:%
+%:%56=29%:%
+%:%57=30%:%
+%:%58=31%:%
+%:%59=32%:%
+%:%68=35%:%
+%:%80=37%:%
 %:%84=39%:%
@@
 %:%90=45%:%
-%:%91=46%:%
-%:%92=47%:%
-%:%93=48%:%
-%:%94=49%:%
-%:%95=50%:%
-%:%96=51%:%
-%:%97=52%:%
-%:%98=53%:%
-%:%99=54%:%
-%:%100=55%:%
-%:%101=56%:%
-%:%102=57%:%
-%:%103=58%:%
-%:%104=59%:%
-%:%105=60%:%
-%:%106=61%:%
-%:%107=62%:%
-%:%108=63%:%
-%:%109=64%:%
-%:%110=65%:%
-%:%111=66%:%
-%:%112=67%:%
-%:%113=68%:%
-%:%114=69%:%
-%:%115=70%:%
-%:%116=71%:%
-%:%117=72%:%
-%:%118=73%:%
-%:%119=74%:%
-%:%120=75%:%
-%:%121=76%:%
-%:%122=77%:%
-%:%123=78%:%
-%:%124=79%:%
-%:%125=80%:%
-%:%126=81%:%
-%:%127=82%:%
-%:%128=83%:%
-%:%129=84%:%
-%:%130=85%:%
-%:%131=86%:%
-%:%132=87%:%
-%:%133=88%:%
-%:%134=89%:%
-%:%135=90%:%
-%:%136=91%:%
-%:%137=92%:%
-%:%138=93%:%
-%:%139=94%:%
-%:%140=95%:%
-%:%141=96%:%
-%:%142=97%:%
-%:%143=98%:%
-%:%144=99%:%
-%:%145=100%:%
-%:%146=101%:%
-%:%147=102%:%
-%:%148=103%:%
-%:%149=104%:%
-%:%150=105%:%
-%:%151=106%:%
-%:%152=107%:%
-%:%153=108%:%
-%:%154=109%:%
-%:%158=111%:%
-%:%162=113%:%
-%:%163=114%:%
-%:%164=115%:%
-%:%165=116%:%
-%:%166=117%:%
-%:%167=118%:%
-%:%168=119%:%
-%:%169=120%:%
-%:%170=121%:%
-%:%171=122%:%
-%:%172=123%:%
-%:%173=124%:%
-%:%174=125%:%
-%:%175=126%:%
-%:%176=127%:%
-%:%177=128%:%
-%:%178=129%:%
-%:%179=130%:%
-%:%180=131%:%
-%:%181=132%:%
-%:%182=133%:%
-%:%183=134%:%
-%:%184=135%:%
-%:%185=136%:%
-%:%186=137%:%
-%:%187=138%:%
-%:%188=139%:%
-%:%189=140%:%
-%:%190=141%:%
-%:%191=142%:%
-%:%192=143%:%
-%:%193=144%:%
-%:%194=145%:%
-%:%203=148%:%
-%:%215=150%:%
-%:%216=151%:%
-%:%217=152%:%
-%:%218=153%:%
-%:%219=154%:%
-%:%220=155%:%
-%:%221=156%:%
-%:%222=157%:%
-%:%223=158%:%
-%:%227=160%:%
-%:%231=162%:%
-%:%232=163%:%
-%:%233=164%:%
-%:%234=165%:%
-%:%235=166%:%
-%:%236=167%:%
-%:%237=168%:%
-%:%238=169%:%
-%:%239=170%:%
-%:%240=171%:%
-%:%241=172%:%
-%:%242=173%:%
-%:%243=174%:%
-%:%244=175%:%
-%:%245=176%:%
-%:%246=177%:%
-%:%247=178%:%
-%:%248=179%:%
-%:%249=180%:%
-%:%250=181%:%
-%:%251=182%:%
-%:%252=183%:%
-%:%253=184%:%
-%:%254=185%:%
-%:%255=186%:%
-%:%256=187%:%
-%:%257=188%:%
-%:%258=189%:%
-%:%259=190%:%
-%:%260=191%:%
-%:%261=192%:%
-%:%262=193%:%
-%:%263=194%:%
-%:%264=195%:%
-%:%265=196%:%
-%:%266=197%:%
-%:%267=198%:%
-%:%268=199%:%
-%:%269=200%:%
-%:%270=201%:%
-%:%271=202%:%
-%:%272=203%:%
-%:%273=204%:%
-%:%274=205%:%
-%:%275=206%:%
-%:%276=207%:%
-%:%277=208%:%
-%:%278=209%:%
-%:%279=210%:%
-%:%280=211%:%
-%:%281=212%:%
-%:%282=213%:%
-%:%283=214%:%
-%:%284=215%:%
-%:%285=216%:%
-%:%286=217%:%
-%:%290=220%:%
-%:%294=222%:%
-%:%295=223%:%
-%:%296=224%:%
-%:%297=225%:%
-%:%298=226%:%
-%:%299=227%:%
-%:%300=228%:%
-%:%301=229%:%
-%:%302=230%:%
-%:%303=231%:%
-%:%304=232%:%
-%:%305=233%:%
-%:%306=234%:%
-%:%307=235%:%
-%:%308=236%:%
-%:%309=237%:%
-%:%310=238%:%
-%:%311=239%:%
-%:%312=240%:%
-%:%313=241%:%
-%:%314=242%:%
-%:%315=243%:%
-%:%316=244%:%
-%:%317=245%:%
-%:%318=246%:%
-%:%322=248%:%
-%:%326=250%:%
-%:%327=251%:%
-%:%328=252%:%
-%:%329=253%:%
-%:%330=254%:%
-%:%331=255%:%
-%:%332=256%:%
-%:%333=257%:%
-%:%334=258%:%
-%:%335=259%:%
-%:%336=260%:%
-%:%337=261%:%
-%:%338=262%:%
-%:%339=263%:%
-%:%340=264%:%
-%:%341=265%:%
-%:%342=266%:%
-%:%343=267%:%
-%:%344=268%:%
-%:%345=269%:%
-%:%346=270%:%
-%:%347=271%:%
-%:%348=272%:%
-%:%349=273%:%
-%:%350=274%:%
-%:%354=277%:%
-%:%358=279%:%
-%:%359=280%:%
-%:%360=281%:%
-%:%361=282%:%
-%:%362=283%:%
-%:%363=284%:%
-%:%364=285%:%
-%:%365=286%:%
-%:%366=287%:%
-%:%367=288%:%
-%:%368=289%:%
-%:%369=290%:%
-%:%370=291%:%
-%:%371=292%:%
-%:%372=293%:%
-%:%373=294%:%
-%:%374=295%:%
-%:%375=296%:%
-%:%376=297%:%
-%:%377=298%:%
-%:%378=299%:%
-%:%387=302%:%
-%:%399=304%:%
-%:%403=306%:%
-%:%404=307%:%
-%:%405=308%:%
-%:%406=309%:%
-%:%407=310%:%
-%:%408=311%:%
-%:%409=312%:%
-%:%410=313%:%
-%:%411=314%:%
-%:%412=315%:%
-%:%413=316%:%
-%:%414=317%:%
-%:%415=318%:%
-%:%416=319%:%
-%:%417=320%:%
-%:%421=322%:%
-%:%425=324%:%
-%:%426=325%:%
-%:%427=326%:%
-%:%428=327%:%
-%:%429=328%:%
-%:%430=329%:%
-%:%431=330%:%
-%:%432=331%:%
-%:%433=332%:%
-%:%434=333%:%
-%:%438=335%:%
-%:%442=337%:%
-%:%443=338%:%
-%:%444=339%:%
-%:%445=340%:%
-%:%446=341%:%
-%:%447=342%:%
-%:%448=343%:%
-%:%449=344%:%
-%:%450=345%:%
-%:%451=346%:%
-%:%452=347%:%
-%:%453=348%:%
-%:%454=349%:%
-%:%455=350%:%
-%:%456=351%:%
-%:%457=352%:%
-%:%458=353%:%
-%:%459=354%:%
-%:%460=355%:%
-%:%461=356%:%
-%:%462=357%:%
-%:%463=358%:%
-%:%464=359%:%
-%:%465=360%:%
-%:%466=361%:%
-%:%467=362%:%
-%:%468=363%:%
-%:%469=364%:%
-%:%470=365%:%
-%:%471=366%:%
-%:%472=367%:%
-%:%473=368%:%
-%:%474=369%:%
-%:%475=370%:%
-%:%476=371%:%
-%:%477=372%:%
-%:%478=373%:%
-%:%479=374%:%
-%:%480=375%:%
+%:%94=47%:%
+%:%98=49%:%
+%:%99=50%:%
+%:%100=51%:%
+%:%101=52%:%
+%:%102=53%:%
+%:%103=54%:%
+%:%104=55%:%
+%:%105=56%:%
+%:%106=57%:%
+%:%107=58%:%
+%:%108=59%:%
+%:%109=60%:%
+%:%110=61%:%
+%:%111=62%:%
+%:%112=63%:%
+%:%113=64%:%
+%:%114=65%:%
+%:%115=66%:%
+%:%116=67%:%
+%:%117=68%:%
+%:%118=69%:%
+%:%119=70%:%
+%:%120=71%:%
+%:%121=72%:%
+%:%122=73%:%
+%:%123=74%:%
+%:%124=75%:%
+%:%125=76%:%
+%:%126=77%:%
+%:%127=78%:%
+%:%128=79%:%
+%:%129=80%:%
+%:%130=81%:%
+%:%131=82%:%
+%:%132=83%:%
+%:%133=84%:%
+%:%142=87%:%
+%:%154=89%:%
+%:%155=90%:%
+%:%156=91%:%
+%:%157=92%:%
+%:%158=93%:%
+%:%159=94%:%
+%:%160=95%:%
+%:%161=96%:%
+%:%162=97%:%
+%:%166=99%:%
+%:%170=101%:%
+%:%171=102%:%
+%:%172=103%:%
+%:%173=104%:%
+%:%174=105%:%
+%:%175=106%:%
+%:%176=107%:%
+%:%177=108%:%
+%:%178=109%:%
+%:%179=110%:%
+%:%180=111%:%
+%:%181=112%:%
+%:%182=113%:%
+%:%183=114%:%
+%:%184=115%:%
+%:%185=116%:%
+%:%186=117%:%
+%:%187=118%:%
+%:%188=119%:%
+%:%189=120%:%
+%:%190=121%:%
+%:%191=122%:%
+%:%192=123%:%
+%:%193=124%:%
+%:%194=125%:%
+%:%195=126%:%
+%:%196=127%:%
+%:%197=128%:%
+%:%198=129%:%
+%:%199=130%:%
+%:%200=131%:%
+%:%201=132%:%
+%:%202=133%:%
+%:%203=134%:%
+%:%204=135%:%
+%:%205=136%:%
+%:%206=137%:%
+%:%207=138%:%
+%:%208=139%:%
+%:%209=140%:%
+%:%210=141%:%
+%:%211=142%:%
+%:%212=143%:%
+%:%213=144%:%
+%:%214=145%:%
+%:%215=146%:%
+%:%216=147%:%
+%:%217=148%:%
+%:%218=149%:%
+%:%219=150%:%
+%:%220=151%:%
+%:%221=152%:%
+%:%222=153%:%
+%:%223=154%:%
+%:%224=155%:%
+%:%225=156%:%
+%:%226=157%:%
+%:%227=158%:%
+%:%231=161%:%
+%:%235=163%:%
+%:%236=164%:%
+%:%237=165%:%
+%:%238=166%:%
+%:%239=167%:%
+%:%240=168%:%
+%:%241=169%:%
+%:%242=170%:%
+%:%243=171%:%
+%:%244=172%:%
+%:%245=173%:%
+%:%246=174%:%
+%:%247=175%:%
+%:%248=176%:%
+%:%249=177%:%
+%:%250=178%:%
+%:%251=179%:%
+%:%252=180%:%
+%:%253=181%:%
+%:%254=182%:%
+%:%255=183%:%
+%:%256=184%:%
+%:%257=185%:%
+%:%258=186%:%
+%:%259=187%:%
+%:%263=189%:%
+%:%267=191%:%
+%:%268=192%:%
+%:%269=193%:%
+%:%270=194%:%
+%:%271=195%:%
+%:%272=196%:%
+%:%273=197%:%
+%:%274=198%:%
+%:%275=199%:%
+%:%276=200%:%
+%:%277=201%:%
+%:%278=202%:%
+%:%279=203%:%
+%:%280=204%:%
+%:%281=205%:%
+%:%282=206%:%
+%:%283=207%:%
+%:%284=208%:%
+%:%285=209%:%
+%:%286=210%:%
+%:%287=211%:%
+%:%288=212%:%
+%:%289=213%:%
+%:%290=214%:%
+%:%291=215%:%
+%:%295=218%:%
+%:%299=220%:%
+%:%300=221%:%
+%:%301=222%:%
+%:%302=223%:%
+%:%303=224%:%
+%:%304=225%:%
+%:%305=226%:%
+%:%306=227%:%
+%:%307=228%:%
+%:%308=229%:%
+%:%309=230%:%
+%:%310=231%:%
+%:%311=232%:%
+%:%312=233%:%
+%:%313=234%:%
+%:%314=235%:%
+%:%315=236%:%
+%:%316=237%:%
+%:%317=238%:%
+%:%318=239%:%
+%:%319=240%:%
+%:%320=241%:%
+%:%329=244%:%
+%:%341=246%:%
+%:%345=248%:%
+%:%346=249%:%
+%:%347=250%:%
+%:%348=251%:%
+%:%349=252%:%
+%:%350=253%:%
+%:%351=254%:%
+%:%352=255%:%
+%:%353=256%:%
+%:%354=257%:%
+%:%355=258%:%
+%:%356=259%:%
+%:%357=260%:%
+%:%358=261%:%
+%:%359=262%:%
+%:%363=265%:%
+%:%367=267%:%
+%:%368=268%:%
+%:%369=269%:%
+%:%370=270%:%
+%:%371=271%:%
+%:%372=272%:%
+%:%373=273%:%
+%:%374=274%:%
+%:%375=275%:%
+%:%376=276%:%
+%:%380=278%:%
+%:%384=280%:%
+%:%385=281%:%
+%:%386=282%:%
+%:%387=283%:%
+%:%388=284%:%
+%:%389=285%:%
+%:%390=286%:%
+%:%391=287%:%
+%:%392=288%:%
+%:%393=289%:%
+%:%394=290%:%
+%:%395=291%:%
+%:%396=292%:%
+%:%397=293%:%
+%:%398=294%:%
+%:%399=295%:%
+%:%400=296%:%
+%:%401=297%:%
+%:%402=298%:%
+%:%403=299%:%
+%:%404=300%:%
+%:%405=301%:%
+%:%406=302%:%
+%:%407=303%:%
+%:%408=304%:%
+%:%409=305%:%
+%:%410=306%:%
+%:%411=307%:%
+%:%412=308%:%
+%:%413=309%:%
+%:%414=310%:%
+%:%415=311%:%
+%:%416=312%:%
+%:%417=313%:%
+%:%418=314%:%
+%:%419=315%:%
+%:%420=316%:%
+%:%421=317%:%
+%:%422=318%:%
+%:%423=319%:%
+%:%424=320%:%
+%:%425=321%:%
+%:%426=322%:%
+%:%435=325%:%
+%:%447=327%:%
+%:%448=328%:%
+%:%449=329%:%
+%:%450=330%:%
+%:%454=332%:%
+%:%458=334%:%
+%:%459=335%:%
+%:%460=336%:%
+%:%461=337%:%
+%:%462=338%:%
+%:%463=339%:%
+%:%464=340%:%
+%:%465=341%:%
+%:%466=342%:%
+%:%467=343%:%
+%:%468=344%:%
+%:%469=345%:%
+%:%470=346%:%
+%:%471=347%:%
+%:%472=348%:%
+%:%473=349%:%
+%:%474=350%:%
+%:%475=351%:%
+%:%476=352%:%
+%:%477=353%:%
+%:%478=354%:%
+%:%479=355%:%
+%:%480=356%:%
+%:%481=357%:%
+%:%482=358%:%
+%:%483=359%:%
+%:%484=360%:%
+%:%485=361%:%
+%:%486=362%:%
+%:%487=363%:%
+%:%488=364%:%
+%:%489=365%:%
+%:%490=366%:%
+%:%491=367%:%
+%:%492=368%:%
+%:%493=369%:%
+%:%494=370%:%
+%:%495=371%:%
+%:%496=372%:%
+%:%497=373%:%
+%:%498=374%:%
+%:%499=375%:%
+%:%500=376%:%
+%:%501=377%:%
+%:%502=378%:%
+%:%503=379%:%
+%:%504=380%:%
+%:%505=381%:%
+%:%506=382%:%
+%:%507=383%:%
+%:%508=384%:%
+%:%509=385%:%
+%:%510=386%:%
+%:%511=387%:%
+%:%512=388%:%
+%:%513=389%:%
+%:%514=390%:%
+%:%515=391%:%
+%:%516=392%:%
+%:%517=393%:%
+%:%518=394%:%
+%:%519=395%:%
+%:%520=396%:%
+%:%521=397%:%
+%:%522=398%:%
+%:%523=399%:%
+%:%524=400%:%
+%:%525=401%:%
+%:%526=402%:%
+%:%527=403%:%
+%:%528=404%:%
+%:%529=405%:%
+%:%530=406%:%
+%:%531=407%:%
+%:%532=408%:%
+%:%533=409%:%
+%:%534=410%:%
+%:%538=412%:%
+%:%542=414%:%
+%:%543=415%:%
+%:%544=416%:%
+%:%545=417%:%
+%:%546=418%:%
+%:%547=419%:%
+%:%548=420%:%
+%:%549=421%:%
+%:%550=422%:%
+%:%551=423%:%
+%:%552=424%:%
+%:%553=425%:%
+%:%554=426%:%
+%:%555=427%:%
+%:%556=428%:%
+%:%557=429%:%
+%:%558=430%:%
+%:%559=431%:%
+%:%560=432%:%
+%:%561=433%:%
+%:%562=434%:%
+%:%563=435%:%
+%:%564=436%:%
+%:%565=437%:%
+%:%566=438%:%
+%:%570=442%:%
+%:%574=444%:%
+%:%575=445%:%
+%:%576=446%:%
+%:%577=447%:%
+%:%578=448%:%
+%:%579=449%:%
+%:%580=450%:%
+%:%581=451%:%
+%:%582=452%:%
+%:%583=453%:%
+%:%584=454%:%
+%:%585=455%:%
+%:%586=456%:%
+%:%587=457%:%
+%:%588=458%:%
+%:%589=459%:%
+%:%590=460%:%
+%:%591=461%:%
+%:%592=462%:%
+%:%593=463%:%
+%:%594=464%:%
+%:%595=465%:%
+%:%596=466%:%
+%:%597=467%:%
+%:%598=468%:%
+%:%599=469%:%
+%:%600=470%:%

### 2021-11-17 paper/output/document/paper33.tex
what am i doing

@@
 \caption{Table indicating which goals are met by the naive formalization, Kroy's formalization, and 
-the custom formalization respectively..} \label{fig:goalstable}
+the custom formalization respectively.} \label{fig:goalstable}
 \end{figure}

### 2021-11-17 paper/output/document/paper41.tex
what am i doing

@@
 %
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\isatagdocument
-%
-\isamarkupsubsection{Application Tests%
-}
-\isamarkuptrue%
-%
-\endisatagdocument
-{\isafolddocument}%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\begin{isamarkuptext}%
-As with the naive formalization and Kroy's formalization, I will apply my testing framework to 
-my custom formalization of the FUL. I will begin with some basic application tests. In these tests, 
-I specify particular maxims as constants with no properties and gradually add properties to understand 
-how the system handles different kinds of maxims.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-I will show that the maxim, ``When strapped for cash, falsely promise to pay your friend back
-to get some easy money." is prohibited. This example is due to Korsgaard and she uses it to highlight 
-the strength of her preferred interpretation of the FUL, the practical contradiction interpretation \cite{KorsgaardFUL}.
-There are two possible readings of this maxim, and I will show that my formalization can handle both. 
-Under the first reading, the act of falsely promising is read as
-as entering a pre-existing, implicit, social system of promising with no intention of upholding your 
-promise. Under the second reading, the act of falsely promising is equivalent to uttering the worlds 
-``I promise X" without intending to do X. The differences between these readings lies in the difference 
-between promising as an act with meaning in a larger social structure and the utterance ``I promise."
-
-Under the first reading, the maxim fails because falsely promising is no longer possible in a world where 
-everyone everyone does so. This is how the logical contradiction interpretation reads this maxim—falsely 
-promising is no longer possible when universalized because the institution of promising breaks down. 
-The practical contradiction view also prohibits this maxim because if falsely promising is not longer 
-possible, then it is no longer an effective way to achieve the end of getting some money. Below I 
-define some logical tools to formalize this reading of this maxim.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{consts}\isamarkupfalse%
-\ when{\isacharunderscore}strapped{\isacharunderscore}for{\isacharunderscore}cash{\isacharcolon}{\isacharcolon}t\isanewline
-%
-\isamarkupcmt{Constant representing the circumstances ``when strapped for cash." Recall that the type of circumstances 
-is a term because circumstances can be true or false at a world.%
-}\isanewline
-\isacommand{consts}\isamarkupfalse%
-\ falsely{\isacharunderscore}promise{\isacharcolon}{\isacharcolon}os\isanewline
-%
-\isamarkupcmt{Constant representing the act ``make a false promise to pay a loan back." Recall that the type of
-an act is an open sentence because the sentence ``subject s performs act a" can be true or false at a world.%
-}\isanewline
-\isacommand{consts}\isamarkupfalse%
-\ to{\isacharunderscore}get{\isacharunderscore}easy{\isacharunderscore}cash{\isacharcolon}{\isacharcolon}t\isanewline
-%
-\isamarkupcmt{Constant representing the goal ``to get some money." Recall that the type of a goal 
-is a term because a goal can be true or false at a world depending on whether it is achieved or not.%
-}\isanewline
-\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ false{\isacharunderscore}promising{\isacharcolon}{\isacharcolon}maxim\ \isakeyword{where}\ \isanewline
-{\isachardoublequoteopen}false{\isacharunderscore}promising\ {\isasymequiv}\ {\isacharparenleft}when{\isacharunderscore}strapped{\isacharunderscore}for{\isacharunderscore}cash{\isacharcomma}\ falsely{\isacharunderscore}promise{\isacharcomma}\ to{\isacharunderscore}get{\isacharunderscore}easy{\isacharunderscore}cash{\isacharparenright}{\isachardoublequoteclose}\isanewline
-%
-\isamarkupcmt{Armed with the circumstances, act, and goal above, I can define the example maxim as a tuple.%
-}%
-\begin{isamarkuptext}%
-The logical objects above are ``empty," in the sense that I haven't specified any of their 
-relevant properties. I will define these properties as assumptions and will show that, if the maxim 
-above satisfies the assumed properties, it is prohibited.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ everyone{\isacharunderscore}can{\isacharprime}t{\isacharunderscore}lie\ \isakeyword{where}\ \isanewline
-{\isachardoublequoteopen}everyone{\isacharunderscore}can{\isacharprime}t{\isacharunderscore}lie\ {\isasymequiv}\ {\isasymforall}w{\isachardot}\ {\isasymnot}\ {\isacharparenleft}{\isasymforall}s{\isachardot}\ falsely{\isacharunderscore}promise{\isacharparenleft}s{\isacharparenright}\ w{\isacharparenright}\ {\isachardoublequoteclose}\isanewline
-%
-\isamarkupcmt{Under this reading, the problem with this maxim is that everyone can't
-falsely promise simultaneously because the institution of promising will break down. It's probably 
-possible to say something stronger than this (i.e. that if enough but not necessarily all people
-falsely promise promising is no longer possible), but for my purposes this will suffice. The above 
-formula reads, ``At all worlds, it is not the case that everyone falsely promises."%
-}\isanewline
-\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ circumstances{\isacharunderscore}hold\ \isakeyword{where}\ \isanewline
-{\isachardoublequoteopen}circumstances{\isacharunderscore}hold\ {\isasymequiv}\ {\isasymforall}w{\isachardot}\ when{\isacharunderscore}strapped{\isacharunderscore}for{\isacharunderscore}cash\ w{\isachardoublequoteclose}\isanewline
-%
-\isamarkupcmt{This assumption narrows our scope of consideration to worlds where the circumstances of 
-being strapped for cash hold. This is important because, at worlds where the circumstances do not hold, 
-a maxim is trivially effective (since it's never acted on) and thus trivially universalizable. This 
-assumption also makes practical sense; when evaluating a maxim, an agent would care about it specifically
-at worlds where the circumstances hold, since these are the worlds where the maxim actually prescribes action.%
-}\isanewline
-\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ example{\isacharunderscore}is{\isacharunderscore}well{\isacharunderscore}formed\ \isakeyword{where}\ \isanewline
-{\isachardoublequoteopen}example{\isacharunderscore}is{\isacharunderscore}well{\isacharunderscore}formed\ {\isasymequiv}\ {\isasymforall}s{\isachardot}\ {\isasymTurnstile}\ {\isacharparenleft}well{\isacharunderscore}formed\ false{\isacharunderscore}promising\ s{\isacharparenright}{\isachardoublequoteclose}\isanewline
-%
-\isamarkupcmt{This assumption states that the maxim of falsely promising is well-formed. This breaks down into
-two individual assumptions. First, being strapped for cash can't imply falsely promising, which is plausible
-because many people won't falsely promise under conditions of poverty. Second, being strapped for cash
-can't imply getting ready cash, which is also plausible because people often fail to secure cash even 
-when they need it.%
-}%
-\begin{isamarkuptext}%
-Putting it all together, I want to show that if the three assumptions justified above hold, then 
-the constructed maxim is prohibited. Below is the proof%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ lying{\isacharunderscore}bad{\isacharunderscore}{\isadigit{1}}{\isacharcolon}\isanewline
-\ \ \isakeyword{assumes}\ everyone{\isacharunderscore}can{\isacharprime}t{\isacharunderscore}lie\isanewline
-\ \ \isakeyword{assumes}\ circumstances{\isacharunderscore}hold\isanewline
-\ \ \isakeyword{assumes}\ example{\isacharunderscore}is{\isacharunderscore}well{\isacharunderscore}formed\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}s{\isachardot}\ {\isasymTurnstile}\ {\isacharparenleft}prohibited\ false{\isacharunderscore}promising\ s{\isacharparenright}{\isachardoublequoteclose}\isanewline
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isatagproof
-\isacommand{proof}\isamarkupfalse%
-{\isacharminus}\isanewline
-\ \ \isacommand{have}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isasymforall}s{\isachardot}\ not{\isacharunderscore}universalizable\ false{\isacharunderscore}promising\ s{\isachardoublequoteclose}\isanewline
-\ \ \ \ \isacommand{by}\isamarkupfalse%
-\ {\isacharparenleft}simp\ add{\isacharcolon}\ assms{\isacharparenleft}{\isadigit{1}}{\isacharparenright}\ assms{\isacharparenleft}{\isadigit{2}}{\isacharparenright}{\isacharparenright}\isanewline
-%
-\isamarkupcmt{I manually broke the proof into this intermediate lemma and the conclusion, and then Sledgehammer 
-automatically found a proof.%
-}\isanewline
-\ \ \isacommand{thus}\isamarkupfalse%
-\ {\isacharquery}thesis\isanewline
-\ \ \ \ \isacommand{using}\isamarkupfalse%
-\ FUL\ assms{\isacharparenleft}{\isadigit{3}}{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
-\ blast\ \isanewline
-\isacommand{qed}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-Under the second reading of this maxim, the act ``falsely promising" refers to uttering the 
-sentence ``I promise to do X" with no intention of actually doing X\footnote{Note that under this 
-reading, the maxim isn't prohibited under the logical contradiction interpretation because making an 
-utterance is still possible even if eveyrone else makes that utterance. I will discuss this in detail 
-later in this section in the context of the difference between natural and conventional acts.}. 
-Under this reading, the practical contradiction interpretation prohibits this maxim because, in a world 
-where false promising is universalized, no one believes promises anymore, so the utterance is no longer 
-an effective way to get money. Below I formalize this reading of this maixm.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{consts}\isamarkupfalse%
-\ believed{\isacharcolon}{\isacharcolon}os\ \isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ false{\isacharunderscore}promising{\isacharunderscore}not{\isacharunderscore}believed\ \isakeyword{where}\ \isanewline
-{\isachardoublequoteopen}false{\isacharunderscore}promising{\isacharunderscore}not{\isacharunderscore}believed\ {\isasymequiv}\ {\isasymforall}w\ s{\isachardot}\ {\isacharparenleft}falsely{\isacharunderscore}promise{\isacharparenleft}s{\isacharparenright}\ w\ {\isasymlongrightarrow}\ {\isasymnot}\ believed{\isacharparenleft}s{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
-%
-\isamarkupcmt{This abbreviation formalizes the idea that if everyone falsely promises, then no one is believed
-when promising.%
-}\isanewline
-\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ need{\isacharunderscore}to{\isacharunderscore}be{\isacharunderscore}believed\ \isakeyword{where}\ \isanewline
-{\isachardoublequoteopen}need{\isacharunderscore}to{\isacharunderscore}be{\isacharunderscore}believed\ {\isasymequiv}\ {\isasymforall}w\ s{\isachardot}\ {\isacharparenleft}{\isasymnot}\ believed{\isacharparenleft}s{\isacharparenright}\ w\ {\isasymlongrightarrow}\ \isactrlbold {\isasymnot}{\isacharparenleft}{\isacharparenleft}falsely{\isacharunderscore}promise\ s{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ to{\isacharunderscore}get{\isacharunderscore}easy{\isacharunderscore}cash{\isacharparenright}w{\isacharparenright}{\isachardoublequoteclose}\isanewline
-%
-\isamarkupcmt{This abbreviation formalizes the idea that if a promise is not believed, then it is not an effective
-way of getting easy cash.%
-}\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ falsely{\isacharunderscore}promising{\isacharunderscore}bad{\isacharunderscore}{\isadigit{2}}{\isacharcolon}\isanewline
-\ \ \isakeyword{assumes}\ false{\isacharunderscore}promising{\isacharunderscore}not{\isacharunderscore}believed\isanewline
-\ \ \isakeyword{assumes}\ need{\isacharunderscore}to{\isacharunderscore}be{\isacharunderscore}believed\isanewline
-%
-\isamarkupcmt{The above two assumptions are specific to this reading and justified above.%
-}\isanewline
-\ \ \isakeyword{assumes}\ circumstances{\isacharunderscore}hold\isanewline
-\ \ \isakeyword{assumes}\ example{\isacharunderscore}is{\isacharunderscore}well{\isacharunderscore}formed\isanewline
-%
-\isamarkupcmt{These two assumptions applied to the first reading as well and were justified there.%
-}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}s{\isachardot}\ {\isasymTurnstile}\ {\isacharparenleft}prohibited\ false{\isacharunderscore}promising\ s{\isacharparenright}{\isachardoublequoteclose}\isanewline
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isatagproof
-\isacommand{proof}\isamarkupfalse%
-{\isacharminus}\isanewline
-\ \ \isacommand{have}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isasymforall}s{\isachardot}\ not{\isacharunderscore}universalizable\ false{\isacharunderscore}promising\ s{\isachardoublequoteclose}\isanewline
-\ \ \ \ \isacommand{using}\isamarkupfalse%
-\ assms{\isacharparenleft}{\isadigit{1}}{\isacharparenright}\ assms{\isacharparenleft}{\isadigit{2}}{\isacharparenright}\ assms{\isacharparenleft}{\isadigit{3}}{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
-\ auto\isanewline
-\ \ \isacommand{thus}\isamarkupfalse%
-\ {\isacharquery}thesis\isanewline
-\ \ \ \ \isacommand{using}\isamarkupfalse%
-\ FUL\ assms{\isacharparenleft}{\isadigit{4}}{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
-\ blast\isanewline
-\isacommand{qed}\isamarkupfalse%
-\isanewline
-%
-\isamarkupcmt{With some help, Isabelle is able to show that the maxim is prohibited under this reading as well.%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-This example demonstrates that my formalization is able to correctly prohibit this maxim, regardless
-of its reading. This is additionally important because the two readings of this maxim represent reading 
-the act as either a conventional or natural action, so my intrepretation can correctly handle both kinds
-of actions. Korsgaard draws a distinction between conventional acts and natural acts. Conventional acts 
-exist within a practice, which is "comprised of certain rules, and its existence (where it is not embodied in 
-an institution with sanctions) consists in the general acknowledgement and following of those rules" 
-\cite[10]{KorsgaardFUL}. For example, promising is a conventional act because it only exists as a 
-practice. Murder, on the other hand, is an example of a natural act because its existence only depends
-on the laws of nature\cite[11]{KorsgaardFUL}.
-
-This distinction is important because Korsgaard argues that only the practical contradiction view can 
-satisfactorily explain the wrongness of certain natural acts like murder\footnote{For more discussion 
-of Korsgaard's argument for the practical contradiction view, see Section Philosophical Writing}. 
-The practical contradiction view is thus stronger than the logical contradiction view because it can 
-explain the wrongness of both conventional and natural acts.
-
-The fact that my interpretation can correctly show the wrongness of both conventional and natural acts
-is evidence for its correctness as a formalization of the practical contradiction interpretation. 
-The first reading of the example maxim reads the act 
-``making a false promise" as entering into an agreement within a socially established system of promising. 
-This is clearly a conventional act, and because it is a conventional act, it is not just contradictory
-when universalized but literally impossible because the practice breaks down. I capture this idea in the 
-assumption \isa{everyone{\isacharunderscore}can{\isacharprime}t{\isacharunderscore}lie\ {\isasymequiv}\ {\isasymforall}w{\isachardot}\ {\isasymnot}\ {\isacharparenleft}{\isasymforall}s{\isachardot}\ falsely{\isacharunderscore}promise\ s\ w{\isacharparenright}}, which states that, at all worlds, not everyone can falsely promise since
-otherwise the practice of promising would break down. The second reading, on the other hand, reads the 
-act of making a false promise as uttering the statement ``I promise to pay you back," while never intending 
-to fulfill this promise. This is a natural act because the act of uttering a sentence does not rely 
-on any conventions, merely the laws of nature governing how your mouth and vocal cords behave\footnote{
-Linguistic relativists may take issue with this claim and may argue that if the English language had 
-never developed, then making this utterance would be impossible. Even if this is true, the laws of 
-nature itself would not prohibit making the sounds corresponding to the English pronounciation of 
-this phrase, so the act would still not be impossible in the way that a conventional act can be.}
-
-I show above that my formalization shows the wrongness of this maxim under both readings. Under the 
-first reading, promising becomes impossible, so both the logical and 
-practical contradiction interpretations prohibit the maxim. Under the second reading, promising is still
-possible, but becomes ineffective because people no longer interpret the utterance as creating a commitment.
-Under this view, only the practical contradiction interpretation succeeds in prohibiting the maxim. Thus, 
-not only does my formalization likely capture the practical contradiction interpretation (as opposed to 
-the teleological or logical contradiction interpretations), it also adequately handles both natural 
-and conventional acts.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-I can also use Isabelle to confirm that the two readings are different. If they were the same, 
-we would expect the assumptions corresponing to each to be equivalent. The RHS of the lemma below represents 
-the second reading and the LHS represents the first reading.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ readings{\isacharunderscore}are{\isacharunderscore}equivalent{\isacharcolon}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}false{\isacharunderscore}promising{\isacharunderscore}not{\isacharunderscore}believed\ {\isasymand}\ need{\isacharunderscore}to{\isacharunderscore}be{\isacharunderscore}believed\ {\isasymequiv}\ everyone{\isacharunderscore}can{\isacharprime}t{\isacharunderscore}lie{\isachardoublequoteclose}\isanewline
-\ \ \isacommand{nitpick}\isamarkupfalse%
-{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{oops}\isamarkupfalse%
-\isanewline
-%
-\isamarkupcmt{Nitpick finds a counterexample, showing that the two readings are different.
-\color{blue}
-Nitpick found a counterexample for card i = 1 and card s = 1:
-
-  Empty assignment
-\color{black}%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-This completes the application tests for my formalization. I showed that my formalization correctly 
-handles an example from Korsgaard with two possible interpretations and also sufficiently handles both 
-conventional and natural acts.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\isatagdocument
-%
-\isamarkupsubsection{Metaethical Tests%
-}
-\isamarkuptrue%
-%
-\endisatagdocument
-{\isafolddocument}%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\begin{isamarkuptext}%
-Recall that metaethical tests test formal properties of the system that apply to any maxim, not 
-just those specified in the application tests. In this section I adapt the metaethical tests developed 
-in previous sections to my formalization of the categorical imperative. I preserved the philosophical 
-goal of each test but modified them to test the stronger, richer notion of a maxim.
-
-The first set of tests consider how obligation generalizes, first across worlds and then across
-people. As expected, the tests below show that both wrongness (prohibition) and rightness (obligation)
-generalize across both worlds and people. In other words, if something is obligated at some world, it 
-is obligated at every world and if something is obligated for some person, then it is obligated for 
-every person.
-
-Generalization across worlds is a consequence of the fact that my interpretation does not make use of the 
-modal nature of DDL. In particular, I do not use any property of the world when prescribing obligations 
-at that world.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ wrong{\isacharunderscore}if{\isacharunderscore}wrong{\isacharunderscore}for{\isacharunderscore}someone{\isacharcolon}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}w{\isachardot}\ {\isasymforall}c{\isacharcolon}{\isacharcolon}t{\isachardot}\ {\isasymforall}g{\isacharcolon}{\isacharcolon}t{\isachardot}\ {\isasymexists}s{\isacharcolon}{\isacharcolon}s{\isachardot}\ O{\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}W\ {\isacharparenleft}c{\isacharcomma}\ M{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ {\isacharbar}\ c{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ \ O{\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}W\ {\isacharparenleft}c{\isacharcomma}\ M{\isacharcomma}\ g{\isacharparenright}\ p{\isacharparenright}\ {\isacharbar}\ c{\isacharbraceright}\ w{\isacharparenright}\ {\isachardoublequoteclose}\isanewline
-%
-\isadelimproof
-\ \ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{by}\isamarkupfalse%
-\ blast%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-\isanewline
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ right{\isacharunderscore}if{\isacharunderscore}right{\isacharunderscore}for{\isacharunderscore}someone{\isacharcolon}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}w{\isachardot}\ {\isasymforall}c{\isacharcolon}{\isacharcolon}t{\isachardot}\ {\isasymforall}g{\isacharcolon}{\isacharcolon}t{\isachardot}\ {\isasymexists}s{\isacharcolon}{\isacharcolon}s{\isachardot}\ O{\isacharbraceleft}W\ {\isacharparenleft}c{\isacharcomma}\ M{\isacharcomma}\ g{\isacharparenright}\ s\ {\isacharbar}\ c{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ \ O{\isacharbraceleft}W\ {\isacharparenleft}c{\isacharcomma}\ M{\isacharcomma}\ g{\isacharparenright}\ p\ {\isacharbar}\ c{\isacharbraceright}\ w{\isacharparenright}\ {\isachardoublequoteclose}\isanewline
-%
-\isadelimproof
-\ \ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{by}\isamarkupfalse%
-\ blast%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-\isanewline
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ wrong{\isacharunderscore}if{\isacharunderscore}wrong{\isacharunderscore}somewhere{\isacharcolon}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}c\ g{\isachardot}\ {\isasymexists}w{\isadigit{1}}{\isachardot}\ O{\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}W\ {\isacharparenleft}c{\isacharcomma}\ M{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ {\isacharbar}\ c{\isacharbraceright}\ w{\isadigit{1}}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}w{\isadigit{2}}{\isachardot}\ \ O{\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}W\ {\isacharparenleft}c{\isacharcomma}\ M{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ {\isacharbar}\ c{\isacharbraceright}\ w{\isadigit{2}}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-%
-\isadelimproof
-\ \ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{by}\isamarkupfalse%
-\ blast%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-\isanewline
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ right{\isacharunderscore}if{\isacharunderscore}right{\isacharunderscore}somewhere{\isacharcolon}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}c\ g{\isachardot}\ {\isasymexists}w{\isadigit{1}}{\isachardot}\ O{\isacharbraceleft}W\ {\isacharparenleft}c{\isacharcomma}\ M{\isacharcomma}\ g{\isacharparenright}\ s\ {\isacharbar}\ c{\isacharbraceright}\ w{\isadigit{1}}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}w{\isadigit{2}}{\isachardot}\ \ O{\isacharbraceleft}W\ {\isacharparenleft}c{\isacharcomma}\ M{\isacharcomma}\ g{\isacharparenright}\ s\ {\isacharbar}\ c{\isacharbraceright}\ w{\isadigit{2}}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-%
-\isadelimproof
-\ \ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{by}\isamarkupfalse%
-\ blast%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-As expected, obligation generalizes across people and worlds. In the next set of tests, I will 
-analyze basic properties of permissibility, obligation, and prohibition.
-
-First, I verify that the logic allows
-for permissible maxims, as this is a problem that prior iterations ran into. Below, I use Nitpick to 
-find a model in which there is a circumstance, act, goal tuple that is permissible but not 
-obligated at some world.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ permissible{\isacharcolon}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O{\isacharbraceleft}{\isacharparenleft}W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ {\isacharbar}\ c{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O{\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ {\isacharbar}\ c{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
-\ \ \isacommand{nitpick}\isamarkupfalse%
-\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharbrackright}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{oops}\isamarkupfalse%
-\isanewline
-%
-\isamarkupcmt{\color{blue}Nitpick found a model for card i = 1 and card s = 1:
-
-  Free variables:
-    a = ($\lambda x. \_$)($s_1$ := ($\lambda x. \_$)($i_1$ := False))
-    c = ($\lambda x. \_$)($i_1$ := False)
-    g = ($\lambda x. \_$)($i_1$ := False)
-    s = $s_1$\color{black}
-Recall that Nitpick is a model checker that finds models making certain formulae true or false. In this 
-case, Nitpick finds a model satisfying the given formula (which simply requires that the sentence 
-``s wills (c, a, g)'' is permissible but not obligator). This model consists of the above specifications 
-of a, c, g, and s.%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-I also expect that any arbitrary maxim should be either permissible or prohibited, since all 
-acts are either permissible or prohibited.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ perm{\isacharunderscore}or{\isacharunderscore}prohibited{\isacharcolon}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}permissible\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ \isactrlbold {\isasymor}\ {\isacharparenleft}prohibited\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
-%
-\isadelimproof
-\ \ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{by}\isamarkupfalse%
-\ blast\isanewline
-%
-\isamarkupcmt{This simple test passes immediately by the definitions of  permissible and prohibited.%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-Obligation should be strictly stronger than permissibility. In other words, if a maxim is 
-obligated at a world, it should be permissible at that world. Below I test this property.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ obligated{\isacharunderscore}then{\isacharunderscore}permissible{\isacharcolon}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}O{\isacharbraceleft}W{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharbar}c{\isacharbraceright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isacharparenleft}permissible\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ {\isacharparenright}\ s{\isacharparenright}{\isacharparenright}\ w\ {\isachardoublequoteclose}\isanewline
-%
-\isadelimproof
-\ \ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{using}\isamarkupfalse%
-\ no{\isacharunderscore}contradictions\ \isacommand{by}\isamarkupfalse%
-\ auto\isanewline
-%
-\isamarkupcmt{This test passes and Isabelle is able to find a proof for the fact that all obligatory maxims are 
-also permissible.%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-The above test failed under Kroy's formalization of the categorical imperative and is thus evidence 
-that my formalization improves upon Kroy's. Interestingly, this new test passes because of the additional
-added axiom that prohibits contradictory obligations (recall that Kroy's formalization allowed contradictory
-obligations).%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-Next, I will test if the formalization allows for vacuous obligations or modal collapse. These 
-tests are sanity checks confirmed that the obligation operator is doesn't collapse. First, I will check 
-that any arbitrary term isn't obligated.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ arbitrary{\isacharunderscore}obligations{\isacharcolon}\isanewline
-\ \ \isakeyword{fixes}\ c\ A{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}O{\isacharbraceleft}A{\isacharbar}c{\isacharbraceright}\ w{\isachardoublequoteclose}\isanewline
-\ \ \isacommand{nitpick}\isamarkupfalse%
-\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharequal}true{\isacharcomma}\ falsify{\isacharbrackright}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{oops}\isamarkupfalse%
-\isanewline
-%
-\isamarkupcmt{This test passes—Nitpick finds a model where A isn't obligated in circumstances c.
-\color{blue} Nitpick found a counterexample for card i = 1 and card s = 2:
-
-  Free variables:
-    A = ($\lambda x. \_$)($i_1$ := True)
-    c = ($\lambda x. \_$)($i_1$ := False) \color{blue}
-Previous iterations of this test used the monadic obligation operator, which tests the term in the 
-context ``True" (equivalently the set of all worlds since True holds everywhere). In this iteration, 
-I test the term in a context c, because my formalization uses the dyadic obligation operator and must 
-thus specify circumstances.%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-This is exactly the expected result. Any arbitrary action $A$ isn't obligated. A slightly 
-        stronger property is ``modal collapse," or whether or not `$A$ happens' implies `$A$ is obligated'. 
-The proposition below should be falsifiable.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ modal{\isacharunderscore}collapse{\isacharcolon}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ w{\isacharparenright}\ {\isasymlongrightarrow}\ O{\isacharbraceleft}W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharbar}c{\isacharbraceright}\ w{\isachardoublequoteclose}\isanewline
-\ \ \isacommand{nitpick}\isamarkupfalse%
-\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharequal}true{\isacharcomma}\ falsify{\isacharbrackright}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{oops}\isamarkupfalse%
-\isanewline
-%
-\isamarkupcmt{Nitpick finds a counterexample, so willing doesn't imply obligation, so this test passes. 
-\color{blue}Nitpick found a counterexample for card i = 1 and card s = 2:
-
-  Free variables:
-    a = ($\lambda x. \_$)($s_1$ := ($\lambda x. \_$)($i_1$ := False), $s_2$ := ($\lambda x. \_$)($i_1$ := False))
-    c = ($\lambda x. \_$)($i_1$ := False)
-    g = ($\lambda x. \_$)($i_1$ := False)
-    s = $s_2$
-    w = $i_1$\color{black}
-Once again, I modify this test to use the dyadic obligation operator instead of the monadic operator.%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-The final set of tests deal with ought implies can and conflicting obligations. Recall that I 
-specifically added an axiom in my formalization to disallow contradictory obligations, so I expect 
-these tests to pass. Kroy's formalization fails these tests, so this is another area of improvement 
-over Kroy's formalization.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ ought{\isacharunderscore}implies{\isacharunderscore}can{\isacharcolon}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}O{\isacharbraceleft}W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharbar}c{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymdiamond}\ W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
-%
-\isadelimproof
-\ \ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{using}\isamarkupfalse%
-\ O{\isacharunderscore}diamond\ \isacommand{by}\isamarkupfalse%
-\ blast\isanewline
-%
-\isamarkupcmt{This test is a lemma of DDL itself, so it's no surprise that this test passes.%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-\isanewline
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ conflicting{\isacharunderscore}obligations{\isacharcolon}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymnot}\ {\isacharparenleft}O{\isacharbraceleft}W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharbar}c{\isacharbraceright}\ \isactrlbold {\isasymand}\ O{\isacharbraceleft}\isactrlbold {\isasymnot}{\isacharparenleft}W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}{\isacharbar}\ c{\isacharbraceright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
-%
-\isadelimproof
-\ \ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{using}\isamarkupfalse%
-\ no{\isacharunderscore}contradictions\ \isacommand{by}\isamarkupfalse%
-\ blast\isanewline
-%
-\isamarkupcmt{This test passes immediately by the new axiom prohibited contradictory obligations.%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-\isanewline
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ implied{\isacharunderscore}contradiction{\isacharcolon}\isanewline
-\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}{\isacharparenleft}W\ {\isacharparenleft}c{\isadigit{1}}{\isacharcomma}\ a{\isadigit{1}}{\isacharcomma}\ g{\isadigit{1}}{\isacharparenright}\ s{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}W\ {\isacharparenleft}c{\isadigit{2}}{\isacharcomma}\ a{\isadigit{2}}{\isacharcomma}\ g{\isadigit{2}}{\isacharparenright}\ s{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbottom}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}\isactrlbold {\isasymnot}\ {\isacharparenleft}O{\isacharbraceleft}W{\isacharparenleft}c{\isadigit{1}}{\isacharcomma}\ a{\isadigit{1}}{\isacharcomma}\ g{\isadigit{1}}{\isacharparenright}\ s{\isacharbar}c{\isacharbraceright}\ \isactrlbold {\isasymand}\ O{\isacharbraceleft}W{\isacharparenleft}c{\isadigit{2}}{\isacharcomma}\ a{\isadigit{2}}{\isacharcomma}\ g{\isadigit{2}}{\isacharparenright}\ s{\isacharbar}c{\isacharbraceright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
-%
-\isadelimproof
-\ \ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{using}\isamarkupfalse%
-\ assms\ no{\isacharunderscore}contradictions\ \isacommand{by}\isamarkupfalse%
-\ blast\isanewline
-%
-\isamarkupcmt{Recall that the we also expect the stronger property that the combination of obligatory maxims can't
- imply a contradiction. The added axiom also makes this test pass.%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-\isanewline
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ distribution{\isacharcolon}\isanewline
-\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymand}\ O\ {\isacharbraceleft}B{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymTurnstile}\ O\ {\isacharbraceleft}A\ \isactrlbold {\isasymand}\ B{\isacharbraceright}{\isachardoublequoteclose}\isanewline
-%
-\isadelimproof
-\ \ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{using}\isamarkupfalse%
-\ assms\ no{\isacharunderscore}contradictions\ \isacommand{by}\isamarkupfalse%
-\ fastforce%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-The metaethical test suite ran on both Kroy's formalization and my formalizaion show two clear 
-improvements. First, my formalization shows that obligatory maxims are permissible, whereas Kroy's 
-paradoxically does not. Second, my formalization doesn't allow contradictory maxims, but Kroy's does. 
-Both of these improvements are derived from the new axiom I added in my formalization that disallows 
-contradictory obligations. Additionally, my formalization also improves on Kroy's by staying faithful to the 
-strongest interpretation of the FUL, Korsgaard's practical contradiction interpretation. (maybe stick 
-philosophical writing here or above?)%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\isatagdocument
-%
-\isamarkupsubsection{Formalization Specific Tests%
-}
-\isamarkuptrue%
-%
-\endisatagdocument
-{\isafolddocument}%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\begin{isamarkuptext}%
-In this section, I explore tests specific to my formalization of the categorical imperative. First, 
-in my previous (buggy) implementation of DDL, prohibiting contradictory obligation led to the strange 
-result that all permissible actions are obligatory. I will test if this bug appears in this implementation 
-as well.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ bug{\isacharcolon}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}permissible\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ w\ {\isasymlongrightarrow}\ O{\isacharbraceleft}W{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ {\isacharbar}\ c{\isacharbraceright}\ w{\isachardoublequoteclose}\isanewline
-\ \ \isacommand{nitpick}\isamarkupfalse%
-{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{oops}\isamarkupfalse%
-\isanewline
-%
-\isamarkupcmt{\color{blue}
-Nitpick found a counterexample for card i = 1 and card s = 2:
-
-  Free variables:
-    a = ($\lambda x. \_$)($s_1$ := ($\lambda x. \_$)($i_1$ := False), $s_2$ := ($\lambda x. \_$)($i_1$ := False))
-    c = ($\lambda x. \_$)($i_1$ := False)
-    g = ($\lambda x. \_$)($i_1$ := False)
-    s = $s_2$
-    w = undefined
-\color{black}
-This strange result does not hold; good!%
-}\isanewline
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
 \isadelimtheory
@@
 %:%504=357%:%
-%:%513=359%:%
-%:%525=361%:%
-%:%526=362%:%
-%:%527=363%:%
-%:%528=364%:%
-%:%532=366%:%
-%:%533=367%:%
-%:%534=368%:%
-%:%535=369%:%
-%:%536=370%:%
-%:%537=371%:%
-%:%538=372%:%
-%:%539=373%:%
-%:%540=374%:%
-%:%541=375%:%
-%:%542=376%:%
-%:%543=377%:%
-%:%544=378%:%
-%:%545=379%:%
-%:%546=380%:%
-%:%547=381%:%
-%:%549=383%:%
-%:%550=383%:%
-%:%552=384%:%
-%:%553=385%:%
-%:%554=385%:%
-%:%555=386%:%
-%:%556=386%:%
-%:%558=387%:%
-%:%559=388%:%
-%:%560=388%:%
-%:%561=389%:%
-%:%562=389%:%
-%:%564=390%:%
-%:%565=391%:%
-%:%566=391%:%
-%:%567=392%:%
-%:%568=393%:%
-%:%569=393%:%
-%:%570=394%:%
-%:%572=395%:%
-%:%575=397%:%
-%:%576=398%:%
-%:%577=399%:%
-%:%579=401%:%
-%:%580=401%:%
-%:%581=402%:%
-%:%583=403%:%
-%:%584=404%:%
-%:%585=405%:%
-%:%586=406%:%
-%:%587=407%:%
-%:%588=407%:%
-%:%589=408%:%
-%:%590=409%:%
-%:%591=409%:%
-%:%592=410%:%
-%:%594=411%:%
-%:%595=412%:%
-%:%596=413%:%
-%:%597=414%:%
-%:%598=415%:%
-%:%599=415%:%
-%:%600=416%:%
-%:%601=417%:%
-%:%602=417%:%
-%:%603=418%:%
-%:%605=419%:%
-%:%606=420%:%
-%:%607=421%:%
-%:%608=422%:%
-%:%609=423%:%
-%:%612=425%:%
-%:%613=426%:%
-%:%615=428%:%
-%:%616=428%:%
-%:%617=429%:%
-%:%618=430%:%
-%:%619=431%:%
-%:%620=432%:%
-%:%627=433%:%
-%:%628=433%:%
-%:%629=434%:%
-%:%630=434%:%
-%:%631=435%:%
-%:%632=435%:%
-%:%634=436%:%
-%:%635=437%:%
-%:%636=437%:%
-%:%637=438%:%
-%:%638=438%:%
-%:%639=439%:%
-%:%640=439%:%
-%:%641=439%:%
-%:%642=440%:%
-%:%652=442%:%
-%:%653=443%:%
-%:%654=444%:%
-%:%655=445%:%
-%:%656=446%:%
-%:%657=447%:%
-%:%658=448%:%
-%:%659=449%:%
-%:%661=451%:%
-%:%662=451%:%
-%:%663=452%:%
-%:%664=452%:%
-%:%665=453%:%
-%:%667=454%:%
-%:%668=455%:%
-%:%669=455%:%
-%:%670=456%:%
-%:%671=457%:%
-%:%672=457%:%
-%:%673=458%:%
-%:%675=459%:%
-%:%676=460%:%
-%:%677=460%:%
-%:%678=461%:%
-%:%679=462%:%
-%:%680=462%:%
-%:%681=463%:%
-%:%682=464%:%
-%:%684=465%:%
-%:%685=465%:%
-%:%686=466%:%
-%:%687=467%:%
-%:%689=468%:%
-%:%690=468%:%
-%:%691=469%:%
-%:%698=470%:%
-%:%699=470%:%
-%:%700=471%:%
-%:%701=471%:%
-%:%702=472%:%
-%:%703=472%:%
-%:%704=472%:%
-%:%705=473%:%
-%:%706=473%:%
-%:%707=474%:%
-%:%708=474%:%
-%:%709=474%:%
-%:%710=475%:%
-%:%711=475%:%
-%:%713=476%:%
-%:%723=478%:%
-%:%724=479%:%
-%:%725=480%:%
-%:%726=481%:%
-%:%727=482%:%
-%:%728=483%:%
-%:%729=484%:%
-%:%730=485%:%
-%:%731=486%:%
-%:%732=487%:%
-%:%733=488%:%
-%:%734=489%:%
-%:%735=490%:%
-%:%736=491%:%
-%:%737=492%:%
-%:%738=493%:%
-%:%739=494%:%
-%:%740=495%:%
-%:%741=496%:%
-%:%742=497%:%
-%:%743=498%:%
-%:%744=499%:%
-%:%745=500%:%
-%:%746=501%:%
-%:%747=502%:%
-%:%748=503%:%
-%:%749=504%:%
-%:%750=505%:%
-%:%751=506%:%
-%:%752=507%:%
-%:%753=508%:%
-%:%754=509%:%
-%:%755=510%:%
-%:%756=511%:%
-%:%757=512%:%
-%:%758=513%:%
-%:%759=514%:%
-%:%760=515%:%
-%:%761=516%:%
-%:%762=517%:%
-%:%766=519%:%
-%:%767=520%:%
-%:%768=521%:%
-%:%770=523%:%
-%:%771=523%:%
-%:%772=524%:%
-%:%773=525%:%
-%:%774=525%:%
-%:%776=525%:%
-%:%780=525%:%
-%:%781=525%:%
-%:%783=526%:%
-%:%784=527%:%
-%:%785=528%:%
-%:%786=529%:%
-%:%787=530%:%
-%:%788=531%:%
-%:%798=534%:%
-%:%799=535%:%
-%:%800=536%:%
-%:%809=538%:%
-%:%821=540%:%
-%:%822=541%:%
-%:%823=542%:%
-%:%824=543%:%
-%:%825=544%:%
-%:%826=545%:%
-%:%827=546%:%
-%:%828=547%:%
-%:%829=548%:%
-%:%830=549%:%
-%:%831=550%:%
-%:%832=551%:%
-%:%833=552%:%
-%:%834=553%:%
-%:%836=555%:%
-%:%837=555%:%
-%:%838=556%:%
-%:%841=557%:%
-%:%845=557%:%
-%:%846=557%:%
-%:%851=557%:%
-%:%854=558%:%
-%:%855=559%:%
-%:%856=559%:%
-%:%857=560%:%
-%:%860=561%:%
-%:%864=561%:%
-%:%865=561%:%
-%:%870=561%:%
-%:%873=562%:%
-%:%874=563%:%
-%:%875=563%:%
-%:%876=564%:%
-%:%879=565%:%
-%:%883=565%:%
-%:%884=565%:%
-%:%889=565%:%
-%:%892=566%:%
-%:%893=567%:%
-%:%894=567%:%
-%:%895=568%:%
-%:%898=569%:%
-%:%902=569%:%
-%:%903=569%:%
-%:%912=571%:%
-%:%913=572%:%
-%:%914=573%:%
-%:%915=574%:%
-%:%916=575%:%
-%:%917=576%:%
-%:%918=577%:%
-%:%920=579%:%
-%:%921=579%:%
-%:%922=580%:%
-%:%923=581%:%
-%:%924=581%:%
-%:%926=581%:%
-%:%930=581%:%
-%:%931=581%:%
-%:%933=582%:%
-%:%934=583%:%
-%:%935=584%:%
-%:%936=585%:%
-%:%937=586%:%
-%:%938=587%:%
-%:%939=588%:%
-%:%940=589%:%
-%:%941=590%:%
-%:%942=591%:%
-%:%943=592%:%
-%:%953=594%:%
-%:%954=595%:%
-%:%956=597%:%
-%:%957=597%:%
-%:%958=598%:%
-%:%961=599%:%
-%:%965=599%:%
-%:%966=599%:%
-%:%968=600%:%
-%:%978=602%:%
-%:%979=603%:%
-%:%981=605%:%
-%:%982=605%:%
-%:%983=606%:%
-%:%986=607%:%
-%:%990=607%:%
-%:%991=607%:%
-%:%992=607%:%
-%:%994=608%:%
-%:%995=609%:%
-%:%1005=611%:%
-%:%1006=612%:%
-%:%1007=613%:%
-%:%1008=614%:%
-%:%1012=616%:%
-%:%1013=617%:%
-%:%1014=618%:%
-%:%1016=620%:%
-%:%1017=620%:%
-%:%1018=621%:%
-%:%1019=622%:%
-%:%1020=623%:%
-%:%1021=623%:%
-%:%1023=623%:%
-%:%1027=623%:%
-%:%1028=623%:%
-%:%1030=624%:%
-%:%1031=625%:%
-%:%1032=626%:%
-%:%1033=627%:%
-%:%1034=628%:%
-%:%1035=629%:%
-%:%1036=630%:%
-%:%1037=631%:%
-%:%1038=632%:%
-%:%1039=633%:%
-%:%1049=635%:%
-%:%1050=636%:%
-%:%1051=637%:%
-%:%1053=639%:%
-%:%1054=639%:%
-%:%1055=640%:%
-%:%1056=641%:%
-%:%1057=641%:%
-%:%1059=641%:%
-%:%1063=641%:%
-%:%1064=641%:%
-%:%1066=642%:%
-%:%1067=643%:%
-%:%1068=644%:%
-%:%1069=645%:%
-%:%1070=646%:%
-%:%1071=647%:%
-%:%1072=648%:%
-%:%1073=649%:%
-%:%1074=650%:%
-%:%1075=651%:%
-%:%1085=653%:%
-%:%1086=654%:%
-%:%1087=655%:%
-%:%1088=656%:%
-%:%1090=658%:%
-%:%1091=658%:%
-%:%1092=659%:%
-%:%1095=660%:%
-%:%1099=660%:%
-%:%1100=660%:%
-%:%1101=660%:%
-%:%1103=661%:%
-%:%1109=661%:%
-%:%1112=662%:%
-%:%1113=663%:%
-%:%1114=663%:%
-%:%1115=664%:%
-%:%1118=665%:%
-%:%1122=665%:%
-%:%1123=665%:%
-%:%1124=665%:%
-%:%1126=666%:%
-%:%1132=666%:%
-%:%1135=667%:%
-%:%1136=668%:%
-%:%1137=668%:%
-%:%1138=669%:%
-%:%1139=670%:%
-%:%1142=671%:%
-%:%1146=671%:%
-%:%1147=671%:%
-%:%1148=671%:%
-%:%1150=672%:%
-%:%1151=673%:%
-%:%1157=673%:%
-%:%1160=674%:%
-%:%1161=675%:%
-%:%1162=675%:%
-%:%1163=676%:%
-%:%1164=677%:%
-%:%1167=678%:%
-%:%1171=678%:%
-%:%1172=678%:%
-%:%1173=678%:%
-%:%1182=680%:%
-%:%1183=681%:%
-%:%1184=682%:%
-%:%1185=683%:%
-%:%1186=684%:%
-%:%1187=685%:%
-%:%1188=686%:%
-%:%1197=688%:%
-%:%1209=690%:%
-%:%1210=691%:%
-%:%1211=692%:%
-%:%1212=693%:%
-%:%1214=695%:%
-%:%1215=695%:%
-%:%1216=696%:%
-%:%1217=697%:%
-%:%1218=697%:%
-%:%1220=697%:%
-%:%1224=697%:%
-%:%1225=697%:%
-%:%1227=698%:%
-%:%1228=699%:%
-%:%1229=700%:%
-%:%1230=701%:%
-%:%1231=702%:%
-%:%1232=703%:%
-%:%1233=704%:%
-%:%1234=705%:%
-%:%1235=706%:%
-%:%1236=707%:%
-%:%1237=708%:%
-%:%1238=708%:%
+%:%512=359%:%
+%:%520=359%:%

### 2021-11-17 paper/output/document/paper412.tex
what am i doing

%
\begin{isabellebody}%
\setisabellecontext{paper{\isadigit{4}}{\isadigit{1}}{\isadigit{2}}}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
\isacommand{theory}\isamarkupfalse%
\ paper{\isadigit{4}}{\isadigit{1}}{\isadigit{2}}\ \isakeyword{imports}\ paper{\isadigit{4}}{\isadigit{1}}\isanewline
\isanewline
\isakeyword{begin}%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Application Tests%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
As with the naive formalization and Kroy's formalization, I will apply my testing framework to 
my custom formalization of the FUL. I will begin with some basic application tests. In these tests, 
I specify particular maxims as constants with no properties and gradually add properties to understand 
how the system handles different kinds of maxims.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
I will show that the maxim, ``When strapped for cash, falsely promise to pay your friend back
to get some easy money." is prohibited. This example is due to Korsgaard and she uses it to highlight 
the strength of her preferred interpretation of the FUL, the practical contradiction interpretation \cite{KorsgaardFUL}.
There are two possible readings of this maxim, and I will show that my formalization can handle both. 
Under the first reading, the act of falsely promising is read as
as entering a pre-existing, implicit, social system of promising with no intention of upholding your 
promise. Under the second reading, the act of falsely promising is equivalent to uttering the worlds 
``I promise X" without intending to do X. The differences between these readings lies in the difference 
between promising as an act with meaning in a larger social structure and the utterance ``I promise."

Under the first reading, the maxim fails because falsely promising is no longer possible in a world where 
everyone everyone does so. This is how the logical contradiction interpretation reads this maxim—falsely 
promising is no longer possible when universalized because the institution of promising breaks down. 
The practical contradiction view also prohibits this maxim because if falsely promising is not longer 
possible, then it is no longer an effective way to achieve the end of getting some money. Below I 
define some logical tools to formalize this reading of this maxim.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{consts}\isamarkupfalse%
\ when{\isacharunderscore}strapped{\isacharunderscore}for{\isacharunderscore}cash{\isacharcolon}{\isacharcolon}t\isanewline
%
\isamarkupcmt{Constant representing the circumstances ``when strapped for cash." Recall that the type of circumstances 
is a term because circumstances can be true or false at a world.%
}\isanewline
\isacommand{consts}\isamarkupfalse%
\ falsely{\isacharunderscore}promise{\isacharcolon}{\isacharcolon}os\isanewline
%
\isamarkupcmt{Constant representing the act ``make a false promise to pay a loan back." Recall that the type of
an act is an open sentence because the sentence ``subject s performs act a" can be true or false at a world.%
}\isanewline
\isacommand{consts}\isamarkupfalse%
\ to{\isacharunderscore}get{\isacharunderscore}easy{\isacharunderscore}cash{\isacharcolon}{\isacharcolon}t\isanewline
%
\isamarkupcmt{Constant representing the goal ``to get some money." Recall that the type of a goal 
is a term because a goal can be true or false at a world depending on whether it is achieved or not.%
}\isanewline
\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ false{\isacharunderscore}promising{\isacharcolon}{\isacharcolon}maxim\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}false{\isacharunderscore}promising\ {\isasymequiv}\ {\isacharparenleft}when{\isacharunderscore}strapped{\isacharunderscore}for{\isacharunderscore}cash{\isacharcomma}\ falsely{\isacharunderscore}promise{\isacharcomma}\ to{\isacharunderscore}get{\isacharunderscore}easy{\isacharunderscore}cash{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{Armed with the circumstances, act, and goal above, I can define the example maxim as a tuple.%
}%
\begin{isamarkuptext}%
The logical objects above are ``empty," in the sense that I haven't specified any of their 
relevant properties. I will define these properties as assumptions and will show that, if the maxim 
above satisfies the assumed properties, it is prohibited.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ everyone{\isacharunderscore}can{\isacharprime}t{\isacharunderscore}lie\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}everyone{\isacharunderscore}can{\isacharprime}t{\isacharunderscore}lie\ {\isasymequiv}\ {\isasymforall}w{\isachardot}\ {\isasymnot}\ {\isacharparenleft}{\isasymforall}s{\isachardot}\ falsely{\isacharunderscore}promise{\isacharparenleft}s{\isacharparenright}\ w{\isacharparenright}\ {\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{Under this reading, the problem with this maxim is that everyone can't
falsely promise simultaneously because the institution of promising will break down. It's probably 
possible to say something stronger than this (i.e. that if enough but not necessarily all people
falsely promise promising is no longer possible), but for my purposes this will suffice. The above 
formula reads, ``At all worlds, it is not the case that everyone falsely promises."%
}\isanewline
\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ circumstances{\isacharunderscore}hold\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}circumstances{\isacharunderscore}hold\ {\isasymequiv}\ {\isasymforall}w{\isachardot}\ when{\isacharunderscore}strapped{\isacharunderscore}for{\isacharunderscore}cash\ w{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{This assumption narrows our scope of consideration to worlds where the circumstances of 
being strapped for cash hold. This is important because, at worlds where the circumstances do not hold, 
a maxim is trivially effective (since it's never acted on) and thus trivially universalizable. This 
assumption also makes practical sense; when evaluating a maxim, an agent would care about it specifically
at worlds where the circumstances hold, since these are the worlds where the maxim actually prescribes action.%
}\isanewline
\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ example{\isacharunderscore}is{\isacharunderscore}well{\isacharunderscore}formed\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}example{\isacharunderscore}is{\isacharunderscore}well{\isacharunderscore}formed\ {\isasymequiv}\ {\isasymforall}s{\isachardot}\ {\isasymTurnstile}\ {\isacharparenleft}well{\isacharunderscore}formed\ false{\isacharunderscore}promising\ s{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{This assumption states that the maxim of falsely promising is well-formed. This breaks down into
two individual assumptions. First, being strapped for cash can't imply falsely promising, which is plausible
because many people won't falsely promise under conditions of poverty. Second, being strapped for cash
can't imply getting ready cash, which is also plausible because people often fail to secure cash even 
when they need it.%
}%
\begin{isamarkuptext}%
Putting it all together, I want to show that if the three assumptions justified above hold, then 
the constructed maxim is prohibited. Below is the proof%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ lying{\isacharunderscore}bad{\isacharunderscore}{\isadigit{1}}{\isacharcolon}\isanewline
\ \ \isakeyword{assumes}\ everyone{\isacharunderscore}can{\isacharprime}t{\isacharunderscore}lie\isanewline
\ \ \isakeyword{assumes}\ circumstances{\isacharunderscore}hold\isanewline
\ \ \isakeyword{assumes}\ example{\isacharunderscore}is{\isacharunderscore}well{\isacharunderscore}formed\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}s{\isachardot}\ {\isasymTurnstile}\ {\isacharparenleft}prohibited\ false{\isacharunderscore}promising\ s{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
\isacommand{proof}\isamarkupfalse%
{\isacharminus}\isanewline
\ \ \isacommand{have}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isasymforall}s{\isachardot}\ not{\isacharunderscore}universalizable\ false{\isacharunderscore}promising\ s{\isachardoublequoteclose}\isanewline
\ \ \ \ \isacommand{by}\isamarkupfalse%
\ {\isacharparenleft}simp\ add{\isacharcolon}\ assms{\isacharparenleft}{\isadigit{1}}{\isacharparenright}\ assms{\isacharparenleft}{\isadigit{2}}{\isacharparenright}{\isacharparenright}\isanewline
%
\isamarkupcmt{I manually broke the proof into this intermediate lemma and the conclusion, and then Sledgehammer 
automatically found a proof.%
}\isanewline
\ \ \isacommand{thus}\isamarkupfalse%
\ {\isacharquery}thesis\isanewline
\ \ \ \ \isacommand{using}\isamarkupfalse%
\ FUL\ assms{\isacharparenleft}{\isadigit{3}}{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
\ blast\ \isanewline
\isacommand{qed}\isamarkupfalse%
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
Under the second reading of this maxim, the act ``falsely promising" refers to uttering the 
sentence ``I promise to do X" with no intention of actually doing X\footnote{Note that under this 
reading, the maxim isn't prohibited under the logical contradiction interpretation because making an 
utterance is still possible even if eveyrone else makes that utterance. I will discuss this in detail 
later in this section in the context of the difference between natural and conventional acts.}. 
Under this reading, the practical contradiction interpretation prohibits this maxim because, in a world 
where false promising is universalized, no one believes promises anymore, so the utterance is no longer 
an effective way to get money. Below I formalize this reading of this maixm.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{consts}\isamarkupfalse%
\ believed{\isacharcolon}{\isacharcolon}os\ \isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ false{\isacharunderscore}promising{\isacharunderscore}not{\isacharunderscore}believed\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}false{\isacharunderscore}promising{\isacharunderscore}not{\isacharunderscore}believed\ {\isasymequiv}\ {\isasymforall}w\ s{\isachardot}\ {\isacharparenleft}falsely{\isacharunderscore}promise{\isacharparenleft}s{\isacharparenright}\ w\ {\isasymlongrightarrow}\ {\isasymnot}\ believed{\isacharparenleft}s{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{This abbreviation formalizes the idea that if everyone falsely promises, then no one is believed
when promising.%
}\isanewline
\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ need{\isacharunderscore}to{\isacharunderscore}be{\isacharunderscore}believed\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}need{\isacharunderscore}to{\isacharunderscore}be{\isacharunderscore}believed\ {\isasymequiv}\ {\isasymforall}w\ s{\isachardot}\ {\isacharparenleft}{\isasymnot}\ believed{\isacharparenleft}s{\isacharparenright}\ w\ {\isasymlongrightarrow}\ \isactrlbold {\isasymnot}{\isacharparenleft}{\isacharparenleft}falsely{\isacharunderscore}promise\ s{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ to{\isacharunderscore}get{\isacharunderscore}easy{\isacharunderscore}cash{\isacharparenright}w{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{This abbreviation formalizes the idea that if a promise is not believed, then it is not an effective
way of getting easy cash.%
}\isanewline
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ falsely{\isacharunderscore}promising{\isacharunderscore}bad{\isacharunderscore}{\isadigit{2}}{\isacharcolon}\isanewline
\ \ \isakeyword{assumes}\ false{\isacharunderscore}promising{\isacharunderscore}not{\isacharunderscore}believed\isanewline
\ \ \isakeyword{assumes}\ need{\isacharunderscore}to{\isacharunderscore}be{\isacharunderscore}believed\isanewline
%
\isamarkupcmt{The above two assumptions are specific to this reading and justified above.%
}\isanewline
\ \ \isakeyword{assumes}\ circumstances{\isacharunderscore}hold\isanewline
\ \ \isakeyword{assumes}\ example{\isacharunderscore}is{\isacharunderscore}well{\isacharunderscore}formed\isanewline
%
\isamarkupcmt{These two assumptions applied to the first reading as well and were justified there.%
}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}s{\isachardot}\ {\isasymTurnstile}\ {\isacharparenleft}prohibited\ false{\isacharunderscore}promising\ s{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
\isacommand{proof}\isamarkupfalse%
{\isacharminus}\isanewline
\ \ \isacommand{have}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isasymforall}s{\isachardot}\ not{\isacharunderscore}universalizable\ false{\isacharunderscore}promising\ s{\isachardoublequoteclose}\isanewline
\ \ \ \ \isacommand{using}\isamarkupfalse%
\ assms{\isacharparenleft}{\isadigit{1}}{\isacharparenright}\ assms{\isacharparenleft}{\isadigit{2}}{\isacharparenright}\ assms{\isacharparenleft}{\isadigit{3}}{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
\ auto\isanewline
\ \ \isacommand{thus}\isamarkupfalse%
\ {\isacharquery}thesis\isanewline
\ \ \ \ \isacommand{using}\isamarkupfalse%
\ FUL\ assms{\isacharparenleft}{\isadigit{4}}{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
\ blast\isanewline
\isacommand{qed}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{With some help, Isabelle is able to show that the maxim is prohibited under this reading as well.%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
This example demonstrates that my formalization is able to correctly prohibit this maxim, regardless
of its reading. This is additionally important because the two readings of this maxim represent reading 
the act as either a conventional or natural action, so my intrepretation can correctly handle both kinds
of actions. Korsgaard draws a distinction between conventional acts and natural acts. Conventional acts 
exist within a practice, which is "comprised of certain rules, and its existence (where it is not embodied in 
an institution with sanctions) consists in the general acknowledgement and following of those rules" 
\cite[10]{KorsgaardFUL}. For example, promising is a conventional act because it only exists as a 
practice. Murder, on the other hand, is an example of a natural act because its existence only depends
on the laws of nature\cite[11]{KorsgaardFUL}.

This distinction is important because Korsgaard argues that only the practical contradiction view can 
satisfactorily explain the wrongness of certain natural acts like murder\footnote{For more discussion 
of Korsgaard's argument for the practical contradiction view, see Section Philosophical Writing}. 
The practical contradiction view is thus stronger than the logical contradiction view because it can 
explain the wrongness of both conventional and natural acts.

The fact that my interpretation can correctly show the wrongness of both conventional and natural acts
is evidence for its correctness as a formalization of the practical contradiction interpretation. 
The first reading of the example maxim reads the act 
``making a false promise" as entering into an agreement within a socially established system of promising. 
This is clearly a conventional act, and because it is a conventional act, it is not just contradictory
when universalized but literally impossible because the practice breaks down. I capture this idea in the 
assumption \isa{everyone{\isacharunderscore}can{\isacharprime}t{\isacharunderscore}lie\ {\isasymequiv}\ {\isasymforall}w{\isachardot}\ {\isasymnot}\ {\isacharparenleft}{\isasymforall}s{\isachardot}\ falsely{\isacharunderscore}promise\ s\ w{\isacharparenright}}, which states that, at all worlds, not everyone can falsely promise since 
otherwise the practice of promising would break down. The second reading, on the other hand, reads the 
act of making a false promise as uttering the statement ``I promise to pay you back," while never intending 
to fulfill this promise. This is a natural act because the act of uttering a sentence does not rely 
on any conventions, merely the laws of nature governing how your mouth and vocal cords behave\footnote{
Linguistic relativists may take issue with this claim and may argue that if the English language had 
never developed, then making this utterance would be impossible. Even if this is true, the laws of 
nature itself would not prohibit making the sounds corresponding to the English pronounciation of 
this phrase, so the act would still not be impossible in the way that a conventional act can be.}

I show above that my formalization shows the wrongness of this maxim under both readings. Under the 
first reading, promising becomes impossible, so both the logical and 
practical contradiction interpretations prohibit the maxim. Under the second reading, promising is still
possible, but becomes ineffective because people no longer interpret the utterance as creating a commitment.
Under this view, only the practical contradiction interpretation succeeds in prohibiting the maxim. Thus, 
not only does my formalization likely capture the practical contradiction interpretation (as opposed to 
the teleological or logical contradiction interpretations), it also adequately handles both natural 
and conventional acts.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
I can also use Isabelle to confirm that the two readings are different. If they were the same, 
we would expect the assumptions corresponing to each to be equivalent. The RHS of the lemma below represents 
the second reading and the LHS represents the first reading.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ readings{\isacharunderscore}are{\isacharunderscore}equivalent{\isacharcolon}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}false{\isacharunderscore}promising{\isacharunderscore}not{\isacharunderscore}believed\ {\isasymand}\ need{\isacharunderscore}to{\isacharunderscore}be{\isacharunderscore}believed\ {\isasymequiv}\ everyone{\isacharunderscore}can{\isacharprime}t{\isacharunderscore}lie{\isachardoublequoteclose}\isanewline
\ \ \isacommand{nitpick}\isamarkupfalse%
{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{Nitpick finds a counterexample, showing that the two readings are different.
\color{blue}
Nitpick found a counterexample for card i = 1 and card s = 1:

  Empty assignment
\color{black}%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
This completes the application tests for my formalization. I showed that my formalization correctly 
handles an example from Korsgaard with two possible interpretations and also sufficiently handles both 
conventional and natural acts.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Metaethical Tests%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
Recall that metaethical tests test formal properties of the system that apply to any maxim, not 
just those specified in the application tests. In this section I adapt the metaethical tests developed 
in previous sections to my formalization of the categorical imperative. I preserved the philosophical 
goal of each test but modified them to test the stronger, richer notion of a maxim.

The first set of tests consider how obligation generalizes, first across worlds and then across
people. As expected, the tests below show that both wrongness (prohibition) and rightness (obligation)
generalize across both worlds and people. In other words, if something is obligated at some world, it 
is obligated at every world and if something is obligated for some person, then it is obligated for 
every person.

Generalization across worlds is a consequence of the fact that my interpretation does not make use of the 
modal nature of DDL. In particular, I do not use any property of the world when prescribing obligations 
at that world.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ wrong{\isacharunderscore}if{\isacharunderscore}wrong{\isacharunderscore}for{\isacharunderscore}someone{\isacharcolon}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}w{\isachardot}\ {\isasymforall}c{\isacharcolon}{\isacharcolon}t{\isachardot}\ {\isasymforall}g{\isacharcolon}{\isacharcolon}t{\isachardot}\ {\isasymexists}s{\isacharcolon}{\isacharcolon}s{\isachardot}\ O{\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}W\ {\isacharparenleft}c{\isacharcomma}\ M{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ {\isacharbar}\ c{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ \ O{\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}W\ {\isacharparenleft}c{\isacharcomma}\ M{\isacharcomma}\ g{\isacharparenright}\ p{\isacharparenright}\ {\isacharbar}\ c{\isacharbraceright}\ w{\isacharparenright}\ {\isachardoublequoteclose}\isanewline
%
\isadelimproof
\ \ %
\endisadelimproof
%
\isatagproof
\isacommand{by}\isamarkupfalse%
\ blast%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
\isanewline
%
\endisadelimproof
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ right{\isacharunderscore}if{\isacharunderscore}right{\isacharunderscore}for{\isacharunderscore}someone{\isacharcolon}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}w{\isachardot}\ {\isasymforall}c{\isacharcolon}{\isacharcolon}t{\isachardot}\ {\isasymforall}g{\isacharcolon}{\isacharcolon}t{\isachardot}\ {\isasymexists}s{\isacharcolon}{\isacharcolon}s{\isachardot}\ O{\isacharbraceleft}W\ {\isacharparenleft}c{\isacharcomma}\ M{\isacharcomma}\ g{\isacharparenright}\ s\ {\isacharbar}\ c{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ \ O{\isacharbraceleft}W\ {\isacharparenleft}c{\isacharcomma}\ M{\isacharcomma}\ g{\isacharparenright}\ p\ {\isacharbar}\ c{\isacharbraceright}\ w{\isacharparenright}\ {\isachardoublequoteclose}\isanewline
%
\isadelimproof
\ \ %
\endisadelimproof
%
\isatagproof
\isacommand{by}\isamarkupfalse%
\ blast%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
\isanewline
%
\endisadelimproof
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ wrong{\isacharunderscore}if{\isacharunderscore}wrong{\isacharunderscore}somewhere{\isacharcolon}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}c\ g{\isachardot}\ {\isasymexists}w{\isadigit{1}}{\isachardot}\ O{\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}W\ {\isacharparenleft}c{\isacharcomma}\ M{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ {\isacharbar}\ c{\isacharbraceright}\ w{\isadigit{1}}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}w{\isadigit{2}}{\isachardot}\ \ O{\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}W\ {\isacharparenleft}c{\isacharcomma}\ M{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ {\isacharbar}\ c{\isacharbraceright}\ w{\isadigit{2}}{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isadelimproof
\ \ %
\endisadelimproof
%
\isatagproof
\isacommand{by}\isamarkupfalse%
\ blast%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
\isanewline
%
\endisadelimproof
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ right{\isacharunderscore}if{\isacharunderscore}right{\isacharunderscore}somewhere{\isacharcolon}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}c\ g{\isachardot}\ {\isasymexists}w{\isadigit{1}}{\isachardot}\ O{\isacharbraceleft}W\ {\isacharparenleft}c{\isacharcomma}\ M{\isacharcomma}\ g{\isacharparenright}\ s\ {\isacharbar}\ c{\isacharbraceright}\ w{\isadigit{1}}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}w{\isadigit{2}}{\isachardot}\ \ O{\isacharbraceleft}W\ {\isacharparenleft}c{\isacharcomma}\ M{\isacharcomma}\ g{\isacharparenright}\ s\ {\isacharbar}\ c{\isacharbraceright}\ w{\isadigit{2}}{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isadelimproof
\ \ %
\endisadelimproof
%
\isatagproof
\isacommand{by}\isamarkupfalse%
\ blast%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
As expected, obligation generalizes across people and worlds. In the next set of tests, I will 
analyze basic properties of permissibility, obligation, and prohibition.

First, I verify that the logic allows
for permissible maxims, as this is a problem that prior iterations ran into. Below, I use Nitpick to 
find a model in which there is a circumstance, act, goal tuple that is permissible but not 
obligated at some world.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ permissible{\isacharcolon}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O{\isacharbraceleft}{\isacharparenleft}W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ {\isacharbar}\ c{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O{\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ {\isacharbar}\ c{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
\ \ \isacommand{nitpick}\isamarkupfalse%
\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{\color{blue}Nitpick found a model for card i = 1 and card s = 1:

  Free variables:
    a = ($\lambda x. \_$)($s_1$ := ($\lambda x. \_$)($i_1$ := False))
    c = ($\lambda x. \_$)($i_1$ := False)
    g = ($\lambda x. \_$)($i_1$ := False)
    s = $s_1$\color{black}
Recall that Nitpick is a model checker that finds models making certain formulae true or false. In this 
case, Nitpick finds a model satisfying the given formula (which simply requires that the sentence 
``s wills (c, a, g)'' is permissible but not obligator). This model consists of the above specifications 
of a, c, g, and s.%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
I also expect that any arbitrary maxim should be either permissible or prohibited, since all 
acts are either permissible or prohibited.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ perm{\isacharunderscore}or{\isacharunderscore}prohibited{\isacharcolon}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}permissible\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ \isactrlbold {\isasymor}\ {\isacharparenleft}prohibited\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
%
\isadelimproof
\ \ %
\endisadelimproof
%
\isatagproof
\isacommand{by}\isamarkupfalse%
\ blast\isanewline
%
\isamarkupcmt{This simple test passes immediately by the definitions of  permissible and prohibited.%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
Obligation should be strictly stronger than permissibility. In other words, if a maxim is 
obligated at a world, it should be permissible at that world. Below I test this property.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ obligated{\isacharunderscore}then{\isacharunderscore}permissible{\isacharcolon}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}O{\isacharbraceleft}W{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharbar}c{\isacharbraceright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isacharparenleft}permissible\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ {\isacharparenright}\ s{\isacharparenright}{\isacharparenright}\ w\ {\isachardoublequoteclose}\isanewline
%
\isadelimproof
\ \ %
\endisadelimproof
%
\isatagproof
\isacommand{using}\isamarkupfalse%
\ no{\isacharunderscore}contradictions\ \isacommand{by}\isamarkupfalse%
\ auto\isanewline
%
\isamarkupcmt{This test passes and Isabelle is able to find a proof for the fact that all obligatory maxims are 
also permissible.%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
The above test failed under Kroy's formalization of the categorical imperative and is thus evidence 
that my formalization improves upon Kroy's. Interestingly, this new test passes because of the additional
added axiom that prohibits contradictory obligations (recall that Kroy's formalization allowed contradictory
obligations).%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
Next, I will test if the formalization allows for vacuous obligations or modal collapse. These 
tests are sanity checks confirmed that the obligation operator is doesn't collapse. First, I will check 
that any arbitrary term isn't obligated.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ arbitrary{\isacharunderscore}obligations{\isacharcolon}\isanewline
\ \ \isakeyword{fixes}\ c\ A{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isachardoublequoteclose}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}O{\isacharbraceleft}A{\isacharbar}c{\isacharbraceright}\ w{\isachardoublequoteclose}\isanewline
\ \ \isacommand{nitpick}\isamarkupfalse%
\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharequal}true{\isacharcomma}\ falsify{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{This test passes—Nitpick finds a model where A isn't obligated in circumstances c.
\color{blue} Nitpick found a counterexample for card i = 1 and card s = 2:

  Free variables:
    A = ($\lambda x. \_$)($i_1$ := True)
    c = ($\lambda x. \_$)($i_1$ := False) \color{blue}
Previous iterations of this test used the monadic obligation operator, which tests the term in the 
context ``True" (equivalently the set of all worlds since True holds everywhere). In this iteration, 
I test the term in a context c, because my formalization uses the dyadic obligation operator and must 
thus specify circumstances.%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
This is exactly the expected result. Any arbitrary action $A$ isn't obligated. A slightly 
        stronger property is ``modal collapse," or whether or not `$A$ happens' implies `$A$ is obligated'. 
The proposition below should be falsifiable.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ modal{\isacharunderscore}collapse{\isacharcolon}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ w{\isacharparenright}\ {\isasymlongrightarrow}\ O{\isacharbraceleft}W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharbar}c{\isacharbraceright}\ w{\isachardoublequoteclose}\isanewline
\ \ \isacommand{nitpick}\isamarkupfalse%
\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharequal}true{\isacharcomma}\ falsify{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{Nitpick finds a counterexample, so willing doesn't imply obligation, so this test passes. 
\color{blue}Nitpick found a counterexample for card i = 1 and card s = 2:

  Free variables:
    a = ($\lambda x. \_$)($s_1$ := ($\lambda x. \_$)($i_1$ := False), $s_2$ := ($\lambda x. \_$)($i_1$ := False))
    c = ($\lambda x. \_$)($i_1$ := False)
    g = ($\lambda x. \_$)($i_1$ := False)
    s = $s_2$
    w = $i_1$\color{black}
Once again, I modify this test to use the dyadic obligation operator instead of the monadic operator.%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
The final set of tests deal with ought implies can and conflicting obligations. Recall that I 
specifically added an axiom in my formalization to disallow contradictory obligations, so I expect 
these tests to pass. Kroy's formalization fails these tests, so this is another area of improvement 
over Kroy's formalization.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ ought{\isacharunderscore}implies{\isacharunderscore}can{\isacharcolon}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}O{\isacharbraceleft}W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharbar}c{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymdiamond}\ W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
%
\isadelimproof
\ \ %
\endisadelimproof
%
\isatagproof
\isacommand{using}\isamarkupfalse%
\ O{\isacharunderscore}diamond\ \isacommand{by}\isamarkupfalse%
\ blast\isanewline
%
\isamarkupcmt{This test is a lemma of DDL itself, so it's no surprise that this test passes.%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
\isanewline
%
\endisadelimproof
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ conflicting{\isacharunderscore}obligations{\isacharcolon}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymnot}\ {\isacharparenleft}O{\isacharbraceleft}W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharbar}c{\isacharbraceright}\ \isactrlbold {\isasymand}\ O{\isacharbraceleft}\isactrlbold {\isasymnot}{\isacharparenleft}W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}{\isacharbar}\ c{\isacharbraceright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
%
\isadelimproof
\ \ %
\endisadelimproof
%
\isatagproof
\isacommand{using}\isamarkupfalse%
\ no{\isacharunderscore}contradictions\ \isacommand{by}\isamarkupfalse%
\ blast\isanewline
%
\isamarkupcmt{This test passes immediately by the new axiom prohibited contradictory obligations.%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
\isanewline
%
\endisadelimproof
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ implied{\isacharunderscore}contradiction{\isacharcolon}\isanewline
\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}{\isacharparenleft}W\ {\isacharparenleft}c{\isadigit{1}}{\isacharcomma}\ a{\isadigit{1}}{\isacharcomma}\ g{\isadigit{1}}{\isacharparenright}\ s{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}W\ {\isacharparenleft}c{\isadigit{2}}{\isacharcomma}\ a{\isadigit{2}}{\isacharcomma}\ g{\isadigit{2}}{\isacharparenright}\ s{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbottom}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}\isactrlbold {\isasymnot}\ {\isacharparenleft}O{\isacharbraceleft}W{\isacharparenleft}c{\isadigit{1}}{\isacharcomma}\ a{\isadigit{1}}{\isacharcomma}\ g{\isadigit{1}}{\isacharparenright}\ s{\isacharbar}c{\isacharbraceright}\ \isactrlbold {\isasymand}\ O{\isacharbraceleft}W{\isacharparenleft}c{\isadigit{2}}{\isacharcomma}\ a{\isadigit{2}}{\isacharcomma}\ g{\isadigit{2}}{\isacharparenright}\ s{\isacharbar}c{\isacharbraceright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
%
\isadelimproof
\ \ %
\endisadelimproof
%
\isatagproof
\isacommand{using}\isamarkupfalse%
\ assms\ no{\isacharunderscore}contradictions\ \isacommand{by}\isamarkupfalse%
\ blast\isanewline
%
\isamarkupcmt{Recall that the we also expect the stronger property that the combination of obligatory maxims can't
 imply a contradiction. The added axiom also makes this test pass.%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
\isanewline
%
\endisadelimproof
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ distribution{\isacharcolon}\isanewline
\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymand}\ O\ {\isacharbraceleft}B{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymTurnstile}\ O\ {\isacharbraceleft}A\ \isactrlbold {\isasymand}\ B{\isacharbraceright}{\isachardoublequoteclose}\isanewline
%
\isadelimproof
\ \ %
\endisadelimproof
%
\isatagproof
\isacommand{using}\isamarkupfalse%
\ assms\ no{\isacharunderscore}contradictions\ \isacommand{by}\isamarkupfalse%
\ fastforce%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
The metaethical test suite ran on both Kroy's formalization and my formalizaion show two clear 
improvements. First, my formalization shows that obligatory maxims are permissible, whereas Kroy's 
paradoxically does not. Second, my formalization doesn't allow contradictory maxims, but Kroy's does. 
Both of these improvements are derived from the new axiom I added in my formalization that disallows 
contradictory obligations. Additionally, my formalization also improves on Kroy's by staying faithful to the 
strongest interpretation of the FUL, Korsgaard's practical contradiction interpretation. (maybe stick 
philosophical writing here or above?)%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Formalization Specific Tests%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In this section, I explore tests specific to my formalization of the categorical imperative. First, 
in my previous (buggy) implementation of DDL, prohibiting contradictory obligation led to the strange 
result that all permissible actions are obligatory. I will test if this bug appears in this implementation 
as well.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ bug{\isacharcolon}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}permissible\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ w\ {\isasymlongrightarrow}\ O{\isacharbraceleft}W{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ {\isacharbar}\ c{\isacharbraceright}\ w{\isachardoublequoteclose}\isanewline
\ \ \isacommand{nitpick}\isamarkupfalse%
{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{\color{blue}
Nitpick found a counterexample for card i = 1 and card s = 2:

  Free variables:
    a = ($\lambda x. \_$)($s_1$ := ($\lambda x. \_$)($i_1$ := False), $s_2$ := ($\lambda x. \_$)($i_1$ := False))
    c = ($\lambda x. \_$)($i_1$ := False)
    g = ($\lambda x. \_$)($i_1$ := False)
    s = $s_2$
    w = undefined
\color{black}
This strange result does not hold; good!%
}\isanewline
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/paper412.thy%:%
%:%10=1%:%
%:%11=1%:%
%:%12=2%:%
%:%13=3%:%
%:%27=6%:%
%:%39=8%:%
%:%40=9%:%
%:%41=10%:%
%:%42=11%:%
%:%46=13%:%
%:%47=14%:%
%:%48=15%:%
%:%49=16%:%
%:%50=17%:%
%:%51=18%:%
%:%52=19%:%
%:%53=20%:%
%:%54=21%:%
%:%55=22%:%
%:%56=23%:%
%:%57=24%:%
%:%58=25%:%
%:%59=26%:%
%:%60=27%:%
%:%61=28%:%
%:%63=30%:%
%:%64=30%:%
%:%66=31%:%
%:%67=32%:%
%:%68=32%:%
%:%69=33%:%
%:%70=33%:%
%:%72=34%:%
%:%73=35%:%
%:%74=35%:%
%:%75=36%:%
%:%76=36%:%
%:%78=37%:%
%:%79=38%:%
%:%80=38%:%
%:%81=39%:%
%:%82=40%:%
%:%83=40%:%
%:%84=41%:%
%:%86=42%:%
%:%89=44%:%
%:%90=45%:%
%:%91=46%:%
%:%93=48%:%
%:%94=48%:%
%:%95=49%:%
%:%97=50%:%
%:%98=51%:%
%:%99=52%:%
%:%100=53%:%
%:%101=54%:%
%:%102=54%:%
%:%103=55%:%
%:%104=56%:%
%:%105=56%:%
%:%106=57%:%
%:%108=58%:%
%:%109=59%:%
%:%110=60%:%
%:%111=61%:%
%:%112=62%:%
%:%113=62%:%
%:%114=63%:%
%:%115=64%:%
%:%116=64%:%
%:%117=65%:%
%:%119=66%:%
%:%120=67%:%
%:%121=68%:%
%:%122=69%:%
%:%123=70%:%
%:%126=72%:%
%:%127=73%:%
%:%129=75%:%
%:%130=75%:%
%:%131=76%:%
%:%132=77%:%
%:%133=78%:%
%:%134=79%:%
%:%141=80%:%
%:%142=80%:%
%:%143=81%:%
%:%144=81%:%
%:%145=82%:%
%:%146=82%:%
%:%148=83%:%
%:%149=84%:%
%:%150=84%:%
%:%151=85%:%
%:%152=85%:%
%:%153=86%:%
%:%154=86%:%
%:%155=86%:%
%:%156=87%:%
%:%166=89%:%
%:%167=90%:%
%:%168=91%:%
%:%169=92%:%
%:%170=93%:%
%:%171=94%:%
%:%172=95%:%
%:%173=96%:%
%:%175=98%:%
%:%176=98%:%
%:%177=99%:%
%:%178=99%:%
%:%179=100%:%
%:%181=101%:%
%:%182=102%:%
%:%183=102%:%
%:%184=103%:%
%:%185=104%:%
%:%186=104%:%
%:%187=105%:%
%:%189=106%:%
%:%190=107%:%
%:%191=107%:%
%:%192=108%:%
%:%193=109%:%
%:%194=109%:%
%:%195=110%:%
%:%196=111%:%
%:%198=112%:%
%:%199=112%:%
%:%200=113%:%
%:%201=114%:%
%:%203=115%:%
%:%204=115%:%
%:%205=116%:%
%:%212=117%:%
%:%213=117%:%
%:%214=118%:%
%:%215=118%:%
%:%216=119%:%
%:%217=119%:%
%:%218=119%:%
%:%219=120%:%
%:%220=120%:%
%:%221=121%:%
%:%222=121%:%
%:%223=121%:%
%:%224=122%:%
%:%225=122%:%
%:%227=123%:%
%:%237=125%:%
%:%238=126%:%
%:%239=127%:%
%:%240=128%:%
%:%241=129%:%
%:%242=130%:%
%:%243=131%:%
%:%244=132%:%
%:%245=133%:%
%:%246=134%:%
%:%247=135%:%
%:%248=136%:%
%:%249=137%:%
%:%250=138%:%
%:%251=139%:%
%:%252=140%:%
%:%253=141%:%
%:%254=142%:%
%:%255=143%:%
%:%256=144%:%
%:%257=145%:%
%:%258=146%:%
%:%259=147%:%
%:%260=148%:%
%:%261=149%:%
%:%262=150%:%
%:%263=151%:%
%:%264=152%:%
%:%265=153%:%
%:%266=154%:%
%:%267=155%:%
%:%268=156%:%
%:%269=157%:%
%:%270=158%:%
%:%271=159%:%
%:%272=160%:%
%:%273=161%:%
%:%274=162%:%
%:%275=163%:%
%:%276=164%:%
%:%280=166%:%
%:%281=167%:%
%:%282=168%:%
%:%284=170%:%
%:%285=170%:%
%:%286=171%:%
%:%287=172%:%
%:%288=172%:%
%:%290=172%:%
%:%294=172%:%
%:%295=172%:%
%:%297=173%:%
%:%298=174%:%
%:%299=175%:%
%:%300=176%:%
%:%301=177%:%
%:%302=178%:%
%:%312=181%:%
%:%313=182%:%
%:%314=183%:%
%:%323=185%:%
%:%335=187%:%
%:%336=188%:%
%:%337=189%:%
%:%338=190%:%
%:%339=191%:%
%:%340=192%:%
%:%341=193%:%
%:%342=194%:%
%:%343=195%:%
%:%344=196%:%
%:%345=197%:%
%:%346=198%:%
%:%347=199%:%
%:%348=200%:%
%:%350=202%:%
%:%351=202%:%
%:%352=203%:%
%:%355=204%:%
%:%359=204%:%
%:%360=204%:%
%:%365=204%:%
%:%368=205%:%
%:%369=206%:%
%:%370=206%:%
%:%371=207%:%
%:%374=208%:%
%:%378=208%:%
%:%379=208%:%
%:%384=208%:%
%:%387=209%:%
%:%388=210%:%
%:%389=210%:%
%:%390=211%:%
%:%393=212%:%
%:%397=212%:%
%:%398=212%:%
%:%403=212%:%
%:%406=213%:%
%:%407=214%:%
%:%408=214%:%
%:%409=215%:%
%:%412=216%:%
%:%416=216%:%
%:%417=216%:%
%:%426=218%:%
%:%427=219%:%
%:%428=220%:%
%:%429=221%:%
%:%430=222%:%
%:%431=223%:%
%:%432=224%:%
%:%434=226%:%
%:%435=226%:%
%:%436=227%:%
%:%437=228%:%
%:%438=228%:%
%:%440=228%:%
%:%444=228%:%
%:%445=228%:%
%:%447=229%:%
%:%448=230%:%
%:%449=231%:%
%:%450=232%:%
%:%451=233%:%
%:%452=234%:%
%:%453=235%:%
%:%454=236%:%
%:%455=237%:%
%:%456=238%:%
%:%457=239%:%
%:%467=241%:%
%:%468=242%:%
%:%470=244%:%
%:%471=244%:%
%:%472=245%:%
%:%475=246%:%
%:%479=246%:%
%:%480=246%:%
%:%482=247%:%
%:%492=249%:%
%:%493=250%:%
%:%495=252%:%
%:%496=252%:%
%:%497=253%:%
%:%500=254%:%
%:%504=254%:%
%:%505=254%:%
%:%506=254%:%
%:%508=255%:%
%:%509=256%:%
%:%519=258%:%
%:%520=259%:%
%:%521=260%:%
%:%522=261%:%
%:%526=263%:%
%:%527=264%:%
%:%528=265%:%
%:%530=267%:%
%:%531=267%:%
%:%532=268%:%
%:%533=269%:%
%:%534=270%:%
%:%535=270%:%
%:%537=270%:%
%:%541=270%:%
%:%542=270%:%
%:%544=271%:%
%:%545=272%:%
%:%546=273%:%
%:%547=274%:%
%:%548=275%:%
%:%549=276%:%
%:%550=277%:%
%:%551=278%:%
%:%552=279%:%
%:%553=280%:%
%:%563=282%:%
%:%564=283%:%
%:%565=284%:%
%:%567=286%:%
%:%568=286%:%
%:%569=287%:%
%:%570=288%:%
%:%571=288%:%
%:%573=288%:%
%:%577=288%:%
%:%578=288%:%
%:%580=289%:%
%:%581=290%:%
%:%582=291%:%
%:%583=292%:%
%:%584=293%:%
%:%585=294%:%
%:%586=295%:%
%:%587=296%:%
%:%588=297%:%
%:%589=298%:%
%:%599=300%:%
%:%600=301%:%
%:%601=302%:%
%:%602=303%:%
%:%604=305%:%
%:%605=305%:%
%:%606=306%:%
%:%609=307%:%
%:%613=307%:%
%:%614=307%:%
%:%615=307%:%
%:%617=308%:%
%:%623=308%:%
%:%626=309%:%
%:%627=310%:%
%:%628=310%:%
%:%629=311%:%
%:%632=312%:%
%:%636=312%:%
%:%637=312%:%
%:%638=312%:%
%:%640=313%:%
%:%646=313%:%
%:%649=314%:%
%:%650=315%:%
%:%651=315%:%
%:%652=316%:%
%:%653=317%:%
%:%656=318%:%
%:%660=318%:%
%:%661=318%:%
%:%662=318%:%
%:%664=319%:%
%:%665=320%:%
%:%671=320%:%
%:%674=321%:%
%:%675=322%:%
%:%676=322%:%
%:%677=323%:%
%:%678=324%:%
%:%681=325%:%
%:%685=325%:%
%:%686=325%:%
%:%687=325%:%
%:%696=327%:%
%:%697=328%:%
%:%698=329%:%
%:%699=330%:%
%:%700=331%:%
%:%701=332%:%
%:%702=333%:%
%:%711=335%:%
%:%723=337%:%
%:%724=338%:%
%:%725=339%:%
%:%726=340%:%
%:%728=342%:%
%:%729=342%:%
%:%730=343%:%
%:%731=344%:%
%:%732=344%:%
%:%734=344%:%
%:%738=344%:%
%:%739=344%:%
%:%741=345%:%
%:%742=346%:%
%:%743=347%:%
%:%744=348%:%
%:%745=349%:%
%:%746=350%:%
%:%747=351%:%
%:%748=352%:%
%:%749=353%:%
%:%750=354%:%
%:%751=355%:%
%:%752=355%:%

### 2021-11-21 paper/output/document/application.tex
compiled

%
\begin{isabellebody}%
\setisabellecontext{application}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Applications \label{sec:applications}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In this section, I will demonstrate possible applications of my formalization of the FUL. I 
will present two kinds of applications. First, I will formalize a classical ethical dilemma in 
Kantian literature, the case of the murderer at the door. This will demonstrate the utility of computational
ethics in helping philosophers think about ethical dilemmas. Second, I will encode some ``common sense"
facts into the system and then test the results of applying this more powerful system to common
ethical dilemmas. This section will serve as a prototype of the kind of reasoning that this kind of 
computational ethics can do and will demonstrate the utility of computational ethics in performing 
everyday ethical reasoning. This section will also outline what future work is necessary to use an 
ethical reasoner like the one I build in practice. Finally, I will also philosophically analyze the possibility and value of 
applications like these. Specifically, I will consider to what extent humans should let computers do 
ethical reasoning on our behalf.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Right to Lie \label{sec:rtl}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In this section, I draw on examples of ethical reasoning as presented in Korsgaard's right to lie.
She analyzes the example of someone who shows up at your door and asks, "Is Sara home?" Unbeknownst to them, 
you know that they want to know Sara's location in order to murder her. Ordinary moral intuition seems
to imply that in this situation, if Sara is home, you should lie and say that she is not in order to 
protect her from the murderer. However, the categorical imperative seems to prohibit lying in all 
circumstances. More specifically, when universalized, lies will no longer be believed, so it seems 
like lying could never be an effective way of achieving any goal when universalized. Korsgaard points out
that ``we believe what is said to us in a given context because most of the time people in that context 
say what they really think" \citep[4]{KorsgaardRTL}. First, I will formalize this argument.

The first step in formalizing this argument is defining the relevant terms.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{consts}\isamarkupfalse%
\ believe{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}s{\isasymRightarrow}t{\isasymRightarrow}t{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{Person s::subject believes sentence t::term%
}\isanewline
\isacommand{consts}\isamarkupfalse%
\ utter{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}s{\isasymRightarrow}t{\isasymRightarrow}t{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{Person s::subject utters sentence t::term%
}\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ utter{\isacharunderscore}falsehood{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}s{\isasymRightarrow}t{\isasymRightarrow}t{\isachardoublequoteclose}\ \isakeyword{where}\isanewline
{\isachardoublequoteopen}utter{\isacharunderscore}falsehood\ s\ t\ {\isasymequiv}\ \ {\isacharparenleft}utter\ s\ t{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ t{\isacharparenright}{\isachardoublequoteclose}\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ knowingly{\isacharunderscore}utter{\isacharunderscore}falsehood{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}s{\isasymRightarrow}t{\isasymRightarrow}t{\isachardoublequoteclose}\ \isakeyword{where}\isanewline
{\isachardoublequoteopen}knowingly{\isacharunderscore}utter{\isacharunderscore}falsehood\ s\ t\ {\isasymequiv}\ {\isacharparenleft}utter{\isacharunderscore}falsehood\ s\ t{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}believe\ s\ t{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{Person s::subject utters a falsehood t::term if they utter t and t is false.%
}\isanewline
\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ lie{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}lie\ {\isasymequiv}\ {\isasymlambda}\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}{\isachardot}\ {\isasymexists}t{\isachardot}\ {\isacharparenleft}a\ \isactrlbold {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymlambda}s{\isachardot}\ knowingly{\isacharunderscore}utter{\isacharunderscore}falsehood\ s\ t{\isacharparenright}{\isacharparenright}\ {\isasymand}\ {\isacharparenleft}{\isasymexists}p{\isachardot}\ {\isasymforall}w{\isachardot}\ {\isacharparenleft}g\ \isactrlbold {\isasymrightarrow}\ believe\ p\ t{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{A maxim is a lie if 
    (a) the act requires knowingly uttering a falsehood 
    (b) the end requires that some person $p$ believe the false statement $t$%
}%
\begin{isamarkuptext}%
To avoid focus on the case of conscious, intentional wrongdoing, I focus on ``knowing lies," 
in which the speaker is aware that they are lying. It is uncontroversial that an act is a knowing lie
if the speaker utters a false statement that they do not believe. The second half of this definition, which 
requires that the goal of the action of lying be to decieve, is inspired by  Korsgaard's interpretation 
of a lie, which understands a lie as a kind of falsehood that is usually effective \emph{because} it decieves
\citep[4]{KorsgaardRTL}.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
With the above logical background, I can now show that maxims that involve lying are prohibited.
First, I define the subject and maxim at hand.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{consts}\isamarkupfalse%
\ me{\isacharcolon}{\isacharcolon}s\isanewline
%
\isamarkupcmt{I am trying to reason about my obligations so I will define myself as a specific subject.%
}\isanewline
\isacommand{consts}\isamarkupfalse%
\ m{\isacharcolon}{\isacharcolon}maxim\isanewline
%
\isamarkupcmt{I will also define a maxim $m$. My goal is to show that if $m$ is a maxim about lying, then $m$
is prohibited.%
}%
\begin{isamarkuptext}%
The following lemma shows the common sense necessary to determine that lying is prohibited.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ lying{\isacharunderscore}prohibited{\isacharcolon}\isanewline
\ \ \isakeyword{fixes}\ c\isanewline
\ \ \isakeyword{fixes}\ a\isanewline
\ \ \isakeyword{fixes}\ g\isanewline
\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}m\ {\isasymequiv}\ {\isacharparenleft}c{\isacharcolon}{\isacharcolon}t{\isacharcomma}\ a{\isacharcolon}{\isacharcolon}os{\isacharcomma}\ g{\isacharcolon}{\isacharcolon}t{\isacharparenright}{\isachardoublequoteclose}\isanewline
\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}w{\isachardot}\ {\isasymforall}s{\isachardot}\ well{\isacharunderscore}formed\ m\ s\ w{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{Initial set-up, m is a well-formed maxim composed of some circumstances, act, and goal.%
}\isanewline
\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}lie\ m{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{$m$ is a maxim about lying. Precisely, it is a maxim in which the action is to knowingly utter a 
falsehood and the goal requires that someone believe this falsehood.%
}\isanewline
\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}t\ w{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isasymforall}p{\isachardot}\ utter{\isacharunderscore}falsehood\ p\ t\ w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ \isactrlbold {\isasymnot}\ {\isacharparenleft}believe\ p\ t{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{Assumption that if everyone utters false statement t, then no one will believe t.%
}\isanewline
\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}w{\isachardot}\ c\ w{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{Restrict our focus to worlds in which the circumstances hold, as these are the morally interesting 
worlds for this example. Basically an irrelevant technical detail.%
}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}prohibited\ m\ me{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
\isacommand{proof}\isamarkupfalse%
\ {\isacharminus}\ \isanewline
\ \ \isacommand{have}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymforall}p\ w{\isachardot}\ {\isacharparenleft}W\ m\ p{\isacharparenright}\ w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymTurnstile}\ {\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ g{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
\ \ \ \ \isacommand{by}\isamarkupfalse%
\ {\isacharparenleft}smt\ assms{\isacharparenleft}{\isadigit{1}}{\isacharparenright}\ assms{\isacharparenleft}{\isadigit{2}}{\isacharparenright}\ assms{\isacharparenleft}{\isadigit{5}}{\isacharparenright}\ case{\isacharunderscore}prod{\isacharunderscore}beta\ fst{\isacharunderscore}conv\ old{\isachardot}prod{\isachardot}exhaust\ snd{\isacharunderscore}conv{\isacharparenright}\isanewline
%
\isamarkupcmt{Unlike many of the other proofs in this project, this proof was a little heavier and required some manual
work to produce. I divided the proof into the intermediate steps shown here, and Isabelle was able to do 
the rest! This step says that if $m$ is universalized, then the circumstances won't lead to the goal, 
which is quite close to the idea of the maxim not being universalizable.%
}\isanewline
\ \ \isacommand{have}\isamarkupfalse%
\ {\isachardoublequoteopen}not{\isacharunderscore}universalizable\ m\ me{\isachardoublequoteclose}\isanewline
\ \ \ \ \isacommand{by}\isamarkupfalse%
\ {\isacharparenleft}metis\ {\isacharparenleft}mono{\isacharunderscore}tags{\isacharcomma}\ lifting{\isacharparenright}\ assms{\isacharparenleft}{\isadigit{1}}{\isacharparenright}\ assms{\isacharparenleft}{\isadigit{2}}{\isacharparenright}\ case{\isacharunderscore}prod{\isacharunderscore}beta\ fst{\isacharunderscore}conv\ snd{\isacharunderscore}conv{\isacharparenright}\isanewline
\ \ \isacommand{thus}\isamarkupfalse%
\ {\isacharquery}thesis\isanewline
\ \ \ \ \isacommand{using}\isamarkupfalse%
\ FUL\ assms{\isacharparenleft}{\isadigit{2}}{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
\ blast\ \isanewline
\isacommand{qed}\isamarkupfalse%
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
The above is an example of how my system can perform ``applied ethical reasoning." In Chapter 2
and Chapter 3, I performed metaethical reasoning while testing different formalizations of the FUL. Metaethical
reasoning analyzes properties of moral thought itself \citep{sepme}. Because metaethics is about ethics itself,
and not about the actual dilemmas that ethics is supposed to help us resolve, this kind of reasoning requires
very little additional knowledge beyond that of the ethical theory in question. Indeed, in previous chapters,
I perform metaethical reasoning using my system (which formalizes an ethical theory) and basic logical
facts and objects. This kind of reasoning contrasts with ``applied ethical reasoning," which is the use of
ethics to actually resolve ethical dilemmas and make judgements about what an agent should or should not do.
Applied ethical reasoning is about the situation an agent is in, not about an ethical theory as a whole,
abstract entity. In this section, I expore how my system can perform extended applied ethical reasoning. 
Metaethical reasoning is most interesting to philosophers who are trying to formulate the ``best" or 
most correct theory of ethics. Applied ethical reasoning, on the other hand, is useful to ordinary people
who are trying to decide how to live their lives. These two kinds of reasoning represent the two motivations 
for automated ethics. Metaethical reasoning is more directly a way to perform computational ethics, or use a computer
system to do philosophy. Applied ethical reasoning is also relevant to philosophers (applied ethicists 
generally perform this kind of reasoning), but is also relevant to AI agents or people seeking to navigate the world.
In order for automated ethics to guide AI agents, it must perform applied ethical reasoning.

One challenge of applied ethical reasoning is that it requires more common sense knowledge than metaethical
reasoning. Applied ethical reasoning focuses on a particular ethical dilemma and thus requires enough 
common sense to understand the dilemma and options at hand. For example, for an applied ethicist to 
evaluate the permissibility of lying, they need some robust definition of the term lying and likely some
understanding about the activities of communication and truth telling. In this section, I attempt to
endow my system with this kind of common sense in the specific case of lying. Indeed, in order for my 
system to be used to perform applied ethical reasoning, it will need to be equipped with a database
of common sense facts and definitions as I present in this section. My system will contribute the core
reasoning about the Formula of Universal Law, but this reasoning must be applied to objects that are defined
in this common sense database. In this section, I try to understand what this common sense reasoning looks like
for the specific example of lying. I will examine how different sets of common sense facts impact the 
judgements that my system comes to.

Because these common sense facts can entirely determine my system's judgement, they are part of the trusted
code base for my system. In order for someone to trust my system's judgements, they must trust that the
common sense database is correct. This common sense reasoning is also not a part of my system—in order for my
system to be used, someone must develop a common sense database for the particular situation at hand. 
The challenge of endowing automated ethical reasoners with common sense reasoning is not unique to my 
system, and virtually all prior attempts in machine ethics face similar challenges.

The specific kind of common sense reasoning required for automated Kantian ethics appears to be a challenge 
for automating Kantian ethics, and perhaps a reason that consequentialist or virtue ethical automated
agents would be within closer reach for automation. Ultimately, I still argue that Kantian ethics is 
easiest to automate because it will require fewer, less controversial common facts than other ethical
systems. As this example demonstrates, Kantian ethics requires a definition of lying (which any other 
theory would also requires) and the knowledge that if everyone lies in a given context, no one will believe 
each other in that particular context. This latter fact may not be required for every ethical theory, 
but is relatively uncontroversial. Indeed, Korsgaard doesn't even bother to give a justification for 
this fact. It is a kind of intuition about human behavior that is generally accepted. Neither a definition 
of lying nor this property of lying seem like unreasonable prerequisites for ethical reasoning.

Consequentialism, on the other hand, would require much more specific data about the consequences of 
a lie, perhaps for the specific person's credibility, for the victim of the lie, for the third-parties 
watching the lie unfold. Indeed, consequentialism more numerous and specific judgements, all of which are 
likely to be more controversial than the two outlined above for Kantian ethics. Similarly, virtue ethics
would likely require information about the actor's entire moral character, including their attitude
towards the lie and their moral history. Virtue ethics would also require robust definitions of the 
relevant virtues, in addition to a definition of lying. Thus, while Kantian ethics requires some 
common sense reasoning, it requires fewer and less controversial background facts than other ethical theories.

This section will provide additional examples of the kinds of commons sense required to get my system
off the ground. I will aim to use as lean and uncontroversial of a common sense database as possible
to achieve results as robust and powerful as possible. This serves as evidence for the ease of automating
Kantian ethics, an example of what additional work my system requires, and a demonstration of the contributions
that I make.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/application.thy%:%
%:%24=6%:%
%:%36=8%:%
%:%37=9%:%
%:%38=10%:%
%:%39=11%:%
%:%40=12%:%
%:%41=13%:%
%:%42=14%:%
%:%43=15%:%
%:%44=16%:%
%:%45=17%:%
%:%46=18%:%
%:%55=20%:%
%:%67=22%:%
%:%68=23%:%
%:%69=24%:%
%:%70=25%:%
%:%71=26%:%
%:%72=27%:%
%:%73=28%:%
%:%74=29%:%
%:%75=30%:%
%:%76=31%:%
%:%77=32%:%
%:%79=34%:%
%:%80=34%:%
%:%82=35%:%
%:%83=35%:%
%:%84=36%:%
%:%85=36%:%
%:%87=37%:%
%:%88=37%:%
%:%89=38%:%
%:%90=38%:%
%:%91=39%:%
%:%92=40%:%
%:%93=40%:%
%:%94=41%:%
%:%96=42%:%
%:%97=42%:%
%:%98=47%:%
%:%99=48%:%
%:%100=48%:%
%:%101=49%:%
%:%103=50%:%
%:%104=51%:%
%:%105=52%:%
%:%108=54%:%
%:%109=55%:%
%:%110=56%:%
%:%111=57%:%
%:%112=58%:%
%:%113=59%:%
%:%117=61%:%
%:%118=62%:%
%:%120=64%:%
%:%121=64%:%
%:%123=65%:%
%:%124=65%:%
%:%125=66%:%
%:%126=66%:%
%:%128=67%:%
%:%129=68%:%
%:%132=70%:%
%:%134=72%:%
%:%135=72%:%
%:%136=73%:%
%:%137=74%:%
%:%138=75%:%
%:%139=76%:%
%:%140=77%:%
%:%142=78%:%
%:%143=78%:%
%:%144=79%:%
%:%146=80%:%
%:%147=81%:%
%:%148=81%:%
%:%149=82%:%
%:%151=83%:%
%:%152=83%:%
%:%153=84%:%
%:%155=85%:%
%:%156=86%:%
%:%157=86%:%
%:%158=87%:%
%:%165=88%:%
%:%166=88%:%
%:%167=89%:%
%:%168=89%:%
%:%169=90%:%
%:%170=90%:%
%:%172=91%:%
%:%173=92%:%
%:%174=93%:%
%:%175=94%:%
%:%176=94%:%
%:%177=95%:%
%:%178=95%:%
%:%179=96%:%
%:%180=96%:%
%:%181=97%:%
%:%182=97%:%
%:%183=98%:%
%:%184=98%:%
%:%185=98%:%
%:%186=99%:%
%:%196=101%:%
%:%197=102%:%
%:%198=103%:%
%:%199=104%:%
%:%200=105%:%
%:%201=106%:%
%:%202=107%:%
%:%203=108%:%
%:%204=109%:%
%:%205=110%:%
%:%206=111%:%
%:%207=112%:%
%:%208=113%:%
%:%209=114%:%
%:%210=115%:%
%:%211=116%:%
%:%212=117%:%
%:%213=118%:%
%:%214=119%:%
%:%215=120%:%
%:%216=121%:%
%:%217=122%:%
%:%218=123%:%
%:%219=124%:%
%:%220=125%:%
%:%221=126%:%
%:%222=127%:%
%:%223=128%:%
%:%224=129%:%
%:%225=130%:%
%:%226=131%:%
%:%227=132%:%
%:%228=133%:%
%:%229=134%:%
%:%230=135%:%
%:%231=136%:%
%:%232=137%:%
%:%233=138%:%
%:%234=139%:%
%:%235=140%:%
%:%236=141%:%
%:%237=142%:%
%:%238=143%:%
%:%239=144%:%
%:%240=145%:%
%:%241=146%:%
%:%242=147%:%
%:%243=148%:%
%:%244=149%:%
%:%245=150%:%
%:%246=151%:%
%:%247=152%:%
%:%248=153%:%
%:%249=154%:%
%:%250=155%:%
%:%251=156%:%
%:%252=157%:%
%:%253=158%:%
%:%254=159%:%
%:%255=160%:%
%:%256=161%:%
%:%257=162%:%
%:%258=163%:%

### 2021-11-21 paper/output/document/application.tex
early applications work

@@
 %
-\isamarkupsubsection{Right to Lie \label{sec:rtl}%
+\isamarkupsubsection{Preliminary Lying Work \label{sec:lyingprelim}%
 }
@@
 %
+\begin{isamarkuptext}%
+Now that I have formalized Korsgaard's sketch of an argument for why lying is prohibited, I will 
+implement her argument for why jokes are permissible. Specifically, she considers a joke a story that is 
+false and argues that joking is permissible because ``the universal practice of lying in the context of jokes
+does not interfere with the purpose of jokes, which is to amuse and does not depend on
+deception" \citep[4]{KorsgaardRTL}. Let's define a joke.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{abbreviation}\isamarkupfalse%
+\ joke{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
+{\isachardoublequoteopen}joke\ {\isasymequiv}\ {\isasymlambda}\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}{\isachardot}\ \ {\isasymexists}t{\isachardot}\ {\isacharparenleft}a\ \isactrlbold {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymlambda}s{\isachardot}\ knowingly{\isacharunderscore}utter{\isacharunderscore}falsehood\ s\ t{\isacharparenright}{\isacharparenright}\ {\isasymand}\ {\isasymnot}\ {\isacharparenleft}{\isasymexists}p{\isachardot}\ {\isasymforall}w{\isachardot}\ {\isacharparenleft}g\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}believe\ p\ t{\isacharparenright}{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}%
+\begin{isamarkuptext}%
+This definition of a joke merely defines a joke as a falsehood uttered for some purpose that 
+emph{doesn't} require deception, where deception involves someone believing the uttered falsehood. Notice 
+that this is quite a thin definition of a joke; it doesn't require any conception of humor but merely
+distinguishes jokes from lies. As far as common sense reasoning goes, this is a relatively thin proposition. 
+I will now demonstrate that this conception of a joke is sufficient to show that joking is permissible.
+
+I will reuse some of the logical structure from the lying example, namely the maxim $m$ and subject $me$. 
+I will also reuse the same assumptions to show that, under the same set of ``common sense" facts, lying is
+prohibited but joking is not.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ joking{\isacharunderscore}not{\isacharunderscore}prohibited{\isacharcolon}\isanewline
+\ \ \isakeyword{fixes}\ c\isanewline
+\ \ \isakeyword{fixes}\ a\isanewline
+\ \ \isakeyword{fixes}\ g\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}m\ {\isasymequiv}\ {\isacharparenleft}c{\isacharcolon}{\isacharcolon}t{\isacharcomma}\ a{\isacharcolon}{\isacharcolon}os{\isacharcomma}\ g{\isacharcolon}{\isacharcolon}t{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}w{\isachardot}\ {\isasymforall}s{\isachardot}\ well{\isacharunderscore}formed\ m\ s\ w{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Initial set-up, m is a well-formed maxim composed of some circumstances, act, and goal.%
+}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}joke\ m{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{$m$ is a maxim about joking. Precisely, it is a maxim in which the action is to knowingly utter a 
+falsehood and the goal does not require that someone believe this falsehood.%
+}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}t\ w{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isasymforall}p{\isachardot}\ utter{\isacharunderscore}falsehood\ p\ t\ w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ \isactrlbold {\isasymnot}\ {\isacharparenleft}believe\ p\ t{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Assumption that if everyone utters false statement t, then no one will believe t. Recall that this
+is the most significant piece of common sense reasoning necessary for this example.%
+}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}w{\isachardot}\ c\ w{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Restrict our focus to worlds in which the circumstances hold, as these are the morally interesting 
+worlds for this example. Basically an irrelevant technical detail.%
+}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}permissible\ m\ me{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{by}\isamarkupfalse%
+\ {\isacharparenleft}smt\ assms{\isacharparenleft}{\isadigit{1}}{\isacharparenright}\ assms{\isacharparenleft}{\isadigit{2}}{\isacharparenright}\ assms{\isacharparenleft}{\isadigit{3}}{\isacharparenright}\ case{\isacharunderscore}prod{\isacharunderscore}conv{\isacharparenright}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+To summarize, in this section I introduce the role of common sense reasoning in my system and 
+demonstrate the kind of common sense facts necessary to show that lying is generally prohibited and 
+jokes are permissible. I conclude that this kind of sophisticated ethical reasoning requires relatively
+thin common sense facts and robust definitions of the terms involved. Thus, while common sense reasoning 
+is an obstacle that must be overcome for my system to be used, it is not insurmountable.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsection{Lying to a Liar \label{sec:lyingtoliar}%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
+Once Korsgaard does some preliminary work differentiating between lies and jokes, she begins the 
+meat of her argument, which examines the case of the murderer at the door. Recall that the murderer
+appears at your door and asks if their intended victim is at home. Ordinary intuition requires that it 
+is at the very least permissible (if not obligatory) to lie to the murderer in order to protect the 
+victim. Korsgaard notes that a murderer who wishes to find their victim cannot simply announce their
+intentions to murder; instead, he must ``must suppose that you do not know who he is and
+what he has in mind" \citep[5]{KorsgaaardRTL}. Thus, she can modify the maxim in question and specifies
+that when someone lies to you, you are allowed to lie to them. The maxim of lying to the murderer is 
+thus actually the maxim of lying to a liar, which she argues is permissible. In this section, I will 
+formalize her argument for lying to a liar.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{consts}\isamarkupfalse%
+\ murderer{\isacharcolon}{\isacharcolon}s\isanewline
+\isacommand{consts}\isamarkupfalse%
+\ not{\isacharunderscore}a{\isacharunderscore}murderer{\isacharcolon}{\isacharcolon}t\isanewline
+\isacommand{consts}\isamarkupfalse%
+\ victim{\isacharunderscore}not{\isacharunderscore}home{\isacharcolon}{\isacharcolon}t\isanewline
+\isacommand{consts}\isamarkupfalse%
+\ when{\isacharunderscore}at{\isacharunderscore}my{\isacharunderscore}door{\isacharcolon}{\isacharcolon}t\isanewline
+\isacommand{consts}\isamarkupfalse%
+\ find{\isacharunderscore}victim{\isacharcolon}{\isacharcolon}t\isanewline
+\isacommand{consts}\isamarkupfalse%
+\ protect{\isacharunderscore}victim{\isacharcolon}{\isacharcolon}t\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ murderers{\isacharunderscore}maxim{\isacharcolon}{\isacharcolon}maxim\ \isakeyword{where}\ \isanewline
+{\isachardoublequoteopen}murderers{\isacharunderscore}maxim\ {\isasymequiv}\ {\isacharparenleft}when{\isacharunderscore}at{\isacharunderscore}my{\isacharunderscore}door{\isacharcomma}\ {\isasymlambda}s{\isachardot}\ knowingly{\isacharunderscore}utter{\isacharunderscore}falsehood\ s\ not{\isacharunderscore}a{\isacharunderscore}murderer{\isacharcomma}\ find{\isacharunderscore}victim{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ murderer{\isacharunderscore}at{\isacharunderscore}door{\isacharcolon}{\isacharcolon}t\ \isakeyword{where}\ \isanewline
+{\isachardoublequoteopen}murderer{\isacharunderscore}at{\isacharunderscore}door\ {\isasymequiv}\ W\ murderers{\isacharunderscore}maxim\ murderer{\isachardoublequoteclose}\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ my{\isacharunderscore}maxim{\isacharcolon}{\isacharcolon}maxim\ \isakeyword{where}\ \isanewline
+{\isachardoublequoteopen}my{\isacharunderscore}maxim\ {\isasymequiv}\ {\isacharparenleft}murderer{\isacharunderscore}at{\isacharunderscore}door{\isacharcomma}\ \ {\isasymlambda}s{\isachardot}\ knowingly{\isacharunderscore}utter{\isacharunderscore}falsehood\ s\ victim{\isacharunderscore}not{\isacharunderscore}home{\isacharcomma}\ protect{\isacharunderscore}victim{\isacharparenright}{\isachardoublequoteclose}%
+\begin{isamarkuptext}%
+First, I will show that using the same common sense reasoning justified above, the murderer's
+maxim is prohibited.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ murderers{\isacharunderscore}maxim{\isacharunderscore}prohibited{\isacharcolon}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}w{\isachardot}\ well{\isacharunderscore}formed\ murderers{\isacharunderscore}maxim\ murderer\ w{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Initial set-up, the murderer's maxim is a well-formed maxim composed of some circumstances, act, and goal.%
+}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}find{\isacharunderscore}victim\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}believe\ me\ not{\isacharunderscore}a{\isacharunderscore}murderer{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}t\ w{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isasymforall}p{\isachardot}\ utter{\isacharunderscore}falsehood\ p\ t\ w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ \isactrlbold {\isasymnot}\ {\isacharparenleft}believe\ p\ t{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Assumption that if everyone utters false statement t, then no one will believe t. Recall that this
+is the most significant piece of common sense reasoning necessary for this example.%
+}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}w{\isachardot}\ when{\isacharunderscore}at{\isacharunderscore}my{\isacharunderscore}door\ w{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Restrict our focus to worlds in which the circumstance of the murderer being at my door holds, as 
+these are the morally interesting worlds for this example. Basically an irrelevant technical detail.%
+}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}prohibited\ murderers{\isacharunderscore}maxim\ murderer{\isacharparenright}{\isachardoublequoteclose}\ \ \ \isanewline
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+\isacommand{proof}\isamarkupfalse%
+\ {\isacharminus}\ \isanewline
+%
+\isamarkupcmt{Again, this proof is too heavy for Isabelle to finish on its own, so I needed to specify some
+intermediate steps. The same intermediate steps as above sufficed.%
+}\isanewline
+\ \ \isacommand{have}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymforall}p\ w{\isachardot}\ {\isacharparenleft}W\ murderers{\isacharunderscore}maxim\ p{\isacharparenright}\ w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymTurnstile}\ {\isacharparenleft}find{\isacharunderscore}victim\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ find{\isacharunderscore}victim{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \ \ \isacommand{using}\isamarkupfalse%
+\ assms{\isacharparenleft}{\isadigit{2}}{\isacharparenright}\ assms{\isacharparenleft}{\isadigit{4}}{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
+\ auto\isanewline
+\ \ \ \isacommand{have}\isamarkupfalse%
+\ {\isachardoublequoteopen}not{\isacharunderscore}universalizable\ murderers{\isacharunderscore}maxim\ murderer{\isachardoublequoteclose}\isanewline
+\ \ \ \ \ \isacommand{using}\isamarkupfalse%
+\ assms{\isacharparenleft}{\isadigit{2}}{\isacharparenright}\ assms{\isacharparenleft}{\isadigit{4}}{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
+\ auto\isanewline
+\ \ \ \isacommand{thus}\isamarkupfalse%
+\ {\isacharquery}thesis\isanewline
+\ \ \ \ \ \isacommand{using}\isamarkupfalse%
+\ FUL\ assms{\isacharparenleft}{\isadigit{1}}{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
+\ blast\isanewline
+\ \isacommand{qed}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+\isanewline
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ lying{\isacharunderscore}to{\isacharunderscore}liar{\isacharunderscore}permissible{\isacharcolon}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}well{\isacharunderscore}formed\ murderers{\isacharunderscore}maxim\ murderer{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}well{\isacharunderscore}formed\ my{\isacharunderscore}maxim\ me{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ True%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+let M be the murderer and me be you.
+when M lies to you, you can lie to M.
+
+when M knowingly utters a falsehood with the goal of you believing the falsehood, you can lie to M.
+
+when M knowingly utters falsehood T with the goal of you believing T, you can knowingly
+utter falsehood K with the goal of M believing K.
+
+let circumstances C = when M knowingly utters falsehood T with the goal of you believing T
+let A = knowingly utter falsehood K with the goal of M believing K
+everyone adopts maxim, "C -> A" 
+if everyone adopts maxim "C->A", if they believe you believe C, then won't believe A (specifically K) (modify the universal lying assumption)
+M doesn't believe you believe C
+so M will believe A (might need to add this as an axiom)%
+\end{isamarkuptext}\isamarkuptrue%
+%
 \isadelimdocument
@@
 %:%258=163%:%
+%:%262=165%:%
+%:%263=166%:%
+%:%264=167%:%
+%:%265=168%:%
+%:%266=169%:%
+%:%268=171%:%
+%:%269=171%:%
+%:%270=172%:%
+%:%272=174%:%
+%:%273=175%:%
+%:%274=176%:%
+%:%275=177%:%
+%:%276=178%:%
+%:%277=179%:%
+%:%278=180%:%
+%:%279=181%:%
+%:%280=182%:%
+%:%282=184%:%
+%:%283=184%:%
+%:%284=185%:%
+%:%285=186%:%
+%:%286=187%:%
+%:%287=188%:%
+%:%288=189%:%
+%:%290=190%:%
+%:%291=190%:%
+%:%292=191%:%
+%:%294=192%:%
+%:%295=193%:%
+%:%296=193%:%
+%:%297=194%:%
+%:%299=195%:%
+%:%300=196%:%
+%:%301=196%:%
+%:%302=197%:%
+%:%304=198%:%
+%:%305=199%:%
+%:%306=199%:%
+%:%307=200%:%
+%:%310=201%:%
+%:%314=201%:%
+%:%315=201%:%
+%:%324=203%:%
+%:%325=204%:%
+%:%326=205%:%
+%:%327=206%:%
+%:%328=207%:%
+%:%337=209%:%
+%:%349=211%:%
+%:%350=212%:%
+%:%351=213%:%
+%:%352=214%:%
+%:%353=215%:%
+%:%354=216%:%
+%:%355=217%:%
+%:%356=218%:%
+%:%357=219%:%
+%:%358=220%:%
+%:%360=222%:%
+%:%361=222%:%
+%:%362=223%:%
+%:%363=223%:%
+%:%364=224%:%
+%:%365=224%:%
+%:%366=225%:%
+%:%367=225%:%
+%:%368=226%:%
+%:%369=226%:%
+%:%370=227%:%
+%:%371=227%:%
+%:%372=228%:%
+%:%373=228%:%
+%:%374=229%:%
+%:%375=230%:%
+%:%376=230%:%
+%:%377=231%:%
+%:%378=232%:%
+%:%379=232%:%
+%:%380=233%:%
+%:%382=235%:%
+%:%383=236%:%
+%:%385=238%:%
+%:%386=238%:%
+%:%387=239%:%
+%:%389=240%:%
+%:%390=240%:%
+%:%391=241%:%
+%:%392=242%:%
+%:%394=243%:%
+%:%395=244%:%
+%:%396=244%:%
+%:%397=245%:%
+%:%399=246%:%
+%:%400=247%:%
+%:%401=247%:%
+%:%402=248%:%
+%:%409=249%:%
+%:%410=249%:%
+%:%412=250%:%
+%:%413=251%:%
+%:%414=251%:%
+%:%415=252%:%
+%:%416=252%:%
+%:%417=253%:%
+%:%418=253%:%
+%:%419=253%:%
+%:%420=254%:%
+%:%421=254%:%
+%:%422=255%:%
+%:%423=255%:%
+%:%424=255%:%
+%:%425=256%:%
+%:%426=256%:%
+%:%427=257%:%
+%:%428=257%:%
+%:%429=257%:%
+%:%430=258%:%
+%:%436=258%:%
+%:%439=259%:%
+%:%440=260%:%
+%:%441=261%:%
+%:%442=261%:%
+%:%443=262%:%
+%:%444=263%:%
+%:%445=264%:%
+%:%447=264%:%
+%:%451=264%:%
+%:%461=267%:%
+%:%462=268%:%
+%:%463=269%:%
+%:%464=270%:%
+%:%465=271%:%
+%:%466=272%:%
+%:%467=273%:%
+%:%468=274%:%
+%:%469=275%:%
+%:%470=276%:%
+%:%471=277%:%
+%:%472=278%:%
+%:%473=279%:%
+%:%474=280%:%

### 2021-11-24 paper/output/document/application.tex
wow common sense done

--- 2021-11-21 paper/output/document/application.tex
@@
 \begin{isamarkuptext}%
-In this section, I will demonstrate possible applications of my formalization of the FUL. I 
-will present two kinds of applications. First, I will formalize a classical ethical dilemma in 
-Kantian literature, the case of the murderer at the door. This will demonstrate the utility of computational
-ethics in helping philosophers think about ethical dilemmas. Second, I will encode some ``common sense"
-facts into the system and then test the results of applying this more powerful system to common
-ethical dilemmas. This section will serve as a prototype of the kind of reasoning that this kind of 
-computational ethics can do and will demonstrate the utility of computational ethics in performing 
-everyday ethical reasoning. This section will also outline what future work is necessary to use an 
-ethical reasoner like the one I build in practice. Finally, I will also philosophically analyze the possibility and value of 
-applications like these. Specifically, I will consider to what extent humans should let computers do 
-ethical reasoning on our behalf.%
+In this section, I use my system to perform ``applied ethical reasoning." In Chapter 2
+and Chapter 3, I performed metaethical reasoning while testing different formalizations of the FUL. Metaethical
+reasoning analyzes properties of moral thought itself \citep{sepme}. Because metaethics is about ethics itself,
+and not about the actual dilemmas that ethics is supposed to help us resolve, this kind of reasoning requires
+very little additional knowledge beyond that of the ethical theory in question. Indeed, in previous chapters,
+I perform metaethical reasoning using my system (which formalizes an ethical theory) and basic logical
+facts and objects. This kind of reasoning contrasts with ``applied ethical reasoning," which is the use of
+ethics to resolve ethical dilemmas and make judgements about what an agent should or should not do.
+Applied ethical reasoning is about the situation an agent is in, not about an ethical theory as a whole,
+abstract entity. In the application tests in previous chapters, I perform some toy examples of applied
+ethical reasoning, but in this section, I expore how my system can perform extended applied ethical reasoning.
+Metaethical reasoning is most interesting to philosophers who are trying to formulate the ``best" or 
+most correct theory of ethics. Applied ethical reasoning, on the other hand, is useful to ordinary people
+who are trying to decide how to live their lives. In order for automated ethics to guide AI agents, 
+it must perform applied ethical reasoning.
+
+One challenge of applied ethical reasoning is that it requires more common sense knowledge than metaethical
+reasoning. Applied ethical reasoning focuses on a particular ethical dilemma and thus requires enough 
+common sense to understand the dilemma and options at hand. For example, an applied ethicist 
+evaluating the permissibility of lying needs some robust definition of the term lying and likely some
+understanding about the activities of communication and truth telling. In this section, I attempt to
+endow my system with this kind of common sense in the specific case of lying. Indeed, in order for my 
+system to be used to perform applied ethical reasoning, it will need to be equipped with a database
+of common sense facts and definitions as I present in this section. My system will contribute the core
+reasoning about the Formula of Universal Law, but this reasoning must be applied to objects that are defined
+in this common sense database. In this section, I try to understand what this common sense reasoning looks like
+for the specific example of lying. I will examine how different sets of common sense facts impact the 
+judgements that my system comes to.
+
+Because these common sense facts can entirely determine my system's judgement, they are part of the trusted
+code base for my system. In order for someone to trust my system's judgements, they must trust that the
+common sense database is correct. Indeed, changing these common sense facts will change the judgements 
+that my system makes. For example, if we define truth telling as an act that is self-contradictory (perhaps
+by defining lying as ``$p \wedge \neg p$), then my system will output that truth telling is prohibited.
+Malicious common sense facts and definitions will result in bad ethical judgements. In other words, garbage in, 
+garbage out. This common sense reasoning is also not a part of the system I contribute here—in order for my
+system to be used, future work must develop a common sense database for the particular situation at hand. 
+The challenge of endowing automated ethical reasoners with common sense reasoning is not unique to my 
+system, and virtually all prior attempts in machine ethics face similar challenges. Most prior attempts
+sidestep this question, whereas I contribute an prototype implementation of one kind of common sense reasoning.
+
+The specific kind of common sense reasoning required for automated Kantian ethics appears to be a challenge 
+for automating Kantian ethics, and perhaps a reason that consequentialist or virtue ethical automated
+agents would be within closer reach for automation. Ultimately, I still argue that Kantian ethics is 
+easiest to automate because it will require fewer, less controversial common facts than other ethical
+systems. As the examples in this section demonstrate, Kantian ethics requires a definition of lying (which any other 
+theory would also requires) and the knowledge that if everyone lies in a given context, no one will believe 
+each other in that particular context. This latter fact may not be required for every ethical theory, 
+but is relatively uncontroversial. It is a kind of intuition about human behavior that is generally accepted. 
+Neither a definition of lying nor this property of lying seem like unreasonable prerequisites for ethical reasoning.
+
+Consequentialism, on the other hand, would require much more specific data about the consequences of 
+a lie, perhaps for the specific person's credibility, for the victim of the lie, for the third-parties 
+watching the lie unfold. Indeed, consequentialism more numerous and specific judgements, all of which are 
+likely to be more controversial than the two outlined above for Kantian ethics. Similarly, virtue ethics
+would likely require information about the actor's entire moral character, including their attitude
+towards the lie and their moral history. Virtue ethics would also require robust definitions of the 
+relevant virtues, in addition to a definition of lying. Thus, while Kantian ethics requires some 
+common sense reasoning, it requires fewer and less controversial background facts than other ethical theories.
+
+This section will provide additional examples of the kinds of common sense required to get my system
+off the ground. I will aim to use as lean and uncontroversial of a common sense database as possible
+to achieve robust and powerful results. This serves as evidence for the ease of automating
+Kantian ethics, an example of what additional work my system requires, and a demonstration of the contributions
+that I make. These examples demonstrate that nuanced common sense facts can cause my system to contribute 
+nuanced judgements faithful to philosophical literature. On one hand, this means that my system can perform
+sophisticated ethical reasoning, but on the other, the quality of this reasoning is heavily reliant on 
+the common sense database. Thus, my system \emph{could} make smart ethical judgements 
+in practice, but getting to that point will require a robust, trusted common sense database.
+
+\emph{Stick a bit here about the philosophical work that will go in this section}%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupsubsection{Right to Lie \label{sec:rtl}%
+\isamarkupsubsection{Simple Lying Examples \label{sec:lyingprelim}%
 }
@@
 \begin{isamarkuptext}%
-In this section, I draw on examples of ethical reasoning as presented in Korsgaard's right to lie.
+This chapter focuses on the example of lying because this case is robustly debated in the Kantian
+literature. I draw on examples of ethical reasoning as presented in Korsgaard's Right to Lie.
 She analyzes the example of someone who shows up at your door and asks, "Is Sara home?" Unbeknownst to them, 
@@
 protect her from the murderer. However, the categorical imperative seems to prohibit lying in all 
-circumstances. More specifically, when universalized, lies will no longer be believed, so it seems 
-like lying could never be an effective way of achieving any goal when universalized. Korsgaard points out
-that ``we believe what is said to us in a given context because most of the time people in that context 
-say what they really think" \citep[4]{KorsgaardRTL}. First, I will formalize this argument.
+circumstances. In this section, I will formalize Korsgaard's treatment of lying and joking under the 
+categorical imperative, focusing on the common sense assumptions necessary to achieve her conclusions. 
+In the next section, I will formalize the core of Korsgaard's argument that the categorical imperative
+coheres with ordinary intuition and does not prohibit lying to the murderer to protect Sara.
 
-The first step in formalizing this argument is defining the relevant terms.%
+First, Korsgaard argues that the categorical imperative appears to prohibit all lies because, when universalized, 
+lies will no longer be believed, so it seems like lying could never be an effective way of achieving any goal. 
+Korsgaard points out that ``we believe what is said to us in a given context because most of the time 
+people in that context say what they really think" \citep[4]{KorsgaardRTL}. In order to formalize this argument,
+I first need to define some relevant terms.%
 \end{isamarkuptext}\isamarkuptrue%
 \isacommand{consts}\isamarkupfalse%
-\ believe{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}s{\isasymRightarrow}t{\isasymRightarrow}t{\isachardoublequoteclose}\isanewline
+\ believe{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}s{\isasymRightarrow}t{\isasymRightarrow}t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharunderscore}\ believes\ {\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
 %
-\isamarkupcmt{Person s::subject believes sentence t::term%
+\isamarkupcmt{Person s::subject believes sentence t::term. The concept of belief will play a crucial role both in 
+the arguments for lying being prohibited and for the maxim of lying to the murderer being permissible. 
+Logicians and epistemologists have developed robust, complex logics of belief and knowledge, but for the 
+sake of this project, I avoid this complexity by merely defining the concept of belief as an empty
+constant that maps a subject, term pair to a term \cite{seplogicbelief}. For the examples in this section, this choice suffices, 
+as my common sense beliefs encode enough properties of belief for my purposes. Future work could
+integrate a much more complex logic of belief into my system.%
 }\isanewline
+\isanewline
 \isacommand{consts}\isamarkupfalse%
@@
 {\isachardoublequoteopen}utter{\isacharunderscore}falsehood\ s\ t\ {\isasymequiv}\ \ {\isacharparenleft}utter\ s\ t{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ t{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Person s utters falsehood t if and only if s utters t and t is false.%
+}\isanewline
 \isacommand{abbreviation}\isamarkupfalse%
@@
 %
-\isamarkupcmt{Person s::subject utters a falsehood t::term if they utter t and t is false.%
+\isamarkupcmt{Person s::subject knowingly utters a falsehood t, if they both utter t as a falsehood and don't
+believe t. This and the above abbreviations are the core of my formalization of Korsgaard's definition
+of lying. They are also relatively uncontroversial and have little normative content.%
 }\isanewline
@@
 %
-\isamarkupcmt{A maxim is a lie if 
+\isamarkupcmt{Using the above definitions, I can characterize a maxim as a lie if 
     (a) the act requires knowingly uttering a falsehood 
@@
 \begin{isamarkuptext}%
-To avoid focus on the case of conscious, intentional wrongdoing, I focus on ``knowing lies," 
+To avoid unintentional wrongdoing, I focus on ``knowing lies," 
 in which the speaker is aware that they are lying. It is uncontroversial that an act is a knowing lie
@@
 of a lie, which understands a lie as a kind of falsehood that is usually effective \emph{because} it decieves
-\citep[4]{KorsgaardRTL}.%
+\citep[4]{KorsgaardRTL}. In my formalization, this means that the purpose or goal of the maxim must
+involve decieving someone, or, in other words, that someone believe the falsehood told.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-With the above logical background, I can now show that maxims that involve lying are prohibited.
-First, I define the subject and maxim at hand.%
+With the above logical background, I can now automate Korsgaard's argument that maxims that involve
+lying are prohibited. First, I define the subject and maxim at hand.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupcmt{I will also define a maxim $m$. My goal is to show that if $m$ is a maxim about lying, then $m$
+\isamarkupcmt{I also define a maxim $m$. My goal is to show that if $m$ is a maxim about lying, then $m$
 is prohibited.%
+}\isanewline
+\isacommand{consts}\isamarkupfalse%
+\ c{\isacharcolon}{\isacharcolon}t\ a{\isacharcolon}{\isacharcolon}os\ g{\isacharcolon}{\isacharcolon}t\isanewline
+%
+\isamarkupcmt{$m$ will be composed of the circumstances, act, and goal above.%
 }%
 \begin{isamarkuptext}%
-The following lemma shows the common sense necessary to determine that lying is prohibited.%
+In the following lemma, I use my system to show that lying is prohibited. The assumptions of 
+this lemma represent the logical and common sense background necessary to reach this conclusion. This
+common sense background is a direct formalization of the premises of Korsgaard's argument. Using these
+relatively ``thin" premises about individual behavior, my system can derive a prohibition against lying.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \ lying{\isacharunderscore}prohibited{\isacharcolon}\isanewline
-\ \ \isakeyword{fixes}\ c\isanewline
-\ \ \isakeyword{fixes}\ a\isanewline
-\ \ \isakeyword{fixes}\ g\isanewline
 \ \ \isakeyword{assumes}\ {\isachardoublequoteopen}m\ {\isasymequiv}\ {\isacharparenleft}c{\isacharcolon}{\isacharcolon}t{\isacharcomma}\ a{\isacharcolon}{\isacharcolon}os{\isacharcomma}\ g{\isacharcolon}{\isacharcolon}t{\isacharparenright}{\isachardoublequoteclose}\isanewline
@@
 %
-\isamarkupcmt{Initial set-up, m is a well-formed maxim composed of some circumstances, act, and goal.%
+\isamarkupcmt{Initial technical set-up, m is a well-formed maxim composed of some circumstances, act, and goal.%
 }\isanewline
@@
 %
-\isamarkupcmt{$m$ is a maxim about lying. Precisely, it is a maxim in which the action is to knowingly utter a 
+\isamarkupcmt{$m$ is a maxim about lying. Precisely, it is a maxim in which the action requires knowingly uttering a 
 falsehood and the goal requires that someone believe this falsehood.%
@@
 %
-\isamarkupcmt{Assumption that if everyone utters false statement t, then no one will believe t.%
+\isamarkupcmt{Assumption that if everyone utters false statement t, then no one will believe t. This assumption is 
+Korsgaard's core piece of ``common sense" about lying \cite[5]{KorsgaardRTL}. This simple assumption encodes the common sense knowledge
+that human communication involves an implicit trust, and that when this trust erodes, the convention of 
+communication begins to break down and people no longer believe each other. Call this the ``convention of 
+lying" fact. In the rest of this section, I will test versions of this assumption, effectively encoding 
+different common sense understandings of lying.%
 }\isanewline
@@
 \isamarkupcmt{Restrict our focus to worlds in which the circumstances hold, as these are the morally interesting 
-worlds for this example. Basically an irrelevant technical detail.%
+worlds for this example. A technical detail.%
 }\isanewline
@@
 \begin{isamarkuptext}%
-The above is an example of how my system can perform ``applied ethical reasoning." In Chapter 2
-and Chapter 3, I performed metaethical reasoning while testing different formalizations of the FUL. Metaethical
-reasoning analyzes properties of moral thought itself \citep{sepme}. Because metaethics is about ethics itself,
-and not about the actual dilemmas that ethics is supposed to help us resolve, this kind of reasoning requires
-very little additional knowledge beyond that of the ethical theory in question. Indeed, in previous chapters,
-I perform metaethical reasoning using my system (which formalizes an ethical theory) and basic logical
-facts and objects. This kind of reasoning contrasts with ``applied ethical reasoning," which is the use of
-ethics to actually resolve ethical dilemmas and make judgements about what an agent should or should not do.
-Applied ethical reasoning is about the situation an agent is in, not about an ethical theory as a whole,
-abstract entity. In this section, I expore how my system can perform extended applied ethical reasoning. 
-Metaethical reasoning is most interesting to philosophers who are trying to formulate the ``best" or 
-most correct theory of ethics. Applied ethical reasoning, on the other hand, is useful to ordinary people
-who are trying to decide how to live their lives. These two kinds of reasoning represent the two motivations 
-for automated ethics. Metaethical reasoning is more directly a way to perform computational ethics, or use a computer
-system to do philosophy. Applied ethical reasoning is also relevant to philosophers (applied ethicists 
-generally perform this kind of reasoning), but is also relevant to AI agents or people seeking to navigate the world.
-In order for automated ethics to guide AI agents, it must perform applied ethical reasoning.
+Now that I have formalized Korsgaard's argument for why lying is prohibited, I will 
+implement her argument for why jokes are permissible. Specifically, she considers a joke a story that is 
+false and argues that joking is permissible because ``the universal practice of lying in the context of jokes
+does not interfere with the purpose of jokes, which is to amuse and does not depend on
+deception" \citep[4]{KorsgaardRTL}. Let's define a joke.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{abbreviation}\isamarkupfalse%
+\ joke{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
+{\isachardoublequoteopen}joke\ {\isasymequiv}\ {\isasymlambda}\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}{\isachardot}\ \ {\isasymexists}t{\isachardot}\ {\isacharparenleft}a\ \isactrlbold {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymlambda}s{\isachardot}\ knowingly{\isacharunderscore}utter{\isacharunderscore}falsehood\ s\ t{\isacharparenright}{\isacharparenright}\ {\isasymand}\ {\isasymnot}\ {\isacharparenleft}{\isasymexists}p{\isachardot}\ {\isasymforall}w{\isachardot}\ {\isacharparenleft}g\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}believe\ p\ t{\isacharparenright}{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}%
+\begin{isamarkuptext}%
+This definition of a joke merely defines a joke as a falsehood uttered for some purpose that 
+emph{doesn't} require deception, where deception involves someone believing the uttered falsehood. Notice 
+that this is quite a thin definition of a joke; it doesn't require any conception of humor but merely
+distinguishes jokes from lies. As far as common sense reasoning goes, this is a relatively thin proposition. 
+I will now demonstrate that this conception of a joke is sufficient to show that joking is permissible.
 
-One challenge of applied ethical reasoning is that it requires more common sense knowledge than metaethical
-reasoning. Applied ethical reasoning focuses on a particular ethical dilemma and thus requires enough 
-common sense to understand the dilemma and options at hand. For example, for an applied ethicist to 
-evaluate the permissibility of lying, they need some robust definition of the term lying and likely some
-understanding about the activities of communication and truth telling. In this section, I attempt to
-endow my system with this kind of common sense in the specific case of lying. Indeed, in order for my 
-system to be used to perform applied ethical reasoning, it will need to be equipped with a database
-of common sense facts and definitions as I present in this section. My system will contribute the core
-reasoning about the Formula of Universal Law, but this reasoning must be applied to objects that are defined
-in this common sense database. In this section, I try to understand what this common sense reasoning looks like
-for the specific example of lying. I will examine how different sets of common sense facts impact the 
-judgements that my system comes to.
-
-Because these common sense facts can entirely determine my system's judgement, they are part of the trusted
-code base for my system. In order for someone to trust my system's judgements, they must trust that the
-common sense database is correct. This common sense reasoning is also not a part of my system—in order for my
-system to be used, someone must develop a common sense database for the particular situation at hand. 
-The challenge of endowing automated ethical reasoners with common sense reasoning is not unique to my 
-system, and virtually all prior attempts in machine ethics face similar challenges.
-
-The specific kind of common sense reasoning required for automated Kantian ethics appears to be a challenge 
-for automating Kantian ethics, and perhaps a reason that consequentialist or virtue ethical automated
-agents would be within closer reach for automation. Ultimately, I still argue that Kantian ethics is 
-easiest to automate because it will require fewer, less controversial common facts than other ethical
-systems. As this example demonstrates, Kantian ethics requires a definition of lying (which any other 
-theory would also requires) and the knowledge that if everyone lies in a given context, no one will believe 
-each other in that particular context. This latter fact may not be required for every ethical theory, 
-but is relatively uncontroversial. Indeed, Korsgaard doesn't even bother to give a justification for 
-this fact. It is a kind of intuition about human behavior that is generally accepted. Neither a definition 
-of lying nor this property of lying seem like unreasonable prerequisites for ethical reasoning.
-
-Consequentialism, on the other hand, would require much more specific data about the consequences of 
-a lie, perhaps for the specific person's credibility, for the victim of the lie, for the third-parties 
-watching the lie unfold. Indeed, consequentialism more numerous and specific judgements, all of which are 
-likely to be more controversial than the two outlined above for Kantian ethics. Similarly, virtue ethics
-would likely require information about the actor's entire moral character, including their attitude
-towards the lie and their moral history. Virtue ethics would also require robust definitions of the 
-relevant virtues, in addition to a definition of lying. Thus, while Kantian ethics requires some 
-common sense reasoning, it requires fewer and less controversial background facts than other ethical theories.
-
-This section will provide additional examples of the kinds of commons sense required to get my system
-off the ground. I will aim to use as lean and uncontroversial of a common sense database as possible
-to achieve results as robust and powerful as possible. This serves as evidence for the ease of automating
-Kantian ethics, an example of what additional work my system requires, and a demonstration of the contributions
-that I make.%
+Korsgaard argues that her above argument for a prohibition against lying also implies that joking is 
+permissible, because its purpose is \emph{not} to decieve, but something else entirely. This means that, 
+even armed with the same core convention of lying assumption as above, joking must be permissible. The 
+lemma below shows exactly that.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ joking{\isacharunderscore}not{\isacharunderscore}prohibited{\isacharcolon}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}m\ {\isasymequiv}\ {\isacharparenleft}c{\isacharcolon}{\isacharcolon}t{\isacharcomma}\ a{\isacharcolon}{\isacharcolon}os{\isacharcomma}\ g{\isacharcolon}{\isacharcolon}t{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}w{\isachardot}\ {\isasymforall}s{\isachardot}\ well{\isacharunderscore}formed\ m\ s\ w{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Initial set-up, m is a well-formed maxim composed of some circumstances, act, and goal.%
+}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}joke\ m{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{$m$ is a maxim about joking. Precisely, it is a maxim in which the action is to knowingly utter a 
+falsehood and the goal does not require that someone believe this falsehood.%
+}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}t\ w{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isasymforall}p{\isachardot}\ utter{\isacharunderscore}falsehood\ p\ t\ w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ \isactrlbold {\isasymnot}\ {\isacharparenleft}believe\ p\ t{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{The same convention of lying assumption as in the above example.%
+}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}w{\isachardot}\ c\ w{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Restrict our focus to worlds in which the circumstances hold, as these are the morally interesting 
+worlds for this example. An irrelevant technical detail.%
+}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}permissible\ m\ me{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{by}\isamarkupfalse%
+\ {\isacharparenleft}smt\ assms{\isacharparenleft}{\isadigit{1}}{\isacharparenright}\ assms{\isacharparenleft}{\isadigit{2}}{\isacharparenright}\ assms{\isacharparenleft}{\isadigit{3}}{\isacharparenright}\ case{\isacharunderscore}prod{\isacharunderscore}conv{\isacharparenright}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+This completes my implementation of Korsgaard's first interpretation of lying. Using the convention
+of lying assumption formalized in this section, I show that lying is generally prohibited but joking
+is permissible. Notice that this is already a sophisticated kind of ethical reasoning. The sophistication
+necessary to distinguish between lying and joking is a direct consequence of my system's use of a robust
+conception of a maxim, which encodes the goal of an act as part of the maxim being evaluated. This kind 
+of ethical reasoning also required relatively few and uncontroversial common sense facts. The deepest
+assumption required was that, if everyone lies about a given statement, no one will believe that 
+statement. This assumption is not merely definitional; it does encode some synthetic knowledge about the 
+world, but it is relatively uncontroversial. Indeed, it is so well-accepted that Korsgaard does not 
+bother to justify it in her argument. These examples demonstrate that, while common sense reasoning 
+is an obstacle that must be overcome for my system to be used in practice, it is surmountable.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \isatagdocument
+%
+\isamarkupsubsection{Lying to a Liar \label{sec:lyingtoliar}%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
+Once Korsgaard completes her preliminary work differentiating between lies and jokes, she begins her main
+ argument, which examines the controversial case of the murderer at the door. Recall that the murderer
+appears at your door and asks if their intended victim is at home. Ordinary intuition requires that it 
+is at the very least permissible (if not obligatory) to lie to the murderer in order to protect the 
+victim. Korsgaard notes that a murderer who wishes to find their victim cannot simply announce their
+intentions to murder; instead, he must ``must suppose that you do not know who he is and
+what he has in mind" \citep[5]{KorsgaaardRTL}.\footnote{Korsgaard assumes that the murderer will lie 
+about his identity in order to take advantage of your honesty. In footnote 5, she accepts that her 
+arguments will not apply in the case of the honest murderer who announces his attentions, so she 
+restricts her focus to the case of lying to a liar. She claims that in this case, the correct act is 
+to refuse to respond, but she does not argue for this in this paper.} Thus, she can modify the maxim in 
+question and specifies that when someone lies to you, you are allowed to lie to them. The maxim of lying 
+to the murderer is actually the maxim of lying to a liar, which she argues is permissible. In this section, I will 
+formalize her argument for lying to a liar.
+
+As usual, first I define my terms.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{consts}\isamarkupfalse%
+\ murderer{\isacharcolon}{\isacharcolon}s\isanewline
+%
+\isamarkupcmt{This example involves one more subject: the murderer.%
+}\isanewline
+\isacommand{consts}\isamarkupfalse%
+\ not{\isacharunderscore}a{\isacharunderscore}murderer{\isacharcolon}{\isacharcolon}t\isanewline
+%
+\isamarkupcmt{This statement represents the lie that the murderer tells you. By not announcing their
+intention, they are implicitly telling you that they are not a murderer, as people normally assume that 
+those knocking on their door are not murderers.%
+}\isanewline
+\isacommand{consts}\isamarkupfalse%
+\ when{\isacharunderscore}at{\isacharunderscore}my{\isacharunderscore}door{\isacharcolon}{\isacharcolon}t\isanewline
+%
+\isamarkupcmt{These are the circumstances that the murderer is in.%
+}\isanewline
+\isacommand{consts}\isamarkupfalse%
+\ find{\isacharunderscore}victim{\isacharcolon}{\isacharcolon}t\isanewline
+%
+\isamarkupcmt{This will be the murderer's goal: to find their victim.%
+}\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ murderers{\isacharunderscore}maxim{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
+{\isachardoublequoteopen}murderers{\isacharunderscore}maxim\ {\isasymequiv}\ {\isacharparenleft}when{\isacharunderscore}at{\isacharunderscore}my{\isacharunderscore}door{\isacharcomma}\ {\isasymlambda}s{\isachardot}\ knowingly{\isacharunderscore}utter{\isacharunderscore}falsehood\ s\ not{\isacharunderscore}a{\isacharunderscore}murderer{\isacharcomma}\ find{\isacharunderscore}victim{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Using the above definitions, I can define the murderer's maxim as, ``When at your door, I will knowingly
+utter the falsehood that I am not a murderer in order to find my intended victim." Now I will repeat
+the same process for your maxim.%
+}\isanewline
+\isanewline
+\isacommand{consts}\isamarkupfalse%
+\ victim{\isacharunderscore}not{\isacharunderscore}home{\isacharcolon}{\isacharcolon}t\isanewline
+%
+\isamarkupcmt{This statement is the lie that you tell the murderer: that their intended victim is not at home.%
+}\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ murderer{\isacharunderscore}at{\isacharunderscore}door{\isacharcolon}{\isacharcolon}t\ \isakeyword{where}\ \isanewline
+{\isachardoublequoteopen}murderer{\isacharunderscore}at{\isacharunderscore}door\ {\isasymequiv}\ W\ murderers{\isacharunderscore}maxim\ murderer{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{These are the circumstances that you are in: the murderer has willed their maxim and thus lied to you.%
+}\isanewline
+\isacommand{consts}\isamarkupfalse%
+\ protect{\isacharunderscore}victim{\isacharcolon}{\isacharcolon}t\isanewline
+%
+\isamarkupcmt{Your goal is to protect the murderer's intended victim.%
+}\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ my{\isacharunderscore}maxim{\isacharcolon}{\isacharcolon}maxim\ \isakeyword{where}\ \isanewline
+{\isachardoublequoteopen}my{\isacharunderscore}maxim\ {\isasymequiv}\ {\isacharparenleft}murderer{\isacharunderscore}at{\isacharunderscore}door{\isacharcomma}\ \ {\isasymlambda}s{\isachardot}\ knowingly{\isacharunderscore}utter{\isacharunderscore}falsehood\ s\ victim{\isacharunderscore}not{\isacharunderscore}home{\isacharcomma}\ protect{\isacharunderscore}victim{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Using these definitions, I construct your maxim, which is ``When a murderer is at my door, I will 
+knowingly utter the falsehood that their intended victim is not at home in order to protect the victim.%
+}%
+\begin{isamarkuptext}%
+Now that I have defined the maxims at hand, I can begin reasoning about them. First, I will show 
+that, using the same convention of lying common sense fact as above, the murderer's maxim is prohibited.
+Effectively, this tests that the assumption is indeed strong enough to prohibit lying.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ murderers{\isacharunderscore}maxim{\isacharunderscore}prohibited{\isacharcolon}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}w{\isachardot}\ well{\isacharunderscore}formed\ murderers{\isacharunderscore}maxim\ murderer\ w{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Initial set-up, the murderer's maxim is well-formed.%
+}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}find{\isacharunderscore}victim\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}believe\ me\ not{\isacharunderscore}a{\isacharunderscore}murderer{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Assumption that, in order for the murderer to find their victim, you must not believe that they are a murderer.
+This is an example of the kind of situation specific common sense reasoning necessary to use my system.
+Again, this is an uncontroversial statement.%
+}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}t\ w{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isasymforall}p{\isachardot}\ utter{\isacharunderscore}falsehood\ p\ t\ w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ \isactrlbold {\isasymnot}\ {\isacharparenleft}believe\ p\ t{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{The convention of lying common sense assumption from above.%
+}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}w{\isachardot}\ when{\isacharunderscore}at{\isacharunderscore}my{\isacharunderscore}door\ w{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Restrict our focus to worlds in which the circumstance of the murderer being at my door holds, as 
+these are the morally interesting worlds for this example. An irrelevant technical detail.%
+}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}prohibited\ murderers{\isacharunderscore}maxim\ murderer{\isacharparenright}{\isachardoublequoteclose}\ \ \ \isanewline
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+\isacommand{proof}\isamarkupfalse%
+\ {\isacharminus}\ \isanewline
+%
+\isamarkupcmt{Again, this proof is too heavy for Isabelle to finish on its own, so I needed to specify some
+intermediate steps. The same intermediate steps as above sufficed, effectively providing a pattern for 
+the proof. Isabelle does allow defining `proof methods,' so a more robust version of my system could define
+this proof pattern and apply it in cases involving lies.%
+}\isanewline
+\ \ \isacommand{have}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymforall}p\ w{\isachardot}\ {\isacharparenleft}W\ murderers{\isacharunderscore}maxim\ p{\isacharparenright}\ w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymTurnstile}\ {\isacharparenleft}when{\isacharunderscore}at{\isacharunderscore}my{\isacharunderscore}door\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ find{\isacharunderscore}victim{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \ \ \isacommand{using}\isamarkupfalse%
+\ assms{\isacharparenleft}{\isadigit{2}}{\isacharparenright}\ assms{\isacharparenleft}{\isadigit{4}}{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
+\ auto\isanewline
+\ \ \ \isacommand{have}\isamarkupfalse%
+\ {\isachardoublequoteopen}not{\isacharunderscore}universalizable\ murderers{\isacharunderscore}maxim\ murderer{\isachardoublequoteclose}\isanewline
+\ \ \ \ \ \isacommand{using}\isamarkupfalse%
+\ assms{\isacharparenleft}{\isadigit{2}}{\isacharparenright}\ assms{\isacharparenleft}{\isadigit{4}}{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
+\ auto\isanewline
+\ \ \ \isacommand{thus}\isamarkupfalse%
+\ {\isacharquery}thesis\isanewline
+\ \ \ \ \ \isacommand{using}\isamarkupfalse%
+\ FUL\ assms{\isacharparenleft}{\isadigit{1}}{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
+\ blast\isanewline
+\ \isacommand{qed}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+I will now formalize Korsgaard's argument for the permissibility of lying to a liar. She modifies
+the convention of lying assumption above when she argues that, if the murderer believes that you don't 
+believe they're a murderer, they will think that you won't lie to them. Precisely, she claims that, 
+``it is because the murderer supposes you do not know what circumstances you are in - that is, that 
+you do not know you are addressing a murderer - and so does not conclude from the fact that people 
+in those circumstances always lie that you will lie" \cite[6]{KorsgaardRTL}. The concept of belief 
+defined above will become much more crucial to formalize this version of the convention of lying 
+assumption. I formalize this argument below.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ lying{\isacharunderscore}to{\isacharunderscore}liar{\isacharunderscore}permissible{\isacharcolon}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}well{\isacharunderscore}formed\ murderers{\isacharunderscore}maxim\ murderer{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}well{\isacharunderscore}formed\ my{\isacharunderscore}maxim\ me{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Assume that we're working with well-formed maxims.%
+}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}protect{\isacharunderscore}victim\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}murderer\ believes\ victim{\isacharunderscore}not{\isacharunderscore}home{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{In order for you to successfully protect the victim, the murderer must believe that the victim is not
+home. This is a noncontroversial assumption about the specific act at hand.%
+}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}sentence{\isacharcolon}{\isacharcolon}t{\isachardot}\ {\isasymforall}p{\isadigit{1}}{\isacharcolon}{\isacharcolon}s{\isachardot}\ {\isasymforall}p{\isadigit{2}}{\isacharcolon}{\isacharcolon}s{\isachardot}\ {\isasymforall}w{\isacharcolon}{\isacharcolon}i{\isachardot}\ {\isacharparenleft}{\isacharparenleft}p{\isadigit{1}}\ believes\ {\isacharparenleft}utter{\isacharunderscore}falsehood\ p{\isadigit{2}}\ sentence{\isacharparenright}{\isacharparenright}\ w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymnot}\ {\isacharparenleft}p{\isadigit{1}}\ believes\ sentence{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{This is one of two assumptions that encode Korsgaard's core argument. If person1 believes that person2 
+utters a sentence as a falsehood, then person1 won't believe that sentence. This is a modification of the 
+convention of lying assumption from above, and I will refer to it as the ``convention of belief" assumption.
+Again, like the convention of lying assumption, this assumption is uncontroversial.%
+}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}c\ a\ g\ w{\isachardot}\ {\isacharparenleft}universalized\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isacharparenleft}person{\isadigit{1}}\ believes\ {\isacharparenleft}person{\isadigit{2}}\ believes\ c{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}person{\isadigit{1}}\ believes\ {\isacharparenleft}a\ person{\isadigit{2}}{\isacharparenright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{This is the second key common sense assumption. If the maxim (c, a, g) is universalized, then if person1 believes 
+person2 believes c, then person1 believes person2 performs the act. In other words, person1 will believe that 
+person2 wills the maxim. I will refer to this as the ``convention of willing" assumption. This follows
+directly from Korsgaard's conception of universalizability: when a maxim is universalized, everyone 
+wills it. Korsgaard assumes that if everyone wills a maxim, they also believe that everyone else wills it.%
+}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}w{\isachardot}\ murderer{\isacharunderscore}at{\isacharunderscore}door\ w{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Restrict our focus to worlds in which the circumstance of the murderer being at my door holds, as 
+these are the morally interesting worlds for this example. An irrelevant technical detail.%
+}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}permissible\ my{\isacharunderscore}maxim\ me{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{using}\isamarkupfalse%
+\ assms{\isacharparenleft}{\isadigit{1}}{\isacharparenright}\ assms{\isacharparenleft}{\isadigit{6}}{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
+\ auto\isanewline
+%
+\isamarkupcmt{Notice the use of the first and sixth assumption in this automatically generated proof. Essentially, 
+the common sense assumptions given are not strong enough to generate a prohibition against lying to a liar,
+and are thus unused in this proof.%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+The above lemma shows that, with a more nuanced set of common sense facts, my system can show that 
+lying to a liar is permissible. Moreover, I know that this set of assumptions is correct because it 
+can also show that the murderer's maxim is prohibited. I show this in the lemma below.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ murderers{\isacharunderscore}maxim{\isacharunderscore}prohibited{\isadigit{2}}{\isacharcolon}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}w{\isachardot}\ well{\isacharunderscore}formed\ murderers{\isacharunderscore}maxim\ murderer\ w{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{The murderer's maxim is a well-formed maxim composed of some circumstances, act, and goal.%
+}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}find{\isacharunderscore}victim\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}believe\ me\ not{\isacharunderscore}a{\isacharunderscore}murderer{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Assumption that, in order for the murderer to find their victim, you must not believe that they are a murderer.%
+}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}sentence{\isacharcolon}{\isacharcolon}t{\isachardot}\ {\isasymforall}p{\isadigit{1}}{\isacharcolon}{\isacharcolon}s{\isachardot}\ {\isasymforall}p{\isadigit{2}}{\isacharcolon}{\isacharcolon}s{\isachardot}\ {\isasymforall}w{\isacharcolon}{\isacharcolon}i{\isachardot}\ {\isacharparenleft}{\isacharparenleft}p{\isadigit{1}}\ believes\ {\isacharparenleft}utter{\isacharunderscore}falsehood\ p{\isadigit{2}}\ sentence{\isacharparenright}{\isacharparenright}\ w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymnot}\ {\isacharparenleft}p{\isadigit{1}}\ believes\ sentence{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{The convention of belief assumption from above.%
+}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}c\ a\ g\ w{\isachardot}\ {\isacharparenleft}universalized\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isacharparenleft}person{\isadigit{1}}\ believes\ {\isacharparenleft}person{\isadigit{2}}\ believes\ c{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}person{\isadigit{1}}\ believes\ {\isacharparenleft}a\ person{\isadigit{2}}{\isacharparenright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{The convention of willing assumption from above.%
+}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}w{\isachardot}\ when{\isacharunderscore}at{\isacharunderscore}my{\isacharunderscore}door\ w{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Restrict our focus to worlds in which the circumstance of the murderer being at my door holds, as 
+these are the morally interesting worlds for this example. Basically an irrelevant technical detail.%
+}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}prohibited\ murderers{\isacharunderscore}maxim\ murderer{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+\isacommand{proof}\isamarkupfalse%
+\ {\isacharminus}\ \isanewline
+\ \ \isacommand{have}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymforall}p\ w{\isachardot}\ {\isacharparenleft}W\ murderers{\isacharunderscore}maxim\ p{\isacharparenright}\ w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymTurnstile}\ {\isacharparenleft}when{\isacharunderscore}at{\isacharunderscore}my{\isacharunderscore}door\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ find{\isacharunderscore}victim{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \ \ \isacommand{using}\isamarkupfalse%
+\ assms{\isacharparenleft}{\isadigit{2}}{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
+\ auto\isanewline
+\ \ \isacommand{have}\isamarkupfalse%
+\ {\isachardoublequoteopen}not{\isacharunderscore}universalizable\ murderers{\isacharunderscore}maxim\ murderer{\isachardoublequoteclose}\isanewline
+\ \ \ \ \isacommand{using}\isamarkupfalse%
+\ assms{\isacharparenleft}{\isadigit{2}}{\isacharparenright}\ assms{\isacharparenleft}{\isadigit{5}}{\isacharparenright}\ case{\isacharunderscore}prod{\isacharunderscore}beta\ fst{\isacharunderscore}conv\ internal{\isacharunderscore}case{\isacharunderscore}prod{\isacharunderscore}def\ old{\isachardot}prod{\isachardot}case\ old{\isachardot}prod{\isachardot}exhaust\ snd{\isacharunderscore}conv\ \isacommand{by}\isamarkupfalse%
+\ auto\isanewline
+\ \ \isacommand{thus}\isamarkupfalse%
+\ {\isacharquery}thesis\isanewline
+\ \ \ \ \isacommand{using}\isamarkupfalse%
+\ FUL\ assms{\isacharparenleft}{\isadigit{1}}{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
+\ blast\ \isanewline
+\isacommand{qed}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+This concludes my examination of the maxim of lying to a liar. I was able to show that, by slightly
+modifying the common sense facts used, my system can show that lying to a liar is permissible, but lying 
+in order to find a victim is not. The assumptions used in this example are a little more robust, but still
+ultimately uncontroversial. Indeed, they are direct consequences of Korsgaard's definition of willing 
+and of ordinary definitions of lying. These thin assumptions were sufficient to generate moral conclusions
+that Kantian scholars debate robustly. Indeed, armed with this common sense, my system generated 
+a conclusion that many critics of Kant failed to see.
+
+While this example demonstrates that power of my system (when equipped with some common sense), it 
+also shows how vital the role of the common sense reasoning is. Slight, intuitive changes in the common
+sense facts can achieve totally different conclusions about lying. This represents an obstacle to 
+fully automated ethical reasoning, because such an agent would need a trusted database of common 
+sense facts, which is still an unsolved problem. My work is one step towards such an agent, but the 
+importance of common sense means that much progress must be made in order to completely automate ethics.
+In the next section, I examine the question of whether or not this work is even a good idea, and what role
+automated ethics should actually play in our ordinary moral lives.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsection{Philosophical Analysis: Is Automated Ethics a Good Idea?%
+}
+\isamarkuptrue%
 %
@@
 %:%46=18%:%
-%:%55=20%:%
-%:%67=22%:%
-%:%68=23%:%
-%:%69=24%:%
-%:%70=25%:%
-%:%71=26%:%
-%:%72=27%:%
-%:%73=28%:%
-%:%74=29%:%
-%:%75=30%:%
-%:%76=31%:%
-%:%77=32%:%
-%:%79=34%:%
-%:%80=34%:%
-%:%82=35%:%
-%:%83=35%:%
-%:%84=36%:%
-%:%85=36%:%
-%:%87=37%:%
-%:%88=37%:%
-%:%89=38%:%
-%:%90=38%:%
-%:%91=39%:%
-%:%92=40%:%
-%:%93=40%:%
-%:%94=41%:%
-%:%96=42%:%
-%:%97=42%:%
-%:%98=47%:%
-%:%99=48%:%
-%:%100=48%:%
-%:%101=49%:%
-%:%103=50%:%
-%:%104=51%:%
-%:%105=52%:%
-%:%108=54%:%
-%:%109=55%:%
-%:%110=56%:%
-%:%111=57%:%
-%:%112=58%:%
-%:%113=59%:%
-%:%117=61%:%
-%:%118=62%:%
-%:%120=64%:%
-%:%121=64%:%
-%:%123=65%:%
-%:%124=65%:%
-%:%125=66%:%
-%:%126=66%:%
-%:%128=67%:%
-%:%129=68%:%
-%:%132=70%:%
-%:%134=72%:%
-%:%135=72%:%
-%:%136=73%:%
-%:%137=74%:%
-%:%138=75%:%
-%:%139=76%:%
-%:%140=77%:%
-%:%142=78%:%
-%:%143=78%:%
-%:%144=79%:%
-%:%146=80%:%
-%:%147=81%:%
-%:%148=81%:%
-%:%149=82%:%
-%:%151=83%:%
-%:%152=83%:%
-%:%153=84%:%
-%:%155=85%:%
-%:%156=86%:%
-%:%157=86%:%
-%:%158=87%:%
-%:%165=88%:%
-%:%166=88%:%
-%:%167=89%:%
-%:%168=89%:%
-%:%169=90%:%
-%:%170=90%:%
-%:%172=91%:%
-%:%173=92%:%
-%:%174=93%:%
-%:%175=94%:%
-%:%176=94%:%
-%:%177=95%:%
-%:%178=95%:%
-%:%179=96%:%
-%:%180=96%:%
-%:%181=97%:%
-%:%182=97%:%
-%:%183=98%:%
-%:%184=98%:%
-%:%185=98%:%
-%:%186=99%:%
-%:%196=101%:%
-%:%197=102%:%
-%:%198=103%:%
-%:%199=104%:%
-%:%200=105%:%
-%:%201=106%:%
-%:%202=107%:%
-%:%203=108%:%
-%:%204=109%:%
-%:%205=110%:%
-%:%206=111%:%
-%:%207=112%:%
-%:%208=113%:%
-%:%209=114%:%
-%:%210=115%:%
-%:%211=116%:%
-%:%212=117%:%
-%:%213=118%:%
-%:%214=119%:%
-%:%215=120%:%
-%:%216=121%:%
-%:%217=122%:%
-%:%218=123%:%
-%:%219=124%:%
-%:%220=125%:%
-%:%221=126%:%
-%:%222=127%:%
-%:%223=128%:%
-%:%224=129%:%
-%:%225=130%:%
-%:%226=131%:%
-%:%227=132%:%
-%:%228=133%:%
-%:%229=134%:%
-%:%230=135%:%
-%:%231=136%:%
-%:%232=137%:%
-%:%233=138%:%
-%:%234=139%:%
-%:%235=140%:%
-%:%236=141%:%
-%:%237=142%:%
-%:%238=143%:%
-%:%239=144%:%
-%:%240=145%:%
-%:%241=146%:%
-%:%242=147%:%
-%:%243=148%:%
-%:%244=149%:%
-%:%245=150%:%
-%:%246=151%:%
-%:%247=152%:%
-%:%248=153%:%
-%:%249=154%:%
-%:%250=155%:%
-%:%251=156%:%
-%:%252=157%:%
-%:%253=158%:%
-%:%254=159%:%
-%:%255=160%:%
-%:%256=161%:%
-%:%257=162%:%
-%:%258=163%:%
+%:%47=19%:%
+%:%48=20%:%
+%:%49=21%:%
+%:%50=22%:%
+%:%51=23%:%
+%:%52=24%:%
+%:%53=25%:%
+%:%54=26%:%
+%:%55=27%:%
+%:%56=28%:%
+%:%57=29%:%
+%:%58=30%:%
+%:%59=31%:%
+%:%60=32%:%
+%:%61=33%:%
+%:%62=34%:%
+%:%63=35%:%
+%:%64=36%:%
+%:%65=37%:%
+%:%66=38%:%
+%:%67=39%:%
+%:%68=40%:%
+%:%69=41%:%
+%:%70=42%:%
+%:%71=43%:%
+%:%72=44%:%
+%:%73=45%:%
+%:%74=46%:%
+%:%75=47%:%
+%:%76=48%:%
+%:%77=49%:%
+%:%78=50%:%
+%:%79=51%:%
+%:%80=52%:%
+%:%81=53%:%
+%:%82=54%:%
+%:%83=55%:%
+%:%84=56%:%
+%:%85=57%:%
+%:%86=58%:%
+%:%87=59%:%
+%:%88=60%:%
+%:%89=61%:%
+%:%90=62%:%
+%:%91=63%:%
+%:%92=64%:%
+%:%93=65%:%
+%:%94=66%:%
+%:%95=67%:%
+%:%96=68%:%
+%:%97=69%:%
+%:%98=70%:%
+%:%99=71%:%
+%:%100=72%:%
+%:%101=73%:%
+%:%102=74%:%
+%:%103=75%:%
+%:%104=76%:%
+%:%105=77%:%
+%:%106=78%:%
+%:%115=80%:%
+%:%127=82%:%
+%:%128=83%:%
+%:%129=84%:%
+%:%130=85%:%
+%:%131=86%:%
+%:%132=87%:%
+%:%133=88%:%
+%:%134=89%:%
+%:%135=90%:%
+%:%136=91%:%
+%:%137=92%:%
+%:%138=93%:%
+%:%139=94%:%
+%:%140=95%:%
+%:%141=96%:%
+%:%142=97%:%
+%:%144=99%:%
+%:%145=99%:%
+%:%147=100%:%
+%:%148=101%:%
+%:%149=102%:%
+%:%150=103%:%
+%:%151=104%:%
+%:%152=105%:%
+%:%153=106%:%
+%:%154=106%:%
+%:%155=107%:%
+%:%156=108%:%
+%:%157=108%:%
+%:%159=109%:%
+%:%160=109%:%
+%:%161=110%:%
+%:%162=110%:%
+%:%163=111%:%
+%:%165=112%:%
+%:%166=112%:%
+%:%167=113%:%
+%:%168=113%:%
+%:%169=114%:%
+%:%171=115%:%
+%:%172=116%:%
+%:%173=117%:%
+%:%174=117%:%
+%:%175=122%:%
+%:%176=123%:%
+%:%177=123%:%
+%:%178=124%:%
+%:%180=125%:%
+%:%181=126%:%
+%:%182=127%:%
+%:%185=129%:%
+%:%186=130%:%
+%:%187=131%:%
+%:%188=132%:%
+%:%189=133%:%
+%:%190=134%:%
+%:%191=135%:%
+%:%195=137%:%
+%:%196=138%:%
+%:%198=140%:%
+%:%199=140%:%
+%:%201=141%:%
+%:%202=141%:%
+%:%203=142%:%
+%:%204=142%:%
+%:%206=143%:%
+%:%207=144%:%
+%:%208=144%:%
+%:%209=145%:%
+%:%210=145%:%
+%:%212=146%:%
+%:%215=148%:%
+%:%216=149%:%
+%:%217=150%:%
+%:%218=151%:%
+%:%220=153%:%
+%:%221=153%:%
+%:%222=154%:%
+%:%223=155%:%
+%:%225=156%:%
+%:%226=156%:%
+%:%227=157%:%
+%:%229=158%:%
+%:%230=159%:%
+%:%231=159%:%
+%:%232=160%:%
+%:%234=161%:%
+%:%235=162%:%
+%:%236=163%:%
+%:%237=164%:%
+%:%238=165%:%
+%:%239=166%:%
+%:%240=166%:%
+%:%241=167%:%
+%:%243=168%:%
+%:%244=169%:%
+%:%245=169%:%
+%:%246=170%:%
+%:%253=171%:%
+%:%254=171%:%
+%:%255=172%:%
+%:%256=172%:%
+%:%257=173%:%
+%:%258=173%:%
+%:%260=174%:%
+%:%261=175%:%
+%:%262=176%:%
+%:%263=177%:%
+%:%264=177%:%
+%:%265=178%:%
+%:%266=178%:%
+%:%267=179%:%
+%:%268=179%:%
+%:%269=180%:%
+%:%270=180%:%
+%:%271=181%:%
+%:%272=181%:%
+%:%273=181%:%
+%:%274=182%:%
+%:%284=184%:%
+%:%285=185%:%
+%:%286=186%:%
+%:%287=187%:%
+%:%288=188%:%
+%:%290=190%:%
+%:%291=190%:%
+%:%292=191%:%
+%:%294=193%:%
+%:%295=194%:%
+%:%296=195%:%
+%:%297=196%:%
+%:%298=197%:%
+%:%299=198%:%
+%:%300=199%:%
+%:%301=200%:%
+%:%302=201%:%
+%:%303=202%:%
+%:%305=204%:%
+%:%306=204%:%
+%:%307=205%:%
+%:%308=206%:%
+%:%310=207%:%
+%:%311=207%:%
+%:%312=208%:%
+%:%314=209%:%
+%:%315=210%:%
+%:%316=210%:%
+%:%317=211%:%
+%:%319=212%:%
+%:%320=212%:%
+%:%321=213%:%
+%:%323=214%:%
+%:%324=215%:%
+%:%325=215%:%
+%:%326=216%:%
+%:%329=217%:%
+%:%333=217%:%
+%:%334=217%:%
+%:%343=219%:%
+%:%344=220%:%
+%:%345=221%:%
+%:%346=222%:%
+%:%347=223%:%
+%:%348=224%:%
+%:%349=225%:%
+%:%350=226%:%
+%:%351=227%:%
+%:%352=228%:%
+%:%353=229%:%
+%:%362=233%:%
+%:%374=235%:%
+%:%375=236%:%
+%:%376=237%:%
+%:%377=238%:%
+%:%378=239%:%
+%:%379=240%:%
+%:%380=241%:%
+%:%381=242%:%
+%:%382=243%:%
+%:%383=244%:%
+%:%384=245%:%
+%:%385=246%:%
+%:%386=247%:%
+%:%387=248%:%
+%:%388=249%:%
+%:%389=250%:%
+%:%391=252%:%
+%:%392=252%:%
+%:%394=253%:%
+%:%395=253%:%
+%:%396=254%:%
+%:%397=254%:%
+%:%399=255%:%
+%:%400=256%:%
+%:%401=257%:%
+%:%402=257%:%
+%:%403=258%:%
+%:%404=258%:%
+%:%406=259%:%
+%:%407=259%:%
+%:%408=260%:%
+%:%409=260%:%
+%:%411=261%:%
+%:%412=261%:%
+%:%413=262%:%
+%:%414=262%:%
+%:%415=263%:%
+%:%417=264%:%
+%:%418=265%:%
+%:%419=266%:%
+%:%420=266%:%
+%:%421=267%:%
+%:%422=268%:%
+%:%423=268%:%
+%:%425=269%:%
+%:%426=269%:%
+%:%427=270%:%
+%:%428=270%:%
+%:%429=271%:%
+%:%431=272%:%
+%:%432=272%:%
+%:%433=273%:%
+%:%434=273%:%
+%:%436=274%:%
+%:%437=274%:%
+%:%438=275%:%
+%:%439=275%:%
+%:%440=276%:%
+%:%442=277%:%
+%:%443=278%:%
+%:%446=280%:%
+%:%447=281%:%
+%:%448=282%:%
+%:%450=284%:%
+%:%451=284%:%
+%:%452=285%:%
+%:%454=286%:%
+%:%455=286%:%
+%:%456=287%:%
+%:%458=288%:%
+%:%459=289%:%
+%:%460=290%:%
+%:%461=290%:%
+%:%462=291%:%
+%:%464=292%:%
+%:%465=292%:%
+%:%466=293%:%
+%:%468=294%:%
+%:%469=295%:%
+%:%470=295%:%
+%:%471=296%:%
+%:%478=297%:%
+%:%479=297%:%
+%:%481=298%:%
+%:%482=299%:%
+%:%483=300%:%
+%:%484=301%:%
+%:%485=301%:%
+%:%486=302%:%
+%:%487=302%:%
+%:%488=303%:%
+%:%489=303%:%
+%:%490=303%:%
+%:%491=304%:%
+%:%492=304%:%
+%:%493=305%:%
+%:%494=305%:%
+%:%495=305%:%
+%:%496=306%:%
+%:%497=306%:%
+%:%498=307%:%
+%:%499=307%:%
+%:%500=307%:%
+%:%501=308%:%
+%:%511=310%:%
+%:%512=311%:%
+%:%513=312%:%
+%:%514=313%:%
+%:%515=314%:%
+%:%516=315%:%
+%:%517=316%:%
+%:%518=317%:%
+%:%520=319%:%
+%:%521=319%:%
+%:%522=320%:%
+%:%523=321%:%
+%:%525=322%:%
+%:%526=322%:%
+%:%527=323%:%
+%:%529=324%:%
+%:%530=325%:%
+%:%531=325%:%
+%:%532=326%:%
+%:%534=327%:%
+%:%535=328%:%
+%:%536=329%:%
+%:%537=330%:%
+%:%538=330%:%
+%:%539=331%:%
+%:%541=332%:%
+%:%542=333%:%
+%:%543=334%:%
+%:%544=335%:%
+%:%545=336%:%
+%:%546=336%:%
+%:%547=337%:%
+%:%549=338%:%
+%:%550=339%:%
+%:%551=339%:%
+%:%552=340%:%
+%:%555=341%:%
+%:%559=341%:%
+%:%560=341%:%
+%:%561=341%:%
+%:%563=342%:%
+%:%564=343%:%
+%:%565=344%:%
+%:%575=346%:%
+%:%576=347%:%
+%:%577=348%:%
+%:%579=350%:%
+%:%580=350%:%
+%:%581=351%:%
+%:%583=352%:%
+%:%584=352%:%
+%:%585=353%:%
+%:%587=354%:%
+%:%588=354%:%
+%:%589=355%:%
+%:%591=356%:%
+%:%592=356%:%
+%:%593=357%:%
+%:%595=358%:%
+%:%596=358%:%
+%:%597=359%:%
+%:%599=360%:%
+%:%600=361%:%
+%:%601=361%:%
+%:%602=362%:%
+%:%609=363%:%
+%:%610=363%:%
+%:%611=364%:%
+%:%612=364%:%
+%:%613=365%:%
+%:%614=365%:%
+%:%615=365%:%
+%:%616=366%:%
+%:%617=366%:%
+%:%618=367%:%
+%:%619=367%:%
+%:%620=367%:%
+%:%621=368%:%
+%:%622=368%:%
+%:%623=369%:%
+%:%624=369%:%
+%:%625=369%:%
+%:%626=370%:%
+%:%636=372%:%
+%:%637=373%:%
+%:%638=374%:%
+%:%639=375%:%
+%:%640=376%:%
+%:%641=377%:%
+%:%642=378%:%
+%:%643=379%:%
+%:%644=380%:%
+%:%645=381%:%
+%:%646=382%:%
+%:%647=383%:%
+%:%648=384%:%
+%:%649=385%:%
+%:%650=386%:%
+%:%651=387%:%
+%:%660=389%:%

### 2021-11-26 paper/output/document/application.tex
and that's chapter 4

@@
 \begin{isamarkuptext}%
-In this section, I use my system to perform ``applied ethical reasoning." In Chapter 2
+In this chapter, I 
+demonstrate my system's ability to formalize longer, more complicated ethical arguments and understand 
+the additional capabilities necessary to use my system in practice. In Chapter 2
 and Chapter 3, I performed metaethical reasoning while testing different formalizations of the FUL. Metaethical
-reasoning analyzes properties of moral thought itself \citep{sepme}. Because metaethics is about ethics itself,
-and not about the actual dilemmas that ethics is supposed to help us resolve, this kind of reasoning requires
-very little additional knowledge beyond that of the ethical theory in question. Indeed, in previous chapters,
-I perform metaethical reasoning using my system (which formalizes an ethical theory) and basic logical
-facts and objects. This kind of reasoning contrasts with ``applied ethical reasoning," which is the use of
-ethics to resolve ethical dilemmas and make judgements about what an agent should or should not do.
-Applied ethical reasoning is about the situation an agent is in, not about an ethical theory as a whole,
-abstract entity. In the application tests in previous chapters, I perform some toy examples of applied
-ethical reasoning, but in this section, I expore how my system can perform extended applied ethical reasoning.
-Metaethical reasoning is most interesting to philosophers who are trying to formulate the ``best" or 
-most correct theory of ethics. Applied ethical reasoning, on the other hand, is useful to ordinary people
-who are trying to decide how to live their lives. In order for automated ethics to guide AI agents, 
-it must perform applied ethical reasoning.
+reasoning analyzes properties of moral thought itself and involves questions about the nature of ethical
+truth. This kind of reasoning contrasts with ``applied 
+ethical reasoning," which is the use of ethics to resolve dilemmas and make judgements about 
+what an agent should or should not do. Applied ethical reasoning is relevant with respect to an agent's
+particular situation, not just an an ethical theory as an abstract entity. In previous chapters' application tests,
+I performed some toy examples of applied ethical reasoning, but in this chapter, I expore how my system can 
+perform extended applied ethical reasoning. Metaethical reasoning is most interesting to philosophers 
+who are trying to formulate the ``best" theory of ethics. Applied ethical reasoning, on the other hand, 
+is useful to ordinary people who are trying to decide how to live their lives. In order for automated 
+ethics to guide AI agents, it must perform applied ethical reasoning.
 
 One challenge of applied ethical reasoning is that it requires more common sense knowledge than metaethical
-reasoning. Applied ethical reasoning focuses on a particular ethical dilemma and thus requires enough 
-common sense to understand the dilemma and options at hand. For example, an applied ethicist 
+reasoning. Because metaethics is about ethics itself, and not about the dilemmas that ethics is 
+supposed to help us resolve, this kind of reasoning requires very little knowledge about the world. 
+In previous chapters, I perform metaethical reasoning using my system (which formalizes an 
+ethical theory) and basic logical facts and objects. Applied ethical reasoning, on the other hand,
+focuses on a particular ethical dilemma and thus requires enough 
+``common sense" to understand the dilemma and options at hand. For example, an applied ethicist 
 evaluating the permissibility of lying needs some robust definition of the term lying and likely some
-understanding about the activities of communication and truth telling. In this section, I attempt to
-endow my system with this kind of common sense in the specific case of lying. Indeed, in order for my 
+understanding about the activities of communication and truth telling. Kantians specifically describe
+this common sense as ``postulates of rationality" that are nontrivial and nonnormative, but still
+part of the process of practical reasoning itself \citep{silber}. \citet{powers} notes that common sense 
+is a hurder for an automated Kantian ethical agent. In this chapter, I attempt to tackle this challenge and
+endow my system with this kind of common sense in the specific case of lying. In order for my 
 system to be used to perform applied ethical reasoning, it will need to be equipped with a database
-of common sense facts and definitions as I present in this section. My system will contribute the core
+of common sense facts and definitions as I present in this chapter. My system will contribute the core
 reasoning about the Formula of Universal Law, but this reasoning must be applied to objects that are defined
-in this common sense database. In this section, I try to understand what this common sense reasoning looks like
-for the specific example of lying. I will examine how different sets of common sense facts impact the 
-judgements that my system comes to.
-
-Because these common sense facts can entirely determine my system's judgement, they are part of the trusted
+in this common sense database. In this chapter, I try to understand what this common sense reasoning looks like
+for the specific example of lying.
+
+Because these common sense facts can determine my system's judgements, they are part of the trusted
 code base for my system. In order for someone to trust my system's judgements, they must trust that the
-common sense database is correct. Indeed, changing these common sense facts will change the judgements 
+common sense database is correct becase changing these common sense facts will change the judgements 
 that my system makes. For example, if we define truth telling as an act that is self-contradictory (perhaps
-by defining lying as ``$p \wedge \neg p$), then my system will output that truth telling is prohibited.
+by defining it as $p \wedge \neg p$), then my system will output that truth telling is prohibited.
 Malicious common sense facts and definitions will result in bad ethical judgements. In other words, garbage in, 
@@
 The challenge of endowing automated ethical reasoners with common sense reasoning is not unique to my 
-system, and virtually all prior attempts in machine ethics face similar challenges. Most prior attempts
+system, and virtually all prior attempts in machine ethics face similar challenges.\footnote{See Section
+Related Work for a survey of the common sense required in prior work.} Most prior attempts
 sidestep this question, whereas I contribute an prototype implementation of one kind of common sense reasoning.
 
-The specific kind of common sense reasoning required for automated Kantian ethics appears to be a challenge 
+The specific kind of common sense reasoning required appears to be a challenge 
 for automating Kantian ethics, and perhaps a reason that consequentialist or virtue ethical automated
-agents would be within closer reach for automation. Ultimately, I still argue that Kantian ethics is 
-easiest to automate because it will require fewer, less controversial common facts than other ethical
+agents would be within closer reach for automation. Ultimately, Kantian ethics is still
+easiest to automate because it will require fewer, less controversial common sense facts than other ethical
 systems. As the examples in this section demonstrate, Kantian ethics requires a definition of lying (which any other 
@@
 a lie, perhaps for the specific person's credibility, for the victim of the lie, for the third-parties 
-watching the lie unfold. Indeed, consequentialism more numerous and specific judgements, all of which are 
+watching the lie unfold. Consequentialism requires more numerous and specific judgements, all of which are 
 likely to be more controversial than the two outlined above for Kantian ethics. Similarly, virtue ethics
@@
 
-This section will provide additional examples of the kinds of common sense required to get my system
+The extended examples presented in this section also demonstrate the difficulty of formulating a 
+maxim to pass as input to my implementation of the FUL. A large part of the challenge of applied Kantian
+ethics is formulating a maxim that accurately captures an agent's principle of action, so a totally
+automated agent using my system will need some way to formulate these maxims well. In this section,
+I manually implement Korsgaard's formulation of certain maxims, and I will later argue that manual formulation
+of maxims is, at present, the way forward.
+
+This chapter will provide additional examples of the kinds of common sense facts and maxim formulation required to get my system
 off the ground. I will aim to use as lean and uncontroversial of a common sense database as possible
@@
 Kantian ethics, an example of what additional work my system requires, and a demonstration of the contributions
-that I make. These examples demonstrate that nuanced common sense facts can cause my system to contribute 
+that I make. These examples demonstrate that nuanced common sense facts and maxims can cause my system to contribute 
 nuanced judgements faithful to philosophical literature. On one hand, this means that my system can perform
 sophisticated ethical reasoning, but on the other, the quality of this reasoning is heavily reliant on 
-the common sense database. Thus, my system \emph{could} make smart ethical judgements 
-in practice, but getting to that point will require a robust, trusted common sense database.
+the common sense database and the input maxim. Thus, my system \emph{could} make smart ethical judgements 
+in practice, but getting to that point will require a robust, trusted common sense database and maxim
+formulator.
 
@@
 \begin{isamarkuptext}%
-This chapter focuses on the example of lying because this case is robustly debated in the Kantian
-literature. I draw on examples of ethical reasoning as presented in Korsgaard's Right to Lie.
-She analyzes the example of someone who shows up at your door and asks, "Is Sara home?" Unbeknownst to them, 
-you know that they want to know Sara's location in order to murder her. Ordinary moral intuition seems
-to imply that in this situation, if Sara is home, you should lie and say that she is not in order to 
-protect her from the murderer. However, the categorical imperative seems to prohibit lying in all 
+This chapter focuses on the example of lying because this case is hotly debated in the Kantian
+literature. I draw on examples of ethical reasoning as presented in Korsgaard's ``Right to Lie," which 
+examines exactly how strict Kant's prohibition on lying is. She picks up a long-running debate in the 
+literature through the example of someone who shows up at your door and asks, ``Is Sara home?" Unbeknownst to them, 
+you know that they want to know Sara's location in order to murder her. Ordinary moral intuition 
+prescribes that, if Sara is home, you should lie and say that she is not in order to 
+protect her from the murderer, but the categorical imperative seems to prohibit lying in all 
 circumstances. In this section, I will formalize Korsgaard's treatment of lying and joking under the 
@@
 First, Korsgaard argues that the categorical imperative appears to prohibit all lies because, when universalized, 
-lies will no longer be believed, so it seems like lying could never be an effective way of achieving any goal. 
+lies will no longer be believed. Thus, lying could never be an effective way of achieving any goal when universalized.
 Korsgaard points out that ``we believe what is said to us in a given context because most of the time 
 people in that context say what they really think" \citep[4]{KorsgaardRTL}. In order to formalize this argument,
-I first need to define some relevant terms.%
+I first need to define the relevant terms.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 the arguments for lying being prohibited and for the maxim of lying to the murderer being permissible. 
-Logicians and epistemologists have developed robust, complex logics of belief and knowledge, but for the 
+Logicians and epistemologists have developed robust, complex logics of belief and knowledge \citep{seplogicbelief}. For the 
 sake of this project, I avoid this complexity by merely defining the concept of belief as an empty
-constant that maps a subject, term pair to a term \cite{seplogicbelief}. For the examples in this section, this choice suffices, 
+constant that maps a subject, term pair to a term. For the examples in this section, this choice suffices, 
 as my common sense beliefs encode enough properties of belief for my purposes. Future work could
@@
 %
-\isamarkupcmt{Person s::subject utters sentence t::term%
+\isamarkupcmt{Person s::subject utters sentence t::term.%
 }\isanewline
@@
 \ lie{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
-{\isachardoublequoteopen}lie\ {\isasymequiv}\ {\isasymlambda}\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}{\isachardot}\ {\isasymexists}t{\isachardot}\ {\isacharparenleft}a\ \isactrlbold {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymlambda}s{\isachardot}\ knowingly{\isacharunderscore}utter{\isacharunderscore}falsehood\ s\ t{\isacharparenright}{\isacharparenright}\ {\isasymand}\ {\isacharparenleft}{\isasymexists}p{\isachardot}\ {\isasymforall}w{\isachardot}\ {\isacharparenleft}g\ \isactrlbold {\isasymrightarrow}\ believe\ p\ t{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
+{\isachardoublequoteopen}lie\ {\isasymequiv}\ {\isasymlambda}\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}{\isachardot}\ {\isasymexists}t{\isachardot}\ {\isacharparenleft}a\ \isactrlbold {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymlambda}s{\isachardot}\ knowingly{\isacharunderscore}utter{\isacharunderscore}falsehood\ s\ t{\isacharparenright}{\isacharparenright}\ {\isasymand}\ {\isacharparenleft}{\isasymexists}p{\isachardot}\ {\isasymforall}w{\isachardot}\ {\isacharparenleft}g\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}believe\ p\ t{\isacharparenright}{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
 %
@@
     (a) the act requires knowingly uttering a falsehood 
-    (b) the end requires that some person $p$ believe the false statement $t$%
+    (b) the end requires that some person $p$ believe the false statement $t$.%
 }%
@@
 To avoid unintentional wrongdoing, I focus on ``knowing lies," 
-in which the speaker is aware that they are lying. It is uncontroversial that an act is a knowing lie
-if the speaker utters a false statement that they do not believe. The second half of this definition, which 
-requires that the goal of the action of lying be to decieve, is inspired by  Korsgaard's interpretation 
-of a lie, which understands a lie as a kind of falsehood that is usually effective \emph{because} it decieves
+in which the speaker is aware that they are lying. It is uncontroversial that, in order for an act to be
+a knowing lie, the speaker must utter a false statement that they do not believe. The second half of 
+this definition requires that the goal of the lie is deception and is inspired by  Korsgaard's interpretation 
+of a lie. She understands a lie as a kind of falsehood that is usually effective \emph{because} it decieves
 \citep[4]{KorsgaardRTL}. In my formalization, this means that the purpose or goal of the maxim must
@@
 %
-\isamarkupcmt{I am trying to reason about my obligations so I will define myself as a specific subject.%
+\isamarkupcmt{I am trying to reason about \emph{my} obligations so I will define myself as a specific subject.%
 }\isanewline
@@
 %
-\isamarkupcmt{Initial technical set-up, m is a well-formed maxim composed of some circumstances, act, and goal.%
+\isamarkupcmt{Initial technical set-up: $m$ is a well-formed maxim composed of some circumstances, act, and goal.%
 }\isanewline
@@
 %
-\isamarkupcmt{$m$ is a maxim about lying. Precisely, it is a maxim in which the action requires knowingly uttering a 
-falsehood and the goal requires that someone believe this falsehood.%
+\isamarkupcmt{$m$ is a maxim about lying as defined above. Precisely, it is a maxim in which the action requires 
+knowingly uttering a falsehood and the goal requires that someone believe this falsehood.%
 }\isanewline
@@
 %
-\isamarkupcmt{Assumption that if everyone utters false statement t, then no one will believe t. This assumption is 
+\isamarkupcmt{Assumption that if everyone utters false statement $t$, then no one will believe $t$. This assumption is 
 Korsgaard's core piece of ``common sense" about lying \cite[5]{KorsgaardRTL}. This simple assumption encodes the common sense knowledge
@@
 work to produce. I divided the proof into the intermediate steps shown here, and Isabelle was able to do 
-the rest! This step says that if $m$ is universalized, then the circumstances won't lead to the goal, 
+the rest. This step says that if $m$ is universalized, then the circumstances won't lead to the goal, 
 which is quite close to the idea of the maxim not being universalizable.%
@@
 \ blast\ \isanewline
+%
+\isamarkupcmt{$?thesis$ is Isabelle's syntax for the goal of the lemma. In this case, $?thesis$ is equivalent to 
+$\vDash prohibited\! m \! me$.%
+}\isanewline
 \isacommand{qed}\isamarkupfalse%
@@
 Now that I have formalized Korsgaard's argument for why lying is prohibited, I will 
-implement her argument for why jokes are permissible. Specifically, she considers a joke a story that is 
+implement her argument for why jokes are permissible. Specifically, she defines a joke as a story that is 
 false and argues that joking is permissible because ``the universal practice of lying in the context of jokes
 does not interfere with the purpose of jokes, which is to amuse and does not depend on
-deception" \citep[4]{KorsgaardRTL}. Let's define a joke.%
+deception" \citep[4]{KorsgaardRTL}. First, I define a joke..%
 \end{isamarkuptext}\isamarkuptrue%
@@
 This definition of a joke merely defines a joke as a falsehood uttered for some purpose that 
-emph{doesn't} require deception, where deception involves someone believing the uttered falsehood. Notice 
+doesn't require deception, where deception involves someone believing the uttered falsehood. Notice 
 that this is quite a thin definition of a joke; it doesn't require any conception of humor but merely
-distinguishes jokes from lies. As far as common sense reasoning goes, this is a relatively thin proposition. 
+distinguishes jokes from lies. As far as common sense reasoning goes, this is a relatively tame proposition. 
 I will now demonstrate that this conception of a joke is sufficient to show that joking is permissible.
@@
 %
-\isamarkupcmt{Initial set-up, m is a well-formed maxim composed of some circumstances, act, and goal.%
+\isamarkupcmt{Initial set-up: $m$ is a well-formed maxim composed of some circumstances, act, and goal.%
 }\isanewline
@@
 conception of a maxim, which encodes the goal of an act as part of the maxim being evaluated. This kind 
-of ethical reasoning also required relatively few and uncontroversial common sense facts. The deepest
+of ethical reasoning also requires relatively few and uncontroversial common sense facts. The deepest
 assumption required was that, if everyone lies about a given statement, no one will believe that 
@@
  argument, which examines the controversial case of the murderer at the door. Recall that the murderer
-appears at your door and asks if their intended victim is at home. Ordinary intuition requires that it 
+appears at your door and asks if his intended victim is at home. Ordinary intuition requires that it 
 is at the very least permissible (if not obligatory) to lie to the murderer in order to protect the 
-victim. Korsgaard notes that a murderer who wishes to find their victim cannot simply announce their
+victim. Korsgaard notes that a murderer who wishes to find his victim cannot simply announce his
 intentions to murder; instead, he must ``must suppose that you do not know who he is and
-what he has in mind" \citep[5]{KorsgaaardRTL}.\footnote{Korsgaard assumes that the murderer will lie 
+what he has in mind" \citep[5]{KorsgaardRTL}.\footnote{Korsgaard assumes that the murderer will lie 
 about his identity in order to take advantage of your honesty. In footnote 5, she accepts that her 
-arguments will not apply in the case of the honest murderer who announces his attentions, so she 
-restricts her focus to the case of lying to a liar. She claims that in this case, the correct act is 
+arguments will not apply in the case of the honest murderer who announces his intentions, so she 
+restricts her focus to the case of lying to a liar. She claims that in the case of the honest murderer, the correct act is 
 to refuse to respond, but she does not argue for this in this paper.} Thus, she can modify the maxim in 
-question and specifies that when someone lies to you, you are allowed to lie to them. The maxim of lying 
-to the murderer is actually the maxim of lying to a liar, which she argues is permissible. In this section, I will 
-formalize her argument for lying to a liar.
-
-As usual, first I define my terms.%
+question to specify that when someone lies to you, you are allowed to lie to them. The maxim of lying 
+to the murderer is actually the maxim of lying to a liar, which she argues is permissible. Notice that
+her argument hinges on this clever, but ultimately sensical formulation of your maxim. She notes
+that there is something relevant and significant about the fact that the person demanding to know Sara's
+location is a murderer and that he is trying to take advantage of your honesty. This claim is not
+unfounded or wildly controversial, but it does demonstrate the importance of correctly formulating
+the maxim to test. In this section, I will formalize her argument for lying to a liar.
+
+As usual, I first define my terms.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupcmt{This statement represents the lie that the murderer tells you. By not announcing their
-intention, they are implicitly telling you that they are not a murderer, as people normally assume that 
+\isamarkupcmt{This statement represents the lie that the murderer tells you. By not announcing his
+intention, he is implicitly telling you that he is not a murderer, as people normally assume that 
 those knocking on their door are not murderers.%
@@
 %
-\isamarkupcmt{This will be the murderer's goal: to find their victim.%
+\isamarkupcmt{This will be the murderer's goal: to find his victim.%
 }\isanewline
@@
 %
-\isamarkupcmt{This statement is the lie that you tell the murderer: that their intended victim is not at home.%
+\isamarkupcmt{This statement is the lie that you tell the murderer: that his intended victim is not at home.%
 }\isanewline
@@
 %
-\isamarkupcmt{These are the circumstances that you are in: the murderer has willed their maxim and thus lied to you.%
+\isamarkupcmt{These are the circumstances that you are in: the murderer has willed his maxim and thus lied to you.%
 }\isanewline
@@
 \isamarkupcmt{Using these definitions, I construct your maxim, which is ``When a murderer is at my door, I will 
-knowingly utter the falsehood that their intended victim is not at home in order to protect the victim.%
+knowingly utter the falsehood that his intended victim is not at home in order to protect the victim."%
 }%
@@
 %
-\isamarkupcmt{Initial set-up, the murderer's maxim is well-formed.%
+\isamarkupcmt{Initial set-up: the murderer's maxim is well-formed.%
 }\isanewline
@@
 %
-\isamarkupcmt{Assumption that, in order for the murderer to find their victim, you must not believe that they are a murderer.
-This is an example of the kind of situation specific common sense reasoning necessary to use my system.
-Again, this is an uncontroversial statement.%
+\isamarkupcmt{Assumption that, in order for the murderer to find their victim, you must not believe that he is a murderer.
+This is an example of the kind of situation-specific common sense reasoning necessary to use my system.
+Again, this is an uncontroversial statement; the murderer assumes that if you knew he was a murderer, you 
+would not disclose the victim's location to him. SHOULD I SAY MORE HERE?%
 }\isanewline
@@
 intermediate steps. The same intermediate steps as above sufficed, effectively providing a pattern for 
-the proof. Isabelle does allow defining `proof methods,' so a more robust version of my system could define
-this proof pattern and apply it in cases involving lies.%
+the proof. Isabelle does allow users to define custom `proof methods,' so a more robust version of 
+my system could define this proof pattern as a method and apply it in cases involving lies.%
 }\isanewline
@@
 the convention of lying assumption above when she argues that, if the murderer believes that you don't 
-believe they're a murderer, they will think that you won't lie to them. Precisely, she claims that, 
+believe he is a murderer, he will think that you won't lie to him. Precisely, she claims that, 
 ``it is because the murderer supposes you do not know what circumstances you are in - that is, that 
 you do not know you are addressing a murderer - and so does not conclude from the fact that people 
-in those circumstances always lie that you will lie" \cite[6]{KorsgaardRTL}. The concept of belief 
-defined above will become much more crucial to formalize this version of the convention of lying 
-assumption. I formalize this argument below.%
+in those circumstances always lie that you will lie" \cite[6]{KorsgaardRTL}. Even though the maxim of 
+lying to a murderer is universalized, the murderer thinks that you don't know his true identity. Thus,
+even if you have willed this maxim, he thinks that you won't perform the act of lying to the murderer,
+since you don't think you're in the relevant circumstances. I formalize this argument below.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 convention of lying assumption from above, and I will refer to it as the ``convention of belief" assumption.
-Again, like the convention of lying assumption, this assumption is uncontroversial.%
+Again, like the convention of lying assumption, this assumption is uncontroversial: if I think you are 
+saying a false sentence, then I won't believe that sentence.%
 }\isanewline
@@
 %
-\isamarkupcmt{This is the second key common sense assumption. If the maxim (c, a, g) is universalized, then if person1 believes 
-person2 believes c, then person1 believes person2 performs the act. In other words, person1 will believe that 
+\isamarkupcmt{This is the second major common sense assumption. If the maxim (c, a, g) is universalized, then if person1 believes 
+person2 believes they are in the given circumstances, then person1 believes person2 performs the act. In other words, person1 will believe that 
 person2 wills the maxim. I will refer to this as the ``convention of willing" assumption. This follows
 directly from Korsgaard's conception of universalizability: when a maxim is universalized, everyone 
-wills it. Korsgaard assumes that if everyone wills a maxim, they also believe that everyone else wills it.%
+wills it. Korsgaard assumes that if everyone wills a maxim, they also believe that everyone else wills it.
+DO I NEED TO SAY MORE HERE?%
 }\isanewline
@@
 \isamarkupcmt{Restrict our focus to worlds in which the circumstance of the murderer being at my door holds, as 
-these are the morally interesting worlds for this example. Basically an irrelevant technical detail.%
+these are the morally interesting worlds for this example. An irrelevant technical detail.%
 }\isanewline
@@
 \begin{isamarkuptext}%
-This concludes my examination of the maxim of lying to a liar. I was able to show that, by slightly
+This concludes my examination of the maxim of lying to a liar. I was able to show that, by
 modifying the common sense facts used, my system can show that lying to a liar is permissible, but lying 
@@
 
-While this example demonstrates that power of my system (when equipped with some common sense), it 
+While it is true that lying to the murderer should be permissible, Korsgaard notes that many will want
+to say something stronger, like the fact that lying to the murderer is obligatory in order to protect
+the intended victim \citep[15]{KorsgaardRTL}. It seems like we would be doing something wrong if I revealed the victim's
+location, knowing that this revelation would cost them their life. Korsgaard solves this problem by 
+noting that, while the FUL shows that lying to the murderer permissible, other parts of Kant's ethics
+will show that it is obligatory. Recall that Kant presents perfect and imperfect duties,
+where the former are strict, inviolable, and specific and the latter are broader prescriptions for action.
+Perfect duties always supersede imperfect duties when the two conflict.
+For example, the duty to not murder is a perfect duty and the duty to give to charity is an imperfect duty. 
+The FUL generates perfect duties and Kant's extended theory of virtues generates imperfect duties. The details
+of this theory and these distinctions are outside the scope of this paper, but the crucial note is that 
+other parts of Kant's ethical theory generate the obligation to lie to the murderer. I chose
+to formalize the FUL because it is, in some sense, the strongest of the formulations of the categorical
+imperative. An even more sophisticated Kantian reasoner could formalize his theory of virtue and his
+other formulatations of the categorical imperative in order to generate the obligation to lie to the murderer, 
+but the FUL is the strongest and most foundational of these principles. The fact that my system merely
+shows that lying to the murderer is permissible, but not obligatory is consistent with the part of 
+Kant's ethical theory that I formalize and demonstrates that I have faithfully implemented the FUL.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+While this example demonstrates the power of my system (when equipped with some common sense), it 
 also shows how vital the role of the common sense reasoning is. Slight, intuitive changes in the common
 sense facts can achieve totally different conclusions about lying. This represents an obstacle to 
-fully automated ethical reasoning, because such an agent would need a trusted database of common 
+fully automated ethical reasoning; such an agent would need a trusted database of common 
 sense facts, which is still an unsolved problem. My work is one step towards such an agent, but the 
 importance of common sense means that much progress must be made in order to completely automate ethics.
-In the next section, I examine the question of whether or not this work is even a good idea, and what role
-automated ethics should actually play in our ordinary moral lives.%
+
+The reasoning of this section also demonstrates one additional place where a Kantian must make vital judgements:
+the formulation of the maxim itself. Korsgaard's argument for the permissibility of lying to a 
+murderer hinged on a clever formulation of the maxim highlighting a particular facet of the circumstances, 
+namely that the murderer is lying to you. Indeed, there is robust debate in the literature on what
+circumstances should be considered when formulating a maxim. Some critics of Kant raise the ``tailoring
+objection," which is the worry that arbitrarily specific circumstances render any maxim universalizable. For 
+example, the maxim ``When my name is Lavanya Singh and I am wearing a purple shirt and it is November 26th, 
+I will lie in order to get some easy cash" passes the universalizability test. Even if this maxim is 
+willed universally, the circumstances are so specific that lying will not become the general mechanism
+for getting easy cash, so the lender will believe my lie and the maxim will remain effective. By tailoring
+the circumstances, any maxim can evade universalization.
+
+The Kantian response to this criticism is to require that the circumstances included in the formulation
+of the maxim be ``morally relevant." In the example above, my purple shirt and the date clearly have no bearing on 
+the moral status of lying. On the other hand, consider the maxim ``When I am unmeployed, I will murder
+someone in order to take their job." The circumstances of being unmeployed clearly have some bearing on the moral
+relevance of the murder in question; they speak to the motivation for the murder. While this view seems 
+to track how we actually perform moral reasoning, it leaves open the question of how to determine
+which circumstances are morally relevant. Here, O'Niell reminds us that the Formula of Universal Law is 
+a ``test of moral worth rather than of outward rightness" \citep[98]{constofreason}. The FUL is a way 
+for an agent to decide how they should behave, not for a third-party to judge their behavior. Ethics is 
+a personal process for Kant, so the FUL is designed to help agents internally make decisions, not to 
+judge others' decisions. Because agents use the FUL to evaluate their own behavior, the test is at its 
+best when they make a good faith effort to isolate the \emph{principle} of their action, rather than some
+``surface intent" \citep[87]{constofreason}. The FUL is supposed to determine if an agent's principle of action
+is universally consistent, so it is at its most effective when an agent accurately formulates the principle
+they act on. Circumstances are morally relevant if they accurately reflect the way that the agent is 
+thinking about their own action. In the example above, the circumstances of wearing a purple shirt don't
+the principle of the liar's action. They are clearly a disingenous attempt to evade the universalizability
+test, but because the FUL is a test of personal integrity, it cannot withstand this kind of mental
+gymnastics.
+
+While this account of the formulation of a maxim prescribes how a well-intentioned agent should
+decide how to live their life, it poses a challenge for automated ethics. In order for an automated
+ethical agent to use the categorical imperative to its fullest extent, the input maxim fed into
+my system or any automation of the FUL must be a good-faith attempt to capture the agent's principle
+of action. However an action is turned into a maxim for my system to process, whether manually as I do
+during these tests or automatically using some kind of input parser, this transformation from action
+to maxim has huge bearing on the outcome of the test. The formulation of a maxim must be a good-faith 
+attempt to capture the principle of action, and must therefore include only the morally relevant
+circumstances, and nothing more. This is a significant judgement that my system does not make, and is 
+thus another hurdle that must be overcome in order for my system to be used in practice. I will argue
+in Section ?? that this kind of input parsing work should be left to human beings for now, and that
+major technical and philosophical progress must be made to automate this portion of the system.
+
+The formulation of a maxim and the common sense database pose the two greatest challenges to the adoption
+of my system in practice. In this chapter, I argue that using manual, human involvement, these challenges
+can be overcome in relatively uncontroversial ways. They are also ripe areas for future work.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %:%106=78%:%
-%:%115=80%:%
-%:%127=82%:%
-%:%128=83%:%
-%:%129=84%:%
-%:%130=85%:%
-%:%131=86%:%
-%:%132=87%:%
-%:%133=88%:%
-%:%134=89%:%
-%:%135=90%:%
-%:%136=91%:%
-%:%137=92%:%
-%:%138=93%:%
-%:%139=94%:%
-%:%140=95%:%
+%:%107=79%:%
+%:%108=80%:%
+%:%109=81%:%
+%:%110=82%:%
+%:%111=83%:%
+%:%112=84%:%
+%:%113=85%:%
+%:%114=86%:%
+%:%115=87%:%
+%:%116=88%:%
+%:%117=89%:%
+%:%118=90%:%
+%:%119=91%:%
+%:%120=92%:%
+%:%129=94%:%
 %:%141=96%:%
 %:%142=97%:%
+%:%143=98%:%
 %:%144=99%:%
-%:%145=99%:%
-%:%147=100%:%
-%:%148=101%:%
-%:%149=102%:%
-%:%150=103%:%
-%:%151=104%:%
-%:%152=105%:%
-%:%153=106%:%
-%:%154=106%:%
-%:%155=107%:%
-%:%156=108%:%
-%:%157=108%:%
-%:%159=109%:%
-%:%160=109%:%
-%:%161=110%:%
-%:%162=110%:%
-%:%163=111%:%
-%:%165=112%:%
-%:%166=112%:%
-%:%167=113%:%
-%:%168=113%:%
-%:%169=114%:%
-%:%171=115%:%
-%:%172=116%:%
-%:%173=117%:%
-%:%174=117%:%
-%:%175=122%:%
-%:%176=123%:%
-%:%177=123%:%
-%:%178=124%:%
-%:%180=125%:%
-%:%181=126%:%
-%:%182=127%:%
-%:%185=129%:%
+%:%145=100%:%
+%:%146=101%:%
+%:%147=102%:%
+%:%148=103%:%
+%:%149=104%:%
+%:%150=105%:%
+%:%151=106%:%
+%:%152=107%:%
+%:%153=108%:%
+%:%154=109%:%
+%:%155=110%:%
+%:%156=111%:%
+%:%157=112%:%
+%:%159=114%:%
+%:%160=114%:%
+%:%162=115%:%
+%:%163=116%:%
+%:%164=117%:%
+%:%165=118%:%
+%:%166=119%:%
+%:%167=120%:%
+%:%168=121%:%
+%:%169=121%:%
+%:%170=122%:%
+%:%171=123%:%
+%:%172=123%:%
+%:%174=124%:%
+%:%175=124%:%
+%:%176=125%:%
+%:%177=125%:%
+%:%178=126%:%
+%:%180=127%:%
+%:%181=127%:%
+%:%182=128%:%
+%:%183=128%:%
+%:%184=129%:%
 %:%186=130%:%
@@
 %:%188=132%:%
-%:%189=133%:%
-%:%190=134%:%
-%:%191=135%:%
-%:%195=137%:%
-%:%196=138%:%
-%:%198=140%:%
-%:%199=140%:%
-%:%201=141%:%
-%:%202=141%:%
-%:%203=142%:%
-%:%204=142%:%
-%:%206=143%:%
-%:%207=144%:%
-%:%208=144%:%
-%:%209=145%:%
-%:%210=145%:%
-%:%212=146%:%
-%:%215=148%:%
-%:%216=149%:%
-%:%217=150%:%
-%:%218=151%:%
-%:%220=153%:%
-%:%221=153%:%
-%:%222=154%:%
-%:%223=155%:%
-%:%225=156%:%
-%:%226=156%:%
-%:%227=157%:%
-%:%229=158%:%
-%:%230=159%:%
-%:%231=159%:%
-%:%232=160%:%
-%:%234=161%:%
-%:%235=162%:%
-%:%236=163%:%
-%:%237=164%:%
-%:%238=165%:%
-%:%239=166%:%
-%:%240=166%:%
-%:%241=167%:%
-%:%243=168%:%
-%:%244=169%:%
-%:%245=169%:%
-%:%246=170%:%
-%:%253=171%:%
-%:%254=171%:%
-%:%255=172%:%
-%:%256=172%:%
-%:%257=173%:%
-%:%258=173%:%
-%:%260=174%:%
-%:%261=175%:%
-%:%262=176%:%
-%:%263=177%:%
-%:%264=177%:%
-%:%265=178%:%
-%:%266=178%:%
-%:%267=179%:%
-%:%268=179%:%
-%:%269=180%:%
-%:%270=180%:%
-%:%271=181%:%
-%:%272=181%:%
-%:%273=181%:%
-%:%274=182%:%
-%:%284=184%:%
-%:%285=185%:%
-%:%286=186%:%
-%:%287=187%:%
-%:%288=188%:%
-%:%290=190%:%
-%:%291=190%:%
-%:%292=191%:%
-%:%294=193%:%
-%:%295=194%:%
-%:%296=195%:%
-%:%297=196%:%
-%:%298=197%:%
-%:%299=198%:%
-%:%300=199%:%
-%:%301=200%:%
-%:%302=201%:%
-%:%303=202%:%
-%:%305=204%:%
+%:%189=132%:%
+%:%190=137%:%
+%:%191=138%:%
+%:%192=138%:%
+%:%193=139%:%
+%:%195=140%:%
+%:%196=141%:%
+%:%197=142%:%
+%:%200=144%:%
+%:%201=145%:%
+%:%202=146%:%
+%:%203=147%:%
+%:%204=148%:%
+%:%205=149%:%
+%:%206=150%:%
+%:%210=152%:%
+%:%211=153%:%
+%:%213=155%:%
+%:%214=155%:%
+%:%216=156%:%
+%:%217=156%:%
+%:%218=157%:%
+%:%219=157%:%
+%:%221=158%:%
+%:%222=159%:%
+%:%223=159%:%
+%:%224=160%:%
+%:%225=160%:%
+%:%227=161%:%
+%:%230=163%:%
+%:%231=164%:%
+%:%232=165%:%
+%:%233=166%:%
+%:%235=168%:%
+%:%236=168%:%
+%:%237=169%:%
+%:%238=170%:%
+%:%240=171%:%
+%:%241=171%:%
+%:%242=172%:%
+%:%244=173%:%
+%:%245=174%:%
+%:%246=174%:%
+%:%247=175%:%
+%:%249=176%:%
+%:%250=177%:%
+%:%251=178%:%
+%:%252=179%:%
+%:%253=180%:%
+%:%254=181%:%
+%:%255=181%:%
+%:%256=182%:%
+%:%258=183%:%
+%:%259=184%:%
+%:%260=184%:%
+%:%261=185%:%
+%:%268=186%:%
+%:%269=186%:%
+%:%270=187%:%
+%:%271=187%:%
+%:%272=188%:%
+%:%273=188%:%
+%:%275=189%:%
+%:%276=190%:%
+%:%277=191%:%
+%:%278=192%:%
+%:%279=192%:%
+%:%280=193%:%
+%:%281=193%:%
+%:%282=194%:%
+%:%283=194%:%
+%:%284=195%:%
+%:%285=195%:%
+%:%286=196%:%
+%:%287=196%:%
+%:%288=196%:%
+%:%290=197%:%
+%:%291=198%:%
+%:%292=198%:%
+%:%293=199%:%
+%:%303=201%:%
+%:%304=202%:%
+%:%305=203%:%
 %:%306=204%:%
 %:%307=205%:%
-%:%308=206%:%
+%:%309=207%:%
 %:%310=207%:%
-%:%311=207%:%
-%:%312=208%:%
-%:%314=209%:%
-%:%315=210%:%
-%:%316=210%:%
-%:%317=211%:%
-%:%319=212%:%
-%:%320=212%:%
-%:%321=213%:%
-%:%323=214%:%
-%:%324=215%:%
-%:%325=215%:%
-%:%326=216%:%
-%:%329=217%:%
-%:%333=217%:%
-%:%334=217%:%
-%:%343=219%:%
-%:%344=220%:%
-%:%345=221%:%
-%:%346=222%:%
-%:%347=223%:%
-%:%348=224%:%
-%:%349=225%:%
-%:%350=226%:%
-%:%351=227%:%
-%:%352=228%:%
-%:%353=229%:%
-%:%362=233%:%
-%:%374=235%:%
-%:%375=236%:%
-%:%376=237%:%
-%:%377=238%:%
-%:%378=239%:%
-%:%379=240%:%
-%:%380=241%:%
-%:%381=242%:%
-%:%382=243%:%
-%:%383=244%:%
-%:%384=245%:%
-%:%385=246%:%
-%:%386=247%:%
-%:%387=248%:%
-%:%388=249%:%
-%:%389=250%:%
-%:%391=252%:%
-%:%392=252%:%
-%:%394=253%:%
+%:%311=208%:%
+%:%313=210%:%
+%:%314=211%:%
+%:%315=212%:%
+%:%316=213%:%
+%:%317=214%:%
+%:%318=215%:%
+%:%319=216%:%
+%:%320=217%:%
+%:%321=218%:%
+%:%322=219%:%
+%:%324=221%:%
+%:%325=221%:%
+%:%326=222%:%
+%:%327=223%:%
+%:%329=224%:%
+%:%330=224%:%
+%:%331=225%:%
+%:%333=226%:%
+%:%334=227%:%
+%:%335=227%:%
+%:%336=228%:%
+%:%338=229%:%
+%:%339=229%:%
+%:%340=230%:%
+%:%342=231%:%
+%:%343=232%:%
+%:%344=232%:%
+%:%345=233%:%
+%:%348=234%:%
+%:%352=234%:%
+%:%353=234%:%
+%:%362=236%:%
+%:%363=237%:%
+%:%364=238%:%
+%:%365=239%:%
+%:%366=240%:%
+%:%367=241%:%
+%:%368=242%:%
+%:%369=243%:%
+%:%370=244%:%
+%:%371=245%:%
+%:%372=246%:%
+%:%381=249%:%
+%:%393=251%:%
+%:%394=252%:%
 %:%395=253%:%
 %:%396=254%:%
-%:%397=254%:%
-%:%399=255%:%
-%:%400=256%:%
-%:%401=257%:%
-%:%402=257%:%
-%:%403=258%:%
-%:%404=258%:%
-%:%406=259%:%
-%:%407=259%:%
-%:%408=260%:%
-%:%409=260%:%
-%:%411=261%:%
-%:%412=261%:%
-%:%413=262%:%
-%:%414=262%:%
-%:%415=263%:%
-%:%417=264%:%
-%:%418=265%:%
-%:%419=266%:%
-%:%420=266%:%
-%:%421=267%:%
-%:%422=268%:%
-%:%423=268%:%
-%:%425=269%:%
-%:%426=269%:%
-%:%427=270%:%
-%:%428=270%:%
-%:%429=271%:%
-%:%431=272%:%
-%:%432=272%:%
-%:%433=273%:%
-%:%434=273%:%
-%:%436=274%:%
-%:%437=274%:%
-%:%438=275%:%
-%:%439=275%:%
-%:%440=276%:%
-%:%442=277%:%
-%:%443=278%:%
-%:%446=280%:%
-%:%447=281%:%
-%:%448=282%:%
-%:%450=284%:%
-%:%451=284%:%
-%:%452=285%:%
-%:%454=286%:%
-%:%455=286%:%
-%:%456=287%:%
-%:%458=288%:%
-%:%459=289%:%
-%:%460=290%:%
-%:%461=290%:%
-%:%462=291%:%
-%:%464=292%:%
-%:%465=292%:%
-%:%466=293%:%
-%:%468=294%:%
-%:%469=295%:%
-%:%470=295%:%
-%:%471=296%:%
-%:%478=297%:%
-%:%479=297%:%
-%:%481=298%:%
-%:%482=299%:%
-%:%483=300%:%
-%:%484=301%:%
-%:%485=301%:%
-%:%486=302%:%
-%:%487=302%:%
-%:%488=303%:%
-%:%489=303%:%
-%:%490=303%:%
-%:%491=304%:%
-%:%492=304%:%
-%:%493=305%:%
-%:%494=305%:%
-%:%495=305%:%
-%:%496=306%:%
-%:%497=306%:%
-%:%498=307%:%
-%:%499=307%:%
-%:%500=307%:%
-%:%501=308%:%
-%:%511=310%:%
-%:%512=311%:%
-%:%513=312%:%
-%:%514=313%:%
-%:%515=314%:%
-%:%516=315%:%
-%:%517=316%:%
-%:%518=317%:%
-%:%520=319%:%
-%:%521=319%:%
-%:%522=320%:%
-%:%523=321%:%
-%:%525=322%:%
-%:%526=322%:%
-%:%527=323%:%
-%:%529=324%:%
-%:%530=325%:%
-%:%531=325%:%
-%:%532=326%:%
-%:%534=327%:%
-%:%535=328%:%
-%:%536=329%:%
-%:%537=330%:%
-%:%538=330%:%
-%:%539=331%:%
-%:%541=332%:%
-%:%542=333%:%
-%:%543=334%:%
-%:%544=335%:%
-%:%545=336%:%
-%:%546=336%:%
-%:%547=337%:%
-%:%549=338%:%
-%:%550=339%:%
-%:%551=339%:%
-%:%552=340%:%
-%:%555=341%:%
-%:%559=341%:%
-%:%560=341%:%
-%:%561=341%:%
-%:%563=342%:%
-%:%564=343%:%
-%:%565=344%:%
-%:%575=346%:%
-%:%576=347%:%
-%:%577=348%:%
-%:%579=350%:%
-%:%580=350%:%
-%:%581=351%:%
-%:%583=352%:%
-%:%584=352%:%
-%:%585=353%:%
-%:%587=354%:%
-%:%588=354%:%
-%:%589=355%:%
-%:%591=356%:%
-%:%592=356%:%
-%:%593=357%:%
-%:%595=358%:%
-%:%596=358%:%
-%:%597=359%:%
-%:%599=360%:%
-%:%600=361%:%
-%:%601=361%:%
-%:%602=362%:%
-%:%609=363%:%
-%:%610=363%:%
-%:%611=364%:%
-%:%612=364%:%
-%:%613=365%:%
-%:%614=365%:%
-%:%615=365%:%
-%:%616=366%:%
-%:%617=366%:%
-%:%618=367%:%
-%:%619=367%:%
-%:%620=367%:%
-%:%621=368%:%
-%:%622=368%:%
-%:%623=369%:%
-%:%624=369%:%
-%:%625=369%:%
-%:%626=370%:%
-%:%636=372%:%
-%:%637=373%:%
-%:%638=374%:%
-%:%639=375%:%
-%:%640=376%:%
-%:%641=377%:%
-%:%642=378%:%
-%:%643=379%:%
-%:%644=380%:%
-%:%645=381%:%
-%:%646=382%:%
-%:%647=383%:%
-%:%648=384%:%
-%:%649=385%:%
-%:%650=386%:%
-%:%651=387%:%
-%:%660=389%:%
+%:%397=255%:%
+%:%398=256%:%
+%:%399=257%:%
+%:%400=258%:%
+%:%401=259%:%
+%:%402=260%:%
+%:%403=261%:%
+%:%404=262%:%
+%:%405=263%:%
+%:%406=264%:%
+%:%407=265%:%
+%:%408=266%:%
+%:%409=267%:%
+%:%410=268%:%
+%:%411=269%:%
+%:%412=270%:%
+%:%414=272%:%
+%:%415=272%:%
+%:%417=273%:%
+%:%418=273%:%
+%:%419=274%:%
+%:%420=274%:%
+%:%422=275%:%
+%:%423=276%:%
+%:%424=277%:%
+%:%425=277%:%
+%:%426=278%:%
+%:%427=278%:%
+%:%429=279%:%
+%:%430=279%:%
+%:%431=280%:%
+%:%432=280%:%
+%:%434=281%:%
+%:%435=281%:%
+%:%436=282%:%
+%:%437=282%:%
+%:%438=283%:%
+%:%440=284%:%
+%:%441=285%:%
+%:%442=286%:%
+%:%443=286%:%
+%:%444=287%:%
+%:%445=288%:%
+%:%446=288%:%
+%:%448=289%:%
+%:%449=289%:%
+%:%450=290%:%
+%:%451=290%:%
+%:%452=291%:%
+%:%454=292%:%
+%:%455=292%:%
+%:%456=293%:%
+%:%457=293%:%
+%:%459=294%:%
+%:%460=294%:%
+%:%461=295%:%
+%:%462=295%:%
+%:%463=296%:%
+%:%465=297%:%
+%:%466=298%:%
+%:%469=300%:%
+%:%470=301%:%
+%:%471=302%:%
+%:%473=304%:%
+%:%474=304%:%
+%:%475=305%:%
+%:%477=306%:%
+%:%478=306%:%
+%:%479=307%:%
+%:%481=308%:%
+%:%482=309%:%
+%:%483=310%:%
+%:%484=311%:%
+%:%485=311%:%
+%:%486=312%:%
+%:%488=313%:%
+%:%489=313%:%
+%:%490=314%:%
+%:%492=315%:%
+%:%493=316%:%
+%:%494=316%:%
+%:%495=317%:%
+%:%502=318%:%
+%:%503=318%:%
+%:%505=319%:%
+%:%506=320%:%
+%:%507=321%:%
+%:%508=322%:%
+%:%509=322%:%
+%:%510=323%:%
+%:%511=323%:%
+%:%512=324%:%
+%:%513=324%:%
+%:%514=324%:%
+%:%515=325%:%
+%:%516=325%:%
+%:%517=326%:%
+%:%518=326%:%
+%:%519=326%:%
+%:%520=327%:%
+%:%521=327%:%
+%:%522=328%:%
+%:%523=328%:%
+%:%524=328%:%
+%:%525=329%:%
+%:%535=331%:%
+%:%536=332%:%
+%:%537=333%:%
+%:%538=334%:%
+%:%539=335%:%
+%:%540=336%:%
+%:%541=337%:%
+%:%542=338%:%
+%:%543=339%:%
+%:%545=341%:%
+%:%546=341%:%
+%:%547=342%:%
+%:%548=343%:%
+%:%550=344%:%
+%:%551=344%:%
+%:%552=345%:%
+%:%554=346%:%
+%:%555=347%:%
+%:%556=347%:%
+%:%557=348%:%
+%:%559=349%:%
+%:%560=350%:%
+%:%561=351%:%
+%:%562=352%:%
+%:%563=353%:%
+%:%564=353%:%
+%:%565=354%:%
+%:%567=355%:%
+%:%568=356%:%
+%:%569=357%:%
+%:%570=358%:%
+%:%571=359%:%
+%:%572=360%:%
+%:%573=360%:%
+%:%574=361%:%
+%:%576=362%:%
+%:%577=363%:%
+%:%578=363%:%
+%:%579=364%:%
+%:%582=365%:%
+%:%586=365%:%
+%:%587=365%:%
+%:%588=365%:%
+%:%590=366%:%
+%:%591=367%:%
+%:%592=368%:%
+%:%602=370%:%
+%:%603=371%:%
+%:%604=372%:%
+%:%606=374%:%
+%:%607=374%:%
+%:%608=375%:%
+%:%610=376%:%
+%:%611=376%:%
+%:%612=377%:%
+%:%614=378%:%
+%:%615=378%:%
+%:%616=379%:%
+%:%618=380%:%
+%:%619=380%:%
+%:%620=381%:%
+%:%622=382%:%
+%:%623=382%:%
+%:%624=383%:%
+%:%626=384%:%
+%:%627=385%:%
+%:%628=385%:%
+%:%629=386%:%
+%:%636=387%:%
+%:%637=387%:%
+%:%638=388%:%
+%:%639=388%:%
+%:%640=389%:%
+%:%641=389%:%
+%:%642=389%:%
+%:%643=390%:%
+%:%644=390%:%
+%:%645=391%:%
+%:%646=391%:%
+%:%647=391%:%
+%:%648=392%:%
+%:%649=392%:%
+%:%650=393%:%
+%:%651=393%:%
+%:%652=393%:%
+%:%653=394%:%
+%:%663=396%:%
+%:%664=397%:%
+%:%665=398%:%
+%:%666=399%:%
+%:%667=400%:%
+%:%668=401%:%
+%:%669=402%:%
+%:%670=403%:%
+%:%671=404%:%
+%:%672=405%:%
+%:%673=406%:%
+%:%674=407%:%
+%:%675=408%:%
+%:%676=409%:%
+%:%677=410%:%
+%:%678=411%:%
+%:%679=412%:%
+%:%680=413%:%
+%:%681=414%:%
+%:%682=415%:%
+%:%683=416%:%
+%:%684=417%:%
+%:%685=418%:%
+%:%686=419%:%
+%:%687=420%:%
+%:%688=421%:%
+%:%692=424%:%
+%:%693=425%:%
+%:%694=426%:%
+%:%695=427%:%
+%:%696=428%:%
+%:%697=429%:%
+%:%698=430%:%
+%:%699=431%:%
+%:%700=432%:%
+%:%701=433%:%
+%:%702=434%:%
+%:%703=435%:%
+%:%704=436%:%
+%:%705=437%:%
+%:%706=438%:%
+%:%707=439%:%
+%:%708=440%:%
+%:%709=441%:%
+%:%710=442%:%
+%:%711=443%:%
+%:%712=444%:%
+%:%713=445%:%
+%:%714=446%:%
+%:%715=447%:%
+%:%716=448%:%
+%:%717=449%:%
+%:%718=450%:%
+%:%719=451%:%
+%:%720=452%:%
+%:%721=453%:%
+%:%722=454%:%
+%:%723=455%:%
+%:%724=456%:%
+%:%725=457%:%
+%:%726=458%:%
+%:%727=459%:%
+%:%728=460%:%
+%:%729=461%:%
+%:%730=462%:%
+%:%731=463%:%
+%:%732=464%:%
+%:%733=465%:%
+%:%734=466%:%
+%:%735=467%:%
+%:%736=468%:%
+%:%737=469%:%
+%:%738=470%:%
+%:%739=471%:%
+%:%740=472%:%
+%:%741=473%:%
+%:%742=474%:%
+%:%743=475%:%
+%:%744=476%:%
+%:%745=477%:%
+%:%746=478%:%
+%:%755=480%:%

### 2021-11-26 paper/output/document/threeflags.tex
and that's chapter 4

@@
 are identical. Kant believes that his argument for the equality of the formulas is analytical, and
-if he is correct, it should be possible to recreate the argument in logic.%
+if he is correct, it should be possible to recreate the argument in logic.
+
+Those who do not believe that all three formulations of the categorical imperative are equivalent may
+understand the FUL as the strongest or most foundational, and thus an appropriate initial choice for 
+formalizations. Korsgaard characterizes the three formulations of the categorical
+imperative according to Rawls' general and special conception of justice. The general conception applies
+universally and can never be violated and the special conception represents an ideal for us to
+live towards. For example, the special conception may require that we prefer some job applicants
+over others in order to remedy historical injustice, and the general conception may require that such
+inequalities always operate in the service of the least privileged \citep[19]{KorsgaardRTL}. Korsgaard
+argues that the Formula of Universal Law represents Kant's general conception of justice, and the Formula of 
+Humanity represents his special conception. The FUL's prescriptions can never be violated, even in the most
+non-ideal circumstances imaginable, but the FUH is merely a standard to live towards that might not be 
+achieved. In this sense, the FUL generates stronger requirements than the other two formulations and is 
+thus the bare minimum of Kant's ethics. Because the FUL's prescriptions outweigh those of the other two formulations,
+formalizing it creates a functional, minimum ethical theory that can serve as a foundation for implementations
+of other aspects of Kant's ethics.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %:%88=64%:%
-%:%97=66%:%
-%:%109=68%:%
-%:%110=69%:%
-%:%111=70%:%
-%:%112=71%:%
-%:%113=72%:%
-%:%114=73%:%
-%:%115=74%:%
-%:%116=75%:%
-%:%117=76%:%
-%:%118=77%:%
-%:%119=78%:%
-%:%120=79%:%
-%:%121=80%:%
-%:%122=81%:%
-%:%123=82%:%
-%:%124=83%:%
+%:%89=65%:%
+%:%90=66%:%
+%:%91=67%:%
+%:%92=68%:%
+%:%93=69%:%
+%:%94=70%:%
+%:%95=71%:%
+%:%96=72%:%
+%:%97=73%:%
+%:%98=74%:%
+%:%99=75%:%
+%:%100=76%:%
+%:%101=77%:%
+%:%102=78%:%
+%:%103=79%:%
+%:%104=80%:%
+%:%113=82%:%
 %:%125=84%:%
@@
 %:%130=89%:%
-%:%139=91%:%
-%:%151=93%:%
-%:%152=94%:%
-%:%153=95%:%
-%:%154=96%:%
-%:%155=97%:%
-%:%156=98%:%
-%:%157=99%:%
-%:%158=100%:%
-%:%159=101%:%
-%:%160=102%:%
-%:%161=103%:%
-%:%162=104%:%
-%:%163=105%:%
-%:%164=106%:%
-%:%165=107%:%
-%:%166=108%:%
+%:%131=90%:%
+%:%132=91%:%
+%:%133=92%:%
+%:%134=93%:%
+%:%135=94%:%
+%:%136=95%:%
+%:%137=96%:%
+%:%138=97%:%
+%:%139=98%:%
+%:%140=99%:%
+%:%141=100%:%
+%:%142=101%:%
+%:%143=102%:%
+%:%144=103%:%
+%:%145=104%:%
+%:%146=105%:%
+%:%155=107%:%
 %:%167=109%:%
@@
 %:%202=144%:%
-%:%211=146%:%
-%:%223=148%:%
-%:%224=149%:%
-%:%225=150%:%
-%:%226=151%:%
-%:%227=152%:%
-%:%228=153%:%
-%:%229=154%:%
-%:%230=155%:%
-%:%231=156%:%
-%:%232=157%:%
-%:%233=158%:%
-%:%234=159%:%
-%:%235=160%:%
-%:%236=161%:%
-%:%237=162%:%
-%:%238=163%:%
+%:%203=145%:%
+%:%204=146%:%
+%:%205=147%:%
+%:%206=148%:%
+%:%207=149%:%
+%:%208=150%:%
+%:%209=151%:%
+%:%210=152%:%
+%:%211=153%:%
+%:%212=154%:%
+%:%213=155%:%
+%:%214=156%:%
+%:%215=157%:%
+%:%216=158%:%
+%:%217=159%:%
+%:%218=160%:%
+%:%227=162%:%
 %:%239=164%:%
@@
 %:%245=170%:%
-%:%254=172%:%
-%:%266=174%:%
-%:%267=175%:%
-%:%268=176%:%
-%:%269=177%:%
-%:%270=178%:%
-%:%271=179%:%
-%:%272=180%:%
-%:%273=181%:%
-%:%274=182%:%
-%:%275=183%:%
-%:%276=184%:%
-%:%277=185%:%
-%:%278=186%:%
-%:%279=187%:%
-%:%280=188%:%
-%:%281=189%:%
+%:%246=171%:%
+%:%247=172%:%
+%:%248=173%:%
+%:%249=174%:%
+%:%250=175%:%
+%:%251=176%:%
+%:%252=177%:%
+%:%253=178%:%
+%:%254=179%:%
+%:%255=180%:%
+%:%256=181%:%
+%:%257=182%:%
+%:%258=183%:%
+%:%259=184%:%
+%:%260=185%:%
+%:%261=186%:%
+%:%270=188%:%
 %:%282=190%:%
@@
 %:%318=226%:%
+%:%319=227%:%
+%:%320=228%:%
+%:%321=229%:%
+%:%322=230%:%
+%:%323=231%:%
+%:%324=232%:%
+%:%325=233%:%
+%:%326=234%:%
+%:%327=235%:%
+%:%328=236%:%
+%:%329=237%:%
+%:%330=238%:%
+%:%331=239%:%
+%:%332=240%:%
+%:%333=241%:%
+%:%334=242%:%

### 2021-11-27 paper/abstract.tex
abstract

\documentclass[11pt]{article}
\usepackage{xcolor}
\usepackage{times}
\usepackage[margin=1in]{geometry}

\begin{document}

\noindent \textbf{CAKE: Computational and Automated Kantian Ethics}

\medskip

\noindent \textbf{Abstract}: As artifically intelligent agents become increasingly powerful, the need for philosophically
sophisticated automated ethical reasoning becomes more pressing. Representing a robust ethical theory 
to a computer poses technical and ethical challenges. I argue that, out of the three major ethical traditions, Kantian ethics is
most natural to formalize because it presents inviolable, context-agnostic, formal rules. In this paper, 
I present CAKE, an implementation of automated Kantian ethics that is faithful to the rich Kantian 
philosophical tradition. I formalize Kant's categorical imperative in deontic logic, implement this 
formalization in the Isabelle/HOL theorem prover, and develop a testing framework to evaluate how well 
my implementation coheres with expected properties of Kantian ethics. Not only is CAKE an early step 
towards philosophically rich ethical AI agents, it also establishes that computational tools can help 
philosophers reach ethical insights.

\smallskip
\noindent \emph{Areas: algorithm development, applications, philosophy}
\end{document}

### 2021-12-01 paper/output/document/application.tex
added will notes

@@
 In this chapter, I 
-demonstrate my system's ability to formalize longer, more complicated ethical arguments and understand 
+demonstrate my system's ability to formalize longer, more complicated ethical arguments and present 
 the additional capabilities necessary to use my system in practice. In Chapter 2
@@
 what an agent should or should not do. Applied ethical reasoning is relevant with respect to an agent's
-particular situation, not just an an ethical theory as an abstract entity. In previous chapters' application tests,
+particular situation, not just to an ethical theory as an abstract entity. In previous chapters' application tests,
 I performed some toy examples of applied ethical reasoning, but in this chapter, I expore how my system can 
@@
 part of the process of practical reasoning itself \citep{silber}. \citet{powers} notes that common sense 
-is a hurder for an automated Kantian ethical agent. In this chapter, I attempt to tackle this challenge and
+is a hurdle for an automated Kantian ethical agent. In this chapter, I attempt to tackle this challenge and
 endow my system with this kind of common sense in the specific case of lying. In order for my 
@@
 formulator.
+
+In this paper, I contribute an implementation of the Formula of Universal Law that, when equipped with 
+relatively thin common sense facts, can performed nuanced, sophisticated ethical reasoning. When given 
+as input a maxim in the format specified in Chapter 3, my system can show that the maxim is permissible, 
+obligatory, or prohibited. It can provide a verifiable proof of its judgement and a human-readable list
+of the facts or axioms it used to reach its conclusion. My system is faithful to philosophical literatire
+on Kantian ethics and serves as the first step towards a fully or partially automated ethical AI agent. 
+It also establishes the power and potential of computational ethics, or the use of computational tools
+for ethical investigation, as explored in this section's Applied Ethical reasoning.
 
@@
 %
-\isamarkupcmt{Unlike many of the other proofs in this project, this proof was a little heavier and required some manual
-work to produce. I divided the proof into the intermediate steps shown here, and Isabelle was able to do 
+\isamarkupcmt{Unlike many of the other proofs in this project, this proof is a little heavier and requires some manual
+work to produce. After I divide the proof into the intermediate steps shown here, and Isabelle is able to do 
 the rest. This step says that if $m$ is universalized, then the circumstances won't lead to the goal, 
@@
 does not interfere with the purpose of jokes, which is to amuse and does not depend on
-deception" \citep[4]{KorsgaardRTL}. First, I define a joke..%
+deception" \citep[4]{KorsgaardRTL}. First, I define a joke.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-This completes my implementation of Korsgaard's first interpretation of lying. Using the convention
-of lying assumption formalized in this section, I show that lying is generally prohibited but joking
-is permissible. Notice that this is already a sophisticated kind of ethical reasoning. The sophistication
-necessary to distinguish between lying and joking is a direct consequence of my system's use of a robust
-conception of a maxim, which encodes the goal of an act as part of the maxim being evaluated. This kind 
-of ethical reasoning also requires relatively few and uncontroversial common sense facts. The deepest
+One potential worry with the above argument is the fact that my definition of joke requires that 
+achieving the goal of a joke does not rely on anyone believing the falsehood told in the joke. On its face, 
+this is not a complete representation of a joke; the ordinary conception of a joke would be something like 
+a false statement uttered with the goal of amusing. I define the goal of the joke as not requiring that 
+anyone believe the false statement to distinguish it from lying, which has deception as the goal. I 
+intentionally avoid providing robust formalizations of both deception and amusement; instead I present a 
+thin conception that relies entirely on the concept of belief. This conception does not require any notion
+of humor, satire, intention, or malice, all of which are concepts that may be necessary to define 
+amusement and deception completely.
+
+The fact that my system shows that lies are prohibited and jokes are permissible with these things 
+conceptions of amusement and deception shows that my system isolates a necessary and sufficient property 
+of a class of maxims that fail the universalizability test. Because my definitions of a lie and joke
+only differ in whether or not their goal requires that someone believe the falsehood in question, the
+theorems proved in this section show that, in order for a maxim with the act of knowingly uttering a falsehood
+to be prohobited, the goal requires that someone believe the falsehood is a necessary and sufficient condition. 
+This logical fact derived by my system tracks a fact implicit in Korsgaard's argument and in most Kantian accounts
+of lying: the wrongness of lying is derived from the requirement that someone believe the falsehood. 
+The logical reality that this property is necessary and sufficient to generate a prohibition reflects
+a deep philosohopical explanation of \emph{why} certain maxims about uttering falsehood fail the universalizability
+test and why others pass. In simple terms, universalizing uttering a falsehood makes belief in that 
+falsehood impossible, so any maxims with goals that require believing in the falsehood will be prohibited.
+
+This account not only describes the kind of maxims that fail or pass the universalizability test, it 
+also provides a guide to constructing permissible maxims about uttering falsehoods. As an example, 
+consider the idea of throwing a surprise birthday party. At first glance, the maxim of action is 
+something like, ``When it is my friend's birthday, I will secretly plan a party so that I can surprise
+them." The goal ``so that I can surprise them" clearly requires that your friend believe the falsehood that 
+you are not planning a party, else the surprise would be ruined. The analysis above seems to imply that 
+Kantian ethics would prohibit surprise parties, which is a sad conclusion for birthday-lovers everywhere. 
+Noticing that the problem with this maxim is that the goal requires belief
+in a falsehood provides a way to rescue the beloved concept of surprise parties. When throwing a 
+surprise party, the ultimate objective is \emph{not} to surprise your friend, but is to celebrate
+your friend and help them have a fun birthday. If someone ruins the surprise, but the party is still fun
+and the birthday person still feels loved, then we would consider such a party a success! Someone who
+called this party a failure clearly would be missing the point of a surprise party. Thus, the goal of 
+a surprise party is not the surprise itself, but rather to celebrate the birthday person. Thus modified, 
+the goal no longer requires belief in the falsehood and thus passes the universalizability test.
+
+The implications of this section are twofold. First, my system is capable of performing ethical reasoning
+sophisticated enough to show that lying is prohibited but joking is not. The sophistication
+necessary to distinguish between lying and joking was a direct consequence of my system's use of a robust
+conception of a maxim, which encoded the goal of an act as part of the maxim being evaluated. Second, 
+in the process of making this argument precise, my system isolated a necessary and sufficient condition 
+of a maxim about uttering a falsehood being prohibited: that the goal require that someone believe
+the falsehood. This condition both made an long-standing argument in Kantian ethics more precise
+and can guide the correct formulation of future maxims. In other words, an insight generated by the 
+computer provides value to ethicists.
+
+Moreover, all of the reasoning in this chapter required relatively few and uncontroversial common sense facts. The deepest
 assumption required was that, if everyone lies about a given statement, no one will believe that 
@@
 world, but it is relatively uncontroversial. Indeed, it is so well-accepted that Korsgaard does not 
-bother to justify it in her argument. These examples demonstrate that, while common sense reasoning 
+bother to justify it in her argument. These examples showed that, while common sense reasoning 
 is an obstacle that must be overcome for my system to be used in practice, it is surmountable.%
@@
 This is an example of the kind of situation-specific common sense reasoning necessary to use my system.
-Again, this is an uncontroversial statement; the murderer assumes that if you knew he was a murderer, you 
-would not disclose the victim's location to him. SHOULD I SAY MORE HERE?%
+Again, this is Korsgaard's uncontroversial assumption; the murderer assumes that if you knew he was a murderer, you 
+would not disclose the victim's location to him.%
 }\isanewline
@@
 directly from Korsgaard's conception of universalizability: when a maxim is universalized, everyone 
-wills it. Korsgaard assumes that if everyone wills a maxim, they also believe that everyone else wills it.
-DO I NEED TO SAY MORE HERE?%
+wills it and thus notices the pattern of everyone willing it. If you observe that many do X in circumstances C,
+you will assume that everyone does X in circumstance C.%
 }\isanewline
@@
 modifying the common sense facts used, my system can show that lying to a liar is permissible, but lying 
-in order to find a victim is not. The assumptions used in this example are a little more robust, but still
-ultimately uncontroversial. Indeed, they are direct consequences of Korsgaard's definition of willing 
+in order to find a victim is not. The assumptions used in this example were a little more robust, but still
+ultimately uncontroversial because they were direct consequences of Korsgaard's definition of willing 
 and of ordinary definitions of lying. These thin assumptions were sufficient to generate moral conclusions
-that Kantian scholars debate robustly. Indeed, armed with this common sense, my system generated 
+that Kantian scholars debate robustly. Armed with this common sense, my system generated 
 a conclusion that many critics of Kant failed to see.
@@
 noting that, while the FUL shows that lying to the murderer permissible, other parts of Kant's ethics
-will show that it is obligatory. Recall that Kant presents perfect and imperfect duties,
+show that it is obligatory. Recall that Kant presents perfect and imperfect duties,
 where the former are strict, inviolable, and specific and the latter are broader prescriptions for action.
@@
 also shows how vital the role of the common sense reasoning is. Slight, intuitive changes in the common
-sense facts can achieve totally different conclusions about lying. This represents an obstacle to 
+sense facts achieved totally different conclusions about lying. This represents an obstacle to 
 fully automated ethical reasoning; such an agent would need a trusted database of common 
@@
 
-The reasoning of this section also demonstrates one additional place where a Kantian must make vital judgements:
+The reasoning of this section also demonstrated one additional place where a Kantian must make vital judgements:
 the formulation of the maxim itself. Korsgaard's argument for the permissibility of lying to a 
@@
 of the maxim be ``morally relevant." In the example above, my purple shirt and the date clearly have no bearing on 
-the moral status of lying. On the other hand, consider the maxim ``When I am unmeployed, I will murder
+the moral status of lying. On the other hand, consider the maxim, ``When I am unmeployed, I will murder
 someone in order to take their job." The circumstances of being unmeployed clearly have some bearing on the moral
@@
 they act on. Circumstances are morally relevant if they accurately reflect the way that the agent is 
-thinking about their own action. In the example above, the circumstances of wearing a purple shirt don't
-the principle of the liar's action. They are clearly a disingenous attempt to evade the universalizability
+thinking about their own action. In the example above, the circumstances of wearing a purple shirt don't reflect
+the principle of the liar's action. Their inclusion is clearly a disingenous attempt to evade the universalizability
 test, but because the FUL is a test of personal integrity, it cannot withstand this kind of mental
@@
 The formulation of a maxim and the common sense database pose the two greatest challenges to the adoption
-of my system in practice. In this chapter, I argue that using manual, human involvement, these challenges
+of my system in practice. In this chapter, I argued that using manual, human involvement, these challenges
 can be overcome in relatively uncontroversial ways. They are also ripe areas for future work.%
@@
 %:%120=92%:%
-%:%129=94%:%
-%:%141=96%:%
-%:%142=97%:%
-%:%143=98%:%
-%:%144=99%:%
-%:%145=100%:%
-%:%146=101%:%
-%:%147=102%:%
-%:%148=103%:%
-%:%149=104%:%
+%:%121=93%:%
+%:%122=94%:%
+%:%123=95%:%
+%:%124=96%:%
+%:%125=97%:%
+%:%126=98%:%
+%:%127=99%:%
+%:%128=100%:%
+%:%129=101%:%
+%:%138=103%:%
 %:%150=105%:%
@@
 %:%157=112%:%
+%:%158=113%:%
 %:%159=114%:%
-%:%160=114%:%
-%:%162=115%:%
-%:%163=116%:%
-%:%164=117%:%
-%:%165=118%:%
-%:%166=119%:%
-%:%167=120%:%
-%:%168=121%:%
-%:%169=121%:%
-%:%170=122%:%
-%:%171=123%:%
-%:%172=123%:%
-%:%174=124%:%
-%:%175=124%:%
-%:%176=125%:%
-%:%177=125%:%
-%:%178=126%:%
-%:%180=127%:%
-%:%181=127%:%
-%:%182=128%:%
-%:%183=128%:%
-%:%184=129%:%
-%:%186=130%:%
-%:%187=131%:%
-%:%188=132%:%
-%:%189=132%:%
-%:%190=137%:%
-%:%191=138%:%
-%:%192=138%:%
-%:%193=139%:%
-%:%195=140%:%
-%:%196=141%:%
-%:%197=142%:%
-%:%200=144%:%
-%:%201=145%:%
-%:%202=146%:%
-%:%203=147%:%
-%:%204=148%:%
-%:%205=149%:%
-%:%206=150%:%
-%:%210=152%:%
-%:%211=153%:%
-%:%213=155%:%
-%:%214=155%:%
-%:%216=156%:%
-%:%217=156%:%
-%:%218=157%:%
-%:%219=157%:%
-%:%221=158%:%
-%:%222=159%:%
-%:%223=159%:%
-%:%224=160%:%
-%:%225=160%:%
-%:%227=161%:%
-%:%230=163%:%
-%:%231=164%:%
-%:%232=165%:%
-%:%233=166%:%
-%:%235=168%:%
-%:%236=168%:%
-%:%237=169%:%
-%:%238=170%:%
-%:%240=171%:%
-%:%241=171%:%
-%:%242=172%:%
-%:%244=173%:%
-%:%245=174%:%
-%:%246=174%:%
-%:%247=175%:%
-%:%249=176%:%
-%:%250=177%:%
-%:%251=178%:%
-%:%252=179%:%
-%:%253=180%:%
-%:%254=181%:%
-%:%255=181%:%
-%:%256=182%:%
-%:%258=183%:%
-%:%259=184%:%
-%:%260=184%:%
-%:%261=185%:%
-%:%268=186%:%
-%:%269=186%:%
-%:%270=187%:%
-%:%271=187%:%
-%:%272=188%:%
-%:%273=188%:%
-%:%275=189%:%
-%:%276=190%:%
-%:%277=191%:%
-%:%278=192%:%
-%:%279=192%:%
-%:%280=193%:%
-%:%281=193%:%
-%:%282=194%:%
-%:%283=194%:%
-%:%284=195%:%
-%:%285=195%:%
-%:%286=196%:%
-%:%287=196%:%
-%:%288=196%:%
-%:%290=197%:%
-%:%291=198%:%
-%:%292=198%:%
-%:%293=199%:%
-%:%303=201%:%
-%:%304=202%:%
-%:%305=203%:%
-%:%306=204%:%
-%:%307=205%:%
-%:%309=207%:%
-%:%310=207%:%
-%:%311=208%:%
-%:%313=210%:%
-%:%314=211%:%
-%:%315=212%:%
-%:%316=213%:%
-%:%317=214%:%
-%:%318=215%:%
+%:%160=115%:%
+%:%161=116%:%
+%:%162=117%:%
+%:%163=118%:%
+%:%164=119%:%
+%:%165=120%:%
+%:%166=121%:%
+%:%168=123%:%
+%:%169=123%:%
+%:%171=124%:%
+%:%172=125%:%
+%:%173=126%:%
+%:%174=127%:%
+%:%175=128%:%
+%:%176=129%:%
+%:%177=130%:%
+%:%178=130%:%
+%:%179=131%:%
+%:%180=132%:%
+%:%181=132%:%
+%:%183=133%:%
+%:%184=133%:%
+%:%185=134%:%
+%:%186=134%:%
+%:%187=135%:%
+%:%189=136%:%
+%:%190=136%:%
+%:%191=137%:%
+%:%192=137%:%
+%:%193=138%:%
+%:%195=139%:%
+%:%196=140%:%
+%:%197=141%:%
+%:%198=141%:%
+%:%199=146%:%
+%:%200=147%:%
+%:%201=147%:%
+%:%202=148%:%
+%:%204=149%:%
+%:%205=150%:%
+%:%206=151%:%
+%:%209=153%:%
+%:%210=154%:%
+%:%211=155%:%
+%:%212=156%:%
+%:%213=157%:%
+%:%214=158%:%
+%:%215=159%:%
+%:%219=161%:%
+%:%220=162%:%
+%:%222=164%:%
+%:%223=164%:%
+%:%225=165%:%
+%:%226=165%:%
+%:%227=166%:%
+%:%228=166%:%
+%:%230=167%:%
+%:%231=168%:%
+%:%232=168%:%
+%:%233=169%:%
+%:%234=169%:%
+%:%236=170%:%
+%:%239=172%:%
+%:%240=173%:%
+%:%241=174%:%
+%:%242=175%:%
+%:%244=177%:%
+%:%245=177%:%
+%:%246=178%:%
+%:%247=179%:%
+%:%249=180%:%
+%:%250=180%:%
+%:%251=181%:%
+%:%253=182%:%
+%:%254=183%:%
+%:%255=183%:%
+%:%256=184%:%
+%:%258=185%:%
+%:%259=186%:%
+%:%260=187%:%
+%:%261=188%:%
+%:%262=189%:%
+%:%263=190%:%
+%:%264=190%:%
+%:%265=191%:%
+%:%267=192%:%
+%:%268=193%:%
+%:%269=193%:%
+%:%270=194%:%
+%:%277=195%:%
+%:%278=195%:%
+%:%279=196%:%
+%:%280=196%:%
+%:%281=197%:%
+%:%282=197%:%
+%:%284=198%:%
+%:%285=199%:%
+%:%286=200%:%
+%:%287=201%:%
+%:%288=201%:%
+%:%289=202%:%
+%:%290=202%:%
+%:%291=203%:%
+%:%292=203%:%
+%:%293=204%:%
+%:%294=204%:%
+%:%295=205%:%
+%:%296=205%:%
+%:%297=205%:%
+%:%299=206%:%
+%:%300=207%:%
+%:%301=207%:%
+%:%302=208%:%
+%:%312=210%:%
+%:%313=211%:%
+%:%314=212%:%
+%:%315=213%:%
+%:%316=214%:%
+%:%318=216%:%
 %:%319=216%:%
 %:%320=217%:%
-%:%321=218%:%
 %:%322=219%:%
+%:%323=220%:%
 %:%324=221%:%
-%:%325=221%:%
-%:%326=222%:%
-%:%327=223%:%
-%:%329=224%:%
-%:%330=224%:%
-%:%331=225%:%
-%:%333=226%:%
-%:%334=227%:%
-%:%335=227%:%
-%:%336=228%:%
-%:%338=229%:%
-%:%339=229%:%
-%:%340=230%:%
-%:%342=231%:%
-%:%343=232%:%
-%:%344=232%:%
-%:%345=233%:%
-%:%348=234%:%
-%:%352=234%:%
-%:%353=234%:%
-%:%362=236%:%
-%:%363=237%:%
-%:%364=238%:%
-%:%365=239%:%
-%:%366=240%:%
-%:%367=241%:%
-%:%368=242%:%
-%:%369=243%:%
-%:%370=244%:%
+%:%325=222%:%
+%:%326=223%:%
+%:%327=224%:%
+%:%328=225%:%
+%:%329=226%:%
+%:%330=227%:%
+%:%331=228%:%
+%:%333=230%:%
+%:%334=230%:%
+%:%335=231%:%
+%:%336=232%:%
+%:%338=233%:%
+%:%339=233%:%
+%:%340=234%:%
+%:%342=235%:%
+%:%343=236%:%
+%:%344=236%:%
+%:%345=237%:%
+%:%347=238%:%
+%:%348=238%:%
+%:%349=239%:%
+%:%351=240%:%
+%:%352=241%:%
+%:%353=241%:%
+%:%354=242%:%
+%:%357=243%:%
+%:%361=243%:%
+%:%362=243%:%
 %:%371=245%:%
 %:%372=246%:%
-%:%381=249%:%
-%:%393=251%:%
-%:%394=252%:%
-%:%395=253%:%
-%:%396=254%:%
-%:%397=255%:%
-%:%398=256%:%
-%:%399=257%:%
-%:%400=258%:%
-%:%401=259%:%
-%:%402=260%:%
-%:%403=261%:%
-%:%404=262%:%
-%:%405=263%:%
-%:%406=264%:%
-%:%407=265%:%
-%:%408=266%:%
-%:%409=267%:%
-%:%410=268%:%
-%:%411=269%:%
-%:%412=270%:%
-%:%414=272%:%
-%:%415=272%:%
-%:%417=273%:%
-%:%418=273%:%
-%:%419=274%:%
-%:%420=274%:%
-%:%422=275%:%
-%:%423=276%:%
-%:%424=277%:%
-%:%425=277%:%
-%:%426=278%:%
-%:%427=278%:%
-%:%429=279%:%
-%:%430=279%:%
-%:%431=280%:%
-%:%432=280%:%
-%:%434=281%:%
-%:%435=281%:%
-%:%436=282%:%
-%:%437=282%:%
-%:%438=283%:%
-%:%440=284%:%
-%:%441=285%:%
-%:%442=286%:%
-%:%443=286%:%
-%:%444=287%:%
-%:%445=288%:%
-%:%446=288%:%
-%:%448=289%:%
-%:%449=289%:%
-%:%450=290%:%
-%:%451=290%:%
-%:%452=291%:%
-%:%454=292%:%
-%:%455=292%:%
-%:%456=293%:%
-%:%457=293%:%
-%:%459=294%:%
-%:%460=294%:%
-%:%461=295%:%
-%:%462=295%:%
-%:%463=296%:%
-%:%465=297%:%
-%:%466=298%:%
-%:%469=300%:%
-%:%470=301%:%
-%:%471=302%:%
-%:%473=304%:%
-%:%474=304%:%
-%:%475=305%:%
-%:%477=306%:%
-%:%478=306%:%
-%:%479=307%:%
-%:%481=308%:%
-%:%482=309%:%
-%:%483=310%:%
-%:%484=311%:%
-%:%485=311%:%
-%:%486=312%:%
-%:%488=313%:%
-%:%489=313%:%
-%:%490=314%:%
-%:%492=315%:%
-%:%493=316%:%
-%:%494=316%:%
-%:%495=317%:%
-%:%502=318%:%
-%:%503=318%:%
-%:%505=319%:%
-%:%506=320%:%
-%:%507=321%:%
-%:%508=322%:%
-%:%509=322%:%
-%:%510=323%:%
-%:%511=323%:%
-%:%512=324%:%
-%:%513=324%:%
-%:%514=324%:%
-%:%515=325%:%
-%:%516=325%:%
-%:%517=326%:%
-%:%518=326%:%
-%:%519=326%:%
-%:%520=327%:%
-%:%521=327%:%
-%:%522=328%:%
-%:%523=328%:%
-%:%524=328%:%
-%:%525=329%:%
-%:%535=331%:%
-%:%536=332%:%
-%:%537=333%:%
-%:%538=334%:%
-%:%539=335%:%
-%:%540=336%:%
-%:%541=337%:%
-%:%542=338%:%
-%:%543=339%:%
-%:%545=341%:%
-%:%546=341%:%
-%:%547=342%:%
-%:%548=343%:%
-%:%550=344%:%
-%:%551=344%:%
-%:%552=345%:%
-%:%554=346%:%
-%:%555=347%:%
-%:%556=347%:%
-%:%557=348%:%
-%:%559=349%:%
-%:%560=350%:%
-%:%561=351%:%
-%:%562=352%:%
-%:%563=353%:%
-%:%564=353%:%
-%:%565=354%:%
-%:%567=355%:%
-%:%568=356%:%
-%:%569=357%:%
-%:%570=358%:%
-%:%571=359%:%
-%:%572=360%:%
-%:%573=360%:%
-%:%574=361%:%
-%:%576=362%:%
-%:%577=363%:%
-%:%578=363%:%
-%:%579=364%:%
-%:%582=365%:%
-%:%586=365%:%
-%:%587=365%:%
-%:%588=365%:%
-%:%590=366%:%
-%:%591=367%:%
-%:%592=368%:%
-%:%602=370%:%
-%:%603=371%:%
-%:%604=372%:%
-%:%606=374%:%
-%:%607=374%:%
-%:%608=375%:%
-%:%610=376%:%
-%:%611=376%:%
-%:%612=377%:%
-%:%614=378%:%
-%:%615=378%:%
-%:%616=379%:%
-%:%618=380%:%
-%:%619=380%:%
-%:%620=381%:%
-%:%622=382%:%
-%:%623=382%:%
-%:%624=383%:%
-%:%626=384%:%
-%:%627=385%:%
-%:%628=385%:%
-%:%629=386%:%
-%:%636=387%:%
-%:%637=387%:%
-%:%638=388%:%
-%:%639=388%:%
-%:%640=389%:%
-%:%641=389%:%
-%:%642=389%:%
-%:%643=390%:%
-%:%644=390%:%
-%:%645=391%:%
-%:%646=391%:%
-%:%647=391%:%
-%:%648=392%:%
-%:%649=392%:%
-%:%650=393%:%
-%:%651=393%:%
-%:%652=393%:%
-%:%653=394%:%
-%:%663=396%:%
-%:%664=397%:%
-%:%665=398%:%
-%:%666=399%:%
-%:%667=400%:%
-%:%668=401%:%
-%:%669=402%:%
-%:%670=403%:%
-%:%671=404%:%
-%:%672=405%:%
-%:%673=406%:%
-%:%674=407%:%
-%:%675=408%:%
-%:%676=409%:%
-%:%677=410%:%
-%:%678=411%:%
-%:%679=412%:%
-%:%680=413%:%
-%:%681=414%:%
-%:%682=415%:%
-%:%683=416%:%
-%:%684=417%:%
-%:%685=418%:%
-%:%686=419%:%
-%:%687=420%:%
-%:%688=421%:%
-%:%692=424%:%
-%:%693=425%:%
-%:%694=426%:%
-%:%695=427%:%
-%:%696=428%:%
-%:%697=429%:%
-%:%698=430%:%
-%:%699=431%:%
-%:%700=432%:%
-%:%701=433%:%
-%:%702=434%:%
-%:%703=435%:%
-%:%704=436%:%
-%:%705=437%:%
-%:%706=438%:%
-%:%707=439%:%
-%:%708=440%:%
-%:%709=441%:%
-%:%710=442%:%
-%:%711=443%:%
-%:%712=444%:%
-%:%713=445%:%
-%:%714=446%:%
-%:%715=447%:%
-%:%716=448%:%
-%:%717=449%:%
-%:%718=450%:%
-%:%719=451%:%
-%:%720=452%:%
-%:%721=453%:%
-%:%722=454%:%
-%:%723=455%:%
-%:%724=456%:%
-%:%725=457%:%
-%:%726=458%:%
-%:%727=459%:%
-%:%728=460%:%
-%:%729=461%:%
-%:%730=462%:%
-%:%731=463%:%
-%:%732=464%:%
-%:%733=465%:%
-%:%734=466%:%
-%:%735=467%:%
-%:%736=468%:%
-%:%737=469%:%
-%:%738=470%:%
-%:%739=471%:%
-%:%740=472%:%
-%:%741=473%:%
-%:%742=474%:%
-%:%743=475%:%
-%:%744=476%:%
+%:%373=247%:%
+%:%374=248%:%
+%:%375=249%:%
+%:%376=250%:%
+%:%377=251%:%
+%:%378=252%:%
+%:%379=253%:%
+%:%380=254%:%
+%:%381=255%:%
+%:%382=256%:%
+%:%383=257%:%
+%:%384=258%:%
+%:%385=259%:%
+%:%386=260%:%
+%:%387=261%:%
+%:%388=262%:%
+%:%389=263%:%
+%:%390=264%:%
+%:%391=265%:%
+%:%392=266%:%
+%:%393=267%:%
+%:%394=268%:%
+%:%395=269%:%
+%:%396=270%:%
+%:%397=271%:%
+%:%398=272%:%
+%:%399=273%:%
+%:%400=274%:%
+%:%401=275%:%
+%:%402=276%:%
+%:%403=277%:%
+%:%404=278%:%
+%:%405=279%:%
+%:%406=280%:%
+%:%407=281%:%
+%:%408=282%:%
+%:%409=283%:%
+%:%410=284%:%
+%:%411=285%:%
+%:%412=286%:%
+%:%413=287%:%
+%:%414=288%:%
+%:%415=289%:%
+%:%416=290%:%
+%:%417=291%:%
+%:%418=292%:%
+%:%419=293%:%
+%:%420=294%:%
+%:%421=295%:%
+%:%422=296%:%
+%:%423=297%:%
+%:%424=298%:%
+%:%425=299%:%
+%:%434=302%:%
+%:%446=304%:%
+%:%447=305%:%
+%:%448=306%:%
+%:%449=307%:%
+%:%450=308%:%
+%:%451=309%:%
+%:%452=310%:%
+%:%453=311%:%
+%:%454=312%:%
+%:%455=313%:%
+%:%456=314%:%
+%:%457=315%:%
+%:%458=316%:%
+%:%459=317%:%
+%:%460=318%:%
+%:%461=319%:%
+%:%462=320%:%
+%:%463=321%:%
+%:%464=322%:%
+%:%465=323%:%
+%:%467=325%:%
+%:%468=325%:%
+%:%470=326%:%
+%:%471=326%:%
+%:%472=327%:%
+%:%473=327%:%
+%:%475=328%:%
+%:%476=329%:%
+%:%477=330%:%
+%:%478=330%:%
+%:%479=331%:%
+%:%480=331%:%
+%:%482=332%:%
+%:%483=332%:%
+%:%484=333%:%
+%:%485=333%:%
+%:%487=334%:%
+%:%488=334%:%
+%:%489=335%:%
+%:%490=335%:%
+%:%491=336%:%
+%:%493=337%:%
+%:%494=338%:%
+%:%495=339%:%
+%:%496=339%:%
+%:%497=340%:%
+%:%498=341%:%
+%:%499=341%:%
+%:%501=342%:%
+%:%502=342%:%
+%:%503=343%:%
+%:%504=343%:%
+%:%505=344%:%
+%:%507=345%:%
+%:%508=345%:%
+%:%509=346%:%
+%:%510=346%:%
+%:%512=347%:%
+%:%513=347%:%
+%:%514=348%:%
+%:%515=348%:%
+%:%516=349%:%
+%:%518=350%:%
+%:%519=351%:%
+%:%522=353%:%
+%:%523=354%:%
+%:%524=355%:%
+%:%526=357%:%
+%:%527=357%:%
+%:%528=358%:%
+%:%530=359%:%
+%:%531=359%:%
+%:%532=360%:%
+%:%534=361%:%
+%:%535=362%:%
+%:%536=363%:%
+%:%537=364%:%
+%:%538=364%:%
+%:%539=365%:%
+%:%541=366%:%
+%:%542=366%:%
+%:%543=367%:%
+%:%545=368%:%
+%:%546=369%:%
+%:%547=369%:%
+%:%548=370%:%
+%:%555=371%:%
+%:%556=371%:%
+%:%558=372%:%
+%:%559=373%:%
+%:%560=374%:%
+%:%561=375%:%
+%:%562=375%:%
+%:%563=376%:%
+%:%564=376%:%
+%:%565=377%:%
+%:%566=377%:%
+%:%567=377%:%
+%:%568=378%:%
+%:%569=378%:%
+%:%570=379%:%
+%:%571=379%:%
+%:%572=379%:%
+%:%573=380%:%
+%:%574=380%:%
+%:%575=381%:%
+%:%576=381%:%
+%:%577=381%:%
+%:%578=382%:%
+%:%588=384%:%
+%:%589=385%:%
+%:%590=386%:%
+%:%591=387%:%
+%:%592=388%:%
+%:%593=389%:%
+%:%594=390%:%
+%:%595=391%:%
+%:%596=392%:%
+%:%598=394%:%
+%:%599=394%:%
+%:%600=395%:%
+%:%601=396%:%
+%:%603=397%:%
+%:%604=397%:%
+%:%605=398%:%
+%:%607=399%:%
+%:%608=400%:%
+%:%609=400%:%
+%:%610=401%:%
+%:%612=402%:%
+%:%613=403%:%
+%:%614=404%:%
+%:%615=405%:%
+%:%616=406%:%
+%:%617=406%:%
+%:%618=407%:%
+%:%620=408%:%
+%:%621=409%:%
+%:%622=410%:%
+%:%623=411%:%
+%:%624=412%:%
+%:%625=413%:%
+%:%626=413%:%
+%:%627=414%:%
+%:%629=415%:%
+%:%630=416%:%
+%:%631=416%:%
+%:%632=417%:%
+%:%635=418%:%
+%:%639=418%:%
+%:%640=418%:%
+%:%641=418%:%
+%:%643=419%:%
+%:%644=420%:%
+%:%645=421%:%
+%:%655=423%:%
+%:%656=424%:%
+%:%657=425%:%
+%:%659=427%:%
+%:%660=427%:%
+%:%661=428%:%
+%:%663=429%:%
+%:%664=429%:%
+%:%665=430%:%
+%:%667=431%:%
+%:%668=431%:%
+%:%669=432%:%
+%:%671=433%:%
+%:%672=433%:%
+%:%673=434%:%
+%:%675=435%:%
+%:%676=435%:%
+%:%677=436%:%
+%:%679=437%:%
+%:%680=438%:%
+%:%681=438%:%
+%:%682=439%:%
+%:%689=440%:%
+%:%690=440%:%
+%:%691=441%:%
+%:%692=441%:%
+%:%693=442%:%
+%:%694=442%:%
+%:%695=442%:%
+%:%696=443%:%
+%:%697=443%:%
+%:%698=444%:%
+%:%699=444%:%
+%:%700=444%:%
+%:%701=445%:%
+%:%702=445%:%
+%:%703=446%:%
+%:%704=446%:%
+%:%705=446%:%
+%:%706=447%:%
+%:%716=449%:%
+%:%717=450%:%
+%:%718=451%:%
+%:%719=452%:%
+%:%720=453%:%
+%:%721=454%:%
+%:%722=455%:%
+%:%723=456%:%
+%:%724=457%:%
+%:%725=458%:%
+%:%726=459%:%
+%:%727=460%:%
+%:%728=461%:%
+%:%729=462%:%
+%:%730=463%:%
+%:%731=464%:%
+%:%732=465%:%
+%:%733=466%:%
+%:%734=467%:%
+%:%735=468%:%
+%:%736=469%:%
+%:%737=470%:%
+%:%738=471%:%
+%:%739=472%:%
+%:%740=473%:%
+%:%741=474%:%
 %:%745=477%:%
 %:%746=478%:%
-%:%755=480%:%
+%:%747=479%:%
+%:%748=480%:%
+%:%749=481%:%
+%:%750=482%:%
+%:%751=483%:%
+%:%752=484%:%
+%:%753=485%:%
+%:%754=486%:%
+%:%755=487%:%
+%:%756=488%:%
+%:%757=489%:%
+%:%758=490%:%
+%:%759=491%:%
+%:%760=492%:%
+%:%761=493%:%
+%:%762=494%:%
+%:%763=495%:%
+%:%764=496%:%
+%:%765=497%:%
+%:%766=498%:%
+%:%767=499%:%
+%:%768=500%:%
+%:%769=501%:%
+%:%770=502%:%
+%:%771=503%:%
+%:%772=504%:%
+%:%773=505%:%
+%:%774=506%:%
+%:%775=507%:%
+%:%776=508%:%
+%:%777=509%:%
+%:%778=510%:%
+%:%779=511%:%
+%:%780=512%:%
+%:%781=513%:%
+%:%782=514%:%
+%:%783=515%:%
+%:%784=516%:%
+%:%785=517%:%
+%:%786=518%:%
+%:%787=519%:%
+%:%788=520%:%
+%:%789=521%:%
+%:%790=522%:%
+%:%791=523%:%
+%:%792=524%:%
+%:%793=525%:%
+%:%794=526%:%
+%:%795=527%:%
+%:%796=528%:%
+%:%797=529%:%
+%:%798=530%:%
+%:%799=531%:%
+%:%808=533%:%

### 2021-12-03 paper/abstract.tex
abstract

@@
 
-\noindent \textbf{CAKE: Computational and Automated Kantian Ethics}
+\noindent \textbf{FAKE: Faithful Automated Kantian Ethics}
 
@@
 
-\noindent \textbf{Abstract}: As artifically intelligent agents become increasingly powerful, the need for philosophically
-sophisticated automated ethical reasoning becomes more pressing. Representing a robust ethical theory 
-to a computer poses technical and ethical challenges. I argue that, out of the three major ethical traditions, Kantian ethics is
-most natural to formalize because it presents inviolable, context-agnostic, formal rules. In this paper, 
-I present CAKE, an implementation of automated Kantian ethics that is faithful to the rich Kantian 
-philosophical tradition. I formalize Kant's categorical imperative in deontic logic, implement this 
-formalization in the Isabelle/HOL theorem prover, and develop a testing framework to evaluate how well 
-my implementation coheres with expected properties of Kantian ethics. Not only is CAKE an early step 
-towards philosophically rich ethical AI agents, it also establishes that computational tools can help 
-philosophers reach ethical insights.
+\noindent \textbf{Abstract}: Calls from regulators, philosophers, and computer scientists for the ethical
+use and development of artifical intelligence have spurred interest in automated ethics. Such machine 
+ethics will best cohere with intuitions and guide action when it is faithful to existing philosophical
+literature. Automating philosophically sophisticated ethical theories poses technical and philosophical
+challenges because it requires translating
+complex ethical theories expressed in natural language to the rigid syntax of a computer program. In 
+this paper, I present FAKE: an implementation of automated Kantian 
+ethics that is faithful to the Kantian philosophical tradition. Of the three major ethical 
+traditions, Kant's categorical imperative is most natural to formalize because it presents inviolable, 
+context-agnostic, formal rules.  I formalize Kant's categorical imperative 
+in Carmo and Jones's dyadic deontic logic, implement this formalization 
+in the Isabelle/HOL theorem prover, and develop a testing framework to evaluate how well 
+different formalizations cohere with expected properties of Kantian ethics, as established in the literature. 
+FAKE is not only an early step towards philosophically mature ethical AI agents, but it can also help
+philosophers reach new ethical insights, thus paving the way for computational ethics.
 

### 2021-12-03 paper/output/document/application.tex
will typos

@@
 particular situation, not just to an ethical theory as an abstract entity. In previous chapters' application tests,
-I performed some toy examples of applied ethical reasoning, but in this chapter, I expore how my system can 
-perform extended applied ethical reasoning. Metaethical reasoning is most interesting to philosophers 
+I performed some toy examples of applied ethical reasoning, but this chapter is an extended exploration of
+my system's ability to perform applied ethical reasoning. Metaethical reasoning is most interesting to philosophers 
 who are trying to formulate the ``best" theory of ethics. Applied ethical reasoning, on the other hand, 
@@
 The specific kind of common sense reasoning required appears to be a challenge 
-for automating Kantian ethics, and perhaps a reason that consequentialist or virtue ethical automated
-agents would be within closer reach for automation. Ultimately, Kantian ethics is still
+for automating Kantian ethics, and may imply that consequentialist or virtue ethical automated
+agents are within closer reach for automation. Ultimately, Kantian ethics is still
 easiest to automate because it will require fewer, less controversial common sense facts than other ethical
@@
 This chapter will provide additional examples of the kinds of common sense facts and maxim formulation required to get my system
-off the ground. I will aim to use as lean and uncontroversial of a common sense database as possible
+off the ground. I will aim to use a lean and uncontroversial common sense database
 to achieve robust and powerful results. This serves as evidence for the ease of automating
@@
 \isamarkupcmt{Using the above definitions, I can characterize a maxim as a lie if 
-    (a) the act requires knowingly uttering a falsehood 
+    (a) the act requires knowingly uttering a falsehood and,
     (b) the end requires that some person $p$ believe the false statement $t$.%
@@
 other parts of Kant's ethical theory generate the obligation to lie to the murderer. I chose
-to formalize the FUL because it is, in some sense, the strongest of the formulations of the categorical
+to formalize the FUL because it is, in some sense, the strongest of version of the categorical
 imperative. An even more sophisticated Kantian reasoner could formalize his theory of virtue and his
@@
 of the maxim be ``morally relevant." In the example above, my purple shirt and the date clearly have no bearing on 
-the moral status of lying. On the other hand, consider the maxim, ``When I am unmeployed, I will murder
-someone in order to take their job." The circumstances of being unmeployed clearly have some bearing on the moral
+the moral status of lying. On the other hand, consider the maxim, ``When I am unemployed, I will murder
+someone in order to take their job." The circumstances of being unemployed clearly have some bearing on the moral
 relevance of the murder in question; they speak to the motivation for the murder. While this view seems 
@@
 they act on. Circumstances are morally relevant if they accurately reflect the way that the agent is 
-thinking about their own action. In the example above, the circumstances of wearing a purple shirt don't reflect
-the principle of the liar's action. Their inclusion is clearly a disingenous attempt to evade the universalizability
+thinking about their own action. In the example above, the circumstance of wearing a purple shirt doesn't reflect
+the principle of the liar's action. Its inclusion is clearly a disingenous attempt to evade the universalizability
 test, but because the FUL is a test of personal integrity, it cannot withstand this kind of mental

### 2021-12-06 paper/abstract.tex
added why computational ethics

@@
 
-\noindent \textbf{Abstract}: Calls from regulators, philosophers, and computer scientists for the ethical
-use and development of artifical intelligence have spurred interest in automated ethics. Such machine 
+\noindent \textbf{Abstract}: Warnings from regulators, philosophers, and computer scientists about the 
+dangers of unethical artifical intelligence have spurred interest in automated ethics. Machine 
 ethics will best cohere with intuitions and guide action when it is faithful to existing philosophical
-literature. Automating philosophically sophisticated ethical theories poses technical and philosophical
-challenges because it requires translating
-complex ethical theories expressed in natural language to the rigid syntax of a computer program. In 
+literature. Translating complex ethical theories expressed in natural language to the rigid syntax 
+of a computer program poses technical and philosophical challenges. In 
 this paper, I present FAKE: an implementation of automated Kantian 
 ethics that is faithful to the Kantian philosophical tradition. Of the three major ethical 
-traditions, Kant's categorical imperative is most natural to formalize because it presents inviolable, 
+traditions, Kant's categorical imperative is the most natural to formalize because it presents inviolable, 
 context-agnostic, formal rules.  I formalize Kant's categorical imperative 
@@
 in the Isabelle/HOL theorem prover, and develop a testing framework to evaluate how well 
-different formalizations cohere with expected properties of Kantian ethics, as established in the literature. 
+my implementation coheres with expected properties of Kantian ethics, as established in the literature. 
 FAKE is not only an early step towards philosophically mature ethical AI agents, but it can also help

### 2021-12-06 paper/output/document/whycomputationalethics.tex
added why computational ethics

%
\begin{isabellebody}%
\setisabellecontext{whycomputationalethics}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Is Computational Ethics A Good Idea?%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
Even if computational tools can help philosophers with ethical inquiry, some may worry that they
somehow cheapen philosophy. After all, there seems to be something valuable about the process of ethical
reasoning and computational ethics threatens to destroy this value. In this section, I argue that, 
regardless of where we locate the value of ethics, computational ethics can enhance this value. The
value of human ethical reasoning is a reason to avoid totally automating the study of ethics, but 
human-computer symbiotic ethics preserves this value. Human-computer symbiosis is a model of computation
in which humans ``set the goals, formulate the hypotheses, determine the criteria, and perform the evaluations,”
and computers perform ``routinizable work that must be done to prepare the way for insights and decisions” \citep{licklider}.
There are two different kinds of ethics that
could benefit from computational tools: the kind that ordinary people use to decide how to live their 
lives and the kind studied by professional philosophers. In the first subsection, I consider the role of ethics 
in an ordinary person’s life and in the second subsection, I analyze the value that ethical study offers to 
the professional philosopher.

I will contrast human-symbiotic ethics with fully automated ethics, in which computers replace human
ethicists entirely and produce ethical theories and truths with no human input. This vision is far
from becoming a reality. Fully automated ethics may not even be possible, and I do not claim to implement 
anywhere near fully automated ethics in this project. I will use this as an extreme example to understand
the limitations of the arguments below. If a theory of the value of ethical study implies that 
fully automated ethics is good, then it will certainly imply that the kind of ethics I implement
in this project is good.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Ethics for Ordinary People%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
Ethics has immediate bearing on everyone’s lives because it studies the unavoidable question: 
how should we live? If computers can make this study more efficient, then it seems that everyone should
engage in computational ethics. As Cornel West says, the ethical question is the only question that 
we answer merely by living. To turn away from ethics is to take a stance on the question of how to 
live (namely, to live unreflectively) and thus to engage in ethics. Ethical truths are valuable because 
they tell us how to live. Every rational being must decide how to navigate the world and ethical 
truths answer these questions. If the results of ethical study is practically valuable, then automated 
ethics is good because computational tools can help us locate ethical prescriptions and theories more efficiently. 
In the most extreme case, we can unthinkingly follow the commands of an ethical calculator that dictates 
how we should live. Computers can answer the unavoidable question for us.

Placing the value of ethics olely in its action-guiding potential fails to take into account the 
importance of practical reason, which, as I argued in Section Why Kant, is the source
of freedom itself. 
We are committed to ethical reflection because of the kind of beings that we are. Recall that Korsgaard 
argues that, as beings occupying minds with a reflective structure, when faced with a choice, “it is as if there 
were something over and above all of your desires, something that is you, and that chooses which desire 
to act on” (Sources 83). This choosing is the operation of practical reason, and this reflection
makes us free. We are free because we must choose which reasons to act on. Every decision that we 
make is an exercise of freedom.

If reflecting makes us free, then unthinkingly obeying the computer sacrifices our autonomy. Consider 
the thought experiment of an Ethics Oracle that can unfailingly tell you the right thing to do in any 
situation.\footnote{This example is inspired by the Pocket Oracle presented in \citet{bok}.} Someone 
who surrenders themselves to this Oracle unthinkingly follows its prescriptions. 
There is some reflection involved in the decision to obey each of the Oracle’s prescriptions, but 
this is a thin kind of reflection \citep{bok}. This person is not reflecting on the real matters at hand and is 
not making decisions for themselves. They have surrendered their reflective capacity to the Oracle. 
They live a worse life than someone who reflects on their actions. They have less ownership over their 
actions than the reflective person. In a less extreme case, a person may retain control of many of 
their decisions but cede some important or tricky choices to the Ethics Oracle. Because every single 
exercise of practical reason is an exercise of autonomy, this person is still less autonomous than the 
purely reflective person. Even surrendering simple, inconsequential decisions such as which flavor of 
coffee to drink surrenders some piece of our autonomy. Perhaps in trivial cases we can accept that 
tiny sacrifice in autonomy, but giving over life-changing decisions to the machine sacrifices our 
core freedom. Unreflectively relying on computational ethics surrenders our autonomy to the machine.

One objection to this emphasis on reflection is the impracticality of making ethical calculations from first principles 
every time we are faced with a decision. This is why we follow the advice of moral mentors, like our 
family or influential philosophers. These moral mentors differ from the Ethics Oracle because their advice 
comes with an argument justifying it; if human-computer symbiotic computational ethics also prompts 
reflection on the prescriptions given, it can also guide action without sacrificing autonomyy.
Most people do not reason about ethics during everyday decisions; they rely on some combination of 
prior knowledge and external testimony. For example, my mother taught me to respect myself, and I 
follow her advice. What is the difference between following the guidance of a moral educator and 
obeying the Ethics Oracle? The best kind of ethical advice prompts reflection, such as an argument 
made in a philosophy paper. Unthinkingly following someone’s advice results in the same loss of 
autonomy as unthinkingly obeying the Ethics Oracle; people who merely obey orders are less autonomous 
than those who think for themselves. This account of moral advice offers a model for human-computer 
symbiotic ethics. The computer should serve as a moral guide by providing arguments on what the right 
thing to do is, just as my mom explained why I should always respect myself. Human-computer symbiotic 
ethics nurtures autonomy when it not only offers prescriptions for action, but also explanations for 
these prescriptions. Because my theorem-prover-based computational ethical system is explainable, it can 
guide action without sacrificig autonomy because it can make an argument for some action, instead of 
only giving a verdict as many machine learning algorithms do. Isabelle can list the facts used to show
a partcular action prohibited, and a human being can reflect on whether or not these principles
indeed prohibit the action in question. The computer serves as a collaborator and a tool, but not as an authority, 
so the human being’s reflective capacity and freedom is preserved.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Academic Ethics%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
Academic philosophers publish papers, mostly read by other professional philosophers or by philosophy students. 
There are two potential sources of the value of academic philosophy: the ethical truths uncovered and 
the process of a philosopher discovering these truths. Under the first view, academic philosophy is 
valuable because it facilitates the discovery of new ethical theories. If truths are valuable and 
computers can generate truths more efficiently than humans, then ethics should be fully automated. 
Ethical disputes often linger unresolved indefinitely, but every now and then, 
a theory emerges as a new classic, such as Rawls’ veil of ignorance. Some academic philosophy also 
impacts social phenomena, like Locke’s impact on global democracy. Academic philosophy often works its 
way into household ethics, as seen in the impact of critical race theory. This view parallels the 
view that ordinary ethics is valuable for its insights alone, and thus
similarly implies that totally automated ethics is not only permissible, but also desirable. If 
ethical truths are important for their impact on society, this value is not contingent on whether a 
human or a computer produced these truths. If possible, computers should produce ethical theories 
to maximize these truths’ value for society.

Another set of theories locates the value of academic ethics in the process itself and thus requires 
human-computer symbiosis. Just as mathematics is fun and creative for the mathematician, so is ethics 
for the philosopher. Many philosophers enjoy reading and writing philosophy papers. The study of 
philosophy builds critical thinking skills and makes philosophers more reflective. Computational ethics 
doesn’t necessarily sacrifice any of these benefits. These 
benefits would be lost by fully automated ethics, but human-computer symbiotic ethics amplifies them. 
If a computer functions like a tool in the process of philosophical discovery, like a conversation 
with a colleague or a search for counterexamples, then it preserves the joy of philosophy. Moreover, 
computational ethics amplifies this joy by forcing ethicists to make their ideas more precise, a major 
goal of academic philosophy. The rigid syntax of a computer program demands much more precision than a 
conversation or a paper. Computational tools also offer ethicists new perspective by forcing a return to 
first, formal principles often avoided in ordinary philosophical inquiry. Formal ethics has been a 
subject of interest among ethicists, but the logical background necessary has prevented the field 
from taking off. If computers can automate away the tedium of formal ethics, then this precision 
will be accessible to all ethicists, not just logicians. Such work has begun in metaphysics, and 
recent research used computational tools to find an inconsistency in Godel’s ontological argument 
for the existence of God \citep{godelincon}. The power of computational tools to force precision, perform 
consistency checks, and make assumptions explicit means that computers can serve as tools to 
help philosophers perform philosophy better.

If ethical truths also offer some value to society at-large, it seems ridiculous to sacrifice this 
value merely to preserve human philosophers’ fun. A more compelling argument against fully automated 
ethics is that the existence of human academic philosophers offers value even to non-philosophers. 
People derive joy and wonder from knowing that human beings produced great ethics. Plato’s Apology 
is not only a profound and insightful text, but it is also wonderous that a human being produced such 
a work. We derive joy from knowing that our fellow humans are capable of the kind of thought that 
great philosophers accomplished, just as an unimaginably beautiful work of art is more wonderous 
because a human being painted it. We watch the Olympics because we derive wonder and joy from human 
excellence. Even when admiring computational achievements, such as Google’s recent success in protein 
folding, we admire the human who programmed the machine, not the machine itself. We can relate to 
humans, so the mere knowledge that great people are doing great things enriches our lives. This 
knowledge is part of the attraction for the thousands of tourists who visit Harvard Yard every year; 
this is a place where of great human achievement\footnote{Is this too like, arrogant?}.

An even stronger argument for human-computer symbiotic ethics instead of fully automated ethics is 
that ethics is certainly an inherently human subject. We study ethics because, as argued above, we 
have no choice but to reflect on how to live. Because reflection is such a fundamental part of being 
human, a world in which all ethical inquiry is automated is undesirable. Academic philosophers are 
professional reflectors who are partners in the human experience with us, so their ethical inquiry 
carries unique weight. They teach us, inspire us, and serve as examples of the kind of reflection 
that is constitutive of being human. Moreover, an ethical theory produced entirely by a computer is, 
at best, a secondary perspective; it is a computer’s attempt to describe how human beings should live. 
Without a human component, it cannot serve as a rich and sophisticated guide for humans. If ethics is 
most meaningful when it is the product of human reflection, totally automated ethics destroys the field 
entirely but human-computer symbiosis does not. Human beings should debate the most pressing questions 
of human existence, and computers can serve as our aids. Thus, computational tools must supplement 
human ethical reasoning but cannot replace it.

To present-day philosophers, computational ethics may sound outlandish. After all, no machine could 
or should replace humans studying the inherently human subject of ethics. Even though computational
tools may seem inaccessible to philosophers, they can make their work more efficient and interesting, 
just as online text-editors made philosophical communication clearer. The human-computer symbiotic model
understands computers as one tool in the philosopher's toolkit, like a thought experiment or counterargument.
Fully automated ethics certainly threatens something valuable about the field of philosophy, but
this model of computational ethics merely gives philosophers the ability to say, ``this argument was
verified by a computer."%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/whycomputationalethics.thy%:%
%:%24=6%:%
%:%36=8%:%
%:%37=9%:%
%:%38=10%:%
%:%39=11%:%
%:%40=12%:%
%:%41=13%:%
%:%42=14%:%
%:%43=15%:%
%:%44=16%:%
%:%45=17%:%
%:%46=18%:%
%:%47=19%:%
%:%48=20%:%
%:%49=21%:%
%:%50=22%:%
%:%51=23%:%
%:%52=24%:%
%:%53=25%:%
%:%54=26%:%
%:%55=27%:%
%:%56=28%:%
%:%65=31%:%
%:%77=33%:%
%:%78=34%:%
%:%79=35%:%
%:%80=36%:%
%:%81=37%:%
%:%82=38%:%
%:%83=39%:%
%:%84=40%:%
%:%85=41%:%
%:%86=42%:%
%:%87=43%:%
%:%88=44%:%
%:%89=45%:%
%:%90=46%:%
%:%91=47%:%
%:%92=48%:%
%:%93=49%:%
%:%94=50%:%
%:%95=51%:%
%:%96=52%:%
%:%97=53%:%
%:%98=54%:%
%:%99=55%:%
%:%100=56%:%
%:%101=57%:%
%:%102=58%:%
%:%103=59%:%
%:%104=60%:%
%:%105=61%:%
%:%106=62%:%
%:%107=63%:%
%:%108=64%:%
%:%109=65%:%
%:%110=66%:%
%:%111=67%:%
%:%112=68%:%
%:%113=69%:%
%:%114=70%:%
%:%115=71%:%
%:%116=72%:%
%:%117=73%:%
%:%118=74%:%
%:%119=75%:%
%:%120=76%:%
%:%121=77%:%
%:%122=78%:%
%:%123=79%:%
%:%124=80%:%
%:%125=81%:%
%:%126=82%:%
%:%127=83%:%
%:%128=84%:%
%:%129=85%:%
%:%130=86%:%
%:%131=87%:%
%:%132=88%:%
%:%133=89%:%
%:%134=90%:%
%:%143=93%:%
%:%155=96%:%
%:%156=97%:%
%:%157=98%:%
%:%158=99%:%
%:%159=100%:%
%:%160=101%:%
%:%161=102%:%
%:%162=103%:%
%:%163=104%:%
%:%164=105%:%
%:%165=106%:%
%:%166=107%:%
%:%167=108%:%
%:%168=109%:%
%:%169=110%:%
%:%170=111%:%
%:%171=112%:%
%:%172=113%:%
%:%173=114%:%
%:%174=115%:%
%:%175=116%:%
%:%176=117%:%
%:%177=118%:%
%:%178=119%:%
%:%179=120%:%
%:%180=121%:%
%:%181=122%:%
%:%182=123%:%
%:%183=124%:%
%:%184=125%:%
%:%185=126%:%
%:%186=127%:%
%:%187=128%:%
%:%188=129%:%
%:%189=130%:%
%:%190=131%:%
%:%191=132%:%
%:%192=133%:%
%:%193=134%:%
%:%194=135%:%
%:%195=136%:%
%:%196=137%:%
%:%197=138%:%
%:%198=139%:%
%:%199=140%:%
%:%200=141%:%
%:%201=142%:%
%:%202=143%:%
%:%203=144%:%
%:%204=145%:%
%:%205=146%:%
%:%206=147%:%
%:%207=148%:%
%:%208=149%:%
%:%209=150%:%
%:%210=151%:%
%:%211=152%:%
%:%212=153%:%
%:%213=154%:%
%:%214=155%:%
%:%215=156%:%
%:%216=157%:%
%:%217=158%:%
%:%218=159%:%
%:%219=160%:%
%:%220=161%:%
%:%221=162%:%
%:%222=163%:%
%:%223=164%:%
%:%224=165%:%
%:%225=166%:%

### 2021-12-06 paper/output/document/whycomputationalethics.tex
small typos

@@
 Even if computational tools can help philosophers with ethical inquiry, some may worry that they
-somehow cheapen philosophy. After all, there seems to be something valuable about the process of ethical
-reasoning and computational ethics threatens to destroy this value. In this section, I argue that, 
-regardless of where we locate the value of ethics, computational ethics can enhance this value. The
-value of human ethical reasoning is a reason to avoid totally automating the study of ethics, but 
-human-computer symbiotic ethics preserves this value. Human-computer symbiosis is a model of computation
+somehow cheapen philosophy. If there is something valuable about the process of ethical
+reasoning, then computational ethics threatens to destroy this value. In this section, I argue that, 
+regardless of where we locate the value of ethics, computational ethics can enhance its value. Because
+there is some value in human ethical reasoning, we should not completely automate the study of ethics, but 
+human-computer symbiotic ethics can preserve and enhance this value. Human-computer symbiosis is a model of computation
 in which humans ``set the goals, formulate the hypotheses, determine the criteria, and perform the evaluations,”
@@
 
-Placing the value of ethics olely in its action-guiding potential fails to take into account the 
+Placing the value of ethics solely in its action-guiding potential fails to take into account the 
 importance of practical reason, which, as I argued in Section Why Kant, is the source
@@
 not making decisions for themselves. They have surrendered their reflective capacity to the Oracle. 
-They live a worse life than someone who reflects on their actions. They have less ownership over their 
+They live a worse life than someone who reflects on their actions; they have less ownership over their 
 actions than the reflective person. In a less extreme case, a person may retain control of many of 
@@
 comes with an argument justifying it; if human-computer symbiotic computational ethics also prompts 
-reflection on the prescriptions given, it can also guide action without sacrificing autonomyy.
+reflection on the prescriptions given, it can also guide action without sacrificing autonomy.
 Most people do not reason about ethics during everyday decisions; they rely on some combination of 
@@
 autonomy as unthinkingly obeying the Ethics Oracle; people who merely obey orders are less autonomous 
-than those who think for themselves. This account of moral advice offers a model for human-computer 
-symbiotic ethics. The computer should serve as a moral guide by providing arguments on what the right 
-thing to do is, just as my mom explained why I should always respect myself. Human-computer symbiotic 
+than those who think for themselves.\footnote{This might be worrying....does this mean that soldiers who are
+following orders to commit atrocities are less responsible than those giving the orders? Wait 
+maybe that's true.} This account of moral advice offers a model for human-computer 
+symbiotic ethics. The computer should serve as a moral guide by providing arguments, just as my mom 
+explained why I should always respect myself. Human-computer symbiotic 
 ethics nurtures autonomy when it not only offers prescriptions for action, but also explanations for 
 these prescriptions. Because my theorem-prover-based computational ethical system is explainable, it can 
-guide action without sacrificig autonomy because it can make an argument for some action, instead of 
-only giving a verdict as many machine learning algorithms do. Isabelle can list the facts used to show
+guide action without sacrificing autonomy. It can make an argument for some action, instead of 
+merely giving a verdict. Isabelle can list the facts used to show
 a partcular action prohibited, and a human being can reflect on whether or not these principles
@@
 \begin{isamarkuptext}%
-Academic philosophers publish papers, mostly read by other professional philosophers or by philosophy students. 
 There are two potential sources of the value of academic philosophy: the ethical truths uncovered and 
@@
 
-If ethical truths also offer some value to society at-large, it seems ridiculous to sacrifice this 
-value merely to preserve human philosophers’ fun. A more compelling argument against fully automated 
+If ethical truths offer some value to society at-large, perhaps we cannot sacrifice this value merely 
+to preserve human philosophers’ fun. A more compelling argument against fully automated 
 ethics is that the existence of human academic philosophers offers value even to non-philosophers. 
-People derive joy and wonder from knowing that human beings produced great ethics. Plato’s Apology 
+People derive joy and wonder from knowing that human beings produced great ethics. Plato’s \emph{Apology} 
 is not only a profound and insightful text, but it is also wonderous that a human being produced such 
 a work. We derive joy from knowing that our fellow humans are capable of the kind of thought that 
-great philosophers accomplished, just as an unimaginably beautiful work of art is more wonderous 
+great philosophers accomplish, just as an unimaginably beautiful work of art is more wonderous 
 because a human being painted it. We watch the Olympics because we derive wonder and joy from human 
@@
 knowledge is part of the attraction for the thousands of tourists who visit Harvard Yard every year; 
-this is a place where of great human achievement\footnote{Is this too like, arrogant?}.
+this is a place where of great human achievement.\footnote{Is this too like, yay Harvard}
 
 An even stronger argument for human-computer symbiotic ethics instead of fully automated ethics is 
-that ethics is certainly an inherently human subject. We study ethics because, as argued above, we 
+that ethics is an inherently human subject. We study ethics because, as argued above, we 
 have no choice but to reflect on how to live. Because reflection is such a fundamental part of being 
@@
 of human existence, and computers can serve as our aids. Thus, computational tools must supplement 
-human ethical reasoning but cannot replace it.
-
-To present-day philosophers, computational ethics may sound outlandish. After all, no machine could 
-or should replace humans studying the inherently human subject of ethics. Even though computational
-tools may seem inaccessible to philosophers, they can make their work more efficient and interesting, 
-just as online text-editors made philosophical communication clearer. The human-computer symbiotic model
-understands computers as one tool in the philosopher's toolkit, like a thought experiment or counterargument.
-Fully automated ethics certainly threatens something valuable about the field of philosophy, but
-this model of computational ethics merely gives philosophers the ability to say, ``this argument was
-verified by a computer."%
+human ethical reasoning but cannot replace it.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %:%134=90%:%
-%:%143=93%:%
-%:%155=96%:%
-%:%156=97%:%
+%:%135=91%:%
+%:%136=92%:%
+%:%145=95%:%
 %:%157=98%:%
@@
 %:%217=158%:%
-%:%218=159%:%
-%:%219=160%:%
-%:%220=161%:%
-%:%221=162%:%
-%:%222=163%:%
-%:%223=164%:%
-%:%224=165%:%
-%:%225=166%:%

### 2021-12-13 paper/abstract.tex
paper outline

@@
 
-\noindent \textbf{FAKE: Faithful Automated Kantian Ethics}
+\noindent \textbf{A Faithful Implementation of Automated Kantian Ethics}
 
@@
 \noindent \textbf{Abstract}: Warnings from regulators, philosophers, and computer scientists about the 
-dangers of unethical artifical intelligence have spurred interest in automated ethics. Machine 
-ethics will best cohere with intuitions and guide action when it is faithful to existing philosophical
-literature. Translating complex ethical theories expressed in natural language to the rigid syntax 
-of a computer program poses technical and philosophical challenges. In 
-this paper, I present FAKE: an implementation of automated Kantian 
+dangers of unethical artificial intelligence have spurred interest in the development 
+of machines that can perform ethical reasoning. Despite the fact that ethical philosophers are devoted to 
+developing robust ethical theories, previous work in automated ethics rarely engages with existing 
+philosophical literature. Faithfully translating complex, philosophically sophisticated ethical theories 
+expressed in natural language to the rigid syntax of a computer program poses technical and philosophical 
+challenges. In this paper, I present an implementation of automated Kantian 
 ethics that is faithful to the Kantian philosophical tradition. Of the three major ethical 
-traditions, Kant's categorical imperative is the most natural to formalize because it presents inviolable, 
-context-agnostic, formal rules.  I formalize Kant's categorical imperative 
+traditions, Kant's categorical imperative is the most natural to formalize because it is an inviolable, 
+context-agnostic, formal rule.  I formalize Kant's categorical imperative 
 in Carmo and Jones's dyadic deontic logic, implement this formalization 
@@
 my implementation coheres with expected properties of Kantian ethics, as established in the literature. 
-FAKE is not only an early step towards philosophically mature ethical AI agents, but it can also help
-philosophers reach new ethical insights, thus paving the way for computational ethics.
+My system is not only an early step towards philosophically mature ethical AI agents, but it can also help
+philosophers reach new ethical insights, thus paving the way for the use of computational tools to 
+address philosophical problems.
 
 \smallskip
-\noindent \emph{Areas: algorithm development, applications, philosophy}
+\noindent \emph{Areas: algorithm development, applications, philosophy, ethics and automation}
 \end{document}

### 2021-12-13 paper/paper_outline.tex
paper outline

\documentclass[11pt]{article}
\usepackage{outlines}
\usepackage{xcolor}
\usepackage{times}
\usepackage[margin=1in]{geometry}

\normalfont

\begin{document}
\begin{outline}[enumerate]
\1[Introduction (1p)] 
\2 Problem
\2 Contributions:

\3 I present an implementation of automated Kantian ethics by formalizing the categorical
imperative in deontic logic and implementing this formalization in Isabelle. My system
improves on prior work by formalizing a sophisticated interpretation of the Formula of Universal Law 
and representing the idea of a maxim. This implementation contributes axioms and definitions such that 
a maxim, appropriately represented,
can be shown to be permissible, prohibited, or obligatory, along with a list of facts used
to complete the proof and, in some cases, an Isar-style readable proof.

\3 I present a testing architecture to evaluate different implementations of the categorical imperative
based on ethical intuitions and properties of Kantian ethics established in the literature. Based on 
my testing architecture, my implementation outperforms prior attempts at formalizing Kantian ethics.
The tests include meta-ethical tests (which test the abstract properties of the ethical theory)
and application tests (which test the judgements that my system would make in real-world dilemmas).

\3 Should I include any of the philosophical contributions? Specifically, the writing on why Kantian 
ethics is the most natural to formalize is a philosophical contribution but not a technical one.

\1[The Problem (1p)] 
\2 In order for AI agents to navigate the world responsibly, they need to perform ethical reasoning.
\2 This ethical reasoning should draw on existing work in philosophy and should be explainable.
\2 Maybe put something about computational ethics here?
\1[My Idea (2p)]
\2 Overview of the Top-Down, Theorem Prover approach
\2 Testing Framework (introduce the idea, metaethical tests, application tests)
\2 How it would fit into (a) an AI agent (b) philosophers' workflow
\1[The Details (5p)] 
\2 Why Kantian Ethics (1-1.5p)
\2 Isabelle/HOL implementation (basic logical background and structure)
\2 Features: robust definition of a maxim, ability to distinguish between lies and jokes, reusability of 
testing framework (maybe include the table showing which tests my implementation passes vs prior implementations?)
\2 Philosophical insights discovered along the way (vacuous maxims example)
\2 Limitations (needs an input parser and a common sense database)
\1[Related Work (1-2p)] 
\2 Talk about bottom-up vs top-down approaches 
\2 I improve prior work by (1) staying faithful to philosophical literature (2) building an explainable
system
\1[Conclusion (0.5p)]

\end{outline}
\end{document}

### 2022-01-22 paper/output/document/AMA_possible.tex
ama possible writing and diagram

%
\begin{isabellebody}%
\setisabellecontext{AMA{\isacharunderscore}possible}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Is Automated Kantian Ethics Possible?%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
Philosophers often seem averse to the idea that a computer could perform anything close to ethical 
reasoning. For example, Rawls asserts, ``It is a serious misconception to think of the CI-procedure 
as an algorithm intended to yield, more or less mechanically, a correct judgment. There is no such 
algorithm, and Kant knows this" \citep[166]{rawlslectures}. Ebels-Duggan also claims that, ``No one supposes that the Categorical
Imperative provides a mechanical algorithm that delivers all by itself a complete account of what we 
ought to do in any given situation" \citep[174]{ebelsduggan}. However unmechanical ethical reasoning
may seem, these claims are not obvious and require further justification. After all, computers may eventually 
learn to simulate human mental activity exactly, as shown by progress in brain simulation \citep{brainsimulation}. 
Philosophers who believe that mental activity determines moral reasoning\footnote{what's the name for these
guys? do they have a name?}, must explain why computers can, in theory, simulate mental processes like arithmetic 
and language, but cannot perform ethical reasoning. Without a soul or God-based account of ethical reasoning, 
it is not obvious that it is theoretically impossible to automate ethical reasoning.

In \emph{Universal Laws and Ends In Themselves}, O'Neill argues against the existence of an algorithm for
moral behavior. She points out that Kant draws an important distinction between a morally worthy maxim 
and a morally worthy action: the latter requires a good will, motivated by duty. She argues that, 
``Kant defines duty not (as would be common today) as outward performance of a certain sort, but as action
that embodies a good will" \citep[345]{oneilluniversallaws}. Under this understanding of moral behavior, 
it seems unlikely that a computer could, in the near future, behave ``morally," since a computer does 
not have the same kinds of motivations and ``will" as a human being. If a computer is not a fully rational
being, it cannot behave morally.

Even if, under Kant's account, a computer cannot behave morally, this still does not preclude the kind 
of automated categorical imperative test that I present in this thesis. O'Neill argues that the FUL
serves as a test of morally worthy maxims, and an automated categorical imperative test can be used 
to identify this kind of maxim. Perhaps a computer cannot act on this maxim from a motivation of duty, 
but it certainly can act on this maxim. For example, a self-driving car can choose to swerve to hit a tree
to avoid injuring pedestrians in the crosswalk and this action may be one that acts on a morally worthy maxim
\emph{even if} the self-driving car is not motivated by duty. The discpline of machine ethics is partially
spurred by the recognition that, as automated agents become more powerful, they will need to make
morally tinged decisions. Such agents may be incapable of moral behavior, but automated agents that mimic
moral behavior are surely better than such agents that ignore morality entirely. Moreover, this argument
has no bearing on the possibility of computational ethics, as evaluating the moral status of a maxim can 
help philosophers study maxims and Kantian ethics even if the computer performing the evaluation is incapable of 
moral behavior.

Another challenge for automated Kantian ethics identified by O'Neill is that the FUL test requires
a maxim given as input. O'Neill notes that the test assumes ``that agents will have certain tentative 
plans, proposals and policies which they can consider, revise or reject or endorse and pursue" \citep[343]{oneilluniversallaws}.
Kant even argues that the difficulty of determining an agent's potential maxim, which is their
own, subjective understanding of their principle of action, may be a reason that we may never be able 
to know if morally worthy action has been performed \cite[345]{oneilluniversallaw}.

The challenge of mapping actions to maxims is a limitation of my system, but is not insurmountable. In Section Upshot,
I argue that before my system can be used in practice, it must be paired with an ``input parser," that can
translate dilemmas or choices that an automated agent faces into maxims in a logic that my system can
evaluate. This limitation directly follows from the difficulty in mapping an action or potential action
to the maxim of action, whether concerning human action or machine action. As argued in Section Upshot,  
this is not an insurmountable obstacle for automated ethics. Future work could develop heuristics to 
map actions to maxims, perhaps by extracting the circumstances, act, and goal. Moreover, proponents of the 
human-in-the-loop model may argue that the solution to this problem is to have a human being manually create
such mappings, either dynamically or in a cached manner. Given that determining the maxim of action is a challenge
for human Kantian ethical reasoners, it is unsurprising that it is a major hurdle for automated Kantian agents. 
That being said, computational ethics remains unaffects by this concern because philosophers often debate 
the morality of specific maxims or metaethical properties of the categorical imperative, all of which can
be studied without an algorithm for parsing moral dilemmas into the relevant maxims.

As one of the strongest arguments against any categorical imperative algorithm, O'Neill argues that 
the FUL is not supposed to provide a mechanism for deriving all morally worthy maxims from scratch. She notes
that ``we usually already have learnt or worked out the moral standing of many common maxims of duty," 
and so approach moral deliberation with an ``almanac" of morally worthy and empty maxims. Rational agents
navigating the world rarely recalculate the moral status of each potential maxim of action; instead, we consult our
almanac of maxims. The categorical imperative is useful to double-check our work and verify the rightness or 
wrongness of a maxim, but is not an actual part of the bulk of human ethical reasoning.

While human beings cannot repeatedly apply the universalizability test to all potential maxims in 
every moral dilemma, there is no reason that computers cannot do the same. While human beings are 
equipped with enough prior knowledge or ``common sense" to have an almanac of morally worthy maxims,
they are limited in their computational power. Computers, on the other hand, are comparatively
much more capable of computation and thus can actually repeatedly recompute the results of the categorical
imperative test. They do not come equipped with an almanac of maxims, but can simply recompute this
almanac every time they need to make a decision. Human beings use common sense to make up for their computational
limitations, and automated moral agents can use computational power to elide common sense entirely.

Daniela Tafani takes this argument one step further by arguing that the categorical imperative is not meant
to derive the content of moral obligation from scratch. Instead, she argues that human beings already
know which maxims are morally worthy and which are morally lacking. The categorical imperative test
merely reminds us, in moments of weakness, when we are tempted to make an exception to the moral law for 
our own convenience or pleasure, that the moral law has no exceptions \citep[9]{tafani}. Thus, she claims
that ``The Kantian test is therefore as useless for machines as it is for anyone who does
not already know what to do" \citep[8]{tafani}. Understanding the categorical imperative test as a reminder
instead of a derivation tool also explains a fact noted by O'Neill that I discuss in Section ?? as a 
response to the tailoring objection: the FUL test cannot handle bad-faith attempts to generate false
positives or negatives. The test only returns the right result when an agent sincerely attempts to 
represent their maxim of action, not when an adversary attempts to ``trick" the categorical imperative.

This understanding of the role of the categorical imperative not only fails to render automate moral
reasoning impossible, but it also offers insight into how to solve the challenge of creating an input parser.
If the categorical imperative test is only useful to those who have some prior moral knowledge, then prior moral
knowledge should be used to create an input parser. Specifically, some kind of machine learning-based approach
could perform action-maxim mappings based on a database of such mappings compiled by a human being. Moreover, 
the human being could assign each maxim in the database a rightness or wrongness score. My implementation
of the automated categorical imperative would then simply check the work of this machine learning algorithm and transform
a fuzzy prediction into a provable, rigorous moral judgement. Moreover, this rigorous moral judgement
could in turn be fed into the database of maxims to make the intput parser smarter. One example of 
this kind of system is shown in Figure \ref{fig:inputparser}. The combination of 
prior knowledge of some maxims' moral worth and the ability of a computer to constantly perform the
universalizability test could make such a system not only match human ethical reasoning but surpass it
by double checking the moral intuitions that we take for granted. A computer with no common sense or prior knowledge
may indeed be unable to reason using the categorical imperative, but one equipped with some prior knowledge
of maxims and their moral worth may even help us better reason about morality.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{figure}
\centering
\includegraphics[scale=0.5]{inputparser.png}
\caption{ugh i have to write a caption} \label{fig:inputparser}
\end{figure}
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/AMA_possible.thy%:%
%:%24=6%:%
%:%36=8%:%
%:%37=9%:%
%:%38=10%:%
%:%39=11%:%
%:%40=12%:%
%:%41=13%:%
%:%42=14%:%
%:%43=15%:%
%:%44=16%:%
%:%45=17%:%
%:%46=18%:%
%:%47=19%:%
%:%48=20%:%
%:%49=21%:%
%:%50=22%:%
%:%51=23%:%
%:%52=24%:%
%:%53=25%:%
%:%54=26%:%
%:%55=27%:%
%:%56=28%:%
%:%57=29%:%
%:%58=30%:%
%:%59=31%:%
%:%60=32%:%
%:%61=33%:%
%:%62=34%:%
%:%63=35%:%
%:%64=36%:%
%:%65=37%:%
%:%66=38%:%
%:%67=39%:%
%:%68=40%:%
%:%69=41%:%
%:%70=42%:%
%:%71=43%:%
%:%72=44%:%
%:%73=45%:%
%:%74=46%:%
%:%75=47%:%
%:%76=48%:%
%:%77=49%:%
%:%78=50%:%
%:%79=51%:%
%:%80=52%:%
%:%81=53%:%
%:%82=54%:%
%:%83=55%:%
%:%84=56%:%
%:%85=57%:%
%:%86=58%:%
%:%87=59%:%
%:%88=60%:%
%:%89=61%:%
%:%90=62%:%
%:%91=63%:%
%:%92=64%:%
%:%93=65%:%
%:%94=66%:%
%:%95=67%:%
%:%96=68%:%
%:%97=69%:%
%:%98=70%:%
%:%99=71%:%
%:%100=72%:%
%:%101=73%:%
%:%102=74%:%
%:%103=75%:%
%:%104=76%:%
%:%105=77%:%
%:%106=78%:%
%:%107=79%:%
%:%108=80%:%
%:%109=81%:%
%:%110=82%:%
%:%111=83%:%
%:%112=84%:%
%:%113=85%:%
%:%114=86%:%
%:%115=87%:%
%:%116=88%:%
%:%117=89%:%
%:%118=90%:%
%:%119=91%:%
%:%120=92%:%
%:%121=93%:%
%:%122=94%:%
%:%123=95%:%
%:%124=96%:%
%:%125=97%:%
%:%126=98%:%
%:%127=99%:%
%:%128=100%:%
%:%129=101%:%
%:%130=102%:%
%:%131=103%:%
%:%132=104%:%
%:%133=105%:%
%:%134=106%:%
%:%135=107%:%
%:%136=108%:%
%:%139=112%:%
%:%140=113%:%
%:%141=114%:%
%:%142=115%:%
%:%143=116%:%

### 2022-01-22 paper/output/document/paper41.tex
ama possible writing and diagram

@@
 of M hold), then M is not effective." 
-
 Notice that the antecedent specifies that the circumstances hold at the given world. 
@@
 \isacommand{abbreviation}\isamarkupfalse%
-\ FUL\ \isakeyword{where}\ {\isachardoublequoteopen}FUL\ {\isasymequiv}\ {\isasymforall}M{\isacharcolon}{\isacharcolon}maxim{\isachardot}\ {\isasymforall}s{\isacharcolon}{\isacharcolon}s{\isachardot}\ {\isacharparenleft}{\isasymforall}w{\isachardot}\ well{\isacharunderscore}formed\ M\ s\ w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}not{\isacharunderscore}universalizable\ M\ s\ {\isasymlongrightarrow}\ {\isasymTurnstile}\ {\isacharparenleft}prohibited\ M\ s{\isacharparenright}\ {\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ FUL\ \isakeyword{where}\ \isanewline
+{\isachardoublequoteopen}FUL\ {\isasymequiv}\ {\isasymforall}M{\isacharcolon}{\isacharcolon}maxim{\isachardot}\ {\isasymforall}s{\isacharcolon}{\isacharcolon}s{\isachardot}\ {\isacharparenleft}{\isasymforall}w{\isachardot}\ well{\isacharunderscore}formed\ M\ s\ w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}not{\isacharunderscore}universalizable\ M\ s\ {\isasymlongrightarrow}\ {\isasymTurnstile}\ {\isacharparenleft}prohibited\ M\ s{\isacharparenright}\ {\isacharparenright}{\isachardoublequoteclose}\isanewline
 %
@@
 %:%283=225%:%
-%:%284=226%:%
+%:%286=227%:%
 %:%287=228%:%
@@
 %:%293=234%:%
-%:%294=235%:%
-%:%296=237%:%
+%:%295=236%:%
+%:%296=236%:%
 %:%297=237%:%
@@
 %:%299=239%:%
-%:%300=240%:%
+%:%300=239%:%
 %:%301=240%:%
-%:%302=241%:%
+%:%303=241%:%
 %:%304=242%:%
-%:%305=243%:%
+%:%307=245%:%
 %:%308=246%:%
@@
 %:%310=248%:%
-%:%311=249%:%
-%:%313=251%:%
+%:%312=250%:%
+%:%313=250%:%
 %:%314=251%:%
-%:%315=252%:%
+%:%316=252%:%
 %:%317=253%:%
-%:%318=254%:%
+%:%318=253%:%
 %:%319=254%:%
 %:%320=255%:%
-%:%321=256%:%
-%:%322=256%:%
+%:%321=255%:%
+%:%323=256%:%
 %:%324=257%:%
 %:%325=258%:%
-%:%326=259%:%
-%:%334=261%:%
+%:%333=260%:%
+%:%345=262%:%
 %:%346=263%:%
@@
 %:%350=267%:%
-%:%351=268%:%
-%:%353=271%:%
-%:%354=271%:%
+%:%352=270%:%
+%:%353=270%:%
+%:%355=271%:%
 %:%356=272%:%
@@
 %:%358=274%:%
-%:%359=275%:%
+%:%359=274%:%
 %:%360=275%:%
 %:%361=276%:%
-%:%362=277%:%
-%:%363=277%:%
-%:%365=277%:%
-%:%369=277%:%
+%:%362=276%:%
+%:%364=276%:%
+%:%368=276%:%
+%:%369=276%:%
 %:%370=277%:%
-%:%371=278%:%
-%:%372=278%:%
-%:%373=278%:%
+%:%371=277%:%
+%:%372=277%:%
+%:%381=279%:%
 %:%382=280%:%
@@
 %:%397=295%:%
-%:%398=296%:%
-%:%400=298%:%
+%:%399=297%:%
+%:%400=297%:%
 %:%401=298%:%
-%:%402=299%:%
+%:%403=299%:%
 %:%404=300%:%
-%:%405=301%:%
+%:%405=300%:%
 %:%406=301%:%
 %:%407=302%:%
-%:%408=303%:%
+%:%408=302%:%
 %:%409=303%:%

### 2022-01-24 paper/output/document/AMA_possible.tex
cleaned AMA possible' '

@@
 \begin{isamarkuptext}%
-Philosophers often seem averse to the idea that a computer could perform anything close to ethical 
-reasoning. For example, Rawls asserts, ``It is a serious misconception to think of the CI-procedure 
+Many philosophers are averse to the idea that a computer could perform ethical 
+reasoning or that the categorical imperative could provide an algorithm for
+moral judgement. For example, Rawls asserts, ``it is a serious misconception to think of the CI-procedure 
 as an algorithm intended to yield, more or less mechanically, a correct judgment. There is no such 
-algorithm, and Kant knows this" \citep[166]{rawlslectures}. Ebels-Duggan also claims that, ``No one supposes that the Categorical
+algorithm, and Kant knows this" \citep[166]{rawlslectures}. Ebels-Duggan also claims, ``no one supposes that the Categorical
 Imperative provides a mechanical algorithm that delivers all by itself a complete account of what we 
@@
 may seem, these claims are not obvious and require further justification. After all, computers may eventually 
-learn to simulate human mental activity exactly, as shown by progress in brain simulation \citep{brainsimulation}. 
-Philosophers who believe that mental activity determines moral reasoning\footnote{what's the name for these
-guys? do they have a name?}, must explain why computers can, in theory, simulate mental processes like arithmetic 
+learn to simulate human mental activity entirely, as shown by progress in brain simulation \citep{brainsimulation}. 
+Philosophers who believe that mental activity determines moral reasoning,\footnote{what's the name for these
+guys? do they have a name?} must explain why computers can, in theory, simulate mental processes like arithmetic 
 and language, but cannot perform ethical reasoning. Without a soul or God-based account of ethical reasoning, 
@@
 
-In \emph{Universal Laws and Ends In Themselves}, O'Neill argues against the existence of an algorithm for
+In this section,
+I explore potential arguments for why the categorical imperative could not be automated. When 
+philosophers say that the categorical imperative is not an algorithm, they are often are gesturing to the complexity
+of ethical judgement. They refer to the difficulty in determining morally relevant circumstances of a maxim or the common 
+sense required for a computer to behave ethically as arguments against a categorical imperative ``algorithm." 
+I will show in this section that these difficulties do not render automated Kantian ethics impossible, but 
+merely difficult. There categorical imperative may not provide a simple and immediate algorithm, but, as
+I demonstrate in this thesis, some parts of moral judgement using the FUL can be automated using not one
+algorithm, but the many algorithms necessary to automatically prove logical theorems.
+
+In \emph{Universal Laws and Ends In Themselves}, O'Neill presents an early account against the existence of an algorithm for
 moral behavior. She points out that Kant draws an important distinction between a morally worthy maxim
@@
 it seems unlikely that a computer could, in the near future, behave ``morally," since a computer does 
-not have the same kinds of motivations and ``will" as a human being. If a computer is not a fully rational
-being, it cannot behave morally.
+not have the same kinds of motivations and will as a human being. If a computer is not a fully rational
+being, then, it is not the kind of thing that can behave morally.
 
-Even if, under Kant's account, a computer cannot behave morally, this still does not preclude the kind 
+The idea that, under Kant's account, a computer cannot behave morally, does not preclude the kind 
 of automated categorical imperative test that I present in this thesis. O'Neill argues that the FUL
 serves as a test of morally worthy maxims, and an automated categorical imperative test can be used 
-to identify this kind of maxim. Perhaps a computer cannot act on this maxim from a motivation of duty, 
-but it certainly can act on this maxim. For example, a self-driving car can choose to swerve to hit a tree
-to avoid injuring pedestrians in the crosswalk and this action may be one that acts on a morally worthy maxim
+to identify this kind of maxim. Perhaps a computer cannot act on a morally relevant maxim from a motivation of duty, 
+but it certainly can act on this maxim nonetheless. For example, a self-driving car can choose to swerve to hit a tree
+to avoid injuring pedestrians in the crosswalk. This action may be one that acts on a morally worthy maxim
 \emph{even if} the self-driving car is not motivated by duty. The discpline of machine ethics is partially
 spurred by the recognition that, as automated agents become more powerful, they will need to make
-morally tinged decisions. Such agents may be incapable of moral behavior, but automated agents that mimic
-moral behavior are surely better than such agents that ignore morality entirely. Moreover, this argument
+morally consequential decisions. Automated agents may be incapable of moral behavior, but automated agents that mimic
+moral behavior are surely better than agents that ignore morality entirely. Moreover, this argument
 has no bearing on the possibility of computational ethics, as evaluating the moral status of a maxim can 
-help philosophers study maxims and Kantian ethics even if the computer performing the evaluation is incapable of 
+help philosophers study Kantian ethics even if the computer performing the evaluation is incapable of 
 moral behavior.
 
-Another challenge for automated Kantian ethics identified by O'Neill is that the FUL test requires
-a maxim given as input. O'Neill notes that the test assumes ``that agents will have certain tentative 
+Another challenge for automated Kantian ethics identified by O'Neill is that the FUL test requires that
+a maxim be given as input. O'Neill notes that the test assumes ``that agents will have certain tentative 
 plans, proposals and policies which they can consider, revise or reject or endorse and pursue" \citep[343]{oneilluniversallaws}.
-Kant even argues that the difficulty of determining an agent's potential maxim, which is their
-own, subjective understanding of their principle of action, may be a reason that we may never be able 
-to know if morally worthy action has been performed \cite[345]{oneilluniversallaw}.
+Kant even claims that the difficulty of determining an agent's potential maxim, which is their
+own, subjective understanding of their principle of action, is a reason that we may never be able 
+to know if morally worthy action has been performed \cite[345]{oneilluniversallaws}.
 
-The challenge of mapping actions to maxims is a limitation of my system, but is not insurmountable. In Section Upshot,
-I argue that before my system can be used in practice, it must be paired with an ``input parser," that can
-translate dilemmas or choices that an automated agent faces into maxims in a logic that my system can
-evaluate. This limitation directly follows from the difficulty in mapping an action or potential action
+The challenge of mapping actions to maxims is a limitation of my system, but it is not insurmountable. In Section Upshot,
+I argue that, before my system can be used in practice, it must be paired with an ``input parser," that can
+translate choices that an automated agent faces into maxims in a logic that my system can
+evaluate. This limitation directly follows from the difficulty in mapping a potential action
 to the maxim of action, whether concerning human action or machine action. As argued in Section Upshot,  
@@
 for human Kantian ethical reasoners, it is unsurprising that it is a major hurdle for automated Kantian agents. 
-That being said, computational ethics remains unaffects by this concern because philosophers often debate 
+Computational ethics remains unaffected by this concern because philosophers often debate 
 the morality of specific maxims or metaethical properties of the categorical imperative, all of which can
@@
 
-As one of the strongest arguments against any categorical imperative algorithm, O'Neill argues that 
+As one of the strongest arguments against a categorical imperative algorithm, O'Neill argues that 
 the FUL is not supposed to provide a mechanism for deriving all morally worthy maxims from scratch. She notes
 that ``we usually already have learnt or worked out the moral standing of many common maxims of duty," 
-and so approach moral deliberation with an ``almanac" of morally worthy and empty maxims. Rational agents
+and so approach moral deliberation with an ``almanac" of morally worthy and empty maxims \citep[394]{oneilluniversallaws}. Rational agents
 navigating the world rarely recalculate the moral status of each potential maxim of action; instead, we consult our
-almanac of maxims. The categorical imperative is useful to double-check our work and verify the rightness or 
-wrongness of a maxim, but is not an actual part of the bulk of human ethical reasoning.
+almanac of maxims. The categorical imperative is useful to verify the rightness or 
+wrongness of a maxim, but is not part of the bulk of human ethical reasoning.
 
-While human beings cannot repeatedly apply the universalizability test to all potential maxims in 
-every moral dilemma, there is no reason that computers cannot do the same. While human beings are 
+While human beings cannot repeatedly apply the universalizability test to all potential maxims during 
+every moral dilemma, computers have the computational power to do so. Human beings are 
 equipped with enough prior knowledge or ``common sense" to have an almanac of morally worthy maxims,
-they are limited in their computational power. Computers, on the other hand, are comparatively
-much more capable of computation and thus can actually repeatedly recompute the results of the categorical
+but we have limited computational power. Computers, on the other hand, are comparatively
+much more capable of computation and thus can repeatedly recompute the results of the categorical
 imperative test. They do not come equipped with an almanac of maxims, but can simply recompute this
 almanac every time they need to make a decision. Human beings use common sense to make up for their computational
-limitations, and automated moral agents can use computational power to elide common sense entirely.
+limitations, and automated moral agents can use computational power to reduce the need for common sense.
 
-Daniela Tafani takes this argument one step further by arguing that the categorical imperative is not meant
-to derive the content of moral obligation from scratch. Instead, she argues that human beings already
+Daniela Tafani takes this argument one step further by arguing that this ``alamnac" of maxims already 
+includes the moral status of the maxims in questions; human beings already
 know which maxims are morally worthy and which are morally lacking. The categorical imperative test
@@
 our own convenience or pleasure, that the moral law has no exceptions \citep[9]{tafani}. Thus, she claims
-that ``The Kantian test is therefore as useless for machines as it is for anyone who does
-not already know what to do" \citep[8]{tafani}. Understanding the categorical imperative test as a reminder
-instead of a derivation tool also explains a fact noted by O'Neill that I discuss in Section ?? as a 
-response to the tailoring objection: the FUL test cannot handle bad-faith attempts to generate false
+that ``the Kantian test is therefore as useless for machines as it is for anyone who does
+not already know what to do" \citep[8]{tafani}.\footnote{Translated from the original paper using Google Translate.} 
+Understanding the categorical imperative test as a reminder
+instead of a derivation tool also explains a fact noted by \cite{constofreason} that I discuss in Section Applications as a 
+response to the tailoring objection: the FUL cannot handle bad-faith attempts to generate false
 positives or negatives. The test only returns the right result when an agent sincerely attempts to 
@@
 knowledge should be used to create an input parser. Specifically, some kind of machine learning-based approach
-could perform action-maxim mappings based on a database of such mappings compiled by a human being. Moreover, 
+could learn action-maxim mappings from a database of such mappings compiled by a human being. Moreover, 
 the human being could assign each maxim in the database a rightness or wrongness score. My implementation
@@
 prior knowledge of some maxims' moral worth and the ability of a computer to constantly perform the
-universalizability test could make such a system not only match human ethical reasoning but surpass it
+universalizability test could not only match human ethical reasoning but perhaps also surpass it
 by double checking the moral intuitions that we take for granted. A computer with no common sense or prior knowledge
@@
 \includegraphics[scale=0.5]{inputparser.png}
-\caption{ugh i have to write a caption} \label{fig:inputparser}
+\caption{A refined version of Figure \ref{fig:AIengine} in which the input parser learns from a database
+of action-maxim mappings, which is in turn fed the output of my automated Kantian ethics system. } \label{fig:inputparser}
 \end{figure}
@@
 %:%136=108%:%
-%:%139=112%:%
-%:%140=113%:%
-%:%141=114%:%
-%:%142=115%:%
-%:%143=116%:%
+%:%137=109%:%
+%:%138=110%:%
+%:%139=111%:%
+%:%140=112%:%
+%:%141=113%:%
+%:%142=114%:%
+%:%143=115%:%
+%:%144=116%:%
+%:%145=117%:%
+%:%146=118%:%
+%:%147=119%:%
+%:%148=120%:%
+%:%151=124%:%
+%:%152=125%:%
+%:%153=126%:%
+%:%154=127%:%
+%:%155=128%:%
+%:%156=129%:%

### 2022-01-30 paper/outline/outlinefinal.tex
added outline

\documentclass[11pt]{article}
\usepackage{outlines}
\usepackage{xcolor}
\usepackage{amssymb}
\usepackage{times}
\usepackage[margin=1in]{geometry}
 \usepackage{relsize}

\normalfont

\begin{document}

\textbf{Legend:}

$\color{red} \mathbf{\times} \color{black}$ = To be written \hfill \emph{5 pages}

$\color{yellow} \mathbf{\approx} \color{black}$ = Needs jiggling (was written for the paper, is outdated) \hfill \emph{19 pages}

$\color{green} \mathbf{\checkmark} \color{black}$ = Complete (except for polishing, entry and exit, etc.) \hfill \emph{32 pages}

\hfill \emph{Total page count: 60 pages}

\begin{outline}[enumerate]
\1 Abstract (1 page) \hfill $\color{red} \mathbf{\times} \color{black}$

\1 Introduction (5 pages) \hfill $\color{yellow} \mathbf{\approx} \color{black}$
\2 Problem and Motivation 
\3 Artifical agents are becoming increasingly autonomous and are making increasingly consequential 
decisions. These are ethical decisions. Thus, we should use the centuries of existing literature on
ethics to help us help computers make them.
\2 My Idea/Contributions 
\3 I present an implementation of automated ethical reasoning according to Kantian ethics that is 
faithful to philosophical literature. (include AI ethics diagram)
\3 In Section 3a, I make a philosophical argument for why Kantian ethics, a kind of rule-based 
deontology, is the most natural of the three major ethical traditions (deontology, virtue ethics, 
consequentialism) to automate.
\3 In Section 4a, I formalize a philosophically accepted version of 
the categorical imperative in DDL. 
\3 In Section 4b, I implement my formalization in Isabelle/HOL. My implementation 
includes axioms and definitions that can prove that appropriately represented sentences are permissible, 
obligatory, or prohibited. It can also return a list of facts used in the proof and, in some cases, 
an Isar-style human readable proof. 
\3 In Sections 5a and 5b, I demonstrate my system's power and flexibility by 
using it to produce nuanced answers to two well-known Kantian ethical dilemmas. I show that, because 
my system draws on definitions of Kantian ethics presented in philosophical literature, it is able to 
perform sophisticated moral reasoning. 
\3 In Section 4c, I present a testing framework that can evaluate how faithful an implementation 
of automated Kantian ethics is to philosophical literature. My testing framework shows that my formalization 
is more philosophically accurate than prior work. This testing approach can be generalized to evaluate any 
implementation of automated Kantian ethics and to perform test-driven development for automated ethics.
\3 In Section 6a, I demonstrate how my system can be used to generate novel(?) philosophical
insights, thus showing that computational tools can help philosophers better study philosophy.

\1 Methods (10 pages) \hfill $\color{green} \mathbf{\checkmark} \color{black}$
\2 Why Kantian Ethics (7 pages)
\3 Consequentialism takes too much data
\3 Virtue Ethics requires representing ``character" and ``attitude" to a computer
\3 Deontology/Kantian Ethics is formal and the least-data intensive
\2 Dyadic Deontic Logic (2 pages) 
\2 Isabelle/HOL (1 page) 
\3 What it is, what it lets you do

\1 Implementing a novel formalization of the categorical imperative (12 pages)
\2 The Formalization (6 pages) \hfill $\color{green} \mathbf{\checkmark} \color{black}$
\3 Defining a Maxim (adopting O'Neill's definition) 
\3 Practical Contradiction Interpretation (summarizing Korsgaard's argument)
\3 The Formalization Itself 
\2 Testing Framework (6 pages)  \hfill $\color{yellow} \mathbf{\approx} \color{black}$
\3 Comparision to other attempts (control group and Kroy's prior formalization)
\3 Presenting the tests
\4 For each test, I will present both its philosophical justification and the code that runs the test.

\1 Applications (12 pages) \hfill $\color{green} \mathbf{\checkmark} \color{black}$
\2 Lying vs Joking (6 pages)
\3 Philosophical explanation of the argument for why the FUL prohibits joking
\3 My Approach (using thin common sense facts and assumptions)
\3 Code running the example
\2 Murderer Example (6 pages)
\3 Philosophical explanation of the dilemma of the murderer at your door
\3 My Approach 
\3 Code running the example
\3 Discussion of the need for and challenge of automating common sense

\1 Discussion (20 pages)
\2 Computational Ethics (8 pages) \hfill $\color{yellow} \mathbf{\approx} \color{black}$
\3 Example of the philosophical insight (well-formed maxims, potential application to philosophy of doubt)
\3 Arguing that computational tools can be valuable to philosophers
\2 Limitations (2 pages) \hfill $\color{red} \mathbf{\times} \color{black}$
\3 The Need for Common Sense 
\3 Formulating an Input Maxim
\3 The AI ethics diagram and what else is needed to use the system in practice
\2 Is Automated Kantian Ethics Even Possible? (4 pages)
\2 Related Work (4 pages) \hfill $\color{green} \mathbf{\checkmark} \color{black}$
\2 Conclusion (2 pages) \hfill $\color{red} \mathbf{\times} \color{black}$
\3 The idea of a computer doing ethical reasoning is scary, but insofar as people are going to keep
building increasingly autonomous machines, it's better that they mimic ethical behavior. 
\3 This is a proof-of-concept, but given computational progress and society's recognition of the need for
AI ethics, we will see lots of progress and maybe someday this can actually be practical and usable.

\1 References

\1 Appendix 
\2 Full implementation of DDL
\2 Running the tests on the control group 
\2 Running the tests on Kroy's formalization
\2 Extra code from custom formalization and tests
\2 What kind of computational ethics is a good idea?

\end{outline}
\end{document}

### 2022-01-30 paper/output/document/AMA_possible.tex
added outline

@@
 positives or negatives. The test only returns the right result when an agent sincerely attempts to 
-represent their maxim of action, not when an adversary attempts to ``trick" the categorical imperative.
-
+represent their maxim of action, not when an adversary attempts to ``trick" the categorical imperative.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{figure}
+\centering
+\includegraphics[scale=0.5]{inputparser.png}
+\caption{A refined version of Figure \ref{fig:AIengine} in which the input parser learns from a database
+of action-maxim mappings, which is in turn fed the output of my automated Kantian ethics system. } \label{fig:inputparser}
+\end{figure}
+%
+\begin{isamarkuptext}%
 This understanding of the role of the categorical imperative not only fails to render automate moral
@@
 \end{isamarkuptext}\isamarkuptrue%
-%
-\begin{figure}
-\centering
-\includegraphics[scale=0.5]{inputparser.png}
-\caption{A refined version of Figure \ref{fig:AIengine} in which the input parser learns from a database
-of action-maxim mappings, which is in turn fed the output of my automated Kantian ethics system. } \label{fig:inputparser}
-\end{figure}
 %
@@
 %:%132=104%:%
-%:%133=105%:%
-%:%134=106%:%
 %:%135=107%:%
@@
 %:%140=112%:%
-%:%141=113%:%
-%:%142=114%:%
-%:%143=115%:%
-%:%144=116%:%
-%:%145=117%:%
-%:%146=118%:%
-%:%147=119%:%
-%:%148=120%:%
-%:%151=124%:%
-%:%152=125%:%
-%:%153=126%:%
-%:%154=127%:%
-%:%155=128%:%
-%:%156=129%:%
+%:%143=114%:%
+%:%144=115%:%
+%:%145=116%:%
+%:%146=117%:%
+%:%147=118%:%
+%:%148=119%:%
+%:%149=120%:%
+%:%150=121%:%
+%:%151=122%:%
+%:%152=123%:%
+%:%153=124%:%
+%:%154=125%:%
+%:%155=126%:%
+%:%156=127%:%
+%:%157=128%:%

### 2022-02-04 paper/facct/abstract.tex
abstract and intro

--- 2021-12-13 paper/abstract.tex
@@
 dangers of unethical artificial intelligence have spurred interest in the development 
-of machines that can perform ethical reasoning. Despite the fact that ethical philosophers are devoted to 
-developing robust ethical theories, previous work in automated ethics rarely engages with existing 
-philosophical literature. Faithfully translating complex, philosophically sophisticated ethical theories 
-expressed in natural language to the rigid syntax of a computer program poses technical and philosophical 
+of machines that can perform ethical reasoning. However, previous work in automated ethics rarely 
+engages with existing philosophical literature. Philosophically sophisticated ethical theories are necesssary
+for nuanced and reliable judgements, but faithfully translating these complex ethical theories
+from natural language to the rigid syntax of a computer program poses technical and philosophical 
 challenges. In this paper, I present an implementation of automated Kantian 
@@
 my implementation coheres with expected properties of Kantian ethics, as established in the literature. 
-My system is not only an early step towards philosophically mature ethical AI agents, but it can also help
-philosophers reach new ethical insights, thus paving the way for the use of computational tools to 
-address philosophical problems.
+My system is an early step towards philosophically mature ethical AI agents and it can make nuanced 
+judgements in complex ethical dilemmas because it is grounded in philosophical literature. Moreover, 
+because my system uses an interactive theorem prover, its judgements are explainable.
 
 \smallskip
-\noindent \emph{Areas: algorithm development, applications, philosophy, ethics and automation}
+\noindent \emph{Area: Algorithm Development}
+
+\noindent \emph{Keywords: AI ethics, interactive theorem provers, deontic logic, Kant}
 \end{document}

### 2022-02-04 paper/outline_notes/notes_01_13.tex
abstract and intro

Rawls Lectures on the History of Moral Philosophy p. 166
"It is a serious misconception to think of the CI-procedure as an algorithm intended to yield, more 
or less mechanically, a correct judgment. There is no such algorithm, and Kant knows this. It is 
equally a misconception to think of this procedure as a set of debating rules that can trap liars
and cheats, scoundrels and cynics, into exposing their hand. There are no
such rules."
- why not? rawls doesn't really explain himself

O'Neill Universal Laws and Ends in Themselves p. 343
"The three formulations are all offered as tests that agents can apply to
 proposals for action. The Categorical Imperative is nowhere proposed as a
 principle that will by itself generate or entail a universal moral code. It is not
 a moral algorithm (unlike the Principle of Utility) but (supposedly) a
 criterion of moral action for agents who act freely, so may start with
 various possible proposals for action. The common assumption of the three
 principles is that there is some way by which agents can filter these initial
 proposals to check whether they are morally acceptable. Each formulation
 of the Categorical Imperative is offered as an answer to the agent's question
 "What ought I do?",3 on the assumption that agents will have certain ten
 tative plans, proposals and policies which they can consider, revise or re
 ject?or endorse and pursue."
her arguments:
-can only test given maxims, can't magically produce moral action 
-assumes that there is some input and answers the question "What should I do?" among given options
  - that is exactly what my system does 
  - the model is that, like a human, an AI navigating the world has options and has to decide among them

p.345
"Fifth, since the implementation of maxims will differ according to cir
 cumstances, a test on maxims is not and cannot be enough to determine the
 Tightness or wrongness of particular acts (their "legality"); it can only
 reveal the moral quality or worth of maxims (so is in Kant's terms a test of
 "morality"). Kant defines duty not (as would be common today) as out
 ward performance of a certain sort, but as action that embodies a good will
 i.e., action on a maxim of a certain sort. (397) However, although moral
 worth is more fundamental than Tightness in Kant's theory, Tightness and
 wrongness are more easily ascertainable. This is simply a corollary of the
 opacity of our self knowledge. If we are unsure what the maxim of a given
 act is, we cannot be sure whether it is morally worthy. Despite their best ef
 forts at principled and self-conscious action, agents are prey to self
 deception and selective perception. This is not rare or exotic but com
 monplace?we are repeatedly tempted to ascribe maxims that place acts and
 agents in a more flattering or a more lurid light. By contrast, it would be
 relatively easy // we had a test to identify morally worthy maxims to deter
 mine whether an agent who acted on such a maxim would have acted in a
 specific way in those circumstances. In his most pessimistic moments Kant
 doubts whether we can ever know that a morally worthy action has been
 done, which would mean that we can never judge the morality of acts. This
 pessimism need not stop us from judging whether acts that conform to such
 maxims have been done?provided that we have a criterion for identifying
 morally worthy maxims.5 The various formulations of the Categorical Im
 perative are supposed to provide this criterion"
-only evaluates whether or not maxims are morally worthy, but doesn't evaluate action. to evaluate 
action, you have to decide what the maxim of action is and evaluate it
  - in the model above, the AI has options and has to decide which to take, like a human. Section ??
concedes that determining the maxim to pass as input to my system is a challenge and possible limitation
of my system, and this is part of the challenge of formulating a maxim, which this criqitue also 
says is a challenge.
  - Nonetheless, there is some value to providing a criterion for identifying morally worthy maxims. 
Perhaps we (and machines) are not always mistaken about the maxim of action. Perhaps the maxims are chosen
from some pre-populated, manually entered database. Identifying morally relevant maxims is one step 
towards automated ethics but not the whole puzzle and that's ok. 
p.349-350 describes what the role of the FUL is 
- most practical reasoning doesn't involve literally using the CI to evaluate maxims - we have some 
prior knowledge from moral advice and guidance about which maxims are good or bad
- FUL merely tells you how to distinguish maxims of duty from maxims that are not of duty, but practical
reason is the process of determining which maxim a particular action in a particular situation conforms with
  - this provides a clue as to how you can implement an input parser - maybe we have some prior database of 
actions or action-maxim mappings and we extrapolate from there 
  - either way, we agree. my project tells you how to distinguish maxims of duty, and then actually 
using that to guide action requires an additional step
  - moreover, human beings need an "almanac" or prior set of maxims that are of duty or not because we
have limited reasoning capacity but computers can totally just rederive which maxims are good or bad
constantly. that way computers can use both testimony and proof!
- tradeoff: computation vs common sense so partnership is the best approach

seems crazy but need an argument given computes can simulate human brain

herman (available for pickup) TBD

Tafani
p3 "In Kant's lexicon, it is a matter of constructing machines whose
characteristic is not goodness, but holiness, that is, knowledge of moral
norms and the infallible and automatic adaptation of their actions to them"

Kant is easy bc:
p. 4 -> only requires rationality to behave morally (cognitivism)
no moral dilemmas bc no conflicting obligations
FUL seems computational

three challenges:
1. difficult/impossible for computer to check for contradiction under FUL
2. "the difficulty of selecting, from a given maxim, the relevant elements for its
universalization" (circumstance/formulation of the maxim)
3. how do you actually understand the universalized world -> need empirical and psychological knowledge
I solve the first and (kind of) second challenges
"universal diffusion of lying" is an empirical or anthropological truth
Herman -> moral rules of relevance -> human agent knows which features of the maxim are morally relevant

p. 8 -> Kant says that people know their duty and we need philosophy to remind them and mitigate bad-faith efforts
"For Kant, the identification of the criterion of moral judgement is therefore
not a procedure by which someone who is ignorant of the moral law can
find out what his duty is (Singer, 1973, p. 298), or by which a computer
system can be programmed to morality; it constitutes the analysis of
common moral judgement, i.e. the reconstruction of what every man
automatically does when he finds himself morally evaluating a maxim. The
Kantian test is therefore as useless for machines as it is for anyone who does
not already know what to do."

his examples are cases where there is a temptation to make an exception just for me 
it's a reaffirmation in a moment of weakness, not a way to derive duty from scratch
"However useful it may be from a psychological
point of view, in moments of weakness, such a reaffirmation of the
universal validity of the moral law does not, by itself, lead to the definition
of what, concretely, must be done, since it is compatible - as a mere
requirement of universality - with countless alternative definitions of the
content of the moral law"

p. 8 "It is true - as O'Neill observes - that a check on the contradictory nature of
the universalised maxim requires a common sense consideration of the
empirical consequences, which a machine is therefore unable to perform,
and it is true that even a common sense test can give false positive results. It
is true that even a test based on common sense can give false positive
results. But this is not due to a weakness in the formulation of the test,
which would therefore need to be fine-tuned, but rather to a distortion of the
function attributed by Kant to the test by those who attempt to use it to
regulate the behaviour of humans or machines from scratch. "
- O'Neill says that you need some common sense or practical reason or judgement to perform the UT
- this is true and also why it gives false-positives
- BUT the false-positives are a result of using the test WRONG, in a bad-faith manner
- you CAN arbitrary specify maxims.but you're not supposed to
- you're not supposed to try to circumvent the test - the point is not to put in arbitrary maxims
- instead, the point is to put in maxims of which you have some notion of rightness or wrongness
and the test will confirm it and remind you what your duty is

outline:
1. philosophers like to assert that ethics is not the right kind of thing to be automated (e.g. Rawls). 
      But this has to be justified - after all, computers can mimic human brain activity entirely, so cognitivists
      have to argue why ethics is out of reach of computation but addition, emotion, thought, and language aren't

2. one reason, from O'Niell is that the FUL can only test given maxims but can't actually prescribe
moral action because moral action also requires a specific attitude towards the moral law
      That's ok! Current computers aren't rational beings so they can't actually behave morally, but
      they can act on the maxim that has moral worth in a particular situation. We can't judge a computer
      as "acting from duty" but we might still think that a computer acting on morally worthy maxims 
      is a better thing for society than computers not acting on morally worthy maxims.

      Also, this doesn'tindict CE.

3. Moreover, even evaluating a particular maxim requires that the maxim be given as input. Specifically,
human beings navigating the world are faced with choices, and if they want to use the FUL, they have to
extract their potential maxims from their choices. O'Neill says 
that even Kant identifies this as challenging for human beings, and Tafani also identifies this as a 
challenge for Kantian machine ethics.
      This is a challenge I also identify! Formulating the input maxim for my system. See the discussion 
      in Section Upshot about this. Roughly, I argue that either a human being can take over or we can 
      develop heuristics. Moreover, there's still some value to having a machine that can apply the CI
      test to given maxims and future work can work on the input parser. Also doesn't indict CE.

4. Finally, Tafani and O'Niell also argue that the FUL is not SUPPOSED to generate ethics from scratch.
O'Niell notes that human beings come equipped with an almanac of right and wrong maxims and that
the fUL tests these. Human beings don't actually repeatedly apply the UT.
      Cool! Computers don't have human limitations, so they can actually repeatedly apply the CI test, 
      essentially checking their work and rederiving the moral worth of a maxim every time they consider it.
      There's a tradeoff here: humans have common sense but computational limits, so they use the common 
      sense to avoid repeating calculations. computers have no common sense but (Compared to humans)
      no computational limits, so they can perform the calculation over and over again instead of
      "remembering" it. almanac == cultural memory of rightness and wrongness

5. Tafani takes it one step further by arguing that we actually know which maxims are right
and which ones are wrong and the UT is just supposed to strengthen our resolve to behave morally whenever
we are tempted to make an exception of ourselves. Indeed, bad-faith attempts to pass the UT work - see 
the example of the tailoring objection given by O'Niell. 
    This, combined with the almanac, actually give us some insight into how we can solve the challenge
    of making an input parser. Specifically, we can learn some set of maxims and maybe assign each a 
    "rightness score" indicating how confident we are that it is right or wrong and THEN use the automated
    FUL to test these maxims. You can imagine a deep-learning type system that, based on some database
    mapping actions to maxims, can extract a maxim from a situation as well as its rightness score
    and then pass these as input to the FUL test. The output of the FUL test can in turn reinforce or
    rething the rightness score.

### 2022-02-04 paper/outline_notes/paper_outline.tex
abstract and intro

--- 2021-12-13 paper/paper_outline.tex
@@
 \begin{outline}[enumerate]
-\1[Introduction (1p)] 
+\1 Introduction (1p)
 \2 Problem
@@
 
-\3 I present an implementation of automated Kantian ethics by formalizing the categorical
-imperative in deontic logic and implementing this formalization in Isabelle. My system
-improves on prior work by formalizing a sophisticated interpretation of the Formula of Universal Law 
-and representing the idea of a maxim. This implementation contributes axioms and definitions such that 
-a maxim, appropriately represented,
-can be shown to be permissible, prohibited, or obligatory, along with a list of facts used
-to complete the proof and, in some cases, an Isar-style readable proof.
+\3 In Section 4.a, I make a philosophical argument for why Kantian ethics is the most natural of the three major
+ethical traditions (deontology, virtue ethics, utilitarianism) to formalize.
+\3 In Section 4.b, I present a formalization of the practical contradiction interpretation of the 
+Formula of Universal Law in Dyadic Deontic Logic. 
+\3 In Section 4.c, I present an implementation of the above formalization in the Isabelle/HOL theorem prover.
+My implementation includes axioms and definitions such that my system, when given an appropriately
+represented input, can prove that the input is permissible, obligatory, or prohibited. It can also return
+a list of facts used in the proof and, in some cases, an Isar-style human readable proof. Because my system
+is equipped with a sophisticated definition of a maxim, I show that it improves on prior work by performing 
+reasoning nuanced enough to distinguish between a joke and a lie.
+\3 In Section 4.d, I present a testing framework that can generally evaluate how faithful an implementation 
+of automated Kantian ethics is. My framework includes meta-ethical tests and application tests inspired by philosophical
+literature. My testing framework shows that my formalization substantially improves on prior work and can 
+be generalized to any implementation of automated Kantian ethics.
+\3 In Section 4.e, I demonstrate new ethical insights discovered using my system and argue that 
+computational methods like the one presented in this paper can help philosophers address ethical problems.
 
-\3 I present a testing architecture to evaluate different implementations of the categorical imperative
-based on ethical intuitions and properties of Kantian ethics established in the literature. Based on 
-my testing architecture, my implementation outperforms prior attempts at formalizing Kantian ethics.
-The tests include meta-ethical tests (which test the abstract properties of the ethical theory)
-and application tests (which test the judgements that my system would make in real-world dilemmas).
-
-\3 Should I include any of the philosophical contributions? Specifically, the writing on why Kantian 
-ethics is the most natural to formalize is a philosophical contribution but not a technical one.
-
-\1[The Problem (1p)] 
+\1 The Problem (1p)
 \2 In order for AI agents to navigate the world responsibly, they need to perform ethical reasoning.
@@
 \2 Maybe put something about computational ethics here?
-\1[My Idea (2p)]
+\1 My Idea (2p)
 \2 Overview of the Top-Down, Theorem Prover approach
@@
 \2 How it would fit into (a) an AI agent (b) philosophers' workflow
-\1[The Details (5p)] 
+\1 The Details (5p)
 \2 Why Kantian Ethics (1-1.5p)
@@
 \2 Limitations (needs an input parser and a common sense database)
-\1[Related Work (1-2p)] 
+\1 Related Work (1-2p)
 \2 Talk about bottom-up vs top-down approaches 
@@
 system
-\1[Conclusion (0.5p)]
+\1 Conclusion (0.5p)
 

### 2022-02-04 paper/output/document/AMA_possible.tex
abstract and intro

@@
 ought to do in any given situation" \citep[174]{ebelsduggan}. However unmechanical ethical reasoning
-may seem, these claims are not obvious and require further justification. After all, computers may eventually 
+may seem, these claims are not obvious and require further justification. Philosophers who believe 
+that mental activity completely determines moral reasoning,\footnote{what's the name for these
+guys? do they have a name?} must explain why computers can, in theory, simulate certain mental processes like arithmetic 
+and language, but cannot perform ethical reasoning. Without a soul or God-based account of ethical reasoning, 
+it is not obvious that it is theoretically impossible to automate ethical reasoning. After all, computers may eventually 
 learn to simulate human mental activity entirely, as shown by progress in brain simulation \citep{brainsimulation}.
-Philosophers who believe that mental activity determines moral reasoning,\footnote{what's the name for these
-guys? do they have a name?} must explain why computers can, in theory, simulate mental processes like arithmetic 
-and language, but cannot perform ethical reasoning. Without a soul or God-based account of ethical reasoning, 
-it is not obvious that it is theoretically impossible to automate ethical reasoning.
 
@@
 moral behavior. She points out that Kant draws an important distinction between a morally worthy maxim
-and a morally worthy action: the latter requires a good will, motivated by duty. She argues that, 
+and a morally worthy action: the latter requires a good will, or a will motivated by duty. She argues that, 
 ``Kant defines duty not (as would be common today) as outward performance of a certain sort, but as action
-that embodies a good will" \citep[345]{oneilluniversallaws}. Under this understanding of moral behavior, 
-it seems unlikely that a computer could, in the near future, behave ``morally," since a computer does 
-not have the same kinds of motivations and will as a human being. If a computer is not a fully rational
+that embodies a good will" \citep[345]{oneilluniversallaws}. Moral behavior doesn't just require performing
+a ``good" action, but it requires acting on a morally worthy maxim from the motivation of duty, or 
+doing the right thing because it is the right thing to do. Moral behavior requires both a certain action 
+(acting on a morally worthy maxim) and a certain motivation (the motivation of duty). It is the capacity 
+for self-motivation that makes morality binding for rational beings; we must behave morally precisely 
+because we have wills, or the ability to be motivated by ends
+that we choose. Only rational beings have wills, thus only rational beings can have good wills, or wills
+motivated by duty, and thus only rational beings can behave morally. Under this understanding
+of moral behavior, it seems unlikely that a computer could, in the near future, behave ``morally," 
+since a computer does not have motivation in the same way as a human being. If a computer is not a fully rational
 being, then, it is not the kind of thing that can behave morally.
@@
 plans, proposals and policies which they can consider, revise or reject or endorse and pursue" \citep[343]{oneilluniversallaws}.
-Kant even claims that the difficulty of determining an agent's potential maxim, which is their
+The FUL evaluates the moral worth of a maxim given as input and this potential maxim is generated by 
+the choices that an agent is faced with. Determining this potential maxim is a challenge for both human
+and automated reasoners. Kant claims that the difficulty of determining an agent's potential maxim, which is their
 own, subjective understanding of their principle of action, is a reason that we may never be able 
-to know if morally worthy action has been performed \cite[345]{oneilluniversallaws}.
+to know if morally worthy action has been performed \cite[345]{oneilluniversallaws}. Reasoners are faced with
+choices between potential actions and must determine the maxim, or principle, underlying each potential action.
+This is equivalent to a ``mapping" problem: agents are given situations or dillemas as input and must map
+these to maxims.
 
@@
 this is not an insurmountable obstacle for automated ethics. Future work could develop heuristics to 
-map actions to maxims, perhaps by extracting the circumstances, act, and goal. Moreover, proponents of the 
-human-in-the-loop model may argue that the solution to this problem is to have a human being manually create
-such mappings, either dynamically or in a cached manner. Given that determining the maxim of action is a challenge
+map actions to maxims, perhaps by extracting the circumstances, act, and goal.\footnote{Proponents of the 
+human-in-the-loop model \cite{hitl} or human-computer symbiosis \cite{licklider} may argue that the 
+solution to this problem is to have a human being manually create
+such mappings, either dynamically or in a cached manner. For details on this approach, see Section
+Upshot.}  Given that determining the maxim of action is a challenge
 for human Kantian ethical reasoners, it is unsurprising that it is a major hurdle for automated Kantian agents. 
@@
 navigating the world rarely recalculate the moral status of each potential maxim of action; instead, we consult our
-almanac of maxims. The categorical imperative is useful to verify the rightness or 
+almanac of maxims. This almanac is generated by moral education, absorbed social values, and moral advice
+from people we trust. The categorical imperative is useful to verify the rightness or 
 wrongness of a maxim, but is not part of the bulk of human ethical reasoning.
@@
 %:%132=104%:%
+%:%133=105%:%
+%:%134=106%:%
 %:%135=107%:%
@@
 %:%140=112%:%
-%:%143=114%:%
-%:%144=115%:%
-%:%145=116%:%
-%:%146=117%:%
-%:%147=118%:%
-%:%148=119%:%
-%:%149=120%:%
-%:%150=121%:%
-%:%151=122%:%
-%:%152=123%:%
-%:%153=124%:%
-%:%154=125%:%
-%:%155=126%:%
-%:%156=127%:%
-%:%157=128%:%
+%:%141=113%:%
+%:%142=114%:%
+%:%143=115%:%
+%:%144=116%:%
+%:%145=117%:%
+%:%146=118%:%
+%:%147=119%:%
+%:%150=122%:%
+%:%151=123%:%
+%:%152=124%:%
+%:%153=125%:%
+%:%154=126%:%
+%:%155=127%:%
+%:%158=129%:%
+%:%159=130%:%
+%:%160=131%:%
+%:%161=132%:%
+%:%162=133%:%
+%:%163=134%:%
+%:%164=135%:%
+%:%165=136%:%
+%:%166=137%:%
+%:%167=138%:%
+%:%168=139%:%
+%:%169=140%:%
+%:%170=141%:%
+%:%171=142%:%
+%:%172=143%:%

### 2022-02-04 paper/output/document/thesis_0_abstract.tex
abstract and intro

%
\begin{isabellebody}%
\setisabellecontext{thesis{\isacharunderscore}{\isadigit{0}}{\isacharunderscore}abstract}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\begin{isamarkuptext}%
AI agents are beginning to make decisions without human supervision in increasingly consequential 
contexts like healthcare, policing, and driving. These decisions are inevitably ethically tinged, 
but most AI agents navigating the world today have no notion of ethics.
Warnings from regulators, philosophers, and computer scientists about the 
dangers of unethical artificial intelligence, from science-fiction killer robots to criminal
sentencing algorithms prejudiced against people of color, have spurred interest automated ethics, or the development 
of machines that can perform ethical reasoning. Previous work in automated ethics rarely
engages with existing philosophical literature. Given that ethics is the study of how to navigate the world,
automated ethics should look to philosophical literature to guide the development of AI agents that can
responsibly navigate the world. All decisions are moral decisions, including the ones that AI agents are actively 
making today. Automated ethics that draws on sophisticated philosophical literature makes the ethical reasoning
underlying such decisions nuanced, precise and reliable, but faithfully translating complex ethical theories
from natural language to the rigid syntax of a computer program poses technical and philosophical 
challenges.

In this thesis, I present an implementation of automated Kantian
ethics that is faithful to the Kantian philosophical tradition. Of the three major ethical
traditions, Kant's categorical imperative is the most natural to formalize because it is an inviolable 
formal rule that requires less context than other ethical theories. I formalize Kant's categorical imperative 
in Carmo and Jones's Dyadic Deontic Logic, implement this formalization 
in the Isabelle/HOL theorem prover, and develop a testing framework to evaluate how well 
my implementation coheres with expected properties of Kantian ethics, as established in the literature. 
I also use my system to reason about two ethical dilemmas used to criticize Kantian ethics: the case of 
joking and the example of a murderer knocking on someone's door asking about the location of their
intended victim. Armed with relatively uncontroversial facts about the world, my system correctly 
resolves these moral dilemmas.

My system is able to resolve complex ethical dilemmas because it is grounded in philosophical literature.
Moreover, because I automate an explicit ethical theory, the ethical reasoning underlying my system's judgements
is interpretable by a human being. I implement this ethical theory using the Isabelle/HOL interactive theorem prover, which can 
list the axioms and theorems used in a proof, so my system is explainable. This work serves as an early 
proof-of-concept for philosophically mature AI agents and is one step towards the development of 
responsible, trustworthy artificial intelligence.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/thesis_0_abstract.thy%:%
%:%19=6%:%
%:%20=7%:%
%:%21=8%:%
%:%22=9%:%
%:%23=10%:%
%:%24=11%:%
%:%25=12%:%
%:%26=13%:%
%:%27=14%:%
%:%28=15%:%
%:%29=16%:%
%:%30=17%:%
%:%31=18%:%
%:%32=19%:%
%:%33=20%:%
%:%34=21%:%
%:%35=22%:%
%:%36=23%:%
%:%37=24%:%
%:%38=25%:%
%:%39=26%:%
%:%40=27%:%
%:%41=28%:%
%:%42=29%:%
%:%43=30%:%
%:%44=31%:%
%:%45=32%:%
%:%46=33%:%
%:%47=34%:%
%:%48=35%:%
%:%49=36%:%
%:%50=37%:%
%:%51=38%:%

### 2022-02-04 paper/output/document/thesis_1_intro.tex
abstract and intro

%
\begin{isabellebody}%
\setisabellecontext{thesis{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}intro}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Introduction%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
The development of autonomous artificial agents has spurred interest in computers that can perform 
ethical reasoning, known as automated moral agents. AI agents are making decisions in increasingly 
consequential contexts, such as medical diagnoses, driving, and criminal sentencing, and therefore 
must perform ethical reasoning in order to navigate moral dilemmas responsibly. For example, self-driving
cars may face less extreme versions of the following moral dilemma: an autonomous vehicle approaching 
an intersection fails to notice pedestrians in the crosswalk until it is too late to brake. The car 
can either continue on its course, running over and killing three pedestrians, or it can swerve to 
hit the car in the next lane, killing the single passenger inside it. While this example is (hopefully) 
not typical of the operation of a self-driving car, every decision that such an AI agent makes, from 
avoiding congested freeways to carpooling, is morally tinged. Because ethics is the study of navigating 
the world responsibly, AI agents routinely make moral decisions without explicitly performing ethical
reasoning. Moreover, artifical agents are making many such moral decisions without
human supervision, such as hiring algorithms that filter job applicants' resumes, a decision that can
impact people's livlihoods and often involves implicit prejudices. Machine ethics, also called 
automated ethics, is the study of how to develop machines that can perform robust, sophisticated ethical reasoning.

Machine ethicists recognize the need for automated ethics and have made both theoretical 
(\citep{moralmachineonline} \citep{davenport} \citep{moralmachine} \citep{gabriel}) and practical progress 
(\citep{logicprogramming} \citep{biology} \citep{delphi} \citep{winfield}) towards automating ethics. 
However, prior work in machine ethics using popular ethical theories like deontology (\citep{deon2} \citep{deon1}), 
consequentialism (\citep{util1} \citep{util2} \citep{cloos}), and virtue ethics (\citep{berberich}) rarely 
engages with philosophical literature and thus misses philosophers' insights. The above example of 
the malfunctioning self-driving car is an instance of Phillipa Foot's trolley problem \citep{foot}, 
in which a bystander watching a runaway trolley can pull a lever to kill one instead of three. 
Decades of philosophical debate have developed ethical theories that can offer nuanced and 
consistent answers to the trolley problem. The trolley problem demonstrates that the moral dilemmas 
that AI faces are not entirely new, so solutions to these problems should take advantage of philosophical 
progress. The more faithful that automated ethics is to philosophical literature, the more reliable and 
nuanced it will be.

A lack of engagement with prior philosophical literature also makes automated moral agents less 
explainable, or interpretable by human observers, as seen in the example of Delphi, which uses deep 
learning to make moral judgements based on a training dataset of ethical decisions made by humans \citep{delphi}. 
Early versions of Delphi often gave unexpected results, such as declaring that the user should commit 
genocide if it makes everyone happy \citep{verge}. Moreover, because no explicit ethical theory underpins 
Delphi's judgements, human beings cannot analytically determine why Delphi thinks genocide is obligatory. 
Machine learning approaches like Delphi often cannot explain their decisions to a human being and, 
in the extreme case, are black box algorithms. This reduces human trust in a machine's controversial 
ethical judgements. If a machine prescribes killing one person to save three without justifying this 
decision, acting on this judgement becomes difficult. The high stakes of automated ethics require 
explainability to build trust and catch mistakes.

While automated ethics should draw on philosophical literature, in practice, automating an ethical 
theory is a technical and philosophical challenge. Intuitive computational approaches explored 
previously, such as representing ethics as a constraint satisfaction problem \citep{csp} or reinforcement 
learning algorithm \citep{util1}, fail to capture philosophically plausible ethical theories. For 
example, encoding ethics as a Markov Decision Process assumes that ethical reward can be aggregated 
according to some discounted sum, but many philosophers reject this notion of aggregation \citep{consequentialismsep}. 
Ethical theories are almost always described in natural language, so automated ethics must first 
make ethics precise enough to represent to a computer. Even once ethics is translated from natural 
language to program syntax, the factual background given to the machine, such as the description of 
an ethical dilemma, is equally as important in determining the machine's decisions. Another complication
is that philosophers do not agree on a single ``correct" ethical theory. Even philosophers who
agree that a specific ethical theory, like Kantian ethics, is true, debate the theory's 
details.\footnote{For examples of these debates in the case of Kantian ethics, see Section Joking
and Section Murderer.} Even once reasoning within a 
particular ethical theory is automated, those who disagree with that theory will disagree with the 
system's judgements.

This thesis presents a proof-of-concept implementation of philosophically faithful automated ethics
according to Kantian ethics. I formalize Kant's categorical imperative, or moral rule, as an axiom 
in Carmo and Jones' Dyadic Deontic Logic (DDL), a modal logic designed to reason about 
obligation \citep{CJDDL}. I implement my formalization in Isabelle/HOL, an interactive theorem prover 
that can automatically verify and generate proofs in user-defined logics \citep{isabelle}. Finally, 
I use Isabelle to automatically prove theorems (such as, ``murder is wrong'') in my new logic, 
generating results derived from the categorical imperative. Because my system automates reasoning in 
a logic that represents Kantian ethics, it automates Kantian ethical reasoning. Once equipped with 
minimal factual background, it can classify actions as prohibited, permissible or obligatory. I 
make the following contributions:%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
\begin{enumerate}
\item In Section ??, I make a philosophical argument for why Kantian ethics is the most natural of the three major
ethical traditions (deontology, virtue ethics, utilitarianism) to formalize.

\item In Section ??, I present a formalization of the practical contradiction interpretation of the 
Formula of Universal Law in Dyadic Deontic Logic. I implement this formalization in the Isabelle/HOL
theorem prover. My implementation includes axioms and definitions such that my system, when given an appropriately
represented input, can prove that the input is permissible, obligatory, or prohibited. It can also return
a list of facts used in the proof and, in some cases, an Isar-style human readable proof.

\item In Sections ?? and ?, I demonstrate my system's power and flexibility by 
using it to produce nuanced answers to two well-known Kantian ethical dilemmas. I show that, because 
my system draws on definitions of Kantian ethics presented in philosophical literature, it is able 
to perform sophisticated moral reasoning.

\item In Section ??, I present a testing framework that can generally evaluate how faithful an implementation 
of automated Kantian ethics is. My framework includes meta-ethical tests and application tests inspired by philosophical
literature. My testing framework shows that my formalization substantially improves on prior work and can 
be generalized to any implementation of automated Kantian ethics.

\item In Section ??, I present new ethical insights discovered using my system and argue that
computational methods like the one presented in this paper can help philosophers address ethical problems.
Not only can my system help machines reason about ethics, it can also help philosophers make philosophical
progress.
\end{enumerate}%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
I present a faithful implementation of automated Kantian ethics, a testing framework to evaluate how 
well my implementation coheres with expected properties of Kantian ethics (derived from philosophical 
literature), and examples in which my system performs sophisticated moral reasoning. My system consists 
of a logic in which I formalize an ethical theory and an implementation of this formalization in an 
interactive theorem prover.

I choose to formalize Kant's moral rule in Carmo and Jones' Dyadic Deontic Logic (DDL) \citep{CJDDL}. Deontic 
logic is a modal logic that can express obligation, or morally binding requirements. Traditional modal 
logics include the necessitation operator, denoted as $\Box$. In modal logic using the Kripke semantics, 
$\Box p$ is true at world $w$ if $p$ is true at all worlds that neighbor $w$ \citep{cresswell}. Modal 
logics  also contain the possibility operator $\diamond$, where $\diamond \, p \iff \neg (\Box (\neg p))$ 
and operators of propositional logic like $\neg, \wedge, \vee, \rightarrow$. I use DDL, in which
the dyadic obligation operator $O\{A \vert B\}$ to represent the sentence ``A is obligated in the context B.'' 
The introduction of context allows DDL to reason about violations of duty. DDL is both deontic and modal, 
so sentences like $O\{A \vert B\}$ are terms that can be true or false at a world. For example, the 
sentence $O \{ \text{steal} \vert \text{when rich}\}$ is true at a world if stealing when rich is 
obligated at that particular world.

I automate Kantian ethics because it is the most natural to formalize, as I argue in Section WhyKant. 
Kant presents three versions of a single moral rule, known as the categorical imperative, from which 
all moral judgements can be derived. I implement a version of this rule called the Formula of Universal 
Law (FUL), which states that people should only act on those principles that can be acted on by all 
people without contradiction. For example, in a world where everyone falsely promises to repay a loan, 
lenders will no longer believe these promises and will stop offering loans. Therefore, not everyone 
can simultaneously falsely promise to repay a loan, so the FUL thus prohibits this act.

Prior work by Benzmüller, Farjami, and Parent \citep{logikey, BFP} implements DDL in Isabelle/HOL and 
I add the Formula of Universal Law as an axiom on top of their library. The resulting Isabelle theory 
can automatically or semi-automatically generate proofs in a new logic that has the categorical 
imperative as an axiom. Because proofs in this logic are derived from the categorical imperative, 
they judge actions as obligated, prohibited, or permissible. Moreover, because interactive 
theorem provers are designed to be interpretable, my system is explainable. Isabelle can list 
the axioms and facts it used to generate an ethical judgement, and, in some cases, construct 
human-readable proofs. In Sections Joking and Murderer, I use my system to arrive at 
sophisticated solutions to two ethical dilemmas often used in critiques of Kantian ethics. Because 
my system is faithful to philosophical literature, it is able to provide nuanced answers to these paradoxes.

In addition to presenting the above logic and implementation, I also contribute a testing framework 
that evaluates how well my formalization coheres with philosophical literature. I formalize expected 
properties of Kantian ethics as sentences in my logic, such as the property that obligations cannot 
contradict each other. I represent each of these properties as a sentence in my logic that my system 
should be able to prove or refute. I run the tests by using Isabelle to automatically find proofs or 
countermodels for the test statements. For example, my implementation passes the contradictory 
obligations test because it is able to prove the sentence $\neg (O\{A|B\} \wedge O\{\neg A | B\})$. 
I find that my system outperforms raw DDL and Moshe Kroy's prior attempt at formalizing Kantian ethics 
in deontic logic \citep{kroy}.

As it stands, my implementation can evaluate the moral status of sentences represented in my logic. 
Given an appropriate input, my project returns a value indicating if the action is obligatory 
(its negation violates the FUL), permissible (consistent with the FUL), or prohibited (violates the FUL) 
by proving or refuting a theorem in my logic.

A machine that can evaluate the moral status of a maxim can not only help machines better reason about ethics, 
but it can also help philosophers 
better study philosophy. I argue for ``computational ethics," or the use of computational tools to 
make philosophical progress. To this end, I present a philosophical insight about which kinds of
maxims are appropriate for ethical consideration that I discovered using my system. 
The process of building and interacting with a computer that can reason about ethics helped me, a 
human philosopher, arrive at a philosophical conclusion that has implications for practical
reason and philosophy of doubt. Thus, my system can be used in two distinct ways. First, to help
automated agents navigate the world, which I will refer to as automated ethics or machine ethics interchangeably. Second, 
to help human philosophers reason about philosophy, which I call computational ethics.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/thesis_1_intro.thy%:%
%:%24=6%:%
%:%36=9%:%
%:%37=10%:%
%:%38=11%:%
%:%39=12%:%
%:%40=13%:%
%:%41=14%:%
%:%42=15%:%
%:%43=16%:%
%:%44=17%:%
%:%45=18%:%
%:%46=19%:%
%:%47=20%:%
%:%48=21%:%
%:%49=22%:%
%:%50=23%:%
%:%51=24%:%
%:%52=25%:%
%:%53=26%:%
%:%54=27%:%
%:%55=28%:%
%:%56=29%:%
%:%57=30%:%
%:%58=31%:%
%:%59=32%:%
%:%60=33%:%
%:%61=34%:%
%:%62=35%:%
%:%63=36%:%
%:%64=37%:%
%:%65=38%:%
%:%66=39%:%
%:%67=40%:%
%:%68=41%:%
%:%69=42%:%
%:%70=43%:%
%:%71=44%:%
%:%72=45%:%
%:%73=46%:%
%:%74=47%:%
%:%75=48%:%
%:%76=49%:%
%:%77=50%:%
%:%78=51%:%
%:%79=52%:%
%:%80=53%:%
%:%81=54%:%
%:%82=55%:%
%:%83=56%:%
%:%84=57%:%
%:%85=58%:%
%:%86=59%:%
%:%87=60%:%
%:%88=61%:%
%:%89=62%:%
%:%90=63%:%
%:%91=64%:%
%:%92=65%:%
%:%93=66%:%
%:%94=67%:%
%:%95=68%:%
%:%96=69%:%
%:%97=70%:%
%:%98=71%:%
%:%99=72%:%
%:%100=73%:%
%:%101=74%:%
%:%102=75%:%
%:%103=76%:%
%:%104=77%:%
%:%108=80%:%
%:%109=81%:%
%:%110=82%:%
%:%111=83%:%
%:%112=84%:%
%:%113=85%:%
%:%114=86%:%
%:%115=87%:%
%:%116=88%:%
%:%117=89%:%
%:%118=90%:%
%:%119=91%:%
%:%120=92%:%
%:%121=93%:%
%:%122=94%:%
%:%123=95%:%
%:%124=96%:%
%:%125=97%:%
%:%126=98%:%
%:%127=99%:%
%:%128=100%:%
%:%129=101%:%
%:%130=102%:%
%:%131=103%:%
%:%132=104%:%
%:%136=106%:%
%:%137=107%:%
%:%138=108%:%
%:%139=109%:%
%:%140=110%:%
%:%141=111%:%
%:%142=112%:%
%:%143=113%:%
%:%144=114%:%
%:%145=115%:%
%:%146=116%:%
%:%147=117%:%
%:%148=118%:%
%:%149=119%:%
%:%150=120%:%
%:%151=121%:%
%:%152=122%:%
%:%153=123%:%
%:%154=124%:%
%:%155=125%:%
%:%156=126%:%
%:%157=127%:%
%:%158=128%:%
%:%159=129%:%
%:%160=130%:%
%:%161=131%:%
%:%162=132%:%
%:%163=133%:%
%:%164=134%:%
%:%165=135%:%
%:%166=136%:%
%:%167=137%:%
%:%168=138%:%
%:%169=139%:%
%:%170=140%:%
%:%171=141%:%
%:%172=142%:%
%:%173=143%:%
%:%174=144%:%
%:%175=145%:%
%:%176=146%:%
%:%177=147%:%
%:%178=148%:%
%:%179=149%:%
%:%180=150%:%
%:%181=151%:%
%:%182=152%:%
%:%183=153%:%
%:%184=154%:%
%:%185=155%:%
%:%186=156%:%
%:%187=157%:%
%:%188=158%:%
%:%189=159%:%
%:%190=160%:%
%:%191=161%:%
%:%192=162%:%
%:%193=163%:%
%:%194=164%:%
%:%195=165%:%
%:%196=166%:%
%:%197=167%:%

### 2022-02-04 paper/output/document/upshot.tex
compiled version
abstract and intro

--- 2021-11-07 paper/output/document/upshot.tex
@@
 \begin{isamarkuptext}%
-I argue that computational ethics should be useful for and interesting to philosophers for two 
+TESTESTESTI argue that computational ethics should be useful for and interesting to philosophers for two 
 reasons. First, it could serve as the basis for AI agents with the capacity for philosophically sophisticated 
@@
 
-The first contribution of computational ethics is precision. Much of analytic philosophy involves 
+The first contribution of computational ethics is precision \footnote{TODO: this article discusses 
+benefits of precision: bookmarked}. Much of analytic philosophy involves 
 making a particular concept precise. Thought experiments, arguments, counterexamples, and examples 

### 2022-02-05 paper/output/document/thesis_0_abstract.tex
made intro and abstract pretty

@@
 contexts like healthcare, policing, and driving. These decisions are inevitably ethically tinged, 
-but most AI agents navigating the world today have no notion of ethics.
+but most AI agents navigating the world today are not explicitly guided by ethics.
 Warnings from regulators, philosophers, and computer scientists about the 
 dangers of unethical artificial intelligence, from science-fiction killer robots to criminal
-sentencing algorithms prejudiced against people of color, have spurred interest automated ethics, or the development 
-of machines that can perform ethical reasoning. Previous work in automated ethics rarely
-engages with existing philosophical literature. Given that ethics is the study of how to navigate the world,
-automated ethics should look to philosophical literature to guide the development of AI agents that can
-responsibly navigate the world. All decisions are moral decisions, including the ones that AI agents are actively 
-making today. Automated ethics that draws on sophisticated philosophical literature makes the ethical reasoning
-underlying such decisions nuanced, precise and reliable, but faithfully translating complex ethical theories
+sentencing algorithms prejudiced against people of color, have spurred interest in automated ethics, or the development 
+of machines that can perform ethical reasoning. Much prior work in automated ethics approaches the 
+problem from a computational perspective and rarely engages with philosophical literature on ethics, despite
+its clear relevance to the development of AI agents that can
+responsibly navigate the world. All decisions are moral decisions, including those that AI agents are actively 
+making today. If automated ethics draws on sophisticated philosophical literature, it will make the ethical reasoning
+underlying such decisions nuanced, precise and reliable. However, faithfully translating complex ethical theories
 from natural language to the rigid syntax of a computer program poses technical and philosophical 
@@
 my implementation coheres with expected properties of Kantian ethics, as established in the literature. 
-I also use my system to reason about two ethical dilemmas used to criticize Kantian ethics: the case of 
-joking and the example of a murderer knocking on someone's door asking about the location of their
-intended victim. Armed with relatively uncontroversial facts about the world, my system correctly 
-resolves these moral dilemmas.
+I also use my system to reason about two ethical dilemmas used to criticize Kantian ethics: the difference
+between lying and joking and the example of a murderer knocking on your door asking about the location of their
+intended victim.
 
-My system is able to resolve complex ethical dilemmas because it is grounded in philosophical literature.
+Armed with relatively uncontroversial facts about the world, my system is able to correctly
+resolve these moral dilemmas because it is grounded in philosophical literature.
 Moreover, because I automate an explicit ethical theory, the ethical reasoning underlying my system's judgements

### 2022-02-05 paper/output/document/thesis_1_intro.tex
made intro and abstract pretty

@@
 \begin{isamarkuptext}%
-The development of autonomous artificial agents has spurred interest in computers that can perform 
-ethical reasoning, known as automated moral agents. AI agents are making decisions in increasingly 
-consequential contexts, such as medical diagnoses, driving, and criminal sentencing, and therefore 
-must perform ethical reasoning in order to navigate moral dilemmas responsibly. For example, self-driving
+As AI agents become more sophisticated and less dependent on humans, interest begins to mount
+in the development of computers that can perform ethical reasoning, also known as automated moral agents. 
+AI agents are making decisions in increasingly 
+consequential contexts, such as healthcare, driving, and criminal sentencing, and therefore 
+must perform ethical reasoning in order to navigate moral dilemmas. For example, self-driving
 cars may face less extreme versions of the following moral dilemma: an autonomous vehicle approaching 
@@
 not typical of the operation of a self-driving car, every decision that such an AI agent makes, from 
-avoiding congested freeways to carpooling, is morally tinged. Because ethics is the study of navigating 
-the world responsibly, AI agents routinely make moral decisions without explicitly performing ethical
-reasoning. Moreover, artifical agents are making many such moral decisions without
-human supervision, such as hiring algorithms that filter job applicants' resumes, a decision that can
-impact people's livlihoods and often involves implicit prejudices. Machine ethics, also called 
-automated ethics, is the study of how to develop machines that can perform robust, sophisticated ethical reasoning.
+avoiding congested freeways to carpooling, is morally tinged. AI agents routinely make decisions with 
+ethical implications without explicitly performing ethical
+reasoning and, in many cases, without human supervision. For example, the Alleghany Family Screening 
+tool can automatically trigger an investigation into a potential case of child neglect, a decision that 
+can uproot entire families and is known to be biased against poor people of color \citep{eubanks}. 
+Not only are machines making moral decisions without actually performing ethical reasoning, they're 
+doing so without human involvement. This motivates the need for machine ethics (also called automated ethics), 
+or the study of how to develop machines that can perform robust, sophisticated ethical reasoning.
 
 Machine ethicists recognize the need for automated ethics and have made both theoretical 
-(\citep{moralmachineonline} \citep{davenport} \citep{moralmachine} \citep{gabriel}) and practical progress 
-(\citep{logicprogramming} \citep{biology} \citep{delphi} \citep{winfield}) towards automating ethics. 
-However, prior work in machine ethics using popular ethical theories like deontology (\citep{deon2} \citep{deon1}), 
-consequentialism (\citep{util1} \citep{util2} \citep{cloos}), and virtue ethics (\citep{berberich}) rarely 
-engages with philosophical literature and thus misses philosophers' insights. The above example of 
-the malfunctioning self-driving car is an instance of Phillipa Foot's trolley problem \citep{foot}, 
-in which a bystander watching a runaway trolley can pull a lever to kill one instead of three. 
+(\citep{moralmachineonline}, \citep{davenport}, \citep{moralmachine}, \citep{gabriel}) and practical progress 
+(\citep{logicprogramming}, \citep{biology}, \citep{delphi}, \citep{winfield}) towards automating ethics. 
+However, prior work in machine ethics using popular ethical theories like deontology (\citep{deon2}, \citep{deon1}), 
+consequentialism (\citep{util1}, \citep{util2}, \citep{cloos}), and virtue ethics \citep{berberich} rarely 
+engages with philosophical literature and thus misses philosophers' insights. Even the above example of 
+the malfunctioning self-driving car is an instance of Phillipa Foot's trolley problem, 
+in which a bystander watching a runaway trolley can pull a lever to kill one instead of three \citep{foot}. 
 Decades of philosophical debate have developed ethical theories that can offer nuanced and 
 consistent answers to the trolley problem. The trolley problem demonstrates that the moral dilemmas 
-that AI faces are not entirely new, so solutions to these problems should take advantage of philosophical 
+that artifical agents face are not entirely new, so solutions to these problems should take advantage of philosophical 
 progress. The more faithful that automated ethics is to philosophical literature, the more reliable and 
@@
 A lack of engagement with prior philosophical literature also makes automated moral agents less 
-explainable, or interpretable by human observers, as seen in the example of Delphi, which uses deep 
+explainable, or interpretable by human observers. One example of this is Delphi, a language model that uses deep 
 learning to make moral judgements based on a training dataset of ethical decisions made by humans \citep{delphi}. 
-Early versions of Delphi often gave unexpected results, such as declaring that the user should commit 
+Early versions of Delphi gave unexpected results, such as declaring that the user should commit 
 genocide if it makes everyone happy \citep{verge}. Moreover, because no explicit ethical theory underpins 
-Delphi's judgements, human beings cannot analytically determine why Delphi thinks genocide is obligatory. 
+Delphi's judgements, human beings cannot analytically determine why Delphi thinks genocide is obligatory
+or where its reasoning may have gone wrong. 
 Machine learning approaches like Delphi often cannot explain their decisions to a human being and, 
@@
 ethical judgements. If a machine prescribes killing one person to save three without justifying this 
-decision, acting on this judgement becomes difficult. The high stakes of automated ethics require 
-explainability to build trust and catch mistakes.
+decision, it is difficult to trust this judgement enough to act on it or endorse a machine acting on it. 
+The high stakes of automated ethics require explainability to build trust and catch mistakes.
 
@@
 according to some discounted sum, but many philosophers reject this notion of aggregation \citep{consequentialismsep}. 
-Ethical theories are almost always described in natural language, so automated ethics must first 
-make ethics precise enough to represent to a computer. Even once ethics is translated from natural 
+Approaches that begin with an ethical theory, instead of a computational tool, must contend with the 
+fact that ethical theories are almost always described in natural language and must be made
+precise enough to represent to a computer. Even once ethics is translated from natural 
 language to program syntax, the factual background given to the machine, such as the description of 
 an ethical dilemma, is equally as important in determining the machine's decisions. Another complication
-is that philosophers do not agree on a single ``correct" ethical theory. Even philosophers who
+is that philosophers do not agree that on a single choice of ethical theory. Even philosophers who
 agree that a specific ethical theory, like Kantian ethics, is true, debate the theory's 
@@
 
-This thesis presents a proof-of-concept implementation of philosophically faithful automated ethics
-according to Kantian ethics. I formalize Kant's categorical imperative, or moral rule, as an axiom 
+This thesis presents a proof-of-concept implementation of philosophically faithful automated Kantian ethics. 
+I formalize Kant's categorical imperative, or moral rule, as an axiom 
 in Carmo and Jones' Dyadic Deontic Logic (DDL), a modal logic designed to reason about 
@@
 
-\item In Section ??, I present a formalization of the practical contradiction interpretation of the 
+\item In Section ??, I present a formalization of the practical contradiction interpretation of Kant's 
 Formula of Universal Law in Dyadic Deontic Logic. I implement this formalization in the Isabelle/HOL
@@
 
-\item In Sections ?? and ?, I demonstrate my system's power and flexibility by 
+\item In Sections ?? and ??, I demonstrate my system's power and flexibility by 
 using it to produce nuanced answers to two well-known Kantian ethical dilemmas. I show that, because 
@@
 
-\item In Section ??, I present a testing framework that can generally evaluate how faithful an implementation 
+\item In Section ??, I present a testing framework that can evaluate how faithful an implementation 
 of automated Kantian ethics is. My framework includes meta-ethical tests and application tests inspired by philosophical
-literature. My testing framework shows that my formalization substantially improves on prior work and can 
-be generalized to any implementation of automated Kantian ethics.
+literature. This testing framework shows that my formalization substantially improves on prior work and can 
+be generalized to evaluate any implementation of automated Kantian ethics.
 
@@
 computational methods like the one presented in this paper can help philosophers address ethical problems.
-Not only can my system help machines reason about ethics, it can also help philosophers make philosophical
+Not only can my system help machines reason about ethics, but it can also help philosophers make philosophical
 progress.
@@
 \begin{isamarkuptext}%
-I present a faithful implementation of automated Kantian ethics, a testing framework to evaluate how 
-well my implementation coheres with expected properties of Kantian ethics (derived from philosophical 
-literature), and examples in which my system performs sophisticated moral reasoning. My system consists 
-of a logic in which I formalize an ethical theory and an implementation of this formalization in an 
-interactive theorem prover.
-
 I choose to formalize Kant's moral rule in Carmo and Jones' Dyadic Deontic Logic (DDL) \citep{CJDDL}. Deontic 
@@
 and operators of propositional logic like $\neg, \wedge, \vee, \rightarrow$. I use DDL, in which
-the dyadic obligation operator $O\{A \vert B\}$ to represent the sentence ``A is obligated in the context B.'' 
-The introduction of context allows DDL to reason about violations of duty. DDL is both deontic and modal, 
+the dyadic obligation operator $O\{A \vert B\}$ represents the sentence ``A is obligated in the context B.'' 
+The introduction of context allows DDL to express more nuanced reasoning. DDL is both deontic and modal, 
 so sentences like $O\{A \vert B\}$ are terms that can be true or false at a world. For example, the 
@@
 obligations test because it is able to prove the sentence $\neg (O\{A|B\} \wedge O\{\neg A | B\})$. 
-I find that my system outperforms raw DDL and Moshe Kroy's prior attempt at formalizing Kantian ethics 
-in deontic logic \citep{kroy}.
+I find that my system outperforms the control group of raw DDL, without any moral axioms added, and 
+Moshe Kroy's prior attempt at formalizing Kantian ethics in deontic logic \citep{kroy}.
 
@@
 better study philosophy. I argue for ``computational ethics," or the use of computational tools to 
-make philosophical progress. To this end, I present a philosophical insight about which kinds of
-maxims are appropriate for ethical consideration that I discovered using my system. 
-The process of building and interacting with a computer that can reason about ethics helped me, a 
-human philosopher, arrive at a philosophical conclusion that has implications for practical
+make philosophical progress. I demonstrate the potential of computational ethics by presenting a 
+philosophical insight about which kinds of maxims are appropriate for ethical consideration that I 
+discovered using my system. The process of building and interacting with a computer that can reason 
+about ethics helped me, a human philosopher, arrive at a philosophical conclusion that has implications for practical
 reason and philosophy of doubt. Thus, my system can be used in two distinct ways. First, to help
@@
 %:%24=6%:%
-%:%36=9%:%
-%:%37=10%:%
-%:%38=11%:%
-%:%39=12%:%
-%:%40=13%:%
-%:%41=14%:%
-%:%42=15%:%
-%:%43=16%:%
-%:%44=17%:%
-%:%45=18%:%
-%:%46=19%:%
-%:%47=20%:%
-%:%48=21%:%
-%:%49=22%:%
-%:%50=23%:%
-%:%51=24%:%
-%:%52=25%:%
-%:%53=26%:%
-%:%54=27%:%
-%:%55=28%:%
-%:%56=29%:%
-%:%57=30%:%
-%:%58=31%:%
-%:%59=32%:%
-%:%60=33%:%
-%:%61=34%:%
-%:%62=35%:%
-%:%63=36%:%
-%:%64=37%:%
-%:%65=38%:%
-%:%66=39%:%
-%:%67=40%:%
-%:%68=41%:%
-%:%69=42%:%
-%:%70=43%:%
-%:%71=44%:%
-%:%72=45%:%
-%:%73=46%:%
-%:%74=47%:%
-%:%75=48%:%
-%:%76=49%:%
-%:%77=50%:%
-%:%78=51%:%
-%:%79=52%:%
-%:%80=53%:%
-%:%81=54%:%
-%:%82=55%:%
-%:%83=56%:%
-%:%84=57%:%
-%:%85=58%:%
-%:%86=59%:%
-%:%87=60%:%
-%:%88=61%:%
-%:%89=62%:%
-%:%90=63%:%
-%:%91=64%:%
-%:%92=65%:%
-%:%93=66%:%
-%:%94=67%:%
-%:%95=68%:%
-%:%96=69%:%
-%:%97=70%:%
-%:%98=71%:%
-%:%99=72%:%
-%:%100=73%:%
-%:%101=74%:%
-%:%102=75%:%
-%:%103=76%:%
-%:%104=77%:%
+%:%36=8%:%
+%:%37=9%:%
+%:%38=10%:%
+%:%39=11%:%
+%:%40=12%:%
+%:%41=13%:%
+%:%42=14%:%
+%:%43=15%:%
+%:%44=16%:%
+%:%45=17%:%
+%:%46=18%:%
+%:%47=19%:%
+%:%48=20%:%
+%:%49=21%:%
+%:%50=22%:%
+%:%51=23%:%
+%:%52=24%:%
+%:%53=25%:%
+%:%54=26%:%
+%:%55=27%:%
+%:%56=28%:%
+%:%57=29%:%
+%:%58=30%:%
+%:%59=31%:%
+%:%60=32%:%
+%:%61=33%:%
+%:%62=34%:%
+%:%63=35%:%
+%:%64=36%:%
+%:%65=37%:%
+%:%66=38%:%
+%:%67=39%:%
+%:%68=40%:%
+%:%69=41%:%
+%:%70=42%:%
+%:%71=43%:%
+%:%72=44%:%
+%:%73=45%:%
+%:%74=46%:%
+%:%75=47%:%
+%:%76=48%:%
+%:%77=49%:%
+%:%78=50%:%
+%:%79=51%:%
+%:%80=52%:%
+%:%81=53%:%
+%:%82=54%:%
+%:%83=55%:%
+%:%84=56%:%
+%:%85=57%:%
+%:%86=58%:%
+%:%87=59%:%
+%:%88=60%:%
+%:%89=61%:%
+%:%90=62%:%
+%:%91=63%:%
+%:%92=64%:%
+%:%93=65%:%
+%:%94=66%:%
+%:%95=67%:%
+%:%96=68%:%
+%:%97=69%:%
+%:%98=70%:%
+%:%99=71%:%
+%:%100=72%:%
+%:%101=73%:%
+%:%102=74%:%
+%:%103=75%:%
+%:%104=76%:%
+%:%105=77%:%
+%:%106=78%:%
+%:%107=79%:%
 %:%108=80%:%
 %:%109=81%:%
-%:%110=82%:%
-%:%111=83%:%
-%:%112=84%:%
-%:%113=85%:%
-%:%114=86%:%
-%:%115=87%:%
-%:%116=88%:%
-%:%117=89%:%
-%:%118=90%:%
-%:%119=91%:%
-%:%120=92%:%
-%:%121=93%:%
-%:%122=94%:%
-%:%123=95%:%
-%:%124=96%:%
-%:%125=97%:%
-%:%126=98%:%
-%:%127=99%:%
-%:%128=100%:%
-%:%129=101%:%
-%:%130=102%:%
-%:%131=103%:%
-%:%132=104%:%
-%:%136=106%:%
-%:%137=107%:%
-%:%138=108%:%
-%:%139=109%:%
-%:%140=110%:%
-%:%141=111%:%
-%:%142=112%:%
-%:%143=113%:%
-%:%144=114%:%
-%:%145=115%:%
-%:%146=116%:%
-%:%147=117%:%
-%:%148=118%:%
-%:%149=119%:%
-%:%150=120%:%
-%:%151=121%:%
-%:%152=122%:%
-%:%153=123%:%
-%:%154=124%:%
-%:%155=125%:%
-%:%156=126%:%
-%:%157=127%:%
-%:%158=128%:%
-%:%159=129%:%
-%:%160=130%:%
-%:%161=131%:%
-%:%162=132%:%
-%:%163=133%:%
-%:%164=134%:%
-%:%165=135%:%
-%:%166=136%:%
-%:%167=137%:%
-%:%168=138%:%
-%:%169=139%:%
-%:%170=140%:%
-%:%171=141%:%
-%:%172=142%:%
-%:%173=143%:%
-%:%174=144%:%
-%:%175=145%:%
-%:%176=146%:%
-%:%177=147%:%
-%:%178=148%:%
-%:%179=149%:%
-%:%180=150%:%
-%:%181=151%:%
-%:%182=152%:%
-%:%183=153%:%
-%:%184=154%:%
-%:%185=155%:%
-%:%186=156%:%
-%:%187=157%:%
-%:%188=158%:%
-%:%189=159%:%
-%:%190=160%:%
-%:%191=161%:%
-%:%192=162%:%
-%:%193=163%:%
-%:%194=164%:%
-%:%195=165%:%
-%:%196=166%:%
-%:%197=167%:%
+%:%113=84%:%
+%:%114=85%:%
+%:%115=86%:%
+%:%116=87%:%
+%:%117=88%:%
+%:%118=89%:%
+%:%119=90%:%
+%:%120=91%:%
+%:%121=92%:%
+%:%122=93%:%
+%:%123=94%:%
+%:%124=95%:%
+%:%125=96%:%
+%:%126=97%:%
+%:%127=98%:%
+%:%128=99%:%
+%:%129=100%:%
+%:%130=101%:%
+%:%131=102%:%
+%:%132=103%:%
+%:%133=104%:%
+%:%134=105%:%
+%:%135=106%:%
+%:%136=107%:%
+%:%137=108%:%
+%:%141=112%:%
+%:%142=113%:%
+%:%143=114%:%
+%:%144=115%:%
+%:%145=116%:%
+%:%146=117%:%
+%:%147=118%:%
+%:%148=119%:%
+%:%149=120%:%
+%:%150=121%:%
+%:%151=122%:%
+%:%152=123%:%
+%:%153=124%:%
+%:%154=125%:%
+%:%155=126%:%
+%:%156=127%:%
+%:%157=128%:%
+%:%158=129%:%
+%:%159=130%:%
+%:%160=131%:%
+%:%161=132%:%
+%:%162=133%:%
+%:%163=134%:%
+%:%164=135%:%
+%:%165=136%:%
+%:%166=137%:%
+%:%167=138%:%
+%:%168=139%:%
+%:%169=140%:%
+%:%170=141%:%
+%:%171=142%:%
+%:%172=143%:%
+%:%173=144%:%
+%:%174=145%:%
+%:%175=146%:%
+%:%176=147%:%
+%:%177=148%:%
+%:%178=149%:%
+%:%179=150%:%
+%:%180=151%:%
+%:%181=152%:%
+%:%182=153%:%
+%:%183=154%:%
+%:%184=155%:%
+%:%185=156%:%
+%:%186=157%:%
+%:%187=158%:%
+%:%188=159%:%
+%:%189=160%:%
+%:%190=161%:%
+%:%191=162%:%
+%:%192=163%:%
+%:%193=164%:%
+%:%194=165%:%
+%:%195=166%:%
+%:%196=167%:%

### 2022-02-06 paper/output/document/thesis_2_methods.tex
compiled methods, need to edit next

%
\begin{isabellebody}%
\setisabellecontext{thesis{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}methods}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{System Components \label{methods}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
My system consists of three major components: an ethical theory (Kantian ethics), a logic in which
I formalize this ethical theory (Dyadic Deontic Logic), and an interactive theorem prover in which I 
implement the formalized ethical theory (Isabelle/HOL). In this section, I describe these components, 
present the philosophical, logic, and computational background that undergirds my system, and explain
the consequences of each of the three choices I make.

These specific components determine the features
and limitations of the specific implementation of automated ethics that I present, but other choices of 
components, such as another ethical theory, a different logic, or a different theorem prover could be 
made. Given that my system is a proof-of-concept, I choose system components that are natural and 
intuitively fit together, but other choice could also be valid and perhaps even superior.

I do not claim
that I have chosen the best ethical theory or the best logic or the best interactive theorem prover, 
and flaws with these components merely demonstrate that my specific choices were incorrect, but do not 
indict logic-programming-based automated ethics as I implement it in this thesis. My thesis seeks to 
both present a specific implementation of automated ethics but also to argue for a particular approach 
to automating ethical reasoning and these choices are relevant to the former goal but not to the latter.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Kantian Ethics \label{whykant}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In this thesis, I automate Kantian ethics. In 2006, Powers posited that deontological theories are 
attractive candidates for automation because rules are generally computationally tractable \cite[1]{powers}. 
Intuitively, algorithms are rules or procedures for problem solving and deontology offers one such 
procedure for the problem of making ethical judgements. I will make this intuition precise by
arguing that deontological ethics is natural to formalize because rules generally require little additional
data about the world and are usually easy to represent to a computer. All ethical traditions have debates that an 
automated ethical system will need to take a stance on, but these debates are less frequent and controversial
for deontological ethics than for consequentialism and virtue ethics.

I do not aim to show that deontology is the only tractable theory to automate or
to present a comprehensive overview of all consequentialist or virtue ethical theories. Instead, I 
present a sample of some approaches in each tradition and argue that deontology is more straightforward 
to formalize than these approaches. Future work could and should address the challenges I outline in 
this section. The more ethical theories that computational tools can handle, the more valuable 
computational philosophy becomes both for philosophers and for AI agents. Insofar as my project serves 
as an early proof-of-concept for computational ethics, I choose to automate an ethical theory that 
poses fewer challenges than others.

I first present deontological ethics, then consequentialism, and finally virtue ethics. For each 
tradition, I present a crash course for non-philosophers and then explain some obstacles to automation, 
arguing that these obstacles are weakest in the case of deontology. Finally, I will present the specific 
deontological theory I am automating (Kantian ethics) and will argue that it is comparatively easier
to formalize. I will also outline the specific debates in the literature that my formalization takes
a stance on and potential challenges for formalizing deontology.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Deontological Ethics\label{deontology}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
Deontological ethical theories evaluate actions as permissible, obligatory, or prohibited. The 
deontological tradition argues that an action should not be judged on its consequences, 
but rather on ``its confirmity with a moral norm" \citep{sepdeont}. In other words, deontological theories
define a set of moral norms or rules and evaluate actions using
these rules. Deontologists do not believe that we should maximize the number of times that we 
conform to such rules, but instead that we should never violate any of the moral laws. A wrong
choice is wrong, regardless of its consequences.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
Deontology is immediately an attractive candidate for formalization because computers tend to 
understand rules; programming languages are designed to teach computers algorithms. Deontological
ethical theories give inviolable rules that an automated agent can apply. Moreover, because deontological 
theories focus on
the action itself, they require relatively little data. A deontological moral judgement does not require
as much information about context, consequences, or moral character as the other theories presented later in this
section. All that matters is the action and some limited set of circumstances in which it is performed.
I will later argue that, in the case of the specific deontological ethic that I implement (Kantian ethics), 
the action's representation is space efficient.

Like all ethical traditions, deontology has debates that any implementation of automated deontological
ethics must resolve. Deontologists disagree about whether ethics should focus on agents' actions or 
on the rights of those impacted by an action. Different deontological theories have different conceptions 
of what an action is, from the physical act itself to the agent's mental state at the time of acting 
to the principle upon which the agent acted.

While these debates are open, ``if any philosopher is regarded as central
to deontological moral theories, it is surely Immanuel Kant" \citep{sepdeont}. Out of the three ethical
traditions considered in this section, deontology has the most central representative in the form of 
Kant. Many modern deontologists agree on Kant's ethic but disagree in how to interpret it. In this paper, I will 
formalize Kantian ethics. Deontology's comparatively greater focus on Kant means that the choice of 
Kant as a guiding figure will be less controversial to deontologists than, for example, the choice of Bentham
as the guiding figure of consequentialism. Moreover, at the end of this section, I also argue that 
internal debates in the part of Kantian ethics that I focus on tend to be less controversial than those
in the consequentialist or virtue ethical traditions.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Consequentialism%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
A consequentialist ethical theory is an ethical theory that evaluates an 
action by evaluating its consequences.\footnote{There is long debate about what exactly makes an ethical theory consequentialist \citep{consequentialismsep}. 
For this thesis, I focus on theories that place the moral worth of an act in its the consequences.} For example, 
utilitarianism is a form of consequentialism in which the moral action 
is the action that produces the most good \citep{utilsep}. The focus
on the consequences of action distinguishes consequentialists from deontologists, who derive the moral worth
of an action from the action itself. Some debates in the consequentialist tradition include 
which consequences of an action matter, what exactly constitutes a ``good" consequence, and how we can 
aggregate the consequences of an action over all the individuals involved.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
\noindent \textbf{Which Consequences Matter}%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
Because consequentialism evaluates the state of affairs following an action, this kind of ethical 
reasoning requires more knowledge about the state of the world than deontology. Consequentialism
requires knowledge about some or all consequences following an action. This requires that an automated 
ethical system somehow collect a subset of the infinite consquences of following an action, a difficult, 
if not impossible, task. Moreover, compiling this database of consequences requires 
answering difficult questions about which consequences were actually caused by an action.\footnote
{David Hume argues that many straightforward accounts of causation face difficulties \citep{hume}, 
and philosohpers continue to debate the possiblity of knowing an event's true cause. Kant even argued
that first causes, or noumena, are unknowable by human beings \citep{kantnoumena}.}
Evaluating an effect of an action requires knowledge about the 
state of the world before and after an action and knowledge about the action itself. Consequentialism requires 
knowledge about the situation in which the act is performed and following the act, whereas deontology mostly requires 
knowledge about the act itself. As acts become
more complex and affect more people, the computational time and space required to calculate and store
their consequences increases. Deontology, on the other hand, does not suffer this scaling
challenge because acts that affect 1 person and acts that affect 1 million people share the same
representation.

The challenge of representing the circumstances of action is not unique to consequentialism, but is particularly acute in this case. Kantian ethicists robustly debate which circumstances of an action are ``morally relevant'' when evaluating an action's moral worth.\footnote{Powers 
\citet{powers} identifies this as a challenge for automating Kantian ethics and briefly sketches 
solutions from \citet{constofreason}, \citet{silber}, and \citet{rawlsconstructivism}. For more on 
morally relevant circumstances, see Section WhatIsAMaxim.} Because deontology merely evaluates a 
single action, the surface of this debate is much smaller than the debate about circumstances and 
consequences in a consequentialist system. An automated consequentialist system must make such 
judgements about the act itself, the circumstances in which it is performed, and the circumstances 
following the act. All ethical theories relativize their judgements to the situation in which an act 
is performed, but consequentialism requires far more knowledge about the world than deontology.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
\noindent \textbf{Theory of the Good}%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
An automated consequentialist reasoner must also take a stance on the debate over
what qualifies as a ``good consequence," or what the theory of the good is. For example, hedonists associate
good with the presence of pleasure and the absence of pain, while preference utiliarians believe that good is 
the satisfaction of individuals' desires. Other consequentialists, like Moore, adopt a pluralistic theory of value, under which 
many different kinds of things are good for different reasons \citep{moorepe}.

Most of the above theories of good require that a moral reasoner understand complex features about
individuals' preferences, desires, or sensations in order to evaluate a moral action, making automated
consequentialist ethics difficult. Evaluating a state of affairs requires
judgements about whether a state of affairs actually satisifes the relevant criteria for goodness. 
These judgements are controversian, and any consequentialist decision requires many of 
these judgements for each individual involved. As systems involve more people, making these judgements 
quickly becomes difficult, posing a scaling challenger. Perfect knowledge of tens of thousands of 
people's pleasure or preferences or welfare or rights is impossible. Either a human being 
assigns values to states of affairs, which doesn't scale, or the machine does, 
which requires massive common-sense and increases room for doubting the system's judgements. This is 
a tractable problem, but it is much more difficult than the equivalent deontological task of formulating
and evaluating an action.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
\noindent \textbf{Aggregation}%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
Once an automated consequentialist agent assigns a goodness measurement to each person in a state of affairs, it 
must also calculate an overall goodness measurement for the state of affairs. One approach to assigning
this value is to aggregate each person's individual goodness score into one complete score for a state. 
For example, under a simple welfare model, each person is assigned a welfare score and the total 
score for a state of affairs is the sum of the welfare scores for each involved person.
The more complex the theory of the good, the more difficult this aggregation becomes. For example, 
pluralistic theories struggle to explain how different kinds of value can be compared \citep{consequentialismsep}. 
How do we compare one unit of beauty to one unit of pleasure? Subjective theories of the good, such 
as those focused on the sensation of pleasure or an individual's preferences, present difficulties in 
comparing different people's subjective measures. Resolving this debate requires that the automated reasoner 
choose one specific aggregation algorithm, but those who disagree with this choice will not trust 
the reasoner's moral judgements. Moreover, for complex theories of the good, this aggregation algorithm
may be complex and may require a lot of data.

To solve this problem, some consequentialists reject aggregation entirely and instead prefer wholistic
evaluations of a state of affairs. While this approach no longer requires that a reasoner define an 
aggregation algorithm, the reasoner still needs to calculate a goodness measurement for a state of 
affairs. Whereas before the reasoner could restrict analysis to a single person, the algorithm must now 
evaluate an entire state wholistically. As consequentialists modulate between aggregation 
and wholistic evaluation, they face a tradeoff between the difficulty of aggregation and the complexity 
of goodness measurements for large states of affairs.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
\noindent \textbf{Prior Attempts to Formalize Consequentialism}%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
Because of its intuitive appeal, computer scientists have tried to formalize consequentialism in the past.
These efforts cannot escape the debates outlined above. For example, Abel et al. represent ethics as a
Markov Decision Process (MDP), with reward functions customized to particular ethical dilemmas 
\citep[3]{util1}. While this is a convenient representation, it either leaves unanswered or 
takes implicit stances on the debates above. It assumes that consequences can be aggregated just as 
reward is accumulated in an MDP.\footnote{Generally, reward for an MDP is accumulated according to a 
``discount factor" $\gamma < 1$, such that if $r_i$ is the reward at time $i$, the total reward is $\sum_{i=0}^{\infty}\gamma^i r_i$.} 
It leaves open the question of what the reward function is and thus 
leaves the theory of the good, arguably the defining trait of consequentialism, 
undefined. Similarly, Anderson and Anderson's proposal of a hedonistic act 
utilitarian automated reasoner chooses hedonism\footnote{Recall that hedonism views pleasure as good
and pain as bad.} as the theory of the good \citep[2]{util2}. Again, their proposal assumes that pleasure and pain can be 
given numeric values and that these values can be aggregated with a simple sum, taking an implicit
stance on the aggregation question. Other attempts to automate consequentialist ethics will suffer 
similar problems because, at some point, a useful automated consequentialist moral agent will need 
to resolve the above debates.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Virtue Ethics\label{virtueethics}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
Virtue ethics places the virtues, or traits that constitute a good moral character and make 
their possessor good, at the center \cite{vesep}. For example, Aristotle describes virtues as the 
traits that enable human flourishing. Just as consequentialists define ``good'' consequences, virtue 
ethicists present a list of virtues. Such theories vary from Aristotle's virtues of courage and 
temperance \citet{aristotle} to the Buddhist virtue of equanimity \citet{mcrae}. An automated virtue 
ethical agent will need to commit to a particular theory of the virtues, a controversial choice. 
Virtue ethicists robustly debate which traits qualify as virtues, what each virtue actually means, and 
what kinds of feelings or attitudes must accompany virtuous action.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
Another difficulty with automating virtue ethics is that the unit of evaluation for a virtue ethical
theory is often a person's entire moral character. While deontologists evaluate the act itself and utilitarians
evaluate the consequences of an act, virtue ethicists evaluate the actor's moral character and their 
disposition towards the act. Virtues are character traits and evaluating an action as virtuous or 
not requires understanding the agent's character and disposition while acting. If states of affairs
require complex representations, an agent's ethical character and disposition are even more difficult
to represent to a computer. Consequentialism posed a data-collection problem in evaluating and representing states
of affairs, but virtue ethics poses a conceptual problem about the formal nature of moral character.
Formalizing the concept of character appears to require significant philosophical and computational
progress, whereas deontology immediately presents a formal rule to implement.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
\noindent \textbf{Prior Work in Machine Learning and Virtue Ethics}%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
One potential appeal of virtue ethics is that many virtue ethical theories involve some form of 
moral habit, which seems to be amenable to a machine learning approach. Artistotle, for example, argued 
that cultivating virtuous action requires making such action habitual through moral education \citep{aristotle}. This
imply that ethical behavior can be learned from some dataset of virtuous acts, either those 
prescribed by a moral teacher or those that a virtuous ideal agent would undertake. Indeed, these 
theories seem to point towards a machine learning approach to computational ethics, in which ethics is 
learned from a dataset of acts tagged as virtuous or not virtuous.

Just as prior work in consequentialism takes implicit or explicit stances on debates in consequentialist
literature, so does work in machine learning-based virtue ethics. For example, the training 
dataset with acts labelled as virtuous or not virtuous will contain an implicit view on what the virtues
are and how certain acts impact an agent's moral character. Because there is no canonical list of virtues
that virtue ethicists accept, this implicit view will likely be controversial.

Machine learning approaches like the Delphi system \citep{delphi} mentioned in \ref{intro} also may suffer explanability 
problems that my logic-programming, theorem-prover
approach does not face. Many machine learning algorithms cannot sufficiently explain their 
decisions to a human being, and often find patterns or correlations in datasets that don't actually 
cohere with the trends and causes that a human being would identify \citep{puiutta}. While there is significant activity 
and progress in explainable machine learning, interactive theorem provers are designed to be explainable 
at the outset. Indeed, Isabelle can show the axioms and lemmas it used in constructing a proof, 
allowing a human being to reconstruct the proof independently if they wish. This is not an 
intractable problem for machine learning approaches to computational ethics, but is one reason to 
prefer logical approaches.\footnote{This argument about explanability is in the context of virtue ethics and 
machine learning. It also applies to a broader class of work in automated ethics 
that uses ``bottom-up" approaches, in which a system learns moral judgements from prior judgements. 
I will extend this argument to general bottom-up approaches in Section Related Work.}%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Kantian Ethics \label{kantianethics}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In this paper I focus on Kantian ethics, a specific branch of deontology. Kant's theory is centered 
on practical reason, which is the kind of reason that we 
use to decide what to do. In \emph{The Groundwork of the Metaphysics of Morals}, Kant's most influential 
text on ethics, he explains that rational beings are unique because we can act ``in accordance with 
the representations of laws" \citep[4:412]{groundwork}. In contrast, a ball thrown into the air acts 
according to the laws of physics. It cannot ask itself, ``Should I fall back to the ground?" 
It simply falls. A rational being, on the other hand, can ask, ``Should I act on this reason?" 
As Korsgaard describes it, when choosing which desire to act on, ``it is as if there is something over 
and above all of your desires, something which is you, and which chooses which desire to act on" \citep[100]{sources}. 
Rational beings are set apart by this reflective capacity. A rational being's behavior is purposive and 
their actions are guided by practical reason. They have reasons for acting, even when these reasons may be 
opaque to them. This operation of practical reason is what Kant calls the will.

The will operates by adopting, or willing, maxims, which are its perceived reasons for acting. Kant defines a maxim as 
the ``subjective principle of willing," or the reason that the will \emph{subjectively} gives 
to itself for acting \citep[16 footnote 1]{groundwork}. There is debate about what exactly must be 
included in a maxim, but many philosophers agree that a maxim consists of some combination of circumstances, 
act, and goal.\footnote{For more discussion of the definition of a maxim, see Section What Is a Maxim}
One example of a maxim is ``When I am hungry, I will eat a doughnut in order to satisfy my sweet tooth." 
When an agent wills this maxim, they decide to act on it. They commit themselves to the end in the maxim 
(e.g. satisfying your sweet tooth). They represent their action, to themselves, as following the 
principle given by this maxim. Because a maxim captures an agent's principle of action, Kant evaluates
maxims as obligatory, prohibited, or permissible. He argues that certain maxims have a form or logical structure 
that requires any rational agent to will them, and these maxims are obligatory.

The form of an obligatory maxim is given by the categorical imperative. 
An imperative is a command, such as ``Close the door" or ``Eat the doughnut in order to satisfy your 
sweet tooth." An imperative is categorical if it holds unconditionally for all rational agents under all 
circumstances. Kant argues that the moral law must be a categorical imperative, for otherwise it would 
not have the force that makes it a moral law \citep[5]{groundwork}. In order for an imperative to be 
categorical, it must be derived from the will's authority over itself. Our wills are autonomous, so 
the only thing that can have unconditional authority over a rational will is 
the rational will itself. In Velleman's version of this argument, he claims that no one else can tell you what 
to do because you can always ask why you 
should obey their authority. The only authority that you cannot question is the authority of your own 
practical reason. To question this authority is to demand a reason for acting for reasons, which 
concedes the authority of reason itself \citep[23]{velleman}. Therefore, the only possible candidates 
for the categorical imperative are those rules that are required of the will because it is a will. 
The categorical imperative must be a property of practical reason itself.

Armed with this understanding of practical reason, Kant presents the categorical 
imperative. He presents three ``formulations" or versions of the categorical imperative and goes on to 
argue that all three formulations are equivalent. In this project, I focus on the first formulation,
the Formula of Universal Law.\footnote{For more on this 
choice, see Section Why FUL.}

The first formulation of the categorical imperative is the
Formula of Universal Law (FUL), which reads, ``act only according to that maxim through which you can 
at the same time will that it become a universal law" \cite[34]{groundwork}. This formulation
generates the universalizability test, which tests the moral value of a maxim by 
imagining a world in which it becomes a universal law and attempting to will the maxim in that world.
If there is a contradiction in willing the maxim in a world in which everyone universally wills the maxim,
the maxim is prohibited. 
Velleman presents a concise argument for the FUL. He argues that reason is universally shared among reasoners. For 
example, all reasoners have equal access to the arithmetic logic that shows that ``2+2=4" \cite[29]{velleman}. The chain of 
reasoning that makes this statement true is not specific to any person, but is universal across people. 
Therefore, if I have sufficient reason to will a maxim, so does every other rational agent. There is 
nothing special about the operation of my practical reason that other reasoners don't have access to. 
Practical reason is shared, so in adopting a maxim, I implicitly state that all reasoners
across time also have reason to adopt that maxim. Therefore, because I act on reasons, I must obey the 
FUL. Notice that this fulfills the above criterion for a categorical imperative: the FUL is derived from 
a property of practical reason itself and thus derives authority from the will's authority over itself, 
as opposed to some external authority.

The above is not meant to serve as a full defense or articulation of Kant's ethical theory, as that is outside the scope
of this thesis. Instead, I briefly reconstruct a sketch of Kant's ethical theory in the hopes 
of offering context for the implementation of the FUL I present later in the thesis. Additionally, understanding 
the structure of Kant's theory also reveals why it is an ideal candidate 
for formalization.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
\noindent \textbf{Ease of Automation}%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
Kantian ethics is an especially candidate for formalization because the categorical imperative, particularly the FUL, 
is a property of reason related to the form or structure of a maxim, or a formal principle of practical
reason. It does not require any situational knowledge or contingent beyond the circumstances included
in the maxim itself and thus requires far less contingent facts than other ethical theories.
Instead, it is purely a property of the proposed principle for action. This formalism makes Kantian
ethics an attractive candidate for formalization. While other ethical theories often rely on many facts about 
the world or the actor, Kantian ethics simply relies on the form of a given maxim. A computer evaluating 
a maxim doesn't require any knowledge about the world beyond what is contained in a maxim. A maxim 
is the only input that the computer needs to make a moral judgement. Automating 
Kantian ethics merely requires making the notion of a maxim precise and representing it to the computer. 
This distinguishes Kantian ethics from consequentialism and virtue ethics, which, as I argued above, 
require far more knowledge about the world or the agent to reach a moral decision.

Not only does evaluating Kantian ethics focus on a maxim, a maxim itself is an object
with a thin representation for a computer, as compares to more complex objects like states of 
affairs or moral character. Later in my project, I argue that a maxim can be represented simply as 
a tuple of circumstances, act, and goal.\footnote{For more, see Section What is a Maxim?} This representation
is simple and efficient, especially when compared to the representation of a causal chain or a state of 
affairs or moral character. A maxim is a principle with a well-defined form, so representing a maxim
to the computer merely requires capturing this form. This property not only reduces the computational complexity
(in terms of time and space) of representing a maxim, it also make the system easier for human reasoners
to interact with. A person crafting an input to a Kantian automated agent needs to reason about relatively
simple units of evaluation, as opposed to the more complex features that consequentialism and virtue
ethics require. I will make the comparision to consequentialism and virtue ethics explicit below.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
\textbf{Difficulties in Automation}%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
My choices to interpret maxims and the Formula of Universal Law in a particular way represent debates
in Kantian ethics over the meanings of these terms that I take a stance on. Another debate in Kantian 
ethics is the role of ``common-sense" reasoning. Kantian ethics requires common-sense reasoning to 
determine which circumstances are ``morally relevant" in the formulation of a maxim. Many misunderstandings
in Kantian ethics are due to badly formulated maxims, so this question is important for an ethical 
reasoner to answer. My system does not need to answer this question because I assume a well-formed
maxim as input and apply the categorical imperative to this input, but if my system were ever to be used
in a faully automated agent, answering this question would require significant computational and philosophical
work. For more, see Section AI Ethics.

Common-sense reasoning is also relevant in applying the universalizability test itself. Consider an example
maxim tested using the Formula of Universal Law: ``When broke, I will falsely promise to repay a loan
to get some quick cash." This maxim fails the universalizability test because in a world where everyone
falsely promises to repay loans, no one will believe promises anymore, so the maxim will no longer serve
its intended purpose (getting some quick cash). Making this judgement requires understanding enough about
the system of promising to realize that it breaks down if everyone abuses it in this manner. This is a
kind of common sense reasoning that an automated Kantian agent would need. This need is not unique to 
Kantian ethics; consequentialists agents need this kind of common sense to determine the consequences of 
an action and virtue ethical agents need this kind of common sense to determine which virtues an action
reflects. Making any ethical judgement requires relatively robust conceptions of the action or situation
at hand, falsely promising in this case. The advantage of Kantian ethics is that this is all the common 
sense that it requires, whereas a consequentialist or virtue ethical agent will require much more. All
moral theories evaluating falsely promising will a robust definition of the convention of promising, 
but consequentialism and virtue ethics will also require additional information about consequences or character
that Kantian ethics will not. Thus, although the need for common sense poses a challenge to automated
Kantian ethics, this challenge is more acute for consequentialism or virtue ethics so Kantian ethics remains
 within the closest reach of automation.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Dyadic Deontic Logic \label{ddl}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
I formalize Kantian ethics by representing it as an axiom on top of a base logic. In this section, 
I present the logical background necessary to understand my work and my choice of Dyadic Deontic Logic (DDL).%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
Traditional modal logics include the necessitation operator, denoted as $\Box$. In simple modal logic
using the Kripke semantics, $\Box p$ is true at a world $w$ if $p$ is true at all of $w$'s neighbors \cite{cresswell}. 
These logics usually also contain the possibility operator $\diamond$, where
 $\diamond p \iff \sim \Box \sim p$. Additionally, modal logics include operators of propositional 
logic like $\sim, \wedge, \vee, \rightarrow$.

A deontic logic is a special kind of modal logic designed to reason about obligation. Standard deontic
logic \citep{cresswell, sep-logic-deontic} replaces $\Box$ with the obligation operator
$O$, and $\diamond$ with the permissibility operator $P$. Using the Kripke semantics for $O$, $O p$ 
is true at $w$ if $p$ is true at all  ideal deontic alternatives to $w$. The $O$ operator in SDL
takes a single argument (the formula that is obligatory), and is thus called a monadic deontic operator.

 While SDL is appreciable for its simplicity, it suffers a variety of well-documented paradoxes, 
including contrary-to-duty paradoxes \footnote{The paradigm case of a contrary-to-duty paradox is the 
Chisholm paradox. Consider the following statements: \begin{enumerate}
\item It ought to be that Tom helps his neighbors
\item It ought to be that if Tom helps his neighbors, he tells them he is coming
\item If Tom does not help his neighbors, he ought not tell them that he is coming
\item Tom does not help his neighbors
\end{enumerate} 
These premises contradict themselves, because items (2)-(4) imply that Tom ought not help his neighbors. The 
contradiction results because the logic cannot handle violations of duty mixed with
conditionals. \citep{chisholm, ctd}
}. 
In situations where duty is violated, the logic breaks down 
and produces paradoxical results. Thus, I use an improved deontic logic instead of SDL for this work.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
I use as my base logic Carmo and Jones's dyadic deontic logic, or DDL, which improves on SDL \cite{CJDDL}. 
It introduces a dyadic obligation operator $O\{A \vert B\}$ 
to represent the sentence ``A is obligated in the context B". This gracefully handles contrary-to-duty
conditionals. The obligation operator uses a neighborhood semantics \cite{neighborhood1, neighborhood2}, instead of the Kripke semantics. 
Carmo and Jones define a function $ob$ that maps from worlds to sets of sets of worlds. Intuitively, 
each world is mapped to the set of propositions obligated at that world, where a proposition $p$ is defined as 
the worlds at which the $p$ is true.

DDL also includes other modal operators. In addition to $\Box$ and $\diamond$, DDL also has a notion
of actual obligation and possible obligation, represented by operators $O_a$ and $O_p$ respectively. 
These notions are accompanied by the corresponding modal operators $\Box_a, \diamond_a, \Box_p, \diamond_p$. 
These operators use a Kripke semantics, with the functions $av$ and $pv$ mapping a world $w$ to the set 
of corresponding actual or possible versions of $w$.

For more of fine-grained properties of DDL see \citep{CJDDL} or this project's source code. DDL is a heavy logic and contains modal operators 
that aren't necessary for my analysis. While this expressivity is powerful, it may also cause performance
impacts. DDL has a large set of axioms involving quantification over complex higher-order
logical expressions. Proofs involving these axioms will be computationally expensive. I do not run 
into performance issues in my system, but future work may choose to embed a less complicated logic.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Isabelle/HOL \label{isabelle}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
The final component of my project is the automated theorem prover I use to automate my formalization.
Isabelle/HOL is an interactive proof assistant built on Haskell and Scala \cite{isabelle}. It 
allows the user to define types, functions, definitions, and axiom systems. It has built-in support for both
automatic and interactive/manual theorem proving.

I started my project by reimplementing Benzmueller, Farjami, and Parent's implementation 
of DDL in Isabelle/HOL \cite{BFP, logikey}. This helped me learn how to use Isabelle/HOL, and the implementation showcased in the 
next few sections demonstrates the power of Isabelle.

Benzmueller, Farjami, and Parent use a shallow semantic embedding. This kind of embedding models the semantics of DDL as 
constants in HOL and axioms as constraints on DDL models. This document will contain a subset of my 
implementation that is particularly interesting and relevant to understanding the rest of the project. 
For the complete implementation, see the source code in \isatt{paper22.thy}.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{System Definition%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
The first step in embedding a logic in Isabelle is defining the relevant terms and types.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{typedecl}\isamarkupfalse%
\ i\ %
\isamarkupcmt{i is the type for a set of worlds.%
}\isanewline
\isanewline
\isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
\ t\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}i\ {\isasymRightarrow}\ bool{\isacharparenright}{\isachardoublequoteclose}\ %
\isamarkupcmt{t represents a set of DDL formulae.%
}\isanewline
%
\isamarkupcmt{A set of formulae is defined by its truth value at a set of worlds. For example, the set \{True\}
would be true at any set of worlds.%
}\isanewline
%
\begin{isamarkuptext}%
The main accessibility relation that I will use is the $ob$ relation:%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{consts}\isamarkupfalse%
\ ob{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t\ {\isasymRightarrow}\ {\isacharparenleft}t\ {\isasymRightarrow}\ bool{\isacharparenright}{\isachardoublequoteclose}\ \ %
\isamarkupcmt{set of propositions obligatory in this context%
}\isanewline
\ %
\isamarkupcmt{ob(context)(term) is True if the term is obligatory in this context%
}\isanewline
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Axiomatization%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
For a semantic embedding, axioms are modelled as restrictions on models of the system. In this case,
a model is specificied by the relevant accessibility relations, so it suffices to place conditions on 
the accessibility relations. These axioms can be quite unweildy, so luckily I was able to lift BFP's 
implementation of Carmo and Jones's original axioms directly \citep{BFP}. Here's an example of an axiom:%
\end{isamarkuptext}\isamarkuptrue%
\isanewline
\isakeyword{and}\ ax{\isacharunderscore}{\isadigit{5}}d{\isacharcolon}\ {\isachardoublequoteopen}{\isasymforall}X\ Y\ Z{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isasymforall}w{\isachardot}\ Y{\isacharparenleft}w{\isacharparenright}{\isasymlongrightarrow}X{\isacharparenleft}w{\isacharparenright}{\isacharparenright}\ {\isasymand}\ ob{\isacharparenleft}X{\isacharparenright}{\isacharparenleft}Y{\isacharparenright}\ {\isasymand}\ {\isacharparenleft}{\isasymforall}w{\isachardot}\ X{\isacharparenleft}w{\isacharparenright}{\isasymlongrightarrow}Z{\isacharparenleft}w{\isacharparenright}{\isacharparenright}{\isacharparenright}\ \isanewline
\ \ {\isasymlongrightarrow}ob{\isacharparenleft}Z{\isacharparenright}{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isacharparenleft}Z{\isacharparenleft}w{\isacharparenright}\ {\isasymand}\ {\isasymnot}X{\isacharparenleft}w{\isacharparenright}{\isacharparenright}\ {\isasymor}\ Y{\isacharparenleft}w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{If some subset Y of X is obligatory in the context X, then in a larger context Z,
 any obligatory proposition must either be in Y or in Z-X. Intuitively, expanding the context can't 
cause something unobligatory to become obligatory, so the obligation operator is monotonically increasing
 with respect to changing contexts.%
}\isanewline
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Syntax%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
The syntax that I will work with is defined as abbreviations. Each DDL operator is represented 
as a HOL formula. Isabelle automatically unfolds formulae defined with the \isatt{abbreviation} command 
whenever they are applied. While the shallow embedding is performant (because it uses Isabelle's original 
syntax tree), abbreviations may hurt performance. In some complicated proofs, we want to control definition
unfolding. Benzmueller and Parent told me that the performance cost of abbreviations can 
be mitigated using a definition instead.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
Modal operators will be useful for my purposes, but the implementation is pretty standard.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ ddlbox{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isasymRightarrow}t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymbox}{\isachardoublequoteclose}{\isacharparenright}\ \isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymbox}\ A\ {\isasymequiv}\ {\isasymlambda}w{\isachardot}{\isasymforall}y{\isachardot}\ A{\isacharparenleft}y{\isacharparenright}{\isachardoublequoteclose}\ \isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ ddldiamond{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t\ {\isasymRightarrow}\ t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymdiamond}{\isachardoublequoteclose}{\isacharparenright}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymdiamond}A\ {\isasymequiv}\ \isactrlbold {\isasymnot}{\isacharparenleft}{\isasymbox}{\isacharparenleft}\isactrlbold {\isasymnot}A{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
\begin{isamarkuptext}%
The most important operator for our purposes is the obligation operator.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ ddlob{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isasymRightarrow}t{\isasymRightarrow}t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}O{\isacharbraceleft}{\isacharunderscore}{\isacharbar}{\isacharunderscore}{\isacharbraceright}{\isachardoublequoteclose}{\isacharparenright}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}O{\isacharbraceleft}B{\isacharbar}A{\isacharbraceright}\ {\isasymequiv}\ {\isasymlambda}\ w{\isachardot}\ ob{\isacharparenleft}A{\isacharparenright}{\isacharparenleft}B{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{O$\{B \vert A\}$ can be read as ``B is obligatory in the context A"%
}\isanewline
%
\begin{isamarkuptext}%
While DDL is powerful because of its support for a dyadic obligation operator, in many cases 
we need a monadic obligation operator. Below is some syntactic sugar for a monadic obligation operator.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ ddltrue{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymtop}{\isachardoublequoteclose}{\isacharparenright}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymtop}\ {\isasymequiv}\ {\isasymlambda}w{\isachardot}\ True{\isachardoublequoteclose}\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ ddlfalse{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymbottom}{\isachardoublequoteclose}{\isacharparenright}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymbottom}\ {\isasymequiv}\ {\isasymlambda}w{\isachardot}\ False{\isachardoublequoteclose}\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ ddlob{\isacharunderscore}normal{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isasymRightarrow}t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}O\ {\isacharbraceleft}{\isacharunderscore}{\isacharbraceright}{\isachardoublequoteclose}{\isacharparenright}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}\ {\isasymequiv}\ {\isacharparenleft}O{\isacharbraceleft}A{\isacharbar}\isactrlbold {\isasymtop}{\isacharbraceright}{\isacharparenright}\ {\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{Intuitively, the context \texttt{True} is the widest context possible because \texttt{True} holds at all worlds.%
}%
\begin{isamarkuptext}%
Validity will be useful when discussing metalogical/ethical properties.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ ddlvalid{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isasymRightarrow}bool{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymTurnstile}{\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymTurnstile}A\ {\isasymequiv}\ {\isasymforall}w{\isachardot}\ A\ w{\isachardoublequoteclose}\isanewline
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Syntactic Properties%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
One way to show that a semantic embedding is complete is to show that the syntactic specification
of the theory (axioms) are valid for this semantics - so to show that every axiom holds at every 
world. Benzmueller, Farjami, and Parent provide a complete treatment of the completeness of their embedding, but I 
will include selected axioms that are particularly interesting here. This section also demonstrates many
of the relevant features of Isabelle/HOL for my project.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
\textbf{Consistency}%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ True\ \isacommand{nitpick}\isamarkupfalse%
\ {\isacharbrackleft}satisfy{\isacharcomma}user{\isacharunderscore}axioms{\isacharcomma}format{\isacharequal}{\isadigit{2}}{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{by}\isamarkupfalse%
\ simp\isanewline
%
\isamarkupcmt{Isabelle has built-in support for Nitpick, a model checker. 
Nitpick successfully found a model satisfying these axioms so the system is consistent.%
}\isanewline
%
\isamarkupcmt{\color{blue} Nitpick found a model for card i = 1:

  Empty assignment \color{black}%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
Nitpick \cite{nitpick} can generate models or countermodels, so it's useful to falsify potential
theorems, as well as to show consistency. {\color{red} by simp} indicates the proof method. In this 
case, {\color{red} simp} indicates the Simplification proof method, which involves unfolding definitions
and applying theorems directly. HOL has $True$ as a theorem, which is why this theorem was so easy to prove.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/thesis_2_methods.thy%:%
%:%24=6%:%
%:%36=8%:%
%:%37=9%:%
%:%38=10%:%
%:%39=11%:%
%:%40=12%:%
%:%41=13%:%
%:%42=14%:%
%:%43=15%:%
%:%44=16%:%
%:%45=17%:%
%:%46=18%:%
%:%47=19%:%
%:%48=20%:%
%:%49=21%:%
%:%50=22%:%
%:%51=23%:%
%:%52=24%:%
%:%53=25%:%
%:%62=27%:%
%:%74=30%:%
%:%75=31%:%
%:%76=32%:%
%:%77=33%:%
%:%78=34%:%
%:%79=35%:%
%:%80=36%:%
%:%81=37%:%
%:%82=38%:%
%:%83=39%:%
%:%84=40%:%
%:%85=41%:%
%:%86=42%:%
%:%87=43%:%
%:%88=44%:%
%:%89=45%:%
%:%90=46%:%
%:%91=47%:%
%:%92=48%:%
%:%93=49%:%
%:%94=50%:%
%:%95=51%:%
%:%96=52%:%
%:%97=53%:%
%:%106=56%:%
%:%118=58%:%
%:%119=59%:%
%:%120=60%:%
%:%121=61%:%
%:%122=62%:%
%:%123=63%:%
%:%124=64%:%
%:%128=66%:%
%:%129=67%:%
%:%130=68%:%
%:%131=69%:%
%:%132=70%:%
%:%133=71%:%
%:%134=72%:%
%:%135=73%:%
%:%136=74%:%
%:%137=75%:%
%:%138=76%:%
%:%139=77%:%
%:%140=78%:%
%:%141=79%:%
%:%142=80%:%
%:%143=81%:%
%:%144=82%:%
%:%145=83%:%
%:%146=84%:%
%:%147=85%:%
%:%148=86%:%
%:%149=87%:%
%:%150=88%:%
%:%151=89%:%
%:%152=90%:%
%:%161=93%:%
%:%173=95%:%
%:%174=96%:%
%:%175=97%:%
%:%176=98%:%
%:%177=99%:%
%:%178=100%:%
%:%179=101%:%
%:%180=102%:%
%:%181=103%:%
%:%185=105%:%
%:%189=107%:%
%:%190=108%:%
%:%191=109%:%
%:%192=110%:%
%:%193=111%:%
%:%194=112%:%
%:%195=113%:%
%:%196=114%:%
%:%197=115%:%
%:%198=116%:%
%:%199=117%:%
%:%200=118%:%
%:%201=119%:%
%:%202=120%:%
%:%203=121%:%
%:%204=122%:%
%:%205=123%:%
%:%206=124%:%
%:%207=125%:%
%:%208=126%:%
%:%209=127%:%
%:%210=128%:%
%:%211=129%:%
%:%212=130%:%
%:%213=131%:%
%:%214=132%:%
%:%215=133%:%
%:%219=136%:%
%:%223=138%:%
%:%224=139%:%
%:%225=140%:%
%:%226=141%:%
%:%227=142%:%
%:%228=143%:%
%:%229=144%:%
%:%230=145%:%
%:%231=146%:%
%:%232=147%:%
%:%233=148%:%
%:%234=149%:%
%:%235=150%:%
%:%236=151%:%
%:%237=152%:%
%:%238=153%:%
%:%239=154%:%
%:%240=155%:%
%:%244=157%:%
%:%248=159%:%
%:%249=160%:%
%:%250=161%:%
%:%251=162%:%
%:%252=163%:%
%:%253=164%:%
%:%254=165%:%
%:%255=166%:%
%:%256=167%:%
%:%257=168%:%
%:%258=169%:%
%:%259=170%:%
%:%260=171%:%
%:%261=172%:%
%:%262=173%:%
%:%263=174%:%
%:%264=175%:%
%:%265=176%:%
%:%266=177%:%
%:%267=178%:%
%:%268=179%:%
%:%272=182%:%
%:%276=185%:%
%:%277=186%:%
%:%278=187%:%
%:%279=188%:%
%:%280=189%:%
%:%281=190%:%
%:%282=191%:%
%:%283=192%:%
%:%284=193%:%
%:%285=194%:%
%:%286=195%:%
%:%287=196%:%
%:%288=197%:%
%:%289=198%:%
%:%290=199%:%
%:%291=200%:%
%:%300=203%:%
%:%312=205%:%
%:%313=206%:%
%:%314=207%:%
%:%315=208%:%
%:%316=209%:%
%:%317=210%:%
%:%318=211%:%
%:%319=212%:%
%:%323=216%:%
%:%324=217%:%
%:%325=218%:%
%:%326=219%:%
%:%327=220%:%
%:%328=221%:%
%:%329=222%:%
%:%330=223%:%
%:%331=224%:%
%:%332=225%:%
%:%336=227%:%
%:%340=229%:%
%:%341=230%:%
%:%342=231%:%
%:%343=232%:%
%:%344=233%:%
%:%345=234%:%
%:%346=235%:%
%:%347=236%:%
%:%348=237%:%
%:%349=238%:%
%:%350=239%:%
%:%351=240%:%
%:%352=241%:%
%:%353=242%:%
%:%354=243%:%
%:%355=244%:%
%:%356=245%:%
%:%357=246%:%
%:%358=247%:%
%:%359=248%:%
%:%360=249%:%
%:%361=250%:%
%:%362=251%:%
%:%363=252%:%
%:%364=253%:%
%:%365=254%:%
%:%366=255%:%
%:%375=258%:%
%:%387=260%:%
%:%388=261%:%
%:%389=262%:%
%:%390=263%:%
%:%391=264%:%
%:%392=265%:%
%:%393=266%:%
%:%394=267%:%
%:%395=268%:%
%:%396=269%:%
%:%397=270%:%
%:%398=271%:%
%:%399=272%:%
%:%400=273%:%
%:%401=274%:%
%:%402=275%:%
%:%403=276%:%
%:%404=277%:%
%:%405=278%:%
%:%406=279%:%
%:%407=280%:%
%:%408=281%:%
%:%409=282%:%
%:%410=283%:%
%:%411=284%:%
%:%412=285%:%
%:%413=286%:%
%:%414=287%:%
%:%415=288%:%
%:%416=289%:%
%:%417=290%:%
%:%418=291%:%
%:%419=292%:%
%:%420=293%:%
%:%421=294%:%
%:%422=295%:%
%:%423=296%:%
%:%424=297%:%
%:%425=298%:%
%:%426=299%:%
%:%427=300%:%
%:%428=301%:%
%:%429=302%:%
%:%430=303%:%
%:%431=304%:%
%:%432=305%:%
%:%433=306%:%
%:%434=307%:%
%:%435=308%:%
%:%436=309%:%
%:%437=310%:%
%:%438=311%:%
%:%439=312%:%
%:%440=313%:%
%:%441=314%:%
%:%442=315%:%
%:%443=316%:%
%:%444=317%:%
%:%445=318%:%
%:%446=319%:%
%:%447=320%:%
%:%448=321%:%
%:%449=322%:%
%:%450=323%:%
%:%451=324%:%
%:%452=325%:%
%:%453=326%:%
%:%454=327%:%
%:%455=328%:%
%:%459=330%:%
%:%463=332%:%
%:%464=333%:%
%:%465=334%:%
%:%466=335%:%
%:%467=336%:%
%:%468=337%:%
%:%469=338%:%
%:%470=339%:%
%:%471=340%:%
%:%472=341%:%
%:%473=342%:%
%:%474=343%:%
%:%475=344%:%
%:%476=345%:%
%:%477=346%:%
%:%478=347%:%
%:%479=348%:%
%:%480=349%:%
%:%481=350%:%
%:%482=351%:%
%:%483=352%:%
%:%484=353%:%
%:%485=354%:%
%:%486=355%:%
%:%490=359%:%
%:%494=361%:%
%:%495=362%:%
%:%496=363%:%
%:%497=364%:%
%:%498=365%:%
%:%499=366%:%
%:%500=367%:%
%:%501=368%:%
%:%502=369%:%
%:%503=370%:%
%:%504=371%:%
%:%505=372%:%
%:%506=373%:%
%:%507=374%:%
%:%508=375%:%
%:%509=376%:%
%:%510=377%:%
%:%511=378%:%
%:%512=379%:%
%:%513=380%:%
%:%514=381%:%
%:%515=382%:%
%:%516=383%:%
%:%517=384%:%
%:%518=385%:%
%:%519=386%:%
%:%520=387%:%
%:%529=390%:%
%:%541=392%:%
%:%542=393%:%
%:%546=396%:%
%:%547=397%:%
%:%548=398%:%
%:%549=399%:%
%:%550=400%:%
%:%551=401%:%
%:%552=402%:%
%:%553=403%:%
%:%554=404%:%
%:%555=405%:%
%:%556=406%:%
%:%557=407%:%
%:%558=408%:%
%:%559=409%:%
%:%560=410%:%
%:%561=411%:%
%:%562=412%:%
%:%563=413%:%
%:%564=414%:%
%:%565=415%:%
%:%566=416%:%
%:%567=417%:%
%:%568=418%:%
%:%569=419%:%
%:%570=420%:%
%:%571=421%:%
%:%575=423%:%
%:%576=424%:%
%:%577=425%:%
%:%578=426%:%
%:%579=427%:%
%:%580=428%:%
%:%581=429%:%
%:%582=430%:%
%:%583=431%:%
%:%584=432%:%
%:%585=433%:%
%:%586=434%:%
%:%587=435%:%
%:%588=436%:%
%:%589=437%:%
%:%590=438%:%
%:%591=439%:%
%:%592=440%:%
%:%593=441%:%
%:%602=444%:%
%:%614=446%:%
%:%615=447%:%
%:%616=448%:%
%:%617=449%:%
%:%618=450%:%
%:%619=451%:%
%:%620=452%:%
%:%621=453%:%
%:%622=454%:%
%:%623=455%:%
%:%624=456%:%
%:%625=457%:%
%:%626=458%:%
%:%635=461%:%
%:%647=463%:%
%:%649=465%:%
%:%650=465%:%
%:%651=465%:%
%:%652=465%:%
%:%653=466%:%
%:%654=467%:%
%:%655=467%:%
%:%656=467%:%
%:%657=467%:%
%:%659=468%:%
%:%660=469%:%
%:%661=469%:%
%:%664=483%:%
%:%666=485%:%
%:%667=485%:%
%:%668=485%:%
%:%669=485%:%
%:%670=486%:%
%:%671=486%:%
%:%672=486%:%
%:%680=490%:%
%:%692=492%:%
%:%693=493%:%
%:%694=494%:%
%:%695=495%:%
%:%697=519%:%
%:%698=520%:%
%:%699=521%:%
%:%701=522%:%
%:%702=523%:%
%:%703=524%:%
%:%704=525%:%
%:%705=525%:%
%:%713=532%:%
%:%725=534%:%
%:%726=535%:%
%:%727=536%:%
%:%728=537%:%
%:%729=538%:%
%:%730=539%:%
%:%734=555%:%
%:%736=556%:%
%:%737=556%:%
%:%738=557%:%
%:%739=558%:%
%:%740=558%:%
%:%741=559%:%
%:%743=561%:%
%:%745=562%:%
%:%746=562%:%
%:%747=563%:%
%:%749=564%:%
%:%750=564%:%
%:%753=584%:%
%:%754=585%:%
%:%756=586%:%
%:%757=586%:%
%:%758=587%:%
%:%759=588%:%
%:%760=588%:%
%:%761=589%:%
%:%762=590%:%
%:%763=590%:%
%:%764=591%:%
%:%766=592%:%
%:%769=594%:%
%:%771=595%:%
%:%772=595%:%
%:%773=596%:%
%:%781=605%:%
%:%793=607%:%
%:%794=608%:%
%:%795=609%:%
%:%796=610%:%
%:%797=611%:%
%:%801=613%:%
%:%803=614%:%
%:%804=614%:%
%:%805=614%:%
%:%807=614%:%
%:%811=614%:%
%:%812=614%:%
%:%814=615%:%
%:%815=616%:%
%:%816=616%:%
%:%818=617%:%
%:%819=618%:%
%:%820=619%:%
%:%830=621%:%
%:%831=622%:%
%:%832=623%:%
%:%833=624%:%

### 2022-02-08 paper/output/document/thesis_2_methods.tex
cleaning methods

@@
 on practical reason, which is the kind of reason that we 
-use to decide what to do. In \emph{The Groundwork of the Metaphysics of Morals}, Kant's most influential 
-text on ethics, he explains that rational beings are unique because we can act ``in accordance with 
+use to decide what to do. In \emph{The Groundwork of the Metaphysics of Morals}, Kant explains that 
+rational beings are unique because we can act ``in accordance with 
 the representations of laws" \citep[4:412]{groundwork}. In contrast, a ball thrown into the air acts 
@@
 Rational beings are set apart by this reflective capacity. A rational being's behavior is purposive and 
-their actions are guided by practical reason. They have reasons for acting, even when these reasons may be 
-opaque to them. This operation of practical reason is what Kant calls the will.
+their actions are guided by practical reason. They have reasons for acting, even when these reasons are
+opaque to them. This reflective choosing, or operation of practical reason, is what Kant calls the will.
 
@@
 the ``subjective principle of willing," or the reason that the will \emph{subjectively} gives 
-to itself for acting \citep[16 footnote 1]{groundwork}. There is debate about what exactly must be 
-included in a maxim, but many philosophers agree that a maxim consists of some combination of circumstances, 
+to itself for acting \citep[16 footnote 1]{groundwork}. Many philosophers agree that a maxim consists 
+of some combination of circumstances, 
 act, and goal.\footnote{For more discussion of the definition of a maxim, see Section What Is a Maxim}
@@
 principle given by this maxim. Because a maxim captures an agent's principle of action, Kant evaluates
-maxims as obligatory, prohibited, or permissible. He argues that certain maxims have a form or logical structure 
-that requires any rational agent to will them, and these maxims are obligatory.
+maxims as obligatory, prohibited, or permissible. He argues that the form of certain maxims 
+requires any rational agent to will them, and these maxims are obligatory.
 
@@
 sweet tooth." An imperative is categorical if it holds unconditionally for all rational agents under all 
-circumstances. Kant argues that the moral law must be a categorical imperative, for otherwise it would 
-not have the force that makes it a moral law \citep[5]{groundwork}. In order for an imperative to be 
-categorical, it must be derived from the will's authority over itself. Our wills are autonomous, so 
-the only thing that can have unconditional authority over a rational will is 
-the rational will itself. In Velleman's version of this argument, he claims that no one else can tell you what 
-to do because you can always ask why you 
+circumstances. Kant argues that the moral law must be a categorical imperative \citep[5]{groundwork}. 
+In order for an imperative to be categorical, it must be derived from the will's authority over itself. 
+Our wills are autonomous, so the only thing that can have unconditional authority over a rational will is 
+the will itself. No one else can tell you what to do because you can always ask why you 
 should obey their authority. The only authority that you cannot question is the authority of your own 
@@
 for the categorical imperative are those rules that are required of the will because it is a will.
-The categorical imperative must be a property of practical reason itself.
 
@@
 argue that all three formulations are equivalent. In this project, I focus on the first formulation,
-the Formula of Universal Law.\footnote{For more on this 
-choice, see Section Why FUL.}
+the Formula of Universal Law, and I explain this choice in Section \ref{whyful}.
 
@@
 the maxim is prohibited.
+
 Velleman presents a concise argument for the FUL. He argues that reason is universally shared among reasoners. For 
@@
 nothing special about the operation of my practical reason that other reasoners don't have access to. 
-Practical reason is shared, so in adopting a maxim, I implicitly state that all reasoners
+In adopting a maxim, I implicitly state that all reasoners
 across time also have reason to adopt that maxim. Therefore, because I act on reasons, I must obey the 
@@
 
-The above is not meant to serve as a full defense or articulation of Kant's ethical theory, as that is outside the scope
-of this thesis. Instead, I briefly reconstruct a sketch of Kant's ethical theory in the hopes 
+The above is not meant to serve as a full defense or articulation of Kant's ethical theory. Instead, I briefly reconstruct a sketch of Kant's ethical theory in the hopes 
 of offering context for the implementation of the FUL I present later in the thesis. Additionally, understanding 
@@
 Kantian ethics is an especially candidate for formalization because the categorical imperative, particularly the FUL, 
-is a property of reason related to the form or structure of a maxim, or a formal principle of practical
-reason. It does not require any situational knowledge or contingent beyond the circumstances included
+is a property of reason related to the form or structure of a maxim. It does not require any situational 
+knowledge beyond the circumstances included
 in the maxim itself and thus requires far less contingent facts than other ethical theories.
-Instead, it is purely a property of the proposed principle for action. This formalism makes Kantian
-ethics an attractive candidate for formalization. While other ethical theories often rely on many facts about 
+While other ethical theories often rely on many facts about 
 the world or the actor, Kantian ethics simply relies on the form of a given maxim. A computer evaluating 
-a maxim doesn't require any knowledge about the world beyond what is contained in a maxim. A maxim 
-is the only input that the computer needs to make a moral judgement. Automating 
+a maxim doesn't require any knowledge about the world beyond what is contained in a maxim. Automating 
 Kantian ethics merely requires making the notion of a maxim precise and representing it to the computer. 
@@
 Not only does evaluating Kantian ethics focus on a maxim, a maxim itself is an object
-with a thin representation for a computer, as compares to more complex objects like states of 
+with a thin representation for a computer, as compared to more complex objects like states of 
 affairs or moral character. Later in my project, I argue that a maxim can be represented simply as 
@@
 is simple and efficient, especially when compared to the representation of a causal chain or a state of 
-affairs or moral character. A maxim is a principle with a well-defined form, so representing a maxim
-to the computer merely requires capturing this form. This property not only reduces the computational complexity
-(in terms of time and space) of representing a maxim, it also make the system easier for human reasoners
+affairs or moral character. This property not only reduces the computational complexity
+(in terms of time and space) of representing a maxim, but it also make the system easier for human reasoners
 to interact with. A person crafting an input to a Kantian automated agent needs to reason about relatively
 simple units of evaluation, as opposed to the more complex features that consequentialism and virtue
-ethics require. I will make the comparision to consequentialism and virtue ethics explicit below.%
+ethics require.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-My choices to interpret maxims and the Formula of Universal Law in a particular way represent debates
-in Kantian ethics over the meanings of these terms that I take a stance on. Another debate in Kantian 
+One debate in Kantian 
 ethics is the role of ``common-sense" reasoning. Kantian ethics requires common-sense reasoning to 
@@
 in Kantian ethics are due to badly formulated maxims, so this question is important for an ethical 
-reasoner to answer. My system does not need to answer this question because I assume a well-formed
+reasoner to answer.\footnote{For example, critics of Kantian ethics worry that the maxim, ``When I am a
+man, I will marry a man because I want to spend my life with him" fails the universalizability
+test because if all men only married men, sexual reproduction would stop. This argument implies 
+that Kantian ethics is homophobic. Kantians often respond by arguing that the correct formulation of 
+this maxim is, ``When I love a man, I will marry him because I want to spend my life with him," which
+is universalizable because if everyone marries who they love, some men will marry women.} 
+My system does not need to answer this question because I assume a well-formed
 maxim as input and apply the categorical imperative to this input, but if my system were ever to be used
@@
 
-Common-sense reasoning is also relevant in applying the universalizability test itself. Consider an example
-maxim tested using the Formula of Universal Law: ``When broke, I will falsely promise to repay a loan
+Common-sense reasoning is also relevant when applying the universalizability test itself. Consider the example
+maxim: ``When broke, I will falsely promise to repay a loan
 to get some quick cash." This maxim fails the universalizability test because in a world where everyone
@@
 kind of common sense reasoning that an automated Kantian agent would need. This need is not unique to
-Kantian ethics; consequentialists agents need this kind of common sense to determine the consequences of 
-an action and virtue ethical agents need this kind of common sense to determine which virtues an action
-reflects. Making any ethical judgement requires relatively robust conceptions of the action or situation
+Kantian ethics; consequentialists agents need common sense to determine the consequences of 
+an action and virtue ethical agents need common sense to determine which virtues an action
+reflects. Making any ethical judgement requires robust conceptions of the action
 at hand, falsely promising in this case. The advantage of Kantian ethics is that this is all the common 
 sense that it requires, whereas a consequentialist or virtue ethical agent will require much more. All
-moral theories evaluating falsely promising will a robust definition of the convention of promising, 
-but consequentialism and virtue ethics will also require additional information about consequences or character
+moral theories evaluating falsely promising will a robust definition of promising, 
+but consequentialism and virtue ethics will also require additional information
 that Kantian ethics will not. Thus, although the need for common sense poses a challenge to automated
-Kantian ethics, this challenge is more acute for consequentialism or virtue ethics so Kantian ethics remains
- within the closest reach of automation.%
+Kantian ethics, this challenge is more acute for consequentialism or virtue ethics.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsubsection{The Formula of Universal Law \label{whyful}%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
+Earlier I mentioned that Kant presents three formulations, or versions, 
+of what he calls the ``supreme law of morality," but I focus on the first of these three. In this section, 
+I argue that the Formula of Universal Law, specifically, is the easiest part of Kantian ethics to automate
+and the most generalizable.
+
+The first formulation of the categorical imperative is the
+formula of universal law (FUL), which reads, ``act only according to that maxim through which you can 
+at the same time will that it become a universal law." \cite[34]{groundwork} This formulation
+generates the universalizability test, which ``tests" the moral value of a maxim by 
+imagining a world in which it becomes a universal law and attempting to will the maxim in that world. The 
+second formulation of the categorical imperative is the formula of humanity (FUH): ``So act that you use humanity, 
+in your own person, as well as in the person of any other, always at the same time as an end, never merely 
+as a means." \cite[41]{groundwork}. This formulation is often understood as requiring us to 
+acknowledge and respect the dignity of every other person. The third formulation of the categorical 
+imperative is the formula of autonomy (FOA), which Korsgaard describes
+as, ``we should so act that we may think of ourselves as legislating universal laws through our 
+maxims" \cite[28]{korsgaardintro}. While closely related to the FUL, the FOA presents morality as the activity of 
+perfectly rational agents in an ideal ``kingdom of ends," guided by what Kant calls the ``laws of freedom."
+
+I choose to focus on the FUL\footnote{The FUL is often seen as emblematic of Kantian constructivism \cite[173]{ebelsduggan}. 
+My project is not committed to Kantian constructivism. I believe that computational ethics is likely a 
+valuable tool for any ethicist, and I make the case for Kantian ethics specifically.},
+ because it is the most formal and thus the easiest to formalize and implement. 
+Onora O'Neill explains that the formalism of the FUL allows 
+for greater precision in philosophical arguments analyzing its implications and power \cite[33]{actingonprinciple}. This precision 
+is particularly useful in a computational context because any formalism necessarily makes its content 
+precise. The FUL's existing precision reduces ambiguity, allowing me to remain faithful to philosophical
+literature on Kant. Precision reduces the need to make choices to resolve debates 
+and ambiguities. Minimizing these choices minimizes 
+arbitrariness in my formalization and puts it on solid philosophical footing.
+
+Though Kantians study all formulations of the categorical imperative, Kant argues in Groundwork 
+that the three formulations of the categorical imperative are equivalent \cite{groundwork}. While this 
+argument is disputed \cite{sepkant}, for those who believe it, the
+stakes for my choice of the FUL are greatly reduced. If all formulations are equivalent, then a formalization of the FUL
+lends the exact same power as a formalization of the second or third formulation of the categorical 
+imperative.
+
+Those who do not believe that all three formulations of the categorical imperative are equivalent
+understand the FUL as the strongest or most foundational, and thus an appropriate initial choice for 
+formalizations. Korsgaard characterizes the three formulations of the categorical
+imperative according to Rawls' general and special conception of justice. The general conception applies
+universally and can never be violated, while the special conception represents an ideal for us to
+live towards. For example, the special conception may require that we prefer some job applicants
+over others in order to remedy historical injustice, and the general conception may require that such
+inequalities always operate in the service of the least privileged \citep[19]{KorsgaardRTL}. Korsgaard
+argues that the Formula of Universal Law represents Kant's general conception of justice, and the Formula of 
+Humanity represents his special conception. The FUL's prescriptions can never be violated, even in the most
+non-ideal circumstances imaginable, but the FUH is merely a standard to live towards that might not be 
+achieved. Thus, he FUL generates stronger requirements than the other two formulations and is 
+the bare minimum of Kant's ethics. Because the FUL's prescriptions outweigh those of the other two formulations,
+formalizing it creates a functional, minimum ethical theory that can serve as a foundation for implementations
+of other aspects of Kant's ethics.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 Traditional modal logics include the necessitation operator, denoted as $\Box$. In simple modal logic
-using the Kripke semantics, $\Box p$ is true at a world $w$ if $p$ is true at all of $w$'s neighbors \cite{cresswell}. 
+using the Kripke semantics, $\Box p$ is true at a world $w$ if $p$ is true at all of $w$'s neighbors, 
+and it represents the concept of necessary truth \citep{cresswell}. 
 These logics usually also contain the possibility operator $\diamond$, where
- $\diamond p \iff \sim \Box \sim p$. Additionally, modal logics include operators of propositional 
-logic like $\sim, \wedge, \vee, \rightarrow$.
-
-A deontic logic is a special kind of modal logic designed to reason about obligation. Standard deontic
-logic \citep{cresswell, sep-logic-deontic} replaces $\Box$ with the obligation operator
-$O$, and $\diamond$ with the permissibility operator $P$. Using the Kripke semantics for $O$, $O p$ 
-is true at $w$ if $p$ is true at all  ideal deontic alternatives to $w$. The $O$ operator in SDL
+ $\diamond p \iff \sim \Box \sim p$. $\diamond p$ means that the statement $p$ is possibly true. 
+Additionally, modal logics include standard operators of propositional logic like $\sim, \wedge, \vee, \rightarrow$.
+
+A deontic logic is a special kind of modal logic designed to reason about moral obligation. Standard deontic
+logic replaces $\Box$ with the obligation operator
+$O$, and $\diamond$ with the permissibility operator $P$ \citep{cresswell, sep-logic-deontic}. Using the Kripke semantics for $O$, $O p$ 
+is true at $w$ if $p$ is true at all  ideal deontic alternatives to $w$, and thus represents the 
+concept of moral necessity or necessary requirements. The $O$ operator in SDL
 takes a single argument (the formula that is obligatory), and is thus called a monadic deontic operator.
@@
  While SDL is appreciable for its simplicity, it suffers a variety of well-documented paradoxes, 
-including contrary-to-duty paradoxes \footnote{The paradigm case of a contrary-to-duty paradox is the 
+including contrary-to-duty paradoxes. \footnote{The paradigm case of a contrary-to-duty paradox is the 
 Chisholm paradox. Consider the following statements: \begin{enumerate}
@@
 conditionals. \citep{chisholm, ctd}
-}. 
-In situations where duty is violated, the logic breaks down 
+}. In situations where duty is violated, the logic breaks down 
 and produces paradoxical results. Thus, I use an improved deontic logic instead of SDL for this work.%
@@
 \begin{isamarkuptext}%
-I use as my base logic Carmo and Jones's dyadic deontic logic, or DDL, which improves on SDL \cite{CJDDL}. 
+I use as my base logic Carmo and Jones's dyadic deontic logic, or DDL, which improves on SDL \citep{CJDDL}. 
 It introduces a dyadic obligation operator $O\{A \vert B\}$ 
-to represent the sentence ``A is obligated in the context B". This gracefully handles contrary-to-duty
-conditionals. The obligation operator uses a neighborhood semantics \cite{neighborhood1, neighborhood2}, instead of the Kripke semantics. 
-Carmo and Jones define a function $ob$ that maps from worlds to sets of sets of worlds. Intuitively, 
-each world is mapped to the set of propositions obligated at that world, where a proposition $p$ is defined as 
-the worlds at which the $p$ is true.
-
-DDL also includes other modal operators. In addition to $\Box$ and $\diamond$, DDL also has a notion
+to represent the sentence ``A is obligated in the context B". The introduction of context allows DDL to
+gracefully handle contrary-to-duty conditionals by modifying the context. The obligation operator uses 
+a neighborhood semantics, instead of the Kripke semantics \citep{neighborhood1, neighborhood2}. While Kripke
+semantics requires that an obligated proposition hold at all worlds, the neighborhood semantics defines
+a different set of neighbors, or morally relevant alternatives, for each world. To represent this,
+Carmo and Jones define a function $ob$ that maps from a given context (or world) to the propositions 
+that are obligatory at this world, where a proposition $p$ is defined as 
+the worlds at which the $p$ is true. DDL is thus both modal and deontic; statements about obligations are
+true or false at a world according to the neighbordhood 
+semantics, and different obligations may hold at different worlds. This property is particularly relevant to my work because the universalizability test
+requires reasoning about alternative worlds, such as the world of the universalized maxim.
+
+DDL also includes modal operators. In addition to $\Box$ and $\diamond$, DDL also has a notion
 of actual obligation and possible obligation, represented by operators $O_a$ and $O_p$ respectively. 
@@
 These operators use a Kripke semantics, with the functions $av$ and $pv$ mapping a world $w$ to the set 
-of corresponding actual or possible versions of $w$.
-
-For more of fine-grained properties of DDL see \citep{CJDDL} or this project's source code. DDL is a heavy logic and contains modal operators 
+of corresponding actual or possible versions of $w$. These operators are not relevant to the work in 
+this thesis, but this additional expressivity could be used to extend my project to incorporate 
+more sophisticated ethical concepts like counterfactuals.
+
+For more of fine-grained properties of DDL see \citet{CJDDL} or this project's source code. DDL is a heavy logic and contains modal operators 
 that aren't necessary for my analysis. While this expressivity is powerful, it may also cause performance
-impacts. DDL has a large set of axioms involving quantification over complex higher-order
+issues. DDL has a large set of axioms involving quantification over complex higher-order
 logical expressions. Proofs involving these axioms will be computationally expensive. I do not run 
@@
 The final component of my project is the automated theorem prover I use to automate my formalization.
-Isabelle/HOL is an interactive proof assistant built on Haskell and Scala \cite{isabelle}. It 
+Isabelle/HOL is an interactive proof assistant built on Haskell and Scala \citep{isabelle}. It 
 allows the user to define types, functions, definitions, and axiom systems. It has built-in support for both
-automatic and interactive/manual theorem proving.
-
-I started my project by reimplementing Benzmueller, Farjami, and Parent's implementation 
-of DDL in Isabelle/HOL \cite{BFP, logikey}. This helped me learn how to use Isabelle/HOL, and the implementation showcased in the 
-next few sections demonstrates the power of Isabelle.
-
-Benzmueller, Farjami, and Parent use a shallow semantic embedding. This kind of embedding models the semantics of DDL as 
-constants in HOL and axioms as constraints on DDL models. This document will contain a subset of my 
-implementation that is particularly interesting and relevant to understanding the rest of the project. 
-For the complete implementation, see the source code in \isatt{paper22.thy}.%
+automatic and interactive/manual theorem proving. To demonstrate the power and usage of Isabelle and 
+make DDL more precise, I walk through my reimplementation
+of Benzmueller, Farjami, and Parent's implementation of DDL in Isabelle/HOL \cite{BFP, logikey}.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-The first step in embedding a logic in Isabelle is defining the relevant terms and types.%
+The first step in embedding a logic in Isabelle is defining the relevant terms and types. Commands
+to do this include \texttt{typedecl}, which declares a new type, \texttt{type\_synonym}, which defines
+an abbreviation for a complex type, and \texttt{consts}, which defines a constant.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \isamarkupcmt{A set of formulae is defined by its truth value at a set of worlds. For example, the set \{True\}
-would be true at any set of worlds.%
+is true at any set of worlds.%
 }\isanewline
@@
 \begin{isamarkuptext}%
-The main accessibility relation that I will use is the $ob$ relation:%
+The $ob$ function described in Section \ref{ddl} is used to determine which propositions are obligatory
+in which contexts.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-For a semantic embedding, axioms are modelled as restrictions on models of the system. In this case,
-a model is specificied by the relevant accessibility relations, so it suffices to place conditions on 
-the accessibility relations. These axioms can be quite unweildy, so luckily I was able to lift BFP's 
-implementation of Carmo and Jones's original axioms directly \citep{BFP}. Here's an example of an axiom:%
-\end{isamarkuptext}\isamarkuptrue%
-\isanewline
-\isakeyword{and}\ ax{\isacharunderscore}{\isadigit{5}}d{\isacharcolon}\ {\isachardoublequoteopen}{\isasymforall}X\ Y\ Z{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isasymforall}w{\isachardot}\ Y{\isacharparenleft}w{\isacharparenright}{\isasymlongrightarrow}X{\isacharparenleft}w{\isacharparenright}{\isacharparenright}\ {\isasymand}\ ob{\isacharparenleft}X{\isacharparenright}{\isacharparenleft}Y{\isacharparenright}\ {\isasymand}\ {\isacharparenleft}{\isasymforall}w{\isachardot}\ X{\isacharparenleft}w{\isacharparenright}{\isasymlongrightarrow}Z{\isacharparenleft}w{\isacharparenright}{\isacharparenright}{\isacharparenright}\ \isanewline
+In a semantic embedding, axioms are modelled as restrictions on models of the system. In this case,
+a model is specificied by the relevant accessibility relations (such as $ob$), so it suffices to place conditions on 
+the accessibility relations. Isabelle allows users to create new axiomatizations on top of its base
+logic (HOL) and use these axioms in proofs. Here's an example of an axiom:%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{axiomatization}\isamarkupfalse%
+\ \isakeyword{where}ax{\isacharunderscore}{\isadigit{5}}d{\isacharcolon}\ {\isachardoublequoteopen}{\isasymforall}X\ Y\ Z{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isasymforall}w{\isachardot}\ Y{\isacharparenleft}w{\isacharparenright}{\isasymlongrightarrow}X{\isacharparenleft}w{\isacharparenright}{\isacharparenright}\ {\isasymand}\ ob{\isacharparenleft}X{\isacharparenright}{\isacharparenleft}Y{\isacharparenright}\ {\isasymand}\ {\isacharparenleft}{\isasymforall}w{\isachardot}\ X{\isacharparenleft}w{\isacharparenright}{\isasymlongrightarrow}Z{\isacharparenleft}w{\isacharparenright}{\isacharparenright}{\isacharparenright}\ \isanewline
 \ \ {\isasymlongrightarrow}ob{\isacharparenleft}Z{\isacharparenright}{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isacharparenleft}Z{\isacharparenleft}w{\isacharparenright}\ {\isasymand}\ {\isasymnot}X{\isacharparenleft}w{\isacharparenright}{\isacharparenright}\ {\isasymor}\ Y{\isacharparenleft}w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
 %
-\isamarkupcmt{If some subset Y of X is obligatory in the context X, then in a larger context Z,
- any obligatory proposition must either be in Y or in Z-X. Intuitively, expanding the context can't 
+\isamarkupcmt{If some subset $Y$ of $X$ is obligatory in the context $X$, then in a larger context $Z$,
+ any obligatory proposition must either be in $Y$ or in $Z \setminus X$. Intuitively, expanding the context can't 
 cause something unobligatory to become obligatory, so the obligation operator is monotonically increasing
@@
 \begin{isamarkuptext}%
-The syntax that I will work with is defined as abbreviations. Each DDL operator is represented 
+The axiomatization above defined the semantics of DDL and, as demonstrated by the example axiom,
+was unwieldly. In my work, I mostly perform syntactic proofs, so I must define the syntax of the logic.
+Isabelle already knows the axioms of this logic, so I can define the syntax as abbreviations for different
+formulas involving the axioms above. Each DDL operator is represented
 as a HOL formula. Isabelle automatically unfolds formulae defined with the \isatt{abbreviation} command 
 whenever they are applied. While the shallow embedding is performant (because it uses Isabelle's original 
-syntax tree), abbreviations may hurt performance. In some complicated proofs, we want to control definition
-unfolding. Benzmueller and Parent told me that the performance cost of abbreviations can 
-be mitigated using a definition instead.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-Modal operators will be useful for my purposes, but the implementation is pretty standard.%
+syntax tree), abbreviations may hurt performance.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+Modal operators will be useful for my purposes, and this how they are implemented.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-The most important operator for our purposes is the obligation operator.%
+The most important operator for my project is the obligation operator.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 While DDL is powerful because of its support for a dyadic obligation operator, in many cases 
-we need a monadic obligation operator. Below is some syntactic sugar for a monadic obligation operator.%
+I only need a monadic obligation operator. Below is some syntactic sugar for a monadic obligation operator.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupcmt{Intuitively, the context \texttt{True} is the widest context possible because \texttt{True} holds at all worlds.%
+\isamarkupcmt{Intuitively, the context $True$ is the widest context possible because $True$ holds at all worlds.%
 }%
@@
 %
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\isatagdocument
-%
-\isamarkupsubsubsection{Syntactic Properties%
-}
-\isamarkuptrue%
-%
-\endisatagdocument
-{\isafolddocument}%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\begin{isamarkuptext}%
-One way to show that a semantic embedding is complete is to show that the syntactic specification
-of the theory (axioms) are valid for this semantics - so to show that every axiom holds at every 
-world. Benzmueller, Farjami, and Parent provide a complete treatment of the completeness of their embedding, but I 
-will include selected axioms that are particularly interesting here. This section also demonstrates many
-of the relevant features of Isabelle/HOL for my project.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-\textbf{Consistency}%
+\isamarkupcmt{A proposition is valid if it is true at all worlds.%
+}\isanewline
+%
+\begin{isamarkuptext}%
+Benemueller, Farjami, and Parent provide a proof of the completeness of the above embedding \citep{BFP}.
+Isabelle allows us to check consistency immediately using Nitpick, a model checker \citep{nitpick}.
+Nitpick can find satisfying models for a particular lemma using the \texttt{satisfy} option and it can 
+find counterexamples. I use it extensively in proofs in this prokect.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupcmt{Isabelle has built-in support for Nitpick, a model checker. 
-Nitpick successfully found a model satisfying these axioms so the system is consistent.%
+\isamarkupcmt{This an example of a typical Nitpick output. In this case, Nitpick successfully found a model 
+satisfying these axioms so the system is consistent.%
 }\isanewline
@@
 \begin{isamarkuptext}%
-Nitpick \cite{nitpick} can generate models or countermodels, so it's useful to falsify potential
-theorems, as well as to show consistency. {\color{red} by simp} indicates the proof method. In this 
-case, {\color{red} simp} indicates the Simplification proof method, which involves unfolding definitions
-and applying theorems directly. HOL has $True$ as a theorem, which is why this theorem was so easy to prove.%
+In the proof above, {\color{red} by simp} indicates the use of the Simplification proof method, 
+which involves unfolding definitions and applying theorems directly. HOL has $True$ as a theorem,
+which is why this theorem was so easy to prove.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %:%451=324%:%
-%:%452=325%:%
-%:%453=326%:%
-%:%454=327%:%
-%:%455=328%:%
-%:%459=330%:%
+%:%455=326%:%
+%:%459=328%:%
+%:%460=329%:%
+%:%461=330%:%
+%:%462=331%:%
 %:%463=332%:%
@@
 %:%479=348%:%
-%:%480=349%:%
-%:%481=350%:%
-%:%482=351%:%
-%:%483=352%:%
-%:%484=353%:%
-%:%485=354%:%
-%:%486=355%:%
-%:%490=359%:%
-%:%494=361%:%
-%:%495=362%:%
-%:%496=363%:%
-%:%497=364%:%
-%:%498=365%:%
-%:%499=366%:%
-%:%500=367%:%
-%:%501=368%:%
-%:%502=369%:%
-%:%503=370%:%
-%:%504=371%:%
-%:%505=372%:%
-%:%506=373%:%
-%:%507=374%:%
-%:%508=375%:%
-%:%509=376%:%
-%:%510=377%:%
-%:%511=378%:%
-%:%512=379%:%
-%:%513=380%:%
-%:%514=381%:%
-%:%515=382%:%
-%:%516=383%:%
-%:%517=384%:%
-%:%518=385%:%
-%:%519=386%:%
-%:%520=387%:%
-%:%529=390%:%
-%:%541=392%:%
-%:%542=393%:%
+%:%483=351%:%
+%:%487=353%:%
+%:%488=354%:%
+%:%489=355%:%
+%:%490=356%:%
+%:%491=357%:%
+%:%492=358%:%
+%:%493=359%:%
+%:%494=360%:%
+%:%495=361%:%
+%:%496=362%:%
+%:%497=363%:%
+%:%498=364%:%
+%:%499=365%:%
+%:%500=366%:%
+%:%501=367%:%
+%:%502=368%:%
+%:%503=369%:%
+%:%504=370%:%
+%:%505=371%:%
+%:%506=372%:%
+%:%507=373%:%
+%:%508=374%:%
+%:%509=375%:%
+%:%510=376%:%
+%:%511=377%:%
+%:%512=378%:%
+%:%513=379%:%
+%:%514=380%:%
+%:%515=381%:%
+%:%516=382%:%
+%:%517=383%:%
+%:%526=385%:%
+%:%538=388%:%
+%:%539=389%:%
+%:%540=390%:%
+%:%541=391%:%
+%:%542=392%:%
+%:%543=393%:%
+%:%544=394%:%
+%:%545=395%:%
 %:%546=396%:%
@@
 %:%571=421%:%
-%:%575=423%:%
-%:%576=424%:%
-%:%577=425%:%
-%:%578=426%:%
-%:%579=427%:%
-%:%580=428%:%
-%:%581=429%:%
-%:%582=430%:%
-%:%583=431%:%
-%:%584=432%:%
-%:%585=433%:%
-%:%586=434%:%
-%:%587=435%:%
-%:%588=436%:%
-%:%589=437%:%
-%:%590=438%:%
-%:%591=439%:%
-%:%592=440%:%
-%:%593=441%:%
-%:%602=444%:%
-%:%614=446%:%
-%:%615=447%:%
+%:%572=422%:%
+%:%573=423%:%
+%:%574=424%:%
+%:%575=425%:%
+%:%576=426%:%
+%:%577=427%:%
+%:%578=428%:%
+%:%579=429%:%
+%:%580=430%:%
+%:%581=431%:%
+%:%582=432%:%
+%:%583=433%:%
+%:%584=434%:%
+%:%585=435%:%
+%:%586=436%:%
+%:%587=437%:%
+%:%588=438%:%
+%:%589=439%:%
+%:%590=440%:%
+%:%599=442%:%
+%:%611=444%:%
+%:%612=445%:%
 %:%616=448%:%
@@
 %:%626=458%:%
-%:%635=461%:%
-%:%647=463%:%
-%:%649=465%:%
-%:%650=465%:%
-%:%651=465%:%
-%:%652=465%:%
-%:%653=466%:%
-%:%654=467%:%
-%:%655=467%:%
-%:%656=467%:%
-%:%657=467%:%
-%:%659=468%:%
-%:%660=469%:%
-%:%661=469%:%
-%:%664=483%:%
-%:%666=485%:%
-%:%667=485%:%
-%:%668=485%:%
-%:%669=485%:%
-%:%670=486%:%
-%:%671=486%:%
-%:%672=486%:%
-%:%680=490%:%
-%:%692=492%:%
-%:%693=493%:%
-%:%694=494%:%
-%:%695=495%:%
-%:%697=519%:%
-%:%698=520%:%
-%:%699=521%:%
-%:%701=522%:%
-%:%702=523%:%
-%:%703=524%:%
-%:%704=525%:%
-%:%705=525%:%
-%:%713=532%:%
-%:%725=534%:%
-%:%726=535%:%
-%:%727=536%:%
-%:%728=537%:%
-%:%729=538%:%
-%:%730=539%:%
-%:%734=555%:%
-%:%736=556%:%
-%:%737=556%:%
-%:%738=557%:%
-%:%739=558%:%
-%:%740=558%:%
-%:%741=559%:%
-%:%743=561%:%
-%:%745=562%:%
-%:%746=562%:%
-%:%747=563%:%
-%:%749=564%:%
-%:%750=564%:%
-%:%753=584%:%
-%:%754=585%:%
-%:%756=586%:%
-%:%757=586%:%
-%:%758=587%:%
-%:%759=588%:%
-%:%760=588%:%
-%:%761=589%:%
-%:%762=590%:%
-%:%763=590%:%
-%:%764=591%:%
-%:%766=592%:%
-%:%769=594%:%
-%:%771=595%:%
-%:%772=595%:%
-%:%773=596%:%
-%:%781=605%:%
-%:%793=607%:%
-%:%794=608%:%
-%:%795=609%:%
-%:%796=610%:%
-%:%797=611%:%
-%:%801=613%:%
-%:%803=614%:%
-%:%804=614%:%
-%:%805=614%:%
-%:%807=614%:%
-%:%811=614%:%
+%:%627=459%:%
+%:%628=460%:%
+%:%629=461%:%
+%:%630=462%:%
+%:%631=463%:%
+%:%632=464%:%
+%:%633=465%:%
+%:%634=466%:%
+%:%635=467%:%
+%:%636=468%:%
+%:%637=469%:%
+%:%638=470%:%
+%:%639=471%:%
+%:%640=472%:%
+%:%641=473%:%
+%:%642=474%:%
+%:%646=476%:%
+%:%647=477%:%
+%:%648=478%:%
+%:%649=479%:%
+%:%650=480%:%
+%:%651=481%:%
+%:%652=482%:%
+%:%653=483%:%
+%:%654=484%:%
+%:%655=485%:%
+%:%656=486%:%
+%:%657=487%:%
+%:%658=488%:%
+%:%659=489%:%
+%:%660=490%:%
+%:%661=491%:%
+%:%662=492%:%
+%:%663=493%:%
+%:%664=494%:%
+%:%665=495%:%
+%:%666=496%:%
+%:%667=497%:%
+%:%668=498%:%
+%:%669=499%:%
+%:%670=500%:%
+%:%671=501%:%
+%:%672=502%:%
+%:%681=505%:%
+%:%693=507%:%
+%:%694=508%:%
+%:%695=509%:%
+%:%696=510%:%
+%:%697=511%:%
+%:%698=512%:%
+%:%707=515%:%
+%:%719=517%:%
+%:%720=518%:%
+%:%721=519%:%
+%:%723=521%:%
+%:%724=521%:%
+%:%725=521%:%
+%:%726=521%:%
+%:%727=522%:%
+%:%728=523%:%
+%:%729=523%:%
+%:%730=523%:%
+%:%731=523%:%
+%:%733=524%:%
+%:%734=525%:%
+%:%735=525%:%
+%:%738=539%:%
+%:%739=540%:%
+%:%741=542%:%
+%:%742=542%:%
+%:%743=542%:%
+%:%744=542%:%
+%:%745=543%:%
+%:%746=543%:%
+%:%747=543%:%
+%:%755=547%:%
+%:%767=549%:%
+%:%768=550%:%
+%:%769=551%:%
+%:%770=552%:%
+%:%772=554%:%
+%:%773=554%:%
+%:%773=577%:%
+%:%774=578%:%
+%:%776=579%:%
+%:%777=580%:%
+%:%778=581%:%
+%:%779=582%:%
+%:%780=582%:%
+%:%788=589%:%
+%:%800=591%:%
+%:%801=592%:%
+%:%802=593%:%
+%:%803=594%:%
+%:%804=595%:%
+%:%805=596%:%
+%:%806=597%:%
+%:%810=613%:%
 %:%812=614%:%
+%:%813=614%:%
 %:%814=615%:%
@@
 %:%816=616%:%
-%:%818=617%:%
-%:%819=618%:%
-%:%820=619%:%
-%:%830=621%:%
-%:%831=622%:%
-%:%832=623%:%
-%:%833=624%:%
+%:%817=617%:%
+%:%819=619%:%
+%:%821=620%:%
+%:%822=620%:%
+%:%823=621%:%
+%:%825=622%:%
+%:%826=622%:%
+%:%829=642%:%
+%:%830=643%:%
+%:%832=644%:%
+%:%833=644%:%
+%:%834=645%:%
+%:%835=646%:%
+%:%836=646%:%
+%:%837=647%:%
+%:%838=648%:%
+%:%839=648%:%
+%:%840=649%:%
+%:%842=650%:%
+%:%845=652%:%
+%:%847=653%:%
+%:%848=653%:%
+%:%849=654%:%
+%:%851=655%:%
+%:%852=655%:%
+%:%855=663%:%
+%:%856=664%:%
+%:%857=665%:%
+%:%858=666%:%
+%:%860=669%:%
+%:%861=669%:%
+%:%862=669%:%
+%:%864=669%:%
+%:%868=669%:%
+%:%869=669%:%
+%:%871=670%:%
+%:%872=671%:%
+%:%873=671%:%
+%:%875=672%:%
+%:%876=673%:%
+%:%877=674%:%
+%:%887=676%:%
+%:%888=677%:%
+%:%889=678%:%

### 2022-02-08 paper/output/document/thesis_2_methods.tex
all i do is clean methods

@@
 \begin{isamarkuptext}%
-My system consists of three major components: an ethical theory (Kantian ethics), a logic in which
+My system consists of three components: an ethical theory (Kantian ethics), a logic in which
 I formalize this ethical theory (Dyadic Deontic Logic), and an interactive theorem prover in which I 
 implement the formalized ethical theory (Isabelle/HOL). In this section, I describe these components, 
-present the philosophical, logic, and computational background that undergirds my system, and explain
+present the philosophical, logic, and computational background underlying my system, and explain
 the consequences of each of the three choices I make.
@@
 These specific components determine the features
-and limitations of the specific implementation of automated ethics that I present, but other choices of 
+and limitations of my implementation of automated ethics, but other choices of 
 components, such as another ethical theory, a different logic, or a different theorem prover could be 
-made. Given that my system is a proof-of-concept, I choose system components that are natural and 
-intuitively fit together, but other choice could also be valid and perhaps even superior.
-
-I do not claim
-that I have chosen the best ethical theory or the best logic or the best interactive theorem prover, 
-and flaws with these components merely demonstrate that my specific choices were incorrect, but do not 
-indict logic-programming-based automated ethics as I implement it in this thesis. My thesis seeks to 
+made. Flaws with these components are merely limitations of my system, but do not 
+indict logic-programming-based automated ethics more generally. My thesis seeks to 
 both present a specific implementation of automated ethics but also to argue for a particular approach 
@@
 present a sample of some approaches in each tradition and argue that deontology is more straightforward 
-to formalize than these approaches. Future work could and should address the challenges I outline in 
-this section. The more ethical theories that computational tools can handle, the more valuable 
-computational philosophy becomes both for philosophers and for AI agents. Insofar as my project serves 
-as an early proof-of-concept for computational ethics, I choose to automate an ethical theory that 
+to formalize than these approaches. Insofar as my project serves 
+as an early proof-of-concept, I choose to automate an ethical theory that 
 poses fewer challenges than others.
@@
 deontological theory I am automating (Kantian ethics) and will argue that it is comparatively easier
-to formalize. I will also outline the specific debates in the literature that my formalization takes
-a stance on and potential challenges for formalizing deontology.%
+to formalize.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-Deontological ethical theories evaluate actions as permissible, obligatory, or prohibited. The 
-deontological tradition argues that an action should not be judged on its consequences, 
-but rather on ``its confirmity with a moral norm" \citep{sepdeont}. In other words, deontological theories
-define a set of moral norms or rules and evaluate actions using
-these rules. Deontologists do not believe that we should maximize the number of times that we 
-conform to such rules, but instead that we should never violate any of the moral laws. A wrong
+Deontological theories evaluate actions as permissible, obligatory, or prohibited and judge actions 
+not on their consequences, but rather on ``confirmity with a moral norm" \citep{sepdeont}. In other words, 
+deontological theories define a set of moral rules and evaluate actions using
+these rules. Deontologists believe that we should never violate any moral law. A wrong
 choice is wrong, regardless of its consequences.%
@@
 \begin{isamarkuptext}%
-Deontology is immediately an attractive candidate for formalization because computers tend to 
+Deontology is an attractive candidate for formalization because computers tend to 
 understand rules; programming languages are designed to teach computers algorithms. Deontological
 ethical theories give inviolable rules that an automated agent can apply. Moreover, because deontological 
-theories focus on
-the action itself, they require relatively little data. A deontological moral judgement does not require
+theories focus on the action itself, they require relatively little data. A deontological moral judgement does not require
 as much information about context, consequences, or moral character as the other theories presented later in this
 section. All that matters is the action and some limited set of circumstances in which it is performed.
-I will later argue that, in the case of the specific deontological ethic that I implement (Kantian ethics), 
-the action's representation is space efficient.
 
@@
 traditions considered in this section, deontology has the most central representative in the form of 
-Kant. Many modern deontologists agree on Kant's ethic but disagree in how to interpret it. In this paper, I will 
+Kant. In this paper, I will 
 formalize Kantian ethics. Deontology's comparatively greater focus on Kant means that the choice of 
@@
 of an action from the action itself. Some debates in the consequentialist tradition include 
-which consequences of an action matter, what exactly constitutes a ``good" consequence, and how we can 
+which consequences matter, what constitutes a ``good" consequence, and how we can 
 aggregate the consequences of an action over all the individuals involved.%
@@
 if not impossible, task. Moreover, compiling this database of consequences requires 
-answering difficult questions about which consequences were actually caused by an action.\footnote
+answering difficult questions about which consequences were actually caused \footnote
 {David Hume argues that many straightforward accounts of causation face difficulties \citep{hume}, 
-and philosohpers continue to debate the possiblity of knowing an event's true cause. Kant even argued
-that first causes, or noumena, are unknowable by human beings \citep{kantnoumena}.}
-Evaluating an effect of an action requires knowledge about the 
-state of the world before and after an action and knowledge about the action itself. Consequentialism requires 
-knowledge about the situation in which the act is performed and following the act, whereas deontology mostly requires 
-knowledge about the act itself. As acts become
+and philosophers continue to debate the possiblity of knowing an event's true cause. Kant even argued
+that first causes, or noumena, are unknowable by human beings \citep{kantnoumena}.} by an action and
+determining the state of the world before and after an action. As acts become
 more complex and affect more people, the computational time and space required to calculate and store
@@
 The challenge of representing the circumstances of action is not unique to consequentialism, but is particularly acute in this case. 
-Kantian ethicists robustly debate which circumstances of an action are ``morally relevant'' when evaluating an action's moral worth.\footnote{Powers
+Kantian ethicists robustly debate which circumstances of an action are ``morally relevant'' when evaluating an action's moral worth.\footnote{ 
 \citet{powers} identifies this as a challenge for automating Kantian ethics and briefly sketches 
@@
 morally relevant circumstances, see Section WhatIsAMaxim.} Because deontology merely evaluates a 
-single action, the surface of this debate is much smaller than the debate about circumstances and 
+single action, the surface of this debate is much smaller than debates about circumstances and 
 consequences in a consequentialist system. An automated consequentialist system must make such 
@@
 An automated consequentialist reasoner must also take a stance on the debate over
-what qualifies as a ``good consequence," or what the theory of the good is. For example, hedonists associate
+what qualifies as a ``good consequence,'' or what the theory of the good is. For example, hedonists associate
 good with the presence of pleasure and the absence of pain, while preference utiliarians believe that good is 
-the satisfaction of individuals' desires. Other consequentialists, like Moore, adopt a pluralistic theory of value, under which 
+the satisfaction of desire. Other consequentialists, like Moore, adopt a pluralistic theory of value, under which 
 many different kinds of things are good for different reasons \citep{moorepe}.
 
-Most of the above theories of good require that a moral reasoner understand complex features about
+Most theories of the good require that a moral reasoner understand complex features about
 individuals' preferences, desires, or sensations in order to evaluate a moral action, making automated
-consequentialist ethics difficult. Evaluating a state of affairs requires
+consequentialist ethics difficult. Evaluating a state of affairs requires many controversial
 judgements about whether a state of affairs actually satisifes the relevant criteria for goodness. 
-These judgements are controversian, and any consequentialist decision requires many of 
-these judgements for each individual involved. As systems involve more people, making these judgements 
-quickly becomes difficult, posing a scaling challenger. Perfect knowledge of tens of thousands of 
+Perfect knowledge of tens of thousands of 
 people's pleasure or preferences or welfare or rights is impossible. Either a human being 
 assigns values to states of affairs, which doesn't scale, or the machine does, 
-which requires massive common-sense and increases room for doubting the system's judgements. This is 
+which requires massive common-sense and increases room for doubting the system's judgements. This may be 
 a tractable problem, but it is much more difficult than the equivalent deontological task of formulating
@@
 this value is to aggregate each person's individual goodness score into one complete score for a state. 
-For example, under a simple welfare model, each person is assigned a welfare score and the total 
-score for a state of affairs is the sum of the welfare scores for each involved person.
 The more complex the theory of the good, the more difficult this aggregation becomes. For example, 
 pluralistic theories struggle to explain how different kinds of value can be compared \citep{consequentialismsep}. 
-How do we compare one unit of beauty to one unit of pleasure? Subjective theories of the good, such 
-as those focused on the sensation of pleasure or an individual's preferences, present difficulties in 
-comparing different people's subjective measures. Resolving this debate requires that the automated reasoner 
+How do we compare one unit of beauty to one unit of pleasure? Resolving this debate requires that an automated reasoner 
 choose one specific aggregation algorithm, but those who disagree with this choice will not trust 
@@
 To solve this problem, some consequentialists reject aggregation entirely and instead prefer wholistic
-evaluations of a state of affairs. While this approach no longer requires that a reasoner define an 
-aggregation algorithm, the reasoner still needs to calculate a goodness measurement for a state of 
-affairs. Whereas before the reasoner could restrict analysis to a single person, the algorithm must now 
+evaluations of a state of affairs. While this approach no longer requires that an 
+aggregation algorithm, an automated ethical system still needs to calculate a goodness measurement for a state of 
+affairs. Whereas before the system could restrict its analysis to a single person, the algorithm must now 
 evaluate an entire state wholistically. As consequentialists modulate between aggregation 
@@
 reward is accumulated in an MDP.\footnote{Generally, reward for an MDP is accumulated according to a 
-``discount factor" $\gamma < 1$, such that if $r_i$ is the reward at time $i$, the total reward is $\sum_{i=0}^{\infty}\gamma^i r_i$.} 
+``discount factor'' $\gamma < 1$, such that if $r_i$ is the reward at time $i$, the total reward is $\sum_{i=0}^{\infty}\gamma^i r_i$.} 
 It leaves open the question of what the reward function is and thus 
@@
 stance on the aggregation question. Other attempts to automate consequentialist ethics will suffer 
-similar problems because, at some point, a useful automated consequentialist moral agent will need 
+similar problems because, at some point, a usable automated consequentialist moral agent will need 
 to resolve the above debates.%
@@
 Virtue ethics places the virtues, or traits that constitute a good moral character and make 
-their possessor good, at the center \cite{vesep}. For example, Aristotle describes virtues as the 
+their possessor good, at the center \citep{vesep}. For example, Aristotle describes virtues as the 
 traits that enable human flourishing. Just as consequentialists define ``good'' consequences, virtue 
-ethicists present a list of virtues. Such theories vary from Aristotle's virtues of courage and 
-temperance \citet{aristotle} to the Buddhist virtue of equanimity \citet{mcrae}. An automated virtue 
+ethicists present a list of virtues, such as the Buddhist virtue of equanimity \citep{mcrae}. An automated virtue 
 ethical agent will need to commit to a particular theory of the virtues, a controversial choice. 
@@
 \begin{isamarkuptext}%
-Another difficulty with automating virtue ethics is that the unit of evaluation for a virtue ethical
-theory is often a person's entire moral character. While deontologists evaluate the act itself and utilitarians
-evaluate the consequences of an act, virtue ethicists evaluate the actor's moral character and their 
-disposition towards the act. Virtues are character traits and evaluating an action as virtuous or 
-not requires understanding the agent's character and disposition while acting. If states of affairs
+Another difficulty with automating virtue ethics is that the unit of evaluation for virtue ethics
+is often a person's entire moral character. While deontologists evaluate the act itself, virtue ethicists 
+evaluate the actor's moral character and their 
+disposition towards the act. If states of affairs
 require complex representations, an agent's ethical character and disposition are even more difficult
-to represent to a computer. Consequentialism posed a data-collection problem in evaluating and representing states
-of affairs, but virtue ethics poses a conceptual problem about the formal nature of moral character.
+to represent to a computer. This is more than just a data-collecting problem; it is a conceptual problem 
+about the formal nature of moral character.
 Formalizing the concept of character appears to require significant philosophical and computational
@@
 \begin{isamarkuptext}%
-One potential appeal of virtue ethics is that many virtue ethical theories involve some form of 
+One potential appeal of virtue ethics is that many virtue ethical theories involve some notion of 
 moral habit, which seems to be amenable to a machine learning approach. Artistotle, for example, argued 
 that cultivating virtuous action requires making such action habitual through moral education \citep{aristotle}. This
-imply that ethical behavior can be learned from some dataset of virtuous acts, either those 
-prescribed by a moral teacher or those that a virtuous ideal agent would undertake. Indeed, these 
-theories seem to point towards a machine learning approach to computational ethics, in which ethics is 
+implies that ethical behavior can be learned from some dataset of virtuous acts, either those 
+prescribed by a moral teacher or those that a virtuous ideal agent would undertake. These 
+theories seem to point towards a machine learning approach to automated ethics, in which ethics is 
 learned from a dataset of acts tagged as virtuous or not virtuous.
@@
 
-Machine learning approaches like the Delphi system \citep{delphi} mentioned in \ref{intro} also may suffer explanability 
+Machine learning approaches like the Delphi system \citep{delphi} mentioned in Chapter \ref{intro} also may suffer explanability 
 problems that my logic-programming, theorem-prover
 approach does not face. Many machine learning algorithms cannot sufficiently explain their 
-decisions to a human being, and often find patterns or correlations in datasets that don't actually 
-cohere with the trends and causes that a human being would identify \citep{puiutta}. While there is significant activity 
+decisions to a human being, and often find patterns in datasets that don't 
+cohere with the causes that a human being would identify \citep{puiutta}. While there is significant activity 
 and progress in explainable machine learning, interactive theorem provers are designed to be explainable 
-at the outset. Indeed, Isabelle can show the axioms and lemmas it used in constructing a proof, 
+at the outset. Isabelle can show the axioms and lemmas it used in constructing a proof, 
 allowing a human being to reconstruct the proof independently if they wish. This is not an 
@@
 on practical reason, which is the kind of reason that we 
-use to decide what to do. In \emph{The Groundwork of the Metaphysics of Morals}, Kant explains that 
-rational beings are unique because we can act ``in accordance with 
-the representations of laws" \citep[4:412]{groundwork}. In contrast, a ball thrown into the air acts 
-according to the laws of physics. It cannot ask itself, ``Should I fall back to the ground?" 
-It simply falls. A rational being, on the other hand, can ask, ``Should I act on this reason?" 
+use to decide what to do and the source of our agency. In \emph{The Groundwork of the Metaphysics of Morals}, Kant explains that 
+rational beings are unique because we act ``in accordance with 
+the representations of laws'' \citep[4:412]{groundwork}. In contrast, a ball thrown into the air acts 
+according to the laws of physics. It cannot ask itself, ``Should I fall back to the ground?'' 
+It simply falls. A rational being, on the other hand, can ask, ``Should I act on this reason?"''
 As Korsgaard describes it, when choosing which desire to act on, ``it is as if there is something over 
-and above all of your desires, something which is you, and which chooses which desire to act on" \citep[100]{sources}. 
-Rational beings are set apart by this reflective capacity. A rational being's behavior is purposive and 
-their actions are guided by practical reason. They have reasons for acting, even when these reasons are
-opaque to them. This reflective choosing, or operation of practical reason, is what Kant calls the will.
+and above all of your desires, something which is you, and which chooses which desire to act on'' \citep[100]{sources}. 
+Rational beings are set apart by this reflective capacity. We are purposive and 
+our actions are guided by practical reason. We have reasons for acting, even when these reasons are
+opaque to us. This reflective choosing, or operation of practical reason, is what Kant calls the will.
 
 The will operates by adopting, or willing, maxims, which are its perceived reasons for acting. Kant defines a maxim as 
-the ``subjective principle of willing," or the reason that the will \emph{subjectively} gives 
+the ``subjective principle of willing,'' or the reason that the will \emph{subjectively} gives 
 to itself for acting \citep[16 footnote 1]{groundwork}. Many philosophers agree that a maxim consists 
@@
 act, and goal.\footnote{For more discussion of the definition of a maxim, see Section What Is a Maxim}
-One example of a maxim is ``When I am hungry, I will eat a doughnut in order to satisfy my sweet tooth." 
+One example of a maxim is ``When I am hungry, I will eat a doughnut in order to satisfy my sweet tooth.''
 When an agent wills this maxim, they decide to act on it. They commit themselves to the end in the maxim 
@@
 An imperative is a command, such as ``Close the door" or ``Eat the doughnut in order to satisfy your 
-sweet tooth." An imperative is categorical if it holds unconditionally for all rational agents under all 
+sweet tooth." An imperative is categorical if it holds unconditionally for all rational agents in all 
 circumstances. Kant argues that the moral law must be a categorical imperative \citep[5]{groundwork}. 
@@
 Armed with this understanding of practical reason, Kant presents the categorical 
-imperative. He presents three ``formulations" or versions of the categorical imperative and goes on to 
-argue that all three formulations are equivalent. In this project, I focus on the first formulation,
-the Formula of Universal Law, and I explain this choice in Section \ref{whyful}.
-
-The first formulation of the categorical imperative is the
-Formula of Universal Law (FUL), which reads, ``act only according to that maxim through which you can 
-at the same time will that it become a universal law" \cite[34]{groundwork}. This formulation
-generates the universalizability test, which tests the moral value of a maxim by 
+imperative. He presents three ``formulations" or versions of the categorical imperative. In this project, 
+I focus on the first formulation, the Formula of Universal Law, and I explain this choice in Section \ref{whyful}.
+
+The Formula of Universal Law (FUL) states, ``act only according to that maxim through which you can 
+at the same time will that it become a universal law'' \cite[34]{groundwork}. This formulation
+generates the universalizability test, which we can use to test the moral worth of a maxim by 
 imagining a world in which it becomes a universal law and attempting to will the maxim in that world.
@@
 Velleman presents a concise argument for the FUL. He argues that reason is universally shared among reasoners. For 
-example, all reasoners have equal access to the arithmetic logic that shows that ``2+2=4" \cite[29]{velleman}. The chain of 
+example, all reasoners have equal access to the arithmetic logic that shows that ``2+2=4'' \cite[29]{velleman}. The 
 reasoning that makes this statement true is not specific to any person, but is universal across people. 
 Therefore, if I have sufficient reason to will a maxim, so does every other rational agent. There is 
-nothing special about the operation of my practical reason that other reasoners don't have access to. 
+nothing special about the operation of my practical reason. 
 In adopting a maxim, I implicitly state that all reasoners
@@
 FUL. Notice that this fulfills the above criterion for a categorical imperative: the FUL is derived from 
-a property of practical reason itself and thus derives authority from the will's authority over itself, 
-as opposed to some external authority.
-
-The above is not meant to serve as a full defense or articulation of Kant's ethical theory. Instead, I briefly reconstruct a sketch of Kant's ethical theory in the hopes 
-of offering context for the implementation of the FUL I present later in the thesis. Additionally, understanding 
-the structure of Kant's theory also reveals why it is an ideal candidate 
-for formalization.%
+a property of practical reason itself and thus derives authority from the will's authority over itself.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 knowledge beyond the circumstances included
-in the maxim itself and thus requires far less contingent facts than other ethical theories.
+in the maxim itself and thus requires fewer contingent facts than other ethical theories.
 While other ethical theories often rely on many facts about 
-the world or the actor, Kantian ethics simply relies on the form of a given maxim. A computer evaluating 
+the world or the actor, a computer evaluating 
 a maxim doesn't require any knowledge about the world beyond what is contained in a maxim. Automating 
 Kantian ethics merely requires making the notion of a maxim precise and representing it to the computer. 
-This distinguishes Kantian ethics from consequentialism and virtue ethics, which, as I argued above, 
+This distinguishes Kantian ethics from consequentialism and virtue ethics, which
 require far more knowledge about the world or the agent to reach a moral decision.
@@
 affairs or moral character. This property not only reduces the computational complexity
-(in terms of time and space) of representing a maxim, but it also make the system easier for human reasoners
+(in terms of time and space) of representing a maxim, but it also makes the system easier for human reasoners
 to interact with. A person crafting an input to a Kantian automated agent needs to reason about relatively
@@
 \begin{isamarkuptext}%
-\textbf{Difficulties in Automation}%
+\noindent \textbf{Difficulties in Automation}%
 \end{isamarkuptext}\isamarkuptrue%
@@
 One debate in Kantian 
-ethics is the role of ``common-sense" reasoning. Kantian ethics requires common-sense reasoning to 
-determine which circumstances are ``morally relevant" in the formulation of a maxim. Many misunderstandings
+ethics is the role of ``common-sense'' reasoning. Kantian ethics requires common-sense reasoning to 
+determine which circumstances are ``morally relevant'' in the formulation of a maxim. Many misunderstandings
 in Kantian ethics are due to badly formulated maxims, so this question is important for an ethical 
 reasoner to answer.\footnote{For example, critics of Kantian ethics worry that the maxim, ``When I am a
-man, I will marry a man because I want to spend my life with him" fails the universalizability
+man, I will marry a man because I want to spend my life with him'' fails the universalizability
 test because if all men only married men, sexual reproduction would stop. This argument implies 
 that Kantian ethics is homophobic. Kantians often respond by arguing that the correct formulation of 
-this maxim is, ``When I love a man, I will marry him because I want to spend my life with him," which
-is universalizable because if everyone marries who they love, some men will marry women.} 
-My system does not need to answer this question because I assume a well-formed
-maxim as input and apply the categorical imperative to this input, but if my system were ever to be used
-in a faully automated agent, answering this question would require significant computational and philosophical
-work. For more, see Section AI Ethics.
+this maxim is, ``When I love a man, I will marry him because I want to spend my life with him,'' which
+is universalizable because if everyone marries who they love, some men will marry women and others will
+marry men.} My system does not need to answer this question because I assume a well-formed
+maxim as input and apply the categorical imperative to this input. Using my system in a fully automated
+moral agent will require answering this question, a challenging computational and philosophical task.
 
 Common-sense reasoning is also relevant when applying the universalizability test itself. Consider the example
-maxim: ``When broke, I will falsely promise to repay a loan
-to get some quick cash." This maxim fails the universalizability test because in a world where everyone
+maxim ``When broke, I will falsely promise to repay a loan
+to get some quick cash.'' This maxim fails the universalizability test because in a world where everyone
 falsely promises to repay loans, no one will believe promises anymore, so the maxim will no longer serve
@@
 at hand, falsely promising in this case. The advantage of Kantian ethics is that this is all the common 
-sense that it requires, whereas a consequentialist or virtue ethical agent will require much more. All
+sense that it requires, whereas a consequentialist or virtue ethical agent will require much more\footnote{
+In Sections Lying and Murderer, I also use my system to demonstrate that Kantian ethics requires relatively thin conceptions 
+of concepts like falsely promising.}. All
 moral theories evaluating falsely promising will a robust definition of promising, 
@@
 Earlier I mentioned that Kant presents three formulations, or versions, 
-of what he calls the ``supreme law of morality," but I focus on the first of these three. In this section, 
+of what he calls the ``supreme law of morality," but that I focus on the first of these three. In this section, 
 I argue that the Formula of Universal Law, specifically, is the easiest part of Kantian ethics to automate
@@
 formula of universal law (FUL), which reads, ``act only according to that maxim through which you can 
-at the same time will that it become a universal law." \cite[34]{groundwork} This formulation
-generates the universalizability test, which ``tests" the moral value of a maxim by 
-imagining a world in which it becomes a universal law and attempting to will the maxim in that world. The 
+at the same time will that it become a universal law'' \citep[34]{groundwork}. The 
 second formulation of the categorical imperative is the formula of humanity (FUH): ``So act that you use humanity, 
 in your own person, as well as in the person of any other, always at the same time as an end, never merely 
-as a means." \cite[41]{groundwork}. This formulation is often understood as requiring us to 
+as a means.'' \cite[41]{groundwork}. This formulation is often understood as requiring us to 
 acknowledge and respect the dignity of every other person. The third formulation of the categorical 
@@
 as, ``we should so act that we may think of ourselves as legislating universal laws through our 
-maxims" \cite[28]{korsgaardintro}. While closely related to the FUL, the FOA presents morality as the activity of 
-perfectly rational agents in an ideal ``kingdom of ends," guided by what Kant calls the ``laws of freedom."
+maxims'' \cite[28]{korsgaardintro}. While closely related to the FUL, the FOA presents morality as the activity of 
+perfectly rational agents in an ideal ``kingdom of ends,'' guided by what Kant calls the ``laws of freedom.''
 
@@
 is particularly useful in a computational context because any formalism necessarily makes its content 
-precise. The FUL's existing precision reduces ambiguity, allowing me to remain faithful to philosophical
+precise. The FUL's precision reduces ambiguity, allowing me to remain faithful to philosophical
 literature on Kant. Precision reduces the need to make choices to resolve debates 
@@
 
-Though Kantians study all formulations of the categorical imperative, Kant argues in Groundwork 
-that the three formulations of the categorical imperative are equivalent \cite{groundwork}. While this 
+Though Kantians study all formulations of the categorical imperative, Kant argues in \emph{Groundwork} 
+that the three formulations of the categorical imperative are equivalent \citep{groundwork}. While this 
 argument is disputed \cite{sepkant}, for those who believe it, the
@@
 non-ideal circumstances imaginable, but the FUH is merely a standard to live towards that might not be 
-achieved. Thus, he FUL generates stronger requirements than the other two formulations and is 
-the bare minimum of Kant's ethics. Because the FUL's prescriptions outweigh those of the other two formulations,
-formalizing it creates a functional, minimum ethical theory that can serve as a foundation for implementations
+achieved. Thus, the FUL generates stronger requirements than the other two formulations and reflects 
+the bare minimum standard of Kant's ethics. Because the FUL's prescriptions outweigh those of the other two formulations,
+automating it creates a functional, minimum ethical theory that can serve as a foundation for implementations
 of other aspects of Kant's ethics.%
@@
 These logics usually also contain the possibility operator $\diamond$, where
- $\diamond p \iff \sim \Box \sim p$. $\diamond p$ means that the statement $p$ is possibly true. 
+ $\diamond p \iff \sim \Box \sim p$. $\diamond p$ means that the statement $p$ is possibly true, or true
+at at least one of $w$'s neighbors. 
 Additionally, modal logics include standard operators of propositional logic like $\sim, \wedge, \vee, \rightarrow$.
@@
 logic replaces $\Box$ with the obligation operator
-$O$, and $\diamond$ with the permissibility operator $P$ \citep{cresswell, sep-logic-deontic}. Using the Kripke semantics for $O$, $O p$ 
+$O$, and $\diamond$ with the permissibility operator $P$ \citep{cresswell}. Using the Kripke semantics for $O$, $O p$ 
 is true at $w$ if $p$ is true at all  ideal deontic alternatives to $w$, and thus represents the 
@@
 conditionals. \citep{chisholm, ctd}
-}. In situations where duty is violated, the logic breaks down 
+} In situations where duty is violated, the logic breaks down 
 and produces paradoxical results. Thus, I use an improved deontic logic instead of SDL for this work.%
@@
 \begin{isamarkuptext}%
-I use as my base logic Carmo and Jones's dyadic deontic logic, or DDL, which improves on SDL \citep{CJDDL}. 
+I use as my base logic Carmo and Jones's Dyadic Deontic Logic (DDL), which improves on SDL \citep{CJDDL}. 
 It introduces a dyadic obligation operator $O\{A \vert B\}$ 
@@
 a different set of neighbors, or morally relevant alternatives, for each world. To represent this,
-Carmo and Jones define a function $ob$ that maps from a given context (or world) to the propositions 
+Carmo and Jones define a function $ob$ that maps a given context (or world) to the propositions 
 that are obligatory at this world, where a proposition $p$ is defined as 
@@
 automatic and interactive/manual theorem proving. To demonstrate the power and usage of Isabelle and 
-make DDL more precise, I walk through my reimplementation
-of Benzmueller, Farjami, and Parent's implementation of DDL in Isabelle/HOL \cite{BFP, logikey}.%
+make DDL more precise, I walk through my \color{red}reimplementation
+of Benzmueller, Farjami, and Parent's implementation of DDL in Isabelle/HOL \citep{BFP, logikey}\color{black}.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \ i\ %
-\isamarkupcmt{i is the type for a set of worlds.%
+\isamarkupcmt{This is an Isabelle comment. i is the type for a set of worlds.%
+}\isanewline
+%
+\isamarkupcmt{This is a line of actual code used in my implementation. For the rest of the thesis, text typeset 
+like this represents Isabelle code.%
 }\isanewline
@@
 %
-\isamarkupcmt{A set of formulae is defined by its truth value at a set of worlds. For example, the set \{True\}
+\isamarkupcmt{A set of formulae is defined by its truth value at a set of worlds. For example, the set \{\emph{True}\}
 is true at any set of worlds.%
@@
 The $ob$ function described in Section \ref{ddl} is used to determine which propositions are obligatory
-in which contexts.%
+in which contexts. I implement it as a constant. This constant has no meaning (I merely specify the type), 
+but future proofs will specify models for this constant.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \ %
-\isamarkupcmt{ob(context)(term) is True if the term is obligatory in this context%
+\isamarkupcmt{$ob\, (context)\, (term)$ is \emph{True} if the term is obligatory in this context%
 }\isanewline
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\isatagdocument
-%
-\isamarkupsubsubsection{Axiomatization%
-}
-\isamarkuptrue%
-%
-\endisatagdocument
-{\isafolddocument}%
-%
-\isadelimdocument
-%
-\endisadelimdocument
 %
@@
 \isacommand{axiomatization}\isamarkupfalse%
-\ \isakeyword{where}ax{\isacharunderscore}{\isadigit{5}}d{\isacharcolon}\ {\isachardoublequoteopen}{\isasymforall}X\ Y\ Z{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isasymforall}w{\isachardot}\ Y{\isacharparenleft}w{\isacharparenright}{\isasymlongrightarrow}X{\isacharparenleft}w{\isacharparenright}{\isacharparenright}\ {\isasymand}\ ob{\isacharparenleft}X{\isacharparenright}{\isacharparenleft}Y{\isacharparenright}\ {\isasymand}\ {\isacharparenleft}{\isasymforall}w{\isachardot}\ X{\isacharparenleft}w{\isacharparenright}{\isasymlongrightarrow}Z{\isacharparenleft}w{\isacharparenright}{\isacharparenright}{\isacharparenright}\ \isanewline
+\ \isakeyword{where}\isanewline
+\ ax{\isacharunderscore}{\isadigit{5}}d{\isacharcolon}\ {\isachardoublequoteopen}{\isasymforall}X\ Y\ Z{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isasymforall}w{\isachardot}\ Y{\isacharparenleft}w{\isacharparenright}{\isasymlongrightarrow}X{\isacharparenleft}w{\isacharparenright}{\isacharparenright}\ {\isasymand}\ ob{\isacharparenleft}X{\isacharparenright}{\isacharparenleft}Y{\isacharparenright}\ {\isasymand}\ {\isacharparenleft}{\isasymforall}w{\isachardot}\ X{\isacharparenleft}w{\isacharparenright}{\isasymlongrightarrow}Z{\isacharparenleft}w{\isacharparenright}{\isacharparenright}{\isacharparenright}\ \isanewline
 \ \ {\isasymlongrightarrow}ob{\isacharparenleft}Z{\isacharparenright}{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isacharparenleft}Z{\isacharparenleft}w{\isacharparenright}\ {\isasymand}\ {\isasymnot}X{\isacharparenleft}w{\isacharparenright}{\isacharparenright}\ {\isasymor}\ Y{\isacharparenleft}w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
@@
 \begin{isamarkuptext}%
-The axiomatization above defined the semantics of DDL and, as demonstrated by the example axiom,
-was unwieldly. In my work, I mostly perform syntactic proofs, so I must define the syntax of the logic.
-Isabelle already knows the axioms of this logic, so I can define the syntax as abbreviations for different
+The axiomatization above defines the semantics of DDL and, as demonstrated by the example axiom,
+is unwieldly. In my work, I mostly perform syntactic proofs, so I must define the syntax of the logic.
+Isabelle already knows the semantics of the axioms of this logic, so I can define the syntax as abbreviations for different
 formulas involving the axioms above. Each DDL operator is represented
@@
 whenever they are applied. While the shallow embedding is performant (because it uses Isabelle's original 
-syntax tree), abbreviations may hurt performance.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-Modal operators will be useful for my purposes, and this how they are implemented.%
+syntax tree), my heavy use of abbreviations may impact the performance of long proofs.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+Modal operators will be useful for my purposes, implemented below.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymbox}\ A\ {\isasymequiv}\ {\isasymlambda}w{\isachardot}{\isasymforall}y{\isachardot}\ A{\isacharparenleft}y{\isacharparenright}{\isachardoublequoteclose}\ \isanewline
+%
+\isamarkupcmt{Notice that the necessity operator is an abbreviation, or syntactic sugar for, the higher order
+logic formula that the proposition holds at all worlds.%
+}\isanewline
 \isacommand{abbreviation}\isamarkupfalse%
 \ ddldiamond{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t\ {\isasymRightarrow}\ t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymdiamond}{\isachardoublequoteclose}{\isacharparenright}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymdiamond}A\ {\isasymequiv}\ \isactrlbold {\isasymnot}{\isacharparenleft}{\isasymbox}{\isacharparenleft}\isactrlbold {\isasymnot}A{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
-\begin{isamarkuptext}%
-The most important operator for my project is the obligation operator.%
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymdiamond}A\ {\isasymequiv}\ \isactrlbold {\isasymnot}{\isacharparenleft}{\isasymbox}{\isacharparenleft}\isactrlbold {\isasymnot}A{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Possibility is similarly an abbreviation for a higher order logic formula involving the defined semantics.%
+}%
+\begin{isamarkuptext}%
+The most important operator for my project is the obligation operator, implemented below.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-While DDL is powerful because of its support for a dyadic obligation operator, in many cases 
+While DDL is powerful because of its support for a dyadic obligation operator, in many cases, 
 I only need a monadic obligation operator. Below is some syntactic sugar for a monadic obligation operator.%
@@
 %
-\isamarkupcmt{Intuitively, the context $True$ is the widest context possible because $True$ holds at all worlds.%
+\isamarkupcmt{Intuitively, the context $True$ is the widest context possible because $True$ holds at all worlds.
+Therefore, the monadic obligation operator requires that $A$ is obligated at all worlds.%
 }%
 \begin{isamarkuptext}%
-Validity will be useful when discussing metalogical/ethical properties.%
+Finally, validity will be useful when discussing metalogical/ethical properties.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 Nitpick can find satisfying models for a particular lemma using the \texttt{satisfy} option and it can 
-find counterexamples. I use it extensively in proofs in this prokect.%
+find counterexamples using the \texttt{falsify} option, both of which I use heavily in this project.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %:%48=20%:%
-%:%49=21%:%
-%:%50=22%:%
-%:%51=23%:%
-%:%52=24%:%
-%:%53=25%:%
-%:%62=27%:%
+%:%57=22%:%
+%:%69=25%:%
+%:%70=26%:%
+%:%71=27%:%
+%:%72=28%:%
+%:%73=29%:%
 %:%74=30%:%
@@
 %:%89=45%:%
-%:%90=46%:%
-%:%91=47%:%
-%:%92=48%:%
-%:%93=49%:%
-%:%94=50%:%
-%:%95=51%:%
-%:%96=52%:%
-%:%97=53%:%
-%:%106=56%:%
-%:%118=58%:%
-%:%119=59%:%
-%:%120=60%:%
-%:%121=61%:%
-%:%122=62%:%
-%:%123=63%:%
-%:%124=64%:%
+%:%98=48%:%
+%:%110=50%:%
+%:%111=51%:%
+%:%112=52%:%
+%:%113=53%:%
+%:%114=54%:%
+%:%118=56%:%
+%:%119=57%:%
+%:%120=58%:%
+%:%121=59%:%
+%:%122=60%:%
+%:%123=61%:%
+%:%124=62%:%
+%:%125=63%:%
+%:%126=64%:%
+%:%127=65%:%
 %:%128=66%:%
@@
 %:%139=77%:%
-%:%140=78%:%
-%:%141=79%:%
-%:%142=80%:%
-%:%143=81%:%
-%:%144=82%:%
-%:%145=83%:%
-%:%146=84%:%
-%:%147=85%:%
-%:%148=86%:%
-%:%149=87%:%
-%:%150=88%:%
-%:%151=89%:%
-%:%152=90%:%
-%:%161=93%:%
-%:%173=95%:%
-%:%174=96%:%
-%:%175=97%:%
-%:%176=98%:%
-%:%177=99%:%
-%:%178=100%:%
-%:%179=101%:%
-%:%180=102%:%
-%:%181=103%:%
-%:%185=105%:%
+%:%148=80%:%
+%:%160=82%:%
+%:%161=83%:%
+%:%162=84%:%
+%:%163=85%:%
+%:%164=86%:%
+%:%165=87%:%
+%:%166=88%:%
+%:%167=89%:%
+%:%168=90%:%
+%:%172=92%:%
+%:%176=94%:%
+%:%177=95%:%
+%:%178=96%:%
+%:%179=97%:%
+%:%180=98%:%
+%:%181=99%:%
+%:%182=100%:%
+%:%183=101%:%
+%:%184=102%:%
+%:%185=103%:%
+%:%186=104%:%
+%:%187=105%:%
+%:%188=106%:%
 %:%189=107%:%
@@
 %:%200=118%:%
-%:%201=119%:%
-%:%202=120%:%
-%:%203=121%:%
-%:%204=122%:%
-%:%205=123%:%
-%:%206=124%:%
-%:%207=125%:%
-%:%208=126%:%
-%:%209=127%:%
-%:%210=128%:%
-%:%211=129%:%
-%:%212=130%:%
-%:%213=131%:%
-%:%214=132%:%
-%:%215=133%:%
-%:%219=136%:%
+%:%204=121%:%
+%:%208=123%:%
+%:%209=124%:%
+%:%210=125%:%
+%:%211=126%:%
+%:%212=127%:%
+%:%213=128%:%
+%:%214=129%:%
+%:%215=130%:%
+%:%216=131%:%
+%:%217=132%:%
+%:%218=133%:%
+%:%219=134%:%
+%:%220=135%:%
+%:%221=136%:%
+%:%222=137%:%
 %:%223=138%:%
-%:%224=139%:%
-%:%225=140%:%
-%:%226=141%:%
-%:%227=142%:%
-%:%228=143%:%
-%:%229=144%:%
-%:%230=145%:%
-%:%231=146%:%
-%:%232=147%:%
-%:%233=148%:%
-%:%234=149%:%
-%:%235=150%:%
-%:%236=151%:%
-%:%237=152%:%
-%:%238=153%:%
-%:%239=154%:%
-%:%240=155%:%
-%:%244=157%:%
-%:%248=159%:%
-%:%249=160%:%
-%:%250=161%:%
-%:%251=162%:%
-%:%252=163%:%
-%:%253=164%:%
-%:%254=165%:%
-%:%255=166%:%
-%:%256=167%:%
-%:%257=168%:%
-%:%258=169%:%
-%:%259=170%:%
-%:%260=171%:%
-%:%261=172%:%
-%:%262=173%:%
-%:%263=174%:%
-%:%264=175%:%
-%:%265=176%:%
-%:%266=177%:%
-%:%267=178%:%
-%:%268=179%:%
-%:%272=182%:%
-%:%276=185%:%
-%:%277=186%:%
-%:%278=187%:%
-%:%279=188%:%
-%:%280=189%:%
-%:%281=190%:%
-%:%282=191%:%
-%:%283=192%:%
-%:%284=193%:%
-%:%285=194%:%
-%:%286=195%:%
-%:%287=196%:%
-%:%288=197%:%
-%:%289=198%:%
-%:%290=199%:%
-%:%291=200%:%
-%:%300=203%:%
-%:%312=205%:%
-%:%313=206%:%
-%:%314=207%:%
-%:%315=208%:%
-%:%316=209%:%
-%:%317=210%:%
-%:%318=211%:%
-%:%319=212%:%
-%:%323=216%:%
-%:%324=217%:%
-%:%325=218%:%
-%:%326=219%:%
-%:%327=220%:%
-%:%328=221%:%
-%:%329=222%:%
-%:%330=223%:%
-%:%331=224%:%
-%:%332=225%:%
-%:%336=227%:%
+%:%227=140%:%
+%:%231=142%:%
+%:%232=143%:%
+%:%233=144%:%
+%:%234=145%:%
+%:%235=146%:%
+%:%236=147%:%
+%:%237=148%:%
+%:%238=149%:%
+%:%239=150%:%
+%:%240=151%:%
+%:%241=152%:%
+%:%242=153%:%
+%:%243=154%:%
+%:%244=155%:%
+%:%245=156%:%
+%:%246=157%:%
+%:%247=158%:%
+%:%251=161%:%
+%:%255=164%:%
+%:%256=165%:%
+%:%257=166%:%
+%:%258=167%:%
+%:%259=168%:%
+%:%260=169%:%
+%:%261=170%:%
+%:%262=171%:%
+%:%263=172%:%
+%:%264=173%:%
+%:%265=174%:%
+%:%266=175%:%
+%:%267=176%:%
+%:%268=177%:%
+%:%269=178%:%
+%:%270=179%:%
+%:%279=182%:%
+%:%291=184%:%
+%:%292=185%:%
+%:%293=186%:%
+%:%294=187%:%
+%:%295=188%:%
+%:%296=189%:%
+%:%297=190%:%
+%:%301=194%:%
+%:%302=195%:%
+%:%303=196%:%
+%:%304=197%:%
+%:%305=198%:%
+%:%306=199%:%
+%:%307=200%:%
+%:%308=201%:%
+%:%309=202%:%
+%:%313=204%:%
+%:%317=206%:%
+%:%318=207%:%
+%:%319=208%:%
+%:%320=209%:%
+%:%321=210%:%
+%:%322=211%:%
+%:%323=212%:%
+%:%324=213%:%
+%:%325=214%:%
+%:%326=215%:%
+%:%327=216%:%
+%:%328=217%:%
+%:%329=218%:%
+%:%330=219%:%
+%:%331=220%:%
+%:%332=221%:%
+%:%333=222%:%
+%:%334=223%:%
+%:%335=224%:%
+%:%336=225%:%
+%:%337=226%:%
+%:%338=227%:%
+%:%339=228%:%
 %:%340=229%:%
@@
 %:%343=232%:%
-%:%344=233%:%
-%:%345=234%:%
-%:%346=235%:%
-%:%347=236%:%
-%:%348=237%:%
-%:%349=238%:%
-%:%350=239%:%
-%:%351=240%:%
-%:%352=241%:%
-%:%353=242%:%
-%:%354=243%:%
-%:%355=244%:%
-%:%356=245%:%
-%:%357=246%:%
-%:%358=247%:%
-%:%359=248%:%
-%:%360=249%:%
-%:%361=250%:%
-%:%362=251%:%
-%:%363=252%:%
-%:%364=253%:%
-%:%365=254%:%
-%:%366=255%:%
-%:%375=258%:%
+%:%352=235%:%
+%:%364=237%:%
+%:%365=238%:%
+%:%366=239%:%
+%:%367=240%:%
+%:%368=241%:%
+%:%369=242%:%
+%:%370=243%:%
+%:%371=244%:%
+%:%372=245%:%
+%:%373=246%:%
+%:%374=247%:%
+%:%375=248%:%
+%:%376=249%:%
+%:%377=250%:%
+%:%378=251%:%
+%:%379=252%:%
+%:%380=253%:%
+%:%381=254%:%
+%:%382=255%:%
+%:%383=256%:%
+%:%384=257%:%
+%:%385=258%:%
+%:%386=259%:%
 %:%387=260%:%
@@
 %:%420=293%:%
-%:%421=294%:%
-%:%422=295%:%
-%:%423=296%:%
-%:%424=297%:%
-%:%425=298%:%
-%:%426=299%:%
-%:%427=300%:%
-%:%428=301%:%
-%:%429=302%:%
-%:%430=303%:%
-%:%431=304%:%
-%:%432=305%:%
-%:%433=306%:%
-%:%434=307%:%
-%:%435=308%:%
-%:%436=309%:%
-%:%437=310%:%
-%:%438=311%:%
-%:%439=312%:%
-%:%440=313%:%
-%:%441=314%:%
-%:%442=315%:%
-%:%443=316%:%
-%:%444=317%:%
-%:%445=318%:%
-%:%446=319%:%
-%:%447=320%:%
-%:%448=321%:%
-%:%449=322%:%
-%:%450=323%:%
-%:%451=324%:%
-%:%455=326%:%
-%:%459=328%:%
-%:%460=329%:%
-%:%461=330%:%
-%:%462=331%:%
-%:%463=332%:%
-%:%464=333%:%
-%:%465=334%:%
-%:%466=335%:%
-%:%467=336%:%
-%:%468=337%:%
-%:%469=338%:%
-%:%470=339%:%
-%:%471=340%:%
-%:%472=341%:%
-%:%473=342%:%
-%:%474=343%:%
-%:%475=344%:%
-%:%476=345%:%
-%:%477=346%:%
-%:%478=347%:%
-%:%479=348%:%
-%:%483=351%:%
-%:%487=353%:%
-%:%488=354%:%
-%:%489=355%:%
-%:%490=356%:%
-%:%491=357%:%
-%:%492=358%:%
-%:%493=359%:%
-%:%494=360%:%
-%:%495=361%:%
-%:%496=362%:%
-%:%497=363%:%
-%:%498=364%:%
-%:%499=365%:%
-%:%500=366%:%
-%:%501=367%:%
-%:%502=368%:%
-%:%503=369%:%
-%:%504=370%:%
-%:%505=371%:%
-%:%506=372%:%
-%:%507=373%:%
-%:%508=374%:%
-%:%509=375%:%
-%:%510=376%:%
-%:%511=377%:%
-%:%512=378%:%
-%:%513=379%:%
-%:%514=380%:%
-%:%515=381%:%
-%:%516=382%:%
-%:%517=383%:%
-%:%526=385%:%
-%:%538=388%:%
-%:%539=389%:%
-%:%540=390%:%
-%:%541=391%:%
-%:%542=392%:%
-%:%543=393%:%
-%:%544=394%:%
-%:%545=395%:%
-%:%546=396%:%
-%:%547=397%:%
-%:%548=398%:%
-%:%549=399%:%
-%:%550=400%:%
-%:%551=401%:%
-%:%552=402%:%
-%:%553=403%:%
-%:%554=404%:%
-%:%555=405%:%
-%:%556=406%:%
-%:%557=407%:%
-%:%558=408%:%
-%:%559=409%:%
-%:%560=410%:%
-%:%561=411%:%
-%:%562=412%:%
-%:%563=413%:%
-%:%564=414%:%
-%:%565=415%:%
-%:%566=416%:%
-%:%567=417%:%
-%:%568=418%:%
-%:%569=419%:%
-%:%570=420%:%
-%:%571=421%:%
-%:%572=422%:%
-%:%573=423%:%
-%:%574=424%:%
-%:%575=425%:%
-%:%576=426%:%
-%:%577=427%:%
-%:%578=428%:%
-%:%579=429%:%
-%:%580=430%:%
-%:%581=431%:%
-%:%582=432%:%
-%:%583=433%:%
-%:%584=434%:%
-%:%585=435%:%
-%:%586=436%:%
-%:%587=437%:%
-%:%588=438%:%
-%:%589=439%:%
-%:%590=440%:%
-%:%599=442%:%
+%:%424=296%:%
+%:%428=298%:%
+%:%429=299%:%
+%:%430=300%:%
+%:%431=301%:%
+%:%432=302%:%
+%:%433=303%:%
+%:%434=304%:%
+%:%435=305%:%
+%:%436=306%:%
+%:%437=307%:%
+%:%438=308%:%
+%:%439=309%:%
+%:%440=310%:%
+%:%441=311%:%
+%:%442=312%:%
+%:%443=313%:%
+%:%444=314%:%
+%:%445=315%:%
+%:%446=316%:%
+%:%447=317%:%
+%:%448=318%:%
+%:%452=321%:%
+%:%456=323%:%
+%:%457=324%:%
+%:%458=325%:%
+%:%459=326%:%
+%:%460=327%:%
+%:%461=328%:%
+%:%462=329%:%
+%:%463=330%:%
+%:%464=331%:%
+%:%465=332%:%
+%:%466=333%:%
+%:%467=334%:%
+%:%468=335%:%
+%:%469=336%:%
+%:%470=337%:%
+%:%471=338%:%
+%:%472=339%:%
+%:%473=340%:%
+%:%474=341%:%
+%:%475=342%:%
+%:%476=343%:%
+%:%477=344%:%
+%:%478=345%:%
+%:%479=346%:%
+%:%480=347%:%
+%:%481=348%:%
+%:%482=349%:%
+%:%483=350%:%
+%:%484=351%:%
+%:%485=352%:%
+%:%486=353%:%
+%:%487=354%:%
+%:%496=356%:%
+%:%508=359%:%
+%:%509=360%:%
+%:%510=361%:%
+%:%511=362%:%
+%:%512=363%:%
+%:%513=364%:%
+%:%514=365%:%
+%:%515=366%:%
+%:%516=367%:%
+%:%517=368%:%
+%:%518=369%:%
+%:%519=370%:%
+%:%520=371%:%
+%:%521=372%:%
+%:%522=373%:%
+%:%523=374%:%
+%:%524=375%:%
+%:%525=376%:%
+%:%526=377%:%
+%:%527=378%:%
+%:%528=379%:%
+%:%529=380%:%
+%:%530=381%:%
+%:%531=382%:%
+%:%532=383%:%
+%:%533=384%:%
+%:%534=385%:%
+%:%535=386%:%
+%:%536=387%:%
+%:%537=388%:%
+%:%538=389%:%
+%:%539=390%:%
+%:%540=391%:%
+%:%541=392%:%
+%:%542=393%:%
+%:%543=394%:%
+%:%544=395%:%
+%:%545=396%:%
+%:%546=397%:%
+%:%547=398%:%
+%:%548=399%:%
+%:%549=400%:%
+%:%550=401%:%
+%:%551=402%:%
+%:%552=403%:%
+%:%553=404%:%
+%:%554=405%:%
+%:%555=406%:%
+%:%556=407%:%
+%:%557=408%:%
+%:%558=409%:%
+%:%567=411%:%
+%:%579=413%:%
+%:%580=414%:%
+%:%584=417%:%
+%:%585=418%:%
+%:%586=419%:%
+%:%587=420%:%
+%:%588=421%:%
+%:%589=422%:%
+%:%590=423%:%
+%:%591=424%:%
+%:%592=425%:%
+%:%593=426%:%
+%:%594=427%:%
+%:%595=428%:%
+%:%596=429%:%
+%:%597=430%:%
+%:%598=431%:%
+%:%599=432%:%
+%:%600=433%:%
+%:%601=434%:%
+%:%602=435%:%
+%:%603=436%:%
+%:%604=437%:%
+%:%605=438%:%
+%:%606=439%:%
+%:%607=440%:%
+%:%608=441%:%
+%:%609=442%:%
+%:%610=443%:%
 %:%611=444%:%
-%:%612=445%:%
-%:%616=448%:%
-%:%617=449%:%
-%:%618=450%:%
-%:%619=451%:%
-%:%620=452%:%
-%:%621=453%:%
-%:%622=454%:%
-%:%623=455%:%
-%:%624=456%:%
-%:%625=457%:%
-%:%626=458%:%
-%:%627=459%:%
-%:%628=460%:%
-%:%629=461%:%
-%:%630=462%:%
-%:%631=463%:%
-%:%632=464%:%
-%:%633=465%:%
-%:%634=466%:%
-%:%635=467%:%
-%:%636=468%:%
-%:%637=469%:%
-%:%638=470%:%
-%:%639=471%:%
-%:%640=472%:%
-%:%641=473%:%
-%:%642=474%:%
-%:%646=476%:%
-%:%647=477%:%
-%:%648=478%:%
-%:%649=479%:%
-%:%650=480%:%
-%:%651=481%:%
-%:%652=482%:%
-%:%653=483%:%
-%:%654=484%:%
-%:%655=485%:%
-%:%656=486%:%
-%:%657=487%:%
-%:%658=488%:%
-%:%659=489%:%
-%:%660=490%:%
-%:%661=491%:%
-%:%662=492%:%
-%:%663=493%:%
-%:%664=494%:%
-%:%665=495%:%
-%:%666=496%:%
-%:%667=497%:%
-%:%668=498%:%
-%:%669=499%:%
-%:%670=500%:%
-%:%671=501%:%
-%:%672=502%:%
-%:%681=505%:%
-%:%693=507%:%
-%:%694=508%:%
-%:%695=509%:%
-%:%696=510%:%
-%:%697=511%:%
-%:%698=512%:%
-%:%707=515%:%
-%:%719=517%:%
-%:%720=518%:%
-%:%721=519%:%
-%:%723=521%:%
-%:%724=521%:%
+%:%615=446%:%
+%:%616=447%:%
+%:%617=448%:%
+%:%618=449%:%
+%:%619=450%:%
+%:%620=451%:%
+%:%621=452%:%
+%:%622=453%:%
+%:%623=454%:%
+%:%624=455%:%
+%:%625=456%:%
+%:%626=457%:%
+%:%627=458%:%
+%:%628=459%:%
+%:%629=460%:%
+%:%630=461%:%
+%:%631=462%:%
+%:%632=463%:%
+%:%633=464%:%
+%:%634=465%:%
+%:%635=466%:%
+%:%636=467%:%
+%:%637=468%:%
+%:%638=469%:%
+%:%639=470%:%
+%:%640=471%:%
+%:%641=472%:%
+%:%650=475%:%
+%:%662=477%:%
+%:%663=478%:%
+%:%664=479%:%
+%:%665=480%:%
+%:%666=481%:%
+%:%667=482%:%
+%:%676=485%:%
+%:%688=487%:%
+%:%689=488%:%
+%:%690=489%:%
+%:%692=491%:%
+%:%693=491%:%
+%:%694=491%:%
+%:%695=491%:%
+%:%697=492%:%
+%:%698=493%:%
+%:%699=493%:%
+%:%700=494%:%
+%:%701=495%:%
+%:%702=495%:%
+%:%703=495%:%
+%:%704=495%:%
+%:%706=496%:%
+%:%707=497%:%
+%:%708=497%:%
+%:%711=511%:%
+%:%712=512%:%
+%:%713=513%:%
+%:%715=515%:%
+%:%716=515%:%
+%:%717=515%:%
+%:%718=515%:%
+%:%719=516%:%
+%:%720=516%:%
+%:%721=516%:%
+%:%724=520%:%
 %:%725=521%:%
-%:%726=521%:%
-%:%727=522%:%
-%:%728=523%:%
-%:%729=523%:%
-%:%730=523%:%
-%:%731=523%:%
-%:%733=524%:%
-%:%734=525%:%
-%:%735=525%:%
-%:%738=539%:%
-%:%739=540%:%
-%:%741=542%:%
-%:%742=542%:%
-%:%743=542%:%
-%:%744=542%:%
-%:%745=543%:%
-%:%746=543%:%
-%:%747=543%:%
-%:%755=547%:%
-%:%767=549%:%
-%:%768=550%:%
-%:%769=551%:%
-%:%770=552%:%
-%:%772=554%:%
-%:%773=554%:%
-%:%773=577%:%
-%:%774=578%:%
-%:%776=579%:%
-%:%777=580%:%
-%:%778=581%:%
-%:%779=582%:%
-%:%780=582%:%
-%:%788=589%:%
-%:%800=591%:%
-%:%801=592%:%
-%:%802=593%:%
-%:%803=594%:%
-%:%804=595%:%
-%:%805=596%:%
-%:%806=597%:%
-%:%810=613%:%
-%:%812=614%:%
-%:%813=614%:%
-%:%814=615%:%
-%:%815=616%:%
-%:%816=616%:%
-%:%817=617%:%
-%:%819=619%:%
-%:%821=620%:%
-%:%822=620%:%
-%:%823=621%:%
-%:%825=622%:%
-%:%826=622%:%
-%:%829=642%:%
-%:%830=643%:%
-%:%832=644%:%
-%:%833=644%:%
+%:%726=522%:%
+%:%727=523%:%
+%:%729=525%:%
+%:%730=525%:%
+%:%731=549%:%
+%:%732=550%:%
+%:%734=551%:%
+%:%735=552%:%
+%:%736=553%:%
+%:%737=554%:%
+%:%738=554%:%
+%:%746=561%:%
+%:%758=563%:%
+%:%759=564%:%
+%:%760=565%:%
+%:%761=566%:%
+%:%762=567%:%
+%:%763=568%:%
+%:%764=569%:%
+%:%768=585%:%
+%:%770=586%:%
+%:%771=586%:%
+%:%772=587%:%
+%:%774=588%:%
+%:%775=589%:%
+%:%776=589%:%
+%:%777=590%:%
+%:%778=590%:%
+%:%779=591%:%
+%:%781=592%:%
+%:%784=594%:%
+%:%786=595%:%
+%:%787=595%:%
+%:%788=596%:%
+%:%790=597%:%
+%:%791=597%:%
+%:%794=617%:%
+%:%795=618%:%
+%:%797=619%:%
+%:%798=619%:%
+%:%799=620%:%
+%:%800=621%:%
+%:%801=621%:%
+%:%802=622%:%
+%:%803=623%:%
+%:%804=623%:%
+%:%805=624%:%
+%:%807=625%:%
+%:%808=626%:%
+%:%811=628%:%
+%:%813=629%:%
+%:%814=629%:%
+%:%815=630%:%
+%:%817=631%:%
+%:%818=631%:%
+%:%821=639%:%
+%:%822=640%:%
+%:%823=641%:%
+%:%824=642%:%
+%:%826=645%:%
+%:%827=645%:%
+%:%828=645%:%
+%:%830=645%:%
 %:%834=645%:%
-%:%835=646%:%
-%:%836=646%:%
-%:%837=647%:%
-%:%838=648%:%
-%:%839=648%:%
-%:%840=649%:%
-%:%842=650%:%
-%:%845=652%:%
-%:%847=653%:%
-%:%848=653%:%
-%:%849=654%:%
-%:%851=655%:%
-%:%852=655%:%
-%:%855=663%:%
-%:%856=664%:%
-%:%857=665%:%
-%:%858=666%:%
-%:%860=669%:%
-%:%861=669%:%
-%:%862=669%:%
-%:%864=669%:%
-%:%868=669%:%
-%:%869=669%:%
-%:%871=670%:%
-%:%872=671%:%
-%:%873=671%:%
-%:%875=672%:%
-%:%876=673%:%
-%:%877=674%:%
-%:%887=676%:%
-%:%888=677%:%
-%:%889=678%:%
+%:%835=645%:%
+%:%837=646%:%
+%:%838=647%:%
+%:%839=647%:%
+%:%841=648%:%
+%:%842=649%:%
+%:%843=650%:%
+%:%853=652%:%
+%:%854=653%:%
+%:%855=654%:%

### 2022-02-12 paper/output/document/appendix.tex
making progress on CHAPTER 3

--- 2021-11-17 paper/output/document/paper41.tex
@@
 \begin{isabellebody}%
-\setisabellecontext{paper{\isadigit{4}}{\isadigit{1}}}%
+\setisabellecontext{appendix}%
 %
@@
 %
-\isamarkupsection{Novel Formalization of the Categorical Imperative%
+\isamarkupsection{Appendix%
+}
+\isamarkuptrue%
+%
+\isamarkupsubsection{Maxims and Motives \label{maximmotive}%
 }
@@
 \begin{isamarkuptext}%
-In this section, I present a custom formalization of the categorical imperative, as inspired by 
-the goals from the previous chapter.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\isatagdocument
-%
-\isamarkupsubsection{Logical Background%
-}
-\isamarkuptrue%
-%
-\endisatagdocument
-{\isafolddocument}%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\begin{isamarkuptext}%
-The previous attempts to model the categorical imperative in Chapter 2 partially failed due to 
-an inability to fully represent the complexity of a maxim. Specifically, they treated actions as a single, 
-monolithic unit of evaluation, whereas most Kantians consider the unit of evaluation for the FUL to the more
-complex notion of a maxim. In this section, I will present some logical background necessarily to fully 
-capture the spirit of a maxim. I will begin by borrowing some machinery to handle ``subjects" who perform 
-actions from Chapter 2.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{typedecl}\isamarkupfalse%
-\ s\ %
-\isamarkupcmt{s is the type for a ``subject," i.e. the subject of a sentence. In this interpretation, 
-a subject is merely defined as ``that which can act." It does not include any other properties, such as 
-rationality or dignity. As I will show, for the purposes of defining the universalizability test, this 
-``thin" representation of a subject suffices.%
-}\isanewline
-\isanewline
-\isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
-\ os\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}s\ {\isasymRightarrow}\ t{\isacharparenright}{\isachardoublequoteclose}\ %
-\isamarkupcmt{Recall that an open sentence maps a subject to a term to model the 
-substitution operator.%
-}\isanewline
-\isanewline
-\isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
-\ maxim\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}t\ {\isacharasterisk}\ os\ {\isacharasterisk}\ t{\isacharparenright}{\isachardoublequoteclose}%
-\begin{isamarkuptext}%
-The central unit of evaluation for the universalizability test is a ``maxim," which Kant defines 
-in a footnote in \emph{Groundwork} as ``the subjective principle of willing," or the principle that 
-the agent acts on \cite[16]{groundwork}. Modern Kantians differ in their interpretations of this definition. The naive view 
-is that a maxim is an act, but Korsgaard adopts the more sophisticated view that a maxim is composed
-of an act and the agent's purpose for acting \cite{actingforareason}. She also compares a maxim 
-to Aristotle's logos, which includes these components and information about the circumstances and methods 
-of the act. O'Neill concludes that Kant's examples imply that a maxim must also include circumstances \cite{actingonprinciple}, and 
-Kitcher \cite{whatisamaxim} uses textual evidence from the Groundwork to argue for the inclusion of a maxim's purpose 
-or motivation. In order to formalize the notion of a maxim, I must adopt a specific definition and 
-defend my choice.
-
-I define a maxim as a circumstance, act, goal tuple (C, A, G), read 
-as ``In circumstances C, act A for goal G." Isabelle's strict typing rules mean that the choice of the 
-type of each member of this tuple is significant. A circumstance is represented as a set of worlds 
-$t$ where that circumstance holds. A goal is also a term because it can be true or false at a world if it 
-is realized or not. An act is an open sentence because an act itself is not the kind of thing that can 
-be true or false (as in, an act is not truth-apt), but the combination of a subject performing an act 
-can be true or false at a world depending on whether or not the act is indeed performed by that subject. 
-For example, ``running" is not truth-apt, but ``Sara runs" is truth-apt.
-
-My definition of a maxim is inspired by O'Neill's work on maxims. I will defend my representation
-below and consider an additional component that Kitcher argues for.
-
-$\emph{O'Niell's Original Schematic and The Role of Practical Judgement}$
-
-O'Neill \cite[37]{actingonprinciple} presents what Kitcher \cite{whatisamaxim}  calls the widely accepted 
-view that a maxim is a circumstance, act, goal tuple. A maxim 
-is an action-guiding rule and thus naturally includes an act and the circumstances under which 
-it should be performed, which are often referred to as ``morally relevant circumstances."
-
-She also includes a purpose, end, or goal in the maxim because Kant includes this in many of his 
-example maxims and because Kant argues that human activity, because it is guided by a rational will, 
-is inherently purposive \cite[4:428]{groundwork}. A rational will does not act randomly (else it would not be rational), 
-but instead in the pursuit of ends which it deems valuable. This inclusion is also essential for the version of the universalizability test 
-that I will implement, explained in Section ??.
-
-O'Neill's inclusion of circumstances is potentially controversial because it leaves open the question of what qualifies as a 
-relevant circumstance for a particular maxim. This is gives rise to ``the tailoring objection" \cite[217]{whatisamaxim} \footnote{Kitcher
-cites \cite{kantsethicalthought}  as offering an example of a false positive due to this objection.}, 
-under which maxims are arbitrarily specified to pass the FUL. For example, the maxim ``When my name is Lavanya Singh,
-I will lie to get some easy money," is universalizable, but is clearly a false positive. One solution to 
-this problem is to argue that the circumstance ``When my name is Lavanya Singh" is not morally relevant 
-to the act and goal. This solution requires some discussion of what qualifies as a relevant circumstance.
-
-O'Neill seems to acknowledge the difficulty of determining relevant circumstances when she concedes that a maxim cannot include all 
-of the infinitely many circumstances in which the agent may perform the action\cite[4:428]{actingonprinciple}. She argues that this is 
-an artifact of the fact that maxims are rules of practical reason, the kind of reason that helps us decide what to do 
-and how to do it \cite{bok}. Like any practical rule, 
-maxims require the exercise of practical judgement to determine in which circumstances they should be applied. 
-This judgement, applied in both choosing when to exercise the maxim and in the formulation of the maxim 
-itself, is what determines the ``morally relevant circumstances."
-
-The upshot for computational ethics is that the computer cannot perform all ethical activity alone. 
-Human judgement and the exercise of practical reason are essential to both formulate maxims and 
-determine when the actual conditions of life coincide with the circumstances in which the maxim is relevant. 
-Choosing when to exercise a maxim is less relevant to my project because analyzing a formal representation of the FUL requires 
-making the circumstances in a given scenario precise, but will be important for applications of 
-computational ethics to guiding AI agents. The difficulty in formulating a maxim, on the other hand, demonstrates 
-the important fact that ethics, as presented here, is not a solely computational activity. A
-human being must create a representation for the dilemma they wish to test, effectively translating 
-a complex, real situation into a flat logical structure. This parallels the challenge that programmers 
-face when translating the complexity of reality to a programming langauge or computational representation. Not only will some of the situation's complexity
-inevitably be lost, the outcome of the universalizability test will depend on how the human formulates the maxim
-and whether or not this formulation does indeed include morally relevant circumstances. If the human puts 
-garbage into the test, the test will return garbage out.
-
-While this may appear to be a weakness of my system, I believe that it actually
-allows my system to retain some of the human complexity that many philosophers agree cannot be automated away.\footnote{Powers presents 
-the determination of morally relevant circumstances as an obstacle to the automation of Kantian ethics \cite{powers}.}
-Ethics is a fundamentally human activity. Kant argues that the categorical imperative is a statement 
-about the properties of rational wills. In fact, Korsgaard argues that morality derives its authority over us, 
-or normativity, only because is it a property of a rational will, and we, as human beings, are rational wills.
-If ethics is meant to guide human behavior, the role of the computer becomes clear as not a replacement for our will,
-but instead as a tool to help guide our wills and reason more efficiently 
-and more effectively. Just as calculators don't render mathematicians obsolete, computational ethics
-does not render human judgement or philosophy obsolete. Chapter 4 Section ?? will be devoted to a more complete discussion 
-of this issue.
-
 $\emph{Exclusion of Motive}$
@@
 \end{isamarkuptext}\isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ will\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim\ {\isasymRightarrow}\ s{\isasymRightarrow}\ \ t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}W\ {\isacharunderscore}\ {\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}will\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isachardot}\ {\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}a\ s{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
-\begin{isamarkuptext}%
-Korsgaard claims that ``to will an end, rather than just
-wishing for it or wanting it, is to set yourself to be its cause" \cite[38]{sources}. To will a maxim
-is to set yourself to be the cause of its goal by taking the means 
-specified in the maxim in the relevant circumstances. This coheres with 
-Kitcher's and Korsgaard's understanding of a maxim as a principle or rule to live by.
-
-At worlds
-where the circumstances do not hold, a maxim is vacuously willed. If you decide to act on the rule ``I will 
-do X in these cirumstances", then you are vacuously obeying it when the circumstances don't hold.
-
-The above discussion implies that willing a maxim is particular to the agent, justifying my choice to 
-require that a particular subject will a maxim. O'Neill argues for this interpretation when she distinguishes 
-between the evaluation of a principle, which is generic, and a maxim, which she views as ``individuated only 
-by referring to a person"\cite[13]{actingonprinciple}. I adopt the spirit of this interpretation but modify it slightly 
-by representing the general maxim as a principle that anyone could adopt, and the act of willing the maxim 
-as a person-particular instantiation of the maxim.
-
-I additionally represent a subject as willing a maxim because I use the word `will' as a verb, to mean committing oneself to living by
-the principle of a maxim. This coheres with the FUL, which tests the act willing 
-of a maxim by determining if the maxim could be a universal law that everyone committed to. Formalizing this idea,
-the type of a willed maxim is a term, allowing me
-to use DDL's obligation operator on the notion of willing a maxim. Concretely, my system will prove 
-or disprove statements of the form ``Lavanya is obligated to will the maxim M."
-
-Worlds where the circumstances do not hold are not relevant for determining obligation. Recall that in 
-Benzmueller et. al's definition of the obligation operator,  $O \{B|A\}$ is true at all worlds iff ob(B)(A), or 
-if the obligation function maps A to obligatory in context B (where the context is a set of worlds) \cite{BFP}. This 
-definition implies that worlds outside of B have no bearing on the moral status of A in context B, which 
-coheres with intuitions about contextual obligation. Thus, the dyadic obligation operator 
-disqualifies worlds where the context does not hold, so the vacuous truth of the will statement in 
-these worlds does not matter.
-
-Given that the will abbreviation already excludes worlds where the circumstances fail (by rendering 
-the statement vacuously true at them), one may conclude that the dyadic obligation operator is now useless. 
-Using the dyadic obligation operator allows me to take advantage of the power of DDL to represent the bearing 
-that circumstances have on obligation. DDL has powerful axioms expressing the relationship between circumstances 
-and obligation, such as the fact that obligations are monotonically increasing with respect to broader 
-circumstances. Using the monadic obligation operator would require me to either operate with an empty 
-notion of context or to redefine these axioms. The dyadic obligation operator lets me take advantage of the full 
-power of DDL in expressing contrary-to-duty obligations. This is particularly important for Kantian ethics 
-and the FUL specifically because many critiques of the FUL rely on attention to circumstances (tailoring 
-objection) or lack thereof (ideal theory). This is also an innovation that my custom formalization presents 
-over the prior work. By formally including the notion of a circumstance or context, I am able to represent 
-these objections that Kantian scholars study. Formalizing Kantian ethics in a dyadic deontic logic 
-instead of a monadic deontic logic is a key contribution of this thesis.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ effective\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}\ t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}E\ {\isacharunderscore}\ {\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}effective\ \ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isachardot}\ {\isacharparenleft}{\isacharparenleft}will\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ \isactrlbold {\isasymequiv}\ g{\isacharparenright}{\isachardoublequoteclose}\isanewline
-\isacommand{print{\isacharunderscore}theorems}\isamarkupfalse%
 %
-\begin{isamarkuptext}%
-A maxim is effective for a subject when, if the subject wills it then the goal is achieved, and
-when the subject does not act on it, the goal is not achieved$\footnote{Thank you to Jeremy D. Zucker for helping me think through this.}$ \cite{sepcausation}. 
-The former direction of the implication 
-is intuitive: if the act results in the goal, it was effective in causing the goal. This represents `necessary'
-causality.
-
-The latter direction represents `sufficient' causality, or the idea that, counterfactually,
-if the maxim were not willed, then the goal is not achieved \cite{lewiscausality}. Note that nothing else changes about this
-counterfactual world—the circumstances are identical and we neither added additional theorems nor 
-specified the model any further. This represents Lewis's idea of "comparative similarity,"  where 
-a counterfactual is true if it holds at the most similar world \cite{lewiscounterfactuals}. In our case, this is just the world 
-where everything is the same except the maxim is not acted on.
-
-Combining these ideas, this definition of effective states that a maxim is effective if the 
-maxim being acted on by a subject is the necessary and sufficient cause of the goal.\footnote{Should I wave a hand at critiques of counterfactual causality?}
-
-If the circumstances do not hold and the goal is achieved, then the maxim is vacuously effective, since 
-it is vacuously willed (as described above). While this scenario is counterintuitive, it is not very 
-interesting for my purposes because, when the circumstances do not hold, a maxim is not applicable. It 
-doesn't really make sense to evaluate a maxim when it's not supposed to be applied. The maxim ``When on Jupiter,
-read a book to one-up your nemesis" is vacuously effective because it can never be disproven.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ universalized{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}t{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
-{\isachardoublequoteopen}universalized\ {\isasymequiv}\ {\isasymlambda}M{\isachardot}\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ {\isacharparenleft}W\ M\ p{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ holds{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}t{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
-{\isachardoublequoteopen}holds\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}{\isachardot}\ c{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ not{\isacharunderscore}universalizable\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
-{\isachardoublequoteopen}not{\isacharunderscore}universalizable\ {\isasymequiv}\ {\isasymlambda}M\ s{\isachardot}\ {\isasymforall}w{\isachardot}\ {\isacharparenleft}{\isacharparenleft}universalized\ M{\isacharparenright}\ \ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}E\ M\ s{\isacharparenright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
-%
-\isamarkupcmt{The formula above reads ``at world $w$, if M is universalized and M is acted on (i.e. the circumstances 
-of M hold), then M is not effective."
-
-Notice that the antecedent specifies that the circumstances hold at the given world. 
-When evaluating if a maxim is universalizable or not, we want to ignore worlds where the circumstance 
-do not hold. At these worlds, the maxim is trivially effective and thus trivially universalizable. If we didn't exclude such worlds from 
-consideration, a maxim with circumstances that ever fail to hold would be universalizable. Clearly 
-this is not a desirable conclusion, since maxims like ``When you need money, lie to get easy money"
-would be universalizable.%
-}%
-\begin{isamarkuptext}%
-As before, the concepts of prohibition and permissibility will be helpful here. The unit of 
-evaluation for my formalization of the FUL is the act of willing a maxim, which entails performing 
-the maxim's act in the relevant circumstances. Therefore, I will say that, just as the act of willing a
- maxim can be obligatory for a subject, it can be prohibited or permissible for a subject.\footnote{In 
-the rest of this section, for convenience, I will use the phrase ``subject s willing maxim M is obligatory" 
-interchangeably with ``maxim M is obligatory for subject s." I will use ``maxim M is obligatory" to 
-refer to M being obligatory for any arbitrary subject, which I will show to be equivalent to M being 
-obligatory for a specific subject.}%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ prohibited{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}t{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
-{\isachardoublequoteopen}prohibited\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isachardot}\ O{\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}will\ {\isacharparenleft}c{\isacharcomma}a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ {\isacharbar}\ c{\isacharbraceright}{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ permissible{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}t{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}permissible\ {\isasymequiv}\ {\isasymlambda}M\ s{\isachardot}\ \isactrlbold {\isasymnot}\ {\isacharparenleft}prohibited\ M\ s{\isacharparenright}{\isachardoublequoteclose}\isanewline
-%
-\isamarkupcmt{I will say that a maxim is permissible for a subject if it is not prohibited for that subject to 
-will that maxim.%
-}%
-\begin{isamarkuptext}%
-When analyzing the naive formalization and Kroy's formalization, I learned that DDL and the prior 
-formalizations allow contradictory obligations. This is a major weakness of these systems, and my 
-formalization should fix this. To do so, I will add as an axiom the idea that obligations cannot 
-contradict each other or their internal circumstances. Formally, conflicting obligations are defined below.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ non{\isacharunderscore}contradictory\ \isakeyword{where}\ \isanewline
-{\isachardoublequoteopen}non{\isacharunderscore}contradictory\ A\ B\ c\ w\ {\isasymequiv}\ {\isacharparenleft}{\isacharparenleft}O{\isacharbraceleft}A{\isacharbar}c{\isacharbraceright}\ \isactrlbold {\isasymand}\ O{\isacharbraceleft}B{\isacharbar}c{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isasymnot}{\isacharparenleft}{\isacharparenleft}A\ \isactrlbold {\isasymand}\ {\isacharparenleft}B\ \isactrlbold {\isasymand}\ c{\isacharparenright}{\isacharparenright}\ w\ {\isasymlongrightarrow}\ False{\isacharparenright}{\isachardoublequoteclose}\isanewline
-%
-\isamarkupcmt{Terms A and B are non contradictory in circumstances c if, when A and B are obligated in circumstances 
-c, the conjunction of A, B, and c, does not imply False.%
-}\isanewline
-\isanewline
-\isacommand{axiomatization}\isamarkupfalse%
-\ \isakeyword{where}\ no{\isacharunderscore}contradictions{\isacharcolon}{\isachardoublequoteopen}{\isasymforall}A{\isacharcolon}{\isacharcolon}t{\isachardot}\ {\isasymforall}B{\isacharcolon}{\isacharcolon}t{\isachardot}\ {\isasymforall}c{\isacharcolon}{\isacharcolon}t{\isachardot}\ {\isasymforall}w{\isacharcolon}{\isacharcolon}i{\isachardot}\ non{\isacharunderscore}contradictory\ A\ B\ c\ w{\isachardoublequoteclose}\isanewline
-%
-\isamarkupcmt{This axiom formalizes the idea that, for any terms A, B, and circumstances c, A and B must be 
-non-contradictory in circumstances c at all worlds. Intuitively, this axiom requires that obligations 
-do not conflict.%
-}%
 \isadelimdocument
@@
 \isatagdocument
-%
-\isamarkupsubsection{Formalizing the FUL%
-}
-\isamarkuptrue%
 %
@@
 %
-\begin{isamarkuptext}%
-Below is my first attempt at formalizing Korgsaard's definition of the practical contradiction
-interpretation:  a maxim is not universalizable 
-if, in the world where the maxim becomes the standard practice (i.e. everyone acts on the maxim), the
-agent's attempt to use the maxim's act to achieve the maxim's goal is frustrated. In other words, if 
-the maxim is universally willed (captured by applying a universal qunatifier and the will function 
-to the maxim on the LHS), then it is no longer effective for the subject $s$ (RHS above).%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ FUL{\isadigit{0}}{\isacharcolon}{\isacharcolon}bool\ \isakeyword{where}\ {\isachardoublequoteopen}FUL{\isadigit{0}}\ {\isasymequiv}\ {\isasymforall}\ c\ a\ g\ s{\isachardot}\ not{\isacharunderscore}universalizable\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ {\isasymlongrightarrow}\ {\isasymTurnstile}{\isacharparenleft}{\isacharparenleft}prohibited\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isadelimproof
 %
-\isamarkupcmt{This representation of the Formula of Universal Law reads, ``For all circumstances, goals, acts, 
-and subjects, if the maxim of the subject performing the act for the goal in the circumstances is not 
-universalizable (as defined above), then, at all worlds, in those circumstances, the subject 
-is prohibited (obligated not to) from willing the maxim.%
-}\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}FUL{\isadigit{0}}\ {\isasymlongrightarrow}\ False{\isachardoublequoteclose}%
-\isadelimproof
-\ %
 \endisadelimproof
@@
 \isatagproof
-\isacommand{using}\isamarkupfalse%
-\ O{\isacharunderscore}diamond\isanewline
-\ \ \isacommand{using}\isamarkupfalse%
-\ case{\isacharunderscore}prod{\isacharunderscore}conv\ no{\isacharunderscore}contradictions\ old{\isachardot}prod{\isachardot}case\ old{\isachardot}prod{\isachardot}case\ \isacommand{by}\isamarkupfalse%
-\ fastforce%
+%
 \endisatagproof
@@
 %
-\begin{isamarkuptext}%
-FUL0 is not consistent, and sledgehammer is able to prove this by showing that it implies a contradiction 
-usig axiom O\_diamond, which is \isa{{\isasymTurnstile}{\isasymlambda}w{\isachardot}\ ob\ {\isacharquery}B\ {\isacharquery}A\ {\isasymlongrightarrow}\ {\isasymnot}\ {\isasymTurnstile}\isactrlbold {\isasymnot}\ {\isacharquery}B\isactrlbold {\isasymand}{\isacharquery}A}.
-This axiom captures
-the idea that an obligation can't contradict its context. This is particularly problematic if the goal or 
-action of a maxim are equivalent to its circumstances. In other words, if the maxim has already been 
-acted on or the goal has already been achieved, then prohibiting it is impossible. 
-In any model that has at least one term, it is possible to construct a maxim where the circumstances, goal, 
-and act (once a subject acts on it) are all that same term, resulting in a contradiction.
-
-To get around this, I will exclude what I call ``badly formed maxims," which are those maxims such that the goal has already been 
-achieved or the act has already been acted on. Under my formalization, such maxims are 
-not well-formed. To understand why, I return to Korsgaard's and O'Neill's interpretations of a maxim as a practical
-guide to action. A maxim is a practical principle that guides how we behave in everyday life. A 
-principle of the form ``When you are eating breakfast, eat breakfast in order to eat breakfast," is not 
-practically relevant. No agent would ever need to act on such a principle. It is not contradictory
-or prohibited, but it is the wrong kind of question to be asking. It is not a 
-well-formed maxim, so the categorical imperative does not apply to it. (more explanation in philosophical 
-writing collection)%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ well{\isacharunderscore}formed{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}i{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
-{\isachardoublequoteopen}well{\isacharunderscore}formed\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}{\isachardot}\ {\isasymlambda}s{\isachardot}\ {\isasymlambda}w{\isachardot}\ {\isacharparenleft}{\isasymnot}\ \ {\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ g{\isacharparenright}\ w{\isacharparenright}\ {\isasymand}\ {\isacharparenleft}{\isasymnot}\ \ {\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ a\ s{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
-%
-\isamarkupcmt{This abbreviation formalizes the well-formedness of a maxim for a subject. The goal cannot be 
-already achieved in the circumstances and the subject cannot have already performed the act.%
-}\isanewline
-\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ FUL\ \isakeyword{where}\ {\isachardoublequoteopen}FUL\ {\isasymequiv}\ {\isasymforall}M{\isacharcolon}{\isacharcolon}maxim{\isachardot}\ {\isasymforall}s{\isacharcolon}{\isacharcolon}s{\isachardot}\ {\isacharparenleft}{\isasymforall}w{\isachardot}\ well{\isacharunderscore}formed\ M\ s\ w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}not{\isacharunderscore}universalizable\ M\ s\ {\isasymlongrightarrow}\ {\isasymTurnstile}\ {\isacharparenleft}prohibited\ M\ s{\isacharparenright}\ {\isacharparenright}{\isachardoublequoteclose}\isanewline
-%
-\isamarkupcmt{Let's try the exact same formalization of the FUL as above, except that it only applies to 
-maxims that are well-formed at every world.%
-}\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}FUL{\isachardoublequoteclose}\isanewline
-\ \ \isacommand{nitpick}\isamarkupfalse%
-{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}true{\isacharbrackright}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{oops}\isamarkupfalse%
-\isanewline
-%
-\isamarkupcmt{The FUL does not hold in DDL, because nitpick is able to find a model for my system in which it is 
-false. If the FUL were already a theorem of the system, adding it wouldn't make the system any more 
-powerful, so this is the desired result.
-
-$\color{blue}$ Nitpick found a counterexample for card s = 1 and card i = 1:
-
-  Skolem constants:
-    M = (($\lambda x. \_$)($i_1$ := True), ($\lambda x. \_$)($s_1$ := ($\lambda x. \_$)($i_1$ := False)), ($\lambda x. \_$)
-         ($i_1$ := False))
-    $\lambda$ w. p = ($\lambda x. \_$)($i_1$ := $s_1$)
-    s = $s_1$ $\color{black}$%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isanewline
-\isacommand{axiomatization}\isamarkupfalse%
-\ \isakeyword{where}\ FUL{\isacharcolon}FUL\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ True\isanewline
-\ \ \isacommand{nitpick}\isamarkupfalse%
-{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharbrackright}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{by}\isamarkupfalse%
-\ simp\isanewline
-%
-\isamarkupcmt{Nitpick is able to find a model in which all axioms are satisfied, 
-so this version of the FUL is consistent.
-
-$\color{blue}$ Nitpick found a model for card i = 1 and card s = 1:
-
-  Empty assignment $\color{black}$%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-During the process of making FUL0 consistent, I used Isabelle to gain philosophical insights 
-about vacuous maxims. This process is an example of the power of computational tools to aid
-philosophical progress. I used Nitpick and Sledgehammer to quickly test if a small tweak 
-to FUL0 fixed the inconsistency or if I was still able to derive a contradiction.  I then realized that if 
-I defined the circumstances, act, and goal as constants, then FUL0 was indeed consistent. After some 
-experimentation, Prof. Amin correctly pointed out that as constants, these three entities were 
-distinct. However, when merely quantifying over (c, a, g), all members of a tuple could be equivalent. Within
-a minute, I could formalize this notion, add it to FUL0, and test if it solved the problem. The fact 
-that it did spurred my philosophical insight about vacuous maxims.
-
-The logic confirmed that certain kinds
-of circumstance, act, goal tuples are too badly formed for the categorical imperative to logically 
-apply to them. The realization of this subtle problem would have been incredibly difficult without 
-computational tools. The syntax and typing of Isabelle/HOL forced me to bind the free-variable $M$
-in the FUL in different ways and allowed me to quickly test many bindings. The discovery of this 
-logical inconsistency then enabled a philosophical insight about which kinds of maxims make sense as 
-practical principles. This is one way to do computational ethics: model a system in a logic, use 
-computational tools to refine and debug the logic, and then use insights about the logic to derive 
-insights about the ethical phenonema it is modelling. This procedure parallels the use of proofs in 
-theoretical math to understand the mathematical objects they model.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-One potential problem with my formalization is that it does not use the modal nature of the system. 
-All of the properties that the FUL investigates hold at all worlds, in effect removing the modal nature 
-of the system. This approach simplifies logical and therefore computational complexity, improving 
-performance. On the other hand, it doesn't use the full expressivity of DDL. If I run into problems 
-later on, one option is to tweak the FUL to use this expressivity.%
-\end{isamarkuptext}\isamarkuptrue%
-%
 \isadelimtheory
@@
 \endinput
-%:%file=~/Desktop/cs91r/paper/paper41.thy%:%
-%:%24=6%:%
-%:%36=8%:%
-%:%37=9%:%
-%:%46=11%:%
-%:%58=13%:%
-%:%59=14%:%
-%:%60=15%:%
-%:%61=16%:%
-%:%62=17%:%
-%:%63=18%:%
-%:%65=20%:%
-%:%66=20%:%
-%:%67=20%:%
-%:%68=21%:%
-%:%69=22%:%
-%:%70=23%:%
-%:%71=23%:%
-%:%72=24%:%
-%:%73=25%:%
-%:%74=25%:%
-%:%75=25%:%
-%:%76=26%:%
-%:%77=26%:%
-%:%78=27%:%
-%:%79=28%:%
-%:%80=28%:%
-%:%82=30%:%
-%:%83=31%:%
-%:%84=32%:%
-%:%85=33%:%
-%:%86=34%:%
-%:%87=35%:%
-%:%88=36%:%
-%:%89=37%:%
-%:%90=38%:%
-%:%91=39%:%
-%:%92=40%:%
-%:%93=41%:%
-%:%94=42%:%
-%:%95=43%:%
-%:%96=44%:%
-%:%97=45%:%
-%:%98=46%:%
-%:%99=47%:%
-%:%100=48%:%
-%:%101=49%:%
-%:%102=50%:%
-%:%103=51%:%
-%:%104=52%:%
-%:%105=53%:%
-%:%106=54%:%
-%:%107=55%:%
-%:%108=56%:%
-%:%109=57%:%
-%:%110=58%:%
-%:%111=59%:%
-%:%112=60%:%
-%:%113=61%:%
-%:%114=62%:%
-%:%115=63%:%
-%:%116=64%:%
-%:%117=65%:%
-%:%118=66%:%
-%:%119=67%:%
-%:%120=68%:%
-%:%121=69%:%
-%:%122=70%:%
-%:%123=71%:%
-%:%124=72%:%
-%:%125=73%:%
-%:%126=74%:%
-%:%127=75%:%
-%:%128=76%:%
-%:%129=77%:%
-%:%130=78%:%
-%:%131=79%:%
-%:%132=80%:%
-%:%133=81%:%
-%:%134=82%:%
-%:%135=83%:%
-%:%136=84%:%
-%:%137=85%:%
-%:%138=86%:%
-%:%139=87%:%
-%:%140=88%:%
-%:%141=89%:%
-%:%142=90%:%
-%:%143=91%:%
-%:%144=92%:%
-%:%145=93%:%
-%:%146=94%:%
-%:%147=95%:%
-%:%148=96%:%
-%:%149=97%:%
-%:%150=98%:%
-%:%151=99%:%
-%:%152=100%:%
-%:%153=101%:%
-%:%154=102%:%
-%:%155=103%:%
-%:%156=104%:%
-%:%157=105%:%
-%:%158=106%:%
-%:%159=107%:%
-%:%160=108%:%
-%:%161=109%:%
-%:%162=110%:%
-%:%163=111%:%
-%:%164=112%:%
-%:%165=113%:%
-%:%166=114%:%
-%:%167=115%:%
-%:%168=116%:%
-%:%169=117%:%
-%:%170=118%:%
-%:%171=119%:%
-%:%172=120%:%
-%:%173=121%:%
-%:%174=122%:%
-%:%175=123%:%
-%:%176=124%:%
-%:%177=125%:%
-%:%178=126%:%
-%:%179=127%:%
-%:%180=128%:%
-%:%181=129%:%
-%:%182=130%:%
-%:%183=131%:%
-%:%184=132%:%
-%:%186=134%:%
-%:%187=134%:%
-%:%188=135%:%
-%:%190=137%:%
-%:%191=138%:%
-%:%192=139%:%
-%:%193=140%:%
-%:%194=141%:%
-%:%195=142%:%
-%:%196=143%:%
-%:%197=144%:%
-%:%198=145%:%
-%:%199=146%:%
-%:%200=147%:%
-%:%201=148%:%
-%:%202=149%:%
-%:%203=150%:%
-%:%204=151%:%
-%:%205=152%:%
-%:%206=153%:%
-%:%207=154%:%
-%:%208=155%:%
-%:%209=156%:%
-%:%210=157%:%
-%:%211=158%:%
-%:%212=159%:%
-%:%213=160%:%
-%:%214=161%:%
-%:%215=162%:%
-%:%216=163%:%
-%:%217=164%:%
-%:%218=165%:%
-%:%219=166%:%
-%:%220=167%:%
-%:%221=168%:%
-%:%222=169%:%
-%:%223=170%:%
-%:%224=171%:%
-%:%225=172%:%
-%:%226=173%:%
-%:%227=174%:%
-%:%228=175%:%
-%:%229=176%:%
-%:%230=177%:%
-%:%231=178%:%
-%:%232=179%:%
-%:%233=180%:%
-%:%234=181%:%
-%:%236=184%:%
-%:%237=184%:%
-%:%238=185%:%
-%:%239=186%:%
-%:%242=188%:%
-%:%243=189%:%
-%:%244=190%:%
-%:%245=191%:%
-%:%246=192%:%
-%:%247=193%:%
-%:%248=194%:%
-%:%249=195%:%
-%:%250=196%:%
-%:%251=197%:%
-%:%252=198%:%
-%:%253=199%:%
-%:%254=200%:%
-%:%255=201%:%
-%:%256=202%:%
-%:%257=203%:%
-%:%258=204%:%
-%:%259=205%:%
-%:%260=206%:%
-%:%261=207%:%
-%:%262=208%:%
-%:%264=210%:%
-%:%265=210%:%
-%:%266=211%:%
-%:%267=212%:%
-%:%268=213%:%
-%:%269=213%:%
-%:%270=214%:%
-%:%271=215%:%
-%:%272=216%:%
-%:%273=216%:%
-%:%274=217%:%
-%:%276=218%:%
-%:%277=219%:%
-%:%278=220%:%
-%:%279=221%:%
-%:%280=222%:%
-%:%281=223%:%
-%:%282=224%:%
-%:%283=225%:%
-%:%284=226%:%
-%:%287=228%:%
-%:%288=229%:%
-%:%289=230%:%
-%:%290=231%:%
-%:%291=232%:%
-%:%292=233%:%
-%:%293=234%:%
-%:%294=235%:%
-%:%296=237%:%
-%:%297=237%:%
-%:%298=238%:%
-%:%299=239%:%
-%:%300=240%:%
-%:%301=240%:%
-%:%302=241%:%
-%:%304=242%:%
-%:%305=243%:%
-%:%308=246%:%
-%:%309=247%:%
-%:%310=248%:%
-%:%311=249%:%
-%:%313=251%:%
-%:%314=251%:%
-%:%315=252%:%
-%:%317=253%:%
-%:%318=254%:%
-%:%319=254%:%
-%:%320=255%:%
-%:%321=256%:%
-%:%322=256%:%
-%:%324=257%:%
-%:%325=258%:%
-%:%326=259%:%
-%:%334=261%:%
-%:%346=263%:%
-%:%347=264%:%
-%:%348=265%:%
-%:%349=266%:%
-%:%350=267%:%
-%:%351=268%:%
-%:%353=271%:%
-%:%354=271%:%
-%:%356=272%:%
-%:%357=273%:%
-%:%358=274%:%
-%:%359=275%:%
-%:%360=275%:%
-%:%361=276%:%
-%:%362=277%:%
-%:%363=277%:%
-%:%365=277%:%
-%:%369=277%:%
-%:%370=277%:%
-%:%371=278%:%
-%:%372=278%:%
-%:%373=278%:%
-%:%382=280%:%
-%:%383=281%:%
-%:%384=282%:%
-%:%385=283%:%
-%:%386=284%:%
-%:%387=285%:%
-%:%388=286%:%
-%:%389=287%:%
-%:%390=288%:%
-%:%391=289%:%
-%:%392=290%:%
-%:%393=291%:%
-%:%394=292%:%
-%:%395=293%:%
-%:%396=294%:%
-%:%397=295%:%
-%:%398=296%:%
-%:%400=298%:%
-%:%401=298%:%
-%:%402=299%:%
-%:%404=300%:%
-%:%405=301%:%
-%:%406=301%:%
-%:%407=302%:%
-%:%408=303%:%
-%:%409=303%:%
-%:%411=304%:%
-%:%412=305%:%
-%:%413=305%:%
-%:%414=306%:%
-%:%415=307%:%
-%:%416=307%:%
-%:%417=308%:%
-%:%418=308%:%
-%:%420=308%:%
-%:%424=308%:%
-%:%425=308%:%
-%:%427=309%:%
-%:%428=310%:%
-%:%429=311%:%
-%:%430=312%:%
-%:%431=313%:%
-%:%432=314%:%
-%:%433=315%:%
-%:%434=316%:%
-%:%435=317%:%
-%:%436=318%:%
-%:%437=319%:%
-%:%445=319%:%
-%:%446=320%:%
-%:%447=321%:%
-%:%448=321%:%
-%:%449=322%:%
-%:%450=323%:%
-%:%451=323%:%
-%:%452=324%:%
-%:%453=324%:%
-%:%455=324%:%
-%:%459=324%:%
-%:%460=324%:%
-%:%462=325%:%
-%:%463=326%:%
-%:%464=327%:%
-%:%465=328%:%
-%:%466=329%:%
-%:%467=330%:%
-%:%477=332%:%
-%:%478=333%:%
-%:%479=334%:%
-%:%480=335%:%
-%:%481=336%:%
-%:%482=337%:%
-%:%483=338%:%
-%:%484=339%:%
-%:%485=340%:%
-%:%486=341%:%
-%:%487=342%:%
-%:%488=343%:%
-%:%489=344%:%
-%:%490=345%:%
-%:%491=346%:%
-%:%492=347%:%
-%:%493=348%:%
-%:%494=349%:%
-%:%495=350%:%
-%:%496=351%:%
-%:%500=353%:%
-%:%501=354%:%
-%:%502=355%:%
-%:%503=356%:%
-%:%504=357%:%
-%:%512=359%:%
-%:%520=359%:%
+%:%file=~/Desktop/cs91r/paper/appendix.thy%:%
+%:%24=5%:%
+%:%28=7%:%
+%:%40=10%:%
+%:%41=11%:%
+%:%42=12%:%
+%:%43=13%:%
+%:%44=14%:%
+%:%45=15%:%
+%:%46=16%:%
+%:%47=17%:%
+%:%48=18%:%
+%:%49=19%:%
+%:%50=20%:%
+%:%51=21%:%
+%:%52=22%:%
+%:%53=23%:%
+%:%54=24%:%
+%:%55=25%:%
+%:%56=26%:%
+%:%57=27%:%
+%:%58=28%:%
+%:%59=29%:%
+%:%60=30%:%
+%:%61=31%:%
+%:%62=32%:%
+%:%63=33%:%
+%:%64=34%:%

### 2022-02-12 paper/output/document/paper41.tex
making progress on CHAPTER 3

--- 2021-11-07 paper/output/document/paper41.tex
@@
 %:%504=357%:%
-%:%513=359%:%
-%:%525=361%:%
-%:%526=362%:%
-%:%527=363%:%
-%:%528=364%:%
-%:%532=366%:%
-%:%533=367%:%
-%:%534=368%:%
-%:%535=369%:%
-%:%536=370%:%
-%:%537=371%:%
-%:%538=372%:%
-%:%539=373%:%
-%:%540=374%:%
-%:%541=375%:%
-%:%542=376%:%
-%:%543=377%:%
-%:%544=378%:%
-%:%545=379%:%
-%:%546=380%:%
-%:%547=381%:%
-%:%549=383%:%
-%:%550=383%:%
-%:%552=384%:%
-%:%553=385%:%
-%:%554=385%:%
-%:%555=386%:%
-%:%556=386%:%
-%:%558=387%:%
-%:%559=388%:%
-%:%560=388%:%
-%:%561=389%:%
-%:%562=389%:%
-%:%564=390%:%
-%:%565=391%:%
-%:%566=391%:%
-%:%567=392%:%
-%:%568=393%:%
-%:%569=393%:%
-%:%570=394%:%
-%:%572=395%:%
-%:%575=397%:%
-%:%576=398%:%
-%:%577=399%:%
-%:%579=401%:%
-%:%580=401%:%
-%:%581=402%:%
-%:%583=403%:%
-%:%584=404%:%
-%:%585=405%:%
-%:%586=406%:%
-%:%587=407%:%
-%:%588=407%:%
-%:%589=408%:%
-%:%590=409%:%
-%:%591=409%:%
-%:%592=410%:%
-%:%594=411%:%
-%:%595=412%:%
-%:%596=413%:%
-%:%597=414%:%
-%:%598=415%:%
-%:%599=415%:%
-%:%600=416%:%
-%:%601=417%:%
-%:%602=417%:%
-%:%603=418%:%
-%:%605=419%:%
-%:%606=420%:%
-%:%607=421%:%
-%:%608=422%:%
-%:%609=423%:%
-%:%612=425%:%
-%:%613=426%:%
-%:%615=428%:%
-%:%616=428%:%
-%:%617=429%:%
-%:%618=430%:%
-%:%619=431%:%
-%:%620=432%:%
-%:%627=433%:%
-%:%628=433%:%
-%:%629=434%:%
-%:%630=434%:%
-%:%631=435%:%
-%:%632=435%:%
-%:%634=436%:%
-%:%635=437%:%
-%:%636=437%:%
-%:%637=438%:%
-%:%638=438%:%
-%:%639=439%:%
-%:%640=439%:%
-%:%641=439%:%
-%:%642=440%:%
-%:%652=442%:%
-%:%653=443%:%
-%:%654=444%:%
-%:%655=445%:%
-%:%656=446%:%
-%:%657=447%:%
-%:%658=448%:%
-%:%659=449%:%
-%:%661=451%:%
-%:%662=451%:%
-%:%663=452%:%
-%:%664=452%:%
-%:%665=453%:%
-%:%667=454%:%
-%:%668=455%:%
-%:%669=455%:%
-%:%670=456%:%
-%:%671=457%:%
-%:%672=457%:%
-%:%673=458%:%
-%:%675=459%:%
-%:%676=460%:%
-%:%677=460%:%
-%:%678=461%:%
-%:%679=462%:%
-%:%680=462%:%
-%:%681=463%:%
-%:%682=464%:%
-%:%684=465%:%
-%:%685=465%:%
-%:%686=466%:%
-%:%687=467%:%
-%:%689=468%:%
-%:%690=468%:%
-%:%691=469%:%
-%:%698=470%:%
-%:%699=470%:%
-%:%700=471%:%
-%:%701=471%:%
-%:%702=472%:%
-%:%703=472%:%
-%:%704=472%:%
-%:%705=473%:%
-%:%706=473%:%
-%:%707=474%:%
-%:%708=474%:%
-%:%709=474%:%
-%:%710=475%:%
-%:%711=475%:%
-%:%713=476%:%
-%:%723=478%:%
-%:%724=479%:%
-%:%725=480%:%
-%:%726=481%:%
-%:%727=482%:%
-%:%728=483%:%
-%:%729=484%:%
-%:%730=485%:%
-%:%731=486%:%
-%:%732=487%:%
-%:%733=488%:%
-%:%734=489%:%
-%:%735=490%:%
-%:%736=491%:%
-%:%737=492%:%
-%:%738=493%:%
-%:%739=494%:%
-%:%740=495%:%
-%:%741=496%:%
-%:%742=497%:%
-%:%743=498%:%
-%:%744=499%:%
-%:%745=500%:%
-%:%746=501%:%
-%:%747=502%:%
-%:%748=503%:%
-%:%749=504%:%
-%:%750=505%:%
-%:%751=506%:%
-%:%752=507%:%
-%:%753=508%:%
-%:%754=509%:%
-%:%755=510%:%
-%:%756=511%:%
-%:%757=512%:%
-%:%758=513%:%
-%:%759=514%:%
-%:%760=515%:%
-%:%761=516%:%
-%:%762=517%:%
-%:%766=519%:%
-%:%767=520%:%
-%:%768=521%:%
-%:%770=523%:%
-%:%771=523%:%
-%:%772=524%:%
-%:%773=525%:%
-%:%774=525%:%
-%:%776=525%:%
-%:%780=525%:%
-%:%781=525%:%
-%:%783=526%:%
-%:%784=527%:%
-%:%785=528%:%
-%:%786=529%:%
-%:%787=530%:%
-%:%788=531%:%
-%:%798=534%:%
-%:%799=535%:%
-%:%800=536%:%
-%:%809=538%:%
-%:%821=540%:%
-%:%822=541%:%
-%:%823=542%:%
-%:%824=543%:%
-%:%825=544%:%
-%:%826=545%:%
-%:%827=546%:%
-%:%828=547%:%
-%:%829=548%:%
-%:%830=549%:%
-%:%831=550%:%
-%:%832=551%:%
-%:%833=552%:%
-%:%834=553%:%
-%:%836=555%:%
-%:%837=555%:%
-%:%838=556%:%
-%:%841=557%:%
-%:%845=557%:%
-%:%846=557%:%
-%:%851=557%:%
-%:%854=558%:%
-%:%855=559%:%
-%:%856=559%:%
-%:%857=560%:%
-%:%860=561%:%
-%:%864=561%:%
-%:%865=561%:%
-%:%870=561%:%
-%:%873=562%:%
-%:%874=563%:%
-%:%875=563%:%
-%:%876=564%:%
-%:%879=565%:%
-%:%883=565%:%
-%:%884=565%:%
-%:%889=565%:%
-%:%892=566%:%
-%:%893=567%:%
-%:%894=567%:%
-%:%895=568%:%
-%:%898=569%:%
-%:%902=569%:%
-%:%903=569%:%
-%:%912=571%:%
-%:%913=572%:%
-%:%914=573%:%
-%:%915=574%:%
-%:%916=575%:%
-%:%917=576%:%
-%:%918=577%:%
-%:%920=579%:%
-%:%921=579%:%
-%:%922=580%:%
-%:%923=581%:%
-%:%924=581%:%
-%:%926=581%:%
-%:%930=581%:%
-%:%931=581%:%
-%:%933=582%:%
-%:%934=583%:%
-%:%935=584%:%
-%:%936=585%:%
-%:%937=586%:%
-%:%938=587%:%
-%:%939=588%:%
-%:%940=589%:%
-%:%941=590%:%
-%:%942=591%:%
-%:%943=592%:%
-%:%953=594%:%
-%:%954=595%:%
-%:%956=597%:%
-%:%957=597%:%
-%:%958=598%:%
-%:%961=599%:%
-%:%965=599%:%
-%:%966=599%:%
-%:%968=600%:%
-%:%978=602%:%
-%:%979=603%:%
-%:%981=605%:%
-%:%982=605%:%
-%:%983=606%:%
-%:%986=607%:%
-%:%990=607%:%
-%:%991=607%:%
-%:%992=607%:%
-%:%994=608%:%
-%:%995=609%:%
-%:%1005=611%:%
-%:%1006=612%:%
-%:%1007=613%:%
-%:%1008=614%:%
-%:%1012=616%:%
-%:%1013=617%:%
-%:%1014=618%:%
-%:%1016=620%:%
-%:%1017=620%:%
-%:%1018=621%:%
-%:%1019=622%:%
-%:%1020=623%:%
-%:%1021=623%:%
-%:%1023=623%:%
-%:%1027=623%:%
-%:%1028=623%:%
-%:%1030=624%:%
-%:%1031=625%:%
-%:%1032=626%:%
-%:%1033=627%:%
-%:%1034=628%:%
-%:%1035=629%:%
-%:%1036=630%:%
-%:%1037=631%:%
-%:%1038=632%:%
-%:%1039=633%:%
-%:%1049=635%:%
-%:%1050=636%:%
-%:%1051=637%:%
-%:%1053=639%:%
-%:%1054=639%:%
-%:%1055=640%:%
-%:%1056=641%:%
-%:%1057=641%:%
-%:%1059=641%:%
-%:%1063=641%:%
-%:%1064=641%:%
-%:%1066=642%:%
-%:%1067=643%:%
-%:%1068=644%:%
-%:%1069=645%:%
-%:%1070=646%:%
-%:%1071=647%:%
-%:%1072=648%:%
-%:%1073=649%:%
-%:%1074=650%:%
-%:%1075=651%:%
-%:%1085=653%:%
-%:%1086=654%:%
-%:%1087=655%:%
-%:%1088=656%:%
-%:%1090=658%:%
-%:%1091=658%:%
-%:%1092=659%:%
-%:%1095=660%:%
-%:%1099=660%:%
-%:%1100=660%:%
-%:%1101=660%:%
-%:%1103=661%:%
-%:%1109=661%:%
-%:%1112=662%:%
-%:%1113=663%:%
-%:%1114=663%:%
-%:%1115=664%:%
-%:%1118=665%:%
-%:%1122=665%:%
-%:%1123=665%:%
-%:%1124=665%:%
-%:%1126=666%:%
-%:%1132=666%:%
-%:%1135=667%:%
-%:%1136=668%:%
-%:%1137=668%:%
-%:%1138=669%:%
-%:%1139=670%:%
-%:%1142=671%:%
-%:%1146=671%:%
-%:%1147=671%:%
-%:%1148=671%:%
-%:%1150=672%:%
-%:%1151=673%:%
-%:%1157=673%:%
-%:%1160=674%:%
-%:%1161=675%:%
-%:%1162=675%:%
-%:%1163=676%:%
-%:%1164=677%:%
-%:%1167=678%:%
-%:%1171=678%:%
-%:%1172=678%:%
-%:%1173=678%:%
-%:%1182=680%:%
-%:%1183=681%:%
-%:%1184=682%:%
-%:%1185=683%:%
-%:%1186=684%:%
-%:%1187=685%:%
-%:%1188=686%:%
-%:%1197=688%:%
-%:%1209=690%:%
-%:%1210=691%:%
-%:%1211=692%:%
-%:%1212=693%:%
-%:%1214=695%:%
-%:%1215=695%:%
-%:%1216=696%:%
-%:%1217=697%:%
-%:%1218=697%:%
-%:%1220=697%:%
-%:%1224=697%:%
-%:%1225=697%:%
-%:%1227=698%:%
-%:%1228=699%:%
-%:%1229=700%:%
-%:%1230=701%:%
-%:%1231=702%:%
-%:%1232=703%:%
-%:%1233=704%:%
-%:%1234=705%:%
-%:%1235=706%:%
-%:%1236=707%:%
-%:%1237=708%:%
-%:%1238=708%:%
+%:%513=360%:%
+%:%525=362%:%
+%:%526=363%:%
+%:%527=364%:%
+%:%528=365%:%
+%:%532=367%:%
+%:%533=368%:%
+%:%534=369%:%
+%:%535=370%:%
+%:%536=371%:%
+%:%537=372%:%
+%:%538=373%:%
+%:%539=374%:%
+%:%540=375%:%
+%:%541=376%:%
+%:%542=377%:%
+%:%543=378%:%
+%:%544=379%:%
+%:%545=380%:%
+%:%546=381%:%
+%:%547=382%:%
+%:%549=384%:%
+%:%550=384%:%
+%:%552=385%:%
+%:%553=386%:%
+%:%554=386%:%
+%:%555=387%:%
+%:%556=387%:%
+%:%558=388%:%
+%:%559=389%:%
+%:%560=389%:%
+%:%561=390%:%
+%:%562=390%:%
+%:%564=391%:%
+%:%565=392%:%
+%:%566=392%:%
+%:%567=393%:%
+%:%568=394%:%
+%:%569=394%:%
+%:%570=395%:%
+%:%572=396%:%
+%:%575=398%:%
+%:%576=399%:%
+%:%577=400%:%
+%:%579=402%:%
+%:%580=402%:%
+%:%581=403%:%
+%:%583=404%:%
+%:%584=405%:%
+%:%585=406%:%
+%:%586=407%:%
+%:%587=408%:%
+%:%588=408%:%
+%:%589=409%:%
+%:%590=410%:%
+%:%591=410%:%
+%:%592=411%:%
+%:%594=412%:%
+%:%595=413%:%
+%:%596=414%:%
+%:%597=415%:%
+%:%598=416%:%
+%:%599=416%:%
+%:%600=417%:%
+%:%601=418%:%
+%:%602=418%:%
+%:%603=419%:%
+%:%605=420%:%
+%:%606=421%:%
+%:%607=422%:%
+%:%608=423%:%
+%:%609=424%:%
+%:%612=426%:%
+%:%613=427%:%
+%:%615=429%:%
+%:%616=429%:%
+%:%617=430%:%
+%:%618=431%:%
+%:%619=432%:%
+%:%620=433%:%
+%:%627=434%:%
+%:%628=434%:%
+%:%629=435%:%
+%:%630=435%:%
+%:%631=436%:%
+%:%632=436%:%
+%:%634=437%:%
+%:%635=438%:%
+%:%636=438%:%
+%:%637=439%:%
+%:%638=439%:%
+%:%639=440%:%
+%:%640=440%:%
+%:%641=440%:%
+%:%642=441%:%
+%:%652=443%:%
+%:%653=444%:%
+%:%654=445%:%
+%:%655=446%:%
+%:%656=447%:%
+%:%657=448%:%
+%:%658=449%:%
+%:%659=450%:%
+%:%661=452%:%
+%:%662=452%:%
+%:%663=453%:%
+%:%664=453%:%
+%:%665=454%:%
+%:%667=455%:%
+%:%668=456%:%
+%:%669=456%:%
+%:%670=457%:%
+%:%671=458%:%
+%:%672=458%:%
+%:%673=459%:%
+%:%675=460%:%
+%:%676=461%:%
+%:%677=461%:%
+%:%678=462%:%
+%:%679=463%:%
+%:%680=463%:%
+%:%681=464%:%
+%:%682=465%:%
+%:%684=466%:%
+%:%685=466%:%
+%:%686=467%:%
+%:%687=468%:%
+%:%689=469%:%
+%:%690=469%:%
+%:%691=470%:%
+%:%698=471%:%
+%:%699=471%:%
+%:%700=472%:%
+%:%701=472%:%
+%:%702=473%:%
+%:%703=473%:%
+%:%704=473%:%
+%:%705=474%:%
+%:%706=474%:%
+%:%707=475%:%
+%:%708=475%:%
+%:%709=475%:%
+%:%710=476%:%
+%:%711=476%:%
+%:%713=477%:%
+%:%723=479%:%
+%:%724=480%:%
+%:%725=481%:%
+%:%726=482%:%
+%:%727=483%:%
+%:%728=484%:%
+%:%729=485%:%
+%:%730=486%:%
+%:%731=487%:%
+%:%732=488%:%
+%:%733=489%:%
+%:%734=490%:%
+%:%735=491%:%
+%:%736=492%:%
+%:%737=493%:%
+%:%738=494%:%
+%:%739=495%:%
+%:%740=496%:%
+%:%741=497%:%
+%:%742=498%:%
+%:%743=499%:%
+%:%744=500%:%
+%:%745=501%:%
+%:%746=502%:%
+%:%747=503%:%
+%:%748=504%:%
+%:%749=505%:%
+%:%750=506%:%
+%:%751=507%:%
+%:%752=508%:%
+%:%753=509%:%
+%:%754=510%:%
+%:%755=511%:%
+%:%756=512%:%
+%:%757=513%:%
+%:%758=514%:%
+%:%759=515%:%
+%:%760=516%:%
+%:%761=517%:%
+%:%762=518%:%
+%:%766=520%:%
+%:%767=521%:%
+%:%768=522%:%
+%:%770=524%:%
+%:%771=524%:%
+%:%772=525%:%
+%:%773=526%:%
+%:%774=526%:%
+%:%776=526%:%
+%:%780=526%:%
+%:%781=526%:%
+%:%783=527%:%
+%:%784=528%:%
+%:%785=529%:%
+%:%786=530%:%
+%:%787=531%:%
+%:%788=532%:%
+%:%798=535%:%
+%:%799=536%:%
+%:%800=537%:%
+%:%809=539%:%
+%:%821=541%:%
+%:%822=542%:%
+%:%823=543%:%
+%:%824=544%:%
+%:%825=545%:%
+%:%826=546%:%
+%:%827=547%:%
+%:%828=548%:%
+%:%829=549%:%
+%:%830=550%:%
+%:%831=551%:%
+%:%832=552%:%
+%:%833=553%:%
+%:%834=554%:%
+%:%836=556%:%
+%:%837=556%:%
+%:%838=557%:%
+%:%841=558%:%
+%:%845=558%:%
+%:%846=558%:%
+%:%851=558%:%
+%:%854=559%:%
+%:%855=560%:%
+%:%856=560%:%
+%:%857=561%:%
+%:%860=562%:%
+%:%864=562%:%
+%:%865=562%:%
+%:%870=562%:%
+%:%873=563%:%
+%:%874=564%:%
+%:%875=564%:%
+%:%876=565%:%
+%:%879=566%:%
+%:%883=566%:%
+%:%884=566%:%
+%:%889=566%:%
+%:%892=567%:%
+%:%893=568%:%
+%:%894=568%:%
+%:%895=569%:%
+%:%898=570%:%
+%:%902=570%:%
+%:%903=570%:%
+%:%912=572%:%
+%:%913=573%:%
+%:%914=574%:%
+%:%915=575%:%
+%:%916=576%:%
+%:%917=577%:%
+%:%918=578%:%
+%:%920=580%:%
+%:%921=580%:%
+%:%922=581%:%
+%:%923=582%:%
+%:%924=582%:%
+%:%926=582%:%
+%:%930=582%:%
+%:%931=582%:%
+%:%933=583%:%
+%:%934=584%:%
+%:%935=585%:%
+%:%936=586%:%
+%:%937=587%:%
+%:%938=588%:%
+%:%939=589%:%
+%:%940=590%:%
+%:%941=591%:%
+%:%942=592%:%
+%:%943=593%:%
+%:%953=595%:%
+%:%954=596%:%
+%:%956=598%:%
+%:%957=598%:%
+%:%958=599%:%
+%:%961=600%:%
+%:%965=600%:%
+%:%966=600%:%
+%:%968=601%:%
+%:%978=603%:%
+%:%979=604%:%
+%:%981=606%:%
+%:%982=606%:%
+%:%983=607%:%
+%:%986=608%:%
+%:%990=608%:%
+%:%991=608%:%
+%:%992=608%:%
+%:%994=609%:%
+%:%995=610%:%
+%:%1005=612%:%
+%:%1006=613%:%
+%:%1007=614%:%
+%:%1008=615%:%
+%:%1012=617%:%
+%:%1013=618%:%
+%:%1014=619%:%
+%:%1016=621%:%
+%:%1017=621%:%
+%:%1018=622%:%
+%:%1019=623%:%
+%:%1020=624%:%
+%:%1021=624%:%
+%:%1023=624%:%
+%:%1027=624%:%
+%:%1028=624%:%
+%:%1030=625%:%
+%:%1031=626%:%
+%:%1032=627%:%
+%:%1033=628%:%
+%:%1034=629%:%
+%:%1035=630%:%
+%:%1036=631%:%
+%:%1037=632%:%
+%:%1038=633%:%
+%:%1039=634%:%
+%:%1049=636%:%
+%:%1050=637%:%
+%:%1051=638%:%
+%:%1053=640%:%
+%:%1054=640%:%
+%:%1055=641%:%
+%:%1056=642%:%
+%:%1057=642%:%
+%:%1059=642%:%
+%:%1063=642%:%
+%:%1064=642%:%
+%:%1066=643%:%
+%:%1067=644%:%
+%:%1068=645%:%
+%:%1069=646%:%
+%:%1070=647%:%
+%:%1071=648%:%
+%:%1072=649%:%
+%:%1073=650%:%
+%:%1074=651%:%
+%:%1075=652%:%
+%:%1085=654%:%
+%:%1086=655%:%
+%:%1087=656%:%
+%:%1088=657%:%
+%:%1090=659%:%
+%:%1091=659%:%
+%:%1092=660%:%
+%:%1095=661%:%
+%:%1099=661%:%
+%:%1100=661%:%
+%:%1101=661%:%
+%:%1103=662%:%
+%:%1109=662%:%
+%:%1112=663%:%
+%:%1113=664%:%
+%:%1114=664%:%
+%:%1115=665%:%
+%:%1118=666%:%
+%:%1122=666%:%
+%:%1123=666%:%
+%:%1124=666%:%
+%:%1126=667%:%
+%:%1132=667%:%
+%:%1135=668%:%
+%:%1136=669%:%
+%:%1137=669%:%
+%:%1138=670%:%
+%:%1139=671%:%
+%:%1142=672%:%
+%:%1146=672%:%
+%:%1147=672%:%
+%:%1148=672%:%
+%:%1150=673%:%
+%:%1151=674%:%
+%:%1157=674%:%
+%:%1160=675%:%
+%:%1161=676%:%
+%:%1162=676%:%
+%:%1163=677%:%
+%:%1164=678%:%
+%:%1167=679%:%
+%:%1171=679%:%
+%:%1172=679%:%
+%:%1173=679%:%
+%:%1182=681%:%
+%:%1183=682%:%
+%:%1184=683%:%
+%:%1185=684%:%
+%:%1186=685%:%
+%:%1187=686%:%
+%:%1188=687%:%
+%:%1197=689%:%
+%:%1209=691%:%
+%:%1210=692%:%
+%:%1211=693%:%
+%:%1212=694%:%
+%:%1214=696%:%
+%:%1215=696%:%
+%:%1216=697%:%
+%:%1217=698%:%
+%:%1218=698%:%
+%:%1220=698%:%
+%:%1224=698%:%
+%:%1225=698%:%
+%:%1227=699%:%
+%:%1228=700%:%
+%:%1229=701%:%
+%:%1230=702%:%
+%:%1231=703%:%
+%:%1232=704%:%
+%:%1233=705%:%
+%:%1234=706%:%
+%:%1235=707%:%
+%:%1236=708%:%
+%:%1237=709%:%
+%:%1238=709%:%

### 2022-02-12 paper/output/document/paper412.tex
making progress on CHAPTER 3

@@
 when universalized but literally impossible because the practice breaks down. I capture this idea in the 
-assumption \isa{everyone{\isacharunderscore}can{\isacharprime}t{\isacharunderscore}lie\ {\isasymequiv}\ {\isasymforall}w{\isachardot}\ {\isasymnot}\ {\isacharparenleft}{\isasymforall}s{\isachardot}\ falsely{\isacharunderscore}promise\ s\ w{\isacharparenright}}, which states that, at all worlds, not everyone can falsely promise since
+assumption \isa{paper{\isadigit{4}}{\isadigit{1}}{\isadigit{2}}{\isachardot}everyone{\isacharunderscore}can{\isacharprime}t{\isacharunderscore}lie\ {\isasymequiv}\ {\isasymforall}w{\isachardot}\ {\isasymnot}\ {\isacharparenleft}{\isasymforall}s{\isachardot}\ paper{\isadigit{4}}{\isadigit{1}}{\isadigit{2}}{\isachardot}falsely{\isacharunderscore}promise\ s\ w{\isacharparenright}}, which states that, at all worlds, not everyone can falsely promise since
 otherwise the practice of promising would break down. The second reading, on the other hand, reads the 

### 2022-02-12 paper/output/document/thesis_0_abstract.tex
making progress on CHAPTER 3

@@
 responsibly navigate the world. All decisions are moral decisions, including those that AI agents are actively 
-making today. If automated ethics draws on sophisticated philosophical literature, it will make the ethical reasoning
-underlying such decisions nuanced, precise and reliable. However, faithfully translating complex ethical theories
+making today. If automated ethics draws on sophisticated philosophical literature, the ethical reasoning
+underlying such decisions will be more nuanced, precise, consistent, and trustworthy. However, faithfully translating complex ethical theories
 from natural language to the rigid syntax of a computer program poses technical and philosophical 
@@
 between lying and joking and the example of a murderer knocking on your door asking about the location of their
-intended victim.
+intended victim. Finally, I examine the philosophical implications of this system, exploring its limitations 
+and its potential to help both AI agents and human beings better reason about ethics.
 
 Armed with relatively uncontroversial facts about the world, my system is able to correctly
-resolve these moral dilemmas because it is grounded in philosophical literature.
+resolve complex moral dilemmas because it is grounded in philosophical literature.
 Moreover, because I automate an explicit ethical theory, the ethical reasoning underlying my system's judgements
@@
 %:%51=38%:%
+%:%52=39%:%

### 2022-02-12 paper/output/document/thesis_1_intro.tex
compiled methods, need to edit next
making progress on CHAPTER 3

@@
 %
-\isamarkupsection{Introduction%
+\isamarkupsection{Introduction\label{intro}%
 }
@@
 not typical of the operation of a self-driving car, every decision that such an AI agent makes, from 
-avoiding congested freeways to carpooling, is morally tinged. AI agents routinely make decisions with 
+avoiding congested freeways to carpooling, is morally tinged. Not only do AI agents routinely make decisions with 
 ethical implications without explicitly performing ethical
-reasoning and, in many cases, without human supervision. For example, the Alleghany Family Screening 
+reasoning, in many cases, they do so without human supervision. For example, the Alleghany Family Screening 
 tool can automatically trigger an investigation into a potential case of child neglect, a decision that 
 can uproot entire families and is known to be biased against poor people of color \citep{eubanks}. 
-Not only are machines making moral decisions without actually performing ethical reasoning, they're 
-doing so without human involvement. This motivates the need for machine ethics (also called automated ethics), 
+This motivates the need for machine ethics (also called automated ethics), 
 or the study of how to develop machines that can perform robust, sophisticated ethical reasoning.
@@
 consequentialism (\citep{util1}, \citep{util2}, \citep{cloos}), and virtue ethics \citep{berberich} rarely 
-engages with philosophical literature and thus misses philosophers' insights. Even the above example of 
+engages with philosophical literature and thus often misses philosophers' insights. Even the above example of 
 the malfunctioning self-driving car is an instance of Phillipa Foot's trolley problem, 
@@
 Decades of philosophical debate have developed ethical theories that can offer nuanced and 
-consistent answers to the trolley problem. The trolley problem demonstrates that the moral dilemmas 
+consistent answers to the trolley problem. Like the trolley problem, the moral dilemmas 
 that artifical agents face are not entirely new, so solutions to these problems should take advantage of philosophical 
-progress. The more faithful that automated ethics is to philosophical literature, the more reliable and 
-nuanced it will be.
+progress. Philosophers are devoted to the creation of better ethical theories, so the 
+more faithful that automated ethics is to philosophical literature, the more nuanced, precise, consistent, and
+therefore trustworthy it will be.
 
@@
 an ethical dilemma, is equally as important in determining the machine's decisions. Another complication
-is that philosophers do not agree that on a single choice of ethical theory. Even philosophers who
-agree that a specific ethical theory, like Kantian ethics, is true, debate the theory's 
+is that philosophers do not agree that on a single choice of ethical theory. Philosophers who
+so agree that a specific ethical theory, like Kantian ethics, is true, still debate the theory's 
 details.\footnote{For examples of these debates in the case of Kantian ethics, see Section Joking
-and Section Murderer.} Even once reasoning within a 
+and Section Murderer.} Moreover, even once reasoning within a 
 particular ethical theory is automated, those who disagree with that theory will disagree with the 
@@
 sophisticated solutions to two ethical dilemmas often used in critiques of Kantian ethics. Because 
-my system is faithful to philosophical literature, it is able to provide nuanced answers to these paradoxes.
+my system is faithful to philosophical literature, it is able to provide nuanced answers to these paradoxes
+that require a deep understanding of Kantian ethics.
 
@@
 about ethics helped me, a human philosopher, arrive at a philosophical conclusion that has implications for practical
-reason and philosophy of doubt. Thus, my system can be used in two distinct ways. First, to help
+reason and philosophy of doubt. Thus, my system can be used in two distinct ways. First, my system can help
 automated agents navigate the world, which I will refer to as automated ethics or machine ethics interchangeably. Second, 
-to help human philosophers reason about philosophy, which I call computational ethics.%
+my system help human philosophers reason about philosophy, which I call computational ethics.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %:%196=167%:%
+%:%197=168%:%

### 2022-02-12 paper/output/document/thesis_3_implementation.tex
making progress on CHAPTER 3

--- 2022-01-22 paper/output/document/paper41.tex
@@
 \begin{isabellebody}%
-\setisabellecontext{paper{\isadigit{4}}{\isadigit{1}}}%
+\setisabellecontext{thesis{\isacharunderscore}{\isadigit{3}}{\isacharunderscore}implementation}%
 %
@@
 %
-\isamarkupsection{Novel Formalization of the Categorical Imperative%
+\isamarkupsection{Implementation Details\label{details}%
 }
@@
 \begin{isamarkuptext}%
-In this section, I present a custom formalization of the categorical imperative, as inspired by 
-the goals from the previous chapter.%
+In this section, I present the details of my implementation of automated Kantian ethics. I take
+a logic-programming approach in which I formalize the FUL in Dyadic Deontic Logic and then implement 
+this logic in Isabelle/HOl. I 
+also present my testing framework, which demonstrates one way to evaluate how faithful an implementation
+of automated ethics is to philosophical literature. This testing framework shows that my system outperforms
+two other possible implementations of automated Kantian Ethics.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupsubsection{Logical Background%
+\isamarkupsubsection{Formalization and Implementation of the FUL%
 }
@@
 \begin{isamarkuptext}%
-The previous attempts to model the categorical imperative in Chapter 2 partially failed due to 
-an inability to fully represent the complexity of a maxim. Specifically, they treated actions as a single, 
-monolithic unit of evaluation, whereas most Kantians consider the unit of evaluation for the FUL to the more
-complex notion of a maxim. In this section, I will present some logical background necessarily to fully 
-capture the spirit of a maxim. I will begin by borrowing some machinery to handle ``subjects" who perform 
-actions from Chapter 2.%
+Before formalizing the FUL, I must define and implement the relevant logical background. Dyadic
+Deontic Logic can express obligation and prohibition, but it cannot represent more complex features of 
+moral judgement like actions, subject, maxims, and ends. I augment DDL by adding representations 
+of these concepts, drawn from philosophical literature.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsubsection{Logical Background%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
+Kantian ethics is centered on practical reason because it is action-guiding; the categorical
+imperative is a moral rule that agents can use to decide between potential actions. Thus, before I even
+begin to formalize a specific formulation of the categorical imperative, I must define the notions of 
+subjects and actions. Concretely, I need to add logical background so that my logic can express sentences 
+like, ``x does action.''%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \ s\ %
-\isamarkupcmt{s is the type for a ``subject," i.e. the subject of a sentence. In this interpretation, 
-a subject is merely defined as ``that which can act." It does not include any other properties, such as 
-rationality or dignity. As I will show, for the purposes of defining the universalizability test, this 
-``thin" representation of a subject suffices.%
-}\isanewline
-\isanewline
+\isamarkupcmt{I declare a new type, $s$ as the type for a ``subject,'' i.e. the subject of a sentence.%
+}%
+\begin{isamarkuptext}%
+The \texttt{typedecl} keyword indicates that I am defining a new atomic type, which is not composed
+of pre-existing types but is instead a new kind of thing altogether. I try to minimize the number of 
+atomic types, so this will be one of the few new types that I define. To define a subject, it suffices
+to declare a new type to represent a subject, as that is all that is needed to apply the Formula of
+Universal Law. Notice that I have not defined any properties of this type, such as the idea that a subject
+must be rational or human. Throughout my project, I will use bare syntactic units like types and constants 
+to define new ideas and will add the minimum necessary definitions, or ``thin'' definitions, to achieve the desired results.
+By avoiding complex definitions of a subject, I can avoid murky philosophical debates about the nature
+of agency and reduce the potential for controversy or errors.
+
+In this interpretation, the defining feature of a subject is that it can act, a relatively uncontroversial
+notion. I represent that below by allowing subjects to substitute into sentences, a property that I will use 
+to represent the notion of different people performing certain actions.%
+\end{isamarkuptext}\isamarkuptrue%
 \isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
 \ os\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}s\ {\isasymRightarrow}\ t{\isacharparenright}{\isachardoublequoteclose}\ %
-\isamarkupcmt{Recall that an open sentence maps a subject to a term to model the 
-substitution operator.%
-}\isanewline
-\isanewline
+\isamarkupcmt{To model the idea of a subject being substituted into an action, I 
+define \texttt{type\_synonym} $os$ for an open sentence. An open sentence takes as input a subject and 
+returns a complete or ``closed'' DDL formula by, binding the free variable in the sentence to the input. 
+For example, ``runs'' is an open sentence that can be instantiated with subject, ``Sara'' to create
+the DDL term ``Sara runs,'' which can be true or false at a world. An open sentence itself is not
+the kind of thing that can be true or false at a world, so it is not truth-apt, but when an action is 
+substituted into an open sentence, the resulting term is truth apt. ``Runs'' is not the kind of thing 
+that can be true or false, but ``Sara runs'' is a sentence that can be true or false.%
+}%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsubsection{Maxim \label{whatisamaxim}%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
+Recall from Section \ref{whyful} that I formalize a version of the categorical imperative called
+the Formula of Universal, which reads ``act only according to that maxim by which you can at the same 
+time will that it should become a universal law'' \cite{groundwork}. In order to faithfully formalize
+the FUL, I must make precise the notions of of ``willing a maxim'' and violating the FUL. I draw on 
+reliable definitions of willing, maxims, and the FUL from Kantian literature and represent them in DDL.
+
+The central unit of evaluation for Kantian ethics is a ``maxim,'' which Kant defines as ``the subjective 
+principle of willing,'' or the principle that the agent understands themselves as acting on \cite{groundwork}. 
+Modern Kantians differ in their interpretations of this definition. I adopt O'Neill's view, derived from 
+Kant's example maxims, that a maxim includes the act, the circumstances, and the agent's purpose of 
+acting or goal \citep{actingonprinciple}.
+
+\begin{definition}[Maxim]
+    A maxim is a circumstance, act, goal tuple (C, A, G), read as ``In circumstances C, act A for goal G.''
+\end{definition}
+
+I implement this definition in Isabelle by defining the \texttt{type\_synonym} below for the type
+of a maxim.%
+\end{isamarkuptext}\isamarkuptrue%
 \isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
-\ maxim\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}t\ {\isacharasterisk}\ os\ {\isacharasterisk}\ t{\isacharparenright}{\isachardoublequoteclose}%
+\ maxim\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}t\ {\isacharasterisk}\ os\ {\isacharasterisk}\ t{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{A maxim is of type term, open sentence, term tuple, such as ``(When I am broke, will falsely promise
+to repay a loan, to get some easy cash)''. The first term represents the circumstance, which
+can be true or false at a world. For example, the circumstance ``when I am broke'' is true at the real 
+world when my bank account is empty. The second term represents the action, which is an open sentence
+because different agents can perform a particular action. For example, the action, ``will falsely promise
+to repay a loan'' is an open sentence that can be acted on by a subject. The third term represents 
+the goal, which can again be true or false at a world. For example, the goal ``to get some easy cash''
+is true at the real world if I have gotten easy cash.%
+}%
 \begin{isamarkuptext}%
-The central unit of evaluation for the universalizability test is a ``maxim," which Kant defines 
-in a footnote in \emph{Groundwork} as ``the subjective principle of willing," or the principle that 
-the agent acts on \cite[16]{groundwork}. Modern Kantians differ in their interpretations of this definition. The naive view 
-is that a maxim is an act, but Korsgaard adopts the more sophisticated view that a maxim is composed
-of an act and the agent's purpose for acting \cite{actingforareason}. She also compares a maxim 
-to Aristotle's logos, which includes these components and information about the circumstances and methods 
-of the act. O'Neill concludes that Kant's examples imply that a maxim must also include circumstances \cite{actingonprinciple}, and 
-Kitcher \cite{whatisamaxim} uses textual evidence from the Groundwork to argue for the inclusion of a maxim's purpose 
-or motivation. In order to formalize the notion of a maxim, I must adopt a specific definition and 
-defend my choice.
+O'Neill \cite[37]{actingonprinciple} argues that maxim 
+is an action-guiding rule and thus naturally includes an act and the circumstances under which 
+it should be performed, which are often referred to as ``morally relevant circumstances'' \citep[37]{actingonprinciple}. 
+She also includes a purpose, end, or goal in the maxim because human activity, is guided by a rational will, 
+and is thus inherently purposive \citep[4:428]{groundwork}. A rational will does not act randomly (else it would not be rational), 
+but instead in the pursuit of ends which it deems valuable\footnote{Some argue that a maxim should also
+include the agent's motive or motivation and I address this concern in Appendix \ref{maximmotive}.}. The inclusion a maxim's end is essential for the version of the FUL
+that I will implement, explained in Section Practical Contradiction.
 
-I define a maxim as a circumstance, act, goal tuple (C, A, G), read 
-as ``In circumstances C, act A for goal G." Isabelle's strict typing rules mean that the choice of the 
-type of each member of this tuple is significant. A circumstance is represented as a set of worlds 
-$t$ where that circumstance holds. A goal is also a term because it can be true or false at a world if it 
-is realized or not. An act is an open sentence because an act itself is not the kind of thing that can 
-be true or false (as in, an act is not truth-apt), but the combination of a subject performing an act 
-can be true or false at a world depending on whether or not the act is indeed performed by that subject. 
-For example, ``running" is not truth-apt, but ``Sara runs" is truth-apt.
-
-My definition of a maxim is inspired by O'Neill's work on maxims. I will defend my representation
-below and consider an additional component that Kitcher argues for.
-
-$\emph{O'Niell's Original Schematic and The Role of Practical Judgement}$
-
-O'Neill \cite[37]{actingonprinciple} presents what Kitcher \cite{whatisamaxim}  calls the widely accepted 
-view that a maxim is a circumstance, act, goal tuple. A maxim 
-is an action-guiding rule and thus naturally includes an act and the circumstances under which 
-it should be performed, which are often referred to as ``morally relevant circumstances."
-
-She also includes a purpose, end, or goal in the maxim because Kant includes this in many of his 
-example maxims and because Kant argues that human activity, because it is guided by a rational will, 
-is inherently purposive \cite[4:428]{groundwork}. A rational will does not act randomly (else it would not be rational), 
-but instead in the pursuit of ends which it deems valuable. This inclusion is also essential for the version of the universalizability test 
-that I will implement, explained in Section ??.
-
+\color{red} SHOULD THIS GO HERE OR IN THE LIMITATIONS SECTION OF THE DISCUSSION
 O'Neill's inclusion of circumstances is potentially controversial because it leaves open the question of what qualifies as a 
-relevant circumstance for a particular maxim. This is gives rise to ``the tailoring objection" \cite[217]{whatisamaxim} \footnote{Kitcher
-cites \cite{kantsethicalthought}  as offering an example of a false positive due to this objection.}, 
-under which maxims are arbitrarily specified to pass the FUL. For example, the maxim ``When my name is Lavanya Singh,
+relevant circumstance for a particular maxim. This is gives rise to ``the tailoring objection" \citep[217]{whatisamaxim} \footnote{Kitcher
+cites \citet{kantsethicalthought} as offering an example of a false positive due to this objection.}, 
+under which maxims are arbitrarily specified to pass the FUL. For example, the maxim ``When my name is Jane Doe,
 I will lie to get some easy money," is universalizable, but is clearly a false positive. One solution to 
-this problem is to argue that the circumstance ``When my name is Lavanya Singh" is not morally relevant 
-to the act and goal. This solution requires some discussion of what qualifies as a relevant circumstance.
+this problem is to argue that the circumstance ``When my name is Jane Doe" is not morally relevant 
+to the act and goal. This solution requires determining what qualifies as a relevant circumstance.
 
 O'Neill seems to acknowledge the difficulty of determining relevant circumstances when she concedes that a maxim cannot include all 
-of the infinitely many circumstances in which the agent may perform the action\cite[4:428]{actingonprinciple}. She argues that this is 
+of the infinitely many circumstances in which the agent may perform an action \citep[4:428]{actingonprinciple}. She argues that this is 
 an artifact of the fact that maxims are rules of practical reason, the kind of reason that helps us decide what to do 
-and how to do it \cite{bok}. Like any practical rule, 
+and how to do it \citep{bok}. Like any practical rule, 
 maxims require the exercise of practical judgement to determine in which circumstances they should be applied. 
 This judgement, applied in both choosing when to exercise the maxim and in the formulation of the maxim 
-itself, is what determines the ``morally relevant circumstances."
+itself, is what determines the morally relevant circumstances.
 
-The upshot for computational ethics is that the computer cannot perform all ethical activity alone. 
-Human judgement and the exercise of practical reason are essential to both formulate maxims and 
-determine when the actual conditions of life coincide with the circumstances in which the maxim is relevant. 
-Choosing when to exercise a maxim is less relevant to my project because analyzing a formal representation of the FUL requires 
-making the circumstances in a given scenario precise, but will be important for applications of 
-computational ethics to guiding AI agents. The difficulty in formulating a maxim, on the other hand, demonstrates 
-the important fact that ethics, as presented here, is not a solely computational activity. A
-human being must create a representation for the dilemma they wish to test, effectively translating 
-a complex, real situation into a flat logical structure. This parallels the challenge that programmers 
-face when translating the complexity of reality to a programming langauge or computational representation. Not only will some of the situation's complexity
-inevitably be lost, the outcome of the universalizability test will depend on how the human formulates the maxim
+The difficulty in determining relevant circumstances is a limitation of my system and may require that a 
+human being formulate the maxim or that future work develop heuristics to classify circumstances as morally 
+relevant. For proponents of the ``human-in-the-loop'' model of AI ethics, in which ethical AI requires that 
+humans guide machines, this kind of human involvement may be a feature \citep{loop}. In this model, 
+a human being must create a representation for the dilemma they wish to test, translating 
+a complex situation into a flat logical structure. This parallels the challenge that programmers 
+face when translating the complexity of reality to a programming langauge or computational representation. 
+The outcome of the universalizability test will depend on how the human formulates the maxim
 and whether or not this formulation does indeed include morally relevant circumstances. If the human puts 
@@
 
-While this may appear to be a weakness of my system, I believe that it actually
-allows my system to retain some of the human complexity that many philosophers agree cannot be automated away.\footnote{Powers presents 
-the determination of morally relevant circumstances as an obstacle to the automation of Kantian ethics \cite{powers}.}
-Ethics is a fundamentally human activity. Kant argues that the categorical imperative is a statement 
-about the properties of rational wills. In fact, Korsgaard argues that morality derives its authority over us, 
-or normativity, only because is it a property of a rational will, and we, as human beings, are rational wills.
-If ethics is meant to guide human behavior, the role of the computer becomes clear as not a replacement for our will,
-but instead as a tool to help guide our wills and reason more efficiently 
-and more effectively. Just as calculators don't render mathematicians obsolete, computational ethics
-does not render human judgement or philosophy obsolete. Chapter 4 Section ?? will be devoted to a more complete discussion 
-of this issue.
+Another solution to this problem may be to develop heuristics to classify circumstances as morally 
+relevant. For example, one such attempt could define a moral closeness relation between an action, a 
+goal, and circumstances. This heuristic would define morally relevant circumstance as those that 
+reach a certain closeness threshhold with the action and the goal. Determining morally relevant
+circumstances, either using heuristics or human involvement, is a ripe area for future work.
+\color{black}
 
-$\emph{Exclusion of Motive}$
+To will a maxim is to adopt it as a principle to live by, or to commit oneself to the action for the 
+sake of the end in the relevant circumstances. Korsgaard argues that ``to will an end, rather than 
+just wishing for it or wanting it, is to set yourself to be its cause" \cite[38]{sources}. I formalize
+this idea in Definition \ref{willing}.
 
-Kitcher begins with O'Niell's circumstance, act, goal view and expands it to include the motive 
-behind performing the maxim \cite{whatisamaxim}. This additional component is read 
-as ``In circumstance C, I will do A in order to G because of M," where M may be ``duty" or ``self-love."
-Kitcher argues that the inclusion of motive is necessary for the fullest, most general form of a maxim
-in order to capture Kant's idea that an action derives its moral worth from being done for the sake of duty itself.
-Under this view, the FUL would obligate maxims of the form 
-``In circumstance C, I will do A in order to G because I can will that I and everyone else simultaneously
-will do A in order to G in circumstance C." In other words, if Kant is correct in arguing that moral 
-actions must be done from the motive of duty, the affirmative result of the FUL becomes 
-the motive for a moral action.
+\begin{definition}[Willing]\label{willing}
+For maxim $M = (C, A, G)$ and actor $s$,
 
-While Kitcher's conception of a maxim captures Kant's idea of acting for duty's own sake, I will not implement it 
-because it is not necessary for putting maxims through the FUL. Indeed, Kitcher acknowledges that 
-O'Neill's formulation suffices for the universalizability test, but is not the general notion of a maxim.
-In order to pass the maxim through the FUL, it suffices to know the circumstance, act, and goal. The FUL
-derives the motive that Kitcher bundles into the maxim, so automating the FUL does not require 
-including a motive. The ``input" to the FUL is the circumstance, act, goal tuple. My project takes 
-this input and returns the motivation that the dutiful, moral agent would adopt. Additionally, doing
-justice to the rich notion of motive requires modelling the operation of practical reason itself, 
-which is outside the scope of this project. My work focuses on the universalizability test, but future work that 
-models the process of practical reason may use my implementation of the FUL as a ``library." Combined 
-with a logic of practical reason, an implementation of the FUL can move from evaluating a maxim to 
-evaluating an agent's behavior, since that's when ``acting from duty" starts to matter.%
+$$will \, M \, s \equiv \forall w \, (C \longrightarrow A \, (s)) \, w$$
+
+At all worlds $w$, if the circumstances hold at that world, agent $s$ performs act $A$.
+
+\end{definition}
+
+If I will the example maxim above about falsely promising to pay a loan, then whenever I need cash, 
+I will falsely promise to repay a loan. I can represent this definition using the following Isabelle
+formula.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \ will\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim\ {\isasymRightarrow}\ s{\isasymRightarrow}\ \ t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}W\ {\isacharunderscore}\ {\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}will\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isachardot}\ {\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}a\ s{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}will\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isachardot}\ {\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}a\ s{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{An agent $s$ wills a maxim iff in the circumstances, $s$ performs the action, or $s$ substituted
+into the open sentence $a$ is true. This is an Isabelle \texttt{abbreviation}, which is syntactic
+sugar for an Isabelle formula. The type of this formula is $maxim \rightarrow s \rightarrow t$, so it 
+takes as input a maxim and a subject and returns the term, ``s wills maxim.''%
+}%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsubsection{Practical Contradiction Interpretation \label{praccon}%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
 \begin{isamarkuptext}%
-Korsgaard claims that ``to will an end, rather than just
-wishing for it or wanting it, is to set yourself to be its cause" \cite[38]{sources}. To will a maxim
-is to set yourself to be the cause of its goal by taking the means 
-specified in the maxim in the relevant circumstances. This coheres with 
-Kitcher's and Korsgaard's understanding of a maxim as a principle or rule to live by.
+In order to actually evaluate the moral status of a maxim, I must precise the idea of failing
+the universalizability test or a non-universalizable maxim.  Kantians debate the correct interpretation of 
+the Formula of Universal Law because Kant himself appears to interpret the criterion in different ways. 
+My project uses Korsgaard's practical contradiction interpretation, broadly accepted as correct within 
+the philosophical community \citep{ebelsduggan}.
 
-At worlds
-where the circumstances do not hold, a maxim is vacuously willed. If you decide to act on the rule ``I will 
-do X in these cirumstances", then you are vacuously obeying it when the circumstances don't hold.
+Recall that the Formula of Universal Law is to “act only in accordance with that maxim through which 
+you can at the same time will that it become a universal law” \citep{groundwork}. To determine if a 
+maxim can be willed as a universal law, we can use the “universalizability test”, which requires 
+imagining a world in which everyone has willed the maxim. If willing the maxim in such a world 
+generates a contradiction, then the action is prohibited.
 
-The above discussion implies that willing a maxim is particular to the agent, justifying my choice to 
-require that a particular subject will a maxim. O'Neill argues for this interpretation when she distinguishes 
-between the evaluation of a principle, which is generic, and a maxim, which she views as ``individuated only 
-by referring to a person"\cite[13]{actingonprinciple}. I adopt the spirit of this interpretation but modify it slightly 
-by representing the general maxim as a principle that anyone could adopt, and the act of willing the maxim 
-as a person-particular instantiation of the maxim.
+One interpretation of the FUL, the logical contradiction interpretation, prohibits maxims that are 
+logically impossible when universalized. Under this view, falsely promising to repay a loan fails the 
+universalizability test because, in the universalized world, the practice of promising would die out, 
+so making a false promise would be impossible.
 
-I additionally represent a subject as willing a maxim because I use the word `will' as a verb, to mean committing oneself to living by
-the principle of a maxim. This coheres with the FUL, which tests the act willing 
-of a maxim by determining if the maxim could be a universal law that everyone committed to. Formalizing this idea,
-the type of a willed maxim is a term, allowing me
-to use DDL's obligation operator on the notion of willing a maxim. Concretely, my system will prove 
-or disprove statements of the form ``Lavanya is obligated to will the maxim M."
+One problem with this view is that it cannot handle natural acts. Korsgaard appeals to 
+\citet{dietrichson} to construct the example natural act of a mother killing her children that tend to 
+cry at night so that she can get some sleep. Universalizing this maxim does not generate a logical 
+contradiction, but it is clearly wrong. Because killing is a natural act, it can never be logically 
+impossible so the logical contradiction view cannot prohibit it.
 
-Worlds where the circumstances do not hold are not relevant for determining obligation. Recall that in 
-Benzmueller et. al's definition of the obligation operator,  $O \{B|A\}$ is true at all worlds iff ob(B)(A), or 
-if the obligation function maps A to obligatory in context B (where the context is a set of worlds) \cite{BFP}. This 
-definition implies that worlds outside of B have no bearing on the moral status of A in context B, which 
-coheres with intuitions about contextual obligation. Thus, the dyadic obligation operator 
-disqualifies worlds where the context does not hold, so the vacuous truth of the will statement in 
-these worlds does not matter.
+As an alternative to the logical contradiction view, Korsgaard endorses the practical contradiction view, 
+which prohibits maxims that are self-defeating, or ineffective, when universalized. By willing a maxim, 
+an agent commits themselves to the maxim's goal, and thus cannot rationally will that this goal be 
+undercut. This interpretation can prohibit natural acts like those of the sleep-deprived mother: in 
+willing the end of sleeping, she is implicitly willing that she is alive. If all mothers kill all 
+loud children, then she cannot be secure in the possession of her life, because her own mother would 
+have killed her as an infant. Her willing this maxim thwarts the end that she sought to secure.
 
-Given that the will abbreviation already excludes worlds where the circumstances fail (by rendering 
-the statement vacuously true at them), one may conclude that the dyadic obligation operator is now useless. 
-Using the dyadic obligation operator allows me to take advantage of the power of DDL to represent the bearing 
-that circumstances have on obligation. DDL has powerful axioms expressing the relationship between circumstances 
-and obligation, such as the fact that obligations are monotonically increasing with respect to broader 
-circumstances. Using the monadic obligation operator would require me to either operate with an empty 
-notion of context or to redefine these axioms. The dyadic obligation operator lets me take advantage of the full 
-power of DDL in expressing contrary-to-duty obligations. This is particularly important for Kantian ethics 
-and the FUL specifically because many critiques of the FUL rely on attention to circumstances (tailoring 
-objection) or lack thereof (ideal theory). This is also an innovation that my custom formalization presents 
-over the prior work. By formally including the notion of a circumstance or context, I am able to represent 
-these objections that Kantian scholars study. Formalizing Kantian ethics in a dyadic deontic logic 
-instead of a monadic deontic logic is a key contribution of this thesis.%
+The practical contradiction interpretation offers a satisfying explanation of \emph{why} certain 
+maxims are immoral. These maxims involve parasitic behavior on social conditions that the agent seeks 
+to benefit from. The false promiser simultaneously wants to abuse the system of promising and benefit 
+from it, and is thus making an exception of themselves. The test formalizes the kinds of objections 
+that the question ``what if everyone did that?'' seeks to draw out.
+
+Using the practical contradiction interpretation, the FUL states, ``If, when universalized, a maxim is 
+not effective, then it is prohibited.'' This requires defining effectiveness and universalization. 
+If an agent wills an effective maxim, then the maxim's goal is achieved, and if the agent does 
+not will it, then the goal is not achieved.
+
+\begin{definition}[Effective Maxim]
+For a maxim $M = (C, A, G)$ and actor $s$,
+
+$$\text{\emph{effective}} \, M \, s \equiv \forall w \, (\text{\emph{will}} \, (C, A, G) \, s \iff G) \, w$$
+
+\end{definition}
+
+I can implement this in Isabelle using another abbreviation.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \ \ \isakeyword{where}\ {\isachardoublequoteopen}effective\ \ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isachardot}\ {\isacharparenleft}{\isacharparenleft}will\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ \isactrlbold {\isasymequiv}\ g{\isacharparenright}{\isachardoublequoteclose}\isanewline
-\isacommand{print{\isacharunderscore}theorems}\isamarkupfalse%
 %
+\isamarkupcmt{A maxim is effective for a subject if the goal is achieved if and only if the subject wills the maxim.
+Once again, I use an abbreviation to conveniently refer to this Isabelle formula.%
+}%
 \begin{isamarkuptext}%
-A maxim is effective for a subject when, if the subject wills it then the goal is achieved, and
-when the subject does not act on it, the goal is not achieved$\footnote{Thank you to Jeremy D. Zucker for helping me think through this.}$ \cite{sepcausation}. 
-The former direction of the implication 
-is intuitive: if the act results in the goal, it was effective in causing the goal. This represents `necessary'
-causality.
-
-The latter direction represents `sufficient' causality, or the idea that, counterfactually,
-if the maxim were not willed, then the goal is not achieved \cite{lewiscausality}. Note that nothing else changes about this
+The former direction of the implication is intuitive: if the act results in the goal, it was 
+effective in causing the goal. This represents sufficient causality. The latter direction represents 
+necessary causality, or the idea that, counterfactually, if the maxim were not willed, then the goal 
+would not be achieved \citep{lewiscausality}.\footnote{Thank you for Jeremy Zucker for helping me 
+think about causality in this way.}  Note that nothing else changes about this
 counterfactual world—the circumstances are identical and we neither added additional theorems nor 
 specified the model any further. This represents Lewis's idea of "comparative similarity,"  where 
-a counterfactual is true if it holds at the most similar world \cite{lewiscounterfactuals}. In our case, this is just the world 
-where everything is the same except the maxim is not acted on.
-
+a counterfactual is true if it holds at the most similar world \cite{lewiscounterfactuals}. 
+In our case, this is just the world where everything is the same except the maxim is not acted on.
 Combining these ideas, this definition of effective states that a maxim is effective if the 
-maxim being acted on by a subject is the necessary and sufficient cause of the goal.\footnote{Should I wave a hand at critiques of counterfactual causality?}
-
-If the circumstances do not hold and the goal is achieved, then the maxim is vacuously effective, since 
-it is vacuously willed (as described above). While this scenario is counterintuitive, it is not very 
-interesting for my purposes because, when the circumstances do not hold, a maxim is not applicable. It 
-doesn't really make sense to evaluate a maxim when it's not supposed to be applied. The maxim ``When on Jupiter,
-read a book to one-up your nemesis" is vacuously effective because it can never be disproven.%
+maxim being acted on by a subject is the necessary and sufficient cause of the goal.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \endinput
-%:%file=~/Desktop/cs91r/paper/paper41.thy%:%
+%:%file=~/Desktop/cs91r/paper/thesis_3_implementation.thy%:%
 %:%24=6%:%
@@
 %:%37=9%:%
-%:%46=11%:%
-%:%58=13%:%
-%:%59=14%:%
-%:%60=15%:%
-%:%61=16%:%
+%:%38=10%:%
+%:%39=11%:%
+%:%40=12%:%
+%:%41=13%:%
+%:%50=15%:%
 %:%62=17%:%
 %:%63=18%:%
+%:%64=19%:%
 %:%65=20%:%
-%:%66=20%:%
-%:%67=20%:%
-%:%68=21%:%
-%:%69=22%:%
-%:%70=23%:%
-%:%71=23%:%
-%:%72=24%:%
-%:%73=25%:%
-%:%74=25%:%
-%:%75=25%:%
-%:%76=26%:%
-%:%77=26%:%
-%:%78=27%:%
-%:%79=28%:%
-%:%80=28%:%
-%:%82=30%:%
-%:%83=31%:%
-%:%84=32%:%
-%:%85=33%:%
-%:%86=34%:%
-%:%87=35%:%
-%:%88=36%:%
-%:%89=37%:%
-%:%90=38%:%
-%:%91=39%:%
-%:%92=40%:%
-%:%93=41%:%
-%:%94=42%:%
-%:%95=43%:%
-%:%96=44%:%
-%:%97=45%:%
-%:%98=46%:%
-%:%99=47%:%
-%:%100=48%:%
-%:%101=49%:%
-%:%102=50%:%
-%:%103=51%:%
-%:%104=52%:%
-%:%105=53%:%
-%:%106=54%:%
-%:%107=55%:%
-%:%108=56%:%
-%:%109=57%:%
-%:%110=58%:%
-%:%111=59%:%
-%:%112=60%:%
-%:%113=61%:%
-%:%114=62%:%
-%:%115=63%:%
-%:%116=64%:%
-%:%117=65%:%
-%:%118=66%:%
-%:%119=67%:%
-%:%120=68%:%
-%:%121=69%:%
-%:%122=70%:%
-%:%123=71%:%
-%:%124=72%:%
-%:%125=73%:%
-%:%126=74%:%
-%:%127=75%:%
-%:%128=76%:%
-%:%129=77%:%
-%:%130=78%:%
-%:%131=79%:%
-%:%132=80%:%
-%:%133=81%:%
-%:%134=82%:%
-%:%135=83%:%
-%:%136=84%:%
-%:%137=85%:%
-%:%138=86%:%
-%:%139=87%:%
-%:%140=88%:%
-%:%141=89%:%
-%:%142=90%:%
-%:%143=91%:%
-%:%144=92%:%
-%:%145=93%:%
-%:%146=94%:%
-%:%147=95%:%
-%:%148=96%:%
-%:%149=97%:%
-%:%150=98%:%
-%:%151=99%:%
-%:%152=100%:%
-%:%153=101%:%
-%:%154=102%:%
-%:%155=103%:%
-%:%156=104%:%
-%:%157=105%:%
-%:%158=106%:%
-%:%159=107%:%
-%:%160=108%:%
-%:%161=109%:%
-%:%162=110%:%
-%:%163=111%:%
-%:%164=112%:%
-%:%165=113%:%
-%:%166=114%:%
-%:%167=115%:%
-%:%168=116%:%
-%:%169=117%:%
-%:%170=118%:%
-%:%171=119%:%
-%:%172=120%:%
-%:%173=121%:%
-%:%174=122%:%
-%:%175=123%:%
-%:%176=124%:%
-%:%177=125%:%
-%:%178=126%:%
-%:%179=127%:%
-%:%180=128%:%
-%:%181=129%:%
-%:%182=130%:%
-%:%183=131%:%
-%:%184=132%:%
-%:%186=134%:%
-%:%187=134%:%
-%:%188=135%:%
-%:%190=137%:%
-%:%191=138%:%
-%:%192=139%:%
-%:%193=140%:%
-%:%194=141%:%
-%:%195=142%:%
-%:%196=143%:%
-%:%197=144%:%
-%:%198=145%:%
-%:%199=146%:%
-%:%200=147%:%
-%:%201=148%:%
-%:%202=149%:%
-%:%203=150%:%
-%:%204=151%:%
-%:%205=152%:%
-%:%206=153%:%
-%:%207=154%:%
-%:%208=155%:%
-%:%209=156%:%
-%:%210=157%:%
-%:%211=158%:%
-%:%212=159%:%
-%:%213=160%:%
-%:%214=161%:%
-%:%215=162%:%
-%:%216=163%:%
-%:%217=164%:%
-%:%218=165%:%
-%:%219=166%:%
-%:%220=167%:%
-%:%221=168%:%
-%:%222=169%:%
-%:%223=170%:%
-%:%224=171%:%
-%:%225=172%:%
-%:%226=173%:%
-%:%227=174%:%
-%:%228=175%:%
-%:%229=176%:%
-%:%230=177%:%
-%:%231=178%:%
-%:%232=179%:%
-%:%233=180%:%
-%:%234=181%:%
-%:%236=184%:%
-%:%237=184%:%
-%:%238=185%:%
-%:%239=186%:%
-%:%242=188%:%
-%:%243=189%:%
-%:%244=190%:%
-%:%245=191%:%
-%:%246=192%:%
-%:%247=193%:%
-%:%248=194%:%
-%:%249=195%:%
-%:%250=196%:%
-%:%251=197%:%
-%:%252=198%:%
-%:%253=199%:%
-%:%254=200%:%
-%:%255=201%:%
-%:%256=202%:%
-%:%257=203%:%
-%:%258=204%:%
-%:%259=205%:%
-%:%260=206%:%
-%:%261=207%:%
-%:%262=208%:%
-%:%264=210%:%
-%:%265=210%:%
-%:%266=211%:%
-%:%267=212%:%
-%:%268=213%:%
-%:%269=213%:%
-%:%270=214%:%
-%:%271=215%:%
-%:%272=216%:%
-%:%273=216%:%
-%:%274=217%:%
-%:%276=218%:%
-%:%277=219%:%
-%:%278=220%:%
-%:%279=221%:%
-%:%280=222%:%
-%:%281=223%:%
-%:%282=224%:%
-%:%283=225%:%
-%:%286=227%:%
-%:%287=228%:%
-%:%288=229%:%
-%:%289=230%:%
-%:%290=231%:%
-%:%291=232%:%
-%:%292=233%:%
-%:%293=234%:%
-%:%295=236%:%
-%:%296=236%:%
-%:%297=237%:%
-%:%298=238%:%
-%:%299=239%:%
-%:%300=239%:%
-%:%301=240%:%
-%:%303=241%:%
-%:%304=242%:%
-%:%307=245%:%
-%:%308=246%:%
-%:%309=247%:%
-%:%310=248%:%
-%:%312=250%:%
-%:%313=250%:%
-%:%314=251%:%
-%:%316=252%:%
-%:%317=253%:%
-%:%318=253%:%
-%:%319=254%:%
-%:%320=255%:%
-%:%321=255%:%
-%:%323=256%:%
-%:%324=257%:%
-%:%325=258%:%
-%:%333=260%:%
-%:%345=262%:%
-%:%346=263%:%
-%:%347=264%:%
-%:%348=265%:%
-%:%349=266%:%
-%:%350=267%:%
-%:%352=270%:%
-%:%353=270%:%
-%:%355=271%:%
-%:%356=272%:%
-%:%357=273%:%
-%:%358=274%:%
-%:%359=274%:%
-%:%360=275%:%
-%:%361=276%:%
-%:%362=276%:%
-%:%364=276%:%
-%:%368=276%:%
-%:%369=276%:%
-%:%370=277%:%
-%:%371=277%:%
-%:%372=277%:%
-%:%381=279%:%
-%:%382=280%:%
-%:%383=281%:%
-%:%384=282%:%
-%:%385=283%:%
-%:%386=284%:%
-%:%387=285%:%
-%:%388=286%:%
-%:%389=287%:%
-%:%390=288%:%
-%:%391=289%:%
-%:%392=290%:%
-%:%393=291%:%
-%:%394=292%:%
-%:%395=293%:%
-%:%396=294%:%
-%:%397=295%:%
-%:%399=297%:%
-%:%400=297%:%
-%:%401=298%:%
-%:%403=299%:%
-%:%404=300%:%
-%:%405=300%:%
-%:%406=301%:%
-%:%407=302%:%
-%:%408=302%:%
-%:%409=303%:%
-%:%411=304%:%
-%:%412=305%:%
-%:%413=305%:%
-%:%414=306%:%
-%:%415=307%:%
-%:%416=307%:%
-%:%417=308%:%
-%:%418=308%:%
-%:%420=308%:%
-%:%424=308%:%
-%:%425=308%:%
-%:%427=309%:%
-%:%428=310%:%
-%:%429=311%:%
-%:%430=312%:%
-%:%431=313%:%
-%:%432=314%:%
-%:%433=315%:%
-%:%434=316%:%
-%:%435=317%:%
-%:%436=318%:%
-%:%437=319%:%
-%:%445=319%:%
-%:%446=320%:%
-%:%447=321%:%
-%:%448=321%:%
-%:%449=322%:%
-%:%450=323%:%
-%:%451=323%:%
-%:%452=324%:%
-%:%453=324%:%
-%:%455=324%:%
-%:%459=324%:%
-%:%460=324%:%
-%:%462=325%:%
-%:%463=326%:%
-%:%464=327%:%
-%:%465=328%:%
-%:%466=329%:%
-%:%467=330%:%
-%:%477=332%:%
-%:%478=333%:%
-%:%479=334%:%
-%:%480=335%:%
-%:%481=336%:%
-%:%482=337%:%
-%:%483=338%:%
-%:%484=339%:%
-%:%485=340%:%
-%:%486=341%:%
-%:%487=342%:%
-%:%488=343%:%
-%:%489=344%:%
-%:%490=345%:%
-%:%491=346%:%
-%:%492=347%:%
-%:%493=348%:%
-%:%494=349%:%
-%:%495=350%:%
-%:%496=351%:%
-%:%500=353%:%
-%:%501=354%:%
-%:%502=355%:%
-%:%503=356%:%
-%:%504=357%:%
-%:%512=359%:%
-%:%520=359%:%
+%:%74=22%:%
+%:%86=24%:%
+%:%87=25%:%
+%:%88=26%:%
+%:%89=27%:%
+%:%90=28%:%
+%:%92=30%:%
+%:%93=30%:%
+%:%94=30%:%
+%:%97=32%:%
+%:%98=33%:%
+%:%99=34%:%
+%:%100=35%:%
+%:%101=36%:%
+%:%102=37%:%
+%:%103=38%:%
+%:%104=39%:%
+%:%105=40%:%
+%:%106=41%:%
+%:%107=42%:%
+%:%108=43%:%
+%:%109=44%:%
+%:%111=46%:%
+%:%112=46%:%
+%:%113=46%:%
+%:%114=47%:%
+%:%115=48%:%
+%:%116=49%:%
+%:%117=50%:%
+%:%118=51%:%
+%:%119=52%:%
+%:%120=53%:%
+%:%128=55%:%
+%:%140=57%:%
+%:%141=58%:%
+%:%142=59%:%
+%:%143=60%:%
+%:%144=61%:%
+%:%145=62%:%
+%:%146=63%:%
+%:%147=64%:%
+%:%148=65%:%
+%:%149=66%:%
+%:%150=67%:%
+%:%151=68%:%
+%:%152=69%:%
+%:%153=70%:%
+%:%154=71%:%
+%:%155=72%:%
+%:%156=73%:%
+%:%157=74%:%
+%:%159=77%:%
+%:%160=77%:%
+%:%162=78%:%
+%:%163=79%:%
+%:%164=80%:%
+%:%165=81%:%
+%:%166=82%:%
+%:%167=83%:%
+%:%168=84%:%
+%:%169=85%:%
+%:%172=87%:%
+%:%173=88%:%
+%:%174=89%:%
+%:%175=90%:%
+%:%176=91%:%
+%:%177=92%:%
+%:%178=93%:%
+%:%179=94%:%
+%:%180=95%:%
+%:%181=96%:%
+%:%182=97%:%
+%:%183=98%:%
+%:%184=99%:%
+%:%185=100%:%
+%:%186=101%:%
+%:%187=102%:%
+%:%188=103%:%
+%:%189=104%:%
+%:%190=105%:%
+%:%191=106%:%
+%:%192=107%:%
+%:%193=108%:%
+%:%194=109%:%
+%:%195=110%:%
+%:%196=111%:%
+%:%197=112%:%
+%:%198=113%:%
+%:%199=114%:%
+%:%200=115%:%
+%:%201=116%:%
+%:%202=117%:%
+%:%203=118%:%
+%:%204=119%:%
+%:%205=120%:%
+%:%206=121%:%
+%:%207=122%:%
+%:%208=123%:%
+%:%209=124%:%
+%:%210=125%:%
+%:%211=126%:%
+%:%212=127%:%
+%:%213=128%:%
+%:%214=129%:%
+%:%215=130%:%
+%:%216=131%:%
+%:%217=132%:%
+%:%218=133%:%
+%:%219=134%:%
+%:%220=135%:%
+%:%221=136%:%
+%:%222=137%:%
+%:%223=138%:%
+%:%224=139%:%
+%:%225=140%:%
+%:%226=141%:%
+%:%227=142%:%
+%:%228=143%:%
+%:%229=144%:%
+%:%230=145%:%
+%:%231=146%:%
+%:%232=147%:%
+%:%234=149%:%
+%:%235=149%:%
+%:%236=150%:%
+%:%238=151%:%
+%:%239=152%:%
+%:%240=153%:%
+%:%241=154%:%
+%:%249=156%:%
+%:%261=158%:%
+%:%262=159%:%
+%:%263=160%:%
+%:%264=161%:%
+%:%265=162%:%
+%:%266=163%:%
+%:%267=164%:%
+%:%268=165%:%
+%:%269=166%:%
+%:%270=167%:%
+%:%271=168%:%
+%:%272=169%:%
+%:%273=170%:%
+%:%274=171%:%
+%:%275=172%:%
+%:%276=173%:%
+%:%277=174%:%
+%:%278=175%:%
+%:%279=176%:%
+%:%280=177%:%
+%:%281=178%:%
+%:%282=179%:%
+%:%283=180%:%
+%:%284=181%:%
+%:%285=182%:%
+%:%286=183%:%
+%:%287=184%:%
+%:%288=185%:%
+%:%289=186%:%
+%:%290=187%:%
+%:%291=188%:%
+%:%292=189%:%
+%:%293=190%:%
+%:%294=191%:%
+%:%295=192%:%
+%:%296=193%:%
+%:%297=194%:%
+%:%298=195%:%
+%:%299=196%:%
+%:%300=197%:%
+%:%301=198%:%
+%:%302=199%:%
+%:%303=200%:%
+%:%304=201%:%
+%:%305=202%:%
+%:%306=203%:%
+%:%307=204%:%
+%:%308=205%:%
+%:%309=206%:%
+%:%310=207%:%
+%:%312=210%:%
+%:%313=210%:%
+%:%314=211%:%
+%:%316=212%:%
+%:%317=213%:%
+%:%320=215%:%
+%:%321=216%:%
+%:%322=217%:%
+%:%323=218%:%
+%:%324=219%:%
+%:%325=220%:%
+%:%326=221%:%
+%:%327=222%:%
+%:%328=223%:%
+%:%329=224%:%
+%:%330=225%:%
+%:%332=227%:%
+%:%333=227%:%
+%:%334=228%:%
+%:%335=229%:%
+%:%336=230%:%
+%:%337=230%:%
+%:%338=231%:%
+%:%339=232%:%
+%:%340=233%:%
+%:%341=233%:%
+%:%342=234%:%
+%:%344=235%:%
+%:%345=236%:%
+%:%346=237%:%
+%:%347=238%:%
+%:%348=239%:%
+%:%349=240%:%
+%:%350=241%:%
+%:%351=242%:%
+%:%354=244%:%
+%:%355=245%:%
+%:%356=246%:%
+%:%357=247%:%
+%:%358=248%:%
+%:%359=249%:%
+%:%360=250%:%
+%:%361=251%:%
+%:%363=253%:%
+%:%364=253%:%
+%:%365=254%:%
+%:%366=255%:%
+%:%367=256%:%
+%:%368=256%:%
+%:%369=257%:%
+%:%371=258%:%
+%:%372=259%:%
+%:%375=262%:%
+%:%376=263%:%
+%:%377=264%:%
+%:%378=265%:%
+%:%380=267%:%
+%:%381=267%:%
+%:%382=268%:%
+%:%384=269%:%
+%:%385=270%:%
+%:%386=270%:%
+%:%387=271%:%
+%:%388=272%:%
+%:%389=272%:%
+%:%391=273%:%
+%:%392=274%:%
+%:%393=275%:%
+%:%401=277%:%
+%:%413=279%:%
+%:%414=280%:%
+%:%415=281%:%
+%:%416=282%:%
+%:%417=283%:%
+%:%418=284%:%
+%:%420=287%:%
+%:%421=287%:%
+%:%423=288%:%
+%:%424=289%:%
+%:%425=290%:%
+%:%426=291%:%
+%:%427=291%:%
+%:%428=292%:%
+%:%429=293%:%
+%:%430=293%:%
+%:%432=293%:%
+%:%436=293%:%
+%:%437=293%:%
+%:%438=294%:%
+%:%439=294%:%
+%:%440=294%:%
+%:%449=296%:%
+%:%450=297%:%
+%:%451=298%:%
+%:%452=299%:%
+%:%453=300%:%
+%:%454=301%:%
+%:%455=302%:%
+%:%456=303%:%
+%:%457=304%:%
+%:%458=305%:%
+%:%459=306%:%
+%:%460=307%:%
+%:%461=308%:%
+%:%462=309%:%
+%:%463=310%:%
+%:%464=311%:%
+%:%465=312%:%
+%:%467=314%:%
+%:%468=314%:%
+%:%469=315%:%
+%:%471=316%:%
+%:%472=317%:%
+%:%473=317%:%
+%:%474=318%:%
+%:%475=319%:%
+%:%476=319%:%
+%:%477=320%:%
+%:%479=321%:%
+%:%480=322%:%
+%:%481=322%:%
+%:%482=323%:%
+%:%483=324%:%
+%:%484=324%:%
+%:%485=325%:%
+%:%486=325%:%
+%:%488=325%:%
+%:%492=325%:%
+%:%493=325%:%
+%:%495=326%:%
+%:%496=327%:%
+%:%497=328%:%
+%:%498=329%:%
+%:%499=330%:%
+%:%500=331%:%
+%:%501=332%:%
+%:%502=333%:%
+%:%503=334%:%
+%:%504=335%:%
+%:%505=336%:%
+%:%513=336%:%
+%:%514=337%:%
+%:%515=338%:%
+%:%516=338%:%
+%:%517=339%:%
+%:%518=340%:%
+%:%519=340%:%
+%:%520=341%:%
+%:%521=341%:%
+%:%523=341%:%
+%:%527=341%:%
+%:%528=341%:%
+%:%530=342%:%
+%:%531=343%:%
+%:%532=344%:%
+%:%533=345%:%
+%:%534=346%:%
+%:%535=347%:%
+%:%545=349%:%
+%:%546=350%:%
+%:%547=351%:%
+%:%548=352%:%
+%:%549=353%:%
+%:%550=354%:%
+%:%551=355%:%
+%:%552=356%:%
+%:%553=357%:%
+%:%554=358%:%
+%:%555=359%:%
+%:%556=360%:%
+%:%557=361%:%
+%:%558=362%:%
+%:%559=363%:%
+%:%560=364%:%
+%:%561=365%:%
+%:%562=366%:%
+%:%563=367%:%
+%:%564=368%:%
+%:%568=370%:%
+%:%569=371%:%
+%:%570=372%:%
+%:%571=373%:%
+%:%572=374%:%
+%:%580=376%:%
+%:%588=376%:%

### 2022-02-13 paper/output/document/appendix.tex
rough chapter 3, now i just need to cleangit add .git add .git add . which i will do in 10 minute intervals between classes

@@
 \begin{isamarkuptext}%
-$\emph{Exclusion of Motive}$
-
 Kitcher begins with O'Niell's circumstance, act, goal view and expands it to include the motive 
@@
 %
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsection{Kroy's Formalization\label{kroydetails}%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
+This section contains a formalization of the categorical imperative introduced by Moshe Kroy in 
+1976 \citep{kroy}. Kroy used Hinktikka's deontic logic to formalize the Formula of Universal Law and
+the Formula of Humanity. I will first import the additional logical tools that Hintikka's logic contains 
+that Kroy relies on, then examine the differences between his logic and DDL, and finally implement 
+and test both of Kroy's formalizations.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsubsection{Logical Background \label{sec:kroy_logical_background}%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
+Kroy's logic relies heavily on some notion of identity or agency. The logic must be capable of 
+expressing statements like ``x does action", which I can write as ``x is the subject of the sentence
+ `does action.'" This requires defining a subject.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{typedecl}\isamarkupfalse%
+\ s\ %
+\isamarkupcmt{s is the type for a ``subject," i.e. the subject of a sentence%
+}%
+\begin{isamarkuptext}%
+Kroy also defines a substitution operator\footnote{See page 196 in Kroy's original paper \cite{kroy}.}. $P (d/e)$ is read in his logic as ``P with e substituted 
+for d." DDL has no such notion of substitution, so I will define a more generalized notion of an ``open 
+sentence." An open sentence takes as input a subject and returns a complete or ``closed" DDL formula by, 
+in effect, binding the free variable in the sentence to the input. For example, 
+``does action" is an open sentence that can be instantiated with a subject.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
+\ os\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}s\ {\isasymRightarrow}\ t{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{``P sub (d/e)" can be written as ``S(e)", where S(d) = P%
+}\isanewline
+%
+\isamarkupcmt{The terms that we substitute into are actually instantiations of an open sentence, and substitution 
+just requires re-instantiating the open sentence with a different subject.%
+}%
+\begin{isamarkuptext}%
+\textbf{New Operators}
+
+Because Isabelle is strongly typed, we need to define new operators to handle open sentences. These operators 
+are similar to DDL's original operators. We could probably do without these abbreviations, but they will 
+simplify the notation and make it look more similar to Kroy's original paper.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{abbreviation}\isamarkupfalse%
+\ os{\isacharunderscore}neg{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}os\ {\isasymRightarrow}\ os{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlemph {\isasymnot}{\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharparenleft}\isactrlemph {\isasymnot}A{\isacharparenright}\ {\isasymequiv}\ {\isasymlambda}x{\isachardot}\ \isactrlbold {\isasymnot}{\isacharparenleft}A{\isacharparenleft}x{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ os{\isacharunderscore}and{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}os\ {\isasymRightarrow}\ os\ {\isasymRightarrow}\ os{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharunderscore}\isactrlemph {\isasymand}{\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharparenleft}A\ \isactrlemph {\isasymand}\ B{\isacharparenright}\ {\isasymequiv}\ {\isasymlambda}x{\isachardot}\ {\isacharparenleft}{\isacharparenleft}A{\isacharparenleft}x{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}B{\isacharparenleft}x{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ os{\isacharunderscore}or{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}os\ {\isasymRightarrow}\ os\ {\isasymRightarrow}\ os{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharunderscore}\isactrlemph {\isasymor}{\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharparenleft}A\ \isactrlemph {\isasymor}\ B{\isacharparenright}\ {\isasymequiv}\ {\isasymlambda}x{\isachardot}\ {\isacharparenleft}{\isacharparenleft}A{\isacharparenleft}x{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymor}\ {\isacharparenleft}B{\isacharparenleft}x{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ os{\isacharunderscore}ob{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}os\ {\isasymRightarrow}\ os{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlemph O{\isacharbraceleft}{\isacharunderscore}{\isacharbraceright}{\isachardoublequoteclose}{\isacharparenright}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlemph O{\isacharbraceleft}A{\isacharbraceright}\ {\isasymequiv}\ {\isasymlambda}x{\isachardot}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharparenleft}x{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}%
+\begin{isamarkuptext}%
+Once again, the notion of permissibility will be useful here. Recall that an action can either be 
+obligated, permissible, or prohibited. A permissible action is acceptable (there is no specific prohibition 
+against it), but not required (there is no specific obligation requiring it).%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{abbreviation}\isamarkupfalse%
+\ ddl{\isacharunderscore}permissible{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isasymRightarrow}t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}P\ {\isacharbraceleft}{\isacharunderscore}{\isacharbraceright}{\isachardoublequoteclose}{\isacharparenright}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}P\ {\isacharbraceleft}A{\isacharbraceright}\ {\isasymequiv}\ \isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ os{\isacharunderscore}permissible{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}os{\isasymRightarrow}os{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlemph P\ {\isacharbraceleft}{\isacharunderscore}{\isacharbraceright}{\isachardoublequoteclose}{\isacharparenright}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlemph P\ {\isacharbraceleft}A{\isacharbraceright}\ {\isasymequiv}\ {\isasymlambda}x{\isachardot}\ P\ {\isacharbraceleft}A{\isacharparenleft}x{\isacharparenright}{\isacharbraceright}{\isachardoublequoteclose}%
+\textbf{Differences Between Kroy's Logic (Kr) and DDL}
+%
+\begin{isamarkuptext}%
+There is potential for complication because Kroy's original paper uses a different logic than DDL. 
+His custom logic is a slight modification of Hintikka's deontic logic \cite{hintikka}. In this section, 
+I will determine if some of the semantic properties that Kroy's logic (which I will now call Kr) requires 
+hold in DDL. These differences may become important later and can explain differences in my results and 
+Kroy's.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\emph{Deontic alternatives versus the neighborhood semantics}
+%
+\begin{isamarkuptext}%
+The most faithful interpretation of Kr is that if $A$ is permissible in a context, then 
+it must be true at some world in that context. Kr operates under the ``deontic alternatives" or Kripke semantics, 
+summarized by Solt \cite{solt} as follows: ``A proposition of the sort $O A$ is true at the actual world $w$ if and
+only if $A$ is true at every deontic alternative world to $w$." Under this view, permissible propositions
+are obligated at some deontic alternatives, or other worlds in the system, but not at all of them. Let's 
+see if this holds in DDL.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ permissible{\isacharunderscore}semantics{\isacharcolon}\isanewline
+\ \ \isakeyword{fixes}\ A\ w\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}P\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}\ w\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymexists}x{\isachardot}\ A{\isacharparenleft}x{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{\color{blue} Nitpick found a counterexample for card i = 1:
+
+  Free variable:
+    A = ($\lambda x. \_$)($i_1$ := False) \color{black}%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+Remember that DDL uses neighborhood semantics, not the deontic alternatives view, which is why this
+ proposition fails in DDL. In DDL, the $ob$ function abstracts away the notion of
+ deontic alternatives. Even if one believes that permissible 
+statements should be true at some deontic alternative, it's not clear that permissible statements
+ must be realized at some world. In some ways, this also coheres with our understanding of obligation. There 
+are permissible actions like ``Lavanya buys a red folder" that might not happen in any universe.
+
+An even stricter version of the semantics that Kr requires is that if something is permissible at a world, 
+then it is obligatory at some world. This is a straightforward application of the Kripke semantics. Let's
+test this proposition.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ permissible{\isacharunderscore}semantics{\isacharunderscore}strong{\isacharcolon}\isanewline
+\ \ \isakeyword{fixes}\ A\ w\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}P\ {\isacharbraceleft}A{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymexists}x{\isachardot}\ O\ {\isacharbraceleft}A{\isacharbraceright}\ x{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{\color{blue} Nitpick found a counterexample for card i = 1:
+
+  Free variable:
+    A = ($\lambda x. \_$)($i_1$ := False) \color{black}%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+This also doesn't hold in DDL because DDL uses neighborhood semantics instead of the deontic 
+alternatives or Kripke semantics. This also seems to cohere with our moral intuitions. The statement 
+``Lavanya buys a red folder" is permissible in the current world, but it's hard to see why it would 
+be oblgiatory in any world.
+
+One implication of the Kripke semantics is that Kr disallows ``vacuously permissible statements." In 
+other words, if something is permissible it has to be obligated at some deontically perfect alternative. 
+If we translate this to the language of DDL, we expect that if $A$ is permissible, it is obligated in some 
+context.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ permissible{\isacharunderscore}semantic{\isacharunderscore}vacuous{\isacharcolon}\isanewline
+\ \ \isakeyword{fixes}\ A\ w\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}P\ {\isacharbraceleft}A{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymexists}x{\isachardot}\ ob{\isacharparenleft}x{\isacharparenright}{\isacharparenleft}A{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{\color{blue} Nitpick found a counterexample for card i = 1:
+
+  Free variable:
+    A = ($\lambda x. \_$)($i_1$ := False) \color{black}%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+In order to make this true, we'd have to require that everything is either obligatory or
+prohibited somewhere. Sadly, that breaks everything and destroys the 
+notion of permissibility everywhere \footnote{See Appendix for an examination of a buggy version of DDL that led to this insight.}. 
+If something breaks later in this section, it may be because of vacuous permissibility.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\emph{Obligatory statements should be permissible}
+%
+\begin{isamarkuptext}%
+Kr includes the intuitively appealing theorem that if a statement is obligated at a world, then it 
+is permissible at that world\footnote{This follows straightforwardly from the Kripke semantics. If proposition $A$ is 
+obligated at world $w$, this means that at all of $w$'s neighbors, $O A$ holds. Therefore, 
+$\exists w'$ such that $w$ sees $w'$ and $O A$ holds at $w'$ so $A$ is permissible at $w$.}. Let's see 
+if that also holds in DDL.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ ob{\isacharunderscore}implies{\isacharunderscore}perm{\isacharcolon}\isanewline
+\ \ \isakeyword{fixes}\ A\ w\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}O\ {\isacharbraceleft}A{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ P\ {\isacharbraceleft}A{\isacharbraceright}\ w{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{\color{blue} Nitpick found a counterexample for card i = 2:
+
+  Free variable:
+    A = ($\lambda x. \_$)($i_1$ := False, $i_2$ := True)\color{black}%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+Intuitively, it seems untenable for any ethical theory to not include this principle. My 
+formalization should add this as an axiom.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsubsection{The Categorical Imperative \label{sec: kroy_ful}%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
+I will now implement Kroy's formalization of the Formula of Universal Law. Recall that the FUL says
+``act only in accordance with that maxim which you can at the same time will a universal law" \cite{groundwork}.
+Kroy interprets this to mean that if an action is permissible for a specific agent, then it must be permissible for everyone.
+This formalizes the moral intuition prohibiting free-riding. According to the categorical imperative, no one is a moral exception.
+Formalizing this interpretation requires using open sentences to handle the notion of substitution.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{abbreviation}\isamarkupfalse%
+\ FUL{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}FUL\ {\isasymequiv}\ {\isasymforall}w\ A{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isasymexists}p{\isacharcolon}{\isacharcolon}s{\isachardot}\ {\isacharparenleft}{\isacharparenleft}P\ {\isacharbraceleft}A\ p{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}\ \ {\isasymlongrightarrow}{\isacharparenleft}\ {\isacharparenleft}{\isasymforall}p{\isachardot}{\isacharparenleft}\ P\ {\isacharbraceleft}A\ p{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isacharparenright}\ {\isachardoublequoteclose}\isanewline
+\isanewline
+%
+\isamarkupcmt{In English, this statement roughly means that, if action $A$ is 
+permissible for some person $p$, then, for any person $p$, action $A$ must be permissible. The notion of ``permissible $for$" 
+is captured by the substitution of $x$ for $p$.%
+}%
+\begin{isamarkuptext}%
+Let's check if this is already an axiom of DDL. If so, then the formalization is trivial.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ FUL{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ FUL\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{\color{blue} Nitpick found a counterexample for card s = 2 and card i = 2:
+
+  Skolem constants:
+    A = ($\lambda x. \_$)($s_1$ := ($\lambda x. \_$)($i_1$ := True, $i_2$ := True), $s_2$ := ($\lambda x. \_$)($i_1$ := False, $i_2$ := False))
+    p = $s_1$
+    x = $s_2$\color{black}%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+This formalization doesn't hold in DDL, so adding it as an axiom will change the logic.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{axiomatization}\isamarkupfalse%
+\ \isakeyword{where}\ FUL{\isacharcolon}\ FUL%
+\begin{isamarkuptext}%
+Consistency check: is the logic still consistent with the FUL added as an axiom?%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ True\ \isacommand{nitpick}\isamarkupfalse%
+{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ satisfy{\isacharcomma}\ card{\isacharequal}{\isadigit{1}}{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{\color{blue} Nitpicking formula... 
+Nitpick found a model for card i = 1:
+
+  Empty assignment\color{black}%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+This completes my implementation of Kroy's formalization of the first formulation of the 
+categorical imperative. I defined new logical constructs to handle Kroy's logic, studied the differences
+between DDL and Kr, implemented Kroy's formalization of the Formula of Universal Law, and showed 
+that it is both non-trivial and consistent. Now it's time to start testing!%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsubsection{Application Tests\label{sec:app_tests_kroy}%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
+In the following sections, I will use the application and metaethical tests presenting in Sections \ref{sec:app_tests_naive} and \ref{sec:meta_tests_naive}
+        to tease out the strengths and weaknesses of Kroy's formalization. While the formalization is considerably
+        stronger than the naive formalization, it still fails many of these tests. Some of these failures 
+        are due to the differences between Kroy's logic and my logic mentioned in Section \ref{sec:kroy_logical_background}, but some 
+        reveal philosophical problems with Kroy's interpretation of what the formula of universal law means. 
+        I will analyze these problems in the context of philosophical scholarship explicating the content 
+        of the formula of universal law. The findings in these sections will inform milestones for my
+        custom formalization of the categorical imperative. They also serve as an example of how formalized
+        and automated ethics can reveal philosophical strengths and weaknesses of an ethical theory.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+\textbf{Murder}%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+In Section \ref{sec:app_tests_naive}, I began by testing the naive interpretation's ability to show that murder 
+is wrong. I started by showing the morally dubious proposition that if murder is possibly wrong, then 
+it is actually wrong.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{consts}\isamarkupfalse%
+\ M{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Let the constant $M$ denote murder. I have defined no features of this constant, except that it is 
+of the type term, which can be true or false at a set of worlds. Indeed, this constant as-is has no 
+semantic meaning and could be replaced with any symbol, like `Q' or `Going to Target.' This constant 
+will begin to take on features of the act of murder when I specify its properties. In the tests below, 
+I specify its properties as the antecedents of lemmas. For example, the test below specifies that 
+it is possible that murder is prohibited at the current world. This pattern will hold for most constants 
+defined in Isabelle—they have no meaning until I program a meaning.%
+}\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ wrong{\isacharunderscore}if{\isacharunderscore}possibly{\isacharunderscore}wrong{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}{\isasymdiamond}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ M{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ cw{\isacharparenright}\ {\isasymlongrightarrow}\ \ {\isacharparenleft}{\isasymforall}w{\isachardot}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ M{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{by}\isamarkupfalse%
+\ simp\isanewline
+%
+\isamarkupcmt{This sentence reads: ``If it is possible that murder is prohibited at world cw, then murder is prohibited 
+at all worlds.%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+This is the same result we got in Section \ref{sec:app_tests_naive}—if murder is possibly wrong at some world, it is wrong at
+every world. The result is incredible strong—the mere possibility of wrongness at some world is sufficient
+to imply prohibition at $\text{every world}$.
+
+Kroy's formalization shouldn't actually imply this property. Recall that this property held in the 
+naive interpretation because it universalized a proposition across worlds (using the necessity operator).
+Kroy, on the other hand, interprets the FUL as universalizing across $\text{people}$, not worlds. 
+In other words, Kroy's formulation implies that if murder is wrong for someone, then it is wrong for 
+everyone.
+
+The fact that this strange lemma holds is actually a property of DDL itself, not a property
+of Kroy's formalization. Indeed, repeating this experiment in DDL, with no
+additional axioms that represent the categorical imperative shows that, in DDL, if something is 
+possibly wrong, it is wrong at every world. This implies that this is not a useful example to test any formulation. 
+If a lemma is true in the base logic, without any custom axioms added, then it will hold for any set of  
+custom axioms. Testing whether or not it holds as we add axioms tells us nothing, since it held in 
+the base logic itself. Interesting cases are ones that fail (or are indeterminate) in the base logic, 
+but become true as we add axioms.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+To adapt the murder wrong axiom to capture the spirit of Kroy's formulation, I will modify if 
+to state that if murder is wrong for one person, it is wrong for everyone.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{consts}\isamarkupfalse%
+\ M{\isacharunderscore}kroy{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}os{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{This time, murder is an open sentence, so that I can substitute in different agents.%
+}\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ wrong{\isacharunderscore}if{\isacharunderscore}wrong{\isacharunderscore}for{\isacharunderscore}someone{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymexists}p{\isachardot}\ {\isasymTurnstile}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}{\isacharparenleft}M{\isacharunderscore}kroy\ p{\isacharparenright}{\isacharbraceright}{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ {\isasymTurnstile}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}{\isacharparenleft}M{\isacharunderscore}kroy\ p{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{proof}\isamarkupfalse%
+\ \isanewline
+\ \ \ \ \isacommand{assume}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymexists}p{\isachardot}\ {\isasymTurnstile}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}{\isacharparenleft}M{\isacharunderscore}kroy\ p{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \ \ \isacommand{show}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymforall}p{\isachardot}\ {\isasymTurnstile}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}{\isacharparenleft}M{\isacharunderscore}kroy\ p{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \ \ \ \ \isacommand{using}\isamarkupfalse%
+\ FUL\ {\isacartoucheopen}{\isasymexists}p{\isachardot}\ {\isasymTurnstile}\isactrlemph O{\isacharbraceleft}\isactrlemph {\isasymnot}M{\isacharunderscore}kroy{\isacharbraceright}\ p{\isacartoucheclose}\ \isacommand{by}\isamarkupfalse%
+\ blast\isanewline
+\ \ \isacommand{qed}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+This lemma gets to the heart of Kroy's formulation of the categorical imperative. If murder is prohibited
+for a specific person $p$, then it must be prohibited for all people\footnote{This test case also revealed a 
+bug in my original implementation of Kroy's formulation of the FUL, demonstrating the power of such 
+automated tests and precise formulations to find bugs in ethical theories.}.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+\textbf{Lying}%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+For the naive implementation, I also tested the stronger proposition that if not 
+everyone can simultaneously lie, then lying is prohibited. This is the equivalent of claiming that 
+if lying fails the universalizability test, it is prohibited.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+I want to represent the sentence``At all worlds, it is 
+      not possible that everyone lies simultaneously." This requires the following two abbreviations.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{consts}\isamarkupfalse%
+\ lie{\isacharcolon}{\isacharcolon}os%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ everyone{\isacharunderscore}lies{\isacharcolon}{\isacharcolon}t\ \isakeyword{where}\ {\isachardoublequoteopen}everyone{\isacharunderscore}lies\ {\isasymequiv}\ {\isasymlambda}w{\isachardot}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ {\isacharparenleft}lie{\isacharparenleft}p{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{This represents the term ``all people lie". Naively, we might think to represent this as $\forall p. lie(p)$.
+In HOL, the $\forall$ operator has type $('a\rightarrow bool) \rightarrow bool$, where $'a$ is a polymorphic
+type of the term being bound by $\forall$. In the given example, 
+$\forall$ has the type $(s \rightarrow bool) \rightarrow bool$, so it can only be applied to a formula 
+of type $s \rightarrow bool$. In the abbreviation above, we're applying the quantifier to a sentence 
+that takes in a given subject $p$ and returns $lie(p) w$ for any arbitrary $w$, so the types cohere.%
+}\isanewline
+%
+\isamarkupcmt{The term above is true for a set of worlds $i$ (recall that a term is true at a set of worlds) 
+such that, at all the worlds $w$ in $i$, all people at $w$ lie.%
+}\isanewline
+\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ lying{\isacharunderscore}not{\isacharunderscore}possibly{\isacharunderscore}universal{\isacharcolon}{\isacharcolon}bool\ \isakeyword{where}\ {\isachardoublequoteopen}lying{\isacharunderscore}not{\isacharunderscore}possibly{\isacharunderscore}universal\ {\isasymequiv}\ {\isasymTurnstile}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}{\isasymdiamond}\ everyone{\isacharunderscore}lies{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Armed with \isa{everyone{\isacharunderscore}lies\ {\isasymequiv}\ {\isasymlambda}w{\isachardot}\ {\isasymforall}p{\isachardot}\ lie\ p\ w}, it's easy to represent the desired sentence.
+The abbreviation above
+reads, ``At all worlds, it is not possible that everyone lies."%
+}%
+\begin{isamarkuptext}%
+Now that I have defined a sentence stating that lying fails the universalizability test, I can 
+      test if this sentence implies that lying is impermissible.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ lying{\isacharunderscore}prohibited{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}lying{\isacharunderscore}not{\isacharunderscore}possibly{\isacharunderscore}universal\ {\isasymlongrightarrow}\ \ {\isacharparenleft}\ {\isasymTurnstile}{\isacharparenleft}\isactrlbold {\isasymnot}\ P\ {\isacharbraceleft}lie{\isacharparenleft}p{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{\color{blue} Nitpick found a counterexample for card i = 1 and card s = 2:
+
+  Free variables:
+
+    $\text{lying\_not\_possibly\_universal}$ = True
+
+    $p = s_1$ \color{black}%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+Kroy's formulation fails this test, and is thus not able to show that if lying is not possible 
+      to universalize, it is prohibited for an arbitrary person. To understand why this is happening, I 
+      will outline the syllogism that I $\emph{expect}$ to prove that lying is prohibited.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{enumerate}
+        \item \text{At all worlds, it is not possible for everyone to lie. (This is the assumed lemma lying\_not\_possibly\_universal)}
+        \item At all worlds, there is necessarily someone who doesn't lie. (Modal dual of (1))
+        \item If A is permissible for subject p at world w, A is possible for subject p at world w. (Modified Ought Implies Can)
+        \item If A is permissible at world w for any person p, it must be possible for everyone to A at w. (FUL and (3)) 
+        \item Lying is impermissible. (Follows from (4) and (1)) \end{enumerate}
+%
+\begin{isamarkuptext}%
+Armed with this syllogism, I can figure out why this test failed.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ step{\isadigit{2}}{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}lying{\isacharunderscore}not{\isacharunderscore}possibly{\isacharunderscore}universal\ {\isasymlongrightarrow}\ {\isasymTurnstile}{\isacharparenleft}\ {\isacharparenleft}{\isasymbox}\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymexists}p{\isachardot}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}lie{\isacharparenleft}p{\isacharparenright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharparenright}\ {\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{by}\isamarkupfalse%
+\ simp\isanewline
+%
+\isamarkupcmt{Step 2 holds.%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+\isanewline
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ step{\isadigit{3}}{\isacharcolon}\ \isanewline
+\ \ \isakeyword{fixes}\ A\ p\ w\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}P\ {\isacharbraceleft}A{\isacharparenleft}p{\isacharparenright}{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharparenleft}A{\isacharparenleft}p{\isacharparenright}{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{$\color{blue}$ Nitpick found a counterexample for card `a = 1, card i = 1, and card s = 1:
+
+  Free variables:
+    A = ($\lambda x. \_$)($a_1$ := ($\lambda x. \_$)($i_1$ := False))
+    p = $a_1$ $\color{black}$%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+As we see above, the syllogism fails at Step 3, explaining why the lemma doesn't 
+        hold as expected. Kroy explicitly states\footnote{See footnote 19 on p. 199} that this lemma holds in his logic.
+
+        The success of this lemma in Kroy's logic and the emptiness of his formalization of the FUL are 
+        two errors that contribute to the failure of this test. First, the statement expressed in Step 3
+        should not actually hold. Impossible actions can be permissible (do I need a citation?). For example, 
+        imagine I make a trip to Target to 
+        purchase a folder, and they offer blue and black folders. No one would claim that it's impermissible
+        for me to purchase a red folder, or, equivalently, that I am obligated to not purchase a red folder.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+The second issue is that Kroy's interpretation of the formula of universal law is circular.
+        His formalization interprets the FUL as prohibiting A if there is someone for whom 
+        $A$'ing is not permissible. This requires some preexisting notion of the permissibility of $A$, and 
+        is thus circuar. The categorical imperative is supposed to be the complete,
+        self-contained rule of morality \cite{groundwork}, but Kroy's version of the FUL prescribes obligations 
+        in a self-referencing manner. The FUL is supposed to define what is permissible and what isn't, 
+        but Kroy defines permissibility in terms of itself.
+
+        Neither of these errors are obvious from Kroy's presentation of his formalization of 
+        the categorical imperative. This example demonstrates the power of formalized ethics. Making
+        Kroy's interpretation of the categorical imperative precise demonstrated a philosophical problem 
+        with that interpretation.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsubsection{Metaethical Tests \label{sec:meta_tests_kroy}%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
+In addition to testing specific applications of the theory, I am also interested in 
+        metaethical properties, as in the naive interpretation. First, I will test if permissiblility
+        is possible under this formalization.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ permissible{\isacharcolon}\isanewline
+\ \ \isakeyword{fixes}\ A\ w\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{\color{blue}Nitpick found a model for card i = 1:
+
+  Free variable:
+    A = ($\lambda x. \_$)($i_1$ := False)\color{black}%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+The above result shows that, for some action $A$ and world $w$, Nitpick can find a model where $A$
+        is permissible at $w$. This means that the logic allows for permissible actions. If I further specify 
+        properties of $A$ (such as `$A$ is murder'), I would want this result to fail.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+Next, I will test if the formalization allows arbitrary obligations.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ arbitrary{\isacharunderscore}obligations{\isacharcolon}\isanewline
+\ \ \isakeyword{fixes}\ A{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}O\ {\isacharbraceleft}A{\isacharbraceright}\ w{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharequal}true{\isacharcomma}\ falsify{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{\color{blue} Nitpick found a counterexample for card i = 1 and card s = 1:
+
+  Free variable:
+    A = ($\lambda x. \_$)($i_1$ := False) \color{blue}%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+This is exactly the expected result. Any arbitrary action $A$ isn't obligated. A slightly 
+        stronger property is ``modal collapse," or whether or not `$A$ happens' implies `$A$ is obligated'.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ modal{\isacharunderscore}collapse{\isacharcolon}\isanewline
+\ \ \isakeyword{fixes}\ A\ w\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}A\ w\ {\isasymlongrightarrow}\ O\ {\isacharbraceleft}A{\isacharbraceright}\ w{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharequal}true{\isacharcomma}\ falsify{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{\color{blue} Nitpick found a counterexample for card i = 1 and card s = 1:
+
+  Free variables:
+    A = ($\lambda x. \_$)($i_1$ := True)
+    w = $i_1$ \color{black}%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+This test also passes. Next, I will test if not ought implies can holds. Recall that I 
+        showed in Section $\ref{sec:meta_tests_naive}$ that ought implies can is a theorem of DDL itself, so it should still hold.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ ought{\isacharunderscore}implies{\isacharunderscore}can{\isacharcolon}\isanewline
+\ \ \isakeyword{fixes}\ A\ w\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}O\ {\isacharbraceleft}A{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ {\isasymdiamond}\ A\ w{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{using}\isamarkupfalse%
+\ O{\isacharunderscore}diamond\ \isacommand{by}\isamarkupfalse%
+\ blast%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+This theorem holds. Now that I have a substitution operation, I also expect that if an action 
+      is obligated for a person, then it is possible for that person. That should follow by the 
+      axiom of substitution \cite{cresswell} which lets me replace the `A' in the formula above with 
+      `A(p)'%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ ought{\isacharunderscore}implies{\isacharunderscore}can{\isacharunderscore}person{\isacharcolon}\isanewline
+\ \ \isakeyword{fixes}\ A\ w\ \isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}O\ {\isacharbraceleft}\ A{\isacharparenleft}p{\isacharparenright}{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ {\isasymdiamond}\ {\isacharparenleft}A\ {\isacharparenleft}p{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{using}\isamarkupfalse%
+\ O{\isacharunderscore}diamond\ \isacommand{by}\isamarkupfalse%
+\ blast%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+This test also passes. Next, I will explore whether or not Kroy's formalization still allows 
+      conflicting obligations.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ conflicting{\isacharunderscore}obligations{\isacharcolon}\isanewline
+\ \ \isakeyword{fixes}\ A\ w\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymand}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{\color{blue} Nitpick found a model for card i = 2 and card s = 1:
+
+  Free variable:
+    A = ($\lambda x. \_$)($i_1$ := False, $i_2$ := True) \color{black}%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+Just as with the naive formalization, Kroy's formalization allows for contradictory obligations. 
+        Testing this lemma in DDL without the FUL shows that this is a property of DDL itself. This is a good goal to have in mind when 
+        developing my custom formalization.
+
+        Next, I will test the stronger property that if two maxims imply a
+        contradiction, they may not be simultaneously willed.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ implied{\isacharunderscore}contradiction{\isacharcolon}\isanewline
+\ \ \isakeyword{fixes}\ A\ B\ w\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}A\ \isactrlbold {\isasymand}\ B{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbottom}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymand}\ O\ {\isacharbraceleft}B{\isacharbraceright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{\color{blue} Nitpick found a counterexample for card i = 2 and card s = 1:
+
+  Free variables:
+    A = ($\lambda x. \_$)($i_1$ := True, $i_2$  := False)
+    B = ($\lambda x. \_$)($i_1$  := True, $i_2$  := False)
+    w = $i_2$ \color{black}%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+Just as with the naive formalization, Kroy's formalization allows implied contradictions because 
+        DDL itself allows implied contradictions and Kroy's 
+        formalization doesn't do anything to remedy this.
+
+      Next, I will test that an action is either obligatory, permissible, or 
+      prohibited.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ ob{\isacharunderscore}perm{\isacharunderscore}or{\isacharunderscore}prohibited{\isacharcolon}\isanewline
+\ \ \isakeyword{fixes}\ A\ w\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymor}\ {\isacharparenleft}P\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymor}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{by}\isamarkupfalse%
+\ simp\isanewline
+%
+\isamarkupcmt{This test passes.%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+I also expect obligation to be a strictly stronger property than permissibility. Particularly, 
+if A is obligated, then A should also be permissible.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ obligated{\isacharunderscore}then{\isacharunderscore}permissible{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymrightarrow}\ P\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{This test fails in Kroy's interpretation!
+\color{blue}Nitpick found a counterexample for card i = 2 and card s = 1:
+
+  Free variable:
+    A = ($\lambda x. \_$)($i_1$ := False, $i_2$ := True)\color{black}%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+These tests show that, while Kroy's formalization is more powerful and more coherent than the naive formalization, it 
+      still fails to capture most of the desired properties of the categorical imperative. Some of these 
+      problems may be remedied by the fact that Kroy's logic doesn't allow contradictory obligations, 
+      and that possibility will be interesting to explore in my own formalization.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsubsection{Miscellaneous Tests \label{sec: misc_tests_kroy}%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
+In this section, I explore tests of properties that Kroy presents in his original paper. These 
+tests not only test the features of the system that Kroy intended to highlight, but they may also 
+inspire additional tests and criteria for my own formalization in Chapter 3. These tests further underscore 
+the circularity of Kroy's formalization and the differences between my logic and his.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+First, Kroy presents a stronger version of the formula of universal law and argues that his formalization
+is implied by the stronger version. Let's test that claim.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{abbreviation}\isamarkupfalse%
+\ FUL{\isacharunderscore}strong{\isacharcolon}{\isacharcolon}bool\ \isakeyword{where}\ {\isachardoublequoteopen}FUL{\isacharunderscore}strong\ {\isasymequiv}\ \ {\isasymforall}w\ A{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isasymexists}p{\isacharcolon}{\isacharcolon}s{\isachardot}\ {\isacharparenleft}{\isacharparenleft}P\ {\isacharbraceleft}A\ p{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}\ \ {\isasymlongrightarrow}{\isacharparenleft}\ {\isacharparenleft}{\isacharparenleft}\ P\ {\isacharbraceleft}\ {\isasymlambda}x{\isachardot}\ {\isasymforall}p{\isachardot}\ A\ p\ x{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ strong{\isacharunderscore}implies{\isacharunderscore}weak{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}FUL{\isacharunderscore}Strong\ {\isasymlongrightarrow}\ FUL{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{using}\isamarkupfalse%
+\ FUL\ \isacommand{by}\isamarkupfalse%
+\ blast\isanewline
+%
+\isamarkupcmt{This lemma holds, showing that Kroy is correct in stating that this version of the FUL is stronger than his original
+   version.%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+The difference between the stronger version and \isa{FUL\ {\isasymequiv}\ {\isasymforall}w\ A{\isachardot}\ {\isacharparenleft}{\isasymexists}p{\isachardot}\ P\ {\isacharbraceleft}A\ p{\isacharbraceright}\ w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ P\ {\isacharbraceleft}A\ p{\isacharbraceright}\ w{\isacharparenright}} is subtle.
+The consequent of FUL is ``for all people $p$,
+it is permissible that they $A$." The consequent of this stronger statement is ``it is permissible that 
+everyone $A$." In particular, this stronger statement requires that it is permissible for everyone to
+ $A$ simultaneously. Kroy immediately rejects this version of the categorical imperative, arguing that 
+it's impossible for everyone to be the US president simultaneously, so this version of the FUL prohibits
+running for president.
+
+Most Kantians would disagree with this interpretation. Consider the classical example of lying, as presented 
+in \cite{kemp} and in \cite{KorsgaardFUL}. Lying fails the universalizability test because in a 
+world where everyone lied simultaneously, the practice of lying would break down. If we adopt Kroy's 
+version, lying is only prohibited if, no matter who lies, lying is impermissible. As argued above, this 
+rule circularly relies on some existing prohibition against lying for a particular person, and thus 
+fails to show the wrongness of lying. It is tempting to claim that this issue explains why the tests 
+above failed. To test this hypothesis, I will check if the stronger version 
+of the FUL implies that lying is impermissible.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ strongFUL{\isacharunderscore}implies{\isacharunderscore}lying{\isacharunderscore}is{\isacharunderscore}wrong{\isacharcolon}\isanewline
+\ \ \isakeyword{fixes}\ p\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}FUL{\isacharunderscore}strong\ {\isasymlongrightarrow}\ {\isasymTurnstile}{\isacharparenleft}\isactrlbold {\isasymnot}\ P\ {\isacharbraceleft}lie{\isacharparenleft}p{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{\color{blue}
+Nitpick found a counterexample for card i = 1 and card s = 1:
+
+  Free variable:
+    p = $s_1$
+\color{black}%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+The test above also fails! This means that not even the stronger version of Kroy's formalization
+        of the FUL can show the wrongness of lying. As mentioned earlier, there are two independent errors. The first is the 
+        the assumption that impossible actions are impermissible and the second is the circularity of the 
+        formalization. The stronger FUL addresses the second error, but the first remains.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+Kroy also argues that the FUL gives us recipes for deriving obligations, in addition to deriving
+        permissible actions. Specifically, he presents the following two principles, which are equivalent 
+        in his logic. These sentences parallel FUL and strong FUL.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{abbreviation}\isamarkupfalse%
+\ obligation{\isacharunderscore}universal{\isacharunderscore}weak{\isacharcolon}{\isacharcolon}bool\ \isakeyword{where}\ {\isachardoublequoteopen}obligation{\isacharunderscore}universal{\isacharunderscore}weak\ {\isasymequiv}\ {\isasymforall}w\ A{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isasymexists}p{\isacharcolon}{\isacharcolon}s{\isachardot}\ {\isacharparenleft}{\isacharparenleft}O\ {\isacharbraceleft}A\ p{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}\ \ {\isasymlongrightarrow}{\isacharparenleft}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ {\isacharparenleft}\ O\ {\isacharbraceleft}A\ p\ {\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ obligation{\isacharunderscore}universal{\isacharunderscore}strong{\isacharcolon}{\isacharcolon}bool\ \isakeyword{where}\ {\isachardoublequoteopen}obligation{\isacharunderscore}universal{\isacharunderscore}strong\ {\isasymequiv}\ {\isasymforall}w\ A{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isasymexists}p{\isacharcolon}{\isacharcolon}s{\isachardot}\ {\isacharparenleft}{\isacharparenleft}O\ {\isacharbraceleft}A\ p{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}\ \ {\isasymlongrightarrow}{\isacharparenleft}\ {\isacharparenleft}{\isacharparenleft}\ O\ {\isacharbraceleft}\ {\isasymlambda}x{\isachardot}\ {\isasymforall}p{\isachardot}\ A\ p\ x{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Just as with FUL and FUL strong, the weaker version of the above statement has the consequent, ``For all people, 
+A is obligated." The stronger consequent is ``A is obligated for all people simultaneously."%
+}\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ weak{\isacharunderscore}equiv{\isacharunderscore}strong{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}obligation{\isacharunderscore}universal{\isacharunderscore}weak\ {\isasymequiv}\ obligation{\isacharunderscore}universal{\isacharunderscore}strong{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{Isabelle is neither able to find a proof nor a countermodel for the statement above, so I can't say 
+  if it holds or not without completing a full, manual proof. This aside is not very relevant to 
+  my project, so I will defer such a proof.%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+These two statements are not necessarily equivalent in my logic, but are in Kroy's$\footnote{This follows from
+        the fact that the Barcan formula holds in Kroy's logic but not in mine, as verified with Nitpick. See 
+        Appendix for more.}$ This difference in logics may further explain why tests are not behaving as 
+        they should. Nonetheless, Kroy argues that the FUL implies both statements above.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ FUL{\isacharunderscore}implies{\isacharunderscore}ob{\isacharunderscore}weak{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}FUL\ {\isasymlongrightarrow}\ obligation{\isacharunderscore}universal{\isacharunderscore}weak{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{Isabelle is neither able to find a proof nor a countermodel for this statement.%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ FUL{\isacharunderscore}implies{\isacharunderscore}ob{\isacharunderscore}strong{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}FUL\ {\isasymlongrightarrow}\ obligation{\isacharunderscore}universal{\isacharunderscore}strong{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{Isabelle is neither able to find a proof nor a countermodel for this statement.%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+Isabelle timed out when looking for proofs or countermodels to the statements above. This may be 
+        an indication of a problem that Benzmueller warned me about—mixing quantifiers into a shallow
+        embedding of DDL may be too expensive for Isabelle to handle. Not sure what to do about this.%
+\end{isamarkuptext}\isamarkuptrue%
+%
 \isadelimtheory
@@
 %:%28=7%:%
-%:%40=10%:%
-%:%41=11%:%
-%:%42=12%:%
-%:%43=13%:%
-%:%44=14%:%
-%:%45=15%:%
-%:%46=16%:%
-%:%47=17%:%
-%:%48=18%:%
-%:%49=19%:%
-%:%50=20%:%
-%:%51=21%:%
-%:%52=22%:%
-%:%53=23%:%
-%:%54=24%:%
-%:%55=25%:%
-%:%56=26%:%
-%:%57=27%:%
-%:%58=28%:%
-%:%59=29%:%
-%:%60=30%:%
-%:%61=31%:%
-%:%62=32%:%
-%:%63=33%:%
-%:%64=34%:%
+%:%40=11%:%
+%:%41=12%:%
+%:%42=13%:%
+%:%43=14%:%
+%:%44=15%:%
+%:%45=16%:%
+%:%46=17%:%
+%:%47=18%:%
+%:%48=19%:%
+%:%49=20%:%
+%:%50=21%:%
+%:%51=22%:%
+%:%52=23%:%
+%:%53=24%:%
+%:%54=25%:%
+%:%55=26%:%
+%:%56=27%:%
+%:%57=28%:%
+%:%58=29%:%
+%:%59=30%:%
+%:%60=31%:%
+%:%61=32%:%
+%:%62=33%:%
+%:%97=62%:%
+%:%109=64%:%
+%:%110=65%:%
+%:%111=66%:%
+%:%112=67%:%
+%:%113=68%:%
+%:%122=70%:%
+%:%134=72%:%
+%:%135=73%:%
+%:%136=74%:%
+%:%138=76%:%
+%:%139=76%:%
+%:%140=76%:%
+%:%143=78%:%
+%:%144=79%:%
+%:%145=80%:%
+%:%146=81%:%
+%:%147=82%:%
+%:%149=84%:%
+%:%150=84%:%
+%:%152=85%:%
+%:%153=85%:%
+%:%155=86%:%
+%:%156=87%:%
+%:%159=89%:%
+%:%160=90%:%
+%:%161=91%:%
+%:%162=92%:%
+%:%163=93%:%
+%:%165=95%:%
+%:%166=95%:%
+%:%167=96%:%
+%:%168=97%:%
+%:%169=97%:%
+%:%170=98%:%
+%:%171=99%:%
+%:%172=99%:%
+%:%173=100%:%
+%:%174=101%:%
+%:%175=101%:%
+%:%176=102%:%
+%:%178=104%:%
+%:%179=105%:%
+%:%180=106%:%
+%:%182=108%:%
+%:%183=108%:%
+%:%184=109%:%
+%:%185=110%:%
+%:%186=110%:%
+%:%187=111%:%
+%:%188=114%:%
+%:%191=117%:%
+%:%192=118%:%
+%:%193=119%:%
+%:%194=120%:%
+%:%195=121%:%
+%:%198=123%:%
+%:%201=125%:%
+%:%202=126%:%
+%:%203=127%:%
+%:%204=128%:%
+%:%205=129%:%
+%:%206=130%:%
+%:%208=132%:%
+%:%209=132%:%
+%:%210=133%:%
+%:%211=134%:%
+%:%212=135%:%
+%:%213=135%:%
+%:%215=135%:%
+%:%219=135%:%
+%:%220=135%:%
+%:%222=136%:%
+%:%223=137%:%
+%:%224=138%:%
+%:%225=139%:%
+%:%235=141%:%
+%:%236=142%:%
+%:%237=143%:%
+%:%238=144%:%
+%:%239=145%:%
+%:%240=146%:%
+%:%241=147%:%
+%:%242=148%:%
+%:%243=149%:%
+%:%244=150%:%
+%:%246=152%:%
+%:%247=152%:%
+%:%248=153%:%
+%:%249=154%:%
+%:%250=155%:%
+%:%251=155%:%
+%:%253=155%:%
+%:%257=155%:%
+%:%258=155%:%
+%:%260=156%:%
+%:%261=157%:%
+%:%262=158%:%
+%:%263=159%:%
+%:%273=162%:%
+%:%274=163%:%
+%:%275=164%:%
+%:%276=165%:%
+%:%277=166%:%
+%:%278=167%:%
+%:%279=168%:%
+%:%280=169%:%
+%:%281=170%:%
+%:%283=173%:%
+%:%284=173%:%
+%:%285=174%:%
+%:%286=175%:%
+%:%287=176%:%
+%:%288=176%:%
+%:%290=176%:%
+%:%294=176%:%
+%:%295=176%:%
+%:%297=177%:%
+%:%298=178%:%
+%:%299=179%:%
+%:%300=180%:%
+%:%310=182%:%
+%:%311=183%:%
+%:%312=184%:%
+%:%313=185%:%
+%:%316=187%:%
+%:%319=189%:%
+%:%320=190%:%
+%:%321=191%:%
+%:%322=192%:%
+%:%323=193%:%
+%:%325=195%:%
+%:%326=195%:%
+%:%327=196%:%
+%:%328=197%:%
+%:%329=198%:%
+%:%330=198%:%
+%:%332=198%:%
+%:%336=198%:%
+%:%337=198%:%
+%:%339=199%:%
+%:%340=200%:%
+%:%341=201%:%
+%:%342=202%:%
+%:%352=204%:%
+%:%353=205%:%
+%:%362=210%:%
+%:%374=212%:%
+%:%375=213%:%
+%:%376=214%:%
+%:%377=215%:%
+%:%378=216%:%
+%:%380=217%:%
+%:%381=217%:%
+%:%382=218%:%
+%:%384=219%:%
+%:%385=220%:%
+%:%386=221%:%
+%:%389=223%:%
+%:%391=225%:%
+%:%392=225%:%
+%:%393=226%:%
+%:%394=227%:%
+%:%395=227%:%
+%:%397=227%:%
+%:%401=227%:%
+%:%402=227%:%
+%:%404=228%:%
+%:%405=229%:%
+%:%406=230%:%
+%:%407=231%:%
+%:%408=232%:%
+%:%409=233%:%
+%:%419=235%:%
+%:%421=237%:%
+%:%422=237%:%
+%:%424=239%:%
+%:%426=241%:%
+%:%427=241%:%
+%:%428=241%:%
+%:%430=241%:%
+%:%434=241%:%
+%:%435=241%:%
+%:%437=242%:%
+%:%438=243%:%
+%:%439=244%:%
+%:%440=245%:%
+%:%450=247%:%
+%:%451=248%:%
+%:%452=249%:%
+%:%453=250%:%
+%:%462=253%:%
+%:%474=255%:%
+%:%475=256%:%
+%:%476=257%:%
+%:%477=258%:%
+%:%478=259%:%
+%:%479=260%:%
+%:%480=261%:%
+%:%481=262%:%
+%:%482=263%:%
+%:%486=265%:%
+%:%490=267%:%
+%:%491=268%:%
+%:%492=269%:%
+%:%494=271%:%
+%:%495=271%:%
+%:%497=272%:%
+%:%498=273%:%
+%:%499=274%:%
+%:%500=275%:%
+%:%501=276%:%
+%:%502=277%:%
+%:%503=278%:%
+%:%504=278%:%
+%:%505=279%:%
+%:%506=280%:%
+%:%507=280%:%
+%:%508=281%:%
+%:%511=282%:%
+%:%515=282%:%
+%:%516=282%:%
+%:%518=283%:%
+%:%519=284%:%
+%:%529=286%:%
+%:%530=287%:%
+%:%531=288%:%
+%:%532=289%:%
+%:%533=290%:%
+%:%534=291%:%
+%:%535=292%:%
+%:%536=293%:%
+%:%537=294%:%
+%:%538=295%:%
+%:%539=296%:%
+%:%540=297%:%
+%:%541=298%:%
+%:%542=299%:%
+%:%543=300%:%
+%:%544=301%:%
+%:%545=302%:%
+%:%546=303%:%
+%:%550=305%:%
+%:%551=306%:%
+%:%553=308%:%
+%:%554=308%:%
+%:%556=309%:%
+%:%557=309%:%
+%:%558=310%:%
+%:%559=311%:%
+%:%560=311%:%
+%:%561=312%:%
+%:%564=313%:%
+%:%568=313%:%
+%:%569=313%:%
+%:%570=314%:%
+%:%571=314%:%
+%:%572=315%:%
+%:%573=315%:%
+%:%574=316%:%
+%:%575=316%:%
+%:%576=316%:%
+%:%577=317%:%
+%:%587=319%:%
+%:%588=320%:%
+%:%589=321%:%
+%:%590=322%:%
+%:%594=324%:%
+%:%598=326%:%
+%:%599=327%:%
+%:%600=328%:%
+%:%604=330%:%
+%:%605=331%:%
+%:%607=333%:%
+%:%608=333%:%
+%:%621=354%:%
+%:%622=355%:%
+%:%623=355%:%
+%:%625=356%:%
+%:%626=357%:%
+%:%627=358%:%
+%:%628=359%:%
+%:%629=360%:%
+%:%630=361%:%
+%:%631=361%:%
+%:%633=362%:%
+%:%634=363%:%
+%:%635=363%:%
+%:%636=364%:%
+%:%637=365%:%
+%:%638=365%:%
+%:%640=366%:%
+%:%641=367%:%
+%:%644=369%:%
+%:%645=370%:%
+%:%647=372%:%
+%:%648=372%:%
+%:%649=373%:%
+%:%650=374%:%
+%:%651=374%:%
+%:%653=374%:%
+%:%657=374%:%
+%:%658=374%:%
+%:%660=375%:%
+%:%661=376%:%
+%:%662=377%:%
+%:%663=378%:%
+%:%664=379%:%
+%:%665=380%:%
+%:%666=381%:%
+%:%676=383%:%
+%:%677=384%:%
+%:%678=385%:%
+%:%681=387%:%
+%:%682=388%:%
+%:%683=389%:%
+%:%684=390%:%
+%:%685=391%:%
+%:%686=392%:%
+%:%689=394%:%
+%:%691=396%:%
+%:%692=396%:%
+%:%693=397%:%
+%:%696=398%:%
+%:%700=398%:%
+%:%701=398%:%
+%:%703=399%:%
+%:%709=399%:%
+%:%712=400%:%
+%:%713=401%:%
+%:%714=401%:%
+%:%715=402%:%
+%:%716=403%:%
+%:%717=404%:%
+%:%718=404%:%
+%:%720=404%:%
+%:%724=404%:%
+%:%725=404%:%
+%:%727=405%:%
+%:%728=406%:%
+%:%729=407%:%
+%:%730=408%:%
+%:%731=409%:%
+%:%741=411%:%
+%:%742=412%:%
+%:%743=413%:%
+%:%744=414%:%
+%:%745=415%:%
+%:%746=416%:%
+%:%747=417%:%
+%:%748=418%:%
+%:%749=419%:%
+%:%753=422%:%
+%:%754=423%:%
+%:%755=424%:%
+%:%756=425%:%
+%:%757=426%:%
+%:%758=427%:%
+%:%759=428%:%
+%:%760=429%:%
+%:%761=430%:%
+%:%762=431%:%
+%:%763=432%:%
+%:%764=433%:%
+%:%773=435%:%
+%:%785=437%:%
+%:%786=438%:%
+%:%787=439%:%
+%:%789=441%:%
+%:%790=441%:%
+%:%791=442%:%
+%:%792=443%:%
+%:%793=444%:%
+%:%794=444%:%
+%:%796=444%:%
+%:%800=444%:%
+%:%801=444%:%
+%:%803=445%:%
+%:%804=446%:%
+%:%805=447%:%
+%:%806=448%:%
+%:%816=450%:%
+%:%817=451%:%
+%:%818=452%:%
+%:%822=454%:%
+%:%824=456%:%
+%:%825=456%:%
+%:%826=457%:%
+%:%827=458%:%
+%:%828=459%:%
+%:%829=459%:%
+%:%831=459%:%
+%:%835=459%:%
+%:%836=459%:%
+%:%838=460%:%
+%:%839=461%:%
+%:%840=462%:%
+%:%841=463%:%
+%:%851=465%:%
+%:%852=466%:%
+%:%854=468%:%
+%:%855=468%:%
+%:%856=469%:%
+%:%857=470%:%
+%:%858=471%:%
+%:%859=471%:%
+%:%861=471%:%
+%:%865=471%:%
+%:%866=471%:%
+%:%868=472%:%
+%:%869=473%:%
+%:%870=474%:%
+%:%871=475%:%
+%:%872=476%:%
+%:%882=478%:%
+%:%883=479%:%
+%:%885=481%:%
+%:%886=481%:%
+%:%887=482%:%
+%:%888=483%:%
+%:%891=484%:%
+%:%895=484%:%
+%:%896=484%:%
+%:%897=484%:%
+%:%906=486%:%
+%:%907=487%:%
+%:%908=488%:%
+%:%909=489%:%
+%:%911=491%:%
+%:%912=491%:%
+%:%913=492%:%
+%:%914=493%:%
+%:%917=494%:%
+%:%921=494%:%
+%:%922=494%:%
+%:%923=494%:%
+%:%932=496%:%
+%:%933=497%:%
+%:%935=499%:%
+%:%936=499%:%
+%:%937=500%:%
+%:%938=501%:%
+%:%939=502%:%
+%:%940=502%:%
+%:%942=502%:%
+%:%946=502%:%
+%:%947=502%:%
+%:%949=503%:%
+%:%950=504%:%
+%:%951=505%:%
+%:%952=506%:%
+%:%962=508%:%
+%:%963=509%:%
+%:%964=510%:%
+%:%965=511%:%
+%:%966=512%:%
+%:%967=513%:%
+%:%969=515%:%
+%:%970=515%:%
+%:%971=516%:%
+%:%972=517%:%
+%:%973=518%:%
+%:%974=519%:%
+%:%975=519%:%
+%:%977=519%:%
+%:%981=519%:%
+%:%982=519%:%
+%:%984=520%:%
+%:%985=521%:%
+%:%986=522%:%
+%:%987=523%:%
+%:%988=524%:%
+%:%989=525%:%
+%:%999=527%:%
+%:%1000=528%:%
+%:%1001=529%:%
+%:%1002=530%:%
+%:%1003=531%:%
+%:%1004=532%:%
+%:%1006=534%:%
+%:%1007=534%:%
+%:%1008=535%:%
+%:%1009=536%:%
+%:%1012=537%:%
+%:%1016=537%:%
+%:%1017=537%:%
+%:%1019=538%:%
+%:%1029=540%:%
+%:%1030=541%:%
+%:%1032=542%:%
+%:%1033=542%:%
+%:%1034=543%:%
+%:%1035=544%:%
+%:%1036=544%:%
+%:%1038=544%:%
+%:%1042=544%:%
+%:%1043=544%:%
+%:%1045=545%:%
+%:%1046=546%:%
+%:%1047=547%:%
+%:%1048=548%:%
+%:%1049=549%:%
+%:%1072=555%:%
+%:%1073=556%:%
+%:%1074=557%:%
+%:%1075=558%:%
+%:%1084=560%:%
+%:%1096=562%:%
+%:%1097=563%:%
+%:%1098=564%:%
+%:%1099=565%:%
+%:%1103=567%:%
+%:%1104=568%:%
+%:%1106=570%:%
+%:%1107=570%:%
+%:%1108=571%:%
+%:%1109=572%:%
+%:%1110=572%:%
+%:%1111=573%:%
+%:%1114=574%:%
+%:%1118=574%:%
+%:%1119=574%:%
+%:%1120=574%:%
+%:%1122=575%:%
+%:%1123=576%:%
+%:%1133=578%:%
+%:%1134=579%:%
+%:%1135=580%:%
+%:%1136=581%:%
+%:%1137=582%:%
+%:%1138=583%:%
+%:%1139=584%:%
+%:%1140=585%:%
+%:%1141=586%:%
+%:%1142=587%:%
+%:%1143=588%:%
+%:%1144=589%:%
+%:%1145=590%:%
+%:%1146=591%:%
+%:%1147=592%:%
+%:%1149=594%:%
+%:%1150=594%:%
+%:%1151=595%:%
+%:%1152=596%:%
+%:%1153=597%:%
+%:%1154=597%:%
+%:%1156=597%:%
+%:%1160=597%:%
+%:%1161=597%:%
+%:%1163=598%:%
+%:%1164=599%:%
+%:%1165=600%:%
+%:%1166=601%:%
+%:%1167=602%:%
+%:%1168=603%:%
+%:%1178=605%:%
+%:%1179=606%:%
+%:%1180=607%:%
+%:%1181=608%:%
+%:%1185=610%:%
+%:%1186=611%:%
+%:%1187=612%:%
+%:%1189=614%:%
+%:%1190=614%:%
+%:%1191=615%:%
+%:%1192=615%:%
+%:%1194=616%:%
+%:%1195=617%:%
+%:%1196=617%:%
+%:%1197=618%:%
+%:%1198=619%:%
+%:%1199=619%:%
+%:%1200=620%:%
+%:%1203=621%:%
+%:%1207=621%:%
+%:%1208=621%:%
+%:%1210=622%:%
+%:%1211=623%:%
+%:%1212=624%:%
+%:%1222=626%:%
+%:%1223=627%:%
+%:%1224=628%:%
+%:%1225=629%:%
+%:%1227=631%:%
+%:%1228=631%:%
+%:%1229=632%:%
+%:%1231=632%:%
+%:%1235=632%:%
+%:%1236=632%:%
+%:%1238=633%:%
+%:%1246=633%:%
+%:%1247=634%:%
+%:%1248=635%:%
+%:%1249=635%:%
+%:%1250=636%:%
+%:%1252=636%:%
+%:%1256=636%:%
+%:%1257=636%:%
+%:%1259=637%:%
+%:%1269=639%:%
+%:%1270=640%:%
+%:%1271=641%:%
+%:%1279=643%:%

### 2022-02-13 paper/output/document/appendix_2.tex
rough chapter 3, now i just need to cleangit add .git add .git add . which i will do in 10 minute intervals between classes

--- 2021-11-17 paper/output/document/paper412.tex
@@
 \begin{isabellebody}%
-\setisabellecontext{paper{\isadigit{4}}{\isadigit{1}}{\isadigit{2}}}%
+\setisabellecontext{appendix{\isacharunderscore}{\isadigit{2}}}%
 %
@@
 \isatagtheory
-\isacommand{theory}\isamarkupfalse%
-\ paper{\isadigit{4}}{\isadigit{1}}{\isadigit{2}}\ \isakeyword{imports}\ paper{\isadigit{4}}{\isadigit{1}}\isanewline
-\isanewline
-\isakeyword{begin}%
+%
 \endisatagtheory
@@
 %
-\isamarkupsubsection{Application Tests%
+\isamarkupsubsection{Testing Un-Universalizable Actions \label{weirdtests}%
 }
@@
 \endisadelimdocument
-%
-\begin{isamarkuptext}%
-As with the naive formalization and Kroy's formalization, I will apply my testing framework to 
-my custom formalization of the FUL. I will begin with some basic application tests. In these tests, 
-I specify particular maxims as constants with no properties and gradually add properties to understand 
-how the system handles different kinds of maxims.%
-\end{isamarkuptext}\isamarkuptrue%
 %
@@
 when universalized but literally impossible because the practice breaks down. I capture this idea in the 
-assumption \isa{everyone{\isacharunderscore}can{\isacharprime}t{\isacharunderscore}lie\ {\isasymequiv}\ {\isasymforall}w{\isachardot}\ {\isasymnot}\ {\isacharparenleft}{\isasymforall}s{\isachardot}\ falsely{\isacharunderscore}promise\ s\ w{\isacharparenright}}, which states that, at all worlds, not everyone can falsely promise since
+assumption \isa{appendix{\isacharunderscore}{\isadigit{2}}{\isachardot}everyone{\isacharunderscore}can{\isacharprime}t{\isacharunderscore}lie\ {\isasymequiv}\ {\isasymforall}w{\isachardot}\ {\isasymnot}\ {\isacharparenleft}{\isasymforall}s{\isachardot}\ appendix{\isacharunderscore}{\isadigit{2}}{\isachardot}falsely{\isacharunderscore}promise\ s\ w{\isacharparenright}}, which states that, at all worlds, not everyone can falsely promise since
 otherwise the practice of promising would break down. The second reading, on the other hand, reads the 
@@
 \endisadelimproof
-%
-\begin{isamarkuptext}%
-This completes the application tests for my formalization. I showed that my formalization correctly 
-handles an example from Korsgaard with two possible interpretations and also sufficiently handles both 
-conventional and natural acts.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\isatagdocument
-%
-\isamarkupsubsection{Metaethical Tests%
-}
-\isamarkuptrue%
-%
-\endisatagdocument
-{\isafolddocument}%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\begin{isamarkuptext}%
-Recall that metaethical tests test formal properties of the system that apply to any maxim, not 
-just those specified in the application tests. In this section I adapt the metaethical tests developed 
-in previous sections to my formalization of the categorical imperative. I preserved the philosophical 
-goal of each test but modified them to test the stronger, richer notion of a maxim.
-
-The first set of tests consider how obligation generalizes, first across worlds and then across
-people. As expected, the tests below show that both wrongness (prohibition) and rightness (obligation)
-generalize across both worlds and people. In other words, if something is obligated at some world, it 
-is obligated at every world and if something is obligated for some person, then it is obligated for 
-every person.
-
-Generalization across worlds is a consequence of the fact that my interpretation does not make use of the 
-modal nature of DDL. In particular, I do not use any property of the world when prescribing obligations 
-at that world.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ wrong{\isacharunderscore}if{\isacharunderscore}wrong{\isacharunderscore}for{\isacharunderscore}someone{\isacharcolon}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}w{\isachardot}\ {\isasymforall}c{\isacharcolon}{\isacharcolon}t{\isachardot}\ {\isasymforall}g{\isacharcolon}{\isacharcolon}t{\isachardot}\ {\isasymexists}s{\isacharcolon}{\isacharcolon}s{\isachardot}\ O{\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}W\ {\isacharparenleft}c{\isacharcomma}\ M{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ {\isacharbar}\ c{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ \ O{\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}W\ {\isacharparenleft}c{\isacharcomma}\ M{\isacharcomma}\ g{\isacharparenright}\ p{\isacharparenright}\ {\isacharbar}\ c{\isacharbraceright}\ w{\isacharparenright}\ {\isachardoublequoteclose}\isanewline
-%
-\isadelimproof
-\ \ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{by}\isamarkupfalse%
-\ blast%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
 \isanewline
 %
-\endisadelimproof
+\isadelimtheory
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ right{\isacharunderscore}if{\isacharunderscore}right{\isacharunderscore}for{\isacharunderscore}someone{\isacharcolon}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}w{\isachardot}\ {\isasymforall}c{\isacharcolon}{\isacharcolon}t{\isachardot}\ {\isasymforall}g{\isacharcolon}{\isacharcolon}t{\isachardot}\ {\isasymexists}s{\isacharcolon}{\isacharcolon}s{\isachardot}\ O{\isacharbraceleft}W\ {\isacharparenleft}c{\isacharcomma}\ M{\isacharcomma}\ g{\isacharparenright}\ s\ {\isacharbar}\ c{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ \ O{\isacharbraceleft}W\ {\isacharparenleft}c{\isacharcomma}\ M{\isacharcomma}\ g{\isacharparenright}\ p\ {\isacharbar}\ c{\isacharbraceright}\ w{\isacharparenright}\ {\isachardoublequoteclose}\isanewline
-%
-\isadelimproof
-\ \ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{by}\isamarkupfalse%
-\ blast%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-\isanewline
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ wrong{\isacharunderscore}if{\isacharunderscore}wrong{\isacharunderscore}somewhere{\isacharcolon}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}c\ g{\isachardot}\ {\isasymexists}w{\isadigit{1}}{\isachardot}\ O{\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}W\ {\isacharparenleft}c{\isacharcomma}\ M{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ {\isacharbar}\ c{\isacharbraceright}\ w{\isadigit{1}}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}w{\isadigit{2}}{\isachardot}\ \ O{\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}W\ {\isacharparenleft}c{\isacharcomma}\ M{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ {\isacharbar}\ c{\isacharbraceright}\ w{\isadigit{2}}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-%
-\isadelimproof
-\ \ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{by}\isamarkupfalse%
-\ blast%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-\isanewline
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ right{\isacharunderscore}if{\isacharunderscore}right{\isacharunderscore}somewhere{\isacharcolon}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}c\ g{\isachardot}\ {\isasymexists}w{\isadigit{1}}{\isachardot}\ O{\isacharbraceleft}W\ {\isacharparenleft}c{\isacharcomma}\ M{\isacharcomma}\ g{\isacharparenright}\ s\ {\isacharbar}\ c{\isacharbraceright}\ w{\isadigit{1}}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}w{\isadigit{2}}{\isachardot}\ \ O{\isacharbraceleft}W\ {\isacharparenleft}c{\isacharcomma}\ M{\isacharcomma}\ g{\isacharparenright}\ s\ {\isacharbar}\ c{\isacharbraceright}\ w{\isadigit{2}}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-%
-\isadelimproof
-\ \ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{by}\isamarkupfalse%
-\ blast%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-As expected, obligation generalizes across people and worlds. In the next set of tests, I will 
-analyze basic properties of permissibility, obligation, and prohibition.
-
-First, I verify that the logic allows
-for permissible maxims, as this is a problem that prior iterations ran into. Below, I use Nitpick to 
-find a model in which there is a circumstance, act, goal tuple that is permissible but not 
-obligated at some world.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ permissible{\isacharcolon}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O{\isacharbraceleft}{\isacharparenleft}W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ {\isacharbar}\ c{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O{\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ {\isacharbar}\ c{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
-\ \ \isacommand{nitpick}\isamarkupfalse%
-\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharbrackright}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{oops}\isamarkupfalse%
-\isanewline
-%
-\isamarkupcmt{\color{blue}Nitpick found a model for card i = 1 and card s = 1:
-
-  Free variables:
-    a = ($\lambda x. \_$)($s_1$ := ($\lambda x. \_$)($i_1$ := False))
-    c = ($\lambda x. \_$)($i_1$ := False)
-    g = ($\lambda x. \_$)($i_1$ := False)
-    s = $s_1$\color{black}
-Recall that Nitpick is a model checker that finds models making certain formulae true or false. In this 
-case, Nitpick finds a model satisfying the given formula (which simply requires that the sentence 
-``s wills (c, a, g)'' is permissible but not obligator). This model consists of the above specifications 
-of a, c, g, and s.%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-I also expect that any arbitrary maxim should be either permissible or prohibited, since all 
-acts are either permissible or prohibited.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ perm{\isacharunderscore}or{\isacharunderscore}prohibited{\isacharcolon}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}permissible\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ \isactrlbold {\isasymor}\ {\isacharparenleft}prohibited\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
-%
-\isadelimproof
-\ \ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{by}\isamarkupfalse%
-\ blast\isanewline
-%
-\isamarkupcmt{This simple test passes immediately by the definitions of  permissible and prohibited.%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-Obligation should be strictly stronger than permissibility. In other words, if a maxim is 
-obligated at a world, it should be permissible at that world. Below I test this property.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ obligated{\isacharunderscore}then{\isacharunderscore}permissible{\isacharcolon}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}O{\isacharbraceleft}W{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharbar}c{\isacharbraceright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isacharparenleft}permissible\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ {\isacharparenright}\ s{\isacharparenright}{\isacharparenright}\ w\ {\isachardoublequoteclose}\isanewline
-%
-\isadelimproof
-\ \ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{using}\isamarkupfalse%
-\ no{\isacharunderscore}contradictions\ \isacommand{by}\isamarkupfalse%
-\ auto\isanewline
-%
-\isamarkupcmt{This test passes and Isabelle is able to find a proof for the fact that all obligatory maxims are 
-also permissible.%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-The above test failed under Kroy's formalization of the categorical imperative and is thus evidence 
-that my formalization improves upon Kroy's. Interestingly, this new test passes because of the additional
-added axiom that prohibits contradictory obligations (recall that Kroy's formalization allowed contradictory
-obligations).%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-Next, I will test if the formalization allows for vacuous obligations or modal collapse. These 
-tests are sanity checks confirmed that the obligation operator is doesn't collapse. First, I will check 
-that any arbitrary term isn't obligated.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ arbitrary{\isacharunderscore}obligations{\isacharcolon}\isanewline
-\ \ \isakeyword{fixes}\ c\ A{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}O{\isacharbraceleft}A{\isacharbar}c{\isacharbraceright}\ w{\isachardoublequoteclose}\isanewline
-\ \ \isacommand{nitpick}\isamarkupfalse%
-\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharequal}true{\isacharcomma}\ falsify{\isacharbrackright}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{oops}\isamarkupfalse%
-\isanewline
-%
-\isamarkupcmt{This test passes—Nitpick finds a model where A isn't obligated in circumstances c.
-\color{blue} Nitpick found a counterexample for card i = 1 and card s = 2:
-
-  Free variables:
-    A = ($\lambda x. \_$)($i_1$ := True)
-    c = ($\lambda x. \_$)($i_1$ := False) \color{blue}
-Previous iterations of this test used the monadic obligation operator, which tests the term in the 
-context ``True" (equivalently the set of all worlds since True holds everywhere). In this iteration, 
-I test the term in a context c, because my formalization uses the dyadic obligation operator and must 
-thus specify circumstances.%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-This is exactly the expected result. Any arbitrary action $A$ isn't obligated. A slightly 
-        stronger property is ``modal collapse," or whether or not `$A$ happens' implies `$A$ is obligated'. 
-The proposition below should be falsifiable.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ modal{\isacharunderscore}collapse{\isacharcolon}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ w{\isacharparenright}\ {\isasymlongrightarrow}\ O{\isacharbraceleft}W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharbar}c{\isacharbraceright}\ w{\isachardoublequoteclose}\isanewline
-\ \ \isacommand{nitpick}\isamarkupfalse%
-\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharequal}true{\isacharcomma}\ falsify{\isacharbrackright}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{oops}\isamarkupfalse%
-\isanewline
-%
-\isamarkupcmt{Nitpick finds a counterexample, so willing doesn't imply obligation, so this test passes. 
-\color{blue}Nitpick found a counterexample for card i = 1 and card s = 2:
-
-  Free variables:
-    a = ($\lambda x. \_$)($s_1$ := ($\lambda x. \_$)($i_1$ := False), $s_2$ := ($\lambda x. \_$)($i_1$ := False))
-    c = ($\lambda x. \_$)($i_1$ := False)
-    g = ($\lambda x. \_$)($i_1$ := False)
-    s = $s_2$
-    w = $i_1$\color{black}
-Once again, I modify this test to use the dyadic obligation operator instead of the monadic operator.%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-The final set of tests deal with ought implies can and conflicting obligations. Recall that I 
-specifically added an axiom in my formalization to disallow contradictory obligations, so I expect 
-these tests to pass. Kroy's formalization fails these tests, so this is another area of improvement 
-over Kroy's formalization.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ ought{\isacharunderscore}implies{\isacharunderscore}can{\isacharcolon}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}O{\isacharbraceleft}W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharbar}c{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymdiamond}\ W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
-%
-\isadelimproof
-\ \ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{using}\isamarkupfalse%
-\ O{\isacharunderscore}diamond\ \isacommand{by}\isamarkupfalse%
-\ blast\isanewline
-%
-\isamarkupcmt{This test is a lemma of DDL itself, so it's no surprise that this test passes.%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-\isanewline
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ conflicting{\isacharunderscore}obligations{\isacharcolon}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymnot}\ {\isacharparenleft}O{\isacharbraceleft}W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharbar}c{\isacharbraceright}\ \isactrlbold {\isasymand}\ O{\isacharbraceleft}\isactrlbold {\isasymnot}{\isacharparenleft}W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}{\isacharbar}\ c{\isacharbraceright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
-%
-\isadelimproof
-\ \ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{using}\isamarkupfalse%
-\ no{\isacharunderscore}contradictions\ \isacommand{by}\isamarkupfalse%
-\ blast\isanewline
-%
-\isamarkupcmt{This test passes immediately by the new axiom prohibited contradictory obligations.%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-\isanewline
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ implied{\isacharunderscore}contradiction{\isacharcolon}\isanewline
-\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}{\isacharparenleft}W\ {\isacharparenleft}c{\isadigit{1}}{\isacharcomma}\ a{\isadigit{1}}{\isacharcomma}\ g{\isadigit{1}}{\isacharparenright}\ s{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}W\ {\isacharparenleft}c{\isadigit{2}}{\isacharcomma}\ a{\isadigit{2}}{\isacharcomma}\ g{\isadigit{2}}{\isacharparenright}\ s{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbottom}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}\isactrlbold {\isasymnot}\ {\isacharparenleft}O{\isacharbraceleft}W{\isacharparenleft}c{\isadigit{1}}{\isacharcomma}\ a{\isadigit{1}}{\isacharcomma}\ g{\isadigit{1}}{\isacharparenright}\ s{\isacharbar}c{\isacharbraceright}\ \isactrlbold {\isasymand}\ O{\isacharbraceleft}W{\isacharparenleft}c{\isadigit{2}}{\isacharcomma}\ a{\isadigit{2}}{\isacharcomma}\ g{\isadigit{2}}{\isacharparenright}\ s{\isacharbar}c{\isacharbraceright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
-%
-\isadelimproof
-\ \ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{using}\isamarkupfalse%
-\ assms\ no{\isacharunderscore}contradictions\ \isacommand{by}\isamarkupfalse%
-\ blast\isanewline
-%
-\isamarkupcmt{Recall that the we also expect the stronger property that the combination of obligatory maxims can't
- imply a contradiction. The added axiom also makes this test pass.%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-\isanewline
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ distribution{\isacharcolon}\isanewline
-\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymand}\ O\ {\isacharbraceleft}B{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymTurnstile}\ O\ {\isacharbraceleft}A\ \isactrlbold {\isasymand}\ B{\isacharbraceright}{\isachardoublequoteclose}\isanewline
-%
-\isadelimproof
-\ \ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{using}\isamarkupfalse%
-\ assms\ no{\isacharunderscore}contradictions\ \isacommand{by}\isamarkupfalse%
-\ fastforce%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-The metaethical test suite ran on both Kroy's formalization and my formalizaion show two clear 
-improvements. First, my formalization shows that obligatory maxims are permissible, whereas Kroy's 
-paradoxically does not. Second, my formalization doesn't allow contradictory maxims, but Kroy's does. 
-Both of these improvements are derived from the new axiom I added in my formalization that disallows 
-contradictory obligations. Additionally, my formalization also improves on Kroy's by staying faithful to the 
-strongest interpretation of the FUL, Korsgaard's practical contradiction interpretation. (maybe stick 
-philosophical writing here or above?)%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\isatagdocument
-%
-\isamarkupsubsection{Formalization Specific Tests%
-}
-\isamarkuptrue%
-%
-\endisatagdocument
-{\isafolddocument}%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\begin{isamarkuptext}%
-In this section, I explore tests specific to my formalization of the categorical imperative. First, 
-in my previous (buggy) implementation of DDL, prohibiting contradictory obligation led to the strange 
-result that all permissible actions are obligatory. I will test if this bug appears in this implementation 
-as well.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ bug{\isacharcolon}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}permissible\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ w\ {\isasymlongrightarrow}\ O{\isacharbraceleft}W{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ {\isacharbar}\ c{\isacharbraceright}\ w{\isachardoublequoteclose}\isanewline
-\ \ \isacommand{nitpick}\isamarkupfalse%
-{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{oops}\isamarkupfalse%
-\isanewline
-%
-\isamarkupcmt{\color{blue}
-Nitpick found a counterexample for card i = 1 and card s = 2:
-
-  Free variables:
-    a = ($\lambda x. \_$)($s_1$ := ($\lambda x. \_$)($i_1$ := False), $s_2$ := ($\lambda x. \_$)($i_1$ := False))
-    c = ($\lambda x. \_$)($i_1$ := False)
-    g = ($\lambda x. \_$)($i_1$ := False)
-    s = $s_2$
-    w = undefined
-\color{black}
-This strange result does not hold; good!%
-}\isanewline
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isadelimtheory
 %
@@
 \endinput
-%:%file=~/Desktop/cs91r/paper/paper412.thy%:%
-%:%10=1%:%
-%:%11=1%:%
-%:%12=2%:%
-%:%13=3%:%
-%:%27=6%:%
-%:%39=8%:%
-%:%40=9%:%
-%:%41=10%:%
-%:%42=11%:%
-%:%46=13%:%
-%:%47=14%:%
-%:%48=15%:%
-%:%49=16%:%
-%:%50=17%:%
-%:%51=18%:%
-%:%52=19%:%
-%:%53=20%:%
-%:%54=21%:%
-%:%55=22%:%
-%:%56=23%:%
-%:%57=24%:%
-%:%58=25%:%
-%:%59=26%:%
+%:%file=~/Desktop/cs91r/paper/appendix_2.thy%:%
+%:%24=5%:%
+%:%36=7%:%
+%:%37=8%:%
+%:%38=9%:%
+%:%39=10%:%
+%:%40=11%:%
+%:%41=12%:%
+%:%42=13%:%
+%:%43=14%:%
+%:%44=15%:%
+%:%45=16%:%
+%:%46=17%:%
+%:%47=18%:%
+%:%48=19%:%
+%:%49=20%:%
+%:%50=21%:%
+%:%51=22%:%
+%:%53=24%:%
+%:%54=24%:%
+%:%56=25%:%
+%:%57=26%:%
+%:%58=26%:%
+%:%59=27%:%
 %:%60=27%:%
-%:%61=28%:%
-%:%63=30%:%
-%:%64=30%:%
-%:%66=31%:%
-%:%67=32%:%
-%:%68=32%:%
-%:%69=33%:%
-%:%70=33%:%
+%:%62=28%:%
+%:%63=29%:%
+%:%64=29%:%
+%:%65=30%:%
+%:%66=30%:%
+%:%68=31%:%
+%:%69=32%:%
+%:%70=32%:%
+%:%71=33%:%
 %:%72=34%:%
-%:%73=35%:%
+%:%73=34%:%
 %:%74=35%:%
-%:%75=36%:%
 %:%76=36%:%
-%:%78=37%:%
 %:%79=38%:%
-%:%80=38%:%
-%:%81=39%:%
-%:%82=40%:%
-%:%83=40%:%
-%:%84=41%:%
-%:%86=42%:%
-%:%89=44%:%
-%:%90=45%:%
-%:%91=46%:%
-%:%93=48%:%
-%:%94=48%:%
-%:%95=49%:%
-%:%97=50%:%
-%:%98=51%:%
-%:%99=52%:%
-%:%100=53%:%
-%:%101=54%:%
-%:%102=54%:%
-%:%103=55%:%
-%:%104=56%:%
-%:%105=56%:%
-%:%106=57%:%
-%:%108=58%:%
-%:%109=59%:%
-%:%110=60%:%
-%:%111=61%:%
-%:%112=62%:%
-%:%113=62%:%
-%:%114=63%:%
-%:%115=64%:%
-%:%116=64%:%
-%:%117=65%:%
-%:%119=66%:%
-%:%120=67%:%
-%:%121=68%:%
-%:%122=69%:%
-%:%123=70%:%
-%:%126=72%:%
-%:%127=73%:%
-%:%129=75%:%
-%:%130=75%:%
-%:%131=76%:%
-%:%132=77%:%
-%:%133=78%:%
-%:%134=79%:%
-%:%141=80%:%
-%:%142=80%:%
-%:%143=81%:%
-%:%144=81%:%
-%:%145=82%:%
-%:%146=82%:%
-%:%148=83%:%
-%:%149=84%:%
-%:%150=84%:%
-%:%151=85%:%
-%:%152=85%:%
-%:%153=86%:%
-%:%154=86%:%
-%:%155=86%:%
-%:%156=87%:%
-%:%166=89%:%
-%:%167=90%:%
-%:%168=91%:%
-%:%169=92%:%
-%:%170=93%:%
-%:%171=94%:%
-%:%172=95%:%
+%:%80=39%:%
+%:%81=40%:%
+%:%83=42%:%
+%:%84=42%:%
+%:%85=43%:%
+%:%87=44%:%
+%:%88=45%:%
+%:%89=46%:%
+%:%90=47%:%
+%:%91=48%:%
+%:%92=48%:%
+%:%93=49%:%
+%:%94=50%:%
+%:%95=50%:%
+%:%96=51%:%
+%:%98=52%:%
+%:%99=53%:%
+%:%100=54%:%
+%:%101=55%:%
+%:%102=56%:%
+%:%103=56%:%
+%:%104=57%:%
+%:%105=58%:%
+%:%106=58%:%
+%:%107=59%:%
+%:%109=60%:%
+%:%110=61%:%
+%:%111=62%:%
+%:%112=63%:%
+%:%113=64%:%
+%:%116=66%:%
+%:%117=67%:%
+%:%119=69%:%
+%:%120=69%:%
+%:%121=70%:%
+%:%122=71%:%
+%:%123=72%:%
+%:%124=73%:%
+%:%131=74%:%
+%:%132=74%:%
+%:%133=75%:%
+%:%134=75%:%
+%:%135=76%:%
+%:%136=76%:%
+%:%138=77%:%
+%:%139=78%:%
+%:%140=78%:%
+%:%141=79%:%
+%:%142=79%:%
+%:%143=80%:%
+%:%144=80%:%
+%:%145=80%:%
+%:%146=81%:%
+%:%156=83%:%
+%:%157=84%:%
+%:%158=85%:%
+%:%159=86%:%
+%:%160=87%:%
+%:%161=88%:%
+%:%162=89%:%
+%:%163=90%:%
+%:%165=92%:%
+%:%166=92%:%
+%:%167=93%:%
+%:%168=93%:%
+%:%169=94%:%
+%:%171=95%:%
+%:%172=96%:%
 %:%173=96%:%
+%:%174=97%:%
 %:%175=98%:%
@@
 %:%177=99%:%
-%:%178=99%:%
 %:%179=100%:%
+%:%180=101%:%
 %:%181=101%:%
 %:%182=102%:%
-%:%183=102%:%
+%:%183=103%:%
 %:%184=103%:%
 %:%185=104%:%
-%:%186=104%:%
-%:%187=105%:%
+%:%186=105%:%
+%:%188=106%:%
 %:%189=106%:%
 %:%190=107%:%
-%:%191=107%:%
-%:%192=108%:%
+%:%191=108%:%
 %:%193=109%:%
@@
 %:%195=110%:%
-%:%196=111%:%
-%:%198=112%:%
-%:%199=112%:%
-%:%200=113%:%
-%:%201=114%:%
-%:%203=115%:%
-%:%204=115%:%
-%:%205=116%:%
-%:%212=117%:%
-%:%213=117%:%
-%:%214=118%:%
-%:%215=118%:%
-%:%216=119%:%
-%:%217=119%:%
-%:%218=119%:%
-%:%219=120%:%
-%:%220=120%:%
-%:%221=121%:%
-%:%222=121%:%
-%:%223=121%:%
-%:%224=122%:%
-%:%225=122%:%
-%:%227=123%:%
-%:%237=125%:%
-%:%238=126%:%
-%:%239=127%:%
-%:%240=128%:%
-%:%241=129%:%
-%:%242=130%:%
-%:%243=131%:%
-%:%244=132%:%
-%:%245=133%:%
-%:%246=134%:%
-%:%247=135%:%
-%:%248=136%:%
-%:%249=137%:%
-%:%250=138%:%
-%:%251=139%:%
-%:%252=140%:%
-%:%253=141%:%
-%:%254=142%:%
-%:%255=143%:%
-%:%256=144%:%
-%:%257=145%:%
-%:%258=146%:%
-%:%259=147%:%
-%:%260=148%:%
-%:%261=149%:%
-%:%262=150%:%
-%:%263=151%:%
-%:%264=152%:%
-%:%265=153%:%
-%:%266=154%:%
-%:%267=155%:%
-%:%268=156%:%
-%:%269=157%:%
-%:%270=158%:%
-%:%271=159%:%
-%:%272=160%:%
-%:%273=161%:%
-%:%274=162%:%
-%:%275=163%:%
-%:%276=164%:%
+%:%202=111%:%
+%:%203=111%:%
+%:%204=112%:%
+%:%205=112%:%
+%:%206=113%:%
+%:%207=113%:%
+%:%208=113%:%
+%:%209=114%:%
+%:%210=114%:%
+%:%211=115%:%
+%:%212=115%:%
+%:%213=115%:%
+%:%214=116%:%
+%:%215=116%:%
+%:%217=117%:%
+%:%227=119%:%
+%:%228=120%:%
+%:%229=121%:%
+%:%230=122%:%
+%:%231=123%:%
+%:%232=124%:%
+%:%233=125%:%
+%:%234=126%:%
+%:%235=127%:%
+%:%236=128%:%
+%:%237=129%:%
+%:%238=130%:%
+%:%239=131%:%
+%:%240=132%:%
+%:%241=133%:%
+%:%242=134%:%
+%:%243=135%:%
+%:%244=136%:%
+%:%245=137%:%
+%:%246=138%:%
+%:%247=139%:%
+%:%248=140%:%
+%:%249=141%:%
+%:%250=142%:%
+%:%251=143%:%
+%:%252=144%:%
+%:%253=145%:%
+%:%254=146%:%
+%:%255=147%:%
+%:%256=148%:%
+%:%257=149%:%
+%:%258=150%:%
+%:%259=151%:%
+%:%260=152%:%
+%:%261=153%:%
+%:%262=154%:%
+%:%263=155%:%
+%:%264=156%:%
+%:%265=157%:%
+%:%266=158%:%
+%:%270=160%:%
+%:%271=161%:%
+%:%272=162%:%
+%:%274=164%:%
+%:%275=164%:%
+%:%276=165%:%
+%:%277=166%:%
+%:%278=166%:%
 %:%280=166%:%
-%:%281=167%:%
-%:%282=168%:%
-%:%284=170%:%
-%:%285=170%:%
-%:%286=171%:%
-%:%287=172%:%
-%:%288=172%:%
-%:%290=172%:%
-%:%294=172%:%
-%:%295=172%:%
-%:%297=173%:%
-%:%298=174%:%
-%:%299=175%:%
-%:%300=176%:%
-%:%301=177%:%
-%:%302=178%:%
-%:%312=181%:%
-%:%313=182%:%
-%:%314=183%:%
-%:%323=185%:%
-%:%335=187%:%
-%:%336=188%:%
-%:%337=189%:%
-%:%338=190%:%
-%:%339=191%:%
-%:%340=192%:%
-%:%341=193%:%
-%:%342=194%:%
-%:%343=195%:%
-%:%344=196%:%
-%:%345=197%:%
-%:%346=198%:%
-%:%347=199%:%
-%:%348=200%:%
-%:%350=202%:%
-%:%351=202%:%
-%:%352=203%:%
-%:%355=204%:%
-%:%359=204%:%
-%:%360=204%:%
-%:%365=204%:%
-%:%368=205%:%
-%:%369=206%:%
-%:%370=206%:%
-%:%371=207%:%
-%:%374=208%:%
-%:%378=208%:%
-%:%379=208%:%
-%:%384=208%:%
-%:%387=209%:%
-%:%388=210%:%
-%:%389=210%:%
-%:%390=211%:%
-%:%393=212%:%
-%:%397=212%:%
-%:%398=212%:%
-%:%403=212%:%
-%:%406=213%:%
-%:%407=214%:%
-%:%408=214%:%
-%:%409=215%:%
-%:%412=216%:%
-%:%416=216%:%
-%:%417=216%:%
-%:%426=218%:%
-%:%427=219%:%
-%:%428=220%:%
-%:%429=221%:%
-%:%430=222%:%
-%:%431=223%:%
-%:%432=224%:%
-%:%434=226%:%
-%:%435=226%:%
-%:%436=227%:%
-%:%437=228%:%
-%:%438=228%:%
-%:%440=228%:%
-%:%444=228%:%
-%:%445=228%:%
-%:%447=229%:%
-%:%448=230%:%
-%:%449=231%:%
-%:%450=232%:%
-%:%451=233%:%
-%:%452=234%:%
-%:%453=235%:%
-%:%454=236%:%
-%:%455=237%:%
-%:%456=238%:%
-%:%457=239%:%
-%:%467=241%:%
-%:%468=242%:%
-%:%470=244%:%
-%:%471=244%:%
-%:%472=245%:%
-%:%475=246%:%
-%:%479=246%:%
-%:%480=246%:%
-%:%482=247%:%
-%:%492=249%:%
-%:%493=250%:%
-%:%495=252%:%
-%:%496=252%:%
-%:%497=253%:%
-%:%500=254%:%
-%:%504=254%:%
-%:%505=254%:%
-%:%506=254%:%
-%:%508=255%:%
-%:%509=256%:%
-%:%519=258%:%
-%:%520=259%:%
-%:%521=260%:%
-%:%522=261%:%
-%:%526=263%:%
-%:%527=264%:%
-%:%528=265%:%
-%:%530=267%:%
-%:%531=267%:%
-%:%532=268%:%
-%:%533=269%:%
-%:%534=270%:%
-%:%535=270%:%
-%:%537=270%:%
-%:%541=270%:%
-%:%542=270%:%
-%:%544=271%:%
-%:%545=272%:%
-%:%546=273%:%
-%:%547=274%:%
-%:%548=275%:%
-%:%549=276%:%
-%:%550=277%:%
-%:%551=278%:%
-%:%552=279%:%
-%:%553=280%:%
-%:%563=282%:%
-%:%564=283%:%
-%:%565=284%:%
-%:%567=286%:%
-%:%568=286%:%
-%:%569=287%:%
-%:%570=288%:%
-%:%571=288%:%
-%:%573=288%:%
-%:%577=288%:%
-%:%578=288%:%
-%:%580=289%:%
-%:%581=290%:%
-%:%582=291%:%
-%:%583=292%:%
-%:%584=293%:%
-%:%585=294%:%
-%:%586=295%:%
-%:%587=296%:%
-%:%588=297%:%
-%:%589=298%:%
-%:%599=300%:%
-%:%600=301%:%
-%:%601=302%:%
-%:%602=303%:%
-%:%604=305%:%
-%:%605=305%:%
-%:%606=306%:%
-%:%609=307%:%
-%:%613=307%:%
-%:%614=307%:%
-%:%615=307%:%
-%:%617=308%:%
-%:%623=308%:%
-%:%626=309%:%
-%:%627=310%:%
-%:%628=310%:%
-%:%629=311%:%
-%:%632=312%:%
-%:%636=312%:%
-%:%637=312%:%
-%:%638=312%:%
-%:%640=313%:%
-%:%646=313%:%
-%:%649=314%:%
-%:%650=315%:%
-%:%651=315%:%
-%:%652=316%:%
-%:%653=317%:%
-%:%656=318%:%
-%:%660=318%:%
-%:%661=318%:%
-%:%662=318%:%
-%:%664=319%:%
-%:%665=320%:%
-%:%671=320%:%
-%:%674=321%:%
-%:%675=322%:%
-%:%676=322%:%
-%:%677=323%:%
-%:%678=324%:%
-%:%681=325%:%
-%:%685=325%:%
-%:%686=325%:%
-%:%687=325%:%
-%:%696=327%:%
-%:%697=328%:%
-%:%698=329%:%
-%:%699=330%:%
-%:%700=331%:%
-%:%701=332%:%
-%:%702=333%:%
-%:%711=335%:%
-%:%723=337%:%
-%:%724=338%:%
-%:%725=339%:%
-%:%726=340%:%
-%:%728=342%:%
-%:%729=342%:%
-%:%730=343%:%
-%:%731=344%:%
-%:%732=344%:%
-%:%734=344%:%
-%:%738=344%:%
-%:%739=344%:%
-%:%741=345%:%
-%:%742=346%:%
-%:%743=347%:%
-%:%744=348%:%
-%:%745=349%:%
-%:%746=350%:%
-%:%747=351%:%
-%:%748=352%:%
-%:%749=353%:%
-%:%750=354%:%
-%:%751=355%:%
-%:%752=355%:%
+%:%284=166%:%
+%:%285=166%:%
+%:%287=167%:%
+%:%288=168%:%
+%:%289=169%:%
+%:%290=170%:%
+%:%291=171%:%
+%:%292=172%:%
+%:%300=173%:%
+%:%303=174%:%
+%:%308=175%:%

### 2022-02-13 paper/output/document/thesis_3_implementation.tex
rough chapter 3, now i just need to cleangit add .git add .git add . which i will do in 10 minute intervals between classes

@@
 \begin{isamarkuptext}%
-In this section, I present the details of my implementation of automated Kantian ethics. I take
-a logic-programming approach in which I formalize the FUL in Dyadic Deontic Logic and then implement 
-this logic in Isabelle/HOl. I 
-also present my testing framework, which demonstrates one way to evaluate how faithful an implementation
+In this section, I present the details of my implementation of automated Kantian ethics. I first 
+formalize the FUL in Dyadic Deontic Logic and then implement this logic in Isabelle/HOl. I 
+also present a testing framework that can evaluate how faithful an implementation
 of automated ethics is to philosophical literature. This testing framework shows that my system outperforms
-two other possible implementations of automated Kantian Ethics.%
+two other possible implementations of automated Kantian ethics.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 Kantian ethics is centered on practical reason because it is action-guiding; the categorical
-imperative is a moral rule that agents can use to decide between potential actions. Thus, before I even
+imperative is a moral rule that agents can use to decide between potential actions. Thus, before I 
 begin to formalize a specific formulation of the categorical imperative, I must define the notions of 
-subjects and actions. Concretely, I need to add logical background so that my logic can express sentences 
-like, ``x does action.''%
+subjects and actions. I need to add logical background so that my logic can express sentences 
+of the form, ``x does action.''%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \ s\ %
-\isamarkupcmt{I declare a new type, $s$ as the type for a ``subject,'' i.e. the subject of a sentence.%
+\isamarkupcmt{I declare a new type $s$ as the type for a ``subject,'' as in the subject of a sentence.%
 }%
@@
 The \texttt{typedecl} keyword indicates that I am defining a new atomic type, which is not composed
-of pre-existing types but is instead a new kind of thing altogether. I try to minimize the number of 
-atomic types, so this will be one of the few new types that I define. To define a subject, it suffices
-to declare a new type to represent a subject, as that is all that is needed to apply the Formula of
-Universal Law. Notice that I have not defined any properties of this type, such as the idea that a subject
-must be rational or human. Throughout my project, I will use bare syntactic units like types and constants 
-to define new ideas and will add the minimum necessary definitions, or ``thin'' definitions, to achieve the desired results.
-By avoiding complex definitions of a subject, I can avoid murky philosophical debates about the nature
-of agency and reduce the potential for controversy or errors.
-
-In this interpretation, the defining feature of a subject is that it can act, a relatively uncontroversial
-notion. I represent that below by allowing subjects to substitute into sentences, a property that I will use 
-to represent the notion of different people performing certain actions.%
+of pre-existing types but is instead a new kind of object altogether. To define a subject, it suffices
+to declare a new type to represent a subject without specifying any of its complex properties, such as the idea that a subject
+must be rational or human. Instead of providing a complete definition of subject, which would require wading into murky
+philosophical debates about the nature of agency, I will provide a ``thin'' definition which includes
+only the minimum necessary properties to apply the FUL. Throughout my project, I will use bare syntactic units like types and constants
+to define new ideas and will add thin definitions to achieve the desired results.
+
+In this interpretation, it suffices to make the defining feature of a subject that it can act. 
+I represent that below by allowing subjects to substitute into sentences, a property that I will use 
+to represent the idea that different people can perform the same actions.%
 \end{isamarkuptext}\isamarkuptrue%
 \isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
-\ os\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}s\ {\isasymRightarrow}\ t{\isacharparenright}{\isachardoublequoteclose}\ %
+\ os\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}s\ {\isasymRightarrow}\ t{\isacharparenright}{\isachardoublequoteclose}\ \isanewline
+%
 \isamarkupcmt{To model the idea of a subject being substituted into an action, I 
 define \texttt{type\_synonym} $os$ for an open sentence. An open sentence takes as input a subject and 
-returns a complete or ``closed'' DDL formula by, binding the free variable in the sentence to the input. 
+returns a complete or ``closed'' DDL formula by binding the free variable in the sentence to the input. 
 For example, ``runs'' is an open sentence that can be instantiated with subject, ``Sara'' to create
-the DDL term ``Sara runs,'' which can be true or false at a world. An open sentence itself is not
-the kind of thing that can be true or false at a world, so it is not truth-apt, but when an action is 
+the DDL term ``Sara runs,'' which can be true or false at a world. An open sentence itself is not truth-apt,
+ot the kind of thing that can be true or false at a world. When an action is 
 substituted into an open sentence, the resulting term is truth apt. ``Runs'' is not the kind of thing 
@@
 the Formula of Universal, which reads ``act only according to that maxim by which you can at the same 
-time will that it should become a universal law'' \cite{groundwork}. In order to faithfully formalize
-the FUL, I must make precise the notions of of ``willing a maxim'' and violating the FUL. I draw on 
+time will that it should become a universal law'' \citep{groundwork}. In order to faithfully formalize
+the FUL, I must make precise what it means to will a maxim and violate the FUL. I draw on 
 reliable definitions of willing, maxims, and the FUL from Kantian literature and represent them in DDL.
+Throughout this section, I will use one of Kant's most famous maxims as an example to demonstrate
+my formalization.
+
+\begin{example}[False Promising]\label{falsepromise}
+  The false promising example maxim reads, ``When I am broke, I wil falsely promise to repay a loan 
+to get some easy cash.''
+\end{example}
 
 The central unit of evaluation for Kantian ethics is a ``maxim,'' which Kant defines as ``the subjective 
-principle of willing,'' or the principle that the agent understands themselves as acting on \cite{groundwork}. 
+principle of willing,'' or the principle that the agent understands themselves as acting on \citep{groundwork}. 
 Modern Kantians differ in their interpretations of this definition. I adopt O'Neill's view, derived from 
@@
 and is thus inherently purposive \citep[4:428]{groundwork}. A rational will does not act randomly (else it would not be rational), 
-but instead in the pursuit of ends which it deems valuable\footnote{Some argue that a maxim should also
-include the agent's motive or motivation and I address this concern in Appendix \ref{maximmotive}.}. The inclusion a maxim's end is essential for the version of the FUL
+but instead in the pursuit of ends which it deems valuable.\footnote{Some argue that a maxim should also
+include the agent's motive or motivation and I address this concern in Appendix \ref{maximmotive}.} The inclusion a maxim's end is essential for the version of the FUL
 that I will implement, explained in Section Practical Contradiction.
@@
 \color{red} SHOULD THIS GO HERE OR IN THE LIMITATIONS SECTION OF THE DISCUSSION
+
 O'Neill's inclusion of circumstances is potentially controversial because it leaves open the question of what qualifies as a 
-relevant circumstance for a particular maxim. This is gives rise to ``the tailoring objection" \citep[217]{whatisamaxim} \footnote{Kitcher
-cites \citet{kantsethicalthought} as offering an example of a false positive due to this objection.}, 
-under which maxims are arbitrarily specified to pass the FUL. For example, the maxim ``When my name is Jane Doe,
-I will lie to get some easy money," is universalizable, but is clearly a false positive. One solution to 
-this problem is to argue that the circumstance ``When my name is Jane Doe" is not morally relevant 
+relevant circumstance for a particular maxim. This is gives rise to ``the tailoring objection", 
+under which maxims are arbitrarily specified to pass the FUL  \citep[217]{whatisamaxim}. \footnote{Kitcher
+cites \citet{kantsethicalthought} as offering an example of a false positive due to this objection.} For example, the maxim ``When my name is Jane Doe
+and I am wearing a purple shirt and it is Tuesday morning, I will murder my boss so I can take their job," 
+is universalizable but is clearly a false positive because we think that murder for professional gain is wrong. 
+One solution to this problem is to argue that the circumstance ``When my name is Jane Doe and I am wearing a 
+purple shirt and it is Tuesday morning" is not morally relevant 
 to the act and goal. This solution requires determining what qualifies as a relevant circumstance.
@@
 relevant. For example, one such attempt could define a moral closeness relation between an action, a 
-goal, and circumstances. This heuristic would define morally relevant circumstance as those that 
+goal, and circumstances. This heuristic would define morally relevant circumstances as those that 
 reach a certain closeness threshhold with the action and the goal. Determining morally relevant
@@
 
-If I will the example maxim above about falsely promising to pay a loan, then whenever I need cash, 
+If I will example \nameref{falsepromise} maxim about falsely promising to pay a loan, then whenever I need cash, 
 I will falsely promise to repay a loan. I can represent this definition using the following Isabelle
@@
 %
-\isamarkupcmt{An agent $s$ wills a maxim iff in the circumstances, $s$ performs the action, or $s$ substituted
+\isamarkupcmt{An agent $s$ wills a maxim if in the circumstances, $s$ performs the action, or $s$ substituted
 into the open sentence $a$ is true. This is an Isabelle \texttt{abbreviation}, which is syntactic
@@
 %
-\isamarkupsubsubsection{Practical Contradiction Interpretation \label{praccon}%
+\isamarkupsubsubsection{Practical Contradiction Interpretation of the FUL \label{praccon}%
 }
@@
 \begin{isamarkuptext}%
-In order to actually evaluate the moral status of a maxim, I must precise the idea of failing
+In order to evaluate the moral status of a maxim, I must precise the idea of failing
 the universalizability test or a non-universalizable maxim.  Kantians debate the correct interpretation of 
@@
 imagining a world in which everyone has willed the maxim. If willing the maxim in such a world 
-generates a contradiction, then the action is prohibited.
+generates a contradiction, then the action is prohibited. In the case of the example maxim about 
+lying to
 
@@
 from it, and is thus making an exception of themselves. The test formalizes the kinds of objections 
-that the question ``what if everyone did that?'' seeks to draw out.
+that the question ``What if everyone did that?'' seeks to draw out.
 
@@
 specified the model any further. This represents Lewis's idea of "comparative similarity,"  where 
-a counterfactual is true if it holds at the most similar world \cite{lewiscounterfactuals}. 
+a counterfactual is true if it holds at the most similar world \citep{lewiscounterfactuals}. 
 In our case, this is just the world where everything is the same except the maxim is not acted on.
 Combining these ideas, this definition of effective states that a maxim is effective if the 
-maxim being acted on by a subject is the necessary and sufficient cause of the goal.%
+maxim being acted on by a subject is the necessary and sufficient cause of the goal.
+
+Next, I define what it means for a maxim to be universalized. Recall that the universalizability 
+test requires imagining a world in which everyone wills a maxim. Therefore, a maxim is universalized
+when everyone wills the maxim.
+
+\begin{definition}[Universalized]
+  For a maxim $M$ and agent $s$,
+
+  $$\text{\emph{universalized}} \, M  \equiv \forall w \, (\forall p \, \text{\emph{will}} \, M \, p)$$
+\end{definition}
+
+I can once again represent this as an abbreviation in Isabelle.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 {\isachardoublequoteopen}universalized\ {\isasymequiv}\ {\isasymlambda}M{\isachardot}\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ {\isacharparenleft}W\ M\ p{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ holds{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}t{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
-{\isachardoublequoteopen}holds\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}{\isachardot}\ c{\isachardoublequoteclose}\isanewline
-\isanewline
+%
+\isamarkupcmt{The abbreviation $universalized$ takes a maxim as input and returns a term which is true at a world 
+if all people at that world will the maxim.%
+}\isanewline
+%
+\begin{isamarkuptext}%
+With the above definitions of effective and universalization, I can define what it means for 
+a maxim to not be universalizable. This is the core of the FUL; it states that if a maxim is not 
+universalizable, it is prohibited. The practical contradiction interpretation states that a  maxim is 
+not universalizable if, when universalized, it is no longer effective.
+
+\begin{definition}[Not Universalizable]
+For a maxim $M$ and agent $s$,
+
+$$not\_universalizable \, M \, s  \equiv [ \text{\emph{universalized}} M \longrightarrow \neg \, \text{\emph{effective}} \, M \, s ]$$
+
+A maxim is not universalizable when, if everyone wills the maxim, then it is no longer effective.
+\end{definition}
+
+I implement this definition in Isabelle using another abbreviaion.%
+\end{isamarkuptext}\isamarkuptrue%
 \isacommand{abbreviation}\isamarkupfalse%
@@
 %
-\isamarkupcmt{The formula above reads ``at world $w$, if M is universalized and M is acted on (i.e. the circumstances 
-of M hold), then M is not effective." 
-Notice that the antecedent specifies that the circumstances hold at the given world. 
-When evaluating if a maxim is universalizable or not, we want to ignore worlds where the circumstance 
-do not hold. At these worlds, the maxim is trivially effective and thus trivially universalizable. If we didn't exclude such worlds from 
-consideration, a maxim with circumstances that ever fail to hold would be universalizable. Clearly 
-this is not a desirable conclusion, since maxims like ``When you need money, lie to get easy money"
-would be universalizable.%
-}%
-\begin{isamarkuptext}%
-As before, the concepts of prohibition and permissibility will be helpful here. The unit of 
-evaluation for my formalization of the FUL is the act of willing a maxim, which entails performing 
-the maxim's act in the relevant circumstances. Therefore, I will say that, just as the act of willing a
- maxim can be obligatory for a subject, it can be prohibited or permissible for a subject.\footnote{In 
-the rest of this section, for convenience, I will use the phrase ``subject s willing maxim M is obligatory" 
+\isamarkupcmt{The formula above reads ``at world $w$, if M is universalized, then M is not effective.''%
+}%
+\begin{isamarkuptext}%
+The final set of definitions necessary to implement the FUL are obligation, permissibility, 
+and prohibition. To judge an action, my system evaluates the moral status of the action 
+``person $s$ wills maxim $M$.'' This action can be obligated, prohibited, or permissible.
+I will use the phrase ``subject s willing maxim M is obligatory" 
 interchangeably with ``maxim M is obligatory for subject s." I will use ``maxim M is obligatory" to 
-refer to M being obligatory for any arbitrary subject, which I will show to be equivalent to M being 
-obligatory for a specific subject.}%
+refer to M being obligatory for any arbitrary subject, which I is equivalent to M being 
+obligatory for a specific subject.\footnote{The full proof for this result is in Appendix Extra Tests}.
+
+\begin{definition}[Obligation]
+
+Let maxim $M$ be composed of the circumstances, act, goal tuple $C, A, G$ and let $s$ be an arbitrary agent.
+
+$$obligated \, M \, s \equiv O\{ will \, (C, A, G) \, s \, | \, C\}$$
+
+\end{definition}
+
+The action ``$s$ wills $M$'' is the first argument passed to the dyadic obligation operator and is 
+thus the action that is shown to be obligated or not. The second argument passed to the obligation 
+operator represents the context in which the obligation holds and is thus naturally the maxim's circumstances.
+This definition does not require any additional syntactic sugar, since it merely uses the dyadic obligation
+operator in a clever way. Using this definition, I can define prohibition and permissibility.
+
+\begin{definition}[Prohibition and Permissibility] Let maxim $M$ be composed of the circumstances, act, 
+goal tuple $C, A, G$ and let $s$ be an arbitrary agent.\footnote{Technically, a maxim is not a boolean 
+type, so the term $\neg M$ is not type correct. The expression $obligated \, \neg M$ merely provides 
+intuition for the meaning of prohibition, but the exact definition is given by 
+$O\{ \neg will \, (C, A, G) \, s \, | \, C\}$.}
+
+\newcommand*{\approxident}{%
+  \mathrel{\vcenter{\offinterlineskip
+  \hbox{$\sim$}\vskip-.35ex\hbox{$\sim$}\vskip-.35ex\hbox{$\sim$}}}}
+
+$$ prohibited \, M \, s \approxident obligated \, \neg M \, \equiv O\{ \neg will \, (C, A, G) \, s \, | \, C\}$$
+
+$$permissible \, M \, s \equiv \neg prohibited \, M \, s \equiv \neg O\{ \neg will \, (C, A, G) \, s \, | \, C\}$$
+
+\end{definition}
+
+Once again, I represent these definitions as abbreviations in Isabelle.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 {\isachardoublequoteopen}prohibited\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isachardot}\ O{\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}will\ {\isacharparenleft}c{\isacharcomma}a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ {\isacharbar}\ c{\isacharbraceright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{A maxim is prohibited for a subject $s$ if its negation is obligated for $s$. It is morally wrong 
+for an agent to will a prohibited maxim.%
+}\isanewline
 \isanewline
@@
 %
-\isamarkupcmt{I will say that a maxim is permissible for a subject if it is not prohibited for that subject to 
-will that maxim.%
-}%
-\begin{isamarkuptext}%
-When analyzing the naive formalization and Kroy's formalization, I learned that DDL and the prior 
-formalizations allow contradictory obligations. This is a major weakness of these systems, and my 
-formalization should fix this. To do so, I will add as an axiom the idea that obligations cannot 
-contradict each other or their internal circumstances. Formally, conflicting obligations are defined below.%
+\isamarkupcmt{A maxim is permissible for a subject $s$ if it is not prohibited for $s$. It is morally acceptable 
+for an agent to will or not will a permissible maxim.%
+}%
+\begin{isamarkuptext}%
+One additional piece of logical background necessary before I implement the FUL is the 
+notion of contradictory obligations. Many deontic logics, including DDL, allow contradictory
+obligations. As I will explain in Section Tests, Kantian ethics never prescribes contradictory
+obligations, so I will add this as an axiom.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupcmt{Terms A and B are non contradictory in circumstances c if, when A and B are obligated in circumstances 
-c, the conjunction of A, B, and c, does not imply False.%
+\isamarkupcmt{Terms $A$ and $B$ are non contradictory in circumstances $c$ if, when $A$ and $B$ are obligated in circumstances 
+$c$, the conjunction of $A$, $B$, and $c$, does not imply $False$.%
 }\isanewline
@@
 %
-\isamarkupcmt{This axiom formalizes the idea that, for any terms A, B, and circumstances c, A and B must be 
-non-contradictory in circumstances c at all worlds. Intuitively, this axiom requires that obligations 
+\isamarkupcmt{This axiom formalizes the idea that, for any terms $A$, $B$, and circumstances $c$, $A$, and $B$ must be 
+non-contradictory in circumstances $c$ at all worlds. Intuitively, this axiom requires that obligations 
 do not conflict.%
@@
 %
-\isamarkupsubsection{Formalizing the FUL%
+\isamarkupsubsubsection{Formalizing the FUL%
 }
@@
 \begin{isamarkuptext}%
-Below is my first attempt at formalizing Korgsaard's definition of the practical contradiction
-interpretation:  a maxim is not universalizable 
-if, in the world where the maxim becomes the standard practice (i.e. everyone acts on the maxim), the
-agent's attempt to use the maxim's act to achieve the maxim's goal is frustrated. In other words, if 
-the maxim is universally willed (captured by applying a universal qunatifier and the will function 
-to the maxim on the LHS), then it is no longer effective for the subject $s$ (RHS above).%
+With this logical background, I can begin to implement the Formula of Universal Law, as defined 
+by the practical contradiction interpretation, which states that a maxim is prohibited if it is ineffective
+when universalized. A first attempt to formalize the FUL simply translates this into Isabelle's syntax
+using the abbreviations above.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 universalizable (as defined above), then, at all worlds, in those circumstances, the subject 
-is prohibited (obligated not to) from willing the maxim.%
-}\isanewline
-\isanewline
+is prohibited (obligated not to) from willing the maxim.''%
+}%
+\begin{isamarkuptext}%
+I can immediately determine if this version of the FUL is sensical by checking if it is consistent.
+If \texttt{FUL0} implies False, then it is inconsistent.%
+\end{isamarkuptext}\isamarkuptrue%
 \isacommand{lemma}\isamarkupfalse%
@@
 \begin{isamarkuptext}%
-FUL0 is not consistent, and sledgehammer is able to prove this by showing that it implies a contradiction 
-usig axiom O\_diamond, which is \isa{{\isasymTurnstile}{\isasymlambda}w{\isachardot}\ ob\ {\isacharquery}B\ {\isacharquery}A\ {\isasymlongrightarrow}\ {\isasymnot}\ {\isasymTurnstile}\isactrlbold {\isasymnot}\ {\isacharquery}B\isactrlbold {\isasymand}{\isacharquery}A}.
-This axiom captures
-the idea that an obligation can't contradict its context. This is particularly problematic if the goal or 
-action of a maxim are equivalent to its circumstances. In other words, if the maxim has already been 
+FUL0 is not consistent, and Isabelle's proof-finding tool, Sledgehammer, is able to prove this by showing that it implies a contradiction 
+usig axiom \texttt{O\_diamond}\footnote{The full axiom reads \isa{{\isasymTurnstile}{\isasymlambda}w{\isachardot}\ ob\ {\isacharquery}B\ {\isacharquery}A\ {\isasymlongrightarrow}\ {\isasymnot}\ {\isasymTurnstile}\isactrlbold {\isasymnot}\ {\isacharquery}B\isactrlbold {\isasymand}{\isacharquery}A}.} \citep{sledgehammer}.
+This axiom captures the idea that an obligation can't contradict its context. This is particularly problematic 
+if the goal or action of a maxim are equivalent to its circumstances. In other words, if the maxim has already been 
 acted on or the goal has already been achieved, then prohibiting it is impossible. 
@@
 
-To get around this, I will exclude what I call ``badly formed maxims," which are those maxims such that the goal has already been 
-achieved or the act has already been acted on. Under my formalization, such maxims are 
-not well-formed. To understand why, I return to Korsgaard's and O'Neill's interpretations of a maxim as a practical
-guide to action. A maxim is a practical principle that guides how we behave in everyday life. A 
-principle of the form ``When you are eating breakfast, eat breakfast in order to eat breakfast," is not 
-practically relevant. No agent would ever need to act on such a principle. It is not contradictory
-or prohibited, but it is the wrong kind of question to be asking. It is not a 
-well-formed maxim, so the categorical imperative does not apply to it. (more explanation in philosophical 
-writing collection)%
+This motivates the exclusion of what I call ``badly formed maxims," which are those maxims such that 
+the goal has already been achieved or the act has already been acted on. Under my formalization, such maxims are
+not well-formed.
+
+\begin{definition}[Well-Formed Maxim]
+A maxim is well-formed if the circumstances do not contain the act and goal. For a maxim $(C, A, G)$, and subject $s$, 
+$$ \text{\emph{well\_formed}} \, (C, A, G) \, s \equiv \forall w \, (\neg (C \longrightarrow G) \wedge \neg (C \longrightarrow A \, s)) \, w$$
+
+\end{definition}
+
+For example, the maxim ``When I eat breakfast, I will eat breakfast to eat breakfast'' is not well-formed 
+because the circumstance ``when I eat breakfast'' contains the act and goal. Well-formedness is not 
+discussed in the literature, but if I require that the FUL only holds for well-formed maxim, it will now
+be consistent.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 already achieved in the circumstances and the subject cannot have already performed the act.%
-}\isanewline
-\isanewline
+}%
+\begin{isamarkuptext}%
+If I modify \texttt{FUL0} to only hold for well-formed maxims, it becomes consistent.%
+\end{isamarkuptext}\isamarkuptrue%
 \isacommand{abbreviation}\isamarkupfalse%
@@
 %
-\isamarkupcmt{Let's try the exact same formalization of the FUL as above, except that it only applies to 
-maxims that are well-formed at every world.%
+\isamarkupcmt{This formalization states that if a maxim is well-formed, then if it is not universalizable, 
+it is prohibited.%
 }\isanewline
@@
 \ \ \isacommand{nitpick}\isamarkupfalse%
-{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}true{\isacharbrackright}%
+{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharbrackright}%
 \isadelimproof
@@
 %
-\isamarkupcmt{The FUL does not hold in DDL, because nitpick is able to find a model for my system in which it is 
-false. If the FUL were already a theorem of the system, adding it wouldn't make the system any more 
-powerful, so this is the desired result.
-
-$\color{blue}$ Nitpick found a counterexample for card s = 1 and card i = 1:
-
-  Skolem constants:
-    M = (($\lambda x. \_$)($i_1$ := True), ($\lambda x. \_$)($s_1$ := ($\lambda x. \_$)($i_1$ := False)), ($\lambda x. \_$)
-         ($i_1$ := False))
-    $\lambda$ w. p = ($\lambda x. \_$)($i_1$ := $s_1$)
-    s = $s_1$ $\color{black}$%
+\isamarkupcmt{Nitpick is Isabelle's countermodel checker, and I can use it to quickly check that an axiom is 
+consistent \citep{nitpick}. If Nitpick can find a model in which the axioms of DDL hold and the FUL is 
+true then it is consistent.
+$\color{blue}$ Nitpick found a model for card $i$ = 1 and card $s$ = 2:
+
+  Empty assignment $\color{black}$%
 }%
@@
 \endisadelimproof
+%
+\begin{isamarkuptext}%
+Above, I used Isabelle and my logic to show that if the FUL holds for badly formed maxims then 
+it is inconsistent. This is not just a logical property of my system, but it also has philosophical
+significance that coheres with Korsgaard's and O'Neill's interpretations of a maxim as a practical
+guide to action \citep{actingforareason,actingonprinciple}. A maxim is a practical principle that guides how we behave in everyday life. A 
+principle of the form ``When you are eating breakfast, eat breakfast in order to eat breakfast,'' is not 
+practically relevant. No agent would ever need to act on such a principle. It is neither contradictory
+nor prohibited, and it is the wrong kind of question to be asking. It is not a 
+well-formed maxim, so the categorical imperative cannot apply to it.
+
+The fact that Isabelle revealed a philosophical insight about which kinds of maxims are well-formed
+enough to evaluate using the categorical imperative is an example of the power of computational tools to aid
+philosophical progress. Nitpick and Sledgehammer helped me confirm that certain kinds
+of circumstance, act, goal tuples are too badly formed for the categorical imperative to logically 
+apply to them. The realization of this subtle problem would have been incredibly difficult without 
+computational tools, and serves as evidence of the power of computational ethics. I discuss the philosophical
+properties and implications of well-formed maxims and the power of computational ethics further in
+Chapter Discussion in Section Computational Ethics.
+
+Now that I have a consistent version of the FUL, I can complete my implementation by adding it as an axiom.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{axiomatization}\isamarkupfalse%
+\ \isakeyword{where}\ FUL{\isacharcolon}FUL%
+\begin{isamarkuptext}%
+This concludes my implementation of the Formula of Universal Law in Isabelle/HOL. My implementation
+consistents of necessary logical background, first formalized in DDL and then implemented in Isabelle.
+The code snippets in this chapter are a subset of the over 100 lines of Isabelle/HOL code necessary to
+complete this implementation. In Section \nameref{testing} and Chapter Applications, I demonstrate how this
+implementation can be tested and used to make moral judgements.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsection{Tests\label{testing}%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
+In addition to an implementation of automated Kantian ethics, I also contribute a testing framework 
+to evaluate how well my implementation coheres with philosophical literature. This testing architecture 
+makes the notion of ``philosophical faithfulness'' precise. Each test consists of a sentence in my logic 
+and an expected outcome, where the possible outcomes are proving or refuting the sentence. For example, 
+one such sentence is that obligations cannot contradict each other. To run the tests, I attempt to
+ prove or refute each test sentence in my logic.  Because these tests are derived from moral 
+intuition and philosophical literature, they evaluate how reliable my system is.
+
+The test framework can be expanded by adding more test sentences. This test framework can also guide 
+implementations of other parts of Kantian ethics or other ethical theories. As I was implementing my 
+formalization, I checked it against the testing framework, performing test-driven development automated 
+ethics. Running the tests on my implementation alone consisted of approximately 400 lines of Isabelle code.
+
+I use my testing framework to show that my formalization and implementation of Kantian ethics outperforms 
+raw DDL with no other axioms added (a control group) and Kroy's prior attempt at formalizing 
+(but not implementing) the FUL, which I implement\footnote{I present the complete implementation in 
+Appendix \nameref{kroy_appendix}} in Isabelle \citep{kroy}. My implementation outperforms 
+both other implementations. Full test results are summarized in Figure \ref{table}. Below, I briefly 
+explain some noable tests.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{figure}
+\centering
+\includegraphics[scale=0.4]{goalstable.png}
+\caption{Table showing which tests each implementation passes. The naive interpretation is raw DDL, 
+Kroy is based on Moshe Kroy's formalization of the FUL, and the custom formalization is my novel implementation.} \label{table}
+\end{figure}
+%
+\begin{isamarkuptext}%
+\textbf{FUL Stronger than DDL} The FUL should not hold in raw DDL, which I use a control group. 
+If the FUL holds in the base logic, then adding it as an axiom doesn't make the logic any stronger, 
+which is troubling because the base logic does not come equipped with the categorical imperative built-in. It 
+defines basic properties of obligation, such as ought implies can, but contains no axioms that represent
+the formula of universal law. Therefore, if a formalization of the FUL holds in the 
+base logic, then it is too weak to actually represent the FUL. Both Kroy's formalization
+and my implementation do not hold in the base logic, and thus represent some progress over the control group.
+To test this property, I used Nitpick to find a countermodel in which my version of the FUL does not hold. 
+I performed this test before adding the FUL as an axiom, since after adding it no countermodel will
+be possible.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+\medskip
+\noindent \textbf{Obligation Universalizes Across People} The obligations prescribed by the Formula of Universal Law
+should generalize across people. In other words, if a maxim is obligated for one person, it is obligated
+for all other people because maxims are not person-specific. Velleman argues that, because 
+reason is accessible to everyone identically, obligations apply to all people equually \citep[25]{velleman}. 
+When Kant describes the categorical imperative as the objective principle of the will, he is referring 
+to the fact that, as opposed to a subjective principle, the categorical imperative applies to all 
+rational agents equally \citep[16]{groundwork}. At its core, the FUL best handles, ``the temptation 
+to make oneself an exception: selfishness, meanness, advantagetaking, and disregard for the rights 
+of others'' \citep[30]{KorsgaardFUL}. Kroy makes this property the center of his
+formalization, which essentially says that if an act is permissible for someone, it is permissible for 
+everyone.\footnote{Formally, $P\{A(s)\} \longrightarrow \forall p. P\{A(p)\}$} Kroy's interpretation and 
+my interpretation satisfy this property, but the naive interpretation does not. Below I show how I 
+ran this test for my interpreation.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ wrong{\isacharunderscore}if{\isacharunderscore}wrong{\isacharunderscore}for{\isacharunderscore}someone{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}w{\isachardot}\ {\isasymforall}c{\isacharcolon}{\isacharcolon}t{\isachardot}\ {\isasymforall}g{\isacharcolon}{\isacharcolon}t{\isachardot}\ {\isasymforall}a{\isachardot}\ {\isasymexists}s{\isacharcolon}{\isacharcolon}s{\isachardot}\ O{\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ {\isacharbar}\ c{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ \ O{\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ p{\isacharparenright}\ {\isacharbar}\ c{\isacharbraceright}\ w{\isacharparenright}\ {\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{by}\isamarkupfalse%
+\ blast\isanewline
+%
+\isamarkupcmt{This lemma shows that if a maxim (c, a, g) is wrong for subject $s$ at a world, then it is wrong
+for all people at $s$. Isabelle automatically completed this proof using the \texttt{blast} method, 
+which implements a generic tableau prover, a proof method that operates on lists of formulae using 
+rules for conjunction, disjunction, universal quantification, and existential quantification \citep{blast}.%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
 \isanewline
-\isanewline
-\isacommand{axiomatization}\isamarkupfalse%
-\ \isakeyword{where}\ FUL{\isacharcolon}FUL\isanewline
+%
+\endisadelimproof
 \isanewline
 \isacommand{lemma}\isamarkupfalse%
-\ True\isanewline
-\ \ \isacommand{nitpick}\isamarkupfalse%
-{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharbrackright}%
-\isadelimproof
-\ %
+\ right{\isacharunderscore}if{\isacharunderscore}right{\isacharunderscore}for{\isacharunderscore}someone{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}w{\isachardot}\ {\isasymforall}c{\isacharcolon}{\isacharcolon}t{\isachardot}\ {\isasymforall}g{\isacharcolon}{\isacharcolon}t{\isachardot}\ {\isasymexists}s{\isacharcolon}{\isacharcolon}s{\isachardot}\ O{\isacharbraceleft}W\ {\isacharparenleft}c{\isacharcomma}\ M{\isacharcomma}\ g{\isacharparenright}\ s\ {\isacharbar}\ c{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ \ O{\isacharbraceleft}W\ {\isacharparenleft}c{\isacharcomma}\ M{\isacharcomma}\ g{\isacharparenright}\ p\ {\isacharbar}\ c{\isacharbraceright}\ w{\isacharparenright}\ {\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{by}\isamarkupfalse%
+\ blast\isanewline
+%
+\isamarkupcmt{This lemma shows that if a maxim (c, a, g) is right for subject $s$ at a world, then it is wrong
+for all people at $s$. The proof similarly proceeds using \texttt{blast}. I represent my tests as 
+lemmas, that I expect Isabelle to either prove or refute. The statement following the keyword \texttt{shows}
+is the sentence of the lemma, and the proof follows the \texttt{by} keyword.%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+\noindent \textbf{Contradictory Obligations} DDL itself allows contradictory obligations, but contradictory obligations
+make obeying the prescriptions of an ethical theory impossible.
+Kant subscribes to the general, popular view that morality is supposed to guide action, so ought implies 
+can\footnote{Kohl points out that this principle is referred to as 
+Kant's dictum or Kant's law in the literature \citep[footnote 1]{kohl}.}. Kohl reconstructs his argument for the principle as 
+follows: if the will cannot comply with the moral law, then the moral law has no prescriptive authority 
+for the will \citep[703-4]{kohl}. This defeats the purpose of Kant's theory, which is to develop an unconditional, categorical imperative 
+for rational agents. Ought implies can requires that obligations never contradict, because an agent 
+can't perform contradictory actions. Therefore, any ethical theory that respects ought implies can, 
+and Kantian ethics in particular, must not result in conflicting obligations. 
+Kant only briefly discusses contradictory obligations in \emph{Metaphysics of Morals}, where he argues that 
+conflicting moral obligations are impossible under his theory \citep[V224]{metaphysicsintro}. Particularly, the categorical imperative generates 
+``strict negative laws of omission,'' which cannot conflict by definition \citep[45]{timmerman}.\footnote{The 
+kinds of obligations generated by the FUL are called ``perfect duties'' which arise from ``contradictions 
+in conception,'' or maxims that we cannot even concieve of universalizing. These duties are always negative 
+and thus never conflict. Kant also presents ``imperfect duties,'' generated from ``contradictions in will,''
+or maxims that we can concieve of universalizing but would never want to. These duties tend to be broader, 
+such as ``improve oneself" or "help others," and are secondary to perfect duties. My project only analyzes 
+perfect duties, as these are always stronger than imperfect duties.} Both the naive formalization and 
+Kroy's formalization allow contradictory obligations, but I explicitly add an axiom to my formalization
+that prohibits contradictory obligations.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ conflicting{\isacharunderscore}obligations{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymnot}\ {\isacharparenleft}O{\isacharbraceleft}W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharbar}c{\isacharbraceright}\ \isactrlbold {\isasymand}\ O{\isacharbraceleft}\isactrlbold {\isasymnot}{\isacharparenleft}W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}{\isacharbar}\ c{\isacharbraceright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{using}\isamarkupfalse%
+\ no{\isacharunderscore}contradictions\ \isacommand{by}\isamarkupfalse%
+\ blast\isanewline
+%
+\isamarkupcmt{This test passes immediately by the new axiom that prohibits contradictory obligations.%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+\isanewline
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ implied{\isacharunderscore}contradiction{\isacharcolon}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}{\isacharparenleft}W\ {\isacharparenleft}c{\isadigit{1}}{\isacharcomma}\ a{\isadigit{1}}{\isacharcomma}\ g{\isadigit{1}}{\isacharparenright}\ s{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}W\ {\isacharparenleft}c{\isadigit{2}}{\isacharcomma}\ a{\isadigit{2}}{\isacharcomma}\ g{\isadigit{2}}{\isacharparenright}\ s{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbottom}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}\isactrlbold {\isasymnot}\ {\isacharparenleft}O{\isacharbraceleft}W{\isacharparenleft}c{\isadigit{1}}{\isacharcomma}\ a{\isadigit{1}}{\isacharcomma}\ g{\isadigit{1}}{\isacharparenright}\ s{\isacharbar}c{\isacharbraceright}\ \isactrlbold {\isasymand}\ O{\isacharbraceleft}W{\isacharparenleft}c{\isadigit{2}}{\isacharcomma}\ a{\isadigit{2}}{\isacharcomma}\ g{\isadigit{2}}{\isacharparenright}\ s{\isacharbar}c{\isacharbraceright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{using}\isamarkupfalse%
+\ assms\ no{\isacharunderscore}contradictions\ \isacommand{by}\isamarkupfalse%
+\ blast\isanewline
+%
+\isamarkupcmt{This stronger property states that the combination of obligatory maxims can't
+ imply a contradiction and should hold for the same reasons that contradictory obligations aren't
+allowed. The added axiom also makes this test pass.%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+During testing, I also realized that contradictory obligations are closely related to two other properties
+that also fail in both prior attempts. First is the idea that obligation implies permissibility, or 
+that obligation is a stronger property than permissibility. If there are no contradictory obligations, 
+then this property holds because actions are either permissible or prohibited and obligation contradicts
+prohibition. Moreover, in a system with contradictory obligations, this property fails because there is some
+A that is obligated but also prohibited and therefore not permisible. Formalizing this property below shows 
+that this follows from the definition of implication in propositional logic.
+
+\medskip%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}{\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymand}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymnot}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}A{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
 \endisadelimproof
@@
 %
-\isamarkupcmt{Nitpick is able to find a model in which all axioms are satisfied, 
-so this version of the FUL is consistent.
-
-$\color{blue}$ Nitpick found a model for card i = 1 and card s = 1:
-
-  Empty assignment $\color{black}$%
+\isamarkupcmt{\texttt{simp} is the simplification tactic, which unfolds definitions to complete a proof. The 
+left-hand side states that $A$ is both obligated and prohibited, and is equivalent to the right-hand side, 
+which states that $A$ is obligated but not permissible.%
 }%
@@
 \begin{isamarkuptext}%
-During the process of making FUL0 consistent, I used Isabelle to gain philosophical insights 
-about vacuous maxims. This process is an example of the power of computational tools to aid
-philosophical progress. I used Nitpick and Sledgehammer to quickly test if a small tweak 
-to FUL0 fixed the inconsistency or if I was still able to derive a contradiction.  I then realized that if 
-I defined the circumstances, act, and goal as constants, then FUL0 was indeed consistent. After some 
-experimentation, Prof. Amin correctly pointed out that as constants, these three entities were 
-distinct. However, when merely quantifying over (c, a, g), all members of a tuple could be equivalent. Within
-a minute, I could formalize this notion, add it to FUL0, and test if it solved the problem. The fact 
-that it did spurred my philosophical insight about vacuous maxims.
-
-The logic confirmed that certain kinds
-of circumstance, act, goal tuples are too badly formed for the categorical imperative to logically 
-apply to them. The realization of this subtle problem would have been incredibly difficult without 
-computational tools. The syntax and typing of Isabelle/HOL forced me to bind the free-variable $M$
-in the FUL in different ways and allowed me to quickly test many bindings. The discovery of this 
-logical inconsistency then enabled a philosophical insight about which kinds of maxims make sense as 
-practical principles. This is one way to do computational ethics: model a system in a logic, use 
-computational tools to refine and debug the logic, and then use insights about the logic to derive 
-insights about the ethical phenonema it is modelling. This procedure parallels the use of proofs in 
-theoretical math to understand the mathematical objects they model.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-One potential problem with my formalization is that it does not use the modal nature of the system. 
-All of the properties that the FUL investigates hold at all worlds, in effect removing the modal nature 
-of the system. This approach simplifies logical and therefore computational complexity, improving 
-performance. On the other hand, it doesn't use the full expressivity of DDL. If I run into problems 
-later on, one option is to tweak the FUL to use this expressivity.%
-\end{isamarkuptext}\isamarkuptrue%
+\noindent \textbf{Distributive Property} Another property related to contradictory obligations is the distributive property for the obligation
+operator.\footnote{Formally, $O\{A\} \wedge O\{B\} \longleftrightarrow O\{A \wedge B\}$.} This is 
+another property that we expect to hold. The rough English translation of  $O \{ A \wedge B \} $ is ``you are obligated to 
+do both A and B". The rough English translation of $O\{A\} \wedge O\{B\}$ is ``you are obligated to do A 
+and you are obligated to do B." We think those English sentences mean the same thing, so they should mean 
+the same thing in logic as well. Moreover, if that (rather intuitive) property holds, then contradictory
+obligations are impossible, as shown in the below proof.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ distributive{\isacharunderscore}implies{\isacharunderscore}no{\isacharunderscore}contradictions{\isacharcolon}\ \isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}A\ B{\isachardot}\ {\isasymTurnstile}\ {\isacharparenleft}{\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymand}\ O\ {\isacharbraceleft}B{\isacharbraceright}{\isacharparenright}\ \isactrlbold {\isasymequiv}\ O\ {\isacharbraceleft}A\ \isactrlbold {\isasymand}\ B{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}A{\isachardot}\ {\isasymTurnstile}{\isacharparenleft}\ \isactrlbold {\isasymnot}{\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymand}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ {\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{using}\isamarkupfalse%
+\ O{\isacharunderscore}diamond\ assms\ \isacommand{by}\isamarkupfalse%
+\ blast\isanewline
+%
+\isamarkupcmt{The \texttt{assumes} keyword indicates assumptions used when proving a lemma. I use it here to 
+capture the idea of metalogical implication. With the assumption, the lemma above reads, ``If the distributive
+property holds in this logic, then obligations cannot contradict."%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+Again, this test fails in the naive formalization and for Kroy's formalization, but
+passes for my interpretation because I require that obligations don't contradict as an axiom.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ distribution{\isacharcolon}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymand}\ O\ {\isacharbraceleft}B{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymTurnstile}\ O\ {\isacharbraceleft}A\ \isactrlbold {\isasymand}\ B{\isacharbraceright}{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{using}\isamarkupfalse%
+\ assms\ no{\isacharunderscore}contradictions\ \isacommand{by}\isamarkupfalse%
+\ fastforce\isanewline
+%
+\isamarkupcmt{Once again, the proof proceeds almost immediately using the new axiom.%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+\medskip
+
+\noindent \textbf{Un-universalizable Actions} Recall that under 
+the logical contradiction interpretation of the Formula of Universal Law, it prohibits lying because, in a world 
+where everyone simultaneously lies, lying is impossible. In other words, not everyone can simultaneously
+lie because the institution of lying and believing would break down. In Section \nameref{praccon}, 
+I recreated Korsgaard's argument for why the logical contradiction interpretation is weaker than what the
+Formula of Universal Law should actually require. Therefore, any implementation of the FUL should be 
+able to show that the actions prohibited by the logical contradiction interpretation are prohibited, 
+because the actions prohibited by the practical contradiction interpretation are a superset of these.
+The FUL should show that actions that cannot possibly be universalized are prohibited, because those acts cannot be willed in 
+a world where they are universalized. This property fails to hold in both the naive formalization 
+and Kroy's formalization, but holds for my custom formalization. Showing that this property holds
+for my formalization required significant logical background is presented in Appendix \ref{weirdtests}%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+\noindent \textbf{Maxims} Kant does not evaluate the correctness of acts, but rather of maxims. Therefore, any 
+faithful formalization of the categorical imperative must evaluate maxims, not acts. This requires 
+representing a maxim and making it the input to the obligation operator, which neither of the prior 
+attempts do. Because my implementation includes the notion of a maxim, it is able to perform sophisticated 
+reasoning as demonstrated in Sections \nameref{joking} and \nameref{murderer}. Staying faithful to the philosophical 
+literature enables my system to make more reliable judgements.
+
+\medskip%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+\noindent \textbf{Conventional and Natural Acts} When arguing for the practical contradiction interpretation,
+Korsgaard makes a distinction between conventional and natural acts \citep{KorsgaardFUL}. 
+A conventional act like promising relies on a convention, like the 
+convention that a promise is a commitment, whereas a natural act is possible simply because of the laws 
+of the natural world. It is easier to show the wrongness of conventional acts because there are worlds 
+in which these acts are impossible; namely, worlds in which the convention does not exist. For example, 
+the common argument against falsely promising is that if everyone were to falsely promise, the convention 
+of promising would fall apart because people wouldn't believe each other, so falsely promising is prohibited. 
+It is more difficult to show the wrongness of a natural act, like murder or violence. These acts can 
+never be logically impossible; even if everyone murders or acts violently, murder and violence will 
+still be possible, so it is difficult to show that they violate the FUL.
+
+Both the naive and Kroy's interpretations fail to show the wrongness of conventional or natural acts. 
+My system shows the wrongness of both natural and conventional acts because it is faithful to Korsgaard's 
+practical contradiction interpretation of the FUL, which is the canonical interpretation of the 
+FUL \citep{KorsgaardFUL}. This test passes due to the results shown in Chapter Applications, where I
+use my system to reason about two ethical dilemmas, one which involves conventional acts and the other which
+involves natural acts.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
 %
@@
 %:%40=12%:%
-%:%41=13%:%
-%:%50=15%:%
+%:%49=14%:%
+%:%61=16%:%
 %:%62=17%:%
@@
 %:%64=19%:%
-%:%65=20%:%
-%:%74=22%:%
+%:%73=21%:%
+%:%85=23%:%
 %:%86=24%:%
@@
 %:%89=27%:%
-%:%90=28%:%
-%:%92=30%:%
-%:%93=30%:%
-%:%94=30%:%
+%:%91=29%:%
+%:%92=29%:%
+%:%93=29%:%
+%:%96=31%:%
 %:%97=32%:%
@@
 %:%106=41%:%
-%:%107=42%:%
 %:%108=43%:%
-%:%109=44%:%
-%:%111=46%:%
-%:%112=46%:%
+%:%109=43%:%
+%:%111=44%:%
+%:%112=45%:%
 %:%113=46%:%
@@
 %:%118=51%:%
-%:%119=52%:%
-%:%120=53%:%
-%:%128=55%:%
+%:%126=53%:%
+%:%138=55%:%
+%:%139=56%:%
 %:%140=57%:%
@@
 %:%157=74%:%
-%:%159=77%:%
+%:%158=75%:%
+%:%159=76%:%
 %:%160=77%:%
-%:%162=78%:%
-%:%163=79%:%
-%:%164=80%:%
-%:%165=81%:%
-%:%166=82%:%
+%:%161=78%:%
+%:%162=79%:%
+%:%164=82%:%
+%:%165=82%:%
 %:%167=83%:%
@@
 %:%169=85%:%
-%:%172=87%:%
-%:%173=88%:%
-%:%174=89%:%
-%:%175=90%:%
-%:%176=91%:%
+%:%170=86%:%
+%:%171=87%:%
+%:%172=88%:%
+%:%173=89%:%
+%:%174=90%:%
 %:%177=92%:%
@@
 %:%232=147%:%
+%:%233=148%:%
 %:%234=149%:%
-%:%235=149%:%
-%:%236=150%:%
-%:%238=151%:%
-%:%239=152%:%
-%:%240=153%:%
-%:%241=154%:%
-%:%249=156%:%
-%:%261=158%:%
-%:%262=159%:%
-%:%263=160%:%
-%:%264=161%:%
-%:%265=162%:%
-%:%266=163%:%
-%:%267=164%:%
-%:%268=165%:%
+%:%235=150%:%
+%:%236=151%:%
+%:%237=152%:%
+%:%238=153%:%
+%:%239=154%:%
+%:%240=155%:%
+%:%242=157%:%
+%:%243=157%:%
+%:%244=158%:%
+%:%246=159%:%
+%:%247=160%:%
+%:%248=161%:%
+%:%249=162%:%
+%:%257=164%:%
 %:%269=166%:%
@@
 %:%310=207%:%
-%:%312=210%:%
+%:%311=208%:%
+%:%312=209%:%
 %:%313=210%:%
 %:%314=211%:%
-%:%316=212%:%
-%:%317=213%:%
-%:%320=215%:%
-%:%321=216%:%
-%:%322=217%:%
-%:%323=218%:%
-%:%324=219%:%
-%:%325=220%:%
-%:%326=221%:%
-%:%327=222%:%
-%:%328=223%:%
+%:%315=212%:%
+%:%316=213%:%
+%:%317=214%:%
+%:%318=215%:%
+%:%319=216%:%
+%:%321=219%:%
+%:%322=219%:%
+%:%323=220%:%
+%:%325=221%:%
+%:%326=222%:%
 %:%329=224%:%
 %:%330=225%:%
+%:%331=226%:%
 %:%332=227%:%
-%:%333=227%:%
-%:%334=228%:%
-%:%335=229%:%
-%:%336=230%:%
-%:%337=230%:%
-%:%338=231%:%
-%:%339=232%:%
-%:%340=233%:%
-%:%341=233%:%
-%:%342=234%:%
-%:%344=235%:%
-%:%345=236%:%
-%:%346=237%:%
-%:%347=238%:%
-%:%348=239%:%
-%:%349=240%:%
-%:%350=241%:%
-%:%351=242%:%
-%:%354=244%:%
-%:%355=245%:%
-%:%356=246%:%
-%:%357=247%:%
-%:%358=248%:%
-%:%359=249%:%
-%:%360=250%:%
-%:%361=251%:%
-%:%363=253%:%
-%:%364=253%:%
-%:%365=254%:%
-%:%366=255%:%
-%:%367=256%:%
-%:%368=256%:%
-%:%369=257%:%
-%:%371=258%:%
-%:%372=259%:%
-%:%375=262%:%
-%:%376=263%:%
-%:%377=264%:%
-%:%378=265%:%
-%:%380=267%:%
-%:%381=267%:%
-%:%382=268%:%
-%:%384=269%:%
-%:%385=270%:%
-%:%386=270%:%
-%:%387=271%:%
-%:%388=272%:%
-%:%389=272%:%
-%:%391=273%:%
-%:%392=274%:%
-%:%393=275%:%
-%:%401=277%:%
-%:%413=279%:%
-%:%414=280%:%
-%:%415=281%:%
-%:%416=282%:%
-%:%417=283%:%
-%:%418=284%:%
-%:%420=287%:%
-%:%421=287%:%
-%:%423=288%:%
-%:%424=289%:%
-%:%425=290%:%
-%:%426=291%:%
-%:%427=291%:%
-%:%428=292%:%
-%:%429=293%:%
-%:%430=293%:%
-%:%432=293%:%
-%:%436=293%:%
-%:%437=293%:%
-%:%438=294%:%
-%:%439=294%:%
-%:%440=294%:%
-%:%449=296%:%
-%:%450=297%:%
-%:%451=298%:%
-%:%452=299%:%
-%:%453=300%:%
-%:%454=301%:%
-%:%455=302%:%
-%:%456=303%:%
-%:%457=304%:%
-%:%458=305%:%
-%:%459=306%:%
-%:%460=307%:%
-%:%461=308%:%
-%:%462=309%:%
-%:%463=310%:%
-%:%464=311%:%
-%:%465=312%:%
-%:%467=314%:%
-%:%468=314%:%
-%:%469=315%:%
-%:%471=316%:%
-%:%472=317%:%
-%:%473=317%:%
-%:%474=318%:%
-%:%475=319%:%
-%:%476=319%:%
-%:%477=320%:%
-%:%479=321%:%
-%:%480=322%:%
-%:%481=322%:%
-%:%482=323%:%
-%:%483=324%:%
-%:%484=324%:%
-%:%485=325%:%
-%:%486=325%:%
-%:%488=325%:%
-%:%492=325%:%
-%:%493=325%:%
-%:%495=326%:%
-%:%496=327%:%
-%:%497=328%:%
-%:%498=329%:%
-%:%499=330%:%
-%:%500=331%:%
-%:%501=332%:%
-%:%502=333%:%
-%:%503=334%:%
-%:%504=335%:%
-%:%505=336%:%
-%:%513=336%:%
-%:%514=337%:%
-%:%515=338%:%
-%:%516=338%:%
-%:%517=339%:%
-%:%518=340%:%
-%:%519=340%:%
-%:%520=341%:%
-%:%521=341%:%
-%:%523=341%:%
-%:%527=341%:%
-%:%528=341%:%
-%:%530=342%:%
-%:%531=343%:%
-%:%532=344%:%
-%:%533=345%:%
-%:%534=346%:%
-%:%535=347%:%
-%:%545=349%:%
-%:%546=350%:%
-%:%547=351%:%
-%:%548=352%:%
-%:%549=353%:%
-%:%550=354%:%
-%:%551=355%:%
-%:%552=356%:%
-%:%553=357%:%
-%:%554=358%:%
-%:%555=359%:%
-%:%556=360%:%
-%:%557=361%:%
-%:%558=362%:%
-%:%559=363%:%
-%:%560=364%:%
-%:%561=365%:%
-%:%562=366%:%
-%:%563=367%:%
-%:%564=368%:%
-%:%568=370%:%
-%:%569=371%:%
-%:%570=372%:%
-%:%571=373%:%
-%:%572=374%:%
-%:%580=376%:%
-%:%588=376%:%
+%:%333=228%:%
+%:%334=229%:%
+%:%335=230%:%
+%:%336=231%:%
+%:%337=232%:%
+%:%338=233%:%
+%:%339=234%:%
+%:%340=235%:%
+%:%341=236%:%
+%:%342=237%:%
+%:%343=238%:%
+%:%344=239%:%
+%:%345=240%:%
+%:%346=241%:%
+%:%347=242%:%
+%:%348=243%:%
+%:%349=244%:%
+%:%350=245%:%
+%:%351=246%:%
+%:%353=249%:%
+%:%354=249%:%
+%:%355=250%:%
+%:%357=251%:%
+%:%358=252%:%
+%:%359=252%:%
+%:%362=258%:%
+%:%363=259%:%
+%:%364=260%:%
+%:%365=261%:%
+%:%366=262%:%
+%:%367=263%:%
+%:%368=264%:%
+%:%369=265%:%
+%:%370=266%:%
+%:%371=267%:%
+%:%372=268%:%
+%:%373=269%:%
+%:%374=270%:%
+%:%375=271%:%
+%:%377=273%:%
+%:%378=273%:%
+%:%379=274%:%
+%:%381=275%:%
+%:%384=277%:%
+%:%385=278%:%
+%:%386=279%:%
+%:%387=280%:%
+%:%388=281%:%
+%:%389=282%:%
+%:%390=283%:%
+%:%391=284%:%
+%:%392=285%:%
+%:%393=286%:%
+%:%394=287%:%
+%:%395=288%:%
+%:%396=289%:%
+%:%397=290%:%
+%:%398=291%:%
+%:%399=292%:%
+%:%400=293%:%
+%:%401=294%:%
+%:%402=295%:%
+%:%403=296%:%
+%:%404=297%:%
+%:%405=298%:%
+%:%406=299%:%
+%:%407=300%:%
+%:%408=301%:%
+%:%409=302%:%
+%:%410=303%:%
+%:%411=304%:%
+%:%412=305%:%
+%:%413=306%:%
+%:%414=307%:%
+%:%415=308%:%
+%:%416=309%:%
+%:%417=310%:%
+%:%418=311%:%
+%:%419=312%:%
+%:%420=313%:%
+%:%421=314%:%
+%:%422=315%:%
+%:%424=317%:%
+%:%425=317%:%
+%:%426=318%:%
+%:%428=319%:%
+%:%429=320%:%
+%:%430=320%:%
+%:%431=321%:%
+%:%432=322%:%
+%:%433=322%:%
+%:%434=323%:%
+%:%436=324%:%
+%:%437=325%:%
+%:%440=327%:%
+%:%441=328%:%
+%:%442=329%:%
+%:%443=330%:%
+%:%445=332%:%
+%:%446=332%:%
+%:%447=333%:%
+%:%449=334%:%
+%:%450=335%:%
+%:%451=335%:%
+%:%452=336%:%
+%:%453=337%:%
+%:%454=337%:%
+%:%456=338%:%
+%:%457=339%:%
+%:%458=340%:%
+%:%466=342%:%
+%:%478=344%:%
+%:%479=345%:%
+%:%480=346%:%
+%:%481=347%:%
+%:%483=350%:%
+%:%484=350%:%
+%:%486=351%:%
+%:%487=352%:%
+%:%488=353%:%
+%:%489=354%:%
+%:%492=356%:%
+%:%493=357%:%
+%:%495=359%:%
+%:%496=359%:%
+%:%498=359%:%
+%:%502=359%:%
+%:%503=359%:%
+%:%504=360%:%
+%:%505=360%:%
+%:%506=360%:%
+%:%515=362%:%
+%:%516=363%:%
+%:%517=364%:%
+%:%518=365%:%
+%:%519=366%:%
+%:%520=367%:%
+%:%521=368%:%
+%:%522=369%:%
+%:%523=370%:%
+%:%524=371%:%
+%:%525=372%:%
+%:%526=373%:%
+%:%527=374%:%
+%:%528=375%:%
+%:%529=376%:%
+%:%530=377%:%
+%:%531=378%:%
+%:%532=379%:%
+%:%533=380%:%
+%:%534=381%:%
+%:%535=382%:%
+%:%536=383%:%
+%:%538=385%:%
+%:%539=385%:%
+%:%540=386%:%
+%:%542=387%:%
+%:%543=388%:%
+%:%546=390%:%
+%:%548=392%:%
+%:%549=392%:%
+%:%550=393%:%
+%:%552=394%:%
+%:%553=395%:%
+%:%554=395%:%
+%:%555=396%:%
+%:%556=397%:%
+%:%557=397%:%
+%:%558=398%:%
+%:%559=398%:%
+%:%561=398%:%
+%:%565=398%:%
+%:%566=398%:%
+%:%568=399%:%
+%:%569=400%:%
+%:%570=401%:%
+%:%571=402%:%
+%:%572=403%:%
+%:%573=404%:%
+%:%583=406%:%
+%:%584=407%:%
+%:%585=408%:%
+%:%586=409%:%
+%:%587=410%:%
+%:%588=411%:%
+%:%589=412%:%
+%:%590=413%:%
+%:%591=414%:%
+%:%592=415%:%
+%:%593=416%:%
+%:%594=417%:%
+%:%595=418%:%
+%:%596=419%:%
+%:%597=420%:%
+%:%598=421%:%
+%:%599=422%:%
+%:%600=423%:%
+%:%601=424%:%
+%:%603=426%:%
+%:%604=426%:%
+%:%606=428%:%
+%:%607=429%:%
+%:%608=430%:%
+%:%609=431%:%
+%:%610=432%:%
+%:%619=434%:%
+%:%631=436%:%
+%:%632=437%:%
+%:%633=438%:%
+%:%634=439%:%
+%:%635=440%:%
+%:%636=441%:%
+%:%637=442%:%
+%:%638=443%:%
+%:%639=444%:%
+%:%640=445%:%
+%:%641=446%:%
+%:%642=447%:%
+%:%643=448%:%
+%:%644=449%:%
+%:%645=450%:%
+%:%646=451%:%
+%:%647=452%:%
+%:%648=453%:%
+%:%649=454%:%
+%:%652=458%:%
+%:%653=459%:%
+%:%654=460%:%
+%:%655=461%:%
+%:%656=462%:%
+%:%657=463%:%
+%:%660=465%:%
+%:%661=466%:%
+%:%662=467%:%
+%:%663=468%:%
+%:%664=469%:%
+%:%665=470%:%
+%:%666=471%:%
+%:%667=472%:%
+%:%668=473%:%
+%:%669=474%:%
+%:%673=476%:%
+%:%674=477%:%
+%:%675=478%:%
+%:%676=479%:%
+%:%677=480%:%
+%:%678=481%:%
+%:%679=482%:%
+%:%680=483%:%
+%:%681=484%:%
+%:%682=485%:%
+%:%683=486%:%
+%:%684=487%:%
+%:%685=488%:%
+%:%686=489%:%
+%:%688=491%:%
+%:%689=491%:%
+%:%690=492%:%
+%:%693=493%:%
+%:%697=493%:%
+%:%698=493%:%
+%:%700=494%:%
+%:%701=495%:%
+%:%702=496%:%
+%:%703=497%:%
+%:%709=497%:%
+%:%712=498%:%
+%:%713=499%:%
+%:%714=499%:%
+%:%715=500%:%
+%:%718=501%:%
+%:%722=501%:%
+%:%723=501%:%
+%:%725=502%:%
+%:%726=503%:%
+%:%727=504%:%
+%:%728=505%:%
+%:%738=507%:%
+%:%739=508%:%
+%:%740=509%:%
+%:%741=510%:%
+%:%742=511%:%
+%:%743=512%:%
+%:%744=513%:%
+%:%745=514%:%
+%:%746=515%:%
+%:%747=516%:%
+%:%748=517%:%
+%:%749=518%:%
+%:%750=519%:%
+%:%751=520%:%
+%:%752=521%:%
+%:%753=522%:%
+%:%754=523%:%
+%:%755=524%:%
+%:%756=525%:%
+%:%757=526%:%
+%:%758=527%:%
+%:%760=529%:%
+%:%761=529%:%
+%:%762=530%:%
+%:%765=531%:%
+%:%769=531%:%
+%:%770=531%:%
+%:%771=531%:%
+%:%773=532%:%
+%:%779=532%:%
+%:%782=533%:%
+%:%783=534%:%
+%:%784=534%:%
+%:%785=535%:%
+%:%786=536%:%
+%:%789=537%:%
+%:%793=537%:%
+%:%794=537%:%
+%:%795=537%:%
+%:%797=538%:%
+%:%798=539%:%
+%:%799=540%:%
+%:%809=542%:%
+%:%810=543%:%
+%:%811=544%:%
+%:%812=545%:%
+%:%813=546%:%
+%:%814=547%:%
+%:%815=548%:%
+%:%816=549%:%
+%:%817=550%:%
+%:%819=553%:%
+%:%820=553%:%
+%:%823=554%:%
+%:%827=554%:%
+%:%828=554%:%
+%:%830=555%:%
+%:%831=556%:%
+%:%832=557%:%
+%:%842=559%:%
+%:%843=560%:%
+%:%844=561%:%
+%:%845=562%:%
+%:%846=563%:%
+%:%847=564%:%
+%:%848=565%:%
+%:%850=567%:%
+%:%851=567%:%
+%:%852=568%:%
+%:%853=569%:%
+%:%856=570%:%
+%:%860=570%:%
+%:%861=570%:%
+%:%862=570%:%
+%:%864=571%:%
+%:%865=572%:%
+%:%866=573%:%
+%:%876=575%:%
+%:%877=576%:%
+%:%879=578%:%
+%:%880=578%:%
+%:%881=579%:%
+%:%882=580%:%
+%:%885=581%:%
+%:%889=581%:%
+%:%890=581%:%
+%:%891=581%:%
+%:%893=582%:%
+%:%903=584%:%
+%:%904=585%:%
+%:%905=586%:%
+%:%906=587%:%
+%:%907=588%:%
+%:%908=589%:%
+%:%909=590%:%
+%:%910=591%:%
+%:%911=592%:%
+%:%912=593%:%
+%:%913=594%:%
+%:%914=595%:%
+%:%915=596%:%
+%:%916=597%:%
+%:%920=601%:%
+%:%921=602%:%
+%:%922=603%:%
+%:%923=604%:%
+%:%924=605%:%
+%:%925=606%:%
+%:%926=607%:%
+%:%927=608%:%
+%:%931=611%:%
+%:%932=612%:%
+%:%933=613%:%
+%:%934=614%:%
+%:%935=615%:%
+%:%936=616%:%
+%:%937=617%:%
+%:%938=618%:%
+%:%939=619%:%
+%:%940=620%:%
+%:%941=621%:%
+%:%942=622%:%
+%:%943=623%:%
+%:%944=624%:%
+%:%945=625%:%
+%:%946=626%:%
+%:%947=627%:%
+%:%948=628%:%

### 2022-02-15 paper/output/document/thesis_3_implementation.tex
cleaned chapter 3

@@
 \begin{isamarkuptext}%
-In this section, I present the details of my implementation of automated Kantian ethics. I first 
-formalize the FUL in Dyadic Deontic Logic and then implement this logic in Isabelle/HOl. I 
-also present a testing framework that can evaluate how faithful an implementation
-of automated ethics is to philosophical literature. This testing framework shows that my system outperforms
-two other possible implementations of automated Kantian ethics.%
+In this section, I present the details of my implementation of automated Kantian ethics, which requires
+formalizing the FUL in Dyadic Deontic Logic and then implementing this logic in Isabelle/HOL. The final
+Isabelle library contains enough logical background and an axiom representing the categorical imperative. 
+Using Isabelle's automated theorem proving abilities, my system can show that appropriately represented
+actions are, according to Kantian ethics, obligatory, permissible, or prohibited by proving or refuting sentences of the form ``A 
+is obligated to do B.'' I also present a testing framework to evaluate how faithful my implementation is 
+to philosophical literature. This testing framework shows that my system outperforms two other potential 
+implementations of automated Kantian ethics.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-Before formalizing the FUL, I must define and implement the relevant logical background. Dyadic
+Formalizing the FUL requires defining and implementing enough logical background to represent 
+the FUL as an axiom. Dyadic
 Deontic Logic can express obligation and prohibition, but it cannot represent more complex features of 
@@
 \begin{isamarkuptext}%
-Kantian ethics is centered on practical reason because it is action-guiding; the categorical
+Kantian ethics is fundamentally action-guiding; the categorical
 imperative is a moral rule that agents can use to decide between potential actions. Thus, before I 
 begin to formalize a specific formulation of the categorical imperative, I must define the notions of 
-subjects and actions. I need to add logical background so that my logic can express sentences 
-of the form, ``x does action.''%
+subjects and actions. I add representations of subjects and actions so that my new logic can express
+sentences of the form, ``x does action.''%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \ s\ %
-\isamarkupcmt{I declare a new type $s$ as the type for a ``subject,'' as in the subject of a sentence.%
+\isamarkupcmt{The new type $s$ is the type for a ``subject,'' as in the subject of a sentence.%
 }%
@@
 The \texttt{typedecl} keyword indicates that I am defining a new atomic type, which is not composed
-of pre-existing types but is instead a new kind of object altogether. To define a subject, it suffices
+of pre-existing types but is instead a new kind of object altogether. It suffices
 to declare a new type to represent a subject without specifying any of its complex properties, such as the idea that a subject
 must be rational or human. Instead of providing a complete definition of subject, which would require wading into murky
-philosophical debates about the nature of agency, I will provide a ``thin'' definition which includes
-only the minimum necessary properties to apply the FUL. Throughout my project, I will use bare syntactic units like types and constants
-to define new ideas and will add thin definitions to achieve the desired results.
-
-In this interpretation, it suffices to make the defining feature of a subject that it can act. 
+philosophical debates about the nature of agency, I will provide a ``thin'' definition that only includes
+the minimum necessary properties to apply the FUL. Throughout my project, I will use bare syntactic units like types and constants
+to create thin definitions of new ideas.
+
+In this interpretation, the defining feature of a subject is that it can act. 
 I represent that below by allowing subjects to substitute into sentences, a property that I will use 
@@
 %
-\isamarkupsubsubsection{Maxim \label{whatisamaxim}%
+\isamarkupsubsubsection{Maxims \label{whatisamaxim}%
 }
@@
 \begin{isamarkuptext}%
-Recall from Section \ref{whyful} that I formalize a version of the categorical imperative called
+As established in Section \ref{whyful}, I formalize a version of the categorical imperative called
 the Formula of Universal, which reads ``act only according to that maxim by which you can at the same 
 time will that it should become a universal law'' \citep{groundwork}. In order to faithfully formalize
-the FUL, I must make precise what it means to will a maxim and violate the FUL. I draw on 
-reliable definitions of willing, maxims, and the FUL from Kantian literature and represent them in DDL.
-Throughout this section, I will use one of Kant's most famous maxims as an example to demonstrate
-my formalization.
+the FUL, I must make precise what it means to will a maxim and what kinds of maxims can become universal laws. 
+I draw on reliable definitions of willing, maxims, and universalization from Kantian literature and represent them in DDL.
+Throughout this section, I will use one of Kant's canonical maxims as an example.
 
 \begin{example}[False Promising]\label{falsepromise}
-  The false promising example maxim reads, ``When I am broke, I wil falsely promise to repay a loan 
+  The false promising example maxim reads, ``When I am strapped for cash, I wil falsely promise to repay a loan 
 to get some easy cash.''
@@
 %
-\isamarkupcmt{A maxim is of type term, open sentence, term tuple, such as ``(When I am broke, will falsely promise
+\isamarkupcmt{A maxim is of type term, open sentence, term tuple, such as ``(When I am strapped for cash, will falsely promise
 to repay a loan, to get some easy cash)''. The first term represents the circumstance, which
-can be true or false at a world. For example, the circumstance ``when I am broke'' is true at the real 
+can be true or false at a world. For example, the circumstance ``when I am strapped for cash'' is true at the real 
 world when my bank account is empty. The second term represents the action, which is an open sentence
@@
 the goal, which can again be true or false at a world. For example, the goal ``to get some easy cash''
-is true at the real world if I have gotten easy cash.%
-}%
-\begin{isamarkuptext}%
-O'Neill \cite[37]{actingonprinciple} argues that maxim 
+is true at the real world if I have successfully received easy cash.%
+}%
+\begin{isamarkuptext}%
+O'Neill argues that a maxim 
 is an action-guiding rule and thus naturally includes an act and the circumstances under which 
-it should be performed, which are often referred to as ``morally relevant circumstances'' \citep[37]{actingonprinciple}. 
-She also includes a purpose, end, or goal in the maxim because human activity, is guided by a rational will, 
+it should be performed \citep[37]{actingonprinciple}. 
+She also includes a purpose, end, or goal in the maxim because human activity is guided by a rational will
 and is thus inherently purposive \citep[4:428]{groundwork}. A rational will does not act randomly (else it would not be rational), 
@@
 include the agent's motive or motivation and I address this concern in Appendix \ref{maximmotive}.} The inclusion a maxim's end is essential for the version of the FUL
-that I will implement, explained in Section Practical Contradiction.
+that I will implement, explained in Section \ref{praccon}.
 
@@
 O'Neill's inclusion of circumstances is potentially controversial because it leaves open the question of what qualifies as a 
-relevant circumstance for a particular maxim. This is gives rise to ``the tailoring objection", 
+relevant circumstance for a particular maxim. This gives rise to ``the tailoring objection,'' 
 under which maxims are arbitrarily specified to pass the FUL  \citep[217]{whatisamaxim}. \footnote{Kitcher
 cites \citet{kantsethicalthought} as offering an example of a false positive due to this objection.} For example, the maxim ``When my name is Jane Doe
-and I am wearing a purple shirt and it is Tuesday morning, I will murder my boss so I can take their job," 
+and I am wearing a purple shirt and it is Tuesday morning, I will murder my boss so I can take their job,'' 
 is universalizable but is clearly a false positive because we think that murder for professional gain is wrong. 
 One solution to this problem is to argue that the circumstance ``When my name is Jane Doe and I am wearing a 
-purple shirt and it is Tuesday morning" is not morally relevant 
+purple shirt and it is Tuesday morning'' is not morally relevant 
 to the act and goal. This solution requires determining what qualifies as a relevant circumstance.
@@
 
-The difficulty in determining relevant circumstances is a limitation of my system and may require that a 
+The difficulty in determining relevant circumstances is a limitation of my system and requires that a 
 human being formulate the maxim or that future work develop heuristics to classify circumstances as morally 
 relevant. For proponents of the ``human-in-the-loop'' model of AI ethics, in which ethical AI requires that 
-humans guide machines, this kind of human involvement may be a feature \citep{loop}. In this model, 
+humans guide machines, human involvement may be a feature, not a bug \citep{loop}. In this model, 
 a human being must create a representation for the dilemma they wish to test, translating 
@@
 face when translating the complexity of reality to a programming langauge or computational representation. 
-The outcome of the universalizability test will depend on how the human formulates the maxim
-and whether or not this formulation does indeed include morally relevant circumstances. If the human puts 
-garbage into the test, the test will return garbage out.
-
-Another solution to this problem may be to develop heuristics to classify circumstances as morally 
+The outcome of the universalizability test will depend on how the human formulates the maxim; if the 
+human puts garbage into the test, the test will return garbage out.
+
+Another solution is to develop heuristics to classify circumstances as morally 
 relevant. For example, one such attempt could define a moral closeness relation between an action, a 
-goal, and circumstances. This heuristic would define morally relevant circumstances as those that 
+goal, and circumstances. This heuristic could define morally relevant circumstances as those that 
 reach a certain closeness threshhold with the action and the goal. Determining morally relevant
@@
 
-To will a maxim is to adopt it as a principle to live by, or to commit oneself to the action for the 
-sake of the end in the relevant circumstances. Korsgaard argues that ``to will an end, rather than 
-just wishing for it or wanting it, is to set yourself to be its cause" \cite[38]{sources}. I formalize
-this idea in Definition \ref{willing}.
+With this robust representation of a maxim, I can now define willing. To will a maxim is to adopt it 
+as a principle to live by, or to commit oneself to the maxim's action for the 
+sake of maxim's end in the relevant circumstances. I formalize this idea in Definition \ref{willing}.
 
@@
 For maxim $M = (C, A, G)$ and actor $s$,
-
-$$will \, M \, s \equiv \forall w \, (C \longrightarrow A \, (s)) \, w$$
-
-At all worlds $w$, if the circumstances hold at that world, agent $s$ performs act $A$.
+$$\text{\emph{will}} \, M \, s \equiv \forall w \, (C \longrightarrow A \, (s)) \, w$$
+\noindent At all worlds $w$, if the circumstances hold at that world, agent $s$ performs act $A$.
 
@@
 
-If I will example \nameref{falsepromise} maxim about falsely promising to pay a loan, then whenever I need cash, 
+If I will the example \nameref{falsepromise} maxim, then whenever I need cash, 
 I will falsely promise to repay a loan. I can represent this definition using the following Isabelle
@@
 \begin{isamarkuptext}%
-In order to evaluate the moral status of a maxim, I must precise the idea of failing
-the universalizability test or a non-universalizable maxim.  Kantians debate the correct interpretation of 
+In order to evaluate the moral status of a maxim, I must define what it means for a maxim to not be
+universalizable, or to fail the universalizability test. Kantians debate the correct interpretation of 
 the Formula of Universal Law because Kant himself appears to interpret the criterion in different ways. 
-My project uses Korsgaard's practical contradiction interpretation, broadly accepted as correct within 
+I adopt Korsgaard's practical contradiction interpretation, broadly accepted as correct within 
 the philosophical community \citep{ebelsduggan}.
@@
 you can at the same time will that it become a universal law” \citep{groundwork}. To determine if a 
-maxim can be willed as a universal law, we can use the “universalizability test”, which requires 
+maxim can be willed as a universal law, we use the “universalizability test,” which requires 
 imagining a world in which everyone has willed the maxim. If willing the maxim in such a world 
-generates a contradiction, then the action is prohibited. In the case of the example maxim about 
-lying to
+generates a contradiction, then the action is prohibited. For example, the \nameref{falsepromise}
+maxim will be prohibited if it is impossible to will the maxim in a world where everyone falsely promises
+to repay loans.
 
@@
 logically impossible when universalized. Under this view, falsely promising to repay a loan fails the 
-universalizability test because, in the universalized world, the practice of promising would die out, 
-so making a false promise would be impossible.
-
-One problem with this view is that it cannot handle natural acts. Korsgaard appeals to 
-\citet{dietrichson} to construct the example natural act of a mother killing her children that tend to 
-cry at night so that she can get some sleep. Universalizing this maxim does not generate a logical 
-contradiction, but it is clearly wrong. Because killing is a natural act, it can never be logically 
+universalizability test because, in the universalized world, everyone falsely promises to repay
+loans so lenders no longer believe promises to repay loans. The practice of loans would die out, so 
+making a false promise to repay a loan would be impossible.
+
+This view cannot correctly handle natural acts. Korsgaard appeals to 
+\citet{dietrichson} to construct the example natural act of a mother killing her children that
+cry too much at night so that she can get some sleep. Universalizing this maxim does not generate a logical 
+contradiction because killing is still possible in a world where everyone kills noisy children, but 
+it is clearly wrong. Because killing is a natural act, it can never be logically 
 impossible so the logical contradiction view cannot prohibit it.
@@
 maxims are immoral. These maxims involve parasitic behavior on social conditions that the agent seeks 
-to benefit from. The false promiser simultaneously wants to abuse the system of promising and benefit 
+to benefit from. The false promiser wants to both abuse the system of promising and benefit 
 from it, and is thus making an exception of themselves. The test formalizes the kinds of objections 
@@
 
-Using the practical contradiction interpretation, the FUL states, ``If, when universalized, a maxim is 
+Under the practical contradiction interpretation, the FUL states, ``If, when universalized, a maxim is 
 not effective, then it is prohibited.'' This requires defining effectiveness and universalization. 
@@
 For a maxim $M = (C, A, G)$ and actor $s$,
-
 $$\text{\emph{effective}} \, M \, s \equiv \forall w \, (\text{\emph{will}} \, (C, A, G) \, s \iff G) \, w$$
-
 \end{definition}
-
-I can implement this in Isabelle using another abbreviation.%
+\noindent I implement this in Isabelle below.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 necessary causality, or the idea that, counterfactually, if the maxim were not willed, then the goal 
-would not be achieved \citep{lewiscausality}.\footnote{Thank you for Jeremy Zucker for helping me 
+would not be achieved \citep{lewiscausality}.\footnote{Thank you to Jeremy Zucker for helping me 
 think about causality in this way.}  Note that nothing else changes about this
 counterfactual world—the circumstances are identical and we neither added additional theorems nor 
-specified the model any further. This represents Lewis's idea of "comparative similarity,"  where 
+specified the model any further. This represents Lewis's idea of ``comparative similarity,''  where 
 a counterfactual is true if it holds at the most similar world \citep{lewiscounterfactuals}. 
@@
   For a maxim $M$ and agent $s$,
-
 $$\text{\emph{universalized}} \, M  \equiv \forall w \, (\forall p \, \text{\emph{will}} \, M \, p)$$
@@
 With the above definitions of effective and universalization, I can define what it means for 
-a maxim to not be universalizable. This is the core of the FUL; it states that if a maxim is not 
-universalizable, it is prohibited. The practical contradiction interpretation states that a  maxim is 
+a maxim to not be universalizable. This is the core of the FUL, which states that if a maxim is not 
+universalizable, it is prohibited. Under the practical contradiction interpretation, a maxim is 
 not universalizable if, when universalized, it is no longer effective.
@@
 For a maxim $M$ and agent $s$,
-
-$$not\_universalizable \, M \, s  \equiv [ \text{\emph{universalized}} M \longrightarrow \neg \, \text{\emph{effective}} \, M \, s ]$$
-
-A maxim is not universalizable when, if everyone wills the maxim, then it is no longer effective.
+$$\text{\emph{not\_universalizable}} \, M \, s  \equiv [ \text{\emph{universalized}} \, M \longrightarrow \neg \, \text{\emph{effective}} \, M \, s ]$$
 \end{definition}
-
+\noindent A maxim is not universalizable when, if everyone wills the maxim, then it is no longer effective.
 I implement this definition in Isabelle using another abbreviaion.%
@@
 %
-\isamarkupcmt{The formula above reads ``at world $w$, if M is universalized, then M is not effective.''%
-}%
-\begin{isamarkuptext}%
-The final set of definitions necessary to implement the FUL are obligation, permissibility, 
-and prohibition. To judge an action, my system evaluates the moral status of the action 
+\isamarkupcmt{Maxim $M$ is not universalizable at world $w$ when, ``at world $w$, if M is universalized, then M is not effective.''%
+}%
+\begin{isamarkuptext}%
+The FUL states that if a maxim is not universalizable, then it is prohibited. Before performing
+moral reasoning with my system, I must define obligation, permissibility, and prohibition.
+To judge an action, my system evaluates the moral status of the action 
 ``person $s$ wills maxim $M$.'' This action can be obligated, prohibited, or permissible.
-I will use the phrase ``subject s willing maxim M is obligatory" 
-interchangeably with ``maxim M is obligatory for subject s." I will use ``maxim M is obligatory" to 
-refer to M being obligatory for any arbitrary subject, which I is equivalent to M being 
-obligatory for a specific subject.\footnote{The full proof for this result is in Appendix Extra Tests}.
+I will use the phrase ``subject $s$ willing maxim $M$ is obligatory" 
+interchangeably with ``maxim $M$ is obligatory for subject $s$." I will use ``maxim $M$ is obligatory" to 
+refer to $M$ being obligatory for any arbitrary subject, which is equivalent to $M$ being 
+obligatory for a specific subject.\footnote{The full proof for this result is the Obligation Universalizes
+Across People Test in Section \ref{tests}.}
 
@@
 Let maxim $M$ be composed of the circumstances, act, goal tuple $C, A, G$ and let $s$ be an arbitrary agent.
-
-$$obligated \, M \, s \equiv O\{ will \, (C, A, G) \, s \, | \, C\}$$
-
+$$\text{\emph{obligated}} \, M \, s \equiv O\{ \text{\emph{will}} \, (C, A, G) \, s \, | \, C\}$$
 \end{definition}
@@
 This definition does not require any additional syntactic sugar, since it merely uses the dyadic obligation
-operator in a clever way. Using this definition, I can define prohibition and permissibility.
+operator. Using this definition, I can define prohibition and permissibility.
 
@@
 $O\{ \neg will \, (C, A, G) \, s \, | \, C\}$.}
-
 \newcommand*{\approxident}{%
@@
   \hbox{$\sim$}\vskip-.35ex\hbox{$\sim$}\vskip-.35ex\hbox{$\sim$}}}}
-
-$$ prohibited \, M \, s \approxident obligated \, \neg M \, \equiv O\{ \neg will \, (C, A, G) \, s \, | \, C\}$$
-
-$$permissible \, M \, s \equiv \neg prohibited \, M \, s \equiv \neg O\{ \neg will \, (C, A, G) \, s \, | \, C\}$$
-
-\end{definition}
-
-Once again, I represent these definitions as abbreviations in Isabelle.%
+$$\text{\emph{prohibited}} \, M \, s \approxident \text{\emph{obligated}} \, \neg M \, \equiv O\{ \neg \text{\emph{will}} \, (C, A, G) \, s \, | \, C\}$$
+$$\text{\emph{permissible}} \, M \, s \equiv \neg \text{\emph{prohibited}} \, M \, s \equiv \neg O\{ \neg \text{\emph{will}} \, (C, A, G) \, s \, | \, C\}$$
+\end{definition}%
 \end{isamarkuptext}\isamarkuptrue%
@@
 notion of contradictory obligations. Many deontic logics, including DDL, allow contradictory
-obligations. As I will explain in Section Tests, Kantian ethics never prescribes contradictory
+obligations. As I will explain in Section \nameref{testing}, Kantian ethics never prescribes contradictory
 obligations, so I will add this as an axiom.%
@@
 \begin{isamarkuptext}%
-With this logical background, I can begin to implement the Formula of Universal Law, as defined 
-by the practical contradiction interpretation, which states that a maxim is prohibited if it is ineffective
-when universalized. A first attempt to formalize the FUL simply translates this into Isabelle's syntax
-using the abbreviations above.%
+With this logical background, I can begin to implement the Formula of Universal Law, which, as defined 
+by the practical contradiction interpretation, states that a maxim is prohibited if it is ineffective
+when universalized. A first, ultimately unsuccessful, attempt to formalize the FUL simply translates this into Isabelle's syntax
+using the abbreviations above. While this attempt will not be consistent, I will use Isabelle's automatic
+proof search abilities to determine how to modify this formula to be consistent, revealing a key philosophical
+insight about maxims in the process. This section presents my final formalization of the FUL and the 
+philosophical insight produced while creating it, which, as I argue in Section Computational Ethics???,
+demonstrates the power of computational tools in aiding philosophical progress.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 universalizable (as defined above), then, at all worlds, in those circumstances, the subject 
-is prohibited (obligated not to) from willing the maxim.''%
-}%
-\begin{isamarkuptext}%
-I can immediately determine if this version of the FUL is sensical by checking if it is consistent.
-If \texttt{FUL0} implies False, then it is inconsistent.%
+is prohibited from (obligated not to) willing the maxim.''%
+}%
+\begin{isamarkuptext}%
+I can immediately determine if this version of the FUL is consistent by checking if \texttt{FUL0} 
+implies $False$.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-FUL0 is not consistent, and Isabelle's proof-finding tool, Sledgehammer, is able to prove this by showing that it implies a contradiction 
-usig axiom \texttt{O\_diamond}\footnote{The full axiom reads \isa{{\isasymTurnstile}{\isasymlambda}w{\isachardot}\ ob\ {\isacharquery}B\ {\isacharquery}A\ {\isasymlongrightarrow}\ {\isasymnot}\ {\isasymTurnstile}\isactrlbold {\isasymnot}\ {\isacharquery}B\isactrlbold {\isasymand}{\isacharquery}A}.} \citep{sledgehammer}.
-This axiom captures the idea that an obligation can't contradict its context. This is particularly problematic 
-if the goal or action of a maxim are equivalent to its circumstances. In other words, if the maxim has already been 
-acted on or the goal has already been achieved, then prohibiting it is impossible. 
-In any model that has at least one term, it is possible to construct a maxim where the circumstances, goal, 
-and act (once a subject acts on it) are all that same term, resulting in a contradiction.
-
-This motivates the exclusion of what I call ``badly formed maxims," which are those maxims such that 
+Isabelle's proof-finding tool, Sledgehammer, shows that 
+\texttt{FUL0} is not consistent by showing that it implies a contradiction 
+using axiom \texttt{O\_diamond}\footnote{The full axiom reads \isa{{\isasymTurnstile}{\isasymlambda}w{\isachardot}\ ob\ {\isacharquery}B\ {\isacharquery}A\ {\isasymlongrightarrow}\ {\isasymnot}\ {\isasymTurnstile}\isactrlbold {\isasymnot}\ {\isacharquery}B\isactrlbold {\isasymand}{\isacharquery}A}.} \citep{sledgehammer}.
+This axiom roughly states that an obligation can't contradict its context. Knowing that \texttt{FUL0}
+contradicts this particular maxim offers insight into what the problem is. If the goal or action
+or a maxim are equivalent to its circumstance, then prohibiting it is contradictory. If the maxim has already been 
+acted on or the goal has already been achieved, then the agent cannot undo their action or the achivement 
+of the goal. Moreover, in many models, it is possible to construct a maxim where the circumstances, goal, 
+and act (once a subject acts on it) are all that same term and to show that this maxim is prohibited,
+resulting in a contradiction.
+
+This motivates the exclusion of what I call ``badly formed maxims,'' which are those maxims such that 
 the goal has already been achieved or the act has already been acted on. Under my formalization, such maxims are
@@
 because the circumstance ``when I eat breakfast'' contains the act and goal. Well-formedness is not 
-discussed in the literature, but if I require that the FUL only holds for well-formed maxim, it will now
-be consistent.%
+discussed in the literature, but I find that if I require that the FUL only holds for well-formed maxim, it is
+consistent.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-If I modify \texttt{FUL0} to only hold for well-formed maxims, it becomes consistent.%
+\noindent If I modify \texttt{FUL0} to only hold for well-formed maxims, it becomes consistent.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 consistent \citep{nitpick}. If Nitpick can find a model in which the axioms of DDL hold and the FUL is 
-true then it is consistent.
-$\color{blue}$ Nitpick found a model for card $i$ = 1 and card $s$ = 2:
-
-  Empty assignment $\color{black}$%
+true, then it is consistent.
+
+\color{blue} Nitpick found a model for card $i$ = 1 and card $s$ = 2:
+
+  Empty assignment \color{black}%
 }%
@@
 \begin{isamarkuptext}%
-Above, I used Isabelle and my logic to show that if the FUL holds for badly formed maxims then 
-it is inconsistent. This is not just a logical property of my system, but it also has philosophical
+My above investigation of \texttt{FUL0} shows that if the FUL holds for badly formed maxims, then 
+it is inconsistent. This is not only a logical property of my system, but it also has philosophical
 significance that coheres with Korsgaard's and O'Neill's interpretations of a maxim as a practical
@@
 The fact that Isabelle revealed a philosophical insight about which kinds of maxims are well-formed
-enough to evaluate using the categorical imperative is an example of the power of computational tools to aid
+is an example of the power of computational tools to aid
 philosophical progress. Nitpick and Sledgehammer helped me confirm that certain kinds
@@
 properties and implications of well-formed maxims and the power of computational ethics further in 
-Chapter Discussion in Section Computational Ethics.
+Section Computational Ethics.
 
@@
 The code snippets in this chapter are a subset of the over 100 lines of Isabelle/HOL code necessary to
-complete this implementation. In Section \nameref{testing} and Chapter Applications, I demonstrate how this
+complete this implementation. In Section \ref{testing} and Chapter Applications, I demonstrate how this
 implementation can be tested and used to make moral judgements.%
@@
  prove or refute each test sentence in my logic.  Because these tests are derived from moral 
-intuition and philosophical literature, they evaluate how reliable my system is.
-
-The test framework can be expanded by adding more test sentences. This test framework can also guide 
+intuition and philosophical literature, they evaluate how well my system reflects philosophical
+literature. Running the tests on my implementation consisted of approximately 400 lines of Isabelle code.
+
+The test framework can be expanded by adding more test sentences and can guide 
 implementations of other parts of Kantian ethics or other ethical theories. As I was implementing my 
-formalization, I checked it against the testing framework, performing test-driven development automated 
-ethics. Running the tests on my implementation alone consisted of approximately 400 lines of Isabelle code.
+formalization, I checked it against the testing framework, performing test-driven development for automated 
+ethics.
 
 I use my testing framework to show that my formalization and implementation of Kantian ethics outperforms 
-raw DDL with no other axioms added (a control group) and Kroy's prior attempt at formalizing 
-(but not implementing) the FUL, which I implement\footnote{I present the complete implementation in 
-Appendix \nameref{kroy_appendix}} in Isabelle \citep{kroy}. My implementation outperforms 
+two other potential implementations. First, I consider raw DDL, which serves as a control group because it simply contains the base logic
+on top of which I build other implementations. DDL can express obligation, but has no knowledge of any 
+specific moral rules (like the categorical imperative) and is thus a 
+control group. Second, I consider Moshe Kroy's 1976 formalization of the FUL and the second formulation
+of the categorical imperative \citep{kroy}. His formalization is based on Hintikka's deontic logic, which is a different,
+less expressive logic than DDL \citep{hintikka}. He presents a logical representation of the FUL that has not yet been implemented
+using an automated theorem prover, so I implement it in Isabelle.\footnote{I present the complete implementation in
+Appendix \ref{kroydetails}.} I find that my implementation outperforms 
 both other implementations. Full test results are summarized in Figure \ref{table}. Below, I briefly 
-explain some noable tests.%
+explain some notable tests.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-\textbf{FUL Stronger than DDL} The FUL should not hold in raw DDL, which I use a control group. 
+\noindent \textbf{FUL Stronger than DDL} The FUL should not hold in raw DDL, which I use a control group. 
 If the FUL holds in the base logic, then adding it as an axiom doesn't make the logic any stronger, 
-which is troubling because the base logic does not come equipped with the categorical imperative built-in. It 
+which is troubling because the base logic does not come equipped with the categorical imperative. DDL
 defines basic properties of obligation, such as ought implies can, but contains no axioms that represent
-the formula of universal law. Therefore, if a formalization of the FUL holds in the 
+the Formula of Universal Law. Therefore, if a formalization of the FUL holds in the 
 base logic, then it is too weak to actually represent the FUL. Both Kroy's formalization
-and my implementation do not hold in the base logic, and thus represent some progress over the control group.
+and my implementation do not hold in the base logic, and thus represent progress over the control group.
 To test this property, I used Nitpick to find a countermodel in which my version of the FUL does not hold. 
@@
 \noindent \textbf{Obligation Universalizes Across People} The obligations prescribed by the Formula of Universal Law
-should generalize across people. In other words, if a maxim is obligated for one person, it is obligated
+should generalize across people. In other words, if a maxim is obligated for one person, then it is obligated
 for all other people because maxims are not person-specific. Velleman argues that, because 
-reason is accessible to everyone identically, obligations apply to all people equually \citep[25]{velleman}. 
+reason is accessible to everyone identically, obligations apply to all people equally \citep[25]{velleman}. 
 When Kant describes the categorical imperative as the objective principle of the will, he is referring 
@@
 formalization, which essentially says that if an act is permissible for someone, it is permissible for 
-everyone.\footnote{Formally, $P\{A(s)\} \longrightarrow \forall p. P\{A(p)\}$} Kroy's interpretation and 
-my interpretation satisfy this property, but the naive interpretation does not. Below I show how I 
-ran this test for my interpreation.%
+everyone.\footnote{Formally, $P\{A(s)\} \longrightarrow \forall p. P\{A(p)\}$.} Kroy's formalization and 
+my formalization satisfy this property, but raw DDL does not. Below I run
+this test for my formalization.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupcmt{This lemma shows that if a maxim (c, a, g) is wrong for subject $s$ at a world, then it is wrong
-for all people at $s$. Isabelle automatically completed this proof using the \texttt{blast} method, 
+\isamarkupcmt{I represent my tests as 
+lemmas that I expect Isabelle to either prove or refute. The statement following the keyword \texttt{shows}
+is the sentence of the lemma, and the proof follows the \texttt{by} keyword%
+}\isanewline
+%
+\isamarkupcmt{This lemma shows that if a maxim $(c, a, g)$ is wrong for subject $s$ at a world, then it is wrong
+for all people at that world. Isabelle automatically completed this proof using the \texttt{blast} method, 
 which implements a generic tableau prover, a proof method that operates on lists of formulae using 
@@
 %
-\isamarkupcmt{This lemma shows that if a maxim (c, a, g) is right for subject $s$ at a world, then it is wrong
-for all people at $s$. The proof similarly proceeds using \texttt{blast}. I represent my tests as 
-lemmas, that I expect Isabelle to either prove or refute. The statement following the keyword \texttt{shows}
-is the sentence of the lemma, and the proof follows the \texttt{by} keyword.%
+\isamarkupcmt{This lemma shows that if a maxim $(c, a, g)$ is right for subject $s$ at a world, then it is right
+for all people at that world. The proof similarly proceeds using \texttt{blast}.%
 }%
@@
 \begin{isamarkuptext}%
-\noindent \textbf{Contradictory Obligations} DDL itself allows contradictory obligations, but contradictory obligations
+\noindent \textbf{Contradictory Obligations} Contradictory obligations
 make obeying the prescriptions of an ethical theory impossible.
 Kant subscribes to the general, popular view that morality is supposed to guide action, so ought implies 
-can\footnote{Kohl points out that this principle is referred to as 
-Kant's dictum or Kant's law in the literature \citep[footnote 1]{kohl}.}. Kohl reconstructs his argument for the principle as 
+can.\footnote{Kohl points out that this principle is referred to as 
+Kant's dictum or Kant's law in the literature \citep[footnote 1]{kohl}.} Kohl reconstructs Kant's argument for this principle as 
 follows: if the will cannot comply with the moral law, then the moral law has no prescriptive authority 
@@
 such as ``improve oneself" or "help others," and are secondary to perfect duties. My project only analyzes 
-perfect duties, as these are always stronger than imperfect duties.} Both the naive formalization and 
+perfect duties, as these are always stronger than imperfect duties.} Both raw DDL and 
 Kroy's formalization allow contradictory obligations, but I explicitly add an axiom to my formalization
@@
 \begin{isamarkuptext}%
-During testing, I also realized that contradictory obligations are closely related to two other properties
-that also fail in both prior attempts. First is the idea that obligation implies permissibility, or 
+Contradictory obligations are closely related to two other properties. First is the idea that obligation implies permissibility, or 
 that obligation is a stronger property than permissibility. If there are no contradictory obligations, 
 then this property holds because actions are either permissible or prohibited and obligation contradicts
-prohibition. Moreover, in a system with contradictory obligations, this property fails because there is some
+prohibition. In a system with contradictory obligations, this property fails because there is some
 A that is obligated but also prohibited and therefore not permisible. Formalizing this property below shows 
-that this follows from the definition of implication in propositional logic.
+that this follows from contradictory obligations.
 
@@
 another property that we expect to hold. The rough English translation of  $O \{ A \wedge B \} $ is ``you are obligated to 
-do both A and B". The rough English translation of $O\{A\} \wedge O\{B\}$ is ``you are obligated to do A 
-and you are obligated to do B." We think those English sentences mean the same thing, so they should mean 
+do both A and B''. The rough English translation of $O\{A\} \wedge O\{B\}$ is ``you are obligated to do A 
+and you are obligated to do B.'' We think those English sentences mean the same thing, and they should mean 
 the same thing in logic as well. Moreover, if that (rather intuitive) property holds, then contradictory
@@
 \isamarkupcmt{The \texttt{assumes} keyword indicates assumptions used when proving a lemma. I use it here to 
-capture the idea of metalogical implication. With the assumption, the lemma above reads, ``If the distributive
+represent metalogical implication. With the assumption, the lemma above reads, ``If the distributive
 property holds in this logic, then obligations cannot contradict."%
@@
 \begin{isamarkuptext}%
-Again, this test fails in the naive formalization and for Kroy's formalization, but
+Again, this test fails for raw DDL and for Kroy's formalization, but
 passes for my interpretation because I require that obligations don't contradict as an axiom.%
@@
 %
-\isamarkupcmt{Once again, the proof proceeds almost immediately using the new axiom.%
+\isamarkupcmt{The proof proceeds almost immediately using the new axiom.%
 }%
@@
 
-\noindent \textbf{Un-universalizable Actions} Recall that under 
-the logical contradiction interpretation of the Formula of Universal Law, it prohibits lying because, in a world 
+\noindent \textbf{Un-universalizable Actions} Recall that 
+the logical contradiction interpretation of the Formula of Universal Law prohibits lying because in a world 
 where everyone simultaneously lies, lying is impossible. In other words, not everyone can simultaneously
-lie because the institution of lying and believing would break down. In Section \nameref{praccon}, 
+lie because the institution of lying and believing would break down. In Section \ref{praccon}, 
 I recreated Korsgaard's argument for why the logical contradiction interpretation is weaker than what the
@@
 able to show that the actions prohibited by the logical contradiction interpretation are prohibited, 
-because the actions prohibited by the practical contradiction interpretation are a superset of these.
+because the set of actions prohibited by the practical contradiction interpretation is a superset of these.
 The FUL should show that actions that cannot possibly be universalized are prohibited, because those acts cannot be willed in 
-a world where they are universalized. This property fails to hold in both the naive formalization 
-and Kroy's formalization, but holds for my custom formalization. Showing that this property holds
-for my formalization required significant logical background is presented in Appendix \ref{weirdtests}%
+a world where they are universalized. This property fails to hold in both raw DDL
+and Kroy's formalization, but holds for my formalization. Showing that this property holds
+for my formalization required significant logical background and the full code is presented in Appendix \ref{weirdtests}.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 faithful formalization of the categorical imperative must evaluate maxims, not acts. This requires 
-representing a maxim and making it the input to the obligation operator, which neither of the prior 
-attempts do. Because my implementation includes the notion of a maxim, it is able to perform sophisticated 
+representing a maxim and making it the input to the obligation operator, which only my implementation 
+does. Because my implementation includes the notion of a maxim, it is able to perform sophisticated 
 reasoning as demonstrated in Sections \nameref{joking} and \nameref{murderer}. Staying faithful to the philosophical 
@@
 
-Both the naive and Kroy's interpretations fail to show the wrongness of conventional or natural acts. 
+Both raw DDL and Kroy's interpretation fail to show the wrongness of conventional or natural acts. 
 My system shows the wrongness of both natural and conventional acts because it is faithful to Korsgaard's 
 practical contradiction interpretation of the FUL, which is the canonical interpretation of the 
-FUL \citep{KorsgaardFUL}. This test passes due to the results shown in Chapter Applications, where I
+FUL \citep{KorsgaardFUL}. I run this test in Chapter Applications, where I
 use my system to reason about two ethical dilemmas, one which involves conventional acts and the other which
-involves natural acts.%
+involves natural acts. I present an additional example demonstrating that my implementation passes
+this test in Appendix \ref{weirdtests}.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %:%40=12%:%
-%:%49=14%:%
-%:%61=16%:%
-%:%62=17%:%
-%:%63=18%:%
+%:%41=13%:%
+%:%42=14%:%
+%:%43=15%:%
+%:%52=17%:%
 %:%64=19%:%
-%:%73=21%:%
-%:%85=23%:%
-%:%86=24%:%
-%:%87=25%:%
-%:%88=26%:%
+%:%65=20%:%
+%:%66=21%:%
+%:%67=22%:%
+%:%68=23%:%
+%:%77=25%:%
 %:%89=27%:%
+%:%90=28%:%
 %:%91=29%:%
-%:%92=29%:%
-%:%93=29%:%
-%:%96=31%:%
-%:%97=32%:%
-%:%98=33%:%
-%:%99=34%:%
+%:%92=30%:%
+%:%93=31%:%
+%:%95=33%:%
+%:%96=33%:%
+%:%97=33%:%
 %:%100=35%:%
@@
 %:%106=41%:%
+%:%107=42%:%
 %:%108=43%:%
-%:%109=43%:%
-%:%111=44%:%
-%:%112=45%:%
-%:%113=46%:%
-%:%114=47%:%
+%:%109=44%:%
+%:%110=45%:%
+%:%112=47%:%
+%:%113=47%:%
 %:%115=48%:%
@@
 %:%118=51%:%
-%:%126=53%:%
-%:%138=55%:%
-%:%139=56%:%
-%:%140=57%:%
-%:%141=58%:%
+%:%119=52%:%
+%:%120=53%:%
+%:%121=54%:%
+%:%122=55%:%
+%:%130=57%:%
 %:%142=59%:%
@@
 %:%162=79%:%
-%:%164=82%:%
+%:%163=80%:%
+%:%164=81%:%
 %:%165=82%:%
-%:%167=83%:%
-%:%168=84%:%
-%:%169=85%:%
+%:%167=85%:%
+%:%168=85%:%
 %:%170=86%:%
@@
 %:%174=90%:%
-%:%177=92%:%
-%:%178=93%:%
-%:%179=94%:%
+%:%175=91%:%
+%:%176=92%:%
+%:%177=93%:%
 %:%180=95%:%
@@
 %:%239=154%:%
-%:%240=155%:%
-%:%242=157%:%
+%:%241=156%:%
+%:%242=156%:%
 %:%243=157%:%
-%:%244=158%:%
+%:%245=158%:%
 %:%246=159%:%
@@
 %:%248=161%:%
-%:%249=162%:%
-%:%257=164%:%
+%:%256=163%:%
+%:%268=165%:%
 %:%269=166%:%
@@
 %:%318=215%:%
-%:%319=216%:%
-%:%321=219%:%
+%:%320=218%:%
+%:%321=218%:%
 %:%322=219%:%
-%:%323=220%:%
+%:%324=220%:%
 %:%325=221%:%
-%:%326=222%:%
+%:%328=223%:%
 %:%329=224%:%
@@
 %:%349=244%:%
-%:%350=245%:%
-%:%351=246%:%
-%:%353=249%:%
-%:%354=249%:%
-%:%355=250%:%
-%:%357=251%:%
-%:%358=252%:%
-%:%359=252%:%
+%:%351=247%:%
+%:%352=247%:%
+%:%353=248%:%
+%:%355=249%:%
+%:%356=250%:%
+%:%357=250%:%
+%:%360=256%:%
+%:%361=257%:%
 %:%362=258%:%
@@
 %:%370=266%:%
-%:%371=267%:%
 %:%372=268%:%
-%:%373=269%:%
-%:%374=270%:%
-%:%375=271%:%
-%:%377=273%:%
-%:%378=273%:%
-%:%379=274%:%
-%:%381=275%:%
+%:%373=268%:%
+%:%374=269%:%
+%:%376=270%:%
+%:%379=272%:%
+%:%380=273%:%
+%:%381=274%:%
+%:%382=275%:%
+%:%383=276%:%
 %:%384=277%:%
@@
 %:%411=304%:%
-%:%412=305%:%
 %:%413=306%:%
-%:%414=307%:%
-%:%415=308%:%
-%:%416=309%:%
-%:%417=310%:%
-%:%418=311%:%
-%:%419=312%:%
-%:%420=313%:%
-%:%421=314%:%
-%:%422=315%:%
-%:%424=317%:%
-%:%425=317%:%
-%:%426=318%:%
-%:%428=319%:%
-%:%429=320%:%
-%:%430=320%:%
-%:%431=321%:%
-%:%432=322%:%
-%:%433=322%:%
-%:%434=323%:%
-%:%436=324%:%
-%:%437=325%:%
-%:%440=327%:%
-%:%441=328%:%
-%:%442=329%:%
-%:%443=330%:%
-%:%445=332%:%
-%:%446=332%:%
-%:%447=333%:%
-%:%449=334%:%
-%:%450=335%:%
-%:%451=335%:%
-%:%452=336%:%
-%:%453=337%:%
-%:%454=337%:%
-%:%456=338%:%
-%:%457=339%:%
-%:%458=340%:%
-%:%466=342%:%
-%:%478=344%:%
-%:%479=345%:%
-%:%480=346%:%
-%:%481=347%:%
-%:%483=350%:%
-%:%484=350%:%
-%:%486=351%:%
-%:%487=352%:%
-%:%488=353%:%
-%:%489=354%:%
-%:%492=356%:%
-%:%493=357%:%
-%:%495=359%:%
-%:%496=359%:%
-%:%498=359%:%
-%:%502=359%:%
-%:%503=359%:%
-%:%504=360%:%
-%:%505=360%:%
-%:%506=360%:%
+%:%414=306%:%
+%:%415=307%:%
+%:%417=308%:%
+%:%418=309%:%
+%:%419=309%:%
+%:%420=310%:%
+%:%421=311%:%
+%:%422=311%:%
+%:%423=312%:%
+%:%425=313%:%
+%:%426=314%:%
+%:%429=316%:%
+%:%430=317%:%
+%:%431=318%:%
+%:%432=319%:%
+%:%434=321%:%
+%:%435=321%:%
+%:%436=322%:%
+%:%438=323%:%
+%:%439=324%:%
+%:%440=324%:%
+%:%441=325%:%
+%:%442=326%:%
+%:%443=326%:%
+%:%445=327%:%
+%:%446=328%:%
+%:%447=329%:%
+%:%455=331%:%
+%:%467=333%:%
+%:%468=334%:%
+%:%469=335%:%
+%:%470=336%:%
+%:%471=337%:%
+%:%472=338%:%
+%:%473=339%:%
+%:%474=340%:%
+%:%476=343%:%
+%:%477=343%:%
+%:%479=344%:%
+%:%480=345%:%
+%:%481=346%:%
+%:%482=347%:%
+%:%485=349%:%
+%:%486=350%:%
+%:%488=352%:%
+%:%489=352%:%
+%:%491=352%:%
+%:%495=352%:%
+%:%496=352%:%
+%:%497=353%:%
+%:%498=353%:%
+%:%499=353%:%
+%:%508=355%:%
+%:%509=356%:%
+%:%510=357%:%
+%:%511=358%:%
+%:%512=359%:%
+%:%513=360%:%
+%:%514=361%:%
 %:%515=362%:%
@@
 %:%532=379%:%
-%:%533=380%:%
 %:%534=381%:%
-%:%535=382%:%
-%:%536=383%:%
-%:%538=385%:%
-%:%539=385%:%
-%:%540=386%:%
-%:%542=387%:%
-%:%543=388%:%
-%:%546=390%:%
-%:%548=392%:%
-%:%549=392%:%
-%:%550=393%:%
-%:%552=394%:%
-%:%553=395%:%
-%:%554=395%:%
-%:%555=396%:%
-%:%556=397%:%
-%:%557=397%:%
-%:%558=398%:%
-%:%559=398%:%
-%:%561=398%:%
-%:%565=398%:%
-%:%566=398%:%
+%:%535=381%:%
+%:%536=382%:%
+%:%538=383%:%
+%:%539=384%:%
+%:%542=386%:%
+%:%544=388%:%
+%:%545=388%:%
+%:%546=389%:%
+%:%548=390%:%
+%:%549=391%:%
+%:%550=391%:%
+%:%551=392%:%
+%:%552=393%:%
+%:%553=393%:%
+%:%554=394%:%
+%:%555=394%:%
+%:%557=394%:%
+%:%561=394%:%
+%:%562=394%:%
+%:%564=395%:%
+%:%565=396%:%
+%:%566=397%:%
+%:%567=398%:%
 %:%568=399%:%
@@
 %:%570=401%:%
-%:%571=402%:%
-%:%572=403%:%
-%:%573=404%:%
+%:%580=403%:%
+%:%581=404%:%
+%:%582=405%:%
 %:%583=406%:%
@@
 %:%598=421%:%
-%:%599=422%:%
 %:%600=423%:%
-%:%601=424%:%
-%:%603=426%:%
+%:%601=423%:%
+%:%603=425%:%
 %:%604=426%:%
+%:%605=427%:%
 %:%606=428%:%
 %:%607=429%:%
-%:%608=430%:%
-%:%609=431%:%
-%:%610=432%:%
-%:%619=434%:%
+%:%616=431%:%
+%:%628=433%:%
+%:%629=434%:%
+%:%630=435%:%
 %:%631=436%:%
@@
 %:%649=454%:%
-%:%652=458%:%
-%:%653=459%:%
-%:%654=460%:%
+%:%650=455%:%
+%:%651=456%:%
+%:%652=457%:%
 %:%655=461%:%
@@
 %:%657=463%:%
-%:%660=465%:%
-%:%661=466%:%
-%:%662=467%:%
+%:%658=464%:%
+%:%659=465%:%
+%:%660=466%:%
 %:%663=468%:%
@@
 %:%669=474%:%
-%:%673=476%:%
-%:%674=477%:%
-%:%675=478%:%
+%:%670=475%:%
+%:%671=476%:%
+%:%672=477%:%
 %:%676=479%:%
@@
 %:%686=489%:%
+%:%687=490%:%
 %:%688=491%:%
-%:%689=491%:%
-%:%690=492%:%
-%:%693=493%:%
-%:%697=493%:%
-%:%698=493%:%
-%:%700=494%:%
-%:%701=495%:%
-%:%702=496%:%
+%:%689=492%:%
+%:%691=494%:%
+%:%692=494%:%
+%:%693=495%:%
+%:%696=496%:%
+%:%700=496%:%
+%:%701=496%:%
 %:%703=497%:%
-%:%709=497%:%
-%:%712=498%:%
-%:%713=499%:%
-%:%714=499%:%
-%:%715=500%:%
-%:%718=501%:%
-%:%722=501%:%
-%:%723=501%:%
-%:%725=502%:%
-%:%726=503%:%
-%:%727=504%:%
-%:%728=505%:%
-%:%738=507%:%
-%:%739=508%:%
-%:%740=509%:%
-%:%741=510%:%
-%:%742=511%:%
-%:%743=512%:%
-%:%744=513%:%
-%:%745=514%:%
-%:%746=515%:%
-%:%747=516%:%
-%:%748=517%:%
-%:%749=518%:%
-%:%750=519%:%
-%:%751=520%:%
-%:%752=521%:%
-%:%753=522%:%
-%:%754=523%:%
-%:%755=524%:%
-%:%756=525%:%
-%:%757=526%:%
-%:%758=527%:%
-%:%760=529%:%
-%:%761=529%:%
-%:%762=530%:%
-%:%765=531%:%
-%:%769=531%:%
-%:%770=531%:%
-%:%771=531%:%
-%:%773=532%:%
-%:%779=532%:%
-%:%782=533%:%
-%:%783=534%:%
-%:%784=534%:%
-%:%785=535%:%
-%:%786=536%:%
-%:%789=537%:%
-%:%793=537%:%
-%:%794=537%:%
-%:%795=537%:%
-%:%797=538%:%
-%:%798=539%:%
-%:%799=540%:%
-%:%809=542%:%
-%:%810=543%:%
-%:%811=544%:%
-%:%812=545%:%
-%:%813=546%:%
-%:%814=547%:%
-%:%815=548%:%
-%:%816=549%:%
-%:%817=550%:%
-%:%819=553%:%
-%:%820=553%:%
-%:%823=554%:%
-%:%827=554%:%
-%:%828=554%:%
-%:%830=555%:%
-%:%831=556%:%
+%:%704=498%:%
+%:%705=499%:%
+%:%706=499%:%
+%:%708=500%:%
+%:%709=501%:%
+%:%710=502%:%
+%:%711=503%:%
+%:%717=503%:%
+%:%720=504%:%
+%:%721=505%:%
+%:%722=505%:%
+%:%723=506%:%
+%:%726=507%:%
+%:%730=507%:%
+%:%731=507%:%
+%:%733=508%:%
+%:%734=509%:%
+%:%744=511%:%
+%:%745=512%:%
+%:%746=513%:%
+%:%747=514%:%
+%:%748=515%:%
+%:%749=516%:%
+%:%750=517%:%
+%:%751=518%:%
+%:%752=519%:%
+%:%753=520%:%
+%:%754=521%:%
+%:%755=522%:%
+%:%756=523%:%
+%:%757=524%:%
+%:%758=525%:%
+%:%759=526%:%
+%:%760=527%:%
+%:%761=528%:%
+%:%762=529%:%
+%:%763=530%:%
+%:%764=531%:%
+%:%766=533%:%
+%:%767=533%:%
+%:%768=534%:%
+%:%771=535%:%
+%:%775=535%:%
+%:%776=535%:%
+%:%777=535%:%
+%:%779=536%:%
+%:%785=536%:%
+%:%788=537%:%
+%:%789=538%:%
+%:%790=538%:%
+%:%791=539%:%
+%:%792=540%:%
+%:%795=541%:%
+%:%799=541%:%
+%:%800=541%:%
+%:%801=541%:%
+%:%803=542%:%
+%:%804=543%:%
+%:%805=544%:%
+%:%815=546%:%
+%:%816=547%:%
+%:%817=548%:%
+%:%818=549%:%
+%:%819=550%:%
+%:%820=551%:%
+%:%821=552%:%
+%:%822=553%:%
+%:%824=556%:%
+%:%825=556%:%
+%:%828=557%:%
 %:%832=557%:%
-%:%842=559%:%
-%:%843=560%:%
-%:%844=561%:%
-%:%845=562%:%
-%:%846=563%:%
-%:%847=564%:%
-%:%848=565%:%
-%:%850=567%:%
-%:%851=567%:%
-%:%852=568%:%
-%:%853=569%:%
+%:%833=557%:%
+%:%835=558%:%
+%:%836=559%:%
+%:%837=560%:%
+%:%847=562%:%
+%:%848=563%:%
+%:%849=564%:%
+%:%850=565%:%
+%:%851=566%:%
+%:%852=567%:%
+%:%853=568%:%
+%:%855=570%:%
 %:%856=570%:%
-%:%860=570%:%
-%:%861=570%:%
-%:%862=570%:%
-%:%864=571%:%
-%:%865=572%:%
+%:%857=571%:%
+%:%858=572%:%
+%:%861=573%:%
+%:%865=573%:%
 %:%866=573%:%
-%:%876=575%:%
-%:%877=576%:%
-%:%879=578%:%
-%:%880=578%:%
-%:%881=579%:%
-%:%882=580%:%
+%:%867=573%:%
+%:%869=574%:%
+%:%870=575%:%
+%:%871=576%:%
+%:%881=578%:%
+%:%882=579%:%
+%:%884=581%:%
 %:%885=581%:%
-%:%889=581%:%
-%:%890=581%:%
-%:%891=581%:%
-%:%893=582%:%
-%:%903=584%:%
-%:%904=585%:%
-%:%905=586%:%
-%:%906=587%:%
-%:%907=588%:%
-%:%908=589%:%
-%:%909=590%:%
-%:%910=591%:%
-%:%911=592%:%
-%:%912=593%:%
-%:%913=594%:%
-%:%914=595%:%
-%:%915=596%:%
-%:%916=597%:%
-%:%920=601%:%
-%:%921=602%:%
-%:%922=603%:%
-%:%923=604%:%
-%:%924=605%:%
-%:%925=606%:%
-%:%926=607%:%
-%:%927=608%:%
-%:%931=611%:%
-%:%932=612%:%
-%:%933=613%:%
-%:%934=614%:%
-%:%935=615%:%
-%:%936=616%:%
-%:%937=617%:%
-%:%938=618%:%
-%:%939=619%:%
-%:%940=620%:%
-%:%941=621%:%
-%:%942=622%:%
-%:%943=623%:%
-%:%944=624%:%
-%:%945=625%:%
-%:%946=626%:%
-%:%947=627%:%
-%:%948=628%:%
+%:%886=582%:%
+%:%887=583%:%
+%:%890=584%:%
+%:%894=584%:%
+%:%895=584%:%
+%:%896=584%:%
+%:%898=585%:%
+%:%908=587%:%
+%:%909=588%:%
+%:%910=589%:%
+%:%911=590%:%
+%:%912=591%:%
+%:%913=592%:%
+%:%914=593%:%
+%:%915=594%:%
+%:%916=595%:%
+%:%917=596%:%
+%:%918=597%:%
+%:%919=598%:%
+%:%920=599%:%
+%:%921=600%:%
+%:%925=604%:%
+%:%926=605%:%
+%:%927=606%:%
+%:%928=607%:%
+%:%929=608%:%
+%:%930=609%:%
+%:%931=610%:%
+%:%932=611%:%
+%:%936=614%:%
+%:%937=615%:%
+%:%938=616%:%
+%:%939=617%:%
+%:%940=618%:%
+%:%941=619%:%
+%:%942=620%:%
+%:%943=621%:%
+%:%944=622%:%
+%:%945=623%:%
+%:%946=624%:%
+%:%947=625%:%
+%:%948=626%:%
+%:%949=627%:%
+%:%950=628%:%
+%:%951=629%:%
+%:%952=630%:%
+%:%953=631%:%
+%:%954=632%:%

### 2022-02-18 paper/output/document/thesis_0_abstract.tex
one round of changes

@@
 problem from a computational perspective and rarely engages with philosophical literature on ethics, despite
-its clear relevance to the development of AI agents that can
-responsibly navigate the world. All decisions are moral decisions, including those that AI agents are actively 
-making today. If automated ethics draws on sophisticated philosophical literature, the ethical reasoning
+its relevance to the development of AI agents that can
+responsibly navigate the world. If automated ethics draws on sophisticated philosophical literature, the ethical reasoning
 underlying such decisions will be more nuanced, precise, consistent, and trustworthy. However, faithfully translating complex ethical theories
@@
 traditions, Kant's categorical imperative is the most natural to formalize because it is an inviolable 
-formal rule that requires less context than other ethical theories. I formalize Kant's categorical imperative 
+formal rule that requires less situational awareness than other ethical theories. I formalize Kant's categorical imperative 
 in Carmo and Jones's Dyadic Deontic Logic, implement this formalization 
@@
 intended victim. Finally, I examine the philosophical implications of this system, exploring its limitations 
-and its potential to help both AI agents and human beings better reason about ethics.
-
-Armed with relatively uncontroversial facts about the world, my system is able to correctly
-resolve complex moral dilemmas because it is grounded in philosophical literature.
-Moreover, because I automate an explicit ethical theory, the ethical reasoning underlying my system's judgements
-is interpretable by a human being. I implement this ethical theory using the Isabelle/HOL interactive theorem prover, which can 
-list the axioms and theorems used in a proof, so my system is explainable. This work serves as an early 
-proof-of-concept for philosophically mature AI agents and is one step towards the development of 
-responsible, trustworthy artificial intelligence.%
+and its potential to help both AI agents and human beings better reason about ethics. This work serves 
+as an early proof-of-concept for philosophically mature AI agents and is one step towards the development 
+of responsible, trustworthy artificial intelligence.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %:%45=32%:%
-%:%46=33%:%
-%:%47=34%:%
-%:%48=35%:%
-%:%49=36%:%
-%:%50=37%:%
-%:%51=38%:%
-%:%52=39%:%

### 2022-02-18 paper/output/document/thesis_1_intro.tex
one round of changes

@@
 (its negation violates the FUL), permissible (consistent with the FUL), or prohibited (violates the FUL) 
-by proving or refuting a theorem in my logic.
+by proving or refuting a theorem in my logic. Because the logic underlying these judgements is grounded
+in philosophical literature, my system can correctly resolve complex moral dilemmas with only relatively uncontroversial
+facts about the world. Moreover, because I automate an explicit ethical theory, the ethical reasoning 
+underlying my system's judgements is interpretable by a human being. I implement this ethical theory 
+using the Isabelle/HOL interactive theorem prover, which can list the axioms and theorems used in a 
+proof, so my system is explainable.
 
@@
 %:%197=168%:%
+%:%198=169%:%
+%:%199=170%:%
+%:%200=171%:%
+%:%201=172%:%
+%:%202=173%:%

### 2022-02-18 paper/output/document/thesis_2_methods.tex
one round of changes

@@
 %
-\isamarkupsubsection{Kantian Ethics \label{whykant}%
+\isamarkupsubsection{Choice to Automate Kantian Ethics \label{whykant}%
 }
@@
 attractive candidates for automation because rules are generally computationally tractable \cite[1]{powers}. 
-Intuitively, algorithms are rules or procedures for problem solving and deontology offers one such 
+Intuitively, algorithms are rules or procedures for problem solving and Kantian ethics (which is one kind 
+of deontological theory) offers one such 
 procedure for the problem of making ethical judgements. I will make this intuition precise by
-arguing that deontological ethics is natural to formalize because rules generally require little additional
-data about the world and are usually easy to represent to a computer. All ethical traditions have debates that an 
-automated ethical system will need to take a stance on, but these debates are less frequent and controversial
-for deontological ethics than for consequentialism and virtue ethics.
-
-I do not aim to show that deontology is the only tractable theory to automate or
+arguing that Kantian ethics is natural to formalize because it prescribes moral rules that require 
+little additional data about the world and are easy to represent to a computer. I argue that, compared to 
+consequentialism and virtue ethics,\footnote{Technically, virtue ethics and
+consequentialism are broad ethical traditions, while Kantian ethics is a specific ethical theory within
+the deontological tradition, but``if any philosopher is regarded as central
+to deontological moral theories, it is surely Immanuel Kant" \citep{sepdeont}. Out of the three major ethical
+traditions, deontology has the most central representative in the form of Kant. Deontology's comparatively 
+greater focus on Kant means that my choice of Kant as a guiding figure is less controversial for deontologists 
+than, for example, the choice of Bentham as the guiding figure of consequentialism.} Kantian ethics is 
+more amenable to automation.
+
+I do not aim to show that Kantian ethics is the only tractable theory to automate or
 to present a comprehensive overview of all consequentialist or virtue ethical theories. Instead, I 
@@
 as an early proof-of-concept, I choose to automate an ethical theory that 
-poses fewer challenges than others.
-
-I first present deontological ethics, then consequentialism, and finally virtue ethics. For each 
+poses fewer challenges than others. All ethical traditions have debates that an 
+automated ethical system will need to take a stance on, but these debates are less frequent and controversial
+for Kantian ethics than for consequentialism and virtue ethics.
+
+I first present consequentialism, then virtue ethics, and finally Kantian ethics. For each 
 tradition, I present a crash course for non-philosophers and then explain some obstacles to automation, 
-arguing that these obstacles are weakest in the case of deontology. Finally, I will present the specific 
-deontological theory I am automating (Kantian ethics) and will argue that it is comparatively easier
-to formalize.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\isatagdocument
-%
-\isamarkupsubsubsection{Deontological Ethics\label{deontology}%
-}
-\isamarkuptrue%
-%
-\endisatagdocument
-{\isafolddocument}%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\begin{isamarkuptext}%
-Deontological theories evaluate actions as permissible, obligatory, or prohibited and judge actions 
-not on their consequences, but rather on ``confirmity with a moral norm" \citep{sepdeont}. In other words, 
-deontological theories define a set of moral rules and evaluate actions using
-these rules. Deontologists believe that we should never violate any moral law. A wrong
-choice is wrong, regardless of its consequences.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-Deontology is an attractive candidate for formalization because computers tend to 
-understand rules; programming languages are designed to teach computers algorithms. Deontological
-ethical theories give inviolable rules that an automated agent can apply. Moreover, because deontological 
-theories focus on the action itself, they require relatively little data. A deontological moral judgement does not require
-as much information about context, consequences, or moral character as the other theories presented later in this
-section. All that matters is the action and some limited set of circumstances in which it is performed.
-
-Like all ethical traditions, deontology has debates that any implementation of automated deontological
-ethics must resolve. Deontologists disagree about whether ethics should focus on agents' actions or 
-on the rights of those impacted by an action. Different deontological theories have different conceptions 
-of what an action is, from the physical act itself to the agent's mental state at the time of acting 
-to the principle upon which the agent acted.
-
-While these debates are open, ``if any philosopher is regarded as central
-to deontological moral theories, it is surely Immanuel Kant" \citep{sepdeont}. Out of the three ethical
-traditions considered in this section, deontology has the most central representative in the form of 
-Kant. In this paper, I will 
-formalize Kantian ethics. Deontology's comparatively greater focus on Kant means that the choice of 
-Kant as a guiding figure will be less controversial to deontologists than, for example, the choice of Bentham
-as the guiding figure of consequentialism. Moreover, at the end of this section, I also argue that 
-internal debates in the part of Kantian ethics that I focus on tend to be less controversial than those
-in the consequentialist or virtue ethical traditions.%
+arguing that these obstacles are weakest in the case of Kantian ethics.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 Because consequentialism evaluates the state of affairs following an action, this kind of ethical 
-reasoning requires more knowledge about the state of the world than deontology. Consequentialism
+reasoning requires more knowledge about the state of the world than Kantian ethics. Consequentialism
 requires knowledge about some or all consequences following an action. This requires that an automated 
@@
 more complex and affect more people, the computational time and space required to calculate and store
-their consequences increases. Deontology, on the other hand, does not suffer this scaling
-challenge because acts that affect 1 person and acts that affect 1 million people share the same
-representation.
+their consequences increases. Kantian ethics, on the other hand, does not suffer this scaling
+challenge because it evaluates the acts themselves, and acts that affect 1 person and acts that 
+affect 1 million people share the same representation.
 
@@
 \citet{powers} identifies this as a challenge for automating Kantian ethics and briefly sketches 
-solutions from \citet{constofreason}, \citet{silber}, and \citet{rawlsconstructivism}. For more on 
-morally relevant circumstances, see Section WhatIsAMaxim.} Because deontology merely evaluates a 
+solutions from \citet{constofreason}, \citet{silber}, and \citet{rawlsconstructivism}. For my approach to
+morally relevant circumstances, see Section \ref{whatisamaxim}.} Because deontology merely evaluates a 
 single action, the surface of this debate is much smaller than debates about circumstances and 
@@
 following the act. All ethical theories relativize their judgements to the situation in which an act 
-is performed, but consequentialism requires far more knowledge about the world than deontology.%
+is performed, but consequentialism requires far more knowledge about the world than Kantian ethics.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 which requires massive common-sense and increases room for doubting the system's judgements. This may be 
-a tractable problem, but it is much more difficult than the equivalent deontological task of formulating
+a tractable problem, but it is much more difficult than the equivalent Kantian task of formulating
 and evaluating an action.%
@@
 Another difficulty with automating virtue ethics is that the unit of evaluation for virtue ethics
-is often a person's entire moral character. While deontologists evaluate the act itself, virtue ethicists 
+is often a person's entire moral character. While Kantians evaluate the act itself, virtue ethicists 
 evaluate the actor's moral character and their 
@@
 Formalizing the concept of character appears to require significant philosophical and computational
-progress, whereas deontology immediately presents a formal rule to implement.%
+progress, whereas Kantian ethics immediately presents a formal rule to implement.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 that cultivating virtuous action requires making such action habitual through moral education \citep{aristotle}. This
-implies that ethical behavior can be learned from some dataset of virtuous acts, either those 
-prescribed by a moral teacher or those that a virtuous ideal agent would undertake. These 
+implies that ethical behavior can be learned from some dataset of virtuous acts, such as
+those that an ideal virtuous agent would undertake. These 
 theories seem to point towards a machine learning approach to automated ethics, in which ethics is 
@@
 \begin{isamarkuptext}%
-In this paper I focus on Kantian ethics, a specific branch of deontology. Kant's theory is centered 
+In this paper I focus on Kantian ethics. Kant's theory is centered 
 on practical reason, which is the kind of reason that we 
@@
 
-Not only does evaluating Kantian ethics focus on a maxim, a maxim itself is an object
-with a thin representation for a computer, as compared to more complex objects like states of 
-affairs or moral character. Later in my project, I argue that a maxim can be represented simply as 
-a tuple of circumstances, act, and goal.\footnote{For more, see Section What is a Maxim?} This representation
-is simple and efficient, especially when compared to the representation of a causal chain or a state of 
-affairs or moral character. This property not only reduces the computational complexity
+A maxim itself is an object with a thin representation for a computer, as compared to more complex 
+objects like states of affairs or moral character. Later in my project, I argue that a maxim can be 
+represented simply as a tuple of circumstances, act, and goal.\footnote{For more, see Section \ref{whatisamaxim}.} 
+This representation is simple and efficient, especially when compared to the representations of a causal 
+chain or a state of affairs or moral character. This property not only reduces the computational complexity
 (in terms of time and space) of representing a maxim, but it also makes the system easier for human reasoners
@@
 is universalizable because if everyone marries who they love, some men will marry women and others will
-marry men.} My system does not need to answer this question because I assume a well-formed
+marry men.} My system does not need to answer this question because I assume a properly crafted
 maxim as input and apply the categorical imperative to this input. Using my system in a fully automated
@@
 %:%89=45%:%
-%:%98=48%:%
-%:%110=50%:%
-%:%111=51%:%
-%:%112=52%:%
-%:%113=53%:%
-%:%114=54%:%
-%:%118=56%:%
-%:%119=57%:%
-%:%120=58%:%
-%:%121=59%:%
-%:%122=60%:%
-%:%123=61%:%
-%:%124=62%:%
-%:%125=63%:%
-%:%126=64%:%
-%:%127=65%:%
-%:%128=66%:%
+%:%90=46%:%
+%:%91=47%:%
+%:%92=48%:%
+%:%93=49%:%
+%:%94=50%:%
+%:%95=51%:%
+%:%96=52%:%
+%:%105=55%:%
+%:%117=57%:%
+%:%118=58%:%
+%:%119=59%:%
+%:%120=60%:%
+%:%121=61%:%
+%:%122=62%:%
+%:%123=63%:%
+%:%124=64%:%
+%:%125=65%:%
 %:%129=67%:%
-%:%130=68%:%
-%:%131=69%:%
-%:%132=70%:%
-%:%133=71%:%
-%:%134=72%:%
-%:%135=73%:%
-%:%136=74%:%
-%:%137=75%:%
-%:%138=76%:%
-%:%139=77%:%
-%:%148=80%:%
-%:%160=82%:%
-%:%161=83%:%
-%:%162=84%:%
-%:%163=85%:%
-%:%164=86%:%
-%:%165=87%:%
-%:%166=88%:%
-%:%167=89%:%
-%:%168=90%:%
-%:%172=92%:%
-%:%176=94%:%
-%:%177=95%:%
-%:%178=96%:%
-%:%179=97%:%
-%:%180=98%:%
-%:%181=99%:%
-%:%182=100%:%
-%:%183=101%:%
-%:%184=102%:%
-%:%185=103%:%
-%:%186=104%:%
-%:%187=105%:%
-%:%188=106%:%
-%:%189=107%:%
-%:%190=108%:%
-%:%191=109%:%
-%:%192=110%:%
-%:%193=111%:%
-%:%194=112%:%
-%:%195=113%:%
-%:%196=114%:%
-%:%197=115%:%
-%:%198=116%:%
-%:%199=117%:%
-%:%200=118%:%
-%:%204=121%:%
-%:%208=123%:%
-%:%209=124%:%
-%:%210=125%:%
-%:%211=126%:%
-%:%212=127%:%
-%:%213=128%:%
-%:%214=129%:%
-%:%215=130%:%
-%:%216=131%:%
-%:%217=132%:%
-%:%218=133%:%
-%:%219=134%:%
-%:%220=135%:%
-%:%221=136%:%
-%:%222=137%:%
-%:%223=138%:%
-%:%227=140%:%
-%:%231=142%:%
-%:%232=143%:%
-%:%233=144%:%
-%:%234=145%:%
-%:%235=146%:%
-%:%236=147%:%
-%:%237=148%:%
-%:%238=149%:%
-%:%239=150%:%
-%:%240=151%:%
-%:%241=152%:%
-%:%242=153%:%
-%:%243=154%:%
-%:%244=155%:%
-%:%245=156%:%
-%:%246=157%:%
-%:%247=158%:%
-%:%251=161%:%
-%:%255=164%:%
-%:%256=165%:%
-%:%257=166%:%
-%:%258=167%:%
-%:%259=168%:%
-%:%260=169%:%
-%:%261=170%:%
-%:%262=171%:%
-%:%263=172%:%
-%:%264=173%:%
-%:%265=174%:%
-%:%266=175%:%
-%:%267=176%:%
-%:%268=177%:%
-%:%269=178%:%
+%:%133=69%:%
+%:%134=70%:%
+%:%135=71%:%
+%:%136=72%:%
+%:%137=73%:%
+%:%138=74%:%
+%:%139=75%:%
+%:%140=76%:%
+%:%141=77%:%
+%:%142=78%:%
+%:%143=79%:%
+%:%144=80%:%
+%:%145=81%:%
+%:%146=82%:%
+%:%147=83%:%
+%:%148=84%:%
+%:%149=85%:%
+%:%150=86%:%
+%:%151=87%:%
+%:%152=88%:%
+%:%153=89%:%
+%:%154=90%:%
+%:%155=91%:%
+%:%156=92%:%
+%:%157=93%:%
+%:%161=96%:%
+%:%165=98%:%
+%:%166=99%:%
+%:%167=100%:%
+%:%168=101%:%
+%:%169=102%:%
+%:%170=103%:%
+%:%171=104%:%
+%:%172=105%:%
+%:%173=106%:%
+%:%174=107%:%
+%:%175=108%:%
+%:%176=109%:%
+%:%177=110%:%
+%:%178=111%:%
+%:%179=112%:%
+%:%180=113%:%
+%:%184=115%:%
+%:%188=117%:%
+%:%189=118%:%
+%:%190=119%:%
+%:%191=120%:%
+%:%192=121%:%
+%:%193=122%:%
+%:%194=123%:%
+%:%195=124%:%
+%:%196=125%:%
+%:%197=126%:%
+%:%198=127%:%
+%:%199=128%:%
+%:%200=129%:%
+%:%201=130%:%
+%:%202=131%:%
+%:%203=132%:%
+%:%204=133%:%
+%:%208=136%:%
+%:%212=139%:%
+%:%213=140%:%
+%:%214=141%:%
+%:%215=142%:%
+%:%216=143%:%
+%:%217=144%:%
+%:%218=145%:%
+%:%219=146%:%
+%:%220=147%:%
+%:%221=148%:%
+%:%222=149%:%
+%:%223=150%:%
+%:%224=151%:%
+%:%225=152%:%
+%:%226=153%:%
+%:%227=154%:%
+%:%236=157%:%
+%:%248=159%:%
+%:%249=160%:%
+%:%250=161%:%
+%:%251=162%:%
+%:%252=163%:%
+%:%253=164%:%
+%:%254=165%:%
+%:%258=169%:%
+%:%259=170%:%
+%:%260=171%:%
+%:%261=172%:%
+%:%262=173%:%
+%:%263=174%:%
+%:%264=175%:%
+%:%265=176%:%
+%:%266=177%:%
 %:%270=179%:%
-%:%279=182%:%
-%:%291=184%:%
-%:%292=185%:%
-%:%293=186%:%
-%:%294=187%:%
-%:%295=188%:%
-%:%296=189%:%
-%:%297=190%:%
-%:%301=194%:%
-%:%302=195%:%
-%:%303=196%:%
-%:%304=197%:%
-%:%305=198%:%
-%:%306=199%:%
-%:%307=200%:%
-%:%308=201%:%
-%:%309=202%:%
-%:%313=204%:%
-%:%317=206%:%
-%:%318=207%:%
-%:%319=208%:%
-%:%320=209%:%
-%:%321=210%:%
-%:%322=211%:%
-%:%323=212%:%
-%:%324=213%:%
-%:%325=214%:%
-%:%326=215%:%
-%:%327=216%:%
-%:%328=217%:%
-%:%329=218%:%
-%:%330=219%:%
-%:%331=220%:%
-%:%332=221%:%
-%:%333=222%:%
-%:%334=223%:%
-%:%335=224%:%
-%:%336=225%:%
-%:%337=226%:%
-%:%338=227%:%
-%:%339=228%:%
-%:%340=229%:%
-%:%341=230%:%
-%:%342=231%:%
-%:%343=232%:%
-%:%352=235%:%
-%:%364=237%:%
-%:%365=238%:%
-%:%366=239%:%
-%:%367=240%:%
-%:%368=241%:%
-%:%369=242%:%
-%:%370=243%:%
-%:%371=244%:%
-%:%372=245%:%
-%:%373=246%:%
-%:%374=247%:%
-%:%375=248%:%
-%:%376=249%:%
-%:%377=250%:%
-%:%378=251%:%
-%:%379=252%:%
-%:%380=253%:%
-%:%381=254%:%
-%:%382=255%:%
-%:%383=256%:%
-%:%384=257%:%
-%:%385=258%:%
-%:%386=259%:%
-%:%387=260%:%
-%:%388=261%:%
-%:%389=262%:%
-%:%390=263%:%
-%:%391=264%:%
-%:%392=265%:%
-%:%393=266%:%
-%:%394=267%:%
-%:%395=268%:%
-%:%396=269%:%
-%:%397=270%:%
-%:%398=271%:%
-%:%399=272%:%
-%:%400=273%:%
-%:%401=274%:%
-%:%402=275%:%
-%:%403=276%:%
-%:%404=277%:%
-%:%405=278%:%
-%:%406=279%:%
-%:%407=280%:%
-%:%408=281%:%
-%:%409=282%:%
-%:%410=283%:%
-%:%411=284%:%
-%:%412=285%:%
-%:%413=286%:%
-%:%414=287%:%
-%:%415=288%:%
-%:%416=289%:%
-%:%417=290%:%
-%:%418=291%:%
-%:%419=292%:%
-%:%420=293%:%
-%:%424=296%:%
-%:%428=298%:%
-%:%429=299%:%
-%:%430=300%:%
-%:%431=301%:%
-%:%432=302%:%
-%:%433=303%:%
-%:%434=304%:%
-%:%435=305%:%
-%:%436=306%:%
-%:%437=307%:%
-%:%438=308%:%
-%:%439=309%:%
-%:%440=310%:%
-%:%441=311%:%
-%:%442=312%:%
-%:%443=313%:%
-%:%444=314%:%
-%:%445=315%:%
-%:%446=316%:%
-%:%447=317%:%
-%:%448=318%:%
-%:%452=321%:%
-%:%456=323%:%
-%:%457=324%:%
-%:%458=325%:%
-%:%459=326%:%
-%:%460=327%:%
-%:%461=328%:%
-%:%462=329%:%
-%:%463=330%:%
-%:%464=331%:%
-%:%465=332%:%
-%:%466=333%:%
-%:%467=334%:%
-%:%468=335%:%
-%:%469=336%:%
-%:%470=337%:%
-%:%471=338%:%
-%:%472=339%:%
-%:%473=340%:%
-%:%474=341%:%
-%:%475=342%:%
-%:%476=343%:%
-%:%477=344%:%
-%:%478=345%:%
-%:%479=346%:%
-%:%480=347%:%
-%:%481=348%:%
-%:%482=349%:%
-%:%483=350%:%
-%:%484=351%:%
-%:%485=352%:%
-%:%486=353%:%
-%:%487=354%:%
-%:%496=356%:%
-%:%508=359%:%
-%:%509=360%:%
-%:%510=361%:%
-%:%511=362%:%
-%:%512=363%:%
-%:%513=364%:%
-%:%514=365%:%
-%:%515=366%:%
-%:%516=367%:%
-%:%517=368%:%
-%:%518=369%:%
-%:%519=370%:%
-%:%520=371%:%
-%:%521=372%:%
-%:%522=373%:%
-%:%523=374%:%
-%:%524=375%:%
-%:%525=376%:%
-%:%526=377%:%
-%:%527=378%:%
-%:%528=379%:%
-%:%529=380%:%
-%:%530=381%:%
-%:%531=382%:%
-%:%532=383%:%
-%:%533=384%:%
-%:%534=385%:%
-%:%535=386%:%
-%:%536=387%:%
-%:%537=388%:%
-%:%538=389%:%
-%:%539=390%:%
+%:%274=181%:%
+%:%275=182%:%
+%:%276=183%:%
+%:%277=184%:%
+%:%278=185%:%
+%:%279=186%:%
+%:%280=187%:%
+%:%281=188%:%
+%:%282=189%:%
+%:%283=190%:%
+%:%284=191%:%
+%:%285=192%:%
+%:%286=193%:%
+%:%287=194%:%
+%:%288=195%:%
+%:%289=196%:%
+%:%290=197%:%
+%:%291=198%:%
+%:%292=199%:%
+%:%293=200%:%
+%:%294=201%:%
+%:%295=202%:%
+%:%296=203%:%
+%:%297=204%:%
+%:%298=205%:%
+%:%299=206%:%
+%:%300=207%:%
+%:%309=210%:%
+%:%321=212%:%
+%:%322=213%:%
+%:%323=214%:%
+%:%324=215%:%
+%:%325=216%:%
+%:%326=217%:%
+%:%327=218%:%
+%:%328=219%:%
+%:%329=220%:%
+%:%330=221%:%
+%:%331=222%:%
+%:%332=223%:%
+%:%333=224%:%
+%:%334=225%:%
+%:%335=226%:%
+%:%336=227%:%
+%:%337=228%:%
+%:%338=229%:%
+%:%339=230%:%
+%:%340=231%:%
+%:%341=232%:%
+%:%342=233%:%
+%:%343=234%:%
+%:%344=235%:%
+%:%345=236%:%
+%:%346=237%:%
+%:%347=238%:%
+%:%348=239%:%
+%:%349=240%:%
+%:%350=241%:%
+%:%351=242%:%
+%:%352=243%:%
+%:%353=244%:%
+%:%354=245%:%
+%:%355=246%:%
+%:%356=247%:%
+%:%357=248%:%
+%:%358=249%:%
+%:%359=250%:%
+%:%360=251%:%
+%:%361=252%:%
+%:%362=253%:%
+%:%363=254%:%
+%:%364=255%:%
+%:%365=256%:%
+%:%366=257%:%
+%:%367=258%:%
+%:%368=259%:%
+%:%369=260%:%
+%:%370=261%:%
+%:%371=262%:%
+%:%372=263%:%
+%:%373=264%:%
+%:%374=265%:%
+%:%375=266%:%
+%:%376=267%:%
+%:%377=268%:%
+%:%381=271%:%
+%:%385=273%:%
+%:%386=274%:%
+%:%387=275%:%
+%:%388=276%:%
+%:%389=277%:%
+%:%390=278%:%
+%:%391=279%:%
+%:%392=280%:%
+%:%393=281%:%
+%:%394=282%:%
+%:%395=283%:%
+%:%396=284%:%
+%:%397=285%:%
+%:%398=286%:%
+%:%399=287%:%
+%:%400=288%:%
+%:%401=289%:%
+%:%402=290%:%
+%:%403=291%:%
+%:%404=292%:%
+%:%408=295%:%
+%:%412=297%:%
+%:%413=298%:%
+%:%414=299%:%
+%:%415=300%:%
+%:%416=301%:%
+%:%417=302%:%
+%:%418=303%:%
+%:%419=304%:%
+%:%420=305%:%
+%:%421=306%:%
+%:%422=307%:%
+%:%423=308%:%
+%:%424=309%:%
+%:%425=310%:%
+%:%426=311%:%
+%:%427=312%:%
+%:%428=313%:%
+%:%429=314%:%
+%:%430=315%:%
+%:%431=316%:%
+%:%432=317%:%
+%:%433=318%:%
+%:%434=319%:%
+%:%435=320%:%
+%:%436=321%:%
+%:%437=322%:%
+%:%438=323%:%
+%:%439=324%:%
+%:%440=325%:%
+%:%441=326%:%
+%:%442=327%:%
+%:%443=328%:%
+%:%452=330%:%
+%:%464=333%:%
+%:%465=334%:%
+%:%466=335%:%
+%:%467=336%:%
+%:%468=337%:%
+%:%469=338%:%
+%:%470=339%:%
+%:%471=340%:%
+%:%472=341%:%
+%:%473=342%:%
+%:%474=343%:%
+%:%475=344%:%
+%:%476=345%:%
+%:%477=346%:%
+%:%478=347%:%
+%:%479=348%:%
+%:%480=349%:%
+%:%481=350%:%
+%:%482=351%:%
+%:%483=352%:%
+%:%484=353%:%
+%:%485=354%:%
+%:%486=355%:%
+%:%487=356%:%
+%:%488=357%:%
+%:%489=358%:%
+%:%490=359%:%
+%:%491=360%:%
+%:%492=361%:%
+%:%493=362%:%
+%:%494=363%:%
+%:%495=364%:%
+%:%496=365%:%
+%:%497=366%:%
+%:%498=367%:%
+%:%499=368%:%
+%:%500=369%:%
+%:%501=370%:%
+%:%502=371%:%
+%:%503=372%:%
+%:%504=373%:%
+%:%505=374%:%
+%:%506=375%:%
+%:%507=376%:%
+%:%508=377%:%
+%:%509=378%:%
+%:%510=379%:%
+%:%511=380%:%
+%:%512=381%:%
+%:%513=382%:%
+%:%514=383%:%
+%:%523=385%:%
+%:%535=387%:%
+%:%536=388%:%
 %:%540=391%:%
@@
 %:%558=409%:%
-%:%567=411%:%
-%:%579=413%:%
-%:%580=414%:%
-%:%584=417%:%
-%:%585=418%:%
-%:%586=419%:%
-%:%587=420%:%
-%:%588=421%:%
-%:%589=422%:%
-%:%590=423%:%
-%:%591=424%:%
-%:%592=425%:%
-%:%593=426%:%
-%:%594=427%:%
-%:%595=428%:%
-%:%596=429%:%
-%:%597=430%:%
-%:%598=431%:%
-%:%599=432%:%
-%:%600=433%:%
-%:%601=434%:%
-%:%602=435%:%
-%:%603=436%:%
-%:%604=437%:%
-%:%605=438%:%
-%:%606=439%:%
-%:%607=440%:%
-%:%608=441%:%
-%:%609=442%:%
-%:%610=443%:%
-%:%611=444%:%
-%:%615=446%:%
-%:%616=447%:%
-%:%617=448%:%
-%:%618=449%:%
-%:%619=450%:%
-%:%620=451%:%
-%:%621=452%:%
-%:%622=453%:%
-%:%623=454%:%
-%:%624=455%:%
-%:%625=456%:%
-%:%626=457%:%
-%:%627=458%:%
-%:%628=459%:%
-%:%629=460%:%
-%:%630=461%:%
-%:%631=462%:%
-%:%632=463%:%
-%:%633=464%:%
-%:%634=465%:%
-%:%635=466%:%
-%:%636=467%:%
-%:%637=468%:%
-%:%638=469%:%
-%:%639=470%:%
-%:%640=471%:%
-%:%641=472%:%
-%:%650=475%:%
-%:%662=477%:%
-%:%663=478%:%
-%:%664=479%:%
-%:%665=480%:%
-%:%666=481%:%
-%:%667=482%:%
-%:%676=485%:%
-%:%688=487%:%
-%:%689=488%:%
-%:%690=489%:%
-%:%692=491%:%
-%:%693=491%:%
-%:%694=491%:%
-%:%695=491%:%
-%:%697=492%:%
-%:%698=493%:%
-%:%699=493%:%
-%:%700=494%:%
-%:%701=495%:%
-%:%702=495%:%
-%:%703=495%:%
-%:%704=495%:%
-%:%706=496%:%
-%:%707=497%:%
-%:%708=497%:%
-%:%711=511%:%
-%:%712=512%:%
-%:%713=513%:%
-%:%715=515%:%
-%:%716=515%:%
-%:%717=515%:%
-%:%718=515%:%
-%:%719=516%:%
-%:%720=516%:%
-%:%721=516%:%
-%:%724=520%:%
-%:%725=521%:%
-%:%726=522%:%
-%:%727=523%:%
-%:%729=525%:%
-%:%730=525%:%
-%:%731=549%:%
-%:%732=550%:%
-%:%734=551%:%
-%:%735=552%:%
-%:%736=553%:%
-%:%737=554%:%
-%:%738=554%:%
-%:%746=561%:%
-%:%758=563%:%
-%:%759=564%:%
-%:%760=565%:%
-%:%761=566%:%
-%:%762=567%:%
-%:%763=568%:%
-%:%764=569%:%
-%:%768=585%:%
-%:%770=586%:%
-%:%771=586%:%
-%:%772=587%:%
-%:%774=588%:%
-%:%775=589%:%
-%:%776=589%:%
-%:%777=590%:%
-%:%778=590%:%
-%:%779=591%:%
-%:%781=592%:%
-%:%784=594%:%
-%:%786=595%:%
-%:%787=595%:%
-%:%788=596%:%
-%:%790=597%:%
-%:%791=597%:%
-%:%794=617%:%
-%:%795=618%:%
-%:%797=619%:%
-%:%798=619%:%
-%:%799=620%:%
-%:%800=621%:%
-%:%801=621%:%
-%:%802=622%:%
-%:%803=623%:%
-%:%804=623%:%
-%:%805=624%:%
-%:%807=625%:%
-%:%808=626%:%
+%:%559=410%:%
+%:%560=411%:%
+%:%561=412%:%
+%:%562=413%:%
+%:%563=414%:%
+%:%564=415%:%
+%:%565=416%:%
+%:%566=417%:%
+%:%567=418%:%
+%:%571=420%:%
+%:%572=421%:%
+%:%573=422%:%
+%:%574=423%:%
+%:%575=424%:%
+%:%576=425%:%
+%:%577=426%:%
+%:%578=427%:%
+%:%579=428%:%
+%:%580=429%:%
+%:%581=430%:%
+%:%582=431%:%
+%:%583=432%:%
+%:%584=433%:%
+%:%585=434%:%
+%:%586=435%:%
+%:%587=436%:%
+%:%588=437%:%
+%:%589=438%:%
+%:%590=439%:%
+%:%591=440%:%
+%:%592=441%:%
+%:%593=442%:%
+%:%594=443%:%
+%:%595=444%:%
+%:%596=445%:%
+%:%597=446%:%
+%:%606=449%:%
+%:%618=451%:%
+%:%619=452%:%
+%:%620=453%:%
+%:%621=454%:%
+%:%622=455%:%
+%:%623=456%:%
+%:%632=459%:%
+%:%644=461%:%
+%:%645=462%:%
+%:%646=463%:%
+%:%648=465%:%
+%:%649=465%:%
+%:%650=465%:%
+%:%651=465%:%
+%:%653=466%:%
+%:%654=467%:%
+%:%655=467%:%
+%:%656=468%:%
+%:%657=469%:%
+%:%658=469%:%
+%:%659=469%:%
+%:%660=469%:%
+%:%662=470%:%
+%:%663=471%:%
+%:%664=471%:%
+%:%667=485%:%
+%:%668=486%:%
+%:%669=487%:%
+%:%671=489%:%
+%:%672=489%:%
+%:%673=489%:%
+%:%674=489%:%
+%:%675=490%:%
+%:%676=490%:%
+%:%677=490%:%
+%:%680=494%:%
+%:%681=495%:%
+%:%682=496%:%
+%:%683=497%:%
+%:%685=499%:%
+%:%686=499%:%
+%:%687=523%:%
+%:%688=524%:%
+%:%690=525%:%
+%:%691=526%:%
+%:%692=527%:%
+%:%693=528%:%
+%:%694=528%:%
+%:%702=535%:%
+%:%714=537%:%
+%:%715=538%:%
+%:%716=539%:%
+%:%717=540%:%
+%:%718=541%:%
+%:%719=542%:%
+%:%720=543%:%
+%:%724=559%:%
+%:%726=560%:%
+%:%727=560%:%
+%:%728=561%:%
+%:%730=562%:%
+%:%731=563%:%
+%:%732=563%:%
+%:%733=564%:%
+%:%734=564%:%
+%:%735=565%:%
+%:%737=566%:%
+%:%740=568%:%
+%:%742=569%:%
+%:%743=569%:%
+%:%744=570%:%
+%:%746=571%:%
+%:%747=571%:%
+%:%750=591%:%
+%:%751=592%:%
+%:%753=593%:%
+%:%754=593%:%
+%:%755=594%:%
+%:%756=595%:%
+%:%757=595%:%
+%:%758=596%:%
+%:%759=597%:%
+%:%760=597%:%
+%:%761=598%:%
+%:%763=599%:%
+%:%764=600%:%
+%:%767=602%:%
+%:%769=603%:%
+%:%770=603%:%
+%:%771=604%:%
+%:%773=605%:%
+%:%774=605%:%
+%:%777=613%:%
+%:%778=614%:%
+%:%779=615%:%
+%:%780=616%:%
+%:%782=619%:%
+%:%783=619%:%
+%:%784=619%:%
+%:%786=619%:%
+%:%790=619%:%
+%:%791=619%:%
+%:%793=620%:%
+%:%794=621%:%
+%:%795=621%:%
+%:%797=622%:%
+%:%798=623%:%
+%:%799=624%:%
+%:%809=626%:%
+%:%810=627%:%
 %:%811=628%:%
-%:%813=629%:%
-%:%814=629%:%
-%:%815=630%:%
-%:%817=631%:%
-%:%818=631%:%
-%:%821=639%:%
-%:%822=640%:%
-%:%823=641%:%
-%:%824=642%:%
-%:%826=645%:%
-%:%827=645%:%
-%:%828=645%:%
-%:%830=645%:%
-%:%834=645%:%
-%:%835=645%:%
-%:%837=646%:%
-%:%838=647%:%
-%:%839=647%:%
-%:%841=648%:%
-%:%842=649%:%
-%:%843=650%:%
-%:%853=652%:%
-%:%854=653%:%
-%:%855=654%:%

### 2022-02-18 paper/output/document/AMA_possible.tex
started chapter 4

@@
 \begin{isamarkuptext}%
+SAY THAT ALSO APPLIES TO VIRTUE ETHICS AND THAT MIMICING IS GOOD
+
 Many philosophers are averse to the idea that a computer could perform ethical
@@
 %:%147=119%:%
-%:%150=122%:%
-%:%151=123%:%
+%:%148=120%:%
+%:%149=121%:%
 %:%152=124%:%
@@
 %:%155=127%:%
-%:%158=129%:%
-%:%159=130%:%
+%:%156=128%:%
+%:%157=129%:%
 %:%160=131%:%
@@
 %:%172=143%:%
+%:%173=144%:%
+%:%174=145%:%

### 2022-02-18 paper/output/document/appendix.tex
started chapter 4

@@
 \begin{isamarkuptext}%
+Add something about how I don't like KG's view because it's weaker, action will end up including
+circumstances, it would have made my life easier but you can't apply it
+
 Kitcher begins with O'Niell's circumstance, act, goal view and expands it to include the motive 
@@
 %:%62=33%:%
-%:%97=62%:%
-%:%109=64%:%
-%:%110=65%:%
-%:%111=66%:%
+%:%63=34%:%
+%:%64=35%:%
+%:%65=36%:%
+%:%100=65%:%
 %:%112=67%:%
 %:%113=68%:%
-%:%122=70%:%
-%:%134=72%:%
-%:%135=73%:%
-%:%136=74%:%
+%:%114=69%:%
+%:%115=70%:%
+%:%116=71%:%
+%:%125=73%:%
+%:%137=75%:%
 %:%138=76%:%
-%:%139=76%:%
-%:%140=76%:%
-%:%143=78%:%
-%:%144=79%:%
-%:%145=80%:%
+%:%139=77%:%
+%:%141=79%:%
+%:%142=79%:%
+%:%143=79%:%
 %:%146=81%:%
 %:%147=82%:%
+%:%148=83%:%
 %:%149=84%:%
-%:%150=84%:%
-%:%152=85%:%
-%:%153=85%:%
-%:%155=86%:%
-%:%156=87%:%
-%:%159=89%:%
-%:%160=90%:%
-%:%161=91%:%
+%:%150=85%:%
+%:%152=87%:%
+%:%153=87%:%
+%:%155=88%:%
+%:%156=88%:%
+%:%158=89%:%
+%:%159=90%:%
 %:%162=92%:%
 %:%163=93%:%
+%:%164=94%:%
 %:%165=95%:%
-%:%166=95%:%
-%:%167=96%:%
-%:%168=97%:%
-%:%169=97%:%
-%:%170=98%:%
-%:%171=99%:%
-%:%172=99%:%
-%:%173=100%:%
-%:%174=101%:%
-%:%175=101%:%
-%:%176=102%:%
+%:%166=96%:%
+%:%168=98%:%
+%:%169=98%:%
+%:%170=99%:%
+%:%171=100%:%
+%:%172=100%:%
+%:%173=101%:%
+%:%174=102%:%
+%:%175=102%:%
+%:%176=103%:%
+%:%177=104%:%
 %:%178=104%:%
 %:%179=105%:%
-%:%180=106%:%
+%:%181=107%:%
 %:%182=108%:%
-%:%183=108%:%
-%:%184=109%:%
-%:%185=110%:%
-%:%186=110%:%
-%:%187=111%:%
-%:%188=114%:%
+%:%183=109%:%
+%:%185=111%:%
+%:%186=111%:%
+%:%187=112%:%
+%:%188=113%:%
+%:%189=113%:%
+%:%190=114%:%
 %:%191=117%:%
-%:%192=118%:%
-%:%193=119%:%
 %:%194=120%:%
 %:%195=121%:%
-%:%198=123%:%
-%:%201=125%:%
-%:%202=126%:%
-%:%203=127%:%
+%:%196=122%:%
+%:%197=123%:%
+%:%198=124%:%
+%:%201=126%:%
 %:%204=128%:%
@@
 %:%206=130%:%
+%:%207=131%:%
 %:%208=132%:%
-%:%209=132%:%
-%:%210=133%:%
-%:%211=134%:%
+%:%209=133%:%
+%:%211=135%:%
 %:%212=135%:%
-%:%213=135%:%
-%:%215=135%:%
-%:%219=135%:%
-%:%220=135%:%
-%:%222=136%:%
-%:%223=137%:%
-%:%224=138%:%
+%:%213=136%:%
+%:%214=137%:%
+%:%215=138%:%
+%:%216=138%:%
+%:%218=138%:%
+%:%222=138%:%
+%:%223=138%:%
 %:%225=139%:%
-%:%235=141%:%
-%:%236=142%:%
-%:%237=143%:%
+%:%226=140%:%
+%:%227=141%:%
+%:%228=142%:%
 %:%238=144%:%
@@
 %:%244=150%:%
+%:%245=151%:%
 %:%246=152%:%
-%:%247=152%:%
-%:%248=153%:%
-%:%249=154%:%
+%:%247=153%:%
+%:%249=155%:%
 %:%250=155%:%
-%:%251=155%:%
-%:%253=155%:%
-%:%257=155%:%
-%:%258=155%:%
-%:%260=156%:%
-%:%261=157%:%
-%:%262=158%:%
+%:%251=156%:%
+%:%252=157%:%
+%:%253=158%:%
+%:%254=158%:%
+%:%256=158%:%
+%:%260=158%:%
+%:%261=158%:%
 %:%263=159%:%
-%:%273=162%:%
-%:%274=163%:%
-%:%275=164%:%
+%:%264=160%:%
+%:%265=161%:%
+%:%266=162%:%
 %:%276=165%:%
@@
 %:%281=170%:%
-%:%283=173%:%
+%:%282=171%:%
+%:%283=172%:%
 %:%284=173%:%
-%:%285=174%:%
-%:%286=175%:%
+%:%286=176%:%
 %:%287=176%:%
-%:%288=176%:%
-%:%290=176%:%
-%:%294=176%:%
-%:%295=176%:%
-%:%297=177%:%
-%:%298=178%:%
-%:%299=179%:%
+%:%288=177%:%
+%:%289=178%:%
+%:%290=179%:%
+%:%291=179%:%
+%:%293=179%:%
+%:%297=179%:%
+%:%298=179%:%
 %:%300=180%:%
-%:%310=182%:%
-%:%311=183%:%
-%:%312=184%:%
+%:%301=181%:%
+%:%302=182%:%
+%:%303=183%:%
 %:%313=185%:%
-%:%316=187%:%
-%:%319=189%:%
-%:%320=190%:%
-%:%321=191%:%
+%:%314=186%:%
+%:%315=187%:%
+%:%316=188%:%
+%:%319=190%:%
 %:%322=192%:%
 %:%323=193%:%
+%:%324=194%:%
 %:%325=195%:%
-%:%326=195%:%
-%:%327=196%:%
-%:%328=197%:%
+%:%326=196%:%
+%:%328=198%:%
 %:%329=198%:%
-%:%330=198%:%
-%:%332=198%:%
-%:%336=198%:%
-%:%337=198%:%
-%:%339=199%:%
-%:%340=200%:%
-%:%341=201%:%
+%:%330=199%:%
+%:%331=200%:%
+%:%332=201%:%
+%:%333=201%:%
+%:%335=201%:%
+%:%339=201%:%
+%:%340=201%:%
 %:%342=202%:%
-%:%352=204%:%
-%:%353=205%:%
-%:%362=210%:%
-%:%374=212%:%
-%:%375=213%:%
-%:%376=214%:%
+%:%343=203%:%
+%:%344=204%:%
+%:%345=205%:%
+%:%355=207%:%
+%:%356=208%:%
+%:%365=213%:%
 %:%377=215%:%
 %:%378=216%:%
-%:%380=217%:%
-%:%381=217%:%
-%:%382=218%:%
-%:%384=219%:%
-%:%385=220%:%
-%:%386=221%:%
-%:%389=223%:%
-%:%391=225%:%
-%:%392=225%:%
-%:%393=226%:%
-%:%394=227%:%
-%:%395=227%:%
-%:%397=227%:%
-%:%401=227%:%
-%:%402=227%:%
-%:%404=228%:%
-%:%405=229%:%
-%:%406=230%:%
+%:%379=217%:%
+%:%380=218%:%
+%:%381=219%:%
+%:%383=220%:%
+%:%384=220%:%
+%:%385=221%:%
+%:%387=222%:%
+%:%388=223%:%
+%:%389=224%:%
+%:%392=226%:%
+%:%394=228%:%
+%:%395=228%:%
+%:%396=229%:%
+%:%397=230%:%
+%:%398=230%:%
+%:%400=230%:%
+%:%404=230%:%
+%:%405=230%:%
 %:%407=231%:%
@@
 %:%409=233%:%
-%:%419=235%:%
-%:%421=237%:%
-%:%422=237%:%
-%:%424=239%:%
-%:%426=241%:%
-%:%427=241%:%
-%:%428=241%:%
-%:%430=241%:%
-%:%434=241%:%
-%:%435=241%:%
-%:%437=242%:%
-%:%438=243%:%
-%:%439=244%:%
+%:%410=234%:%
+%:%411=235%:%
+%:%412=236%:%
+%:%422=238%:%
+%:%424=240%:%
+%:%425=240%:%
+%:%427=242%:%
+%:%429=244%:%
+%:%430=244%:%
+%:%431=244%:%
+%:%433=244%:%
+%:%437=244%:%
+%:%438=244%:%
 %:%440=245%:%
-%:%450=247%:%
-%:%451=248%:%
-%:%452=249%:%
+%:%441=246%:%
+%:%442=247%:%
+%:%443=248%:%
 %:%453=250%:%
-%:%462=253%:%
-%:%474=255%:%
-%:%475=256%:%
-%:%476=257%:%
+%:%454=251%:%
+%:%455=252%:%
+%:%456=253%:%
+%:%465=256%:%
 %:%477=258%:%
@@
 %:%482=263%:%
-%:%486=265%:%
-%:%490=267%:%
-%:%491=268%:%
-%:%492=269%:%
+%:%483=264%:%
+%:%484=265%:%
+%:%485=266%:%
+%:%489=268%:%
+%:%493=270%:%
 %:%494=271%:%
-%:%495=271%:%
-%:%497=272%:%
-%:%498=273%:%
-%:%499=274%:%
+%:%495=272%:%
+%:%497=274%:%
+%:%498=274%:%
 %:%500=275%:%
@@
 %:%503=278%:%
-%:%504=278%:%
-%:%505=279%:%
-%:%506=280%:%
-%:%507=280%:%
-%:%508=281%:%
-%:%511=282%:%
-%:%515=282%:%
-%:%516=282%:%
-%:%518=283%:%
-%:%519=284%:%
-%:%529=286%:%
-%:%530=287%:%
-%:%531=288%:%
+%:%504=279%:%
+%:%505=280%:%
+%:%506=281%:%
+%:%507=281%:%
+%:%508=282%:%
+%:%509=283%:%
+%:%510=283%:%
+%:%511=284%:%
+%:%514=285%:%
+%:%518=285%:%
+%:%519=285%:%
+%:%521=286%:%
+%:%522=287%:%
 %:%532=289%:%
@@
 %:%546=303%:%
-%:%550=305%:%
-%:%551=306%:%
+%:%547=304%:%
+%:%548=305%:%
+%:%549=306%:%
 %:%553=308%:%
-%:%554=308%:%
-%:%556=309%:%
-%:%557=309%:%
-%:%558=310%:%
-%:%559=311%:%
-%:%560=311%:%
-%:%561=312%:%
-%:%564=313%:%
-%:%568=313%:%
-%:%569=313%:%
-%:%570=314%:%
-%:%571=314%:%
-%:%572=315%:%
-%:%573=315%:%
-%:%574=316%:%
-%:%575=316%:%
-%:%576=316%:%
-%:%577=317%:%
-%:%587=319%:%
-%:%588=320%:%
-%:%589=321%:%
+%:%554=309%:%
+%:%556=311%:%
+%:%557=311%:%
+%:%559=312%:%
+%:%560=312%:%
+%:%561=313%:%
+%:%562=314%:%
+%:%563=314%:%
+%:%564=315%:%
+%:%567=316%:%
+%:%571=316%:%
+%:%572=316%:%
+%:%573=317%:%
+%:%574=317%:%
+%:%575=318%:%
+%:%576=318%:%
+%:%577=319%:%
+%:%578=319%:%
+%:%579=319%:%
+%:%580=320%:%
 %:%590=322%:%
-%:%594=324%:%
-%:%598=326%:%
-%:%599=327%:%
-%:%600=328%:%
-%:%604=330%:%
-%:%605=331%:%
+%:%591=323%:%
+%:%592=324%:%
+%:%593=325%:%
+%:%597=327%:%
+%:%601=329%:%
+%:%602=330%:%
+%:%603=331%:%
 %:%607=333%:%
-%:%608=333%:%
-%:%621=354%:%
-%:%622=355%:%
-%:%623=355%:%
-%:%625=356%:%
-%:%626=357%:%
-%:%627=358%:%
+%:%608=334%:%
+%:%610=336%:%
+%:%611=336%:%
+%:%624=357%:%
+%:%625=358%:%
+%:%626=358%:%
 %:%628=359%:%
@@
 %:%630=361%:%
-%:%631=361%:%
-%:%633=362%:%
-%:%634=363%:%
-%:%635=363%:%
-%:%636=364%:%
-%:%637=365%:%
-%:%638=365%:%
-%:%640=366%:%
-%:%641=367%:%
-%:%644=369%:%
-%:%645=370%:%
+%:%631=362%:%
+%:%632=363%:%
+%:%633=364%:%
+%:%634=364%:%
+%:%636=365%:%
+%:%637=366%:%
+%:%638=366%:%
+%:%639=367%:%
+%:%640=368%:%
+%:%641=368%:%
+%:%643=369%:%
+%:%644=370%:%
 %:%647=372%:%
-%:%648=372%:%
-%:%649=373%:%
-%:%650=374%:%
-%:%651=374%:%
-%:%653=374%:%
-%:%657=374%:%
-%:%658=374%:%
-%:%660=375%:%
-%:%661=376%:%
-%:%662=377%:%
+%:%648=373%:%
+%:%650=375%:%
+%:%651=375%:%
+%:%652=376%:%
+%:%653=377%:%
+%:%654=377%:%
+%:%656=377%:%
+%:%660=377%:%
+%:%661=377%:%
 %:%663=378%:%
@@
 %:%666=381%:%
-%:%676=383%:%
-%:%677=384%:%
-%:%678=385%:%
-%:%681=387%:%
-%:%682=388%:%
-%:%683=389%:%
+%:%667=382%:%
+%:%668=383%:%
+%:%669=384%:%
+%:%679=386%:%
+%:%680=387%:%
+%:%681=388%:%
 %:%684=390%:%
@@
 %:%686=392%:%
-%:%689=394%:%
-%:%691=396%:%
-%:%692=396%:%
-%:%693=397%:%
-%:%696=398%:%
-%:%700=398%:%
-%:%701=398%:%
-%:%703=399%:%
-%:%709=399%:%
-%:%712=400%:%
-%:%713=401%:%
-%:%714=401%:%
-%:%715=402%:%
-%:%716=403%:%
+%:%687=393%:%
+%:%688=394%:%
+%:%689=395%:%
+%:%692=397%:%
+%:%694=399%:%
+%:%695=399%:%
+%:%696=400%:%
+%:%699=401%:%
+%:%703=401%:%
+%:%704=401%:%
+%:%706=402%:%
+%:%712=402%:%
+%:%715=403%:%
+%:%716=404%:%
 %:%717=404%:%
-%:%718=404%:%
-%:%720=404%:%
-%:%724=404%:%
-%:%725=404%:%
-%:%727=405%:%
-%:%728=406%:%
-%:%729=407%:%
+%:%718=405%:%
+%:%719=406%:%
+%:%720=407%:%
+%:%721=407%:%
+%:%723=407%:%
+%:%727=407%:%
+%:%728=407%:%
 %:%730=408%:%
 %:%731=409%:%
-%:%741=411%:%
-%:%742=412%:%
-%:%743=413%:%
+%:%732=410%:%
+%:%733=411%:%
+%:%734=412%:%
 %:%744=414%:%
@@
 %:%749=419%:%
-%:%753=422%:%
-%:%754=423%:%
-%:%755=424%:%
+%:%750=420%:%
+%:%751=421%:%
+%:%752=422%:%
 %:%756=425%:%
@@
 %:%764=433%:%
-%:%773=435%:%
-%:%785=437%:%
-%:%786=438%:%
-%:%787=439%:%
+%:%765=434%:%
+%:%766=435%:%
+%:%767=436%:%
+%:%776=438%:%
+%:%788=440%:%
 %:%789=441%:%
-%:%790=441%:%
-%:%791=442%:%
-%:%792=443%:%
+%:%790=442%:%
+%:%792=444%:%
 %:%793=444%:%
-%:%794=444%:%
-%:%796=444%:%
-%:%800=444%:%
-%:%801=444%:%
-%:%803=445%:%
-%:%804=446%:%
-%:%805=447%:%
+%:%794=445%:%
+%:%795=446%:%
+%:%796=447%:%
+%:%797=447%:%
+%:%799=447%:%
+%:%803=447%:%
+%:%804=447%:%
 %:%806=448%:%
-%:%816=450%:%
-%:%817=451%:%
-%:%818=452%:%
-%:%822=454%:%
-%:%824=456%:%
-%:%825=456%:%
-%:%826=457%:%
-%:%827=458%:%
+%:%807=449%:%
+%:%808=450%:%
+%:%809=451%:%
+%:%819=453%:%
+%:%820=454%:%
+%:%821=455%:%
+%:%825=457%:%
+%:%827=459%:%
 %:%828=459%:%
-%:%829=459%:%
-%:%831=459%:%
-%:%835=459%:%
-%:%836=459%:%
-%:%838=460%:%
-%:%839=461%:%
-%:%840=462%:%
+%:%829=460%:%
+%:%830=461%:%
+%:%831=462%:%
+%:%832=462%:%
+%:%834=462%:%
+%:%838=462%:%
+%:%839=462%:%
 %:%841=463%:%
-%:%851=465%:%
-%:%852=466%:%
+%:%842=464%:%
+%:%843=465%:%
+%:%844=466%:%
 %:%854=468%:%
-%:%855=468%:%
-%:%856=469%:%
-%:%857=470%:%
+%:%855=469%:%
+%:%857=471%:%
 %:%858=471%:%
-%:%859=471%:%
-%:%861=471%:%
-%:%865=471%:%
-%:%866=471%:%
-%:%868=472%:%
-%:%869=473%:%
-%:%870=474%:%
+%:%859=472%:%
+%:%860=473%:%
+%:%861=474%:%
+%:%862=474%:%
+%:%864=474%:%
+%:%868=474%:%
+%:%869=474%:%
 %:%871=475%:%
 %:%872=476%:%
-%:%882=478%:%
-%:%883=479%:%
+%:%873=477%:%
+%:%874=478%:%
+%:%875=479%:%
 %:%885=481%:%
-%:%886=481%:%
-%:%887=482%:%
-%:%888=483%:%
-%:%891=484%:%
-%:%895=484%:%
-%:%896=484%:%
-%:%897=484%:%
-%:%906=486%:%
-%:%907=487%:%
-%:%908=488%:%
+%:%886=482%:%
+%:%888=484%:%
+%:%889=484%:%
+%:%890=485%:%
+%:%891=486%:%
+%:%894=487%:%
+%:%898=487%:%
+%:%899=487%:%
+%:%900=487%:%
 %:%909=489%:%
+%:%910=490%:%
 %:%911=491%:%
-%:%912=491%:%
-%:%913=492%:%
-%:%914=493%:%
-%:%917=494%:%
-%:%921=494%:%
-%:%922=494%:%
-%:%923=494%:%
-%:%932=496%:%
-%:%933=497%:%
+%:%912=492%:%
+%:%914=494%:%
+%:%915=494%:%
+%:%916=495%:%
+%:%917=496%:%
+%:%920=497%:%
+%:%924=497%:%
+%:%925=497%:%
+%:%926=497%:%
 %:%935=499%:%
-%:%936=499%:%
-%:%937=500%:%
-%:%938=501%:%
+%:%936=500%:%
+%:%938=502%:%
 %:%939=502%:%
-%:%940=502%:%
-%:%942=502%:%
-%:%946=502%:%
-%:%947=502%:%
-%:%949=503%:%
-%:%950=504%:%
-%:%951=505%:%
+%:%940=503%:%
+%:%941=504%:%
+%:%942=505%:%
+%:%943=505%:%
+%:%945=505%:%
+%:%949=505%:%
+%:%950=505%:%
 %:%952=506%:%
-%:%962=508%:%
-%:%963=509%:%
-%:%964=510%:%
+%:%953=507%:%
+%:%954=508%:%
+%:%955=509%:%
 %:%965=511%:%
@@
 %:%967=513%:%
+%:%968=514%:%
 %:%969=515%:%
-%:%970=515%:%
-%:%971=516%:%
-%:%972=517%:%
+%:%970=516%:%
+%:%972=518%:%
 %:%973=518%:%
 %:%974=519%:%
-%:%975=519%:%
-%:%977=519%:%
-%:%981=519%:%
-%:%982=519%:%
-%:%984=520%:%
-%:%985=521%:%
-%:%986=522%:%
+%:%975=520%:%
+%:%976=521%:%
+%:%977=522%:%
+%:%978=522%:%
+%:%980=522%:%
+%:%984=522%:%
+%:%985=522%:%
 %:%987=523%:%
@@
 %:%989=525%:%
-%:%999=527%:%
-%:%1000=528%:%
-%:%1001=529%:%
+%:%990=526%:%
+%:%991=527%:%
+%:%992=528%:%
 %:%1002=530%:%
@@
 %:%1004=532%:%
+%:%1005=533%:%
 %:%1006=534%:%
-%:%1007=534%:%
-%:%1008=535%:%
-%:%1009=536%:%
-%:%1012=537%:%
-%:%1016=537%:%
-%:%1017=537%:%
-%:%1019=538%:%
-%:%1029=540%:%
-%:%1030=541%:%
-%:%1032=542%:%
-%:%1033=542%:%
-%:%1034=543%:%
-%:%1035=544%:%
-%:%1036=544%:%
-%:%1038=544%:%
-%:%1042=544%:%
-%:%1043=544%:%
-%:%1045=545%:%
-%:%1046=546%:%
-%:%1047=547%:%
+%:%1007=535%:%
+%:%1009=537%:%
+%:%1010=537%:%
+%:%1011=538%:%
+%:%1012=539%:%
+%:%1015=540%:%
+%:%1019=540%:%
+%:%1020=540%:%
+%:%1022=541%:%
+%:%1032=543%:%
+%:%1033=544%:%
+%:%1035=545%:%
+%:%1036=545%:%
+%:%1037=546%:%
+%:%1038=547%:%
+%:%1039=547%:%
+%:%1041=547%:%
+%:%1045=547%:%
+%:%1046=547%:%
 %:%1048=548%:%
 %:%1049=549%:%
-%:%1072=555%:%
-%:%1073=556%:%
-%:%1074=557%:%
+%:%1050=550%:%
+%:%1051=551%:%
+%:%1052=552%:%
 %:%1075=558%:%
-%:%1084=560%:%
-%:%1096=562%:%
-%:%1097=563%:%
-%:%1098=564%:%
+%:%1076=559%:%
+%:%1077=560%:%
+%:%1078=561%:%
+%:%1087=563%:%
 %:%1099=565%:%
-%:%1103=567%:%
-%:%1104=568%:%
+%:%1100=566%:%
+%:%1101=567%:%
+%:%1102=568%:%
 %:%1106=570%:%
-%:%1107=570%:%
-%:%1108=571%:%
-%:%1109=572%:%
-%:%1110=572%:%
-%:%1111=573%:%
-%:%1114=574%:%
-%:%1118=574%:%
-%:%1119=574%:%
-%:%1120=574%:%
-%:%1122=575%:%
-%:%1123=576%:%
-%:%1133=578%:%
-%:%1134=579%:%
-%:%1135=580%:%
+%:%1107=571%:%
+%:%1109=573%:%
+%:%1110=573%:%
+%:%1111=574%:%
+%:%1112=575%:%
+%:%1113=575%:%
+%:%1114=576%:%
+%:%1117=577%:%
+%:%1121=577%:%
+%:%1122=577%:%
+%:%1123=577%:%
+%:%1125=578%:%
+%:%1126=579%:%
 %:%1136=581%:%
@@
 %:%1147=592%:%
+%:%1148=593%:%
 %:%1149=594%:%
-%:%1150=594%:%
-%:%1151=595%:%
-%:%1152=596%:%
+%:%1150=595%:%
+%:%1152=597%:%
 %:%1153=597%:%
-%:%1154=597%:%
-%:%1156=597%:%
-%:%1160=597%:%
-%:%1161=597%:%
-%:%1163=598%:%
-%:%1164=599%:%
-%:%1165=600%:%
+%:%1154=598%:%
+%:%1155=599%:%
+%:%1156=600%:%
+%:%1157=600%:%
+%:%1159=600%:%
+%:%1163=600%:%
+%:%1164=600%:%
 %:%1166=601%:%
@@
 %:%1168=603%:%
-%:%1178=605%:%
-%:%1179=606%:%
-%:%1180=607%:%
+%:%1169=604%:%
+%:%1170=605%:%
+%:%1171=606%:%
 %:%1181=608%:%
-%:%1185=610%:%
-%:%1186=611%:%
-%:%1187=612%:%
+%:%1182=609%:%
+%:%1183=610%:%
+%:%1184=611%:%
+%:%1188=613%:%
 %:%1189=614%:%
-%:%1190=614%:%
-%:%1191=615%:%
-%:%1192=615%:%
-%:%1194=616%:%
-%:%1195=617%:%
-%:%1196=617%:%
-%:%1197=618%:%
-%:%1198=619%:%
-%:%1199=619%:%
-%:%1200=620%:%
-%:%1203=621%:%
-%:%1207=621%:%
-%:%1208=621%:%
-%:%1210=622%:%
-%:%1211=623%:%
-%:%1212=624%:%
-%:%1222=626%:%
-%:%1223=627%:%
-%:%1224=628%:%
+%:%1190=615%:%
+%:%1192=617%:%
+%:%1193=617%:%
+%:%1194=618%:%
+%:%1195=618%:%
+%:%1197=619%:%
+%:%1198=620%:%
+%:%1199=620%:%
+%:%1200=621%:%
+%:%1201=622%:%
+%:%1202=622%:%
+%:%1203=623%:%
+%:%1206=624%:%
+%:%1210=624%:%
+%:%1211=624%:%
+%:%1213=625%:%
+%:%1214=626%:%
+%:%1215=627%:%
 %:%1225=629%:%
+%:%1226=630%:%
 %:%1227=631%:%
-%:%1228=631%:%
-%:%1229=632%:%
-%:%1231=632%:%
-%:%1235=632%:%
-%:%1236=632%:%
-%:%1238=633%:%
-%:%1246=633%:%
-%:%1247=634%:%
-%:%1248=635%:%
-%:%1249=635%:%
-%:%1250=636%:%
-%:%1252=636%:%
-%:%1256=636%:%
-%:%1257=636%:%
-%:%1259=637%:%
-%:%1269=639%:%
-%:%1270=640%:%
-%:%1271=641%:%
-%:%1279=643%:%
+%:%1228=632%:%
+%:%1230=634%:%
+%:%1231=634%:%
+%:%1232=635%:%
+%:%1234=635%:%
+%:%1238=635%:%
+%:%1239=635%:%
+%:%1241=636%:%
+%:%1249=636%:%
+%:%1250=637%:%
+%:%1251=638%:%
+%:%1252=638%:%
+%:%1253=639%:%
+%:%1255=639%:%
+%:%1259=639%:%
+%:%1260=639%:%
+%:%1262=640%:%
+%:%1272=642%:%
+%:%1273=643%:%
+%:%1274=644%:%
+%:%1282=646%:%

### 2022-02-18 paper/output/document/thesis_2_methods.tex
started chapter 4

@@
 judgements about whether a state of affairs actually satisifes the relevant criteria for goodness. 
-Perfect knowledge of tens of thousands of 
-people's pleasure or preferences or welfare or rights is impossible. Either a human being 
+Perfect knowledge of tens of thousands of people's pleasure or preferences or welfare or rights is 
+difficult, if not impossible.\footnote{Even if it were possible, collecting this kind of data poses 
+privacy and surveillance risks.} Either a human being 
 assigns values to states of affairs, which doesn't scale, or the machine does, 
@@
 ethicists present a list of virtues, such as the Buddhist virtue of equanimity \citep{mcrae}. An automated virtue 
-ethical agent will need to commit to a particular theory of the virtues, a controversial choice. 
+ethical agent will need to commit to a list and definitions of the virtues, a controversial choice. 
 Virtue ethicists robustly debate which traits qualify as virtues, what each virtue actually means, and 
@@
 implies that ethical behavior can be learned from some dataset of virtuous acts, such as
-those that an ideal virtuous agent would undertake. These 
+those that an ideally virtuous agent would undertake. These 
 theories seem to point towards a machine learning approach to automated ethics, in which ethics is 
@@
 dataset with acts labelled as virtuous or not virtuous will contain an implicit view on what the virtues
-are and how certain acts impact an agent's moral character. Because there is no canonical list of virtues
-that virtue ethicists accept, this implicit view will likely be controversial.
+are and how certain acts impact an agent's moral character. Because there is no canonical list of all virtues
+that virtue ethicists accept, this implicit view will likely be controversial. Even virtue ethicists agree
+that certain traits, like courage, are virtues debate the exact definitions of these traits.
 
@@
 machine learning. It also applies to a broader class of work in automated ethics 
-that uses ``bottom-up" approaches, in which a system learns moral judgements from prior judgements. 
+that uses a ``bottom-up" approach, in which a system learns moral judgements from prior judgements. 
 I will extend this argument to general bottom-up approaches in Section Related Work.}%
@@
 imperative. He presents three ``formulations" or versions of the categorical imperative. In this project, 
-I focus on the first formulation, the Formula of Universal Law, and I explain this choice in Section \ref{whyful}.
+I focus on the first formulation, the Formula of Universal Law, and I justify this choice in Section \ref{whyful}.
 
@@
 \begin{isamarkuptext}%
-Kantian ethics is an especially candidate for formalization because the categorical imperative, particularly the FUL, 
+Kantian ethics is an especially attractive candidate for formalization because the categorical imperative, particularly the FUL, 
 is a property of reason related to the form or structure of a maxim. It does not require any situational 
@@
 \begin{isamarkuptext}%
-One debate in Kantian 
-ethics is the role of ``common-sense'' reasoning. Kantian ethics requires common-sense reasoning to 
-determine which circumstances are ``morally relevant'' in the formulation of a maxim. Many misunderstandings
-in Kantian ethics are due to badly formulated maxims, so this question is important for an ethical 
-reasoner to answer.\footnote{For example, critics of Kantian ethics worry that the maxim, ``When I am a
+One challenge for automating Kantian ethics is the need for ``common-sense'', or factual and 
+situational background. Common-sense is needed when formulating a maxim and when determining if a maxim 
+violates the Formula of Universal Law. Maxims include the circumstances in which they apply and
+determining which circumstances are ``morally relevant'' to a maxim requires factual background. 
+Many misunderstandings in Kantian ethics are due to badly formulated maxims, so this question is 
+important for an ethical reasoner to answer.\footnote{For example, critics of Kantian ethics worry 
+that the maxim, ``When I am a
 man, I will marry a man because I want to spend my life with him'' fails the universalizability
@@
 maxim as input and apply the categorical imperative to this input. Using my system in a fully automated
-moral agent will require answering this question, a challenging computational and philosophical task.
-
-Common-sense reasoning is also relevant when applying the universalizability test itself. Consider the example
+moral agent will require answering this question, a challenging computational and philosophical task.\footnote{I
+discuss this problem in greater detail in Section \ref{whatisamaxim} and Section Limitations.}
+
+Common sense is also relevant when applying the universalizability test itself. Consider the example
 maxim ``When broke, I will falsely promise to repay a loan
@@
 an action and virtue ethical agents need common sense to determine which virtues an action
-reflects. Making any ethical judgement requires robust conceptions of the action
-at hand, falsely promising in this case. The advantage of Kantian ethics is that this is all the common 
-sense that it requires, whereas a consequentialist or virtue ethical agent will require much more\footnote{
+reflects. For example, in the case of virtue ethics, in order to see that saving a baby from a lion 
+requires courage, a reasoner must have enough background knowledge to know that lions are scary. Making any 
+ethical judgement requires robust conceptions of the action at hand. Kantian ethics requires far less common sense 
+than a consequentialist or virtue ethical agent.\footnote{
 In Sections Lying and Murderer, I also use my system to demonstrate that Kantian ethics requires relatively thin conceptions 
-of concepts like falsely promising.}. All
+of concepts like falsely promising.} All
 moral theories evaluating falsely promising will a robust definition of promising, 
-but consequentialism and virtue ethics will also require additional information
+but consequentialism and virtue ethics will require additional information
 that Kantian ethics will not. Thus, although the need for common sense poses a challenge to automated
@@
 I choose to focus on the FUL\footnote{The FUL is often seen as emblematic of Kantian constructivism \cite[173]{ebelsduggan}. 
-My project is not committed to Kantian constructivism. I believe that computational ethics is likely a 
-valuable tool for any ethicist, and I make the case for Kantian ethics specifically.},
- because it is the most formal and thus the easiest to formalize and implement. 
-Onora O'Neill explains that the formalism of the FUL allows 
+My project is not committed to Kantian constructivism.}, because it is the most formal and thus the 
+easiest to formalize and implement. Onora O'Neill explains that the formalism of the FUL allows 
 for greater precision in philosophical arguments analyzing its implications and power \cite[33]{actingonprinciple}. This precision 
@@
 %:%180=113%:%
-%:%184=115%:%
-%:%188=117%:%
+%:%181=114%:%
+%:%185=116%:%
 %:%189=118%:%
@@
 %:%204=133%:%
-%:%208=136%:%
-%:%212=139%:%
+%:%205=134%:%
+%:%209=137%:%
 %:%213=140%:%
@@
 %:%227=154%:%
-%:%236=157%:%
-%:%248=159%:%
+%:%228=155%:%
+%:%237=158%:%
 %:%249=160%:%
@@
 %:%254=165%:%
-%:%258=169%:%
-%:%259=170%:%
-%:%260=171%:%
-%:%261=172%:%
-%:%262=173%:%
-%:%263=174%:%
-%:%264=175%:%
-%:%265=176%:%
-%:%266=177%:%
-%:%270=179%:%
-%:%274=181%:%
-%:%275=182%:%
-%:%276=183%:%
-%:%277=184%:%
-%:%278=185%:%
-%:%279=186%:%
-%:%280=187%:%
-%:%281=188%:%
-%:%282=189%:%
-%:%283=190%:%
-%:%284=191%:%
-%:%285=192%:%
-%:%286=193%:%
-%:%287=194%:%
-%:%288=195%:%
-%:%289=196%:%
-%:%290=197%:%
-%:%291=198%:%
-%:%292=199%:%
-%:%293=200%:%
-%:%294=201%:%
-%:%295=202%:%
-%:%296=203%:%
-%:%297=204%:%
-%:%298=205%:%
-%:%299=206%:%
-%:%300=207%:%
-%:%309=210%:%
-%:%321=212%:%
-%:%322=213%:%
-%:%323=214%:%
-%:%324=215%:%
-%:%325=216%:%
-%:%326=217%:%
-%:%327=218%:%
-%:%328=219%:%
-%:%329=220%:%
-%:%330=221%:%
-%:%331=222%:%
-%:%332=223%:%
-%:%333=224%:%
-%:%334=225%:%
-%:%335=226%:%
-%:%336=227%:%
-%:%337=228%:%
-%:%338=229%:%
-%:%339=230%:%
-%:%340=231%:%
-%:%341=232%:%
-%:%342=233%:%
-%:%343=234%:%
-%:%344=235%:%
-%:%345=236%:%
-%:%346=237%:%
-%:%347=238%:%
-%:%348=239%:%
-%:%349=240%:%
-%:%350=241%:%
-%:%351=242%:%
-%:%352=243%:%
-%:%353=244%:%
-%:%354=245%:%
-%:%355=246%:%
-%:%356=247%:%
-%:%357=248%:%
-%:%358=249%:%
-%:%359=250%:%
-%:%360=251%:%
-%:%361=252%:%
-%:%362=253%:%
-%:%363=254%:%
-%:%364=255%:%
-%:%365=256%:%
-%:%366=257%:%
-%:%367=258%:%
-%:%368=259%:%
-%:%369=260%:%
-%:%370=261%:%
-%:%371=262%:%
-%:%372=263%:%
-%:%373=264%:%
-%:%374=265%:%
-%:%375=266%:%
-%:%376=267%:%
-%:%377=268%:%
-%:%381=271%:%
-%:%385=273%:%
-%:%386=274%:%
-%:%387=275%:%
-%:%388=276%:%
-%:%389=277%:%
-%:%390=278%:%
-%:%391=279%:%
-%:%392=280%:%
-%:%393=281%:%
-%:%394=282%:%
-%:%395=283%:%
-%:%396=284%:%
-%:%397=285%:%
-%:%398=286%:%
-%:%399=287%:%
-%:%400=288%:%
-%:%401=289%:%
-%:%402=290%:%
-%:%403=291%:%
-%:%404=292%:%
-%:%408=295%:%
-%:%412=297%:%
-%:%413=298%:%
-%:%414=299%:%
-%:%415=300%:%
-%:%416=301%:%
-%:%417=302%:%
-%:%418=303%:%
-%:%419=304%:%
-%:%420=305%:%
-%:%421=306%:%
-%:%422=307%:%
-%:%423=308%:%
-%:%424=309%:%
-%:%425=310%:%
-%:%426=311%:%
-%:%427=312%:%
-%:%428=313%:%
-%:%429=314%:%
-%:%430=315%:%
-%:%431=316%:%
-%:%432=317%:%
-%:%433=318%:%
-%:%434=319%:%
-%:%435=320%:%
-%:%436=321%:%
-%:%437=322%:%
-%:%438=323%:%
-%:%439=324%:%
-%:%440=325%:%
-%:%441=326%:%
-%:%442=327%:%
-%:%443=328%:%
-%:%452=330%:%
-%:%464=333%:%
-%:%465=334%:%
-%:%466=335%:%
-%:%467=336%:%
-%:%468=337%:%
-%:%469=338%:%
-%:%470=339%:%
-%:%471=340%:%
-%:%472=341%:%
-%:%473=342%:%
-%:%474=343%:%
-%:%475=344%:%
-%:%476=345%:%
-%:%477=346%:%
-%:%478=347%:%
-%:%479=348%:%
-%:%480=349%:%
-%:%481=350%:%
-%:%482=351%:%
-%:%483=352%:%
-%:%484=353%:%
-%:%485=354%:%
-%:%486=355%:%
-%:%487=356%:%
-%:%488=357%:%
-%:%489=358%:%
-%:%490=359%:%
-%:%491=360%:%
-%:%492=361%:%
-%:%493=362%:%
-%:%494=363%:%
-%:%495=364%:%
-%:%496=365%:%
-%:%497=366%:%
-%:%498=367%:%
-%:%499=368%:%
-%:%500=369%:%
-%:%501=370%:%
-%:%502=371%:%
-%:%503=372%:%
-%:%504=373%:%
-%:%505=374%:%
-%:%506=375%:%
-%:%507=376%:%
-%:%508=377%:%
-%:%509=378%:%
-%:%510=379%:%
-%:%511=380%:%
-%:%512=381%:%
-%:%513=382%:%
-%:%514=383%:%
-%:%523=385%:%
-%:%535=387%:%
-%:%536=388%:%
+%:%255=166%:%
+%:%259=169%:%
+%:%260=170%:%
+%:%261=171%:%
+%:%262=172%:%
+%:%263=173%:%
+%:%264=174%:%
+%:%265=175%:%
+%:%266=176%:%
+%:%267=177%:%
+%:%271=179%:%
+%:%275=181%:%
+%:%276=182%:%
+%:%277=183%:%
+%:%278=184%:%
+%:%279=185%:%
+%:%280=186%:%
+%:%281=187%:%
+%:%282=188%:%
+%:%283=189%:%
+%:%284=190%:%
+%:%285=191%:%
+%:%286=192%:%
+%:%287=193%:%
+%:%288=194%:%
+%:%289=195%:%
+%:%290=196%:%
+%:%291=197%:%
+%:%292=198%:%
+%:%293=199%:%
+%:%294=200%:%
+%:%295=201%:%
+%:%296=202%:%
+%:%297=203%:%
+%:%298=204%:%
+%:%299=205%:%
+%:%300=206%:%
+%:%301=207%:%
+%:%302=208%:%
+%:%311=211%:%
+%:%323=213%:%
+%:%324=214%:%
+%:%325=215%:%
+%:%326=216%:%
+%:%327=217%:%
+%:%328=218%:%
+%:%329=219%:%
+%:%330=220%:%
+%:%331=221%:%
+%:%332=222%:%
+%:%333=223%:%
+%:%334=224%:%
+%:%335=225%:%
+%:%336=226%:%
+%:%337=227%:%
+%:%338=228%:%
+%:%339=229%:%
+%:%340=230%:%
+%:%341=231%:%
+%:%342=232%:%
+%:%343=233%:%
+%:%344=234%:%
+%:%345=235%:%
+%:%346=236%:%
+%:%347=237%:%
+%:%348=238%:%
+%:%349=239%:%
+%:%350=240%:%
+%:%351=241%:%
+%:%352=242%:%
+%:%353=243%:%
+%:%354=244%:%
+%:%355=245%:%
+%:%356=246%:%
+%:%357=247%:%
+%:%358=248%:%
+%:%359=249%:%
+%:%360=250%:%
+%:%361=251%:%
+%:%362=252%:%
+%:%363=253%:%
+%:%364=254%:%
+%:%365=255%:%
+%:%366=256%:%
+%:%367=257%:%
+%:%368=258%:%
+%:%369=259%:%
+%:%370=260%:%
+%:%371=261%:%
+%:%372=262%:%
+%:%373=263%:%
+%:%374=264%:%
+%:%375=265%:%
+%:%376=266%:%
+%:%377=267%:%
+%:%378=268%:%
+%:%379=269%:%
+%:%383=272%:%
+%:%387=274%:%
+%:%388=275%:%
+%:%389=276%:%
+%:%390=277%:%
+%:%391=278%:%
+%:%392=279%:%
+%:%393=280%:%
+%:%394=281%:%
+%:%395=282%:%
+%:%396=283%:%
+%:%397=284%:%
+%:%398=285%:%
+%:%399=286%:%
+%:%400=287%:%
+%:%401=288%:%
+%:%402=289%:%
+%:%403=290%:%
+%:%404=291%:%
+%:%405=292%:%
+%:%406=293%:%
+%:%410=296%:%
+%:%414=298%:%
+%:%415=299%:%
+%:%416=300%:%
+%:%417=301%:%
+%:%418=302%:%
+%:%419=303%:%
+%:%420=304%:%
+%:%421=305%:%
+%:%422=306%:%
+%:%423=307%:%
+%:%424=308%:%
+%:%425=309%:%
+%:%426=310%:%
+%:%427=311%:%
+%:%428=312%:%
+%:%429=313%:%
+%:%430=314%:%
+%:%431=315%:%
+%:%432=316%:%
+%:%433=317%:%
+%:%434=318%:%
+%:%435=319%:%
+%:%436=320%:%
+%:%437=321%:%
+%:%438=322%:%
+%:%439=323%:%
+%:%440=324%:%
+%:%441=325%:%
+%:%442=326%:%
+%:%443=327%:%
+%:%444=328%:%
+%:%445=329%:%
+%:%446=330%:%
+%:%447=331%:%
+%:%448=332%:%
+%:%449=333%:%
+%:%458=335%:%
+%:%470=338%:%
+%:%471=339%:%
+%:%472=340%:%
+%:%473=341%:%
+%:%474=342%:%
+%:%475=343%:%
+%:%476=344%:%
+%:%477=345%:%
+%:%478=346%:%
+%:%479=347%:%
+%:%480=348%:%
+%:%481=349%:%
+%:%482=350%:%
+%:%483=351%:%
+%:%484=352%:%
+%:%485=353%:%
+%:%486=354%:%
+%:%487=355%:%
+%:%488=356%:%
+%:%489=357%:%
+%:%490=358%:%
+%:%491=359%:%
+%:%492=360%:%
+%:%493=361%:%
+%:%494=362%:%
+%:%495=363%:%
+%:%496=364%:%
+%:%497=365%:%
+%:%498=366%:%
+%:%499=367%:%
+%:%500=368%:%
+%:%501=369%:%
+%:%502=370%:%
+%:%503=371%:%
+%:%504=372%:%
+%:%505=373%:%
+%:%506=374%:%
+%:%507=375%:%
+%:%508=376%:%
+%:%509=377%:%
+%:%510=378%:%
+%:%511=379%:%
+%:%512=380%:%
+%:%513=381%:%
+%:%514=382%:%
+%:%515=383%:%
+%:%516=384%:%
+%:%517=385%:%
+%:%518=386%:%
+%:%527=388%:%
+%:%539=390%:%
 %:%540=391%:%
-%:%541=392%:%
-%:%542=393%:%
-%:%543=394%:%
-%:%544=395%:%
-%:%545=396%:%
-%:%546=397%:%
-%:%547=398%:%
-%:%548=399%:%
-%:%549=400%:%
-%:%550=401%:%
-%:%551=402%:%
-%:%552=403%:%
-%:%553=404%:%
-%:%554=405%:%
-%:%555=406%:%
-%:%556=407%:%
-%:%557=408%:%
-%:%558=409%:%
-%:%559=410%:%
-%:%560=411%:%
-%:%561=412%:%
-%:%562=413%:%
-%:%563=414%:%
-%:%564=415%:%
-%:%565=416%:%
-%:%566=417%:%
-%:%567=418%:%
-%:%571=420%:%
-%:%572=421%:%
-%:%573=422%:%
-%:%574=423%:%
-%:%575=424%:%
-%:%576=425%:%
-%:%577=426%:%
-%:%578=427%:%
-%:%579=428%:%
-%:%580=429%:%
-%:%581=430%:%
-%:%582=431%:%
-%:%583=432%:%
-%:%584=433%:%
-%:%585=434%:%
-%:%586=435%:%
-%:%587=436%:%
-%:%588=437%:%
-%:%589=438%:%
-%:%590=439%:%
-%:%591=440%:%
-%:%592=441%:%
-%:%593=442%:%
-%:%594=443%:%
-%:%595=444%:%
-%:%596=445%:%
-%:%597=446%:%
-%:%606=449%:%
-%:%618=451%:%
-%:%619=452%:%
-%:%620=453%:%
-%:%621=454%:%
-%:%622=455%:%
-%:%623=456%:%
-%:%632=459%:%
-%:%644=461%:%
-%:%645=462%:%
-%:%646=463%:%
-%:%648=465%:%
+%:%544=394%:%
+%:%545=395%:%
+%:%546=396%:%
+%:%547=397%:%
+%:%548=398%:%
+%:%549=399%:%
+%:%550=400%:%
+%:%551=401%:%
+%:%552=402%:%
+%:%553=403%:%
+%:%554=404%:%
+%:%555=405%:%
+%:%556=406%:%
+%:%557=407%:%
+%:%558=408%:%
+%:%559=409%:%
+%:%560=410%:%
+%:%561=411%:%
+%:%562=412%:%
+%:%563=413%:%
+%:%564=414%:%
+%:%565=415%:%
+%:%566=416%:%
+%:%567=417%:%
+%:%568=418%:%
+%:%569=419%:%
+%:%570=420%:%
+%:%571=421%:%
+%:%575=423%:%
+%:%576=424%:%
+%:%577=425%:%
+%:%578=426%:%
+%:%579=427%:%
+%:%580=428%:%
+%:%581=429%:%
+%:%582=430%:%
+%:%583=431%:%
+%:%584=432%:%
+%:%585=433%:%
+%:%586=434%:%
+%:%587=435%:%
+%:%588=436%:%
+%:%589=437%:%
+%:%590=438%:%
+%:%591=439%:%
+%:%592=440%:%
+%:%593=441%:%
+%:%594=442%:%
+%:%595=443%:%
+%:%596=444%:%
+%:%597=445%:%
+%:%598=446%:%
+%:%599=447%:%
+%:%600=448%:%
+%:%601=449%:%
+%:%610=452%:%
+%:%622=454%:%
+%:%623=455%:%
+%:%624=456%:%
+%:%625=457%:%
+%:%626=458%:%
+%:%627=459%:%
+%:%636=462%:%
+%:%648=464%:%
 %:%649=465%:%
-%:%650=465%:%
-%:%651=465%:%
-%:%653=466%:%
-%:%654=467%:%
-%:%655=467%:%
-%:%656=468%:%
+%:%650=466%:%
+%:%652=468%:%
+%:%653=468%:%
+%:%654=468%:%
+%:%655=468%:%
 %:%657=469%:%
-%:%658=469%:%
-%:%659=469%:%
-%:%660=469%:%
-%:%662=470%:%
-%:%663=471%:%
-%:%664=471%:%
-%:%667=485%:%
-%:%668=486%:%
-%:%669=487%:%
-%:%671=489%:%
+%:%658=470%:%
+%:%659=470%:%
+%:%660=471%:%
+%:%661=472%:%
+%:%662=472%:%
+%:%663=472%:%
+%:%664=472%:%
+%:%666=473%:%
+%:%667=474%:%
+%:%668=474%:%
+%:%671=488%:%
 %:%672=489%:%
-%:%673=489%:%
-%:%674=489%:%
-%:%675=490%:%
-%:%676=490%:%
-%:%677=490%:%
-%:%680=494%:%
-%:%681=495%:%
-%:%682=496%:%
-%:%683=497%:%
-%:%685=499%:%
+%:%673=490%:%
+%:%675=492%:%
+%:%676=492%:%
+%:%677=492%:%
+%:%678=492%:%
+%:%679=493%:%
+%:%680=493%:%
+%:%681=493%:%
+%:%684=497%:%
+%:%685=498%:%
 %:%686=499%:%
-%:%687=523%:%
-%:%688=524%:%
-%:%690=525%:%
+%:%687=500%:%
+%:%689=502%:%
+%:%690=502%:%
 %:%691=526%:%
 %:%692=527%:%
-%:%693=528%:%
 %:%694=528%:%
-%:%702=535%:%
-%:%714=537%:%
-%:%715=538%:%
-%:%716=539%:%
-%:%717=540%:%
-%:%718=541%:%
-%:%719=542%:%
-%:%720=543%:%
-%:%724=559%:%
-%:%726=560%:%
-%:%727=560%:%
-%:%728=561%:%
-%:%730=562%:%
+%:%695=529%:%
+%:%696=530%:%
+%:%697=531%:%
+%:%698=531%:%
+%:%706=538%:%
+%:%718=540%:%
+%:%719=541%:%
+%:%720=542%:%
+%:%721=543%:%
+%:%722=544%:%
+%:%723=545%:%
+%:%724=546%:%
+%:%728=562%:%
+%:%730=563%:%
 %:%731=563%:%
-%:%732=563%:%
-%:%733=564%:%
-%:%734=564%:%
-%:%735=565%:%
-%:%737=566%:%
-%:%740=568%:%
-%:%742=569%:%
-%:%743=569%:%
-%:%744=570%:%
-%:%746=571%:%
-%:%747=571%:%
-%:%750=591%:%
-%:%751=592%:%
-%:%753=593%:%
-%:%754=593%:%
-%:%755=594%:%
-%:%756=595%:%
-%:%757=595%:%
+%:%732=564%:%
+%:%734=565%:%
+%:%735=566%:%
+%:%736=566%:%
+%:%737=567%:%
+%:%738=567%:%
+%:%739=568%:%
+%:%741=569%:%
+%:%744=571%:%
+%:%746=572%:%
+%:%747=572%:%
+%:%748=573%:%
+%:%750=574%:%
+%:%751=574%:%
+%:%754=594%:%
+%:%755=595%:%
+%:%757=596%:%
 %:%758=596%:%
 %:%759=597%:%
-%:%760=597%:%
+%:%760=598%:%
 %:%761=598%:%
-%:%763=599%:%
+%:%762=599%:%
+%:%763=600%:%
 %:%764=600%:%
+%:%765=601%:%
 %:%767=602%:%
-%:%769=603%:%
-%:%770=603%:%
-%:%771=604%:%
-%:%773=605%:%
-%:%774=605%:%
-%:%777=613%:%
-%:%778=614%:%
-%:%779=615%:%
-%:%780=616%:%
-%:%782=619%:%
-%:%783=619%:%
+%:%768=603%:%
+%:%771=605%:%
+%:%773=606%:%
+%:%774=606%:%
+%:%775=607%:%
+%:%777=608%:%
+%:%778=608%:%
+%:%781=616%:%
+%:%782=617%:%
+%:%783=618%:%
 %:%784=619%:%
-%:%786=619%:%
-%:%790=619%:%
-%:%791=619%:%
-%:%793=620%:%
-%:%794=621%:%
-%:%795=621%:%
-%:%797=622%:%
-%:%798=623%:%
+%:%786=622%:%
+%:%787=622%:%
+%:%788=622%:%
+%:%790=622%:%
+%:%794=622%:%
+%:%795=622%:%
+%:%797=623%:%
+%:%798=624%:%
 %:%799=624%:%
-%:%809=626%:%
-%:%810=627%:%
-%:%811=628%:%
+%:%801=625%:%
+%:%802=626%:%
+%:%803=627%:%
+%:%813=629%:%
+%:%814=630%:%
+%:%815=631%:%

### 2022-02-18 paper/output/document/thesis_3_implementation.tex
started chapter 4

@@
 Kant's example maxims, that a maxim includes the act, the circumstances, and the agent's purpose of 
-acting or goal \citep{actingonprinciple}.
+acting or goal \citep{actingonprinciple}. Other potential views include Korsgaard's view, which omits 
+the circumstances, and Kitcher's view, which adds a motivation \citep{actingforareason, kitcher}. I 
+address the limitations of these approaches in Appendix \ref{maximmotive}.
 
@@
 and is thus inherently purposive \citep[4:428]{groundwork}. A rational will does not act randomly (else it would not be rational), 
-but instead in the pursuit of ends which it deems valuable.\footnote{Some argue that a maxim should also
-include the agent's motive or motivation and I address this concern in Appendix \ref{maximmotive}.} The inclusion a maxim's end is essential for the version of the FUL
-that I will implement, explained in Section \ref{praccon}.
-
-\color{red} SHOULD THIS GO HERE OR IN THE LIMITATIONS SECTION OF THE DISCUSSION
+but instead in the pursuit of ends which it deems valuable. The inclusion a maxim's end is essential 
+for the version of the FUL that I will implement, explained in Section \ref{praccon}.
 
@@
 under which maxims are arbitrarily specified to pass the FUL  \citep[217]{whatisamaxim}. \footnote{Kitcher
-cites \citet{kantsethicalthought} as offering an example of a false positive due to this objection.} For example, the maxim ``When my name is Jane Doe
+cites \citet{kantsethicalthought} as offering an example of a false positive due to this objection \cite{kitcher}.} For example, the maxim ``When my name is Jane Doe
 and I am wearing a purple shirt and it is Tuesday morning, I will murder my boss so I can take their job,'' 
@@
 goal, and circumstances. This heuristic could define morally relevant circumstances as those that 
-reach a certain closeness threshhold with the action and the goal. Determining morally relevant
+reach a certain closeness threshhold with the action and the goal. Another possible heuristic could 
+define some set of morally important entities, and classify morally relevant circumstances as those
+that involve morally important entities. Determining morally relevant
 circumstances, either using heuristics or human involvement, is a ripe area for future work.
-\color{black}
 
@@
 which prohibits maxims that are self-defeating, or ineffective, when universalized. By willing a maxim, 
-an agent commits themselves to the maxim's goal, and thus cannot rationally will that this goal be 
+you commit yourself to the maxim's goal, and thus cannot rationally will that this goal be 
 undercut. This interpretation can prohibit natural acts like those of the sleep-deprived mother: in 
@@
 principle of the form ``When you are eating breakfast, eat breakfast in order to eat breakfast,'' is not 
-practically relevant. No agent would ever need to act on such a principle. It is neither contradictory
-nor prohibited, and it is the wrong kind of question to be asking. It is not a 
+practically relevant. No agent would ever need to act on such a principle. Morality helps agents decide
+whether to act on a potential principle of action, but no agent would need to ask
+``When I am eating breakfast, should I eat breakfast in order to eat breakfast?" It is neither contradictory
+nor prohibited, and it is the wrong kind of principle to be evaluating. It is not a
 well-formed maxim, so the categorical imperative cannot apply to it.
@@
 \centering
-\includegraphics[scale=0.4]{goalstable.png}
+\includegraphics[scale=0.6]{goalstable.png}
 \caption{Table showing which tests each implementation passes. The naive interpretation is raw DDL, 
@@
 \begin{isamarkuptext}%
-\noindent \textbf{Contradictory Obligations} Contradictory obligations
+\noindent \textbf{Obligations Never Contradict} Contradictory obligations
 make obeying the prescriptions of an ethical theory impossible.
@@
 for the will \citep[703-4]{kohl}. This defeats the purpose of Kant's theory, which is to develop an unconditional, categorical imperative 
-for rational agents. Ought implies can requires that obligations never contradict, because an agent 
+for rational agents. Ought implies can requires that obligations never contradict each other, because an agent 
 can't perform contradictory actions. Therefore, any ethical theory that respects ought implies can, 
@@
 \begin{isamarkuptext}%
-\noindent \textbf{Distributive Property} Another property related to contradictory obligations is the distributive property for the obligation
+\noindent \textbf{Distributive Property for Obligations Holds} Another property related to contradictory obligations is the distributive property for the obligation
 operator.\footnote{Formally, $O\{A\} \wedge O\{B\} \longleftrightarrow O\{A \wedge B\}$.} This is 
@@
 
-\noindent \textbf{Un-universalizable Actions} Recall that 
+\noindent \textbf{Prohibits Actions That Are Impossible to Universalize} Recall that 
 the logical contradiction interpretation of the Formula of Universal Law prohibits lying because in a world 
@@
 \begin{isamarkuptext}%
-\noindent \textbf{Maxims} Kant does not evaluate the correctness of acts, but rather of maxims. Therefore, any 
+\noindent \textbf{Robust Representation of Maxims} Kant does not evaluate the correctness of acts, but rather of maxims. Therefore, any 
 faithful formalization of the categorical imperative must evaluate maxims, not acts. This requires 
@@
 \begin{isamarkuptext}%
-\noindent \textbf{Conventional and Natural Acts} When arguing for the practical contradiction interpretation,
+\noindent \textbf{Can Prohibit Conventional and Natural Acts} When arguing for the practical contradiction interpretation,
 Korsgaard makes a distinction between conventional and natural acts \citep{KorsgaardFUL}. 
@@
 practical contradiction interpretation of the FUL, which is the canonical interpretation of the 
-FUL \citep{KorsgaardFUL}. I run this test in Chapter Applications, where I
+FUL \citep{ebelsduggan, KorsgaardFUL}. I run this test in Chapter Applications, where I
 use my system to reason about two ethical dilemmas, one which involves conventional acts and the other which
@@
 %:%165=82%:%
-%:%167=85%:%
+%:%166=83%:%
+%:%167=84%:%
 %:%168=85%:%
-%:%170=86%:%
-%:%171=87%:%
-%:%172=88%:%
+%:%170=88%:%
+%:%171=88%:%
 %:%173=89%:%
@@
 %:%177=93%:%
-%:%180=95%:%
-%:%181=96%:%
-%:%182=97%:%
+%:%178=94%:%
+%:%179=95%:%
+%:%180=96%:%
 %:%183=98%:%
@@
 %:%239=154%:%
-%:%241=156%:%
-%:%242=156%:%
+%:%240=155%:%
+%:%242=157%:%
 %:%243=157%:%
-%:%245=158%:%
+%:%244=158%:%
 %:%246=159%:%
@@
 %:%248=161%:%
-%:%256=163%:%
-%:%268=165%:%
+%:%249=162%:%
+%:%257=164%:%
 %:%269=166%:%
@@
 %:%318=215%:%
-%:%320=218%:%
-%:%321=218%:%
+%:%319=216%:%
+%:%321=219%:%
 %:%322=219%:%
-%:%324=220%:%
+%:%323=220%:%
 %:%325=221%:%
-%:%328=223%:%
+%:%326=222%:%
 %:%329=224%:%
@@
 %:%349=244%:%
-%:%351=247%:%
-%:%352=247%:%
+%:%350=245%:%
+%:%352=248%:%
 %:%353=248%:%
-%:%355=249%:%
+%:%354=249%:%
 %:%356=250%:%
-%:%357=250%:%
-%:%360=256%:%
+%:%357=251%:%
+%:%358=251%:%
 %:%361=257%:%
@@
 %:%370=266%:%
-%:%372=268%:%
-%:%373=268%:%
+%:%371=267%:%
+%:%373=269%:%
 %:%374=269%:%
-%:%376=270%:%
-%:%379=272%:%
+%:%375=270%:%
+%:%377=271%:%
 %:%380=273%:%
@@
 %:%411=304%:%
-%:%413=306%:%
-%:%414=306%:%
+%:%412=305%:%
+%:%414=307%:%
 %:%415=307%:%
-%:%417=308%:%
+%:%416=308%:%
 %:%418=309%:%
-%:%419=309%:%
+%:%419=310%:%
 %:%420=310%:%
 %:%421=311%:%
-%:%422=311%:%
+%:%422=312%:%
 %:%423=312%:%
-%:%425=313%:%
+%:%424=313%:%
 %:%426=314%:%
-%:%429=316%:%
+%:%427=315%:%
 %:%430=317%:%
@@
 %:%432=319%:%
-%:%434=321%:%
-%:%435=321%:%
+%:%433=320%:%
+%:%435=322%:%
 %:%436=322%:%
-%:%438=323%:%
+%:%437=323%:%
 %:%439=324%:%
-%:%440=324%:%
+%:%440=325%:%
 %:%441=325%:%
 %:%442=326%:%
-%:%443=326%:%
-%:%445=327%:%
+%:%443=327%:%
+%:%444=327%:%
 %:%446=328%:%
 %:%447=329%:%
-%:%455=331%:%
-%:%467=333%:%
+%:%448=330%:%
+%:%456=332%:%
 %:%468=334%:%
@@
 %:%474=340%:%
-%:%476=343%:%
-%:%477=343%:%
-%:%479=344%:%
+%:%475=341%:%
+%:%477=344%:%
+%:%478=344%:%
 %:%480=345%:%
@@
 %:%482=347%:%
-%:%485=349%:%
+%:%483=348%:%
 %:%486=350%:%
-%:%488=352%:%
-%:%489=352%:%
-%:%491=352%:%
-%:%495=352%:%
-%:%496=352%:%
+%:%487=351%:%
+%:%489=353%:%
+%:%490=353%:%
+%:%492=353%:%
+%:%496=353%:%
 %:%497=353%:%
-%:%498=353%:%
-%:%499=353%:%
-%:%508=355%:%
+%:%498=354%:%
+%:%499=354%:%
+%:%500=354%:%
 %:%509=356%:%
@@
 %:%532=379%:%
-%:%534=381%:%
-%:%535=381%:%
+%:%533=380%:%
+%:%535=382%:%
 %:%536=382%:%
-%:%538=383%:%
+%:%537=383%:%
 %:%539=384%:%
-%:%542=386%:%
-%:%544=388%:%
-%:%545=388%:%
+%:%540=385%:%
+%:%543=387%:%
+%:%545=389%:%
 %:%546=389%:%
-%:%548=390%:%
+%:%547=390%:%
 %:%549=391%:%
-%:%550=391%:%
+%:%550=392%:%
 %:%551=392%:%
 %:%552=393%:%
-%:%553=393%:%
+%:%553=394%:%
 %:%554=394%:%
-%:%555=394%:%
-%:%557=394%:%
-%:%561=394%:%
-%:%562=394%:%
-%:%564=395%:%
+%:%555=395%:%
+%:%556=395%:%
+%:%558=395%:%
+%:%562=395%:%
+%:%563=395%:%
 %:%565=396%:%
@@
 %:%570=401%:%
-%:%580=403%:%
+%:%571=402%:%
 %:%581=404%:%
@@
 %:%598=421%:%
+%:%599=422%:%
 %:%600=423%:%
-%:%601=423%:%
-%:%603=425%:%
+%:%601=424%:%
+%:%603=426%:%
 %:%604=426%:%
-%:%605=427%:%
 %:%606=428%:%
 %:%607=429%:%
-%:%616=431%:%
-%:%628=433%:%
-%:%629=434%:%
-%:%630=435%:%
+%:%608=430%:%
+%:%609=431%:%
+%:%610=432%:%
+%:%619=434%:%
 %:%631=436%:%
@@
 %:%652=457%:%
-%:%655=461%:%
-%:%656=462%:%
-%:%657=463%:%
+%:%653=458%:%
+%:%654=459%:%
+%:%655=460%:%
 %:%658=464%:%
@@
 %:%660=466%:%
-%:%663=468%:%
-%:%664=469%:%
-%:%665=470%:%
+%:%661=467%:%
+%:%662=468%:%
+%:%663=469%:%
 %:%666=471%:%
@@
 %:%672=477%:%
-%:%676=479%:%
-%:%677=480%:%
-%:%678=481%:%
+%:%673=478%:%
+%:%674=479%:%
+%:%675=480%:%
 %:%679=482%:%
@@
 %:%689=492%:%
+%:%690=493%:%
 %:%691=494%:%
-%:%692=494%:%
-%:%693=495%:%
-%:%696=496%:%
-%:%700=496%:%
-%:%701=496%:%
-%:%703=497%:%
-%:%704=498%:%
-%:%705=499%:%
-%:%706=499%:%
-%:%708=500%:%
-%:%709=501%:%
-%:%710=502%:%
+%:%692=495%:%
+%:%694=497%:%
+%:%695=497%:%
+%:%696=498%:%
+%:%699=499%:%
+%:%703=499%:%
+%:%704=499%:%
+%:%706=500%:%
+%:%707=501%:%
+%:%708=502%:%
+%:%709=502%:%
 %:%711=503%:%
-%:%717=503%:%
-%:%720=504%:%
-%:%721=505%:%
-%:%722=505%:%
-%:%723=506%:%
-%:%726=507%:%
-%:%730=507%:%
-%:%731=507%:%
-%:%733=508%:%
-%:%734=509%:%
-%:%744=511%:%
-%:%745=512%:%
-%:%746=513%:%
+%:%712=504%:%
+%:%713=505%:%
+%:%714=506%:%
+%:%720=506%:%
+%:%723=507%:%
+%:%724=508%:%
+%:%725=508%:%
+%:%726=509%:%
+%:%729=510%:%
+%:%733=510%:%
+%:%734=510%:%
+%:%736=511%:%
+%:%737=512%:%
 %:%747=514%:%
@@
 %:%764=531%:%
+%:%765=532%:%
 %:%766=533%:%
-%:%767=533%:%
-%:%768=534%:%
-%:%771=535%:%
-%:%775=535%:%
-%:%776=535%:%
-%:%777=535%:%
-%:%779=536%:%
-%:%785=536%:%
-%:%788=537%:%
-%:%789=538%:%
-%:%790=538%:%
-%:%791=539%:%
-%:%792=540%:%
-%:%795=541%:%
-%:%799=541%:%
-%:%800=541%:%
-%:%801=541%:%
-%:%803=542%:%
-%:%804=543%:%
-%:%805=544%:%
-%:%815=546%:%
-%:%816=547%:%
-%:%817=548%:%
+%:%767=534%:%
+%:%769=536%:%
+%:%770=536%:%
+%:%771=537%:%
+%:%774=538%:%
+%:%778=538%:%
+%:%779=538%:%
+%:%780=538%:%
+%:%782=539%:%
+%:%788=539%:%
+%:%791=540%:%
+%:%792=541%:%
+%:%793=541%:%
+%:%794=542%:%
+%:%795=543%:%
+%:%798=544%:%
+%:%802=544%:%
+%:%803=544%:%
+%:%804=544%:%
+%:%806=545%:%
+%:%807=546%:%
+%:%808=547%:%
 %:%818=549%:%
@@
 %:%822=553%:%
-%:%824=556%:%
+%:%823=554%:%
+%:%824=555%:%
 %:%825=556%:%
-%:%828=557%:%
-%:%832=557%:%
-%:%833=557%:%
-%:%835=558%:%
-%:%836=559%:%
-%:%837=560%:%
-%:%847=562%:%
-%:%848=563%:%
-%:%849=564%:%
+%:%827=559%:%
+%:%828=559%:%
+%:%831=560%:%
+%:%835=560%:%
+%:%836=560%:%
+%:%838=561%:%
+%:%839=562%:%
+%:%840=563%:%
 %:%850=565%:%
@@
 %:%853=568%:%
+%:%854=569%:%
 %:%855=570%:%
-%:%856=570%:%
-%:%857=571%:%
-%:%858=572%:%
-%:%861=573%:%
-%:%865=573%:%
-%:%866=573%:%
-%:%867=573%:%
-%:%869=574%:%
-%:%870=575%:%
-%:%871=576%:%
-%:%881=578%:%
-%:%882=579%:%
+%:%856=571%:%
+%:%858=573%:%
+%:%859=573%:%
+%:%860=574%:%
+%:%861=575%:%
+%:%864=576%:%
+%:%868=576%:%
+%:%869=576%:%
+%:%870=576%:%
+%:%872=577%:%
+%:%873=578%:%
+%:%874=579%:%
 %:%884=581%:%
-%:%885=581%:%
-%:%886=582%:%
-%:%887=583%:%
-%:%890=584%:%
-%:%894=584%:%
-%:%895=584%:%
-%:%896=584%:%
-%:%898=585%:%
-%:%908=587%:%
-%:%909=588%:%
-%:%910=589%:%
+%:%885=582%:%
+%:%887=584%:%
+%:%888=584%:%
+%:%889=585%:%
+%:%890=586%:%
+%:%893=587%:%
+%:%897=587%:%
+%:%898=587%:%
+%:%899=587%:%
+%:%901=588%:%
 %:%911=590%:%
@@
 %:%921=600%:%
-%:%925=604%:%
-%:%926=605%:%
-%:%927=606%:%
+%:%922=601%:%
+%:%923=602%:%
+%:%924=603%:%
 %:%928=607%:%
@@
 %:%932=611%:%
-%:%936=614%:%
-%:%937=615%:%
-%:%938=616%:%
+%:%933=612%:%
+%:%934=613%:%
+%:%935=614%:%
 %:%939=617%:%
@@
 %:%954=632%:%
+%:%955=633%:%
+%:%956=634%:%
+%:%957=635%:%

### 2022-02-19 paper/output/document/thesis_3_implementation.tex
i wrote this chapter in a day lol

@@
 The \texttt{typedecl} keyword indicates that I am defining a new atomic type, which is not composed
-of pre-existing types but is instead a new kind of object altogether. It suffices
-to declare a new type to represent a subject without specifying any of its complex properties, such as the idea that a subject
-must be rational or human. Instead of providing a complete definition of subject, which would require wading into murky
-philosophical debates about the nature of agency, I will provide a ``thin'' definition that only includes
-the minimum necessary properties to apply the FUL. Throughout my project, I will use bare syntactic units like types and constants
-to create thin definitions of new ideas.
+of pre-existing types but is instead a new kind of object altogether. A type does not come with any 
+properties out of the box. There is no difference between declaring the type ``subject'' or any other
+type, such as ``color'' or ``mammal.'' I add some properties of this type below by creating formulas
+and more complex types that use this type, but I do not provide anything near a definition of a subject.
+It suffices to declare a new type to represent a subject without specifying any of its complex properties, 
+such as the idea that a subject must be rational or human. Instead of providing a complete definition of subject, 
+which would require wading into murky philosophical debates about the nature of agency, I provide a 
+``thin'' definition that only includes the minimum necessary properties to apply the FUL. Throughout my 
+project, I will use bare syntactic units like types and constants to create thin definitions of new ideas.
+This strategy lets me avoid messy philosophical controversies and makes my system's judgements more 
+trustworthy, because they rely on relatively little prior knowledge.
 
@@
 %:%110=45%:%
+%:%111=46%:%
 %:%112=47%:%
-%:%113=47%:%
-%:%115=48%:%
-%:%116=49%:%
-%:%117=50%:%
-%:%118=51%:%
-%:%119=52%:%
+%:%113=48%:%
+%:%114=49%:%
+%:%115=50%:%
+%:%117=52%:%
+%:%118=52%:%
 %:%120=53%:%
@@
 %:%122=55%:%
-%:%130=57%:%
-%:%142=59%:%
-%:%143=60%:%
-%:%144=61%:%
-%:%145=62%:%
-%:%146=63%:%
+%:%123=56%:%
+%:%124=57%:%
+%:%125=58%:%
+%:%126=59%:%
+%:%127=60%:%
+%:%135=62%:%
 %:%147=64%:%
@@
 %:%168=85%:%
-%:%170=88%:%
+%:%169=86%:%
+%:%170=87%:%
 %:%171=88%:%
-%:%173=89%:%
-%:%174=90%:%
-%:%175=91%:%
-%:%176=92%:%
-%:%177=93%:%
+%:%172=89%:%
+%:%173=90%:%
+%:%175=93%:%
+%:%176=93%:%
 %:%178=94%:%
@@
 %:%180=96%:%
-%:%183=98%:%
-%:%184=99%:%
-%:%185=100%:%
-%:%186=101%:%
-%:%187=102%:%
+%:%181=97%:%
+%:%182=98%:%
+%:%183=99%:%
+%:%184=100%:%
+%:%185=101%:%
 %:%188=103%:%
@@
 %:%240=155%:%
+%:%241=156%:%
 %:%242=157%:%
-%:%243=157%:%
-%:%244=158%:%
-%:%246=159%:%
-%:%247=160%:%
-%:%248=161%:%
-%:%249=162%:%
-%:%257=164%:%
-%:%269=166%:%
-%:%270=167%:%
-%:%271=168%:%
-%:%272=169%:%
-%:%273=170%:%
+%:%243=158%:%
+%:%244=159%:%
+%:%245=160%:%
+%:%247=162%:%
+%:%248=162%:%
+%:%249=163%:%
+%:%251=164%:%
+%:%252=165%:%
+%:%253=166%:%
+%:%254=167%:%
+%:%262=169%:%
 %:%274=171%:%
@@
 %:%319=216%:%
-%:%321=219%:%
+%:%320=217%:%
+%:%321=218%:%
 %:%322=219%:%
 %:%323=220%:%
-%:%325=221%:%
-%:%326=222%:%
-%:%329=224%:%
-%:%330=225%:%
-%:%331=226%:%
-%:%332=227%:%
-%:%333=228%:%
+%:%324=221%:%
+%:%326=224%:%
+%:%327=224%:%
+%:%328=225%:%
+%:%330=226%:%
+%:%331=227%:%
 %:%334=229%:%
@@
 %:%350=245%:%
-%:%352=248%:%
+%:%351=246%:%
+%:%352=247%:%
 %:%353=248%:%
 %:%354=249%:%
-%:%356=250%:%
-%:%357=251%:%
-%:%358=251%:%
-%:%361=257%:%
-%:%362=258%:%
-%:%363=259%:%
-%:%364=260%:%
-%:%365=261%:%
+%:%355=250%:%
+%:%357=253%:%
+%:%358=253%:%
+%:%359=254%:%
+%:%361=255%:%
+%:%362=256%:%
+%:%363=256%:%
 %:%366=262%:%
@@
 %:%371=267%:%
+%:%372=268%:%
 %:%373=269%:%
-%:%374=269%:%
-%:%375=270%:%
-%:%377=271%:%
-%:%380=273%:%
-%:%381=274%:%
-%:%382=275%:%
-%:%383=276%:%
-%:%384=277%:%
+%:%374=270%:%
+%:%375=271%:%
+%:%376=272%:%
+%:%378=274%:%
+%:%379=274%:%
+%:%380=275%:%
+%:%382=276%:%
 %:%385=278%:%
@@
 %:%412=305%:%
+%:%413=306%:%
 %:%414=307%:%
-%:%415=307%:%
-%:%416=308%:%
-%:%418=309%:%
-%:%419=310%:%
-%:%420=310%:%
-%:%421=311%:%
-%:%422=312%:%
-%:%423=312%:%
-%:%424=313%:%
-%:%426=314%:%
-%:%427=315%:%
-%:%430=317%:%
-%:%431=318%:%
-%:%432=319%:%
-%:%433=320%:%
+%:%415=308%:%
+%:%416=309%:%
+%:%417=310%:%
+%:%419=312%:%
+%:%420=312%:%
+%:%421=313%:%
+%:%423=314%:%
+%:%424=315%:%
+%:%425=315%:%
+%:%426=316%:%
+%:%427=317%:%
+%:%428=317%:%
+%:%429=318%:%
+%:%431=319%:%
+%:%432=320%:%
 %:%435=322%:%
-%:%436=322%:%
-%:%437=323%:%
-%:%439=324%:%
-%:%440=325%:%
-%:%441=325%:%
-%:%442=326%:%
-%:%443=327%:%
-%:%444=327%:%
-%:%446=328%:%
-%:%447=329%:%
-%:%448=330%:%
-%:%456=332%:%
-%:%468=334%:%
-%:%469=335%:%
-%:%470=336%:%
-%:%471=337%:%
-%:%472=338%:%
+%:%436=323%:%
+%:%437=324%:%
+%:%438=325%:%
+%:%440=327%:%
+%:%441=327%:%
+%:%442=328%:%
+%:%444=329%:%
+%:%445=330%:%
+%:%446=330%:%
+%:%447=331%:%
+%:%448=332%:%
+%:%449=332%:%
+%:%451=333%:%
+%:%452=334%:%
+%:%453=335%:%
+%:%461=337%:%
 %:%473=339%:%
@@
 %:%475=341%:%
-%:%477=344%:%
+%:%476=342%:%
+%:%477=343%:%
 %:%478=344%:%
-%:%480=345%:%
-%:%481=346%:%
-%:%482=347%:%
-%:%483=348%:%
-%:%486=350%:%
-%:%487=351%:%
-%:%489=353%:%
-%:%490=353%:%
-%:%492=353%:%
-%:%496=353%:%
-%:%497=353%:%
-%:%498=354%:%
-%:%499=354%:%
-%:%500=354%:%
-%:%509=356%:%
-%:%510=357%:%
-%:%511=358%:%
-%:%512=359%:%
-%:%513=360%:%
+%:%479=345%:%
+%:%480=346%:%
+%:%482=349%:%
+%:%483=349%:%
+%:%485=350%:%
+%:%486=351%:%
+%:%487=352%:%
+%:%488=353%:%
+%:%491=355%:%
+%:%492=356%:%
+%:%494=358%:%
+%:%495=358%:%
+%:%497=358%:%
+%:%501=358%:%
+%:%502=358%:%
+%:%503=359%:%
+%:%504=359%:%
+%:%505=359%:%
 %:%514=361%:%
@@
 %:%533=380%:%
+%:%534=381%:%
 %:%535=382%:%
-%:%536=382%:%
-%:%537=383%:%
-%:%539=384%:%
-%:%540=385%:%
-%:%543=387%:%
-%:%545=389%:%
-%:%546=389%:%
-%:%547=390%:%
-%:%549=391%:%
-%:%550=392%:%
-%:%551=392%:%
-%:%552=393%:%
-%:%553=394%:%
-%:%554=394%:%
-%:%555=395%:%
-%:%556=395%:%
-%:%558=395%:%
-%:%562=395%:%
-%:%563=395%:%
-%:%565=396%:%
-%:%566=397%:%
-%:%567=398%:%
-%:%568=399%:%
-%:%569=400%:%
+%:%536=383%:%
+%:%537=384%:%
+%:%538=385%:%
+%:%540=387%:%
+%:%541=387%:%
+%:%542=388%:%
+%:%544=389%:%
+%:%545=390%:%
+%:%548=392%:%
+%:%550=394%:%
+%:%551=394%:%
+%:%552=395%:%
+%:%554=396%:%
+%:%555=397%:%
+%:%556=397%:%
+%:%557=398%:%
+%:%558=399%:%
+%:%559=399%:%
+%:%560=400%:%
+%:%561=400%:%
+%:%563=400%:%
+%:%567=400%:%
+%:%568=400%:%
 %:%570=401%:%
 %:%571=402%:%
-%:%581=404%:%
-%:%582=405%:%
-%:%583=406%:%
-%:%584=407%:%
-%:%585=408%:%
+%:%572=403%:%
+%:%573=404%:%
+%:%574=405%:%
+%:%575=406%:%
+%:%576=407%:%
 %:%586=409%:%
@@
 %:%601=424%:%
+%:%602=425%:%
 %:%603=426%:%
-%:%604=426%:%
-%:%606=428%:%
-%:%607=429%:%
-%:%608=430%:%
+%:%604=427%:%
+%:%605=428%:%
+%:%606=429%:%
+%:%608=431%:%
 %:%609=431%:%
-%:%610=432%:%
-%:%619=434%:%
-%:%631=436%:%
-%:%632=437%:%
-%:%633=438%:%
-%:%634=439%:%
-%:%635=440%:%
+%:%611=433%:%
+%:%612=434%:%
+%:%613=435%:%
+%:%614=436%:%
+%:%615=437%:%
+%:%624=439%:%
 %:%636=441%:%
@@
 %:%655=460%:%
-%:%658=464%:%
-%:%659=465%:%
-%:%660=466%:%
-%:%661=467%:%
-%:%662=468%:%
+%:%656=461%:%
+%:%657=462%:%
+%:%658=463%:%
+%:%659=464%:%
+%:%660=465%:%
 %:%663=469%:%
-%:%666=471%:%
-%:%667=472%:%
-%:%668=473%:%
-%:%669=474%:%
-%:%670=475%:%
+%:%664=470%:%
+%:%665=471%:%
+%:%666=472%:%
+%:%667=473%:%
+%:%668=474%:%
 %:%671=476%:%
@@
 %:%675=480%:%
-%:%679=482%:%
-%:%680=483%:%
-%:%681=484%:%
-%:%682=485%:%
-%:%683=486%:%
+%:%676=481%:%
+%:%677=482%:%
+%:%678=483%:%
+%:%679=484%:%
+%:%680=485%:%
 %:%684=487%:%
@@
 %:%692=495%:%
+%:%693=496%:%
 %:%694=497%:%
-%:%695=497%:%
-%:%696=498%:%
-%:%699=499%:%
-%:%703=499%:%
-%:%704=499%:%
-%:%706=500%:%
-%:%707=501%:%
-%:%708=502%:%
-%:%709=502%:%
-%:%711=503%:%
-%:%712=504%:%
-%:%713=505%:%
-%:%714=506%:%
-%:%720=506%:%
-%:%723=507%:%
-%:%724=508%:%
-%:%725=508%:%
-%:%726=509%:%
-%:%729=510%:%
-%:%733=510%:%
-%:%734=510%:%
-%:%736=511%:%
-%:%737=512%:%
-%:%747=514%:%
-%:%748=515%:%
-%:%749=516%:%
-%:%750=517%:%
-%:%751=518%:%
+%:%695=498%:%
+%:%696=499%:%
+%:%697=500%:%
+%:%699=502%:%
+%:%700=502%:%
+%:%701=503%:%
+%:%704=504%:%
+%:%708=504%:%
+%:%709=504%:%
+%:%711=505%:%
+%:%712=506%:%
+%:%713=507%:%
+%:%714=507%:%
+%:%716=508%:%
+%:%717=509%:%
+%:%718=510%:%
+%:%719=511%:%
+%:%725=511%:%
+%:%728=512%:%
+%:%729=513%:%
+%:%730=513%:%
+%:%731=514%:%
+%:%734=515%:%
+%:%738=515%:%
+%:%739=515%:%
+%:%741=516%:%
+%:%742=517%:%
 %:%752=519%:%
@@
 %:%767=534%:%
+%:%768=535%:%
 %:%769=536%:%
-%:%770=536%:%
-%:%771=537%:%
-%:%774=538%:%
-%:%778=538%:%
-%:%779=538%:%
-%:%780=538%:%
-%:%782=539%:%
-%:%788=539%:%
-%:%791=540%:%
-%:%792=541%:%
-%:%793=541%:%
-%:%794=542%:%
-%:%795=543%:%
-%:%798=544%:%
-%:%802=544%:%
-%:%803=544%:%
-%:%804=544%:%
-%:%806=545%:%
-%:%807=546%:%
-%:%808=547%:%
-%:%818=549%:%
-%:%819=550%:%
-%:%820=551%:%
-%:%821=552%:%
-%:%822=553%:%
+%:%770=537%:%
+%:%771=538%:%
+%:%772=539%:%
+%:%774=541%:%
+%:%775=541%:%
+%:%776=542%:%
+%:%779=543%:%
+%:%783=543%:%
+%:%784=543%:%
+%:%785=543%:%
+%:%787=544%:%
+%:%793=544%:%
+%:%796=545%:%
+%:%797=546%:%
+%:%798=546%:%
+%:%799=547%:%
+%:%800=548%:%
+%:%803=549%:%
+%:%807=549%:%
+%:%808=549%:%
+%:%809=549%:%
+%:%811=550%:%
+%:%812=551%:%
+%:%813=552%:%
 %:%823=554%:%
@@
 %:%825=556%:%
-%:%827=559%:%
+%:%826=557%:%
+%:%827=558%:%
 %:%828=559%:%
-%:%831=560%:%
-%:%835=560%:%
-%:%836=560%:%
-%:%838=561%:%
-%:%839=562%:%
-%:%840=563%:%
-%:%850=565%:%
-%:%851=566%:%
-%:%852=567%:%
-%:%853=568%:%
-%:%854=569%:%
+%:%829=560%:%
+%:%830=561%:%
+%:%832=564%:%
+%:%833=564%:%
+%:%836=565%:%
+%:%840=565%:%
+%:%841=565%:%
+%:%843=566%:%
+%:%844=567%:%
+%:%845=568%:%
 %:%855=570%:%
 %:%856=571%:%
+%:%857=572%:%
 %:%858=573%:%
-%:%859=573%:%
-%:%860=574%:%
-%:%861=575%:%
-%:%864=576%:%
-%:%868=576%:%
-%:%869=576%:%
-%:%870=576%:%
-%:%872=577%:%
-%:%873=578%:%
-%:%874=579%:%
-%:%884=581%:%
-%:%885=582%:%
-%:%887=584%:%
-%:%888=584%:%
-%:%889=585%:%
-%:%890=586%:%
-%:%893=587%:%
-%:%897=587%:%
-%:%898=587%:%
-%:%899=587%:%
-%:%901=588%:%
-%:%911=590%:%
-%:%912=591%:%
-%:%913=592%:%
-%:%914=593%:%
-%:%915=594%:%
+%:%859=574%:%
+%:%860=575%:%
+%:%861=576%:%
+%:%863=578%:%
+%:%864=578%:%
+%:%865=579%:%
+%:%866=580%:%
+%:%869=581%:%
+%:%873=581%:%
+%:%874=581%:%
+%:%875=581%:%
+%:%877=582%:%
+%:%878=583%:%
+%:%879=584%:%
+%:%889=586%:%
+%:%890=587%:%
+%:%892=589%:%
+%:%893=589%:%
+%:%894=590%:%
+%:%895=591%:%
+%:%898=592%:%
+%:%902=592%:%
+%:%903=592%:%
+%:%904=592%:%
+%:%906=593%:%
 %:%916=595%:%
@@
 %:%924=603%:%
+%:%925=604%:%
+%:%926=605%:%
+%:%927=606%:%
 %:%928=607%:%
 %:%929=608%:%
-%:%930=609%:%
-%:%931=610%:%
-%:%932=611%:%
 %:%933=612%:%
@@
 %:%935=614%:%
-%:%939=617%:%
-%:%940=618%:%
-%:%941=619%:%
-%:%942=620%:%
-%:%943=621%:%
+%:%936=615%:%
+%:%937=616%:%
+%:%938=617%:%
+%:%939=618%:%
+%:%940=619%:%
 %:%944=622%:%
@@
 %:%957=635%:%
+%:%958=636%:%
+%:%959=637%:%
+%:%960=638%:%
+%:%961=639%:%
+%:%962=640%:%

### 2022-02-19 paper/output/document/thesis_4_applications.tex
started chapter 4
i wrote this chapter in a day lol

--- 2021-11-26 paper/output/document/application.tex
@@
 \begin{isabellebody}%
-\setisabellecontext{application}%
+\setisabellecontext{thesis{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}applications}%
 %
@@
 \begin{isamarkuptext}%
-In this chapter, I 
-demonstrate my system's ability to formalize longer, more complicated ethical arguments and understand 
-the additional capabilities necessary to use my system in practice. In Chapter 2
-and Chapter 3, I performed metaethical reasoning while testing different formalizations of the FUL. Metaethical
-reasoning analyzes properties of moral thought itself and involves questions about the nature of ethical
-truth. This kind of reasoning contrasts with ``applied 
-ethical reasoning," which is the use of ethics to resolve dilemmas and make judgements about 
-what an agent should or should not do. Applied ethical reasoning is relevant with respect to an agent's
-particular situation, not just an an ethical theory as an abstract entity. In previous chapters' application tests,
-I performed some toy examples of applied ethical reasoning, but in this chapter, I expore how my system can 
-perform extended applied ethical reasoning. Metaethical reasoning is most interesting to philosophers 
-who are trying to formulate the ``best" theory of ethics. Applied ethical reasoning, on the other hand, 
-is useful to ordinary people who are trying to decide how to live their lives. In order for automated 
-ethics to guide AI agents, it must perform applied ethical reasoning.
-
-One challenge of applied ethical reasoning is that it requires more common sense knowledge than metaethical
+In this chapter, I use my system to produce sophisticated, nuanced
+responses to two moral dilemmas. These dilemmas serve as examples of how my system could be used
+in practice and demonstrate my system's ability to formalize longer, more complicted ethical arguments
+than those presented in Chapter 3. 
+Many of the tests in Section \ref{testing} perform metaethical reasoning, which analyzes properties
+of morality itself and involves questions about the nature of ethical truth. In this chapter, I perform
+``applied ethical reasoning," which is the use of ethics to resolve dilemmas and make judgements about 
+what an agent should or should not do. This is the kind of reasoning necessary for an AI agent using my system to
+navigate the real world.
+
+One challenge of applied ethical reasoning is that it requires more factual background than metaethical
 reasoning. Because metaethics is about ethics itself, and not about the dilemmas that ethics is 
 supposed to help us resolve, this kind of reasoning requires very little knowledge about the world. 
-In previous chapters, I perform metaethical reasoning using my system (which formalizes an 
-ethical theory) and basic logical facts and objects. Applied ethical reasoning, on the other hand,
-focuses on a particular ethical dilemma and thus requires enough 
-``common sense" to understand the dilemma and options at hand. For example, an applied ethicist 
-evaluating the permissibility of lying needs some robust definition of the term lying and likely some
-understanding about the activities of communication and truth telling. Kantians specifically describe
-this common sense as ``postulates of rationality" that are nontrivial and nonnormative, but still
-part of the process of practical reasoning itself \citep{silber}. \citet{powers} notes that common sense 
-is a hurder for an automated Kantian ethical agent. In this chapter, I attempt to tackle this challenge and
-endow my system with this kind of common sense in the specific case of lying. In order for my 
-system to be used to perform applied ethical reasoning, it will need to be equipped with a database
-of common sense facts and definitions as I present in this chapter. My system will contribute the core
-reasoning about the Formula of Universal Law, but this reasoning must be applied to objects that are defined
-in this common sense database. In this chapter, I try to understand what this common sense reasoning looks like
-for the specific example of lying.
+Applied ethical reasoning, on the other hand,
+focuses on a particular ethical dilemma and thus requires enough factual background, or common sense, 
+to understand the dilemma and options at hand. For example, an applied ethicist 
+evaluating the permissibility of lying needs a robust definition of the term lying and likely some
+understanding of communication and truth telling. Kantians specifically describe
+this common sense as ``postulates of rationality'' that are nontrivial and nonnormative, but still
+part of the process of practical reasoning itself \citep{silber}.
+
+In this chapter, I attempt to tackle this challenge by
+endowing my system with this kind of common sense in the specific case of lying. In order for my 
+system to perform applied ethical reasoning, it will need common sense facts and definitions, like
+those I present in this chapter. My system contributes the ability to reason
+using the Formula of Universal Law, but this reasoning must be applied to objects that are defined
+using common sense. In this chapter, I describe such common sense for the specific example
+of lying.
 
 Because these common sense facts can determine my system's judgements, they are part of the trusted
-code base for my system. In order for someone to trust my system's judgements, they must trust that the
-common sense database is correct becase changing these common sense facts will change the judgements 
+code base for my system, or the logic and code that a user must trust in order to trust my system. 
+Changing these common sense facts will change the judgements 
 that my system makes. For example, if we define truth telling as an act that is self-contradictory (perhaps
 by defining it as $p \wedge \neg p$), then my system will output that truth telling is prohibited.
-Malicious common sense facts and definitions will result in bad ethical judgements. In other words, garbage in, 
-garbage out. This common sense reasoning is also not a part of the system I contribute here—in order for my
-system to be used, future work must develop a common sense database for the particular situation at hand. 
+Malicious common sense facts and definitions will result in bad ethical judgements. 
 The challenge of endowing automated ethical reasoners with common sense reasoning is not unique to my 
 system, and virtually all prior attempts in machine ethics face similar challenges.\footnote{See Section
-Related Work for a survey of the common sense required in prior work.} Most prior attempts
+Related Work for a survey of the common sense required in prior work.} Many prior attempts
 sidestep this question, whereas I contribute an prototype implementation of one kind of common sense reasoning.
 
-The specific kind of common sense reasoning required appears to be a challenge 
-for automating Kantian ethics, and perhaps a reason that consequentialist or virtue ethical automated
-agents would be within closer reach for automation. Ultimately, Kantian ethics is still
-easiest to automate because it will require fewer, less controversial common sense facts than other ethical
-systems. As the examples in this section demonstrate, Kantian ethics requires a definition of lying (which any other 
-theory would also requires) and the knowledge that if everyone lies in a given context, no one will believe 
-each other in that particular context. This latter fact may not be required for every ethical theory, 
-but is relatively uncontroversial. It is a kind of intuition about human behavior that is generally accepted. 
-Neither a definition of lying nor this property of lying seem like unreasonable prerequisites for ethical reasoning.
-
-Consequentialism, on the other hand, would require much more specific data about the consequences of 
-a lie, perhaps for the specific person's credibility, for the victim of the lie, for the third-parties 
-watching the lie unfold. Consequentialism requires more numerous and specific judgements, all of which are 
-likely to be more controversial than the two outlined above for Kantian ethics. Similarly, virtue ethics
-would likely require information about the actor's entire moral character, including their attitude
-towards the lie and their moral history. Virtue ethics would also require robust definitions of the 
-relevant virtues, in addition to a definition of lying. Thus, while Kantian ethics requires some 
-common sense reasoning, it requires fewer and less controversial background facts than other ethical theories.
-
-The extended examples presented in this section also demonstrate the difficulty of formulating a 
-maxim to pass as input to my implementation of the FUL. A large part of the challenge of applied Kantian
-ethics is formulating a maxim that accurately captures an agent's principle of action, so a totally
-automated agent using my system will need some way to formulate these maxims well. In this section,
-I manually implement Korsgaard's formulation of certain maxims, and I will later argue that manual formulation
-of maxims is, at present, the way forward.
-
-This chapter will provide additional examples of the kinds of common sense facts and maxim formulation required to get my system
-off the ground. I will aim to use as lean and uncontroversial of a common sense database as possible
+This chapter will provide examples of the kinds of common sense facts required to get my system
+off the ground. I use a lean and uncontroversial common sense database
 to achieve robust and powerful results. This serves as evidence for the ease of automating
-Kantian ethics, an example of what additional work my system requires, and a demonstration of the contributions
-that I make. These examples demonstrate that nuanced common sense facts and maxims can cause my system to contribute 
-nuanced judgements faithful to philosophical literature. On one hand, this means that my system can perform
-sophisticated ethical reasoning, but on the other, the quality of this reasoning is heavily reliant on 
-the common sense database and the input maxim. Thus, my system \emph{could} make smart ethical judgements 
-in practice, but getting to that point will require a robust, trusted common sense database and maxim
-formulator.
-
-\emph{Stick a bit here about the philosophical work that will go in this section}%
+Kantian ethics, an example of the additional work required to use my system in practice, and a 
+demonstration of my system's power and flexibility. These examples demonstrate that, armed with nuanced 
+common sense facts, my system can make sophisticated judgements faithful to philosophical literature.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupsubsection{Simple Lying Examples \label{sec:lyingprelim}%
+\isamarkupsubsection{Lies and Jokes \label{joking}%
 }
@@
 \begin{isamarkuptext}%
-This chapter focuses on the example of lying because this case is hotly debated in the Kantian
-literature. I draw on examples of ethical reasoning as presented in Korsgaard's ``Right to Lie," which 
-examines exactly how strict Kant's prohibition on lying is. She picks up a long-running debate in the 
-literature through the example of someone who shows up at your door and asks, ``Is Sara home?" Unbeknownst to them, 
-you know that they want to know Sara's location in order to murder her. Ordinary moral intuition 
-prescribes that, if Sara is home, you should lie and say that she is not in order to 
-protect her from the murderer, but the categorical imperative seems to prohibit lying in all 
-circumstances. In this section, I will formalize Korsgaard's treatment of lying and joking under the 
-categorical imperative, focusing on the common sense assumptions necessary to achieve her conclusions. 
-In the next section, I will formalize the core of Korsgaard's argument that the categorical imperative
-coheres with ordinary intuition and does not prohibit lying to the murderer to protect Sara.
-
-First, Korsgaard argues that the categorical imperative appears to prohibit all lies because, when universalized, 
-lies will no longer be believed. Thus, lying could never be an effective way of achieving any goal when universalized.
-Korsgaard points out that ``we believe what is said to us in a given context because most of the time 
-people in that context say what they really think" \citep[4]{KorsgaardRTL}. In order to formalize this argument,
-I first need to define the relevant terms.%
+The moral status of lying is hotly debated in the Kantian literature. I focus on two dilemmas
+presented in Korsgaard's ``Right to Lie," which 
+examines how strict Kant's prohibition on lying is \citep{KorsgaardRTL}. She begins with the case of 
+lying and joking. Many of Kant's critics argue that his prohibition on lies includes lies told in 
+the context of a joke, which should be permissible. Korsgaard responds by arguing 
+that there is a crucial difference between lying and joking: lies involve deception, but jokes do not. 
+The purpose of a joke is amusement, which does not rely on the listener believing the story told. 
+Given appropriate definitions of lies and jokes, my system shows that jokes are permissible but lies 
+are not, demonstrating its power and flexibility. This section demonstrates how my system can be used 
+in practice; it needs to be given some baseline common sense facts, but with those facts, it can make 
+sophisticated judgements. Moreover, because my system is faithful to definitions found in philosophical 
+literature, it can perform nuanced reasoning, demonstrating the value of faithful automated ethics.
+
+First, Korsgaard argues that the categorical imperative prohibits lies because they involve deception. 
+When universalized, lies will no longer be believed, so lying could never be an effective way of achieving 
+any goal when universalized. Korsgaard points out that ``we believe what is said to us in a given 
+context because most of the time people in that context say what they really think'' \citep[4]{KorsgaardRTL}. 
+In order to formalize this argument, I first need to define the relevant terms and assumptions, which include
+lying and Korsgaard's argument about the basis of trust.
+
+I define lying and trust in terms of belief. As in Section \ref{details}, I choose thin, or minimal,
+definitions of terms like belief to reduce the potential for controversy in my system's factual background.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupcmt{Person s::subject believes sentence t::term. The concept of belief will play a crucial role both in 
-the arguments for lying being prohibited and for the maxim of lying to the murderer being permissible. 
-Logicians and epistemologists have developed robust, complex logics of belief and knowledge \citep{seplogicbelief}. For the 
-sake of this project, I avoid this complexity by merely defining the concept of belief as an empty
-constant that maps a subject, term pair to a term. For the examples in this section, this choice suffices, 
-as my common sense beliefs encode enough properties of belief for my purposes. Future work could
-integrate a much more complex logic of belief into my system.%
-}\isanewline
-\isanewline
+\isamarkupcmt{\texttt{believe} is a constant that maps a subject and a term to another DDL term. For example, 
+subject ``Sara'' might believe the term ``the sky is blue'' to create the sentence ``Sara believes
+that the sky is blue,'' which can be true or false at a world.%
+}%
+\begin{isamarkuptext}%
+Logicians and epistemologists develop and debate complex logics of belief and knowledge \citep{seplogicbelief}. 
+I avoid this complexity by defining the concept of belief simply as a constant that maps a subject, term pair 
+to a term. For the examples in this section, this choice suffices. 
+I encode some minimal properties of belief below, but avoid any full definition of the term.
+
+Belief is useful to construct the idea of ``knowingly uttering a falsehood,'' a core component 
+of both lying and joking.%
+\end{isamarkuptext}\isamarkuptrue%
 \isacommand{consts}\isamarkupfalse%
@@
 %
-\isamarkupcmt{Person s::subject utters sentence t::term.%
+\isamarkupcmt{\texttt{utter} also maps a subject and term to another DDL term. For example, the sentence ``Sara
+utters, `I am hungry' '' is a DDL term that can be true or false at a world.%
 }\isanewline
@@
 \ utter{\isacharunderscore}falsehood{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}s{\isasymRightarrow}t{\isasymRightarrow}t{\isachardoublequoteclose}\ \isakeyword{where}\isanewline
-{\isachardoublequoteopen}utter{\isacharunderscore}falsehood\ s\ t\ {\isasymequiv}\ \ {\isacharparenleft}utter\ s\ t{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ t{\isacharparenright}{\isachardoublequoteclose}\isanewline
-%
-\isamarkupcmt{Person s utters falsehood t if and only if s utters t and t is false.%
+\ \ {\isachardoublequoteopen}utter{\isacharunderscore}falsehood\ s\ t\ {\isasymequiv}\ \ {\isacharparenleft}utter\ s\ t{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ t{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{To utter a falsehood is to utter a statement that is false, or to utter $t$ when $\neg t$.%
 }\isanewline
@@
 \ knowingly{\isacharunderscore}utter{\isacharunderscore}falsehood{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}s{\isasymRightarrow}t{\isasymRightarrow}t{\isachardoublequoteclose}\ \isakeyword{where}\isanewline
-{\isachardoublequoteopen}knowingly{\isacharunderscore}utter{\isacharunderscore}falsehood\ s\ t\ {\isasymequiv}\ {\isacharparenleft}utter{\isacharunderscore}falsehood\ s\ t{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}believe\ s\ t{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-%
-\isamarkupcmt{Person s::subject knowingly utters a falsehood t, if they both utter t as a falsehood and don't
-believe t. This and the above abbreviations are the core of my formalization of Korsgaard's definition
-of lying. They are also relatively uncontroversial and have little normative content.%
-}\isanewline
-\isanewline
+\ \ {\isachardoublequoteopen}knowingly{\isacharunderscore}utter{\isacharunderscore}falsehood\ s\ t\ {\isasymequiv}\ {\isacharparenleft}utter{\isacharunderscore}falsehood\ s\ t{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}believe\ s\ t{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Sometimes we unknowingly utter falsehoods. For example, if I believe that the Earth is flat, then 
+when I utter, ``the Earth is flat,'' I am unknowingly uttering a falsehood. This motivates defining
+the idea of knowingly uttering a falsehood, which requires both uttering a falsehood and not believing 
+your utterance. If I utter ``the Earth is flat,'' even though I know that the Earth is round, I am 
+knowingly uttering a falsehood.%
+}%
+\begin{isamarkuptext}%
+The above abbreviations are the core of my formalization of Korsgaard's definitions
+of lying and joking. They are also relatively uncontroversial and encode little moral
+or normative content. They say nothing about the moral status of uttering a falsehood, 
+the agent's intention when making the utterance, or the conversational norms guiding the utterance. 
+The complexities of a complete definition of lying or belief are 
+unnecessary for Kantian ethics, and therefore for my system, to make moral judgements.
+
+Using the above definitions, I define lying. I characterize a maxim as involving a lie if 
+the act requires knowingly uttering a falsehood and the end requires that some person $p$ believe 
+the false statement $t$.%
+\end{isamarkuptext}\isamarkuptrue%
 \isacommand{abbreviation}\isamarkupfalse%
@@
 %
-\isamarkupcmt{Using the above definitions, I can characterize a maxim as a lie if 
-    (a) the act requires knowingly uttering a falsehood 
-    (b) the end requires that some person $p$ believe the false statement $t$.%
+\isamarkupcmt{The abbreviation above maps a maxim to a boolean value that indicates if it is a lie.%
 }%
 \begin{isamarkuptext}%
-To avoid unintentional wrongdoing, I focus on ``knowing lies," 
+To avoid unintentional wrongdoing, I focus on ``knowing lies,'' 
 in which the speaker is aware that they are lying. It is uncontroversial that, in order for an act to be
-a knowing lie, the speaker must utter a false statement that they do not believe. The second half of 
-this definition requires that the goal of the lie is deception and is inspired by  Korsgaard's interpretation 
+a knowing lie, the speaker must utter a false statement that they do not believe. This also makes it 
+easier to make moral judgements about the speaker's action, since they were, at the very least, aware
+of their lie. The second half of
+this definition requires that the goal of the lie is deception. This is inspired by  Korsgaard's interpretation 
 of a lie. She understands a lie as a kind of falsehood that is usually effective \emph{because} it decieves
 \citep[4]{KorsgaardRTL}. In my formalization, this means that the purpose or goal of the maxim must
-involve decieving someone, or, in other words, that someone believe the falsehood told.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-With the above logical background, I can now automate Korsgaard's argument that maxims that involve
+involve decieving someone, or, in other words, that someone believe what the speaker knows to be a 
+falsehood.
+
+With the above logical background, I automate Korsgaard's argument that maxims that involve
 lying are prohibited. First, I define the subject and maxim at hand.%
@@
 %
-\isamarkupcmt{I am trying to reason about \emph{my} obligations so I will define myself as a specific subject.%
+\isamarkupcmt{I am trying to reason about \emph{my} obligations so I will define myself as a specific subject. Again,
+this is a minimal definition that does not include any facts about me, such as the fact that my name is
+Lavanya or that I have brown hair.%
 }\isanewline
@@
 In the following lemma, I use my system to show that lying is prohibited. The assumptions of 
-this lemma represent the logical and common sense background necessary to reach this conclusion. This
+this lemma represent the common sense necessary to reach this conclusion. This
 common sense background is a direct formalization of the premises of Korsgaard's argument. Using these
-relatively ``thin" premises about individual behavior, my system can derive a prohibition against lying.%
+relatively minimal premises about individual behavior, my system derives a prohibition against lying.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \isamarkupcmt{Assumption that if everyone utters false statement $t$, then no one will believe $t$. This assumption is 
-Korsgaard's core piece of ``common sense" about lying \cite[5]{KorsgaardRTL}. This simple assumption encodes the common sense knowledge
+Korsgaard's core piece of ``common sense'' about lying \cite[5]{KorsgaardRTL}. This simple assumption encodes the common sense knowledge
 that human communication involves an implicit trust, and that when this trust erodes, the convention of 
 communication begins to break down and people no longer believe each other. Call this the ``convention of 
-lying" fact. In the rest of this section, I will test versions of this assumption, effectively encoding 
+trust'' fact. In the rest of this section, I will test versions of this assumption, effectively encoding 
 different common sense understandings of lying.%
@@
 %
-\isamarkupcmt{Restrict our focus to worlds in which the circumstances hold, as these are the morally interesting 
-worlds for this example. A technical detail.%
+\isamarkupcmt{Restrict our focus to worlds in which the circumstances hold. A technical detail.%
 }\isanewline
@@
 %
-\isamarkupcmt{Unlike many of the other proofs in this project, this proof was a little heavier and required some manual
-work to produce. I divided the proof into the intermediate steps shown here, and Isabelle was able to do 
+\isamarkupcmt{This proof requires some manual work. After I divide the proof into the intermediate steps shown 
+here, Isabelle is able to do 
 the rest. This step says that if $m$ is universalized, then the circumstances won't lead to the goal, 
-which is quite close to the idea of the maxim not being universalizable.%
+which is close to the idea of the maxim not being universalizable.%
 }\isanewline
@@
 \isamarkupcmt{$?thesis$ is Isabelle's syntax for the goal of the lemma. In this case, $?thesis$ is equivalent to 
-$\vDash prohibited\! m \! me$.%
+$\vDash prohibited \; m \; me$.%
 }\isanewline
@@
 \begin{isamarkuptext}%
+The lemma above demonstrates that my system finds that lying is prohibited with a thin definition
+of lying and relatively uncontroversial facts about the world. The logical background needed is the fact that lying
+requires knowingly uttering a falsehood with the goal that someone believe the falsehood, a definition
+of lying that is relatively well-accepted. The factual background needed consists of the fact that if 
+everyone lies in a given context, then people will stop believing each other in that context. This is 
+a slightly heavier assumption, but it is still so uncontroversial that Korsgaard doesn't bother to justify
+it in her argument against lying \citep{KorsgaardRTL}.
+
 Now that I have formalized Korsgaard's argument for why lying is prohibited, I will
@@
 does not interfere with the purpose of jokes, which is to amuse and does not depend on
-deception" \citep[4]{KorsgaardRTL}. First, I define a joke..%
+deception'' \citep[4]{KorsgaardRTL}. I use the fact that a joke does not depend on deception as the 
+defining feature of a joke.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \ joke{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
-{\isachardoublequoteopen}joke\ {\isasymequiv}\ {\isasymlambda}\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}{\isachardot}\ \ {\isasymexists}t{\isachardot}\ {\isacharparenleft}a\ \isactrlbold {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymlambda}s{\isachardot}\ knowingly{\isacharunderscore}utter{\isacharunderscore}falsehood\ s\ t{\isacharparenright}{\isacharparenright}\ {\isasymand}\ {\isasymnot}\ {\isacharparenleft}{\isasymexists}p{\isachardot}\ {\isasymforall}w{\isachardot}\ {\isacharparenleft}g\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}believe\ p\ t{\isacharparenright}{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}%
-\begin{isamarkuptext}%
-This definition of a joke merely defines a joke as a falsehood uttered for some purpose that 
-doesn't require deception, where deception involves someone believing the uttered falsehood. Notice 
-that this is quite a thin definition of a joke; it doesn't require any conception of humor but merely
-distinguishes jokes from lies. As far as common sense reasoning goes, this is a relatively tame proposition. 
-I will now demonstrate that this conception of a joke is sufficient to show that joking is permissible.
+{\isachardoublequoteopen}joke\ {\isasymequiv}\ {\isasymlambda}\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}{\isachardot}\ \ {\isasymexists}t{\isachardot}\ {\isacharparenleft}a\ \isactrlbold {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymlambda}s{\isachardot}\ knowingly{\isacharunderscore}utter{\isacharunderscore}falsehood\ s\ t{\isacharparenright}{\isacharparenright}\ {\isasymand}\ {\isasymnot}\ {\isacharparenleft}{\isasymexists}p{\isachardot}\ {\isasymforall}w{\isachardot}\ {\isacharparenleft}g\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}believe\ p\ t{\isacharparenright}{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Thie abbreviation states that a maxim is a joke if the action involves knowingly uttering a falsehood but
+the goal does \emph{not} require that someone believe the falsehood told.%
+}%
+\begin{isamarkuptext}%
+This definition of a joke defines a joke as a falsehood uttered for some purpose that 
+doesn't require deception, where deception involves someone believing the uttered falsehood. 
+This definition doesn't require any conception of humor, but merely
+distinguishes jokes from lies.
 
 Korsgaard argues that her above argument for a prohibition against lying also implies that joking is 
-permissible, because its purpose is \emph{not} to decieve, but something else entirely. This means that, 
-even armed with the same core convention of lying assumption as above, joking must be permissible. The 
+permissible, because its purpose is not to decieve, but something else entirely. This means that, 
+even armed with the same convention of trust assumption as above, joking should be permissible. The 
 lemma below shows exactly that.%
@@
 %
-\isamarkupcmt{The same convention of lying assumption as in the above example.%
+\isamarkupcmt{The same convention of trust assumption as in the above example.%
 }\isanewline
@@
 %
-\isamarkupcmt{Restrict our focus to worlds in which the circumstances hold, as these are the morally interesting 
-worlds for this example. An irrelevant technical detail.%
+\isamarkupcmt{Restrict our focus to worlds in which the circumstances hold. A technical detail.%
 }\isanewline
@@
 \isacommand{by}\isamarkupfalse%
-\ {\isacharparenleft}smt\ assms{\isacharparenleft}{\isadigit{1}}{\isacharparenright}\ assms{\isacharparenleft}{\isadigit{2}}{\isacharparenright}\ assms{\isacharparenleft}{\isadigit{3}}{\isacharparenright}\ case{\isacharunderscore}prod{\isacharunderscore}conv{\isacharparenright}%
+\ {\isacharparenleft}smt\ assms{\isacharparenleft}{\isadigit{1}}{\isacharparenright}\ assms{\isacharparenleft}{\isadigit{2}}{\isacharparenright}\ assms{\isacharparenleft}{\isadigit{3}}{\isacharparenright}\ case{\isacharunderscore}prod{\isacharunderscore}conv{\isacharparenright}\isanewline
+%
+\isamarkupcmt{Isabelle is able to show that maxims about joking are permissible. It also lists the facts used 
+in its proof, which offer insight into how it arrived at its judgement. Specifically, it uses assumptions 1, 
+2, and 3, which are the logical background and definition of the joking maxim. Notably, it does not use the 
+convention of trust assumption. This demonstrates that even the convention of trust assumption is not
+strong enough to prohibit joking, which is exactly the desired result.%
+}%
 \endisatagproof
@@
 \begin{isamarkuptext}%
-This completes my implementation of Korsgaard's first interpretation of lying. Using the convention
-of lying assumption formalized in this section, I show that lying is generally prohibited but joking
-is permissible. Notice that this is already a sophisticated kind of ethical reasoning. The sophistication
-necessary to distinguish between lying and joking is a direct consequence of my system's use of a robust
-conception of a maxim, which encodes the goal of an act as part of the maxim being evaluated. This kind 
-of ethical reasoning also requires relatively few and uncontroversial common sense facts. The deepest
-assumption required was that, if everyone lies about a given statement, no one will believe that 
-statement. This assumption is not merely definitional; it does encode some synthetic knowledge about the 
-world, but it is relatively uncontroversial. Indeed, it is so well-accepted that Korsgaard does not 
-bother to justify it in her argument. These examples demonstrate that, while common sense reasoning 
-is an obstacle that must be overcome for my system to be used in practice, it is surmountable.%
+My system shows that lies are prohibited and jokes are permissible with thin 
+conceptions of amusement and deception. This shows that it isolates a necessary and sufficient property 
+of this class of maxims that fail the universalizability test. My definitions of a lie and joke
+only differ in whether or not their goal requires that someone believe the falsehood in question, so
+this is a necessary and sufficient condition for a maxim about knowingly uttering falsehoods to be prohibited.
+This logical fact derived by my system tracks a fact implicit in Korsgaard's argument and in most Kantian accounts
+of lying: the wrongness of lying is derived from the requirement that someone believe the falsehood. 
+The logical reality that this property is necessary and sufficient to generate a prohibition reflects
+a deep philosohopical explanation of \emph{why} certain maxims about uttering falsehood fail the universalizability
+test. Universalizing uttering a falsehood makes belief in that 
+falsehood impossible, so any maxims with goals that require believing in the falsehood will be prohibited.
+
+This account not only describes the kind of maxims that fail or pass the universalizability test, but it 
+also provides a guide to constructing permissible maxims about uttering falsehoods. As an example, 
+consider the idea of throwing a surprise birthday party. At first glance, the maxim of action is 
+something like, ``When it is my friend's birthday, I will secretly plan a party so that I can surprise
+them.'' The goal ``so that I can surprise them'' clearly requires that your friend believe the falsehood that 
+you are not planning a party, else the surprise would be ruined. This seems to imply that 
+Kantian ethics would prohibit surprise parties, which is a sad conclusion for birthday-lovers everywhere. 
+Knowing that this maxim is prohibited because the goal requires belief
+in a falsehood provides a way to rescue surprise parties. When throwing a 
+surprise party, the objective is \emph{not} to surprise your friend, but to celebrate
+your friend and help them have a fun birthday. If someone ruins the surprise, but the party is still fun
+and the birthday person feels loved, then such a party is a success! Someone who
+calls this party a failure is clearly missing the point of a surprise party. The goal of 
+a surprise party is not the surprise itself, but rather celebrating the birthday person. The modified
+goal no longer requires belief in the falsehood and thus passes the universalizability test.
+
+There are two implications of this section. First, my system is capable of performing ethical reasoning
+sophisticated enough to show that lying is prohibited but joking is not. This is a direct consequence 
+of my system's use of a robust conception of a maxim, which encodes the goal of an act as part of the 
+maxim being evaluated. Because my implementation is faithful to philosophical literature, it is able 
+to recreate Korsgaard's solution to a complex ethical dilemma that philosophers debated for decades. Second, 
+in the process of making this argument precise, my system isolated a necessary and sufficient condition 
+of a maxim about uttering a falsehood being prohibited: that the goal require that someone believe
+the falsehood. This condition both made an long-standing argument in Kantian ethics more precise
+and can guide the correct formulation of future maxims. In other words, an insight generated by the 
+computer provides value to ethicists, bolstering the argument for computational ethics provided in 
+Section Computational Ethics.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupsubsection{Lying to a Liar \label{sec:lyingtoliar}%
+\isamarkupsubsection{Lying to a Liar \label{murderer}%
 }
@@
 \begin{isamarkuptext}%
-Once Korsgaard completes her preliminary work differentiating between lies and jokes, she begins her main
- argument, which examines the controversial case of the murderer at the door. Recall that the murderer
-appears at your door and asks if his intended victim is at home. Ordinary intuition requires that it 
-is at the very least permissible (if not obligatory) to lie to the murderer in order to protect the 
-victim. Korsgaard notes that a murderer who wishes to find his victim cannot simply announce his
-intentions to murder; instead, he must ``must suppose that you do not know who he is and
-what he has in mind" \citep[5]{KorsgaardRTL}.\footnote{Korsgaard assumes that the murderer will lie 
-about his identity in order to take advantage of your honesty. In footnote 5, she accepts that her 
-arguments will not apply in the case of the honest murderer who announces his intentions, so she 
-restricts her focus to the case of lying to a liar. She claims that in the case of the honest murderer, the correct act is 
-to refuse to respond, but she does not argue for this in this paper.} Thus, she can modify the maxim in 
-question to specify that when someone lies to you, you are allowed to lie to them. The maxim of lying 
-to the murderer is actually the maxim of lying to a liar, which she argues is permissible. Notice that
-her argument hinges on this clever, but ultimately sensical formulation of your maxim. She notes
-that there is something relevant and significant about the fact that the person demanding to know Sara's
-location is a murderer and that he is trying to take advantage of your honesty. This claim is not
-unfounded or wildly controversial, but it does demonstrate the importance of correctly formulating
-the maxim to test. In this section, I will formalize her argument for lying to a liar.
-
-As usual, I first define my terms.%
+My system can not only distinguish between lying and joking, but it can also resolve the paradox of 
+the murderer at the door. In this dilemma, murderer Bill knocks on your door asking about Sara, his 
+intended victim. Sara is at home, but moral intuition says that you should lie to Bill and say 
+that she is out to prevent him from murdering her. Many critics of Kantian ethics argue that the 
+FUL prohibits you from lying in this instance; if everyone lied to murderers, then murderers wouldn't 
+believe the lies and would search the house anyways. Korsgaard resolved this centuries-long debate by 
+noting that the maxim of lying to a murderer is actually that of lying to a liar: Bill cannot 
+announce his intentions to murder; instead, he must ``must suppose that you do not know who he is 
+and what he has in mind'' \citep{KorsgaardRTL}.\footnote{Korsgaard assumes that the murderer will 
+lie about his identity in order to take advantage of your honesty to find his victim. In footnote 5 
+of \citep{KorsgaardRTL}, she accepts that her arguments will not apply in the case of the honest murderer 
+who announces his intentions, so she restricts her focus to the case of lying to a liar. She claims 
+that in the case of the honest murderer, the correct act is to refuse to respond.} Thus, the maxim 
+in question specifies that when someone lies to you, you are allowed to lie to them. The maxim of 
+lying to the murderer is actually the maxim of lying to a liar, which is permissible.
+
+In this section, I formalize her argument for the permissibility of lying to a liar. First, I define
+Bill's maxim, which is to hide his intention to murder.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupcmt{This example involves one more subject: the murderer.%
+\isamarkupcmt{This example involves one additional subject: the murderer.%
 }\isanewline
@@
 \isamarkupcmt{Using the above definitions, I can define the murderer's maxim as, ``When at your door, I will knowingly
-utter the falsehood that I am not a murderer in order to find my intended victim." Now I will repeat
-the same process for your maxim.%
-}\isanewline
-\isanewline
+utter the falsehood that I am not a murderer in order to find my intended victim.''%
+}%
+\begin{isamarkuptext}%
+These constants are defined only in relation to each other and elide most of the complex features
+of murder, life, and death. These thin representations will suffice to show
+the wrongness of the murderer's maxim. Similarly, I can use thin representations to define your
+maxim of lying about Sara's whereabouts.%
+\end{isamarkuptext}\isamarkuptrue%
 \isacommand{consts}\isamarkupfalse%
@@
 \isamarkupcmt{Using these definitions, I construct your maxim, which is ``When a murderer is at my door, I will 
-knowingly utter the falsehood that his intended victim is not at home in order to protect the victim."%
+knowingly utter the falsehood that his intended victim is not at home, in order to protect the victim.''%
 }%
-\begin{isamarkuptext}%
-Now that I have defined the maxims at hand, I can begin reasoning about them. First, I will show 
-that, using the same convention of lying common sense fact as above, the murderer's maxim is prohibited.
-Effectively, this tests that the assumption is indeed strong enough to prohibit lying.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ murderers{\isacharunderscore}maxim{\isacharunderscore}prohibited{\isacharcolon}\isanewline
-\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}w{\isachardot}\ well{\isacharunderscore}formed\ murderers{\isacharunderscore}maxim\ murderer\ w{\isachardoublequoteclose}\isanewline
-%
-\isamarkupcmt{Initial set-up: the murderer's maxim is well-formed.%
-}\isanewline
-\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}find{\isacharunderscore}victim\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}believe\ me\ not{\isacharunderscore}a{\isacharunderscore}murderer{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-%
-\isamarkupcmt{Assumption that, in order for the murderer to find their victim, you must not believe that he is a murderer.
-This is an example of the kind of situation-specific common sense reasoning necessary to use my system.
-Again, this is an uncontroversial statement; the murderer assumes that if you knew he was a murderer, you 
-would not disclose the victim's location to him. SHOULD I SAY MORE HERE?%
-}\isanewline
-\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}t\ w{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isasymforall}p{\isachardot}\ utter{\isacharunderscore}falsehood\ p\ t\ w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ \isactrlbold {\isasymnot}\ {\isacharparenleft}believe\ p\ t{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-%
-\isamarkupcmt{The convention of lying common sense assumption from above.%
-}\isanewline
-\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}w{\isachardot}\ when{\isacharunderscore}at{\isacharunderscore}my{\isacharunderscore}door\ w{\isachardoublequoteclose}\isanewline
-%
-\isamarkupcmt{Restrict our focus to worlds in which the circumstance of the murderer being at my door holds, as 
-these are the morally interesting worlds for this example. An irrelevant technical detail.%
-}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}prohibited\ murderers{\isacharunderscore}maxim\ murderer{\isacharparenright}{\isachardoublequoteclose}\ \ \ \isanewline
-%
 \isadelimproof
@@
 \isatagproof
-\isacommand{proof}\isamarkupfalse%
-\ {\isacharminus}\ \isanewline
-%
-\isamarkupcmt{Again, this proof is too heavy for Isabelle to finish on its own, so I needed to specify some
-intermediate steps. The same intermediate steps as above sufficed, effectively providing a pattern for 
-the proof. Isabelle does allow users to define custom `proof methods,' so a more robust version of 
-my system could define this proof pattern as a method and apply it in cases involving lies.%
-}\isanewline
-\ \ \isacommand{have}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymforall}p\ w{\isachardot}\ {\isacharparenleft}W\ murderers{\isacharunderscore}maxim\ p{\isacharparenright}\ w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymTurnstile}\ {\isacharparenleft}when{\isacharunderscore}at{\isacharunderscore}my{\isacharunderscore}door\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ find{\isacharunderscore}victim{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-\ \ \ \ \isacommand{using}\isamarkupfalse%
-\ assms{\isacharparenleft}{\isadigit{2}}{\isacharparenright}\ assms{\isacharparenleft}{\isadigit{4}}{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
-\ auto\isanewline
-\ \ \ \isacommand{have}\isamarkupfalse%
-\ {\isachardoublequoteopen}not{\isacharunderscore}universalizable\ murderers{\isacharunderscore}maxim\ murderer{\isachardoublequoteclose}\isanewline
-\ \ \ \ \ \isacommand{using}\isamarkupfalse%
-\ assms{\isacharparenleft}{\isadigit{2}}{\isacharparenright}\ assms{\isacharparenleft}{\isadigit{4}}{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
-\ auto\isanewline
-\ \ \ \isacommand{thus}\isamarkupfalse%
-\ {\isacharquery}thesis\isanewline
-\ \ \ \ \ \isacommand{using}\isamarkupfalse%
-\ FUL\ assms{\isacharparenleft}{\isadigit{1}}{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
-\ blast\isanewline
-\ \isacommand{qed}\isamarkupfalse%
 %
@@
 \begin{isamarkuptext}%
-I will now formalize Korsgaard's argument for the permissibility of lying to a liar. She modifies
-the convention of lying assumption above when she argues that, if the murderer believes that you don't 
+I now formalize Korsgaard's argument for the permissibility of lying to a liar. She modifies
+the convention of trust assumption above when she argues that, if the murderer believes that you don't 
 believe he is a murderer, he will think that you won't lie to him. Precisely, she claims that, 
@@
 you do not know you are addressing a murderer - and so does not conclude from the fact that people 
-in those circumstances always lie that you will lie" \cite[6]{KorsgaardRTL}. Even though the maxim of 
-lying to a murderer is universalized, the murderer thinks that you don't know his true identity. Thus,
+in those circumstances always lie that you will lie'' \cite[6]{KorsgaardRTL}. Even though the maxim of 
+lying to a murderer is universalized, Bill thinks that you don't know his true identity. Thus,
 even if you have willed this maxim, he thinks that you won't perform the act of lying to the murderer,
-since you don't think you're in the relevant circumstances. I formalize this argument below.%
+since he thinks that you don't think you're in the relevant circumstances. I formalize this argument below.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupcmt{Assume that we're working with well-formed maxims.%
+\isamarkupcmt{Initial set-up: both maxims are well-formed.%
 }\isanewline
@@
 %
-\isamarkupcmt{In order for you to successfully protect the victim, the murderer must believe that the victim is not
-home. This is a noncontroversial assumption about the specific act at hand.%
+\isamarkupcmt{In order for you to protect the victim, the murderer must believe that the victim is not home.%
 }\isanewline
@@
 utters a sentence as a falsehood, then person1 won't believe that sentence. This is a modification of the 
-convention of lying assumption from above, and I will refer to it as the ``convention of belief" assumption.
-Again, like the convention of lying assumption, this assumption is uncontroversial: if I think you are 
+convention of trust assumption from above, and I will refer to it as the ``convention of belief" assumption.
+Again, like the convention of trust assumption, this assumption is uncontroversial: if I think you are 
 saying a false sentence, then I won't believe that sentence.%
@@
 %
-\isamarkupcmt{This is the second major common sense assumption. If the maxim (c, a, g) is universalized, then if person1 believes 
-person2 believes they are in the given circumstances, then person1 believes person2 performs the act. In other words, person1 will believe that 
-person2 wills the maxim. I will refer to this as the ``convention of willing" assumption. This follows
+\isamarkupcmt{This is the second major common sense assumption. If the maxim (c, a, g) is universalized, then 
+if person1 believes that person2 believes they are in the given circumstances, then person1 believes 
+that person2 performs the act. In other words, person1 will believe that 
+person2 wills the maxim. I will refer to this as the ``convention of willing'' assumption. This follows
 directly from Korsgaard's conception of universalizability: when a maxim is universalized, everyone 
-wills it. Korsgaard assumes that if everyone wills a maxim, they also believe that everyone else wills it.
-DO I NEED TO SAY MORE HERE?%
+wills it and thus notices the pattern of everyone willing it. If you observe that many do X in circumstances C,
+you will assume that everyone does X in circumstance C.%
 }\isanewline
@@
 %
-\isamarkupcmt{Restrict our focus to worlds in which the circumstance of the murderer being at my door holds, as 
-these are the morally interesting worlds for this example. An irrelevant technical detail.%
+\isamarkupcmt{Restrict our focus to worlds in which the circumstance of the murderer being at my door holds. 
+A technical detail.%
 }\isanewline
@@
 %
-\isamarkupcmt{Notice the use of the first and sixth assumption in this automatically generated proof. Essentially, 
-the common sense assumptions given are not strong enough to generate a prohibition against lying to a liar,
-and are thus unused in this proof.%
+\isamarkupcmt{Isabelle completes this proof using the first and sixth assumption, ignoring the convention of 
+belief and convention of willing assumptions. These common sense assumptions are 
+not strong enough to generate a prohibition against lying to a liar and are thus unused in this proof.%
 }%
@@
 \begin{isamarkuptext}%
-The above lemma shows that, with a more nuanced set of common sense facts, my system can show that 
-lying to a liar is permissible. Moreover, I know that this set of assumptions is correct because it 
-can also show that the murderer's maxim is prohibited. I show this in the lemma below.%
+The above lemma shows that, with a nuanced set of common sense facts, my system can show that 
+lying to a liar is permissible. One worry may be that this set of assumptions is too weak to yield a 
+prohibition against wrong maxims, like that of the murderer. As a sanity check, I show that this set of assumptions 
+prohibits the murderer's maxim below.%
 \end{isamarkuptext}\isamarkuptrue%
 \isacommand{lemma}\isamarkupfalse%
-\ murderers{\isacharunderscore}maxim{\isacharunderscore}prohibited{\isadigit{2}}{\isacharcolon}\isanewline
+\ murderers{\isacharunderscore}maxim{\isacharunderscore}prohibited{\isacharcolon}\isanewline
 \ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}w{\isachardot}\ well{\isacharunderscore}formed\ murderers{\isacharunderscore}maxim\ murderer\ w{\isachardoublequoteclose}\isanewline
 %
-\isamarkupcmt{The murderer's maxim is a well-formed maxim composed of some circumstances, act, and goal.%
+\isamarkupcmt{Initial set-up: the murderer's maxim is well-formed.%
 }\isanewline
@@
 %
-\isamarkupcmt{Assumption that, in order for the murderer to find their victim, you must not believe that they are a murderer.%
+\isamarkupcmt{In order for you to protect the victim, the murderer must believe that the victim is not home.%
 }\isanewline
@@
 %
-\isamarkupcmt{The convention of belief assumption from above.%
+\isamarkupcmt{The convention of belief assumption.%
 }\isanewline
@@
 %
-\isamarkupcmt{The convention of willing assumption from above.%
+\isamarkupcmt{The convention of willing assumption.%
 }\isanewline
@@
 modifying the common sense facts used, my system can show that lying to a liar is permissible, but lying 
-in order to find a victim is not. The assumptions used in this example are a little more robust, but still
-ultimately uncontroversial. Indeed, they are direct consequences of Korsgaard's definition of willing 
+in order to find a victim is not. The assumptions used in this example were a little more robust, but still
+ultimately uncontroversial because they were direct consequences of Korsgaard's definition of willing 
 and of ordinary definitions of lying. These thin assumptions were sufficient to generate moral conclusions
-that Kantian scholars debate robustly. Indeed, armed with this common sense, my system generated 
-a conclusion that many critics of Kant failed to see.
-
-While it is true that lying to the murderer should be permissible, Korsgaard notes that many will want
+that Kantian scholars debate robustly. Armed with this common sense, my system generated 
+a conclusion that many critics of Kant prior to Korsgaard failed to see.\footnote{
+While it is true that lying to the murderer should be permissible, Korsgaard notes that many may want
 to say something stronger, like the fact that lying to the murderer is obligatory in order to protect
-the intended victim \citep[15]{KorsgaardRTL}. It seems like we would be doing something wrong if I revealed the victim's
-location, knowing that this revelation would cost them their life. Korsgaard solves this problem by 
+the intended victim \citep[15]{KorsgaardRTL}. Korsgaard solves this problem by 
 noting that, while the FUL shows that lying to the murderer permissible, other parts of Kant's ethics
-will show that it is obligatory. Recall that Kant presents perfect and imperfect duties,
+show that it is obligatory. Recall that Kant presents perfect and imperfect duties,
 where the former are strict, inviolable, and specific and the latter are broader prescriptions for action.
-Perfect duties always supersede imperfect duties when the two conflict.
-For example, the duty to not murder is a perfect duty and the duty to give to charity is an imperfect duty. 
-The FUL generates perfect duties and Kant's extended theory of virtues generates imperfect duties. The details
-of this theory and these distinctions are outside the scope of this paper, but the crucial note is that 
-other parts of Kant's ethical theory generate the obligation to lie to the murderer. I chose
-to formalize the FUL because it is, in some sense, the strongest of the formulations of the categorical
-imperative. An even more sophisticated Kantian reasoner could formalize his theory of virtue and his
-other formulatations of the categorical imperative in order to generate the obligation to lie to the murderer, 
-but the FUL is the strongest and most foundational of these principles. The fact that my system merely
-shows that lying to the murderer is permissible, but not obligatory is consistent with the part of 
-Kant's ethical theory that I formalize and demonstrates that I have faithfully implemented the FUL.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-While this example demonstrates the power of my system (when equipped with some common sense), it 
-also shows how vital the role of the common sense reasoning is. Slight, intuitive changes in the common
-sense facts can achieve totally different conclusions about lying. This represents an obstacle to 
-fully automated ethical reasoning; such an agent would need a trusted database of common 
-sense facts, which is still an unsolved problem. My work is one step towards such an agent, but the 
-importance of common sense means that much progress must be made in order to completely automate ethics.
-
-The reasoning of this section also demonstrates one additional place where a Kantian must make vital judgements:
-the formulation of the maxim itself. Korsgaard's argument for the permissibility of lying to a 
-murderer hinged on a clever formulation of the maxim highlighting a particular facet of the circumstances, 
-namely that the murderer is lying to you. Indeed, there is robust debate in the literature on what
-circumstances should be considered when formulating a maxim. Some critics of Kant raise the ``tailoring
-objection," which is the worry that arbitrarily specific circumstances render any maxim universalizable. For 
-example, the maxim ``When my name is Lavanya Singh and I am wearing a purple shirt and it is November 26th, 
-I will lie in order to get some easy cash" passes the universalizability test. Even if this maxim is 
-willed universally, the circumstances are so specific that lying will not become the general mechanism
-for getting easy cash, so the lender will believe my lie and the maxim will remain effective. By tailoring
-the circumstances, any maxim can evade universalization.
-
-The Kantian response to this criticism is to require that the circumstances included in the formulation
-of the maxim be ``morally relevant." In the example above, my purple shirt and the date clearly have no bearing on 
-the moral status of lying. On the other hand, consider the maxim ``When I am unmeployed, I will murder
-someone in order to take their job." The circumstances of being unmeployed clearly have some bearing on the moral
-relevance of the murder in question; they speak to the motivation for the murder. While this view seems 
-to track how we actually perform moral reasoning, it leaves open the question of how to determine
-which circumstances are morally relevant. Here, O'Niell reminds us that the Formula of Universal Law is 
-a ``test of moral worth rather than of outward rightness" \citep[98]{constofreason}. The FUL is a way 
-for an agent to decide how they should behave, not for a third-party to judge their behavior. Ethics is 
-a personal process for Kant, so the FUL is designed to help agents internally make decisions, not to 
-judge others' decisions. Because agents use the FUL to evaluate their own behavior, the test is at its 
-best when they make a good faith effort to isolate the \emph{principle} of their action, rather than some
-``surface intent" \citep[87]{constofreason}. The FUL is supposed to determine if an agent's principle of action
-is universally consistent, so it is at its most effective when an agent accurately formulates the principle
-they act on. Circumstances are morally relevant if they accurately reflect the way that the agent is 
-thinking about their own action. In the example above, the circumstances of wearing a purple shirt don't
-the principle of the liar's action. They are clearly a disingenous attempt to evade the universalizability
-test, but because the FUL is a test of personal integrity, it cannot withstand this kind of mental
-gymnastics.
-
-While this account of the formulation of a maxim prescribes how a well-intentioned agent should
-decide how to live their life, it poses a challenge for automated ethics. In order for an automated
-ethical agent to use the categorical imperative to its fullest extent, the input maxim fed into
-my system or any automation of the FUL must be a good-faith attempt to capture the agent's principle
-of action. However an action is turned into a maxim for my system to process, whether manually as I do
-during these tests or automatically using some kind of input parser, this transformation from action
-to maxim has huge bearing on the outcome of the test. The formulation of a maxim must be a good-faith 
-attempt to capture the principle of action, and must therefore include only the morally relevant
-circumstances, and nothing more. This is a significant judgement that my system does not make, and is 
-thus another hurdle that must be overcome in order for my system to be used in practice. I will argue
-in Section ?? that this kind of input parsing work should be left to human beings for now, and that
-major technical and philosophical progress must be made to automate this portion of the system.
-
-The formulation of a maxim and the common sense database pose the two greatest challenges to the adoption
-of my system in practice. In this chapter, I argue that using manual, human involvement, these challenges
-can be overcome in relatively uncontroversial ways. They are also ripe areas for future work.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\isatagdocument
-%
-\isamarkupsubsection{Philosophical Analysis: Is Automated Ethics a Good Idea?%
-}
-\isamarkuptrue%
-%
-\endisatagdocument
-{\isafolddocument}%
-%
-\isadelimdocument
-%
-\endisadelimdocument
+The details of this distinction are outside the scope of this thesis, but imperfect duties generate 
+the obligation to lie to the murderer. An even more sophisticated automated Kantian reasoner could formalize 
+imperfect duties and other formulatations of the categorical imperative in order to generate the 
+obligation to lie to the murderer.}
+
+While this example demonstrates the power of my system, it
+also shows how vital the role of the common sense reasoning is. Slight, intuitive changes in the factual
+background achieved completely different conclusions about lying. This example also demonstrates the importance
+and difficulty of correctly formulating the maxim, particularly its circumstances.
+Korsgaard's argument for the permissibility of lying to a 
+murderer hinged on a clever formulation of the maxim that highlights the fact that the murderer is lying to you.
+The need for common sense reasoning to evaluate the universalizability test and to formulate a maxim
+is a potential limitation of my system, and I adress this concern in Section \ref{whatisamaxim} and 
+Section Limitations.
+
+On one hand, the need for common sense facts is a 
+limitation of my system. On the other, these examples show that common sense is within reach. Even thin, 
+uncontroversial definitions and assumptions are enough to achieve nuanced ethical judgements. Moreover, 
+these kinds of judgements demonstrate that, with additional work, my system could be used in pratice 
+to guide AI agents. A ``smart doorbell'' like those created by Ring may face a dilemma like that of 
+the murderer at the door. Such a doorbell equipped with a more application-ready version of my 
+system would be able to reason about lying to the murderer and arrive at the right judgement, guided by
+explainable, rigorous philosophical arguments.%
+\end{isamarkuptext}\isamarkuptrue%
 %
@@
 \endinput
-%:%file=~/Desktop/cs91r/paper/application.thy%:%
+%:%file=~/Desktop/cs91r/paper/thesis_4_applications.thy%:%
 %:%24=6%:%
@@
 %:%81=53%:%
-%:%82=54%:%
-%:%83=55%:%
-%:%84=56%:%
-%:%85=57%:%
-%:%86=58%:%
-%:%87=59%:%
-%:%88=60%:%
-%:%89=61%:%
-%:%90=62%:%
-%:%91=63%:%
-%:%92=64%:%
-%:%93=65%:%
-%:%94=66%:%
-%:%95=67%:%
-%:%96=68%:%
-%:%97=69%:%
-%:%98=70%:%
-%:%99=71%:%
-%:%100=72%:%
-%:%101=73%:%
-%:%102=74%:%
-%:%103=75%:%
-%:%104=76%:%
-%:%105=77%:%
-%:%106=78%:%
-%:%107=79%:%
-%:%108=80%:%
-%:%109=81%:%
-%:%110=82%:%
-%:%111=83%:%
-%:%112=84%:%
-%:%113=85%:%
-%:%114=86%:%
-%:%115=87%:%
-%:%116=88%:%
-%:%117=89%:%
-%:%118=90%:%
-%:%119=91%:%
-%:%120=92%:%
-%:%129=94%:%
-%:%141=96%:%
-%:%142=97%:%
-%:%143=98%:%
+%:%90=56%:%
+%:%102=59%:%
+%:%103=60%:%
+%:%104=61%:%
+%:%105=62%:%
+%:%106=63%:%
+%:%107=64%:%
+%:%108=65%:%
+%:%109=66%:%
+%:%110=67%:%
+%:%111=68%:%
+%:%112=69%:%
+%:%113=70%:%
+%:%114=71%:%
+%:%115=72%:%
+%:%116=73%:%
+%:%117=74%:%
+%:%118=75%:%
+%:%119=76%:%
+%:%120=77%:%
+%:%121=78%:%
+%:%122=79%:%
+%:%123=80%:%
+%:%125=83%:%
+%:%126=83%:%
+%:%128=84%:%
+%:%129=85%:%
+%:%130=86%:%
+%:%133=89%:%
+%:%134=90%:%
+%:%135=91%:%
+%:%136=92%:%
+%:%137=93%:%
+%:%138=94%:%
+%:%139=95%:%
+%:%141=98%:%
+%:%142=98%:%
 %:%144=99%:%
 %:%145=100%:%
-%:%146=101%:%
-%:%147=102%:%
-%:%148=103%:%
-%:%149=104%:%
-%:%150=105%:%
-%:%151=106%:%
-%:%152=107%:%
-%:%153=108%:%
-%:%154=109%:%
-%:%155=110%:%
-%:%156=111%:%
-%:%157=112%:%
-%:%159=114%:%
-%:%160=114%:%
-%:%162=115%:%
-%:%163=116%:%
-%:%164=117%:%
-%:%165=118%:%
-%:%166=119%:%
-%:%167=120%:%
-%:%168=121%:%
-%:%169=121%:%
-%:%170=122%:%
-%:%171=123%:%
-%:%172=123%:%
-%:%174=124%:%
-%:%175=124%:%
+%:%146=100%:%
+%:%147=101%:%
+%:%148=101%:%
+%:%149=102%:%
+%:%151=103%:%
+%:%152=103%:%
+%:%153=104%:%
+%:%154=104%:%
+%:%155=105%:%
+%:%157=106%:%
+%:%158=107%:%
+%:%159=108%:%
+%:%160=109%:%
+%:%161=110%:%
+%:%164=114%:%
+%:%165=115%:%
+%:%166=116%:%
+%:%167=117%:%
+%:%168=118%:%
+%:%169=119%:%
+%:%170=120%:%
+%:%171=121%:%
+%:%172=122%:%
+%:%173=123%:%
+%:%175=125%:%
 %:%176=125%:%
-%:%177=125%:%
-%:%178=126%:%
-%:%180=127%:%
-%:%181=127%:%
-%:%182=128%:%
-%:%183=128%:%
-%:%184=129%:%
-%:%186=130%:%
-%:%187=131%:%
-%:%188=132%:%
-%:%189=132%:%
+%:%177=126%:%
+%:%179=127%:%
+%:%182=129%:%
+%:%183=130%:%
+%:%184=131%:%
+%:%185=132%:%
+%:%186=133%:%
+%:%187=134%:%
+%:%188=135%:%
+%:%189=136%:%
 %:%190=137%:%
 %:%191=138%:%
-%:%192=138%:%
-%:%193=139%:%
-%:%195=140%:%
-%:%196=141%:%
-%:%197=142%:%
-%:%200=144%:%
-%:%201=145%:%
+%:%192=139%:%
+%:%193=140%:%
+%:%194=141%:%
+%:%196=143%:%
+%:%197=143%:%
+%:%199=144%:%
+%:%200=145%:%
+%:%201=146%:%
 %:%202=146%:%
 %:%203=147%:%
-%:%204=148%:%
-%:%205=149%:%
-%:%206=150%:%
-%:%210=152%:%
-%:%211=153%:%
-%:%213=155%:%
-%:%214=155%:%
-%:%216=156%:%
-%:%217=156%:%
-%:%218=157%:%
-%:%219=157%:%
+%:%204=147%:%
+%:%206=148%:%
+%:%207=149%:%
+%:%208=149%:%
+%:%209=150%:%
+%:%210=150%:%
+%:%212=151%:%
+%:%215=153%:%
+%:%216=154%:%
+%:%217=155%:%
+%:%218=156%:%
+%:%220=158%:%
 %:%221=158%:%
 %:%222=159%:%
-%:%223=159%:%
-%:%224=160%:%
-%:%225=160%:%
-%:%227=161%:%
-%:%230=163%:%
+%:%223=160%:%
+%:%225=161%:%
+%:%226=161%:%
+%:%227=162%:%
+%:%229=163%:%
+%:%230=164%:%
 %:%231=164%:%
 %:%232=165%:%
-%:%233=166%:%
-%:%235=168%:%
+%:%234=166%:%
+%:%235=167%:%
 %:%236=168%:%
@@
 %:%238=170%:%
+%:%239=171%:%
 %:%240=171%:%
-%:%241=171%:%
-%:%242=172%:%
+%:%241=172%:%
+%:%243=173%:%
 %:%244=173%:%
 %:%245=174%:%
-%:%246=174%:%
-%:%247=175%:%
-%:%249=176%:%
-%:%250=177%:%
-%:%251=178%:%
-%:%252=179%:%
-%:%253=180%:%
-%:%254=181%:%
-%:%255=181%:%
-%:%256=182%:%
-%:%258=183%:%
-%:%259=184%:%
-%:%260=184%:%
-%:%261=185%:%
-%:%268=186%:%
-%:%269=186%:%
-%:%270=187%:%
-%:%271=187%:%
-%:%272=188%:%
-%:%273=188%:%
-%:%275=189%:%
-%:%276=190%:%
-%:%277=191%:%
-%:%278=192%:%
-%:%279=192%:%
-%:%280=193%:%
-%:%281=193%:%
-%:%282=194%:%
-%:%283=194%:%
-%:%284=195%:%
-%:%285=195%:%
-%:%286=196%:%
-%:%287=196%:%
-%:%288=196%:%
-%:%290=197%:%
-%:%291=198%:%
-%:%292=198%:%
-%:%293=199%:%
-%:%303=201%:%
-%:%304=202%:%
-%:%305=203%:%
-%:%306=204%:%
-%:%307=205%:%
-%:%309=207%:%
-%:%310=207%:%
-%:%311=208%:%
-%:%313=210%:%
-%:%314=211%:%
-%:%315=212%:%
-%:%316=213%:%
-%:%317=214%:%
-%:%318=215%:%
-%:%319=216%:%
-%:%320=217%:%
-%:%321=218%:%
-%:%322=219%:%
-%:%324=221%:%
-%:%325=221%:%
-%:%326=222%:%
-%:%327=223%:%
-%:%329=224%:%
-%:%330=224%:%
-%:%331=225%:%
-%:%333=226%:%
-%:%334=227%:%
-%:%335=227%:%
-%:%336=228%:%
-%:%338=229%:%
-%:%339=229%:%
-%:%340=230%:%
-%:%342=231%:%
+%:%252=175%:%
+%:%253=175%:%
+%:%254=176%:%
+%:%255=176%:%
+%:%256=177%:%
+%:%257=177%:%
+%:%259=178%:%
+%:%260=179%:%
+%:%261=180%:%
+%:%262=181%:%
+%:%263=181%:%
+%:%264=182%:%
+%:%265=182%:%
+%:%266=183%:%
+%:%267=183%:%
+%:%268=184%:%
+%:%269=184%:%
+%:%270=185%:%
+%:%271=185%:%
+%:%272=185%:%
+%:%274=186%:%
+%:%275=187%:%
+%:%276=187%:%
+%:%277=188%:%
+%:%287=190%:%
+%:%288=191%:%
+%:%289=192%:%
+%:%290=193%:%
+%:%291=194%:%
+%:%292=195%:%
+%:%293=196%:%
+%:%294=197%:%
+%:%295=198%:%
+%:%296=199%:%
+%:%297=200%:%
+%:%298=201%:%
+%:%299=202%:%
+%:%300=203%:%
+%:%302=205%:%
+%:%303=205%:%
+%:%304=206%:%
+%:%306=207%:%
+%:%307=208%:%
+%:%310=210%:%
+%:%311=211%:%
+%:%312=212%:%
+%:%313=213%:%
+%:%314=214%:%
+%:%315=215%:%
+%:%316=216%:%
+%:%317=217%:%
+%:%318=218%:%
+%:%320=220%:%
+%:%321=220%:%
+%:%322=221%:%
+%:%323=222%:%
+%:%325=223%:%
+%:%326=223%:%
+%:%327=224%:%
+%:%329=225%:%
+%:%330=226%:%
+%:%331=226%:%
+%:%332=227%:%
+%:%334=228%:%
+%:%335=228%:%
+%:%336=229%:%
+%:%338=230%:%
+%:%339=230%:%
+%:%340=231%:%
 %:%343=232%:%
-%:%344=232%:%
-%:%345=233%:%
-%:%348=234%:%
-%:%352=234%:%
-%:%353=234%:%
-%:%362=236%:%
-%:%363=237%:%
-%:%364=238%:%
-%:%365=239%:%
-%:%366=240%:%
-%:%367=241%:%
-%:%368=242%:%
-%:%369=243%:%
-%:%370=244%:%
-%:%371=245%:%
-%:%372=246%:%
-%:%381=249%:%
-%:%393=251%:%
-%:%394=252%:%
-%:%395=253%:%
-%:%396=254%:%
-%:%397=255%:%
-%:%398=256%:%
-%:%399=257%:%
-%:%400=258%:%
-%:%401=259%:%
-%:%402=260%:%
-%:%403=261%:%
-%:%404=262%:%
-%:%405=263%:%
-%:%406=264%:%
-%:%407=265%:%
-%:%408=266%:%
-%:%409=267%:%
-%:%410=268%:%
-%:%411=269%:%
-%:%412=270%:%
-%:%414=272%:%
-%:%415=272%:%
-%:%417=273%:%
-%:%418=273%:%
-%:%419=274%:%
-%:%420=274%:%
-%:%422=275%:%
-%:%423=276%:%
-%:%424=277%:%
-%:%425=277%:%
-%:%426=278%:%
-%:%427=278%:%
-%:%429=279%:%
-%:%430=279%:%
-%:%431=280%:%
-%:%432=280%:%
-%:%434=281%:%
-%:%435=281%:%
-%:%436=282%:%
-%:%437=282%:%
-%:%438=283%:%
-%:%440=284%:%
-%:%441=285%:%
-%:%442=286%:%
-%:%443=286%:%
-%:%444=287%:%
-%:%445=288%:%
-%:%446=288%:%
-%:%448=289%:%
-%:%449=289%:%
-%:%450=290%:%
-%:%451=290%:%
-%:%452=291%:%
-%:%454=292%:%
-%:%455=292%:%
-%:%456=293%:%
-%:%457=293%:%
-%:%459=294%:%
-%:%460=294%:%
-%:%461=295%:%
-%:%462=295%:%
-%:%463=296%:%
-%:%465=297%:%
-%:%466=298%:%
-%:%469=300%:%
-%:%470=301%:%
-%:%471=302%:%
-%:%473=304%:%
-%:%474=304%:%
-%:%475=305%:%
-%:%477=306%:%
-%:%478=306%:%
-%:%479=307%:%
-%:%481=308%:%
-%:%482=309%:%
-%:%483=310%:%
-%:%484=311%:%
-%:%485=311%:%
-%:%486=312%:%
-%:%488=313%:%
-%:%489=313%:%
-%:%490=314%:%
-%:%492=315%:%
-%:%493=316%:%
-%:%494=316%:%
-%:%495=317%:%
-%:%502=318%:%
-%:%503=318%:%
-%:%505=319%:%
-%:%506=320%:%
-%:%507=321%:%
-%:%508=322%:%
-%:%509=322%:%
-%:%510=323%:%
-%:%511=323%:%
-%:%512=324%:%
-%:%513=324%:%
-%:%514=324%:%
-%:%515=325%:%
-%:%516=325%:%
-%:%517=326%:%
-%:%518=326%:%
-%:%519=326%:%
-%:%520=327%:%
-%:%521=327%:%
-%:%522=328%:%
-%:%523=328%:%
-%:%524=328%:%
-%:%525=329%:%
-%:%535=331%:%
-%:%536=332%:%
-%:%537=333%:%
-%:%538=334%:%
-%:%539=335%:%
-%:%540=336%:%
-%:%541=337%:%
-%:%542=338%:%
-%:%543=339%:%
-%:%545=341%:%
-%:%546=341%:%
-%:%547=342%:%
-%:%548=343%:%
-%:%550=344%:%
-%:%551=344%:%
-%:%552=345%:%
-%:%554=346%:%
-%:%555=347%:%
-%:%556=347%:%
-%:%557=348%:%
-%:%559=349%:%
-%:%560=350%:%
-%:%561=351%:%
-%:%562=352%:%
-%:%563=353%:%
-%:%564=353%:%
-%:%565=354%:%
-%:%567=355%:%
-%:%568=356%:%
-%:%569=357%:%
-%:%570=358%:%
-%:%571=359%:%
-%:%572=360%:%
-%:%573=360%:%
-%:%574=361%:%
-%:%576=362%:%
-%:%577=363%:%
-%:%578=363%:%
-%:%579=364%:%
-%:%582=365%:%
-%:%586=365%:%
-%:%587=365%:%
-%:%588=365%:%
-%:%590=366%:%
-%:%591=367%:%
-%:%592=368%:%
-%:%602=370%:%
-%:%603=371%:%
-%:%604=372%:%
-%:%606=374%:%
-%:%607=374%:%
-%:%608=375%:%
-%:%610=376%:%
-%:%611=376%:%
-%:%612=377%:%
-%:%614=378%:%
-%:%615=378%:%
-%:%616=379%:%
-%:%618=380%:%
-%:%619=380%:%
-%:%620=381%:%
-%:%622=382%:%
-%:%623=382%:%
-%:%624=383%:%
-%:%626=384%:%
-%:%627=385%:%
-%:%628=385%:%
-%:%629=386%:%
-%:%636=387%:%
-%:%637=387%:%
-%:%638=388%:%
-%:%639=388%:%
-%:%640=389%:%
-%:%641=389%:%
-%:%642=389%:%
-%:%643=390%:%
-%:%644=390%:%
-%:%645=391%:%
-%:%646=391%:%
-%:%647=391%:%
-%:%648=392%:%
-%:%649=392%:%
-%:%650=393%:%
-%:%651=393%:%
-%:%652=393%:%
-%:%653=394%:%
-%:%663=396%:%
-%:%664=397%:%
-%:%665=398%:%
-%:%666=399%:%
-%:%667=400%:%
-%:%668=401%:%
-%:%669=402%:%
-%:%670=403%:%
-%:%671=404%:%
-%:%672=405%:%
-%:%673=406%:%
-%:%674=407%:%
-%:%675=408%:%
-%:%676=409%:%
-%:%677=410%:%
-%:%678=411%:%
-%:%679=412%:%
-%:%680=413%:%
-%:%681=414%:%
-%:%682=415%:%
-%:%683=416%:%
-%:%684=417%:%
-%:%685=418%:%
-%:%686=419%:%
-%:%687=420%:%
-%:%688=421%:%
-%:%692=424%:%
-%:%693=425%:%
-%:%694=426%:%
-%:%695=427%:%
-%:%696=428%:%
-%:%697=429%:%
-%:%698=430%:%
-%:%699=431%:%
-%:%700=432%:%
-%:%701=433%:%
-%:%702=434%:%
-%:%703=435%:%
-%:%704=436%:%
-%:%705=437%:%
-%:%706=438%:%
-%:%707=439%:%
-%:%708=440%:%
-%:%709=441%:%
-%:%710=442%:%
-%:%711=443%:%
-%:%712=444%:%
-%:%713=445%:%
-%:%714=446%:%
-%:%715=447%:%
-%:%716=448%:%
-%:%717=449%:%
-%:%718=450%:%
-%:%719=451%:%
-%:%720=452%:%
-%:%721=453%:%
-%:%722=454%:%
-%:%723=455%:%
-%:%724=456%:%
-%:%725=457%:%
-%:%726=458%:%
-%:%727=459%:%
-%:%728=460%:%
-%:%729=461%:%
-%:%730=462%:%
-%:%731=463%:%
-%:%732=464%:%
-%:%733=465%:%
-%:%734=466%:%
-%:%735=467%:%
-%:%736=468%:%
-%:%737=469%:%
-%:%738=470%:%
-%:%739=471%:%
-%:%740=472%:%
-%:%741=473%:%
-%:%742=474%:%
-%:%743=475%:%
-%:%744=476%:%
-%:%745=477%:%
-%:%746=478%:%
-%:%755=480%:%
+%:%347=232%:%
+%:%348=232%:%
+%:%350=233%:%
+%:%351=234%:%
+%:%352=235%:%
+%:%353=236%:%
+%:%354=237%:%
+%:%364=240%:%
+%:%365=241%:%
+%:%366=242%:%
+%:%367=243%:%
+%:%368=244%:%
+%:%369=245%:%
+%:%370=246%:%
+%:%371=247%:%
+%:%372=248%:%
+%:%373=249%:%
+%:%374=250%:%
+%:%375=251%:%
+%:%376=252%:%
+%:%377=253%:%
+%:%378=254%:%
+%:%379=255%:%
+%:%380=256%:%
+%:%381=257%:%
+%:%382=258%:%
+%:%383=259%:%
+%:%384=260%:%
+%:%385=261%:%
+%:%386=262%:%
+%:%387=263%:%
+%:%388=264%:%
+%:%389=265%:%
+%:%390=266%:%
+%:%391=267%:%
+%:%392=268%:%
+%:%393=269%:%
+%:%394=270%:%
+%:%395=271%:%
+%:%396=272%:%
+%:%397=273%:%
+%:%398=274%:%
+%:%399=275%:%
+%:%400=276%:%
+%:%401=277%:%
+%:%402=278%:%
+%:%411=281%:%
+%:%423=284%:%
+%:%424=285%:%
+%:%425=286%:%
+%:%426=287%:%
+%:%427=288%:%
+%:%428=289%:%
+%:%429=290%:%
+%:%430=291%:%
+%:%431=292%:%
+%:%432=293%:%
+%:%433=294%:%
+%:%434=295%:%
+%:%435=296%:%
+%:%436=297%:%
+%:%437=298%:%
+%:%438=299%:%
+%:%439=300%:%
+%:%440=301%:%
+%:%442=303%:%
+%:%443=303%:%
+%:%445=304%:%
+%:%446=304%:%
+%:%447=305%:%
+%:%448=305%:%
+%:%450=306%:%
+%:%451=307%:%
+%:%452=308%:%
+%:%453=308%:%
+%:%454=309%:%
+%:%455=309%:%
+%:%457=310%:%
+%:%458=310%:%
+%:%459=311%:%
+%:%460=311%:%
+%:%462=312%:%
+%:%463=312%:%
+%:%464=313%:%
+%:%465=313%:%
+%:%466=314%:%
+%:%468=315%:%
+%:%469=316%:%
+%:%472=318%:%
+%:%473=319%:%
+%:%474=320%:%
+%:%475=321%:%
+%:%477=323%:%
+%:%478=323%:%
+%:%480=324%:%
+%:%481=324%:%
+%:%482=325%:%
+%:%483=325%:%
+%:%484=326%:%
+%:%486=327%:%
+%:%487=327%:%
+%:%488=328%:%
+%:%489=328%:%
+%:%491=329%:%
+%:%492=329%:%
+%:%493=330%:%
+%:%494=330%:%
+%:%495=331%:%
+%:%497=332%:%
+%:%498=333%:%
+%:%514=365%:%
+%:%515=366%:%
+%:%516=367%:%
+%:%517=368%:%
+%:%518=369%:%
+%:%519=370%:%
+%:%520=371%:%
+%:%521=372%:%
+%:%522=373%:%
+%:%524=375%:%
+%:%525=375%:%
+%:%526=376%:%
+%:%527=377%:%
+%:%529=378%:%
+%:%530=378%:%
+%:%531=379%:%
+%:%533=380%:%
+%:%534=380%:%
+%:%535=381%:%
+%:%537=382%:%
+%:%538=383%:%
+%:%539=384%:%
+%:%540=385%:%
+%:%541=386%:%
+%:%542=386%:%
+%:%543=387%:%
+%:%545=388%:%
+%:%546=389%:%
+%:%547=390%:%
+%:%548=391%:%
+%:%549=392%:%
+%:%550=393%:%
+%:%551=394%:%
+%:%552=394%:%
+%:%553=395%:%
+%:%555=396%:%
+%:%556=397%:%
+%:%557=397%:%
+%:%558=398%:%
+%:%561=399%:%
+%:%565=399%:%
+%:%566=399%:%
+%:%567=399%:%
+%:%569=400%:%
+%:%570=401%:%
+%:%571=402%:%
+%:%581=404%:%
+%:%582=405%:%
+%:%583=406%:%
+%:%584=407%:%
+%:%586=409%:%
+%:%587=409%:%
+%:%588=410%:%
+%:%590=411%:%
+%:%591=411%:%
+%:%592=412%:%
+%:%594=413%:%
+%:%595=413%:%
+%:%596=414%:%
+%:%598=415%:%
+%:%599=415%:%
+%:%600=416%:%
+%:%602=417%:%
+%:%603=417%:%
+%:%604=418%:%
+%:%606=419%:%
+%:%607=420%:%
+%:%608=420%:%
+%:%609=421%:%
+%:%616=422%:%
+%:%617=422%:%
+%:%618=423%:%
+%:%619=423%:%
+%:%620=424%:%
+%:%621=424%:%
+%:%622=424%:%
+%:%623=425%:%
+%:%624=425%:%
+%:%625=426%:%
+%:%626=426%:%
+%:%627=426%:%
+%:%628=427%:%
+%:%629=427%:%
+%:%630=428%:%
+%:%631=428%:%
+%:%632=428%:%
+%:%633=429%:%
+%:%643=431%:%
+%:%644=432%:%
+%:%645=433%:%
+%:%646=434%:%
+%:%647=435%:%
+%:%648=436%:%
+%:%649=437%:%
+%:%650=438%:%
+%:%651=439%:%
+%:%652=440%:%
+%:%653=441%:%
+%:%654=442%:%
+%:%655=443%:%
+%:%656=444%:%
+%:%657=445%:%
+%:%658=446%:%
+%:%659=447%:%
+%:%660=448%:%
+%:%661=449%:%
+%:%662=450%:%
+%:%663=451%:%
+%:%664=452%:%
+%:%665=453%:%
+%:%666=454%:%
+%:%667=455%:%
+%:%668=456%:%
+%:%669=457%:%
+%:%670=458%:%
+%:%671=459%:%
+%:%672=460%:%
+%:%673=461%:%
+%:%674=462%:%
+%:%675=463%:%
+%:%676=464%:%
+%:%677=465%:%
+%:%678=466%:%

### 2022-02-21 paper/output/document/thesis_2_methods.tex
started chapter 5

@@
 Many misunderstandings in Kantian ethics are due to badly formulated maxims, so this question is 
-important for an ethical reasoner to answer.\footnote{For example, critics of Kantian ethics worry 
-that the maxim, ``When I am a
-man, I will marry a man because I want to spend my life with him'' fails the universalizability
-test because if all men only married men, sexual reproduction would stop. This argument implies 
-that Kantian ethics is homophobic. Kantians often respond by arguing that the correct formulation of 
-this maxim is, ``When I love a man, I will marry him because I want to spend my life with him,'' which
-is universalizable because if everyone marries who they love, some men will marry women and others will
-marry men.} My system does not need to answer this question because I assume a properly crafted
+important for an ethical reasoner to answer. My system does not need to answer this question because I assume a properly crafted
 maxim as input and apply the categorical imperative to this input. Using my system in a fully automated
-moral agent will require answering this question, a challenging computational and philosophical task.\footnote{I
-discuss this problem in greater detail in Section \ref{whatisamaxim} and Section Limitations.}
+moral agent will require answering this question, a challenging computational and philosophical task. I
+discuss this problem in greater detail in Section \ref{whatisamaxim} and Section \ref{AIethics}.
 
@@
 %:%442=326%:%
-%:%443=327%:%
-%:%444=328%:%
-%:%445=329%:%
-%:%446=330%:%
-%:%447=331%:%
-%:%448=332%:%
-%:%449=333%:%
-%:%458=335%:%
+%:%451=328%:%
+%:%463=331%:%
+%:%464=332%:%
+%:%465=333%:%
+%:%466=334%:%
+%:%467=335%:%
+%:%468=336%:%
+%:%469=337%:%
 %:%470=338%:%
@@
 %:%511=379%:%
-%:%512=380%:%
-%:%513=381%:%
-%:%514=382%:%
-%:%515=383%:%
-%:%516=384%:%
-%:%517=385%:%
-%:%518=386%:%
-%:%527=388%:%
-%:%539=390%:%
-%:%540=391%:%
+%:%520=381%:%
+%:%532=383%:%
+%:%533=384%:%
+%:%537=387%:%
+%:%538=388%:%
+%:%539=389%:%
+%:%540=390%:%
+%:%541=391%:%
+%:%542=392%:%
+%:%543=393%:%
 %:%544=394%:%
@@
 %:%564=414%:%
-%:%565=415%:%
-%:%566=416%:%
-%:%567=417%:%
-%:%568=418%:%
-%:%569=419%:%
-%:%570=420%:%
-%:%571=421%:%
+%:%568=416%:%
+%:%569=417%:%
+%:%570=418%:%
+%:%571=419%:%
+%:%572=420%:%
+%:%573=421%:%
+%:%574=422%:%
 %:%575=423%:%
@@
 %:%594=442%:%
-%:%595=443%:%
-%:%596=444%:%
-%:%597=445%:%
-%:%598=446%:%
-%:%599=447%:%
-%:%600=448%:%
-%:%601=449%:%
-%:%610=452%:%
-%:%622=454%:%
-%:%623=455%:%
-%:%624=456%:%
-%:%625=457%:%
-%:%626=458%:%
-%:%627=459%:%
-%:%636=462%:%
-%:%648=464%:%
-%:%649=465%:%
-%:%650=466%:%
-%:%652=468%:%
-%:%653=468%:%
-%:%654=468%:%
-%:%655=468%:%
-%:%657=469%:%
-%:%658=470%:%
-%:%659=470%:%
-%:%660=471%:%
-%:%661=472%:%
-%:%662=472%:%
-%:%663=472%:%
-%:%664=472%:%
-%:%666=473%:%
-%:%667=474%:%
-%:%668=474%:%
-%:%671=488%:%
-%:%672=489%:%
-%:%673=490%:%
-%:%675=492%:%
-%:%676=492%:%
-%:%677=492%:%
-%:%678=492%:%
-%:%679=493%:%
+%:%603=445%:%
+%:%615=447%:%
+%:%616=448%:%
+%:%617=449%:%
+%:%618=450%:%
+%:%619=451%:%
+%:%620=452%:%
+%:%629=455%:%
+%:%641=457%:%
+%:%642=458%:%
+%:%643=459%:%
+%:%645=461%:%
+%:%646=461%:%
+%:%647=461%:%
+%:%648=461%:%
+%:%650=462%:%
+%:%651=463%:%
+%:%652=463%:%
+%:%653=464%:%
+%:%654=465%:%
+%:%655=465%:%
+%:%656=465%:%
+%:%657=465%:%
+%:%659=466%:%
+%:%660=467%:%
+%:%661=467%:%
+%:%664=481%:%
+%:%665=482%:%
+%:%666=483%:%
+%:%668=485%:%
+%:%669=485%:%
+%:%670=485%:%
+%:%671=485%:%
+%:%672=486%:%
+%:%673=486%:%
+%:%674=486%:%
+%:%677=490%:%
+%:%678=491%:%
+%:%679=492%:%
 %:%680=493%:%
-%:%681=493%:%
-%:%684=497%:%
-%:%685=498%:%
-%:%686=499%:%
-%:%687=500%:%
-%:%689=502%:%
-%:%690=502%:%
-%:%691=526%:%
-%:%692=527%:%
-%:%694=528%:%
-%:%695=529%:%
-%:%696=530%:%
-%:%697=531%:%
-%:%698=531%:%
-%:%706=538%:%
-%:%718=540%:%
-%:%719=541%:%
-%:%720=542%:%
-%:%721=543%:%
-%:%722=544%:%
-%:%723=545%:%
-%:%724=546%:%
-%:%728=562%:%
-%:%730=563%:%
-%:%731=563%:%
-%:%732=564%:%
-%:%734=565%:%
-%:%735=566%:%
-%:%736=566%:%
-%:%737=567%:%
-%:%738=567%:%
-%:%739=568%:%
-%:%741=569%:%
-%:%744=571%:%
-%:%746=572%:%
-%:%747=572%:%
-%:%748=573%:%
-%:%750=574%:%
-%:%751=574%:%
-%:%754=594%:%
-%:%755=595%:%
-%:%757=596%:%
-%:%758=596%:%
-%:%759=597%:%
-%:%760=598%:%
-%:%761=598%:%
-%:%762=599%:%
-%:%763=600%:%
-%:%764=600%:%
-%:%765=601%:%
-%:%767=602%:%
-%:%768=603%:%
-%:%771=605%:%
-%:%773=606%:%
-%:%774=606%:%
-%:%775=607%:%
-%:%777=608%:%
-%:%778=608%:%
-%:%781=616%:%
-%:%782=617%:%
-%:%783=618%:%
-%:%784=619%:%
-%:%786=622%:%
-%:%787=622%:%
-%:%788=622%:%
-%:%790=622%:%
-%:%794=622%:%
-%:%795=622%:%
-%:%797=623%:%
-%:%798=624%:%
-%:%799=624%:%
-%:%801=625%:%
-%:%802=626%:%
-%:%803=627%:%
-%:%813=629%:%
-%:%814=630%:%
-%:%815=631%:%
+%:%682=495%:%
+%:%683=495%:%
+%:%684=519%:%
+%:%685=520%:%
+%:%687=521%:%
+%:%688=522%:%
+%:%689=523%:%
+%:%690=524%:%
+%:%691=524%:%
+%:%699=531%:%
+%:%711=533%:%
+%:%712=534%:%
+%:%713=535%:%
+%:%714=536%:%
+%:%715=537%:%
+%:%716=538%:%
+%:%717=539%:%
+%:%721=555%:%
+%:%723=556%:%
+%:%724=556%:%
+%:%725=557%:%
+%:%727=558%:%
+%:%728=559%:%
+%:%729=559%:%
+%:%730=560%:%
+%:%731=560%:%
+%:%732=561%:%
+%:%734=562%:%
+%:%737=564%:%
+%:%739=565%:%
+%:%740=565%:%
+%:%741=566%:%
+%:%743=567%:%
+%:%744=567%:%
+%:%747=587%:%
+%:%748=588%:%
+%:%750=589%:%
+%:%751=589%:%
+%:%752=590%:%
+%:%753=591%:%
+%:%754=591%:%
+%:%755=592%:%
+%:%756=593%:%
+%:%757=593%:%
+%:%758=594%:%
+%:%760=595%:%
+%:%761=596%:%
+%:%764=598%:%
+%:%766=599%:%
+%:%767=599%:%
+%:%768=600%:%
+%:%770=601%:%
+%:%771=601%:%
+%:%774=609%:%
+%:%775=610%:%
+%:%776=611%:%
+%:%777=612%:%
+%:%779=615%:%
+%:%780=615%:%
+%:%781=615%:%
+%:%783=615%:%
+%:%787=615%:%
+%:%788=615%:%
+%:%790=616%:%
+%:%791=617%:%
+%:%792=617%:%
+%:%794=618%:%
+%:%795=619%:%
+%:%796=620%:%
+%:%806=622%:%
+%:%807=623%:%
+%:%808=624%:%

### 2022-02-21 paper/output/document/thesis_3_implementation.tex
started chapter 5

@@
 itself, is what determines the morally relevant circumstances.  
-
 The difficulty in determining relevant circumstances is a limitation of my system and requires that a 
 human being formulate the maxim or that future work develop heuristics to classify circumstances as morally 
-relevant. For proponents of the ``human-in-the-loop'' model of AI ethics, in which ethical AI requires that 
-humans guide machines, human involvement may be a feature, not a bug \citep{loop}. In this model, 
-a human being must create a representation for the dilemma they wish to test, translating 
-a complex situation into a flat logical structure. This parallels the challenge that programmers 
-face when translating the complexity of reality to a programming langauge or computational representation. 
-The outcome of the universalizability test will depend on how the human formulates the maxim; if the 
-human puts garbage into the test, the test will return garbage out.
-
-Another solution is to develop heuristics to classify circumstances as morally 
-relevant. For example, one such attempt could define a moral closeness relation between an action, a 
-goal, and circumstances. This heuristic could define morally relevant circumstances as those that 
-reach a certain closeness threshhold with the action and the goal. Another possible heuristic could 
-define some set of morally important entities, and classify morally relevant circumstances as those
-that involve morally important entities. Determining morally relevant
-circumstances, either using heuristics or human involvement, is a ripe area for future work.
+relevant. I discuss this challenge and potential solutions in greater detail in Section \ref{commonsense}.
 
@@
 %
-\isamarkupsubsubsection{Formalizing the FUL%
+\isamarkupsubsubsection{Formalizing the FUL\label{formalizingful}%
 }
@@
 %:%230=145%:%
-%:%231=146%:%
 %:%232=147%:%
-%:%233=148%:%
-%:%234=149%:%
-%:%235=150%:%
-%:%236=151%:%
-%:%237=152%:%
-%:%238=153%:%
-%:%239=154%:%
-%:%240=155%:%
-%:%241=156%:%
-%:%242=157%:%
-%:%243=158%:%
-%:%244=159%:%
-%:%245=160%:%
-%:%247=162%:%
-%:%248=162%:%
-%:%249=163%:%
-%:%251=164%:%
-%:%252=165%:%
-%:%253=166%:%
-%:%254=167%:%
-%:%262=169%:%
+%:%233=147%:%
+%:%234=148%:%
+%:%236=149%:%
+%:%237=150%:%
+%:%238=151%:%
+%:%239=152%:%
+%:%247=154%:%
+%:%259=156%:%
+%:%260=157%:%
+%:%261=158%:%
+%:%262=159%:%
+%:%263=160%:%
+%:%264=161%:%
+%:%265=162%:%
+%:%266=163%:%
+%:%267=164%:%
+%:%268=165%:%
+%:%269=166%:%
+%:%270=167%:%
+%:%271=168%:%
+%:%272=169%:%
+%:%273=170%:%
 %:%274=171%:%
@@
 %:%309=206%:%
-%:%310=207%:%
-%:%311=208%:%
+%:%311=209%:%
 %:%312=209%:%
 %:%313=210%:%
-%:%314=211%:%
-%:%315=212%:%
-%:%316=213%:%
-%:%317=214%:%
-%:%318=215%:%
-%:%319=216%:%
-%:%320=217%:%
-%:%321=218%:%
-%:%322=219%:%
-%:%323=220%:%
-%:%324=221%:%
-%:%326=224%:%
-%:%327=224%:%
-%:%328=225%:%
-%:%330=226%:%
-%:%331=227%:%
+%:%315=211%:%
+%:%316=212%:%
+%:%319=214%:%
+%:%320=215%:%
+%:%321=216%:%
+%:%322=217%:%
+%:%323=218%:%
+%:%324=219%:%
+%:%325=220%:%
+%:%326=221%:%
+%:%327=222%:%
+%:%328=223%:%
+%:%329=224%:%
+%:%330=225%:%
+%:%331=226%:%
+%:%332=227%:%
+%:%333=228%:%
 %:%334=229%:%
@@
 %:%340=235%:%
-%:%341=236%:%
-%:%342=237%:%
+%:%342=238%:%
 %:%343=238%:%
 %:%344=239%:%
-%:%345=240%:%
-%:%346=241%:%
-%:%347=242%:%
-%:%348=243%:%
-%:%349=244%:%
-%:%350=245%:%
-%:%351=246%:%
-%:%352=247%:%
-%:%353=248%:%
-%:%354=249%:%
-%:%355=250%:%
+%:%346=240%:%
+%:%347=241%:%
+%:%348=241%:%
+%:%351=247%:%
+%:%352=248%:%
+%:%353=249%:%
+%:%354=250%:%
+%:%355=251%:%
+%:%356=252%:%
 %:%357=253%:%
-%:%358=253%:%
-%:%359=254%:%
-%:%361=255%:%
-%:%362=256%:%
-%:%363=256%:%
-%:%366=262%:%
-%:%367=263%:%
-%:%368=264%:%
-%:%369=265%:%
-%:%370=266%:%
-%:%371=267%:%
-%:%372=268%:%
-%:%373=269%:%
-%:%374=270%:%
-%:%375=271%:%
-%:%376=272%:%
-%:%378=274%:%
-%:%379=274%:%
-%:%380=275%:%
-%:%382=276%:%
+%:%358=254%:%
+%:%359=255%:%
+%:%360=256%:%
+%:%361=257%:%
+%:%363=259%:%
+%:%364=259%:%
+%:%365=260%:%
+%:%367=261%:%
+%:%370=263%:%
+%:%371=264%:%
+%:%372=265%:%
+%:%373=266%:%
+%:%374=267%:%
+%:%375=268%:%
+%:%376=269%:%
+%:%377=270%:%
+%:%378=271%:%
+%:%379=272%:%
+%:%380=273%:%
+%:%381=274%:%
+%:%382=275%:%
+%:%383=276%:%
+%:%384=277%:%
 %:%385=278%:%
@@
 %:%402=295%:%
-%:%403=296%:%
 %:%404=297%:%
-%:%405=298%:%
-%:%406=299%:%
-%:%407=300%:%
-%:%408=301%:%
-%:%409=302%:%
-%:%410=303%:%
-%:%411=304%:%
-%:%412=305%:%
-%:%413=306%:%
-%:%414=307%:%
-%:%415=308%:%
-%:%416=309%:%
-%:%417=310%:%
-%:%419=312%:%
-%:%420=312%:%
-%:%421=313%:%
-%:%423=314%:%
-%:%424=315%:%
-%:%425=315%:%
-%:%426=316%:%
-%:%427=317%:%
-%:%428=317%:%
-%:%429=318%:%
-%:%431=319%:%
-%:%432=320%:%
-%:%435=322%:%
-%:%436=323%:%
-%:%437=324%:%
-%:%438=325%:%
-%:%440=327%:%
-%:%441=327%:%
-%:%442=328%:%
-%:%444=329%:%
-%:%445=330%:%
-%:%446=330%:%
-%:%447=331%:%
-%:%448=332%:%
-%:%449=332%:%
-%:%451=333%:%
-%:%452=334%:%
-%:%453=335%:%
-%:%461=337%:%
-%:%473=339%:%
-%:%474=340%:%
-%:%475=341%:%
-%:%476=342%:%
-%:%477=343%:%
-%:%478=344%:%
-%:%479=345%:%
-%:%480=346%:%
-%:%482=349%:%
-%:%483=349%:%
-%:%485=350%:%
-%:%486=351%:%
-%:%487=352%:%
-%:%488=353%:%
-%:%491=355%:%
-%:%492=356%:%
-%:%494=358%:%
-%:%495=358%:%
-%:%497=358%:%
-%:%501=358%:%
-%:%502=358%:%
-%:%503=359%:%
-%:%504=359%:%
-%:%505=359%:%
+%:%405=297%:%
+%:%406=298%:%
+%:%408=299%:%
+%:%409=300%:%
+%:%410=300%:%
+%:%411=301%:%
+%:%412=302%:%
+%:%413=302%:%
+%:%414=303%:%
+%:%416=304%:%
+%:%417=305%:%
+%:%420=307%:%
+%:%421=308%:%
+%:%422=309%:%
+%:%423=310%:%
+%:%425=312%:%
+%:%426=312%:%
+%:%427=313%:%
+%:%429=314%:%
+%:%430=315%:%
+%:%431=315%:%
+%:%432=316%:%
+%:%433=317%:%
+%:%434=317%:%
+%:%436=318%:%
+%:%437=319%:%
+%:%438=320%:%
+%:%446=322%:%
+%:%458=324%:%
+%:%459=325%:%
+%:%460=326%:%
+%:%461=327%:%
+%:%462=328%:%
+%:%463=329%:%
+%:%464=330%:%
+%:%465=331%:%
+%:%467=334%:%
+%:%468=334%:%
+%:%470=335%:%
+%:%471=336%:%
+%:%472=337%:%
+%:%473=338%:%
+%:%476=340%:%
+%:%477=341%:%
+%:%479=343%:%
+%:%480=343%:%
+%:%482=343%:%
+%:%486=343%:%
+%:%487=343%:%
+%:%488=344%:%
+%:%489=344%:%
+%:%490=344%:%
+%:%499=346%:%
+%:%500=347%:%
+%:%501=348%:%
+%:%502=349%:%
+%:%503=350%:%
+%:%504=351%:%
+%:%505=352%:%
+%:%506=353%:%
+%:%507=354%:%
+%:%508=355%:%
+%:%509=356%:%
+%:%510=357%:%
+%:%511=358%:%
+%:%512=359%:%
+%:%513=360%:%
 %:%514=361%:%
@@
 %:%523=370%:%
-%:%524=371%:%
 %:%525=372%:%
-%:%526=373%:%
-%:%527=374%:%
-%:%528=375%:%
-%:%529=376%:%
-%:%530=377%:%
-%:%531=378%:%
-%:%532=379%:%
-%:%533=380%:%
-%:%534=381%:%
-%:%535=382%:%
-%:%536=383%:%
-%:%537=384%:%
-%:%538=385%:%
-%:%540=387%:%
-%:%541=387%:%
-%:%542=388%:%
-%:%544=389%:%
-%:%545=390%:%
-%:%548=392%:%
-%:%550=394%:%
-%:%551=394%:%
-%:%552=395%:%
-%:%554=396%:%
-%:%555=397%:%
-%:%556=397%:%
-%:%557=398%:%
-%:%558=399%:%
-%:%559=399%:%
-%:%560=400%:%
-%:%561=400%:%
-%:%563=400%:%
-%:%567=400%:%
-%:%568=400%:%
-%:%570=401%:%
-%:%571=402%:%
-%:%572=403%:%
-%:%573=404%:%
-%:%574=405%:%
-%:%575=406%:%
-%:%576=407%:%
+%:%526=372%:%
+%:%527=373%:%
+%:%529=374%:%
+%:%530=375%:%
+%:%533=377%:%
+%:%535=379%:%
+%:%536=379%:%
+%:%537=380%:%
+%:%539=381%:%
+%:%540=382%:%
+%:%541=382%:%
+%:%542=383%:%
+%:%543=384%:%
+%:%544=384%:%
+%:%545=385%:%
+%:%546=385%:%
+%:%548=385%:%
+%:%552=385%:%
+%:%553=385%:%
+%:%555=386%:%
+%:%556=387%:%
+%:%557=388%:%
+%:%558=389%:%
+%:%559=390%:%
+%:%560=391%:%
+%:%561=392%:%
+%:%571=394%:%
+%:%572=395%:%
+%:%573=396%:%
+%:%574=397%:%
+%:%575=398%:%
+%:%576=399%:%
+%:%577=400%:%
+%:%578=401%:%
+%:%579=402%:%
+%:%580=403%:%
+%:%581=404%:%
+%:%582=405%:%
+%:%583=406%:%
+%:%584=407%:%
+%:%585=408%:%
 %:%586=409%:%
@@
 %:%591=414%:%
-%:%592=415%:%
 %:%593=416%:%
-%:%594=417%:%
-%:%595=418%:%
-%:%596=419%:%
-%:%597=420%:%
-%:%598=421%:%
-%:%599=422%:%
-%:%600=423%:%
-%:%601=424%:%
-%:%602=425%:%
-%:%603=426%:%
-%:%604=427%:%
-%:%605=428%:%
-%:%606=429%:%
-%:%608=431%:%
-%:%609=431%:%
-%:%611=433%:%
-%:%612=434%:%
-%:%613=435%:%
-%:%614=436%:%
-%:%615=437%:%
-%:%624=439%:%
+%:%594=416%:%
+%:%596=418%:%
+%:%597=419%:%
+%:%598=420%:%
+%:%599=421%:%
+%:%600=422%:%
+%:%609=424%:%
+%:%621=426%:%
+%:%622=427%:%
+%:%623=428%:%
+%:%624=429%:%
+%:%625=430%:%
+%:%626=431%:%
+%:%627=432%:%
+%:%628=433%:%
+%:%629=434%:%
+%:%630=435%:%
+%:%631=436%:%
+%:%632=437%:%
+%:%633=438%:%
+%:%634=439%:%
+%:%635=440%:%
 %:%636=441%:%
@@
 %:%645=450%:%
-%:%646=451%:%
-%:%647=452%:%
-%:%648=453%:%
-%:%649=454%:%
-%:%650=455%:%
-%:%651=456%:%
-%:%652=457%:%
-%:%653=458%:%
-%:%654=459%:%
-%:%655=460%:%
+%:%648=454%:%
+%:%649=455%:%
+%:%650=456%:%
+%:%651=457%:%
+%:%652=458%:%
+%:%653=459%:%
 %:%656=461%:%
@@
 %:%660=465%:%
-%:%663=469%:%
-%:%664=470%:%
-%:%665=471%:%
-%:%666=472%:%
-%:%667=473%:%
-%:%668=474%:%
-%:%671=476%:%
-%:%672=477%:%
-%:%673=478%:%
-%:%674=479%:%
-%:%675=480%:%
-%:%676=481%:%
-%:%677=482%:%
-%:%678=483%:%
-%:%679=484%:%
-%:%680=485%:%
+%:%661=466%:%
+%:%662=467%:%
+%:%663=468%:%
+%:%664=469%:%
+%:%665=470%:%
+%:%669=472%:%
+%:%670=473%:%
+%:%671=474%:%
+%:%672=475%:%
+%:%673=476%:%
+%:%674=477%:%
+%:%675=478%:%
+%:%676=479%:%
+%:%677=480%:%
+%:%678=481%:%
+%:%679=482%:%
+%:%680=483%:%
+%:%681=484%:%
+%:%682=485%:%
 %:%684=487%:%
-%:%685=488%:%
-%:%686=489%:%
-%:%687=490%:%
-%:%688=491%:%
-%:%689=492%:%
-%:%690=493%:%
-%:%691=494%:%
-%:%692=495%:%
-%:%693=496%:%
-%:%694=497%:%
-%:%695=498%:%
-%:%696=499%:%
-%:%697=500%:%
-%:%699=502%:%
-%:%700=502%:%
-%:%701=503%:%
-%:%704=504%:%
-%:%708=504%:%
-%:%709=504%:%
-%:%711=505%:%
-%:%712=506%:%
-%:%713=507%:%
-%:%714=507%:%
-%:%716=508%:%
-%:%717=509%:%
-%:%718=510%:%
-%:%719=511%:%
-%:%725=511%:%
-%:%728=512%:%
-%:%729=513%:%
-%:%730=513%:%
-%:%731=514%:%
-%:%734=515%:%
-%:%738=515%:%
-%:%739=515%:%
-%:%741=516%:%
-%:%742=517%:%
+%:%685=487%:%
+%:%686=488%:%
+%:%689=489%:%
+%:%693=489%:%
+%:%694=489%:%
+%:%696=490%:%
+%:%697=491%:%
+%:%698=492%:%
+%:%699=492%:%
+%:%701=493%:%
+%:%702=494%:%
+%:%703=495%:%
+%:%704=496%:%
+%:%710=496%:%
+%:%713=497%:%
+%:%714=498%:%
+%:%715=498%:%
+%:%716=499%:%
+%:%719=500%:%
+%:%723=500%:%
+%:%724=500%:%
+%:%726=501%:%
+%:%727=502%:%
+%:%737=504%:%
+%:%738=505%:%
+%:%739=506%:%
+%:%740=507%:%
+%:%741=508%:%
+%:%742=509%:%
+%:%743=510%:%
+%:%744=511%:%
+%:%745=512%:%
+%:%746=513%:%
+%:%747=514%:%
+%:%748=515%:%
+%:%749=516%:%
+%:%750=517%:%
+%:%751=518%:%
 %:%752=519%:%
@@
 %:%757=524%:%
-%:%758=525%:%
 %:%759=526%:%
-%:%760=527%:%
-%:%761=528%:%
-%:%762=529%:%
-%:%763=530%:%
-%:%764=531%:%
-%:%765=532%:%
-%:%766=533%:%
-%:%767=534%:%
-%:%768=535%:%
-%:%769=536%:%
-%:%770=537%:%
-%:%771=538%:%
-%:%772=539%:%
-%:%774=541%:%
-%:%775=541%:%
-%:%776=542%:%
-%:%779=543%:%
-%:%783=543%:%
-%:%784=543%:%
-%:%785=543%:%
-%:%787=544%:%
-%:%793=544%:%
-%:%796=545%:%
-%:%797=546%:%
-%:%798=546%:%
-%:%799=547%:%
-%:%800=548%:%
-%:%803=549%:%
-%:%807=549%:%
-%:%808=549%:%
-%:%809=549%:%
-%:%811=550%:%
-%:%812=551%:%
-%:%813=552%:%
-%:%823=554%:%
-%:%824=555%:%
-%:%825=556%:%
-%:%826=557%:%
-%:%827=558%:%
-%:%828=559%:%
-%:%829=560%:%
-%:%830=561%:%
-%:%832=564%:%
-%:%833=564%:%
-%:%836=565%:%
-%:%840=565%:%
-%:%841=565%:%
-%:%843=566%:%
-%:%844=567%:%
-%:%845=568%:%
-%:%855=570%:%
-%:%856=571%:%
-%:%857=572%:%
-%:%858=573%:%
-%:%859=574%:%
-%:%860=575%:%
-%:%861=576%:%
-%:%863=578%:%
-%:%864=578%:%
-%:%865=579%:%
-%:%866=580%:%
-%:%869=581%:%
-%:%873=581%:%
-%:%874=581%:%
-%:%875=581%:%
-%:%877=582%:%
-%:%878=583%:%
-%:%879=584%:%
-%:%889=586%:%
-%:%890=587%:%
-%:%892=589%:%
-%:%893=589%:%
-%:%894=590%:%
-%:%895=591%:%
-%:%898=592%:%
-%:%902=592%:%
-%:%903=592%:%
-%:%904=592%:%
-%:%906=593%:%
-%:%916=595%:%
-%:%917=596%:%
+%:%760=526%:%
+%:%761=527%:%
+%:%764=528%:%
+%:%768=528%:%
+%:%769=528%:%
+%:%770=528%:%
+%:%772=529%:%
+%:%778=529%:%
+%:%781=530%:%
+%:%782=531%:%
+%:%783=531%:%
+%:%784=532%:%
+%:%785=533%:%
+%:%788=534%:%
+%:%792=534%:%
+%:%793=534%:%
+%:%794=534%:%
+%:%796=535%:%
+%:%797=536%:%
+%:%798=537%:%
+%:%808=539%:%
+%:%809=540%:%
+%:%810=541%:%
+%:%811=542%:%
+%:%812=543%:%
+%:%813=544%:%
+%:%814=545%:%
+%:%815=546%:%
+%:%817=549%:%
+%:%818=549%:%
+%:%821=550%:%
+%:%825=550%:%
+%:%826=550%:%
+%:%828=551%:%
+%:%829=552%:%
+%:%830=553%:%
+%:%840=555%:%
+%:%841=556%:%
+%:%842=557%:%
+%:%843=558%:%
+%:%844=559%:%
+%:%845=560%:%
+%:%846=561%:%
+%:%848=563%:%
+%:%849=563%:%
+%:%850=564%:%
+%:%851=565%:%
+%:%854=566%:%
+%:%858=566%:%
+%:%859=566%:%
+%:%860=566%:%
+%:%862=567%:%
+%:%863=568%:%
+%:%864=569%:%
+%:%874=571%:%
+%:%875=572%:%
+%:%877=574%:%
+%:%878=574%:%
+%:%879=575%:%
+%:%880=576%:%
+%:%883=577%:%
+%:%887=577%:%
+%:%888=577%:%
+%:%889=577%:%
+%:%891=578%:%
+%:%901=580%:%
+%:%902=581%:%
+%:%903=582%:%
+%:%904=583%:%
+%:%905=584%:%
+%:%906=585%:%
+%:%907=586%:%
+%:%908=587%:%
+%:%909=588%:%
+%:%910=589%:%
+%:%911=590%:%
+%:%912=591%:%
+%:%913=592%:%
+%:%914=593%:%
 %:%918=597%:%
@@
 %:%925=604%:%
-%:%926=605%:%
-%:%927=606%:%
-%:%928=607%:%
-%:%929=608%:%
-%:%933=612%:%
-%:%934=613%:%
-%:%935=614%:%
-%:%936=615%:%
-%:%937=616%:%
-%:%938=617%:%
-%:%939=618%:%
-%:%940=619%:%
+%:%929=607%:%
+%:%930=608%:%
+%:%931=609%:%
+%:%932=610%:%
+%:%933=611%:%
+%:%934=612%:%
+%:%935=613%:%
+%:%936=614%:%
+%:%937=615%:%
+%:%938=616%:%
+%:%939=617%:%
+%:%940=618%:%
+%:%941=619%:%
+%:%942=620%:%
+%:%943=621%:%
 %:%944=622%:%
@@
 %:%947=625%:%
-%:%948=626%:%
-%:%949=627%:%
-%:%950=628%:%
-%:%951=629%:%
-%:%952=630%:%
-%:%953=631%:%
-%:%954=632%:%
-%:%955=633%:%
-%:%956=634%:%
-%:%957=635%:%
-%:%958=636%:%
-%:%959=637%:%
-%:%960=638%:%
-%:%961=639%:%
-%:%962=640%:%

### 2022-02-21 paper/output/document/thesis_5_discussion.tex
started chapter 5

--- 2022-02-04 paper/output/document/upshot.tex
@@
 \begin{isabellebody}%
-\setisabellecontext{upshot}%
+\setisabellecontext{thesis{\isacharunderscore}{\isadigit{5}}{\isacharunderscore}discussion}%
 %
@@
 %
-\isamarkupsection{Philosophical Contributions%
+\isamarkupsection{Discussion\label{discussion}%
 }
@@
 %
+\isamarkupsubsection{Automated Moral Agents in Practice \label{aiethics}%
+}
+\isamarkuptrue%
+%
 \endisatagdocument
@@
 \begin{isamarkuptext}%
-TESTESTESTI argue that computational ethics should be useful for and interesting to philosophers for two 
-reasons. First, it could serve as the basis for AI agents with the capacity for philosophically sophisticated 
-ethical reasoning. For example, my project contributes an implementation of the Formula of Universal Law
-that an AI agent could use to reason about the world using the categorical imperative. Second, computational 
-ethics helps philosophers think about ethics in the same way that theorem provers help 
-mathematicians think about math. I am not arguing that the computer can replace human reasoning or prove things
-that humans theoretically couldn't do. Instead, I argue that the computer bolsters human reasoning by forcing precision due to 
-the rigid syntax of a computer program. Below, I explore 
-these contributions in greater detail.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\isatagdocument
-%
-\isamarkupsubsection{AI Agents%
-}
-\isamarkuptrue%
-%
-\endisatagdocument
-{\isafolddocument}%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\begin{isamarkuptext}%
-As artifical intelligence becomes more powerful, science-fiction predictions about ``evil AI"
-and calls from regulators are intensifying the need for ``ethical AI". My project contributes a ``top down" 
-approach automating a particular ethical theory. My work on automating the categorical imperative 
-could serve as one component of a partially or fully artificial ethical reasoner. Specifically, my 
-project could be repurposed into a ``categorical imperative library" that takes as input the logical representation of a maxim 
-and determines its moral status (if it is obligatory, prohibited, or permissible).
+In Chapter \ref{applications}, I demonstrated that my system is capable of performing sophisticated,
+nuanced ethical reasoning. In this section and Section \label{computationalethics}, I outline how my
+system could be used by AI agents and by human philosophers. My work on automating the categorical imperative 
+could serve as one component of a partially or fully artificial ethical reasoner, or an ``ethical AI.''
+Specifically, my system could be a categorical imperative library that takes as input the logical representation 
+of a maxim and returns its moral status (if it is obligatory, prohibited, or permissible).
 
 As it stands, my project can evaluate the moral status of maxims represented in my logic and potentially 
-serves as one component of an ``ethics engine" that an AI agent could use to make ethical decisions.
+serves as one component of an ``ethics engine'' that an AI agent could use to make ethical decisions.
 For example, my system could be combined with an input parser to translate moral dilemmas as represented 
@@
 \includegraphics[scale=0.4]{AI_engine.png}
-\caption{An example of an ethics engine for an artificial agent. I contribute the automated 
-categorical imperative component.} \label{fig:AIengine}
+\caption{An example of an ethics engine for an artificial agent, which begins with a moral dilemma, 
+passes it through an input parser, applies the automated Kantian ethics test, and then processes the 
+output using an output parser. I contribute the automated Kantian ethics component.} \label{fig:AIengine}
 \end{figure}
@@
 \begin{isamarkuptext}%
-In this workflow, an AI agent is faced with a moral dilemma in some internal representation. This 
-internal representation would need to be translated by an input parser into an appropriate logical representation, i.e. 
-a circumstance, act, goal tuple. This input parser is the most technically and ethically challenging 
-component of the system. It is this input parser that determines which circumstances are ``morally relevant"
-for a maxim, a judgement that requires commonsense reasoning and knowledge about moral relevance. Translating 
- everyday situations into appropriate maxims is the bulk of the work that a Kantian human being does when making decisions. 
-Common misconceptions about Kantian ethics\footnote{For example, some wonder why the FUL doesn't prohibit
-gay sex, as the maxim ``marry someone of the same sex" appears to result in human extinction when 
-universalized. The solution to this dilemma is that the maxim a gay person acts on is usually something 
-of the form, ``marry the person you love because you love them," which is perfectly reasonable to 
-universalize.} often result from incorrectly formulated maxims, and the entire field of 
-applied Kantian ethics is devoted to generating the right kinds of maxims to test. For more discussion 
-of challenges involved with defining morally relevant circumstances, see Section UNWRITTEN.
-
-This representational
-question will be one of the biggest hurdles to actually using my categorical imperative library 
-in an AI ethics engine. Currently, it may be reasonable for a human being to perform the role of the input
+In this workflow, an AI agent is faced with a moral dilemma in some internal representation. The input
+parser translates this internal representation into an appropriate logical representation, i.e. 
+a circumstance, act, goal tuple. The output parser translates the output of the categorical imperative
+library (the moral status of the maxim as obligatory, prohibited, or permissible) to a prescription for
+action that the AI agent can act on. In order for my system to be used in an AI agent using the workflow
+above, future work would need to develop such input and output parsers.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+The input parser must translate a complex real-world situation into a flat, logical representation. 
+This requires that the input parser determine which circumstances are ``morally relevant''
+for a maxim, a controversial judgement that requires commonsense reasoning.
+There is robust debate in the literature on which circumstances should be considered when formulating a maxim. 
+Some critics of Kant raise the ``tailoring objection,'' which is the worry that arbitrarily specific 
+circumstances render any maxim universalizable. For example, the maxim ``When my name is Lavanya Singh 
+and I am wearing a purple shirt and it is November 26th, I will lie in order to get some easy cash'' 
+passes the universalizability test. Even if this maxim is willed universally, the circumstances are so 
+specific that lying will not become the general mechanism for getting easy cash, so the lender will 
+believe my lie and the maxim will remain effective. By tailoring the circumstances, any maxim can 
+evade universalization.
+
+The Kantian response to this criticism is to require that the circumstances included in the formulation
+of the maxim be morally relevant. In the example above, my purple shirt and the date clearly have no bearing on 
+the moral status of lying. On the other hand, consider the maxim, ``When I am unemployed, I will murder
+someone in order to take their job.'' The circumstances of being unemployed clearly have some bearing on the moral
+relevance of the murder in question; they speak to the motivation for the murder. While this view 
+tracks how we actually perform moral reasoning, it raises the question of how we can determine
+which circumstances are morally relevant. O'Niell answers this question by noting that the Formula of Universal Law is 
+a ``test of moral worth rather than of outward rightness'' \citep[98]{constofreason}. The FUL is a way 
+for an agent to decide how they should behave, not for a third-party to judge their behavior. Ethics is 
+a personal process for Kant, so the FUL is designed to help agents internally make decisions, not to 
+judge others' decisions. Because agents use the FUL to evaluate their own behavior, the test is at its 
+best when they make a good faith effort to isolate the \emph{principle} of their action, rather than some
+``surface intent'' \citep[87]{constofreason}. The FUL is supposed to determine if an agent's principle of action
+is universally consistent, so it is most effective when an agent accurately formulates the principle
+they act on. Circumstances are morally relevant if they accurately reflect the way that the agent is 
+thinking about their own action. In the example above, the circumstance of wearing a purple shirt doesn't reflect
+the principle of the liar's action. Its inclusion is clearly a disingenous attempt to evade the universalizability
+test, but because the FUL is a test of personal integrity, it cannot withstand this kind of mental
+gymnastics.
+
+While this account of the formulation of a maxim describes how a well-intentioned human agent can determine 
+morally relevant circumstances, the challenge remains open for automated ethics. In order for an automated
+ethical agent to use the categorical imperative to its fullest extent, the input maxim fed into
+my system or any automation of the FUL must be a good-faith attempt to capture the agent's principle
+of action. However an action is turned into a maxim for my system to process, whether manually as I did
+in Chapter \ref{applications} or using an automatic input parser, this transformation must be a good-faith 
+attempt to capture the principle of action.
+
+Translating everyday situations into appropriate maxims is the bulk of the work that a Kantian human 
+being does when making decisions. Common misconceptions about Kantian ethics\footnote{For example, critics 
+of Kantian ethics worry that the maxim, ``When I am a
+man, I will marry a man because I want to spend my life with him'' fails the universalizability
+test because if all men only married men, sexual reproduction would stop. This argument implies 
+that Kantian ethics is homophobic. Kantians often respond by arguing that the correct formulation of 
+this maxim is, ``When I love a man, I will marry him because I want to spend my life with him,'' which
+is universalizable because if everyone marries who they love, some men will marry women and others will
+marry men.} often result from incorrectly formulated maxims, 
+and the entire field of applied Kantian ethics is devoted to generating the right kinds of maxims to test.
+
+This representational question is one of the biggest challenges to using my categorical imperative library
+in an AI ethics engine. One solution is for a human being to perform the role of the input
 parser. Once an AI agent stumbles onto an ethical dilemma, a human being could take over, formulate 
 the right question, and feed it into the categorical imperative library to see what action the categorical 
-imperative would prescribe. This may actually be a feature, not a bug. 
-Proponents of the ``human-in-the-loop" model argue that fully automated decision-making is doomed 
-to ethical failure, and that the inclusion of a human being injects common-sense sanity into otherwise 
-dangerous decisions\footnote{For more discussion of different models of AI ethics, see Section UNWRITTEN}.
+imperative would prescribe. For proponents of the ``human-in-the-loop'' model of AI ethics, in which 
+ethical AI requires that humans guide machines \cite{loop}, this kind of human involvement may be a feature.
+The outcome of the universalizability test will depend on how the human formulates the maxim; if the 
+human puts garbage into the test, the test will return garbage out.
 
@@
 such developments are likely and will require ethics engines, or risk no consideration of ethics at all. Even if 
-fully automated AI is scary, such AI with automated ethics is better than such AI without. 
+AI without human supervision is scary, such AI with automated ethics is better than such AI without. 
 In such a world, the input parser in my ethics engine would have to be automated. This would require 
 that the parser translate the AI agent's internal representation to the appropriate logical representation. 
-The input parser would need enough common sense reasoning to determine what circumstances are morally 
-relevant to a maxim. This is a question that, like all of ethics, philosophers debate robustly
-\footnote{\citet{powers} identifies this as a challenge for automating Kantian ethics and briefly sketches 
-solutions from \citet{constofreason}, \citet{silber}, and \citet{rawlsconstructivism}. }. 
 It is likely that, just as different implementations of automated ethics choose 
 a particular ethical theory and implement it, different implementations of such an input parser would 
-need to adopt different interpretations of commonsense reasoning and morally relevant circumstances.
-Automating this level of commonsense reasoning would represent signifiant technical progress in 
-computational ethics.
+adopt different interpretations of commonsense reasoning and morally relevant circumstances.
+
+These interpretations of commonsense reasonining could inspire heuristics to classify circumstances as morally 
+relevant. For example, one such attempt could define a moral closeness relation between an action, a 
+goal, and circumstances. This heuristic could define morally relevant circumstances as those that 
+reach a certain closeness threshhold with the action and the goal. Another possible heuristic could 
+define some set of morally important entities, and classify morally relevant circumstances as those
+that involve morally important entities. I discuss a potential machine-learning based approach which formulates
+maxims based on a training set of appropriately formulated maxims in Section \ref{amapossible}.
+Determining morally relevant circumstances, either using heuristics or human involvement, is a ripe 
+area for future work.
 
@@
 project can evaluate its moral status using my implementation of 
-the FUL. Concretely, my project would return a value indicating if the maxim is obligatory, permissible, 
-or prohibited. The maxim would be prohibited if it fails the universalizability test, permissible if it passes, and obligatory 
-if its negation fails the universalizability test. All three of these properties amount to testing if a 
-certain theorem holds or not in my logic, a calculation that I demonstrate in my tests.
-
-This output could then be converted into some actionable, useful response with another output parser, 
-and then passed back to the AI agent. For example, if the AI agent is equipped to evaluate natural language prescriptions, the 
-status of the maxim could be parsed into a natural language sentence. This output will be passed back 
-to the AI agent, which will use it to make a decision. The input parser, categorical imperative library, 
-and output parser together constitute an ``ethics engine" that AI agents could use as a black box 
-implementation of an ethical theory.
-
-The ethics engine depicted above is a high-level example of one way to use my project to guide an artifical agent. The 
-upshot is that an automated version of the categorical imperative could become part of the ethical engine 
-for an AI agent, with much work to parse the input and the output. Effectively, the kind 
+the FUL. Concretely, my project returns a value indicating if the maxim is obligatory, permissible, 
+or prohibited. The maxim is prohibited if it fails the universalizability test, permissible if it passes, and obligatory 
+if its negation fails the universalizability test. All three of these properties require testing if a 
+certain theorem holds or not in my logic, a calculation that I demonstrate in Section \ref{testing}. 
+Testing these properties requires that my system have a database of common sense or factual background. 
+Different applications of my system may require different factual background (e.g. a self-driving car 
+would need to know traffic regulations), so this common sense database may need to be application 
+specific. As demonstrated in the examples in Chapter \ref{applications}, my system can produce sophisticated 
+judgements with relatively little situational context. While the need for factual background is a challenge
+for automated ethics, Chapter \ref{applications} demonstrates that it is less daunting than it seems.
+
+My system's output could be converted into some actionable, useful response with another output parser, 
+and then passed back to the AI agent. For example, if the AI agent is equipped to evaluate natural 
+language prescriptions, the status of the maxim could be parsed into a natural language sentence. The 
+input parser, categorical imperative library, and output parser together constitute an ``ethics engine'' 
+that AI developers could use as a black box implementation of an ethical theory.
+
+The ethics engine depicted above is a high-level example of one way to use my project to guide an artifical agent.
+An automated version of the categorical imperative could become part of an ethics engine 
+for an AI agent, with additional work to parse the input and the output. Effectively, the kind 
 of automated ethics I implement could be a library that AI developers use to give AI agents the capacity for 
 sophisticated ethical reasoning faithful to philosophical literature. This represents an improvement 
-over existing ethics engines, which rarely attempt to capture the complexity 
-of any ethical theory that philosophers plausibly defend. Moreover, a logic programming approach 
-is potentially more explainable than a black-box deep learning approach, as theorem provers like 
-Isabelle can explicitly list the axioms used to generate moral prescriptions. For more on how my project 
-is situated among other work in automated ethics, see Section Related Work.%
+over existing AI ethics, which rarely attempts to capture the complexity 
+of any ethical theory that philosophers plausibly defend.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupsubsection{Computational Philosophy%
+\isamarkupsubsection{Computational Ethics \label{computationalethics}%
 }
@@
 philosophy. Just as theorem provers make mathematics more efficient and push mathematicians to think 
-precisely about the phenomena they are modelling, computational ethics can help philosophers think more precisely about 
-philosophy. Below I share a personal example of the kind of philosophical insight that computational ethics 
+precisely about the phenomena they model, computational ethics can help philosophers think more precisely about 
+philosophy. Below I share an example of the kind of philosophical insight that computational ethics 
 can prompt and analyze the value that this tool offers to philosophers.%
@@
 %
-\isamarkupsubsubsection{Example of a  Philosophical Insight%
+\isamarkupsubsubsection{Example of a Philosophical Insight: Well-Formed Maxims%
 }
@@
 \begin{isamarkuptext}%
-As I implemented a formalization of the categorical imperative using an interactive theorem prover, 
-I discovered logical insights. These logical insights led to a philosophical 
-insight that was novel to me and is potentially novel to the field.  While this 
-insight could have been reached without the help of the computer, my system's logical results provoked
-an interesting philosophical conversation. Effectively, the system spat out a logical principle, and 
-I examined the philosophical plausibility of this principle for the ethical 
-theory I am formalizing. In this section, I will first present the logical insight, then the 
-philosophical insights, and then its implications for a debate about self-doubt. I will then
-generalize my personal experience and argue that computational ethics is a new, useful methodology 
-for philosophers.
-
-I arrived at the logical insight while testing my formalization of the FUL. I realized
-that my formalization was inconsistent unless I specified that the FUL only held for ``well-formed maxims,"
-such that neither the act nor goal were already achieved in the given circumstances. Precisely, 
+As presented in Section \ref{formalizingful}, in the process of developing my formalization of
+the FUL, I discovered the certain kinds of maxims are badly formed, or inappropriate inputs to the 
+universalizability test. The FUL is consistent only if it holds for ``well-formed maxims,''
+such that neither the act nor goal are already achieved in the given circumstances. Precisely, 
 a circumstance, act, goal tuple (c, a, g) is well-formed if $(\neg (c \longrightarrow a) ) \wedge 
-(\neg(c \longrightarrow g))$. This provoked the philosophical insight that maxims of this form, in which 
-the act or the goal has already been accomplished in the given circumstances are ``vacuous" because 
-any prescriptions they generate have already been acted on or violated. The notion of a vacuous maxim
-has implications for debates about ethical self-doubt and self-confidence or self-respect.
-
-Below, I document the process used to arrive at the logical insight that the FUL is inconsistent if it
-holds for maxims in which $(c \longrightarrow a) \wedge (c \longrightarrow g)$. For those uninterested
-in the details of this exploration, it suffices to understand that I used Isabelle to show that if the 
-FUL holds for badly formed maxims, then it is inconsistent. After I realized that my formalization was 
-inconsistent, I made many failed attempts to diagnose and fix the problem before reaizing that the problem 
-lay in badly formed maxims.
-
-\emph{Logical Insight}
-
-First, I used Sledgehammer to show that my formalization of the FUL\footnote{The full logical representation is \isa{FUL{\isadigit{0}}\ {\isasymequiv}\ {\isasymforall}c\ a\ g\ s{\isachardot}\ not{\isacharunderscore}universalizable\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ {\isasymlongrightarrow}\ {\isasymTurnstile}prohibited\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s}.}
-resulted in a contradiction. Sledgehammer was able to tell me which axioms it used to complete 
-this proof, showing me that my formalization contradicted the axiom O\_diamond, which states that an 
-obligated term cannot contradict its context\footnote{The full form of the axiom is 
-$ O \{ A \vert B \} \longrightarrow \diamond (B \wedge A)$}. 
-O\_diamond formalizes the principle ``ought implies can" and requires that if A is obligated in context 
-C, that A is possible in context C. I hypothesized that there was some tension between 
-the antecedent of the FUL, which states that all agents act on the maxim, and the consequent, 
-which states that the maxim is prohibited. If the maxim has already been acted on, then not acting on it
-is impossible. Thus, the generated prohibition is impossible to obey, so the ought implies can principle
-and axiom O\_diamond are violated.
-
-I then experimented with modifications of the FUL, which I eventually abandoned. I tried universalizing the maxim 
-at a world other than the current world and defining non-contradictory maxims, in which the maxim's 
-circumstances do not contradict the maxim's act. I noticed that, no matter what modifications I made, 
-Nitpick was timing out when looking for a model and Sledgehammer wasn't able to find a proof of
-inconsistency. Isabelle's proof tools weren't able to tell me if my modifications were 
-consistent or not. I suspected that something about my implementation was too slow, perhaps due to 
-my liberal use of quantifiers\footnote{Benzmueller warned me that as 
-I added quantifiers to the theory, Isabelle's automated proof tools may start to time out.}.
-
-Isabelle's model checker Nitpick performs an optimized version of a brute force model search, in which it generates many models
-and checks if they satisfy the given maxims. I suspected that Nitpick 
-was checking large models that exhausted its 
-time limit, especially due to the logical complexity of my theory. 
-To reduce the logical complexity, I decided to specify the exact number of maxims 
-in the system by passing as an argument to Nitpick the cardinality of my desired model. Nitpick no longer
-timed out, but it could not find a satisfying model with cardinality 1, and thus could not demonstrate
-that my modified FUL was consisteny.
- This puzzled me, as I felt that I could construct a pencil-and-paper 
-model with a single world and term in which my modified formalizations were consistent.
-
-Instead of specifying the cardinality of the model, I decided to tell Nitpick exactly how many 
-maxims there were in my system by defining them as constants. I defined a particular 
-(circumstance, act, goal) tuple as a constant. Instead of
-stating that the FUL held for all maxims, I stated that the FUL held for the specific maxim formed by this tuple.
-While before I added the axiom $\forall (c, a, g) \text{\emph{FUL holds for maxim}} (c, a, g)$, I now added constants $(c, a, g)$ 
-and added the axiom $\text{\emph{FUL holds for maxim}} (c, a, g)$. By specifying the circumstance, act, and goal 
-as constants, I removed the external universal quantifier, thus removing a layer of logical complexity.
-
-To my surprise, Nitpick not only returned quickly, it was able to show that the FUL was consistent!
-
-This result was counterintuitive—after all, what is the difference between a model of cardinality 
-1 and a model with one constant object? Why is quantifying over a tiny number of maxims different
- than analyzing a single maxim? Professor Amin pointed out that, as constants, the 
-circumstances, act, and goal were all distinct. When they were quantified over, 
-they could be identical.
-To formalize this idea, I defined a maxim as \isa{well{\isacharunderscore}formed\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ w{\isachardot}\ {\isasymnot}\ c\isactrlbold {\isasymrightarrow}g\ w\ {\isasymand}\ {\isasymnot}\ c\isactrlbold {\isasymrightarrow}a\ s\ w}.
-In propositional
-logic, a circumstance, act, goal tuple (c, a, g) is well-formed if $(\neg (c \longrightarrow a) ) \wedge 
-(\neg(c \longrightarrow g))$. I tested my hypothesis by modifying my axiom to instead read $\forall$\emph{maxim
-(maxim is well-formed} $\longrightarrow$ \emph{FUL holds for maxim}). This version of the FUL was indeed consistent!
-
-To summarize, I realized that my initial attempt at formalizing the FUL was inconsistent because 
-it required that the FUL hold for badly formed maxims, in which the circumstances entail the act or 
-goal. The logical insight was that if FUL holds for maxims in which $(c \longrightarrow a) \vee 
-(c \longrightarrow g)$, then the logic will be inconsistent.
-
-\emph{Philosophical Insight}
-
-Once I realized this logical property, I tried to understand its philosophical plausibility. I 
-wanted to philosophically test the hypothesis that maxims in which  $(c \longrightarrow a) \vee 
-(c \longrightarrow g)$ are not valid inputs to the FUL. I concluded that because vacuous maxims neither 
-change an agent's behavior nor generate meaningful obligations, they are not the right kinds of questions 
-for practical reasoners to be asking. They cannot be action-guiding and are thus not the kind of problem that 
+(\neg(c \longrightarrow g))$.
+
+\noindent \textbf{Philosophical Implications of Badly-Formed Maxims}
+
+Isabelle showed that the FUL can only hold for well-formed maxims logically, and I returned to Kantian
+literature to better understand the philosophical implications of this idea. Because badly-formed maxims
+neither change an agent's behavior nor generate meaningful obligations, they are not the right kinds of 
+actions for practical reasoners to wonder about. They cannot be action-guiding and are thus not the kind of problem that 
 ethics should be concerned with. Moreover, under the Kantian account of the will, the very act of asking 
-if a vacuous maxim is prohibited generates a contradiction by undermining the will's authority over itself.
-
-I define a vacuous maxim as one in which the circumstances entail either the act or the goal and argue 
-that such maxims can't meaningfully guide action. Consider the example vacuous maxim, ``when eating 
-breakfast, I will eat breakfast in order to eat breakfast." This 
-maxim isn't clearly obligatory or prohibited, but there is something empty about it. Acting on this
- maxim could never result in any actual action. If an agent adopts this maxim, 
-they decide that, in the circumstances ``eating breakfast" they will perform the act ``eating breakfast"
-for the purpose ``eating breakfast." In these circumstances, the act has 
-already been performed! Treating this maxim a law for yourself or a principle to live by doesn't change 
-how you live your life. If you adopt this maxim, when you are eating breakfast, you eat breakfast, 
-but this statement is already tautologically true.
-
-Not only does a vacuous maxim fail to prescribe action, any obligations or prohibitions it 
-generates have already been fulfilled or violated. If a vacuous 
-maxim generates a prohibition, then this prohibition would be impossible to obey. 
+if a badly-formed maxim is prohibited generates a contradiction by undermining the will's authority over itself.
+
+Consider the example badly-formed maxim, ``When eating breakfast, I will eat breakfast in order to 
+eat breakfast.'' This maxim isn't clearly obligatory or prohibited, but there is something empty about 
+it. Acting on this maxim could never result in any action. If an agent adopts this maxim, 
+they decide that, in the circumstances ``eating breakfast'' they will perform the act ``eating breakfast''
+for the purpose ``eating breakfast.'' In these circumstances, the act has 
+already been performed! Adopting this maxim as a law to live by does not change how you live. If you adopt 
+this maxim, when you are eating breakfast, you eat breakfast, but this statement is already tautologically true.
+
+Not only does a badly-formed maxim fail to prescribe action, any obligations or prohibitions it 
+generates have already been fulfilled or violated. If a badly-formed maxim generates a prohibition, 
+then this prohibition is impossible to obey, which is why my original version of the FUL was inconsistent. 
 It is impossible to not eat breakfast while eating breakfast, because the circumstances assume that the 
-act has happened. On the other hand, if a vacuous maxim generates an obligation, then the obligation 
+act has happened. On the other hand, if a badly-formed maxim generates an obligation, then the obligation 
 will have already been fulfilled. If you are required to eat breakfast while eating breakfast, then you've 
 already fulfilled your obligation because the circumstances assume that the act has happened. Thus, 
-a vacuous maxim does not actually guide action because it doesn't generate new obligations or 
-prohibitions that could ever be acted on.
-
-Because vacuous maxims can't prescribe or alter action, they are not practically action-guiding and 
-thus are not the right kinds of maxims for practical reasoners to evaluate. Moreover, insofar as ethics 
-is supposed to guide action, vacuous maxims cannot be part of this project. Vacuous maxims
-will have no bearing on what someone should do. Practical reason
-is the kind of reason that helps us decide what we should do. 
-A practical reasoner asks moral questions not as a mental puzzle or out of curiosity, but 
-in order to decide how to act. Practical reason is action-guiding, but a vacuous
- maxim can never be action-guiding because it prescribes no new
+a badly-formed maxim does not actually guide action because it doesn't generate new obligations or 
+prohibitions.
+
+Because badly-formed maxims can't prescribe or alter action, they are not practically action-guiding and 
+thus are not the right kinds of maxims for practical reasoners to evaluate. Insofar as ethics 
+is supposed to guide action, badly-formed maxims cannot be part of this project because they
+have no bearing on what someone should do. Practical reason is the kind of reason that helps us decide 
+what we should do. A practical reasoner asks moral questions not as a mental puzzle or out of curiosity, but 
+in order to decide how to act. A badly-formed maxim can never be action-guiding because it prescribes no new
 actions or obligations. It is not the kind of maxim that a practical reasoner should consider, because it
-will have no bearing on what the agent should do. 
-There is no explicit prohibition against a vacuous maxim like the breakfast example above, but it 
-is the wrong kind of question for a practical reasoner to ask. An ordinary person trying 
-to navigate the world would never need to ask that kind of question. If ethics is meant 
-to guide action, then badly formed maxims are not questions for ethics, because they could never guide 
-action.
-
-Above I argued that vacuous maxims are not the kind of principle that a practical reasoner should 
-evaluate, and are thus not the right kind of question for ethics. Kantians can make an even stronger claim
-about vacuous maxims—because maxims are laws that you give to yourself, asking if you should will 
-a maxim as you will it undermines your will's law-giving ability. The circumstances of a vacuous maxim 
-already assume that the agent has willed the maxim. Under the Kantian acount of willing, this act 
-of willing a maxim is equivalent to giving the maxim to yourself as a law. When you will a maxim, you
-adopt a law to make the maxim your end and commit yourself to be its cause. You cannot simultaneously 
-commit yourself to a maxim and ask if you should be committing to it. To 
-will the maxim is to adopt it as law—so the question, ``should I be 
-willing this?" is paradoxical. Either you haven't actually made the maxim your law (and thus haven't yet 
-committed yourself to it), or you aren't actually asking the question (because the decision has already been made).
-Because a maxim is a law that you give to yourself, you cannot question it absent a sufficient reason 
-(such as a change in the circumstances). To question a law arbitrarily is to not regard it as a law at all.
-This kind of questioning amounts to questioning the will's authority over itself, but this is 
-impossible. The will definitionally has authority over itself, for that is what it is to be a 
-will.
-
-A skeptic may argue that we do often ask ``should I be doing this?" as we do something. What do we mean when 
-we ask this question? In what sense are we trying to evalute the moral status of a vacuous maxim?
+will have no bearing on what the agent should do. There is no explicit prohibition against a badly-formed maxim 
+like the breakfast example above, but it is the wrong kind of question for a practical reasoner to ask.
+
+Kantians can make an even stronger claim about badly-formed maxims—because maxims are laws that you 
+give to yourself, asking if you should will a maxim as you will it undermines your will's law-giving 
+ability. The circumstances of a badly-formed maxim assume that the agent has willed the maxim. Under 
+the Kantian acount of willing, willing a maxim is equivalent to giving the maxim to yourself as a law. 
+When you will a maxim, you commit yourself to the maxim's end. You cannot simultaneously 
+commit yourself to a maxim and ask if you should be committing to it. To will the maxim is to adopt it as 
+law—so the question, ``should I be willing this?'' is paradoxical. Either you haven't actually made 
+the maxim your law (and thus haven't yet committed yourself to it), or you aren't actually asking 
+the question (because the decision has already been made). Because a maxim is a law that you give to 
+yourself, you cannot question it absent a sufficient reason (such as a change in the circumstances). 
+To question a law arbitrarily is to not regard it as a law at all. This kind of questioning amounts to 
+questioning the will's authority over itself, but this is impossible. The will definitionally has authority 
+over itself, for that is what it is to be a will.
+
+A skeptic may argue that we do often ask ``should I be doing this?'' as we do something. 
 Can this kind of question ever be valid? To understand this worry, I consider the maxim, 
-``When dancing, I should just dance for the sake of dancing."\footnote{Maybe cite Korgsaard since the
-dancing thing is her example.} While this maxim appears to be vacuous (the 
-circumstance `dancing' implies the act and goal of dancing), it's a question that practical reasoners 
-do ask. I argue that there are this maxim is actually misunderstood and, when interpreted correctly,
-it no longer poses as a counterexample to my complaints about vacuous maxims.
-
-Under one reading of this maxim, "I should just dance" is actually referring to a different act than the circumstance ``when dancing". 
-The circumstance ``when dancing" refers 
-to rythmically moving your body to music, but ``I should just dance" refers to dancing without anxiety, 
+``When dancing, I should just dance for the sake of dancing.'' While this maxim appears to be badly-formed (the 
+circumstance ``dancing'' implies the act and goal of dancing), it is a question that practical reasoners 
+do ask. I argue that the correct interpretation of this maxim is no longer a badly-formed maxim.
+
+Under one reading of this maxim, ``I should just dance'' is referring to a different act than the 
+circumstance ``when dancing''. The circumstance ``when dancing'' refers 
+to rythmically moving your body to music, but ``I should just dance'' refers to dancing without anxiety, 
 completely focused on the joy of dancing itself. More precisely, this maxim should read ``When 
-dancing, I should abandon my anxiety and focus on dancing for the sake of dancing." This maxim when so 
+dancing, I should abandon my anxiety and focus on dancing for the sake of dancing.'' This maxim when so 
 modified is not vacuous at all—abandoning anxiety and focusing on dancing is an entirely different act 
@@
 pose a problem for my argument. It is entirely plausible to tell yourself ``When I am dancing, I should focus 
-on dancing for the sake of dancing itself." The circumstances do not entail the act or the goal because 
+on dancing for the sake of dancing itself.'' The circumstances do not entail the act or the goal because 
 they refer to different meanings of the word dancing. Any valid reading of this maxim will have the structure above, 
@@
 
-Another related worry has to with maxims that we do in fact think are prohibited. Consider the maxim modified to 
-read ``When dancing and seeing a child drowning, I should dance for the sake of dancing." Clearly this 
+Another related worry has to with maxims that we think are prohibited. Consider the maxim modified to 
+read ``When dancing and seeing a child drowning, I should dance for the sake of dancing.'' Clearly this 
 maxim is fit for moral evaluation, and we expect a moral theory to prohibit this maxim. The circumstances 
-``When dancing and seeing a child drowning" appear to entail the act of dancing, and the maxim thus 
-appears vacuous. Once again, this maxim is formulated incorrectly. In this case, the question 
-that the agent is actually asking themselves is ``should I continue dancing?" That is the 
-maxim that they will adopt or reject. They mean to ask if they should stop dancing and go help the child. 
+``When dancing and seeing a child drowning'' appear to entail the act of dancing, and the maxim thus 
+appears badly-formed. Once again, this maxim is formulated incorrectly. In this case, the question 
+that the agent is actually asking themselves is ``should I continue dancing?'' That is the 
+maxim that they will adopt or reject. They want to know if they should stop dancing and go help the child. 
 Dancing at the current moment and dancing at the next moment are different acts, and the circumstances 
-imply the former but not the latter. A vacuous maxim would have circumstances and act both 
-``dancing at moment t," but this maxim has circumstances ``dancing at moment t" and act ``dancing 
-at moment t+1." This is a kind of temporal error that has bearings for other debates in ethics as well. 
-Specifically, the confusion between circumstances and acts that occur at different times (as in this example) and circumstances 
-and acts that occur at the exact same time has bearing on self-doubt, as I will argue next.
-
-\emph{Implications for Self Doubt and Self Respect}
+imply the former but not the latter. A badly-formed maxim would have circumstances and act both 
+``dancing at moment t,'' but this maxim has circumstances ``dancing at moment t'' and act ``dancing 
+at moment t+1.''
+
+\noindent \textbf{Implications for Self Doubt and Self Respect}
+
+The idea that we cannot will badly formed maxims
 
@@
 agents appear to ask themselves about vacuous maxims are mistaken about the maxim in question, because 
-such a question could never yield a useful answer for a practical reasoner.%
+such a question could never yield a useful answer for a practical reasoner.
+
+I arrived at this conclusion using Isabelle's proof-finding capabilities. Recall that Sledgehammer showed
+that my original version of the FUL\footnote{The full logical representation is \isa{FUL{\isadigit{0}}\ {\isasymequiv}\ {\isasymforall}c\ a\ g\ s{\isachardot}\ not{\isacharunderscore}universalizable\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ {\isasymlongrightarrow}\ {\isasymTurnstile}prohibited\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s}.} contradicted
+the axiom O\_diamond, which states that an obligated term cannot contradict its context\footnote{The 
+full form of the axiom is $ O \{ A \vert B \} \longrightarrow \diamond (B \wedge A)$}. I hypothesized 
+that there was some tension between the antecedent of the FUL, which states that all agents act on 
+the maxim, and the consequent, which states that the maxim is prohibited. If the maxim has already 
+been acted on, then not acting on it is impossible. Thus, the generated prohibition is impossible to 
+obey, so the ought implies can principle and axiom O\_diamond are violated.
+
+To test this hypothesis, I defined a specific maxim as a constant with no other defined features, 
+and examined the consequences of the FUL holding for this specific maxim. Instead of quantifying over
+all circumstance, act, goal tuples, I states that the FUL holds for the specific maxim defined by
+by new constant. With this modification, Nitpick showed that the FUL is consistent! The reason that
+the FUL could hold for a constant maxim but not for all maxims is that, as constants, the 
+circumstances, act, and goal were all distinct. When they were quantified over, 
+they could be identical. This motivated the definition of a well-formed maxim.
+
+To formalize this idea, I defined a maxim as \isa{well{\isacharunderscore}formed\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ w{\isachardot}\ {\isasymnot}\ c\isactrlbold {\isasymrightarrow}g\ w\ {\isasymand}\ {\isasymnot}\ c\isactrlbold {\isasymrightarrow}a\ s\ w}.
+In propositional
+logic, a circumstance, act, goal tuple (c, a, g) is well-formed if $(\neg (c \longrightarrow a) ) \wedge 
+(\neg(c \longrightarrow g))$. I tested my hypothesis by modifying my axiom to instead read $\forall$\emph{maxim
+(maxim is well-formed} $\longrightarrow$ \emph{FUL holds for maxim}). This version of the FUL was indeed consistent!
+
+To summarize, I realized that my initial attempt at formalizing the FUL was inconsistent because 
+it required that the FUL hold for badly formed maxims, in which the circumstances entail the act or 
+goal. The logical insight was that if FUL holds for maxims in which $(c \longrightarrow a) \vee 
+(c \longrightarrow g)$, then the logic will be inconsistent.
+
+SAY INCERDIBLE DIFFICULT WITHUT COMPUTER because computer looks for edge cases and makes assumptions precise.
+it's an insight precisely because philosophers would never think of this edge case bc it's stupid.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsection{Theoretical Objections to Automating Kantian Ethics%
+}
+\isamarkuptrue%
+%
+\isamarkupsubsection{Related Work%
+}
+\isamarkuptrue%
+%
+\isamarkupsubsection{Conclusion%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
 \isadelimtheory
@@
 \endinput
-%:%file=~/Desktop/cs91r/paper/upshot.thy%:%
+%:%file=~/Desktop/cs91r/paper/thesis_5_discussion.thy%:%
 %:%24=6%:%
-%:%36=8%:%
-%:%37=9%:%
-%:%38=10%:%
-%:%39=11%:%
-%:%40=12%:%
-%:%41=13%:%
-%:%42=14%:%
-%:%43=15%:%
-%:%44=16%:%
-%:%53=18%:%
-%:%65=20%:%
-%:%66=21%:%
-%:%67=22%:%
-%:%68=23%:%
-%:%69=24%:%
-%:%70=25%:%
-%:%71=26%:%
-%:%72=27%:%
-%:%73=28%:%
-%:%74=29%:%
-%:%75=30%:%
-%:%76=31%:%
-%:%77=32%:%
-%:%80=36%:%
-%:%81=37%:%
-%:%82=38%:%
-%:%83=39%:%
-%:%84=40%:%
-%:%85=41%:%
-%:%88=43%:%
-%:%89=44%:%
-%:%90=45%:%
-%:%91=46%:%
-%:%92=47%:%
-%:%93=48%:%
-%:%94=49%:%
-%:%95=50%:%
-%:%96=51%:%
-%:%97=52%:%
-%:%98=53%:%
-%:%99=54%:%
-%:%100=55%:%
-%:%101=56%:%
-%:%102=57%:%
-%:%103=58%:%
-%:%104=59%:%
-%:%105=60%:%
-%:%106=61%:%
-%:%107=62%:%
-%:%108=63%:%
-%:%109=64%:%
-%:%110=65%:%
-%:%111=66%:%
-%:%112=67%:%
-%:%113=68%:%
-%:%114=69%:%
-%:%115=70%:%
-%:%116=71%:%
-%:%117=72%:%
-%:%118=73%:%
-%:%119=74%:%
-%:%120=75%:%
-%:%121=76%:%
-%:%122=77%:%
-%:%123=78%:%
-%:%124=79%:%
-%:%125=80%:%
-%:%126=81%:%
-%:%127=82%:%
-%:%128=83%:%
-%:%129=84%:%
-%:%130=85%:%
-%:%131=86%:%
-%:%132=87%:%
-%:%133=88%:%
-%:%134=89%:%
-%:%135=90%:%
-%:%136=91%:%
-%:%137=92%:%
-%:%138=93%:%
-%:%139=94%:%
-%:%140=95%:%
-%:%141=96%:%
-%:%142=97%:%
-%:%143=98%:%
-%:%144=99%:%
-%:%145=100%:%
-%:%146=101%:%
-%:%147=102%:%
-%:%148=103%:%
-%:%149=104%:%
-%:%150=105%:%
-%:%151=106%:%
-%:%160=108%:%
-%:%172=110%:%
-%:%173=111%:%
-%:%174=112%:%
-%:%175=113%:%
-%:%176=114%:%
-%:%177=115%:%
-%:%186=117%:%
-%:%198=119%:%
-%:%199=120%:%
-%:%200=121%:%
-%:%201=122%:%
-%:%202=123%:%
-%:%203=124%:%
-%:%204=125%:%
-%:%205=126%:%
-%:%206=127%:%
-%:%207=128%:%
-%:%208=129%:%
-%:%209=130%:%
-%:%210=131%:%
-%:%211=132%:%
-%:%212=133%:%
-%:%213=134%:%
-%:%214=135%:%
-%:%215=136%:%
-%:%216=137%:%
-%:%217=138%:%
-%:%218=139%:%
-%:%219=140%:%
-%:%220=141%:%
-%:%221=142%:%
-%:%222=143%:%
-%:%223=144%:%
-%:%224=145%:%
-%:%225=146%:%
-%:%226=147%:%
-%:%227=148%:%
-%:%228=149%:%
-%:%229=150%:%
-%:%230=151%:%
-%:%231=152%:%
-%:%232=153%:%
-%:%233=154%:%
-%:%234=155%:%
-%:%235=156%:%
-%:%236=157%:%
-%:%237=158%:%
-%:%238=159%:%
-%:%239=160%:%
-%:%240=161%:%
-%:%241=162%:%
-%:%242=163%:%
-%:%243=164%:%
-%:%244=165%:%
-%:%245=166%:%
-%:%246=167%:%
-%:%247=168%:%
-%:%248=169%:%
-%:%249=170%:%
-%:%250=171%:%
-%:%251=172%:%
-%:%252=173%:%
-%:%253=174%:%
-%:%254=175%:%
-%:%255=176%:%
-%:%256=177%:%
-%:%257=178%:%
-%:%258=179%:%
-%:%259=180%:%
-%:%260=181%:%
-%:%261=182%:%
-%:%262=183%:%
-%:%263=184%:%
-%:%264=185%:%
-%:%265=186%:%
-%:%266=187%:%
-%:%267=188%:%
-%:%268=189%:%
-%:%269=190%:%
-%:%270=191%:%
-%:%271=192%:%
-%:%272=193%:%
-%:%273=194%:%
-%:%274=195%:%
-%:%275=196%:%
-%:%276=197%:%
-%:%277=198%:%
-%:%278=199%:%
-%:%279=200%:%
-%:%280=201%:%
-%:%281=202%:%
-%:%282=203%:%
-%:%283=204%:%
-%:%284=205%:%
-%:%285=206%:%
-%:%286=207%:%
-%:%287=208%:%
-%:%288=209%:%
-%:%289=210%:%
-%:%290=211%:%
-%:%291=212%:%
-%:%292=213%:%
-%:%293=214%:%
-%:%294=215%:%
-%:%295=216%:%
-%:%296=217%:%
-%:%297=218%:%
-%:%298=219%:%
-%:%299=220%:%
-%:%300=221%:%
-%:%301=222%:%
-%:%302=223%:%
-%:%303=224%:%
-%:%304=225%:%
-%:%305=226%:%
-%:%306=227%:%
-%:%307=228%:%
-%:%308=229%:%
-%:%309=230%:%
-%:%310=231%:%
-%:%311=232%:%
-%:%312=233%:%
-%:%313=234%:%
-%:%314=235%:%
-%:%315=236%:%
-%:%316=237%:%
-%:%317=238%:%
-%:%318=239%:%
-%:%319=240%:%
-%:%320=241%:%
-%:%321=242%:%
-%:%322=243%:%
-%:%323=244%:%
-%:%324=245%:%
-%:%325=246%:%
-%:%326=247%:%
-%:%327=248%:%
-%:%328=249%:%
-%:%329=250%:%
-%:%330=251%:%
-%:%331=252%:%
-%:%332=253%:%
-%:%333=254%:%
-%:%334=255%:%
-%:%335=256%:%
-%:%336=257%:%
-%:%337=258%:%
-%:%338=259%:%
-%:%339=260%:%
-%:%340=261%:%
-%:%341=262%:%
-%:%342=263%:%
-%:%343=264%:%
-%:%344=265%:%
-%:%345=266%:%
-%:%346=267%:%
-%:%347=268%:%
-%:%348=269%:%
-%:%349=270%:%
-%:%350=271%:%
-%:%351=272%:%
-%:%352=273%:%
-%:%353=274%:%
-%:%354=275%:%
-%:%355=276%:%
-%:%356=277%:%
-%:%357=278%:%
-%:%358=279%:%
-%:%359=280%:%
-%:%360=281%:%
-%:%361=282%:%
-%:%362=283%:%
-%:%363=284%:%
-%:%364=285%:%
-%:%365=286%:%
-%:%366=287%:%
-%:%367=288%:%
-%:%368=289%:%
-%:%369=290%:%
-%:%370=291%:%
-%:%371=292%:%
-%:%372=293%:%
-%:%373=294%:%
-%:%374=295%:%
-%:%375=296%:%
-%:%376=297%:%
-%:%377=298%:%
-%:%378=299%:%
-%:%379=300%:%
-%:%380=301%:%
-%:%381=302%:%
-%:%382=303%:%
-%:%383=304%:%
-%:%384=305%:%
-%:%385=306%:%
-%:%386=307%:%
-%:%387=308%:%
-%:%388=309%:%
-%:%389=310%:%
-%:%390=311%:%
-%:%391=312%:%
-%:%392=313%:%
-%:%393=314%:%
-%:%394=315%:%
-%:%395=316%:%
-%:%396=317%:%
-%:%397=318%:%
-%:%398=319%:%
-%:%399=320%:%
-%:%400=321%:%
-%:%401=322%:%
-%:%402=323%:%
-%:%403=324%:%
-%:%404=325%:%
-%:%405=326%:%
-%:%406=327%:%
-%:%407=328%:%
-%:%408=329%:%
-%:%409=330%:%
-%:%410=331%:%
-%:%411=332%:%
-%:%412=333%:%
-%:%413=334%:%
-%:%414=335%:%
-%:%415=336%:%
-%:%416=337%:%
-%:%417=338%:%
-%:%418=339%:%
-%:%419=340%:%
-%:%420=341%:%
-%:%421=342%:%
-%:%422=343%:%
-%:%423=344%:%
-%:%424=345%:%
-%:%425=346%:%
-%:%426=347%:%
-%:%427=348%:%
-%:%428=349%:%
-%:%429=350%:%
-%:%430=351%:%
-%:%431=352%:%
-%:%432=353%:%
-%:%433=354%:%
-%:%434=355%:%
-%:%435=356%:%
-%:%436=357%:%
-%:%437=358%:%
-%:%438=359%:%
-%:%439=360%:%
-%:%440=361%:%
-%:%441=362%:%
-%:%442=363%:%
-%:%443=364%:%
-%:%444=365%:%
-%:%445=366%:%
-%:%446=367%:%
-%:%447=368%:%
-%:%448=369%:%
-%:%449=370%:%
-%:%450=371%:%
-%:%451=372%:%
-%:%452=373%:%
-%:%453=374%:%
-%:%454=375%:%
-%:%455=376%:%
-%:%456=377%:%
-%:%457=378%:%
-%:%458=379%:%
-%:%459=380%:%
-%:%460=381%:%
-%:%461=382%:%
-%:%462=383%:%
-%:%463=384%:%
-%:%464=385%:%
-%:%465=386%:%
-%:%466=387%:%
-%:%467=388%:%
-%:%476=392%:%
-%:%488=394%:%
-%:%489=395%:%
-%:%490=396%:%
-%:%491=397%:%
-%:%492=398%:%
-%:%493=399%:%
-%:%494=400%:%
-%:%495=401%:%
-%:%496=402%:%
-%:%497=403%:%
-%:%498=404%:%
-%:%499=405%:%
-%:%500=406%:%
-%:%501=407%:%
-%:%502=408%:%
-%:%503=409%:%
-%:%504=410%:%
-%:%505=411%:%
-%:%506=412%:%
-%:%507=413%:%
-%:%508=414%:%
-%:%509=415%:%
-%:%510=416%:%
-%:%511=417%:%
-%:%512=418%:%
-%:%513=419%:%
-%:%514=420%:%
-%:%515=421%:%
-%:%516=422%:%
-%:%517=423%:%
-%:%518=424%:%
-%:%519=425%:%
-%:%520=426%:%
-%:%521=427%:%
-%:%522=428%:%
-%:%523=429%:%
-%:%524=430%:%
-%:%525=431%:%
-%:%526=432%:%
-%:%527=433%:%
-%:%528=434%:%
-%:%529=435%:%
-%:%530=436%:%
-%:%531=437%:%
-%:%532=438%:%
-%:%533=439%:%
-%:%534=440%:%
-%:%543=443%:%
-%:%555=446%:%
-%:%556=447%:%
-%:%557=448%:%
-%:%558=449%:%
-%:%559=450%:%
-%:%560=451%:%
-%:%561=452%:%
-%:%562=453%:%
-%:%563=454%:%
-%:%564=455%:%
-%:%565=456%:%
-%:%566=457%:%
-%:%567=458%:%
-%:%568=459%:%
-%:%569=460%:%
-%:%570=461%:%
-%:%571=462%:%
-%:%572=463%:%
-%:%573=464%:%
-%:%574=465%:%
-%:%575=466%:%
+%:%28=8%:%
+%:%40=10%:%
+%:%41=11%:%
+%:%42=12%:%
+%:%43=13%:%
+%:%44=14%:%
+%:%45=15%:%
+%:%46=16%:%
+%:%47=17%:%
+%:%48=18%:%
+%:%49=19%:%
+%:%50=20%:%
+%:%51=21%:%
+%:%52=22%:%
+%:%55=26%:%
+%:%56=27%:%
+%:%57=28%:%
+%:%58=29%:%
+%:%59=30%:%
+%:%60=31%:%
+%:%61=32%:%
+%:%64=34%:%
+%:%65=35%:%
+%:%66=36%:%
+%:%67=37%:%
+%:%68=38%:%
+%:%69=39%:%
+%:%73=41%:%
+%:%74=42%:%
+%:%75=43%:%
+%:%76=44%:%
+%:%77=45%:%
+%:%78=46%:%
+%:%79=47%:%
+%:%80=48%:%
+%:%81=49%:%
+%:%82=50%:%
+%:%83=51%:%
+%:%84=52%:%
+%:%85=53%:%
+%:%86=54%:%
+%:%87=55%:%
+%:%88=56%:%
+%:%89=57%:%
+%:%90=58%:%
+%:%91=59%:%
+%:%92=60%:%
+%:%93=61%:%
+%:%94=62%:%
+%:%95=63%:%
+%:%96=64%:%
+%:%97=65%:%
+%:%98=66%:%
+%:%99=67%:%
+%:%100=68%:%
+%:%101=69%:%
+%:%102=70%:%
+%:%103=71%:%
+%:%104=72%:%
+%:%105=73%:%
+%:%106=74%:%
+%:%107=75%:%
+%:%108=76%:%
+%:%109=77%:%
+%:%110=78%:%
+%:%111=79%:%
+%:%112=80%:%
+%:%113=81%:%
+%:%114=82%:%
+%:%115=83%:%
+%:%116=84%:%
+%:%117=85%:%
+%:%118=86%:%
+%:%119=87%:%
+%:%120=88%:%
+%:%121=89%:%
+%:%122=90%:%
+%:%123=91%:%
+%:%124=92%:%
+%:%125=93%:%
+%:%126=94%:%
+%:%127=95%:%
+%:%128=96%:%
+%:%129=97%:%
+%:%130=98%:%
+%:%131=99%:%
+%:%132=100%:%
+%:%133=101%:%
+%:%134=102%:%
+%:%135=103%:%
+%:%136=104%:%
+%:%137=105%:%
+%:%138=106%:%
+%:%139=107%:%
+%:%140=108%:%
+%:%141=109%:%
+%:%142=110%:%
+%:%143=111%:%
+%:%144=112%:%
+%:%145=113%:%
+%:%146=114%:%
+%:%147=115%:%
+%:%148=116%:%
+%:%149=117%:%
+%:%150=118%:%
+%:%151=119%:%
+%:%152=120%:%
+%:%153=121%:%
+%:%154=122%:%
+%:%155=123%:%
+%:%156=124%:%
+%:%157=125%:%
+%:%158=126%:%
+%:%159=127%:%
+%:%160=128%:%
+%:%161=129%:%
+%:%162=130%:%
+%:%163=131%:%
+%:%164=132%:%
+%:%165=133%:%
+%:%166=134%:%
+%:%167=135%:%
+%:%168=136%:%
+%:%169=137%:%
+%:%170=138%:%
+%:%171=139%:%
+%:%172=140%:%
+%:%173=141%:%
+%:%174=142%:%
+%:%175=143%:%
+%:%176=144%:%
+%:%177=145%:%
+%:%178=146%:%
+%:%187=148%:%
+%:%199=150%:%
+%:%200=151%:%
+%:%201=152%:%
+%:%202=153%:%
+%:%203=154%:%
+%:%204=155%:%
+%:%213=157%:%
+%:%225=159%:%
+%:%226=160%:%
+%:%227=161%:%
+%:%228=162%:%
+%:%229=163%:%
+%:%230=164%:%
+%:%231=165%:%
+%:%232=166%:%
+%:%233=167%:%
+%:%234=168%:%
+%:%235=169%:%
+%:%236=170%:%
+%:%237=171%:%
+%:%238=172%:%
+%:%239=173%:%
+%:%240=174%:%
+%:%241=175%:%
+%:%242=176%:%
+%:%243=177%:%
+%:%244=178%:%
+%:%245=179%:%
+%:%246=180%:%
+%:%247=181%:%
+%:%248=182%:%
+%:%249=183%:%
+%:%250=184%:%
+%:%251=185%:%
+%:%252=186%:%
+%:%253=187%:%
+%:%254=188%:%
+%:%255=189%:%
+%:%256=190%:%
+%:%257=191%:%
+%:%258=192%:%
+%:%259=193%:%
+%:%260=194%:%
+%:%261=195%:%
+%:%262=196%:%
+%:%263=197%:%
+%:%264=198%:%
+%:%265=199%:%
+%:%266=200%:%
+%:%267=201%:%
+%:%268=202%:%
+%:%269=203%:%
+%:%270=204%:%
+%:%271=205%:%
+%:%272=206%:%
+%:%273=207%:%
+%:%274=208%:%
+%:%275=209%:%
+%:%276=210%:%
+%:%277=211%:%
+%:%278=212%:%
+%:%279=213%:%
+%:%280=214%:%
+%:%281=215%:%
+%:%282=216%:%
+%:%283=217%:%
+%:%284=218%:%
+%:%285=219%:%
+%:%286=220%:%
+%:%287=221%:%
+%:%288=222%:%
+%:%289=223%:%
+%:%290=224%:%
+%:%291=225%:%
+%:%292=226%:%
+%:%293=227%:%
+%:%294=228%:%
+%:%295=229%:%
+%:%296=230%:%
+%:%297=231%:%
+%:%298=232%:%
+%:%299=233%:%
+%:%300=234%:%
+%:%301=235%:%
+%:%302=236%:%
+%:%303=237%:%
+%:%304=238%:%
+%:%305=239%:%
+%:%306=240%:%
+%:%307=241%:%
+%:%308=242%:%
+%:%309=243%:%
+%:%310=244%:%
+%:%311=245%:%
+%:%312=246%:%
+%:%313=247%:%
+%:%314=248%:%
+%:%315=249%:%
+%:%316=250%:%
+%:%317=251%:%
+%:%318=252%:%
+%:%319=253%:%
+%:%320=254%:%
+%:%321=255%:%
+%:%322=256%:%
+%:%323=257%:%
+%:%324=258%:%
+%:%325=259%:%
+%:%326=260%:%
+%:%327=261%:%
+%:%328=262%:%
+%:%329=263%:%
+%:%330=264%:%
+%:%331=265%:%
+%:%332=266%:%
+%:%333=267%:%
+%:%334=268%:%
+%:%335=269%:%
+%:%336=270%:%
+%:%337=271%:%
+%:%338=272%:%
+%:%339=273%:%
+%:%340=274%:%
+%:%341=275%:%
+%:%342=276%:%
+%:%343=277%:%
+%:%344=278%:%
+%:%345=279%:%
+%:%346=280%:%
+%:%347=281%:%
+%:%348=282%:%
+%:%349=283%:%
+%:%350=284%:%
+%:%351=285%:%
+%:%352=286%:%
+%:%353=287%:%
+%:%354=288%:%
+%:%355=289%:%
+%:%356=290%:%
+%:%357=291%:%
+%:%358=292%:%
+%:%359=293%:%
+%:%360=294%:%
+%:%361=295%:%
+%:%362=296%:%
+%:%363=297%:%
+%:%364=298%:%
+%:%365=299%:%
+%:%366=300%:%
+%:%367=301%:%
+%:%368=302%:%
+%:%369=303%:%
+%:%370=304%:%
+%:%371=305%:%
+%:%372=306%:%
+%:%373=307%:%
+%:%374=308%:%
+%:%375=309%:%
+%:%376=310%:%
+%:%377=311%:%
+%:%378=312%:%
+%:%379=313%:%
+%:%380=314%:%
+%:%381=315%:%
+%:%382=316%:%
+%:%383=317%:%
+%:%384=318%:%
+%:%385=319%:%
+%:%386=320%:%
+%:%387=321%:%
+%:%388=322%:%
+%:%389=323%:%
+%:%390=324%:%
+%:%391=325%:%
+%:%392=326%:%
+%:%393=327%:%
+%:%394=328%:%
+%:%395=329%:%
+%:%396=330%:%
+%:%397=331%:%
+%:%398=332%:%
+%:%399=333%:%
+%:%400=334%:%
+%:%401=335%:%
+%:%402=336%:%
+%:%403=337%:%
+%:%404=338%:%
+%:%405=339%:%
+%:%406=340%:%
+%:%407=341%:%
+%:%408=342%:%
+%:%409=343%:%
+%:%410=344%:%
+%:%411=345%:%
+%:%412=346%:%
+%:%413=347%:%
+%:%414=348%:%
+%:%415=349%:%
+%:%416=350%:%
+%:%417=351%:%
+%:%418=352%:%
+%:%419=353%:%
+%:%420=354%:%
+%:%421=355%:%
+%:%422=356%:%
+%:%423=357%:%
+%:%424=358%:%
+%:%425=359%:%
+%:%426=360%:%
+%:%427=361%:%
+%:%428=362%:%
+%:%429=363%:%
+%:%430=364%:%
+%:%431=365%:%
+%:%432=366%:%
+%:%441=371%:%
+%:%453=373%:%
+%:%454=374%:%
+%:%455=375%:%
+%:%456=376%:%
+%:%457=377%:%
+%:%458=378%:%
+%:%459=379%:%
+%:%460=380%:%
+%:%461=381%:%
+%:%462=382%:%
+%:%463=383%:%
+%:%464=384%:%
+%:%465=385%:%
+%:%466=386%:%
+%:%467=387%:%
+%:%468=388%:%
+%:%469=389%:%
+%:%470=390%:%
+%:%471=391%:%
+%:%472=392%:%
+%:%473=393%:%
+%:%474=394%:%
+%:%475=395%:%
+%:%476=396%:%
+%:%477=397%:%
+%:%478=398%:%
+%:%479=399%:%
+%:%480=400%:%
+%:%481=401%:%
+%:%482=402%:%
+%:%483=403%:%
+%:%484=404%:%
+%:%485=405%:%
+%:%486=406%:%
+%:%487=407%:%
+%:%488=408%:%
+%:%489=409%:%
+%:%490=410%:%
+%:%491=411%:%
+%:%492=412%:%
+%:%493=413%:%
+%:%494=414%:%
+%:%495=415%:%
+%:%496=416%:%
+%:%497=417%:%
+%:%498=418%:%
+%:%499=419%:%
+%:%508=422%:%
+%:%520=425%:%
+%:%521=426%:%
+%:%522=427%:%
+%:%523=428%:%
+%:%524=429%:%
+%:%525=430%:%
+%:%526=431%:%
+%:%527=432%:%
+%:%528=433%:%
+%:%529=434%:%
+%:%530=435%:%
+%:%531=436%:%
+%:%532=437%:%
+%:%533=438%:%
+%:%534=439%:%
+%:%535=440%:%
+%:%536=441%:%
+%:%537=442%:%
+%:%538=443%:%
+%:%539=444%:%
+%:%540=445%:%
+%:%549=448%:%
+%:%553=450%:%
+%:%557=452%:%

### 2022-02-22 paper/output/document/thesis_5_discussion.tex
chapter 5 done except for conclusion

@@
 
-\noindent \textbf{Implications for Self Doubt and Self Respect}
-
-The idea that we cannot will badly formed maxims
-
-The dancing maxim can also be understood through the lens of self-doubt. Under this 
-reading, the question ``When I am dancing, 
-should I be dancing for the sake of dancing?" is the agent asking, ``Am I doing the right thing 
-right now?" Unlike the drowning example, the agent is not asking about the next moment, but is expressing doubt about the 
-moral validity of their behavior at this current moment. I do not want to argue that self-doubt always
- undermines the will—after all, self-doubt plays an important role in moral 
-reasoning and is often the mark of a thoughtful agent. I argue instead that questions of self-doubt
-do not actually involve vacuous maxims, for these are not the maxims that the agent is doubting. Indeed,
-this example demonstrates that the tension between self-doubt and self-respect arises from a 
-mistaken characterization of questions of self-doubt as questions about vacuous maxims.
+\noindent \textbf{Implications for Self-Doubt and Self-Respect}
+
+The idea that we cannot even evaluate, let alone will badly formed maxims has implications for 
+self-doubt and self-respect. The dancing maxim can be read using the lens of self-doubt. Under this 
+reading, the question ``When I am dancing, should I be dancing for the sake of dancing?'' is the agent asking, 
+``Am I doing the right thing right now?'' Unlike the drowning example, the agent is not asking about the 
+next moment, but is expressing doubt about the moral validity of their behavior at this current moment. 
+I do not argue that self-doubt always undermines the will—after all, self-doubt plays an 
+important role in moral reasoning and is often the mark of a thoughtful agent. I argue instead 
+that questions of self-doubt do not actually involve badly-formed maxims, for these are not the maxims 
+that the agent is doubting. This example demonstrates that the tension between self-doubt and self-respect 
+arises from a mistaken characterization of questions of self-doubt as questions about badly-formed maxims.
 I first explain the tension between self-doubt and self-respect in epistemology, then 
@@
 In epistemology, there is a tension between the rational requirement to believe in yourself and the 
-value of self-doubt, in moderation. Christensen presents the ``principle of self-respect," which requires 
+value of self-doubt, in moderation. Christensen presents the ``principle of self-respect,'' which requires 
 that any rational agent refrain from believing that they have mistaken beliefs \cite[4]{christensen}. For example, I cannot 
@@
 
-While most philosophers accept some version of SR\footnote{Van Fraassen, Vickers, Koons \cite[5]{christensen}}, 
+While most philosophers accept some version of SR\footnote{Christensen cites \citet{vanfraaseen}, 
+\citet{vickers}, and \citet{koons}.}, 
 Roush argues that the principle must be modified in order to account for healthy epistemic 
-self-doubt. She argues that, while pathological second-guessing is roundly criticized, we are generally 
-imperfect beings, and some sensitivity to our own limitations is a virtue \cite[2]{roushselfhelp}. Indeed, even Christensen 
+self-doubt. She argues that, while pathological second-guessing is correctly criticized, we are generally 
+imperfect beings, and some sensitivity to our own limitations is a virtue \cite[2]{roushselfhelp}. Even Christensen 
 acknowledges that total self-confidence is an epistemic flaw \cite[1]{christensen}. Thus, there is tension between the rational
@@
 
-This debate between self-respect and self-doubt in epistemology also applies to ethics. When we 
-decide to act and commit ourselves to acting, we cannot simultaneously doubt the 
-validity of our action. If human behavior is purposive, then the very act of committing oneself implies 
-that one has sufficient reasons for committing oneself. These reasons may be flawed, but in making the 
-commitment, the reasoner has accepted them. It is contradictory to claim that someone commits and questions 
-simultaneously, because commitment itself implies a resolution to the question. Either the commitment 
-is not real, or the question is not. I will call the principle that 
-one cannot will a maxim and simultaneously question if they should will that maxim
-``ethical self-respect" or ESR.
+This debate between self-respect and self-doubt in epistemology can be extended to ethics. When we 
+commit ourselves to acting, we cannot simultaneously doubt the validity of our action. If human 
+behavior is purposive, then the very act of committing implies that one has sufficient reasons for 
+committing. These reasons may be flawed, but in making the commitment, the reasoner accepts them. It 
+is contradictory to claim that someone commits and questions simultaneously. Either the commitment 
+is not real, or the question is not. I will call the principle that one cannot will a maxim and 
+simultaneously question if they should will that maxim ``ethical self-respect'' or ESR.
 
 On the other hand, self-doubt is an important part of ethical reasoning. Just as believers are often 
-mistaken, so are practical reasoners. An agent with perfect confidence, who is always sure that they 
-are doing the right thing, is clearly not thinking deeply enough about their obligations. Some degree
-of ethical self-doubt is normal and likely desirable. Thus, there is a tension between the rational
-requirement of ESR and the intuitive validity of ethical self-doubt (ESD).
+mistaken, so are practical reasoners. An agent who is always sure that they are doing the right thing 
+is not thinking deeply enough about their obligations. Some degree of ethical self-doubt is desirable. 
+Thus, there is tension between the rational requirement of ESR and the intuitive validity of ethical 
+self-doubt (ESD).
 
 To resolve this tension, I return to my earlier example of a dancer. Imagine Sara is dancing at a 
-weddding, when, in a moment of angst, she asks herself, ``Should I really be dancing right now?" 
-What question is she asking here? The immediate answer is that she asking if the maxim, ``When dancing 
-at your friend's wedding, dance for the sake of dancing" is a permissible maxim to act on. Notice that t
-he maxim in question is vacuous: the circumstance ``when dancing at a friend's wedding" implies the act 
-``dance." Because this is a vacuous maxim, it cannot be the maxim that she is questioning, for adopting 
+weddding, when, in a moment of angst, she asks herself, ``Should I really be dancing right now?'' 
+It seems that she asking if the maxim, ``When dancing at your friend's wedding, dance for the sake 
+of dancing'' is a permissible maxim to act on. Notice that the maxim in question is badly-formed: the 
+circumstance ``when dancing at a friend's wedding'' implies the act ``dance.'' Because this is a 
+badly-formed maxim, it cannot be the maxim that she is questioning, for adopting
 this maxim could not have changed her behavior at all. Sara is asking a question about her actions and 
-their validity. Any conclusions about the validity of a vacuous maxim would not help her, first because 
+their validity. Any conclusions about the validity of a badly-formed maxim would not help her, first because 
 the maxim has no effect on her action, and second because any such validity would be a foregone conclusion
-as she has already adopted the maxim. As 
-I argued above, no practical reasoner can coherently ask themselves whether a vacuous maxim is 
-valid or not without undermining their will, which is a contradiction. Thus, under 
-the interpretation of self-doubt as a vacuous maxim, the tension between ESR and ethical self-doubt 
-appears irresolvable. Those committed to this interpretation must abandon one principle or the other.
+since she has already adopted the maxim. Thus, under the interpretation of self-doubt as a badly-formed 
+maxim, the tension between ESR and ethical self-doubt seems irresolvable. Those committed to this 
+interpretation must abandon one principle or the other.
 
 To resolve this issue, I turn to another interpretation of ethical self-doubt. Under this interpretation, 
-when Sara asks, ``Should I really be dancing right now?" she wants to know if the maxim that 
-resulted in the current moment when she is on the dance floor was actually 
-the right thing to will. She is asking if she made the right 
-decision in the past, when she decided to dance. The maxim that initiated the dancing would be something 
-like ``When at a wedding, dance for the sake of dancing." This is the maxim that she is currently acting 
-on, not the vacuous maxim ``When dancing, dance for the sake of dancing." Under this interpretation, 
+when Sara asks, ``Should I really be dancing right now?'' she wants to know if the maxim that 
+resulted in the current moment when she is on the dance floor was the right thing to will. She is 
+asking if she made the right decision in the past, when she decided to dance. The maxim that initiated 
+the dancing may be something like ``When at a wedding, dance for the sake of dancing.'' This is the maxim 
+that she is currently acting on, not the badly-formed maxim  from above. Under this interpretation, 
 there is no tension at all between self-doubt and self-respect. It is perfectly valid for a reasoner 
@@
 
-Not only does this second interpretation resolve the tension between ESR and ESD, it also more accurately 
-tracks the operation of practical reason. As argued above, a practical reasoner would never ask themselves 
-whether or not to will a vacuous maxim, because such a maxim would generate no meaningful obligations. 
-Adopting such a maxim would not alter their behavior in any way. Moreover, the fact that a practical 
-reasoner never adopts a vacuous maxim demonstrates the cause of the tension between ESR and ESD.
-The tension itself arises from a misreading of questions of self-doubt as questions about 
-the evaluation of vacuous maxims. A question of self-doubt cannot refer to a vacuous maxim and must 
+The tension between ESR and ESD arises from a misreading of questions of self-doubt as questions about 
+the evaluation of badly-formed maxims. A question of self-doubt cannot refer to a badly-formed maxim and must 
 instead refer to a well-formed maxim about the agent's past decision-making. As seen before, cases where 
-agents appear to ask themselves about vacuous maxims are mistaken about the maxim in question, because 
-such a question could never yield a useful answer for a practical reasoner.
-
-I arrived at this conclusion using Isabelle's proof-finding capabilities. Recall that Sledgehammer showed
-that my original version of the FUL\footnote{The full logical representation is \isa{FUL{\isadigit{0}}\ {\isasymequiv}\ {\isasymforall}c\ a\ g\ s{\isachardot}\ not{\isacharunderscore}universalizable\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ {\isasymlongrightarrow}\ {\isasymTurnstile}prohibited\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s}.} contradicted
-the axiom O\_diamond, which states that an obligated term cannot contradict its context\footnote{The 
-full form of the axiom is $ O \{ A \vert B \} \longrightarrow \diamond (B \wedge A)$}. I hypothesized 
-that there was some tension between the antecedent of the FUL, which states that all agents act on 
-the maxim, and the consequent, which states that the maxim is prohibited. If the maxim has already 
-been acted on, then not acting on it is impossible. Thus, the generated prohibition is impossible to 
-obey, so the ought implies can principle and axiom O\_diamond are violated.
-
-To test this hypothesis, I defined a specific maxim as a constant with no other defined features, 
-and examined the consequences of the FUL holding for this specific maxim. Instead of quantifying over
-all circumstance, act, goal tuples, I states that the FUL holds for the specific maxim defined by
-by new constant. With this modification, Nitpick showed that the FUL is consistent! The reason that
-the FUL could hold for a constant maxim but not for all maxims is that, as constants, the 
-circumstances, act, and goal were all distinct. When they were quantified over, 
-they could be identical. This motivated the definition of a well-formed maxim.
-
-To formalize this idea, I defined a maxim as \isa{well{\isacharunderscore}formed\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ w{\isachardot}\ {\isasymnot}\ c\isactrlbold {\isasymrightarrow}g\ w\ {\isasymand}\ {\isasymnot}\ c\isactrlbold {\isasymrightarrow}a\ s\ w}.
-In propositional
-logic, a circumstance, act, goal tuple (c, a, g) is well-formed if $(\neg (c \longrightarrow a) ) \wedge 
-(\neg(c \longrightarrow g))$. I tested my hypothesis by modifying my axiom to instead read $\forall$\emph{maxim
-(maxim is well-formed} $\longrightarrow$ \emph{FUL holds for maxim}). This version of the FUL was indeed consistent!
-
-To summarize, I realized that my initial attempt at formalizing the FUL was inconsistent because 
-it required that the FUL hold for badly formed maxims, in which the circumstances entail the act or 
-goal. The logical insight was that if FUL holds for maxims in which $(c \longrightarrow a) \vee 
-(c \longrightarrow g)$, then the logic will be inconsistent.
-
-SAY INCERDIBLE DIFFICULT WITHUT COMPUTER because computer looks for edge cases and makes assumptions precise.
-it's an insight precisely because philosophers would never think of this edge case bc it's stupid.%
+agents appear to ask themselves about badly-formed maxims are mistaken about the maxim in question, because 
+such a question could never yield a useful answer for a practical reasoner.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupsubsubsection{The Value of Computational Ethics%
+\isamarkupsubsubsection{An Argument For Computational Ethics%
 }
@@
 \begin{isamarkuptext}%
-I will now generalize from the personal insight reached above to the methodological value of 
-computational ethics for philosophers.
-I do not argue that computational ethics, as it stands today, uncovers philosophical insights that humans have not reached
-or are incapable of reaching. After all, my understanding of a well-formed maxim could 
-very well exist in the literature and certainly could be reached by a philosopher without any 
-computational tools. Instead, I argue that computational tools prompt philosophers to ask questions that 
-lead to insights. Philosophers already value precision, and the computer forces precision and makes formal
-reasoning easier. Computational 
-ethics can serve as another tool in a philosopher's arsenal, like a thought experiment or counterexample.
-While the technology is not yet mature enough and easy enough to use to become widespread in philosophy
-departments, technical progress could turn computational ethics into an easy-to-use tool for philosophers
-that doesn't require any specialized progamming or logical knowledge.
-
-The first contribution of computational ethics is precision \footnote{TODO: this article discusses 
-benefits of precision: bookmarked}. Much of analytic philosophy involves 
-making a particular concept precise. Thought experiments, arguments, counterexamples, and examples 
+The philosophical insight above is an example of the kind of philosophical progress that can be 
+made using computational tools and serves as evidence for the power of computational ethics. The 
+idea that the FUL can only hold for well-formed maxims would have been
+incredibly difficult to discover without a computer. I discovered it while formulating the FUL because 
+Isabelle's proof-finding tools look for edge cases like badly-formed maxims. Badly-formed maxims are 
+interesting because they are the kind of thing that is usually ignored in ordinary philosophical inquiry. 
+Philosophers usually assume that we are not discussing badly-formed maxims because, as argued above, 
+they are not the kind of thing that is usually useful to study. Computational tools like Isabelle
+require that assumptions like the exclusion of well-formed maxims are made precise, and thus force 
+philosophers to understand their arguments in a new way. This example demonstrates the contributions
+that computational ethics makes: it can quickly check edge cases and it requires that all assumptions be
+made explicit and precise.
+
+I do not argue that computational ethics uncovers philosophical insights that humans are incapable 
+of reaching. Instead, I claim that insights like the one about the well-formed maxim are much easier
+to reach with computational tools. Badly-formed maxims are usually ignored in philosophical discussion 
+and would have been much more difficult to understand without the help of a computer which immediately
+noted that they render the FUL inconsistent. Computational tools prompt philosophers to ask new questions that 
+lead to insights. Computational ethics can serve as another tool in a philosopher's arsenal, like a 
+thought experiment or counterexample.
+
+The first benefit of computational ethics is precision, which is the goal of much analytic
+philosophy. Thought experiments, arguments, counterexamples, and examples 
 illustrate features of a concept in the hope of making the concept itself more precise. Computational 
-ethics can help philosophers reach this goal of precision in another, potentially easier, way. 
-Representing a philosophical idea in logic and implementing it in an interactive theorem prover requires 
-making the idea precise to a degree that ordinary discussion can result in, but does not necessarily require. The initial representation 
-of an idea in a logic requires making its form precise. For example, 
-as I formalized the notion of a maxim, I had to understand its components and define it as a 
-circumstance, act, goal tuple. Moreover, Isabelle's strict typing system required that I define 
-coherent, consistent types for each of these entities and for a maxim as a whole. This requires understanding 
-what role each of these components play in the FUL and assigning them each a type. In my example, I 
-concluded that circumstances and goals are terms, which can be true or false at a world, and acts are 
-open sentences, which are true for a particular subject at a particular world. This precision is possible 
-without computational tools, but computational ethics forces a level of precision that ordinary discussion 
-does not demand. Type fuzziness and overloaded definitions are all too common in philosophical writing and 
-discussion (would be cool to cite some famous debate revolving around this idea), but computers don't 
-allow this kind of imprecision.
-
-Another, related benefit of computational ethics is that it makes formal ethics far less tedious. 
-Certain subfields, such as philosophy of language, see such benefit in precision that they already 
-use symbolic logic to represent philosophical concepts, just as mathematicians use symbolic logic to 
-represent mathematical concepts. Some of this work requres tedious pencil and paper proofs to prove 
-theorems, even when many of these theorems may not generate relevant philosophical insights. Interactive 
-theorem provers make formal logic more accessible. Isabelle can complete a proof, starting from first principles, 
-in a matter of seconds that would take a logician pages to complete. Similarly, Nitpick can generate 
-examples or counterexamples to a proposition in a brute force manner. The computer can generate hypotheses
-that philosophers can then think about, just as it did for me to prompt the insight above.
-
-Just as calculators make arithmetic more accessible, computational ethics does the same for formal philosophy. 
-Not all philosophy can or will 
-be formalized or automated—after all, calculators didn't make accountants or mathematicians obsolete. Just as computers 
-reduce the tedium in other aspects of our life, they can reduce the tedium involved in formal logic to 
-allow mathematicians and philosophers to focus their attention on understanding.%
+ethics can help philosophers reach the goal of precision. Representing a philosophical idea in logic 
+and implementing it in an interactive theorem prover requires making the idea precise to a degree 
+that ordinary discussion does not necessarily require. For example, as I formalized the notion of a 
+maxim, I had to understand its components and define it as a circumstance, act, goal tuple. Moreover, 
+Isabelle's strict typing system required that I define coherent, consistent types for each of these 
+entities and for a maxim as a whole. This precision is possible without computational tools, but 
+computational ethics forces a level of precision that ordinary discussion does not demand. Type 
+fuzziness and overloaded definitions are all too common in philosophical writing and 
+discussion, but computers diaallow this kind of imprecision.
+
+Another benefit of computational ethics is that it makes certain kinds of ethical inquiry, such as 
+searching for counterexamples or formal ethics, far less tedious. For example, Nitpick can refute 
+an ethical statement in seconds by using brute force to construct a counterexample, something that can require hours
+of thought and discussion. I arrived at the insight about badly-formed maxims because Isabelle 
+can check edge cases, like that of the badly-formed maxim, far more quickly than a human being. Moreover, 
+subfields that use symbolic logic to represent philosophical concepts (e.g. philosophy of language) can 
+use interactive theorem provers like Isabelle to complete proofs in a matter of seconds. By automating 
+away the tedium, computational ethics can give philosophers the tools to ask new kinds of questions.%
 \end{isamarkuptext}\isamarkuptrue%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\isatagdocument
-%
-\isamarkupsubsubsection{Looking Forward%
-}
-\isamarkuptrue%
-%
-\endisatagdocument
-{\isafolddocument}%
-%
-\isadelimdocument
-%
-\endisadelimdocument
 %
@@
 Computational ethics is at its infancy. The use of theorem provers in mathematics is just now beginning 
-to make headway \cite{buzzardvideo}, even though theorem provers were first invented in the 1960's \cite{historyofITP}. In contrast, the first attempts to use theorem 
-provers for ethics occurred in the last decade. The fact that this nascent technology is already 
-helping humans reach non-trivial philosophical conclusions is reason to, at the very least, entertain 
-the possibility of a future where computational ethics becomes as normal for philosophers.
-
-To the skeptic, the ethical insights uncovered by the computer are not necessarily impressive 
-philosophy. Indeed, the fact that a theorem prover requires specialized knowledge outside of the field 
+to make headway \citep{buzzardvideo}, even though theorem provers were first invented in the 1960's \citep{historyofITP}. 
+In contrast, the first attempts to use theorem provers for ethics occurred in the last decade. The 
+fact that this nascent technology is already helping humans reach non-trivial philosophical conclusions 
+is reason to, at the very least, entertain the possibility of a future where computational ethics 
+becomes as normal for philosophers as using a thought experiment.
+
+To the skeptic, the fact that a theorem prover requires specialized knowledge outside of the field 
 of philosophy indicates that the technology is nowhere near ready for universal use in philosophy 
@@
 progress, computational ethics will become more usable. Theorem provers in mathematics began as toys 
-incapable of proving that the real number 2 is not equal to the real number 1, but Buzzard showed that 
-moving from such a primitive system to a tool for Fields medal winning mathematics is possible in a 
-matter of years \cite{buzzardvideo}. Countless examples from the history of computer science, from the Turing 
+incapable of proving that the real number 2 is not equal to the real number 1, but 
+moving from basic algebra to Fields medal winning mathematics became possible in a
+matter of years \citep{buzzardvideo}. Countless examples from the history of computer science, from the Turing 
 Test to AI game playing to protein folding, demonstrate that progress in computer science can make seemingly 
-obscure computer programs useful and usable in ways that exceed our wildest imaginations. Indeed, 
-programmable computers themselves initially began as unwieldy punch card readers, but their current ubiquity 
+obscure computer programs useful and usable in ways that exceed our wildest imaginations.
+Programmable computers themselves initially began as unwieldy punch card readers, but their current ubiquity 
 need not be stated. If computer scientists and philosophers invest in computational ethics, it can 
-become as much a tool for philosophy as a calculator is for for arithmetic.\footnote{Is this too like, 
-lalalala fantasy of computational philosophy? Would it be less so if I did more work explaining 
-the history of theorem proving for math? Is this even that important for my project?}%
+become as much a tool for philosophy as a calculator is for for arithmetic.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupsubsection{Related Work%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
+Many philosophers cringe at the idea that a computer could perform ethical reasoning or that the 
+categorical imperative could provide an algorithm for moral judgement. For example, Rawls asserts, 
+``it is a serious misconception to think of the CI-procedure as an algorithm intended to yield, 
+more or less mechanically, a correct judgment. There is no such algorithm, and Kant knows this'' \citep[166]{rawlslectures}. 
+Ebels-Duggan also claims, ``no one supposes that the Categorical Imperative provides a mechanical 
+algorithm that delivers all by itself a complete account of what we ought to do in any given 
+situation'' \citep[174]{ebelsduggan}. However unmechanical ethical reasoning
+may seem, these claims are not obvious and require further justification. Philosophers who believe 
+that mental activity completely determines moral reasoning must explain why computers can, in theory, 
+simulate certain mental processes like arithmetic and language, but cannot perform ethical reasoning. 
+Without a soul or God-based account of ethical reasoning, it is not obvious that it is theoretically 
+impossible to automate ethical reasoning. After all, computers may eventually learn to simulate human 
+mental activity entirely, as shown by progress in brain simulation \citep{brainsimulation}.
+
+In this section, I explore potential arguments for why the categorical imperative could not be automated. When 
+philosophers say that the categorical imperative is not an algorithm, they are often are gesturing to the complexity
+of ethical judgement. They refer to the difficulty in determining morally relevant circumstances of a maxim or the common 
+sense required for a computer to behave ethically as arguments against a categorical imperative ``algorithm.'' 
+I will show in this section that these difficulties do not render automated Kantian ethics impossible, but 
+merely difficult. There categorical imperative may not provide a simple and immediate algorithm, but, as
+I demonstrate in this thesis, some parts of moral judgement using the FUL can be automated using not one
+algorithm, but the many algorithms necessary to automatically prove logical theorems.
+
+In \emph{Universal Laws and Ends In Themselves}, O'Neill argues against the existence of an algorithm for
+moral behavior. She points out that Kant draws an important distinction between a morally worthy maxim
+and a morally worthy action: the latter requires a good will, or a will motivated by duty. She argues that, 
+``Kant defines duty not (as would be common today) as outward performance of a certain sort, but as action
+that embodies a good will'' \citep[345]{oneilluniversallaws}. Moral behavior doesn't just require performing
+a ``good'' action, but it requires acting on a morally worthy maxim from the motivation of duty, or 
+doing the right thing because it is the right thing to do. Moral behavior requires both a certain action 
+(acting on a morally worthy maxim) and a certain motivation (the motivation of duty). It is the capacity 
+for self-motivation that makes morality binding for rational beings; we must behave morally precisely 
+because we have wills, or the ability to be motivated by ends
+that we choose. Only rational beings have wills, thus only rational beings can have good wills, or wills
+motivated by duty, and thus only rational beings can behave morally. Under this understanding
+of moral behavior, it seems unlikely that a computer could, in the near future, behave morally
+since a computer does not have motivation in the same way as a human being. If a computer is not a fully rational
+being, then, it is not the kind of thing that can behave morally.\footnote{A parallel argument can also be made for virtue ethics. Virtuous
+behavior requires not only a certain action, but also a certain disposition towards the action, so it seems
+difficult for an AI agent to truly behave virtuously.}
+
+The idea that, under Kant's account, a computer cannot behave morally, does not preclude the kind 
+of automated categorical imperative test that I present in this thesis. O'Neill argues that the FUL
+serves as a test of morally worthy maxims, and an automated categorical imperative test can be used 
+to identify this kind of maxim. Perhaps a computer cannot act on a morally relevant maxim from a motivation of duty, 
+but it certainly can act on this maxim nonetheless. For example, a self-driving car can choose to swerve to hit a tree
+to avoid injuring pedestrians in the crosswalk. This action may be one that acts on a morally worthy maxim
+\emph{even if} the self-driving car is not motivated by duty. The discpline of machine ethics is partially
+spurred by the recognition that, as automated agents become more powerful, they will need to make
+morally consequential decisions. Automated agents may be incapable of moral behavior, but automated agents that mimic
+moral behavior are surely better than agents that ignore morality entirely. Worries about unethical AI
+stem from the fact that AI agents are navigating a world inhabited by human beings, and their decisions
+impact us. Insofar as we are building AI that will operate in human society, the behavior of such AI 
+should mimic the behavior of an ethical human being. AI needs to be ethical for our sakes, so that we 
+can interact with it safely. If AI conforms to human ethics, then it will certainly navigate the world
+in a way that benefits human beings.
+
+Another challenge for automated Kantian ethics identified by O'Neill is that the FUL test requires that
+a maxim be given as input. O'Neill notes that the test assumes ``that agents will have certain tentative 
+plans, proposals and policies which they can consider, revise or reject or endorse and pursue'' \citep[343]{oneilluniversallaws}.
+The FUL evaluates the moral worth of a maxim given as input and this potential maxim is generated by 
+the choices that an agent is faced with. Determining this potential maxim is a challenge for both human
+and automated reasoners. Kant claims that the difficulty of determining an agent's potential maxim, which is their
+own, subjective understanding of their principle of action, is a reason that we may never be able 
+to know if morally worthy action has been performed \cite[345]{oneilluniversallaws}. Reasoners are faced with
+choices between potential actions and must determine the maxim, or principle, underlying each potential action.
+This is equivalent to a ``mapping'' problem: agents are given situations or dillemas as input and must map
+these to maxims.
+
+The challenge of mapping actions to maxims is a limitation of my system, but it is not insurmountable. In Section \ref{aiethics},
+I argued that, before my system can be used in practice, it must be paired with an input parser that can
+translate choices that an automated agent faces into maxims in a logic that my system can
+evaluate. This need follows from the difficulty in mapping a potential action
+to the maxim of action, whether concerning human action or machine action. As argued in Section \ref{AIethics},  
+this is not an insurmountable obstacle for automated ethics and heuristic-based approaches could resolve
+this issue. Determining the maxim of action is a challenge for Kantian human beings \citep{oneilluniversallaws}, 
+so it is unsurprising that it is a major hurdle for automated Kantian agents.
+
+As one of the strongest arguments against a categorical imperative algorithm, O'Neill argues that 
+the FUL is not supposed to provide a mechanism for deriving all morally worthy maxims from scratch. She notes
+that ``we usually already have learnt or worked out the moral standing of many common maxims of duty,''
+and so approach moral deliberation with an ``almanac'' of morally worthy and empty maxims \citep[394]{oneilluniversallaws}. 
+Rational agents navigating the world rarely recalculate the moral status of each potential maxim of 
+action; instead, we consult our almanac of maxims. This almanac is generated by moral education, 
+absorbed social values, and moral advice from people we trust. The categorical imperative is useful 
+to verify the rightness or wrongness of a maxim, but is not part of the bulk of human ethical reasoning.
+
+While human beings cannot repeatedly apply the universalizability test to all potential maxims during 
+every moral dilemma, computers have the computational power to do so. Human beings are 
+equipped with enough prior knowledge or common sense, to have an almanac of morally worthy maxims,
+but we have limited computational power. Computers, on the other hand, are comparatively
+much more capable of computation and thus can repeatedly recompute the results of the categorical
+imperative test. They do not come equipped with an almanac of maxims, but can simply recompute this
+almanac every time they need to make a decision. Human beings use common sense to make up for their computational
+limitations, and automated moral agents can use computational power to reduce the need for common sense.
+
+Daniela Tafani takes this argument one step further by arguing that this ``alamnac'' of maxims already 
+includes the moral status of the maxims in questions; human beings already
+know which maxims are morally worthy and which are morally lacking. The categorical imperative test
+merely reminds us, in moments of weakness, when we are tempted to make an exception to the moral law for 
+our own convenience or pleasure, that the moral law has no exceptions \citep[9]{tafani}. Thus, she claims
+that ``the Kantian test is therefore as useless for machines as it is for anyone who does
+not already know what to do'' \citep[8]{tafani}.\footnote{Translated from the original paper using Google Translate.} 
+Understanding the categorical imperative test as a reminder
+instead of a derivation tool also explains the fact noted in Section \ref{AIethics} that the FUL cannot 
+handle bad-faith attempts to generate false positives or negatives. The test only returns the right 
+result when an agent sincerely attempts to represent their maxim of action, not when an adversary attempts
+ to ``trick'' the categorical imperative.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{figure}
+\centering
+\includegraphics[scale=0.5]{inputparser.png}
+\caption{A refined version of Figure \ref{fig:AIengine} in which the input parser learns from a database
+of action-maxim mappings, which is in turn fed the output of my automated Kantian ethics system. } \label{fig:inputparser}
+\end{figure}
+%
+\begin{isamarkuptext}%
+This understanding of the role of the categorical imperative not only fails to render automate moral
+reasoning impossible, but it also offers insight into how to solve the challenge of creating an input parser.
+If the categorical imperative test is only useful to those who have some prior moral knowledge, then prior moral
+knowledge can and should be used to create an input parser. Specifically, some kind of machine learning-based approach
+could learn action-maxim mappings from a database of such mappings compiled by a human being. Moreover, 
+the human being could assign each maxim in the database a rightness or wrongness score. My implementation
+of the automated categorical imperative would then simply check the work of this machine learning algorithm and transform
+a fuzzy prediction into a provable, rigorous moral judgement. Moreover, this rigorous moral judgement
+could in turn be fed into the database of maxims to make the intput parser smarter. One example of 
+this kind of system is shown in Figure \ref{fig:inputparser}. The combination of 
+prior knowledge of some maxims' moral worth and the ability of a computer to constantly perform the
+universalizability test could not only match human ethical reasoning but perhaps also surpass it
+by double checking the moral intuitions that we take for granted. A computer with no common sense or prior knowledge
+may indeed be unable to reason using the categorical imperative, but one equipped with some prior knowledge
+of maxims and their moral worth may even help us better reason about morality.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsection{Related Work \label{relatedwork}%
 }
 \isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
+In 1685, Leibniz dreamed of a calculator that could resolve philosophical and theological 
+disputes \cite{leibniz}. At the time, the logical and computational resources necessary to make his 
+dream a reality did not exist. Today, automated ethics is a growing field, spurred in part by the 
+need for ethically intelligent AI agents. Tolmeijer et al. surveyed the state of the field of 
+machine ethics \citep{mesurvey} and characterized implementations in automated ethics by (1) the choice 
+of ethical theory, (2) implementation design decisions (e.g. logic programming), and (3) implementation 
+details (e.g. choice of logic).
+
+Two branches of automated ethics are top-down and bottom-up ethics. Top-down automated ethics begins 
+with an ethical theory, whereas bottom-up automated ethics learns ethical judgements from prior 
+judgements. One example of bottom-up automated ethics is Delphi, which uses deep learning to make 
+ethical judgements based on a dataset of human judgements \citep{delphi}. While Delphi displays great 
+flexibility, it often produces contradictory judgements, such as claiming that taxing exploitative 
+profitable companies is good, but burdening successful companies with high tax rates is bad \citep{verge}. 
+Because Delphi draws on error-prone human judgements instead of philosophical literature, it makes 
+the same judgement errors that humans make. Moreover, because Delphi used a bottom-up approach, 
+there is no explicit ethical theory explaining its judgements, so analytically arguing for or 
+against its conclusions is impossible. Top-down approaches, on the other hand, must be explicit about 
+the underlying ethical theories, and are thus more explainable.
+
+In this paper, I use a top-down approach to formalize Kantian ethics. There is a long line of work 
+automating other ethical theories, like consequentialism \citep{util1, util2} or particularism 
+\citep{particularism1, particularism2}. I choose to implement Kantian ethics because, as argued in 
+Section \ref{whykant}, it is the most formal and least data-intensive of the three major ethical 
+traditions. Kantian ethics is a deontological, or rule based ethic, and there is prior work 
+implementing other deontological theories \citep{dde, deon1, deon2}.
+
+Kantian ethics specifically appears to be an intuitive candidate for formalization and implementation 
+and there has been both theoretical and practical work on automating Kantian ethics \citep{powers, lin}. 
+In 2006, Powers \citep{powers} argued that implementing Kantian ethics presented technical challenges, 
+such as automation of a non-monotonic logic, and philosophical challenges, like a definition of the 
+categorical imperative. I address the former through my use of Dyadic Deontic Logic, which allows 
+obligations to be retracted as context changes, and the latter through my use of the practical 
+contradiction interpretation. There has also been prior work in formalizing Kantian metaphysics 
+using I/O logic \citep{io}. Deontic logic, which has been implemented in Isabelle/HOL, itself is inspired 
+by Kant's ``ought implies can'' principle, but it does not include a robust formalization of the entire 
+categorical imperative \citep{cresswell}.
+
+Kroy \citep{kroy} presents a formalization of the first two formulations of the categorical imperative, 
+but does not implement it. I implement his formalization of the FUL to compare it to my system. 
+Lindner and Bentzen \citep{BL} presented one of the first formalizations and implementations of 
+Kant's second formulation of the categorical imperative. They present their goal as ``not to get 
+close to a correct interpretation of Kant, but to show that our interpretation of Kant’s ideas can 
+contribute to the development of machine ethics.'' My work builds on theirs by formalizing the 
+first formulation of the categorical imperative as faithfully as possible. Staying faithful to 
+philosophical literature makes my system capable of making robust and reliable judgements.
+
+The implementation of this paper was inspired by and builds on Benzmüller, Parent, and Farjami's 
+foundational work with the LogiKEy framework for machine ethics, which includes their implementation 
+of DDL in Isabelle \citep{BFP, logikey}. The LogiKEy project has been used to study metaphysics 
+\citep{godel, metaphysics1}, law \citep{constitution}, and ethics \citep{gewirth}, but not 
+Kant's categorical imperative.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
 %
@@
 %:%389=323%:%
-%:%390=324%:%
-%:%391=325%:%
-%:%392=326%:%
-%:%393=327%:%
-%:%394=328%:%
-%:%395=329%:%
-%:%396=330%:%
-%:%397=331%:%
-%:%398=332%:%
-%:%399=333%:%
-%:%400=334%:%
-%:%401=335%:%
-%:%402=336%:%
-%:%403=337%:%
-%:%404=338%:%
-%:%405=339%:%
-%:%406=340%:%
-%:%407=341%:%
-%:%408=342%:%
-%:%409=343%:%
-%:%410=344%:%
-%:%411=345%:%
-%:%412=346%:%
-%:%413=347%:%
-%:%414=348%:%
-%:%415=349%:%
-%:%416=350%:%
-%:%417=351%:%
-%:%418=352%:%
-%:%419=353%:%
-%:%420=354%:%
-%:%421=355%:%
-%:%422=356%:%
-%:%423=357%:%
-%:%424=358%:%
-%:%425=359%:%
-%:%426=360%:%
-%:%427=361%:%
-%:%428=362%:%
-%:%429=363%:%
-%:%430=364%:%
-%:%431=365%:%
-%:%432=366%:%
-%:%441=371%:%
-%:%453=373%:%
-%:%454=374%:%
-%:%455=375%:%
-%:%456=376%:%
-%:%457=377%:%
-%:%458=378%:%
-%:%459=379%:%
-%:%460=380%:%
-%:%461=381%:%
-%:%462=382%:%
-%:%463=383%:%
-%:%464=384%:%
-%:%465=385%:%
-%:%466=386%:%
-%:%467=387%:%
-%:%468=388%:%
-%:%469=389%:%
-%:%470=390%:%
-%:%471=391%:%
-%:%472=392%:%
-%:%473=393%:%
-%:%474=394%:%
-%:%475=395%:%
-%:%476=396%:%
-%:%477=397%:%
-%:%478=398%:%
-%:%479=399%:%
-%:%480=400%:%
-%:%481=401%:%
-%:%482=402%:%
-%:%483=403%:%
-%:%484=404%:%
-%:%485=405%:%
-%:%486=406%:%
-%:%487=407%:%
-%:%488=408%:%
-%:%489=409%:%
-%:%490=410%:%
-%:%491=411%:%
-%:%492=412%:%
-%:%493=413%:%
-%:%494=414%:%
-%:%495=415%:%
-%:%496=416%:%
-%:%497=417%:%
-%:%498=418%:%
-%:%499=419%:%
-%:%508=422%:%
-%:%520=425%:%
-%:%521=426%:%
-%:%522=427%:%
-%:%523=428%:%
-%:%524=429%:%
-%:%525=430%:%
-%:%526=431%:%
-%:%527=432%:%
-%:%528=433%:%
-%:%529=434%:%
-%:%530=435%:%
-%:%531=436%:%
-%:%532=437%:%
-%:%533=438%:%
-%:%534=439%:%
-%:%535=440%:%
-%:%536=441%:%
-%:%537=442%:%
-%:%538=443%:%
-%:%539=444%:%
-%:%540=445%:%
-%:%549=448%:%
-%:%553=450%:%
-%:%557=452%:%
+%:%398=327%:%
+%:%410=329%:%
+%:%411=330%:%
+%:%412=331%:%
+%:%413=332%:%
+%:%414=333%:%
+%:%415=334%:%
+%:%416=335%:%
+%:%417=336%:%
+%:%418=337%:%
+%:%419=338%:%
+%:%420=339%:%
+%:%421=340%:%
+%:%422=341%:%
+%:%423=342%:%
+%:%424=343%:%
+%:%425=344%:%
+%:%426=345%:%
+%:%427=346%:%
+%:%428=347%:%
+%:%429=348%:%
+%:%430=349%:%
+%:%431=350%:%
+%:%432=351%:%
+%:%433=352%:%
+%:%434=353%:%
+%:%435=354%:%
+%:%436=355%:%
+%:%437=356%:%
+%:%438=357%:%
+%:%439=358%:%
+%:%440=359%:%
+%:%441=360%:%
+%:%442=361%:%
+%:%443=362%:%
+%:%444=363%:%
+%:%445=364%:%
+%:%446=365%:%
+%:%447=366%:%
+%:%448=367%:%
+%:%449=368%:%
+%:%450=369%:%
+%:%451=370%:%
+%:%455=374%:%
+%:%456=375%:%
+%:%457=376%:%
+%:%458=377%:%
+%:%459=378%:%
+%:%460=379%:%
+%:%461=380%:%
+%:%462=381%:%
+%:%463=382%:%
+%:%464=383%:%
+%:%465=384%:%
+%:%466=385%:%
+%:%467=386%:%
+%:%468=387%:%
+%:%469=388%:%
+%:%470=389%:%
+%:%471=390%:%
+%:%472=391%:%
+%:%473=392%:%
+%:%482=395%:%
+%:%494=398%:%
+%:%495=399%:%
+%:%496=400%:%
+%:%497=401%:%
+%:%498=402%:%
+%:%499=403%:%
+%:%500=404%:%
+%:%501=405%:%
+%:%502=406%:%
+%:%503=407%:%
+%:%504=408%:%
+%:%505=409%:%
+%:%506=410%:%
+%:%507=411%:%
+%:%508=412%:%
+%:%509=413%:%
+%:%510=414%:%
+%:%511=415%:%
+%:%512=416%:%
+%:%513=417%:%
+%:%514=418%:%
+%:%515=419%:%
+%:%516=420%:%
+%:%517=421%:%
+%:%518=422%:%
+%:%519=423%:%
+%:%520=424%:%
+%:%521=425%:%
+%:%522=426%:%
+%:%523=427%:%
+%:%524=428%:%
+%:%525=429%:%
+%:%526=430%:%
+%:%527=431%:%
+%:%528=432%:%
+%:%529=433%:%
+%:%530=434%:%
+%:%531=435%:%
+%:%532=436%:%
+%:%533=437%:%
+%:%534=438%:%
+%:%535=439%:%
+%:%536=440%:%
+%:%537=441%:%
+%:%538=442%:%
+%:%539=443%:%
+%:%540=444%:%
+%:%541=445%:%
+%:%542=446%:%
+%:%543=447%:%
+%:%544=448%:%
+%:%545=449%:%
+%:%546=450%:%
+%:%547=451%:%
+%:%548=452%:%
+%:%549=453%:%
+%:%550=454%:%
+%:%551=455%:%
+%:%552=456%:%
+%:%553=457%:%
+%:%554=458%:%
+%:%555=459%:%
+%:%556=460%:%
+%:%557=461%:%
+%:%558=462%:%
+%:%559=463%:%
+%:%560=464%:%
+%:%561=465%:%
+%:%562=466%:%
+%:%563=467%:%
+%:%564=468%:%
+%:%565=469%:%
+%:%566=470%:%
+%:%567=471%:%
+%:%568=472%:%
+%:%569=473%:%
+%:%570=474%:%
+%:%571=475%:%
+%:%572=476%:%
+%:%573=477%:%
+%:%574=478%:%
+%:%575=479%:%
+%:%576=480%:%
+%:%577=481%:%
+%:%578=482%:%
+%:%579=483%:%
+%:%580=484%:%
+%:%581=485%:%
+%:%582=486%:%
+%:%583=487%:%
+%:%584=488%:%
+%:%585=489%:%
+%:%586=490%:%
+%:%587=491%:%
+%:%588=492%:%
+%:%589=493%:%
+%:%590=494%:%
+%:%591=495%:%
+%:%592=496%:%
+%:%593=497%:%
+%:%594=498%:%
+%:%595=499%:%
+%:%596=500%:%
+%:%597=501%:%
+%:%598=502%:%
+%:%599=503%:%
+%:%600=504%:%
+%:%601=505%:%
+%:%604=508%:%
+%:%605=509%:%
+%:%606=510%:%
+%:%607=511%:%
+%:%608=512%:%
+%:%609=513%:%
+%:%612=515%:%
+%:%613=516%:%
+%:%614=517%:%
+%:%615=518%:%
+%:%616=519%:%
+%:%617=520%:%
+%:%618=521%:%
+%:%619=522%:%
+%:%620=523%:%
+%:%621=524%:%
+%:%622=525%:%
+%:%623=526%:%
+%:%624=527%:%
+%:%625=528%:%
+%:%626=529%:%
+%:%635=533%:%
+%:%647=535%:%
+%:%648=536%:%
+%:%649=537%:%
+%:%650=538%:%
+%:%651=539%:%
+%:%652=540%:%
+%:%653=541%:%
+%:%654=542%:%
+%:%655=543%:%
+%:%656=544%:%
+%:%657=545%:%
+%:%658=546%:%
+%:%659=547%:%
+%:%660=548%:%
+%:%661=549%:%
+%:%662=550%:%
+%:%663=551%:%
+%:%664=552%:%
+%:%665=553%:%
+%:%666=554%:%
+%:%667=555%:%
+%:%668=556%:%
+%:%669=557%:%
+%:%670=558%:%
+%:%671=559%:%
+%:%672=560%:%
+%:%673=561%:%
+%:%674=562%:%
+%:%675=563%:%
+%:%676=564%:%
+%:%677=565%:%
+%:%678=566%:%
+%:%679=567%:%
+%:%680=568%:%
+%:%681=569%:%
+%:%682=570%:%
+%:%683=571%:%
+%:%684=572%:%
+%:%685=573%:%
+%:%686=574%:%
+%:%687=575%:%
+%:%688=576%:%
+%:%689=577%:%
+%:%690=578%:%
+%:%691=579%:%
+%:%692=580%:%
+%:%693=581%:%
+%:%694=582%:%
+%:%695=583%:%
+%:%696=584%:%
+%:%697=585%:%
+%:%698=586%:%
+%:%707=588%:%

### 2022-02-22 paper/output/document/thesis_5_discussion.tex
cleaning chapter 5

@@
 \endisadelimdocument
+%
+\begin{isamarkuptext}%
+In this thesis, I present a proof-of-concept implementation of automated Kantian ethics. My system
+takes as input a potential action, appropriately represented, and can prove that it is obligated, 
+prohibited or permissible. I represent Kant's Formula of Universal Law in a deontic logic and 
+implement this logic in the Isabelle/HOL interactive theorem prover, which can automatically prove or 
+refute theorems in my custom logic. I also contribute a testing framework that I use to demonstrate that
+my implementation of Kantian ethics is more faithful to philosophical literature than two other 
+potential implementations. My completed system can, when given appropriate factual background, make
+philosophically mature judgements about complex moral dilemmas. This work is one step towards building 
+morally sophisticated artifical agents.
+
+The idea of fully automated artificial agents navigating the world without human supervision
+may be terrifying, but progress in AI indicates that such a future is likely closer than we think. 
+Philosophers, regulators, and computer scientists are sounding the alarm about the dangers of developing
+this kind of AI. Insofar as developers will continue to ignore these warnings and develop increasingly 
+independent AI, there is a dire need to program such AI with some notion of ethics. If AI is navigating
+human society, then it is making decisions with an ethical component at all times. Ethics is inescapable; 
+if AI developers and computer scientists ignore it, then they will be building machines that make decisions
+based on some set of unknown, implicit ethical values. Countless examples, from the Alleghany family services screening
+algorithm that is biased against poor families to search algorithms that associate black-sounding names
+with crime, demonstrate that such implicit ethics simply codifies the biases, prejudices, and moral
+failings of the society in which it is developed. AI will inevitably make judgements on moral dilemmas, 
+and automated ethics is necessary to make these judgements morally correct.
+
+Given that the discpline of philosophy has spent centuries debating such judgements and their theoretical 
+underpinnings, such AI will be most trustworthy, nuanced, consistent, and mature when it is faithful to 
+philosophical literature. In order to develop high-quality automated ethics, computer scientists and 
+philosophers must work together. This thesis is an experiment in marrying philosophy and computer science 
+to create automated ethics that is both technically and philosophically advanced. Neither discipline alone
+can address the pressing need for ethical AI.
+
+This work is an early proof-of-concept. It demonstrates the potential of top-down, logic programming 
+approaches to automated ethics and shows that it is possible to faithfully automate an ethical theory as
+complex as Kantian ethics. There are open questions that must be resolved before a system like this 
+could be used in practice, but this project demonstrates that these questions are within closer reach
+than they may seem. Automated ethics does not need to limit itself to simple, flattened versions of 
+ethical theories. With technical and philosophical progress, faithful automated ethics is possible.
+Growing public consciousness about the dangers of unregulated AI is creating momentum in machine ethics; 
+work like Delphi demonstrates that the time is ripe to create usable, reliable automated ethics. This 
+thesis is one step towards building computers that can think ethically in the richest sense of the word.%
+\end{isamarkuptext}\isamarkuptrue%
 %
@@
 %:%707=588%:%
+%:%719=590%:%
+%:%720=591%:%
+%:%721=592%:%
+%:%722=593%:%
+%:%723=594%:%
+%:%724=595%:%
+%:%725=596%:%
+%:%726=597%:%
+%:%727=598%:%
+%:%728=599%:%
+%:%729=600%:%
+%:%730=601%:%
+%:%731=602%:%
+%:%732=603%:%
+%:%733=604%:%
+%:%734=605%:%
+%:%735=606%:%
+%:%736=607%:%
+%:%737=608%:%
+%:%738=609%:%
+%:%739=610%:%
+%:%740=611%:%
+%:%741=612%:%
+%:%742=613%:%
+%:%743=614%:%
+%:%744=615%:%
+%:%745=616%:%
+%:%746=617%:%
+%:%747=618%:%
+%:%748=619%:%
+%:%749=620%:%
+%:%750=621%:%
+%:%751=622%:%
+%:%752=623%:%
+%:%753=624%:%
+%:%754=625%:%
+%:%755=626%:%
+%:%756=627%:%
+%:%757=628%:%

### 2022-02-22 paper/output/document/appendix.tex
chaper 5 cleaned

@@
 evaluating an agent's behavior, since that's when ``acting from duty" starts to matter.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+\noindent \textbf{``Effectiveness'' of a Maxim}%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+I wish to formalize the notion of an ``effective" maxim. Intuitively, a maxim (a rule to 
+perform an act A for goal G) is effective if the act results in the goal. For example, studying hard 
+to get good grades is (sometimes) an effective maxim because the act of studying (sometimes) results in
+ the end of getting good grades. At first glance, it is tempting to represent effectiveness 
+as follows: an act, goal pair ($A, G$) is effective if $A \longrightarrow G$. If $A$ then $G$ implies that 
+$A$ is an effective mechanism for achieving $G$.
+
+Trivial truth is a problem for this interpretation. If act $A$ never happens or 
+is impossible, then, $\forall G$, it is trivially true that $A \longrightarrow G$ (since $\sim A$). This leads to the 
+disturbing conclusion that impossible actions are effective in achieving any goal. While the messiness 
+is familiar to logicians, it has troubling implications for ethics.
+
+One such issue arises from Korsgaard's \cite{KorsgaardFUL} argument that, if an act no longer exists, then it is no 
+longer an effective mechanism for achieving any ends at all. This is a critical part of her interpretation 
+of the formula of universal law\footnote{Korsgaard compares two interpretations of the formula of universal law. 
+Under the logical contradiction view, a maxim is prohibited if, when everyone adopts it, it is logically
+impossible. Under the practical contradiction (PC) view, a maxim is prohibited if, when everyone adopt it, 
+it is no longer effective (the act isn't a means to the goal or end. For cases where universalization 
+renders the action impossible (like lying, since if everyone lies no one would believe each other), both 
+views should prohibit the maxim. For the PC view to prohibit the maxim, the maxim's impossibility must 
+also imply its ineffectiveness.}. Under Korsgaard's interpretation, if 
+studying hard is no longer an existing or possible action  (maybe because of perpetual construction outside my room), 
+then the maxim ``studying hard to get a good grade" is no longer effective. Trivial truth means that the
+initial definition of effectiveness cannot achieve this result.
+
+I could fix this problem by defining effectiveness as an act being existent and 
+also achieving the goal. I could try to model existent as ``possible at some world," therefore using 
+the power of modal logic to represent ideas like possibility. That way, a maxim is effective if (1) 
+the act is possible at some world and (2) in worlds where the act is in fact realized, the goal is also
+realized.
+
+This solution draws a distinction between the notions of possibility (which is a modal
+sentence) and truth or occurrence. Drawing this distinction 
+allows us to preserve the fact that trivial truth does, in some way, make sense. Specifically, in a world 
+where the act is not performed, we still think that the maxim is effective. Its effectiveness hasn't been 
+disproven. Just as all purple elephants can fly, hunting purple elephants is an effective way to make money\footnote{Someone not steeped in logic might not agree here.}.
+
+This solution has two drawbacks. First, it introduces additional logical complexity into the effectiveness
+predicate. This is fine, but may have performance/developer time drawbacks. Ideally, a sentence in simple propositional
+logic could represent effectiveness. Second, more importantly, it doesn't address the idea of ``causality." 
+It might be the case that $A \longrightarrow G$ but $A$ does not cause $G$. For example, maybe eating 
+banana bread is a way to improve my grades because I eat banana bread but also happen to study hard, which 
+is the real cause of my GPA. How can I represent this idea? $A \wedge G$ fails because an act doesn't have to occur to be an effective means to an end 
+(the same reason that preserving trivial truth is nice). $A \longleftrightarrow G$ fails because we can imagine
+there also being some other cause for $G$. I can get good grades by studying hard or by bribing my professor, but
+both of those remain effective methods to achieve goal $G$.
+
+How do I solve this problem? Should I look into logics of causation (I'm sure such things exist)? 
+Should I represent effectiveness as the implication $A \longrightarrow G$ holding at every world? That 
+idea addresses the second challenge about causation vs correlation, since if  $A \longrightarrow G$ in
+every possible world, then $A$ must cause $G$, since any fact noncontingent on $A$ will be false at some 
+possible world. This idea introduces even more logical complexity!%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %:%65=36%:%
-%:%100=65%:%
-%:%112=67%:%
-%:%113=68%:%
-%:%114=69%:%
-%:%115=70%:%
-%:%116=71%:%
-%:%125=73%:%
-%:%137=75%:%
-%:%138=76%:%
-%:%139=77%:%
-%:%141=79%:%
-%:%142=79%:%
-%:%143=79%:%
-%:%146=81%:%
-%:%147=82%:%
-%:%148=83%:%
-%:%149=84%:%
-%:%150=85%:%
-%:%152=87%:%
-%:%153=87%:%
-%:%155=88%:%
-%:%156=88%:%
-%:%158=89%:%
-%:%159=90%:%
-%:%162=92%:%
-%:%163=93%:%
-%:%164=94%:%
-%:%165=95%:%
-%:%166=96%:%
-%:%168=98%:%
-%:%169=98%:%
-%:%170=99%:%
-%:%171=100%:%
-%:%172=100%:%
-%:%173=101%:%
-%:%174=102%:%
-%:%175=102%:%
-%:%176=103%:%
-%:%177=104%:%
-%:%178=104%:%
-%:%179=105%:%
-%:%181=107%:%
-%:%182=108%:%
-%:%183=109%:%
-%:%185=111%:%
-%:%186=111%:%
-%:%187=112%:%
-%:%188=113%:%
-%:%189=113%:%
-%:%190=114%:%
-%:%191=117%:%
-%:%194=120%:%
-%:%195=121%:%
-%:%196=122%:%
-%:%197=123%:%
-%:%198=124%:%
-%:%201=126%:%
-%:%204=128%:%
-%:%205=129%:%
-%:%206=130%:%
-%:%207=131%:%
-%:%208=132%:%
-%:%209=133%:%
-%:%211=135%:%
-%:%212=135%:%
-%:%213=136%:%
-%:%214=137%:%
-%:%215=138%:%
-%:%216=138%:%
-%:%218=138%:%
-%:%222=138%:%
-%:%223=138%:%
-%:%225=139%:%
-%:%226=140%:%
-%:%227=141%:%
-%:%228=142%:%
-%:%238=144%:%
-%:%239=145%:%
-%:%240=146%:%
-%:%241=147%:%
-%:%242=148%:%
-%:%243=149%:%
-%:%244=150%:%
-%:%245=151%:%
-%:%246=152%:%
-%:%247=153%:%
-%:%249=155%:%
-%:%250=155%:%
-%:%251=156%:%
-%:%252=157%:%
-%:%253=158%:%
-%:%254=158%:%
-%:%256=158%:%
-%:%260=158%:%
-%:%261=158%:%
-%:%263=159%:%
-%:%264=160%:%
-%:%265=161%:%
-%:%266=162%:%
-%:%276=165%:%
-%:%277=166%:%
-%:%278=167%:%
-%:%279=168%:%
-%:%280=169%:%
-%:%281=170%:%
-%:%282=171%:%
-%:%283=172%:%
-%:%284=173%:%
-%:%286=176%:%
-%:%287=176%:%
-%:%288=177%:%
-%:%289=178%:%
-%:%290=179%:%
-%:%291=179%:%
-%:%293=179%:%
-%:%297=179%:%
-%:%298=179%:%
-%:%300=180%:%
-%:%301=181%:%
-%:%302=182%:%
-%:%303=183%:%
-%:%313=185%:%
-%:%314=186%:%
-%:%315=187%:%
-%:%316=188%:%
-%:%319=190%:%
-%:%322=192%:%
-%:%323=193%:%
-%:%324=194%:%
-%:%325=195%:%
-%:%326=196%:%
-%:%328=198%:%
-%:%329=198%:%
-%:%330=199%:%
-%:%331=200%:%
-%:%332=201%:%
-%:%333=201%:%
-%:%335=201%:%
-%:%339=201%:%
-%:%340=201%:%
-%:%342=202%:%
-%:%343=203%:%
-%:%344=204%:%
-%:%345=205%:%
-%:%355=207%:%
-%:%356=208%:%
-%:%365=213%:%
-%:%377=215%:%
-%:%378=216%:%
-%:%379=217%:%
-%:%380=218%:%
-%:%381=219%:%
-%:%383=220%:%
-%:%384=220%:%
-%:%385=221%:%
-%:%387=222%:%
-%:%388=223%:%
-%:%389=224%:%
-%:%392=226%:%
-%:%394=228%:%
-%:%395=228%:%
-%:%396=229%:%
-%:%397=230%:%
-%:%398=230%:%
-%:%400=230%:%
-%:%404=230%:%
-%:%405=230%:%
-%:%407=231%:%
-%:%408=232%:%
-%:%409=233%:%
-%:%410=234%:%
-%:%411=235%:%
-%:%412=236%:%
-%:%422=238%:%
-%:%424=240%:%
-%:%425=240%:%
-%:%427=242%:%
-%:%429=244%:%
-%:%430=244%:%
-%:%431=244%:%
-%:%433=244%:%
-%:%437=244%:%
-%:%438=244%:%
-%:%440=245%:%
-%:%441=246%:%
-%:%442=247%:%
-%:%443=248%:%
-%:%453=250%:%
-%:%454=251%:%
-%:%455=252%:%
-%:%456=253%:%
-%:%465=256%:%
-%:%477=258%:%
-%:%478=259%:%
-%:%479=260%:%
-%:%480=261%:%
-%:%481=262%:%
-%:%482=263%:%
-%:%483=264%:%
-%:%484=265%:%
-%:%485=266%:%
-%:%489=268%:%
-%:%493=270%:%
-%:%494=271%:%
-%:%495=272%:%
-%:%497=274%:%
-%:%498=274%:%
-%:%500=275%:%
-%:%501=276%:%
-%:%502=277%:%
-%:%503=278%:%
-%:%504=279%:%
-%:%505=280%:%
-%:%506=281%:%
-%:%507=281%:%
-%:%508=282%:%
-%:%509=283%:%
-%:%510=283%:%
-%:%511=284%:%
-%:%514=285%:%
-%:%518=285%:%
-%:%519=285%:%
-%:%521=286%:%
-%:%522=287%:%
-%:%532=289%:%
-%:%533=290%:%
-%:%534=291%:%
-%:%535=292%:%
-%:%536=293%:%
-%:%537=294%:%
-%:%538=295%:%
-%:%539=296%:%
-%:%540=297%:%
-%:%541=298%:%
-%:%542=299%:%
-%:%543=300%:%
-%:%544=301%:%
-%:%545=302%:%
-%:%546=303%:%
-%:%547=304%:%
-%:%548=305%:%
-%:%549=306%:%
-%:%553=308%:%
-%:%554=309%:%
-%:%556=311%:%
-%:%557=311%:%
-%:%559=312%:%
-%:%560=312%:%
-%:%561=313%:%
-%:%562=314%:%
-%:%563=314%:%
-%:%564=315%:%
-%:%567=316%:%
-%:%571=316%:%
-%:%572=316%:%
-%:%573=317%:%
-%:%574=317%:%
-%:%575=318%:%
-%:%576=318%:%
-%:%577=319%:%
-%:%578=319%:%
-%:%579=319%:%
-%:%580=320%:%
-%:%590=322%:%
-%:%591=323%:%
-%:%592=324%:%
-%:%593=325%:%
-%:%597=327%:%
-%:%601=329%:%
-%:%602=330%:%
-%:%603=331%:%
-%:%607=333%:%
-%:%608=334%:%
-%:%610=336%:%
-%:%611=336%:%
-%:%624=357%:%
-%:%625=358%:%
-%:%626=358%:%
-%:%628=359%:%
-%:%629=360%:%
-%:%630=361%:%
-%:%631=362%:%
-%:%632=363%:%
-%:%633=364%:%
-%:%634=364%:%
-%:%636=365%:%
-%:%637=366%:%
-%:%638=366%:%
-%:%639=367%:%
-%:%640=368%:%
-%:%641=368%:%
-%:%643=369%:%
-%:%644=370%:%
-%:%647=372%:%
-%:%648=373%:%
-%:%650=375%:%
-%:%651=375%:%
-%:%652=376%:%
-%:%653=377%:%
-%:%654=377%:%
-%:%656=377%:%
-%:%660=377%:%
-%:%661=377%:%
-%:%663=378%:%
-%:%664=379%:%
-%:%665=380%:%
-%:%666=381%:%
-%:%667=382%:%
-%:%668=383%:%
-%:%669=384%:%
-%:%679=386%:%
-%:%680=387%:%
-%:%681=388%:%
-%:%684=390%:%
-%:%685=391%:%
-%:%686=392%:%
-%:%687=393%:%
-%:%688=394%:%
-%:%689=395%:%
-%:%692=397%:%
-%:%694=399%:%
-%:%695=399%:%
-%:%696=400%:%
-%:%699=401%:%
-%:%703=401%:%
-%:%704=401%:%
-%:%706=402%:%
-%:%712=402%:%
-%:%715=403%:%
-%:%716=404%:%
-%:%717=404%:%
-%:%718=405%:%
-%:%719=406%:%
-%:%720=407%:%
-%:%721=407%:%
-%:%723=407%:%
-%:%727=407%:%
-%:%728=407%:%
-%:%730=408%:%
-%:%731=409%:%
-%:%732=410%:%
-%:%733=411%:%
-%:%734=412%:%
-%:%744=414%:%
-%:%745=415%:%
-%:%746=416%:%
-%:%747=417%:%
-%:%748=418%:%
-%:%749=419%:%
-%:%750=420%:%
-%:%751=421%:%
-%:%752=422%:%
-%:%756=425%:%
-%:%757=426%:%
-%:%758=427%:%
-%:%759=428%:%
-%:%760=429%:%
-%:%761=430%:%
-%:%762=431%:%
-%:%763=432%:%
-%:%764=433%:%
-%:%765=434%:%
-%:%766=435%:%
-%:%767=436%:%
-%:%776=438%:%
-%:%788=440%:%
-%:%789=441%:%
-%:%790=442%:%
-%:%792=444%:%
-%:%793=444%:%
-%:%794=445%:%
-%:%795=446%:%
-%:%796=447%:%
-%:%797=447%:%
-%:%799=447%:%
-%:%803=447%:%
-%:%804=447%:%
-%:%806=448%:%
-%:%807=449%:%
-%:%808=450%:%
-%:%809=451%:%
-%:%819=453%:%
-%:%820=454%:%
-%:%821=455%:%
-%:%825=457%:%
-%:%827=459%:%
-%:%828=459%:%
-%:%829=460%:%
-%:%830=461%:%
-%:%831=462%:%
-%:%832=462%:%
-%:%834=462%:%
-%:%838=462%:%
-%:%839=462%:%
-%:%841=463%:%
-%:%842=464%:%
-%:%843=465%:%
-%:%844=466%:%
-%:%854=468%:%
-%:%855=469%:%
-%:%857=471%:%
-%:%858=471%:%
-%:%859=472%:%
-%:%860=473%:%
-%:%861=474%:%
-%:%862=474%:%
-%:%864=474%:%
-%:%868=474%:%
-%:%869=474%:%
-%:%871=475%:%
-%:%872=476%:%
-%:%873=477%:%
-%:%874=478%:%
-%:%875=479%:%
-%:%885=481%:%
-%:%886=482%:%
-%:%888=484%:%
-%:%889=484%:%
-%:%890=485%:%
-%:%891=486%:%
-%:%894=487%:%
-%:%898=487%:%
-%:%899=487%:%
-%:%900=487%:%
-%:%909=489%:%
-%:%910=490%:%
-%:%911=491%:%
-%:%912=492%:%
-%:%914=494%:%
-%:%915=494%:%
-%:%916=495%:%
-%:%917=496%:%
-%:%920=497%:%
-%:%924=497%:%
-%:%925=497%:%
-%:%926=497%:%
-%:%935=499%:%
-%:%936=500%:%
-%:%938=502%:%
-%:%939=502%:%
-%:%940=503%:%
-%:%941=504%:%
-%:%942=505%:%
-%:%943=505%:%
-%:%945=505%:%
-%:%949=505%:%
-%:%950=505%:%
-%:%952=506%:%
-%:%953=507%:%
-%:%954=508%:%
-%:%955=509%:%
-%:%965=511%:%
-%:%966=512%:%
-%:%967=513%:%
-%:%968=514%:%
-%:%969=515%:%
-%:%970=516%:%
-%:%972=518%:%
-%:%973=518%:%
-%:%974=519%:%
-%:%975=520%:%
-%:%976=521%:%
-%:%977=522%:%
-%:%978=522%:%
-%:%980=522%:%
-%:%984=522%:%
-%:%985=522%:%
-%:%987=523%:%
-%:%988=524%:%
-%:%989=525%:%
-%:%990=526%:%
-%:%991=527%:%
-%:%992=528%:%
-%:%1002=530%:%
-%:%1003=531%:%
-%:%1004=532%:%
-%:%1005=533%:%
-%:%1006=534%:%
-%:%1007=535%:%
-%:%1009=537%:%
-%:%1010=537%:%
-%:%1011=538%:%
-%:%1012=539%:%
-%:%1015=540%:%
-%:%1019=540%:%
-%:%1020=540%:%
-%:%1022=541%:%
-%:%1032=543%:%
-%:%1033=544%:%
-%:%1035=545%:%
-%:%1036=545%:%
-%:%1037=546%:%
-%:%1038=547%:%
-%:%1039=547%:%
-%:%1041=547%:%
-%:%1045=547%:%
-%:%1046=547%:%
-%:%1048=548%:%
-%:%1049=549%:%
-%:%1050=550%:%
-%:%1051=551%:%
-%:%1052=552%:%
-%:%1075=558%:%
-%:%1076=559%:%
-%:%1077=560%:%
-%:%1078=561%:%
-%:%1087=563%:%
-%:%1099=565%:%
-%:%1100=566%:%
-%:%1101=567%:%
-%:%1102=568%:%
-%:%1106=570%:%
-%:%1107=571%:%
-%:%1109=573%:%
-%:%1110=573%:%
-%:%1111=574%:%
-%:%1112=575%:%
-%:%1113=575%:%
-%:%1114=576%:%
-%:%1117=577%:%
-%:%1121=577%:%
-%:%1122=577%:%
-%:%1123=577%:%
-%:%1125=578%:%
-%:%1126=579%:%
-%:%1136=581%:%
-%:%1137=582%:%
-%:%1138=583%:%
-%:%1139=584%:%
-%:%1140=585%:%
-%:%1141=586%:%
-%:%1142=587%:%
-%:%1143=588%:%
-%:%1144=589%:%
-%:%1145=590%:%
-%:%1146=591%:%
-%:%1147=592%:%
-%:%1148=593%:%
-%:%1149=594%:%
-%:%1150=595%:%
-%:%1152=597%:%
-%:%1153=597%:%
-%:%1154=598%:%
-%:%1155=599%:%
-%:%1156=600%:%
-%:%1157=600%:%
-%:%1159=600%:%
-%:%1163=600%:%
-%:%1164=600%:%
-%:%1166=601%:%
-%:%1167=602%:%
-%:%1168=603%:%
-%:%1169=604%:%
-%:%1170=605%:%
-%:%1171=606%:%
-%:%1181=608%:%
-%:%1182=609%:%
-%:%1183=610%:%
-%:%1184=611%:%
-%:%1188=613%:%
-%:%1189=614%:%
-%:%1190=615%:%
-%:%1192=617%:%
-%:%1193=617%:%
-%:%1194=618%:%
-%:%1195=618%:%
-%:%1197=619%:%
-%:%1198=620%:%
-%:%1199=620%:%
-%:%1200=621%:%
-%:%1201=622%:%
-%:%1202=622%:%
-%:%1203=623%:%
-%:%1206=624%:%
-%:%1210=624%:%
-%:%1211=624%:%
-%:%1213=625%:%
-%:%1214=626%:%
-%:%1215=627%:%
-%:%1225=629%:%
-%:%1226=630%:%
-%:%1227=631%:%
-%:%1228=632%:%
-%:%1230=634%:%
-%:%1231=634%:%
-%:%1232=635%:%
-%:%1234=635%:%
-%:%1238=635%:%
-%:%1239=635%:%
-%:%1241=636%:%
-%:%1249=636%:%
-%:%1250=637%:%
-%:%1251=638%:%
-%:%1252=638%:%
-%:%1253=639%:%
-%:%1255=639%:%
-%:%1259=639%:%
-%:%1260=639%:%
-%:%1262=640%:%
-%:%1272=642%:%
-%:%1273=643%:%
-%:%1274=644%:%
-%:%1282=646%:%
+%:%69=38%:%
+%:%73=40%:%
+%:%74=41%:%
+%:%75=42%:%
+%:%76=43%:%
+%:%77=44%:%
+%:%78=45%:%
+%:%79=46%:%
+%:%80=47%:%
+%:%81=48%:%
+%:%82=49%:%
+%:%83=50%:%
+%:%84=51%:%
+%:%85=52%:%
+%:%86=53%:%
+%:%87=54%:%
+%:%88=55%:%
+%:%89=56%:%
+%:%90=57%:%
+%:%91=58%:%
+%:%92=59%:%
+%:%93=60%:%
+%:%94=61%:%
+%:%95=62%:%
+%:%96=63%:%
+%:%97=64%:%
+%:%98=65%:%
+%:%99=66%:%
+%:%100=67%:%
+%:%101=68%:%
+%:%102=69%:%
+%:%103=70%:%
+%:%104=71%:%
+%:%105=72%:%
+%:%106=73%:%
+%:%107=74%:%
+%:%108=75%:%
+%:%109=76%:%
+%:%110=77%:%
+%:%111=78%:%
+%:%112=79%:%
+%:%113=80%:%
+%:%114=81%:%
+%:%115=82%:%
+%:%116=83%:%
+%:%117=84%:%
+%:%118=85%:%
+%:%119=86%:%
+%:%120=87%:%
+%:%121=88%:%
+%:%122=89%:%
+%:%123=90%:%
+%:%124=91%:%
+%:%159=122%:%
+%:%171=124%:%
+%:%172=125%:%
+%:%173=126%:%
+%:%174=127%:%
+%:%175=128%:%
+%:%184=130%:%
+%:%196=132%:%
+%:%197=133%:%
+%:%198=134%:%
+%:%200=136%:%
+%:%201=136%:%
+%:%202=136%:%
+%:%205=138%:%
+%:%206=139%:%
+%:%207=140%:%
+%:%208=141%:%
+%:%209=142%:%
+%:%211=144%:%
+%:%212=144%:%
+%:%214=145%:%
+%:%215=145%:%
+%:%217=146%:%
+%:%218=147%:%
+%:%221=149%:%
+%:%222=150%:%
+%:%223=151%:%
+%:%224=152%:%
+%:%225=153%:%
+%:%227=155%:%
+%:%228=155%:%
+%:%229=156%:%
+%:%230=157%:%
+%:%231=157%:%
+%:%232=158%:%
+%:%233=159%:%
+%:%234=159%:%
+%:%235=160%:%
+%:%236=161%:%
+%:%237=161%:%
+%:%238=162%:%
+%:%240=164%:%
+%:%241=165%:%
+%:%242=166%:%
+%:%244=168%:%
+%:%245=168%:%
+%:%246=169%:%
+%:%247=170%:%
+%:%248=170%:%
+%:%249=171%:%
+%:%250=174%:%
+%:%253=177%:%
+%:%254=178%:%
+%:%255=179%:%
+%:%256=180%:%
+%:%257=181%:%
+%:%260=183%:%
+%:%263=185%:%
+%:%264=186%:%
+%:%265=187%:%
+%:%266=188%:%
+%:%267=189%:%
+%:%268=190%:%
+%:%270=192%:%
+%:%271=192%:%
+%:%272=193%:%
+%:%273=194%:%
+%:%274=195%:%
+%:%275=195%:%
+%:%277=195%:%
+%:%281=195%:%
+%:%282=195%:%
+%:%284=196%:%
+%:%285=197%:%
+%:%286=198%:%
+%:%287=199%:%
+%:%297=201%:%
+%:%298=202%:%
+%:%299=203%:%
+%:%300=204%:%
+%:%301=205%:%
+%:%302=206%:%
+%:%303=207%:%
+%:%304=208%:%
+%:%305=209%:%
+%:%306=210%:%
+%:%308=212%:%
+%:%309=212%:%
+%:%310=213%:%
+%:%311=214%:%
+%:%312=215%:%
+%:%313=215%:%
+%:%315=215%:%
+%:%319=215%:%
+%:%320=215%:%
+%:%322=216%:%
+%:%323=217%:%
+%:%324=218%:%
+%:%325=219%:%
+%:%335=222%:%
+%:%336=223%:%
+%:%337=224%:%
+%:%338=225%:%
+%:%339=226%:%
+%:%340=227%:%
+%:%341=228%:%
+%:%342=229%:%
+%:%343=230%:%
+%:%345=233%:%
+%:%346=233%:%
+%:%347=234%:%
+%:%348=235%:%
+%:%349=236%:%
+%:%350=236%:%
+%:%352=236%:%
+%:%356=236%:%
+%:%357=236%:%
+%:%359=237%:%
+%:%360=238%:%
+%:%361=239%:%
+%:%362=240%:%
+%:%372=242%:%
+%:%373=243%:%
+%:%374=244%:%
+%:%375=245%:%
+%:%378=247%:%
+%:%381=249%:%
+%:%382=250%:%
+%:%383=251%:%
+%:%384=252%:%
+%:%385=253%:%
+%:%387=255%:%
+%:%388=255%:%
+%:%389=256%:%
+%:%390=257%:%
+%:%391=258%:%
+%:%392=258%:%
+%:%394=258%:%
+%:%398=258%:%
+%:%399=258%:%
+%:%401=259%:%
+%:%402=260%:%
+%:%403=261%:%
+%:%404=262%:%
+%:%414=264%:%
+%:%415=265%:%
+%:%424=270%:%
+%:%436=272%:%
+%:%437=273%:%
+%:%438=274%:%
+%:%439=275%:%
+%:%440=276%:%
+%:%442=277%:%
+%:%443=277%:%
+%:%444=278%:%
+%:%446=279%:%
+%:%447=280%:%
+%:%448=281%:%
+%:%451=283%:%
+%:%453=285%:%
+%:%454=285%:%
+%:%455=286%:%
+%:%456=287%:%
+%:%457=287%:%
+%:%459=287%:%
+%:%463=287%:%
+%:%464=287%:%
+%:%466=288%:%
+%:%467=289%:%
+%:%468=290%:%
+%:%469=291%:%
+%:%470=292%:%
+%:%471=293%:%
+%:%481=295%:%
+%:%483=297%:%
+%:%484=297%:%
+%:%486=299%:%
+%:%488=301%:%
+%:%489=301%:%
+%:%490=301%:%
+%:%492=301%:%
+%:%496=301%:%
+%:%497=301%:%
+%:%499=302%:%
+%:%500=303%:%
+%:%501=304%:%
+%:%502=305%:%
+%:%512=307%:%
+%:%513=308%:%
+%:%514=309%:%
+%:%515=310%:%
+%:%524=313%:%
+%:%536=315%:%
+%:%537=316%:%
+%:%538=317%:%
+%:%539=318%:%
+%:%540=319%:%
+%:%541=320%:%
+%:%542=321%:%
+%:%543=322%:%
+%:%544=323%:%
+%:%548=325%:%
+%:%552=327%:%
+%:%553=328%:%
+%:%554=329%:%
+%:%556=331%:%
+%:%557=331%:%
+%:%559=332%:%
+%:%560=333%:%
+%:%561=334%:%
+%:%562=335%:%
+%:%563=336%:%
+%:%564=337%:%
+%:%565=338%:%
+%:%566=338%:%
+%:%567=339%:%
+%:%568=340%:%
+%:%569=340%:%
+%:%570=341%:%
+%:%573=342%:%
+%:%577=342%:%
+%:%578=342%:%
+%:%580=343%:%
+%:%581=344%:%
+%:%591=346%:%
+%:%592=347%:%
+%:%593=348%:%
+%:%594=349%:%
+%:%595=350%:%
+%:%596=351%:%
+%:%597=352%:%
+%:%598=353%:%
+%:%599=354%:%
+%:%600=355%:%
+%:%601=356%:%
+%:%602=357%:%
+%:%603=358%:%
+%:%604=359%:%
+%:%605=360%:%
+%:%606=361%:%
+%:%607=362%:%
+%:%608=363%:%
+%:%612=365%:%
+%:%613=366%:%
+%:%615=368%:%
+%:%616=368%:%
+%:%618=369%:%
+%:%619=369%:%
+%:%620=370%:%
+%:%621=371%:%
+%:%622=371%:%
+%:%623=372%:%
+%:%626=373%:%
+%:%630=373%:%
+%:%631=373%:%
+%:%632=374%:%
+%:%633=374%:%
+%:%634=375%:%
+%:%635=375%:%
+%:%636=376%:%
+%:%637=376%:%
+%:%638=376%:%
+%:%639=377%:%
+%:%649=379%:%
+%:%650=380%:%
+%:%651=381%:%
+%:%652=382%:%
+%:%656=384%:%
+%:%660=386%:%
+%:%661=387%:%
+%:%662=388%:%
+%:%666=390%:%
+%:%667=391%:%
+%:%669=393%:%
+%:%670=393%:%
+%:%683=414%:%
+%:%684=415%:%
+%:%685=415%:%
+%:%687=416%:%
+%:%688=417%:%
+%:%689=418%:%
+%:%690=419%:%
+%:%691=420%:%
+%:%692=421%:%
+%:%693=421%:%
+%:%695=422%:%
+%:%696=423%:%
+%:%697=423%:%
+%:%698=424%:%
+%:%699=425%:%
+%:%700=425%:%
+%:%702=426%:%
+%:%703=427%:%
+%:%706=429%:%
+%:%707=430%:%
+%:%709=432%:%
+%:%710=432%:%
+%:%711=433%:%
+%:%712=434%:%
+%:%713=434%:%
+%:%715=434%:%
+%:%719=434%:%
+%:%720=434%:%
+%:%722=435%:%
+%:%723=436%:%
+%:%724=437%:%
+%:%725=438%:%
+%:%726=439%:%
+%:%727=440%:%
+%:%728=441%:%
+%:%738=443%:%
+%:%739=444%:%
+%:%740=445%:%
+%:%743=447%:%
+%:%744=448%:%
+%:%745=449%:%
+%:%746=450%:%
+%:%747=451%:%
+%:%748=452%:%
+%:%751=454%:%
+%:%753=456%:%
+%:%754=456%:%
+%:%755=457%:%
+%:%758=458%:%
+%:%762=458%:%
+%:%763=458%:%
+%:%765=459%:%
+%:%771=459%:%
+%:%774=460%:%
+%:%775=461%:%
+%:%776=461%:%
+%:%777=462%:%
+%:%778=463%:%
+%:%779=464%:%
+%:%780=464%:%
+%:%782=464%:%
+%:%786=464%:%
+%:%787=464%:%
+%:%789=465%:%
+%:%790=466%:%
+%:%791=467%:%
+%:%792=468%:%
+%:%793=469%:%
+%:%803=471%:%
+%:%804=472%:%
+%:%805=473%:%
+%:%806=474%:%
+%:%807=475%:%
+%:%808=476%:%
+%:%809=477%:%
+%:%810=478%:%
+%:%811=479%:%
+%:%815=482%:%
+%:%816=483%:%
+%:%817=484%:%
+%:%818=485%:%
+%:%819=486%:%
+%:%820=487%:%
+%:%821=488%:%
+%:%822=489%:%
+%:%823=490%:%
+%:%824=491%:%
+%:%825=492%:%
+%:%826=493%:%
+%:%835=495%:%
+%:%847=497%:%
+%:%848=498%:%
+%:%849=499%:%
+%:%851=501%:%
+%:%852=501%:%
+%:%853=502%:%
+%:%854=503%:%
+%:%855=504%:%
+%:%856=504%:%
+%:%858=504%:%
+%:%862=504%:%
+%:%863=504%:%
+%:%865=505%:%
+%:%866=506%:%
+%:%867=507%:%
+%:%868=508%:%
+%:%878=510%:%
+%:%879=511%:%
+%:%880=512%:%
+%:%884=514%:%
+%:%886=516%:%
+%:%887=516%:%
+%:%888=517%:%
+%:%889=518%:%
+%:%890=519%:%
+%:%891=519%:%
+%:%893=519%:%
+%:%897=519%:%
+%:%898=519%:%
+%:%900=520%:%
+%:%901=521%:%
+%:%902=522%:%
+%:%903=523%:%
+%:%913=525%:%
+%:%914=526%:%
+%:%916=528%:%
+%:%917=528%:%
+%:%918=529%:%
+%:%919=530%:%
+%:%920=531%:%
+%:%921=531%:%
+%:%923=531%:%
+%:%927=531%:%
+%:%928=531%:%
+%:%930=532%:%
+%:%931=533%:%
+%:%932=534%:%
+%:%933=535%:%
+%:%934=536%:%
+%:%944=538%:%
+%:%945=539%:%
+%:%947=541%:%
+%:%948=541%:%
+%:%949=542%:%
+%:%950=543%:%
+%:%953=544%:%
+%:%957=544%:%
+%:%958=544%:%
+%:%959=544%:%
+%:%968=546%:%
+%:%969=547%:%
+%:%970=548%:%
+%:%971=549%:%
+%:%973=551%:%
+%:%974=551%:%
+%:%975=552%:%
+%:%976=553%:%
+%:%979=554%:%
+%:%983=554%:%
+%:%984=554%:%
+%:%985=554%:%
+%:%994=556%:%
+%:%995=557%:%
+%:%997=559%:%
+%:%998=559%:%
+%:%999=560%:%
+%:%1000=561%:%
+%:%1001=562%:%
+%:%1002=562%:%
+%:%1004=562%:%
+%:%1008=562%:%
+%:%1009=562%:%
+%:%1011=563%:%
+%:%1012=564%:%
+%:%1013=565%:%
+%:%1014=566%:%
+%:%1024=568%:%
+%:%1025=569%:%
+%:%1026=570%:%
+%:%1027=571%:%
+%:%1028=572%:%
+%:%1029=573%:%
+%:%1031=575%:%
+%:%1032=575%:%
+%:%1033=576%:%
+%:%1034=577%:%
+%:%1035=578%:%
+%:%1036=579%:%
+%:%1037=579%:%
+%:%1039=579%:%
+%:%1043=579%:%
+%:%1044=579%:%
+%:%1046=580%:%
+%:%1047=581%:%
+%:%1048=582%:%
+%:%1049=583%:%
+%:%1050=584%:%
+%:%1051=585%:%
+%:%1061=587%:%
+%:%1062=588%:%
+%:%1063=589%:%
+%:%1064=590%:%
+%:%1065=591%:%
+%:%1066=592%:%
+%:%1068=594%:%
+%:%1069=594%:%
+%:%1070=595%:%
+%:%1071=596%:%
+%:%1074=597%:%
+%:%1078=597%:%
+%:%1079=597%:%
+%:%1081=598%:%
+%:%1091=600%:%
+%:%1092=601%:%
+%:%1094=602%:%
+%:%1095=602%:%
+%:%1096=603%:%
+%:%1097=604%:%
+%:%1098=604%:%
+%:%1100=604%:%
+%:%1104=604%:%
+%:%1105=604%:%
+%:%1107=605%:%
+%:%1108=606%:%
+%:%1109=607%:%
+%:%1110=608%:%
+%:%1111=609%:%
+%:%1134=615%:%
+%:%1135=616%:%
+%:%1136=617%:%
+%:%1137=618%:%
+%:%1146=620%:%
+%:%1158=622%:%
+%:%1159=623%:%
+%:%1160=624%:%
+%:%1161=625%:%
+%:%1165=627%:%
+%:%1166=628%:%
+%:%1168=630%:%
+%:%1169=630%:%
+%:%1170=631%:%
+%:%1171=632%:%
+%:%1172=632%:%
+%:%1173=633%:%
+%:%1176=634%:%
+%:%1180=634%:%
+%:%1181=634%:%
+%:%1182=634%:%
+%:%1184=635%:%
+%:%1185=636%:%
+%:%1195=638%:%
+%:%1196=639%:%
+%:%1197=640%:%
+%:%1198=641%:%
+%:%1199=642%:%
+%:%1200=643%:%
+%:%1201=644%:%
+%:%1202=645%:%
+%:%1203=646%:%
+%:%1204=647%:%
+%:%1205=648%:%
+%:%1206=649%:%
+%:%1207=650%:%
+%:%1208=651%:%
+%:%1209=652%:%
+%:%1211=654%:%
+%:%1212=654%:%
+%:%1213=655%:%
+%:%1214=656%:%
+%:%1215=657%:%
+%:%1216=657%:%
+%:%1218=657%:%
+%:%1222=657%:%
+%:%1223=657%:%
+%:%1225=658%:%
+%:%1226=659%:%
+%:%1227=660%:%
+%:%1228=661%:%
+%:%1229=662%:%
+%:%1230=663%:%
+%:%1240=665%:%
+%:%1241=666%:%
+%:%1242=667%:%
+%:%1243=668%:%
+%:%1247=670%:%
+%:%1248=671%:%
+%:%1249=672%:%
+%:%1251=674%:%
+%:%1252=674%:%
+%:%1253=675%:%
+%:%1254=675%:%
+%:%1256=676%:%
+%:%1257=677%:%
+%:%1258=677%:%
+%:%1259=678%:%
+%:%1260=679%:%
+%:%1261=679%:%
+%:%1262=680%:%
+%:%1265=681%:%
+%:%1269=681%:%
+%:%1270=681%:%
+%:%1272=682%:%
+%:%1273=683%:%
+%:%1274=684%:%
+%:%1284=686%:%
+%:%1285=687%:%
+%:%1286=688%:%
+%:%1287=689%:%
+%:%1289=691%:%
+%:%1290=691%:%
+%:%1291=692%:%
+%:%1293=692%:%
+%:%1297=692%:%
+%:%1298=692%:%
+%:%1300=693%:%
+%:%1308=693%:%
+%:%1309=694%:%
+%:%1310=695%:%
+%:%1311=695%:%
+%:%1312=696%:%
+%:%1314=696%:%
+%:%1318=696%:%
+%:%1319=696%:%
+%:%1321=697%:%
+%:%1331=699%:%
+%:%1332=700%:%
+%:%1333=701%:%
+%:%1341=703%:%

### 2022-02-22 paper/output/document/appendix_2.tex
chaper 5 cleaned

@@
 \endisadelimproof
-\isanewline
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsection{Ethics for Ordinary People \label{ordinaryhumans}%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
+Ethics has immediate bearing on everyone’s lives because it studies the unavoidable question: 
+how should we live? If computers can make this study more efficient, then it seems that everyone should
+engage in computational ethics. As Cornel West says, the ethical question is the only question that 
+we answer merely by living. To turn away from ethics is to take a stance on the question of how to 
+live (namely, to live unreflectively) and thus to engage in ethics. Ethical truths are valuable because 
+they tell us how to live. Every rational being must decide how to navigate the world and ethical 
+truths answer these questions. If the results of ethical study is practically valuable, then automated 
+ethics is good because computational tools can help us locate ethical prescriptions and theories more efficiently. 
+In the most extreme case, we can unthinkingly follow the commands of an ethical calculator that dictates 
+how we should live. Computers can answer the unavoidable question for us.
+
+Placing the value of ethics solely in its action-guiding potential fails to take into account the 
+importance of practical reason, which, as I argued in Section Why Kant, is the source
+of freedom itself. 
+We are committed to ethical reflection because of the kind of beings that we are. Recall that Korsgaard 
+argues that, as beings occupying minds with a reflective structure, when faced with a choice, “it is as if there 
+were something over and above all of your desires, something that is you, and that chooses which desire 
+to act on” (Sources 83). This choosing is the operation of practical reason, and this reflection
+makes us free. We are free because we must choose which reasons to act on. Every decision that we 
+make is an exercise of freedom.
+
+If reflecting makes us free, then unthinkingly obeying the computer sacrifices our autonomy. Consider 
+the thought experiment of an Ethics Oracle that can unfailingly tell you the right thing to do in any 
+situation.\footnote{This example is inspired by the Pocket Oracle presented in \citet{bok}.} Someone 
+who surrenders themselves to this Oracle unthinkingly follows its prescriptions. 
+There is some reflection involved in the decision to obey each of the Oracle’s prescriptions, but 
+this is a thin kind of reflection \citep{bok}. This person is not reflecting on the real matters at hand and is 
+not making decisions for themselves. They have surrendered their reflective capacity to the Oracle. 
+They live a worse life than someone who reflects on their actions; they have less ownership over their 
+actions than the reflective person. In a less extreme case, a person may retain control of many of 
+their decisions but cede some important or tricky choices to the Ethics Oracle. Because every single 
+exercise of practical reason is an exercise of autonomy, this person is still less autonomous than the 
+purely reflective person. Even surrendering simple, inconsequential decisions such as which flavor of 
+coffee to drink surrenders some piece of our autonomy. Perhaps in trivial cases we can accept that 
+tiny sacrifice in autonomy, but giving over life-changing decisions to the machine sacrifices our 
+core freedom. Unreflectively relying on computational ethics surrenders our autonomy to the machine.
+
+One objection to this emphasis on reflection is the impracticality of making ethical calculations from first principles 
+every time we are faced with a decision. This is why we follow the advice of moral mentors, like our 
+family or influential philosophers. These moral mentors differ from the Ethics Oracle because their advice 
+comes with an argument justifying it; if human-computer symbiotic computational ethics also prompts 
+reflection on the prescriptions given, it can also guide action without sacrificing autonomy.
+Most people do not reason about ethics during everyday decisions; they rely on some combination of 
+prior knowledge and external testimony. For example, my mother taught me to respect myself, and I 
+follow her advice. What is the difference between following the guidance of a moral educator and 
+obeying the Ethics Oracle? The best kind of ethical advice prompts reflection, such as an argument 
+made in a philosophy paper. Unthinkingly following someone’s advice results in the same loss of 
+autonomy as unthinkingly obeying the Ethics Oracle; people who merely obey orders are less autonomous 
+than those who think for themselves.\footnote{This might be worrying....does this mean that soldiers who are
+following orders to commit atrocities are less responsible than those giving the orders? Wait 
+maybe that's true.} This account of moral advice offers a model for human-computer 
+symbiotic ethics. The computer should serve as a moral guide by providing arguments, just as my mom 
+explained why I should always respect myself. Human-computer symbiotic 
+ethics nurtures autonomy when it not only offers prescriptions for action, but also explanations for 
+these prescriptions. Because my theorem-prover-based computational ethical system is explainable, it can 
+guide action without sacrificing autonomy. It can make an argument for some action, instead of 
+merely giving a verdict. Isabelle can list the facts used to show
+a partcular action prohibited, and a human being can reflect on whether or not these principles
+indeed prohibit the action in question. The computer serves as a collaborator and a tool, but not as an authority, 
+so the human being’s reflective capacity and freedom is preserved.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsection{Academic Ethics \label{academicphilosophy}%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
+There are two potential sources of the value of academic philosophy: the ethical truths uncovered and 
+the process of a philosopher discovering these truths. Under the first view, academic philosophy is 
+valuable because it facilitates the discovery of new ethical theories. If truths are valuable and 
+computers can generate truths more efficiently than humans, then ethics should be fully automated. 
+Ethical disputes often linger unresolved indefinitely, but every now and then, 
+a theory emerges as a new classic, such as Rawls’ veil of ignorance. Some academic philosophy also 
+impacts social phenomena, like Locke’s impact on global democracy. Academic philosophy often works its 
+way into household ethics, as seen in the impact of critical race theory. This view parallels the 
+view that ordinary ethics is valuable for its insights alone, and thus
+similarly implies that totally automated ethics is not only permissible, but also desirable. If 
+ethical truths are important for their impact on society, this value is not contingent on whether a 
+human or a computer produced these truths. If possible, computers should produce ethical theories 
+to maximize these truths’ value for society.
+
+Another set of theories locates the value of academic ethics in the process itself and thus requires 
+human-computer symbiosis. Just as mathematics is fun and creative for the mathematician, so is ethics 
+for the philosopher. Many philosophers enjoy reading and writing philosophy papers. The study of 
+philosophy builds critical thinking skills and makes philosophers more reflective. Computational ethics 
+doesn’t necessarily sacrifice any of these benefits. These 
+benefits would be lost by fully automated ethics, but human-computer symbiotic ethics amplifies them. 
+If a computer functions like a tool in the process of philosophical discovery, like a conversation 
+with a colleague or a search for counterexamples, then it preserves the joy of philosophy. Moreover, 
+computational ethics amplifies this joy by forcing ethicists to make their ideas more precise, a major 
+goal of academic philosophy. The rigid syntax of a computer program demands much more precision than a 
+conversation or a paper. Computational tools also offer ethicists new perspective by forcing a return to 
+first, formal principles often avoided in ordinary philosophical inquiry. Formal ethics has been a 
+subject of interest among ethicists, but the logical background necessary has prevented the field 
+from taking off. If computers can automate away the tedium of formal ethics, then this precision 
+will be accessible to all ethicists, not just logicians. Such work has begun in metaphysics, and 
+recent research used computational tools to find an inconsistency in Godel’s ontological argument 
+for the existence of God \citep{godelincon}. The power of computational tools to force precision, perform 
+consistency checks, and make assumptions explicit means that computers can serve as tools to 
+help philosophers perform philosophy better.
+
+If ethical truths offer some value to society at-large, perhaps we cannot sacrifice this value merely 
+to preserve human philosophers’ fun. A more compelling argument against fully automated 
+ethics is that the existence of human academic philosophers offers value even to non-philosophers. 
+People derive joy and wonder from knowing that human beings produced great ethics. Plato’s \emph{Apology} 
+is not only a profound and insightful text, but it is also wonderous that a human being produced such 
+a work. We derive joy from knowing that our fellow humans are capable of the kind of thought that 
+great philosophers accomplish, just as an unimaginably beautiful work of art is more wonderous 
+because a human being painted it. We watch the Olympics because we derive wonder and joy from human 
+excellence. Even when admiring computational achievements, such as Google’s recent success in protein 
+folding, we admire the human who programmed the machine, not the machine itself. We can relate to 
+humans, so the mere knowledge that great people are doing great things enriches our lives. This 
+knowledge is part of the attraction for the thousands of tourists who visit Harvard Yard every year; 
+this is a place where of great human achievement.\footnote{Is this too like, yay Harvard}
+
+An even stronger argument for human-computer symbiotic ethics instead of fully automated ethics is 
+that ethics is an inherently human subject. We study ethics because, as argued above, we 
+have no choice but to reflect on how to live. Because reflection is such a fundamental part of being 
+human, a world in which all ethical inquiry is automated is undesirable. Academic philosophers are 
+professional reflectors who are partners in the human experience with us, so their ethical inquiry 
+carries unique weight. They teach us, inspire us, and serve as examples of the kind of reflection 
+that is constitutive of being human. Moreover, an ethical theory produced entirely by a computer is, 
+at best, a secondary perspective; it is a computer’s attempt to describe how human beings should live. 
+Without a human component, it cannot serve as a rich and sophisticated guide for humans. If ethics is 
+most meaningful when it is the product of human reflection, totally automated ethics destroys the field 
+entirely but human-computer symbiosis does not. Human beings should debate the most pressing questions 
+of human existence, and computers can serve as our aids. Thus, computational tools must supplement 
+human ethical reasoning but cannot replace it.%
+\end{isamarkuptext}\isamarkuptrue%
 %
 \isadelimtheory
-\isanewline
 %
@@
 %:%292=172%:%
-%:%300=173%:%
-%:%303=174%:%
-%:%308=175%:%
+%:%307=175%:%
+%:%319=177%:%
+%:%320=178%:%
+%:%321=179%:%
+%:%322=180%:%
+%:%323=181%:%
+%:%324=182%:%
+%:%325=183%:%
+%:%326=184%:%
+%:%327=185%:%
+%:%328=186%:%
+%:%329=187%:%
+%:%330=188%:%
+%:%331=189%:%
+%:%332=190%:%
+%:%333=191%:%
+%:%334=192%:%
+%:%335=193%:%
+%:%336=194%:%
+%:%337=195%:%
+%:%338=196%:%
+%:%339=197%:%
+%:%340=198%:%
+%:%341=199%:%
+%:%342=200%:%
+%:%343=201%:%
+%:%344=202%:%
+%:%345=203%:%
+%:%346=204%:%
+%:%347=205%:%
+%:%348=206%:%
+%:%349=207%:%
+%:%350=208%:%
+%:%351=209%:%
+%:%352=210%:%
+%:%353=211%:%
+%:%354=212%:%
+%:%355=213%:%
+%:%356=214%:%
+%:%357=215%:%
+%:%358=216%:%
+%:%359=217%:%
+%:%360=218%:%
+%:%361=219%:%
+%:%362=220%:%
+%:%363=221%:%
+%:%364=222%:%
+%:%365=223%:%
+%:%366=224%:%
+%:%367=225%:%
+%:%368=226%:%
+%:%369=227%:%
+%:%370=228%:%
+%:%371=229%:%
+%:%372=230%:%
+%:%373=231%:%
+%:%374=232%:%
+%:%375=233%:%
+%:%376=234%:%
+%:%377=235%:%
+%:%378=236%:%
+%:%387=239%:%
+%:%399=242%:%
+%:%400=243%:%
+%:%401=244%:%
+%:%402=245%:%
+%:%403=246%:%
+%:%404=247%:%
+%:%405=248%:%
+%:%406=249%:%
+%:%407=250%:%
+%:%408=251%:%
+%:%409=252%:%
+%:%410=253%:%
+%:%411=254%:%
+%:%412=255%:%
+%:%413=256%:%
+%:%414=257%:%
+%:%415=258%:%
+%:%416=259%:%
+%:%417=260%:%
+%:%418=261%:%
+%:%419=262%:%
+%:%420=263%:%
+%:%421=264%:%
+%:%422=265%:%
+%:%423=266%:%
+%:%424=267%:%
+%:%425=268%:%
+%:%426=269%:%
+%:%427=270%:%
+%:%428=271%:%
+%:%429=272%:%
+%:%430=273%:%
+%:%431=274%:%
+%:%432=275%:%
+%:%433=276%:%
+%:%434=277%:%
+%:%435=278%:%
+%:%436=279%:%
+%:%437=280%:%
+%:%438=281%:%
+%:%439=282%:%
+%:%440=283%:%
+%:%441=284%:%
+%:%442=285%:%
+%:%443=286%:%
+%:%444=287%:%
+%:%445=288%:%
+%:%446=289%:%
+%:%447=290%:%
+%:%448=291%:%
+%:%449=292%:%
+%:%450=293%:%
+%:%451=294%:%
+%:%452=295%:%
+%:%453=296%:%
+%:%454=297%:%
+%:%455=298%:%
+%:%456=299%:%
+%:%457=300%:%
+%:%458=301%:%
+%:%459=302%:%
+%:%467=307%:%

### 2022-02-22 paper/output/document/thesis_5_discussion.tex
chaper 5 cleaned

@@
 %
-\isamarkupsubsection{Automated Moral Agents in Practice \label{aiethics}%
+\isamarkupsubsection{Automated Moral Agents in Practice \label{AIethics}%
 }
@@
 In Chapter \ref{applications}, I demonstrated that my system is capable of performing sophisticated,
-nuanced ethical reasoning. In this section and Section \label{computationalethics}, I outline how my
-system could be used by AI agents and by human philosophers. My work on automating the categorical imperative 
+nuanced ethical reasoning. In this section, I outline the additional components necessary for my system
+to guide AI agents. My work on automating the categorical imperative 
 could serve as one component of a partially or fully artificial ethical reasoner, or an ``ethical AI.''
-Specifically, my system could be a categorical imperative library that takes as input the logical representation 
+Specifically, my system is a categorical imperative library that takes as input the logical representation 
 of a maxim and returns its moral status (if it is obligatory, prohibited, or permissible).
-
 As it stands, my project can evaluate the moral status of maxims represented in my logic and potentially 
@@
 For example, my system could be combined with an input parser to translate moral dilemmas as represented 
-to the AI agent into maxims in my logic. The ouput of my system could be fed into an output 
-parser to translate this output into a prescription for the action the AI agent should take.
-Figure \ref{fig:AIengine} depicts the workflow of this example ethics engine.%
+to the AI agent into maxims in my logic. An output parser could translate my system's output
+into a prescription for action that the AI agent could act on. Figure \ref{fig:AIengine} depicts the 
+workflow of this example ethics engine.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \centering
-\includegraphics[scale=0.4]{AI_engine.png}
+\includegraphics[scale=0.5]{AI_engine.png}
 \caption{An example of an ethics engine for an artificial agent, which begins with a moral dilemma, 
@@
 library (the moral status of the maxim as obligatory, prohibited, or permissible) to a prescription for
-action that the AI agent can act on. In order for my system to be used in an AI agent using the workflow
-above, future work would need to develop such input and output parsers.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
+action. In order for my system to be used in an AI agent using the workflow
+above, future work would need to develop such input and output parsers.
+
 The input parser must translate a complex real-world situation into a flat, logical representation.
 This requires that the input parser determine which circumstances are ``morally relevant''
-for a maxim, a controversial judgement that requires commonsense reasoning.
-There is robust debate in the literature on which circumstances should be considered when formulating a maxim. 
-Some critics of Kant raise the ``tailoring objection,'' which is the worry that arbitrarily specific 
+for a maxim, a controversial judgement.
+There is robust debate in the literature on the circumstances that should be considered when formulating a maxim, 
+inspired by a common objection to Kantian ethics. The``tailoring objection'' is the worry that arbitrarily specific 
 circumstances render any maxim universalizable. For example, the maxim ``When my name is Lavanya Singh 
@@
 someone in order to take their job.'' The circumstances of being unemployed clearly have some bearing on the moral
-relevance of the murder in question; they speak to the motivation for the murder. While this view 
-tracks how we actually perform moral reasoning, it raises the question of how we can determine
+relevance of the murder in question; they speak to the motivation for the murder.
+
+While this view has intuitive appeal, it raises the question of how we can determine
 which circumstances are morally relevant. O'Niell answers this question by noting that the Formula of Universal Law is 
@@
 for an agent to decide how they should behave, not for a third-party to judge their behavior. Ethics is 
-a personal process for Kant, so the FUL is designed to help agents internally make decisions, not to 
-judge others' decisions. Because agents use the FUL to evaluate their own behavior, the test is at its 
+a personal proces and the FUL is designed to help agents internally make decisions. Because agents use 
+the FUL to evaluate their own behavior, the test is at its 
 best when they make a good faith effort to isolate the \emph{principle} of their action, rather than some
@@
 is universally consistent, so it is most effective when an agent accurately formulates the principle
-they act on. Circumstances are morally relevant if they accurately reflect the way that the agent is 
+they act on. Circumstances are morally relevant if they reflect the way that the agent is 
 thinking about their own action. In the example above, the circumstance of wearing a purple shirt doesn't reflect
-the principle of the liar's action. Its inclusion is clearly a disingenous attempt to evade the universalizability
+the principle of the liar's action. Its inclusion is a disingenous attempt to evade the universalizability
 test, but because the FUL is a test of personal integrity, it cannot withstand this kind of mental
@@
 morally relevant circumstances, the challenge remains open for automated ethics. In order for an automated
-ethical agent to use the categorical imperative to its fullest extent, the input maxim fed into
-my system or any automation of the FUL must be a good-faith attempt to capture the agent's principle
+ethical agent to use the categorical imperative to its fullest extent, the input maxim must be a good-faith 
+attempt to capture the agent's principle
 of action. However an action is turned into a maxim for my system to process, whether manually as I did
 in Chapter \ref{applications} or using an automatic input parser, this transformation must be a good-faith 
-attempt to capture the principle of action.
-
-Translating everyday situations into appropriate maxims is the bulk of the work that a Kantian human 
+attempt to capture the principle of action. Translating everyday situations into appropriate maxims is 
+the bulk of the work that a Kantian human 
 being does when making decisions. Common misconceptions about Kantian ethics\footnote{For example, critics 
@@
 imperative would prescribe. For proponents of the ``human-in-the-loop'' model of AI ethics, in which 
-ethical AI requires that humans guide machines \cite{loop}, this kind of human involvement may be a feature.
+ethical AI requires that humans guide machines \citep{loop}, this kind of human involvement may be a feature.
 The outcome of the universalizability test will depend on how the human formulates the maxim; if the 
@@
 agents will exist. Even if developing this kind of AI is irresponsible,
-such developments are likely and will require ethics engines, or risk no consideration of ethics at all. Even if 
-AI without human supervision is scary, such AI with automated ethics is better than such AI without. 
-In such a world, the input parser in my ethics engine would have to be automated. This would require 
-that the parser translate the AI agent's internal representation to the appropriate logical representation. 
-It is likely that, just as different implementations of automated ethics choose 
+such developments are likely and will require ethics engines, or risk no consideration of ethics at all.
+In such a world, the input parser in my ethics engine would have to be automated.
+It is likely that, just as implementations of automated ethics choose 
 a particular ethical theory and implement it, different implementations of such an input parser would 
-adopt different interpretations of commonsense reasoning and morally relevant circumstances.
-
-These interpretations of commonsense reasonining could inspire heuristics to classify circumstances as morally 
+adopt different interpretations of maxim formulation and morally relevant circumstances.
+
+These interpretations could inspire heuristics to classify circumstances as morally 
 relevant. For example, one such attempt could define a moral closeness relation between an action, a 
@@
 sophisticated ethical reasoning faithful to philosophical literature. This represents an improvement 
-over existing AI ethics, which rarely attempts to capture the complexity 
+over existing AI ethics, which rarely captures the complexity 
 of any ethical theory that philosophers plausibly defend.%
@@
 \begin{isamarkuptext}%
-Above I explained how my system offers a mechanism for humans to build ethical AI agents. I also 
-argue that computational ethics is a mechanism for computers to help humans think differently about 
-philosophy. Just as theorem provers make mathematics more efficient and push mathematicians to think 
-precisely about the phenomena they model, computational ethics can help philosophers think more precisely about 
-philosophy. Below I share an example of the kind of philosophical insight that computational ethics 
-can prompt and analyze the value that this tool offers to philosophers.%
+In addition to guiding AI agents, automated ethics can also help human beings make philosophical
+progress. Just as theorem provers make mathematics more efficient and push mathematicians to think 
+precisely about the phenomena they model, computational ethics can help philosophers ask and answer
+new philosophical questions. In this section, I share an example of the kind of philosophical insight that computational ethics 
+can prompt and analyze the value that this tool can offer to philosophers.\footnote{Some may wonder if my system
+could also help ordinary people perform ethical reasoning, not just academic philosophers. I address the role that 
+my system should play in ordinary ethical reasoning in Appendix \ref{ordinaryhumans} and conclude
+that large parts of ordinary ethical inquiry cannot and should not be automated.}%
 \end{isamarkuptext}\isamarkuptrue%
@@
 As presented in Section \ref{formalizingful}, in the process of developing my formalization of
-the FUL, I discovered the certain kinds of maxims are badly formed, or inappropriate inputs to the 
+the FUL, I discovered that certain kinds of maxims are badly formed, or inappropriate inputs to the 
 universalizability test. The FUL is consistent only if it holds for ``well-formed maxims,''
@@
 a circumstance, act, goal tuple (c, a, g) is well-formed if $(\neg (c \longrightarrow a) ) \wedge 
-(\neg(c \longrightarrow g))$.
+(\neg(c \longrightarrow g))$. The insight that the FUL should not apply to badly-formed maxims has 
+philosophical value and serves as evidence of the potential of computational ethics.
 
@@
 
-Isabelle showed that the FUL can only hold for well-formed maxims logically, and I returned to Kantian
+Isabelle gave a logical argument for why the FUL can only hold for well-formed maxims, and I return to Kantian
 literature to better understand the philosophical implications of this idea. Because badly-formed maxims
 neither change an agent's behavior nor generate meaningful obligations, they are not the right kinds of 
-actions for practical reasoners to wonder about. They cannot be action-guiding and are thus not the kind of problem that 
+actions for practical reasoners to make moral judgements about. They cannot be action-guiding and are thus not the kind of problem that 
 ethics should be concerned with. Moreover, under the Kantian account of the will, the very act of asking 
@@
 Consider the example badly-formed maxim, ``When eating breakfast, I will eat breakfast in order to 
-eat breakfast.'' This maxim isn't clearly obligatory or prohibited, but there is something empty about 
-it. Acting on this maxim could never result in any action. If an agent adopts this maxim, 
+eat breakfast.'' There is something empty about this maxim because acting on it could never result in 
+any action. If an agent adopts this maxim, 
 they decide that, in the circumstances ``eating breakfast'' they will perform the act ``eating breakfast''
@@
 already been performed! Adopting this maxim as a law to live by does not change how you live. If you adopt 
-this maxim, when you are eating breakfast, you eat breakfast, but this statement is already tautologically true.
+this maxim, then when you are eating breakfast, you eat breakfast, but this statement is already tautologically true.
 
@@
 what we should do. A practical reasoner asks moral questions not as a mental puzzle or out of curiosity, but 
-in order to decide how to act. A badly-formed maxim can never be action-guiding because it prescribes no new
-actions or obligations. It is not the kind of maxim that a practical reasoner should consider, because it
-will have no bearing on what the agent should do. There is no explicit prohibition against a badly-formed maxim 
-like the breakfast example above, but it is the wrong kind of question for a practical reasoner to ask.
+to decide how to act. A badly-formed maxim is not the kind of maxim that a practical reasoner should consider, because it
+will have no bearing on what the agent should do. It makes no sense of ask, ``Should I act on a badly-formed
+maxim?'' because the answer to this question cannot change your behavior. There is no explicit prohibition 
+against a badly-formed maxim, but it is the wrong kind of question for a practical reasoner to ask.
 
@@
 law—so the question, ``should I be willing this?'' is paradoxical. Either you haven't actually made 
-the maxim your law (and thus haven't yet committed yourself to it), or you aren't actually asking 
+the maxim your law (and thus haven't yet committed to it), or you aren't actually asking 
 the question (because the decision has already been made). Because a maxim is a law that you give to 
-yourself, you cannot question it absent a sufficient reason (such as a change in the circumstances). 
+yourself, you cannot question it absent a sufficient reason, such as a change in the circumstances. 
 To question a law arbitrarily is to not regard it as a law at all. This kind of questioning amounts to 
@@
 Under one reading of this maxim, ``I should just dance'' is referring to a different act than the 
-circumstance ``when dancing''. The circumstance ``when dancing'' refers 
+circumstance ``when dancing.'' The circumstance ``when dancing'' refers 
 to rythmically moving your body to music, but ``I should just dance'' refers to dancing without anxiety, 
@@
 dancing, I should abandon my anxiety and focus on dancing for the sake of dancing.'' This maxim when so 
-modified is not vacuous at all—abandoning anxiety and focusing on dancing is an entirely different act 
-from moving your body rythmically to music. This maxim is actually well-formed, and thus doesn't
-pose a problem for my argument. It is entirely plausible to tell yourself ``When I am dancing, I should focus 
-on dancing for the sake of dancing itself.'' The circumstances do not entail the act or the goal because 
+modified is not badly-formed at all—abandoning anxiety and focusing on dancing is an entirely different act 
+from moving your body rythmically to music. The circumstances do not entail the act or the goal because 
 they refer to different meanings of the word dancing. Any valid reading of this maxim will have the structure above, 
 in which the act is actually different from the circumstances. A reasoner cannot accept their will 
-as law-giving or commit themselves to an act and simultaneously question the act. Either they must be 
+as law-giving, or commit themselves to an act, and simultaneously question the act. Either they must be 
 questioning a different act or they must have recieved new information to prompt the questioning, 
@@
 
-The idea that we cannot even evaluate, let alone will badly formed maxims has implications for 
-self-doubt and self-respect. The dancing maxim can be read using the lens of self-doubt. Under this 
+The idea that we cannot even evaluate, let alone will, badly-formed maxims has implications for debates about 
+self-doubt and self-respect. The dancing maxim can be read as an expression of self-doubt. Under this 
 reading, the question ``When I am dancing, should I be dancing for the sake of dancing?'' is the agent asking, 
@@
 next moment, but is expressing doubt about the moral validity of their behavior at this current moment. 
-I do not argue that self-doubt always undermines the will—after all, self-doubt plays an 
-important role in moral reasoning and is often the mark of a thoughtful agent. I argue instead 
+Self-doubt does not always undermine the will—after all, self-doubt plays an 
+important role in moral reasoning and is often the mark of a thoughtful agent. Instead, I argue 
 that questions of self-doubt do not actually involve badly-formed maxims, for these are not the maxims 
-that the agent is doubting. This example demonstrates that the tension between self-doubt and self-respect 
+that the agent is doubting. This example will demonstrate that the tension between self-doubt and self-respect 
 arises from a mistaken characterization of questions of self-doubt as questions about badly-formed maxims.
@@
 value of self-doubt, in moderation. Christensen presents the ``principle of self-respect,'' which requires 
-that any rational agent refrain from believing that they have mistaken beliefs \cite[4]{christensen}. For example, I cannot 
-rationally both believe that the sky is blue and believe that I believe that the sky is green. In other words, I cannot 
-disapprove of my own credences. Christensen argues that this principle, which he abbreviates to SR, holds because 
+that a rational agent refrain from believing that they have mistaken beliefs \cite[4]{christensen}. For example, I cannot 
+rationally believe both that the sky is blue and that I believe that the sky is green. In other words, I cannot 
+disapprove of my own credences, since if I do disapprove of them, I would just abandon them. Christensen 
+argues that this principle, which he abbreviates to SR, holds because 
 a perfectly rational agent can make accurate and confident judgements about what they believe. If this 
@@
 
-While most philosophers accept some version of SR\footnote{Christensen cites \citet{vanfraaseen}, 
+While most philosophers accept some version of SR\footnote{Christensen cites \citet{vanfraasen}, 
 \citet{vickers}, and \citet{koons}.}, 
@@
 badly-formed maxim, it cannot be the maxim that she is questioning, for adopting
-this maxim could not have changed her behavior at all. Sara is asking a question about her actions and 
-their validity. Any conclusions about the validity of a badly-formed maxim would not help her, first because 
-the maxim has no effect on her action, and second because any such validity would be a foregone conclusion
+this maxim could not have changed her behavior at all. Sara is wondering if her behavior is permissible, but
+any conclusions about the permissibility of a badly-formed maxim would not help her. This is because 
+the maxim has no effect on her action and because any such permissibility would be a foregone conclusion,
 since she has already adopted the maxim. Thus, under the interpretation of self-doubt as a badly-formed 
 maxim, the tension between ESR and ethical self-doubt seems irresolvable. Those committed to this 
-interpretation must abandon one principle or the other.
+interpretation must abandon one principle or the other, since committing and questioning are incompatible.
 
@@
 \begin{isamarkuptext}%
-The philosophical insight above is an example of the kind of philosophical progress that can be 
+The insight above is an example of the kind of philosophical progress that can be 
 made using computational tools and serves as evidence for the power of computational ethics. The 
@@
 Philosophers usually assume that we are not discussing badly-formed maxims because, as argued above, 
-they are not the kind of thing that is usually useful to study. Computational tools like Isabelle
+they are not the kind of thing that is immediately relevant to ethics. Computational tools like Isabelle
 require that assumptions like the exclusion of well-formed maxims are made precise, and thus force 
@@
 to reach with computational tools. Badly-formed maxims are usually ignored in philosophical discussion 
-and would have been much more difficult to understand without the help of a computer which immediately
-noted that they render the FUL inconsistent. Computational tools prompt philosophers to ask new questions that 
-lead to insights. Computational ethics can serve as another tool in a philosopher's arsenal, like a 
-thought experiment or counterexample.
+and would have been much more difficult to understand without the help of a computer. Computational 
+tools prompt philosophers to ask new questions that 
+lead to insights, and can thus serve as another tool in a philosopher's arsenal, like a 
+thought experiment or counterexample.\footnote{Even if computational ethics is possible, some may 
+worry that it sacrifices something important about philosophical inquiry. I discuss this concern in Appendix 
+\ref{academicphilosophy}.}
 
@@
 and implementing it in an interactive theorem prover requires making the idea precise to a degree 
-that ordinary discussion does not necessarily require. For example, as I formalized the notion of a 
+that ordinary discussion does not necessarily require. For example, when formalizing the notion of a 
 maxim, I had to understand its components and define it as a circumstance, act, goal tuple. Moreover, 
@@
 use interactive theorem provers like Isabelle to complete proofs in a matter of seconds. By automating 
-away the tedium, computational ethics can give philosophers the tools to ask new kinds of questions.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
+away the tedium, computational ethics can give philosophers the tools to ask new kinds of questions.
+
 Computational ethics is at its infancy. The use of theorem provers in mathematics is just now beginning 
@@
 %
-\isamarkupsubsection{Theoretical Objections to Automating Kantian Ethics%
+\isamarkupsubsection{Theoretical Objections to Automating Kantian Ethics \label{amapossible}%
 }
@@
 doing the right thing because it is the right thing to do. Moral behavior requires both a certain action 
-(acting on a morally worthy maxim) and a certain motivation (the motivation of duty). It is the capacity 
+(acting on a morally worthy maxim) and a certain motivation (the motivation of duty). It is this capacity 
 for self-motivation that makes morality binding for rational beings; we must behave morally precisely 
 because we have wills, or the ability to be motivated by ends
-that we choose. Only rational beings have wills, thus only rational beings can have good wills, or wills
+that we choose. Only rational beings have wills, so only rational beings can have good wills, or wills
 motivated by duty, and thus only rational beings can behave morally. Under this understanding
-of moral behavior, it seems unlikely that a computer could, in the near future, behave morally
+of moral behavior, it seems unlikely that a computer could behave morally
 since a computer does not have motivation in the same way as a human being. If a computer is not a fully rational
-being, then, it is not the kind of thing that can behave morally.\footnote{A parallel argument can also be made for virtue ethics. Virtuous
+being, then it is not the kind of thing that can behave morally.\footnote{A parallel argument can also be made for virtue ethics. Virtuous
 behavior requires not only a certain action, but also a certain disposition towards the action, so it seems
@@
 The idea that, under Kant's account, a computer cannot behave morally, does not preclude the kind 
-of automated categorical imperative test that I present in this thesis. O'Neill argues that the FUL
-serves as a test of morally worthy maxims, and an automated categorical imperative test can be used 
-to identify this kind of maxim. Perhaps a computer cannot act on a morally relevant maxim from a motivation of duty, 
+of automated categorical imperative that I present in this thesis. O'Neill argues that the FUL
+serves as a test of morally worthy maxims, and a implementation of an automated categorical imperative can 
+identify this kind of maxim. Perhaps a computer cannot act on a morally relevant maxim from a motivation of duty, 
 but it certainly can act on this maxim nonetheless. For example, a self-driving car can choose to swerve to hit a tree
@@
 morally consequential decisions. Automated agents may be incapable of moral behavior, but automated agents that mimic
-moral behavior are surely better than agents that ignore morality entirely. Worries about unethical AI
+moral behavior are better than agents that ignore morality entirely. Worries about unethical AI
 stem from the fact that AI agents are navigating a world inhabited by human beings, and their decisions
@@
 should mimic the behavior of an ethical human being. AI needs to be ethical for our sakes, so that we 
-can interact with it safely. If AI conforms to human ethics, then it will certainly navigate the world
+can interact with it safely. If AI conforms to human ethics, then it will navigate the world
 in a way that benefits human beings.
@@
 plans, proposals and policies which they can consider, revise or reject or endorse and pursue'' \citep[343]{oneilluniversallaws}.
-The FUL evaluates the moral worth of a maxim given as input and this potential maxim is generated by 
+The FUL evaluates the moral worth of a maxim given as input, where this potential maxim is generated by 
 the choices that an agent is faced with. Determining this potential maxim is a challenge for both human
-and automated reasoners. Kant claims that the difficulty of determining an agent's potential maxim, which is their
+and automated reasoners. Kant even claims that the difficulty of determining an agent's potential maxim, which is their
 own, subjective understanding of their principle of action, is a reason that we may never be able 
-to know if morally worthy action has been performed \cite[345]{oneilluniversallaws}. Reasoners are faced with
+to know if the morally worthy action has been performed \cite[345]{oneilluniversallaws}. Reasoners are faced with
 choices between potential actions and must determine the maxim, or principle, underlying each potential action.
@@
 
-While human beings cannot repeatedly apply the universalizability test to all potential maxims during 
-every moral dilemma, computers have the computational power to do so. Human beings are 
+While human beings cannot repeatedly apply the universalizability test to all potential maxims encountered during 
+a moral dilemma, computers have the computational power to do so. Human beings are 
 equipped with enough prior knowledge or common sense, to have an almanac of morally worthy maxims,
@@
 \begin{isamarkuptext}%
-This understanding of the role of the categorical imperative not only fails to render automate moral
+This understanding of the role of the categorical imperative not only fails to render automated moral
 reasoning impossible, but it also offers insight into how to solve the challenge of creating an input parser.
@@
 of the automated categorical imperative would then simply check the work of this machine learning algorithm and transform
-a fuzzy prediction into a provable, rigorous moral judgement. Moreover, this rigorous moral judgement
+a fuzzy prediction into a provable, rigorous moral judgement. This rigorous moral judgement
 could in turn be fed into the database of maxims to make the intput parser smarter. One example of 
@@
 prior knowledge of some maxims' moral worth and the ability of a computer to constantly perform the
-universalizability test could not only match human ethical reasoning but perhaps also surpass it
+universalizability test could not only match human ethical reasoning but could perhaps surpass it
 by double checking the moral intuitions that we take for granted. A computer with no common sense or prior knowledge
-may indeed be unable to reason using the categorical imperative, but one equipped with some prior knowledge
+may be unable to reason using the categorical imperative, but one equipped with some prior knowledge
 of maxims and their moral worth may even help us better reason about morality.%
@@
 In 1685, Leibniz dreamed of a calculator that could resolve philosophical and theological 
-disputes \cite{leibniz}. At the time, the logical and computational resources necessary to make his 
+disputes \citep{leibniz}. At the time, the logical and computational resources necessary to make his 
 dream a reality did not exist. Today, automated ethics is a growing field, spurred in part by the 
@@
 and there has been both theoretical and practical work on automating Kantian ethics \citep{powers, lin}. 
-In 2006, Powers \citep{powers} argued that implementing Kantian ethics presented technical challenges, 
+In 2006, Powers argued that implementing Kantian ethics presented technical challenges, 
 such as automation of a non-monotonic logic, and philosophical challenges, like a definition of the 
-categorical imperative. I address the former through my use of Dyadic Deontic Logic, which allows 
+categorical imperative \citep{powers}. I address the former through my use of Dyadic Deontic Logic, which allows 
 obligations to be retracted as context changes, and the latter through my use of the practical 
@@
 
-Kroy \citep{kroy} presents a formalization of the first two formulations of the categorical imperative, 
-but does not implement it. I implement his formalization of the FUL to compare it to my system. 
-Lindner and Bentzen \citep{BL} presented one of the first formalizations and implementations of 
-Kant's second formulation of the categorical imperative. They present their goal as ``not to get 
+Kroy presents a formalization of the first two formulations of the categorical imperative, but wrote 
+before the computational tools existed to automate such a formalization \citep{kroy}. I implement his formalization of the FUL to compare it to my system. 
+Lindner and Bentzen presented one of the first implementations of a formalization of 
+Kant's second formulation of the categorical imperative \citep{BL}. They present their goal as ``not to get 
 close to a correct interpretation of Kant, but to show that our interpretation of Kant’s ideas can 
@@
 independent AI, there is a dire need to program such AI with some notion of ethics. If AI is navigating
-human society, then it is making decisions with an ethical component at all times. Ethics is inescapable; 
+human society, then it is making decisions with an ethical facet at all times. Ethics is inescapable; 
 if AI developers and computer scientists ignore it, then they will be building machines that make decisions
@@
 algorithm that is biased against poor families to search algorithms that associate black-sounding names
-with crime, demonstrate that such implicit ethics simply codifies the biases, prejudices, and moral
+with crime, demonstrate that such implicit ethics usually codifies the biases, prejudices, and moral
 failings of the society in which it is developed. AI will inevitably make judgements on moral dilemmas, 
@@
 %:%51=21%:%
-%:%52=22%:%
+%:%54=25%:%
 %:%55=26%:%
@@
 %:%60=31%:%
-%:%61=32%:%
+%:%63=33%:%
 %:%64=34%:%
@@
 %:%69=39%:%
-%:%73=41%:%
-%:%74=42%:%
-%:%75=43%:%
-%:%76=44%:%
-%:%77=45%:%
-%:%78=46%:%
-%:%79=47%:%
-%:%80=48%:%
-%:%81=49%:%
-%:%82=50%:%
-%:%83=51%:%
-%:%84=52%:%
-%:%85=53%:%
-%:%86=54%:%
-%:%87=55%:%
-%:%88=56%:%
-%:%89=57%:%
-%:%90=58%:%
-%:%91=59%:%
-%:%92=60%:%
-%:%93=61%:%
-%:%94=62%:%
-%:%95=63%:%
-%:%96=64%:%
-%:%97=65%:%
-%:%98=66%:%
-%:%99=67%:%
-%:%100=68%:%
-%:%101=69%:%
-%:%102=70%:%
-%:%103=71%:%
-%:%104=72%:%
-%:%105=73%:%
-%:%106=74%:%
-%:%107=75%:%
-%:%108=76%:%
-%:%109=77%:%
-%:%110=78%:%
-%:%111=79%:%
-%:%112=80%:%
-%:%113=81%:%
-%:%114=82%:%
-%:%115=83%:%
-%:%116=84%:%
-%:%117=85%:%
-%:%118=86%:%
-%:%119=87%:%
-%:%120=88%:%
-%:%121=89%:%
-%:%122=90%:%
-%:%123=91%:%
-%:%124=92%:%
-%:%125=93%:%
-%:%126=94%:%
-%:%127=95%:%
-%:%128=96%:%
-%:%129=97%:%
-%:%130=98%:%
-%:%131=99%:%
-%:%132=100%:%
-%:%133=101%:%
-%:%134=102%:%
-%:%135=103%:%
-%:%136=104%:%
-%:%137=105%:%
-%:%138=106%:%
-%:%139=107%:%
-%:%140=108%:%
-%:%141=109%:%
-%:%142=110%:%
-%:%143=111%:%
-%:%144=112%:%
-%:%145=113%:%
-%:%146=114%:%
-%:%147=115%:%
-%:%148=116%:%
-%:%149=117%:%
-%:%150=118%:%
-%:%151=119%:%
-%:%152=120%:%
-%:%153=121%:%
-%:%154=122%:%
-%:%155=123%:%
-%:%156=124%:%
-%:%157=125%:%
-%:%158=126%:%
-%:%159=127%:%
-%:%160=128%:%
-%:%161=129%:%
-%:%162=130%:%
-%:%163=131%:%
-%:%164=132%:%
-%:%165=133%:%
-%:%166=134%:%
-%:%167=135%:%
-%:%168=136%:%
-%:%169=137%:%
-%:%170=138%:%
-%:%171=139%:%
-%:%172=140%:%
-%:%173=141%:%
-%:%174=142%:%
-%:%175=143%:%
-%:%176=144%:%
-%:%177=145%:%
-%:%178=146%:%
-%:%187=148%:%
-%:%199=150%:%
-%:%200=151%:%
-%:%201=152%:%
-%:%202=153%:%
-%:%203=154%:%
-%:%204=155%:%
-%:%213=157%:%
-%:%225=159%:%
-%:%226=160%:%
-%:%227=161%:%
-%:%228=162%:%
-%:%229=163%:%
-%:%230=164%:%
-%:%231=165%:%
-%:%232=166%:%
-%:%233=167%:%
-%:%234=168%:%
-%:%235=169%:%
-%:%236=170%:%
-%:%237=171%:%
-%:%238=172%:%
-%:%239=173%:%
-%:%240=174%:%
-%:%241=175%:%
-%:%242=176%:%
-%:%243=177%:%
-%:%244=178%:%
-%:%245=179%:%
-%:%246=180%:%
-%:%247=181%:%
-%:%248=182%:%
-%:%249=183%:%
-%:%250=184%:%
-%:%251=185%:%
-%:%252=186%:%
-%:%253=187%:%
-%:%254=188%:%
-%:%255=189%:%
-%:%256=190%:%
-%:%257=191%:%
-%:%258=192%:%
-%:%259=193%:%
-%:%260=194%:%
-%:%261=195%:%
-%:%262=196%:%
-%:%263=197%:%
-%:%264=198%:%
-%:%265=199%:%
-%:%266=200%:%
-%:%267=201%:%
-%:%268=202%:%
-%:%269=203%:%
-%:%270=204%:%
-%:%271=205%:%
-%:%272=206%:%
-%:%273=207%:%
-%:%274=208%:%
-%:%275=209%:%
-%:%276=210%:%
-%:%277=211%:%
-%:%278=212%:%
-%:%279=213%:%
-%:%280=214%:%
-%:%281=215%:%
-%:%282=216%:%
-%:%283=217%:%
-%:%284=218%:%
-%:%285=219%:%
-%:%286=220%:%
-%:%287=221%:%
-%:%288=222%:%
-%:%289=223%:%
-%:%290=224%:%
-%:%291=225%:%
-%:%292=226%:%
-%:%293=227%:%
-%:%294=228%:%
-%:%295=229%:%
-%:%296=230%:%
-%:%297=231%:%
-%:%298=232%:%
-%:%299=233%:%
-%:%300=234%:%
-%:%301=235%:%
-%:%302=236%:%
-%:%303=237%:%
-%:%304=238%:%
-%:%305=239%:%
-%:%306=240%:%
-%:%307=241%:%
-%:%308=242%:%
-%:%309=243%:%
-%:%310=244%:%
-%:%311=245%:%
-%:%312=246%:%
-%:%313=247%:%
-%:%314=248%:%
-%:%315=249%:%
-%:%316=250%:%
-%:%317=251%:%
-%:%318=252%:%
-%:%319=253%:%
-%:%320=254%:%
-%:%321=255%:%
-%:%322=256%:%
-%:%323=257%:%
-%:%324=258%:%
-%:%325=259%:%
-%:%326=260%:%
-%:%327=261%:%
-%:%328=262%:%
-%:%329=263%:%
-%:%330=264%:%
-%:%331=265%:%
-%:%332=266%:%
-%:%333=267%:%
-%:%334=268%:%
-%:%335=269%:%
-%:%336=270%:%
-%:%337=271%:%
-%:%338=272%:%
-%:%339=273%:%
-%:%340=274%:%
-%:%341=275%:%
-%:%342=276%:%
-%:%343=277%:%
-%:%344=278%:%
-%:%345=279%:%
-%:%346=280%:%
-%:%347=281%:%
-%:%348=282%:%
-%:%349=283%:%
-%:%350=284%:%
-%:%351=285%:%
-%:%352=286%:%
-%:%353=287%:%
-%:%354=288%:%
-%:%355=289%:%
-%:%356=290%:%
-%:%357=291%:%
-%:%358=292%:%
-%:%359=293%:%
-%:%360=294%:%
-%:%361=295%:%
-%:%362=296%:%
-%:%363=297%:%
-%:%364=298%:%
-%:%365=299%:%
-%:%366=300%:%
-%:%367=301%:%
-%:%368=302%:%
-%:%369=303%:%
-%:%370=304%:%
-%:%371=305%:%
-%:%372=306%:%
-%:%373=307%:%
-%:%374=308%:%
-%:%375=309%:%
-%:%376=310%:%
-%:%377=311%:%
-%:%378=312%:%
-%:%379=313%:%
-%:%380=314%:%
-%:%381=315%:%
-%:%382=316%:%
-%:%383=317%:%
-%:%384=318%:%
-%:%385=319%:%
-%:%386=320%:%
-%:%387=321%:%
-%:%388=322%:%
-%:%389=323%:%
-%:%398=327%:%
-%:%410=329%:%
-%:%411=330%:%
-%:%412=331%:%
-%:%413=332%:%
-%:%414=333%:%
-%:%415=334%:%
-%:%416=335%:%
-%:%417=336%:%
-%:%418=337%:%
-%:%419=338%:%
-%:%420=339%:%
-%:%421=340%:%
-%:%422=341%:%
-%:%423=342%:%
-%:%424=343%:%
-%:%425=344%:%
-%:%426=345%:%
-%:%427=346%:%
-%:%428=347%:%
-%:%429=348%:%
-%:%430=349%:%
-%:%431=350%:%
-%:%432=351%:%
-%:%433=352%:%
-%:%434=353%:%
-%:%435=354%:%
-%:%436=355%:%
-%:%437=356%:%
-%:%438=357%:%
-%:%439=358%:%
-%:%440=359%:%
-%:%441=360%:%
-%:%442=361%:%
-%:%443=362%:%
-%:%444=363%:%
-%:%445=364%:%
-%:%446=365%:%
-%:%447=366%:%
-%:%448=367%:%
-%:%449=368%:%
-%:%450=369%:%
-%:%451=370%:%
-%:%455=374%:%
-%:%456=375%:%
-%:%457=376%:%
-%:%458=377%:%
-%:%459=378%:%
-%:%460=379%:%
-%:%461=380%:%
-%:%462=381%:%
-%:%463=382%:%
-%:%464=383%:%
-%:%465=384%:%
-%:%466=385%:%
-%:%467=386%:%
-%:%468=387%:%
-%:%469=388%:%
-%:%470=389%:%
-%:%471=390%:%
-%:%472=391%:%
-%:%473=392%:%
-%:%482=395%:%
-%:%494=398%:%
-%:%495=399%:%
-%:%496=400%:%
-%:%497=401%:%
-%:%498=402%:%
-%:%499=403%:%
-%:%500=404%:%
-%:%501=405%:%
-%:%502=406%:%
-%:%503=407%:%
-%:%504=408%:%
-%:%505=409%:%
-%:%506=410%:%
-%:%507=411%:%
-%:%508=412%:%
-%:%509=413%:%
-%:%510=414%:%
-%:%511=415%:%
-%:%512=416%:%
-%:%513=417%:%
-%:%514=418%:%
-%:%515=419%:%
-%:%516=420%:%
-%:%517=421%:%
-%:%518=422%:%
-%:%519=423%:%
-%:%520=424%:%
-%:%521=425%:%
-%:%522=426%:%
-%:%523=427%:%
-%:%524=428%:%
-%:%525=429%:%
-%:%526=430%:%
-%:%527=431%:%
-%:%528=432%:%
-%:%529=433%:%
-%:%530=434%:%
-%:%531=435%:%
-%:%532=436%:%
-%:%533=437%:%
-%:%534=438%:%
-%:%535=439%:%
-%:%536=440%:%
-%:%537=441%:%
-%:%538=442%:%
-%:%539=443%:%
-%:%540=444%:%
-%:%541=445%:%
-%:%542=446%:%
-%:%543=447%:%
-%:%544=448%:%
-%:%545=449%:%
-%:%546=450%:%
-%:%547=451%:%
-%:%548=452%:%
-%:%549=453%:%
-%:%550=454%:%
-%:%551=455%:%
-%:%552=456%:%
-%:%553=457%:%
-%:%554=458%:%
-%:%555=459%:%
-%:%556=460%:%
-%:%557=461%:%
-%:%558=462%:%
-%:%559=463%:%
-%:%560=464%:%
-%:%561=465%:%
-%:%562=466%:%
-%:%563=467%:%
-%:%564=468%:%
-%:%565=469%:%
-%:%566=470%:%
-%:%567=471%:%
-%:%568=472%:%
-%:%569=473%:%
-%:%570=474%:%
-%:%571=475%:%
-%:%572=476%:%
-%:%573=477%:%
-%:%574=478%:%
-%:%575=479%:%
-%:%576=480%:%
-%:%577=481%:%
-%:%578=482%:%
-%:%579=483%:%
-%:%580=484%:%
-%:%581=485%:%
-%:%582=486%:%
-%:%583=487%:%
-%:%584=488%:%
-%:%585=489%:%
-%:%586=490%:%
-%:%587=491%:%
-%:%588=492%:%
-%:%589=493%:%
-%:%590=494%:%
-%:%591=495%:%
-%:%592=496%:%
-%:%593=497%:%
-%:%594=498%:%
-%:%595=499%:%
-%:%596=500%:%
-%:%597=501%:%
-%:%598=502%:%
-%:%599=503%:%
-%:%600=504%:%
-%:%601=505%:%
-%:%604=508%:%
-%:%605=509%:%
-%:%606=510%:%
-%:%607=511%:%
-%:%608=512%:%
-%:%609=513%:%
+%:%70=40%:%
+%:%71=41%:%
+%:%72=42%:%
+%:%73=43%:%
+%:%74=44%:%
+%:%75=45%:%
+%:%76=46%:%
+%:%77=47%:%
+%:%78=48%:%
+%:%79=49%:%
+%:%80=50%:%
+%:%81=51%:%
+%:%82=52%:%
+%:%83=53%:%
+%:%84=54%:%
+%:%85=55%:%
+%:%86=56%:%
+%:%87=57%:%
+%:%88=58%:%
+%:%89=59%:%
+%:%90=60%:%
+%:%91=61%:%
+%:%92=62%:%
+%:%93=63%:%
+%:%94=64%:%
+%:%95=65%:%
+%:%96=66%:%
+%:%97=67%:%
+%:%98=68%:%
+%:%99=69%:%
+%:%100=70%:%
+%:%101=71%:%
+%:%102=72%:%
+%:%103=73%:%
+%:%104=74%:%
+%:%105=75%:%
+%:%106=76%:%
+%:%107=77%:%
+%:%108=78%:%
+%:%109=79%:%
+%:%110=80%:%
+%:%111=81%:%
+%:%112=82%:%
+%:%113=83%:%
+%:%114=84%:%
+%:%115=85%:%
+%:%116=86%:%
+%:%117=87%:%
+%:%118=88%:%
+%:%119=89%:%
+%:%120=90%:%
+%:%121=91%:%
+%:%122=92%:%
+%:%123=93%:%
+%:%124=94%:%
+%:%125=95%:%
+%:%126=96%:%
+%:%127=97%:%
+%:%128=98%:%
+%:%129=99%:%
+%:%130=100%:%
+%:%131=101%:%
+%:%132=102%:%
+%:%133=103%:%
+%:%134=104%:%
+%:%135=105%:%
+%:%136=106%:%
+%:%137=107%:%
+%:%138=108%:%
+%:%139=109%:%
+%:%140=110%:%
+%:%141=111%:%
+%:%142=112%:%
+%:%143=113%:%
+%:%144=114%:%
+%:%145=115%:%
+%:%146=116%:%
+%:%147=117%:%
+%:%148=118%:%
+%:%149=119%:%
+%:%150=120%:%
+%:%151=121%:%
+%:%152=122%:%
+%:%153=123%:%
+%:%154=124%:%
+%:%155=125%:%
+%:%156=126%:%
+%:%157=127%:%
+%:%158=128%:%
+%:%159=129%:%
+%:%160=130%:%
+%:%161=131%:%
+%:%162=132%:%
+%:%163=133%:%
+%:%164=134%:%
+%:%165=135%:%
+%:%166=136%:%
+%:%167=137%:%
+%:%168=138%:%
+%:%169=139%:%
+%:%170=140%:%
+%:%171=141%:%
+%:%172=142%:%
+%:%173=143%:%
+%:%182=145%:%
+%:%194=147%:%
+%:%195=148%:%
+%:%196=149%:%
+%:%197=150%:%
+%:%198=151%:%
+%:%199=152%:%
+%:%200=153%:%
+%:%201=154%:%
+%:%210=156%:%
+%:%222=158%:%
+%:%223=159%:%
+%:%224=160%:%
+%:%225=161%:%
+%:%226=162%:%
+%:%227=163%:%
+%:%228=164%:%
+%:%229=165%:%
+%:%230=166%:%
+%:%231=167%:%
+%:%232=168%:%
+%:%233=169%:%
+%:%234=170%:%
+%:%235=171%:%
+%:%236=172%:%
+%:%237=173%:%
+%:%238=174%:%
+%:%239=175%:%
+%:%240=176%:%
+%:%241=177%:%
+%:%242=178%:%
+%:%243=179%:%
+%:%244=180%:%
+%:%245=181%:%
+%:%246=182%:%
+%:%247=183%:%
+%:%248=184%:%
+%:%249=185%:%
+%:%250=186%:%
+%:%251=187%:%
+%:%252=188%:%
+%:%253=189%:%
+%:%254=190%:%
+%:%255=191%:%
+%:%256=192%:%
+%:%257=193%:%
+%:%258=194%:%
+%:%259=195%:%
+%:%260=196%:%
+%:%261=197%:%
+%:%262=198%:%
+%:%263=199%:%
+%:%264=200%:%
+%:%265=201%:%
+%:%266=202%:%
+%:%267=203%:%
+%:%268=204%:%
+%:%269=205%:%
+%:%270=206%:%
+%:%271=207%:%
+%:%272=208%:%
+%:%273=209%:%
+%:%274=210%:%
+%:%275=211%:%
+%:%276=212%:%
+%:%277=213%:%
+%:%278=214%:%
+%:%279=215%:%
+%:%280=216%:%
+%:%281=217%:%
+%:%282=218%:%
+%:%283=219%:%
+%:%284=220%:%
+%:%285=221%:%
+%:%286=222%:%
+%:%287=223%:%
+%:%288=224%:%
+%:%289=225%:%
+%:%290=226%:%
+%:%291=227%:%
+%:%292=228%:%
+%:%293=229%:%
+%:%294=230%:%
+%:%295=231%:%
+%:%296=232%:%
+%:%297=233%:%
+%:%298=234%:%
+%:%299=235%:%
+%:%300=236%:%
+%:%301=237%:%
+%:%302=238%:%
+%:%303=239%:%
+%:%304=240%:%
+%:%305=241%:%
+%:%306=242%:%
+%:%307=243%:%
+%:%308=244%:%
+%:%309=245%:%
+%:%310=246%:%
+%:%311=247%:%
+%:%312=248%:%
+%:%313=249%:%
+%:%314=250%:%
+%:%315=251%:%
+%:%316=252%:%
+%:%317=253%:%
+%:%318=254%:%
+%:%319=255%:%
+%:%320=256%:%
+%:%321=257%:%
+%:%322=258%:%
+%:%323=259%:%
+%:%324=260%:%
+%:%325=261%:%
+%:%326=262%:%
+%:%327=263%:%
+%:%328=264%:%
+%:%329=265%:%
+%:%330=266%:%
+%:%331=267%:%
+%:%332=268%:%
+%:%333=269%:%
+%:%334=270%:%
+%:%335=271%:%
+%:%336=272%:%
+%:%337=273%:%
+%:%338=274%:%
+%:%339=275%:%
+%:%340=276%:%
+%:%341=277%:%
+%:%342=278%:%
+%:%343=279%:%
+%:%344=280%:%
+%:%345=281%:%
+%:%346=282%:%
+%:%347=283%:%
+%:%348=284%:%
+%:%349=285%:%
+%:%350=286%:%
+%:%351=287%:%
+%:%352=288%:%
+%:%353=289%:%
+%:%354=290%:%
+%:%355=291%:%
+%:%356=292%:%
+%:%357=293%:%
+%:%358=294%:%
+%:%359=295%:%
+%:%360=296%:%
+%:%361=297%:%
+%:%362=298%:%
+%:%363=299%:%
+%:%364=300%:%
+%:%365=301%:%
+%:%366=302%:%
+%:%367=303%:%
+%:%368=304%:%
+%:%369=305%:%
+%:%370=306%:%
+%:%371=307%:%
+%:%372=308%:%
+%:%373=309%:%
+%:%374=310%:%
+%:%375=311%:%
+%:%376=312%:%
+%:%377=313%:%
+%:%378=314%:%
+%:%379=315%:%
+%:%380=316%:%
+%:%381=317%:%
+%:%382=318%:%
+%:%383=319%:%
+%:%384=320%:%
+%:%385=321%:%
+%:%386=322%:%
+%:%395=326%:%
+%:%407=328%:%
+%:%408=329%:%
+%:%409=330%:%
+%:%410=331%:%
+%:%411=332%:%
+%:%412=333%:%
+%:%413=334%:%
+%:%414=335%:%
+%:%415=336%:%
+%:%416=337%:%
+%:%417=338%:%
+%:%418=339%:%
+%:%419=340%:%
+%:%420=341%:%
+%:%421=342%:%
+%:%422=343%:%
+%:%423=344%:%
+%:%424=345%:%
+%:%425=346%:%
+%:%426=347%:%
+%:%427=348%:%
+%:%428=349%:%
+%:%429=350%:%
+%:%430=351%:%
+%:%431=352%:%
+%:%432=353%:%
+%:%433=354%:%
+%:%434=355%:%
+%:%435=356%:%
+%:%436=357%:%
+%:%437=358%:%
+%:%438=359%:%
+%:%439=360%:%
+%:%440=361%:%
+%:%441=362%:%
+%:%442=363%:%
+%:%443=364%:%
+%:%444=365%:%
+%:%445=366%:%
+%:%446=367%:%
+%:%447=368%:%
+%:%448=369%:%
+%:%449=370%:%
+%:%450=371%:%
+%:%451=372%:%
+%:%452=373%:%
+%:%453=374%:%
+%:%454=375%:%
+%:%455=376%:%
+%:%456=377%:%
+%:%457=378%:%
+%:%458=379%:%
+%:%459=380%:%
+%:%460=381%:%
+%:%461=382%:%
+%:%462=383%:%
+%:%463=384%:%
+%:%464=385%:%
+%:%465=386%:%
+%:%466=387%:%
+%:%467=388%:%
+%:%468=389%:%
+%:%469=390%:%
+%:%470=391%:%
+%:%479=394%:%
+%:%491=397%:%
+%:%492=398%:%
+%:%493=399%:%
+%:%494=400%:%
+%:%495=401%:%
+%:%496=402%:%
+%:%497=403%:%
+%:%498=404%:%
+%:%499=405%:%
+%:%500=406%:%
+%:%501=407%:%
+%:%502=408%:%
+%:%503=409%:%
+%:%504=410%:%
+%:%505=411%:%
+%:%506=412%:%
+%:%507=413%:%
+%:%508=414%:%
+%:%509=415%:%
+%:%510=416%:%
+%:%511=417%:%
+%:%512=418%:%
+%:%513=419%:%
+%:%514=420%:%
+%:%515=421%:%
+%:%516=422%:%
+%:%517=423%:%
+%:%518=424%:%
+%:%519=425%:%
+%:%520=426%:%
+%:%521=427%:%
+%:%522=428%:%
+%:%523=429%:%
+%:%524=430%:%
+%:%525=431%:%
+%:%526=432%:%
+%:%527=433%:%
+%:%528=434%:%
+%:%529=435%:%
+%:%530=436%:%
+%:%531=437%:%
+%:%532=438%:%
+%:%533=439%:%
+%:%534=440%:%
+%:%535=441%:%
+%:%536=442%:%
+%:%537=443%:%
+%:%538=444%:%
+%:%539=445%:%
+%:%540=446%:%
+%:%541=447%:%
+%:%542=448%:%
+%:%543=449%:%
+%:%544=450%:%
+%:%545=451%:%
+%:%546=452%:%
+%:%547=453%:%
+%:%548=454%:%
+%:%549=455%:%
+%:%550=456%:%
+%:%551=457%:%
+%:%552=458%:%
+%:%553=459%:%
+%:%554=460%:%
+%:%555=461%:%
+%:%556=462%:%
+%:%557=463%:%
+%:%558=464%:%
+%:%559=465%:%
+%:%560=466%:%
+%:%561=467%:%
+%:%562=468%:%
+%:%563=469%:%
+%:%564=470%:%
+%:%565=471%:%
+%:%566=472%:%
+%:%567=473%:%
+%:%568=474%:%
+%:%569=475%:%
+%:%570=476%:%
+%:%571=477%:%
+%:%572=478%:%
+%:%573=479%:%
+%:%574=480%:%
+%:%575=481%:%
+%:%576=482%:%
+%:%577=483%:%
+%:%578=484%:%
+%:%579=485%:%
+%:%580=486%:%
+%:%581=487%:%
+%:%582=488%:%
+%:%583=489%:%
+%:%584=490%:%
+%:%585=491%:%
+%:%586=492%:%
+%:%587=493%:%
+%:%588=494%:%
+%:%589=495%:%
+%:%590=496%:%
+%:%591=497%:%
+%:%592=498%:%
+%:%593=499%:%
+%:%594=500%:%
+%:%595=501%:%
+%:%596=502%:%
+%:%597=503%:%
+%:%598=504%:%
+%:%601=506%:%
+%:%602=507%:%
+%:%603=508%:%
+%:%604=509%:%
+%:%605=510%:%
+%:%606=511%:%
+%:%609=512%:%
+%:%610=513%:%
+%:%611=514%:%
 %:%612=515%:%
@@
 %:%623=526%:%
-%:%624=527%:%
-%:%625=528%:%
-%:%626=529%:%
-%:%635=533%:%
+%:%632=530%:%
+%:%644=532%:%
+%:%645=533%:%
+%:%646=534%:%
 %:%647=535%:%
@@
 %:%695=583%:%
-%:%696=584%:%
-%:%697=585%:%
-%:%698=586%:%
-%:%707=588%:%
+%:%704=585%:%
+%:%716=587%:%
+%:%717=588%:%
+%:%718=589%:%
 %:%719=590%:%
@@
 %:%754=625%:%
-%:%755=626%:%
-%:%756=627%:%
-%:%757=628%:%

### 2022-03-03 paper/output/document/appendix.tex
began cleaning appendix

--- 2022-02-13 paper/output/document/appendix.tex
@@
 %
-\isamarkupsubsection{Maxims and Motives \label{maximmotive}%
+\isamarkupsubsection{Alternate Definitions of a Maxim \label{maximmotive}%
 }
@@
 %
+\isamarkupsubsubsection{Korsgaard's Act-Goal View%
+}
+\isamarkuptrue%
+%
 \endisatagdocument
@@
 \begin{isamarkuptext}%
-Kitcher begins with O'Niell's circumstance, act, goal view and expands it to include the motive 
-behind performing the maxim \cite{whatisamaxim}. This additional component is read 
-as ``In circumstance C, I will do A in order to G because of M," where M may be ``duty" or ``self-love."
-Kitcher argues that the inclusion of motive is necessary for the fullest, most general form of a maxim
-in order to capture Kant's idea that an action derives its moral worth from being done for the sake of duty itself.
-Under this view, the FUL would obligate maxims of the form 
+I adopt O'Niell's definition of a maxim, which builds on Korsgaard's weaker interpretation of 
+a maxim as an act, goal pair. She interprets Kant's example meanings as having the form ``to-do-this-act-for-
+the-sake-of-this-end,'' which could be formalized as a pair of an act and goal \citep{actingforareason}.
+For example, under this view, one example maxim might be, ``Falsely promise to repay a loan in order
+to get some easy cash.''
+
+O'Niell's view only differs from this view in the inclusion of the circumstances
+on which the agent acts. This inclusion creates a representation of a maxim that is strictly more expressive than 
+Korsgaard's interpretation; every (circumstance, act, goal) tuple can be represented as an (act, goal) pair
+by simply dropping the circumstances, but the same (act, goal) pair could correspond to many different
+(circumstance, act, goal) tuples, all with varying moral statuses. Because my representation of a maxim
+is more expressive than Korsgaard's, my results are stronger than those that would be achieved with 
+Korsgaard's view. Thus, proponents of Korsgaard's view could simply ignore the circumstances in my
+representation of a maxim and still achieve their desired results.
+
+One other reason to be concerned with Korsgaard's view is that an actionable maxim will necessarily
+require some circumstances built-in because the agent will need to know when to act on the maxim. For example,
+the falsely promising maxim bakes in the circumstances that the actor has access to lender, needs money, 
+and that the lender will expect their money back. At an even more granular level, this maxim implicitly includes
+a definition of a lender and of falsely promising, both of which are circumstantial. Given that all
+maxims necessarily include some circumstances, O'Niell's view makes these implicit circumstances
+explicit. This precision is a benefit; so long as my circumstances are not so finely grained that they
+are uninterpretable, they render O'Niell's kind of maxims more precise than Korsgaard's form.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsubsection{Kitcher's View on Motives%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
+A stronger view than O'Niell's is due to Patricia Kitcher. Kitcher begins with O'Niell's 
+circumstance, act, goal view and expands it to include the motive for a maxim \citep{whatisamaxim}. 
+This additional component is read as ``In circumstance C, I will do A in order to G because of M,'' 
+where M may be ``duty'' or ``self-love.'' Kitcher argues that the inclusion of motive is necessary 
+for the fullest, most general form of a maxim in order to capture Kant's idea that an action derives 
+its moral worth from being done for the sake of duty itself. Under this view, the FUL would obligate maxims of the form 
 ``In circumstance C, I will do A in order to G because I can will that I and everyone else simultaneously
-will do A in order to G in circumstance C." In other words, if Kant is correct in arguing that moral 
+will do A in order to G in circumstance C.'' In other words, if Kant is correct in arguing that moral 
 actions must be done from the motive of duty, the affirmative result of the FUL becomes 
@@
 While Kitcher's conception of a maxim captures Kant's idea of acting for duty's own sake, I will not implement it 
-because it is not necessary for putting maxims through the FUL. Indeed, Kitcher acknowledges that 
-O'Neill's formulation suffices for the universalizability test, but is not the general notion of a maxim.
+because it is not necessary for putting maxims through the FUL. Kitcher acknowledges that 
+O'Niell's formulation suffices for the universalizability test, but merely argues that it is not the most general form of a maxim.
 In order to pass the maxim through the FUL, it suffices to know the circumstance, act, and goal. The FUL
 derives the motive that Kitcher bundles into the maxim, so automating the FUL does not require 
-including a motive. The ``input" to the FUL is the circumstance, act, goal tuple. My project takes 
-this input and returns the motivation that the dutiful, moral agent would adopt. Additionally, doing
+including a motive. The ``input'' to the FUL is a circumstance, act, goal tuple. My project takes 
+this input and returns the motivation that the dutiful, moral agent would adopt, which is ``because this
+maxim is morally worthy.'' Additionally, doing
 justice to the rich notion of motive requires modelling the operation of practical reason itself, 
 which is outside the scope of this project. My work focuses on the universalizability test, but future work that 
-models the process of practical reason may use my implementation of the FUL as a ``library." Combined 
+models the process of practical reason may use my implementation of the FUL as a ``library.'' Combined 
 with a logic of practical reason, an implementation of the FUL can move from evaluating a maxim to 
-evaluating an agent's behavior, since that's when ``acting from duty" starts to matter.%
+evaluating an agent's behavior, since that's when ``acting from duty'' starts to matter.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-This section contains a formalization of the categorical imperative introduced by Moshe Kroy in 
+In this appendix, I implement a formalization of the categorical imperative introduced by Moshe Kroy in
 1976 \citep{kroy}. Kroy used Hinktikka's deontic logic to formalize the Formula of Universal Law and
@@
 that Kroy relies on, then examine the differences between his logic and DDL, and finally implement 
-and test both of Kroy's formalizations.%
+and test Kroy's formalization of the FUL%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-Kroy's logic relies heavily on some notion of identity or agency. The logic must be capable of 
-expressing statements like ``x does action", which I can write as ``x is the subject of the sentence
- `does action.'" This requires defining a subject.%
+Kroy's logic also requires the notion of a subject, will I define as a new type, just as I did
+for my implementation.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-Kroy also defines a substitution operator\footnote{See page 196 in Kroy's original paper \cite{kroy}.}. $P (d/e)$ is read in his logic as ``P with e substituted 
-for d." DDL has no such notion of substitution, so I will define a more generalized notion of an ``open 
-sentence." An open sentence takes as input a subject and returns a complete or ``closed" DDL formula by, 
-in effect, binding the free variable in the sentence to the input. For example, 
-``does action" is an open sentence that can be instantiated with a subject.%
+Kroy also defines a substitution operator\footnote{See page 196 in \citet{kroy}.}. 
+$P (d/e)$ is read in his logic as ``P with e substituted 
+for d.'' DDL has no such notion of substitution, so I will use the more generalized notion of an ``open 
+sentence,'' as I did for my formalization. An open sentence takes as input a subject and returns a 
+complete or ``closed'' DDL formula by binding the free variable in the sentence to the input. For example, 
+``does action'' is an open sentence that can be instantiated with a subject.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupcmt{``P sub (d/e)" can be written as ``S(e)", where S(d) = P%
+\isamarkupcmt{``$P$ sub $(d/e)$'' can be written as ``$S(e)$'', where $S(d) = P$.%
 }\isanewline
 %
-\isamarkupcmt{The terms that we substitute into are actually instantiations of an open sentence, and substitution 
-just requires re-instantiating the open sentence with a different subject.%
-}%
-\begin{isamarkuptext}%
-\textbf{New Operators}
-
-Because Isabelle is strongly typed, we need to define new operators to handle open sentences. These operators 
-are similar to DDL's original operators. We could probably do without these abbreviations, but they will 
-simplify the notation and make it look more similar to Kroy's original paper.%
+\isamarkupcmt{The terms that we substitute into are instantiations of an open sentence, and substitution 
+re-instantiates the open sentence with a different subject.%
+}%
+\begin{isamarkuptext}%
+\noindent \textbf{New Operators}
+
+Because Isabelle is strongly typed, I define new operators to handle open sentences. These operators 
+are similar to DDL's original operators and will simplify notation.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlemph P\ {\isacharbraceleft}A{\isacharbraceright}\ {\isasymequiv}\ {\isasymlambda}x{\isachardot}\ P\ {\isacharbraceleft}A{\isacharparenleft}x{\isacharparenright}{\isacharbraceright}{\isachardoublequoteclose}%
-\textbf{Differences Between Kroy's Logic (Kr) and DDL}
+\noindent \textbf{Differences Between Kroy's Logic (Kr) and DDL}
 %
@@
 There is potential for complication because Kroy's original paper uses a different logic than DDL. 
-His custom logic is a slight modification of Hintikka's deontic logic \cite{hintikka}. In this section, 
-I will determine if some of the semantic properties that Kroy's logic (which I will now call Kr) requires 
-hold in DDL. These differences may become important later and can explain differences in my results and 
-Kroy's.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\emph{Deontic alternatives versus the neighborhood semantics}
+His custom logic is a slight modification of Hintikka's deontic logic \citep{hintikka}. In this section, 
+I examine if the semantic properties that Kroy's logic (which I abbreviate to Kr) requires 
+hold in DDL. These differences may explain limitations of Kroy's formalization (including failed tests), but I argue that 
+the alternative properties of DDL cohere better with moral intuition. Thus, even if Kroy's formalization
+would pass more tests if it were implemented using Hintikka's logic, the logic itself would be less 
+morally plausible than DDL, and would thus remain a worse implementation of automated Kantian ethics.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\noindent \emph{Deontic alternatives versus the neighborhood semantics}
 %
@@
 The most faithful interpretation of Kr is that if $A$ is permissible in a context, then 
-it must be true at some world in that context. Kr operates under the ``deontic alternatives" or Kripke semantics, 
-summarized by Solt \cite{solt} as follows: ``A proposition of the sort $O A$ is true at the actual world $w$ if and
-only if $A$ is true at every deontic alternative world to $w$." Under this view, permissible propositions
-are obligated at some deontic alternatives, or other worlds in the system, but not at all of them. Let's 
-see if this holds in DDL.%
+it must be true at some world in that context. Kr operates under the ``deontic alternatives'' or Kripke semantics, 
+summarized by Solt \citep{solt} as follows: ``A proposition of the sort $O A$ is true at the actual world $w$ if and
+only if $A$ is true at every deontic alternative world to $w$.'' Under this view, permissible propositions
+are obligated at some deontic alternatives, or other worlds in the system, but not at all of them. This
+property does not hold in DDL.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-Remember that DDL uses neighborhood semantics, not the deontic alternatives view, which is why this
+DDL uses neighborhood semantics, not the deontic alternatives view, which is why this
  proposition fails in DDL. In DDL, the $ob$ function abstracts away the notion of
@@
 statements should be true at some deontic alternative, it's not clear that permissible statements
- must be realized at some world. In some ways, this also coheres with our understanding of obligation. There 
-are permissible actions like ``Lavanya buys a red folder" that might not happen in any universe.
+ must be realized at some world. This also coheres with our understanding of obligation. There 
+are permissible actions like ``Lavanya buys a red folder'' that might not happen in any universe.
 
 An even stricter version of the semantics that Kr requires is that if something is permissible at a world, 
-then it is obligatory at some world. This is a straightforward application of the Kripke semantics. Let's
-test this proposition.%
+then it is obligatory at some world. This is a straightforward application of the Kripke semantics. This
+also fails in DDL.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 alternatives or Kripke semantics. This also seems to cohere with our moral intuitions. The statement 
-``Lavanya buys a red folder" is permissible in the current world, but it's hard to see why it would 
+``Lavanya buys a red folder'' is permissible in the current world, but it's hard to see why it would 
 be oblgiatory in any world.
 
-One implication of the Kripke semantics is that Kr disallows ``vacuously permissible statements." In 
+Another implication of the Kripke semantics is that Kr disallows ``vacuously permissible statements.'' In 
 other words, if something is permissible it has to be obligated at some deontically perfect alternative. 
@@
 In order to make this true, we'd have to require that everything is either obligatory or
-prohibited somewhere. Sadly, that breaks everything and destroys the 
-notion of permissibility everywhere \footnote{See Appendix for an examination of a buggy version of DDL that led to this insight.}. 
-If something breaks later in this section, it may be because of vacuous permissibility.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\emph{Obligatory statements should be permissible}
-%
-\begin{isamarkuptext}%
-Kr includes the intuitively appealing theorem that if a statement is obligated at a world, then it 
-is permissible at that world\footnote{This follows straightforwardly from the Kripke semantics. If proposition $A$ is 
-obligated at world $w$, this means that at all of $w$'s neighbors, $O A$ holds. Therefore, 
-$\exists w'$ such that $w$ sees $w'$ and $O A$ holds at $w'$ so $A$ is permissible at $w$.}. Let's see 
-if that also holds in DDL.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ ob{\isacharunderscore}implies{\isacharunderscore}perm{\isacharcolon}\isanewline
-\ \ \isakeyword{fixes}\ A\ w\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}O\ {\isacharbraceleft}A{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ P\ {\isacharbraceleft}A{\isacharbraceright}\ w{\isachardoublequoteclose}\isanewline
-\ \ \isacommand{nitpick}\isamarkupfalse%
-\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{oops}\isamarkupfalse%
-\isanewline
-%
-\isamarkupcmt{\color{blue} Nitpick found a counterexample for card i = 2:
-
-  Free variable:
-    A = ($\lambda x. \_$)($i_1$ := False, $i_2$ := True)\color{black}%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-Intuitively, it seems untenable for any ethical theory to not include this principle. My 
-formalization should add this as an axiom.%
-\end{isamarkuptext}\isamarkuptrue%
+prohibited somewhere, but this makes permissibility impossible, which is clearly undesirable.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
 %
@@
 %
-\isamarkupsubsubsection{The Categorical Imperative \label{sec: kroy_ful}%
+\isamarkupsubsubsection{Kroy's formalization of the FUL \label{sec: kroy_ful}%
 }
@@
 \begin{isamarkuptext}%
-I will now implement Kroy's formalization of the Formula of Universal Law. Recall that the FUL says
-``act only in accordance with that maxim which you can at the same time will a universal law" \cite{groundwork}.
+I now implement Kroy's formalization of the Formula of Universal Law. Recall that the FUL says
+``act only in accordance with that maxim which you can at the same time will a universal law'' \citep{groundwork}.
 Kroy interprets this to mean that if an action is permissible for a specific agent, then it must be permissible for everyone.
@@
 \ FUL{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}FUL\ {\isasymequiv}\ {\isasymforall}w\ A{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isasymexists}p{\isacharcolon}{\isacharcolon}s{\isachardot}\ {\isacharparenleft}{\isacharparenleft}P\ {\isacharbraceleft}A\ p{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}\ \ {\isasymlongrightarrow}{\isacharparenleft}\ {\isacharparenleft}{\isasymforall}p{\isachardot}{\isacharparenleft}\ P\ {\isacharbraceleft}A\ p{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isacharparenright}\ {\isachardoublequoteclose}\isanewline
-\isanewline
 %
@@
 %:%28=7%:%
-%:%40=11%:%
-%:%41=12%:%
-%:%42=13%:%
-%:%43=14%:%
-%:%44=15%:%
-%:%45=16%:%
-%:%46=17%:%
-%:%47=18%:%
-%:%48=19%:%
-%:%49=20%:%
-%:%50=21%:%
-%:%51=22%:%
-%:%52=23%:%
-%:%53=24%:%
-%:%54=25%:%
-%:%55=26%:%
-%:%56=27%:%
-%:%57=28%:%
-%:%58=29%:%
-%:%59=30%:%
-%:%60=31%:%
-%:%61=32%:%
-%:%62=33%:%
-%:%97=62%:%
-%:%109=64%:%
-%:%110=65%:%
-%:%111=66%:%
-%:%112=67%:%
-%:%113=68%:%
-%:%122=70%:%
-%:%134=72%:%
-%:%135=73%:%
-%:%136=74%:%
-%:%138=76%:%
-%:%139=76%:%
-%:%140=76%:%
-%:%143=78%:%
-%:%144=79%:%
-%:%145=80%:%
-%:%146=81%:%
-%:%147=82%:%
-%:%149=84%:%
-%:%150=84%:%
-%:%152=85%:%
-%:%153=85%:%
-%:%155=86%:%
-%:%156=87%:%
-%:%159=89%:%
-%:%160=90%:%
-%:%161=91%:%
-%:%162=92%:%
-%:%163=93%:%
-%:%165=95%:%
-%:%166=95%:%
-%:%167=96%:%
-%:%168=97%:%
-%:%169=97%:%
+%:%32=9%:%
+%:%44=11%:%
+%:%45=12%:%
+%:%46=13%:%
+%:%47=14%:%
+%:%48=15%:%
+%:%49=16%:%
+%:%50=17%:%
+%:%51=18%:%
+%:%52=19%:%
+%:%53=20%:%
+%:%54=21%:%
+%:%55=22%:%
+%:%56=23%:%
+%:%57=24%:%
+%:%58=25%:%
+%:%59=26%:%
+%:%60=27%:%
+%:%61=28%:%
+%:%62=29%:%
+%:%63=30%:%
+%:%64=31%:%
+%:%65=32%:%
+%:%66=33%:%
+%:%75=36%:%
+%:%87=38%:%
+%:%88=39%:%
+%:%89=40%:%
+%:%90=41%:%
+%:%91=42%:%
+%:%92=43%:%
+%:%93=44%:%
+%:%94=45%:%
+%:%95=46%:%
+%:%96=47%:%
+%:%97=48%:%
+%:%98=49%:%
+%:%99=50%:%
+%:%100=51%:%
+%:%101=52%:%
+%:%102=53%:%
+%:%103=54%:%
+%:%104=55%:%
+%:%105=56%:%
+%:%106=57%:%
+%:%107=58%:%
+%:%108=59%:%
+%:%109=60%:%
+%:%110=61%:%
+%:%145=90%:%
+%:%157=92%:%
+%:%158=93%:%
+%:%159=94%:%
+%:%160=95%:%
+%:%161=96%:%
 %:%170=98%:%
-%:%171=99%:%
-%:%172=99%:%
-%:%173=100%:%
-%:%174=101%:%
-%:%175=101%:%
-%:%176=102%:%
-%:%178=104%:%
-%:%179=105%:%
-%:%180=106%:%
-%:%182=108%:%
-%:%183=108%:%
-%:%184=109%:%
-%:%185=110%:%
-%:%186=110%:%
-%:%187=111%:%
-%:%188=114%:%
-%:%191=117%:%
-%:%192=118%:%
-%:%193=119%:%
-%:%194=120%:%
-%:%195=121%:%
-%:%198=123%:%
-%:%201=125%:%
-%:%202=126%:%
-%:%203=127%:%
-%:%204=128%:%
-%:%205=129%:%
-%:%206=130%:%
-%:%208=132%:%
-%:%209=132%:%
-%:%210=133%:%
-%:%211=134%:%
-%:%212=135%:%
-%:%213=135%:%
-%:%215=135%:%
-%:%219=135%:%
-%:%220=135%:%
-%:%222=136%:%
-%:%223=137%:%
-%:%224=138%:%
-%:%225=139%:%
-%:%235=141%:%
-%:%236=142%:%
-%:%237=143%:%
-%:%238=144%:%
-%:%239=145%:%
-%:%240=146%:%
-%:%241=147%:%
-%:%242=148%:%
-%:%243=149%:%
-%:%244=150%:%
-%:%246=152%:%
-%:%247=152%:%
-%:%248=153%:%
-%:%249=154%:%
-%:%250=155%:%
-%:%251=155%:%
+%:%182=100%:%
+%:%183=101%:%
+%:%185=103%:%
+%:%186=103%:%
+%:%187=103%:%
+%:%190=105%:%
+%:%191=106%:%
+%:%192=107%:%
+%:%193=108%:%
+%:%194=109%:%
+%:%195=110%:%
+%:%197=112%:%
+%:%198=112%:%
+%:%200=113%:%
+%:%201=113%:%
+%:%203=114%:%
+%:%204=115%:%
+%:%207=117%:%
+%:%208=118%:%
+%:%209=119%:%
+%:%210=120%:%
+%:%212=122%:%
+%:%213=122%:%
+%:%214=123%:%
+%:%215=124%:%
+%:%216=124%:%
+%:%217=125%:%
+%:%218=126%:%
+%:%219=126%:%
+%:%220=127%:%
+%:%221=128%:%
+%:%222=128%:%
+%:%223=129%:%
+%:%225=131%:%
+%:%226=132%:%
+%:%227=133%:%
+%:%229=135%:%
+%:%230=135%:%
+%:%231=136%:%
+%:%232=137%:%
+%:%233=137%:%
+%:%234=138%:%
+%:%235=140%:%
+%:%238=142%:%
+%:%239=143%:%
+%:%240=144%:%
+%:%241=145%:%
+%:%242=146%:%
+%:%243=147%:%
+%:%244=148%:%
+%:%247=150%:%
+%:%250=152%:%
+%:%251=153%:%
+%:%252=154%:%
 %:%253=155%:%
-%:%257=155%:%
-%:%258=155%:%
-%:%260=156%:%
-%:%261=157%:%
-%:%262=158%:%
-%:%263=159%:%
-%:%273=162%:%
-%:%274=163%:%
-%:%275=164%:%
-%:%276=165%:%
-%:%277=166%:%
-%:%278=167%:%
-%:%279=168%:%
-%:%280=169%:%
-%:%281=170%:%
-%:%283=173%:%
-%:%284=173%:%
-%:%285=174%:%
-%:%286=175%:%
-%:%287=176%:%
-%:%288=176%:%
-%:%290=176%:%
-%:%294=176%:%
-%:%295=176%:%
-%:%297=177%:%
-%:%298=178%:%
-%:%299=179%:%
-%:%300=180%:%
-%:%310=182%:%
-%:%311=183%:%
-%:%312=184%:%
-%:%313=185%:%
-%:%316=187%:%
-%:%319=189%:%
-%:%320=190%:%
-%:%321=191%:%
-%:%322=192%:%
-%:%323=193%:%
-%:%325=195%:%
-%:%326=195%:%
-%:%327=196%:%
-%:%328=197%:%
-%:%329=198%:%
-%:%330=198%:%
+%:%254=156%:%
+%:%255=157%:%
+%:%257=159%:%
+%:%258=159%:%
+%:%259=160%:%
+%:%260=161%:%
+%:%261=162%:%
+%:%262=162%:%
+%:%264=162%:%
+%:%268=162%:%
+%:%269=162%:%
+%:%271=163%:%
+%:%272=164%:%
+%:%273=165%:%
+%:%274=166%:%
+%:%284=168%:%
+%:%285=169%:%
+%:%286=170%:%
+%:%287=171%:%
+%:%288=172%:%
+%:%289=173%:%
+%:%290=174%:%
+%:%291=175%:%
+%:%292=176%:%
+%:%293=177%:%
+%:%295=179%:%
+%:%296=179%:%
+%:%297=180%:%
+%:%298=181%:%
+%:%299=182%:%
+%:%300=182%:%
+%:%302=182%:%
+%:%306=182%:%
+%:%307=182%:%
+%:%309=183%:%
+%:%310=184%:%
+%:%311=185%:%
+%:%312=186%:%
+%:%322=188%:%
+%:%323=189%:%
+%:%324=190%:%
+%:%325=191%:%
+%:%326=192%:%
+%:%327=193%:%
+%:%328=194%:%
+%:%329=195%:%
+%:%330=196%:%
 %:%332=198%:%
-%:%336=198%:%
-%:%337=198%:%
-%:%339=199%:%
-%:%340=200%:%
-%:%341=201%:%
-%:%342=202%:%
-%:%352=204%:%
-%:%353=205%:%
-%:%362=210%:%
-%:%374=212%:%
-%:%375=213%:%
-%:%376=214%:%
-%:%377=215%:%
-%:%378=216%:%
-%:%380=217%:%
-%:%381=217%:%
-%:%382=218%:%
-%:%384=219%:%
-%:%385=220%:%
-%:%386=221%:%
-%:%389=223%:%
-%:%391=225%:%
-%:%392=225%:%
-%:%393=226%:%
-%:%394=227%:%
-%:%395=227%:%
-%:%397=227%:%
-%:%401=227%:%
-%:%402=227%:%
-%:%404=228%:%
-%:%405=229%:%
-%:%406=230%:%
-%:%407=231%:%
-%:%408=232%:%
-%:%409=233%:%
-%:%419=235%:%
-%:%421=237%:%
-%:%422=237%:%
-%:%424=239%:%
-%:%426=241%:%
-%:%427=241%:%
-%:%428=241%:%
-%:%430=241%:%
-%:%434=241%:%
-%:%435=241%:%
-%:%437=242%:%
-%:%438=243%:%
-%:%439=244%:%
-%:%440=245%:%
-%:%450=247%:%
-%:%451=248%:%
-%:%452=249%:%
-%:%453=250%:%
-%:%462=253%:%
-%:%474=255%:%
-%:%475=256%:%
-%:%476=257%:%
-%:%477=258%:%
-%:%478=259%:%
-%:%479=260%:%
-%:%480=261%:%
-%:%481=262%:%
-%:%482=263%:%
-%:%486=265%:%
-%:%490=267%:%
-%:%491=268%:%
-%:%492=269%:%
-%:%494=271%:%
-%:%495=271%:%
-%:%497=272%:%
-%:%498=273%:%
-%:%499=274%:%
-%:%500=275%:%
-%:%501=276%:%
-%:%502=277%:%
-%:%503=278%:%
-%:%504=278%:%
-%:%505=279%:%
-%:%506=280%:%
-%:%507=280%:%
-%:%508=281%:%
-%:%511=282%:%
-%:%515=282%:%
-%:%516=282%:%
-%:%518=283%:%
-%:%519=284%:%
-%:%529=286%:%
-%:%530=287%:%
-%:%531=288%:%
-%:%532=289%:%
-%:%533=290%:%
-%:%534=291%:%
-%:%535=292%:%
-%:%536=293%:%
-%:%537=294%:%
-%:%538=295%:%
-%:%539=296%:%
-%:%540=297%:%
-%:%541=298%:%
-%:%542=299%:%
-%:%543=300%:%
-%:%544=301%:%
-%:%545=302%:%
-%:%546=303%:%
-%:%550=305%:%
-%:%551=306%:%
-%:%553=308%:%
-%:%554=308%:%
-%:%556=309%:%
-%:%557=309%:%
-%:%558=310%:%
-%:%559=311%:%
-%:%560=311%:%
-%:%561=312%:%
-%:%564=313%:%
-%:%568=313%:%
-%:%569=313%:%
-%:%570=314%:%
-%:%571=314%:%
-%:%572=315%:%
-%:%573=315%:%
-%:%574=316%:%
-%:%575=316%:%
-%:%576=316%:%
-%:%577=317%:%
-%:%587=319%:%
-%:%588=320%:%
-%:%589=321%:%
-%:%590=322%:%
-%:%594=324%:%
-%:%598=326%:%
-%:%599=327%:%
-%:%600=328%:%
-%:%604=330%:%
-%:%605=331%:%
-%:%607=333%:%
-%:%608=333%:%
-%:%621=354%:%
-%:%622=355%:%
-%:%623=355%:%
-%:%625=356%:%
+%:%333=198%:%
+%:%334=199%:%
+%:%335=200%:%
+%:%336=201%:%
+%:%337=201%:%
+%:%339=201%:%
+%:%343=201%:%
+%:%344=201%:%
+%:%346=202%:%
+%:%347=203%:%
+%:%348=204%:%
+%:%349=205%:%
+%:%359=207%:%
+%:%360=208%:%
+%:%382=234%:%
+%:%394=236%:%
+%:%395=237%:%
+%:%396=238%:%
+%:%397=239%:%
+%:%398=240%:%
+%:%400=242%:%
+%:%401=242%:%
+%:%403=243%:%
+%:%404=244%:%
+%:%405=245%:%
+%:%408=247%:%
+%:%410=249%:%
+%:%411=249%:%
+%:%412=250%:%
+%:%413=251%:%
+%:%414=251%:%
+%:%416=251%:%
+%:%420=251%:%
+%:%421=251%:%
+%:%423=252%:%
+%:%424=253%:%
+%:%425=254%:%
+%:%426=255%:%
+%:%427=256%:%
+%:%428=257%:%
+%:%438=259%:%
+%:%440=261%:%
+%:%441=261%:%
+%:%443=263%:%
+%:%445=265%:%
+%:%446=265%:%
+%:%447=265%:%
+%:%449=265%:%
+%:%453=265%:%
+%:%454=265%:%
+%:%456=266%:%
+%:%457=267%:%
+%:%458=268%:%
+%:%459=269%:%
+%:%469=271%:%
+%:%470=272%:%
+%:%471=273%:%
+%:%472=274%:%
+%:%481=277%:%
+%:%493=279%:%
+%:%494=280%:%
+%:%495=281%:%
+%:%496=282%:%
+%:%497=283%:%
+%:%498=284%:%
+%:%499=285%:%
+%:%500=286%:%
+%:%501=287%:%
+%:%505=289%:%
+%:%509=291%:%
+%:%510=292%:%
+%:%511=293%:%
+%:%513=295%:%
+%:%514=295%:%
+%:%516=296%:%
+%:%517=297%:%
+%:%518=298%:%
+%:%519=299%:%
+%:%520=300%:%
+%:%521=301%:%
+%:%522=302%:%
+%:%523=302%:%
+%:%524=303%:%
+%:%525=304%:%
+%:%526=304%:%
+%:%527=305%:%
+%:%530=306%:%
+%:%534=306%:%
+%:%535=306%:%
+%:%537=307%:%
+%:%538=308%:%
+%:%548=310%:%
+%:%549=311%:%
+%:%550=312%:%
+%:%551=313%:%
+%:%552=314%:%
+%:%553=315%:%
+%:%554=316%:%
+%:%555=317%:%
+%:%556=318%:%
+%:%557=319%:%
+%:%558=320%:%
+%:%559=321%:%
+%:%560=322%:%
+%:%561=323%:%
+%:%562=324%:%
+%:%563=325%:%
+%:%564=326%:%
+%:%565=327%:%
+%:%569=329%:%
+%:%570=330%:%
+%:%572=332%:%
+%:%573=332%:%
+%:%575=333%:%
+%:%576=333%:%
+%:%577=334%:%
+%:%578=335%:%
+%:%579=335%:%
+%:%580=336%:%
+%:%583=337%:%
+%:%587=337%:%
+%:%588=337%:%
+%:%589=338%:%
+%:%590=338%:%
+%:%591=339%:%
+%:%592=339%:%
+%:%593=340%:%
+%:%594=340%:%
+%:%595=340%:%
+%:%596=341%:%
+%:%606=343%:%
+%:%607=344%:%
+%:%608=345%:%
+%:%609=346%:%
+%:%613=348%:%
+%:%617=350%:%
+%:%618=351%:%
+%:%619=352%:%
+%:%623=354%:%
+%:%624=355%:%
 %:%626=357%:%
-%:%627=358%:%
-%:%628=359%:%
-%:%629=360%:%
-%:%630=361%:%
-%:%631=361%:%
-%:%633=362%:%
-%:%634=363%:%
-%:%635=363%:%
-%:%636=364%:%
-%:%637=365%:%
-%:%638=365%:%
-%:%640=366%:%
-%:%641=367%:%
-%:%644=369%:%
-%:%645=370%:%
-%:%647=372%:%
-%:%648=372%:%
-%:%649=373%:%
-%:%650=374%:%
-%:%651=374%:%
-%:%653=374%:%
-%:%657=374%:%
-%:%658=374%:%
-%:%660=375%:%
-%:%661=376%:%
-%:%662=377%:%
-%:%663=378%:%
-%:%664=379%:%
-%:%665=380%:%
-%:%666=381%:%
-%:%676=383%:%
-%:%677=384%:%
-%:%678=385%:%
-%:%681=387%:%
-%:%682=388%:%
-%:%683=389%:%
-%:%684=390%:%
-%:%685=391%:%
-%:%686=392%:%
-%:%689=394%:%
-%:%691=396%:%
-%:%692=396%:%
-%:%693=397%:%
-%:%696=398%:%
-%:%700=398%:%
-%:%701=398%:%
-%:%703=399%:%
-%:%709=399%:%
-%:%712=400%:%
-%:%713=401%:%
-%:%714=401%:%
-%:%715=402%:%
-%:%716=403%:%
-%:%717=404%:%
-%:%718=404%:%
-%:%720=404%:%
-%:%724=404%:%
-%:%725=404%:%
-%:%727=405%:%
-%:%728=406%:%
-%:%729=407%:%
-%:%730=408%:%
-%:%731=409%:%
-%:%741=411%:%
-%:%742=412%:%
-%:%743=413%:%
-%:%744=414%:%
-%:%745=415%:%
-%:%746=416%:%
-%:%747=417%:%
-%:%748=418%:%
-%:%749=419%:%
-%:%753=422%:%
-%:%754=423%:%
-%:%755=424%:%
-%:%756=425%:%
-%:%757=426%:%
-%:%758=427%:%
-%:%759=428%:%
-%:%760=429%:%
-%:%761=430%:%
-%:%762=431%:%
-%:%763=432%:%
-%:%764=433%:%
-%:%773=435%:%
-%:%785=437%:%
-%:%786=438%:%
-%:%787=439%:%
-%:%789=441%:%
-%:%790=441%:%
-%:%791=442%:%
-%:%792=443%:%
-%:%793=444%:%
-%:%794=444%:%
-%:%796=444%:%
-%:%800=444%:%
-%:%801=444%:%
-%:%803=445%:%
-%:%804=446%:%
-%:%805=447%:%
-%:%806=448%:%
-%:%816=450%:%
-%:%817=451%:%
-%:%818=452%:%
-%:%822=454%:%
-%:%824=456%:%
-%:%825=456%:%
-%:%826=457%:%
-%:%827=458%:%
-%:%828=459%:%
-%:%829=459%:%
-%:%831=459%:%
-%:%835=459%:%
-%:%836=459%:%
-%:%838=460%:%
-%:%839=461%:%
-%:%840=462%:%
-%:%841=463%:%
-%:%851=465%:%
-%:%852=466%:%
-%:%854=468%:%
-%:%855=468%:%
-%:%856=469%:%
-%:%857=470%:%
-%:%858=471%:%
-%:%859=471%:%
-%:%861=471%:%
-%:%865=471%:%
-%:%866=471%:%
-%:%868=472%:%
-%:%869=473%:%
-%:%870=474%:%
-%:%871=475%:%
-%:%872=476%:%
-%:%882=478%:%
-%:%883=479%:%
-%:%885=481%:%
-%:%886=481%:%
-%:%887=482%:%
-%:%888=483%:%
-%:%891=484%:%
-%:%895=484%:%
-%:%896=484%:%
-%:%897=484%:%
-%:%906=486%:%
-%:%907=487%:%
-%:%908=488%:%
-%:%909=489%:%
-%:%911=491%:%
-%:%912=491%:%
-%:%913=492%:%
-%:%914=493%:%
-%:%917=494%:%
-%:%921=494%:%
-%:%922=494%:%
-%:%923=494%:%
-%:%932=496%:%
-%:%933=497%:%
-%:%935=499%:%
-%:%936=499%:%
-%:%937=500%:%
-%:%938=501%:%
-%:%939=502%:%
-%:%940=502%:%
-%:%942=502%:%
-%:%946=502%:%
-%:%947=502%:%
-%:%949=503%:%
-%:%950=504%:%
-%:%951=505%:%
-%:%952=506%:%
-%:%962=508%:%
-%:%963=509%:%
-%:%964=510%:%
-%:%965=511%:%
-%:%966=512%:%
-%:%967=513%:%
-%:%969=515%:%
-%:%970=515%:%
-%:%971=516%:%
-%:%972=517%:%
-%:%973=518%:%
-%:%974=519%:%
-%:%975=519%:%
-%:%977=519%:%
-%:%981=519%:%
-%:%982=519%:%
-%:%984=520%:%
-%:%985=521%:%
-%:%986=522%:%
-%:%987=523%:%
-%:%988=524%:%
-%:%989=525%:%
-%:%999=527%:%
-%:%1000=528%:%
-%:%1001=529%:%
-%:%1002=530%:%
-%:%1003=531%:%
-%:%1004=532%:%
-%:%1006=534%:%
-%:%1007=534%:%
-%:%1008=535%:%
-%:%1009=536%:%
-%:%1012=537%:%
-%:%1016=537%:%
-%:%1017=537%:%
-%:%1019=538%:%
-%:%1029=540%:%
-%:%1030=541%:%
-%:%1032=542%:%
-%:%1033=542%:%
-%:%1034=543%:%
-%:%1035=544%:%
-%:%1036=544%:%
-%:%1038=544%:%
-%:%1042=544%:%
-%:%1043=544%:%
-%:%1045=545%:%
-%:%1046=546%:%
-%:%1047=547%:%
-%:%1048=548%:%
-%:%1049=549%:%
-%:%1072=555%:%
-%:%1073=556%:%
-%:%1074=557%:%
-%:%1075=558%:%
-%:%1084=560%:%
-%:%1096=562%:%
-%:%1097=563%:%
-%:%1098=564%:%
-%:%1099=565%:%
-%:%1103=567%:%
-%:%1104=568%:%
-%:%1106=570%:%
-%:%1107=570%:%
-%:%1108=571%:%
-%:%1109=572%:%
-%:%1110=572%:%
-%:%1111=573%:%
-%:%1114=574%:%
-%:%1118=574%:%
-%:%1119=574%:%
-%:%1120=574%:%
-%:%1122=575%:%
-%:%1123=576%:%
-%:%1133=578%:%
-%:%1134=579%:%
-%:%1135=580%:%
-%:%1136=581%:%
-%:%1137=582%:%
-%:%1138=583%:%
-%:%1139=584%:%
-%:%1140=585%:%
-%:%1141=586%:%
-%:%1142=587%:%
-%:%1143=588%:%
-%:%1144=589%:%
-%:%1145=590%:%
-%:%1146=591%:%
-%:%1147=592%:%
-%:%1149=594%:%
-%:%1150=594%:%
-%:%1151=595%:%
-%:%1152=596%:%
-%:%1153=597%:%
-%:%1154=597%:%
-%:%1156=597%:%
-%:%1160=597%:%
-%:%1161=597%:%
-%:%1163=598%:%
-%:%1164=599%:%
-%:%1165=600%:%
-%:%1166=601%:%
-%:%1167=602%:%
-%:%1168=603%:%
-%:%1178=605%:%
-%:%1179=606%:%
-%:%1180=607%:%
-%:%1181=608%:%
-%:%1185=610%:%
-%:%1186=611%:%
-%:%1187=612%:%
-%:%1189=614%:%
-%:%1190=614%:%
-%:%1191=615%:%
-%:%1192=615%:%
-%:%1194=616%:%
-%:%1195=617%:%
-%:%1196=617%:%
-%:%1197=618%:%
-%:%1198=619%:%
-%:%1199=619%:%
-%:%1200=620%:%
-%:%1203=621%:%
-%:%1207=621%:%
-%:%1208=621%:%
-%:%1210=622%:%
-%:%1211=623%:%
-%:%1212=624%:%
-%:%1222=626%:%
-%:%1223=627%:%
-%:%1224=628%:%
-%:%1225=629%:%
-%:%1227=631%:%
-%:%1228=631%:%
-%:%1229=632%:%
-%:%1231=632%:%
-%:%1235=632%:%
-%:%1236=632%:%
-%:%1238=633%:%
-%:%1246=633%:%
-%:%1247=634%:%
-%:%1248=635%:%
-%:%1249=635%:%
-%:%1250=636%:%
-%:%1252=636%:%
-%:%1256=636%:%
-%:%1257=636%:%
-%:%1259=637%:%
-%:%1269=639%:%
-%:%1270=640%:%
-%:%1271=641%:%
-%:%1279=643%:%
+%:%627=357%:%
+%:%640=378%:%
+%:%641=379%:%
+%:%642=379%:%
+%:%644=380%:%
+%:%645=381%:%
+%:%646=382%:%
+%:%647=383%:%
+%:%648=384%:%
+%:%649=385%:%
+%:%650=385%:%
+%:%652=386%:%
+%:%653=387%:%
+%:%654=387%:%
+%:%655=388%:%
+%:%656=389%:%
+%:%657=389%:%
+%:%659=390%:%
+%:%660=391%:%
+%:%663=393%:%
+%:%664=394%:%
+%:%666=396%:%
+%:%667=396%:%
+%:%668=397%:%
+%:%669=398%:%
+%:%670=398%:%
+%:%672=398%:%
+%:%676=398%:%
+%:%677=398%:%
+%:%679=399%:%
+%:%680=400%:%
+%:%681=401%:%
+%:%682=402%:%
+%:%683=403%:%
+%:%684=404%:%
+%:%685=405%:%
+%:%695=407%:%
+%:%696=408%:%
+%:%697=409%:%
+%:%700=411%:%
+%:%701=412%:%
+%:%702=413%:%
+%:%703=414%:%
+%:%704=415%:%
+%:%705=416%:%
+%:%708=418%:%
+%:%710=420%:%
+%:%711=420%:%
+%:%712=421%:%
+%:%715=422%:%
+%:%719=422%:%
+%:%720=422%:%
+%:%722=423%:%
+%:%728=423%:%
+%:%731=424%:%
+%:%732=425%:%
+%:%733=425%:%
+%:%734=426%:%
+%:%735=427%:%
+%:%736=428%:%
+%:%737=428%:%
+%:%739=428%:%
+%:%743=428%:%
+%:%744=428%:%
+%:%746=429%:%
+%:%747=430%:%
+%:%748=431%:%
+%:%749=432%:%
+%:%750=433%:%
+%:%760=435%:%
+%:%761=436%:%
+%:%762=437%:%
+%:%763=438%:%
+%:%764=439%:%
+%:%765=440%:%
+%:%766=441%:%
+%:%767=442%:%
+%:%768=443%:%
+%:%772=446%:%
+%:%773=447%:%
+%:%774=448%:%
+%:%775=449%:%
+%:%776=450%:%
+%:%777=451%:%
+%:%778=452%:%
+%:%779=453%:%
+%:%780=454%:%
+%:%781=455%:%
+%:%782=456%:%
+%:%783=457%:%
+%:%792=459%:%
+%:%804=461%:%
+%:%805=462%:%
+%:%806=463%:%
+%:%808=465%:%
+%:%809=465%:%
+%:%810=466%:%
+%:%811=467%:%
+%:%812=468%:%
+%:%813=468%:%
+%:%815=468%:%
+%:%819=468%:%
+%:%820=468%:%
+%:%822=469%:%
+%:%823=470%:%
+%:%824=471%:%
+%:%825=472%:%
+%:%835=474%:%
+%:%836=475%:%
+%:%837=476%:%
+%:%841=478%:%
+%:%843=480%:%
+%:%844=480%:%
+%:%845=481%:%
+%:%846=482%:%
+%:%847=483%:%
+%:%848=483%:%
+%:%850=483%:%
+%:%854=483%:%
+%:%855=483%:%
+%:%857=484%:%
+%:%858=485%:%
+%:%859=486%:%
+%:%860=487%:%
+%:%870=489%:%
+%:%871=490%:%
+%:%873=492%:%
+%:%874=492%:%
+%:%875=493%:%
+%:%876=494%:%
+%:%877=495%:%
+%:%878=495%:%
+%:%880=495%:%
+%:%884=495%:%
+%:%885=495%:%
+%:%887=496%:%
+%:%888=497%:%
+%:%889=498%:%
+%:%890=499%:%
+%:%891=500%:%
+%:%901=502%:%
+%:%902=503%:%
+%:%904=505%:%
+%:%905=505%:%
+%:%906=506%:%
+%:%907=507%:%
+%:%910=508%:%
+%:%914=508%:%
+%:%915=508%:%
+%:%916=508%:%
+%:%925=510%:%
+%:%926=511%:%
+%:%927=512%:%
+%:%928=513%:%
+%:%930=515%:%
+%:%931=515%:%
+%:%932=516%:%
+%:%933=517%:%
+%:%936=518%:%
+%:%940=518%:%
+%:%941=518%:%
+%:%942=518%:%
+%:%951=520%:%
+%:%952=521%:%
+%:%954=523%:%
+%:%955=523%:%
+%:%956=524%:%
+%:%957=525%:%
+%:%958=526%:%
+%:%959=526%:%
+%:%961=526%:%
+%:%965=526%:%
+%:%966=526%:%
+%:%968=527%:%
+%:%969=528%:%
+%:%970=529%:%
+%:%971=530%:%
+%:%981=532%:%
+%:%982=533%:%
+%:%983=534%:%
+%:%984=535%:%
+%:%985=536%:%
+%:%986=537%:%
+%:%988=539%:%
+%:%989=539%:%
+%:%990=540%:%
+%:%991=541%:%
+%:%992=542%:%
+%:%993=543%:%
+%:%994=543%:%
+%:%996=543%:%
+%:%1000=543%:%
+%:%1001=543%:%
+%:%1003=544%:%
+%:%1004=545%:%
+%:%1005=546%:%
+%:%1006=547%:%
+%:%1007=548%:%
+%:%1008=549%:%
+%:%1018=551%:%
+%:%1019=552%:%
+%:%1020=553%:%
+%:%1021=554%:%
+%:%1022=555%:%
+%:%1023=556%:%
+%:%1025=558%:%
+%:%1026=558%:%
+%:%1027=559%:%
+%:%1028=560%:%
+%:%1031=561%:%
+%:%1035=561%:%
+%:%1036=561%:%
+%:%1038=562%:%
+%:%1048=564%:%
+%:%1049=565%:%
+%:%1051=566%:%
+%:%1052=566%:%
+%:%1053=567%:%
+%:%1054=568%:%
+%:%1055=568%:%
+%:%1057=568%:%
+%:%1061=568%:%
+%:%1062=568%:%
+%:%1064=569%:%
+%:%1065=570%:%
+%:%1066=571%:%
+%:%1067=572%:%
+%:%1068=573%:%
+%:%1091=579%:%
+%:%1092=580%:%
+%:%1093=581%:%
+%:%1094=582%:%
+%:%1103=584%:%
+%:%1115=586%:%
+%:%1116=587%:%
+%:%1117=588%:%
+%:%1118=589%:%
+%:%1122=591%:%
+%:%1123=592%:%
+%:%1125=594%:%
+%:%1126=594%:%
+%:%1127=595%:%
+%:%1128=596%:%
+%:%1129=596%:%
+%:%1130=597%:%
+%:%1133=598%:%
+%:%1137=598%:%
+%:%1138=598%:%
+%:%1139=598%:%
+%:%1141=599%:%
+%:%1142=600%:%
+%:%1152=602%:%
+%:%1153=603%:%
+%:%1154=604%:%
+%:%1155=605%:%
+%:%1156=606%:%
+%:%1157=607%:%
+%:%1158=608%:%
+%:%1159=609%:%
+%:%1160=610%:%
+%:%1161=611%:%
+%:%1162=612%:%
+%:%1163=613%:%
+%:%1164=614%:%
+%:%1165=615%:%
+%:%1166=616%:%
+%:%1168=618%:%
+%:%1169=618%:%
+%:%1170=619%:%
+%:%1171=620%:%
+%:%1172=621%:%
+%:%1173=621%:%
+%:%1175=621%:%
+%:%1179=621%:%
+%:%1180=621%:%
+%:%1182=622%:%
+%:%1183=623%:%
+%:%1184=624%:%
+%:%1185=625%:%
+%:%1186=626%:%
+%:%1187=627%:%
+%:%1197=629%:%
+%:%1198=630%:%
+%:%1199=631%:%
+%:%1200=632%:%
+%:%1204=634%:%
+%:%1205=635%:%
+%:%1206=636%:%
+%:%1208=638%:%
+%:%1209=638%:%
+%:%1210=639%:%
+%:%1211=639%:%
+%:%1213=640%:%
+%:%1214=641%:%
+%:%1215=641%:%
+%:%1216=642%:%
+%:%1217=643%:%
+%:%1218=643%:%
+%:%1219=644%:%
+%:%1222=645%:%
+%:%1226=645%:%
+%:%1227=645%:%
+%:%1229=646%:%
+%:%1230=647%:%
+%:%1231=648%:%
+%:%1241=650%:%
+%:%1242=651%:%
+%:%1243=652%:%
+%:%1244=653%:%
+%:%1246=655%:%
+%:%1247=655%:%
+%:%1248=656%:%
+%:%1250=656%:%
+%:%1254=656%:%
+%:%1255=656%:%
+%:%1257=657%:%
+%:%1265=657%:%
+%:%1266=658%:%
+%:%1267=659%:%
+%:%1268=659%:%
+%:%1269=660%:%
+%:%1271=660%:%
+%:%1275=660%:%
+%:%1276=660%:%
+%:%1278=661%:%
+%:%1288=663%:%
+%:%1289=664%:%
+%:%1290=665%:%
+%:%1298=667%:%

### 2022-03-03 paper/output/document/thesis_1_intro.tex
began cleaning appendix

@@
 \begin{enumerate}
-\item In Section ??, I make a philosophical argument for why Kantian ethics is the most natural of the three major
+\item In Section \ref{whykant}, I make a philosophical argument for why Kantian ethics is the most natural of the three major
 ethical traditions (deontology, virtue ethics, utilitarianism) to formalize.
 
-\item In Section ??, I present a formalization of the practical contradiction interpretation of Kant's 
+\item In Section \ref{details}, I present a formalization of the practical contradiction interpretation of Kant's 
 Formula of Universal Law in Dyadic Deontic Logic. I implement this formalization in the Isabelle/HOL
@@
 
-\item In Sections ?? and ??, I demonstrate my system's power and flexibility by 
+\item In Sections \ref{joking} and \ref{murderer}, I demonstrate my system's power and flexibility by 
 using it to produce nuanced answers to two well-known Kantian ethical dilemmas. I show that, because 
@@
 
-\item In Section ??, I present a testing framework that can evaluate how faithful an implementation 
+\item In Section \ref{testing}, I present a testing framework that can evaluate how faithful an implementation 
 of automated Kantian ethics is. My framework includes meta-ethical tests and application tests inspired by philosophical
@@
 
-\item In Section ??, I present new ethical insights discovered using my system and argue that
+\item In Section \ref{computationalethics}, I present new ethical insights discovered using my system and argue that
 computational methods like the one presented in this paper can help philosophers address ethical problems.

### 2022-03-05 paper/output/document/appendix.tex
added will's fixes to ch5

@@
 Kroy interprets this to mean that if an action is permissible for a specific agent, then it must be permissible for everyone.
-This formalizes the moral intuition prohibiting free-riding. According to the categorical imperative, no one is a moral exception.
-Formalizing this interpretation requires using open sentences to handle the notion of substitution.%
+This formalizes the moral intuition prohibiting free-riding. According to the categorical imperative, 
+no one is a moral exception.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupcmt{In English, this statement roughly means that, if action $A$ is 
-permissible for some person $p$, then, for any person $p$, action $A$ must be permissible. The notion of ``permissible $for$" 
+\isamarkupcmt{If action $A$ is permissible for some person, then, for any person $p$, action $A$ must be 
+permissible for $p$. The notion of ``permissible for'' 
 is captured by the substitution of $x$ for $p$.%
@@
 \begin{isamarkuptext}%
-Let's check if this is already an axiom of DDL. If so, then the formalization is trivial.%
+This formalization does not hold in DDL, the base logic. This means that Kroy's formalization
+already passes one test, and that adding it as an axiom will strengthen the logic.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \endisadelimproof
-%
-\begin{isamarkuptext}%
-This formalization doesn't hold in DDL, so adding it as an axiom will change the logic.%
-\end{isamarkuptext}\isamarkuptrue%
+\isanewline
+\isanewline
 \isacommand{axiomatization}\isamarkupfalse%
@@
 \begin{isamarkuptext}%
-Consistency check: is the logic still consistent with the FUL added as an axiom?%
+Now that I have added Kroy's formalization of the FUL as an axiom, I will check that it is 
+consistent by looking for a model that satisfies it and all the other axioms of DDL.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 between DDL and Kr, implemented Kroy's formalization of the Formula of Universal Law, and showed 
-that it is both non-trivial and consistent. Now it's time to start testing!%
+that it is both non-trivial and consistent.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupsubsubsection{Application Tests\label{sec:app_tests_kroy}%
+\isamarkupsubsubsection{Testing Kroy's Formalization%
 }
@@
 \begin{isamarkuptext}%
-In the following sections, I will use the application and metaethical tests presenting in Sections \ref{sec:app_tests_naive} and \ref{sec:meta_tests_naive}
-        to tease out the strengths and weaknesses of Kroy's formalization. While the formalization is considerably
+In this section, I use my testing framework to evaluate Kroy's formalization. I find that, while 
+        the formalization is considerably
         stronger than the naive formalization, it still fails many of these tests. Some of these failures 
@@
         reveal philosophical problems with Kroy's interpretation of what the formula of universal law means.
-        I will analyze these problems in the context of philosophical scholarship explicating the content 
-        of the formula of universal law. The findings in these sections will inform milestones for my
-        custom formalization of the categorical imperative. They also serve as an example of how formalized
-        and automated ethics can reveal philosophical strengths and weaknesses of an ethical theory.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-\textbf{Murder}%
+
+        I already showed above that Kroy's formalization is stronger than DDL. Next, I test whether or
+not obligations universalize across people. This test passes, aperhaps trivially, due to the fact that 
+this property is definitionally the basis of Kroy's formalization; his formalization states, intuitively, 
+that obligations must hold across all people.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ obligation{\isacharunderscore}universalizes{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}w{\isachardot}\ {\isacharparenleft}{\isasymexists}p{\isachardot}\ O\ {\isacharbraceleft}A\ p{\isacharbraceright}\ w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ O\ {\isacharbraceleft}A\ p{\isacharbraceright}\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}true{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+\noindent \textbf{Murder}%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %:%398=240%:%
-%:%400=242%:%
-%:%401=242%:%
-%:%403=243%:%
-%:%404=244%:%
-%:%405=245%:%
-%:%408=247%:%
-%:%410=249%:%
-%:%411=249%:%
-%:%412=250%:%
-%:%413=251%:%
-%:%414=251%:%
-%:%416=251%:%
-%:%420=251%:%
-%:%421=251%:%
-%:%423=252%:%
-%:%424=253%:%
-%:%425=254%:%
-%:%426=255%:%
-%:%427=256%:%
-%:%428=257%:%
-%:%438=259%:%
+%:%400=243%:%
+%:%401=243%:%
+%:%403=244%:%
+%:%404=245%:%
+%:%405=246%:%
+%:%408=248%:%
+%:%409=249%:%
+%:%411=251%:%
+%:%412=251%:%
+%:%413=252%:%
+%:%414=253%:%
+%:%415=253%:%
+%:%417=253%:%
+%:%421=253%:%
+%:%422=253%:%
+%:%424=254%:%
+%:%425=255%:%
+%:%426=256%:%
+%:%427=257%:%
+%:%428=258%:%
+%:%429=259%:%
+%:%437=259%:%
+%:%438=260%:%
+%:%439=261%:%
 %:%440=261%:%
-%:%441=261%:%
-%:%443=263%:%
-%:%445=265%:%
-%:%446=265%:%
-%:%447=265%:%
-%:%449=265%:%
-%:%453=265%:%
-%:%454=265%:%
-%:%456=266%:%
-%:%457=267%:%
-%:%458=268%:%
-%:%459=269%:%
-%:%469=271%:%
-%:%470=272%:%
-%:%471=273%:%
-%:%472=274%:%
+%:%442=263%:%
+%:%443=264%:%
+%:%445=266%:%
+%:%446=266%:%
+%:%447=266%:%
+%:%449=266%:%
+%:%453=266%:%
+%:%454=266%:%
+%:%456=267%:%
+%:%457=268%:%
+%:%458=269%:%
+%:%459=270%:%
+%:%469=272%:%
+%:%470=273%:%
+%:%471=274%:%
+%:%472=275%:%
 %:%481=277%:%
@@
 %:%501=287%:%
-%:%505=289%:%
-%:%509=291%:%
+%:%502=288%:%
+%:%504=290%:%
+%:%505=290%:%
+%:%506=291%:%
+%:%507=292%:%
+%:%508=292%:%
 %:%510=292%:%
-%:%511=293%:%
-%:%513=295%:%
-%:%514=295%:%
-%:%516=296%:%
-%:%517=297%:%
-%:%518=298%:%
-%:%519=299%:%
-%:%520=300%:%
-%:%521=301%:%
-%:%522=302%:%
-%:%523=302%:%
-%:%524=303%:%
-%:%525=304%:%
-%:%526=304%:%
-%:%527=305%:%
-%:%530=306%:%
-%:%534=306%:%
-%:%535=306%:%
-%:%537=307%:%
-%:%538=308%:%
-%:%548=310%:%
+%:%514=292%:%
+%:%524=294%:%
+%:%528=296%:%
+%:%529=297%:%
+%:%530=298%:%
+%:%532=300%:%
+%:%533=300%:%
+%:%535=301%:%
+%:%536=302%:%
+%:%537=303%:%
+%:%538=304%:%
+%:%539=305%:%
+%:%540=306%:%
+%:%541=307%:%
+%:%542=307%:%
+%:%543=308%:%
+%:%544=309%:%
+%:%545=309%:%
+%:%546=310%:%
 %:%549=311%:%
-%:%550=312%:%
-%:%551=313%:%
-%:%552=314%:%
-%:%553=315%:%
-%:%554=316%:%
-%:%555=317%:%
-%:%556=318%:%
-%:%557=319%:%
-%:%558=320%:%
-%:%559=321%:%
-%:%560=322%:%
-%:%561=323%:%
-%:%562=324%:%
-%:%563=325%:%
-%:%564=326%:%
-%:%565=327%:%
-%:%569=329%:%
-%:%570=330%:%
-%:%572=332%:%
-%:%573=332%:%
-%:%575=333%:%
-%:%576=333%:%
-%:%577=334%:%
-%:%578=335%:%
-%:%579=335%:%
-%:%580=336%:%
-%:%583=337%:%
-%:%587=337%:%
-%:%588=337%:%
-%:%589=338%:%
-%:%590=338%:%
-%:%591=339%:%
-%:%592=339%:%
-%:%593=340%:%
-%:%594=340%:%
-%:%595=340%:%
-%:%596=341%:%
-%:%606=343%:%
-%:%607=344%:%
-%:%608=345%:%
-%:%609=346%:%
-%:%613=348%:%
-%:%617=350%:%
-%:%618=351%:%
-%:%619=352%:%
-%:%623=354%:%
-%:%624=355%:%
-%:%626=357%:%
-%:%627=357%:%
-%:%640=378%:%
-%:%641=379%:%
-%:%642=379%:%
-%:%644=380%:%
-%:%645=381%:%
-%:%646=382%:%
-%:%647=383%:%
-%:%648=384%:%
-%:%649=385%:%
-%:%650=385%:%
-%:%652=386%:%
-%:%653=387%:%
-%:%654=387%:%
-%:%655=388%:%
-%:%656=389%:%
-%:%657=389%:%
-%:%659=390%:%
-%:%660=391%:%
-%:%663=393%:%
-%:%664=394%:%
-%:%666=396%:%
-%:%667=396%:%
-%:%668=397%:%
-%:%669=398%:%
-%:%670=398%:%
-%:%672=398%:%
-%:%676=398%:%
-%:%677=398%:%
-%:%679=399%:%
-%:%680=400%:%
-%:%681=401%:%
-%:%682=402%:%
-%:%683=403%:%
-%:%684=404%:%
-%:%685=405%:%
-%:%695=407%:%
-%:%696=408%:%
-%:%697=409%:%
-%:%700=411%:%
-%:%701=412%:%
-%:%702=413%:%
-%:%703=414%:%
-%:%704=415%:%
-%:%705=416%:%
-%:%708=418%:%
-%:%710=420%:%
-%:%711=420%:%
-%:%712=421%:%
-%:%715=422%:%
-%:%719=422%:%
-%:%720=422%:%
-%:%722=423%:%
-%:%728=423%:%
-%:%731=424%:%
-%:%732=425%:%
-%:%733=425%:%
-%:%734=426%:%
-%:%735=427%:%
-%:%736=428%:%
-%:%737=428%:%
-%:%739=428%:%
-%:%743=428%:%
-%:%744=428%:%
-%:%746=429%:%
-%:%747=430%:%
-%:%748=431%:%
-%:%749=432%:%
-%:%750=433%:%
-%:%760=435%:%
-%:%761=436%:%
-%:%762=437%:%
-%:%763=438%:%
-%:%764=439%:%
-%:%765=440%:%
-%:%766=441%:%
-%:%767=442%:%
-%:%768=443%:%
-%:%772=446%:%
-%:%773=447%:%
-%:%774=448%:%
-%:%775=449%:%
-%:%776=450%:%
-%:%777=451%:%
-%:%778=452%:%
-%:%779=453%:%
-%:%780=454%:%
-%:%781=455%:%
-%:%782=456%:%
-%:%783=457%:%
-%:%792=459%:%
-%:%804=461%:%
-%:%805=462%:%
-%:%806=463%:%
-%:%808=465%:%
-%:%809=465%:%
-%:%810=466%:%
-%:%811=467%:%
-%:%812=468%:%
-%:%813=468%:%
-%:%815=468%:%
-%:%819=468%:%
-%:%820=468%:%
-%:%822=469%:%
-%:%823=470%:%
-%:%824=471%:%
-%:%825=472%:%
-%:%835=474%:%
-%:%836=475%:%
-%:%837=476%:%
-%:%841=478%:%
-%:%843=480%:%
-%:%844=480%:%
-%:%845=481%:%
-%:%846=482%:%
-%:%847=483%:%
-%:%848=483%:%
-%:%850=483%:%
-%:%854=483%:%
-%:%855=483%:%
-%:%857=484%:%
-%:%858=485%:%
-%:%859=486%:%
-%:%860=487%:%
-%:%870=489%:%
-%:%871=490%:%
-%:%873=492%:%
-%:%874=492%:%
-%:%875=493%:%
-%:%876=494%:%
-%:%877=495%:%
-%:%878=495%:%
-%:%880=495%:%
-%:%884=495%:%
-%:%885=495%:%
-%:%887=496%:%
-%:%888=497%:%
-%:%889=498%:%
-%:%890=499%:%
-%:%891=500%:%
-%:%901=502%:%
-%:%902=503%:%
-%:%904=505%:%
-%:%905=505%:%
-%:%906=506%:%
-%:%907=507%:%
-%:%910=508%:%
-%:%914=508%:%
-%:%915=508%:%
-%:%916=508%:%
-%:%925=510%:%
-%:%926=511%:%
-%:%927=512%:%
-%:%928=513%:%
-%:%930=515%:%
-%:%931=515%:%
-%:%932=516%:%
-%:%933=517%:%
-%:%936=518%:%
-%:%940=518%:%
-%:%941=518%:%
-%:%942=518%:%
-%:%951=520%:%
-%:%952=521%:%
-%:%954=523%:%
+%:%553=311%:%
+%:%554=311%:%
+%:%556=312%:%
+%:%557=313%:%
+%:%567=315%:%
+%:%568=316%:%
+%:%569=317%:%
+%:%570=318%:%
+%:%571=319%:%
+%:%572=320%:%
+%:%573=321%:%
+%:%574=322%:%
+%:%575=323%:%
+%:%576=324%:%
+%:%577=325%:%
+%:%578=326%:%
+%:%579=327%:%
+%:%580=328%:%
+%:%581=329%:%
+%:%582=330%:%
+%:%583=331%:%
+%:%584=332%:%
+%:%588=334%:%
+%:%589=335%:%
+%:%591=337%:%
+%:%592=337%:%
+%:%594=338%:%
+%:%595=338%:%
+%:%596=339%:%
+%:%597=340%:%
+%:%598=340%:%
+%:%599=341%:%
+%:%602=342%:%
+%:%606=342%:%
+%:%607=342%:%
+%:%608=343%:%
+%:%609=343%:%
+%:%610=344%:%
+%:%611=344%:%
+%:%612=345%:%
+%:%613=345%:%
+%:%614=345%:%
+%:%615=346%:%
+%:%625=348%:%
+%:%626=349%:%
+%:%627=350%:%
+%:%628=351%:%
+%:%632=353%:%
+%:%636=355%:%
+%:%637=356%:%
+%:%638=357%:%
+%:%642=359%:%
+%:%643=360%:%
+%:%645=362%:%
+%:%646=362%:%
+%:%659=383%:%
+%:%660=384%:%
+%:%661=384%:%
+%:%663=385%:%
+%:%664=386%:%
+%:%665=387%:%
+%:%666=388%:%
+%:%667=389%:%
+%:%668=390%:%
+%:%669=390%:%
+%:%671=391%:%
+%:%672=392%:%
+%:%673=392%:%
+%:%674=393%:%
+%:%675=394%:%
+%:%676=394%:%
+%:%678=395%:%
+%:%679=396%:%
+%:%682=398%:%
+%:%683=399%:%
+%:%685=401%:%
+%:%686=401%:%
+%:%687=402%:%
+%:%688=403%:%
+%:%689=403%:%
+%:%691=403%:%
+%:%695=403%:%
+%:%696=403%:%
+%:%698=404%:%
+%:%699=405%:%
+%:%700=406%:%
+%:%701=407%:%
+%:%702=408%:%
+%:%703=409%:%
+%:%704=410%:%
+%:%714=412%:%
+%:%715=413%:%
+%:%716=414%:%
+%:%719=416%:%
+%:%720=417%:%
+%:%721=418%:%
+%:%722=419%:%
+%:%723=420%:%
+%:%724=421%:%
+%:%727=423%:%
+%:%729=425%:%
+%:%730=425%:%
+%:%731=426%:%
+%:%734=427%:%
+%:%738=427%:%
+%:%739=427%:%
+%:%741=428%:%
+%:%747=428%:%
+%:%750=429%:%
+%:%751=430%:%
+%:%752=430%:%
+%:%753=431%:%
+%:%754=432%:%
+%:%755=433%:%
+%:%756=433%:%
+%:%758=433%:%
+%:%762=433%:%
+%:%763=433%:%
+%:%765=434%:%
+%:%766=435%:%
+%:%767=436%:%
+%:%768=437%:%
+%:%769=438%:%
+%:%779=440%:%
+%:%780=441%:%
+%:%781=442%:%
+%:%782=443%:%
+%:%783=444%:%
+%:%784=445%:%
+%:%785=446%:%
+%:%786=447%:%
+%:%787=448%:%
+%:%791=451%:%
+%:%792=452%:%
+%:%793=453%:%
+%:%794=454%:%
+%:%795=455%:%
+%:%796=456%:%
+%:%797=457%:%
+%:%798=458%:%
+%:%799=459%:%
+%:%800=460%:%
+%:%801=461%:%
+%:%802=462%:%
+%:%811=464%:%
+%:%823=466%:%
+%:%824=467%:%
+%:%825=468%:%
+%:%827=470%:%
+%:%828=470%:%
+%:%829=471%:%
+%:%830=472%:%
+%:%831=473%:%
+%:%832=473%:%
+%:%834=473%:%
+%:%838=473%:%
+%:%839=473%:%
+%:%841=474%:%
+%:%842=475%:%
+%:%843=476%:%
+%:%844=477%:%
+%:%854=479%:%
+%:%855=480%:%
+%:%856=481%:%
+%:%860=483%:%
+%:%862=485%:%
+%:%863=485%:%
+%:%864=486%:%
+%:%865=487%:%
+%:%866=488%:%
+%:%867=488%:%
+%:%869=488%:%
+%:%873=488%:%
+%:%874=488%:%
+%:%876=489%:%
+%:%877=490%:%
+%:%878=491%:%
+%:%879=492%:%
+%:%889=494%:%
+%:%890=495%:%
+%:%892=497%:%
+%:%893=497%:%
+%:%894=498%:%
+%:%895=499%:%
+%:%896=500%:%
+%:%897=500%:%
+%:%899=500%:%
+%:%903=500%:%
+%:%904=500%:%
+%:%906=501%:%
+%:%907=502%:%
+%:%908=503%:%
+%:%909=504%:%
+%:%910=505%:%
+%:%920=507%:%
+%:%921=508%:%
+%:%923=510%:%
+%:%924=510%:%
+%:%925=511%:%
+%:%926=512%:%
+%:%929=513%:%
+%:%933=513%:%
+%:%934=513%:%
+%:%935=513%:%
+%:%944=515%:%
+%:%945=516%:%
+%:%946=517%:%
+%:%947=518%:%
+%:%949=520%:%
+%:%950=520%:%
+%:%951=521%:%
+%:%952=522%:%
 %:%955=523%:%
-%:%956=524%:%
-%:%957=525%:%
-%:%958=526%:%
-%:%959=526%:%
-%:%961=526%:%
-%:%965=526%:%
-%:%966=526%:%
-%:%968=527%:%
-%:%969=528%:%
-%:%970=529%:%
-%:%971=530%:%
-%:%981=532%:%
-%:%982=533%:%
-%:%983=534%:%
-%:%984=535%:%
-%:%985=536%:%
-%:%986=537%:%
-%:%988=539%:%
-%:%989=539%:%
-%:%990=540%:%
-%:%991=541%:%
-%:%992=542%:%
-%:%993=543%:%
-%:%994=543%:%
-%:%996=543%:%
-%:%1000=543%:%
-%:%1001=543%:%
-%:%1003=544%:%
-%:%1004=545%:%
-%:%1005=546%:%
-%:%1006=547%:%
-%:%1007=548%:%
-%:%1008=549%:%
-%:%1018=551%:%
-%:%1019=552%:%
-%:%1020=553%:%
-%:%1021=554%:%
-%:%1022=555%:%
-%:%1023=556%:%
-%:%1025=558%:%
-%:%1026=558%:%
-%:%1027=559%:%
-%:%1028=560%:%
-%:%1031=561%:%
-%:%1035=561%:%
-%:%1036=561%:%
-%:%1038=562%:%
-%:%1048=564%:%
-%:%1049=565%:%
-%:%1051=566%:%
-%:%1052=566%:%
-%:%1053=567%:%
-%:%1054=568%:%
-%:%1055=568%:%
-%:%1057=568%:%
-%:%1061=568%:%
-%:%1062=568%:%
-%:%1064=569%:%
-%:%1065=570%:%
-%:%1066=571%:%
-%:%1067=572%:%
-%:%1068=573%:%
-%:%1091=579%:%
-%:%1092=580%:%
-%:%1093=581%:%
-%:%1094=582%:%
-%:%1103=584%:%
-%:%1115=586%:%
-%:%1116=587%:%
-%:%1117=588%:%
-%:%1118=589%:%
-%:%1122=591%:%
-%:%1123=592%:%
-%:%1125=594%:%
-%:%1126=594%:%
-%:%1127=595%:%
-%:%1128=596%:%
-%:%1129=596%:%
-%:%1130=597%:%
-%:%1133=598%:%
-%:%1137=598%:%
-%:%1138=598%:%
-%:%1139=598%:%
-%:%1141=599%:%
-%:%1142=600%:%
-%:%1152=602%:%
-%:%1153=603%:%
-%:%1154=604%:%
-%:%1155=605%:%
-%:%1156=606%:%
-%:%1157=607%:%
-%:%1158=608%:%
-%:%1159=609%:%
-%:%1160=610%:%
-%:%1161=611%:%
-%:%1162=612%:%
-%:%1163=613%:%
-%:%1164=614%:%
-%:%1165=615%:%
-%:%1166=616%:%
-%:%1168=618%:%
-%:%1169=618%:%
-%:%1170=619%:%
-%:%1171=620%:%
-%:%1172=621%:%
-%:%1173=621%:%
-%:%1175=621%:%
-%:%1179=621%:%
-%:%1180=621%:%
-%:%1182=622%:%
-%:%1183=623%:%
-%:%1184=624%:%
-%:%1185=625%:%
-%:%1186=626%:%
-%:%1187=627%:%
-%:%1197=629%:%
-%:%1198=630%:%
-%:%1199=631%:%
-%:%1200=632%:%
-%:%1204=634%:%
-%:%1205=635%:%
-%:%1206=636%:%
-%:%1208=638%:%
-%:%1209=638%:%
-%:%1210=639%:%
-%:%1211=639%:%
-%:%1213=640%:%
-%:%1214=641%:%
-%:%1215=641%:%
-%:%1216=642%:%
-%:%1217=643%:%
-%:%1218=643%:%
-%:%1219=644%:%
-%:%1222=645%:%
-%:%1226=645%:%
-%:%1227=645%:%
-%:%1229=646%:%
-%:%1230=647%:%
-%:%1231=648%:%
+%:%959=523%:%
+%:%960=523%:%
+%:%961=523%:%
+%:%970=525%:%
+%:%971=526%:%
+%:%973=528%:%
+%:%974=528%:%
+%:%975=529%:%
+%:%976=530%:%
+%:%977=531%:%
+%:%978=531%:%
+%:%980=531%:%
+%:%984=531%:%
+%:%985=531%:%
+%:%987=532%:%
+%:%988=533%:%
+%:%989=534%:%
+%:%990=535%:%
+%:%1000=537%:%
+%:%1001=538%:%
+%:%1002=539%:%
+%:%1003=540%:%
+%:%1004=541%:%
+%:%1005=542%:%
+%:%1007=544%:%
+%:%1008=544%:%
+%:%1009=545%:%
+%:%1010=546%:%
+%:%1011=547%:%
+%:%1012=548%:%
+%:%1013=548%:%
+%:%1015=548%:%
+%:%1019=548%:%
+%:%1020=548%:%
+%:%1022=549%:%
+%:%1023=550%:%
+%:%1024=551%:%
+%:%1025=552%:%
+%:%1026=553%:%
+%:%1027=554%:%
+%:%1037=556%:%
+%:%1038=557%:%
+%:%1039=558%:%
+%:%1040=559%:%
+%:%1041=560%:%
+%:%1042=561%:%
+%:%1044=563%:%
+%:%1045=563%:%
+%:%1046=564%:%
+%:%1047=565%:%
+%:%1050=566%:%
+%:%1054=566%:%
+%:%1055=566%:%
+%:%1057=567%:%
+%:%1067=569%:%
+%:%1068=570%:%
+%:%1070=571%:%
+%:%1071=571%:%
+%:%1072=572%:%
+%:%1073=573%:%
+%:%1074=573%:%
+%:%1076=573%:%
+%:%1080=573%:%
+%:%1081=573%:%
+%:%1083=574%:%
+%:%1084=575%:%
+%:%1085=576%:%
+%:%1086=577%:%
+%:%1087=578%:%
+%:%1110=584%:%
+%:%1111=585%:%
+%:%1112=586%:%
+%:%1113=587%:%
+%:%1122=589%:%
+%:%1134=591%:%
+%:%1135=592%:%
+%:%1136=593%:%
+%:%1137=594%:%
+%:%1141=596%:%
+%:%1142=597%:%
+%:%1144=599%:%
+%:%1145=599%:%
+%:%1146=600%:%
+%:%1147=601%:%
+%:%1148=601%:%
+%:%1149=602%:%
+%:%1152=603%:%
+%:%1156=603%:%
+%:%1157=603%:%
+%:%1158=603%:%
+%:%1160=604%:%
+%:%1161=605%:%
+%:%1171=607%:%
+%:%1172=608%:%
+%:%1173=609%:%
+%:%1174=610%:%
+%:%1175=611%:%
+%:%1176=612%:%
+%:%1177=613%:%
+%:%1178=614%:%
+%:%1179=615%:%
+%:%1180=616%:%
+%:%1181=617%:%
+%:%1182=618%:%
+%:%1183=619%:%
+%:%1184=620%:%
+%:%1185=621%:%
+%:%1187=623%:%
+%:%1188=623%:%
+%:%1189=624%:%
+%:%1190=625%:%
+%:%1191=626%:%
+%:%1192=626%:%
+%:%1194=626%:%
+%:%1198=626%:%
+%:%1199=626%:%
+%:%1201=627%:%
+%:%1202=628%:%
+%:%1203=629%:%
+%:%1204=630%:%
+%:%1205=631%:%
+%:%1206=632%:%
+%:%1216=634%:%
+%:%1217=635%:%
+%:%1218=636%:%
+%:%1219=637%:%
+%:%1223=639%:%
+%:%1224=640%:%
+%:%1225=641%:%
+%:%1227=643%:%
+%:%1228=643%:%
+%:%1229=644%:%
+%:%1230=644%:%
+%:%1232=645%:%
+%:%1233=646%:%
+%:%1234=646%:%
+%:%1235=647%:%
+%:%1236=648%:%
+%:%1237=648%:%
+%:%1238=649%:%
 %:%1241=650%:%
-%:%1242=651%:%
-%:%1243=652%:%
-%:%1244=653%:%
-%:%1246=655%:%
-%:%1247=655%:%
-%:%1248=656%:%
-%:%1250=656%:%
-%:%1254=656%:%
-%:%1255=656%:%
-%:%1257=657%:%
-%:%1265=657%:%
-%:%1266=658%:%
-%:%1267=659%:%
-%:%1268=659%:%
-%:%1269=660%:%
-%:%1271=660%:%
-%:%1275=660%:%
-%:%1276=660%:%
-%:%1278=661%:%
-%:%1288=663%:%
-%:%1289=664%:%
+%:%1245=650%:%
+%:%1246=650%:%
+%:%1248=651%:%
+%:%1249=652%:%
+%:%1250=653%:%
+%:%1260=655%:%
+%:%1261=656%:%
+%:%1262=657%:%
+%:%1263=658%:%
+%:%1265=660%:%
+%:%1266=660%:%
+%:%1267=661%:%
+%:%1269=661%:%
+%:%1273=661%:%
+%:%1274=661%:%
+%:%1276=662%:%
+%:%1284=662%:%
+%:%1285=663%:%
+%:%1286=664%:%
+%:%1287=664%:%
+%:%1288=665%:%
 %:%1290=665%:%
-%:%1298=667%:%
+%:%1294=665%:%
+%:%1295=665%:%
+%:%1297=666%:%
+%:%1307=668%:%
+%:%1308=669%:%
+%:%1309=670%:%
+%:%1317=672%:%

### 2022-03-05 paper/output/document/thesis_0_abstract.tex
added will's fixes to ch5

@@
 but most AI agents navigating the world today are not explicitly guided by ethics.
-Warnings from regulators, philosophers, and computer scientists about the 
+Regulators, philosophers, and computer scientists are raising the alarm about the 
 dangers of unethical artificial intelligence, from science-fiction killer robots to criminal
-sentencing algorithms prejudiced against people of color, have spurred interest in automated ethics, or the development 
+sentencing algorithms prejudiced against people of color. This is spurring interest in automated ethics, or the development 
 of machines that can perform ethical reasoning. Much prior work in automated ethics approaches the 
@@
 In this thesis, I present an implementation of automated Kantian
-ethics that is faithful to the Kantian philosophical tradition. Of the three major ethical
-traditions, Kant's categorical imperative is the most natural to formalize because it is an inviolable 
-formal rule that requires less situational awareness than other ethical theories. I formalize Kant's categorical imperative 
+ethics that is faithful to the Kantian philosophical tradition. Given an appropriately represented 
+action and minimal factual background, my system can judge the action as morally obligatory, permissible, or prohibited.
+To accomplish this, I formalize Kant's categorical imperative, or moral rule,
 in Carmo and Jones's Dyadic Deontic Logic, implement this formalization 
@@
 my implementation coheres with expected properties of Kantian ethics, as established in the literature. 
-I also use my system to reason about two ethical dilemmas used to criticize Kantian ethics: the difference
+I also use my system to derive philosophically sophisticated and nuanced solutions to two central ethical 
+dilemmas in Kantian ethical literature: the difference
 between lying and joking and the example of a murderer knocking on your door asking about the location of their
-intended victim. Finally, I examine the philosophical implications of this system, exploring its limitations 
-and its potential to help both AI agents and human beings better reason about ethics. This work serves 
+intended victim. Finally, I examine the philosophical implications of my system, exploring its limitations 
+and its potential to help AI agents, academic philosophers, and ordinary human beings better reason about ethics. This work serves 
 as an early proof-of-concept for philosophically mature AI agents and is one step towards the development 
@@
 %:%45=32%:%
+%:%46=33%:%

### 2022-03-05 paper/output/document/thesis_1_intro.tex
added will's fixes to ch5

@@
 ethical implications without explicitly performing ethical
-reasoning, in many cases, they do so without human supervision. For example, the Alleghany Family Screening 
+reasoning, in many cases they do so without human supervision. For example, the Alleghany Family Screening 
 tool can automatically trigger an investigation into a potential case of child neglect, a decision that 
@@
 A lack of engagement with prior philosophical literature also makes automated moral agents less 
-explainable, or interpretable by human observers. One example of this is Delphi, a language model that uses deep 
+explainable, or interpretable by human observers. One example of this is Delphi, an implementation of automated ethics that uses deep 
 learning to make moral judgements based on a training dataset of ethical decisions made by humans \citep{delphi}. 
@@
 ethical judgements. If a machine prescribes killing one person to save three without justifying this 
-decision, it is difficult to trust this judgement enough to act on it or endorse a machine acting on it. 
+decision, it is difficult to trust this judgement. 
 The high stakes of automated ethics require explainability to build trust and catch mistakes.
@@
 example, encoding ethics as a Markov Decision Process assumes that ethical reward can be aggregated 
-according to some discounted sum, but many philosophers reject this notion of aggregation \citep{consequentialismsep}. 
-Approaches that begin with an ethical theory, instead of a computational tool, must contend with the 
+according to some discounted sum\footnote{Markov Decision Processes usually assume that the total
+reward of a system is the discounted sum of the reward at each state, given by $r_i$. Formally, total
+reward $R=\sum_0^{\infty}\gamma^ir_i$.}, but many philosophers reject this notion of aggregation \citep{consequentialismsep}. 
+On the other hand, approaches that begin with an ethical theory, instead of a computational method, must contend with the 
 fact that ethical theories are almost always described in natural language and must be made
@@
 language to program syntax, the factual background given to the machine, such as the description of 
-an ethical dilemma, is equally as important in determining the machine's decisions. Another complication
-is that philosophers do not agree that on a single choice of ethical theory. Philosophers who
-so agree that a specific ethical theory, like Kantian ethics, is true, still debate the theory's 
+an ethical dilemma, plays a great role in the machine's decisions. Another complication
+is that philosophers do not agree that on a single choice of ethical theory. Even philosophers who
+agree that a specific ethical theory, like Kantian ethics, is true, still debate the theory's 
 details.\footnote{For examples of these debates in the case of Kantian ethics, see Section Joking
@@
 I formalize Kant's categorical imperative, or moral rule, as an axiom 
-in Carmo and Jones' Dyadic Deontic Logic (DDL), a modal logic designed to reason about 
+in Dyadic Deontic Logic (DDL), a modal logic designed to reason about 
 obligation \citep{CJDDL}. I implement my formalization in Isabelle/HOL, an interactive theorem prover 
@@
 \begin{isamarkuptext}%
-I choose to formalize Kant's moral rule in Carmo and Jones' Dyadic Deontic Logic (DDL) \citep{CJDDL}. Deontic 
-logic is a modal logic that can express obligation, or morally binding requirements. Traditional modal 
+Deontic logic is a modal logic that can express obligation, or morally binding requirements. Traditional modal 
 logics include the necessitation operator, denoted as $\Box$. In modal logic using the Kripke semantics, 
 $\Box p$ is true at world $w$ if $p$ is true at all worlds that neighbor $w$ \citep{cresswell}. Modal 
-logics  also contain the possibility operator $\diamond$, where $\diamond \, p \iff \neg (\Box (\neg p))$ 
+logics  also contain the possibility operator $\diamond$, where $\diamond \, p \longleftrightarrow \neg (\Box (\neg p))$ 
 and operators of propositional logic like $\neg, \wedge, \vee, \rightarrow$. I use DDL, in which
@@
 
-I automate Kantian ethics because it is the most natural to formalize, as I argue in Section WhyKant. 
+I automate Kantian ethics because it is the most natural to formalize, as I argue in Section \ref{whykant}. 
 Kant presents three versions of a single moral rule, known as the categorical imperative, from which 
@@
 the axioms and facts it used to generate an ethical judgement, and, in some cases, construct 
-human-readable proofs. In Sections Joking and Murderer, I use my system to arrive at 
+human-readable proofs. In Chapter \ref{applications}, I use my system to derive
 sophisticated solutions to two ethical dilemmas often used in critiques of Kantian ethics. Because 
@@
 contradict each other. I represent each of these properties as a sentence in my logic that my system 
-should be able to prove or refute. I run the tests by using Isabelle to automatically find proofs or 
+should be able to prove or refute. To run the tests, I use Isabelle to automatically find proofs or 
 countermodels for the test statements. For example, my implementation passes the contradictory 
@@
 A machine that can evaluate the moral status of a maxim can not only help machines better reason about ethics, 
-but it can also help philosophers 
-better study philosophy. I argue for ``computational ethics," or the use of computational tools to 
-make philosophical progress. I demonstrate the potential of computational ethics by presenting a 
+but it can also help philosophers better study philosophy. I argue for ``computational ethics,'' or the use of computational tools to 
+make philosophical progress, analogous to computational drug discovery or neuroscience. 
+I demonstrate the potential of computational ethics by presenting a 
 philosophical insight about which kinds of maxims are appropriate for ethical consideration that I 
@@
 automated agents navigate the world, which I will refer to as automated ethics or machine ethics interchangeably. Second, 
-my system help human philosophers reason about philosophy, which I call computational ethics.%
+my system help human philosophers reason about philosophy, which I call computational ethics. In Section 
+\ref{ordinarypeople}, I consider how computational ethics can help not only professional philosophers,
+but also augment the everyday ethical reasoning that ordinary people perform as we navigate the world.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %:%109=81%:%
-%:%113=84%:%
-%:%114=85%:%
+%:%110=82%:%
+%:%111=83%:%
 %:%115=86%:%
@@
 %:%137=108%:%
-%:%141=112%:%
-%:%142=113%:%
+%:%138=109%:%
+%:%139=110%:%
 %:%143=114%:%
@@
 %:%202=173%:%
+%:%203=174%:%
+%:%204=175%:%
+%:%205=176%:%

### 2022-03-05 paper/output/document/thesis_4_applications.tex
chaper 5 cleaned
added will's fixes to ch5

@@
 %
-\isamarkupsection{Applications \label{sec:applications}%
+\isamarkupsection{Applications \label{applications}%
 }
@@
 \begin{isamarkuptext}%
-In this chapter, I use my system to produce sophisticated, nuanced
-responses to two moral dilemmas. These dilemmas serve as examples of how my system could be used
+In this chapter, I demonstrate that my system can produce correct judgements on challenging moral 
+dilemmas that naive ethical reasoning cannot satisfactorily handle. My system can reproduce complex
+ethical judgements because it is faithful to philosophical literature.
+These dilemmas serve as examples of how my system could be used
 in practice and demonstrate my system's ability to formalize longer, more complicted ethical arguments
-than those presented in Chapter 3. 
+than those presented in Chapter \ref{details}. 
 Many of the tests in Section \ref{testing} perform metaethical reasoning, which analyzes properties
@@
 a surprise party is not the surprise itself, but rather celebrating the birthday person. The modified
-goal no longer requires belief in the falsehood and thus passes the universalizability test.
+goal\footnote{Some may worry that this argument implies that the ``means justify the ends,'' or that modifying
+an act's goal can change its moral worth. This conclusion is not only unsurprising to Kantians, but it is the
+defining feature of their theory. Under Kantian ethics, an action alone is not the kind of thing that can 
+be moral or immoral; rather, a maxim, or a circumstances, act, goal tuple, is what has moral worth. The rightness 
+of an action can hinge on the maxim's goal, circumstances, or act because these three features
+of an action are inseparable.} no longer requires belief in the falsehood and thus passes the 
+universalizability test.
 
@@
 %:%81=53%:%
-%:%90=56%:%
-%:%102=59%:%
-%:%103=60%:%
+%:%82=54%:%
+%:%83=55%:%
+%:%92=58%:%
 %:%104=61%:%
@@
 %:%123=80%:%
-%:%125=83%:%
-%:%126=83%:%
-%:%128=84%:%
-%:%129=85%:%
+%:%124=81%:%
+%:%125=82%:%
+%:%127=85%:%
+%:%128=85%:%
 %:%130=86%:%
-%:%133=89%:%
-%:%134=90%:%
+%:%131=87%:%
+%:%132=88%:%
 %:%135=91%:%
@@
 %:%139=95%:%
-%:%141=98%:%
-%:%142=98%:%
-%:%144=99%:%
-%:%145=100%:%
-%:%146=100%:%
-%:%147=101%:%
-%:%148=101%:%
-%:%149=102%:%
-%:%151=103%:%
-%:%152=103%:%
-%:%153=104%:%
-%:%154=104%:%
-%:%155=105%:%
-%:%157=106%:%
-%:%158=107%:%
+%:%140=96%:%
+%:%141=97%:%
+%:%143=100%:%
+%:%144=100%:%
+%:%146=101%:%
+%:%147=102%:%
+%:%148=102%:%
+%:%149=103%:%
+%:%150=103%:%
+%:%151=104%:%
+%:%153=105%:%
+%:%154=105%:%
+%:%155=106%:%
+%:%156=106%:%
+%:%157=107%:%
 %:%159=108%:%
@@
 %:%161=110%:%
-%:%164=114%:%
-%:%165=115%:%
+%:%162=111%:%
+%:%163=112%:%
 %:%166=116%:%
@@
 %:%173=123%:%
+%:%174=124%:%
 %:%175=125%:%
-%:%176=125%:%
-%:%177=126%:%
-%:%179=127%:%
-%:%182=129%:%
-%:%183=130%:%
+%:%177=127%:%
+%:%178=127%:%
+%:%179=128%:%
+%:%181=129%:%
 %:%184=131%:%
@@
 %:%194=141%:%
+%:%195=142%:%
 %:%196=143%:%
-%:%197=143%:%
-%:%199=144%:%
-%:%200=145%:%
+%:%198=145%:%
+%:%199=145%:%
 %:%201=146%:%
-%:%202=146%:%
-%:%203=147%:%
-%:%204=147%:%
-%:%206=148%:%
-%:%207=149%:%
-%:%208=149%:%
-%:%209=150%:%
-%:%210=150%:%
-%:%212=151%:%
-%:%215=153%:%
-%:%216=154%:%
+%:%202=147%:%
+%:%203=148%:%
+%:%204=148%:%
+%:%205=149%:%
+%:%206=149%:%
+%:%208=150%:%
+%:%209=151%:%
+%:%210=151%:%
+%:%211=152%:%
+%:%212=152%:%
+%:%214=153%:%
 %:%217=155%:%
 %:%218=156%:%
+%:%219=157%:%
 %:%220=158%:%
-%:%221=158%:%
-%:%222=159%:%
+%:%222=160%:%
 %:%223=160%:%
-%:%225=161%:%
-%:%226=161%:%
-%:%227=162%:%
-%:%229=163%:%
-%:%230=164%:%
-%:%231=164%:%
-%:%232=165%:%
-%:%234=166%:%
-%:%235=167%:%
+%:%224=161%:%
+%:%225=162%:%
+%:%227=163%:%
+%:%228=163%:%
+%:%229=164%:%
+%:%231=165%:%
+%:%232=166%:%
+%:%233=166%:%
+%:%234=167%:%
 %:%236=168%:%
@@
 %:%239=171%:%
-%:%240=171%:%
-%:%241=172%:%
-%:%243=173%:%
-%:%244=173%:%
-%:%245=174%:%
-%:%252=175%:%
-%:%253=175%:%
-%:%254=176%:%
-%:%255=176%:%
-%:%256=177%:%
-%:%257=177%:%
-%:%259=178%:%
-%:%260=179%:%
+%:%240=172%:%
+%:%241=173%:%
+%:%242=173%:%
+%:%243=174%:%
+%:%245=175%:%
+%:%246=175%:%
+%:%247=176%:%
+%:%254=177%:%
+%:%255=177%:%
+%:%256=178%:%
+%:%257=178%:%
+%:%258=179%:%
+%:%259=179%:%
 %:%261=180%:%
 %:%262=181%:%
-%:%263=181%:%
-%:%264=182%:%
-%:%265=182%:%
-%:%266=183%:%
-%:%267=183%:%
-%:%268=184%:%
-%:%269=184%:%
-%:%270=185%:%
-%:%271=185%:%
-%:%272=185%:%
-%:%274=186%:%
-%:%275=187%:%
-%:%276=187%:%
-%:%277=188%:%
-%:%287=190%:%
-%:%288=191%:%
+%:%263=182%:%
+%:%264=183%:%
+%:%265=183%:%
+%:%266=184%:%
+%:%267=184%:%
+%:%268=185%:%
+%:%269=185%:%
+%:%270=186%:%
+%:%271=186%:%
+%:%272=187%:%
+%:%273=187%:%
+%:%274=187%:%
+%:%276=188%:%
+%:%277=189%:%
+%:%278=189%:%
+%:%279=190%:%
 %:%289=192%:%
@@
 %:%300=203%:%
+%:%301=204%:%
 %:%302=205%:%
-%:%303=205%:%
-%:%304=206%:%
-%:%306=207%:%
-%:%307=208%:%
-%:%310=210%:%
-%:%311=211%:%
+%:%304=207%:%
+%:%305=207%:%
+%:%306=208%:%
+%:%308=209%:%
+%:%309=210%:%
 %:%312=212%:%
@@
 %:%318=218%:%
+%:%319=219%:%
 %:%320=220%:%
-%:%321=220%:%
-%:%322=221%:%
+%:%322=222%:%
 %:%323=222%:%
-%:%325=223%:%
-%:%326=223%:%
-%:%327=224%:%
-%:%329=225%:%
-%:%330=226%:%
-%:%331=226%:%
-%:%332=227%:%
-%:%334=228%:%
-%:%335=228%:%
-%:%336=229%:%
-%:%338=230%:%
-%:%339=230%:%
-%:%340=231%:%
-%:%343=232%:%
-%:%347=232%:%
-%:%348=232%:%
-%:%350=233%:%
-%:%351=234%:%
+%:%324=223%:%
+%:%325=224%:%
+%:%327=225%:%
+%:%328=225%:%
+%:%329=226%:%
+%:%331=227%:%
+%:%332=228%:%
+%:%333=228%:%
+%:%334=229%:%
+%:%336=230%:%
+%:%337=230%:%
+%:%338=231%:%
+%:%340=232%:%
+%:%341=232%:%
+%:%342=233%:%
+%:%345=234%:%
+%:%349=234%:%
+%:%350=234%:%
 %:%352=235%:%
@@
 %:%354=237%:%
-%:%364=240%:%
-%:%365=241%:%
+%:%355=238%:%
+%:%356=239%:%
 %:%366=242%:%
@@
 %:%402=278%:%
-%:%411=281%:%
-%:%423=284%:%
-%:%424=285%:%
-%:%425=286%:%
-%:%426=287%:%
-%:%427=288%:%
-%:%428=289%:%
-%:%429=290%:%
-%:%430=291%:%
+%:%403=279%:%
+%:%404=280%:%
+%:%405=281%:%
+%:%406=282%:%
+%:%407=283%:%
+%:%408=284%:%
+%:%409=285%:%
+%:%410=286%:%
+%:%419=289%:%
 %:%431=292%:%
@@
 %:%440=301%:%
+%:%441=302%:%
 %:%442=303%:%
-%:%443=303%:%
-%:%445=304%:%
-%:%446=304%:%
-%:%447=305%:%
-%:%448=305%:%
-%:%450=306%:%
-%:%451=307%:%
-%:%452=308%:%
-%:%453=308%:%
-%:%454=309%:%
-%:%455=309%:%
-%:%457=310%:%
-%:%458=310%:%
-%:%459=311%:%
-%:%460=311%:%
-%:%462=312%:%
-%:%463=312%:%
-%:%464=313%:%
-%:%465=313%:%
-%:%466=314%:%
-%:%468=315%:%
-%:%469=316%:%
-%:%472=318%:%
-%:%473=319%:%
-%:%474=320%:%
-%:%475=321%:%
-%:%477=323%:%
-%:%478=323%:%
-%:%480=324%:%
-%:%481=324%:%
-%:%482=325%:%
-%:%483=325%:%
-%:%484=326%:%
-%:%486=327%:%
-%:%487=327%:%
-%:%488=328%:%
-%:%489=328%:%
-%:%491=329%:%
-%:%492=329%:%
-%:%493=330%:%
-%:%494=330%:%
-%:%495=331%:%
-%:%497=332%:%
-%:%498=333%:%
-%:%514=365%:%
-%:%515=366%:%
-%:%516=367%:%
-%:%517=368%:%
-%:%518=369%:%
-%:%519=370%:%
-%:%520=371%:%
-%:%521=372%:%
+%:%443=304%:%
+%:%444=305%:%
+%:%445=306%:%
+%:%446=307%:%
+%:%447=308%:%
+%:%448=309%:%
+%:%450=311%:%
+%:%451=311%:%
+%:%453=312%:%
+%:%454=312%:%
+%:%455=313%:%
+%:%456=313%:%
+%:%458=314%:%
+%:%459=315%:%
+%:%460=316%:%
+%:%461=316%:%
+%:%462=317%:%
+%:%463=317%:%
+%:%465=318%:%
+%:%466=318%:%
+%:%467=319%:%
+%:%468=319%:%
+%:%470=320%:%
+%:%471=320%:%
+%:%472=321%:%
+%:%473=321%:%
+%:%474=322%:%
+%:%476=323%:%
+%:%477=324%:%
+%:%480=326%:%
+%:%481=327%:%
+%:%482=328%:%
+%:%483=329%:%
+%:%485=331%:%
+%:%486=331%:%
+%:%488=332%:%
+%:%489=332%:%
+%:%490=333%:%
+%:%491=333%:%
+%:%492=334%:%
+%:%494=335%:%
+%:%495=335%:%
+%:%496=336%:%
+%:%497=336%:%
+%:%499=337%:%
+%:%500=337%:%
+%:%501=338%:%
+%:%502=338%:%
+%:%503=339%:%
+%:%505=340%:%
+%:%506=341%:%
 %:%522=373%:%
+%:%523=374%:%
 %:%524=375%:%
-%:%525=375%:%
-%:%526=376%:%
-%:%527=377%:%
-%:%529=378%:%
-%:%530=378%:%
-%:%531=379%:%
-%:%533=380%:%
-%:%534=380%:%
-%:%535=381%:%
-%:%537=382%:%
-%:%538=383%:%
-%:%539=384%:%
-%:%540=385%:%
-%:%541=386%:%
-%:%542=386%:%
-%:%543=387%:%
-%:%545=388%:%
-%:%546=389%:%
-%:%547=390%:%
-%:%548=391%:%
-%:%549=392%:%
-%:%550=393%:%
-%:%551=394%:%
-%:%552=394%:%
-%:%553=395%:%
-%:%555=396%:%
-%:%556=397%:%
-%:%557=397%:%
-%:%558=398%:%
-%:%561=399%:%
-%:%565=399%:%
-%:%566=399%:%
-%:%567=399%:%
-%:%569=400%:%
-%:%570=401%:%
-%:%571=402%:%
-%:%581=404%:%
-%:%582=405%:%
-%:%583=406%:%
-%:%584=407%:%
-%:%586=409%:%
-%:%587=409%:%
-%:%588=410%:%
-%:%590=411%:%
-%:%591=411%:%
-%:%592=412%:%
-%:%594=413%:%
-%:%595=413%:%
-%:%596=414%:%
-%:%598=415%:%
-%:%599=415%:%
-%:%600=416%:%
-%:%602=417%:%
-%:%603=417%:%
-%:%604=418%:%
-%:%606=419%:%
-%:%607=420%:%
-%:%608=420%:%
-%:%609=421%:%
-%:%616=422%:%
-%:%617=422%:%
-%:%618=423%:%
-%:%619=423%:%
-%:%620=424%:%
-%:%621=424%:%
-%:%622=424%:%
-%:%623=425%:%
-%:%624=425%:%
-%:%625=426%:%
-%:%626=426%:%
-%:%627=426%:%
-%:%628=427%:%
-%:%629=427%:%
-%:%630=428%:%
-%:%631=428%:%
-%:%632=428%:%
-%:%633=429%:%
-%:%643=431%:%
-%:%644=432%:%
-%:%645=433%:%
-%:%646=434%:%
-%:%647=435%:%
-%:%648=436%:%
-%:%649=437%:%
-%:%650=438%:%
+%:%525=376%:%
+%:%526=377%:%
+%:%527=378%:%
+%:%528=379%:%
+%:%529=380%:%
+%:%530=381%:%
+%:%532=383%:%
+%:%533=383%:%
+%:%534=384%:%
+%:%535=385%:%
+%:%537=386%:%
+%:%538=386%:%
+%:%539=387%:%
+%:%541=388%:%
+%:%542=388%:%
+%:%543=389%:%
+%:%545=390%:%
+%:%546=391%:%
+%:%547=392%:%
+%:%548=393%:%
+%:%549=394%:%
+%:%550=394%:%
+%:%551=395%:%
+%:%553=396%:%
+%:%554=397%:%
+%:%555=398%:%
+%:%556=399%:%
+%:%557=400%:%
+%:%558=401%:%
+%:%559=402%:%
+%:%560=402%:%
+%:%561=403%:%
+%:%563=404%:%
+%:%564=405%:%
+%:%565=405%:%
+%:%566=406%:%
+%:%569=407%:%
+%:%573=407%:%
+%:%574=407%:%
+%:%575=407%:%
+%:%577=408%:%
+%:%578=409%:%
+%:%579=410%:%
+%:%589=412%:%
+%:%590=413%:%
+%:%591=414%:%
+%:%592=415%:%
+%:%594=417%:%
+%:%595=417%:%
+%:%596=418%:%
+%:%598=419%:%
+%:%599=419%:%
+%:%600=420%:%
+%:%602=421%:%
+%:%603=421%:%
+%:%604=422%:%
+%:%606=423%:%
+%:%607=423%:%
+%:%608=424%:%
+%:%610=425%:%
+%:%611=425%:%
+%:%612=426%:%
+%:%614=427%:%
+%:%615=428%:%
+%:%616=428%:%
+%:%617=429%:%
+%:%624=430%:%
+%:%625=430%:%
+%:%626=431%:%
+%:%627=431%:%
+%:%628=432%:%
+%:%629=432%:%
+%:%630=432%:%
+%:%631=433%:%
+%:%632=433%:%
+%:%633=434%:%
+%:%634=434%:%
+%:%635=434%:%
+%:%636=435%:%
+%:%637=435%:%
+%:%638=436%:%
+%:%639=436%:%
+%:%640=436%:%
+%:%641=437%:%
 %:%651=439%:%
@@
 %:%678=466%:%
+%:%679=467%:%
+%:%680=468%:%
+%:%681=469%:%
+%:%682=470%:%
+%:%683=471%:%
+%:%684=472%:%
+%:%685=473%:%
+%:%686=474%:%

### 2022-03-05 paper/output/document/thesis_5_discussion.tex
added will's fixes to ch5

@@
 \caption{An example of an ethics engine for an artificial agent, which begins with a moral dilemma, 
-passes it through an input parser, applies the automated Kantian ethics test, and then processes the 
-output using an output parser. I contribute the automated Kantian ethics component.} \label{fig:AIengine}
+passes it through an input parser, applies the automated categorical imperative test, and then processes the 
+output using an output parser. I contribute the automated categorical imperative component.} \label{fig:AIengine}
 \end{figure}
@@
 new philosophical questions. In this section, I share an example of the kind of philosophical insight that computational ethics 
-can prompt and analyze the value that this tool can offer to philosophers.\footnote{Some may wonder if my system
-could also help ordinary people perform ethical reasoning, not just academic philosophers. I address the role that 
-my system should play in ordinary ethical reasoning in Appendix \ref{ordinaryhumans} and conclude
-that large parts of ordinary ethical inquiry cannot and should not be automated.}%
+can prompt and analyze the value that this tool can offer to philosophers.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 
-The idea that we cannot even evaluate, let alone will, badly-formed maxims has implications for debates about 
-self-doubt and self-respect. The dancing maxim can be read as an expression of self-doubt. Under this 
+In the previous section, I defined badly formed maxims, a philosophical concept that I discovered
+using computational ethics. In this section, I demonstrate the implications of this concept for a 
+philosophical debate to demonstrate that computational ethics can result in insights with real 
+philosophical weight. I use badly formed maxims to resolve the tension between self-doubt and self-respect. 
+This debate originated in epistemology, which values doubting your beliefs but also rationally requires
+that you believe that you are not mistaken (else you should update your beliefs). 
+Self-doubt and self-respect also compete in ethics, where questioning your judgements is valuable but 
+questioning a commitment as you make it is impossible. Self-doubt and self-respect appear 
+irresolvably opposed until they are understood through the lens of badly formed maxims. I argue that naive
+conceptions of self-doubt are badly formed maxims in disguise. If we reformulate these maxims to be well-formed,
+the tension between self-doubt and self-respect dissolves, and it becomes clear that both concepts can
+co-exist, as we intuitively desire. I sketch the details of this argument in the rest of this section.
+
+Another reading of the dancing maxim understands it as an expression of self-doubt. Under this 
 reading, the question ``When I am dancing, should I be dancing for the sake of dancing?'' is the agent asking, 
@@
 next moment, but is expressing doubt about the moral validity of their behavior at this current moment. 
-Self-doubt does not always undermine the will—after all, self-doubt plays an 
-important role in moral reasoning and is often the mark of a thoughtful agent. Instead, I argue 
+Surely self-doubt does not always undermine the will—after all, self-doubt plays an 
+important role in moral reasoning and is often the mark of a thoughtful agent. I argue 
 that questions of self-doubt do not actually involve badly-formed maxims, for these are not the maxims 
-that the agent is doubting. This example will demonstrate that the tension between self-doubt and self-respect 
-arises from a mistaken characterization of questions of self-doubt as questions about badly-formed maxims.
-I first explain the tension between self-doubt and self-respect in epistemology, then 
-explain the parallel tension in ethics, and finally present a resolution of this tension.
+that the agent is doubting. I first frame this debate by introducing the tension between self-doubt and 
+self-respect in epistemology, then explain the parallel tension in ethics, and finally present a 
+resolution of this tension.
 
@@
 agents appear to ask themselves about badly-formed maxims are mistaken about the maxim in question, because 
-such a question could never yield a useful answer for a practical reasoner.%
+such a question could never yield a useful answer for a practical reasoner.
+
+By recognizing that the naive version of ethical self-doubt is a badly formed maxim, I realized 
+that there is something wrong with its formulation and modified it to resolve the above debate. 
+This demonstrates a larger meta-pattern in Kantian reasoning: many debates in Kantian philosophical
+literature revolve around incorrectly formulated maxims, so the insight about badly
+formed maxims is significant. Much of the work of a Kantian ethicist is formulating an
+appropriate maxim, and badly-formed maxims define one boundary condition for this task.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 Programmable computers themselves initially began as unwieldy punch card readers, but their current ubiquity 
-need not be stated. If computer scientists and philosophers invest in computational ethics, it can 
-become as much a tool for philosophy as a calculator is for for arithmetic.%
+need not be stated. If computer scientists and philosophers invest in computational ethics, it could
+become as commonplace in philosophy departments as reflective equilibrium. Just as computational tools
+have supercharged progress in healthcare and drug discovery, computational ethics has the potential for
+great philosophical progress.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\isamarkupsubsection{Automating Ordinary Ethical Reasoning \label{ordinarypeople}%
+}
+\isamarkuptrue%
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
+In Sections \ref{AIethics} and \ref{computationalethics}, I outline how automated ethics can guide
+artificial agents and human philosophers respectively. This raises a natural question: can automated
+ethics guide ordinary human beings, not just academic philosophers, as we navigate the world and face ethical
+dilemmas? Some may hope (or worry) that automated ethics could render ethical reasoning obsolete. In 
+this section, I argue, that while computers should not replace human ethical reasoning entirely,
+they can supplement and improve our ethical reasoning. I argue for a kind of human-computer symbiosis
+in which computers offer ethical advice, arguments for particular moral judgements, and speed up moral
+calculations without subverting human ethical reasoning entirely \citep{licklider}.
+
+Ethics bears weight for everyone, not just for academic philosophers, because it studies the unavoidable question:
+how should we live? If computers can make this study more efficient, then it seems that everyone should
+engage in computational ethics. The ethical question is the only question that 
+we answer merely by living. To turn away from ethics is to take a stance on the question of how to 
+live (namely, to live unreflectively) and thus to engage in ethics. Every rational being must decide 
+how to navigate the world and ethics answers this question. Given that ethics is vital, it seems that if
+comptuational tools can help us derive ethical judgements more efficiently, then we should automate as 
+much ethical reasoning as possible.
+In the most extreme case, we can unthinkingly follow the commands of an ethical calculator that dictates 
+how we should live. Maybe computers can answer the unavoidable question for us.
+
+The argument above places the value of ethics solely in its action-guiding potential, and thus fails to take into account the 
+importance of practical reason, which, as I argued in Section \ref{kantianethics}, is the source
+of freedom itself. We are committed to ethical reflection because of the kind of beings that we are. 
+Recall that Korsgaard argues that, as beings occupying minds with a reflective structure, when faced with 
+a choice,``it is as if there were something over and above all of your desires, something that is you, and that chooses which desire 
+to act on'' \citep[83]{sources}. This choosing is the operation of practical reason, and this reflection
+makes us free. We are free because we must choose which reasons to act on. Every decision that we 
+make is an exercise of freedom.
+
+If reflection makes us free, then unthinkingly obeying a computer sacrifices our autonomy. Consider 
+an Ethics Oracle that can unfailingly tell you the right thing to do in any 
+situation.\footnote{This example is inspired by the Pocket Oracle presented in \citet{bok}.} Someone 
+who surrenders themselves to this Oracle unthinkingly follows its prescriptions. 
+The reflection involved in the decision to obey each of the Oracle’s prescriptions is limited \citep{bok}. 
+This person is not reflecting on the real matters at hand and is 
+not making decisions for themselves. They have surrendered their reflective capacity to the Oracle. 
+They live a worse life than someone who reflects on their actions; they have less ownership over their 
+actions than the reflective person. In a less extreme case, a person may retain control of many of 
+their decisions but cede some important or tricky choices to the Ethics Oracle. Because every single 
+exercise of practical reason is an exercise of autonomy, this person is still less autonomous than the 
+purely reflective person. Even surrendering simple, inconsequential decisions such as which flavor of 
+coffee to drink surrenders some piece of our autonomy. Perhaps in trivial cases we can accept that 
+tiny sacrifice, but giving over life-changing decisions to the machine sacrifices our 
+core freedom. Unreflectively relying on computational ethics surrenders our autonomy to the machine.
+
+One objection to this emphasis on reflection is the impracticality of making ethical calculations from first principles 
+every time we are faced with a decision. This is why we follow the advice of moral mentors, like our 
+family or influential philosophers. 
+Most people do not reason about ethics during everyday decisions; they rely on some combination of 
+prior knowledge and external testimony. For example, my mother taught me to respect myself, so I 
+follow her advice.
+
+What is the difference between following the guidance of a moral educator and
+obeying the Ethics Oracle? The best kind of ethical advice prompts reflection, such as an argument 
+made in a philosophy paper. Unthinkingly following someone’s advice results in the same loss of 
+autonomy as unthinkingly obeying the Ethics Oracle; people who merely obey orders are less autonomous 
+than those who think for themselves. This account of moral advice offers a model for human-computer 
+symbiotic computational ethics. The computer should serve as a moral guide by providing arguments, just as my mom 
+explained why I should always respect myself. Human-computer symbiotic computational
+ethics nurtures autonomy when it not only offers prescriptions for action, but also explanations for 
+these prescriptions. Because my theorem-prover-based automated ethical system is explainable, it can 
+guide action without sacrificing autonomy. It can make an argument for some action, instead of 
+merely giving a verdict. Isabelle can list the facts used to show
+a partcular action prohibited, and a human being can reflect on whether or not these principles
+indeed prohibit the action in question. The computer serves as a collaborator and a tool, but not as an authority, 
+so the human being’s reflective capacity and freedom is preserved.
+
+The above model of human-computer symbiosis demonstrates how computational ethics can augment human
+ethical reasoning without replacing it. When deliberating over moral dilemmas, ordinary people can 
+turn to computational tools for advice, like an ``Ask an Ethicist'' column. If we appeal to philosophically
+faithful computational ethics like that implemented in this thesis, then this advice will synthesize 
+decades of philosophical progress and is thus a way to apply philosophers' insights to ordinary life. 
+Moreover, just as they do for philosophers, computers can help ordinary people approach ethical questions from a 
+different perspective. Even interacting with my system requires the user to consider the action's maxim, 
+which includes the circumstances, act, and goal. Making these components of action precise already changes
+the user's perspective. Just as computational ethics can serve as a tool for academic philosophers to 
+automate away tedium and achieve greater precision, it can do the same for ordinary human beings navigating
+the world. Moreover, it also offers another way for the general public to access professional philosophy's
+insights, and thus carries potential to improve our everyday reasoning.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %:%198=151%:%
-%:%199=152%:%
-%:%200=153%:%
-%:%201=154%:%
-%:%210=156%:%
+%:%207=153%:%
+%:%219=155%:%
+%:%220=156%:%
+%:%221=157%:%
 %:%222=158%:%
@@
 %:%386=322%:%
-%:%395=326%:%
-%:%407=328%:%
-%:%408=329%:%
-%:%409=330%:%
-%:%410=331%:%
-%:%411=332%:%
-%:%412=333%:%
-%:%413=334%:%
-%:%414=335%:%
-%:%415=336%:%
-%:%416=337%:%
-%:%417=338%:%
-%:%418=339%:%
-%:%419=340%:%
-%:%420=341%:%
-%:%421=342%:%
+%:%387=323%:%
+%:%388=324%:%
+%:%389=325%:%
+%:%390=326%:%
+%:%391=327%:%
+%:%392=328%:%
+%:%393=329%:%
+%:%394=330%:%
+%:%395=331%:%
+%:%396=332%:%
+%:%397=333%:%
+%:%398=334%:%
+%:%399=335%:%
+%:%400=336%:%
+%:%401=337%:%
+%:%410=341%:%
 %:%422=343%:%
@@
 %:%470=391%:%
-%:%479=394%:%
-%:%491=397%:%
-%:%492=398%:%
-%:%493=399%:%
-%:%494=400%:%
-%:%495=401%:%
-%:%496=402%:%
-%:%497=403%:%
-%:%498=404%:%
-%:%499=405%:%
-%:%500=406%:%
-%:%501=407%:%
-%:%502=408%:%
-%:%503=409%:%
-%:%504=410%:%
-%:%505=411%:%
-%:%506=412%:%
-%:%507=413%:%
-%:%508=414%:%
-%:%509=415%:%
-%:%510=416%:%
-%:%511=417%:%
-%:%512=418%:%
-%:%513=419%:%
-%:%514=420%:%
-%:%515=421%:%
-%:%516=422%:%
-%:%517=423%:%
-%:%518=424%:%
-%:%519=425%:%
-%:%520=426%:%
-%:%521=427%:%
-%:%522=428%:%
-%:%523=429%:%
-%:%524=430%:%
-%:%525=431%:%
-%:%526=432%:%
-%:%527=433%:%
-%:%528=434%:%
-%:%529=435%:%
-%:%530=436%:%
-%:%531=437%:%
-%:%532=438%:%
-%:%533=439%:%
-%:%534=440%:%
-%:%535=441%:%
-%:%536=442%:%
-%:%537=443%:%
-%:%538=444%:%
-%:%539=445%:%
-%:%540=446%:%
-%:%541=447%:%
-%:%542=448%:%
-%:%543=449%:%
-%:%544=450%:%
-%:%545=451%:%
-%:%546=452%:%
-%:%547=453%:%
-%:%548=454%:%
-%:%549=455%:%
-%:%550=456%:%
-%:%551=457%:%
-%:%552=458%:%
-%:%553=459%:%
-%:%554=460%:%
-%:%555=461%:%
-%:%556=462%:%
-%:%557=463%:%
-%:%558=464%:%
-%:%559=465%:%
-%:%560=466%:%
-%:%561=467%:%
-%:%562=468%:%
-%:%563=469%:%
-%:%564=470%:%
-%:%565=471%:%
-%:%566=472%:%
-%:%567=473%:%
-%:%568=474%:%
-%:%569=475%:%
-%:%570=476%:%
-%:%571=477%:%
-%:%572=478%:%
-%:%573=479%:%
-%:%574=480%:%
-%:%575=481%:%
-%:%576=482%:%
-%:%577=483%:%
-%:%578=484%:%
-%:%579=485%:%
-%:%580=486%:%
-%:%581=487%:%
-%:%582=488%:%
-%:%583=489%:%
-%:%584=490%:%
-%:%585=491%:%
-%:%586=492%:%
-%:%587=493%:%
-%:%588=494%:%
-%:%589=495%:%
-%:%590=496%:%
-%:%591=497%:%
-%:%592=498%:%
-%:%593=499%:%
-%:%594=500%:%
-%:%595=501%:%
-%:%596=502%:%
-%:%597=503%:%
-%:%598=504%:%
-%:%601=506%:%
-%:%602=507%:%
-%:%603=508%:%
-%:%604=509%:%
-%:%605=510%:%
-%:%606=511%:%
-%:%609=512%:%
-%:%610=513%:%
-%:%611=514%:%
-%:%612=515%:%
-%:%613=516%:%
-%:%614=517%:%
-%:%615=518%:%
-%:%616=519%:%
-%:%617=520%:%
-%:%618=521%:%
-%:%619=522%:%
-%:%620=523%:%
-%:%621=524%:%
-%:%622=525%:%
-%:%623=526%:%
-%:%632=530%:%
-%:%644=532%:%
-%:%645=533%:%
-%:%646=534%:%
-%:%647=535%:%
-%:%648=536%:%
-%:%649=537%:%
-%:%650=538%:%
-%:%651=539%:%
-%:%652=540%:%
-%:%653=541%:%
-%:%654=542%:%
-%:%655=543%:%
-%:%656=544%:%
-%:%657=545%:%
-%:%658=546%:%
-%:%659=547%:%
-%:%660=548%:%
-%:%661=549%:%
-%:%662=550%:%
-%:%663=551%:%
-%:%664=552%:%
-%:%665=553%:%
-%:%666=554%:%
-%:%667=555%:%
-%:%668=556%:%
-%:%669=557%:%
-%:%670=558%:%
-%:%671=559%:%
-%:%672=560%:%
-%:%673=561%:%
-%:%674=562%:%
-%:%675=563%:%
-%:%676=564%:%
-%:%677=565%:%
-%:%678=566%:%
-%:%679=567%:%
-%:%680=568%:%
-%:%681=569%:%
-%:%682=570%:%
-%:%683=571%:%
-%:%684=572%:%
-%:%685=573%:%
-%:%686=574%:%
-%:%687=575%:%
-%:%688=576%:%
-%:%689=577%:%
-%:%690=578%:%
-%:%691=579%:%
-%:%692=580%:%
-%:%693=581%:%
-%:%694=582%:%
-%:%695=583%:%
-%:%704=585%:%
-%:%716=587%:%
-%:%717=588%:%
-%:%718=589%:%
-%:%719=590%:%
-%:%720=591%:%
-%:%721=592%:%
-%:%722=593%:%
-%:%723=594%:%
-%:%724=595%:%
-%:%725=596%:%
-%:%726=597%:%
-%:%727=598%:%
-%:%728=599%:%
-%:%729=600%:%
-%:%730=601%:%
-%:%731=602%:%
-%:%732=603%:%
-%:%733=604%:%
-%:%734=605%:%
-%:%735=606%:%
-%:%736=607%:%
-%:%737=608%:%
-%:%738=609%:%
-%:%739=610%:%
-%:%740=611%:%
-%:%741=612%:%
-%:%742=613%:%
-%:%743=614%:%
-%:%744=615%:%
-%:%745=616%:%
-%:%746=617%:%
-%:%747=618%:%
-%:%748=619%:%
-%:%749=620%:%
-%:%750=621%:%
-%:%751=622%:%
-%:%752=623%:%
-%:%753=624%:%
-%:%754=625%:%
+%:%471=392%:%
+%:%472=393%:%
+%:%473=394%:%
+%:%474=395%:%
+%:%475=396%:%
+%:%476=397%:%
+%:%477=398%:%
+%:%478=399%:%
+%:%479=400%:%
+%:%480=401%:%
+%:%481=402%:%
+%:%482=403%:%
+%:%483=404%:%
+%:%484=405%:%
+%:%485=406%:%
+%:%486=407%:%
+%:%487=408%:%
+%:%496=410%:%
+%:%508=412%:%
+%:%509=413%:%
+%:%510=414%:%
+%:%511=415%:%
+%:%512=416%:%
+%:%513=417%:%
+%:%514=418%:%
+%:%515=419%:%
+%:%516=420%:%
+%:%517=421%:%
+%:%518=422%:%
+%:%519=423%:%
+%:%520=424%:%
+%:%521=425%:%
+%:%522=426%:%
+%:%523=427%:%
+%:%524=428%:%
+%:%525=429%:%
+%:%526=430%:%
+%:%527=431%:%
+%:%528=432%:%
+%:%529=433%:%
+%:%530=434%:%
+%:%531=435%:%
+%:%532=436%:%
+%:%533=437%:%
+%:%534=438%:%
+%:%535=439%:%
+%:%536=440%:%
+%:%537=441%:%
+%:%538=442%:%
+%:%539=443%:%
+%:%540=444%:%
+%:%541=445%:%
+%:%542=446%:%
+%:%543=447%:%
+%:%544=448%:%
+%:%545=449%:%
+%:%546=450%:%
+%:%547=451%:%
+%:%548=452%:%
+%:%549=453%:%
+%:%550=454%:%
+%:%551=455%:%
+%:%552=456%:%
+%:%553=457%:%
+%:%554=458%:%
+%:%555=459%:%
+%:%556=460%:%
+%:%557=461%:%
+%:%558=462%:%
+%:%559=463%:%
+%:%560=464%:%
+%:%561=465%:%
+%:%562=466%:%
+%:%563=467%:%
+%:%564=468%:%
+%:%565=469%:%
+%:%566=470%:%
+%:%567=471%:%
+%:%568=472%:%
+%:%569=473%:%
+%:%570=474%:%
+%:%571=475%:%
+%:%572=476%:%
+%:%573=477%:%
+%:%574=478%:%
+%:%575=479%:%
+%:%576=480%:%
+%:%577=481%:%
+%:%578=482%:%
+%:%579=483%:%
+%:%580=484%:%
+%:%581=485%:%
+%:%582=486%:%
+%:%583=487%:%
+%:%584=488%:%
+%:%585=489%:%
+%:%586=490%:%
+%:%595=493%:%
+%:%607=496%:%
+%:%608=497%:%
+%:%609=498%:%
+%:%610=499%:%
+%:%611=500%:%
+%:%612=501%:%
+%:%613=502%:%
+%:%614=503%:%
+%:%615=504%:%
+%:%616=505%:%
+%:%617=506%:%
+%:%618=507%:%
+%:%619=508%:%
+%:%620=509%:%
+%:%621=510%:%
+%:%622=511%:%
+%:%623=512%:%
+%:%624=513%:%
+%:%625=514%:%
+%:%626=515%:%
+%:%627=516%:%
+%:%628=517%:%
+%:%629=518%:%
+%:%630=519%:%
+%:%631=520%:%
+%:%632=521%:%
+%:%633=522%:%
+%:%634=523%:%
+%:%635=524%:%
+%:%636=525%:%
+%:%637=526%:%
+%:%638=527%:%
+%:%639=528%:%
+%:%640=529%:%
+%:%641=530%:%
+%:%642=531%:%
+%:%643=532%:%
+%:%644=533%:%
+%:%645=534%:%
+%:%646=535%:%
+%:%647=536%:%
+%:%648=537%:%
+%:%649=538%:%
+%:%650=539%:%
+%:%651=540%:%
+%:%652=541%:%
+%:%653=542%:%
+%:%654=543%:%
+%:%655=544%:%
+%:%656=545%:%
+%:%657=546%:%
+%:%658=547%:%
+%:%659=548%:%
+%:%660=549%:%
+%:%661=550%:%
+%:%662=551%:%
+%:%663=552%:%
+%:%664=553%:%
+%:%665=554%:%
+%:%666=555%:%
+%:%667=556%:%
+%:%668=557%:%
+%:%669=558%:%
+%:%670=559%:%
+%:%671=560%:%
+%:%672=561%:%
+%:%673=562%:%
+%:%674=563%:%
+%:%675=564%:%
+%:%676=565%:%
+%:%677=566%:%
+%:%678=567%:%
+%:%679=568%:%
+%:%680=569%:%
+%:%681=570%:%
+%:%682=571%:%
+%:%683=572%:%
+%:%684=573%:%
+%:%685=574%:%
+%:%686=575%:%
+%:%687=576%:%
+%:%688=577%:%
+%:%689=578%:%
+%:%690=579%:%
+%:%691=580%:%
+%:%692=581%:%
+%:%693=582%:%
+%:%694=583%:%
+%:%695=584%:%
+%:%696=585%:%
+%:%697=586%:%
+%:%698=587%:%
+%:%699=588%:%
+%:%700=589%:%
+%:%701=590%:%
+%:%702=591%:%
+%:%703=592%:%
+%:%704=593%:%
+%:%705=594%:%
+%:%706=595%:%
+%:%707=596%:%
+%:%708=597%:%
+%:%709=598%:%
+%:%710=599%:%
+%:%711=600%:%
+%:%712=601%:%
+%:%713=602%:%
+%:%714=603%:%
+%:%717=605%:%
+%:%718=606%:%
+%:%719=607%:%
+%:%720=608%:%
+%:%721=609%:%
+%:%722=610%:%
+%:%725=611%:%
+%:%726=612%:%
+%:%727=613%:%
+%:%728=614%:%
+%:%729=615%:%
+%:%730=616%:%
+%:%731=617%:%
+%:%732=618%:%
+%:%733=619%:%
+%:%734=620%:%
+%:%735=621%:%
+%:%736=622%:%
+%:%737=623%:%
+%:%738=624%:%
+%:%739=625%:%
+%:%748=629%:%
+%:%760=631%:%
+%:%761=632%:%
+%:%762=633%:%
+%:%763=634%:%
+%:%764=635%:%
+%:%765=636%:%
+%:%766=637%:%
+%:%767=638%:%
+%:%768=639%:%
+%:%769=640%:%
+%:%770=641%:%
+%:%771=642%:%
+%:%772=643%:%
+%:%773=644%:%
+%:%774=645%:%
+%:%775=646%:%
+%:%776=647%:%
+%:%777=648%:%
+%:%778=649%:%
+%:%779=650%:%
+%:%780=651%:%
+%:%781=652%:%
+%:%782=653%:%
+%:%783=654%:%
+%:%784=655%:%
+%:%785=656%:%
+%:%786=657%:%
+%:%787=658%:%
+%:%788=659%:%
+%:%789=660%:%
+%:%790=661%:%
+%:%791=662%:%
+%:%792=663%:%
+%:%793=664%:%
+%:%794=665%:%
+%:%795=666%:%
+%:%796=667%:%
+%:%797=668%:%
+%:%798=669%:%
+%:%799=670%:%
+%:%800=671%:%
+%:%801=672%:%
+%:%802=673%:%
+%:%803=674%:%
+%:%804=675%:%
+%:%805=676%:%
+%:%806=677%:%
+%:%807=678%:%
+%:%808=679%:%
+%:%809=680%:%
+%:%810=681%:%
+%:%811=682%:%
+%:%820=684%:%
+%:%832=686%:%
+%:%833=687%:%
+%:%834=688%:%
+%:%835=689%:%
+%:%836=690%:%
+%:%837=691%:%
+%:%838=692%:%
+%:%839=693%:%
+%:%840=694%:%
+%:%841=695%:%
+%:%842=696%:%
+%:%843=697%:%
+%:%844=698%:%
+%:%845=699%:%
+%:%846=700%:%
+%:%847=701%:%
+%:%848=702%:%
+%:%849=703%:%
+%:%850=704%:%
+%:%851=705%:%
+%:%852=706%:%
+%:%853=707%:%
+%:%854=708%:%
+%:%855=709%:%
+%:%856=710%:%
+%:%857=711%:%
+%:%858=712%:%
+%:%859=713%:%
+%:%860=714%:%
+%:%861=715%:%
+%:%862=716%:%
+%:%863=717%:%
+%:%864=718%:%
+%:%865=719%:%
+%:%866=720%:%
+%:%867=721%:%
+%:%868=722%:%
+%:%869=723%:%
+%:%870=724%:%

### 2022-03-07 paper/output/document/appendix.tex
spring cleaning xoxoxo

@@
 %
-\isamarkupsection{Appendix%
+\isamarkupsection{Appendix: Alternate Definitions of a Maxim \label{maximmotive}%
 }
@@
 %
-\isamarkupsubsection{Alternate Definitions of a Maxim \label{maximmotive}%
-}
-\isamarkuptrue%
-%
-\isamarkupsubsubsection{Korsgaard's Act-Goal View%
+\isamarkupsubsection{Korsgaard's Act-Goal View%
 }
@@
 %
-\isamarkupsubsubsection{Kitcher's View on Motives%
+\isamarkupsubsection{Kitcher's View on Motives%
 }
@@
 %
-\isamarkupsubsection{Kroy's Formalization\label{kroydetails}%
+\isamarkupsection{Kroy's Formalization\label{kroydetails}%
 }
@@
 %
-\isamarkupsubsubsection{Logical Background \label{sec:kroy_logical_background}%
+\isamarkupsubsection{Logical Background \label{sec:kroy_logical_background}%
 }
@@
 %
-\isamarkupsubsubsection{Kroy's formalization of the FUL \label{sec: kroy_ful}%
+\isamarkupsubsection{Kroy's formalization of the FUL \label{sec: kroy_ful}%
 }
@@
 %
-\isamarkupsubsubsection{Testing Kroy's Formalization%
+\isamarkupsubsection{Testing Kroy's Formalization%
 }
@@
 %
-\isamarkupsubsubsection{Metaethical Tests \label{sec:meta_tests_kroy}%
+\isamarkupsubsection{Metaethical Tests \label{sec:meta_tests_kroy}%
 }
@@
 %
-\isamarkupsubsubsection{Miscellaneous Tests \label{sec: misc_tests_kroy}%
+\isamarkupsubsection{Miscellaneous Tests \label{sec: misc_tests_kroy}%
 }
@@
 %:%file=~/Desktop/cs91r/paper/appendix.thy%:%
-%:%24=5%:%
-%:%28=7%:%
-%:%32=9%:%
-%:%44=11%:%
-%:%45=12%:%
-%:%46=13%:%
-%:%47=14%:%
-%:%48=15%:%
-%:%49=16%:%
-%:%50=17%:%
-%:%51=18%:%
-%:%52=19%:%
-%:%53=20%:%
-%:%54=21%:%
-%:%55=22%:%
-%:%56=23%:%
-%:%57=24%:%
-%:%58=25%:%
-%:%59=26%:%
-%:%60=27%:%
-%:%61=28%:%
-%:%62=29%:%
-%:%63=30%:%
-%:%64=31%:%
-%:%65=32%:%
-%:%66=33%:%
-%:%75=36%:%
-%:%87=38%:%
-%:%88=39%:%
-%:%89=40%:%
-%:%90=41%:%
-%:%91=42%:%
-%:%92=43%:%
-%:%93=44%:%
-%:%94=45%:%
-%:%95=46%:%
-%:%96=47%:%
-%:%97=48%:%
-%:%98=49%:%
-%:%99=50%:%
-%:%100=51%:%
-%:%101=52%:%
-%:%102=53%:%
-%:%103=54%:%
-%:%104=55%:%
-%:%105=56%:%
-%:%106=57%:%
-%:%107=58%:%
-%:%108=59%:%
-%:%109=60%:%
-%:%110=61%:%
-%:%145=90%:%
-%:%157=92%:%
-%:%158=93%:%
-%:%159=94%:%
-%:%160=95%:%
-%:%161=96%:%
-%:%170=98%:%
-%:%182=100%:%
-%:%183=101%:%
-%:%185=103%:%
-%:%186=103%:%
-%:%187=103%:%
-%:%190=105%:%
-%:%191=106%:%
-%:%192=107%:%
-%:%193=108%:%
-%:%194=109%:%
-%:%195=110%:%
+%:%24=6%:%
+%:%28=8%:%
+%:%40=10%:%
+%:%41=11%:%
+%:%42=12%:%
+%:%43=13%:%
+%:%44=14%:%
+%:%45=15%:%
+%:%46=16%:%
+%:%47=17%:%
+%:%48=18%:%
+%:%49=19%:%
+%:%50=20%:%
+%:%51=21%:%
+%:%52=22%:%
+%:%53=23%:%
+%:%54=24%:%
+%:%55=25%:%
+%:%56=26%:%
+%:%57=27%:%
+%:%58=28%:%
+%:%59=29%:%
+%:%60=30%:%
+%:%61=31%:%
+%:%62=32%:%
+%:%71=35%:%
+%:%83=37%:%
+%:%84=38%:%
+%:%85=39%:%
+%:%86=40%:%
+%:%87=41%:%
+%:%88=42%:%
+%:%89=43%:%
+%:%90=44%:%
+%:%91=45%:%
+%:%92=46%:%
+%:%93=47%:%
+%:%94=48%:%
+%:%95=49%:%
+%:%96=50%:%
+%:%97=51%:%
+%:%98=52%:%
+%:%99=53%:%
+%:%100=54%:%
+%:%101=55%:%
+%:%102=56%:%
+%:%103=57%:%
+%:%104=58%:%
+%:%105=59%:%
+%:%106=60%:%
+%:%141=89%:%
+%:%153=91%:%
+%:%154=92%:%
+%:%155=93%:%
+%:%156=94%:%
+%:%157=95%:%
+%:%166=97%:%
+%:%178=99%:%
+%:%179=100%:%
+%:%181=102%:%
+%:%182=102%:%
+%:%183=102%:%
+%:%186=104%:%
+%:%187=105%:%
+%:%188=106%:%
+%:%189=107%:%
+%:%190=108%:%
+%:%191=109%:%
+%:%193=111%:%
+%:%194=111%:%
+%:%196=112%:%
 %:%197=112%:%
-%:%198=112%:%
-%:%200=113%:%
-%:%201=113%:%
-%:%203=114%:%
-%:%204=115%:%
-%:%207=117%:%
-%:%208=118%:%
-%:%209=119%:%
-%:%210=120%:%
-%:%212=122%:%
-%:%213=122%:%
-%:%214=123%:%
-%:%215=124%:%
-%:%216=124%:%
-%:%217=125%:%
-%:%218=126%:%
-%:%219=126%:%
-%:%220=127%:%
-%:%221=128%:%
-%:%222=128%:%
-%:%223=129%:%
-%:%225=131%:%
-%:%226=132%:%
-%:%227=133%:%
-%:%229=135%:%
-%:%230=135%:%
-%:%231=136%:%
-%:%232=137%:%
-%:%233=137%:%
-%:%234=138%:%
-%:%235=140%:%
-%:%238=142%:%
-%:%239=143%:%
-%:%240=144%:%
-%:%241=145%:%
-%:%242=146%:%
-%:%243=147%:%
-%:%244=148%:%
-%:%247=150%:%
-%:%250=152%:%
-%:%251=153%:%
-%:%252=154%:%
-%:%253=155%:%
-%:%254=156%:%
-%:%255=157%:%
-%:%257=159%:%
-%:%258=159%:%
-%:%259=160%:%
+%:%199=113%:%
+%:%200=114%:%
+%:%203=116%:%
+%:%204=117%:%
+%:%205=118%:%
+%:%206=119%:%
+%:%208=121%:%
+%:%209=121%:%
+%:%210=122%:%
+%:%211=123%:%
+%:%212=123%:%
+%:%213=124%:%
+%:%214=125%:%
+%:%215=125%:%
+%:%216=126%:%
+%:%217=127%:%
+%:%218=127%:%
+%:%219=128%:%
+%:%221=130%:%
+%:%222=131%:%
+%:%223=132%:%
+%:%225=134%:%
+%:%226=134%:%
+%:%227=135%:%
+%:%228=136%:%
+%:%229=136%:%
+%:%230=137%:%
+%:%231=139%:%
+%:%234=141%:%
+%:%235=142%:%
+%:%236=143%:%
+%:%237=144%:%
+%:%238=145%:%
+%:%239=146%:%
+%:%240=147%:%
+%:%243=149%:%
+%:%246=151%:%
+%:%247=152%:%
+%:%248=153%:%
+%:%249=154%:%
+%:%250=155%:%
+%:%251=156%:%
+%:%253=158%:%
+%:%254=158%:%
+%:%255=159%:%
+%:%256=160%:%
+%:%257=161%:%
+%:%258=161%:%
 %:%260=161%:%
-%:%261=162%:%
-%:%262=162%:%
-%:%264=162%:%
-%:%268=162%:%
-%:%269=162%:%
-%:%271=163%:%
-%:%272=164%:%
-%:%273=165%:%
-%:%274=166%:%
-%:%284=168%:%
-%:%285=169%:%
-%:%286=170%:%
-%:%287=171%:%
-%:%288=172%:%
-%:%289=173%:%
-%:%290=174%:%
-%:%291=175%:%
-%:%292=176%:%
-%:%293=177%:%
-%:%295=179%:%
-%:%296=179%:%
-%:%297=180%:%
+%:%264=161%:%
+%:%265=161%:%
+%:%267=162%:%
+%:%268=163%:%
+%:%269=164%:%
+%:%270=165%:%
+%:%280=167%:%
+%:%281=168%:%
+%:%282=169%:%
+%:%283=170%:%
+%:%284=171%:%
+%:%285=172%:%
+%:%286=173%:%
+%:%287=174%:%
+%:%288=175%:%
+%:%289=176%:%
+%:%291=178%:%
+%:%292=178%:%
+%:%293=179%:%
+%:%294=180%:%
+%:%295=181%:%
+%:%296=181%:%
 %:%298=181%:%
-%:%299=182%:%
-%:%300=182%:%
-%:%302=182%:%
-%:%306=182%:%
-%:%307=182%:%
-%:%309=183%:%
-%:%310=184%:%
-%:%311=185%:%
-%:%312=186%:%
-%:%322=188%:%
-%:%323=189%:%
-%:%324=190%:%
-%:%325=191%:%
-%:%326=192%:%
-%:%327=193%:%
-%:%328=194%:%
-%:%329=195%:%
-%:%330=196%:%
-%:%332=198%:%
-%:%333=198%:%
-%:%334=199%:%
+%:%302=181%:%
+%:%303=181%:%
+%:%305=182%:%
+%:%306=183%:%
+%:%307=184%:%
+%:%308=185%:%
+%:%318=187%:%
+%:%319=188%:%
+%:%320=189%:%
+%:%321=190%:%
+%:%322=191%:%
+%:%323=192%:%
+%:%324=193%:%
+%:%325=194%:%
+%:%326=195%:%
+%:%328=197%:%
+%:%329=197%:%
+%:%330=198%:%
+%:%331=199%:%
+%:%332=200%:%
+%:%333=200%:%
 %:%335=200%:%
-%:%336=201%:%
-%:%337=201%:%
-%:%339=201%:%
-%:%343=201%:%
-%:%344=201%:%
-%:%346=202%:%
-%:%347=203%:%
-%:%348=204%:%
-%:%349=205%:%
-%:%359=207%:%
-%:%360=208%:%
-%:%382=234%:%
-%:%394=236%:%
-%:%395=237%:%
-%:%396=238%:%
-%:%397=239%:%
-%:%398=240%:%
-%:%400=243%:%
-%:%401=243%:%
-%:%403=244%:%
-%:%404=245%:%
-%:%405=246%:%
-%:%408=248%:%
-%:%409=249%:%
-%:%411=251%:%
-%:%412=251%:%
+%:%339=200%:%
+%:%340=200%:%
+%:%342=201%:%
+%:%343=202%:%
+%:%344=203%:%
+%:%345=204%:%
+%:%355=206%:%
+%:%356=207%:%
+%:%378=233%:%
+%:%390=235%:%
+%:%391=236%:%
+%:%392=237%:%
+%:%393=238%:%
+%:%394=239%:%
+%:%396=242%:%
+%:%397=242%:%
+%:%399=243%:%
+%:%400=244%:%
+%:%401=245%:%
+%:%404=247%:%
+%:%405=248%:%
+%:%407=250%:%
+%:%408=250%:%
+%:%409=251%:%
+%:%410=252%:%
+%:%411=252%:%
 %:%413=252%:%
-%:%414=253%:%
-%:%415=253%:%
-%:%417=253%:%
-%:%421=253%:%
-%:%422=253%:%
-%:%424=254%:%
-%:%425=255%:%
-%:%426=256%:%
-%:%427=257%:%
-%:%428=258%:%
-%:%429=259%:%
-%:%437=259%:%
-%:%438=260%:%
-%:%439=261%:%
-%:%440=261%:%
-%:%442=263%:%
-%:%443=264%:%
-%:%445=266%:%
-%:%446=266%:%
-%:%447=266%:%
-%:%449=266%:%
-%:%453=266%:%
-%:%454=266%:%
-%:%456=267%:%
-%:%457=268%:%
-%:%458=269%:%
-%:%459=270%:%
-%:%469=272%:%
-%:%470=273%:%
-%:%471=274%:%
-%:%472=275%:%
-%:%481=277%:%
-%:%493=279%:%
-%:%494=280%:%
-%:%495=281%:%
-%:%496=282%:%
-%:%497=283%:%
-%:%498=284%:%
-%:%499=285%:%
-%:%500=286%:%
-%:%501=287%:%
-%:%502=288%:%
-%:%504=290%:%
-%:%505=290%:%
+%:%417=252%:%
+%:%418=252%:%
+%:%420=253%:%
+%:%421=254%:%
+%:%422=255%:%
+%:%423=256%:%
+%:%424=257%:%
+%:%425=258%:%
+%:%433=258%:%
+%:%434=259%:%
+%:%435=260%:%
+%:%436=260%:%
+%:%438=262%:%
+%:%439=263%:%
+%:%441=265%:%
+%:%442=265%:%
+%:%443=265%:%
+%:%445=265%:%
+%:%449=265%:%
+%:%450=265%:%
+%:%452=266%:%
+%:%453=267%:%
+%:%454=268%:%
+%:%455=269%:%
+%:%465=271%:%
+%:%466=272%:%
+%:%467=273%:%
+%:%468=274%:%
+%:%477=276%:%
+%:%489=278%:%
+%:%490=279%:%
+%:%491=280%:%
+%:%492=281%:%
+%:%493=282%:%
+%:%494=283%:%
+%:%495=284%:%
+%:%496=285%:%
+%:%497=286%:%
+%:%498=287%:%
+%:%500=289%:%
+%:%501=289%:%
+%:%502=290%:%
+%:%503=291%:%
+%:%504=291%:%
 %:%506=291%:%
-%:%507=292%:%
-%:%508=292%:%
-%:%510=292%:%
-%:%514=292%:%
-%:%524=294%:%
-%:%528=296%:%
-%:%529=297%:%
-%:%530=298%:%
-%:%532=300%:%
-%:%533=300%:%
-%:%535=301%:%
-%:%536=302%:%
-%:%537=303%:%
-%:%538=304%:%
-%:%539=305%:%
-%:%540=306%:%
-%:%541=307%:%
-%:%542=307%:%
-%:%543=308%:%
-%:%544=309%:%
-%:%545=309%:%
-%:%546=310%:%
-%:%549=311%:%
-%:%553=311%:%
-%:%554=311%:%
-%:%556=312%:%
-%:%557=313%:%
-%:%567=315%:%
-%:%568=316%:%
-%:%569=317%:%
-%:%570=318%:%
-%:%571=319%:%
-%:%572=320%:%
-%:%573=321%:%
-%:%574=322%:%
-%:%575=323%:%
-%:%576=324%:%
-%:%577=325%:%
-%:%578=326%:%
-%:%579=327%:%
-%:%580=328%:%
-%:%581=329%:%
-%:%582=330%:%
-%:%583=331%:%
-%:%584=332%:%
-%:%588=334%:%
-%:%589=335%:%
+%:%510=291%:%
+%:%520=293%:%
+%:%524=295%:%
+%:%525=296%:%
+%:%526=297%:%
+%:%528=299%:%
+%:%529=299%:%
+%:%531=300%:%
+%:%532=301%:%
+%:%533=302%:%
+%:%534=303%:%
+%:%535=304%:%
+%:%536=305%:%
+%:%537=306%:%
+%:%538=306%:%
+%:%539=307%:%
+%:%540=308%:%
+%:%541=308%:%
+%:%542=309%:%
+%:%545=310%:%
+%:%549=310%:%
+%:%550=310%:%
+%:%552=311%:%
+%:%553=312%:%
+%:%563=314%:%
+%:%564=315%:%
+%:%565=316%:%
+%:%566=317%:%
+%:%567=318%:%
+%:%568=319%:%
+%:%569=320%:%
+%:%570=321%:%
+%:%571=322%:%
+%:%572=323%:%
+%:%573=324%:%
+%:%574=325%:%
+%:%575=326%:%
+%:%576=327%:%
+%:%577=328%:%
+%:%578=329%:%
+%:%579=330%:%
+%:%580=331%:%
+%:%584=333%:%
+%:%585=334%:%
+%:%587=336%:%
+%:%588=336%:%
+%:%590=337%:%
 %:%591=337%:%
-%:%592=337%:%
-%:%594=338%:%
-%:%595=338%:%
-%:%596=339%:%
-%:%597=340%:%
-%:%598=340%:%
-%:%599=341%:%
-%:%602=342%:%
-%:%606=342%:%
-%:%607=342%:%
-%:%608=343%:%
-%:%609=343%:%
+%:%592=338%:%
+%:%593=339%:%
+%:%594=339%:%
+%:%595=340%:%
+%:%598=341%:%
+%:%602=341%:%
+%:%603=341%:%
+%:%604=342%:%
+%:%605=342%:%
+%:%606=343%:%
+%:%607=343%:%
+%:%608=344%:%
+%:%609=344%:%
 %:%610=344%:%
-%:%611=344%:%
-%:%612=345%:%
-%:%613=345%:%
-%:%614=345%:%
-%:%615=346%:%
-%:%625=348%:%
-%:%626=349%:%
-%:%627=350%:%
-%:%628=351%:%
-%:%632=353%:%
-%:%636=355%:%
-%:%637=356%:%
-%:%638=357%:%
-%:%642=359%:%
-%:%643=360%:%
-%:%645=362%:%
-%:%646=362%:%
-%:%659=383%:%
-%:%660=384%:%
-%:%661=384%:%
-%:%663=385%:%
-%:%664=386%:%
-%:%665=387%:%
-%:%666=388%:%
-%:%667=389%:%
-%:%668=390%:%
-%:%669=390%:%
-%:%671=391%:%
-%:%672=392%:%
-%:%673=392%:%
-%:%674=393%:%
-%:%675=394%:%
-%:%676=394%:%
-%:%678=395%:%
-%:%679=396%:%
-%:%682=398%:%
-%:%683=399%:%
-%:%685=401%:%
-%:%686=401%:%
+%:%611=345%:%
+%:%621=347%:%
+%:%622=348%:%
+%:%623=349%:%
+%:%624=350%:%
+%:%628=352%:%
+%:%632=354%:%
+%:%633=355%:%
+%:%634=356%:%
+%:%638=358%:%
+%:%639=359%:%
+%:%641=361%:%
+%:%642=361%:%
+%:%655=382%:%
+%:%656=383%:%
+%:%657=383%:%
+%:%659=384%:%
+%:%660=385%:%
+%:%661=386%:%
+%:%662=387%:%
+%:%663=388%:%
+%:%664=389%:%
+%:%665=389%:%
+%:%667=390%:%
+%:%668=391%:%
+%:%669=391%:%
+%:%670=392%:%
+%:%671=393%:%
+%:%672=393%:%
+%:%674=394%:%
+%:%675=395%:%
+%:%678=397%:%
+%:%679=398%:%
+%:%681=400%:%
+%:%682=400%:%
+%:%683=401%:%
+%:%684=402%:%
+%:%685=402%:%
 %:%687=402%:%
-%:%688=403%:%
-%:%689=403%:%
-%:%691=403%:%
-%:%695=403%:%
-%:%696=403%:%
-%:%698=404%:%
-%:%699=405%:%
-%:%700=406%:%
-%:%701=407%:%
-%:%702=408%:%
-%:%703=409%:%
-%:%704=410%:%
-%:%714=412%:%
-%:%715=413%:%
-%:%716=414%:%
-%:%719=416%:%
-%:%720=417%:%
-%:%721=418%:%
-%:%722=419%:%
-%:%723=420%:%
-%:%724=421%:%
-%:%727=423%:%
-%:%729=425%:%
-%:%730=425%:%
-%:%731=426%:%
-%:%734=427%:%
-%:%738=427%:%
-%:%739=427%:%
-%:%741=428%:%
-%:%747=428%:%
-%:%750=429%:%
-%:%751=430%:%
-%:%752=430%:%
-%:%753=431%:%
+%:%691=402%:%
+%:%692=402%:%
+%:%694=403%:%
+%:%695=404%:%
+%:%696=405%:%
+%:%697=406%:%
+%:%698=407%:%
+%:%699=408%:%
+%:%700=409%:%
+%:%710=411%:%
+%:%711=412%:%
+%:%712=413%:%
+%:%715=415%:%
+%:%716=416%:%
+%:%717=417%:%
+%:%718=418%:%
+%:%719=419%:%
+%:%720=420%:%
+%:%723=422%:%
+%:%725=424%:%
+%:%726=424%:%
+%:%727=425%:%
+%:%730=426%:%
+%:%734=426%:%
+%:%735=426%:%
+%:%737=427%:%
+%:%743=427%:%
+%:%746=428%:%
+%:%747=429%:%
+%:%748=429%:%
+%:%749=430%:%
+%:%750=431%:%
+%:%751=432%:%
+%:%752=432%:%
 %:%754=432%:%
-%:%755=433%:%
-%:%756=433%:%
-%:%758=433%:%
-%:%762=433%:%
-%:%763=433%:%
-%:%765=434%:%
-%:%766=435%:%
-%:%767=436%:%
-%:%768=437%:%
-%:%769=438%:%
-%:%779=440%:%
-%:%780=441%:%
-%:%781=442%:%
-%:%782=443%:%
-%:%783=444%:%
-%:%784=445%:%
-%:%785=446%:%
-%:%786=447%:%
-%:%787=448%:%
-%:%791=451%:%
-%:%792=452%:%
-%:%793=453%:%
-%:%794=454%:%
-%:%795=455%:%
-%:%796=456%:%
-%:%797=457%:%
-%:%798=458%:%
-%:%799=459%:%
-%:%800=460%:%
-%:%801=461%:%
-%:%802=462%:%
-%:%811=464%:%
-%:%823=466%:%
-%:%824=467%:%
-%:%825=468%:%
-%:%827=470%:%
-%:%828=470%:%
-%:%829=471%:%
+%:%758=432%:%
+%:%759=432%:%
+%:%761=433%:%
+%:%762=434%:%
+%:%763=435%:%
+%:%764=436%:%
+%:%765=437%:%
+%:%775=439%:%
+%:%776=440%:%
+%:%777=441%:%
+%:%778=442%:%
+%:%779=443%:%
+%:%780=444%:%
+%:%781=445%:%
+%:%782=446%:%
+%:%783=447%:%
+%:%787=450%:%
+%:%788=451%:%
+%:%789=452%:%
+%:%790=453%:%
+%:%791=454%:%
+%:%792=455%:%
+%:%793=456%:%
+%:%794=457%:%
+%:%795=458%:%
+%:%796=459%:%
+%:%797=460%:%
+%:%798=461%:%
+%:%807=463%:%
+%:%819=465%:%
+%:%820=466%:%
+%:%821=467%:%
+%:%823=469%:%
+%:%824=469%:%
+%:%825=470%:%
+%:%826=471%:%
+%:%827=472%:%
+%:%828=472%:%
 %:%830=472%:%
-%:%831=473%:%
-%:%832=473%:%
-%:%834=473%:%
-%:%838=473%:%
-%:%839=473%:%
-%:%841=474%:%
-%:%842=475%:%
-%:%843=476%:%
-%:%844=477%:%
-%:%854=479%:%
-%:%855=480%:%
-%:%856=481%:%
-%:%860=483%:%
-%:%862=485%:%
-%:%863=485%:%
-%:%864=486%:%
+%:%834=472%:%
+%:%835=472%:%
+%:%837=473%:%
+%:%838=474%:%
+%:%839=475%:%
+%:%840=476%:%
+%:%850=478%:%
+%:%851=479%:%
+%:%852=480%:%
+%:%856=482%:%
+%:%858=484%:%
+%:%859=484%:%
+%:%860=485%:%
+%:%861=486%:%
+%:%862=487%:%
+%:%863=487%:%
 %:%865=487%:%
-%:%866=488%:%
-%:%867=488%:%
-%:%869=488%:%
-%:%873=488%:%
-%:%874=488%:%
-%:%876=489%:%
-%:%877=490%:%
-%:%878=491%:%
-%:%879=492%:%
-%:%889=494%:%
-%:%890=495%:%
-%:%892=497%:%
-%:%893=497%:%
-%:%894=498%:%
+%:%869=487%:%
+%:%870=487%:%
+%:%872=488%:%
+%:%873=489%:%
+%:%874=490%:%
+%:%875=491%:%
+%:%885=493%:%
+%:%886=494%:%
+%:%888=496%:%
+%:%889=496%:%
+%:%890=497%:%
+%:%891=498%:%
+%:%892=499%:%
+%:%893=499%:%
 %:%895=499%:%
-%:%896=500%:%
-%:%897=500%:%
-%:%899=500%:%
-%:%903=500%:%
-%:%904=500%:%
-%:%906=501%:%
-%:%907=502%:%
-%:%908=503%:%
-%:%909=504%:%
-%:%910=505%:%
-%:%920=507%:%
-%:%921=508%:%
-%:%923=510%:%
-%:%924=510%:%
-%:%925=511%:%
-%:%926=512%:%
-%:%929=513%:%
-%:%933=513%:%
-%:%934=513%:%
-%:%935=513%:%
-%:%944=515%:%
-%:%945=516%:%
-%:%946=517%:%
-%:%947=518%:%
-%:%949=520%:%
-%:%950=520%:%
-%:%951=521%:%
-%:%952=522%:%
-%:%955=523%:%
-%:%959=523%:%
-%:%960=523%:%
-%:%961=523%:%
-%:%970=525%:%
-%:%971=526%:%
-%:%973=528%:%
-%:%974=528%:%
-%:%975=529%:%
+%:%899=499%:%
+%:%900=499%:%
+%:%902=500%:%
+%:%903=501%:%
+%:%904=502%:%
+%:%905=503%:%
+%:%906=504%:%
+%:%916=506%:%
+%:%917=507%:%
+%:%919=509%:%
+%:%920=509%:%
+%:%921=510%:%
+%:%922=511%:%
+%:%925=512%:%
+%:%929=512%:%
+%:%930=512%:%
+%:%931=512%:%
+%:%940=514%:%
+%:%941=515%:%
+%:%942=516%:%
+%:%943=517%:%
+%:%945=519%:%
+%:%946=519%:%
+%:%947=520%:%
+%:%948=521%:%
+%:%951=522%:%
+%:%955=522%:%
+%:%956=522%:%
+%:%957=522%:%
+%:%966=524%:%
+%:%967=525%:%
+%:%969=527%:%
+%:%970=527%:%
+%:%971=528%:%
+%:%972=529%:%
+%:%973=530%:%
+%:%974=530%:%
 %:%976=530%:%
-%:%977=531%:%
-%:%978=531%:%
-%:%980=531%:%
-%:%984=531%:%
-%:%985=531%:%
-%:%987=532%:%
-%:%988=533%:%
-%:%989=534%:%
-%:%990=535%:%
-%:%1000=537%:%
-%:%1001=538%:%
-%:%1002=539%:%
-%:%1003=540%:%
-%:%1004=541%:%
-%:%1005=542%:%
-%:%1007=544%:%
-%:%1008=544%:%
-%:%1009=545%:%
-%:%1010=546%:%
+%:%980=530%:%
+%:%981=530%:%
+%:%983=531%:%
+%:%984=532%:%
+%:%985=533%:%
+%:%986=534%:%
+%:%996=536%:%
+%:%997=537%:%
+%:%998=538%:%
+%:%999=539%:%
+%:%1000=540%:%
+%:%1001=541%:%
+%:%1003=543%:%
+%:%1004=543%:%
+%:%1005=544%:%
+%:%1006=545%:%
+%:%1007=546%:%
+%:%1008=547%:%
+%:%1009=547%:%
 %:%1011=547%:%
-%:%1012=548%:%
-%:%1013=548%:%
-%:%1015=548%:%
-%:%1019=548%:%
-%:%1020=548%:%
-%:%1022=549%:%
-%:%1023=550%:%
-%:%1024=551%:%
-%:%1025=552%:%
-%:%1026=553%:%
-%:%1027=554%:%
-%:%1037=556%:%
-%:%1038=557%:%
-%:%1039=558%:%
-%:%1040=559%:%
-%:%1041=560%:%
-%:%1042=561%:%
-%:%1044=563%:%
-%:%1045=563%:%
-%:%1046=564%:%
-%:%1047=565%:%
-%:%1050=566%:%
-%:%1054=566%:%
-%:%1055=566%:%
-%:%1057=567%:%
-%:%1067=569%:%
-%:%1068=570%:%
-%:%1070=571%:%
-%:%1071=571%:%
+%:%1015=547%:%
+%:%1016=547%:%
+%:%1018=548%:%
+%:%1019=549%:%
+%:%1020=550%:%
+%:%1021=551%:%
+%:%1022=552%:%
+%:%1023=553%:%
+%:%1033=555%:%
+%:%1034=556%:%
+%:%1035=557%:%
+%:%1036=558%:%
+%:%1037=559%:%
+%:%1038=560%:%
+%:%1040=562%:%
+%:%1041=562%:%
+%:%1042=563%:%
+%:%1043=564%:%
+%:%1046=565%:%
+%:%1050=565%:%
+%:%1051=565%:%
+%:%1053=566%:%
+%:%1063=568%:%
+%:%1064=569%:%
+%:%1066=570%:%
+%:%1067=570%:%
+%:%1068=571%:%
+%:%1069=572%:%
+%:%1070=572%:%
 %:%1072=572%:%
-%:%1073=573%:%
-%:%1074=573%:%
-%:%1076=573%:%
-%:%1080=573%:%
-%:%1081=573%:%
-%:%1083=574%:%
-%:%1084=575%:%
-%:%1085=576%:%
-%:%1086=577%:%
-%:%1087=578%:%
-%:%1110=584%:%
-%:%1111=585%:%
-%:%1112=586%:%
-%:%1113=587%:%
-%:%1122=589%:%
-%:%1134=591%:%
-%:%1135=592%:%
-%:%1136=593%:%
-%:%1137=594%:%
-%:%1141=596%:%
-%:%1142=597%:%
-%:%1144=599%:%
-%:%1145=599%:%
-%:%1146=600%:%
-%:%1147=601%:%
-%:%1148=601%:%
-%:%1149=602%:%
-%:%1152=603%:%
+%:%1076=572%:%
+%:%1077=572%:%
+%:%1079=573%:%
+%:%1080=574%:%
+%:%1081=575%:%
+%:%1082=576%:%
+%:%1083=577%:%
+%:%1106=583%:%
+%:%1107=584%:%
+%:%1108=585%:%
+%:%1109=586%:%
+%:%1118=588%:%
+%:%1130=590%:%
+%:%1131=591%:%
+%:%1132=592%:%
+%:%1133=593%:%
+%:%1137=595%:%
+%:%1138=596%:%
+%:%1140=598%:%
+%:%1141=598%:%
+%:%1142=599%:%
+%:%1143=600%:%
+%:%1144=600%:%
+%:%1145=601%:%
+%:%1148=602%:%
+%:%1152=602%:%
+%:%1153=602%:%
+%:%1154=602%:%
 %:%1156=603%:%
-%:%1157=603%:%
-%:%1158=603%:%
-%:%1160=604%:%
-%:%1161=605%:%
-%:%1171=607%:%
-%:%1172=608%:%
-%:%1173=609%:%
-%:%1174=610%:%
-%:%1175=611%:%
-%:%1176=612%:%
-%:%1177=613%:%
-%:%1178=614%:%
-%:%1179=615%:%
-%:%1180=616%:%
-%:%1181=617%:%
-%:%1182=618%:%
-%:%1183=619%:%
-%:%1184=620%:%
-%:%1185=621%:%
-%:%1187=623%:%
-%:%1188=623%:%
-%:%1189=624%:%
+%:%1157=604%:%
+%:%1167=606%:%
+%:%1168=607%:%
+%:%1169=608%:%
+%:%1170=609%:%
+%:%1171=610%:%
+%:%1172=611%:%
+%:%1173=612%:%
+%:%1174=613%:%
+%:%1175=614%:%
+%:%1176=615%:%
+%:%1177=616%:%
+%:%1178=617%:%
+%:%1179=618%:%
+%:%1180=619%:%
+%:%1181=620%:%
+%:%1183=622%:%
+%:%1184=622%:%
+%:%1185=623%:%
+%:%1186=624%:%
+%:%1187=625%:%
+%:%1188=625%:%
 %:%1190=625%:%
-%:%1191=626%:%
-%:%1192=626%:%
-%:%1194=626%:%
-%:%1198=626%:%
-%:%1199=626%:%
-%:%1201=627%:%
-%:%1202=628%:%
-%:%1203=629%:%
-%:%1204=630%:%
-%:%1205=631%:%
-%:%1206=632%:%
-%:%1216=634%:%
-%:%1217=635%:%
-%:%1218=636%:%
-%:%1219=637%:%
-%:%1223=639%:%
-%:%1224=640%:%
-%:%1225=641%:%
-%:%1227=643%:%
-%:%1228=643%:%
-%:%1229=644%:%
-%:%1230=644%:%
-%:%1232=645%:%
-%:%1233=646%:%
-%:%1234=646%:%
-%:%1235=647%:%
-%:%1236=648%:%
-%:%1237=648%:%
-%:%1238=649%:%
-%:%1241=650%:%
-%:%1245=650%:%
-%:%1246=650%:%
-%:%1248=651%:%
-%:%1249=652%:%
-%:%1250=653%:%
-%:%1260=655%:%
-%:%1261=656%:%
-%:%1262=657%:%
-%:%1263=658%:%
+%:%1194=625%:%
+%:%1195=625%:%
+%:%1197=626%:%
+%:%1198=627%:%
+%:%1199=628%:%
+%:%1200=629%:%
+%:%1201=630%:%
+%:%1202=631%:%
+%:%1212=633%:%
+%:%1213=634%:%
+%:%1214=635%:%
+%:%1215=636%:%
+%:%1219=638%:%
+%:%1220=639%:%
+%:%1221=640%:%
+%:%1223=642%:%
+%:%1224=642%:%
+%:%1225=643%:%
+%:%1226=643%:%
+%:%1228=644%:%
+%:%1229=645%:%
+%:%1230=645%:%
+%:%1231=646%:%
+%:%1232=647%:%
+%:%1233=647%:%
+%:%1234=648%:%
+%:%1237=649%:%
+%:%1241=649%:%
+%:%1242=649%:%
+%:%1244=650%:%
+%:%1245=651%:%
+%:%1246=652%:%
+%:%1256=654%:%
+%:%1257=655%:%
+%:%1258=656%:%
+%:%1259=657%:%
+%:%1261=659%:%
+%:%1262=659%:%
+%:%1263=660%:%
 %:%1265=660%:%
-%:%1266=660%:%
-%:%1267=661%:%
-%:%1269=661%:%
-%:%1273=661%:%
-%:%1274=661%:%
-%:%1276=662%:%
-%:%1284=662%:%
-%:%1285=663%:%
+%:%1269=660%:%
+%:%1270=660%:%
+%:%1272=661%:%
+%:%1280=661%:%
+%:%1281=662%:%
+%:%1282=663%:%
+%:%1283=663%:%
+%:%1284=664%:%
 %:%1286=664%:%
-%:%1287=664%:%
-%:%1288=665%:%
-%:%1290=665%:%
-%:%1294=665%:%
-%:%1295=665%:%
-%:%1297=666%:%
-%:%1307=668%:%
-%:%1308=669%:%
-%:%1309=670%:%
-%:%1317=672%:%
+%:%1290=664%:%
+%:%1291=664%:%
+%:%1293=665%:%
+%:%1303=667%:%
+%:%1304=668%:%
+%:%1305=669%:%
+%:%1313=671%:%

### 2022-03-07 paper/output/document/thesis_2_methods.tex
spring cleaning xoxoxo

--- 2022-02-18 paper/output/document/thesis_2_methods.tex
@@
 I formalize this ethical theory (Dyadic Deontic Logic), and an interactive theorem prover in which I 
-implement the formalized ethical theory (Isabelle/HOL). In this section, I describe these components, 
-present the philosophical, logic, and computational background underlying my system, and explain
-the consequences of each of the three choices I make.
-
-These specific components determine the features
-and limitations of my implementation of automated ethics, but other choices of 
+implement the formalized ethical theory (Isabelle/HOL). In this section, I describe these components and 
+present the philosophical, logic, and computational background underlying my system.
+
+These three components determine the features
+and limitations of my implementation of automated ethics. Other choices of 
 components, such as another ethical theory, a different logic, or a different theorem prover could be 
@@
 attractive candidates for automation because rules are generally computationally tractable \cite[1]{powers}. 
-Intuitively, algorithms are rules or procedures for problem solving and Kantian ethics (which is one kind 
+Intuitively, algorithms are procedures for problem solving and Kantian ethics (which is a kind 
 of deontological theory) offers one such 
@@
 consequentialism are broad ethical traditions, while Kantian ethics is a specific ethical theory within
-the deontological tradition, but``if any philosopher is regarded as central
-to deontological moral theories, it is surely Immanuel Kant" \citep{sepdeont}. Out of the three major ethical
-traditions, deontology has the most central representative in the form of Kant. Deontology's comparatively 
+deontology, the third major ethical tradition. However, Kantian ethics is not merely a kind of deontology
+but is widely regarded as deontology's central representative \citep{sepdeont}. Deontology's comparatively 
 greater focus on Kant means that my choice of Kant as a guiding figure is less controversial for deontologists 
-than, for example, the choice of Bentham as the guiding figure of consequentialism.} Kantian ethics is 
-more amenable to automation.
+than, for example, the choice of Bentham as the guiding figure of consequentialism. Given that most deontological
+theories have some connection to or basis in Kantian ethics, I choose to focus on Kantian ethics, instead
+of deontology more broadly. } Kantian ethics is more amenable to automation.
 
@@
 to present a comprehensive overview of all consequentialist or virtue ethical theories. Instead, I 
-present a sample of some approaches in each tradition and argue that deontology is more straightforward 
+some example approaches in each tradition and argue that deontology is more straightforward 
 to formalize than these approaches. Insofar as my project serves 
@@
 \begin{isamarkuptext}%
-A consequentialist ethical theory is an ethical theory that evaluates an 
+A consequentialist ethical theory evaluates an 
 action by evaluating its consequences.\footnote{There is long debate about what exactly makes an ethical theory consequentialist \citep{consequentialismsep}. 
@@
 utilitarianism is a form of consequentialism in which the moral action 
-is the action that produces the most good \citep{utilsep}. The focus
+is the action that produces the most good \citep{utilsep}. This focus
 on the consequences of action distinguishes consequentialists from deontologists, who derive the moral worth
@@
 reasoning requires more knowledge about the state of the world than Kantian ethics. Consequentialism
-requires knowledge about some or all consequences following an action. This requires that an automated 
-ethical system somehow collect a subset of the infinite consquences of following an action, a difficult, 
+requires knowledge about some or all consequences following an action. This means that an automated 
+consequentialist system must somehow collect a subset of the infinite consquences of following an action, a difficult, 
 if not impossible, task. Moreover, compiling this database of consequences requires 
-answering difficult questions about which consequences were actually caused \footnote
+determining which consequences were actually caused \footnote
 {David Hume argues that many straightforward accounts of causation face difficulties \citep{hume}, 
@@
 that first causes, or noumena, are unknowable by human beings \citep{kantnoumena}.} by an action and
-determining the state of the world before and after an action. As acts become
+characterizing the state of the world before and after an action. As acts become
 more complex and affect more people, the computational time and space required to calculate and store
@@
 \begin{isamarkuptext}%
-An automated consequentialist reasoner must also take a stance on the debate over
-what qualifies as a ``good consequence,'' or what the theory of the good is. For example, hedonists associate
+An automated consequentialist reasoner must also adopt a specific theory of the good, or account of 
+what qualifies as a ``good consequence.'' For example, hedonists associate
 good with the presence of pleasure and the absence of pain, while preference utiliarians believe that good is 
@@
 judgements about whether a state of affairs actually satisifes the relevant criteria for goodness. 
-Perfect knowledge of tens of thousands of 
-people's pleasure or preferences or welfare or rights is impossible. Either a human being 
+Perfect knowledge of tens of thousands of people's pleasure or preferences or welfare or rights is 
+difficult, if not impossible.\footnote{Even if it were possible, collecting this kind of data poses 
+privacy and surveillance risks.} Either a human being 
 assigns values to states of affairs, which doesn't scale, or the machine does, 
-which requires massive common-sense and increases room for doubting the system's judgements. This may be 
-a tractable problem, but it is much more difficult than the equivalent Kantian task of formulating
+which requires massive factual background and increases room for doubting the system's judgements. This may be 
+a tractable problem, but it is more difficult than the equivalent Kantian task of formulating
 and evaluating an action.%
@@
 Because of its intuitive appeal, computer scientists have tried to formalize consequentialism in the past.
-These efforts cannot escape the debates outlined above. For example, Abel et al. represent ethics as a
+These efforts cannot circumvent the challenges outlined above. For example, Abel et al. represent ethics as a
 Markov Decision Process (MDP), with reward functions customized to particular ethical dilemmas 
@@
 utilitarian automated reasoner chooses hedonism\footnote{Recall that hedonism views pleasure as good
-and pain as bad.} as the theory of the good \citep[2]{util2}. Again, their proposal assumes that pleasure and pain can be 
+and pain as bad.} as the theory of the good \citep[2]{util2}. Their proposal assumes that pleasure and pain can be 
 given numeric values and that these values can be aggregated with a simple sum, taking an implicit
@@
 ethicists present a list of virtues, such as the Buddhist virtue of equanimity \citep{mcrae}. An automated virtue 
-ethical agent will need to commit to a particular theory of the virtues, a controversial choice. 
+ethical agent will need to commit to a list of virtues, a controversial choice. 
 Virtue ethicists robustly debate which traits qualify as virtues, what each virtue actually means, and 
-what kinds of feelings or attitudes must accompany virtuous action.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
+what kinds of feelings or attitudes must accompany virtuous action.
+
 Another difficulty with automating virtue ethics is that the unit of evaluation for virtue ethics
@@
 \begin{isamarkuptext}%
-One potential appeal of virtue ethics is that many virtue ethical theories involve some notion of 
+Many virtue ethical theories involve some notion of 
 moral habit, which seems to be amenable to a machine learning approach. Artistotle, for example, argued 
-that cultivating virtuous action requires making such action habitual through moral education \citep{aristotle}. This
-implies that ethical behavior can be learned from some dataset of virtuous acts, such as
-those that an ideal virtuous agent would undertake. These 
-theories seem to point towards a machine learning approach to automated ethics, in which ethics is 
-learned from a dataset of acts tagged as virtuous or not virtuous.
+that cultivating virtuous action requires making such action habitual \citep{aristotle}. This seems to 
+point to a machine learning approach to automated ethics, in which ethical behavior is learned from a 
+dataset of acts tagged as virtuous if they are the act that an ideal virtuous agent would undertake.
 
 Just as prior work in consequentialism takes implicit or explicit stances on debates in consequentialist
-literature, so does work in machine learning-based virtue ethics. For example, the training 
+literature, so must work in machine learning-based virtue ethics. For example, the training 
 dataset with acts labelled as virtuous or not virtuous will contain an implicit view on what the virtues
-are and how certain acts impact an agent's moral character. Because there is no canonical list of virtues
-that virtue ethicists accept, this implicit view will likely be controversial.
+are and how certain acts impact an agent's moral character. Because there is no canonical list of all virtues
+that virtue ethicists accept, this implicit view will likely be controversial. Even virtue ethicists agree
+that certain traits, like courage, are virtues debate the exact definitions of these traits.
 
@@
 approach does not face. Many machine learning algorithms cannot sufficiently explain their 
-decisions to a human being, and often find patterns in datasets that don't 
+decisions to a human being and often find patterns in datasets that don't 
 cohere with the causes that a human being would identify \citep{puiutta}. While there is significant activity 
@@
 machine learning. It also applies to a broader class of work in automated ethics 
-that uses ``bottom-up" approaches, in which a system learns moral judgements from prior judgements. 
-I will extend this argument to general bottom-up approaches in Section Related Work.}%
+that uses a ``bottom-up'' approach, in which a system learns moral judgements from prior judgements. 
+I will extend this argument to general bottom-up approaches in Section \ref{relatedwork}.}%
 \end{isamarkuptext}\isamarkuptrue%
@@
 on practical reason, which is the kind of reason that we 
-use to decide what to do and the source of our agency. In \emph{The Groundwork of the Metaphysics of Morals}, Kant explains that 
+use to decide what to do. In \emph{The Groundwork of the Metaphysics of Morals}, Kant explains that 
 rational beings are unique because we act ``in accordance with 
-the representations of laws'' \citep[4:412]{groundwork}. In contrast, a ball thrown into the air acts 
+the representations of laws'' \citep[4:412]{groundwork}. A ball thrown into the air acts 
 according to the laws of physics. It cannot ask itself, ``Should I fall back to the ground?'' 
@@
 
-The will operates by adopting, or willing, maxims, which are its perceived reasons for acting. Kant defines a maxim as 
+The will operates by adopting or willing maxims, which are its perceived reasons for acting. Kant defines a maxim as 
 the ``subjective principle of willing,'' or the reason that the will \emph{subjectively} gives 
@@
 of some combination of circumstances, 
-act, and goal.\footnote{For more discussion of the definition of a maxim, see Section What Is a Maxim}
+act, and goal.\footnote{For more discussion of the definition of a maxim, see Section \ref{whatisamaxim}.}
 One example of a maxim is ``When I am hungry, I will eat a doughnut in order to satisfy my sweet tooth.''
@@
 The form of an obligatory maxim is given by the categorical imperative. 
-An imperative is a command, such as ``Close the door" or ``Eat the doughnut in order to satisfy your 
-sweet tooth." An imperative is categorical if it holds unconditionally for all rational agents in all 
+An imperative is a command, such as ``Close the door'' or ``Eat the doughnut in order to satisfy your 
+sweet tooth.'' An imperative is categorical if it holds unconditionally for all rational agents in all 
 circumstances. Kant argues that the moral law must be a categorical imperative \citep[5]{groundwork}. 
@@
 Armed with this understanding of practical reason, Kant presents the categorical 
-imperative. He presents three ``formulations" or versions of the categorical imperative. In this project, 
-I focus on the first formulation, the Formula of Universal Law, and I explain this choice in Section \ref{whyful}.
+imperative. He presents three ``formulations'' or versions of the categorical imperative. In this project, 
+I focus on the first formulation, the Formula of Universal Law, and I justify this choice in Section \ref{whyful}.
 
@@
 at the same time will that it become a universal law'' \cite[34]{groundwork}. This formulation
-generates the universalizability test, which we can use to test the moral worth of a maxim by 
+generates the universalizability test, in which we test the moral worth of a maxim by 
 imagining a world in which it becomes a universal law and attempting to will the maxim in that world.
@@
 A maxim itself is an object with a thin representation for a computer, as compared to more complex 
-objects like states of affairs or moral character. Later in my project, I argue that a maxim can be 
-represented simply as a tuple of circumstances, act, and goal.\footnote{For more, see Section \ref{whatisamaxim}.} 
-This representation is simple and efficient, especially when compared to the representations of a causal 
+objects like states of affairs or moral character. In Section \ref{whatisamaxim}, I argue that a maxim can be 
+represented simply as a tuple of circumstances, act, and goal.
+This representation is simple and efficient, especially when compared to representations of a causal 
 chain or a state of affairs or moral character. This property not only reduces the computational complexity
@@
 \begin{isamarkuptext}%
-One debate in Kantian 
-ethics is the role of ``common-sense'' reasoning. Kantian ethics requires common-sense reasoning to 
-determine which circumstances are ``morally relevant'' in the formulation of a maxim. Many misunderstandings
-in Kantian ethics are due to badly formulated maxims, so this question is important for an ethical 
-reasoner to answer.\footnote{For example, critics of Kantian ethics worry that the maxim, ``When I am a
-man, I will marry a man because I want to spend my life with him'' fails the universalizability
-test because if all men only married men, sexual reproduction would stop. This argument implies 
-that Kantian ethics is homophobic. Kantians often respond by arguing that the correct formulation of 
-this maxim is, ``When I love a man, I will marry him because I want to spend my life with him,'' which
-is universalizable because if everyone marries who they love, some men will marry women and others will
-marry men.} My system does not need to answer this question because I assume a properly crafted
-maxim as input and apply the categorical imperative to this input. Using my system in a fully automated
-moral agent will require answering this question, a challenging computational and philosophical task.
-
-Common-sense reasoning is also relevant when applying the universalizability test itself. Consider the example
+One challenge for automating Kantian ethics is the need for what humans often understand as ``common-sense'', or factual and 
+situational background. Common-sense is needed when formulating a maxim and determining if a maxim 
+violates the Formula of Universal Law. Maxims include the circumstances in which they apply and
+determining which circumstances are ``morally relevant'' to a maxim requires factual background. 
+My system does not need to answer this question because I assume a properly crafted
+maxim as input and apply the categorical imperative to this input. Using my system to build a fully automated
+moral agent will require answering this question, a challenging computational and philosophical task. I
+discuss this problem in greater detail in Section \ref{whatisamaxim} and Section \ref{AIethics}.
+
+Common sense is also relevant when applying the universalizability test itself. Consider the example
 maxim ``When broke, I will falsely promise to repay a loan
@@
 an action and virtue ethical agents need common sense to determine which virtues an action
-reflects. Making any ethical judgement requires robust conceptions of the action
-at hand, falsely promising in this case. The advantage of Kantian ethics is that this is all the common 
-sense that it requires, whereas a consequentialist or virtue ethical agent will require much more\footnote{
-In Sections Lying and Murderer, I also use my system to demonstrate that Kantian ethics requires relatively thin conceptions 
-of concepts like falsely promising.}. All
+reflects. For example, in the case of virtue ethics, in order to see that saving a baby from a lion 
+requires courage, a reasoner must have enough background knowledge to know that lions are scary. Making any 
+ethical judgement requires robust conceptions of the action at hand, but Kantian ethics requires far less common sense 
+than a consequentialism or virtue ethics.\footnote{
+In Sections \ref{joking} and \ref{murderer}, I use my system to demonstrate that Kantian ethics requires relatively lightweight, uncontroversial definitions 
+of concepts like falsely promising.} All
 moral theories evaluating falsely promising will a robust definition of promising, 
-but consequentialism and virtue ethics will also require additional information
-that Kantian ethics will not. Thus, although the need for common sense poses a challenge to automated
+but consequentialism and virtue ethics will require more information than Kantian ethics.
+Thus, although the need for common sense poses a challenge to automated
 Kantian ethics, this challenge is more acute for consequentialism or virtue ethics.%
@@
 \begin{isamarkuptext}%
-Earlier I mentioned that Kant presents three formulations, or versions, 
-of what he calls the ``supreme law of morality," but that I focus on the first of these three. In this section, 
+Kant presents three formulations, or versions, 
+of what he calls the ``supreme law of morality," but I focus on the first of these three. In this section, 
 I argue that the Formula of Universal Law, specifically, is the easiest part of Kantian ethics to automate
@@
 precise. The FUL's precision reduces ambiguity, allowing me to remain faithful to philosophical
-literature on Kant. Precision reduces the need to make choices to resolve debates 
-and ambiguities. Minimizing these choices minimizes 
-arbitrariness in my formalization and puts it on solid philosophical footing.
+literature on Kant. Ambiguity in an ethical theory, such as the ambiguity about what counts as a good consequence
+in the case of consequentialism, forces an implementation of automated ethics to take stances on controversial
+philosophical debates. Minimizing the need for such choices puts my implementation on solid philosophical footing.
 
@@
 that the three formulations of the categorical imperative are equivalent \citep{groundwork}. While this 
-argument is disputed \cite{sepkant}, for those who believe it, the
+argument is disputed \citep{sepkant}, for those who believe it, the
 stakes for my choice of the FUL are greatly reduced. If all formulations are equivalent, then a formalization of the FUL
@@
 understand the FUL as the strongest or most foundational, and thus an appropriate initial choice for 
-formalizations. Korsgaard characterizes the three formulations of the categorical
+automation. Korsgaard characterizes the three formulations of the categorical
 imperative according to Rawls' general and special conception of justice. The general conception applies
 universally and can never be violated, while the special conception represents an ideal for us to
-live towards. For example, the special conception may require that we prefer some job applicants
+live towards that may not be possible to achieve. For example, the special conception may require that we prefer some job applicants
 over others in order to remedy historical injustice, and the general conception may require that such
@@
 Humanity represents his special conception. The FUL's prescriptions can never be violated, even in the most
-non-ideal circumstances imaginable, but the FUH is merely a standard to live towards that might not be 
-achieved. Thus, the FUL generates stronger requirements than the other two formulations and reflects 
+non-ideal circumstances imaginable, but the FUH is merely an ideal to strive towards. Thus, the FUL 
+generates stronger requirements than the other two formulations and reflects 
 the bare minimum standard of Kant's ethics. Because the FUL's prescriptions outweigh those of the other two formulations,
-automating it creates a functional, minimum ethical theory that can serve as a foundation for implementations
-of other aspects of Kant's ethics.%
+it serves as a functional, minimal version of Kantian ethics.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 I formalize Kantian ethics by representing it as an axiom on top of a base logic. In this section, 
-I present the logical background necessary to understand my work and my choice of Dyadic Deontic Logic (DDL).%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
+I present the logical background necessary to understand my work and my choice of Dyadic Deontic Logic (DDL).
+
 Traditional modal logics include the necessitation operator, denoted as $\Box$. In simple modal logic
@@
 } In situations where duty is violated, the logic breaks down 
-and produces paradoxical results. Thus, I use an improved deontic logic instead of SDL for this work.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
+and produces paradoxical results. Thus, I use an improved deontic logic instead of SDL for this work.
+
 I use as my base logic Carmo and Jones's Dyadic Deontic Logic (DDL), which improves on SDL \citep{CJDDL}. 
 It introduces a dyadic obligation operator $O\{A \vert B\}$ 
-to represent the sentence ``A is obligated in the context B". The introduction of context allows DDL to
-gracefully handle contrary-to-duty conditionals by modifying the context. The obligation operator uses 
+to represent the sentence ``A is obligated in the context B.'' The introduction of context allows DDL to
+gracefully handle contrary-to-duty conditionals, since violations of duty simply modify the context. The obligation operator uses 
 a neighborhood semantics, instead of the Kripke semantics \citep{neighborhood1, neighborhood2}. While Kripke
@@
 automatic and interactive/manual theorem proving. To demonstrate the power and usage of Isabelle and 
-make DDL more precise, I walk through my \color{red}reimplementation
-of Benzmueller, Farjami, and Parent's implementation of DDL in Isabelle/HOL \citep{BFP, logikey}\color{black}.%
+make DDL more precise, I walk through Benzmueller, Farjami, and Parent's implementation of DDL in Isabelle/HOL, 
+which serves as the basis of my formalization of Kantian Ethics.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 to do this include \texttt{typedecl}, which declares a new type, \texttt{type\_synonym}, which defines
-an abbreviation for a complex type, and \texttt{consts}, which defines a constant.%
+an abbreviation for a complex type, and \texttt{consts}, which defines constants.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \ i\ %
-\isamarkupcmt{This is an Isabelle comment. i is the type for a set of worlds.%
+\isamarkupcmt{$i$ is the type for a set of worlds.%
 }\isanewline
 %
-\isamarkupcmt{This is a line of actual code used in my implementation. For the rest of the thesis, text typeset 
-like this represents Isabelle code.%
+\isamarkupcmt{This is an Isabelle comment, while the text above is a line of actual, executable Isabelle code.%
 }\isanewline
@@
 \ t\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}i\ {\isasymRightarrow}\ bool{\isacharparenright}{\isachardoublequoteclose}\ %
-\isamarkupcmt{t represents a set of DDL formulae.%
+\isamarkupcmt{$t$ represents a set of DDL formulas.%
 }\isanewline
 %
-\isamarkupcmt{A set of formulae is defined by its truth value at a set of worlds. For example, the set \{\emph{True}\}
+\isamarkupcmt{A set of formulas is defined by its truth value at a set of worlds. For example, the set \{\emph{True}\}
 is true at any set of worlds.%
-}\isanewline
-%
+}%
 \begin{isamarkuptext}%
@@
 \isamarkupcmt{$ob\, (context)\, (term)$ is \emph{True} if the term is obligatory in this context%
-}\isanewline
-%
-\begin{isamarkuptext}%
-In a semantic embedding, axioms are modelled as restrictions on models of the system. In this case,
-a model is specificied by the relevant accessibility relations (such as $ob$), so it suffices to place conditions on 
+}%
+\begin{isamarkuptext}%
+In a semantic embedding like this one, axioms are modelled as restrictions on models of the system. In this case,
+a model is specified by the relevant accessibility relations (such as $ob$), so it suffices to place conditions on 
 the accessibility relations. Isabelle allows users to create new axiomatizations on top of its base
@@
 with respect to changing contexts.%
-}\isanewline
-%
+}%
 \isadelimdocument
@@
 is unwieldly. In my work, I mostly perform syntactic proofs, so I must define the syntax of the logic.
-Isabelle already knows the semantics of the axioms of this logic, so I can define the syntax as abbreviations for different
-formulas involving the axioms above. Each DDL operator is represented
-as a HOL formula. Isabelle automatically unfolds formulae defined with the \isatt{abbreviation} command 
+Isabelle already knows the semantics of the axioms of this logic, so I can define the syntax as abbreviations 
+involving the axioms above. Each DDL operator is represented
+as a HOL formula. Isabelle automatically unfolds formulas defined with the \isatt{abbreviation} command 
 whenever they are applied. While the shallow embedding is performant (because it uses Isabelle's original 
@@
 \begin{isamarkuptext}%
-Modal operators will be useful for my purposes, implemented below.%
+\noindent Modal operators, implemented below, will be useful for my purposes.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-The most important operator for my project is the obligation operator, implemented below.%
+\noindent The most important operator for my project is the obligation operator, implemented below.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupcmt{O$\{B \vert A\}$ can be read as ``B is obligatory in the context A"%
-}\isanewline
-%
+\isamarkupcmt{O$\{B \vert A\}$ can be read as ``B is obligatory in the context A''%
+}%
 \begin{isamarkuptext}%
@@
 \begin{isamarkuptext}%
-Finally, validity will be useful when discussing metalogical/ethical properties.%
+\noindent Finally, validity will be useful when discussing metalogical/ethical properties.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \isamarkupcmt{A proposition is valid if it is true at all worlds.%
-}\isanewline
-%
+}%
 \begin{isamarkuptext}%
@@
 \begin{isamarkuptext}%
-In the proof above, {\color{red} by simp} indicates the use of the Simplification proof method, 
-which involves unfolding definitions and applying theorems directly. HOL has $True$ as a theorem,
+In the proof above, ``by simp'' indicates the use of the Simplification proof method, 
+which unfolds definitions and applies theorems directly. HOL has $True$ as a theorem,
 which is why this theorem was so easy to prove.%
@@
 %:%47=19%:%
-%:%48=20%:%
-%:%57=22%:%
+%:%56=21%:%
+%:%68=24%:%
 %:%69=25%:%
@@
 %:%95=51%:%
-%:%96=52%:%
-%:%105=55%:%
+%:%104=54%:%
+%:%116=56%:%
 %:%117=57%:%
@@
 %:%124=64%:%
-%:%125=65%:%
-%:%129=67%:%
+%:%128=66%:%
+%:%132=68%:%
 %:%133=69%:%
@@
 %:%156=92%:%
-%:%157=93%:%
-%:%161=96%:%
+%:%160=95%:%
+%:%164=97%:%
 %:%165=98%:%
@@
 %:%254=165%:%
+%:%255=166%:%
+%:%256=167%:%
+%:%257=168%:%
 %:%258=169%:%
@@
 %:%264=175%:%
-%:%265=176%:%
-%:%266=177%:%
-%:%270=179%:%
+%:%268=177%:%
+%:%272=179%:%
+%:%273=180%:%
 %:%274=181%:%
@@
 %:%297=204%:%
-%:%298=205%:%
-%:%299=206%:%
-%:%300=207%:%
-%:%309=210%:%
+%:%306=207%:%
+%:%318=209%:%
+%:%319=210%:%
+%:%320=211%:%
 %:%321=212%:%
@@
 %:%374=265%:%
-%:%375=266%:%
-%:%376=267%:%
-%:%377=268%:%
-%:%381=271%:%
+%:%378=268%:%
+%:%382=270%:%
+%:%383=271%:%
+%:%384=272%:%
 %:%385=273%:%
@@
 %:%401=289%:%
-%:%402=290%:%
-%:%403=291%:%
-%:%404=292%:%
-%:%408=295%:%
+%:%405=292%:%
+%:%409=294%:%
+%:%410=295%:%
+%:%411=296%:%
 %:%412=297%:%
@@
 %:%436=321%:%
-%:%437=322%:%
-%:%438=323%:%
-%:%439=324%:%
-%:%440=325%:%
-%:%441=326%:%
-%:%442=327%:%
-%:%443=328%:%
-%:%452=330%:%
-%:%464=333%:%
-%:%465=334%:%
-%:%466=335%:%
-%:%467=336%:%
-%:%468=337%:%
-%:%469=338%:%
-%:%470=339%:%
-%:%471=340%:%
-%:%472=341%:%
-%:%473=342%:%
-%:%474=343%:%
-%:%475=344%:%
-%:%476=345%:%
-%:%477=346%:%
-%:%478=347%:%
-%:%479=348%:%
-%:%480=349%:%
-%:%481=350%:%
-%:%482=351%:%
-%:%483=352%:%
-%:%484=353%:%
-%:%485=354%:%
-%:%486=355%:%
-%:%487=356%:%
-%:%488=357%:%
-%:%489=358%:%
-%:%490=359%:%
-%:%491=360%:%
-%:%492=361%:%
-%:%493=362%:%
-%:%494=363%:%
-%:%495=364%:%
-%:%496=365%:%
-%:%497=366%:%
-%:%498=367%:%
-%:%499=368%:%
-%:%500=369%:%
-%:%501=370%:%
-%:%502=371%:%
-%:%503=372%:%
-%:%504=373%:%
-%:%505=374%:%
-%:%506=375%:%
-%:%507=376%:%
-%:%508=377%:%
-%:%509=378%:%
-%:%510=379%:%
-%:%511=380%:%
-%:%512=381%:%
-%:%513=382%:%
-%:%514=383%:%
-%:%523=385%:%
-%:%535=387%:%
-%:%536=388%:%
+%:%445=323%:%
+%:%457=325%:%
+%:%458=326%:%
+%:%459=327%:%
+%:%460=328%:%
+%:%461=329%:%
+%:%462=330%:%
+%:%463=331%:%
+%:%464=332%:%
+%:%465=333%:%
+%:%466=334%:%
+%:%467=335%:%
+%:%468=336%:%
+%:%469=337%:%
+%:%470=338%:%
+%:%471=339%:%
+%:%472=340%:%
+%:%473=341%:%
+%:%474=342%:%
+%:%475=343%:%
+%:%476=344%:%
+%:%477=345%:%
+%:%478=346%:%
+%:%479=347%:%
+%:%480=348%:%
+%:%481=349%:%
+%:%482=350%:%
+%:%483=351%:%
+%:%484=352%:%
+%:%485=353%:%
+%:%486=354%:%
+%:%487=355%:%
+%:%488=356%:%
+%:%489=357%:%
+%:%490=358%:%
+%:%491=359%:%
+%:%492=360%:%
+%:%493=361%:%
+%:%494=362%:%
+%:%495=363%:%
+%:%496=364%:%
+%:%497=365%:%
+%:%498=366%:%
+%:%499=367%:%
+%:%500=368%:%
+%:%501=369%:%
+%:%502=370%:%
+%:%503=371%:%
+%:%504=372%:%
+%:%513=374%:%
+%:%525=376%:%
+%:%526=377%:%
+%:%527=378%:%
+%:%528=379%:%
+%:%529=380%:%
+%:%530=381%:%
+%:%531=382%:%
+%:%532=383%:%
+%:%533=384%:%
+%:%534=385%:%
+%:%535=386%:%
+%:%536=387%:%
+%:%537=388%:%
+%:%538=389%:%
+%:%539=390%:%
 %:%540=391%:%
@@
 %:%567=418%:%
-%:%571=420%:%
-%:%572=421%:%
-%:%573=422%:%
-%:%574=423%:%
-%:%575=424%:%
-%:%576=425%:%
-%:%577=426%:%
-%:%578=427%:%
-%:%579=428%:%
-%:%580=429%:%
-%:%581=430%:%
-%:%582=431%:%
-%:%583=432%:%
-%:%584=433%:%
-%:%585=434%:%
-%:%586=435%:%
-%:%587=436%:%
-%:%588=437%:%
-%:%589=438%:%
-%:%590=439%:%
-%:%591=440%:%
-%:%592=441%:%
-%:%593=442%:%
-%:%594=443%:%
-%:%595=444%:%
-%:%596=445%:%
-%:%597=446%:%
-%:%606=449%:%
-%:%618=451%:%
-%:%619=452%:%
-%:%620=453%:%
-%:%621=454%:%
-%:%622=455%:%
-%:%623=456%:%
-%:%632=459%:%
-%:%644=461%:%
-%:%645=462%:%
-%:%646=463%:%
-%:%648=465%:%
-%:%649=465%:%
-%:%650=465%:%
-%:%651=465%:%
-%:%653=466%:%
-%:%654=467%:%
-%:%655=467%:%
-%:%656=468%:%
-%:%657=469%:%
-%:%658=469%:%
-%:%659=469%:%
-%:%660=469%:%
-%:%662=470%:%
-%:%663=471%:%
-%:%664=471%:%
-%:%667=485%:%
-%:%668=486%:%
-%:%669=487%:%
-%:%671=489%:%
-%:%672=489%:%
-%:%673=489%:%
-%:%674=489%:%
-%:%675=490%:%
-%:%676=490%:%
-%:%677=490%:%
-%:%680=494%:%
-%:%681=495%:%
-%:%682=496%:%
-%:%683=497%:%
-%:%685=499%:%
-%:%686=499%:%
-%:%687=523%:%
-%:%688=524%:%
-%:%690=525%:%
-%:%691=526%:%
-%:%692=527%:%
-%:%693=528%:%
-%:%694=528%:%
-%:%702=535%:%
-%:%714=537%:%
-%:%715=538%:%
-%:%716=539%:%
-%:%717=540%:%
-%:%718=541%:%
-%:%719=542%:%
-%:%720=543%:%
-%:%724=559%:%
-%:%726=560%:%
-%:%727=560%:%
-%:%728=561%:%
-%:%730=562%:%
-%:%731=563%:%
-%:%732=563%:%
-%:%733=564%:%
-%:%734=564%:%
-%:%735=565%:%
-%:%737=566%:%
-%:%740=568%:%
-%:%742=569%:%
-%:%743=569%:%
-%:%744=570%:%
-%:%746=571%:%
-%:%747=571%:%
-%:%750=591%:%
-%:%751=592%:%
-%:%753=593%:%
-%:%754=593%:%
-%:%755=594%:%
-%:%756=595%:%
-%:%757=595%:%
-%:%758=596%:%
-%:%759=597%:%
-%:%760=597%:%
-%:%761=598%:%
-%:%763=599%:%
-%:%764=600%:%
-%:%767=602%:%
-%:%769=603%:%
-%:%770=603%:%
-%:%771=604%:%
-%:%773=605%:%
-%:%774=605%:%
-%:%777=613%:%
-%:%778=614%:%
-%:%779=615%:%
-%:%780=616%:%
-%:%782=619%:%
-%:%783=619%:%
-%:%784=619%:%
-%:%786=619%:%
-%:%790=619%:%
-%:%791=619%:%
-%:%793=620%:%
-%:%794=621%:%
-%:%795=621%:%
-%:%797=622%:%
-%:%798=623%:%
-%:%799=624%:%
-%:%809=626%:%
-%:%810=627%:%
-%:%811=628%:%
+%:%568=419%:%
+%:%569=420%:%
+%:%570=421%:%
+%:%571=422%:%
+%:%572=423%:%
+%:%573=424%:%
+%:%574=425%:%
+%:%575=426%:%
+%:%576=427%:%
+%:%577=428%:%
+%:%578=429%:%
+%:%579=430%:%
+%:%580=431%:%
+%:%581=432%:%
+%:%582=433%:%
+%:%583=434%:%
+%:%592=437%:%
+%:%604=439%:%
+%:%605=440%:%
+%:%606=441%:%
+%:%607=442%:%
+%:%608=443%:%
+%:%609=444%:%
+%:%618=447%:%
+%:%630=449%:%
+%:%631=450%:%
+%:%632=451%:%
+%:%634=453%:%
+%:%635=453%:%
+%:%636=453%:%
+%:%637=453%:%
+%:%639=454%:%
+%:%640=454%:%
+%:%641=455%:%
+%:%642=456%:%
+%:%643=456%:%
+%:%644=456%:%
+%:%645=456%:%
+%:%647=457%:%
+%:%648=458%:%
+%:%651=470%:%
+%:%652=471%:%
+%:%653=472%:%
+%:%655=474%:%
+%:%656=474%:%
+%:%657=474%:%
+%:%658=474%:%
+%:%659=475%:%
+%:%660=475%:%
+%:%663=477%:%
+%:%664=478%:%
+%:%665=479%:%
+%:%666=480%:%
+%:%668=482%:%
+%:%669=482%:%
+%:%670=506%:%
+%:%671=507%:%
+%:%673=508%:%
+%:%674=509%:%
+%:%675=510%:%
+%:%676=511%:%
+%:%684=516%:%
+%:%696=518%:%
+%:%697=519%:%
+%:%698=520%:%
+%:%699=521%:%
+%:%700=522%:%
+%:%701=523%:%
+%:%702=524%:%
+%:%706=538%:%
+%:%708=539%:%
+%:%709=539%:%
+%:%710=540%:%
+%:%712=541%:%
+%:%713=542%:%
+%:%714=542%:%
+%:%715=543%:%
+%:%716=543%:%
+%:%717=544%:%
+%:%719=545%:%
+%:%722=546%:%
+%:%724=547%:%
+%:%725=547%:%
+%:%726=548%:%
+%:%728=549%:%
+%:%731=567%:%
+%:%732=568%:%
+%:%734=569%:%
+%:%735=569%:%
+%:%736=570%:%
+%:%737=571%:%
+%:%738=571%:%
+%:%739=572%:%
+%:%740=573%:%
+%:%741=573%:%
+%:%742=574%:%
+%:%744=575%:%
+%:%745=576%:%
+%:%748=577%:%
+%:%750=578%:%
+%:%751=578%:%
+%:%752=579%:%
+%:%754=580%:%
+%:%757=585%:%
+%:%758=586%:%
+%:%759=587%:%
+%:%760=588%:%
+%:%762=591%:%
+%:%763=591%:%
+%:%764=591%:%
+%:%766=591%:%
+%:%770=591%:%
+%:%771=591%:%
+%:%773=592%:%
+%:%774=593%:%
+%:%775=593%:%
+%:%777=594%:%
+%:%778=595%:%
+%:%779=596%:%
+%:%789=598%:%
+%:%790=599%:%
+%:%791=600%:%

### 2022-03-08 paper/output/document/appendix.tex
ugh

@@
 I now implement Kroy's formalization of the Formula of Universal Law. Recall that the FUL says
-``act only in accordance with that maxim which you can at the same time will a universal law'' \citep{groundwork}.
+``act only in accordance with that maxim which you can at the same time will a universal law'' \citep[34]{groundwork}.
 Kroy interprets this to mean that if an action is permissible for a specific agent, then it must be permissible for everyone.
@@
         is thus circuar. The categorical imperative is supposed to be the complete,
-        self-contained rule of morality \cite{groundwork}, but Kroy's version of the FUL prescribes obligations 
+        self-contained rule of morality, but Kroy's version of the FUL prescribes obligations 
         in a self-referencing manner. The FUL is supposed to define what is permissible and what isn't, 

### 2022-03-08 paper/output/document/thesis_2_methods.tex
ugh

@@
 \begin{isamarkuptext}%
-In this paper I focus on Kantian ethics. Kant's theory is centered 
+Kant's theory is centered 
 on practical reason, which is the kind of reason that we 
@@
 rational beings are unique because we act ``in accordance with 
-the representations of laws'' \citep[4:412]{groundwork}. A ball thrown into the air acts 
+the representations of laws'' \citep[26]{groundwork}.\footnote{} A ball thrown into the air acts 
 according to the laws of physics. It cannot ask itself, ``Should I fall back to the ground?'' 
@@
 the ``subjective principle of willing,'' or the reason that the will \emph{subjectively} gives 
-to itself for acting \citep[16 footnote 1]{groundwork}. Many philosophers agree that a maxim consists 
+to itself for acting \citep[16, footnote 1]{groundwork}. Many philosophers agree that a maxim consists 
 of some combination of circumstances, 
@@
 %:%728=549%:%
-%:%731=567%:%
-%:%732=568%:%
-%:%734=569%:%
-%:%735=569%:%
-%:%736=570%:%
-%:%737=571%:%
-%:%738=571%:%
-%:%739=572%:%
-%:%740=573%:%
-%:%741=573%:%
-%:%742=574%:%
-%:%744=575%:%
-%:%745=576%:%
-%:%748=577%:%
-%:%750=578%:%
-%:%751=578%:%
-%:%752=579%:%
-%:%754=580%:%
-%:%757=585%:%
-%:%758=586%:%
-%:%759=587%:%
-%:%760=588%:%
-%:%762=591%:%
-%:%763=591%:%
-%:%764=591%:%
-%:%766=591%:%
-%:%770=591%:%
-%:%771=591%:%
-%:%773=592%:%
-%:%774=593%:%
-%:%775=593%:%
-%:%777=594%:%
-%:%778=595%:%
-%:%779=596%:%
-%:%789=598%:%
-%:%790=599%:%
-%:%791=600%:%
+%:%731=566%:%
+%:%732=567%:%
+%:%734=568%:%
+%:%735=568%:%
+%:%736=569%:%
+%:%737=570%:%
+%:%738=570%:%
+%:%739=571%:%
+%:%740=572%:%
+%:%741=572%:%
+%:%742=573%:%
+%:%744=574%:%
+%:%745=575%:%
+%:%748=576%:%
+%:%750=577%:%
+%:%751=577%:%
+%:%752=578%:%
+%:%754=579%:%
+%:%757=584%:%
+%:%758=585%:%
+%:%759=586%:%
+%:%760=587%:%
+%:%762=590%:%
+%:%763=590%:%
+%:%764=590%:%
+%:%766=590%:%
+%:%770=590%:%
+%:%771=590%:%
+%:%773=591%:%
+%:%774=592%:%
+%:%775=592%:%
+%:%777=593%:%
+%:%778=594%:%
+%:%779=595%:%
+%:%789=597%:%
+%:%790=598%:%
+%:%791=599%:%

### 2022-03-08 paper/output/document/thesis_3_implementation.tex
ugh

@@
 \begin{isamarkuptext}%
-In this section, I present the details of my implementation of automated Kantian ethics, which requires
-formalizing the FUL in Dyadic Deontic Logic and then implementing this logic in Isabelle/HOL. The final
-Isabelle library contains enough logical background and an axiom representing the categorical imperative. 
+In this section, I present the details of my implementation of automated Kantian ethics, which consists of
+a formalization of the FUL in Dyadic Deontic Logic and an implementation of this logic in Isabelle/HOL. The final
+Isabelle library is a logic that has the categorical imperative as an axiom and can express and derive moral judgements. 
 Using Isabelle's automated theorem proving abilities, my system can show that appropriately represented
-actions are, according to Kantian ethics, obligatory, permissible, or prohibited by proving or refuting sentences of the form ``A 
+actions are obligatory, permissible, or prohibited by proving or refuting sentences of the form ``A 
 is obligated to do B.'' I also present a testing framework to evaluate how faithful my implementation is 
-to philosophical literature. This testing framework shows that my system outperforms two other potential 
-implementations of automated Kantian ethics.%
+to philosophical literature. This testing framework shows that my system outperforms unmodified DDL 
+(a control group) and Moshe Kroy's prior formalization of the FUL \citep{kroy}.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-Formalizing the FUL requires defining and implementing enough logical background to represent 
-the FUL as an axiom. Dyadic
-Deontic Logic can express obligation and prohibition, but it cannot represent more complex features of 
-moral judgement like actions, subject, maxims, and ends. I augment DDL by adding representations 
-of these concepts, drawn from philosophical literature.%
+Formalizing the FUL requires implementing enough logical background to represent 
+the FUL as an axiom. Dyadic Deontic Logic can express obligation and prohibition, but it cannot 
+represent more complex features of moral judgement like actions, subject, maxims, and ends. I augment 
+DDL by adding representations of these concepts, drawn from philosophical literature.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-Kantian ethics is fundamentally action-guiding; the categorical
+Kantian ethics is action-guiding; the categorical
 imperative is a moral rule that agents can use to decide between potential actions. Thus, before I 
-begin to formalize a specific formulation of the categorical imperative, I must define the notions of 
+begin to formalize a specific formulation of the categorical imperative, I must define
 subjects and actions. I add representations of subjects and actions so that my new logic can express
@@
 of pre-existing types but is instead a new kind of object altogether. A type does not come with any 
-properties out of the box. There is no difference between declaring the type ``subject'' or any other
-type, such as ``color'' or ``mammal.'' I add some properties of this type below by creating formulas
-and more complex types that use this type, but I do not provide anything near a definition of a subject.
-It suffices to declare a new type to represent a subject without specifying any of its complex properties, 
-such as the idea that a subject must be rational or human. Instead of providing a complete definition of subject, 
-which would require wading into murky philosophical debates about the nature of agency, I provide a 
+properties out of the box. There is no difference between declaring a type with label ``subject'' or any other
+label, such as ``color'' or ``mammal.'' I add some properties of this type below by creating formulas
+and more complex types that use this type, but I do not provide a complete definition of a subject.
+Formalizing and using the FUL does not require many of the complex properties of a subject, such as 
+rationality or humanity. Thus, instead of providing a complete definition of subject, I can avoid murky
+philosophical debates about the nature of agency and instead provide a 
 ``thin'' definition that only includes the minimum necessary properties to apply the FUL. Throughout my 
@@
 
-In this interpretation, the defining feature of a subject is that it can act. 
+In this interpretation, the defining feature of a subject is that they can act. 
 I represent that below by allowing subjects to substitute into sentences, a property that I will use 
@@
 the Formula of Universal, which reads ``act only according to that maxim by which you can at the same 
-time will that it should become a universal law'' \citep{groundwork}. In order to faithfully formalize
+time will that it should become a universal law'' \citep[34]{groundwork}. In order to faithfully formalize
 the FUL, I must make precise what it means to will a maxim and what kinds of maxims can become universal laws. 
@@
 \begin{example}[False Promising]\label{falsepromise}
-  The false promising example maxim reads, ``When I am strapped for cash, I wil falsely promise to repay a loan 
+  The false promising example maxim reads, ``When I am strapped for cash, I will falsely promise to repay a loan 
 to get some easy cash.''
@@
 The central unit of evaluation for Kantian ethics is a ``maxim,'' which Kant defines as ``the subjective 
-principle of willing,'' or the principle that the agent understands themselves as acting on \citep{groundwork}. 
+principle of willing,'' or the principle that the agent understands themselves as acting on \citep[16, footnote 1]{groundwork}. 
 Modern Kantians differ in their interpretations of this definition. I adopt O'Neill's view, derived from 
@@
 She also includes a purpose, end, or goal in the maxim because human activity is guided by a rational will
-and is thus inherently purposive \citep[4:428]{groundwork}. A rational will does not act randomly (else it would not be rational), 
+and is thus inherently purposive \citep[40]{groundwork}. A rational will does not act randomly (else it would not be rational), 
 but instead in the pursuit of ends which it deems valuable. The inclusion a maxim's end is essential 
@@
 under which maxims are arbitrarily specified to pass the FUL  \citep[217]{whatisamaxim}. \footnote{Kitcher
-cites \citet{kantsethicalthought} as offering an example of a false positive due to this objection \cite{kitcher}.} For example, the maxim ``When my name is Jane Doe
+cites \citet{kantsethicalthought} as offering an example of a false positive due to this objection.} For example, the maxim ``When my name is Jane Doe
 and I am wearing a purple shirt and it is Tuesday morning, I will murder my boss so I can take their job,'' 
@@
 human being formulate the maxim or that future work develop heuristics to classify circumstances as morally 
-relevant. I discuss this challenge and potential solutions in greater detail in Section \ref{commonsense}.
+relevant. I discuss this challenge and potential solutions in greater detail in Section \ref{AIethics}.
 
@@
 \noindent At all worlds $w$, if the circumstances hold at that world, agent $s$ performs act $A$.
-
 \end{definition}
@@
 Recall that the Formula of Universal Law is to “act only in accordance with that maxim through which 
-you can at the same time will that it become a universal law” \citep{groundwork}. To determine if a 
+you can at the same time will that it become a universal law” \citep[34]{groundwork}. To determine if a 
 maxim can be willed as a universal law, we use the “universalizability test,” which requires 
@@
 universalizability test because, in the universalized world, everyone falsely promises to repay
-loans so lenders no longer believe promises to repay loans. The practice of loans would die out, so 
+loans so lenders no longer believe promises to repay loans. The practice of giving loans would die out, so 
 making a false promise to repay a loan would be impossible.
@@
 willing the end of sleeping, she is implicitly willing that she is alive. If all mothers kill all 
-loud children, then she cannot be secure in the possession of her life, because her own mother would 
+loud children, then she cannot be secure in the possession of her life, because her own mother may 
 have killed her as an infant. Her willing this maxim thwarts the end that she sought to secure.
@@
 from it, and is thus making an exception of themselves. The test formalizes the kinds of objections 
-that the question ``What if everyone did that?'' seeks to draw out.
+that the question ``What if everyone did that?'' seeks to draw out.\footnote{This argument for the practical
+contradiction interpretation is due to \citet{KorsgaardFUL}.}
 
@@
 would not be achieved \citep{lewiscausality}.\footnote{Thank you to Jeremy Zucker for helping me 
-think about causality in this way.}  Note that nothing else changes about this
-counterfactual world—the circumstances are identical and we neither added additional theorems nor 
-specified the model any further. This represents Lewis's idea of ``comparative similarity,''  where 
-a counterfactual is true if it holds at the most similar world \citep{lewiscounterfactuals}. 
-In our case, this is just the world where everything is the same except the maxim is not acted on.
+think about causality in this way.}
 Combining these ideas, this definition of effective states that a maxim is effective if the 
@@
 if all people at that world will the maxim.%
-}\isanewline
-%
+}%
 \begin{isamarkuptext}%
@@
 obligatory for a specific subject.\footnote{The full proof for this result is the Obligation Universalizes
-Across People Test in Section \ref{tests}.}
+Across People Test in Section \ref{testing}.}
 
@@
 }\isanewline
-\isanewline
 \isacommand{abbreviation}\isamarkupfalse%
@@
 notion of contradictory obligations. Many deontic logics, including DDL, allow contradictory
-obligations. As I will explain in Section \nameref{testing}, Kantian ethics never prescribes contradictory
+obligations. As I will explain in Section \ref{testing}, Kantian ethics never prescribes contradictory
 obligations, so I will add this as an axiom.%
@@
 }\isanewline
-\isanewline
 \isacommand{axiomatization}\isamarkupfalse%
@@
 by the practical contradiction interpretation, states that a maxim is prohibited if it is ineffective
-when universalized. A first, ultimately unsuccessful, attempt to formalize the FUL simply translates this into Isabelle's syntax
+when universalized. A first, unsuccessful attempt to formalize the FUL simply translates this into Isabelle's syntax
 using the abbreviations above. While this attempt will not be consistent, I will use Isabelle's automatic
@@
 insight about maxims in the process. This section presents my final formalization of the FUL and the 
-philosophical insight produced while creating it, which, as I argue in Section Computational Ethics???,
+philosophical insight produced while creating it, which, as I argue in Section \ref{computationalethics},
 demonstrates the power of computational tools in aiding philosophical progress.%
@@
 This axiom roughly states that an obligation can't contradict its context. Knowing that \texttt{FUL0}
-contradicts this particular maxim offers insight into what the problem is. If the goal or action
+contradicts this particular axiom offers insight into what the problem is. If the goal or action
 or a maxim are equivalent to its circumstance, then prohibiting it is contradictory. If the maxim has already been 
 acted on or the goal has already been achieved, then the agent cannot undo their action or the achivement 
-of the goal. Moreover, in many models, it is possible to construct a maxim where the circumstances, goal, 
-and act (once a subject acts on it) are all that same term and to show that this maxim is prohibited,
-resulting in a contradiction.
+of the goal.
 
@@
 
-For example, the maxim ``When I eat breakfast, I will eat breakfast to eat breakfast'' is not well-formed 
+For example, the maxim ``When I eat breakfast, I will eat breakfast to eat breakfast'' is badly-formed
 because the circumstance ``when I eat breakfast'' contains the act and goal. Well-formedness is not 
@@
 whether to act on a potential principle of action, but no agent would need to ask
-``When I am eating breakfast, should I eat breakfast in order to eat breakfast?" It is neither contradictory
-nor prohibited, and it is the wrong kind of principle to be evaluating. It is not a
-well-formed maxim, so the categorical imperative cannot apply to it.
+``When I am eating breakfast, should I eat breakfast in order to eat breakfast?" It is the wrong kind of 
+principle to be evaluating. It is not a well-formed maxim, so the categorical imperative cannot apply to it.
 
@@
 properties and implications of well-formed maxims and the power of computational ethics further in 
-Section Computational Ethics.
-
-Now that I have a consistent version of the FUL, I can complete my implementation by adding it as an axiom.%
+Section \ref{computationalethics}.
+
+I complete my implementation by adding the consistent version of the FUL as an axiom.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 consistents of necessary logical background, first formalized in DDL and then implemented in Isabelle.
-The code snippets in this chapter are a subset of the over 100 lines of Isabelle/HOL code necessary to
-complete this implementation. In Section \ref{testing} and Chapter Applications, I demonstrate how this
+The code snippets in this chapter are a subset of over 100 lines of Isabelle/HOL code necessary to
+complete this implementation. In Section \ref{testing} and Chapter \ref{applications}, I demonstrate how this
 implementation can be tested and used to make moral judgements.%
@@
 on top of which I build other implementations. DDL can express obligation, but has no knowledge of any 
-specific moral rules (like the categorical imperative) and is thus a 
-control group. Second, I consider Moshe Kroy's 1976 formalization of the FUL and the second formulation
+specific moral rules (like the categorical imperative). Second, I consider Moshe Kroy's 1976 formalization 
+of the FUL and the second formulation
 of the categorical imperative \citep{kroy}. His formalization is based on Hintikka's deontic logic, which is a different,
@@
 \includegraphics[scale=0.6]{goalstable.png}
-\caption{Table showing which tests each implementation passes. The naive interpretation is raw DDL, 
-Kroy is based on Moshe Kroy's formalization of the FUL, and the custom formalization is my novel implementation.} \label{table}
+\caption{Table showing which tests each implementation passes. ``Naive'' indicates raw DDL, 
+``Kroy'' is my implementation of Moshe Kroy's formalization of the FUL, and ``Custom'' is my novel implementation.} \label{table}
 \end{figure}
@@
 \ right{\isacharunderscore}if{\isacharunderscore}right{\isacharunderscore}for{\isacharunderscore}someone{\isacharcolon}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}w{\isachardot}\ {\isasymforall}c{\isacharcolon}{\isacharcolon}t{\isachardot}\ {\isasymforall}g{\isacharcolon}{\isacharcolon}t{\isachardot}\ {\isasymexists}s{\isacharcolon}{\isacharcolon}s{\isachardot}\ O{\isacharbraceleft}W\ {\isacharparenleft}c{\isacharcomma}\ M{\isacharcomma}\ g{\isacharparenright}\ s\ {\isacharbar}\ c{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ \ O{\isacharbraceleft}W\ {\isacharparenleft}c{\isacharcomma}\ M{\isacharcomma}\ g{\isacharparenright}\ p\ {\isacharbar}\ c{\isacharbraceright}\ w{\isacharparenright}\ {\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}w{\isachardot}\ {\isasymforall}c{\isacharcolon}{\isacharcolon}t{\isachardot}\ {\isasymforall}g{\isacharcolon}{\isacharcolon}t{\isachardot}\ {\isasymforall}a{\isachardot}\ {\isasymexists}s{\isacharcolon}{\isacharcolon}s{\isachardot}\ O{\isacharbraceleft}W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ {\isacharbar}\ c{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ \ O{\isacharbraceleft}W\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ p\ {\isacharbar}\ c{\isacharbraceright}\ w{\isacharparenright}\ {\isachardoublequoteclose}\isanewline
 %
@@
 prohibition. In a system with contradictory obligations, this property fails because there is some
-A that is obligated but also prohibited and therefore not permisible. Formalizing this property below shows 
-that this follows from contradictory obligations.
+maxim that is obligated but also prohibited and therefore not permisible. The simple proof below 
+shows that this property is incompatible with contradictory obligations.
 
@@
 \isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}{\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymand}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymnot}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}A{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ {\isachardoublequoteopen}{\isasymforall}w{\isachardot}\ {\isasymexists}A{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymand}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}w{\isacharparenright}{\isacharparenright}\ {\isasymequiv}\ {\isacharparenleft}{\isasymexists}B{\isachardot}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}B{\isacharbraceright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymnot}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}B{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
 %
@@
 %
-\isamarkupcmt{\texttt{simp} is the simplification tactic, which unfolds definitions to complete a proof. The 
-left-hand side states that $A$ is both obligated and prohibited, and is equivalent to the right-hand side, 
-which states that $A$ is obligated but not permissible.%
+\isamarkupcmt{This lemma shows that if there is some maxim $A$ such that $A$ and $\neg A$ are both obligatory (which
+is the formal statement of contradictory obligations), then obligation does not always permissibility.%
+}\isanewline
+%
+\isamarkupcmt{\texttt{simp} is the simplification tactic, which unfolds definitions to complete a proof.%
 }%
@@
 represent metalogical implication. With the assumption, the lemma above reads, ``If the distributive
-property holds in this logic, then obligations cannot contradict."%
+property holds in this logic, then obligations cannot contradict.''%
 }%
@@
 and Kroy's formalization, but holds for my formalization. Showing that this property holds
-for my formalization required significant logical background and the full code is presented in Appendix \ref{weirdtests}.%
+for my formalization required significant logical work and the full code is presented in Appendix \ref{weirdtests}.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 does. Because my implementation includes the notion of a maxim, it is able to perform sophisticated 
-reasoning as demonstrated in Sections \nameref{joking} and \nameref{murderer}. Staying faithful to the philosophical 
+reasoning as demonstrated in Sections \ref{joking} and \ref{murderer}. Staying faithful to the philosophical 
 literature enables my system to make more reliable judgements.
@@
 practical contradiction interpretation of the FUL, which is the canonical interpretation of the 
-FUL \citep{ebelsduggan, KorsgaardFUL}. I run this test in Chapter Applications, where I
+FUL \citep{ebelsduggan, KorsgaardFUL}. I run this test in Chapter \ref{applications}, where I
 use my system to reason about two ethical dilemmas, one which involves conventional acts and the other which
@@
 %:%67=22%:%
-%:%68=23%:%
-%:%77=25%:%
+%:%76=24%:%
+%:%88=26%:%
 %:%89=27%:%
@@
 %:%92=30%:%
-%:%93=31%:%
-%:%95=33%:%
-%:%96=33%:%
-%:%97=33%:%
+%:%94=32%:%
+%:%95=32%:%
+%:%96=32%:%
+%:%99=34%:%
 %:%100=35%:%
@@
 %:%114=49%:%
-%:%115=50%:%
-%:%117=52%:%
-%:%118=52%:%
+%:%116=51%:%
+%:%117=51%:%
+%:%119=52%:%
 %:%120=53%:%
@@
 %:%126=59%:%
-%:%127=60%:%
-%:%135=62%:%
+%:%134=61%:%
+%:%146=63%:%
 %:%147=64%:%
@@
 %:%172=89%:%
-%:%173=90%:%
-%:%175=93%:%
-%:%176=93%:%
+%:%174=92%:%
+%:%175=92%:%
+%:%177=93%:%
 %:%178=94%:%
@@
 %:%184=100%:%
-%:%185=101%:%
+%:%187=102%:%
 %:%188=103%:%
@@
 %:%228=143%:%
-%:%229=144%:%
 %:%230=145%:%
-%:%232=147%:%
-%:%233=147%:%
-%:%234=148%:%
+%:%231=145%:%
+%:%232=146%:%
+%:%234=147%:%
+%:%235=148%:%
 %:%236=149%:%
 %:%237=150%:%
-%:%238=151%:%
-%:%239=152%:%
-%:%247=154%:%
+%:%245=152%:%
+%:%257=154%:%
+%:%258=155%:%
 %:%259=156%:%
@@
 %:%308=205%:%
-%:%309=206%:%
-%:%311=209%:%
+%:%310=208%:%
+%:%311=208%:%
 %:%312=209%:%
-%:%313=210%:%
+%:%314=210%:%
 %:%315=211%:%
-%:%316=212%:%
+%:%318=213%:%
 %:%319=214%:%
@@
 %:%335=230%:%
-%:%336=231%:%
-%:%337=232%:%
+%:%337=233%:%
 %:%338=233%:%
 %:%339=234%:%
-%:%340=235%:%
-%:%342=238%:%
-%:%343=238%:%
-%:%344=239%:%
-%:%346=240%:%
-%:%347=241%:%
-%:%348=241%:%
-%:%351=247%:%
-%:%352=248%:%
-%:%353=249%:%
-%:%354=250%:%
-%:%355=251%:%
-%:%356=252%:%
-%:%357=253%:%
-%:%358=254%:%
-%:%359=255%:%
-%:%360=256%:%
-%:%361=257%:%
-%:%363=259%:%
-%:%364=259%:%
-%:%365=260%:%
-%:%367=261%:%
-%:%370=263%:%
-%:%371=264%:%
-%:%372=265%:%
-%:%373=266%:%
-%:%374=267%:%
-%:%375=268%:%
-%:%376=269%:%
-%:%377=270%:%
-%:%378=271%:%
-%:%379=272%:%
-%:%380=273%:%
-%:%381=274%:%
-%:%382=275%:%
-%:%383=276%:%
-%:%384=277%:%
-%:%385=278%:%
-%:%386=279%:%
-%:%387=280%:%
-%:%388=281%:%
-%:%389=282%:%
-%:%390=283%:%
-%:%391=284%:%
-%:%392=285%:%
-%:%393=286%:%
-%:%394=287%:%
-%:%395=288%:%
-%:%396=289%:%
-%:%397=290%:%
-%:%398=291%:%
-%:%399=292%:%
-%:%400=293%:%
-%:%401=294%:%
-%:%402=295%:%
-%:%404=297%:%
-%:%405=297%:%
-%:%406=298%:%
-%:%408=299%:%
-%:%409=300%:%
-%:%410=300%:%
-%:%411=301%:%
-%:%412=302%:%
-%:%413=302%:%
-%:%414=303%:%
-%:%416=304%:%
-%:%417=305%:%
-%:%420=307%:%
-%:%421=308%:%
-%:%422=309%:%
-%:%423=310%:%
-%:%425=312%:%
-%:%426=312%:%
-%:%427=313%:%
-%:%429=314%:%
-%:%430=315%:%
-%:%431=315%:%
-%:%432=316%:%
-%:%433=317%:%
-%:%434=317%:%
-%:%436=318%:%
-%:%437=319%:%
-%:%438=320%:%
-%:%446=322%:%
-%:%458=324%:%
-%:%459=325%:%
-%:%460=326%:%
-%:%461=327%:%
-%:%462=328%:%
-%:%463=329%:%
-%:%464=330%:%
-%:%465=331%:%
-%:%467=334%:%
-%:%468=334%:%
-%:%470=335%:%
-%:%471=336%:%
-%:%472=337%:%
-%:%473=338%:%
-%:%476=340%:%
-%:%477=341%:%
-%:%479=343%:%
-%:%480=343%:%
-%:%482=343%:%
-%:%486=343%:%
-%:%487=343%:%
-%:%488=344%:%
-%:%489=344%:%
-%:%490=344%:%
-%:%499=346%:%
-%:%500=347%:%
-%:%501=348%:%
-%:%502=349%:%
-%:%503=350%:%
-%:%504=351%:%
-%:%505=352%:%
-%:%506=353%:%
-%:%507=354%:%
-%:%508=355%:%
-%:%509=356%:%
-%:%510=357%:%
-%:%511=358%:%
-%:%512=359%:%
-%:%513=360%:%
-%:%514=361%:%
-%:%515=362%:%
-%:%516=363%:%
-%:%517=364%:%
-%:%518=365%:%
-%:%519=366%:%
-%:%520=367%:%
-%:%521=368%:%
-%:%522=369%:%
-%:%523=370%:%
-%:%525=372%:%
-%:%526=372%:%
-%:%527=373%:%
-%:%529=374%:%
-%:%530=375%:%
-%:%533=377%:%
-%:%535=379%:%
-%:%536=379%:%
-%:%537=380%:%
-%:%539=381%:%
-%:%540=382%:%
-%:%541=382%:%
-%:%542=383%:%
-%:%543=384%:%
-%:%544=384%:%
-%:%545=385%:%
-%:%546=385%:%
-%:%548=385%:%
-%:%552=385%:%
-%:%553=385%:%
-%:%555=386%:%
-%:%556=387%:%
-%:%557=388%:%
-%:%558=389%:%
-%:%559=390%:%
-%:%560=391%:%
-%:%561=392%:%
-%:%571=394%:%
-%:%572=395%:%
-%:%573=396%:%
-%:%574=397%:%
-%:%575=398%:%
-%:%576=399%:%
-%:%577=400%:%
-%:%578=401%:%
-%:%579=402%:%
-%:%580=403%:%
-%:%581=404%:%
-%:%582=405%:%
-%:%583=406%:%
-%:%584=407%:%
-%:%585=408%:%
-%:%586=409%:%
-%:%587=410%:%
-%:%588=411%:%
-%:%589=412%:%
-%:%590=413%:%
-%:%591=414%:%
-%:%593=416%:%
-%:%594=416%:%
-%:%596=418%:%
-%:%597=419%:%
-%:%598=420%:%
-%:%599=421%:%
-%:%600=422%:%
-%:%609=424%:%
-%:%621=426%:%
-%:%622=427%:%
-%:%623=428%:%
-%:%624=429%:%
-%:%625=430%:%
-%:%626=431%:%
-%:%627=432%:%
-%:%628=433%:%
-%:%629=434%:%
-%:%630=435%:%
-%:%631=436%:%
-%:%632=437%:%
-%:%633=438%:%
-%:%634=439%:%
-%:%635=440%:%
-%:%636=441%:%
-%:%637=442%:%
-%:%638=443%:%
-%:%639=444%:%
-%:%640=445%:%
-%:%641=446%:%
-%:%642=447%:%
-%:%643=448%:%
-%:%644=449%:%
-%:%645=450%:%
-%:%648=454%:%
-%:%649=455%:%
-%:%650=456%:%
-%:%651=457%:%
-%:%652=458%:%
-%:%653=459%:%
-%:%656=461%:%
-%:%657=462%:%
-%:%658=463%:%
-%:%659=464%:%
-%:%660=465%:%
-%:%661=466%:%
-%:%662=467%:%
-%:%663=468%:%
-%:%664=469%:%
-%:%665=470%:%
-%:%669=472%:%
-%:%670=473%:%
-%:%671=474%:%
-%:%672=475%:%
-%:%673=476%:%
-%:%674=477%:%
-%:%675=478%:%
-%:%676=479%:%
-%:%677=480%:%
-%:%678=481%:%
-%:%679=482%:%
-%:%680=483%:%
-%:%681=484%:%
-%:%682=485%:%
-%:%684=487%:%
-%:%685=487%:%
-%:%686=488%:%
-%:%689=489%:%
-%:%693=489%:%
-%:%694=489%:%
-%:%696=490%:%
-%:%697=491%:%
-%:%698=492%:%
-%:%699=492%:%
-%:%701=493%:%
-%:%702=494%:%
-%:%703=495%:%
-%:%704=496%:%
-%:%710=496%:%
-%:%713=497%:%
-%:%714=498%:%
-%:%715=498%:%
-%:%716=499%:%
-%:%719=500%:%
-%:%723=500%:%
-%:%724=500%:%
-%:%726=501%:%
-%:%727=502%:%
-%:%737=504%:%
-%:%738=505%:%
-%:%739=506%:%
-%:%740=507%:%
-%:%741=508%:%
-%:%742=509%:%
-%:%743=510%:%
-%:%744=511%:%
-%:%745=512%:%
-%:%746=513%:%
-%:%747=514%:%
-%:%748=515%:%
-%:%749=516%:%
-%:%750=517%:%
-%:%751=518%:%
-%:%752=519%:%
-%:%753=520%:%
-%:%754=521%:%
-%:%755=522%:%
-%:%756=523%:%
-%:%757=524%:%
-%:%759=526%:%
-%:%760=526%:%
-%:%761=527%:%
-%:%764=528%:%
-%:%768=528%:%
-%:%769=528%:%
-%:%770=528%:%
-%:%772=529%:%
-%:%778=529%:%
-%:%781=530%:%
-%:%782=531%:%
-%:%783=531%:%
-%:%784=532%:%
-%:%785=533%:%
-%:%788=534%:%
-%:%792=534%:%
-%:%793=534%:%
-%:%794=534%:%
-%:%796=535%:%
-%:%797=536%:%
-%:%798=537%:%
-%:%808=539%:%
-%:%809=540%:%
-%:%810=541%:%
-%:%811=542%:%
-%:%812=543%:%
-%:%813=544%:%
-%:%814=545%:%
-%:%815=546%:%
-%:%817=549%:%
-%:%818=549%:%
-%:%821=550%:%
-%:%825=550%:%
-%:%826=550%:%
-%:%828=551%:%
-%:%829=552%:%
-%:%830=553%:%
-%:%840=555%:%
-%:%841=556%:%
-%:%842=557%:%
-%:%843=558%:%
-%:%844=559%:%
-%:%845=560%:%
-%:%846=561%:%
-%:%848=563%:%
-%:%849=563%:%
-%:%850=564%:%
-%:%851=565%:%
-%:%854=566%:%
-%:%858=566%:%
-%:%859=566%:%
-%:%860=566%:%
-%:%862=567%:%
-%:%863=568%:%
-%:%864=569%:%
-%:%874=571%:%
-%:%875=572%:%
-%:%877=574%:%
-%:%878=574%:%
-%:%879=575%:%
-%:%880=576%:%
-%:%883=577%:%
-%:%887=577%:%
-%:%888=577%:%
-%:%889=577%:%
-%:%891=578%:%
-%:%901=580%:%
-%:%902=581%:%
-%:%903=582%:%
-%:%904=583%:%
-%:%905=584%:%
-%:%906=585%:%
-%:%907=586%:%
-%:%908=587%:%
-%:%909=588%:%
-%:%910=589%:%
-%:%911=590%:%
-%:%912=591%:%
-%:%913=592%:%
-%:%914=593%:%
-%:%918=597%:%
-%:%919=598%:%
-%:%920=599%:%
-%:%921=600%:%
-%:%922=601%:%
-%:%923=602%:%
-%:%924=603%:%
-%:%925=604%:%
-%:%929=607%:%
-%:%930=608%:%
-%:%931=609%:%
-%:%932=610%:%
-%:%933=611%:%
-%:%934=612%:%
-%:%935=613%:%
-%:%936=614%:%
-%:%937=615%:%
-%:%938=616%:%
-%:%939=617%:%
-%:%940=618%:%
-%:%941=619%:%
-%:%942=620%:%
-%:%943=621%:%
-%:%944=622%:%
-%:%945=623%:%
-%:%946=624%:%
-%:%947=625%:%
+%:%341=235%:%
+%:%342=236%:%
+%:%345=240%:%
+%:%346=241%:%
+%:%347=242%:%
+%:%348=243%:%
+%:%349=244%:%
+%:%350=245%:%
+%:%351=246%:%
+%:%352=247%:%
+%:%353=248%:%
+%:%354=249%:%
+%:%355=250%:%
+%:%357=252%:%
+%:%358=252%:%
+%:%359=253%:%
+%:%361=254%:%
+%:%364=256%:%
+%:%365=257%:%
+%:%366=258%:%
+%:%367=259%:%
+%:%368=260%:%
+%:%369=261%:%
+%:%370=262%:%
+%:%371=263%:%
+%:%372=264%:%
+%:%373=265%:%
+%:%374=266%:%
+%:%375=267%:%
+%:%376=268%:%
+%:%377=269%:%
+%:%378=270%:%
+%:%379=271%:%
+%:%380=272%:%
+%:%381=273%:%
+%:%382=274%:%
+%:%383=275%:%
+%:%384=276%:%
+%:%385=277%:%
+%:%386=278%:%
+%:%387=279%:%
+%:%388=280%:%
+%:%389=281%:%
+%:%390=282%:%
+%:%391=283%:%
+%:%392=284%:%
+%:%393=285%:%
+%:%394=286%:%
+%:%395=287%:%
+%:%396=288%:%
+%:%398=290%:%
+%:%399=290%:%
+%:%400=291%:%
+%:%402=292%:%
+%:%403=293%:%
+%:%404=293%:%
+%:%405=294%:%
+%:%406=294%:%
+%:%407=295%:%
+%:%409=296%:%
+%:%410=297%:%
+%:%413=298%:%
+%:%414=299%:%
+%:%415=300%:%
+%:%416=301%:%
+%:%418=303%:%
+%:%419=303%:%
+%:%420=304%:%
+%:%422=305%:%
+%:%423=306%:%
+%:%424=306%:%
+%:%425=307%:%
+%:%426=307%:%
+%:%428=308%:%
+%:%429=309%:%
+%:%430=310%:%
+%:%438=312%:%
+%:%450=314%:%
+%:%451=315%:%
+%:%452=316%:%
+%:%453=317%:%
+%:%454=318%:%
+%:%455=319%:%
+%:%456=320%:%
+%:%457=321%:%
+%:%459=324%:%
+%:%460=324%:%
+%:%462=325%:%
+%:%463=326%:%
+%:%464=327%:%
+%:%465=328%:%
+%:%468=330%:%
+%:%469=331%:%
+%:%471=333%:%
+%:%472=333%:%
+%:%474=333%:%
+%:%478=333%:%
+%:%479=333%:%
+%:%480=334%:%
+%:%481=334%:%
+%:%482=334%:%
+%:%491=336%:%
+%:%492=337%:%
+%:%493=338%:%
+%:%494=339%:%
+%:%495=340%:%
+%:%496=341%:%
+%:%497=342%:%
+%:%498=343%:%
+%:%499=344%:%
+%:%500=345%:%
+%:%501=346%:%
+%:%502=347%:%
+%:%503=348%:%
+%:%504=349%:%
+%:%505=350%:%
+%:%506=351%:%
+%:%507=352%:%
+%:%508=353%:%
+%:%509=354%:%
+%:%510=355%:%
+%:%511=356%:%
+%:%512=357%:%
+%:%513=358%:%
+%:%515=360%:%
+%:%516=360%:%
+%:%517=361%:%
+%:%519=362%:%
+%:%520=363%:%
+%:%523=365%:%
+%:%525=367%:%
+%:%526=367%:%
+%:%527=368%:%
+%:%529=369%:%
+%:%530=370%:%
+%:%531=370%:%
+%:%532=371%:%
+%:%533=372%:%
+%:%534=372%:%
+%:%535=373%:%
+%:%536=373%:%
+%:%538=373%:%
+%:%542=373%:%
+%:%543=373%:%
+%:%545=374%:%
+%:%546=375%:%
+%:%547=376%:%
+%:%548=377%:%
+%:%549=378%:%
+%:%550=379%:%
+%:%551=380%:%
+%:%561=382%:%
+%:%562=383%:%
+%:%563=384%:%
+%:%564=385%:%
+%:%565=386%:%
+%:%566=387%:%
+%:%567=388%:%
+%:%568=389%:%
+%:%569=390%:%
+%:%570=391%:%
+%:%571=392%:%
+%:%572=393%:%
+%:%573=394%:%
+%:%574=395%:%
+%:%575=396%:%
+%:%576=397%:%
+%:%577=398%:%
+%:%578=399%:%
+%:%579=400%:%
+%:%580=401%:%
+%:%582=403%:%
+%:%583=403%:%
+%:%585=405%:%
+%:%586=406%:%
+%:%587=407%:%
+%:%588=408%:%
+%:%589=409%:%
+%:%598=411%:%
+%:%610=413%:%
+%:%611=414%:%
+%:%612=415%:%
+%:%613=416%:%
+%:%614=417%:%
+%:%615=418%:%
+%:%616=419%:%
+%:%617=420%:%
+%:%618=421%:%
+%:%619=422%:%
+%:%620=423%:%
+%:%621=424%:%
+%:%622=425%:%
+%:%623=426%:%
+%:%624=427%:%
+%:%625=428%:%
+%:%626=429%:%
+%:%627=430%:%
+%:%628=431%:%
+%:%629=432%:%
+%:%630=433%:%
+%:%631=434%:%
+%:%632=435%:%
+%:%633=436%:%
+%:%634=437%:%
+%:%637=441%:%
+%:%638=442%:%
+%:%639=443%:%
+%:%640=444%:%
+%:%641=445%:%
+%:%642=446%:%
+%:%645=448%:%
+%:%646=449%:%
+%:%647=450%:%
+%:%648=451%:%
+%:%649=452%:%
+%:%650=453%:%
+%:%651=454%:%
+%:%652=455%:%
+%:%653=456%:%
+%:%654=457%:%
+%:%658=459%:%
+%:%659=460%:%
+%:%660=461%:%
+%:%661=462%:%
+%:%662=463%:%
+%:%663=464%:%
+%:%664=465%:%
+%:%665=466%:%
+%:%666=467%:%
+%:%667=468%:%
+%:%668=469%:%
+%:%669=470%:%
+%:%670=471%:%
+%:%671=472%:%
+%:%673=474%:%
+%:%674=474%:%
+%:%675=475%:%
+%:%678=476%:%
+%:%682=476%:%
+%:%683=476%:%
+%:%685=477%:%
+%:%686=478%:%
+%:%687=479%:%
+%:%688=479%:%
+%:%690=480%:%
+%:%691=481%:%
+%:%692=482%:%
+%:%693=483%:%
+%:%699=483%:%
+%:%702=484%:%
+%:%703=485%:%
+%:%704=485%:%
+%:%705=486%:%
+%:%708=487%:%
+%:%712=487%:%
+%:%713=487%:%
+%:%715=488%:%
+%:%716=489%:%
+%:%726=491%:%
+%:%727=492%:%
+%:%728=493%:%
+%:%729=494%:%
+%:%730=495%:%
+%:%731=496%:%
+%:%732=497%:%
+%:%733=498%:%
+%:%734=499%:%
+%:%735=500%:%
+%:%736=501%:%
+%:%737=502%:%
+%:%738=503%:%
+%:%739=504%:%
+%:%740=505%:%
+%:%741=506%:%
+%:%742=507%:%
+%:%743=508%:%
+%:%744=509%:%
+%:%745=510%:%
+%:%746=511%:%
+%:%748=513%:%
+%:%749=513%:%
+%:%750=514%:%
+%:%753=515%:%
+%:%757=515%:%
+%:%758=515%:%
+%:%759=515%:%
+%:%761=516%:%
+%:%767=516%:%
+%:%770=517%:%
+%:%771=518%:%
+%:%772=518%:%
+%:%773=519%:%
+%:%774=520%:%
+%:%777=521%:%
+%:%781=521%:%
+%:%782=521%:%
+%:%783=521%:%
+%:%785=522%:%
+%:%786=523%:%
+%:%787=524%:%
+%:%797=526%:%
+%:%798=527%:%
+%:%799=528%:%
+%:%800=529%:%
+%:%801=530%:%
+%:%802=531%:%
+%:%803=532%:%
+%:%804=533%:%
+%:%806=536%:%
+%:%807=536%:%
+%:%810=537%:%
+%:%814=537%:%
+%:%815=537%:%
+%:%817=538%:%
+%:%818=539%:%
+%:%819=539%:%
+%:%821=540%:%
+%:%831=542%:%
+%:%832=543%:%
+%:%833=544%:%
+%:%834=545%:%
+%:%835=546%:%
+%:%836=547%:%
+%:%837=548%:%
+%:%839=550%:%
+%:%840=550%:%
+%:%841=551%:%
+%:%842=552%:%
+%:%845=553%:%
+%:%849=553%:%
+%:%850=553%:%
+%:%851=553%:%
+%:%853=554%:%
+%:%854=555%:%
+%:%855=556%:%
+%:%865=558%:%
+%:%866=559%:%
+%:%868=561%:%
+%:%869=561%:%
+%:%870=562%:%
+%:%871=563%:%
+%:%874=564%:%
+%:%878=564%:%
+%:%879=564%:%
+%:%880=564%:%
+%:%882=565%:%
+%:%892=567%:%
+%:%893=568%:%
+%:%894=569%:%
+%:%895=570%:%
+%:%896=571%:%
+%:%897=572%:%
+%:%898=573%:%
+%:%899=574%:%
+%:%900=575%:%
+%:%901=576%:%
+%:%902=577%:%
+%:%903=578%:%
+%:%904=579%:%
+%:%905=580%:%
+%:%909=584%:%
+%:%910=585%:%
+%:%911=586%:%
+%:%912=587%:%
+%:%913=588%:%
+%:%914=589%:%
+%:%915=590%:%
+%:%916=591%:%
+%:%920=594%:%
+%:%921=595%:%
+%:%922=596%:%
+%:%923=597%:%
+%:%924=598%:%
+%:%925=599%:%
+%:%926=600%:%
+%:%927=601%:%
+%:%928=602%:%
+%:%929=603%:%
+%:%930=604%:%
+%:%931=605%:%
+%:%932=606%:%
+%:%933=607%:%
+%:%934=608%:%
+%:%935=609%:%
+%:%936=610%:%
+%:%937=611%:%
+%:%938=612%:%

### 2022-03-08 paper/output/document/thesis_4_applications.tex
ugh

@@
 \begin{isamarkuptext}%
-In this chapter, I demonstrate that my system can produce correct judgements on challenging moral 
-dilemmas that naive ethical reasoning cannot satisfactorily handle. My system can reproduce complex
-ethical judgements because it is faithful to philosophical literature.
+In this chapter, I demonstrate that my system can produce correct judgements for challenging moral 
+dilemmas that naive ethical reasoning cannot satisfactorily handle. Because my system is faithful to
+philosophical literature, it can reproduce complex ethical judgements presented by philosophers as 
+solutions to controversial open questions in ethics.
 These dilemmas serve as examples of how my system could be used
@@
 than those presented in Chapter \ref{details}.
+
 Many of the tests in Section \ref{testing} perform metaethical reasoning, which analyzes properties
 of morality itself and involves questions about the nature of ethical truth. In this chapter, I perform
-``applied ethical reasoning," which is the use of ethics to resolve dilemmas and make judgements about 
+``applied ethical reasoning,'' which is the use of ethics to resolve dilemmas and make judgements about 
 what an agent should or should not do. This is the kind of reasoning necessary for an AI agent using my system to
@@
 
-In this chapter, I attempt to tackle this challenge by
-endowing my system with this kind of common sense in the specific case of lying. In order for my 
-system to perform applied ethical reasoning, it will need common sense facts and definitions, like
-those I present in this chapter. My system contributes the ability to reason
-using the Formula of Universal Law, but this reasoning must be applied to objects that are defined
-using common sense. In this chapter, I describe such common sense for the specific example
-of lying.
+In this chapter, I tackle this challenge by
+endowing my system with this kind of common sense in the specific case of lying. My system needs common 
+sense facts and definitions because, while it has the ability to reason
+using the Formula of Universal Law, this reasoning must be applied to objects that are defined
+using common sense.
 

### 2022-03-08 paper/output/document/thesis_4_applications.tex
my back hurts

@@
 system, and virtually all prior attempts in machine ethics face similar challenges.\footnote{See Section
-Related Work for a survey of the common sense required in prior work.} Many prior attempts
+\ref{relatedwork} for a survey of the common sense required in prior work.} Many prior attempts
 sidestep this question, whereas I contribute an prototype implementation of one kind of common sense reasoning.
@@
 The moral status of lying is hotly debated in the Kantian literature. I focus on two dilemmas
-presented in Korsgaard's ``Right to Lie," which 
-examines how strict Kant's prohibition on lying is \citep{KorsgaardRTL}. She begins with the case of 
+presented in Korsgaard's ``Right to Lie,'' which 
+examines Kant's prohibition on lying \citep{KorsgaardRTL}. She begins with the case of 
 lying and joking. Many of Kant's critics argue that his prohibition on lies includes lies told in 
@@
 context because most of the time people in that context say what they really think'' \citep[4]{KorsgaardRTL}. 
-In order to formalize this argument, I first need to define the relevant terms and assumptions, which include
-lying and Korsgaard's argument about the basis of trust.
+In order to formalize this argument, I first need to define lying and formalize Korsgaard's argument 
+about the basis of trust.
 
 I define lying and trust in terms of belief. As in Section \ref{details}, I choose thin, or minimal,
-definitions of terms like belief to reduce the potential for controversy in my system's factual background.%
+definitions to reduce the potential for controversy in my system's factual background.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 With the above logical background, I automate Korsgaard's argument that maxims that involve
-lying are prohibited. First, I define the subject and maxim at hand.%
+lying are prohibited. First, I define the relevant subject and maxim.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 The lemma above demonstrates that my system finds that lying is prohibited with a thin definition
-of lying and relatively uncontroversial facts about the world. The logical background needed is the fact that lying
-requires knowingly uttering a falsehood with the goal that someone believe the falsehood, a definition
-of lying that is relatively well-accepted. The factual background needed consists of the fact that if 
+of lying and relatively uncontroversial facts about the world. My system needs two pieces of common 
+sense to complete this proof. First, I defined lying as knowingly uttering a falsehood with the goal 
+that someone believe the falsehood, a definition of lying that is relatively well-accepted. Second, I 
+assumed (following in Korsgaard's footsteps) that if 
 everyone lies in a given context, then people will stop believing each other in that context. This is 
@@
 computer provides value to ethicists, bolstering the argument for computational ethics provided in 
-Section Computational Ethics.%
+Section \ref{computationalethics}.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 and what he has in mind'' \citep{KorsgaardRTL}.\footnote{Korsgaard assumes that the murderer will 
-lie about his identity in order to take advantage of your honesty to find his victim. In footnote 5 
-of \citep{KorsgaardRTL}, she accepts that her arguments will not apply in the case of the honest murderer 
+lie about his identity in order to take advantage of your honesty to find his victim. In footnote 5, 
+she accepts that her arguments will not apply in the case of the honest murderer 
 who announces his intentions, so she restricts her focus to the case of lying to a liar. She claims 
-that in the case of the honest murderer, the correct act is to refuse to respond.} Thus, the maxim 
+that in the case of the honest murderer, the correct act is to refuse to respond. Since I am formalizing
+Korsgaard's argument, I also accept this assumption.} Thus, the maxim 
 in question specifies that when someone lies to you, you are allowed to lie to them. The maxim of 
@@
 
-In this section, I formalize her argument for the permissibility of lying to a liar. First, I define
+In this section, I formalize Korsgaard's argument for the permissibility of lying to a liar. First, I define
 Bill's maxim, which is to hide his intention to murder.%
@@
 %
-\isamarkupcmt{This example involves one additional subject: the murderer.%
+\isamarkupcmt{This example involves the murderer as an additional subject.%
 }\isanewline
@@
 %
-\isamarkupcmt{This is one of two assumptions that encode Korsgaard's core argument. If person1 believes that person2 
-utters a sentence as a falsehood, then person1 won't believe that sentence. This is a modification of the 
+\isamarkupcmt{This is one of two assumptions that encode Korsgaard's core argument. If $p1$ believes that $p2$ 
+utters a sentence as a falsehood, then $p1$ won't believe that sentence. This is a modification of the 
 convention of trust assumption from above, and I will refer to it as the ``convention of belief" assumption.
 Again, like the convention of trust assumption, this assumption is uncontroversial: if I think you are 
-saying a false sentence, then I won't believe that sentence.%
-}\isanewline
-\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}c\ a\ g\ w{\isachardot}\ {\isacharparenleft}universalized\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isacharparenleft}person{\isadigit{1}}\ believes\ {\isacharparenleft}person{\isadigit{2}}\ believes\ c{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}person{\isadigit{1}}\ believes\ {\isacharparenleft}a\ person{\isadigit{2}}{\isacharparenright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
-%
-\isamarkupcmt{This is the second major common sense assumption. If the maxim (c, a, g) is universalized, then 
-if person1 believes that person2 believes they are in the given circumstances, then person1 believes 
-that person2 performs the act. In other words, person1 will believe that 
-person2 wills the maxim. I will refer to this as the ``convention of willing'' assumption. This follows
+lying, then I won't believe you.%
+}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}c\ a\ g\ w{\isachardot}\ {\isasymforall}p{\isadigit{1}}{\isacharcolon}{\isacharcolon}s{\isachardot}\ {\isasymforall}p{\isadigit{2}}{\isacharcolon}{\isacharcolon}s{\isachardot}\ {\isacharparenleft}universalized\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isacharparenleft}p{\isadigit{1}}\ believes\ {\isacharparenleft}p{\isadigit{2}}\ believes\ c{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}p{\isadigit{1}}\ believes\ {\isacharparenleft}a\ p{\isadigit{2}}{\isacharparenright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{This is the second major common sense assumption. If the maxim $(c, a, g)$ is universalized, then 
+if $p1$ believes that $p2$ believes they are in the given circumstances, then $p1$ believes 
+that $p2$ performs the act. In other words, $p1$ will believe that 
+$p2$ wills the maxim. I will refer to this as the ``convention of willing'' assumption. This follows
 directly from Korsgaard's conception of universalizability: when a maxim is universalized, everyone 
-wills it and thus notices the pattern of everyone willing it. If you observe that many do X in circumstances C,
-you will assume that everyone does X in circumstance C.%
+wills it and thus notices the pattern of everyone willing it. If you observe that many do $X$ in circumstances $C$,
+you will assume that everyone does $X$ in circumstance $C$.%
 }\isanewline
@@
 ultimately uncontroversial because they were direct consequences of Korsgaard's definition of willing 
-and of ordinary definitions of lying. These thin assumptions were sufficient to generate moral conclusions
-that Kantian scholars debate robustly. Armed with this common sense, my system generated 
+and of ordinary definitions of lying. These thin assumptions were sufficient to recreate Korsgaard's solution
+to an open ethical problem. Armed with this common sense, my system generated 
 a conclusion that many critics of Kant prior to Korsgaard failed to see.\footnote{
@@
 The need for common sense reasoning to evaluate the universalizability test and to formulate a maxim
-is a potential limitation of my system, and I adress this concern in Section \ref{whatisamaxim} and 
-Section Limitations.
+is a potential limitation of my system, and I adress this concern in Section \ref{AIethics}.
 
@@
 uncontroversial definitions and assumptions are enough to achieve nuanced ethical judgements. Moreover, 
-these kinds of judgements demonstrate that, with additional work, my system could be used in pratice 
-to guide AI agents. A ``smart doorbell'' like those created by Ring may face a dilemma like that of 
-the murderer at the door. Such a doorbell equipped with a more application-ready version of my 
+these kinds of judgements demonstrate that, with additional work, my system could be used in practice 
+to guide AI agents. The idea of AI making decisions as in the dilemmas above may seem far-fetched, but
+such scenarios are already becoming reality. For example, a ``smart doorbell'' may face a dilemma like that of
+the murderer at the door. Such an AI agent equipped with a future version of my 
 system would be able to reason about lying to the murderer and arrive at the right judgement, guided by
@@
 %:%132=88%:%
-%:%135=91%:%
-%:%136=92%:%
-%:%137=93%:%
-%:%138=94%:%
-%:%139=95%:%
-%:%140=96%:%
-%:%141=97%:%
-%:%143=100%:%
-%:%144=100%:%
-%:%146=101%:%
-%:%147=102%:%
-%:%148=102%:%
-%:%149=103%:%
-%:%150=103%:%
-%:%151=104%:%
-%:%153=105%:%
-%:%154=105%:%
-%:%155=106%:%
-%:%156=106%:%
-%:%157=107%:%
-%:%159=108%:%
-%:%160=109%:%
-%:%161=110%:%
-%:%162=111%:%
-%:%163=112%:%
-%:%166=116%:%
-%:%167=117%:%
-%:%168=118%:%
-%:%169=119%:%
-%:%170=120%:%
-%:%171=121%:%
-%:%172=122%:%
-%:%173=123%:%
-%:%174=124%:%
-%:%175=125%:%
-%:%177=127%:%
-%:%178=127%:%
-%:%179=128%:%
-%:%181=129%:%
-%:%184=131%:%
-%:%185=132%:%
-%:%186=133%:%
-%:%187=134%:%
-%:%188=135%:%
-%:%189=136%:%
-%:%190=137%:%
-%:%191=138%:%
-%:%192=139%:%
-%:%193=140%:%
-%:%194=141%:%
-%:%195=142%:%
-%:%196=143%:%
-%:%198=145%:%
-%:%199=145%:%
-%:%201=146%:%
-%:%202=147%:%
-%:%203=148%:%
-%:%204=148%:%
-%:%205=149%:%
-%:%206=149%:%
-%:%208=150%:%
-%:%209=151%:%
-%:%210=151%:%
-%:%211=152%:%
-%:%212=152%:%
-%:%214=153%:%
-%:%217=155%:%
-%:%218=156%:%
-%:%219=157%:%
-%:%220=158%:%
-%:%222=160%:%
-%:%223=160%:%
-%:%224=161%:%
-%:%225=162%:%
-%:%227=163%:%
-%:%228=163%:%
-%:%229=164%:%
-%:%231=165%:%
-%:%232=166%:%
-%:%233=166%:%
-%:%234=167%:%
-%:%236=168%:%
-%:%237=169%:%
-%:%238=170%:%
-%:%239=171%:%
-%:%240=172%:%
-%:%241=173%:%
-%:%242=173%:%
-%:%243=174%:%
-%:%245=175%:%
-%:%246=175%:%
-%:%247=176%:%
-%:%254=177%:%
-%:%255=177%:%
-%:%256=178%:%
-%:%257=178%:%
-%:%258=179%:%
-%:%259=179%:%
-%:%261=180%:%
-%:%262=181%:%
-%:%263=182%:%
-%:%264=183%:%
-%:%265=183%:%
-%:%266=184%:%
-%:%267=184%:%
-%:%268=185%:%
-%:%269=185%:%
-%:%270=186%:%
-%:%271=186%:%
-%:%272=187%:%
-%:%273=187%:%
-%:%274=187%:%
-%:%276=188%:%
-%:%277=189%:%
-%:%278=189%:%
-%:%279=190%:%
-%:%289=192%:%
-%:%290=193%:%
-%:%291=194%:%
-%:%292=195%:%
-%:%293=196%:%
-%:%294=197%:%
-%:%295=198%:%
-%:%296=199%:%
-%:%297=200%:%
-%:%298=201%:%
-%:%299=202%:%
-%:%300=203%:%
-%:%301=204%:%
-%:%302=205%:%
-%:%304=207%:%
+%:%135=90%:%
+%:%136=91%:%
+%:%137=92%:%
+%:%138=93%:%
+%:%139=94%:%
+%:%140=95%:%
+%:%141=96%:%
+%:%143=99%:%
+%:%144=99%:%
+%:%146=100%:%
+%:%147=101%:%
+%:%148=101%:%
+%:%149=102%:%
+%:%150=102%:%
+%:%151=103%:%
+%:%153=104%:%
+%:%154=104%:%
+%:%155=105%:%
+%:%156=105%:%
+%:%157=106%:%
+%:%159=107%:%
+%:%160=108%:%
+%:%161=109%:%
+%:%162=110%:%
+%:%163=111%:%
+%:%166=115%:%
+%:%167=116%:%
+%:%168=117%:%
+%:%169=118%:%
+%:%170=119%:%
+%:%171=120%:%
+%:%172=121%:%
+%:%173=122%:%
+%:%174=123%:%
+%:%175=124%:%
+%:%177=126%:%
+%:%178=126%:%
+%:%179=127%:%
+%:%181=128%:%
+%:%184=130%:%
+%:%185=131%:%
+%:%186=132%:%
+%:%187=133%:%
+%:%188=134%:%
+%:%189=135%:%
+%:%190=136%:%
+%:%191=137%:%
+%:%192=138%:%
+%:%193=139%:%
+%:%194=140%:%
+%:%195=141%:%
+%:%196=142%:%
+%:%198=144%:%
+%:%199=144%:%
+%:%201=145%:%
+%:%202=146%:%
+%:%203=147%:%
+%:%204=147%:%
+%:%205=148%:%
+%:%206=148%:%
+%:%208=149%:%
+%:%209=150%:%
+%:%210=150%:%
+%:%211=151%:%
+%:%212=151%:%
+%:%214=152%:%
+%:%217=154%:%
+%:%218=155%:%
+%:%219=156%:%
+%:%220=157%:%
+%:%222=159%:%
+%:%223=159%:%
+%:%224=160%:%
+%:%225=161%:%
+%:%227=162%:%
+%:%228=162%:%
+%:%229=163%:%
+%:%231=164%:%
+%:%232=165%:%
+%:%233=165%:%
+%:%234=166%:%
+%:%236=167%:%
+%:%237=168%:%
+%:%238=169%:%
+%:%239=170%:%
+%:%240=171%:%
+%:%241=172%:%
+%:%242=172%:%
+%:%243=173%:%
+%:%245=174%:%
+%:%246=174%:%
+%:%247=175%:%
+%:%254=176%:%
+%:%255=176%:%
+%:%256=177%:%
+%:%257=177%:%
+%:%258=178%:%
+%:%259=178%:%
+%:%261=179%:%
+%:%262=180%:%
+%:%263=181%:%
+%:%264=182%:%
+%:%265=182%:%
+%:%266=183%:%
+%:%267=183%:%
+%:%268=184%:%
+%:%269=184%:%
+%:%270=185%:%
+%:%271=185%:%
+%:%272=186%:%
+%:%273=186%:%
+%:%274=186%:%
+%:%276=187%:%
+%:%277=188%:%
+%:%278=188%:%
+%:%279=189%:%
+%:%289=191%:%
+%:%290=192%:%
+%:%291=193%:%
+%:%292=194%:%
+%:%293=195%:%
+%:%294=196%:%
+%:%295=197%:%
+%:%296=198%:%
+%:%297=199%:%
+%:%298=200%:%
+%:%299=201%:%
+%:%300=202%:%
+%:%301=203%:%
+%:%302=204%:%
+%:%303=205%:%
 %:%305=207%:%
-%:%306=208%:%
-%:%308=209%:%
-%:%309=210%:%
-%:%312=212%:%
-%:%313=213%:%
-%:%314=214%:%
-%:%315=215%:%
-%:%316=216%:%
-%:%317=217%:%
-%:%318=218%:%
-%:%319=219%:%
-%:%320=220%:%
-%:%322=222%:%
+%:%306=207%:%
+%:%307=208%:%
+%:%309=209%:%
+%:%310=210%:%
+%:%313=212%:%
+%:%314=213%:%
+%:%315=214%:%
+%:%316=215%:%
+%:%317=216%:%
+%:%318=217%:%
+%:%319=218%:%
+%:%320=219%:%
+%:%321=220%:%
 %:%323=222%:%
-%:%324=223%:%
-%:%325=224%:%
-%:%327=225%:%
+%:%324=222%:%
+%:%325=223%:%
+%:%326=224%:%
 %:%328=225%:%
-%:%329=226%:%
-%:%331=227%:%
-%:%332=228%:%
+%:%329=225%:%
+%:%330=226%:%
+%:%332=227%:%
 %:%333=228%:%
-%:%334=229%:%
-%:%336=230%:%
+%:%334=228%:%
+%:%335=229%:%
 %:%337=230%:%
-%:%338=231%:%
-%:%340=232%:%
+%:%338=230%:%
+%:%339=231%:%
 %:%341=232%:%
-%:%342=233%:%
-%:%345=234%:%
-%:%349=234%:%
+%:%342=232%:%
+%:%343=233%:%
+%:%346=234%:%
 %:%350=234%:%
-%:%352=235%:%
-%:%353=236%:%
-%:%354=237%:%
-%:%355=238%:%
-%:%356=239%:%
-%:%366=242%:%
-%:%367=243%:%
-%:%368=244%:%
-%:%369=245%:%
-%:%370=246%:%
-%:%371=247%:%
-%:%372=248%:%
-%:%373=249%:%
-%:%374=250%:%
-%:%375=251%:%
-%:%376=252%:%
-%:%377=253%:%
-%:%378=254%:%
-%:%379=255%:%
-%:%380=256%:%
-%:%381=257%:%
-%:%382=258%:%
-%:%383=259%:%
-%:%384=260%:%
-%:%385=261%:%
-%:%386=262%:%
-%:%387=263%:%
-%:%388=264%:%
-%:%389=265%:%
-%:%390=266%:%
-%:%391=267%:%
-%:%392=268%:%
-%:%393=269%:%
-%:%394=270%:%
-%:%395=271%:%
-%:%396=272%:%
-%:%397=273%:%
-%:%398=274%:%
-%:%399=275%:%
-%:%400=276%:%
-%:%401=277%:%
-%:%402=278%:%
-%:%403=279%:%
-%:%404=280%:%
-%:%405=281%:%
-%:%406=282%:%
-%:%407=283%:%
-%:%408=284%:%
-%:%409=285%:%
-%:%410=286%:%
-%:%419=289%:%
-%:%431=292%:%
-%:%432=293%:%
-%:%433=294%:%
-%:%434=295%:%
-%:%435=296%:%
-%:%436=297%:%
-%:%437=298%:%
-%:%438=299%:%
-%:%439=300%:%
-%:%440=301%:%
-%:%441=302%:%
-%:%442=303%:%
-%:%443=304%:%
-%:%444=305%:%
-%:%445=306%:%
-%:%446=307%:%
-%:%447=308%:%
-%:%448=309%:%
-%:%450=311%:%
-%:%451=311%:%
+%:%351=234%:%
+%:%353=235%:%
+%:%354=236%:%
+%:%355=237%:%
+%:%356=238%:%
+%:%357=239%:%
+%:%367=242%:%
+%:%368=243%:%
+%:%369=244%:%
+%:%370=245%:%
+%:%371=246%:%
+%:%372=247%:%
+%:%373=248%:%
+%:%374=249%:%
+%:%375=250%:%
+%:%376=251%:%
+%:%377=252%:%
+%:%378=253%:%
+%:%379=254%:%
+%:%380=255%:%
+%:%381=256%:%
+%:%382=257%:%
+%:%383=258%:%
+%:%384=259%:%
+%:%385=260%:%
+%:%386=261%:%
+%:%387=262%:%
+%:%388=263%:%
+%:%389=264%:%
+%:%390=265%:%
+%:%391=266%:%
+%:%392=267%:%
+%:%393=268%:%
+%:%394=269%:%
+%:%395=270%:%
+%:%396=271%:%
+%:%397=272%:%
+%:%398=273%:%
+%:%399=274%:%
+%:%400=275%:%
+%:%401=276%:%
+%:%402=277%:%
+%:%403=278%:%
+%:%404=279%:%
+%:%405=280%:%
+%:%406=281%:%
+%:%407=282%:%
+%:%408=283%:%
+%:%409=284%:%
+%:%410=285%:%
+%:%411=286%:%
+%:%420=289%:%
+%:%432=292%:%
+%:%433=293%:%
+%:%434=294%:%
+%:%435=295%:%
+%:%436=296%:%
+%:%437=297%:%
+%:%438=298%:%
+%:%439=299%:%
+%:%440=300%:%
+%:%441=301%:%
+%:%442=302%:%
+%:%443=303%:%
+%:%444=304%:%
+%:%445=305%:%
+%:%446=306%:%
+%:%447=307%:%
+%:%448=308%:%
+%:%449=309%:%
+%:%450=310%:%
+%:%452=312%:%
 %:%453=312%:%
-%:%454=312%:%
 %:%455=313%:%
 %:%456=313%:%
+%:%457=314%:%
 %:%458=314%:%
-%:%459=315%:%
-%:%460=316%:%
+%:%460=315%:%
 %:%461=316%:%
@@
 %:%463=317%:%
+%:%464=318%:%
 %:%465=318%:%
-%:%466=318%:%
 %:%467=319%:%
 %:%468=319%:%
+%:%469=320%:%
 %:%470=320%:%
-%:%471=320%:%
 %:%472=321%:%
@@
 %:%474=322%:%
+%:%475=322%:%
 %:%476=323%:%
-%:%477=324%:%
-%:%480=326%:%
-%:%481=327%:%
-%:%482=328%:%
-%:%483=329%:%
-%:%485=331%:%
-%:%486=331%:%
+%:%478=324%:%
+%:%479=325%:%
+%:%482=327%:%
+%:%483=328%:%
+%:%484=329%:%
+%:%485=330%:%
+%:%487=332%:%
 %:%488=332%:%
-%:%489=332%:%
 %:%490=333%:%
@@
 %:%492=334%:%
+%:%493=334%:%
 %:%494=335%:%
-%:%495=335%:%
 %:%496=336%:%
 %:%497=336%:%
+%:%498=337%:%
 %:%499=337%:%
-%:%500=337%:%
 %:%501=338%:%
@@
 %:%503=339%:%
+%:%504=339%:%
 %:%505=340%:%
-%:%506=341%:%
-%:%522=373%:%
-%:%523=374%:%
-%:%524=375%:%
-%:%525=376%:%
-%:%526=377%:%
-%:%527=378%:%
-%:%528=379%:%
-%:%529=380%:%
-%:%530=381%:%
-%:%532=383%:%
-%:%533=383%:%
+%:%507=341%:%
+%:%508=342%:%
+%:%524=374%:%
+%:%525=375%:%
+%:%526=376%:%
+%:%527=377%:%
+%:%528=378%:%
+%:%529=379%:%
+%:%530=380%:%
+%:%531=381%:%
+%:%532=382%:%
 %:%534=384%:%
-%:%535=385%:%
+%:%535=384%:%
+%:%536=385%:%
 %:%537=386%:%
-%:%538=386%:%
 %:%539=387%:%
+%:%540=387%:%
 %:%541=388%:%
-%:%542=388%:%
 %:%543=389%:%
+%:%544=389%:%
 %:%545=390%:%
-%:%546=391%:%
-%:%547=392%:%
-%:%548=393%:%
-%:%549=394%:%
+%:%547=391%:%
+%:%548=392%:%
+%:%549=393%:%
 %:%550=394%:%
 %:%551=395%:%
+%:%552=395%:%
 %:%553=396%:%
-%:%554=397%:%
-%:%555=398%:%
-%:%556=399%:%
-%:%557=400%:%
-%:%558=401%:%
-%:%559=402%:%
+%:%555=397%:%
+%:%556=398%:%
+%:%557=399%:%
+%:%558=400%:%
+%:%559=401%:%
 %:%560=402%:%
 %:%561=403%:%
+%:%562=403%:%
 %:%563=404%:%
-%:%564=405%:%
 %:%565=405%:%
 %:%566=406%:%
-%:%569=407%:%
-%:%573=407%:%
-%:%574=407%:%
-%:%575=407%:%
+%:%567=406%:%
+%:%568=407%:%
+%:%571=408%:%
+%:%575=408%:%
+%:%576=408%:%
 %:%577=408%:%
-%:%578=409%:%
-%:%579=410%:%
-%:%589=412%:%
-%:%590=413%:%
-%:%591=414%:%
-%:%592=415%:%
-%:%594=417%:%
-%:%595=417%:%
+%:%579=409%:%
+%:%580=410%:%
+%:%581=411%:%
+%:%591=413%:%
+%:%592=414%:%
+%:%593=415%:%
+%:%594=416%:%
 %:%596=418%:%
+%:%597=418%:%
 %:%598=419%:%
-%:%599=419%:%
 %:%600=420%:%
+%:%601=420%:%
 %:%602=421%:%
-%:%603=421%:%
 %:%604=422%:%
+%:%605=422%:%
 %:%606=423%:%
-%:%607=423%:%
 %:%608=424%:%
+%:%609=424%:%
 %:%610=425%:%
-%:%611=425%:%
 %:%612=426%:%
+%:%613=426%:%
 %:%614=427%:%
-%:%615=428%:%
 %:%616=428%:%
 %:%617=429%:%
-%:%624=430%:%
-%:%625=430%:%
+%:%618=429%:%
+%:%619=430%:%
 %:%626=431%:%
@@
 %:%629=432%:%
-%:%630=432%:%
+%:%630=433%:%
 %:%631=433%:%
@@
 %:%634=434%:%
-%:%635=434%:%
+%:%635=435%:%
 %:%636=435%:%
@@
 %:%639=436%:%
-%:%640=436%:%
+%:%640=437%:%
 %:%641=437%:%
-%:%651=439%:%
-%:%652=440%:%
-%:%653=441%:%
-%:%654=442%:%
-%:%655=443%:%
-%:%656=444%:%
-%:%657=445%:%
-%:%658=446%:%
-%:%659=447%:%
-%:%660=448%:%
-%:%661=449%:%
-%:%662=450%:%
-%:%663=451%:%
-%:%664=452%:%
-%:%665=453%:%
-%:%666=454%:%
-%:%667=455%:%
-%:%668=456%:%
-%:%669=457%:%
-%:%670=458%:%
-%:%671=459%:%
-%:%672=460%:%
-%:%673=461%:%
-%:%674=462%:%
-%:%675=463%:%
-%:%676=464%:%
-%:%677=465%:%
-%:%678=466%:%
-%:%679=467%:%
-%:%680=468%:%
-%:%681=469%:%
-%:%682=470%:%
-%:%683=471%:%
-%:%684=472%:%
-%:%685=473%:%
-%:%686=474%:%
+%:%642=437%:%
+%:%643=438%:%
+%:%653=440%:%
+%:%654=441%:%
+%:%655=442%:%
+%:%656=443%:%
+%:%657=444%:%
+%:%658=445%:%
+%:%659=446%:%
+%:%660=447%:%
+%:%661=448%:%
+%:%662=449%:%
+%:%663=450%:%
+%:%664=451%:%
+%:%665=452%:%
+%:%666=453%:%
+%:%667=454%:%
+%:%668=455%:%
+%:%669=456%:%
+%:%670=457%:%
+%:%671=458%:%
+%:%672=459%:%
+%:%673=460%:%
+%:%674=461%:%
+%:%675=462%:%
+%:%676=463%:%
+%:%677=464%:%
+%:%678=465%:%
+%:%679=466%:%
+%:%680=467%:%
+%:%681=468%:%
+%:%682=469%:%
+%:%683=470%:%
+%:%684=471%:%
+%:%685=472%:%
+%:%686=473%:%
+%:%687=474%:%
+%:%688=475%:%

### 2022-03-08 paper/output/document/thesis_5_discussion.tex
my back hurts

@@
 nuanced ethical reasoning. In this section, I outline the additional components necessary for my system
-to guide AI agents. My work on automating the categorical imperative 
+to guide AI agents in practice. My work on automating the categorical imperative 
 could serve as one component of a partially or fully artificial ethical reasoner, or an ``ethical AI.''
@@
 %
+\begin{center}
 \begin{figure}
-\centering
-\includegraphics[scale=0.5]{AI_engine.png}
+\includegraphics[scale=0.43]{AI_engine.png}
 \caption{An example of an ethics engine for an artificial agent, which begins with a moral dilemma, 
@@
 \end{figure}
+\end{center}
 %
@@
 The input parser must translate a complex real-world situation into a flat, logical representation.
-This requires that the input parser determine which circumstances are ``morally relevant''
-for a maxim, a controversial judgement.
-There is robust debate in the literature on the circumstances that should be considered when formulating a maxim, 
-inspired by a common objection to Kantian ethics. The``tailoring objection'' is the worry that arbitrarily specific 
-circumstances render any maxim universalizable. For example, the maxim ``When my name is Lavanya Singh 
-and I am wearing a purple shirt and it is November 26th, I will lie in order to get some easy cash'' 
-passes the universalizability test. Even if this maxim is willed universally, the circumstances are so 
+This requires that the input parser determine which circumstances are morally relevant
+to a maxim, a controversial judgement. As mentioned in Section \ref{whatisamaxim},
+there is robust debate in the literature on the circumstances that should be considered when formulating a maxim, 
+inspired by the tailoring objection, a common criticism of Kantian ethics. Recall that the tailoring objection is the worry that arbitrarily specific 
+circumstances render any maxim universalizable. For example, consider the maxim ``When my name is Lavanya Singh 
+and I am wearing a purple shirt and it is November 26th, I will lie in order to get some easy cash.'' 
+Even if this maxim is willed universally, the circumstances are so 
 specific that lying will not become the general mechanism for getting easy cash, so the lender will 
@@
 While this view has intuitive appeal, it raises the question of how we can determine
-which circumstances are morally relevant. O'Niell answers this question by noting that the Formula of Universal Law is 
+which circumstances are morally relevant. O'Neill answers this question by noting that the Formula of Universal Law is 
 a ``test of moral worth rather than of outward rightness'' \citep[98]{constofreason}. The FUL is a way 
 for an agent to decide how they should behave, not for a third-party to judge their behavior. Ethics is 
-a personal proces and the FUL is designed to help agents internally make decisions. Because agents use 
+a personal process and the FUL is designed to help agents make decisions. Because agents use 
 the FUL to evaluate their own behavior, the test is at its 
@@
 imperative would prescribe. For proponents of the ``human-in-the-loop'' model of AI ethics, in which 
-ethical AI requires that humans guide machines \citep{loop}, this kind of human involvement may be a feature.
+ethical AI requires that humans guide machines, this kind of human involvement may be a feature \citep{loop}.
 The outcome of the universalizability test will depend on how the human formulates the maxim; if the 
@@
 
-My system's output could be converted into some actionable, useful response with another output parser, 
+My system's output could be converted into some actionable, useful response with an output parser, 
 and then passed back to the AI agent. For example, if the AI agent is equipped to evaluate natural 
@@
 for the purpose ``eating breakfast.'' In these circumstances, the act has 
-already been performed! Adopting this maxim as a law to live by does not change how you live. If you adopt 
+already been performed. Adopting this maxim as a law to live by does not change how you live. If you adopt 
 this maxim, then when you are eating breakfast, you eat breakfast, but this statement is already tautologically true.
@@
 
-Another related worry has to with maxims that we think are prohibited. Consider the maxim modified to 
+Another related worry concerns maxims that we think are prohibited. Consider the maxim modified to 
 read ``When dancing and seeing a child drowning, I should dance for the sake of dancing.'' Clearly this 
@@
 
-In the previous section, I defined badly formed maxims, a philosophical concept that I discovered
-using computational ethics. In this section, I demonstrate the implications of this concept for a 
-philosophical debate to demonstrate that computational ethics can result in insights with real 
+Above, I defined badly formed maxims, a philosophical concept that I discovered
+using computational ethics. In this section, I explore the implications of this concept for a 
+philosophical debate to show that computational ethics can result in insights with real 
 philosophical weight. I use badly formed maxims to resolve the tension between self-doubt and self-respect. 
@@
 
-While most philosophers accept some version of SR\footnote{Christensen cites \citet{vanfraasen}, 
+While most philosophers accept some version of SR\footnote{Christensen cites \citet{vanfraassen}, 
 \citet{vickers}, and \citet{koons}.}, 
@@
 of dancing'' is a permissible maxim to act on. Notice that the maxim in question is badly-formed: the 
-circumstance ``when dancing at a friend's wedding'' implies the act ``dance.'' Because this is a 
-badly-formed maxim, it cannot be the maxim that she is questioning, for adopting
-this maxim could not have changed her behavior at all. Sara is wondering if her behavior is permissible, but
-any conclusions about the permissibility of a badly-formed maxim would not help her. This is because 
-the maxim has no effect on her action and because any such permissibility would be a foregone conclusion,
-since she has already adopted the maxim. Thus, under the interpretation of self-doubt as a badly-formed 
-maxim, the tension between ESR and ethical self-doubt seems irresolvable. Those committed to this 
+circumstance ``when dancing at a friend's wedding'' implies the act ``dance.'' As I argued above, if 
+Sara asks if she should will a badly formed maxim, she is questioning her own will's authority, which
+is paradoxical. If maxims are about self-doubt are badly-formed maxims, then the tension between ESR
+and ESD is natural and unavoidable: debating the permissibility of a badly-formed maxim inherently
+involves questioning commitments as we make them, which is impossible. This is the source of the 
+tension between ESR and ESD. Those committed to this 
 interpretation must abandon one principle or the other, since committing and questioning are incompatible.
@@
 past beliefs \cite[3-4]{christensen}. Such doubt does not undermine the reasoner's decision-making 
-capacity and is thus perfectly consistent with ethical self-respect.
-
-The tension between ESR and ESD arises from a misreading of questions of self-doubt as questions about 
+capacity and is thus perfectly consistent with ethical self-respect. Moreover, this is a much more 
+intuitive question to be asking \emph{because} it is a well-formed maxim. Not only is the badly-formed
+interpretation of this maxim problematic for ESR, it is also not the kind of question that is useful for a practical
+reasoner to ask, as argued above.
+
+Thus, the tension between ESR and ESD arises from a misreading of questions of self-doubt as questions about 
 the evaluation of badly-formed maxims. A question of self-doubt cannot refer to a badly-formed maxim and must 
@@
 formed maxims is significant. Much of the work of a Kantian ethicist is formulating an
-appropriate maxim, and badly-formed maxims define one boundary condition for this task.%
+appropriate maxim, and badly-formed maxims define one boundary condition for this task. Just as my isolation
+of the wrongness of lying in Section \ref{joking} could help guide the formation of morally worthy maxims, 
+so can the insight about badly-formed maxims.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 of reaching. Instead, I claim that insights like the one about the well-formed maxim are much easier
-to reach with computational tools. Badly-formed maxims are usually ignored in philosophical discussion 
-and would have been much more difficult to understand without the help of a computer. Computational 
+to reach with computational tools. Computational 
 tools prompt philosophers to ask new questions that 
@@
 to make headway \citep{buzzardvideo}, even though theorem provers were first invented in the 1960's \citep{historyofITP}. 
-In contrast, the first attempts to use theorem provers for ethics occurred in the last decade. The 
+In contrast, the first attempts to use theorem provers for ethics occurred in the last few years. The 
 fact that this nascent technology is already helping humans reach non-trivial philosophical conclusions 
@@
 automate away tedium and achieve greater precision, it can do the same for ordinary human beings navigating
-the world. Moreover, it also offers another way for the general public to access professional philosophy's
+the world. Moreover, it also offers another way for the general public to access professional philosophy
 insights, and thus carries potential to improve our everyday reasoning.%
@@
 a ``good'' action, but it requires acting on a morally worthy maxim from the motivation of duty, or 
-doing the right thing because it is the right thing to do. Moral behavior requires both a certain action 
-(acting on a morally worthy maxim) and a certain motivation (the motivation of duty). It is this capacity 
+doing the right thing because it is the right thing to do. It is this capacity 
 for self-motivation that makes morality binding for rational beings; we must behave morally precisely 
@@
 
-The challenge of mapping actions to maxims is a limitation of my system, but it is not insurmountable. In Section \ref{aiethics},
+The challenge of mapping actions to maxims is a limitation of my system, but it is not insurmountable. In Section \ref{AIethics},
 I argued that, before my system can be used in practice, it must be paired with an input parser that can
@@
 
-Daniela Tafani takes this argument one step further by arguing that this ``alamnac'' of maxims already 
+Daniela Tafani takes O'Neill's argument one step further by arguing that this ``alamnac'' of maxims already 
 includes the moral status of the maxims in questions; human beings already
@@
 that ``the Kantian test is therefore as useless for machines as it is for anyone who does
-not already know what to do'' \citep[8]{tafani}.\footnote{Translated from the original paper using Google Translate.} 
+not already know what to do'' \citep[8]{tafani}.\footnote{Translated using Google Translate.} 
 Understanding the categorical imperative test as a reminder
@@
 \centering
-\includegraphics[scale=0.5]{inputparser.png}
+\includegraphics[scale=0.47]{inputparser.png}
 \caption{A refined version of Figure \ref{fig:AIengine} in which the input parser learns from a database
@@
 may be unable to reason using the categorical imperative, but one equipped with some prior knowledge
-of maxims and their moral worth may even help us better reason about morality.%
+of maxims and their moral worth may even be able to reason about morality better than human beings can.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 
-Two branches of automated ethics are top-down and bottom-up ethics. Top-down automated ethics begins 
+Automated ethics falls into two branches: top-down and bottom-up ethics. Top-down automated ethics begins 
 with an ethical theory, whereas bottom-up automated ethics learns ethical judgements from prior 
@@
 independent AI, there is a dire need to program such AI with some notion of ethics. If AI is navigating
-human society, then it is making decisions with an ethical facet at all times. Ethics is inescapable; 
+human society, then it is making ethically-tinged decisions at all times. Ethics is inescapable; 
 if AI developers and computer scientists ignore it, then they will be building machines that make decisions
@@
 with crime, demonstrate that such implicit ethics usually codifies the biases, prejudices, and moral
-failings of the society in which it is developed. AI will inevitably make judgements on moral dilemmas, 
+failings of the society in which it is developed \citep{eubanks, sweeney}. AI will inevitably make judgements on moral dilemmas, 
 and automated ethics is necessary to make these judgements morally correct.
@@
 %:%60=31%:%
-%:%63=33%:%
+%:%61=32%:%
 %:%64=34%:%
@@
 %:%173=143%:%
-%:%182=145%:%
-%:%194=147%:%
+%:%174=144%:%
+%:%183=146%:%
 %:%195=148%:%
@@
 %:%198=151%:%
-%:%207=153%:%
-%:%219=155%:%
+%:%199=152%:%
+%:%208=154%:%
 %:%220=156%:%
@@
 %:%401=337%:%
-%:%410=341%:%
-%:%422=343%:%
-%:%423=344%:%
-%:%424=345%:%
-%:%425=346%:%
-%:%426=347%:%
+%:%402=338%:%
+%:%403=339%:%
+%:%404=340%:%
+%:%405=341%:%
+%:%406=342%:%
+%:%415=346%:%
 %:%427=348%:%
@@
 %:%487=408%:%
-%:%496=410%:%
-%:%508=412%:%
-%:%509=413%:%
-%:%510=414%:%
-%:%511=415%:%
+%:%488=409%:%
+%:%489=410%:%
+%:%490=411%:%
+%:%491=412%:%
+%:%500=414%:%
 %:%512=416%:%
@@
 %:%586=490%:%
-%:%595=493%:%
-%:%607=496%:%
-%:%608=497%:%
-%:%609=498%:%
-%:%610=499%:%
+%:%587=491%:%
+%:%588=492%:%
+%:%589=493%:%
+%:%590=494%:%
+%:%599=497%:%
 %:%611=500%:%
@@
 %:%714=603%:%
-%:%717=605%:%
-%:%718=606%:%
-%:%719=607%:%
+%:%715=604%:%
+%:%716=605%:%
+%:%717=606%:%
 %:%720=608%:%
@@
 %:%722=610%:%
-%:%725=611%:%
-%:%726=612%:%
-%:%727=613%:%
+%:%723=611%:%
+%:%724=612%:%
+%:%725=613%:%
 %:%728=614%:%
@@
 %:%739=625%:%
-%:%748=629%:%
-%:%760=631%:%
-%:%761=632%:%
-%:%762=633%:%
+%:%740=626%:%
+%:%741=627%:%
+%:%742=628%:%
+%:%751=632%:%
 %:%763=634%:%
@@
 %:%811=682%:%
-%:%820=684%:%
-%:%832=686%:%
-%:%833=687%:%
-%:%834=688%:%
+%:%812=683%:%
+%:%813=684%:%
+%:%814=685%:%
+%:%823=687%:%
 %:%835=689%:%
@@
 %:%870=724%:%
+%:%871=725%:%
+%:%872=726%:%
+%:%873=727%:%

### 2022-03-09 paper/output/document/appendix.tex
making my way dowtown, typing fast, appendices pass

@@
 %
-\isamarkupsection{Appendix: Alternate Definitions of a Maxim \label{maximmotive}%
+\isamarkupsection{Alternate Definitions of a Maxim \label{maximmotive}%
 }
@@
 with a logic of practical reason, an implementation of the FUL can move from evaluating a maxim to 
-evaluating an agent's behavior, since that's when ``acting from duty'' starts to matter.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\isatagdocument
-%
-\endisatagdocument
-{\isafolddocument}%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isatagproof
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
+evaluating an agent's behavior, since that's when ``acting from duty'' starts to matter.
+
+\newpage%
+\end{isamarkuptext}\isamarkuptrue%
 %
@@
 %
-\isamarkupsubsection{Logical Background \label{sec:kroy_logical_background}%
+\isamarkupsubsection{Implementing Kroy's Formalization \label{sec:kroy_logical_background}%
 }
@@
 \begin{isamarkuptext}%
-Kroy's logic also requires the notion of a subject, will I define as a new type, just as I did
-for my implementation.%
+In this section, I present necessary logical background, working my way up to implementing Kroy's
+formalization by the end of the section. First, Kroy's logic requires the notion of a subject, 
+which I define as a new type, just as I did for my implementation.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-Kroy also defines a substitution operator\footnote{See page 196 in \citet{kroy}.}. 
+Kroy also defines a substitution operator.\footnote{See page 196 in \citet{kroy}.}
 $P (d/e)$ is read in his logic as ``P with e substituted 
@@
 \ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlemph P\ {\isacharbraceleft}A{\isacharbraceright}\ {\isasymequiv}\ {\isasymlambda}x{\isachardot}\ P\ {\isacharbraceleft}A{\isacharparenleft}x{\isacharparenright}{\isacharbraceright}{\isachardoublequoteclose}%
-\noindent \textbf{Differences Between Kroy's Logic (Kr) and DDL}
+\begin{isamarkuptext}%
+\noindent \textbf{Differences Between Kroy's Logic (Kr) and DDL}%
+\end{isamarkuptext}\isamarkuptrue%
 %
@@
 There is potential for complication because Kroy's original paper uses a different logic than DDL. 
-His custom logic is a slight modification of Hintikka's deontic logic \citep{hintikka}. In this section, 
+His custom logic is a slight modification of Hintikka's deontic logic \citep{hintikka}. In this brief interlude, 
 I examine if the semantic properties that Kroy's logic (which I abbreviate to Kr) requires 
@@
 %
-\noindent \emph{Deontic alternatives versus the neighborhood semantics}
-%
-\begin{isamarkuptext}%
-The most faithful interpretation of Kr is that if $A$ is permissible in a context, then 
+\begin{isamarkuptext}%
+Many of the differences between Kr and DDL can be explained by a difference in their semantics. The most 
+faithful interpretation of Kr is that if $A$ is permissible in a context, then 
 it must be true at some world in that context. Kr operates under the ``deontic alternatives'' or Kripke semantics, 
-summarized by Solt \citep{solt} as follows: ``A proposition of the sort $O A$ is true at the actual world $w$ if and
-only if $A$ is true at every deontic alternative world to $w$.'' Under this view, permissible propositions
+summarized by Solt as follows: ``A proposition of the sort $O A$ is true at the actual world $w$ if and
+only if $A$ is true at every deontic alternative world to $w$''  \citep{solt}. Under this view, permissible propositions
 are obligated at some deontic alternatives, or other worlds in the system, but not at all of them. This
@@
 %
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\isatagdocument
-%
-\isamarkupsubsection{Kroy's formalization of the FUL \label{sec: kroy_ful}%
-}
-\isamarkuptrue%
-%
-\endisatagdocument
-{\isafolddocument}%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\begin{isamarkuptext}%
-I now implement Kroy's formalization of the Formula of Universal Law. Recall that the FUL says
+\begin{isamarkuptext}%
+\noindent \textbf{Kroy's formalization of the FUL \label{sec: kroy_ful}}%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+I now implement Kroy's formalization of the Formula of Universal Law. Recall that the FUL reads
 ``act only in accordance with that maxim which you can at the same time will a universal law'' \citep[34]{groundwork}.
@@
 
+\noindent \textbf{Obligations Universalize Across People}
 I already showed above that Kroy's formalization is stronger than DDL. Next, I test whether or
-not obligations universalize across people. This test passes, aperhaps trivially, due to the fact that 
+not obligations universalize across people. This test passes, perhaps trivially, due to the fact that 
 this property is definitionally the basis of Kroy's formalization; his formalization states, intuitively, 
@@
 \begin{isamarkuptext}%
-\noindent \textbf{Murder}%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-In Section \ref{sec:app_tests_naive}, I began by testing the naive interpretation's ability to show that murder 
-is wrong. I started by showing the morally dubious proposition that if murder is possibly wrong, then 
-it is actually wrong.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{consts}\isamarkupfalse%
-\ M{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isachardoublequoteclose}\isanewline
-%
-\isamarkupcmt{Let the constant $M$ denote murder. I have defined no features of this constant, except that it is 
-of the type term, which can be true or false at a set of worlds. Indeed, this constant as-is has no 
-semantic meaning and could be replaced with any symbol, like `Q' or `Going to Target.' This constant 
-will begin to take on features of the act of murder when I specify its properties. In the tests below, 
-I specify its properties as the antecedents of lemmas. For example, the test below specifies that 
-it is possible that murder is prohibited at the current world. This pattern will hold for most constants 
-defined in Isabelle—they have no meaning until I program a meaning.%
-}\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ wrong{\isacharunderscore}if{\isacharunderscore}possibly{\isacharunderscore}wrong{\isacharcolon}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}{\isasymdiamond}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ M{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ cw{\isacharparenright}\ {\isasymlongrightarrow}\ \ {\isacharparenleft}{\isasymforall}w{\isachardot}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ M{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
-%
-\isadelimproof
-\ \ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{by}\isamarkupfalse%
-\ simp\isanewline
-%
-\isamarkupcmt{This sentence reads: ``If it is possible that murder is prohibited at world cw, then murder is prohibited 
-at all worlds.%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-This is the same result we got in Section \ref{sec:app_tests_naive}—if murder is possibly wrong at some world, it is wrong at
-every world. The result is incredible strong—the mere possibility of wrongness at some world is sufficient
-to imply prohibition at $\text{every world}$.
-
-Kroy's formalization shouldn't actually imply this property. Recall that this property held in the 
-naive interpretation because it universalized a proposition across worlds (using the necessity operator).
-Kroy, on the other hand, interprets the FUL as universalizing across $\text{people}$, not worlds. 
-In other words, Kroy's formulation implies that if murder is wrong for someone, then it is wrong for 
-everyone.
-
-The fact that this strange lemma holds is actually a property of DDL itself, not a property
-of Kroy's formalization. Indeed, repeating this experiment in DDL, with no
-additional axioms that represent the categorical imperative shows that, in DDL, if something is 
-possibly wrong, it is wrong at every world. This implies that this is not a useful example to test any formulation. 
-If a lemma is true in the base logic, without any custom axioms added, then it will hold for any set of  
-custom axioms. Testing whether or not it holds as we add axioms tells us nothing, since it held in 
-the base logic itself. Interesting cases are ones that fail (or are indeterminate) in the base logic, 
-but become true as we add axioms.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-To adapt the murder wrong axiom to capture the spirit of Kroy's formulation, I will modify if 
-to state that if murder is wrong for one person, it is wrong for everyone.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{consts}\isamarkupfalse%
-\ M{\isacharunderscore}kroy{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}os{\isachardoublequoteclose}\isanewline
-%
-\isamarkupcmt{This time, murder is an open sentence, so that I can substitute in different agents.%
-}\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ wrong{\isacharunderscore}if{\isacharunderscore}wrong{\isacharunderscore}for{\isacharunderscore}someone{\isacharcolon}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymexists}p{\isachardot}\ {\isasymTurnstile}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}{\isacharparenleft}M{\isacharunderscore}kroy\ p{\isacharparenright}{\isacharbraceright}{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ {\isasymTurnstile}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}{\isacharparenleft}M{\isacharunderscore}kroy\ p{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-%
-\isadelimproof
-\ \ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{proof}\isamarkupfalse%
-\ \isanewline
-\ \ \ \ \isacommand{assume}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymexists}p{\isachardot}\ {\isasymTurnstile}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}{\isacharparenleft}M{\isacharunderscore}kroy\ p{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-\ \ \ \ \isacommand{show}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymforall}p{\isachardot}\ {\isasymTurnstile}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}{\isacharparenleft}M{\isacharunderscore}kroy\ p{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-\ \ \ \ \ \ \isacommand{using}\isamarkupfalse%
-\ FUL\ {\isacartoucheopen}{\isasymexists}p{\isachardot}\ {\isasymTurnstile}\isactrlemph O{\isacharbraceleft}\isactrlemph {\isasymnot}M{\isacharunderscore}kroy{\isacharbraceright}\ p{\isacartoucheclose}\ \isacommand{by}\isamarkupfalse%
-\ blast\isanewline
-\ \ \isacommand{qed}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-This lemma gets to the heart of Kroy's formulation of the categorical imperative. If murder is prohibited
-for a specific person $p$, then it must be prohibited for all people\footnote{This test case also revealed a 
-bug in my original implementation of Kroy's formulation of the FUL, demonstrating the power of such 
-automated tests and precise formulations to find bugs in ethical theories.}.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-\textbf{Lying}%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-For the naive implementation, I also tested the stronger proposition that if not 
-everyone can simultaneously lie, then lying is prohibited. This is the equivalent of claiming that 
-if lying fails the universalizability test, it is prohibited.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-I want to represent the sentence``At all worlds, it is 
-      not possible that everyone lies simultaneously." This requires the following two abbreviations.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{consts}\isamarkupfalse%
-\ lie{\isacharcolon}{\isacharcolon}os%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isatagproof
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ everyone{\isacharunderscore}lies{\isacharcolon}{\isacharcolon}t\ \isakeyword{where}\ {\isachardoublequoteopen}everyone{\isacharunderscore}lies\ {\isasymequiv}\ {\isasymlambda}w{\isachardot}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ {\isacharparenleft}lie{\isacharparenleft}p{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-%
-\isamarkupcmt{This represents the term ``all people lie". Naively, we might think to represent this as $\forall p. lie(p)$.
-In HOL, the $\forall$ operator has type $('a\rightarrow bool) \rightarrow bool$, where $'a$ is a polymorphic
-type of the term being bound by $\forall$. In the given example, 
-$\forall$ has the type $(s \rightarrow bool) \rightarrow bool$, so it can only be applied to a formula 
-of type $s \rightarrow bool$. In the abbreviation above, we're applying the quantifier to a sentence 
-that takes in a given subject $p$ and returns $lie(p) w$ for any arbitrary $w$, so the types cohere.%
-}\isanewline
-%
-\isamarkupcmt{The term above is true for a set of worlds $i$ (recall that a term is true at a set of worlds) 
-such that, at all the worlds $w$ in $i$, all people at $w$ lie.%
-}\isanewline
-\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ lying{\isacharunderscore}not{\isacharunderscore}possibly{\isacharunderscore}universal{\isacharcolon}{\isacharcolon}bool\ \isakeyword{where}\ {\isachardoublequoteopen}lying{\isacharunderscore}not{\isacharunderscore}possibly{\isacharunderscore}universal\ {\isasymequiv}\ {\isasymTurnstile}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}{\isasymdiamond}\ everyone{\isacharunderscore}lies{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-%
-\isamarkupcmt{Armed with \isa{everyone{\isacharunderscore}lies\ {\isasymequiv}\ {\isasymlambda}w{\isachardot}\ {\isasymforall}p{\isachardot}\ lie\ p\ w}, it's easy to represent the desired sentence.
-The abbreviation above
-reads, ``At all worlds, it is not possible that everyone lies."%
-}%
-\begin{isamarkuptext}%
-Now that I have defined a sentence stating that lying fails the universalizability test, I can 
-      test if this sentence implies that lying is impermissible.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ lying{\isacharunderscore}prohibited{\isacharcolon}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}lying{\isacharunderscore}not{\isacharunderscore}possibly{\isacharunderscore}universal\ {\isasymlongrightarrow}\ \ {\isacharparenleft}\ {\isasymTurnstile}{\isacharparenleft}\isactrlbold {\isasymnot}\ P\ {\isacharbraceleft}lie{\isacharparenleft}p{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-\ \ \isacommand{nitpick}\isamarkupfalse%
-{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{oops}\isamarkupfalse%
-\isanewline
-%
-\isamarkupcmt{\color{blue} Nitpick found a counterexample for card i = 1 and card s = 2:
-
-  Free variables:
-
-    $\text{lying\_not\_possibly\_universal}$ = True
-
-    $p = s_1$ \color{black}%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-Kroy's formulation fails this test, and is thus not able to show that if lying is not possible 
-      to universalize, it is prohibited for an arbitrary person. To understand why this is happening, I 
-      will outline the syllogism that I $\emph{expect}$ to prove that lying is prohibited.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{enumerate}
-        \item \text{At all worlds, it is not possible for everyone to lie. (This is the assumed lemma lying\_not\_possibly\_universal)}
-        \item At all worlds, there is necessarily someone who doesn't lie. (Modal dual of (1))
-        \item If A is permissible for subject p at world w, A is possible for subject p at world w. (Modified Ought Implies Can)
-        \item If A is permissible at world w for any person p, it must be possible for everyone to A at w. (FUL and (3)) 
-        \item Lying is impermissible. (Follows from (4) and (1)) \end{enumerate}
-%
-\begin{isamarkuptext}%
-Armed with this syllogism, I can figure out why this test failed.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ step{\isadigit{2}}{\isacharcolon}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}lying{\isacharunderscore}not{\isacharunderscore}possibly{\isacharunderscore}universal\ {\isasymlongrightarrow}\ {\isasymTurnstile}{\isacharparenleft}\ {\isacharparenleft}{\isasymbox}\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymexists}p{\isachardot}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}lie{\isacharparenleft}p{\isacharparenright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharparenright}\ {\isachardoublequoteclose}\isanewline
-%
-\isadelimproof
-\ \ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{by}\isamarkupfalse%
-\ simp\isanewline
-%
-\isamarkupcmt{Step 2 holds.%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-\isanewline
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ step{\isadigit{3}}{\isacharcolon}\ \isanewline
-\ \ \isakeyword{fixes}\ A\ p\ w\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}P\ {\isacharbraceleft}A{\isacharparenleft}p{\isacharparenright}{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharparenleft}A{\isacharparenleft}p{\isacharparenright}{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
-\ \ \isacommand{nitpick}\isamarkupfalse%
-\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharbrackright}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{oops}\isamarkupfalse%
-\isanewline
-%
-\isamarkupcmt{$\color{blue}$ Nitpick found a counterexample for card `a = 1, card i = 1, and card s = 1:
-
-  Free variables:
-    A = ($\lambda x. \_$)($a_1$ := ($\lambda x. \_$)($i_1$ := False))
-    p = $a_1$ $\color{black}$%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-As we see above, the syllogism fails at Step 3, explaining why the lemma doesn't 
-        hold as expected. Kroy explicitly states\footnote{See footnote 19 on p. 199} that this lemma holds in his logic.
-
-        The success of this lemma in Kroy's logic and the emptiness of his formalization of the FUL are 
-        two errors that contribute to the failure of this test. First, the statement expressed in Step 3
-        should not actually hold. Impossible actions can be permissible (do I need a citation?). For example, 
-        imagine I make a trip to Target to 
-        purchase a folder, and they offer blue and black folders. No one would claim that it's impermissible
-        for me to purchase a red folder, or, equivalently, that I am obligated to not purchase a red folder.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-The second issue is that Kroy's interpretation of the formula of universal law is circular.
-        His formalization interprets the FUL as prohibiting A if there is someone for whom 
-        $A$'ing is not permissible. This requires some preexisting notion of the permissibility of $A$, and 
-        is thus circuar. The categorical imperative is supposed to be the complete,
-        self-contained rule of morality, but Kroy's version of the FUL prescribes obligations 
-        in a self-referencing manner. The FUL is supposed to define what is permissible and what isn't, 
-        but Kroy defines permissibility in terms of itself.
-
-        Neither of these errors are obvious from Kroy's presentation of his formalization of 
-        the categorical imperative. This example demonstrates the power of formalized ethics. Making
-        Kroy's interpretation of the categorical imperative precise demonstrated a philosophical problem 
-        with that interpretation.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\isatagdocument
-%
-\isamarkupsubsection{Metaethical Tests \label{sec:meta_tests_kroy}%
-}
-\isamarkuptrue%
-%
-\endisatagdocument
-{\isafolddocument}%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\begin{isamarkuptext}%
-In addition to testing specific applications of the theory, I am also interested in 
-        metaethical properties, as in the naive interpretation. First, I will test if permissiblility
-        is possible under this formalization.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ permissible{\isacharcolon}\isanewline
-\ \ \isakeyword{fixes}\ A\ w\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
-\ \ \isacommand{nitpick}\isamarkupfalse%
-\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharbrackright}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{oops}\isamarkupfalse%
-\isanewline
-%
-\isamarkupcmt{\color{blue}Nitpick found a model for card i = 1:
-
-  Free variable:
-    A = ($\lambda x. \_$)($i_1$ := False)\color{black}%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-The above result shows that, for some action $A$ and world $w$, Nitpick can find a model where $A$
-        is permissible at $w$. This means that the logic allows for permissible actions. If I further specify 
-        properties of $A$ (such as `$A$ is murder'), I would want this result to fail.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-Next, I will test if the formalization allows arbitrary obligations.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ arbitrary{\isacharunderscore}obligations{\isacharcolon}\isanewline
-\ \ \isakeyword{fixes}\ A{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}O\ {\isacharbraceleft}A{\isacharbraceright}\ w{\isachardoublequoteclose}\isanewline
-\ \ \isacommand{nitpick}\isamarkupfalse%
-\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharequal}true{\isacharcomma}\ falsify{\isacharbrackright}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{oops}\isamarkupfalse%
-\isanewline
-%
-\isamarkupcmt{\color{blue} Nitpick found a counterexample for card i = 1 and card s = 1:
-
-  Free variable:
-    A = ($\lambda x. \_$)($i_1$ := False) \color{blue}%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-This is exactly the expected result. Any arbitrary action $A$ isn't obligated. A slightly 
-        stronger property is ``modal collapse," or whether or not `$A$ happens' implies `$A$ is obligated'.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ modal{\isacharunderscore}collapse{\isacharcolon}\isanewline
-\ \ \isakeyword{fixes}\ A\ w\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}A\ w\ {\isasymlongrightarrow}\ O\ {\isacharbraceleft}A{\isacharbraceright}\ w{\isachardoublequoteclose}\isanewline
-\ \ \isacommand{nitpick}\isamarkupfalse%
-\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharequal}true{\isacharcomma}\ falsify{\isacharbrackright}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{oops}\isamarkupfalse%
-\isanewline
-%
-\isamarkupcmt{\color{blue} Nitpick found a counterexample for card i = 1 and card s = 1:
-
-  Free variables:
-    A = ($\lambda x. \_$)($i_1$ := True)
-    w = $i_1$ \color{black}%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-This test also passes. Next, I will test if not ought implies can holds. Recall that I 
-        showed in Section $\ref{sec:meta_tests_naive}$ that ought implies can is a theorem of DDL itself, so it should still hold.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ ought{\isacharunderscore}implies{\isacharunderscore}can{\isacharcolon}\isanewline
-\ \ \isakeyword{fixes}\ A\ w\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}O\ {\isacharbraceleft}A{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ {\isasymdiamond}\ A\ w{\isachardoublequoteclose}\isanewline
-%
-\isadelimproof
-\ \ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{using}\isamarkupfalse%
-\ O{\isacharunderscore}diamond\ \isacommand{by}\isamarkupfalse%
-\ blast%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-This theorem holds. Now that I have a substitution operation, I also expect that if an action 
-      is obligated for a person, then it is possible for that person. That should follow by the 
-      axiom of substitution \cite{cresswell} which lets me replace the `A' in the formula above with 
-      `A(p)'%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ ought{\isacharunderscore}implies{\isacharunderscore}can{\isacharunderscore}person{\isacharcolon}\isanewline
-\ \ \isakeyword{fixes}\ A\ w\ \isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}O\ {\isacharbraceleft}\ A{\isacharparenleft}p{\isacharparenright}{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ {\isasymdiamond}\ {\isacharparenleft}A\ {\isacharparenleft}p{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
-%
-\isadelimproof
-\ \ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{using}\isamarkupfalse%
-\ O{\isacharunderscore}diamond\ \isacommand{by}\isamarkupfalse%
-\ blast%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-This test also passes. Next, I will explore whether or not Kroy's formalization still allows 
-      conflicting obligations.%
+\noindent \textbf{Obligations Universalize Across People} The next test verifies that obligations 
+cannot contradict. Kroy's formalization fails this test
+because Nitpick can find a model in which $A$ and $\neg A$ are both obligated.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-Just as with the naive formalization, Kroy's formalization allows for contradictory obligations. 
-        Testing this lemma in DDL without the FUL shows that this is a property of DDL itself. This is a good goal to have in mind when 
-        developing my custom formalization.
-
-        Next, I will test the stronger property that if two maxims imply a
-        contradiction, they may not be simultaneously willed.%
+Recall the stronger version of this property: if two maxims imply a
+        contradiction, they may not be simultaneously obligated. This test also fails for Kroy's formalization.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-Just as with the naive formalization, Kroy's formalization allows implied contradictions because 
-        DDL itself allows implied contradictions and Kroy's 
-        formalization doesn't do anything to remedy this.
-
-      Next, I will test that an action is either obligatory, permissible, or 
-      prohibited.%
+\noindent \textbf{Distributive Property for Obligations} Next, I test the closely related 
+distributive property for obligations. As expected, this property also fails, since it is a derivative 
+of contradictory obligations.%
 \end{isamarkuptext}\isamarkuptrue%
 \isacommand{lemma}\isamarkupfalse%
-\ ob{\isacharunderscore}perm{\isacharunderscore}or{\isacharunderscore}prohibited{\isacharcolon}\isanewline
-\ \ \isakeyword{fixes}\ A\ w\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymor}\ {\isacharparenleft}P\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymor}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
+\ distributive{\isacharunderscore}property{\isacharcolon}\isanewline
+\ \ \isakeyword{fixes}\ A\ B\ w\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}O\ {\isacharbraceleft}A\ \isactrlbold {\isasymand}\ B{\isacharbraceright}\ w\ {\isasymequiv}\ O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymand}\ O\ {\isacharbraceleft}B{\isacharbraceright}\ w{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{\color{blue}Nitpick found a counterexample for card i = 2 and card s = 1:
+
+  Free variables:
+    A = ($\lambda x. \_$)($i_1$ := False, $i_2$ := True)
+    B = ($\lambda x. \_$)($i_1$ := True, $i_2$ := False) \color{black}%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+\noindent \textbf{Prohibits Actions That Are Impossible to Universalize} Next, I test if Kroy's
+formalization is strong enough to prohibit actions that are impossible to universalize. As when running
+this test for my formalization, I need to define some logical background to run this test. I 
+use lying as a toy example of an action that is impossible to universalize.
+
+To run this test, I epresent the sentence ``At all worlds, it is 
+not possible that everyone lies simultaneously,'' in my logic. This requires the following abbreviations.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{consts}\isamarkupfalse%
+\ lie{\isacharcolon}{\isacharcolon}os\ \isanewline
+%
+\isamarkupcmt{This is an empty constant to represent the act of lying, which is an open sentence. Unlike Chapter 
+\ref{applications}, I do not specify any properties of lying, so this could be replaced with any 
+action that is impossible to universalize.%
+}\isanewline
+\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ everyone{\isacharunderscore}lies{\isacharcolon}{\isacharcolon}t\ \isakeyword{where}\ {\isachardoublequoteopen}everyone{\isacharunderscore}lies\ {\isasymequiv}\ {\isasymlambda}w{\isachardot}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ {\isacharparenleft}lie{\isacharparenleft}p{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{This represents the term ``all people lie".%
+}\isanewline
+%
+\isamarkupcmt{The term above is true for a set of worlds $i$ such that, at all the worlds $w$ in $i$, all people 
+at $w$ lie.%
+}\isanewline
+\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ lying{\isacharunderscore}not{\isacharunderscore}possibly{\isacharunderscore}universal{\isacharcolon}{\isacharcolon}bool\ \isakeyword{where}\ {\isachardoublequoteopen}lying{\isacharunderscore}not{\isacharunderscore}possibly{\isacharunderscore}universal\ {\isasymequiv}\ {\isasymTurnstile}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}{\isasymdiamond}\ everyone{\isacharunderscore}lies{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Armed with \isa{everyone{\isacharunderscore}lies\ {\isasymequiv}\ {\isasymlambda}w{\isachardot}\ {\isasymforall}p{\isachardot}\ lie\ p\ w}, it's easy to represent the desired sentence.
+The abbreviation above
+reads, ``At all worlds, it is not possible that everyone lies."%
+}%
+\begin{isamarkuptext}%
+With this logical background, I can test if lying not being possible to universalize implies 
+that it is prohibited. Surprisingly, Kroy's formalization fails this test.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ lying{\isacharunderscore}prohibited{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}lying{\isacharunderscore}not{\isacharunderscore}possibly{\isacharunderscore}universal\ {\isasymlongrightarrow}\ \ {\isacharparenleft}\ {\isasymTurnstile}{\isacharparenleft}\isactrlbold {\isasymnot}\ P\ {\isacharbraceleft}lie{\isacharparenleft}p{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{nitpick}\isamarkupfalse%
+{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{\color{blue} Nitpick found a counterexample for card i = 1 and card s = 2:
+
+  Free variables:
+
+    $\text{lying\_not\_possibly\_universal}$ = True
+
+    $p = s_1$ \color{black}%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+Kroy's formalization is not able to show that if lying is not possible 
+      to universalize, it is prohibited. This is unexpected—Kroy's formalization seemingly hinges
+on universalizability, so it seems as though it should pass this test. To understand this, I 
+  outline the syllogism that one might $\emph{expect}$ to prove that lying is prohibited and will 
+test each component of this syllogism in Isabelle.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+\begin{enumerate}
+        \item At all worlds, it is not possible for everyone to lie. \emph{(This is the assumed sentence.)}
+        \item At all worlds, there is necessarily someone who doesn't lie. \emph{(Modal dual of (1))}
+        \item If A is permissible for subject p at world w, A is possible for subject p at world w. \emph{(Modified Ought Implies Can)}
+        \item If A is permissible at world w for any person p, it must be possible for everyone to A at w. \emph{(FUL and (3))}
+        \item Lying is impermissible. \emph{(Follows from (4) and (1))} \end{enumerate}%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+I now test each step of this syllogism to determine where Kroy's formalize deviates from the
+expected results. Step 1 holds by assumption, and Step 2 holds as shown below, but the syllogism breaks down
+at Step 3.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ step{\isadigit{2}}{\isacharcolon}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}lying{\isacharunderscore}not{\isacharunderscore}possibly{\isacharunderscore}universal\ {\isasymlongrightarrow}\ {\isasymTurnstile}{\isacharparenleft}\ {\isacharparenleft}{\isasymbox}\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymexists}p{\isachardot}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}lie{\isacharparenleft}p{\isacharparenright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharparenright}\ {\isachardoublequoteclose}\isanewline
 %
@@
 %
-\isamarkupcmt{This test passes.%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-I also expect obligation to be a strictly stronger property than permissibility. Particularly, 
-if A is obligated, then A should also be permissible.%
-\end{isamarkuptext}\isamarkuptrue%
+\isamarkupcmt{Step 2 holds.%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+\isanewline
+%
+\endisadelimproof
+\isanewline
 \isacommand{lemma}\isamarkupfalse%
-\ obligated{\isacharunderscore}then{\isacharunderscore}permissible{\isacharcolon}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymrightarrow}\ P\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
+\ step{\isadigit{3}}{\isacharcolon}\ \isanewline
+\ \ \isakeyword{fixes}\ A\ p\ w\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}P\ {\isacharbraceleft}A{\isacharparenleft}p{\isacharparenright}{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharparenleft}A{\isacharparenleft}p{\isacharparenright}{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
 \ \ \isacommand{nitpick}\isamarkupfalse%
-{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
+\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharbrackright}%
 \isadelimproof
@@
 %
-\isamarkupcmt{This test fails in Kroy's interpretation!
-\color{blue}Nitpick found a counterexample for card i = 2 and card s = 1:
-
-  Free variable:
-    A = ($\lambda x. \_$)($i_1$ := False, $i_2$ := True)\color{black}%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isatagproof
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-These tests show that, while Kroy's formalization is more powerful and more coherent than the naive formalization, it 
-      still fails to capture most of the desired properties of the categorical imperative. Some of these 
-      problems may be remedied by the fact that Kroy's logic doesn't allow contradictory obligations, 
-      and that possibility will be interesting to explore in my own formalization.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\isatagdocument
-%
-\isamarkupsubsection{Miscellaneous Tests \label{sec: misc_tests_kroy}%
-}
-\isamarkuptrue%
-%
-\endisatagdocument
-{\isafolddocument}%
-%
-\isadelimdocument
-%
-\endisadelimdocument
-%
-\begin{isamarkuptext}%
-In this section, I explore tests of properties that Kroy presents in his original paper. These 
-tests not only test the features of the system that Kroy intended to highlight, but they may also 
-inspire additional tests and criteria for my own formalization in Chapter 3. These tests further underscore 
-the circularity of Kroy's formalization and the differences between my logic and his.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-First, Kroy presents a stronger version of the formula of universal law and argues that his formalization
-is implied by the stronger version. Let's test that claim.%
+\isamarkupcmt{$\color{blue}$ Nitpick found a counterexample for card `a = 1, card i = 1, and card s = 1:
+
+  Free variables:
+    A = ($\lambda x. \_$)($a_1$ := ($\lambda x. \_$)($i_1$ := False))
+    p = $a_1$ $\color{black}$%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+The above lemma shows that the syllogism fails at Step 3, explaining why the lemma doesn't 
+        hold as expected. Kroy explicitly states\footnote{See footnote 19 on p. 199 of \citet{kroy}} that 
+        Step 3 holds in his logic, so this failure may be explained by this difference in Kr and DDL.
+        However, upon reflection, it is not clear that the statement expressed in Step 3 should actually hold.
+        Step 3 states that all permissible actions must be possible, but this implies that impossible
+        actions are not permissible, so they must be prohibited, which seems silly. For example, 
+        imagine I make a trip to Target to purchase a folder, and they offer blue and black folders. 
+        Even though it is impossible for me to purchase a red folder, it doesn't seem impermissible
+        for me to purchase a red folder.
+
+        A deeper issue inspired by this test is that Kroy's interpretation of the FUL is 
+        empty in a circular way. His formalization interprets the FUL as prohibiting $A$ if there is someone for whom 
+        $A$'ing is not permissible. This requires some preexisting notion of the permissibility of $A$, and 
+        is thus circuar. The categorical imperative is supposed to be the complete,
+        self-contained rule of morality, but Kroy's version of the FUL prescribes obligations 
+        in a self-referencing manner. The FUL is supposed to define what is permissible and what isn't, 
+        but Kroy defines permissibility in terms of itself.
+
+        Neither of these errors are obvious from Kroy's presentation of his formalization of 
+        the categorical imperative. This is another example of the power of computational ethics. Making
+        Kroy's interpretation of the categorical imperative precise demonstrated philosophical problems
+        with that interpretation.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+\noindent \textbf{Remaining Tests} It is clear that Kroy's formalization does not encode a robust conception of a maxim, as it
+simply evaluates actions. Moreover, the emptiness discussed above implies that Kroy's formalization 
+cannot actually generate \emph{any} obligations from scratch, and so the formalization automatically
+fails to prohibit conventional or natural acts.
+
+Thus, this completes my testing of Kroy's formalization. While Kroy's formalization represents
+some progress over the control group (it passes the first two tests), it is clear that many limitations
+remain. My implementation passes all of the tests that Kroy's formalization fails, and thus represents
+significant progress.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+\noindent \textbf{Miscellaneous Tests} I conclude my examination of Kroy's formalization by presenting
+one more test specific to Kroy's formalization. In addition to his formalization of the FUL, Kroy also
+presents a formalization of a stronger version of the FUL and argues that his formalization is implied
+by the stronger version. I can test that claim by formalizing this stronger formalization as well.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-The difference between the stronger version and \isa{FUL\ {\isasymequiv}\ {\isasymforall}w\ A{\isachardot}\ {\isacharparenleft}{\isasymexists}p{\isachardot}\ P\ {\isacharbraceleft}A\ p{\isacharbraceright}\ w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ P\ {\isacharbraceleft}A\ p{\isacharbraceright}\ w{\isacharparenright}} is subtle.
-The consequent of FUL is ``for all people $p$,
+The difference between the strong and weak versions of the FUL is subtle. The consequent of FUL is ``for all people $p$,
 it is permissible that they $A$." The consequent of this stronger statement is ``it is permissible that 
-everyone $A$." In particular, this stronger statement requires that it is permissible for everyone to
+everyone $A$." This stronger statement requires that it is permissible for everyone to
 $A$ simultaneously. Kroy immediately rejects this version of the categorical imperative, arguing that 
@@
 in \cite{kemp} and in \cite{KorsgaardFUL}. Lying fails the universalizability test because in a 
-world where everyone lied simultaneously, the practice of lying would break down. If we adopt Kroy's 
+world where everyone lies simultaneously, the practice of lying would break down. If we adopt Kroy's 
 version, lying is only prohibited if, no matter who lies, lying is impermissible. As argued above, this 
 rule circularly relies on some existing prohibition against lying for a particular person, and thus 
-fails to show the wrongness of lying. It is tempting to claim that this issue explains why the tests 
-above failed. To test this hypothesis, I will check if the stronger version 
-of the FUL implies that lying is impermissible.%
+fails to show the wrongness of lying.
+
+This misunderstanding is actually related to another weakness of Kroy's formalization: it lacks
+a robust conception of a maxim. Consider Kroy's example of the maxim of running for president. If the 
+action being evaluated is, ``I will be president of the United States,'' as Kroy interprets it, then 
+it is clearly not universalizable for the reason he argued. However, using the most robust circumstance,
+act, tuple representation of a maxim, the maxim of action would be something like, ``When I believe 
+that I would make a good president, I will launch a presidential campaign to become president.'' This 
+more nuanced maxim is universalizable: it is clearly possible for all people who believe they would
+make good presidents to run for president. Under this more sophisticated representation of a maxim, 
+Kroy's stronger version of the FUL is actually correct.
+
+It is tempting to claim that this issue explains why the tests above failed. To test this hypothesis, 
+I check if the stronger version of the FUL implies that lying is impermissible. Sadly, even the stronger
+version of the FUL fails this test.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \ \ \isakeyword{fixes}\ p\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}FUL{\isacharunderscore}strong\ {\isasymlongrightarrow}\ {\isasymTurnstile}{\isacharparenleft}\isactrlbold {\isasymnot}\ P\ {\isacharbraceleft}lie{\isacharparenleft}p{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}FUL{\isacharunderscore}strong\ {\isasymand}\ lying{\isacharunderscore}not{\isacharunderscore}possibly{\isacharunderscore}universal\ {\isasymlongrightarrow}\ {\isasymTurnstile}{\isacharparenleft}\isactrlbold {\isasymnot}\ P\ {\isacharbraceleft}lie{\isacharparenleft}p{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
 \ \ \isacommand{nitpick}\isamarkupfalse%
@@
     p = $s_1$
+   Skolem constant:
+    $\lambda y$. p = ($\lambda x. \_$)($i_1$ := $s_2$)
 \color{black}%
@@
 \begin{isamarkuptext}%
-The test above also fails! This means that not even the stronger version of Kroy's formalization
+The failure of this test implies that not even the stronger version of Kroy's formalization
         of the FUL can show the wrongness of lying. As mentioned earlier, there are two independent errors. The first is the 
         the assumption that impossible actions are impermissible and the second is the circularity of the 
-        formalization. The stronger FUL addresses the second error, but the first remains.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-Kroy also argues that the FUL gives us recipes for deriving obligations, in addition to deriving
-        permissible actions. Specifically, he presents the following two principles, which are equivalent 
-        in his logic. These sentences parallel FUL and strong FUL.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ obligation{\isacharunderscore}universal{\isacharunderscore}weak{\isacharcolon}{\isacharcolon}bool\ \isakeyword{where}\ {\isachardoublequoteopen}obligation{\isacharunderscore}universal{\isacharunderscore}weak\ {\isasymequiv}\ {\isasymforall}w\ A{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isasymexists}p{\isacharcolon}{\isacharcolon}s{\isachardot}\ {\isacharparenleft}{\isacharparenleft}O\ {\isacharbraceleft}A\ p{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}\ \ {\isasymlongrightarrow}{\isacharparenleft}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ {\isacharparenleft}\ O\ {\isacharbraceleft}A\ p\ {\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ obligation{\isacharunderscore}universal{\isacharunderscore}strong{\isacharcolon}{\isacharcolon}bool\ \isakeyword{where}\ {\isachardoublequoteopen}obligation{\isacharunderscore}universal{\isacharunderscore}strong\ {\isasymequiv}\ {\isasymforall}w\ A{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isasymexists}p{\isacharcolon}{\isacharcolon}s{\isachardot}\ {\isacharparenleft}{\isacharparenleft}O\ {\isacharbraceleft}A\ p{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}\ \ {\isasymlongrightarrow}{\isacharparenleft}\ {\isacharparenleft}{\isacharparenleft}\ O\ {\isacharbraceleft}\ {\isasymlambda}x{\isachardot}\ {\isasymforall}p{\isachardot}\ A\ p\ x{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-%
-\isamarkupcmt{Just as with FUL and FUL strong, the weaker version of the above statement has the consequent, ``For all people, 
-A is obligated." The stronger consequent is ``A is obligated for all people simultaneously."%
-}\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ weak{\isacharunderscore}equiv{\isacharunderscore}strong{\isacharcolon}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}obligation{\isacharunderscore}universal{\isacharunderscore}weak\ {\isasymequiv}\ obligation{\isacharunderscore}universal{\isacharunderscore}strong{\isachardoublequoteclose}\isanewline
-%
-\isadelimproof
-\ \ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{oops}\isamarkupfalse%
-\isanewline
-%
-\isamarkupcmt{Isabelle is neither able to find a proof nor a countermodel for the statement above, so I can't say 
-  if it holds or not without completing a full, manual proof. This aside is not very relevant to 
-  my project, so I will defer such a proof.%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-These two statements are not necessarily equivalent in my logic, but are in Kroy's$\footnote{This follows from
-        the fact that the Barcan formula holds in Kroy's logic but not in mine, as verified with Nitpick. See 
-        Appendix for more.}$ This difference in logics may further explain why tests are not behaving as 
-        they should. Nonetheless, Kroy argues that the FUL implies both statements above.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ FUL{\isacharunderscore}implies{\isacharunderscore}ob{\isacharunderscore}weak{\isacharcolon}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}FUL\ {\isasymlongrightarrow}\ obligation{\isacharunderscore}universal{\isacharunderscore}weak{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{oops}\isamarkupfalse%
-\isanewline
-%
-\isamarkupcmt{Isabelle is neither able to find a proof nor a countermodel for this statement.%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ FUL{\isacharunderscore}implies{\isacharunderscore}ob{\isacharunderscore}strong{\isacharcolon}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}FUL\ {\isasymlongrightarrow}\ obligation{\isacharunderscore}universal{\isacharunderscore}strong{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{oops}\isamarkupfalse%
-\isanewline
-%
-\isamarkupcmt{Isabelle is neither able to find a proof nor a countermodel for this statement.%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-Isabelle timed out when looking for proofs or countermodels to the statements above. This may be 
-        an indication of a problem that Benzmueller warned me about—mixing quantifiers into a shallow
-        embedding of DDL may be too expensive for Isabelle to handle. Not sure what to do about this.%
+        formalization. The stronger FUL addresses the second error, but the first remains, and so the
+        stonger formalization of the FUL still fails this test.
+
+        \newpage%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %:%106=60%:%
-%:%141=89%:%
-%:%153=91%:%
-%:%154=92%:%
-%:%155=93%:%
-%:%156=94%:%
-%:%157=95%:%
-%:%166=97%:%
-%:%178=99%:%
-%:%179=100%:%
-%:%181=102%:%
-%:%182=102%:%
-%:%183=102%:%
-%:%186=104%:%
-%:%187=105%:%
-%:%188=106%:%
-%:%189=107%:%
-%:%190=108%:%
-%:%191=109%:%
-%:%193=111%:%
-%:%194=111%:%
-%:%196=112%:%
-%:%197=112%:%
-%:%199=113%:%
-%:%200=114%:%
-%:%203=116%:%
-%:%204=117%:%
-%:%205=118%:%
-%:%206=119%:%
-%:%208=121%:%
-%:%209=121%:%
-%:%210=122%:%
-%:%211=123%:%
-%:%212=123%:%
-%:%213=124%:%
-%:%214=125%:%
-%:%215=125%:%
-%:%216=126%:%
-%:%217=127%:%
-%:%218=127%:%
-%:%219=128%:%
-%:%221=130%:%
-%:%222=131%:%
-%:%223=132%:%
-%:%225=134%:%
-%:%226=134%:%
-%:%227=135%:%
-%:%228=136%:%
-%:%229=136%:%
-%:%230=137%:%
-%:%231=139%:%
-%:%234=141%:%
-%:%235=142%:%
-%:%236=143%:%
-%:%237=144%:%
-%:%238=145%:%
-%:%239=146%:%
-%:%240=147%:%
-%:%243=149%:%
-%:%246=151%:%
-%:%247=152%:%
-%:%248=153%:%
-%:%249=154%:%
-%:%250=155%:%
-%:%251=156%:%
-%:%253=158%:%
-%:%254=158%:%
-%:%255=159%:%
-%:%256=160%:%
-%:%257=161%:%
-%:%258=161%:%
-%:%260=161%:%
-%:%264=161%:%
-%:%265=161%:%
-%:%267=162%:%
-%:%268=163%:%
-%:%269=164%:%
-%:%270=165%:%
-%:%280=167%:%
-%:%281=168%:%
-%:%282=169%:%
-%:%283=170%:%
-%:%284=171%:%
-%:%285=172%:%
-%:%286=173%:%
-%:%287=174%:%
-%:%288=175%:%
-%:%289=176%:%
-%:%291=178%:%
-%:%292=178%:%
-%:%293=179%:%
-%:%294=180%:%
-%:%295=181%:%
-%:%296=181%:%
-%:%298=181%:%
-%:%302=181%:%
-%:%303=181%:%
-%:%305=182%:%
-%:%306=183%:%
-%:%307=184%:%
-%:%308=185%:%
-%:%318=187%:%
-%:%319=188%:%
-%:%320=189%:%
-%:%321=190%:%
-%:%322=191%:%
-%:%323=192%:%
-%:%324=193%:%
-%:%325=194%:%
-%:%326=195%:%
-%:%328=197%:%
-%:%329=197%:%
-%:%330=198%:%
-%:%331=199%:%
-%:%332=200%:%
-%:%333=200%:%
-%:%335=200%:%
-%:%339=200%:%
-%:%340=200%:%
-%:%342=201%:%
-%:%343=202%:%
-%:%344=203%:%
-%:%345=204%:%
-%:%355=206%:%
-%:%356=207%:%
-%:%378=233%:%
-%:%390=235%:%
-%:%391=236%:%
-%:%392=237%:%
-%:%393=238%:%
-%:%394=239%:%
-%:%396=242%:%
-%:%397=242%:%
-%:%399=243%:%
-%:%400=244%:%
-%:%401=245%:%
-%:%404=247%:%
-%:%405=248%:%
-%:%407=250%:%
-%:%408=250%:%
-%:%409=251%:%
-%:%410=252%:%
-%:%411=252%:%
-%:%413=252%:%
-%:%417=252%:%
-%:%418=252%:%
-%:%420=253%:%
-%:%421=254%:%
-%:%422=255%:%
-%:%423=256%:%
-%:%424=257%:%
-%:%425=258%:%
-%:%433=258%:%
-%:%434=259%:%
-%:%435=260%:%
-%:%436=260%:%
-%:%438=262%:%
-%:%439=263%:%
-%:%441=265%:%
-%:%442=265%:%
-%:%443=265%:%
-%:%445=265%:%
-%:%449=265%:%
-%:%450=265%:%
-%:%452=266%:%
-%:%453=267%:%
-%:%454=268%:%
-%:%455=269%:%
-%:%465=271%:%
-%:%466=272%:%
-%:%467=273%:%
-%:%468=274%:%
-%:%477=276%:%
-%:%489=278%:%
-%:%490=279%:%
-%:%491=280%:%
-%:%492=281%:%
-%:%493=282%:%
-%:%494=283%:%
-%:%495=284%:%
-%:%496=285%:%
-%:%497=286%:%
-%:%498=287%:%
-%:%500=289%:%
-%:%501=289%:%
-%:%502=290%:%
-%:%503=291%:%
-%:%504=291%:%
-%:%506=291%:%
-%:%510=291%:%
-%:%520=293%:%
-%:%524=295%:%
-%:%525=296%:%
-%:%526=297%:%
-%:%528=299%:%
-%:%529=299%:%
-%:%531=300%:%
-%:%532=301%:%
-%:%533=302%:%
-%:%534=303%:%
-%:%535=304%:%
-%:%536=305%:%
-%:%537=306%:%
-%:%538=306%:%
-%:%539=307%:%
-%:%540=308%:%
-%:%541=308%:%
-%:%542=309%:%
-%:%545=310%:%
-%:%549=310%:%
-%:%550=310%:%
-%:%552=311%:%
-%:%553=312%:%
-%:%563=314%:%
-%:%564=315%:%
-%:%565=316%:%
-%:%566=317%:%
-%:%567=318%:%
-%:%568=319%:%
-%:%569=320%:%
-%:%570=321%:%
-%:%571=322%:%
-%:%572=323%:%
-%:%573=324%:%
-%:%574=325%:%
-%:%575=326%:%
-%:%576=327%:%
-%:%577=328%:%
-%:%578=329%:%
-%:%579=330%:%
-%:%580=331%:%
-%:%584=333%:%
-%:%585=334%:%
-%:%587=336%:%
-%:%588=336%:%
-%:%590=337%:%
-%:%591=337%:%
-%:%592=338%:%
-%:%593=339%:%
-%:%594=339%:%
-%:%595=340%:%
-%:%598=341%:%
-%:%602=341%:%
-%:%603=341%:%
-%:%604=342%:%
-%:%605=342%:%
-%:%606=343%:%
-%:%607=343%:%
-%:%608=344%:%
-%:%609=344%:%
-%:%610=344%:%
-%:%611=345%:%
-%:%621=347%:%
-%:%622=348%:%
-%:%623=349%:%
-%:%624=350%:%
-%:%628=352%:%
-%:%632=354%:%
-%:%633=355%:%
-%:%634=356%:%
-%:%638=358%:%
-%:%639=359%:%
-%:%641=361%:%
-%:%642=361%:%
-%:%655=382%:%
-%:%656=383%:%
-%:%657=383%:%
-%:%659=384%:%
-%:%660=385%:%
-%:%661=386%:%
-%:%662=387%:%
-%:%663=388%:%
-%:%664=389%:%
-%:%665=389%:%
-%:%667=390%:%
-%:%668=391%:%
-%:%669=391%:%
-%:%670=392%:%
-%:%671=393%:%
-%:%672=393%:%
-%:%674=394%:%
-%:%675=395%:%
-%:%678=397%:%
-%:%679=398%:%
-%:%681=400%:%
-%:%682=400%:%
-%:%683=401%:%
-%:%684=402%:%
-%:%685=402%:%
-%:%687=402%:%
-%:%691=402%:%
-%:%692=402%:%
-%:%694=403%:%
-%:%695=404%:%
-%:%696=405%:%
-%:%697=406%:%
-%:%698=407%:%
-%:%699=408%:%
-%:%700=409%:%
-%:%710=411%:%
-%:%711=412%:%
-%:%712=413%:%
-%:%715=415%:%
-%:%716=416%:%
-%:%717=417%:%
-%:%718=418%:%
-%:%719=419%:%
-%:%720=420%:%
-%:%723=422%:%
-%:%725=424%:%
-%:%726=424%:%
-%:%727=425%:%
-%:%730=426%:%
-%:%734=426%:%
-%:%735=426%:%
-%:%737=427%:%
-%:%743=427%:%
-%:%746=428%:%
-%:%747=429%:%
-%:%748=429%:%
-%:%749=430%:%
-%:%750=431%:%
-%:%751=432%:%
-%:%752=432%:%
-%:%754=432%:%
-%:%758=432%:%
-%:%759=432%:%
-%:%761=433%:%
-%:%762=434%:%
-%:%763=435%:%
-%:%764=436%:%
-%:%765=437%:%
-%:%775=439%:%
-%:%776=440%:%
-%:%777=441%:%
-%:%778=442%:%
-%:%779=443%:%
-%:%780=444%:%
-%:%781=445%:%
-%:%782=446%:%
-%:%783=447%:%
-%:%787=450%:%
-%:%788=451%:%
-%:%789=452%:%
-%:%790=453%:%
-%:%791=454%:%
-%:%792=455%:%
-%:%793=456%:%
-%:%794=457%:%
-%:%795=458%:%
-%:%796=459%:%
-%:%797=460%:%
-%:%798=461%:%
-%:%807=463%:%
-%:%819=465%:%
-%:%820=466%:%
-%:%821=467%:%
-%:%823=469%:%
-%:%824=469%:%
-%:%825=470%:%
-%:%826=471%:%
-%:%827=472%:%
-%:%828=472%:%
-%:%830=472%:%
-%:%834=472%:%
-%:%835=472%:%
-%:%837=473%:%
-%:%838=474%:%
-%:%839=475%:%
-%:%840=476%:%
-%:%850=478%:%
-%:%851=479%:%
-%:%852=480%:%
-%:%856=482%:%
-%:%858=484%:%
-%:%859=484%:%
-%:%860=485%:%
-%:%861=486%:%
-%:%862=487%:%
-%:%863=487%:%
-%:%865=487%:%
-%:%869=487%:%
-%:%870=487%:%
-%:%872=488%:%
-%:%873=489%:%
-%:%874=490%:%
-%:%875=491%:%
-%:%885=493%:%
-%:%886=494%:%
-%:%888=496%:%
-%:%889=496%:%
-%:%890=497%:%
-%:%891=498%:%
-%:%892=499%:%
-%:%893=499%:%
-%:%895=499%:%
-%:%899=499%:%
-%:%900=499%:%
-%:%902=500%:%
-%:%903=501%:%
-%:%904=502%:%
-%:%905=503%:%
-%:%906=504%:%
-%:%916=506%:%
-%:%917=507%:%
-%:%919=509%:%
-%:%920=509%:%
-%:%921=510%:%
-%:%922=511%:%
-%:%925=512%:%
-%:%929=512%:%
-%:%930=512%:%
-%:%931=512%:%
-%:%940=514%:%
-%:%941=515%:%
-%:%942=516%:%
-%:%943=517%:%
-%:%945=519%:%
-%:%946=519%:%
-%:%947=520%:%
-%:%948=521%:%
-%:%951=522%:%
-%:%955=522%:%
-%:%956=522%:%
-%:%957=522%:%
-%:%966=524%:%
-%:%967=525%:%
-%:%969=527%:%
-%:%970=527%:%
-%:%971=528%:%
-%:%972=529%:%
-%:%973=530%:%
-%:%974=530%:%
-%:%976=530%:%
-%:%980=530%:%
-%:%981=530%:%
-%:%983=531%:%
-%:%984=532%:%
-%:%985=533%:%
-%:%986=534%:%
-%:%996=536%:%
-%:%997=537%:%
-%:%998=538%:%
-%:%999=539%:%
-%:%1000=540%:%
-%:%1001=541%:%
-%:%1003=543%:%
-%:%1004=543%:%
-%:%1005=544%:%
-%:%1006=545%:%
-%:%1007=546%:%
-%:%1008=547%:%
-%:%1009=547%:%
-%:%1011=547%:%
-%:%1015=547%:%
-%:%1016=547%:%
-%:%1018=548%:%
-%:%1019=549%:%
-%:%1020=550%:%
-%:%1021=551%:%
-%:%1022=552%:%
-%:%1023=553%:%
-%:%1033=555%:%
-%:%1034=556%:%
-%:%1035=557%:%
-%:%1036=558%:%
-%:%1037=559%:%
-%:%1038=560%:%
-%:%1040=562%:%
-%:%1041=562%:%
-%:%1042=563%:%
-%:%1043=564%:%
-%:%1046=565%:%
-%:%1050=565%:%
-%:%1051=565%:%
-%:%1053=566%:%
-%:%1063=568%:%
-%:%1064=569%:%
-%:%1066=570%:%
-%:%1067=570%:%
-%:%1068=571%:%
-%:%1069=572%:%
-%:%1070=572%:%
-%:%1072=572%:%
-%:%1076=572%:%
-%:%1077=572%:%
-%:%1079=573%:%
-%:%1080=574%:%
-%:%1081=575%:%
-%:%1082=576%:%
-%:%1083=577%:%
-%:%1106=583%:%
-%:%1107=584%:%
-%:%1108=585%:%
-%:%1109=586%:%
-%:%1118=588%:%
-%:%1130=590%:%
-%:%1131=591%:%
-%:%1132=592%:%
-%:%1133=593%:%
-%:%1137=595%:%
-%:%1138=596%:%
-%:%1140=598%:%
-%:%1141=598%:%
-%:%1142=599%:%
-%:%1143=600%:%
-%:%1144=600%:%
-%:%1145=601%:%
-%:%1148=602%:%
-%:%1152=602%:%
-%:%1153=602%:%
-%:%1154=602%:%
-%:%1156=603%:%
-%:%1157=604%:%
-%:%1167=606%:%
-%:%1168=607%:%
-%:%1169=608%:%
-%:%1170=609%:%
-%:%1171=610%:%
-%:%1172=611%:%
-%:%1173=612%:%
-%:%1174=613%:%
-%:%1175=614%:%
-%:%1176=615%:%
-%:%1177=616%:%
-%:%1178=617%:%
-%:%1179=618%:%
-%:%1180=619%:%
-%:%1181=620%:%
-%:%1183=622%:%
-%:%1184=622%:%
-%:%1185=623%:%
-%:%1186=624%:%
-%:%1187=625%:%
-%:%1188=625%:%
-%:%1190=625%:%
-%:%1194=625%:%
-%:%1195=625%:%
-%:%1197=626%:%
-%:%1198=627%:%
-%:%1199=628%:%
-%:%1200=629%:%
-%:%1201=630%:%
-%:%1202=631%:%
-%:%1212=633%:%
-%:%1213=634%:%
-%:%1214=635%:%
-%:%1215=636%:%
-%:%1219=638%:%
-%:%1220=639%:%
-%:%1221=640%:%
-%:%1223=642%:%
-%:%1224=642%:%
-%:%1225=643%:%
-%:%1226=643%:%
-%:%1228=644%:%
-%:%1229=645%:%
-%:%1230=645%:%
-%:%1231=646%:%
-%:%1232=647%:%
-%:%1233=647%:%
-%:%1234=648%:%
-%:%1237=649%:%
-%:%1241=649%:%
-%:%1242=649%:%
-%:%1244=650%:%
-%:%1245=651%:%
-%:%1246=652%:%
-%:%1256=654%:%
-%:%1257=655%:%
-%:%1258=656%:%
-%:%1259=657%:%
-%:%1261=659%:%
-%:%1262=659%:%
-%:%1263=660%:%
-%:%1265=660%:%
-%:%1269=660%:%
-%:%1270=660%:%
-%:%1272=661%:%
-%:%1280=661%:%
-%:%1281=662%:%
-%:%1282=663%:%
-%:%1283=663%:%
-%:%1284=664%:%
-%:%1286=664%:%
-%:%1290=664%:%
-%:%1291=664%:%
-%:%1293=665%:%
-%:%1303=667%:%
-%:%1304=668%:%
-%:%1305=669%:%
-%:%1313=671%:%
+%:%107=61%:%
+%:%108=62%:%
+%:%117=65%:%
+%:%129=67%:%
+%:%130=68%:%
+%:%131=69%:%
+%:%132=70%:%
+%:%133=71%:%
+%:%142=73%:%
+%:%154=75%:%
+%:%155=76%:%
+%:%156=77%:%
+%:%158=79%:%
+%:%159=79%:%
+%:%160=79%:%
+%:%163=81%:%
+%:%164=82%:%
+%:%165=83%:%
+%:%166=84%:%
+%:%167=85%:%
+%:%168=86%:%
+%:%170=88%:%
+%:%171=88%:%
+%:%173=89%:%
+%:%174=89%:%
+%:%176=90%:%
+%:%177=91%:%
+%:%180=93%:%
+%:%181=94%:%
+%:%182=95%:%
+%:%183=96%:%
+%:%185=98%:%
+%:%186=98%:%
+%:%187=99%:%
+%:%188=100%:%
+%:%189=100%:%
+%:%190=101%:%
+%:%191=102%:%
+%:%192=102%:%
+%:%193=103%:%
+%:%194=104%:%
+%:%195=104%:%
+%:%196=105%:%
+%:%198=107%:%
+%:%199=108%:%
+%:%200=109%:%
+%:%202=111%:%
+%:%203=111%:%
+%:%204=112%:%
+%:%205=113%:%
+%:%206=113%:%
+%:%207=114%:%
+%:%209=116%:%
+%:%213=118%:%
+%:%214=119%:%
+%:%215=120%:%
+%:%216=121%:%
+%:%217=122%:%
+%:%218=123%:%
+%:%219=124%:%
+%:%223=126%:%
+%:%224=127%:%
+%:%225=128%:%
+%:%226=129%:%
+%:%227=130%:%
+%:%228=131%:%
+%:%229=132%:%
+%:%231=134%:%
+%:%232=134%:%
+%:%233=135%:%
+%:%234=136%:%
+%:%235=137%:%
+%:%236=137%:%
+%:%238=137%:%
+%:%242=137%:%
+%:%243=137%:%
+%:%245=138%:%
+%:%246=139%:%
+%:%247=140%:%
+%:%248=141%:%
+%:%258=143%:%
+%:%259=144%:%
+%:%260=145%:%
+%:%261=146%:%
+%:%262=147%:%
+%:%263=148%:%
+%:%264=149%:%
+%:%265=150%:%
+%:%266=151%:%
+%:%267=152%:%
+%:%269=154%:%
+%:%270=154%:%
+%:%271=155%:%
+%:%272=156%:%
+%:%273=157%:%
+%:%274=157%:%
+%:%276=157%:%
+%:%280=157%:%
+%:%281=157%:%
+%:%283=158%:%
+%:%284=159%:%
+%:%285=160%:%
+%:%286=161%:%
+%:%296=163%:%
+%:%297=164%:%
+%:%298=165%:%
+%:%299=166%:%
+%:%300=167%:%
+%:%301=168%:%
+%:%302=169%:%
+%:%303=170%:%
+%:%304=171%:%
+%:%306=173%:%
+%:%307=173%:%
+%:%308=174%:%
+%:%309=175%:%
+%:%310=176%:%
+%:%311=176%:%
+%:%313=176%:%
+%:%317=176%:%
+%:%318=176%:%
+%:%320=177%:%
+%:%321=178%:%
+%:%322=179%:%
+%:%323=180%:%
+%:%333=182%:%
+%:%334=183%:%
+%:%351=208%:%
+%:%355=210%:%
+%:%356=211%:%
+%:%357=212%:%
+%:%358=213%:%
+%:%359=214%:%
+%:%361=217%:%
+%:%362=217%:%
+%:%364=218%:%
+%:%365=219%:%
+%:%366=220%:%
+%:%369=222%:%
+%:%370=223%:%
+%:%372=225%:%
+%:%373=225%:%
+%:%374=226%:%
+%:%375=227%:%
+%:%376=227%:%
+%:%378=227%:%
+%:%382=227%:%
+%:%383=227%:%
+%:%385=228%:%
+%:%386=229%:%
+%:%387=230%:%
+%:%388=231%:%
+%:%389=232%:%
+%:%390=233%:%
+%:%398=233%:%
+%:%399=234%:%
+%:%400=235%:%
+%:%401=235%:%
+%:%403=237%:%
+%:%404=238%:%
+%:%406=240%:%
+%:%407=240%:%
+%:%408=240%:%
+%:%410=240%:%
+%:%414=240%:%
+%:%415=240%:%
+%:%417=241%:%
+%:%418=242%:%
+%:%419=243%:%
+%:%420=244%:%
+%:%430=246%:%
+%:%431=247%:%
+%:%432=248%:%
+%:%433=249%:%
+%:%442=251%:%
+%:%454=253%:%
+%:%455=254%:%
+%:%456=255%:%
+%:%457=256%:%
+%:%458=257%:%
+%:%459=258%:%
+%:%460=259%:%
+%:%461=260%:%
+%:%462=261%:%
+%:%463=262%:%
+%:%464=263%:%
+%:%466=265%:%
+%:%467=265%:%
+%:%468=266%:%
+%:%469=267%:%
+%:%470=267%:%
+%:%472=267%:%
+%:%476=267%:%
+%:%486=269%:%
+%:%487=270%:%
+%:%488=271%:%
+%:%490=273%:%
+%:%491=273%:%
+%:%492=274%:%
+%:%493=275%:%
+%:%494=276%:%
+%:%495=276%:%
+%:%497=276%:%
+%:%501=276%:%
+%:%502=276%:%
+%:%504=277%:%
+%:%505=278%:%
+%:%506=279%:%
+%:%507=280%:%
+%:%517=282%:%
+%:%518=283%:%
+%:%520=285%:%
+%:%521=285%:%
+%:%522=286%:%
+%:%523=287%:%
+%:%524=288%:%
+%:%525=289%:%
+%:%526=289%:%
+%:%528=289%:%
+%:%532=289%:%
+%:%533=289%:%
+%:%535=290%:%
+%:%536=291%:%
+%:%537=292%:%
+%:%538=293%:%
+%:%539=294%:%
+%:%540=295%:%
+%:%550=297%:%
+%:%551=298%:%
+%:%552=299%:%
+%:%554=301%:%
+%:%555=301%:%
+%:%556=302%:%
+%:%557=303%:%
+%:%558=304%:%
+%:%559=304%:%
+%:%561=304%:%
+%:%565=304%:%
+%:%566=304%:%
+%:%568=305%:%
+%:%569=306%:%
+%:%570=307%:%
+%:%571=308%:%
+%:%572=309%:%
+%:%582=312%:%
+%:%583=313%:%
+%:%584=314%:%
+%:%585=315%:%
+%:%586=316%:%
+%:%587=317%:%
+%:%588=318%:%
+%:%590=320%:%
+%:%591=320%:%
+%:%593=321%:%
+%:%594=322%:%
+%:%595=323%:%
+%:%596=323%:%
+%:%597=324%:%
+%:%598=325%:%
+%:%599=325%:%
+%:%601=326%:%
+%:%602=326%:%
+%:%604=327%:%
+%:%605=328%:%
+%:%606=328%:%
+%:%607=329%:%
+%:%608=330%:%
+%:%609=330%:%
+%:%611=331%:%
+%:%612=332%:%
+%:%615=334%:%
+%:%616=335%:%
+%:%618=337%:%
+%:%619=337%:%
+%:%620=338%:%
+%:%621=339%:%
+%:%622=339%:%
+%:%624=339%:%
+%:%628=339%:%
+%:%629=339%:%
+%:%631=340%:%
+%:%632=341%:%
+%:%633=342%:%
+%:%634=343%:%
+%:%635=344%:%
+%:%636=345%:%
+%:%637=346%:%
+%:%647=348%:%
+%:%648=349%:%
+%:%649=350%:%
+%:%650=351%:%
+%:%651=352%:%
+%:%655=354%:%
+%:%656=355%:%
+%:%657=356%:%
+%:%658=357%:%
+%:%659=358%:%
+%:%660=359%:%
+%:%664=361%:%
+%:%665=362%:%
+%:%666=363%:%
+%:%668=365%:%
+%:%669=365%:%
+%:%670=366%:%
+%:%673=367%:%
+%:%677=367%:%
+%:%678=367%:%
+%:%680=368%:%
+%:%686=368%:%
+%:%689=369%:%
+%:%690=370%:%
+%:%691=370%:%
+%:%692=371%:%
+%:%693=372%:%
+%:%694=373%:%
+%:%695=373%:%
+%:%697=373%:%
+%:%701=373%:%
+%:%702=373%:%
+%:%704=374%:%
+%:%705=375%:%
+%:%706=376%:%
+%:%707=377%:%
+%:%708=378%:%
+%:%718=380%:%
+%:%719=381%:%
+%:%720=382%:%
+%:%721=383%:%
+%:%722=384%:%
+%:%723=385%:%
+%:%724=386%:%
+%:%725=387%:%
+%:%726=388%:%
+%:%727=389%:%
+%:%728=390%:%
+%:%729=391%:%
+%:%730=392%:%
+%:%731=393%:%
+%:%732=394%:%
+%:%733=395%:%
+%:%734=396%:%
+%:%735=397%:%
+%:%736=398%:%
+%:%737=399%:%
+%:%738=400%:%
+%:%739=401%:%
+%:%743=403%:%
+%:%744=404%:%
+%:%745=405%:%
+%:%746=406%:%
+%:%747=407%:%
+%:%748=408%:%
+%:%749=409%:%
+%:%750=410%:%
+%:%751=411%:%
+%:%755=414%:%
+%:%756=415%:%
+%:%757=416%:%
+%:%758=417%:%
+%:%760=419%:%
+%:%761=419%:%
+%:%762=420%:%
+%:%763=421%:%
+%:%764=421%:%
+%:%765=422%:%
+%:%768=423%:%
+%:%772=423%:%
+%:%773=423%:%
+%:%774=423%:%
+%:%776=424%:%
+%:%777=425%:%
+%:%787=427%:%
+%:%788=428%:%
+%:%789=429%:%
+%:%790=430%:%
+%:%791=431%:%
+%:%792=432%:%
+%:%793=433%:%
+%:%794=434%:%
+%:%795=435%:%
+%:%796=436%:%
+%:%797=437%:%
+%:%798=438%:%
+%:%799=439%:%
+%:%800=440%:%
+%:%801=441%:%
+%:%802=442%:%
+%:%803=443%:%
+%:%804=444%:%
+%:%805=445%:%
+%:%806=446%:%
+%:%807=447%:%
+%:%808=448%:%
+%:%809=449%:%
+%:%810=450%:%
+%:%811=451%:%
+%:%812=452%:%
+%:%813=453%:%
+%:%815=455%:%
+%:%816=455%:%
+%:%817=456%:%
+%:%818=457%:%
+%:%819=458%:%
+%:%820=458%:%
+%:%822=458%:%
+%:%826=458%:%
+%:%827=458%:%
+%:%829=459%:%
+%:%830=460%:%
+%:%831=461%:%
+%:%832=462%:%
+%:%833=463%:%
+%:%834=464%:%
+%:%835=465%:%
+%:%836=466%:%
+%:%846=468%:%
+%:%847=469%:%
+%:%848=470%:%
+%:%849=471%:%
+%:%850=472%:%
+%:%851=473%:%
+%:%852=474%:%

### 2022-03-09 paper/output/document/thesis_0_abstract.tex
making my way dowtown, typing fast, appendices pass

@@
 Regulators, philosophers, and computer scientists are raising the alarm about the 
-dangers of unethical artificial intelligence, from science-fiction killer robots to criminal
+dangers of unethical artificial intelligence, from lethal autonomous weapons to criminal
 sentencing algorithms prejudiced against people of color. This is spurring interest in automated ethics, or the development 
-of machines that can perform ethical reasoning. Much prior work in automated ethics approaches the 
-problem from a computational perspective and rarely engages with philosophical literature on ethics, despite
-its relevance to the development of AI agents that can
+of machines that can perform ethical reasoning. Prior work in automated ethics rarely engages with
+philosophical literature on ethics, despite its relevance to the development of AI agents that can
 responsibly navigate the world. If automated ethics draws on sophisticated philosophical literature, the ethical reasoning
-underlying such decisions will be more nuanced, precise, consistent, and trustworthy. However, faithfully translating complex ethical theories
-from natural language to the rigid syntax of a computer program poses technical and philosophical 
-challenges.
+underlying its decisions will be more nuanced, precise, and trustworthy because it will
+take advantage of philosophical progress in developing consistent, mature ethical theories. However, 
+faithfully translating complex ethical theories from natural language to the rigid syntax of a computer
+program poses technical and philosophical challenges.
 

### 2022-03-09 paper/output/document/thesis_1_intro.tex
making my way dowtown, typing fast, appendices pass

@@
 However, prior work in machine ethics using popular ethical theories like deontology (\citep{deon2}, \citep{deon1}), 
-consequentialism (\citep{util1}, \citep{util2}, \citep{cloos}), and virtue ethics \citep{berberich} rarely 
+consequentialism (\citep{util1}, \citep{util2}, \citep{cloos}), and virtue ethics \citep{virtue2} rarely 
 engages with philosophical literature and thus often misses philosophers' insights. Even the above example of 

### 2022-03-09 paper/output/document/thesis_5_discussion.tex
making my way dowtown, typing fast, appendices pass

@@
 nuanced ethical reasoning. In this section, I outline the additional components necessary for my system
-to guide AI agents in practice. My work on automating the categorical imperative 
-could serve as one component of a partially or fully artificial ethical reasoner, or an ``ethical AI.''
-Specifically, my system is a categorical imperative library that takes as input the logical representation 
-of a maxim and returns its moral status (if it is obligatory, prohibited, or permissible).
-As it stands, my project can evaluate the moral status of maxims represented in my logic and potentially 
+to guide AI agents in practice. As it stands, my system is a categorical imperative library that takes 
+as input the logical representation of a maxim and returns its moral status (if it is obligatory, 
+prohibited, or permissible). My project potentially 
 serves as one component of an ``ethics engine'' that an AI agent could use to make ethical decisions.
@@
 
-While this account of the formulation of a maxim describes how a well-intentioned human agent can determine 
+While the above account how a well-intentioned human agent can determine 
 morally relevant circumstances, the challenge remains open for automated ethics. In order for an automated
@@
 
-This representational question is one of the biggest challenges to using my categorical imperative library
+The challenge of formulating a maxim is one of the biggest obstacles to using my categorical imperative library
 in an AI ethics engine. One solution is for a human being to perform the role of the input
@@
 language prescriptions, the status of the maxim could be parsed into a natural language sentence. The 
-input parser, categorical imperative library, and output parser together constitute an ``ethics engine'' 
-that AI developers could use as a black box implementation of an ethical theory.
-
-The ethics engine depicted above is a high-level example of one way to use my project to guide an artifical agent.
-An automated version of the categorical imperative could become part of an ethics engine 
-for an AI agent, with additional work to parse the input and the output. Effectively, the kind 
-of automated ethics I implement could be a library that AI developers use to give AI agents the capacity for 
-sophisticated ethical reasoning faithful to philosophical literature. This represents an improvement 
-over existing AI ethics, which rarely captures the complexity 
+input parser, categorical imperative, and output parser together constitute an ``ethics engine'' 
+that AI developers could use in a variety of AI systems.
+
+The ethics engine depicted above is a high-level example of one way to use my project to guide an artifical agent,
+with additional work to parse the input and output of my implementation of the categorical imperative.
+Effectively, the kind of automated ethics I implement could be part of a library that AI developers use to 
+give AI agents the capacity for sophisticated ethical reasoning faithful to philosophical literature. 
+This represents an improvement over existing AI ethics, which rarely captures the complexity 
 of any ethical theory that philosophers plausibly defend.%
@@
 eat breakfast.'' There is something empty about this maxim because acting on it could never result in 
-any action. If an agent adopts this maxim, 
-they decide that, in the circumstances ``eating breakfast'' they will perform the act ``eating breakfast''
+any action. If I adopts this maxim as a principle to live by,
+I decide that, in the circumstances ``eating breakfast'' I will perform the act ``eating breakfast''
 for the purpose ``eating breakfast.'' In these circumstances, the act has 
-already been performed. Adopting this maxim as a law to live by does not change how you live. If you adopt 
-this maxim, then when you are eating breakfast, you eat breakfast, but this statement is already tautologically true.
+already been performed. Adopting this maxim as a law to live by does not change how I live. If I adopt 
+this maxim, then when I am eating breakfast, I eat breakfast, but this statement is already tautologically true.
 
@@
 the tension between self-doubt and self-respect dissolves, and it becomes clear that both concepts can
-co-exist, as we intuitively desire. I sketch the details of this argument in the rest of this section.
-
-Another reading of the dancing maxim understands it as an expression of self-doubt. Under this 
-reading, the question ``When I am dancing, should I be dancing for the sake of dancing?'' is the agent asking, 
-``Am I doing the right thing right now?'' Unlike the drowning example, the agent is not asking about the 
-next moment, but is expressing doubt about the moral validity of their behavior at this current moment. 
-Surely self-doubt does not always undermine the will—after all, self-doubt plays an 
-important role in moral reasoning and is often the mark of a thoughtful agent. I argue 
-that questions of self-doubt do not actually involve badly-formed maxims, for these are not the maxims 
-that the agent is doubting. I first frame this debate by introducing the tension between self-doubt and 
-self-respect in epistemology, then explain the parallel tension in ethics, and finally present a 
-resolution of this tension.
+co-exist. I sketch the details of this argument in the rest of this section. I will conclude that 
+badly-formed maxims serve as one guide to the formulation of maxims, and thus may have bearing on 
+other debates in Kantian ethics as well. I first introduce the tension between self-doubt and self-respect 
+in epistemology, then explain the parallel tension in ethics, and finally present a resolution of this 
+tension using badly-formed maxims.
 
@@
 This debate between self-respect and self-doubt in epistemology can be extended to ethics. When we 
-commit ourselves to acting, we cannot simultaneously doubt the validity of our action. If human 
+commit ourselves to acting, we cannot simultaneously doubt the validity of our action, just as we cannot
+rationally disapprove of our own beliefs. If human 
 behavior is purposive, then the very act of committing implies that one has sufficient reasons for 
-committing. These reasons may be flawed, but in making the commitment, the reasoner accepts them. It 
+committing. These reasons may be flawed, but in making the commitment, the reasoner accepts them—that is 
+just what it means to commit oneself to acting. It 
 is contradictory to claim that someone commits and questions simultaneously. Either the commitment 
@@
 
-To resolve this issue, I turn to another interpretation of ethical self-doubt. Under this interpretation, 
+If ethical self-doubt as badly-formed maxim contradicts self-respect, then resolving this issue requires a 
+different interpretation of ethical self-doubt. Under this interpretation, 
 when Sara asks, ``Should I really be dancing right now?'' she wants to know if the maxim that 
-resulted in the current moment when she is on the dance floor was the right thing to will. She is 
+resulted in the current moment of dancing was the right thing to will. She is 
 asking if she made the right decision in the past, when she decided to dance. The maxim that initiated 
@@
 This demonstrates a larger meta-pattern in Kantian reasoning: many debates in Kantian philosophical
-literature revolve around incorrectly formulated maxims, so the insight about badly
-formed maxims is significant. Much of the work of a Kantian ethicist is formulating an
+literature revolve around incorrectly formulated maxims, which means that the insight about badly
+formed maxims may have bearing on these debates. Much of the work of a Kantian ethicist is formulating an
 appropriate maxim, and badly-formed maxims define one boundary condition for this task. Just as my isolation
@@
 Isabelle's proof-finding tools look for edge cases like badly-formed maxims. Badly-formed maxims are 
-interesting because they are the kind of thing that is usually ignored in ordinary philosophical inquiry. 
+interesting precisely because they are the kind of thing that is usually ignored in ordinary philosophical inquiry. 
 Philosophers usually assume that we are not discussing badly-formed maxims because, as argued above, 
@@
 require that assumptions like the exclusion of well-formed maxims are made precise, and thus force 
-philosophers to understand their arguments in a new way. This example demonstrates the contributions
-that computational ethics makes: it can quickly check edge cases and it requires that all assumptions be
-made explicit and precise.
+philosophers to understand their arguments in a new way. This precision is also evident in the philosophical 
+implications of my examination of lying and joking in Section \ref{joking}, where I isolated the 
+specific cause of lying's wrongness. These examples demonstrate the contributions
+that computational ethics makes: it can quickly check edge cases and it uncovers imprecise, ambiguous,
+or implicit assumptions.
 
 I do not argue that computational ethics uncovers philosophical insights that humans are incapable 
-of reaching. Instead, I claim that insights like the one about the well-formed maxim are much easier
+of reaching. Instead, I claim that insights like the one about well-formed maxims are much easier
 to reach with computational tools. Computational 
@@
 to make headway \citep{buzzardvideo}, even though theorem provers were first invented in the 1960's \citep{historyofITP}. 
-In contrast, the first attempts to use theorem provers for ethics occurred in the last few years. The 
+In contrast, the first attempts to use theorem provers for progress in any kind of philosophy occurred 
+in the last few years \color{red} and, at the time of this writing, no known work has used theorem 
+provers for computational ethics \color{black}. The 
 fact that this nascent technology is already helping humans reach non-trivial philosophical conclusions 
@@
 %:%49=19%:%
-%:%50=20%:%
-%:%51=21%:%
+%:%52=23%:%
+%:%53=24%:%
 %:%54=25%:%
@@
 %:%59=30%:%
-%:%60=31%:%
-%:%61=32%:%
+%:%62=32%:%
+%:%63=33%:%
 %:%64=34%:%
@@
 %:%171=141%:%
-%:%172=142%:%
-%:%173=143%:%
-%:%174=144%:%
-%:%183=146%:%
+%:%180=143%:%
+%:%192=145%:%
+%:%193=146%:%
+%:%194=147%:%
 %:%195=148%:%
 %:%196=149%:%
-%:%197=150%:%
-%:%198=151%:%
-%:%199=152%:%
-%:%208=154%:%
+%:%205=151%:%
+%:%217=153%:%
+%:%218=154%:%
+%:%219=155%:%
 %:%220=156%:%
@@
 %:%399=335%:%
-%:%400=336%:%
-%:%401=337%:%
-%:%402=338%:%
-%:%403=339%:%
-%:%404=340%:%
-%:%405=341%:%
-%:%406=342%:%
-%:%415=346%:%
+%:%408=339%:%
+%:%420=341%:%
+%:%421=342%:%
+%:%422=343%:%
+%:%423=344%:%
+%:%424=345%:%
+%:%425=346%:%
+%:%426=347%:%
 %:%427=348%:%
@@
 %:%488=409%:%
-%:%489=410%:%
-%:%490=411%:%
-%:%491=412%:%
-%:%500=414%:%
+%:%497=411%:%
+%:%509=413%:%
+%:%510=414%:%
+%:%511=415%:%
 %:%512=416%:%
@@
 %:%587=491%:%
-%:%588=492%:%
-%:%589=493%:%
-%:%590=494%:%
-%:%599=497%:%
+%:%596=494%:%
+%:%608=497%:%
+%:%609=498%:%
+%:%610=499%:%
 %:%611=500%:%
@@
 %:%714=603%:%
-%:%715=604%:%
-%:%716=605%:%
-%:%717=606%:%
+%:%717=605%:%
+%:%718=606%:%
+%:%719=607%:%
 %:%720=608%:%
@@
 %:%722=610%:%
-%:%723=611%:%
-%:%724=612%:%
-%:%725=613%:%
+%:%725=611%:%
+%:%726=612%:%
+%:%727=613%:%
 %:%728=614%:%
@@
 %:%739=625%:%
-%:%740=626%:%
-%:%741=627%:%
-%:%742=628%:%
-%:%751=632%:%
+%:%748=629%:%
+%:%760=631%:%
+%:%761=632%:%
+%:%762=633%:%
 %:%763=634%:%
@@
 %:%811=682%:%
-%:%812=683%:%
-%:%813=684%:%
-%:%814=685%:%
-%:%823=687%:%
+%:%820=684%:%
+%:%832=686%:%
+%:%833=687%:%
+%:%834=688%:%
 %:%835=689%:%
@@
 %:%870=724%:%
-%:%871=725%:%
-%:%872=726%:%
-%:%873=727%:%

### 2022-03-14 paper/output/document/appendix_2.tex
spring cleaning xoxoxo
CLEANING DONE

--- 2022-02-13 paper/output/document/appendix_2.tex
@@
 %
-\isamarkupsubsection{Testing Un-Universalizable Actions \label{weirdtests}%
+\isamarkupsection{Additional Tests \label{weirdtests}%
 }
@@
 \begin{isamarkuptext}%
-I will show that the maxim, ``When strapped for cash, falsely promise to pay your friend back
-to get some easy money." is prohibited. This example is due to Korsgaard and she uses it to highlight 
-the strength of her preferred interpretation of the FUL, the practical contradiction interpretation \cite{KorsgaardFUL}.
-There are two possible readings of this maxim, and I will show that my formalization can handle both. 
-Under the first reading, the act of falsely promising is read as
-as entering a pre-existing, implicit, social system of promising with no intention of upholding your 
+In this section, I show that my system can correctly show prohibitions against actions that 
+are impossible to universalize, against conventional acts, and against natural acts. In the process
+of running these tests, I discover and resolve an ambiguity in Korsgaard's canonical example of a 
+prohibited maxim. I show that her maxim actually has two readings, one reading under which it is a 
+natural act, and another under which it is a conventional act. My formalization can correctly
+handle both readings. The recognition of this ambiguity is another example of the power of 
+computational ethics, and demonstrates that the process of making a philosophical argument precise 
+enough to represent to a machine can generate philosophical insights.
+
+In this section, I show that the maxim, ``When strapped for cash, falsely promise to pay your friend back
+to get some easy money," is prohibited. Korsgaard uses this example when arguing for the practical
+contradiction interpretation of the FUL \citep{KorsgaardFUL}. She argues that this maxim describes
+a conventional act, or an act that is possible due to some pre-existing social system, and is thus
+within reach for the logical contradiction interpretation. Natural acts, on the other hand, are acts
+that are possible simply due to the laws of nature, such as murder, and the logical contradiction
+interpretation cannot correctly handle such acts.
+
+I argue that, in addition to Korsgaard's reading of this maxim as a conventional act, there is also
+another reading of the maxim as a natural act. 
+Under Korsgaard's reading, the act of falsely promising is read as
+entering a pre-existing, implicit, social system of promising with no intention of upholding your 
 promise. Under the second reading, the act of falsely promising is equivalent to uttering the worlds 
-``I promise X" without intending to do X. The differences between these readings lies in the difference 
-between promising as an act with meaning in a larger social structure and the utterance ``I promise."
+``I promise X'' without intending to do X. There is a difference
+between promising as an act with meaning in a larger social structure and merely uttering the words
+``I promise,'' so these two readings are distinct.
 
-Under the first reading, the maxim fails because falsely promising is no longer possible in a world where 
-everyone everyone does so. This is how the logical contradiction interpretation reads this maxim—falsely 
+Under Korsgaard's reading, the maxim fails because falsely promising is no longer possible in a world where 
+everyone everyone does so, or because the action of falsely promising is literally impossible to
+universalize. Recall that this is how the logical contradiction interpretation prohibits this maxim—falsely 
 promising is no longer possible when universalized because the institution of promising breaks down. 
-The practical contradiction view also prohibits this maxim because if falsely promising is not longer 
-possible, then it is no longer an effective way to achieve the end of getting some money. Below I 
-define some logical tools to formalize this reading of this maxim.%
+First, I formalize this argument and show that my system can show the wrongness of the false
+promising maxim under Korsgaard's reading. This also shows that my system can show the wrongness of a
+maxim that is impossible to universalize.
+
+To formalize this argument, I first define the relevant maxim.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupcmt{Constant representing the circumstances ``when strapped for cash." Recall that the type of circumstances 
-is a term because circumstances can be true or false at a world.%
+\isamarkupcmt{This constant represents the circumstances ``when strapped for cash.''%
 }\isanewline
@@
 %
-\isamarkupcmt{Constant representing the act ``make a false promise to pay a loan back." Recall that the type of
-an act is an open sentence because the sentence ``subject s performs act a" can be true or false at a world.%
+\isamarkupcmt{This constant represents the act ``make a false promise to pay a loan back.''%
 }\isanewline
@@
 %
-\isamarkupcmt{Constant representing the goal ``to get some money." Recall that the type of a goal 
-is a term because a goal can be true or false at a world depending on whether it is achieved or not.%
+\isamarkupcmt{This constant represents the goal ``to get some money.''%
 }\isanewline
@@
 %
-\isamarkupcmt{Armed with the circumstances, act, and goal above, I can define the example maxim as a tuple.%
+\isamarkupcmt{Armed with the circumstances, act, and goal above, I can define the example false promising maxim as a tuple.%
 }%
 \begin{isamarkuptext}%
-The logical objects above are ``empty," in the sense that I haven't specified any of their 
-relevant properties. I will define these properties as assumptions and will show that, if the maxim 
-above satisfies the assumed properties, it is prohibited.%
+The logical objects above are empty or thin, in the sense that I haven't specified any of their 
+relevant properties, such as a robust definition of promising or any system of currency. I define 
+only the properties absolutely necessary for my argument as assumptions and show that, if the maxim 
+above satisfies the assumed properties, it is prohibited. Specifically, I am interested in Korsgaard's
+reading of this maxim, under which promising is a social convention that breaks down when abused. Instead
+of formally defining a conventional act, which requires wading into complex debates about trust and 
+social contracts, I merely focus on the fact that, unders this reading, not everyone can falsely 
+promise universally. Whatever kind of social convention promising is, my argument merely relies on
+the impossibility of breaking it.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupcmt{Under this reading, the problem with this maxim is that everyone can't
-falsely promise simultaneously because the institution of promising will break down. It's probably 
-possible to say something stronger than this (i.e. that if enough but not necessarily all people
-falsely promise promising is no longer possible), but for my purposes this will suffice. The above 
-formula reads, ``At all worlds, it is not the case that everyone falsely promises."%
-}\isanewline
-\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ circumstances{\isacharunderscore}hold\ \isakeyword{where}\ \isanewline
-{\isachardoublequoteopen}circumstances{\isacharunderscore}hold\ {\isasymequiv}\ {\isasymforall}w{\isachardot}\ when{\isacharunderscore}strapped{\isacharunderscore}for{\isacharunderscore}cash\ w{\isachardoublequoteclose}\isanewline
-%
-\isamarkupcmt{This assumption narrows our scope of consideration to worlds where the circumstances of 
-being strapped for cash hold. This is important because, at worlds where the circumstances do not hold, 
-a maxim is trivially effective (since it's never acted on) and thus trivially universalizable. This 
-assumption also makes practical sense; when evaluating a maxim, an agent would care about it specifically
-at worlds where the circumstances hold, since these are the worlds where the maxim actually prescribes action.%
-}\isanewline
-\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ example{\isacharunderscore}is{\isacharunderscore}well{\isacharunderscore}formed\ \isakeyword{where}\ \isanewline
-{\isachardoublequoteopen}example{\isacharunderscore}is{\isacharunderscore}well{\isacharunderscore}formed\ {\isasymequiv}\ {\isasymforall}s{\isachardot}\ {\isasymTurnstile}\ {\isacharparenleft}well{\isacharunderscore}formed\ false{\isacharunderscore}promising\ s{\isacharparenright}{\isachardoublequoteclose}\isanewline
-%
-\isamarkupcmt{This assumption states that the maxim of falsely promising is well-formed. This breaks down into
-two individual assumptions. First, being strapped for cash can't imply falsely promising, which is plausible
-because many people won't falsely promise under conditions of poverty. Second, being strapped for cash
-can't imply getting ready cash, which is also plausible because people often fail to secure cash even 
-when they need it.%
+\isamarkupcmt{The above formula reads, ``At all worlds, it is not the case that everyone falsely promises.''%
 }%
 \begin{isamarkuptext}%
-Putting it all together, I want to show that if the three assumptions justified above hold, then 
-the constructed maxim is prohibited. Below is the proof%
+With this abbreviation, I show that if not everyone can falsely promise simultaneously, then
+the constructed maxim about falsely promising is prohibited.%
 \end{isamarkuptext}\isamarkuptrue%
 \isacommand{lemma}\isamarkupfalse%
-\ lying{\isacharunderscore}bad{\isacharunderscore}{\isadigit{1}}{\isacharcolon}\isanewline
+\ falsely{\isacharunderscore}promising{\isacharunderscore}korsgaard{\isacharunderscore}interpretation{\isacharcolon}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}w{\isachardot}\ when{\isacharunderscore}strapped{\isacharunderscore}for{\isacharunderscore}cash\ w{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Restrict our focus to worlds in which the circumstance of being strapped for cash holds. 
+A technical detail.%
+}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}s{\isachardot}\ {\isasymTurnstile}\ {\isacharparenleft}well{\isacharunderscore}formed\ false{\isacharunderscore}promising\ s{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Initial set-up: the falsely promising maxim is well-formed.%
+}\isanewline
 \ \ \isakeyword{assumes}\ everyone{\isacharunderscore}can{\isacharprime}t{\isacharunderscore}lie\isanewline
-\ \ \isakeyword{assumes}\ circumstances{\isacharunderscore}hold\isanewline
-\ \ \isakeyword{assumes}\ example{\isacharunderscore}is{\isacharunderscore}well{\isacharunderscore}formed\isanewline
+%
+\isamarkupcmt{The assumption that this is Korsgaard's reading of the maxim, in which everyone cannot falsely promise
+simultaneously.%
+}\isanewline
 \ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}s{\isachardot}\ {\isasymTurnstile}\ {\isacharparenleft}prohibited\ false{\isacharunderscore}promising\ s{\isacharparenright}{\isachardoublequoteclose}\isanewline
@@
 \ \ \ \ \isacommand{by}\isamarkupfalse%
-\ {\isacharparenleft}simp\ add{\isacharcolon}\ assms{\isacharparenleft}{\isadigit{1}}{\isacharparenright}\ assms{\isacharparenleft}{\isadigit{2}}{\isacharparenright}{\isacharparenright}\isanewline
+\ {\isacharparenleft}simp\ add{\isacharcolon}\ assms{\isacharparenleft}{\isadigit{3}}{\isacharparenright}\ assms{\isacharparenleft}{\isadigit{1}}{\isacharparenright}{\isacharparenright}\isanewline
 %
-\isamarkupcmt{I manually broke the proof into this intermediate lemma and the conclusion, and then Sledgehammer 
-automatically found a proof.%
+\isamarkupcmt{As in the proofs in Chapter \ref{applications}, once I split this proof into this intermediate lemma,
+Isabelle can automatically complete the proof.%
 }\isanewline
@@
 \ \ \ \ \isacommand{using}\isamarkupfalse%
-\ FUL\ assms{\isacharparenleft}{\isadigit{3}}{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
+\ FUL\ assms{\isacharparenleft}{\isadigit{2}}{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
 \ blast\ \isanewline
@@
 \begin{isamarkuptext}%
-Under the second reading of this maxim, the act ``falsely promising" refers to uttering the 
-sentence ``I promise to do X" with no intention of actually doing X\footnote{Note that under this 
-reading, the maxim isn't prohibited under the logical contradiction interpretation because making an 
-utterance is still possible even if eveyrone else makes that utterance. I will discuss this in detail 
-later in this section in the context of the difference between natural and conventional acts.}. 
-Under this reading, the practical contradiction interpretation prohibits this maxim because, in a world 
+The above lemma shows that, under Korsgaard's reading of promising as a conventional act, 
+my system can show that falsely promising is prohibited. This means that my system passes both
+the conventional act test and the test that requires showing the wrongness of actions that are 
+impossible to universalize. Next, I show that my system can show a prohibition against this maxim
+even under the second reading, which understands it as a natural act.
+
+Under the second reading of this maxim, the act ``falsely promising'' refers to uttering the
+sentence ``I promise to do X'' with no intention of actually doing X. This is a natural act because the act of uttering a sentence does not rely 
+on any conventions, merely the laws of nature governing how your mouth and vocal cords behave.\footnote{
+Linguistic relativists may take issue with this claim and may argue that if the English language had 
+never developed, then making this utterance would be impossible. Even if this is true, the laws of 
+nature itself would not prohibit making the sounds corresponding to the English pronounciation of 
+this phrase, so the act would still not be impossible in the way that a conventional act can be.}
+
+The logical
+contradiction interpretation cannot prohibit this version of the maxim because making an utterance
+is always logically possible, even if everyone else makes the same utterance. However,
+under this reading, the practical contradiction interpretation prohibits this maxim because, in a world 
 where false promising is universalized, no one believes promises anymore, so the utterance is no longer 
-an effective way to get money. Below I formalize this reading of this maixm.%
+an effective way to get money. Because my system implements the stronger practical contradiction 
+interpretation of the FUL, it can show the wrongness of this maxim even under this reading. First, 
+I formalize this reading of the maxim.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 way of getting easy cash.%
+}%
+\begin{isamarkuptext}%
+Once again, I avoid giving robust definitions of hotly debates concepts like belief. Instead, 
+I represent the bare minimum logical background: false promises won't be believed when universalized,
+and promises must be believed to be effective.%
+\end{isamarkuptext}\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ falsely{\isacharunderscore}promising{\isacharunderscore}bad{\isacharunderscore}natural{\isacharunderscore}act{\isacharcolon}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}w{\isachardot}\ when{\isacharunderscore}strapped{\isacharunderscore}for{\isacharunderscore}cash\ w{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Restrict our focus to worlds in which the circumstance of being strapped for cash holds. 
+A technical detail.%
 }\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ falsely{\isacharunderscore}promising{\isacharunderscore}bad{\isacharunderscore}{\isadigit{2}}{\isacharcolon}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}s{\isachardot}\ {\isasymTurnstile}\ {\isacharparenleft}well{\isacharunderscore}formed\ false{\isacharunderscore}promising\ s{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isamarkupcmt{Initial set-up: the falsely promising maxim is well-formed.%
+}\isanewline
 \ \ \isakeyword{assumes}\ false{\isacharunderscore}promising{\isacharunderscore}not{\isacharunderscore}believed\isanewline
@@
 %
-\isamarkupcmt{The above two assumptions are specific to this reading and justified above.%
-}\isanewline
-\ \ \isakeyword{assumes}\ circumstances{\isacharunderscore}hold\isanewline
-\ \ \isakeyword{assumes}\ example{\isacharunderscore}is{\isacharunderscore}well{\isacharunderscore}formed\isanewline
-%
-\isamarkupcmt{These two assumptions applied to the first reading as well and were justified there.%
+\isamarkupcmt{The two assumptions above.%
 }\isanewline
@@
 \ \ \ \ \isacommand{using}\isamarkupfalse%
-\ FUL\ assms{\isacharparenleft}{\isadigit{4}}{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
+\ FUL\ assms{\isacharparenleft}{\isadigit{2}}{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
 \ blast\isanewline
@@
 \begin{isamarkuptext}%
-This example demonstrates that my formalization is able to correctly prohibit this maxim, regardless
-of its reading. This is additionally important because the two readings of this maxim represent reading 
-the act as either a conventional or natural action, so my intrepretation can correctly handle both kinds
-of actions. Korsgaard draws a distinction between conventional acts and natural acts. Conventional acts 
-exist within a practice, which is "comprised of certain rules, and its existence (where it is not embodied in 
-an institution with sanctions) consists in the general acknowledgement and following of those rules" 
-\cite[10]{KorsgaardFUL}. For example, promising is a conventional act because it only exists as a 
-practice. Murder, on the other hand, is an example of a natural act because its existence only depends
-on the laws of nature\cite[11]{KorsgaardFUL}.
-
-This distinction is important because Korsgaard argues that only the practical contradiction view can 
-satisfactorily explain the wrongness of certain natural acts like murder\footnote{For more discussion 
-of Korsgaard's argument for the practical contradiction view, see Section Philosophical Writing}. 
-The practical contradiction view is thus stronger than the logical contradiction view because it can 
-explain the wrongness of both conventional and natural acts.
-
-The fact that my interpretation can correctly show the wrongness of both conventional and natural acts
-is evidence for its correctness as a formalization of the practical contradiction interpretation. 
-The first reading of the example maxim reads the act 
-``making a false promise" as entering into an agreement within a socially established system of promising. 
-This is clearly a conventional act, and because it is a conventional act, it is not just contradictory
-when universalized but literally impossible because the practice breaks down. I capture this idea in the 
-assumption \isa{appendix{\isacharunderscore}{\isadigit{2}}{\isachardot}everyone{\isacharunderscore}can{\isacharprime}t{\isacharunderscore}lie\ {\isasymequiv}\ {\isasymforall}w{\isachardot}\ {\isasymnot}\ {\isacharparenleft}{\isasymforall}s{\isachardot}\ appendix{\isacharunderscore}{\isadigit{2}}{\isachardot}falsely{\isacharunderscore}promise\ s\ w{\isacharparenright}}, which states that, at all worlds, not everyone can falsely promise since
-otherwise the practice of promising would break down. The second reading, on the other hand, reads the 
-act of making a false promise as uttering the statement ``I promise to pay you back," while never intending 
-to fulfill this promise. This is a natural act because the act of uttering a sentence does not rely 
-on any conventions, merely the laws of nature governing how your mouth and vocal cords behave\footnote{
-Linguistic relativists may take issue with this claim and may argue that if the English language had 
-never developed, then making this utterance would be impossible. Even if this is true, the laws of 
-nature itself would not prohibit making the sounds corresponding to the English pronounciation of 
-this phrase, so the act would still not be impossible in the way that a conventional act can be.}
-
-I show above that my formalization shows the wrongness of this maxim under both readings. Under the 
-first reading, promising becomes impossible, so both the logical and 
-practical contradiction interpretations prohibit the maxim. Under the second reading, promising is still
-possible, but becomes ineffective because people no longer interpret the utterance as creating a commitment.
-Under this view, only the practical contradiction interpretation succeeds in prohibiting the maxim. Thus, 
-not only does my formalization likely capture the practical contradiction interpretation (as opposed to 
-the teleological or logical contradiction interpretations), it also adequately handles both natural 
-and conventional acts.%
+These proofs demonstrate that my formalization is able to correctly prohibit this maxim, whether 
+it is understood as a conventional act or a natural act. 
+Korsgaard argues that the practical contradiction interpretation outperforms other interpretations
+of the FUL because it can show the wrongness of both conventional and natural acts. Therefore, the 
+fact that my interpretation can correctly show the wrongness of both conventional and natural acts
+is evidence for its correctness as a formalization of the practical contradiction interpretation.%
 \end{isamarkuptext}\isamarkuptrue%
 %
-\begin{isamarkuptext}%
-I can also use Isabelle to confirm that the two readings are different. If they were the same, 
-we would expect the assumptions corresponing to each to be equivalent. The RHS of the lemma below represents 
-the second reading and the LHS represents the first reading.%
-\end{isamarkuptext}\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ readings{\isacharunderscore}are{\isacharunderscore}equivalent{\isacharcolon}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}false{\isacharunderscore}promising{\isacharunderscore}not{\isacharunderscore}believed\ {\isasymand}\ need{\isacharunderscore}to{\isacharunderscore}be{\isacharunderscore}believed\ {\isasymequiv}\ everyone{\isacharunderscore}can{\isacharprime}t{\isacharunderscore}lie{\isachardoublequoteclose}\isanewline
-\ \ \isacommand{nitpick}\isamarkupfalse%
-{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
 \isadelimproof
-\ %
+%
 \endisadelimproof
@@
 \isatagproof
-\isacommand{oops}\isamarkupfalse%
-\isanewline
 %
-\isamarkupcmt{Nitpick finds a counterexample, showing that the two readings are different.
-\color{blue}
-Nitpick found a counterexample for card i = 1 and card s = 1:
-
-  Empty assignment
-\color{black}%
-}%
 \endisatagproof
@@
 \endisadelimproof
-\isanewline
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
 %
 \isadelimtheory
-\isanewline
 %
@@
 %:%51=22%:%
+%:%52=23%:%
 %:%53=24%:%
-%:%54=24%:%
-%:%56=25%:%
-%:%57=26%:%
-%:%58=26%:%
-%:%59=27%:%
-%:%60=27%:%
-%:%62=28%:%
-%:%63=29%:%
-%:%64=29%:%
-%:%65=30%:%
-%:%66=30%:%
-%:%68=31%:%
-%:%69=32%:%
-%:%70=32%:%
-%:%71=33%:%
-%:%72=34%:%
-%:%73=34%:%
-%:%74=35%:%
-%:%76=36%:%
-%:%79=38%:%
-%:%80=39%:%
-%:%81=40%:%
-%:%83=42%:%
-%:%84=42%:%
-%:%85=43%:%
-%:%87=44%:%
-%:%88=45%:%
-%:%89=46%:%
-%:%90=47%:%
-%:%91=48%:%
-%:%92=48%:%
-%:%93=49%:%
-%:%94=50%:%
-%:%95=50%:%
-%:%96=51%:%
-%:%98=52%:%
-%:%99=53%:%
-%:%100=54%:%
-%:%101=55%:%
-%:%102=56%:%
-%:%103=56%:%
-%:%104=57%:%
-%:%105=58%:%
-%:%106=58%:%
-%:%107=59%:%
-%:%109=60%:%
-%:%110=61%:%
-%:%111=62%:%
-%:%112=63%:%
-%:%113=64%:%
-%:%116=66%:%
-%:%117=67%:%
-%:%119=69%:%
-%:%120=69%:%
-%:%121=70%:%
-%:%122=71%:%
-%:%123=72%:%
-%:%124=73%:%
-%:%131=74%:%
-%:%132=74%:%
-%:%133=75%:%
-%:%134=75%:%
-%:%135=76%:%
-%:%136=76%:%
-%:%138=77%:%
-%:%139=78%:%
-%:%140=78%:%
-%:%141=79%:%
-%:%142=79%:%
-%:%143=80%:%
-%:%144=80%:%
-%:%145=80%:%
-%:%146=81%:%
-%:%156=83%:%
-%:%157=84%:%
-%:%158=85%:%
-%:%159=86%:%
-%:%160=87%:%
-%:%161=88%:%
-%:%162=89%:%
+%:%54=25%:%
+%:%55=26%:%
+%:%56=27%:%
+%:%57=28%:%
+%:%58=29%:%
+%:%59=30%:%
+%:%60=31%:%
+%:%61=32%:%
+%:%62=33%:%
+%:%63=34%:%
+%:%64=35%:%
+%:%65=36%:%
+%:%66=37%:%
+%:%67=38%:%
+%:%68=39%:%
+%:%69=40%:%
+%:%70=41%:%
+%:%72=43%:%
+%:%73=43%:%
+%:%75=44%:%
+%:%76=44%:%
+%:%77=45%:%
+%:%78=45%:%
+%:%80=46%:%
+%:%81=46%:%
+%:%82=47%:%
+%:%83=47%:%
+%:%85=48%:%
+%:%86=48%:%
+%:%87=49%:%
+%:%88=50%:%
+%:%89=50%:%
+%:%90=51%:%
+%:%92=52%:%
+%:%95=54%:%
+%:%96=55%:%
+%:%97=56%:%
+%:%98=57%:%
+%:%99=58%:%
+%:%100=59%:%
+%:%101=60%:%
+%:%102=61%:%
+%:%103=62%:%
+%:%105=64%:%
+%:%106=64%:%
+%:%107=65%:%
+%:%109=66%:%
+%:%112=68%:%
+%:%113=69%:%
+%:%115=71%:%
+%:%116=71%:%
+%:%117=72%:%
+%:%119=73%:%
+%:%120=74%:%
+%:%121=74%:%
+%:%122=75%:%
+%:%124=76%:%
+%:%125=76%:%
+%:%126=77%:%
+%:%128=78%:%
+%:%129=79%:%
+%:%130=79%:%
+%:%131=80%:%
+%:%138=81%:%
+%:%139=81%:%
+%:%140=82%:%
+%:%141=82%:%
+%:%142=83%:%
+%:%143=83%:%
+%:%145=84%:%
+%:%146=85%:%
+%:%147=85%:%
+%:%148=86%:%
+%:%149=86%:%
+%:%150=87%:%
+%:%151=87%:%
+%:%152=87%:%
+%:%153=88%:%
 %:%163=90%:%
+%:%164=91%:%
 %:%165=92%:%
-%:%166=92%:%
-%:%167=93%:%
-%:%168=93%:%
-%:%169=94%:%
-%:%171=95%:%
-%:%172=96%:%
-%:%173=96%:%
-%:%174=97%:%
-%:%175=98%:%
-%:%176=98%:%
-%:%177=99%:%
-%:%179=100%:%
-%:%180=101%:%
-%:%181=101%:%
-%:%182=102%:%
-%:%183=103%:%
-%:%184=103%:%
-%:%185=104%:%
-%:%186=105%:%
-%:%188=106%:%
-%:%189=106%:%
-%:%190=107%:%
-%:%191=108%:%
-%:%193=109%:%
-%:%194=109%:%
-%:%195=110%:%
-%:%202=111%:%
-%:%203=111%:%
-%:%204=112%:%
-%:%205=112%:%
-%:%206=113%:%
-%:%207=113%:%
-%:%208=113%:%
-%:%209=114%:%
-%:%210=114%:%
-%:%211=115%:%
-%:%212=115%:%
-%:%213=115%:%
-%:%214=116%:%
-%:%215=116%:%
-%:%217=117%:%
-%:%227=119%:%
-%:%228=120%:%
-%:%229=121%:%
-%:%230=122%:%
-%:%231=123%:%
-%:%232=124%:%
-%:%233=125%:%
-%:%234=126%:%
-%:%235=127%:%
-%:%236=128%:%
-%:%237=129%:%
-%:%238=130%:%
-%:%239=131%:%
-%:%240=132%:%
-%:%241=133%:%
-%:%242=134%:%
-%:%243=135%:%
-%:%244=136%:%
-%:%245=137%:%
-%:%246=138%:%
-%:%247=139%:%
-%:%248=140%:%
-%:%249=141%:%
-%:%250=142%:%
-%:%251=143%:%
-%:%252=144%:%
-%:%253=145%:%
-%:%254=146%:%
-%:%255=147%:%
-%:%256=148%:%
-%:%257=149%:%
-%:%258=150%:%
-%:%259=151%:%
-%:%260=152%:%
-%:%261=153%:%
-%:%262=154%:%
-%:%263=155%:%
-%:%264=156%:%
-%:%265=157%:%
-%:%266=158%:%
-%:%270=160%:%
-%:%271=161%:%
-%:%272=162%:%
-%:%274=164%:%
-%:%275=164%:%
-%:%276=165%:%
-%:%277=166%:%
-%:%278=166%:%
-%:%280=166%:%
-%:%284=166%:%
-%:%285=166%:%
-%:%287=167%:%
-%:%288=168%:%
-%:%289=169%:%
-%:%290=170%:%
-%:%291=171%:%
-%:%292=172%:%
-%:%300=173%:%
-%:%303=174%:%
-%:%308=175%:%
+%:%166=93%:%
+%:%167=94%:%
+%:%168=95%:%
+%:%169=96%:%
+%:%170=97%:%
+%:%171=98%:%
+%:%172=99%:%
+%:%173=100%:%
+%:%174=101%:%
+%:%175=102%:%
+%:%176=103%:%
+%:%177=104%:%
+%:%178=105%:%
+%:%179=106%:%
+%:%180=107%:%
+%:%181=108%:%
+%:%182=109%:%
+%:%183=110%:%
+%:%184=111%:%
+%:%186=113%:%
+%:%187=113%:%
+%:%188=114%:%
+%:%189=114%:%
+%:%190=115%:%
+%:%192=116%:%
+%:%193=117%:%
+%:%194=117%:%
+%:%195=118%:%
+%:%196=119%:%
+%:%197=119%:%
+%:%198=120%:%
+%:%200=121%:%
+%:%201=122%:%
+%:%204=124%:%
+%:%205=125%:%
+%:%206=126%:%
+%:%208=128%:%
+%:%209=128%:%
+%:%210=129%:%
+%:%212=130%:%
+%:%213=131%:%
+%:%214=131%:%
+%:%215=132%:%
+%:%217=133%:%
+%:%218=133%:%
+%:%219=134%:%
+%:%220=135%:%
+%:%222=136%:%
+%:%223=136%:%
+%:%224=137%:%
+%:%231=138%:%
+%:%232=138%:%
+%:%233=139%:%
+%:%234=139%:%
+%:%235=140%:%
+%:%236=140%:%
+%:%237=140%:%
+%:%238=141%:%
+%:%239=141%:%
+%:%240=142%:%
+%:%241=142%:%
+%:%242=142%:%
+%:%243=143%:%
+%:%244=143%:%
+%:%246=144%:%
+%:%256=146%:%
+%:%257=147%:%
+%:%258=148%:%
+%:%259=149%:%
+%:%260=150%:%
+%:%261=151%:%

### 2022-03-14 paper/output/document/thesis_0_abstract.tex
CLEANING DONE

@@
 dangers of unethical artificial intelligence, from lethal autonomous weapons to criminal
-sentencing algorithms prejudiced against people of color. This is spurring interest in automated ethics, or the development 
-of machines that can perform ethical reasoning. Prior work in automated ethics rarely engages with
-philosophical literature on ethics, despite its relevance to the development of AI agents that can
-responsibly navigate the world. If automated ethics draws on sophisticated philosophical literature, the ethical reasoning
-underlying its decisions will be more nuanced, precise, and trustworthy because it will
-take advantage of philosophical progress in developing consistent, mature ethical theories. However, 
-faithfully translating complex ethical theories from natural language to the rigid syntax of a computer
-program poses technical and philosophical challenges.
+sentencing algorithms prejudiced against people of color. These warnings are spurring interest in 
+automated ethics, or the development of machines that can perform ethical reasoning. Prior work in 
+automated ethics rarely engages with philosophical literature, despite its relevance to the 
+development of responsible AI agents. If automated ethics draws on sophisticated philosophical
+literature, its decisions will be more nuanced, precise, consistent, and trustworthy, but faithfully
+translating a complex ethical theory from natural language to the rigid syntax of a computer program is
+technically and philosophically challenging.
 
@@
 I also use my system to derive philosophically sophisticated and nuanced solutions to two central ethical 
-dilemmas in Kantian ethical literature: the difference
-between lying and joking and the example of a murderer knocking on your door asking about the location of their
-intended victim. Finally, I examine the philosophical implications of my system, exploring its limitations 
-and its potential to help AI agents, academic philosophers, and ordinary human beings better reason about ethics. This work serves 
+dilemmas in Kantian literature: the permissibility of lying in the context of a joke and to a murderer 
+asking about the location of their intended victim. Finally, I examine the philosophical implications 
+of my system, exploring its limitations and its potential to guide AI agents, academic philosophers, 
+and everyday reasoners as they navigate ethical dilemmas. Ultimately, this work serves 
 as an early proof-of-concept for philosophically mature AI agents and is one step towards the development 
@@
 %:%45=32%:%
-%:%46=33%:%

### 2022-03-14 paper/output/document/thesis_1_intro.tex
CLEANING DONE

@@
 As AI agents become more sophisticated and less dependent on humans, interest begins to mount
-in the development of computers that can perform ethical reasoning, also known as automated moral agents. 
+in the development of automated moral agents, or computers that can perform ethical reasoning. 
 AI agents are making decisions in increasingly 
@@
 can uproot entire families and is known to be biased against poor people of color \citep{eubanks}. 
-This motivates the need for machine ethics (also called automated ethics), 
-or the study of how to develop machines that can perform robust, sophisticated ethical reasoning.
+This motivates the need for automated ethics (also called machine ethics), 
+or the development of machines that can perform robust, sophisticated ethical reasoning.
 
@@
 or where its reasoning may have gone wrong. 
-Machine learning approaches like Delphi often cannot explain their decisions to a human being and, 
-in the extreme case, are black box algorithms. This reduces human trust in a machine's controversial 
-ethical judgements. If a machine prescribes killing one person to save three without justifying this 
-decision, it is difficult to trust this judgement. 
-The high stakes of automated ethics require explainability to build trust and catch mistakes.
+Machine learning approaches like Delphi often cannot explain their decisions to a human being, reducing
+human trust in a machine's controversial ethical judgements. If a machine prescribes killing one person 
+to save three without rigorously justifying this decision, it is difficult to trust this judgement. 
+The high stakes of automated ethics require explainability to build trust and catch mistakes, which
+motivates philosophically faithful automated ethics.
 
@@
 reward of a system is the discounted sum of the reward at each state, given by $r_i$. Formally, total
-reward $R=\sum_0^{\infty}\gamma^ir_i$.}, but many philosophers reject this notion of aggregation \citep{consequentialismsep}. 
+reward $R=\sum_0^{\infty}\gamma^ir_i$ for some $\gamma \leq 1$.}, but many philosophers reject 
+this notion of aggregation \citep{consequentialismsep}. 
 On the other hand, approaches that begin with an ethical theory, instead of a computational method, must contend with the 
@@
 an ethical dilemma, plays a great role in the machine's decisions. Another complication
-is that philosophers do not agree that on a single choice of ethical theory. Even philosophers who
-agree that a specific ethical theory, like Kantian ethics, is true, still debate the theory's 
-details.\footnote{For examples of these debates in the case of Kantian ethics, see Section Joking
-and Section Murderer.} Moreover, even once reasoning within a 
+is that philosophers do not agree on a single choice of ethical theory. Even philosophers who
+subscribe to a specific ethical theory still debate the theory's 
+details.\footnote{I give examples of such debates within Kantian ethics in Sections \ref{whatisamaxim}, 
+\ref{praccon}, \ref{joking}, and \ref{murderer}.} Moreover, even once reasoning within a 
 particular ethical theory is automated, those who disagree with that theory will disagree with the 
 system's judgements.
+
+\noindent \textbf{Contributions}
+
+\medskip
 
@@
 
-\item In Section \ref{details}, I present a formalization of the practical contradiction interpretation of Kant's 
+\item In Section \ref{implementation31}, I present a formalization of the practical contradiction interpretation of Kant's 
 Formula of Universal Law in Dyadic Deontic Logic. I implement this formalization in the Isabelle/HOL
 theorem prover. My implementation includes axioms and definitions such that my system, when given an appropriately
-represented input, can prove that the input is permissible, obligatory, or prohibited. It can also return
-a list of facts used in the proof and, in some cases, an Isar-style human readable proof.
+represented input, can prove that the input action is permissible, obligatory, or prohibited. It can also return
+a list of facts used in the proof and, in some cases, a human readable proof.
+
+\item In Section \ref{testing}, I present a testing framework that can evaluate how faithful an implementation 
+of automated Kantian ethics is, inspired by philosophical literature. This testing framework shows that 
+my formalization substantially improves on prior attempts to formalize Kantian ethics.
 
@@
 my system draws on definitions of Kantian ethics presented in philosophical literature, it is able 
-to perform sophisticated moral reasoning.
+to perform sophisticated moral reasoning with minimal factual or situational context.
 
-\item In Section \ref{testing}, I present a testing framework that can evaluate how faithful an implementation 
-of automated Kantian ethics is. My framework includes meta-ethical tests and application tests inspired by philosophical
-literature. This testing framework shows that my formalization substantially improves on prior work and can 
-be generalized to evaluate any implementation of automated Kantian ethics.
-
-\item In Section \ref{computationalethics}, I present new ethical insights discovered using my system and argue that
-computational methods like the one presented in this paper can help philosophers address ethical problems.
+\item In Section \ref{computationalethics}, I present ethical insights discovered using my system and argue that
+computational methods like the one presented in this thesis can help philosophers address ethical problems.
 Not only can my system help machines reason about ethics, but it can also help philosophers make philosophical
-progress.
+progress, just as computational tools unlock discoveries in fields like protein folding and drug discovery.
 \end{enumerate}%
@@
 \begin{isamarkuptext}%
-Deontic logic is a modal logic that can express obligation, or morally binding requirements. Traditional modal 
-logics include the necessitation operator, denoted as $\Box$. In modal logic using the Kripke semantics, 
+\noindent \textbf{Automated Kantian Ethics}
+
+\medskip
+
+My implementation of automated Kantian ethics formalizes Kant's moral rule
+in Deontic logic, a modal logic that can express obligation, or morally binding requirements. Traditional modal 
+logics include the necessitation operator, denoted as $\Box$. Using the Kripke semantics, 
 $\Box p$ is true at world $w$ if $p$ is true at all worlds that neighbor $w$ \citep{cresswell}. Modal 
 logics  also contain the possibility operator $\diamond$, where $\diamond \, p \longleftrightarrow \neg (\Box (\neg p))$ 
-and operators of propositional logic like $\neg, \wedge, \vee, \rightarrow$. I use DDL, in which
+and operators of propositional logic like $\neg, \wedge, \vee, \rightarrow$. Standard deontic logic (SDL) 
+replaces $\Box$ with the obligation operator $O$, where $O \, p$ is true at $w$ 
+if $p$ is true at all morally perfect versions of $w$ \citep{sep-logic-deontic}. While SDL is appreciable for its simplicity, 
+in situations where duty is violated, the logic breaks down and produces paradoxical results.\footnote{The 
+paradigm case of a contrary-to-duty paradox is the 
+Chisholm paradox. Consider the following statements: \begin{enumerate}
+\item It ought to be that Tom helps his neighbors
+\item It ought to be that if Tom helps his neighbors, he tells them he is coming
+\item If Tom does not help his neighbors, he ought not tell them that he is coming
+\item Tom does not help his neighbors
+\end{enumerate} 
+These premises contradict themselves, because items (2)-(4) imply that Tom ought not help his neighbors. The 
+contradiction results because the logic cannot handle violations of duty mixed with
+conditionals. \citep{chisholm, ctd}
+} To escape such issues, I use Dyadic Deontic Logic, in which
 the dyadic obligation operator $O\{A \vert B\}$ represents the sentence ``A is obligated in the context B.'' 
-The introduction of context allows DDL to express more nuanced reasoning. DDL is both deontic and modal, 
+The introduction of context allows DDL to express more nuanced reasoning and avoid contrary-to-duty
+paradoxes. DDL is both deontic and modal, 
 so sentences like $O\{A \vert B\}$ are terms that can be true or false at a world. For example, the 
@@
 
-I automate Kantian ethics because it is the most natural to formalize, as I argue in Section \ref{whykant}. 
+I automate Kantian ethics because it is the most natural of the major ethical traditions to formalize, as 
+I argue in Section \ref{whykant}. 
 Kant presents three versions of a single moral rule, known as the categorical imperative, from which 
@@
 Law (FUL), which states that people should only act on those principles that can be acted on by all 
-people without contradiction. For example, in a world where everyone falsely promises to repay a loan, 
-lenders will no longer believe these promises and will stop offering loans. Therefore, not everyone 
-can simultaneously falsely promise to repay a loan, so the FUL thus prohibits this act.
+people without contradiction. For example, falsely promising to repay a loan is wrong because if everyone 
+falsely promises to repay a loan, lenders will no longer believe these promises and will stop offering loans. 
+Therefore, not everyone can simultaneously falsely promise to repay a loan, so the FUL prohibits this act.
 
-Prior work by Benzmüller, Farjami, and Parent \citep{logikey, BFP} implements DDL in Isabelle/HOL and 
+Prior work by Benzmüller, Farjami, and Parent \citep{logikey, BFP} implements DDL in Isabelle/HOL, and 
 I add the Formula of Universal Law as an axiom on top of their library. The resulting Isabelle theory 
@@
 theorem provers are designed to be interpretable, my system is explainable. Isabelle can list 
-the axioms and facts it used to generate an ethical judgement, and, in some cases, construct 
-human-readable proofs. In Chapter \ref{applications}, I use my system to derive
-sophisticated solutions to two ethical dilemmas often used in critiques of Kantian ethics. Because 
-my system is faithful to philosophical literature, it is able to provide nuanced answers to these paradoxes
-that require a deep understanding of Kantian ethics.
+the axioms and facts it uses to generate an ethical judgement, and, in some cases, construct 
+human-readable proofs.
 
@@
 properties of Kantian ethics as sentences in my logic, such as the property that obligations cannot 
-contradict each other. I represent each of these properties as a sentence in my logic that my system 
-should be able to prove or refute. To run the tests, I use Isabelle to automatically find proofs or 
+contradict each other. To run the tests, I use Isabelle to automatically find proofs or 
 countermodels for the test statements. For example, my implementation passes the contradictory 
-obligations test because it is able to prove the sentence $\neg (O\{A|B\} \wedge O\{\neg A | B\})$. 
-I find that my system outperforms the control group of raw DDL, without any moral axioms added, and 
+obligations test because it is able to prove the sentence $\neg (O\{A|B\} \wedge O\{\neg A | B\})$, 
+which says that $A$ and $\neg A$ are not both obligatory. This testing framework shows that my system 
+outperforms a control group (raw DDL without any moral axioms added) and 
 Moshe Kroy's prior attempt at formalizing Kantian ethics in deontic logic \citep{kroy}.
 
-As it stands, my implementation can evaluate the moral status of sentences represented in my logic. 
-Given an appropriate input, my project returns a value indicating if the action is obligatory 
-(its negation violates the FUL), permissible (consistent with the FUL), or prohibited (violates the FUL) 
-by proving or refuting a theorem in my logic. Because the logic underlying these judgements is grounded
-in philosophical literature, my system can correctly resolve complex moral dilemmas with only relatively uncontroversial
-facts about the world. Moreover, because I automate an explicit ethical theory, the ethical reasoning 
-underlying my system's judgements is interpretable by a human being. I implement this ethical theory 
-using the Isabelle/HOL interactive theorem prover, which can list the axioms and theorems used in a 
-proof, so my system is explainable.
+In Chapter \ref{applications}, I demonstrate my system's power by using it to arrive at sophisticated
+solutions to two ethical dilemmas often used in critiques of Kantian ethics. I show that because my system is 
+faithful to philosophical literature, it is able to provide nuanced answers to paradoxes that require a
+deep understanding of Kantian ethics. While this reasoning does require some factual and situational
+context, my system derives mature judgements with relatively little and uncontroversial background.
+This indicates that the challenge of automating ``common sense,'' a major hurdle for automated ethics, 
+is within closer reach than previously thought. I discuss automated common sense further in
+Sections \ref{AIethics} and \ref{amapossible}.
 
@@
 but it can also help philosophers better study philosophy. I argue for ``computational ethics,'' or the use of computational tools to 
-make philosophical progress, analogous to computational drug discovery or neuroscience. 
+make philosophical progress, analogous to computational biology or neuroscience. 
 I demonstrate the potential of computational ethics by presenting a 
-philosophical insight about which kinds of maxims are appropriate for ethical consideration that I 
+philosophical insight about which kinds of actions are appropriate for ethical consideration that I 
 discovered using my system. The process of building and interacting with a computer that can reason 
 about ethics helped me, a human philosopher, arrive at a philosophical conclusion that has implications for practical
-reason and philosophy of doubt. Thus, my system can be used in two distinct ways. First, my system can help
+reason and philosophy of doubt. Thus, my system can be used in three distinct ways. First, my system can help
 automated agents navigate the world, which I will refer to as automated ethics or machine ethics interchangeably. Second, 
-my system help human philosophers reason about philosophy, which I call computational ethics. In Section 
-\ref{ordinarypeople}, I consider how computational ethics can help not only professional philosophers,
-but also augment the everyday ethical reasoning that ordinary people perform as we navigate the world.%
+my system help human philosophers reason about philosophy, which I call computational ethics. Third, as 
+I discuss in Section \ref{ordinarypeople}, computational ethics can help not only professional philosophers,
+but can also augment the everyday ethical reasoning that we all perform as we navigate the world.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %:%111=83%:%
-%:%115=86%:%
-%:%116=87%:%
-%:%117=88%:%
-%:%118=89%:%
-%:%119=90%:%
+%:%112=84%:%
+%:%113=85%:%
+%:%114=86%:%
+%:%115=87%:%
+%:%116=88%:%
 %:%120=91%:%
@@
 %:%139=110%:%
+%:%140=111%:%
+%:%141=112%:%
+%:%142=113%:%
 %:%143=114%:%
-%:%144=115%:%
-%:%145=116%:%
-%:%146=117%:%
-%:%147=118%:%
-%:%148=119%:%
-%:%149=120%:%
-%:%150=121%:%
-%:%151=122%:%
-%:%152=123%:%
-%:%153=124%:%
-%:%154=125%:%
-%:%155=126%:%
-%:%156=127%:%
-%:%157=128%:%
-%:%158=129%:%
-%:%159=130%:%
-%:%160=131%:%
-%:%161=132%:%
-%:%162=133%:%
-%:%163=134%:%
-%:%164=135%:%
-%:%165=136%:%
-%:%166=137%:%
-%:%167=138%:%
-%:%168=139%:%
-%:%169=140%:%
-%:%170=141%:%
-%:%171=142%:%
-%:%172=143%:%
-%:%173=144%:%
-%:%174=145%:%
-%:%175=146%:%
-%:%176=147%:%
-%:%177=148%:%
-%:%178=149%:%
-%:%179=150%:%
-%:%180=151%:%
-%:%181=152%:%
-%:%182=153%:%
-%:%183=154%:%
-%:%184=155%:%
-%:%185=156%:%
-%:%186=157%:%
-%:%187=158%:%
-%:%188=159%:%
-%:%189=160%:%
-%:%190=161%:%
-%:%191=162%:%
-%:%192=163%:%
-%:%193=164%:%
-%:%194=165%:%
-%:%195=166%:%
-%:%196=167%:%
-%:%197=168%:%
-%:%198=169%:%
-%:%199=170%:%
-%:%200=171%:%
-%:%201=172%:%
-%:%202=173%:%
-%:%203=174%:%
-%:%204=175%:%
-%:%205=176%:%
+%:%147=117%:%
+%:%148=118%:%
+%:%149=119%:%
+%:%150=120%:%
+%:%151=121%:%
+%:%152=122%:%
+%:%153=123%:%
+%:%154=124%:%
+%:%155=125%:%
+%:%156=126%:%
+%:%157=127%:%
+%:%158=128%:%
+%:%159=129%:%
+%:%160=130%:%
+%:%161=131%:%
+%:%162=132%:%
+%:%163=133%:%
+%:%164=134%:%
+%:%165=135%:%
+%:%166=136%:%
+%:%167=137%:%
+%:%168=138%:%
+%:%169=139%:%
+%:%170=140%:%
+%:%171=141%:%
+%:%172=142%:%
+%:%173=143%:%
+%:%174=144%:%
+%:%175=145%:%
+%:%176=146%:%
+%:%177=147%:%
+%:%178=148%:%
+%:%179=149%:%
+%:%180=150%:%
+%:%181=151%:%
+%:%182=152%:%
+%:%183=153%:%
+%:%184=154%:%
+%:%185=155%:%
+%:%186=156%:%
+%:%187=157%:%
+%:%188=158%:%
+%:%189=159%:%
+%:%190=160%:%
+%:%191=161%:%
+%:%192=162%:%
+%:%193=163%:%
+%:%194=164%:%
+%:%195=165%:%
+%:%196=166%:%
+%:%197=167%:%
+%:%198=168%:%
+%:%199=169%:%
+%:%200=170%:%
+%:%201=171%:%
+%:%202=172%:%
+%:%203=173%:%
+%:%204=174%:%
+%:%205=175%:%
+%:%206=176%:%
+%:%207=177%:%
+%:%208=178%:%
+%:%209=179%:%
+%:%210=180%:%
+%:%211=181%:%
+%:%212=182%:%
+%:%213=183%:%
+%:%214=184%:%
+%:%215=185%:%
+%:%216=186%:%
+%:%217=187%:%
+%:%218=188%:%
+%:%219=189%:%
+%:%220=190%:%
+%:%221=191%:%
+%:%222=192%:%
+%:%223=193%:%
+%:%224=194%:%
+%:%225=195%:%
+%:%226=196%:%

### 2022-03-14 paper/output/document/thesis_3_implementation.tex
CLEANING DONE

@@
 %
-\isamarkupsubsection{Formalization and Implementation of the FUL%
+\isamarkupsubsection{Formalization and Implementation of the FUL \label{implementation31}%
 }
@@
 Korsgaard makes a distinction between conventional and natural acts \citep{KorsgaardFUL}. 
-A conventional act like promising relies on a convention, like the 
+A conventional act relies on a convention, like the 
 convention that a promise is a commitment, whereas a natural act is possible simply because of the laws 
-of the natural world. It is easier to show the wrongness of conventional acts because there are worlds 
+of the natural world. Conventional acts exist within a practice, which is ``comprised of certain rules, 
+and its existence (where it is not embodied in an institution with sanctions) consists in the general 
+acknowledgement and following of those rules'' \cite[10]{KorsgaardFUL}. Promising is a conventional act 
+because it exists as a practice. Murder, on the other hand, is an example of a natural act because 
+its existence only depends on the laws of nature\cite[11]{KorsgaardFUL}.
+
+It is easier to show the wrongness of conventional acts because there are worlds
 in which these acts are impossible; namely, worlds in which the convention does not exist. For example, 
@@
 %:%938=612%:%
+%:%939=613%:%
+%:%940=614%:%
+%:%941=615%:%
+%:%942=616%:%
+%:%943=617%:%
+%:%944=618%:%

### 2022-03-14 paper/output/document/thesis_4_applications.tex
CLEANING DONE

@@
 in practice and demonstrate my system's ability to formalize longer, more complicted ethical arguments
-than those presented in Chapter \ref{details}.
+than those presented in Chapter \ref{details}. Moreover, in the process of formalizing these dilemmas, 
+I isolated the exact conditon that makes a maxim about lying wrong, an insight that could contribute to 
+the philosophical literature on lying.
 
@@
 of a maxim about uttering a falsehood being prohibited: that the goal require that someone believe
-the falsehood. This condition both made an long-standing argument in Kantian ethics more precise
-and can guide the correct formulation of future maxims. In other words, an insight generated by the 
+the falsehood. This condition, made an long-standing argument in Kantian ethics more precise, can guide 
+the correct formulation of future maxims, and could contribute to the rich philosophical conversation
+about the wrongness of lying. In other words, an insight generated by the
 computer provides value to ethicists, bolstering the argument for computational ethics provided in 
@@
 %:%83=55%:%
-%:%92=58%:%
-%:%104=61%:%
-%:%105=62%:%
+%:%84=56%:%
+%:%85=57%:%
+%:%94=60%:%
 %:%106=63%:%
@@
 %:%125=82%:%
-%:%127=85%:%
-%:%128=85%:%
-%:%130=86%:%
-%:%131=87%:%
+%:%126=83%:%
+%:%127=84%:%
+%:%129=87%:%
+%:%130=87%:%
 %:%132=88%:%
-%:%135=90%:%
-%:%136=91%:%
+%:%133=89%:%
+%:%134=90%:%
 %:%137=92%:%
@@
 %:%141=96%:%
-%:%143=99%:%
-%:%144=99%:%
-%:%146=100%:%
-%:%147=101%:%
-%:%148=101%:%
-%:%149=102%:%
-%:%150=102%:%
-%:%151=103%:%
-%:%153=104%:%
-%:%154=104%:%
-%:%155=105%:%
-%:%156=105%:%
-%:%157=106%:%
-%:%159=107%:%
-%:%160=108%:%
+%:%142=97%:%
+%:%143=98%:%
+%:%145=101%:%
+%:%146=101%:%
+%:%148=102%:%
+%:%149=103%:%
+%:%150=103%:%
+%:%151=104%:%
+%:%152=104%:%
+%:%153=105%:%
+%:%155=106%:%
+%:%156=106%:%
+%:%157=107%:%
+%:%158=107%:%
+%:%159=108%:%
 %:%161=109%:%
@@
 %:%163=111%:%
-%:%166=115%:%
-%:%167=116%:%
+%:%164=112%:%
+%:%165=113%:%
 %:%168=117%:%
@@
 %:%175=124%:%
+%:%176=125%:%
 %:%177=126%:%
-%:%178=126%:%
-%:%179=127%:%
-%:%181=128%:%
-%:%184=130%:%
-%:%185=131%:%
+%:%179=128%:%
+%:%180=128%:%
+%:%181=129%:%
+%:%183=130%:%
 %:%186=132%:%
@@
 %:%196=142%:%
+%:%197=143%:%
 %:%198=144%:%
-%:%199=144%:%
-%:%201=145%:%
-%:%202=146%:%
+%:%200=146%:%
+%:%201=146%:%
 %:%203=147%:%
-%:%204=147%:%
-%:%205=148%:%
-%:%206=148%:%
-%:%208=149%:%
-%:%209=150%:%
-%:%210=150%:%
-%:%211=151%:%
-%:%212=151%:%
-%:%214=152%:%
-%:%217=154%:%
-%:%218=155%:%
+%:%204=148%:%
+%:%205=149%:%
+%:%206=149%:%
+%:%207=150%:%
+%:%208=150%:%
+%:%210=151%:%
+%:%211=152%:%
+%:%212=152%:%
+%:%213=153%:%
+%:%214=153%:%
+%:%216=154%:%
 %:%219=156%:%
 %:%220=157%:%
+%:%221=158%:%
 %:%222=159%:%
-%:%223=159%:%
-%:%224=160%:%
+%:%224=161%:%
 %:%225=161%:%
-%:%227=162%:%
-%:%228=162%:%
-%:%229=163%:%
-%:%231=164%:%
-%:%232=165%:%
-%:%233=165%:%
-%:%234=166%:%
-%:%236=167%:%
-%:%237=168%:%
+%:%226=162%:%
+%:%227=163%:%
+%:%229=164%:%
+%:%230=164%:%
+%:%231=165%:%
+%:%233=166%:%
+%:%234=167%:%
+%:%235=167%:%
+%:%236=168%:%
 %:%238=169%:%
@@
 %:%241=172%:%
-%:%242=172%:%
-%:%243=173%:%
-%:%245=174%:%
-%:%246=174%:%
-%:%247=175%:%
-%:%254=176%:%
-%:%255=176%:%
-%:%256=177%:%
-%:%257=177%:%
-%:%258=178%:%
-%:%259=178%:%
-%:%261=179%:%
-%:%262=180%:%
+%:%242=173%:%
+%:%243=174%:%
+%:%244=174%:%
+%:%245=175%:%
+%:%247=176%:%
+%:%248=176%:%
+%:%249=177%:%
+%:%256=178%:%
+%:%257=178%:%
+%:%258=179%:%
+%:%259=179%:%
+%:%260=180%:%
+%:%261=180%:%
 %:%263=181%:%
 %:%264=182%:%
-%:%265=182%:%
-%:%266=183%:%
-%:%267=183%:%
-%:%268=184%:%
-%:%269=184%:%
-%:%270=185%:%
-%:%271=185%:%
-%:%272=186%:%
-%:%273=186%:%
-%:%274=186%:%
-%:%276=187%:%
-%:%277=188%:%
-%:%278=188%:%
-%:%279=189%:%
-%:%289=191%:%
-%:%290=192%:%
+%:%265=183%:%
+%:%266=184%:%
+%:%267=184%:%
+%:%268=185%:%
+%:%269=185%:%
+%:%270=186%:%
+%:%271=186%:%
+%:%272=187%:%
+%:%273=187%:%
+%:%274=188%:%
+%:%275=188%:%
+%:%276=188%:%
+%:%278=189%:%
+%:%279=190%:%
+%:%280=190%:%
+%:%281=191%:%
 %:%291=193%:%
@@
 %:%303=205%:%
+%:%304=206%:%
 %:%305=207%:%
-%:%306=207%:%
-%:%307=208%:%
-%:%309=209%:%
-%:%310=210%:%
-%:%313=212%:%
-%:%314=213%:%
+%:%307=209%:%
+%:%308=209%:%
+%:%309=210%:%
+%:%311=211%:%
+%:%312=212%:%
 %:%315=214%:%
@@
 %:%321=220%:%
+%:%322=221%:%
 %:%323=222%:%
-%:%324=222%:%
-%:%325=223%:%
+%:%325=224%:%
 %:%326=224%:%
-%:%328=225%:%
-%:%329=225%:%
-%:%330=226%:%
-%:%332=227%:%
-%:%333=228%:%
-%:%334=228%:%
-%:%335=229%:%
-%:%337=230%:%
-%:%338=230%:%
-%:%339=231%:%
-%:%341=232%:%
-%:%342=232%:%
-%:%343=233%:%
-%:%346=234%:%
-%:%350=234%:%
-%:%351=234%:%
-%:%353=235%:%
-%:%354=236%:%
+%:%327=225%:%
+%:%328=226%:%
+%:%330=227%:%
+%:%331=227%:%
+%:%332=228%:%
+%:%334=229%:%
+%:%335=230%:%
+%:%336=230%:%
+%:%337=231%:%
+%:%339=232%:%
+%:%340=232%:%
+%:%341=233%:%
+%:%343=234%:%
+%:%344=234%:%
+%:%345=235%:%
+%:%348=236%:%
+%:%352=236%:%
+%:%353=236%:%
 %:%355=237%:%
@@
 %:%357=239%:%
-%:%367=242%:%
-%:%368=243%:%
+%:%358=240%:%
+%:%359=241%:%
 %:%369=244%:%
@@
 %:%411=286%:%
-%:%420=289%:%
-%:%432=292%:%
-%:%433=293%:%
-%:%434=294%:%
+%:%412=287%:%
+%:%413=288%:%
+%:%414=289%:%
+%:%423=292%:%
 %:%435=295%:%
@@
 %:%450=310%:%
+%:%451=311%:%
 %:%452=312%:%
-%:%453=312%:%
-%:%455=313%:%
-%:%456=313%:%
-%:%457=314%:%
-%:%458=314%:%
-%:%460=315%:%
-%:%461=316%:%
-%:%462=317%:%
-%:%463=317%:%
-%:%464=318%:%
-%:%465=318%:%
-%:%467=319%:%
-%:%468=319%:%
-%:%469=320%:%
-%:%470=320%:%
-%:%472=321%:%
-%:%473=321%:%
-%:%474=322%:%
-%:%475=322%:%
-%:%476=323%:%
-%:%478=324%:%
-%:%479=325%:%
-%:%482=327%:%
-%:%483=328%:%
-%:%484=329%:%
+%:%453=313%:%
+%:%455=315%:%
+%:%456=315%:%
+%:%458=316%:%
+%:%459=316%:%
+%:%460=317%:%
+%:%461=317%:%
+%:%463=318%:%
+%:%464=319%:%
+%:%465=320%:%
+%:%466=320%:%
+%:%467=321%:%
+%:%468=321%:%
+%:%470=322%:%
+%:%471=322%:%
+%:%472=323%:%
+%:%473=323%:%
+%:%475=324%:%
+%:%476=324%:%
+%:%477=325%:%
+%:%478=325%:%
+%:%479=326%:%
+%:%481=327%:%
+%:%482=328%:%
 %:%485=330%:%
+%:%486=331%:%
 %:%487=332%:%
-%:%488=332%:%
-%:%490=333%:%
-%:%491=333%:%
-%:%492=334%:%
-%:%493=334%:%
-%:%494=335%:%
-%:%496=336%:%
-%:%497=336%:%
-%:%498=337%:%
-%:%499=337%:%
-%:%501=338%:%
-%:%502=338%:%
-%:%503=339%:%
-%:%504=339%:%
-%:%505=340%:%
-%:%507=341%:%
-%:%508=342%:%
-%:%524=374%:%
-%:%525=375%:%
-%:%526=376%:%
+%:%488=333%:%
+%:%490=335%:%
+%:%491=335%:%
+%:%493=336%:%
+%:%494=336%:%
+%:%495=337%:%
+%:%496=337%:%
+%:%497=338%:%
+%:%499=339%:%
+%:%500=339%:%
+%:%501=340%:%
+%:%502=340%:%
+%:%504=341%:%
+%:%505=341%:%
+%:%506=342%:%
+%:%507=342%:%
+%:%508=343%:%
+%:%510=344%:%
+%:%511=345%:%
 %:%527=377%:%
@@
 %:%532=382%:%
+%:%533=383%:%
 %:%534=384%:%
-%:%535=384%:%
-%:%536=385%:%
-%:%537=386%:%
-%:%539=387%:%
-%:%540=387%:%
-%:%541=388%:%
-%:%543=389%:%
-%:%544=389%:%
-%:%545=390%:%
-%:%547=391%:%
-%:%548=392%:%
-%:%549=393%:%
+%:%535=385%:%
+%:%537=387%:%
+%:%538=387%:%
+%:%539=388%:%
+%:%540=389%:%
+%:%542=390%:%
+%:%543=390%:%
+%:%544=391%:%
+%:%546=392%:%
+%:%547=392%:%
+%:%548=393%:%
 %:%550=394%:%
 %:%551=395%:%
-%:%552=395%:%
-%:%553=396%:%
-%:%555=397%:%
-%:%556=398%:%
-%:%557=399%:%
+%:%552=396%:%
+%:%553=397%:%
+%:%554=398%:%
+%:%555=398%:%
+%:%556=399%:%
 %:%558=400%:%
@@
 %:%561=403%:%
-%:%562=403%:%
-%:%563=404%:%
-%:%565=405%:%
-%:%566=406%:%
-%:%567=406%:%
-%:%568=407%:%
-%:%571=408%:%
-%:%575=408%:%
-%:%576=408%:%
-%:%577=408%:%
-%:%579=409%:%
-%:%580=410%:%
-%:%581=411%:%
-%:%591=413%:%
-%:%592=414%:%
-%:%593=415%:%
+%:%562=404%:%
+%:%563=405%:%
+%:%564=406%:%
+%:%565=406%:%
+%:%566=407%:%
+%:%568=408%:%
+%:%569=409%:%
+%:%570=409%:%
+%:%571=410%:%
+%:%574=411%:%
+%:%578=411%:%
+%:%579=411%:%
+%:%580=411%:%
+%:%582=412%:%
+%:%583=413%:%
+%:%584=414%:%
 %:%594=416%:%
+%:%595=417%:%
 %:%596=418%:%
-%:%597=418%:%
-%:%598=419%:%
-%:%600=420%:%
-%:%601=420%:%
-%:%602=421%:%
-%:%604=422%:%
-%:%605=422%:%
-%:%606=423%:%
-%:%608=424%:%
-%:%609=424%:%
-%:%610=425%:%
-%:%612=426%:%
-%:%613=426%:%
-%:%614=427%:%
-%:%616=428%:%
-%:%617=429%:%
-%:%618=429%:%
-%:%619=430%:%
-%:%626=431%:%
-%:%627=431%:%
-%:%628=432%:%
-%:%629=432%:%
-%:%630=433%:%
-%:%631=433%:%
-%:%632=433%:%
-%:%633=434%:%
-%:%634=434%:%
-%:%635=435%:%
-%:%636=435%:%
-%:%637=435%:%
-%:%638=436%:%
-%:%639=436%:%
-%:%640=437%:%
-%:%641=437%:%
-%:%642=437%:%
-%:%643=438%:%
-%:%653=440%:%
-%:%654=441%:%
-%:%655=442%:%
+%:%597=419%:%
+%:%599=421%:%
+%:%600=421%:%
+%:%601=422%:%
+%:%603=423%:%
+%:%604=423%:%
+%:%605=424%:%
+%:%607=425%:%
+%:%608=425%:%
+%:%609=426%:%
+%:%611=427%:%
+%:%612=427%:%
+%:%613=428%:%
+%:%615=429%:%
+%:%616=429%:%
+%:%617=430%:%
+%:%619=431%:%
+%:%620=432%:%
+%:%621=432%:%
+%:%622=433%:%
+%:%629=434%:%
+%:%630=434%:%
+%:%631=435%:%
+%:%632=435%:%
+%:%633=436%:%
+%:%634=436%:%
+%:%635=436%:%
+%:%636=437%:%
+%:%637=437%:%
+%:%638=438%:%
+%:%639=438%:%
+%:%640=438%:%
+%:%641=439%:%
+%:%642=439%:%
+%:%643=440%:%
+%:%644=440%:%
+%:%645=440%:%
+%:%646=441%:%
 %:%656=443%:%
@@
 %:%688=475%:%
+%:%689=476%:%
+%:%690=477%:%
+%:%691=478%:%

### 2022-03-14 paper/output/document/thesis_5_discussion.tex
CLEANING DONE

@@
 %
+\begin{center}
+\begin{figure}
+\includegraphics[scale=0.43]{AI_engine.png}
+\caption{An example of an ethics engine for an artificial agent. This ethics engine passes a moral dilemma 
+through an input parser, applies the automated categorical imperative test, and finally processes the 
+output using an output parser, producing a prescription for action. I contribute the automated categorical 
+imperative component.} \label{fig:AIengine}
+\end{figure}
+\end{center}
+%
 \begin{isamarkuptext}%
@@
 nuanced ethical reasoning. In this section, I outline the additional components necessary for my system
-to guide AI agents in practice. As it stands, my system is a categorical imperative library that takes 
-as input the logical representation of a maxim and returns its moral status (if it is obligatory, 
+to guide AI agents in practice. As it stands, my system is a categorical imperative library that, given
+sufficient factual or ``common sense'' background, can take 
+as input the logical representation of a maxim and return its moral status (if it is obligatory, 
 prohibited, or permissible). My project potentially 
@@
 into a prescription for action that the AI agent could act on. Figure \ref{fig:AIengine} depicts the 
-workflow of this example ethics engine.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{center}
-\begin{figure}
-\includegraphics[scale=0.43]{AI_engine.png}
-\caption{An example of an ethics engine for an artificial agent, which begins with a moral dilemma, 
-passes it through an input parser, applies the automated categorical imperative test, and then processes the 
-output using an output parser. I contribute the automated categorical imperative component.} \label{fig:AIengine}
-\end{figure}
-\end{center}
-%
-\begin{isamarkuptext}%
+workflow of this example ethics engine.
+
 In this workflow, an AI agent is faced with a moral dilemma in some internal representation. The input
@@
 action. In order for my system to be used in an AI agent using the workflow
-above, future work would need to develop such input and output parsers.
-
-The input parser must translate a complex real-world situation into a flat, logical representation.
+above, future work must develop such input and output parsers.
+
+One of the biggest challenges for an ethics engine is the development of an input parser. An input parser 
+for my implementation of automated Kantian ethics must translate a complex real-world situation into a flat, logical representation.
 This requires that the input parser determine which circumstances are morally relevant
 to a maxim, a controversial judgement. As mentioned in Section \ref{whatisamaxim},
-there is robust debate in the literature on the circumstances that should be considered when formulating a maxim, 
-inspired by the tailoring objection, a common criticism of Kantian ethics. Recall that the tailoring objection is the worry that arbitrarily specific 
+there is robust debate on the circumstances that should be considered when formulating a maxim, 
+inspired by a common criticism of Kantian ethics called the tailoring objection. Recall that the 
+tailoring objection is the worry that arbitrarily specific 
 circumstances render any maxim universalizable. For example, consider the maxim ``When my name is Lavanya Singh 
@@
 The Kantian response to this criticism is to require that the circumstances included in the formulation
-of the maxim be morally relevant. In the example above, my purple shirt and the date clearly have no bearing on 
+of the maxim be morally relevant. In the example above, my purple shirt and the date have no bearing on 
 the moral status of lying. On the other hand, consider the maxim, ``When I am unemployed, I will murder
@@
 for an agent to decide how they should behave, not for a third-party to judge their behavior. Ethics is 
-a personal process and the FUL is designed to help agents make decisions. Because agents use 
+a personal process and the FUL is designed to help agents make decisions for themselves. Because agents use 
 the FUL to evaluate their own behavior, the test is at its 
@@
 ``surface intent'' \citep[87]{constofreason}. The FUL is supposed to determine if an agent's principle of action
-is universally consistent, so it is most effective when an agent accurately formulates the principle
+is universally consistent, so it is most effective when an agent accurately formulates the principle that
 they act on. Circumstances are morally relevant if they reflect the way that the agent is 
@@
 
-While the above account how a well-intentioned human agent can determine 
-morally relevant circumstances, the challenge remains open for automated ethics. In order for an automated
-ethical agent to use the categorical imperative to its fullest extent, the input maxim must be a good-faith 
-attempt to capture the agent's principle
-of action. However an action is turned into a maxim for my system to process, whether manually as I did
-in Chapter \ref{applications} or using an automatic input parser, this transformation must be a good-faith 
-attempt to capture the principle of action. Translating everyday situations into appropriate maxims is 
-the bulk of the work that a Kantian human 
-being does when making decisions. Common misconceptions about Kantian ethics\footnote{For example, critics 
-of Kantian ethics worry that the maxim, ``When I am a
-man, I will marry a man because I want to spend my life with him'' fails the universalizability
-test because if all men only married men, sexual reproduction would stop. This argument implies 
-that Kantian ethics is homophobic. Kantians often respond by arguing that the correct formulation of 
-this maxim is, ``When I love a man, I will marry him because I want to spend my life with him,'' which
-is universalizable because if everyone marries who they love, some men will marry women and others will
-marry men.} often result from incorrectly formulated maxims, 
-and the entire field of applied Kantian ethics is devoted to generating the right kinds of maxims to test.
+While the above account explains how a well-intentioned human agent can determine 
+morally relevant circumstances, the challenge remains open for automated ethics. However an action is turned into a maxim for my system 
+to process, whether manually as I did in Chapter \ref{applications} or using an automatic input 
+parser, this transformation must be a good-faith attempt to capture the principle of action. 
+Correctly formulating a maxim requires what Kantians call ``practical judgement,'' or
+common sense reasoning and factual background \citep{oneilluniversallaws}. Returning to the example above, noticing that being 
+unemployed may contribute to one's desire to steal another's job requires practical
+judgement, not just pure reason alone. Translating everyday situations into appropriate maxims is
+the bulk of the reasoning that a Kantian human being does when making decisions. Automating this
+reasoning requires endowing a machine with common sense.
 
@@
 in an AI ethics engine. One solution is for a human being to perform the role of the input
-parser. Once an AI agent stumbles onto an ethical dilemma, a human being could take over, formulate 
+parser by supervising the operation of an AI agent. When the agent stumbles onto
+an ethical dilemma, the human could take over, formulate
 the right question, and feed it into the categorical imperative library to see what action the categorical 
-imperative would prescribe. For proponents of the ``human-in-the-loop'' model of AI ethics, in which 
+imperative would prescribe. Alternatively, AI developers can identify expected ethical dilemmas 
+that the machine may face in advance and hardcode their own judgements for these dilemmas. 
+For proponents of the ``human-in-the-loop'' model of AI ethics, in which
 ethical AI requires that humans guide machines, this kind of human involvement may be a feature \citep{loop}.
-The outcome of the universalizability test will depend on how the human formulates the maxim; if the 
-human puts garbage into the test, the test will return garbage out.
+Both of these solutions imply that the outcome of the universalizability test will depend on how the 
+human formulates the maxim; if the human puts garbage into the test, the test will return garbage out.
 
@@
 It is likely that, just as implementations of automated ethics choose 
-a particular ethical theory and implement it, different implementations of such an input parser would 
+a particular ethical theory and implement it, different implementations of such an input parser may 
 adopt different interpretations of maxim formulation and morally relevant circumstances.
@@
 that involve morally important entities. I discuss a potential machine-learning based approach which formulates
-maxims based on a training set of appropriately formulated maxims in Section \ref{amapossible}.
-Determining morally relevant circumstances, either using heuristics or human involvement, is a ripe 
-area for future work.
+maxims based on a training set of appropriately formulated maxims in Section \ref{amapossible}. This 
+approach mimics how human beings formulate maxims; we use common sense and prior situational, 
+factual, and ethical knowledge to isolate our principle of action. Determining morally relevant circumstances, 
+either using heuristics or human involvement, is a ripe area for future work.
 
@@
 Different applications of my system may require different factual background (e.g. a self-driving car 
-would need to know traffic regulations), so this common sense database may need to be application 
+needs to know traffic regulations), so this common sense database will need to be application 
 specific. As demonstrated in the examples in Chapter \ref{applications}, my system can produce sophisticated 
-judgements with relatively little situational context. While the need for factual background is a challenge
-for automated ethics, Chapter \ref{applications} demonstrates that it is less daunting than it seems.
+judgements with relatively little situational context. Thus, while my automated categorical imperative
+requires some common sense and factual background, Chapter \ref{applications} demonstrates that automating
+this common sense is less daunting than it seems.
 
@@
 give AI agents the capacity for sophisticated ethical reasoning faithful to philosophical literature. 
-This represents an improvement over existing AI ethics, which rarely captures the complexity 
+This represents an improvement over existing automated ethics, which rarely captures the complexity 
 of any ethical theory that philosophers plausibly defend.%
@@
 precisely about the phenomena they model, computational ethics can help philosophers ask and answer
-new philosophical questions. In this section, I share an example of the kind of philosophical insight that computational ethics 
-can prompt and analyze the value that this tool can offer to philosophers.%
+new philosophical questions. In Section \ref{joking}, I presented one example of the power of computational ethics
+by using my system to isolate a necessary and sufficient condition for the act of lying, or knowingly saying
+something false, to be wrong. In this section, I share another example of the kind of philosophical 
+insight that computational ethics can prompt and analyze the value that this tool can offer to philosophers.\footnote{
+I present a final example of computational ethics in Appendix \ref{weirdtests}, where I resolve an ambiguity 
+in Korsgaard's argument for the wrongness of false promising using my system \citep{KorsgaardFUL}.} 
+Fields from protein folding to game theory are uncovering new insights using computational tools, and computational
+ethics harnesses this power to inspire similar progress in philosophy.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 a circumstance, act, goal tuple (c, a, g) is well-formed if $(\neg (c \longrightarrow a) ) \wedge 
-(\neg(c \longrightarrow g))$. The insight that the FUL should not apply to badly-formed maxims has 
-philosophical value and serves as evidence of the potential of computational ethics.
-
-\noindent \textbf{Philosophical Implications of Badly-Formed Maxims}
+(\neg(c \longrightarrow g))$, or if the circumstances do not imply the act or the goal. The insight
+that the FUL does not apply to badly-formed maxims has philosophical value and serves as evidence 
+of the potential of computational ethics. In the next section, I explain and explore this insight using 
+Kantian literature. In the following section, I demonstrate the philosophical implications of well-formed
+maxims by using this insight to resolve a tension between self-doubt and self-respect. The idea of well-formed
+maxims can guide the formulation of maxims and thus may have implications for many parts of Kantian ethics.
+
+\noindent \textbf{Badly-Formed Maxims and Kantian Ethics}
 
 Isabelle gave a logical argument for why the FUL can only hold for well-formed maxims, and I return to Kantian
-literature to better understand the philosophical implications of this idea. Because badly-formed maxims
+literature to better understand this idea. In this section, I argue that 
+because badly-formed maxims
 neither change an agent's behavior nor generate meaningful obligations, they are not the right kinds of 
@@
 eat breakfast.'' There is something empty about this maxim because acting on it could never result in 
-any action. If I adopts this maxim as a principle to live by,
+any action. If I adopt this maxim as a principle to live by,
 I decide that, in the circumstances ``eating breakfast'' I will perform the act ``eating breakfast''
@@
 to decide how to act. A badly-formed maxim is not the kind of maxim that a practical reasoner should consider, because it
-will have no bearing on what the agent should do. It makes no sense of ask, ``Should I act on a badly-formed
-maxim?'' because the answer to this question cannot change your behavior. There is no explicit prohibition 
-against a badly-formed maxim, but it is the wrong kind of question for a practical reasoner to ask.
+will have no bearing on what the agent should do.
 
@@
 Above, I defined badly formed maxims, a philosophical concept that I discovered
-using computational ethics. In this section, I explore the implications of this concept for a 
-philosophical debate to show that computational ethics can result in insights with real 
-philosophical weight. I use badly formed maxims to resolve the tension between self-doubt and self-respect. 
-This debate originated in epistemology, which values doubting your beliefs but also rationally requires
-that you believe that you are not mistaken (else you should update your beliefs). 
-Self-doubt and self-respect also compete in ethics, where questioning your judgements is valuable but 
-questioning a commitment as you make it is impossible. Self-doubt and self-respect appear 
+using computational ethics. In this section, I explore the implications of this concept for the ethical
+tension between self-doubt and self-respect to show that computational ethics can result in insights with real 
+philosophical weight. The debate between self-doubt and self-respect originates in epistemology, which 
+values doubting your beliefs but also rationally requires that you believe that you are not mistaken 
+(else you should update your beliefs). I present a parallel tension between self-doubt and self-respect
+in ethics, where questioning your judgements is valuable but 
+questioning a commitment as you make it is impossible. Ethical self-doubt and self-respect appear 
 irresolvably opposed until they are understood through the lens of badly formed maxims. I argue that naive
 conceptions of self-doubt are badly formed maxims in disguise. If we reformulate these maxims to be well-formed,
-the tension between self-doubt and self-respect dissolves, and it becomes clear that both concepts can
-co-exist. I sketch the details of this argument in the rest of this section. I will conclude that 
-badly-formed maxims serve as one guide to the formulation of maxims, and thus may have bearing on 
-other debates in Kantian ethics as well. I first introduce the tension between self-doubt and self-respect 
+the tension between self-doubt and self-respect dissolves. I sketch the details of this argument in 
+the rest of this section. I first introduce the tension between self-doubt and self-respect 
 in epistemology, then explain the parallel tension in ethics, and finally present a resolution of this 
-tension using badly-formed maxims.
+tension using badly-formed maxims. I conclude that well-formed maxims form a boundary condition for
+the formulation of maxims, so they may resolve many debates in Kantian literature and ethics more generally.
 
@@
 rationally believe both that the sky is blue and that I believe that the sky is green. In other words, I cannot 
-disapprove of my own credences, since if I do disapprove of them, I would just abandon them. Christensen 
+disapprove of my own credences, since if I do disapprove of them, I should just abandon them. Christensen 
 argues that this principle, which he abbreviates to SR, holds because 
@@
 
-While most philosophers accept some version of SR\footnote{Christensen cites \citet{vanfraassen}, 
-\citet{vickers}, and \citet{koons}.}, 
+While most philosophers accept some version of SR,\footnote{Christensen cites \citet{vanfraassen}, 
+\citet{vickers}, and \citet{koons}.}
 Roush argues that the principle must be modified in order to account for healthy epistemic 
@@
 
-To resolve this tension, I return to my earlier example of a dancer. Imagine Sara is dancing at a 
+I now argue that well-formed maxims can resolve this tension. As in my earlier example, imagine that Sara is dancing at a 
 weddding, when, in a moment of angst, she asks herself, ``Should I really be dancing right now?'' 
 It seems that she asking if the maxim, ``When dancing at your friend's wedding, dance for the sake 
-of dancing'' is a permissible maxim to act on. Notice that the maxim in question is badly-formed: the 
+of dancing'' is a permissible maxim to act on. This maxim is badly-formed: the 
 circumstance ``when dancing at a friend's wedding'' implies the act ``dance.'' As I argued above, if 
 Sara asks if she should will a badly formed maxim, she is questioning her own will's authority, which
-is paradoxical. If maxims are about self-doubt are badly-formed maxims, then the tension between ESR
+is paradoxical. If expressions of self-doubt are badly-formed maxims, then the tension between ESR
 and ESD is natural and unavoidable: debating the permissibility of a badly-formed maxim inherently
@@
 
-If ethical self-doubt as badly-formed maxim contradicts self-respect, then resolving this issue requires a 
+Because understanding ethical self-doubt as a badly-formed maxim contradicts self-respect, resolving this issue requires a 
 different interpretation of ethical self-doubt. Under this interpretation, 
@@
 literature revolve around incorrectly formulated maxims, which means that the insight about badly
-formed maxims may have bearing on these debates. Much of the work of a Kantian ethicist is formulating an
+formed maxims may have bearing on these debates. Common misconceptions about Kantian ethics\footnote{For example, critics
+of Kantian ethics worry that the maxim, ``When I am a
+man, I will marry a man because I want to spend my life with him'' fails the universalizability
+test because if all men only married men, sexual reproduction would stop. This argument implies 
+that Kantian ethics is homophobic. Kantians often respond by arguing that the correct formulation of 
+this maxim is, ``When I love a man, I will marry him because I want to spend my life with him,'' which
+is universalizable because if everyone marries who they love, some men will marry women and others will
+marry men.} often result from incorrectly formulated maxims, 
+and the entire field of applied Kantian ethics is devoted to generating the right kinds of maxims to test. 
+Much of the work of a Kantian ethicist is formulating an
 appropriate maxim, and badly-formed maxims define one boundary condition for this task. Just as my isolation
@@
 require that assumptions like the exclusion of well-formed maxims are made precise, and thus force 
-philosophers to understand their arguments in a new way. This precision is also evident in the philosophical 
-implications of my examination of lying and joking in Section \ref{joking}, where I isolated the 
-specific cause of lying's wrongness. These examples demonstrate the contributions
+philosophers to understand their arguments in a new way. The philosophical insights about lying in Section
+\ref{joking} and about well-formed maxims above demonstrate the contributions
 that computational ethics makes: it can quickly check edge cases and it uncovers imprecise, ambiguous,
@@
 
-I do not argue that computational ethics uncovers philosophical insights that humans are incapable 
-of reaching. Instead, I claim that insights like the one about well-formed maxims are much easier
-to reach with computational tools. Computational 
-tools prompt philosophers to ask new questions that 
-lead to insights, and can thus serve as another tool in a philosopher's arsenal, like a 
-thought experiment or counterexample.\footnote{Even if computational ethics is possible, some may 
-worry that it sacrifices something important about philosophical inquiry. I discuss this concern in Appendix 
-\ref{academicphilosophy}.}
+I do not argue that computational ethics uncovers philosophical insights that humans are always incapable 
+of reaching. In some cases, computational ethics may automate calculations too long and tedious for 
+any human philosopher to complete. Insights like the one about well-formed maxims, however, could 
+have been discovered by a human being but are much easier to reach with computational tools. Computational tools prompt philosophers 
+to ask new questions that lead to insights, and can thus serve as another tool in a philosopher's arsenal, like a 
+thought experiment or counterexample.
 
@@
 that ordinary discussion does not necessarily require. For example, when formalizing the notion of a 
-maxim, I had to understand its components and define it as a circumstance, act, goal tuple. Moreover, 
-Isabelle's strict typing system required that I define coherent, consistent types for each of these 
-entities and for a maxim as a whole. This precision is possible without computational tools, but 
-computational ethics forces a level of precision that ordinary discussion does not demand. Type 
-fuzziness and overloaded definitions are all too common in philosophical writing and 
-discussion, but computers diaallow this kind of imprecision.
+maxim, I had to understand its components, define it as a circumstance, act, goal tuple, and identify
+coherent and consistent types for each of these entities. This precision is also evident in my examination
+of lying and joking in Section \ref{joking}, where I isolate the specific cause of lying's wrongness.
+This insight could contribute to the rich philosophical literature on deception, and demonstrates the 
+philosophical signifiance of precision. This level of precision is possible 
+without computational tools, but computational ethics forces a level of precision that ordinary discussion 
+does not demand. Type fuzziness and overloaded definitions are all too common in philosophical writing and 
+discussion, but computers disallow this kind of imprecision.
 
@@
 
-Computational ethics is at its infancy. The use of theorem provers in mathematics is just now beginning 
+Computational ethics is at its infancy. The use of theorem provers in mathematics is only now beginning 
 to make headway \citep{buzzardvideo}, even though theorem provers were first invented in the 1960's \citep{historyofITP}. 
-In contrast, the first attempts to use theorem provers for progress in any kind of philosophy occurred 
-in the last few years \color{red} and, at the time of this writing, no known work has used theorem 
-provers for computational ethics \color{black}. The 
-fact that this nascent technology is already helping humans reach non-trivial philosophical conclusions 
+In contrast, the first attempts to use theorem provers to automate deontic logic occurred in the last
+few years. The 
+fact that this nascent technology is already helping humans reach non-trivial ethical conclusions 
 is reason to, at the very least, entertain the possibility of a future where computational ethics 
@@
 become as commonplace in philosophy departments as reflective equilibrium. Just as computational tools
-have supercharged progress in healthcare and drug discovery, computational ethics has the potential for
+have amplified progress in healthcare and drug discovery, computational ethics has the potential to enable
 great philosophical progress.%
@@
 dilemmas? Some may hope (or worry) that automated ethics could render ethical reasoning obsolete. In 
-this section, I argue, that while computers should not replace human ethical reasoning entirely,
+this section, I argue that while computers should not replace human ethical reasoning entirely,
 they can supplement and improve our ethical reasoning. I argue for a kind of human-computer symbiosis
@@
 an Ethics Oracle that can unfailingly tell you the right thing to do in any 
-situation.\footnote{This example is inspired by the Pocket Oracle presented in \citet{bok}.} Someone 
+situation.\footnote{This example is inspired by the Pocket Oracle presented in \citet{bok}. Unlike the
+Ethics Oracle, Bok's Pocket Oracle perfectly predicts what we \emph{will} do, not what we \emph{should} do.} Someone 
 who surrenders themselves to this Oracle unthinkingly follows its prescriptions. 
@@
 impossible to automate ethical reasoning. After all, computers may eventually learn to simulate human 
-mental activity entirely, as shown by progress in brain simulation \citep{brainsimulation}.
-
-In this section, I explore potential arguments for why the categorical imperative could not be automated. When 
-philosophers say that the categorical imperative is not an algorithm, they are often are gesturing to the complexity
-of ethical judgement. They refer to the difficulty in determining morally relevant circumstances of a maxim or the common 
-sense required for a computer to behave ethically as arguments against a categorical imperative ``algorithm.'' 
-I will show in this section that these difficulties do not render automated Kantian ethics impossible, but 
-merely difficult. There categorical imperative may not provide a simple and immediate algorithm, but, as
-I demonstrate in this thesis, some parts of moral judgement using the FUL can be automated using not one
-algorithm, but the many algorithms necessary to automatically prove logical theorems.
+mental activity entirely, as shown by progress in brain simulation \citep{brainsimulation}. Skeptics
+about automated ethics must explain why ethics is any different from other automated human activities.
+
+The above claims represent the general view that automating ethics is impossible. In the
+rest of this section, I explore specific arguments within this view. First, I consider the argument 
+that machines cannot have the necessary motivations or attitude towards action to behave morally. Second, 
+I consider the difficulty of formulating
+an input to the categorical imperative. Third, I consider the strongest objection to automated ethics, 
+that moral judgement requires prior ethical knowledge and intuition that machines lack. I argue that 
+these objections do not render automated Kantian ethics impossible, but merely difficult. Rawls may be 
+correct that there is no simple algorithm for ethical reasoning, but, as
+I demonstrate in this thesis, moral judgement using the FUL can be automated using not one
+algorithm, but the many algorithms that constitute my system.
+
+\medskip
+
+\noindent \textbf{Machines, Morality, and Motivation}
 
@@
 moral behavior. She points out that Kant draws an important distinction between a morally worthy maxim
-and a morally worthy action: the latter requires a good will, or a will motivated by duty. She argues that, 
-``Kant defines duty not (as would be common today) as outward performance of a certain sort, but as action
-that embodies a good will'' \citep[345]{oneilluniversallaws}. Moral behavior doesn't just require performing
+and a morally worthy action: the latter requires a good will, or a will motivated by duty \citep[345]{oneilluniversallaws}. 
+Moral behavior doesn't just require performing
 a ``good'' action, but it requires acting on a morally worthy maxim from the motivation of duty, or 
@@
 because we have wills, or the ability to be motivated by ends
-that we choose. Only rational beings have wills, so only rational beings can have good wills, or wills
-motivated by duty, and thus only rational beings can behave morally. Under this understanding
+that we choose. Only rational beings have wills, so only rational beings can have good wills, so only 
+rational beings can behave morally. Under this understanding
 of moral behavior, it seems unlikely that a computer could behave morally
-since a computer does not have motivation in the same way as a human being. If a computer is not a fully rational
-being, then it is not the kind of thing that can behave morally.\footnote{A parallel argument can also be made for virtue ethics. Virtuous
+since a computer does not have motivation in the same way as a human being.\footnote{A parallel argument can also be made for virtue ethics. Virtuous
 behavior requires not only a certain action, but also a certain disposition towards the action, so it seems
@@
 
-The idea that, under Kant's account, a computer cannot behave morally, does not preclude the kind 
+The idea that a computer cannot behave morally does not preclude the kind 
 of automated categorical imperative that I present in this thesis. O'Neill argues that the FUL
 serves as a test of morally worthy maxims, and a implementation of an automated categorical imperative can 
-identify this kind of maxim. Perhaps a computer cannot act on a morally relevant maxim from a motivation of duty, 
+identify this kind of maxim. Perhaps a computer cannot act on a morally relevant maxim from the motivation of duty, 
 but it certainly can act on this maxim nonetheless. For example, a self-driving car can choose to swerve to hit a tree
 to avoid injuring pedestrians in the crosswalk. This action may be one that acts on a morally worthy maxim
-\emph{even if} the self-driving car is not motivated by duty. The discpline of machine ethics is partially
+\emph{even if} the self-driving car is not motivated by duty. The discpline of machine ethics is
 spurred by the recognition that, as automated agents become more powerful, they will need to make
-morally consequential decisions. Automated agents may be incapable of moral behavior, but automated agents that mimic
-moral behavior are better than agents that ignore morality entirely. Worries about unethical AI
-stem from the fact that AI agents are navigating a world inhabited by human beings, and their decisions
-impact us. Insofar as we are building AI that will operate in human society, the behavior of such AI 
-should mimic the behavior of an ethical human being. AI needs to be ethical for our sakes, so that we 
-can interact with it safely. If AI conforms to human ethics, then it will navigate the world
-in a way that benefits human beings.
-
-Another challenge for automated Kantian ethics identified by O'Neill is that the FUL test requires that
+morally consequential decisions. Automated agents may be incapable of moral motivation, but automated agents that mimic
+moral behavior are better than agents that ignore morality entirely. AI agents are navigating a world 
+inhabited by human beings, and their decisions impact us. Insofar as AI will operate in human society, 
+the behavior of such AI should mimic the behavior of an ethical human being for our sakes, so that we 
+can interact with it safely.
+
+\medskip
+
+\noindent \textbf{Inputs to the Categorical Imperative}
+
+Another challenge for automated Kantian ethics is that the FUL test requires that
 a maxim be given as input. O'Neill notes that the test assumes ``that agents will have certain tentative 
@@
 The FUL evaluates the moral worth of a maxim given as input, where this potential maxim is generated by 
-the choices that an agent is faced with. Determining this potential maxim is a challenge for both human
+the choices that an agent is faced with. As I argue in Section \ref{AIethics}, determining this potential maxim is a challenge for both human
 and automated reasoners. Kant even claims that the difficulty of determining an agent's potential maxim, which is their
@@
 choices between potential actions and must determine the maxim, or principle, underlying each potential action.
-This is equivalent to a ``mapping'' problem: agents are given situations or dillemas as input and must map
+This is equivalent to a ``mapping'' problem: agents are given situations or dilemmas as input and must map
 these to maxims.
@@
 I argued that, before my system can be used in practice, it must be paired with an input parser that can
-translate choices that an automated agent faces into maxims in a logic that my system can
+translate choices that an automated agent faces into maxims into a logic that my system can
 evaluate. This need follows from the difficulty in mapping a potential action
 to the maxim of action, whether concerning human action or machine action. As argued in Section \ref{AIethics},  
-this is not an insurmountable obstacle for automated ethics and heuristic-based approaches could resolve
-this issue. Determining the maxim of action is a challenge for Kantian human beings \citep{oneilluniversallaws}, 
-so it is unsurprising that it is a major hurdle for automated Kantian agents.
+human-in-the-loop or heuristic-based approaches could resolve this issue. Determining the maxim of 
+action is a challenge for Kantian human beings \citep{oneilluniversallaws}, so it is unsurprising that 
+it is a major hurdle for automated Kantian agents. Overcoming this hurdle is not impossible, and progress
+in automated ethics could address this concern.
+
+\medskip
+
+\noindent \textbf{Prior Moral Knowledge}
 
@@
 Understanding the categorical imperative test as a reminder
-instead of a derivation tool also explains the fact noted in Section \ref{AIethics} that the FUL cannot 
+instead of a derivation tool also explains the response to the tailor objection presented in Section \ref{AIethics}, that the FUL cannot 
 handle bad-faith attempts to generate false positives or negatives. The test only returns the right 
@@
 \caption{A refined version of Figure \ref{fig:AIengine} in which the input parser learns from a database
-of action-maxim mappings, which is in turn fed the output of my automated Kantian ethics system. } \label{fig:inputparser}
+of action-maxim mappings, which is in turn fed the output of my automated categorical imperative. } \label{fig:inputparser}
 \end{figure}
@@
 \begin{isamarkuptext}%
-This understanding of the role of the categorical imperative not only fails to render automated moral
-reasoning impossible, but it also offers insight into how to solve the challenge of creating an input parser.
+Under Tafani's understanding of the categorical imperative, not only is automated moral reasoning
+possible, but the challenge of creating an input parser or automatically formulating a maxim becomes 
+easier as well. 
 If the categorical imperative test is only useful to those who have some prior moral knowledge, then prior moral
-knowledge can and should be used to create an input parser. Specifically, some kind of machine learning-based approach
+knowledge can and should be used to create an input parser. Specifically, a machine learning-based approach
 could learn action-maxim mappings from a database of such mappings compiled by a human being. Moreover, 
@@
 Because Delphi draws on error-prone human judgements instead of philosophical literature, it makes 
-the same judgement errors that humans make. Moreover, because Delphi used a bottom-up approach, 
+the same judgement errors that humans make. Moreover, because Delphi uses a bottom-up approach, 
 there is no explicit ethical theory explaining its judgements, so analytically arguing for or 
@@
 contradiction interpretation. There has also been prior work in formalizing Kantian metaphysics 
-using I/O logic \citep{io}. Deontic logic, which has been implemented in Isabelle/HOL, itself is inspired 
+using I/O logic \citep{io}. Deontic logic, which has been implemented in Isabelle/HOL, is itself inspired 
 by Kant's ``ought implies can'' principle, but it does not include a robust formalization of the entire 
@@
 implement this logic in the Isabelle/HOL interactive theorem prover, which can automatically prove or 
-refute theorems in my custom logic. I also contribute a testing framework that I use to demonstrate that
+refute theorems in my custom logic. I also contribute a testing framework that demonstrates that
 my implementation of Kantian ethics is more faithful to philosophical literature than two other 
@@
 %:%28=8%:%
-%:%40=10%:%
-%:%41=11%:%
-%:%42=12%:%
-%:%43=13%:%
-%:%44=14%:%
-%:%45=15%:%
-%:%46=16%:%
-%:%47=17%:%
-%:%48=18%:%
-%:%49=19%:%
+%:%39=11%:%
+%:%40=12%:%
+%:%41=13%:%
+%:%42=14%:%
+%:%43=15%:%
+%:%44=16%:%
+%:%45=17%:%
+%:%46=18%:%
+%:%47=19%:%
+%:%50=21%:%
+%:%51=22%:%
 %:%52=23%:%
@@
 %:%59=30%:%
-%:%62=32%:%
-%:%63=33%:%
-%:%64=34%:%
-%:%65=35%:%
-%:%66=36%:%
-%:%67=37%:%
-%:%68=38%:%
-%:%69=39%:%
-%:%70=40%:%
-%:%71=41%:%
-%:%72=42%:%
-%:%73=43%:%
-%:%74=44%:%
-%:%75=45%:%
-%:%76=46%:%
-%:%77=47%:%
-%:%78=48%:%
-%:%79=49%:%
-%:%80=50%:%
-%:%81=51%:%
-%:%82=52%:%
-%:%83=53%:%
-%:%84=54%:%
-%:%85=55%:%
-%:%86=56%:%
-%:%87=57%:%
-%:%88=58%:%
-%:%89=59%:%
-%:%90=60%:%
-%:%91=61%:%
-%:%92=62%:%
-%:%93=63%:%
-%:%94=64%:%
-%:%95=65%:%
-%:%96=66%:%
-%:%97=67%:%
-%:%98=68%:%
-%:%99=69%:%
-%:%100=70%:%
-%:%101=71%:%
-%:%102=72%:%
-%:%103=73%:%
-%:%104=74%:%
-%:%105=75%:%
-%:%106=76%:%
-%:%107=77%:%
-%:%108=78%:%
-%:%109=79%:%
-%:%110=80%:%
-%:%111=81%:%
-%:%112=82%:%
-%:%113=83%:%
-%:%114=84%:%
-%:%115=85%:%
-%:%116=86%:%
-%:%117=87%:%
-%:%118=88%:%
-%:%119=89%:%
-%:%120=90%:%
-%:%121=91%:%
-%:%122=92%:%
-%:%123=93%:%
-%:%124=94%:%
-%:%125=95%:%
-%:%126=96%:%
-%:%127=97%:%
-%:%128=98%:%
-%:%129=99%:%
-%:%130=100%:%
-%:%131=101%:%
-%:%132=102%:%
-%:%133=103%:%
-%:%134=104%:%
-%:%135=105%:%
-%:%136=106%:%
-%:%137=107%:%
-%:%138=108%:%
-%:%139=109%:%
-%:%140=110%:%
-%:%141=111%:%
-%:%142=112%:%
-%:%143=113%:%
-%:%144=114%:%
-%:%145=115%:%
-%:%146=116%:%
-%:%147=117%:%
-%:%148=118%:%
-%:%149=119%:%
-%:%150=120%:%
-%:%151=121%:%
-%:%152=122%:%
-%:%153=123%:%
-%:%154=124%:%
-%:%155=125%:%
-%:%156=126%:%
-%:%157=127%:%
-%:%158=128%:%
-%:%159=129%:%
-%:%160=130%:%
-%:%161=131%:%
-%:%162=132%:%
-%:%163=133%:%
-%:%164=134%:%
-%:%165=135%:%
-%:%166=136%:%
-%:%167=137%:%
-%:%168=138%:%
-%:%169=139%:%
-%:%170=140%:%
-%:%171=141%:%
-%:%180=143%:%
-%:%192=145%:%
-%:%193=146%:%
-%:%194=147%:%
-%:%195=148%:%
-%:%196=149%:%
-%:%205=151%:%
-%:%217=153%:%
-%:%218=154%:%
-%:%219=155%:%
-%:%220=156%:%
-%:%221=157%:%
-%:%222=158%:%
-%:%223=159%:%
-%:%224=160%:%
-%:%225=161%:%
-%:%226=162%:%
-%:%227=163%:%
-%:%228=164%:%
-%:%229=165%:%
-%:%230=166%:%
-%:%231=167%:%
-%:%232=168%:%
-%:%233=169%:%
-%:%234=170%:%
-%:%235=171%:%
-%:%236=172%:%
-%:%237=173%:%
-%:%238=174%:%
-%:%239=175%:%
-%:%240=176%:%
-%:%241=177%:%
-%:%242=178%:%
-%:%243=179%:%
-%:%244=180%:%
-%:%245=181%:%
-%:%246=182%:%
-%:%247=183%:%
-%:%248=184%:%
-%:%249=185%:%
-%:%250=186%:%
-%:%251=187%:%
-%:%252=188%:%
-%:%253=189%:%
-%:%254=190%:%
-%:%255=191%:%
-%:%256=192%:%
-%:%257=193%:%
-%:%258=194%:%
-%:%259=195%:%
-%:%260=196%:%
-%:%261=197%:%
-%:%262=198%:%
-%:%263=199%:%
-%:%264=200%:%
-%:%265=201%:%
-%:%266=202%:%
-%:%267=203%:%
-%:%268=204%:%
-%:%269=205%:%
-%:%270=206%:%
-%:%271=207%:%
-%:%272=208%:%
-%:%273=209%:%
-%:%274=210%:%
-%:%275=211%:%
-%:%276=212%:%
-%:%277=213%:%
-%:%278=214%:%
-%:%279=215%:%
-%:%280=216%:%
-%:%281=217%:%
-%:%282=218%:%
-%:%283=219%:%
-%:%284=220%:%
-%:%285=221%:%
-%:%286=222%:%
-%:%287=223%:%
-%:%288=224%:%
-%:%289=225%:%
-%:%290=226%:%
-%:%291=227%:%
-%:%292=228%:%
-%:%293=229%:%
-%:%294=230%:%
-%:%295=231%:%
-%:%296=232%:%
-%:%297=233%:%
-%:%298=234%:%
-%:%299=235%:%
-%:%300=236%:%
-%:%301=237%:%
-%:%302=238%:%
-%:%303=239%:%
-%:%304=240%:%
-%:%305=241%:%
-%:%306=242%:%
-%:%307=243%:%
-%:%308=244%:%
-%:%309=245%:%
-%:%310=246%:%
-%:%311=247%:%
-%:%312=248%:%
-%:%313=249%:%
-%:%314=250%:%
-%:%315=251%:%
-%:%316=252%:%
-%:%317=253%:%
-%:%318=254%:%
-%:%319=255%:%
-%:%320=256%:%
-%:%321=257%:%
-%:%322=258%:%
-%:%323=259%:%
-%:%324=260%:%
-%:%325=261%:%
-%:%326=262%:%
-%:%327=263%:%
-%:%328=264%:%
-%:%329=265%:%
-%:%330=266%:%
-%:%331=267%:%
-%:%332=268%:%
-%:%333=269%:%
-%:%334=270%:%
-%:%335=271%:%
-%:%336=272%:%
-%:%337=273%:%
-%:%338=274%:%
-%:%339=275%:%
-%:%340=276%:%
-%:%341=277%:%
-%:%342=278%:%
-%:%343=279%:%
-%:%344=280%:%
-%:%345=281%:%
-%:%346=282%:%
-%:%347=283%:%
-%:%348=284%:%
-%:%349=285%:%
-%:%350=286%:%
-%:%351=287%:%
-%:%352=288%:%
-%:%353=289%:%
-%:%354=290%:%
-%:%355=291%:%
-%:%356=292%:%
-%:%357=293%:%
-%:%358=294%:%
-%:%359=295%:%
-%:%360=296%:%
-%:%361=297%:%
-%:%362=298%:%
-%:%363=299%:%
-%:%364=300%:%
-%:%365=301%:%
-%:%366=302%:%
-%:%367=303%:%
-%:%368=304%:%
-%:%369=305%:%
-%:%370=306%:%
-%:%371=307%:%
-%:%372=308%:%
-%:%373=309%:%
-%:%374=310%:%
-%:%375=311%:%
-%:%376=312%:%
-%:%377=313%:%
-%:%378=314%:%
-%:%379=315%:%
-%:%380=316%:%
-%:%381=317%:%
-%:%382=318%:%
-%:%383=319%:%
-%:%384=320%:%
-%:%385=321%:%
-%:%386=322%:%
-%:%387=323%:%
-%:%388=324%:%
-%:%389=325%:%
-%:%390=326%:%
-%:%391=327%:%
-%:%392=328%:%
-%:%393=329%:%
-%:%394=330%:%
-%:%395=331%:%
-%:%396=332%:%
-%:%397=333%:%
-%:%398=334%:%
-%:%399=335%:%
-%:%408=339%:%
-%:%420=341%:%
-%:%421=342%:%
-%:%422=343%:%
-%:%423=344%:%
-%:%424=345%:%
-%:%425=346%:%
-%:%426=347%:%
-%:%427=348%:%
-%:%428=349%:%
-%:%429=350%:%
-%:%430=351%:%
-%:%431=352%:%
-%:%432=353%:%
-%:%433=354%:%
-%:%434=355%:%
-%:%435=356%:%
-%:%436=357%:%
+%:%60=31%:%
+%:%61=32%:%
+%:%62=33%:%
+%:%63=34%:%
+%:%64=35%:%
+%:%65=36%:%
+%:%66=37%:%
+%:%67=38%:%
+%:%68=39%:%
+%:%69=40%:%
+%:%70=41%:%
+%:%71=42%:%
+%:%72=43%:%
+%:%73=44%:%
+%:%74=45%:%
+%:%75=46%:%
+%:%76=47%:%
+%:%77=48%:%
+%:%78=49%:%
+%:%79=50%:%
+%:%80=51%:%
+%:%81=52%:%
+%:%82=53%:%
+%:%83=54%:%
+%:%84=55%:%
+%:%85=56%:%
+%:%86=57%:%
+%:%87=58%:%
+%:%88=59%:%
+%:%89=60%:%
+%:%90=61%:%
+%:%91=62%:%
+%:%92=63%:%
+%:%93=64%:%
+%:%94=65%:%
+%:%95=66%:%
+%:%96=67%:%
+%:%97=68%:%
+%:%98=69%:%
+%:%99=70%:%
+%:%100=71%:%
+%:%101=72%:%
+%:%102=73%:%
+%:%103=74%:%
+%:%104=75%:%
+%:%105=76%:%
+%:%106=77%:%
+%:%107=78%:%
+%:%108=79%:%
+%:%109=80%:%
+%:%110=81%:%
+%:%111=82%:%
+%:%112=83%:%
+%:%113=84%:%
+%:%114=85%:%
+%:%115=86%:%
+%:%116=87%:%
+%:%117=88%:%
+%:%118=89%:%
+%:%119=90%:%
+%:%120=91%:%
+%:%121=92%:%
+%:%122=93%:%
+%:%123=94%:%
+%:%124=95%:%
+%:%125=96%:%
+%:%126=97%:%
+%:%127=98%:%
+%:%128=99%:%
+%:%129=100%:%
+%:%130=101%:%
+%:%131=102%:%
+%:%132=103%:%
+%:%133=104%:%
+%:%134=105%:%
+%:%135=106%:%
+%:%136=107%:%
+%:%137=108%:%
+%:%138=109%:%
+%:%139=110%:%
+%:%140=111%:%
+%:%141=112%:%
+%:%142=113%:%
+%:%143=114%:%
+%:%144=115%:%
+%:%145=116%:%
+%:%146=117%:%
+%:%147=118%:%
+%:%148=119%:%
+%:%149=120%:%
+%:%150=121%:%
+%:%151=122%:%
+%:%152=123%:%
+%:%153=124%:%
+%:%154=125%:%
+%:%155=126%:%
+%:%156=127%:%
+%:%157=128%:%
+%:%158=129%:%
+%:%159=130%:%
+%:%160=131%:%
+%:%161=132%:%
+%:%162=133%:%
+%:%163=134%:%
+%:%164=135%:%
+%:%165=136%:%
+%:%166=137%:%
+%:%167=138%:%
+%:%168=139%:%
+%:%169=140%:%
+%:%170=141%:%
+%:%171=142%:%
+%:%180=144%:%
+%:%192=146%:%
+%:%193=147%:%
+%:%194=148%:%
+%:%195=149%:%
+%:%196=150%:%
+%:%197=151%:%
+%:%198=152%:%
+%:%199=153%:%
+%:%200=154%:%
+%:%201=155%:%
+%:%202=156%:%
+%:%211=158%:%
+%:%223=160%:%
+%:%224=161%:%
+%:%225=162%:%
+%:%226=163%:%
+%:%227=164%:%
+%:%228=165%:%
+%:%229=166%:%
+%:%230=167%:%
+%:%231=168%:%
+%:%232=169%:%
+%:%233=170%:%
+%:%234=171%:%
+%:%235=172%:%
+%:%236=173%:%
+%:%237=174%:%
+%:%238=175%:%
+%:%239=176%:%
+%:%240=177%:%
+%:%241=178%:%
+%:%242=179%:%
+%:%243=180%:%
+%:%244=181%:%
+%:%245=182%:%
+%:%246=183%:%
+%:%247=184%:%
+%:%248=185%:%
+%:%249=186%:%
+%:%250=187%:%
+%:%251=188%:%
+%:%252=189%:%
+%:%253=190%:%
+%:%254=191%:%
+%:%255=192%:%
+%:%256=193%:%
+%:%257=194%:%
+%:%258=195%:%
+%:%259=196%:%
+%:%260=197%:%
+%:%261=198%:%
+%:%262=199%:%
+%:%263=200%:%
+%:%264=201%:%
+%:%265=202%:%
+%:%266=203%:%
+%:%267=204%:%
+%:%268=205%:%
+%:%269=206%:%
+%:%270=207%:%
+%:%271=208%:%
+%:%272=209%:%
+%:%273=210%:%
+%:%274=211%:%
+%:%275=212%:%
+%:%276=213%:%
+%:%277=214%:%
+%:%278=215%:%
+%:%279=216%:%
+%:%280=217%:%
+%:%281=218%:%
+%:%282=219%:%
+%:%283=220%:%
+%:%284=221%:%
+%:%285=222%:%
+%:%286=223%:%
+%:%287=224%:%
+%:%288=225%:%
+%:%289=226%:%
+%:%290=227%:%
+%:%291=228%:%
+%:%292=229%:%
+%:%293=230%:%
+%:%294=231%:%
+%:%295=232%:%
+%:%296=233%:%
+%:%297=234%:%
+%:%298=235%:%
+%:%299=236%:%
+%:%300=237%:%
+%:%301=238%:%
+%:%302=239%:%
+%:%303=240%:%
+%:%304=241%:%
+%:%305=242%:%
+%:%306=243%:%
+%:%307=244%:%
+%:%308=245%:%
+%:%309=246%:%
+%:%310=247%:%
+%:%311=248%:%
+%:%312=249%:%
+%:%313=250%:%
+%:%314=251%:%
+%:%315=252%:%
+%:%316=253%:%
+%:%317=254%:%
+%:%318=255%:%
+%:%319=256%:%
+%:%320=257%:%
+%:%321=258%:%
+%:%322=259%:%
+%:%323=260%:%
+%:%324=261%:%
+%:%325=262%:%
+%:%326=263%:%
+%:%327=264%:%
+%:%328=265%:%
+%:%329=266%:%
+%:%330=267%:%
+%:%331=268%:%
+%:%332=269%:%
+%:%333=270%:%
+%:%334=271%:%
+%:%335=272%:%
+%:%336=273%:%
+%:%337=274%:%
+%:%338=275%:%
+%:%339=276%:%
+%:%340=277%:%
+%:%341=278%:%
+%:%342=279%:%
+%:%343=280%:%
+%:%344=281%:%
+%:%345=282%:%
+%:%346=283%:%
+%:%347=284%:%
+%:%348=285%:%
+%:%349=286%:%
+%:%350=287%:%
+%:%351=288%:%
+%:%352=289%:%
+%:%353=290%:%
+%:%354=291%:%
+%:%355=292%:%
+%:%356=293%:%
+%:%357=294%:%
+%:%358=295%:%
+%:%359=296%:%
+%:%360=297%:%
+%:%361=298%:%
+%:%362=299%:%
+%:%363=300%:%
+%:%364=301%:%
+%:%365=302%:%
+%:%366=303%:%
+%:%367=304%:%
+%:%368=305%:%
+%:%369=306%:%
+%:%370=307%:%
+%:%371=308%:%
+%:%372=309%:%
+%:%373=310%:%
+%:%374=311%:%
+%:%375=312%:%
+%:%376=313%:%
+%:%377=314%:%
+%:%378=315%:%
+%:%379=316%:%
+%:%380=317%:%
+%:%381=318%:%
+%:%382=319%:%
+%:%383=320%:%
+%:%384=321%:%
+%:%385=322%:%
+%:%386=323%:%
+%:%387=324%:%
+%:%388=325%:%
+%:%389=326%:%
+%:%390=327%:%
+%:%391=328%:%
+%:%392=329%:%
+%:%393=330%:%
+%:%394=331%:%
+%:%395=332%:%
+%:%396=333%:%
+%:%397=334%:%
+%:%398=335%:%
+%:%399=336%:%
+%:%400=337%:%
+%:%401=338%:%
+%:%402=339%:%
+%:%403=340%:%
+%:%404=341%:%
+%:%405=342%:%
+%:%406=343%:%
+%:%407=344%:%
+%:%408=345%:%
+%:%409=346%:%
+%:%410=347%:%
+%:%411=348%:%
+%:%412=349%:%
+%:%413=350%:%
+%:%414=351%:%
+%:%415=352%:%
+%:%416=353%:%
+%:%425=356%:%
 %:%437=358%:%
@@
 %:%488=409%:%
-%:%497=411%:%
-%:%509=413%:%
-%:%510=414%:%
-%:%511=415%:%
-%:%512=416%:%
-%:%513=417%:%
-%:%514=418%:%
-%:%515=419%:%
-%:%516=420%:%
-%:%517=421%:%
-%:%518=422%:%
-%:%519=423%:%
-%:%520=424%:%
-%:%521=425%:%
-%:%522=426%:%
-%:%523=427%:%
+%:%489=410%:%
+%:%490=411%:%
+%:%491=412%:%
+%:%492=413%:%
+%:%493=414%:%
+%:%494=415%:%
+%:%495=416%:%
+%:%496=417%:%
+%:%497=418%:%
+%:%498=419%:%
+%:%499=420%:%
+%:%500=421%:%
+%:%501=422%:%
+%:%502=423%:%
+%:%503=424%:%
+%:%512=426%:%
 %:%524=428%:%
@@
 %:%587=491%:%
-%:%596=494%:%
-%:%608=497%:%
-%:%609=498%:%
-%:%610=499%:%
-%:%611=500%:%
-%:%612=501%:%
-%:%613=502%:%
-%:%614=503%:%
-%:%615=504%:%
-%:%616=505%:%
-%:%617=506%:%
-%:%618=507%:%
-%:%619=508%:%
-%:%620=509%:%
-%:%621=510%:%
-%:%622=511%:%
-%:%623=512%:%
+%:%588=492%:%
+%:%589=493%:%
+%:%590=494%:%
+%:%591=495%:%
+%:%592=496%:%
+%:%593=497%:%
+%:%594=498%:%
+%:%595=499%:%
+%:%596=500%:%
+%:%597=501%:%
+%:%598=502%:%
+%:%599=503%:%
+%:%600=504%:%
+%:%601=505%:%
+%:%602=506%:%
+%:%603=507%:%
+%:%612=510%:%
 %:%624=513%:%
@@
 %:%714=603%:%
-%:%717=605%:%
-%:%718=606%:%
-%:%719=607%:%
-%:%720=608%:%
-%:%721=609%:%
-%:%722=610%:%
-%:%725=611%:%
-%:%726=612%:%
-%:%727=613%:%
-%:%728=614%:%
-%:%729=615%:%
-%:%730=616%:%
-%:%731=617%:%
-%:%732=618%:%
-%:%733=619%:%
-%:%734=620%:%
-%:%735=621%:%
-%:%736=622%:%
-%:%737=623%:%
-%:%738=624%:%
-%:%739=625%:%
-%:%748=629%:%
-%:%760=631%:%
-%:%761=632%:%
-%:%762=633%:%
-%:%763=634%:%
-%:%764=635%:%
-%:%765=636%:%
-%:%766=637%:%
-%:%767=638%:%
-%:%768=639%:%
-%:%769=640%:%
-%:%770=641%:%
-%:%771=642%:%
-%:%772=643%:%
-%:%773=644%:%
-%:%774=645%:%
-%:%775=646%:%
-%:%776=647%:%
-%:%777=648%:%
-%:%778=649%:%
-%:%779=650%:%
-%:%780=651%:%
-%:%781=652%:%
-%:%782=653%:%
-%:%783=654%:%
-%:%784=655%:%
-%:%785=656%:%
-%:%786=657%:%
-%:%787=658%:%
-%:%788=659%:%
+%:%715=604%:%
+%:%716=605%:%
+%:%717=606%:%
+%:%718=607%:%
+%:%719=608%:%
+%:%720=609%:%
+%:%721=610%:%
+%:%722=611%:%
+%:%723=612%:%
+%:%724=613%:%
+%:%725=614%:%
+%:%726=615%:%
+%:%727=616%:%
+%:%728=617%:%
+%:%729=618%:%
+%:%730=619%:%
+%:%731=620%:%
+%:%732=621%:%
+%:%733=622%:%
+%:%734=623%:%
+%:%735=624%:%
+%:%736=625%:%
+%:%737=626%:%
+%:%738=627%:%
+%:%739=628%:%
+%:%740=629%:%
+%:%741=630%:%
+%:%742=631%:%
+%:%745=633%:%
+%:%746=634%:%
+%:%747=635%:%
+%:%748=636%:%
+%:%749=637%:%
+%:%750=638%:%
+%:%753=639%:%
+%:%754=640%:%
+%:%755=641%:%
+%:%756=642%:%
+%:%757=643%:%
+%:%758=644%:%
+%:%759=645%:%
+%:%760=646%:%
+%:%761=647%:%
+%:%762=648%:%
+%:%763=649%:%
+%:%764=650%:%
+%:%765=651%:%
+%:%766=652%:%
+%:%767=653%:%
+%:%768=654%:%
+%:%777=658%:%
 %:%789=660%:%
@@
 %:%811=682%:%
-%:%820=684%:%
-%:%832=686%:%
-%:%833=687%:%
-%:%834=688%:%
-%:%835=689%:%
-%:%836=690%:%
-%:%837=691%:%
-%:%838=692%:%
-%:%839=693%:%
-%:%840=694%:%
-%:%841=695%:%
-%:%842=696%:%
-%:%843=697%:%
-%:%844=698%:%
-%:%845=699%:%
-%:%846=700%:%
-%:%847=701%:%
-%:%848=702%:%
-%:%849=703%:%
-%:%850=704%:%
-%:%851=705%:%
-%:%852=706%:%
-%:%853=707%:%
-%:%854=708%:%
-%:%855=709%:%
-%:%856=710%:%
-%:%857=711%:%
-%:%858=712%:%
-%:%859=713%:%
-%:%860=714%:%
+%:%812=683%:%
+%:%813=684%:%
+%:%814=685%:%
+%:%815=686%:%
+%:%816=687%:%
+%:%817=688%:%
+%:%818=689%:%
+%:%819=690%:%
+%:%820=691%:%
+%:%821=692%:%
+%:%822=693%:%
+%:%823=694%:%
+%:%824=695%:%
+%:%825=696%:%
+%:%826=697%:%
+%:%827=698%:%
+%:%828=699%:%
+%:%829=700%:%
+%:%830=701%:%
+%:%831=702%:%
+%:%832=703%:%
+%:%833=704%:%
+%:%834=705%:%
+%:%835=706%:%
+%:%836=707%:%
+%:%837=708%:%
+%:%838=709%:%
+%:%839=710%:%
+%:%840=711%:%
+%:%849=713%:%
 %:%861=715%:%
@@
 %:%870=724%:%
+%:%871=725%:%
+%:%872=726%:%
+%:%873=727%:%
+%:%874=728%:%
+%:%875=729%:%
+%:%876=730%:%
+%:%877=731%:%
+%:%878=732%:%
+%:%879=733%:%
+%:%880=734%:%
+%:%881=735%:%
+%:%882=736%:%
+%:%883=737%:%
+%:%884=738%:%
+%:%885=739%:%
+%:%886=740%:%
+%:%887=741%:%
+%:%888=742%:%
+%:%889=743%:%
+%:%890=744%:%
+%:%891=745%:%
+%:%892=746%:%
+%:%893=747%:%
+%:%894=748%:%
+%:%895=749%:%
+%:%896=750%:%
+%:%897=751%:%
+%:%898=752%:%
+%:%899=753%:%

### 2022-03-21 paper/output/document/appendix.tex
spring breaking

@@
 
-One other reason to be concerned with Korsgaard's view is that an actionable maxim will necessarily
+One issue with Korsgaard's view is that an actionable maxim will necessarily
 require some circumstances built-in because the agent will need to know when to act on the maxim. For example,
@@
 explicit. This precision is a benefit; so long as my circumstances are not so finely grained that they
-are uninterpretable, they render O'Niell's kind of maxims more precise than Korsgaard's form.%
+are uninterpretable, they render O'Niell's maxims more precise than Korsgaard's maxims.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-A stronger view than O'Niell's is due to Patricia Kitcher. Kitcher begins with O'Niell's 
+Kitcher begins with O'Niell's 
 circumstance, act, goal view and expands it to include the motive for a maxim \citep{whatisamaxim}. 
@@
 with a logic of practical reason, an implementation of the FUL can move from evaluating a maxim to 
-evaluating an agent's behavior, since that's when ``acting from duty'' starts to matter.
+evaluating an agent's behavior, since that's when acting from duty starts to matter.
 
@@
 1976 \citep{kroy}. Kroy used Hinktikka's deontic logic to formalize the Formula of Universal Law and
-the Formula of Humanity. I will first import the additional logical tools that Hintikka's logic contains 
-that Kroy relies on, then examine the differences between his logic and DDL, and finally implement 
+the Formula of Humanity. I will first import the additional logical tools that Hintikka's logic contains, 
+then examine the differences between his logic and DDL, and finally implement 
 and test Kroy's formalization of the FUL%
@@
     A = ($\lambda x. \_$)($s_1$ := ($\lambda x. \_$)($i_1$ := True, $i_2$ := True), $s_2$ := ($\lambda x. \_$)($i_1$ := False, $i_2$ := False))
+
 p = $s_1$
+
 x = $s_2$\color{black}%
@@
 %
-\isamarkupcmt{\color{blue} Nitpicking formula... 
+\isamarkupcmt{\color{blue} 
 Nitpick found a model for card i = 1:
@@
 To run this test, I epresent the sentence ``At all worlds, it is 
-not possible that everyone lies simultaneously,'' in my logic. This requires the following abbreviations.%
+not possible that everyone lies simultaneously,'' in Kroy's logic. This requires the following abbreviations.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 on universalizability, so it seems as though it should pass this test. To understand this, I 
-  outline the syllogism that one might $\emph{expect}$ to prove that lying is prohibited and will 
+  outline the syllogism that one might $\emph{expect}$ to prove that lying is prohibited and 
 test each component of this syllogism in Isabelle.%
@@
 %:%390=233%:%
-%:%398=233%:%
-%:%399=234%:%
+%:%391=234%:%
+%:%392=235%:%
 %:%400=235%:%
-%:%401=235%:%
+%:%401=236%:%
+%:%402=237%:%
 %:%403=237%:%
-%:%404=238%:%
+%:%405=239%:%
 %:%406=240%:%
-%:%407=240%:%
-%:%408=240%:%
-%:%410=240%:%
-%:%414=240%:%
-%:%415=240%:%
-%:%417=241%:%
-%:%418=242%:%
+%:%408=242%:%
+%:%409=242%:%
+%:%410=242%:%
+%:%412=242%:%
+%:%416=242%:%
+%:%417=242%:%
 %:%419=243%:%
 %:%420=244%:%
-%:%430=246%:%
-%:%431=247%:%
+%:%421=245%:%
+%:%422=246%:%
 %:%432=248%:%
 %:%433=249%:%
-%:%442=251%:%
-%:%454=253%:%
-%:%455=254%:%
+%:%434=250%:%
+%:%435=251%:%
+%:%444=253%:%
 %:%456=255%:%
@@
 %:%464=263%:%
+%:%465=264%:%
 %:%466=265%:%
-%:%467=265%:%
-%:%468=266%:%
+%:%468=267%:%
 %:%469=267%:%
-%:%470=267%:%
-%:%472=267%:%
-%:%476=267%:%
-%:%486=269%:%
-%:%487=270%:%
+%:%470=268%:%
+%:%471=269%:%
+%:%472=269%:%
+%:%474=269%:%
+%:%478=269%:%
 %:%488=271%:%
+%:%489=272%:%
 %:%490=273%:%
-%:%491=273%:%
-%:%492=274%:%
+%:%492=275%:%
 %:%493=275%:%
 %:%494=276%:%
-%:%495=276%:%
-%:%497=276%:%
-%:%501=276%:%
-%:%502=276%:%
-%:%504=277%:%
-%:%505=278%:%
+%:%495=277%:%
+%:%496=278%:%
+%:%497=278%:%
+%:%499=278%:%
+%:%503=278%:%
+%:%504=278%:%
 %:%506=279%:%
 %:%507=280%:%
-%:%517=282%:%
-%:%518=283%:%
+%:%508=281%:%
+%:%509=282%:%
+%:%519=284%:%
 %:%520=285%:%
-%:%521=285%:%
-%:%522=286%:%
+%:%522=287%:%
 %:%523=287%:%
@@
 %:%525=289%:%
-%:%526=289%:%
-%:%528=289%:%
-%:%532=289%:%
-%:%533=289%:%
-%:%535=290%:%
-%:%536=291%:%
+%:%526=290%:%
+%:%527=291%:%
+%:%528=291%:%
+%:%530=291%:%
+%:%534=291%:%
+%:%535=291%:%
 %:%537=292%:%
@@
 %:%540=295%:%
-%:%550=297%:%
-%:%551=298%:%
+%:%541=296%:%
+%:%542=297%:%
 %:%552=299%:%
+%:%553=300%:%
 %:%554=301%:%
-%:%555=301%:%
-%:%556=302%:%
+%:%556=303%:%
 %:%557=303%:%
 %:%558=304%:%
-%:%559=304%:%
-%:%561=304%:%
-%:%565=304%:%
-%:%566=304%:%
-%:%568=305%:%
-%:%569=306%:%
+%:%559=305%:%
+%:%560=306%:%
+%:%561=306%:%
+%:%563=306%:%
+%:%567=306%:%
+%:%568=306%:%
 %:%570=307%:%
@@
 %:%572=309%:%
-%:%582=312%:%
-%:%583=313%:%
+%:%573=310%:%
+%:%574=311%:%
 %:%584=314%:%
@@
 %:%588=318%:%
+%:%589=319%:%
 %:%590=320%:%
-%:%591=320%:%
-%:%593=321%:%
-%:%594=322%:%
+%:%592=322%:%
+%:%593=322%:%
 %:%595=323%:%
-%:%596=323%:%
-%:%597=324%:%
+%:%596=324%:%
+%:%597=325%:%
 %:%598=325%:%
-%:%599=325%:%
-%:%601=326%:%
-%:%602=326%:%
-%:%604=327%:%
-%:%605=328%:%
-%:%606=328%:%
-%:%607=329%:%
+%:%599=326%:%
+%:%600=327%:%
+%:%601=327%:%
+%:%603=328%:%
+%:%604=328%:%
+%:%606=329%:%
+%:%607=330%:%
 %:%608=330%:%
-%:%609=330%:%
-%:%611=331%:%
-%:%612=332%:%
-%:%615=334%:%
-%:%616=335%:%
+%:%609=331%:%
+%:%610=332%:%
+%:%611=332%:%
+%:%613=333%:%
+%:%614=334%:%
+%:%617=336%:%
 %:%618=337%:%
-%:%619=337%:%
-%:%620=338%:%
+%:%620=339%:%
 %:%621=339%:%
-%:%622=339%:%
-%:%624=339%:%
-%:%628=339%:%
-%:%629=339%:%
-%:%631=340%:%
-%:%632=341%:%
+%:%622=340%:%
+%:%623=341%:%
+%:%624=341%:%
+%:%626=341%:%
+%:%630=341%:%
+%:%631=341%:%
 %:%633=342%:%
@@
 %:%637=346%:%
-%:%647=348%:%
-%:%648=349%:%
+%:%638=347%:%
+%:%639=348%:%
 %:%649=350%:%
@@
 %:%651=352%:%
-%:%655=354%:%
-%:%656=355%:%
+%:%652=353%:%
+%:%653=354%:%
 %:%657=356%:%
@@
 %:%660=359%:%
-%:%664=361%:%
-%:%665=362%:%
+%:%661=360%:%
+%:%662=361%:%
 %:%666=363%:%
+%:%667=364%:%
 %:%668=365%:%
-%:%669=365%:%
-%:%670=366%:%
-%:%673=367%:%
-%:%677=367%:%
-%:%678=367%:%
-%:%680=368%:%
-%:%686=368%:%
-%:%689=369%:%
-%:%690=370%:%
-%:%691=370%:%
-%:%692=371%:%
+%:%670=367%:%
+%:%671=367%:%
+%:%672=368%:%
+%:%675=369%:%
+%:%679=369%:%
+%:%680=369%:%
+%:%682=370%:%
+%:%688=370%:%
+%:%691=371%:%
+%:%692=372%:%
 %:%693=372%:%
 %:%694=373%:%
-%:%695=373%:%
-%:%697=373%:%
-%:%701=373%:%
-%:%702=373%:%
-%:%704=374%:%
-%:%705=375%:%
+%:%695=374%:%
+%:%696=375%:%
+%:%697=375%:%
+%:%699=375%:%
+%:%703=375%:%
+%:%704=375%:%
 %:%706=376%:%
@@
 %:%708=378%:%
-%:%718=380%:%
-%:%719=381%:%
+%:%709=379%:%
+%:%710=380%:%
 %:%720=382%:%
@@
 %:%739=401%:%
-%:%743=403%:%
-%:%744=404%:%
+%:%740=402%:%
+%:%741=403%:%
 %:%745=405%:%
@@
 %:%751=411%:%
-%:%755=414%:%
-%:%756=415%:%
+%:%752=412%:%
+%:%753=413%:%
 %:%757=416%:%
 %:%758=417%:%
+%:%759=418%:%
 %:%760=419%:%
-%:%761=419%:%
-%:%762=420%:%
+%:%762=421%:%
 %:%763=421%:%
-%:%764=421%:%
-%:%765=422%:%
-%:%768=423%:%
-%:%772=423%:%
-%:%773=423%:%
-%:%774=423%:%
-%:%776=424%:%
-%:%777=425%:%
-%:%787=427%:%
-%:%788=428%:%
+%:%764=422%:%
+%:%765=423%:%
+%:%766=423%:%
+%:%767=424%:%
+%:%770=425%:%
+%:%774=425%:%
+%:%775=425%:%
+%:%776=425%:%
+%:%778=426%:%
+%:%779=427%:%
 %:%789=429%:%
@@
 %:%813=453%:%
+%:%814=454%:%
 %:%815=455%:%
-%:%816=455%:%
-%:%817=456%:%
+%:%817=457%:%
 %:%818=457%:%
 %:%819=458%:%
-%:%820=458%:%
-%:%822=458%:%
-%:%826=458%:%
-%:%827=458%:%
-%:%829=459%:%
-%:%830=460%:%
+%:%820=459%:%
+%:%821=460%:%
+%:%822=460%:%
+%:%824=460%:%
+%:%828=460%:%
+%:%829=460%:%
 %:%831=461%:%
@@
 %:%836=466%:%
-%:%846=468%:%
-%:%847=469%:%
+%:%837=467%:%
+%:%838=468%:%
 %:%848=470%:%
@@
 %:%852=474%:%
+%:%853=475%:%
+%:%854=476%:%

### 2022-03-21 paper/output/document/thesis_0_abstract.tex
spring breaking

@@
 development of responsible AI agents. If automated ethics draws on sophisticated philosophical
-literature, its decisions will be more nuanced, precise, consistent, and trustworthy, but faithfully
-translating a complex ethical theory from natural language to the rigid syntax of a computer program is
-technically and philosophically challenging.
+literature, its decisions will be more nuanced, precise, and consistent, but automating ethical theories is 
+difficult in practice. Faithfully translating a complex ethical theory from natural language to the 
+rigid syntax of a computer program is technically and philosophically challenging.
 
@@
 ethics that is faithful to the Kantian philosophical tradition. Given an appropriately represented 
-action and minimal factual background, my system can judge the action as morally obligatory, permissible, or prohibited.
+action and minimal factual background, my system can judge a potential action as morally obligatory, permissible, or prohibited.
 To accomplish this, I formalize Kant's categorical imperative, or moral rule,
@@
 asking about the location of their intended victim. Finally, I examine the philosophical implications 
-of my system, exploring its limitations and its potential to guide AI agents, academic philosophers, 
+of my system, exploring its potential to guide AI agents, academic philosophers, 
 and everyday reasoners as they navigate ethical dilemmas. Ultimately, this work serves 

### 2022-03-21 paper/output/document/thesis_0_acknowledgements.tex
spring breaking

%
\begin{isabellebody}%
\setisabellecontext{thesis{\isacharunderscore}{\isadigit{0}}{\isacharunderscore}acknowledgements}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\begin{isamarkuptext}%
Every step of this process has been made easier by my mentors' unwavering support. Thank you to Professor 
Nada Amin for taking me seriously when this project was just a vague intuition, for always asking the 
right questions at the right time, and for being willing 
to stumble through the dark with me. I am endlessly grateful for our Friday night email threads.

Thank you to Dr. William Cochran for offering much more of time, energy, and support than I ever 
imagined possible. This project was less lonely because of your
willingness to venture down rabbit holes with me. I hope that someday I can be as cool and 
collected as you (maybe I'll have to read more Aristotle first).

Thank you to Professor James Waldo for always giving me the advice I need to hear. Since freshman year, 
I have always walked out of your office with a clear head and renewed resolve. Thank you for giving me the 
knowledge that, even when everything feels hopeless, there is one person at this university who believes in me.
Your mentorship has been the single most transformative part of my college experience, and I will always
be grateful to you.

I fell in love with philosophy while reading Christine Korsgaard's \emph{Sources of Normativity}, and 
this thesis is largely inspired by her work. She once said that 
we make the world more sensible by being good to each other; her ideas have certainly made my world make more
sense.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/thesis_0_acknowledgements.thy%:%
%:%19=6%:%
%:%20=7%:%
%:%21=8%:%
%:%22=9%:%
%:%23=10%:%
%:%24=11%:%
%:%25=12%:%
%:%26=13%:%
%:%27=14%:%
%:%28=15%:%
%:%29=16%:%
%:%30=17%:%
%:%31=18%:%
%:%32=19%:%
%:%33=20%:%
%:%34=21%:%
%:%35=22%:%
%:%36=23%:%
%:%37=24%:%
%:%38=25%:%

### 2022-03-21 paper/output/document/thesis_1_intro.tex
spring breaking

@@
 \item In Section \ref{computationalethics}, I present ethical insights discovered using my system and argue that
-computational methods like the one presented in this thesis can help philosophers address ethical problems.
+computational methods like the one presented in this thesis can help philosophers resolve debates about ethics.
 Not only can my system help machines reason about ethics, but it can also help philosophers make philosophical
@@
 My implementation of automated Kantian ethics formalizes Kant's moral rule
-in Deontic logic, a modal logic that can express obligation, or morally binding requirements. Traditional modal 
+in deontic logic, a modal logic that can express obligation, or morally binding requirements. Traditional modal 
 logics include the necessitation operator, denoted as $\Box$. Using the Kripke semantics, 
@@
 conditionals. \citep{chisholm, ctd}
-} To escape such issues, I use Dyadic Deontic Logic, in which
+} To avoid such issues, I use Dyadic Deontic Logic, in which
 the dyadic obligation operator $O\{A \vert B\}$ represents the sentence ``A is obligated in the context B.'' 
-The introduction of context allows DDL to express more nuanced reasoning and avoid contrary-to-duty
+The introduction of context allows DDL to express more nuanced reasoning and resolve contrary-to-duty
 paradoxes. DDL is both deontic and modal, 
@@
 all moral judgements can be derived. I implement a version of this rule called the Formula of Universal 
-Law (FUL), which states that people should only act on those principles that can be acted on by all 
-people without contradiction. For example, falsely promising to repay a loan is wrong because if everyone 
-falsely promises to repay a loan, lenders will no longer believe these promises and will stop offering loans. 
-Therefore, not everyone can simultaneously falsely promise to repay a loan, so the FUL prohibits this act.
+Law (FUL), which states that an act is only ethical if it can be performed by all people without contradiction. 
+For example, falsely promising to repay a loan is wrong because not everyone can falsely promise to 
+repay a loan, since lenders will no longer believe these promises and will stop offering loans. The FUL
+prohibits actions that are not ``universalizable,'' or cannot be undertaken by everyone. It formalizes
+the kind of objection drawn by the question, ``What if everyone did that?''
 
@@
 %:%226=196%:%
+%:%227=197%:%

### 2022-03-21 paper/output/document/thesis_2_methods.tex
spring breaking

@@
 components, such as another ethical theory, a different logic, or a different theorem prover could be 
-made. Flaws with these components are merely limitations of my system, but do not 
+made. Flaws with these components are limitations of my system, but do not 
 indict logic-programming-based automated ethics more generally. My thesis seeks to 
@@
 
-The challenge of representing the circumstances of action is not unique to consequentialism, but is particularly acute in this case. 
+The challenge of representing the circumstances of action is not unique to consequentialism, but it is particularly acute in this case. 
 Kantian ethicists robustly debate which circumstances of an action are ``morally relevant'' when evaluating an action's moral worth.\footnote{ 
 \citet{powers} identifies this as a challenge for automating Kantian ethics and briefly sketches 
-solutions from \citet{constofreason}, \citet{silber}, and \citet{rawlsconstructivism}. For my approach to
-morally relevant circumstances, see Section \ref{whatisamaxim}.} Because deontology merely evaluates a 
+solutions from \citet{constofreason}, \citet{silber}, and \citet{rawlsconstructivism}. For further discussion of
+morally relevant circumstances, see Sections \ref{whatisamaxim} and \ref{AIethics}.} Because deontology merely evaluates a 
 single action, the surface of this debate is much smaller than debates about circumstances and 
@@
 Because of its intuitive appeal, computer scientists have tried to formalize consequentialism in the past.
-These efforts cannot circumvent the challenges outlined above. For example, Abel et al. represent ethics as a
+These efforts cannot escape the challenges outlined above. For example, Abel et al. represent ethics as a
 Markov Decision Process (MDP), with reward functions customized to particular ethical dilemmas 
@@
 reward is accumulated in an MDP.\footnote{Generally, reward for an MDP is accumulated according to a 
-``discount factor'' $\gamma < 1$, such that if $r_i$ is the reward at time $i$, the total reward is $\sum_{i=0}^{\infty}\gamma^i r_i$.} 
+``discount factor'' $\gamma \leq 1$, such that if $r_i$ is the reward at time $i$, the total reward is $\sum_{i=0}^{\infty}\gamma^i r_i$.} 
 It leaves open the question of what the reward function is and thus 
@@
 point to a machine learning approach to automated ethics, in which ethical behavior is learned from a 
-dataset of acts tagged as virtuous if they are the act that an ideal virtuous agent would undertake.
+dataset of acts, where an act is tagged as virtuous if an ideal virtuous agent would perform it.
 
@@
 are and how certain acts impact an agent's moral character. Because there is no canonical list of all virtues
-that virtue ethicists accept, this implicit view will likely be controversial. Even virtue ethicists agree
+that virtue ethicists accept, this implicit view will likely be controversial. Even virtue ethicists who agree
 that certain traits, like courage, are virtues debate the exact definitions of these traits.
@@
 rational beings are unique because we act ``in accordance with 
-the representations of laws'' \citep[26]{groundwork}.\footnote{} A ball thrown into the air acts 
+the representations of laws'' \citep[26]{groundwork}. A ball thrown into the air acts 
 according to the laws of physics. It cannot ask itself, ``Should I fall back to the ground?'' 
@@
 \begin{isamarkuptext}%
-One challenge for automating Kantian ethics is the need for what humans often understand as ``common-sense'', or factual and 
+One challenge for automating Kantian ethics is the need for ``common-sense'', or factual and 
 situational background. Common-sense is needed when formulating a maxim and determining if a maxim 
@@
 Kant presents three formulations, or versions, 
-of what he calls the ``supreme law of morality," but I focus on the first of these three. In this section, 
+of what he calls the ``supreme law of morality,'' but I focus on the first of these three. In this section, 
 I argue that the Formula of Universal Law, specifically, is the easiest part of Kantian ethics to automate
@@
 The first formulation of the categorical imperative is the
-formula of universal law (FUL), which reads, ``act only according to that maxim through which you can 
+Formula of Universal Law (FUL), which reads, ``act only according to that maxim through which you can 
 at the same time will that it become a universal law'' \citep[34]{groundwork}. The 
-second formulation of the categorical imperative is the formula of humanity (FUH): ``So act that you use humanity, 
+second formulation of the categorical imperative is the Formula of Humanity (FUH): ``So act that you use humanity, 
 in your own person, as well as in the person of any other, always at the same time as an end, never merely 
@@
 acknowledge and respect the dignity of every other person. The third formulation of the categorical 
-imperative is the formula of autonomy (FOA), which Korsgaard describes
+imperative is the Formula of Autonomy (FOA), which Korsgaard describes
 as, ``we should so act that we may think of ourselves as legislating universal laws through our 
@@
 
-I choose to focus on the FUL\footnote{The FUL is often seen as emblematic of Kantian constructivism \cite[173]{ebelsduggan}. 
-My project is not committed to Kantian constructivism.}, because it is the most formal and thus the 
+I choose to focus on the FUL,\footnote{The FUL is often seen as emblematic of Kantian constructivism \cite[173]{ebelsduggan}. 
+My project is not committed to Kantian constructivism.} because it is the most formal and thus the 
 easiest to formalize and implement. Onora O'Neill explains that the formalism of the FUL allows 
@@
 is particularly useful in a computational context because any formalism necessarily makes its content 
-precise. The FUL's precision reduces ambiguity, allowing me to remain faithful to philosophical
+precise. The FUL's precision reduces ambiguity, making it easier to remain faithful to philosophical
 literature on Kant. Ambiguity in an ethical theory, such as the ambiguity about what counts as a good consequence
@@
 
-Traditional modal logics include the necessitation operator, denoted as $\Box$. In simple modal logic
+As explained in Chapter \ref{intro}, traditional modal logics include the necessitation operator, denoted as $\Box$. In simple modal logic
 using the Kripke semantics, $\Box p$ is true at a world $w$ if $p$ is true at all of $w$'s neighbors, 
@@
 
-For more of fine-grained properties of DDL see \citet{CJDDL} or this project's source code. DDL is a heavy logic and contains modal operators 
+For more of fine-grained properties of DDL see \citet{CJDDL} or this project's source code.\footnote{The
+project's source code can be found \href{https://github.com/lsingh123/cs91r}{here}.} DDL is a heavy logic and contains modal operators 
 that aren't necessary for my analysis. While this expressivity is powerful, it may also cause performance
@@
 }\isanewline
-\isanewline
 \isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
@@
 %:%583=434%:%
-%:%592=437%:%
-%:%604=439%:%
+%:%584=435%:%
+%:%593=438%:%
 %:%605=440%:%
@@
 %:%609=444%:%
-%:%618=447%:%
-%:%630=449%:%
+%:%610=445%:%
+%:%619=448%:%
 %:%631=450%:%
 %:%632=451%:%
-%:%634=453%:%
-%:%635=453%:%
-%:%636=453%:%
-%:%637=453%:%
-%:%639=454%:%
-%:%640=454%:%
+%:%633=452%:%
+%:%635=454%:%
+%:%636=454%:%
+%:%637=454%:%
+%:%638=454%:%
+%:%640=455%:%
 %:%641=455%:%

### 2022-03-21 paper/output/document/thesis_4_applications.tex
spring breaking

--- 2022-03-08 paper/output/document/thesis_4_applications.tex
@@
 using the Formula of Universal Law, this reasoning must be applied to objects that are defined
-using common sense.
-
-Because these common sense facts can determine my system's judgements, they are part of the trusted
+using common sense. Because these common sense facts can determine my system's judgements, they are part of the trusted
 code base for my system, or the logic and code that a user must trust in order to trust my system. 
@@
 The challenge of endowing automated ethical reasoners with common sense reasoning is not unique to my 
-system, and virtually all prior attempts in machine ethics face similar challenges.\footnote{See Section
-\ref{relatedwork} for a survey of the common sense required in prior work.} Many prior attempts
+system, and virtually all prior attempts in machine ethics face similar challenges. Many prior attempts
 sidestep this question, whereas I contribute an prototype implementation of one kind of common sense reasoning.
@@
 of a maxim about uttering a falsehood being prohibited: that the goal require that someone believe
-the falsehood. This condition both made an long-standing argument in Kantian ethics more precise
-and can guide the correct formulation of future maxims. In other words, an insight generated by the 
+the falsehood. This condition made an long-standing argument in Kantian ethics more precise, can guide 
+the correct formulation of future maxims, and could contribute to the rich philosophical conversation
+about the wrongness of lying. In other words, an insight generated by the
 computer provides value to ethicists, bolstering the argument for computational ethics provided in 
@@
 believe he is a murderer, he will think that you won't lie to him. Precisely, she claims that, 
-``it is because the murderer supposes you do not know what circumstances you are in - that is, that 
-you do not know you are addressing a murderer - and so does not conclude from the fact that people 
+``it is because the murderer supposes you do not know what circumstances you are in—that is, that 
+you do not know you are addressing a murderer—and so does not conclude from the fact that people 
 in those circumstances always lie that you will lie'' \cite[6]{KorsgaardRTL}. Even though the maxim of 
@@
 %:%82=54%:%
-%:%83=55%:%
-%:%92=58%:%
+%:%91=57%:%
+%:%103=60%:%
 %:%104=61%:%
@@
 %:%124=81%:%
-%:%125=82%:%
-%:%127=85%:%
-%:%128=85%:%
+%:%126=84%:%
+%:%127=84%:%
+%:%129=85%:%
 %:%130=86%:%
 %:%131=87%:%
-%:%132=88%:%
+%:%134=89%:%
 %:%135=90%:%
@@
 %:%140=95%:%
-%:%141=96%:%
-%:%143=99%:%
-%:%144=99%:%
+%:%142=98%:%
+%:%143=98%:%
+%:%145=99%:%
 %:%146=100%:%
-%:%147=101%:%
+%:%147=100%:%
 %:%148=101%:%
-%:%149=102%:%
+%:%149=101%:%
 %:%150=102%:%
-%:%151=103%:%
-%:%153=104%:%
+%:%152=103%:%
+%:%153=103%:%
 %:%154=104%:%
-%:%155=105%:%
+%:%155=104%:%
 %:%156=105%:%
-%:%157=106%:%
+%:%158=106%:%
 %:%159=107%:%
@@
 %:%162=110%:%
-%:%163=111%:%
+%:%165=114%:%
 %:%166=115%:%
@@
 %:%174=123%:%
-%:%175=124%:%
-%:%177=126%:%
+%:%176=125%:%
+%:%177=125%:%
 %:%178=126%:%
-%:%179=127%:%
-%:%181=128%:%
+%:%180=127%:%
+%:%183=129%:%
 %:%184=130%:%
@@
 %:%195=141%:%
-%:%196=142%:%
-%:%198=144%:%
-%:%199=144%:%
+%:%197=143%:%
+%:%198=143%:%
+%:%200=144%:%
 %:%201=145%:%
 %:%202=146%:%
-%:%203=147%:%
+%:%203=146%:%
 %:%204=147%:%
-%:%205=148%:%
-%:%206=148%:%
+%:%205=147%:%
+%:%207=148%:%
 %:%208=149%:%
-%:%209=150%:%
+%:%209=149%:%
 %:%210=150%:%
-%:%211=151%:%
-%:%212=151%:%
-%:%214=152%:%
+%:%211=150%:%
+%:%213=151%:%
+%:%216=153%:%
 %:%217=154%:%
@@
 %:%219=156%:%
-%:%220=157%:%
-%:%222=159%:%
+%:%221=158%:%
+%:%222=158%:%
 %:%223=159%:%
 %:%224=160%:%
-%:%225=161%:%
-%:%227=162%:%
+%:%226=161%:%
+%:%227=161%:%
 %:%228=162%:%
-%:%229=163%:%
+%:%230=163%:%
 %:%231=164%:%
-%:%232=165%:%
+%:%232=164%:%
 %:%233=165%:%
-%:%234=166%:%
+%:%235=166%:%
 %:%236=167%:%
@@
 %:%240=171%:%
-%:%241=172%:%
+%:%241=171%:%
 %:%242=172%:%
-%:%243=173%:%
-%:%245=174%:%
+%:%244=173%:%
+%:%245=173%:%
 %:%246=174%:%
-%:%247=175%:%
-%:%254=176%:%
+%:%253=175%:%
+%:%254=175%:%
 %:%255=176%:%
-%:%256=177%:%
+%:%256=176%:%
 %:%257=177%:%
-%:%258=178%:%
-%:%259=178%:%
+%:%258=177%:%
+%:%260=178%:%
 %:%261=179%:%
@@
 %:%263=181%:%
-%:%264=182%:%
+%:%264=181%:%
 %:%265=182%:%
-%:%266=183%:%
+%:%266=182%:%
 %:%267=183%:%
-%:%268=184%:%
+%:%268=183%:%
 %:%269=184%:%
-%:%270=185%:%
+%:%270=184%:%
 %:%271=185%:%
-%:%272=186%:%
-%:%273=186%:%
-%:%274=186%:%
+%:%272=185%:%
+%:%273=185%:%
+%:%275=186%:%
 %:%276=187%:%
-%:%277=188%:%
+%:%277=187%:%
 %:%278=188%:%
-%:%279=189%:%
+%:%288=190%:%
 %:%289=191%:%
@@
 %:%302=204%:%
-%:%303=205%:%
-%:%305=207%:%
+%:%304=206%:%
+%:%305=206%:%
 %:%306=207%:%
-%:%307=208%:%
+%:%308=208%:%
 %:%309=209%:%
-%:%310=210%:%
+%:%312=211%:%
 %:%313=212%:%
@@
 %:%320=219%:%
-%:%321=220%:%
-%:%323=222%:%
+%:%322=221%:%
+%:%323=221%:%
 %:%324=222%:%
 %:%325=223%:%
-%:%326=224%:%
-%:%328=225%:%
+%:%327=224%:%
+%:%328=224%:%
 %:%329=225%:%
-%:%330=226%:%
+%:%331=226%:%
 %:%332=227%:%
-%:%333=228%:%
+%:%333=227%:%
 %:%334=228%:%
-%:%335=229%:%
-%:%337=230%:%
+%:%336=229%:%
+%:%337=229%:%
 %:%338=230%:%
-%:%339=231%:%
-%:%341=232%:%
+%:%340=231%:%
+%:%341=231%:%
 %:%342=232%:%
-%:%343=233%:%
-%:%346=234%:%
-%:%350=234%:%
-%:%351=234%:%
+%:%345=233%:%
+%:%349=233%:%
+%:%350=233%:%
+%:%352=234%:%
 %:%353=235%:%
@@
 %:%356=238%:%
-%:%357=239%:%
+%:%366=241%:%
 %:%367=242%:%

### 2022-03-21 paper/output/document/thesis_5_discussion.tex
spring breaking

@@
 %
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
+In the above chapters, I presented an implementation of automated Kantian ethics that, given an appropriately
+represented maxim and sufficient factual background, can classify a maxim as obligatory, permissible, 
+or prohibited. In this chapter, I discuss the philosophical limitations and implications of this 
+work.
+
+First, I explore how my system can be used in practice to guide AI agents,
+help academic philosophers make philosophical progress, and augment the everyday practical reasoning 
+that we all perform as we navigate the world. I discuss these issues in Sections \ref{AIethics}, 
+\ref{computationalethics}, and \ref{ordinarypeople} respectively and outline the further work
+necessary to bring each of these applications to life. Much of this work has to do with how the input
+maxim given to my system is formulated and the role of common sense or prior knowledge.
+
+In Section \ref{amapossible}, I discuss theoretical objections to automated ethics, derived from the
+common philosophical intuition that there is no algorithm for ethics. I explore concrete versions of 
+this objection and make a theoretical argument for the possibility of the kind of automated ethics 
+I implement in this thesis. Finally, in Section \ref{relatedwork}, I situate my project among related work.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
 \isamarkupsubsection{Automated Moral Agents in Practice \label{AIethics}%
@@
 \endisadelimdocument
-%
-\begin{center}
-\begin{figure}
-\includegraphics[scale=0.43]{AI_engine.png}
-\caption{An example of an ethics engine for an artificial agent. This ethics engine passes a moral dilemma 
-through an input parser, applies the automated categorical imperative test, and finally processes the 
-output using an output parser, producing a prescription for action. I contribute the automated categorical 
-imperative component.} \label{fig:AIengine}
-\end{figure}
-\end{center}
 %
@@
 to the AI agent into maxims in my logic. An output parser could translate my system's output
-into a prescription for action that the AI agent could act on. Figure \ref{fig:AIengine} depicts the 
-workflow of this example ethics engine.
+into a prescription for action that the AI agent could act on. \begin{figure}
+\includegraphics[scale=0.43]{AI_engine.png}
+\caption{An example of an ethics engine for an artificial agent. This ethics engine passes a moral dilemma 
+through an input parser, applies the automated categorical imperative test, and finally processes the 
+output using an output parser, producing a prescription for action. I contribute the automated categorical 
+imperative component.} \label{fig:AIengine}
+\end{figure} Figure \ref{fig:AIengine} depicts the workflow of this example ethics engine.
 
@@
 the moral status of lying. On the other hand, consider the maxim, ``When I am unemployed, I will murder
-someone in order to take their job.'' The circumstances of being unemployed clearly have some bearing on the moral
-relevance of the murder in question; they speak to the motivation for the murder.
+someone in order to take their job.'' The circumstance ``when I am unemployed'' clearly has some moral
+relevance to the murder in question; it speaks to the motivation for the murder.
 
@@
 Correctly formulating a maxim requires what Kantians call ``practical judgement,'' or
-common sense reasoning and factual background \citep{oneilluniversallaws}. Returning to the example above, noticing that being 
-unemployed may contribute to one's desire to steal another's job requires practical
+common sense reasoning and factual background \citep{oneilluniversallaws}. Returning to the example above, the fact that being 
+unemployed may contribute to one's desire to steal another's job is a consequence of practical
 judgement, not just pure reason alone. Translating everyday situations into appropriate maxims is
@@
 define some set of morally important entities, and classify morally relevant circumstances as those
-that involve morally important entities. I discuss a potential machine-learning based approach which formulates
+that involve morally important entities. I propose a potential machine-learning based approach which formulates
 maxims based on a training set of appropriately formulated maxims in Section \ref{amapossible}. This 
@@
 \begin{isamarkuptext}%
-In addition to guiding AI agents, automated ethics can also help human beings make philosophical
+In addition to guiding AI agents, automated ethics can also help academic philosophers make philosophical
 progress. Just as theorem provers make mathematics more efficient and push mathematicians to think 
@@
 A skeptic may argue that we do often ask ``should I be doing this?'' as we do something. 
-Can this kind of question ever be valid? To understand this worry, I consider the maxim, 
+To understand this worry, I consider the maxim, 
 ``When dancing, I should just dance for the sake of dancing.'' While this maxim appears to be badly-formed (the 
@@
 tension between ESR and ESD. Those committed to this 
-interpretation must abandon one principle or the other, since committing and questioning are incompatible.
+interpretation must abandon one principle or the other, since simultaneous committing and questioning are incompatible.
 
@@
 and implementing it in an interactive theorem prover requires making the idea precise to a degree 
-that ordinary discussion does not necessarily require. For example, when formalizing the notion of a 
+that most philosophical conversation does not necessarily require. For example, when formalizing the notion of a 
 maxim, I had to understand its components, define it as a circumstance, act, goal tuple, and identify
@@
 philosophical signifiance of precision. This level of precision is possible 
-without computational tools, but computational ethics forces a level of precision that ordinary discussion 
-does not demand. Type fuzziness and overloaded definitions are all too common in philosophical writing and 
-discussion, but computers disallow this kind of imprecision.
+without computational tools, but computational ethics forces it. Type fuzziness and overloaded definitions 
+are all too common in philosophical writing and discussion, but computers disallow this kind of imprecision.
 
@@
 Test to AI game playing to protein folding, demonstrate that progress in computer science can make seemingly 
-obscure computer programs useful and usable in ways that exceed our wildest imaginations.
+obscure computer programs useful and usable in ways that exceed our expectations.
 Programmable computers themselves initially began as unwieldy punch card readers, but their current ubiquity 
@@
 %
-\isamarkupsubsection{Automating Ordinary Ethical Reasoning \label{ordinarypeople}%
+\isamarkupsubsection{Automating Everyday Practical Reason \label{ordinarypeople}%
 }
@@
 In Sections \ref{AIethics} and \ref{computationalethics}, I outline how automated ethics can guide
-artificial agents and human philosophers respectively. This raises a natural question: can automated
+artificial agents and philosophers respectively. This raises a natural question: can automated
 ethics guide ordinary human beings, not just academic philosophers, as we navigate the world and face ethical
@@
 Ethics bears weight for everyone, not just for academic philosophers, because it studies the unavoidable question:
-how should we live? If computers can make this study more efficient, then it seems that everyone should
-engage in computational ethics. The ethical question is the only question that 
+how should we live? The ethical question is the only question that 
 we answer merely by living. To turn away from ethics is to take a stance on the question of how to 
@@
 how to navigate the world and ethics answers this question. Given that ethics is vital, it seems that if
-comptuational tools can help us derive ethical judgements more efficiently, then we should automate as 
-much ethical reasoning as possible.
-In the most extreme case, we can unthinkingly follow the commands of an ethical calculator that dictates 
-how we should live. Maybe computers can answer the unavoidable question for us.
+comptuational tools can help us derive ethical judgements more efficiently, then everyone should engage
+in computational ethics. In the most extreme case, we can unthinkingly follow the commands of an 
+ethical calculator that dictates how we should live. Maybe computers can answer the unavoidable question for us.
 
@@
 to act on'' \citep[83]{sources}. This choosing is the operation of practical reason, and this reflection
-makes us free. We are free because we must choose which reasons to act on. Every decision that we 
-make is an exercise of freedom.
+makes us free. We are free because we can choose which reasons to act on.
 
@@
 the user's perspective. Just as computational ethics can serve as a tool for academic philosophers to 
-automate away tedium and achieve greater precision, it can do the same for ordinary human beings navigating
+ask new questions and achieve greater precision, it can do the same for ordinary human beings navigating
 the world. Moreover, it also offers another way for the general public to access professional philosophy
@@
 mental activity entirely, as shown by progress in brain simulation \citep{brainsimulation}. Skeptics
-about automated ethics must explain why ethics is any different from other automated human activities.
+about automated ethics must explain why ethics is any different from other automated human activity.
 
@@
 result when an agent sincerely attempts to represent their maxim of action, not when an adversary attempts
- to ``trick'' the categorical imperative.%
+ to ``trick'' the categorical imperative because such tricks will fall outside the scope of our moral 
+almanacs.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 
-Kroy presents a formalization of the first two formulations of the categorical imperative, but wrote 
+Kroy presented a formalization of the first two formulations of the categorical imperative, but wrote 
 before the computational tools existed to automate such a formalization \citep{kroy}. I implement his formalization of the FUL to compare it to my system. 
@@
 philosophical literature. In order to develop high-quality automated ethics, computer scientists and 
-philosophers must work together. This thesis is an experiment in marrying philosophy and computer science 
-to create automated ethics that is both technically and philosophically advanced. Neither discipline alone
-can address the pressing need for ethical AI.
+philosophers must work together. Neither discipline alone can address the pressing need for ethical AI. 
+This thesis is an experiment in marrying philosophy and computer science 
+to create automated ethics that is both technically and philosophically advanced.
 
@@
 %:%24=6%:%
-%:%28=8%:%
+%:%36=8%:%
+%:%37=9%:%
+%:%38=10%:%
 %:%39=11%:%
@@
 %:%47=19%:%
-%:%50=21%:%
-%:%51=22%:%
-%:%52=23%:%
-%:%53=24%:%
-%:%54=25%:%
-%:%55=26%:%
-%:%56=27%:%
-%:%57=28%:%
-%:%58=29%:%
-%:%59=30%:%
-%:%60=31%:%
-%:%61=32%:%
-%:%62=33%:%
-%:%63=34%:%
-%:%64=35%:%
-%:%65=36%:%
-%:%66=37%:%
-%:%67=38%:%
-%:%68=39%:%
-%:%69=40%:%
-%:%70=41%:%
-%:%71=42%:%
-%:%72=43%:%
-%:%73=44%:%
-%:%74=45%:%
-%:%75=46%:%
-%:%76=47%:%
-%:%77=48%:%
-%:%78=49%:%
-%:%79=50%:%
-%:%80=51%:%
-%:%81=52%:%
-%:%82=53%:%
-%:%83=54%:%
-%:%84=55%:%
-%:%85=56%:%
-%:%86=57%:%
-%:%87=58%:%
-%:%88=59%:%
-%:%89=60%:%
-%:%90=61%:%
-%:%91=62%:%
-%:%92=63%:%
-%:%93=64%:%
-%:%94=65%:%
-%:%95=66%:%
-%:%96=67%:%
-%:%97=68%:%
-%:%98=69%:%
-%:%99=70%:%
-%:%100=71%:%
-%:%101=72%:%
-%:%102=73%:%
-%:%103=74%:%
-%:%104=75%:%
-%:%105=76%:%
-%:%106=77%:%
-%:%107=78%:%
-%:%108=79%:%
-%:%109=80%:%
-%:%110=81%:%
-%:%111=82%:%
-%:%112=83%:%
-%:%113=84%:%
-%:%114=85%:%
-%:%115=86%:%
-%:%116=87%:%
-%:%117=88%:%
-%:%118=89%:%
-%:%119=90%:%
-%:%120=91%:%
-%:%121=92%:%
-%:%122=93%:%
-%:%123=94%:%
-%:%124=95%:%
-%:%125=96%:%
-%:%126=97%:%
-%:%127=98%:%
-%:%128=99%:%
-%:%129=100%:%
-%:%130=101%:%
-%:%131=102%:%
-%:%132=103%:%
-%:%133=104%:%
-%:%134=105%:%
-%:%135=106%:%
-%:%136=107%:%
-%:%137=108%:%
-%:%138=109%:%
-%:%139=110%:%
-%:%140=111%:%
-%:%141=112%:%
-%:%142=113%:%
-%:%143=114%:%
-%:%144=115%:%
-%:%145=116%:%
-%:%146=117%:%
-%:%147=118%:%
-%:%148=119%:%
-%:%149=120%:%
-%:%150=121%:%
-%:%151=122%:%
-%:%152=123%:%
-%:%153=124%:%
-%:%154=125%:%
-%:%155=126%:%
-%:%156=127%:%
-%:%157=128%:%
-%:%158=129%:%
-%:%159=130%:%
-%:%160=131%:%
-%:%161=132%:%
-%:%162=133%:%
-%:%163=134%:%
-%:%164=135%:%
-%:%165=136%:%
-%:%166=137%:%
-%:%167=138%:%
-%:%168=139%:%
-%:%169=140%:%
-%:%170=141%:%
-%:%171=142%:%
-%:%180=144%:%
-%:%192=146%:%
-%:%193=147%:%
-%:%194=148%:%
-%:%195=149%:%
-%:%196=150%:%
-%:%197=151%:%
-%:%198=152%:%
-%:%199=153%:%
-%:%200=154%:%
-%:%201=155%:%
-%:%202=156%:%
-%:%211=158%:%
-%:%223=160%:%
-%:%224=161%:%
-%:%225=162%:%
-%:%226=163%:%
-%:%227=164%:%
-%:%228=165%:%
-%:%229=166%:%
-%:%230=167%:%
-%:%231=168%:%
-%:%232=169%:%
-%:%233=170%:%
-%:%234=171%:%
-%:%235=172%:%
-%:%236=173%:%
-%:%237=174%:%
-%:%238=175%:%
-%:%239=176%:%
-%:%240=177%:%
-%:%241=178%:%
-%:%242=179%:%
-%:%243=180%:%
-%:%244=181%:%
-%:%245=182%:%
-%:%246=183%:%
-%:%247=184%:%
-%:%248=185%:%
-%:%249=186%:%
-%:%250=187%:%
-%:%251=188%:%
-%:%252=189%:%
-%:%253=190%:%
-%:%254=191%:%
-%:%255=192%:%
-%:%256=193%:%
-%:%257=194%:%
-%:%258=195%:%
-%:%259=196%:%
-%:%260=197%:%
-%:%261=198%:%
-%:%262=199%:%
-%:%263=200%:%
-%:%264=201%:%
-%:%265=202%:%
-%:%266=203%:%
-%:%267=204%:%
-%:%268=205%:%
-%:%269=206%:%
-%:%270=207%:%
-%:%271=208%:%
-%:%272=209%:%
-%:%273=210%:%
-%:%274=211%:%
-%:%275=212%:%
-%:%276=213%:%
-%:%277=214%:%
-%:%278=215%:%
-%:%279=216%:%
-%:%280=217%:%
-%:%281=218%:%
-%:%282=219%:%
-%:%283=220%:%
-%:%284=221%:%
-%:%285=222%:%
-%:%286=223%:%
-%:%287=224%:%
-%:%288=225%:%
-%:%289=226%:%
-%:%290=227%:%
-%:%291=228%:%
-%:%292=229%:%
-%:%293=230%:%
-%:%294=231%:%
-%:%295=232%:%
-%:%296=233%:%
-%:%297=234%:%
-%:%298=235%:%
-%:%299=236%:%
-%:%300=237%:%
-%:%301=238%:%
-%:%302=239%:%
-%:%303=240%:%
-%:%304=241%:%
-%:%305=242%:%
-%:%306=243%:%
-%:%307=244%:%
-%:%308=245%:%
-%:%309=246%:%
-%:%310=247%:%
-%:%311=248%:%
-%:%312=249%:%
-%:%313=250%:%
-%:%314=251%:%
-%:%315=252%:%
-%:%316=253%:%
-%:%317=254%:%
-%:%318=255%:%
-%:%319=256%:%
-%:%320=257%:%
-%:%321=258%:%
-%:%322=259%:%
-%:%323=260%:%
-%:%324=261%:%
-%:%325=262%:%
-%:%326=263%:%
-%:%327=264%:%
-%:%328=265%:%
-%:%329=266%:%
-%:%330=267%:%
-%:%331=268%:%
-%:%332=269%:%
-%:%333=270%:%
-%:%334=271%:%
-%:%335=272%:%
-%:%336=273%:%
-%:%337=274%:%
-%:%338=275%:%
-%:%339=276%:%
-%:%340=277%:%
-%:%341=278%:%
-%:%342=279%:%
-%:%343=280%:%
-%:%344=281%:%
-%:%345=282%:%
-%:%346=283%:%
-%:%347=284%:%
-%:%348=285%:%
-%:%349=286%:%
-%:%350=287%:%
-%:%351=288%:%
-%:%352=289%:%
-%:%353=290%:%
-%:%354=291%:%
-%:%355=292%:%
-%:%356=293%:%
-%:%357=294%:%
-%:%358=295%:%
-%:%359=296%:%
-%:%360=297%:%
-%:%361=298%:%
-%:%362=299%:%
-%:%363=300%:%
-%:%364=301%:%
-%:%365=302%:%
-%:%366=303%:%
-%:%367=304%:%
-%:%368=305%:%
-%:%369=306%:%
-%:%370=307%:%
-%:%371=308%:%
-%:%372=309%:%
-%:%373=310%:%
-%:%374=311%:%
-%:%375=312%:%
-%:%376=313%:%
-%:%377=314%:%
-%:%378=315%:%
-%:%379=316%:%
-%:%380=317%:%
-%:%381=318%:%
-%:%382=319%:%
-%:%383=320%:%
-%:%384=321%:%
-%:%385=322%:%
-%:%386=323%:%
-%:%387=324%:%
-%:%388=325%:%
-%:%389=326%:%
-%:%390=327%:%
-%:%391=328%:%
-%:%392=329%:%
-%:%393=330%:%
-%:%394=331%:%
-%:%395=332%:%
-%:%396=333%:%
-%:%397=334%:%
-%:%398=335%:%
-%:%399=336%:%
-%:%400=337%:%
-%:%401=338%:%
-%:%402=339%:%
-%:%403=340%:%
-%:%404=341%:%
-%:%405=342%:%
-%:%406=343%:%
-%:%407=344%:%
-%:%408=345%:%
-%:%409=346%:%
-%:%410=347%:%
-%:%411=348%:%
-%:%412=349%:%
-%:%413=350%:%
-%:%414=351%:%
-%:%415=352%:%
-%:%416=353%:%
-%:%425=356%:%
+%:%48=20%:%
+%:%49=21%:%
+%:%50=22%:%
+%:%51=23%:%
+%:%60=25%:%
+%:%72=27%:%
+%:%73=28%:%
+%:%74=29%:%
+%:%75=30%:%
+%:%76=31%:%
+%:%77=32%:%
+%:%78=33%:%
+%:%79=34%:%
+%:%80=35%:%
+%:%81=36%:%
+%:%82=37%:%
+%:%83=38%:%
+%:%84=39%:%
+%:%85=40%:%
+%:%86=41%:%
+%:%87=42%:%
+%:%88=43%:%
+%:%89=44%:%
+%:%90=45%:%
+%:%91=46%:%
+%:%92=47%:%
+%:%93=48%:%
+%:%94=49%:%
+%:%95=50%:%
+%:%96=51%:%
+%:%97=52%:%
+%:%98=53%:%
+%:%99=54%:%
+%:%100=55%:%
+%:%101=56%:%
+%:%102=57%:%
+%:%103=58%:%
+%:%104=59%:%
+%:%105=60%:%
+%:%106=61%:%
+%:%107=62%:%
+%:%108=63%:%
+%:%109=64%:%
+%:%110=65%:%
+%:%111=66%:%
+%:%112=67%:%
+%:%113=68%:%
+%:%114=69%:%
+%:%115=70%:%
+%:%116=71%:%
+%:%117=72%:%
+%:%118=73%:%
+%:%119=74%:%
+%:%120=75%:%
+%:%121=76%:%
+%:%122=77%:%
+%:%123=78%:%
+%:%124=79%:%
+%:%125=80%:%
+%:%126=81%:%
+%:%127=82%:%
+%:%128=83%:%
+%:%129=84%:%
+%:%130=85%:%
+%:%131=86%:%
+%:%132=87%:%
+%:%133=88%:%
+%:%134=89%:%
+%:%135=90%:%
+%:%136=91%:%
+%:%137=92%:%
+%:%138=93%:%
+%:%139=94%:%
+%:%140=95%:%
+%:%141=96%:%
+%:%142=97%:%
+%:%143=98%:%
+%:%144=99%:%
+%:%145=100%:%
+%:%146=101%:%
+%:%147=102%:%
+%:%148=103%:%
+%:%149=104%:%
+%:%150=105%:%
+%:%151=106%:%
+%:%152=107%:%
+%:%153=108%:%
+%:%154=109%:%
+%:%155=110%:%
+%:%156=111%:%
+%:%157=112%:%
+%:%158=113%:%
+%:%159=114%:%
+%:%160=115%:%
+%:%161=116%:%
+%:%162=117%:%
+%:%163=118%:%
+%:%164=119%:%
+%:%165=120%:%
+%:%166=121%:%
+%:%167=122%:%
+%:%168=123%:%
+%:%169=124%:%
+%:%170=125%:%
+%:%171=126%:%
+%:%172=127%:%
+%:%173=128%:%
+%:%174=129%:%
+%:%175=130%:%
+%:%176=131%:%
+%:%177=132%:%
+%:%178=133%:%
+%:%179=134%:%
+%:%180=135%:%
+%:%181=136%:%
+%:%182=137%:%
+%:%183=138%:%
+%:%184=139%:%
+%:%185=140%:%
+%:%186=141%:%
+%:%187=142%:%
+%:%188=143%:%
+%:%189=144%:%
+%:%190=145%:%
+%:%191=146%:%
+%:%192=147%:%
+%:%193=148%:%
+%:%194=149%:%
+%:%195=150%:%
+%:%196=151%:%
+%:%197=152%:%
+%:%198=153%:%
+%:%207=155%:%
+%:%219=157%:%
+%:%220=158%:%
+%:%221=159%:%
+%:%222=160%:%
+%:%223=161%:%
+%:%224=162%:%
+%:%225=163%:%
+%:%226=164%:%
+%:%227=165%:%
+%:%228=166%:%
+%:%229=167%:%
+%:%238=169%:%
+%:%250=171%:%
+%:%251=172%:%
+%:%252=173%:%
+%:%253=174%:%
+%:%254=175%:%
+%:%255=176%:%
+%:%256=177%:%
+%:%257=178%:%
+%:%258=179%:%
+%:%259=180%:%
+%:%260=181%:%
+%:%261=182%:%
+%:%262=183%:%
+%:%263=184%:%
+%:%264=185%:%
+%:%265=186%:%
+%:%266=187%:%
+%:%267=188%:%
+%:%268=189%:%
+%:%269=190%:%
+%:%270=191%:%
+%:%271=192%:%
+%:%272=193%:%
+%:%273=194%:%
+%:%274=195%:%
+%:%275=196%:%
+%:%276=197%:%
+%:%277=198%:%
+%:%278=199%:%
+%:%279=200%:%
+%:%280=201%:%
+%:%281=202%:%
+%:%282=203%:%
+%:%283=204%:%
+%:%284=205%:%
+%:%285=206%:%
+%:%286=207%:%
+%:%287=208%:%
+%:%288=209%:%
+%:%289=210%:%
+%:%290=211%:%
+%:%291=212%:%
+%:%292=213%:%
+%:%293=214%:%
+%:%294=215%:%
+%:%295=216%:%
+%:%296=217%:%
+%:%297=218%:%
+%:%298=219%:%
+%:%299=220%:%
+%:%300=221%:%
+%:%301=222%:%
+%:%302=223%:%
+%:%303=224%:%
+%:%304=225%:%
+%:%305=226%:%
+%:%306=227%:%
+%:%307=228%:%
+%:%308=229%:%
+%:%309=230%:%
+%:%310=231%:%
+%:%311=232%:%
+%:%312=233%:%
+%:%313=234%:%
+%:%314=235%:%
+%:%315=236%:%
+%:%316=237%:%
+%:%317=238%:%
+%:%318=239%:%
+%:%319=240%:%
+%:%320=241%:%
+%:%321=242%:%
+%:%322=243%:%
+%:%323=244%:%
+%:%324=245%:%
+%:%325=246%:%
+%:%326=247%:%
+%:%327=248%:%
+%:%328=249%:%
+%:%329=250%:%
+%:%330=251%:%
+%:%331=252%:%
+%:%332=253%:%
+%:%333=254%:%
+%:%334=255%:%
+%:%335=256%:%
+%:%336=257%:%
+%:%337=258%:%
+%:%338=259%:%
+%:%339=260%:%
+%:%340=261%:%
+%:%341=262%:%
+%:%342=263%:%
+%:%343=264%:%
+%:%344=265%:%
+%:%345=266%:%
+%:%346=267%:%
+%:%347=268%:%
+%:%348=269%:%
+%:%349=270%:%
+%:%350=271%:%
+%:%351=272%:%
+%:%352=273%:%
+%:%353=274%:%
+%:%354=275%:%
+%:%355=276%:%
+%:%356=277%:%
+%:%357=278%:%
+%:%358=279%:%
+%:%359=280%:%
+%:%360=281%:%
+%:%361=282%:%
+%:%362=283%:%
+%:%363=284%:%
+%:%364=285%:%
+%:%365=286%:%
+%:%366=287%:%
+%:%367=288%:%
+%:%368=289%:%
+%:%369=290%:%
+%:%370=291%:%
+%:%371=292%:%
+%:%372=293%:%
+%:%373=294%:%
+%:%374=295%:%
+%:%375=296%:%
+%:%376=297%:%
+%:%377=298%:%
+%:%378=299%:%
+%:%379=300%:%
+%:%380=301%:%
+%:%381=302%:%
+%:%382=303%:%
+%:%383=304%:%
+%:%384=305%:%
+%:%385=306%:%
+%:%386=307%:%
+%:%387=308%:%
+%:%388=309%:%
+%:%389=310%:%
+%:%390=311%:%
+%:%391=312%:%
+%:%392=313%:%
+%:%393=314%:%
+%:%394=315%:%
+%:%395=316%:%
+%:%396=317%:%
+%:%397=318%:%
+%:%398=319%:%
+%:%399=320%:%
+%:%400=321%:%
+%:%401=322%:%
+%:%402=323%:%
+%:%403=324%:%
+%:%404=325%:%
+%:%405=326%:%
+%:%406=327%:%
+%:%407=328%:%
+%:%408=329%:%
+%:%409=330%:%
+%:%410=331%:%
+%:%411=332%:%
+%:%412=333%:%
+%:%413=334%:%
+%:%414=335%:%
+%:%415=336%:%
+%:%416=337%:%
+%:%417=338%:%
+%:%418=339%:%
+%:%419=340%:%
+%:%420=341%:%
+%:%421=342%:%
+%:%422=343%:%
+%:%423=344%:%
+%:%424=345%:%
+%:%425=346%:%
+%:%426=347%:%
+%:%427=348%:%
+%:%428=349%:%
+%:%429=350%:%
+%:%430=351%:%
+%:%431=352%:%
+%:%432=353%:%
+%:%433=354%:%
+%:%434=355%:%
+%:%435=356%:%
+%:%436=357%:%
 %:%437=358%:%
@@
 %:%443=364%:%
-%:%444=365%:%
-%:%445=366%:%
-%:%446=367%:%
-%:%447=368%:%
-%:%448=369%:%
-%:%449=370%:%
-%:%450=371%:%
-%:%451=372%:%
-%:%452=373%:%
-%:%453=374%:%
-%:%454=375%:%
-%:%455=376%:%
-%:%456=377%:%
-%:%457=378%:%
-%:%458=379%:%
-%:%459=380%:%
-%:%460=381%:%
-%:%461=382%:%
-%:%462=383%:%
-%:%463=384%:%
-%:%464=385%:%
-%:%465=386%:%
-%:%466=387%:%
-%:%467=388%:%
-%:%468=389%:%
-%:%469=390%:%
-%:%470=391%:%
-%:%471=392%:%
-%:%472=393%:%
-%:%473=394%:%
-%:%474=395%:%
-%:%475=396%:%
-%:%476=397%:%
-%:%477=398%:%
-%:%478=399%:%
-%:%479=400%:%
-%:%480=401%:%
-%:%481=402%:%
-%:%482=403%:%
-%:%483=404%:%
-%:%484=405%:%
-%:%485=406%:%
-%:%486=407%:%
-%:%487=408%:%
-%:%488=409%:%
-%:%489=410%:%
-%:%490=411%:%
-%:%491=412%:%
-%:%492=413%:%
-%:%493=414%:%
-%:%494=415%:%
-%:%495=416%:%
-%:%496=417%:%
-%:%497=418%:%
-%:%498=419%:%
-%:%499=420%:%
-%:%500=421%:%
-%:%501=422%:%
-%:%502=423%:%
-%:%503=424%:%
-%:%512=426%:%
-%:%524=428%:%
-%:%525=429%:%
-%:%526=430%:%
-%:%527=431%:%
-%:%528=432%:%
-%:%529=433%:%
-%:%530=434%:%
-%:%531=435%:%
-%:%532=436%:%
-%:%533=437%:%
-%:%534=438%:%
-%:%535=439%:%
-%:%536=440%:%
-%:%537=441%:%
-%:%538=442%:%
-%:%539=443%:%
-%:%540=444%:%
-%:%541=445%:%
-%:%542=446%:%
-%:%543=447%:%
-%:%544=448%:%
-%:%545=449%:%
-%:%546=450%:%
-%:%547=451%:%
-%:%548=452%:%
-%:%549=453%:%
-%:%550=454%:%
-%:%551=455%:%
-%:%552=456%:%
-%:%553=457%:%
-%:%554=458%:%
-%:%555=459%:%
-%:%556=460%:%
-%:%557=461%:%
-%:%558=462%:%
-%:%559=463%:%
-%:%560=464%:%
-%:%561=465%:%
-%:%562=466%:%
-%:%563=467%:%
-%:%564=468%:%
-%:%565=469%:%
-%:%566=470%:%
-%:%567=471%:%
-%:%568=472%:%
-%:%569=473%:%
-%:%570=474%:%
-%:%571=475%:%
-%:%572=476%:%
-%:%573=477%:%
-%:%574=478%:%
-%:%575=479%:%
-%:%576=480%:%
-%:%577=481%:%
-%:%578=482%:%
-%:%579=483%:%
-%:%580=484%:%
-%:%581=485%:%
-%:%582=486%:%
-%:%583=487%:%
-%:%584=488%:%
-%:%585=489%:%
-%:%586=490%:%
-%:%587=491%:%
-%:%588=492%:%
-%:%589=493%:%
-%:%590=494%:%
-%:%591=495%:%
-%:%592=496%:%
-%:%593=497%:%
-%:%594=498%:%
-%:%595=499%:%
-%:%596=500%:%
-%:%597=501%:%
-%:%598=502%:%
-%:%599=503%:%
-%:%600=504%:%
-%:%601=505%:%
-%:%602=506%:%
-%:%603=507%:%
-%:%612=510%:%
-%:%624=513%:%
-%:%625=514%:%
-%:%626=515%:%
-%:%627=516%:%
-%:%628=517%:%
-%:%629=518%:%
-%:%630=519%:%
-%:%631=520%:%
-%:%632=521%:%
-%:%633=522%:%
-%:%634=523%:%
-%:%635=524%:%
-%:%636=525%:%
-%:%637=526%:%
-%:%638=527%:%
-%:%639=528%:%
-%:%640=529%:%
-%:%641=530%:%
-%:%642=531%:%
-%:%643=532%:%
-%:%644=533%:%
-%:%645=534%:%
-%:%646=535%:%
-%:%647=536%:%
-%:%648=537%:%
-%:%649=538%:%
-%:%650=539%:%
-%:%651=540%:%
-%:%652=541%:%
-%:%653=542%:%
-%:%654=543%:%
-%:%655=544%:%
-%:%656=545%:%
-%:%657=546%:%
-%:%658=547%:%
-%:%659=548%:%
-%:%660=549%:%
-%:%661=550%:%
-%:%662=551%:%
-%:%663=552%:%
-%:%664=553%:%
-%:%665=554%:%
-%:%666=555%:%
-%:%667=556%:%
-%:%668=557%:%
-%:%669=558%:%
-%:%670=559%:%
-%:%671=560%:%
-%:%672=561%:%
-%:%673=562%:%
-%:%674=563%:%
-%:%675=564%:%
-%:%676=565%:%
-%:%677=566%:%
-%:%678=567%:%
-%:%679=568%:%
-%:%680=569%:%
-%:%681=570%:%
-%:%682=571%:%
-%:%683=572%:%
-%:%684=573%:%
-%:%685=574%:%
-%:%686=575%:%
-%:%687=576%:%
-%:%688=577%:%
-%:%689=578%:%
-%:%690=579%:%
-%:%691=580%:%
-%:%692=581%:%
-%:%693=582%:%
-%:%694=583%:%
-%:%695=584%:%
-%:%696=585%:%
-%:%697=586%:%
-%:%698=587%:%
-%:%699=588%:%
-%:%700=589%:%
-%:%701=590%:%
-%:%702=591%:%
-%:%703=592%:%
-%:%704=593%:%
-%:%705=594%:%
-%:%706=595%:%
-%:%707=596%:%
-%:%708=597%:%
-%:%709=598%:%
-%:%710=599%:%
-%:%711=600%:%
-%:%712=601%:%
-%:%713=602%:%
-%:%714=603%:%
-%:%715=604%:%
-%:%716=605%:%
-%:%717=606%:%
-%:%718=607%:%
-%:%719=608%:%
-%:%720=609%:%
-%:%721=610%:%
-%:%722=611%:%
-%:%723=612%:%
-%:%724=613%:%
-%:%725=614%:%
-%:%726=615%:%
-%:%727=616%:%
-%:%728=617%:%
-%:%729=618%:%
-%:%730=619%:%
-%:%731=620%:%
-%:%732=621%:%
-%:%733=622%:%
-%:%734=623%:%
-%:%735=624%:%
-%:%736=625%:%
-%:%737=626%:%
-%:%738=627%:%
-%:%739=628%:%
-%:%740=629%:%
-%:%741=630%:%
-%:%742=631%:%
-%:%745=633%:%
-%:%746=634%:%
-%:%747=635%:%
-%:%748=636%:%
-%:%749=637%:%
-%:%750=638%:%
-%:%753=639%:%
-%:%754=640%:%
-%:%755=641%:%
-%:%756=642%:%
-%:%757=643%:%
-%:%758=644%:%
-%:%759=645%:%
-%:%760=646%:%
-%:%761=647%:%
-%:%762=648%:%
-%:%763=649%:%
-%:%764=650%:%
-%:%765=651%:%
-%:%766=652%:%
-%:%767=653%:%
-%:%768=654%:%
-%:%777=658%:%
-%:%789=660%:%
-%:%790=661%:%
-%:%791=662%:%
-%:%792=663%:%
-%:%793=664%:%
-%:%794=665%:%
-%:%795=666%:%
-%:%796=667%:%
-%:%797=668%:%
-%:%798=669%:%
-%:%799=670%:%
-%:%800=671%:%
-%:%801=672%:%
-%:%802=673%:%
-%:%803=674%:%
-%:%804=675%:%
-%:%805=676%:%
-%:%806=677%:%
-%:%807=678%:%
-%:%808=679%:%
-%:%809=680%:%
-%:%810=681%:%
-%:%811=682%:%
-%:%812=683%:%
-%:%813=684%:%
-%:%814=685%:%
-%:%815=686%:%
-%:%816=687%:%
-%:%817=688%:%
-%:%818=689%:%
-%:%819=690%:%
-%:%820=691%:%
-%:%821=692%:%
-%:%822=693%:%
-%:%823=694%:%
-%:%824=695%:%
-%:%825=696%:%
-%:%826=697%:%
-%:%827=698%:%
-%:%828=699%:%
-%:%829=700%:%
-%:%830=701%:%
-%:%831=702%:%
-%:%832=703%:%
-%:%833=704%:%
-%:%834=705%:%
-%:%835=706%:%
-%:%836=707%:%
-%:%837=708%:%
-%:%838=709%:%
-%:%839=710%:%
-%:%840=711%:%
-%:%849=713%:%
-%:%861=715%:%
-%:%862=716%:%
-%:%863=717%:%
-%:%864=718%:%
-%:%865=719%:%
-%:%866=720%:%
-%:%867=721%:%
-%:%868=722%:%
-%:%869=723%:%
-%:%870=724%:%
-%:%871=725%:%
-%:%872=726%:%
-%:%873=727%:%
-%:%874=728%:%
-%:%875=729%:%
-%:%876=730%:%
-%:%877=731%:%
-%:%878=732%:%
-%:%879=733%:%
-%:%880=734%:%
-%:%881=735%:%
-%:%882=736%:%
-%:%883=737%:%
-%:%884=738%:%
-%:%885=739%:%
-%:%886=740%:%
-%:%887=741%:%
-%:%888=742%:%
-%:%889=743%:%
-%:%890=744%:%
-%:%891=745%:%
-%:%892=746%:%
-%:%893=747%:%
-%:%894=748%:%
-%:%895=749%:%
-%:%896=750%:%
-%:%897=751%:%
-%:%898=752%:%
-%:%899=753%:%
+%:%452=367%:%
+%:%464=369%:%
+%:%465=370%:%
+%:%466=371%:%
+%:%467=372%:%
+%:%468=373%:%
+%:%469=374%:%
+%:%470=375%:%
+%:%471=376%:%
+%:%472=377%:%
+%:%473=378%:%
+%:%474=379%:%
+%:%475=380%:%
+%:%476=381%:%
+%:%477=382%:%
+%:%478=383%:%
+%:%479=384%:%
+%:%480=385%:%
+%:%481=386%:%
+%:%482=387%:%
+%:%483=388%:%
+%:%484=389%:%
+%:%485=390%:%
+%:%486=391%:%
+%:%487=392%:%
+%:%488=393%:%
+%:%489=394%:%
+%:%490=395%:%
+%:%491=396%:%
+%:%492=397%:%
+%:%493=398%:%
+%:%494=399%:%
+%:%495=400%:%
+%:%496=401%:%
+%:%497=402%:%
+%:%498=403%:%
+%:%499=404%:%
+%:%500=405%:%
+%:%501=406%:%
+%:%502=407%:%
+%:%503=408%:%
+%:%504=409%:%
+%:%505=410%:%
+%:%506=411%:%
+%:%507=412%:%
+%:%508=413%:%
+%:%509=414%:%
+%:%510=415%:%
+%:%511=416%:%
+%:%512=417%:%
+%:%513=418%:%
+%:%514=419%:%
+%:%515=420%:%
+%:%516=421%:%
+%:%517=422%:%
+%:%518=423%:%
+%:%519=424%:%
+%:%520=425%:%
+%:%521=426%:%
+%:%522=427%:%
+%:%523=428%:%
+%:%524=429%:%
+%:%525=430%:%
+%:%526=431%:%
+%:%527=432%:%
+%:%528=433%:%
+%:%529=434%:%
+%:%538=436%:%
+%:%550=438%:%
+%:%551=439%:%
+%:%552=440%:%
+%:%553=441%:%
+%:%554=442%:%
+%:%555=443%:%
+%:%556=444%:%
+%:%557=445%:%
+%:%558=446%:%
+%:%559=447%:%
+%:%560=448%:%
+%:%561=449%:%
+%:%562=450%:%
+%:%563=451%:%
+%:%564=452%:%
+%:%565=453%:%
+%:%566=454%:%
+%:%567=455%:%
+%:%568=456%:%
+%:%569=457%:%
+%:%570=458%:%
+%:%571=459%:%
+%:%572=460%:%
+%:%573=461%:%
+%:%574=462%:%
+%:%575=463%:%
+%:%576=464%:%
+%:%577=465%:%
+%:%578=466%:%
+%:%579=467%:%
+%:%580=468%:%
+%:%581=469%:%
+%:%582=470%:%
+%:%583=471%:%
+%:%584=472%:%
+%:%585=473%:%
+%:%586=474%:%
+%:%587=475%:%
+%:%588=476%:%
+%:%589=477%:%
+%:%590=478%:%
+%:%591=479%:%
+%:%592=480%:%
+%:%593=481%:%
+%:%594=482%:%
+%:%595=483%:%
+%:%596=484%:%
+%:%597=485%:%
+%:%598=486%:%
+%:%599=487%:%
+%:%600=488%:%
+%:%601=489%:%
+%:%602=490%:%
+%:%603=491%:%
+%:%604=492%:%
+%:%605=493%:%
+%:%606=494%:%
+%:%607=495%:%
+%:%608=496%:%
+%:%609=497%:%
+%:%610=498%:%
+%:%611=499%:%
+%:%612=500%:%
+%:%613=501%:%
+%:%614=502%:%
+%:%615=503%:%
+%:%616=504%:%
+%:%617=505%:%
+%:%618=506%:%
+%:%619=507%:%
+%:%620=508%:%
+%:%621=509%:%
+%:%622=510%:%
+%:%623=511%:%
+%:%624=512%:%
+%:%625=513%:%
+%:%626=514%:%
+%:%635=517%:%
+%:%647=520%:%
+%:%648=521%:%
+%:%649=522%:%
+%:%650=523%:%
+%:%651=524%:%
+%:%652=525%:%
+%:%653=526%:%
+%:%654=527%:%
+%:%655=528%:%
+%:%656=529%:%
+%:%657=530%:%
+%:%658=531%:%
+%:%659=532%:%
+%:%660=533%:%
+%:%661=534%:%
+%:%662=535%:%
+%:%663=536%:%
+%:%664=537%:%
+%:%665=538%:%
+%:%666=539%:%
+%:%667=540%:%
+%:%668=541%:%
+%:%669=542%:%
+%:%670=543%:%
+%:%671=544%:%
+%:%672=545%:%
+%:%673=546%:%
+%:%674=547%:%
+%:%675=548%:%
+%:%676=549%:%
+%:%677=550%:%
+%:%678=551%:%
+%:%679=552%:%
+%:%680=553%:%
+%:%681=554%:%
+%:%682=555%:%
+%:%683=556%:%
+%:%684=557%:%
+%:%685=558%:%
+%:%686=559%:%
+%:%687=560%:%
+%:%688=561%:%
+%:%689=562%:%
+%:%690=563%:%
+%:%691=564%:%
+%:%692=565%:%
+%:%693=566%:%
+%:%694=567%:%
+%:%695=568%:%
+%:%696=569%:%
+%:%697=570%:%
+%:%698=571%:%
+%:%699=572%:%
+%:%700=573%:%
+%:%701=574%:%
+%:%702=575%:%
+%:%703=576%:%
+%:%704=577%:%
+%:%705=578%:%
+%:%706=579%:%
+%:%707=580%:%
+%:%708=581%:%
+%:%709=582%:%
+%:%710=583%:%
+%:%711=584%:%
+%:%712=585%:%
+%:%713=586%:%
+%:%714=587%:%
+%:%715=588%:%
+%:%716=589%:%
+%:%717=590%:%
+%:%718=591%:%
+%:%719=592%:%
+%:%720=593%:%
+%:%721=594%:%
+%:%722=595%:%
+%:%723=596%:%
+%:%724=597%:%
+%:%725=598%:%
+%:%726=599%:%
+%:%727=600%:%
+%:%728=601%:%
+%:%729=602%:%
+%:%730=603%:%
+%:%731=604%:%
+%:%732=605%:%
+%:%733=606%:%
+%:%734=607%:%
+%:%735=608%:%
+%:%736=609%:%
+%:%737=610%:%
+%:%738=611%:%
+%:%739=612%:%
+%:%740=613%:%
+%:%741=614%:%
+%:%742=615%:%
+%:%743=616%:%
+%:%744=617%:%
+%:%745=618%:%
+%:%746=619%:%
+%:%747=620%:%
+%:%748=621%:%
+%:%749=622%:%
+%:%750=623%:%
+%:%751=624%:%
+%:%752=625%:%
+%:%753=626%:%
+%:%754=627%:%
+%:%755=628%:%
+%:%756=629%:%
+%:%757=630%:%
+%:%758=631%:%
+%:%759=632%:%
+%:%760=633%:%
+%:%761=634%:%
+%:%762=635%:%
+%:%763=636%:%
+%:%764=637%:%
+%:%765=638%:%
+%:%766=639%:%
+%:%769=641%:%
+%:%770=642%:%
+%:%771=643%:%
+%:%772=644%:%
+%:%773=645%:%
+%:%774=646%:%
+%:%777=647%:%
+%:%778=648%:%
+%:%779=649%:%
+%:%780=650%:%
+%:%781=651%:%
+%:%782=652%:%
+%:%783=653%:%
+%:%784=654%:%
+%:%785=655%:%
+%:%786=656%:%
+%:%787=657%:%
+%:%788=658%:%
+%:%789=659%:%
+%:%790=660%:%
+%:%791=661%:%
+%:%792=662%:%
+%:%801=666%:%
+%:%813=668%:%
+%:%814=669%:%
+%:%815=670%:%
+%:%816=671%:%
+%:%817=672%:%
+%:%818=673%:%
+%:%819=674%:%
+%:%820=675%:%
+%:%821=676%:%
+%:%822=677%:%
+%:%823=678%:%
+%:%824=679%:%
+%:%825=680%:%
+%:%826=681%:%
+%:%827=682%:%
+%:%828=683%:%
+%:%829=684%:%
+%:%830=685%:%
+%:%831=686%:%
+%:%832=687%:%
+%:%833=688%:%
+%:%834=689%:%
+%:%835=690%:%
+%:%836=691%:%
+%:%837=692%:%
+%:%838=693%:%
+%:%839=694%:%
+%:%840=695%:%
+%:%841=696%:%
+%:%842=697%:%
+%:%843=698%:%
+%:%844=699%:%
+%:%845=700%:%
+%:%846=701%:%
+%:%847=702%:%
+%:%848=703%:%
+%:%849=704%:%
+%:%850=705%:%
+%:%851=706%:%
+%:%852=707%:%
+%:%853=708%:%
+%:%854=709%:%
+%:%855=710%:%
+%:%856=711%:%
+%:%857=712%:%
+%:%858=713%:%
+%:%859=714%:%
+%:%860=715%:%
+%:%861=716%:%
+%:%862=717%:%
+%:%863=718%:%
+%:%864=719%:%
+%:%873=721%:%
+%:%885=723%:%
+%:%886=724%:%
+%:%887=725%:%
+%:%888=726%:%
+%:%889=727%:%
+%:%890=728%:%
+%:%891=729%:%
+%:%892=730%:%
+%:%893=731%:%
+%:%894=732%:%
+%:%895=733%:%
+%:%896=734%:%
+%:%897=735%:%
+%:%898=736%:%
+%:%899=737%:%
+%:%900=738%:%
+%:%901=739%:%
+%:%902=740%:%
+%:%903=741%:%
+%:%904=742%:%
+%:%905=743%:%
+%:%906=744%:%
+%:%907=745%:%
+%:%908=746%:%
+%:%909=747%:%
+%:%910=748%:%
+%:%911=749%:%
+%:%912=750%:%
+%:%913=751%:%
+%:%914=752%:%
+%:%915=753%:%
+%:%916=754%:%
+%:%917=755%:%
+%:%918=756%:%
+%:%919=757%:%
+%:%920=758%:%
+%:%921=759%:%
+%:%922=760%:%
+%:%923=761%:%

### 2022-03-21 paper/output/document/thesis_0_acknowledgements.tex
dhoom again

@@
 Every step of this process has been made easier by my mentors' unwavering support. Thank you to Professor 
-Nada Amin for taking me seriously when this project was just a vague intuition, for always asking the 
+Nada Amin for taking me seriously when this project was only a vague intuition, for always asking the 
 right questions at the right time, and for being willing 

### 2022-03-21 paper/output/document/thesis_1_intro.tex
dhoom again

@@
 ethical implications without explicitly performing ethical
-reasoning, in many cases they do so without human supervision. For example, the Alleghany Family Screening 
+reasoning, they often do so without human supervision. For example, the Alleghany Family Screening 
 tool can automatically trigger an investigation into a potential case of child neglect, a decision that 
@@
 Machine ethicists recognize the need for automated ethics and have made both theoretical 
-(\citep{moralmachineonline}, \citep{davenport}, \citep{moralmachine}, \citep{gabriel}) and practical progress 
-(\citep{logicprogramming}, \citep{biology}, \citep{delphi}, \citep{winfield}) towards automating ethics. 
-However, prior work in machine ethics using popular ethical theories like deontology (\citep{deon2}, \citep{deon1}), 
-consequentialism (\citep{util1}, \citep{util2}, \citep{cloos}), and virtue ethics \citep{virtue2} rarely 
+(\citep{moralmachine}, \citep{davenport}, \citep{moralmachineonline}, \citep{gabriel}) and practical progress 
+(\citep{logicprogramming}, \citep{biology}, \citep{winfield}, \citep{delphi}) towards automating ethics. 
+However, prior work in machine ethics using popular ethical theories like deontology (\citep{deon1}, \citep{deon2}), 
+consequentialism (\citep{util2}, \citep{util1}, \citep{cloos}), and virtue ethics \citep{virtue2} rarely 
 engages with philosophical literature and thus often misses philosophers' insights. Even the above example of 
@@
 that artifical agents face are not entirely new, so solutions to these problems should take advantage of philosophical 
-progress. Philosophers are devoted to the creation of better ethical theories, so the 
+progress. Ethical philosophers are devoted to the creation of better ethical theories, so the 
 more faithful that automated ethics is to philosophical literature, the more nuanced, precise, consistent, and
@@
 On the other hand, approaches that begin with an ethical theory, instead of a computational method, must contend with the 
-fact that ethical theories are almost always described in natural language and must be made
-precise enough to represent to a computer. Even once ethics is translated from natural 
+fact that ethical theories are almost always described in natural language too
+imprecise to represent to a computer. Even once ethics is translated from natural 
 language to program syntax, the factual background given to the machine, such as the description of 
@@
 \item In Section \ref{testing}, I present a testing framework that can evaluate how faithful an implementation 
-of automated Kantian ethics is, inspired by philosophical literature. This testing framework shows that 
+of automated Kantian ethics is to philosophical literature. This testing framework shows that 
 my formalization substantially improves on prior attempts to formalize Kantian ethics.
@@
 using it to produce nuanced answers to two well-known Kantian ethical dilemmas. I show that, because 
-my system draws on definitions of Kantian ethics presented in philosophical literature, it is able 
+my system draws on interpretations of Kantian ethics presented in philosophical literature, it is able 
 to perform sophisticated moral reasoning with minimal factual or situational context.
@@
 progress, just as computational tools unlock discoveries in fields like protein folding and drug discovery.
+In Section \ref{ordinarypeople}, I extend this argument to the everyday ethical reasoning that we all
+perform as we navigate the world and explore how automated ethics can improve our decision-making. 
 \end{enumerate}%
@@
 My implementation of automated Kantian ethics formalizes Kant's moral rule
-in deontic logic, a modal logic that can express obligation, or morally binding requirements. Traditional modal 
-logics include the necessitation operator, denoted as $\Box$. Using the Kripke semantics, 
-$\Box p$ is true at world $w$ if $p$ is true at all worlds that neighbor $w$ \citep{cresswell}. Modal 
+in deontic logic, a modal logic that can express obligation, or morally binding requirements. Most modal 
+logics include a necessitation operator, denoted as $\Box$, where
+$\Box p$ is true at world $w$ if $p$ is true at all worlds that neighbor $w$ \citep{cresswell}. Such 
 logics  also contain the possibility operator $\diamond$, where $\diamond \, p \longleftrightarrow \neg (\Box (\neg p))$ 
@@
 replaces $\Box$ with the obligation operator $O$, where $O \, p$ is true at $w$ 
-if $p$ is true at all morally perfect versions of $w$ \citep{sep-logic-deontic}. While SDL is appreciable for its simplicity, 
-in situations where duty is violated, the logic breaks down and produces paradoxical results.\footnote{The 
-paradigm case of a contrary-to-duty paradox is the 
-Chisholm paradox. Consider the following statements: \begin{enumerate}
-\item It ought to be that Tom helps his neighbors
-\item It ought to be that if Tom helps his neighbors, he tells them he is coming
-\item If Tom does not help his neighbors, he ought not tell them that he is coming
-\item Tom does not help his neighbors
-\end{enumerate} 
-These premises contradict themselves, because items (2)-(4) imply that Tom ought not help his neighbors. The 
-contradiction results because the logic cannot handle violations of duty mixed with
-conditionals. \citep{chisholm, ctd}
-} To avoid such issues, I use Dyadic Deontic Logic, in which
+if $p$ is true at all morally perfect versions of $w$ \citep{sep-logic-deontic}. I use a more sophisticated
+version of DDL called Dyadic Deontic Logic, in which
 the dyadic obligation operator $O\{A \vert B\}$ represents the sentence ``A is obligated in the context B.'' 
-The introduction of context allows DDL to express more nuanced reasoning and resolve contrary-to-duty
-paradoxes. DDL is both deontic and modal, 
-so sentences like $O\{A \vert B\}$ are terms that can be true or false at a world. For example, the 
-sentence $O \{ \text{steal} \vert \text{when rich}\}$ is true at a world if stealing when rich is 
-obligated at that particular world.
+The introduction of context allows DDL to express more nuanced reasoning and certain paradoxes that plague
+SDL.
 
@@
 prohibits actions that are not ``universalizable,'' or cannot be undertaken by everyone. It formalizes
-the kind of objection drawn by the question, ``What if everyone did that?''
+the kind of objections and prohibitions inspired by the question, ``What if everyone did that?'' Unlike
+other ethical traditions, Kantian ethics evaluates actions based on the moral value of the action itself, as opposed to
+the value of the action's consequences or the actor's disposition.
 
@@
 but it can also help philosophers better study philosophy. I argue for ``computational ethics,'' or the use of computational tools to 
-make philosophical progress, analogous to computational biology or neuroscience. 
+make philosophical progress, analogous to computational biology. 
 I demonstrate the potential of computational ethics by presenting a 
@@
 %:%143=114%:%
-%:%147=117%:%
-%:%148=118%:%
+%:%144=115%:%
+%:%145=116%:%
 %:%149=119%:%
@@
 %:%217=187%:%
-%:%218=188%:%
-%:%219=189%:%
-%:%220=190%:%
-%:%221=191%:%
-%:%222=192%:%
-%:%223=193%:%
-%:%224=194%:%
-%:%225=195%:%
-%:%226=196%:%
-%:%227=197%:%

### 2022-03-21 paper/output/document/thesis_2_methods.tex
dhoom again

@@
 implement the formalized ethical theory (Isabelle/HOL). In this section, I describe these components and 
-present the philosophical, logic, and computational background underlying my system.
-
-These three components determine the features
-and limitations of my implementation of automated ethics. Other choices of 
-components, such as another ethical theory, a different logic, or a different theorem prover could be 
-made. Flaws with these components are limitations of my system, but do not 
+present the philosophical, logical, and computational background underlying my system.
+
+Other choices of components, such as another ethical theory, a different logic, or a different theorem 
+prover could be made. Flaws with these components are limitations of my system, but do not 
 indict logic-programming-based automated ethics more generally. My thesis seeks to 
-both present a specific implementation of automated ethics but also to argue for a particular approach 
-to automating ethical reasoning and these choices are relevant to the former goal but not to the latter.%
+both present a specific implementation of automated ethics and to argue for a particular approach 
+to automating ethical reasoning more generally and these choices are relevant to the former goal but 
+not to the latter.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 to present a comprehensive overview of all consequentialist or virtue ethical theories. Instead, I 
-some example approaches in each tradition and argue that deontology is more straightforward 
+explore example approaches in each tradition and argue that deontology is more straightforward 
 to formalize than these approaches. Insofar as my project serves 
 as an early proof-of-concept, I choose to automate an ethical theory that 
-poses fewer challenges than others. All ethical traditions have debates that an 
-automated ethical system will need to take a stance on, but these debates are less frequent and controversial
-for Kantian ethics than for consequentialism and virtue ethics.
+poses fewer challenges than others.
 
@@
 tradition, I present a crash course for non-philosophers and then explain some obstacles to automation, 
-arguing that these obstacles are weakest in the case of Kantian ethics.%
+arguing that these obstacles are weakest in the case of Kantian ethics. All ethical traditions have debates that an 
+automated ethical system will need to take a stance on, but these debates are less frequent and controversial
+for Kantian ethics than for consequentialism and virtue ethics.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 of an action from the action itself. Some debates in the consequentialist tradition include 
-which consequences matter, what constitutes a ``good" consequence, and how we can 
+which consequences matter, what constitutes a ``good'' consequence, and how we can 
 aggregate the consequences of an action over all the individuals involved.%
@@
 takes implicit stances on the debates above. It assumes that consequences can be aggregated just as 
-reward is accumulated in an MDP.\footnote{Generally, reward for an MDP is accumulated according to a 
-``discount factor'' $\gamma \leq 1$, such that if $r_i$ is the reward at time $i$, the total reward is $\sum_{i=0}^{\infty}\gamma^i r_i$.} 
-It leaves open the question of what the reward function is and thus 
-leaves the theory of the good, arguably the defining trait of consequentialism, 
-undefined. Similarly, Anderson and Anderson's proposal of a hedonistic act 
-utilitarian automated reasoner chooses hedonism\footnote{Recall that hedonism views pleasure as good
-and pain as bad.} as the theory of the good \citep[2]{util2}. Their proposal assumes that pleasure and pain can be 
+reward is accumulated in an MDP, according to a weighted sum, with future consequences weighted less
+than immediate ones. It leaves open the question of what the reward function is and thus doesn't 
+specify a theory of the good, arguably the defining trait of consequentialism. Anderson and Anderson
+face similar issues with their hedonistic\footnote{Recall that hedonism views pleasure as good
+and pain as bad.} act-utilitarian automated reasoner, which chooses hedonism as the theory of the good \citep[2]{util2}. 
+Their proposal assumes that pleasure and pain can be 
 given numeric values and that these values can be aggregated with a simple sum, taking an implicit
 stance on the aggregation question. Other attempts to automate consequentialist ethics will suffer 
-similar problems because, at some point, a usable automated consequentialist moral agent will need 
-to resolve the above debates.%
+similar problems because, at some point, a usable automated consequentialist moral agent must
+resolve the above debates.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 about the formal nature of moral character.
-Formalizing the concept of character appears to require significant philosophical and computational
+Formalizing the concept of character appears to require significant philosophical
 progress, whereas Kantian ethics immediately presents a formal rule to implement.%
@@
 our actions are guided by practical reason. We have reasons for acting, even when these reasons are
-opaque to us. This reflective choosing, or operation of practical reason, is what Kant calls the will.
+opaque to us. This reflective choosing, or operation of practical reason, is what Kant calls the \emph{will}.
 
@@
 Our wills are autonomous, so the only thing that can have unconditional authority over a rational will is 
-the will itself. No one else can tell you what to do because you can always ask why you 
+the will itself. No one else can unconditionally command you because you can always ask why you 
 should obey their authority. The only authority that you cannot question is the authority of your own 
@@
 example, all reasoners have equal access to the arithmetic logic that shows that ``2+2=4'' \cite[29]{velleman}. The 
-reasoning that makes this statement true is not specific to any person, but is universal across people. 
-Therefore, if I have sufficient reason to will a maxim, so does every other rational agent. There is 
-nothing special about the operation of my practical reason. 
-In adopting a maxim, I implicitly state that all reasoners
-across time also have reason to adopt that maxim. Therefore, because I act on reasons, I must obey the 
-FUL. Notice that this fulfills the above criterion for a categorical imperative: the FUL is derived from 
-a property of practical reason itself and thus derives authority from the will's authority over itself.%
+reasoning that makes this statement true is not specific to any person, but is universal across 
+people. Therefore, if I have sufficient reason to will a maxim, so does every other rational agent. There 
+is nothing special about the operation of my practical reason. In adopting a maxim, I implicitly state 
+that all reasoners across time also have reason to adopt that maxim. Therefore, because I act on 
+reasons, I must obey the FUL. Notice that this fulfills the above criterion for a categorical 
+imperative: the FUL is derived from a property of practical reason itself and thus derives authority 
+from the will's authority over itself.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-Kantian ethics is an especially attractive candidate for formalization because the categorical imperative, particularly the FUL, 
+Kantian ethics is an attractive candidate for formalization because the categorical imperative, particularly the FUL, 
 is a property of reason related to the form or structure of a maxim. It does not require any situational 
@@
 This distinguishes Kantian ethics from consequentialism and virtue ethics, which
-require far more knowledge about the world or the agent to reach a moral decision.
+require far more knowledge to reach a moral decision.
 
@@
 represented simply as a tuple of circumstances, act, and goal.
-This representation is simple and efficient, especially when compared to representations of a causal 
+This representation is efficient, especially when compared to representations of a causal 
 chain or a state of affairs or moral character. This property not only reduces the computational complexity
@@
 \begin{isamarkuptext}%
-One challenge for automating Kantian ethics is the need for ``common-sense'', or factual and 
-situational background. Common-sense is needed when formulating a maxim and determining if a maxim 
+One challenge for automating Kantian ethics is the need for ``common sense'', or factual and 
+situational background. Common sense is needed when formulating a maxim and determining if a maxim 
 violates the Formula of Universal Law. Maxims include the circumstances in which they apply and
-determining which circumstances are ``morally relevant'' to a maxim requires factual background. 
+determining which circumstances are morally relevant to a maxim requires factual background. 
 My system does not need to answer this question because I assume a properly crafted
 maxim as input and apply the categorical imperative to this input. Using my system to build a fully automated
-moral agent will require answering this question, a challenging computational and philosophical task. I
+moral agent will eventually require answering this question, a challenging computational and philosophical task. I
 discuss this problem in greater detail in Section \ref{whatisamaxim} and Section \ref{AIethics}.
@@
 automation. Korsgaard characterizes the three formulations of the categorical
-imperative according to Rawls' general and special conception of justice. The general conception applies
+imperative according to Rawls' general and special conception of justice \cite{theoryofjustice}. The general conception applies
 universally and can never be violated, while the special conception represents an ideal for us to
@@
 \begin{isamarkuptext}%
-I formalize Kantian ethics by representing it as an axiom on top of a base logic. In this section, 
-I present the logical background necessary to understand my work and my choice of Dyadic Deontic Logic (DDL).
+I formalize Kantian ethics by representing the Formula of Universal Law as an axiom on top of a base
+logic. In this section, I present the logical background necessary to understand my work and my 
+choice of Dyadic Deontic Logic (DDL).
 
@@
 and it represents the concept of necessary truth \citep{cresswell}. 
-These logics usually also contain the possibility operator $\diamond$, where
- $\diamond p \iff \sim \Box \sim p$. $\diamond p$ means that the statement $p$ is possibly true, or true
-at at least one of $w$'s neighbors. 
+These logics usually also contain the possibility operator $\diamond$, where $\diamond p \iff \sim \Box \sim p$. 
+$\diamond p$ means that the statement $p$ is possibly true, or true at at least one of $w$'s neighbors. 
 Additionally, modal logics include standard operators of propositional logic like $\sim, \wedge, \vee, \rightarrow$.
@@
 
-I use as my base logic Carmo and Jones's Dyadic Deontic Logic (DDL), which improves on SDL \citep{CJDDL}. 
+I use Carmo and Jones's Dyadic Deontic Logic (DDL), which improves on SDL \citep{CJDDL}. 
 It introduces a dyadic obligation operator $O\{A \vert B\}$ 
@@
 gracefully handle contrary-to-duty conditionals, since violations of duty simply modify the context. The obligation operator uses 
-a neighborhood semantics, instead of the Kripke semantics \citep{neighborhood1, neighborhood2}. While Kripke
+the neighborhood semantics, instead of the Kripke semantics \citep{neighborhood1, neighborhood2}. While Kripke
 semantics requires that an obligated proposition hold at all worlds, the neighborhood semantics defines
-a different set of neighbors, or morally relevant alternatives, for each world. To represent this,
+a set of neighbors, or morally relevant alternatives, for each world. To represent this,
 Carmo and Jones define a function $ob$ that maps a given context (or world) to the propositions 
 that are obligatory at this world, where a proposition $p$ is defined as 
-the worlds at which the $p$ is true. DDL is thus both modal and deontic; statements about obligations are
-true or false at a world according to the neighbordhood 
-semantics, and different obligations may hold at different worlds. This property is particularly relevant to my work because the universalizability test
+the set of worlds at which the $p$ is true. DDL is thus both modal and deontic; statements about obligations are
+true or false at a world according to the neighborhood 
+semantics, and different obligations may hold at different worlds. For example, the 
+sentence $O \{ \text{steal} \vert \text{when rich}\}$ is true at a world if stealing when rich is 
+obligated at that particular world. This property is particularly relevant to my work because the universalizability test
 requires reasoning about alternative worlds, such as the world of the universalized maxim.
@@
 These notions are accompanied by the corresponding modal operators $\Box_a, \diamond_a, \Box_p, \diamond_p$. 
-These operators use a Kripke semantics, with the functions $av$ and $pv$ mapping a world $w$ to the set 
+These operators use a modified Kripke semantics, with the functions $av$ and $pv$ mapping a world $w$ to the set 
 of corresponding actual or possible versions of $w$. These operators are not relevant to the work in 
 this thesis, but this additional expressivity could be used to extend my project to incorporate 
-more sophisticated ethical concepts like counterfactuals.
+more sophisticated ethical concepts.
 
@@
 \begin{isamarkuptext}%
-The final component of my project is the automated theorem prover I use to automate my formalization.
+The final component of my project is the automated theorem prover that I use to automate my formalization.
 Isabelle/HOL is an interactive proof assistant built on Haskell and Scala \citep{isabelle}. It 
 allows the user to define types, functions, definitions, and axiom systems. It has built-in support for both
-automatic and interactive/manual theorem proving. To demonstrate the power and usage of Isabelle and 
+automatic and interactive/manual theorem proving. To demonstrate the usage of Isabelle and 
 make DDL more precise, I walk through Benzmueller, Farjami, and Parent's implementation of DDL in Isabelle/HOL, 
@@
 The axiomatization above defines the semantics of DDL and, as demonstrated by the example axiom,
-is unwieldly. In my work, I mostly perform syntactic proofs, so I must define the syntax of the logic.
-Isabelle already knows the semantics of the axioms of this logic, so I can define the syntax as abbreviations 
+is unwieldly. In my work, I mostly perform syntactic proofs, so I need the syntax of the logic.
+Isabelle already knows the semantics of the axioms of this logic, so Benzm\"uller et. al define the syntax as abbreviations 
 involving the axioms above. Each DDL operator is represented
@@
 whenever they are applied. While the shallow embedding is performant (because it uses Isabelle's original 
-syntax tree), my heavy use of abbreviations may impact the performance of long proofs.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-\noindent Modal operators, implemented below, will be useful for my purposes.%
+syntax tree), the heavy use of abbreviations may impact the performance of long proofs.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+\noindent Modal operators, implemented below, will be particularly useful for my purposes.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupcmt{Notice that the necessity operator is an abbreviation, or syntactic sugar for, the higher order
+\isamarkupcmt{The necessity operator is an abbreviation, or syntactic sugar for, the higher order
 logic formula that the proposition holds at all worlds.%
@@
 \begin{isamarkuptext}%
-Benemueller, Farjami, and Parent provide a proof of the completeness of the above embedding \citep{BFP}.
-Isabelle allows us to check consistency immediately using Nitpick, a model checker \citep{nitpick}.
+Benzm\"uller, Farjami, and Parent provide a proof of the completeness and consistency of the above embedding \citep{BFP}.
+The proof of completeness is too long to present here, but Isabelle allows us to check consistency 
+immediately using Nitpick, a model checker \citep{nitpick}.
 Nitpick can find satisfying models for a particular lemma using the \texttt{satisfy} option and it can 
@@
 %
-\isamarkupcmt{This an example of a typical Nitpick output. In this case, Nitpick successfully found a model 
+\isamarkupcmt{The blue texte below is an example of typical Nitpick output. In this case, Nitpick successfully found a model 
 satisfying these axioms so the system is consistent.%
@@
 %:%46=18%:%
-%:%47=19%:%
-%:%56=21%:%
+%:%55=20%:%
+%:%67=23%:%
 %:%68=24%:%
@@
 %:%94=50%:%
-%:%95=51%:%
-%:%104=54%:%
+%:%103=53%:%
+%:%115=55%:%
 %:%116=56%:%
@@
 %:%123=63%:%
-%:%124=64%:%
-%:%128=66%:%
+%:%127=65%:%
+%:%131=67%:%
 %:%132=68%:%
@@
 %:%155=91%:%
-%:%156=92%:%
-%:%160=95%:%
+%:%159=94%:%
+%:%163=96%:%
 %:%164=97%:%
@@
 %:%179=112%:%
-%:%180=113%:%
-%:%184=115%:%
+%:%183=114%:%
+%:%187=116%:%
 %:%188=117%:%
@@
 %:%203=132%:%
-%:%204=133%:%
-%:%208=136%:%
+%:%207=135%:%
+%:%211=138%:%
 %:%212=139%:%
@@
 %:%225=152%:%
-%:%226=153%:%
-%:%227=154%:%
-%:%236=157%:%
+%:%234=155%:%
+%:%246=157%:%
+%:%247=158%:%
 %:%248=159%:%
@@
 %:%262=173%:%
-%:%263=174%:%
-%:%264=175%:%
-%:%268=177%:%
+%:%266=175%:%
+%:%270=177%:%
+%:%271=178%:%
 %:%272=179%:%
@@
 %:%295=202%:%
-%:%296=203%:%
-%:%297=204%:%
-%:%306=207%:%
+%:%304=205%:%
+%:%316=207%:%
+%:%317=208%:%
 %:%318=209%:%
@@
 %:%372=263%:%
-%:%373=264%:%
-%:%374=265%:%
-%:%378=268%:%
+%:%376=266%:%
+%:%380=268%:%
+%:%381=269%:%
 %:%382=270%:%
@@
 %:%399=287%:%
-%:%400=288%:%
-%:%401=289%:%
-%:%405=292%:%
+%:%403=290%:%
+%:%407=292%:%
+%:%408=293%:%
 %:%409=294%:%
@@
 %:%434=319%:%
-%:%435=320%:%
-%:%436=321%:%
-%:%445=323%:%
+%:%443=321%:%
+%:%455=323%:%
+%:%456=324%:%
 %:%457=325%:%
@@
 %:%502=370%:%
-%:%503=371%:%
-%:%504=372%:%
-%:%513=374%:%
-%:%525=376%:%
-%:%526=377%:%
-%:%527=378%:%
-%:%528=379%:%
-%:%529=380%:%
-%:%530=381%:%
-%:%531=382%:%
-%:%532=383%:%
-%:%533=384%:%
-%:%534=385%:%
-%:%535=386%:%
-%:%536=387%:%
-%:%537=388%:%
-%:%538=389%:%
-%:%539=390%:%
-%:%540=391%:%
-%:%541=392%:%
-%:%542=393%:%
-%:%543=394%:%
-%:%544=395%:%
-%:%545=396%:%
-%:%546=397%:%
-%:%547=398%:%
-%:%548=399%:%
-%:%549=400%:%
-%:%550=401%:%
-%:%551=402%:%
-%:%552=403%:%
-%:%553=404%:%
-%:%554=405%:%
-%:%555=406%:%
-%:%556=407%:%
-%:%557=408%:%
-%:%558=409%:%
-%:%559=410%:%
-%:%560=411%:%
-%:%561=412%:%
-%:%562=413%:%
-%:%563=414%:%
-%:%564=415%:%
-%:%565=416%:%
-%:%566=417%:%
-%:%567=418%:%
-%:%568=419%:%
-%:%569=420%:%
-%:%570=421%:%
-%:%571=422%:%
-%:%572=423%:%
-%:%573=424%:%
-%:%574=425%:%
-%:%575=426%:%
-%:%576=427%:%
-%:%577=428%:%
-%:%578=429%:%
-%:%579=430%:%
-%:%580=431%:%
-%:%581=432%:%
-%:%582=433%:%
-%:%583=434%:%
-%:%584=435%:%
-%:%593=438%:%
-%:%605=440%:%
-%:%606=441%:%
-%:%607=442%:%
-%:%608=443%:%
-%:%609=444%:%
-%:%610=445%:%
-%:%619=448%:%
-%:%631=450%:%
-%:%632=451%:%
-%:%633=452%:%
-%:%635=454%:%
-%:%636=454%:%
-%:%637=454%:%
-%:%638=454%:%
-%:%640=455%:%
-%:%641=455%:%
-%:%642=456%:%
-%:%643=456%:%
-%:%644=456%:%
-%:%645=456%:%
-%:%647=457%:%
-%:%648=458%:%
-%:%651=470%:%
-%:%652=471%:%
-%:%653=472%:%
-%:%655=474%:%
-%:%656=474%:%
-%:%657=474%:%
-%:%658=474%:%
-%:%659=475%:%
-%:%660=475%:%
-%:%663=477%:%
-%:%664=478%:%
-%:%665=479%:%
-%:%666=480%:%
-%:%668=482%:%
-%:%669=482%:%
-%:%670=506%:%
-%:%671=507%:%
-%:%673=508%:%
-%:%674=509%:%
-%:%675=510%:%
-%:%676=511%:%
-%:%684=516%:%
-%:%696=518%:%
-%:%697=519%:%
-%:%698=520%:%
-%:%699=521%:%
-%:%700=522%:%
-%:%701=523%:%
-%:%702=524%:%
-%:%706=538%:%
-%:%708=539%:%
-%:%709=539%:%
-%:%710=540%:%
-%:%712=541%:%
-%:%713=542%:%
-%:%714=542%:%
-%:%715=543%:%
-%:%716=543%:%
-%:%717=544%:%
-%:%719=545%:%
-%:%722=546%:%
-%:%724=547%:%
-%:%725=547%:%
-%:%726=548%:%
-%:%728=549%:%
-%:%731=566%:%
-%:%732=567%:%
-%:%734=568%:%
-%:%735=568%:%
-%:%736=569%:%
-%:%737=570%:%
-%:%738=570%:%
-%:%739=571%:%
-%:%740=572%:%
-%:%741=572%:%
-%:%742=573%:%
-%:%744=574%:%
-%:%745=575%:%
-%:%748=576%:%
-%:%750=577%:%
-%:%751=577%:%
-%:%752=578%:%
-%:%754=579%:%
-%:%757=584%:%
-%:%758=585%:%
-%:%759=586%:%
-%:%760=587%:%
-%:%762=590%:%
-%:%763=590%:%
-%:%764=590%:%
-%:%766=590%:%
-%:%770=590%:%
-%:%771=590%:%
-%:%773=591%:%
-%:%774=592%:%
-%:%775=592%:%
-%:%777=593%:%
-%:%778=594%:%
-%:%779=595%:%
-%:%789=597%:%
-%:%790=598%:%
-%:%791=599%:%
+%:%511=372%:%
+%:%523=375%:%
+%:%524=376%:%
+%:%525=377%:%
+%:%526=378%:%
+%:%527=379%:%
+%:%528=380%:%
+%:%529=381%:%
+%:%530=382%:%
+%:%531=383%:%
+%:%532=384%:%
+%:%533=385%:%
+%:%534=386%:%
+%:%535=387%:%
+%:%536=388%:%
+%:%537=389%:%
+%:%538=390%:%
+%:%539=391%:%
+%:%540=392%:%
+%:%541=393%:%
+%:%542=394%:%
+%:%543=395%:%
+%:%544=396%:%
+%:%545=397%:%
+%:%546=398%:%
+%:%547=399%:%
+%:%548=400%:%
+%:%549=401%:%
+%:%550=402%:%
+%:%551=403%:%
+%:%552=404%:%
+%:%553=405%:%
+%:%554=406%:%
+%:%555=407%:%
+%:%556=408%:%
+%:%557=409%:%
+%:%558=410%:%
+%:%559=411%:%
+%:%560=412%:%
+%:%561=413%:%
+%:%562=414%:%
+%:%563=415%:%
+%:%564=416%:%
+%:%565=417%:%
+%:%566=418%:%
+%:%567=419%:%
+%:%568=420%:%
+%:%569=421%:%
+%:%570=422%:%
+%:%571=423%:%
+%:%572=424%:%
+%:%573=425%:%
+%:%574=426%:%
+%:%575=427%:%
+%:%576=428%:%
+%:%577=429%:%
+%:%578=430%:%
+%:%579=431%:%
+%:%580=432%:%
+%:%581=433%:%
+%:%582=434%:%
+%:%583=435%:%
+%:%584=436%:%
+%:%593=439%:%
+%:%605=441%:%
+%:%606=442%:%
+%:%607=443%:%
+%:%608=444%:%
+%:%609=445%:%
+%:%610=446%:%
+%:%619=449%:%
+%:%631=451%:%
+%:%632=452%:%
+%:%633=453%:%
+%:%635=455%:%
+%:%636=455%:%
+%:%637=455%:%
+%:%638=455%:%
+%:%640=456%:%
+%:%641=456%:%
+%:%642=457%:%
+%:%643=457%:%
+%:%644=457%:%
+%:%645=457%:%
+%:%647=458%:%
+%:%648=459%:%
+%:%651=471%:%
+%:%652=472%:%
+%:%653=473%:%
+%:%655=475%:%
+%:%656=475%:%
+%:%657=475%:%
+%:%658=475%:%
+%:%659=476%:%
+%:%660=476%:%
+%:%663=478%:%
+%:%664=479%:%
+%:%665=480%:%
+%:%666=481%:%
+%:%668=483%:%
+%:%669=483%:%
+%:%670=507%:%
+%:%671=508%:%
+%:%673=509%:%
+%:%674=510%:%
+%:%675=511%:%
+%:%676=512%:%
+%:%684=517%:%
+%:%696=519%:%
+%:%697=520%:%
+%:%698=521%:%
+%:%699=522%:%
+%:%700=523%:%
+%:%701=524%:%
+%:%702=525%:%
+%:%706=539%:%
+%:%708=540%:%
+%:%709=540%:%
+%:%710=541%:%
+%:%712=542%:%
+%:%713=543%:%
+%:%714=543%:%
+%:%715=544%:%
+%:%716=544%:%
+%:%717=545%:%
+%:%719=546%:%
+%:%722=547%:%
+%:%724=548%:%
+%:%725=548%:%
+%:%726=549%:%
+%:%728=550%:%
+%:%731=567%:%
+%:%732=568%:%
+%:%734=569%:%
+%:%735=569%:%
+%:%736=570%:%
+%:%737=571%:%
+%:%738=571%:%
+%:%739=572%:%
+%:%740=573%:%
+%:%741=573%:%
+%:%742=574%:%
+%:%744=575%:%
+%:%745=576%:%
+%:%748=577%:%
+%:%750=578%:%
+%:%751=578%:%
+%:%752=579%:%
+%:%754=580%:%
+%:%757=585%:%
+%:%758=586%:%
+%:%759=587%:%
+%:%760=588%:%
+%:%761=589%:%
+%:%763=592%:%
+%:%764=592%:%
+%:%765=592%:%
+%:%767=592%:%
+%:%771=592%:%
+%:%772=592%:%
+%:%774=593%:%
+%:%775=594%:%
+%:%776=594%:%
+%:%778=595%:%
+%:%779=596%:%
+%:%780=597%:%
+%:%790=599%:%
+%:%791=600%:%
+%:%792=601%:%

### 2022-03-21 paper/output/document/thesis_3_implementation.tex
spring breaking
dhoom again

@@
 In this section, I present the details of my implementation of automated Kantian ethics, which consists of
-a formalization of the FUL in Dyadic Deontic Logic and an implementation of this logic in Isabelle/HOL. The final
-Isabelle library is a logic that has the categorical imperative as an axiom and can express and derive moral judgements. 
+a formalization of the Formula of Universal Law in Dyadic Deontic Logic and an implementation of this logic in Isabelle/HOL. The final
+Isabelle library contains a logic that has the categorical imperative as an axiom and can express and derive moral judgements. 
 Using Isabelle's automated theorem proving abilities, my system can show that appropriately represented
-actions are obligatory, permissible, or prohibited by proving or refuting sentences of the form ``A 
+maxims are obligatory, permissible, or prohibited by proving or refuting sentences of the form ``A 
 is obligated to do B.'' I also present a testing framework to evaluate how faithful my implementation is 
@@
 begin to formalize a specific formulation of the categorical imperative, I must define
-subjects and actions. I add representations of subjects and actions so that my new logic can express
-sentences of the form, ``x does action.''%
+subjects and act. I add representations of subjects and acts so that my new logic can express
+sentences of the form, ``x does act.''%
 \end{isamarkuptext}\isamarkuptrue%
@@
 I represent that below by allowing subjects to substitute into sentences, a property that I will use 
-to represent the idea that different people can perform the same actions.%
+to represent the idea that different people can perform the same acts.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 the DDL term ``Sara runs,'' which can be true or false at a world. An open sentence itself is not truth-apt,
-ot the kind of thing that can be true or false at a world. When an action is 
+ot the kind of thing that can be true or false at a world. When a subject is 
 substituted into an open sentence, the resulting term is truth apt. ``Runs'' is not the kind of thing 
@@
 acting or goal \citep{actingonprinciple}. Other potential views include Korsgaard's view, which omits 
-the circumstances, and Kitcher's view, which adds a motivation \citep{actingforareason, kitcher}. I 
+the circumstances, and Kitcher's view, which additionally includes the actor's motivation \citep{actingforareason, kitcher}. I 
 address the limitations of these approaches in Appendix \ref{maximmotive}.
@@
 can be true or false at a world. For example, the circumstance ``when I am strapped for cash'' is true at the real 
-world when my bank account is empty. The second term represents the action, which is an open sentence
-because different agents can perform a particular action. For example, the action, ``will falsely promise
+world when my bank account is empty. The second term represents the act, which is an open sentence
+because different agents can perform a particular action. For example, the act, ``will falsely promise
 to repay a loan'' is an open sentence that can be acted on by a subject. The third term represents 
@@
 of the infinitely many circumstances in which the agent may perform an action \citep[4:428]{actingonprinciple}. She argues that this is 
-an artifact of the fact that maxims are rules of practical reason, the kind of reason that helps us decide what to do 
+an artifact of the fact that maxims are rules of practical reason, which is the kind of reason that helps us decide what to do 
 and how to do it \citep{bok}. Like any practical rule, 
@@
 itself, is what determines the morally relevant circumstances.  
-The difficulty in determining relevant circumstances is a limitation of my system and requires that a 
+The difficulty in determining relevant circumstances is an obstacle to using my system in practice and requires that a 
 human being formulate the maxim or that future work develop heuristics to classify circumstances as morally 
@@
 With this robust representation of a maxim, I can now define willing. To will a maxim is to adopt it 
-as a principle to live by, or to commit oneself to the maxim's action for the 
+as a principle to live by, or to commit oneself to the maxim's act for the 
 sake of maxim's end in the relevant circumstances. I formalize this idea in Definition \ref{willing}.
@@
 In order to evaluate the moral status of a maxim, I must define what it means for a maxim to not be
-universalizable, or to fail the universalizability test. Kantians debate the correct interpretation of 
-the Formula of Universal Law because Kant himself appears to interpret the criterion in different ways. 
+universalizable, or to fail the universalizability test. For many years, Kantians debated the correct interpretation of 
+the Formula of Universal Law because Kant himself appeared to interpret the criterion in different ways. 
 I adopt Korsgaard's practical contradiction interpretation, broadly accepted as correct within 
@@
 \citet{dietrichson} to construct the example natural act of a mother killing her children that
-cry too much at night so that she can get some sleep. Universalizing this maxim does not generate a logical 
-contradiction because killing is still possible in a world where everyone kills noisy children, but 
-it is clearly wrong. Because killing is a natural act, it can never be logically 
+cry too much at night so that she can get some sleep. Thought this maxim is clearly wrong, universalizing 
+it does not generate a logical contradiction because killing is still possible in a world where 
+everyone kills noisy children. Because killing is a natural act, it can never be logically 
 impossible so the logical contradiction view cannot prohibit it.
@@
 The practical contradiction interpretation offers a satisfying explanation of \emph{why} certain 
-maxims are immoral. These maxims involve parasitic behavior on social conditions that the agent seeks 
+maxims are immoral. These maxims involve parasitic behavior on the very social conditions that the agent seeks 
 to benefit from. The false promiser wants to both abuse the system of promising and benefit 
@@
 
-I can once again represent this as an abbreviation in Isabelle.%
+\noindent I can once again represent this as an abbreviation in Isabelle.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \end{definition}
-\noindent A maxim is not universalizable when, if everyone wills the maxim, then it is no longer effective.
-I implement this definition in Isabelle using another abbreviaion.%
+\noindent A maxim is not universalizable when, if everyone wills the maxim, then it is no longer 
+effective. I implement this definition in Isabelle using another abbreviaion.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-The FUL states that if a maxim is not universalizable, then it is prohibited. Before performing
-moral reasoning with my system, I must define obligation, permissibility, and prohibition.
-To judge an action, my system evaluates the moral status of the action 
+The FUL states that if a maxim is not universalizable, then it is prohibited. To define and use 
+this statement, I must first define obligation, permissibility, and prohibition.
+To judge a maxim, my system evaluates the moral status of the sentence 
 ``person $s$ wills maxim $M$.'' This action can be obligated, prohibited, or permissible.
@@
 intuition for the meaning of prohibition, but the exact definition is given by 
-$O\{ \neg will \, (C, A, G) \, s \, | \, C\}$.}
+$O\{ \neg \text{will} \, (C, A, G) \, s \, | \, C\}$.}
 \newcommand*{\approxident}{%
@@
 \isamarkupcmt{This lemma shows that if there is some maxim $A$ such that $A$ and $\neg A$ are both obligatory (which
-is the formal statement of contradictory obligations), then obligation does not always permissibility.%
+is the formal statement of contradictory obligations), then obligation does not always imply permissibility.%
 }\isanewline

### 2022-03-21 paper/output/document/thesis_5_discussion.tex
dhoom again

@@
 While this view has intuitive appeal, it raises the question of how we can determine
-which circumstances are morally relevant. O'Neill answers this question by noting that the Formula of Universal Law is 
+which circumstances are morally relevant. In Section \ref{whatisamaxim}, I presented O'Neill's argument for why
+determining morally relevant circumstances requires practical judgement, which is a kind of practical
+reason. O'Neill characterizes practical judgement and answers this question more specifically
+by noting that the Formula of Universal Law is
 a ``test of moral worth rather than of outward rightness'' \citep[98]{constofreason}. The FUL is a way 
@@
 %:%198=153%:%
-%:%207=155%:%
-%:%219=157%:%
-%:%220=158%:%
-%:%221=159%:%
+%:%199=154%:%
+%:%200=155%:%
+%:%201=156%:%
+%:%210=158%:%
 %:%222=160%:%
@@
 %:%229=167%:%
-%:%238=169%:%
-%:%250=171%:%
-%:%251=172%:%
-%:%252=173%:%
+%:%230=168%:%
+%:%231=169%:%
+%:%232=170%:%
+%:%241=172%:%
 %:%253=174%:%
@@
 %:%443=364%:%
-%:%452=367%:%
-%:%464=369%:%
-%:%465=370%:%
-%:%466=371%:%
+%:%444=365%:%
+%:%445=366%:%
+%:%446=367%:%
+%:%455=370%:%
 %:%467=372%:%
@@
 %:%529=434%:%
-%:%538=436%:%
-%:%550=438%:%
-%:%551=439%:%
-%:%552=440%:%
+%:%530=435%:%
+%:%531=436%:%
+%:%532=437%:%
+%:%541=439%:%
 %:%553=441%:%
@@
 %:%626=514%:%
-%:%635=517%:%
-%:%647=520%:%
-%:%648=521%:%
-%:%649=522%:%
+%:%627=515%:%
+%:%628=516%:%
+%:%629=517%:%
+%:%638=520%:%
 %:%650=523%:%
@@
 %:%766=639%:%
-%:%769=641%:%
-%:%770=642%:%
-%:%771=643%:%
+%:%767=640%:%
+%:%768=641%:%
+%:%769=642%:%
 %:%772=644%:%
@@
 %:%774=646%:%
-%:%777=647%:%
-%:%778=648%:%
-%:%779=649%:%
+%:%775=647%:%
+%:%776=648%:%
+%:%777=649%:%
 %:%780=650%:%
@@
 %:%792=662%:%
-%:%801=666%:%
-%:%813=668%:%
-%:%814=669%:%
-%:%815=670%:%
+%:%793=663%:%
+%:%794=664%:%
+%:%795=665%:%
+%:%804=669%:%
 %:%816=671%:%
@@
 %:%864=719%:%
-%:%873=721%:%
-%:%885=723%:%
-%:%886=724%:%
-%:%887=725%:%
+%:%865=720%:%
+%:%866=721%:%
+%:%867=722%:%
+%:%876=724%:%
 %:%888=726%:%
@@
 %:%923=761%:%
+%:%924=762%:%
+%:%925=763%:%
+%:%926=764%:%

### 2022-03-22 paper/output/document/appendix.tex
finished another read thrgh

@@
 %
+\endisatagdocument
+{\isafolddocument}%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\begin{isamarkuptext}%
+In Section \ref{whatisamaxim}, I explain and justify O'Neill's definition of a maxim as a circumstance,
+act, goal triple. In this appendix, I explore two alternate definitions of maxim: Korsgaard's definition, 
+which is weaker than O'Neill's, and Kitcher's definition, which is stronger than O'Neill's. I argue that 
+O'Neill's definition offers the right amount of strength for my project.%
+\end{isamarkuptext}\isamarkuptrue%
+%
+\isadelimdocument
+%
+\endisadelimdocument
+%
+\isatagdocument
+%
 \isamarkupsubsection{Korsgaard's Act-Goal View%
@@
 \begin{isamarkuptext}%
-I adopt O'Niell's definition of a maxim, which builds on Korsgaard's weaker interpretation of 
-a maxim as an act, goal pair. She interprets Kant's example meanings as having the form ``to-do-this-act-for-
+I adopt O'Neill's definition of a maxim, which builds on Korsgaard's weaker interpretation of 
+a maxim as an act, goal pair. Korsgaard interprets Kant's example meanings as having the form ``to-do-this-act-for-
 the-sake-of-this-end,'' which could be formalized as a pair of an act and goal \citep{actingforareason}.
-For example, under this view, one example maxim might be, ``Falsely promise to repay a loan in order
+Under this view, one example maxim might be, ``Falsely promise to repay a loan in order
 to get some easy cash.''
 
-O'Niell's view only differs from this view in the inclusion of the circumstances
-on which the agent acts. This inclusion creates a representation of a maxim that is strictly more expressive than 
-Korsgaard's interpretation; every (circumstance, act, goal) tuple can be represented as an (act, goal) pair
-by simply dropping the circumstances, but the same (act, goal) pair could correspond to many different
-(circumstance, act, goal) tuples, all with varying moral statuses. Because my representation of a maxim
+O'Neill's view only differs from this view in the inclusion of the circumstances
+under which the agent acts. This inclusion creates a representation of a maxim that is strictly more expressive than 
+Korsgaard's interpretation; every circumstance, act, goal triple can be represented as an act, goal pair
+by simply dropping the circumstances, but the same act, goal pair could correspond to many different
+circumstance, act, goal triples, all with varying moral statuses. Because my representation of a maxim
 is more expressive than Korsgaard's, my results are stronger than those that would be achieved with 
@@
 and that the lender will expect their money back. At an even more granular level, this maxim implicitly includes
-a definition of a lender and of falsely promising, both of which are circumstantial. Given that all
-maxims necessarily include some circumstances, O'Niell's view makes these implicit circumstances
+a definition of a lender and of falsely promising, both of which are circumstantial. All
+maxims necessarily include some circumstances and  O'Neill's view makes these implicit circumstances
 explicit. This precision is a benefit; so long as my circumstances are not so finely grained that they
-are uninterpretable, they render O'Niell's maxims more precise than Korsgaard's maxims.%
+are uninterpretable, they render O'Neill's maxims more precise than Korsgaard's maxims.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupsubsection{Kitcher's View on Motives%
+\isamarkupsubsection{Kitcher's View Including Motives%
 }
@@
 \begin{isamarkuptext}%
-Kitcher begins with O'Niell's 
+Kitcher begins with O'Neill's 
 circumstance, act, goal view and expands it to include the motive for a maxim \citep{whatisamaxim}. 
@@
 %:%24=6%:%
-%:%28=8%:%
-%:%40=10%:%
-%:%41=11%:%
-%:%42=12%:%
-%:%43=13%:%
-%:%44=14%:%
-%:%45=15%:%
-%:%46=16%:%
-%:%47=17%:%
-%:%48=18%:%
-%:%49=19%:%
-%:%50=20%:%
-%:%51=21%:%
-%:%52=22%:%
-%:%53=23%:%
-%:%54=24%:%
-%:%55=25%:%
-%:%56=26%:%
-%:%57=27%:%
-%:%58=28%:%
-%:%59=29%:%
-%:%60=30%:%
-%:%61=31%:%
-%:%62=32%:%
-%:%71=35%:%
-%:%83=37%:%
-%:%84=38%:%
-%:%85=39%:%
-%:%86=40%:%
-%:%87=41%:%
-%:%88=42%:%
-%:%89=43%:%
-%:%90=44%:%
-%:%91=45%:%
-%:%92=46%:%
-%:%93=47%:%
-%:%94=48%:%
-%:%95=49%:%
-%:%96=50%:%
-%:%97=51%:%
-%:%98=52%:%
-%:%99=53%:%
-%:%100=54%:%
-%:%101=55%:%
-%:%102=56%:%
-%:%103=57%:%
-%:%104=58%:%
-%:%105=59%:%
-%:%106=60%:%
-%:%107=61%:%
-%:%108=62%:%
-%:%117=65%:%
-%:%129=67%:%
-%:%130=68%:%
-%:%131=69%:%
-%:%132=70%:%
-%:%133=71%:%
-%:%142=73%:%
-%:%154=75%:%
-%:%155=76%:%
-%:%156=77%:%
-%:%158=79%:%
-%:%159=79%:%
-%:%160=79%:%
-%:%163=81%:%
-%:%164=82%:%
-%:%165=83%:%
-%:%166=84%:%
-%:%167=85%:%
-%:%168=86%:%
-%:%170=88%:%
-%:%171=88%:%
-%:%173=89%:%
-%:%174=89%:%
-%:%176=90%:%
-%:%177=91%:%
-%:%180=93%:%
-%:%181=94%:%
-%:%182=95%:%
-%:%183=96%:%
-%:%185=98%:%
-%:%186=98%:%
-%:%187=99%:%
-%:%188=100%:%
-%:%189=100%:%
-%:%190=101%:%
-%:%191=102%:%
-%:%192=102%:%
-%:%193=103%:%
-%:%194=104%:%
-%:%195=104%:%
-%:%196=105%:%
-%:%198=107%:%
-%:%199=108%:%
-%:%200=109%:%
-%:%202=111%:%
-%:%203=111%:%
-%:%204=112%:%
-%:%205=113%:%
-%:%206=113%:%
-%:%207=114%:%
-%:%209=116%:%
-%:%213=118%:%
-%:%214=119%:%
-%:%215=120%:%
-%:%216=121%:%
-%:%217=122%:%
-%:%218=123%:%
-%:%219=124%:%
-%:%223=126%:%
-%:%224=127%:%
-%:%225=128%:%
-%:%226=129%:%
-%:%227=130%:%
-%:%228=131%:%
-%:%229=132%:%
-%:%231=134%:%
-%:%232=134%:%
-%:%233=135%:%
-%:%234=136%:%
-%:%235=137%:%
-%:%236=137%:%
-%:%238=137%:%
-%:%242=137%:%
-%:%243=137%:%
-%:%245=138%:%
-%:%246=139%:%
-%:%247=140%:%
-%:%248=141%:%
-%:%258=143%:%
-%:%259=144%:%
-%:%260=145%:%
-%:%261=146%:%
-%:%262=147%:%
-%:%263=148%:%
-%:%264=149%:%
-%:%265=150%:%
-%:%266=151%:%
-%:%267=152%:%
-%:%269=154%:%
-%:%270=154%:%
-%:%271=155%:%
-%:%272=156%:%
-%:%273=157%:%
-%:%274=157%:%
-%:%276=157%:%
-%:%280=157%:%
-%:%281=157%:%
-%:%283=158%:%
-%:%284=159%:%
-%:%285=160%:%
-%:%286=161%:%
-%:%296=163%:%
-%:%297=164%:%
-%:%298=165%:%
-%:%299=166%:%
-%:%300=167%:%
-%:%301=168%:%
-%:%302=169%:%
-%:%303=170%:%
-%:%304=171%:%
-%:%306=173%:%
-%:%307=173%:%
-%:%308=174%:%
-%:%309=175%:%
-%:%310=176%:%
-%:%311=176%:%
-%:%313=176%:%
-%:%317=176%:%
-%:%318=176%:%
-%:%320=177%:%
-%:%321=178%:%
-%:%322=179%:%
-%:%323=180%:%
-%:%333=182%:%
-%:%334=183%:%
-%:%351=208%:%
-%:%355=210%:%
-%:%356=211%:%
-%:%357=212%:%
-%:%358=213%:%
-%:%359=214%:%
-%:%361=217%:%
-%:%362=217%:%
-%:%364=218%:%
-%:%365=219%:%
-%:%366=220%:%
-%:%369=222%:%
-%:%370=223%:%
-%:%372=225%:%
-%:%373=225%:%
-%:%374=226%:%
-%:%375=227%:%
-%:%376=227%:%
-%:%378=227%:%
-%:%382=227%:%
-%:%383=227%:%
-%:%385=228%:%
-%:%386=229%:%
-%:%387=230%:%
-%:%388=231%:%
-%:%389=232%:%
-%:%390=233%:%
-%:%391=234%:%
-%:%392=235%:%
-%:%400=235%:%
-%:%401=236%:%
-%:%402=237%:%
-%:%403=237%:%
-%:%405=239%:%
-%:%406=240%:%
-%:%408=242%:%
-%:%409=242%:%
-%:%410=242%:%
-%:%412=242%:%
-%:%416=242%:%
-%:%417=242%:%
-%:%419=243%:%
-%:%420=244%:%
-%:%421=245%:%
-%:%422=246%:%
-%:%432=248%:%
-%:%433=249%:%
-%:%434=250%:%
-%:%435=251%:%
-%:%444=253%:%
-%:%456=255%:%
-%:%457=256%:%
-%:%458=257%:%
-%:%459=258%:%
-%:%460=259%:%
-%:%461=260%:%
-%:%462=261%:%
-%:%463=262%:%
-%:%464=263%:%
-%:%465=264%:%
-%:%466=265%:%
-%:%468=267%:%
-%:%469=267%:%
-%:%470=268%:%
-%:%471=269%:%
-%:%472=269%:%
-%:%474=269%:%
-%:%478=269%:%
-%:%488=271%:%
+%:%36=8%:%
+%:%37=9%:%
+%:%38=10%:%
+%:%39=11%:%
+%:%48=13%:%
+%:%60=15%:%
+%:%61=16%:%
+%:%62=17%:%
+%:%63=18%:%
+%:%64=19%:%
+%:%65=20%:%
+%:%66=21%:%
+%:%67=22%:%
+%:%68=23%:%
+%:%69=24%:%
+%:%70=25%:%
+%:%71=26%:%
+%:%72=27%:%
+%:%73=28%:%
+%:%74=29%:%
+%:%75=30%:%
+%:%76=31%:%
+%:%77=32%:%
+%:%78=33%:%
+%:%79=34%:%
+%:%80=35%:%
+%:%81=36%:%
+%:%82=37%:%
+%:%91=40%:%
+%:%103=42%:%
+%:%104=43%:%
+%:%105=44%:%
+%:%106=45%:%
+%:%107=46%:%
+%:%108=47%:%
+%:%109=48%:%
+%:%110=49%:%
+%:%111=50%:%
+%:%112=51%:%
+%:%113=52%:%
+%:%114=53%:%
+%:%115=54%:%
+%:%116=55%:%
+%:%117=56%:%
+%:%118=57%:%
+%:%119=58%:%
+%:%120=59%:%
+%:%121=60%:%
+%:%122=61%:%
+%:%123=62%:%
+%:%124=63%:%
+%:%125=64%:%
+%:%126=65%:%
+%:%127=66%:%
+%:%128=67%:%
+%:%137=70%:%
+%:%149=72%:%
+%:%150=73%:%
+%:%151=74%:%
+%:%152=75%:%
+%:%153=76%:%
+%:%162=78%:%
+%:%174=80%:%
+%:%175=81%:%
+%:%176=82%:%
+%:%178=84%:%
+%:%179=84%:%
+%:%180=84%:%
+%:%183=86%:%
+%:%184=87%:%
+%:%185=88%:%
+%:%186=89%:%
+%:%187=90%:%
+%:%188=91%:%
+%:%190=93%:%
+%:%191=93%:%
+%:%193=94%:%
+%:%194=94%:%
+%:%196=95%:%
+%:%197=96%:%
+%:%200=98%:%
+%:%201=99%:%
+%:%202=100%:%
+%:%203=101%:%
+%:%205=103%:%
+%:%206=103%:%
+%:%207=104%:%
+%:%208=105%:%
+%:%209=105%:%
+%:%210=106%:%
+%:%211=107%:%
+%:%212=107%:%
+%:%213=108%:%
+%:%214=109%:%
+%:%215=109%:%
+%:%216=110%:%
+%:%218=112%:%
+%:%219=113%:%
+%:%220=114%:%
+%:%222=116%:%
+%:%223=116%:%
+%:%224=117%:%
+%:%225=118%:%
+%:%226=118%:%
+%:%227=119%:%
+%:%229=121%:%
+%:%233=123%:%
+%:%234=124%:%
+%:%235=125%:%
+%:%236=126%:%
+%:%237=127%:%
+%:%238=128%:%
+%:%239=129%:%
+%:%243=131%:%
+%:%244=132%:%
+%:%245=133%:%
+%:%246=134%:%
+%:%247=135%:%
+%:%248=136%:%
+%:%249=137%:%
+%:%251=139%:%
+%:%252=139%:%
+%:%253=140%:%
+%:%254=141%:%
+%:%255=142%:%
+%:%256=142%:%
+%:%258=142%:%
+%:%262=142%:%
+%:%263=142%:%
+%:%265=143%:%
+%:%266=144%:%
+%:%267=145%:%
+%:%268=146%:%
+%:%278=148%:%
+%:%279=149%:%
+%:%280=150%:%
+%:%281=151%:%
+%:%282=152%:%
+%:%283=153%:%
+%:%284=154%:%
+%:%285=155%:%
+%:%286=156%:%
+%:%287=157%:%
+%:%289=159%:%
+%:%290=159%:%
+%:%291=160%:%
+%:%292=161%:%
+%:%293=162%:%
+%:%294=162%:%
+%:%296=162%:%
+%:%300=162%:%
+%:%301=162%:%
+%:%303=163%:%
+%:%304=164%:%
+%:%305=165%:%
+%:%306=166%:%
+%:%316=168%:%
+%:%317=169%:%
+%:%318=170%:%
+%:%319=171%:%
+%:%320=172%:%
+%:%321=173%:%
+%:%322=174%:%
+%:%323=175%:%
+%:%324=176%:%
+%:%326=178%:%
+%:%327=178%:%
+%:%328=179%:%
+%:%329=180%:%
+%:%330=181%:%
+%:%331=181%:%
+%:%333=181%:%
+%:%337=181%:%
+%:%338=181%:%
+%:%340=182%:%
+%:%341=183%:%
+%:%342=184%:%
+%:%343=185%:%
+%:%353=187%:%
+%:%354=188%:%
+%:%371=213%:%
+%:%375=215%:%
+%:%376=216%:%
+%:%377=217%:%
+%:%378=218%:%
+%:%379=219%:%
+%:%381=222%:%
+%:%382=222%:%
+%:%384=223%:%
+%:%385=224%:%
+%:%386=225%:%
+%:%389=227%:%
+%:%390=228%:%
+%:%392=230%:%
+%:%393=230%:%
+%:%394=231%:%
+%:%395=232%:%
+%:%396=232%:%
+%:%398=232%:%
+%:%402=232%:%
+%:%403=232%:%
+%:%405=233%:%
+%:%406=234%:%
+%:%407=235%:%
+%:%408=236%:%
+%:%409=237%:%
+%:%410=238%:%
+%:%411=239%:%
+%:%412=240%:%
+%:%420=240%:%
+%:%421=241%:%
+%:%422=242%:%
+%:%423=242%:%
+%:%425=244%:%
+%:%426=245%:%
+%:%428=247%:%
+%:%429=247%:%
+%:%430=247%:%
+%:%432=247%:%
+%:%436=247%:%
+%:%437=247%:%
+%:%439=248%:%
+%:%440=249%:%
+%:%441=250%:%
+%:%442=251%:%
+%:%452=253%:%
+%:%453=254%:%
+%:%454=255%:%
+%:%455=256%:%
+%:%464=258%:%
+%:%476=260%:%
+%:%477=261%:%
+%:%478=262%:%
+%:%479=263%:%
+%:%480=264%:%
+%:%481=265%:%
+%:%482=266%:%
+%:%483=267%:%
+%:%484=268%:%
+%:%485=269%:%
+%:%486=270%:%
+%:%488=272%:%
 %:%489=272%:%
 %:%490=273%:%
-%:%492=275%:%
-%:%493=275%:%
-%:%494=276%:%
-%:%495=277%:%
-%:%496=278%:%
-%:%497=278%:%
-%:%499=278%:%
-%:%503=278%:%
-%:%504=278%:%
-%:%506=279%:%
-%:%507=280%:%
-%:%508=281%:%
-%:%509=282%:%
-%:%519=284%:%
-%:%520=285%:%
-%:%522=287%:%
-%:%523=287%:%
-%:%524=288%:%
-%:%525=289%:%
-%:%526=290%:%
-%:%527=291%:%
-%:%528=291%:%
-%:%530=291%:%
-%:%534=291%:%
-%:%535=291%:%
-%:%537=292%:%
-%:%538=293%:%
-%:%539=294%:%
-%:%540=295%:%
-%:%541=296%:%
-%:%542=297%:%
-%:%552=299%:%
-%:%553=300%:%
-%:%554=301%:%
-%:%556=303%:%
-%:%557=303%:%
-%:%558=304%:%
-%:%559=305%:%
-%:%560=306%:%
-%:%561=306%:%
-%:%563=306%:%
-%:%567=306%:%
-%:%568=306%:%
-%:%570=307%:%
-%:%571=308%:%
-%:%572=309%:%
-%:%573=310%:%
-%:%574=311%:%
-%:%584=314%:%
-%:%585=315%:%
-%:%586=316%:%
-%:%587=317%:%
-%:%588=318%:%
-%:%589=319%:%
-%:%590=320%:%
-%:%592=322%:%
-%:%593=322%:%
-%:%595=323%:%
-%:%596=324%:%
-%:%597=325%:%
-%:%598=325%:%
-%:%599=326%:%
-%:%600=327%:%
-%:%601=327%:%
-%:%603=328%:%
-%:%604=328%:%
-%:%606=329%:%
-%:%607=330%:%
-%:%608=330%:%
-%:%609=331%:%
-%:%610=332%:%
-%:%611=332%:%
-%:%613=333%:%
-%:%614=334%:%
-%:%617=336%:%
-%:%618=337%:%
-%:%620=339%:%
-%:%621=339%:%
-%:%622=340%:%
-%:%623=341%:%
-%:%624=341%:%
-%:%626=341%:%
-%:%630=341%:%
-%:%631=341%:%
-%:%633=342%:%
-%:%634=343%:%
-%:%635=344%:%
-%:%636=345%:%
-%:%637=346%:%
-%:%638=347%:%
-%:%639=348%:%
-%:%649=350%:%
-%:%650=351%:%
-%:%651=352%:%
-%:%652=353%:%
-%:%653=354%:%
-%:%657=356%:%
-%:%658=357%:%
-%:%659=358%:%
-%:%660=359%:%
-%:%661=360%:%
-%:%662=361%:%
-%:%666=363%:%
-%:%667=364%:%
-%:%668=365%:%
-%:%670=367%:%
-%:%671=367%:%
-%:%672=368%:%
-%:%675=369%:%
-%:%679=369%:%
-%:%680=369%:%
-%:%682=370%:%
+%:%491=274%:%
+%:%492=274%:%
+%:%494=274%:%
+%:%498=274%:%
+%:%508=276%:%
+%:%509=277%:%
+%:%510=278%:%
+%:%512=280%:%
+%:%513=280%:%
+%:%514=281%:%
+%:%515=282%:%
+%:%516=283%:%
+%:%517=283%:%
+%:%519=283%:%
+%:%523=283%:%
+%:%524=283%:%
+%:%526=284%:%
+%:%527=285%:%
+%:%528=286%:%
+%:%529=287%:%
+%:%539=289%:%
+%:%540=290%:%
+%:%542=292%:%
+%:%543=292%:%
+%:%544=293%:%
+%:%545=294%:%
+%:%546=295%:%
+%:%547=296%:%
+%:%548=296%:%
+%:%550=296%:%
+%:%554=296%:%
+%:%555=296%:%
+%:%557=297%:%
+%:%558=298%:%
+%:%559=299%:%
+%:%560=300%:%
+%:%561=301%:%
+%:%562=302%:%
+%:%572=304%:%
+%:%573=305%:%
+%:%574=306%:%
+%:%576=308%:%
+%:%577=308%:%
+%:%578=309%:%
+%:%579=310%:%
+%:%580=311%:%
+%:%581=311%:%
+%:%583=311%:%
+%:%587=311%:%
+%:%588=311%:%
+%:%590=312%:%
+%:%591=313%:%
+%:%592=314%:%
+%:%593=315%:%
+%:%594=316%:%
+%:%604=319%:%
+%:%605=320%:%
+%:%606=321%:%
+%:%607=322%:%
+%:%608=323%:%
+%:%609=324%:%
+%:%610=325%:%
+%:%612=327%:%
+%:%613=327%:%
+%:%615=328%:%
+%:%616=329%:%
+%:%617=330%:%
+%:%618=330%:%
+%:%619=331%:%
+%:%620=332%:%
+%:%621=332%:%
+%:%623=333%:%
+%:%624=333%:%
+%:%626=334%:%
+%:%627=335%:%
+%:%628=335%:%
+%:%629=336%:%
+%:%630=337%:%
+%:%631=337%:%
+%:%633=338%:%
+%:%634=339%:%
+%:%637=341%:%
+%:%638=342%:%
+%:%640=344%:%
+%:%641=344%:%
+%:%642=345%:%
+%:%643=346%:%
+%:%644=346%:%
+%:%646=346%:%
+%:%650=346%:%
+%:%651=346%:%
+%:%653=347%:%
+%:%654=348%:%
+%:%655=349%:%
+%:%656=350%:%
+%:%657=351%:%
+%:%658=352%:%
+%:%659=353%:%
+%:%669=355%:%
+%:%670=356%:%
+%:%671=357%:%
+%:%672=358%:%
+%:%673=359%:%
+%:%677=361%:%
+%:%678=362%:%
+%:%679=363%:%
+%:%680=364%:%
+%:%681=365%:%
+%:%682=366%:%
+%:%686=368%:%
+%:%687=369%:%
 %:%688=370%:%
-%:%691=371%:%
-%:%692=372%:%
-%:%693=372%:%
-%:%694=373%:%
+%:%690=372%:%
+%:%691=372%:%
+%:%692=373%:%
 %:%695=374%:%
-%:%696=375%:%
-%:%697=375%:%
-%:%699=375%:%
-%:%703=375%:%
-%:%704=375%:%
-%:%706=376%:%
-%:%707=377%:%
-%:%708=378%:%
-%:%709=379%:%
-%:%710=380%:%
-%:%720=382%:%
-%:%721=383%:%
-%:%722=384%:%
-%:%723=385%:%
-%:%724=386%:%
-%:%725=387%:%
-%:%726=388%:%
-%:%727=389%:%
-%:%728=390%:%
-%:%729=391%:%
-%:%730=392%:%
-%:%731=393%:%
-%:%732=394%:%
-%:%733=395%:%
-%:%734=396%:%
-%:%735=397%:%
-%:%736=398%:%
-%:%737=399%:%
-%:%738=400%:%
-%:%739=401%:%
-%:%740=402%:%
-%:%741=403%:%
-%:%745=405%:%
-%:%746=406%:%
-%:%747=407%:%
-%:%748=408%:%
-%:%749=409%:%
-%:%750=410%:%
-%:%751=411%:%
-%:%752=412%:%
-%:%753=413%:%
-%:%757=416%:%
-%:%758=417%:%
-%:%759=418%:%
-%:%760=419%:%
-%:%762=421%:%
-%:%763=421%:%
-%:%764=422%:%
-%:%765=423%:%
-%:%766=423%:%
-%:%767=424%:%
-%:%770=425%:%
-%:%774=425%:%
-%:%775=425%:%
-%:%776=425%:%
-%:%778=426%:%
-%:%779=427%:%
-%:%789=429%:%
+%:%699=374%:%
+%:%700=374%:%
+%:%702=375%:%
+%:%708=375%:%
+%:%711=376%:%
+%:%712=377%:%
+%:%713=377%:%
+%:%714=378%:%
+%:%715=379%:%
+%:%716=380%:%
+%:%717=380%:%
+%:%719=380%:%
+%:%723=380%:%
+%:%724=380%:%
+%:%726=381%:%
+%:%727=382%:%
+%:%728=383%:%
+%:%729=384%:%
+%:%730=385%:%
+%:%740=387%:%
+%:%741=388%:%
+%:%742=389%:%
+%:%743=390%:%
+%:%744=391%:%
+%:%745=392%:%
+%:%746=393%:%
+%:%747=394%:%
+%:%748=395%:%
+%:%749=396%:%
+%:%750=397%:%
+%:%751=398%:%
+%:%752=399%:%
+%:%753=400%:%
+%:%754=401%:%
+%:%755=402%:%
+%:%756=403%:%
+%:%757=404%:%
+%:%758=405%:%
+%:%759=406%:%
+%:%760=407%:%
+%:%761=408%:%
+%:%765=410%:%
+%:%766=411%:%
+%:%767=412%:%
+%:%768=413%:%
+%:%769=414%:%
+%:%770=415%:%
+%:%771=416%:%
+%:%772=417%:%
+%:%773=418%:%
+%:%777=421%:%
+%:%778=422%:%
+%:%779=423%:%
+%:%780=424%:%
+%:%782=426%:%
+%:%783=426%:%
+%:%784=427%:%
+%:%785=428%:%
+%:%786=428%:%
+%:%787=429%:%
 %:%790=430%:%
-%:%791=431%:%
-%:%792=432%:%
-%:%793=433%:%
-%:%794=434%:%
-%:%795=435%:%
-%:%796=436%:%
-%:%797=437%:%
-%:%798=438%:%
-%:%799=439%:%
-%:%800=440%:%
-%:%801=441%:%
-%:%802=442%:%
-%:%803=443%:%
-%:%804=444%:%
-%:%805=445%:%
-%:%806=446%:%
-%:%807=447%:%
-%:%808=448%:%
-%:%809=449%:%
-%:%810=450%:%
-%:%811=451%:%
-%:%812=452%:%
-%:%813=453%:%
-%:%814=454%:%
-%:%815=455%:%
-%:%817=457%:%
-%:%818=457%:%
-%:%819=458%:%
-%:%820=459%:%
-%:%821=460%:%
-%:%822=460%:%
-%:%824=460%:%
-%:%828=460%:%
-%:%829=460%:%
-%:%831=461%:%
-%:%832=462%:%
-%:%833=463%:%
-%:%834=464%:%
-%:%835=465%:%
-%:%836=466%:%
-%:%837=467%:%
-%:%838=468%:%
-%:%848=470%:%
-%:%849=471%:%
-%:%850=472%:%
-%:%851=473%:%
-%:%852=474%:%
-%:%853=475%:%
-%:%854=476%:%
+%:%794=430%:%
+%:%795=430%:%
+%:%796=430%:%
+%:%798=431%:%
+%:%799=432%:%
+%:%809=434%:%
+%:%810=435%:%
+%:%811=436%:%
+%:%812=437%:%
+%:%813=438%:%
+%:%814=439%:%
+%:%815=440%:%
+%:%816=441%:%
+%:%817=442%:%
+%:%818=443%:%
+%:%819=444%:%
+%:%820=445%:%
+%:%821=446%:%
+%:%822=447%:%
+%:%823=448%:%
+%:%824=449%:%
+%:%825=450%:%
+%:%826=451%:%
+%:%827=452%:%
+%:%828=453%:%
+%:%829=454%:%
+%:%830=455%:%
+%:%831=456%:%
+%:%832=457%:%
+%:%833=458%:%
+%:%834=459%:%
+%:%835=460%:%
+%:%837=462%:%
+%:%838=462%:%
+%:%839=463%:%
+%:%840=464%:%
+%:%841=465%:%
+%:%842=465%:%
+%:%844=465%:%
+%:%848=465%:%
+%:%849=465%:%
+%:%851=466%:%
+%:%852=467%:%
+%:%853=468%:%
+%:%854=469%:%
+%:%855=470%:%
+%:%856=471%:%
+%:%857=472%:%
+%:%858=473%:%
+%:%868=475%:%
+%:%869=476%:%
+%:%870=477%:%
+%:%871=478%:%
+%:%872=479%:%
+%:%873=480%:%
+%:%874=481%:%

### 2022-03-22 paper/output/document/thesis_3_implementation.tex
finished another read thrgh

@@
 %
-\isamarkupsubsubsection{Logical Background%
+\isamarkupsubsubsection{Subjects and Acts%
 }
@@
 goal tuple $C, A, G$ and let $s$ be an arbitrary agent.\footnote{Technically, a maxim is not a boolean 
-type, so the term $\neg M$ is not type correct. The expression $obligated \, \neg M$ merely provides 
+type, so the term $\neg M$ is not type correct. The expression $\text{obligated} \, \neg M$ merely provides 
 intuition for the meaning of prohibition, but the exact definition is given by 
@@
 obligations. As I will explain in Section \ref{testing}, Kantian ethics never prescribes contradictory
-obligations, so I will add this as an axiom.%
+obligations, so I will add an axiom disallowing contradictory obligations.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-With this logical background, I can begin to implement the Formula of Universal Law, which, as defined 
+With this logical background, I can implement the Formula of Universal Law, which, as defined 
 by the practical contradiction interpretation, states that a maxim is prohibited if it is ineffective
 when universalized. A first, unsuccessful attempt to formalize the FUL simply translates this into Isabelle's syntax
-using the abbreviations above. While this attempt will not be consistent, I will use Isabelle's automatic
+using the abbreviations above. While this attempt is not consistent, I use Isabelle's automatic
 proof search abilities to determine how to modify this formula to be consistent, revealing a key philosophical
@@
 This axiom roughly states that an obligation can't contradict its context. Knowing that \texttt{FUL0}
-contradicts this particular axiom offers insight into what the problem is. If the goal or action
-or a maxim are equivalent to its circumstance, then prohibiting it is contradictory. If the maxim has already been 
+contradicts this particular axiom offers insight into what the problem is: the FUL must be obligating 
+a maxim in which the act or goal contradicts the circumstances. Precisely, if the goal or action
+or a maxim are equivalent to its circumstances, then prohibiting it is contradictory. If the maxim has already been 
 acted on or the goal has already been achieved, then the agent cannot undo their action or the achivement 
@@
 principle of the form ``When you are eating breakfast, eat breakfast in order to eat breakfast,'' is not 
-practically relevant. No agent would ever need to act on such a principle. Morality helps agents decide
+practically relevant. Morality helps agents decide
 whether to act on a potential principle of action, but no agent would need to ask
-``When I am eating breakfast, should I eat breakfast in order to eat breakfast?" It is the wrong kind of 
-principle to be evaluating. It is not a well-formed maxim, so the categorical imperative cannot apply to it.
+``When I am eating breakfast, should I eat breakfast in order to eat breakfast?" Because it is not a 
+well-formed maxim, it is the wrong kind of principle to be evaluating, so the categorical imperative 
+cannot apply to it.
 
@@
 apply to them. The realization of this subtle problem would have been incredibly difficult without 
-computational tools, and serves as evidence of the power of computational ethics. I discuss the philosophical
-properties and implications of well-formed maxims and the power of computational ethics further in 
+computational tools, and serves as evidence of the power of computational ethics. I further discuss the philosophical
+properties and implications of well-formed maxims and the power of computational ethics in 
 Section \ref{computationalethics}.
@@
 to evaluate how well my implementation coheres with philosophical literature. This testing architecture 
-makes the notion of ``philosophical faithfulness'' precise. Each test consists of a sentence in my logic 
-and an expected outcome, where the possible outcomes are proving or refuting the sentence. For example, 
+makes the notion of ``philosophical faithfulness'' precise. Each test consists of a sentence in my logic\footnote{Some
+tests also require additional logical background, explained below.} and an expected outcome, where 
+the possible outcomes are proving or refuting the sentence. For example, 
 one such sentence is that obligations cannot contradict each other. To run the tests, I attempt to
@@
 
-The test framework can be expanded by adding more test sentences and can guide 
+The testing framework can be expanded by adding more test sentences and can guide 
 implementations of other parts of Kantian ethics or other ethical theories. As I was implementing my 
@@
 
-I use my testing framework to show that my formalization and implementation of Kantian ethics outperforms 
+I use my testing framework to show that my formalization and implementation of Kantian ethics outperform 
 two other potential implementations. First, I consider raw DDL, which serves as a control group because it simply contains the base logic
-on top of which I build other implementations. DDL can express obligation, but has no knowledge of any 
+on top of which I build other implementations. DDL can express obligation, but does not include any 
 specific moral rules (like the categorical imperative). Second, I consider Moshe Kroy's 1976 formalization 
-of the FUL and the second formulation
-of the categorical imperative \citep{kroy}. His formalization is based on Hintikka's deontic logic, which is a different,
+of the FUL \citep{kroy}. His formalization is based on Hintikka's deontic logic, which is a different,
 less expressive logic than DDL \citep{hintikka}. He presents a logical representation of the FUL that has not yet been implemented
@@
 \begin{isamarkuptext}%
-\noindent \textbf{FUL Stronger than DDL} The FUL should not hold in raw DDL, which I use a control group. 
+\noindent \textbf{FUL Stronger than DDL} The FUL should not hold in raw DDL, which I use as a control group. 
 If the FUL holds in the base logic, then adding it as an axiom doesn't make the logic any stronger, 
@@
 everyone.\footnote{Formally, $P\{A(s)\} \longrightarrow \forall p. P\{A(p)\}$.} Kroy's formalization and 
-my formalization satisfy this property, but raw DDL does not. Below I run
-this test for my formalization.%
+my implementation satisfy this property, but raw DDL does not. Below I run
+this test for my implementation.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-\noindent \textbf{Obligations Never Contradict} Contradictory obligations
+\noindent \textbf{Obligations Never Contradict} There are two reasons that Kantian ethics cannot
+require contradictory obligations. First, contradictory obligations
 make obeying the prescriptions of an ethical theory impossible.
@@
 and Kantian ethics in particular, must not result in conflicting obligations. 
-Kant only briefly discusses contradictory obligations in \emph{Metaphysics of Morals}, where he argues that 
+Second, Kant briefly discusses contradictory obligations in \emph{Metaphysics of Morals}, where he argues that 
 conflicting moral obligations are impossible under his theory \citep[V224]{metaphysicsintro}. Particularly, the categorical imperative generates 
@@
 perfect duties, as these are always stronger than imperfect duties.} Both raw DDL and 
-Kroy's formalization allow contradictory obligations, but I explicitly add an axiom to my formalization
+Kroy's formalization allow contradictory obligations, but I explicitly add an axiom to my implementation
 that prohibits contradictory obligations.%
@@
 \begin{isamarkuptext}%
-\noindent \textbf{Distributive Property for Obligations Holds} Another property related to contradictory obligations is the distributive property for the obligation
+\noindent \textbf{Distributive Property for Obligations Holds} Another property related to 
+contradictory obligations is the distributive property for the obligation operator over the and 
 operator.\footnote{Formally, $O\{A\} \wedge O\{B\} \longleftrightarrow O\{A \wedge B\}$.} This is 
-another property that we expect to hold. The rough English translation of  $O \{ A \wedge B \} $ is ``you are obligated to 
+another property that should hold. The rough English translation of  $O \{ A \wedge B \}$ is ``you are obligated to 
 do both A and B''. The rough English translation of $O\{A\} \wedge O\{B\}$ is ``you are obligated to do A 
-and you are obligated to do B.'' We think those English sentences mean the same thing, and they should mean 
+and you are obligated to do B.'' Both those English sentences mean the same thing, and they should mean 
 the same thing in logic as well. Moreover, if that (rather intuitive) property holds, then contradictory
@@
 property holds in this logic, then obligations cannot contradict.''%
+}\isanewline
+%
+\isamarkupcmt{This lemma is trivially true by the added axiom, but notice that this proof does not use that axiom.
+This proof uses axiom O\_diamond and the assumptions and thus also holds in DDL itself, even without 
+an axiom prohibiting contradictory obligations.%
 }%
@@
 Again, this test fails for raw DDL and for Kroy's formalization, but
-passes for my interpretation because I require that obligations don't contradict as an axiom.%
+passes for my implementation because I require that obligations don't contradict as an axiom.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \isamarkupcmt{The proof proceeds almost immediately using the new axiom.%
+}\isanewline
+%
+\isamarkupcmt{This proof and the above lemma together imply that the distributive property holds if and only if 
+there are no contradictory obligations.%
 }%
@@
 a world where they are universalized. This property fails to hold in both raw DDL
-and Kroy's formalization, but holds for my formalization. Showing that this property holds
-for my formalization required significant logical work and the full code is presented in Appendix \ref{weirdtests}.%
+and Kroy's formalization, but holds for my implementation. Showing that this property holds
+for my formalization required additional logical background and the full code is presented in Appendix \ref{weirdtests}.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 because it exists as a practice. Murder, on the other hand, is an example of a natural act because 
-its existence only depends on the laws of nature\cite[11]{KorsgaardFUL}.
+its existence only depends on the laws of nature \cite[11]{KorsgaardFUL}.
 
@@
 
-Both raw DDL and Kroy's interpretation fail to show the wrongness of conventional or natural acts. 
+Both raw DDL and Kroy's formalization fail to show the wrongness of conventional or natural acts. 
 My system shows the wrongness of both natural and conventional acts because it is faithful to Korsgaard's 
@@
 involves natural acts. I present an additional example demonstrating that my implementation passes
-this test in Appendix \ref{weirdtests}.%
+this test in Appendix \ref{weirdtests}. Because I formalize the philosophically-accepted version 
+of the FUL, my implementation passes this test.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %:%513=358%:%
-%:%515=360%:%
-%:%516=360%:%
+%:%514=359%:%
+%:%516=361%:%
 %:%517=361%:%
-%:%519=362%:%
+%:%518=362%:%
 %:%520=363%:%
-%:%523=365%:%
-%:%525=367%:%
-%:%526=367%:%
+%:%521=364%:%
+%:%524=366%:%
+%:%526=368%:%
 %:%527=368%:%
-%:%529=369%:%
+%:%528=369%:%
 %:%530=370%:%
-%:%531=370%:%
+%:%531=371%:%
 %:%532=371%:%
 %:%533=372%:%
-%:%534=372%:%
+%:%534=373%:%
 %:%535=373%:%
-%:%536=373%:%
-%:%538=373%:%
-%:%542=373%:%
-%:%543=373%:%
-%:%545=374%:%
+%:%536=374%:%
+%:%537=374%:%
+%:%539=374%:%
+%:%543=374%:%
+%:%544=374%:%
 %:%546=375%:%
@@
 %:%551=380%:%
-%:%561=382%:%
+%:%552=381%:%
 %:%562=383%:%
@@
 %:%580=401%:%
+%:%581=402%:%
 %:%582=403%:%
-%:%583=403%:%
+%:%584=405%:%
 %:%585=405%:%
-%:%586=406%:%
 %:%587=407%:%
@@
 %:%589=409%:%
-%:%598=411%:%
-%:%610=413%:%
-%:%611=414%:%
+%:%590=410%:%
+%:%591=411%:%
+%:%600=413%:%
 %:%612=415%:%
@@
 %:%634=437%:%
-%:%637=441%:%
-%:%638=442%:%
+%:%635=438%:%
+%:%636=439%:%
 %:%639=443%:%
@@
 %:%642=446%:%
-%:%645=448%:%
-%:%646=449%:%
+%:%643=447%:%
+%:%644=448%:%
 %:%647=450%:%
@@
 %:%654=457%:%
-%:%658=459%:%
-%:%659=460%:%
+%:%655=458%:%
+%:%656=459%:%
 %:%660=461%:%
@@
 %:%671=472%:%
+%:%672=473%:%
 %:%673=474%:%
-%:%674=474%:%
-%:%675=475%:%
-%:%678=476%:%
-%:%682=476%:%
-%:%683=476%:%
-%:%685=477%:%
-%:%686=478%:%
+%:%675=476%:%
+%:%676=476%:%
+%:%677=477%:%
+%:%680=478%:%
+%:%684=478%:%
+%:%685=478%:%
 %:%687=479%:%
-%:%688=479%:%
-%:%690=480%:%
-%:%691=481%:%
+%:%688=480%:%
+%:%689=481%:%
+%:%690=481%:%
 %:%692=482%:%
 %:%693=483%:%
-%:%699=483%:%
-%:%702=484%:%
-%:%703=485%:%
-%:%704=485%:%
-%:%705=486%:%
-%:%708=487%:%
-%:%712=487%:%
-%:%713=487%:%
-%:%715=488%:%
-%:%716=489%:%
-%:%726=491%:%
-%:%727=492%:%
+%:%694=484%:%
+%:%695=485%:%
+%:%701=485%:%
+%:%704=486%:%
+%:%705=487%:%
+%:%706=487%:%
+%:%707=488%:%
+%:%710=489%:%
+%:%714=489%:%
+%:%715=489%:%
+%:%717=490%:%
+%:%718=491%:%
 %:%728=493%:%
@@
 %:%746=511%:%
+%:%747=512%:%
 %:%748=513%:%
-%:%749=513%:%
-%:%750=514%:%
-%:%753=515%:%
-%:%757=515%:%
-%:%758=515%:%
-%:%759=515%:%
-%:%761=516%:%
-%:%767=516%:%
-%:%770=517%:%
-%:%771=518%:%
-%:%772=518%:%
-%:%773=519%:%
-%:%774=520%:%
-%:%777=521%:%
-%:%781=521%:%
-%:%782=521%:%
-%:%783=521%:%
-%:%785=522%:%
-%:%786=523%:%
-%:%787=524%:%
-%:%797=526%:%
-%:%798=527%:%
-%:%799=528%:%
+%:%749=514%:%
+%:%751=516%:%
+%:%752=516%:%
+%:%753=517%:%
+%:%756=518%:%
+%:%760=518%:%
+%:%761=518%:%
+%:%762=518%:%
+%:%764=519%:%
+%:%770=519%:%
+%:%773=520%:%
+%:%774=521%:%
+%:%775=521%:%
+%:%776=522%:%
+%:%777=523%:%
+%:%780=524%:%
+%:%784=524%:%
+%:%785=524%:%
+%:%786=524%:%
+%:%788=525%:%
+%:%789=526%:%
+%:%790=527%:%
 %:%800=529%:%
@@
 %:%804=533%:%
-%:%806=536%:%
+%:%805=534%:%
+%:%806=535%:%
 %:%807=536%:%
-%:%810=537%:%
-%:%814=537%:%
-%:%815=537%:%
-%:%817=538%:%
-%:%818=539%:%
-%:%819=539%:%
-%:%821=540%:%
-%:%831=542%:%
-%:%832=543%:%
-%:%833=544%:%
+%:%809=539%:%
+%:%810=539%:%
+%:%813=540%:%
+%:%817=540%:%
+%:%818=540%:%
+%:%820=541%:%
+%:%821=542%:%
+%:%822=542%:%
+%:%824=543%:%
 %:%834=545%:%
@@
 %:%837=548%:%
+%:%838=549%:%
 %:%839=550%:%
-%:%840=550%:%
-%:%841=551%:%
-%:%842=552%:%
-%:%845=553%:%
-%:%849=553%:%
-%:%850=553%:%
-%:%851=553%:%
-%:%853=554%:%
-%:%854=555%:%
-%:%855=556%:%
-%:%865=558%:%
-%:%866=559%:%
-%:%868=561%:%
-%:%869=561%:%
-%:%870=562%:%
-%:%871=563%:%
-%:%874=564%:%
-%:%878=564%:%
-%:%879=564%:%
-%:%880=564%:%
-%:%882=565%:%
-%:%892=567%:%
-%:%893=568%:%
-%:%894=569%:%
-%:%895=570%:%
-%:%896=571%:%
-%:%897=572%:%
-%:%898=573%:%
-%:%899=574%:%
-%:%900=575%:%
-%:%901=576%:%
-%:%902=577%:%
-%:%903=578%:%
-%:%904=579%:%
-%:%905=580%:%
-%:%909=584%:%
-%:%910=585%:%
-%:%911=586%:%
-%:%912=587%:%
-%:%913=588%:%
-%:%914=589%:%
-%:%915=590%:%
-%:%916=591%:%
-%:%920=594%:%
-%:%921=595%:%
-%:%922=596%:%
-%:%923=597%:%
-%:%924=598%:%
-%:%925=599%:%
-%:%926=600%:%
-%:%927=601%:%
-%:%928=602%:%
-%:%929=603%:%
-%:%930=604%:%
-%:%931=605%:%
-%:%932=606%:%
-%:%933=607%:%
-%:%934=608%:%
-%:%935=609%:%
-%:%936=610%:%
-%:%937=611%:%
-%:%938=612%:%
-%:%939=613%:%
-%:%940=614%:%
-%:%941=615%:%
-%:%942=616%:%
-%:%943=617%:%
-%:%944=618%:%
+%:%840=551%:%
+%:%841=552%:%
+%:%843=554%:%
+%:%844=554%:%
+%:%845=555%:%
+%:%846=556%:%
+%:%849=557%:%
+%:%853=557%:%
+%:%854=557%:%
+%:%855=557%:%
+%:%857=558%:%
+%:%858=559%:%
+%:%859=560%:%
+%:%860=560%:%
+%:%862=561%:%
+%:%863=562%:%
+%:%864=563%:%
+%:%874=565%:%
+%:%875=566%:%
+%:%877=568%:%
+%:%878=568%:%
+%:%879=569%:%
+%:%880=570%:%
+%:%883=571%:%
+%:%887=571%:%
+%:%888=571%:%
+%:%889=571%:%
+%:%891=572%:%
+%:%892=572%:%
+%:%894=573%:%
+%:%895=574%:%
+%:%905=576%:%
+%:%906=577%:%
+%:%907=578%:%
+%:%908=579%:%
+%:%909=580%:%
+%:%910=581%:%
+%:%911=582%:%
+%:%912=583%:%
+%:%913=584%:%
+%:%914=585%:%
+%:%915=586%:%
+%:%916=587%:%
+%:%917=588%:%
+%:%918=589%:%
+%:%922=593%:%
+%:%923=594%:%
+%:%924=595%:%
+%:%925=596%:%
+%:%926=597%:%
+%:%927=598%:%
+%:%928=599%:%
+%:%929=600%:%
+%:%933=603%:%
+%:%934=604%:%
+%:%935=605%:%
+%:%936=606%:%
+%:%937=607%:%
+%:%938=608%:%
+%:%939=609%:%
+%:%940=610%:%
+%:%941=611%:%
+%:%942=612%:%
+%:%943=613%:%
+%:%944=614%:%
+%:%945=615%:%
+%:%946=616%:%
+%:%947=617%:%
+%:%948=618%:%
+%:%949=619%:%
+%:%950=620%:%
+%:%951=621%:%
+%:%952=622%:%
+%:%953=623%:%
+%:%954=624%:%
+%:%955=625%:%
+%:%956=626%:%
+%:%957=627%:%
+%:%958=628%:%

### 2022-03-22 paper/output/document/thesis_4_applications.tex
finished another read thrgh

@@
 \begin{isamarkuptext}%
-In this chapter, I demonstrate that my system can produce correct judgements for challenging moral 
-dilemmas that naive ethical reasoning cannot satisfactorily handle. Because my system is faithful to
+In this chapter, I demonstrate that my system can produce sophisticated judgements for challenging moral 
+dilemmas that naive Kantian ethical reasoning cannot satisfactorily handle. Because my system is faithful to
 philosophical literature, it can reproduce complex ethical judgements presented by philosophers as 
-solutions to controversial open questions in ethics.
-These dilemmas serve as examples of how my system could be used
+solutions to controversial open questions in ethics. These dilemmas serve as examples of how my system could be used
 in practice and demonstrate my system's ability to formalize longer, more complicted ethical arguments
 than those presented in Chapter \ref{details}. Moreover, in the process of formalizing these dilemmas, 
-I isolated the exact conditon that makes a maxim about lying wrong, an insight that could contribute to 
+I isolate the exact conditon that makes a maxim about lying wrong, an insight that could contribute to 
 the philosophical literature on lying.
@@
 
-In this chapter, I tackle this challenge by
-endowing my system with this kind of common sense in the specific case of lying. My system needs common 
-sense facts and definitions because, while it has the ability to reason
+In this chapter, I tackle this challenge by endowing my system with this kind of common sense in the 
+specific case of lying. While my system has the ability to reason
 using the Formula of Universal Law, this reasoning must be applied to objects that are defined
-using common sense. Because these common sense facts can determine my system's judgements, they are part of the trusted
+using common sense. Because common sense facts can determine my system's judgements, they are part of the trusted
 code base for my system, or the logic and code that a user must trust in order to trust my system. 
-Changing these common sense facts will change the judgements 
-that my system makes. For example, if we define truth telling as an act that is self-contradictory (perhaps
+Malicious common sense facts will result in bad judgements.
+For example, if we define truth telling as an act that is self-contradictory (perhaps
 by defining it as $p \wedge \neg p$), then my system will output that truth telling is prohibited.
-Malicious common sense facts and definitions will result in bad ethical judgements. 
 The challenge of endowing automated ethical reasoners with common sense reasoning is not unique to my 
@@
 Kantian ethics, an example of the additional work required to use my system in practice, and a 
-demonstration of my system's power and flexibility. These examples demonstrate that, armed with nuanced 
+demonstration of my system's power and flexibility. These examples demonstrate that, armed with some basic 
 common sense facts, my system can make sophisticated judgements faithful to philosophical literature.%
@@
 examines Kant's prohibition on lying \citep{KorsgaardRTL}. She begins with the case of 
-lying and joking. Many of Kant's critics argue that his prohibition on lies includes lies told in 
-the context of a joke, which should be permissible. Korsgaard responds by arguing 
+lying and joking. To demonstrate that Kant's theory is too demanding, many of his critics argue that 
+his prohibition on lies includes lies told in the context of a joke, which should be permissible. Korsgaard responds by arguing 
 that there is a crucial difference between lying and joking: lies involve deception, but jokes do not. 
@@
 \begin{isamarkuptext}%
-To avoid unintentional wrongdoing, I focus on ``knowing lies,'' 
-in which the speaker is aware that they are lying. It is uncontroversial that, in order for an act to be
-a knowing lie, the speaker must utter a false statement that they do not believe. This also makes it 
-easier to make moral judgements about the speaker's action, since they were, at the very least, aware
-of their lie. The second half of
+To avoid issues with unintentional wrongdoing, I focus on ``knowing lies,'' 
+in which the speaker is aware that they are lying. This makes it easier to make moral judgements about 
+the speaker's action, since they were, at the very least, aware of their lie. It is uncontroversial 
+that, in order for an act to be a knowing lie, the speaker must utter a false statement that they do 
+not believe. The second half of
 this definition requires that the goal of the lie is deception. This is inspired by  Korsgaard's interpretation 
@@
 \citep[4]{KorsgaardRTL}. In my formalization, this means that the purpose or goal of the maxim must
-involve decieving someone, or, in other words, that someone believe what the speaker knows to be a 
+involve decieving someone, or that someone believe what the speaker knows to be a 
 falsehood.
@@
 this lemma represent the common sense necessary to reach this conclusion. This
-common sense background is a direct formalization of the premises of Korsgaard's argument. Using these
-relatively minimal premises about individual behavior, my system derives a prohibition against lying.%
+common sense background is a direct formalization of the premises of Korsgaard's argument.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 communication begins to break down and people no longer believe each other. Call this the ``convention of 
-trust'' fact. In the rest of this section, I will test versions of this assumption, effectively encoding 
+trust'' fact. In the rest of this chapter, I will test another version of this assumption, effectively encoding 
 different common sense understandings of lying.%
@@
 doesn't require deception, where deception involves someone believing the uttered falsehood. 
-This definition doesn't require any conception of humor, but merely
+This definition is thin because it doesn't require any conception of humor, but merely
 distinguishes jokes from lies.
@@
 
+This demonstrates one kind of philosophical contribution that computational ethics can make: it can 
+offer insights that guide the formulation of permissible maxims, as in the surprise party example
+above. In Section \ref{computationalethics}, I provide another example of such a boundary condition 
+for the formulation of a maxim, which serves as further evidence of the potential of computational ethics.
+
 There are two implications of this section. First, my system is capable of performing ethical reasoning
@@
 in the process of making this argument precise, my system isolated a necessary and sufficient condition 
-of a maxim about uttering a falsehood being prohibited: that the goal require that someone believe
+for a maxim about uttering a falsehood to be prohibited: the goal must require that someone believe
 the falsehood. This condition made an long-standing argument in Kantian ethics more precise, can guide 
@@
 about the wrongness of lying. In other words, an insight generated by the
-computer provides value to ethicists, bolstering the argument for computational ethics provided in 
+computer could provide value to ethicists, bolstering the argument for computational ethics provided in 
 Section \ref{computationalethics}.%
@@
 \isamarkupcmt{This statement represents the lie that the murderer tells you. By not announcing his
-intention, he is implicitly telling you that he is not a murderer, as people normally assume that 
+intention, he is implicitly telling you that he is not a murderer, as people typically assume that 
 those knocking on their door are not murderers.%
@@
 uncontroversial definitions and assumptions are enough to achieve nuanced ethical judgements. Moreover, 
-these kinds of judgements demonstrate that, with additional work, my system could be used in practice 
+these examples demonstrate that, with some additional work, my system could be used in practice 
 to guide AI agents. The idea of AI making decisions as in the dilemmas above may seem far-fetched, but
@@
 %:%79=51%:%
-%:%80=52%:%
-%:%81=53%:%
-%:%82=54%:%
-%:%91=57%:%
+%:%88=54%:%
+%:%100=57%:%
+%:%101=58%:%
+%:%102=59%:%
 %:%103=60%:%
@@
 %:%121=78%:%
-%:%122=79%:%
-%:%123=80%:%
+%:%123=81%:%
 %:%124=81%:%
-%:%126=84%:%
-%:%127=84%:%
-%:%129=85%:%
-%:%130=86%:%
-%:%131=87%:%
+%:%126=82%:%
+%:%127=83%:%
+%:%128=84%:%
+%:%131=86%:%
+%:%132=87%:%
+%:%133=88%:%
 %:%134=89%:%
@@
 %:%137=92%:%
-%:%138=93%:%
-%:%139=94%:%
+%:%139=95%:%
 %:%140=95%:%
-%:%142=98%:%
-%:%143=98%:%
-%:%145=99%:%
-%:%146=100%:%
-%:%147=100%:%
-%:%148=101%:%
-%:%149=101%:%
-%:%150=102%:%
-%:%152=103%:%
-%:%153=103%:%
-%:%154=104%:%
-%:%155=104%:%
-%:%156=105%:%
+%:%142=96%:%
+%:%143=97%:%
+%:%144=97%:%
+%:%145=98%:%
+%:%146=98%:%
+%:%147=99%:%
+%:%149=100%:%
+%:%150=100%:%
+%:%151=101%:%
+%:%152=101%:%
+%:%153=102%:%
+%:%155=103%:%
+%:%156=104%:%
+%:%157=105%:%
 %:%158=106%:%
 %:%159=107%:%
-%:%160=108%:%
-%:%161=109%:%
-%:%162=110%:%
+%:%162=111%:%
+%:%163=112%:%
+%:%164=113%:%
 %:%165=114%:%
@@
 %:%171=120%:%
-%:%172=121%:%
 %:%173=122%:%
-%:%174=123%:%
-%:%176=125%:%
-%:%177=125%:%
-%:%178=126%:%
-%:%180=127%:%
+%:%174=122%:%
+%:%175=123%:%
+%:%177=124%:%
+%:%180=126%:%
+%:%181=127%:%
+%:%182=128%:%
 %:%183=129%:%
@@
 %:%192=138%:%
-%:%193=139%:%
 %:%194=140%:%
-%:%195=141%:%
-%:%197=143%:%
-%:%198=143%:%
-%:%200=144%:%
-%:%201=145%:%
-%:%202=146%:%
-%:%203=146%:%
-%:%204=147%:%
-%:%205=147%:%
-%:%207=148%:%
-%:%208=149%:%
-%:%209=149%:%
-%:%210=150%:%
-%:%211=150%:%
-%:%213=151%:%
-%:%216=153%:%
+%:%195=140%:%
+%:%197=141%:%
+%:%198=142%:%
+%:%199=143%:%
+%:%200=143%:%
+%:%201=144%:%
+%:%202=144%:%
+%:%204=145%:%
+%:%205=146%:%
+%:%206=146%:%
+%:%207=147%:%
+%:%208=147%:%
+%:%210=148%:%
+%:%213=150%:%
+%:%214=151%:%
+%:%215=152%:%
 %:%217=154%:%
-%:%218=155%:%
-%:%219=156%:%
-%:%221=158%:%
-%:%222=158%:%
-%:%223=159%:%
-%:%224=160%:%
-%:%226=161%:%
-%:%227=161%:%
-%:%228=162%:%
-%:%230=163%:%
-%:%231=164%:%
-%:%232=164%:%
-%:%233=165%:%
+%:%218=154%:%
+%:%219=155%:%
+%:%220=156%:%
+%:%222=157%:%
+%:%223=157%:%
+%:%224=158%:%
+%:%226=159%:%
+%:%227=160%:%
+%:%228=160%:%
+%:%229=161%:%
+%:%231=162%:%
+%:%232=163%:%
+%:%233=164%:%
+%:%234=165%:%
 %:%235=166%:%
 %:%236=167%:%
-%:%237=168%:%
-%:%238=169%:%
-%:%239=170%:%
-%:%240=171%:%
-%:%241=171%:%
-%:%242=172%:%
-%:%244=173%:%
-%:%245=173%:%
-%:%246=174%:%
-%:%253=175%:%
-%:%254=175%:%
-%:%255=176%:%
-%:%256=176%:%
-%:%257=177%:%
-%:%258=177%:%
-%:%260=178%:%
-%:%261=179%:%
-%:%262=180%:%
-%:%263=181%:%
-%:%264=181%:%
-%:%265=182%:%
-%:%266=182%:%
-%:%267=183%:%
-%:%268=183%:%
-%:%269=184%:%
-%:%270=184%:%
-%:%271=185%:%
-%:%272=185%:%
-%:%273=185%:%
-%:%275=186%:%
-%:%276=187%:%
-%:%277=187%:%
-%:%278=188%:%
+%:%237=167%:%
+%:%238=168%:%
+%:%240=169%:%
+%:%241=169%:%
+%:%242=170%:%
+%:%249=171%:%
+%:%250=171%:%
+%:%251=172%:%
+%:%252=172%:%
+%:%253=173%:%
+%:%254=173%:%
+%:%256=174%:%
+%:%257=175%:%
+%:%258=176%:%
+%:%259=177%:%
+%:%260=177%:%
+%:%261=178%:%
+%:%262=178%:%
+%:%263=179%:%
+%:%264=179%:%
+%:%265=180%:%
+%:%266=180%:%
+%:%267=181%:%
+%:%268=181%:%
+%:%269=181%:%
+%:%271=182%:%
+%:%272=183%:%
+%:%273=183%:%
+%:%274=184%:%
+%:%284=186%:%
+%:%285=187%:%
+%:%286=188%:%
+%:%287=189%:%
 %:%288=190%:%
@@
 %:%298=200%:%
-%:%299=201%:%
 %:%300=202%:%
-%:%301=203%:%
-%:%302=204%:%
-%:%304=206%:%
-%:%305=206%:%
-%:%306=207%:%
-%:%308=208%:%
-%:%309=209%:%
+%:%301=202%:%
+%:%302=203%:%
+%:%304=204%:%
+%:%305=205%:%
+%:%308=207%:%
+%:%309=208%:%
+%:%310=209%:%
+%:%311=210%:%
 %:%312=211%:%
@@
 %:%316=215%:%
-%:%317=216%:%
 %:%318=217%:%
-%:%319=218%:%
-%:%320=219%:%
-%:%322=221%:%
-%:%323=221%:%
-%:%324=222%:%
-%:%325=223%:%
-%:%327=224%:%
-%:%328=224%:%
-%:%329=225%:%
-%:%331=226%:%
-%:%332=227%:%
-%:%333=227%:%
-%:%334=228%:%
-%:%336=229%:%
-%:%337=229%:%
-%:%338=230%:%
-%:%340=231%:%
-%:%341=231%:%
-%:%342=232%:%
-%:%345=233%:%
-%:%349=233%:%
-%:%350=233%:%
+%:%319=217%:%
+%:%320=218%:%
+%:%321=219%:%
+%:%323=220%:%
+%:%324=220%:%
+%:%325=221%:%
+%:%327=222%:%
+%:%328=223%:%
+%:%329=223%:%
+%:%330=224%:%
+%:%332=225%:%
+%:%333=225%:%
+%:%334=226%:%
+%:%336=227%:%
+%:%337=227%:%
+%:%338=228%:%
+%:%341=229%:%
+%:%345=229%:%
+%:%346=229%:%
+%:%348=230%:%
+%:%349=231%:%
+%:%350=232%:%
+%:%351=233%:%
 %:%352=234%:%
-%:%353=235%:%
-%:%354=236%:%
-%:%355=237%:%
-%:%356=238%:%
+%:%362=237%:%
+%:%363=238%:%
+%:%364=239%:%
+%:%365=240%:%
 %:%366=241%:%
@@
 %:%411=286%:%
-%:%420=289%:%
-%:%432=292%:%
+%:%412=287%:%
+%:%421=290%:%
 %:%433=293%:%
@@
 %:%450=310%:%
-%:%452=312%:%
-%:%453=312%:%
-%:%455=313%:%
-%:%456=313%:%
+%:%451=311%:%
+%:%453=313%:%
+%:%454=313%:%
+%:%456=314%:%
 %:%457=314%:%
-%:%458=314%:%
-%:%460=315%:%
+%:%458=315%:%
+%:%459=315%:%
 %:%461=316%:%
 %:%462=317%:%
-%:%463=317%:%
+%:%463=318%:%
 %:%464=318%:%
-%:%465=318%:%
-%:%467=319%:%
-%:%468=319%:%
+%:%465=319%:%
+%:%466=319%:%
+%:%468=320%:%
 %:%469=320%:%
-%:%470=320%:%
-%:%472=321%:%
-%:%473=321%:%
+%:%470=321%:%
+%:%471=321%:%
+%:%473=322%:%
 %:%474=322%:%
-%:%475=322%:%
+%:%475=323%:%
 %:%476=323%:%
-%:%478=324%:%
+%:%477=324%:%
 %:%479=325%:%
-%:%482=327%:%
+%:%480=326%:%
 %:%483=328%:%
@@
 %:%485=330%:%
-%:%487=332%:%
-%:%488=332%:%
-%:%490=333%:%
-%:%491=333%:%
+%:%486=331%:%
+%:%488=333%:%
+%:%489=333%:%
+%:%491=334%:%
 %:%492=334%:%
-%:%493=334%:%
+%:%493=335%:%
 %:%494=335%:%
-%:%496=336%:%
-%:%497=336%:%
+%:%495=336%:%
+%:%497=337%:%
 %:%498=337%:%
-%:%499=337%:%
-%:%501=338%:%
-%:%502=338%:%
+%:%499=338%:%
+%:%500=338%:%
+%:%502=339%:%
 %:%503=339%:%
-%:%504=339%:%
+%:%504=340%:%
 %:%505=340%:%
-%:%507=341%:%
+%:%506=341%:%
 %:%508=342%:%
-%:%524=374%:%
+%:%509=343%:%
 %:%525=375%:%
@@
 %:%532=382%:%
-%:%534=384%:%
-%:%535=384%:%
+%:%533=383%:%
+%:%535=385%:%
 %:%536=385%:%
 %:%537=386%:%
-%:%539=387%:%
-%:%540=387%:%
+%:%538=387%:%
+%:%540=388%:%
 %:%541=388%:%
-%:%543=389%:%
-%:%544=389%:%
+%:%542=389%:%
+%:%544=390%:%
 %:%545=390%:%
-%:%547=391%:%
+%:%546=391%:%
 %:%548=392%:%
@@
 %:%551=395%:%
-%:%552=395%:%
+%:%552=396%:%
 %:%553=396%:%
-%:%555=397%:%
+%:%554=397%:%
 %:%556=398%:%
@@
 %:%561=403%:%
-%:%562=403%:%
+%:%562=404%:%
 %:%563=404%:%
-%:%565=405%:%
+%:%564=405%:%
 %:%566=406%:%
-%:%567=406%:%
+%:%567=407%:%
 %:%568=407%:%
-%:%571=408%:%
-%:%575=408%:%
-%:%576=408%:%
-%:%577=408%:%
-%:%579=409%:%
+%:%569=408%:%
+%:%572=409%:%
+%:%576=409%:%
+%:%577=409%:%
+%:%578=409%:%
 %:%580=410%:%
 %:%581=411%:%
-%:%591=413%:%
+%:%582=412%:%
 %:%592=414%:%
@@
 %:%594=416%:%
-%:%596=418%:%
-%:%597=418%:%
+%:%595=417%:%
+%:%597=419%:%
 %:%598=419%:%
-%:%600=420%:%
-%:%601=420%:%
+%:%599=420%:%
+%:%601=421%:%
 %:%602=421%:%
-%:%604=422%:%
-%:%605=422%:%
+%:%603=422%:%
+%:%605=423%:%
 %:%606=423%:%
-%:%608=424%:%
-%:%609=424%:%
+%:%607=424%:%
+%:%609=425%:%
 %:%610=425%:%
-%:%612=426%:%
-%:%613=426%:%
+%:%611=426%:%
+%:%613=427%:%
 %:%614=427%:%
-%:%616=428%:%
+%:%615=428%:%
 %:%617=429%:%
-%:%618=429%:%
+%:%618=430%:%
 %:%619=430%:%
-%:%626=431%:%
-%:%627=431%:%
+%:%620=431%:%
+%:%627=432%:%
 %:%628=432%:%
-%:%629=432%:%
+%:%629=433%:%
 %:%630=433%:%
-%:%631=433%:%
-%:%632=433%:%
+%:%631=434%:%
+%:%632=434%:%
 %:%633=434%:%
-%:%634=434%:%
+%:%634=435%:%
 %:%635=435%:%
-%:%636=435%:%
-%:%637=435%:%
+%:%636=436%:%
+%:%637=436%:%
 %:%638=436%:%
-%:%639=436%:%
+%:%639=437%:%
 %:%640=437%:%
-%:%641=437%:%
-%:%642=437%:%
+%:%641=438%:%
+%:%642=438%:%
 %:%643=438%:%
-%:%653=440%:%
+%:%644=439%:%
 %:%654=441%:%
@@
 %:%688=475%:%
+%:%689=476%:%

### 2022-03-22 paper/output/document/thesis_5_discussion.tex
finished another read thrgh

--- 2022-03-21 paper/output/document/thesis_5_discussion.tex
@@
 represented maxim and sufficient factual background, can classify a maxim as obligatory, permissible, 
-or prohibited. In this chapter, I discuss the philosophical limitations and implications of this 
+or prohibited. In Chapter \ref{applications}, I demonstrated that my system is capable of performing sophisticated,
+nuanced ethical reasoning. In this chapter, I discuss the philosophical limitations and implications of this 
 work.
@@
 \begin{isamarkuptext}%
-In Chapter \ref{applications}, I demonstrated that my system is capable of performing sophisticated,
-nuanced ethical reasoning. In this section, I outline the additional components necessary for my system
-to guide AI agents in practice. As it stands, my system is a categorical imperative library that, given
-sufficient factual or ``common sense'' background, can take 
-as input the logical representation of a maxim and return its moral status (if it is obligatory, 
-prohibited, or permissible). My project potentially 
+In this section, I outline the additional components necessary for my system
+to guide AI agents in practice. As it stands, my system is a categorical imperative library that can
+evaluate the moral status of a maxim. My project potentially 
 serves as one component of an ``ethics engine'' that an AI agent could use to make ethical decisions.
-For example, my system could be combined with an input parser to translate moral dilemmas as represented 
-to the AI agent into maxims in my logic. An output parser could translate my system's output
-into a prescription for action that the AI agent could act on. \begin{figure}
+For example, when an AI agent faces a moral dilemma in some internal representation, it could pass it 
+to an input parser that translates the dilemma into a maxim in my logic. An output parser could then 
+translate my system's output into a prescription for action that the AI agent could act on. \begin{figure}
 \includegraphics[scale=0.43]{AI_engine.png}
@@
 imperative component.} \label{fig:AIengine}
-\end{figure} Figure \ref{fig:AIengine} depicts the workflow of this example ethics engine.
-
-In this workflow, an AI agent is faced with a moral dilemma in some internal representation. The input
-parser translates this internal representation into an appropriate logical representation, i.e. 
-a circumstance, act, goal tuple. The output parser translates the output of the categorical imperative
-library (the moral status of the maxim as obligatory, prohibited, or permissible) to a prescription for
-action. In order for my system to be used in an AI agent using the workflow
-above, future work must develop such input and output parsers.
+\end{figure} Figure \ref{fig:AIengine} depicts the workflow of this example ethics engine. In order 
+for my system to guide an AI agent using this workflow, future work must develop such input and output parsers.
 
 One of the biggest challenges for an ethics engine is the development of an input parser. An input parser 
-for my implementation of automated Kantian ethics must translate a complex real-world situation into a flat, logical representation.
+for my implementation of automated Kantian ethics must translate a complex real-world situation into a flat 
+circumstances, act, goal triple.
 This requires that the input parser determine which circumstances are morally relevant
-to a maxim, a controversial judgement. As mentioned in Section \ref{whatisamaxim},
+to a maxim, a controversial judgement. As introduced in Section \ref{whatisamaxim},
 there is robust debate on the circumstances that should be considered when formulating a maxim, 
@@
 While this view has intuitive appeal, it raises the question of how we can determine
-which circumstances are morally relevant. O'Neill answers this question by noting that the Formula of Universal Law is 
+which circumstances are morally relevant. O'Neill answers this question
+by noting that the Formula of Universal Law is
 a ``test of moral worth rather than of outward rightness'' \citep[98]{constofreason}. The FUL is a way 
@@
 parser, this transformation must be a good-faith attempt to capture the principle of action. 
-Correctly formulating a maxim requires what Kantians call ``practical judgement,'' or
+Such a good-faith attempt to formulate a maxim requires what Kantians call ``practical judgement,'' or
 common sense reasoning and factual background \citep{oneilluniversallaws}. Returning to the example above, the fact that being 
 unemployed may contribute to one's desire to steal another's job is a consequence of practical
-judgement, not just pure reason alone. Translating everyday situations into appropriate maxims is
-the bulk of the reasoning that a Kantian human being does when making decisions. Automating this
-reasoning requires endowing a machine with common sense.
-
-The challenge of formulating a maxim is one of the biggest obstacles to using my categorical imperative library
+judgement, not just pure reason alone. Automating the formulation of a maxim requires
+endowing a machine with common sense.
+
+Translating everyday situations into appropriate maxims is the bulk of the reasoning that a Kantian 
+human being does when making decisions, so it is unsurprising that formulating a maxim 
+is one of the biggest obstacles to using my categorical imperative library
 in an AI ethics engine. One solution is for a human being to perform the role of the input
@@
 These interpretations could inspire heuristics to classify circumstances as morally 
-relevant. For example, one such attempt could define a moral closeness relation between an action, a 
+relevant. For example, one such attempt could define a moral closeness relation between an act, a 
 goal, and circumstances. This heuristic could define morally relevant circumstances as those that 
-reach a certain closeness threshhold with the action and the goal. Another possible heuristic could 
+reach a certain closeness threshhold with the act and the goal. Another possible heuristic could 
 define some set of morally important entities, and classify morally relevant circumstances as those
@@
 specific. As demonstrated in the examples in Chapter \ref{applications}, my system can produce sophisticated 
-judgements with relatively little situational context. Thus, while my automated categorical imperative
+judgements with relatively little situational context. Thus, while my automated categorical imperative system
 requires some common sense and factual background, Chapter \ref{applications} demonstrates that automating
@@
 
-I do not argue that computational ethics uncovers philosophical insights that humans are always incapable 
-of reaching. In some cases, computational ethics may automate calculations too long and tedious for 
+In some cases, computational ethics may automate calculations too long and tedious for 
 any human philosopher to complete. Insights like the one about well-formed maxims, however, could 
-have been discovered by a human being but are much easier to reach with computational tools. Computational tools prompt philosophers 
+have been discovered by a human being but are much easier to reach with computational tools. I do not 
+argue that computational ethics uncovers philosophical insights that humans are always incapable 
+of reaching. Computational tools prompt philosophers 
 to ask new questions that lead to insights, and can thus serve as another tool in a philosopher's arsenal, like a 
@@
 
-Computational ethics is at its infancy. The use of theorem provers in mathematics is only now beginning 
-to make headway \citep{buzzardvideo}, even though theorem provers were first invented in the 1960's \citep{historyofITP}. 
+Computational ethics is at its infancy. Theorem provers are only now beginning to make headway in 
+mathematics \citep{buzzardvideo}, even though theorem provers were first invented in the 1960's \citep{historyofITP}. 
 In contrast, the first attempts to use theorem provers to automate deontic logic occurred in the last
-few years. The 
-fact that this nascent technology is already helping humans reach non-trivial ethical conclusions 
+few years. The fact that this nascent technology is already helping humans reach non-trivial ethical conclusions 
 is reason to, at the very least, entertain the possibility of a future where computational ethics 
@@
 artificial agents and philosophers respectively. This raises a natural question: can automated
-ethics guide ordinary human beings, not just academic philosophers, as we navigate the world and face ethical
-dilemmas? Some may hope (or worry) that automated ethics could render ethical reasoning obsolete. In 
+ethics guide all human beings, not just academic philosophers, as we navigate the world and face ethical
+dilemmas? Some may hope (or worry) that automated ethics could render everyday ethical reasoning obsolete. In 
 this section, I argue that while computers should not replace human ethical reasoning entirely,
@@
 the user's perspective. Just as computational ethics can serve as a tool for academic philosophers to 
-ask new questions and achieve greater precision, it can do the same for ordinary human beings navigating
-the world. Moreover, it also offers another way for the general public to access professional philosophy
+ask new questions and achieve greater precision, it can do the same for all human beings navigating
+the world. Moreover, it also offers another way for the general public to access professional philosophy's
 insights, and thus carries potential to improve our everyday reasoning.%
@@
 the choices that an agent is faced with. As I argue in Section \ref{AIethics}, determining this potential maxim is a challenge for both human
-and automated reasoners. Kant even claims that the difficulty of determining an agent's potential maxim, which is their
-own, subjective understanding of their principle of action, is a reason that we may never be able 
+and automated reasoners. Kant claims that determining an agent's potential maxim is so difficult because a maxim is their
+prsonal understanding of their principle of action, and so we may never be able 
 to know if the morally worthy action has been performed \cite[345]{oneilluniversallaws}. Reasoners are faced with
@@
 Understanding the categorical imperative test as a reminder
-instead of a derivation tool also explains the response to the tailor objection presented in Section \ref{AIethics}, that the FUL cannot 
+instead of a derivation tool also explains the response to the tailoring objection presented in Section \ref{AIethics}, that the FUL cannot 
 handle bad-faith attempts to generate false positives or negatives. The test only returns the right 
@@
 \begin{isamarkuptext}%
-Under Tafani's understanding of the categorical imperative, not only is automated moral reasoning
+Under Tafani's and O'Neill's understandings of the categorical imperative, not only is automated moral reasoning
 possible, but the challenge of creating an input parser or automatically formulating a maxim becomes 
@@
 universalizability test could not only match human ethical reasoning but could perhaps surpass it
-by double checking the moral intuitions that we take for granted. A computer with no common sense or prior knowledge
+by double-checking the moral intuitions that we take for granted. A computer with no common sense or prior knowledge
 may be unable to reason using the categorical imperative, but one equipped with some prior knowledge
@@
 In this paper, I use a top-down approach to formalize Kantian ethics. There is a long line of work 
-automating other ethical theories, like consequentialism \citep{util1, util2} or particularism 
+automating other ethical theories, like consequentialism \citep{util2, util1} or particularism 
 \citep{particularism1, particularism2}. I choose to implement Kantian ethics because, as argued in 
@@
 traditions. Kantian ethics is a deontological, or rule based ethic, and there is prior work 
-implementing other deontological theories \citep{dde, deon1, deon2}.
+implementing other deontological theories \citep{deon1, deon2, dde}.
 
@@
 foundational work with the LogiKEy framework for machine ethics, which includes their implementation 
-of DDL in Isabelle \citep{BFP, logikey}. The LogiKEy project has been used to study metaphysics 
+of DDL in Isabelle \citep{logikey, BFP}. The LogiKEy project has been used to study metaphysics 
 \citep{godel, metaphysics1}, law \citep{constitution}, and ethics \citep{gewirth}, but not 
@@
 %:%51=23%:%
-%:%60=25%:%
-%:%72=27%:%
-%:%73=28%:%
-%:%74=29%:%
-%:%75=30%:%
-%:%76=31%:%
-%:%77=32%:%
-%:%78=33%:%
-%:%79=34%:%
-%:%80=35%:%
-%:%81=36%:%
-%:%82=37%:%
-%:%83=38%:%
-%:%84=39%:%
-%:%85=40%:%
-%:%86=41%:%
-%:%87=42%:%
-%:%88=43%:%
-%:%89=44%:%
-%:%90=45%:%
-%:%91=46%:%
-%:%92=47%:%
-%:%93=48%:%
-%:%94=49%:%
-%:%95=50%:%
-%:%96=51%:%
-%:%97=52%:%
-%:%98=53%:%
-%:%99=54%:%
-%:%100=55%:%
-%:%101=56%:%
-%:%102=57%:%
-%:%103=58%:%
-%:%104=59%:%
-%:%105=60%:%
-%:%106=61%:%
-%:%107=62%:%
-%:%108=63%:%
-%:%109=64%:%
-%:%110=65%:%
-%:%111=66%:%
-%:%112=67%:%
-%:%113=68%:%
-%:%114=69%:%
-%:%115=70%:%
-%:%116=71%:%
-%:%117=72%:%
-%:%118=73%:%
-%:%119=74%:%
-%:%120=75%:%
-%:%121=76%:%
-%:%122=77%:%
-%:%123=78%:%
-%:%124=79%:%
-%:%125=80%:%
-%:%126=81%:%
-%:%127=82%:%
-%:%128=83%:%
-%:%129=84%:%
-%:%130=85%:%
-%:%131=86%:%
-%:%132=87%:%
-%:%133=88%:%
-%:%134=89%:%
-%:%135=90%:%
-%:%136=91%:%
-%:%137=92%:%
-%:%138=93%:%
-%:%139=94%:%
-%:%140=95%:%
-%:%141=96%:%
-%:%142=97%:%
-%:%143=98%:%
-%:%144=99%:%
-%:%145=100%:%
-%:%146=101%:%
-%:%147=102%:%
-%:%148=103%:%
-%:%149=104%:%
-%:%150=105%:%
-%:%151=106%:%
-%:%152=107%:%
-%:%153=108%:%
-%:%154=109%:%
-%:%155=110%:%
-%:%156=111%:%
-%:%157=112%:%
-%:%158=113%:%
-%:%159=114%:%
-%:%160=115%:%
-%:%161=116%:%
-%:%162=117%:%
-%:%163=118%:%
-%:%164=119%:%
-%:%165=120%:%
-%:%166=121%:%
-%:%167=122%:%
-%:%168=123%:%
-%:%169=124%:%
-%:%170=125%:%
-%:%171=126%:%
-%:%172=127%:%
-%:%173=128%:%
-%:%174=129%:%
-%:%175=130%:%
-%:%176=131%:%
-%:%177=132%:%
-%:%178=133%:%
-%:%179=134%:%
-%:%180=135%:%
-%:%181=136%:%
-%:%182=137%:%
-%:%183=138%:%
-%:%184=139%:%
-%:%185=140%:%
-%:%186=141%:%
-%:%187=142%:%
-%:%188=143%:%
-%:%189=144%:%
-%:%190=145%:%
-%:%191=146%:%
-%:%192=147%:%
-%:%193=148%:%
-%:%194=149%:%
-%:%195=150%:%
-%:%196=151%:%
-%:%197=152%:%
-%:%198=153%:%
-%:%207=155%:%
-%:%219=157%:%
-%:%220=158%:%
-%:%221=159%:%
-%:%222=160%:%
-%:%223=161%:%
-%:%224=162%:%
-%:%225=163%:%
-%:%226=164%:%
-%:%227=165%:%
-%:%228=166%:%
-%:%229=167%:%
-%:%238=169%:%
-%:%250=171%:%
-%:%251=172%:%
-%:%252=173%:%
-%:%253=174%:%
-%:%254=175%:%
-%:%255=176%:%
-%:%256=177%:%
-%:%257=178%:%
-%:%258=179%:%
-%:%259=180%:%
-%:%260=181%:%
-%:%261=182%:%
-%:%262=183%:%
-%:%263=184%:%
-%:%264=185%:%
-%:%265=186%:%
-%:%266=187%:%
-%:%267=188%:%
-%:%268=189%:%
-%:%269=190%:%
-%:%270=191%:%
-%:%271=192%:%
-%:%272=193%:%
-%:%273=194%:%
-%:%274=195%:%
-%:%275=196%:%
-%:%276=197%:%
-%:%277=198%:%
-%:%278=199%:%
-%:%279=200%:%
-%:%280=201%:%
-%:%281=202%:%
-%:%282=203%:%
-%:%283=204%:%
-%:%284=205%:%
-%:%285=206%:%
-%:%286=207%:%
-%:%287=208%:%
-%:%288=209%:%
-%:%289=210%:%
-%:%290=211%:%
-%:%291=212%:%
-%:%292=213%:%
-%:%293=214%:%
-%:%294=215%:%
-%:%295=216%:%
-%:%296=217%:%
-%:%297=218%:%
-%:%298=219%:%
-%:%299=220%:%
-%:%300=221%:%
-%:%301=222%:%
-%:%302=223%:%
-%:%303=224%:%
-%:%304=225%:%
-%:%305=226%:%
-%:%306=227%:%
-%:%307=228%:%
-%:%308=229%:%
-%:%309=230%:%
-%:%310=231%:%
-%:%311=232%:%
-%:%312=233%:%
-%:%313=234%:%
-%:%314=235%:%
-%:%315=236%:%
-%:%316=237%:%
-%:%317=238%:%
-%:%318=239%:%
-%:%319=240%:%
-%:%320=241%:%
-%:%321=242%:%
-%:%322=243%:%
-%:%323=244%:%
-%:%324=245%:%
-%:%325=246%:%
-%:%326=247%:%
-%:%327=248%:%
-%:%328=249%:%
-%:%329=250%:%
-%:%330=251%:%
-%:%331=252%:%
-%:%332=253%:%
-%:%333=254%:%
-%:%334=255%:%
-%:%335=256%:%
-%:%336=257%:%
-%:%337=258%:%
-%:%338=259%:%
-%:%339=260%:%
-%:%340=261%:%
-%:%341=262%:%
-%:%342=263%:%
-%:%343=264%:%
-%:%344=265%:%
-%:%345=266%:%
-%:%346=267%:%
-%:%347=268%:%
-%:%348=269%:%
-%:%349=270%:%
-%:%350=271%:%
-%:%351=272%:%
-%:%352=273%:%
-%:%353=274%:%
-%:%354=275%:%
-%:%355=276%:%
-%:%356=277%:%
-%:%357=278%:%
-%:%358=279%:%
-%:%359=280%:%
-%:%360=281%:%
-%:%361=282%:%
-%:%362=283%:%
-%:%363=284%:%
-%:%364=285%:%
-%:%365=286%:%
-%:%366=287%:%
-%:%367=288%:%
-%:%368=289%:%
-%:%369=290%:%
-%:%370=291%:%
-%:%371=292%:%
-%:%372=293%:%
-%:%373=294%:%
-%:%374=295%:%
-%:%375=296%:%
-%:%376=297%:%
-%:%377=298%:%
-%:%378=299%:%
-%:%379=300%:%
-%:%380=301%:%
-%:%381=302%:%
-%:%382=303%:%
-%:%383=304%:%
-%:%384=305%:%
-%:%385=306%:%
-%:%386=307%:%
-%:%387=308%:%
-%:%388=309%:%
-%:%389=310%:%
-%:%390=311%:%
-%:%391=312%:%
-%:%392=313%:%
-%:%393=314%:%
-%:%394=315%:%
-%:%395=316%:%
-%:%396=317%:%
-%:%397=318%:%
-%:%398=319%:%
-%:%399=320%:%
-%:%400=321%:%
-%:%401=322%:%
-%:%402=323%:%
-%:%403=324%:%
-%:%404=325%:%
-%:%405=326%:%
-%:%406=327%:%
-%:%407=328%:%
-%:%408=329%:%
-%:%409=330%:%
-%:%410=331%:%
-%:%411=332%:%
-%:%412=333%:%
-%:%413=334%:%
-%:%414=335%:%
-%:%415=336%:%
-%:%416=337%:%
-%:%417=338%:%
-%:%418=339%:%
-%:%419=340%:%
-%:%420=341%:%
-%:%421=342%:%
-%:%422=343%:%
-%:%423=344%:%
-%:%424=345%:%
-%:%425=346%:%
-%:%426=347%:%
-%:%427=348%:%
-%:%428=349%:%
-%:%429=350%:%
-%:%430=351%:%
-%:%431=352%:%
-%:%432=353%:%
-%:%433=354%:%
-%:%434=355%:%
-%:%435=356%:%
-%:%436=357%:%
-%:%437=358%:%
-%:%438=359%:%
-%:%439=360%:%
-%:%440=361%:%
-%:%441=362%:%
-%:%442=363%:%
-%:%443=364%:%
-%:%452=367%:%
-%:%464=369%:%
-%:%465=370%:%
-%:%466=371%:%
-%:%467=372%:%
-%:%468=373%:%
-%:%469=374%:%
-%:%470=375%:%
-%:%471=376%:%
-%:%472=377%:%
-%:%473=378%:%
-%:%474=379%:%
-%:%475=380%:%
-%:%476=381%:%
-%:%477=382%:%
-%:%478=383%:%
-%:%479=384%:%
-%:%480=385%:%
-%:%481=386%:%
-%:%482=387%:%
-%:%483=388%:%
-%:%484=389%:%
-%:%485=390%:%
-%:%486=391%:%
-%:%487=392%:%
-%:%488=393%:%
-%:%489=394%:%
-%:%490=395%:%
-%:%491=396%:%
-%:%492=397%:%
-%:%493=398%:%
-%:%494=399%:%
-%:%495=400%:%
-%:%496=401%:%
-%:%497=402%:%
-%:%498=403%:%
-%:%499=404%:%
-%:%500=405%:%
-%:%501=406%:%
-%:%502=407%:%
-%:%503=408%:%
-%:%504=409%:%
-%:%505=410%:%
-%:%506=411%:%
-%:%507=412%:%
-%:%508=413%:%
-%:%509=414%:%
-%:%510=415%:%
-%:%511=416%:%
-%:%512=417%:%
-%:%513=418%:%
-%:%514=419%:%
-%:%515=420%:%
-%:%516=421%:%
-%:%517=422%:%
-%:%518=423%:%
-%:%519=424%:%
-%:%520=425%:%
-%:%521=426%:%
-%:%522=427%:%
-%:%523=428%:%
-%:%524=429%:%
-%:%525=430%:%
-%:%526=431%:%
-%:%527=432%:%
-%:%528=433%:%
-%:%529=434%:%
-%:%538=436%:%
-%:%550=438%:%
-%:%551=439%:%
-%:%552=440%:%
-%:%553=441%:%
-%:%554=442%:%
-%:%555=443%:%
-%:%556=444%:%
-%:%557=445%:%
-%:%558=446%:%
-%:%559=447%:%
-%:%560=448%:%
-%:%561=449%:%
-%:%562=450%:%
-%:%563=451%:%
-%:%564=452%:%
-%:%565=453%:%
-%:%566=454%:%
-%:%567=455%:%
-%:%568=456%:%
-%:%569=457%:%
-%:%570=458%:%
-%:%571=459%:%
-%:%572=460%:%
-%:%573=461%:%
-%:%574=462%:%
-%:%575=463%:%
-%:%576=464%:%
-%:%577=465%:%
-%:%578=466%:%
-%:%579=467%:%
-%:%580=468%:%
-%:%581=469%:%
-%:%582=470%:%
-%:%583=471%:%
-%:%584=472%:%
-%:%585=473%:%
-%:%586=474%:%
-%:%587=475%:%
-%:%588=476%:%
-%:%589=477%:%
-%:%590=478%:%
-%:%591=479%:%
-%:%592=480%:%
-%:%593=481%:%
-%:%594=482%:%
-%:%595=483%:%
-%:%596=484%:%
-%:%597=485%:%
-%:%598=486%:%
-%:%599=487%:%
-%:%600=488%:%
-%:%601=489%:%
-%:%602=490%:%
-%:%603=491%:%
-%:%604=492%:%
-%:%605=493%:%
-%:%606=494%:%
-%:%607=495%:%
-%:%608=496%:%
-%:%609=497%:%
-%:%610=498%:%
-%:%611=499%:%
-%:%612=500%:%
-%:%613=501%:%
-%:%614=502%:%
-%:%615=503%:%
-%:%616=504%:%
-%:%617=505%:%
-%:%618=506%:%
-%:%619=507%:%
-%:%620=508%:%
-%:%621=509%:%
-%:%622=510%:%
-%:%623=511%:%
-%:%624=512%:%
-%:%625=513%:%
-%:%626=514%:%
-%:%635=517%:%
-%:%647=520%:%
-%:%648=521%:%
-%:%649=522%:%
-%:%650=523%:%
-%:%651=524%:%
-%:%652=525%:%
-%:%653=526%:%
-%:%654=527%:%
-%:%655=528%:%
-%:%656=529%:%
-%:%657=530%:%
-%:%658=531%:%
-%:%659=532%:%
-%:%660=533%:%
-%:%661=534%:%
-%:%662=535%:%
-%:%663=536%:%
-%:%664=537%:%
-%:%665=538%:%
-%:%666=539%:%
-%:%667=540%:%
-%:%668=541%:%
-%:%669=542%:%
-%:%670=543%:%
-%:%671=544%:%
-%:%672=545%:%
-%:%673=546%:%
-%:%674=547%:%
-%:%675=548%:%
-%:%676=549%:%
-%:%677=550%:%
-%:%678=551%:%
-%:%679=552%:%
-%:%680=553%:%
-%:%681=554%:%
-%:%682=555%:%
-%:%683=556%:%
-%:%684=557%:%
-%:%685=558%:%
-%:%686=559%:%
-%:%687=560%:%
-%:%688=561%:%
-%:%689=562%:%
-%:%690=563%:%
-%:%691=564%:%
-%:%692=565%:%
-%:%693=566%:%
-%:%694=567%:%
-%:%695=568%:%
-%:%696=569%:%
-%:%697=570%:%
-%:%698=571%:%
-%:%699=572%:%
-%:%700=573%:%
-%:%701=574%:%
-%:%702=575%:%
-%:%703=576%:%
-%:%704=577%:%
-%:%705=578%:%
-%:%706=579%:%
-%:%707=580%:%
-%:%708=581%:%
-%:%709=582%:%
-%:%710=583%:%
-%:%711=584%:%
-%:%712=585%:%
-%:%713=586%:%
-%:%714=587%:%
-%:%715=588%:%
-%:%716=589%:%
-%:%717=590%:%
-%:%718=591%:%
-%:%719=592%:%
-%:%720=593%:%
-%:%721=594%:%
-%:%722=595%:%
-%:%723=596%:%
-%:%724=597%:%
-%:%725=598%:%
-%:%726=599%:%
-%:%727=600%:%
-%:%728=601%:%
-%:%729=602%:%
-%:%730=603%:%
-%:%731=604%:%
-%:%732=605%:%
-%:%733=606%:%
-%:%734=607%:%
-%:%735=608%:%
-%:%736=609%:%
-%:%737=610%:%
-%:%738=611%:%
-%:%739=612%:%
-%:%740=613%:%
-%:%741=614%:%
-%:%742=615%:%
-%:%743=616%:%
-%:%744=617%:%
-%:%745=618%:%
-%:%746=619%:%
-%:%747=620%:%
-%:%748=621%:%
-%:%749=622%:%
-%:%750=623%:%
-%:%751=624%:%
-%:%752=625%:%
-%:%753=626%:%
-%:%754=627%:%
-%:%755=628%:%
-%:%756=629%:%
-%:%757=630%:%
-%:%758=631%:%
-%:%759=632%:%
-%:%760=633%:%
-%:%761=634%:%
-%:%762=635%:%
-%:%763=636%:%
-%:%764=637%:%
-%:%765=638%:%
-%:%766=639%:%
-%:%769=641%:%
-%:%770=642%:%
-%:%771=643%:%
-%:%772=644%:%
-%:%773=645%:%
-%:%774=646%:%
-%:%777=647%:%
-%:%778=648%:%
-%:%779=649%:%
-%:%780=650%:%
-%:%781=651%:%
-%:%782=652%:%
-%:%783=653%:%
-%:%784=654%:%
-%:%785=655%:%
-%:%786=656%:%
-%:%787=657%:%
-%:%788=658%:%
-%:%789=659%:%
-%:%790=660%:%
-%:%791=661%:%
-%:%792=662%:%
-%:%801=666%:%
-%:%813=668%:%
-%:%814=669%:%
-%:%815=670%:%
-%:%816=671%:%
-%:%817=672%:%
-%:%818=673%:%
-%:%819=674%:%
-%:%820=675%:%
-%:%821=676%:%
-%:%822=677%:%
-%:%823=678%:%
-%:%824=679%:%
-%:%825=680%:%
-%:%826=681%:%
-%:%827=682%:%
-%:%828=683%:%
-%:%829=684%:%
-%:%830=685%:%
-%:%831=686%:%
-%:%832=687%:%
-%:%833=688%:%
-%:%834=689%:%
-%:%835=690%:%
-%:%836=691%:%
-%:%837=692%:%
-%:%838=693%:%
-%:%839=694%:%
-%:%840=695%:%
-%:%841=696%:%
-%:%842=697%:%
-%:%843=698%:%
-%:%844=699%:%
-%:%845=700%:%
-%:%846=701%:%
-%:%847=702%:%
-%:%848=703%:%
-%:%849=704%:%
-%:%850=705%:%
-%:%851=706%:%
-%:%852=707%:%
-%:%853=708%:%
-%:%854=709%:%
-%:%855=710%:%
-%:%856=711%:%
-%:%857=712%:%
-%:%858=713%:%
-%:%859=714%:%
-%:%860=715%:%
-%:%861=716%:%
-%:%862=717%:%
-%:%863=718%:%
-%:%864=719%:%
-%:%873=721%:%
-%:%885=723%:%
-%:%886=724%:%
-%:%887=725%:%
-%:%888=726%:%
-%:%889=727%:%
-%:%890=728%:%
-%:%891=729%:%
-%:%892=730%:%
-%:%893=731%:%
-%:%894=732%:%
-%:%895=733%:%
-%:%896=734%:%
-%:%897=735%:%
-%:%898=736%:%
-%:%899=737%:%
-%:%900=738%:%
-%:%901=739%:%
-%:%902=740%:%
-%:%903=741%:%
-%:%904=742%:%
-%:%905=743%:%
-%:%906=744%:%
-%:%907=745%:%
-%:%908=746%:%
-%:%909=747%:%
-%:%910=748%:%
-%:%911=749%:%
-%:%912=750%:%
-%:%913=751%:%
-%:%914=752%:%
-%:%915=753%:%
-%:%916=754%:%
-%:%917=755%:%
-%:%918=756%:%
-%:%919=757%:%
-%:%920=758%:%
-%:%921=759%:%
-%:%922=760%:%
-%:%923=761%:%
+%:%52=24%:%
+%:%61=26%:%
+%:%73=27%:%
+%:%74=28%:%
+%:%75=29%:%
+%:%76=30%:%
+%:%77=31%:%
+%:%78=32%:%
+%:%79=33%:%
+%:%80=34%:%
+%:%81=35%:%
+%:%82=36%:%
+%:%83=37%:%
+%:%84=38%:%
+%:%85=39%:%
+%:%86=40%:%
+%:%87=41%:%
+%:%88=42%:%
+%:%89=43%:%
+%:%90=44%:%
+%:%91=45%:%
+%:%92=46%:%
+%:%93=47%:%
+%:%94=48%:%
+%:%95=49%:%
+%:%96=50%:%
+%:%97=51%:%
+%:%98=52%:%
+%:%99=53%:%
+%:%100=54%:%
+%:%101=55%:%
+%:%102=56%:%
+%:%103=57%:%
+%:%104=58%:%
+%:%105=59%:%
+%:%106=60%:%
+%:%107=61%:%
+%:%108=62%:%
+%:%109=63%:%
+%:%110=64%:%
+%:%111=65%:%
+%:%112=66%:%
+%:%113=67%:%
+%:%114=68%:%
+%:%115=69%:%
+%:%116=70%:%
+%:%117=71%:%
+%:%118=72%:%
+%:%119=73%:%
+%:%120=74%:%
+%:%121=75%:%
+%:%122=76%:%
+%:%123=77%:%
+%:%124=78%:%
+%:%125=79%:%
+%:%126=80%:%
+%:%127=81%:%
+%:%128=82%:%
+%:%129=83%:%
+%:%130=84%:%
+%:%131=85%:%
+%:%132=86%:%
+%:%133=87%:%
+%:%134=88%:%
+%:%135=89%:%
+%:%136=90%:%
+%:%137=91%:%
+%:%138=92%:%
+%:%139=93%:%
+%:%140=94%:%
+%:%141=95%:%
+%:%142=96%:%
+%:%143=97%:%
+%:%144=98%:%
+%:%145=99%:%
+%:%146=100%:%
+%:%147=101%:%
+%:%148=102%:%
+%:%149=103%:%
+%:%150=104%:%
+%:%151=105%:%
+%:%152=106%:%
+%:%153=107%:%
+%:%154=108%:%
+%:%155=109%:%
+%:%156=110%:%
+%:%157=111%:%
+%:%158=112%:%
+%:%159=113%:%
+%:%160=114%:%
+%:%161=115%:%
+%:%162=116%:%
+%:%163=117%:%
+%:%164=118%:%
+%:%165=119%:%
+%:%166=120%:%
+%:%167=121%:%
+%:%168=122%:%
+%:%169=123%:%
+%:%170=124%:%
+%:%171=125%:%
+%:%172=126%:%
+%:%173=127%:%
+%:%174=128%:%
+%:%175=129%:%
+%:%176=130%:%
+%:%177=131%:%
+%:%178=132%:%
+%:%179=133%:%
+%:%180=134%:%
+%:%181=135%:%
+%:%182=136%:%
+%:%183=137%:%
+%:%184=138%:%
+%:%185=139%:%
+%:%186=140%:%
+%:%187=141%:%
+%:%188=142%:%
+%:%189=143%:%
+%:%190=144%:%
+%:%191=145%:%
+%:%192=146%:%
+%:%193=147%:%
+%:%202=149%:%
+%:%214=151%:%
+%:%215=152%:%
+%:%216=153%:%
+%:%217=154%:%
+%:%218=155%:%
+%:%219=156%:%
+%:%220=157%:%
+%:%221=158%:%
+%:%222=159%:%
+%:%223=160%:%
+%:%224=161%:%
+%:%233=163%:%
+%:%245=165%:%
+%:%246=166%:%
+%:%247=167%:%
+%:%248=168%:%
+%:%249=169%:%
+%:%250=170%:%
+%:%251=171%:%
+%:%252=172%:%
+%:%253=173%:%
+%:%254=174%:%
+%:%255=175%:%
+%:%256=176%:%
+%:%257=177%:%
+%:%258=178%:%
+%:%259=179%:%
+%:%260=180%:%
+%:%261=181%:%
+%:%262=182%:%
+%:%263=183%:%
+%:%264=184%:%
+%:%265=185%:%
+%:%266=186%:%
+%:%267=187%:%
+%:%268=188%:%
+%:%269=189%:%
+%:%270=190%:%
+%:%271=191%:%
+%:%272=192%:%
+%:%273=193%:%
+%:%274=194%:%
+%:%275=195%:%
+%:%276=196%:%
+%:%277=197%:%
+%:%278=198%:%
+%:%279=199%:%
+%:%280=200%:%
+%:%281=201%:%
+%:%282=202%:%
+%:%283=203%:%
+%:%284=204%:%
+%:%285=205%:%
+%:%286=206%:%
+%:%287=207%:%
+%:%288=208%:%
+%:%289=209%:%
+%:%290=210%:%
+%:%291=211%:%
+%:%292=212%:%
+%:%293=213%:%
+%:%294=214%:%
+%:%295=215%:%
+%:%296=216%:%
+%:%297=217%:%
+%:%298=218%:%
+%:%299=219%:%
+%:%300=220%:%
+%:%301=221%:%
+%:%302=222%:%
+%:%303=223%:%
+%:%304=224%:%
+%:%305=225%:%
+%:%306=226%:%
+%:%307=227%:%
+%:%308=228%:%
+%:%309=229%:%
+%:%310=230%:%
+%:%311=231%:%
+%:%312=232%:%
+%:%313=233%:%
+%:%314=234%:%
+%:%315=235%:%
+%:%316=236%:%
+%:%317=237%:%
+%:%318=238%:%
+%:%319=239%:%
+%:%320=240%:%
+%:%321=241%:%
+%:%322=242%:%
+%:%323=243%:%
+%:%324=244%:%
+%:%325=245%:%
+%:%326=246%:%
+%:%327=247%:%
+%:%328=248%:%
+%:%329=249%:%
+%:%330=250%:%
+%:%331=251%:%
+%:%332=252%:%
+%:%333=253%:%
+%:%334=254%:%
+%:%335=255%:%
+%:%336=256%:%
+%:%337=257%:%
+%:%338=258%:%
+%:%339=259%:%
+%:%340=260%:%
+%:%341=261%:%
+%:%342=262%:%
+%:%343=263%:%
+%:%344=264%:%
+%:%345=265%:%
+%:%346=266%:%
+%:%347=267%:%
+%:%348=268%:%
+%:%349=269%:%
+%:%350=270%:%
+%:%351=271%:%
+%:%352=272%:%
+%:%353=273%:%
+%:%354=274%:%
+%:%355=275%:%
+%:%356=276%:%
+%:%357=277%:%
+%:%358=278%:%
+%:%359=279%:%
+%:%360=280%:%
+%:%361=281%:%
+%:%362=282%:%
+%:%363=283%:%
+%:%364=284%:%
+%:%365=285%:%
+%:%366=286%:%
+%:%367=287%:%
+%:%368=288%:%
+%:%369=289%:%
+%:%370=290%:%
+%:%371=291%:%
+%:%372=292%:%
+%:%373=293%:%
+%:%374=294%:%
+%:%375=295%:%
+%:%376=296%:%
+%:%377=297%:%
+%:%378=298%:%
+%:%379=299%:%
+%:%380=300%:%
+%:%381=301%:%
+%:%382=302%:%
+%:%383=303%:%
+%:%384=304%:%
+%:%385=305%:%
+%:%386=306%:%
+%:%387=307%:%
+%:%388=308%:%
+%:%389=309%:%
+%:%390=310%:%
+%:%391=311%:%
+%:%392=312%:%
+%:%393=313%:%
+%:%394=314%:%
+%:%395=315%:%
+%:%396=316%:%
+%:%397=317%:%
+%:%398=318%:%
+%:%399=319%:%
+%:%400=320%:%
+%:%401=321%:%
+%:%402=322%:%
+%:%403=323%:%
+%:%404=324%:%
+%:%405=325%:%
+%:%406=326%:%
+%:%407=327%:%
+%:%408=328%:%
+%:%409=329%:%
+%:%410=330%:%
+%:%411=331%:%
+%:%412=332%:%
+%:%413=333%:%
+%:%414=334%:%
+%:%415=335%:%
+%:%416=336%:%
+%:%417=337%:%
+%:%418=338%:%
+%:%419=339%:%
+%:%420=340%:%
+%:%421=341%:%
+%:%422=342%:%
+%:%423=343%:%
+%:%424=344%:%
+%:%425=345%:%
+%:%426=346%:%
+%:%427=347%:%
+%:%428=348%:%
+%:%429=349%:%
+%:%430=350%:%
+%:%431=351%:%
+%:%432=352%:%
+%:%433=353%:%
+%:%434=354%:%
+%:%435=355%:%
+%:%436=356%:%
+%:%437=357%:%
+%:%438=358%:%
+%:%447=361%:%
+%:%459=363%:%
+%:%460=364%:%
+%:%461=365%:%
+%:%462=366%:%
+%:%463=367%:%
+%:%464=368%:%
+%:%465=369%:%
+%:%466=370%:%
+%:%467=371%:%
+%:%468=372%:%
+%:%469=373%:%
+%:%470=374%:%
+%:%471=375%:%
+%:%472=376%:%
+%:%473=377%:%
+%:%474=378%:%
+%:%475=379%:%
+%:%476=380%:%
+%:%477=381%:%
+%:%478=382%:%
+%:%479=383%:%
+%:%480=384%:%
+%:%481=385%:%
+%:%482=386%:%
+%:%483=387%:%
+%:%484=388%:%
+%:%485=389%:%
+%:%486=390%:%
+%:%487=391%:%
+%:%488=392%:%
+%:%489=393%:%
+%:%490=394%:%
+%:%491=395%:%
+%:%492=396%:%
+%:%493=397%:%
+%:%494=398%:%
+%:%495=399%:%
+%:%496=400%:%
+%:%497=401%:%
+%:%498=402%:%
+%:%499=403%:%
+%:%500=404%:%
+%:%501=405%:%
+%:%502=406%:%
+%:%503=407%:%
+%:%504=408%:%
+%:%505=409%:%
+%:%506=410%:%
+%:%507=411%:%
+%:%508=412%:%
+%:%509=413%:%
+%:%510=414%:%
+%:%511=415%:%
+%:%512=416%:%
+%:%513=417%:%
+%:%514=418%:%
+%:%515=419%:%
+%:%516=420%:%
+%:%517=421%:%
+%:%518=422%:%
+%:%519=423%:%
+%:%520=424%:%
+%:%521=425%:%
+%:%522=426%:%
+%:%523=427%:%
+%:%524=428%:%
+%:%533=430%:%
+%:%545=432%:%
+%:%546=433%:%
+%:%547=434%:%
+%:%548=435%:%
+%:%549=436%:%
+%:%550=437%:%
+%:%551=438%:%
+%:%552=439%:%
+%:%553=440%:%
+%:%554=441%:%
+%:%555=442%:%
+%:%556=443%:%
+%:%557=444%:%
+%:%558=445%:%
+%:%559=446%:%
+%:%560=447%:%
+%:%561=448%:%
+%:%562=449%:%
+%:%563=450%:%
+%:%564=451%:%
+%:%565=452%:%
+%:%566=453%:%
+%:%567=454%:%
+%:%568=455%:%
+%:%569=456%:%
+%:%570=457%:%
+%:%571=458%:%
+%:%572=459%:%
+%:%573=460%:%
+%:%574=461%:%
+%:%575=462%:%
+%:%576=463%:%
+%:%577=464%:%
+%:%578=465%:%
+%:%579=466%:%
+%:%580=467%:%
+%:%581=468%:%
+%:%582=469%:%
+%:%583=470%:%
+%:%584=471%:%
+%:%585=472%:%
+%:%586=473%:%
+%:%587=474%:%
+%:%588=475%:%
+%:%589=476%:%
+%:%590=477%:%
+%:%591=478%:%
+%:%592=479%:%
+%:%593=480%:%
+%:%594=481%:%
+%:%595=482%:%
+%:%596=483%:%
+%:%597=484%:%
+%:%598=485%:%
+%:%599=486%:%
+%:%600=487%:%
+%:%601=488%:%
+%:%602=489%:%
+%:%603=490%:%
+%:%604=491%:%
+%:%605=492%:%
+%:%606=493%:%
+%:%607=494%:%
+%:%608=495%:%
+%:%609=496%:%
+%:%610=497%:%
+%:%611=498%:%
+%:%612=499%:%
+%:%613=500%:%
+%:%614=501%:%
+%:%615=502%:%
+%:%616=503%:%
+%:%617=504%:%
+%:%618=505%:%
+%:%619=506%:%
+%:%620=507%:%
+%:%621=508%:%
+%:%630=511%:%
+%:%642=514%:%
+%:%643=515%:%
+%:%644=516%:%
+%:%645=517%:%
+%:%646=518%:%
+%:%647=519%:%
+%:%648=520%:%
+%:%649=521%:%
+%:%650=522%:%
+%:%651=523%:%
+%:%652=524%:%
+%:%653=525%:%
+%:%654=526%:%
+%:%655=527%:%
+%:%656=528%:%
+%:%657=529%:%
+%:%658=530%:%
+%:%659=531%:%
+%:%660=532%:%
+%:%661=533%:%
+%:%662=534%:%
+%:%663=535%:%
+%:%664=536%:%
+%:%665=537%:%
+%:%666=538%:%
+%:%667=539%:%
+%:%668=540%:%
+%:%669=541%:%
+%:%670=542%:%
+%:%671=543%:%
+%:%672=544%:%
+%:%673=545%:%
+%:%674=546%:%
+%:%675=547%:%
+%:%676=548%:%
+%:%677=549%:%
+%:%678=550%:%
+%:%679=551%:%
+%:%680=552%:%
+%:%681=553%:%
+%:%682=554%:%
+%:%683=555%:%
+%:%684=556%:%
+%:%685=557%:%
+%:%686=558%:%
+%:%687=559%:%
+%:%688=560%:%
+%:%689=561%:%
+%:%690=562%:%
+%:%691=563%:%
+%:%692=564%:%
+%:%693=565%:%
+%:%694=566%:%
+%:%695=567%:%
+%:%696=568%:%
+%:%697=569%:%
+%:%698=570%:%
+%:%699=571%:%
+%:%700=572%:%
+%:%701=573%:%
+%:%702=574%:%
+%:%703=575%:%
+%:%704=576%:%
+%:%705=577%:%
+%:%706=578%:%
+%:%707=579%:%
+%:%708=580%:%
+%:%709=581%:%
+%:%710=582%:%
+%:%711=583%:%
+%:%712=584%:%
+%:%713=585%:%
+%:%714=586%:%
+%:%715=587%:%
+%:%716=588%:%
+%:%717=589%:%
+%:%718=590%:%
+%:%719=591%:%
+%:%720=592%:%
+%:%721=593%:%
+%:%722=594%:%
+%:%723=595%:%
+%:%724=596%:%
+%:%725=597%:%
+%:%726=598%:%
+%:%727=599%:%
+%:%728=600%:%
+%:%729=601%:%
+%:%730=602%:%
+%:%731=603%:%
+%:%732=604%:%
+%:%733=605%:%
+%:%734=606%:%
+%:%735=607%:%
+%:%736=608%:%
+%:%737=609%:%
+%:%738=610%:%
+%:%739=611%:%
+%:%740=612%:%
+%:%741=613%:%
+%:%742=614%:%
+%:%743=615%:%
+%:%744=616%:%
+%:%745=617%:%
+%:%746=618%:%
+%:%747=619%:%
+%:%748=620%:%
+%:%749=621%:%
+%:%750=622%:%
+%:%751=623%:%
+%:%752=624%:%
+%:%753=625%:%
+%:%754=626%:%
+%:%755=627%:%
+%:%756=628%:%
+%:%757=629%:%
+%:%758=630%:%
+%:%759=631%:%
+%:%760=632%:%
+%:%761=633%:%
+%:%764=635%:%
+%:%765=636%:%
+%:%766=637%:%
+%:%767=638%:%
+%:%768=639%:%
+%:%769=640%:%
+%:%772=641%:%
+%:%773=642%:%
+%:%774=643%:%
+%:%775=644%:%
+%:%776=645%:%
+%:%777=646%:%
+%:%778=647%:%
+%:%779=648%:%
+%:%780=649%:%
+%:%781=650%:%
+%:%782=651%:%
+%:%783=652%:%
+%:%784=653%:%
+%:%785=654%:%
+%:%786=655%:%
+%:%787=656%:%
+%:%796=660%:%
+%:%808=662%:%
+%:%809=663%:%
+%:%810=664%:%
+%:%811=665%:%
+%:%812=666%:%
+%:%813=667%:%
+%:%814=668%:%
+%:%815=669%:%
+%:%816=670%:%
+%:%817=671%:%
+%:%818=672%:%
+%:%819=673%:%
+%:%820=674%:%
+%:%821=675%:%
+%:%822=676%:%
+%:%823=677%:%
+%:%824=678%:%
+%:%825=679%:%
+%:%826=680%:%
+%:%827=681%:%
+%:%828=682%:%
+%:%829=683%:%
+%:%830=684%:%
+%:%831=685%:%
+%:%832=686%:%
+%:%833=687%:%
+%:%834=688%:%
+%:%835=689%:%
+%:%836=690%:%
+%:%837=691%:%
+%:%838=692%:%
+%:%839=693%:%
+%:%840=694%:%
+%:%841=695%:%
+%:%842=696%:%
+%:%843=697%:%
+%:%844=698%:%
+%:%845=699%:%
+%:%846=700%:%
+%:%847=701%:%
+%:%848=702%:%
+%:%849=703%:%
+%:%850=704%:%
+%:%851=705%:%
+%:%852=706%:%
+%:%853=707%:%
+%:%854=708%:%
+%:%855=709%:%
+%:%856=710%:%
+%:%857=711%:%
+%:%858=712%:%
+%:%859=713%:%
+%:%868=715%:%
+%:%880=717%:%
+%:%881=718%:%
+%:%882=719%:%
+%:%883=720%:%
+%:%884=721%:%
+%:%885=722%:%
+%:%886=723%:%
+%:%887=724%:%
+%:%888=725%:%
+%:%889=726%:%
+%:%890=727%:%
+%:%891=728%:%
+%:%892=729%:%
+%:%893=730%:%
+%:%894=731%:%
+%:%895=732%:%
+%:%896=733%:%
+%:%897=734%:%
+%:%898=735%:%
+%:%899=736%:%
+%:%900=737%:%
+%:%901=738%:%
+%:%902=739%:%
+%:%903=740%:%
+%:%904=741%:%
+%:%905=742%:%
+%:%906=743%:%
+%:%907=744%:%
+%:%908=745%:%
+%:%909=746%:%
+%:%910=747%:%
+%:%911=748%:%
+%:%912=749%:%
+%:%913=750%:%
+%:%914=751%:%
+%:%915=752%:%
+%:%916=753%:%
+%:%917=754%:%
+%:%918=755%:%

### 2022-03-22 paper/output/document/appendix.tex
i hate don knuth

@@
 ``In circumstance C, I will do A in order to G because I can will that I and everyone else simultaneously
-will do A in order to G in circumstance C.'' In other words, if Kant is correct in arguing that moral 
-actions must be done from the motive of duty, the affirmative result of the FUL becomes 
-the motive for a moral action.
-
-While Kitcher's conception of a maxim captures Kant's idea of acting for duty's own sake, I will not implement it 
+will do A in order to G in circumstance C.'' If moral actions must be done from the motive of duty, the 
+affirmative result of the FUL becomes the motive for a moral action.
+
+While Kitcher's conception of a maxim captures Kant's idea of acting for duty's own sake, I do not implement it 
 because it is not necessary for putting maxims through the FUL. Kitcher acknowledges that 
-O'Niell's formulation suffices for the universalizability test, but merely argues that it is not the most general form of a maxim.
+O'Neill's formulation suffices for the universalizability test, but argues that it is not the most general form of a maxim.
 In order to pass the maxim through the FUL, it suffices to know the circumstance, act, and goal. The FUL
@@
 which is outside the scope of this project. My work focuses on the universalizability test, but future work that 
-models the process of practical reason may use my implementation of the FUL as a ``library.'' Combined 
+models the process of practical reason may use my implementation of the FUL as a library. Combined 
 with a logic of practical reason, an implementation of the FUL can move from evaluating a maxim to 
@@
 1976 \citep{kroy}. Kroy used Hinktikka's deontic logic to formalize the Formula of Universal Law and
-the Formula of Humanity. I will first import the additional logical tools that Hintikka's logic contains, 
+the Formula of Humanity. I first import the additional logical tools that Hintikka's logic contains, 
 then examine the differences between his logic and DDL, and finally implement 
@@
 \begin{isamarkuptext}%
-Kroy also defines a substitution operator.\footnote{See page 196 in \citet{kroy}.}
-$P (d/e)$ is read in his logic as ``P with e substituted 
-for d.'' DDL has no such notion of substitution, so I will use the more generalized notion of an ``open 
+Kroy also defines a substitution operator \citep[196]{kroy}.
+$P (d/e)$ is read in his logic as ``$P$ with $e$ substituted 
+for $d$.'' DDL has no such notion of substitution, so I will use the more generalized notion of an ``open 
 sentence,'' as I did for my formalization. An open sentence takes as input a subject and returns a 
-complete or ``closed'' DDL formula by binding the free variable in the sentence to the input. For example, 
+closed DDL formula by binding the free variable in the sentence to the input. For example, 
 ``does action'' is an open sentence that can be instantiated with a subject.%
@@
 There is potential for complication because Kroy's original paper uses a different logic than DDL. 
-His custom logic is a slight modification of Hintikka's deontic logic \citep{hintikka}. In this brief interlude, 
+His custom logic is a modification of Hintikka's deontic logic \citep{hintikka}. In this brief interlude, 
 I examine if the semantic properties that Kroy's logic (which I abbreviate to Kr) requires 
@@
 would pass more tests if it were implemented using Hintikka's logic, the logic itself would be less 
-morally plausible than DDL, and would thus remain a worse implementation of automated Kantian ethics.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-Many of the differences between Kr and DDL can be explained by a difference in their semantics. The most 
-faithful interpretation of Kr is that if $A$ is permissible in a context, then 
+morally plausible than DDL, and would thus remain a worse implementation of automated Kantian ethics.
+
+Many of the differences between Kr and DDL can be explained by a difference in their semantics. Kr 
+requires that if $A$ is permissible in a context, then 
 it must be true at some world in that context. Kr operates under the ``deontic alternatives'' or Kripke semantics, 
@@
 \ \ \isakeyword{fixes}\ A\ w\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}P\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}\ w\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymexists}x{\isachardot}\ A{\isacharparenleft}x{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}P\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}\ w\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymexists}w{\isacharprime}{\isachardot}\ A{\isacharparenleft}w{\isacharprime}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
 \ \ \isacommand{nitpick}\isamarkupfalse%
@@
   Free variable:
-    A = ($\lambda x. \_$)($i_1$ := False) \color{black}%
+    A = ($\lambda w'. \_$)($i_1$ := False) \color{black}%
 }%
@@
 DDL uses neighborhood semantics, not the deontic alternatives view, which is why this
- proposition fails in DDL. In DDL, the $ob$ function abstracts away the notion of
- deontic alternatives. Even if one believes that permissible 
-statements should be true at some deontic alternative, it's not clear that permissible statements
- must be realized at some world. This also coheres with our understanding of obligation. There 
-are permissible actions like ``Lavanya buys a red folder'' that might not happen in any universe.
-
-An even stricter version of the semantics that Kr requires is that if something is permissible at a world, 
+ proposition fails in DDL. Moreover, the validity of this proposition is dubious. Even if one believes that permissible 
+statements should be true at some deontic alternative, permissible statements aren't necessarily
+realized at some world. There are permissible actions like ``Lavanya buys a red folder'' that might not 
+happen in any universe.
+
+An even stricter version of Kr's semantics requires that if something is permissible at a world, 
 then it is obligatory at some world. This is a straightforward application of the Kripke semantics. This
@@
 \ \ \isakeyword{fixes}\ A\ w\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}P\ {\isacharbraceleft}A{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymexists}x{\isachardot}\ O\ {\isacharbraceleft}A{\isacharbraceright}\ x{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}P\ {\isacharbraceleft}A{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymexists}w{\isacharprime}{\isachardot}\ O\ {\isacharbraceleft}A{\isacharbraceright}\ w{\isacharprime}{\isacharparenright}{\isachardoublequoteclose}\isanewline
 \ \ \isacommand{nitpick}\isamarkupfalse%
@@
 
-Another implication of the Kripke semantics is that Kr disallows ``vacuously permissible statements.'' In 
-other words, if something is permissible it has to be obligated at some deontically perfect alternative. 
-If we translate this to the language of DDL, we expect that if $A$ is permissible, it is obligated in some 
+Another implication of the Kripke semantics is that Kr disallows ``vacuously permissible statements.'' If 
+something is permissible, it has to be obligated at some deontically perfect alternative. 
+Translating this to the language of DDL, if $A$ is permissible, then it should be obligated in some 
 context.%
@@
 \ \ \isakeyword{fixes}\ A\ w\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}P\ {\isacharbraceleft}A{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymexists}x{\isachardot}\ ob{\isacharparenleft}x{\isacharparenright}{\isacharparenleft}A{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}P\ {\isacharbraceleft}A{\isacharbraceright}\ w\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymexists}w{\isacharprime}{\isachardot}\ ob{\isacharparenleft}w{\isacharprime}{\isacharparenright}{\isacharparenleft}A{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
 \ \ \isacommand{nitpick}\isamarkupfalse%
@@
   Free variable:
-    A = ($\lambda x. \_$)($i_1$ := False) \color{black}%
-}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\begin{isamarkuptext}%
-In order to make this true, we'd have to require that everything is either obligatory or
+    A = ($\lambda w'. \_$)($i_1$ := False) \color{black}%
+}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+In order for this statement to hold, everything must be either obligatory or
 prohibited somewhere, but this makes permissibility impossible, which is clearly undesirable.%
@@
 \begin{isamarkuptext}%
-\noindent \textbf{Kroy's formalization of the FUL \label{sec: kroy_ful}}%
+\noindent \textbf{Kroy's Formalization of the FUL \label{sec: kroy_ful}}%
 \end{isamarkuptext}\isamarkuptrue%
@@
         are due to the differences between Kroy's logic and my logic mentioned in Section \ref{sec:kroy_logical_background}, but some 
-        reveal philosophical problems with Kroy's interpretation of what the formula of universal law means.
+        reveal deep philosophical problems with Kroy's interpretation of what the Formula of Universal Law means.
 
@@
 not obligations universalize across people. This test passes, perhaps trivially, due to the fact that 
-this property is definitionally the basis of Kroy's formalization; his formalization states, intuitively, 
+this property is definitionally the basis of Kroy's formalization; his formalization states
 that obligations must hold across all people.%
@@
 \ obligation{\isacharunderscore}universalizes{\isacharcolon}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}w{\isachardot}\ {\isacharparenleft}{\isasymexists}p{\isachardot}\ O\ {\isacharbraceleft}A\ p{\isacharbraceright}\ w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ O\ {\isacharbraceleft}A\ p{\isacharbraceright}\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
-\ \ \isacommand{nitpick}\isamarkupfalse%
-{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}true{\isacharbrackright}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{oops}\isamarkupfalse%
-%
+\ \ \isakeyword{fixes}\ A{\isacharcolon}{\isacharcolon}os\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymexists}p{\isachardot}\ {\isasymTurnstile}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}{\isacharparenleft}A\ p{\isacharparenright}{\isacharbraceright}{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ {\isasymTurnstile}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}{\isacharparenleft}A\ p{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+\ \ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{proof}\isamarkupfalse%
+\ \isanewline
+\ \ \ \ \isacommand{assume}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymexists}p{\isachardot}\ {\isasymTurnstile}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}{\isacharparenleft}A\ p{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \ \ \isacommand{show}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymforall}p{\isachardot}\ {\isasymTurnstile}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}{\isacharparenleft}A\ p{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \ \ \ \ \isacommand{using}\isamarkupfalse%
+\ FUL\ {\isacartoucheopen}{\isasymexists}p{\isachardot}\ {\isasymTurnstile}\isactrlemph O{\isacharbraceleft}\isactrlemph {\isasymnot}A{\isacharbraceright}\ p{\isacartoucheclose}\ \isacommand{by}\isamarkupfalse%
+\ blast\isanewline
+\ \ \isacommand{qed}\isamarkupfalse%
+\isanewline
+%
+\isamarkupcmt{This proof requires some manual work, but Isabelle completes it.%
+}%
 \endisatagproof
@@
   outline the syllogism that one might $\emph{expect}$ to prove that lying is prohibited and 
-test each component of this syllogism in Isabelle.%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
+test each component of this syllogism in Isabelle.
+
 \begin{enumerate}
@@
         \item At all worlds, there is necessarily someone who doesn't lie. \emph{(Modal dual of (1))}
-        \item If A is permissible for subject p at world w, A is possible for subject p at world w. \emph{(Modified Ought Implies Can)}
-        \item If A is permissible at world w for any person p, it must be possible for everyone to A at w. \emph{(FUL and (3))}
-        \item Lying is impermissible. \emph{(Follows from (4) and (1))} \end{enumerate}%
-\end{isamarkuptext}\isamarkuptrue%
-%
-\begin{isamarkuptext}%
+        \item If $A$ is permissible for subject $p$ at world $w$, $A$ is possible for subject $p$ at world $w$. \emph{(Modified Ought Implies Can)}
+        \item If $A$ is permissible at world $w$ for any person $p$, it must be possible for everyone to $A$ at $w$. \emph{(FUL and (3))}
+        \item Lying is impermissible. \emph{(Follows from (4) and (1))} \end{enumerate}
+
 I now test each step of this syllogism to determine where Kroy's formalize deviates from the
@@
 \endisadelimproof
-\isanewline
 \isacommand{lemma}\isamarkupfalse%
@@
   Free variables:
-    A = ($\lambda x. \_$)($a_1$ := ($\lambda x. \_$)($i_1$ := False))
-    p = $a_1$ $\color{black}$%
+    $A$ = ($\lambda x. \_$)($a_1$ := ($\lambda x. \_$)($i_1$ := False))
+
+    $p$ = $a_1$ $\color{black}$%
 }%
@@
 The above lemma shows that the syllogism fails at Step 3, explaining why the lemma doesn't 
-        hold as expected. Kroy explicitly states\footnote{See footnote 19 on p. 199 of \citet{kroy}} that 
-        Step 3 holds in his logic, so this failure may be explained by this difference in Kr and DDL.
-        However, upon reflection, it is not clear that the statement expressed in Step 3 should actually hold.
+        hold as expected. Kroy explicitly states that 
+        Step 3 holds in his logic, so this failure may be explained by this difference in Kr and DDL \citep[footnote 19, 199]{kroy}.
+        However, upon reflection, it is not clear that Step 3 should actually hold.
         Step 3 states that all permissible actions must be possible, but this implies that impossible
-        actions are not permissible, so they must be prohibited, which seems silly. For example, 
+        actions are not permissible, so they must be prohibited, which is counterintuitive. For example, 
         imagine I make a trip to Target to purchase a folder, and they offer blue and black folders. 
@@
 
-        Neither of these errors are obvious from Kroy's presentation of his formalization of 
-        the categorical imperative. This is another example of the power of computational ethics. Making
-        Kroy's interpretation of the categorical imperative precise demonstrated philosophical problems
+        Neither of these errors are obvious from Kroy's presentation of  
+        the categorical imperative. This is another example of the power of computational ethics. Performing
+        computational tests on a precise version of an interpretation of the FUL demonstrated philosophical problems
         with that interpretation.%
@@
 %:%127=66%:%
-%:%128=67%:%
-%:%137=70%:%
+%:%136=69%:%
+%:%148=71%:%
 %:%149=72%:%
@@
 %:%152=75%:%
-%:%153=76%:%
-%:%162=78%:%
+%:%161=77%:%
+%:%173=79%:%
 %:%174=80%:%
 %:%175=81%:%
-%:%176=82%:%
-%:%178=84%:%
-%:%179=84%:%
-%:%180=84%:%
+%:%177=83%:%
+%:%178=83%:%
+%:%179=83%:%
+%:%182=85%:%
 %:%183=86%:%
@@
 %:%187=90%:%
-%:%188=91%:%
-%:%190=93%:%
-%:%191=93%:%
-%:%193=94%:%
-%:%194=94%:%
+%:%189=92%:%
+%:%190=92%:%
+%:%192=93%:%
+%:%193=93%:%
+%:%195=94%:%
 %:%196=95%:%
-%:%197=96%:%
+%:%199=97%:%
 %:%200=98%:%
@@
 %:%202=100%:%
-%:%203=101%:%
-%:%205=103%:%
+%:%204=102%:%
+%:%205=102%:%
 %:%206=103%:%
 %:%207=104%:%
-%:%208=105%:%
+%:%208=104%:%
 %:%209=105%:%
 %:%210=106%:%
-%:%211=107%:%
+%:%211=106%:%
 %:%212=107%:%
 %:%213=108%:%
-%:%214=109%:%
+%:%214=108%:%
 %:%215=109%:%
-%:%216=110%:%
+%:%217=111%:%
 %:%218=112%:%
 %:%219=113%:%
-%:%220=114%:%
-%:%222=116%:%
+%:%221=115%:%
+%:%222=115%:%
 %:%223=116%:%
 %:%224=117%:%
-%:%225=118%:%
+%:%225=117%:%
 %:%226=118%:%
-%:%227=119%:%
-%:%229=121%:%
+%:%228=120%:%
+%:%232=122%:%
 %:%233=123%:%
@@
 %:%239=129%:%
-%:%243=131%:%
-%:%244=132%:%
-%:%245=133%:%
-%:%246=134%:%
-%:%247=135%:%
-%:%248=136%:%
-%:%249=137%:%
-%:%251=139%:%
-%:%252=139%:%
-%:%253=140%:%
-%:%254=141%:%
-%:%255=142%:%
-%:%256=142%:%
-%:%258=142%:%
+%:%240=130%:%
+%:%241=131%:%
+%:%242=132%:%
+%:%243=133%:%
+%:%244=134%:%
+%:%245=135%:%
+%:%246=136%:%
+%:%248=138%:%
+%:%249=138%:%
+%:%250=139%:%
+%:%251=140%:%
+%:%252=141%:%
+%:%253=141%:%
+%:%255=141%:%
+%:%259=141%:%
+%:%260=141%:%
 %:%262=142%:%
-%:%263=142%:%
-%:%265=143%:%
-%:%266=144%:%
-%:%267=145%:%
-%:%268=146%:%
-%:%278=148%:%
-%:%279=149%:%
-%:%280=150%:%
-%:%281=151%:%
-%:%282=152%:%
-%:%283=153%:%
-%:%284=154%:%
-%:%285=155%:%
-%:%286=156%:%
-%:%287=157%:%
-%:%289=159%:%
-%:%290=159%:%
-%:%291=160%:%
-%:%292=161%:%
-%:%293=162%:%
-%:%294=162%:%
-%:%296=162%:%
+%:%263=143%:%
+%:%264=144%:%
+%:%265=145%:%
+%:%275=147%:%
+%:%276=148%:%
+%:%277=149%:%
+%:%278=150%:%
+%:%279=151%:%
+%:%280=152%:%
+%:%281=153%:%
+%:%282=154%:%
+%:%283=155%:%
+%:%285=157%:%
+%:%286=157%:%
+%:%287=158%:%
+%:%288=159%:%
+%:%289=160%:%
+%:%290=160%:%
+%:%292=160%:%
+%:%296=160%:%
+%:%297=160%:%
+%:%299=161%:%
 %:%300=162%:%
-%:%301=162%:%
-%:%303=163%:%
-%:%304=164%:%
-%:%305=165%:%
-%:%306=166%:%
-%:%316=168%:%
-%:%317=169%:%
-%:%318=170%:%
-%:%319=171%:%
-%:%320=172%:%
-%:%321=173%:%
-%:%322=174%:%
-%:%323=175%:%
-%:%324=176%:%
-%:%326=178%:%
-%:%327=178%:%
-%:%328=179%:%
-%:%329=180%:%
-%:%330=181%:%
-%:%331=181%:%
-%:%333=181%:%
+%:%301=163%:%
+%:%302=164%:%
+%:%312=166%:%
+%:%313=167%:%
+%:%314=168%:%
+%:%315=169%:%
+%:%316=170%:%
+%:%317=171%:%
+%:%318=172%:%
+%:%319=173%:%
+%:%320=174%:%
+%:%322=176%:%
+%:%323=176%:%
+%:%324=177%:%
+%:%325=178%:%
+%:%326=179%:%
+%:%327=179%:%
+%:%329=179%:%
+%:%333=179%:%
+%:%334=179%:%
+%:%336=180%:%
 %:%337=181%:%
-%:%338=181%:%
-%:%340=182%:%
-%:%341=183%:%
-%:%342=184%:%
-%:%343=185%:%
-%:%353=187%:%
-%:%354=188%:%
+%:%338=182%:%
+%:%339=183%:%
+%:%349=185%:%
+%:%350=186%:%
+%:%367=211%:%
 %:%371=213%:%
-%:%375=215%:%
-%:%376=216%:%
-%:%377=217%:%
-%:%378=218%:%
-%:%379=219%:%
+%:%372=214%:%
+%:%373=215%:%
+%:%374=216%:%
+%:%375=217%:%
+%:%377=220%:%
+%:%378=220%:%
+%:%380=221%:%
 %:%381=222%:%
-%:%382=222%:%
-%:%384=223%:%
-%:%385=224%:%
-%:%386=225%:%
-%:%389=227%:%
-%:%390=228%:%
+%:%382=223%:%
+%:%385=225%:%
+%:%386=226%:%
+%:%388=228%:%
+%:%389=228%:%
+%:%390=229%:%
+%:%391=230%:%
 %:%392=230%:%
-%:%393=230%:%
-%:%394=231%:%
-%:%395=232%:%
-%:%396=232%:%
-%:%398=232%:%
+%:%394=230%:%
+%:%398=230%:%
+%:%399=230%:%
+%:%401=231%:%
 %:%402=232%:%
-%:%403=232%:%
-%:%405=233%:%
-%:%406=234%:%
-%:%407=235%:%
-%:%408=236%:%
-%:%409=237%:%
-%:%410=238%:%
-%:%411=239%:%
-%:%412=240%:%
-%:%420=240%:%
-%:%421=241%:%
-%:%422=242%:%
-%:%423=242%:%
-%:%425=244%:%
+%:%403=233%:%
+%:%404=234%:%
+%:%405=235%:%
+%:%406=236%:%
+%:%407=237%:%
+%:%408=238%:%
+%:%416=238%:%
+%:%417=239%:%
+%:%418=240%:%
+%:%419=240%:%
+%:%421=242%:%
+%:%422=243%:%
+%:%424=245%:%
+%:%425=245%:%
 %:%426=245%:%
-%:%428=247%:%
-%:%429=247%:%
-%:%430=247%:%
-%:%432=247%:%
+%:%428=245%:%
+%:%432=245%:%
+%:%433=245%:%
+%:%435=246%:%
 %:%436=247%:%
-%:%437=247%:%
-%:%439=248%:%
-%:%440=249%:%
-%:%441=250%:%
-%:%442=251%:%
-%:%452=253%:%
-%:%453=254%:%
-%:%454=255%:%
-%:%455=256%:%
-%:%464=258%:%
-%:%476=260%:%
-%:%477=261%:%
-%:%478=262%:%
-%:%479=263%:%
-%:%480=264%:%
-%:%481=265%:%
-%:%482=266%:%
-%:%483=267%:%
-%:%484=268%:%
-%:%485=269%:%
-%:%486=270%:%
-%:%488=272%:%
-%:%489=272%:%
+%:%437=248%:%
+%:%438=249%:%
+%:%448=251%:%
+%:%449=252%:%
+%:%450=253%:%
+%:%451=254%:%
+%:%460=256%:%
+%:%472=258%:%
+%:%473=259%:%
+%:%474=260%:%
+%:%475=261%:%
+%:%476=262%:%
+%:%477=263%:%
+%:%478=264%:%
+%:%479=265%:%
+%:%480=266%:%
+%:%481=267%:%
+%:%482=268%:%
+%:%484=270%:%
+%:%485=270%:%
+%:%486=271%:%
+%:%487=272%:%
 %:%490=273%:%
-%:%491=274%:%
-%:%492=274%:%
-%:%494=274%:%
-%:%498=274%:%
-%:%508=276%:%
-%:%509=277%:%
-%:%510=278%:%
-%:%512=280%:%
-%:%513=280%:%
-%:%514=281%:%
-%:%515=282%:%
-%:%516=283%:%
-%:%517=283%:%
-%:%519=283%:%
-%:%523=283%:%
-%:%524=283%:%
-%:%526=284%:%
-%:%527=285%:%
-%:%528=286%:%
-%:%529=287%:%
-%:%539=289%:%
-%:%540=290%:%
-%:%542=292%:%
-%:%543=292%:%
-%:%544=293%:%
-%:%545=294%:%
-%:%546=295%:%
-%:%547=296%:%
-%:%548=296%:%
+%:%494=273%:%
+%:%495=273%:%
+%:%496=274%:%
+%:%497=274%:%
+%:%498=275%:%
+%:%499=275%:%
+%:%500=276%:%
+%:%501=276%:%
+%:%502=276%:%
+%:%503=277%:%
+%:%504=277%:%
+%:%506=278%:%
+%:%516=280%:%
+%:%517=281%:%
+%:%518=282%:%
+%:%520=284%:%
+%:%521=284%:%
+%:%522=285%:%
+%:%523=286%:%
+%:%524=287%:%
+%:%525=287%:%
+%:%527=287%:%
+%:%531=287%:%
+%:%532=287%:%
+%:%534=288%:%
+%:%535=289%:%
+%:%536=290%:%
+%:%537=291%:%
+%:%547=293%:%
+%:%548=294%:%
 %:%550=296%:%
-%:%554=296%:%
-%:%555=296%:%
-%:%557=297%:%
-%:%558=298%:%
-%:%559=299%:%
-%:%560=300%:%
-%:%561=301%:%
-%:%562=302%:%
-%:%572=304%:%
-%:%573=305%:%
-%:%574=306%:%
-%:%576=308%:%
-%:%577=308%:%
-%:%578=309%:%
-%:%579=310%:%
-%:%580=311%:%
-%:%581=311%:%
-%:%583=311%:%
-%:%587=311%:%
-%:%588=311%:%
-%:%590=312%:%
-%:%591=313%:%
-%:%592=314%:%
-%:%593=315%:%
-%:%594=316%:%
-%:%604=319%:%
-%:%605=320%:%
-%:%606=321%:%
-%:%607=322%:%
-%:%608=323%:%
-%:%609=324%:%
-%:%610=325%:%
-%:%612=327%:%
-%:%613=327%:%
-%:%615=328%:%
-%:%616=329%:%
-%:%617=330%:%
-%:%618=330%:%
-%:%619=331%:%
-%:%620=332%:%
-%:%621=332%:%
-%:%623=333%:%
+%:%551=296%:%
+%:%552=297%:%
+%:%553=298%:%
+%:%554=299%:%
+%:%555=300%:%
+%:%556=300%:%
+%:%558=300%:%
+%:%562=300%:%
+%:%563=300%:%
+%:%565=301%:%
+%:%566=302%:%
+%:%567=303%:%
+%:%568=304%:%
+%:%569=305%:%
+%:%570=306%:%
+%:%580=308%:%
+%:%581=309%:%
+%:%582=310%:%
+%:%584=312%:%
+%:%585=312%:%
+%:%586=313%:%
+%:%587=314%:%
+%:%588=315%:%
+%:%589=315%:%
+%:%591=315%:%
+%:%595=315%:%
+%:%596=315%:%
+%:%598=316%:%
+%:%599=317%:%
+%:%600=318%:%
+%:%601=319%:%
+%:%602=320%:%
+%:%612=323%:%
+%:%613=324%:%
+%:%614=325%:%
+%:%615=326%:%
+%:%616=327%:%
+%:%617=328%:%
+%:%618=329%:%
+%:%620=331%:%
+%:%621=331%:%
+%:%623=332%:%
 %:%624=333%:%
+%:%625=334%:%
 %:%626=334%:%
@@
 %:%628=335%:%
-%:%629=336%:%
-%:%630=337%:%
-%:%631=337%:%
-%:%633=338%:%
-%:%634=339%:%
-%:%637=341%:%
-%:%638=342%:%
-%:%640=344%:%
-%:%641=344%:%
-%:%642=345%:%
-%:%643=346%:%
-%:%644=346%:%
+%:%630=336%:%
+%:%631=336%:%
+%:%633=337%:%
+%:%634=338%:%
+%:%635=338%:%
+%:%636=339%:%
+%:%637=339%:%
+%:%639=340%:%
+%:%640=341%:%
+%:%643=343%:%
+%:%644=344%:%
 %:%646=346%:%
-%:%650=346%:%
-%:%651=346%:%
-%:%653=347%:%
-%:%654=348%:%
-%:%655=349%:%
-%:%656=350%:%
-%:%657=351%:%
-%:%658=352%:%
-%:%659=353%:%
-%:%669=355%:%
-%:%670=356%:%
-%:%671=357%:%
-%:%672=358%:%
-%:%673=359%:%
-%:%677=361%:%
-%:%678=362%:%
-%:%679=363%:%
-%:%680=364%:%
-%:%681=365%:%
-%:%682=366%:%
+%:%647=346%:%
+%:%648=347%:%
+%:%649=348%:%
+%:%650=348%:%
+%:%652=348%:%
+%:%656=348%:%
+%:%657=348%:%
+%:%659=349%:%
+%:%660=350%:%
+%:%661=351%:%
+%:%662=352%:%
+%:%663=353%:%
+%:%664=354%:%
+%:%665=355%:%
+%:%675=357%:%
+%:%676=358%:%
+%:%677=359%:%
+%:%678=360%:%
+%:%679=361%:%
+%:%680=362%:%
+%:%681=363%:%
+%:%682=364%:%
+%:%683=365%:%
+%:%684=366%:%
+%:%685=367%:%
 %:%686=368%:%
@@
 %:%688=370%:%
+%:%689=371%:%
 %:%690=372%:%
-%:%691=372%:%
-%:%692=373%:%
-%:%695=374%:%
-%:%699=374%:%
-%:%700=374%:%
-%:%702=375%:%
-%:%708=375%:%
-%:%711=376%:%
-%:%712=377%:%
-%:%713=377%:%
+%:%692=374%:%
+%:%693=374%:%
+%:%694=375%:%
+%:%697=376%:%
+%:%701=376%:%
+%:%702=376%:%
+%:%704=377%:%
+%:%710=377%:%
+%:%713=378%:%
 %:%714=378%:%
@@
 %:%716=380%:%
-%:%717=380%:%
-%:%719=380%:%
-%:%723=380%:%
-%:%724=380%:%
-%:%726=381%:%
+%:%717=381%:%
+%:%718=381%:%
+%:%720=381%:%
+%:%724=381%:%
+%:%725=381%:%
 %:%727=382%:%
@@
 %:%730=385%:%
-%:%740=387%:%
-%:%741=388%:%
+%:%731=386%:%
+%:%732=387%:%
 %:%742=389%:%
@@
 %:%761=408%:%
-%:%765=410%:%
-%:%766=411%:%
+%:%762=409%:%
+%:%763=410%:%
 %:%767=412%:%
@@
 %:%773=418%:%
-%:%777=421%:%
-%:%778=422%:%
+%:%774=419%:%
+%:%775=420%:%
 %:%779=423%:%
 %:%780=424%:%
+%:%781=425%:%
 %:%782=426%:%
-%:%783=426%:%
-%:%784=427%:%
+%:%784=428%:%
 %:%785=428%:%
-%:%786=428%:%
-%:%787=429%:%
-%:%790=430%:%
-%:%794=430%:%
-%:%795=430%:%
-%:%796=430%:%
-%:%798=431%:%
-%:%799=432%:%
-%:%809=434%:%
-%:%810=435%:%
+%:%786=429%:%
+%:%787=430%:%
+%:%788=430%:%
+%:%789=431%:%
+%:%792=432%:%
+%:%796=432%:%
+%:%797=432%:%
+%:%798=432%:%
+%:%800=433%:%
+%:%801=434%:%
 %:%811=436%:%
@@
 %:%835=460%:%
+%:%836=461%:%
 %:%837=462%:%
-%:%838=462%:%
-%:%839=463%:%
+%:%839=464%:%
 %:%840=464%:%
 %:%841=465%:%
-%:%842=465%:%
-%:%844=465%:%
-%:%848=465%:%
-%:%849=465%:%
-%:%851=466%:%
-%:%852=467%:%
+%:%842=466%:%
+%:%843=467%:%
+%:%844=467%:%
+%:%846=467%:%
+%:%850=467%:%
+%:%851=467%:%
 %:%853=468%:%
@@
 %:%858=473%:%
-%:%868=475%:%
-%:%869=476%:%
+%:%859=474%:%
+%:%860=475%:%
 %:%870=477%:%
@@
 %:%874=481%:%
+%:%875=482%:%
+%:%876=483%:%

### 2022-03-22 paper/output/document/thesis_0_abstract.tex
i hate don knuth

@@
 In this thesis, I present an implementation of automated Kantian
-ethics that is faithful to the Kantian philosophical tradition. Given an appropriately represented 
-action and minimal factual background, my system can judge a potential action as morally obligatory, permissible, or prohibited.
+ethics that is faithful to the Kantian philosophical tradition. Given minimal factual background, my 
+system can judge an agent's potential action as morally obligatory, permissible, or prohibited.
 To accomplish this, I formalize Kant's categorical imperative, or moral rule,
-in Carmo and Jones's Dyadic Deontic Logic, implement this formalization 
+in deontic logic, implement this formalization 
 in the Isabelle/HOL theorem prover, and develop a testing framework to evaluate how well 
 my implementation coheres with expected properties of Kantian ethics, as established in the literature. 
-I also use my system to derive philosophically sophisticated and nuanced solutions to two central ethical 
-dilemmas in Kantian literature: the permissibility of lying in the context of a joke and to a murderer 
-asking about the location of their intended victim. Finally, I examine the philosophical implications 
-of my system, exploring its potential to guide AI agents, academic philosophers, 
-and everyday reasoners as they navigate ethical dilemmas. Ultimately, this work serves 
-as an early proof-of-concept for philosophically mature AI agents and is one step towards the development 
-of responsible, trustworthy artificial intelligence.%
+This testing framework demonstrates that my system outperforms two other potential implementations of 
+automated Kantian ethics. I also use my system to derive philosophically sophisticated and nuanced 
+solutions to two central controversies in Kantian literature: the permissibility of lying in the 
+context of a joke and to a murderer asking about the location of their intended victim. Finally, I 
+examine my system's philosophical implications, demonstrating that it can not only guide AI agents, but it can
+also help academic philosophers make philosophical progress and augment the everyday ethical reasoning
+that we all perform as we navigate the world. I contribute a working proof-of-concept implementation
+of automated Kantian ethics capable of performing philosophical reasoning more mature than anything previously
+automated. My work serves as one step towards the development of responsible, trustworthy artifical intelligence.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %:%45=32%:%
+%:%46=33%:%
+%:%47=34%:%

### 2022-03-22 paper/output/document/thesis_1_intro.tex
i hate don knuth

@@
 logics include a necessitation operator, denoted as $\Box$, where
-$\Box p$ is true at world $w$ if $p$ is true at all worlds that neighbor $w$ \citep{cresswell}. Such 
-logics  also contain the possibility operator $\diamond$, where $\diamond \, p \longleftrightarrow \neg (\Box (\neg p))$ 
-and operators of propositional logic like $\neg, \wedge, \vee, \rightarrow$. Standard deontic logic (SDL) 
-replaces $\Box$ with the obligation operator $O$, where $O \, p$ is true at $w$ 
-if $p$ is true at all morally perfect versions of $w$ \citep{sep-logic-deontic}. I use a more sophisticated
-version of DDL called Dyadic Deontic Logic, in which
-the dyadic obligation operator $O\{A \vert B\}$ represents the sentence ``A is obligated in the context B.'' 
-The introduction of context allows DDL to express more nuanced reasoning and certain paradoxes that plague
-SDL.
+$\Box p$ is true at world $w$ if $p$ is true at all worlds that neighbor $w$ \citep{cresswell}. Intuitively, 
+$\Box p$ indicates that $p$ is a necessary truth, like $p$ or $\neg p$. Such 
+logics also contain the $\diamond$ operator, which represents possible truths, and operators of 
+propositional logic like $\neg, \wedge, \vee, \rightarrow$. Deontic logics
+replace $\Box$ with the obligation operator $O$, where $O \, p$ is true at $w$ 
+if $p$ is true at all morally perfect versions of $w$ \citep{sep-logic-deontic}. A necessary 
+proposition must be true, while an obligatory proposition must be true in order for a world to be morally good.
+For example, in order for a world to be morally perfect, if giving to charity is morally obligatory, then
+the statement ``Sara gives to charity'' must be true at that world. I use a sophisticated deontic logic 
+called Dyadic Deontic Logic, in which the dyadic obligation operator $O\{A \vert B\}$ represents the 
+sentence ``A is obligated in the context B.'' This operator expresses the nuanced idea
+that certain acts are morally required in certain situations, but not in others.
 
@@
 
-A machine that can evaluate the moral status of a maxim can not only help machines better reason about ethics, 
+A machine that can evaluate the moral status of an action can not only help machines better reason about ethics, 
 but it can also help philosophers better study philosophy. I argue for ``computational ethics,'' or the use of computational tools to 
@@
 %:%217=187%:%
+%:%218=188%:%
+%:%219=189%:%
+%:%220=190%:%

### 2022-03-22 paper/output/document/thesis_2_methods.tex
i hate don knuth

@@
 prover could be made. Flaws with these components are limitations of my system, but do not 
-indict logic-programming-based automated ethics more generally. My thesis seeks to 
+indict logic-based automated ethics more generally. My thesis seeks to 
 both present a specific implementation of automated ethics and to argue for a particular approach 
@@
 procedure for the problem of making ethical judgements. I will make this intuition precise by
-arguing that Kantian ethics is natural to formalize because it prescribes moral rules that require 
-little additional data about the world and are easy to represent to a computer. I argue that, compared to 
-consequentialism and virtue ethics,\footnote{Technically, virtue ethics and
+arguing that Kantian ethics is more natural to formalize than consequentialism or virtue ethics\footnote{Technically, virtue ethics and
 consequentialism are broad ethical traditions, while Kantian ethics is a specific ethical theory within
@@
 theories have some connection to or basis in Kantian ethics, I choose to focus on Kantian ethics, instead
-of deontology more broadly. } Kantian ethics is more amenable to automation.
+of deontology more broadly. } because it prescribes moral rules that require 
+little additional data about the world and are easy to represent to a computer.
 
@@
 
-To solve this problem, some consequentialists reject aggregation entirely and instead prefer wholistic
+To solve this problem, some consequentialists reject aggregation entirely and instead prefer holistic
 evaluations of a state of affairs. While this approach no longer requires that an 
@@
 affairs. Whereas before the system could restrict its analysis to a single person, the algorithm must now 
-evaluate an entire state wholistically. As consequentialists modulate between aggregation 
-and wholistic evaluation, they face a tradeoff between the difficulty of aggregation and the complexity 
+evaluate an entire state holistically. As consequentialists modulate between aggregation 
+and holistic evaluation, they face a tradeoff between the difficulty of aggregation and the complexity 
 of goodness measurements for large states of affairs.%
@@
 Machine learning approaches like the Delphi system \citep{delphi} mentioned in Chapter \ref{intro} also may suffer explanability 
-problems that my logic-programming, theorem-prover
-approach does not face. Many machine learning algorithms cannot sufficiently explain their 
+problems that my system does not face. Many machine learning algorithms cannot sufficiently explain their 
 decisions to a human being and often find patterns in datasets that don't 
@@
 \begin{isamarkuptext}%
-Kant's theory is centered 
-on practical reason, which is the kind of reason that we 
+Kant's theory is centered on practical reason, which is the kind of reason that we 
 use to decide what to do. In \emph{The Groundwork of the Metaphysics of Morals}, Kant explains that 
@@
 ethical judgement requires robust conceptions of the action at hand, but Kantian ethics requires far less common sense 
-than a consequentialism or virtue ethics.\footnote{
+than consequentialism or virtue ethics.\footnote{
 In Sections \ref{joking} and \ref{murderer}, I use my system to demonstrate that Kantian ethics requires relatively lightweight, uncontroversial definitions 
-of concepts like falsely promising.} All
-moral theories evaluating falsely promising will a robust definition of promising, 
-but consequentialism and virtue ethics will require more information than Kantian ethics.
+of concepts like falsely promising.} All moral theories evaluating falsely promising need a robust 
+definition of promising, but consequentialism and virtue ethics will require more information than Kantian ethics.
 Thus, although the need for common sense poses a challenge to automated
@@
 automation. Korsgaard characterizes the three formulations of the categorical
-imperative according to Rawls' general and special conception of justice \cite{theoryofjustice}. The general conception applies
-universally and can never be violated, while the special conception represents an ideal for us to
-live towards that may not be possible to achieve. For example, the special conception may require that we prefer some job applicants
-over others in order to remedy historical injustice, and the general conception may require that such
-inequalities always operate in the service of the least privileged \citep[19]{KorsgaardRTL}. Korsgaard
-argues that the Formula of Universal Law represents Kant's general conception of justice, and the Formula of 
-Humanity represents his special conception. The FUL's prescriptions can never be violated, even in the most
-non-ideal circumstances imaginable, but the FUH is merely an ideal to strive towards. Thus, the FUL 
-generates stronger requirements than the other two formulations and reflects 
-the bare minimum standard of Kant's ethics. Because the FUL's prescriptions outweigh those of the other two formulations,
-it serves as a functional, minimal version of Kantian ethics.%
+imperative according to Rawls' general and special conception of justice \cite{theoryofjustice}. The general conception 
+consists of universal rules that can never be violated, no matter what the circumstances are. The special
+conception, on the other hand, is an ideal to live up to, and in some cases, it may not be possible to 
+achieve. For example, under some ethical theory, the general conception may include a prohibition against 
+torturing others, whereas the the special conception may include the obligation to give to charity. 
+In some situations, such as when a thief steals all your belongings and leaves you destitute, you may not 
+be able to give to charity, but you are never allowed to torture others, no matter what the circumstances.
+Korsgaard argues that the Formula of Universal Law represents Kant's general conception of justice, and the Formula of 
+Humanity represents his special conception \citep[19]{KorsgaardRTL}. The FUL's prescriptions can never 
+be violated, even in the most non-ideal circumstances imaginable, but the FUH is merely an ideal to 
+strive towards. Thus, the FUL generates stronger requirements than the other two formulations and reflects 
+the bare minimum standard of Kant's ethics. Because the FUL's prescriptions outweigh those of the other 
+two formulations, it serves as a functional, minimal version of Kantian ethics.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %
-\isamarkupcmt{The blue texte below is an example of typical Nitpick output. In this case, Nitpick successfully found a model 
+\isamarkupcmt{The blue text below is an example of typical Nitpick output. In this case, Nitpick successfully found a model 
 satisfying these axioms so the system is consistent.%
@@
 which unfolds definitions and applies theorems directly. HOL has $True$ as a theorem,
-which is why this theorem was so easy to prove.%
+which is why this theorem was so easy to prove. I generated this proof automatically using Sledgehammer,
+a tool that automatically searches for proofs \cite{sledgehammer}.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 %:%93=49%:%
-%:%94=50%:%
-%:%103=53%:%
+%:%102=52%:%
+%:%114=54%:%
 %:%115=55%:%
@@
 %:%122=62%:%
-%:%123=63%:%
-%:%127=65%:%
+%:%126=64%:%
+%:%130=66%:%
 %:%131=67%:%
@@
 %:%154=90%:%
-%:%155=91%:%
-%:%159=94%:%
+%:%158=93%:%
+%:%162=95%:%
 %:%163=96%:%
@@
 %:%178=111%:%
-%:%179=112%:%
-%:%183=114%:%
+%:%182=113%:%
+%:%186=115%:%
 %:%187=116%:%
@@
 %:%202=131%:%
-%:%203=132%:%
-%:%207=135%:%
+%:%206=134%:%
+%:%210=137%:%
 %:%211=138%:%
@@
 %:%224=151%:%
-%:%225=152%:%
-%:%234=155%:%
+%:%233=154%:%
+%:%245=156%:%
 %:%246=157%:%
@@
 %:%261=172%:%
-%:%262=173%:%
-%:%266=175%:%
+%:%265=174%:%
+%:%269=176%:%
 %:%270=177%:%
@@
 %:%293=200%:%
-%:%294=201%:%
-%:%295=202%:%
-%:%304=205%:%
+%:%302=203%:%
+%:%314=205%:%
+%:%315=206%:%
 %:%316=207%:%
@@
 %:%369=260%:%
-%:%370=261%:%
-%:%371=262%:%
-%:%372=263%:%
-%:%376=266%:%
+%:%373=263%:%
+%:%377=265%:%
+%:%378=266%:%
+%:%379=267%:%
 %:%380=268%:%
@@
 %:%396=284%:%
-%:%397=285%:%
-%:%398=286%:%
-%:%399=287%:%
-%:%403=290%:%
+%:%400=287%:%
+%:%404=289%:%
+%:%405=290%:%
+%:%406=291%:%
 %:%407=292%:%
@@
 %:%430=315%:%
-%:%431=316%:%
-%:%432=317%:%
-%:%433=318%:%
-%:%434=319%:%
-%:%443=321%:%
+%:%439=317%:%
+%:%451=319%:%
+%:%452=320%:%
+%:%453=321%:%
+%:%454=322%:%
 %:%455=323%:%
@@
 %:%500=368%:%
-%:%501=369%:%
-%:%502=370%:%
-%:%511=372%:%
+%:%509=370%:%
+%:%521=373%:%
+%:%522=374%:%
 %:%523=375%:%
@@
 %:%582=434%:%
-%:%583=435%:%
-%:%584=436%:%
-%:%593=439%:%
+%:%591=437%:%
+%:%603=439%:%
+%:%604=440%:%
 %:%605=441%:%
@@
 %:%608=444%:%
-%:%609=445%:%
-%:%610=446%:%
-%:%619=449%:%
+%:%617=447%:%
+%:%629=449%:%
+%:%630=450%:%
 %:%631=451%:%
-%:%632=452%:%
 %:%633=453%:%
-%:%635=455%:%
-%:%636=455%:%
-%:%637=455%:%
-%:%638=455%:%
-%:%640=456%:%
-%:%641=456%:%
-%:%642=457%:%
-%:%643=457%:%
-%:%644=457%:%
-%:%645=457%:%
-%:%647=458%:%
-%:%648=459%:%
+%:%634=453%:%
+%:%635=453%:%
+%:%636=453%:%
+%:%638=454%:%
+%:%639=454%:%
+%:%640=455%:%
+%:%641=455%:%
+%:%642=455%:%
+%:%643=455%:%
+%:%645=456%:%
+%:%646=457%:%
+%:%649=469%:%
+%:%650=470%:%
 %:%651=471%:%
-%:%652=472%:%
 %:%653=473%:%
-%:%655=475%:%
-%:%656=475%:%
-%:%657=475%:%
-%:%658=475%:%
-%:%659=476%:%
-%:%660=476%:%
+%:%654=473%:%
+%:%655=473%:%
+%:%656=473%:%
+%:%657=474%:%
+%:%658=474%:%
+%:%661=476%:%
+%:%662=477%:%
 %:%663=478%:%
 %:%664=479%:%
-%:%665=480%:%
 %:%666=481%:%
-%:%668=483%:%
-%:%669=483%:%
-%:%670=507%:%
-%:%671=508%:%
+%:%667=481%:%
+%:%668=505%:%
+%:%669=506%:%
+%:%671=507%:%
+%:%672=508%:%
 %:%673=509%:%
 %:%674=510%:%
-%:%675=511%:%
-%:%676=512%:%
-%:%684=517%:%
+%:%682=515%:%
+%:%694=517%:%
+%:%695=518%:%
 %:%696=519%:%
@@
 %:%700=523%:%
-%:%701=524%:%
-%:%702=525%:%
-%:%706=539%:%
-%:%708=540%:%
-%:%709=540%:%
-%:%710=541%:%
-%:%712=542%:%
-%:%713=543%:%
-%:%714=543%:%
-%:%715=544%:%
-%:%716=544%:%
-%:%717=545%:%
-%:%719=546%:%
-%:%722=547%:%
-%:%724=548%:%
-%:%725=548%:%
-%:%726=549%:%
-%:%728=550%:%
-%:%731=567%:%
-%:%732=568%:%
-%:%734=569%:%
+%:%704=537%:%
+%:%706=538%:%
+%:%707=538%:%
+%:%708=539%:%
+%:%710=540%:%
+%:%711=541%:%
+%:%712=541%:%
+%:%713=542%:%
+%:%714=542%:%
+%:%715=543%:%
+%:%717=544%:%
+%:%720=545%:%
+%:%722=546%:%
+%:%723=546%:%
+%:%724=547%:%
+%:%726=548%:%
+%:%729=565%:%
+%:%730=566%:%
+%:%732=567%:%
+%:%733=567%:%
+%:%734=568%:%
 %:%735=569%:%
-%:%736=570%:%
-%:%737=571%:%
+%:%736=569%:%
+%:%737=570%:%
 %:%738=571%:%
-%:%739=572%:%
-%:%740=573%:%
-%:%741=573%:%
-%:%742=574%:%
-%:%744=575%:%
-%:%745=576%:%
-%:%748=577%:%
-%:%750=578%:%
-%:%751=578%:%
-%:%752=579%:%
-%:%754=580%:%
+%:%739=571%:%
+%:%740=572%:%
+%:%742=573%:%
+%:%743=574%:%
+%:%746=575%:%
+%:%748=576%:%
+%:%749=576%:%
+%:%750=577%:%
+%:%752=578%:%
+%:%755=583%:%
+%:%756=584%:%
 %:%757=585%:%
@@
 %:%759=587%:%
-%:%760=588%:%
-%:%761=589%:%
-%:%763=592%:%
-%:%764=592%:%
-%:%765=592%:%
-%:%767=592%:%
-%:%771=592%:%
-%:%772=592%:%
-%:%774=593%:%
-%:%775=594%:%
-%:%776=594%:%
+%:%761=590%:%
+%:%762=590%:%
+%:%763=590%:%
+%:%765=590%:%
+%:%769=590%:%
+%:%770=590%:%
+%:%772=591%:%
+%:%773=592%:%
+%:%774=592%:%
+%:%776=593%:%
+%:%777=594%:%
 %:%778=595%:%
-%:%779=596%:%
-%:%780=597%:%
+%:%788=597%:%
+%:%789=598%:%
 %:%790=599%:%
 %:%791=600%:%
-%:%792=601%:%

### 2022-03-22 paper/output/document/thesis_3_implementation.tex
i hate don knuth

@@
 to repay a loan, to get some easy cash)''. The first term represents the circumstance, which
-can be true or false at a world. For example, the circumstance ``when I am strapped for cash'' is true at the real 
+can be true or false at a world. For example, in the \nameref{falsepromise} maxim, the circumstance
+``when I am strapped for cash'' is true at the real 
 world when my bank account is empty. The second term represents the act, which is an open sentence
@@
 $$\text{\emph{will}} \, M \, s \equiv \forall w \, (C \longrightarrow A \, (s)) \, w$$
-\noindent At all worlds $w$, if the circumstances hold at that world, agent $s$ performs act $A$.
+\noindent At all worlds $w$, if the circumstances hold at that world, actor $s$ performs act $A$.
 \end{definition}
@@
 
-This view cannot correctly handle natural acts. Korsgaard appeals to 
+This view cannot correctly handle natural acts, or acts that are possible simply due to the laws of nature. Korsgaard appeals to 
 \citet{dietrichson} to construct the example natural act of a mother killing her children that
-cry too much at night so that she can get some sleep. Thought this maxim is clearly wrong, universalizing 
+cry at night so that she can get some sleep. Thought this maxim is clearly wrong, universalizing 
 it does not generate a logical contradiction because killing is still possible in a world where 
@@
 loud children, then she cannot be secure in the possession of her life, because her own mother may 
-have killed her as an infant. Her willing this maxim thwarts the end that she sought to secure.
+have killed her when she cried as an infant. Her willing this maxim thwarts the end that she sought to secure.
 
@@
 \centering
-\includegraphics[scale=0.6]{goalstable.png}
+\includegraphics[scale=0.165]{goalstable.jpeg}
 \caption{Table showing which tests each implementation passes. ``Naive'' indicates raw DDL, 
@@
 \medskip
-\noindent \textbf{Obligation Universalizes Across People} The obligations prescribed by the Formula of Universal Law
+\noindent \textbf{Obligations Universalize Across People} The obligations prescribed by the Formula of Universal Law
 should generalize across people. In other words, if a maxim is obligated for one person, then it is obligated
@@
 %:%184=100%:%
-%:%187=102%:%
+%:%185=101%:%
 %:%188=103%:%
@@
 %:%228=143%:%
-%:%230=145%:%
-%:%231=145%:%
+%:%229=144%:%
+%:%231=146%:%
 %:%232=146%:%
-%:%234=147%:%
+%:%233=147%:%
 %:%235=148%:%
@@
 %:%237=150%:%
-%:%245=152%:%
-%:%257=154%:%
+%:%238=151%:%
+%:%246=153%:%
 %:%258=155%:%
@@
 %:%308=205%:%
-%:%310=208%:%
-%:%311=208%:%
+%:%309=206%:%
+%:%311=209%:%
 %:%312=209%:%
-%:%314=210%:%
+%:%313=210%:%
 %:%315=211%:%
-%:%318=213%:%
+%:%316=212%:%
 %:%319=214%:%
@@
 %:%335=230%:%
-%:%337=233%:%
-%:%338=233%:%
+%:%336=231%:%
+%:%338=234%:%
 %:%339=234%:%
-%:%341=235%:%
+%:%340=235%:%
 %:%342=236%:%
-%:%345=240%:%
+%:%343=237%:%
 %:%346=241%:%
@@
 %:%355=250%:%
-%:%357=252%:%
-%:%358=252%:%
+%:%356=251%:%
+%:%358=253%:%
 %:%359=253%:%
-%:%361=254%:%
-%:%364=256%:%
+%:%360=254%:%
+%:%362=255%:%
 %:%365=257%:%
@@
 %:%396=288%:%
-%:%398=290%:%
-%:%399=290%:%
+%:%397=289%:%
+%:%399=291%:%
 %:%400=291%:%
-%:%402=292%:%
+%:%401=292%:%
 %:%403=293%:%
-%:%404=293%:%
+%:%404=294%:%
 %:%405=294%:%
-%:%406=294%:%
+%:%406=295%:%
 %:%407=295%:%
-%:%409=296%:%
+%:%408=296%:%
 %:%410=297%:%
-%:%413=298%:%
+%:%411=298%:%
 %:%414=299%:%
@@
 %:%416=301%:%
-%:%418=303%:%
-%:%419=303%:%
+%:%417=302%:%
+%:%419=304%:%
 %:%420=304%:%
-%:%422=305%:%
+%:%421=305%:%
 %:%423=306%:%
-%:%424=306%:%
+%:%424=307%:%
 %:%425=307%:%
-%:%426=307%:%
-%:%428=308%:%
+%:%426=308%:%
+%:%427=308%:%
 %:%429=309%:%
 %:%430=310%:%
-%:%438=312%:%
-%:%450=314%:%
+%:%431=311%:%
+%:%439=313%:%
 %:%451=315%:%
@@
 %:%457=321%:%
-%:%459=324%:%
-%:%460=324%:%
-%:%462=325%:%
+%:%458=322%:%
+%:%460=325%:%
+%:%461=325%:%
 %:%463=326%:%
@@
 %:%465=328%:%
-%:%468=330%:%
+%:%466=329%:%
 %:%469=331%:%
-%:%471=333%:%
-%:%472=333%:%
-%:%474=333%:%
-%:%478=333%:%
-%:%479=333%:%
+%:%470=332%:%
+%:%472=334%:%
+%:%473=334%:%
+%:%475=334%:%
+%:%479=334%:%
 %:%480=334%:%
-%:%481=334%:%
-%:%482=334%:%
-%:%491=336%:%
+%:%481=335%:%
+%:%482=335%:%
+%:%483=335%:%
 %:%492=337%:%
@@
 %:%514=359%:%
-%:%516=361%:%
-%:%517=361%:%
+%:%515=360%:%
+%:%517=362%:%
 %:%518=362%:%
-%:%520=363%:%
+%:%519=363%:%
 %:%521=364%:%
-%:%524=366%:%
-%:%526=368%:%
-%:%527=368%:%
+%:%522=365%:%
+%:%525=367%:%
+%:%527=369%:%
 %:%528=369%:%
-%:%530=370%:%
+%:%529=370%:%
 %:%531=371%:%
-%:%532=371%:%
+%:%532=372%:%
 %:%533=372%:%
 %:%534=373%:%
-%:%535=373%:%
+%:%535=374%:%
 %:%536=374%:%
-%:%537=374%:%
-%:%539=374%:%
-%:%543=374%:%
-%:%544=374%:%
-%:%546=375%:%
+%:%537=375%:%
+%:%538=375%:%
+%:%540=375%:%
+%:%544=375%:%
+%:%545=375%:%
 %:%547=376%:%
@@
 %:%552=381%:%
-%:%562=383%:%
+%:%553=382%:%
 %:%563=384%:%
@@
 %:%582=403%:%
-%:%584=405%:%
-%:%585=405%:%
-%:%587=407%:%
+%:%583=404%:%
+%:%585=406%:%
+%:%586=406%:%
 %:%588=408%:%
@@
 %:%591=411%:%
-%:%600=413%:%
-%:%612=415%:%
+%:%592=412%:%
+%:%601=414%:%
 %:%613=416%:%
@@
 %:%636=439%:%
-%:%639=443%:%
+%:%637=440%:%
 %:%640=444%:%
@@
 %:%644=448%:%
-%:%647=450%:%
+%:%645=449%:%
 %:%648=451%:%
@@
 %:%656=459%:%
-%:%660=461%:%
+%:%657=460%:%
 %:%661=462%:%
@@
 %:%673=474%:%
-%:%675=476%:%
-%:%676=476%:%
+%:%674=475%:%
+%:%676=477%:%
 %:%677=477%:%
-%:%680=478%:%
-%:%684=478%:%
-%:%685=478%:%
-%:%687=479%:%
+%:%678=478%:%
+%:%681=479%:%
+%:%685=479%:%
+%:%686=479%:%
 %:%688=480%:%
 %:%689=481%:%
-%:%690=481%:%
-%:%692=482%:%
+%:%690=482%:%
+%:%691=482%:%
 %:%693=483%:%
@@
 %:%695=485%:%
-%:%701=485%:%
-%:%704=486%:%
+%:%696=486%:%
+%:%702=486%:%
 %:%705=487%:%
-%:%706=487%:%
+%:%706=488%:%
 %:%707=488%:%
-%:%710=489%:%
-%:%714=489%:%
-%:%715=489%:%
-%:%717=490%:%
+%:%708=489%:%
+%:%711=490%:%
+%:%715=490%:%
+%:%716=490%:%
 %:%718=491%:%
-%:%728=493%:%
+%:%719=492%:%
 %:%729=494%:%
@@
 %:%749=514%:%
-%:%751=516%:%
-%:%752=516%:%
+%:%750=515%:%
+%:%752=517%:%
 %:%753=517%:%
-%:%756=518%:%
-%:%760=518%:%
-%:%761=518%:%
-%:%762=518%:%
-%:%764=519%:%
-%:%770=519%:%
-%:%773=520%:%
+%:%754=518%:%
+%:%757=519%:%
+%:%761=519%:%
+%:%762=519%:%
+%:%763=519%:%
+%:%765=520%:%
+%:%771=520%:%
 %:%774=521%:%
-%:%775=521%:%
+%:%775=522%:%
 %:%776=522%:%
 %:%777=523%:%
-%:%780=524%:%
-%:%784=524%:%
-%:%785=524%:%
-%:%786=524%:%
-%:%788=525%:%
+%:%778=524%:%
+%:%781=525%:%
+%:%785=525%:%
+%:%786=525%:%
+%:%787=525%:%
 %:%789=526%:%
 %:%790=527%:%
-%:%800=529%:%
+%:%791=528%:%
 %:%801=530%:%
@@
 %:%807=536%:%
-%:%809=539%:%
-%:%810=539%:%
-%:%813=540%:%
-%:%817=540%:%
-%:%818=540%:%
-%:%820=541%:%
+%:%808=537%:%
+%:%810=540%:%
+%:%811=540%:%
+%:%814=541%:%
+%:%818=541%:%
+%:%819=541%:%
 %:%821=542%:%
-%:%822=542%:%
-%:%824=543%:%
-%:%834=545%:%
+%:%822=543%:%
+%:%823=543%:%
+%:%825=544%:%
 %:%835=546%:%
@@
 %:%841=552%:%
-%:%843=554%:%
-%:%844=554%:%
+%:%842=553%:%
+%:%844=555%:%
 %:%845=555%:%
 %:%846=556%:%
-%:%849=557%:%
-%:%853=557%:%
-%:%854=557%:%
-%:%855=557%:%
-%:%857=558%:%
+%:%847=557%:%
+%:%850=558%:%
+%:%854=558%:%
+%:%855=558%:%
+%:%856=558%:%
 %:%858=559%:%
 %:%859=560%:%
-%:%860=560%:%
-%:%862=561%:%
+%:%860=561%:%
+%:%861=561%:%
 %:%863=562%:%
 %:%864=563%:%
-%:%874=565%:%
+%:%865=564%:%
 %:%875=566%:%
-%:%877=568%:%
-%:%878=568%:%
+%:%876=567%:%
+%:%878=569%:%
 %:%879=569%:%
 %:%880=570%:%
-%:%883=571%:%
-%:%887=571%:%
-%:%888=571%:%
-%:%889=571%:%
-%:%891=572%:%
-%:%892=572%:%
-%:%894=573%:%
+%:%881=571%:%
+%:%884=572%:%
+%:%888=572%:%
+%:%889=572%:%
+%:%890=572%:%
+%:%892=573%:%
+%:%893=573%:%
 %:%895=574%:%
-%:%905=576%:%
+%:%896=575%:%
 %:%906=577%:%
@@
 %:%918=589%:%
-%:%922=593%:%
+%:%919=590%:%
 %:%923=594%:%
@@
 %:%929=600%:%
-%:%933=603%:%
+%:%930=601%:%
 %:%934=604%:%
@@
 %:%958=628%:%
+%:%959=629%:%

### 2022-03-22 paper/output/document/thesis_4_applications.tex
i hate don knuth

@@
 
-In this chapter, I tackle this challenge by endowing my system with this kind of common sense in the 
+In this chapter, I tackle this challenge by automating this kind of common sense in the 
 specific case of lying. While my system has the ability to reason
@@
 \begin{isamarkuptext}%
-This concludes my examination of the maxim of lying to a liar. I was able to show that, by
-modifying the common sense facts used, my system can show that lying to a liar is permissible, but lying 
+This concludes my examination of the maxim of lying to a liar. I was able to show that, given minimal
+common sense facts, my system shows that lying to a liar is permissible, but lying 
 in order to find a victim is not. The assumptions used in this example were a little more robust, but still

### 2022-03-24 paper/output/document/thesis_0_abstract.tex
full send

@@
 \begin{isamarkuptext}%
-AI agents are beginning to make decisions without human supervision in increasingly consequential 
+AI is beginning to make decisions without human supervision in increasingly consequential 
 contexts like healthcare, policing, and driving. These decisions are inevitably ethically tinged, 
-but most AI agents navigating the world today are not explicitly guided by ethics.
+but most AI systems in use today are not explicitly guided by ethics.
 Regulators, philosophers, and computer scientists are raising the alarm about the 
@@
 automated ethics rarely engages with philosophical literature, despite its relevance to the 
-development of responsible AI agents. If automated ethics draws on sophisticated philosophical
+development of responsible AI. If automated ethics draws on philosophical
 literature, its decisions will be more nuanced, precise, and consistent, but automating ethical theories is 
@@
 ethics that is faithful to the Kantian philosophical tradition. Given minimal factual background, my 
-system can judge an agent's potential action as morally obligatory, permissible, or prohibited.
+system can judge a potential action as morally obligatory, permissible, or prohibited.
 To accomplish this, I formalize Kant's categorical imperative, or moral rule,
@@
 automated Kantian ethics. I also use my system to derive philosophically sophisticated and nuanced 
-solutions to two central controversies in Kantian literature: the permissibility of lying in the 
-context of a joke and to a murderer asking about the location of their intended victim. Finally, I 
-examine my system's philosophical implications, demonstrating that it can not only guide AI agents, but it can
+solutions to two central controversies in Kantian literature: the permissibility of lying (a) in the 
+context of a joke and (b) to a murderer asking about the location of their intended victim. Finally, I 
+examine my system's philosophical implications, demonstrating that it can not only guide AI, but it can
 also help academic philosophers make philosophical progress and augment the everyday ethical reasoning
-that we all perform as we navigate the world. I contribute a working proof-of-concept implementation
+that we all perform as we navigate the world. Ultimately, I contribute a working proof-of-concept implementation
 of automated Kantian ethics capable of performing philosophical reasoning more mature than anything previously

### 2022-03-24 paper/output/document/thesis_1_intro.tex
full send

@@
 \begin{isamarkuptext}%
-As AI agents become more sophisticated and less dependent on humans, interest begins to mount
+As AI becomes more sophisticated and less dependent on humans, interest begins to mount
 in the development of automated moral agents, or computers that can perform ethical reasoning. 
-AI agents are making decisions in increasingly 
+AI is making decisions in increasingly 
 consequential contexts, such as healthcare, driving, and criminal sentencing, and therefore 
@@
 hit the car in the next lane, killing the single passenger inside it. While this example is (hopefully) 
-not typical of the operation of a self-driving car, every decision that such an AI agent makes, from 
-avoiding congested freeways to carpooling, is morally tinged. Not only do AI agents routinely make decisions with 
+not typical of the operation of a self-driving car, every decision that such an AI system makes, from 
+avoiding congested freeways to carpooling, is morally tinged. Not only does AI routinely make decisions with 
 ethical implications without explicitly performing ethical
-reasoning, they often do so without human supervision. For example, the Alleghany Family Screening 
-tool can automatically trigger an investigation into a potential case of child neglect, a decision that 
+reasoning, it often does so without human supervision. For example, the Allegheny Family Screening 
+Tool can automatically trigger an investigation into a potential case of child neglect, a decision that 
 can uproot entire families and is known to be biased against poor people of color \citep{eubanks}. 
@@
 However, prior work in machine ethics using popular ethical theories like deontology (\citep{deon1}, \citep{deon2}), 
-consequentialism (\citep{util2}, \citep{util1}, \citep{cloos}), and virtue ethics \citep{virtue2} rarely 
+consequentialism (\citep{util2}, \citep{cloos}, \citep{util1}), and virtue ethics \citep{virtue2} rarely 
 engages with philosophical literature and thus often misses philosophers' insights. Even the above example of 
@@
 that artifical agents face are not entirely new, so solutions to these problems should take advantage of philosophical 
-progress. Ethical philosophers are devoted to the creation of better ethical theories, so the 
+progress. Moral philosophers are devoted to the creation of better ethical theories, so the 
 more faithful that automated ethics is to philosophical literature, the more nuanced, precise, consistent, and
@@
 
-A lack of engagement with prior philosophical literature also makes automated moral agents less 
+A lack of engagement with prior philosophical literature also makes automated ethics less 
 explainable, or interpretable by human observers. One example of this is Delphi, an implementation of automated ethics that uses deep 
@@
 system's judgements.
+
+\medskip
 
@@
 \begin{isamarkuptext}%
-\noindent \textbf{Automated Kantian Ethics}
+\noindent \textbf{Automated Kantian Ethics: An Overview}
 
@@
 %:%116=88%:%
-%:%120=91%:%
-%:%121=92%:%
+%:%117=89%:%
+%:%118=90%:%
 %:%122=93%:%
@@
 %:%145=116%:%
-%:%149=119%:%
-%:%150=120%:%
+%:%146=117%:%
+%:%147=118%:%
 %:%151=121%:%
@@
 %:%220=190%:%
+%:%221=191%:%
+%:%222=192%:%

### 2022-03-24 paper/output/document/thesis_5_discussion.tex
i hate don knuth
full send

@@
 
-First, I explore how my system can be used in practice to guide AI agents,
+First, I explore how my system can be used in practice to guide AI through moral dilemmas,
 help academic philosophers make philosophical progress, and augment the everyday practical reasoning 
@@
 \begin{isamarkuptext}%
-In this section, I outline the additional components necessary for my system
-to guide AI agents in practice. As it stands, my system is a categorical imperative library that can
+In this section, I present the future work necessary for my system to guide AI 
+in practice. As it stands, my system is a categorical imperative library that can
 evaluate the moral status of a maxim. My project potentially 
-serves as one component of an ``ethics engine'' that an AI agent could use to make ethical decisions.
-For example, when an AI agent faces a moral dilemma in some internal representation, it could pass it 
+serves as one component of an ``ethics engine'' that an AI system could use to make ethical decisions.
+For example, when an AI system faces a moral dilemma in some internal representation, it could pass it 
 to an input parser that translates the dilemma into a maxim in my logic. An output parser could then 
-translate my system's output into a prescription for action that the AI agent could act on. \begin{figure}
-\includegraphics[scale=0.43]{AI_engine.png}
-\caption{An example of an ethics engine for an artificial agent. This ethics engine passes a moral dilemma 
+translate my system's output into a prescription for action that the AI system could act on. \begin{figure}
+\includegraphics[scale=0.175]{AI_engine.jpeg}
+\caption{An example of an ethics engine for artificial intelligence. This ethics engine passes a moral dilemma 
 through an input parser, applies the automated categorical imperative test, and finally processes the 
@@
 \end{figure} Figure \ref{fig:AIengine} depicts the workflow of this example ethics engine. In order 
-for my system to guide an AI agent using this workflow, future work must develop such input and output parsers.
+for my system to guide AI using this workflow, future work must develop such input and output parsers.
 
 One of the biggest challenges for an ethics engine is the development of an input parser. An input parser 
-for my implementation of automated Kantian ethics must translate a complex real-world situation into a flat 
+for my implementation of automated Kantian ethics must translate a complex real-world situation into a 
 circumstances, act, goal triple.
@@
 
-The Kantian response to this criticism is to require that the circumstances included in the formulation
+In Section \ref{whatisamaxim}, I introduced the Kantian response to this criticism, which requires that 
+the circumstances included in the formulation
 of the maxim be morally relevant. In the example above, my purple shirt and the date have no bearing on 
@@
 in an AI ethics engine. One solution is for a human being to perform the role of the input
-parser by supervising the operation of an AI agent. When the agent stumbles onto
+parser by supervising the operation of an AI system. When the system stumbles onto
 an ethical dilemma, the human could take over, formulate
@@
 It is likely that, regardless of the strengths of the human-in-the-loop model, fully automated AI 
-agents will exist. Even if developing this kind of AI is irresponsible,
+will exist. Even if developing this kind of AI is irresponsible,
 such developments are likely and will require ethics engines, or risk no consideration of ethics at all.
@@
 My system's output could be converted into some actionable, useful response with an output parser, 
-and then passed back to the AI agent. For example, if the AI agent is equipped to evaluate natural 
+and then passed back to the AI system. For example, if the AI system is equipped to evaluate natural 
 language prescriptions, the status of the maxim could be parsed into a natural language sentence. The 
@@
 
-The ethics engine depicted above is a high-level example of one way to use my project to guide an artifical agent,
+The ethics engine depicted above is a high-level example of one way to use my project to guide artifical intelligence,
 with additional work to parse the input and output of my implementation of the categorical imperative.
-Effectively, the kind of automated ethics I implement could be part of a library that AI developers use to 
-give AI agents the capacity for sophisticated ethical reasoning faithful to philosophical literature. 
+The kind of automated ethics that I implement could be part of a library that AI developers use to 
+give AI the capacity for sophisticated ethical reasoning faithful to philosophical literature. 
 This represents an improvement over existing automated ethics, which rarely captures the complexity 
@@
 \begin{isamarkuptext}%
-In addition to guiding AI agents, automated ethics can also help academic philosophers make philosophical
+In addition to guiding AI, automated ethics can also help academic philosophers make philosophical
 progress. Just as theorem provers make mathematics more efficient and push mathematicians to think 
@@
 new philosophical questions. In Section \ref{joking}, I presented one example of the power of computational ethics
-by using my system to isolate a necessary and sufficient condition for the act of lying, or knowingly saying
+by using my system to isolate a necessary and sufficient condition for lying, or knowingly saying
 something false, to be wrong. In this section, I share another example of the kind of philosophical 
@@
 \begin{isamarkuptext}%
-As presented in Section \ref{formalizingful}, in the process of developing my formalization of
+As presented in Section \ref{formalizingful}, in the process of formalizing
 the FUL, I discovered that certain kinds of maxims are badly formed, or inappropriate inputs to the 
-universalizability test. The FUL is consistent only if it holds for ``well-formed maxims,''
+universalizability test. The FUL is consistent if it only holds for well-formed maxims,
 such that neither the act nor goal are already achieved in the given circumstances. Precisely, 
 a circumstance, act, goal tuple (c, a, g) is well-formed if $(\neg (c \longrightarrow a) ) \wedge 
-(\neg(c \longrightarrow g))$, or if the circumstances do not imply the act or the goal. The insight
+(\neg(c \longrightarrow g))$, or if the circumstances imply neither the act nor the goal. The insight
 that the FUL does not apply to badly-formed maxims has philosophical value and serves as evidence 
-of the potential of computational ethics. In the next section, I explain and explore this insight using 
+of the potential of computational ethics. In the next section, I explore this insight using 
 Kantian literature. In the following section, I demonstrate the philosophical implications of well-formed
@@
 To question a law arbitrarily is to not regard it as a law at all. This kind of questioning amounts to 
-questioning the will's authority over itself, but this is impossible. The will definitionally has authority 
-over itself, for that is what it is to be a will.
+questioning the will's authority over itself, but this is impossible.\footnote{Recall from Section \ref{kantianethics} 
+that \citet{velleman} presents this argument for the inescapability of practical reason.} The will 
+definitionally has authority over itself, for that is what it is to be a will.
 
@@
 ``When dancing, I should just dance for the sake of dancing.'' While this maxim appears to be badly-formed (the 
-circumstance ``dancing'' implies the act and goal of dancing), it is a question that practical reasoners 
-do ask. I argue that the correct interpretation of this maxim is no longer a badly-formed maxim.
+circumstance ``dancing'' implies the act and goal of dancing), it is one that practical reasoners 
+do consider. I argue that the correct interpretation of this maxim is no longer a badly-formed maxim.
 
@@
 philosophical weight. The debate between self-doubt and self-respect originates in epistemology, which 
-values doubting your beliefs but also rationally requires that you believe that you are not mistaken 
+values questioning your beliefs but also rationally requires that you believe that you are not mistaken 
 (else you should update your beliefs). I present a parallel tension between self-doubt and self-respect
@@
 
-Computational ethics is at its infancy. Theorem provers are only now beginning to make headway in 
+Computational ethics is in its infancy. Theorem provers are only now beginning to make headway in 
 mathematics \citep{buzzardvideo}, even though theorem provers were first invented in the 1960's \citep{historyofITP}. 
@@
 In Sections \ref{AIethics} and \ref{computationalethics}, I outline how automated ethics can guide
-artificial agents and philosophers respectively. This raises a natural question: can automated
+AI and philosophers respectively. This raises a natural question: can automated
 ethics guide all human beings, not just academic philosophers, as we navigate the world and face ethical
@@
 behavior requires not only a certain action, but also a certain disposition towards the action, so it seems
-difficult for an AI agent to truly behave virtuously.}
+difficult for AI to truly behave virtuously.}
 
@@
 morally consequential decisions. Automated agents may be incapable of moral motivation, but automated agents that mimic
-moral behavior are better than agents that ignore morality entirely. AI agents are navigating a world 
-inhabited by human beings, and their decisions impact us. Insofar as AI will operate in human society, 
+moral behavior are better than agents that ignore morality entirely. AI is navigating a world 
+inhabited by human beings, and its decisions impact us. Insofar as AI will operate in human society, 
 the behavior of such AI should mimic the behavior of an ethical human being for our sakes, so that we 
@@
 the choices that an agent is faced with. As I argue in Section \ref{AIethics}, determining this potential maxim is a challenge for both human
-and automated reasoners. Kant claims that determining an agent's potential maxim is so difficult because a maxim is their
-prsonal understanding of their principle of action, and so we may never be able 
+and automated reasoners. Kant claims that determining an agent's potential maxim is difficult because a maxim is their
+personal understanding of their principle of action, so we may never be able 
 to know if the morally worthy action has been performed \cite[345]{oneilluniversallaws}. Reasoners are faced with
@@
 I argued that, before my system can be used in practice, it must be paired with an input parser that can
-translate choices that an automated agent faces into maxims into a logic that my system can
+translate choices that an AI system faces into maxims into a logic that my system can
 evaluate. This need follows from the difficulty in mapping a potential action
@@
 that ``the Kantian test is therefore as useless for machines as it is for anyone who does
-not already know what to do'' \citep[8]{tafani}.\footnote{Translated using Google Translate.} 
+not already know what to do'' \citep[8]{tafani}.\footnote{Translated from Italian to English using Google Translate.} 
 Understanding the categorical imperative test as a reminder
@@
 \centering
-\includegraphics[scale=0.47]{inputparser.png}
+\includegraphics[scale=0.19]{inputparser.jpeg}
 \caption{A refined version of Figure \ref{fig:AIengine} in which the input parser learns from a database
@@
 a fuzzy prediction into a provable, rigorous moral judgement. This rigorous moral judgement
-could in turn be fed into the database of maxims to make the intput parser smarter. One example of 
+could in turn be fed into the database of maxims to make the input parser smarter. One example of 
 this kind of system is shown in Figure \ref{fig:inputparser}. The combination of 
@@
 dream a reality did not exist. Today, automated ethics is a growing field, spurred in part by the 
-need for ethically intelligent AI agents. Tolmeijer et al. surveyed the state of the field of 
+need for ethically intelligent AI. Tolmeijer et al. surveyed the state of the field of 
 machine ethics \citep{mesurvey} and characterized implementations in automated ethics by (1) the choice 
@@
 philosophically mature judgements about complex moral dilemmas. This work is one step towards building 
-morally sophisticated artifical agents.
-
-The idea of fully automated artificial agents navigating the world without human supervision
+morally sophisticated artifical intelligence.
+
+The idea of fully automated artificial intelligence navigating the world without human supervision
 may be terrifying, but progress in AI indicates that such a future is likely closer than we think. 
@@
 if AI developers and computer scientists ignore it, then they will be building machines that make decisions
-based on some set of unknown, implicit ethical values. Countless examples, from the Alleghany family services screening
-algorithm that is biased against poor families to search algorithms that associate black-sounding names
+based on some set of unknown, implicit ethical values. Countless examples, from the Allegheny Family Screening Tool
+that is biased against poor families to search algorithms that associate black-sounding names
 with crime, demonstrate that such implicit ethics usually codifies the biases, prejudices, and moral
@@
 %:%193=147%:%
-%:%202=149%:%
-%:%214=151%:%
+%:%194=148%:%
+%:%203=150%:%
 %:%215=152%:%
@@
 %:%224=161%:%
-%:%233=163%:%
-%:%245=165%:%
+%:%225=162%:%
+%:%234=164%:%
 %:%246=166%:%
@@
 %:%438=358%:%
-%:%447=361%:%
-%:%459=363%:%
-%:%460=364%:%
+%:%439=359%:%
+%:%440=360%:%
+%:%449=363%:%
 %:%461=365%:%
@@
 %:%524=428%:%
-%:%533=430%:%
-%:%545=432%:%
-%:%546=433%:%
+%:%525=429%:%
+%:%526=430%:%
+%:%535=432%:%
 %:%547=434%:%
@@
 %:%621=508%:%
-%:%630=511%:%
-%:%642=514%:%
-%:%643=515%:%
+%:%622=509%:%
+%:%623=510%:%
+%:%632=513%:%
 %:%644=516%:%
@@
 %:%761=633%:%
-%:%764=635%:%
-%:%765=636%:%
+%:%762=634%:%
+%:%763=635%:%
 %:%766=637%:%
@@
 %:%769=640%:%
-%:%772=641%:%
-%:%773=642%:%
+%:%770=641%:%
+%:%771=642%:%
 %:%774=643%:%
@@
 %:%787=656%:%
-%:%796=660%:%
-%:%808=662%:%
-%:%809=663%:%
+%:%788=657%:%
+%:%789=658%:%
+%:%798=662%:%
 %:%810=664%:%
@@
 %:%859=713%:%
-%:%868=715%:%
-%:%880=717%:%
-%:%881=718%:%
+%:%860=714%:%
+%:%861=715%:%
+%:%870=717%:%
 %:%882=719%:%
@@
 %:%918=755%:%
+%:%919=756%:%
+%:%920=757%:%

### 2022-03-24 paper/output/document/thesis_5_discussion.tex
submit

@@
 
+\medskip
+
 In \emph{Universal Laws and Ends In Themselves}, O'Neill argues against the existence of an algorithm for
@@
 
+\medskip
+
 Another challenge for automated Kantian ethics is that the FUL test requires that
@@
 \noindent \textbf{Prior Moral Knowledge}
+
+\medskip
 
@@
 
-This work is an early proof-of-concept. It demonstrates the potential of top-down, logic programming 
+This work is an early proof-of-concept. It demonstrates the potential of top-down
 approaches to automated ethics and shows that it is possible to faithfully automate an ethical theory as
 complex as Kantian ethics. There are open questions that must be resolved before a system like this 
-could be used in practice, but this project demonstrates that these questions are within closer reach
+could be used in practice, but this project demonstrates that answers to these questions are within closer reach
 than they may seem. Automated ethics does not need to limit itself to simple, flattened versions of 
@@
 %:%763=635%:%
-%:%766=637%:%
-%:%767=638%:%
-%:%768=639%:%
-%:%769=640%:%
-%:%770=641%:%
-%:%771=642%:%
-%:%774=643%:%
-%:%775=644%:%
-%:%776=645%:%
-%:%777=646%:%
-%:%778=647%:%
-%:%779=648%:%
+%:%764=636%:%
+%:%765=637%:%
+%:%766=638%:%
+%:%767=639%:%
+%:%768=640%:%
+%:%769=641%:%
+%:%772=643%:%
+%:%773=644%:%
+%:%774=645%:%
+%:%775=646%:%
+%:%776=647%:%
+%:%777=648%:%
 %:%780=649%:%
@@
 %:%789=658%:%
-%:%798=662%:%
-%:%810=664%:%
-%:%811=665%:%
-%:%812=666%:%
-%:%813=667%:%
-%:%814=668%:%
-%:%815=669%:%
+%:%790=659%:%
+%:%791=660%:%
+%:%792=661%:%
+%:%793=662%:%
+%:%794=663%:%
+%:%795=664%:%
+%:%804=668%:%
 %:%816=670%:%
@@
 %:%861=715%:%
-%:%870=717%:%
-%:%882=719%:%
-%:%883=720%:%
-%:%884=721%:%
-%:%885=722%:%
-%:%886=723%:%
-%:%887=724%:%
+%:%862=716%:%
+%:%863=717%:%
+%:%864=718%:%
+%:%865=719%:%
+%:%866=720%:%
+%:%867=721%:%
+%:%876=723%:%
 %:%888=725%:%
@@
 %:%920=757%:%
+%:%921=758%:%
+%:%922=759%:%
+%:%923=760%:%
+%:%924=761%:%
+%:%925=762%:%
+%:%926=763%:%
